### 2018-08-20 lineages_18Q3.Rmd
add Rmd

---
title: "Lineage Analysis of CRISPR and shRNA Screens"
author: "Sally Claridge"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    theme: cerulean
    number_sections: true
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: true
    code_folding: hide
---

Analysis of the Broad's Avana CRISPR (Broad Institute Cancer Dependency Map 2018, Meyers et al. 2017) and the Broad and Dana-Farber Cancer Institite's Achilles shRNA (MacFarland et al. 2018, Data Science 2018).

The Avana screen produced results using [CERES](https://depmap.org/ceres/) (Meyers et al. 2017) ([GitHub](https://github.com/cancerdatasci/ceres)), which generates gene dependency scores from sgRNA depletion scores from gene essentiality screens and eliminates bias arising from the effect of copy number variation on Cas9 DNA cleavage. The lower the CERES score, the higher the likelihood that the gene is essential in the associated cell line. Scores are scaled per cell line such that a score of 0 is the median effect of nonessential genes and -1 is the median effect of common core essential genes.

In a previous version of the shRNA screen, DEMETER ([GitHub](https://github.com/cancerdatasci/demeter)) was used to compute a dependency score for each gene by using the depletion values from each shRNA to infer the effect of target knockdown (on-target) and of expressing a given miRNA seed (off-target) in each cell line. More negative values indicate increased dependency, while more positive values indicate lower dependency. Zero represents the avergae dependency across all cell lines.

In the new data release, [DEMETER2](https://depmap.org/R2-D2/) ([GitHub repository](https://github.com/cancerdatasci/demeter2)), developed by McFarland et al. (2018) was used to analyze the Achilles screen. DEMETER2 expands on DEMETER by including parameters for cell-line-specific screen effects and noisy data, correcting for global differences in shRNA levels across cell lines, pooling data acorss cell lines via hierarchical modeling, and using Bayesian inference to compute uncertainty estimates. Now, a score of zero represents no dependency.

All annotation files (copy number, mutation status, and gene expression) (Consortium and Consortium 2015, Barretina et al. 2012) were downloaded from the [DepMap Data Portal](https://depmap.org/portal/download/).

# Set up

--------------------------------------------------------------------------------

```{r setup, include=FALSE}
set.seed(1234)
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

num_cores <- parallel::detectCores()
options(mc.cores = num_cores)
```

Load libraries.
```{r}
library(NMF)
library(ggsignif)
library(ggpubr)
library(rowr)
library(data.table)
library(CePa)
library(plyr)
library(tidyverse)
library(magrittr)
library(ggrepel)
library(matrixStats)
library(parallel)
library(kableExtra)
library(gridExtra)
library(broom)
library(glmnet)
library(devtools)
library(reshape2)
library(caret)
library(bsselectR)
library(ComplexHeatmap)
library(circlize)
```

## Functions {.tabset .tabset-fade .tabset-pills}

### Significance thresholding

```{r}
adj_signif <- function(df) {
  # Takes df from compare_means and creates a signif code column for adjusted p-vals
  df$p.signif <- ifelse(df$p.signif == "ns", NA, df$p.signif)
  df$p.signif.adj <- ifelse(df$p.adj <= 0.0001, "****",
                     ifelse(df$p.adj <= 0.001, "***",
                     ifelse(df$p.adj <= 0.01, "**",
                     ifelse(df$p.adj <= 0.05, "*", NA))))
  df$p.short <- formatC(df$p, format = "g", digits =  2)
  df$p.adj.short <- formatC(df$p.adj, format = "g", digits =  2)

  return(df)
}
```

### Make CRISPR grobs

```{r}
make_CRISPRgrob <- function(g) {

  gene <- filter(crispr_data, Hugo_Symbol == g)

  # Mutation status
  crispr_color <- as.character(gene$Color)
  names(crispr_color) <- gene$Mutation_Status
  sig <- filter(crispr_signif, Hugo_Symbol == g)
  plot_mut <- ggplot(data = gene, aes(x = Mutation_Status, y = Score, color = Mutation_Status)) +
    geom_boxplot(outlier.shape = NA) +
    geom_jitter(alpha = 0.3, size = 0.7, position = position_jitter(w = 0.05)) +
    scale_color_manual(values = crispr_color) +
    geom_hline(yintercept = 0, linetype = 2, lwd = 0.3) +
    theme_light() +
    theme(legend.position = "none") +
    labs(x = paste0(g, " Mutation Status"), y = "CERES Score",
         title = "Mutation Status",
         subtitle = paste0("Wilcoxon test:\n\tBH-corrected p-value: ", sig$p.adj.short, "\n\tUncorrected p-value: ", sig$p.short))

  # Copy number
  lo_cn <- range(gene$Copy_Number[!is.na(gene$Copy_Number)])[1]
  hi_cn <- range(gene$Copy_Number[!is.na(gene$Copy_Number)])[2]
  mid_cn <- (hi_cn - lo_cn) / 2
  plot_cn <- ggplot(data = gene, aes(x = Copy_Number, y = Score, color = Mutation_Status)) +
    geom_point(size = 0.5, alpha = 0.5) +
    geom_smooth(method = "lm", size = 0.5) +
    geom_hline(yintercept = 0, linetype = 2, lwd = 0.3) +
    scale_color_manual(values = crispr_color) +
    stat_cor(method = "pearson", show.legend = FALSE, label.x = c((lo_cn + mid_cn) / 2, (hi_cn - mid_cn) / 2 + mid_cn), label.y = max(gene$Score)) +
    theme(legend.position = "none") +
    labs(y = "CERES Score", color = "Mutation Status",
         x = paste0(g, " Copy number"), title = "Copy Number",
         subtitle = "r: Pearson correlation coeffcient")

  # Gene expression
  lo_ge <- range(gene$RPKM[!is.na(gene$RPKM)])[1]
  hi_ge <- range(gene$RPKM[!is.na(gene$RPKM)])[2]
  mid_ge <- (hi_ge - lo_ge) / 2
  plot_ge <- ggplot(data = gene, aes(x = RPKM, y = Score, color = Mutation_Status)) +
    geom_point(size = 0.5, alpha = 0.5) +
    geom_smooth(method = "lm", size = 0.5) +
    geom_hline(yintercept = 0, linetype = 2, lwd = 0.3) +
    scale_color_manual(values = crispr_color) +
    stat_cor(method = "pearson", show.legend = FALSE, label.x = c((lo_ge + mid_ge) / 2, (hi_ge - mid_ge) / 2 + mid_ge), label.y = max(gene$Score)) +
    theme(legend.position = "none") +
    labs(y = "CERES Score", color = "Mutation Status",
         x = paste0(g, " Gene Expression (RPKM)"),
         title = "Gene Expression",
         subtitle = "r: Pearson correlation coeffcient")

  # Cell line lineage
  plot_lin <- ggplot(data = gene, aes(x = lineage_name, y = Score, color = Mutation_Status)) +
    geom_point(alpha = 0.5) +
    scale_color_manual(values = crispr_color) +
    geom_hline(yintercept = 0, linetype = 2, lwd = 0.3) +
    scale_y_continuous(sec.axis = sec_axis(~ .)) +
    coord_flip() +
    theme(legend.position = "none") +
    labs(y = "CERES Score", x = "Cell Line Lineage",
         color = "Mutation Status", title = g)

  # Arrange plots
  plot <- ggarrange(ggarrange(plot_lin, nrow = 1, labels = c("A")),
                    ggarrange(plot_mut, plot_cn, plot_ge, nrow = 3,
                              labels = c("B", "C", "D"), heights = c(2, 3, 3)),
                    font.label = list(size = 30, face = "bold"),
                    nrow = 1, ncol = 2, widths = c(3, 2))
  return(plot)
}
```

### Make lineage plot

```{r}
make_CRISPRlinplot <- function(g) {
  gene <- filter(crispr_data, Hugo_Symbol == g)
  sig <- filter(crispr_signif_lineage, Hugo_Symbol == g)
  gene <- merge(gene, sig, by = c("Hugo_Symbol", "lineage_name"))
  gene <- mutate(gene, lineage_name = reorder(lineage_name, p, mean))
  crispr_color <- as.character(gene$Color)
  names(crispr_color) <- gene$Mutation_Status
  score_range <- abs(range(gene$Score)[2] - range(gene$Score)[1])
  round_accuracy <- ifelse(score_range <= 2, 0.25,
                           ifelse(score_range <= 3, 0.5, 1.0))

  plot <- ggplot(data = gene, aes(x = lineage_name, y = Score)) +
    geom_point(alpha = 0.5, mapping = aes(color = Mutation_Status)) +
    scale_color_manual(values = crispr_color) +
    coord_cartesian(y = c(min(gene$Score), round_any(x = max(gene$Score), accuracy = round_accuracy, f = ceiling))) +
    geom_signif(data = gene, mapping = aes(xmin = lineage_name, xmax = lineage_name, annotations = paste(p.short, "\n", p.adj.short), y_position = max(gene$Score)), manual = TRUE, tip_length   = 0, size = 0, textsize = 3) +
    theme(legend.position = "top", axis.text.x = element_text(angle = 70, hjust = 1, size = 10)) +
    labs(y = "CERES Score",
         x = "Lineage",
         color = "Mutation Status",
         title = paste0(g, ": CERES score by cell line lineage"),
         subtitle = "Lineages sorted by increasing p-value; labels indicate unadjusted p-value / BH-corrected p-value.")
  return(plot)
}
```

## Cell line converter

This comprehensive cancer cell line information curated by Daniel Charytonowicz.
```{r}
ccl_converter <- read.delim("./../data_munging/danielc_cell_line_database_completed_extra_SE.tsv", sep = "\t", row.names = NULL, header = TRUE)
colnames(ccl_converter)[4] <- "CCLE_Name"
colnames(ccl_converter)[10] <- "Broad_ID"
```

## Cell line metadata

```{r}
ccl_info <- read.delim("./data_munging/DepMap-2018q3-celllines.csv", sep = ",", header = TRUE, na.strings = c("", NA))
ccl_info$Primary.Disease <- gsub("\\\\", "", ccl_info$Primary.Disease)
ccl_info$Primary.Disease <- gsub("Ewings", "Ewing's", ccl_info$Primary.Disease)

crispr_meta <- read.delim("./data_munging/sample_info_18Q3_crispr.csv", sep = ",", header = TRUE, na.strings = c("", NA))
colnames(crispr_meta)[7] <- "CCLE_Name"

shrna_meta <- read.delim("./data_munging/sample_info_18Q3_shrna.csv", sep = ",", header = TRUE, na.strings = c("", NA))
colnames(shrna_meta)[1] <- "CCLE_Name"
```

```{r}
dan_test <- select(ccl_converter, CCLE_Name, Broad_ID, cell_line_name)
dan_test <- dan_test[-which(dan_test$CCLE_Name == ""), ]
ccl_test <- select(ccl_info, CCLE_Name, Broad_ID)

test <- merge(ccl_test, dan_test, by = "CCLE_Name", all = TRUE, suffixes = c("_DepMap", "_Daniel"))
test$BroadIDs_match <- ifelse(as.character(test$Broad_ID_DepMap) == as.character(test$Broad_ID_Daniel), TRUE, FALSE)
```

## MAF file

For mutation calling, get paired gene name and cell line fields in a data frame. For this analysis, we don't care about how many mutations there are per gene or what type of mutations there are, so I didn't save more information. I took unique gene-cell line combinations since we only cared about mutation presence/absence. Add a `Mutation_Status` column denoting all entries in MAF files as mutations present in the associated cell lines.
```{r}
maf_raw <- read.delim("./data_munging/CCLE_DepMap_18q3_maf_20180718.txt.gz", header = TRUE, sep = "\t")

# Remove silent mutations
maf_df <- maf_raw[maf_raw$Variant_Classification != "Silent",]

# Select columns
maf_df <- unique(subset(maf_raw, select = c("Hugo_Symbol", "Tumor_Sample_Barcode", "Broad_ID")))
colnames(maf_df)[2] <- "CCLE_Name"
# Add Mutation_Status column
maf_df$Mutation_Status <- "Mutant"

# MAF summary table
maf_summ <- maf_raw[, c("Variant_Classification", "isDeleterious")] %>% group_by(Variant_Classification, isDeleterious) %>% tally()
maf_summ$percent <- maf_summ$n / sum(maf_summ$n) * 100
knitr::kable(maf_summ, caption = "Distribution of variant classifications in the MAF file") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

## Copy number file

```{r, eval=FALSE}
cn <- read.delim("./data_munging/public_18Q3_gene_cn.csv.gz", sep = ",", check.names = FALSE, header = TRUE)

# Convert log2 ratios (log2(CN/2)) to CN
cn[2:ncol(cn)] <- lapply(cn[2:ncol(cn)], function(x) 2 * (2 ^ x))

# Remove Entrez gene IDs from colnames
colnames(cn) <- gsub(" .*", "", colnames(cn))
colnames(cn)[1] <- "Broad_ID"

# Melt
cn_melt <- melt(data = cn, id.vars = "Broad_ID", measure.vars = colnames(cn[2:ncol(cn)]))
colnames(cn_melt) <- c("Broad_ID", "Hugo_Symbol", "Copy_Number")

saveRDS(cn_melt, "./data_munging/rds/cn_melt_18Q3.rds", compress = "xz")
```

```{r}
cn_melt <- readRDS("./data_munging/rds/cn_melt_18Q3.rds")
```

## Gene expression file

Gene expression data (Reads Per Kilobase of transcript, per Million mapped reads, RPKM).
```{r}
ge <- read.delim("./../CCLE_DepMap_18q3_RNAseq_RPKM_20180718.gct.gz", skip = 2, header = TRUE, sep = "\t", check.names = FALSE)
```

```{r, eval=FALSE}
# Edit columns
ge$Name <- NULL
colnames(ge)[1] <- "Hugo_Symbol"

# Melt
ge_melt <- melt(data = ge, id.vars = "Hugo_Symbol", measure.vars = colnames(ge[2:ncol(ge)]))
colnames(ge_melt)[3] <- "RPKM"
## Split variable column
ge_melt <- with(ge_melt, cbind(Hugo_Symbol, colsplit(variable, pattern = " ", names = c("CCLE_Name", "Broad_ID")), RPKM))
## Remove parentheses around Broad IDs
ge_melt$Broad_ID <- gsub("\\(|\\)", "", ge_melt$Broad_ID)

saveRDS(ge_melt, "./data_munging/rds/ge_melt_18Q3.rds", compress = "xz")
```

```{r}
ge_melt <- readRDS("./data_munging/rds/ge_melt_18Q3.rds")
```

## CRISPR data and annotations

The latest CRISPR CERES score data (18Q3, August 2018) was pulled from the [DepMap Data Portal](https://depmap.org/portal/download/) (Broad Institute Cancer Dependency Map 2018, Meyers et al. 2017).
```{r, eval=TRUE}
crispr <- read.delim("././data_munging/gene_effect_18Q3.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
# Remove Entrez gene IDs from colnames
colnames(crispr) <- gsub(" .*", "", colnames(crispr))
```

Merge annotation data:
```{r, eval=FALSE}
# Melt CRISPR dataset for merging
crispr_melt <- melt(crispr, id.vars = "Broad_ID", measure.vars = colnames(crispr)[2:ncol(crispr)])
colnames(crispr_melt) <- c("Broad_ID", "Hugo_Symbol", "Score")

# Merge cell line metadata
crispr_melt <- merge(crispr_melt, ccl_info, by = "Broad_ID", all.x = TRUE)
crispr_melt <- merge(crispr_melt, crispr_meta, by = c("CCLE_Name", "Broad_ID"), all.x = TRUE)

# Merge mutation annotations
crispr_muts <- merge(crispr_melt, maf_df, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
crispr_muts <- crispr_muts %>% mutate(Mutation_Status = if_else(is.na(Mutation_Status), "Wildtype", Mutation_Status))
crispr_muts$Hugo_Symbol <- factor(crispr_muts$Hugo_Symbol)

# Summarize number of mutant and wildtype cell lines
crispr_muts_summ <- crispr_muts %>% group_by(Hugo_Symbol) %>%
  summarize(N_Wildtype = sum(Mutation_Status == "Wildtype"),
            N_Mutant = sum(Mutation_Status == "Mutant"))

# Merge test results back into full dataset, which restores information lost in the summarization
crispr_data <- merge(crispr_muts_summ, crispr_muts, by = "Hugo_Symbol")

# Add Color column
crispr_data$Color <- ifelse(crispr_data$Mutation_Status == "Wildtype", "cyan3", "darkorchid")
crispr_data$Color <- factor(crispr_data$Color)

# Cell line lineages
crispr_data <- merge(crispr_data, ccl_converter, by = c("CCLE_Name", "Broad_ID"), all.x = TRUE)
levels(crispr_data$lineage_name) <- sort(levels(crispr_data$lineage_name), decreasing = TRUE)

# Copy number
crispr_data <- merge(crispr_data, cn_melt, by = c("Hugo_Symbol", "Broad_ID"), all.x = TRUE)

# Gene expression (RPKM)
ge_filt <- filter(ge_melt, Hugo_Symbol %in% unique(crispr_data$Hugo_Symbol))
crispr_data <- merge(crispr_data, ge_filt, by = c("Hugo_Symbol", "Broad_ID", "CCLE_Name"), all.x = TRUE)

saveRDS(crispr_data, "./data_munging/rds/crispr_data_18Q3.rds", compress = "xz")
```

```{r}
crispr_data <- readRDS("./data_munging/rds/crispr_data_18Q3.rds")
crispr_ccl <- data.frame("Broad_ID" = crispr_data$Broad_ID)
```

## shRNA data and annotations

The Achilles shRNA DEMETER score data was pulled from the [CTD^2^ Data Portal](https://ocg.cancer.gov/programs/ctd2/data-portal) (Tsherniak et al 2017).
```{r, eval=FALSE}
shrna <- read.table("./data_munging/D2_combined_gene_dep_scores.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
colnames(shrna)[1] <- "Hugo_Symbol"
# Remove Entrez gene IDs from gene names
shrna$Hugo_Symbol <- gsub(" .*", "", shrna$Hugo_Symbol)

# Melt shRNA dataset for merging
shrna_melt <- melt(shrna , id.vars = "Hugo_Symbol", measure.vars = colnames(shrna)[2:ncol(shrna)])
colnames(shrna_melt) <- c("Hugo_Symbol", "CCLE_Name", "Score")
shrna_melt <- drop_na(shrna_melt)
```

Merge annotation data:
```{r, eval=FALSE}
# Merge cell line metadata
shrna_melt <- merge(shrna_melt, ccl_info, by = "CCLE_Name", all.x = TRUE)
shrna_melt <- merge(shrna_melt, shrna_meta, by = "CCLE_Name", all.x = TRUE)

# Merge mutation annotations
shrna_muts <- merge(shrna_melt, maf_df, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
shrna_muts <- shrna_muts %>% mutate(Mutation_Status = if_else(is.na(Mutation_Status), "Wildtype", Mutation_Status))
shrna_muts$Hugo_Symbol <- factor(shrna_muts$Hugo_Symbol)

# Summarize number of mutant and wildtype cell lines
shrna_muts_summ <- shrna_muts %>% group_by(Hugo_Symbol) %>%
  summarize(N_Wildtype = sum(Mutation_Status == "Wildtype"),
            N_Mutant = sum(Mutation_Status == "Mutant"))

# Merge test results back into full dataset, which restores information lost in the summarization
shrna_data <- merge(shrna_muts_summ, shrna_muts, by = "Hugo_Symbol")

# Add Color column
shrna_data$Color <- ifelse(shrna_data$Mutation_Status == "Wildtype", "cyan3", "darkorchid")
shrna_data$Color <- factor(shrna_data$Color)

# Cell line lineages
shrna_data <- merge(shrna_data, ccl_converter, by = c("CCLE_Name", "Broad_ID"), all.x = TRUE)
levels(shrna_data$lineage_name) <- sort(levels(shrna_data$lineage_name), decreasing = TRUE)

# Copy number
shrna_data <- merge(shrna_data, cn_melt, by = c("Hugo_Symbol", "Broad_ID"), all.x = TRUE)

# Gene expression (RPKM)
ge_filt <- filter(ge_melt, Hugo_Symbol %in% unique(shrna_data$Hugo_Symbol))
shrna_data <- merge(shrna_data, ge_filt, by = c("Hugo_Symbol", "Broad_ID", "CCLE_Name"), all.x = TRUE)

saveRDS(shrna_data, "./data_munging/rds/shrna_data_18Q3.rds", compress = "xz")
```

```{r}
shrna_data <- readRDS("./data_munging/rds/shrna_data_18Q3.rds")
shrna_ccl <- data.frame("Broad_ID" = shrna_data$Broad_ID)
```

```{r, eval=FALSE}
write(union(as.character(distinct(crispr_data[which(is.na(crispr_data$lineage_name)), c("CCLE_Name", "lineage_name")])$CCLE_Name), as.character(distinct(shrna_data[which(is.na(shrna_data$lineage_name)), c("CCLE_Name", "lineage_name")])$CCLE_Name)), file = "./../../../Desktop/na_ccl_in_converter.txt")
```

# Wilcoxon tests

--------------------------------------------------------------------------------

## CRISPR

### Grouped by gene

```{r, eval=FALSE}
crispr_signif <- compare_means(Score ~ Mutation_Status, group.by = c("Hugo_Symbol"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
crispr_signif <- adj_signif(crispr_signif)
crispr_signif <- crispr_signif[order(crispr_signif$p),]
saveRDS(crispr_signif, "./data_munging/rds/crispr_signif.rds")
```

```{r}
crispr_signif <- readRDS("./data_munging/rds/crispr_signif.rds")

knitr::kable(crispr_signif[, c(1, 5, 6, 7, 8, 10)], caption = "CRISPR Screen: Wilcoxon Test Results Comparing Mutant and Wildtype Cell Lines (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
```

### Grouped by gene and lineage

```{r, eval=FALSE}
crispr_signif_lineage <- compare_means(Score ~ Mutation_Status, group.by = c("Hugo_Symbol", "lineage_name"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
crispr_signif_lineage <- adj_signif(crispr_signif_lineage)
crispr_signif_lineage <- mutate(crispr_signif_lineage, lineage_name = reorder(lineage_name, p.adj, mean))
saveRDS(crispr_signif_lineage, "./data_munging/rds/crispr_signif_lineage.rds")
```

```{r}
crispr_signif_lineage <- readRDS("./data_munging/rds/crispr_signif_lineage.rds")
```

## shRNA

### Grouped by gene

```{r, eval=FALSE}
shrna_signif <- compare_means(Score ~ Mutation_Status, group.by = c("Hugo_Symbol"), data = shrna_data, method = "wilcox.test", p.adjust.method = "BH")
shrna_signif <- adj_signif(shrna_signif)
shrna_signif <- shrna_signif[order(shrna_signif$p),]
saveRDS(shrna_signif, "./data_munging/rds/shrna_signif.rds")
```

```{r}
shrna_signif <- readRDS("./data_munging/rds/shrna_signif.rds")

knitr::kable(shrna_signif[, c(1, 5, 6, 7, 8, 10)], caption = "shRNA Screen: Wilcoxon Test Results Comparing Mutant and Wildtype Cell Lines (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
```

### Grouped by gene and lineage

```{r, eval=FALSE}
shrna_signif_lineage <- compare_means(Score ~ Mutation_Status, group.by = c("Hugo_Symbol", "lineage_name"), data = shrna_data, method = "wilcox.test", p.adjust.method = "BH")
shrna_signif_lineage <- adj_signif(shrna_signif_lineage)
shrna_signif_lineage <- mutate(shrna_signif_lineage, lineage_name = reorder(lineage_name, p.adj, mean))
saveRDS(shrna_signif_lineage, "./data_munging/rds/shrna_signif_lineage.rds")
```

```{r, eval=FALSE}
shrna_signif_lineage <- readRDS("./data_munging/rds/shrna_signif_lineage.rds")
```

# Heatmaps

--------------------------------------------------------------------------------

## CRISPR

```{r, eval=FALSE}
# Set up heatmap data
chm_data <- t(crispr)
colnames(chm_data) <- chm_data[1, ]
chm_data <- chm_data[-1, ]
chm_cols <- colnames(chm_data)
chm_data <- apply(chm_data, 2, as.double)
chm_data <- apply(chm_data, 2, function(x) (x - mean(x)) / var(x))
colnames(chm_data) <- chm_cols

# Metadata anotation dataframe
chm_annot <- merge(merge(data.frame("Broad_ID" = crispr$Broad_ID), crispr_meta[, c("Broad_ID", "cell_line_SSMD", "cas9_activity", "culture_type", "primary_tissue")], by = "Broad_ID", all.x = TRUE), ccl_info[, c("Broad_ID", "Primary.Disease", "Gender", "Source")], by = "Broad_ID", all.x = TRUE)
rownames(chm_annot) <- chm_annot$Broad_ID
chm_annot$Broad_ID <- NULL
colnames(chm_annot) <- c("Cell_Line_SSMD", "Cas9_Activity", "Culture_Type", "Primary_Tissue", "Primary_Disease", "Gender", "Source")
chm_annot$Cell_Line_SSMD <- as.numeric(chm_annot$Cell_Line_SSMD)
chm_annot$Cas9_Activity <- as.numeric(chm_annot$Cas9_Activity)

# Make full grid for genomic features
crispr_grid_ccls <- unique(crispr_data$Broad_ID)
crispr_grid_genes <- unique(crispr_data$Hugo_Symbol)
crispr_grid <- expand.grid("Broad_ID" = crispr_grid_ccls, "Hugo_Symbol" = crispr_grid_genes)

# Gene expression
ge_chm_grid <- merge(crispr_grid, ge_melt[, c("Hugo_Symbol", "Broad_ID", "RPKM")], by = c("Broad_ID", "Hugo_Symbol"), all.x = TRUE)
```

```{r, eval=FALSE}
chma <- HeatmapAnnotation(df = chm_annot)

chm_euc <- Heatmap(chm_data, name = "CERES Score",
        bottom_annotation = chma,
        bottom_annotation_height = unit(5, "in"),
        row_title = "Genes", column_title = "Cancer Cell Lines (Broad IDs)",
        col = colorRamp2(c(-15, 0, 5), c("purple4", "white", "seagreen4")),
        column_title_gp = gpar(fontsize = 60, fontface = "bold"),
        show_column_names = FALSE,
        row_title_gp = gpar(fontsize = 60, fontface = "bold"),
        show_row_names = FALSE,
        row_dend_reorder = TRUE,
        column_dend_reorder = TRUE,
        clustering_distance_rows = "euclidean",
        clustering_distance_columns = "euclidean",
        clustering_method_rows = "complete",
        clustering_method_columns = "complete",
        column_dend_height = unit(4, "in"),
        row_dend_width = unit(4, "in"),
        width = 3)

pdf("./plots_18Q3/crispr_heatmap_euclidean.pdf", width = 100, height = 100, paper = "special") 
draw(chm_euc, heatmap_legend_side = "right", annotation_legend_side = "right")
seekViewport("annotation_Cell_Line_SSMD")
grid.text("Cell Line SSMD", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Cas9_Activity")
grid.text("Cas9 Activity", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Culture_Type")
grid.text("Culture Type", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Primary_Tissue")
grid.text("Primary Tissue", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Primary_Disease")
grid.text("Primary Disease", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Gender")
grid.text("Gender", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
seekViewport("annotation_Source")
grid.text("Source", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
dev.off()
```

# Per-gene plots

--------------------------------------------------------------------------------

## Grouped plots {.tabset .tabset-fade .tabset-pills}

### KRAS

```{r fig.height=12, fig.width=12}
make_CRISPRgrob("KRAS")
```

### TP53

```{r fig.height=12, fig.width=12}
make_CRISPRgrob("TP53")
```

### BRAF

```{r fig.height=12, fig.width=12}
make_CRISPRgrob("BRAF")
```

### NRAS

```{r fig.height=12, fig.width=12}
make_CRISPRgrob("NRAS")
```

## Sorted lineage plots {.tabset .tabset-fade .tabset-pills}

### KRAS

```{r fig.height=10, fig.width=15}
make_CRISPRlinplot("KRAS")
```

### TP53

```{r fig.height=10, fig.width=15}
make_CRISPRlinplot("TP53")
```

### BRAF

```{r fig.height=10, fig.width=15}
make_CRISPRlinplot("BRAF")
```

### NRAS

```{r fig.height=10, fig.width=15}
make_CRISPRlinplot("NRAS")
```

# References

--------------------------------------------------------------------------------

Barretina, J., Caponigro, G., Stransky, N., Venkatesan, K., Margolin, A. A., Kim, S., … Garraway, L. A. (2012). The Cancer Cell Line Encyclopedia enables predictive modelling of anticancer drug sensitivity. Nature, 483(7391), 603–607. https://doi.org/10.1038/nature11003

Broad Institute Cancer Dependency Map; Cancer Data Science (2018): Cancer Dependency Map, CRISPR Avana dataset 18Q3 (Avana_public_18Q3). figshare. Fileset. doi:10.6084/m9.figshare.6931364.v1

Consortium, T. C. C. L. E., & Consortium, T. G. of D. S. in C. (2015). Pharmacogenomic agreement between two cancer cell line data sets. Nature, 528(7580), 84–87. https://doi.org/10.1038/nature15736

Data Science, Cancer (2018): DEMETER2 data. figshare. Fileset. doi:10.6084/m9.figshare.6025238.v2

Doench, J. G., Fusi, N., Sullender, M., Hegde, M., Vaimberg, E. W., Donovan, K. F., … Root, D. E. (2016). Optimized sgRNA design to maximize activity and minimize off-target effects of CRISPR-Cas9. Nature Biotechnology, 34(2), 184–191. https://doi.org/10.1038/nbt.3437

Meyers, R. M., Bryan, J. G., McFarland, J. M., Weir, B. A., Sizemore, A. E., Xu, H., … Tsherniak, A. (2017). Computational correction of copy-number effect improves specificity of CRISPR-Cas9 essentiality screens in cancer cells. Nature Genetics, 49(12), 1779–1784. https://doi.org/10.1038/ng.3984

McFarland, J. M., Ho, Z. V., Kugener, G., Dempster, J. M., Montgomery, P. G., Bryan, J. G., … Tsherniak, A. (2018). Improved estimation of cancer dependencies from large-scale RNAi screens using model-based normalization and data integration. https://doi.org/10.1101/305656

# Session information

--------------------------------------------------------------------------------

```{r}
print(sessionInfo())
```

### 2018-08-20 lineages_18Q3.Rmd

@@
 ```{r}
-ccl_converter <- read.delim("./../data_munging/danielc_cell_line_database_completed_extra_SE.tsv", sep = "\t", row.names = NULL, header = TRUE)
+ccl_converter <- read.delim("./data_munging/danielc_cell_line_database_completed_extra_SE.tsv", sep = "\t", row.names = NULL, header = TRUE)
 colnames(ccl_converter)[4] <- "CCLE_Name"
@@
 
-saveRDS(ge_melt, "./data_munging/rds/ge_melt_18Q3.rds", compress = "xz")
+saveRDS(ge_melt, "./../ge_melt_18Q3.rds", compress = "xz")
 ```
@@
 ```{r}
-ge_melt <- readRDS("./data_munging/rds/ge_melt_18Q3.rds")
+ge_melt <- readRDS("./../ge_melt_18Q3.rds")
 ```
@@
 ```{r, eval=TRUE}
-crispr <- read.delim("././data_munging/gene_effect_18Q3.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
+crispr <- read.delim("./data_munging/gene_effect_18Q3.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
 # Remove Entrez gene IDs from colnames
@@
 
-saveRDS(shrna_data, "./data_munging/rds/shrna_data_18Q3.rds", compress = "xz")
+saveRDS(shrna_data, "./../shrna_data_18Q3.rds", compress = "xz")
 ```
@@
 ```{r}
-shrna_data <- readRDS("./data_munging/rds/shrna_data_18Q3.rds")
+shrna_data <- readRDS("./../shrna_data_18Q3.rds")
 shrna_ccl <- data.frame("Broad_ID" = shrna_data$Broad_ID)
@@
 ```{r, eval=FALSE}
-write(union(as.character(distinct(crispr_data[which(is.na(crispr_data$lineage_name)), c("CCLE_Name", "lineage_name")])$CCLE_Name), as.character(distinct(shrna_data[which(is.na(shrna_data$lineage_name)), c("CCLE_Name", "lineage_name")])$CCLE_Name)), file = "./../../../Desktop/na_ccl_in_converter.txt")
+write(union(as.character(distinct(crispr_data[which(is.na(crispr_data$lineage_name)), c("CCLE_Name", "lineage_name")])$CCLE_Name), as.character(distinct(shrna_data[which(is.na(shrna_data$lineage_name)), c("CCLE_Name", "lineage_name")])$CCLE_Name)), file = "./data_munging//na_ccl_in_converter.txt")
 ```
@@
 shrna_signif_lineage <- mutate(shrna_signif_lineage, lineage_name = reorder(lineage_name, p.adj, mean))
-saveRDS(shrna_signif_lineage, "./data_munging/rds/shrna_signif_lineage.rds")
+saveRDS(shrna_signif_lineage, "./../shrna_signif_lineage.rds")
 ```
@@
 ```{r, eval=FALSE}
-shrna_signif_lineage <- readRDS("./data_munging/rds/shrna_signif_lineage.rds")
+shrna_signif_lineage <- readRDS("./../shrna_signif_lineage.rds")
 ```

### 2018-08-21 lineages_18Q3.Rmd
add CRISPR heatmap code; save data matrices for heatmap

@@
          title = "Mutation Status",
-         subtitle = paste0("Wilcoxon test:\n\tBH-corrected p-value: ", sig$p.adj.short, "\n\tUncorrected p-value: ", sig$p.short))
+         subtitle = paste0("Wilcoxon test:\n- BH-corrected p-value: ", sig$p.adj.short, "\n- Uncorrected p-value: ", sig$p.short))
 
@@
 # Melt
-cn_melt <- melt(data = cn, id.vars = "Broad_ID", measure.vars = colnames(cn[2:ncol(cn)]))
-colnames(cn_melt) <- c("Broad_ID", "Hugo_Symbol", "Copy_Number")
+cn_melt <- melt(data = cn, id.vars = "Broad_ID", measure.vars = colnames(cn[2:ncol(cn)]), variable.name = "Hugo_Symbol", value.name = "Copy_Number")
 
@@
 Gene expression data (Reads Per Kilobase of transcript, per Million mapped reads, RPKM).
-```{r}
-ge <- read.delim("./../CCLE_DepMap_18q3_RNAseq_RPKM_20180718.gct.gz", skip = 2, header = TRUE, sep = "\t", check.names = FALSE)
-```
+```{r, eval=FALSE}
+ge <- read.delim("./../crispr_lineages_giant_files/CCLE_DepMap_18q3_RNAseq_RPKM_20180718.gct.gz", skip = 2, header = TRUE, sep = "\t", check.names = FALSE)
 
-```{r, eval=FALSE}
 # Edit columns
@@
 # Melt
-ge_melt <- melt(data = ge, id.vars = "Hugo_Symbol", measure.vars = colnames(ge[2:ncol(ge)]))
-colnames(ge_melt)[3] <- "RPKM"
+ge_melt <- melt(data = ge, id.vars = "Hugo_Symbol", measure.vars = colnames(ge[2:ncol(ge)]), value.name = "RPKM")
 ## Split variable column
@@
 
-saveRDS(ge_melt, "./../ge_melt_18Q3.rds", compress = "xz")
+saveRDS(ge_melt, "./../crispr_lineages_giant_files/ge_melt_18Q3.rds", compress = "xz")
 ```
@@
 ```{r}
-ge_melt <- readRDS("./../ge_melt_18Q3.rds")
+ge_melt <- readRDS("./../crispr_lineages_giant_files/ge_melt_18Q3.rds")
 ```
@@
 # Melt CRISPR dataset for merging
-crispr_melt <- melt(crispr, id.vars = "Broad_ID", measure.vars = colnames(crispr)[2:ncol(crispr)])
-colnames(crispr_melt) <- c("Broad_ID", "Hugo_Symbol", "Score")
+crispr_melt <- melt(crispr, id.vars = "Broad_ID", measure.vars = colnames(crispr)[2:ncol(crispr)], variable.name = "Hugo_Symbol", value.name = "Score")
 
@@
 # Melt shRNA dataset for merging
-shrna_melt <- melt(shrna , id.vars = "Hugo_Symbol", measure.vars = colnames(shrna)[2:ncol(shrna)])
-colnames(shrna_melt) <- c("Hugo_Symbol", "CCLE_Name", "Score")
+shrna_melt <- melt(shrna , id.vars = "Hugo_Symbol", measure.vars = colnames(shrna)[2:ncol(shrna)], variable.name = "CCLE_Name", value.name = "Score")
 shrna_melt <- drop_na(shrna_melt)
@@
 
-saveRDS(shrna_data, "./../shrna_data_18Q3.rds", compress = "xz")
+saveRDS(shrna_data, "./../crispr_lineages_giant_files/shrna_data_18Q3.rds", compress = "xz")
 ```
@@
 ```{r}
-shrna_data <- readRDS("./../shrna_data_18Q3.rds")
+shrna_data <- readRDS("./../crispr_lineages_giant_files/shrna_data_18Q3.rds")
 shrna_ccl <- data.frame("Broad_ID" = shrna_data$Broad_ID)
@@
 
-knitr::kable(crispr_signif[, c(1, 5, 6, 7, 8, 10)], caption = "CRISPR Screen: Wilcoxon Test Results Comparing Mutant and Wildtype Cell Lines (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(crispr_signif[1:100, c(1, 5, 6, 7, 8, 10)], caption = "CRISPR Screen: Wilcoxon Test Results Comparing Mutant and Wildtype Cell Lines (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
-knitr::kable(shrna_signif[, c(1, 5, 6, 7, 8, 10)], caption = "shRNA Screen: Wilcoxon Test Results Comparing Mutant and Wildtype Cell Lines (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(shrna_signif[1:100, c(1, 5, 6, 7, 8, 10)], caption = "shRNA Screen: Wilcoxon Test Results Comparing Mutant and Wildtype Cell Lines (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 shrna_signif_lineage <- mutate(shrna_signif_lineage, lineage_name = reorder(lineage_name, p.adj, mean))
-saveRDS(shrna_signif_lineage, "./../shrna_signif_lineage.rds")
+saveRDS(shrna_signif_lineage, "./../crispr_lineages_giant_files/shrna_signif_lineage.rds")
 ```
@@
 ```{r, eval=FALSE}
-shrna_signif_lineage <- readRDS("./../shrna_signif_lineage.rds")
+shrna_signif_lineage <- readRDS("./../crispr_lineages_giant_files/shrna_signif_lineage.rds")
 ```
@@
 
+Make and save heatmap data matrices:
 ```{r, eval=FALSE}
 # Set up heatmap data
-chm_data <- t(crispr)
-colnames(chm_data) <- chm_data[1, ]
-chm_data <- chm_data[-1, ]
-chm_cols <- colnames(chm_data)
-chm_data <- apply(chm_data, 2, as.double)
-chm_data <- apply(chm_data, 2, function(x) (x - mean(x)) / var(x))
-colnames(chm_data) <- chm_cols
+chm_scores <- t(crispr)
+colnames(chm_scores) <- chm_scores[1, ]
+chm_scores <- chm_scores[-1, ]
+chm_cols <- colnames(chm_scores)
+chm_scores <- apply(chm_scores, 2, as.double)
+chm_scores <- apply(chm_scores, 2, function(x) (x - mean(x)) / var(x))
+colnames(chm_scores) <- chm_cols
+saveRDS(chm_scores, "./data_munging/rds/crispr_heatmap_scores.rds")
+
+# Make full grid for genomic features
+crispr_grid_ccls <- unique(crispr_data$Broad_ID)
+crispr_grid_genes <- unique(crispr_data$Hugo_Symbol)
+crispr_grid <- expand.grid("Broad_ID" = crispr_grid_ccls, "Hugo_Symbol" = crispr_grid_genes)
+
+# Gene expression
+ge_filt <- filter(ge_melt, Hugo_Symbol %in% unique(crispr_data$Hugo_Symbol))[, c("Hugo_Symbol", "Broad_ID", "RPKM")]
+chm_ge_grid <- merge(crispr_grid, ge_filt, by = c("Broad_ID", "Hugo_Symbol"), all.x = TRUE)
+chm_ge <- reshape(chm_ge_grid, idvar = "Hugo_Symbol", timevar = "Broad_ID", direction = "wide")
+chm_ge_rows <- chm_ge$Hugo_Symbol
+chm_ge$Hugo_Symbol <- NULL
+chm_ge_cols <- colnames(chm_ge) %>% gsub("RPKM.", "", .)
+chm_ge <- matrix(as.numeric(unlist(chm_ge)), nrow = nrow(chm_ge))
+rownames(chm_ge) <- chm_ge_rows
+colnames(chm_ge) <- chm_ge_cols
+saveRDS(chm_ge, "./data_munging/rds/crispr_heatmap_ge.rds")
+
+# Mutation status
+chm_mut_grid <- merge(crispr_grid, maf_df[, c("Broad_ID", "Hugo_Symbol", "Mutation_Status")], by = c("Broad_ID", "Hugo_Symbol"), all.x = TRUE)
+chm_mut_grid$Mutation_Status <- ifelse(is.na(chm_mut_grid$Mutation_Status), 0, 1)
+chm_mut <- reshape(chm_mut_grid, idvar = "Hugo_Symbol", timevar = "Broad_ID", direction = "wide")
+chm_mut_rows <- chm_mut$Hugo_Symbol
+chm_mut$Hugo_Symbol <- NULL
+chm_mut_cols <- colnames(chm_mut) %>% gsub("Mutation_Status.", "", .)
+chm_mut <- matrix(as.numeric(unlist(chm_mut)), nrow = nrow(chm_mut))
+rownames(chm_mut) <- chm_mut_rows
+colnames(chm_mut) <- chm_mut_cols
+saveRDS(chm_mut, "./data_munging/rds/crispr_heatmap_mut.rds")
+
+# Copy number
+cn_filt <- filter(cn_melt, Hugo_Symbol %in% unique(crispr_data$Hugo_Symbol))
+chm_cn_grid <- merge(crispr_grid, cn_melt, by = c("Broad_ID", "Hugo_Symbol"), all.x = TRUE)
+chm_cn <- reshape(chm_cn_grid, idvar = "Hugo_Symbol", timevar = "Broad_ID", direction = "wide")
+chm_cn_rows <- chm_cn$Hugo_Symbol
+chm_cn$Hugo_Symbol <- NULL
+chm_cn_cols <- colnames(chm_cn) %>% gsub("Copy_Number.", "", .)
+chm_cn <- matrix(as.numeric(unlist(chm_cn)), nrow = nrow(chm_cn))
+rownames(chm_cn) <- chm_cn_rows
+colnames(chm_cn) <- chm_cn_cols
+saveRDS(chm_cn, "./data_munging/rds/crispr_heatmap_cn.rds")
+```
+
+Load heatmap matrices:
+```{r}
+chm_scores <- readRDS("./data_munging/rds/crispr_heatmap_scores.rds")
+chm_ge <- readRDS("./data_munging/rds/crispr_heatmap_ge.rds")
+chm_mut <- readRDS("./data_munging/rds/crispr_heatmap_mut.rds")
+chm_cn <- readRDS("./data_munging/rds/crispr_heatmap_cn.rds")
 
@@
 chm_annot$Cas9_Activity <- as.numeric(chm_annot$Cas9_Activity)
-
-# Make full grid for genomic features
-crispr_grid_ccls <- unique(crispr_data$Broad_ID)
-crispr_grid_genes <- unique(crispr_data$Hugo_Symbol)
-crispr_grid <- expand.grid("Broad_ID" = crispr_grid_ccls, "Hugo_Symbol" = crispr_grid_genes)
-
-# Gene expression
-ge_chm_grid <- merge(crispr_grid, ge_melt[, c("Hugo_Symbol", "Broad_ID", "RPKM")], by = c("Broad_ID", "Hugo_Symbol"), all.x = TRUE)
 ```
 
+Heatmap code:
 ```{r, eval=FALSE}
-chma <- HeatmapAnnotation(df = chm_annot)
-
-chm_euc <- Heatmap(chm_data, name = "CERES Score",
-        bottom_annotation = chma,
+chm_scores_plot <- Heatmap(chm_scores, name = "CERES Score",
+        bottom_annotation = HeatmapAnnotation(df = chm_annot),
         bottom_annotation_height = unit(5, "in"),
@@
         col = colorRamp2(c(-15, 0, 5), c("purple4", "white", "seagreen4")),
+        na_col = "black",
         column_title_gp = gpar(fontsize = 60, fontface = "bold"),
@@
         width = 3)
+chm_ge_plot <- Heatmap(chm_ge, name = "Gene Expression (RPKM)",
+        cluster_rows = FALSE, cluster_columns = FALSE,
+        show_row_names = FALSE, show_column_names = FALSE,
+        column_title = "Gene Expression",
+        column_title_gp = gpar(fontsize = 60, fontface = "bold"),
+        column_order = colnames(chm_scores)[unlist(column_order(chm_scores_plot))],
+        row_order = rownames(chm_scores)[unlist(row_order(chm_scores_plot))],
+        width = 1)
+chm_cn_plot <- Heatmap(chm_cn, name = "Copy Number",
+        cluster_rows = FALSE, cluster_columns = FALSE,
+        show_row_names = FALSE, show_column_names = FALSE,
+        column_title = "Copy Number",
+        column_title_gp = gpar(fontsize = 60, fontface = "bold"),
+        column_order = colnames(chm_scores)[unlist(column_order(chm_scores_plot))],
+        row_order = rownames(chm_scores)[unlist(row_order(chm_scores_plot))],
+        width = 1)
+chm_mut_plot <- Heatmap(chm_mut, name = "Mutation Status",
+        col = c("cyan3", "darkorchid"),
+        cluster_rows = FALSE, cluster_columns = FALSE,
+        show_row_names = FALSE, show_column_names = FALSE,
+        column_title = "Mutation Status",
+        column_title_gp = gpar(fontsize = 60, fontface = "bold"),
+        column_order = colnames(chm_scores)[unlist(column_order(chm_scores_plot))],
+        row_order = rownames(chm_scores)[unlist(row_order(chm_scores_plot))],
+        width = 1)
 
-pdf("./plots_18Q3/crispr_heatmap_euclidean.pdf", width = 100, height = 100, paper = "special") 
-draw(chm_euc, heatmap_legend_side = "right", annotation_legend_side = "right")
+chm_all_plot <- chm_scores_plot + chm_ge_plot + chm_cn_plot + chm_mut_plot
+
+pdf("./plots_18Q3/crispr_heatmap_all.pdf", width = 100, height = 100, paper = "special") 
+draw(chm_all_plot, heatmap_legend_side = "right", annotation_legend_side = "right")
 seekViewport("annotation_Cell_Line_SSMD")

### 2018-08-21 lineages_18Q3.Rmd
update CRISPR heatmap code

@@
 Heatmap code:
-```{r, eval=FALSE}
+```{r, eval=TRUE}
 chm_scores_plot <- Heatmap(chm_scores, name = "CERES Score",
@@
         width = 3)
+
+chm_plot_cols <- colnames(chm_scores)[unlist(column_order(chm_scores_plot))]
+chm_plot_rows <- rownames(chm_scores)[unlist(row_order(chm_scores_plot))]
+
 chm_ge_plot <- Heatmap(chm_ge, name = "Gene Expression (RPKM)",
+        na_col = "black",
         cluster_rows = FALSE, cluster_columns = FALSE,
@@
         column_title_gp = gpar(fontsize = 60, fontface = "bold"),
-        column_order = colnames(chm_scores)[unlist(column_order(chm_scores_plot))],
-        row_order = rownames(chm_scores)[unlist(row_order(chm_scores_plot))],
+        column_order = chm_plot_cols,
+        row_order = chm_plot_rows,
         width = 1)
 chm_cn_plot <- Heatmap(chm_cn, name = "Copy Number",
+        na_col = "black",
         cluster_rows = FALSE, cluster_columns = FALSE,
@@
         column_title_gp = gpar(fontsize = 60, fontface = "bold"),
-        column_order = colnames(chm_scores)[unlist(column_order(chm_scores_plot))],
-        row_order = rownames(chm_scores)[unlist(row_order(chm_scores_plot))],
+        column_order = chm_plot_cols,
+        row_order = chm_plot_rows,
         width = 1)
 chm_mut_plot <- Heatmap(chm_mut, name = "Mutation Status",
+        na_col = "black",
         col = c("cyan3", "darkorchid"),
@@
         column_title_gp = gpar(fontsize = 60, fontface = "bold"),
-        column_order = colnames(chm_scores)[unlist(column_order(chm_scores_plot))],
-        row_order = rownames(chm_scores)[unlist(row_order(chm_scores_plot))],
+        column_order = chm_plot_cols,
+        row_order = chm_plot_rows,
         width = 1)
 
-chm_all_plot <- chm_scores_plot + chm_ge_plot + chm_cn_plot + chm_mut_plot
+# chm_all_plot <- chm_scores_plot + chm_ge_plot + chm_cn_plot + chm_mut_plot
+#   
+# pdf("./../crispr_lineages_giant_files/crispr_heatmap_all.pdf", width = 100, height = 100, paper = "special") 
+# draw(chm_all_plot, heatmap_legend_side = "right", annotation_legend_side = "right")
+# seekViewport("annotation_Cell_Line_SSMD")
+# grid.text("Cell Line SSMD", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+# seekViewport("annotation_Cas9_Activity")
+# grid.text("Cas9 Activity", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+# seekViewport("annotation_Culture_Type")
+# grid.text("Culture Type", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+# seekViewport("annotation_Primary_Tissue")
+# grid.text("Primary Tissue", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+# seekViewport("annotation_Primary_Disease")
+# grid.text("Primary Disease", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+# seekViewport("annotation_Gender")
+# grid.text("Gender", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+# seekViewport("annotation_Source")
+# grid.text("Source", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+# dev.off()
 
-pdf("./plots_18Q3/crispr_heatmap_all.pdf", width = 100, height = 100, paper = "special") 
-draw(chm_all_plot, heatmap_legend_side = "right", annotation_legend_side = "right")
+# pdf("./../crispr_lineages_giant_files/crispr_heatmap_ge.pdf", width = 100, height = 100, paper = "special") 
+# draw(chm_scores_plot + chm_ge_plot, heatmap_legend_side = "right", annotation_legend_side = "right")
+# seekViewport("annotation_Cell_Line_SSMD")
+# grid.text("Cell Line SSMD", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+# seekViewport("annotation_Cas9_Activity")
+# grid.text("Cas9 Activity", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+# seekViewport("annotation_Culture_Type")
+# grid.text("Culture Type", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+# seekViewport("annotation_Primary_Tissue")
+# grid.text("Primary Tissue", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+# seekViewport("annotation_Primary_Disease")
+# grid.text("Primary Disease", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+# seekViewport("annotation_Gender")
+# grid.text("Gender", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+# seekViewport("annotation_Source")
+# grid.text("Source", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+# dev.off()
+
+pdf("./../crispr_lineages_giant_files/crispr_heatmap_mut.pdf", width = 100, height = 100, paper = "special") 
+draw(chm_scores_plot + chm_mut_plot, heatmap_legend_side = "right", annotation_legend_side = "right")
+seekViewport("annotation_Cell_Line_SSMD")
+grid.text("Cell Line SSMD", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+seekViewport("annotation_Cas9_Activity")
+grid.text("Cas9 Activity", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+seekViewport("annotation_Culture_Type")
+grid.text("Culture Type", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+seekViewport("annotation_Primary_Tissue")
+grid.text("Primary Tissue", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+seekViewport("annotation_Primary_Disease")
+grid.text("Primary Disease", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+seekViewport("annotation_Gender")
+grid.text("Gender", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+seekViewport("annotation_Source")
+grid.text("Source", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+dev.off()
+
+pdf("./../crispr_lineages_giant_files/crispr_heatmap_cn.pdf", width = 100, height = 100, paper = "special") 
+draw(chm_scores_plot + chm_cn_plot, heatmap_legend_side = "right", annotation_legend_side = "right")
 seekViewport("annotation_Cell_Line_SSMD")

### 2018-08-22 lineages_18Q3.Rmd
heatmaps: 5 clusterrs (all genes) and CGC genes only

--- 2018-08-21 lineages_18Q3.Rmd
@@
 ```{r}
-make_CRISPRgrob <- function(g) {
+makeCRISPRgrob <- function(g) {
 
@@
 ```{r}
-make_CRISPRlinplot <- function(g) {
+makeCRISPRlinplot <- function(g) {
   gene <- filter(crispr_data, Hugo_Symbol == g)
@@
 
+### Make individual heatmaps per cluster
+
+Take in a sorted gene list from a larger heatmap and produce smaller, individual heatmaps:
+```{r, eval=FALSE}
+makeHeatmaps <- function(clust_obj, clust_num) {
+  chm_plot_cols <- colnames(clust_obj)
+  chm_plot_rows <- rownames(clust_obj)
+
+  chm_plot <- Heatmap(clust_obj, name = "CERES Score",
+          bottom_annotation = HeatmapAnnotation(df = chm_annot),
+          bottom_annotation_height = unit(5, "in"),
+          row_title = "Genes", column_title = "Cancer Cell Lines (Broad IDs)",
+          col = colorRamp2(c(min(chm_scores), 0, max(chm_scores)), c("purple4", "white", "seagreen4")),
+          na_col = "black",
+          column_title_gp = gpar(fontsize = 60, fontface = "bold"),
+          show_column_names = FALSE,
+          row_title_gp = gpar(fontsize = 60, fontface = "bold"),
+          show_row_names = FALSE,
+          row_dend_reorder = TRUE,
+          column_dend_reorder = TRUE,
+          column_order = chm_plot_cols,
+          row_order = chm_plot_rows,
+          column_dend_height = unit(4, "in"),
+          row_dend_width = unit(4, "in"),
+          width = 3)
+
+  chm_ge_plot <- Heatmap(chm_ge[row_order(chm_scores_draw)[[clust_num]],], name = "Gene Expression (RPKM)",
+          col = colorRamp2(c(min(chm_ge[!is.na(chm_ge)]), 0.25, max(chm_ge[!is.na(chm_ge)])), c("dodgerblue4", "white", "firebrick4")),
+          na_col = "black",
+          cluster_rows = FALSE, cluster_columns = FALSE,
+          show_row_names = FALSE, show_column_names = FALSE,
+          column_title = "Gene Expression",
+          column_title_gp = gpar(fontsize = 60, fontface = "bold"),
+          column_order = chm_plot_cols,
+          row_order = chm_plot_rows,
+          width = 1)
+  chm_cn_plot <- Heatmap(chm_cn[row_order(chm_scores_draw)[[clust_num]],], name = "Copy Number",
+          col = colorRamp2(c(min(chm_cn[!is.na(chm_cn)]), 2, max(chm_cn[!is.na(chm_cn)])), c("dodgerblue4", "white", "firebrick4")),
+          na_col = "black",
+          cluster_rows = FALSE, cluster_columns = FALSE,
+          show_row_names = FALSE, show_column_names = FALSE,
+          column_title = "Copy Number",
+          column_title_gp = gpar(fontsize = 60, fontface = "bold"),
+          column_order = chm_plot_cols,
+          row_order = chm_plot_rows,
+          width = 1)
+  chm_mut_plot <- Heatmap(chm_mut[row_order(chm_scores_draw)[[clust_num]],], name = "Mutation Status",
+          na_col = "black",
+          col = c("cyan3", "darkorchid"),
+          cluster_rows = FALSE, cluster_columns = FALSE,
+          show_row_names = FALSE, show_column_names = FALSE,
+          column_title = "Mutation Status",
+          column_title_gp = gpar(fontsize = 60, fontface = "bold"),
+          column_order = chm_plot_cols,
+          row_order = chm_plot_rows,
+          width = 1)
+
+  chm_all_plot <- chm_plot + chm_ge_plot + chm_cn_plot + chm_mut_plot
+
+  pdf(paste0("./plots_18Q3/crispr_heatmap_all_c", clust_num, ".pdf"), width = 100, height = 100, paper = "special")
+  draw(chm_all_plot, heatmap_legend_side = "right", annotation_legend_side = "right")
+  seekViewport("annotation_Cell_Line_SSMD")
+  grid.text("Cell Line SSMD", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+  seekViewport("annotation_Cas9_Activity")
+  grid.text("Cas9 Activity", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+  seekViewport("annotation_Culture_Type")
+  grid.text("Culture Type", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+  seekViewport("annotation_Primary_Tissue")
+  grid.text("Primary Tissue", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+  seekViewport("annotation_Primary_Disease")
+  grid.text("Primary Disease", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+  seekViewport("annotation_Gender")
+  grid.text("Gender", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+  seekViewport("annotation_Source")
+  grid.text("Source", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+  dev.off()
+
+  pdf(paste0("./plots_18Q3/crispr_heatmap_ge_c", clust_num, ".pdf"), width = 100, height = 100, paper = "special")
+  draw(chm_plot + chm_ge_plot, heatmap_legend_side = "right", annotation_legend_side = "right")
+  seekViewport("annotation_Cell_Line_SSMD")
+  grid.text("Cell Line SSMD", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+  seekViewport("annotation_Cas9_Activity")
+  grid.text("Cas9 Activity", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+  seekViewport("annotation_Culture_Type")
+  grid.text("Culture Type", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+  seekViewport("annotation_Primary_Tissue")
+  grid.text("Primary Tissue", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+  seekViewport("annotation_Primary_Disease")
+  grid.text("Primary Disease", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+  seekViewport("annotation_Gender")
+  grid.text("Gender", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+  seekViewport("annotation_Source")
+  grid.text("Source", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+  dev.off()
+
+  pdf(paste0("./plots_18Q3/crispr_heatmap_mut_c", clust_num, ".pdf"), width = 100, height = 100, paper = "special") 
+  draw(chm_plot + chm_mut_plot, heatmap_legend_side = "right", annotation_legend_side = "right")
+  seekViewport("annotation_Cell_Line_SSMD")
+  grid.text("Cell Line SSMD", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+  seekViewport("annotation_Cas9_Activity")
+  grid.text("Cas9 Activity", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+  seekViewport("annotation_Culture_Type")
+  grid.text("Culture Type", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+  seekViewport("annotation_Primary_Tissue")
+  grid.text("Primary Tissue", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+  seekViewport("annotation_Primary_Disease")
+  grid.text("Primary Disease", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+  seekViewport("annotation_Gender")
+  grid.text("Gender", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+  seekViewport("annotation_Source")
+  grid.text("Source", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+  dev.off()
+
+  pdf(paste0("./plots_18Q3/crispr_heatmap_cn_c", clust_num, ".pdf"), width = 100, height = 100, paper = "special") 
+  draw(chm_plot + chm_cn_plot, heatmap_legend_side = "right", annotation_legend_side = "right")
+  seekViewport("annotation_Cell_Line_SSMD")
+  grid.text("Cell Line SSMD", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+  seekViewport("annotation_Cas9_Activity")
+  grid.text("Cas9 Activity", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+  seekViewport("annotation_Culture_Type")
+  grid.text("Culture Type", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+  seekViewport("annotation_Primary_Tissue")
+  grid.text("Primary Tissue", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+  seekViewport("annotation_Primary_Disease")
+  grid.text("Primary Disease", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+  seekViewport("annotation_Gender")
+  grid.text("Gender", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+  seekViewport("annotation_Source")
+  grid.text("Source", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+  dev.off()
+}
+```
+
 ## Cell line converter
@@
 ```{r}
-ccl_converter <- read.delim("./data_munging/danielc_cell_line_database_completed_extra_SE.tsv", sep = "\t", row.names = NULL, header = TRUE)
-colnames(ccl_converter)[4] <- "CCLE_Name"
-colnames(ccl_converter)[10] <- "Broad_ID"
+ccl_converter <- read.delim("./data_munging/cell_line_database_FINAL_MASTER.tsv", sep = "\t", row.names = 1, header = TRUE)
+colnames(ccl_converter)[colnames(ccl_converter) == "ccle_cell_line_name"] <- "CCLE_Name"
+colnames(ccl_converter)[colnames(ccl_converter) == "broad_id"] <- "Broad_ID"
 ```
@@
 test$BroadIDs_match <- ifelse(as.character(test$Broad_ID_DepMap) == as.character(test$Broad_ID_Daniel), TRUE, FALSE)
+```
+
+## Cancer Gene Census (CGC) gene list
+
+Select genes from the Cancer Gene Census (CGC).
+The list was pulled from the [International Cancer Genome Consortium (ICGC) data portal](https://dcc.icgc.org/search/g?filters=%7B%22gene%22:%7B%22curatedSetId%22:%7B%22is%22:%5B%22GS1%22%5D%7D%7D%7D) (Advaced Search > Genes > Curated Gene Set > Cancer Gene Census).
+```{r}
+cgc <- data_frame("Hugo_Symbol" = read.delim("./data_munging/gene-ids-for-set-Cancer Gene Census.tsv", header = FALSE, sep = "\t")[, 2])
 ```
@@
 
+### Data management
+
 Make and save heatmap data matrices:
@@
 chm_scores <- chm_scores[-1, ]
+chm_rows <- rownames(chm_scores)
 chm_cols <- colnames(chm_scores)
@@
 colnames(chm_scores) <- chm_cols
+rownames(chm_scores) <- chm_rows
 saveRDS(chm_scores, "./data_munging/rds/crispr_heatmap_scores.rds")
@@
 
-Heatmap code:
+### K-means clustered
+
+Code for k-means clustered heatmap:
 ```{r, eval=FALSE}
@@
         row_title = "Genes", column_title = "Cancer Cell Lines (Broad IDs)",
-        col = colorRamp2(c(-15, 0, 5), c("purple4", "white", "seagreen4")),
+        col = colorRamp2(c(min(chm_scores), 0, max(chm_scores)), c("purple4", "white", "seagreen4")),
         na_col = "black",
@@
         row_dend_width = unit(4, "in"),
+        width = 3,
+        km = 5, gap = unit(0.5, "in"))
+
+chm_scores_draw <- draw(chm_scores_plot, heatmap_legend_side = "right", annotation_legend_side = "right")
+
+pdf("./plots_18Q3/crispr_heatmap_euclidean_split5.pdf", width = 100, height = 100, paper = "special")
+chm_scores_draw
+seekViewport("annotation_Cell_Line_SSMD")
+grid.text("Cell Line SSMD", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+seekViewport("annotation_Cas9_Activity")
+grid.text("Cas9 Activity", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+seekViewport("annotation_Culture_Type")
+grid.text("Culture Type", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+seekViewport("annotation_Primary_Tissue")
+grid.text("Primary Tissue", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+seekViewport("annotation_Primary_Disease")
+grid.text("Primary Disease", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+seekViewport("annotation_Gender")
+grid.text("Gender", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+seekViewport("annotation_Source")
+grid.text("Source", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+dev.off()
+
+# chm_scores_c1 <- t(t(rownames(chm_scores[row_order(chm_scores_draw)[[1]],])))
+# chm_scores_c2 <- t(t(rownames(chm_scores[row_order(chm_scores_draw)[[2]],])))
+# chm_scores_c3 <- t(t(rownames(chm_scores[row_order(chm_scores_draw)[[3]],])))
+# chm_scores_c4 <- t(t(rownames(chm_scores[row_order(chm_scores_draw)[[4]],])))
+
+chm_scores_c1 <- chm_scores[row_order(chm_scores_draw)[[1]],]
+chm_scores_c2 <- chm_scores[row_order(chm_scores_draw)[[2]],]
+chm_scores_c3 <- chm_scores[row_order(chm_scores_draw)[[3]],]
+chm_scores_c4 <- chm_scores[row_order(chm_scores_draw)[[4]],]
+chm_scores_c5 <- chm_scores[row_order(chm_scores_draw)[[5]],]
+
+makeHeatmaps(chm_scores_c1, 1)
+makeHeatmaps(chm_scores_c2, 2)
+makeHeatmaps(chm_scores_c3, 3)
+makeHeatmaps(chm_scores_c4, 4)
+makeHeatmaps(chm_scores_c5, 5)
+```
+
+### CGC genes
+
+Code for heatmap of CGC-filtered genes only:
+```{r, eval=FALSE}
+chm_scores_cgc <- subset(chm_scores, rownames(chm_scores) %in% cgc$Hugo_Symbol)
+chm_ge_cgc <- subset(chm_ge, rownames(chm_ge) %in% cgc$Hugo_Symbol)
+chm_mut_cgc <- subset(chm_mut, rownames(chm_mut) %in% cgc$Hugo_Symbol)
+chm_cn_cgc <- subset(chm_cn, rownames(chm_cn) %in% cgc$Hugo_Symbol)
+
+chm_plot_cgc <- Heatmap(chm_scores_cgc, name = "CERES Score",
+        bottom_annotation = HeatmapAnnotation(df = chm_annot),
+        bottom_annotation_height = unit(5, "in"),
+        row_title = "Genes", column_title = "Cancer Cell Lines (Broad IDs)",
+        col = colorRamp2(c(min(chm_scores_cgc), 0, max(chm_scores_cgc)), c("purple4", "white", "seagreen4")),
+        na_col = "black",
+        row_title_gp = gpar(fontsize = 60, fontface = "bold"),
+        row_names_gp = gpar(fontsize = 10),
+        column_title_gp = gpar(fontsize = 60, fontface = "bold"),
+        column_names_gp = gpar(fontsize = 10),
+        row_dend_reorder = TRUE,
+        column_dend_reorder = TRUE,
+        clustering_distance_rows = "euclidean",
+        clustering_distance_columns = "euclidean",
+        clustering_method_rows = "complete",
+        clustering_method_columns = "complete",
+        column_dend_height = unit(4, "in"),
+        row_dend_width = unit(4, "in"),
         width = 3)
-chm_ge_plot <- Heatmap(chm_ge, name = "Gene Expression (RPKM)",
+
+chm_plot_cgc_cols <- colnames(chm_scores_cgc)[unlist(column_order(chm_plot_cgc))]
+chm_plot_cgc_rows <- rownames(chm_scores_cgc)[unlist(row_order(chm_plot_cgc))]
+
+chm_ge_plot_cgc <- Heatmap(chm_ge_cgc, name = "Gene Expression (RPKM)",
+        col = colorRamp2(c(min(chm_ge_cgc[!is.na(chm_ge_cgc)]), 0.25, max(chm_ge_cgc[!is.na(chm_ge_cgc)])), c("dodgerblue4", "white", "firebrick4")),
+        na_col = "black",
         cluster_rows = FALSE, cluster_columns = FALSE,
@@
         column_title_gp = gpar(fontsize = 60, fontface = "bold"),
-        column_order = colnames(chm_scores)[unlist(column_order(chm_scores_plot))],
-        row_order = rownames(chm_scores)[unlist(row_order(chm_scores_plot))],
+        column_order = chm_plot_cgc_cols,
+        row_order = chm_plot_cgc_rows,
         width = 1)
-chm_cn_plot <- Heatmap(chm_cn, name = "Copy Number",
+chm_cn_plot_cgc <- Heatmap(chm_cn_cgc, name = "Copy Number",
+        col = colorRamp2(c(min(chm_cn_cgc[!is.na(chm_cn_cgc)]), 2, max(chm_cn_cgc[!is.na(chm_cn_cgc)])), c("dodgerblue4", "white", "firebrick4")),
+        na_col = "black",
         cluster_rows = FALSE, cluster_columns = FALSE,
@@
         column_title_gp = gpar(fontsize = 60, fontface = "bold"),
-        column_order = colnames(chm_scores)[unlist(column_order(chm_scores_plot))],
-        row_order = rownames(chm_scores)[unlist(row_order(chm_scores_plot))],
+        column_order = chm_plot_cgc_cols,
+        row_order = chm_plot_cgc_rows,
         width = 1)
-chm_mut_plot <- Heatmap(chm_mut, name = "Mutation Status",
+chm_mut_plot_cgc <- Heatmap(chm_mut_cgc, name = "Mutation Status",
+        na_col = "black",
         col = c("cyan3", "darkorchid"),
@@
         column_title_gp = gpar(fontsize = 60, fontface = "bold"),
-        column_order = colnames(chm_scores)[unlist(column_order(chm_scores_plot))],
-        row_order = rownames(chm_scores)[unlist(row_order(chm_scores_plot))],
+        column_order = chm_plot_cgc_cols,
+        row_order = chm_plot_cgc_rows,
         width = 1)
 
-chm_all_plot <- chm_scores_plot + chm_ge_plot + chm_cn_plot + chm_mut_plot
+chm_all_plot_cgc <- chm_plot_cgc + chm_ge_plot_cgc + chm_cn_plot_cgc + chm_mut_plot_cgc
 
-pdf("./plots_18Q3/crispr_heatmap_all.pdf", width = 100, height = 100, paper = "special") 
-draw(chm_all_plot, heatmap_legend_side = "right", annotation_legend_side = "right")
+pdf("./plots_18Q3/crispr_heatmap_all_cgc.pdf", width = 100, height = 100, paper = "special")
+draw(chm_all_plot_cgc, heatmap_legend_side = "right", annotation_legend_side = "right")
 seekViewport("annotation_Cell_Line_SSMD")
@@
 ```{r fig.height=12, fig.width=12}
-make_CRISPRgrob("KRAS")
+makeCRISPRgrob("KRAS")
 ```
@@
 ```{r fig.height=12, fig.width=12}
-make_CRISPRgrob("TP53")
+makeCRISPRgrob("TP53")
 ```
@@
 ```{r fig.height=12, fig.width=12}
-make_CRISPRgrob("BRAF")
+makeCRISPRgrob("BRAF")
 ```
@@
 ```{r fig.height=12, fig.width=12}
-make_CRISPRgrob("NRAS")
+makeCRISPRgrob("NRAS")
 ```
@@
 ```{r fig.height=10, fig.width=15}
-make_CRISPRlinplot("KRAS")
+makeCRISPRlinplot("KRAS")
 ```
@@
 ```{r fig.height=10, fig.width=15}
-make_CRISPRlinplot("TP53")
+makeCRISPRlinplot("TP53")
 ```
@@
 ```{r fig.height=10, fig.width=15}
-make_CRISPRlinplot("BRAF")
+makeCRISPRlinplot("BRAF")
 ```
@@
 ```{r fig.height=10, fig.width=15}
-make_CRISPRlinplot("NRAS")
+makeCRISPRlinplot("NRAS")
 ```

### 2018-08-22 lineages_18Q3.Rmd
update Rmd

@@
         column_title_gp = gpar(fontsize = 60, fontface = "bold"),
-        column_names_gp = gpar(fontsize = 10),
+        column_names_gp = gpar(fontsize = 8),
         row_dend_reorder = TRUE,

### 2018-08-23 lineages_18Q3.Rmd
rename heatmaps with clustering metric

@@
 Load heatmap matrices:
-```{r}
+```{r, eval=FALSE}
 chm_scores <- readRDS("./data_munging/rds/crispr_heatmap_scores.rds")
@@
 ### K-means clustered
+
+#### Euclidean distance
 
@@
 
-# chm_scores_c1 <- t(t(rownames(chm_scores[row_order(chm_scores_draw)[[1]],])))
-# chm_scores_c2 <- t(t(rownames(chm_scores[row_order(chm_scores_draw)[[2]],])))
-# chm_scores_c3 <- t(t(rownames(chm_scores[row_order(chm_scores_draw)[[3]],])))
-# chm_scores_c4 <- t(t(rownames(chm_scores[row_order(chm_scores_draw)[[4]],])))
-
 chm_scores_c1 <- chm_scores[row_order(chm_scores_draw)[[1]],]
@@
 
-Code for heatmap of CGC-filtered genes only:
+Code for heatmap of CGC-filtered genes only
+
+#### Euclidean distance
+
 ```{r, eval=FALSE}
@@
 
-pdf("./plots_18Q3/crispr_heatmap_all_cgc.pdf", width = 100, height = 100, paper = "special")
+pdf("./plots_18Q3/crispr_heatmap_euclidean_all_cgc.pdf", width = 100, height = 100, paper = "special")
+draw(chm_all_plot_cgc, heatmap_legend_side = "right", annotation_legend_side = "right")
+seekViewport("annotation_Cell_Line_SSMD")
+grid.text("Cell Line SSMD", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+seekViewport("annotation_Cas9_Activity")
+grid.text("Cas9 Activity", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+seekViewport("annotation_Culture_Type")
+grid.text("Culture Type", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+seekViewport("annotation_Primary_Tissue")
+grid.text("Primary Tissue", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+seekViewport("annotation_Primary_Disease")
+grid.text("Primary Disease", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+seekViewport("annotation_Gender")
+grid.text("Gender", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+seekViewport("annotation_Source")
+grid.text("Source", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+dev.off()
+```
+
+#### Pearson correlation
+
+```{r, eval=FALSE}
+chm_scores_cgc <- subset(chm_scores, rownames(chm_scores) %in% cgc$Hugo_Symbol)
+chm_ge_cgc <- subset(chm_ge, rownames(chm_ge) %in% cgc$Hugo_Symbol)
+chm_mut_cgc <- subset(chm_mut, rownames(chm_mut) %in% cgc$Hugo_Symbol)
+chm_cn_cgc <- subset(chm_cn, rownames(chm_cn) %in% cgc$Hugo_Symbol)
+
+chm_plot_cgc <- Heatmap(chm_scores_cgc, name = "CERES Score",
+        bottom_annotation = HeatmapAnnotation(df = chm_annot),
+        bottom_annotation_height = unit(5, "in"),
+        row_title = "Genes", column_title = "Cancer Cell Lines (Broad IDs)",
+        col = colorRamp2(c(min(chm_scores_cgc), 0, max(chm_scores_cgc)), c("purple4", "white", "seagreen4")),
+        na_col = "black",
+        row_title_gp = gpar(fontsize = 60, fontface = "bold"),
+        row_names_gp = gpar(fontsize = 10),
+        column_title_gp = gpar(fontsize = 60, fontface = "bold"),
+        column_names_gp = gpar(fontsize = 8),
+        row_dend_reorder = TRUE,
+        column_dend_reorder = TRUE,
+        clustering_distance_rows = "pearson",
+        clustering_distance_columns = "pearson",
+        clustering_method_rows = "complete",
+        clustering_method_columns = "complete",
+        column_dend_height = unit(4, "in"),
+        row_dend_width = unit(4, "in"),
+        width = 3)
+
+chm_plot_cgc_cols <- colnames(chm_scores_cgc)[unlist(column_order(chm_plot_cgc))]
+chm_plot_cgc_rows <- rownames(chm_scores_cgc)[unlist(row_order(chm_plot_cgc))]
+
+chm_ge_plot_cgc <- Heatmap(chm_ge_cgc, name = "Gene Expression (RPKM)",
+        col = colorRamp2(c(min(chm_ge_cgc[!is.na(chm_ge_cgc)]), 0.25, max(chm_ge_cgc[!is.na(chm_ge_cgc)])), c("dodgerblue4", "white", "firebrick4")),
+        na_col = "black",
+        cluster_rows = FALSE, cluster_columns = FALSE,
+        show_row_names = FALSE, show_column_names = FALSE,
+        column_title = "Gene Expression",
+        column_title_gp = gpar(fontsize = 60, fontface = "bold"),
+        column_order = chm_plot_cgc_cols,
+        row_order = chm_plot_cgc_rows,
+        width = 1)
+chm_cn_plot_cgc <- Heatmap(chm_cn_cgc, name = "Copy Number",
+        col = colorRamp2(c(min(chm_cn_cgc[!is.na(chm_cn_cgc)]), 2, max(chm_cn_cgc[!is.na(chm_cn_cgc)])), c("dodgerblue4", "white", "firebrick4")),
+        na_col = "black",
+        cluster_rows = FALSE, cluster_columns = FALSE,
+        show_row_names = FALSE, show_column_names = FALSE,
+        column_title = "Copy Number",
+        column_title_gp = gpar(fontsize = 60, fontface = "bold"),
+        column_order = chm_plot_cgc_cols,
+        row_order = chm_plot_cgc_rows,
+        width = 1)
+chm_mut_plot_cgc <- Heatmap(chm_mut_cgc, name = "Mutation Status",
+        na_col = "black",
+        col = c("cyan3", "darkorchid"),
+        cluster_rows = FALSE, cluster_columns = FALSE,
+        show_row_names = FALSE, show_column_names = FALSE,
+        column_title = "Mutation Status",
+        column_title_gp = gpar(fontsize = 60, fontface = "bold"),
+        column_order = chm_plot_cgc_cols,
+        row_order = chm_plot_cgc_rows,
+        width = 1)
+
+chm_all_plot_cgc <- chm_plot_cgc + chm_ge_plot_cgc + chm_cn_plot_cgc + chm_mut_plot_cgc
+
+pdf("./plots_18Q3/crispr_heatmap_pearson_all_cgc.pdf", width = 100, height = 100, paper = "special")
 draw(chm_all_plot_cgc, heatmap_legend_side = "right", annotation_legend_side = "right")
@@
 
-## Grouped plots {.tabset .tabset-fade .tabset-pills}
+## Grouped plots
 
-### KRAS
-
-```{r fig.height=12, fig.width=12}
-makeCRISPRgrob("KRAS")
+Plot code:
+```{r, eval=FALSE}
+crispr_all_genes <- unique(crispr_data$Hugo_Symbol)
+crispr_all_groups <- lapply(crispr_all_genes, makeCRISPRgrob)
+crispr_all_groups_paths <- paste0(crispr_all_genes, "_crispr_grouped.png")
+pwalk(list(crispr_all_groups_paths, crispr_all_groups), ggsave, path = "./plots_18Q3/crispr_grouped_plots", dpi = 300, width = 12, height = 12, units = "in")
 ```
 
-### TP53
-
-```{r fig.height=12, fig.width=12}
-makeCRISPRgrob("TP53")
+Data management:
+```{r, eval=FALSE}
+crispr_all_bygene <- paste0(list.files("./plots_18Q3/crispr_grouped_plots", full.names = TRUE))
+names(crispr_all_bygene) <- str_replace_all(crispr_all_bygene, c("_crispr_grouped.png" = "", "./plots_18Q3/crispr_grouped_plots/" = ""))
 ```
 
-### BRAF
-
-```{r fig.height=12, fig.width=12}
-makeCRISPRgrob("BRAF")
-```
-
-### NRAS
-
-```{r fig.height=12, fig.width=12}
-makeCRISPRgrob("NRAS")
+Plots:
+```{r, eval=FALSE}
+crispr_bygene_order <- c(intersect(crispr_signif$Hugo_Symbol, names(crispr_all_bygene)), setdiff(names(crispr_all_bygene), crispr_signif$Hugo_Symbol))
+crispr_all_bygene <- crispr_all_bygene[match(crispr_bygene_order, names(crispr_all_bygene))]
+bsselect(crispr_all_bygene, type = "img", selected = "KRAS", live_search = TRUE, show_tick = TRUE, height = 300, frame_height = 275)
 ```

### 2018-08-24 lineages_18Q3.Rmd

@@
 
-knitr::kable(crispr_signif[1:100, c(1, 5, 6, 7, 8, 10)], caption = "CRISPR Screen: Wilcoxon Test Results Comparing Mutant and Wildtype Cell Lines (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(filter(crispr_signif, p < 0.1)[, c(1, 5, 6, 7, 8, 10)], caption = "CRISPR Screen: Wilcoxon Test Results Comparing Mutant and Wildtype Cell Lines (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
-knitr::kable(shrna_signif[1:100, c(1, 5, 6, 7, 8, 10)], caption = "shRNA Screen: Wilcoxon Test Results Comparing Mutant and Wildtype Cell Lines (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(filter(shrna_signif, p < 0.1), c(1, 5, 6, 7, 8, 10)], caption = "shRNA Screen: Wilcoxon Test Results Comparing Mutant and Wildtype Cell Lines (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
+### KRAS
+
+```{r fig.height=12, fig.width=12}
+makeCRISPRgrob("KRAS")
+```
+
+### TP53
+
+```{r fig.height=12, fig.width=12}
+makeCRISPRgrob("TP53")
+```
+
 ## Sorted lineage plots {.tabset .tabset-fade .tabset-pills}

### 2018-08-24 lineages_18Q3.Rmd
updated Rmd/html w/ per-gene plots

--- 2018-08-23 lineages_18Q3.Rmd
@@
 makeCRISPRlinplot <- function(g) {
+  sig <- filter(crispr_signif_lineage, Hugo_Symbol == g)
+  if(nrow(sig) == 0) {
+    return(NULL)
+  }
+  else {
     gene <- filter(crispr_data, Hugo_Symbol == g)
-  sig <- filter(crispr_signif_lineage, Hugo_Symbol == g)
     gene <- merge(gene, sig, by = c("Hugo_Symbol", "lineage_name"))
@@
   }
+}
 ```
@@
 
-  pdf(paste0("./plots_18Q3/crispr_heatmap_all_c", clust_num, ".pdf"), width = 100, height = 100, paper = "special")
+  pdf(paste0("./plots_18Q3/crispr_heatmap_clustered/crispr_heatmap_all_c", clust_num, ".pdf"), width = 100, height = 100, paper = "special")
   draw(chm_all_plot, heatmap_legend_side = "right", annotation_legend_side = "right")
@@
 
-knitr::kable(crispr_signif[1:100, c(1, 5, 6, 7, 8, 10)], caption = "CRISPR Screen: Wilcoxon Test Results Comparing Mutant and Wildtype Cell Lines (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(filter(crispr_signif, p < 0.1)[, c(1, 5, 6, 7, 8, 10)], caption = "CRISPR Screen: Wilcoxon Test Results Comparing Mutant and Wildtype Cell Lines, p < 0.1 (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
-knitr::kable(shrna_signif[1:100, c(1, 5, 6, 7, 8, 10)], caption = "shRNA Screen: Wilcoxon Test Results Comparing Mutant and Wildtype Cell Lines (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(filter(shrna_signif, p < 0.1)[, c(1, 5, 6, 7, 8, 10)], caption = "shRNA Screen: Wilcoxon Test Results Comparing Mutant and Wildtype Cell Lines, p < 0.1  (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 ```{r, eval=FALSE}
-crispr_all_genes <- unique(crispr_data$Hugo_Symbol)
+crispr_data_cgc <- filter(crispr_data, Hugo_Symbol %in% cgc$Hugo_Symbol)
+crispr_all_genes <- unique(crispr_data_cgc$Hugo_Symbol)
 crispr_all_groups <- lapply(crispr_all_genes, makeCRISPRgrob)
 crispr_all_groups_paths <- paste0(crispr_all_genes, "_crispr_grouped.png")
-pwalk(list(crispr_all_groups_paths, crispr_all_groups), ggsave, path = "./plots_18Q3/crispr_grouped_plots", dpi = 300, width = 12, height = 12, units = "in")
+pwalk(list(crispr_all_groups_paths, crispr_all_groups), ggsave, path = "./plots_18Q3/crispr_grouped_plots_cgc", dpi = 300, width = 12, height = 12, units = "in")
 ```
@@
 Data management:
-```{r, eval=FALSE}
-crispr_all_bygene <- paste0(list.files("./plots_18Q3/crispr_grouped_plots", full.names = TRUE))
-names(crispr_all_bygene) <- str_replace_all(crispr_all_bygene, c("_crispr_grouped.png" = "", "./plots_18Q3/crispr_grouped_plots/" = ""))
-```
-
-Plots:
-```{r, eval=FALSE}
+```{r}
+crispr_all_bygene <- paste0(list.files("./plots_18Q3/crispr_grouped_plots_cgc", full.names = TRUE))
+names(crispr_all_bygene) <- str_replace_all(crispr_all_bygene, c("_crispr_grouped.png" = "", "./plots_18Q3/crispr_grouped_plots_cgc/" = ""))
 crispr_bygene_order <- c(intersect(crispr_signif$Hugo_Symbol, names(crispr_all_bygene)), setdiff(names(crispr_all_bygene), crispr_signif$Hugo_Symbol))
@@
 
-## Sorted lineage plots {.tabset .tabset-fade .tabset-pills}
-
-### KRAS
-
-```{r fig.height=10, fig.width=15}
-makeCRISPRlinplot("KRAS")
-```
-
-### TP53
-
-```{r fig.height=10, fig.width=15}
-makeCRISPRlinplot("TP53")
-```
-
-### BRAF
-
-```{r fig.height=10, fig.width=15}
-makeCRISPRlinplot("BRAF")
-```
-
-### NRAS
-
-```{r fig.height=10, fig.width=15}
-makeCRISPRlinplot("NRAS")
+## Sorted lineage plots
+
+Plot code:
+```{r, eval=FALSE}
+crispr_data_cgc <- filter(crispr_data, Hugo_Symbol %in% cgc$Hugo_Symbol)
+crispr_all_genes <- unique(crispr_data_cgc$Hugo_Symbol)
+crispr_all_lins <- lapply(crispr_all_genes, makeCRISPRlinplot)
+crispr_all_lins_paths <- paste0(crispr_all_genes, "_crispr_lineage.png")
+pwalk(list(crispr_all_lins_paths, crispr_all_lins), ggsave, path = "./plots_18Q3/crispr_lineage_plots_cgc", dpi = 300, width = 12, height = 12, units = "in")
+```
+
+```{r}
+makeCRISPRlinplot("HMGA1")
+test <- filter(crispr_signif_lineage, Hugo_Symbol == "HMGA1")
+```
+
+Data management:
+```{r}
+crispr_all_bygene <- paste0(list.files("./plots_18Q3/crispr_lineage_plots_cgc", full.names = TRUE))
+names(crispr_all_bygene) <- str_replace_all(crispr_all_bygene, c("_crispr_lineage.png" = "", "./plots_18Q3/crispr_lineage_plots_cgc/" = ""))
+crispr_bygene_order <- c(intersect(crispr_signif$Hugo_Symbol, names(crispr_all_bygene)), setdiff(names(crispr_all_bygene), crispr_signif$Hugo_Symbol))
+crispr_all_bygene <- crispr_all_bygene[match(crispr_bygene_order, names(crispr_all_bygene))]
+bsselect(crispr_all_bygene, type = "img", selected = "KRAS", live_search = TRUE, show_tick = TRUE, height = 300, frame_height = 275)
 ```

### 2018-08-24 lineages_18Q3.Rmd
updated rmd

@@
 crispr_ccl <- data.frame("Broad_ID" = crispr_data$Broad_ID)
+# write.table(crispr_data, file = "crispr_data.tsv", quote = FALSE, sep = "\t")
+```
+
+```{r, include=FALSE, eval=FALSE}
+length(intersect(unique(crispr_data$Hugo_Symbol), unique(maf_df$Hugo_Symbol)))
+length(intersect(unique(crispr_data$Hugo_Symbol), unique(cn_melt$Hugo_Symbol)))
+length(intersect(unique(crispr_data$Hugo_Symbol), unique(ge_melt$Hugo_Symbol)))
+
+length(intersect(unique(crispr_data$Broad_ID), unique(maf_df$Broad_ID)))
+length(intersect(unique(crispr_data$Broad_ID), unique(cn_melt$Broad_ID)))
+length(intersect(unique(crispr_data$Broad_ID), unique(ge_melt$Broad_ID)))
+
+length(intersect(intersect(unique(crispr_data$Broad_ID), unique(cn_melt$Broad_ID)), unique(ge_melt$Broad_ID)))
+setdiff(crispr_data$Broad_ID, intersect(intersect(unique(crispr_data$Broad_ID), unique(cn_melt$Broad_ID)), unique(ge_melt$Broad_ID)))
 ```
@@
 
+# Mutation exploration
+
+--------------------------------------------------------------------------------
+
+```{r}
+maf_annot <- merge(maf_raw[maf_raw$Variant_Classification != "Silent",] %>% group_by(Broad_ID) %>% tally(), crispr_meta, by = "Broad_ID", all.y = TRUE)
+```
+
+```{r fig.height=6, fig.width=12}
+ggplot(data = maf_annot, aes(x = primary_tissue, y = n)) +
+  geom_jitter(alpha = 0.6, size = 0.7, position = position_jitter(w = 0.15)) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+```
+
 # Wilcoxon tests
@@
 crispr_signif_lineage <- readRDS("./data_munging/rds/crispr_signif_lineage.rds")
+
+knitr::kable(filter(crispr_signif_lineage, p < 0.1)[, c(1, 2, 5, 6, 7, 8, 10)], caption = "CRISPR Screen: Wilcoxon Test Results Comparing Mutant and Wildtype Cell Lines by Lineage, p < 0.1 (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
 ```

### 2018-08-27 lineages_18Q3.Rmd
added metadata exploration section

@@
 
+###  Metadata exploration
+
+```{r}
+tissue_summ <- crispr_meta %>% group_by(primary_tissue) %>% tally()
+disease_summ <- ccl_info %>% group_by(Primary.Disease) %>% tally()
+```
+
+```{r fig.height=5, fig.width=8}
+ggplot(data = tissue_summ) + 
+  aes(x = 0, y = n, fill = primary_tissue, label = primary_tissue) +
+  geom_histogram(color = "black", stat = "identity") +
+  geom_text(position = position_stack(vjust = 0.5))
+```
+
 ```{r}
@@
 crispr_ccl <- data.frame("Broad_ID" = crispr_data$Broad_ID)
-# write.table(crispr_data, file = "crispr_data.tsv", quote = FALSE, sep = "\t")
+write.table(crispr_data[, c("Hugo_Symbol", "Broad_ID", "Score", "Primary.Disease", "primary_tissue", "Mutation_Status")], file = "~/Desktop/crispr_data_select.tsv", quote = FALSE, sep = "\t")
 ```

### 2018-08-29 lineages_18Q3.Rmd
Wilcox tests: CRISPR, gene-tissue grouping

@@
 library(NMF)
-library(ggsignif)
 library(ggpubr)
@@
 library(magrittr)
-library(ggrepel)
 library(matrixStats)
@@
   # Gene expression
-  lo_ge <- range(gene$RPKM[!is.na(gene$RPKM)])[1]
-  hi_ge <- range(gene$RPKM[!is.na(gene$RPKM)])[2]
+  lo_ge <- range(gene$RPKM_log2[!is.na(gene$RPKM_log2)])[1]
+  hi_ge <- range(gene$RPKM_log2[!is.na(gene$RPKM_log2)])[2]
   mid_ge <- (hi_ge - lo_ge) / 2
-  plot_ge <- ggplot(data = gene, aes(x = RPKM, y = Score, color = Mutation_Status)) +
+  plot_ge <- ggplot(data = gene, aes(x = RPKM_log2, y = Score, color = Mutation_Status)) +
     geom_point(size = 0.5, alpha = 0.5) +
@@
     labs(y = "CERES Score", color = "Mutation Status",
-         x = paste0(g, " Gene Expression (RPKM)"),
+         x = paste0(g, " Gene Expression [log2(RPKM)]"),
          title = "Gene Expression",
@@
 # Convert log2 ratios (log2(CN/2)) to CN
-cn[2:ncol(cn)] <- lapply(cn[2:ncol(cn)], function(x) 2 * (2 ^ x))
+# cn[2:ncol(cn)] <- lapply(cn[2:ncol(cn)], function(x) 2 * (2 ^ x))
 
@@
 crispr_data <- merge(crispr_data, ge_filt, by = c("Hugo_Symbol", "Broad_ID", "CCLE_Name"), all.x = TRUE)
-
-saveRDS(crispr_data, "./data_munging/rds/crispr_data_18Q3.rds", compress = "xz")
-```
-
-```{r}
-crispr_data <- readRDS("./data_munging/rds/crispr_data_18Q3.rds")
+crispr_data$RPKM_log2 <- log2(crispr_data$RPKM + 0.0001)
+
+saveRDS(crispr_data, "./../crispr_lineages_giant_files/crispr_data_18Q3.rds", compress = "xz")
+```
+
+```{r}
+crispr_data <- readRDS("./../crispr_lineages_giant_files/crispr_data_18Q3.rds")
 crispr_ccl <- data.frame("Broad_ID" = crispr_data$Broad_ID)
@@
 knitr::kable(filter(crispr_signif_lineage, p < 0.1)[, c(1, 2, 5, 6, 7, 8, 10)], caption = "CRISPR Screen: Wilcoxon Test Results Comparing Mutant and Wildtype Cell Lines by Lineage, p < 0.1 (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+```
+
+### Grouped by gene and tissue
+
+```{r, eval=TRUE}
+crispr_signif_tissue <- compare_means(Score ~ Mutation_Status, group.by = c("Hugo_Symbol", "primary_tissue"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
+crispr_signif_tissue <- adj_signif(crispr_signif_tissue)
+# crispr_signif_tissue <- mutate(crispr_signif_tissue, primary_tissue = reorder(primary_tissue, p.adj, mean))
+crispr_signif_tissue <- crispr_signif_tissue[order(crispr_signif_tissue$p),]
+saveRDS(crispr_signif_tissue, "./data_munging/rds/crispr_signif_tissue.rds")
+```
+
+```{r}
+crispr_signif_tissue <- readRDS("./data_munging/rds/crispr_signif_tissue.rds")
+
+knitr::kable(filter(crispr_signif_tissue, p < 0.1)[, c("Hugo_Symbol", "primary_tissue", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CRISPR Screen: Wilcoxon Test Results Comparing Mutant and Wildtype Cell Lines by Primary Tissue, p < 0.1 (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 ge_filt <- filter(ge_melt, Hugo_Symbol %in% unique(crispr_data$Hugo_Symbol))[, c("Hugo_Symbol", "Broad_ID", "RPKM")]
+ge_filt$RPKM <- log2(ge_filt$RPKM + 0.0001)
 chm_ge_grid <- merge(crispr_grid, ge_filt, by = c("Broad_ID", "Hugo_Symbol"), all.x = TRUE)
@@
 chm_ge_cols <- colnames(chm_ge) %>% gsub("RPKM.", "", .)
-chm_ge <- matrix(as.numeric(unlist(chm_ge)), nrow = nrow(chm_ge))
+chm_ge <- apply(chm_ge, 2, as.double)
+chm_ge <- apply(chm_ge, 2, function(x) (x - mean(x, na.rm = TRUE)) / var(x, na.rm = TRUE))
 rownames(chm_ge) <- chm_ge_rows
@@
 chm_cn_cols <- colnames(chm_cn) %>% gsub("Copy_Number.", "", .)
-chm_cn <- matrix(as.numeric(unlist(chm_cn)), nrow = nrow(chm_cn))
+chm_cn <- apply(chm_cn, 2, as.double)
+chm_cn <- apply(chm_cn, 2, function(x) (x - mean(x, na.rm = TRUE)) / var(x, na.rm = TRUE))
 rownames(chm_cn) <- chm_cn_rows
@@
 
+```{r}
+mean(chm_cn_cgc[!is.na(chm_cn_cgc)])
+```
+
 ```{r, eval=FALSE}
@@
         bottom_annotation_height = unit(5, "in"),
-        row_title = "Genes", column_title = "Cancer Cell Lines (Broad IDs)",
+        row_title = "Genes", column_title = "Cancer Cell Lines",
         col = colorRamp2(c(min(chm_scores_cgc), 0, max(chm_scores_cgc)), c("purple4", "white", "seagreen4")),
@@
 
-chm_ge_plot_cgc <- Heatmap(chm_ge_cgc, name = "Gene Expression (RPKM)",
-        col = colorRamp2(c(min(chm_ge_cgc[!is.na(chm_ge_cgc)]), 0.25, max(chm_ge_cgc[!is.na(chm_ge_cgc)])), c("dodgerblue4", "white", "firebrick4")),
+chm_ge_plot_cgc <- Heatmap(chm_ge_cgc, name = "Gene Expression [log2(RPKM)]",
+        col = colorRamp2(c(min(chm_ge_cgc[!is.na(chm_ge_cgc)]), 0, max(chm_ge_cgc[!is.na(chm_ge_cgc)])), c("dodgerblue4", "white", "firebrick4")),
         na_col = "black",
         cluster_rows = FALSE, cluster_columns = FALSE,
-        show_row_names = FALSE, show_column_names = FALSE,
+        row_names_gp = gpar(fontsize = 10), show_column_names = FALSE,
         column_title = "Gene Expression",
@@
         width = 1)
-chm_cn_plot_cgc <- Heatmap(chm_cn_cgc, name = "Copy Number",
-        col = colorRamp2(c(min(chm_cn_cgc[!is.na(chm_cn_cgc)]), 2, max(chm_cn_cgc[!is.na(chm_cn_cgc)])), c("dodgerblue4", "white", "firebrick4")),
+chm_cn_plot_cgc <- Heatmap(chm_cn_cgc, name = "Copy Number log2(CN/2)",
+        col = colorRamp2(c(min(chm_cn_cgc[!is.na(chm_cn_cgc)]), 0, max(chm_cn_cgc[!is.na(chm_cn_cgc)])), c("white", "thistle2", "mediumorchid4")),
         na_col = "black",
         cluster_rows = FALSE, cluster_columns = FALSE,
-        show_row_names = FALSE, show_column_names = FALSE,
+        row_names_gp = gpar(fontsize = 10), show_column_names = FALSE,
         column_title = "Copy Number",
@@
         cluster_rows = FALSE, cluster_columns = FALSE,
-        show_row_names = FALSE, show_column_names = FALSE,
+        row_names_gp = gpar(fontsize = 10), show_column_names = FALSE,
         column_title = "Mutation Status",
@@
 chm_ge_plot_cgc <- Heatmap(chm_ge_cgc, name = "Gene Expression (RPKM)",
-        col = colorRamp2(c(min(chm_ge_cgc[!is.na(chm_ge_cgc)]), 0.25, max(chm_ge_cgc[!is.na(chm_ge_cgc)])), c("dodgerblue4", "white", "firebrick4")),
+        col = colorRamp2(c(min(chm_ge_cgc[!is.na(chm_ge_cgc)]), 0, max(chm_ge_cgc[!is.na(chm_ge_cgc)])), c("dodgerblue4", "white", "firebrick4")),
         na_col = "black",
         cluster_rows = FALSE, cluster_columns = FALSE,
-        show_row_names = FALSE, show_column_names = FALSE,
+        row_names_gp = gpar(fontsize = 10), show_column_names = FALSE,
         column_title = "Gene Expression",
@@
 chm_cn_plot_cgc <- Heatmap(chm_cn_cgc, name = "Copy Number",
-        col = colorRamp2(c(min(chm_cn_cgc[!is.na(chm_cn_cgc)]), 2, max(chm_cn_cgc[!is.na(chm_cn_cgc)])), c("dodgerblue4", "white", "firebrick4")),
+        col = colorRamp2(c(min(chm_cn_cgc[!is.na(chm_cn_cgc)]), 0, max(chm_cn_cgc[!is.na(chm_cn_cgc)])), c("dodgerblue4", "white", "firebrick4")),
         na_col = "black",
         cluster_rows = FALSE, cluster_columns = FALSE,
-        show_row_names = FALSE, show_column_names = FALSE,
+        row_names_gp = gpar(fontsize = 10), show_column_names = FALSE,
         column_title = "Copy Number",
@@
 
+```{r fig.height=12, fig.width=12, include=FALSE}
+makeCRISPRgrob("KRAS")
+```
+
 Plot code:
@@
 
+```{r fig.height=12, fig.width=12, include=FALSE}
+makeCRISPRlinplot("KRAS")
+```
+
 Plot code:
@@
 pwalk(list(crispr_all_lins_paths, crispr_all_lins), ggsave, path = "./plots_18Q3/crispr_lineage_plots_cgc", dpi = 300, width = 12, height = 12, units = "in")
-```
-
-```{r}
-makeCRISPRlinplot("HMGA1")
-test <- filter(crispr_signif_lineage, Hugo_Symbol == "HMGA1")
 ```

### 2018-08-30 lineages_18Q3.Rmd

@@
 library(ggpubr)
+library(ggsignif)
 library(rowr)
@@
     labs(y = "CERES Score", color = "Mutation Status",
-         x = paste0(g, " Copy number"), title = "Copy Number",
+         x = paste0(g, " Theoretical Copy number"), title = "Copy Number",
          subtitle = "r: Pearson correlation coeffcient")
@@
            subtitle = "Lineages sorted by increasing p-value; labels indicate unadjusted p-value / BH-corrected p-value.")
+    return(plot)
+  }
+}
+```
+
+### Make tissue plot
+
+```{r}
+makeCRISPRtissueplot <- function(g) {
+  sig <- filter(crispr_signif_tissue, Hugo_Symbol == g)
+  if(nrow(sig) == 0) {
+    return(NULL)
+  }
+  else {
+    gene <- filter(crispr_data, Hugo_Symbol == g)
+    gene <- merge(gene, sig, by = c("Hugo_Symbol", "primary_tissue"))
+    gene <- mutate(gene, primary_tissue = reorder(primary_tissue, p, mean))
+    crispr_color <- as.character(gene$Color)
+    names(crispr_color) <- gene$Mutation_Status
+    score_range <- abs(range(gene$Score)[2] - range(gene$Score)[1])
+    round_accuracy <- ifelse(score_range <= 2, 0.25,
+                             ifelse(score_range <= 3, 0.5, 1.0))
+
+    plot <- ggplot(data = gene, aes(x = primary_tissue, y = Score)) +
+      geom_point(alpha = 0.5, mapping = aes(color = Mutation_Status)) +
+      scale_color_manual(values = crispr_color) +
+      coord_cartesian(y = c(min(gene$Score), round_any(x = max(gene$Score), accuracy = round_accuracy, f = ceiling))) +
+      geom_signif(data = gene, mapping = aes(xmin = primary_tissue, xmax = primary_tissue, annotations = paste(p.short, "\n", p.adj.short), y_position = max(gene$Score)), manual = TRUE, tip_length   = 0, size = 0, textsize = 3) +
+      theme(legend.position = "top", axis.text.x = element_text(angle = 70, hjust = 1, size = 10)) +
+      labs(y = "CERES Score",
+           x = "Primary Tissue",
+           color = "Mutation Status",
+           title = paste0(g, ": CERES score by cell line primary tissue"),
+           subtitle = "Primary tissues sorted by increasing p-value; labels indicate unadjusted p-value / BH-corrected p-value.")
     return(plot)
@@
 
-###  Metadata exploration
-
-```{r}
-tissue_summ <- crispr_meta %>% group_by(primary_tissue) %>% tally()
-disease_summ <- ccl_info %>% group_by(Primary.Disease) %>% tally()
-```
-
-```{r fig.height=5, fig.width=8}
-ggplot(data = tissue_summ) + 
-  aes(x = 0, y = n, fill = primary_tissue, label = primary_tissue) +
-  geom_histogram(color = "black", stat = "identity") +
-  geom_text(position = position_stack(vjust = 0.5))
-```
-
 ```{r}
@@
 # Convert log2 ratios (log2(CN/2)) to CN
-# cn[2:ncol(cn)] <- lapply(cn[2:ncol(cn)], function(x) 2 * (2 ^ x))
+cn[2:ncol(cn)] <- lapply(cn[2:ncol(cn)], function(x) 2 * (2 ^ x))
 
@@
 
+## CRISPR dependency probabilities
+
+```{r}
+dep <- read.delim("./data_munging/gene_dependency_18Q3.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
+# Remove Entrez gene IDs from colnames
+colnames(dep) <- gsub(" .*", "", colnames(dep))
+```
+
 ## CRISPR data and annotations
@@
 
+# Melt dependency probabilities dataset for merging
+dep_melt <- melt(dep, id.vars = "Broad_ID", measure.vars = colnames(dep)[2:ncol(dep)], variable.name = "Hugo_Symbol", value.name = "Dep_Prob")
+
+# Merge dependency probabilities
+crispr_melt <- merge(crispr_melt, dep_melt, by = c("Broad_ID", "Hugo_Symbol"), all.x = TRUE)
+
 # Merge cell line metadata
@@
 crispr_ccl <- data.frame("Broad_ID" = crispr_data$Broad_ID)
-write.table(crispr_data[, c("Hugo_Symbol", "Broad_ID", "Score", "Primary.Disease", "primary_tissue", "Mutation_Status")], file = "~/Desktop/crispr_data_select.tsv", quote = FALSE, sep = "\t")
+# write.table(crispr_data[, c("Hugo_Symbol", "Broad_ID", "Score", "Primary.Disease", "primary_tissue", "Mutation_Status")], file = "~/Desktop/crispr_data_select.tsv", quote = FALSE, sep = "\t")
 ```
@@
 
-# Mutation exploration
+# Exploration
 
@@
 
+##  Metadata
+
+```{r}
+tissue_summ <- crispr_meta %>% group_by(primary_tissue) %>% tally()
+disease_summ <- ccl_info %>% group_by(Primary.Disease) %>% tally()
+```
+
+```{r fig.height=5, fig.width=8}
+ggplot(data = tissue_summ) + 
+  aes(x = 0, y = n, fill = primary_tissue, label = primary_tissue) +
+  geom_histogram(color = "black", stat = "identity") +
+  geom_text(position = position_stack(vjust = 0.5))
+```
+
+## Mutations
+
 ```{r}
@@
 
-```{r fig.height=6, fig.width=12}
+```{r fig.height=3, fig.width=6}
 ggplot(data = maf_annot, aes(x = primary_tissue, y = n)) +
   geom_jitter(alpha = 0.6, size = 0.7, position = position_jitter(w = 0.15)) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  labs(title = "Distribution of mutations across cell lines and primary tissues", subtitle = "Each data point represents a single cell line.", x = "Primary Tissue", y = "Number of Mutations")
+```
+
+## Dependency probabilities
+
+```{r fig.height=3, fig.width=6}
+ggplot(data = crispr_data, aes(x = Dep_Prob)) +
+  geom_histogram(breaks = seq(0, 1, by = 0.05), fill = "darkslategray3", color = "black", alpha = 0.7) +
+  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
+  scale_y_continuous(breaks = seq(0, 5500000, by = 500000), labels = formatC(seq(0, 5500000, by = 500000), format = "d")) +
+  stat_bin(breaks = seq(0, 1, by = 0.05), geom = "text", colour = "black", size = 3.5, aes(label = ..count..), vjust = -1) +
+  labs(title = "Distribution of all dependency probabilities", x = "Probability of Real Dependency", y = "Frequency")
+```
+
+```{r}
+dep95 <- filter(crispr_data, Dep_Prob >= 0.95)
+```
+
+```{r fig.height=6, fig.width=8}
+ggplot(data = dep95, aes(x = Dep_Prob)) +
+  geom_histogram(mapping = aes(fill = primary_tissue), breaks = seq(0.95, 1, by = 0.005), color = "black", alpha = 0.7) +
+  scale_y_continuous(breaks = seq(0, 60000, by = 10000), labels = formatC(seq(0, 60000, by = 10000), format = "d")) +
+  theme(legend.position = "bottom") +
+  guides(fill = guide_legend(nrow = 3, byrow = FALSE)) +
+  stat_bin(breaks = seq(0.95, 1, by = 0.005), geom = "text", color = "black", size = 3.5, aes(label = ..count..), vjust = -1) +
+  labs(title = "Distribution of all dependency probabilities > 0.95", x = "Probability of Real Dependency", y = "Frequency", fill = "Primary Tissue")
 ```
@@
 
-knitr::kable(filter(crispr_signif, p < 0.1)[, c(1, 5, 6, 7, 8, 10)], caption = "CRISPR Screen: Wilcoxon Test Results Comparing Mutant and Wildtype Cell Lines, p < 0.1 (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(filter(crispr_signif, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CRISPR Screen: Wilcoxon Test Results Comparing Mutant and Wildtype Cell Lines, p < 0.1 (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
-knitr::kable(filter(crispr_signif_lineage, p < 0.1)[, c(1, 2, 5, 6, 7, 8, 10)], caption = "CRISPR Screen: Wilcoxon Test Results Comparing Mutant and Wildtype Cell Lines by Lineage, p < 0.1 (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(filter(crispr_signif_lineage, p < 0.05)[, c("Hugo_Symbol", "lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CRISPR Screen: Wilcoxon Test Results Comparing Mutant and Wildtype Cell Lines by Lineage, p < 0.1 (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
-```{r, eval=TRUE}
+```{r, eval=FALSE}
 crispr_signif_tissue <- compare_means(Score ~ Mutation_Status, group.by = c("Hugo_Symbol", "primary_tissue"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
@@
 
-knitr::kable(filter(crispr_signif_tissue, p < 0.1)[, c("Hugo_Symbol", "primary_tissue", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CRISPR Screen: Wilcoxon Test Results Comparing Mutant and Wildtype Cell Lines by Primary Tissue, p < 0.1 (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(filter(crispr_signif_tissue, p < 0.05)[, c("Hugo_Symbol", "primary_tissue", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CRISPR Screen: Wilcoxon Test Results Comparing Mutant and Wildtype Cell Lines by Primary Tissue, p < 0.1 (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
-knitr::kable(filter(shrna_signif, p < 0.1)[, c(1, 5, 6, 7, 8, 10)], caption = "shRNA Screen: Wilcoxon Test Results Comparing Mutant and Wildtype Cell Lines, p < 0.1  (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(filter(shrna_signif, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "shRNA Screen: Wilcoxon Test Results Comparing Mutant and Wildtype Cell Lines, p < 0.1  (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 ```{r}
-mean(chm_cn_cgc[!is.na(chm_cn_cgc)])
+colnames(chm_annot)
 ```
@@
 
+chm_annot_list <- HeatmapAnnotation(df = chm_annot,annotation_legend_param = list(Primary_Disease = list(nrow = 6, title = "Primary Disease", title_position = "topleft"), Primary_Tissue = list(nrow = 6, title = "Primary_Tissue", title_position = "topleft"), Culture_Type = list(nrow = 6, title = "Culture Type", title_position = "topleft"), Source = list(nrow = 6, title = "Source", title_position = "topleft")))
+
 chm_plot_cgc <- Heatmap(chm_scores_cgc, name = "CERES Score",
-        bottom_annotation = HeatmapAnnotation(df = chm_annot),
+        bottom_annotation = chm_annot_list,
         bottom_annotation_height = unit(5, "in"),
@@
 pdf("./plots_18Q3/crispr_heatmap_euclidean_all_cgc.pdf", width = 100, height = 100, paper = "special")
-draw(chm_all_plot_cgc, heatmap_legend_side = "right", annotation_legend_side = "right")
+draw(chm_all_plot_cgc, heatmap_legend_side = "bottom", annotation_legend_side = "bottom")
 seekViewport("annotation_Cell_Line_SSMD")
@@
 
+## Sorted tissue plots
+
+```{r fig.height=12, fig.width=12, include=FALSE}
+makeCRISPRtissueplot("KRAS")
+```
+
+Plot code:
+```{r, eval=FALSE}
+crispr_data_cgc <- filter(crispr_data, Hugo_Symbol %in% cgc$Hugo_Symbol)
+crispr_all_genes <- unique(crispr_data_cgc$Hugo_Symbol)
+crispr_all_lins <- lapply(crispr_all_genes, makeCRISPRtissueplot)
+crispr_all_lins_paths <- paste0(crispr_all_genes, "_crispr_tissue.png")
+pwalk(list(crispr_all_lins_paths, crispr_all_lins), ggsave, path = "./plots_18Q3/crispr_tissue_plots_cgc", dpi = 300, width = 12, height = 12, units = "in")
+```
+
+Data management:
+```{r}
+crispr_all_bygene <- paste0(list.files("./plots_18Q3/crispr_tissue_plots_cgc", full.names = TRUE))
+names(crispr_all_bygene) <- str_replace_all(crispr_all_bygene, c("_crispr_tissue.png" = "", "./plots_18Q3/crispr_tissue_plots_cgc/" = ""))
+crispr_bygene_order <- c(intersect(crispr_signif$Hugo_Symbol, names(crispr_all_bygene)), setdiff(names(crispr_all_bygene), crispr_signif$Hugo_Symbol))
+crispr_all_bygene <- crispr_all_bygene[match(crispr_bygene_order, names(crispr_all_bygene))]
+bsselect(crispr_all_bygene, type = "img", selected = "KRAS", live_search = TRUE, show_tick = TRUE, height = 300, frame_height = 275)
+```
+
 # References

### 2018-08-31 lineages_18Q3.Rmd

@@
 maf_raw <- read.delim("./data_munging/CCLE_DepMap_18q3_maf_20180718.txt.gz", header = TRUE, sep = "\t")
-
-# Remove silent mutations
-maf_df <- maf_raw[maf_raw$Variant_Classification != "Silent",]
+# Filter for cell lines in CRISPR screen
+maf_raw <- filter(maf_raw, Broad_ID %in% unique(crispr_meta$Broad_ID))
 
 # Select columns
-maf_df <- unique(subset(maf_raw, select = c("Hugo_Symbol", "Tumor_Sample_Barcode", "Broad_ID")))
-colnames(maf_df)[2] <- "CCLE_Name"
+maf_df <- subset(maf_raw, select = c("Hugo_Symbol", "Tumor_Sample_Barcode", "Broad_ID", "Variant_Classification", "isDeleterious"))
+colnames(maf_df)[colnames(maf_df) == "Tumor_Sample_Barcode"] <- "CCLE_Name"
 # Add Mutation_Status column
-maf_df$Mutation_Status <- "Mutant"
-
-# MAF summary table
+maf_df$Mutation_Status <- ifelse(maf_df$Variant_Classification == "Missense_Mutation" | maf_df$isDeleterious == TRUE, "Mutant", "Other")
+maf_df <- unique(subset(maf_df, select = c("Hugo_Symbol", "CCLE_Name", "Broad_ID", "Mutation_Status")))
+
+# Whole MAF summary table
 maf_summ <- maf_raw[, c("Variant_Classification", "isDeleterious")] %>% group_by(Variant_Classification, isDeleterious) %>% tally()
-maf_summ$percent <- maf_summ$n / sum(maf_summ$n) * 100
+maf_summ$Percent <- format(round(maf_summ$n / sum(maf_summ$n) * 100, 4), nsmall = 2)
+maf_summ$isDeleterious <- ifelse(maf_summ$isDeleterious == "TRUE", "Yes", "No")
 knitr::kable(maf_summ, caption = "Distribution of variant classifications in the MAF file") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
@@
 crispr_muts <- merge(crispr_melt, maf_df, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
-crispr_muts <- crispr_muts %>% mutate(Mutation_Status = if_else(is.na(Mutation_Status), "Wildtype", Mutation_Status))
+crispr_muts <- crispr_muts %>% mutate(Mutation_Status = if_else(is.na(Mutation_Status), "Other", Mutation_Status))
 crispr_muts$Hugo_Symbol <- factor(crispr_muts$Hugo_Symbol)
 
-# Summarize number of mutant and wildtype cell lines
+# Summarize number of mutant and Other cell lines
 crispr_muts_summ <- crispr_muts %>% group_by(Hugo_Symbol) %>%
-  summarize(N_Wildtype = sum(Mutation_Status == "Wildtype"),
+  summarize(N_Other = sum(Mutation_Status == "Other"),
             N_Mutant = sum(Mutation_Status == "Mutant"))
@@
 # Add Color column
-crispr_data$Color <- ifelse(crispr_data$Mutation_Status == "Wildtype", "cyan3", "darkorchid")
+crispr_data$Color <- ifelse(crispr_data$Mutation_Status == "Other", "cyan3", "darkorchid")
 crispr_data$Color <- factor(crispr_data$Color)
@@
 
+setdiff(unique(crispr_data$Broad_ID), unique(maf_df$Broad_ID))
+setdiff(unique(crispr_data$Broad_ID), unique(cn_melt$Broad_ID))
+setdiff(unique(crispr_data$Broad_ID), unique(ge_melt$Broad_ID))
+
 length(intersect(intersect(unique(crispr_data$Broad_ID), unique(cn_melt$Broad_ID)), unique(ge_melt$Broad_ID)))
@@
 shrna_muts <- merge(shrna_melt, maf_df, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
-shrna_muts <- shrna_muts %>% mutate(Mutation_Status = if_else(is.na(Mutation_Status), "Wildtype", Mutation_Status))
+shrna_muts <- shrna_muts %>% mutate(Mutation_Status = if_else(is.na(Mutation_Status), "Other", Mutation_Status))
 shrna_muts$Hugo_Symbol <- factor(shrna_muts$Hugo_Symbol)
 
-# Summarize number of mutant and wildtype cell lines
+# Summarize number of mutant and Other cell lines
 shrna_muts_summ <- shrna_muts %>% group_by(Hugo_Symbol) %>%
-  summarize(N_Wildtype = sum(Mutation_Status == "Wildtype"),
+  summarize(N_Other = sum(Mutation_Status == "Other"),
             N_Mutant = sum(Mutation_Status == "Mutant"))
@@
 # Add Color column
-shrna_data$Color <- ifelse(shrna_data$Mutation_Status == "Wildtype", "cyan3", "darkorchid")
+shrna_data$Color <- ifelse(shrna_data$Mutation_Status == "Other", "cyan3", "darkorchid")
 shrna_data$Color <- factor(shrna_data$Color)
@@
 
-```{r fig.height=5, fig.width=8}
+```{r fig.height=12, fig.width=3}
 ggplot(data = tissue_summ) + 
@@
   geom_histogram(color = "black", stat = "identity") +
-  geom_text(position = position_stack(vjust = 0.5))
+  geom_text(position = position_stack(vjust = 0.5)) +
+  scale_y_continuous(breaks = seq(0, 500, by = 25), labels = seq(0, 500, by = 25)) +
+  coord_cartesian(ylim = c(0, 500)) +
+  theme(legend.position = "none", axis.text.x = element_blank(), axis.ticks.x = element_blank(), axis.title.x = element_blank()) +
+  labs(y = "Count")
 ```
@@
 ```{r}
-maf_annot <- merge(maf_raw[maf_raw$Variant_Classification != "Silent",] %>% group_by(Broad_ID) %>% tally(), crispr_meta, by = "Broad_ID", all.y = TRUE)
-```
-
-```{r fig.height=3, fig.width=6}
-ggplot(data = maf_annot, aes(x = primary_tissue, y = n)) +
-  geom_jitter(alpha = 0.6, size = 0.7, position = position_jitter(w = 0.15)) +
+maf_df_filt <- filter(maf_df, Hugo_Symbol %in% unique(crispr_data$Hugo_Symbol))
+maf_summ_filt <- maf_df_filt %>% group_by(Mutation_Status) %>% tally()
+maf_summ_filt$Percent <- format(round(maf_summ_filt$n / sum(maf_summ_filt$n) * 100, 4), nsmall = 2)
+maf_summ_filt$Percent <- as.numeric(as.character(maf_summ_filt$Percent))
+```
+
+Distribution of mutations across cell lines and primary tissues. Each data point represents a single cell line.
+```{r fig.height=4, fig.width=10}
+maf_ccl_annot <- merge(maf_df %>% group_by(Broad_ID) %>% tally(), crispr_meta, by = "Broad_ID", all.y = TRUE)
+
+maf_ccl_annot_plot <- ggplot(data = maf_ccl_annot, aes(x = primary_tissue, y = n, color = primary_tissue)) +
+  geom_jitter(alpha = 0.8, size = 1, position = position_jitter(w = 0.25)) +
+  scale_y_continuous(breaks = seq(0, 9000, by = 1000), labels = seq(0, 9000, by = 1000)) +
+  theme(axis.text.x = element_text(angle = 30, hjust = 1), legend.position = "none") +
+  labs(x = "Primary Tissue", y = "Number of Mutations")
+
+ggsave(filename = "./plots_18Q3/crispr/maf_ccl_annot_plot.pdf", plot = maf_ccl_annot_plot, width = 12, height = 5, device = "pdf")
+```
+
+```{r fig.height=6, fig.width=12}
+maf_gene_annot <- maf_df_filt %>% group_by(Hugo_Symbol) %>% tally()
+
+ggplot(data = maf_gene_annot, aes(x = n)) +
+  geom_histogram(breaks = seq(0, 600, by = 20), fill = "darkslategray3", color = "black", alpha = 0.7) +
+  coord_cartesian(ylim = c(0, 13000)) +
+  scale_y_continuous(breaks = seq(0, 13500, by = 500), labels = formatC(seq(0, 13500, by = 500), format = "d")) +
+  scale_x_continuous(breaks = seq(0, 600, by = 20), labels = seq(0, 600, by = 20)) +
   theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-  labs(title = "Distribution of mutations across cell lines and primary tissues", subtitle = "Each data point represents a single cell line.", x = "Primary Tissue", y = "Number of Mutations")
+  stat_bin(breaks = seq(0, 600, by = 20), geom = "text", colour = "black", size = 2.5, aes(label = ..count..), vjust = -0.2, angle = 45, hjust = -0.1) +
+  labs(x = "Number of Mutations", y = "Frequency", title = paste0("Distribution of mutational load for ", length(unique(maf_gene_annot$Hugo_Symbol)), " genes in the CCLE MAF file across all ", length(unique(crispr_ccl$Broad_ID)), " cell lines in the CRISPR screen"))
 ```
@@
 
-```{r fig.height=3, fig.width=6}
-ggplot(data = crispr_data, aes(x = Dep_Prob)) +
+```{r fig.height=6, fig.width=12}
+drop_prob_100 <- ggplot(data = crispr_data, aes(x = Dep_Prob)) +
   geom_histogram(breaks = seq(0, 1, by = 0.05), fill = "darkslategray3", color = "black", alpha = 0.7) +
@@
   labs(title = "Distribution of all dependency probabilities", x = "Probability of Real Dependency", y = "Frequency")
-```
-
-```{r}
-dep95 <- filter(crispr_data, Dep_Prob >= 0.95)
-```
-
-```{r fig.height=6, fig.width=8}
-ggplot(data = dep95, aes(x = Dep_Prob)) +
-  geom_histogram(mapping = aes(fill = primary_tissue), breaks = seq(0.95, 1, by = 0.005), color = "black", alpha = 0.7) +
+
+dep_prob_5 <- ggplot(data = filter(crispr_data, Dep_Prob >= 0.95), aes(x = Dep_Prob)) +
+  geom_histogram(mapping = aes(fill = primary_tissue), breaks = seq(0.95, 1, by = 0.005), color = "black") +
   scale_y_continuous(breaks = seq(0, 60000, by = 10000), labels = formatC(seq(0, 60000, by = 10000), format = "d")) +
   theme(legend.position = "bottom") +
-  guides(fill = guide_legend(nrow = 3, byrow = FALSE)) +
+  guides(fill = guide_legend(nrow = 4, byrow = FALSE)) +
   stat_bin(breaks = seq(0.95, 1, by = 0.005), geom = "text", color = "black", size = 3.5, aes(label = ..count..), vjust = -1) +
   labs(title = "Distribution of all dependency probabilities > 0.95", x = "Probability of Real Dependency", y = "Frequency", fill = "Primary Tissue")
+
+dep_prob_inset <- dep_prob_100 + annotation_custom(ggplotGrob(dep_prob_5), xmin = 0.49, xmax = 0.99, ymin = 2500000, ymax = 5000000)
+
+ggsave("./../crispr_lineages_giant_files/dependency_probability_inset.pdf", plot = dep_prob_inset, width = 12, height = 6, units = "in", device = "pdf")
 ```
@@
 
-knitr::kable(filter(crispr_signif, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CRISPR Screen: Wilcoxon Test Results Comparing Mutant and Wildtype Cell Lines, p < 0.1 (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(filter(crispr_signif, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CRISPR Screen: Wilcoxon Test Results Comparing Mutant and Other Cell Lines, p < 0.1 (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 crispr_signif_lineage <- adj_signif(crispr_signif_lineage)
-crispr_signif_lineage <- mutate(crispr_signif_lineage, lineage_name = reorder(lineage_name, p.adj, mean))
+crispr_signif_lineage <- crispr_signif_lineage[order(crispr_signif_lineage$p),]
 saveRDS(crispr_signif_lineage, "./data_munging/rds/crispr_signif_lineage.rds")
@@
 
-knitr::kable(filter(crispr_signif_lineage, p < 0.05)[, c("Hugo_Symbol", "lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CRISPR Screen: Wilcoxon Test Results Comparing Mutant and Wildtype Cell Lines by Lineage, p < 0.1 (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(filter(crispr_signif_lineage, p < 0.05)[, c("Hugo_Symbol", "lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CRISPR Screen: Wilcoxon Test Results Comparing Mutant and Other Cell Lines by Lineage, p < 0.1 (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 crispr_signif_tissue <- adj_signif(crispr_signif_tissue)
-# crispr_signif_tissue <- mutate(crispr_signif_tissue, primary_tissue = reorder(primary_tissue, p.adj, mean))
 crispr_signif_tissue <- crispr_signif_tissue[order(crispr_signif_tissue$p),]
@@
 
-knitr::kable(filter(crispr_signif_tissue, p < 0.05)[, c("Hugo_Symbol", "primary_tissue", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CRISPR Screen: Wilcoxon Test Results Comparing Mutant and Wildtype Cell Lines by Primary Tissue, p < 0.1 (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(filter(crispr_signif_tissue, p < 0.05)[, c("Hugo_Symbol", "primary_tissue", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CRISPR Screen: Wilcoxon Test Results Comparing Mutant and Other Cell Lines by Primary Tissue, p < 0.1 (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
-knitr::kable(filter(shrna_signif, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "shRNA Screen: Wilcoxon Test Results Comparing Mutant and Wildtype Cell Lines, p < 0.1  (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(filter(shrna_signif, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "shRNA Screen: Wilcoxon Test Results Comparing Mutant and Other Cell Lines, p < 0.1  (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
 ```

### 2018-09-03 lineages_18Q3.Rmd
replace old Rmd with new

@@
   labs(title = "Distribution of all dependency probabilities > 0.95", x = "Probability of Real Dependency", y = "Frequency", fill = "Primary Tissue")
-
-dep_prob_inset <- dep_prob_100 + annotation_custom(ggplotGrob(dep_prob_5), xmin = 0.49, xmax = 0.99, ymin = 2500000, ymax = 5000000)
-
-ggsave("./../crispr_lineages_giant_files/dependency_probability_inset.pdf", plot = dep_prob_inset, width = 12, height = 6, units = "in", device = "pdf")
 ```

### 2018-09-05 lineages_18Q3.Rmd

@@
   # Cell line lineage
-  plot_lin <- ggplot(data = gene, aes(x = lineage_name, y = Score, color = Mutation_Status)) +
+  plot_tissue <- ggplot(data = gene, aes(x = primary_tissue, y = Score, color = Mutation_Status)) +
     geom_point(alpha = 0.5) +
@@
     theme(legend.position = "none") +
-    labs(y = "CERES Score", x = "Cell Line Lineage",
+    labs(y = "CERES Score", x = "Primary Tissue",
          color = "Mutation Status", title = g)
@@
   # Arrange plots
-  plot <- ggarrange(ggarrange(plot_lin, nrow = 1, labels = c("A")),
+  plot <- ggarrange(ggarrange(plot_tissue, nrow = 1, labels = c("A")),
                     ggarrange(plot_mut, plot_cn, plot_ge, nrow = 3,
@@
 
-### Make individual heatmaps per cluster
-
-Take in a sorted gene list from a larger heatmap and produce smaller, individual heatmaps:
-```{r, eval=FALSE}
-makeHeatmaps <- function(clust_obj, clust_num) {
-  chm_plot_cols <- colnames(clust_obj)
-  chm_plot_rows <- rownames(clust_obj)
-
-  chm_plot <- Heatmap(clust_obj, name = "CERES Score",
-          bottom_annotation = HeatmapAnnotation(df = chm_annot),
-          bottom_annotation_height = unit(5, "in"),
-          row_title = "Genes", column_title = "Cancer Cell Lines (Broad IDs)",
-          col = colorRamp2(c(min(chm_scores), 0, max(chm_scores)), c("purple4", "white", "seagreen4")),
-          na_col = "black",
-          column_title_gp = gpar(fontsize = 60, fontface = "bold"),
-          show_column_names = FALSE,
-          row_title_gp = gpar(fontsize = 60, fontface = "bold"),
-          show_row_names = FALSE,
-          row_dend_reorder = TRUE,
-          column_dend_reorder = TRUE,
-          column_order = chm_plot_cols,
-          row_order = chm_plot_rows,
-          column_dend_height = unit(4, "in"),
-          row_dend_width = unit(4, "in"),
-          width = 3)
-
-  chm_ge_plot <- Heatmap(chm_ge[row_order(chm_scores_draw)[[clust_num]],], name = "Gene Expression (RPKM)",
-          col = colorRamp2(c(min(chm_ge[!is.na(chm_ge)]), 0.25, max(chm_ge[!is.na(chm_ge)])), c("dodgerblue4", "white", "firebrick4")),
-          na_col = "black",
-          cluster_rows = FALSE, cluster_columns = FALSE,
-          show_row_names = FALSE, show_column_names = FALSE,
-          column_title = "Gene Expression",
-          column_title_gp = gpar(fontsize = 60, fontface = "bold"),
-          column_order = chm_plot_cols,
-          row_order = chm_plot_rows,
-          width = 1)
-  chm_cn_plot <- Heatmap(chm_cn[row_order(chm_scores_draw)[[clust_num]],], name = "Copy Number",
-          col = colorRamp2(c(min(chm_cn[!is.na(chm_cn)]), 2, max(chm_cn[!is.na(chm_cn)])), c("dodgerblue4", "white", "firebrick4")),
-          na_col = "black",
-          cluster_rows = FALSE, cluster_columns = FALSE,
-          show_row_names = FALSE, show_column_names = FALSE,
-          column_title = "Copy Number",
-          column_title_gp = gpar(fontsize = 60, fontface = "bold"),
-          column_order = chm_plot_cols,
-          row_order = chm_plot_rows,
-          width = 1)
-  chm_mut_plot <- Heatmap(chm_mut[row_order(chm_scores_draw)[[clust_num]],], name = "Mutation Status",
-          na_col = "black",
-          col = c("cyan3", "darkorchid"),
-          cluster_rows = FALSE, cluster_columns = FALSE,
-          show_row_names = FALSE, show_column_names = FALSE,
-          column_title = "Mutation Status",
-          column_title_gp = gpar(fontsize = 60, fontface = "bold"),
-          column_order = chm_plot_cols,
-          row_order = chm_plot_rows,
-          width = 1)
-
-  chm_all_plot <- chm_plot + chm_ge_plot + chm_cn_plot + chm_mut_plot
-
-  pdf(paste0("./plots_18Q3/crispr_heatmap_clustered/crispr_heatmap_all_c", clust_num, ".pdf"), width = 100, height = 100, paper = "special")
-  draw(chm_all_plot, heatmap_legend_side = "right", annotation_legend_side = "right")
-  seekViewport("annotation_Cell_Line_SSMD")
-  grid.text("Cell Line SSMD", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
-  seekViewport("annotation_Cas9_Activity")
-  grid.text("Cas9 Activity", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
-  seekViewport("annotation_Culture_Type")
-  grid.text("Culture Type", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
-  seekViewport("annotation_Primary_Tissue")
-  grid.text("Primary Tissue", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
-  seekViewport("annotation_Primary_Disease")
-  grid.text("Primary Disease", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
-  seekViewport("annotation_Gender")
-  grid.text("Gender", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
-  seekViewport("annotation_Source")
-  grid.text("Source", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
-  dev.off()
-
-  pdf(paste0("./plots_18Q3/crispr_heatmap_ge_c", clust_num, ".pdf"), width = 100, height = 100, paper = "special")
-  draw(chm_plot + chm_ge_plot, heatmap_legend_side = "right", annotation_legend_side = "right")
-  seekViewport("annotation_Cell_Line_SSMD")
-  grid.text("Cell Line SSMD", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
-  seekViewport("annotation_Cas9_Activity")
-  grid.text("Cas9 Activity", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
-  seekViewport("annotation_Culture_Type")
-  grid.text("Culture Type", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
-  seekViewport("annotation_Primary_Tissue")
-  grid.text("Primary Tissue", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
-  seekViewport("annotation_Primary_Disease")
-  grid.text("Primary Disease", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
-  seekViewport("annotation_Gender")
-  grid.text("Gender", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
-  seekViewport("annotation_Source")
-  grid.text("Source", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
-  dev.off()
-
-  pdf(paste0("./plots_18Q3/crispr_heatmap_mut_c", clust_num, ".pdf"), width = 100, height = 100, paper = "special") 
-  draw(chm_plot + chm_mut_plot, heatmap_legend_side = "right", annotation_legend_side = "right")
-  seekViewport("annotation_Cell_Line_SSMD")
-  grid.text("Cell Line SSMD", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
-  seekViewport("annotation_Cas9_Activity")
-  grid.text("Cas9 Activity", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
-  seekViewport("annotation_Culture_Type")
-  grid.text("Culture Type", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
-  seekViewport("annotation_Primary_Tissue")
-  grid.text("Primary Tissue", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
-  seekViewport("annotation_Primary_Disease")
-  grid.text("Primary Disease", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
-  seekViewport("annotation_Gender")
-  grid.text("Gender", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
-  seekViewport("annotation_Source")
-  grid.text("Source", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
-  dev.off()
-
-  pdf(paste0("./plots_18Q3/crispr_heatmap_cn_c", clust_num, ".pdf"), width = 100, height = 100, paper = "special") 
-  draw(chm_plot + chm_cn_plot, heatmap_legend_side = "right", annotation_legend_side = "right")
-  seekViewport("annotation_Cell_Line_SSMD")
-  grid.text("Cell Line SSMD", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
-  seekViewport("annotation_Cas9_Activity")
-  grid.text("Cas9 Activity", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
-  seekViewport("annotation_Culture_Type")
-  grid.text("Culture Type", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
-  seekViewport("annotation_Primary_Tissue")
-  grid.text("Primary Tissue", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
-  seekViewport("annotation_Primary_Disease")
-  grid.text("Primary Disease", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
-  seekViewport("annotation_Gender")
-  grid.text("Gender", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
-  seekViewport("annotation_Source")
-  grid.text("Source", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
-  dev.off()
-}
-```
-
 ## Cell line converter
@@
 
+## Scores
+
+Distribution of scores across cell lines and primary tissues. Each data point represents a single cell line.
+```{r fig.height=4, fig.width=12}
+ceres_summ <- crispr_data %>% group_by(primary_tissue) %>% summarize(Max = max(Score),
+                                                                     Min = min(Score))
+score_summ_plot <- ggplot(data = crispr_data, aes(x = primary_tissue, color = primary_tissue)) +
+  geom_boxplot(mapping = aes(y = Score), outlier.shape = NA) +
+  geom_point(data = ceres_summ, mapping = aes(x = primary_tissue, y = Min)) +
+  geom_point(data = ceres_summ, mapping = aes(x = primary_tissue, y = Max)) +
+  scale_y_continuous(breaks = seq(-4, 6, by = 1), labels = seq(-4, 6, by = 1)) +
+  theme(axis.text.x = element_text(angle = 30, hjust = 1), legend.position = "none") +
+  labs(x = "Primary Tissue", y = "CERES Score")
+
+# ggsave(filename = "./plots_18Q3/crispr/ceres_score_summ_plot.pdf", plot = score_summ_plot, width = 12, height = 4, device = "pdf")
+```
+
 ## Mutations
@@
 
-ggsave(filename = "./plots_18Q3/crispr/maf_ccl_annot_plot.pdf", plot = maf_ccl_annot_plot, width = 12, height = 5, device = "pdf")
+# ggsave(filename = "./plots_18Q3/crispr/maf_ccl_annot_plot.pdf", plot = maf_ccl_annot_plot, width = 12, height = 4, device = "pdf")
 ```
@@
 saveRDS(crispr_signif, "./data_munging/rds/crispr_signif.rds")
+
+write.table(crispr_signif, file = "~/Desktop/crispr_signif_gene.csv", quote = FALSE, sep = ",", row.names = FALSE)
 ```
@@
 knitr::kable(filter(crispr_signif, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CRISPR Screen: Wilcoxon Test Results Comparing Mutant and Other Cell Lines, p < 0.1 (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+```
+
+```{r fig.height=3, fig.width=6}
+wilcox_gene_plot <- ggplot(data = crispr_signif, aes(x = p.adj)) +
+  geom_histogram(breaks = seq(0, 1, by = 0.025), fill = "darkslategray3", color = "black", alpha = 0.7) +
+  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
+  coord_cartesian(ylim = c(0, 4500)) +
+  scale_y_continuous(breaks = seq(0, 4500, by = 500), labels = formatC(seq(0, 4500, by = 500), format = "d")) +
+  stat_bin(breaks = seq(0, 1, by = 0.025), geom = "text", colour = "black", size = 3, aes(label = ..count..), vjust = 0.3, angle = 80, hjust = -0.4) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  labs(x = "BH-adjusted p-values", y = "Frequency")
+
+ggsave(filename = "./plots_18Q3/crispr/pvals_genes.pdf", plot = wilcox_gene_plot, width = 10, height = 5, device = "pdf")
 ```
@@
 saveRDS(crispr_signif_lineage, "./data_munging/rds/crispr_signif_lineage.rds")
+
+write.table(crispr_signif_lineage, file = "~/Desktop/crispr_signif_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
 ```
@@
 saveRDS(crispr_signif_tissue, "./data_munging/rds/crispr_signif_tissue.rds")
+
+write.table(crispr_signif_tissue, file = "~/Desktop/crispr_signif_tissue.csv", quote = FALSE, sep = ",", row.names = FALSE)
 ```
@@
 knitr::kable(filter(crispr_signif_tissue, p < 0.05)[, c("Hugo_Symbol", "primary_tissue", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CRISPR Screen: Wilcoxon Test Results Comparing Mutant and Other Cell Lines by Primary Tissue, p < 0.1 (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+```
+
+```{r fig.height=3, fig.width=6}
+wilcox_gene_tissue_plot <- ggplot(data = crispr_signif_tissue, aes(x = p.adj)) +
+  geom_histogram(breaks = seq(0, 1, by = 0.025), fill = "darkslateblue", color = "black", alpha = 0.7) +
+  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
+  coord_cartesian(ylim = c(0, 55000)) +
+  scale_y_continuous(breaks = seq(0, 55000, by = 5000), labels = formatC(seq(0, 55000, by = 5000), format = "d")) +
+  stat_bin(breaks = seq(0, 1, by = 0.025), geom = "text", colour = "black", size = 3, aes(label = ..count..), vjust = 0.3, angle = 80, hjust = -0.4) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  labs(x = "BH-adjusted p-values", y = "Frequency")
+
+ggsave(filename = "./plots_18Q3/crispr/pvals_genes_tissues.pdf", plot = wilcox_gene_tissue_plot, width = 10, height = 5, device = "pdf")
 ```
@@
 
-```{r}
+```{r, eval=FALSE}
 shrna_signif <- readRDS("./data_munging/rds/shrna_signif.rds")
@@
 chm_mut_grid <- merge(crispr_grid, maf_df[, c("Broad_ID", "Hugo_Symbol", "Mutation_Status")], by = c("Broad_ID", "Hugo_Symbol"), all.x = TRUE)
-chm_mut_grid$Mutation_Status <- ifelse(is.na(chm_mut_grid$Mutation_Status), 0, 1)
+chm_mut_grid$Mutation_Status <- ifelse(is.na(chm_mut_grid$Mutation_Status), "Other", chm_mut_grid$Mutation_Status)
+chm_mut_grid$Mutation_Status <- ifelse(chm_mut_grid$Mutation_Status == "Other", 0, 1)
 chm_mut <- reshape(chm_mut_grid, idvar = "Hugo_Symbol", timevar = "Broad_ID", direction = "wide")
@@
 
-### K-means clustered
-
-#### Euclidean distance
-
-Code for k-means clustered heatmap:
-```{r, eval=FALSE}
-chm_scores_plot <- Heatmap(chm_scores, name = "CERES Score",
-        bottom_annotation = HeatmapAnnotation(df = chm_annot),
+### All genes, no omics
+
+```{r, eval=FALSE}
+chm_annot_list <- HeatmapAnnotation(df = chm_annot, annotation_legend_param = list(
+  Cell_Line_SSMD = list(title = "Cell Line SSMD", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), title_position = "topcenter", legend_height = unit(2, "in")),
+  Cas9_Activity = list(title = "Cas9 Activity", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), title_position = "topcenter", legend_height = unit(2, "in")),
+  Culture_Type = list(title = "Culture Type", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), nrow = 8, title = "Culture Type", title_position = "topleft", grid_height = unit(0.3, "in")),
+  Primary_Tissue = list(title = "Primary Tissue", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), nrow = 8, title = "Primary_Tissue", title_position = "topleft", grid_height = unit(0.3, "in")),
+  Primary_Disease = list(title = "Primary Disease", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), nrow = 8, title = "Primary Disease", title_position = "topleft", grid_height = unit(0.3, "in")),
+  Gender = list(title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), grid_height = unit(0.3, "in")),
+  Source = list(title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), nrow = 8, title = "Source", title_position = "topleft", grid_height = unit(0.3, "in"))))
+
+chm_all_plot <- Heatmap(chm_scores, name = "CERES Score",
+        bottom_annotation = chm_annot_list,
         bottom_annotation_height = unit(5, "in"),
-        row_title = "Genes", column_title = "Cancer Cell Lines (Broad IDs)",
-        col = colorRamp2(c(min(chm_scores), 0, max(chm_scores)), c("purple4", "white", "seagreen4")),
+        heatmap_legend_param = list(title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), title_position = "topcenter", legend_height = unit(2, "in")),
+        row_title = "Genes", column_title = "Cancer Cell Lines",
+        col = colorRamp2(c(min(chm_scores_cgc), 0, max(chm_scores_cgc)), c("purple4", "white", "seagreen4")),
         na_col = "black",
-        column_title_gp = gpar(fontsize = 60, fontface = "bold"),
-        show_column_names = FALSE,
-        row_title_gp = gpar(fontsize = 60, fontface = "bold"),
-        show_row_names = FALSE,
+        row_title_gp = gpar(fontsize = 30, fontface = "bold"),
+        row_names_gp = gpar(fontsize = 5),
+        column_title_gp = gpar(fontsize = 30, fontface = "bold"),
+        column_names_gp = gpar(fontsize = 5),
         row_dend_reorder = TRUE,
@@
         clustering_method_columns = "complete",
-        column_dend_height = unit(4, "in"),
+        column_dend_height = unit(2, "in"),
         row_dend_width = unit(4, "in"),
-        width = 3,
-        km = 5, gap = unit(0.5, "in"))
-
-chm_scores_draw <- draw(chm_scores_plot, heatmap_legend_side = "right", annotation_legend_side = "right")
-
-pdf("./plots_18Q3/crispr_heatmap_euclidean_split5.pdf", width = 100, height = 100, paper = "special")
-chm_scores_draw
+        width = 3)
+
+pdf("./plots_18Q3/crispr_heatmap_euclidean_all.pdf", width = 50, height = 50, paper = "special")
+draw(chm_all_plot, heatmap_legend_side = "bottom", annotation_legend_side = "bottom")
 seekViewport("annotation_Cell_Line_SSMD")
-grid.text("Cell Line SSMD", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+grid.text("Cell Line SSMD", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
 seekViewport("annotation_Cas9_Activity")
-grid.text("Cas9 Activity", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+grid.text("Cas9 Activity", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
 seekViewport("annotation_Culture_Type")
-grid.text("Culture Type", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+grid.text("Culture Type", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
 seekViewport("annotation_Primary_Tissue")
-grid.text("Primary Tissue", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+grid.text("Primary Tissue", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
 seekViewport("annotation_Primary_Disease")
-grid.text("Primary Disease", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+grid.text("Primary Disease", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
 seekViewport("annotation_Gender")
-grid.text("Gender", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+grid.text("Gender", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
 seekViewport("annotation_Source")
-grid.text("Source", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+grid.text("Source", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
 dev.off()
-
-chm_scores_c1 <- chm_scores[row_order(chm_scores_draw)[[1]],]
-chm_scores_c2 <- chm_scores[row_order(chm_scores_draw)[[2]],]
-chm_scores_c3 <- chm_scores[row_order(chm_scores_draw)[[3]],]
-chm_scores_c4 <- chm_scores[row_order(chm_scores_draw)[[4]],]
-chm_scores_c5 <- chm_scores[row_order(chm_scores_draw)[[5]],]
-
-makeHeatmaps(chm_scores_c1, 1)
-makeHeatmaps(chm_scores_c2, 2)
-makeHeatmaps(chm_scores_c3, 3)
-makeHeatmaps(chm_scores_c4, 4)
-makeHeatmaps(chm_scores_c5, 5)
 ```
@@
 #### Euclidean distance
-
-```{r}
-colnames(chm_annot)
-```
 
@@
 
-chm_annot_list <- HeatmapAnnotation(df = chm_annot,annotation_legend_param = list(Primary_Disease = list(nrow = 6, title = "Primary Disease", title_position = "topleft"), Primary_Tissue = list(nrow = 6, title = "Primary_Tissue", title_position = "topleft"), Culture_Type = list(nrow = 6, title = "Culture Type", title_position = "topleft"), Source = list(nrow = 6, title = "Source", title_position = "topleft")))
+chm_annot_list <- HeatmapAnnotation(df = chm_annot, annotation_legend_param = list(
+  Cell_Line_SSMD = list(title = "Cell Line SSMD", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), title_position = "topcenter", legend_height = unit(2, "in")),
+  Cas9_Activity = list(title = "Cas9 Activity", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), title_position = "topcenter", legend_height = unit(2, "in")),
+  Culture_Type = list(title = "Culture Type", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), nrow = 8, title = "Culture Type", title_position = "topleft", grid_height = unit(0.3, "in")),
+  Primary_Tissue = list(title = "Primary Tissue", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), nrow = 8, title = "Primary_Tissue", title_position = "topleft", grid_height = unit(0.3, "in")),
+  Primary_Disease = list(title = "Primary Disease", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), nrow = 8, title = "Primary Disease", title_position = "topleft", grid_height = unit(0.3, "in")),
+  Gender = list(title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), grid_height = unit(0.3, "in")),
+  Source = list(title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), nrow = 8, title = "Source", title_position = "topleft", grid_height = unit(0.3, "in"))))
 
@@
         bottom_annotation_height = unit(5, "in"),
+        heatmap_legend_param = list(title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), title_position = "topcenter", legend_height = unit(2, "in")),
         row_title = "Genes", column_title = "Cancer Cell Lines",
@@
         na_col = "black",
-        row_title_gp = gpar(fontsize = 60, fontface = "bold"),
-        row_names_gp = gpar(fontsize = 10),
-        column_title_gp = gpar(fontsize = 60, fontface = "bold"),
-        column_names_gp = gpar(fontsize = 8),
+        row_title_gp = gpar(fontsize = 30, fontface = "bold"),
+        row_names_gp = gpar(fontsize = 5),
+        column_title_gp = gpar(fontsize = 30, fontface = "bold"),
+        column_names_gp = gpar(fontsize = 5),
         row_dend_reorder = TRUE,
@@
         clustering_method_columns = "complete",
-        column_dend_height = unit(4, "in"),
+        column_dend_height = unit(2, "in"),
         row_dend_width = unit(4, "in"),
@@
 
-chm_ge_plot_cgc <- Heatmap(chm_ge_cgc, name = "Gene Expression [log2(RPKM)]",
+chm_ge_plot_cgc <- Heatmap(chm_ge_cgc, name = "Gene Expression",
         col = colorRamp2(c(min(chm_ge_cgc[!is.na(chm_ge_cgc)]), 0, max(chm_ge_cgc[!is.na(chm_ge_cgc)])), c("dodgerblue4", "white", "firebrick4")),
+        heatmap_legend_param = list(title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), title_position = "topcenter", legend_height = unit(2, "in")),
         na_col = "black",
         cluster_rows = FALSE, cluster_columns = FALSE,
-        row_names_gp = gpar(fontsize = 10), show_column_names = FALSE,
+        row_names_gp = gpar(fontsize = 5), show_column_names = FALSE,
         column_title = "Gene Expression",
-        column_title_gp = gpar(fontsize = 60, fontface = "bold"),
+        column_title_gp = gpar(fontsize = 30, fontface = "bold"),
         column_order = chm_plot_cgc_cols,
@@
         width = 1)
-chm_cn_plot_cgc <- Heatmap(chm_cn_cgc, name = "Copy Number log2(CN/2)",
+chm_cn_plot_cgc <- Heatmap(chm_cn_cgc, name = "Copy Number",
         col = colorRamp2(c(min(chm_cn_cgc[!is.na(chm_cn_cgc)]), 0, max(chm_cn_cgc[!is.na(chm_cn_cgc)])), c("white", "thistle2", "mediumorchid4")),
+        heatmap_legend_param = list(title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), title_position = "topcenter", legend_height = unit(2, "in")),
         na_col = "black",
         cluster_rows = FALSE, cluster_columns = FALSE,
-        row_names_gp = gpar(fontsize = 10), show_column_names = FALSE,
+        row_names_gp = gpar(fontsize = 5), show_column_names = FALSE,
         column_title = "Copy Number",
-        column_title_gp = gpar(fontsize = 60, fontface = "bold"),
+        column_title_gp = gpar(fontsize = 30, fontface = "bold"),
         column_order = chm_plot_cgc_cols,
@@
         na_col = "black",
+        heatmap_legend_param = list(title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), at = c(0, 1), labels = c("Other", "Mutant"), title_position = "topcenter", grid_height = unit(0.3, "in")),
         col = c("cyan3", "darkorchid"),
         cluster_rows = FALSE, cluster_columns = FALSE,
-        row_names_gp = gpar(fontsize = 10), show_column_names = FALSE,
+        row_names_gp = gpar(fontsize = 5), show_column_names = FALSE,
         column_title = "Mutation Status",
-        column_title_gp = gpar(fontsize = 60, fontface = "bold"),
+        column_title_gp = gpar(fontsize = 30, fontface = "bold"),
         column_order = chm_plot_cgc_cols,
@@
 
-pdf("./plots_18Q3/crispr_heatmap_euclidean_all_cgc.pdf", width = 100, height = 100, paper = "special")
+pdf("./plots_18Q3/crispr_heatmap_euclidean_all_cgc.pdf", width = 50, height = 50, paper = "special")
 draw(chm_all_plot_cgc, heatmap_legend_side = "bottom", annotation_legend_side = "bottom")
 seekViewport("annotation_Cell_Line_SSMD")
-grid.text("Cell Line SSMD", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+grid.text("Cell Line SSMD", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
 seekViewport("annotation_Cas9_Activity")
-grid.text("Cas9 Activity", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+grid.text("Cas9 Activity", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
 seekViewport("annotation_Culture_Type")
-grid.text("Culture Type", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+grid.text("Culture Type", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
 seekViewport("annotation_Primary_Tissue")
-grid.text("Primary Tissue", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+grid.text("Primary Tissue", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
 seekViewport("annotation_Primary_Disease")
-grid.text("Primary Disease", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+grid.text("Primary Disease", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
 seekViewport("annotation_Gender")
-grid.text("Gender", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+grid.text("Gender", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
 seekViewport("annotation_Source")
-grid.text("Source", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+grid.text("Source", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
 dev.off()
@@
 
+chm_annot_list <- HeatmapAnnotation(df = chm_annot, annotation_legend_param = list(
+  Cell_Line_SSMD = list(title = "Cell Line SSMD", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), title_position = "topcenter", legend_height = unit(2, "in")),
+  Cas9_Activity = list(title = "Cas9 Activity", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), title_position = "topcenter", legend_height = unit(2, "in")),
+  Culture_Type = list(title = "Culture Type", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), nrow = 8, title = "Culture Type", title_position = "topleft", grid_height = unit(0.3, "in")),
+  Primary_Tissue = list(title = "Primary Tissue", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), nrow = 8, title = "Primary_Tissue", title_position = "topleft", grid_height = unit(0.3, "in")),
+  Primary_Disease = list(title = "Primary Disease", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), nrow = 8, title = "Primary Disease", title_position = "topleft", grid_height = unit(0.3, "in")),
+  Gender = list(title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), grid_height = unit(0.3, "in")),
+  Source = list(title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), nrow = 8, title = "Source", title_position = "topleft", grid_height = unit(0.3, "in"))))
+
 chm_plot_cgc <- Heatmap(chm_scores_cgc, name = "CERES Score",
-        bottom_annotation = HeatmapAnnotation(df = chm_annot),
+        bottom_annotation = chm_annot_list,
         bottom_annotation_height = unit(5, "in"),
-        row_title = "Genes", column_title = "Cancer Cell Lines (Broad IDs)",
+        heatmap_legend_param = list(title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), title_position = "topcenter", legend_height = unit(2, "in")),
+        row_title = "Genes", column_title = "Cancer Cell Lines",
         col = colorRamp2(c(min(chm_scores_cgc), 0, max(chm_scores_cgc)), c("purple4", "white", "seagreen4")),
         na_col = "black",
-        row_title_gp = gpar(fontsize = 60, fontface = "bold"),
-        row_names_gp = gpar(fontsize = 10),
-        column_title_gp = gpar(fontsize = 60, fontface = "bold"),
-        column_names_gp = gpar(fontsize = 8),
+        row_title_gp = gpar(fontsize = 30, fontface = "bold"),
+        row_names_gp = gpar(fontsize = 5),
+        column_title_gp = gpar(fontsize = 30, fontface = "bold"),
+        column_names_gp = gpar(fontsize = 5),
         row_dend_reorder = TRUE,
@@
 
-chm_ge_plot_cgc <- Heatmap(chm_ge_cgc, name = "Gene Expression (RPKM)",
+chm_ge_plot_cgc <- Heatmap(chm_ge_cgc, name = "Gene Expression",
         col = colorRamp2(c(min(chm_ge_cgc[!is.na(chm_ge_cgc)]), 0, max(chm_ge_cgc[!is.na(chm_ge_cgc)])), c("dodgerblue4", "white", "firebrick4")),
+        heatmap_legend_param = list(title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), title_position = "topcenter", legend_height = unit(2, "in")),
         na_col = "black",
         cluster_rows = FALSE, cluster_columns = FALSE,
-        row_names_gp = gpar(fontsize = 10), show_column_names = FALSE,
+        row_names_gp = gpar(fontsize = 5), show_column_names = FALSE,
         column_title = "Gene Expression",
-        column_title_gp = gpar(fontsize = 60, fontface = "bold"),
+        column_title_gp = gpar(fontsize = 30, fontface = "bold"),
         column_order = chm_plot_cgc_cols,
@@
 chm_cn_plot_cgc <- Heatmap(chm_cn_cgc, name = "Copy Number",
-        col = colorRamp2(c(min(chm_cn_cgc[!is.na(chm_cn_cgc)]), 0, max(chm_cn_cgc[!is.na(chm_cn_cgc)])), c("dodgerblue4", "white", "firebrick4")),
+        col = colorRamp2(c(min(chm_cn_cgc[!is.na(chm_cn_cgc)]), 0, max(chm_cn_cgc[!is.na(chm_cn_cgc)])), c("white", "thistle2", "mediumorchid4")),
+        heatmap_legend_param = list(title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), title_position = "topcenter", legend_height = unit(2, "in")),
         na_col = "black",
         cluster_rows = FALSE, cluster_columns = FALSE,
-        row_names_gp = gpar(fontsize = 10), show_column_names = FALSE,
+        row_names_gp = gpar(fontsize = 5), show_column_names = FALSE,
         column_title = "Copy Number",
-        column_title_gp = gpar(fontsize = 60, fontface = "bold"),
+        column_title_gp = gpar(fontsize = 30, fontface = "bold"),
         column_order = chm_plot_cgc_cols,
@@
 
-pdf("./plots_18Q3/crispr_heatmap_pearson_all_cgc.pdf", width = 100, height = 100, paper = "special")
-draw(chm_all_plot_cgc, heatmap_legend_side = "right", annotation_legend_side = "right")
+pdf("./plots_18Q3/crispr_heatmap_pearson_all_cgc.pdf", width = 50, height = 50, paper = "special")
+draw(chm_all_plot_cgc, heatmap_legend_side = "bottom", annotation_legend_side = "bottom")
 seekViewport("annotation_Cell_Line_SSMD")
-grid.text("Cell Line SSMD", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+grid.text("Cell Line SSMD", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
 seekViewport("annotation_Cas9_Activity")
-grid.text("Cas9 Activity", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+grid.text("Cas9 Activity", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
 seekViewport("annotation_Culture_Type")
-grid.text("Culture Type", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+grid.text("Culture Type", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
 seekViewport("annotation_Primary_Tissue")
-grid.text("Primary Tissue", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+grid.text("Primary Tissue", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
 seekViewport("annotation_Primary_Disease")
-grid.text("Primary Disease", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+grid.text("Primary Disease", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
 seekViewport("annotation_Gender")
-grid.text("Gender", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+grid.text("Gender", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
 seekViewport("annotation_Source")
-grid.text("Source", unit(1, "npc") + unit(2, "mm"), 0.5, gp = gpar(fontsize = 30), default.units = "npc", just = "left")
+grid.text("Source", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
 dev.off()

### 2018-09-05 lineages_18Q3.Rmd

@@
 crispr_ccl <- data.frame("Broad_ID" = crispr_data$Broad_ID)
-# write.table(crispr_data[, c("Hugo_Symbol", "Broad_ID", "Score", "Primary.Disease", "primary_tissue", "Mutation_Status")], file = "~/Desktop/crispr_data_select.tsv", quote = FALSE, sep = "\t")
+# write.table(crispr_data, file = "~/Desktop/crispr_data.tsv", quote = FALSE, sep = "\t")
 ```
@@
   labs(x = "Primary Tissue", y = "CERES Score")
-
+score_summ_plot
 # ggsave(filename = "./plots_18Q3/crispr/ceres_score_summ_plot.pdf", plot = score_summ_plot, width = 12, height = 4, device = "pdf")
@@
 maf_ccl_annot_plot <- ggplot(data = maf_ccl_annot, aes(x = primary_tissue, y = n, color = primary_tissue)) +
-  geom_jitter(alpha = 0.8, size = 1, position = position_jitter(w = 0.25)) +
+  geom_boxplot(outlier.shape = NA, fill = NA) +
+  geom_jitter(alpha = 0.7, size = 1, position = position_jitter(w = 0.25)) +
   scale_y_continuous(breaks = seq(0, 9000, by = 1000), labels = seq(0, 9000, by = 1000)) +
-  theme(axis.text.x = element_text(angle = 30, hjust = 1), legend.position = "none") +
+  theme(axis.ticks.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), legend.position = "none") +
   labs(x = "Primary Tissue", y = "Number of Mutations")
-
+maf_ccl_annot_plot
 # ggsave(filename = "./plots_18Q3/crispr/maf_ccl_annot_plot.pdf", plot = maf_ccl_annot_plot, width = 12, height = 4, device = "pdf")
+```
+
+```{r fig.height=8, fig.width=12}
+ggsave(filename = "./plots_18Q3/crispr/score_mut_summ.pdf", plot = grid.draw(rbind(ggplotGrob(maf_ccl_annot_plot), ggplotGrob(score_summ_plot), size = "first")), width = 12, height = 8, device = "pdf")
 ```
@@
 
-```{r fig.height=3, fig.width=6}
-wilcox_gene_plot <- ggplot(data = crispr_signif, aes(x = p.adj)) +
-  geom_histogram(breaks = seq(0, 1, by = 0.025), fill = "darkslategray3", color = "black", alpha = 0.7) +
+```{r fig.height=4, fig.width=8}
+wilcox_gene_plot <- ggplot(data = crispr_signif) +
+  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
+  geom_histogram(aes(x = p.adj, fill = "darkslategray3",), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
   scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
@@
   scale_y_continuous(breaks = seq(0, 4500, by = 500), labels = formatC(seq(0, 4500, by = 500), format = "d")) +
-  stat_bin(breaks = seq(0, 1, by = 0.025), geom = "text", colour = "black", size = 3, aes(label = ..count..), vjust = 0.3, angle = 80, hjust = -0.4) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  #stat_bin(breaks = seq(0, 1, by = 0.025), geom = "text", colour = "black", size = 3, aes(label = ..count..), vjust = 0.3, angle = 80, hjust = -0.4) +
+  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
   labs(x = "BH-adjusted p-values", y = "Frequency")
-
-ggsave(filename = "./plots_18Q3/crispr/pvals_genes.pdf", plot = wilcox_gene_plot, width = 10, height = 5, device = "pdf")
+wilcox_gene_plot
+# ggsave(filename = "./plots_18Q3/crispr/pvals_genes.pdf", plot = wilcox_gene_plot, width = 8, height = 4, device = "pdf")
 ```
@@
 
-```{r fig.height=3, fig.width=6}
-wilcox_gene_tissue_plot <- ggplot(data = crispr_signif_tissue, aes(x = p.adj)) +
-  geom_histogram(breaks = seq(0, 1, by = 0.025), fill = "darkslateblue", color = "black", alpha = 0.7) +
+```{r fig.height=4, fig.width=8}
+wilcox_gene_tissue_plot <- ggplot(data = crispr_signif_tissue) +
+  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
+  geom_histogram(aes(x = p.adj, fill = "darkslategray3",), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
   scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
-  coord_cartesian(ylim = c(0, 55000)) +
-  scale_y_continuous(breaks = seq(0, 55000, by = 5000), labels = formatC(seq(0, 55000, by = 5000), format = "d")) +
-  stat_bin(breaks = seq(0, 1, by = 0.025), geom = "text", colour = "black", size = 3, aes(label = ..count..), vjust = 0.3, angle = 80, hjust = -0.4) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  scale_y_continuous(breaks = seq(0, 50000, by = 5000), labels = formatC(seq(0, 50000, by = 5000), format = "d")) +
+  #stat_bin(breaks = seq(0, 1, by = 0.025), geom = "text", colour = "black", size = 3, aes(label = ..count..), vjust = 0.3, angle = 80, hjust = -0.4) +
+  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
   labs(x = "BH-adjusted p-values", y = "Frequency")
-
-ggsave(filename = "./plots_18Q3/crispr/pvals_genes_tissues.pdf", plot = wilcox_gene_tissue_plot, width = 10, height = 5, device = "pdf")
+wilcox_gene_tissue_plot
+# ggsave(filename = "./plots_18Q3/crispr/pvals_genes_tissues.pdf", plot = wilcox_gene_tissue_plot, width = 8, height = 4, device = "pdf")
 ```
@@
         row_title = "Genes", column_title = "Cancer Cell Lines",
-        col = colorRamp2(c(min(chm_scores_cgc), 0, max(chm_scores_cgc)), c("purple4", "white", "seagreen4")),
+        col = colorRamp2(c(min(chm_scores), 0, max(chm_scores)), c("purple4", "white", "seagreen4")),
         na_col = "black",
@@
 pdf("./plots_18Q3/crispr_heatmap_euclidean_all.pdf", width = 50, height = 50, paper = "special")
+draw(chm_all_plot, heatmap_legend_side = "bottom", annotation_legend_side = "bottom")
+seekViewport("annotation_Cell_Line_SSMD")
+grid.text("Cell Line SSMD", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
+seekViewport("annotation_Cas9_Activity")
+grid.text("Cas9 Activity", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
+seekViewport("annotation_Culture_Type")
+grid.text("Culture Type", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
+seekViewport("annotation_Primary_Tissue")
+grid.text("Primary Tissue", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
+seekViewport("annotation_Primary_Disease")
+grid.text("Primary Disease", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
+seekViewport("annotation_Gender")
+grid.text("Gender", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
+seekViewport("annotation_Source")
+grid.text("Source", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
+dev.off()
+
+png("./plots_18Q3/crispr_heatmap_euclidean_all.png", width = 50, height = 50, units = "in", res = 96)
 draw(chm_all_plot, heatmap_legend_side = "bottom", annotation_legend_side = "bottom")
@@
 dev.off()
+
+png("./plots_18Q3/crispr_heatmap_euclidean_all_cgc.png", width = 50, height = 50, units = "in", res = 96)
+draw(chm_all_plot_cgc, heatmap_legend_side = "bottom", annotation_legend_side = "bottom")
+seekViewport("annotation_Cell_Line_SSMD")
+grid.text("Cell Line SSMD", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
+seekViewport("annotation_Cas9_Activity")
+grid.text("Cas9 Activity", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
+seekViewport("annotation_Culture_Type")
+grid.text("Culture Type", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
+seekViewport("annotation_Primary_Tissue")
+grid.text("Primary Tissue", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
+seekViewport("annotation_Primary_Disease")
+grid.text("Primary Disease", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
+seekViewport("annotation_Gender")
+grid.text("Gender", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
+seekViewport("annotation_Source")
+grid.text("Source", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
+dev.off()
 ```
@@
 
+## Report 2 plot
+
+```{r}
+sig_genes <- c("KRAS", "TP53", "NRAS", "BRAF", "PIK3CA", "PTEN", "CTNNB1")
+crispr_sig_genes <- filter(crispr_data, Hugo_Symbol %in% sig_genes)
+crispr_sig_genes$Hugo_Symbol <- factor(crispr_sig_genes$Hugo_Symbol, levels = c("KRAS", "TP53", "NRAS", "BRAF", "PIK3CA", "PTEN", "CTNNB1"))
+```
+
+```{r fig.height=18, fig.width=5}
+crispr_color <- as.character(crispr_sig_genes$Color)
+names(crispr_color) <- crispr_sig_genes$Mutation_Status
+
+# Mutation status
+plot_mut <- ggplot(data = crispr_sig_genes, aes(x = Mutation_Status, y = Score, color = Mutation_Status)) +
+  geom_boxplot(outlier.shape = NA) +
+  geom_jitter(alpha = 0.3, size = 0.7, position = position_jitter(w = 0.05)) +
+  facet_wrap(~ Hugo_Symbol, nrow = 7, scales = "free_y") +
+  scale_color_manual(values = crispr_color) +
+  geom_hline(yintercept = 0, linetype = 2, lwd = 0.3) +
+  theme_light() +
+  theme(legend.position = "none") +
+  labs(x = "Mutation Status", y = "CERES Score",
+       title = "Mutation Status")
+# plot_mut
+
+# Copy number
+plot_cn <- ggplot(data = crispr_sig_genes, aes(x = Copy_Number, y = Score, color = Mutation_Status)) +
+  geom_point(size = 0.5, alpha = 0.5) +
+  geom_smooth(method = "lm", size = 0.5) +
+  scale_color_manual(values = crispr_color) +
+  facet_wrap(~ Hugo_Symbol, nrow = 7, scales = "free") +
+  stat_cor(method = "pearson", show.legend = FALSE, label.x.npc = "right", label.y.npc = "top") +
+  theme_light() +
+  theme(legend.position = "none", axis.title.y = element_blank()) +
+  labs(y = "CERES Score", color = "Mutation Status",
+       x = "Theoretical Copy number", title = "Copy Number")
+# plot_cn
+
+# Gene expression
+plot_ge <- ggplot(data = crispr_sig_genes, aes(x = RPKM_log2, y = Score, color = Mutation_Status)) +
+  geom_point(size = 0.5, alpha = 0.5) +
+  geom_smooth(method = "lm", size = 0.5) +
+  facet_wrap(~ Hugo_Symbol, nrow = 7, scales = "free_y") +
+  scale_color_manual(values = crispr_color) +
+  stat_cor(method = "pearson", show.legend = FALSE, label.x.npc = "left", label.y.npc = "top") +
+  theme_light() +
+  theme(legend.position = "none", axis.title.y = element_blank()) +
+  labs(y = "CERES Score", color = "Mutation Status",
+       x = "Gene Expression [log2(RPKM)]",
+       title = "Gene Expression")
+# plot_ge
+```
+
+```{r fig.height=18, fig.width=15}
+grid.newpage()
+grid.draw(cbind(ggplotGrob(plot_mut), ggplotGrob(plot_ge), ggplotGrob(plot_cn), size = "last"))
+
+ggsave(filename = "./plots_18Q3/crispr/omics_sig_genes.pdf", plot = grid.draw(cbind(ggplotGrob(plot_mut), ggplotGrob(plot_ge), ggplotGrob(plot_cn), size = "last")), width = 15, height = 18, device = "pdf")
+```
+
 ## Grouped plots

### 2018-09-06 lineages_18Q3.Rmd

@@
 
-## Functions {.tabset .tabset-fade .tabset-pills}
-
-### Significance thresholding
+# Functions {.tabset .tabset-fade .tabset-pills}
+
+--------------------------------------------------------------------------------
+
+## Significance thresholding
 
@@
 
-### Make CRISPR grobs
+## Make CRISPR grobs
 
@@
          title = "Mutation Status",
-         subtitle = paste0("Wilcoxon test:\n- BH-corrected p-value: ", sig$p.adj.short, "\n- Uncorrected p-value: ", sig$p.short))
+         subtitle = paste0("Wilcoxon test:\n- BH-corrected p-value: ", sig$p.adj.short, "\n- Uncorrected p-value: ", sig$p.short, "\nMutant lines harbor deleterious mutations."))
 
@@
 
-### Make lineage plot
+## Make lineage plot
 
@@
     gene <- filter(crispr_data, Hugo_Symbol == g)
-    gene <- merge(gene, sig, by = c("Hugo_Symbol", "lineage_name"))
-    gene <- mutate(gene, lineage_name = reorder(lineage_name, p, mean))
+    gene <- merge(gene, sig, by = c("Hugo_Symbol", "group_general_lineage_name"))
+    gene <- mutate(gene, group_general_lineage_name = reorder(group_general_lineage_name, p, mean))
     crispr_color <- as.character(gene$Color)
@@
 
-    plot <- ggplot(data = gene, aes(x = lineage_name, y = Score)) +
+    plot <- ggplot(data = gene, aes(x = group_general_lineage_name, y = Score)) +
       geom_point(alpha = 0.5, mapping = aes(color = Mutation_Status)) +
@@
       coord_cartesian(y = c(min(gene$Score), round_any(x = max(gene$Score), accuracy = round_accuracy, f = ceiling))) +
-      geom_signif(data = gene, mapping = aes(xmin = lineage_name, xmax = lineage_name, annotations = paste(p.short, "\n", p.adj.short), y_position = max(gene$Score)), manual = TRUE, tip_length   = 0, size = 0, textsize = 3) +
+      geom_signif(data = gene, mapping = aes(xmin = group_general_lineage_name, xmax = group_general_lineage_name, annotations = paste(p.short, "\n", p.adj.short), y_position = max(gene$Score)), manual = TRUE, tip_length   = 0, size = 0, textsize = 3) +
       theme(legend.position = "top", axis.text.x = element_text(angle = 70, hjust = 1, size = 10)) +
@@
            title = paste0(g, ": CERES score by cell line lineage"),
-           subtitle = "Lineages sorted by increasing p-value; labels indicate unadjusted p-value / BH-corrected p-value.")
+           subtitle = "Lineages sorted by increasing p-value; labels indicate unadjusted p-value / BH-corrected p-value.\nMutant lines harbor deleterious mutations.")
     return(plot)
@@
 
-### Make tissue plot
+## Make tissue plot
 
@@
            title = paste0(g, ": CERES score by cell line primary tissue"),
-           subtitle = "Primary tissues sorted by increasing p-value; labels indicate unadjusted p-value / BH-corrected p-value.")
+           subtitle = "Primary tissues sorted by increasing p-value; labels indicate unadjusted p-value / BH-corrected p-value.\nMutant lines harbor deleterious mutations.")
     return(plot)
@@
 
-## Cell line converter
+# Data management
+
+--------------------------------------------------------------------------------
+
+## D. Charytonowicz ell line converter
 
@@
 ```{r}
-ccl_converter <- read.delim("./data_munging/cell_line_database_FINAL_MASTER.tsv", sep = "\t", row.names = 1, header = TRUE)
+ccl_converter <- read.delim("./data_munging/cell_line_database_completed_extra_grouped_doids_FINAL.csv", sep = "\t", header = TRUE)
 colnames(ccl_converter)[colnames(ccl_converter) == "ccle_cell_line_name"] <- "CCLE_Name"
@@
 
-## Cell line metadata
+```{r}
+ccl_converter_test <- read.delim("./data_munging/cell_line_database_FINAL_MASTER.tsv", sep = "\t", header = TRUE)
+colnames(ccl_converter_test)[colnames(ccl_converter_test) == "ccle_cell_line_name"] <- "CCLE_Name"
+colnames(ccl_converter_test)[colnames(ccl_converter_test) == "broad_id"] <- "Broad_ID"
+```
+
+## DepMap cell line metadata
 
@@
 
+# From figshare
 crispr_meta <- read.delim("./data_munging/sample_info_18Q3_crispr.csv", sep = ",", header = TRUE, na.strings = c("", NA))
 colnames(crispr_meta)[7] <- "CCLE_Name"
-
-shrna_meta <- read.delim("./data_munging/sample_info_18Q3_shrna.csv", sep = ",", header = TRUE, na.strings = c("", NA))
-colnames(shrna_meta)[1] <- "CCLE_Name"
-```
-
-```{r}
+```
+
+```{r, include=FALSE}
 dan_test <- select(ccl_converter, CCLE_Name, Broad_ID, cell_line_name)
 dan_test <- dan_test[-which(dan_test$CCLE_Name == ""), ]
+old_dan_test <- select(ccl_converter_test, CCLE_Name, Broad_ID, cell_line_name)
+old_dan_test <- old_dan_test[-which(old_dan_test$CCLE_Name == ""), ]
+colnames(old_dan_test)[colnames(old_dan_test) == "Broad_ID"] <- "Broad_ID_Old"
 ccl_test <- select(ccl_info, CCLE_Name, Broad_ID)
@@
 test <- merge(ccl_test, dan_test, by = "CCLE_Name", all = TRUE, suffixes = c("_DepMap", "_Daniel"))
-test$BroadIDs_match <- ifelse(as.character(test$Broad_ID_DepMap) == as.character(test$Broad_ID_Daniel), TRUE, FALSE)
-```
-
-## Cancer Gene Census (CGC) gene list
+test <- merge(test, old_dan_test, by = "CCLE_Name", all = TRUE)
+test$BroadIDs_match_Daniel <- ifelse(as.character(test$Broad_ID_DepMap) == as.character(test$Broad_ID_Daniel), TRUE, FALSE)
+test$BroadIDs_match_Old <- ifelse(as.character(test$Broad_ID_DepMap) == as.character(test$Broad_ID_Old), TRUE, FALSE)
+
+test_false_Daniel <- filter(test, BroadIDs_match_Daniel == FALSE)
+test_false_Old <- filter(test, BroadIDs_match_Old == FALSE)
+# write.table(test_false, file = "~/Desktop/cell_line_database_problems.csv", quote = FALSE, sep = ",")
+```
+
+## CGC gene list
 
@@
 
-## MAF file
+## CCLE MAF file
 
@@
 # Add Mutation_Status column
-maf_df$Mutation_Status <- ifelse(maf_df$Variant_Classification == "Missense_Mutation" | maf_df$isDeleterious == TRUE, "Mutant", "Other")
-maf_df <- unique(subset(maf_df, select = c("Hugo_Symbol", "CCLE_Name", "Broad_ID", "Mutation_Status")))
+maf_df$Mutation_Status <- ifelse(maf_df$isDeleterious == TRUE, "Mutant", "Other")
+maf_df$Mutation_Status_Nonsilent <- ifelse(maf_df$Variant_Classification == "Silent", "Other", "Mutant")
+maf_df <- unique(subset(maf_df, select = c("Hugo_Symbol", "CCLE_Name", "Broad_ID", "Mutation_Status", "Mutation_Status_Nonsilent")))
 
@@
 
-## Copy number file
+## CCLE copy number file
 
@@
 
-## Gene expression file
+## CCLE gene expression file
 
@@
 
-## CRISPR dependency probabilities
+## DepMap dependency probabilities
 
@@
 
-## CRISPR data and annotations
+## Merge CRISPR data and annotations
 
@@
 
-```{r, include=FALSE, eval=FALSE}
-length(intersect(unique(crispr_data$Hugo_Symbol), unique(maf_df$Hugo_Symbol)))
-length(intersect(unique(crispr_data$Hugo_Symbol), unique(cn_melt$Hugo_Symbol)))
-length(intersect(unique(crispr_data$Hugo_Symbol), unique(ge_melt$Hugo_Symbol)))
-
-length(intersect(unique(crispr_data$Broad_ID), unique(maf_df$Broad_ID)))
-length(intersect(unique(crispr_data$Broad_ID), unique(cn_melt$Broad_ID)))
-length(intersect(unique(crispr_data$Broad_ID), unique(ge_melt$Broad_ID)))
-
-setdiff(unique(crispr_data$Broad_ID), unique(maf_df$Broad_ID))
-setdiff(unique(crispr_data$Broad_ID), unique(cn_melt$Broad_ID))
-setdiff(unique(crispr_data$Broad_ID), unique(ge_melt$Broad_ID))
-
-length(intersect(intersect(unique(crispr_data$Broad_ID), unique(cn_melt$Broad_ID)), unique(ge_melt$Broad_ID)))
-setdiff(crispr_data$Broad_ID, intersect(intersect(unique(crispr_data$Broad_ID), unique(cn_melt$Broad_ID)), unique(ge_melt$Broad_ID)))
-```
-
-## shRNA data and annotations
-
-The Achilles shRNA DEMETER score data was pulled from the [CTD^2^ Data Portal](https://ocg.cancer.gov/programs/ctd2/data-portal) (Tsherniak et al 2017).
-```{r, eval=FALSE}
-shrna <- read.table("./data_munging/D2_combined_gene_dep_scores.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
-colnames(shrna)[1] <- "Hugo_Symbol"
-# Remove Entrez gene IDs from gene names
-shrna$Hugo_Symbol <- gsub(" .*", "", shrna$Hugo_Symbol)
-
-# Melt shRNA dataset for merging
-shrna_melt <- melt(shrna , id.vars = "Hugo_Symbol", measure.vars = colnames(shrna)[2:ncol(shrna)], variable.name = "CCLE_Name", value.name = "Score")
-shrna_melt <- drop_na(shrna_melt)
-```
-
-Merge annotation data:
-```{r, eval=FALSE}
-# Merge cell line metadata
-shrna_melt <- merge(shrna_melt, ccl_info, by = "CCLE_Name", all.x = TRUE)
-shrna_melt <- merge(shrna_melt, shrna_meta, by = "CCLE_Name", all.x = TRUE)
-
-# Merge mutation annotations
-shrna_muts <- merge(shrna_melt, maf_df, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
-shrna_muts <- shrna_muts %>% mutate(Mutation_Status = if_else(is.na(Mutation_Status), "Other", Mutation_Status))
-shrna_muts$Hugo_Symbol <- factor(shrna_muts$Hugo_Symbol)
-
-# Summarize number of mutant and Other cell lines
-shrna_muts_summ <- shrna_muts %>% group_by(Hugo_Symbol) %>%
-  summarize(N_Other = sum(Mutation_Status == "Other"),
-            N_Mutant = sum(Mutation_Status == "Mutant"))
-
-# Merge test results back into full dataset, which restores information lost in the summarization
-shrna_data <- merge(shrna_muts_summ, shrna_muts, by = "Hugo_Symbol")
-
-# Add Color column
-shrna_data$Color <- ifelse(shrna_data$Mutation_Status == "Other", "cyan3", "darkorchid")
-shrna_data$Color <- factor(shrna_data$Color)
-
-# Cell line lineages
-shrna_data <- merge(shrna_data, ccl_converter, by = c("CCLE_Name", "Broad_ID"), all.x = TRUE)
-levels(shrna_data$lineage_name) <- sort(levels(shrna_data$lineage_name), decreasing = TRUE)
-
-# Copy number
-shrna_data <- merge(shrna_data, cn_melt, by = c("Hugo_Symbol", "Broad_ID"), all.x = TRUE)
-
-# Gene expression (RPKM)
-ge_filt <- filter(ge_melt, Hugo_Symbol %in% unique(shrna_data$Hugo_Symbol))
-shrna_data <- merge(shrna_data, ge_filt, by = c("Hugo_Symbol", "Broad_ID", "CCLE_Name"), all.x = TRUE)
-
-saveRDS(shrna_data, "./../crispr_lineages_giant_files/shrna_data_18Q3.rds", compress = "xz")
-```
-
-```{r}
-shrna_data <- readRDS("./../crispr_lineages_giant_files/shrna_data_18Q3.rds")
-shrna_ccl <- data.frame("Broad_ID" = shrna_data$Broad_ID)
-```
-
-```{r, eval=FALSE}
-write(union(as.character(distinct(crispr_data[which(is.na(crispr_data$lineage_name)), c("CCLE_Name", "lineage_name")])$CCLE_Name), as.character(distinct(shrna_data[which(is.na(shrna_data$lineage_name)), c("CCLE_Name", "lineage_name")])$CCLE_Name)), file = "./data_munging//na_ccl_in_converter.txt")
-```
-
-# Exploration
+# Wilcoxon tests
 
@@
 
-##  Metadata
-
-```{r}
-tissue_summ <- crispr_meta %>% group_by(primary_tissue) %>% tally()
-disease_summ <- ccl_info %>% group_by(Primary.Disease) %>% tally()
-```
-
-```{r fig.height=12, fig.width=3}
-ggplot(data = tissue_summ) + 
-  aes(x = 0, y = n, fill = primary_tissue, label = primary_tissue) +
-  geom_histogram(color = "black", stat = "identity") +
-  geom_text(position = position_stack(vjust = 0.5)) +
-  scale_y_continuous(breaks = seq(0, 500, by = 25), labels = seq(0, 500, by = 25)) +
-  coord_cartesian(ylim = c(0, 500)) +
-  theme(legend.position = "none", axis.text.x = element_blank(), axis.ticks.x = element_blank(), axis.title.x = element_blank()) +
-  labs(y = "Count")
-```
-
-## Scores
-
-Distribution of scores across cell lines and primary tissues. Each data point represents a single cell line.
-```{r fig.height=4, fig.width=12}
-ceres_summ <- crispr_data %>% group_by(primary_tissue) %>% summarize(Max = max(Score),
-                                                                     Min = min(Score))
-score_summ_plot <- ggplot(data = crispr_data, aes(x = primary_tissue, color = primary_tissue)) +
-  geom_boxplot(mapping = aes(y = Score), outlier.shape = NA) +
-  geom_point(data = ceres_summ, mapping = aes(x = primary_tissue, y = Min)) +
-  geom_point(data = ceres_summ, mapping = aes(x = primary_tissue, y = Max)) +
-  scale_y_continuous(breaks = seq(-4, 6, by = 1), labels = seq(-4, 6, by = 1)) +
-  theme(axis.text.x = element_text(angle = 30, hjust = 1), legend.position = "none") +
-  labs(x = "Primary Tissue", y = "CERES Score")
-score_summ_plot
-# ggsave(filename = "./plots_18Q3/crispr/ceres_score_summ_plot.pdf", plot = score_summ_plot, width = 12, height = 4, device = "pdf")
-```
-
-## Mutations
-
-```{r}
-maf_df_filt <- filter(maf_df, Hugo_Symbol %in% unique(crispr_data$Hugo_Symbol))
-maf_summ_filt <- maf_df_filt %>% group_by(Mutation_Status) %>% tally()
-maf_summ_filt$Percent <- format(round(maf_summ_filt$n / sum(maf_summ_filt$n) * 100, 4), nsmall = 2)
-maf_summ_filt$Percent <- as.numeric(as.character(maf_summ_filt$Percent))
-```
-
-Distribution of mutations across cell lines and primary tissues. Each data point represents a single cell line.
-```{r fig.height=4, fig.width=10}
-maf_ccl_annot <- merge(maf_df %>% group_by(Broad_ID) %>% tally(), crispr_meta, by = "Broad_ID", all.y = TRUE)
-
-maf_ccl_annot_plot <- ggplot(data = maf_ccl_annot, aes(x = primary_tissue, y = n, color = primary_tissue)) +
-  geom_boxplot(outlier.shape = NA, fill = NA) +
-  geom_jitter(alpha = 0.7, size = 1, position = position_jitter(w = 0.25)) +
-  scale_y_continuous(breaks = seq(0, 9000, by = 1000), labels = seq(0, 9000, by = 1000)) +
-  theme(axis.ticks.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), legend.position = "none") +
-  labs(x = "Primary Tissue", y = "Number of Mutations")
-maf_ccl_annot_plot
-# ggsave(filename = "./plots_18Q3/crispr/maf_ccl_annot_plot.pdf", plot = maf_ccl_annot_plot, width = 12, height = 4, device = "pdf")
-```
-
-```{r fig.height=8, fig.width=12}
-ggsave(filename = "./plots_18Q3/crispr/score_mut_summ.pdf", plot = grid.draw(rbind(ggplotGrob(maf_ccl_annot_plot), ggplotGrob(score_summ_plot), size = "first")), width = 12, height = 8, device = "pdf")
-```
-
-```{r fig.height=6, fig.width=12}
-maf_gene_annot <- maf_df_filt %>% group_by(Hugo_Symbol) %>% tally()
-
-ggplot(data = maf_gene_annot, aes(x = n)) +
-  geom_histogram(breaks = seq(0, 600, by = 20), fill = "darkslategray3", color = "black", alpha = 0.7) +
-  coord_cartesian(ylim = c(0, 13000)) +
-  scale_y_continuous(breaks = seq(0, 13500, by = 500), labels = formatC(seq(0, 13500, by = 500), format = "d")) +
-  scale_x_continuous(breaks = seq(0, 600, by = 20), labels = seq(0, 600, by = 20)) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-  stat_bin(breaks = seq(0, 600, by = 20), geom = "text", colour = "black", size = 2.5, aes(label = ..count..), vjust = -0.2, angle = 45, hjust = -0.1) +
-  labs(x = "Number of Mutations", y = "Frequency", title = paste0("Distribution of mutational load for ", length(unique(maf_gene_annot$Hugo_Symbol)), " genes in the CCLE MAF file across all ", length(unique(crispr_ccl$Broad_ID)), " cell lines in the CRISPR screen"))
-```
-
-## Dependency probabilities
-
-```{r fig.height=6, fig.width=12}
-drop_prob_100 <- ggplot(data = crispr_data, aes(x = Dep_Prob)) +
-  geom_histogram(breaks = seq(0, 1, by = 0.05), fill = "darkslategray3", color = "black", alpha = 0.7) +
-  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
-  scale_y_continuous(breaks = seq(0, 5500000, by = 500000), labels = formatC(seq(0, 5500000, by = 500000), format = "d")) +
-  stat_bin(breaks = seq(0, 1, by = 0.05), geom = "text", colour = "black", size = 3.5, aes(label = ..count..), vjust = -1) +
-  labs(title = "Distribution of all dependency probabilities", x = "Probability of Real Dependency", y = "Frequency")
-
-dep_prob_5 <- ggplot(data = filter(crispr_data, Dep_Prob >= 0.95), aes(x = Dep_Prob)) +
-  geom_histogram(mapping = aes(fill = primary_tissue), breaks = seq(0.95, 1, by = 0.005), color = "black") +
-  scale_y_continuous(breaks = seq(0, 60000, by = 10000), labels = formatC(seq(0, 60000, by = 10000), format = "d")) +
-  theme(legend.position = "bottom") +
-  guides(fill = guide_legend(nrow = 4, byrow = FALSE)) +
-  stat_bin(breaks = seq(0.95, 1, by = 0.005), geom = "text", color = "black", size = 3.5, aes(label = ..count..), vjust = -1) +
-  labs(title = "Distribution of all dependency probabilities > 0.95", x = "Probability of Real Dependency", y = "Frequency", fill = "Primary Tissue")
-```
-
-# Wilcoxon tests
-
---------------------------------------------------------------------------------
-
-## CRISPR
-
-### Grouped by gene
-
-```{r, eval=FALSE}
+## Grouped by gene
+
+### Deleterious vs. Other
+
+```{r, eval=TRUE}
 crispr_signif <- compare_means(Score ~ Mutation_Status, group.by = c("Hugo_Symbol"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
@@
 
-knitr::kable(filter(crispr_signif, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CRISPR Screen: Wilcoxon Test Results Comparing Mutant and Other Cell Lines, p < 0.1 (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(filter(crispr_signif, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious mutant and other cell lines, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
 ```
@@
   geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
-  geom_histogram(aes(x = p.adj, fill = "darkslategray3",), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
+  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
   scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
-  coord_cartesian(ylim = c(0, 4500)) +
-  scale_y_continuous(breaks = seq(0, 4500, by = 500), labels = formatC(seq(0, 4500, by = 500), format = "d")) +
-  #stat_bin(breaks = seq(0, 1, by = 0.025), geom = "text", colour = "black", size = 3, aes(label = ..count..), vjust = 0.3, angle = 80, hjust = -0.4) +
+  coord_cartesian(ylim = c(0, 3500)) +
+  scale_y_continuous(breaks = seq(0, 3500, by = 500), labels = formatC(seq(0, 3500, by = 500), format = "d")) +
   scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
@@
 
-### Grouped by gene and lineage
-
-```{r, eval=FALSE}
-crispr_signif_lineage <- compare_means(Score ~ Mutation_Status, group.by = c("Hugo_Symbol", "lineage_name"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
+### Non-silent mutant vs. Other
+
+```{r, eval=TRUE}
+crispr_signif_nonsilent<- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
+crispr_signif_nonsilent <- adj_signif(crispr_signif_nonsilent)
+crispr_signif_nonsilent <- crispr_signif_nonsilent[order(crispr_signif_nonsilent$p),]
+saveRDS(crispr_signif_nonsilent, "./data_munging/rds/crispr_signif_nonsilent.rds")
+
+write.table(crispr_signif_nonsilent, file = "~/Desktop/crispr_signif_nonsilent_gene.csv", quote = FALSE, sep = ",", row.names = FALSE)
+```
+
+```{r}
+crispr_signif_nonsilent <- readRDS("./data_munging/rds/crispr_signif_nonsilent.rds")
+
+knitr::kable(filter(crispr_signif_nonsilent, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant and other cell lines, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+```
+
+```{r fig.height=4, fig.width=8}
+wilcox_gene_nonsilent_plot <- ggplot(data = crispr_signif_nonsilent) +
+  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
+  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
+  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
+  # coord_cartesian(ylim = c(0, 3500)) +
+  # scale_y_continuous(breaks = seq(0, 3500, by = 500), labels = formatC(seq(0, 3500, by = 500), format = "d")) +
+  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
+  labs(x = "BH-adjusted p-values", y = "Frequency")
+wilcox_gene_nonsilent_plot
+```
+
+## Grouped by gene and lineage
+
+### Deleterious vs. Other
+
+```{r, eval=TRUE}
+crispr_signif_lineage <- compare_means(Score ~ Mutation_Status, group.by = c("Hugo_Symbol", "group_general_lineage_name"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
 crispr_signif_lineage <- adj_signif(crispr_signif_lineage)
@@
 
-knitr::kable(filter(crispr_signif_lineage, p < 0.05)[, c("Hugo_Symbol", "lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CRISPR Screen: Wilcoxon Test Results Comparing Mutant and Other Cell Lines by Lineage, p < 0.1 (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
-```
-
-### Grouped by gene and tissue
-
-```{r, eval=FALSE}
+knitr::kable(filter(crispr_signif_lineage, p < 0.05)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious mutant and other cell lines by lineage, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+```
+
+```{r fig.height=4, fig.width=8}
+wilcox_lineage_plot <- ggplot(data = crispr_signif_lineage) +
+  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
+  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
+  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
+  # coord_cartesian(ylim = c(0, 3500)) +
+  # scale_y_continuous(breaks = seq(0, 3500, by = 500), labels = formatC(seq(0, 3500, by = 500), format = "d")) +
+  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
+  labs(x = "BH-adjusted p-values", y = "Frequency")
+wilcox_lineage_plot
+# ggsave(filename = "./plots_18Q3/crispr/pvals_genes.pdf", plot = wilcox_gene_plot, width = 8, height = 4, device = "pdf")
+```
+
+### Non-silent mutant vs. Other
+
+```{r, eval=TRUE}
+crispr_signif_nonsilent_lineage <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "group_general_lineage_name"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
+crispr_signif_nonsilent_lineage <- adj_signif(crispr_signif_nonsilent_lineage)
+crispr_signif_nonsilent_lineage <- crispr_signif_nonsilent_lineage[order(crispr_signif_nonsilent_lineage$p),]
+saveRDS(crispr_signif_nonsilent_lineage, "./data_munging/rds/crispr_signif_nonsilent_lineage.rds")
+
+write.table(crispr_signif_nonsilent_lineage, file = "~/Desktop/crispr_signif_nonsilent_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
+```
+
+```{r}
+crispr_signif_nonsilent_lineage <- readRDS("./data_munging/rds/crispr_signif_nonsilent_lineage.rds")
+
+knitr::kable(filter(crispr_signif_nonsilent_lineage, p < 0.05)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant and other cell lines by lineage, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+```
+
+```{r fig.height=4, fig.width=8}
+wilcox_lineage_nonsilent_plot <- ggplot(data = crispr_signif_nonsilent_lineage) +
+  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
+  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
+  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
+  # coord_cartesian(ylim = c(0, 3500)) +
+  # scale_y_continuous(breaks = seq(0, 3500, by = 500), labels = formatC(seq(0, 3500, by = 500), format = "d")) +
+  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
+  labs(x = "BH-adjusted p-values", y = "Frequency")
+wilcox_lineage_nonsilent_plot
+```
+
+## Grouped by gene and tissue
+
+### Deleterious vs. Other
+
+```{r, eval=TRUE}
 crispr_signif_tissue <- compare_means(Score ~ Mutation_Status, group.by = c("Hugo_Symbol", "primary_tissue"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
@@
 
-knitr::kable(filter(crispr_signif_tissue, p < 0.05)[, c("Hugo_Symbol", "primary_tissue", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CRISPR Screen: Wilcoxon Test Results Comparing Mutant and Other Cell Lines by Primary Tissue, p < 0.1 (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(filter(crispr_signif_tissue, p < 0.05)[, c("Hugo_Symbol", "primary_tissue", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious mutant and other cell lines by tissue, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 ```{r fig.height=4, fig.width=8}
-wilcox_gene_tissue_plot <- ggplot(data = crispr_signif_tissue) +
+wilcox_tissue_plot <- ggplot(data = crispr_signif_tissue) +
   geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
-  geom_histogram(aes(x = p.adj, fill = "darkslategray3",), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
+  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
   scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
-  scale_y_continuous(breaks = seq(0, 50000, by = 5000), labels = formatC(seq(0, 50000, by = 5000), format = "d")) +
-  #stat_bin(breaks = seq(0, 1, by = 0.025), geom = "text", colour = "black", size = 3, aes(label = ..count..), vjust = 0.3, angle = 80, hjust = -0.4) +
+  # scale_y_continuous(breaks = seq(0, 50000, by = 5000), labels = formatC(seq(0, 50000, by = 5000), format = "d")) +
   scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
@@
   labs(x = "BH-adjusted p-values", y = "Frequency")
-wilcox_gene_tissue_plot
-# ggsave(filename = "./plots_18Q3/crispr/pvals_genes_tissues.pdf", plot = wilcox_gene_tissue_plot, width = 8, height = 4, device = "pdf")
-```
-
-## shRNA
-
-### Grouped by gene
-
-```{r, eval=FALSE}
-shrna_signif <- compare_means(Score ~ Mutation_Status, group.by = c("Hugo_Symbol"), data = shrna_data, method = "wilcox.test", p.adjust.method = "BH")
-shrna_signif <- adj_signif(shrna_signif)
-shrna_signif <- shrna_signif[order(shrna_signif$p),]
-saveRDS(shrna_signif, "./data_munging/rds/shrna_signif.rds")
-```
-
-```{r, eval=FALSE}
-shrna_signif <- readRDS("./data_munging/rds/shrna_signif.rds")
-
-knitr::kable(filter(shrna_signif, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "shRNA Screen: Wilcoxon Test Results Comparing Mutant and Other Cell Lines, p < 0.1  (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
-```
-
-### Grouped by gene and lineage
-
-```{r, eval=FALSE}
-shrna_signif_lineage <- compare_means(Score ~ Mutation_Status, group.by = c("Hugo_Symbol", "lineage_name"), data = shrna_data, method = "wilcox.test", p.adjust.method = "BH")
-shrna_signif_lineage <- adj_signif(shrna_signif_lineage)
-shrna_signif_lineage <- mutate(shrna_signif_lineage, lineage_name = reorder(lineage_name, p.adj, mean))
-saveRDS(shrna_signif_lineage, "./../crispr_lineages_giant_files/shrna_signif_lineage.rds")
-```
-
-```{r, eval=FALSE}
-shrna_signif_lineage <- readRDS("./../crispr_lineages_giant_files/shrna_signif_lineage.rds")
+wilcox_tissue_plot
+# ggsave(filename = "./plots_18Q3/crispr/pvals_genes_tissues.pdf", plot = wilcox_tissue_plot, width = 8, height = 4, device = "pdf")
+```
+
+### Non-silent mutant vs. Other
+
+```{r, eval=TRUE}
+crispr_signif_nonsilent_tissue <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "primary_tissue"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
+crispr_signif_nonsilent_tissue <- adj_signif(crispr_signif_nonsilent_tissue)
+crispr_signif_nonsilent_tissue <- crispr_signif_nonsilent_tissue[order(crispr_signif_nonsilent_tissue$p),]
+saveRDS(crispr_signif_nonsilent_tissue, "./data_munging/rds/crispr_signif_nonsilent_tissue.rds")
+
+write.table(crispr_signif_nonsilent_tissue, file = "~/Desktop/crispr_signif_nonsilent_tissue.csv", quote = FALSE, sep = ",", row.names = FALSE)
+```
+
+```{r}
+crispr_signif_nonsilent_tissue <- readRDS("./data_munging/rds/crispr_signif_nonsilent_tissue.rds")
+
+knitr::kable(filter(crispr_signif_nonsilent_tissue, p < 0.05)[, c("Hugo_Symbol", "primary_tissue", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant and other cell lines by tissue, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+```
+
+```{r fig.height=4, fig.width=8}
+wilcox_tissue_nonsilent_plot <- ggplot(data = crispr_signif_nonsilent_tissue) +
+  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
+  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
+  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
+  # coord_cartesian(ylim = c(0, 3500)) +
+  # scale_y_continuous(breaks = seq(0, 3500, by = 500), labels = formatC(seq(0, 3500, by = 500), format = "d")) +
+  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
+  labs(x = "BH-adjusted p-values", y = "Frequency")
+wilcox_tissue_nonsilent_plot
 ```
@@
 
-## CRISPR
-
-### Data management
+## Data management
+
+The mutation status portion of these heatmaps was made using deleterious and missense mutations as "mutant" and all others as "other."
 
@@
 
-### All genes, no omics
+## All genes, no omics
 
@@
 
-### CGC genes
+## CGC genes
 
@@
 
-#### Euclidean distance
+### Euclidean distance
 
@@
 
-#### Pearson correlation
+### Pearson correlation
 
@@
 
-## Report 2 plot
-
-```{r}
+## Grouped plots
+
+```{r fig.height=12, fig.width=12, include=FALSE}
+makeCRISPRgrob("KRAS")
+```
+
+Plot code:
+```{r, eval=FALSE}
+crispr_data_cgc <- filter(crispr_data, Hugo_Symbol %in% cgc$Hugo_Symbol)
+crispr_all_genes <- unique(crispr_data_cgc$Hugo_Symbol)
+crispr_all_groups <- lapply(crispr_all_genes, makeCRISPRgrob)
+crispr_all_groups_paths <- paste0(crispr_all_genes, "_crispr_grouped.png")
+pwalk(list(crispr_all_groups_paths, crispr_all_groups), ggsave, path = "./plots_18Q3/crispr_grouped_plots_cgc", dpi = 300, width = 12, height = 12, units = "in")
+```
+
+Data management:
+```{r}
+crispr_all_bygene <- paste0(list.files("./plots_18Q3/crispr_grouped_plots_cgc", full.names = TRUE))
+names(crispr_all_bygene) <- str_replace_all(crispr_all_bygene, c("_crispr_grouped.png" = "", "./plots_18Q3/crispr_grouped_plots_cgc/" = ""))
+crispr_bygene_order <- c(intersect(crispr_signif$Hugo_Symbol, names(crispr_all_bygene)), setdiff(names(crispr_all_bygene), crispr_signif$Hugo_Symbol))
+crispr_all_bygene <- crispr_all_bygene[match(crispr_bygene_order, names(crispr_all_bygene))]
+bsselect(crispr_all_bygene, type = "img", selected = "KRAS", live_search = TRUE, show_tick = TRUE, height = 300, frame_height = 275)
+```
+
+## Sorted lineage plots
+
+```{r fig.height=12, fig.width=12, include=FALSE}
+makeCRISPRlinplot("KRAS")
+```
+
+Plot code:
+```{r, eval=FALSE}
+crispr_data_cgc <- filter(crispr_data, Hugo_Symbol %in% cgc$Hugo_Symbol)
+crispr_all_genes <- unique(crispr_data_cgc$Hugo_Symbol)
+crispr_all_lins <- lapply(crispr_all_genes, makeCRISPRlinplot)
+crispr_all_lins_paths <- paste0(crispr_all_genes, "_crispr_lineage.png")
+pwalk(list(crispr_all_lins_paths, crispr_all_lins), ggsave, path = "./plots_18Q3/crispr_lineage_plots_cgc", dpi = 300, width = 12, height = 12, units = "in")
+```
+
+Data management:
+```{r}
+crispr_all_bygene <- paste0(list.files("./plots_18Q3/crispr_lineage_plots_cgc", full.names = TRUE))
+names(crispr_all_bygene) <- str_replace_all(crispr_all_bygene, c("_crispr_lineage.png" = "", "./plots_18Q3/crispr_lineage_plots_cgc/" = ""))
+crispr_bygene_order <- c(intersect(crispr_signif$Hugo_Symbol, names(crispr_all_bygene)), setdiff(names(crispr_all_bygene), crispr_signif$Hugo_Symbol))
+crispr_all_bygene <- crispr_all_bygene[match(crispr_bygene_order, names(crispr_all_bygene))]
+bsselect(crispr_all_bygene, type = "img", selected = "KRAS", live_search = TRUE, show_tick = TRUE, height = 300, frame_height = 275)
+```
+
+## Sorted tissue plots
+
+```{r fig.height=12, fig.width=12, include=FALSE}
+makeCRISPRtissueplot("KRAS")
+```
+
+Plot code:
+```{r, eval=FALSE}
+crispr_data_cgc <- filter(crispr_data, Hugo_Symbol %in% cgc$Hugo_Symbol)
+crispr_all_genes <- unique(crispr_data_cgc$Hugo_Symbol)
+crispr_all_lins <- lapply(crispr_all_genes, makeCRISPRtissueplot)
+crispr_all_lins_paths <- paste0(crispr_all_genes, "_crispr_tissue.png")
+pwalk(list(crispr_all_lins_paths, crispr_all_lins), ggsave, path = "./plots_18Q3/crispr_tissue_plots_cgc", dpi = 300, width = 12, height = 12, units = "in")
+```
+
+Data management:
+```{r}
+crispr_all_bygene <- paste0(list.files("./plots_18Q3/crispr_tissue_plots_cgc", full.names = TRUE))
+names(crispr_all_bygene) <- str_replace_all(crispr_all_bygene, c("_crispr_tissue.png" = "", "./plots_18Q3/crispr_tissue_plots_cgc/" = ""))
+crispr_bygene_order <- c(intersect(crispr_signif$Hugo_Symbol, names(crispr_all_bygene)), setdiff(names(crispr_all_bygene), crispr_signif$Hugo_Symbol))
+crispr_all_bygene <- crispr_all_bygene[match(crispr_bygene_order, names(crispr_all_bygene))]
+bsselect(crispr_all_bygene, type = "img", selected = "KRAS", live_search = TRUE, show_tick = TRUE, height = 300, frame_height = 275)
+```
+
+# Report #2
+
+--------------------------------------------------------------------------------
+
+##  Metadata
+
+```{r}
+tissue_summ <- crispr_meta %>% group_by(primary_tissue) %>% tally()
+disease_summ <- ccl_info %>% group_by(Primary.Disease) %>% tally()
+```
+
+```{r fig.height=12, fig.width=3}
+ggplot(data = tissue_summ) + 
+  aes(x = 0, y = n, fill = primary_tissue, label = primary_tissue) +
+  geom_histogram(color = "black", stat = "identity") +
+  geom_text(position = position_stack(vjust = 0.5)) +
+  scale_y_continuous(breaks = seq(0, 500, by = 25), labels = seq(0, 500, by = 25)) +
+  coord_cartesian(ylim = c(0, 500)) +
+  theme(legend.position = "none", axis.text.x = element_blank(), axis.ticks.x = element_blank(), axis.title.x = element_blank()) +
+  labs(y = "Count")
+```
+
+```{r, include=FALSE, eval=FALSE}
+length(intersect(unique(crispr_data$Hugo_Symbol), unique(maf_df$Hugo_Symbol)))
+length(intersect(unique(crispr_data$Hugo_Symbol), unique(cn_melt$Hugo_Symbol)))
+length(intersect(unique(crispr_data$Hugo_Symbol), unique(ge_melt$Hugo_Symbol)))
+
+length(intersect(unique(crispr_data$Broad_ID), unique(maf_df$Broad_ID)))
+length(intersect(unique(crispr_data$Broad_ID), unique(cn_melt$Broad_ID)))
+length(intersect(unique(crispr_data$Broad_ID), unique(ge_melt$Broad_ID)))
+
+setdiff(unique(crispr_data$Broad_ID), unique(maf_df$Broad_ID))
+setdiff(unique(crispr_data$Broad_ID), unique(cn_melt$Broad_ID))
+setdiff(unique(crispr_data$Broad_ID), unique(ge_melt$Broad_ID))
+
+length(intersect(intersect(unique(crispr_data$Broad_ID), unique(cn_melt$Broad_ID)), unique(ge_melt$Broad_ID)))
+setdiff(crispr_data$Broad_ID, intersect(intersect(unique(crispr_data$Broad_ID), unique(cn_melt$Broad_ID)), unique(ge_melt$Broad_ID)))
+```
+
+## Scores
+
+Distribution of scores across cell lines and primary tissues. Each data point represents a single cell line.
+```{r fig.height=4, fig.width=12}
+ceres_summ <- crispr_data %>% group_by(primary_tissue) %>% summarize(Max = max(Score),
+                                                                     Min = min(Score))
+score_summ_plot <- ggplot(data = crispr_data, aes(x = primary_tissue, color = primary_tissue)) +
+  geom_boxplot(mapping = aes(y = Score), outlier.shape = NA) +
+  geom_point(data = ceres_summ, mapping = aes(x = primary_tissue, y = Min)) +
+  geom_point(data = ceres_summ, mapping = aes(x = primary_tissue, y = Max)) +
+  scale_y_continuous(breaks = seq(-4, 6, by = 1), labels = seq(-4, 6, by = 1)) +
+  theme(axis.text.x = element_text(angle = 30, hjust = 1), legend.position = "none") +
+  labs(x = "Primary Tissue", y = "CERES Score")
+score_summ_plot
+# ggsave(filename = "./plots_18Q3/crispr/ceres_score_summ_plot.pdf", plot = score_summ_plot, width = 12, height = 4, device = "pdf")
+```
+
+## Mutations
+
+```{r}
+maf_df_filt <- filter(maf_df, Hugo_Symbol %in% unique(crispr_data$Hugo_Symbol))
+maf_summ_filt <- maf_df_filt %>% group_by(Mutation_Status) %>% tally()
+maf_summ_filt$Percent <- format(round(maf_summ_filt$n / sum(maf_summ_filt$n) * 100, 4), nsmall = 2)
+maf_summ_filt$Percent <- as.numeric(as.character(maf_summ_filt$Percent))
+```
+
+Distribution of mutations across cell lines and primary tissues. Each data point represents a single cell line.
+```{r fig.height=4, fig.width=10}
+maf_ccl_annot <- merge(maf_df %>% group_by(Broad_ID) %>% tally(), crispr_meta, by = "Broad_ID", all.y = TRUE)
+
+maf_ccl_annot_plot <- ggplot(data = maf_ccl_annot, aes(x = primary_tissue, y = n, color = primary_tissue)) +
+  geom_boxplot(outlier.shape = NA, fill = NA) +
+  geom_jitter(alpha = 0.7, size = 1, position = position_jitter(w = 0.25)) +
+  scale_y_continuous(breaks = seq(0, 9000, by = 1000), labels = seq(0, 9000, by = 1000)) +
+  theme(axis.ticks.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), legend.position = "none") +
+  labs(x = "Primary Tissue", y = "Number of Mutations")
+maf_ccl_annot_plot
+# ggsave(filename = "./plots_18Q3/crispr/maf_ccl_annot_plot.pdf", plot = maf_ccl_annot_plot, width = 12, height = 4, device = "pdf")
+```
+
+```{r fig.height=8, fig.width=12}
+# ggsave(filename = "./plots_18Q3/crispr/score_mut_summ.pdf", plot = grid.draw(rbind(ggplotGrob(maf_ccl_annot_plot), ggplotGrob(score_summ_plot), size = "first")), width = 12, height = 8, device = "pdf")
+```
+
+```{r fig.height=6, fig.width=12}
+maf_gene_annot <- maf_df_filt %>% group_by(Hugo_Symbol) %>% tally()
+
+ggplot(data = maf_gene_annot, aes(x = n)) +
+  geom_histogram(breaks = seq(0, 600, by = 20), fill = "darkslategray3", color = "black", alpha = 0.7) +
+  coord_cartesian(ylim = c(0, 13000)) +
+  scale_y_continuous(breaks = seq(0, 13500, by = 500), labels = formatC(seq(0, 13500, by = 500), format = "d")) +
+  scale_x_continuous(breaks = seq(0, 600, by = 20), labels = seq(0, 600, by = 20)) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  stat_bin(breaks = seq(0, 600, by = 20), geom = "text", colour = "black", size = 2.5, aes(label = ..count..), vjust = -0.2, angle = 45, hjust = -0.1) +
+  labs(x = "Number of Mutations", y = "Frequency", title = paste0("Distribution of mutational load for ", length(unique(maf_gene_annot$Hugo_Symbol)), " genes in the CCLE MAF file across all ", length(unique(crispr_ccl$Broad_ID)), " cell lines in the CRISPR screen"))
+```
+
+## Dependency probabilities
+
+```{r fig.height=6, fig.width=12}
+drop_prob_100 <- ggplot(data = crispr_data, aes(x = Dep_Prob)) +
+  geom_histogram(breaks = seq(0, 1, by = 0.05), fill = "darkslategray3", color = "black", alpha = 0.7) +
+  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
+  scale_y_continuous(breaks = seq(0, 5500000, by = 500000), labels = formatC(seq(0, 5500000, by = 500000), format = "d")) +
+  stat_bin(breaks = seq(0, 1, by = 0.05), geom = "text", colour = "black", size = 3.5, aes(label = ..count..), vjust = -1) +
+  labs(title = "Distribution of all dependency probabilities", x = "Probability of Real Dependency", y = "Frequency")
+
+dep_prob_5 <- ggplot(data = filter(crispr_data, Dep_Prob >= 0.95), aes(x = Dep_Prob)) +
+  geom_histogram(mapping = aes(fill = primary_tissue), breaks = seq(0.95, 1, by = 0.005), color = "black") +
+  scale_y_continuous(breaks = seq(0, 60000, by = 10000), labels = formatC(seq(0, 60000, by = 10000), format = "d")) +
+  theme(legend.position = "bottom") +
+  guides(fill = guide_legend(nrow = 4, byrow = FALSE)) +
+  stat_bin(breaks = seq(0.95, 1, by = 0.005), geom = "text", color = "black", size = 3.5, aes(label = ..count..), vjust = -1) +
+  labs(title = "Distribution of all dependency probabilities > 0.95", x = "Probability of Real Dependency", y = "Frequency", fill = "Primary Tissue")
+```
+
+## Per-gene plots
+
+```{r fig.height=18, fig.width=5}
 sig_genes <- c("KRAS", "TP53", "NRAS", "BRAF", "PIK3CA", "PTEN", "CTNNB1")
@@
 crispr_sig_genes$Hugo_Symbol <- factor(crispr_sig_genes$Hugo_Symbol, levels = c("KRAS", "TP53", "NRAS", "BRAF", "PIK3CA", "PTEN", "CTNNB1"))
-```
-
-```{r fig.height=18, fig.width=5}
+
 crispr_color <- as.character(crispr_sig_genes$Color)
@@
 # plot_ge
-```
-
-```{r fig.height=18, fig.width=15}
-grid.newpage()
-grid.draw(cbind(ggplotGrob(plot_mut), ggplotGrob(plot_ge), ggplotGrob(plot_cn), size = "last"))
-
-ggsave(filename = "./plots_18Q3/crispr/omics_sig_genes.pdf", plot = grid.draw(cbind(ggplotGrob(plot_mut), ggplotGrob(plot_ge), ggplotGrob(plot_cn), size = "last")), width = 15, height = 18, device = "pdf")
-```
-
-## Grouped plots
-
-```{r fig.height=12, fig.width=12, include=FALSE}
-makeCRISPRgrob("KRAS")
-```
-
-Plot code:
-```{r, eval=FALSE}
-crispr_data_cgc <- filter(crispr_data, Hugo_Symbol %in% cgc$Hugo_Symbol)
-crispr_all_genes <- unique(crispr_data_cgc$Hugo_Symbol)
-crispr_all_groups <- lapply(crispr_all_genes, makeCRISPRgrob)
-crispr_all_groups_paths <- paste0(crispr_all_genes, "_crispr_grouped.png")
-pwalk(list(crispr_all_groups_paths, crispr_all_groups), ggsave, path = "./plots_18Q3/crispr_grouped_plots_cgc", dpi = 300, width = 12, height = 12, units = "in")
-```
-
-Data management:
-```{r}
-crispr_all_bygene <- paste0(list.files("./plots_18Q3/crispr_grouped_plots_cgc", full.names = TRUE))
-names(crispr_all_bygene) <- str_replace_all(crispr_all_bygene, c("_crispr_grouped.png" = "", "./plots_18Q3/crispr_grouped_plots_cgc/" = ""))
-crispr_bygene_order <- c(intersect(crispr_signif$Hugo_Symbol, names(crispr_all_bygene)), setdiff(names(crispr_all_bygene), crispr_signif$Hugo_Symbol))
-crispr_all_bygene <- crispr_all_bygene[match(crispr_bygene_order, names(crispr_all_bygene))]
-bsselect(crispr_all_bygene, type = "img", selected = "KRAS", live_search = TRUE, show_tick = TRUE, height = 300, frame_height = 275)
-```
-
-## Sorted lineage plots
-
-```{r fig.height=12, fig.width=12, include=FALSE}
-makeCRISPRlinplot("KRAS")
-```
-
-Plot code:
-```{r, eval=FALSE}
-crispr_data_cgc <- filter(crispr_data, Hugo_Symbol %in% cgc$Hugo_Symbol)
-crispr_all_genes <- unique(crispr_data_cgc$Hugo_Symbol)
-crispr_all_lins <- lapply(crispr_all_genes, makeCRISPRlinplot)
-crispr_all_lins_paths <- paste0(crispr_all_genes, "_crispr_lineage.png")
-pwalk(list(crispr_all_lins_paths, crispr_all_lins), ggsave, path = "./plots_18Q3/crispr_lineage_plots_cgc", dpi = 300, width = 12, height = 12, units = "in")
-```
-
-Data management:
-```{r}
-crispr_all_bygene <- paste0(list.files("./plots_18Q3/crispr_lineage_plots_cgc", full.names = TRUE))
-names(crispr_all_bygene) <- str_replace_all(crispr_all_bygene, c("_crispr_lineage.png" = "", "./plots_18Q3/crispr_lineage_plots_cgc/" = ""))
-crispr_bygene_order <- c(intersect(crispr_signif$Hugo_Symbol, names(crispr_all_bygene)), setdiff(names(crispr_all_bygene), crispr_signif$Hugo_Symbol))
-crispr_all_bygene <- crispr_all_bygene[match(crispr_bygene_order, names(crispr_all_bygene))]
-bsselect(crispr_all_bygene, type = "img", selected = "KRAS", live_search = TRUE, show_tick = TRUE, height = 300, frame_height = 275)
-```
-
-## Sorted tissue plots
-
-```{r fig.height=12, fig.width=12, include=FALSE}
-makeCRISPRtissueplot("KRAS")
-```
-
-Plot code:
-```{r, eval=FALSE}
-crispr_data_cgc <- filter(crispr_data, Hugo_Symbol %in% cgc$Hugo_Symbol)
-crispr_all_genes <- unique(crispr_data_cgc$Hugo_Symbol)
-crispr_all_lins <- lapply(crispr_all_genes, makeCRISPRtissueplot)
-crispr_all_lins_paths <- paste0(crispr_all_genes, "_crispr_tissue.png")
-pwalk(list(crispr_all_lins_paths, crispr_all_lins), ggsave, path = "./plots_18Q3/crispr_tissue_plots_cgc", dpi = 300, width = 12, height = 12, units = "in")
-```
-
-Data management:
-```{r}
-crispr_all_bygene <- paste0(list.files("./plots_18Q3/crispr_tissue_plots_cgc", full.names = TRUE))
-names(crispr_all_bygene) <- str_replace_all(crispr_all_bygene, c("_crispr_tissue.png" = "", "./plots_18Q3/crispr_tissue_plots_cgc/" = ""))
-crispr_bygene_order <- c(intersect(crispr_signif$Hugo_Symbol, names(crispr_all_bygene)), setdiff(names(crispr_all_bygene), crispr_signif$Hugo_Symbol))
-crispr_all_bygene <- crispr_all_bygene[match(crispr_bygene_order, names(crispr_all_bygene))]
-bsselect(crispr_all_bygene, type = "img", selected = "KRAS", live_search = TRUE, show_tick = TRUE, height = 300, frame_height = 275)
+
+# ggsave(filename = "./plots_18Q3/crispr/omics_sig_genes.pdf", plot = grid.draw(cbind(ggplotGrob(plot_mut), ggplotGrob(plot_ge), ggplotGrob(plot_cn), size = "last")), width = 15, height = 18, device = "pdf")
+```
+
+# shRNA
+
+--------------------------------------------------------------------------------
+
+## Data and annotations
+
+DepMap cell line metadata:
+```{r}
+# From figshare
+shrna_meta <- read.delim("./data_munging/sample_info_18Q3_shrna.csv", sep = ",", header = TRUE, na.strings = c("", NA))
+colnames(shrna_meta)[1] <- "CCLE_Name"
+```
+
+The Achilles shRNA DEMETER score data was pulled from the [CTD^2^ Data Portal](https://ocg.cancer.gov/programs/ctd2/data-portal) (Tsherniak et al 2017).
+```{r, eval=FALSE}
+shrna <- read.table("./data_munging/D2_combined_gene_dep_scores.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
+colnames(shrna)[1] <- "Hugo_Symbol"
+# Remove Entrez gene IDs from gene names
+shrna$Hugo_Symbol <- gsub(" .*", "", shrna$Hugo_Symbol)
+
+# Melt shRNA dataset for merging
+shrna_melt <- melt(shrna , id.vars = "Hugo_Symbol", measure.vars = colnames(shrna)[2:ncol(shrna)], variable.name = "CCLE_Name", value.name = "Score")
+shrna_melt <- drop_na(shrna_melt)
+```
+
+Merge annotation data:
+```{r, eval=FALSE}
+# Merge cell line metadata
+shrna_melt <- merge(shrna_melt, ccl_info, by = "CCLE_Name", all.x = TRUE)
+shrna_melt <- merge(shrna_melt, shrna_meta, by = "CCLE_Name", all.x = TRUE)
+
+# Merge mutation annotations
+shrna_muts <- merge(shrna_melt, maf_df, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
+shrna_muts <- shrna_muts %>% mutate(Mutation_Status = if_else(is.na(Mutation_Status), "Other", Mutation_Status))
+shrna_muts$Hugo_Symbol <- factor(shrna_muts$Hugo_Symbol)
+
+# Summarize number of mutant and Other cell lines
+shrna_muts_summ <- shrna_muts %>% group_by(Hugo_Symbol) %>%
+  summarize(N_Other = sum(Mutation_Status == "Other"),
+            N_Mutant = sum(Mutation_Status == "Mutant"))
+
+# Merge test results back into full dataset, which restores information lost in the summarization
+shrna_data <- merge(shrna_muts_summ, shrna_muts, by = "Hugo_Symbol")
+
+# Add Color column
+shrna_data$Color <- ifelse(shrna_data$Mutation_Status == "Other", "cyan3", "darkorchid")
+shrna_data$Color <- factor(shrna_data$Color)
+
+# Cell line lineages
+shrna_data <- merge(shrna_data, ccl_converter, by = c("CCLE_Name", "Broad_ID"), all.x = TRUE)
+levels(shrna_data$lineage_name) <- sort(levels(shrna_data$lineage_name), decreasing = TRUE)
+
+# Copy number
+shrna_data <- merge(shrna_data, cn_melt, by = c("Hugo_Symbol", "Broad_ID"), all.x = TRUE)
+
+# Gene expression (RPKM)
+ge_filt <- filter(ge_melt, Hugo_Symbol %in% unique(shrna_data$Hugo_Symbol))
+shrna_data <- merge(shrna_data, ge_filt, by = c("Hugo_Symbol", "Broad_ID", "CCLE_Name"), all.x = TRUE)
+
+saveRDS(shrna_data, "./../crispr_lineages_giant_files/shrna_data_18Q3.rds", compress = "xz")
+```
+
+```{r, eval=FALSE}
+shrna_data <- readRDS("./../crispr_lineages_giant_files/shrna_data_18Q3.rds")
+shrna_ccl <- data.frame("Broad_ID" = shrna_data$Broad_ID)
+```
+
+## Wilcoxon tests
+
+### Grouped by gene
+
+```{r, eval=FALSE}
+shrna_signif <- compare_means(Score ~ Mutation_Status, group.by = c("Hugo_Symbol"), data = shrna_data, method = "wilcox.test", p.adjust.method = "BH")
+shrna_signif <- adj_signif(shrna_signif)
+shrna_signif <- shrna_signif[order(shrna_signif$p),]
+saveRDS(shrna_signif, "./data_munging/rds/shrna_signif.rds")
+```
+
+```{r, eval=FALSE}
+shrna_signif <- readRDS("./data_munging/rds/shrna_signif.rds")
+
+knitr::kable(filter(shrna_signif, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "shRNA Screen: Wilcoxon Test Results Comparing Mutant and Other Cell Lines, p < 0.1  (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+```
+
+### Grouped by gene and lineage
+
+```{r, eval=FALSE}
+shrna_signif_lineage <- compare_means(Score ~ Mutation_Status, group.by = c("Hugo_Symbol", "lineage_name"), data = shrna_data, method = "wilcox.test", p.adjust.method = "BH")
+shrna_signif_lineage <- adj_signif(shrna_signif_lineage)
+shrna_signif_lineage <- mutate(shrna_signif_lineage, lineage_name = reorder(lineage_name, p.adj, mean))
+saveRDS(shrna_signif_lineage, "./../crispr_lineages_giant_files/shrna_signif_lineage.rds")
+```
+
+```{r, eval=FALSE}
+shrna_signif_lineage <- readRDS("./../crispr_lineages_giant_files/shrna_signif_lineage.rds")
 ```

### 2018-09-07 lineages_18Q3.Rmd

@@
 
-## D. Charytonowicz ell line converter
+## D. Charytonowicz cell line converter
 
@@
 ```{r}
-ccl_converter <- read.delim("./data_munging/cell_line_database_completed_extra_grouped_doids_FINAL.csv", sep = "\t", header = TRUE)
+ccl_converter <- read.delim("./data_munging/cell_line_database_v1_20180907.tsv", row.names = 1, sep = "\t", header = TRUE)
+```
+
+```{r, eval=FALSE, include=FALSE}
+# Editing CCL DB
+groupings <- read.delim("./data_munging/cell_line_database_completed_extra_grouped_doids_FINAL.csv", sep = "\t", header = TRUE)
+groupings <- unique(select(groupings, lineage_name, grouped_general_doid, group_general_lineage_name))
+
+ccl_converter <- read.delim("./data_munging/cell_line_database_FINAL_MASTER.tsv", sep = "\t", row.names = 1, header = TRUE)
 colnames(ccl_converter)[colnames(ccl_converter) == "ccle_cell_line_name"] <- "CCLE_Name"
 colnames(ccl_converter)[colnames(ccl_converter) == "broad_id"] <- "Broad_ID"
-```
-
-```{r}
-ccl_converter_test <- read.delim("./data_munging/cell_line_database_FINAL_MASTER.tsv", sep = "\t", header = TRUE)
-colnames(ccl_converter_test)[colnames(ccl_converter_test) == "ccle_cell_line_name"] <- "CCLE_Name"
-colnames(ccl_converter_test)[colnames(ccl_converter_test) == "broad_id"] <- "Broad_ID"
+
+ccl_converter <- merge(ccl_converter, groupings, by = "lineage_name", all.x = TRUE)
 ```
@@
 dan_test <- dan_test[-which(dan_test$CCLE_Name == ""), ]
-old_dan_test <- select(ccl_converter_test, CCLE_Name, Broad_ID, cell_line_name)
-old_dan_test <- old_dan_test[-which(old_dan_test$CCLE_Name == ""), ]
-colnames(old_dan_test)[colnames(old_dan_test) == "Broad_ID"] <- "Broad_ID_Old"
 ccl_test <- select(ccl_info, CCLE_Name, Broad_ID)
@@
 test <- merge(ccl_test, dan_test, by = "CCLE_Name", all = TRUE, suffixes = c("_DepMap", "_Daniel"))
-test <- merge(test, old_dan_test, by = "CCLE_Name", all = TRUE)
-test$BroadIDs_match_Daniel <- ifelse(as.character(test$Broad_ID_DepMap) == as.character(test$Broad_ID_Daniel), TRUE, FALSE)
-test$BroadIDs_match_Old <- ifelse(as.character(test$Broad_ID_DepMap) == as.character(test$Broad_ID_Old), TRUE, FALSE)
-
-test_false_Daniel <- filter(test, BroadIDs_match_Daniel == FALSE)
-test_false_Old <- filter(test, BroadIDs_match_Old == FALSE)
-# write.table(test_false, file = "~/Desktop/cell_line_database_problems.csv", quote = FALSE, sep = ",")
+test$BroadIDs_match <- ifelse(as.character(test$Broad_ID_DepMap) == as.character(test$Broad_ID_Daniel), TRUE, FALSE)
+
+test_false <- filter(test, BroadIDs_match == FALSE)
+# write.table(ccl_converter, file = "~/Desktop/cell_line_database_v1_20180907.tsv", quote = FALSE, sep = "\t")
 ```
@@
 maf_summ$isDeleterious <- ifelse(maf_summ$isDeleterious == "TRUE", "Yes", "No")
+
 knitr::kable(maf_summ, caption = "Distribution of variant classifications in the MAF file") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
+```
+
+```{r}
+max(nchar(as.character(maf_raw$Tumor_Seq_Allele1)))
+maf_raw %>% group_by(Variant_Type, isTCGAhotspot) %>% tally()
+
+test <- filter(maf_raw, Hugo_Symbol == "KRAS")
+test %>% group_by(isDeleterious) %>% tally()
 ```

### 2018-09-10 lineages_18Q3.Rmd
updated Rmd, new Wilcoxon test results rds files

@@
 # Add Mutation_Status column
-maf_df$Mutation_Status <- ifelse(maf_df$isDeleterious == TRUE, "Mutant", "Other")
+maf_df$Mutation_Status_Deleterious <- ifelse(maf_df$isDeleterious == TRUE, "Mutant", "Other")
 maf_df$Mutation_Status_Nonsilent <- ifelse(maf_df$Variant_Classification == "Silent", "Other", "Mutant")
-maf_df <- unique(subset(maf_df, select = c("Hugo_Symbol", "CCLE_Name", "Broad_ID", "Mutation_Status", "Mutation_Status_Nonsilent")))
+maf_df$Mutation_Status_DeleteriousMissense <- ifelse(maf_df$isDeleterious == TRUE | maf_df$Variant_Classification == "Missense", "Mutant", "Other")
+maf_df <- unique(subset(maf_df, select = c("Hugo_Symbol", "CCLE_Name", "Broad_ID", "Mutation_Status_Deleterious", "Mutation_Status_Nonsilent", "Mutation_Status_DeleteriousMissense")))
 
@@
 crispr_muts <- merge(crispr_melt, maf_df, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
-crispr_muts <- crispr_muts %>% mutate(Mutation_Status = if_else(is.na(Mutation_Status), "Other", Mutation_Status))
 crispr_muts$Hugo_Symbol <- factor(crispr_muts$Hugo_Symbol)
+crispr_muts <- crispr_muts %>% mutate(Mutation_Status_Deleterious = if_else(is.na(Mutation_Status_Deleterious), "Other", Mutation_Status_Deleterious), Mutation_Status_DeleteriousMissense = if_else(is.na(Mutation_Status_DeleteriousMissense), "Other", Mutation_Status_DeleteriousMissense), Mutation_Status_Nonsilent = if_else(is.na(Mutation_Status_Nonsilent), "Other", Mutation_Status_Nonsilent))
 
@@
 crispr_muts_summ <- crispr_muts %>% group_by(Hugo_Symbol) %>%
-  summarize(N_Other = sum(Mutation_Status == "Other"),
-            N_Mutant = sum(Mutation_Status == "Mutant"))
+  summarize(N_Deleterious_Other = sum(Mutation_Status_Deleterious == "Other"),
+            N_Deleterious_Mutant = sum(Mutation_Status_Deleterious == "Mutant"),
+            N_DeleteriousMissense_Other = sum(Mutation_Status_DeleteriousMissense == "Other"),
+            N_DeleteriousMissense_Mutant = sum(Mutation_Status_DeleteriousMissense == "Mutant"),
+            N_Nonsilent_Other = sum(Mutation_Status_Nonsilent == "Other"),
+            N_Nonsilent_Mutant = sum(Mutation_Status_Nonsilent == "Mutant"))
 
@@
 
-# Add Color column
-crispr_data$Color <- ifelse(crispr_data$Mutation_Status == "Other", "cyan3", "darkorchid")
-crispr_data$Color <- factor(crispr_data$Color)
+# Add Color columns
+crispr_data$Color_Deleterious <- ifelse(crispr_data$Mutation_Status_Deleterious == "Other", "cyan3", "darkorchid")
+crispr_data$Color_Deleterious <- factor(crispr_data$Color_Deleterious)
+crispr_data$Color_DeleteriousMissense <- ifelse(crispr_data$Mutation_Status_DeleteriousMissense == "Other", "cyan3", "darkorchid")
+crispr_data$Color_DeleteriousMissense <- factor(crispr_data$Color_DeleteriousMissense)
+crispr_data$Color_Nonsilent <- ifelse(crispr_data$Mutation_Status_Nonsilent == "Other", "cyan3", "darkorchid")
+crispr_data$Color_Nonsilent <- factor(crispr_data$Color_Nonsilent)
 
@@
 ```{r, eval=TRUE}
-crispr_signif <- compare_means(Score ~ Mutation_Status, group.by = c("Hugo_Symbol"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
+crispr_signif <- compare_means(Score ~ Mutation_Status_Deleterious, group.by = c("Hugo_Symbol"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
 crispr_signif <- adj_signif(crispr_signif)
 crispr_signif <- crispr_signif[order(crispr_signif$p),]
-saveRDS(crispr_signif, "./data_munging/rds/crispr_signif.rds")
-
-write.table(crispr_signif, file = "~/Desktop/crispr_signif_gene.csv", quote = FALSE, sep = ",", row.names = FALSE)
-```
-
-```{r}
-crispr_signif <- readRDS("./data_munging/rds/crispr_signif.rds")
+saveRDS(crispr_signif, "./data_munging/rds/crispr_signif_deleterious_gene.rds")
+
+write.table(crispr_signif, file = "~/Desktop/crispr_signif_deleterious_gene.csv", quote = FALSE, sep = ",", row.names = FALSE)
+```
+
+```{r}
+crispr_signif <- readRDS("./data_munging/rds/crispr_signif_deleterious_gene.rds")
 
@@
 ```{r, eval=TRUE}
-crispr_signif_nonsilent<- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
+crispr_signif_nonsilent <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
 crispr_signif_nonsilent <- adj_signif(crispr_signif_nonsilent)
 crispr_signif_nonsilent <- crispr_signif_nonsilent[order(crispr_signif_nonsilent$p),]
-saveRDS(crispr_signif_nonsilent, "./data_munging/rds/crispr_signif_nonsilent.rds")
+saveRDS(crispr_signif_nonsilent, "./data_munging/rds/crispr_signif_nonsilent_gene.rds")
 
@@
 ```{r}
-crispr_signif_nonsilent <- readRDS("./data_munging/rds/crispr_signif_nonsilent.rds")
+crispr_signif_nonsilent <- readRDS("./data_munging/rds/crispr_signif_nonsilent_gene.rds")
 
@@
 
+### Deleterious and missense mutant vs. Other
+
+```{r, eval=TRUE}
+crispr_signif_delmis <- compare_means(Score ~ Mutation_Status_DeleteriousMissense, group.by = c("Hugo_Symbol"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
+crispr_signif_delmis <- adj_signif(crispr_signif_delmis)
+crispr_signif_delmis <- crispr_signif_delmis[order(crispr_signif_delmis$p),]
+saveRDS(crispr_signif_delmis, "./data_munging/rds/crispr_signif_deleteriousmissense_gene.rds")
+
+write.table(crispr_signif_delmis, file = "~/Desktop/crispr_signif_deleteriousmissense_gene.csv", quote = FALSE, sep = ",", row.names = FALSE)
+```
+
+```{r}
+crispr_signif_delmis <- readRDS("./data_munging/rds/crispr_signif_deleteriousmissense_gene.rds")
+
+knitr::kable(filter(crispr_signif_delmis, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant and other cell lines, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+```
+
+```{r fig.height=4, fig.width=8}
+wilcox_gene_delmis_plot <- ggplot(data = crispr_signif_delmis) +
+  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
+  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
+  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
+  # coord_cartesian(ylim = c(0, 3500)) +
+  # scale_y_continuous(breaks = seq(0, 3500, by = 500), labels = formatC(seq(0, 3500, by = 500), format = "d")) +
+  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
+  labs(x = "BH-adjusted p-values", y = "Frequency")
+wilcox_gene_delmis_plot
+```
+
 ## Grouped by gene and lineage
@@
 ```{r, eval=TRUE}
-crispr_signif_lineage <- compare_means(Score ~ Mutation_Status, group.by = c("Hugo_Symbol", "group_general_lineage_name"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
+crispr_signif_lineage <- compare_means(Score ~ Mutation_Status_Deleterious, group.by = c("Hugo_Symbol", "group_general_lineage_name"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
 crispr_signif_lineage <- adj_signif(crispr_signif_lineage)
 crispr_signif_lineage <- crispr_signif_lineage[order(crispr_signif_lineage$p),]
-saveRDS(crispr_signif_lineage, "./data_munging/rds/crispr_signif_lineage.rds")
-
-write.table(crispr_signif_lineage, file = "~/Desktop/crispr_signif_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
-```
-
-```{r}
-crispr_signif_lineage <- readRDS("./data_munging/rds/crispr_signif_lineage.rds")
+saveRDS(crispr_signif_lineage, "./data_munging/rds/crispr_signif_deleterious_lineage.rds")
+
+write.table(crispr_signif_lineage, file = "~/Desktop/crispr_signif_deleterious_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
+```
+
+```{r}
+crispr_signif_lineage <- readRDS("./data_munging/rds/crispr_signif_deleterious_lineage.rds")
 
@@
 
+### Deleterious and missense mutant vs. Other
+
+```{r, eval=TRUE}
+crispr_signif_delmis_lineage <- compare_means(Score ~ Mutation_Status_DeleteriousMissense, group.by = c("Hugo_Symbol", "group_general_lineage_name"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
+crispr_signif_delmis_lineage <- adj_signif(crispr_signif_delmis_lineage)
+crispr_signif_delmis_lineage <- crispr_signif_delmis_lineage[order(crispr_signif_delmis_lineage$p),]
+saveRDS(crispr_signif_delmis_lineage, "./data_munging/rds/crispr_signif_deleteriousmissense_lineage.rds")
+
+write.table(crispr_signif_delmis_lineage, file = "~/Desktop/crispr_signif_deleteriousmissense_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
+```
+
+```{r}
+crispr_signif_delmis_lineage <- readRDS("./data_munging/rds/crispr_signif_deleteriousmissense_lineage.rds")
+
+knitr::kable(filter(crispr_signif_delmis_lineage, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant and other cell lines, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+```
+
+```{r fig.height=4, fig.width=8}
+wilcox_gene_delmis_lineage_plot <- ggplot(data = crispr_signif_delmis_lineage) +
+  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
+  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
+  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
+  # coord_cartesian(ylim = c(0, 3500)) +
+  # scale_y_continuous(breaks = seq(0, 3500, by = 500), labels = formatC(seq(0, 3500, by = 500), format = "d")) +
+  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
+  labs(x = "BH-adjusted p-values", y = "Frequency")
+wilcox_gene_delmis_lineage_plot
+```
+
 ## Grouped by gene and tissue
@@
 ```{r, eval=TRUE}
-crispr_signif_tissue <- compare_means(Score ~ Mutation_Status, group.by = c("Hugo_Symbol", "primary_tissue"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
+crispr_signif_tissue <- compare_means(Score ~ Mutation_Status_Deleterious, group.by = c("Hugo_Symbol", "primary_tissue"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
 crispr_signif_tissue <- adj_signif(crispr_signif_tissue)
 crispr_signif_tissue <- crispr_signif_tissue[order(crispr_signif_tissue$p),]
-saveRDS(crispr_signif_tissue, "./data_munging/rds/crispr_signif_tissue.rds")
-
-write.table(crispr_signif_tissue, file = "~/Desktop/crispr_signif_tissue.csv", quote = FALSE, sep = ",", row.names = FALSE)
-```
-
-```{r}
-crispr_signif_tissue <- readRDS("./data_munging/rds/crispr_signif_tissue.rds")
+saveRDS(crispr_signif_tissue, "./data_munging/rds/crispr_signif_deleterious_tissue.rds")
+
+write.table(crispr_signif_tissue, file = "~/Desktop/crispr_signif_deleterious_tissue.csv", quote = FALSE, sep = ",", row.names = FALSE)
+```
+
+```{r}
+crispr_signif_tissue <- readRDS("./data_munging/rds/crispr_signif_deleterious_tissue.rds")
 
@@
 wilcox_tissue_nonsilent_plot
+```
+
+### Deleterious and missense mutant vs. Other
+
+```{r, eval=TRUE}
+crispr_signif_delmis_tissue <- compare_means(Score ~ Mutation_Status_DeleteriousMissense, group.by = c("Hugo_Symbol", "primary_tissue"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
+crispr_signif_delmis_tissue <- adj_signif(crispr_signif_delmis_tissue)
+crispr_signif_delmis_tissue <- crispr_signif_delmis_tissue[order(crispr_signif_delmis_tissue$p),]
+saveRDS(crispr_signif_delmis_tissue, "./data_munging/rds/crispr_signif_deleteriousmissense_tissue.rds")
+
+write.table(crispr_signif_delmis_tissue, file = "~/Desktop/crispr_signif_deleteriousmissense_tissue.csv", quote = FALSE, sep = ",", row.names = FALSE)
+```
+
+```{r}
+crispr_signif_delmis_tissue <- readRDS("./data_munging/rds/crispr_signif_deleteriousmissense_tissue.rds")
+
+knitr::kable(filter(crispr_signif_delmis_tissue, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant and other cell lines, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+```
+
+```{r fig.height=4, fig.width=8}
+wilcox_gene_delmis_tissue_plot <- ggplot(data = crispr_signif_delmis_tissue) +
+  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
+  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
+  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
+  # coord_cartesian(ylim = c(0, 3500)) +
+  # scale_y_continuous(breaks = seq(0, 3500, by = 500), labels = formatC(seq(0, 3500, by = 500), format = "d")) +
+  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
+  labs(x = "BH-adjusted p-values", y = "Frequency")
+wilcox_gene_delmis_tissue_plot
 ```

### 2018-09-11 lineages_18Q3.Rmd
delmis/nonsilent tissue Wilcoxon results

@@
 
-knitr::kable(filter(crispr_signif_delmis, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant and other cell lines, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(filter(crispr_signif_delmis, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious and missense mutant and other cell lines, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
-knitr::kable(filter(crispr_signif_delmis_lineage, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant and other cell lines, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(filter(crispr_signif_delmis_lineage, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious and missense mutant and other cell lines, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
-knitr::kable(filter(crispr_signif_delmis_tissue, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant and other cell lines, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(filter(crispr_signif_delmis_tissue, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious and missense mutant and other cell lines, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
 ```

### 2018-09-11 lineages_18Q3.Rmd
updated WIlcoxon tests

@@
 ```{r}
-ccl_converter <- read.delim("./data_munging/cell_line_database_v1_20180907.tsv", row.names = 1, sep = "\t", header = TRUE)
+ccl_converter <- read.delim("./data_munging/cell_line_database_v1_20180911.tsv", row.names = 1, sep = "\t", header = TRUE)
 ```
@@
 # Editing CCL DB
-groupings <- read.delim("./data_munging/cell_line_database_completed_extra_grouped_doids_FINAL.csv", sep = "\t", header = TRUE)
-groupings <- unique(select(groupings, lineage_name, grouped_general_doid, group_general_lineage_name))
-
-ccl_converter <- read.delim("./data_munging/cell_line_database_FINAL_MASTER.tsv", sep = "\t", row.names = 1, header = TRUE)
-colnames(ccl_converter)[colnames(ccl_converter) == "ccle_cell_line_name"] <- "CCLE_Name"
-colnames(ccl_converter)[colnames(ccl_converter) == "broad_id"] <- "Broad_ID"
-
-ccl_converter <- merge(ccl_converter, groupings, by = "lineage_name", all.x = TRUE)
+# groupings <- read.delim("./data_munging/cell_line_database_completed_extra_grouped_doids_FINAL.csv", sep = "\t", header = TRUE)
+# groupings <- unique(select(groupings, lineage_name, grouped_general_doid, group_general_lineage_name))
+# ccl_converter <- read.delim("./data_munging/cell_line_database_FINAL_MASTER.tsv", sep = "\t", row.names = 1, header = TRUE)
+# colnames(ccl_converter)[colnames(ccl_converter) == "ccle_cell_line_name"] <- "CCLE_Name"
+# colnames(ccl_converter)[colnames(ccl_converter) == "broad_id"] <- "Broad_ID"
+# ccl_converter <- merge(ccl_converter, groupings, by = "lineage_name", all.x = TRUE)
+
+# Testing completeness of grouped lineage names
+unique(ccl_converter$group_general_lineage_name)
+test <- filter(ccl_converter, is.na(group_general_lineage_name))
+unique(test$lineage_name)
+test2 <- filter(ccl_converter, is.na(grouped_general_doid))
 ```
@@
 # Select columns
-maf_df <- subset(maf_raw, select = c("Hugo_Symbol", "Tumor_Sample_Barcode", "Broad_ID", "Variant_Classification", "isDeleterious"))
+maf_df <- subset(maf_raw, select = c("Hugo_Symbol", "Tumor_Sample_Barcode", "Broad_ID", "Variant_Classification", "isDeleterious", "Reference_Allele"))
 colnames(maf_df)[colnames(maf_df) == "Tumor_Sample_Barcode"] <- "CCLE_Name"
+maf_df$Var_Length <- nchar(as.character(maf_df$Reference_Allele))
+
 # Add Mutation_Status column
@@
 maf_df$Mutation_Status_Nonsilent <- ifelse(maf_df$Variant_Classification == "Silent", "Other", "Mutant")
-maf_df$Mutation_Status_DeleteriousMissense <- ifelse(maf_df$isDeleterious == TRUE | maf_df$Variant_Classification == "Missense", "Mutant", "Other")
-maf_df <- unique(subset(maf_df, select = c("Hugo_Symbol", "CCLE_Name", "Broad_ID", "Mutation_Status_Deleterious", "Mutation_Status_Nonsilent", "Mutation_Status_DeleteriousMissense")))
+maf_df$Mutation_Status_DeleteriousMissense <- ifelse(maf_df$isDeleterious == TRUE | maf_df$Variant_Classification == "Missense_Mutation", "Mutant", "Other")
+maf_df <- unique(subset(maf_df, select = c("Hugo_Symbol", "CCLE_Name", "Broad_ID", "Mutation_Status_Deleterious", "Mutation_Status_Nonsilent", "Mutation_Status_DeleteriousMissense", "Var_Length")))
 
@@
 ```{r}
-max(nchar(as.character(maf_raw$Tumor_Seq_Allele1)))
+max(nchar(as.character(maf_raw$Reference_Allele)))
 maf_raw %>% group_by(Variant_Type, isTCGAhotspot) %>% tally()
 
-test <- filter(maf_raw, Hugo_Symbol == "KRAS")
+test <- filter(maf_df, Hugo_Symbol == "KRAS")
 test %>% group_by(isDeleterious) %>% tally()
@@
 crispr_data <- readRDS("./../crispr_lineages_giant_files/crispr_data_18Q3.rds")
-crispr_ccl <- data.frame("Broad_ID" = crispr_data$Broad_ID)
+# crispr_ccl <- data.frame("Broad_ID" = crispr_data$Broad_ID)
 # write.table(crispr_data, file = "~/Desktop/crispr_data.tsv", quote = FALSE, sep = "\t")
@@
 
+Filter for point mutations:
+```{r}
+crispr_data_ptmuts <- filter(crispr_data, Var_Length == 1)
+test_ptmuts <- filter(crispr_data_ptmuts, is.na(group_general_lineage_name))
+```
+
 ## Grouped by gene
@@
 
-```{r, eval=TRUE}
-crispr_signif <- compare_means(Score ~ Mutation_Status_Deleterious, group.by = c("Hugo_Symbol"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
-crispr_signif <- adj_signif(crispr_signif)
-crispr_signif <- crispr_signif[order(crispr_signif$p),]
-saveRDS(crispr_signif, "./data_munging/rds/crispr_signif_deleterious_gene.rds")
-
-write.table(crispr_signif, file = "~/Desktop/crispr_signif_deleterious_gene.csv", quote = FALSE, sep = ",", row.names = FALSE)
-```
-
-```{r}
-crispr_signif <- readRDS("./data_munging/rds/crispr_signif_deleterious_gene.rds")
-
-knitr::kable(filter(crispr_signif, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious mutant and other cell lines, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+```{r, eval=FALSE}
+crispr_signif_del <- compare_means(Score ~ Mutation_Status_Deleterious, group.by = c("Hugo_Symbol"), data = crispr_data_ptmuts, method = "wilcox.test", p.adjust.method = "BH")
+crispr_signif_del <- adj_signif(crispr_signif_del)
+crispr_signif_del <- crispr_signif_del[order(crispr_signif_del$p),]
+saveRDS(crispr_signif_del, "./data_munging/rds/crispr_signif_deleterious_gene.rds")
+
+# write.table(crispr_signif_del, file = "~/Desktop/crispr_signif_deleterious_gene.csv", quote = FALSE, sep = ",", row.names = FALSE)
+```
+
+```{r}
+crispr_signif_del <- readRDS("./data_munging/rds/crispr_signif_deleterious_gene.rds")
+
+knitr::kable(filter(crispr_signif_del, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious mutant and other cell lines, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 ```{r fig.height=4, fig.width=8}
-wilcox_gene_plot <- ggplot(data = crispr_signif) +
+wilcox_gene_plot <- ggplot(data = crispr_signif_del) +
   geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
@@
   scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
-  coord_cartesian(ylim = c(0, 3500)) +
-  scale_y_continuous(breaks = seq(0, 3500, by = 500), labels = formatC(seq(0, 3500, by = 500), format = "d")) +
   scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
@@
 
-```{r, eval=TRUE}
-crispr_signif_nonsilent <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
+```{r, eval=FALSE}
+crispr_signif_nonsilent <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol"), data = crispr_data_ptmuts, method = "wilcox.test", p.adjust.method = "BH")
 crispr_signif_nonsilent <- adj_signif(crispr_signif_nonsilent)
@@
 
-write.table(crispr_signif_nonsilent, file = "~/Desktop/crispr_signif_nonsilent_gene.csv", quote = FALSE, sep = ",", row.names = FALSE)
+# write.table(crispr_signif_nonsilent, file = "~/Desktop/crispr_signif_nonsilent_gene.csv", quote = FALSE, sep = ",", row.names = FALSE)
 ```
@@
 
-```{r, eval=TRUE}
-crispr_signif_delmis <- compare_means(Score ~ Mutation_Status_DeleteriousMissense, group.by = c("Hugo_Symbol"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
+```{r, eval=FALSE}
+crispr_signif_delmis <- compare_means(Score ~ Mutation_Status_DeleteriousMissense, group.by = c("Hugo_Symbol"), data = crispr_data_ptmuts, method = "wilcox.test", p.adjust.method = "BH")
 crispr_signif_delmis <- adj_signif(crispr_signif_delmis)
@@
 
-write.table(crispr_signif_delmis, file = "~/Desktop/crispr_signif_deleteriousmissense_gene.csv", quote = FALSE, sep = ",", row.names = FALSE)
+# write.table(crispr_signif_delmis, file = "~/Desktop/crispr_signif_deleteriousmissense_gene.csv", quote = FALSE, sep = ",", row.names = FALSE)
 ```
@@
 
-```{r, eval=TRUE}
-crispr_signif_lineage <- compare_means(Score ~ Mutation_Status_Deleterious, group.by = c("Hugo_Symbol", "group_general_lineage_name"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
-crispr_signif_lineage <- adj_signif(crispr_signif_lineage)
-crispr_signif_lineage <- crispr_signif_lineage[order(crispr_signif_lineage$p),]
-saveRDS(crispr_signif_lineage, "./data_munging/rds/crispr_signif_deleterious_lineage.rds")
-
-write.table(crispr_signif_lineage, file = "~/Desktop/crispr_signif_deleterious_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
-```
-
-```{r}
-crispr_signif_lineage <- readRDS("./data_munging/rds/crispr_signif_deleterious_lineage.rds")
-
-knitr::kable(filter(crispr_signif_lineage, p < 0.05)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious mutant and other cell lines by lineage, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+```{r, eval=FALSE}
+crispr_signif_del_lineage <- compare_means(Score ~ Mutation_Status_Deleterious, group.by = c("Hugo_Symbol", "group_general_lineage_name"), data = crispr_data_ptmuts, method = "wilcox.test", p.adjust.method = "BH")
+crispr_signif_del_lineage <- adj_signif(crispr_signif_del_lineage)
+crispr_signif_del_lineage <- crispr_signif_del_lineage[order(crispr_signif_del_lineage$p),]
+saveRDS(crispr_signif_del_lineage, "./data_munging/rds/crispr_signif_deleterious_lineage.rds")
+
+# write.table(crispr_signif_del_lineage, file = "~/Desktop/crispr_signif_deleterious_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
+```
+
+```{r}
+crispr_signif_del_lineage <- readRDS("./data_munging/rds/crispr_signif_deleterious_lineage.rds")
+
+knitr::kable(filter(crispr_signif_del_lineage, p < 0.05)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious mutant and other cell lines by lineage, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 ```{r fig.height=4, fig.width=8}
-wilcox_lineage_plot <- ggplot(data = crispr_signif_lineage) +
+wilcox_lineage_plot <- ggplot(data = crispr_signif_del_lineage) +
   geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
@@
 
-```{r, eval=TRUE}
-crispr_signif_nonsilent_lineage <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "group_general_lineage_name"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
+```{r, eval=FALSE}
+crispr_signif_nonsilent_lineage <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "group_general_lineage_name"), data = crispr_data_ptmuts, method = "wilcox.test", p.adjust.method = "BH")
 crispr_signif_nonsilent_lineage <- adj_signif(crispr_signif_nonsilent_lineage)
@@
 
-write.table(crispr_signif_nonsilent_lineage, file = "~/Desktop/crispr_signif_nonsilent_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
+# write.table(crispr_signif_nonsilent_lineage, file = "~/Desktop/crispr_signif_nonsilent_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
 ```
@@
 
-```{r, eval=TRUE}
+```{r, eval=FALSE}
 crispr_signif_delmis_lineage <- compare_means(Score ~ Mutation_Status_DeleteriousMissense, group.by = c("Hugo_Symbol", "group_general_lineage_name"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
@@
 
-write.table(crispr_signif_delmis_lineage, file = "~/Desktop/crispr_signif_deleteriousmissense_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
+# write.table(crispr_signif_delmis_lineage, file = "~/Desktop/crispr_signif_deleteriousmissense_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
 ```
@@
 
-knitr::kable(filter(crispr_signif_delmis_lineage, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious and missense mutant and other cell lines, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(filter(crispr_signif_delmis_lineage, p < 0.05)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious and missense mutant and other cell lines, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
-```{r, eval=TRUE}
-crispr_signif_tissue <- compare_means(Score ~ Mutation_Status_Deleterious, group.by = c("Hugo_Symbol", "primary_tissue"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
-crispr_signif_tissue <- adj_signif(crispr_signif_tissue)
-crispr_signif_tissue <- crispr_signif_tissue[order(crispr_signif_tissue$p),]
-saveRDS(crispr_signif_tissue, "./data_munging/rds/crispr_signif_deleterious_tissue.rds")
-
-write.table(crispr_signif_tissue, file = "~/Desktop/crispr_signif_deleterious_tissue.csv", quote = FALSE, sep = ",", row.names = FALSE)
-```
-
-```{r}
-crispr_signif_tissue <- readRDS("./data_munging/rds/crispr_signif_deleterious_tissue.rds")
-
-knitr::kable(filter(crispr_signif_tissue, p < 0.05)[, c("Hugo_Symbol", "primary_tissue", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious mutant and other cell lines by tissue, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+```{r, eval=FALSE}
+crispr_signif_del_tissue <- compare_means(Score ~ Mutation_Status_Deleterious, group.by = c("Hugo_Symbol", "primary_tissue"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
+crispr_signif_del_tissue <- adj_signif(crispr_signif_del_tissue)
+crispr_signif_del_tissue <- crispr_signif_del_tissue[order(crispr_signif_del_tissue$p),]
+saveRDS(crispr_signif_del_tissue, "./data_munging/rds/crispr_signif_deleterious_tissue.rds")
+
+# write.table(crispr_signif_del_tissue, file = "~/Desktop/crispr_signif_deleterious_tissue.csv", quote = FALSE, sep = ",", row.names = FALSE)
+```
+
+```{r}
+crispr_signif_del_tissue <- readRDS("./data_munging/rds/crispr_signif_deleterious_tissue.rds")
+
+knitr::kable(filter(crispr_signif_del_tissue, p < 0.05)[, c("Hugo_Symbol", "primary_tissue", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious mutant and other cell lines by tissue, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 ```{r fig.height=4, fig.width=8}
-wilcox_tissue_plot <- ggplot(data = crispr_signif_tissue) +
+wilcox_tissue_plot <- ggplot(data = crispr_signif_del_tissue) +
   geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
@@
 
-```{r, eval=TRUE}
-crispr_signif_nonsilent_tissue <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "primary_tissue"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
+```{r, eval=FALSE}
+crispr_signif_nonsilent_tissue <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "primary_tissue"), data = crispr_data_ptmuts, method = "wilcox.test", p.adjust.method = "BH")
 crispr_signif_nonsilent_tissue <- adj_signif(crispr_signif_nonsilent_tissue)
@@
 
-write.table(crispr_signif_nonsilent_tissue, file = "~/Desktop/crispr_signif_nonsilent_tissue.csv", quote = FALSE, sep = ",", row.names = FALSE)
+# write.table(crispr_signif_nonsilent_tissue, file = "~/Desktop/crispr_signif_nonsilent_tissue.csv", quote = FALSE, sep = ",", row.names = FALSE)
 ```
@@
 
-```{r, eval=TRUE}
-crispr_signif_delmis_tissue <- compare_means(Score ~ Mutation_Status_DeleteriousMissense, group.by = c("Hugo_Symbol", "primary_tissue"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
+```{r, eval=FALSE}
+crispr_signif_delmis_tissue <- compare_means(Score ~ Mutation_Status_DeleteriousMissense, group.by = c("Hugo_Symbol", "primary_tissue"), data = crispr_data_ptmuts, method = "wilcox.test", p.adjust.method = "BH")
 crispr_signif_delmis_tissue <- adj_signif(crispr_signif_delmis_tissue)
@@
 
-write.table(crispr_signif_delmis_tissue, file = "~/Desktop/crispr_signif_deleteriousmissense_tissue.csv", quote = FALSE, sep = ",", row.names = FALSE)
+# write.table(crispr_signif_delmis_tissue, file = "~/Desktop/crispr_signif_deleteriousmissense_tissue.csv", quote = FALSE, sep = ",", row.names = FALSE)
 ```
@@
 
-```{r fig.height=12, fig.width=12, include=FALSE}
+```{r fig.height=12, fig.width=12, include=FALSE, eval=FALSE}
 makeCRISPRgrob("KRAS")
@@
 
-```{r fig.height=12, fig.width=12, include=FALSE}
+```{r fig.height=12, fig.width=12, include=FALSE, eval=FALSE}
 makeCRISPRlinplot("KRAS")
@@
 
-```{r fig.height=12, fig.width=12, include=FALSE}
+```{r fig.height=12, fig.width=12, include=FALSE, eval=FALSE}
 makeCRISPRtissueplot("KRAS")
@@
 maf_df_filt <- filter(maf_df, Hugo_Symbol %in% unique(crispr_data$Hugo_Symbol))
-maf_summ_filt <- maf_df_filt %>% group_by(Mutation_Status) %>% tally()
-maf_summ_filt$Percent <- format(round(maf_summ_filt$n / sum(maf_summ_filt$n) * 100, 4), nsmall = 2)
-maf_summ_filt$Percent <- as.numeric(as.character(maf_summ_filt$Percent))
+# maf_summ_filt <- maf_df_filt %>% group_by(Mutation_Status) %>% tally()
+# maf_summ_filt$Percent <- format(round(maf_summ_filt$n / sum(maf_summ_filt$n) * 100, 4), nsmall = 2)
+# maf_summ_filt$Percent <- as.numeric(as.character(maf_summ_filt$Percent))
 ```
@@
 
-```{r fig.height=18, fig.width=5}
+```{r fig.height=18, fig.width=5, eval=FALSE}
 sig_genes <- c("KRAS", "TP53", "NRAS", "BRAF", "PIK3CA", "PTEN", "CTNNB1")

### 2018-09-12 lineages_18Q3.Rmd
updaed rmd, knit to html

@@
     code_folding: hide
+    pandoc_args: [
+      "+RTS", "-K1024m",
+      "-RTS"
+    ]
 ---
@@
 
-test <- filter(maf_df, Hugo_Symbol == "KRAS")
+test <- filter(maf_raw, Hugo_Symbol == "KRAS")
 test %>% group_by(isDeleterious) %>% tally()
@@
 crispr_data <- readRDS("./../crispr_lineages_giant_files/crispr_data_18Q3.rds")
-# crispr_ccl <- data.frame("Broad_ID" = crispr_data$Broad_ID)
+crispr_ccl <- data.frame("Broad_ID" = crispr_data$Broad_ID)
 # write.table(crispr_data, file = "~/Desktop/crispr_data.tsv", quote = FALSE, sep = "\t")
@@
 
-knitr::kable(filter(crispr_signif_delmis_lineage, p < 0.05)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious and missense mutant and other cell lines, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(filter(crispr_signif_delmis_lineage, p < 0.05)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious and missense mutant and other cell lines by lineage, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
-knitr::kable(filter(crispr_signif_delmis_tissue, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious and missense mutant and other cell lines, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(filter(crispr_signif_delmis_tissue, p < 0.05)[, c("Hugo_Symbol", "primary_tissue", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious and missense mutant and other cell lines by tissue, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 Data management:
-```{r}
+```{r, eval=FALSE}
 crispr_all_bygene <- paste0(list.files("./plots_18Q3/crispr_grouped_plots_cgc", full.names = TRUE))
@@
 Data management:
-```{r}
+```{r, eval=FALSE}
 crispr_all_bygene <- paste0(list.files("./plots_18Q3/crispr_lineage_plots_cgc", full.names = TRUE))
@@
 Data management:
-```{r}
+```{r, eval=FALSE}
 crispr_all_bygene <- paste0(list.files("./plots_18Q3/crispr_tissue_plots_cgc", full.names = TRUE))
@@
 DepMap cell line metadata:
-```{r}
+```{r, eval=FALSE}
 # From figshare

### 2018-09-12 lineages_18Q3.Rmd
updated rmd

@@
 test_ptmuts <- filter(crispr_data_ptmuts, is.na(group_general_lineage_name))
+test_ptmuts <- filter(crispr_data_ptmuts, Hugo_Symbol == "KRAS")
 ```
@@
 # write.table(crispr_signif_delmis, file = "~/Desktop/crispr_signif_deleteriousmissense_gene.csv", quote = FALSE, sep = ",", row.names = FALSE)
+```
+
+```{r}
+compare_means(Score ~ Mutation_Status_DeleteriousMissense, group.by = c("Hugo_Symbol"), data = crispr_data_ptmuts[which(crispr_data_ptmuts$Hugo_Symbol == "KRAS"),], method = "wilcox.test", p.adjust.method = "BH")
 ```

### 2018-09-14 lineages_18Q3.Rmd

@@
 
-# Wilcoxon tests
+# Wilcoxon tests: Point mutations {.tabset .tabset-fade .tabset-pills}
 
@@
 
-## Grouped by gene
+## Grouped by gene  {.tabset .tabset-fade .tabset-pills}
 
@@
   scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
-  # coord_cartesian(ylim = c(0, 3500)) +
-  # scale_y_continuous(breaks = seq(0, 3500, by = 500), labels = formatC(seq(0, 3500, by = 500), format = "d")) +
   scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
@@
 
-## Grouped by gene and lineage
+## Grouped by gene and lineage {.tabset .tabset-fade .tabset-pills}
 
@@
 
-## Grouped by gene and tissue
+## Grouped by gene and tissue {.tabset .tabset-fade .tabset-pills}
 
@@
   scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
-  # scale_y_continuous(breaks = seq(0, 50000, by = 5000), labels = formatC(seq(0, 50000, by = 5000), format = "d")) +
   scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
@@
 wilcox_gene_delmis_tissue_plot
+```
+
+# Wilcoxon tests: All mutations
+
+--------------------------------------------------------------------------------
+
+## Grouped by gene  {.tabset .tabset-fade .tabset-pills}
+
+### Deleterious vs. Other
+
+```{r, eval=FALSE}
+crispr_signif_allmut_del <- compare_means(Score ~ Mutation_Status_Deleterious, group.by = c("Hugo_Symbol"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
+crispr_signif_allmut_del <- adj_signif(crispr_signif_allmut_del)
+crispr_signif_allmut_del <- crispr_signif_allmut_del[order(crispr_signif_allmut_del$p),]
+saveRDS(crispr_signif_allmut_del, "./data_munging/rds/crispr_signif_allmut_deleterious_gene.rds")
+
+# write.table(crispr_signif_allmut_del, file = "~/Desktop/crispr_signif_allmut_deleterious_gene.csv", quote = FALSE, sep = ",", row.names = FALSE)
+```
+
+```{r}
+crispr_signif_allmut_del <- readRDS("./data_munging/rds/crispr_signif_allmut_deleterious_gene.rds")
+
+knitr::kable(filter(crispr_signif_allmut_del, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious mutant and other cell lines, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+```
+
+```{r fig.height=4, fig.width=8}
+wilcox_gene_allmut_plot <- ggplot(data = crispr_signif_allmut_del) +
+  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
+  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
+  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
+  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
+  labs(x = "BH-adjusted p-values", y = "Frequency")
+wilcox_gene_allmut_plot
+# ggsave(filename = "./plots_18Q3/crispr/pvals_genes.pdf", plot = wilcox_gene_plot, width = 8, height = 4, device = "pdf")
+```
+
+### Non-silent mutant vs. Other
+
+```{r, eval=FALSE}
+crispr_signif_allmut_nonsilent <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
+crispr_signif_allmut_nonsilent <- adj_signif(crispr_signif_allmut_nonsilent)
+crispr_signif_allmut_nonsilent <- crispr_signif_allmut_nonsilent[order(crispr_signif_allmut_nonsilent$p),]
+saveRDS(crispr_signif_allmut_nonsilent, "./data_munging/rds/crispr_signif_allmut_nonsilent_gene.rds")
+
+# write.table(crispr_signif_allmut_nonsilent, file = "~/Desktop/crispr_signif_allmut_nonsilent_gene.csv", quote = FALSE, sep = ",", row.names = FALSE)
+```
+
+```{r}
+crispr_signif_allmut_nonsilent <- readRDS("./data_munging/rds/crispr_signif_allmut_nonsilent_gene.rds")
+
+knitr::kable(filter(crispr_signif_allmut_nonsilent, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant and other cell lines, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+```
+
+```{r fig.height=4, fig.width=8}
+wilcox_gene_allmut_nonsilent_plot <- ggplot(data = crispr_signif_allmut_nonsilent) +
+  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
+  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
+  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
+  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
+  labs(x = "BH-adjusted p-values", y = "Frequency")
+wilcox_gene_allmut_nonsilent_plot
+```
+
+### Deleterious and missense mutant vs. Other
+
+```{r, eval=FALSE}
+crispr_signif_allmut_delmis <- compare_means(Score ~ Mutation_Status_DeleteriousMissense, group.by = c("Hugo_Symbol"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
+crispr_signif_allmut_delmis <- adj_signif(crispr_signif_allmut_delmis)
+crispr_signif_allmut_delmis <- crispr_signif_allmut_delmis[order(crispr_signif_allmut_delmis$p),]
+saveRDS(crispr_signif_allmut_delmis, "./data_munging/rds/crispr_signif_allmut_deleteriousmissense_gene.rds")
+
+# write.table(crispr_signif_allmut_delmis, file = "~/Desktop/crispr_signif_allmut_deleteriousmissense_gene.csv", quote = FALSE, sep = ",", row.names = FALSE)
+```
+
+```{r}
+crispr_signif_allmut_delmis <- readRDS("./data_munging/rds/crispr_signif_allmut_deleteriousmissense_gene.rds")
+
+knitr::kable(filter(crispr_signif_allmut_delmis, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious and missense mutant and other cell lines, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+```
+
+```{r fig.height=4, fig.width=8}
+wilcox_gene_allmut_delmis_plot <- ggplot(data = crispr_signif_allmut_delmis) +
+  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
+  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
+  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
+  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
+  labs(x = "BH-adjusted p-values", y = "Frequency")
+wilcox_gene_allmut_delmis_plot
+```
+
+## Grouped by gene and lineage {.tabset .tabset-fade .tabset-pills}
+
+### Deleterious vs. Other
+
+```{r, eval=FALSE}
+crispr_signif_allmut_del_lineage <- compare_means(Score ~ Mutation_Status_Deleterious, group.by = c("Hugo_Symbol", "group_general_lineage_name"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
+crispr_signif_allmut_del_lineage <- adj_signif(crispr_signif_allmut_del_lineage)
+crispr_signif_allmut_del_lineage <- crispr_signif_allmut_del_lineage[order(crispr_signif_allmut_del_lineage$p),]
+saveRDS(crispr_signif_allmut_del_lineage, "./data_munging/rds/crispr_signif_allmut_deleterious_lineage.rds")
+
+# write.table(crispr_signif_allmut_del_lineage, file = "~/Desktop/crispr_signif_allmut_deleterious_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
+```
+
+```{r}
+crispr_signif_allmut_del_lineage <- readRDS("./data_munging/rds/crispr_signif_allmut_deleterious_lineage.rds")
+
+knitr::kable(filter(crispr_signif_allmut_del_lineage, p < 0.05)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious mutant and other cell lines by lineage, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+```
+
+```{r fig.height=4, fig.width=8}
+wilcox_lineage_allmut_plot <- ggplot(data = crispr_signif_allmut_del_lineage) +
+  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
+  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
+  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
+  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
+  labs(x = "BH-adjusted p-values", y = "Frequency")
+wilcox_lineage_allmut_plot
+```
+
+### Non-silent mutant vs. Other
+
+```{r, eval=FALSE}
+crispr_signif_allmut_nonsilent_lineage <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "group_general_lineage_name"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
+crispr_signif_allmut_nonsilent_lineage <- adj_signif(crispr_signif_allmut_nonsilent_lineage)
+crispr_signif_allmut_nonsilent_lineage <- crispr_signif_allmut_nonsilent_lineage[order(crispr_signif_allmut_nonsilent_lineage$p),]
+saveRDS(crispr_signif_allmut_nonsilent_lineage, "./data_munging/rds/crispr_signif_allmut_nonsilent_lineage.rds")
+
+# write.table(crispr_signif_allmut_nonsilent_lineage, file = "~/Desktop/crispr_signif_allmut_nonsilent_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
+```
+
+```{r}
+crispr_signif_allmut_nonsilent_lineage <- readRDS("./data_munging/rds/crispr_signif_allmut_nonsilent_lineage.rds")
+
+knitr::kable(filter(crispr_signif_allmut_nonsilent_lineage, p < 0.05)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant and other cell lines by lineage, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+```
+
+```{r fig.height=4, fig.width=8}
+wilcox_lineage_allmut_nonsilent_plot <- ggplot(data = crispr_signif_allmut_nonsilent_lineage) +
+  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
+  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
+  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
+  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
+  labs(x = "BH-adjusted p-values", y = "Frequency")
+wilcox_lineage_allmut_nonsilent_plot
+```
+
+### Deleterious and missense mutant vs. Other
+
+```{r, eval=FALSE}
+crispr_signif_allmut_delmis_lineage <- compare_means(Score ~ Mutation_Status_DeleteriousMissense, group.by = c("Hugo_Symbol", "group_general_lineage_name"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
+crispr_signif_allmut_delmis_lineage <- adj_signif(crispr_signif_allmut_delmis_lineage)
+crispr_signif_allmut_delmis_lineage <- crispr_signif_allmut_delmis_lineage[order(crispr_signif_allmut_delmis_lineage$p),]
+saveRDS(crispr_signif_allmut_delmis_lineage, "./data_munging/rds/crispr_signif_allmut_deleteriousmissens_lineage.rds")
+
+# write.table(crispr_signif_allmut_delmis_lineage, file = "~/Desktop/crispr_signif_allmut_deleteriousmissense_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
+```
+
+```{r}
+crispr_signif_allmut_delmis_lineage <- readRDS("./data_munging/rds/crispr_signif_allmut_deleteriousmissens_lineage.rds")
+
+knitr::kable(filter(crispr_signif_allmut_delmis_lineage, p < 0.05)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious and missense mutant and other cell lines, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+```
+
+```{r fig.height=4, fig.width=8}
+wilcox_lineage_allmut_delmis_plot <- ggplot(data = crispr_signif_allmut_delmis_lineage) +
+  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
+  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
+  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
+  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
+  labs(x = "BH-adjusted p-values", y = "Frequency")
+wilcox_lineage_allmut_delmis_plot
 ```

### 2018-09-17 lineages_18Q3.Rmd
updated Rmd/html

@@
     pandoc_args: [
-      "+RTS", "-K1024m",
+      "+RTS", "-K2048m",
       "-RTS"
@@
 crispr_signif_del <- crispr_signif_del[order(crispr_signif_del$p),]
-saveRDS(crispr_signif_del, "./data_munging/rds/crispr_signif_deleterious_gene.rds")
-
-# write.table(crispr_signif_del, file = "~/Desktop/crispr_signif_deleterious_gene.csv", quote = FALSE, sep = ",", row.names = FALSE)
-```
-
-```{r}
-crispr_signif_del <- readRDS("./data_munging/rds/crispr_signif_deleterious_gene.rds")
+saveRDS(crispr_signif_del, "./data_munging/rds/crispr_signif_ptmuts_deleterious_gene.rds")
+
+# write.table(crispr_signif_del, file = "~/Desktop/crispr_signif_ptmuts_deleterious_gene.csv", quote = FALSE, sep = ",", row.names = FALSE)
+```
+
+```{r}
+crispr_signif_del <- readRDS("./data_munging/rds/crispr_signif_ptmuts_deleterious_gene.rds")
 
@@
 wilcox_gene_plot
-# ggsave(filename = "./plots_18Q3/crispr/pvals_genes.pdf", plot = wilcox_gene_plot, width = 8, height = 4, device = "pdf")
 ```
@@
 crispr_signif_nonsilent <- crispr_signif_nonsilent[order(crispr_signif_nonsilent$p),]
-saveRDS(crispr_signif_nonsilent, "./data_munging/rds/crispr_signif_nonsilent_gene.rds")
-
-# write.table(crispr_signif_nonsilent, file = "~/Desktop/crispr_signif_nonsilent_gene.csv", quote = FALSE, sep = ",", row.names = FALSE)
-```
-
-```{r}
-crispr_signif_nonsilent <- readRDS("./data_munging/rds/crispr_signif_nonsilent_gene.rds")
+saveRDS(crispr_signif_nonsilent, "./data_munging/rds/crispr_signif_ptmuts_nonsilent_gene.rds")
+
+# write.table(crispr_signif_nonsilent, file = "~/Desktop/crispr_signif_ptmuts_nonsilent_gene.csv", quote = FALSE, sep = ",", row.names = FALSE)
+```
+
+```{r}
+crispr_signif_nonsilent <- readRDS("./data_munging/rds/crispr_signif_ptmuts_nonsilent_gene.rds")
 
@@
 crispr_signif_delmis <- crispr_signif_delmis[order(crispr_signif_delmis$p),]
-saveRDS(crispr_signif_delmis, "./data_munging/rds/crispr_signif_deleteriousmissense_gene.rds")
-
-# write.table(crispr_signif_delmis, file = "~/Desktop/crispr_signif_deleteriousmissense_gene.csv", quote = FALSE, sep = ",", row.names = FALSE)
+saveRDS(crispr_signif_delmis, "./data_munging/rds/crispr_signif_ptmuts_deleteriousmissense_gene.rds")
+
+# write.table(crispr_signif_delmis, file = "~/Desktop/crispr_signif_ptmuts_deleteriousmissense_gene.csv", quote = FALSE, sep = ",", row.names = FALSE)
 ```
@@
 ```{r}
-crispr_signif_delmis <- readRDS("./data_munging/rds/crispr_signif_deleteriousmissense_gene.rds")
+crispr_signif_delmis <- readRDS("./data_munging/rds/crispr_signif_ptmuts_deleteriousmissense_gene.rds")
 
@@
 crispr_signif_del_lineage <- crispr_signif_del_lineage[order(crispr_signif_del_lineage$p),]
-saveRDS(crispr_signif_del_lineage, "./data_munging/rds/crispr_signif_deleterious_lineage.rds")
-
-# write.table(crispr_signif_del_lineage, file = "~/Desktop/crispr_signif_deleterious_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
-```
-
-```{r}
-crispr_signif_del_lineage <- readRDS("./data_munging/rds/crispr_signif_deleterious_lineage.rds")
+saveRDS(crispr_signif_del_lineage, "./data_munging/rds/crispr_signif_ptmuts_deleterious_lineage.rds")
+
+# write.table(crispr_signif_del_lineage, file = "~/Desktop/crispr_signif_ptmuts_deleterious_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
+```
+
+```{r}
+crispr_signif_del_lineage <- readRDS("./data_munging/rds/crispr_signif_ptmuts_deleterious_lineage.rds")
 
@@
 wilcox_lineage_plot
-# ggsave(filename = "./plots_18Q3/crispr/pvals_genes.pdf", plot = wilcox_gene_plot, width = 8, height = 4, device = "pdf")
 ```
@@
 crispr_signif_nonsilent_lineage <- crispr_signif_nonsilent_lineage[order(crispr_signif_nonsilent_lineage$p),]
-saveRDS(crispr_signif_nonsilent_lineage, "./data_munging/rds/crispr_signif_nonsilent_lineage.rds")
-
-# write.table(crispr_signif_nonsilent_lineage, file = "~/Desktop/crispr_signif_nonsilent_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
-```
-
-```{r}
-crispr_signif_nonsilent_lineage <- readRDS("./data_munging/rds/crispr_signif_nonsilent_lineage.rds")
+saveRDS(crispr_signif_nonsilent_lineage, "./data_munging/rds/crispr_signif_ptmuts_nonsilent_lineage.rds")
+
+# write.table(crispr_signif_nonsilent_lineage, file = "~/Desktop/crispr_signif_ptmuts_nonsilent_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
+```
+
+```{r}
+crispr_signif_nonsilent_lineage <- readRDS("./data_munging/rds/crispr_signif_ptmuts_nonsilent_lineage.rds")
 
@@
 ```{r, eval=FALSE}
-crispr_signif_delmis_lineage <- compare_means(Score ~ Mutation_Status_DeleteriousMissense, group.by = c("Hugo_Symbol", "group_general_lineage_name"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
+crispr_signif_delmis_lineage <- compare_means(Score ~ Mutation_Status_DeleteriousMissense, group.by = c("Hugo_Symbol", "group_general_lineage_name"), data = crispr_data_ptmuts, method = "wilcox.test", p.adjust.method = "BH")
 crispr_signif_delmis_lineage <- adj_signif(crispr_signif_delmis_lineage)
 crispr_signif_delmis_lineage <- crispr_signif_delmis_lineage[order(crispr_signif_delmis_lineage$p),]
-saveRDS(crispr_signif_delmis_lineage, "./data_munging/rds/crispr_signif_deleteriousmissense_lineage.rds")
-
-# write.table(crispr_signif_delmis_lineage, file = "~/Desktop/crispr_signif_deleteriousmissense_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
-```
-
-```{r}
-crispr_signif_delmis_lineage <- readRDS("./data_munging/rds/crispr_signif_deleteriousmissense_lineage.rds")
+saveRDS(crispr_signif_delmis_lineage, "./data_munging/rds/crispr_signif_ptmuts_deleteriousmissense_lineage.rds")
+
+# write.table(crispr_signif_delmis_lineage, file = "~/Desktop/crispr_signif_ptmuts_deleteriousmissense_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
+```
+
+```{r}
+crispr_signif_delmis_lineage <- readRDS("./data_munging/rds/crispr_signif_ptmuts_deleteriousmissense_lineage.rds")
 
@@
 wilcox_gene_delmis_lineage_plot
-```
-
-## Grouped by gene and tissue {.tabset .tabset-fade .tabset-pills}
-
-### Deleterious vs. Other
-
-```{r, eval=FALSE}
-crispr_signif_del_tissue <- compare_means(Score ~ Mutation_Status_Deleterious, group.by = c("Hugo_Symbol", "primary_tissue"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
-crispr_signif_del_tissue <- adj_signif(crispr_signif_del_tissue)
-crispr_signif_del_tissue <- crispr_signif_del_tissue[order(crispr_signif_del_tissue$p),]
-saveRDS(crispr_signif_del_tissue, "./data_munging/rds/crispr_signif_deleterious_tissue.rds")
-
-# write.table(crispr_signif_del_tissue, file = "~/Desktop/crispr_signif_deleterious_tissue.csv", quote = FALSE, sep = ",", row.names = FALSE)
-```
-
-```{r}
-crispr_signif_del_tissue <- readRDS("./data_munging/rds/crispr_signif_deleterious_tissue.rds")
-
-knitr::kable(filter(crispr_signif_del_tissue, p < 0.05)[, c("Hugo_Symbol", "primary_tissue", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious mutant and other cell lines by tissue, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
-```
-
-```{r fig.height=4, fig.width=8}
-wilcox_tissue_plot <- ggplot(data = crispr_signif_del_tissue) +
-  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
-  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
-  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
-  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
-  labs(x = "BH-adjusted p-values", y = "Frequency")
-wilcox_tissue_plot
-# ggsave(filename = "./plots_18Q3/crispr/pvals_genes_tissues.pdf", plot = wilcox_tissue_plot, width = 8, height = 4, device = "pdf")
-```
-
-### Non-silent mutant vs. Other
-
-```{r, eval=FALSE}
-crispr_signif_nonsilent_tissue <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "primary_tissue"), data = crispr_data_ptmuts, method = "wilcox.test", p.adjust.method = "BH")
-crispr_signif_nonsilent_tissue <- adj_signif(crispr_signif_nonsilent_tissue)
-crispr_signif_nonsilent_tissue <- crispr_signif_nonsilent_tissue[order(crispr_signif_nonsilent_tissue$p),]
-saveRDS(crispr_signif_nonsilent_tissue, "./data_munging/rds/crispr_signif_nonsilent_tissue.rds")
-
-# write.table(crispr_signif_nonsilent_tissue, file = "~/Desktop/crispr_signif_nonsilent_tissue.csv", quote = FALSE, sep = ",", row.names = FALSE)
-```
-
-```{r}
-crispr_signif_nonsilent_tissue <- readRDS("./data_munging/rds/crispr_signif_nonsilent_tissue.rds")
-
-knitr::kable(filter(crispr_signif_nonsilent_tissue, p < 0.05)[, c("Hugo_Symbol", "primary_tissue", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant and other cell lines by tissue, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
-```
-
-```{r fig.height=4, fig.width=8}
-wilcox_tissue_nonsilent_plot <- ggplot(data = crispr_signif_nonsilent_tissue) +
-  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
-  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
-  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
-  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
-  labs(x = "BH-adjusted p-values", y = "Frequency")
-wilcox_tissue_nonsilent_plot
-```
-
-### Deleterious and missense mutant vs. Other
-
-```{r, eval=FALSE}
-crispr_signif_delmis_tissue <- compare_means(Score ~ Mutation_Status_DeleteriousMissense, group.by = c("Hugo_Symbol", "primary_tissue"), data = crispr_data_ptmuts, method = "wilcox.test", p.adjust.method = "BH")
-crispr_signif_delmis_tissue <- adj_signif(crispr_signif_delmis_tissue)
-crispr_signif_delmis_tissue <- crispr_signif_delmis_tissue[order(crispr_signif_delmis_tissue$p),]
-saveRDS(crispr_signif_delmis_tissue, "./data_munging/rds/crispr_signif_deleteriousmissense_tissue.rds")
-
-# write.table(crispr_signif_delmis_tissue, file = "~/Desktop/crispr_signif_deleteriousmissense_tissue.csv", quote = FALSE, sep = ",", row.names = FALSE)
-```
-
-```{r}
-crispr_signif_delmis_tissue <- readRDS("./data_munging/rds/crispr_signif_deleteriousmissense_tissue.rds")
-
-knitr::kable(filter(crispr_signif_delmis_tissue, p < 0.05)[, c("Hugo_Symbol", "primary_tissue", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious and missense mutant and other cell lines by tissue, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
-```
-
-```{r fig.height=4, fig.width=8}
-wilcox_gene_delmis_tissue_plot <- ggplot(data = crispr_signif_delmis_tissue) +
-  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
-  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
-  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
-  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
-  labs(x = "BH-adjusted p-values", y = "Frequency")
-wilcox_gene_delmis_tissue_plot
 ```

### 2018-09-17 lineages_18Q3.Rmd
updated rmd

@@
 
-# Wilcoxon tests: Point mutations {.tabset .tabset-fade .tabset-pills}
+# Wilcoxon tests: Point mutations
 
@@
 ```{r}
-crispr_data_ptmuts <- filter(crispr_data, Var_Length == 1)
+crispr_data_ptmuts <- filter(crispr_data, Var_Length == 1 | is.na(Var_Length))
 test_ptmuts <- filter(crispr_data_ptmuts, is.na(group_general_lineage_name))
@@
 wilcox_lineage_allmut_delmis_plot
+```
+
+# Boxplots for paper outline
+
+--------------------------------------------------------------------------------
+
+```{r fig.height=5, fig.width=12}
+genes_lvlA <- c("EGFR", "KRAS", "BRAF", "NRAS", "ERBB2", "MET", "ALK", "AKT1", "PDGFRA", "RET")
+crispr_ptmuts_lvlA <- filter(crispr_data_ptmuts, Hugo_Symbol %in% genes_lvlA)
+crispr_ptmuts_lvlA$Hugo_Symbol <- ordered(crispr_ptmuts_lvlA$Hugo_Symbol, levels = genes_lvlA)
+crispr_ptmuts_lvlA_color <- as.character(crispr_ptmuts_lvlA$Color_DeleteriousMissense)
+names(crispr_ptmuts_lvlA_color) <- crispr_ptmuts_lvlA$Mutation_Status_DeleteriousMissense
+
+crispr_ptmuts_lvlA_plot <- ggplot(data = crispr_ptmuts_lvlA, aes(x = Hugo_Symbol, y = Score)) +
+  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
+  geom_violin(mapping = aes(fill = Mutation_Status_DeleteriousMissense), alpha = 0.7, position = position_dodge(0.85)) +
+  geom_boxplot(mapping = aes(color = Mutation_Status_DeleteriousMissense), position = position_dodge(0.85), width = 0.1) +
+  scale_fill_manual(values = crispr_ptmuts_lvlA_color) +
+  scale_color_manual(values = c("black", "black")) +
+  guides(color = FALSE) +
+  theme(legend.direction = "horizontal", legend.justification = c(1, 0), legend.position = c(1, 0), legend.box.margin = margin(c(10, 10, 10, 10))) +
+  labs(fill = "Mutation Status", y = "CERES Score", x = "Gene")
+crispr_ptmuts_lvlA_plot
+# ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_plot.png", crispr_ptmuts_lvlA_plot, width = 12, height = 5, units = "in")
 ```

### 2018-09-17 lineages_18Q3.Rmd
started work on Fig 1D

@@
 
-knitr::kable(filter(crispr_signif_del, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious mutant and other cell lines, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(filter(crispr_signif_del, p < 0.01)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious mutant vs other cell lines, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
-knitr::kable(filter(crispr_signif_nonsilent, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant and other cell lines, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(filter(crispr_signif_nonsilent, p < 0.01)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant vs other cell lines, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 ```{r}
-compare_means(Score ~ Mutation_Status_DeleteriousMissense, group.by = c("Hugo_Symbol"), data = crispr_data_ptmuts[which(crispr_data_ptmuts$Hugo_Symbol == "KRAS"),], method = "wilcox.test", p.adjust.method = "BH")
-```
-
-```{r}
 crispr_signif_delmis <- readRDS("./data_munging/rds/crispr_signif_ptmuts_deleteriousmissense_gene.rds")
 
-knitr::kable(filter(crispr_signif_delmis, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious and missense mutant and other cell lines, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(filter(crispr_signif_delmis, p < 0.01)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious and missense mutant vs other cell lines, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
-knitr::kable(filter(crispr_signif_del_lineage, p < 0.05)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious mutant and other cell lines by lineage, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(filter(crispr_signif_del_lineage, p < 0.01)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious mutant vs other cell lines by lineage, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
-knitr::kable(filter(crispr_signif_nonsilent_lineage, p < 0.05)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant and other cell lines by lineage, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(filter(crispr_signif_nonsilent_lineage, p < 0.01)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant vs other cell lines by lineage, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
-knitr::kable(filter(crispr_signif_delmis_lineage, p < 0.05)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious and missense mutant and other cell lines by lineage, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(filter(crispr_signif_delmis_lineage, p < 0.01)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious and missense mutant vs other cell lines by lineage, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
-knitr::kable(filter(crispr_signif_allmut_del, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious mutant and other cell lines, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(filter(crispr_signif_allmut_del, p < 0.01)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious mutant vs other cell lines, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
-knitr::kable(filter(crispr_signif_allmut_nonsilent, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant and other cell lines, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(filter(crispr_signif_allmut_nonsilent, p < 0.01)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant vs other cell lines, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
-knitr::kable(filter(crispr_signif_allmut_delmis, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious and missense mutant and other cell lines, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(filter(crispr_signif_allmut_delmis, p < 0.01)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious and missense mutant vs other cell lines, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
-knitr::kable(filter(crispr_signif_allmut_del_lineage, p < 0.05)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious mutant and other cell lines by lineage, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(filter(crispr_signif_allmut_del_lineage, p < 0.01)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious mutant vs other cell lines by lineage, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
-knitr::kable(filter(crispr_signif_allmut_nonsilent_lineage, p < 0.05)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant and other cell lines by lineage, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(filter(crispr_signif_allmut_nonsilent_lineage, p < 0.01)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant vs other cell lines by lineage, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
-knitr::kable(filter(crispr_signif_allmut_delmis_lineage, p < 0.05)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious and missense mutant and other cell lines, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(filter(crispr_signif_allmut_delmis_lineage, p < 0.01)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious vs missense mutant and other cell lines, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
-# Boxplots for paper outline
+# Paper outline
 
 --------------------------------------------------------------------------------
+
+## Figure 1C
+
+Mutation status boxplots for genes identified in G2P.
 
@@
 # ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_plot.png", crispr_ptmuts_lvlA_plot, width = 12, height = 5, units = "in")
+```
+
+## Figure 1D
+
+Match specific point mutations.
+
+```{r}
+g2p_indications <- filter(read.delim("./data_munging/data_mutation_associations_appended.csv", sep = "\t", row.names = 1, header = TRUE), Evidence.Level == "A")
+
+maf_g2p_indications <- filter(maf_raw, Genome_Change %in% g2p_indications$MutationName)
+
+test <- merge(maf_g2p_indications, crispr_data, by = c("Hugo_Symbol", "Broad_ID"))
 ```
@@
 
-knitr::kable(filter(shrna_signif, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "shRNA Screen: Wilcoxon Test Results Comparing Mutant and Other Cell Lines, p < 0.1  (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(filter(shrna_signif, p < 0.01)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "shRNA Screen: Wilcoxon Test Results Comparing Mutant and Other Cell Lines, p < 0.1  (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```

### 2018-09-18 lineages_18Q3.Rmd

@@
 maf_raw <- filter(maf_raw, Broad_ID %in% unique(crispr_meta$Broad_ID))
+colnames(maf_raw)[colnames(maf_raw) == "Tumor_Sample_Barcode"] <- "CCLE_Name"
 
 # Select columns
-maf_df <- subset(maf_raw, select = c("Hugo_Symbol", "Tumor_Sample_Barcode", "Broad_ID", "Variant_Classification", "isDeleterious", "Reference_Allele"))
-colnames(maf_df)[colnames(maf_df) == "Tumor_Sample_Barcode"] <- "CCLE_Name"
+maf_df <- subset(maf_raw, select = c("Hugo_Symbol", "CCLE_Name", "Broad_ID", "Variant_Classification", "isDeleterious", "Reference_Allele"))
 maf_df$Var_Length <- nchar(as.character(maf_df$Reference_Allele))
@@
 
-```{r}
+```{r, eval=FALSE}
 max(nchar(as.character(maf_raw$Reference_Allele)))
@@
 
-```{r}
+```{r, eval=FALSE}
 dep <- read.delim("./data_munging/gene_dependency_18Q3.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
@@
 crispr_ptmuts_lvlA_plot
-# ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_plot.png", crispr_ptmuts_lvlA_plot, width = 12, height = 5, units = "in")
+# ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_plot.png", crispr_ptmuts_lvlA_plot, device = "png", width = 12, height = 5, units = "in")
+
+crispr_ptmuts_lvlA_plot_faceted <- ggplot(data = crispr_ptmuts_lvlA, aes(x = Mutation_Status_DeleteriousMissense, y = Score)) +
+  facet_wrap(~ Hugo_Symbol, ncol = length(unique(crispr_ptmuts_lvlA$Hugo_Symbol))) +
+  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
+  geom_violin(mapping = aes(fill = Mutation_Status_DeleteriousMissense), alpha = 0.7, position = position_dodge(0.85)) +
+  geom_boxplot(mapping = aes(color = Mutation_Status_DeleteriousMissense), position = position_dodge(0.85), width = 0.1) +
+  scale_fill_manual(values = crispr_ptmuts_lvlA_color) +
+  scale_color_manual(values = c("black", "black")) +
+  guides(color = FALSE) +
+  theme(legend.direction = "horizontal", legend.justification = c(0.5, 0), legend.position = c(0.5, 0), legend.box.margin = margin(c(10, 10, 10, 10)), axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
+  labs(fill = "Mutation Status", y = "CERES Score", x = "Mutation Status")
+crispr_ptmuts_lvlA_plot_faceted
+# ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_plot_faceted.png", crispr_ptmuts_lvlA_plot_faceted, device = "png", width = 12, height = 5, units = "in")
 ```
@@
 
-```{r}
+```{r fig.height=5, fig.width=12}
 g2p_indications <- filter(read.delim("./data_munging/data_mutation_associations_appended.csv", sep = "\t", row.names = 1, header = TRUE), Evidence.Level == "A")
-
 maf_g2p_indications <- filter(maf_raw, Genome_Change %in% g2p_indications$MutationName)
-
-test <- merge(maf_g2p_indications, crispr_data, by = c("Hugo_Symbol", "Broad_ID"))
+crispr_g2p_indications <- merge(maf_g2p_indications, crispr_data_ptmuts, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"))
+dup_g2p_indications <- filter(crispr_g2p_indications[, c("Hugo_Symbol", "CCLE_Name", "Broad_ID")] %>% group_by(Hugo_Symbol, CCLE_Name, Broad_ID) %>% tally(), n > 1)
+crispr_g2p_indications <- merge(crispr_g2p_indications, dup_g2p_indications, by = c("Hugo_Symbol", "Broad_ID"), all.x = TRUE)
+crispr_g2p_indications <- filter(crispr_g2p_indications, is.na(n))
+
+crispr_g2p_indications_plot <- ggplot(crispr_g2p_indications, aes(x = Hugo_Symbol, y = Score)) +
+  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
+  geom_boxplot(alpha = 0.5, color = "lightgray", outlier.shape = NA) +
+  geom_jitter(width = 0.3, mapping = aes(color = group_general_lineage_name), size = 1) +
+  theme_light() +
+  theme(legend.title = element_blank()) +
+  labs(x = "Gene", y = "CERES Score")
+crispr_g2p_indications_plot
+
+# ggsave("./plots_18Q3/manuscript/crispr_g2p_indications_plot_test.png", crispr_g2p_indications_plot, width = 12, height = 5, units = "in")
 ```

### 2018-10-01 lineages_18Q3.Rmd
added g2p and SO files from Dan, new plots/analyses

@@
 library(circlize)
+library(jsonlite)
 ```
@@
 
-```{r}
+```{r, eval=FALSE}
 crispr_signif_del <- readRDS("./data_munging/rds/crispr_signif_ptmuts_deleterious_gene.rds")
@@
 
-```{r}
+```{r, eval=TRUE}
 crispr_signif_nonsilent <- readRDS("./data_munging/rds/crispr_signif_ptmuts_nonsilent_gene.rds")
@@
 
-```{r}
+```{r, eval=FALSE}
 crispr_signif_delmis <- readRDS("./data_munging/rds/crispr_signif_ptmuts_deleteriousmissense_gene.rds")
@@
 
-```{r}
+```{r, eval=FALSE}
 crispr_signif_del_lineage <- readRDS("./data_munging/rds/crispr_signif_ptmuts_deleterious_lineage.rds")
@@
 
-```{r}
+```{r, eval=FALSE}
 crispr_signif_nonsilent_lineage <- readRDS("./data_munging/rds/crispr_signif_ptmuts_nonsilent_lineage.rds")
@@
 
-```{r}
+```{r, eval=FALSE}
 crispr_signif_delmis_lineage <- readRDS("./data_munging/rds/crispr_signif_ptmuts_deleteriousmissense_lineage.rds")
@@
 
-```{r}
+```{r, eval=FALSE}
 crispr_signif_allmut_del <- readRDS("./data_munging/rds/crispr_signif_allmut_deleterious_gene.rds")
@@
 
-```{r}
+```{r, eval=FALSE}
 crispr_signif_allmut_nonsilent <- readRDS("./data_munging/rds/crispr_signif_allmut_nonsilent_gene.rds")
@@
 
-```{r}
+```{r, eval=FALSE}
 crispr_signif_allmut_delmis <- readRDS("./data_munging/rds/crispr_signif_allmut_deleteriousmissense_gene.rds")
@@
 
-```{r}
+```{r, eval=FALSE}
 crispr_signif_allmut_del_lineage <- readRDS("./data_munging/rds/crispr_signif_allmut_deleterious_lineage.rds")
@@
 
-```{r}
+```{r, eval=FALSE}
 crispr_signif_allmut_nonsilent_lineage <- readRDS("./data_munging/rds/crispr_signif_allmut_nonsilent_lineage.rds")
@@
 
-```{r}
+```{r, eval=FALSE}
 crispr_signif_allmut_delmis_lineage <- readRDS("./data_munging/rds/crispr_signif_allmut_deleteriousmissens_lineage.rds")
@@
 
-```{r fig.height=5, fig.width=12}
-genes_lvlA <- c("EGFR", "KRAS", "BRAF", "NRAS", "ERBB2", "MET", "ALK", "AKT1", "PDGFRA", "RET")
+```{r fig.height=5, fig.width=20}
+genes_lvlA <- c("ABL1", "ALK", "AR", "ATM", "BRAF", "BRCA1", "BRCA2", "CDKN2A", "DNMT3A", "DPYD", "EGFR", "ERBB2", "ERBB3", "FGFR2", "FLT3", "JAK2", "KIT", "KRAS", "MET", "NOTCH1", "NOTCH2", "NRAS", "PDGFRA", "PDGFRB", "PIK3CA", "PML", "PTCH1", "RET", "ROS1", "SF3B1", "SMO", "TP53", "TSC1")
 crispr_ptmuts_lvlA <- filter(crispr_data_ptmuts, Hugo_Symbol %in% genes_lvlA)
 crispr_ptmuts_lvlA$Hugo_Symbol <- ordered(crispr_ptmuts_lvlA$Hugo_Symbol, levels = genes_lvlA)
-crispr_ptmuts_lvlA_color <- as.character(crispr_ptmuts_lvlA$Color_DeleteriousMissense)
-names(crispr_ptmuts_lvlA_color) <- crispr_ptmuts_lvlA$Mutation_Status_DeleteriousMissense
+crispr_ptmuts_lvlA_color <- as.character(crispr_ptmuts_lvlA$Color_Nonsilent)
+names(crispr_ptmuts_lvlA_color) <- crispr_ptmuts_lvlA$Mutation_Status_Nonsilent
 
@@
   geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
-  geom_violin(mapping = aes(fill = Mutation_Status_DeleteriousMissense), alpha = 0.7, position = position_dodge(0.85)) +
-  geom_boxplot(mapping = aes(color = Mutation_Status_DeleteriousMissense), position = position_dodge(0.85), width = 0.1) +
+  geom_boxplot(mapping = aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85)) +
   scale_fill_manual(values = crispr_ptmuts_lvlA_color) +
-  scale_color_manual(values = c("black", "black")) +
   guides(color = FALSE) +
-  theme(legend.direction = "horizontal", legend.justification = c(1, 0), legend.position = c(1, 0), legend.box.margin = margin(c(10, 10, 10, 10))) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.direction = "horizontal", legend.justification = c(0.5, 0), legend.position = c(0.092, 0.8), legend.box.margin = margin(c(10, 10, 10, 10))) +
   labs(fill = "Mutation Status", y = "CERES Score", x = "Gene")
 crispr_ptmuts_lvlA_plot
-# ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_plot.png", crispr_ptmuts_lvlA_plot, device = "png", width = 12, height = 5, units = "in")
-
-crispr_ptmuts_lvlA_plot_faceted <- ggplot(data = crispr_ptmuts_lvlA, aes(x = Mutation_Status_DeleteriousMissense, y = Score)) +
+ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_plot.png", crispr_ptmuts_lvlA_plot, device = "png", width = 20, height = 5, units = "in")
+
+crispr_ptmuts_lvlA_plot_faceted <- ggplot(data = crispr_ptmuts_lvlA, aes(x = Mutation_Status_Nonsilent, y = Score)) +
   facet_wrap(~ Hugo_Symbol, ncol = length(unique(crispr_ptmuts_lvlA$Hugo_Symbol))) +
   geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
-  geom_violin(mapping = aes(fill = Mutation_Status_DeleteriousMissense), alpha = 0.7, position = position_dodge(0.85)) +
-  geom_boxplot(mapping = aes(color = Mutation_Status_DeleteriousMissense), position = position_dodge(0.85), width = 0.1) +
+  geom_boxplot(mapping = aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85)) +
   scale_fill_manual(values = crispr_ptmuts_lvlA_color) +
-  scale_color_manual(values = c("black", "black")) +
   guides(color = FALSE) +
-  theme(legend.direction = "horizontal", legend.justification = c(0.5, 0), legend.position = c(0.5, 0), legend.box.margin = margin(c(10, 10, 10, 10)), axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
+  theme(legend.direction = "horizontal", legend.justification = c(0.5, 0), legend.position = c(0.092, 0.8), legend.box.margin = margin(c(10, 10, 10, 10)), axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
   labs(fill = "Mutation Status", y = "CERES Score", x = "Mutation Status")
 crispr_ptmuts_lvlA_plot_faceted
-# ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_plot_faceted.png", crispr_ptmuts_lvlA_plot_faceted, device = "png", width = 12, height = 5, units = "in")
+ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_plot_faceted.png", crispr_ptmuts_lvlA_plot_faceted, device = "png", width = 20, height = 5, units = "in")
+
+# label_text <- crispr_signif_nonsilent$p.signif.adj
+# names(label_text) <- crispr_signif_nonsilent$Hugo_Symbol
+# label_text <- label_text[genes_lvlA]
+# 
+# crispr_ptmuts_lvlA_plot_faceted_truncated <- ggplot(data = crispr_ptmuts_lvlA, aes(x = Mutation_Status_Nonsilent, y = Score, fill = Mutation_Status_Nonsilent)) +
+#   facet_wrap(~ Hugo_Symbol, ncol = length(unique(crispr_ptmuts_lvlA$Hugo_Symbol))) +
+#   geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
+#   coord_cartesian(ylim = c(-2, 2)) +
+#   geom_boxplot(position = position_dodge(0.85)) +
+#   scale_fill_manual(values = crispr_ptmuts_lvlA_color) +
+#   geom_text(data = label_text, mapping = aes(label = p.signif.adj)) +
+#   guides(color = FALSE) +
+#   theme(legend.direction = "horizontal", legend.justification = c(0.5, 0), legend.position = c(0.092, 0.8), legend.box.margin = margin(c(10, 10, 10, 10)), axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
+#   labs(fill = "Mutation Status", y = "CERES Score", x = "Mutation Status")
+# crispr_ptmuts_lvlA_plot_faceted_truncated
+# ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_plot_faceted_truncated.png", crispr_ptmuts_lvlA_plot_faceted_truncated, device = "png", width = 20, height = 5, units = "in")
 ```
@@
 ```{r fig.height=5, fig.width=12}
-g2p_indications <- filter(read.delim("./data_munging/data_mutation_associations_appended.csv", sep = "\t", row.names = 1, header = TRUE), Evidence.Level == "A")
+g2p_indications <- filter(read.delim("./data_munging/data_mutation_associations_appended.csv", sep = "\t", header = TRUE), Evidence.Level == "A")
 maf_g2p_indications <- filter(maf_raw, Genome_Change %in% g2p_indications$MutationName)
@@
 # ggsave("./plots_18Q3/manuscript/crispr_g2p_indications_plot_test.png", crispr_g2p_indications_plot, width = 12, height = 5, units = "in")
+```
+
+### JSON
+
+```{r}
+g2p <- read.delim("./data_munging/g2p_full_level_A_dataset.tsv", sep = "\t", header = TRUE, encoding="UTF-8")
+test <- as.character(g2p$JSON[1])
+test2 <- fromJSON(test)
 ```

### 2018-10-02 lineages_18Q3.Rmd
update fig 1c plots

@@
 
-```{r fig.height=4, fig.width=8}
+```{r fig.height=4, fig.width=8, eval=FALSE}
 wilcox_gene_plot <- ggplot(data = crispr_signif_del) +
@@
 
-```{r fig.height=4, fig.width=8}
+```{r fig.height=4, fig.width=8, eval=FALSE}
 wilcox_gene_delmis_plot <- ggplot(data = crispr_signif_delmis) +
@@
 
-```{r fig.height=4, fig.width=8}
+```{r fig.height=4, fig.width=8, eval=FALSE}
 wilcox_lineage_plot <- ggplot(data = crispr_signif_del_lineage) +
@@
 
-```{r fig.height=4, fig.width=8}
+```{r fig.height=4, fig.width=8, eval=FALSE}
 wilcox_lineage_nonsilent_plot <- ggplot(data = crispr_signif_nonsilent_lineage) +
@@
 
-```{r fig.height=4, fig.width=8}
+```{r fig.height=4, fig.width=8, eval=FALSE}
 wilcox_gene_delmis_lineage_plot <- ggplot(data = crispr_signif_delmis_lineage) +
@@
 
-```{r fig.height=4, fig.width=8}
+```{r fig.height=4, fig.width=8, eval=FALSE}
 wilcox_gene_allmut_plot <- ggplot(data = crispr_signif_allmut_del) +
@@
 
-```{r fig.height=4, fig.width=8}
+```{r fig.height=4, fig.width=8, eval=FALSE}
 wilcox_gene_allmut_nonsilent_plot <- ggplot(data = crispr_signif_allmut_nonsilent) +
@@
 
-```{r fig.height=4, fig.width=8}
+```{r fig.height=4, fig.width=8, eval=FALSE}
 wilcox_gene_allmut_delmis_plot <- ggplot(data = crispr_signif_allmut_delmis) +
@@
 
-```{r fig.height=4, fig.width=8}
+```{r fig.height=4, fig.width=8, eval=FALSE}
 wilcox_lineage_allmut_plot <- ggplot(data = crispr_signif_allmut_del_lineage) +
@@
 
-```{r fig.height=4, fig.width=8}
+```{r fig.height=4, fig.width=8, eval=FALSE}
 wilcox_lineage_allmut_nonsilent_plot <- ggplot(data = crispr_signif_allmut_nonsilent_lineage) +
@@
 
-```{r fig.height=4, fig.width=8}
+```{r fig.height=4, fig.width=8, eval=FALSE}
 wilcox_lineage_allmut_delmis_plot <- ggplot(data = crispr_signif_allmut_delmis_lineage) +
@@
 
+label_text <- data.frame(p.signif.adj = crispr_signif_nonsilent$p.signif.adj, Hugo_Symbol = crispr_signif_nonsilent$Hugo_Symbol)
+label_text <- filter(label_text, Hugo_Symbol %in% genes_lvlA)
+label_text$Hugo_Symbol <- factor(label_text$Hugo_Symbol, levels = genes_lvlA)
+
 crispr_ptmuts_lvlA_plot <- ggplot(data = crispr_ptmuts_lvlA, aes(x = Hugo_Symbol, y = Score)) +
@@
 crispr_ptmuts_lvlA_plot
-ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_plot.png", crispr_ptmuts_lvlA_plot, device = "png", width = 20, height = 5, units = "in")
+# ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_plot.png", crispr_ptmuts_lvlA_plot, device = "png", width = 20, height = 5, units = "in")
 
@@
   guides(color = FALSE) +
-  theme(legend.direction = "horizontal", legend.justification = c(0.5, 0), legend.position = c(0.092, 0.8), legend.box.margin = margin(c(10, 10, 10, 10)), axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
+  geom_text(data = label_text, mapping = aes(x = 1.5, y = 4.5, label = p.signif.adj)) +
+  theme(legend.direction = "horizontal", legend.justification = c(0.5, 0), legend.position = c(0.25, 0.8), legend.box.margin = margin(c(10, 10, 10, 10)), axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
   labs(fill = "Mutation Status", y = "CERES Score", x = "Mutation Status")
 crispr_ptmuts_lvlA_plot_faceted
-ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_plot_faceted.png", crispr_ptmuts_lvlA_plot_faceted, device = "png", width = 20, height = 5, units = "in")
-
-# label_text <- crispr_signif_nonsilent$p.signif.adj
-# names(label_text) <- crispr_signif_nonsilent$Hugo_Symbol
-# label_text <- label_text[genes_lvlA]
-# 
-# crispr_ptmuts_lvlA_plot_faceted_truncated <- ggplot(data = crispr_ptmuts_lvlA, aes(x = Mutation_Status_Nonsilent, y = Score, fill = Mutation_Status_Nonsilent)) +
-#   facet_wrap(~ Hugo_Symbol, ncol = length(unique(crispr_ptmuts_lvlA$Hugo_Symbol))) +
-#   geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
-#   coord_cartesian(ylim = c(-2, 2)) +
-#   geom_boxplot(position = position_dodge(0.85)) +
-#   scale_fill_manual(values = crispr_ptmuts_lvlA_color) +
-#   geom_text(data = label_text, mapping = aes(label = p.signif.adj)) +
-#   guides(color = FALSE) +
-#   theme(legend.direction = "horizontal", legend.justification = c(0.5, 0), legend.position = c(0.092, 0.8), legend.box.margin = margin(c(10, 10, 10, 10)), axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
-#   labs(fill = "Mutation Status", y = "CERES Score", x = "Mutation Status")
-# crispr_ptmuts_lvlA_plot_faceted_truncated
+# ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_plot_faceted.png", crispr_ptmuts_lvlA_plot_faceted, device = "png", width = 20, height = 5, units = "in")
+
+crispr_ptmuts_lvlA_plot_faceted_truncated <- ggplot(data = crispr_ptmuts_lvlA, aes(x = Mutation_Status_Nonsilent, y = Score)) +
+  facet_wrap(~ Hugo_Symbol, ncol = length(unique(crispr_ptmuts_lvlA$Hugo_Symbol))) +
+  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
+  coord_cartesian(ylim = c(-2, 2)) +
+  geom_boxplot(aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85)) +
+  scale_fill_manual(values = crispr_ptmuts_lvlA_color) +
+  geom_text(data = label_text, mapping = aes(x = 1.5, y = 2, label = p.signif.adj)) +
+  guides(color = FALSE) +
+  theme(legend.direction = "horizontal", legend.justification = c(0.5, 0), legend.position = c(0.5, 0), legend.box.margin = margin(c(10, 10, 10, 10)), axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
+  labs(fill = "Mutation Status", y = "CERES Score", x = "Mutation Status")
+crispr_ptmuts_lvlA_plot_faceted_truncated
 # ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_plot_faceted_truncated.png", crispr_ptmuts_lvlA_plot_faceted_truncated, device = "png", width = 20, height = 5, units = "in")
@@
 
-```{r}
-g2p <- read.delim("./data_munging/g2p_full_level_A_dataset.tsv", sep = "\t", header = TRUE, encoding="UTF-8")
+```{r, eval=FALSE}
+g2p <- read.delim("./data_munging/g2p_full_level_A_dataset.tsv", sep = "\t", header = TRUE)
 test <- as.character(g2p$JSON[1])

### 2018-10-02 lineages_18Q3.Rmd

@@
 library(ggsignif)
+library(ggfortify)
+library(ggord)
 library(rowr)
@@
 colnames(crispr) <- gsub(" .*", "", colnames(crispr))
+```
+
+```{r fig.height=12, fig.width=12}
+crispr_pca_data <- merge(ccl_converter[, c("Broad_ID", "group_general_lineage_name")], crispr, by = "Broad_ID")
+crispr_lin <- crispr_pca_data[, 2]
+crispr_pca <- prcomp(data.matrix(crispr_pca_data[, 3:ncol(crispr_pca_data)]), scale. = TRUE, center = TRUE)
+plot(crispr_pca, type = "l")
+# autoplot(crispr_pca, data = crispr_pca_data, color = "group_general_lineage_name")
+summary(crispr_pca)
+biplot(crispr_pca, obs.scale = 1, var.scale = 1, groups = crispr_lin, ellipse = TRUE, circle = TRUE, )
+ggord(crispr_pca, crispr_pca_data$group_general_lineage_name)
 ```

### 2018-10-03 lineages_18Q3.Rmd

--- 2018-10-02 lineages_18Q3.Rmd
@@
 num_cores <- parallel::detectCores()
-options(mc.cores = num_cores)
+options(mc.cores = num_cores, expressions = 5e5)
 ```
@@
 library(circlize)
-library(jsonlite)
 ```
@@
 
+```{r fig.height=12, fig.width=12}
+crispr_pca_data <- merge(ccl_converter[, c("Broad_ID", "group_general_lineage_name")], crispr, by = "Broad_ID")
+crispr_lin <- crispr_pca_data[, 2]
+crispr_pca <- prcomp(data.matrix(crispr_pca_data[, 3:ncol(crispr_pca_data)]), scale. = TRUE, center = TRUE)
+plot(crispr_pca, type = "l")
+biplot(crispr_pca, obs.scale = 1, var.scale = 1, groups = crispr_lin, ellipse = TRUE, circle = TRUE, )
+ggord(crispr_pca, crispr_pca_data$group_general_lineage_name)
+```
+
 Merge annotation data:
@@
 
-# Paper outline
+# Paper outline: G2P data
 
@@
 
-## Figure 1C
+```{r}
+g2p <- read.delim("./data_munging/g2p_full_level_A_dataset.tsv", sep = "\t", header = TRUE)
+genes_lvlA <- unique(g2p$Gene)
+```
+
+## Gene mutation frequency
+
+```{r}
+crispr_data_lvlA <- filter(crispr_data_ptmuts, Hugo_Symbol %in% genes_lvlA)
+
+crispr_data_lvlA_summ <- unique(crispr_data_lvlA[, c("Hugo_Symbol", "N_Nonsilent_Mutant", "N_Nonsilent_Other")])
+crispr_data_lvlA_summ$Fraction_Mutant <- crispr_data_lvlA_summ$N_Nonsilent_Mutant / (crispr_data_lvlA_summ$N_Nonsilent_Mutant + crispr_data_lvlA_summ$N_Nonsilent_Other)
+crispr_data_lvlA_summ$Percent_Mutant <- crispr_data_lvlA_summ$Fraction_Mutant * 100
+# write.table(crispr_data_lvlA_summ, file = "~/Desktop/crispr_data_lvlA_summ_20181003.tsv", quote = FALSE, sep = "\t")
+```
+
+## Wilcoxon tests
+
+### Gene
+```{r, eval=FALSE}
+crispr_signif_lvlA <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol"), data = crispr_data_lvlA, method = "wilcox.test", p.adjust.method = "BH")
+crispr_signif_lvlA <- adj_signif(crispr_signif_lvlA)
+crispr_signif_lvlA <- crispr_signif_lvlA[order(crispr_signif_lvlA$p),]
+saveRDS(crispr_signif_lvlA, "./data_munging/rds/crispr_signif_lvlA_gene.rds")
+```
+
+```{r, eval=TRUE}
+crispr_signif_lvlA <- readRDS("./data_munging/rds/crispr_signif_lvlA_gene.rds")
+
+crispr_signif_genes_lvlA <- as.character(filter(crispr_signif_lvlA, !is.na(p.signif.adj))$Hugo_Symbol)
+
+knitr::kable(filter(crispr_signif_lvlA, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results for Level A point mutations, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+```{r fig.height=4, fig.width=8}
+wilcox_gene_lvlA_plot <- ggplot(data = crispr_signif_lvlA) +
+  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
+  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
+  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
+  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
+  labs(x = "BH-adjusted p-values", y = "Frequency")
+wilcox_gene_lvlA_plot
+```
+
+### Gene and lineage
+
+```{r, eval=FALSE}
+crispr_signif_lvlA_lineage <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "group_general_lineage_name"), data = crispr_data_lvlA, method = "wilcox.test", p.adjust.method = "BH")
+crispr_signif_lvlA_lineage <- adj_signif(crispr_signif_lvlA_lineage)
+crispr_signif_lvlA_lineage <- crispr_signif_lvlA_lineage[order(crispr_signif_lvlA_lineage$p),]
+saveRDS(crispr_signif_lvlA_lineage, "./data_munging/rds/crispr_signif_lvlA_lineage.rds")
+
+# write.table(crispr_signif_lvlA_lineage, file = "~/Desktop/crispr_signif_lvlA_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
+```
+
+```{r, eval=FALSE}
+crispr_signif_lvlA_lineage <- readRDS("./data_munging/rds/crispr_signif_lvlA_lineage.rds")
+
+knitr::kable(filter(crispr_signif_lvlA_lineage, p < 0.01)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant vs other cell lines by lineage, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+```{r fig.height=4, fig.width=8, eval=FALSE}
+wilcox_lineage_lvlA_plot <- ggplot(data = crispr_signif_lvlA_lineage) +
+  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
+  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
+  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
+  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
+  labs(x = "BH-adjusted p-values", y = "Frequency")
+wilcox_lineage_lvlA_plot
+```
+
+## Figure 1C plots
 
@@
 ```{r fig.height=5, fig.width=20}
-genes_lvlA <- c("ABL1", "ALK", "AR", "ATM", "BRAF", "BRCA1", "BRCA2", "CDKN2A", "DNMT3A", "DPYD", "EGFR", "ERBB2", "ERBB3", "FGFR2", "FLT3", "JAK2", "KIT", "KRAS", "MET", "NOTCH1", "NOTCH2", "NRAS", "PDGFRA", "PDGFRB", "PIK3CA", "PML", "PTCH1", "RET", "ROS1", "SF3B1", "SMO", "TP53", "TSC1")
-crispr_ptmuts_lvlA <- filter(crispr_data_ptmuts, Hugo_Symbol %in% genes_lvlA)
-crispr_ptmuts_lvlA$Hugo_Symbol <- ordered(crispr_ptmuts_lvlA$Hugo_Symbol, levels = genes_lvlA)
-crispr_ptmuts_lvlA_color <- as.character(crispr_ptmuts_lvlA$Color_Nonsilent)
-names(crispr_ptmuts_lvlA_color) <- crispr_ptmuts_lvlA$Mutation_Status_Nonsilent
-
-label_text <- data.frame(p.signif.adj = crispr_signif_nonsilent$p.signif.adj, Hugo_Symbol = crispr_signif_nonsilent$Hugo_Symbol)
-label_text <- filter(label_text, Hugo_Symbol %in% genes_lvlA)
-label_text$Hugo_Symbol <- factor(label_text$Hugo_Symbol, levels = genes_lvlA)
-
-crispr_ptmuts_lvlA_plot <- ggplot(data = crispr_ptmuts_lvlA, aes(x = Hugo_Symbol, y = Score)) +
+genes_lvlA_filt <- c("ABL1", "ALK", "AR", "ATM", "BRAF", "BRCA1", "BRCA2", "CDKN2A", "DNMT3A", "DPYD", "EGFR", "ERBB2", "ERBB3", "FGFR2", "FLT3", "JAK2", "KIT", "KRAS", "MET", "NOTCH1", "NOTCH2", "NRAS", "PDGFRA", "PDGFRB", "PIK3CA", "PML", "PTCH1", "RET", "ROS1", "SF3B1", "SMO", "TP53", "TSC1")
+crispr_ptmuts_lvlA_filt <- filter(crispr_data_ptmuts, Hugo_Symbol %in% genes_lvlA_filt)
+crispr_ptmuts_lvlA_filt$Hugo_Symbol <- ordered(crispr_ptmuts_lvlA_filt$Hugo_Symbol, levels = genes_lvlA_filt)
+crispr_ptmuts_lvlA_filt_color <- as.character(crispr_ptmuts_lvlA_filt$Color_Nonsilent)
+names(crispr_ptmuts_lvlA_filt_color) <- crispr_ptmuts_lvlA_filt$Mutation_Status_Nonsilent
+
+label_text <- data.frame(p.signif.adj = crispr_signif_lvlA$p.signif.adj, Hugo_Symbol = crispr_signif_lvlA$Hugo_Symbol)
+label_text <- filter(label_text, Hugo_Symbol %in% genes_lvlA_filt)
+label_text$Hugo_Symbol <- factor(label_text$Hugo_Symbol, levels = genes_lvlA_filt)
+
+crispr_ptmuts_lvlA_filt_plot <- ggplot(data = crispr_ptmuts_lvlA_filt, aes(x = Hugo_Symbol, y = Score)) +
   geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
   geom_boxplot(mapping = aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85)) +
-  scale_fill_manual(values = crispr_ptmuts_lvlA_color) +
+  scale_fill_manual(values = crispr_ptmuts_lvlA_filt_color) +
   guides(color = FALSE) +
@@
   labs(fill = "Mutation Status", y = "CERES Score", x = "Gene")
-crispr_ptmuts_lvlA_plot
-# ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_plot.png", crispr_ptmuts_lvlA_plot, device = "png", width = 20, height = 5, units = "in")
-
-crispr_ptmuts_lvlA_plot_faceted <- ggplot(data = crispr_ptmuts_lvlA, aes(x = Mutation_Status_Nonsilent, y = Score)) +
-  facet_wrap(~ Hugo_Symbol, ncol = length(unique(crispr_ptmuts_lvlA$Hugo_Symbol))) +
+crispr_ptmuts_lvlA_filt_plot
+# ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_filt_plot.png", crispr_ptmuts_lvlA_filt_plot, device = "png", width = 20, height = 5, units = "in")
+
+crispr_ptmuts_lvlA_filt_plot_faceted <- ggplot(data = crispr_ptmuts_lvlA_filt, aes(x = Mutation_Status_Nonsilent, y = Score)) +
+  facet_wrap(~ Hugo_Symbol, ncol = length(unique(crispr_ptmuts_lvlA_filt$Hugo_Symbol))) +
   geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
   geom_boxplot(mapping = aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85)) +
-  scale_fill_manual(values = crispr_ptmuts_lvlA_color) +
+  scale_fill_manual(values = crispr_ptmuts_lvlA_filt_color) +
   guides(color = FALSE) +
@@
   labs(fill = "Mutation Status", y = "CERES Score", x = "Mutation Status")
-crispr_ptmuts_lvlA_plot_faceted
-# ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_plot_faceted.png", crispr_ptmuts_lvlA_plot_faceted, device = "png", width = 20, height = 5, units = "in")
-
-crispr_ptmuts_lvlA_plot_faceted_truncated <- ggplot(data = crispr_ptmuts_lvlA, aes(x = Mutation_Status_Nonsilent, y = Score)) +
-  facet_wrap(~ Hugo_Symbol, ncol = length(unique(crispr_ptmuts_lvlA$Hugo_Symbol))) +
+crispr_ptmuts_lvlA_filt_plot_faceted
+# ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_filt_plot_faceted.png", crispr_ptmuts_lvlA_filt_plot_faceted, device = "png", width = 20, height = 5, units = "in")
+
+crispr_ptmuts_lvlA_filt_plot_faceted_truncated <- ggplot(data = crispr_ptmuts_lvlA_filt, aes(x = Mutation_Status_Nonsilent, y = Score)) +
+  facet_wrap(~ Hugo_Symbol, ncol = length(unique(crispr_ptmuts_lvlA_filt$Hugo_Symbol))) +
   geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
@@
   geom_boxplot(aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85)) +
-  scale_fill_manual(values = crispr_ptmuts_lvlA_color) +
+  scale_fill_manual(values = crispr_ptmuts_lvlA_filt_color) +
   geom_text(data = label_text, mapping = aes(x = 1.5, y = 2, label = p.signif.adj)) +
@@
   labs(fill = "Mutation Status", y = "CERES Score", x = "Mutation Status")
-crispr_ptmuts_lvlA_plot_faceted_truncated
-# ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_plot_faceted_truncated.png", crispr_ptmuts_lvlA_plot_faceted_truncated, device = "png", width = 20, height = 5, units = "in")
-```
-
-## Figure 1D
+crispr_ptmuts_lvlA_filt_plot_faceted_truncated
+# ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_filt_plot_faceted_truncated.png", crispr_ptmuts_lvlA_filt_plot_faceted_truncated, device = "png", width = 20, height = 5, units = "in")
+```
+
+```{r fig.height=5, fig.width=12}
+lvlA_genes_signif <- filter(crispr_data_ptmuts, Hugo_Symbol %in% crispr_signif_genes_lvlA)
+lvlA_genes_signif <- merge(lvlA_genes_signif, crispr_signif_lvlA, by = "Hugo_Symbol")
+lvlA_genes_signif$Hugo_Symbol <- ordered(lvlA_genes_signif$Hugo_Symbol, levels = crispr_signif_genes_lvlA)
+lvlA_genes_signif_color <- as.character(lvlA_genes_signif$Color_Nonsilent)
+names(lvlA_genes_signif_color) <- lvlA_genes_signif$Mutation_Status_Nonsilent
+lvlA_genes_signif <- merge(lvlA_genes_signif, lvlA_genes_signif %>% group_by(Hugo_Symbol) %>% summarize(Text_y = max(Score)), by = "Hugo_Symbol")
+
+lvlA_genes_text <- unique(data.frame(p.signif.adj = lvlA_genes_signif$p.signif.adj, Hugo_Symbol = lvlA_genes_signif$Hugo_Symbol, Text_y = lvlA_genes_signif$Text_y))
+lvlA_genes_text$Hugo_Symbol <- factor(lvlA_genes_text$Hugo_Symbol, levels = crispr_signif_genes_lvlA)
+
+lvlA_signif_genes_plot <- ggplot(data = lvlA_genes_signif, aes(x = Mutation_Status_Nonsilent, y = Score)) +
+  facet_wrap(~ Hugo_Symbol, nrow = 1, scales = "free_y") +
+  geom_jitter(aes(color = Mutation_Status_Nonsilent), alpha = 0.5, width = 0.3) +
+  geom_boxplot(color = "black", fill = NA, outlier.shape = NA) +
+  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
+  scale_color_manual(values = lvlA_signif_color) + 
+  geom_text(data = lvlA_genes_text, mapping = aes(x = 1.5, y = Text_y, label = p.signif.adj), nudge_y = 0.2) +
+  theme(legend.position = "top", axis.text.x = element_text(angle = 65, hjust = 1, vjust = 1, size = 10)) +
+  labs(y = "CERES Score",
+       x = "Lineage",
+       color = "Mutation Status",
+       title = "CERES scores for significant Level A G2P genes",
+       subtitle = "BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001\nGenes are sorted by increasing p-value.")
+lvlA_signif_genes_plot
+
+# ggsave("./plots_18Q3/manuscript/crispr_g2p_lvlA_signif_genes_plot.png", lvlA_signif_genes_plot, width = 12, height = 5, units = "in")
+```
+
+## Figure 1D plots
 
@@
 
-### JSON
-
-```{r, eval=FALSE}
-g2p <- read.delim("./data_munging/g2p_full_level_A_dataset.tsv", sep = "\t", header = TRUE)
-test <- as.character(g2p$JSON[1])
-test2 <- fromJSON(test)
+## Lineages
+
+```{r fig.height=15, fig.width=12}
+lvlA_signif <- filter(crispr_data_ptmuts, Hugo_Symbol %in% crispr_signif_genes_lvlA)
+lvlA_signif <- merge(lvlA_signif, crispr_signif_lvlA_lineage, by = c("Hugo_Symbol", "group_general_lineage_name"))
+lvlA_signif$Hugo_Symbol <- ordered(lvlA_signif$Hugo_Symbol, levels = crispr_signif_genes_lvlA)
+lvlA_signif_color <- as.character(lvlA_signif$Color_Nonsilent)
+names(lvlA_signif_color) <- lvlA_signif$Mutation_Status_Nonsilent
+lvlA_signif <- merge(lvlA_signif, lvlA_signif %>% group_by(Hugo_Symbol) %>% summarize(Text_y = max(Score)), by = "Hugo_Symbol")
+
+lvlA_text <- unique(data.frame(p.signif.adj = lvlA_signif$p.signif.adj, group_general_lineage_name = lvlA_signif$group_general_lineage_name, Hugo_Symbol = lvlA_signif$Hugo_Symbol, Text_y = lvlA_signif$Text_y))
+lvlA_text$Hugo_Symbol <- factor(lvlA_text$Hugo_Symbol, levels = crispr_signif_genes_lvlA)
+
+lvlA_signif_lineages_plot <- ggplot(data = lvlA_signif, aes(x = group_general_lineage_name, y = Score)) +
+  facet_wrap(~ Hugo_Symbol, nrow = 4, scales = "free_y") +
+  geom_point(aes(color = Mutation_Status_Nonsilent), alpha = 0.5) +
+  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
+  scale_color_manual(values = lvlA_signif_color) +
+  geom_text(data = lvlA_text, mapping = aes(x = group_general_lineage_name, y = Text_y, label = p.signif.adj), nudge_y = 0.1) +
+  theme(legend.position = "top", axis.text.x = element_text(angle = 65, hjust = 1, vjust = 1, size = 10)) +
+  labs(y = "CERES Score",
+       x = "Lineage",
+       color = "Mutation Status",
+       title = "CERES score by cell line lineage for significant Level A G2P genes",
+       subtitle = "BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001\nGenes are sorted by increasing lineage-agnostic p-value.")
+lvlA_signif_lineages_plot
+
+# ggsave("./plots_18Q3/manuscript/crispr_g2p_lvlA_signif_lineages_plot.png", lvlA_signif_lineages_plot, width = 12, height = 15, units = "in")
 ```

### 2018-10-04 lineages_18Q3.Rmd

@@
 
-```{r, eval=FALSE}
+```{r, eval=TRUE}
 crispr_signif_lvlA_lineage <- readRDS("./data_munging/rds/crispr_signif_lvlA_lineage.rds")
@@
 
-```{r fig.height=5, fig.width=20}
+```{r fig.height=4, fig.width=20}
 genes_lvlA_filt <- c("ABL1", "ALK", "AR", "ATM", "BRAF", "BRCA1", "BRCA2", "CDKN2A", "DNMT3A", "DPYD", "EGFR", "ERBB2", "ERBB3", "FGFR2", "FLT3", "JAK2", "KIT", "KRAS", "MET", "NOTCH1", "NOTCH2", "NRAS", "PDGFRA", "PDGFRB", "PIK3CA", "PML", "PTCH1", "RET", "ROS1", "SF3B1", "SMO", "TP53", "TSC1")
@@
 crispr_ptmuts_lvlA_filt_plot_faceted <- ggplot(data = crispr_ptmuts_lvlA_filt, aes(x = Mutation_Status_Nonsilent, y = Score)) +
-  facet_wrap(~ Hugo_Symbol, ncol = length(unique(crispr_ptmuts_lvlA_filt$Hugo_Symbol))) +
+  facet_wrap(~ Hugo_Symbol, drop = FALSE, ncol = length(unique(genes_lvlA_filt))) +
   geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
@@
 crispr_ptmuts_lvlA_filt_plot_faceted
-# ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_filt_plot_faceted.png", crispr_ptmuts_lvlA_filt_plot_faceted, device = "png", width = 20, height = 5, units = "in")
+# ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_filt_plot_faceted.png", crispr_ptmuts_lvlA_filt_plot_faceted, device = "png", width = 20, height = 4, units = "in")
 
 crispr_ptmuts_lvlA_filt_plot_faceted_truncated <- ggplot(data = crispr_ptmuts_lvlA_filt, aes(x = Mutation_Status_Nonsilent, y = Score)) +
-  facet_wrap(~ Hugo_Symbol, ncol = length(unique(crispr_ptmuts_lvlA_filt$Hugo_Symbol))) +
+  facet_wrap(~ Hugo_Symbol, drop = FALSE, ncol = length(unique(genes_lvlA_filt))) +
   geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
@@
 crispr_ptmuts_lvlA_filt_plot_faceted_truncated
-# ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_filt_plot_faceted_truncated.png", crispr_ptmuts_lvlA_filt_plot_faceted_truncated, device = "png", width = 20, height = 5, units = "in")
+# ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_filt_plot_faceted_truncated.png", crispr_ptmuts_lvlA_filt_plot_faceted_truncated, device = "png", width = 20, height = 4, units = "in")
 ```
@@
   geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
-  scale_color_manual(values = lvlA_signif_color) + 
+  scale_color_manual(values = lvlA_genes_signif_color) + 
   geom_text(data = lvlA_genes_text, mapping = aes(x = 1.5, y = Text_y, label = p.signif.adj), nudge_y = 0.2) +

### 2018-10-05 lineages_18Q3.Rmd
updated manuscript figures

@@
 ```{r, eval=FALSE}
-cn <- read.delim("./data_munging/public_18Q3_gene_cn.csv.gz", sep = ",", check.names = FALSE, header = TRUE)
+cn <- read.delim("./data_munging/public_18Q3_gene_cn_v2.csv.gz", sep = ",", check.names = FALSE, header = TRUE)
 
@@
 plot(crispr_pca, type = "l")
-biplot(crispr_pca, obs.scale = 1, var.scale = 1, groups = crispr_lin, ellipse = TRUE, circle = TRUE, )
+biplot(crispr_pca, obs.scale = 1, var.scale = 1, groups = crispr_lin, ellipse = TRUE, circle = TRUE)
 ggord(crispr_pca, crispr_pca_data$group_general_lineage_name)
@@
 # Gene expression (RPKM)
-ge_filt <- filter(ge_melt, Hugo_Symbol %in% unique(crispr_data$Hugo_Symbol))
+ge_filt <- filter(ge_melt, Hugo_Symbol %in% unique(crispr_data$Hugo_Symbol) & Broad_ID %in% unique(crispr_data$Broad_ID))
 crispr_data <- merge(crispr_data, ge_filt, by = c("Hugo_Symbol", "Broad_ID", "CCLE_Name"), all.x = TRUE)
@@
   geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
-  coord_cartesian(ylim = c(-2, 2)) +
+  coord_cartesian(ylim = c(-2.5, 2.5)) +
   geom_boxplot(aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85)) +
   scale_fill_manual(values = crispr_ptmuts_lvlA_filt_color) +
-  geom_text(data = label_text, mapping = aes(x = 1.5, y = 2, label = p.signif.adj)) +
+  geom_text(data = label_text, mapping = aes(x = 1.5, y = 2.5, label = p.signif.adj)) +
   guides(color = FALSE) +
@@
 # ggsave("./plots_18Q3/manuscript/crispr_g2p_lvlA_signif_lineages_plot.png", lvlA_signif_lineages_plot, width = 12, height = 15, units = "in")
+```
+
+```{r}
+lvlA_signif_summ <- lvlA_signif %>% group_by(Hugo_Symbol, group_general_lineage_name, Mutation_Status_Nonsilent) %>% tally()
+
+# write.table(lvlA_signif_summ, file = "~/Desktop/lvlA_signif_summ_20181005.tsv", quote = FALSE, sep = "\t")
 ```

### 2018-10-08 lineages_18Q3.Rmd
updated Fig 1C plots

@@
   geom_boxplot(mapping = aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85)) +
+  coord_cartesian(ylim = c(-3, 5)) +
   scale_fill_manual(values = crispr_ptmuts_lvlA_filt_color) +
   guides(color = FALSE) +
-  geom_text(data = label_text, mapping = aes(x = 1.5, y = 4.5, label = p.signif.adj)) +
-  theme(legend.direction = "horizontal", legend.justification = c(0.5, 0), legend.position = c(0.25, 0.8), legend.box.margin = margin(c(10, 10, 10, 10)), axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
+  geom_text(data = label_text, mapping = aes(x = 1.5, y = 5, label = p.signif.adj)) +
+  theme(legend.direction = "horizontal", legend.justification = c(0.5, 0), legend.position = c(0.5, 0), legend.box.margin = margin(c(10, 10, 10, 10)), axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
   labs(fill = "Mutation Status", y = "CERES Score", x = "Mutation Status")

### 2018-10-08 lineages_18Q3.Rmd

--- 2018-10-05 lineages_18Q3.Rmd
@@
 ```{r}
-library(NMF)
+library(broom)
+library(bsselectR)
+library(caret)
+library(CePa)
+library(circlize)
+library(ComplexHeatmap)
+library(data.table)
+library(devtools)
 library(ggpubr)
@@
 library(ggord)
-library(rowr)
-library(data.table)
-library(CePa)
-library(plyr)
-library(tidyverse)
+library(glmnet)
+library(gridExtra)
+# devtools::install_github("jeroen/jsonlite")
+# install.packages("jsonlite")
+library(jsonlite)
+library(jsonlite)
+library(kableExtra)
 library(magrittr)
 library(matrixStats)
+library(NMF)
 library(parallel)
-library(kableExtra)
-library(gridExtra)
-library(broom)
-library(glmnet)
-library(devtools)
+library(plyr)
 library(reshape2)
-library(caret)
-library(bsselectR)
-library(ComplexHeatmap)
-library(circlize)
+library(rowr)
+library(tidyverse)
 ```
@@
 crispr_ptmuts_lvlA_filt_plot
-# ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_filt_plot.png", crispr_ptmuts_lvlA_filt_plot, device = "png", width = 20, height = 5, units = "in")
+# ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_filt_plot.png", crispr_ptmuts_lvlA_filt_plot, device = "png", width = 20, height = 6, units = "in")
 
@@
   geom_boxplot(mapping = aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85)) +
+  coord_cartesian(ylim = c(-3, 5)) +
   scale_fill_manual(values = crispr_ptmuts_lvlA_filt_color) +
   guides(color = FALSE) +
-  geom_text(data = label_text, mapping = aes(x = 1.5, y = 4.5, label = p.signif.adj)) +
-  theme(legend.direction = "horizontal", legend.justification = c(0.5, 0), legend.position = c(0.25, 0.8), legend.box.margin = margin(c(10, 10, 10, 10)), axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
+  geom_text(data = label_text, mapping = aes(x = 1.5, y = 5, label = p.signif.adj)) +
+  theme(legend.direction = "horizontal", legend.justification = c(0.5, 0), legend.position = c(0.5, 0), legend.box.margin = margin(c(10, 10, 10, 10)), axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
   labs(fill = "Mutation Status", y = "CERES Score", x = "Mutation Status")
 crispr_ptmuts_lvlA_filt_plot_faceted
-# ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_filt_plot_faceted.png", crispr_ptmuts_lvlA_filt_plot_faceted, device = "png", width = 20, height = 4, units = "in")
+# ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_filt_plot_faceted.png", crispr_ptmuts_lvlA_filt_plot_faceted, device = "png", width = 20, height = 5, units = "in")
 
@@
 crispr_ptmuts_lvlA_filt_plot_faceted_truncated
-# ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_filt_plot_faceted_truncated.png", crispr_ptmuts_lvlA_filt_plot_faceted_truncated, device = "png", width = 20, height = 4, units = "in")
+# ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_filt_plot_faceted_truncated.png", crispr_ptmuts_lvlA_filt_plot_faceted_truncated, device = "png", width = 20, height = 5, units = "in")
 ```
@@
 
-```{r fig.height=5, fig.width=12}
+```{r fig.height=5, fig.width=20}
 g2p_indications <- filter(read.delim("./data_munging/data_mutation_associations_appended.csv", sep = "\t", header = TRUE), Evidence.Level == "A")
@@
 
+crispr_g2p_indications_muts_plot <- ggplot(crispr_g2p_indications, aes(x = Protein_Change, y = Score)) +
+  facet_grid(~ Hugo_Symbol, scales = "free_x", space = "free") +
+  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
+  geom_boxplot(alpha = 0.5, color = "lightgray", outlier.shape = NA) +
+  geom_jitter(width = 0.1, mapping = aes(color = group_general_lineage_name), size = 1) +
+  theme_light() +
+  theme(legend.title = element_blank(), axis.text.x = element_text(angle = 90, hjust = 1)) +
+  labs(x = "Gene", y = "CERES Score")
+crispr_g2p_indications_muts_plot
+
 # ggsave("./plots_18Q3/manuscript/crispr_g2p_indications_plot_test.png", crispr_g2p_indications_plot, width = 12, height = 5, units = "in")
+# ggsave("./plots_18Q3/manuscript/crispr_g2p_indications_muts_plot_test.png", crispr_g2p_indications_muts_plot, width = 20, height = 5, units = "in")
+```
+
+```{r}
+g2pA <- read.delim("./data_munging/g2p_full_level_A_dataset_v2_20181008.tsv", sep = "\t", header = TRUE, na.strings = "-1", quote = "")
+# g2pA[g2pA == "-1"] <- NA
+
+g2pA$JSON[1]
+fromJSON(as.character(g2pA$JSON[[1]]))
+```
+
+```{r}
+test <- '{"feature_names": "ALK positive", "tags": "test", "genes": "ALK"}'
+
+fromJSON(test)
+```
+
+```
+{
+'feature_names': 'ALK positive',
+'jax': '{\"responseType\": \"sensitive\", 
+        \"efficacyEvidence\": \"Zykadia (ceritinib) is FDA approved for the treatment of ALK-positive metastatic non-small cell lung cancer (NSCLC) in patients previously treated with crizotinib (FDA.gov).\",
+        \"molecularProfile\": {\"profileName\": \"ALK positive\",
+                               \"id\": 1772},
+        \"evidenceType\": \"Actionable\",
+        \"indication\": {\"source\": \"DOID\",
+                         \"id\": 3908,
+                         \"name\": \"non-small cell lung carcinoma\"},
+        \"references\": [{\"url\": \"http://www.fda.gov/\",
+                          \"id\": 286,
+                          \"pubMedId\": null,
+                          \"title\": \"FDA.gov\"}],
+        \"approvalStatus\": \"FDA approved\",
+        \"therapy\": {\"id\": 789,
+                      \"therapyName\": \"Ceritinib\"},
+        \"id\": 1481}',
+'tags': [],
+'genes': ['ALK'],
+'source_url': 'https://ckb.jax.org/therapy/show/789',
+'source': 'jax',
+'dev_tags': [],
+'gene_identifiers': [{'symbol': 'ALK',
+                      'entrez_id': '238',
+                      'ensembl_gene_id': 'ENSG00000171094'}],
+'association': {'drug_labels': 'CERITINIB',
+                'description': 'Zykadia (ceritinib) is FDA approved for the treatment of ALK-positive metastatic non-small cell lung cancer (NSCLC) in patients previously treated with crizotinib (FDA.gov).',
+                'publication_url': 'http://www.fda.gov/',
+                'source_link': 'https://ckb.jax.org/molecularProfile/show/1772',
+                'variant_name': [''],
+                'phenotypes': [{'source': 'http://purl.obolibrary.org/obo/DOID_3908',
+                                'term': 'non-small cell lung carcinoma',
+                                'description': 'non-small cell lung carcinoma',
+                                'family': 'lung cancer',
+                                'id': 'DOID:3908'}],
+                'evidence': [{'info': {'publications': ['http://www.fda.gov/']},
+                              'evidenceType': {'sourceName': 'jax'},
+                              'description': 'sensitive'}],
+                              'environmentalContexts': [{'term': 'CERITINIB',
+                                                          'description': 'CERITINIB',
+                                                          'taxonomy': {'kingdom': 'Chemical entities',
+                                                                       'direct-parent': 'Phenylpiperidines',
+                                                                       'class': 'Organoheterocyclic compounds',
+                                                                       'subclass': 'Piperidines',
+                                                                       'superclass': 'Organic compounds'},
+                                                          'source': 'http://rdf.ncbi.nlm.nih.gov/pubchem/compound',
+                                                          'usan_stem': 'tyrosine kinase inhibitors',
+                                                          'toxicity': 'There is not currently any data on carcinogenicity, effect on human fertility, or on early embryonic development.
+However, based on its mechanism of action, ceritinib may cause fetal harm when administered to pregnant women and should therefore be administered with effective contraception during treatment.
+Diarrhea, nausea, vomiting, or abdominal pain occurred in 96% of 255 patients including severe cases in 14% of patients.
+Drug-induced hepatotoxicity also occurred in 27% of 255 patients, presenting as alanine aminotransferase (ALT) levels greater than 5 times the upper limit of normal (ULN).
+Severe, life-threatening, or fatal interstitial lung disease (ILD)/pneumonitis, hyperglycaemia, and bradycardia have also been reported.',
+                                                          'approved_countries': ['Canada',
+                                                                                 'US'],
+                                                          'id': 'CID57379345'}],
+                'evidence_label': 'A',
+                'response_type': 'sensitive',
+                'evidence_level': 1},
+'features': [{'provenance_rule': 'default_feature',
+              'end': 29484957,
+              'description': 'ALK  positive',
+              'links': ['http://reg.genome.network/refseq/RS000050',
+                        'http://reg.genome.network/refseq/RS000026',
+                        'http://reg.genome.network/allele/CA425438613',
+                        'http://reg.genome.network/refseq/RS000002',
+                        'http://myvariant.info/v1/variant/chr2:g.29484957C>G?assembly=hg19',
+                        'http://reg.genome.network/refseq/RS001597'],
+              'sequence_ontology': {'hierarchy': ['SO:0000400',
+                                                  'SO:0000733',
+                                                  'SO:0000401',
+                                                  'SO:0000119',
+                                                  'SO:0000123',
+                                                  'SO:0000125'],
+                                    'soid': 'SO:0000475',
+                                    'root_name': 'sequence_attribute',
+                                    'name': 'positively_autoregulated',
+                                    'root_soid': 'SO:0000400'},
+              'provenance': ['http://myvariant.info/v1/query?q=ALK  positive',
+                             'http://reg.genome.network/allele?hgvs=NC_000002.11%3Ag.29484957C%3EG'], 
+              'start': 29484957,
+              'synonyms': ['NC_000002.11:g.29484957C>G',
+                           'NC_000002.10:g.29338461C>G',
+                           'LRG_488:g.664476G>C',
+                           'chr2:g.29484957C>G',
+                           'NG_009445.1:g.664476G>C',
+                           'NC_000002.12:g.29262091C>G',
+                           'CM000664.1:g.29484957C>G',
+                           'CM000664.2:g.29262091C>G'],
+              'biomarker_type': 'positive',
+              'referenceName': 'GRCh37',
+              'geneSymbol': 'ALK',
+              'alt': 'G',
+              'ref': 'C',
+              'chromosome': '2',
+              'name': 'ALK  positive'}]
+}
 ```
@@
 lvlA_signif_summ <- lvlA_signif %>% group_by(Hugo_Symbol, group_general_lineage_name, Mutation_Status_Nonsilent) %>% tally()
-
+lvlA_signif_summ
 # write.table(lvlA_signif_summ, file = "~/Desktop/lvlA_signif_summ_20181005.tsv", quote = FALSE, sep = "\t")

### 2018-10-09 lineages_18Q3.Rmd

@@
 # Select columns
-maf_df <- subset(maf_raw, select = c("Hugo_Symbol", "CCLE_Name", "Broad_ID", "Variant_Classification", "isDeleterious", "Reference_Allele"))
-maf_df$Var_Length <- nchar(as.character(maf_df$Reference_Allele))
+maf_df <- subset(maf_raw, select = c("Hugo_Symbol", "CCLE_Name", "Broad_ID", "Variant_Classification", "isDeleterious", "Reference_Allele", "Tumor_Seq_Allele1"))
+maf_df$Reference_Allele_Length <- ifelse(maf_df$Reference_Allele == "-", 0, nchar(as.character(maf_df$Reference_Allele)))
+maf_df$Tumor_Seq_Allele1_Length <- nchar(as.character(maf_df$Tumor_Seq_Allele1))
 
@@
 maf_df$Mutation_Status_DeleteriousMissense <- ifelse(maf_df$isDeleterious == TRUE | maf_df$Variant_Classification == "Missense_Mutation", "Mutant", "Other")
-maf_df <- unique(subset(maf_df, select = c("Hugo_Symbol", "CCLE_Name", "Broad_ID", "Mutation_Status_Deleterious", "Mutation_Status_Nonsilent", "Mutation_Status_DeleteriousMissense", "Var_Length")))
+maf_df <- unique(subset(maf_df, select = c("Hugo_Symbol", "CCLE_Name", "Broad_ID", "Mutation_Status_Deleterious", "Mutation_Status_Nonsilent", "Mutation_Status_DeleteriousMissense", "Reference_Allele_Length", "Tumor_Seq_Allele1_Length")))
 
@@
 ```{r}
-crispr_data_ptmuts <- filter(crispr_data, Var_Length == 1 | is.na(Var_Length))
+crispr_data_ptmuts <- filter(crispr_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
+
+crispr_data_ptmuts$Keep_PtMut_Tests <- ifelse(crispr_data_ptmuts$Reference_Allele_Length == 1 | is.na(crispr_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(crispr_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
+
+crispr_data_ptmuts <- filter(crispr_data_ptmuts, Keep_PtMut_Tests == TRUE)
+
 test_ptmuts <- filter(crispr_data_ptmuts, is.na(group_general_lineage_name))
@@
 
-g2pA$JSON[1]
-fromJSON(as.character(g2pA$JSON[[1]]))
+g2pA_JSON <- data.frame(JSON = g2pA$JSON)
 ```

### 2018-10-10 lineages_18Q3.Rmd
edit G2P level A datasets

@@
 ```{r}
-g2pA <- read.delim("./data_munging/g2p_full_level_A_dataset_v2_20181008.tsv", sep = "\t", header = TRUE, na.strings = "-1", quote = "")
+g2pA <- read.delim("./data_munging/g2p_full_level_A_dataset_v2_10_10_2018.csv", sep = "\t", header = TRUE, na.strings = "-1", quote = "")
 # g2pA[g2pA == "-1"] <- NA
+g2pA$X <- NULL
 
 g2pA_JSON <- data.frame(JSON = g2pA$JSON)
+
+g2pA_noJSON <- g2pA
+g2pA_noJSON$JSON <- NULL
+
+# write.table(g2pA, file = "./data_munging/g2p_full_level_A_dataset_v2_10_10_2018.tsv", quote = FALSE, sep = "\t", row.names = FALSE)
+# write.table(g2pA_noJSON, file = "./data_munging/g2pA_noJSON_v2_10_10_2018.tsv", quote = FALSE, sep = "\t", row.names = FALSE)
+# write.table(g2pA_JSON, file = "./data_munging/g2pA_JSON_v2_10_10_2018.tsv", quote = FALSE, sep = "\t", row.names = FALSE)
 ```

### 2018-10-12 lineages_18Q3.Rmd

@@
 
-## DepMap cell line metadata
-
-```{r}
-ccl_info <- read.delim("./data_munging/DepMap-2018q3-celllines.csv", sep = ",", header = TRUE, na.strings = c("", NA))
-ccl_info$Primary.Disease <- gsub("\\\\", "", ccl_info$Primary.Disease)
-ccl_info$Primary.Disease <- gsub("Ewings", "Ewing's", ccl_info$Primary.Disease)
-
-# From figshare
-crispr_meta <- read.delim("./data_munging/sample_info_18Q3_crispr.csv", sep = ",", header = TRUE, na.strings = c("", NA))
-colnames(crispr_meta)[7] <- "CCLE_Name"
-```
-
-```{r, include=FALSE}
-dan_test <- select(ccl_converter, CCLE_Name, Broad_ID, cell_line_name)
-dan_test <- dan_test[-which(dan_test$CCLE_Name == ""), ]
-ccl_test <- select(ccl_info, CCLE_Name, Broad_ID)
-
-test <- merge(ccl_test, dan_test, by = "CCLE_Name", all = TRUE, suffixes = c("_DepMap", "_Daniel"))
-test$BroadIDs_match <- ifelse(as.character(test$Broad_ID_DepMap) == as.character(test$Broad_ID_Daniel), TRUE, FALSE)
-
-test_false <- filter(test, BroadIDs_match == FALSE)
-# write.table(ccl_converter, file = "~/Desktop/cell_line_database_v1_20180907.tsv", quote = FALSE, sep = "\t")
-```
-
 ## CGC gene list
@@
 
-## CCLE MAF file
+## Genomic annotations
+
+### CCLE MAF file
 
@@
 # Add Mutation_Status column
-maf_df$Mutation_Status_Deleterious <- ifelse(maf_df$isDeleterious == TRUE, "Mutant", "Other")
 maf_df$Mutation_Status_Nonsilent <- ifelse(maf_df$Variant_Classification == "Silent", "Other", "Mutant")
-maf_df$Mutation_Status_DeleteriousMissense <- ifelse(maf_df$isDeleterious == TRUE | maf_df$Variant_Classification == "Missense_Mutation", "Mutant", "Other")
-maf_df <- unique(subset(maf_df, select = c("Hugo_Symbol", "CCLE_Name", "Broad_ID", "Mutation_Status_Deleterious", "Mutation_Status_Nonsilent", "Mutation_Status_DeleteriousMissense", "Reference_Allele_Length", "Tumor_Seq_Allele1_Length")))
+maf_df <- unique(subset(maf_df, select = c("Hugo_Symbol", "CCLE_Name", "Broad_ID", "Mutation_Status_Nonsilent", "Reference_Allele_Length", "Tumor_Seq_Allele1_Length")))
 
@@
 
-## CCLE copy number file
+### CCLE copy number file
 
@@
 
-## CCLE gene expression file
+### CCLE gene expression file
 
@@
 
-## DepMap dependency probabilities
+## CRISPR
+
+### DepMap dependency probabilities
 
@@
 
-## Merge CRISPR data and annotations
+### DepMap cell line metadata
+
+```{r}
+ccl_info <- read.delim("./data_munging/DepMap-2018q3-celllines.csv", sep = ",", header = TRUE, na.strings = c("", NA))
+ccl_info$Primary.Disease <- gsub("\\\\", "", ccl_info$Primary.Disease)
+ccl_info$Primary.Disease <- gsub("Ewings", "Ewing's", ccl_info$Primary.Disease)
+
+# From figshare
+crispr_meta <- read.delim("./data_munging/sample_info_18Q3_crispr.csv", sep = ",", header = TRUE, na.strings = c("", NA))
+colnames(crispr_meta)[7] <- "CCLE_Name"
+```
+
+```{r, include=FALSE}
+dan_test <- select(ccl_converter, CCLE_Name, Broad_ID, cell_line_name)
+dan_test <- dan_test[-which(dan_test$CCLE_Name == ""), ]
+ccl_test <- select(ccl_info, CCLE_Name, Broad_ID)
+
+test <- merge(ccl_test, dan_test, by = "CCLE_Name", all = TRUE, suffixes = c("_DepMap", "_Daniel"))
+test$BroadIDs_match <- ifelse(as.character(test$Broad_ID_DepMap) == as.character(test$Broad_ID_Daniel), TRUE, FALSE)
+
+test_false <- filter(test, BroadIDs_match == FALSE)
+# write.table(ccl_converter, file = "~/Desktop/cell_line_database_v1_20180907.tsv", quote = FALSE, sep = "\t")
+```
+
+### Merge CRISPR data and annotations
 
@@
 
-```{r fig.height=12, fig.width=12}
+```{r fig.height=12, fig.width=12, eval=FALSE}
 crispr_pca_data <- merge(ccl_converter[, c("Broad_ID", "group_general_lineage_name")], crispr, by = "Broad_ID")
@@
 crispr_muts$Hugo_Symbol <- factor(crispr_muts$Hugo_Symbol)
-crispr_muts <- crispr_muts %>% mutate(Mutation_Status_Deleterious = if_else(is.na(Mutation_Status_Deleterious), "Other", Mutation_Status_Deleterious), Mutation_Status_DeleteriousMissense = if_else(is.na(Mutation_Status_DeleteriousMissense), "Other", Mutation_Status_DeleteriousMissense), Mutation_Status_Nonsilent = if_else(is.na(Mutation_Status_Nonsilent), "Other", Mutation_Status_Nonsilent))
+crispr_muts <- crispr_muts %>% mutate(Mutation_Status_Nonsilent = if_else(is.na(Mutation_Status_Nonsilent), "Other", Mutation_Status_Nonsilent))
 
@@
 crispr_muts_summ <- crispr_muts %>% group_by(Hugo_Symbol) %>%
-  summarize(N_Deleterious_Other = sum(Mutation_Status_Deleterious == "Other"),
-            N_Deleterious_Mutant = sum(Mutation_Status_Deleterious == "Mutant"),
-            N_DeleteriousMissense_Other = sum(Mutation_Status_DeleteriousMissense == "Other"),
-            N_DeleteriousMissense_Mutant = sum(Mutation_Status_DeleteriousMissense == "Mutant"),
-            N_Nonsilent_Other = sum(Mutation_Status_Nonsilent == "Other"),
+  summarize(N_Nonsilent_Other = sum(Mutation_Status_Nonsilent == "Other"),
             N_Nonsilent_Mutant = sum(Mutation_Status_Nonsilent == "Mutant"))
@@
 # Add Color columns
-crispr_data$Color_Deleterious <- ifelse(crispr_data$Mutation_Status_Deleterious == "Other", "cyan3", "darkorchid")
-crispr_data$Color_Deleterious <- factor(crispr_data$Color_Deleterious)
-crispr_data$Color_DeleteriousMissense <- ifelse(crispr_data$Mutation_Status_DeleteriousMissense == "Other", "cyan3", "darkorchid")
-crispr_data$Color_DeleteriousMissense <- factor(crispr_data$Color_DeleteriousMissense)
-crispr_data$Color_Nonsilent <- ifelse(crispr_data$Mutation_Status_Nonsilent == "Other", "cyan3", "darkorchid")
+crispr_data$Color_Nonsilent <- ifelse(crispr_data$Mutation_Status_Nonsilent == "Other", "thistle", "darkorchid")
 crispr_data$Color_Nonsilent <- factor(crispr_data$Color_Nonsilent)
@@
 
-# Wilcoxon tests: Point mutations
+```{r, eval=FALSE, include=FALSE}
+# Code for testing colors on plots
+test <- filter(crispr_data, Hugo_Symbol == "KRAS")
+ggplot(data = test, aes(x = Mutation_Status_Nonsilent, y = Score, fill = Mutation_Status_Nonsilent)) +
+  geom_boxplot() +
+  geom_jitter(aes(color = Mutation_Status_Nonsilent)) +
+  theme_light() +
+  scale_color_manual(values = c("turquoise4", "paleturquoise3")) +
+  scale_fill_manual(values = c("turquoise4", "paleturquoise3"))
+```
+
+## Drug screens
+
+```{r, eval=FALSE}
+# Drug metadata
+drug_meta <- read.delim("./data_munging/drug_id_drug_name_table_10_12_2018.tsv", sep = "\t", header = FALSE)
+colnames(drug_meta) <- c("CID", "Drug")
+drug_meta$Drug <- tolower(drug_meta$Drug)
+
+# CCLE
+ccle <- read.delim("./data_munging/data_drug_auc_ccle_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
+ccle <- merge(drug_meta, ccle, by = "CID")
+ccle_melt <- melt(ccle, id.vars = c("CID", "Drug"), measure.vars = colnames(ccle)[3:ncol(ccle)], variable.name = "accession_id", value.name = "AUC_CCLE")
+
+# CTRP
+ctrp <- read.delim("./data_munging/data_drug_auc_ctrp_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
+ctrp <- merge(drug_meta, ctrp, by = "CID")
+ctrp_melt <- melt(ctrp, id.vars = c("CID", "Drug"), measure.vars = colnames(ctrp)[3:ncol(ctrp)], variable.name = "accession_id", value.name = "AUC_CTRP")
+
+# GDSC
+gdsc <- read.delim("./data_munging/data_drug_auc_gdsc_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
+gdsc <- merge(drug_meta, gdsc, by = "CID")
+gdsc_melt <- melt(gdsc, id.vars = c("CID", "Drug"), measure.vars = colnames(gdsc)[3:ncol(gdsc)], variable.name = "accession_id", value.name = "AUC_GDSC")
+
+# Merge all data
+drug_data <- merge(merge(ccle_melt, ctrp_melt, by = c("accession_id", "CID", "Drug"), all = TRUE), gdsc_melt, by = c("accession_id", "CID", "Drug"), all = TRUE)
+drug_data <- merge(drug_data, ccl_converter, by = "accession_id", all.x = TRUE)
+drug_data <- merge(drug_data, maf_df, by = c("CCLE_Name", "Broad_ID"))
+drug_data$Hugo_Symbol <- factor(drug_muts$Hugo_Symbol)
+
+saveRDS(drug_data, "./../crispr_lineages_giant_files/drug_data_18Q3.rds", compress = "xz")
+```
+
+```{r}
+crispr_data <- readRDS("./../crispr_lineages_giant_files/crispr_data_18Q3.rds")
+crispr_ccl <- data.frame("Broad_ID" = crispr_data$Broad_ID)
+# write.table(crispr_data, file = "~/Desktop/crispr_data.tsv", quote = FALSE, sep = "\t")
+```
+
+# Wilcoxon tests
 
 --------------------------------------------------------------------------------
+
+## CRISPR
 
@@
 
-## Grouped by gene  {.tabset .tabset-fade .tabset-pills}
-
-### Deleterious vs. Other
-
-```{r, eval=FALSE}
-crispr_signif_del <- compare_means(Score ~ Mutation_Status_Deleterious, group.by = c("Hugo_Symbol"), data = crispr_data_ptmuts, method = "wilcox.test", p.adjust.method = "BH")
-crispr_signif_del <- adj_signif(crispr_signif_del)
-crispr_signif_del <- crispr_signif_del[order(crispr_signif_del$p),]
-saveRDS(crispr_signif_del, "./data_munging/rds/crispr_signif_ptmuts_deleterious_gene.rds")
-
-# write.table(crispr_signif_del, file = "~/Desktop/crispr_signif_ptmuts_deleterious_gene.csv", quote = FALSE, sep = ",", row.names = FALSE)
-```
-
-```{r, eval=FALSE}
-crispr_signif_del <- readRDS("./data_munging/rds/crispr_signif_ptmuts_deleterious_gene.rds")
-
-knitr::kable(filter(crispr_signif_del, p < 0.01)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious mutant vs other cell lines, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-```{r fig.height=4, fig.width=8, eval=FALSE}
-wilcox_gene_plot <- ggplot(data = crispr_signif_del) +
-  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
-  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
-  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
-  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
-  labs(x = "BH-adjusted p-values", y = "Frequency")
-wilcox_gene_plot
-```
-
-### Non-silent mutant vs. Other
+### Grouped by gene
 
@@
 
-### Deleterious and missense mutant vs. Other
-
-```{r, eval=FALSE}
-crispr_signif_delmis <- compare_means(Score ~ Mutation_Status_DeleteriousMissense, group.by = c("Hugo_Symbol"), data = crispr_data_ptmuts, method = "wilcox.test", p.adjust.method = "BH")
-crispr_signif_delmis <- adj_signif(crispr_signif_delmis)
-crispr_signif_delmis <- crispr_signif_delmis[order(crispr_signif_delmis$p),]
-saveRDS(crispr_signif_delmis, "./data_munging/rds/crispr_signif_ptmuts_deleteriousmissense_gene.rds")
-
-# write.table(crispr_signif_delmis, file = "~/Desktop/crispr_signif_ptmuts_deleteriousmissense_gene.csv", quote = FALSE, sep = ",", row.names = FALSE)
-```
-
-```{r, eval=FALSE}
-crispr_signif_delmis <- readRDS("./data_munging/rds/crispr_signif_ptmuts_deleteriousmissense_gene.rds")
-
-knitr::kable(filter(crispr_signif_delmis, p < 0.01)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious and missense mutant vs other cell lines, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-```{r fig.height=4, fig.width=8, eval=FALSE}
-wilcox_gene_delmis_plot <- ggplot(data = crispr_signif_delmis) +
-  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
-  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
-  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
-  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
-  labs(x = "BH-adjusted p-values", y = "Frequency")
-wilcox_gene_delmis_plot
-```
-
-## Grouped by gene and lineage {.tabset .tabset-fade .tabset-pills}
-
-### Deleterious vs. Other
-
-```{r, eval=FALSE}
-crispr_signif_del_lineage <- compare_means(Score ~ Mutation_Status_Deleterious, group.by = c("Hugo_Symbol", "group_general_lineage_name"), data = crispr_data_ptmuts, method = "wilcox.test", p.adjust.method = "BH")
-crispr_signif_del_lineage <- adj_signif(crispr_signif_del_lineage)
-crispr_signif_del_lineage <- crispr_signif_del_lineage[order(crispr_signif_del_lineage$p),]
-saveRDS(crispr_signif_del_lineage, "./data_munging/rds/crispr_signif_ptmuts_deleterious_lineage.rds")
-
-# write.table(crispr_signif_del_lineage, file = "~/Desktop/crispr_signif_ptmuts_deleterious_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
-```
-
-```{r, eval=FALSE}
-crispr_signif_del_lineage <- readRDS("./data_munging/rds/crispr_signif_ptmuts_deleterious_lineage.rds")
-
-knitr::kable(filter(crispr_signif_del_lineage, p < 0.01)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious mutant vs other cell lines by lineage, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-```{r fig.height=4, fig.width=8, eval=FALSE}
-wilcox_lineage_plot <- ggplot(data = crispr_signif_del_lineage) +
-  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
-  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
-  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
-  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
-  labs(x = "BH-adjusted p-values", y = "Frequency")
-wilcox_lineage_plot
-```
-
-### Non-silent mutant vs. Other
+### Grouped by gene and lineage: Non-silent mutant vs. Other
 
@@
 
-### Deleterious and missense mutant vs. Other
-
-```{r, eval=FALSE}
-crispr_signif_delmis_lineage <- compare_means(Score ~ Mutation_Status_DeleteriousMissense, group.by = c("Hugo_Symbol", "group_general_lineage_name"), data = crispr_data_ptmuts, method = "wilcox.test", p.adjust.method = "BH")
-crispr_signif_delmis_lineage <- adj_signif(crispr_signif_delmis_lineage)
-crispr_signif_delmis_lineage <- crispr_signif_delmis_lineage[order(crispr_signif_delmis_lineage$p),]
-saveRDS(crispr_signif_delmis_lineage, "./data_munging/rds/crispr_signif_ptmuts_deleteriousmissense_lineage.rds")
-
-# write.table(crispr_signif_delmis_lineage, file = "~/Desktop/crispr_signif_ptmuts_deleteriousmissense_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
-```
-
-```{r, eval=FALSE}
-crispr_signif_delmis_lineage <- readRDS("./data_munging/rds/crispr_signif_ptmuts_deleteriousmissense_lineage.rds")
-
-knitr::kable(filter(crispr_signif_delmis_lineage, p < 0.01)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious and missense mutant vs other cell lines by lineage, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-```{r fig.height=4, fig.width=8, eval=FALSE}
-wilcox_gene_delmis_lineage_plot <- ggplot(data = crispr_signif_delmis_lineage) +
-  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
-  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
-  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
-  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
-  labs(x = "BH-adjusted p-values", y = "Frequency")
-wilcox_gene_delmis_lineage_plot
-```
-
-# Wilcoxon tests: All mutations
+# Paper outline: G2P data
 
@@
 
-## Grouped by gene  {.tabset .tabset-fade .tabset-pills}
-
-### Deleterious vs. Other
-
-```{r, eval=FALSE}
-crispr_signif_allmut_del <- compare_means(Score ~ Mutation_Status_Deleterious, group.by = c("Hugo_Symbol"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
-crispr_signif_allmut_del <- adj_signif(crispr_signif_allmut_del)
-crispr_signif_allmut_del <- crispr_signif_allmut_del[order(crispr_signif_allmut_del$p),]
-saveRDS(crispr_signif_allmut_del, "./data_munging/rds/crispr_signif_allmut_deleterious_gene.rds")
-
-# write.table(crispr_signif_allmut_del, file = "~/Desktop/crispr_signif_allmut_deleterious_gene.csv", quote = FALSE, sep = ",", row.names = FALSE)
-```
-
-```{r, eval=FALSE}
-crispr_signif_allmut_del <- readRDS("./data_munging/rds/crispr_signif_allmut_deleterious_gene.rds")
-
-knitr::kable(filter(crispr_signif_allmut_del, p < 0.01)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious mutant vs other cell lines, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-```{r fig.height=4, fig.width=8, eval=FALSE}
-wilcox_gene_allmut_plot <- ggplot(data = crispr_signif_allmut_del) +
-  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
-  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
-  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
-  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
-  labs(x = "BH-adjusted p-values", y = "Frequency")
-wilcox_gene_allmut_plot
-# ggsave(filename = "./plots_18Q3/crispr/pvals_genes.pdf", plot = wilcox_gene_plot, width = 8, height = 4, device = "pdf")
-```
-
-### Non-silent mutant vs. Other
-
-```{r, eval=FALSE}
-crispr_signif_allmut_nonsilent <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
-crispr_signif_allmut_nonsilent <- adj_signif(crispr_signif_allmut_nonsilent)
-crispr_signif_allmut_nonsilent <- crispr_signif_allmut_nonsilent[order(crispr_signif_allmut_nonsilent$p),]
-saveRDS(crispr_signif_allmut_nonsilent, "./data_munging/rds/crispr_signif_allmut_nonsilent_gene.rds")
-
-# write.table(crispr_signif_allmut_nonsilent, file = "~/Desktop/crispr_signif_allmut_nonsilent_gene.csv", quote = FALSE, sep = ",", row.names = FALSE)
-```
-
-```{r, eval=FALSE}
-crispr_signif_allmut_nonsilent <- readRDS("./data_munging/rds/crispr_signif_allmut_nonsilent_gene.rds")
-
-knitr::kable(filter(crispr_signif_allmut_nonsilent, p < 0.01)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant vs other cell lines, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-```{r fig.height=4, fig.width=8, eval=FALSE}
-wilcox_gene_allmut_nonsilent_plot <- ggplot(data = crispr_signif_allmut_nonsilent) +
-  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
-  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
-  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
-  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
-  labs(x = "BH-adjusted p-values", y = "Frequency")
-wilcox_gene_allmut_nonsilent_plot
-```
-
-### Deleterious and missense mutant vs. Other
-
-```{r, eval=FALSE}
-crispr_signif_allmut_delmis <- compare_means(Score ~ Mutation_Status_DeleteriousMissense, group.by = c("Hugo_Symbol"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
-crispr_signif_allmut_delmis <- adj_signif(crispr_signif_allmut_delmis)
-crispr_signif_allmut_delmis <- crispr_signif_allmut_delmis[order(crispr_signif_allmut_delmis$p),]
-saveRDS(crispr_signif_allmut_delmis, "./data_munging/rds/crispr_signif_allmut_deleteriousmissense_gene.rds")
-
-# write.table(crispr_signif_allmut_delmis, file = "~/Desktop/crispr_signif_allmut_deleteriousmissense_gene.csv", quote = FALSE, sep = ",", row.names = FALSE)
-```
-
-```{r, eval=FALSE}
-crispr_signif_allmut_delmis <- readRDS("./data_munging/rds/crispr_signif_allmut_deleteriousmissense_gene.rds")
-
-knitr::kable(filter(crispr_signif_allmut_delmis, p < 0.01)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious and missense mutant vs other cell lines, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-```{r fig.height=4, fig.width=8, eval=FALSE}
-wilcox_gene_allmut_delmis_plot <- ggplot(data = crispr_signif_allmut_delmis) +
-  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
-  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
-  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
-  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
-  labs(x = "BH-adjusted p-values", y = "Frequency")
-wilcox_gene_allmut_delmis_plot
-```
-
-## Grouped by gene and lineage {.tabset .tabset-fade .tabset-pills}
-
-### Deleterious vs. Other
-
-```{r, eval=FALSE}
-crispr_signif_allmut_del_lineage <- compare_means(Score ~ Mutation_Status_Deleterious, group.by = c("Hugo_Symbol", "group_general_lineage_name"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
-crispr_signif_allmut_del_lineage <- adj_signif(crispr_signif_allmut_del_lineage)
-crispr_signif_allmut_del_lineage <- crispr_signif_allmut_del_lineage[order(crispr_signif_allmut_del_lineage$p),]
-saveRDS(crispr_signif_allmut_del_lineage, "./data_munging/rds/crispr_signif_allmut_deleterious_lineage.rds")
-
-# write.table(crispr_signif_allmut_del_lineage, file = "~/Desktop/crispr_signif_allmut_deleterious_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
-```
-
-```{r, eval=FALSE}
-crispr_signif_allmut_del_lineage <- readRDS("./data_munging/rds/crispr_signif_allmut_deleterious_lineage.rds")
-
-knitr::kable(filter(crispr_signif_allmut_del_lineage, p < 0.01)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious mutant vs other cell lines by lineage, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-```{r fig.height=4, fig.width=8, eval=FALSE}
-wilcox_lineage_allmut_plot <- ggplot(data = crispr_signif_allmut_del_lineage) +
-  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
-  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
-  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
-  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
-  labs(x = "BH-adjusted p-values", y = "Frequency")
-wilcox_lineage_allmut_plot
-```
-
-### Non-silent mutant vs. Other
-
-```{r, eval=FALSE}
-crispr_signif_allmut_nonsilent_lineage <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "group_general_lineage_name"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
-crispr_signif_allmut_nonsilent_lineage <- adj_signif(crispr_signif_allmut_nonsilent_lineage)
-crispr_signif_allmut_nonsilent_lineage <- crispr_signif_allmut_nonsilent_lineage[order(crispr_signif_allmut_nonsilent_lineage$p),]
-saveRDS(crispr_signif_allmut_nonsilent_lineage, "./data_munging/rds/crispr_signif_allmut_nonsilent_lineage.rds")
-
-# write.table(crispr_signif_allmut_nonsilent_lineage, file = "~/Desktop/crispr_signif_allmut_nonsilent_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
-```
-
-```{r, eval=FALSE}
-crispr_signif_allmut_nonsilent_lineage <- readRDS("./data_munging/rds/crispr_signif_allmut_nonsilent_lineage.rds")
-
-knitr::kable(filter(crispr_signif_allmut_nonsilent_lineage, p < 0.01)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant vs other cell lines by lineage, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-```{r fig.height=4, fig.width=8, eval=FALSE}
-wilcox_lineage_allmut_nonsilent_plot <- ggplot(data = crispr_signif_allmut_nonsilent_lineage) +
-  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
-  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
-  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
-  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
-  labs(x = "BH-adjusted p-values", y = "Frequency")
-wilcox_lineage_allmut_nonsilent_plot
-```
-
-### Deleterious and missense mutant vs. Other
-
-```{r, eval=FALSE}
-crispr_signif_allmut_delmis_lineage <- compare_means(Score ~ Mutation_Status_DeleteriousMissense, group.by = c("Hugo_Symbol", "group_general_lineage_name"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
-crispr_signif_allmut_delmis_lineage <- adj_signif(crispr_signif_allmut_delmis_lineage)
-crispr_signif_allmut_delmis_lineage <- crispr_signif_allmut_delmis_lineage[order(crispr_signif_allmut_delmis_lineage$p),]
-saveRDS(crispr_signif_allmut_delmis_lineage, "./data_munging/rds/crispr_signif_allmut_deleteriousmissens_lineage.rds")
-
-# write.table(crispr_signif_allmut_delmis_lineage, file = "~/Desktop/crispr_signif_allmut_deleteriousmissense_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
-```
-
-```{r, eval=FALSE}
-crispr_signif_allmut_delmis_lineage <- readRDS("./data_munging/rds/crispr_signif_allmut_deleteriousmissens_lineage.rds")
-
-knitr::kable(filter(crispr_signif_allmut_delmis_lineage, p < 0.01)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious vs missense mutant and other cell lines, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-```{r fig.height=4, fig.width=8, eval=FALSE}
-wilcox_lineage_allmut_delmis_plot <- ggplot(data = crispr_signif_allmut_delmis_lineage) +
-  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
-  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
-  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
-  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
-  labs(x = "BH-adjusted p-values", y = "Frequency")
-wilcox_lineage_allmut_delmis_plot
-```
-
-# Paper outline: G2P data
-
---------------------------------------------------------------------------------
-
-```{r}
-g2p <- read.delim("./data_munging/g2p_full_level_A_dataset.tsv", sep = "\t", header = TRUE)
+```{r}
+g2p <- read.delim("./data_munging/g2p_full_level_A_dataset_v2_10_10_2018.tsv", sep = "\t", header = TRUE)
 genes_lvlA <- unique(g2p$Gene)

### 2018-10-16 lineages_18Q3.Rmd
update rmd

@@
 ```{r}
-makeCRISPRgrob <- function(g) {
-
-  gene <- filter(crispr_data, Hugo_Symbol == g)
+makeCRISPRgrob <- function(g, filt_method) {
+  if(filt_method == "lvlA") {
+    gene <- filter(crispr_data_lvlA, Hugo_Symbol == g)
+    sig <- filter(crispr_signif_lvlA, Hugo_Symbol == g)
+  }
+  if(filt_method == "all") {
+    gene <- filter(crispr_data_ptmuts, Hugo_Symbol == g)
+    sig <- filter(crispr_signif_nonsilent, Hugo_Symbol == g)
+  }
 
   # Mutation status
-  crispr_color <- as.character(gene$Color)
-  names(crispr_color) <- gene$Mutation_Status
-  sig <- filter(crispr_signif, Hugo_Symbol == g)
-  plot_mut <- ggplot(data = gene, aes(x = Mutation_Status, y = Score, color = Mutation_Status)) +
+  crispr_color <- as.character(gene$Color_Nonsilent)
+  names(crispr_color) <- gene$Mutation_Status_Nonsilent
+
+  plot_mut <- ggplot(data = gene, aes(x = Mutation_Status_Nonsilent, y = Score, color = Mutation_Status_Nonsilent)) +
     geom_boxplot(outlier.shape = NA) +
@@
          title = "Mutation Status",
-         subtitle = paste0("Wilcoxon test:\n- BH-corrected p-value: ", sig$p.adj.short, "\n- Uncorrected p-value: ", sig$p.short, "\nMutant lines harbor deleterious mutations."))
+         subtitle = paste0("Wilcoxon test:\n- BH-corrected p-value: ", sig$p.adj.short, "\n- Uncorrected p-value: ", sig$p.short))
 
@@
   mid_cn <- (hi_cn - lo_cn) / 2
-  plot_cn <- ggplot(data = gene, aes(x = Copy_Number, y = Score, color = Mutation_Status)) +
+  plot_cn <- ggplot(data = gene, aes(x = Copy_Number, y = Score, color = Mutation_Status_Nonsilent)) +
     geom_point(size = 0.5, alpha = 0.5) +
@@
   mid_ge <- (hi_ge - lo_ge) / 2
-  plot_ge <- ggplot(data = gene, aes(x = RPKM_log2, y = Score, color = Mutation_Status)) +
+  plot_ge <- ggplot(data = gene, aes(x = RPKM_log2, y = Score, color = Mutation_Status_Nonsilent)) +
     geom_point(size = 0.5, alpha = 0.5) +
@@
   # Cell line lineage
-  plot_tissue <- ggplot(data = gene, aes(x = primary_tissue, y = Score, color = Mutation_Status)) +
+  plot_tissue <- ggplot(data = gene, aes(x = primary_tissue, y = Score, color = Mutation_Status_Nonsilent)) +
     geom_point(alpha = 0.5) +
@@
 
-## Make tissue plot
-
-```{r}
-makeCRISPRtissueplot <- function(g) {
-  sig <- filter(crispr_signif_tissue, Hugo_Symbol == g)
-  if(nrow(sig) == 0) {
-    return(NULL)
-  }
-  else {
-    gene <- filter(crispr_data, Hugo_Symbol == g)
-    gene <- merge(gene, sig, by = c("Hugo_Symbol", "primary_tissue"))
-    gene <- mutate(gene, primary_tissue = reorder(primary_tissue, p, mean))
-    crispr_color <- as.character(gene$Color)
-    names(crispr_color) <- gene$Mutation_Status
-    score_range <- abs(range(gene$Score)[2] - range(gene$Score)[1])
-    round_accuracy <- ifelse(score_range <= 2, 0.25,
-                             ifelse(score_range <= 3, 0.5, 1.0))
-
-    plot <- ggplot(data = gene, aes(x = primary_tissue, y = Score)) +
-      geom_point(alpha = 0.5, mapping = aes(color = Mutation_Status)) +
-      scale_color_manual(values = crispr_color) +
-      coord_cartesian(y = c(min(gene$Score), round_any(x = max(gene$Score), accuracy = round_accuracy, f = ceiling))) +
-      geom_signif(data = gene, mapping = aes(xmin = primary_tissue, xmax = primary_tissue, annotations = paste(p.short, "\n", p.adj.short), y_position = max(gene$Score)), manual = TRUE, tip_length   = 0, size = 0, textsize = 3) +
-      theme(legend.position = "top", axis.text.x = element_text(angle = 70, hjust = 1, size = 10)) +
-      labs(y = "CERES Score",
-           x = "Primary Tissue",
-           color = "Mutation Status",
-           title = paste0(g, ": CERES score by cell line primary tissue"),
-           subtitle = "Primary tissues sorted by increasing p-value; labels indicate unadjusted p-value / BH-corrected p-value.\nMutant lines harbor deleterious mutations.")
-    return(plot)
-  }
-}
-```
-
 # Data management
@@
 
+## DepMap cell line metadata
+
+```{r}
+ccl_info <- read.delim("./data_munging/DepMap-2018q3-celllines.csv", sep = ",", header = TRUE, na.strings = c("", NA))
+ccl_info$Primary.Disease <- gsub("\\\\", "", ccl_info$Primary.Disease)
+ccl_info$Primary.Disease <- gsub("Ewings", "Ewing's", ccl_info$Primary.Disease)
+
+# From figshare
+crispr_meta <- read.delim("./data_munging/sample_info_18Q3_crispr.csv", sep = ",", header = TRUE, na.strings = c("", NA))
+colnames(crispr_meta)[7] <- "CCLE_Name"
+```
+
+```{r, include=FALSE}
+dan_test <- select(ccl_converter, CCLE_Name, Broad_ID, cell_line_name)
+dan_test <- dan_test[-which(dan_test$CCLE_Name == ""), ]
+ccl_test <- select(ccl_info, CCLE_Name, Broad_ID)
+
+test <- merge(ccl_test, dan_test, by = "CCLE_Name", all = TRUE, suffixes = c("_DepMap", "_Daniel"))
+test$BroadIDs_match <- ifelse(as.character(test$Broad_ID_DepMap) == as.character(test$Broad_ID_Daniel), TRUE, FALSE)
+
+test_false <- filter(test, BroadIDs_match == FALSE)
+# write.table(ccl_converter, file = "~/Desktop/cell_line_database_v1_20180907.tsv", quote = FALSE, sep = "\t")
+```
+
 ## Genomic annotations
@@
 colnames(dep) <- gsub(" .*", "", colnames(dep))
-```
-
-### DepMap cell line metadata
-
-```{r}
-ccl_info <- read.delim("./data_munging/DepMap-2018q3-celllines.csv", sep = ",", header = TRUE, na.strings = c("", NA))
-ccl_info$Primary.Disease <- gsub("\\\\", "", ccl_info$Primary.Disease)
-ccl_info$Primary.Disease <- gsub("Ewings", "Ewing's", ccl_info$Primary.Disease)
-
-# From figshare
-crispr_meta <- read.delim("./data_munging/sample_info_18Q3_crispr.csv", sep = ",", header = TRUE, na.strings = c("", NA))
-colnames(crispr_meta)[7] <- "CCLE_Name"
-```
-
-```{r, include=FALSE}
-dan_test <- select(ccl_converter, CCLE_Name, Broad_ID, cell_line_name)
-dan_test <- dan_test[-which(dan_test$CCLE_Name == ""), ]
-ccl_test <- select(ccl_info, CCLE_Name, Broad_ID)
-
-test <- merge(ccl_test, dan_test, by = "CCLE_Name", all = TRUE, suffixes = c("_DepMap", "_Daniel"))
-test$BroadIDs_match <- ifelse(as.character(test$Broad_ID_DepMap) == as.character(test$Broad_ID_Daniel), TRUE, FALSE)
-
-test_false <- filter(test, BroadIDs_match == FALSE)
-# write.table(ccl_converter, file = "~/Desktop/cell_line_database_v1_20180907.tsv", quote = FALSE, sep = "\t")
 ```
@@
 drug_data <- merge(drug_data, maf_df, by = c("CCLE_Name", "Broad_ID"))
-drug_data$Hugo_Symbol <- factor(drug_muts$Hugo_Symbol)
-
-saveRDS(drug_data, "./../crispr_lineages_giant_files/drug_data_18Q3.rds", compress = "xz")
-```
-
-```{r}
-crispr_data <- readRDS("./../crispr_lineages_giant_files/crispr_data_18Q3.rds")
-crispr_ccl <- data.frame("Broad_ID" = crispr_data$Broad_ID)
-# write.table(crispr_data, file = "~/Desktop/crispr_data.tsv", quote = FALSE, sep = "\t")
+drug_data$Hugo_Symbol <- factor(drug_data$Hugo_Symbol)
+
+saveRDS(drug_data, "./data_munging/drug_data_18Q3.rds", compress = "xz")
+```
+
+```{r}
+drug_data <- readRDS("./data_munging/drug_data_18Q3.rds")
 ```
@@
 
-### Grouped by gene and lineage: Non-silent mutant vs. Other
+### Grouped by gene and lineage
 
@@
   geom_text(data = lvlA_genes_text, mapping = aes(x = 1.5, y = Text_y, label = p.signif.adj), nudge_y = 0.2) +
-  theme(legend.position = "top", axis.text.x = element_text(angle = 65, hjust = 1, vjust = 1, size = 10)) +
+  theme(legend.position = "top") +
   labs(y = "CERES Score",
@@
 
-```{r}
-test <- '{"feature_names": "ALK positive", "tags": "test", "genes": "ALK"}'
-
-fromJSON(test)
-```
+## Level A: Per-gene grouped plots
+
+Plot code:
+```{r, eval=FALSE}
+crispr_lvlA_groups <- lapply(as.character(genes_lvlA), makeCRISPRgrob, filt_method = "lvlA")
+crispr_lvlA_groups_paths <- paste0(genes_lvlA, "_crispr_grouped.png")
+pwalk(list(crispr_lvlA_groups_paths, crispr_lvlA_groups), ggsave, path = "./plots_18Q3/crispr_grouped_plots_lvlA", dpi = 300, width = 12, height = 12, units = "in")
+```
+
+Data management:
+```{r, eval=TRUE}
+crispr_lvlA_bygene <- paste0(list.files("./plots_18Q3/crispr_grouped_plots_lvlA", full.names = TRUE))
+names(crispr_lvlA_bygene) <- str_replace_all(crispr_lvlA_bygene, c("_crispr_grouped.png" = "", "./plots_18Q3/crispr_grouped_plots_lvlA/" = ""))
+crispr_lvlA_order <- c(intersect(crispr_signif_lvlA$Hugo_Symbol, names(crispr_lvlA_bygene)), setdiff(names(crispr_lvlA_bygene), crispr_signif_lvlA$Hugo_Symbol))
+crispr_lvlA_bygene <- crispr_lvlA_bygene[match(crispr_lvlA_order, names(crispr_lvlA_bygene))]
+bsselect(crispr_lvlA_bygene, type = "img", selected = "KRAS", live_search = TRUE, show_tick = TRUE, height = 300, frame_height = 275)
+```
+
+## All genes: Per-gene grouped plots
+
+Plot code:
+```{r, eval=FALSE}
+crispr_all_groups <- lapply(unique(crispr_data_ptmuts$Hugo_Symbol), makeCRISPRgrob, filt_method = "all")
+crispr_all_groups_paths <- paste0(unique(crispr_data_ptmuts$Hugo_Symbol), "_crispr_grouped.png")
+pwalk(list(crispr_lvlA_groups_paths, crispr_lvlA_groups), ggsave, path = "./plots_18Q3/crispr_grouped_plots", dpi = 300, width = 12, height = 12, units = "in")
+```
+
+Data management:
+```{r, eval=TRUE}
+crispr_all_bygene <- paste0(list.files("./plots_18Q3/crispr_grouped_plots", full.names = TRUE))
+names(crispr_all_bygene) <- str_replace_all(crispr_all_bygene, c("_crispr_grouped.png" = "", "./plots_18Q3/crispr_grouped_plots_lvlA/" = ""))
+crispr_all_order <- c(intersect(crispr_signif_nonsilent$Hugo_Symbol, names(crispr_all_bygene)), setdiff(names(crispr_all_bygene), crispr_signif_nonsilent$Hugo_Symbol))
+crispr_all_bygene <- crispr_all_bygene[match(crispr_all_order, names(crispr_all_bygene))]
+bsselect(crispr_all_bygene, type = "img", selected = "KRAS", live_search = TRUE, show_tick = TRUE, height = 300, frame_height = 275)
+```
+
+## JSON
 
@@
 ```{r fig.height=12, fig.width=12, include=FALSE, eval=FALSE}
-makeCRISPRgrob("KRAS")
+makeCRISPRgrob("KRAS", filt_method = "all")
 ```
@@
 ```{r, eval=FALSE}
-crispr_data_cgc <- filter(crispr_data, Hugo_Symbol %in% cgc$Hugo_Symbol)
-crispr_all_genes <- unique(crispr_data_cgc$Hugo_Symbol)
+crispr_lvlA_genes <- unique(crispr_data_cgc$Hugo_Symbol)
 crispr_all_groups <- lapply(crispr_all_genes, makeCRISPRgrob)
@@
 names(crispr_all_bygene) <- str_replace_all(crispr_all_bygene, c("_crispr_lineage.png" = "", "./plots_18Q3/crispr_lineage_plots_cgc/" = ""))
-crispr_bygene_order <- c(intersect(crispr_signif$Hugo_Symbol, names(crispr_all_bygene)), setdiff(names(crispr_all_bygene), crispr_signif$Hugo_Symbol))
-crispr_all_bygene <- crispr_all_bygene[match(crispr_bygene_order, names(crispr_all_bygene))]
-bsselect(crispr_all_bygene, type = "img", selected = "KRAS", live_search = TRUE, show_tick = TRUE, height = 300, frame_height = 275)
-```
-
-## Sorted tissue plots
-
-```{r fig.height=12, fig.width=12, include=FALSE, eval=FALSE}
-makeCRISPRtissueplot("KRAS")
-```
-
-Plot code:
-```{r, eval=FALSE}
-crispr_data_cgc <- filter(crispr_data, Hugo_Symbol %in% cgc$Hugo_Symbol)
-crispr_all_genes <- unique(crispr_data_cgc$Hugo_Symbol)
-crispr_all_lins <- lapply(crispr_all_genes, makeCRISPRtissueplot)
-crispr_all_lins_paths <- paste0(crispr_all_genes, "_crispr_tissue.png")
-pwalk(list(crispr_all_lins_paths, crispr_all_lins), ggsave, path = "./plots_18Q3/crispr_tissue_plots_cgc", dpi = 300, width = 12, height = 12, units = "in")
-```
-
-Data management:
-```{r, eval=FALSE}
-crispr_all_bygene <- paste0(list.files("./plots_18Q3/crispr_tissue_plots_cgc", full.names = TRUE))
-names(crispr_all_bygene) <- str_replace_all(crispr_all_bygene, c("_crispr_tissue.png" = "", "./plots_18Q3/crispr_tissue_plots_cgc/" = ""))
 crispr_bygene_order <- c(intersect(crispr_signif$Hugo_Symbol, names(crispr_all_bygene)), setdiff(names(crispr_all_bygene), crispr_signif$Hugo_Symbol))

### 2018-10-16 lineages_18Q3.Rmd

@@
 library(gridExtra)
-# devtools::install_github("jeroen/jsonlite")
-# install.packages("jsonlite")
 library(jsonlite)
@@
 
-## Make CRISPR grobs
+## Make CRISPR grouped plots
 
@@
 
-## Make lineage plot
+## Make sorted lineage plots
 
@@
 
-# Data management
+## Make drug screen boxplots
+```{r}
+makeDrugBoxplots <- function(drug, dataset) {
+  if(dataset == "CCLE" | dataset == "ccle") {
+    use_data <- filter(ccle_ptmuts_lvlA_filt, Drug == drug)
+    use_color <- as.character(use_data$Color_Nonsilent)
+    names(use_color) <- use_data$Mutation_Status_Nonsilent
+    sig <- filter(ccle_signif_lvlA, Drug == drug)
+    label_text <- data.frame(p.signif.adj = sig$p.signif.adj, Hugo_Symbol = sig$Hugo_Symbol)
+    label_text <- filter(label_text, Hugo_Symbol %in% genes_lvlA_filt)
+    label_text$Hugo_Symbol <- factor(label_text$Hugo_Symbol, levels = genes_lvlA_filt)
+  }
+  else if(dataset == "CTRP" | dataset == "ctrp") {
+    use_data <- filter(ctrp_ptmuts_lvlA_filt, Drug == drug)
+    use_color <- as.character(use_data$Color_Nonsilent)
+    names(use_color) <- use_data$Mutation_Status_Nonsilent
+    sig <- filter(ctrp_signif_lvlA, Drug == drug)
+    label_text <- data.frame(p.signif.adj = sig$p.signif.adj, Hugo_Symbol = sig$Hugo_Symbol)
+    label_text <- filter(label_text, Hugo_Symbol %in% genes_lvlA_filt)
+    label_text$Hugo_Symbol <- factor(label_text$Hugo_Symbol, levels = genes_lvlA_filt)
+  }
+  else if(dataset == "GDSC" | dataset == "gdsc") {
+    use_data <- filter(gdsc_ptmuts_lvlA_filt, Drug == drug)
+    use_color <- as.character(use_data$Color_Nonsilent)
+    names(use_color) <- use_data$Mutation_Status_Nonsilent
+    sig <- filter(gdsc_signif_lvlA, Drug == drug)
+    label_text <- data.frame(p.signif.adj = sig$p.signif.adj, Hugo_Symbol = sig$Hugo_Symbol)
+    label_text <- filter(label_text, Hugo_Symbol %in% genes_lvlA_filt)
+    label_text$Hugo_Symbol <- factor(label_text$Hugo_Symbol, levels = genes_lvlA_filt)
+  }
+  else { return("Error: Invalid dataset.") }
+
+  plot <- ggplot(data = use_data, aes(x = Mutation_Status_Nonsilent, y = AUC)) +
+    facet_wrap(~ Hugo_Symbol, drop = FALSE, ncol = length(genes_lvlA_filt)) +
+    geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
+    geom_boxplot(mapping = aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85)) +
+    scale_fill_manual(values = use_color) +
+    guides(color = FALSE) +
+    geom_text(data = label_text, mapping = aes(x = 1.5, y = max(use_data$AUC), label = p.signif.adj)) +
+    theme(legend.position = "top", axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
+    labs(fill = "Mutation Status", y = "AUC", x = "Mutation Status", title = paste0(dataset, ": ", drug))
+  return(plot)
+}
+```
+
+# Data management {.tabset .tabset-fade .tabset-pills}
 
@@
 # Select columns
-maf_df <- subset(maf_raw, select = c("Hugo_Symbol", "CCLE_Name", "Broad_ID", "Variant_Classification", "isDeleterious", "Reference_Allele", "Tumor_Seq_Allele1"))
+maf_df <- subset(maf_raw, select = c("Hugo_Symbol", "CCLE_Name", "Broad_ID", "Variant_Classification", "Reference_Allele", "Tumor_Seq_Allele1"))
 maf_df$Reference_Allele_Length <- ifelse(maf_df$Reference_Allele == "-", 0, nchar(as.character(maf_df$Reference_Allele)))
@@
 
-```{r, eval=FALSE}
+```{r, eval=FALSE, include=FALSE}
 max(nchar(as.character(maf_raw$Reference_Allele)))
@@
 
-```{r}
+```{r, eval=FALSE}
 cn_melt <- readRDS("./data_munging/rds/cn_melt_18Q3.rds")
@@
 
-```{r}
+```{r, eval=FALSE}
 ge_melt <- readRDS("./../crispr_lineages_giant_files/ge_melt_18Q3.rds")
@@
 
-```{r fig.height=12, fig.width=12, eval=FALSE}
-crispr_pca_data <- merge(ccl_converter[, c("Broad_ID", "group_general_lineage_name")], crispr, by = "Broad_ID")
-crispr_lin <- crispr_pca_data[, 2]
-crispr_pca <- prcomp(data.matrix(crispr_pca_data[, 3:ncol(crispr_pca_data)]), scale. = TRUE, center = TRUE)
-plot(crispr_pca, type = "l")
-biplot(crispr_pca, obs.scale = 1, var.scale = 1, groups = crispr_lin, ellipse = TRUE, circle = TRUE)
-ggord(crispr_pca, crispr_pca_data$group_general_lineage_name)
-```
-
 Merge annotation data:
@@
 crispr_melt <- melt(crispr, id.vars = "Broad_ID", measure.vars = colnames(crispr)[2:ncol(crispr)], variable.name = "Hugo_Symbol", value.name = "Score")
-
 # Melt dependency probabilities dataset for merging
 dep_melt <- melt(dep, id.vars = "Broad_ID", measure.vars = colnames(dep)[2:ncol(dep)], variable.name = "Hugo_Symbol", value.name = "Dep_Prob")
-
 # Merge dependency probabilities
 crispr_melt <- merge(crispr_melt, dep_melt, by = c("Broad_ID", "Hugo_Symbol"), all.x = TRUE)
-
 # Merge cell line metadata
@@
 crispr_melt <- merge(crispr_melt, crispr_meta, by = c("CCLE_Name", "Broad_ID"), all.x = TRUE)
-
 # Merge mutation annotations
@@
 crispr_muts <- crispr_muts %>% mutate(Mutation_Status_Nonsilent = if_else(is.na(Mutation_Status_Nonsilent), "Other", Mutation_Status_Nonsilent))
-
 # Summarize number of mutant and Other cell lines
@@
             N_Nonsilent_Mutant = sum(Mutation_Status_Nonsilent == "Mutant"))
-
 # Merge test results back into full dataset, which restores information lost in the summarization
 crispr_data <- merge(crispr_muts_summ, crispr_muts, by = "Hugo_Symbol")
-
 # Add Color columns
@@
 crispr_data$Color_Nonsilent <- factor(crispr_data$Color_Nonsilent)
-
 # Cell line lineages
@@
 levels(crispr_data$lineage_name) <- sort(levels(crispr_data$lineage_name), decreasing = TRUE)
-
 # Copy number
 crispr_data <- merge(crispr_data, cn_melt, by = c("Hugo_Symbol", "Broad_ID"), all.x = TRUE)
-
 # Gene expression (RPKM)
@@
 crispr_data$RPKM_log2 <- log2(crispr_data$RPKM + 0.0001)
-
 saveRDS(crispr_data, "./../crispr_lineages_giant_files/crispr_data_18Q3.rds", compress = "xz")
@@
 
+```{r fig.height=12, fig.width=12, eval=FALSE, include=FALSE}
+# Test dimensional scaling
+crispr_pca_data <- merge(ccl_converter[, c("Broad_ID", "group_general_lineage_name")], crispr, by = "Broad_ID")
+crispr_lin <- crispr_pca_data[, 2]
+crispr_pca <- prcomp(data.matrix(crispr_pca_data[, 3:ncol(crispr_pca_data)]), scale. = TRUE, center = TRUE)
+plot(crispr_pca, type = "l")
+biplot(crispr_pca, obs.scale = 1, var.scale = 1, groups = crispr_lin, ellipse = TRUE, circle = TRUE)
+ggord(crispr_pca, crispr_pca_data$group_general_lineage_name)
+```
+
 ## Drug screens
+
+```{r}
+g2p <- read.delim("./data_munging/g2p_full_level_A_dataset_v2_10_10_2018.tsv", sep = "\t", header = TRUE)
+genes_lvlA_df <- data.frame(Hugo_Symbol = unique(g2p$Gene))
+genes_lvlA <- unique(g2p$Gene)
+```
 
@@
 drug_meta$Drug <- tolower(drug_meta$Drug)
+maf_df_lvlA <- filter(maf_df, Hugo_Symbol %in% genes_lvlA)
 
@@
 ccle <- merge(drug_meta, ccle, by = "CID")
-ccle_melt <- melt(ccle, id.vars = c("CID", "Drug"), measure.vars = colnames(ccle)[3:ncol(ccle)], variable.name = "accession_id", value.name = "AUC_CCLE")
+ccle_melt <- melt(ccle, id.vars = c("CID", "Drug"), measure.vars = colnames(ccle)[3:ncol(ccle)], variable.name = "accession_id", value.name = "AUC")
+ccle_grid <- expand.grid("accession_id" = unique(ccle_melt$accession_id), "Hugo_Symbol" = genes_lvlA)
+ccle_data <- merge(ccle_grid, ccle_melt, by = "accession_id", all.x = TRUE)
+ccle_data <- merge(ccle_data, ccl_converter, by = "accession_id", all.x = TRUE)
+ccle_data <- merge(ccle_data, maf_df_lvlA, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
+ccle_data$Mutation_Status_Nonsilent <- ifelse(is.na(ccle_data$Mutation_Status_Nonsilent), "Other", ccle_data$Mutation_Status_Nonsilent)
+ccle_data$Hugo_Symbol <- factor(ccle_data$Hugo_Symbol)
+ccle_data$AUC <- as.numeric(ccle_data$AUC)
+ccle_data$Color_Nonsilent <- ifelse(ccle_data$Mutation_Status_Nonsilent == "Other", "palegreen3", "springgreen4")
+ccle_data$Color_Nonsilent <- factor(ccle_data$Color_Nonsilent)
+ccle_data <- filter(ccle_data, !is.na(ccle_data$AUC))
+saveRDS(ccle_data, "./data_munging/rds/ccle_data_18Q3.rds", compress = "xz")
 
@@
 ctrp <- merge(drug_meta, ctrp, by = "CID")
-ctrp_melt <- melt(ctrp, id.vars = c("CID", "Drug"), measure.vars = colnames(ctrp)[3:ncol(ctrp)], variable.name = "accession_id", value.name = "AUC_CTRP")
+ctrp_melt <- melt(ctrp, id.vars = c("CID", "Drug"), measure.vars = colnames(ctrp)[3:ncol(ctrp)], variable.name = "accession_id", value.name = "AUC")
+ctrp_grid <- expand.grid("accession_id" = unique(ctrp_melt$accession_id), "Hugo_Symbol" = genes_lvlA)
+ctrp_data <- merge(ctrp_grid, ctrp_melt, by = "accession_id", all.x = TRUE)
+ctrp_data <- merge(ctrp_data, ccl_converter, by = "accession_id", all.x = TRUE)
+ctrp_data <- merge(ctrp_data, maf_df_lvlA, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
+ctrp_data$Mutation_Status_Nonsilent <- ifelse(is.na(ctrp_data$Mutation_Status_Nonsilent), "Other", ctrp_data$Mutation_Status_Nonsilent)
+ctrp_data$Hugo_Symbol <- factor(ctrp_data$Hugo_Symbol)
+ctrp_data$AUC <- as.numeric(ctrp_data$AUC)
+ctrp_data$Color_Nonsilent <- ifelse(ctrp_data$Mutation_Status_Nonsilent == "Other", "slategray3", "steelblue4")
+ctrp_data$Color_Nonsilent <- factor(ctrp_data$Color_Nonsilent)
+ctrp_data <- filter(ctrp_data, !is.na(ctrp_data$AUC))
+saveRDS(ctrp_data, "./data_munging/rds/ctrp_data_18Q3.rds", compress = "xz")
 
@@
 gdsc <- merge(drug_meta, gdsc, by = "CID")
-gdsc_melt <- melt(gdsc, id.vars = c("CID", "Drug"), measure.vars = colnames(gdsc)[3:ncol(gdsc)], variable.name = "accession_id", value.name = "AUC_GDSC")
-
-# Merge all data
-drug_data <- merge(merge(ccle_melt, ctrp_melt, by = c("accession_id", "CID", "Drug"), all = TRUE), gdsc_melt, by = c("accession_id", "CID", "Drug"), all = TRUE)
-drug_data <- merge(drug_data, ccl_converter, by = "accession_id", all.x = TRUE)
-drug_data <- merge(drug_data, maf_df, by = c("CCLE_Name", "Broad_ID"))
-drug_data$Hugo_Symbol <- factor(drug_data$Hugo_Symbol)
-
-saveRDS(drug_data, "./data_munging/drug_data_18Q3.rds", compress = "xz")
-```
-
-```{r}
-drug_data <- readRDS("./data_munging/drug_data_18Q3.rds")
-```
-
-# Wilcoxon tests
+gdsc_melt <- melt(gdsc, id.vars = c("CID", "Drug"), measure.vars = colnames(gdsc)[3:ncol(gdsc)], variable.name = "accession_id", value.name = "AUC")
+gdsc_grid <- expand.grid("accession_id" = unique(gdsc_melt$accession_id), "Hugo_Symbol" = genes_lvlA)
+gdsc_data <- merge(gdsc_grid, gdsc_melt, by = "accession_id", all.x = TRUE)
+gdsc_data <- merge(gdsc_data, ccl_converter, by = "accession_id", all.x = TRUE)
+gdsc_data <- merge(gdsc_data, maf_df_lvlA, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
+gdsc_data$Mutation_Status_Nonsilent <- ifelse(is.na(gdsc_data$Mutation_Status_Nonsilent), "Other", gdsc_data$Mutation_Status_Nonsilent)
+gdsc_data$Hugo_Symbol <- factor(gdsc_data$Hugo_Symbol)
+gdsc_data$AUC <- as.numeric(gdsc_data$AUC)
+gdsc_data$Color_Nonsilent <- ifelse(gdsc_data$Mutation_Status_Nonsilent == "Other", "paleturquoise3", "turquoise4")
+gdsc_data$Color_Nonsilent <- factor(gdsc_data$Color_Nonsilent)
+gdsc_data <- filter(gdsc_data, !is.na(gdsc_data$AUC))
+saveRDS(gdsc_data, "./data_munging/rds/ctrp_data_18Q3.rds", compress = "xz")
+```
+
+```{r}
+ccle_data <- readRDS("./data_munging/rds/ccle_data_18Q3.rds")
+ctrp_data <- readRDS("./data_munging/rds/ctrp_data_18Q3.rds")
+gdsc_data <- readRDS("./data_munging/rds/gdsc_data_18Q3.rds")
+```
+
+```{r}
+test_gdsc <- gdsc_data %>% group_by(Drug, Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()
+```
+
+# Wilcoxon tests: All genes
 
@@
 crispr_data_ptmuts <- filter(crispr_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
-
 crispr_data_ptmuts$Keep_PtMut_Tests <- ifelse(crispr_data_ptmuts$Reference_Allele_Length == 1 | is.na(crispr_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(crispr_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
-
 crispr_data_ptmuts <- filter(crispr_data_ptmuts, Keep_PtMut_Tests == TRUE)
@@
 
-# Paper outline: G2P data
+# G2P project
 
 --------------------------------------------------------------------------------
-
-```{r}
-g2p <- read.delim("./data_munging/g2p_full_level_A_dataset_v2_10_10_2018.tsv", sep = "\t", header = TRUE)
-genes_lvlA <- unique(g2p$Gene)
-```
 
@@
 
-### Gene
+### CRISPR: Gene
+
 ```{r, eval=FALSE}
@@
 
-crispr_signif_genes_lvlA <- as.character(filter(crispr_signif_lvlA, !is.na(p.signif.adj))$Hugo_Symbol)
-
-knitr::kable(filter(crispr_signif_lvlA, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results for Level A point mutations, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+crispr_signif_genes_lvlA <- as.character(crispr_signif_lvlA$Hugo_Symbol[0:20])
+
+knitr::kable(filter(crispr_signif_lvlA, p < 0.1)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results for Level A point mutations, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
-### Gene and lineage
+```{r fig.height=7, fig.width=12}
+lvlA_genes_signif <- filter(crispr_data_ptmuts, Hugo_Symbol %in% crispr_signif_genes_lvlA)
+lvlA_genes_signif <- merge(lvlA_genes_signif, crispr_signif_lvlA, by = "Hugo_Symbol")
+lvlA_genes_signif$Hugo_Symbol <- ordered(lvlA_genes_signif$Hugo_Symbol, levels = crispr_signif_genes_lvlA)
+lvlA_genes_signif_color <- as.character(lvlA_genes_signif$Color_Nonsilent)
+names(lvlA_genes_signif_color) <- lvlA_genes_signif$Mutation_Status_Nonsilent
+lvlA_genes_signif <- merge(lvlA_genes_signif, lvlA_genes_signif %>% group_by(Hugo_Symbol) %>% summarize(Text_y = max(Score)), by = "Hugo_Symbol")
+
+lvlA_genes_text <- unique(data.frame(p.signif.adj = lvlA_genes_signif$p.signif.adj, Hugo_Symbol = lvlA_genes_signif$Hugo_Symbol, Text_y = lvlA_genes_signif$Text_y))
+lvlA_genes_text$Hugo_Symbol <- factor(lvlA_genes_text$Hugo_Symbol, levels = crispr_signif_genes_lvlA)
+
+lvlA_signif_genes_plot <- ggplot(data = lvlA_genes_signif, aes(x = Mutation_Status_Nonsilent, y = Score)) +
+  facet_wrap(~ Hugo_Symbol, nrow = 2, scales = "free_y") +
+  geom_jitter(aes(color = Mutation_Status_Nonsilent), alpha = 0.5, width = 0.3) +
+  geom_boxplot(color = "black", fill = NA, outlier.shape = NA) +
+  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
+  scale_color_manual(values = lvlA_genes_signif_color) + 
+  geom_text(data = lvlA_genes_text, mapping = aes(x = 1.5, y = Text_y, label = p.signif.adj), nudge_y = 0.2) +
+  theme(legend.position = "top") +
+  labs(y = "CERES Score",
+       x = "Lineage",
+       color = "Mutation Status",
+       title = "CERES scores for select Level A G2P genes",
+       subtitle = "Genes with adjusted p-values < 0.3 are shown.\nBH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001\nGenes are sorted by increasing p-value.")
+lvlA_signif_genes_plot
+
+# ggsave("./plots_18Q3/manuscript/crispr_g2p_lvlA_signif_genes_plot.png", lvlA_signif_genes_plot, width = 12, height = 7, units = "in")
+```
+
+### CRISPR: Gene and lineage
 
@@
 
-## Figure 1C plots
+```{r fig.height=15, fig.width=15}
+lvlA_signif <- filter(crispr_data_ptmuts, Hugo_Symbol %in% crispr_signif_genes_lvlA)
+lvlA_signif <- merge(lvlA_signif, crispr_signif_lvlA_lineage, by = c("Hugo_Symbol", "group_general_lineage_name"))
+lvlA_signif$Hugo_Symbol <- ordered(lvlA_signif$Hugo_Symbol, levels = crispr_signif_genes_lvlA)
+lvlA_signif_color <- as.character(lvlA_signif$Color_Nonsilent)
+names(lvlA_signif_color) <- lvlA_signif$Mutation_Status_Nonsilent
+lvlA_signif <- merge(lvlA_signif, lvlA_signif %>% group_by(Hugo_Symbol) %>% summarize(Text_y = max(Score)), by = "Hugo_Symbol")
+
+lvlA_text <- unique(data.frame(p.signif.adj = lvlA_signif$p.signif.adj, group_general_lineage_name = lvlA_signif$group_general_lineage_name, Hugo_Symbol = lvlA_signif$Hugo_Symbol, Text_y = lvlA_signif$Text_y))
+lvlA_text$Hugo_Symbol <- factor(lvlA_text$Hugo_Symbol, levels = crispr_signif_genes_lvlA)
+
+lvlA_signif_lineages_plot <- ggplot(data = lvlA_signif, aes(x = group_general_lineage_name, y = Score)) +
+  facet_wrap(~ Hugo_Symbol, nrow = 4, scales = "free_y") +
+  geom_point(aes(color = Mutation_Status_Nonsilent), alpha = 0.5) +
+  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
+  scale_color_manual(values = lvlA_signif_color) +
+  geom_text(data = lvlA_text, mapping = aes(x = group_general_lineage_name, y = Text_y, label = p.signif.adj), nudge_y = 0.1) +
+  theme(legend.position = "top", axis.text.x = element_text(angle = 90, hjust = 1, vjust = 1, size = 10)) +
+  labs(y = "CERES Score",
+       x = "Lineage",
+       color = "Mutation Status",
+       title = "CERES score by cell line lineage for significant Level A G2P genes",
+       subtitle = "Genes with adjusted p-values < 0.3 are shown.\nBH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001\nGenes are sorted by increasing lineage-agnostic p-value.")
+lvlA_signif_lineages_plot
+
+# ggsave("./plots_18Q3/manuscript/crispr_g2p_lvlA_signif_lineages_plot.png", lvlA_signif_lineages_plot, width = 12, height = 15, units = "in")
+```
+
+```{r}
+lvlA_signif_summ <- lvlA_signif %>% group_by(Hugo_Symbol, group_general_lineage_name, Mutation_Status_Nonsilent) %>% tally()
+# write.table(lvlA_signif_summ, file = "~/Desktop/lvlA_signif_summ_20181005.tsv", quote = FALSE, sep = "\t")
+
+knitr::kable(lvlA_signif_summ, caption = "Mutant/Other counts for gene-lineage combinations") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+### CCLE: Gene and drug
+
+```{r}
+ccle_data_ptmuts <- filter(ccle_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
+ccle_data_ptmuts$Keep_PtMut_Tests <- ifelse(ccle_data_ptmuts$Reference_Allele_Length == 1 | is.na(ccle_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(ccle_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
+ccle_data_ptmuts <- filter(ccle_data_ptmuts, Keep_PtMut_Tests == TRUE)
+ccle_data_lvlA <- filter(ccle_data_ptmuts, Hugo_Symbol %in% genes_lvlA)
+```
+
+```{r, eval=FALSE}
+ccle_signif_lvlA <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = c("Drug", "Hugo_Symbol"), data = ccle_data_lvlA, method = "wilcox.test", p.adjust.method = "BH")
+ccle_signif_lvlA <- adj_signif(ccle_signif_lvlA)
+ccle_signif_lvlA <- ccle_signif_lvlA[order(ccle_signif_lvlA$p),]
+saveRDS(ccle_signif_lvlA, "./data_munging/rds/ccle_signif_lvlA_gene.rds")
+```
+
+```{r, eval=TRUE}
+ccle_signif_lvlA <- readRDS("./data_munging/rds/ccle_signif_lvlA_gene.rds")
+
+# ccle_signif_genes_lvlA <- as.character(ccle_signif_lvlA$Hugo_Symbol[0:20])
+
+knitr::kable(ccle_signif_lvlA[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for Level A point mutations, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+```{r fig.height=4, fig.width=8}
+wilcox_ccle_gene_lvlA_plot <- ggplot(data = ccle_signif_lvlA) +
+  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
+  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
+  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
+  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
+  labs(x = "BH-adjusted p-values", y = "Frequency")
+wilcox_ccle_gene_lvlA_plot
+```
+
+### CTRP: Gene and drug
+
+```{r}
+ctrp_data_ptmuts <- filter(ctrp_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
+ctrp_data_ptmuts$Keep_PtMut_Tests <- ifelse(ctrp_data_ptmuts$Reference_Allele_Length == 1 | is.na(ctrp_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(ctrp_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
+ctrp_data_ptmuts <- filter(ctrp_data_ptmuts, Keep_PtMut_Tests == TRUE)
+ctrp_data_lvlA <- filter(ctrp_data_ptmuts, Hugo_Symbol %in% genes_lvlA)
+```
+
+```{r, eval=FALSE}
+ctrp_signif_lvlA <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "Drug"), data = ctrp_data_lvlA, method = "wilcox.test", p.adjust.method = "BH")
+ctrp_signif_lvlA <- adj_signif(ctrp_signif_lvlA)
+ctrp_signif_lvlA <- ctrp_signif_lvlA[order(ctrp_signif_lvlA$p),]
+saveRDS(ctrp_signif_lvlA, "./data_munging/rds/ctrp_signif_lvlA_gene.rds")
+```
+
+```{r, eval=TRUE}
+ctrp_signif_lvlA <- readRDS("./data_munging/rds/ctrp_signif_lvlA_gene.rds")
+
+# ctrp_signif_genes_lvlA <- as.character(ctrp_signif_lvlA$Hugo_Symbol[0:20])
+
+knitr::kable(ctrp_signif_lvlA[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for Level A point mutations, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+```{r fig.height=4, fig.width=8}
+wilcox_ctrp_gene_lvlA_plot <- ggplot(data = ctrp_signif_lvlA) +
+  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
+  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
+  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
+  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
+  labs(x = "BH-adjusted p-values", y = "Frequency")
+wilcox_ctrp_gene_lvlA_plot
+```
+
+### GDSC: Gene and drug
+
+```{r}
+gdsc_data_ptmuts <- filter(gdsc_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
+gdsc_data_ptmuts$Keep_PtMut_Tests <- ifelse(gdsc_data_ptmuts$Reference_Allele_Length == 1 | is.na(gdsc_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(gdsc_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
+gdsc_data_ptmuts <- filter(gdsc_data_ptmuts, Keep_PtMut_Tests == TRUE)
+gdsc_data_lvlA <- filter(gdsc_data_ptmuts, Hugo_Symbol %in% genes_lvlA)
+```
+
+```{r, eval=FALSE}
+gdsc_signif_lvlA <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "Drug"), data = gdsc_data_lvlA, method = "wilcox.test", p.adjust.method = "BH")
+gdsc_signif_lvlA <- adj_signif(gdsc_signif_lvlA)
+gdsc_signif_lvlA <- gdsc_signif_lvlA[order(gdsc_signif_lvlA$p),]
+saveRDS(gdsc_signif_lvlA, "./data_munging/rds/gdsc_signif_lvlA_gene.rds")
+```
+
+```{r, eval=TRUE}
+gdsc_signif_lvlA <- readRDS("./data_munging/rds/gdsc_signif_lvlA_gene.rds")
+
+# gdsc_signif_genes_lvlA <- as.character(gdsc_signif_lvlA$Hugo_Symbol[0:20])
+
+knitr::kable(gdsc_signif_lvlA[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for Level A point mutations, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+```{r fig.height=4, fig.width=8}
+wilcox_gdsc_gene_lvlA_plot <- ggplot(data = gdsc_signif_lvlA) +
+  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
+  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
+  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
+  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
+  labs(x = "BH-adjusted p-values", y = "Frequency")
+wilcox_gdsc_gene_lvlA_plot
+```
+
+## Screen boxplots
 
 Mutation status boxplots for genes identified in G2P.
-
-```{r fig.height=4, fig.width=20}
-genes_lvlA_filt <- c("ABL1", "ALK", "AR", "ATM", "BRAF", "BRCA1", "BRCA2", "CDKN2A", "DNMT3A", "DPYD", "EGFR", "ERBB2", "ERBB3", "FGFR2", "FLT3", "JAK2", "KIT", "KRAS", "MET", "NOTCH1", "NOTCH2", "NRAS", "PDGFRA", "PDGFRB", "PIK3CA", "PML", "PTCH1", "RET", "ROS1", "SF3B1", "SMO", "TP53", "TSC1")
+```{r}
+genes_lvlA_filt <- c("KRAS", "EGFR", "MET", "ALK", "BRAF", "ERBB2", "ABL1", "ROS1", "KIT", "DPYD", "PDGFRA", "RET", "BRCA1", "UGT1A1", "IDH2", "ESR1", "TPMT", "BRCA2", "PDGFRB", "G6PD", "PML", "TSC1", "FLT3", "ERBB3", "CYP19A1", "AKT1", "PTCH1", "MGMT", "DNMT3A", "MYD88", "PDGFB", "TSC2", "NPM1", "JAK2")
+```
+
+### CRISPR
+
+```{r fig.height=7, fig.width=12}
 crispr_ptmuts_lvlA_filt <- filter(crispr_data_ptmuts, Hugo_Symbol %in% genes_lvlA_filt)
@@
 
-crispr_ptmuts_lvlA_filt_plot <- ggplot(data = crispr_ptmuts_lvlA_filt, aes(x = Hugo_Symbol, y = Score)) +
+crispr_ptmuts_lvlA_filt_plot_faceted <- ggplot(data = crispr_ptmuts_lvlA_filt, aes(x = Mutation_Status_Nonsilent, y = Score)) +
+  facet_wrap(~ Hugo_Symbol, drop = FALSE, ncol = length(genes_lvlA)) +
   geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
@@
   guides(color = FALSE) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.direction = "horizontal", legend.justification = c(0.5, 0), legend.position = c(0.092, 0.8), legend.box.margin = margin(c(10, 10, 10, 10))) +
-  labs(fill = "Mutation Status", y = "CERES Score", x = "Gene")
-crispr_ptmuts_lvlA_filt_plot
-# ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_filt_plot.png", crispr_ptmuts_lvlA_filt_plot, device = "png", width = 20, height = 6, units = "in")
-
-crispr_ptmuts_lvlA_filt_plot_faceted <- ggplot(data = crispr_ptmuts_lvlA_filt, aes(x = Mutation_Status_Nonsilent, y = Score)) +
-  facet_wrap(~ Hugo_Symbol, drop = FALSE, ncol = length(unique(genes_lvlA_filt))) +
-  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
-  geom_boxplot(mapping = aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85)) +
-  coord_cartesian(ylim = c(-3, 5)) +
-  scale_fill_manual(values = crispr_ptmuts_lvlA_filt_color) +
-  guides(color = FALSE) +
-  geom_text(data = label_text, mapping = aes(x = 1.5, y = 5, label = p.signif.adj)) +
-  theme(legend.direction = "horizontal", legend.justification = c(0.5, 0), legend.position = c(0.5, 0), legend.box.margin = margin(c(10, 10, 10, 10)), axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
+  geom_text(data = label_text, mapping = aes(x = 1.5, y = 2, label = p.signif.adj)) +
+  theme(legend.position = "top", axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
   labs(fill = "Mutation Status", y = "CERES Score", x = "Mutation Status")
 crispr_ptmuts_lvlA_filt_plot_faceted
-# ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_filt_plot_faceted.png", crispr_ptmuts_lvlA_filt_plot_faceted, device = "png", width = 20, height = 5, units = "in")
-
-crispr_ptmuts_lvlA_filt_plot_faceted_truncated <- ggplot(data = crispr_ptmuts_lvlA_filt, aes(x = Mutation_Status_Nonsilent, y = Score)) +
-  facet_wrap(~ Hugo_Symbol, drop = FALSE, ncol = length(unique(genes_lvlA_filt))) +
-  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
-  coord_cartesian(ylim = c(-2.5, 2.5)) +
-  geom_boxplot(aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85)) +
-  scale_fill_manual(values = crispr_ptmuts_lvlA_filt_color) +
-  geom_text(data = label_text, mapping = aes(x = 1.5, y = 2.5, label = p.signif.adj)) +
-  guides(color = FALSE) +
-  theme(legend.direction = "horizontal", legend.justification = c(0.5, 0), legend.position = c(0.5, 0), legend.box.margin = margin(c(10, 10, 10, 10)), axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
-  labs(fill = "Mutation Status", y = "CERES Score", x = "Mutation Status")
-crispr_ptmuts_lvlA_filt_plot_faceted_truncated
-# ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_filt_plot_faceted_truncated.png", crispr_ptmuts_lvlA_filt_plot_faceted_truncated, device = "png", width = 20, height = 5, units = "in")
-```
-
-```{r fig.height=5, fig.width=12}
-lvlA_genes_signif <- filter(crispr_data_ptmuts, Hugo_Symbol %in% crispr_signif_genes_lvlA)
-lvlA_genes_signif <- merge(lvlA_genes_signif, crispr_signif_lvlA, by = "Hugo_Symbol")
-lvlA_genes_signif$Hugo_Symbol <- ordered(lvlA_genes_signif$Hugo_Symbol, levels = crispr_signif_genes_lvlA)
-lvlA_genes_signif_color <- as.character(lvlA_genes_signif$Color_Nonsilent)
-names(lvlA_genes_signif_color) <- lvlA_genes_signif$Mutation_Status_Nonsilent
-lvlA_genes_signif <- merge(lvlA_genes_signif, lvlA_genes_signif %>% group_by(Hugo_Symbol) %>% summarize(Text_y = max(Score)), by = "Hugo_Symbol")
-
-lvlA_genes_text <- unique(data.frame(p.signif.adj = lvlA_genes_signif$p.signif.adj, Hugo_Symbol = lvlA_genes_signif$Hugo_Symbol, Text_y = lvlA_genes_signif$Text_y))
-lvlA_genes_text$Hugo_Symbol <- factor(lvlA_genes_text$Hugo_Symbol, levels = crispr_signif_genes_lvlA)
-
-lvlA_signif_genes_plot <- ggplot(data = lvlA_genes_signif, aes(x = Mutation_Status_Nonsilent, y = Score)) +
-  facet_wrap(~ Hugo_Symbol, nrow = 1, scales = "free_y") +
-  geom_jitter(aes(color = Mutation_Status_Nonsilent), alpha = 0.5, width = 0.3) +
-  geom_boxplot(color = "black", fill = NA, outlier.shape = NA) +
-  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
-  scale_color_manual(values = lvlA_genes_signif_color) + 
-  geom_text(data = lvlA_genes_text, mapping = aes(x = 1.5, y = Text_y, label = p.signif.adj), nudge_y = 0.2) +
-  theme(legend.position = "top") +
-  labs(y = "CERES Score",
-       x = "Lineage",
-       color = "Mutation Status",
-       title = "CERES scores for significant Level A G2P genes",
-       subtitle = "BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001\nGenes are sorted by increasing p-value.")
-lvlA_signif_genes_plot
-
-# ggsave("./plots_18Q3/manuscript/crispr_g2p_lvlA_signif_genes_plot.png", lvlA_signif_genes_plot, width = 12, height = 5, units = "in")
-```
-
-## Figure 1D plots
+# ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_filt_plot_faceted.png", crispr_ptmuts_lvlA_filt_plot_faceted, device = "png", dpi = 450, width = 20, height = 4, units = "in")
+```
+
+### CCLE
+
+```{r fig.height=4, fig.width=20}
+ccle_ptmuts_lvlA_filt <- filter(ccle_data_ptmuts, Hugo_Symbol %in% genes_lvlA_filt)
+ccle_ptmuts_lvlA_filt$Hugo_Symbol <- ordered(ccle_ptmuts_lvlA_filt$Hugo_Symbol, levels = genes_lvlA_filt)
+ccle_drugs <- as.character(unique(ccle_ptmuts_lvlA_filt$Drug))
+```
+
+Plot code:
+```{r, eval=FALSE}
+ccle_lvlA_drugboxplots <- lapply(ccle_drugs, makeDrugBoxplots, dataset = "CCLE")
+ccle_lvlA_drugboxplot_paths <- paste0(ccle_drugs, "_ccle_boxplots.png")
+pwalk(list(ccle_lvlA_drugboxplot_paths, ccle_lvlA_drugboxplots), ggsave, path = "./plots_18Q3/manuscript/ccle_lvlA_boxplots", dpi = 450, width = 20, height = 4, units = "in")
+```
+
+Data management:
+```{r, eval=TRUE}
+ccle_lvlA_drugboxplots <- paste0(list.files("./plots_18Q3/manuscript/ccle_lvlA_boxplots", full.names = TRUE))
+names(ccle_lvlA_drugboxplots) <- str_replace_all(ccle_lvlA_drugboxplots, c("_ccle_boxplots.png" = "", "./plots_18Q3/manuscript/ccle_lvlA_boxplots/" = ""))
+bsselect(ccle_lvlA_drugboxplots, type = "img", live_search = TRUE, show_tick = TRUE, height = 300, frame_height = 275)
+```
+
+### CTRP
+
+```{r fig.height=4, fig.width=20}
+ctrp_ptmuts_lvlA_filt <- filter(ctrp_data_ptmuts, Hugo_Symbol %in% genes_lvlA_filt)
+ctrp_ptmuts_lvlA_filt$Hugo_Symbol <- ordered(ctrp_ptmuts_lvlA_filt$Hugo_Symbol, levels = genes_lvlA_filt)
+ctrp_drugs <- as.character(unique(ctrp_ptmuts_lvlA_filt$Drug))
+```
+
+Plot code:
+```{r, eval=FALSE}
+ctrp_lvlA_drugboxplots <- lapply(ctrp_drugs, makeDrugBoxplots, dataset = "CTRP")
+ctrp_lvlA_drugboxplot_paths <- paste0(ctrp_drugs, "_ctrp_boxplots.png")
+pwalk(list(ctrp_lvlA_drugboxplot_paths, ctrp_lvlA_drugboxplots), ggsave, path = "./plots_18Q3/manuscript/ctrp_lvlA_boxplots", dpi = 450, width = 20, height = 4, units = "in")
+```
+
+Data management:
+```{r, eval=TRUE}
+ctrp_lvlA_drugboxplots <- paste0(list.files("./plots_18Q3/manuscript/ctrp_lvlA_boxplots", full.names = TRUE))
+names(ctrp_lvlA_drugboxplots) <- str_replace_all(ctrp_lvlA_drugboxplots, c("_ctrp_boxplots.png" = "", "./plots_18Q3/manuscript/ctrp_lvlA_boxplots/" = ""))
+bsselect(ctrp_lvlA_drugboxplots, type = "img", live_search = TRUE, show_tick = TRUE, height = 300, frame_height = 275)
+```
+
+### GDSC
+
+```{r fig.height=4, fig.width=20}
+gdsc_ptmuts_lvlA_filt <- filter(gdsc_data_ptmuts, Hugo_Symbol %in% genes_lvlA_filt)
+gdsc_ptmuts_lvlA_filt$Hugo_Symbol <- ordered(gdsc_ptmuts_lvlA_filt$Hugo_Symbol, levels = genes_lvlA_filt)
+gdsc_drugs <- as.character(unique(gdsc_ptmuts_lvlA_filt$Drug))
+```
+
+Plot code:
+```{r, eval=FALSE}
+gdsc_lvlA_drugboxplots <- lapply(gdsc_drugs, makeDrugBoxplots, dataset = "GDSC")
+gdsc_lvlA_drugboxplot_paths <- paste0(gdsc_drugs, "_gdsc_boxplots.png")
+pwalk(list(gdsc_lvlA_drugboxplot_paths, gdsc_lvlA_drugboxplots), ggsave, path = "./plots_18Q3/manuscript/gdsc_lvlA_boxplots", dpi = 450, width = 20, height = 4, units = "in")
+```
+
+Data management:
+```{r, eval=TRUE}
+gdsc_lvlA_drugboxplots <- paste0(list.files("./plots_18Q3/manuscript/gdsc_lvlA_boxplots", full.names = TRUE))
+names(gdsc_lvlA_drugboxplots) <- str_replace_all(gdsc_lvlA_drugboxplots, c("_gdsc_boxplots.png" = "", "./plots_18Q3/manuscript/gdsc_lvlA_boxplots/" = ""))
+bsselect(gdsc_lvlA_drugboxplots, type = "img", live_search = TRUE, show_tick = TRUE, height = 300, frame_height = 275)
+```
+
+## CRISPR: Point mutation mapping
 
 Match specific point mutations.
-
 ```{r fig.height=5, fig.width=20}
@@
 
-```{r}
-g2pA <- read.delim("./data_munging/g2p_full_level_A_dataset_v2_10_10_2018.csv", sep = "\t", header = TRUE, na.strings = "-1", quote = "")
-# g2pA[g2pA == "-1"] <- NA
-g2pA$X <- NULL
-
-g2pA_JSON <- data.frame(JSON = g2pA$JSON)
-
-g2pA_noJSON <- g2pA
-g2pA_noJSON$JSON <- NULL
-
-# write.table(g2pA, file = "./data_munging/g2p_full_level_A_dataset_v2_10_10_2018.tsv", quote = FALSE, sep = "\t", row.names = FALSE)
-# write.table(g2pA_noJSON, file = "./data_munging/g2pA_noJSON_v2_10_10_2018.tsv", quote = FALSE, sep = "\t", row.names = FALSE)
-# write.table(g2pA_JSON, file = "./data_munging/g2pA_JSON_v2_10_10_2018.tsv", quote = FALSE, sep = "\t", row.names = FALSE)
-```
-
 ## Level A: Per-gene grouped plots
@@
 
-## All genes: Per-gene grouped plots
-
-Plot code:
-```{r, eval=FALSE}
-crispr_all_groups <- lapply(unique(crispr_data_ptmuts$Hugo_Symbol), makeCRISPRgrob, filt_method = "all")
-crispr_all_groups_paths <- paste0(unique(crispr_data_ptmuts$Hugo_Symbol), "_crispr_grouped.png")
-pwalk(list(crispr_lvlA_groups_paths, crispr_lvlA_groups), ggsave, path = "./plots_18Q3/crispr_grouped_plots", dpi = 300, width = 12, height = 12, units = "in")
-```
-
-Data management:
-```{r, eval=TRUE}
-crispr_all_bygene <- paste0(list.files("./plots_18Q3/crispr_grouped_plots", full.names = TRUE))
-names(crispr_all_bygene) <- str_replace_all(crispr_all_bygene, c("_crispr_grouped.png" = "", "./plots_18Q3/crispr_grouped_plots_lvlA/" = ""))
-crispr_all_order <- c(intersect(crispr_signif_nonsilent$Hugo_Symbol, names(crispr_all_bygene)), setdiff(names(crispr_all_bygene), crispr_signif_nonsilent$Hugo_Symbol))
-crispr_all_bygene <- crispr_all_bygene[match(crispr_all_order, names(crispr_all_bygene))]
-bsselect(crispr_all_bygene, type = "img", selected = "KRAS", live_search = TRUE, show_tick = TRUE, height = 300, frame_height = 275)
-```
-
-## JSON
+<!-- ## All genes: Per-gene grouped plots -->
+
+<!-- Plot code: -->
+<!-- ```{r, eval=FALSE} -->
+<!-- crispr_all_groups <- lapply(unique(crispr_data_ptmuts$Hugo_Symbol), makeCRISPRgrob, filt_method = "all") -->
+<!-- crispr_all_groups_paths <- paste0(unique(crispr_data_ptmuts$Hugo_Symbol), "_crispr_grouped.png") -->
+<!-- pwalk(list(crispr_lvlA_groups_paths, crispr_lvlA_groups), ggsave, path = "./plots_18Q3/crispr_grouped_plots", dpi = 300, width = 12, height = 12, units = "in") -->
+<!-- ``` -->
+
+<!-- Data management: -->
+<!-- ```{r, eval=FALSE} -->
+<!-- crispr_all_bygene <- paste0(list.files("./plots_18Q3/crispr_grouped_plots", full.names = TRUE)) -->
+<!-- names(crispr_all_bygene) <- str_replace_all(crispr_all_bygene, c("_crispr_grouped.png" = "", "./plots_18Q3/crispr_grouped_plots_lvlA/" = "")) -->
+<!-- crispr_all_order <- c(intersect(crispr_signif_nonsilent$Hugo_Symbol, names(crispr_all_bygene)), setdiff(names(crispr_all_bygene), crispr_signif_nonsilent$Hugo_Symbol)) -->
+<!-- crispr_all_bygene <- crispr_all_bygene[match(crispr_all_order, names(crispr_all_bygene))] -->
+<!-- bsselect(crispr_all_bygene, type = "img", selected = "KRAS", live_search = TRUE, show_tick = TRUE, height = 300, frame_height = 275) -->
+<!-- ``` -->
+
+## JSON testing
+
+```{r}
+g2pA <- read.delim("./data_munging/g2p_full_level_A_dataset_v2_10_10_2018.csv", sep = "\t", header = TRUE, na.strings = "-1", quote = "")
+# g2pA[g2pA == "-1"] <- NA
+g2pA$X <- NULL
+
+g2pA_JSON <- data.frame(JSON = g2pA$JSON)
+
+g2pA_noJSON <- g2pA
+g2pA_noJSON$JSON <- NULL
+
+# write.table(g2pA, file = "./data_munging/g2p_full_level_A_dataset_v2_10_10_2018.tsv", quote = FALSE, sep = "\t", row.names = FALSE)
+# write.table(g2pA_noJSON, file = "./data_munging/g2pA_noJSON_v2_10_10_2018.tsv", quote = FALSE, sep = "\t", row.names = FALSE)
+# write.table(g2pA_JSON, file = "./data_munging/g2pA_JSON_v2_10_10_2018.tsv", quote = FALSE, sep = "\t", row.names = FALSE)
+```
 
@@
 
-## Lineages
-
-```{r fig.height=15, fig.width=12}
-lvlA_signif <- filter(crispr_data_ptmuts, Hugo_Symbol %in% crispr_signif_genes_lvlA)
-lvlA_signif <- merge(lvlA_signif, crispr_signif_lvlA_lineage, by = c("Hugo_Symbol", "group_general_lineage_name"))
-lvlA_signif$Hugo_Symbol <- ordered(lvlA_signif$Hugo_Symbol, levels = crispr_signif_genes_lvlA)
-lvlA_signif_color <- as.character(lvlA_signif$Color_Nonsilent)
-names(lvlA_signif_color) <- lvlA_signif$Mutation_Status_Nonsilent
-lvlA_signif <- merge(lvlA_signif, lvlA_signif %>% group_by(Hugo_Symbol) %>% summarize(Text_y = max(Score)), by = "Hugo_Symbol")
-
-lvlA_text <- unique(data.frame(p.signif.adj = lvlA_signif$p.signif.adj, group_general_lineage_name = lvlA_signif$group_general_lineage_name, Hugo_Symbol = lvlA_signif$Hugo_Symbol, Text_y = lvlA_signif$Text_y))
-lvlA_text$Hugo_Symbol <- factor(lvlA_text$Hugo_Symbol, levels = crispr_signif_genes_lvlA)
-
-lvlA_signif_lineages_plot <- ggplot(data = lvlA_signif, aes(x = group_general_lineage_name, y = Score)) +
-  facet_wrap(~ Hugo_Symbol, nrow = 4, scales = "free_y") +
-  geom_point(aes(color = Mutation_Status_Nonsilent), alpha = 0.5) +
-  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
-  scale_color_manual(values = lvlA_signif_color) +
-  geom_text(data = lvlA_text, mapping = aes(x = group_general_lineage_name, y = Text_y, label = p.signif.adj), nudge_y = 0.1) +
-  theme(legend.position = "top", axis.text.x = element_text(angle = 65, hjust = 1, vjust = 1, size = 10)) +
-  labs(y = "CERES Score",
-       x = "Lineage",
-       color = "Mutation Status",
-       title = "CERES score by cell line lineage for significant Level A G2P genes",
-       subtitle = "BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001\nGenes are sorted by increasing lineage-agnostic p-value.")
-lvlA_signif_lineages_plot
-
-# ggsave("./plots_18Q3/manuscript/crispr_g2p_lvlA_signif_lineages_plot.png", lvlA_signif_lineages_plot, width = 12, height = 15, units = "in")
-```
-
-```{r}
-lvlA_signif_summ <- lvlA_signif %>% group_by(Hugo_Symbol, group_general_lineage_name, Mutation_Status_Nonsilent) %>% tally()
-lvlA_signif_summ
-# write.table(lvlA_signif_summ, file = "~/Desktop/lvlA_signif_summ_20181005.tsv", quote = FALSE, sep = "\t")
-```
-
 # Heatmaps
@@
 
-```{r}
+```{r, eval=FALSE}
 tissue_summ <- crispr_meta %>% group_by(primary_tissue) %>% tally()
@@
 
-```{r fig.height=12, fig.width=3}
+```{r fig.height=12, fig.width=3, eval=FALSE}
 ggplot(data = tissue_summ) + 

### 2018-10-17 lineages_18Q3.Rmd

@@
 
+## Wilcoxon tests by drug
+
+```{r}
+WilcoxonByDrug <- function(drug, dataset, data_name) {
+  use_data <- filter(dataset, Drug == drug)
+  sig <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = "Hugo_Symbol", data = use_data, method = "wilcox.test", p.adjust.method = "BH")
+  sig <- adj_signif(sig)
+  sig <- sig[order(sig$p),]
+  sig$Drug <- drug
+  sig$Dataset <- data_name
+  return(sig)
+}
+```
+
 ## Make drug screen boxplots
@@
     names(use_color) <- use_data$Mutation_Status_Nonsilent
-    sig <- filter(ccle_signif_lvlA, Drug == drug)
+    sig <- ccle_signif_lvlA_ByDrug[[drug]]
+    # sig <- filter(ccle_signif_lvlA, Drug == drug)
     label_text <- data.frame(p.signif.adj = sig$p.signif.adj, Hugo_Symbol = sig$Hugo_Symbol)
@@
     names(use_color) <- use_data$Mutation_Status_Nonsilent
-    sig <- filter(ctrp_signif_lvlA, Drug == drug)
+    sig <- ctrp_signif_lvlA_ByDrug[[drug]]
+    # sig <- filter(ctrp_signif_lvlA, Drug == drug)
     label_text <- data.frame(p.signif.adj = sig$p.signif.adj, Hugo_Symbol = sig$Hugo_Symbol)
@@
     names(use_color) <- use_data$Mutation_Status_Nonsilent
-    sig <- filter(gdsc_signif_lvlA, Drug == drug)
+    sig <- gdsc_signif_lvlA_ByDrug[[drug]]
+    # sig <- filter(gdsc_signif_lvlA, Drug == drug)
     label_text <- data.frame(p.signif.adj = sig$p.signif.adj, Hugo_Symbol = sig$Hugo_Symbol)
@@
 ```{r, eval=FALSE}
+ccle_signif_lvlA_ByDrug <- lapply(unique(ccle_data_lvlA$Drug), WilcoxonByDrug, dataset = ccle_data_lvlA, data_name = "CCLE")
+names(ccle_signif_lvlA_ByDrug) <- unique(ccle_data_lvlA$Drug)
+saveRDS(ccle_signif_lvlA_ByDrug, "./data_munging/rds/ccle_signif_lvlA_ByDrug.rds")
+
 ccle_signif_lvlA <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = c("Drug", "Hugo_Symbol"), data = ccle_data_lvlA, method = "wilcox.test", p.adjust.method = "BH")
@@
 
-# ccle_signif_genes_lvlA <- as.character(ccle_signif_lvlA$Hugo_Symbol[0:20])
-
 knitr::kable(ccle_signif_lvlA[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for Level A point mutations, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+```{r}
+ccle_signif_lvlA_ByDrug <- readRDS("./data_munging/rds/ccle_signif_lvlA_ByDrug.rds")
+ccle_signif_lvlA_ByDrug_all <- rbindlist(ccle_signif_lvlA_ByDrug, use.names = TRUE)
+ccle_signif_lvlA_ByDrug_all <- ccle_signif_lvlA_ByDrug_all[order(ccle_signif_lvlA_ByDrug_all$p.adj),]
+
+knitr::kable(ccle_signif_lvlA_ByDrug_all[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: by-drug Wilcoxon test results for Level A point mutations, (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 ```{r, eval=FALSE}
-ctrp_signif_lvlA <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "Drug"), data = ctrp_data_lvlA, method = "wilcox.test", p.adjust.method = "BH")
+ctrp_signif_lvlA_ByDrug <- lapply(unique(ctrp_data_lvlA$Drug), WilcoxonByDrug, dataset = ctrp_data_lvlA, data_name = "CTRP")
+names(ctrp_signif_lvlA_ByDrug) <- unique(ctrp_data_lvlA$Drug)
+saveRDS(ctrp_signif_lvlA_ByDrug, "./data_munging/rds/ctrp_signif_lvlA_ByDrug.rds")
+
+ctrp_signif_lvlA <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = c("Drug", "Hugo_Symbol"), data = ctrp_data_lvlA, method = "wilcox.test", p.adjust.method = "BH")
 ctrp_signif_lvlA <- adj_signif(ctrp_signif_lvlA)
@@
 
-# ctrp_signif_genes_lvlA <- as.character(ctrp_signif_lvlA$Hugo_Symbol[0:20])
-
 knitr::kable(ctrp_signif_lvlA[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for Level A point mutations, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+```{r}
+ctrp_signif_lvlA_ByDrug <- readRDS("./data_munging/rds/ctrp_signif_lvlA_ByDrug.rds")
+ctrp_signif_lvlA_ByDrug_all <- rbindlist(ctrp_signif_lvlA_ByDrug, use.names = TRUE)
+ctrp_signif_lvlA_ByDrug_all <- ctrp_signif_lvlA_ByDrug_all[order(ctrp_signif_lvlA_ByDrug_all$p.adj),]
+
+knitr::kable(ctrp_signif_lvlA_ByDrug_all[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: by-drug Wilcoxon test results for Level A point mutations, (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 ```{r, eval=FALSE}
-gdsc_signif_lvlA <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "Drug"), data = gdsc_data_lvlA, method = "wilcox.test", p.adjust.method = "BH")
+gdsc_signif_lvlA_ByDrug <- lapply(unique(gdsc_data_lvlA$Drug), WilcoxonByDrug, dataset = gdsc_data_lvlA, data_name = "GDSC")
+names(gdsc_signif_lvlA_ByDrug) <- unique(gdsc_data_lvlA$Drug)
+saveRDS(gdsc_signif_lvlA_ByDrug, "./data_munging/rds/gdsc_signif_lvlA_ByDrug.rds")
+
+gdsc_signif_lvlA <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = c("Drug", "Hugo_Symbol"), data = gdsc_data_lvlA, method = "wilcox.test", p.adjust.method = "BH")
 gdsc_signif_lvlA <- adj_signif(gdsc_signif_lvlA)
@@
 
-# gdsc_signif_genes_lvlA <- as.character(gdsc_signif_lvlA$Hugo_Symbol[0:20])
-
 knitr::kable(gdsc_signif_lvlA[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for Level A point mutations, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+```{r}
+gdsc_signif_lvlA_ByDrug <- readRDS("./data_munging/rds/gdsc_signif_lvlA_ByDrug.rds")
+gdsc_signif_lvlA_ByDrug_all <- rbindlist(gdsc_signif_lvlA_ByDrug, use.names = TRUE)
+gdsc_signif_lvlA_ByDrug_all <- gdsc_signif_lvlA_ByDrug_all[order(gdsc_signif_lvlA_ByDrug_all$p.adj),]
+
+knitr::kable(gdsc_signif_lvlA_ByDrug_all[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: by-drug Wilcoxon test results for Level A point mutations, (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
-```{r fig.height=7, fig.width=12}
+```{r fig.height=4, fig.width=20}
 crispr_ptmuts_lvlA_filt <- filter(crispr_data_ptmuts, Hugo_Symbol %in% genes_lvlA_filt)

### 2018-10-18 18Q3.Rmd

--- 2018-10-17 lineages_18Q3.Rmd
@@
 
-In a previous version of the shRNA screen, DEMETER ([GitHub](https://github.com/cancerdatasci/demeter)) was used to compute a dependency score for each gene by using the depletion values from each shRNA to infer the effect of target knockdown (on-target) and of expressing a given miRNA seed (off-target) in each cell line.
+All annotation files (copy number, mutation status, and gene expression) (Consortium and Consortium 2015, Barretina et al.
+2012) were downloaded from the [DepMap Data Portal](https://depmap.org/portal/download/).
+
+```{r, include=FALSE, eval=FALSE}
+# In a previous version of the shRNA screen, DEMETER ([GitHub](https://github.com/cancerdatasci/demeter)) was used to compute a dependency score for each gene by using the depletion values from each shRNA to infer the effect of target knockdown (on-target) and of expressing a given miRNA seed (off-target) in each cell line.
 More negative values indicate increased dependency, while more positive values indicate lower dependency.
 Zero represents the avergae dependency across all cell lines.
-
-In the new data release, [DEMETER2](https://depmap.org/R2-D2/) ([GitHub repository](https://github.com/cancerdatasci/demeter2)), developed by McFarland et al.
+# 
+# In the new data release, [DEMETER2](https://depmap.org/R2-D2/) ([GitHub repository](https://github.com/cancerdatasci/demeter2)), developed by McFarland et al.
 (2018) was used to analyze the Achilles screen.
@@
 Now, a score of zero represents no dependency.
-
-All annotation files (copy number, mutation status, and gene expression) (Consortium and Consortium 2015, Barretina et al.
-2012) were downloaded from the [DepMap Data Portal](https://depmap.org/portal/download/).
+```
 
@@
   plot <- ggplot(data = use_data, aes(x = Mutation_Status_Nonsilent, y = AUC)) +
-    facet_wrap(~ Hugo_Symbol, drop = FALSE, ncol = length(genes_lvlA_filt)) +
-    geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
+    facet_wrap(~ Hugo_Symbol, drop = FALSE, nrow = 2) +
+               # ncol = length(genes_lvlA_filt)) +
     geom_boxplot(mapping = aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85)) +
@@
     guides(color = FALSE) +
-    geom_text(data = label_text, mapping = aes(x = 1.5, y = max(use_data$AUC), label = p.signif.adj)) +
+    geom_text(data = label_text, mapping = aes(x = 1.5, y = max(use_data$AUC), label = p.signif.adj), nudge_y = 0.2) +
     theme(legend.position = "top", axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
@@
 gdsc_data <- filter(gdsc_data, !is.na(gdsc_data$AUC))
-saveRDS(gdsc_data, "./data_munging/rds/ctrp_data_18Q3.rds", compress = "xz")
+saveRDS(gdsc_data, "./data_munging/rds/gdsc_data_18Q3.rds", compress = "xz")
 ```
@@
 
-```{r fig.height=4, fig.width=20}
+```{r fig.height=7, fig.width=12}
 crispr_ptmuts_lvlA_filt <- filter(crispr_data_ptmuts, Hugo_Symbol %in% genes_lvlA_filt)
@@
 crispr_ptmuts_lvlA_filt_plot_faceted <- ggplot(data = crispr_ptmuts_lvlA_filt, aes(x = Mutation_Status_Nonsilent, y = Score)) +
-  facet_wrap(~ Hugo_Symbol, drop = FALSE, ncol = length(genes_lvlA)) +
+  facet_wrap(~ Hugo_Symbol, drop = FALSE, nrow = 2) +
+             # ncol = length(genes_lvlA)) +
   geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
@@
   guides(color = FALSE) +
-  geom_text(data = label_text, mapping = aes(x = 1.5, y = 2, label = p.signif.adj)) +
+  geom_text(data = label_text, mapping = aes(x = 1.5, y = 2, label = p.signif.adj), nudge_y = 0.1) +
   theme(legend.position = "top", axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
@@
 ```{r fig.height=4, fig.width=20}
-ccle_ptmuts_lvlA_filt <- filter(ccle_data_ptmuts, Hugo_Symbol %in% genes_lvlA_filt)
+ccle_ptmuts_lvlA_filt <- filter(ccle_data_lvlA, Hugo_Symbol %in% genes_lvlA_filt)
 ccle_ptmuts_lvlA_filt$Hugo_Symbol <- ordered(ccle_ptmuts_lvlA_filt$Hugo_Symbol, levels = genes_lvlA_filt)
@@
 ccle_lvlA_drugboxplot_paths <- paste0(ccle_drugs, "_ccle_boxplots.png")
-pwalk(list(ccle_lvlA_drugboxplot_paths, ccle_lvlA_drugboxplots), ggsave, path = "./plots_18Q3/manuscript/ccle_lvlA_boxplots", dpi = 450, width = 20, height = 4, units = "in")
+pwalk(list(ccle_lvlA_drugboxplot_paths, ccle_lvlA_drugboxplots), ggsave, path = "./plots_18Q3/manuscript/ccle_lvlA_boxplots", dpi = 450, width = 12, height = 7, units = "in")
 ```
@@
 ```{r fig.height=4, fig.width=20}
-ctrp_ptmuts_lvlA_filt <- filter(ctrp_data_ptmuts, Hugo_Symbol %in% genes_lvlA_filt)
+ctrp_ptmuts_lvlA_filt <- filter(ctrp_data_lvlA, Hugo_Symbol %in% genes_lvlA_filt)
 ctrp_ptmuts_lvlA_filt$Hugo_Symbol <- ordered(ctrp_ptmuts_lvlA_filt$Hugo_Symbol, levels = genes_lvlA_filt)
@@
 ctrp_lvlA_drugboxplot_paths <- paste0(ctrp_drugs, "_ctrp_boxplots.png")
-pwalk(list(ctrp_lvlA_drugboxplot_paths, ctrp_lvlA_drugboxplots), ggsave, path = "./plots_18Q3/manuscript/ctrp_lvlA_boxplots", dpi = 450, width = 20, height = 4, units = "in")
+pwalk(list(ctrp_lvlA_drugboxplot_paths, ctrp_lvlA_drugboxplots), ggsave, path = "./plots_18Q3/manuscript/ctrp_lvlA_boxplots", dpi = 450, width = 12, height = 7, units = "in")
 ```
@@
 ```{r fig.height=4, fig.width=20}
-gdsc_ptmuts_lvlA_filt <- filter(gdsc_data_ptmuts, Hugo_Symbol %in% genes_lvlA_filt)
+gdsc_ptmuts_lvlA_filt <- filter(gdsc_data_lvlA, Hugo_Symbol %in% genes_lvlA_filt)
 gdsc_ptmuts_lvlA_filt$Hugo_Symbol <- ordered(gdsc_ptmuts_lvlA_filt$Hugo_Symbol, levels = genes_lvlA_filt)
@@
 gdsc_lvlA_drugboxplot_paths <- paste0(gdsc_drugs, "_gdsc_boxplots.png")
-pwalk(list(gdsc_lvlA_drugboxplot_paths, gdsc_lvlA_drugboxplots), ggsave, path = "./plots_18Q3/manuscript/gdsc_lvlA_boxplots", dpi = 450, width = 20, height = 4, units = "in")
+pwalk(list(gdsc_lvlA_drugboxplot_paths, gdsc_lvlA_drugboxplots), ggsave, path = "./plots_18Q3/manuscript/gdsc_lvlA_boxplots", dpi = 450, width = 12, height = 7, units = "in")
 ```
@@
 Match specific point mutations.
-```{r fig.height=5, fig.width=20}
+```{r fig.height=5, fig.width=20, eval=FALSE}
 g2p_indications <- filter(read.delim("./data_munging/data_mutation_associations_appended.csv", sep = "\t", header = TRUE), Evidence.Level == "A")
 maf_g2p_indications <- filter(maf_raw, Genome_Change %in% g2p_indications$MutationName)
-crispr_g2p_indications <- merge(maf_g2p_indications, crispr_data_ptmuts, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"))
+crispr_g2p_indications <- merge(crispr_data_ptmuts, maf_g2p_indications, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
+crispr_g2p_indications$Mutation_Status_Nonsilent <- ifelse(is.na(crispr_g2p_indications$Mutation_Status_Nonsilent), "Other", crispr_g2p_indications$Mutation_Status_Nonsilent)
 dup_g2p_indications <- filter(crispr_g2p_indications[, c("Hugo_Symbol", "CCLE_Name", "Broad_ID")] %>% group_by(Hugo_Symbol, CCLE_Name, Broad_ID) %>% tally(), n > 1)
-crispr_g2p_indications <- merge(crispr_g2p_indications, dup_g2p_indications, by = c("Hugo_Symbol", "Broad_ID"), all.x = TRUE)
-crispr_g2p_indications <- filter(crispr_g2p_indications, is.na(n))
+crispr_g2p_indications <- merge(crispr_g2p_indications, dup_g2p_indications, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
+crispr_g2p_indications$Genome_Change <- factor(crispr_g2p_indications$Genome_Change, levels = unique(crispr_g2p_indications$Genome_Change))
+crispr_g2p_indications_nonNA <- filter(crispr_g2p_indications, is.na(n))
 
@@
   geom_boxplot(alpha = 0.5, color = "lightgray", outlier.shape = NA) +
-  geom_jitter(width = 0.3, mapping = aes(color = group_general_lineage_name), size = 1) +
+  geom_jitter(width = 0.3, mapping = aes(color = Mutation_Status_Nonsilent), size = 1) +
   theme_light() +
@@
   geom_boxplot(alpha = 0.5, color = "lightgray", outlier.shape = NA) +
-  geom_jitter(width = 0.1, mapping = aes(color = group_general_lineage_name), size = 1) +
+  geom_jitter(width = 0.1, mapping = aes(color = Mutation_Status_Nonsilent), size = 1) +
   theme_light() +

### 2018-10-19 manuscript.Rmd
initiated Rmd for manuscript analyses

--- 2018-10-16 lineages_18Q3.Rmd
@@
 ---
-title: "Lineage Analysis of CRISPR and shRNA Screens"
+title: "Manuscript"
 author: "Sally Claridge"
@@
 ```
-
-Load libraries.
-```{r}
-library(broom)
-library(bsselectR)
-library(caret)
-library(CePa)
-library(circlize)
-library(ComplexHeatmap)
-library(data.table)
-library(devtools)
-library(ggpubr)
-library(ggsignif)
-library(ggfortify)
-library(ggord)
-library(glmnet)
-library(gridExtra)
-library(jsonlite)
-library(jsonlite)
-library(kableExtra)
-library(magrittr)
-library(matrixStats)
-library(NMF)
-library(parallel)
-library(plyr)
-library(reshape2)
-library(rowr)
-library(tidyverse)
-```
-
-# Functions {.tabset .tabset-fade .tabset-pills}
-
---------------------------------------------------------------------------------
-
-## Significance thresholding
-
-```{r}
-adj_signif <- function(df) {
-  # Takes df from compare_means and creates a signif code column for adjusted p-vals
-  df$p.signif <- ifelse(df$p.signif == "ns", NA, df$p.signif)
-  df$p.signif.adj <- ifelse(df$p.adj <= 0.0001, "****",
-                     ifelse(df$p.adj <= 0.001, "***",
-                     ifelse(df$p.adj <= 0.01, "**",
-                     ifelse(df$p.adj <= 0.05, "*", NA))))
-  df$p.short <- formatC(df$p, format = "g", digits =  2)
-  df$p.adj.short <- formatC(df$p.adj, format = "g", digits =  2)
-
-  return(df)
-}
-```
-
-## Make CRISPR grouped plots
-
-```{r}
-makeCRISPRgrob <- function(g, filt_method) {
-  if(filt_method == "lvlA") {
-    gene <- filter(crispr_data_lvlA, Hugo_Symbol == g)
-    sig <- filter(crispr_signif_lvlA, Hugo_Symbol == g)
-  }
-  if(filt_method == "all") {
-    gene <- filter(crispr_data_ptmuts, Hugo_Symbol == g)
-    sig <- filter(crispr_signif_nonsilent, Hugo_Symbol == g)
-  }
-
-  # Mutation status
-  crispr_color <- as.character(gene$Color_Nonsilent)
-  names(crispr_color) <- gene$Mutation_Status_Nonsilent
-
-  plot_mut <- ggplot(data = gene, aes(x = Mutation_Status_Nonsilent, y = Score, color = Mutation_Status_Nonsilent)) +
-    geom_boxplot(outlier.shape = NA) +
-    geom_jitter(alpha = 0.3, size = 0.7, position = position_jitter(w = 0.05)) +
-    scale_color_manual(values = crispr_color) +
-    geom_hline(yintercept = 0, linetype = 2, lwd = 0.3) +
-    theme_light() +
-    theme(legend.position = "none") +
-    labs(x = paste0(g, " Mutation Status"), y = "CERES Score",
-         title = "Mutation Status",
-         subtitle = paste0("Wilcoxon test:\n- BH-corrected p-value: ", sig$p.adj.short, "\n- Uncorrected p-value: ", sig$p.short))
-
-  # Copy number
-  lo_cn <- range(gene$Copy_Number[!is.na(gene$Copy_Number)])[1]
-  hi_cn <- range(gene$Copy_Number[!is.na(gene$Copy_Number)])[2]
-  mid_cn <- (hi_cn - lo_cn) / 2
-  plot_cn <- ggplot(data = gene, aes(x = Copy_Number, y = Score, color = Mutation_Status_Nonsilent)) +
-    geom_point(size = 0.5, alpha = 0.5) +
-    geom_smooth(method = "lm", size = 0.5) +
-    geom_hline(yintercept = 0, linetype = 2, lwd = 0.3) +
-    scale_color_manual(values = crispr_color) +
-    stat_cor(method = "pearson", show.legend = FALSE, label.x = c((lo_cn + mid_cn) / 2, (hi_cn - mid_cn) / 2 + mid_cn), label.y = max(gene$Score)) +
-    theme(legend.position = "none") +
-    labs(y = "CERES Score", color = "Mutation Status",
-         x = paste0(g, " Theoretical Copy number"), title = "Copy Number",
-         subtitle = "r: Pearson correlation coeffcient")
-
-  # Gene expression
-  lo_ge <- range(gene$RPKM_log2[!is.na(gene$RPKM_log2)])[1]
-  hi_ge <- range(gene$RPKM_log2[!is.na(gene$RPKM_log2)])[2]
-  mid_ge <- (hi_ge - lo_ge) / 2
-  plot_ge <- ggplot(data = gene, aes(x = RPKM_log2, y = Score, color = Mutation_Status_Nonsilent)) +
-    geom_point(size = 0.5, alpha = 0.5) +
-    geom_smooth(method = "lm", size = 0.5) +
-    geom_hline(yintercept = 0, linetype = 2, lwd = 0.3) +
-    scale_color_manual(values = crispr_color) +
-    stat_cor(method = "pearson", show.legend = FALSE, label.x = c((lo_ge + mid_ge) / 2, (hi_ge - mid_ge) / 2 + mid_ge), label.y = max(gene$Score)) +
-    theme(legend.position = "none") +
-    labs(y = "CERES Score", color = "Mutation Status",
-         x = paste0(g, " Gene Expression [log2(RPKM)]"),
-         title = "Gene Expression",
-         subtitle = "r: Pearson correlation coeffcient")
-
-  # Cell line lineage
-  plot_tissue <- ggplot(data = gene, aes(x = primary_tissue, y = Score, color = Mutation_Status_Nonsilent)) +
-    geom_point(alpha = 0.5) +
-    scale_color_manual(values = crispr_color) +
-    geom_hline(yintercept = 0, linetype = 2, lwd = 0.3) +
-    scale_y_continuous(sec.axis = sec_axis(~ .)) +
-    coord_flip() +
-    theme(legend.position = "none") +
-    labs(y = "CERES Score", x = "Primary Tissue",
-         color = "Mutation Status", title = g)
-
-  # Arrange plots
-  plot <- ggarrange(ggarrange(plot_tissue, nrow = 1, labels = c("A")),
-                    ggarrange(plot_mut, plot_cn, plot_ge, nrow = 3,
-                              labels = c("B", "C", "D"), heights = c(2, 3, 3)),
-                    font.label = list(size = 30, face = "bold"),
-                    nrow = 1, ncol = 2, widths = c(3, 2))
-  return(plot)
-}
-```
-
-## Make sorted lineage plots
-
-```{r}
-makeCRISPRlinplot <- function(g) {
-  sig <- filter(crispr_signif_lineage, Hugo_Symbol == g)
-  if(nrow(sig) == 0) {
-    return(NULL)
-  }
-  else {
-    gene <- filter(crispr_data, Hugo_Symbol == g)
-    gene <- merge(gene, sig, by = c("Hugo_Symbol", "group_general_lineage_name"))
-    gene <- mutate(gene, group_general_lineage_name = reorder(group_general_lineage_name, p, mean))
-    crispr_color <- as.character(gene$Color)
-    names(crispr_color) <- gene$Mutation_Status
-    score_range <- abs(range(gene$Score)[2] - range(gene$Score)[1])
-    round_accuracy <- ifelse(score_range <= 2, 0.25,
-                             ifelse(score_range <= 3, 0.5, 1.0))
-
-    plot <- ggplot(data = gene, aes(x = group_general_lineage_name, y = Score)) +
-      geom_point(alpha = 0.5, mapping = aes(color = Mutation_Status)) +
-      scale_color_manual(values = crispr_color) +
-      coord_cartesian(y = c(min(gene$Score), round_any(x = max(gene$Score), accuracy = round_accuracy, f = ceiling))) +
-      geom_signif(data = gene, mapping = aes(xmin = group_general_lineage_name, xmax = group_general_lineage_name, annotations = paste(p.short, "\n", p.adj.short), y_position = max(gene$Score)), manual = TRUE, tip_length   = 0, size = 0, textsize = 3) +
-      theme(legend.position = "top", axis.text.x = element_text(angle = 70, hjust = 1, size = 10)) +
-      labs(y = "CERES Score",
-           x = "Lineage",
-           color = "Mutation Status",
-           title = paste0(g, ": CERES score by cell line lineage"),
-           subtitle = "Lineages sorted by increasing p-value; labels indicate unadjusted p-value / BH-corrected p-value.\nMutant lines harbor deleterious mutations.")
-    return(plot)
-  }
-}
-```
-
-## Make drug screen boxplots
-```{r}
-makeDrugBoxplots <- function(drug, dataset) {
-  if(dataset == "CCLE" | dataset == "ccle") {
-    use_data <- filter(ccle_ptmuts_lvlA_filt, Drug == drug)
-    use_color <- as.character(use_data$Color_Nonsilent)
-    names(use_color) <- use_data$Mutation_Status_Nonsilent
-    sig <- filter(ccle_signif_lvlA, Drug == drug)
-    label_text <- data.frame(p.signif.adj = sig$p.signif.adj, Hugo_Symbol = sig$Hugo_Symbol)
-    label_text <- filter(label_text, Hugo_Symbol %in% genes_lvlA_filt)
-    label_text$Hugo_Symbol <- factor(label_text$Hugo_Symbol, levels = genes_lvlA_filt)
-  }
-  else if(dataset == "CTRP" | dataset == "ctrp") {
-    use_data <- filter(ctrp_ptmuts_lvlA_filt, Drug == drug)
-    use_color <- as.character(use_data$Color_Nonsilent)
-    names(use_color) <- use_data$Mutation_Status_Nonsilent
-    sig <- filter(ctrp_signif_lvlA, Drug == drug)
-    label_text <- data.frame(p.signif.adj = sig$p.signif.adj, Hugo_Symbol = sig$Hugo_Symbol)
-    label_text <- filter(label_text, Hugo_Symbol %in% genes_lvlA_filt)
-    label_text$Hugo_Symbol <- factor(label_text$Hugo_Symbol, levels = genes_lvlA_filt)
-  }
-  else if(dataset == "GDSC" | dataset == "gdsc") {
-    use_data <- filter(gdsc_ptmuts_lvlA_filt, Drug == drug)
-    use_color <- as.character(use_data$Color_Nonsilent)
-    names(use_color) <- use_data$Mutation_Status_Nonsilent
-    sig <- filter(gdsc_signif_lvlA, Drug == drug)
-    label_text <- data.frame(p.signif.adj = sig$p.signif.adj, Hugo_Symbol = sig$Hugo_Symbol)
-    label_text <- filter(label_text, Hugo_Symbol %in% genes_lvlA_filt)
-    label_text$Hugo_Symbol <- factor(label_text$Hugo_Symbol, levels = genes_lvlA_filt)
-  }
-  else { return("Error: Invalid dataset.") }
-
-  plot <- ggplot(data = use_data, aes(x = Mutation_Status_Nonsilent, y = AUC)) +
-    facet_wrap(~ Hugo_Symbol, drop = FALSE, ncol = length(genes_lvlA_filt)) +
-    geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
-    geom_boxplot(mapping = aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85)) +
-    scale_fill_manual(values = use_color) +
-    guides(color = FALSE) +
-    geom_text(data = label_text, mapping = aes(x = 1.5, y = max(use_data$AUC), label = p.signif.adj)) +
-    theme(legend.position = "top", axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
-    labs(fill = "Mutation Status", y = "AUC", x = "Mutation Status", title = paste0(dataset, ": ", drug))
-  return(plot)
-}
-```
-
-# Data management {.tabset .tabset-fade .tabset-pills}
-
---------------------------------------------------------------------------------
-
-## D. Charytonowicz cell line converter
-
-This comprehensive cancer cell line information curated by Daniel Charytonowicz.
-```{r}
-ccl_converter <- read.delim("./data_munging/cell_line_database_v1_20180911.tsv", row.names = 1, sep = "\t", header = TRUE)
-```
-
-```{r, eval=FALSE, include=FALSE}
-# Editing CCL DB
-# groupings <- read.delim("./data_munging/cell_line_database_completed_extra_grouped_doids_FINAL.csv", sep = "\t", header = TRUE)
-# groupings <- unique(select(groupings, lineage_name, grouped_general_doid, group_general_lineage_name))
-# ccl_converter <- read.delim("./data_munging/cell_line_database_FINAL_MASTER.tsv", sep = "\t", row.names = 1, header = TRUE)
-# colnames(ccl_converter)[colnames(ccl_converter) == "ccle_cell_line_name"] <- "CCLE_Name"
-# colnames(ccl_converter)[colnames(ccl_converter) == "broad_id"] <- "Broad_ID"
-# ccl_converter <- merge(ccl_converter, groupings, by = "lineage_name", all.x = TRUE)
-
-# Testing completeness of grouped lineage names
-unique(ccl_converter$group_general_lineage_name)
-test <- filter(ccl_converter, is.na(group_general_lineage_name))
-unique(test$lineage_name)
-test2 <- filter(ccl_converter, is.na(grouped_general_doid))
-```
-
-## CGC gene list
-
-Select genes from the Cancer Gene Census (CGC).
-The list was pulled from the [International Cancer Genome Consortium (ICGC) data portal](https://dcc.icgc.org/search/g?filters=%7B%22gene%22:%7B%22curatedSetId%22:%7B%22is%22:%5B%22GS1%22%5D%7D%7D%7D) (Advaced Search > Genes > Curated Gene Set > Cancer Gene Census).
-```{r}
-cgc <- data_frame("Hugo_Symbol" = read.delim("./data_munging/gene-ids-for-set-Cancer Gene Census.tsv", header = FALSE, sep = "\t")[, 2])
-```
-
-## DepMap cell line metadata
-
-```{r}
-ccl_info <- read.delim("./data_munging/DepMap-2018q3-celllines.csv", sep = ",", header = TRUE, na.strings = c("", NA))
-ccl_info$Primary.Disease <- gsub("\\\\", "", ccl_info$Primary.Disease)
-ccl_info$Primary.Disease <- gsub("Ewings", "Ewing's", ccl_info$Primary.Disease)
-
-# From figshare
-crispr_meta <- read.delim("./data_munging/sample_info_18Q3_crispr.csv", sep = ",", header = TRUE, na.strings = c("", NA))
-colnames(crispr_meta)[7] <- "CCLE_Name"
-```
-
-```{r, include=FALSE}
-dan_test <- select(ccl_converter, CCLE_Name, Broad_ID, cell_line_name)
-dan_test <- dan_test[-which(dan_test$CCLE_Name == ""), ]
-ccl_test <- select(ccl_info, CCLE_Name, Broad_ID)
-
-test <- merge(ccl_test, dan_test, by = "CCLE_Name", all = TRUE, suffixes = c("_DepMap", "_Daniel"))
-test$BroadIDs_match <- ifelse(as.character(test$Broad_ID_DepMap) == as.character(test$Broad_ID_Daniel), TRUE, FALSE)
-
-test_false <- filter(test, BroadIDs_match == FALSE)
-# write.table(ccl_converter, file = "~/Desktop/cell_line_database_v1_20180907.tsv", quote = FALSE, sep = "\t")
-```
-
-## Genomic annotations
-
-### CCLE MAF file
-
-For mutation calling, get paired gene name and cell line fields in a data frame.
-For this analysis, we don't care about how many mutations there are per gene or what type of mutations there are, so I didn't save more information.
-I took unique gene-cell line combinations since we only cared about mutation presence/absence.
-Add a `Mutation_Status` column denoting all entries in MAF files as mutations present in the associated cell lines.
-```{r}
-maf_raw <- read.delim("./data_munging/CCLE_DepMap_18q3_maf_20180718.txt.gz", header = TRUE, sep = "\t")
-# Filter for cell lines in CRISPR screen
-maf_raw <- filter(maf_raw, Broad_ID %in% unique(crispr_meta$Broad_ID))
-colnames(maf_raw)[colnames(maf_raw) == "Tumor_Sample_Barcode"] <- "CCLE_Name"
-
-# Select columns
-maf_df <- subset(maf_raw, select = c("Hugo_Symbol", "CCLE_Name", "Broad_ID", "Variant_Classification", "Reference_Allele", "Tumor_Seq_Allele1"))
-maf_df$Reference_Allele_Length <- ifelse(maf_df$Reference_Allele == "-", 0, nchar(as.character(maf_df$Reference_Allele)))
-maf_df$Tumor_Seq_Allele1_Length <- nchar(as.character(maf_df$Tumor_Seq_Allele1))
-
-# Add Mutation_Status column
-maf_df$Mutation_Status_Nonsilent <- ifelse(maf_df$Variant_Classification == "Silent", "Other", "Mutant")
-maf_df <- unique(subset(maf_df, select = c("Hugo_Symbol", "CCLE_Name", "Broad_ID", "Mutation_Status_Nonsilent", "Reference_Allele_Length", "Tumor_Seq_Allele1_Length")))
-
-# Whole MAF summary table
-maf_summ <- maf_raw[, c("Variant_Classification", "isDeleterious")] %>% group_by(Variant_Classification, isDeleterious) %>% tally()
-maf_summ$Percent <- format(round(maf_summ$n / sum(maf_summ$n) * 100, 4), nsmall = 2)
-maf_summ$isDeleterious <- ifelse(maf_summ$isDeleterious == "TRUE", "Yes", "No")
-
-knitr::kable(maf_summ, caption = "Distribution of variant classifications in the MAF file") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
-```
-
-```{r, eval=FALSE, include=FALSE}
-max(nchar(as.character(maf_raw$Reference_Allele)))
-maf_raw %>% group_by(Variant_Type, isTCGAhotspot) %>% tally()
-
-test <- filter(maf_raw, Hugo_Symbol == "KRAS")
-test %>% group_by(isDeleterious) %>% tally()
-```
-
-### CCLE copy number file
-
-```{r, eval=FALSE}
-cn <- read.delim("./data_munging/public_18Q3_gene_cn_v2.csv.gz", sep = ",", check.names = FALSE, header = TRUE)
-
-# Convert log2 ratios (log2(CN/2)) to CN
-cn[2:ncol(cn)] <- lapply(cn[2:ncol(cn)], function(x) 2 * (2 ^ x))
-
-# Remove Entrez gene IDs from colnames
-colnames(cn) <- gsub(" .*", "", colnames(cn))
-colnames(cn)[1] <- "Broad_ID"
-
-# Melt
-cn_melt <- melt(data = cn, id.vars = "Broad_ID", measure.vars = colnames(cn[2:ncol(cn)]), variable.name = "Hugo_Symbol", value.name = "Copy_Number")
-
-saveRDS(cn_melt, "./data_munging/rds/cn_melt_18Q3.rds", compress = "xz")
-```
-
-```{r, eval=FALSE}
-cn_melt <- readRDS("./data_munging/rds/cn_melt_18Q3.rds")
-```
-
-### CCLE gene expression file
-
-Gene expression data (Reads Per Kilobase of transcript, per Million mapped reads, RPKM).
-```{r, eval=FALSE}
-ge <- read.delim("./../crispr_lineages_giant_files/CCLE_DepMap_18q3_RNAseq_RPKM_20180718.gct.gz", skip = 2, header = TRUE, sep = "\t", check.names = FALSE)
-
-# Edit columns
-ge$Name <- NULL
-colnames(ge)[1] <- "Hugo_Symbol"
-
-# Melt
-ge_melt <- melt(data = ge, id.vars = "Hugo_Symbol", measure.vars = colnames(ge[2:ncol(ge)]), value.name = "RPKM")
-## Split variable column
-ge_melt <- with(ge_melt, cbind(Hugo_Symbol, colsplit(variable, pattern = " ", names = c("CCLE_Name", "Broad_ID")), RPKM))
-## Remove parentheses around Broad IDs
-ge_melt$Broad_ID <- gsub("\\(|\\)", "", ge_melt$Broad_ID)
-
-saveRDS(ge_melt, "./../crispr_lineages_giant_files/ge_melt_18Q3.rds", compress = "xz")
-```
-
-```{r, eval=FALSE}
-ge_melt <- readRDS("./../crispr_lineages_giant_files/ge_melt_18Q3.rds")
-```
-
-## CRISPR
-
-### DepMap dependency probabilities
-
-```{r, eval=FALSE}
-dep <- read.delim("./data_munging/gene_dependency_18Q3.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
-# Remove Entrez gene IDs from colnames
-colnames(dep) <- gsub(" .*", "", colnames(dep))
-```
-
-### Merge CRISPR data and annotations
-
-The latest CRISPR CERES score data (18Q3, August 2018) was pulled from the [DepMap Data Portal](https://depmap.org/portal/download/) (Broad Institute Cancer Dependency Map 2018, Meyers et al. 2017).
-```{r, eval=TRUE}
-crispr <- read.delim("./data_munging/gene_effect_18Q3.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
-# Remove Entrez gene IDs from colnames
-colnames(crispr) <- gsub(" .*", "", colnames(crispr))
-```
-
-Merge annotation data:
-```{r, eval=FALSE}
-# Melt CRISPR dataset for merging
-crispr_melt <- melt(crispr, id.vars = "Broad_ID", measure.vars = colnames(crispr)[2:ncol(crispr)], variable.name = "Hugo_Symbol", value.name = "Score")
-# Melt dependency probabilities dataset for merging
-dep_melt <- melt(dep, id.vars = "Broad_ID", measure.vars = colnames(dep)[2:ncol(dep)], variable.name = "Hugo_Symbol", value.name = "Dep_Prob")
-# Merge dependency probabilities
-crispr_melt <- merge(crispr_melt, dep_melt, by = c("Broad_ID", "Hugo_Symbol"), all.x = TRUE)
-# Merge cell line metadata
-crispr_melt <- merge(crispr_melt, ccl_info, by = "Broad_ID", all.x = TRUE)
-crispr_melt <- merge(crispr_melt, crispr_meta, by = c("CCLE_Name", "Broad_ID"), all.x = TRUE)
-# Merge mutation annotations
-crispr_muts <- merge(crispr_melt, maf_df, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
-crispr_muts$Hugo_Symbol <- factor(crispr_muts$Hugo_Symbol)
-crispr_muts <- crispr_muts %>% mutate(Mutation_Status_Nonsilent = if_else(is.na(Mutation_Status_Nonsilent), "Other", Mutation_Status_Nonsilent))
-# Summarize number of mutant and Other cell lines
-crispr_muts_summ <- crispr_muts %>% group_by(Hugo_Symbol) %>%
-  summarize(N_Nonsilent_Other = sum(Mutation_Status_Nonsilent == "Other"),
-            N_Nonsilent_Mutant = sum(Mutation_Status_Nonsilent == "Mutant"))
-# Merge test results back into full dataset, which restores information lost in the summarization
-crispr_data <- merge(crispr_muts_summ, crispr_muts, by = "Hugo_Symbol")
-# Add Color columns
-crispr_data$Color_Nonsilent <- ifelse(crispr_data$Mutation_Status_Nonsilent == "Other", "thistle", "darkorchid")
-crispr_data$Color_Nonsilent <- factor(crispr_data$Color_Nonsilent)
-# Cell line lineages
-crispr_data <- merge(crispr_data, ccl_converter, by = c("CCLE_Name", "Broad_ID"), all.x = TRUE)
-levels(crispr_data$lineage_name) <- sort(levels(crispr_data$lineage_name), decreasing = TRUE)
-# Copy number
-crispr_data <- merge(crispr_data, cn_melt, by = c("Hugo_Symbol", "Broad_ID"), all.x = TRUE)
-# Gene expression (RPKM)
-ge_filt <- filter(ge_melt, Hugo_Symbol %in% unique(crispr_data$Hugo_Symbol) & Broad_ID %in% unique(crispr_data$Broad_ID))
-crispr_data <- merge(crispr_data, ge_filt, by = c("Hugo_Symbol", "Broad_ID", "CCLE_Name"), all.x = TRUE)
-crispr_data$RPKM_log2 <- log2(crispr_data$RPKM + 0.0001)
-saveRDS(crispr_data, "./../crispr_lineages_giant_files/crispr_data_18Q3.rds", compress = "xz")
-```
-
-```{r}
-crispr_data <- readRDS("./../crispr_lineages_giant_files/crispr_data_18Q3.rds")
-crispr_ccl <- data.frame("Broad_ID" = crispr_data$Broad_ID)
-# write.table(crispr_data, file = "~/Desktop/crispr_data.tsv", quote = FALSE, sep = "\t")
-```
-
-```{r, eval=FALSE, include=FALSE}
-# Code for testing colors on plots
-test <- filter(crispr_data, Hugo_Symbol == "KRAS")
-ggplot(data = test, aes(x = Mutation_Status_Nonsilent, y = Score, fill = Mutation_Status_Nonsilent)) +
-  geom_boxplot() +
-  geom_jitter(aes(color = Mutation_Status_Nonsilent)) +
-  theme_light() +
-  scale_color_manual(values = c("turquoise4", "paleturquoise3")) +
-  scale_fill_manual(values = c("turquoise4", "paleturquoise3"))
-```
-
-```{r fig.height=12, fig.width=12, eval=FALSE, include=FALSE}
-# Test dimensional scaling
-crispr_pca_data <- merge(ccl_converter[, c("Broad_ID", "group_general_lineage_name")], crispr, by = "Broad_ID")
-crispr_lin <- crispr_pca_data[, 2]
-crispr_pca <- prcomp(data.matrix(crispr_pca_data[, 3:ncol(crispr_pca_data)]), scale. = TRUE, center = TRUE)
-plot(crispr_pca, type = "l")
-biplot(crispr_pca, obs.scale = 1, var.scale = 1, groups = crispr_lin, ellipse = TRUE, circle = TRUE)
-ggord(crispr_pca, crispr_pca_data$group_general_lineage_name)
-```
-
-## Drug screens
-
-```{r}
-g2p <- read.delim("./data_munging/g2p_full_level_A_dataset_v2_10_10_2018.tsv", sep = "\t", header = TRUE)
-genes_lvlA_df <- data.frame(Hugo_Symbol = unique(g2p$Gene))
-genes_lvlA <- unique(g2p$Gene)
-```
-
-```{r, eval=FALSE}
-# Drug metadata
-drug_meta <- read.delim("./data_munging/drug_id_drug_name_table_10_12_2018.tsv", sep = "\t", header = FALSE)
-colnames(drug_meta) <- c("CID", "Drug")
-drug_meta$Drug <- tolower(drug_meta$Drug)
-maf_df_lvlA <- filter(maf_df, Hugo_Symbol %in% genes_lvlA)
-
-# CCLE
-ccle <- read.delim("./data_munging/data_drug_auc_ccle_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
-ccle <- merge(drug_meta, ccle, by = "CID")
-ccle_melt <- melt(ccle, id.vars = c("CID", "Drug"), measure.vars = colnames(ccle)[3:ncol(ccle)], variable.name = "accession_id", value.name = "AUC")
-ccle_grid <- expand.grid("accession_id" = unique(ccle_melt$accession_id), "Hugo_Symbol" = genes_lvlA)
-ccle_data <- merge(ccle_grid, ccle_melt, by = "accession_id", all.x = TRUE)
-ccle_data <- merge(ccle_data, ccl_converter, by = "accession_id", all.x = TRUE)
-ccle_data <- merge(ccle_data, maf_df_lvlA, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
-ccle_data$Mutation_Status_Nonsilent <- ifelse(is.na(ccle_data$Mutation_Status_Nonsilent), "Other", ccle_data$Mutation_Status_Nonsilent)
-ccle_data$Hugo_Symbol <- factor(ccle_data$Hugo_Symbol)
-ccle_data$AUC <- as.numeric(ccle_data$AUC)
-ccle_data$Color_Nonsilent <- ifelse(ccle_data$Mutation_Status_Nonsilent == "Other", "palegreen3", "springgreen4")
-ccle_data$Color_Nonsilent <- factor(ccle_data$Color_Nonsilent)
-ccle_data <- filter(ccle_data, !is.na(ccle_data$AUC))
-saveRDS(ccle_data, "./data_munging/rds/ccle_data_18Q3.rds", compress = "xz")
-
-# CTRP
-ctrp <- read.delim("./data_munging/data_drug_auc_ctrp_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
-ctrp <- merge(drug_meta, ctrp, by = "CID")
-ctrp_melt <- melt(ctrp, id.vars = c("CID", "Drug"), measure.vars = colnames(ctrp)[3:ncol(ctrp)], variable.name = "accession_id", value.name = "AUC")
-ctrp_grid <- expand.grid("accession_id" = unique(ctrp_melt$accession_id), "Hugo_Symbol" = genes_lvlA)
-ctrp_data <- merge(ctrp_grid, ctrp_melt, by = "accession_id", all.x = TRUE)
-ctrp_data <- merge(ctrp_data, ccl_converter, by = "accession_id", all.x = TRUE)
-ctrp_data <- merge(ctrp_data, maf_df_lvlA, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
-ctrp_data$Mutation_Status_Nonsilent <- ifelse(is.na(ctrp_data$Mutation_Status_Nonsilent), "Other", ctrp_data$Mutation_Status_Nonsilent)
-ctrp_data$Hugo_Symbol <- factor(ctrp_data$Hugo_Symbol)
-ctrp_data$AUC <- as.numeric(ctrp_data$AUC)
-ctrp_data$Color_Nonsilent <- ifelse(ctrp_data$Mutation_Status_Nonsilent == "Other", "slategray3", "steelblue4")
-ctrp_data$Color_Nonsilent <- factor(ctrp_data$Color_Nonsilent)
-ctrp_data <- filter(ctrp_data, !is.na(ctrp_data$AUC))
-saveRDS(ctrp_data, "./data_munging/rds/ctrp_data_18Q3.rds", compress = "xz")
-
-# GDSC
-gdsc <- read.delim("./data_munging/data_drug_auc_gdsc_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
-gdsc <- merge(drug_meta, gdsc, by = "CID")
-gdsc_melt <- melt(gdsc, id.vars = c("CID", "Drug"), measure.vars = colnames(gdsc)[3:ncol(gdsc)], variable.name = "accession_id", value.name = "AUC")
-gdsc_grid <- expand.grid("accession_id" = unique(gdsc_melt$accession_id), "Hugo_Symbol" = genes_lvlA)
-gdsc_data <- merge(gdsc_grid, gdsc_melt, by = "accession_id", all.x = TRUE)
-gdsc_data <- merge(gdsc_data, ccl_converter, by = "accession_id", all.x = TRUE)
-gdsc_data <- merge(gdsc_data, maf_df_lvlA, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
-gdsc_data$Mutation_Status_Nonsilent <- ifelse(is.na(gdsc_data$Mutation_Status_Nonsilent), "Other", gdsc_data$Mutation_Status_Nonsilent)
-gdsc_data$Hugo_Symbol <- factor(gdsc_data$Hugo_Symbol)
-gdsc_data$AUC <- as.numeric(gdsc_data$AUC)
-gdsc_data$Color_Nonsilent <- ifelse(gdsc_data$Mutation_Status_Nonsilent == "Other", "paleturquoise3", "turquoise4")
-gdsc_data$Color_Nonsilent <- factor(gdsc_data$Color_Nonsilent)
-gdsc_data <- filter(gdsc_data, !is.na(gdsc_data$AUC))
-saveRDS(gdsc_data, "./data_munging/rds/ctrp_data_18Q3.rds", compress = "xz")
-```
-
-```{r}
-ccle_data <- readRDS("./data_munging/rds/ccle_data_18Q3.rds")
-ctrp_data <- readRDS("./data_munging/rds/ctrp_data_18Q3.rds")
-gdsc_data <- readRDS("./data_munging/rds/gdsc_data_18Q3.rds")
-```
-
-```{r}
-test_gdsc <- gdsc_data %>% group_by(Drug, Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()
-```
-
-# Wilcoxon tests: All genes
-
---------------------------------------------------------------------------------
-
-## CRISPR
-
-Filter for point mutations:
-```{r}
-crispr_data_ptmuts <- filter(crispr_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
-crispr_data_ptmuts$Keep_PtMut_Tests <- ifelse(crispr_data_ptmuts$Reference_Allele_Length == 1 | is.na(crispr_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(crispr_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
-crispr_data_ptmuts <- filter(crispr_data_ptmuts, Keep_PtMut_Tests == TRUE)
-
-test_ptmuts <- filter(crispr_data_ptmuts, is.na(group_general_lineage_name))
-test_ptmuts <- filter(crispr_data_ptmuts, Hugo_Symbol == "KRAS")
-```
-
-### Grouped by gene
-
-```{r, eval=FALSE}
-crispr_signif_nonsilent <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol"), data = crispr_data_ptmuts, method = "wilcox.test", p.adjust.method = "BH")
-crispr_signif_nonsilent <- adj_signif(crispr_signif_nonsilent)
-crispr_signif_nonsilent <- crispr_signif_nonsilent[order(crispr_signif_nonsilent$p),]
-saveRDS(crispr_signif_nonsilent, "./data_munging/rds/crispr_signif_ptmuts_nonsilent_gene.rds")
-
-# write.table(crispr_signif_nonsilent, file = "~/Desktop/crispr_signif_ptmuts_nonsilent_gene.csv", quote = FALSE, sep = ",", row.names = FALSE)
-```
-
-```{r, eval=TRUE}
-crispr_signif_nonsilent <- readRDS("./data_munging/rds/crispr_signif_ptmuts_nonsilent_gene.rds")
-
-knitr::kable(filter(crispr_signif_nonsilent, p < 0.01)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant vs other cell lines, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-```{r fig.height=4, fig.width=8}
-wilcox_gene_nonsilent_plot <- ggplot(data = crispr_signif_nonsilent) +
-  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
-  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
-  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
-  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
-  labs(x = "BH-adjusted p-values", y = "Frequency")
-wilcox_gene_nonsilent_plot
-```
-
-### Grouped by gene and lineage
-
-```{r, eval=FALSE}
-crispr_signif_nonsilent_lineage <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "group_general_lineage_name"), data = crispr_data_ptmuts, method = "wilcox.test", p.adjust.method = "BH")
-crispr_signif_nonsilent_lineage <- adj_signif(crispr_signif_nonsilent_lineage)
-crispr_signif_nonsilent_lineage <- crispr_signif_nonsilent_lineage[order(crispr_signif_nonsilent_lineage$p),]
-saveRDS(crispr_signif_nonsilent_lineage, "./data_munging/rds/crispr_signif_ptmuts_nonsilent_lineage.rds")
-
-# write.table(crispr_signif_nonsilent_lineage, file = "~/Desktop/crispr_signif_ptmuts_nonsilent_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
-```
-
-```{r, eval=FALSE}
-crispr_signif_nonsilent_lineage <- readRDS("./data_munging/rds/crispr_signif_ptmuts_nonsilent_lineage.rds")
-
-knitr::kable(filter(crispr_signif_nonsilent_lineage, p < 0.01)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant vs other cell lines by lineage, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-```{r fig.height=4, fig.width=8, eval=FALSE}
-wilcox_lineage_nonsilent_plot <- ggplot(data = crispr_signif_nonsilent_lineage) +
-  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
-  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
-  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
-  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
-  labs(x = "BH-adjusted p-values", y = "Frequency")
-wilcox_lineage_nonsilent_plot
-```
-
-# G2P project
-
---------------------------------------------------------------------------------
-
-## Gene mutation frequency
-
-```{r}
-crispr_data_lvlA <- filter(crispr_data_ptmuts, Hugo_Symbol %in% genes_lvlA)
-
-crispr_data_lvlA_summ <- unique(crispr_data_lvlA[, c("Hugo_Symbol", "N_Nonsilent_Mutant", "N_Nonsilent_Other")])
-crispr_data_lvlA_summ$Fraction_Mutant <- crispr_data_lvlA_summ$N_Nonsilent_Mutant / (crispr_data_lvlA_summ$N_Nonsilent_Mutant + crispr_data_lvlA_summ$N_Nonsilent_Other)
-crispr_data_lvlA_summ$Percent_Mutant <- crispr_data_lvlA_summ$Fraction_Mutant * 100
-# write.table(crispr_data_lvlA_summ, file = "~/Desktop/crispr_data_lvlA_summ_20181003.tsv", quote = FALSE, sep = "\t")
-```
-
-## Wilcoxon tests
-
-### CRISPR: Gene
-
-```{r, eval=FALSE}
-crispr_signif_lvlA <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol"), data = crispr_data_lvlA, method = "wilcox.test", p.adjust.method = "BH")
-crispr_signif_lvlA <- adj_signif(crispr_signif_lvlA)
-crispr_signif_lvlA <- crispr_signif_lvlA[order(crispr_signif_lvlA$p),]
-saveRDS(crispr_signif_lvlA, "./data_munging/rds/crispr_signif_lvlA_gene.rds")
-```
-
-```{r, eval=TRUE}
-crispr_signif_lvlA <- readRDS("./data_munging/rds/crispr_signif_lvlA_gene.rds")
-
-crispr_signif_genes_lvlA <- as.character(crispr_signif_lvlA$Hugo_Symbol[0:20])
-
-knitr::kable(filter(crispr_signif_lvlA, p < 0.1)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results for Level A point mutations, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-```{r fig.height=4, fig.width=8}
-wilcox_gene_lvlA_plot <- ggplot(data = crispr_signif_lvlA) +
-  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
-  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
-  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
-  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
-  labs(x = "BH-adjusted p-values", y = "Frequency")
-wilcox_gene_lvlA_plot
-```
-
-```{r fig.height=7, fig.width=12}
-lvlA_genes_signif <- filter(crispr_data_ptmuts, Hugo_Symbol %in% crispr_signif_genes_lvlA)
-lvlA_genes_signif <- merge(lvlA_genes_signif, crispr_signif_lvlA, by = "Hugo_Symbol")
-lvlA_genes_signif$Hugo_Symbol <- ordered(lvlA_genes_signif$Hugo_Symbol, levels = crispr_signif_genes_lvlA)
-lvlA_genes_signif_color <- as.character(lvlA_genes_signif$Color_Nonsilent)
-names(lvlA_genes_signif_color) <- lvlA_genes_signif$Mutation_Status_Nonsilent
-lvlA_genes_signif <- merge(lvlA_genes_signif, lvlA_genes_signif %>% group_by(Hugo_Symbol) %>% summarize(Text_y = max(Score)), by = "Hugo_Symbol")
-
-lvlA_genes_text <- unique(data.frame(p.signif.adj = lvlA_genes_signif$p.signif.adj, Hugo_Symbol = lvlA_genes_signif$Hugo_Symbol, Text_y = lvlA_genes_signif$Text_y))
-lvlA_genes_text$Hugo_Symbol <- factor(lvlA_genes_text$Hugo_Symbol, levels = crispr_signif_genes_lvlA)
-
-lvlA_signif_genes_plot <- ggplot(data = lvlA_genes_signif, aes(x = Mutation_Status_Nonsilent, y = Score)) +
-  facet_wrap(~ Hugo_Symbol, nrow = 2, scales = "free_y") +
-  geom_jitter(aes(color = Mutation_Status_Nonsilent), alpha = 0.5, width = 0.3) +
-  geom_boxplot(color = "black", fill = NA, outlier.shape = NA) +
-  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
-  scale_color_manual(values = lvlA_genes_signif_color) + 
-  geom_text(data = lvlA_genes_text, mapping = aes(x = 1.5, y = Text_y, label = p.signif.adj), nudge_y = 0.2) +
-  theme(legend.position = "top") +
-  labs(y = "CERES Score",
-       x = "Lineage",
-       color = "Mutation Status",
-       title = "CERES scores for select Level A G2P genes",
-       subtitle = "Genes with adjusted p-values < 0.3 are shown.\nBH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001\nGenes are sorted by increasing p-value.")
-lvlA_signif_genes_plot
-
-# ggsave("./plots_18Q3/manuscript/crispr_g2p_lvlA_signif_genes_plot.png", lvlA_signif_genes_plot, width = 12, height = 7, units = "in")
-```
-
-### CRISPR: Gene and lineage
-
-```{r, eval=FALSE}
-crispr_signif_lvlA_lineage <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "group_general_lineage_name"), data = crispr_data_lvlA, method = "wilcox.test", p.adjust.method = "BH")
-crispr_signif_lvlA_lineage <- adj_signif(crispr_signif_lvlA_lineage)
-crispr_signif_lvlA_lineage <- crispr_signif_lvlA_lineage[order(crispr_signif_lvlA_lineage$p),]
-saveRDS(crispr_signif_lvlA_lineage, "./data_munging/rds/crispr_signif_lvlA_lineage.rds")
-
-# write.table(crispr_signif_lvlA_lineage, file = "~/Desktop/crispr_signif_lvlA_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
-```
-
-```{r, eval=TRUE}
-crispr_signif_lvlA_lineage <- readRDS("./data_munging/rds/crispr_signif_lvlA_lineage.rds")
-
-knitr::kable(filter(crispr_signif_lvlA_lineage, p < 0.01)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant vs other cell lines by lineage, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-```{r fig.height=4, fig.width=8, eval=FALSE}
-wilcox_lineage_lvlA_plot <- ggplot(data = crispr_signif_lvlA_lineage) +
-  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
-  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
-  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
-  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
-  labs(x = "BH-adjusted p-values", y = "Frequency")
-wilcox_lineage_lvlA_plot
-```
-
-```{r fig.height=15, fig.width=15}
-lvlA_signif <- filter(crispr_data_ptmuts, Hugo_Symbol %in% crispr_signif_genes_lvlA)
-lvlA_signif <- merge(lvlA_signif, crispr_signif_lvlA_lineage, by = c("Hugo_Symbol", "group_general_lineage_name"))
-lvlA_signif$Hugo_Symbol <- ordered(lvlA_signif$Hugo_Symbol, levels = crispr_signif_genes_lvlA)
-lvlA_signif_color <- as.character(lvlA_signif$Color_Nonsilent)
-names(lvlA_signif_color) <- lvlA_signif$Mutation_Status_Nonsilent
-lvlA_signif <- merge(lvlA_signif, lvlA_signif %>% group_by(Hugo_Symbol) %>% summarize(Text_y = max(Score)), by = "Hugo_Symbol")
-
-lvlA_text <- unique(data.frame(p.signif.adj = lvlA_signif$p.signif.adj, group_general_lineage_name = lvlA_signif$group_general_lineage_name, Hugo_Symbol = lvlA_signif$Hugo_Symbol, Text_y = lvlA_signif$Text_y))
-lvlA_text$Hugo_Symbol <- factor(lvlA_text$Hugo_Symbol, levels = crispr_signif_genes_lvlA)
-
-lvlA_signif_lineages_plot <- ggplot(data = lvlA_signif, aes(x = group_general_lineage_name, y = Score)) +
-  facet_wrap(~ Hugo_Symbol, nrow = 4, scales = "free_y") +
-  geom_point(aes(color = Mutation_Status_Nonsilent), alpha = 0.5) +
-  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
-  scale_color_manual(values = lvlA_signif_color) +
-  geom_text(data = lvlA_text, mapping = aes(x = group_general_lineage_name, y = Text_y, label = p.signif.adj), nudge_y = 0.1) +
-  theme(legend.position = "top", axis.text.x = element_text(angle = 90, hjust = 1, vjust = 1, size = 10)) +
-  labs(y = "CERES Score",
-       x = "Lineage",
-       color = "Mutation Status",
-       title = "CERES score by cell line lineage for significant Level A G2P genes",
-       subtitle = "Genes with adjusted p-values < 0.3 are shown.\nBH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001\nGenes are sorted by increasing lineage-agnostic p-value.")
-lvlA_signif_lineages_plot
-
-# ggsave("./plots_18Q3/manuscript/crispr_g2p_lvlA_signif_lineages_plot.png", lvlA_signif_lineages_plot, width = 12, height = 15, units = "in")
-```
-
-```{r}
-lvlA_signif_summ <- lvlA_signif %>% group_by(Hugo_Symbol, group_general_lineage_name, Mutation_Status_Nonsilent) %>% tally()
-# write.table(lvlA_signif_summ, file = "~/Desktop/lvlA_signif_summ_20181005.tsv", quote = FALSE, sep = "\t")
-
-knitr::kable(lvlA_signif_summ, caption = "Mutant/Other counts for gene-lineage combinations") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-### CCLE: Gene and drug
-
-```{r}
-ccle_data_ptmuts <- filter(ccle_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
-ccle_data_ptmuts$Keep_PtMut_Tests <- ifelse(ccle_data_ptmuts$Reference_Allele_Length == 1 | is.na(ccle_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(ccle_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
-ccle_data_ptmuts <- filter(ccle_data_ptmuts, Keep_PtMut_Tests == TRUE)
-ccle_data_lvlA <- filter(ccle_data_ptmuts, Hugo_Symbol %in% genes_lvlA)
-```
-
-```{r, eval=FALSE}
-ccle_signif_lvlA <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = c("Drug", "Hugo_Symbol"), data = ccle_data_lvlA, method = "wilcox.test", p.adjust.method = "BH")
-ccle_signif_lvlA <- adj_signif(ccle_signif_lvlA)
-ccle_signif_lvlA <- ccle_signif_lvlA[order(ccle_signif_lvlA$p),]
-saveRDS(ccle_signif_lvlA, "./data_munging/rds/ccle_signif_lvlA_gene.rds")
-```
-
-```{r, eval=TRUE}
-ccle_signif_lvlA <- readRDS("./data_munging/rds/ccle_signif_lvlA_gene.rds")
-
-# ccle_signif_genes_lvlA <- as.character(ccle_signif_lvlA$Hugo_Symbol[0:20])
-
-knitr::kable(ccle_signif_lvlA[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for Level A point mutations, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-```{r fig.height=4, fig.width=8}
-wilcox_ccle_gene_lvlA_plot <- ggplot(data = ccle_signif_lvlA) +
-  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
-  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
-  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
-  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
-  labs(x = "BH-adjusted p-values", y = "Frequency")
-wilcox_ccle_gene_lvlA_plot
-```
-
-### CTRP: Gene and drug
-
-```{r}
-ctrp_data_ptmuts <- filter(ctrp_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
-ctrp_data_ptmuts$Keep_PtMut_Tests <- ifelse(ctrp_data_ptmuts$Reference_Allele_Length == 1 | is.na(ctrp_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(ctrp_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
-ctrp_data_ptmuts <- filter(ctrp_data_ptmuts, Keep_PtMut_Tests == TRUE)
-ctrp_data_lvlA <- filter(ctrp_data_ptmuts, Hugo_Symbol %in% genes_lvlA)
-```
-
-```{r, eval=FALSE}
-ctrp_signif_lvlA <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "Drug"), data = ctrp_data_lvlA, method = "wilcox.test", p.adjust.method = "BH")
-ctrp_signif_lvlA <- adj_signif(ctrp_signif_lvlA)
-ctrp_signif_lvlA <- ctrp_signif_lvlA[order(ctrp_signif_lvlA$p),]
-saveRDS(ctrp_signif_lvlA, "./data_munging/rds/ctrp_signif_lvlA_gene.rds")
-```
-
-```{r, eval=TRUE}
-ctrp_signif_lvlA <- readRDS("./data_munging/rds/ctrp_signif_lvlA_gene.rds")
-
-# ctrp_signif_genes_lvlA <- as.character(ctrp_signif_lvlA$Hugo_Symbol[0:20])
-
-knitr::kable(ctrp_signif_lvlA[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for Level A point mutations, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-```{r fig.height=4, fig.width=8}
-wilcox_ctrp_gene_lvlA_plot <- ggplot(data = ctrp_signif_lvlA) +
-  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
-  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
-  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
-  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
-  labs(x = "BH-adjusted p-values", y = "Frequency")
-wilcox_ctrp_gene_lvlA_plot
-```
-
-### GDSC: Gene and drug
-
-```{r}
-gdsc_data_ptmuts <- filter(gdsc_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
-gdsc_data_ptmuts$Keep_PtMut_Tests <- ifelse(gdsc_data_ptmuts$Reference_Allele_Length == 1 | is.na(gdsc_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(gdsc_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
-gdsc_data_ptmuts <- filter(gdsc_data_ptmuts, Keep_PtMut_Tests == TRUE)
-gdsc_data_lvlA <- filter(gdsc_data_ptmuts, Hugo_Symbol %in% genes_lvlA)
-```
-
-```{r, eval=FALSE}
-gdsc_signif_lvlA <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "Drug"), data = gdsc_data_lvlA, method = "wilcox.test", p.adjust.method = "BH")
-gdsc_signif_lvlA <- adj_signif(gdsc_signif_lvlA)
-gdsc_signif_lvlA <- gdsc_signif_lvlA[order(gdsc_signif_lvlA$p),]
-saveRDS(gdsc_signif_lvlA, "./data_munging/rds/gdsc_signif_lvlA_gene.rds")
-```
-
-```{r, eval=TRUE}
-gdsc_signif_lvlA <- readRDS("./data_munging/rds/gdsc_signif_lvlA_gene.rds")
-
-# gdsc_signif_genes_lvlA <- as.character(gdsc_signif_lvlA$Hugo_Symbol[0:20])
-
-knitr::kable(gdsc_signif_lvlA[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for Level A point mutations, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-```{r fig.height=4, fig.width=8}
-wilcox_gdsc_gene_lvlA_plot <- ggplot(data = gdsc_signif_lvlA) +
-  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
-  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
-  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
-  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
-  labs(x = "BH-adjusted p-values", y = "Frequency")
-wilcox_gdsc_gene_lvlA_plot
-```
-
-## Screen boxplots
-
-Mutation status boxplots for genes identified in G2P.
-```{r}
-genes_lvlA_filt <- c("KRAS", "EGFR", "MET", "ALK", "BRAF", "ERBB2", "ABL1", "ROS1", "KIT", "DPYD", "PDGFRA", "RET", "BRCA1", "UGT1A1", "IDH2", "ESR1", "TPMT", "BRCA2", "PDGFRB", "G6PD", "PML", "TSC1", "FLT3", "ERBB3", "CYP19A1", "AKT1", "PTCH1", "MGMT", "DNMT3A", "MYD88", "PDGFB", "TSC2", "NPM1", "JAK2")
-```
-
-### CRISPR
-
-```{r fig.height=7, fig.width=12}
-crispr_ptmuts_lvlA_filt <- filter(crispr_data_ptmuts, Hugo_Symbol %in% genes_lvlA_filt)
-crispr_ptmuts_lvlA_filt$Hugo_Symbol <- ordered(crispr_ptmuts_lvlA_filt$Hugo_Symbol, levels = genes_lvlA_filt)
-crispr_ptmuts_lvlA_filt_color <- as.character(crispr_ptmuts_lvlA_filt$Color_Nonsilent)
-names(crispr_ptmuts_lvlA_filt_color) <- crispr_ptmuts_lvlA_filt$Mutation_Status_Nonsilent
-
-label_text <- data.frame(p.signif.adj = crispr_signif_lvlA$p.signif.adj, Hugo_Symbol = crispr_signif_lvlA$Hugo_Symbol)
-label_text <- filter(label_text, Hugo_Symbol %in% genes_lvlA_filt)
-label_text$Hugo_Symbol <- factor(label_text$Hugo_Symbol, levels = genes_lvlA_filt)
-
-crispr_ptmuts_lvlA_filt_plot_faceted <- ggplot(data = crispr_ptmuts_lvlA_filt, aes(x = Mutation_Status_Nonsilent, y = Score)) +
-  facet_wrap(~ Hugo_Symbol, drop = FALSE, ncol = length(genes_lvlA)) +
-  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
-  geom_boxplot(mapping = aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85)) +
-  scale_fill_manual(values = crispr_ptmuts_lvlA_filt_color) +
-  guides(color = FALSE) +
-  geom_text(data = label_text, mapping = aes(x = 1.5, y = 2, label = p.signif.adj)) +
-  theme(legend.position = "top", axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
-  labs(fill = "Mutation Status", y = "CERES Score", x = "Mutation Status")
-crispr_ptmuts_lvlA_filt_plot_faceted
-# ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_filt_plot_faceted.png", crispr_ptmuts_lvlA_filt_plot_faceted, device = "png", dpi = 450, width = 20, height = 4, units = "in")
-```
-
-### CCLE
-
-```{r fig.height=4, fig.width=20}
-ccle_ptmuts_lvlA_filt <- filter(ccle_data_ptmuts, Hugo_Symbol %in% genes_lvlA_filt)
-ccle_ptmuts_lvlA_filt$Hugo_Symbol <- ordered(ccle_ptmuts_lvlA_filt$Hugo_Symbol, levels = genes_lvlA_filt)
-ccle_drugs <- as.character(unique(ccle_ptmuts_lvlA_filt$Drug))
-```
-
-Plot code:
-```{r, eval=FALSE}
-ccle_lvlA_drugboxplots <- lapply(ccle_drugs, makeDrugBoxplots, dataset = "CCLE")
-ccle_lvlA_drugboxplot_paths <- paste0(ccle_drugs, "_ccle_boxplots.png")
-pwalk(list(ccle_lvlA_drugboxplot_paths, ccle_lvlA_drugboxplots), ggsave, path = "./plots_18Q3/manuscript/ccle_lvlA_boxplots", dpi = 450, width = 20, height = 4, units = "in")
-```
-
-Data management:
-```{r, eval=TRUE}
-ccle_lvlA_drugboxplots <- paste0(list.files("./plots_18Q3/manuscript/ccle_lvlA_boxplots", full.names = TRUE))
-names(ccle_lvlA_drugboxplots) <- str_replace_all(ccle_lvlA_drugboxplots, c("_ccle_boxplots.png" = "", "./plots_18Q3/manuscript/ccle_lvlA_boxplots/" = ""))
-bsselect(ccle_lvlA_drugboxplots, type = "img", live_search = TRUE, show_tick = TRUE, height = 300, frame_height = 275)
-```
-
-### CTRP
-
-```{r fig.height=4, fig.width=20}
-ctrp_ptmuts_lvlA_filt <- filter(ctrp_data_ptmuts, Hugo_Symbol %in% genes_lvlA_filt)
-ctrp_ptmuts_lvlA_filt$Hugo_Symbol <- ordered(ctrp_ptmuts_lvlA_filt$Hugo_Symbol, levels = genes_lvlA_filt)
-ctrp_drugs <- as.character(unique(ctrp_ptmuts_lvlA_filt$Drug))
-```
-
-Plot code:
-```{r, eval=FALSE}
-ctrp_lvlA_drugboxplots <- lapply(ctrp_drugs, makeDrugBoxplots, dataset = "CTRP")
-ctrp_lvlA_drugboxplot_paths <- paste0(ctrp_drugs, "_ctrp_boxplots.png")
-pwalk(list(ctrp_lvlA_drugboxplot_paths, ctrp_lvlA_drugboxplots), ggsave, path = "./plots_18Q3/manuscript/ctrp_lvlA_boxplots", dpi = 450, width = 20, height = 4, units = "in")
-```
-
-Data management:
-```{r, eval=TRUE}
-ctrp_lvlA_drugboxplots <- paste0(list.files("./plots_18Q3/manuscript/ctrp_lvlA_boxplots", full.names = TRUE))
-names(ctrp_lvlA_drugboxplots) <- str_replace_all(ctrp_lvlA_drugboxplots, c("_ctrp_boxplots.png" = "", "./plots_18Q3/manuscript/ctrp_lvlA_boxplots/" = ""))
-bsselect(ctrp_lvlA_drugboxplots, type = "img", live_search = TRUE, show_tick = TRUE, height = 300, frame_height = 275)
-```
-
-### GDSC
-
-```{r fig.height=4, fig.width=20}
-gdsc_ptmuts_lvlA_filt <- filter(gdsc_data_ptmuts, Hugo_Symbol %in% genes_lvlA_filt)
-gdsc_ptmuts_lvlA_filt$Hugo_Symbol <- ordered(gdsc_ptmuts_lvlA_filt$Hugo_Symbol, levels = genes_lvlA_filt)
-gdsc_drugs <- as.character(unique(gdsc_ptmuts_lvlA_filt$Drug))
-```
-
-Plot code:
-```{r, eval=FALSE}
-gdsc_lvlA_drugboxplots <- lapply(gdsc_drugs, makeDrugBoxplots, dataset = "GDSC")
-gdsc_lvlA_drugboxplot_paths <- paste0(gdsc_drugs, "_gdsc_boxplots.png")
-pwalk(list(gdsc_lvlA_drugboxplot_paths, gdsc_lvlA_drugboxplots), ggsave, path = "./plots_18Q3/manuscript/gdsc_lvlA_boxplots", dpi = 450, width = 20, height = 4, units = "in")
-```
-
-Data management:
-```{r, eval=TRUE}
-gdsc_lvlA_drugboxplots <- paste0(list.files("./plots_18Q3/manuscript/gdsc_lvlA_boxplots", full.names = TRUE))
-names(gdsc_lvlA_drugboxplots) <- str_replace_all(gdsc_lvlA_drugboxplots, c("_gdsc_boxplots.png" = "", "./plots_18Q3/manuscript/gdsc_lvlA_boxplots/" = ""))
-bsselect(gdsc_lvlA_drugboxplots, type = "img", live_search = TRUE, show_tick = TRUE, height = 300, frame_height = 275)
-```
-
-## CRISPR: Point mutation mapping
-
-Match specific point mutations.
-```{r fig.height=5, fig.width=20}
-g2p_indications <- filter(read.delim("./data_munging/data_mutation_associations_appended.csv", sep = "\t", header = TRUE), Evidence.Level == "A")
-maf_g2p_indications <- filter(maf_raw, Genome_Change %in% g2p_indications$MutationName)
-crispr_g2p_indications <- merge(maf_g2p_indications, crispr_data_ptmuts, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"))
-dup_g2p_indications <- filter(crispr_g2p_indications[, c("Hugo_Symbol", "CCLE_Name", "Broad_ID")] %>% group_by(Hugo_Symbol, CCLE_Name, Broad_ID) %>% tally(), n > 1)
-crispr_g2p_indications <- merge(crispr_g2p_indications, dup_g2p_indications, by = c("Hugo_Symbol", "Broad_ID"), all.x = TRUE)
-crispr_g2p_indications <- filter(crispr_g2p_indications, is.na(n))
-
-crispr_g2p_indications_plot <- ggplot(crispr_g2p_indications, aes(x = Hugo_Symbol, y = Score)) +
-  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
-  geom_boxplot(alpha = 0.5, color = "lightgray", outlier.shape = NA) +
-  geom_jitter(width = 0.3, mapping = aes(color = group_general_lineage_name), size = 1) +
-  theme_light() +
-  theme(legend.title = element_blank()) +
-  labs(x = "Gene", y = "CERES Score")
-crispr_g2p_indications_plot
-
-crispr_g2p_indications_muts_plot <- ggplot(crispr_g2p_indications, aes(x = Protein_Change, y = Score)) +
-  facet_grid(~ Hugo_Symbol, scales = "free_x", space = "free") +
-  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
-  geom_boxplot(alpha = 0.5, color = "lightgray", outlier.shape = NA) +
-  geom_jitter(width = 0.1, mapping = aes(color = group_general_lineage_name), size = 1) +
-  theme_light() +
-  theme(legend.title = element_blank(), axis.text.x = element_text(angle = 90, hjust = 1)) +
-  labs(x = "Gene", y = "CERES Score")
-crispr_g2p_indications_muts_plot
-
-# ggsave("./plots_18Q3/manuscript/crispr_g2p_indications_plot_test.png", crispr_g2p_indications_plot, width = 12, height = 5, units = "in")
-# ggsave("./plots_18Q3/manuscript/crispr_g2p_indications_muts_plot_test.png", crispr_g2p_indications_muts_plot, width = 20, height = 5, units = "in")
-```
-
-## Level A: Per-gene grouped plots
-
-Plot code:
-```{r, eval=FALSE}
-crispr_lvlA_groups <- lapply(as.character(genes_lvlA), makeCRISPRgrob, filt_method = "lvlA")
-crispr_lvlA_groups_paths <- paste0(genes_lvlA, "_crispr_grouped.png")
-pwalk(list(crispr_lvlA_groups_paths, crispr_lvlA_groups), ggsave, path = "./plots_18Q3/crispr_grouped_plots_lvlA", dpi = 300, width = 12, height = 12, units = "in")
-```
-
-Data management:
-```{r, eval=TRUE}
-crispr_lvlA_bygene <- paste0(list.files("./plots_18Q3/crispr_grouped_plots_lvlA", full.names = TRUE))
-names(crispr_lvlA_bygene) <- str_replace_all(crispr_lvlA_bygene, c("_crispr_grouped.png" = "", "./plots_18Q3/crispr_grouped_plots_lvlA/" = ""))
-crispr_lvlA_order <- c(intersect(crispr_signif_lvlA$Hugo_Symbol, names(crispr_lvlA_bygene)), setdiff(names(crispr_lvlA_bygene), crispr_signif_lvlA$Hugo_Symbol))
-crispr_lvlA_bygene <- crispr_lvlA_bygene[match(crispr_lvlA_order, names(crispr_lvlA_bygene))]
-bsselect(crispr_lvlA_bygene, type = "img", selected = "KRAS", live_search = TRUE, show_tick = TRUE, height = 300, frame_height = 275)
-```
-
-<!-- ## All genes: Per-gene grouped plots -->
-
-<!-- Plot code: -->
-<!-- ```{r, eval=FALSE} -->
-<!-- crispr_all_groups <- lapply(unique(crispr_data_ptmuts$Hugo_Symbol), makeCRISPRgrob, filt_method = "all") -->
-<!-- crispr_all_groups_paths <- paste0(unique(crispr_data_ptmuts$Hugo_Symbol), "_crispr_grouped.png") -->
-<!-- pwalk(list(crispr_lvlA_groups_paths, crispr_lvlA_groups), ggsave, path = "./plots_18Q3/crispr_grouped_plots", dpi = 300, width = 12, height = 12, units = "in") -->
-<!-- ``` -->
-
-<!-- Data management: -->
-<!-- ```{r, eval=FALSE} -->
-<!-- crispr_all_bygene <- paste0(list.files("./plots_18Q3/crispr_grouped_plots", full.names = TRUE)) -->
-<!-- names(crispr_all_bygene) <- str_replace_all(crispr_all_bygene, c("_crispr_grouped.png" = "", "./plots_18Q3/crispr_grouped_plots_lvlA/" = "")) -->
-<!-- crispr_all_order <- c(intersect(crispr_signif_nonsilent$Hugo_Symbol, names(crispr_all_bygene)), setdiff(names(crispr_all_bygene), crispr_signif_nonsilent$Hugo_Symbol)) -->
-<!-- crispr_all_bygene <- crispr_all_bygene[match(crispr_all_order, names(crispr_all_bygene))] -->
-<!-- bsselect(crispr_all_bygene, type = "img", selected = "KRAS", live_search = TRUE, show_tick = TRUE, height = 300, frame_height = 275) -->
-<!-- ``` -->
-
-## JSON testing
-
-```{r}
-g2pA <- read.delim("./data_munging/g2p_full_level_A_dataset_v2_10_10_2018.csv", sep = "\t", header = TRUE, na.strings = "-1", quote = "")
-# g2pA[g2pA == "-1"] <- NA
-g2pA$X <- NULL
-
-g2pA_JSON <- data.frame(JSON = g2pA$JSON)
-
-g2pA_noJSON <- g2pA
-g2pA_noJSON$JSON <- NULL
-
-# write.table(g2pA, file = "./data_munging/g2p_full_level_A_dataset_v2_10_10_2018.tsv", quote = FALSE, sep = "\t", row.names = FALSE)
-# write.table(g2pA_noJSON, file = "./data_munging/g2pA_noJSON_v2_10_10_2018.tsv", quote = FALSE, sep = "\t", row.names = FALSE)
-# write.table(g2pA_JSON, file = "./data_munging/g2pA_JSON_v2_10_10_2018.tsv", quote = FALSE, sep = "\t", row.names = FALSE)
-```
-
-```
-{
-'feature_names': 'ALK positive',
-'jax': '{\"responseType\": \"sensitive\", 
-        \"efficacyEvidence\": \"Zykadia (ceritinib) is FDA approved for the treatment of ALK-positive metastatic non-small cell lung cancer (NSCLC) in patients previously treated with crizotinib (FDA.gov).\",
-        \"molecularProfile\": {\"profileName\": \"ALK positive\",
-                               \"id\": 1772},
-        \"evidenceType\": \"Actionable\",
-        \"indication\": {\"source\": \"DOID\",
-                         \"id\": 3908,
-                         \"name\": \"non-small cell lung carcinoma\"},
-        \"references\": [{\"url\": \"http://www.fda.gov/\",
-                          \"id\": 286,
-                          \"pubMedId\": null,
-                          \"title\": \"FDA.gov\"}],
-        \"approvalStatus\": \"FDA approved\",
-        \"therapy\": {\"id\": 789,
-                      \"therapyName\": \"Ceritinib\"},
-        \"id\": 1481}',
-'tags': [],
-'genes': ['ALK'],
-'source_url': 'https://ckb.jax.org/therapy/show/789',
-'source': 'jax',
-'dev_tags': [],
-'gene_identifiers': [{'symbol': 'ALK',
-                      'entrez_id': '238',
-                      'ensembl_gene_id': 'ENSG00000171094'}],
-'association': {'drug_labels': 'CERITINIB',
-                'description': 'Zykadia (ceritinib) is FDA approved for the treatment of ALK-positive metastatic non-small cell lung cancer (NSCLC) in patients previously treated with crizotinib (FDA.gov).',
-                'publication_url': 'http://www.fda.gov/',
-                'source_link': 'https://ckb.jax.org/molecularProfile/show/1772',
-                'variant_name': [''],
-                'phenotypes': [{'source': 'http://purl.obolibrary.org/obo/DOID_3908',
-                                'term': 'non-small cell lung carcinoma',
-                                'description': 'non-small cell lung carcinoma',
-                                'family': 'lung cancer',
-                                'id': 'DOID:3908'}],
-                'evidence': [{'info': {'publications': ['http://www.fda.gov/']},
-                              'evidenceType': {'sourceName': 'jax'},
-                              'description': 'sensitive'}],
-                              'environmentalContexts': [{'term': 'CERITINIB',
-                                                          'description': 'CERITINIB',
-                                                          'taxonomy': {'kingdom': 'Chemical entities',
-                                                                       'direct-parent': 'Phenylpiperidines',
-                                                                       'class': 'Organoheterocyclic compounds',
-                                                                       'subclass': 'Piperidines',
-                                                                       'superclass': 'Organic compounds'},
-                                                          'source': 'http://rdf.ncbi.nlm.nih.gov/pubchem/compound',
-                                                          'usan_stem': 'tyrosine kinase inhibitors',
-                                                          'toxicity': 'There is not currently any data on carcinogenicity, effect on human fertility, or on early embryonic development.
-However, based on its mechanism of action, ceritinib may cause fetal harm when administered to pregnant women and should therefore be administered with effective contraception during treatment.
-Diarrhea, nausea, vomiting, or abdominal pain occurred in 96% of 255 patients including severe cases in 14% of patients.
-Drug-induced hepatotoxicity also occurred in 27% of 255 patients, presenting as alanine aminotransferase (ALT) levels greater than 5 times the upper limit of normal (ULN).
-Severe, life-threatening, or fatal interstitial lung disease (ILD)/pneumonitis, hyperglycaemia, and bradycardia have also been reported.',
-                                                          'approved_countries': ['Canada',
-                                                                                 'US'],
-                                                          'id': 'CID57379345'}],
-                'evidence_label': 'A',
-                'response_type': 'sensitive',
-                'evidence_level': 1},
-'features': [{'provenance_rule': 'default_feature',
-              'end': 29484957,
-              'description': 'ALK  positive',
-              'links': ['http://reg.genome.network/refseq/RS000050',
-                        'http://reg.genome.network/refseq/RS000026',
-                        'http://reg.genome.network/allele/CA425438613',
-                        'http://reg.genome.network/refseq/RS000002',
-                        'http://myvariant.info/v1/variant/chr2:g.29484957C>G?assembly=hg19',
-                        'http://reg.genome.network/refseq/RS001597'],
-              'sequence_ontology': {'hierarchy': ['SO:0000400',
-                                                  'SO:0000733',
-                                                  'SO:0000401',
-                                                  'SO:0000119',
-                                                  'SO:0000123',
-                                                  'SO:0000125'],
-                                    'soid': 'SO:0000475',
-                                    'root_name': 'sequence_attribute',
-                                    'name': 'positively_autoregulated',
-                                    'root_soid': 'SO:0000400'},
-              'provenance': ['http://myvariant.info/v1/query?q=ALK  positive',
-                             'http://reg.genome.network/allele?hgvs=NC_000002.11%3Ag.29484957C%3EG'], 
-              'start': 29484957,
-              'synonyms': ['NC_000002.11:g.29484957C>G',
-                           'NC_000002.10:g.29338461C>G',
-                           'LRG_488:g.664476G>C',
-                           'chr2:g.29484957C>G',
-                           'NG_009445.1:g.664476G>C',
-                           'NC_000002.12:g.29262091C>G',
-                           'CM000664.1:g.29484957C>G',
-                           'CM000664.2:g.29262091C>G'],
-              'biomarker_type': 'positive',
-              'referenceName': 'GRCh37',
-              'geneSymbol': 'ALK',
-              'alt': 'G',
-              'ref': 'C',
-              'chromosome': '2',
-              'name': 'ALK  positive'}]
-}
-```
-
-# Heatmaps
-
---------------------------------------------------------------------------------
-
-## Data management
-
-The mutation status portion of these heatmaps was made using deleterious and missense mutations as "mutant" and all others as "other."
-
-Make and save heatmap data matrices:
-```{r, eval=FALSE}
-# Set up heatmap data
-chm_scores <- t(crispr)
-colnames(chm_scores) <- chm_scores[1, ]
-chm_scores <- chm_scores[-1, ]
-chm_rows <- rownames(chm_scores)
-chm_cols <- colnames(chm_scores)
-chm_scores <- apply(chm_scores, 2, as.double)
-chm_scores <- apply(chm_scores, 2, function(x) (x - mean(x)) / var(x))
-colnames(chm_scores) <- chm_cols
-rownames(chm_scores) <- chm_rows
-saveRDS(chm_scores, "./data_munging/rds/crispr_heatmap_scores.rds")
-
-# Make full grid for genomic features
-crispr_grid_ccls <- unique(crispr_data$Broad_ID)
-crispr_grid_genes <- unique(crispr_data$Hugo_Symbol)
-crispr_grid <- expand.grid("Broad_ID" = crispr_grid_ccls, "Hugo_Symbol" = crispr_grid_genes)
-
-# Gene expression
-ge_filt <- filter(ge_melt, Hugo_Symbol %in% unique(crispr_data$Hugo_Symbol))[, c("Hugo_Symbol", "Broad_ID", "RPKM")]
-ge_filt$RPKM <- log2(ge_filt$RPKM + 0.0001)
-chm_ge_grid <- merge(crispr_grid, ge_filt, by = c("Broad_ID", "Hugo_Symbol"), all.x = TRUE)
-chm_ge <- reshape(chm_ge_grid, idvar = "Hugo_Symbol", timevar = "Broad_ID", direction = "wide")
-chm_ge_rows <- chm_ge$Hugo_Symbol
-chm_ge$Hugo_Symbol <- NULL
-chm_ge_cols <- colnames(chm_ge) %>% gsub("RPKM.", "", .)
-chm_ge <- apply(chm_ge, 2, as.double)
-chm_ge <- apply(chm_ge, 2, function(x) (x - mean(x, na.rm = TRUE)) / var(x, na.rm = TRUE))
-rownames(chm_ge) <- chm_ge_rows
-colnames(chm_ge) <- chm_ge_cols
-saveRDS(chm_ge, "./data_munging/rds/crispr_heatmap_ge.rds")
-
-# Mutation status
-chm_mut_grid <- merge(crispr_grid, maf_df[, c("Broad_ID", "Hugo_Symbol", "Mutation_Status")], by = c("Broad_ID", "Hugo_Symbol"), all.x = TRUE)
-chm_mut_grid$Mutation_Status <- ifelse(is.na(chm_mut_grid$Mutation_Status), "Other", chm_mut_grid$Mutation_Status)
-chm_mut_grid$Mutation_Status <- ifelse(chm_mut_grid$Mutation_Status == "Other", 0, 1)
-chm_mut <- reshape(chm_mut_grid, idvar = "Hugo_Symbol", timevar = "Broad_ID", direction = "wide")
-chm_mut_rows <- chm_mut$Hugo_Symbol
-chm_mut$Hugo_Symbol <- NULL
-chm_mut_cols <- colnames(chm_mut) %>% gsub("Mutation_Status.", "", .)
-chm_mut <- matrix(as.numeric(unlist(chm_mut)), nrow = nrow(chm_mut))
-rownames(chm_mut) <- chm_mut_rows
-colnames(chm_mut) <- chm_mut_cols
-saveRDS(chm_mut, "./data_munging/rds/crispr_heatmap_mut.rds")
-
-# Copy number
-cn_filt <- filter(cn_melt, Hugo_Symbol %in% unique(crispr_data$Hugo_Symbol))
-chm_cn_grid <- merge(crispr_grid, cn_melt, by = c("Broad_ID", "Hugo_Symbol"), all.x = TRUE)
-chm_cn <- reshape(chm_cn_grid, idvar = "Hugo_Symbol", timevar = "Broad_ID", direction = "wide")
-chm_cn_rows <- chm_cn$Hugo_Symbol
-chm_cn$Hugo_Symbol <- NULL
-chm_cn_cols <- colnames(chm_cn) %>% gsub("Copy_Number.", "", .)
-chm_cn <- apply(chm_cn, 2, as.double)
-chm_cn <- apply(chm_cn, 2, function(x) (x - mean(x, na.rm = TRUE)) / var(x, na.rm = TRUE))
-rownames(chm_cn) <- chm_cn_rows
-colnames(chm_cn) <- chm_cn_cols
-saveRDS(chm_cn, "./data_munging/rds/crispr_heatmap_cn.rds")
-```
-
-Load heatmap matrices:
-```{r, eval=FALSE}
-chm_scores <- readRDS("./data_munging/rds/crispr_heatmap_scores.rds")
-chm_ge <- readRDS("./data_munging/rds/crispr_heatmap_ge.rds")
-chm_mut <- readRDS("./data_munging/rds/crispr_heatmap_mut.rds")
-chm_cn <- readRDS("./data_munging/rds/crispr_heatmap_cn.rds")
-
-# Metadata anotation dataframe
-chm_annot <- merge(merge(data.frame("Broad_ID" = crispr$Broad_ID), crispr_meta[, c("Broad_ID", "cell_line_SSMD", "cas9_activity", "culture_type", "primary_tissue")], by = "Broad_ID", all.x = TRUE), ccl_info[, c("Broad_ID", "Primary.Disease", "Gender", "Source")], by = "Broad_ID", all.x = TRUE)
-rownames(chm_annot) <- chm_annot$Broad_ID
-chm_annot$Broad_ID <- NULL
-colnames(chm_annot) <- c("Cell_Line_SSMD", "Cas9_Activity", "Culture_Type", "Primary_Tissue", "Primary_Disease", "Gender", "Source")
-chm_annot$Cell_Line_SSMD <- as.numeric(chm_annot$Cell_Line_SSMD)
-chm_annot$Cas9_Activity <- as.numeric(chm_annot$Cas9_Activity)
-```
-
-## All genes, no omics
-
-```{r, eval=FALSE}
-chm_annot_list <- HeatmapAnnotation(df = chm_annot, annotation_legend_param = list(
-  Cell_Line_SSMD = list(title = "Cell Line SSMD", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), title_position = "topcenter", legend_height = unit(2, "in")),
-  Cas9_Activity = list(title = "Cas9 Activity", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), title_position = "topcenter", legend_height = unit(2, "in")),
-  Culture_Type = list(title = "Culture Type", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), nrow = 8, title = "Culture Type", title_position = "topleft", grid_height = unit(0.3, "in")),
-  Primary_Tissue = list(title = "Primary Tissue", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), nrow = 8, title = "Primary_Tissue", title_position = "topleft", grid_height = unit(0.3, "in")),
-  Primary_Disease = list(title = "Primary Disease", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), nrow = 8, title = "Primary Disease", title_position = "topleft", grid_height = unit(0.3, "in")),
-  Gender = list(title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), grid_height = unit(0.3, "in")),
-  Source = list(title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), nrow = 8, title = "Source", title_position = "topleft", grid_height = unit(0.3, "in"))))
-
-chm_all_plot <- Heatmap(chm_scores, name = "CERES Score",
-        bottom_annotation = chm_annot_list,
-        bottom_annotation_height = unit(5, "in"),
-        heatmap_legend_param = list(title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), title_position = "topcenter", legend_height = unit(2, "in")),
-        row_title = "Genes", column_title = "Cancer Cell Lines",
-        col = colorRamp2(c(min(chm_scores), 0, max(chm_scores)), c("purple4", "white", "seagreen4")),
-        na_col = "black",
-        row_title_gp = gpar(fontsize = 30, fontface = "bold"),
-        row_names_gp = gpar(fontsize = 5),
-        column_title_gp = gpar(fontsize = 30, fontface = "bold"),
-        column_names_gp = gpar(fontsize = 5),
-        row_dend_reorder = TRUE,
-        column_dend_reorder = TRUE,
-        clustering_distance_rows = "euclidean",
-        clustering_distance_columns = "euclidean",
-        clustering_method_rows = "complete",
-        clustering_method_columns = "complete",
-        column_dend_height = unit(2, "in"),
-        row_dend_width = unit(4, "in"),
-        width = 3)
-
-pdf("./plots_18Q3/crispr_heatmap_euclidean_all.pdf", width = 50, height = 50, paper = "special")
-draw(chm_all_plot, heatmap_legend_side = "bottom", annotation_legend_side = "bottom")
-seekViewport("annotation_Cell_Line_SSMD")
-grid.text("Cell Line SSMD", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
-seekViewport("annotation_Cas9_Activity")
-grid.text("Cas9 Activity", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
-seekViewport("annotation_Culture_Type")
-grid.text("Culture Type", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
-seekViewport("annotation_Primary_Tissue")
-grid.text("Primary Tissue", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
-seekViewport("annotation_Primary_Disease")
-grid.text("Primary Disease", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
-seekViewport("annotation_Gender")
-grid.text("Gender", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
-seekViewport("annotation_Source")
-grid.text("Source", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
-dev.off()
-
-png("./plots_18Q3/crispr_heatmap_euclidean_all.png", width = 50, height = 50, units = "in", res = 96)
-draw(chm_all_plot, heatmap_legend_side = "bottom", annotation_legend_side = "bottom")
-seekViewport("annotation_Cell_Line_SSMD")
-grid.text("Cell Line SSMD", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
-seekViewport("annotation_Cas9_Activity")
-grid.text("Cas9 Activity", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
-seekViewport("annotation_Culture_Type")
-grid.text("Culture Type", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
-seekViewport("annotation_Primary_Tissue")
-grid.text("Primary Tissue", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
-seekViewport("annotation_Primary_Disease")
-grid.text("Primary Disease", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
-seekViewport("annotation_Gender")
-grid.text("Gender", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
-seekViewport("annotation_Source")
-grid.text("Source", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
-dev.off()
-```
-
-## CGC genes
-
-Code for heatmap of CGC-filtered genes only
-
-### Euclidean distance
-
-```{r, eval=FALSE}
-chm_scores_cgc <- subset(chm_scores, rownames(chm_scores) %in% cgc$Hugo_Symbol)
-chm_ge_cgc <- subset(chm_ge, rownames(chm_ge) %in% cgc$Hugo_Symbol)
-chm_mut_cgc <- subset(chm_mut, rownames(chm_mut) %in% cgc$Hugo_Symbol)
-chm_cn_cgc <- subset(chm_cn, rownames(chm_cn) %in% cgc$Hugo_Symbol)
-
-chm_annot_list <- HeatmapAnnotation(df = chm_annot, annotation_legend_param = list(
-  Cell_Line_SSMD = list(title = "Cell Line SSMD", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), title_position = "topcenter", legend_height = unit(2, "in")),
-  Cas9_Activity = list(title = "Cas9 Activity", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), title_position = "topcenter", legend_height = unit(2, "in")),
-  Culture_Type = list(title = "Culture Type", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), nrow = 8, title = "Culture Type", title_position = "topleft", grid_height = unit(0.3, "in")),
-  Primary_Tissue = list(title = "Primary Tissue", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), nrow = 8, title = "Primary_Tissue", title_position = "topleft", grid_height = unit(0.3, "in")),
-  Primary_Disease = list(title = "Primary Disease", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), nrow = 8, title = "Primary Disease", title_position = "topleft", grid_height = unit(0.3, "in")),
-  Gender = list(title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), grid_height = unit(0.3, "in")),
-  Source = list(title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), nrow = 8, title = "Source", title_position = "topleft", grid_height = unit(0.3, "in"))))
-
-chm_plot_cgc <- Heatmap(chm_scores_cgc, name = "CERES Score",
-        bottom_annotation = chm_annot_list,
-        bottom_annotation_height = unit(5, "in"),
-        heatmap_legend_param = list(title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), title_position = "topcenter", legend_height = unit(2, "in")),
-        row_title = "Genes", column_title = "Cancer Cell Lines",
-        col = colorRamp2(c(min(chm_scores_cgc), 0, max(chm_scores_cgc)), c("purple4", "white", "seagreen4")),
-        na_col = "black",
-        row_title_gp = gpar(fontsize = 30, fontface = "bold"),
-        row_names_gp = gpar(fontsize = 5),
-        column_title_gp = gpar(fontsize = 30, fontface = "bold"),
-        column_names_gp = gpar(fontsize = 5),
-        row_dend_reorder = TRUE,
-        column_dend_reorder = TRUE,
-        clustering_distance_rows = "euclidean",
-        clustering_distance_columns = "euclidean",
-        clustering_method_rows = "complete",
-        clustering_method_columns = "complete",
-        column_dend_height = unit(2, "in"),
-        row_dend_width = unit(4, "in"),
-        width = 3)
-
-chm_plot_cgc_cols <- colnames(chm_scores_cgc)[unlist(column_order(chm_plot_cgc))]
-chm_plot_cgc_rows <- rownames(chm_scores_cgc)[unlist(row_order(chm_plot_cgc))]
-
-chm_ge_plot_cgc <- Heatmap(chm_ge_cgc, name = "Gene Expression",
-        col = colorRamp2(c(min(chm_ge_cgc[!is.na(chm_ge_cgc)]), 0, max(chm_ge_cgc[!is.na(chm_ge_cgc)])), c("dodgerblue4", "white", "firebrick4")),
-        heatmap_legend_param = list(title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), title_position = "topcenter", legend_height = unit(2, "in")),
-        na_col = "black",
-        cluster_rows = FALSE, cluster_columns = FALSE,
-        row_names_gp = gpar(fontsize = 5), show_column_names = FALSE,
-        column_title = "Gene Expression",
-        column_title_gp = gpar(fontsize = 30, fontface = "bold"),
-        column_order = chm_plot_cgc_cols,
-        row_order = chm_plot_cgc_rows,
-        width = 1)
-chm_cn_plot_cgc <- Heatmap(chm_cn_cgc, name = "Copy Number",
-        col = colorRamp2(c(min(chm_cn_cgc[!is.na(chm_cn_cgc)]), 0, max(chm_cn_cgc[!is.na(chm_cn_cgc)])), c("white", "thistle2", "mediumorchid4")),
-        heatmap_legend_param = list(title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), title_position = "topcenter", legend_height = unit(2, "in")),
-        na_col = "black",
-        cluster_rows = FALSE, cluster_columns = FALSE,
-        row_names_gp = gpar(fontsize = 5), show_column_names = FALSE,
-        column_title = "Copy Number",
-        column_title_gp = gpar(fontsize = 30, fontface = "bold"),
-        column_order = chm_plot_cgc_cols,
-        row_order = chm_plot_cgc_rows,
-        width = 1)
-chm_mut_plot_cgc <- Heatmap(chm_mut_cgc, name = "Mutation Status",
-        na_col = "black",
-        heatmap_legend_param = list(title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), at = c(0, 1), labels = c("Other", "Mutant"), title_position = "topcenter", grid_height = unit(0.3, "in")),
-        col = c("cyan3", "darkorchid"),
-        cluster_rows = FALSE, cluster_columns = FALSE,
-        row_names_gp = gpar(fontsize = 5), show_column_names = FALSE,
-        column_title = "Mutation Status",
-        column_title_gp = gpar(fontsize = 30, fontface = "bold"),
-        column_order = chm_plot_cgc_cols,
-        row_order = chm_plot_cgc_rows,
-        width = 1)
-
-chm_all_plot_cgc <- chm_plot_cgc + chm_ge_plot_cgc + chm_cn_plot_cgc + chm_mut_plot_cgc
-
-pdf("./plots_18Q3/crispr_heatmap_euclidean_all_cgc.pdf", width = 50, height = 50, paper = "special")
-draw(chm_all_plot_cgc, heatmap_legend_side = "bottom", annotation_legend_side = "bottom")
-seekViewport("annotation_Cell_Line_SSMD")
-grid.text("Cell Line SSMD", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
-seekViewport("annotation_Cas9_Activity")
-grid.text("Cas9 Activity", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
-seekViewport("annotation_Culture_Type")
-grid.text("Culture Type", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
-seekViewport("annotation_Primary_Tissue")
-grid.text("Primary Tissue", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
-seekViewport("annotation_Primary_Disease")
-grid.text("Primary Disease", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
-seekViewport("annotation_Gender")
-grid.text("Gender", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
-seekViewport("annotation_Source")
-grid.text("Source", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
-dev.off()
-
-png("./plots_18Q3/crispr_heatmap_euclidean_all_cgc.png", width = 50, height = 50, units = "in", res = 96)
-draw(chm_all_plot_cgc, heatmap_legend_side = "bottom", annotation_legend_side = "bottom")
-seekViewport("annotation_Cell_Line_SSMD")
-grid.text("Cell Line SSMD", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
-seekViewport("annotation_Cas9_Activity")
-grid.text("Cas9 Activity", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
-seekViewport("annotation_Culture_Type")
-grid.text("Culture Type", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
-seekViewport("annotation_Primary_Tissue")
-grid.text("Primary Tissue", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
-seekViewport("annotation_Primary_Disease")
-grid.text("Primary Disease", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
-seekViewport("annotation_Gender")
-grid.text("Gender", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
-seekViewport("annotation_Source")
-grid.text("Source", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
-dev.off()
-```
-
-### Pearson correlation
-
-```{r, eval=FALSE}
-chm_scores_cgc <- subset(chm_scores, rownames(chm_scores) %in% cgc$Hugo_Symbol)
-chm_ge_cgc <- subset(chm_ge, rownames(chm_ge) %in% cgc$Hugo_Symbol)
-chm_mut_cgc <- subset(chm_mut, rownames(chm_mut) %in% cgc$Hugo_Symbol)
-chm_cn_cgc <- subset(chm_cn, rownames(chm_cn) %in% cgc$Hugo_Symbol)
-
-chm_annot_list <- HeatmapAnnotation(df = chm_annot, annotation_legend_param = list(
-  Cell_Line_SSMD = list(title = "Cell Line SSMD", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), title_position = "topcenter", legend_height = unit(2, "in")),
-  Cas9_Activity = list(title = "Cas9 Activity", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), title_position = "topcenter", legend_height = unit(2, "in")),
-  Culture_Type = list(title = "Culture Type", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), nrow = 8, title = "Culture Type", title_position = "topleft", grid_height = unit(0.3, "in")),
-  Primary_Tissue = list(title = "Primary Tissue", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), nrow = 8, title = "Primary_Tissue", title_position = "topleft", grid_height = unit(0.3, "in")),
-  Primary_Disease = list(title = "Primary Disease", title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), nrow = 8, title = "Primary Disease", title_position = "topleft", grid_height = unit(0.3, "in")),
-  Gender = list(title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), grid_height = unit(0.3, "in")),
-  Source = list(title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), nrow = 8, title = "Source", title_position = "topleft", grid_height = unit(0.3, "in"))))
-
-chm_plot_cgc <- Heatmap(chm_scores_cgc, name = "CERES Score",
-        bottom_annotation = chm_annot_list,
-        bottom_annotation_height = unit(5, "in"),
-        heatmap_legend_param = list(title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), title_position = "topcenter", legend_height = unit(2, "in")),
-        row_title = "Genes", column_title = "Cancer Cell Lines",
-        col = colorRamp2(c(min(chm_scores_cgc), 0, max(chm_scores_cgc)), c("purple4", "white", "seagreen4")),
-        na_col = "black",
-        row_title_gp = gpar(fontsize = 30, fontface = "bold"),
-        row_names_gp = gpar(fontsize = 5),
-        column_title_gp = gpar(fontsize = 30, fontface = "bold"),
-        column_names_gp = gpar(fontsize = 5),
-        row_dend_reorder = TRUE,
-        column_dend_reorder = TRUE,
-        clustering_distance_rows = "pearson",
-        clustering_distance_columns = "pearson",
-        clustering_method_rows = "complete",
-        clustering_method_columns = "complete",
-        column_dend_height = unit(2, "in"),
-        row_dend_width = unit(4, "in"),
-        width = 3)
-
-chm_plot_cgc_cols <- colnames(chm_scores_cgc)[unlist(column_order(chm_plot_cgc))]
-chm_plot_cgc_rows <- rownames(chm_scores_cgc)[unlist(row_order(chm_plot_cgc))]
-
-chm_ge_plot_cgc <- Heatmap(chm_ge_cgc, name = "Gene Expression",
-        col = colorRamp2(c(min(chm_ge_cgc[!is.na(chm_ge_cgc)]), 0, max(chm_ge_cgc[!is.na(chm_ge_cgc)])), c("dodgerblue4", "white", "firebrick4")),
-        heatmap_legend_param = list(title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), title_position = "topcenter", legend_height = unit(2, "in")),
-        na_col = "black",
-        cluster_rows = FALSE, cluster_columns = FALSE,
-        row_names_gp = gpar(fontsize = 5), show_column_names = FALSE,
-        column_title = "Gene Expression",
-        column_title_gp = gpar(fontsize = 30, fontface = "bold"),
-        column_order = chm_plot_cgc_cols,
-        row_order = chm_plot_cgc_rows,
-        width = 1)
-chm_cn_plot_cgc <- Heatmap(chm_cn_cgc, name = "Copy Number",
-        col = colorRamp2(c(min(chm_cn_cgc[!is.na(chm_cn_cgc)]), 0, max(chm_cn_cgc[!is.na(chm_cn_cgc)])), c("white", "thistle2", "mediumorchid4")),
-        heatmap_legend_param = list(title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), title_position = "topcenter", legend_height = unit(2, "in")),
-        na_col = "black",
-        cluster_rows = FALSE, cluster_columns = FALSE,
-        row_names_gp = gpar(fontsize = 5), show_column_names = FALSE,
-        column_title = "Copy Number",
-        column_title_gp = gpar(fontsize = 30, fontface = "bold"),
-        column_order = chm_plot_cgc_cols,
-        row_order = chm_plot_cgc_rows,
-        width = 1)
-chm_mut_plot_cgc <- Heatmap(chm_mut_cgc, name = "Mutation Status",
-        na_col = "black",
-        heatmap_legend_param = list(title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 15), at = c(0, 1), labels = c("Other", "Mutant"), title_position = "topcenter", grid_height = unit(0.3, "in")),
-        col = c("cyan3", "darkorchid"),
-        cluster_rows = FALSE, cluster_columns = FALSE,
-        row_names_gp = gpar(fontsize = 5), show_column_names = FALSE,
-        column_title = "Mutation Status",
-        column_title_gp = gpar(fontsize = 30, fontface = "bold"),
-        column_order = chm_plot_cgc_cols,
-        row_order = chm_plot_cgc_rows,
-        width = 1)
-
-chm_all_plot_cgc <- chm_plot_cgc + chm_ge_plot_cgc + chm_cn_plot_cgc + chm_mut_plot_cgc
-
-pdf("./plots_18Q3/crispr_heatmap_pearson_all_cgc.pdf", width = 50, height = 50, paper = "special")
-draw(chm_all_plot_cgc, heatmap_legend_side = "bottom", annotation_legend_side = "bottom")
-seekViewport("annotation_Cell_Line_SSMD")
-grid.text("Cell Line SSMD", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
-seekViewport("annotation_Cas9_Activity")
-grid.text("Cas9 Activity", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
-seekViewport("annotation_Culture_Type")
-grid.text("Culture Type", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
-seekViewport("annotation_Primary_Tissue")
-grid.text("Primary Tissue", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
-seekViewport("annotation_Primary_Disease")
-grid.text("Primary Disease", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
-seekViewport("annotation_Gender")
-grid.text("Gender", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
-seekViewport("annotation_Source")
-grid.text("Source", unit(1, "npc") + unit(1, "mm"), 0.5, gp = gpar(fontsize = 15), default.units = "npc", just = "left")
-dev.off()
-```
-
-# Per-gene plots
-
---------------------------------------------------------------------------------
-
-## Grouped plots
-
-```{r fig.height=12, fig.width=12, include=FALSE, eval=FALSE}
-makeCRISPRgrob("KRAS", filt_method = "all")
-```
-
-Plot code:
-```{r, eval=FALSE}
-crispr_lvlA_genes <- unique(crispr_data_cgc$Hugo_Symbol)
-crispr_all_groups <- lapply(crispr_all_genes, makeCRISPRgrob)
-crispr_all_groups_paths <- paste0(crispr_all_genes, "_crispr_grouped.png")
-pwalk(list(crispr_all_groups_paths, crispr_all_groups), ggsave, path = "./plots_18Q3/crispr_grouped_plots_cgc", dpi = 300, width = 12, height = 12, units = "in")
-```
-
-Data management:
-```{r, eval=FALSE}
-crispr_all_bygene <- paste0(list.files("./plots_18Q3/crispr_grouped_plots_cgc", full.names = TRUE))
-names(crispr_all_bygene) <- str_replace_all(crispr_all_bygene, c("_crispr_grouped.png" = "", "./plots_18Q3/crispr_grouped_plots_cgc/" = ""))
-crispr_bygene_order <- c(intersect(crispr_signif$Hugo_Symbol, names(crispr_all_bygene)), setdiff(names(crispr_all_bygene), crispr_signif$Hugo_Symbol))
-crispr_all_bygene <- crispr_all_bygene[match(crispr_bygene_order, names(crispr_all_bygene))]
-bsselect(crispr_all_bygene, type = "img", selected = "KRAS", live_search = TRUE, show_tick = TRUE, height = 300, frame_height = 275)
-```
-
-## Sorted lineage plots
-
-```{r fig.height=12, fig.width=12, include=FALSE, eval=FALSE}
-makeCRISPRlinplot("KRAS")
-```
-
-Plot code:
-```{r, eval=FALSE}
-crispr_data_cgc <- filter(crispr_data, Hugo_Symbol %in% cgc$Hugo_Symbol)
-crispr_all_genes <- unique(crispr_data_cgc$Hugo_Symbol)
-crispr_all_lins <- lapply(crispr_all_genes, makeCRISPRlinplot)
-crispr_all_lins_paths <- paste0(crispr_all_genes, "_crispr_lineage.png")
-pwalk(list(crispr_all_lins_paths, crispr_all_lins), ggsave, path = "./plots_18Q3/crispr_lineage_plots_cgc", dpi = 300, width = 12, height = 12, units = "in")
-```
-
-Data management:
-```{r, eval=FALSE}
-crispr_all_bygene <- paste0(list.files("./plots_18Q3/crispr_lineage_plots_cgc", full.names = TRUE))
-names(crispr_all_bygene) <- str_replace_all(crispr_all_bygene, c("_crispr_lineage.png" = "", "./plots_18Q3/crispr_lineage_plots_cgc/" = ""))
-crispr_bygene_order <- c(intersect(crispr_signif$Hugo_Symbol, names(crispr_all_bygene)), setdiff(names(crispr_all_bygene), crispr_signif$Hugo_Symbol))
-crispr_all_bygene <- crispr_all_bygene[match(crispr_bygene_order, names(crispr_all_bygene))]
-bsselect(crispr_all_bygene, type = "img", selected = "KRAS", live_search = TRUE, show_tick = TRUE, height = 300, frame_height = 275)
-```
-
-# Report #2
-
---------------------------------------------------------------------------------
-
-##  Metadata
-
-```{r, eval=FALSE}
-tissue_summ <- crispr_meta %>% group_by(primary_tissue) %>% tally()
-disease_summ <- ccl_info %>% group_by(Primary.Disease) %>% tally()
-```
-
-```{r fig.height=12, fig.width=3, eval=FALSE}
-ggplot(data = tissue_summ) + 
-  aes(x = 0, y = n, fill = primary_tissue, label = primary_tissue) +
-  geom_histogram(color = "black", stat = "identity") +
-  geom_text(position = position_stack(vjust = 0.5)) +
-  scale_y_continuous(breaks = seq(0, 500, by = 25), labels = seq(0, 500, by = 25)) +
-  coord_cartesian(ylim = c(0, 500)) +
-  theme(legend.position = "none", axis.text.x = element_blank(), axis.ticks.x = element_blank(), axis.title.x = element_blank()) +
-  labs(y = "Count")
-```
-
-```{r, include=FALSE, eval=FALSE}
-length(intersect(unique(crispr_data$Hugo_Symbol), unique(maf_df$Hugo_Symbol)))
-length(intersect(unique(crispr_data$Hugo_Symbol), unique(cn_melt$Hugo_Symbol)))
-length(intersect(unique(crispr_data$Hugo_Symbol), unique(ge_melt$Hugo_Symbol)))
-
-length(intersect(unique(crispr_data$Broad_ID), unique(maf_df$Broad_ID)))
-length(intersect(unique(crispr_data$Broad_ID), unique(cn_melt$Broad_ID)))
-length(intersect(unique(crispr_data$Broad_ID), unique(ge_melt$Broad_ID)))
-
-setdiff(unique(crispr_data$Broad_ID), unique(maf_df$Broad_ID))
-setdiff(unique(crispr_data$Broad_ID), unique(cn_melt$Broad_ID))
-setdiff(unique(crispr_data$Broad_ID), unique(ge_melt$Broad_ID))
-
-length(intersect(intersect(unique(crispr_data$Broad_ID), unique(cn_melt$Broad_ID)), unique(ge_melt$Broad_ID)))
-setdiff(crispr_data$Broad_ID, intersect(intersect(unique(crispr_data$Broad_ID), unique(cn_melt$Broad_ID)), unique(ge_melt$Broad_ID)))
-```
-
-## Scores
-
-Distribution of scores across cell lines and primary tissues. Each data point represents a single cell line.
-```{r fig.height=4, fig.width=12}
-ceres_summ <- crispr_data %>% group_by(primary_tissue) %>% summarize(Max = max(Score),
-                                                                     Min = min(Score))
-score_summ_plot <- ggplot(data = crispr_data, aes(x = primary_tissue, color = primary_tissue)) +
-  geom_boxplot(mapping = aes(y = Score), outlier.shape = NA) +
-  geom_point(data = ceres_summ, mapping = aes(x = primary_tissue, y = Min)) +
-  geom_point(data = ceres_summ, mapping = aes(x = primary_tissue, y = Max)) +
-  scale_y_continuous(breaks = seq(-4, 6, by = 1), labels = seq(-4, 6, by = 1)) +
-  theme(axis.text.x = element_text(angle = 30, hjust = 1), legend.position = "none") +
-  labs(x = "Primary Tissue", y = "CERES Score")
-score_summ_plot
-# ggsave(filename = "./plots_18Q3/crispr/ceres_score_summ_plot.pdf", plot = score_summ_plot, width = 12, height = 4, device = "pdf")
-```
-
-## Mutations
-
-```{r}
-maf_df_filt <- filter(maf_df, Hugo_Symbol %in% unique(crispr_data$Hugo_Symbol))
-# maf_summ_filt <- maf_df_filt %>% group_by(Mutation_Status) %>% tally()
-# maf_summ_filt$Percent <- format(round(maf_summ_filt$n / sum(maf_summ_filt$n) * 100, 4), nsmall = 2)
-# maf_summ_filt$Percent <- as.numeric(as.character(maf_summ_filt$Percent))
-```
-
-Distribution of mutations across cell lines and primary tissues. Each data point represents a single cell line.
-```{r fig.height=4, fig.width=10}
-maf_ccl_annot <- merge(maf_df %>% group_by(Broad_ID) %>% tally(), crispr_meta, by = "Broad_ID", all.y = TRUE)
-
-maf_ccl_annot_plot <- ggplot(data = maf_ccl_annot, aes(x = primary_tissue, y = n, color = primary_tissue)) +
-  geom_boxplot(outlier.shape = NA, fill = NA) +
-  geom_jitter(alpha = 0.7, size = 1, position = position_jitter(w = 0.25)) +
-  scale_y_continuous(breaks = seq(0, 9000, by = 1000), labels = seq(0, 9000, by = 1000)) +
-  theme(axis.ticks.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), legend.position = "none") +
-  labs(x = "Primary Tissue", y = "Number of Mutations")
-maf_ccl_annot_plot
-# ggsave(filename = "./plots_18Q3/crispr/maf_ccl_annot_plot.pdf", plot = maf_ccl_annot_plot, width = 12, height = 4, device = "pdf")
-```
-
-```{r fig.height=8, fig.width=12}
-# ggsave(filename = "./plots_18Q3/crispr/score_mut_summ.pdf", plot = grid.draw(rbind(ggplotGrob(maf_ccl_annot_plot), ggplotGrob(score_summ_plot), size = "first")), width = 12, height = 8, device = "pdf")
-```
-
-```{r fig.height=6, fig.width=12}
-maf_gene_annot <- maf_df_filt %>% group_by(Hugo_Symbol) %>% tally()
-
-ggplot(data = maf_gene_annot, aes(x = n)) +
-  geom_histogram(breaks = seq(0, 600, by = 20), fill = "darkslategray3", color = "black", alpha = 0.7) +
-  coord_cartesian(ylim = c(0, 13000)) +
-  scale_y_continuous(breaks = seq(0, 13500, by = 500), labels = formatC(seq(0, 13500, by = 500), format = "d")) +
-  scale_x_continuous(breaks = seq(0, 600, by = 20), labels = seq(0, 600, by = 20)) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-  stat_bin(breaks = seq(0, 600, by = 20), geom = "text", colour = "black", size = 2.5, aes(label = ..count..), vjust = -0.2, angle = 45, hjust = -0.1) +
-  labs(x = "Number of Mutations", y = "Frequency", title = paste0("Distribution of mutational load for ", length(unique(maf_gene_annot$Hugo_Symbol)), " genes in the CCLE MAF file across all ", length(unique(crispr_ccl$Broad_ID)), " cell lines in the CRISPR screen"))
-```
-
-## Dependency probabilities
-
-```{r fig.height=6, fig.width=12}
-drop_prob_100 <- ggplot(data = crispr_data, aes(x = Dep_Prob)) +
-  geom_histogram(breaks = seq(0, 1, by = 0.05), fill = "darkslategray3", color = "black", alpha = 0.7) +
-  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
-  scale_y_continuous(breaks = seq(0, 5500000, by = 500000), labels = formatC(seq(0, 5500000, by = 500000), format = "d")) +
-  stat_bin(breaks = seq(0, 1, by = 0.05), geom = "text", colour = "black", size = 3.5, aes(label = ..count..), vjust = -1) +
-  labs(title = "Distribution of all dependency probabilities", x = "Probability of Real Dependency", y = "Frequency")
-
-dep_prob_5 <- ggplot(data = filter(crispr_data, Dep_Prob >= 0.95), aes(x = Dep_Prob)) +
-  geom_histogram(mapping = aes(fill = primary_tissue), breaks = seq(0.95, 1, by = 0.005), color = "black") +
-  scale_y_continuous(breaks = seq(0, 60000, by = 10000), labels = formatC(seq(0, 60000, by = 10000), format = "d")) +
-  theme(legend.position = "bottom") +
-  guides(fill = guide_legend(nrow = 4, byrow = FALSE)) +
-  stat_bin(breaks = seq(0.95, 1, by = 0.005), geom = "text", color = "black", size = 3.5, aes(label = ..count..), vjust = -1) +
-  labs(title = "Distribution of all dependency probabilities > 0.95", x = "Probability of Real Dependency", y = "Frequency", fill = "Primary Tissue")
-```
-
-## Per-gene plots
-
-```{r fig.height=18, fig.width=5, eval=FALSE}
-sig_genes <- c("KRAS", "TP53", "NRAS", "BRAF", "PIK3CA", "PTEN", "CTNNB1")
-crispr_sig_genes <- filter(crispr_data, Hugo_Symbol %in% sig_genes)
-crispr_sig_genes$Hugo_Symbol <- factor(crispr_sig_genes$Hugo_Symbol, levels = c("KRAS", "TP53", "NRAS", "BRAF", "PIK3CA", "PTEN", "CTNNB1"))
-
-crispr_color <- as.character(crispr_sig_genes$Color)
-names(crispr_color) <- crispr_sig_genes$Mutation_Status
-
-# Mutation status
-plot_mut <- ggplot(data = crispr_sig_genes, aes(x = Mutation_Status, y = Score, color = Mutation_Status)) +
-  geom_boxplot(outlier.shape = NA) +
-  geom_jitter(alpha = 0.3, size = 0.7, position = position_jitter(w = 0.05)) +
-  facet_wrap(~ Hugo_Symbol, nrow = 7, scales = "free_y") +
-  scale_color_manual(values = crispr_color) +
-  geom_hline(yintercept = 0, linetype = 2, lwd = 0.3) +
-  theme_light() +
-  theme(legend.position = "none") +
-  labs(x = "Mutation Status", y = "CERES Score",
-       title = "Mutation Status")
-# plot_mut
-
-# Copy number
-plot_cn <- ggplot(data = crispr_sig_genes, aes(x = Copy_Number, y = Score, color = Mutation_Status)) +
-  geom_point(size = 0.5, alpha = 0.5) +
-  geom_smooth(method = "lm", size = 0.5) +
-  scale_color_manual(values = crispr_color) +
-  facet_wrap(~ Hugo_Symbol, nrow = 7, scales = "free") +
-  stat_cor(method = "pearson", show.legend = FALSE, label.x.npc = "right", label.y.npc = "top") +
-  theme_light() +
-  theme(legend.position = "none", axis.title.y = element_blank()) +
-  labs(y = "CERES Score", color = "Mutation Status",
-       x = "Theoretical Copy number", title = "Copy Number")
-# plot_cn
-
-# Gene expression
-plot_ge <- ggplot(data = crispr_sig_genes, aes(x = RPKM_log2, y = Score, color = Mutation_Status)) +
-  geom_point(size = 0.5, alpha = 0.5) +
-  geom_smooth(method = "lm", size = 0.5) +
-  facet_wrap(~ Hugo_Symbol, nrow = 7, scales = "free_y") +
-  scale_color_manual(values = crispr_color) +
-  stat_cor(method = "pearson", show.legend = FALSE, label.x.npc = "left", label.y.npc = "top") +
-  theme_light() +
-  theme(legend.position = "none", axis.title.y = element_blank()) +
-  labs(y = "CERES Score", color = "Mutation Status",
-       x = "Gene Expression [log2(RPKM)]",
-       title = "Gene Expression")
-# plot_ge
-
-# ggsave(filename = "./plots_18Q3/crispr/omics_sig_genes.pdf", plot = grid.draw(cbind(ggplotGrob(plot_mut), ggplotGrob(plot_ge), ggplotGrob(plot_cn), size = "last")), width = 15, height = 18, device = "pdf")
-```
-
-# shRNA
-
---------------------------------------------------------------------------------
-
-## Data and annotations
-
-DepMap cell line metadata:
-```{r, eval=FALSE}
-# From figshare
-shrna_meta <- read.delim("./data_munging/sample_info_18Q3_shrna.csv", sep = ",", header = TRUE, na.strings = c("", NA))
-colnames(shrna_meta)[1] <- "CCLE_Name"
-```
-
-The Achilles shRNA DEMETER score data was pulled from the [CTD^2^ Data Portal](https://ocg.cancer.gov/programs/ctd2/data-portal) (Tsherniak et al 2017).
-```{r, eval=FALSE}
-shrna <- read.table("./data_munging/D2_combined_gene_dep_scores.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
-colnames(shrna)[1] <- "Hugo_Symbol"
-# Remove Entrez gene IDs from gene names
-shrna$Hugo_Symbol <- gsub(" .*", "", shrna$Hugo_Symbol)
-
-# Melt shRNA dataset for merging
-shrna_melt <- melt(shrna , id.vars = "Hugo_Symbol", measure.vars = colnames(shrna)[2:ncol(shrna)], variable.name = "CCLE_Name", value.name = "Score")
-shrna_melt <- drop_na(shrna_melt)
-```
-
-Merge annotation data:
-```{r, eval=FALSE}
-# Merge cell line metadata
-shrna_melt <- merge(shrna_melt, ccl_info, by = "CCLE_Name", all.x = TRUE)
-shrna_melt <- merge(shrna_melt, shrna_meta, by = "CCLE_Name", all.x = TRUE)
-
-# Merge mutation annotations
-shrna_muts <- merge(shrna_melt, maf_df, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
-shrna_muts <- shrna_muts %>% mutate(Mutation_Status = if_else(is.na(Mutation_Status), "Other", Mutation_Status))
-shrna_muts$Hugo_Symbol <- factor(shrna_muts$Hugo_Symbol)
-
-# Summarize number of mutant and Other cell lines
-shrna_muts_summ <- shrna_muts %>% group_by(Hugo_Symbol) %>%
-  summarize(N_Other = sum(Mutation_Status == "Other"),
-            N_Mutant = sum(Mutation_Status == "Mutant"))
-
-# Merge test results back into full dataset, which restores information lost in the summarization
-shrna_data <- merge(shrna_muts_summ, shrna_muts, by = "Hugo_Symbol")
-
-# Add Color column
-shrna_data$Color <- ifelse(shrna_data$Mutation_Status == "Other", "cyan3", "darkorchid")
-shrna_data$Color <- factor(shrna_data$Color)
-
-# Cell line lineages
-shrna_data <- merge(shrna_data, ccl_converter, by = c("CCLE_Name", "Broad_ID"), all.x = TRUE)
-levels(shrna_data$lineage_name) <- sort(levels(shrna_data$lineage_name), decreasing = TRUE)
-
-# Copy number
-shrna_data <- merge(shrna_data, cn_melt, by = c("Hugo_Symbol", "Broad_ID"), all.x = TRUE)
-
-# Gene expression (RPKM)
-ge_filt <- filter(ge_melt, Hugo_Symbol %in% unique(shrna_data$Hugo_Symbol))
-shrna_data <- merge(shrna_data, ge_filt, by = c("Hugo_Symbol", "Broad_ID", "CCLE_Name"), all.x = TRUE)
-
-saveRDS(shrna_data, "./../crispr_lineages_giant_files/shrna_data_18Q3.rds", compress = "xz")
-```
-
-```{r, eval=FALSE}
-shrna_data <- readRDS("./../crispr_lineages_giant_files/shrna_data_18Q3.rds")
-shrna_ccl <- data.frame("Broad_ID" = shrna_data$Broad_ID)
-```
-
-## Wilcoxon tests
-
-### Grouped by gene
-
-```{r, eval=FALSE}
-shrna_signif <- compare_means(Score ~ Mutation_Status, group.by = c("Hugo_Symbol"), data = shrna_data, method = "wilcox.test", p.adjust.method = "BH")
-shrna_signif <- adj_signif(shrna_signif)
-shrna_signif <- shrna_signif[order(shrna_signif$p),]
-saveRDS(shrna_signif, "./data_munging/rds/shrna_signif.rds")
-```
-
-```{r, eval=FALSE}
-shrna_signif <- readRDS("./data_munging/rds/shrna_signif.rds")
-
-knitr::kable(filter(shrna_signif, p < 0.01)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "shRNA Screen: Wilcoxon Test Results Comparing Mutant and Other Cell Lines, p < 0.1  (Benjamini-Hochberg-corrected p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-### Grouped by gene and lineage
-
-```{r, eval=FALSE}
-shrna_signif_lineage <- compare_means(Score ~ Mutation_Status, group.by = c("Hugo_Symbol", "lineage_name"), data = shrna_data, method = "wilcox.test", p.adjust.method = "BH")
-shrna_signif_lineage <- adj_signif(shrna_signif_lineage)
-shrna_signif_lineage <- mutate(shrna_signif_lineage, lineage_name = reorder(lineage_name, p.adj, mean))
-saveRDS(shrna_signif_lineage, "./../crispr_lineages_giant_files/shrna_signif_lineage.rds")
-```
-
-```{r, eval=FALSE}
-shrna_signif_lineage <- readRDS("./../crispr_lineages_giant_files/shrna_signif_lineage.rds")
-```
-
-# References
-
---------------------------------------------------------------------------------
-
-Barretina, J., Caponigro, G., Stransky, N., Venkatesan, K., Margolin, A.
-A., Kim, S., … Garraway, L.
-A.
-(2012).
-The Cancer Cell Line Encyclopedia enables predictive modelling of anticancer drug sensitivity.
-Nature, 483(7391), 603–607.
-https://doi.org/10.1038/nature11003
-
-Broad Institute Cancer Dependency Map; Cancer Data Science (2018): Cancer Dependency Map, CRISPR Avana dataset 18Q3 (Avana_public_18Q3). figshare. Fileset. doi:10.6084/m9.figshare.6931364.v1
-
-Consortium, T. C. C. L. E., & Consortium, T. G. of D. S. in C. (2015). Pharmacogenomic agreement between two cancer cell line data sets. Nature, 528(7580), 84–87. https://doi.org/10.1038/nature15736
-
-Data Science, Cancer (2018): DEMETER2 data. figshare. Fileset. doi:10.6084/m9.figshare.6025238.v2
-
-Doench, J.
-G., Fusi, N., Sullender, M., Hegde, M., Vaimberg, E.
-W., Donovan, K.
-F., … Root, D.
-E.
-(2016).
-Optimized sgRNA design to maximize activity and minimize off-target effects of CRISPR-Cas9.
-Nature Biotechnology, 34(2), 184–191.
-https://doi.org/10.1038/nbt.3437
-
-Meyers, R.
-M., Bryan, J.
-G., McFarland, J.
-M., Weir, B.
-A., Sizemore, A.
-E., Xu, H., … Tsherniak, A.
-(2017).
-Computational correction of copy-number effect improves specificity of CRISPR-Cas9 essentiality screens in cancer cells.
-Nature Genetics, 49(12), 1779–1784.
-https://doi.org/10.1038/ng.3984
-
-McFarland, J.
-M., Ho, Z.
-V., Kugener, G., Dempster, J.
-M., Montgomery, P.
-G., Bryan, J.
-G., … Tsherniak, A.
-(2018).
-Improved estimation of cancer dependencies from large-scale RNAi screens using model-based normalization and data integration.
-https://doi.org/10.1101/305656
-
-# Session information
-
---------------------------------------------------------------------------------
-
-```{r}
-print(sessionInfo())
-```

### 2018-10-19 18Q3.Rmd
renamed and rearranged for manuscript.Rmd

@@
 ## Make drug screen boxplots
+
 ```{r}

### 2018-10-19 manuscript.Rmd

@@
 
-```{r, include=FALSE, eval=FALSE}
-# In a previous version of the shRNA screen, DEMETER ([GitHub](https://github.com/cancerdatasci/demeter)) was used to compute a dependency score for each gene by using the depletion values from each shRNA to infer the effect of target knockdown (on-target) and of expressing a given miRNA seed (off-target) in each cell line.
-More negative values indicate increased dependency, while more positive values indicate lower dependency.
-Zero represents the avergae dependency across all cell lines.
-# 
-# In the new data release, [DEMETER2](https://depmap.org/R2-D2/) ([GitHub repository](https://github.com/cancerdatasci/demeter2)), developed by McFarland et al.
-(2018) was used to analyze the Achilles screen.
-DEMETER2 expands on DEMETER by including parameters for cell-line-specific screen effects and noisy data, correcting for global differences in shRNA levels across cell lines, pooling data acorss cell lines via hierarchical modeling, and using Bayesian inference to compute uncertainty estimates.
-Now, a score of zero represents no dependency.
-```
-
 # Set up
@@
 ```
+
+```{r}
+library(bsselectR)
+library(data.table)
+library(ggpubr)
+library(ggsignif)
+library(kableExtra)
+library(tidyverse)
+```
+
+# Functions {.tabset .tabset-fade .tabset-pills}
+
+--------------------------------------------------------------------------------
+
+## Significance thresholding
+
+```{r}
+adj_signif <- function(df) {
+  # Takes df from compare_means and creates a signif code column for adjusted p-vals
+  df$p.signif <- ifelse(df$p.signif == "ns", NA, df$p.signif)
+  df$p.signif.adj <- ifelse(df$p.adj <= 0.0001, "****",
+                     ifelse(df$p.adj <= 0.001, "***",
+                     ifelse(df$p.adj <= 0.01, "**",
+                     ifelse(df$p.adj <= 0.05, "*", NA))))
+  df$p.short <- formatC(df$p, format = "g", digits =  2)
+  df$p.adj.short <- formatC(df$p.adj, format = "g", digits =  2)
+
+  return(df)
+}
+```
+
+## Wilcoxon tests by drug
+
+```{r}
+WilcoxonByDrug <- function(drug, dataset, data_name) {
+  use_data <- filter(dataset, Drug == drug)
+  sig <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = "Hugo_Symbol", data = use_data, method = "wilcox.test", p.adjust.method = "BH")
+  sig <- adj_signif(sig)
+  sig <- sig[order(sig$p),]
+  sig$Drug <- drug
+  sig$Dataset <- data_name
+  return(sig)
+}
+```
+
+# Data management {.tabset .tabset-fade .tabset-pills}
+
+--------------------------------------------------------------------------------
+
+## D. Charytonowicz cell line converter
+
+This comprehensive cancer cell line information curated by Daniel Charytonowicz.
+```{r}
+ccl_converter <- read.delim("./data_munging/cell_line_database_v1_20180911.tsv", row.names = 1, sep = "\t", header = TRUE)
+```
+
+## DepMap cell line metadata
+
+```{r}
+ccl_info <- read.delim("./data_munging/DepMap-2018q3-celllines.csv", sep = ",", header = TRUE, na.strings = c("", NA))
+ccl_info$Primary.Disease <- gsub("\\\\", "", ccl_info$Primary.Disease)
+ccl_info$Primary.Disease <- gsub("Ewings", "Ewing's", ccl_info$Primary.Disease)
+
+# From figshare
+crispr_meta <- read.delim("./data_munging/sample_info_18Q3_crispr.csv", sep = ",", header = TRUE, na.strings = c("", NA))
+colnames(crispr_meta)[7] <- "CCLE_Name"
+```
+
+## Genomic annotations
+
+### CCLE MAF file
+
+For mutation calling, get paired gene name and cell line fields in a data frame.
+For this analysis, we don't care about how many mutations there are per gene or what type of mutations there are, so I didn't save more information.
+I took unique gene-cell line combinations since we only cared about mutation presence/absence.
+Add a `Mutation_Status` column denoting all entries in MAF files as mutations present in the associated cell lines.
+```{r}
+maf_raw <- read.delim("./data_munging/CCLE_DepMap_18q3_maf_20180718.txt.gz", header = TRUE, sep = "\t")
+# Filter for cell lines in CRISPR screen
+maf_raw <- filter(maf_raw, Broad_ID %in% unique(crispr_meta$Broad_ID))
+colnames(maf_raw)[colnames(maf_raw) == "Tumor_Sample_Barcode"] <- "CCLE_Name"
+
+# Select columns
+maf_df <- subset(maf_raw, select = c("Hugo_Symbol", "CCLE_Name", "Broad_ID", "Variant_Classification", "Reference_Allele", "Tumor_Seq_Allele1"))
+maf_df$Reference_Allele_Length <- ifelse(maf_df$Reference_Allele == "-", 0, nchar(as.character(maf_df$Reference_Allele)))
+maf_df$Tumor_Seq_Allele1_Length <- nchar(as.character(maf_df$Tumor_Seq_Allele1))
+
+# Add Mutation_Status column
+maf_df$Mutation_Status_Nonsilent <- ifelse(maf_df$Variant_Classification == "Silent", "Other", "Mutant")
+maf_df <- unique(subset(maf_df, select = c("Hugo_Symbol", "CCLE_Name", "Broad_ID", "Mutation_Status_Nonsilent", "Reference_Allele_Length", "Tumor_Seq_Allele1_Length")))
+```
+
+### CCLE copy number file
+
+```{r, eval=FALSE}
+cn <- read.delim("./data_munging/public_18Q3_gene_cn_v2.csv.gz", sep = ",", check.names = FALSE, header = TRUE)
+
+# Convert log2 ratios (log2(CN/2)) to CN
+cn[2:ncol(cn)] <- lapply(cn[2:ncol(cn)], function(x) 2 * (2 ^ x))
+
+# Remove Entrez gene IDs from colnames
+colnames(cn) <- gsub(" .*", "", colnames(cn))
+colnames(cn)[1] <- "Broad_ID"
+
+# Melt
+cn_melt <- melt(data = cn, id.vars = "Broad_ID", measure.vars = colnames(cn[2:ncol(cn)]), variable.name = "Hugo_Symbol", value.name = "Copy_Number")
+
+saveRDS(cn_melt, "./data_munging/rds/cn_melt_18Q3.rds", compress = "xz")
+```
+
+```{r, eval=FALSE}
+cn_melt <- readRDS("./data_munging/rds/cn_melt_18Q3.rds")
+```
+
+### CCLE gene expression file
+
+Gene expression data (Reads Per Kilobase of transcript, per Million mapped reads, RPKM).
+```{r, eval=FALSE}
+ge <- read.delim("./../crispr_lineages_giant_files/CCLE_DepMap_18q3_RNAseq_RPKM_20180718.gct.gz", skip = 2, header = TRUE, sep = "\t", check.names = FALSE)
+
+# Edit columns
+ge$Name <- NULL
+colnames(ge)[1] <- "Hugo_Symbol"
+
+# Melt
+ge_melt <- melt(data = ge, id.vars = "Hugo_Symbol", measure.vars = colnames(ge[2:ncol(ge)]), value.name = "RPKM")
+## Split variable column
+ge_melt <- with(ge_melt, cbind(Hugo_Symbol, colsplit(variable, pattern = " ", names = c("CCLE_Name", "Broad_ID")), RPKM))
+## Remove parentheses around Broad IDs
+ge_melt$Broad_ID <- gsub("\\(|\\)", "", ge_melt$Broad_ID)
+
+saveRDS(ge_melt, "./../crispr_lineages_giant_files/ge_melt_18Q3.rds", compress = "xz")
+```
+
+```{r, eval=FALSE}
+ge_melt <- readRDS("./../crispr_lineages_giant_files/ge_melt_18Q3.rds")
+```
+
+## CRISPR
+
+### DepMap dependency probabilities
+
+```{r, eval=FALSE}
+dep <- read.delim("./data_munging/gene_dependency_18Q3.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
+# Remove Entrez gene IDs from colnames
+colnames(dep) <- gsub(" .*", "", colnames(dep))
+```
+
+### Merge CRISPR data and annotations
+
+The latest CRISPR CERES score data (18Q3, August 2018) was pulled from the [DepMap Data Portal](https://depmap.org/portal/download/) (Broad Institute Cancer Dependency Map 2018, Meyers et al. 2017).
+```{r, eval=TRUE}
+crispr <- read.delim("./data_munging/gene_effect_18Q3.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
+# Remove Entrez gene IDs from colnames
+colnames(crispr) <- gsub(" .*", "", colnames(crispr))
+```
+
+Merge annotation data:
+```{r, eval=FALSE}
+# Melt CRISPR dataset for merging
+crispr_melt <- melt(crispr, id.vars = "Broad_ID", measure.vars = colnames(crispr)[2:ncol(crispr)], variable.name = "Hugo_Symbol", value.name = "Score")
+# Melt dependency probabilities dataset for merging
+dep_melt <- melt(dep, id.vars = "Broad_ID", measure.vars = colnames(dep)[2:ncol(dep)], variable.name = "Hugo_Symbol", value.name = "Dep_Prob")
+# Merge dependency probabilities
+crispr_melt <- merge(crispr_melt, dep_melt, by = c("Broad_ID", "Hugo_Symbol"), all.x = TRUE)
+# Merge cell line metadata
+crispr_melt <- merge(crispr_melt, ccl_info, by = "Broad_ID", all.x = TRUE)
+crispr_melt <- merge(crispr_melt, crispr_meta, by = c("CCLE_Name", "Broad_ID"), all.x = TRUE)
+# Merge mutation annotations
+crispr_muts <- merge(crispr_melt, maf_df, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
+crispr_muts$Hugo_Symbol <- factor(crispr_muts$Hugo_Symbol)
+crispr_muts <- crispr_muts %>% mutate(Mutation_Status_Nonsilent = if_else(is.na(Mutation_Status_Nonsilent), "Other", Mutation_Status_Nonsilent))
+# Summarize number of mutant and Other cell lines
+crispr_muts_summ <- crispr_muts %>% group_by(Hugo_Symbol) %>%
+  summarize(N_Nonsilent_Other = sum(Mutation_Status_Nonsilent == "Other"),
+            N_Nonsilent_Mutant = sum(Mutation_Status_Nonsilent == "Mutant"))
+# Merge test results back into full dataset, which restores information lost in the summarization
+crispr_data <- merge(crispr_muts_summ, crispr_muts, by = "Hugo_Symbol")
+# Add Color columns
+crispr_data$Color_Nonsilent <- ifelse(crispr_data$Mutation_Status_Nonsilent == "Other", "thistle", "darkorchid")
+crispr_data$Color_Nonsilent <- factor(crispr_data$Color_Nonsilent)
+# Cell line lineages
+crispr_data <- merge(crispr_data, ccl_converter, by = c("CCLE_Name", "Broad_ID"), all.x = TRUE)
+levels(crispr_data$lineage_name) <- sort(levels(crispr_data$lineage_name), decreasing = TRUE)
+# Copy number
+crispr_data <- merge(crispr_data, cn_melt, by = c("Hugo_Symbol", "Broad_ID"), all.x = TRUE)
+# Gene expression (RPKM)
+ge_filt <- filter(ge_melt, Hugo_Symbol %in% unique(crispr_data$Hugo_Symbol) & Broad_ID %in% unique(crispr_data$Broad_ID))
+crispr_data <- merge(crispr_data, ge_filt, by = c("Hugo_Symbol", "Broad_ID", "CCLE_Name"), all.x = TRUE)
+crispr_data$RPKM_log2 <- log2(crispr_data$RPKM + 0.0001)
+saveRDS(crispr_data, "./../crispr_lineages_giant_files/crispr_data_18Q3.rds", compress = "xz")
+```
+
+```{r}
+crispr_data <- readRDS("./../crispr_lineages_giant_files/crispr_data_18Q3.rds")
+crispr_ccl <- data.frame("Broad_ID" = crispr_data$Broad_ID)
+# write.table(crispr_data, file = "~/Desktop/crispr_data.tsv", quote = FALSE, sep = "\t")
+```
+
+## G2P
+
+```{r}
+g2p <- read.delim("./data_munging/g2p_full_level_A_dataset_v2_10_10_2018.tsv", sep = "\t", header = TRUE)
+g2p_genes_df <- data.frame(Hugo_Symbol = unique(g2p$Gene))
+g2p_genes <- unique(g2p$Gene)
+
+# Order and genes taken from pink heatmapo from Daniel's analyses
+g2p_genes_filt <- c("KRAS", "EGFR", "MET", "ALK", "BRAF", "ERBB2", "ABL1", "ROS1", "KIT", "DPYD", "PDGFRA", "RET", "BRCA1", "UGT1A1", "IDH2", "ESR1", "TPMT", "BRCA2", "PDGFRB", "G6PD", "PML", "TSC1", "FLT3", "ERBB3", "CYP19A1", "AKT1", "PTCH1", "MGMT", "DNMT3A", "MYD88", "PDGFB", "TSC2", "NPM1", "JAK2")
+```
+
+## Drug screens
+
+```{r, eval=FALSE}
+# Drug metadata
+drug_meta <- read.delim("./data_munging/drug_id_drug_name_table_10_12_2018.tsv", sep = "\t", header = FALSE)
+colnames(drug_meta) <- c("CID", "Drug")
+drug_meta$Drug <- tolower(drug_meta$Drug)
+maf_df_g2p <- filter(maf_df, Hugo_Symbol %in% g2p_genes)
+
+# CCLE
+ccle <- read.delim("./data_munging/data_drug_auc_ccle_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
+ccle <- merge(drug_meta, ccle, by = "CID")
+ccle_melt <- melt(ccle, id.vars = c("CID", "Drug"), measure.vars = colnames(ccle)[3:ncol(ccle)], variable.name = "accession_id", value.name = "AUC")
+ccle_grid <- expand.grid("accession_id" = unique(ccle_melt$accession_id), "Hugo_Symbol" = g2p_genes)
+ccle_data <- merge(ccle_grid, ccle_melt, by = "accession_id", all.x = TRUE)
+ccle_data <- merge(ccle_data, ccl_converter, by = "accession_id", all.x = TRUE)
+ccle_data <- merge(ccle_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
+ccle_data$Mutation_Status_Nonsilent <- ifelse(is.na(ccle_data$Mutation_Status_Nonsilent), "Other", ccle_data$Mutation_Status_Nonsilent)
+ccle_data$Hugo_Symbol <- factor(ccle_data$Hugo_Symbol)
+ccle_data$AUC <- as.numeric(ccle_data$AUC)
+ccle_data$Color_Nonsilent <- ifelse(ccle_data$Mutation_Status_Nonsilent == "Other", "palegreen3", "springgreen4")
+ccle_data$Color_Nonsilent <- factor(ccle_data$Color_Nonsilent)
+ccle_data <- filter(ccle_data, !is.na(ccle_data$AUC))
+saveRDS(ccle_data, "./data_munging/rds/ccle_data_18Q3.rds", compress = "xz")
+
+# CTRP
+ctrp <- read.delim("./data_munging/data_drug_auc_ctrp_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
+ctrp <- merge(drug_meta, ctrp, by = "CID")
+ctrp_melt <- melt(ctrp, id.vars = c("CID", "Drug"), measure.vars = colnames(ctrp)[3:ncol(ctrp)], variable.name = "accession_id", value.name = "AUC")
+ctrp_grid <- expand.grid("accession_id" = unique(ctrp_melt$accession_id), "Hugo_Symbol" = g2p_genes)
+ctrp_data <- merge(ctrp_grid, ctrp_melt, by = "accession_id", all.x = TRUE)
+ctrp_data <- merge(ctrp_data, ccl_converter, by = "accession_id", all.x = TRUE)
+ctrp_data <- merge(ctrp_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
+ctrp_data$Mutation_Status_Nonsilent <- ifelse(is.na(ctrp_data$Mutation_Status_Nonsilent), "Other", ctrp_data$Mutation_Status_Nonsilent)
+ctrp_data$Hugo_Symbol <- factor(ctrp_data$Hugo_Symbol)
+ctrp_data$AUC <- as.numeric(ctrp_data$AUC)
+ctrp_data$Color_Nonsilent <- ifelse(ctrp_data$Mutation_Status_Nonsilent == "Other", "slategray3", "steelblue4")
+ctrp_data$Color_Nonsilent <- factor(ctrp_data$Color_Nonsilent)
+ctrp_data <- filter(ctrp_data, !is.na(ctrp_data$AUC))
+saveRDS(ctrp_data, "./data_munging/rds/ctrp_data_18Q3.rds", compress = "xz")
+
+# GDSC
+gdsc <- read.delim("./data_munging/data_drug_auc_gdsc_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
+gdsc <- merge(drug_meta, gdsc, by = "CID")
+gdsc_melt <- melt(gdsc, id.vars = c("CID", "Drug"), measure.vars = colnames(gdsc)[3:ncol(gdsc)], variable.name = "accession_id", value.name = "AUC")
+gdsc_grid <- expand.grid("accession_id" = unique(gdsc_melt$accession_id), "Hugo_Symbol" = g2p_genes)
+gdsc_data <- merge(gdsc_grid, gdsc_melt, by = "accession_id", all.x = TRUE)
+gdsc_data <- merge(gdsc_data, ccl_converter, by = "accession_id", all.x = TRUE)
+gdsc_data <- merge(gdsc_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
+gdsc_data$Mutation_Status_Nonsilent <- ifelse(is.na(gdsc_data$Mutation_Status_Nonsilent), "Other", gdsc_data$Mutation_Status_Nonsilent)
+gdsc_data$Hugo_Symbol <- factor(gdsc_data$Hugo_Symbol)
+gdsc_data$AUC <- as.numeric(gdsc_data$AUC)
+gdsc_data$Color_Nonsilent <- ifelse(gdsc_data$Mutation_Status_Nonsilent == "Other", "paleturquoise3", "turquoise4")
+gdsc_data$Color_Nonsilent <- factor(gdsc_data$Color_Nonsilent)
+gdsc_data <- filter(gdsc_data, !is.na(gdsc_data$AUC))
+saveRDS(gdsc_data, "./data_munging/rds/gdsc_data_18Q3.rds", compress = "xz")
+```
+
+```{r}
+ccle_data <- readRDS("./data_munging/rds/ccle_data_18Q3.rds")
+ctrp_data <- readRDS("./data_munging/rds/ctrp_data_18Q3.rds")
+gdsc_data <- readRDS("./data_munging/rds/gdsc_data_18Q3.rds")
+```
+
+# Gene mutation frequency
+
+--------------------------------------------------------------------------------
+
+```{r}
+crispr_data_ptmuts <- filter(crispr_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
+crispr_data_ptmuts$Keep_PtMut_Tests <- ifelse(crispr_data_ptmuts$Reference_Allele_Length == 1 | is.na(crispr_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(crispr_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
+crispr_data_ptmuts <- filter(crispr_data_ptmuts, Keep_PtMut_Tests == TRUE)
+
+crispr_data_g2p <- filter(crispr_data_ptmuts, Hugo_Symbol %in% g2p_genes)
+crispr_data_g2p_summ <- unique(crispr_data_g2p[, c("Hugo_Symbol", "N_Nonsilent_Mutant", "N_Nonsilent_Other")])
+crispr_data_g2p_summ$Fraction_Mutant <- crispr_data_g2p_summ$N_Nonsilent_Mutant / (crispr_data_g2p_summ$N_Nonsilent_Mutant + crispr_data_g2p_summ$N_Nonsilent_Other)
+crispr_data_g2p_summ$Percent_Mutant <- crispr_data_g2p_summ$Fraction_Mutant * 100
+# write.table(crispr_data_g2p_summ, file = "~/Desktop/crispr_data_g2p_summ_20181003.tsv", quote = FALSE, sep = "\t")
+```
+
+# Wilcoxon tests
+
+--------------------------------------------------------------------------------
+
+## CRISPR: Gene
+
+```{r, eval=TRUE}
+crispr_signif_g2p_gene <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol"), data = crispr_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
+crispr_signif_g2p_gene <- adj_signif(crispr_signif_g2p_gene)
+crispr_signif_g2p_gene <- crispr_signif_g2p_gene[order(crispr_signif_g2p_gene$p),]
+saveRDS(crispr_signif_g2p_gene, "./data_munging/rds/crispr_signif_g2p_gene.rds")
+```
+
+```{r, eval=TRUE}
+crispr_signif_g2p_gene <- readRDS("./data_munging/rds/crispr_signif_g2p_gene.rds")
+
+crispr_signif_g2p_20gene <- as.character(crispr_signif_g2p_gene$Hugo_Symbol[0:20])
+
+knitr::kable(filter(crispr_signif_g2p_gene, p < 0.1)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results for Level A point mutations, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+```{r fig.height=7, fig.width=12}
+crispr_data_signif_g2p_20gene <- filter(crispr_data_ptmuts, Hugo_Symbol %in% crispr_signif_g2p_20gene)
+crispr_data_signif_g2p_20gene <- merge(crispr_data_signif_g2p_20gene, crispr_signif_g2p_gene, by = "Hugo_Symbol")
+crispr_data_signif_g2p_20gene$Hugo_Symbol <- ordered(crispr_data_signif_g2p_20gene$Hugo_Symbol, levels = crispr_signif_g2p_20gene)
+crispr_data_signif_g2p_20gene_color <- as.character(crispr_data_signif_g2p_20gene$Color_Nonsilent)
+names(crispr_data_signif_g2p_20gene_color) <- crispr_data_signif_g2p_20gene$Mutation_Status_Nonsilent
+crispr_data_signif_g2p_20gene <- merge(crispr_data_signif_g2p_20gene, crispr_data_signif_g2p_20gene %>% group_by(Hugo_Symbol) %>% summarize(Text_y = max(Score)), by = "Hugo_Symbol")
+
+crispr_data_signif_g2p_20gene_text <- unique(data.frame(p.signif.adj = crispr_data_signif_g2p_20gene$p.signif.adj, Hugo_Symbol = crispr_data_signif_g2p_20gene$Hugo_Symbol, Text_y = crispr_data_signif_g2p_20gene$Text_y))
+crispr_data_signif_g2p_20gene$Hugo_Symbol <- factor(crispr_data_signif_g2p_20gene$Hugo_Symbol, levels = crispr_data_signif_g2p_20gene)
+
+crispr_data_signif_g2p_20gene_plot <- ggplot(data = crispr_data_signif_g2p_20gene, aes(x = Mutation_Status_Nonsilent, y = Score)) +
+  facet_wrap(~ Hugo_Symbol, nrow = 2, scales = "free_y") +
+  geom_jitter(aes(color = Mutation_Status_Nonsilent), alpha = 0.5, width = 0.3) +
+  geom_boxplot(color = "black", fill = NA, outlier.shape = NA) +
+  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
+  scale_color_manual(values = crispr_data_signif_g2p_20gene_color) + 
+  geom_text(data = crispr_data_signif_g2p_20gene_text, mapping = aes(x = 1.5, y = Text_y, label = p.signif.adj), nudge_y = 0.2) +
+  theme(legend.position = "top") +
+  labs(y = "CERES Score",
+       x = "Lineage",
+       color = "Mutation Status",
+       title = "CERES scores for select Level A G2P genes",
+       subtitle = "Genes with adjusted p-values < 0.3 are shown.\nBH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001\nGenes are sorted by increasing p-value.")
+crispr_data_signif_g2p_20gene_plot
+
+# ggsave("./plots_18Q3/manuscript/crispr_data_signif_g2p_20gene_plot.png", crispr_data_signif_g2p_20gene_plot, width = 12, height = 7, units = "in")
+```
+
+## CRISPR: Gene and lineage
+
+```{r, eval=TRUE}
+crispr_signif_g2p_lineage <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "group_general_lineage_name"), data = crispr_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
+crispr_signif_g2p_lineage <- adj_signif(crispr_signif_g2p_lineage)
+crispr_signif_g2p_lineage <- crispr_signif_g2p_lineage[order(crispr_signif_g2p_lineage$p),]
+saveRDS(crispr_signif_g2p_lineage, "./data_munging/rds/crispr_signif_g2p_lineage.rds")
+
+# write.table(crispr_signif_g2p_lineage, file = "~/Desktop/crispr_signif_g2p_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
+```
+
+```{r, eval=TRUE}
+crispr_signif_g2p_lineage <- readRDS("./data_munging/rds/crispr_signif_g2p_lineage.rds")
+
+knitr::kable(filter(crispr_signif_g2p_lineage, p < 0.01)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant vs other cell lines by lineage, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+```{r fig.height=15, fig.width=15}
+crispr_data_signif_g2p_lineage <- merge(crispr_data_signif_g2p_20gene, crispr_signif_g2p_lineage, by = c("Hugo_Symbol", "group_general_lineage_name"))
+crispr_data_signif_g2p_lineage$Hugo_Symbol <- ordered(crispr_data_signif_g2p_lineage$Hugo_Symbol, levels = crispr_signif_g2p_20gene)
+crispr_data_signif_g2p_lineage_color <- as.character(crispr_data_signif_g2p_lineage$Color_Nonsilent)
+names(crispr_data_signif_g2p_lineage_color) <- crispr_data_signif_g2p_lineage$Mutation_Status_Nonsilent
+crispr_data_signif_g2p_lineage <- merge(crispr_data_signif_g2p_lineage, crispr_data_signif_g2p_lineage %>% group_by(Hugo_Symbol) %>% summarize(Text_y = max(Score)), by = "Hugo_Symbol")
+
+crispr_data_signif_g2p_lineage_text <- unique(data.frame(p.signif.adj = crispr_data_signif_g2p_lineage$p.signif.adj, group_general_lineage_name = crispr_data_signif_g2p_lineage$group_general_lineage_name, Hugo_Symbol = crispr_data_signif_g2p_lineage$Hugo_Symbol, Text_y = crispr_data_signif_g2p_lineage$Text_y))
+crispr_data_signif_g2p_lineage_text$Hugo_Symbol <- factor(crispr_data_signif_g2p_lineage_text$Hugo_Symbol, levels = crispr_signif_g2p_20gene)
+
+crispr_data_signif_g2p_lineage_plot <- ggplot(data = crispr_data_signif_g2p_lineage, aes(x = group_general_lineage_name, y = Score)) +
+  facet_wrap(~ Hugo_Symbol, nrow = 4, scales = "free_y") +
+  geom_point(aes(color = Mutation_Status_Nonsilent), alpha = 0.5) +
+  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
+  scale_color_manual(values = crispr_data_signif_g2p_lineage_color) +
+  geom_text(data = crispr_data_signif_g2p_lineage_text, mapping = aes(x = group_general_lineage_name, y = Text_y, label = p.signif.adj), nudge_y = 0.1) +
+  theme(legend.position = "top", axis.text.x = element_text(angle = 90, hjust = 1, vjust = 1, size = 10)) +
+  labs(y = "CERES Score",
+       x = "Lineage",
+       color = "Mutation Status",
+       title = "CERES score by cell line lineage for significant Level A G2P genes",
+       subtitle = "Genes with adjusted p-values < 0.3 are shown.\nBH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001\nGenes are sorted by increasing lineage-agnostic p-value.")
+crispr_data_signif_g2p_lineage_plot
+
+# ggsave("./plots_18Q3/manuscript/crispr_crispr_data_signif_g2p_lineage_plot.png", crispr_data_signif_g2p_lineage_plot, width = 12, height = 15, units = "in")
+```
+
+```{r}
+crispr_data_signif_g2p_lineage_summ <- crispr_data_signif_g2p_lineage %>% group_by(Hugo_Symbol, group_general_lineage_name, Mutation_Status_Nonsilent) %>% tally()
+# write.table(crispr_data_signif_g2p_lineage_summ, file = "~/Desktop/crispr_data_signif_g2p_lineage_summ_20181005.tsv", quote = FALSE, sep = "\t")
+
+knitr::kable(crispr_data_signif_g2p_lineage_summ, caption = "Mutant/Other counts for gene-lineage combinations") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+## CCLE: Gene and drug
+
+```{r}
+ccle_data_ptmuts <- filter(ccle_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
+ccle_data_ptmuts$Keep_PtMut_Tests <- ifelse(ccle_data_ptmuts$Reference_Allele_Length == 1 | is.na(ccle_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(ccle_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
+ccle_data_ptmuts <- filter(ccle_data_ptmuts, Keep_PtMut_Tests == TRUE)
+
+ccle_data_g2p <- filter(ccle_data_ptmuts, Hugo_Symbol %in% g2p_genes)
+```
+
+```{r, eval=TRUE}
+ccle_signif_g2p_ByDrug <- lapply(unique(ccle_data_g2p$Drug), WilcoxonByDrug, dataset = ccle_data_g2p, data_name = "CCLE")
+names(ccle_signif_g2p_ByDrug) <- unique(ccle_data_g2p$Drug)
+saveRDS(ccle_signif_g2p_ByDrug, "./data_munging/rds/ccle_signif_g2p_ByDrug.rds")
+
+ccle_signif_g2p <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = c("Drug", "Hugo_Symbol"), data = ccle_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
+ccle_signif_g2p <- adj_signif(ccle_signif_g2p)
+ccle_signif_g2p <- ccle_signif_g2p[order(ccle_signif_g2p$p),]
+saveRDS(ccle_signif_g2p, "./data_munging/rds/ccle_signif_g2p_gene.rds")
+```
+
+```{r, eval=TRUE}
+ccle_signif_g2p <- readRDS("./data_munging/rds/ccle_signif_g2p_gene.rds")
+
+knitr::kable(ccle_signif_g2p[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for Level A point mutations, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+```{r}
+ccle_signif_g2p_ByDrug <- readRDS("./data_munging/rds/ccle_signif_g2p_ByDrug.rds")
+ccle_signif_g2p_ByDrug_all <- rbindlist(ccle_signif_g2p_ByDrug, use.names = TRUE)
+ccle_signif_g2p_ByDrug_all <- ccle_signif_g2p_ByDrug_all[order(ccle_signif_g2p_ByDrug_all$p.adj),]
+
+knitr::kable(ccle_signif_g2p_ByDrug_all[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: by-drug Wilcoxon test results for Level A point mutations, (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+## CTRP: Gene and drug
+
+```{r}
+ctrp_data_ptmuts <- filter(ctrp_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
+ctrp_data_ptmuts$Keep_PtMut_Tests <- ifelse(ctrp_data_ptmuts$Reference_Allele_Length == 1 | is.na(ctrp_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(ctrp_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
+ctrp_data_ptmuts <- filter(ctrp_data_ptmuts, Keep_PtMut_Tests == TRUE)
+ctrp_data_g2p <- filter(ctrp_data_ptmuts, Hugo_Symbol %in% g2p_genes)
+```
+
+```{r, eval=TRUE}
+ctrp_signif_g2p_ByDrug <- lapply(unique(ctrp_data_g2p$Drug), WilcoxonByDrug, dataset = ctrp_data_g2p, data_name = "CTRP")
+names(ctrp_signif_g2p_ByDrug) <- unique(ctrp_data_g2p$Drug)
+saveRDS(ctrp_signif_g2p_ByDrug, "./data_munging/rds/ctrp_signif_g2p_ByDrug.rds")
+
+ctrp_signif_g2p <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = c("Drug", "Hugo_Symbol"), data = ctrp_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
+ctrp_signif_g2p <- adj_signif(ctrp_signif_g2p)
+ctrp_signif_g2p <- ctrp_signif_g2p[order(ctrp_signif_g2p$p),]
+saveRDS(ctrp_signif_g2p, "./data_munging/rds/ctrp_signif_g2p_gene.rds")
+```
+
+```{r, eval=TRUE}
+ctrp_signif_g2p <- readRDS("./data_munging/rds/ctrp_signif_g2p_gene.rds")
+
+knitr::kable(ctrp_signif_g2p[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for Level A point mutations, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+```{r}
+ctrp_signif_g2p_ByDrug <- readRDS("./data_munging/rds/ctrp_signif_g2p_ByDrug.rds")
+ctrp_signif_g2p_ByDrug_all <- rbindlist(ctrp_signif_g2p_ByDrug, use.names = TRUE)
+ctrp_signif_g2p_ByDrug_all <- ctrp_signif_g2p_ByDrug_all[order(ctrp_signif_g2p_ByDrug_all$p.adj),]
+
+knitr::kable(ctrp_signif_g2p_ByDrug_all[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: by-drug Wilcoxon test results for Level A point mutations, (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+## GDSC: Gene and drug
+
+```{r}
+gdsc_data_ptmuts <- filter(gdsc_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
+gdsc_data_ptmuts$Keep_PtMut_Tests <- ifelse(gdsc_data_ptmuts$Reference_Allele_Length == 1 | is.na(gdsc_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(gdsc_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
+gdsc_data_ptmuts <- filter(gdsc_data_ptmuts, Keep_PtMut_Tests == TRUE)
+gdsc_data_g2p <- filter(gdsc_data_ptmuts, Hugo_Symbol %in% g2p_genes)
+```
+
+```{r, eval=TRUE}
+gdsc_signif_g2p_ByDrug <- lapply(unique(gdsc_data_g2p$Drug), WilcoxonByDrug, dataset = gdsc_data_g2p, data_name = "GDSC")
+names(gdsc_signif_g2p_ByDrug) <- unique(gdsc_data_g2p$Drug)
+saveRDS(gdsc_signif_g2p_ByDrug, "./data_munging/rds/gdsc_signif_g2p_ByDrug.rds")
+
+gdsc_signif_g2p <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = c("Drug", "Hugo_Symbol"), data = gdsc_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
+gdsc_signif_g2p <- adj_signif(gdsc_signif_g2p)
+gdsc_signif_g2p <- gdsc_signif_g2p[order(gdsc_signif_g2p$p),]
+saveRDS(gdsc_signif_g2p, "./data_munging/rds/gdsc_signif_g2p_gene.rds")
+```
+
+```{r, eval=TRUE}
+gdsc_signif_g2p <- readRDS("./data_munging/rds/gdsc_signif_g2p_gene.rds")
+
+knitr::kable(gdsc_signif_g2p[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for Level A point mutations, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+```{r}
+gdsc_signif_g2p_ByDrug <- readRDS("./data_munging/rds/gdsc_signif_g2p_ByDrug.rds")
+gdsc_signif_g2p_ByDrug_all <- rbindlist(gdsc_signif_g2p_ByDrug, use.names = TRUE)
+gdsc_signif_g2p_ByDrug_all <- gdsc_signif_g2p_ByDrug_all[order(gdsc_signif_g2p_ByDrug_all$p.adj),]
+
+knitr::kable(gdsc_signif_g2p_ByDrug_all[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: by-drug Wilcoxon test results for Level A point mutations, (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+# Boxplots
+
+--------------------------------------------------------------------------------
+
+Mutation status boxplots for genes identified in G2P.
+
+## CRISPR
+
+```{r fig.height=7, fig.width=12}
+crispr_ptmuts_g2p_filt <- filter(crispr_data_ptmuts, Hugo_Symbol %in% g2p_genes_filt)
+crispr_ptmuts_g2p_filt$Hugo_Symbol <- ordered(crispr_ptmuts_g2p_filt$Hugo_Symbol, levels = g2p_genes_filt)
+crispr_ptmuts_g2p_filt_color <- as.character(crispr_ptmuts_g2p_filt$Color_Nonsilent)
+names(crispr_ptmuts_g2p_filt_color) <- crispr_ptmuts_g2p_filt$Mutation_Status_Nonsilent
+
+label_text <- data.frame(p.signif.adj = crispr_signif_g2p_gene$p.signif.adj, Hugo_Symbol = crispr_signif_g2p_gene$Hugo_Symbol)
+label_text <- filter(label_text, Hugo_Symbol %in% g2p_genes_filt)
+label_text$Hugo_Symbol <- factor(label_text$Hugo_Symbol, levels = g2p_genes_filt)
+
+crispr_ptmuts_g2p_filt_plot_faceted <- ggplot(data = crispr_ptmuts_g2p_filt, aes(x = Mutation_Status_Nonsilent, y = Score)) +
+  facet_wrap(~ Hugo_Symbol, drop = FALSE, nrow = 2) +
+             # ncol = length(g2p_genes)) +
+  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
+  geom_boxplot(mapping = aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85)) +
+  scale_fill_manual(values = crispr_ptmuts_g2p_filt_color) +
+  guides(color = FALSE) +
+  geom_text(data = label_text, mapping = aes(x = 1.5, y = 2, label = p.signif.adj), nudge_y = 0.1) +
+  theme(legend.position = "top", axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
+  labs(fill = "Mutation Status", y = "CERES Score", x = "Mutation Status")
+crispr_ptmuts_g2p_filt_plot_faceted
+# ggsave("./plots_18Q3/manuscript/crispr_ptmuts_g2p_filt_plot_faceted.png", crispr_ptmuts_g2p_filt_plot_faceted, device = "png", dpi = 450, width = 20, height = 4, units = "in")
+```
+
+## CCLE
+
+```{r fig.height=4, fig.width=20}
+ccle_ptmuts_g2p_filt <- filter(ccle_data_g2p, Hugo_Symbol %in% g2p_genes_filt)
+ccle_ptmuts_g2p_filt$Hugo_Symbol <- ordered(ccle_ptmuts_g2p_filt$Hugo_Symbol, levels = g2p_genes_filt)
+ccle_drugs <- as.character(unique(ccle_ptmuts_g2p_filt$Drug))
+```
+
+## CTRP
+
+```{r fig.height=4, fig.width=20}
+ctrp_ptmuts_g2p_filt <- filter(ctrp_data_g2p, Hugo_Symbol %in% g2p_genes_filt)
+ctrp_ptmuts_g2p_filt$Hugo_Symbol <- ordered(ctrp_ptmuts_g2p_filt$Hugo_Symbol, levels = g2p_genes_filt)
+ctrp_drugs <- as.character(unique(ctrp_ptmuts_g2p_filt$Drug))
+```
+
+## GDSC
+
+```{r fig.height=4, fig.width=20}
+gdsc_ptmuts_g2p_filt <- filter(gdsc_data_g2p, Hugo_Symbol %in% g2p_genes_filt)
+gdsc_ptmuts_g2p_filt$Hugo_Symbol <- ordered(gdsc_ptmuts_g2p_filt$Hugo_Symbol, levels = g2p_genes_filt)
+gdsc_drugs <- as.character(unique(gdsc_ptmuts_g2p_filt$Drug))
+```
+
+# CRISPR: Point mutation mapping
+
+--------------------------------------------------------------------------------
+
+Match specific point mutations.
+```{r fig.height=5, fig.width=20, eval=FALSE}
+g2p_indications <- filter(read.delim("./data_munging/data_mutation_associations_appended.csv", sep = "\t", header = TRUE), Evidence.Level == "A")
+maf_g2p_indications <- filter(maf_raw, Genome_Change %in% g2p_indications$MutationName)
+crispr_g2p_indications <- merge(crispr_data_ptmuts, maf_g2p_indications, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
+crispr_g2p_indications$Mutation_Status_Nonsilent <- ifelse(is.na(crispr_g2p_indications$Mutation_Status_Nonsilent), "Other", crispr_g2p_indications$Mutation_Status_Nonsilent)
+dup_g2p_indications <- filter(crispr_g2p_indications[, c("Hugo_Symbol", "CCLE_Name", "Broad_ID")] %>% group_by(Hugo_Symbol, CCLE_Name, Broad_ID) %>% tally(), n > 1)
+crispr_g2p_indications <- merge(crispr_g2p_indications, dup_g2p_indications, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
+crispr_g2p_indications$Genome_Change <- factor(crispr_g2p_indications$Genome_Change, levels = unique(crispr_g2p_indications$Genome_Change))
+crispr_g2p_indications_nonNA <- filter(crispr_g2p_indications, is.na(n))
+
+crispr_g2p_indications_plot <- ggplot(crispr_g2p_indications, aes(x = Hugo_Symbol, y = Score)) +
+  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
+  geom_boxplot(alpha = 0.5, color = "lightgray", outlier.shape = NA) +
+  geom_jitter(width = 0.3, mapping = aes(color = Mutation_Status_Nonsilent), size = 1) +
+  theme_light() +
+  theme(legend.title = element_blank()) +
+  labs(x = "Gene", y = "CERES Score")
+crispr_g2p_indications_plot
+
+crispr_g2p_indications_muts_plot <- ggplot(crispr_g2p_indications, aes(x = Protein_Change, y = Score)) +
+  facet_grid(~ Hugo_Symbol, scales = "free_x", space = "free") +
+  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
+  geom_boxplot(alpha = 0.5, color = "lightgray", outlier.shape = NA) +
+  geom_jitter(width = 0.1, mapping = aes(color = Mutation_Status_Nonsilent), size = 1) +
+  theme_light() +
+  theme(legend.title = element_blank(), axis.text.x = element_text(angle = 90, hjust = 1)) +
+  labs(x = "Gene", y = "CERES Score")
+crispr_g2p_indications_muts_plot
+
+# ggsave("./plots_18Q3/manuscript/crispr_g2p_indications_plot_test.png", crispr_g2p_indications_plot, width = 12, height = 5, units = "in")
+# ggsave("./plots_18Q3/manuscript/crispr_g2p_indications_muts_plot_test.png", crispr_g2p_indications_muts_plot, width = 20, height = 5, units = "in")
+```
+
+# References
+
+--------------------------------------------------------------------------------
+
+Barretina, J., Caponigro, G., Stransky, N., Venkatesan, K., Margolin, A.
+A., Kim, S., … Garraway, L.
+A.
+(2012).
+The Cancer Cell Line Encyclopedia enables predictive modelling of anticancer drug sensitivity.
+Nature, 483(7391), 603–607.
+https://doi.org/10.1038/nature11003
+
+Broad Institute Cancer Dependency Map; Cancer Data Science (2018): Cancer Dependency Map, CRISPR Avana dataset 18Q3 (Avana_public_18Q3). figshare. Fileset. doi:10.6084/m9.figshare.6931364.v1
+
+Consortium, T. C. C. L. E., & Consortium, T. G. of D. S. in C. (2015). Pharmacogenomic agreement between two cancer cell line data sets. Nature, 528(7580), 84–87. https://doi.org/10.1038/nature15736
+
+Data Science, Cancer (2018): DEMETER2 data. figshare. Fileset. doi:10.6084/m9.figshare.6025238.v2
+
+Doench, J.
+G., Fusi, N., Sullender, M., Hegde, M., Vaimberg, E.
+W., Donovan, K.
+F., … Root, D.
+E.
+(2016).
+Optimized sgRNA design to maximize activity and minimize off-target effects of CRISPR-Cas9.
+Nature Biotechnology, 34(2), 184–191.
+https://doi.org/10.1038/nbt.3437
+
+Meyers, R.
+M., Bryan, J.
+G., McFarland, J.
+M., Weir, B.
+A., Sizemore, A.
+E., Xu, H., … Tsherniak, A.
+(2017).
+Computational correction of copy-number effect improves specificity of CRISPR-Cas9 essentiality screens in cancer cells.
+Nature Genetics, 49(12), 1779–1784.
+https://doi.org/10.1038/ng.3984
+
+McFarland, J.
+M., Ho, Z.
+V., Kugener, G., Dempster, J.
+M., Montgomery, P.
+G., Bryan, J.
+G., … Tsherniak, A.
+(2018).
+Improved estimation of cancer dependencies from large-scale RNAi screens using model-based normalization and data integration.
+https://doi.org/10.1101/305656
+
+# Session information
+
+--------------------------------------------------------------------------------
+
+```{r}
+print(sessionInfo())
+```

### 2018-10-22 manuscript.Rmd
update plots and Wilcoxon tests w/ new G2P filtering

--- 2018-10-19 manuscript.Rmd
@@
 
-num_cores <- parallel::detectCores()
-options(mc.cores = num_cores, expressions = 5e5)
+# num_cores <- parallel::detectCores()
+options(mc.cores = parallel::detectCores(), expressions = 5e5)
 ```
+
+```{r}
+library(bsselectR)
+library(data.table)
+library(ggpubr)
+library(ggsignif)
+library(kableExtra)
+library(tidyverse)
+```
+
+# Functions {.tabset .tabset-fade .tabset-pills}
+
+--------------------------------------------------------------------------------
+
+## Significance thresholding
+
+```{r}
+adj_signif <- function(df) {
+  # Takes df from compare_means and creates a signif code column for adjusted p-vals
+  df$p.signif <- ifelse(df$p.signif == "ns", NA, df$p.signif)
+  df$p.signif.adj <- ifelse(df$p.adj <= 0.0001, "****",
+                     ifelse(df$p.adj <= 0.001, "***",
+                     ifelse(df$p.adj <= 0.01, "**",
+                     ifelse(df$p.adj <= 0.05, "*", NA))))
+  df$p.short <- formatC(df$p, format = "g", digits =  2)
+  df$p.adj.short <- formatC(df$p.adj, format = "g", digits =  2)
+
+  return(df)
+}
+```
+
+## Wilcoxon tests by drug
+
+```{r}
+WilcoxonByDrug <- function(drug, dataset, data_name) {
+  use_data <- filter(dataset, Drug == drug)
+  sig <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = "Hugo_Symbol", data = use_data, method = "wilcox.test", p.adjust.method = "BH")
+  sig <- adj_signif(sig)
+  sig <- sig[order(sig$p),]
+  sig$Drug <- drug
+  sig$Dataset <- data_name
+  return(sig)
+}
+```
+
+# Data management {.tabset .tabset-fade .tabset-pills}
+
+--------------------------------------------------------------------------------
+
+## D. Charytonowicz cell line converter
+
+This comprehensive cancer cell line information curated by Daniel Charytonowicz.
+```{r}
+ccl_converter <- read.delim("./data_munging/cell_line_database_v1_20180911.tsv", row.names = 1, sep = "\t", header = TRUE)
+```
+
+## DepMap cell line metadata
+
+```{r}
+ccl_info <- read.delim("./data_munging/DepMap-2018q3-celllines.csv", sep = ",", header = TRUE, na.strings = c("", NA))
+ccl_info$Primary.Disease <- gsub("\\\\", "", ccl_info$Primary.Disease)
+ccl_info$Primary.Disease <- gsub("Ewings", "Ewing's", ccl_info$Primary.Disease)
+
+# From figshare
+crispr_meta <- read.delim("./data_munging/sample_info_18Q3_crispr.csv", sep = ",", header = TRUE, na.strings = c("", NA))
+colnames(crispr_meta)[7] <- "CCLE_Name"
+```
+
+## Genomic annotations
+
+### CCLE MAF file
+
+For mutation calling, get paired gene name and cell line fields in a data frame.
+For this analysis, we don't care about how many mutations there are per gene or what type of mutations there are, so I didn't save more information.
+I took unique gene-cell line combinations since we only cared about mutation presence/absence.
+Add a `Mutation_Status` column denoting all entries in MAF files as mutations present in the associated cell lines.
+```{r}
+maf_raw <- read.delim("./data_munging/CCLE_DepMap_18q3_maf_20180718.txt.gz", header = TRUE, sep = "\t")
+# Filter for cell lines in CRISPR screen
+maf_raw <- filter(maf_raw, Broad_ID %in% unique(crispr_meta$Broad_ID))
+colnames(maf_raw)[colnames(maf_raw) == "Tumor_Sample_Barcode"] <- "CCLE_Name"
+
+# Select columns
+maf_df <- subset(maf_raw, select = c("Hugo_Symbol", "CCLE_Name", "Broad_ID", "Variant_Classification", "Reference_Allele", "Tumor_Seq_Allele1"))
+maf_df$Reference_Allele_Length <- ifelse(maf_df$Reference_Allele == "-", 0, nchar(as.character(maf_df$Reference_Allele)))
+maf_df$Tumor_Seq_Allele1_Length <- nchar(as.character(maf_df$Tumor_Seq_Allele1))
+
+# Add Mutation_Status column
+maf_df$Mutation_Status_Nonsilent <- ifelse(maf_df$Variant_Classification == "Silent", "Other", "Mutant")
+maf_df <- unique(subset(maf_df, select = c("Hugo_Symbol", "CCLE_Name", "Broad_ID", "Mutation_Status_Nonsilent", "Reference_Allele_Length", "Tumor_Seq_Allele1_Length")))
+```
+
+### CCLE copy number file
+
+```{r, eval=FALSE}
+cn <- read.delim("./data_munging/public_18Q3_gene_cn_v2.csv.gz", sep = ",", check.names = FALSE, header = TRUE)
+
+# Convert log2 ratios (log2(CN/2)) to CN
+cn[2:ncol(cn)] <- lapply(cn[2:ncol(cn)], function(x) 2 * (2 ^ x))
+
+# Remove Entrez gene IDs from colnames
+colnames(cn) <- gsub(" .*", "", colnames(cn))
+colnames(cn)[1] <- "Broad_ID"
+
+# Melt
+cn_melt <- melt(data = cn, id.vars = "Broad_ID", measure.vars = colnames(cn[2:ncol(cn)]), variable.name = "Hugo_Symbol", value.name = "Copy_Number")
+
+saveRDS(cn_melt, "./data_munging/rds/cn_melt_18Q3.rds", compress = "xz")
+```
+
+```{r, eval=FALSE}
+cn_melt <- readRDS("./data_munging/rds/cn_melt_18Q3.rds")
+```
+
+### CCLE gene expression file
+
+Gene expression data (Reads Per Kilobase of transcript, per Million mapped reads, RPKM).
+```{r, eval=FALSE}
+ge <- read.delim("./../crispr_lineages_giant_files/CCLE_DepMap_18q3_RNAseq_RPKM_20180718.gct.gz", skip = 2, header = TRUE, sep = "\t", check.names = FALSE)
+
+# Edit columns
+ge$Name <- NULL
+colnames(ge)[1] <- "Hugo_Symbol"
+
+# Melt
+ge_melt <- melt(data = ge, id.vars = "Hugo_Symbol", measure.vars = colnames(ge[2:ncol(ge)]), value.name = "RPKM")
+## Split variable column
+ge_melt <- with(ge_melt, cbind(Hugo_Symbol, colsplit(variable, pattern = " ", names = c("CCLE_Name", "Broad_ID")), RPKM))
+## Remove parentheses around Broad IDs
+ge_melt$Broad_ID <- gsub("\\(|\\)", "", ge_melt$Broad_ID)
+
+saveRDS(ge_melt, "./../crispr_lineages_giant_files/ge_melt_18Q3.rds", compress = "xz")
+```
+
+```{r, eval=FALSE}
+ge_melt <- readRDS("./../crispr_lineages_giant_files/ge_melt_18Q3.rds")
+```
+
+## G2P
+
+```{r}
+g2p <- read.delim("./data_munging/g2p_full_level_A_dataset_v2_10_10_2018.tsv", sep = "\t", header = TRUE)
+g2p$Drug <- tolower(g2p$Drug)
+g2p$Drug_Gene <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene), NA, paste0(g2p$Drug, "_", g2p$Gene))
+g2p <- subset(g2p, grepl("^CID", g2p$DrugID))
+
+g2p_drug_genes <- as.character(unique(g2p$Drug_Gene[!is.na(g2p$Drug_Gene)]))
+g2p_genes <- unique(sapply(strsplit(g2p_drug_genes, "_", fixed = TRUE), function(x) x[2]))
+g2p_drugs <- unique(sapply(strsplit(g2p_drug_genes, "_", fixed = TRUE), function(x) x[1]))
+
+g2p_genes
+g2p_drugs
+# Order and genes taken from pink heatmapo from Daniel's analyses
+# g2p_genes_filt <- c("KRAS", "EGFR", "MET", "ALK", "BRAF", "ERBB2", "ABL1", "ROS1", "KIT", "DPYD", "PDGFRA", "RET", "BRCA1", "UGT1A1", "IDH2", "ESR1", "TPMT", "BRCA2", "PDGFRB", "G6PD", "PML", "TSC1", "FLT3", "ERBB3", "CYP19A1", "AKT1", "PTCH1", "MGMT", "DNMT3A", "MYD88", "PDGFB", "TSC2", "NPM1", "JAK2")
+```
+
+## CRISPR
+
+### DepMap dependency probabilities
+
+```{r, eval=FALSE}
+dep <- read.delim("./data_munging/gene_dependency_18Q3.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
+# Remove Entrez gene IDs from colnames
+colnames(dep) <- gsub(" .*", "", colnames(dep))
+```
+
+### Merge CRISPR data and annotations
+
+The latest CRISPR CERES score data (18Q3, August 2018) was pulled from the [DepMap Data Portal](https://depmap.org/portal/download/) (Broad Institute Cancer Dependency Map 2018, Meyers et al. 2017).
+```{r, eval=TRUE}
+crispr <- read.delim("./data_munging/gene_effect_18Q3.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
+# Remove Entrez gene IDs from colnames
+colnames(crispr) <- gsub(" .*", "", colnames(crispr))
+```
+
+Merge annotation data:
+```{r, eval=FALSE}
+# Melt CRISPR dataset for merging
+crispr_melt <- melt(crispr, id.vars = "Broad_ID", measure.vars = colnames(crispr)[2:ncol(crispr)], variable.name = "Hugo_Symbol", value.name = "Score")
+# Melt dependency probabilities dataset for merging
+dep_melt <- melt(dep, id.vars = "Broad_ID", measure.vars = colnames(dep)[2:ncol(dep)], variable.name = "Hugo_Symbol", value.name = "Dep_Prob")
+# Merge dependency probabilities
+crispr_melt <- merge(crispr_melt, dep_melt, by = c("Broad_ID", "Hugo_Symbol"), all.x = TRUE)
+# Merge cell line metadata
+crispr_melt <- merge(crispr_melt, ccl_info, by = "Broad_ID", all.x = TRUE)
+crispr_melt <- merge(crispr_melt, crispr_meta, by = c("CCLE_Name", "Broad_ID"), all.x = TRUE)
+# Merge mutation annotations
+crispr_muts <- merge(crispr_melt, maf_df, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
+crispr_muts$Hugo_Symbol <- factor(crispr_muts$Hugo_Symbol)
+crispr_muts <- crispr_muts %>% mutate(Mutation_Status_Nonsilent = if_else(is.na(Mutation_Status_Nonsilent), "Other", Mutation_Status_Nonsilent))
+# Summarize number of mutant and Other cell lines
+crispr_muts_summ <- crispr_muts %>% group_by(Hugo_Symbol) %>%
+  summarize(N_Nonsilent_Other = sum(Mutation_Status_Nonsilent == "Other"),
+            N_Nonsilent_Mutant = sum(Mutation_Status_Nonsilent == "Mutant"))
+# Merge test results back into full dataset, which restores information lost in the summarization
+crispr_data <- merge(crispr_muts_summ, crispr_muts, by = "Hugo_Symbol")
+# Add Color columns
+crispr_data$Color_Nonsilent <- ifelse(crispr_data$Mutation_Status_Nonsilent == "Other", "thistle", "darkorchid")
+crispr_data$Color_Nonsilent <- factor(crispr_data$Color_Nonsilent)
+# Cell line lineages
+crispr_data <- merge(crispr_data, ccl_converter, by = c("CCLE_Name", "Broad_ID"), all.x = TRUE)
+levels(crispr_data$lineage_name) <- sort(levels(crispr_data$lineage_name), decreasing = TRUE)
+# Copy number
+crispr_data <- merge(crispr_data, cn_melt, by = c("Hugo_Symbol", "Broad_ID"), all.x = TRUE)
+# Gene expression (RPKM)
+ge_filt <- filter(ge_melt, Hugo_Symbol %in% unique(crispr_data$Hugo_Symbol) & Broad_ID %in% unique(crispr_data$Broad_ID))
+crispr_data <- merge(crispr_data, ge_filt, by = c("Hugo_Symbol", "Broad_ID", "CCLE_Name"), all.x = TRUE)
+crispr_data$RPKM_log2 <- log2(crispr_data$RPKM + 0.0001)
+saveRDS(crispr_data, "./../crispr_lineages_giant_files/crispr_data_18Q3.rds", compress = "xz")
+```
+
+```{r}
+crispr_data <- readRDS("./../crispr_lineages_giant_files/crispr_data_18Q3.rds")
+
+crispr_data_ptmuts <- filter(crispr_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
+crispr_data_ptmuts$Keep_PtMut_Tests <- ifelse(crispr_data_ptmuts$Reference_Allele_Length == 1 | is.na(crispr_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(crispr_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
+crispr_data_ptmuts <- filter(crispr_data_ptmuts, Keep_PtMut_Tests == TRUE)
+
+# Filter CRISPR for G2P genes in G2P
+crispr_data_g2p <- filter(crispr_data_ptmuts, Hugo_Symbol %in% g2p_genes)
+crispr_data_g2p$Hugo_Symbol <- factor(crispr_data_g2p$Hugo_Symbol, levels = g2p_genes)
+```
+
+## Drug screens
+
+```{r, eval=FALSE}
+# Drug metadata
+drug_meta <- read.delim("./data_munging/drug_id_drug_name_table_10_12_2018.tsv", sep = "\t", header = FALSE)
+colnames(drug_meta) <- c("CID", "Drug")
+drug_meta$Drug <- tolower(drug_meta$Drug)
+maf_df_g2p <- filter(maf_df, Hugo_Symbol %in% g2p_genes)
+
+# CCLE
+ccle <- read.delim("./data_munging/data_drug_auc_ccle_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
+ccle <- merge(drug_meta, ccle, by = "CID")
+ccle_melt <- melt(ccle, id.vars = c("CID", "Drug"), measure.vars = colnames(ccle)[3:ncol(ccle)], variable.name = "accession_id", value.name = "AUC")
+ccle_grid <- expand.grid("accession_id" = unique(ccle_melt$accession_id), "Hugo_Symbol" = g2p_genes)
+ccle_data <- merge(ccle_grid, ccle_melt, by = "accession_id", all.x = TRUE)
+ccle_data <- merge(ccle_data, ccl_converter, by = "accession_id", all.x = TRUE)
+ccle_data <- merge(ccle_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
+ccle_data$Mutation_Status_Nonsilent <- ifelse(is.na(ccle_data$Mutation_Status_Nonsilent), "Other", ccle_data$Mutation_Status_Nonsilent)
+ccle_data$Hugo_Symbol <- factor(ccle_data$Hugo_Symbol)
+ccle_data$AUC <- as.numeric(ccle_data$AUC)
+ccle_data$Color_Nonsilent <- ifelse(ccle_data$Mutation_Status_Nonsilent == "Other", "palegreen3", "springgreen4")
+ccle_data$Color_Nonsilent <- factor(ccle_data$Color_Nonsilent)
+ccle_data <- filter(ccle_data, !is.na(ccle_data$AUC))
+ccle_data$Drug_Gene <- paste0(ccle_data$Drug, "_", ccle_data$Hugo_Symbol)
+saveRDS(ccle_data, "./data_munging/rds/ccle_data_18Q3.rds", compress = "xz")
+
+# CTRP
+ctrp <- read.delim("./data_munging/data_drug_auc_ctrp_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
+ctrp <- merge(drug_meta, ctrp, by = "CID")
+ctrp_melt <- melt(ctrp, id.vars = c("CID", "Drug"), measure.vars = colnames(ctrp)[3:ncol(ctrp)], variable.name = "accession_id", value.name = "AUC")
+ctrp_grid <- expand.grid("accession_id" = unique(ctrp_melt$accession_id), "Hugo_Symbol" = g2p_genes)
+ctrp_data <- merge(ctrp_grid, ctrp_melt, by = "accession_id", all.x = TRUE)
+ctrp_data <- merge(ctrp_data, ccl_converter, by = "accession_id", all.x = TRUE)
+ctrp_data <- merge(ctrp_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
+ctrp_data$Mutation_Status_Nonsilent <- ifelse(is.na(ctrp_data$Mutation_Status_Nonsilent), "Other", ctrp_data$Mutation_Status_Nonsilent)
+ctrp_data$Hugo_Symbol <- factor(ctrp_data$Hugo_Symbol)
+ctrp_data$AUC <- as.numeric(ctrp_data$AUC)
+ctrp_data$Color_Nonsilent <- ifelse(ctrp_data$Mutation_Status_Nonsilent == "Other", "slategray3", "steelblue4")
+ctrp_data$Color_Nonsilent <- factor(ctrp_data$Color_Nonsilent)
+ctrp_data <- filter(ctrp_data, !is.na(ctrp_data$AUC))
+ctrp_data$Drug_Gene <- paste0(ctrp_data$Drug, "_", ctrp_data$Hugo_Symbol)
+saveRDS(ctrp_data, "./data_munging/rds/ctrp_data_18Q3.rds", compress = "xz")
+
+# GDSC
+gdsc <- read.delim("./data_munging/data_drug_auc_gdsc_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
+gdsc <- merge(drug_meta, gdsc, by = "CID")
+gdsc_melt <- melt(gdsc, id.vars = c("CID", "Drug"), measure.vars = colnames(gdsc)[3:ncol(gdsc)], variable.name = "accession_id", value.name = "AUC")
+gdsc_grid <- expand.grid("accession_id" = unique(gdsc_melt$accession_id), "Hugo_Symbol" = g2p_genes)
+gdsc_data <- merge(gdsc_grid, gdsc_melt, by = "accession_id", all.x = TRUE)
+gdsc_data <- merge(gdsc_data, ccl_converter, by = "accession_id", all.x = TRUE)
+gdsc_data <- merge(gdsc_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
+gdsc_data$Mutation_Status_Nonsilent <- ifelse(is.na(gdsc_data$Mutation_Status_Nonsilent), "Other", gdsc_data$Mutation_Status_Nonsilent)
+gdsc_data$Hugo_Symbol <- factor(gdsc_data$Hugo_Symbol)
+gdsc_data$AUC <- as.numeric(gdsc_data$AUC)
+gdsc_data$Color_Nonsilent <- ifelse(gdsc_data$Mutation_Status_Nonsilent == "Other", "paleturquoise3", "turquoise4")
+gdsc_data$Color_Nonsilent <- factor(gdsc_data$Color_Nonsilent)
+gdsc_data <- filter(gdsc_data, !is.na(gdsc_data$AUC))
+gdsc_data$Drug_Gene <- paste0(gdsc_data$Drug, "_", gdsc_data$Hugo_Symbol)
+saveRDS(gdsc_data, "./data_munging/rds/gdsc_data_18Q3.rds", compress = "xz")
+```
+
+```{r}
+ccle_data <- readRDS("./data_munging/rds/ccle_data_18Q3.rds")
+ccle_data_ptmuts <- filter(ccle_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
+ccle_data_ptmuts$Keep_PtMut_Tests <- ifelse(ccle_data_ptmuts$Reference_Allele_Length == 1 | is.na(ccle_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(ccle_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
+ccle_data_ptmuts <- filter(ccle_data_ptmuts, Keep_PtMut_Tests == TRUE)
+
+ctrp_data <- readRDS("./data_munging/rds/ctrp_data_18Q3.rds")
+ctrp_data_ptmuts <- filter(ctrp_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
+ctrp_data_ptmuts$Keep_PtMut_Tests <- ifelse(ctrp_data_ptmuts$Reference_Allele_Length == 1 | is.na(ctrp_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(ctrp_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
+ctrp_data_ptmuts <- filter(ctrp_data_ptmuts, Keep_PtMut_Tests == TRUE)
+
+gdsc_data <- readRDS("./data_munging/rds/gdsc_data_18Q3.rds")
+gdsc_data_ptmuts <- filter(gdsc_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
+gdsc_data_ptmuts$Keep_PtMut_Tests <- ifelse(gdsc_data_ptmuts$Reference_Allele_Length == 1 | is.na(gdsc_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(gdsc_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
+gdsc_data_ptmuts <- filter(gdsc_data_ptmuts, Keep_PtMut_Tests == TRUE)
+
+# Filter drug screen datasets for G2P drug-gene associations
+ccle_data_g2p <- filter(ccle_data_ptmuts, Drug_Gene %in% g2p_drug_genes)
+ctrp_data_g2p <- filter(ctrp_data_ptmuts, Drug_Gene %in% g2p_drug_genes)
+gdsc_data_g2p <- filter(gdsc_data_ptmuts, Drug_Gene %in% g2p_drug_genes)
+```
+
+# Gene mutation frequency
+
+--------------------------------------------------------------------------------
+
+```{r}
+crispr_data_g2p_summ <- unique(crispr_data_g2p[, c("Hugo_Symbol", "N_Nonsilent_Mutant", "N_Nonsilent_Other")])
+crispr_data_g2p_summ$Fraction_Mutant <- crispr_data_g2p_summ$N_Nonsilent_Mutant / (crispr_data_g2p_summ$N_Nonsilent_Mutant + crispr_data_g2p_summ$N_Nonsilent_Other)
+crispr_data_g2p_summ$Percent_Mutant <- crispr_data_g2p_summ$Fraction_Mutant * 100
+# write.table(crispr_data_g2p_summ, file = "~/Desktop/crispr_data_g2p_summ_20181003.tsv", quote = FALSE, sep = "\t")
+```
+
+# Wilcoxon tests
+
+--------------------------------------------------------------------------------
+
+## CRISPR: Gene
+
+```{r, eval=FALSE}
+crispr_signif_g2p_gene <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol"), data = crispr_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
+crispr_signif_g2p_gene <- adj_signif(crispr_signif_g2p_gene)
+crispr_signif_g2p_gene <- crispr_signif_g2p_gene[order(crispr_signif_g2p_gene$p),]
+saveRDS(crispr_signif_g2p_gene, "./data_munging/rds/crispr_signif_g2p_gene.rds")
+```
+
+```{r, eval=TRUE}
+crispr_signif_g2p_gene <- readRDS("./data_munging/rds/crispr_signif_g2p_gene.rds")
+
+crispr_signif_g2p_20gene <- as.character(crispr_signif_g2p_gene$Hugo_Symbol[0:20])
+
+knitr::kable(filter(crispr_signif_g2p_gene, p < 0.1)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results for Level A point mutations, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+```{r fig.height=7, fig.width=12}
+crispr_data_signif_g2p_gene_filt <- filter(crispr_data_ptmuts, Hugo_Symbol %in% crispr_signif_g2p_20gene)
+crispr_data_signif_g2p_gene <- merge(crispr_data_signif_g2p_gene_filt, crispr_signif_g2p_gene, by = "Hugo_Symbol")
+crispr_data_signif_g2p_gene$Hugo_Symbol <- ordered(crispr_data_signif_g2p_gene$Hugo_Symbol, levels = crispr_signif_g2p_20gene)
+crispr_data_signif_g2p_gene_color <- as.character(crispr_data_signif_g2p_gene$Color_Nonsilent)
+names(crispr_data_signif_g2p_gene_color) <- crispr_data_signif_g2p_gene$Mutation_Status_Nonsilent
+crispr_data_signif_g2p_gene <- merge(crispr_data_signif_g2p_gene, crispr_data_signif_g2p_gene %>% group_by(Hugo_Symbol) %>% summarize(Text_y = max(Score)), by = "Hugo_Symbol")
+
+crispr_data_signif_g2p_gene_text <- unique(data.frame(p.signif = crispr_data_signif_g2p_gene$p.signif, p.signif.adj = crispr_data_signif_g2p_gene$p.signif.adj,  Hugo_Symbol = crispr_data_signif_g2p_gene$Hugo_Symbol, Text_y = crispr_data_signif_g2p_gene$Text_y))
+
+crispr_data_signif_g2p_gene_plot <- ggplot(data = crispr_data_signif_g2p_gene, aes(x = Mutation_Status_Nonsilent, y = Score)) +
+  facet_wrap(~ Hugo_Symbol, nrow = 2, scales = "free_y") +
+  geom_jitter(aes(color = Mutation_Status_Nonsilent), alpha = 0.5, width = 0.3) +
+  geom_boxplot(color = "black", fill = NA, outlier.shape = NA) +
+  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
+  scale_color_manual(values = crispr_data_signif_g2p_gene_color) + 
+  geom_text(data = crispr_data_signif_g2p_gene_text, mapping = aes(x = 1.5, y = Text_y, label = p.signif), nudge_y = 0.2) +
+  theme(legend.position = "top") +
+  labs(y = "CERES Score",
+       x = "Lineage",
+       color = "Mutation Status",
+       title = "CERES scores for select Level A G2P genes",
+       subtitle = "Genes are sorted by increasing p-value.")
+crispr_data_signif_g2p_gene_plot
+# Genes with adjusted p-values < 0.3 are shown.\nBH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001\n
+# ggsave("./plots_18Q3/manuscript/crispr_data_signif_g2p_gene_plot.png", crispr_data_signif_g2p_gene_plot, width = 12, height = 7, units = "in")
+```
+
+## CRISPR: Gene and lineage
+
+```{r, eval=FALSE}
+crispr_signif_g2p_lineage <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "group_general_lineage_name"), data = crispr_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
+crispr_signif_g2p_lineage <- adj_signif(crispr_signif_g2p_lineage)
+crispr_signif_g2p_lineage <- crispr_signif_g2p_lineage[order(crispr_signif_g2p_lineage$p),]
+saveRDS(crispr_signif_g2p_lineage, "./data_munging/rds/crispr_signif_g2p_lineage.rds")
+
+# write.table(crispr_signif_g2p_lineage, file = "~/Desktop/crispr_signif_g2p_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
+```
+
+```{r, eval=TRUE}
+crispr_signif_g2p_lineage <- readRDS("./data_munging/rds/crispr_signif_g2p_lineage.rds")
+
+knitr::kable(filter(crispr_signif_g2p_lineage, p < 0.01)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant vs other cell lines by lineage, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+```{r fig.height=15, fig.width=15, eval=FALSE}
+crispr_data_signif_g2p_lineage <- merge(crispr_data_signif_g2p_gene_filt, crispr_signif_g2p_lineage, by = c("Hugo_Symbol", "group_general_lineage_name"))
+crispr_data_signif_g2p_lineage$Hugo_Symbol <- ordered(crispr_data_signif_g2p_lineage$Hugo_Symbol, levels = crispr_signif_g2p_20gene)
+crispr_data_signif_g2p_lineage_color <- as.character(crispr_data_signif_g2p_lineage$Color_Nonsilent)
+names(crispr_data_signif_g2p_lineage_color) <- crispr_data_signif_g2p_lineage$Mutation_Status_Nonsilent
+crispr_data_signif_g2p_lineage <- merge(crispr_data_signif_g2p_lineage, crispr_data_signif_g2p_lineage %>% group_by(Hugo_Symbol) %>% summarize(Text_y = max(Score)), by = "Hugo_Symbol")
+
+crispr_data_signif_g2p_lineage_text <- unique(data.frame(p.signif = crispr_data_signif_g2p_lineage$p.signif, p.signif.adj = crispr_data_signif_g2p_lineage$p.signif.adj,  group_general_lineage_name = crispr_data_signif_g2p_lineage$group_general_lineage_name, Hugo_Symbol = crispr_data_signif_g2p_lineage$Hugo_Symbol, Text_y = crispr_data_signif_g2p_lineage$Text_y))
+
+crispr_data_signif_g2p_lineage_plot <- ggplot(data = crispr_data_signif_g2p_lineage, aes(x = group_general_lineage_name, y = Score)) +
+  facet_wrap(~ Hugo_Symbol, nrow = 4, scales = "free_y") +
+  geom_point(aes(color = Mutation_Status_Nonsilent), alpha = 0.5) +
+  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
+  scale_color_manual(values = crispr_data_signif_g2p_lineage_color) +
+  geom_text(data = crispr_data_signif_g2p_lineage_text, mapping = aes(x = group_general_lineage_name, y = Text_y, label = p.signif), angle = 90, nudge_y = 0.1) +
+  theme(legend.position = "top", axis.text.x = element_text(angle = 90, hjust = 1, vjust = 1, size = 10)) +
+  labs(y = "CERES Score",
+       x = "Lineage",
+       color = "Mutation Status",
+       title = "CERES score by cell line lineage for significant Level A G2P genes",
+       subtitle = "Genes with adjusted p-values < 0.3 are shown.\nBH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001\nGenes are sorted by increasing lineage-agnostic p-value.")
+crispr_data_signif_g2p_lineage_plot
+
+# ggsave("./plots_18Q3/manuscript/crispr_crispr_data_signif_g2p_lineage_plot.png", crispr_data_signif_g2p_lineage_plot, width = 12, height = 15, units = "in")
+```
+
+```{r}
+crispr_data_signif_g2p_lineage_summ <- crispr_data_signif_g2p_lineage %>% group_by(Hugo_Symbol, group_general_lineage_name, Mutation_Status_Nonsilent) %>% tally()
+# write.table(crispr_data_signif_g2p_lineage_summ, file = "~/Desktop/crispr_data_signif_g2p_lineage_summ_20181005.tsv", quote = FALSE, sep = "\t")
+
+knitr::kable(crispr_data_signif_g2p_lineage_summ, caption = "Mutant/Other counts for gene-lineage combinations") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+## CCLE: G2P gene and drug
+
+```{r, eval=FALSE}
+ccle_signif_g2p <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene", data = ccle_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
+ccle_signif_g2p <- adj_signif(ccle_signif_g2p)
+ccle_signif_g2p <- ccle_signif_g2p[order(ccle_signif_g2p$p),]
+saveRDS(ccle_signif_g2p, "./data_munging/rds/ccle_signif_g2p_gene.rds")
+```
+
+```{r, eval=TRUE}
+ccle_signif_g2p <- readRDS("./data_munging/rds/ccle_signif_g2p_gene.rds")
+
+knitr::kable(ccle_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for Level A point mutations, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+## CTRP: G2P gene and drug
+
+```{r, eval=FALSE}
+ctrp_signif_g2p <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene", data = ctrp_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
+ctrp_signif_g2p <- adj_signif(ctrp_signif_g2p)
+ctrp_signif_g2p <- ctrp_signif_g2p[order(ctrp_signif_g2p$p),]
+saveRDS(ctrp_signif_g2p, "./data_munging/rds/ctrp_signif_g2p_gene.rds")
+```
+
+```{r, eval=TRUE}
+ctrp_signif_g2p <- readRDS("./data_munging/rds/ctrp_signif_g2p_gene.rds")
+
+knitr::kable(ctrp_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for Level A point mutations, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+## GDSC: G2P gene and drug
+
+```{r, eval=FALSE}
+gdsc_signif_g2p <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene", data = gdsc_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
+gdsc_signif_g2p <- adj_signif(gdsc_signif_g2p)
+gdsc_signif_g2p <- gdsc_signif_g2p[order(gdsc_signif_g2p$p),]
+saveRDS(gdsc_signif_g2p, "./data_munging/rds/gdsc_signif_g2p_gene.rds")
+```
+
+```{r, eval=TRUE}
+gdsc_signif_g2p <- readRDS("./data_munging/rds/gdsc_signif_g2p_gene.rds")
+
+knitr::kable(gdsc_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for Level A point mutations, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+# Boxplots
+
+--------------------------------------------------------------------------------
+
+Mutation status boxplots for genes identified in G2P.
+
+## CRISPR
+
+```{r fig.height=5, fig.width=12, eval=FALSE}
+crispr_data_g2p_color <- as.character(crispr_data_g2p$Color_Nonsilent)
+names(crispr_data_g2p_color) <- crispr_data_g2p$Mutation_Status_Nonsilent
+
+crispr_label_text <- data.frame(p.signif.adj = crispr_signif_g2p_gene$p.signif.adj, p.signif = crispr_signif_g2p_gene$p.signif, Hugo_Symbol = crispr_signif_g2p_gene$Hugo_Symbol)
+crispr_label_text <- filter(crispr_label_text, Hugo_Symbol %in% g2p_genes)
+crispr_label_text$Hugo_Symbol <- factor(crispr_label_text$Hugo_Symbol, levels = g2p_genes)
+
+crispr_data_g2p_plot <- ggplot(data = crispr_data_g2p, aes(x = Mutation_Status_Nonsilent, y = Score)) +
+  facet_wrap(~ Hugo_Symbol, drop = FALSE, nrow = 2) +
+  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
+  geom_boxplot(mapping = aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85)) +
+  scale_fill_manual(values = crispr_ptmuts_g2p_filt_color) +
+  guides(color = FALSE) +
+  geom_text(data = crispr_label_text, mapping = aes(x = 1.5, y = 2, label = p.signif), nudge_y = 0.1) +
+  theme(legend.position = "top", axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
+  labs(title = "CRISPR", fill = "Mutation Status", y = "CERES Score", x = "Mutation Status")
+crispr_data_g2p_plot
+
+# ggsave("./plots_18Q3/manuscript/crispr_data_g2p_plot.png", crispr_data_g2p_plot, device = "png", dpi = 450, width = 20, height = 4, units = "in")
+```
+
+## CCLE
+
+```{r fig.height=4, fig.width=12}
+ccle_g2p_order <- as.character(ccle_signif_g2p$Drug_Gene)
+ccle_data_g2p$Drug_Gene_Ordered <- factor(ccle_data_g2p$Drug_Gene, levels = ccle_g2p_order, labels = sapply(strsplit(x = ccle_g2p_order, split = "_"), function(x) paste0(x[1], "\n", x[2])))
+ccle_signif_g2p$Drug_Gene_Ordered <- factor(ccle_signif_g2p$Drug_Gene, levels = ccle_g2p_order, labels = sapply(strsplit(x = ccle_g2p_order, split = "_"), function(x) paste0(x[1], "\n", x[2])))
+ccle_data_g2p_color <- as.character(ccle_data_g2p$Color_Nonsilent)
+names(ccle_data_g2p_color) <- ccle_data_g2p$Mutation_Status_Nonsilent
+
+ccle_label_text <- data.frame(p.signif.adj = ccle_signif_g2p$p.signif.adj, p.signif = ccle_signif_g2p$p.signif, Drug_Gene_Ordered = ccle_signif_g2p$Drug_Gene_Ordered)
+
+ccle_data_g2p_plot <- ggplot(data = ccle_data_g2p, aes(x = Mutation_Status_Nonsilent, y = AUC)) +
+  facet_wrap(~ Drug_Gene_Ordered, drop = FALSE, nrow = 1) +
+  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
+  geom_boxplot(mapping = aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85), outlier.shape = 3, outlier.size = 0.5) +
+  scale_fill_manual(values = ccle_data_g2p_color) +
+  guides(color = FALSE) +
+  geom_text(data = ccle_label_text, mapping = aes(x = 1.5, y = 7, label = p.signif), nudge_y = 0.1) +
+  theme(legend.position = "top", axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
+  labs(title = "CCLE", fill = "Mutation Status", y = "AUC", x = "Mutation Status")
+ccle_data_g2p_plot
+
+# ggsave("./plots_18Q3/manuscript/ccle_data_g2p_plot.png", ccle_data_g2p_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
+```
+
+## CTRP
+
+```{r fig.height=7, fig.width=12}
+ctrp_g2p_order <- as.character(ctrp_signif_g2p$Drug_Gene)
+ctrp_data_g2p$Drug_Gene_Ordered <- factor(ctrp_data_g2p$Drug_Gene, levels = ctrp_g2p_order, labels = sapply(strsplit(x = ctrp_g2p_order, split = "_"), function(x) paste0(x[1], "\n", x[2])))
+ctrp_signif_g2p$Drug_Gene_Ordered <- factor(ctrp_signif_g2p$Drug_Gene, levels = ctrp_g2p_order, labels = sapply(strsplit(x = ctrp_g2p_order, split = "_"), function(x) paste0(x[1], "\n", x[2])))
+ctrp_data_g2p_color <- as.character(ctrp_data_g2p$Color_Nonsilent)
+names(ctrp_data_g2p_color) <- ctrp_data_g2p$Mutation_Status_Nonsilent
+
+ctrp_label_text <- data.frame(p.signif.adj = ctrp_signif_g2p$p.signif.adj, p.signif = ctrp_signif_g2p$p.signif, Drug_Gene_Ordered = ctrp_signif_g2p$Drug_Gene_Ordered)
+
+ctrp_data_g2p_plot <- ggplot(data = ctrp_data_g2p, aes(x = Mutation_Status_Nonsilent, y = AUC)) +
+  facet_wrap(~ Drug_Gene_Ordered, drop = FALSE, nrow = 3) +
+  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
+  geom_boxplot(mapping = aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85), outlier.shape = 3, outlier.size = 0.5) +
+  scale_fill_manual(values = ctrp_data_g2p_color) +
+  guides(color = FALSE) +
+  geom_text(data = ctrp_label_text, mapping = aes(x = 1.5, y = 22.5, label = p.signif), nudge_y = 0.1) +
+  theme(legend.position = "top", axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
+  labs(title = "CTRP", fill = "Mutation Status", y = "AUC", x = "Mutation Status")
+ctrp_data_g2p_plot
+
+# ggsave("./plots_18Q3/manuscript/ctrp_data_g2p_plot.png", ctrp_data_g2p_plot, device = "png", dpi = 450, width = 12, height = 7, units = "in")
+```
+
+## GDSC
+
+```{r fig.height=7, fig.width=12}
+gdsc_g2p_order <- as.character(gdsc_signif_g2p$Drug_Gene)
+gdsc_data_g2p$Drug_Gene_Ordered <- factor(gdsc_data_g2p$Drug_Gene, levels = gdsc_g2p_order, labels = sapply(strsplit(x = gdsc_g2p_order, split = "_"), function(x) paste0(x[1], "\n", x[2])))
+gdsc_signif_g2p$Drug_Gene_Ordered <- factor(gdsc_signif_g2p$Drug_Gene, levels = gdsc_g2p_order, labels = sapply(strsplit(x = gdsc_g2p_order, split = "_"), function(x) paste0(x[1], "\n", x[2])))
+gdsc_data_g2p_color <- as.character(gdsc_data_g2p$Color_Nonsilent)
+names(gdsc_data_g2p_color) <- gdsc_data_g2p$Mutation_Status_Nonsilent
+
+gdsc_label_text <- data.frame(p.signif.adj = gdsc_signif_g2p$p.signif.adj, p.signif = gdsc_signif_g2p$p.signif, Drug_Gene_Ordered = gdsc_signif_g2p$Drug_Gene_Ordered)
+
+gdsc_data_g2p_plot <- ggplot(data = gdsc_data_g2p, aes(x = Mutation_Status_Nonsilent, y = AUC)) +
+  facet_wrap(~ Drug_Gene_Ordered, drop = FALSE, nrow = 3) +
+  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
+  geom_boxplot(mapping = aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85), outlier.shape = 3, outlier.size = 0.5) +
+  scale_fill_manual(values = gdsc_data_g2p_color) +
+  guides(color = FALSE) +
+  geom_text(data = gdsc_label_text, mapping = aes(x = 1.5, y = 1, label = p.signif), nudge_y = 0.1) +
+  theme(legend.position = "top", axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
+  labs(title = "GDSC", fill = "Mutation Status", y = "AUC", x = "Mutation Status")
+gdsc_data_g2p_plot
+
+# ggsave("./plots_18Q3/manuscript/gdsc_data_g2p_plot.png", gdsc_data_g2p_plot, device = "png", dpi = 450, width = 12, height = 7, units = "in")
+```
+
+# CRISPR: Point mutation mapping
+
+--------------------------------------------------------------------------------
+
+Match specific point mutations.
+```{r fig.height=5, fig.width=20, eval=FALSE}
+g2p_indications <- filter(read.delim("./data_munging/data_mutation_associations_appended.csv", sep = "\t", header = TRUE), Evidence.Level == "A")
+maf_g2p_indications <- filter(maf_raw, Genome_Change %in% g2p_indications$MutationName)
+crispr_g2p_indications <- merge(crispr_data_ptmuts, maf_g2p_indications, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
+crispr_g2p_indications$Mutation_Status_Nonsilent <- ifelse(is.na(crispr_g2p_indications$Mutation_Status_Nonsilent), "Other", crispr_g2p_indications$Mutation_Status_Nonsilent)
+dup_g2p_indications <- filter(crispr_g2p_indications[, c("Hugo_Symbol", "CCLE_Name", "Broad_ID")] %>% group_by(Hugo_Symbol, CCLE_Name, Broad_ID) %>% tally(), n > 1)
+crispr_g2p_indications <- merge(crispr_g2p_indications, dup_g2p_indications, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
+crispr_g2p_indications$Genome_Change <- factor(crispr_g2p_indications$Genome_Change, levels = unique(crispr_g2p_indications$Genome_Change))
+crispr_g2p_indications_nonNA <- filter(crispr_g2p_indications, is.na(n))
+
+crispr_g2p_indications_plot <- ggplot(crispr_g2p_indications, aes(x = Hugo_Symbol, y = Score)) +
+  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
+  geom_boxplot(alpha = 0.5, color = "lightgray", outlier.shape = NA) +
+  geom_jitter(width = 0.3, mapping = aes(color = Mutation_Status_Nonsilent), size = 1) +
+  theme_light() +
+  theme(legend.title = element_blank()) +
+  labs(x = "Gene", y = "CERES Score")
+crispr_g2p_indications_plot
+
+crispr_g2p_indications_muts_plot <- ggplot(crispr_g2p_indications, aes(x = Protein_Change, y = Score)) +
+  facet_grid(~ Hugo_Symbol, scales = "free_x", space = "free") +
+  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
+  geom_boxplot(alpha = 0.5, color = "lightgray", outlier.shape = NA) +
+  geom_jitter(width = 0.1, mapping = aes(color = Mutation_Status_Nonsilent), size = 1) +
+  theme_light() +
+  theme(legend.title = element_blank(), axis.text.x = element_text(angle = 90, hjust = 1)) +
+  labs(x = "Gene", y = "CERES Score")
+crispr_g2p_indications_muts_plot
+
+# ggsave("./plots_18Q3/manuscript/crispr_g2p_indications_plot_test.png", crispr_g2p_indications_plot, width = 12, height = 5, units = "in")
+# ggsave("./plots_18Q3/manuscript/crispr_g2p_indications_muts_plot_test.png", crispr_g2p_indications_muts_plot, width = 20, height = 5, units = "in")
+```
+
+# References
+
+--------------------------------------------------------------------------------
+
+Barretina, J., Caponigro, G., Stransky, N., Venkatesan, K., Margolin, A.
+A., Kim, S., … Garraway, L.
+A.
+(2012).
+The Cancer Cell Line Encyclopedia enables predictive modelling of anticancer drug sensitivity.
+Nature, 483(7391), 603–607.
+https://doi.org/10.1038/nature11003
+
+Broad Institute Cancer Dependency Map; Cancer Data Science (2018): Cancer Dependency Map, CRISPR Avana dataset 18Q3 (Avana_public_18Q3). figshare. Fileset. doi:10.6084/m9.figshare.6931364.v1
+
+Consortium, T. C. C. L. E., & Consortium, T. G. of D. S. in C. (2015). Pharmacogenomic agreement between two cancer cell line data sets. Nature, 528(7580), 84–87. https://doi.org/10.1038/nature15736
+
+Data Science, Cancer (2018): DEMETER2 data. figshare. Fileset. doi:10.6084/m9.figshare.6025238.v2
+
+Doench, J.
+G., Fusi, N., Sullender, M., Hegde, M., Vaimberg, E.
+W., Donovan, K.
+F., … Root, D.
+E.
+(2016).
+Optimized sgRNA design to maximize activity and minimize off-target effects of CRISPR-Cas9.
+Nature Biotechnology, 34(2), 184–191.
+https://doi.org/10.1038/nbt.3437
+
+Meyers, R.
+M., Bryan, J.
+G., McFarland, J.
+M., Weir, B.
+A., Sizemore, A.
+E., Xu, H., … Tsherniak, A.
+(2017).
+Computational correction of copy-number effect improves specificity of CRISPR-Cas9 essentiality screens in cancer cells.
+Nature Genetics, 49(12), 1779–1784.
+https://doi.org/10.1038/ng.3984
+
+McFarland, J.
+M., Ho, Z.
+V., Kugener, G., Dempster, J.
+M., Montgomery, P.
+G., Bryan, J.
+G., … Tsherniak, A.
+(2018).
+Improved estimation of cancer dependencies from large-scale RNAi screens using model-based normalization and data integration.
+https://doi.org/10.1101/305656
+
+# Session information
+
+--------------------------------------------------------------------------------
+
+```{r}
+print(sessionInfo())
+```

### 2018-10-23 manuscript.Rmd
knit updated manuscript.Rmd

@@
     toc: true
-    toc_depth: 3
+    toc_depth: 4
     toc_float:
@@
   return(sig)
+}
+```
+
+## Make per-drug boxplots
+```{r}
+makeDrugBoxplots <- function(drug, dataset) {
+  if(dataset == "CCLE" | dataset == "ccle") {
+    use_data <- filter(ccle_data_g2p_genesfilt, Drug == drug)
+    use_color <- as.character(use_data$Color_Nonsilent)
+    names(use_color) <- use_data$Mutation_Status_Nonsilent
+    sig <- ccle_signif_g2p_ByDrug[[drug]]
+    label_text <- data.frame(p.signif = sig$p.signif, p.signif.adj = sig$p.signif.adj, Hugo_Symbol = sig$Hugo_Symbol)
+    label_text$Hugo_Symbol <- factor(label_text$Hugo_Symbol, levels = g2p_genes)
+  }
+  else if(dataset == "CTRP" | dataset == "ctrp") {
+    use_data <- filter(ctrp_data_g2p_genesfilt, Drug == drug)
+    use_color <- as.character(use_data$Color_Nonsilent)
+    names(use_color) <- use_data$Mutation_Status_Nonsilent
+    sig <- ctrp_signif_g2p_ByDrug[[drug]]
+    label_text <- data.frame(p.signif = sig$p.signif, p.signif.adj = sig$p.signif.adj, Hugo_Symbol = sig$Hugo_Symbol)
+    label_text$Hugo_Symbol <- factor(label_text$Hugo_Symbol, levels = g2p_genes)
+  }
+  else if(dataset == "GDSC" | dataset == "gdsc") {
+    use_data <- filter(gdsc_data_g2p_genesfilt, Drug == drug)
+    use_color <- as.character(use_data$Color_Nonsilent)
+    names(use_color) <- use_data$Mutation_Status_Nonsilent
+    sig <- gdsc_signif_g2p_ByDrug[[drug]]
+    label_text <- data.frame(p.signif = sig$p.signif, p.signif.adj = sig$p.signif.adj, Hugo_Symbol = sig$Hugo_Symbol)
+    label_text$Hugo_Symbol <- factor(label_text$Hugo_Symbol, levels = g2p_genes)
+  }
+  else { return("Error: Invalid dataset.") }
+
+  plot <- ggplot(data = use_data, aes(x = Mutation_Status_Nonsilent, y = AUC)) +
+    facet_wrap(~ Hugo_Symbol, drop = FALSE, nrow = 1) +
+    geom_boxplot(mapping = aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85), outlier.shape = 3, outlier.size = 0.5) +
+    scale_fill_manual(values = use_color) +
+    guides(color = FALSE) +
+    geom_text(data = label_text, mapping = aes(x = 1.5, y = max(use_data$AUC), label = p.signif), nudge_y = 0.2) +
+    theme(legend.position = "top", axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
+    labs(fill = "Mutation Status", y = "AUC", x = "Mutation Status", title = paste0(toupper(dataset), ": ", drug))
+  return(plot)
 }
@@
 # Order and genes taken from pink heatmapo from Daniel's analyses
-# g2p_genes_filt <- c("KRAS", "EGFR", "MET", "ALK", "BRAF", "ERBB2", "ABL1", "ROS1", "KIT", "DPYD", "PDGFRA", "RET", "BRCA1", "UGT1A1", "IDH2", "ESR1", "TPMT", "BRCA2", "PDGFRB", "G6PD", "PML", "TSC1", "FLT3", "ERBB3", "CYP19A1", "AKT1", "PTCH1", "MGMT", "DNMT3A", "MYD88", "PDGFB", "TSC2", "NPM1", "JAK2")
+g2p_genes <- c("KRAS", "EGFR", "MET", "ALK", "BRAF", "ERBB2", "ABL1", "ROS1", "KIT", "DPYD", "PDGFRA", "RET", "BRCA1", "UGT1A1", "IDH2", "ESR1", "TPMT", "BRCA2", "PDGFRB", "G6PD", "PML", "TSC1", "FLT3", "ERBB3", "CYP19A1", "AKT1", "PTCH1", "MGMT", "DNMT3A", "MYD88", "PDGFB", "TSC2", "NPM1", "JAK2")
 ```
@@
 gdsc_data_g2p <- filter(gdsc_data_ptmuts, Drug_Gene %in% g2p_drug_genes)
+
+# Filter drug screen datasets for G2P genes in drug-gene associations
+ccle_data_g2p_genesfilt <- filter(ccle_data_ptmuts, Hugo_Symbol %in% g2p_genes)
+ccle_data_g2p_genesfilt$Hugo_Symbol <- ordered(ccle_data_g2p_genesfilt$Hugo_Symbol, levels = g2p_genes)
+ctrp_data_g2p_genesfilt <- filter(ctrp_data_ptmuts, Hugo_Symbol %in% g2p_genes)
+ctrp_data_g2p_genesfilt$Hugo_Symbol <- ordered(ctrp_data_g2p_genesfilt$Hugo_Symbol, levels = g2p_genes)
+gdsc_data_g2p_genesfilt <- filter(gdsc_data_ptmuts, Hugo_Symbol %in% g2p_genes)
+gdsc_data_g2p_genesfilt$Hugo_Symbol <- ordered(gdsc_data_g2p_genesfilt$Hugo_Symbol, levels = g2p_genes)
 ```
@@
 
-```{r fig.height=15, fig.width=15, eval=FALSE}
+```{r fig.height=15, fig.width=15}
 crispr_data_signif_g2p_lineage <- merge(crispr_data_signif_g2p_gene_filt, crispr_signif_g2p_lineage, by = c("Hugo_Symbol", "group_general_lineage_name"))
@@
 saveRDS(ccle_signif_g2p, "./data_munging/rds/ccle_signif_g2p_gene.rds")
+
+ccle_signif_g2p_ByDrug <- lapply(unique(ccle_data_g2p_genesfilt$Drug), WilcoxonByDrug, dataset = ccle_data_g2p_genesfilt, data_name = "ccle")
+names(ccle_signif_g2p_ByDrug) <- unique(ccle_data_g2p_genesfilt$Drug)
+saveRDS(ccle_signif_g2p_ByDrug, "./data_munging/rds/ccle_signif_g2p_ByDrug.rds")
 ```
@@
 knitr::kable(ccle_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for Level A point mutations, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+```{r}
+ccle_signif_g2p_ByDrug <- readRDS("./data_munging/rds/ccle_signif_g2p_ByDrug.rds")
+ccle_signif_g2p_ByDrug_all <- rbindlist(ccle_signif_g2p_ByDrug, use.names = TRUE)
+ccle_signif_g2p_ByDrug_all <- ccle_signif_g2p_ByDrug_all[order(ccle_signif_g2p_ByDrug_all$p),]
+
+knitr::kable(ccle_signif_g2p_ByDrug_all[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: by-drug Wilcoxon test results for Level A point mutations, (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 saveRDS(ctrp_signif_g2p, "./data_munging/rds/ctrp_signif_g2p_gene.rds")
+
+ctrp_signif_g2p_ByDrug <- lapply(unique(ctrp_data_g2p_genesfilt$Drug), WilcoxonByDrug, dataset = ctrp_data_g2p_genesfilt, data_name = "CTRP")
+names(ctrp_signif_g2p_ByDrug) <- unique(ctrp_data_g2p_genesfilt$Drug)
+saveRDS(ctrp_signif_g2p_ByDrug, "./data_munging/rds/ctrp_signif_g2p_ByDrug.rds")
 ```
 
-```{r, eval=TRUE}
+```{r}
 ctrp_signif_g2p <- readRDS("./data_munging/rds/ctrp_signif_g2p_gene.rds")
@@
 knitr::kable(ctrp_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for Level A point mutations, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+```{r}
+ctrp_signif_g2p_ByDrug <- readRDS("./data_munging/rds/ctrp_signif_g2p_ByDrug.rds")
+ctrp_signif_g2p_ByDrug_all <- rbindlist(ctrp_signif_g2p_ByDrug, use.names = TRUE)
+ctrp_signif_g2p_ByDrug_all <- ctrp_signif_g2p_ByDrug_all[order(ctrp_signif_g2p_ByDrug_all$p),]
+
+knitr::kable(ctrp_signif_g2p_ByDrug_all[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: by-drug Wilcoxon test results for Level A point mutations, (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 saveRDS(gdsc_signif_g2p, "./data_munging/rds/gdsc_signif_g2p_gene.rds")
+
+gdsc_signif_g2p_ByDrug <- lapply(unique(gdsc_data_g2p_genesfilt$Drug), WilcoxonByDrug, dataset = gdsc_data_g2p_genesfilt, data_name = "gdsc")
+names(gdsc_signif_g2p_ByDrug) <- unique(gdsc_data_g2p_genesfilt$Drug)
+saveRDS(gdsc_signif_g2p_ByDrug, "./data_munging/rds/gdsc_signif_g2p_ByDrug.rds")
 ```
 
-```{r, eval=TRUE}
+```{r}
 gdsc_signif_g2p <- readRDS("./data_munging/rds/gdsc_signif_g2p_gene.rds")
@@
 knitr::kable(gdsc_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for Level A point mutations, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+```{r}
+gdsc_signif_g2p_ByDrug <- readRDS("./data_munging/rds/gdsc_signif_g2p_ByDrug.rds")
+gdsc_signif_g2p_ByDrug_all <- rbindlist(gdsc_signif_g2p_ByDrug, use.names = TRUE)
+gdsc_signif_g2p_ByDrug_all <- gdsc_signif_g2p_ByDrug_all[order(gdsc_signif_g2p_ByDrug_all$p),]
+
+knitr::kable(gdsc_signif_g2p_ByDrug_all[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: by-drug Wilcoxon test results for Level A point mutations, (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
-## CRISPR
+## Figure 1
 
-```{r fig.height=5, fig.width=12, eval=FALSE}
+Boxplots ordered by gene based on frequency of G2P associations.
+
+### CRISPR
+
+```{r fig.height=4, fig.width=20}
+crispr_data_g2p$Hugo_Symbol <- factor(crispr_data_g2p$Hugo_Symbol, levels = g2p_genes)
 crispr_data_g2p_color <- as.character(crispr_data_g2p$Color_Nonsilent)
@@
 crispr_data_g2p_plot <- ggplot(data = crispr_data_g2p, aes(x = Mutation_Status_Nonsilent, y = Score)) +
-  facet_wrap(~ Hugo_Symbol, drop = FALSE, nrow = 2) +
+  facet_wrap(~ Hugo_Symbol, drop = FALSE, nrow = 1) +
   geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
   geom_boxplot(mapping = aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85)) +
-  scale_fill_manual(values = crispr_ptmuts_g2p_filt_color) +
+  scale_fill_manual(values = crispr_data_g2p_color) +
   guides(color = FALSE) +
@@
 
-## CCLE
+### CCLE
+
+Plot code:
+```{r, eval=FALSE}
+ccle_drugs <- as.character(unique(ccle_data_g2p_genesfilt$Drug))
+ccle_g2p_drugboxplots <- lapply(ccle_drugs, makeDrugBoxplots, dataset = "CCLE")
+ccle_g2p_drugboxplots_paths <- paste0(ccle_drugs, "_ccle_drugboxplots.png")
+pwalk(list(ccle_g2p_drugboxplots_paths, ccle_g2p_drugboxplots), ggsave, path = "./plots_18Q3/manuscript/ccle_g2p_drugboxplots", dpi = 450, width = 20, height = 4, units = "in")
+```
+
+Data management:
+```{r, eval=TRUE}
+ccle_g2p_drugboxplots <- paste0(list.files("./plots_18Q3/manuscript/ccle_g2p_drugboxplots", full.names = TRUE))
+names(ccle_g2p_drugboxplots) <- str_replace_all(ccle_g2p_drugboxplots, c("_ccle_drugboxplots.png" = "", "./plots_18Q3/manuscript/ccle_g2p_drugboxplots/" = ""))
+bsselect(ccle_g2p_drugboxplots, type = "img", live_search = TRUE, show_tick = TRUE, height = 300, frame_height = 275)
+```
+
+### CTRP
+
+Plot code:
+```{r, eval=FALSE}
+ctrp_drugs <- as.character(unique(ctrp_data_g2p_genesfilt$Drug))
+ctrp_g2p_drugboxplots <- lapply(ctrp_drugs, makeDrugBoxplots, dataset = "ctrp")
+ctrp_g2p_drugboxplots_paths <- paste0(ctrp_drugs, "_ctrp_drugboxplots.png")
+pwalk(list(ctrp_g2p_drugboxplots_paths, ctrp_g2p_drugboxplots), ggsave, path = "./plots_18Q3/manuscript/ctrp_g2p_drugboxplots", dpi = 450, width = 20, height = 4, units = "in")
+```
+
+Data management:
+```{r, eval=TRUE}
+ctrp_g2p_drugboxplots <- paste0(list.files("./plots_18Q3/manuscript/ctrp_g2p_drugboxplots", full.names = TRUE))
+names(ctrp_g2p_drugboxplots) <- str_replace_all(ctrp_g2p_drugboxplots, c("_ctrp_drugboxplots.png" = "", "./plots_18Q3/manuscript/ctrp_g2p_drugboxplots/" = ""))
+bsselect(ctrp_g2p_drugboxplots, type = "img", live_search = TRUE, show_tick = TRUE, height = 300, frame_height = 275)
+```
+
+### GDSC
+
+Plot code:
+```{r, eval=FALSE}
+gdsc_drugs <- as.character(unique(gdsc_data_g2p_genesfilt$Drug))
+gdsc_g2p_drugboxplots <- lapply(gdsc_drugs, makeDrugBoxplots, dataset = "gdsc")
+gdsc_g2p_drugboxplots_paths <- paste0(gdsc_drugs, "_gdsc_drugboxplots.png")
+pwalk(list(gdsc_g2p_drugboxplots_paths, gdsc_g2p_drugboxplots), ggsave, path = "./plots_18Q3/manuscript/gdsc_g2p_drugboxplots", dpi = 450, width = 20, height = 4, units = "in")
+```
+
+Data management:
+```{r, eval=TRUE}
+gdsc_g2p_drugboxplots <- paste0(list.files("./plots_18Q3/manuscript/gdsc_g2p_drugboxplots", full.names = TRUE))
+names(gdsc_g2p_drugboxplots) <- str_replace_all(gdsc_g2p_drugboxplots, c("_gdsc_drugboxplots.png" = "", "./plots_18Q3/manuscript/gdsc_g2p_drugboxplots/" = ""))
+bsselect(gdsc_g2p_drugboxplots, type = "img", live_search = TRUE, show_tick = TRUE, height = 300, frame_height = 275)
+```
+
+## Gene-drug associations only
+
+### CCLE
 
@@
 
-## CTRP
+### CTRP
 
@@
 
-## GDSC
+### GDSC
 

### 2018-10-23 manuscript.Rmd
updated manuscript.Rmd/html

@@
     toc: true
-    toc_depth: 4
+    toc_depth: 3
     toc_float:
@@
     geom_text(data = label_text, mapping = aes(x = 1.5, y = max(use_data$AUC), label = p.signif), nudge_y = 0.2) +
-    theme(legend.position = "top", axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
+    theme(strip.text.x = element_text(size = 10, angle = 45), legend.position = "top", axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
     labs(fill = "Mutation Status", y = "AUC", x = "Mutation Status", title = paste0(toupper(dataset), ": ", drug))
@@
 
-knitr::kable(filter(crispr_signif_g2p_gene, p < 0.1)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results for Level A point mutations, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(crispr_signif_g2p_gene[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results for Level A point mutations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
-knitr::kable(filter(crispr_signif_g2p_lineage, p < 0.01)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant vs other cell lines by lineage, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(filter(crispr_signif_g2p_lineage, p < 0.1)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant vs other cell lines by lineage, p < 0.1 (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
        title = "CERES score by cell line lineage for significant Level A G2P genes",
-       subtitle = "Genes with adjusted p-values < 0.3 are shown.\nBH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001\nGenes are sorted by increasing lineage-agnostic p-value.")
+       subtitle = "* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001\nGenes are sorted by increasing lineage-agnostic p-value.")
 crispr_data_signif_g2p_lineage_plot
@@
 
-knitr::kable(ccle_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for Level A point mutations, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(ccle_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
-knitr::kable(ccle_signif_g2p_ByDrug_all[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: by-drug Wilcoxon test results for Level A point mutations, (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(ccle_signif_g2p_ByDrug_all[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: By-drug Wilcoxon test results for point mutations in level A G2P genes (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
-knitr::kable(ctrp_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for Level A point mutations, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(ctrp_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
-knitr::kable(ctrp_signif_g2p_ByDrug_all[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: by-drug Wilcoxon test results for Level A point mutations, (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(ctrp_signif_g2p_ByDrug_all[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: By-drug Wilcoxon test results for point mutations in level A G2P genes (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
-knitr::kable(gdsc_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for Level A point mutations, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(gdsc_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
-knitr::kable(gdsc_signif_g2p_ByDrug_all[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: by-drug Wilcoxon test results for Level A point mutations, (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(gdsc_signif_g2p_ByDrug_all[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: by-drug Wilcoxon test results for point mutations in level A G2P genes (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
-```{r fig.height=4, fig.width=20}
+```{r fig.height=5, fig.width=20}
 crispr_data_g2p$Hugo_Symbol <- factor(crispr_data_g2p$Hugo_Symbol, levels = g2p_genes)
@@
   geom_text(data = crispr_label_text, mapping = aes(x = 1.5, y = 2, label = p.signif), nudge_y = 0.1) +
-  theme(legend.position = "top", axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
+  theme(strip.text.x = element_text(size = 10, angle = 45), legend.position = "top", axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
   labs(title = "CRISPR", fill = "Mutation Status", y = "CERES Score", x = "Mutation Status")
@@
 
-# ggsave("./plots_18Q3/manuscript/crispr_data_g2p_plot.png", crispr_data_g2p_plot, device = "png", dpi = 450, width = 20, height = 4, units = "in")
+# ggsave("./plots_18Q3/manuscript/crispr_data_g2p_plot.png", crispr_data_g2p_plot, device = "png", dpi = 450, width = 20, height = 5, units = "in")
 ```
@@
 ccle_g2p_drugboxplots_paths <- paste0(ccle_drugs, "_ccle_drugboxplots.png")
-pwalk(list(ccle_g2p_drugboxplots_paths, ccle_g2p_drugboxplots), ggsave, path = "./plots_18Q3/manuscript/ccle_g2p_drugboxplots", dpi = 450, width = 20, height = 4, units = "in")
+pwalk(list(ccle_g2p_drugboxplots_paths, ccle_g2p_drugboxplots), ggsave, path = "./plots_18Q3/manuscript/ccle_g2p_drugboxplots", dpi = 450, width = 20, height = 5, units = "in")
 ```
@@
 names(ccle_g2p_drugboxplots) <- str_replace_all(ccle_g2p_drugboxplots, c("_ccle_drugboxplots.png" = "", "./plots_18Q3/manuscript/ccle_g2p_drugboxplots/" = ""))
-bsselect(ccle_g2p_drugboxplots, type = "img", live_search = TRUE, show_tick = TRUE, height = 300, frame_height = 275)
+bsselect(ccle_g2p_drugboxplots, type = "img", live_search = TRUE, show_tick = TRUE, height = 100)
 ```
@@
 ctrp_g2p_drugboxplots_paths <- paste0(ctrp_drugs, "_ctrp_drugboxplots.png")
-pwalk(list(ctrp_g2p_drugboxplots_paths, ctrp_g2p_drugboxplots), ggsave, path = "./plots_18Q3/manuscript/ctrp_g2p_drugboxplots", dpi = 450, width = 20, height = 4, units = "in")
+pwalk(list(ctrp_g2p_drugboxplots_paths, ctrp_g2p_drugboxplots), ggsave, path = "./plots_18Q3/manuscript/ctrp_g2p_drugboxplots", dpi = 450, width = 20, height = 5, units = "in")
 ```
@@
 names(ctrp_g2p_drugboxplots) <- str_replace_all(ctrp_g2p_drugboxplots, c("_ctrp_drugboxplots.png" = "", "./plots_18Q3/manuscript/ctrp_g2p_drugboxplots/" = ""))
-bsselect(ctrp_g2p_drugboxplots, type = "img", live_search = TRUE, show_tick = TRUE, height = 300, frame_height = 275)
+bsselect(ctrp_g2p_drugboxplots, type = "img", live_search = TRUE, show_tick = TRUE, height = 100)
 ```
@@
 gdsc_g2p_drugboxplots_paths <- paste0(gdsc_drugs, "_gdsc_drugboxplots.png")
-pwalk(list(gdsc_g2p_drugboxplots_paths, gdsc_g2p_drugboxplots), ggsave, path = "./plots_18Q3/manuscript/gdsc_g2p_drugboxplots", dpi = 450, width = 20, height = 4, units = "in")
+pwalk(list(gdsc_g2p_drugboxplots_paths, gdsc_g2p_drugboxplots), ggsave, path = "./plots_18Q3/manuscript/gdsc_g2p_drugboxplots", dpi = 450, width = 20, height = 5, units = "in")
 ```
@@
 names(gdsc_g2p_drugboxplots) <- str_replace_all(gdsc_g2p_drugboxplots, c("_gdsc_drugboxplots.png" = "", "./plots_18Q3/manuscript/gdsc_g2p_drugboxplots/" = ""))
-bsselect(gdsc_g2p_drugboxplots, type = "img", live_search = TRUE, show_tick = TRUE, height = 300, frame_height = 275)
+bsselect(gdsc_g2p_drugboxplots, type = "img", live_search = TRUE, show_tick = TRUE, height = 100)
 ```
 
-## Gene-drug associations only
+## G2P level A gene-drug associations only
 

### 2018-10-24 manuscript.Rmd
new fxn for all CRISPR genes in drug screens

@@
 library(kableExtra)
+library(reshape2)
 library(tidyverse)
@@
   sig$Drug <- drug
-  sig$Dataset <- data_name
+  sig$Dataset <- toupper(data_name)
   return(sig)
+}
+
+WilcoxonByDrugAllGenes <- function(melt_file, grid_file, data_name) {
+  druglist <- as.character(unique(melt_file$Drug))
+  sig_df <- NULL
+  for(i in 1:length(druglist)) {
+    print(paste0("Current drug in process: ", druglist[i], " (drug ", i, " of ", length(druglist), ")."))
+    flush.console()
+    melted <- filter(melt_file, Drug == druglist[i])
+    use_data <- merge(grid_file, melted, by = "accession_id", all.x = TRUE)
+    use_data <- merge(use_data, ccl_converter, by = "accession_id", all.x = TRUE)
+    use_data <- merge(use_data, maf_df, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
+    use_data$Mutation_Status_Nonsilent <- ifelse(is.na(use_data$Mutation_Status_Nonsilent), "Other", use_data$Mutation_Status_Nonsilent)
+    use_data$Hugo_Symbol <- factor(use_data$Hugo_Symbol)
+    use_data$AUC <- as.numeric(use_data$AUC)
+    use_data <- filter(use_data, !is.na(use_data$AUC))
+    use_data$Drug_Gene <- paste0(use_data$Drug, "_", use_data$Hugo_Symbol)
+    use_data_ptmuts <- filter(use_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
+    use_data_ptmuts$Keep_PtMut_Tests <- ifelse(use_data_ptmuts$Reference_Allele_Length == 1 | is.na(use_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(use_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
+    use_data_ptmuts <- filter(use_data_ptmuts, Keep_PtMut_Tests == TRUE)
+
+    sig <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = "Hugo_Symbol", data = use_data_ptmuts, method = "wilcox.test", p.adjust.method = "BH")
+    sig <- adj_signif(sig)
+    sig <- sig[order(sig$p),]
+    sig <- filter(sig, p <= 0.05)
+    sig$Drug <- druglist[i]
+    sig$Dataset <- toupper(data_name)
+    sig_df <- rbind(sig_df, sig)
+  }
+  return(sig_df)
 }
@@
 # Order and genes taken from pink heatmapo from Daniel's analyses
-g2p_genes <- c("KRAS", "EGFR", "MET", "ALK", "BRAF", "ERBB2", "ABL1", "ROS1", "KIT", "DPYD", "PDGFRA", "RET", "BRCA1", "UGT1A1", "IDH2", "ESR1", "TPMT", "BRCA2", "PDGFRB", "G6PD", "PML", "TSC1", "FLT3", "ERBB3", "CYP19A1", "AKT1", "PTCH1", "MGMT", "DNMT3A", "MYD88", "PDGFB", "TSC2", "NPM1", "JAK2")
+g2p_genes <- c("EGFR", "KRAS", "ERBB2", "ERBB3", "MET", "ALK", "ROS1", "PDGFRA", "ABL1", "KIT", "PDGFRB", "PDGFB", "BRAF", "G6PD", "RET", "BRCA1", "BRCA2", "UGT1A1", "TSC1", "TSC2", "AKT1", "IDH2", "DPYD", "ESR1", "CYP19A1", "TPMT", "FLT3", "NPM1", "DNMT3A", "PML", "PTCH1", "JAK2", "MYD88", "MGMT")
 ```
@@
 ccle_data$Drug_Gene <- paste0(ccle_data$Drug, "_", ccle_data$Hugo_Symbol)
-saveRDS(ccle_data, "./data_munging/rds/ccle_data_18Q3.rds", compress = "xz")
+saveRDS(ccle_data, "./data_munging/rds/ccle_data_18Q3_g2pgenes.rds", compress = "xz")
 
@@
 ctrp_data$Drug_Gene <- paste0(ctrp_data$Drug, "_", ctrp_data$Hugo_Symbol)
-saveRDS(ctrp_data, "./data_munging/rds/ctrp_data_18Q3.rds", compress = "xz")
+saveRDS(ctrp_data, "./data_munging/rds/ctrp_data_18Q3_g2pgenes.rds", compress = "xz")
 
@@
 gdsc_data$Drug_Gene <- paste0(gdsc_data$Drug, "_", gdsc_data$Hugo_Symbol)
-saveRDS(gdsc_data, "./data_munging/rds/gdsc_data_18Q3.rds", compress = "xz")
+saveRDS(gdsc_data, "./data_munging/rds/gdsc_data_18Q3_g2pgenes.rds", compress = "xz")
 ```
@@
 ```{r}
-ccle_data <- readRDS("./data_munging/rds/ccle_data_18Q3.rds")
+ccle_data <- readRDS("./data_munging/rds/ccle_data_18Q3_g2pgenes.rds")
 ccle_data_ptmuts <- filter(ccle_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
@@
 
-ctrp_data <- readRDS("./data_munging/rds/ctrp_data_18Q3.rds")
+ctrp_data <- readRDS("./data_munging/rds/ctrp_data_18Q3_g2pgenes.rds")
 ctrp_data_ptmuts <- filter(ctrp_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
@@
 
-gdsc_data <- readRDS("./data_munging/rds/gdsc_data_18Q3.rds")
+gdsc_data <- readRDS("./data_munging/rds/gdsc_data_18Q3_g2pgenes.rds")
 gdsc_data_ptmuts <- filter(gdsc_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
@@
 
-# Gene mutation frequency
-
---------------------------------------------------------------------------------
-
-```{r}
-crispr_data_g2p_summ <- unique(crispr_data_g2p[, c("Hugo_Symbol", "N_Nonsilent_Mutant", "N_Nonsilent_Other")])
-crispr_data_g2p_summ$Fraction_Mutant <- crispr_data_g2p_summ$N_Nonsilent_Mutant / (crispr_data_g2p_summ$N_Nonsilent_Mutant + crispr_data_g2p_summ$N_Nonsilent_Other)
-crispr_data_g2p_summ$Percent_Mutant <- crispr_data_g2p_summ$Fraction_Mutant * 100
-# write.table(crispr_data_g2p_summ, file = "~/Desktop/crispr_data_g2p_summ_20181003.tsv", quote = FALSE, sep = "\t")
-```
-
 # Wilcoxon tests
@@
 
-## CRISPR: Gene
+## CRISPR: G2P genes
 
@@
 crispr_data_signif_g2p_gene_plot <- ggplot(data = crispr_data_signif_g2p_gene, aes(x = Mutation_Status_Nonsilent, y = Score)) +
-  facet_wrap(~ Hugo_Symbol, nrow = 2, scales = "free_y") +
+  facet_wrap(~ Hugo_Symbol, drop = FALSE, nrow = 2, scales = "free_y") +
   geom_jitter(aes(color = Mutation_Status_Nonsilent), alpha = 0.5, width = 0.3) +
@@
 
-## CRISPR: Gene and lineage
+## CRISPR: G2P genes and lineage
 
@@
 knitr::kable(gdsc_signif_g2p_ByDrug_all[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: by-drug Wilcoxon test results for point mutations in level A G2P genes (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+## Drug screens: All CRISPR genes
+
+Drug metadata:
+```{r}
+drug_meta <- read.delim("./data_munging/drug_id_drug_name_table_10_12_2018.tsv", sep = "\t", header = FALSE)
+colnames(drug_meta) <- c("CID", "Drug")
+drug_meta$Drug <- tolower(drug_meta$Drug)
+```
+
+CCLE:
+```{r, eval=FALSE}
+ccle <- read.delim("./data_munging/data_drug_auc_ccle_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
+ccle <- merge(drug_meta, ccle, by = "CID")
+ccle_melt <- melt(ccle, id.vars = c("CID", "Drug"), measure.vars = colnames(ccle)[3:ncol(ccle)], variable.name = "accession_id", value.name = "AUC")
+ccle_grid <- expand.grid("accession_id" = unique(ccle_melt$accession_id), "Hugo_Symbol" = as.character(unique(crispr_data$Hugo_Symbol)))
+ccle_data_allgenes <- WilcoxonByDrugAllGenes(ccle_melt, ccle_grid, "CCLE")
+saveRDS(ccle_data_allgenes, "./data_munging/rds/ccle_data_18Q3_allgenes.rds", compress = "xz")
+```
+
+CTRP:
+```{r, eval=FALSE}
+ctrp <- read.delim("./data_munging/data_drug_auc_ctrp_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
+ctrp <- merge(drug_meta, ctrp, by = "CID")
+ctrp_melt <- melt(ctrp, id.vars = c("CID", "Drug"), measure.vars = colnames(ctrp)[3:ncol(ctrp)], variable.name = "accession_id", value.name = "AUC")
+ctrp_grid <- expand.grid("accession_id" = unique(ctrp_melt$accession_id), "Hugo_Symbol" = as.character(unique(crispr_data$Hugo_Symbol)))
+ctrp_data_allgenes <- WilcoxonByDrugAllGenes(ctrp_melt, ctrp_grid, "CTRP")
+saveRDS(ctrp_data_allgenes, "./data_munging/rds/ctrp_data_18Q3_allgenes.rds", compress = "xz")
+```
+
+GDSC:
+```{r, eal=FALSE}
+gdsc <- read.delim("./data_munging/data_drug_auc_gdsc_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
+gdsc <- merge(drug_meta, gdsc, by = "CID")
+gdsc_melt <- melt(gdsc, id.vars = c("CID", "Drug"), measure.vars = colnames(gdsc)[3:ncol(gdsc)], variable.name = "accession_id", value.name = "AUC")
+gdsc_grid <- expand.grid("accession_id" = unique(gdsc_melt$accession_id), "Hugo_Symbol" = as.character(unique(crispr_data$Hugo_Symbol)))
+gdsc_data_allgenes <- WilcoxonByDrugAllGenes(gdsc_melt, gdsc_grid, "GDSC")
+saveRDS(gdsc_data_allgenes, "./data_munging/rds/gdsc_data_18Q3_allgenes.rds", compress = "xz")
+```
+
+# Dataset summaries
+
+--------------------------------------------------------------------------------
+
+```{r}
+crispr_data_g2p_summ <- unique(crispr_data_g2p[, c("Hugo_Symbol", "N_Nonsilent_Mutant", "N_Nonsilent_Other")])
+crispr_data_g2p_summ$Percent_Mutant <- crispr_data_g2p_summ$N_Nonsilent_Mutant / (crispr_data_g2p_summ$N_Nonsilent_Mutant + crispr_data_g2p_summ$N_Nonsilent_Other) * 100
+rownames(crispr_data_g2p_summ) <- NULL
+# write.table(crispr_data_g2p_summ, file = "~/Desktop/crispr_data_g2p_summ_20181003.tsv", quote = FALSE, sep = "\t")
+
+knitr::kable(crispr_data_g2p_summ, caption = "CRISPR: Level A G2P genes mutation status summary") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+```{r fig.height=4, fig.width=8}
+g2p_druggene_p_summ <- g2p %>% group_by(Drug_Gene) %>% tally()
+g2p_druggene_p_summ <- merge(g2p_druggene_p_summ, ccle_signif_g2p[, c("Drug_Gene", "p")], by = "Drug_Gene", all.x = TRUE)
+g2p_druggene_p_summ <- merge(g2p_druggene_p_summ, ctrp_signif_g2p[, c("Drug_Gene", "p")], by = "Drug_Gene", all.x = TRUE, suffixes = c("_CCLE", "_CTRP"))
+g2p_druggene_p_summ <- merge(g2p_druggene_p_summ, gdsc_signif_g2p[, c("Drug_Gene", "p")], by = "Drug_Gene", all.x = TRUE)
+colnames(g2p_druggene_p_summ)[colnames(g2p_druggene_p_summ) == "p_CCLE"] <- "CCLE"
+colnames(g2p_druggene_p_summ)[colnames(g2p_druggene_p_summ) == "p_CTRP"] <- "CTRP"
+colnames(g2p_druggene_p_summ)[colnames(g2p_druggene_p_summ) == "p"] <- "GDSC"
+g2p_druggene_p_summ_melt <- melt(g2p_druggene_p_summ, id.vars = c("Drug_Gene", "n"), measure.vars = c("CCLE", "CTRP", "GDSC"), variable.name = "Dataset", value.name = "p")
+
+g2p_druggene_p_summ_plot <- ggplot(data = g2p_druggene_p_summ_melt, aes(x = p, y = n, shape = Dataset, color = Dataset)) +
+  geom_point(size = 2) +
+  geom_smooth(method = "lm", se = FALSE, lwd = 0.5) +
+  scale_color_manual(values = c("green3", "darkslategray4", "darkturquoise")) +
+  labs(x = "Gene-drug association p-value by mutation status", y = "Number of level A G2P associations")
+g2p_druggene_p_summ_plot
+# ggsave("./plots_18Q3/manuscript/g2p_druggene_p_summ_plot", g2p_druggene_p_summ_plot.png, device = "png", dpi = 450, width = 8, height = 4, units = "in")
 ```

### 2018-10-25 manuscript.Rmd

@@
 CCLE:
+
+user   system  elapsed 
+1483.399  262.649 1901.698
+
 ```{r, eval=FALSE}
@@
 ccle_grid <- expand.grid("accession_id" = unique(ccle_melt$accession_id), "Hugo_Symbol" = as.character(unique(crispr_data$Hugo_Symbol)))
-ccle_data_allgenes <- WilcoxonByDrugAllGenes(ccle_melt, ccle_grid, "CCLE")
+system.time({ ccle_data_allgenes <- WilcoxonByDrugAllGenes(ccle_melt, ccle_grid, "CCLE") })
 saveRDS(ccle_data_allgenes, "./data_munging/rds/ccle_data_18Q3_allgenes.rds", compress = "xz")
@@
 GDSC:
-```{r, eal=FALSE}
+```{r, eval=FALSE}
 gdsc <- read.delim("./data_munging/data_drug_auc_gdsc_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)

### 2018-10-25 manuscript.Rmd

@@
 
+```{r}
+ccle_data_allgenes <- readRDS("./data_munging/rds/ccle_data_18Q3_allgenes.rds")
+ccle_data_allgenes <- ccle_data_allgenes[order(ccle_data_allgenes$p),]
+
+knitr::kable(ccle_data_allgenes[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: by-drug Wilcoxon test results for point mutations in genes targeted in CRISPR screen (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
 CTRP:
@@
 gdsc_grid <- expand.grid("accession_id" = unique(gdsc_melt$accession_id), "Hugo_Symbol" = as.character(unique(crispr_data$Hugo_Symbol)))
-gdsc_data_allgenes <- WilcoxonByDrugAllGenes(gdsc_melt, gdsc_grid, "GDSC")
+system.time({ gdsc_data_allgenes <- WilcoxonByDrugAllGenes(gdsc_melt, gdsc_grid, "GDSC") })
 saveRDS(gdsc_data_allgenes, "./data_munging/rds/gdsc_data_18Q3_allgenes.rds", compress = "xz")
+```
+
+```{r}
+gdsc_data_allgenes <- readRDS("./data_munging/rds/gdsc_data_18Q3_allgenes.rds")
+gdsc_data_allgenes <- gdsc_data_allgenes[order(gdsc_data_allgenes$p),]
+
+knitr::kable(gdsc_data_allgenes[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: by-drug Wilcoxon test results for point mutations in genes targeted in CRISPR screen (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```

### 2018-10-26 manuscript.Rmd
CTRP allgenes wilcoxon test results

@@
 
-knitr::kable(ccle_data_allgenes[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: by-drug Wilcoxon test results for point mutations in genes targeted in CRISPR screen (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(ccle_data_allgenes[1:1000, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: by-drug Wilcoxon test results for point mutations in genes targeted in CRISPR screen (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 ctrp <- merge(drug_meta, ctrp, by = "CID")
-ctrp_melt <- melt(ctrp, id.vars = c("CID", "Drug"), measure.vars = colnames(ctrp)[3:ncol(ctrp)], variable.name = "accession_id", value.name = "AUC")
+ctrp_melt <- melt(ctrp, id.var  s = c("CID", "Drug"), measure.vars = colnames(ctrp)[3:ncol(ctrp)], variable.name = "accession_id", value.name = "AUC")
 ctrp_grid <- expand.grid("accession_id" = unique(ctrp_melt$accession_id), "Hugo_Symbol" = as.character(unique(crispr_data$Hugo_Symbol)))
@@
 saveRDS(ctrp_data_allgenes, "./data_munging/rds/ctrp_data_18Q3_allgenes.rds", compress = "xz")
+```
+
+```{r}
+ctrp_data_allgenes <- readRDS("./data_munging/rds/ctrp_data_18Q3_allgenes.rds")
+ctrp_data_allgenes <- ctrp_data_allgenes[order(ctrp_data_allgenes$p),]
+
+knitr::kable(ctrp_data_allgenes[1:1000, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: by-drug Wilcoxon test results for point mutations in genes targeted in CRISPR screen (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
-knitr::kable(gdsc_data_allgenes[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: by-drug Wilcoxon test results for point mutations in genes targeted in CRISPR screen (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(gdsc_data_allgenes[1:1000, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: by-drug Wilcoxon test results for point mutations in genes targeted in CRISPR screen (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```

### 2018-10-29 manuscript.Rmd
work on G2P summ plots

@@
 library(data.table)
+library(ggExtra)
 library(ggpubr)
@@
   geom_text(data = crispr_data_signif_g2p_gene_text, mapping = aes(x = 1.5, y = Text_y, label = p.signif), nudge_y = 0.2) +
-  theme(legend.position = "top") +
+  theme(legend.position = "top", axis.text.x = element_blank(), axis.ticks.x = element_blank(), axis.title.x = element_blank()) +
   labs(y = "CERES Score",
-       x = "Lineage",
        color = "Mutation Status",
@@
 crispr_data_signif_g2p_gene_plot
-# Genes with adjusted p-values < 0.3 are shown.\nBH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001\n
+
 # ggsave("./plots_18Q3/manuscript/crispr_data_signif_g2p_gene_plot.png", crispr_data_signif_g2p_gene_plot, width = 12, height = 7, units = "in")
@@
   scale_color_manual(values = crispr_data_signif_g2p_lineage_color) +
-  geom_text(data = crispr_data_signif_g2p_lineage_text, mapping = aes(x = group_general_lineage_name, y = Text_y, label = p.signif), angle = 90, nudge_y = 0.1) +
-  theme(legend.position = "top", axis.text.x = element_text(angle = 90, hjust = 1, vjust = 1, size = 10)) +
+  geom_text(data = crispr_data_signif_g2p_lineage_text, mapping = aes(x = group_general_lineage_name, y = Text_y, label = p.signif), angle = 90, vjust = 0.8, nudge_y = 0.1) +
+  theme(legend.position = "top", axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 10)) +
   labs(y = "CERES Score",
@@
 ```{r fig.height=4, fig.width=8}
-g2p_druggene_p_summ <- g2p %>% group_by(Drug_Gene) %>% tally()
-g2p_druggene_p_summ <- merge(g2p_druggene_p_summ, ccle_signif_g2p[, c("Drug_Gene", "p")], by = "Drug_Gene", all.x = TRUE)
+g2p_druggene_p_tally <- g2p %>% group_by(Drug_Gene) %>% tally()
+g2p_druggene_p_summ <- merge(g2p_druggene_p_tally, ccle_signif_g2p[, c("Drug_Gene", "p")], by = "Drug_Gene", all.x = TRUE)
 g2p_druggene_p_summ <- merge(g2p_druggene_p_summ, ctrp_signif_g2p[, c("Drug_Gene", "p")], by = "Drug_Gene", all.x = TRUE, suffixes = c("_CCLE", "_CTRP"))
@@
   geom_point(size = 2) +
-  geom_smooth(method = "lm", se = FALSE, lwd = 0.5) +
   scale_color_manual(values = c("green3", "darkslategray4", "darkturquoise")) +
@@
 g2p_druggene_p_summ_plot
-# ggsave("./plots_18Q3/manuscript/g2p_druggene_p_summ_plot", g2p_druggene_p_summ_plot.png, device = "png", dpi = 450, width = 8, height = 4, units = "in")
+# ggsave("./plots_18Q3/manuscript/g2p_druggene_p_summ_plot.png", g2p_druggene_p_summ_plot, device = "png", dpi = 450, width = 8, height = 4, units = "in")
+```
+
+```{r}
+ccle_druggene_mad_summ <- ccle_data_ptmuts %>% group_by(Drug_Gene, Mutation_Status_Nonsilent) %>% summarize(Mean_AUC = mean(AUC))
+ccle_druggene_mad_summ <- dcast(ccle_druggene_mad_summ, Drug_Gene ~ Mutation_Status_Nonsilent)
+ccle_druggene_mad_summ$MAD <- abs(ccle_druggene_mad_summ$Mutant - ccle_druggene_mad_summ$Other)
+ccle_druggene_p_summ <- ccle_signif_g2p_ByDrug_all
+ccle_druggene_p_summ$Drug_Gene <- paste0(ccle_druggene_p_summ$Drug, "_", ccle_druggene_p_summ$Hugo_Symbol)
+ccle_druggene_summ <- merge(merge(g2p_druggene_p_tally, ccle_druggene_p_summ[, c("Drug_Gene", "p")], by = "Drug_Gene", all.y = TRUE), ccle_druggene_mad_summ, by = "Drug_Gene", all = TRUE)
+ccle_druggene_summ$n <- ifelse(is.na(ccle_druggene_summ$n), 0, ccle_druggene_summ$n)
+ccle_druggene_summ$InG2P <- ifelse(ccle_druggene_summ$n != 0, "Yes", "No")
+ccle_druggene_summ$Dataset <- "CCLE"
+ccle_p_ttest <- t.test(ccle_druggene_summ$p ~ ccle_druggene_summ$InG2P)
+ccle_p_ttest_res <- paste0("t = ", round(ccle_p_ttest$statistic, 3), ", df = ", round(ccle_p_ttest$parameter, 3), ", p = ", round(ccle_p_ttest$p.value, 3))
+ccle_mad_ttest <- t.test(ccle_druggene_summ$MAD ~ ccle_druggene_summ$InG2P)
+ccle_mad_ttest_res <- paste0("t = ", round(ccle_mad_ttest$statistic, 3), ", df = ", round(ccle_mad_ttest$parameter, 3), ", p = ", round(ccle_mad_ttest$p.value, 3))
+
+ctrp_druggene_mad_summ <- ctrp_data_ptmuts %>% group_by(Drug_Gene, Mutation_Status_Nonsilent) %>% summarize(Mean_AUC = mean(AUC))
+ctrp_druggene_mad_summ <- dcast(ctrp_druggene_mad_summ, Drug_Gene ~ Mutation_Status_Nonsilent)
+ctrp_druggene_mad_summ$MAD <- abs(ctrp_druggene_mad_summ$Mutant - ctrp_druggene_mad_summ$Other)
+ctrp_druggene_p_summ <- ctrp_signif_g2p_ByDrug_all
+ctrp_druggene_p_summ$Drug_Gene <- paste0(ctrp_druggene_p_summ$Drug, "_", ctrp_druggene_p_summ$Hugo_Symbol)
+ctrp_druggene_summ <- merge(merge(g2p_druggene_p_tally, ctrp_druggene_p_summ[, c("Drug_Gene", "p")], by = "Drug_Gene", all.y = TRUE), ctrp_druggene_mad_summ, by = "Drug_Gene", all = TRUE)
+ctrp_druggene_summ$n <- ifelse(is.na(ctrp_druggene_summ$n), 0, ctrp_druggene_summ$n)
+ctrp_druggene_summ$InG2P <- ifelse(ctrp_druggene_summ$n != 0, "Yes", "No")
+ctrp_druggene_summ$Dataset <- "CTRP"
+ctrp_p_ttest <- t.test(ctrp_druggene_summ$p ~ ctrp_druggene_summ$InG2P)
+ctrp_p_ttest_res <- paste0("t = ", round(ctrp_p_ttest$statistic, 3), ", df = ", round(ctrp_p_ttest$parameter, 3), ", p = ", round(ctrp_p_ttest$p.value, 3))
+ctrp_mad_ttest <- t.test(ctrp_druggene_summ$MAD ~ ctrp_druggene_summ$InG2P)
+ctrp_mad_ttest_res <- paste0("t = ", round(ctrp_mad_ttest$statistic, 3), ", df = ", round(ctrp_mad_ttest$parameter, 3), ", p = ", round(ctrp_mad_ttest$p.value, 3))
+
+gdsc_druggene_mad_summ <- gdsc_data_ptmuts %>% group_by(Drug_Gene, Mutation_Status_Nonsilent) %>% summarize(Mean_AUC = mean(AUC))
+gdsc_druggene_mad_summ <- dcast(gdsc_druggene_mad_summ, Drug_Gene ~ Mutation_Status_Nonsilent)
+gdsc_druggene_mad_summ$MAD <- abs(gdsc_druggene_mad_summ$Mutant - gdsc_druggene_mad_summ$Other)
+gdsc_druggene_p_summ <- gdsc_signif_g2p_ByDrug_all
+gdsc_druggene_p_summ$Drug_Gene <- paste0(gdsc_druggene_p_summ$Drug, "_", gdsc_druggene_p_summ$Hugo_Symbol)
+gdsc_druggene_summ <- merge(merge(g2p_druggene_p_tally, gdsc_druggene_p_summ[, c("Drug_Gene", "p")], by = "Drug_Gene", all.y = TRUE), gdsc_druggene_mad_summ, by = "Drug_Gene", all = TRUE)
+gdsc_druggene_summ$n <- ifelse(is.na(gdsc_druggene_summ$n), 0, gdsc_druggene_summ$n)
+gdsc_druggene_summ$InG2P <- ifelse(gdsc_druggene_summ$n != 0, "Yes", "No")
+gdsc_druggene_summ$Dataset <- "GDSC"
+gdsc_p_ttest <- t.test(gdsc_druggene_summ$p ~ gdsc_druggene_summ$InG2P)
+gdsc_p_ttest_res <- paste0("t = ", round(gdsc_p_ttest$statistic, 3), ", df = ", round(gdsc_p_ttest$parameter, 3), ", p = ", round(gdsc_p_ttest$p.value, 3))
+gdsc_mad_ttest <- t.test(gdsc_druggene_summ$MAD ~ gdsc_druggene_summ$InG2P)
+gdsc_mad_ttest_res <- paste0("t = ", round(gdsc_mad_ttest$statistic, 3), ", df = ", round(gdsc_mad_ttest$parameter, 3), ", p = ", round(gdsc_mad_ttest$p.value, 3))
+```
+
+```{r fig.height=4, fig.width=12}
+g2p_druggene_all_summ <- rbind(ccle_druggene_summ, ctrp_druggene_summ, gdsc_druggene_summ)
+g2p_druggene_all_summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"), 
+                                         Test_Results_p = c(ccle_p_ttest_res, ctrp_p_ttest_res, gdsc_p_ttest_res),
+                                         Test_Results_MAD = c(ccle_mad_ttest_res, ctrp_mad_ttest_res, gdsc_mad_ttest_res))
+
+g2p_druggene_all_mad_summ_plot <- ggplot(data = g2p_druggene_all_summ) +
+  facet_wrap(~ Dataset, scales = "free_x") +
+  geom_point(mapping = aes(color = InG2P, x = MAD, y = n), alpha = 0.5) +
+  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
+  geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = c(0.75, 4, 0.2), y = 110, label = Test_Results_MAD)) +
+  labs(x = "Gene-drug association difference in mean AUC between mutation groups", y = "Number of level A G2P associations", color = "Does the gene-drug combination have level A G2P indication?") +
+  geom_rug(size = 1) +
+  theme(legend.position = "top")
+g2p_druggene_all_mad_summ_plot
+
+g2p_druggene_all_p_summ_plot <- ggplot(data = g2p_druggene_all_summ) +
+  facet_wrap(~ Dataset, scales = "free_x") +
+  geom_point(mapping = aes(color = InG2P, x = p, y = n), alpha = 0.5) +
+  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
+  scale_x_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
+  geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = 0.5, y = 110, label = Test_Results_p)) +
+  labs(x = "Gene-drug association p-value by mutation status", y = "Number of level A G2P associations", color = "Does the gene-drug combination have level A G2P indication?") +
+  theme(legend.position = "top")
+g2p_druggene_all_p_summ_plot
+
+# ggsave("./plots_18Q3/manuscript/g2p_druggene_all_mad_summ_plot.png", g2p_druggene_all_mad_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
+# ggsave("./plots_18Q3/manuscript/g2p_druggene_all_p_summ_plot.png", g2p_druggene_all_p_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
 ```

### 2018-10-30 manuscript.Rmd
updated pval vs g2p evidence summary

@@
 library(bsselectR)
+install.packages("cowplot")
 library(data.table)
-library(ggExtra)
 library(ggpubr)
 library(ggsignif)
+library(grid)
+library(gridExtra)
 library(kableExtra)
@@
 
-```{r fig.height=4, fig.width=12}
-g2p_druggene_all_summ <- rbind(ccle_druggene_summ, ctrp_druggene_summ, gdsc_druggene_summ)
-g2p_druggene_all_summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"), 
-                                         Test_Results_p = c(ccle_p_ttest_res, ctrp_p_ttest_res, gdsc_p_ttest_res),
-                                         Test_Results_MAD = c(ccle_mad_ttest_res, ctrp_mad_ttest_res, gdsc_mad_ttest_res))
-
-g2p_druggene_all_mad_summ_plot <- ggplot(data = g2p_druggene_all_summ) +
+```{r, eval=FALSE, include=FALSE}
+plot_mad_ccle_a <- ggplot(data = g2p_druggene_all_summ) +
   facet_wrap(~ Dataset, scales = "free_x") +
@@
   labs(x = "Gene-drug association difference in mean AUC between mutation groups", y = "Number of level A G2P associations", color = "Does the gene-drug combination have level A G2P indication?") +
-  geom_rug(size = 1) +
   theme(legend.position = "top")
-g2p_druggene_all_mad_summ_plot
-
-g2p_druggene_all_p_summ_plot <- ggplot(data = g2p_druggene_all_summ) +
+
+plot_p_a <- ggplot(data = g2p_druggene_all_summ) +
   facet_wrap(~ Dataset, scales = "free_x") +
@@
   theme(legend.position = "top")
+```
+
+```{r}
+g2p_druggene_all_summ <- rbind(ccle_druggene_summ, ctrp_druggene_summ, gdsc_druggene_summ)
+g2p_druggene_all_summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"), 
+                                         Test_Results_p = c(ccle_p_ttest_res, ctrp_p_ttest_res, gdsc_p_ttest_res),
+                                         Test_Results_MAD = c(ccle_mad_ttest_res, ctrp_mad_ttest_res, gdsc_mad_ttest_res))
+```
+
+```{r fig.height=7, fig.width=12}
+## MAD
+plot_mad_point <- ggplot(data = g2p_druggene_all_summ) +
+  facet_wrap(~ Dataset, scales = "free_x") +
+  geom_point(mapping = aes(color = InG2P, x = MAD, y = n), alpha = 0.5) +
+  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
+  geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = c(0.75, 4, 0.19), y = 110, label = Test_Results_MAD)) +
+  labs(x = "Gene-drug association difference in mean AUC between mutation groups", y = "Number of level A G2P associations", color = "Does the gene-drug combination have level A G2P indication?") +
+  theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
+
+plot_mad_box <- ggplot(data = g2p_druggene_all_summ) +
+  facet_wrap(~ Dataset, scales = "free_x") +
+  geom_boxplot(mapping = aes(color = InG2P, y = MAD, x = InG2P), alpha = 0.5) +
+  coord_flip() +
+  labs(x = "Level A G2P\nassociation") +
+  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
+
+plot_mad_point <- ggplot_gtable(ggplot_build(plot_mad_point))
+plot_mad_box <- ggplot_gtable(ggplot_build(plot_mad_box))
+mad_maxWidth <-  grid::unit.pmax(plot_mad_point$widths, plot_mad_box$widths)
+plot_mad_point$widths <- as.list(mad_maxWidth)
+plot_mad_box$widths <- as.list(mad_maxWidth)
+
+g2p_druggene_all_mad_summ_plot <- cowplot::plot_grid(plot_mad_box,
+                   plot_mad_point,
+                   nrow = 2,
+                   rel_heights = c(1, 4))
+g2p_druggene_all_mad_summ_plot
+# ggsave("./plots_18Q3/manuscript/g2p_druggene_all_mad_summ_plot.png", g2p_druggene_all_mad_summ_plot, device = "png", dpi = 450, width = 12, height = 7, units = "in")
+
+## P-value
+plot_p_point <- ggplot(data = g2p_druggene_all_summ) +
+  facet_wrap(~ Dataset, scales = "free_x") +
+  geom_point(mapping = aes(color = InG2P, x = p, y = n), alpha = 0.5) +
+  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
+  geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = 0.5, y = 110, label = Test_Results_p)) +
+  labs(x = "Gene-drug association difference in mean AUC between mutation groups", y = "Number of level A G2P associations", color = "Does the gene-drug combination have level A G2P indication?") +
+  theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
+
+plot_p_box <- ggplot(data = g2p_druggene_all_summ) +
+  facet_wrap(~ Dataset, scales = "free_x") +
+  geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.5) +
+  coord_flip() +
+  labs(x = "Level A G2P\nassociation") +
+  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
+
+plot_p_point <- ggplot_gtable(ggplot_build(plot_p_point))
+plot_p_box <- ggplot_gtable(ggplot_build(plot_p_box))
+p_maxWidth <-  grid::unit.pmax(plot_p_point$widths, plot_p_box$widths)
+plot_p_point$widths <- as.list(p_maxWidth)
+plot_p_box$widths <- as.list(p_maxWidth)
+
+g2p_druggene_all_p_summ_plot <- cowplot::plot_grid(plot_p_box,
+                   plot_p_point,
+                   nrow = 2,
+                   rel_heights = c(1, 4))
 g2p_druggene_all_p_summ_plot
-
-# ggsave("./plots_18Q3/manuscript/g2p_druggene_all_mad_summ_plot.png", g2p_druggene_all_mad_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
-# ggsave("./plots_18Q3/manuscript/g2p_druggene_all_p_summ_plot.png", g2p_druggene_all_p_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
+# ggsave("./plots_18Q3/manuscript/g2p_druggene_all_p_summ_plot.png", g2p_druggene_all_p_summ_plot, device = "png", dpi = 450, width = 12, height = 7, units = "in")
 ```

### 2018-10-30 manuscript.Rmd
start CCLE overlap analysis

@@
 library(bsselectR)
-install.packages("cowplot")
 library(data.table)
@@
 library(ggsignif)
-library(grid)
-library(gridExtra)
 library(kableExtra)
@@
 
+## CRISPR: Mutation status counts
+
 ```{r}
@@
 ```
+
+## Drugscreen G2P evidence
 
@@
 gdsc_mad_ttest_res <- paste0("t = ", round(gdsc_mad_ttest$statistic, 3), ", df = ", round(gdsc_mad_ttest$parameter, 3), ", p = ", round(gdsc_mad_ttest$p.value, 3))
-```
-
-```{r, eval=FALSE, include=FALSE}
-plot_mad_ccle_a <- ggplot(data = g2p_druggene_all_summ) +
-  facet_wrap(~ Dataset, scales = "free_x") +
-  geom_point(mapping = aes(color = InG2P, x = MAD, y = n), alpha = 0.5) +
-  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
-  geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = c(0.75, 4, 0.2), y = 110, label = Test_Results_MAD)) +
-  labs(x = "Gene-drug association difference in mean AUC between mutation groups", y = "Number of level A G2P associations", color = "Does the gene-drug combination have level A G2P indication?") +
-  theme(legend.position = "top")
-
-plot_p_a <- ggplot(data = g2p_druggene_all_summ) +
-  facet_wrap(~ Dataset, scales = "free_x") +
-  geom_point(mapping = aes(color = InG2P, x = p, y = n), alpha = 0.5) +
-  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
-  scale_x_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
-  geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = 0.5, y = 110, label = Test_Results_p)) +
-  labs(x = "Gene-drug association p-value by mutation status", y = "Number of level A G2P associations", color = "Does the gene-drug combination have level A G2P indication?") +
-  theme(legend.position = "top")
-```
-
-```{r}
+
 g2p_druggene_all_summ <- rbind(ccle_druggene_summ, ctrp_druggene_summ, gdsc_druggene_summ)
@@
   geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = 0.5, y = 110, label = Test_Results_p)) +
-  labs(x = "Gene-drug association difference in mean AUC between mutation groups", y = "Number of level A G2P associations", color = "Does the gene-drug combination have level A G2P indication?") +
+  labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations", color = "Does the gene-drug combination have level A G2P indication?") +
   theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
@@
 # ggsave("./plots_18Q3/manuscript/g2p_druggene_all_p_summ_plot.png", g2p_druggene_all_p_summ_plot, device = "png", dpi = 450, width = 12, height = 7, units = "in")
+```
+
+```{r}
+crispr_ccl <- unique(select(crispr_data, Broad_ID, CCLE_Name))
+ccle_ccl <- unique(select(ccle_data, Broad_ID, CCLE_Name, accession_id))
+ctrp_ccl <- unique(select(ctrp_data, Broad_ID, CCLE_Name, accession_id))
+gdsc_ccl <- unique(select(gdsc_data, Broad_ID, CCLE_Name, accession_id))
+
+# all_ccl <- merge(ccle_ccl, ctrp_ccl, by = c("Broad_ID", "CCLE_Name", "accession_id"), all = TRUE)
 ```

### 2018-11-01 manuscript.Rmd

@@
 ```{r}
-g2p <- read.delim("./data_munging/g2p_full_level_A_dataset_v2_10_10_2018.tsv", sep = "\t", header = TRUE)
+g2p <- read.delim("./data_munging/g2p_full_level_A_dataset_withPositions_10_23_2018.csv", sep = "\t", header = TRUE, row.names = 1)
 g2p$Drug <- tolower(g2p$Drug)
@@
 g2p <- subset(g2p, grepl("^CID", g2p$DrugID))
+g2p[g2p == -1] <- NA
 

### 2018-11-02 manuscript.Rmd

--- 2018-10-30 manuscript.Rmd
@@
 library(ggsignif)
+library(htmlwidgets)
 library(kableExtra)
+library(plotly)
 library(reshape2)
@@
 ```{r}
-WilcoxonByDrug <- function(drug, dataset, data_name) {
+WilcoxonByDrug <- function(drug, dataset, data_name, grouping_var) {
+  if(grouping_var == "lineage") {
+    grouper <- c("Hugo_Symbol", "group_general_lineage_name")
+  }
+  else if(grouping_var == "gene") {
+    grouper <- "Hugo_Symbol"
+  }
   use_data <- filter(dataset, Drug == drug)
-  sig <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = "Hugo_Symbol", data = use_data, method = "wilcox.test", p.adjust.method = "BH")
+  sig <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = grouper, data = use_data, method = "wilcox.test", p.adjust.method = "BH")
   sig <- adj_signif(sig)
@@
 
+## Save widget to new directory
+```{r}
+saveWidgetFix <- function (widget , file, ...) {
+  ## A wrapper to saveWidget which compensates for arguable BUG in
+  ## saveWidget which requires `file` to be in current working
+  ## directory.
+  wd <- getwd()
+  on.exit(setwd(wd))
+  outDir <- dirname(file)
+  file <- basename(file)
+  setwd(outDir);
+  saveWidget(widget, file = file,...)
+}
+```
+
 ## Make per-drug boxplots
@@
 ccl_converter <- read.delim("./data_munging/cell_line_database_v1_20180911.tsv", row.names = 1, sep = "\t", header = TRUE)
+lineage_converter <- unique(ccl_converter[, c("grouped_general_doid", "group_general_lineage_name")])
 ```
@@
 ```{r}
-g2p <- read.delim("./data_munging/g2p_full_level_A_dataset_v2_10_10_2018.tsv", sep = "\t", header = TRUE)
+g2p <- read.delim("./data_munging/g2p_full_level_A_dataset_withGroupedLineages.csv", sep = "\t", header = TRUE, row.names = 1)
+g2p <- merge(g2p, lineage_converter, by = "grouped_general_doid", all.x = TRUE)
 g2p$Drug <- tolower(g2p$Drug)
+g2p[g2p == -1] <- NA
+g2p$Ref[g2p$Ref == "None"] <- NA
+g2p$Alt[g2p$Alt == "None"] <- NA
 g2p$Drug_Gene <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene), NA, paste0(g2p$Drug, "_", g2p$Gene))
+g2p$position <- paste0("g.chr", g2p$Chromosome, ":", g2p$End, g2p$Ref, ">", g2p$Alt)
+g2p$position <- ifelse(grepl("NA", g2p$position), NA, g2p$position)
 g2p <- subset(g2p, grepl("^CID", g2p$DrugID))
@@
 
-## CRISPR: G2P genes
+## CRISPR
+
+### G2P genes
 
@@
 
-## CRISPR: G2P genes and lineage
+### G2P genes and lineage
 
@@
 
-## CCLE: G2P gene and drug
+## CCLE
+
+### G2P gene and drug
 
@@
 
-ccle_signif_g2p_ByDrug <- lapply(unique(ccle_data_g2p_genesfilt$Drug), WilcoxonByDrug, dataset = ccle_data_g2p_genesfilt, data_name = "ccle")
+ccle_signif_g2p_ByDrug <- lapply(unique(ccle_data_g2p_genesfilt$Drug), WilcoxonByDrug, dataset = ccle_data_g2p_genesfilt, data_name = "ccle", grouping_var = "gene")
 names(ccle_signif_g2p_ByDrug) <- unique(ccle_data_g2p_genesfilt$Drug)
@@
 
-## CTRP: G2P gene and drug
+### G2P gene, drug, and lineage
+
+```{r, eval=FALSE}
+ccle_signif_g2p_lineage <- lapply(unique(ccle_data_g2p_genesfilt$Drug), WilcoxonByDrug, dataset = ccle_data_g2p_genesfilt, data_name = "ccle", grouping_var = "lineage")
+names(ccle_signif_g2p_lineage) <- unique(ccle_signif_g2p_lineage$Drug)
+saveRDS(ccle_signif_g2p_lineage, "./data_munging/rds/ccle_signif_g2p_lineage.rds")
+```
+
+```{r, eval=TRUE}
+ccle_signif_g2p_lineage <- readRDS("./data_munging/rds/ccle_signif_g2p_lineage.rds")
+ccle_signif_g2p_lineage <- rbindlist(ccle_signif_g2p_lineage, use.names = TRUE)
+ccle_signif_g2p_lineage <- ccle_signif_g2p_lineage[order(ccle_signif_g2p_lineage$p),]
+
+knitr::kable(ccle_signif_g2p_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+## CTRP
+
+### G2P gene and drug
 
@@
 
-ctrp_signif_g2p_ByDrug <- lapply(unique(ctrp_data_g2p_genesfilt$Drug), WilcoxonByDrug, dataset = ctrp_data_g2p_genesfilt, data_name = "CTRP")
+ctrp_signif_g2p_ByDrug <- lapply(unique(ctrp_data_g2p_genesfilt$Drug), WilcoxonByDrug, dataset = ctrp_data_g2p_genesfilt, data_name = "CTRP", grouping_var = "gene")
 names(ctrp_signif_g2p_ByDrug) <- unique(ctrp_data_g2p_genesfilt$Drug)
@@
 
-## GDSC: G2P gene and drug
+### G2P gene, drug, and lineage
+
+```{r, eval=FALSE}
+ctrp_signif_g2p_lineage <- lapply(unique(ctrp_data_g2p_genesfilt$Drug), WilcoxonByDrug, dataset = ctrp_data_g2p_genesfilt, data_name = "ctrp", grouping_var = "lineage")
+names(ctrp_signif_g2p_lineage) <- unique(ctrp_signif_g2p_lineage$Drug)
+saveRDS(ctrp_signif_g2p_lineage, "./data_munging/rds/ctrp_signif_g2p_lineage.rds")
+```
+
+```{r, eval=TRUE}
+ctrp_signif_g2p_lineage <- readRDS("./data_munging/rds/ctrp_signif_g2p_lineage.rds")
+ctrp_signif_g2p_lineage <- rbindlist(ctrp_signif_g2p_lineage, use.names = TRUE)
+ctrp_signif_g2p_lineage <- ctrp_signif_g2p_lineage[order(ctrp_signif_g2p_lineage$p),]
+
+knitr::kable(ctrp_signif_g2p_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+## GDSC
+
+### G2P gene and drug
 
@@
 
-gdsc_signif_g2p_ByDrug <- lapply(unique(gdsc_data_g2p_genesfilt$Drug), WilcoxonByDrug, dataset = gdsc_data_g2p_genesfilt, data_name = "gdsc")
+gdsc_signif_g2p_ByDrug <- lapply(unique(gdsc_data_g2p_genesfilt$Drug), WilcoxonByDrug, dataset = gdsc_data_g2p_genesfilt, data_name = "gdsc", grouping_var = "gene")
 names(gdsc_signif_g2p_ByDrug) <- unique(gdsc_data_g2p_genesfilt$Drug)
@@
 knitr::kable(gdsc_signif_g2p_ByDrug_all[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: by-drug Wilcoxon test results for point mutations in level A G2P genes (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+### G2P gene, drug, and lineage
+
+```{r, eval=FALSE}
+gdsc_signif_g2p_lineage <- lapply(unique(gdsc_data_g2p_genesfilt$Drug), WilcoxonByDrug, dataset = gdsc_data_g2p_genesfilt, data_name = "gdsc", grouping_var = "lineage")
+names(gdsc_signif_g2p_lineage) <- unique(gdsc_signif_g2p_lineage$Drug)
+saveRDS(gdsc_signif_g2p_lineage, "./data_munging/rds/gdsc_signif_g2p_lineage.rds")
+```
+
+```{r, eval=TRUE}
+gdsc_signif_g2p_lineage <- readRDS("./data_munging/rds/gdsc_signif_g2p_lineage.rds")
+gdsc_signif_g2p_lineage <- rbindlist(gdsc_signif_g2p_lineage, use.names = TRUE)
+gdsc_signif_g2p_lineage <- gdsc_signif_g2p_lineage[order(gdsc_signif_g2p_lineage$p),]
+
+knitr::kable(gdsc_signif_g2p_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 ## Drugscreen G2P evidence
+
+### By gene
 
@@
 
-```{r fig.height=7, fig.width=12}
+```{r fig.height=5, fig.width=12}
 ## MAD
@@
   facet_wrap(~ Dataset, scales = "free_x") +
-  geom_boxplot(mapping = aes(color = InG2P, y = MAD, x = InG2P), alpha = 0.5) +
+  geom_violin(mapping = aes(color = InG2P, y = MAD, x = InG2P), alpha = 0.5) +
+  geom_boxplot(mapping = aes(color = InG2P, y = MAD, x = InG2P), alpha = 0.75, width = 0.25) +
   coord_flip() +
@@
 g2p_druggene_all_mad_summ_plot
-# ggsave("./plots_18Q3/manuscript/g2p_druggene_all_mad_summ_plot.png", g2p_druggene_all_mad_summ_plot, device = "png", dpi = 450, width = 12, height = 7, units = "in")
+# ggsave("./plots_18Q3/manuscript/g2p_druggene_all_mad_summ_plot.png", g2p_druggene_all_mad_summ_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
 
@@
   facet_wrap(~ Dataset, scales = "free_x") +
-  geom_point(mapping = aes(color = InG2P, x = p, y = n), alpha = 0.5) +
+  geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = p, y = n), alpha = 0.5) +
   scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
@@
   facet_wrap(~ Dataset, scales = "free_x") +
-  geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.5) +
+  geom_violin(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.5) +
+  geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.75, width = 0.25) +
   coord_flip() +
@@
 g2p_druggene_all_p_summ_plot
-# ggsave("./plots_18Q3/manuscript/g2p_druggene_all_p_summ_plot.png", g2p_druggene_all_p_summ_plot, device = "png", dpi = 450, width = 12, height = 7, units = "in")
-```
-
-```{r}
+# ggsave("./plots_18Q3/manuscript/g2p_druggene_all_p_summ_plot.png", g2p_druggene_all_p_summ_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
+```
+
+```{r}
+plot_p_point <- ggplot(data = g2p_druggene_all_summ) +
+  facet_wrap(~ Dataset, scales = "free_x") +
+  geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = p, y = n), alpha = 0.5) +
+  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
+  geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = 0.5, y = 110, label = Test_Results_p)) +
+  labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations", color = "Does the gene-drug combination have level A G2P indication?") +
+  theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
+
+plot_p_box <- ggplot(data = g2p_druggene_all_summ) +
+  facet_wrap(~ Dataset, scales = "free_x") +
+  geom_violin(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.5) +
+  geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.75, width = 0.25) +
+  coord_flip() +
+  labs(x = "Level A G2P\nassociation") +
+  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
+
+plot <- subplot(plot_p_box, plot_p_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Gene-drug association p-value between mutation groups"), yaxis = list(title = "Level A G2P\nassociation", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
+
+saveWidgetFix(widget = plot, file = "./plots_18Q3/manuscript/g2p_druggene_all_p_summ_plot.html")
+```
+
+### By lineage
+
+```{r}
+g2p_druggenelin_p_tally <- g2p %>% group_by(Drug_Gene, group_general_lineage_name) %>% tally()
+
+ccle_druggenelin_p_summ <- ccle_signif_g2p_lineage
+ccle_druggenelin_p_summ$Drug_Gene <- paste0(ccle_druggenelin_p_summ$Drug, "_", ccle_druggenelin_p_summ$Hugo_Symbol)
+ccle_druggenelin_summ <- merge(g2p_druggenelin_p_tally, ccle_druggenelin_p_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
+ccle_druggenelin_summ$n <- ifelse(is.na(ccle_druggenelin_summ$n), 0, ccle_druggenelin_summ$n)
+ccle_druggenelin_summ$InG2P <- ifelse(ccle_druggenelin_summ$n != 0, "Yes", "No")
+ccle_druggenelin_summ$Dataset <- "CCLE"
+
+ctrp_druggenelin_p_summ <- ctrp_signif_g2p_lineage
+ctrp_druggenelin_p_summ$Drug_Gene <- paste0(ctrp_druggenelin_p_summ$Drug, "_", ctrp_druggenelin_p_summ$Hugo_Symbol)
+ctrp_druggenelin_summ <- merge(g2p_druggenelin_p_tally, ctrp_druggenelin_p_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
+ctrp_druggenelin_summ$n <- ifelse(is.na(ctrp_druggenelin_summ$n), 0, ctrp_druggenelin_summ$n)
+ctrp_druggenelin_summ$InG2P <- ifelse(ctrp_druggenelin_summ$n != 0, "Yes", "No")
+ctrp_druggenelin_summ$Dataset <- "CTRP"
+
+gdsc_druggenelin_p_summ <- gdsc_signif_g2p_lineage
+gdsc_druggenelin_p_summ$Drug_Gene <- paste0(gdsc_druggenelin_p_summ$Drug, "_", gdsc_druggenelin_p_summ$Hugo_Symbol)
+gdsc_druggenelin_summ <- merge(g2p_druggenelin_p_tally, gdsc_druggenelin_p_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
+gdsc_druggenelin_summ$n <- ifelse(is.na(gdsc_druggenelin_summ$n), 0, gdsc_druggenelin_summ$n)
+gdsc_druggenelin_summ$InG2P <- ifelse(gdsc_druggenelin_summ$n != 0, "Yes", "No")
+gdsc_druggenelin_summ$Dataset <- "GDSC"
+
+g2p_druggenelin_all_summ <- rbind(ccle_druggenelin_summ, ctrp_druggenelin_summ, gdsc_druggenelin_summ)
+
+test <- filter(filter(g2p_druggenelin_all_summ, group_general_lineage_name == "breast cancer"), Dataset == "CCLE")
+test <- test[-39,]
+
+```
+
+```{r}
+make_G2Plineage_plotly <- function(lineage_name) {
+  use_data <- filter(g2p_druggenelin_all_summ, group_general_lineage_name == "lineage_name")
+
+  use_data_ccle <- filter(use_data, Dataset == "CCLE")
+  if(sum(use_data_ccle$n) > 0) {
+    ccle_lin_p_ttest <- t.test(use_data_ccle$p ~ use_data_ccle$InG2P)
+    ccle_lin_p_ttest_res <- paste0("t = ", round(ccle_lin_p_ttest$statistic, 3), ", df = ", round(ccle_lin_p_ttest$parameter, 3), ", p = ", round(ccle_lin_p_ttest$p.value, 3))
+  }
+  else if(sum(use_data_ccle$n) == 0) {ccle_lin_p_ttest_res <-  NA}
+
+  use_data_ctrp <- filter(use_data, Dataset == "CTRP")
+  if(sum(use_data_ctrp$n) > 0) {
+    ctrp_lin_p_ttest <- t.test(use_data_ctrp$p ~ use_data_ctrp$InG2P)
+    ctrp_lin_p_ttest_res <- paste0("t = ", round(ctrp_lin_p_ttest$statistic, 3), ", df = ", round(ctrp_lin_p_ttest$parameter, 3), ", p = ", round(ctrp_lin_p_ttest$p.value, 3))
+  }
+  else if(sum(use_data_ctrp$n) == 0) {ctrp_lin_p_ttest_res <-  NA}
+
+  use_data_gdsc <- filter(use_data, Dataset == "GDSC")
+  if(sum(use_data_gdsc$n) > 0) {
+    gdsc_lin_p_ttest <- t.test(use_data_gdsc$p ~ use_data_gdsc$InG2P)
+    gdsc_lin_p_ttest_res <- paste0("t = ", round(gdsc_lin_p_ttest$statistic, 3), ", df = ", round(gdsc_lin_p_ttest$parameter, 3), ", p = ", round(gdsc_lin_p_ttest$p.value, 3))
+  }
+  else if(sum(use_data_gdsc$n) == 0) {gdsc_lin_p_ttest_res <-  NA}
+
+  g2p_druggenelin_all_summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"), Test_Results_p = c(ccle_lin_p_ttest_res, ctrp_lin_p_ttest_res, gdsc_lin_p_ttest_res))
+
+  # plot_p_point <- ggplot(data = use_data) +
+  #   facet_wrap(~ Dataset, scales = "free_x") +
+  #   geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = p, y = n), alpha = 0.5) +
+  #   geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = 0.5, y = max(use_data$n), label = Test_Results_p)) +
+  #   labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations", color = "Does the gene-drug combination have level A G2P indication?") +
+  #   theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
+  # 
+  # plot_p_box <- ggplot(data = use_data) +
+  #   facet_wrap(~ Dataset, scales = "free_x") +
+  #   geom_violin(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.5) +
+  #   geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.75, width = 0.25) +
+  #   coord_flip() +
+  #   labs(x = "Level A G2P\nassociation") +
+  #   theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
+  # 
+  # plot <- subplot(plot_p_box, plot_p_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Gene-drug association p-value between mutation groups"), yaxis = list(title = "Level A G2P\nassociation", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
+  # 
+  # saveWidgetFix(widget = plot, file = paste0("./plots_18Q3/manuscript/lineage_plotly/", lineage_name, "_g2p_evidence_plotly.html"))
+}
+```
+
+```{r, eval=FALSE}
+lapply(as.character(unique(g2p_druggenelin_all_summ$group_general_lineage_name)), make_G2Plineage_plotly)
+```
+
+## Cell line overlap
+
+```{r, eval=FALSE}
 crispr_ccl <- unique(select(crispr_data, Broad_ID, CCLE_Name))

### 2018-11-05 manuscript.Rmd

@@
 library(reshape2)
+library(scales)
 library(tidyverse)
@@
   return(plot)
+}
+```
+
+## Make G2P lineage plotly
+```{r}
+make_G2Plineage_plotly <- function(lineage_name) {
+  use_data <- filter(g2p_druggenelin_all_summ, group_general_lineage_name == lineage_name)
+  use_data$Dataset <- factor(use_data$Dataset, levels = c("CCLE", "CTRP", "GDSC"))
+  ticker <- 0
+
+  use_data_ccle <- filter(use_data, Dataset == "CCLE")
+  use_data_ccle_summ <- use_data_ccle %>% count(InG2P)
+  if(nrow(use_data_ccle_summ) <= 1) {
+    ccle_lin_p_ttest_res <-  NA
+    ticker <- ticker + 1
+    }
+  else if(use_data_ccle_summ[use_data_ccle_summ$InG2P == "Yes",]$nn < 2) { ccle_lin_p_ttest_res <-  NA }
+  else if(use_data_ccle_summ[use_data_ccle_summ$InG2P == "Yes",]$nn >= 2) {
+    ccle_lin_p_ttest <- t.test(use_data_ccle$p ~ use_data_ccle$InG2P)
+    ccle_lin_p_ttest_res <- paste0("t = ", round(ccle_lin_p_ttest$statistic, 3), ", df = ", round(ccle_lin_p_ttest$parameter, 3), ", p = ", round(ccle_lin_p_ttest$p.value, 3))
+  }
+
+  use_data_ctrp <- filter(use_data, Dataset == "CTRP")
+  use_data_ctrp_summ <- use_data_ctrp %>% count(InG2P)
+  if(nrow(use_data_ctrp_summ) <= 1) {
+    ctrp_lin_p_ttest_res <-  NA
+    ticker <- ticker + 1
+    }
+  else if(use_data_ctrp_summ[use_data_ctrp_summ$InG2P == "Yes",]$nn < 2) { ctrp_lin_p_ttest_res <-  NA }
+  else if(use_data_ctrp_summ[use_data_ctrp_summ$InG2P == "Yes",]$nn >= 2) {
+    ctrp_lin_p_ttest <- t.test(use_data_ctrp$p ~ use_data_ctrp$InG2P)
+    ctrp_lin_p_ttest_res <- paste0("t = ", round(ctrp_lin_p_ttest$statistic, 3), ", df = ", round(ctrp_lin_p_ttest$parameter, 3), ", p = ", round(ctrp_lin_p_ttest$p.value, 3))
+  }
+
+  use_data_gdsc <- filter(use_data, Dataset == "GDSC")
+  use_data_gdsc_summ <- use_data_gdsc %>% count(InG2P)
+  if(nrow(use_data_gdsc_summ) <= 1) {
+    gdsc_lin_p_ttest_res <-  NA
+    ticker <- ticker + 1
+    }
+  else if(use_data_gdsc_summ[use_data_gdsc_summ$InG2P == "Yes",]$nn < 2) { gdsc_lin_p_ttest_res <-  NA }
+  else if(use_data_gdsc_summ[use_data_gdsc_summ$InG2P == "Yes",]$nn >= 2) {
+    gdsc_lin_p_ttest <- t.test(use_data_gdsc$p ~ use_data_gdsc$InG2P)
+    gdsc_lin_p_ttest_res <- paste0("t = ", round(gdsc_lin_p_ttest$statistic, 3), ", df = ", round(gdsc_lin_p_ttest$parameter, 3), ", p = ", round(gdsc_lin_p_ttest$p.value, 3))
+  }
+
+  y_value <- ifelse(ticker == 3, 10, max(use_data$n) + 1)
+
+  g2p_druggenelin_all_summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"), Test_Results_p = c(ccle_lin_p_ttest_res, ctrp_lin_p_ttest_res, gdsc_lin_p_ttest_res))
+
+  plot_p_point <- ggplot(data = use_data) +
+    facet_wrap(~ Dataset, drop = FALSE) +
+    coord_cartesian(xlim = c(0, 1), ylim = c(0, y_value)) +
+    scale_x_continuous(breaks = seq(0, 1, by = 0.1), labels = seq(0, 1, by = 0.1)) +
+    scale_y_continuous(breaks = pretty_breaks()) +
+    geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = p, y = n), alpha = 0.5, position = position_jitter(width = 0, height = 0.15)) +
+    geom_text(data = g2p_druggenelin_all_summ_text, mapping = aes(x = 0.5, y = y_value, label = Test_Results_p), nudge_y = 0.1) +
+    labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations", color = "Does the gene-drug combination have level A G2P indication?") +
+    theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
+
+  plot_p_box <- ggplot(data = use_data) +
+    facet_wrap(~ Dataset, drop = FALSE) +
+    coord_cartesian(ylim = c(0, 1)) +
+    scale_y_continuous(breaks = seq(0, 1, by = 0.1), labels = seq(0, 1, by = 0.1)) +
+    geom_violin(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.5) +
+    geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.75, width = 0.25) +
+    coord_flip() +
+    labs(x = "Level A G2P\nassociation") +
+    theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
+
+  plot <- subplot(plot_p_box, plot_p_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(title = lineage_name, margin = list(t = 75, l = 75), xaxis5 = list(title = "Gene-drug association p-value between mutation groups"), yaxis = list(title = "Level A G2P\nassociation", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
+
+  saveWidgetFix(widget = plot, file = paste0("./plots_18Q3/manuscript/plotlys_by_lineage/", lineage_name, "_g2p_evidence_plotly.html"))
 }
@@
 maf_df_g2p <- filter(maf_df, Hugo_Symbol %in% g2p_genes)
+ge_filt <- filter(ge_melt, Hugo_Symbol %in% g2p_genes)
 
@@
 ccle_data$Mutation_Status_Nonsilent <- ifelse(is.na(ccle_data$Mutation_Status_Nonsilent), "Other", ccle_data$Mutation_Status_Nonsilent)
+ccle_data <- merge(ccle_data, ge_filt, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
 ccle_data$Hugo_Symbol <- factor(ccle_data$Hugo_Symbol)
@@
 ctrp_data$Mutation_Status_Nonsilent <- ifelse(is.na(ctrp_data$Mutation_Status_Nonsilent), "Other", ctrp_data$Mutation_Status_Nonsilent)
+ctrp_data <- merge(ctrp_data, ge_filt, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
 ctrp_data$Hugo_Symbol <- factor(ctrp_data$Hugo_Symbol)
@@
 gdsc_data$Mutation_Status_Nonsilent <- ifelse(is.na(gdsc_data$Mutation_Status_Nonsilent), "Other", gdsc_data$Mutation_Status_Nonsilent)
+gdsc_data <- merge(gdsc_data, ge_filt, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
 gdsc_data$Hugo_Symbol <- factor(gdsc_data$Hugo_Symbol)
@@
 
-# Wilcoxon tests
+# Mutation Status Wilcoxon tests
 
@@
 
+# Gene expression
+
+--------------------------------------------------------------------------------
+
 # Dataset summaries
@@
 g2p_druggenelin_all_summ <- rbind(ccle_druggenelin_summ, ctrp_druggenelin_summ, gdsc_druggenelin_summ)
-
-test <- filter(filter(g2p_druggenelin_all_summ, group_general_lineage_name == "breast cancer"), Dataset == "CCLE")
-test <- test[-39,]
-
-```
-
-```{r}
-make_G2Plineage_plotly <- function(lineage_name) {
-  use_data <- filter(g2p_druggenelin_all_summ, group_general_lineage_name == "lineage_name")
-
-  use_data_ccle <- filter(use_data, Dataset == "CCLE")
-  if(sum(use_data_ccle$n) > 0) {
-    ccle_lin_p_ttest <- t.test(use_data_ccle$p ~ use_data_ccle$InG2P)
-    ccle_lin_p_ttest_res <- paste0("t = ", round(ccle_lin_p_ttest$statistic, 3), ", df = ", round(ccle_lin_p_ttest$parameter, 3), ", p = ", round(ccle_lin_p_ttest$p.value, 3))
-  }
-  else if(sum(use_data_ccle$n) == 0) {ccle_lin_p_ttest_res <-  NA}
-
-  use_data_ctrp <- filter(use_data, Dataset == "CTRP")
-  if(sum(use_data_ctrp$n) > 0) {
-    ctrp_lin_p_ttest <- t.test(use_data_ctrp$p ~ use_data_ctrp$InG2P)
-    ctrp_lin_p_ttest_res <- paste0("t = ", round(ctrp_lin_p_ttest$statistic, 3), ", df = ", round(ctrp_lin_p_ttest$parameter, 3), ", p = ", round(ctrp_lin_p_ttest$p.value, 3))
-  }
-  else if(sum(use_data_ctrp$n) == 0) {ctrp_lin_p_ttest_res <-  NA}
-
-  use_data_gdsc <- filter(use_data, Dataset == "GDSC")
-  if(sum(use_data_gdsc$n) > 0) {
-    gdsc_lin_p_ttest <- t.test(use_data_gdsc$p ~ use_data_gdsc$InG2P)
-    gdsc_lin_p_ttest_res <- paste0("t = ", round(gdsc_lin_p_ttest$statistic, 3), ", df = ", round(gdsc_lin_p_ttest$parameter, 3), ", p = ", round(gdsc_lin_p_ttest$p.value, 3))
-  }
-  else if(sum(use_data_gdsc$n) == 0) {gdsc_lin_p_ttest_res <-  NA}
-
-  g2p_druggenelin_all_summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"), Test_Results_p = c(ccle_lin_p_ttest_res, ctrp_lin_p_ttest_res, gdsc_lin_p_ttest_res))
-
-  # plot_p_point <- ggplot(data = use_data) +
-  #   facet_wrap(~ Dataset, scales = "free_x") +
-  #   geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = p, y = n), alpha = 0.5) +
-  #   geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = 0.5, y = max(use_data$n), label = Test_Results_p)) +
-  #   labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations", color = "Does the gene-drug combination have level A G2P indication?") +
-  #   theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
-  # 
-  # plot_p_box <- ggplot(data = use_data) +
-  #   facet_wrap(~ Dataset, scales = "free_x") +
-  #   geom_violin(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.5) +
-  #   geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.75, width = 0.25) +
-  #   coord_flip() +
-  #   labs(x = "Level A G2P\nassociation") +
-  #   theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-  # 
-  # plot <- subplot(plot_p_box, plot_p_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Gene-drug association p-value between mutation groups"), yaxis = list(title = "Level A G2P\nassociation", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
-  # 
-  # saveWidgetFix(widget = plot, file = paste0("./plots_18Q3/manuscript/lineage_plotly/", lineage_name, "_g2p_evidence_plotly.html"))
-}
-```
-
-```{r, eval=FALSE}
+g2p_druggenelin_all_summ$InG2P <- factor(g2p_druggenelin_all_summ$InG2P)
+
+# test <- filter(filter(g2p_druggenelin_all_summ, group_general_lineage_name == "breast cancer"), Dataset == "CCLE")
+# test <- test[-39,]
+
+```
+
+```{r, eval=FALSE, results = 'hide'}
 lapply(as.character(unique(g2p_druggenelin_all_summ$group_general_lineage_name)), make_G2Plineage_plotly)
+
+# test <- filter(g2p_druggenelin_all_summ, Dataset == "CCLE")
+# test_summ <- test %>% count(group_general_lineage_name, InG2P)
+# test2 <- filter(g2p_druggenelin_all_summ, Dataset == "CTRP")
+# test2_summ <- test2 %>% count(group_general_lineage_name, InG2P)
+# test3 <- filter(g2p_druggenelin_all_summ, Dataset == "GDSC")
+# test3_summ <- test3 %>% count(group_general_lineage_name, InG2P)
 ```

### 2018-11-06 manuscript.Rmd

@@
 
-  plot_p_point <- ggplot(data = use_data) +
+  plot_point <- ggplot(data = use_data) +
     facet_wrap(~ Dataset, drop = FALSE) +
@@
     geom_text(data = g2p_druggenelin_all_summ_text, mapping = aes(x = 0.5, y = y_value, label = Test_Results_p), nudge_y = 0.1) +
-    labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations", color = "Does the gene-drug combination have level A G2P indication?") +
+    labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations") +
     theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
 
-  plot_p_box <- ggplot(data = use_data) +
+  plot_box <- ggplot(data = use_data) +
     facet_wrap(~ Dataset, drop = FALSE) +
@@
     geom_violin(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.5) +
-    geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.75, width = 0.25) +
+    geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.75, width = 0.5) +
     coord_flip() +
@@
 
-  plot <- subplot(plot_p_box, plot_p_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(title = lineage_name, margin = list(t = 75, l = 75), xaxis5 = list(title = "Gene-drug association p-value between mutation groups"), yaxis = list(title = "Level A G2P\nassociation", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
-
-  saveWidgetFix(widget = plot, file = paste0("./plots_18Q3/manuscript/plotlys_by_lineage/", lineage_name, "_g2p_evidence_plotly.html"))
+  plot <- subplot(plot_box, plot_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(title = lineage_name, margin = list(t = 75, l = 75), xaxis5 = list(title = "Gene-drug association p-value between mutation groups"), yaxis = list(title = "Level A G2P\nassociation", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
+
+  saveWidgetFix(widget = plot, file = paste0("./plots_18Q3/manuscript/plotlys_p_by_lineage/", lineage_name, "_g2p_evidence_p_plotly.html"))
 }
@@
 ccle_data_ptmuts <- filter(ccle_data_ptmuts, Keep_PtMut_Tests == TRUE)
+ccle_data_ptmuts$Dataset <- "CCLE"
 
@@
 ctrp_data_ptmuts <- filter(ctrp_data_ptmuts, Keep_PtMut_Tests == TRUE)
+ctrp_data_ptmuts$Dataset <- "CTRP"
 
@@
 gdsc_data_ptmuts <- filter(gdsc_data_ptmuts, Keep_PtMut_Tests == TRUE)
+gdsc_data_ptmuts$Dataset <- "GDSC"
 
@@
 
-# Gene expression
-
---------------------------------------------------------------------------------
-
 # Dataset summaries
@@
 
+```{r}
+g2p_druggene_p_tally <- g2p %>% group_by(Drug_Gene) %>% tally()
+```
+
 ### By gene
@@
 ```{r fig.height=4, fig.width=8}
-g2p_druggene_p_tally <- g2p %>% group_by(Drug_Gene) %>% tally()
 g2p_druggene_p_summ <- merge(g2p_druggene_p_tally, ccle_signif_g2p[, c("Drug_Gene", "p")], by = "Drug_Gene", all.x = TRUE)
@@
   geom_violin(mapping = aes(color = InG2P, y = MAD, x = InG2P), alpha = 0.5) +
-  geom_boxplot(mapping = aes(color = InG2P, y = MAD, x = InG2P), alpha = 0.75, width = 0.25) +
+  geom_boxplot(mapping = aes(color = InG2P, y = MAD, x = InG2P), alpha = 0.75, width = 0.5) +
   coord_flip() +
@@
                    nrow = 2,
-                   rel_heights = c(1, 4))
+                   rel_heights = c(1.5, 4))
 g2p_druggene_all_mad_summ_plot
@@
                    nrow = 2,
-                   rel_heights = c(1, 4))
+                   rel_heights = c(1.5, 4))
 g2p_druggene_all_p_summ_plot
@@
 
-```{r}
+```{r, eval=FALSE}
 plot_p_point <- ggplot(data = g2p_druggene_all_summ) +
@@
 ```{r}
-g2p_druggenelin_p_tally <- g2p %>% group_by(Drug_Gene, group_general_lineage_name) %>% tally()
-
 ccle_druggenelin_p_summ <- ccle_signif_g2p_lineage
@@
 
+### Gene expression
+
+```{r}
+drugscreen_ptmuts <- rbind(ccle_data_ptmuts, ctrp_data_ptmuts, gdsc_data_ptmuts)
+```
+
+```{r}
+summ <- ccle_data_ptmuts %>% count(group_general_lineage_name, Drug_Gene)
+```
+
+```{r}
+PearsonByLineage <- function(lineage, dataset) {
+  use_data <- filter(dataset, group_general_lineage_name == lineage)
+  if(nrow(use_data) == 0) {
+    use_data <- NA
+  }
+  # use_data_summ <- use_data %>% count(Drug_Gene)
+  # use_data_summ <- filter(use_data_summ, n >= 3)
+  # use_data <- filter(use_data, Drug_Gene %in% as.character(unique(use_data_summ$Drug_Gene)))
+  # 
+  # pearson_res <- use_data %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate, Pearson_Pval = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value)
+  # pearson_res <- merge(g2p_druggene_p_tally, pearson_res, all.y = TRUE)
+  # pearson_res$group_general_lineage_name <- lineage
+
+  return(use_data)
+}
+
+# test <- PearsonByLineage("breast cancer", ccle_data_ptmuts)
+
+# ccle_signif_pearson <- lapply(as.character(unique(ccle_data_ptmuts$group_general_lineage_name)), PearsonByLineage, dataset = ccle_data_ptmuts)
+```
+
+```{r}
+PearsonPlotlyByLineage <- function(lineage) {
+
+  ticker <- 0
+
+  use_data_ccle <- filter(use_data, Dataset == "CCLE")
+  use_data_ccle_summ <- use_data_ccle %>% count(InG2P)
+  if(nrow(use_data_ccle_summ) <= 1) {
+    ccle_ttest_res <-  NA
+    ticker <- ticker + 1
+    }
+  else if(use_data_ccle_summ[use_data_ccle_summ$InG2P == "Yes",]$nn < 2) { ccle_ttest_res <-  NA }
+  else if(use_data_ccle_summ[use_data_ccle_summ$InG2P == "Yes",]$nn >= 2) {
+    ccle_lin_p_ttest <- t.test(use_data_ccle$p ~ use_data_ccle$InG2P)
+    ccle_ttest_res <- paste0("t = ", round(ccle_lin_p_ttest$statistic, 3), ", df = ", round(ccle_lin_p_ttest$parameter, 3), ", p = ", round(ccle_lin_p_ttest$p.value, 3))
+  }
+
+  use_data_ctrp <- filter(use_data, Dataset == "CTRP")
+  use_data_ctrp_summ <- use_data_ctrp %>% count(InG2P)
+  if(nrow(use_data_ctrp_summ) <= 1) {
+    ctrp_ttest_res <-  NA
+    ticker <- ticker + 1
+    }
+  else if(use_data_ctrp_summ[use_data_ctrp_summ$InG2P == "Yes",]$nn < 2) { ctrp_ttest_res <-  NA }
+  else if(use_data_ctrp_summ[use_data_ctrp_summ$InG2P == "Yes",]$nn >= 2) {
+    ctrp_lin_p_ttest <- t.test(use_data_ctrp$p ~ use_data_ctrp$InG2P)
+    ctrp_ttest_res <- paste0("t = ", round(ctrp_lin_p_ttest$statistic, 3), ", df = ", round(ctrp_lin_p_ttest$parameter, 3), ", p = ", round(ctrp_lin_p_ttest$p.value, 3))
+  }
+
+  use_data_gdsc <- filter(use_data, Dataset == "GDSC")
+  use_data_gdsc_summ <- use_data_gdsc %>% count(InG2P)
+  if(nrow(use_data_gdsc_summ) <= 1) {
+    gdsc_ttest_res <-  NA
+    ticker <- t                                                                                                                                                                                                                icker + 1
+    }
+  else if(use_data_gdsc_summ[use_data_gdsc_summ$InG2P == "Yes",]$nn < 2) { gdsc_ttest_res <-  NA }
+  else if(use_data_gdsc_summ[use_data_gdsc_summ$InG2P == "Yes",]$nn >= 2) {
+    gdsc_lin_p_ttest <- t.test(use_data_gdsc$p ~ use_data_gdsc$InG2P)
+    gdsc_ttest_res <- paste0("t = ", round(gdsc_lin_p_ttest$statistic, 3), ", df = ", round(gdsc_lin_p_ttest$parameter, 3), ", p = ", round(gdsc_lin_p_ttest$p.value, 3))
+  }
+
+  y_value <- ifelse(ticker == 3, 10, max(use_data$n) + 1)
+
+  g2p_druggenelin_all_summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"), Test_Results_p = c(ccle_ttest_res, ctrp_ttest_res, gdsc_ttest_res))
+  # use_data_summ <- use_data %>% count(InG2P)
+  # if(nrow(use_data_ccle_summ) <= 1) { ttest_res <- NA }
+  # else if(use_data_summ[use_data_summ$InG2P == "Yes",]$nn < 2) { ttest_res <- NA }
+  # else if(use_data_summ[use_data_summ$InG2P == "Yes",]$nn >= 2) {
+  #   ttest <- t.test(use_data$p ~ use_data$InG2P)
+  #   ttest_res <- paste0("t = ", round(ttest$statistic, 3), ", df = ", round(ttest$parameter, 3), ", p = ", round(ttest$p.value, 3))
+  # }
+}
+```
+
+```{r}
+ccle_pearson_res <- ccle_data_ptmuts %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate, Pearson_Pval = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value)
+ccle_pearson_res <- merge(g2p_druggene_p_tally, ccle_pearson_res, by = "Drug_Gene", all.y = TRUE)
+ccle_pearson_res$n <- ifelse(is.na(ccle_pearson_res$n), 0, ccle_pearson_res$n)
+ccle_pearson_res$InG2P <- ifelse(ccle_pearson_res$n != 0, "Yes", "No")
+ccle_pearson_res$Dataset <- "CCLE"
+ccle_pearson_ttest <- t.test(ccle_pearson_res$Pearson_Corr ~ ccle_pearson_res$InG2P)
+ccle_pearson_ttest_res <- paste0("t = ", round(ccle_pearson_ttest$statistic, 3), ", df = ", round(ccle_pearson_ttest$parameter, 3), ", p = ", round(ccle_pearson_ttest$p.value, 3))
+
+ctrp_pearson_res <- ctrp_data_ptmuts %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate, Pearson_Pval = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value)
+ctrp_pearson_res <- merge(g2p_druggene_p_tally, ctrp_pearson_res, by = "Drug_Gene", all.y = TRUE)
+ctrp_pearson_res$n <- ifelse(is.na(ctrp_pearson_res$n), 0, ctrp_pearson_res$n)
+ctrp_pearson_res$InG2P <- ifelse(ctrp_pearson_res$n != 0, "Yes", "No")
+ctrp_pearson_res$Dataset <- "CTRP"
+ctrp_pearson_ttest <- t.test(ctrp_pearson_res$Pearson_Corr ~ ctrp_pearson_res$InG2P)
+ctrp_pearson_ttest_res <- paste0("t = ", round(ctrp_pearson_ttest$statistic, 3), ", df = ", round(ctrp_pearson_ttest$parameter, 3), ", p = ", round(ctrp_pearson_ttest$p.value, 3))
+
+gdsc_pearson_res <- gdsc_data_ptmuts %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate, Pearson_Pval = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value)
+gdsc_pearson_res <- merge(g2p_druggene_p_tally, gdsc_pearson_res, by = "Drug_Gene", all.y = TRUE)
+gdsc_pearson_res$n <- ifelse(is.na(gdsc_pearson_res$n), 0, gdsc_pearson_res$n)
+gdsc_pearson_res$InG2P <- ifelse(gdsc_pearson_res$n != 0, "Yes", "No")
+gdsc_pearson_res$Dataset <- "GDSC"
+gdsc_pearson_ttest <- t.test(gdsc_pearson_res$Pearson_Corr ~ gdsc_pearson_res$InG2P)
+gdsc_pearson_ttest_res <- paste0("t = ", round(gdsc_pearson_ttest$statistic, 3), ", df = ", round(gdsc_pearson_ttest$parameter, 3), ", p = ", round(gdsc_pearson_ttest$p.value, 3))
+
+g2p_druggene_pearson <- rbind(ccle_pearson_res, ctrp_pearson_res, gdsc_pearson_res)
+g2p_druggene_pearson_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"), Test_Results_PearCorr = c(ccle_pearson_ttest_res, ctrp_pearson_ttest_res, gdsc_pearson_ttest_res))
+```
+
+```{r fig.height=5, fig.width=12}
+plot_pearson_point <- ggplot(data = g2p_druggene_pearson) +
+  facet_wrap(~ Dataset) +
+  geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = Pearson_Corr, y = n), alpha = 0.5) +
+  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
+  scale_x_continuous(breaks = pretty_breaks()) +
+  geom_text(data = g2p_druggene_pearson_text, mapping = aes(x = -0.05, y = 110, label = Test_Results_PearCorr)) +
+  labs(x = "Pearson correlation coefficient between gene-drug AUC and gene expression", y = "Number of level A G2P associations") +
+  theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
+
+plot_pearson_box <- ggplot(data = g2p_druggene_pearson) +
+  facet_wrap(~ Dataset) +
+  geom_violin(mapping = aes(color = InG2P, y = Pearson_Corr, x = InG2P), alpha = 0.5) +
+  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_Corr, x = InG2P), alpha = 0.75, width = 0.25) +
+  coord_flip() +
+  labs(x = "Level A G2P\nassociation") +
+  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
+
+plot_pearson_point <- ggplot_gtable(ggplot_build(plot_pearson_point))
+plot_pearson_box <- ggplot_gtable(ggplot_build(plot_pearson_box))
+p_maxWidth <-  grid::unit.pmax(plot_pearson_point$widths, plot_pearson_box$widths)
+plot_pearson_point$widths <- as.list(p_maxWidth)
+plot_pearson_box$widths <- as.list(p_maxWidth)
+
+g2p_druggene_pearson_plot <- cowplot::plot_grid(plot_pearson_box, plot_pearson_point, nrow = 2, rel_heights = c(1.5, 4))
+g2p_druggene_pearson_plot
+# ggsave("./plots_18Q3/manuscript/g2p_druggene_pearson_plot.png", g2p_druggene_pearson_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
+```
+
+```{r, eval=FALSE}
+plot_pearson_point <- ggplot(data = g2p_druggene_pearson) +
+  facet_wrap(~ Dataset) +
+  geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = Pearson_Corr, y = n), alpha = 0.5) +
+  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
+  scale_x_continuous(breaks = pretty_breaks()) +
+  geom_text(data = g2p_druggene_pearson_text, mapping = aes(x = -0.05, y = 110, label = Test_Results_PearCorr)) +
+  labs(x = "Pearson correlation coefficient between gene-drug AUC and gene expression", y = "Number of level A G2P associations") +
+  theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
+
+plot_pearson_box <- ggplot(data = g2p_druggene_pearson) +
+  facet_wrap(~ Dataset) +
+  geom_violin(mapping = aes(color = InG2P, y = Pearson_Corr, x = InG2P), alpha = 0.5) +
+  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_Corr, x = InG2P), alpha = 0.75, width = 0.25) +
+  coord_flip() +
+  labs(x = "Level A G2P\nassociation") +
+  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
+
+plot <- subplot(plot_pearson_box, plot_pearson_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Pearson correlation coefficient between gene-drug AUC and gene expression"), yaxis = list(title = "Level A G2P\nassociation", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
+
+saveWidgetFix(widget = plot, file = "./plots_18Q3/manuscript/g2p_druggene_pearson_plot.html")
+```
+
 ## Cell line overlap
@@
 
-## Figure 1
+## G2P genes
 

### 2018-11-07 manuscript.Rmd

@@
 
+### By gene
+
 ```{r}
@@
 ```
-
-### By gene
 
@@
 ```{r}
+g2p_druggenelin_p_tally <- g2p %>% group_by(Drug_Gene, group_general_lineage_name) %>% tally()
+```
+
+```{r}
 ccle_druggenelin_p_summ <- ccle_signif_g2p_lineage
@@
     gdsc_ttest_res <-  NA
-    ticker <- t                                                                                                                                                                                                                icker + 1
+    ticker <- ticker + 1
     }

### 2018-11-08 manuscript.Rmd

@@
 
+## Pearson correlation by lineage
+```{r}
+PearsonByLineage <- function(lin, dataset) {
+  use_data <- filter(dataset, group_general_lineage_name == lin)
+  use_data <- filter(use_data, !is.na(RPKM))
+  use_data_summ <- use_data %>% count(Drug_Gene)
+  use_data_summ <- filter(use_data_summ, n >= 3)
+  use_data_filt <- filter(use_data, Drug_Gene %in% as.character(unique(use_data_summ$Drug_Gene)))
+  if(nrow(use_data_filt) > 0) {
+    pearson_res <- use_data_filt %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate, Pearson_Pval = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value)
+    pearson_res <- merge(g2p_druggene_p_tally, pearson_res, all.y = TRUE)
+    pearson_res$group_general_lineage_name <- lin
+    return(pearson_res)
+  }
+}
+```
+
 ## Save widget to new directory
@@
 
+## Make G2P lineage p-value plotly
+```{r}
+MutPlotlyByLineage <- function(lineage_name) {
+  use_data <- filter(g2p_druggenelin_all_summ, group_general_lineage_name == lineage_name)
+  use_data$Dataset <- factor(use_data$Dataset, levels = c("CCLE", "CTRP", "GDSC"))
+  ticker <- 0
+
+  use_data_ccle <- filter(use_data, Dataset == "CCLE")
+  use_data_ccle_summ <- use_data_ccle %>% count(InG2P)
+  if(nrow(use_data_ccle_summ) <= 1) {
+    ccle_lin_p_ttest_res <-  NA
+    ticker <- ticker + 1
+    }
+  else if(use_data_ccle_summ[use_data_ccle_summ$InG2P == "Yes",]$nn < 2) { ccle_lin_p_ttest_res <-  NA }
+  else if(use_data_ccle_summ[use_data_ccle_summ$InG2P == "Yes",]$nn >= 2) {
+    ccle_lin_p_ttest <- t.test(use_data_ccle$p ~ use_data_ccle$InG2P)
+    ccle_lin_p_ttest_res <- paste0("t = ", round(ccle_lin_p_ttest$statistic, 3), ", df = ", round(ccle_lin_p_ttest$parameter, 3), ", p = ", round(ccle_lin_p_ttest$p.value, 3))
+  }
+
+  use_data_ctrp <- filter(use_data, Dataset == "CTRP")
+  use_data_ctrp_summ <- use_data_ctrp %>% count(InG2P)
+  if(nrow(use_data_ctrp_summ) <= 1) {
+    ctrp_lin_p_ttest_res <-  NA
+    ticker <- ticker + 1
+    }
+  else if(use_data_ctrp_summ[use_data_ctrp_summ$InG2P == "Yes",]$nn < 2) { ctrp_lin_p_ttest_res <-  NA }
+  else if(use_data_ctrp_summ[use_data_ctrp_summ$InG2P == "Yes",]$nn >= 2) {
+    ctrp_lin_p_ttest <- t.test(use_data_ctrp$p ~ use_data_ctrp$InG2P)
+    ctrp_lin_p_ttest_res <- paste0("t = ", round(ctrp_lin_p_ttest$statistic, 3), ", df = ", round(ctrp_lin_p_ttest$parameter, 3), ", p = ", round(ctrp_lin_p_ttest$p.value, 3))
+  }
+
+  use_data_gdsc <- filter(use_data, Dataset == "GDSC")
+  use_data_gdsc_summ <- use_data_gdsc %>% count(InG2P)
+  if(nrow(use_data_gdsc_summ) <= 1) {
+    gdsc_lin_p_ttest_res <-  NA
+    ticker <- ticker + 1
+    }
+  else if(use_data_gdsc_summ[use_data_gdsc_summ$InG2P == "Yes",]$nn < 2) { gdsc_lin_p_ttest_res <-  NA }
+  else if(use_data_gdsc_summ[use_data_gdsc_summ$InG2P == "Yes",]$nn >= 2) {
+    gdsc_lin_p_ttest <- t.test(use_data_gdsc$p ~ use_data_gdsc$InG2P)
+    gdsc_lin_p_ttest_res <- paste0("t = ", round(gdsc_lin_p_ttest$statistic, 3), ", df = ", round(gdsc_lin_p_ttest$parameter, 3), ", p = ", round(gdsc_lin_p_ttest$p.value, 3))
+  }
+
+  y_value <- ifelse(ticker == 3, 10, max(use_data$n) + 1)
+
+  g2p_druggenelin_all_summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"), Test_Results_p = c(ccle_lin_p_ttest_res, ctrp_lin_p_ttest_res, gdsc_lin_p_ttest_res))
+
+  plot_point <- ggplot(data = use_data) +
+    facet_wrap(~ Dataset, drop = FALSE) +
+    coord_cartesian(xlim = c(0, 1), ylim = c(0, y_value)) +
+    scale_x_continuous(breaks = seq(0, 1, by = 0.1), labels = seq(0, 1, by = 0.1)) +
+    scale_y_continuous(breaks = pretty_breaks()) +
+    geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = p, y = n), alpha = 0.5, position = position_jitter(width = 0, height = 0.15)) +
+    geom_text(data = g2p_druggenelin_all_summ_text, mapping = aes(x = 0.5, y = y_value, label = Test_Results_p), nudge_y = 0.1) +
+    labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations") +
+    theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
+
+  plot_box <- ggplot(data = use_data) +
+    facet_wrap(~ Dataset, drop = FALSE) +
+    coord_cartesian(ylim = c(0, 1)) +
+    scale_y_continuous(breaks = seq(0, 1, by = 0.1), labels = seq(0, 1, by = 0.1)) +
+    geom_violin(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.5) +
+    geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.75, width = 0.5) +
+    coord_flip() +
+    labs(x = "Level A G2P\nassociation") +
+    theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
+
+  plot <- subplot(plot_box, plot_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(title = lineage_name, margin = list(t = 75, l = 75), xaxis5 = list(title = "Gene-drug association p-value between mutation groups"), yaxis = list(title = "Level A G2P\nassociation", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
+
+  saveWidgetFix(widget = plot, file = paste0("./plots_18Q3/manuscript/plotlys_p_by_lineage/", lineage_name, "_g2p_evidence_p_plotly.html"))
+}
+```
+
+## Make G2P lineage gene expression plotly
+```{r}
+GexpPlotlyByLineage <- function(lineage) {
+  use_data <- filter(signif_pearson_all_lin, group_general_lineage_name == lineage)
+  use_data$Dataset <- factor(use_data$Dataset, levels = c("CCLE", "CTRP", "GDSC"))
+  use_data$Pearson_Pvalue <- paste0(round(use_data$Pearson_Pval, 3), "\nDrug_Gene: ", use_data$Drug_Gene)
+  ticker <- 0
+
+  use_data_ccle <- filter(use_data, Dataset == "CCLE")
+  use_data_ccle_summ <- use_data_ccle %>% count(InG2P)
+  if(nrow(use_data_ccle_summ) <= 1) {
+    ccle_ttest_res <-  NA
+    ticker <- ticker + 1
+    }
+  else if(use_data_ccle_summ[use_data_ccle_summ$InG2P == "Yes",]$nn < 2) { ccle_ttest_res <-  NA }
+  else if(use_data_ccle_summ[use_data_ccle_summ$InG2P == "Yes",]$nn >= 2) {
+    ccle_lin_ttest <- t.test(use_data_ccle$Pearson_Corr ~ use_data_ccle$InG2P)
+    ccle_ttest_res <- paste0("t = ", round(ccle_lin_ttest$statistic, 3), ", df = ", round(ccle_lin_ttest$parameter, 3), ", p = ", round(ccle_lin_ttest$p.value, 3))
+  }
+
+  use_data_ctrp <- filter(use_data, Dataset == "CTRP")
+  use_data_ctrp_summ <- use_data_ctrp %>% count(InG2P)
+  if(nrow(use_data_ctrp_summ) <= 1) {
+    ctrp_ttest_res <-  NA
+    ticker <- ticker + 1
+    }
+  else if(use_data_ctrp_summ[use_data_ctrp_summ$InG2P == "Yes",]$nn < 2) { ctrp_ttest_res <-  NA }
+  else if(use_data_ctrp_summ[use_data_ctrp_summ$InG2P == "Yes",]$nn >= 2) {
+    ctrp_lin_ttest <- t.test(use_data_ctrp$Pearson_Corr ~ use_data_ctrp$InG2P)
+    ctrp_ttest_res <- paste0("t = ", round(ctrp_lin_ttest$statistic, 3), ", df = ", round(ctrp_lin_ttest$parameter, 3), ", p = ", round(ctrp_lin_ttest$p.value, 3))
+  }
+
+  use_data_gdsc <- filter(use_data, Dataset == "GDSC")
+  use_data_gdsc_summ <- use_data_gdsc %>% count(InG2P)
+  if(nrow(use_data_gdsc_summ) <= 1) {
+    gdsc_ttest_res <-  NA
+    ticker <- ticker + 1
+    }
+  else if(use_data_gdsc_summ[use_data_gdsc_summ$InG2P == "Yes",]$nn < 2) { gdsc_ttest_res <-  NA }
+  else if(use_data_gdsc_summ[use_data_gdsc_summ$InG2P == "Yes",]$nn >= 2) {
+    gdsc_lin_ttest <- t.test(use_data_gdsc$Pearson_Corr ~ use_data_gdsc$InG2P)
+    gdsc_ttest_res <- paste0("t = ", round(gdsc_lin_ttest$statistic, 3), ", df = ", round(gdsc_lin_ttest$parameter, 3), ", p = ", round(gdsc_lin_ttest$p.value, 3))
+  }
+
+  y_value <- ifelse(ticker == 3, 10, max(use_data$n) + 1)
+  x_value <- (max(use_data$Pearson_Corr) + min(use_data$Pearson_Corr)) / 2
+
+  summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"), Test_Results = c(ccle_ttest_res, ctrp_ttest_res, gdsc_ttest_res))
+
+  plot_point <- ggplot(data = use_data) +
+    facet_wrap(~ Dataset, drop = FALSE) +
+    scale_y_continuous(breaks = pretty_breaks()) +
+    geom_point(mapping = aes(label = Pearson_Pvalue, color = InG2P, x = Pearson_Corr, y = n), alpha = 0.5, position = position_jitter(width = 0, height = 0.15)) +
+    geom_text(data = summ_text, mapping = aes(x = x_value, y = y_value, label = Test_Results), nudge_y = 1) +
+    labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations") +
+    theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
+
+  plot_box <- ggplot(data = use_data) +
+    facet_wrap(~ Dataset, drop = FALSE) +
+    geom_violin(mapping = aes(color = InG2P, y = Pearson_Corr, x = InG2P), alpha = 0.5) +
+    geom_boxplot(mapping = aes(color = InG2P, y = Pearson_Corr, x = InG2P), alpha = 0.5, width = 0.5) +
+    coord_flip() +
+    labs(x = "Level A G2P\nassociation") +
+    theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
+
+  plot <- subplot(plot_box, plot_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(title = lineage, margin = list(t = 75, l = 75), xaxis5 = list(title = "Pearson correlation coefficient between gene-drug AUC and gene expression"), yaxis = list(title = "Level A G2P\nassociation", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
+
+  saveWidgetFix(widget = plot, file = paste0("./plots_18Q3/manuscript/plotlys_pearson_by_lineage/", lineage, "_g2p_evidence_pearson_plotly.html"))
+}
+```
+
 ## Make per-drug boxplots
@@
   return(plot)
-}
-```
-
-## Make G2P lineage plotly
-```{r}
-make_G2Plineage_plotly <- function(lineage_name) {
-  use_data <- filter(g2p_druggenelin_all_summ, group_general_lineage_name == lineage_name)
-  use_data$Dataset <- factor(use_data$Dataset, levels = c("CCLE", "CTRP", "GDSC"))
-  ticker <- 0
-
-  use_data_ccle <- filter(use_data, Dataset == "CCLE")
-  use_data_ccle_summ <- use_data_ccle %>% count(InG2P)
-  if(nrow(use_data_ccle_summ) <= 1) {
-    ccle_lin_p_ttest_res <-  NA
-    ticker <- ticker + 1
-    }
-  else if(use_data_ccle_summ[use_data_ccle_summ$InG2P == "Yes",]$nn < 2) { ccle_lin_p_ttest_res <-  NA }
-  else if(use_data_ccle_summ[use_data_ccle_summ$InG2P == "Yes",]$nn >= 2) {
-    ccle_lin_p_ttest <- t.test(use_data_ccle$p ~ use_data_ccle$InG2P)
-    ccle_lin_p_ttest_res <- paste0("t = ", round(ccle_lin_p_ttest$statistic, 3), ", df = ", round(ccle_lin_p_ttest$parameter, 3), ", p = ", round(ccle_lin_p_ttest$p.value, 3))
-  }
-
-  use_data_ctrp <- filter(use_data, Dataset == "CTRP")
-  use_data_ctrp_summ <- use_data_ctrp %>% count(InG2P)
-  if(nrow(use_data_ctrp_summ) <= 1) {
-    ctrp_lin_p_ttest_res <-  NA
-    ticker <- ticker + 1
-    }
-  else if(use_data_ctrp_summ[use_data_ctrp_summ$InG2P == "Yes",]$nn < 2) { ctrp_lin_p_ttest_res <-  NA }
-  else if(use_data_ctrp_summ[use_data_ctrp_summ$InG2P == "Yes",]$nn >= 2) {
-    ctrp_lin_p_ttest <- t.test(use_data_ctrp$p ~ use_data_ctrp$InG2P)
-    ctrp_lin_p_ttest_res <- paste0("t = ", round(ctrp_lin_p_ttest$statistic, 3), ", df = ", round(ctrp_lin_p_ttest$parameter, 3), ", p = ", round(ctrp_lin_p_ttest$p.value, 3))
-  }
-
-  use_data_gdsc <- filter(use_data, Dataset == "GDSC")
-  use_data_gdsc_summ <- use_data_gdsc %>% count(InG2P)
-  if(nrow(use_data_gdsc_summ) <= 1) {
-    gdsc_lin_p_ttest_res <-  NA
-    ticker <- ticker + 1
-    }
-  else if(use_data_gdsc_summ[use_data_gdsc_summ$InG2P == "Yes",]$nn < 2) { gdsc_lin_p_ttest_res <-  NA }
-  else if(use_data_gdsc_summ[use_data_gdsc_summ$InG2P == "Yes",]$nn >= 2) {
-    gdsc_lin_p_ttest <- t.test(use_data_gdsc$p ~ use_data_gdsc$InG2P)
-    gdsc_lin_p_ttest_res <- paste0("t = ", round(gdsc_lin_p_ttest$statistic, 3), ", df = ", round(gdsc_lin_p_ttest$parameter, 3), ", p = ", round(gdsc_lin_p_ttest$p.value, 3))
-  }
-
-  y_value <- ifelse(ticker == 3, 10, max(use_data$n) + 1)
-
-  g2p_druggenelin_all_summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"), Test_Results_p = c(ccle_lin_p_ttest_res, ctrp_lin_p_ttest_res, gdsc_lin_p_ttest_res))
-
-  plot_point <- ggplot(data = use_data) +
-    facet_wrap(~ Dataset, drop = FALSE) +
-    coord_cartesian(xlim = c(0, 1), ylim = c(0, y_value)) +
-    scale_x_continuous(breaks = seq(0, 1, by = 0.1), labels = seq(0, 1, by = 0.1)) +
-    scale_y_continuous(breaks = pretty_breaks()) +
-    geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = p, y = n), alpha = 0.5, position = position_jitter(width = 0, height = 0.15)) +
-    geom_text(data = g2p_druggenelin_all_summ_text, mapping = aes(x = 0.5, y = y_value, label = Test_Results_p), nudge_y = 0.1) +
-    labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations") +
-    theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
-
-  plot_box <- ggplot(data = use_data) +
-    facet_wrap(~ Dataset, drop = FALSE) +
-    coord_cartesian(ylim = c(0, 1)) +
-    scale_y_continuous(breaks = seq(0, 1, by = 0.1), labels = seq(0, 1, by = 0.1)) +
-    geom_violin(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.5) +
-    geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.75, width = 0.5) +
-    coord_flip() +
-    labs(x = "Level A G2P\nassociation") +
-    theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
-  plot <- subplot(plot_box, plot_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(title = lineage_name, margin = list(t = 75, l = 75), xaxis5 = list(title = "Gene-drug association p-value between mutation groups"), yaxis = list(title = "Level A G2P\nassociation", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
-
-  saveWidgetFix(widget = plot, file = paste0("./plots_18Q3/manuscript/plotlys_p_by_lineage/", lineage_name, "_g2p_evidence_p_plotly.html"))
 }
@@
 
-## Drugscreen G2P evidence
-
-### By gene
+## Drugscreen: Mutation status G2P evidence
+
+### Lineage-agnostic
 
@@
 ```{r, eval=FALSE, results = 'hide'}
-lapply(as.character(unique(g2p_druggenelin_all_summ$group_general_lineage_name)), make_G2Plineage_plotly)
+lapply(as.character(unique(g2p_druggenelin_all_summ$group_general_lineage_name)), MutPlotlyByLineage)
 
@@
 
-### Gene expression
-
-```{r}
-drugscreen_ptmuts <- rbind(ccle_data_ptmuts, ctrp_data_ptmuts, gdsc_data_ptmuts)
-```
-
-```{r}
-summ <- ccle_data_ptmuts %>% count(group_general_lineage_name, Drug_Gene)
-```
-
-```{r}
-PearsonByLineage <- function(lineage, dataset) {
-  use_data <- filter(dataset, group_general_lineage_name == lineage)
-  if(nrow(use_data) == 0) {
-    use_data <- NA
-  }
-  # use_data_summ <- use_data %>% count(Drug_Gene)
-  # use_data_summ <- filter(use_data_summ, n >= 3)
-  # use_data <- filter(use_data, Drug_Gene %in% as.character(unique(use_data_summ$Drug_Gene)))
-  # 
-  # pearson_res <- use_data %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate, Pearson_Pval = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value)
-  # pearson_res <- merge(g2p_druggene_p_tally, pearson_res, all.y = TRUE)
-  # pearson_res$group_general_lineage_name <- lineage
-
-  return(use_data)
-}
-
-# test <- PearsonByLineage("breast cancer", ccle_data_ptmuts)
-
-# ccle_signif_pearson <- lapply(as.character(unique(ccle_data_ptmuts$group_general_lineage_name)), PearsonByLineage, dataset = ccle_data_ptmuts)
-```
-
-```{r}
-PearsonPlotlyByLineage <- function(lineage) {
-
-  ticker <- 0
-
-  use_data_ccle <- filter(use_data, Dataset == "CCLE")
-  use_data_ccle_summ <- use_data_ccle %>% count(InG2P)
-  if(nrow(use_data_ccle_summ) <= 1) {
-    ccle_ttest_res <-  NA
-    ticker <- ticker + 1
-    }
-  else if(use_data_ccle_summ[use_data_ccle_summ$InG2P == "Yes",]$nn < 2) { ccle_ttest_res <-  NA }
-  else if(use_data_ccle_summ[use_data_ccle_summ$InG2P == "Yes",]$nn >= 2) {
-    ccle_lin_p_ttest <- t.test(use_data_ccle$p ~ use_data_ccle$InG2P)
-    ccle_ttest_res <- paste0("t = ", round(ccle_lin_p_ttest$statistic, 3), ", df = ", round(ccle_lin_p_ttest$parameter, 3), ", p = ", round(ccle_lin_p_ttest$p.value, 3))
-  }
-
-  use_data_ctrp <- filter(use_data, Dataset == "CTRP")
-  use_data_ctrp_summ <- use_data_ctrp %>% count(InG2P)
-  if(nrow(use_data_ctrp_summ) <= 1) {
-    ctrp_ttest_res <-  NA
-    ticker <- ticker + 1
-    }
-  else if(use_data_ctrp_summ[use_data_ctrp_summ$InG2P == "Yes",]$nn < 2) { ctrp_ttest_res <-  NA }
-  else if(use_data_ctrp_summ[use_data_ctrp_summ$InG2P == "Yes",]$nn >= 2) {
-    ctrp_lin_p_ttest <- t.test(use_data_ctrp$p ~ use_data_ctrp$InG2P)
-    ctrp_ttest_res <- paste0("t = ", round(ctrp_lin_p_ttest$statistic, 3), ", df = ", round(ctrp_lin_p_ttest$parameter, 3), ", p = ", round(ctrp_lin_p_ttest$p.value, 3))
-  }
-
-  use_data_gdsc <- filter(use_data, Dataset == "GDSC")
-  use_data_gdsc_summ <- use_data_gdsc %>% count(InG2P)
-  if(nrow(use_data_gdsc_summ) <= 1) {
-    gdsc_ttest_res <-  NA
-    ticker <- ticker + 1
-    }
-  else if(use_data_gdsc_summ[use_data_gdsc_summ$InG2P == "Yes",]$nn < 2) { gdsc_ttest_res <-  NA }
-  else if(use_data_gdsc_summ[use_data_gdsc_summ$InG2P == "Yes",]$nn >= 2) {
-    gdsc_lin_p_ttest <- t.test(use_data_gdsc$p ~ use_data_gdsc$InG2P)
-    gdsc_ttest_res <- paste0("t = ", round(gdsc_lin_p_ttest$statistic, 3), ", df = ", round(gdsc_lin_p_ttest$parameter, 3), ", p = ", round(gdsc_lin_p_ttest$p.value, 3))
-  }
-
-  y_value <- ifelse(ticker == 3, 10, max(use_data$n) + 1)
-
-  g2p_druggenelin_all_summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"), Test_Results_p = c(ccle_ttest_res, ctrp_ttest_res, gdsc_ttest_res))
-  # use_data_summ <- use_data %>% count(InG2P)
-  # if(nrow(use_data_ccle_summ) <= 1) { ttest_res <- NA }
-  # else if(use_data_summ[use_data_summ$InG2P == "Yes",]$nn < 2) { ttest_res <- NA }
-  # else if(use_data_summ[use_data_summ$InG2P == "Yes",]$nn >= 2) {
-  #   ttest <- t.test(use_data$p ~ use_data$InG2P)
-  #   ttest_res <- paste0("t = ", round(ttest$statistic, 3), ", df = ", round(ttest$parameter, 3), ", p = ", round(ttest$p.value, 3))
-  # }
-}
-```
+## Drugscreen: Gene expression G2P evidence
+
+### Lineage-agnostic
 
@@
   geom_violin(mapping = aes(color = InG2P, y = Pearson_Corr, x = InG2P), alpha = 0.5) +
-  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_Corr, x = InG2P), alpha = 0.75, width = 0.25) +
+  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_Corr, x = InG2P), alpha = 0.5, width = 0.25) +
   coord_flip() +
@@
 saveWidgetFix(widget = plot, file = "./plots_18Q3/manuscript/g2p_druggene_pearson_plot.html")
+```
+
+### By lineage
+
+```{r, eval=FALSE}
+ccle_lineages4pearson <- as.character(unique(ccle_data_ptmuts$group_general_lineage_name))[!is.na(as.character(unique(ccle_data_ptmuts$group_general_lineage_name)))]
+ccle_signif_pearson <- lapply(ccle_lineages4pearson, PearsonByLineage, dataset = ccle_data_ptmuts)
+ccle_signif_pearson_all_lin <- rbindlist(ccle_signif_pearson, use.names = TRUE)
+ccle_signif_pearson_all_lin$Dataset <- "CCLE"
+
+ctrp_lineages4pearson <- as.character(unique(ctrp_data_ptmuts$group_general_lineage_name))[!is.na(as.character(unique(ctrp_data_ptmuts$group_general_lineage_name)))]
+ctrp_signif_pearson <- lapply(ctrp_lineages4pearson, PearsonByLineage, dataset = ctrp_data_ptmuts)
+ctrp_signif_pearson_all_lin <- rbindlist(ctrp_signif_pearson, use.names = TRUE)
+ctrp_signif_pearson_all_lin$Dataset <- "CTRP"
+
+gdsc_lineages4pearson <- as.character(unique(gdsc_data_ptmuts$group_general_lineage_name))[!is.na(as.character(unique(gdsc_data_ptmuts$group_general_lineage_name)))]
+gdsc_signif_pearson <- lapply(gdsc_lineages4pearson, PearsonByLineage, dataset = gdsc_data_ptmuts)
+gdsc_signif_pearson_all_lin <- rbindlist(gdsc_signif_pearson, use.names = TRUE)
+gdsc_signif_pearson_all_lin$Dataset <- "GDSC"
+
+signif_pearson_all_lin <- rbind(ccle_signif_pearson_all_lin, ctrp_signif_pearson_all_lin, gdsc_signif_pearson_all_lin)
+signif_pearson_all_lin$n <- ifelse(is.na(signif_pearson_all_lin$n), 0, signif_pearson_all_lin$n)
+signif_pearson_all_lin$InG2P <- ifelse(signif_pearson_all_lin$n != 0, "Yes", "No")
+```
+
+```{r, results='hide', eval=FALSE}
+lapply(as.character(unique(signif_pearson_all_lin$group_general_lineage_name)), GexpPlotlyByLineage)
 ```

### 2018-11-09 manuscript.Rmd

@@
   use_data_summ <- use_data %>% count(Drug_Gene)
-  use_data_summ <- filter(use_data_summ, n >= 3)
+  use_data_summ <- filter(use_data_summ, n >= 3) # cor.test requires at least 3 non-NA data points
   use_data_filt <- filter(use_data, Drug_Gene %in% as.character(unique(use_data_summ$Drug_Gene)))
@@
     geom_text(data = g2p_druggenelin_all_summ_text, mapping = aes(x = 0.5, y = y_value, label = Test_Results_p), nudge_y = 0.1) +
-    labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations") +
+    labs(x = "Drug-gene association p-value between mutation groups", y = "Number of level A G2P associations") +
     theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
@@
 
-  plot <- subplot(plot_box, plot_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(title = lineage, margin = list(t = 75, l = 75), xaxis5 = list(title = "Pearson correlation coefficient between gene-drug AUC and gene expression"), yaxis = list(title = "Level A G2P\nassociation", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
+  plot <- subplot(plot_box, plot_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(title = lineage, margin = list(t = 75, l = 75), xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and gene expression"), yaxis = list(title = "Level A G2P\nassociation", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
 
@@
   if(dataset == "CCLE" | dataset == "ccle") {
-    use_data <- filter(ccle_data_g2p_genesfilt, Drug == drug)
+    use_data <- filter(ccle_data_ptmuts, Drug == drug)
     use_color <- as.character(use_data$Color_Nonsilent)
@@
   else if(dataset == "CTRP" | dataset == "ctrp") {
-    use_data <- filter(ctrp_data_g2p_genesfilt, Drug == drug)
+    use_data <- filter(ctrp_data_ptmuts, Drug == drug)
     use_color <- as.character(use_data$Color_Nonsilent)
@@
   else if(dataset == "GDSC" | dataset == "gdsc") {
-    use_data <- filter(gdsc_data_g2p_genesfilt, Drug == drug)
+    use_data <- filter(gdsc_data_ptmuts, Drug == drug)
     use_color <- as.character(use_data$Color_Nonsilent)
@@
 ge_filt <- filter(ge_melt, Hugo_Symbol %in% g2p_genes)
+cn_filt <- filter(cn_melt, Hugo_Symbol %in% g2p_genes)
 
@@
 ccle_data <- merge(ccle_data, ge_filt, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
+ccle_data <- merge(ccle_data, cn_filt, by = c("Hugo_Symbol", "Broad_ID"), all.x = TRUE)
 ccle_data$Hugo_Symbol <- factor(ccle_data$Hugo_Symbol)
@@
 ctrp_data <- merge(ctrp_data, ge_filt, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
+ctrp_data <- merge(ctrp_data, cn_filt, by = c("Hugo_Symbol", "Broad_ID"), all.x = TRUE)
 ctrp_data$Hugo_Symbol <- factor(ctrp_data$Hugo_Symbol)
@@
 gdsc_data <- merge(gdsc_data, ge_filt, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
+gdsc_data <- merge(gdsc_data, cn_filt, by = c("Hugo_Symbol", "Broad_ID"), all.x = TRUE)
 gdsc_data$Hugo_Symbol <- factor(gdsc_data$Hugo_Symbol)
@@
 ccle_data_ptmuts$Dataset <- "CCLE"
+ccle_data_ptmuts$Hugo_Symbol <- ordered(ccle_data_ptmuts$Hugo_Symbol, levels = g2p_genes)
 
@@
 ctrp_data_ptmuts$Dataset <- "CTRP"
+ctrp_data_ptmuts$Hugo_Symbol <- ordered(ctrp_data_ptmuts$Hugo_Symbol, levels = g2p_genes)
 
@@
 gdsc_data_ptmuts$Dataset <- "GDSC"
+gdsc_data_ptmuts$Hugo_Symbol <- ordered(gdsc_data_ptmuts$Hugo_Symbol, levels = g2p_genes)
 
@@
 
-# Filter drug screen datasets for G2P genes in drug-gene associations
-ccle_data_g2p_genesfilt <- filter(ccle_data_ptmuts, Hugo_Symbol %in% g2p_genes)
-ccle_data_g2p_genesfilt$Hugo_Symbol <- ordered(ccle_data_g2p_genesfilt$Hugo_Symbol, levels = g2p_genes)
-ctrp_data_g2p_genesfilt <- filter(ctrp_data_ptmuts, Hugo_Symbol %in% g2p_genes)
-ctrp_data_g2p_genesfilt$Hugo_Symbol <- ordered(ctrp_data_g2p_genesfilt$Hugo_Symbol, levels = g2p_genes)
-gdsc_data_g2p_genesfilt <- filter(gdsc_data_ptmuts, Hugo_Symbol %in% g2p_genes)
-gdsc_data_g2p_genesfilt$Hugo_Symbol <- ordered(gdsc_data_g2p_genesfilt$Hugo_Symbol, levels = g2p_genes)
+# Filter drug screen datasets for G2P drugs and genes
+ccle_data_g2p_grid <- filter(ccle_data_ptmuts, Drug %in% g2p_drugs)
+ctrp_data_g2p_grid <- filter(ctrp_data_ptmuts, Drug %in% g2p_drugs)
+gdsc_data_g2p_grid <- filter(gdsc_data_ptmuts, Drug %in% g2p_drugs)
 ```
@@
 
-### G2P genes and lineage
+### Gene
 
@@
 ```{r, eval=FALSE}
+# G2P drug-gene associations only
 ccle_signif_g2p <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene", data = ccle_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
@@
 
-ccle_signif_g2p_ByDrug <- lapply(unique(ccle_data_g2p_genesfilt$Drug), WilcoxonByDrug, dataset = ccle_data_g2p_genesfilt, data_name = "ccle", grouping_var = "gene")
-names(ccle_signif_g2p_ByDrug) <- unique(ccle_data_g2p_genesfilt$Drug)
-saveRDS(ccle_signif_g2p_ByDrug, "./data_munging/rds/ccle_signif_g2p_ByDrug.rds")
+# Grid comparisons of G2P drugs and genes
+ccle_signif_g2p_grid <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "Drug"), data = ccle_data_g2p_grid, method = "wilcox.test", p.adjust.method = "BH")
+ccle_signif_g2p_grid <- adj_signif(ccle_signif_g2p_grid)
+ccle_signif_g2p_grid <- ccle_signif_g2p_grid[order(ccle_signif_g2p_grid$p),]
+saveRDS(ccle_signif_g2p_grid, "./data_munging/rds/ccle_signif_g2p_grid.rds")
 ```
@@
 ```{r}
-ccle_signif_g2p_ByDrug <- readRDS("./data_munging/rds/ccle_signif_g2p_ByDrug.rds")
-ccle_signif_g2p_ByDrug_all <- rbindlist(ccle_signif_g2p_ByDrug, use.names = TRUE)
-ccle_signif_g2p_ByDrug_all <- ccle_signif_g2p_ByDrug_all[order(ccle_signif_g2p_ByDrug_all$p),]
-
-knitr::kable(ccle_signif_g2p_ByDrug_all[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: By-drug Wilcoxon test results for point mutations in level A G2P genes (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+ccle_signif_g2p_grid <- readRDS("./data_munging/rds/ccle_signif_g2p_grid.rds")
+
+knitr::kable(ccle_signif_g2p_grid[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: By-drug Wilcoxon test results for point mutations in level A G2P genes (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 ```{r, eval=FALSE}
-ccle_signif_g2p_lineage <- lapply(unique(ccle_data_g2p_genesfilt$Drug), WilcoxonByDrug, dataset = ccle_data_g2p_genesfilt, data_name = "ccle", grouping_var = "lineage")
+ccle_signif_g2p_lineage <- lapply(unique(ccle_data_ptmuts$Drug), WilcoxonByDrug, dataset = ccle_data_ptmuts, data_name = "ccle", grouping_var = "lineage")
 names(ccle_signif_g2p_lineage) <- unique(ccle_signif_g2p_lineage$Drug)
@@
 
-ctrp_signif_g2p_ByDrug <- lapply(unique(ctrp_data_g2p_genesfilt$Drug), WilcoxonByDrug, dataset = ctrp_data_g2p_genesfilt, data_name = "CTRP", grouping_var = "gene")
-names(ctrp_signif_g2p_ByDrug) <- unique(ctrp_data_g2p_genesfilt$Drug)
+ctrp_signif_g2p_ByDrug <- lapply(unique(ctrp_data_ptmuts$Drug), WilcoxonByDrug, dataset = ctrp_data_ptmuts, data_name = "CTRP", grouping_var = "gene")
+names(ctrp_signif_g2p_ByDrug) <- unique(ctrp_data_ptmuts$Drug)
 saveRDS(ctrp_signif_g2p_ByDrug, "./data_munging/rds/ctrp_signif_g2p_ByDrug.rds")
@@
 ```{r, eval=FALSE}
-ctrp_signif_g2p_lineage <- lapply(unique(ctrp_data_g2p_genesfilt$Drug), WilcoxonByDrug, dataset = ctrp_data_g2p_genesfilt, data_name = "ctrp", grouping_var = "lineage")
+ctrp_signif_g2p_lineage <- lapply(unique(ctrp_data_ptmuts$Drug), WilcoxonByDrug, dataset = ctrp_data_ptmuts, data_name = "ctrp", grouping_var = "lineage")
 names(ctrp_signif_g2p_lineage) <- unique(ctrp_signif_g2p_lineage$Drug)
@@
 
-gdsc_signif_g2p_ByDrug <- lapply(unique(gdsc_data_g2p_genesfilt$Drug), WilcoxonByDrug, dataset = gdsc_data_g2p_genesfilt, data_name = "gdsc", grouping_var = "gene")
-names(gdsc_signif_g2p_ByDrug) <- unique(gdsc_data_g2p_genesfilt$Drug)
+gdsc_signif_g2p_ByDrug <- lapply(unique(gdsc_data_ptmuts$Drug), WilcoxonByDrug, dataset = gdsc_data_ptmuts, data_name = "gdsc", grouping_var = "gene")
+names(gdsc_signif_g2p_ByDrug) <- unique(gdsc_data_ptmuts$Drug)
 saveRDS(gdsc_signif_g2p_ByDrug, "./data_munging/rds/gdsc_signif_g2p_ByDrug.rds")
@@
 ```{r, eval=FALSE}
-gdsc_signif_g2p_lineage <- lapply(unique(gdsc_data_g2p_genesfilt$Drug), WilcoxonByDrug, dataset = gdsc_data_g2p_genesfilt, data_name = "gdsc", grouping_var = "lineage")
+gdsc_signif_g2p_lineage <- lapply(unique(gdsc_data_ptmuts$Drug), WilcoxonByDrug, dataset = gdsc_data_ptmuts, data_name = "gdsc", grouping_var = "lineage")
 names(gdsc_signif_g2p_lineage) <- unique(gdsc_signif_g2p_lineage$Drug)
@@
   geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = c(0.75, 4, 0.19), y = 110, label = Test_Results_MAD)) +
-  labs(x = "Gene-drug association difference in mean AUC between mutation groups", y = "Number of level A G2P associations", color = "Does the gene-drug combination have level A G2P indication?") +
+  labs(x = "Gene-drug association difference in mean AUC between mutation groups", y = "Number of level A G2P associations", color = "Does the drug-gene combination have level A G2P indication?") +
   theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
@@
   geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = 0.5, y = 110, label = Test_Results_p)) +
-  labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations", color = "Does the gene-drug combination have level A G2P indication?") +
+  labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations", color = "Does the drug-gene combination have level A G2P indication?") +
   theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
@@
   geom_text(data = g2p_druggene_pearson_text, mapping = aes(x = -0.05, y = 110, label = Test_Results_PearCorr)) +
-  labs(x = "Pearson correlation coefficient between gene-drug AUC and gene expression", y = "Number of level A G2P associations") +
+  labs(x = "Pearson correlation coefficient between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +
   theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
@@
 
-plot <- subplot(plot_pearson_box, plot_pearson_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Pearson correlation coefficient between gene-drug AUC and gene expression"), yaxis = list(title = "Level A G2P\nassociation", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
+plot <- subplot(plot_pearson_box, plot_pearson_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and gene expression"), yaxis = list(title = "Level A G2P\nassociation", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
 
@@
 ```{r, eval=FALSE}
-ccle_drugs <- as.character(unique(ccle_data_g2p_genesfilt$Drug))
+ccle_drugs <- as.character(unique(ccle_data_ptmuts$Drug))
 ccle_g2p_drugboxplots <- lapply(ccle_drugs, makeDrugBoxplots, dataset = "CCLE")
@@
 ```{r, eval=FALSE}
-ctrp_drugs <- as.character(unique(ctrp_data_g2p_genesfilt$Drug))
+ctrp_drugs <- as.character(unique(ctrp_data_ptmuts$Drug))
 ctrp_g2p_drugboxplots <- lapply(ctrp_drugs, makeDrugBoxplots, dataset = "ctrp")
@@
 ```{r, eval=FALSE}
-gdsc_drugs <- as.character(unique(gdsc_data_g2p_genesfilt$Drug))
+gdsc_drugs <- as.character(unique(gdsc_data_ptmuts$Drug))
 gdsc_g2p_drugboxplots <- lapply(gdsc_drugs, makeDrugBoxplots, dataset = "gdsc")
@@
 
-## G2P level A gene-drug associations only
+## G2P level A drug-gene associations only
 

### 2018-11-12 manuscript.Rmd
update pearson plotlys w/ abs and +/-

@@
     pearson_res$group_general_lineage_name <- lin
+    pearson_res$Pearson_Corr_Abs <- abs(pearson_res$Pearson_Corr)
+    pearson_res$Pearson_Corr_Sign <- ifelse(sign(pearson_res$Pearson_Corr) == 1, "+",
+                                            ifelse(sign(pearson_res$Pearson_Corr) == -1, "-", "0"))
     return(pearson_res)
@@
     geom_violin(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.5) +
-    geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.75, width = 0.5) +
+    geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.75, width = 0.25) +
     coord_flip() +
@@
   else if(use_data_ccle_summ[use_data_ccle_summ$InG2P == "Yes",]$nn >= 2) {
-    ccle_lin_ttest <- t.test(use_data_ccle$Pearson_Corr ~ use_data_ccle$InG2P)
+    ccle_lin_ttest <- t.test(use_data_ccle$Pearson_Corr_Abs ~ use_data_ccle$InG2P)
     ccle_ttest_res <- paste0("t = ", round(ccle_lin_ttest$statistic, 3), ", df = ", round(ccle_lin_ttest$parameter, 3), ", p = ", round(ccle_lin_ttest$p.value, 3))
@@
   else if(use_data_ctrp_summ[use_data_ctrp_summ$InG2P == "Yes",]$nn >= 2) {
-    ctrp_lin_ttest <- t.test(use_data_ctrp$Pearson_Corr ~ use_data_ctrp$InG2P)
+    ctrp_lin_ttest <- t.test(use_data_ctrp$Pearson_Corr_Abs ~ use_data_ctrp$InG2P)
     ctrp_ttest_res <- paste0("t = ", round(ctrp_lin_ttest$statistic, 3), ", df = ", round(ctrp_lin_ttest$parameter, 3), ", p = ", round(ctrp_lin_ttest$p.value, 3))
@@
   else if(use_data_gdsc_summ[use_data_gdsc_summ$InG2P == "Yes",]$nn >= 2) {
-    gdsc_lin_ttest <- t.test(use_data_gdsc$Pearson_Corr ~ use_data_gdsc$InG2P)
+    gdsc_lin_ttest <- t.test(use_data_gdsc$Pearson_Corr_Abs ~ use_data_gdsc$InG2P)
     gdsc_ttest_res <- paste0("t = ", round(gdsc_lin_ttest$statistic, 3), ", df = ", round(gdsc_lin_ttest$parameter, 3), ", p = ", round(gdsc_lin_ttest$p.value, 3))
@@
   y_value <- ifelse(ticker == 3, 10, max(use_data$n) + 1)
-  x_value <- (max(use_data$Pearson_Corr) + min(use_data$Pearson_Corr)) / 2
 
@@
     scale_y_continuous(breaks = pretty_breaks()) +
-    geom_point(mapping = aes(label = Pearson_Pvalue, color = InG2P, x = Pearson_Corr, y = n), alpha = 0.5, position = position_jitter(width = 0, height = 0.15)) +
-    geom_text(data = summ_text, mapping = aes(x = x_value, y = y_value, label = Test_Results), nudge_y = 1) +
-    labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations") +
+    geom_point(mapping = aes(label = Pearson_Pvalue, color = InG2P, shape = Pearson_Corr_Sign, x = Pearson_Corr_Abs, y = n), alpha = 0.5, position = position_jitter(width = 0, height = 0.15)) +
+    scale_shape_manual(values = c(45, 43, 42)) +
+    geom_text(data = summ_text, mapping = aes(x = 0.5, y = y_value, label = Test_Results), nudge_y = 1) +
+    labs(y = "Number of level A G2P associations") +
     theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
@@
     facet_wrap(~ Dataset, drop = FALSE) +
-    geom_violin(mapping = aes(color = InG2P, y = Pearson_Corr, x = InG2P), alpha = 0.5) +
-    geom_boxplot(mapping = aes(color = InG2P, y = Pearson_Corr, x = InG2P), alpha = 0.5, width = 0.5) +
+    geom_violin(mapping = aes(color = InG2P, y = Pearson_Corr_Abs, x = InG2P), alpha = 0.5) +
+    geom_boxplot(mapping = aes(color = InG2P, y = Pearson_Corr_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
     coord_flip() +
@@
 ccle_druggene_mad_summ$MAD <- abs(ccle_druggene_mad_summ$Mutant - ccle_druggene_mad_summ$Other)
-ccle_druggene_p_summ <- ccle_signif_g2p_ByDrug_all
+ccle_druggene_p_summ <- ccle_signif_g2p_lineage
 ccle_druggene_p_summ$Drug_Gene <- paste0(ccle_druggene_p_summ$Drug, "_", ccle_druggene_p_summ$Hugo_Symbol)
@@
 ctrp_druggene_mad_summ$MAD <- abs(ctrp_druggene_mad_summ$Mutant - ctrp_druggene_mad_summ$Other)
-ctrp_druggene_p_summ <- ctrp_signif_g2p_ByDrug_all
+ctrp_druggene_p_summ <- ctrp_signif_g2p_lineage
 ctrp_druggene_p_summ$Drug_Gene <- paste0(ctrp_druggene_p_summ$Drug, "_", ctrp_druggene_p_summ$Hugo_Symbol)
@@
 gdsc_druggene_mad_summ$MAD <- abs(gdsc_druggene_mad_summ$Mutant - gdsc_druggene_mad_summ$Other)
-gdsc_druggene_p_summ <- gdsc_signif_g2p_ByDrug_all
+gdsc_druggene_p_summ <- gdsc_signif_g2p_lineage
 gdsc_druggene_p_summ$Drug_Gene <- paste0(gdsc_druggene_p_summ$Drug, "_", gdsc_druggene_p_summ$Hugo_Symbol)
@@
 g2p_druggene_pearson <- rbind(ccle_pearson_res, ctrp_pearson_res, gdsc_pearson_res)
+g2p_druggene_pearson$Pearson_Corr_Abs <- abs(g2p_druggene_pearson$Pearson_Corr)
+g2p_druggene_pearson$Pearson_Corr_Sign <- ifelse(sign(g2p_druggene_pearson$Pearson_Corr) == 1, "+",
+                                           ifelse(sign(g2p_druggene_pearson$Pearson_Corr) == -1, "-", "0"))
 g2p_druggene_pearson_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"), Test_Results_PearCorr = c(ccle_pearson_ttest_res, ctrp_pearson_ttest_res, gdsc_pearson_ttest_res))
@@
   facet_wrap(~ Dataset) +
-  geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = Pearson_Corr, y = n), alpha = 0.5) +
+  geom_point(mapping = aes(label = Drug_Gene, color = InG2P, shape = Pearson_Corr_Sign, x = Pearson_Corr_Abs, y = n)) +
   scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
   scale_x_continuous(breaks = pretty_breaks()) +
-  geom_text(data = g2p_druggene_pearson_text, mapping = aes(x = -0.05, y = 110, label = Test_Results_PearCorr)) +
+  scale_shape_manual(values = c(45, 43, 42)) +
+  geom_text(data = g2p_druggene_pearson_text, mapping = aes(x = 0.3, y = 110, label = Test_Results_PearCorr)) +
   labs(x = "Pearson correlation coefficient between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +
@@
   facet_wrap(~ Dataset) +
-  geom_violin(mapping = aes(color = InG2P, y = Pearson_Corr, x = InG2P), alpha = 0.5) +
-  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_Corr, x = InG2P), alpha = 0.5, width = 0.25) +
+  geom_violin(mapping = aes(color = InG2P, y = Pearson_Corr_Abs, x = InG2P), alpha = 0.5) +
+  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_Corr_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
   coord_flip() +
@@
   facet_wrap(~ Dataset) +
-  geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = Pearson_Corr, y = n), alpha = 0.5) +
+  geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = Pearson_Corr_Abs, shape = Pearson_Corr_Sign, y = n), alpha = 0.5) +
   scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
   scale_x_continuous(breaks = pretty_breaks()) +
-  geom_text(data = g2p_druggene_pearson_text, mapping = aes(x = -0.05, y = 110, label = Test_Results_PearCorr)) +
+  scale_shape_manual(values = c(45, 43, 42)) +
+  geom_text(data = g2p_druggene_pearson_text, mapping = aes(x = 0.3, y = 110, label = Test_Results_PearCorr)) +
   labs(x = "Pearson correlation coefficient between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +

### 2018-11-13 manuscript.Rmd
updated rmd/html, saved updated rds w/ new grouping

@@
 library(ggpubr)
+library(ggrepel)
 library(ggsignif)
@@
   use_data_ccle_summ <- use_data_ccle %>% count(InG2P)
+  ccle_lin_p_ttest <- data.frame(statistic = NA,
+                                 parameter =  NA,
+                                 p.value = NA)
   if(nrow(use_data_ccle_summ) <= 1) {
@@
   use_data_ctrp_summ <- use_data_ctrp %>% count(InG2P)
+  ctrp_lin_p_ttest <- data.frame(statistic = NA,
+                                 parameter =  NA,
+                                 p.value = NA)
   if(nrow(use_data_ctrp_summ) <= 1) {
@@
   use_data_gdsc_summ <- use_data_gdsc %>% count(InG2P)
+  gdsc_lin_p_ttest <- data.frame(statistic = NA,
+                                 parameter =  NA,
+                                 p.value = NA)
   if(nrow(use_data_gdsc_summ) <= 1) {
@@
 
-  g2p_druggenelin_all_summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"), Test_Results_p = c(ccle_lin_p_ttest_res, ctrp_lin_p_ttest_res, gdsc_lin_p_ttest_res))
+  summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"),
+                          Test_Results_p = c(ccle_lin_p_ttest_res, ctrp_lin_p_ttest_res, gdsc_lin_p_ttest_res),
+                          t_statistic = c(round(ccle_lin_p_ttest$statistic, 3), round(ctrp_lin_p_ttest$statistic, 3), round(gdsc_lin_p_ttest$statistic, 3)),
+                          df = c(round(ccle_lin_p_ttest$parameter, 3), round(ctrp_lin_p_ttest$parameter, 3), round(gdsc_lin_p_ttest$parameter, 3)),
+                          p_value = c(round(ccle_lin_p_ttest$p.value, 3), round(ctrp_lin_p_ttest$p.value, 3), round(gdsc_lin_p_ttest$p.value, 3)),
+                          group_general_lineage_name = lineage_name)
 
@@
     geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = p, y = n), alpha = 0.5, position = position_jitter(width = 0, height = 0.15)) +
-    geom_text(data = g2p_druggenelin_all_summ_text, mapping = aes(x = 0.5, y = y_value, label = Test_Results_p), nudge_y = 0.1) +
+    scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+    geom_text(data = summ_text, mapping = aes(x = 0.5, y = y_value, label = Test_Results_p), nudge_y = 0.1) +
     labs(x = "Drug-gene association p-value between mutation groups", y = "Number of level A G2P associations") +
@@
     geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.75, width = 0.25) +
+    scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
     coord_flip() +
@@
   saveWidgetFix(widget = plot, file = paste0("./plots_18Q3/manuscript/plotlys_p_by_lineage/", lineage_name, "_g2p_evidence_p_plotly.html"))
+  return(summ_text)
 }
@@
   use_data_ccle_summ <- use_data_ccle %>% count(InG2P)
+  ccle_lin_ttest <- data.frame(statistic = NA,
+                                 parameter =  NA,
+                                 p.value = NA)
   if(nrow(use_data_ccle_summ) <= 1) {
@@
   use_data_ctrp_summ <- use_data_ctrp %>% count(InG2P)
+  ctrp_lin_ttest <- data.frame(statistic = NA,
+                                 parameter =  NA,
+                                 p.value = NA)
   if(nrow(use_data_ctrp_summ) <= 1) {
@@
   use_data_gdsc_summ <- use_data_gdsc %>% count(InG2P)
+  gdsc_lin_ttest <- data.frame(statistic = NA,
+                                 parameter =  NA,
+                                 p.value = NA)
   if(nrow(use_data_gdsc_summ) <= 1) {
@@
 
-  summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"), Test_Results = c(ccle_ttest_res, ctrp_ttest_res, gdsc_ttest_res))
+  summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"),
+                          Test_Results_p = c(ccle_ttest_res, ctrp_ttest_res, gdsc_ttest_res),
+                          t_statistic = c(round(ccle_lin_ttest$statistic, 3), round(ctrp_lin_ttest$statistic, 3), round(gdsc_lin_ttest$statistic, 3)),
+                          df = c(round(ccle_lin_ttest$parameter, 3), round(ctrp_lin_ttest$parameter, 3), round(gdsc_lin_ttest$parameter, 3)),
+                          p_value = c(round(ccle_lin_ttest$p.value, 3), round(ctrp_lin_ttest$p.value, 3), round(gdsc_lin_ttest$p.value, 3)),
+                          group_general_lineage_name = lineage)
 
@@
     scale_y_continuous(breaks = pretty_breaks()) +
-    geom_point(mapping = aes(label = Pearson_Pvalue, color = InG2P, shape = Pearson_Corr_Sign, x = Pearson_Corr_Abs, y = n), alpha = 0.5, position = position_jitter(width = 0, height = 0.15)) +
-    scale_shape_manual(values = c(45, 43, 42)) +
-    geom_text(data = summ_text, mapping = aes(x = 0.5, y = y_value, label = Test_Results), nudge_y = 1) +
+    geom_point(mapping = aes(label = Pearson_Pvalue, color = InG2P, fill = InG2P, shape = Pearson_Corr_Sign, x = Pearson_Corr_Abs, y = n), alpha = 0.5, position = position_jitter(width = 0, height = 0.15)) +
+    scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
+    scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+    scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+    geom_text(data = summ_text, mapping = aes(x = 0.5, y = y_value, label = Test_Results_p), nudge_y = 1) +
     labs(y = "Number of level A G2P associations") +
@@
     geom_boxplot(mapping = aes(color = InG2P, y = Pearson_Corr_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
+    scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
     coord_flip() +
@@
   saveWidgetFix(widget = plot, file = paste0("./plots_18Q3/manuscript/plotlys_pearson_by_lineage/", lineage, "_g2p_evidence_pearson_plotly.html"))
+  return(summ_text)
 }
@@
 ccle_signif_g2p_grid <- ccle_signif_g2p_grid[order(ccle_signif_g2p_grid$p),]
+ccle_signif_g2p_grid$Drug_Gene <- paste0(ccle_signif_g2p_grid$Drug, "_", ccle_signif_g2p_grid$Hugo_Symbol)
 saveRDS(ccle_signif_g2p_grid, "./data_munging/rds/ccle_signif_g2p_grid.rds")
@@
 knitr::kable(ccle_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-```{r}
+
 ccle_signif_g2p_grid <- readRDS("./data_munging/rds/ccle_signif_g2p_grid.rds")
 
-knitr::kable(ccle_signif_g2p_grid[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: By-drug Wilcoxon test results for point mutations in level A G2P genes (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(ccle_signif_g2p_grid[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 ```{r, eval=FALSE}
-ccle_signif_g2p_lineage <- lapply(unique(ccle_data_ptmuts$Drug), WilcoxonByDrug, dataset = ccle_data_ptmuts, data_name = "ccle", grouping_var = "lineage")
+ccle_signif_g2p_lineage <- lapply(unique(ccle_data_g2p_grid$Drug), WilcoxonByDrug, dataset = ccle_data_g2p_grid, data_name = "ccle", grouping_var = "lineage")
 names(ccle_signif_g2p_lineage) <- unique(ccle_signif_g2p_lineage$Drug)
+ccle_signif_g2p_lineage <- rbindlist(ccle_signif_g2p_lineage, use.names = TRUE)
+ccle_signif_g2p_lineage <- ccle_signif_g2p_lineage[order(ccle_signif_g2p_lineage$p),]
 saveRDS(ccle_signif_g2p_lineage, "./data_munging/rds/ccle_signif_g2p_lineage.rds")
@@
 ccle_signif_g2p_lineage <- readRDS("./data_munging/rds/ccle_signif_g2p_lineage.rds")
-ccle_signif_g2p_lineage <- rbindlist(ccle_signif_g2p_lineage, use.names = TRUE)
-ccle_signif_g2p_lineage <- ccle_signif_g2p_lineage[order(ccle_signif_g2p_lineage$p),]
 
@@
 
-ctrp_signif_g2p_ByDrug <- lapply(unique(ctrp_data_ptmuts$Drug), WilcoxonByDrug, dataset = ctrp_data_ptmuts, data_name = "CTRP", grouping_var = "gene")
-names(ctrp_signif_g2p_ByDrug) <- unique(ctrp_data_ptmuts$Drug)
-saveRDS(ctrp_signif_g2p_ByDrug, "./data_munging/rds/ctrp_signif_g2p_ByDrug.rds")
+# Grid comparisons of G2P drugs and genes
+ctrp_signif_g2p_grid <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "Drug"), data = ctrp_data_g2p_grid, method = "wilcox.test", p.adjust.method = "BH")
+ctrp_signif_g2p_grid <- adj_signif(ctrp_signif_g2p_grid)
+ctrp_signif_g2p_grid <- ctrp_signif_g2p_grid[order(ctrp_signif_g2p_grid$p),]
+ctrp_signif_g2p_grid$Drug_Gene <- paste0(ctrp_signif_g2p_grid$Drug, "_", ctrp_signif_g2p_grid$Hugo_Symbol)
+saveRDS(ctrp_signif_g2p_grid, "./data_munging/rds/ctrp_signif_g2p_grid.rds")
 ```
@@
 knitr::kable(ctrp_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-```{r}
-ctrp_signif_g2p_ByDrug <- readRDS("./data_munging/rds/ctrp_signif_g2p_ByDrug.rds")
-ctrp_signif_g2p_ByDrug_all <- rbindlist(ctrp_signif_g2p_ByDrug, use.names = TRUE)
-ctrp_signif_g2p_ByDrug_all <- ctrp_signif_g2p_ByDrug_all[order(ctrp_signif_g2p_ByDrug_all$p),]
-
-knitr::kable(ctrp_signif_g2p_ByDrug_all[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: By-drug Wilcoxon test results for point mutations in level A G2P genes (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+
+ctrp_signif_g2p_grid <- readRDS("./data_munging/rds/ctrp_signif_g2p_grid.rds")
+
+knitr::kable(ctrp_signif_g2p_grid[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 ```{r, eval=FALSE}
-ctrp_signif_g2p_lineage <- lapply(unique(ctrp_data_ptmuts$Drug), WilcoxonByDrug, dataset = ctrp_data_ptmuts, data_name = "ctrp", grouping_var = "lineage")
+ctrp_signif_g2p_lineage <- lapply(unique(ctrp_data_g2p_grid$Drug), WilcoxonByDrug, dataset = ctrp_data_g2p_grid, data_name = "ctrp", grouping_var = "lineage")
 names(ctrp_signif_g2p_lineage) <- unique(ctrp_signif_g2p_lineage$Drug)
+ctrp_signif_g2p_lineage <- rbindlist(ctrp_signif_g2p_lineage, use.names = TRUE)
+ctrp_signif_g2p_lineage <- ctrp_signif_g2p_lineage[order(ctrp_signif_g2p_lineage$p),]
 saveRDS(ctrp_signif_g2p_lineage, "./data_munging/rds/ctrp_signif_g2p_lineage.rds")
@@
 ctrp_signif_g2p_lineage <- readRDS("./data_munging/rds/ctrp_signif_g2p_lineage.rds")
-ctrp_signif_g2p_lineage <- rbindlist(ctrp_signif_g2p_lineage, use.names = TRUE)
-ctrp_signif_g2p_lineage <- ctrp_signif_g2p_lineage[order(ctrp_signif_g2p_lineage$p),]
 
@@
 
-gdsc_signif_g2p_ByDrug <- lapply(unique(gdsc_data_ptmuts$Drug), WilcoxonByDrug, dataset = gdsc_data_ptmuts, data_name = "gdsc", grouping_var = "gene")
-names(gdsc_signif_g2p_ByDrug) <- unique(gdsc_data_ptmuts$Drug)
-saveRDS(gdsc_signif_g2p_ByDrug, "./data_munging/rds/gdsc_signif_g2p_ByDrug.rds")
+# Grid comparisons of G2P drugs and genes
+gdsc_signif_g2p_grid <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "Drug"), data = gdsc_data_g2p_grid, method = "wilcox.test", p.adjust.method = "BH")
+gdsc_signif_g2p_grid <- adj_signif(gdsc_signif_g2p_grid)
+gdsc_signif_g2p_grid <- gdsc_signif_g2p_grid[order(gdsc_signif_g2p_grid$p),]
+gdsc_signif_g2p_grid$Drug_Gene <- paste0(gdsc_signif_g2p_grid$Drug, "_", gdsc_signif_g2p_grid$Hugo_Symbol)
+saveRDS(gdsc_signif_g2p_grid, "./data_munging/rds/gdsc_signif_g2p_grid.rds")
 ```
@@
 knitr::kable(gdsc_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-```{r}
-gdsc_signif_g2p_ByDrug <- readRDS("./data_munging/rds/gdsc_signif_g2p_ByDrug.rds")
-gdsc_signif_g2p_ByDrug_all <- rbindlist(gdsc_signif_g2p_ByDrug, use.names = TRUE)
-gdsc_signif_g2p_ByDrug_all <- gdsc_signif_g2p_ByDrug_all[order(gdsc_signif_g2p_ByDrug_all$p),]
-
-knitr::kable(gdsc_signif_g2p_ByDrug_all[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: by-drug Wilcoxon test results for point mutations in level A G2P genes (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+
+gdsc_signif_g2p_grid <- readRDS("./data_munging/rds/gdsc_signif_g2p_grid.rds")
+
+knitr::kable(gdsc_signif_g2p_grid[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 ```{r, eval=FALSE}
-gdsc_signif_g2p_lineage <- lapply(unique(gdsc_data_ptmuts$Drug), WilcoxonByDrug, dataset = gdsc_data_ptmuts, data_name = "gdsc", grouping_var = "lineage")
+gdsc_signif_g2p_lineage <- lapply(unique(gdsc_data_g2p_grid$Drug), WilcoxonByDrug, dataset = gdsc_data_g2p_grid, data_name = "gdsc", grouping_var = "lineage")
 names(gdsc_signif_g2p_lineage) <- unique(gdsc_signif_g2p_lineage$Drug)
+gdsc_signif_g2p_lineage <- rbindlist(gdsc_signif_g2p_lineage, use.names = TRUE)
+gdsc_signif_g2p_lineage <- gdsc_signif_g2p_lineage[order(gdsc_signif_g2p_lineage$p),]
 saveRDS(gdsc_signif_g2p_lineage, "./data_munging/rds/gdsc_signif_g2p_lineage.rds")
@@
 gdsc_signif_g2p_lineage <- readRDS("./data_munging/rds/gdsc_signif_g2p_lineage.rds")
-gdsc_signif_g2p_lineage <- rbindlist(gdsc_signif_g2p_lineage, use.names = TRUE)
-gdsc_signif_g2p_lineage <- gdsc_signif_g2p_lineage[order(gdsc_signif_g2p_lineage$p),]
 
@@
 ```{r}
-g2p_druggene_p_tally <- g2p %>% group_by(Drug_Gene) %>% tally()
+g2p_druggene_p_tally <- g2p %>% group_by(Drug_Gene) %>% tally() %>% drop_na()
 ```
@@
 ```{r}
-ccle_druggene_mad_summ <- ccle_data_ptmuts %>% group_by(Drug_Gene, Mutation_Status_Nonsilent) %>% summarize(Mean_AUC = mean(AUC))
-ccle_druggene_mad_summ <- dcast(ccle_druggene_mad_summ, Drug_Gene ~ Mutation_Status_Nonsilent)
-ccle_druggene_mad_summ$MAD <- abs(ccle_druggene_mad_summ$Mutant - ccle_druggene_mad_summ$Other)
-ccle_druggene_p_summ <- ccle_signif_g2p_lineage
-ccle_druggene_p_summ$Drug_Gene <- paste0(ccle_druggene_p_summ$Drug, "_", ccle_druggene_p_summ$Hugo_Symbol)
-ccle_druggene_summ <- merge(merge(g2p_druggene_p_tally, ccle_druggene_p_summ[, c("Drug_Gene", "p")], by = "Drug_Gene", all.y = TRUE), ccle_druggene_mad_summ, by = "Drug_Gene", all = TRUE)
+ccle_druggene_summ <- merge(g2p_druggene_p_tally, ccle_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
 ccle_druggene_summ$n <- ifelse(is.na(ccle_druggene_summ$n), 0, ccle_druggene_summ$n)
@@
 ccle_p_ttest_res <- paste0("t = ", round(ccle_p_ttest$statistic, 3), ", df = ", round(ccle_p_ttest$parameter, 3), ", p = ", round(ccle_p_ttest$p.value, 3))
-ccle_mad_ttest <- t.test(ccle_druggene_summ$MAD ~ ccle_druggene_summ$InG2P)
-ccle_mad_ttest_res <- paste0("t = ", round(ccle_mad_ttest$statistic, 3), ", df = ", round(ccle_mad_ttest$parameter, 3), ", p = ", round(ccle_mad_ttest$p.value, 3))
-
-ctrp_druggene_mad_summ <- ctrp_data_ptmuts %>% group_by(Drug_Gene, Mutation_Status_Nonsilent) %>% summarize(Mean_AUC = mean(AUC))
-ctrp_druggene_mad_summ <- dcast(ctrp_druggene_mad_summ, Drug_Gene ~ Mutation_Status_Nonsilent)
-ctrp_druggene_mad_summ$MAD <- abs(ctrp_druggene_mad_summ$Mutant - ctrp_druggene_mad_summ$Other)
-ctrp_druggene_p_summ <- ctrp_signif_g2p_lineage
-ctrp_druggene_p_summ$Drug_Gene <- paste0(ctrp_druggene_p_summ$Drug, "_", ctrp_druggene_p_summ$Hugo_Symbol)
-ctrp_druggene_summ <- merge(merge(g2p_druggene_p_tally, ctrp_druggene_p_summ[, c("Drug_Gene", "p")], by = "Drug_Gene", all.y = TRUE), ctrp_druggene_mad_summ, by = "Drug_Gene", all = TRUE)
+
+ctrp_druggene_summ <- merge(g2p_druggene_p_tally, ctrp_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
 ctrp_druggene_summ$n <- ifelse(is.na(ctrp_druggene_summ$n), 0, ctrp_druggene_summ$n)
@@
 ctrp_p_ttest_res <- paste0("t = ", round(ctrp_p_ttest$statistic, 3), ", df = ", round(ctrp_p_ttest$parameter, 3), ", p = ", round(ctrp_p_ttest$p.value, 3))
-ctrp_mad_ttest <- t.test(ctrp_druggene_summ$MAD ~ ctrp_druggene_summ$InG2P)
-ctrp_mad_ttest_res <- paste0("t = ", round(ctrp_mad_ttest$statistic, 3), ", df = ", round(ctrp_mad_ttest$parameter, 3), ", p = ", round(ctrp_mad_ttest$p.value, 3))
-
-gdsc_druggene_mad_summ <- gdsc_data_ptmuts %>% group_by(Drug_Gene, Mutation_Status_Nonsilent) %>% summarize(Mean_AUC = mean(AUC))
-gdsc_druggene_mad_summ <- dcast(gdsc_druggene_mad_summ, Drug_Gene ~ Mutation_Status_Nonsilent)
-gdsc_druggene_mad_summ$MAD <- abs(gdsc_druggene_mad_summ$Mutant - gdsc_druggene_mad_summ$Other)
-gdsc_druggene_p_summ <- gdsc_signif_g2p_lineage
-gdsc_druggene_p_summ$Drug_Gene <- paste0(gdsc_druggene_p_summ$Drug, "_", gdsc_druggene_p_summ$Hugo_Symbol)
-gdsc_druggene_summ <- merge(merge(g2p_druggene_p_tally, gdsc_druggene_p_summ[, c("Drug_Gene", "p")], by = "Drug_Gene", all.y = TRUE), gdsc_druggene_mad_summ, by = "Drug_Gene", all = TRUE)
+
+gdsc_druggene_summ <- merge(g2p_druggene_p_tally, gdsc_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
 gdsc_druggene_summ$n <- ifelse(is.na(gdsc_druggene_summ$n), 0, gdsc_druggene_summ$n)
@@
 gdsc_p_ttest_res <- paste0("t = ", round(gdsc_p_ttest$statistic, 3), ", df = ", round(gdsc_p_ttest$parameter, 3), ", p = ", round(gdsc_p_ttest$p.value, 3))
-gdsc_mad_ttest <- t.test(gdsc_druggene_summ$MAD ~ gdsc_druggene_summ$InG2P)
-gdsc_mad_ttest_res <- paste0("t = ", round(gdsc_mad_ttest$statistic, 3), ", df = ", round(gdsc_mad_ttest$parameter, 3), ", p = ", round(gdsc_mad_ttest$p.value, 3))
 
 g2p_druggene_all_summ <- rbind(ccle_druggene_summ, ctrp_druggene_summ, gdsc_druggene_summ)
-g2p_druggene_all_summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"), 
-                                         Test_Results_p = c(ccle_p_ttest_res, ctrp_p_ttest_res, gdsc_p_ttest_res),
-                                         Test_Results_MAD = c(ccle_mad_ttest_res, ctrp_mad_ttest_res, gdsc_mad_ttest_res))
+g2p_druggene_all_summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"), Test_Results_p = c(ccle_p_ttest_res, ctrp_p_ttest_res, gdsc_p_ttest_res))
+g2p_druggene_all_summ$Drug_Gene_Ordered <- factor(g2p_druggene_all_summ$Drug_Gene, levels = as.character(unique(g2p_druggene_all_summ$Drug_Gene)), labels = sapply(strsplit(x = as.character(unique(g2p_druggene_all_summ$Drug_Gene)), split = "_"), function(x) paste0(x[1], "\n", x[2])))
 ```
@@
 ```{r fig.height=5, fig.width=12}
-## MAD
-plot_mad_point <- ggplot(data = g2p_druggene_all_summ) +
+plot_p_point <- ggplot(data = g2p_druggene_all_summ, aes(x = p, y = n, label = Drug_Gene)) +
   facet_wrap(~ Dataset, scales = "free_x") +
-  geom_point(mapping = aes(color = InG2P, x = MAD, y = n), alpha = 0.5) +
+  geom_point(mapping = aes(color = InG2P), alpha = 0.5) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
   scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
-  geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = c(0.75, 4, 0.19), y = 110, label = Test_Results_MAD)) +
-  labs(x = "Gene-drug association difference in mean AUC between mutation groups", y = "Number of level A G2P associations", color = "Does the drug-gene combination have level A G2P indication?") +
-  theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
-
-plot_mad_box <- ggplot(data = g2p_druggene_all_summ) +
-  facet_wrap(~ Dataset, scales = "free_x") +
-  geom_violin(mapping = aes(color = InG2P, y = MAD, x = InG2P), alpha = 0.5) +
-  geom_boxplot(mapping = aes(color = InG2P, y = MAD, x = InG2P), alpha = 0.75, width = 0.5) +
-  coord_flip() +
-  labs(x = "Level A G2P\nassociation") +
-  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
-plot_mad_point <- ggplot_gtable(ggplot_build(plot_mad_point))
-plot_mad_box <- ggplot_gtable(ggplot_build(plot_mad_box))
-mad_maxWidth <-  grid::unit.pmax(plot_mad_point$widths, plot_mad_box$widths)
-plot_mad_point$widths <- as.list(mad_maxWidth)
-plot_mad_box$widths <- as.list(mad_maxWidth)
-
-g2p_druggene_all_mad_summ_plot <- cowplot::plot_grid(plot_mad_box,
-                   plot_mad_point,
-                   nrow = 2,
-                   rel_heights = c(1.5, 4))
-g2p_druggene_all_mad_summ_plot
-# ggsave("./plots_18Q3/manuscript/g2p_druggene_all_mad_summ_plot.png", g2p_druggene_all_mad_summ_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
-
-## P-value
-plot_p_point <- ggplot(data = g2p_druggene_all_summ) +
-  facet_wrap(~ Dataset, scales = "free_x") +
-  geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = p, y = n), alpha = 0.5) +
-  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
+  geom_text_repel(data = subset(g2p_druggene_all_summ, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
   geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = 0.5, y = 110, label = Test_Results_p)) +
@@
   geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.75, width = 0.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
   coord_flip() +
@@
   geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = p, y = n), alpha = 0.5) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
   scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
@@
 ```{r}
-ccle_druggenelin_p_summ <- ccle_signif_g2p_lineage
-ccle_druggenelin_p_summ$Drug_Gene <- paste0(ccle_druggenelin_p_summ$Drug, "_", ccle_druggenelin_p_summ$Hugo_Symbol)
-ccle_druggenelin_summ <- merge(g2p_druggenelin_p_tally, ccle_druggenelin_p_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
+ccle_druggenelin_summ <- ccle_signif_g2p_lineage
+ccle_druggenelin_summ$Drug_Gene <- paste0(ccle_druggenelin_summ$Drug, "_", ccle_druggenelin_summ$Hugo_Symbol)
+ccle_druggenelin_summ <- merge(g2p_druggenelin_p_tally, ccle_druggenelin_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
 ccle_druggenelin_summ$n <- ifelse(is.na(ccle_druggenelin_summ$n), 0, ccle_druggenelin_summ$n)
@@
 
-ctrp_druggenelin_p_summ <- ctrp_signif_g2p_lineage
-ctrp_druggenelin_p_summ$Drug_Gene <- paste0(ctrp_druggenelin_p_summ$Drug, "_", ctrp_druggenelin_p_summ$Hugo_Symbol)
-ctrp_druggenelin_summ <- merge(g2p_druggenelin_p_tally, ctrp_druggenelin_p_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
+ctrp_druggenelin_summ <- ctrp_signif_g2p_lineage
+ctrp_druggenelin_summ$Drug_Gene <- paste0(ctrp_druggenelin_summ$Drug, "_", ctrp_druggenelin_summ$Hugo_Symbol)
+ctrp_druggenelin_summ <- merge(g2p_druggenelin_p_tally, ctrp_druggenelin_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
 ctrp_druggenelin_summ$n <- ifelse(is.na(ctrp_druggenelin_summ$n), 0, ctrp_druggenelin_summ$n)
@@
 
-gdsc_druggenelin_p_summ <- gdsc_signif_g2p_lineage
-gdsc_druggenelin_p_summ$Drug_Gene <- paste0(gdsc_druggenelin_p_summ$Drug, "_", gdsc_druggenelin_p_summ$Hugo_Symbol)
-gdsc_druggenelin_summ <- merge(g2p_druggenelin_p_tally, gdsc_druggenelin_p_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
+gdsc_druggenelin_summ <- gdsc_signif_g2p_lineage
+gdsc_druggenelin_summ$Drug_Gene <- paste0(gdsc_druggenelin_summ$Drug, "_", gdsc_druggenelin_summ$Hugo_Symbol)
+gdsc_druggenelin_summ <- merge(g2p_druggenelin_p_tally, gdsc_druggenelin_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
 gdsc_druggenelin_summ$n <- ifelse(is.na(gdsc_druggenelin_summ$n), 0, gdsc_druggenelin_summ$n)
@@
 g2p_druggenelin_all_summ <- rbind(ccle_druggenelin_summ, ctrp_druggenelin_summ, gdsc_druggenelin_summ)
-g2p_druggenelin_all_summ$InG2P <- factor(g2p_druggenelin_all_summ$InG2P)
+g2p_druggenelin_all_summ$InG2P <- factor(g2p_druggenelin_all_summ$InG2P, levels = c("Yes", "No"))
 
@@
 ```{r, eval=FALSE, results = 'hide'}
-lapply(as.character(unique(g2p_druggenelin_all_summ$group_general_lineage_name)), MutPlotlyByLineage)
-
+g2p_druggenelin_p_ttest_res <- lapply(as.character(unique(g2p_druggenelin_all_summ$group_general_lineage_name)), MutPlotlyByLineage)
+g2p_druggenelin_p_ttest_res_list <- rbindlist(g2p_druggenelin_p_ttest_res, use.names = TRUE)
+g2p_druggenelin_p_ttest_res_list <- g2p_druggenelin_p_ttest_res_list[order(g2p_druggenelin_p_ttest_res_list$p_value),]
+saveRDS(g2p_druggenelin_p_ttest_res_list, "./data_munging/rds/g2p_druggenelin_p_ttest_res.rds")
 # test <- filter(g2p_druggenelin_all_summ, Dataset == "CCLE")
-# test_summ <- test %>% count(group_general_lineage_name, InG2P)
+# test <- filter(g2p_druggenelin_all_summ, group_general_lineage_name == "biliary tract cancer")
+# test_summ <- test %>% count(InG2P)
 # test2 <- filter(g2p_druggenelin_all_summ, Dataset == "CTRP")
@@
 # test3_summ <- test3 %>% count(group_general_lineage_name, InG2P)
+```
+
+```{r}
+g2p_druggenelin_p_ttest_res_list <- readRDS("./data_munging/rds/g2p_druggenelin_p_ttest_res.rds")
+
+knitr::kable(g2p_druggenelin_p_ttest_res_list, caption = "GDSC: T-test results for level A G2P drug-gene associations across lineages") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
-```{r fig.height=5, fig.width=12}
-plot_pearson_point <- ggplot(data = g2p_druggene_pearson) +
+```{r fig.height=5.5, fig.width=12}
+plot_pearson_point <- ggplot(data = g2p_druggene_pearson, aes(x = Pearson_Corr_Abs, y = n, label = Drug_Gene)) +
   facet_wrap(~ Dataset) +
-  geom_point(mapping = aes(label = Drug_Gene, color = InG2P, shape = Pearson_Corr_Sign, x = Pearson_Corr_Abs, y = n)) +
+  geom_point(mapping = aes(fill = InG2P, color = InG2P, shape = Pearson_Corr_Sign), alpha = 0.5, size = 1.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
   scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
   scale_x_continuous(breaks = pretty_breaks()) +
-  scale_shape_manual(values = c(45, 43, 42)) +
+  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
+  geom_text_repel(data = subset(g2p_druggene_pearson, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
   geom_text(data = g2p_druggene_pearson_text, mapping = aes(x = 0.3, y = 110, label = Test_Results_PearCorr)) +
   labs(x = "Pearson correlation coefficient between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +
-  theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
+  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
+  guides(color = FALSE, fill = FALSE) +
+  labs(shape = "Direction of correlation:")
 
@@
   geom_boxplot(mapping = aes(color = InG2P, y = Pearson_Corr_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
   coord_flip() +
@@
 g2p_druggene_pearson_plot
-# ggsave("./plots_18Q3/manuscript/g2p_druggene_pearson_plot.png", g2p_druggene_pearson_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
+# ggsave("./plots_18Q3/manuscript/g2p_druggene_pearson_plot.png", g2p_druggene_pearson_plot, device = "png", dpi = 450, width = 12, height = 5.5, units = "in")
 ```
@@
   facet_wrap(~ Dataset) +
-  geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = Pearson_Corr_Abs, shape = Pearson_Corr_Sign, y = n), alpha = 0.5) +
+  geom_point(mapping = aes(label = Drug_Gene, fill = InG2P, color = InG2P, shape = Pearson_Corr_Sign, x = Pearson_Corr_Abs, y = n), alpha = 0.5, size = 1.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
   scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
   scale_x_continuous(breaks = pretty_breaks()) +
-  scale_shape_manual(values = c(45, 43, 42)) +
+  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
   geom_text(data = g2p_druggene_pearson_text, mapping = aes(x = 0.3, y = 110, label = Test_Results_PearCorr)) +
   labs(x = "Pearson correlation coefficient between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +
-  theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
+  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
+  guides(color = FALSE, fill = FALSE) +
+  labs(shape = NULL)
 
@@
 ```{r, eval=FALSE}
-ccle_lineages4pearson <- as.character(unique(ccle_data_ptmuts$group_general_lineage_name))[!is.na(as.character(unique(ccle_data_ptmuts$group_general_lineage_name)))]
-ccle_signif_pearson <- lapply(ccle_lineages4pearson, PearsonByLineage, dataset = ccle_data_ptmuts)
+ccle_lineages4pearson <- as.character(unique(ccle_data_g2p_grid$group_general_lineage_name))[!is.na(as.character(unique(ccle_data_g2p_grid$group_general_lineage_name)))]
+ccle_signif_pearson <- lapply(ccle_lineages4pearson, PearsonByLineage, dataset = ccle_data_g2p_grid)
 ccle_signif_pearson_all_lin <- rbindlist(ccle_signif_pearson, use.names = TRUE)
@@
 
-ctrp_lineages4pearson <- as.character(unique(ctrp_data_ptmuts$group_general_lineage_name))[!is.na(as.character(unique(ctrp_data_ptmuts$group_general_lineage_name)))]
-ctrp_signif_pearson <- lapply(ctrp_lineages4pearson, PearsonByLineage, dataset = ctrp_data_ptmuts)
+ctrp_lineages4pearson <- as.character(unique(ctrp_data_g2p_grid$group_general_lineage_name))[!is.na(as.character(unique(ctrp_data_g2p_grid$group_general_lineage_name)))]
+ctrp_signif_pearson <- lapply(ctrp_lineages4pearson, PearsonByLineage, dataset = ctrp_data_g2p_grid)
 ctrp_signif_pearson_all_lin <- rbindlist(ctrp_signif_pearson, use.names = TRUE)
@@
 
-gdsc_lineages4pearson <- as.character(unique(gdsc_data_ptmuts$group_general_lineage_name))[!is.na(as.character(unique(gdsc_data_ptmuts$group_general_lineage_name)))]
-gdsc_signif_pearson <- lapply(gdsc_lineages4pearson, PearsonByLineage, dataset = gdsc_data_ptmuts)
+gdsc_lineages4pearson <- as.character(unique(gdsc_data_g2p_grid$group_general_lineage_name))[!is.na(as.character(unique(gdsc_data_g2p_grid$group_general_lineage_name)))]
+gdsc_signif_pearson <- lapply(gdsc_lineages4pearson, PearsonByLineage, dataset = gdsc_data_g2p_grid)
 gdsc_signif_pearson_all_lin <- rbindlist(gdsc_signif_pearson, use.names = TRUE)
@@
 ```{r, results='hide', eval=FALSE}
-lapply(as.character(unique(signif_pearson_all_lin$group_general_lineage_name)), GexpPlotlyByLineage)
+g2p_druggenelin_pearson_ttest_res <- lapply(as.character(unique(signif_pearson_all_lin$group_general_lineage_name)), GexpPlotlyByLineage)
+g2p_druggenelin_pearson_ttest_res_list <- rbindlist(g2p_druggenelin_pearson_ttest_res, use.names = TRUE)
+g2p_druggenelin_pearson_ttest_res_list <- g2p_druggenelin_pearson_ttest_res_list[order(g2p_druggenelin_pearson_ttest_res_list$p_value),]
+saveRDS(g2p_druggenelin_pearson_ttest_res_list, "./data_munging/rds/g2p_druggenelin_pearson_ttest_res_list.rds")
+```
+
+```{r}
+g2p_druggenelin_pearson_ttest_res_list <- readRDS("./data_munging/rds/g2p_druggenelin_pearson_ttest_res_list.rds")
+
+knitr::kable(g2p_druggenelin_pearson_ttest_res_list, caption = "GDSC: T-test results for level A G2P drug-gene/gene expression associations across lineages") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```

### 2018-11-14 manuscript.Rmd

@@
 ```{r}
-PearsonByLineage <- function(lin, dataset) {
+PearsonByLineage <- function(lin, dataset, variable) {
   use_data <- filter(dataset, group_general_lineage_name == lin)
+  if(variable == "GE") {
     use_data <- filter(use_data, !is.na(RPKM))
@@
     if(nrow(use_data_filt) > 0) {
-    pearson_res <- use_data_filt %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate, Pearson_Pval = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value)
+      pearson_res <- use_data_filt %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate, Pearson_Pval_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value)
       pearson_res <- merge(g2p_druggene_p_tally, pearson_res, all.y = TRUE)
       pearson_res$group_general_lineage_name <- lin
-    pearson_res$Pearson_Corr_Abs <- abs(pearson_res$Pearson_Corr)
-    pearson_res$Pearson_Corr_Sign <- ifelse(sign(pearson_res$Pearson_Corr) == 1, "+",
-                                            ifelse(sign(pearson_res$Pearson_Corr) == -1, "-", "0"))
+      pearson_res$Pearson_GE_Abs <- abs(pearson_res$Pearson_Corr_GE)
+      pearson_res$Pearson_GE_Sign <- ifelse(sign(pearson_res$Pearson_Corr_GE) == 1, "+",
+                                              ifelse(sign(pearson_res$Pearson_Corr_GE) == -1, "-", "0"))
       return(pearson_res)
+    }
+  }
+  else if(variable == "CN") {
+    use_data <- filter(use_data, !is.na(Copy_Number))
+    use_data_summ <- use_data %>% count(Drug_Gene)
+    use_data_summ <- filter(use_data_summ, n >= 3) # cor.test requires at least 3 non-NA data points
+    use_data_filt <- filter(use_data, Drug_Gene %in% as.character(unique(use_data_summ$Drug_Gene)))
+    if(nrow(use_data_filt) > 0) {
+      pearson_res <- use_data_filt %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr_CN = cor.test(y = AUC, x = Copy_Number, method = "pearson", use = "complete.obs")$estimate, Pearson_Pval_CN = cor.test(y = AUC, x = Copy_Number, method = "pearson", use = "complete.obs")$p.value)
+      pearson_res <- merge(g2p_druggene_p_tally, pearson_res, all.y = TRUE)
+      pearson_res$group_general_lineage_name <- lin
+      pearson_res$Pearson_CN_Abs <- abs(pearson_res$Pearson_Corr_CN)
+      pearson_res$Pearson_CN_Sign <- ifelse(sign(pearson_res$Pearson_Corr_CN) == 1, "+",
+                                              ifelse(sign(pearson_res$Pearson_Corr_CN) == -1, "-", "0"))
+      return(pearson_res)
+    }
   }
@@
 
-## Make G2P lineage gene expression plotly
-```{r}
-GexpPlotlyByLineage <- function(lineage) {
-  use_data <- filter(signif_pearson_all_lin, group_general_lineage_name == lineage)
+## Make G2P lineage Pearson plotlys
+```{r}
+PearsonPlotlyByLineage <- function(lineage) {
+  print(paste0("Lineage: ", toupper(lineage)))
+  use_data <- filter(signif_all_lin, group_general_lineage_name == lineage)
   use_data$Dataset <- factor(use_data$Dataset, levels = c("CCLE", "CTRP", "GDSC"))
-  use_data$Pearson_Pvalue <- paste0(round(use_data$Pearson_Pval, 3), "\nDrug_Gene: ", use_data$Drug_Gene)
+  use_data$Pearson_GE_Label <- paste0(round(use_data$Pearson_Pval_GE, 3), "\nDrug_Gene: ", use_data$Drug_Gene)
+  use_data$Pearson_CN_Label <- paste0(round(use_data$Pearson_Pval_CN, 3), "\nDrug_Gene: ", use_data$Drug_Gene)
+  ticker_ge <- 0
+  ticker_cn <- 0
   ticker <- 0
@@
   use_data_ccle <- filter(use_data, Dataset == "CCLE")
-  use_data_ccle_summ <- use_data_ccle %>% count(InG2P)
-  ccle_lin_ttest <- data.frame(statistic = NA,
-                                 parameter =  NA,
-                                 p.value = NA)
-  if(nrow(use_data_ccle_summ) <= 1) {
-    ccle_ttest_res <-  NA
-    ticker <- ticker + 1
-    }
-  else if(use_data_ccle_summ[use_data_ccle_summ$InG2P == "Yes",]$nn < 2) { ccle_ttest_res <-  NA }
-  else if(use_data_ccle_summ[use_data_ccle_summ$InG2P == "Yes",]$nn >= 2) {
-    ccle_lin_ttest <- t.test(use_data_ccle$Pearson_Corr_Abs ~ use_data_ccle$InG2P)
-    ccle_ttest_res <- paste0("t = ", round(ccle_lin_ttest$statistic, 3), ", df = ", round(ccle_lin_ttest$parameter, 3), ", p = ", round(ccle_lin_ttest$p.value, 3))
-  }
+  use_data_ccle_ge_summ <- use_data_ccle[!is.na(use_data_ccle$Pearson_GE_Abs),] %>% count(InG2P)
+  use_data_ccle_cn_summ <- use_data_ccle[!is.na(use_data_ccle$Pearson_CN_Abs),] %>% count(InG2P)
+  ccle_ge_ttest <- data.frame(statistic = NA, parameter = NA, p.value = NA)
+  ccle_cn_ttest <- data.frame(statistic = NA, parameter = NA, p.value = NA)
+  if(nrow(use_data_ccle_ge_summ) <= 1) {
+    ccle_ge_res <-  NA
+    ticker_ge <- ticker_ge + 1
+  }
+  else if(use_data_ccle_ge_summ[use_data_ccle_ge_summ$InG2P == "Yes",]$nn < 2) {
+    ccle_ge_res <-  NA
+  }
+  else if(use_data_ccle_ge_summ[use_data_ccle_ge_summ$InG2P == "Yes",]$nn >= 2) {
+    ccle_ge_ttest <- t.test(use_data_ccle$Pearson_GE_Abs ~ use_data_ccle$InG2P)
+    ccle_ge_res <- paste0("t = ", round(ccle_ge_ttest$statistic, 3), ", df = ", round(ccle_ge_ttest$parameter, 3), ", p = ", round(ccle_ge_ttest$p.value, 3))
+  }
+  if(nrow(use_data_ccle_cn_summ) <= 1) {
+    ccle_cn_res <-  NA
+    ticker_cn <- ticker_cn + 1
+  }
+  else if(use_data_ccle_cn_summ[use_data_ccle_cn_summ$InG2P == "Yes",]$nn < 2) {
+    ccle_cn_res <-  NA
+  }
+  else if(use_data_ccle_cn_summ[use_data_ccle_cn_summ$InG2P == "Yes",]$nn >= 2) {
+    ccle_cn_ttest <- t.test(use_data_ccle$Pearson_CN_Abs ~ use_data_ccle$InG2P)
+    ccle_cn_res <- paste0("t = ", round(ccle_cn_ttest$statistic, 3), ", df = ", round(ccle_cn_ttest$parameter, 3), ", p = ", round(ccle_cn_ttest$p.value, 3))
+  }
+  print("CCLE testing: DONE")
 
   use_data_ctrp <- filter(use_data, Dataset == "CTRP")
-  use_data_ctrp_summ <- use_data_ctrp %>% count(InG2P)
-  ctrp_lin_ttest <- data.frame(statistic = NA,
-                                 parameter =  NA,
-                                 p.value = NA)
-  if(nrow(use_data_ctrp_summ) <= 1) {
-    ctrp_ttest_res <-  NA
-    ticker <- ticker + 1
-    }
-  else if(use_data_ctrp_summ[use_data_ctrp_summ$InG2P == "Yes",]$nn < 2) { ctrp_ttest_res <-  NA }
-  else if(use_data_ctrp_summ[use_data_ctrp_summ$InG2P == "Yes",]$nn >= 2) {
-    ctrp_lin_ttest <- t.test(use_data_ctrp$Pearson_Corr_Abs ~ use_data_ctrp$InG2P)
-    ctrp_ttest_res <- paste0("t = ", round(ctrp_lin_ttest$statistic, 3), ", df = ", round(ctrp_lin_ttest$parameter, 3), ", p = ", round(ctrp_lin_ttest$p.value, 3))
-  }
+  use_data_ctrp_ge_summ <- use_data_ctrp[!is.na(use_data_ctrp$Pearson_GE_Abs),] %>% count(InG2P)
+  use_data_ctrp_cn_summ <- use_data_ctrp[!is.na(use_data_ctrp$Pearson_CN_Abs),] %>% count(InG2P)
+  ctrp_ge_ttest <- data.frame(statistic = NA, parameter = NA, p.value = NA)
+  ctrp_cn_ttest <- data.frame(statistic = NA, parameter = NA, p.value = NA)
+  if(nrow(use_data_ctrp_ge_summ) <= 1) {
+    ctrp_ge_res <-  NA
+    ticker_ge <- ticker_ge + 1
+  }
+  else if(use_data_ctrp_ge_summ[use_data_ctrp_ge_summ$InG2P == "Yes",]$nn < 2) {
+    ctrp_ge_res <-  NA
+  }
+  else if(use_data_ctrp_ge_summ[use_data_ctrp_ge_summ$InG2P == "Yes",]$nn >= 2) {
+    ctrp_ge_ttest <- t.test(use_data_ctrp$Pearson_GE_Abs ~ use_data_ctrp$InG2P)
+    ctrp_ge_res <- paste0("t = ", round(ctrp_ge_ttest$statistic, 3), ", df = ", round(ctrp_ge_ttest$parameter, 3), ", p = ", round(ctrp_ge_ttest$p.value, 3))
+  }
+  if(nrow(use_data_ctrp_cn_summ) <= 1) {
+    ctrp_cn_res <-  NA
+    ticker_cn <- ticker_cn + 1
+  }
+  else if(use_data_ctrp_cn_summ[use_data_ctrp_cn_summ$InG2P == "Yes",]$nn < 2) {
+    ctrp_cn_res <-  NA
+  }
+  else if(use_data_ctrp_cn_summ[use_data_ctrp_cn_summ$InG2P == "Yes",]$nn >= 2) {
+    ctrp_cn_ttest <- t.test(use_data_ctrp$Pearson_CN_Abs ~ use_data_ctrp$InG2P)
+    ctrp_cn_res <- paste0("t = ", round(ctrp_cn_ttest$statistic, 3), ", df = ", round(ctrp_cn_ttest$parameter, 3), ", p = ", round(ctrp_cn_ttest$p.value, 3))
+  }
+  print("CTRP testing: DONE")
 
   use_data_gdsc <- filter(use_data, Dataset == "GDSC")
-  use_data_gdsc_summ <- use_data_gdsc %>% count(InG2P)
-  gdsc_lin_ttest <- data.frame(statistic = NA,
-                                 parameter =  NA,
-                                 p.value = NA)
-  if(nrow(use_data_gdsc_summ) <= 1) {
-    gdsc_ttest_res <-  NA
-    ticker <- ticker + 1
-    }
-  else if(use_data_gdsc_summ[use_data_gdsc_summ$InG2P == "Yes",]$nn < 2) { gdsc_ttest_res <-  NA }
-  else if(use_data_gdsc_summ[use_data_gdsc_summ$InG2P == "Yes",]$nn >= 2) {
-    gdsc_lin_ttest <- t.test(use_data_gdsc$Pearson_Corr_Abs ~ use_data_gdsc$InG2P)
-    gdsc_ttest_res <- paste0("t = ", round(gdsc_lin_ttest$statistic, 3), ", df = ", round(gdsc_lin_ttest$parameter, 3), ", p = ", round(gdsc_lin_ttest$p.value, 3))
-  }
-
-  y_value <- ifelse(ticker == 3, 10, max(use_data$n) + 1)
-
+  use_data_gdsc_ge_summ <- use_data_gdsc[!is.na(use_data_gdsc$Pearson_GE_Abs),] %>% count(InG2P)
+  use_data_gdsc_cn_summ <- use_data_gdsc[!is.na(use_data_gdsc$Pearson_CN_Abs),] %>% count(InG2P)
+  gdsc_ge_ttest <- data.frame(statistic = NA, parameter = NA, p.value = NA)
+  gdsc_cn_ttest <- data.frame(statistic = NA, parameter = NA, p.value = NA)
+  if(nrow(use_data_gdsc_ge_summ) <= 1) {
+    gdsc_ge_res <-  NA
+    ticker_ge <- ticker_ge + 1
+  }
+  else if(use_data_gdsc_ge_summ[use_data_gdsc_ge_summ$InG2P == "Yes",]$nn < 2) {
+    gdsc_ge_res <-  NA
+  }
+  else if(use_data_gdsc_ge_summ[use_data_gdsc_ge_summ$InG2P == "Yes",]$nn >= 2) {
+    gdsc_ge_ttest <- t.test(use_data_gdsc$Pearson_GE_Abs ~ use_data_gdsc$InG2P)
+    gdsc_ge_res <- paste0("t = ", round(gdsc_ge_ttest$statistic, 3), ", df = ", round(gdsc_ge_ttest$parameter, 3), ", p = ", round(gdsc_ge_ttest$p.value, 3))
+  }
+  if(nrow(use_data_gdsc_cn_summ) <= 1) {
+    gdsc_cn_res <-  NA
+    ticker_cn <- ticker_cn + 1
+  }
+  else if(use_data_gdsc_cn_summ[use_data_gdsc_cn_summ$InG2P == "Yes",]$nn < 2) {
+    gdsc_cn_res <-  NA
+  }
+  else if(use_data_gdsc_cn_summ[use_data_gdsc_cn_summ$InG2P == "Yes",]$nn >= 2) {
+    gdsc_cn_ttest <- t.test(use_data_gdsc$Pearson_CN_Abs ~ use_data_gdsc$InG2P)
+    gdsc_cn_res <- paste0("t = ", round(gdsc_cn_ttest$statistic, 3), ", df = ", round(gdsc_cn_ttest$parameter, 3), ", p = ", round(gdsc_cn_ttest$p.value, 3))
+  }
+  print("GDSC testing: DONE")
+
+  y_value_ge <- ifelse(ticker_ge == 3, 10, max(use_data$n) + 1)
+  y_value_cn <- ifelse(ticker_cn == 3, 10, max(use_data$n) + 1)
   summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"),
-                          Test_Results_p = c(ccle_ttest_res, ctrp_ttest_res, gdsc_ttest_res),
-                          t_statistic = c(round(ccle_lin_ttest$statistic, 3), round(ctrp_lin_ttest$statistic, 3), round(gdsc_lin_ttest$statistic, 3)),
-                          df = c(round(ccle_lin_ttest$parameter, 3), round(ctrp_lin_ttest$parameter, 3), round(gdsc_lin_ttest$parameter, 3)),
-                          p_value = c(round(ccle_lin_ttest$p.value, 3), round(ctrp_lin_ttest$p.value, 3), round(gdsc_lin_ttest$p.value, 3)),
+                          Test_Results_GE = c(ccle_ge_res, ctrp_ge_res, gdsc_ge_res),
+                          t_statistic_GE = c(round(ccle_ge_ttest$statistic, 3), round(ctrp_ge_ttest$statistic, 3), round(gdsc_ge_ttest$statistic, 3)),
+                          df_GE = c(round(ccle_ge_ttest$parameter, 3), round(ctrp_ge_ttest$parameter, 3), round(gdsc_ge_ttest$parameter, 3)),
+                          p_value_GE = c(round(ccle_ge_ttest$p.value, 3), round(ctrp_ge_ttest$p.value, 3), round(gdsc_ge_ttest$p.value, 3)),
+                          Test_Results_CN = c(ccle_cn_res, ctrp_cn_res, gdsc_cn_res),
+                          t_statistic_CN = c(round(ccle_cn_ttest$statistic, 3), round(ctrp_cn_ttest$statistic, 3), round(gdsc_cn_ttest$statistic, 3)),
+                          df_CN = c(round(ccle_cn_ttest$parameter, 3), round(ctrp_cn_ttest$parameter, 3), round(gdsc_cn_ttest$parameter, 3)),
+                          p_value_CN = c(round(ccle_cn_ttest$p.value, 3), round(ctrp_cn_ttest$p.value, 3), round(gdsc_cn_ttest$p.value, 3)),
                           group_general_lineage_name = lineage)
 
-  plot_point <- ggplot(data = use_data) +
+  ## Gene expression
+  if(sum(!is.na(use_data$Pearson_GE_Abs)) > 0) {
+    plot_ge_point <- ggplot(data = use_data) +
       facet_wrap(~ Dataset, drop = FALSE) +
       scale_y_continuous(breaks = pretty_breaks()) +
-    geom_point(mapping = aes(label = Pearson_Pvalue, color = InG2P, fill = InG2P, shape = Pearson_Corr_Sign, x = Pearson_Corr_Abs, y = n), alpha = 0.5, position = position_jitter(width = 0, height = 0.15)) +
+      geom_point(mapping = aes(label = Pearson_GE_Label, color = InG2P, fill = InG2P, shape = Pearson_GE_Sign, x = Pearson_GE_Abs, y = n), alpha = 0.5, position = position_jitter(width = 0, height = 0.15)) +
       scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
@@
       scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-    geom_text(data = summ_text, mapping = aes(x = 0.5, y = y_value, label = Test_Results_p), nudge_y = 1) +
+      geom_text(data = summ_text, mapping = aes(x = 0.5, y = y_value_ge, label = Test_Results_GE), nudge_y = 1) +
       labs(y = "Number of level A G2P associations") +
       theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
-
-  plot_box <- ggplot(data = use_data) +
+    plot_ge_box <- ggplot(data = use_data) +
       facet_wrap(~ Dataset, drop = FALSE) +
-    geom_violin(mapping = aes(color = InG2P, y = Pearson_Corr_Abs, x = InG2P), alpha = 0.5) +
-    geom_boxplot(mapping = aes(color = InG2P, y = Pearson_Corr_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
+      geom_violin(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.5) +
+      geom_boxplot(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
       scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
       coord_flip() +
-    labs(x = "Level A G2P\nassociation") +
       theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
-  plot <- subplot(plot_box, plot_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(title = lineage, margin = list(t = 75, l = 75), xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and gene expression"), yaxis = list(title = "Level A G2P\nassociation", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
-
-  saveWidgetFix(widget = plot, file = paste0("./plots_18Q3/manuscript/plotlys_pearson_by_lineage/", lineage, "_g2p_evidence_pearson_plotly.html"))
+    plot_ge <- subplot(plot_ge_box, plot_ge_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>%
+               layout(title = lineage, margin = list(t = 75, l = 75),
+                      xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and gene expression"),
+                      yaxis = list(title = "In G2P?", domain = c(0.8, 1)),
+                      yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
+    saveWidgetFix(widget = plot_ge, file = paste0("./plots_18Q3/manuscript/plotlys_ge_by_lineage/", lineage, "_ge_plotly.html"))
+    print("Gene expression plotly: DONE")
+  }
+  else if(sum(!is.na(use_data$Pearson_GE_Abs)) == 0) { print("Gene expression plotly: None") }
+
+  ## Copy number
+  if(sum(!is.na(use_data$Pearson_CN_Abs)) > 0) {
+    plot_cn_point <- ggplot(data = use_data) +
+      facet_wrap(~ Dataset, drop = FALSE) +
+      scale_y_continuous(breaks = pretty_breaks()) +
+      geom_point(mapping = aes(label = Pearson_CN_Label, color = InG2P, fill = InG2P, shape = Pearson_CN_Sign, x = Pearson_CN_Abs, y = n), alpha = 0.5, position = position_jitter(width = 0, height = 0.15)) +
+      scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
+      scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+      scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+      geom_text(data = summ_text, mapping = aes(x = 0.5, y = y_value_cn, label = Test_Results_CN), nudge_y = 1) +
+      labs(y = "Number of level A G2P associations") +
+      theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
+    plot_cn_box <- ggplot(data = use_data) +
+      facet_wrap(~ Dataset, drop = FALSE) +
+      geom_violin(mapping = aes(color = InG2P, y = Pearson_CN_Abs, x = InG2P), alpha = 0.5) +
+      geom_boxplot(mapping = aes(color = InG2P, y = Pearson_CN_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
+      scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+      coord_flip() +
+      theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
+    plot_cn <- subplot(plot_cn_box, plot_cn_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>%
+               layout(title = lineage, margin = list(t = 75, l = 75),
+                      xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and copy number"),
+                      yaxis = list(title = "In G2P?", domain = c(0.8, 1)),
+                      yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
+    saveWidgetFix(widget = plot_cn, file = paste0("./plots_18Q3/manuscript/plotlys_cn_by_lineage/", lineage, "_cn_plotly.html"))
+    print("Copy number plotly: DONE")
+  }
+  else if(sum(!is.na(use_data$Pearson_CN_Abs)) == 0) { print("Copy number plotly: None") }
+
   return(summ_text)
@@
 
-## Drugscreen: Mutation status G2P evidence
+## Drugscreen: G2P evidence
 
 ### Lineage-agnostic
+
+#### Mutation status
 
@@
   coord_flip() +
-  labs(x = "Level A G2P\nassociation") +
+  labs(x = "In G2P?") +
   theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
@@
 
-g2p_druggene_all_p_summ_plot <- cowplot::plot_grid(plot_p_box,
+g2p_druggene_mut_plot <- cowplot::plot_grid(plot_p_box,
                    plot_p_point,
                    nrow = 2,
-                   rel_heights = c(1.5, 4))
-g2p_druggene_all_p_summ_plot
-# ggsave("./plots_18Q3/manuscript/g2p_druggene_all_p_summ_plot.png", g2p_druggene_all_p_summ_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
+                   rel_heights = c(1, 4))
+g2p_druggene_mut_plot
+# ggsave("./plots_18Q3/manuscript/g2p_druggene_mut_plot.png", g2p_druggene_mut_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
 ```
@@
 
-plot <- subplot(plot_p_box, plot_p_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Gene-drug association p-value between mutation groups"), yaxis = list(title = "Level A G2P\nassociation", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
-
-saveWidgetFix(widget = plot, file = "./plots_18Q3/manuscript/g2p_druggene_all_p_summ_plot.html")
+plot <- subplot(plot_p_box, plot_p_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Gene-drug association p-value between mutation groups"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
+
+saveWidgetFix(widget = plot, file = "./plots_18Q3/manuscript/g2p_druggene_mut_plot.html")
+```
+
+#### GE and CN
+
+```{r}
+ccle_pearson_res <- ccle_data_g2p_grid %>% group_by(Drug_Gene) %>%
+                    summarize(Pearson_Corr_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
+                              Pearson_Pval_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
+                              Pearson_Corr_CN = cor.test(y = AUC, x = Copy_Number, method = "pearson", use = "complete.obs")$estimate,
+                              Pearson_Pval_CN = cor.test(y = AUC, x = Copy_Number, method = "pearson", use = "complete.obs")$p.value)
+ccle_pearson_res <- merge(g2p_druggene_p_tally, ccle_pearson_res, by = "Drug_Gene", all.y = TRUE)
+ccle_pearson_res$n <- ifelse(is.na(ccle_pearson_res$n), 0, ccle_pearson_res$n)
+ccle_pearson_res$InG2P <- ifelse(ccle_pearson_res$n != 0, "Yes", "No")
+ccle_pearson_res$Dataset <- "CCLE"
+ccle_pearson_ttest_GE <- t.test(ccle_pearson_res$Pearson_Corr_GE ~ ccle_pearson_res$InG2P)
+ccle_pearson_ttest_res_GE <- paste0("t = ", round(ccle_pearson_ttest_GE$statistic, 3), ", df = ", round(ccle_pearson_ttest_GE$parameter, 3), ", p = ", round(ccle_pearson_ttest_GE$p.value, 3))
+ccle_pearson_ttest_CN <- t.test(ccle_pearson_res$Pearson_Corr_CN ~ ccle_pearson_res$InG2P)
+ccle_pearson_ttest_res_CN <- paste0("t = ", round(ccle_pearson_ttest_CN$statistic, 3), ", df = ", round(ccle_pearson_ttest_CN$parameter, 3), ", p = ", round(ccle_pearson_ttest_CN$p.value, 3))
+
+ctrp_pearson_res <- ctrp_data_g2p_grid %>% group_by(Drug_Gene) %>%
+                    summarize(Pearson_Corr_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
+                              Pearson_Pval_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
+                              Pearson_Corr_CN = cor.test(y = AUC, x = Copy_Number, method = "pearson", use = "complete.obs")$estimate,
+                              Pearson_Pval_CN = cor.test(y = AUC, x = Copy_Number, method = "pearson", use = "complete.obs")$p.value)
+ctrp_pearson_res <- merge(g2p_druggene_p_tally, ctrp_pearson_res, by = "Drug_Gene", all.y = TRUE)
+ctrp_pearson_res$n <- ifelse(is.na(ctrp_pearson_res$n), 0, ctrp_pearson_res$n)
+ctrp_pearson_res$InG2P <- ifelse(ctrp_pearson_res$n != 0, "Yes", "No")
+ctrp_pearson_res$Dataset <- "CTRP"
+ctrp_pearson_ttest_GE <- t.test(ctrp_pearson_res$Pearson_Corr_GE ~ ctrp_pearson_res$InG2P)
+ctrp_pearson_ttest_res_GE <- paste0("t = ", round(ctrp_pearson_ttest_GE$statistic, 3), ", df = ", round(ctrp_pearson_ttest_GE$parameter, 3), ", p = ", round(ctrp_pearson_ttest_GE$p.value, 3))
+ctrp_pearson_ttest_CN <- t.test(ctrp_pearson_res$Pearson_Corr_CN ~ ctrp_pearson_res$InG2P)
+ctrp_pearson_ttest_res_CN <- paste0("t = ", round(ctrp_pearson_ttest_CN$statistic, 3), ", df = ", round(ctrp_pearson_ttest_CN$parameter, 3), ", p = ", round(ctrp_pearson_ttest_CN$p.value, 3))
+
+gdsc_pearson_res <- gdsc_data_g2p_grid %>% group_by(Drug_Gene) %>%
+                    summarize(Pearson_Corr_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
+                              Pearson_Pval_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
+                              Pearson_Corr_CN = cor.test(y = AUC, x = Copy_Number, method = "pearson", use = "complete.obs")$estimate,
+                              Pearson_Pval_CN = cor.test(y = AUC, x = Copy_Number, method = "pearson", use = "complete.obs")$p.value)
+gdsc_pearson_res <- merge(g2p_druggene_p_tally, gdsc_pearson_res, by = "Drug_Gene", all.y = TRUE)
+gdsc_pearson_res$n <- ifelse(is.na(gdsc_pearson_res$n), 0, gdsc_pearson_res$n)
+gdsc_pearson_res$InG2P <- ifelse(gdsc_pearson_res$n != 0, "Yes", "No")
+gdsc_pearson_res$Dataset <- "GDSC"
+gdsc_pearson_ttest_GE <- t.test(gdsc_pearson_res$Pearson_Corr_GE ~ gdsc_pearson_res$InG2P)
+gdsc_pearson_ttest_res_GE <- paste0("t = ", round(gdsc_pearson_ttest_GE$statistic, 3), ", df = ", round(gdsc_pearson_ttest_GE$parameter, 3), ", p = ", round(gdsc_pearson_ttest_GE$p.value, 3))
+gdsc_pearson_ttest_CN <- t.test(gdsc_pearson_res$Pearson_Corr_CN ~ gdsc_pearson_res$InG2P)
+gdsc_pearson_ttest_res_CN <- paste0("t = ", round(gdsc_pearson_ttest_CN$statistic, 3), ", df = ", round(gdsc_pearson_ttest_CN$parameter, 3), ", p = ", round(gdsc_pearson_ttest_CN$p.value, 3))
+
+g2p_druggene_pearson <- rbind(ccle_pearson_res, ctrp_pearson_res, gdsc_pearson_res)
+g2p_druggene_pearson$Pearson_GE_Abs <- abs(g2p_druggene_pearson$Pearson_Corr_GE)
+g2p_druggene_pearson$Pearson_GE_Sign <- ifelse(sign(g2p_druggene_pearson$Pearson_Corr_GE) == 1, "+",
+                                           ifelse(sign(g2p_druggene_pearson$Pearson_Corr_GE) == -1, "-", "0"))
+g2p_druggene_pearson$Pearson_CN_Abs <- abs(g2p_druggene_pearson$Pearson_Corr_CN)
+g2p_druggene_pearson$Pearson_CN_Sign <- ifelse(sign(g2p_druggene_pearson$Pearson_Corr_CN) == 1, "+",
+                                           ifelse(sign(g2p_druggene_pearson$Pearson_Corr_CN) == -1, "-", "0"))
+g2p_druggene_pearson_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"),
+                                        Test_Results_GE = c(ccle_pearson_ttest_res_GE, ctrp_pearson_ttest_res_GE, gdsc_pearson_ttest_res_GE),
+                                        Test_Results_CN = c(ccle_pearson_ttest_res_CN, ctrp_pearson_ttest_res_CN, gdsc_pearson_ttest_res_CN))
+```
+
+Gene expression:
+```{r fig.height=5.5, fig.width=12}
+plot_ge_point <- ggplot(data = g2p_druggene_pearson, aes(x = Pearson_GE_Abs, y = n, label = Drug_Gene)) +
+  facet_wrap(~ Dataset) +
+  geom_point(mapping = aes(fill = InG2P, color = InG2P, shape = Pearson_GE_Sign), alpha = 0.5, size = 1.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
+  scale_x_continuous(breaks = pretty_breaks()) +
+  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
+  geom_text_repel(data = subset(g2p_druggene_pearson, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
+  geom_text(data = g2p_druggene_pearson_text, mapping = aes(x = 0.3, y = 110, label = Test_Results_GE)) +
+  labs(x = "Pearson correlation coefficient between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +
+  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
+  guides(color = FALSE, fill = FALSE) +
+  labs(shape = "Direction of correlation:")
+
+plot_ge_box <- ggplot(data = g2p_druggene_pearson) +
+  facet_wrap(~ Dataset) +
+  geom_violin(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.5) +
+  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  coord_flip() +
+  labs(x = "In G2P?") +
+  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
+
+plot_ge_point <- ggplot_gtable(ggplot_build(plot_ge_point))
+plot_ge_box <- ggplot_gtable(ggplot_build(plot_ge_box))
+p_maxWidth <-  grid::unit.pmax(plot_ge_point$widths, plot_ge_box$widths)
+plot_ge_point$widths <- as.list(p_maxWidth)
+plot_ge_box$widths <- as.list(p_maxWidth)
+
+g2p_druggene_ge_plot <- cowplot::plot_grid(plot_ge_box, plot_ge_point, nrow = 2, rel_heights = c(1, 4))
+g2p_druggene_ge_plot
+# ggsave("./plots_18Q3/manuscript/g2p_druggene_ge_plot.png", g2p_druggene_ge_plot, device = "png", dpi = 450, width = 12, height = 5.5, units = "in")
+```
+
+```{r, eval=FALSE}
+plot_ge_point <- ggplot(data = g2p_druggene_pearson) +
+  facet_wrap(~ Dataset) +
+  geom_point(mapping = aes(label = Drug_Gene, fill = InG2P, color = InG2P, shape = Pearson_GE_Sign, x = Pearson_GE_Abs, y = n, size = Pearson_Pval_GE), alpha = 0.5, size = 1.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
+  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
+  scale_x_continuous(breaks = pretty_breaks()) +
+  geom_text(data = g2p_druggene_pearson_text, mapping = aes(x = 0.3, y = 110, label = Test_Results_GE)) +
+  labs(x = "Pearson correlation coefficient between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +
+  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
+  guides(color = FALSE, fill = FALSE) +
+  labs(shape = NULL)
+
+plot_ge_box <- ggplot(data = g2p_druggene_pearson) +
+  facet_wrap(~ Dataset) +
+  geom_violin(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.5) +
+  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  coord_flip() +
+  labs(x = "In G2P?") +
+  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
+
+plot <- subplot(plot_ge_box, plot_ge_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and gene expression"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
+
+saveWidgetFix(widget = plot, file = "./plots_18Q3/manuscript/g2p_druggene_ge_plot.html")
+```
+
+Copy number:
+```{r fig.height=5.5, fig.width=12}
+plot_cn_point <- ggplot(data = g2p_druggene_pearson, aes(x = Pearson_CN_Abs, y = n, label = Drug_Gene)) +
+  facet_wrap(~ Dataset) +
+  geom_point(mapping = aes(fill = InG2P, color = InG2P, shape = Pearson_CN_Sign), alpha = 0.5, size = 1.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
+  scale_x_continuous(breaks = pretty_breaks()) +
+  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
+  geom_text_repel(data = subset(g2p_druggene_pearson, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
+  geom_text(data = g2p_druggene_pearson_text, mapping = aes(x = 0.3, y = 110, label = Test_Results_CN)) +
+  labs(x = "Pearson correlation coefficient between drug-gene AUC and copy number", y = "Number of level A G2P associations") +
+  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
+  guides(color = FALSE, fill = FALSE) +
+  labs(shape = "Direction of correlation:")
+
+plot_cn_box <- ggplot(data = g2p_druggene_pearson) +
+  facet_wrap(~ Dataset) +
+  geom_violin(mapping = aes(color = InG2P, y = Pearson_CN_Abs, x = InG2P), alpha = 0.5) +
+  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_CN_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  coord_flip() +
+  labs(x = "In G2P?") +
+  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
+
+plot_cn_point <- ggplot_gtable(ggplot_build(plot_cn_point))
+plot_cn_box <- ggplot_gtable(ggplot_build(plot_cn_box))
+p_maxWidth <-  grid::unit.pmax(plot_cn_point$widths, plot_cn_box$widths)
+plot_cn_point$widths <- as.list(p_maxWidth)
+plot_cn_box$widths <- as.list(p_maxWidth)
+
+g2p_druggene_cn_plot <- cowplot::plot_grid(plot_cn_box, plot_cn_point, nrow = 2, rel_heights = c(1, 4))
+g2p_druggene_cn_plot
+# ggsave("./plots_18Q3/manuscript/g2p_druggene_cn_plot.png", g2p_druggene_cn_plot, device = "png", dpi = 450, width = 12, height = 5.5, units = "in")
+```
+
+```{r, eval=FALSE}
+plot_cn_point <- ggplot(data = g2p_druggene_pearson) +
+  facet_wrap(~ Dataset) +
+  geom_point(mapping = aes(label = Drug_Gene, fill = InG2P, color = InG2P, shape = Pearson_GE_Sign, x = Pearson_GE_Abs, y = n), alpha = 0.5, size = 1.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
+  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
+  scale_x_continuous(breaks = pretty_breaks()) +
+  geom_text(data = g2p_druggene_pearson_text, mapping = aes(x = 0.3, y = 110, label = Test_Results_GE)) +
+  labs(x = "Pearson correlation coefficient between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +
+  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
+  guides(color = FALSE, fill = FALSE) +
+  labs(shape = NULL)
+
+plot_cn_box <- ggplot(data = g2p_druggene_pearson) +
+  facet_wrap(~ Dataset) +
+  geom_violin(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.5) +
+  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  coord_flip() +
+  labs(x = "In G2P?") +
+  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
+
+plot <- subplot(plot_cn_box, plot_cn_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and gene expression"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
+
+saveWidgetFix(widget = plot, file = "./plots_18Q3/manuscript/g2p_druggene_cn_plot.html")
 ```
@@
 ### By lineage
+
+#### Mutation Status
 
@@
 
-## Drugscreen: Gene expression G2P evidence
-
-### Lineage-agnostic
-
-```{r}
-ccle_pearson_res <- ccle_data_ptmuts %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate, Pearson_Pval = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value)
-ccle_pearson_res <- merge(g2p_druggene_p_tally, ccle_pearson_res, by = "Drug_Gene", all.y = TRUE)
-ccle_pearson_res$n <- ifelse(is.na(ccle_pearson_res$n), 0, ccle_pearson_res$n)
-ccle_pearson_res$InG2P <- ifelse(ccle_pearson_res$n != 0, "Yes", "No")
-ccle_pearson_res$Dataset <- "CCLE"
-ccle_pearson_ttest <- t.test(ccle_pearson_res$Pearson_Corr ~ ccle_pearson_res$InG2P)
-ccle_pearson_ttest_res <- paste0("t = ", round(ccle_pearson_ttest$statistic, 3), ", df = ", round(ccle_pearson_ttest$parameter, 3), ", p = ", round(ccle_pearson_ttest$p.value, 3))
-
-ctrp_pearson_res <- ctrp_data_ptmuts %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate, Pearson_Pval = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value)
-ctrp_pearson_res <- merge(g2p_druggene_p_tally, ctrp_pearson_res, by = "Drug_Gene", all.y = TRUE)
-ctrp_pearson_res$n <- ifelse(is.na(ctrp_pearson_res$n), 0, ctrp_pearson_res$n)
-ctrp_pearson_res$InG2P <- ifelse(ctrp_pearson_res$n != 0, "Yes", "No")
-ctrp_pearson_res$Dataset <- "CTRP"
-ctrp_pearson_ttest <- t.test(ctrp_pearson_res$Pearson_Corr ~ ctrp_pearson_res$InG2P)
-ctrp_pearson_ttest_res <- paste0("t = ", round(ctrp_pearson_ttest$statistic, 3), ", df = ", round(ctrp_pearson_ttest$parameter, 3), ", p = ", round(ctrp_pearson_ttest$p.value, 3))
-
-gdsc_pearson_res <- gdsc_data_ptmuts %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate, Pearson_Pval = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value)
-gdsc_pearson_res <- merge(g2p_druggene_p_tally, gdsc_pearson_res, by = "Drug_Gene", all.y = TRUE)
-gdsc_pearson_res$n <- ifelse(is.na(gdsc_pearson_res$n), 0, gdsc_pearson_res$n)
-gdsc_pearson_res$InG2P <- ifelse(gdsc_pearson_res$n != 0, "Yes", "No")
-gdsc_pearson_res$Dataset <- "GDSC"
-gdsc_pearson_ttest <- t.test(gdsc_pearson_res$Pearson_Corr ~ gdsc_pearson_res$InG2P)
-gdsc_pearson_ttest_res <- paste0("t = ", round(gdsc_pearson_ttest$statistic, 3), ", df = ", round(gdsc_pearson_ttest$parameter, 3), ", p = ", round(gdsc_pearson_ttest$p.value, 3))
-
-g2p_druggene_pearson <- rbind(ccle_pearson_res, ctrp_pearson_res, gdsc_pearson_res)
-g2p_druggene_pearson$Pearson_Corr_Abs <- abs(g2p_druggene_pearson$Pearson_Corr)
-g2p_druggene_pearson$Pearson_Corr_Sign <- ifelse(sign(g2p_druggene_pearson$Pearson_Corr) == 1, "+",
-                                           ifelse(sign(g2p_druggene_pearson$Pearson_Corr) == -1, "-", "0"))
-g2p_druggene_pearson_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"), Test_Results_PearCorr = c(ccle_pearson_ttest_res, ctrp_pearson_ttest_res, gdsc_pearson_ttest_res))
-```
-
-```{r fig.height=5.5, fig.width=12}
-plot_pearson_point <- ggplot(data = g2p_druggene_pearson, aes(x = Pearson_Corr_Abs, y = n, label = Drug_Gene)) +
-  facet_wrap(~ Dataset) +
-  geom_point(mapping = aes(fill = InG2P, color = InG2P, shape = Pearson_Corr_Sign), alpha = 0.5, size = 1.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
-  scale_x_continuous(breaks = pretty_breaks()) +
-  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
-  geom_text_repel(data = subset(g2p_druggene_pearson, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
-  geom_text(data = g2p_druggene_pearson_text, mapping = aes(x = 0.3, y = 110, label = Test_Results_PearCorr)) +
-  labs(x = "Pearson correlation coefficient between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +
-  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
-  guides(color = FALSE, fill = FALSE) +
-  labs(shape = "Direction of correlation:")
-
-plot_pearson_box <- ggplot(data = g2p_druggene_pearson) +
-  facet_wrap(~ Dataset) +
-  geom_violin(mapping = aes(color = InG2P, y = Pearson_Corr_Abs, x = InG2P), alpha = 0.5) +
-  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_Corr_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  coord_flip() +
-  labs(x = "Level A G2P\nassociation") +
-  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
-plot_pearson_point <- ggplot_gtable(ggplot_build(plot_pearson_point))
-plot_pearson_box <- ggplot_gtable(ggplot_build(plot_pearson_box))
-p_maxWidth <-  grid::unit.pmax(plot_pearson_point$widths, plot_pearson_box$widths)
-plot_pearson_point$widths <- as.list(p_maxWidth)
-plot_pearson_box$widths <- as.list(p_maxWidth)
-
-g2p_druggene_pearson_plot <- cowplot::plot_grid(plot_pearson_box, plot_pearson_point, nrow = 2, rel_heights = c(1.5, 4))
-g2p_druggene_pearson_plot
-# ggsave("./plots_18Q3/manuscript/g2p_druggene_pearson_plot.png", g2p_druggene_pearson_plot, device = "png", dpi = 450, width = 12, height = 5.5, units = "in")
-```
-
-```{r, eval=FALSE}
-plot_pearson_point <- ggplot(data = g2p_druggene_pearson) +
-  facet_wrap(~ Dataset) +
-  geom_point(mapping = aes(label = Drug_Gene, fill = InG2P, color = InG2P, shape = Pearson_Corr_Sign, x = Pearson_Corr_Abs, y = n), alpha = 0.5, size = 1.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
-  scale_x_continuous(breaks = pretty_breaks()) +
-  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
-  geom_text(data = g2p_druggene_pearson_text, mapping = aes(x = 0.3, y = 110, label = Test_Results_PearCorr)) +
-  labs(x = "Pearson correlation coefficient between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +
-  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
-  guides(color = FALSE, fill = FALSE) +
-  labs(shape = NULL)
-
-plot_pearson_box <- ggplot(data = g2p_druggene_pearson) +
-  facet_wrap(~ Dataset) +
-  geom_violin(mapping = aes(color = InG2P, y = Pearson_Corr_Abs, x = InG2P), alpha = 0.5) +
-  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_Corr_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  coord_flip() +
-  labs(x = "Level A G2P\nassociation") +
-  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
-plot <- subplot(plot_pearson_box, plot_pearson_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and gene expression"), yaxis = list(title = "Level A G2P\nassociation", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
-
-saveWidgetFix(widget = plot, file = "./plots_18Q3/manuscript/g2p_druggene_pearson_plot.html")
-```
-
-### By lineage
-
+#### GE and CN
 ```{r, eval=FALSE}
 ccle_lineages4pearson <- as.character(unique(ccle_data_g2p_grid$group_general_lineage_name))[!is.na(as.character(unique(ccle_data_g2p_grid$group_general_lineage_name)))]
-ccle_signif_pearson <- lapply(ccle_lineages4pearson, PearsonByLineage, dataset = ccle_data_g2p_grid)
-ccle_signif_pearson_all_lin <- rbindlist(ccle_signif_pearson, use.names = TRUE)
-ccle_signif_pearson_all_lin$Dataset <- "CCLE"
+ccle_signif_ge <- lapply(ccle_lineages4pearson, PearsonByLineage, variable = "GE", dataset = ccle_data_g2p_grid)
+ccle_signif_ge_all_lin <- rbindlist(ccle_signif_ge, use.names = TRUE)
+ccle_signif_ge_all_lin$Dataset <- "CCLE"
+ccle_signif_cn <- lapply(ccle_lineages4pearson, PearsonByLineage, variable = "CN", dataset = ccle_data_g2p_grid)
+ccle_signif_cn_all_lin <- rbindlist(ccle_signif_cn, use.names = TRUE)
+ccle_signif_cn_all_lin$Dataset <- "CCLE"
+ccle_signif_all_lin <- merge(ccle_signif_ge_all_lin, ccle_signif_cn_all_lin, by = c("Drug_Gene", "group_general_lineage_name", "n", "Dataset"), all = TRUE)
 
 ctrp_lineages4pearson <- as.character(unique(ctrp_data_g2p_grid$group_general_lineage_name))[!is.na(as.character(unique(ctrp_data_g2p_grid$group_general_lineage_name)))]
-ctrp_signif_pearson <- lapply(ctrp_lineages4pearson, PearsonByLineage, dataset = ctrp_data_g2p_grid)
-ctrp_signif_pearson_all_lin <- rbindlist(ctrp_signif_pearson, use.names = TRUE)
-ctrp_signif_pearson_all_lin$Dataset <- "CTRP"
+ctrp_signif_ge <- lapply(ctrp_lineages4pearson, PearsonByLineage, variable = "GE", dataset = ctrp_data_g2p_grid)
+ctrp_signif_ge_all_lin <- rbindlist(ctrp_signif_ge, use.names = TRUE)
+ctrp_signif_ge_all_lin$Dataset <- "CTRP"
+ctrp_signif_cn <- lapply(ctrp_lineages4pearson, PearsonByLineage, variable = "CN", dataset = ctrp_data_g2p_grid)
+ctrp_signif_cn_all_lin <- rbindlist(ctrp_signif_cn, use.names = TRUE)
+ctrp_signif_cn_all_lin$Dataset <- "CTRP"
+ctrp_signif_all_lin <- merge(ctrp_signif_ge_all_lin, ctrp_signif_cn_all_lin, by = c("Drug_Gene", "group_general_lineage_name", "n", "Dataset"), all = TRUE)
 
 gdsc_lineages4pearson <- as.character(unique(gdsc_data_g2p_grid$group_general_lineage_name))[!is.na(as.character(unique(gdsc_data_g2p_grid$group_general_lineage_name)))]
-gdsc_signif_pearson <- lapply(gdsc_lineages4pearson, PearsonByLineage, dataset = gdsc_data_g2p_grid)
-gdsc_signif_pearson_all_lin <- rbindlist(gdsc_signif_pearson, use.names = TRUE)
-gdsc_signif_pearson_all_lin$Dataset <- "GDSC"
-
-signif_pearson_all_lin <- rbind(ccle_signif_pearson_all_lin, ctrp_signif_pearson_all_lin, gdsc_signif_pearson_all_lin)
-signif_pearson_all_lin$n <- ifelse(is.na(signif_pearson_all_lin$n), 0, signif_pearson_all_lin$n)
-signif_pearson_all_lin$InG2P <- ifelse(signif_pearson_all_lin$n != 0, "Yes", "No")
+gdsc_signif_ge <- lapply(gdsc_lineages4pearson, PearsonByLineage, variable = "GE", dataset = gdsc_data_g2p_grid)
+gdsc_signif_ge_all_lin <- rbindlist(gdsc_signif_ge, use.names = TRUE)
+gdsc_signif_ge_all_lin$Dataset <- "GDSC"
+gdsc_signif_cn <- lapply(gdsc_lineages4pearson, PearsonByLineage, variable = "CN", dataset = gdsc_data_g2p_grid)
+gdsc_signif_cn_all_lin <- rbindlist(gdsc_signif_cn, use.names = TRUE)
+gdsc_signif_cn_all_lin$Dataset <- "GDSC"
+gdsc_signif_all_lin <- merge(gdsc_signif_ge_all_lin, gdsc_signif_cn_all_lin, by = c("Drug_Gene", "group_general_lineage_name", "n", "Dataset"), all = TRUE)
+
+signif_all_lin <- rbind(ccle_signif_all_lin, ctrp_signif_all_lin, gdsc_signif_all_lin)
+signif_all_lin$n <- ifelse(is.na(signif_all_lin$n), 0, signif_all_lin$n)
+signif_all_lin$InG2P <- ifelse(signif_all_lin$n != 0, "Yes", "No")
+saveRDS(signif_all_lin, "./data_munging/rds/signif_all_lin.rds")
 ```
@@
 ```{r, results='hide', eval=FALSE}
-g2p_druggenelin_pearson_ttest_res <- lapply(as.character(unique(signif_pearson_all_lin$group_general_lineage_name)), GexpPlotlyByLineage)
-g2p_druggenelin_pearson_ttest_res_list <- rbindlist(g2p_druggenelin_pearson_ttest_res, use.names = TRUE)
-g2p_druggenelin_pearson_ttest_res_list <- g2p_druggenelin_pearson_ttest_res_list[order(g2p_druggenelin_pearson_ttest_res_list$p_value),]
-saveRDS(g2p_druggenelin_pearson_ttest_res_list, "./data_munging/rds/g2p_druggenelin_pearson_ttest_res_list.rds")
-```
-
-```{r}
-g2p_druggenelin_pearson_ttest_res_list <- readRDS("./data_munging/rds/g2p_druggenelin_pearson_ttest_res_list.rds")
-
-knitr::kable(g2p_druggenelin_pearson_ttest_res_list, caption = "GDSC: T-test results for level A G2P drug-gene/gene expression associations across lineages") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+signif_all_lin <- readRDS("./data_munging/rds/signif_all_lin.rds")
+druggenelin_pearson_ttest_res <- lapply(as.character(unique(signif_all_lin$group_general_lineage_name)), PearsonPlotlyByLineage)
+druggenelin_pearson_ttest_res_list <- rbindlist(druggenelin_pearson_ttest_res, use.names = TRUE)
+saveRDS(druggenelin_pearson_ttest_res_list, "./data_munging/rds/druggenelin_pearson_ttest_res_list.rds")
+```
+
+```{r}
+druggenelin_pearson_ttest_res_list <- readRDS("./data_munging/rds/druggenelin_pearson_ttest_res_list.rds")
+
+knitr::kable(druggenelin_pearson_ttest_res_list[order(druggenelin_pearson_ttest_res_list$p_value_GE), c("Dataset", "group_general_lineage_name", "t_statistic_GE", "df_GE", "p_value_GE")], caption = "Gene expression: T-test results for level A G2P drug-gene/gene expression associations across lineages") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+
+knitr::kable(druggenelin_pearson_ttest_res_list[order(druggenelin_pearson_ttest_res_list$p_value_CN), c("Dataset", "group_general_lineage_name", "t_statistic_CN", "df_CN", "p_value_CN")], caption = "Copy number: T-test results for level A G2P drug-gene/gene expression associations across lineages") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```

### 2018-11-15 manuscript.Rmd
rm old data files, make new 18Q4 Rds

@@
 
+Edited `.Renviron` to avoid "Error: memory exhausted (limit reached?)" when melting the GE dataset, as per the suggestion from [StackOverflow](https://stackoverflow.com/questions/51295402/r-on-macos-error-vector-memory-exhausted-limit-reached)
+```
+cd ~
+touch .Renviron
+open .Renviron
+
+# Added following line to .Renviron:
+R_MAX_VSIZE=100Gb
+```
+
 ```{r}
@@
     use_data <- merge(use_data, ccl_converter, by = "accession_id", all.x = TRUE)
-    use_data <- merge(use_data, maf_df, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
-    use_data$Mutation_Status_Nonsilent <- ifelse(is.na(use_data$Mutation_Status_Nonsilent), "Other", use_data$Mutation_Status_Nonsilent)
+    use_data <- merge(use_data, maf_df, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
+    use_data$Mutation_Status_Nonsilent <- ifelse(is.na(use_data$Mutation_Status_Nonsilent), "Wildtype", use_data$Mutation_Status_Nonsilent)
     use_data$Hugo_Symbol <- factor(use_data$Hugo_Symbol)
@@
   else if(variable == "CN") {
-    use_data <- filter(use_data, !is.na(Copy_Number))
+    use_data <- filter(use_data, !is.na(CN))
     use_data_summ <- use_data %>% count(Drug_Gene)
@@
     if(nrow(use_data_filt) > 0) {
-      pearson_res <- use_data_filt %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr_CN = cor.test(y = AUC, x = Copy_Number, method = "pearson", use = "complete.obs")$estimate, Pearson_Pval_CN = cor.test(y = AUC, x = Copy_Number, method = "pearson", use = "complete.obs")$p.value)
+      pearson_res <- use_data_filt %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$estimate, Pearson_Pval_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$p.value)
       pearson_res <- merge(g2p_druggene_p_tally, pearson_res, all.y = TRUE)
@@
 lineage_converter <- unique(ccl_converter[, c("grouped_general_doid", "group_general_lineage_name")])
+colnames(ccl_converter)[colnames(ccl_converter) == "Broad_ID"] <- "DepMap_ID"
 ```
@@
 ```{r}
-ccl_info <- read.delim("./data_munging/DepMap-2018q3-celllines.csv", sep = ",", header = TRUE, na.strings = c("", NA))
+ccl_info <- read.delim("./data_munging/18Q4/DepMap-2018q4-celllines_20181115.csv", sep = ",", header = TRUE, na.strings = c("", NA))
 ccl_info$Primary.Disease <- gsub("\\\\", "", ccl_info$Primary.Disease)
@@
 # From figshare
-crispr_meta <- read.delim("./data_munging/sample_info_18Q3_crispr.csv", sep = ",", header = TRUE, na.strings = c("", NA))
+crispr_meta <- read.delim("./data_munging/18Q4/sample_info_18Q4_crispr_20181115.csv", sep = ",", header = TRUE, na.strings = c("", NA))
 colnames(crispr_meta)[7] <- "CCLE_Name"
@@
 Add a `Mutation_Status` column denoting all entries in MAF files as mutations present in the associated cell lines.
-```{r}
-maf_raw <- read.delim("./data_munging/CCLE_DepMap_18q3_maf_20180718.txt.gz", header = TRUE, sep = "\t")
-# Filter for cell lines in CRISPR screen
-maf_raw <- filter(maf_raw, Broad_ID %in% unique(crispr_meta$Broad_ID))
+
+Merged mutation calls (coding region, germline filtered):
+```{r, eval=FALSE}
+maf_raw <- read.delim("./data_munging/18Q4/depmap_18Q4_mutation_calls_20181114.csv.gz", header = TRUE, sep = ",", row.names = 1)
 colnames(maf_raw)[colnames(maf_raw) == "Tumor_Sample_Barcode"] <- "CCLE_Name"
@@
 # Select columns
-maf_df <- subset(maf_raw, select = c("Hugo_Symbol", "CCLE_Name", "Broad_ID", "Variant_Classification", "Reference_Allele", "Tumor_Seq_Allele1"))
+maf_df <- subset(maf_raw, select = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID", "Variant_Classification", "Reference_Allele", "Tumor_Seq_Allele1", "Genome_Change"))
 maf_df$Reference_Allele_Length <- ifelse(maf_df$Reference_Allele == "-", 0, nchar(as.character(maf_df$Reference_Allele)))
@@
 # Add Mutation_Status column
-maf_df$Mutation_Status_Nonsilent <- ifelse(maf_df$Variant_Classification == "Silent", "Other", "Mutant")
-maf_df <- unique(subset(maf_df, select = c("Hugo_Symbol", "CCLE_Name", "Broad_ID", "Mutation_Status_Nonsilent", "Reference_Allele_Length", "Tumor_Seq_Allele1_Length")))
+maf_df$Mutation_Status_Nonsilent <- ifelse(maf_df$Variant_Classification == "Silent", "Wiltype", "Mutant")
+maf_df <- unique(maf_df)
+saveRDS(maf_df, "./data_munging/rds/maf_df_18Q4.rds", compress = "xz")
+```
+
+```{r, eval=FALSE}
+maf_df <- readRDS("./data_munging/rds/maf_df_18Q4.rds")
 ```
@@
 
-```{r, eval=FALSE}
-cn <- read.delim("./data_munging/public_18Q3_gene_cn_v2.csv.gz", sep = ",", check.names = FALSE, header = TRUE)
-
-# Convert log2 ratios (log2(CN/2)) to CN
-cn[2:ncol(cn)] <- lapply(cn[2:ncol(cn)], function(x) 2 * (2 ^ x))
+DepMap WES CN Data:
+```{r, eval=FALSE}
+cn <- read.delim("./data_munging/18Q4/public_18Q4_gene_cn_20181115.csv.gz", sep = ",", check.names = FALSE, header = TRUE)
 
 # Remove Entrez gene IDs from colnames
+# Format: Hugo_Symbol (Entrez ID)
 colnames(cn) <- gsub(" .*", "", colnames(cn))
-colnames(cn)[1] <- "Broad_ID"
 
 # Melt
-cn_melt <- melt(data = cn, id.vars = "Broad_ID", measure.vars = colnames(cn[2:ncol(cn)]), variable.name = "Hugo_Symbol", value.name = "Copy_Number")
-
-saveRDS(cn_melt, "./data_munging/rds/cn_melt_18Q3.rds", compress = "xz")
-```
-
-```{r, eval=FALSE}
-cn_melt <- readRDS("./data_munging/rds/cn_melt_18Q3.rds")
+cn_melt <- melt(data = cn, id.vars = "DepMap_ID", measure.vars = colnames(cn[2:ncol(cn)]), variable.name = "Hugo_Symbol", value.name = "CN")
+
+saveRDS(cn_melt, "./data_munging/rds/cn_melt_18Q4.rds", compress = "xz")
+```
+
+```{r, eval=FALSE}
+cn_melt <- readRDS("./data_munging/rds/cn_melt_18Q4.rds")
 ```
@@
 
-Gene expression data (Reads Per Kilobase of transcript, per Million mapped reads, RPKM).
-```{r, eval=FALSE}
-ge <- read.delim("./../crispr_lineages_giant_files/CCLE_DepMap_18q3_RNAseq_RPKM_20180718.gct.gz", skip = 2, header = TRUE, sep = "\t", check.names = FALSE)
-
-# Edit columns
-ge$Name <- NULL
-colnames(ge)[1] <- "Hugo_Symbol"
+CCLE RNAseq gene expression data (log2(TPM+1)):
+```{r, eval=FALSE}
+ge <- read.delim("./../htscreen_lineages_giant_files/CCLE_depMap_18Q4_TPM_v2_20181115.csv.gz", header = TRUE, sep = ",", check.names = FALSE)
+
+# Remove Entrez gene IDs from colnames
+# Format: Hugo_Symbol (Entrez ID)
+colnames(ge) <- gsub(" .*", "", colnames(ge))
+colnames(ge)[1] <- "DepMap_ID"
 
 # Melt
-ge_melt <- melt(data = ge, id.vars = "Hugo_Symbol", measure.vars = colnames(ge[2:ncol(ge)]), value.name = "RPKM")
-## Split variable column
-ge_melt <- with(ge_melt, cbind(Hugo_Symbol, colsplit(variable, pattern = " ", names = c("CCLE_Name", "Broad_ID")), RPKM))
-## Remove parentheses around Broad IDs
-ge_melt$Broad_ID <- gsub("\\(|\\)", "", ge_melt$Broad_ID)
-
-saveRDS(ge_melt, "./../crispr_lineages_giant_files/ge_melt_18Q3.rds", compress = "xz")
-```
-
-```{r, eval=FALSE}
-ge_melt <- readRDS("./../crispr_lineages_giant_files/ge_melt_18Q3.rds")
+ge_melt <- melt(ge, id.vars = "DepMap_ID", measure.vars = colnames(ge)[2:ncol(ge)], variable.name = "Hugo_Symbol", value.name = "TPM")
+
+saveRDS(ge_melt, "./data_munging/rds/ge_melt_18Q4.rds", compress = "xz")
+```
+
+```{r, eval=FALSE}
+ge_melt <- readRDS("./data_munging/rds/ge_melt_18Q4.rds")
 ```
@@
 ```{r, eval=FALSE}
-dep <- read.delim("./data_munging/gene_dependency_18Q3.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
+dep <- read.delim("./data_munging/18Q4/gene_dependency_18Q4_20181115.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
 # Remove Entrez gene IDs from colnames
@@
 The latest CRISPR CERES score data (18Q3, August 2018) was pulled from the [DepMap Data Portal](https://depmap.org/portal/download/) (Broad Institute Cancer Dependency Map 2018, Meyers et al. 2017).
-```{r, eval=TRUE}
-crispr <- read.delim("./data_munging/gene_effect_18Q3.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
+```{r, eval=FALSE}
+crispr <- read.delim("./data_munging/18Q4/gene_effect_18Q4_20181115.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
 # Remove Entrez gene IDs from colnames
@@
 # Melt CRISPR dataset for merging
-crispr_melt <- melt(crispr, id.vars = "Broad_ID", measure.vars = colnames(crispr)[2:ncol(crispr)], variable.name = "Hugo_Symbol", value.name = "Score")
+crispr_melt <- melt(crispr, id.vars = "DepMap_ID", measure.vars = colnames(crispr)[2:ncol(crispr)], variable.name = "Hugo_Symbol", value.name = "Score")
 # Melt dependency probabilities dataset for merging
-dep_melt <- melt(dep, id.vars = "Broad_ID", measure.vars = colnames(dep)[2:ncol(dep)], variable.name = "Hugo_Symbol", value.name = "Dep_Prob")
+dep_melt <- melt(dep, id.vars = "DepMap_ID", measure.vars = colnames(dep)[2:ncol(dep)], variable.name = "Hugo_Symbol", value.name = "Dep_Prob")
 # Merge dependency probabilities
-crispr_melt <- merge(crispr_melt, dep_melt, by = c("Broad_ID", "Hugo_Symbol"), all.x = TRUE)
+crispr_melt <- merge(crispr_melt, dep_melt, by = c("DepMap_ID", "Hugo_Symbol"), all.x = TRUE)
 # Merge cell line metadata
-crispr_melt <- merge(crispr_melt, ccl_info, by = "Broad_ID", all.x = TRUE)
-crispr_melt <- merge(crispr_melt, crispr_meta, by = c("CCLE_Name", "Broad_ID"), all.x = TRUE)
+crispr_melt <- merge(crispr_melt, ccl_info, by = "DepMap_ID", all.x = TRUE)
+crispr_melt <- merge(crispr_melt, crispr_meta, by = c("CCLE_Name", "DepMap_ID"), all.x = TRUE)
 # Merge mutation annotations
-crispr_muts <- merge(crispr_melt, maf_df, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
+maf_filt_crispr <- filter(maf_df, Hugo_Symbol %in% as.character(unique(crispr$Hugo_Symbol)))
+crispr_muts <- merge(crispr_melt, maf_filt_crispr, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
 crispr_muts$Hugo_Symbol <- factor(crispr_muts$Hugo_Symbol)
-crispr_muts <- crispr_muts %>% mutate(Mutation_Status_Nonsilent = if_else(is.na(Mutation_Status_Nonsilent), "Other", Mutation_Status_Nonsilent))
-# Summarize number of mutant and Other cell lines
+crispr_muts <- crispr_muts %>% mutate(Mutation_Status_Nonsilent = if_else(is.na(Mutation_Status_Nonsilent), "Wildtype", Mutation_Status_Nonsilent))
+# Summarize number of mutant and Wildtype cell lines
 crispr_muts_summ <- crispr_muts %>% group_by(Hugo_Symbol) %>%
-  summarize(N_Nonsilent_Other = sum(Mutation_Status_Nonsilent == "Other"),
+  summarize(N_Nonsilent_Wildtype = sum(Mutation_Status_Nonsilent == "Wildtype"),
             N_Nonsilent_Mutant = sum(Mutation_Status_Nonsilent == "Mutant"))
@@
 # Add Color columns
-crispr_data$Color_Nonsilent <- ifelse(crispr_data$Mutation_Status_Nonsilent == "Other", "thistle", "darkorchid")
+crispr_data$Color_Nonsilent <- ifelse(crispr_data$Mutation_Status_Nonsilent == "Wildtype", "thistle", "darkorchid")
 crispr_data$Color_Nonsilent <- factor(crispr_data$Color_Nonsilent)
 # Cell line lineages
-crispr_data <- merge(crispr_data, ccl_converter, by = c("CCLE_Name", "Broad_ID"), all.x = TRUE)
+crispr_data <- merge(crispr_data, ccl_converter, by = c("CCLE_Name", "DepMap_ID"), all.x = TRUE)
 levels(crispr_data$lineage_name) <- sort(levels(crispr_data$lineage_name), decreasing = TRUE)
 # Copy number
-crispr_data <- merge(crispr_data, cn_melt, by = c("Hugo_Symbol", "Broad_ID"), all.x = TRUE)
+crispr_data <- merge(crispr_data, cn_melt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
 # Gene expression (RPKM)
-ge_filt <- filter(ge_melt, Hugo_Symbol %in% unique(crispr_data$Hugo_Symbol) & Broad_ID %in% unique(crispr_data$Broad_ID))
-crispr_data <- merge(crispr_data, ge_filt, by = c("Hugo_Symbol", "Broad_ID", "CCLE_Name"), all.x = TRUE)
+ge_filt <- filter(ge_melt, Hugo_Symbol %in% as.character(unique(crispr_data$Hugo_Symbol)) & DepMap_ID %in% as.character(unique(crispr_data$DepMap_ID)))
+crispr_data <- merge(crispr_data, ge_filt, by = c("Hugo_Symbol", "DepMap_ID", "CCLE_Name"), all.x = TRUE)
 crispr_data$RPKM_log2 <- log2(crispr_data$RPKM + 0.0001)
-saveRDS(crispr_data, "./../crispr_lineages_giant_files/crispr_data_18Q3.rds", compress = "xz")
-```
-
-```{r}
-crispr_data <- readRDS("./../crispr_lineages_giant_files/crispr_data_18Q3.rds")
+saveRDS(crispr_data, "./../htscreen_lineages_giant_files/crispr_data_18Q3.rds", compress = "xz")
+```
+
+```{r}
+crispr_data <- readRDS("./../htscreen_lineages_giant_files/crispr_data_18Q3.rds")
 
@@
 
-```{r, eval=FALSE}
+```{r, eval=TRUE}
 # Drug metadata
@@
 ccle_data <- merge(ccle_data, ccl_converter, by = "accession_id", all.x = TRUE)
-ccle_data <- merge(ccle_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
-ccle_data$Mutation_Status_Nonsilent <- ifelse(is.na(ccle_data$Mutation_Status_Nonsilent), "Other", ccle_data$Mutation_Status_Nonsilent)
-ccle_data <- merge(ccle_data, ge_filt, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
-ccle_data <- merge(ccle_data, cn_filt, by = c("Hugo_Symbol", "Broad_ID"), all.x = TRUE)
+ccle_data <- merge(ccle_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
+ccle_data$Mutation_Status_Nonsilent <- ifelse(is.na(ccle_data$Mutation_Status_Nonsilent), "Wildtype", ccle_data$Mutation_Status_Nonsilent)
+ccle_data <- merge(ccle_data, ge_filt, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
+ccle_data <- merge(ccle_data, cn_filt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
 ccle_data$Hugo_Symbol <- factor(ccle_data$Hugo_Symbol)
 ccle_data$AUC <- as.numeric(ccle_data$AUC)
-ccle_data$Color_Nonsilent <- ifelse(ccle_data$Mutation_Status_Nonsilent == "Other", "palegreen3", "springgreen4")
+ccle_data$Color_Nonsilent <- ifelse(ccle_data$Mutation_Status_Nonsilent == "Wildtype", "palegreen3", "springgreen4")
 ccle_data$Color_Nonsilent <- factor(ccle_data$Color_Nonsilent)
@@
 ctrp_data <- merge(ctrp_data, ccl_converter, by = "accession_id", all.x = TRUE)
-ctrp_data <- merge(ctrp_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
-ctrp_data$Mutation_Status_Nonsilent <- ifelse(is.na(ctrp_data$Mutation_Status_Nonsilent), "Other", ctrp_data$Mutation_Status_Nonsilent)
-ctrp_data <- merge(ctrp_data, ge_filt, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
-ctrp_data <- merge(ctrp_data, cn_filt, by = c("Hugo_Symbol", "Broad_ID"), all.x = TRUE)
+ctrp_data <- merge(ctrp_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
+ctrp_data$Mutation_Status_Nonsilent <- ifelse(is.na(ctrp_data$Mutation_Status_Nonsilent), "Wildtype", ctrp_data$Mutation_Status_Nonsilent)
+ctrp_data <- merge(ctrp_data, ge_filt, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
+ctrp_data <- merge(ctrp_data, cn_filt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
 ctrp_data$Hugo_Symbol <- factor(ctrp_data$Hugo_Symbol)
 ctrp_data$AUC <- as.numeric(ctrp_data$AUC)
-ctrp_data$Color_Nonsilent <- ifelse(ctrp_data$Mutation_Status_Nonsilent == "Other", "slategray3", "steelblue4")
+ctrp_data$Color_Nonsilent <- ifelse(ctrp_data$Mutation_Status_Nonsilent == "Wildtype", "slategray3", "steelblue4")
 ctrp_data$Color_Nonsilent <- factor(ctrp_data$Color_Nonsilent)
@@
 gdsc_data <- merge(gdsc_data, ccl_converter, by = "accession_id", all.x = TRUE)
-gdsc_data <- merge(gdsc_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
-gdsc_data$Mutation_Status_Nonsilent <- ifelse(is.na(gdsc_data$Mutation_Status_Nonsilent), "Other", gdsc_data$Mutation_Status_Nonsilent)
-gdsc_data <- merge(gdsc_data, ge_filt, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
-gdsc_data <- merge(gdsc_data, cn_filt, by = c("Hugo_Symbol", "Broad_ID"), all.x = TRUE)
+gdsc_data <- merge(gdsc_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
+gdsc_data$Mutation_Status_Nonsilent <- ifelse(is.na(gdsc_data$Mutation_Status_Nonsilent), "Wildtype", gdsc_data$Mutation_Status_Nonsilent)
+gdsc_data <- merge(gdsc_data, ge_filt, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
+gdsc_data <- merge(gdsc_data, cn_filt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
 gdsc_data$Hugo_Symbol <- factor(gdsc_data$Hugo_Symbol)
 gdsc_data$AUC <- as.numeric(gdsc_data$AUC)
-gdsc_data$Color_Nonsilent <- ifelse(gdsc_data$Mutation_Status_Nonsilent == "Other", "paleturquoise3", "turquoise4")
+gdsc_data$Color_Nonsilent <- ifelse(gdsc_data$Mutation_Status_Nonsilent == "Wildtype", "paleturquoise3", "turquoise4")
 gdsc_data$Color_Nonsilent <- factor(gdsc_data$Color_Nonsilent)
@@
 
-```{r, eval=FALSE}
+```{r, eval=TRUE}
 crispr_signif_g2p_gene <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol"), data = crispr_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
@@
 
-```{r, eval=TRUE}
+```{r}
 crispr_signif_g2p_gene <- readRDS("./data_munging/rds/crispr_signif_g2p_gene.rds")
@@
 
-```{r, eval=TRUE}
+```{r}
 crispr_signif_g2p_lineage <- readRDS("./data_munging/rds/crispr_signif_g2p_lineage.rds")
 
-knitr::kable(filter(crispr_signif_g2p_lineage, p < 0.1)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant vs other cell lines by lineage, p < 0.1 (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(filter(crispr_signif_g2p_lineage, p < 0.1)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant vs wildtype cell lines by lineage, p < 0.1 (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
-knitr::kable(crispr_data_signif_g2p_lineage_summ, caption = "Mutant/Other counts for gene-lineage combinations") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(crispr_data_signif_g2p_lineage_summ, caption = "Mutant/Wildtype counts for gene-lineage combinations") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
-```{r, eval=FALSE}
+```{r, eval=TRUE}
 # G2P drug-gene associations only
@@
 
+```{r}
+ccle_signif_g2p <- readRDS("./data_munging/rds/ccle_signif_g2p_gene.rds")
+
+knitr::kable(ccle_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+
+ccle_signif_g2p_grid <- readRDS("./data_munging/rds/ccle_signif_g2p_grid.rds")
+
+knitr::kable(ccle_signif_g2p_grid[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+### G2P gene, drug, and lineage
+
 ```{r, eval=TRUE}
-ccle_signif_g2p <- readRDS("./data_munging/rds/ccle_signif_g2p_gene.rds")
-
-knitr::kable(ccle_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-
-ccle_signif_g2p_grid <- readRDS("./data_munging/rds/ccle_signif_g2p_grid.rds")
-
-knitr::kable(ccle_signif_g2p_grid[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-### G2P gene, drug, and lineage
-
-```{r, eval=FALSE}
 ccle_signif_g2p_lineage <- lapply(unique(ccle_data_g2p_grid$Drug), WilcoxonByDrug, dataset = ccle_data_g2p_grid, data_name = "ccle", grouping_var = "lineage")
@@
 
-```{r, eval=TRUE}
+```{r}
 ccle_signif_g2p_lineage <- readRDS("./data_munging/rds/ccle_signif_g2p_lineage.rds")
@@
 
-```{r, eval=TRUE}
+```{r, eval=FALSE}
 ctrp_signif_g2p_lineage <- readRDS("./data_munging/rds/ctrp_signif_g2p_lineage.rds")
@@
 
-```{r, eval=TRUE}
+```{r, eval=FALSE}
 gdsc_signif_g2p_lineage <- readRDS("./data_munging/rds/gdsc_signif_g2p_lineage.rds")
@@
 ```{r}
-crispr_data_g2p_summ <- unique(crispr_data_g2p[, c("Hugo_Symbol", "N_Nonsilent_Mutant", "N_Nonsilent_Other")])
-crispr_data_g2p_summ$Percent_Mutant <- crispr_data_g2p_summ$N_Nonsilent_Mutant / (crispr_data_g2p_summ$N_Nonsilent_Mutant + crispr_data_g2p_summ$N_Nonsilent_Other) * 100
+crispr_data_g2p_summ <- unique(crispr_data_g2p[, c("Hugo_Symbol", "N_Nonsilent_Mutant", "N_Nonsilent_Wildtype")])
+crispr_data_g2p_summ$Percent_Mutant <- crispr_data_g2p_summ$N_Nonsilent_Mutant / (crispr_data_g2p_summ$N_Nonsilent_Mutant + crispr_data_g2p_summ$N_Nonsilent_Wildtype) * 100
 rownames(crispr_data_g2p_summ) <- NULL
@@
                               Pearson_Pval_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
-                              Pearson_Corr_CN = cor.test(y = AUC, x = Copy_Number, method = "pearson", use = "complete.obs")$estimate,
-                              Pearson_Pval_CN = cor.test(y = AUC, x = Copy_Number, method = "pearson", use = "complete.obs")$p.value)
+                              Pearson_Corr_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$estimate,
+                              Pearson_Pval_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$p.value)
 ccle_pearson_res <- merge(g2p_druggene_p_tally, ccle_pearson_res, by = "Drug_Gene", all.y = TRUE)
@@
                               Pearson_Pval_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
-                              Pearson_Corr_CN = cor.test(y = AUC, x = Copy_Number, method = "pearson", use = "complete.obs")$estimate,
-                              Pearson_Pval_CN = cor.test(y = AUC, x = Copy_Number, method = "pearson", use = "complete.obs")$p.value)
+                              Pearson_Corr_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$estimate,
+                              Pearson_Pval_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$p.value)
 ctrp_pearson_res <- merge(g2p_druggene_p_tally, ctrp_pearson_res, by = "Drug_Gene", all.y = TRUE)
@@
                               Pearson_Pval_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
-                              Pearson_Corr_CN = cor.test(y = AUC, x = Copy_Number, method = "pearson", use = "complete.obs")$estimate,
-                              Pearson_Pval_CN = cor.test(y = AUC, x = Copy_Number, method = "pearson", use = "complete.obs")$p.value)
+                              Pearson_Corr_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$estimate,
+                              Pearson_Pval_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$p.value)
 gdsc_pearson_res <- merge(g2p_druggene_p_tally, gdsc_pearson_res, by = "Drug_Gene", all.y = TRUE)
@@
 #### GE and CN
+
 ```{r, eval=FALSE}
@@
 ```{r, eval=FALSE}
-crispr_ccl <- unique(select(crispr_data, Broad_ID, CCLE_Name))
-ccle_ccl <- unique(select(ccle_data, Broad_ID, CCLE_Name, accession_id))
-ctrp_ccl <- unique(select(ctrp_data, Broad_ID, CCLE_Name, accession_id))
-gdsc_ccl <- unique(select(gdsc_data, Broad_ID, CCLE_Name, accession_id))
-
-# all_ccl <- merge(ccle_ccl, ctrp_ccl, by = c("Broad_ID", "CCLE_Name", "accession_id"), all = TRUE)
+crispr_ccl <- unique(select(crispr_data, DepMap_ID, CCLE_Name))
+ccle_ccl <- unique(select(ccle_data, DepMap_ID, CCLE_Name, accession_id))
+ctrp_ccl <- unique(select(ctrp_data, DepMap_ID, CCLE_Name, accession_id))
+gdsc_ccl <- unique(select(gdsc_data, DepMap_ID, CCLE_Name, accession_id))
+
+# all_ccl <- merge(ccle_ccl, ctrp_ccl, by = c("DepMap_ID", "CCLE_Name", "accession_id"), all = TRUE)
 ```
@@
 Data management:
-```{r, eval=TRUE}
+```{r, eval=FALSE}
 ccle_g2p_drugboxplots <- paste0(list.files("./plots_18Q3/manuscript/ccle_g2p_drugboxplots", full.names = TRUE))
@@
 Data management:
-```{r, eval=TRUE}
+```{r, eval=FALSE}
 ctrp_g2p_drugboxplots <- paste0(list.files("./plots_18Q3/manuscript/ctrp_g2p_drugboxplots", full.names = TRUE))
@@
 Data management:
-```{r, eval=TRUE}
+```{r, eval=FALSE}
 gdsc_g2p_drugboxplots <- paste0(list.files("./plots_18Q3/manuscript/gdsc_g2p_drugboxplots", full.names = TRUE))
@@
 maf_g2p_indications <- filter(maf_raw, Genome_Change %in% g2p_indications$MutationName)
-crispr_g2p_indications <- merge(crispr_data_ptmuts, maf_g2p_indications, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
-crispr_g2p_indications$Mutation_Status_Nonsilent <- ifelse(is.na(crispr_g2p_indications$Mutation_Status_Nonsilent), "Other", crispr_g2p_indications$Mutation_Status_Nonsilent)
-dup_g2p_indications <- filter(crispr_g2p_indications[, c("Hugo_Symbol", "CCLE_Name", "Broad_ID")] %>% group_by(Hugo_Symbol, CCLE_Name, Broad_ID) %>% tally(), n > 1)
-crispr_g2p_indications <- merge(crispr_g2p_indications, dup_g2p_indications, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
+crispr_g2p_indications <- merge(crispr_data_ptmuts, maf_g2p_indications, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
+crispr_g2p_indications$Mutation_Status_Nonsilent <- ifelse(is.na(crispr_g2p_indications$Mutation_Status_Nonsilent), "Wildtype", crispr_g2p_indications$Mutation_Status_Nonsilent)
+dup_g2p_indications <- filter(crispr_g2p_indications[, c("Hugo_Symbol", "CCLE_Name", "DepMap_ID")] %>% group_by(Hugo_Symbol, CCLE_Name, DepMap_ID) %>% tally(), n > 1)
+crispr_g2p_indications <- merge(crispr_g2p_indications, dup_g2p_indications, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
 crispr_g2p_indications$Genome_Change <- factor(crispr_g2p_indications$Genome_Change, levels = unique(crispr_g2p_indications$Genome_Change))

### 2018-11-16 manuscript.Rmd
overhaul all plots w/ 18Q4 release/harmonization

@@
   use_data <- filter(dataset, Drug == drug)
-  sig <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = grouper, data = use_data, method = "wilcox.test", p.adjust.method = "BH")
+  sig <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = grouper, data = use_data, method = "wilcox.test", p.adjust.method = "BH")
   sig <- adj_signif(sig)
@@
 
-WilcoxonByDrugAllGenes <- function(melt_file, grid_file, data_name) {
-  druglist <- as.character(unique(melt_file$Drug))
-  sig_df <- NULL
-  for(i in 1:length(druglist)) {
-    print(paste0("Current drug in process: ", druglist[i], " (drug ", i, " of ", length(druglist), ")."))
-    flush.console()
-    melted <- filter(melt_file, Drug == druglist[i])
-    use_data <- merge(grid_file, melted, by = "accession_id", all.x = TRUE)
-    use_data <- merge(use_data, ccl_converter, by = "accession_id", all.x = TRUE)
-    use_data <- merge(use_data, maf_df, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
-    use_data$Mutation_Status_Nonsilent <- ifelse(is.na(use_data$Mutation_Status_Nonsilent), "Wildtype", use_data$Mutation_Status_Nonsilent)
-    use_data$Hugo_Symbol <- factor(use_data$Hugo_Symbol)
-    use_data$AUC <- as.numeric(use_data$AUC)
-    use_data <- filter(use_data, !is.na(use_data$AUC))
-    use_data$Drug_Gene <- paste0(use_data$Drug, "_", use_data$Hugo_Symbol)
-    use_data_ptmuts <- filter(use_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
-    use_data_ptmuts$Keep_PtMut_Tests <- ifelse(use_data_ptmuts$Reference_Allele_Length == 1 | is.na(use_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(use_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
-    use_data_ptmuts <- filter(use_data_ptmuts, Keep_PtMut_Tests == TRUE)
-
-    sig <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = "Hugo_Symbol", data = use_data_ptmuts, method = "wilcox.test", p.adjust.method = "BH")
-    sig <- adj_signif(sig)
-    sig <- sig[order(sig$p),]
-    sig <- filter(sig, p <= 0.05)
-    sig$Drug <- druglist[i]
-    sig$Dataset <- toupper(data_name)
-    sig_df <- rbind(sig_df, sig)
-  }
-  return(sig_df)
-}
+# WilcoxonByDrugAllGenes <- function(melt_file, grid_file, data_name) {
+#   druglist <- as.character(unique(melt_file$Drug))
+#   sig_df <- NULL
+#   for(i in 1:length(druglist)) {
+#     print(paste0("Current drug in process: ", druglist[i], " (drug ", i, " of ", length(druglist), ")."))
+#     flush.console()
+#     melted <- filter(melt_file, Drug == druglist[i])
+#     use_data <- merge(grid_file, melted, by = "accession_id", all.x = TRUE)
+#     use_data <- merge(use_data, ccl_converter, by = "accession_id", all.x = TRUE)
+#     use_data <- merge(use_data, maf_df, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
+#     use_data$Mutation_Status_Nonsilent <- ifelse(is.na(use_data$Mutation_Status_Nonsilent), "Wildtype", use_data$Mutation_Status_Nonsilent)
+#     use_data$Hugo_Symbol <- factor(use_data$Hugo_Symbol)
+#     use_data$AUC <- as.numeric(use_data$AUC)
+#     use_data <- filter(use_data, !is.na(use_data$AUC))
+#     use_data$Drug_Gene <- paste0(use_data$Drug, "_", use_data$Hugo_Symbol)
+#     use_data_ptmuts <- filter(use_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
+#     use_data_ptmuts$Keep_PtMut_Tests <- ifelse(use_data_ptmuts$Reference_Allele_Length == 1 | is.na(use_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(use_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
+#     use_data_ptmuts <- filter(use_data_ptmuts, Keep_PtMut_Tests == TRUE)
+#     
+#     sig <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = "Hugo_Symbol", data = use_data_ptmuts, method = "wilcox.test", p.adjust.method = "BH")
+#     sig <- adj_signif(sig)
+#     sig <- sig[order(sig$p),]
+#     sig <- filter(sig, p <= 0.05)
+#     sig$Drug <- druglist[i]
+#     sig$Dataset <- toupper(data_name)
+#     sig_df <- rbind(sig_df, sig)
+#   }
+#   return(sig_df)
+# }
 ```
@@
     if(nrow(use_data_filt) > 0) {
-      pearson_res <- use_data_filt %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate, Pearson_Pval_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value)
+      pearson_res <- use_data_filt %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$estimate, Pearson_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$p.value)
       pearson_res <- merge(g2p_druggene_p_tally, pearson_res, all.y = TRUE)
@@
     if(nrow(use_data_filt) > 0) {
-      pearson_res <- use_data_filt %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$estimate, Pearson_Pval_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$p.value)
+      pearson_res <- use_data_filt %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$estimate, Pearson_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$p.value)
       pearson_res <- merge(g2p_druggene_p_tally, pearson_res, all.y = TRUE)
@@
 
-CCLE RNAseq gene expression data (log2(TPM+1)):
-```{r, eval=FALSE}
-ge <- read.delim("./../htscreen_lineages_giant_files/CCLE_depMap_18Q4_TPM_v2_20181115.csv.gz", header = TRUE, sep = ",", check.names = FALSE)
+18Q3, Gene expression data (Reads Per Kilobase of transcript, per Million mapped reads, RPKM).
+```{r, eval=FALSE}
+ge_18Q3 <- read.delim("./../htscreen_lineages_giant_files/CCLE_DepMap_18q3_RNAseq_RPKM_20180718.gct.gz", skip = 2, header = TRUE, sep = "\t", check.names = FALSE)
+
+# Edit columns
+ge_18Q3$Name <- NULL
+colnames(ge_18Q3)[1] <- "Hugo_Symbol"
+
+# Melt
+ge_melt_18Q3 <- melt(data = ge_18Q3, id.vars = "Hugo_Symbol", measure.vars = colnames(ge_18Q3[2:ncol(ge_18Q3)]), value.name = "RPKM")
+## Split variable column
+ge_melt_18Q3 <- with(ge_melt_18Q3, cbind(Hugo_Symbol, colsplit(variable, pattern = " ", names = c("CCLE_Name", "DepMap_ID")), RPKM))
+## Remove parentheses around Broad IDs
+ge_melt_18Q3$DepMap_ID <- gsub("\\(|\\)", "", ge_melt_18Q3$DepMap_ID)
+
+saveRDS(ge_melt_18Q3, "./../htscreen_lineages_giant_files/ge_melt_18Q3.rds", compress = "xz")
+```
+
+```{r, eval=FALSE}
+ge_melt_18Q3 <- readRDS("./../htscreen_lineages_giant_files/ge_melt_18Q3.rds")
+```
+
+18Q4, CCLE RNAseq gene expression data (log2(TPM+1)):
+```{r, eval=FALSE}
+ge_18Q4 <- read.delim("./../htscreen_lineages_giant_files/CCLE_depMap_18Q4_TPM_v2_20181115.csv.gz", header = TRUE, sep = ",", check.names = FALSE)
 
@@
 # Format: Hugo_Symbol (Entrez ID)
-colnames(ge) <- gsub(" .*", "", colnames(ge))
-colnames(ge)[1] <- "DepMap_ID"
+colnames(ge_18Q4) <- gsub(" .*", "", colnames(ge_18Q4))
+colnames(ge_18Q4)[1] <- "DepMap_ID"
 
 # Melt
-ge_melt <- melt(ge, id.vars = "DepMap_ID", measure.vars = colnames(ge)[2:ncol(ge)], variable.name = "Hugo_Symbol", value.name = "TPM")
-
-saveRDS(ge_melt, "./data_munging/rds/ge_melt_18Q4.rds", compress = "xz")
-```
-
-```{r, eval=FALSE}
-ge_melt <- readRDS("./data_munging/rds/ge_melt_18Q4.rds")
+ge_melt_18Q4_all <- melt(ge_18Q4, id.vars = "DepMap_ID", measure.vars = colnames(ge_18Q4)[2:ncol(ge_18Q4)], variable.name = "Hugo_Symbol", value.name = "TPM")
+ge_melt_18Q4 <- unique(ge_melt_18Q4)
+
+saveRDS(ge_melt_18Q4, "./data_munging/rds/ge_melt_18Q4.rds", compress = "xz")
+```
+
+```{r, eval=FALSE}
+ge_melt_18Q4 <- readRDS("./data_munging/rds/ge_melt_18Q4.rds")
 ```
@@
 # Gene expression (RPKM)
-ge_filt <- filter(ge_melt, Hugo_Symbol %in% as.character(unique(crispr_data$Hugo_Symbol)) & DepMap_ID %in% as.character(unique(crispr_data$DepMap_ID)))
-crispr_data <- merge(crispr_data, ge_filt, by = c("Hugo_Symbol", "DepMap_ID", "CCLE_Name"), all.x = TRUE)
-crispr_data$RPKM_log2 <- log2(crispr_data$RPKM + 0.0001)
-saveRDS(crispr_data, "./../htscreen_lineages_giant_files/crispr_data_18Q3.rds", compress = "xz")
-```
-
-```{r}
-crispr_data <- readRDS("./../htscreen_lineages_giant_files/crispr_data_18Q3.rds")
+ge_crispr_18Q3 <- filter(ge_melt_18Q3, Hugo_Symbol %in% as.character(unique(crispr_melt$Hugo_Symbol)))
+ge_crispr_18Q4 <- filter(ge_melt_18Q4_test, Hugo_Symbol %in% as.character(unique(crispr_melt$Hugo_Symbol)))
+crispr_data <- merge(crispr_data, ge_crispr_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
+crispr_data <- merge(crispr_data, ge_crispr_18Q4, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
+saveRDS(crispr_data, "./../htscreen_lineages_giant_files/crispr_data_18Q4.rds", compress = "xz")
+```
+
+```{r}
+crispr_data <- readRDS("./../htscreen_lineages_giant_files/crispr_data_18Q4.rds")
 
@@
 
-```{r, eval=TRUE}
+```{r, eval=FALSE}
 # Drug metadata
@@
 maf_df_g2p <- filter(maf_df, Hugo_Symbol %in% g2p_genes)
-ge_filt <- filter(ge_melt, Hugo_Symbol %in% g2p_genes)
+ge_filt_18Q3 <- filter(ge_melt_18Q3, Hugo_Symbol %in% g2p_genes)
+# ge_filt_18Q4 <- filter(ge_melt_18Q4, Hugo_Symbol %in% g2p_genes)
 cn_filt <- filter(cn_melt, Hugo_Symbol %in% g2p_genes)
@@
 ccle_data$Mutation_Status_Nonsilent <- ifelse(is.na(ccle_data$Mutation_Status_Nonsilent), "Wildtype", ccle_data$Mutation_Status_Nonsilent)
-ccle_data <- merge(ccle_data, ge_filt, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
+ccle_data <- merge(ccle_data, ge_filt_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
+# ccle_data <- merge(ccle_data, ge_filt_18Q4, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
 ccle_data <- merge(ccle_data, cn_filt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
@@
 ccle_data$AUC <- as.numeric(ccle_data$AUC)
+# CCLE AUC is actually AOC
+# assuming scale is 0-8, transform to range between 0 and 1
+# get AUC by 1 - AOC
+ccle_data$AUC_transform <- 1 - (ccle_data$AUC / 8)
+ccle_data$AUC_zscore <- (ccle_data$AUC_transform - mean(ccle_data$AUC_transform)) / sd(ccle_data$AUC_transform)
 ccle_data$Color_Nonsilent <- ifelse(ccle_data$Mutation_Status_Nonsilent == "Wildtype", "palegreen3", "springgreen4")
@@
 ccle_data$Drug_Gene <- paste0(ccle_data$Drug, "_", ccle_data$Hugo_Symbol)
-saveRDS(ccle_data, "./data_munging/rds/ccle_data_18Q3_g2pgenes.rds", compress = "xz")
+saveRDS(ccle_data, "./data_munging/rds/ccle_data_18Q4_g2pgenes.rds", compress = "xz")
 
@@
 ctrp_data$Mutation_Status_Nonsilent <- ifelse(is.na(ctrp_data$Mutation_Status_Nonsilent), "Wildtype", ctrp_data$Mutation_Status_Nonsilent)
-ctrp_data <- merge(ctrp_data, ge_filt, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
+ctrp_data <- merge(ctrp_data, ge_filt_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
+# ctrp_data <- merge(ctrp_data, ge_filt_18Q4, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
 ctrp_data <- merge(ctrp_data, cn_filt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
@@
 ctrp_data$AUC <- as.numeric(ctrp_data$AUC)
+ctrp_data$AUC_zscore <- (ctrp_data$AUC - mean(ctrp_data$AUC)) / sd(ctrp_data$AUC)
 ctrp_data$Color_Nonsilent <- ifelse(ctrp_data$Mutation_Status_Nonsilent == "Wildtype", "slategray3", "steelblue4")
@@
 ctrp_data$Drug_Gene <- paste0(ctrp_data$Drug, "_", ctrp_data$Hugo_Symbol)
-saveRDS(ctrp_data, "./data_munging/rds/ctrp_data_18Q3_g2pgenes.rds", compress = "xz")
+saveRDS(ctrp_data, "./data_munging/rds/ctrp_data_18Q4_g2pgenes.rds", compress = "xz")
 
@@
 gdsc_data$Mutation_Status_Nonsilent <- ifelse(is.na(gdsc_data$Mutation_Status_Nonsilent), "Wildtype", gdsc_data$Mutation_Status_Nonsilent)
-gdsc_data <- merge(gdsc_data, ge_filt, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
+gdsc_data <- merge(gdsc_data, ge_filt_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
+# gdsc_data <- merge(gdsc_data, ge_filt_18Q4, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
 gdsc_data <- merge(gdsc_data, cn_filt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
@@
 gdsc_data$AUC <- as.numeric(gdsc_data$AUC)
+gdsc_data$AUC_zscore <- (gdsc_data$AUC - mean(gdsc_data$AUC)) / sd(gdsc_data$AUC)
 gdsc_data$Color_Nonsilent <- ifelse(gdsc_data$Mutation_Status_Nonsilent == "Wildtype", "paleturquoise3", "turquoise4")
@@
 gdsc_data$Drug_Gene <- paste0(gdsc_data$Drug, "_", gdsc_data$Hugo_Symbol)
-saveRDS(gdsc_data, "./data_munging/rds/gdsc_data_18Q3_g2pgenes.rds", compress = "xz")
-```
-
-```{r}
-ccle_data <- readRDS("./data_munging/rds/ccle_data_18Q3_g2pgenes.rds")
+saveRDS(gdsc_data, "./data_munging/rds/gdsc_data_18Q4_g2pgenes.rds", compress = "xz")
+```
+
+```{r}
+ccle_data <- readRDS("./data_munging/rds/ccle_data_18Q4_g2pgenes.rds")
 ccle_data_ptmuts <- filter(ccle_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
@@
 
-ctrp_data <- readRDS("./data_munging/rds/ctrp_data_18Q3_g2pgenes.rds")
+ctrp_data <- readRDS("./data_munging/rds/ctrp_data_18Q4_g2pgenes.rds")
 ctrp_data_ptmuts <- filter(ctrp_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
@@
 
-gdsc_data <- readRDS("./data_munging/rds/gdsc_data_18Q3_g2pgenes.rds")
+gdsc_data <- readRDS("./data_munging/rds/gdsc_data_18Q4_g2pgenes.rds")
 gdsc_data_ptmuts <- filter(gdsc_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
@@
 
-```{r, eval=TRUE}
+```{r, eval=FALSE}
 crispr_signif_g2p_gene <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol"), data = crispr_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
@@
 
-```{r, eval=TRUE}
+```{r, eval=FALSE}
 # G2P drug-gene associations only
-ccle_signif_g2p <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene", data = ccle_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
+ccle_signif_g2p <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene", data = ccle_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
 ccle_signif_g2p <- adj_signif(ccle_signif_g2p)
@@
 # Grid comparisons of G2P drugs and genes
-ccle_signif_g2p_grid <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "Drug"), data = ccle_data_g2p_grid, method = "wilcox.test", p.adjust.method = "BH")
+ccle_signif_g2p_grid <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "Drug"), data = ccle_data_g2p_grid, method = "wilcox.test", p.adjust.method = "BH")
 ccle_signif_g2p_grid <- adj_signif(ccle_signif_g2p_grid)
@@
 
-```{r, eval=TRUE}
+```{r, eval=FALSE}
 ccle_signif_g2p_lineage <- lapply(unique(ccle_data_g2p_grid$Drug), WilcoxonByDrug, dataset = ccle_data_g2p_grid, data_name = "ccle", grouping_var = "lineage")
@@
 ```{r, eval=FALSE}
-ctrp_signif_g2p <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene", data = ctrp_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
+ctrp_signif_g2p <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene", data = ctrp_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
 ctrp_signif_g2p <- adj_signif(ctrp_signif_g2p)
@@
 # Grid comparisons of G2P drugs and genes
-ctrp_signif_g2p_grid <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "Drug"), data = ctrp_data_g2p_grid, method = "wilcox.test", p.adjust.method = "BH")
+ctrp_signif_g2p_grid <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "Drug"), data = ctrp_data_g2p_grid, method = "wilcox.test", p.adjust.method = "BH")
 ctrp_signif_g2p_grid <- adj_signif(ctrp_signif_g2p_grid)
@@
 
-```{r, eval=FALSE}
+```{r}
 ctrp_signif_g2p_lineage <- readRDS("./data_munging/rds/ctrp_signif_g2p_lineage.rds")
@@
 ```{r, eval=FALSE}
-gdsc_signif_g2p <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene", data = gdsc_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
+gdsc_signif_g2p <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene", data = gdsc_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
 gdsc_signif_g2p <- adj_signif(gdsc_signif_g2p)
@@
 # Grid comparisons of G2P drugs and genes
-gdsc_signif_g2p_grid <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "Drug"), data = gdsc_data_g2p_grid, method = "wilcox.test", p.adjust.method = "BH")
+gdsc_signif_g2p_grid <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "Drug"), data = gdsc_data_g2p_grid, method = "wilcox.test", p.adjust.method = "BH")
 gdsc_signif_g2p_grid <- adj_signif(gdsc_signif_g2p_grid)
@@
 
-```{r, eval=FALSE}
+```{r}
 gdsc_signif_g2p_lineage <- readRDS("./data_munging/rds/gdsc_signif_g2p_lineage.rds")
@@
   scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
-  geom_text_repel(data = subset(g2p_druggene_all_summ, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
+  geom_text_repel(data = subset(g2p_druggene_all_summ, InG2P == "Yes" & n > 30), size = 3, segment.size = 0.2, segment.color = "grey50") +
   geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = 0.5, y = 110, label = Test_Results_p)) +
-  labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations", color = "Does the drug-gene combination have level A G2P indication?") +
+  labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations") +
   theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
@@
   geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = 0.5, y = 110, label = Test_Results_p)) +
-  labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations", color = "Does the drug-gene combination have level A G2P indication?") +
+  labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations") +
   theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())

### 2018-11-16 manuscript.Rmd
update lineage plots, make pngs for Adam

@@
 
-## Make G2P lineage p-value plotly
+## Make G2P lineage mutation status plotly
 ```{r}
@@
     scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+    geom_text_repel(data = subset(use_data, InG2P == "Yes"), mapping = aes(x = p, y = n, label = Drug_Gene), size = 3, segment.size = 0.2, segment.color = "grey50") +
     geom_text(data = summ_text, mapping = aes(x = 0.5, y = y_value, label = Test_Results_p), nudge_y = 0.1) +
@@
     coord_flip() +
-    labs(x = "Level A G2P\nassociation") +
+    labs(x = "In G2P?", title = toupper(lineage_name)) +
     theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
 
-  plot <- subplot(plot_box, plot_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(title = lineage_name, margin = list(t = 75, l = 75), xaxis5 = list(title = "Gene-drug association p-value between mutation groups"), yaxis = list(title = "Level A G2P\nassociation", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
-
-  saveWidgetFix(widget = plot, file = paste0("./plots_18Q3/manuscript/plotlys_p_by_lineage/", lineage_name, "_g2p_evidence_p_plotly.html"))
+  plot <- subplot(plot_box, plot_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(title = toupper(lineage_name), margin = list(t = 75, l = 75), xaxis5 = list(title = "Gene-drug association p-value between mutation groups"), yaxis = list(title = "Level A G2P\nassociation", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
+
+  saveWidgetFix(widget = plot, file = paste0("./plots_18Q3/manuscript/plotlys_mut_by_lineage/", lineage_name, "_mut_plotly.html"))
+
+  plot_point <- ggplot_gtable(ggplot_build(plot_point))
+  plot_box <- ggplot_gtable(ggplot_build(plot_box))
+  p_maxWidth <-  grid::unit.pmax(plot_point$widths, plot_box$widths)
+  plot_point$widths <- as.list(p_maxWidth)
+  plot_box$widths <- as.list(p_maxWidth)
+
+  mut_plot <- cowplot::plot_grid(plot_box,
+                     plot_point,
+                     nrow = 2,
+                     rel_heights = c(1, 4))
+  ggsave(paste0("./plots_18Q3/manuscript/pngs_mut_by_lineage/", lineage_name, "_mut_plot.png"), mut_plot, device = "png", dpi = 450, width = 12, height = 6, units =   "in")
+
   return(summ_text)
@@
       scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+      geom_text_repel(data = subset(use_data, InG2P == "Yes"), aes(label = Drug_Gene, x = Pearson_GE_Abs, y = n), size = 3, segment.size = 0.2, segment.color = "grey50") +
       geom_text(data = summ_text, mapping = aes(x = 0.5, y = y_value_ge, label = Test_Results_GE), nudge_y = 1) +
-      labs(y = "Number of level A G2P associations") +
+      labs(y = "Number of level A G2P associations", x = "Pearson correlation coefficient between drug-gene AUC and gene expression") +
       theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
@@
       coord_flip() +
+      labs(x = "In G2P?", title = toupper(lineage)) +
       theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
@@
     print("Gene expression plotly: DONE")
-  }
-  else if(sum(!is.na(use_data$Pearson_GE_Abs)) == 0) { print("Gene expression plotly: None") }
+
+    png_ge_point <- ggplot_gtable(ggplot_build(plot_ge_point))
+    png_ge_box <- ggplot_gtable(ggplot_build(plot_ge_box))
+    p_maxWidth <-  grid::unit.pmax(png_ge_point$widths, png_ge_box$widths)
+    png_ge_point$widths <- as.list(p_maxWidth)
+    png_ge_box$widths <- as.list(p_maxWidth)
+
+    png_ge <- cowplot::plot_grid(png_ge_box, png_ge_point, nrow = 2, rel_heights = c(1, 4))
+    png_ge
+    ggsave(paste0("./plots_18Q3/manuscript/pngs_ge_by_lineage/", lineage, "_ge_plot.png"), png_ge, device = "png", dpi = 450, width = 12, height = 6, units = "in")
+    print("Gene expression plot: DONE")
+  }
+  else if(sum(!is.na(use_data$Pearson_GE_Abs)) == 0) { print("Gene expression plots: None") }
 
@@
       scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+      geom_text_repel(data = subset(use_data, InG2P == "Yes"), aes(label = Drug_Gene, x = Pearson_CN_Abs, y = n), size = 3, segment.size = 0.2, segment.color = "grey50") +
       geom_text(data = summ_text, mapping = aes(x = 0.5, y = y_value_cn, label = Test_Results_CN), nudge_y = 1) +
-      labs(y = "Number of level A G2P associations") +
+      labs(y = "Number of level A G2P associations", x = "Pearson correlation coefficient between drug-gene AUC and copy number") +
       theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
@@
     print("Copy number plotly: DONE")
-  }
-  else if(sum(!is.na(use_data$Pearson_CN_Abs)) == 0) { print("Copy number plotly: None") }
+
+    png_cn_point <- ggplot_gtable(ggplot_build(plot_cn_point))
+    png_cn_box <- ggplot_gtable(ggplot_build(plot_cn_box))
+    p_maxWidth <-  grid::unit.pmax(png_cn_point$widths, png_cn_box$widths)
+    png_cn_point$widths <- as.list(p_maxWidth)
+    png_cn_box$widths <- as.list(p_maxWidth)
+
+    png_cn <- cowplot::plot_grid(png_cn_box, png_cn_point, nrow = 2, rel_heights = c(1, 4))
+    png_cn
+    ggsave(paste0("./plots_18Q3/manuscript/pngs_cn_by_lineage/", lineage, "_cn_plot.png"), png_cn, device = "png", dpi = 450, width = 12, height = 6, units = "in")
+    print("Copy number plot: DONE")
+  }
+  else if(sum(!is.na(use_data$Pearson_CN_Abs)) == 0) { print("Copy number plots: None") }
 
@@
 
-g2p_drug_genes <- as.character(unique(g2p$Drug_Gene[!is.na(g2p$Drug_Gene)]))
+g2p_drug_genes <- unique(g2p$Drug_Gene[!is.na(g2p$Drug_Gene)])
 g2p_genes <- unique(sapply(strsplit(g2p_drug_genes, "_", fixed = TRUE), function(x) x[2]))
@@
 ccle <- merge(drug_meta, ccle, by = "CID")
-ccle_melt <- melt(ccle, id.vars = c("CID", "Drug"), measure.vars = colnames(ccle)[3:ncol(ccle)], variable.name = "accession_id", value.name = "AUC")
+ccle_melt <- melt(ccle, id.vars = c("CID", "Drug"), measure.vars = colnames(ccle)[3:ncol(ccle)], variable.name = "accession_id", value.name = "ActArea")
 ccle_grid <- expand.grid("accession_id" = unique(ccle_melt$accession_id), "Hugo_Symbol" = g2p_genes)
@@
 ccle_data$Hugo_Symbol <- factor(ccle_data$Hugo_Symbol)
-ccle_data$AUC <- as.numeric(ccle_data$AUC)
+ccle_data$ActArea <- as.numeric(ccle_data$ActArea)
 # CCLE AUC is actually AOC
@@
 # get AUC by 1 - AOC
-ccle_data$AUC_transform <- 1 - (ccle_data$AUC / 8)
-ccle_data$AUC_zscore <- (ccle_data$AUC_transform - mean(ccle_data$AUC_transform)) / sd(ccle_data$AUC_transform)
+ccle_data$AUC <- 1 - (ccle_data$ActArea / 8)
+ccle_data <- filter(ccle_data, !is.na(ccle_data$AUC))
+ccle_data$AUC_zscore <- (ccle_data$AUC - mean(ccle_data$AUC)) / sd(ccle_data$AUC)
 ccle_data$Color_Nonsilent <- ifelse(ccle_data$Mutation_Status_Nonsilent == "Wildtype", "palegreen3", "springgreen4")
 ccle_data$Color_Nonsilent <- factor(ccle_data$Color_Nonsilent)
-ccle_data <- filter(ccle_data, !is.na(ccle_data$AUC))
 ccle_data$Drug_Gene <- paste0(ccle_data$Drug, "_", ccle_data$Hugo_Symbol)
@@
 ctrp_data$AUC <- as.numeric(ctrp_data$AUC)
+ctrp_data <- filter(ctrp_data, !is.na(ctrp_data$AUC))
 ctrp_data$AUC_zscore <- (ctrp_data$AUC - mean(ctrp_data$AUC)) / sd(ctrp_data$AUC)
@@
 ctrp_data$Color_Nonsilent <- factor(ctrp_data$Color_Nonsilent)
-ctrp_data <- filter(ctrp_data, !is.na(ctrp_data$AUC))
 ctrp_data$Drug_Gene <- paste0(ctrp_data$Drug, "_", ctrp_data$Hugo_Symbol)
@@
 gdsc_data$AUC <- as.numeric(gdsc_data$AUC)
+gdsc_data <- filter(gdsc_data, !is.na(gdsc_data$AUC))
 gdsc_data$AUC_zscore <- (gdsc_data$AUC - mean(gdsc_data$AUC)) / sd(gdsc_data$AUC)
@@
 gdsc_data$Color_Nonsilent <- factor(gdsc_data$Color_Nonsilent)
-gdsc_data <- filter(gdsc_data, !is.na(gdsc_data$AUC))
 gdsc_data$Drug_Gene <- paste0(gdsc_data$Drug, "_", gdsc_data$Hugo_Symbol)
@@
 # ggsave("./plots_18Q3/manuscript/g2p_druggene_p_summ_plot.png", g2p_druggene_p_summ_plot, device = "png", dpi = 450, width = 8, height = 4, units = "in")
+```
+
+```
+for_dan <- with(g2p_druggene_p_summ, cbind(n, CCLE, CTRP, GDSC, colsplit(Drug_Gene, pattern = "_", names = c("Drug", "Hugo_Symbol"))))
+
+write.table(for_dan, file = "~/Desktop/for_dan.tsv", sep = "\t")
 ```
@@
   facet_wrap(~ Dataset) +
-  geom_point(mapping = aes(label = Drug_Gene, fill = InG2P, color = InG2P, shape = Pearson_GE_Sign, x = Pearson_GE_Abs, y = n), alpha = 0.5, size = 1.25) +
+  geom_point(mapping = aes(label = Drug_Gene, fill = InG2P, color = InG2P, shape = Pearson_CN_Sign, x = Pearson_CN_Abs, y = n), alpha = 0.5, size = 1.25) +
   scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
@@
   geom_text(data = g2p_druggene_pearson_text, mapping = aes(x = 0.3, y = 110, label = Test_Results_GE)) +
-  labs(x = "Pearson correlation coefficient between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +
+  labs(x = "Pearson correlation coefficient between drug-gene AUC and copy number", y = "Number of level A G2P associations") +
   theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
@@
   facet_wrap(~ Dataset) +
-  geom_violin(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.5) +
-  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
+  geom_violin(mapping = aes(color = InG2P, y = Pearson_CN_Abs, x = InG2P), alpha = 0.5) +
+  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_CN_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
   scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
@@
 
-plot <- subplot(plot_cn_box, plot_cn_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and gene expression"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
+plot <- subplot(plot_cn_box, plot_cn_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and copy number"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
 
@@
 
-knitr::kable(g2p_druggenelin_p_ttest_res_list, caption = "GDSC: T-test results for level A G2P drug-gene associations across lineages") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(g2p_druggenelin_p_ttest_res_list, caption = "Mutation status: T-test results for level A G2P drug-gene associations across lineages") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
+```{r}
+signif_all_lin <- readRDS("./data_munging/rds/signif_all_lin.rds")
+```
+
 ```{r, results='hide', eval=FALSE}
-signif_all_lin <- readRDS("./data_munging/rds/signif_all_lin.rds")
 druggenelin_pearson_ttest_res <- lapply(as.character(unique(signif_all_lin$group_general_lineage_name)), PearsonPlotlyByLineage)
@@
 knitr::kable(druggenelin_pearson_ttest_res_list[order(druggenelin_pearson_ttest_res_list$p_value_CN), c("Dataset", "group_general_lineage_name", "t_statistic_CN", "df_CN", "p_value_CN")], caption = "Copy number: T-test results for level A G2P drug-gene/gene expression associations across lineages") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+### All
+
+```{r fig.height=20, fig.width=12}
+all_druggenelin_mut <- g2p_druggenelin_all_summ
+all_druggenelin_mut$Sign <- "None"
+all_druggenelin_mut$Measure <- "Mutation Status"
+colnames(all_druggenelin_mut)[colnames(all_druggenelin_mut) == "p"] <- "Statistic"
+
+all_druggenelin_ge <- select(signif_all_lin, Drug_Gene, group_general_lineage_name, n, Pearson_GE_Abs, InG2P, Dataset, Pearson_GE_Sign)
+all_druggenelin_ge$Measure <- "Gene Expression"
+colnames(all_druggenelin_ge)[colnames(all_druggenelin_ge) == "Pearson_GE_Abs"] <- "Statistic"
+colnames(all_druggenelin_ge)[colnames(all_druggenelin_ge) == "Pearson_GE_Sign"] <- "Sign"
+
+all_druggenelin_cn <- select(signif_all_lin, Drug_Gene, group_general_lineage_name, n, Pearson_CN_Abs, InG2P, Dataset, Pearson_CN_Sign)
+all_druggenelin_cn$Measure <- "Copy Number"
+colnames(all_druggenelin_cn)[colnames(all_druggenelin_cn) == "Pearson_CN_Abs"] <- "Statistic"
+colnames(all_druggenelin_cn)[colnames(all_druggenelin_cn) == "Pearson_CN_Sign"] <- "Sign"
+
+all_druggenelin_summ <- rbind(all_druggenelin_mut, all_druggenelin_ge, all_druggenelin_cn)
+all_druggenelin_summ$Sign <- ifelse(is.na(all_druggenelin_summ$Sign), "None", all_druggenelin_summ$Sign)
+
+all_druggenelin_summ_plot <- ggplot(data = all_druggenelin_summ, aes(x = InG2P, y = Statistic)) +
+  facet_grid(group_general_lineage_name ~ Measure * Dataset) +
+  geom_jitter(mapping = aes(shape = Sign, fill = InG2P, color = InG2P), width = 0.4, alpha = 0.5, size = 1) +
+  geom_boxplot(width = 0.25, fill = NA, outlier.shape = NA) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_shape_manual(values = c(25, 24, 4), labels = c("Negative", "Positive", "NA")) +
+  theme(legend.position = "top") +
+  guides(color = FALSE, fill = FALSE)
+
+ggsave("./plots_18Q3/manuscript/all_druggenelin_summ_plot.png", all_druggenelin_summ_plot, device = "png", dpi = 450, width = 12, height = 40, units = "in")
+```
+
+```
+plot_cn_box <- ggplot(data = g2p_druggene_pearson) +
+  facet_wrap(~ Dataset) +
+  geom_violin(mapping = aes(color = InG2P, y = Pearson_CN_Abs, x = InG2P), alpha = 0.5) +
+  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_CN_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  coord_flip() +
+  labs(x = "In G2P?") +
+  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
 ```

### 2018-11-21 manuscript.Rmd
updated all signif tests w/ factored mut status

@@
     ccle_lin_p_ttest <- t.test(use_data_ccle$p ~ use_data_ccle$InG2P)
-    ccle_lin_p_ttest_res <- paste0("t = ", round(ccle_lin_p_ttest$statistic, 3), ", df = ", round(ccle_lin_p_ttest$parameter, 3), ", p = ", round(ccle_lin_p_ttest$p.value, 3))
+    ccle_lin_p_ttest_res <- paste0("t(", round(ccle_lin_p_ttest$parameter, 1), ") = ", round(ccle_lin_p_ttest$statistic, 2), ", p = ", round(ccle_lin_p_ttest$p.value, 3))
   }
@@
     ctrp_lin_p_ttest <- t.test(use_data_ctrp$p ~ use_data_ctrp$InG2P)
-    ctrp_lin_p_ttest_res <- paste0("t = ", round(ctrp_lin_p_ttest$statistic, 3), ", df = ", round(ctrp_lin_p_ttest$parameter, 3), ", p = ", round(ctrp_lin_p_ttest$p.value, 3))
+    ctrp_lin_p_ttest_res <- paste0("t(", round(ctrp_lin_p_ttest$parameter, 1), ") = ", round(ctrp_lin_p_ttest$statistic, 2), ", p = ", round(ctrp_lin_p_ttest$p.value, 3))
   }
@@
     gdsc_lin_p_ttest <- t.test(use_data_gdsc$p ~ use_data_gdsc$InG2P)
-    gdsc_lin_p_ttest_res <- paste0("t = ", round(gdsc_lin_p_ttest$statistic, 3), ", df = ", round(gdsc_lin_p_ttest$parameter, 3), ", p = ", round(gdsc_lin_p_ttest$p.value, 3))
+    gdsc_lin_p_ttest_res <- paste0("t(", round(gdsc_lin_p_ttest$parameter, 1), ") = ", round(gdsc_lin_p_ttest$statistic, 2), ", p = ", round(gdsc_lin_p_ttest$p.value, 3))
   }
@@
 
-  saveWidgetFix(widget = plot, file = paste0("./plots_18Q3/manuscript/plotlys_mut_by_lineage/", lineage_name, "_mut_plotly.html"))
+  saveWidgetFix(widget = plot, file = paste0("./plots/manuscript/plotlys_mut_by_lineage/", lineage_name, "_mut_plotly.html"))
 
@@
                      rel_heights = c(1, 4))
-  ggsave(paste0("./plots_18Q3/manuscript/pngs_mut_by_lineage/", lineage_name, "_mut_plot.png"), mut_plot, device = "png", dpi = 450, width = 12, height = 6, units =   "in")
+  ggsave(paste0("./plots/manuscript/pngs_mut_by_lineage/", lineage_name, "_mut_plot.png"), mut_plot, device = "png", dpi = 450, width = 12, height = 6, units =   "in")
 
@@
     ccle_ge_ttest <- t.test(use_data_ccle$Pearson_GE_Abs ~ use_data_ccle$InG2P)
-    ccle_ge_res <- paste0("t = ", round(ccle_ge_ttest$statistic, 3), ", df = ", round(ccle_ge_ttest$parameter, 3), ", p = ", round(ccle_ge_ttest$p.value, 3))
+    ccle_ge_res <- paste0("t(", round(ccle_ge_ttest$parameter, 1), ") = ", round(ccle_ge_ttest$statistic, 2), ", p = ", round(ccle_ge_ttest$p.value, 3))
   }
@@
     ccle_cn_ttest <- t.test(use_data_ccle$Pearson_CN_Abs ~ use_data_ccle$InG2P)
-    ccle_cn_res <- paste0("t = ", round(ccle_cn_ttest$statistic, 3), ", df = ", round(ccle_cn_ttest$parameter, 3), ", p = ", round(ccle_cn_ttest$p.value, 3))
+    ccle_cn_res <- paste0("t(", round(ccle_cn_ttest$parameter, 1), ") = ", round(ccle_cn_ttest$statistic, 2), ", p = ", round(ccle_cn_ttest$p.value, 3))
   }
@@
     ctrp_ge_ttest <- t.test(use_data_ctrp$Pearson_GE_Abs ~ use_data_ctrp$InG2P)
-    ctrp_ge_res <- paste0("t = ", round(ctrp_ge_ttest$statistic, 3), ", df = ", round(ctrp_ge_ttest$parameter, 3), ", p = ", round(ctrp_ge_ttest$p.value, 3))
+    ctrp_ge_res <- paste0("t(", round(ctrp_ge_ttest$parameter, 1), ") = ", round(ctrp_ge_ttest$statistic, 2), ", p = ", round(ctrp_ge_ttest$p.value, 3))
   }
@@
     ctrp_cn_ttest <- t.test(use_data_ctrp$Pearson_CN_Abs ~ use_data_ctrp$InG2P)
-    ctrp_cn_res <- paste0("t = ", round(ctrp_cn_ttest$statistic, 3), ", df = ", round(ctrp_cn_ttest$parameter, 3), ", p = ", round(ctrp_cn_ttest$p.value, 3))
+    ctrp_cn_res <- paste0("t(", round(ctrp_cn_ttest$parameter, 1), ") = ", round(ctrp_cn_ttest$statistic, 2), ", p = ", round(ctrp_cn_ttest$p.value, 3))
   }
@@
     gdsc_ge_ttest <- t.test(use_data_gdsc$Pearson_GE_Abs ~ use_data_gdsc$InG2P)
-    gdsc_ge_res <- paste0("t = ", round(gdsc_ge_ttest$statistic, 3), ", df = ", round(gdsc_ge_ttest$parameter, 3), ", p = ", round(gdsc_ge_ttest$p.value, 3))
+    gdsc_ge_res <- paste0("t(", round(gdsc_ge_ttest$parameter, 1), ") = ", round(gdsc_ge_ttest$statistic, 2), ", p = ", round(gdsc_ge_ttest$p.value, 3))
   }
@@
     gdsc_cn_ttest <- t.test(use_data_gdsc$Pearson_CN_Abs ~ use_data_gdsc$InG2P)
-    gdsc_cn_res <- paste0("t = ", round(gdsc_cn_ttest$statistic, 3), ", df = ", round(gdsc_cn_ttest$parameter, 3), ", p = ", round(gdsc_cn_ttest$p.value, 3))
+    gdsc_cn_res <- paste0("t(", round(gdsc_cn_ttest$parameter, 1), ") = ", round(gdsc_cn_ttest$statistic, 2), ", p = ", round(gdsc_cn_ttest$p.value, 3))
   }
@@
                       yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
-    saveWidgetFix(widget = plot_ge, file = paste0("./plots_18Q3/manuscript/plotlys_ge_by_lineage/", lineage, "_ge_plotly.html"))
+    saveWidgetFix(widget = plot_ge, file = paste0("./plots/manuscript/plotlys_ge_by_lineage/", lineage, "_ge_plotly.html"))
     print("Gene expression plotly: DONE")
@@
     png_ge
-    ggsave(paste0("./plots_18Q3/manuscript/pngs_ge_by_lineage/", lineage, "_ge_plot.png"), png_ge, device = "png", dpi = 450, width = 12, height = 6, units = "in")
+    ggsave(paste0("./plots/manuscript/pngs_ge_by_lineage/", lineage, "_ge_plot.png"), png_ge, device = "png", dpi = 450, width = 12, height = 6, units = "in")
     print("Gene expression plot: DONE")
@@
                       yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
-    saveWidgetFix(widget = plot_cn, file = paste0("./plots_18Q3/manuscript/plotlys_cn_by_lineage/", lineage, "_cn_plotly.html"))
+    saveWidgetFix(widget = plot_cn, file = paste0("./plots/manuscript/plotlys_cn_by_lineage/", lineage, "_cn_plotly.html"))
     print("Copy number plotly: DONE")
@@
     png_cn
-    ggsave(paste0("./plots_18Q3/manuscript/pngs_cn_by_lineage/", lineage, "_cn_plot.png"), png_cn, device = "png", dpi = 450, width = 12, height = 6, units = "in")
+    ggsave(paste0("./plots/manuscript/pngs_cn_by_lineage/", lineage, "_cn_plot.png"), png_cn, device = "png", dpi = 450, width = 12, height = 6, units = "in")
     print("Copy number plot: DONE")
@@
 
-```{r, eval=FALSE}
-maf_df <- readRDS("./data_munging/rds/maf_df_18Q4.rds")
-```
-
 ### CCLE copy number file
@@
 saveRDS(cn_melt, "./data_munging/rds/cn_melt_18Q4.rds", compress = "xz")
-```
-
-```{r, eval=FALSE}
-cn_melt <- readRDS("./data_munging/rds/cn_melt_18Q4.rds")
 ```
@@
 
-```{r, eval=FALSE}
-ge_melt_18Q3 <- readRDS("./../htscreen_lineages_giant_files/ge_melt_18Q3.rds")
-```
-
 18Q4, CCLE RNAseq gene expression data (log2(TPM+1)):
@@
 saveRDS(ge_melt_18Q4, "./data_munging/rds/ge_melt_18Q4.rds", compress = "xz")
-```
-
-```{r, eval=FALSE}
-ge_melt_18Q4 <- readRDS("./data_munging/rds/ge_melt_18Q4.rds")
 ```
@@
 g2p_genes <- c("EGFR", "KRAS", "ERBB2", "ERBB3", "MET", "ALK", "ROS1", "PDGFRA", "ABL1", "KIT", "PDGFRB", "PDGFB", "BRAF", "G6PD", "RET", "BRCA1", "BRCA2", "UGT1A1", "TSC1", "TSC2", "AKT1", "IDH2", "DPYD", "ESR1", "CYP19A1", "TPMT", "FLT3", "NPM1", "DNMT3A", "PML", "PTCH1", "JAK2", "MYD88", "MGMT")
+```
+
+```{r, eval=FALSE}
+maf_df <- readRDS("./data_munging/rds/maf_df_18Q4.rds")
+cn_melt <- readRDS("./data_munging/rds/cn_melt_18Q4.rds")
+ge_melt_18Q3 <- readRDS("./../htscreen_lineages_giant_files/ge_melt_18Q3.rds")
+# ge_melt_18Q4 <- readRDS("./data_munging/rds/ge_melt_18Q4.rds")
 ```
@@
 ge_crispr_18Q3 <- filter(ge_melt_18Q3, Hugo_Symbol %in% as.character(unique(crispr_melt$Hugo_Symbol)))
-ge_crispr_18Q4 <- filter(ge_melt_18Q4_test, Hugo_Symbol %in% as.character(unique(crispr_melt$Hugo_Symbol)))
+# ge_crispr_18Q4 <- filter(ge_melt_18Q4, Hugo_Symbol %in% as.character(unique(crispr_melt$Hugo_Symbol)))
 crispr_data <- merge(crispr_data, ge_crispr_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
-crispr_data <- merge(crispr_data, ge_crispr_18Q4, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
+# crispr_data <- merge(crispr_data, ge_crispr_18Q4, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
 saveRDS(crispr_data, "./../htscreen_lineages_giant_files/crispr_data_18Q4.rds", compress = "xz")
@@
 ccle_data_g2p <- filter(ccle_data_ptmuts, Drug_Gene %in% g2p_drug_genes)
+ccle_data_g2p$Mutation_Status_Nonsilent <- factor(ccle_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
 ctrp_data_g2p <- filter(ctrp_data_ptmuts, Drug_Gene %in% g2p_drug_genes)
+ctrp_data_g2p$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
 gdsc_data_g2p <- filter(gdsc_data_ptmuts, Drug_Gene %in% g2p_drug_genes)
+gdsc_data_g2p$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
 
@@
 ccle_data_g2p_grid <- filter(ccle_data_ptmuts, Drug %in% g2p_drugs)
+ccle_data_g2p_grid$Mutation_Status_Nonsilent <- factor(ccle_data_g2p_grid$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
 ctrp_data_g2p_grid <- filter(ctrp_data_ptmuts, Drug %in% g2p_drugs)
+ctrp_data_g2p_grid$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p_grid$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
 gdsc_data_g2p_grid <- filter(gdsc_data_ptmuts, Drug %in% g2p_drugs)
+gdsc_data_g2p_grid$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p_grid$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
 ```
@@
 
-# ggsave("./plots_18Q3/manuscript/crispr_data_signif_g2p_gene_plot.png", crispr_data_signif_g2p_gene_plot, width = 12, height = 7, units = "in")
+# ggsave("./plots/manuscript/crispr_data_signif_g2p_gene_plot.png", crispr_data_signif_g2p_gene_plot, width = 12, height = 7, units = "in")
 ```
@@
 
-# ggsave("./plots_18Q3/manuscript/crispr_crispr_data_signif_g2p_lineage_plot.png", crispr_data_signif_g2p_lineage_plot, width = 12, height = 15, units = "in")
+# ggsave("./plots/manuscript/crispr_crispr_data_signif_g2p_lineage_plot.png", crispr_data_signif_g2p_lineage_plot, width = 12, height = 15, units = "in")
 ```
@@
 ### G2P gene and drug
+```{r}
+test_ccle <- ccle_data_g2p_grid %>% group_by(Hugo_Symbol, Drug) %>% tally()
+```
 
@@
 # Grid comparisons of G2P drugs and genes
-ccle_signif_g2p_grid <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "Drug"), data = ccle_data_g2p_grid, method = "wilcox.test", p.adjust.method = "BH")
+ccle_signif_g2p_grid <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "Drug"), ref.group = "Wildtype", data = ccle_data_g2p_grid, method = "wilcox.test", p.adjust.method = "BH")
 ccle_signif_g2p_grid <- adj_signif(ccle_signif_g2p_grid)
@@
 g2p_druggene_p_tally <- g2p %>% group_by(Drug_Gene) %>% tally() %>% drop_na()
+range(g2p_druggene_p_tally$n)
+mean(g2p_druggene_p_tally$n)
+sd(g2p_druggene_p_tally$n)
+
+g2p_drug_tally <- g2p %>% group_by(Drug) %>% tally() %>% drop_na()
+range(g2p_drug_tally$n)
+mean(g2p_drug_tally$n)
+sd(g2p_drug_tally$n)
+
+g2p_gene_tally <- g2p %>% group_by(Gene) %>% tally() %>% drop_na()
+range(g2p_gene_tally$n)
+mean(g2p_gene_tally$n)
+sd(g2p_gene_tally$n)
 ```
@@
 g2p_druggene_p_summ_plot
-# ggsave("./plots_18Q3/manuscript/g2p_druggene_p_summ_plot.png", g2p_druggene_p_summ_plot, device = "png", dpi = 450, width = 8, height = 4, units = "in")
+# ggsave("./plots/manuscript/g2p_druggene_p_summ_plot.png", g2p_druggene_p_summ_plot, device = "png", dpi = 450, width = 8, height = 4, units = "in")
 ```
@@
 ccle_p_ttest <- t.test(ccle_druggene_summ$p ~ ccle_druggene_summ$InG2P)
-ccle_p_ttest_res <- paste0("t = ", round(ccle_p_ttest$statistic, 3), ", df = ", round(ccle_p_ttest$parameter, 3), ", p = ", round(ccle_p_ttest$p.value, 3))
+ccle_p_ttest_res <- paste0("t(", round(ccle_p_ttest$parameter, 1), ") = ", round(ccle_p_ttest$statistic, 2), ", p = ", round(ccle_p_ttest$p.value, 3))
 
@@
 ctrp_p_ttest <- t.test(ctrp_druggene_summ$p ~ ctrp_druggene_summ$InG2P)
-ctrp_p_ttest_res <- paste0("t = ", round(ctrp_p_ttest$statistic, 3), ", df = ", round(ctrp_p_ttest$parameter, 3), ", p = ", round(ctrp_p_ttest$p.value, 3))
+ctrp_p_ttest_res <- paste0("t(", round(ctrp_p_ttest$parameter, 1), ") = ", round(ctrp_p_ttest$statistic, 2), ", p = ", round(ctrp_p_ttest$p.value, 3))
 
@@
 gdsc_p_ttest <- t.test(gdsc_druggene_summ$p ~ gdsc_druggene_summ$InG2P)
-gdsc_p_ttest_res <- paste0("t = ", round(gdsc_p_ttest$statistic, 3), ", df = ", round(gdsc_p_ttest$parameter, 3), ", p = ", round(gdsc_p_ttest$p.value, 3))
+gdsc_p_ttest_res <- paste0("t(", round(gdsc_p_ttest$parameter, 1), ") = ", round(gdsc_p_ttest$statistic, 2), ", p = ", round(gdsc_p_ttest$p.value, 3))
 
@@
   scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
-  geom_text_repel(data = subset(g2p_druggene_all_summ, InG2P == "Yes" & n > 30), size = 3, segment.size = 0.2, segment.color = "grey50") +
-  geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = 0.5, y = 110, label = Test_Results_p)) +
+  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
+  geom_text_repel(data = subset(g2p_druggene_all_summ, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
+  geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = 0.5, y = 115, label = Test_Results_p)) +
   labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations") +
@@
 g2p_druggene_mut_plot
-# ggsave("./plots_18Q3/manuscript/g2p_druggene_mut_plot.png", g2p_druggene_mut_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
+ggsave("./plots/manuscript/g2p_druggene_mut_plot.png", g2p_druggene_mut_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
 ```
@@
   scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
-  geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = 0.5, y = 110, label = Test_Results_p)) +
+  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
+  geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = 0.5, y = 115, label = Test_Results_p)) +
   labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations") +
@@
 
-saveWidgetFix(widget = plot, file = "./plots_18Q3/manuscript/g2p_druggene_mut_plot.html")
+saveWidgetFix(widget = plot, file = "./plots/manuscript/g2p_druggene_mut_plot.html")
 ```
@@
 ccle_pearson_ttest_GE <- t.test(ccle_pearson_res$Pearson_Corr_GE ~ ccle_pearson_res$InG2P)
-ccle_pearson_ttest_res_GE <- paste0("t = ", round(ccle_pearson_ttest_GE$statistic, 3), ", df = ", round(ccle_pearson_ttest_GE$parameter, 3), ", p = ", round(ccle_pearson_ttest_GE$p.value, 3))
+ccle_pearson_ttest_res_GE <- paste0("t(", round(ccle_pearson_ttest_GE$parameter, 1), ") = ", round(ccle_pearson_ttest_GE$statistic, 2), ", p = ", round(ccle_pearson_ttest_GE$p.value, 3))
 ccle_pearson_ttest_CN <- t.test(ccle_pearson_res$Pearson_Corr_CN ~ ccle_pearson_res$InG2P)
-ccle_pearson_ttest_res_CN <- paste0("t = ", round(ccle_pearson_ttest_CN$statistic, 3), ", df = ", round(ccle_pearson_ttest_CN$parameter, 3), ", p = ", round(ccle_pearson_ttest_CN$p.value, 3))
+ccle_pearson_ttest_res_CN <- paste0("t(", round(ccle_pearson_ttest_CN$parameter, 1), ") = ", round(ccle_pearson_ttest_CN$statistic, 2), ", p = ", round(ccle_pearson_ttest_CN$p.value, 3))
 
@@
 ctrp_pearson_ttest_GE <- t.test(ctrp_pearson_res$Pearson_Corr_GE ~ ctrp_pearson_res$InG2P)
-ctrp_pearson_ttest_res_GE <- paste0("t = ", round(ctrp_pearson_ttest_GE$statistic, 3), ", df = ", round(ctrp_pearson_ttest_GE$parameter, 3), ", p = ", round(ctrp_pearson_ttest_GE$p.value, 3))
+ctrp_pearson_ttest_res_GE <- paste0("t(", round(ctrp_pearson_ttest_GE$parameter, 1), ") = ", round(ctrp_pearson_ttest_GE$statistic, 2), ", p = ", round(ctrp_pearson_ttest_GE$p.value, 3))
 ctrp_pearson_ttest_CN <- t.test(ctrp_pearson_res$Pearson_Corr_CN ~ ctrp_pearson_res$InG2P)
-ctrp_pearson_ttest_res_CN <- paste0("t = ", round(ctrp_pearson_ttest_CN$statistic, 3), ", df = ", round(ctrp_pearson_ttest_CN$parameter, 3), ", p = ", round(ctrp_pearson_ttest_CN$p.value, 3))
+ctrp_pearson_ttest_res_CN <- paste0("t(", round(ctrp_pearson_ttest_CN$parameter, 1), ") = ", round(ctrp_pearson_ttest_CN$statistic, 2), ", p = ", round(ctrp_pearson_ttest_CN$p.value, 3))
 
@@
 gdsc_pearson_ttest_GE <- t.test(gdsc_pearson_res$Pearson_Corr_GE ~ gdsc_pearson_res$InG2P)
-gdsc_pearson_ttest_res_GE <- paste0("t = ", round(gdsc_pearson_ttest_GE$statistic, 3), ", df = ", round(gdsc_pearson_ttest_GE$parameter, 3), ", p = ", round(gdsc_pearson_ttest_GE$p.value, 3))
+gdsc_pearson_ttest_res_GE <- paste0("t(", round(gdsc_pearson_ttest_GE$parameter, 1), ") = ", round(gdsc_pearson_ttest_GE$statistic, 2), ", p = ", round(gdsc_pearson_ttest_GE$p.value, 3))
 gdsc_pearson_ttest_CN <- t.test(gdsc_pearson_res$Pearson_Corr_CN ~ gdsc_pearson_res$InG2P)
-gdsc_pearson_ttest_res_CN <- paste0("t = ", round(gdsc_pearson_ttest_CN$statistic, 3), ", df = ", round(gdsc_pearson_ttest_CN$parameter, 3), ", p = ", round(gdsc_pearson_ttest_CN$p.value, 3))
+gdsc_pearson_ttest_res_CN <- paste0("t(", round(gdsc_pearson_ttest_CN$parameter, 1), ") = ", round(gdsc_pearson_ttest_CN$statistic, 2), ", p = ", round(gdsc_pearson_ttest_CN$p.value, 3))
 
@@
 Gene expression:
-```{r fig.height=5.5, fig.width=12}
+```{r fig.height=5, fig.width=12}
 plot_ge_point <- ggplot(data = g2p_druggene_pearson, aes(x = Pearson_GE_Abs, y = n, label = Drug_Gene)) +
@@
   scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
-  scale_x_continuous(breaks = pretty_breaks()) +
+  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
+  scale_x_continuous(breaks = seq(0, 0.65, by = 0.1), labels = seq(0, 0.65, by = 0.1)) +
+  coord_cartesian(xlim = c(0, 0.65)) +
   scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
   geom_text_repel(data = subset(g2p_druggene_pearson, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
-  geom_text(data = g2p_druggene_pearson_text, mapping = aes(x = 0.3, y = 110, label = Test_Results_GE)) +
+  geom_text(data = g2p_druggene_pearson_text, mapping = aes(x = 0.325, y = 115, label = Test_Results_GE)) +
+  labs(x = "Pearson correlation coefficient between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +
+  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
+  guides(color = FALSE, fill = FALSE, shape = FALSE)
+
+plot_ge_box <- ggplot(data = g2p_druggene_pearson) +
+  facet_wrap(~ Dataset) +
+  geom_violin(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.5) +
+  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
+  scale_y_continuous(breaks = seq(0, 0.65, by = 0.1), labels = seq(0, 0.65, by = 0.1)) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  coord_flip(ylim = c(0, 0.65)) +
+  labs(x = "In G2P?") +
+  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
+
+plot_ge_point <- ggplot_gtable(ggplot_build(plot_ge_point))
+plot_ge_box <- ggplot_gtable(ggplot_build(plot_ge_box))
+p_maxWidth <-  grid::unit.pmax(plot_ge_point$widths[2:3], plot_ge_box$widths[2:3])
+plot_ge_point$widths[2:3] <- p_maxWidth
+plot_ge_box$widths[2:3] <- p_maxWidth
+
+g2p_druggene_ge_plot <- cowplot::plot_grid(plot_ge_box, plot_ge_point, nrow = 2, rel_heights = c(1, 4))
+g2p_druggene_ge_plot
+# ggsave("./plots/manuscript/g2p_druggene_ge_plot.png", g2p_druggene_ge_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
+```
+
+```{r, eval=FALSE}
+plot_ge_point <- ggplot(data = g2p_druggene_pearson) +
+  facet_wrap(~ Dataset) +
+  geom_point(mapping = aes(label = Drug_Gene, fill = InG2P, color = InG2P, shape = Pearson_GE_Sign, x = Pearson_GE_Abs, y = n, size = Pearson_Pval_GE), alpha = 0.5, size = 1.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
+  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
+  scale_x_continuous(breaks = pretty_breaks()) +
+  geom_text(data = g2p_druggene_pearson_text, mapping = aes(x = 0.3, y = 115, label = Test_Results_GE)) +
   labs(x = "Pearson correlation coefficient between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +
@@
   guides(color = FALSE, fill = FALSE) +
-  labs(shape = "Direction of correlation:")
+  labs(shape = NULL)
 
@@
 
-plot_ge_point <- ggplot_gtable(ggplot_build(plot_ge_point))
-plot_ge_box <- ggplot_gtable(ggplot_build(plot_ge_box))
-p_maxWidth <-  grid::unit.pmax(plot_ge_point$widths, plot_ge_box$widths)
-plot_ge_point$widths <- as.list(p_maxWidth)
-plot_ge_box$widths <- as.list(p_maxWidth)
-
-g2p_druggene_ge_plot <- cowplot::plot_grid(plot_ge_box, plot_ge_point, nrow = 2, rel_heights = c(1, 4))
-g2p_druggene_ge_plot
-# ggsave("./plots_18Q3/manuscript/g2p_druggene_ge_plot.png", g2p_druggene_ge_plot, device = "png", dpi = 450, width = 12, height = 5.5, units = "in")
-```
-
-```{r, eval=FALSE}
-plot_ge_point <- ggplot(data = g2p_druggene_pearson) +
-  facet_wrap(~ Dataset) +
-  geom_point(mapping = aes(label = Drug_Gene, fill = InG2P, color = InG2P, shape = Pearson_GE_Sign, x = Pearson_GE_Abs, y = n, size = Pearson_Pval_GE), alpha = 0.5, size = 1.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
-  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
-  scale_x_continuous(breaks = pretty_breaks()) +
-  geom_text(data = g2p_druggene_pearson_text, mapping = aes(x = 0.3, y = 110, label = Test_Results_GE)) +
-  labs(x = "Pearson correlation coefficient between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +
-  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
-  guides(color = FALSE, fill = FALSE) +
-  labs(shape = NULL)
-
-plot_ge_box <- ggplot(data = g2p_druggene_pearson) +
-  facet_wrap(~ Dataset) +
-  geom_violin(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.5) +
-  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  coord_flip() +
-  labs(x = "In G2P?") +
-  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
 plot <- subplot(plot_ge_box, plot_ge_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and gene expression"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
 
-saveWidgetFix(widget = plot, file = "./plots_18Q3/manuscript/g2p_druggene_ge_plot.html")
+saveWidgetFix(widget = plot, file = "./plots/manuscript/g2p_druggene_ge_plot.html")
 ```
@@
   scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
-  scale_x_continuous(breaks = pretty_breaks()) +
+  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
+  scale_x_continuous(breaks = seq(0, 0.5, by = 0.1), labels = seq(0, 0.5, by = 0.1)) +
+  coord_cartesian(xlim = c(0, 0.5)) +
   scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
   geom_text_repel(data = subset(g2p_druggene_pearson, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
-  geom_text(data = g2p_druggene_pearson_text, mapping = aes(x = 0.3, y = 110, label = Test_Results_CN)) +
-  labs(x = "Pearson correlation coefficient between drug-gene AUC and copy number", y = "Number of level A G2P associations") +
+  geom_text(data = g2p_druggene_pearson_text, mapping = aes(x = 0.25, y = 115, label = Test_Results_CN)) +
+  labs(x = "Pearson correlation coefficient between drug-gene AUC and copy number", y = "Number of level A G2P associations", shape = "Direction of correlation:", color = "Level A G2P association:") +
   theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
-  guides(color = FALSE, fill = FALSE) +
-  labs(shape = "Direction of correlation:")
+  guides(color = guide_legend(override.aes = list(size = 4, shape = 15)), shape = guide_legend(override.aes = list(size = 3)), fill = FALSE)
 
@@
   geom_boxplot(mapping = aes(color = InG2P, y = Pearson_CN_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
+  scale_y_continuous(breaks = seq(0, 0.5, by = 0.1), labels = seq(0, 0.5, by = 0.1)) +
   scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  coord_flip() +
+  coord_flip(ylim = c(0, 0.5)) +
   labs(x = "In G2P?") +
@@
 g2p_druggene_cn_plot
-# ggsave("./plots_18Q3/manuscript/g2p_druggene_cn_plot.png", g2p_druggene_cn_plot, device = "png", dpi = 450, width = 12, height = 5.5, units = "in")
+# ggsave("./plots/manuscript/g2p_druggene_cn_plot.png", g2p_druggene_cn_plot, device = "png", dpi = 450, width = 12, height = 5.5, units = "in")
 ```
@@
   theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
-  guides(color = FALSE, fill = FALSE) +
+  guides(color = guide_legend(override.aes = list(size = 4, shape = 15)), shape = guide_legend(override.aes = list(size = 3)), fill = FALSE) +
   labs(shape = NULL)
@@
 
-saveWidgetFix(widget = plot, file = "./plots_18Q3/manuscript/g2p_druggene_cn_plot.html")
+saveWidgetFix(widget = plot, file = "./plots/manuscript/g2p_druggene_cn_plot.html")
 ```
@@
 
-ggsave("./plots_18Q3/manuscript/all_druggenelin_summ_plot.png", all_druggenelin_summ_plot, device = "png", dpi = 450, width = 12, height = 40, units = "in")
+ggsave("./plots/manuscript/all_druggenelin_summ_plot.png", all_druggenelin_summ_plot, device = "png", dpi = 450, width = 12, height = 40, units = "in")
 ```
@@
 
-# ggsave("./plots_18Q3/manuscript/crispr_data_g2p_plot.png", crispr_data_g2p_plot, device = "png", dpi = 450, width = 20, height = 5, units = "in")
+# ggsave("./plots/manuscript/crispr_data_g2p_plot.png", crispr_data_g2p_plot, device = "png", dpi = 450, width = 20, height = 5, units = "in")
 ```
@@
 ccle_g2p_drugboxplots_paths <- paste0(ccle_drugs, "_ccle_drugboxplots.png")
-pwalk(list(ccle_g2p_drugboxplots_paths, ccle_g2p_drugboxplots), ggsave, path = "./plots_18Q3/manuscript/ccle_g2p_drugboxplots", dpi = 450, width = 20, height = 5, units = "in")
+pwalk(list(ccle_g2p_drugboxplots_paths, ccle_g2p_drugboxplots), ggsave, path = "./plots/manuscript/ccle_g2p_drugboxplots", dpi = 450, width = 20, height = 5, units = "in")
 ```
@@
 ```{r, eval=FALSE}
-ccle_g2p_drugboxplots <- paste0(list.files("./plots_18Q3/manuscript/ccle_g2p_drugboxplots", full.names = TRUE))
-names(ccle_g2p_drugboxplots) <- str_replace_all(ccle_g2p_drugboxplots, c("_ccle_drugboxplots.png" = "", "./plots_18Q3/manuscript/ccle_g2p_drugboxplots/" = ""))
+ccle_g2p_drugboxplots <- paste0(list.files("./plots/manuscript/ccle_g2p_drugboxplots", full.names = TRUE))
+names(ccle_g2p_drugboxplots) <- str_replace_all(ccle_g2p_drugboxplots, c("_ccle_drugboxplots.png" = "", "./plots/manuscript/ccle_g2p_drugboxplots/" = ""))
 bsselect(ccle_g2p_drugboxplots, type = "img", live_search = TRUE, show_tick = TRUE, height = 100)
@@
 ctrp_g2p_drugboxplots_paths <- paste0(ctrp_drugs, "_ctrp_drugboxplots.png")
-pwalk(list(ctrp_g2p_drugboxplots_paths, ctrp_g2p_drugboxplots), ggsave, path = "./plots_18Q3/manuscript/ctrp_g2p_drugboxplots", dpi = 450, width = 20, height = 5, units = "in")
+pwalk(list(ctrp_g2p_drugboxplots_paths, ctrp_g2p_drugboxplots), ggsave, path = "./plots/manuscript/ctrp_g2p_drugboxplots", dpi = 450, width = 20, height = 5, units = "in")
 ```
@@
 ```{r, eval=FALSE}
-ctrp_g2p_drugboxplots <- paste0(list.files("./plots_18Q3/manuscript/ctrp_g2p_drugboxplots", full.names = TRUE))
-names(ctrp_g2p_drugboxplots) <- str_replace_all(ctrp_g2p_drugboxplots, c("_ctrp_drugboxplots.png" = "", "./plots_18Q3/manuscript/ctrp_g2p_drugboxplots/" = ""))
+ctrp_g2p_drugboxplots <- paste0(list.files("./plots/manuscript/ctrp_g2p_drugboxplots", full.names = TRUE))
+names(ctrp_g2p_drugboxplots) <- str_replace_all(ctrp_g2p_drugboxplots, c("_ctrp_drugboxplots.png" = "", "./plots/manuscript/ctrp_g2p_drugboxplots/" = ""))
 bsselect(ctrp_g2p_drugboxplots, type = "img", live_search = TRUE, show_tick = TRUE, height = 100)
@@
 gdsc_g2p_drugboxplots_paths <- paste0(gdsc_drugs, "_gdsc_drugboxplots.png")
-pwalk(list(gdsc_g2p_drugboxplots_paths, gdsc_g2p_drugboxplots), ggsave, path = "./plots_18Q3/manuscript/gdsc_g2p_drugboxplots", dpi = 450, width = 20, height = 5, units = "in")
+pwalk(list(gdsc_g2p_drugboxplots_paths, gdsc_g2p_drugboxplots), ggsave, path = "./plots/manuscript/gdsc_g2p_drugboxplots", dpi = 450, width = 20, height = 5, units = "in")
 ```
@@
 ```{r, eval=FALSE}
-gdsc_g2p_drugboxplots <- paste0(list.files("./plots_18Q3/manuscript/gdsc_g2p_drugboxplots", full.names = TRUE))
-names(gdsc_g2p_drugboxplots) <- str_replace_all(gdsc_g2p_drugboxplots, c("_gdsc_drugboxplots.png" = "", "./plots_18Q3/manuscript/gdsc_g2p_drugboxplots/" = ""))
+gdsc_g2p_drugboxplots <- paste0(list.files("./plots/manuscript/gdsc_g2p_drugboxplots", full.names = TRUE))
+names(gdsc_g2p_drugboxplots) <- str_replace_all(gdsc_g2p_drugboxplots, c("_gdsc_drugboxplots.png" = "", "./plots/manuscript/gdsc_g2p_drugboxplots/" = ""))
 bsselect(gdsc_g2p_drugboxplots, type = "img", live_search = TRUE, show_tick = TRUE, height = 100)
@@
 
-# ggsave("./plots_18Q3/manuscript/ccle_data_g2p_plot.png", ccle_data_g2p_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
+# ggsave("./plots/manuscript/ccle_data_g2p_plot.png", ccle_data_g2p_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
 ```
@@
 
-# ggsave("./plots_18Q3/manuscript/ctrp_data_g2p_plot.png", ctrp_data_g2p_plot, device = "png", dpi = 450, width = 12, height = 7, units = "in")
+# ggsave("./plots/manuscript/ctrp_data_g2p_plot.png", ctrp_data_g2p_plot, device = "png", dpi = 450, width = 12, height = 7, units = "in")
 ```
@@
 
-# ggsave("./plots_18Q3/manuscript/gdsc_data_g2p_plot.png", gdsc_data_g2p_plot, device = "png", dpi = 450, width = 12, height = 7, units = "in")
+# ggsave("./plots/manuscript/gdsc_data_g2p_plot.png", gdsc_data_g2p_plot, device = "png", dpi = 450, width = 12, height = 7, units = "in")
 ```
@@
 
-# ggsave("./plots_18Q3/manuscript/crispr_g2p_indications_plot_test.png", crispr_g2p_indications_plot, width = 12, height = 5, units = "in")
-# ggsave("./plots_18Q3/manuscript/crispr_g2p_indications_muts_plot_test.png", crispr_g2p_indications_muts_plot, width = 20, height = 5, units = "in")
+# ggsave("./plots/manuscript/crispr_g2p_indications_plot_test.png", crispr_g2p_indications_plot, width = 12, height = 5, units = "in")
+# ggsave("./plots/manuscript/crispr_g2p_indications_muts_plot_test.png", crispr_g2p_indications_muts_plot, width = 20, height = 5, units = "in")
 ```

### 2018-11-21 manuscript.Rmd
update rmd

@@
 knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
-
 # num_cores <- parallel::detectCores()
@@
 open .Renviron
-
 # Added following line to .Renviron:
@@
 }
-
 # WilcoxonByDrugAllGenes <- function(melt_file, grid_file, data_name) {
@@
   y_value <- ifelse(ticker == 3, 10, max(use_data$n) + 1)
-
   summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"),
@@
                           group_general_lineage_name = lineage_name)
-
   plot_point <- ggplot(data = use_data) +
@@
     theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
-
   plot_box <- ggplot(data = use_data) +
@@
     theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
   plot <- subplot(plot_box, plot_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(title = toupper(lineage_name), margin = list(t = 75, l = 75), xaxis5 = list(title = "Gene-drug association p-value between mutation groups"), yaxis = list(title = "Level A G2P\nassociation", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
-
   saveWidgetFix(widget = plot, file = paste0("./plots/manuscript/plotlys_mut_by_lineage/", lineage_name, "_mut_plotly.html"))
@@
 ccl_info$Primary.Disease <- gsub("Ewings", "Ewing's", ccl_info$Primary.Disease)
-
 # From figshare
@@
 colnames(maf_raw)[colnames(maf_raw) == "Tumor_Sample_Barcode"] <- "CCLE_Name"
-
 # Select columns
@@
 maf_df$Tumor_Seq_Allele1_Length <- nchar(as.character(maf_df$Tumor_Seq_Allele1))
-
 # Add Mutation_Status column
@@
 cn <- read.delim("./data_munging/18Q4/public_18Q4_gene_cn_20181115.csv.gz", sep = ",", check.names = FALSE, header = TRUE)
-
 # Remove Entrez gene IDs from colnames
@@
 colnames(cn) <- gsub(" .*", "", colnames(cn))
-
 # Melt
 cn_melt <- melt(data = cn, id.vars = "DepMap_ID", measure.vars = colnames(cn[2:ncol(cn)]), variable.name = "Hugo_Symbol", value.name = "CN")
-
 saveRDS(cn_melt, "./data_munging/rds/cn_melt_18Q4.rds", compress = "xz")
@@
 ge_18Q3 <- read.delim("./../htscreen_lineages_giant_files/CCLE_DepMap_18q3_RNAseq_RPKM_20180718.gct.gz", skip = 2, header = TRUE, sep = "\t", check.names = FALSE)
-
 # Edit columns
@@
 colnames(ge_18Q3)[1] <- "Hugo_Symbol"
-
 # Melt
@@
 ge_melt_18Q3$DepMap_ID <- gsub("\\(|\\)", "", ge_melt_18Q3$DepMap_ID)
-
 saveRDS(ge_melt_18Q3, "./../htscreen_lineages_giant_files/ge_melt_18Q3.rds", compress = "xz")
@@
 ge_18Q4 <- read.delim("./../htscreen_lineages_giant_files/CCLE_depMap_18Q4_TPM_v2_20181115.csv.gz", header = TRUE, sep = ",", check.names = FALSE)
-
 # Remove Entrez gene IDs from colnames
@@
 colnames(ge_18Q4)[1] <- "DepMap_ID"
-
 # Melt
@@
 ge_melt_18Q4 <- unique(ge_melt_18Q4)
-
 saveRDS(ge_melt_18Q4, "./data_munging/rds/ge_melt_18Q4.rds", compress = "xz")
@@
 g2p <- subset(g2p, grepl("^CID", g2p$DrugID))
-
 g2p_drug_genes <- unique(g2p$Drug_Gene[!is.na(g2p$Drug_Gene)])
@@
 g2p_drugs <- unique(sapply(strsplit(g2p_drug_genes, "_", fixed = TRUE), function(x) x[1]))
-
 g2p_genes
@@
 crispr_data <- readRDS("./../htscreen_lineages_giant_files/crispr_data_18Q4.rds")
-
 crispr_data_ptmuts <- filter(crispr_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
@@
 crispr_data_ptmuts <- filter(crispr_data_ptmuts, Keep_PtMut_Tests == TRUE)
-
 # Filter CRISPR for G2P genes in G2P
@@
 cn_filt <- filter(cn_melt, Hugo_Symbol %in% g2p_genes)
-
 # CCLE
@@
 saveRDS(ccle_data, "./data_munging/rds/ccle_data_18Q4_g2pgenes.rds", compress = "xz")
-
 # CTRP
@@
 saveRDS(ctrp_data, "./data_munging/rds/ctrp_data_18Q4_g2pgenes.rds", compress = "xz")
-
 # GDSC
@@
 ccle_data_ptmuts$Hugo_Symbol <- ordered(ccle_data_ptmuts$Hugo_Symbol, levels = g2p_genes)
-
 ctrp_data <- readRDS("./data_munging/rds/ctrp_data_18Q4_g2pgenes.rds")
@@
 ctrp_data_ptmuts$Hugo_Symbol <- ordered(ctrp_data_ptmuts$Hugo_Symbol, levels = g2p_genes)
-
 gdsc_data <- readRDS("./data_munging/rds/gdsc_data_18Q4_g2pgenes.rds")
@@
 gdsc_data_ptmuts$Hugo_Symbol <- ordered(gdsc_data_ptmuts$Hugo_Symbol, levels = g2p_genes)
-
 # Filter drug screen datasets for G2P drug-gene associations
@@
 gdsc_data_g2p$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-
 # Filter drug screen datasets for G2P drugs and genes
@@
 crispr_signif_g2p_gene <- readRDS("./data_munging/rds/crispr_signif_g2p_gene.rds")
-
 crispr_signif_g2p_20gene <- as.character(crispr_signif_g2p_gene$Hugo_Symbol[0:20])
-
 knitr::kable(crispr_signif_g2p_gene[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results for Level A point mutations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
@@
 crispr_data_signif_g2p_gene <- merge(crispr_data_signif_g2p_gene, crispr_data_signif_g2p_gene %>% group_by(Hugo_Symbol) %>% summarize(Text_y = max(Score)), by = "Hugo_Symbol")
-
 crispr_data_signif_g2p_gene_text <- unique(data.frame(p.signif = crispr_data_signif_g2p_gene$p.signif, p.signif.adj = crispr_data_signif_g2p_gene$p.signif.adj,  Hugo_Symbol = crispr_data_signif_g2p_gene$Hugo_Symbol, Text_y = crispr_data_signif_g2p_gene$Text_y))
-
 crispr_data_signif_g2p_gene_plot <- ggplot(data = crispr_data_signif_g2p_gene, aes(x = Mutation_Status_Nonsilent, y = Score)) +
@@
 crispr_data_signif_g2p_gene_plot
-
 # ggsave("./plots/manuscript/crispr_data_signif_g2p_gene_plot.png", crispr_data_signif_g2p_gene_plot, width = 12, height = 7, units = "in")
@@
 saveRDS(crispr_signif_g2p_lineage, "./data_munging/rds/crispr_signif_g2p_lineage.rds")
-
 # write.table(crispr_signif_g2p_lineage, file = "~/Desktop/crispr_signif_g2p_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
@@
 crispr_signif_g2p_lineage <- readRDS("./data_munging/rds/crispr_signif_g2p_lineage.rds")
-
 knitr::kable(filter(crispr_signif_g2p_lineage, p < 0.1)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant vs wildtype cell lines by lineage, p < 0.1 (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
@@
 crispr_data_signif_g2p_lineage <- merge(crispr_data_signif_g2p_lineage, crispr_data_signif_g2p_lineage %>% group_by(Hugo_Symbol) %>% summarize(Text_y = max(Score)), by = "Hugo_Symbol")
-
 crispr_data_signif_g2p_lineage_text <- unique(data.frame(p.signif = crispr_data_signif_g2p_lineage$p.signif, p.signif.adj = crispr_data_signif_g2p_lineage$p.signif.adj,  group_general_lineage_name = crispr_data_signif_g2p_lineage$group_general_lineage_name, Hugo_Symbol = crispr_data_signif_g2p_lineage$Hugo_Symbol, Text_y = crispr_data_signif_g2p_lineage$Text_y))
-
 crispr_data_signif_g2p_lineage_plot <- ggplot(data = crispr_data_signif_g2p_lineage, aes(x = group_general_lineage_name, y = Score)) +
@@
 crispr_data_signif_g2p_lineage_plot
-
 # ggsave("./plots/manuscript/crispr_crispr_data_signif_g2p_lineage_plot.png", crispr_data_signif_g2p_lineage_plot, width = 12, height = 15, units = "in")
@@
 # write.table(crispr_data_signif_g2p_lineage_summ, file = "~/Desktop/crispr_data_signif_g2p_lineage_summ_20181005.tsv", quote = FALSE, sep = "\t")
-
 knitr::kable(crispr_data_signif_g2p_lineage_summ, caption = "Mutant/Wildtype counts for gene-lineage combinations") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
@@
 saveRDS(ccle_signif_g2p, "./data_munging/rds/ccle_signif_g2p_gene.rds")
-
 # Grid comparisons of G2P drugs and genes
@@
 ccle_signif_g2p <- readRDS("./data_munging/rds/ccle_signif_g2p_gene.rds")
-
 knitr::kable(ccle_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-
 ccle_signif_g2p_grid <- readRDS("./data_munging/rds/ccle_signif_g2p_grid.rds")
-
 knitr::kable(ccle_signif_g2p_grid[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
@@
 ccle_signif_g2p_lineage <- readRDS("./data_munging/rds/ccle_signif_g2p_lineage.rds")
-
 knitr::kable(ccle_signif_g2p_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
@@
 saveRDS(ctrp_signif_g2p, "./data_munging/rds/ctrp_signif_g2p_gene.rds")
-
 # Grid comparisons of G2P drugs and genes
@@
 ctrp_signif_g2p <- readRDS("./data_munging/rds/ctrp_signif_g2p_gene.rds")
-
 knitr::kable(ctrp_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-
 ctrp_signif_g2p_grid <- readRDS("./data_munging/rds/ctrp_signif_g2p_grid.rds")
-
 knitr::kable(ctrp_signif_g2p_grid[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
@@
 ctrp_signif_g2p_lineage <- readRDS("./data_munging/rds/ctrp_signif_g2p_lineage.rds")
-
 knitr::kable(ctrp_signif_g2p_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
@@
 saveRDS(gdsc_signif_g2p, "./data_munging/rds/gdsc_signif_g2p_gene.rds")
-
 # Grid comparisons of G2P drugs and genes
@@
 gdsc_signif_g2p <- readRDS("./data_munging/rds/gdsc_signif_g2p_gene.rds")
-
 knitr::kable(gdsc_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-
 gdsc_signif_g2p_grid <- readRDS("./data_munging/rds/gdsc_signif_g2p_grid.rds")
-
 knitr::kable(gdsc_signif_g2p_grid[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
@@
 gdsc_signif_g2p_lineage <- readRDS("./data_munging/rds/gdsc_signif_g2p_lineage.rds")
-
 knitr::kable(gdsc_signif_g2p_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
@@
 ccle_data_allgenes <- ccle_data_allgenes[order(ccle_data_allgenes$p),]
-
 knitr::kable(ccle_data_allgenes[1:1000, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: by-drug Wilcoxon test results for point mutations in genes targeted in CRISPR screen (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
@@
 ctrp_data_allgenes <- ctrp_data_allgenes[order(ctrp_data_allgenes$p),]
-
 knitr::kable(ctrp_data_allgenes[1:1000, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: by-drug Wilcoxon test results for point mutations in genes targeted in CRISPR screen (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
@@
 gdsc_data_allgenes <- gdsc_data_allgenes[order(gdsc_data_allgenes$p),]
-
 knitr::kable(gdsc_data_allgenes[1:1000, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: by-drug Wilcoxon test results for point mutations in genes targeted in CRISPR screen (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
@@
 # write.table(crispr_data_g2p_summ, file = "~/Desktop/crispr_data_g2p_summ_20181003.tsv", quote = FALSE, sep = "\t")
-
 knitr::kable(crispr_data_g2p_summ, caption = "CRISPR: Level A G2P genes mutation status summary") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
@@
 sd(g2p_druggene_p_tally$n)
-
 g2p_drug_tally <- g2p %>% group_by(Drug) %>% tally() %>% drop_na()
@@
 sd(g2p_drug_tally$n)
-
 g2p_gene_tally <- g2p %>% group_by(Gene) %>% tally() %>% drop_na()
@@
 g2p_druggene_p_summ_melt <- melt(g2p_druggene_p_summ, id.vars = c("Drug_Gene", "n"), measure.vars = c("CCLE", "CTRP", "GDSC"), variable.name = "Dataset", value.name = "p")
-
 g2p_druggene_p_summ_plot <- ggplot(data = g2p_druggene_p_summ_melt, aes(x = p, y = n, shape = Dataset, color = Dataset)) +
@@
 for_dan <- with(g2p_druggene_p_summ, cbind(n, CCLE, CTRP, GDSC, colsplit(Drug_Gene, pattern = "_", names = c("Drug", "Hugo_Symbol"))))
-
 write.table(for_dan, file = "~/Desktop/for_dan.tsv", sep = "\t")
@@
 ccle_p_ttest_res <- paste0("t(", round(ccle_p_ttest$parameter, 1), ") = ", round(ccle_p_ttest$statistic, 2), ", p = ", round(ccle_p_ttest$p.value, 3))
-
 ctrp_druggene_summ <- merge(g2p_druggene_p_tally, ctrp_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
@@
 ctrp_p_ttest_res <- paste0("t(", round(ctrp_p_ttest$parameter, 1), ") = ", round(ctrp_p_ttest$statistic, 2), ", p = ", round(ctrp_p_ttest$p.value, 3))
-
 gdsc_druggene_summ <- merge(g2p_druggene_p_tally, gdsc_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
@@
 gdsc_p_ttest_res <- paste0("t(", round(gdsc_p_ttest$parameter, 1), ") = ", round(gdsc_p_ttest$statistic, 2), ", p = ", round(gdsc_p_ttest$p.value, 3))
-
 g2p_druggene_all_summ <- rbind(ccle_druggene_summ, ctrp_druggene_summ, gdsc_druggene_summ)
@@
   theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
-
 plot_p_box <- ggplot(data = g2p_druggene_all_summ) +
@@
   theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
 plot_p_point <- ggplot_gtable(ggplot_build(plot_p_point))
@@
 plot_p_box$widths <- as.list(p_maxWidth)
-
 g2p_druggene_mut_plot <- cowplot::plot_grid(plot_p_box,
@@
   theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
 plot <- subplot(plot_p_box, plot_p_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Gene-drug association p-value between mutation groups"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
-
 saveWidgetFix(widget = plot, file = "./plots/manuscript/g2p_druggene_mut_plot.html")
@@
 ccle_pearson_ttest_res_CN <- paste0("t(", round(ccle_pearson_ttest_CN$parameter, 1), ") = ", round(ccle_pearson_ttest_CN$statistic, 2), ", p = ", round(ccle_pearson_ttest_CN$p.value, 3))
-
 ctrp_pearson_res <- ctrp_data_g2p_grid %>% group_by(Drug_Gene) %>%
@@
 ctrp_pearson_ttest_res_CN <- paste0("t(", round(ctrp_pearson_ttest_CN$parameter, 1), ") = ", round(ctrp_pearson_ttest_CN$statistic, 2), ", p = ", round(ctrp_pearson_ttest_CN$p.value, 3))
-
 gdsc_pearson_res <- gdsc_data_g2p_grid %>% group_by(Drug_Gene) %>%
@@
 gdsc_pearson_ttest_res_CN <- paste0("t(", round(gdsc_pearson_ttest_CN$parameter, 1), ") = ", round(gdsc_pearson_ttest_CN$statistic, 2), ", p = ", round(gdsc_pearson_ttest_CN$p.value, 3))
-
 g2p_druggene_pearson <- rbind(ccle_pearson_res, ctrp_pearson_res, gdsc_pearson_res)
@@
   guides(color = FALSE, fill = FALSE, shape = FALSE)
-
 plot_ge_box <- ggplot(data = g2p_druggene_pearson) +
@@
   theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
 plot_ge_point <- ggplot_gtable(ggplot_build(plot_ge_point))
@@
 plot_ge_box$widths[2:3] <- p_maxWidth
-
 g2p_druggene_ge_plot <- cowplot::plot_grid(plot_ge_box, plot_ge_point, nrow = 2, rel_heights = c(1, 4))
@@
   labs(shape = NULL)
-
 plot_ge_box <- ggplot(data = g2p_druggene_pearson) +
@@
   theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
 plot <- subplot(plot_ge_box, plot_ge_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and gene expression"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
-
 saveWidgetFix(widget = plot, file = "./plots/manuscript/g2p_druggene_ge_plot.html")
@@
   guides(color = guide_legend(override.aes = list(size = 4, shape = 15)), shape = guide_legend(override.aes = list(size = 3)), fill = FALSE)
-
 plot_cn_box <- ggplot(data = g2p_druggene_pearson) +
@@
   theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
 plot_cn_point <- ggplot_gtable(ggplot_build(plot_cn_point))
@@
 plot_cn_box$widths <- as.list(p_maxWidth)
-
 g2p_druggene_cn_plot <- cowplot::plot_grid(plot_cn_box, plot_cn_point, nrow = 2, rel_heights = c(1, 4))
@@
   labs(shape = NULL)
-
 plot_cn_box <- ggplot(data = g2p_druggene_pearson) +
@@
   theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
 plot <- subplot(plot_cn_box, plot_cn_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and copy number"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
-
 saveWidgetFix(widget = plot, file = "./plots/manuscript/g2p_druggene_cn_plot.html")
@@
 ccle_druggenelin_summ$Dataset <- "CCLE"
-
 ctrp_druggenelin_summ <- ctrp_signif_g2p_lineage
@@
 ctrp_druggenelin_summ$Dataset <- "CTRP"
-
 gdsc_druggenelin_summ <- gdsc_signif_g2p_lineage
@@
 gdsc_druggenelin_summ$Dataset <- "GDSC"
-
 g2p_druggenelin_all_summ <- rbind(ccle_druggenelin_summ, ctrp_druggenelin_summ, gdsc_druggenelin_summ)
 g2p_druggenelin_all_summ$InG2P <- factor(g2p_druggenelin_all_summ$InG2P, levels = c("Yes", "No"))
-
 # test <- filter(filter(g2p_druggenelin_all_summ, group_general_lineage_name == "breast cancer"), Dataset == "CCLE")
 # test <- test[-39,]
-
 ```
@@
 g2p_druggenelin_p_ttest_res_list <- readRDS("./data_munging/rds/g2p_druggenelin_p_ttest_res.rds")
-
 knitr::kable(g2p_druggenelin_p_ttest_res_list, caption = "Mutation status: T-test results for level A G2P drug-gene associations across lineages") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
@@
 ccle_signif_all_lin <- merge(ccle_signif_ge_all_lin, ccle_signif_cn_all_lin, by = c("Drug_Gene", "group_general_lineage_name", "n", "Dataset"), all = TRUE)
-
 ctrp_lineages4pearson <- as.character(unique(ctrp_data_g2p_grid$group_general_lineage_name))[!is.na(as.character(unique(ctrp_data_g2p_grid$group_general_lineage_name)))]
@@
 ctrp_signif_all_lin <- merge(ctrp_signif_ge_all_lin, ctrp_signif_cn_all_lin, by = c("Drug_Gene", "group_general_lineage_name", "n", "Dataset"), all = TRUE)
-
 gdsc_lineages4pearson <- as.character(unique(gdsc_data_g2p_grid$group_general_lineage_name))[!is.na(as.character(unique(gdsc_data_g2p_grid$group_general_lineage_name)))]
@@
 gdsc_signif_all_lin <- merge(gdsc_signif_ge_all_lin, gdsc_signif_cn_all_lin, by = c("Drug_Gene", "group_general_lineage_name", "n", "Dataset"), all = TRUE)
-
 signif_all_lin <- rbind(ccle_signif_all_lin, ctrp_signif_all_lin, gdsc_signif_all_lin)
@@
 druggenelin_pearson_ttest_res_list <- readRDS("./data_munging/rds/druggenelin_pearson_ttest_res_list.rds")
-
 knitr::kable(druggenelin_pearson_ttest_res_list[order(druggenelin_pearson_ttest_res_list$p_value_GE), c("Dataset", "group_general_lineage_name", "t_statistic_GE", "df_GE", "p_value_GE")], caption = "Gene expression: T-test results for level A G2P drug-gene/gene expression associations across lineages") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-
 knitr::kable(druggenelin_pearson_ttest_res_list[order(druggenelin_pearson_ttest_res_list$p_value_CN), c("Dataset", "group_general_lineage_name", "t_statistic_CN", "df_CN", "p_value_CN")], caption = "Copy number: T-test results for level A G2P drug-gene/gene expression associations across lineages") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
@@
 colnames(all_druggenelin_mut)[colnames(all_druggenelin_mut) == "p"] <- "Statistic"
-
 all_druggenelin_ge <- select(signif_all_lin, Drug_Gene, group_general_lineage_name, n, Pearson_GE_Abs, InG2P, Dataset, Pearson_GE_Sign)
@@
 colnames(all_druggenelin_ge)[colnames(all_druggenelin_ge) == "Pearson_GE_Sign"] <- "Sign"
-
 all_druggenelin_cn <- select(signif_all_lin, Drug_Gene, group_general_lineage_name, n, Pearson_CN_Abs, InG2P, Dataset, Pearson_CN_Sign)
@@
 colnames(all_druggenelin_cn)[colnames(all_druggenelin_cn) == "Pearson_CN_Sign"] <- "Sign"
-
 all_druggenelin_summ <- rbind(all_druggenelin_mut, all_druggenelin_ge, all_druggenelin_cn)
 all_druggenelin_summ$Sign <- ifelse(is.na(all_druggenelin_summ$Sign), "None", all_druggenelin_summ$Sign)
-
 all_druggenelin_summ_plot <- ggplot(data = all_druggenelin_summ, aes(x = InG2P, y = Statistic)) +
@@
 gdsc_ccl <- unique(select(gdsc_data, DepMap_ID, CCLE_Name, accession_id))
-
 # all_ccl <- merge(ccle_ccl, ctrp_ccl, by = c("DepMap_ID", "CCLE_Name", "accession_id"), all = TRUE)
@@
 names(crispr_data_g2p_color) <- crispr_data_g2p$Mutation_Status_Nonsilent
-
 crispr_label_text <- data.frame(p.signif.adj = crispr_signif_g2p_gene$p.signif.adj, p.signif = crispr_signif_g2p_gene$p.signif, Hugo_Symbol = crispr_signif_g2p_gene$Hugo_Symbol)
@@
 crispr_label_text$Hugo_Symbol <- factor(crispr_label_text$Hugo_Symbol, levels = g2p_genes)
-
 crispr_data_g2p_plot <- ggplot(data = crispr_data_g2p, aes(x = Mutation_Status_Nonsilent, y = Score)) +
@@
 crispr_data_g2p_plot
-
 # ggsave("./plots/manuscript/crispr_data_g2p_plot.png", crispr_data_g2p_plot, device = "png", dpi = 450, width = 20, height = 5, units = "in")
@@
 names(ccle_data_g2p_color) <- ccle_data_g2p$Mutation_Status_Nonsilent
-
 ccle_label_text <- data.frame(p.signif.adj = ccle_signif_g2p$p.signif.adj, p.signif = ccle_signif_g2p$p.signif, Drug_Gene_Ordered = ccle_signif_g2p$Drug_Gene_Ordered)
-
 ccle_data_g2p_plot <- ggplot(data = ccle_data_g2p, aes(x = Mutation_Status_Nonsilent, y = AUC)) +
@@
 ccle_data_g2p_plot
-
 # ggsave("./plots/manuscript/ccle_data_g2p_plot.png", ccle_data_g2p_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
@@
 names(ctrp_data_g2p_color) <- ctrp_data_g2p$Mutation_Status_Nonsilent
-
 ctrp_label_text <- data.frame(p.signif.adj = ctrp_signif_g2p$p.signif.adj, p.signif = ctrp_signif_g2p$p.signif, Drug_Gene_Ordered = ctrp_signif_g2p$Drug_Gene_Ordered)
-
 ctrp_data_g2p_plot <- ggplot(data = ctrp_data_g2p, aes(x = Mutation_Status_Nonsilent, y = AUC)) +
@@
 ctrp_data_g2p_plot
-
 # ggsave("./plots/manuscript/ctrp_data_g2p_plot.png", ctrp_data_g2p_plot, device = "png", dpi = 450, width = 12, height = 7, units = "in")
@@
 names(gdsc_data_g2p_color) <- gdsc_data_g2p$Mutation_Status_Nonsilent
-
 gdsc_label_text <- data.frame(p.signif.adj = gdsc_signif_g2p$p.signif.adj, p.signif = gdsc_signif_g2p$p.signif, Drug_Gene_Ordered = gdsc_signif_g2p$Drug_Gene_Ordered)
-
 gdsc_data_g2p_plot <- ggplot(data = gdsc_data_g2p, aes(x = Mutation_Status_Nonsilent, y = AUC)) +
@@
 gdsc_data_g2p_plot
-
 # ggsave("./plots/manuscript/gdsc_data_g2p_plot.png", gdsc_data_g2p_plot, device = "png", dpi = 450, width = 12, height = 7, units = "in")
@@
 crispr_g2p_indications_nonNA <- filter(crispr_g2p_indications, is.na(n))
-
 crispr_g2p_indications_plot <- ggplot(crispr_g2p_indications, aes(x = Hugo_Symbol, y = Score)) +
@@
 crispr_g2p_indications_plot
-
 crispr_g2p_indications_muts_plot <- ggplot(crispr_g2p_indications, aes(x = Protein_Change, y = Score)) +
@@
 crispr_g2p_indications_muts_plot
-
 # ggsave("./plots/manuscript/crispr_g2p_indications_plot_test.png", crispr_g2p_indications_plot, width = 12, height = 5, units = "in")

### 2018-11-21 manuscript.Rmd

@@
   plot <- subplot(plot_box, plot_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(title = toupper(lineage_name), margin = list(t = 75, l = 75), xaxis5 = list(title = "Gene-drug association p-value between mutation groups"), yaxis = list(title = "Level A G2P\nassociation", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
+
   saveWidgetFix(widget = plot, file = paste0("./plots/manuscript/plotlys_mut_by_lineage/", lineage_name, "_mut_plotly.html"))
@@
 gdsc_data_g2p$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
+
 # Filter drug screen datasets for G2P drugs and genes
@@
 crispr_data_signif_g2p_gene_plot
+
 # ggsave("./plots/manuscript/crispr_data_signif_g2p_gene_plot.png", crispr_data_signif_g2p_gene_plot, width = 12, height = 7, units = "in")
@@
 crispr_data_signif_g2p_lineage_plot
+
 # ggsave("./plots/manuscript/crispr_crispr_data_signif_g2p_lineage_plot.png", crispr_data_signif_g2p_lineage_plot, width = 12, height = 15, units = "in")
@@
 sd(g2p_druggene_p_tally$n)
+
 g2p_drug_tally <- g2p %>% group_by(Drug) %>% tally() %>% drop_na()
@@
 sd(g2p_drug_tally$n)
+
 g2p_gene_tally <- g2p %>% group_by(Gene) %>% tally() %>% drop_na()
@@
 ccle_p_ttest_res <- paste0("t(", round(ccle_p_ttest$parameter, 1), ") = ", round(ccle_p_ttest$statistic, 2), ", p = ", round(ccle_p_ttest$p.value, 3))
+
 ctrp_druggene_summ <- merge(g2p_druggene_p_tally, ctrp_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
@@
 ctrp_p_ttest_res <- paste0("t(", round(ctrp_p_ttest$parameter, 1), ") = ", round(ctrp_p_ttest$statistic, 2), ", p = ", round(ctrp_p_ttest$p.value, 3))
+
 gdsc_druggene_summ <- merge(g2p_druggene_p_tally, gdsc_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
@@
 gdsc_p_ttest_res <- paste0("t(", round(gdsc_p_ttest$parameter, 1), ") = ", round(gdsc_p_ttest$statistic, 2), ", p = ", round(gdsc_p_ttest$p.value, 3))
+
 g2p_druggene_all_summ <- rbind(ccle_druggene_summ, ctrp_druggene_summ, gdsc_druggene_summ)
@@
 plot <- subplot(plot_p_box, plot_p_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Gene-drug association p-value between mutation groups"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
+
 saveWidgetFix(widget = plot, file = "./plots/manuscript/g2p_druggene_mut_plot.html")
@@
 ccle_pearson_ttest_res_CN <- paste0("t(", round(ccle_pearson_ttest_CN$parameter, 1), ") = ", round(ccle_pearson_ttest_CN$statistic, 2), ", p = ", round(ccle_pearson_ttest_CN$p.value, 3))
+
 ctrp_pearson_res <- ctrp_data_g2p_grid %>% group_by(Drug_Gene) %>%
@@
 ctrp_pearson_ttest_res_CN <- paste0("t(", round(ctrp_pearson_ttest_CN$parameter, 1), ") = ", round(ctrp_pearson_ttest_CN$statistic, 2), ", p = ", round(ctrp_pearson_ttest_CN$p.value, 3))
+
 gdsc_pearson_res <- gdsc_data_g2p_grid %>% group_by(Drug_Gene) %>%
@@
 gdsc_pearson_ttest_res_CN <- paste0("t(", round(gdsc_pearson_ttest_CN$parameter, 1), ") = ", round(gdsc_pearson_ttest_CN$statistic, 2), ", p = ", round(gdsc_pearson_ttest_CN$p.value, 3))
+
 g2p_druggene_pearson <- rbind(ccle_pearson_res, ctrp_pearson_res, gdsc_pearson_res)
@@
   guides(color = FALSE, fill = FALSE, shape = FALSE)
+
 plot_ge_box <- ggplot(data = g2p_druggene_pearson) +
@@
 plot_ge_box$widths[2:3] <- p_maxWidth
+
 g2p_druggene_ge_plot <- cowplot::plot_grid(plot_ge_box, plot_ge_point, nrow = 2, rel_heights = c(1, 4))
@@
 plot <- subplot(plot_ge_box, plot_ge_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and gene expression"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
+
 saveWidgetFix(widget = plot, file = "./plots/manuscript/g2p_druggene_ge_plot.html")
@@
   guides(color = guide_legend(override.aes = list(size = 4, shape = 15)), shape = guide_legend(override.aes = list(size = 3)), fill = FALSE)
+
 plot_cn_box <- ggplot(data = g2p_druggene_pearson) +
@@
 plot <- subplot(plot_cn_box, plot_cn_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and copy number"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
+
 saveWidgetFix(widget = plot, file = "./plots/manuscript/g2p_druggene_cn_plot.html")
@@
 crispr_data_g2p_plot
+
 # ggsave("./plots/manuscript/crispr_data_g2p_plot.png", crispr_data_g2p_plot, device = "png", dpi = 450, width = 20, height = 5, units = "in")
@@
 ccle_data_g2p_plot
+
 # ggsave("./plots/manuscript/ccle_data_g2p_plot.png", ccle_data_g2p_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
@@
 ctrp_data_g2p_plot
+
 # ggsave("./plots/manuscript/ctrp_data_g2p_plot.png", ctrp_data_g2p_plot, device = "png", dpi = 450, width = 12, height = 7, units = "in")
@@
 gdsc_data_g2p_plot
+
 # ggsave("./plots/manuscript/gdsc_data_g2p_plot.png", gdsc_data_g2p_plot, device = "png", dpi = 450, width = 12, height = 7, units = "in")
@@
 crispr_g2p_indications_muts_plot
+
 # ggsave("./plots/manuscript/crispr_g2p_indications_plot_test.png", crispr_g2p_indications_plot, width = 12, height = 5, units = "in")

### 2018-11-22 manuscript.Rmd
summary data/plots for write-up

--- 2018-11-21 manuscript.Rmd
@@
     theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
   plot <- subplot(plot_box, plot_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(title = toupper(lineage_name), margin = list(t = 75, l = 75), xaxis5 = list(title = "Gene-drug association p-value between mutation groups"), yaxis = list(title = "Level A G2P\nassociation", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
@@
 maf_df$Tumor_Seq_Allele1_Length <- nchar(as.character(maf_df$Tumor_Seq_Allele1))
-
 # Add Mutation_Status column
-maf_df$Mutation_Status_Nonsilent <- ifelse(maf_df$Variant_Classification == "Silent", "Wiltype", "Mutant")
+maf_df$Mutation_Status_Nonsilent <- ifelse(maf_df$Variant_Classification == "Silent", "Wildtype", "Mutant")
 maf_df <- unique(maf_df)
@@
 crispr_melt <- merge(crispr_melt, crispr_meta, by = c("CCLE_Name", "DepMap_ID"), all.x = TRUE)
+
 # Merge mutation annotations
-maf_filt_crispr <- filter(maf_df, Hugo_Symbol %in% as.character(unique(crispr$Hugo_Symbol)))
+maf_filt_crispr <- filter(maf_df, Hugo_Symbol %in% as.character(unique(crispr_melt$Hugo_Symbol)))
 crispr_muts <- merge(crispr_melt, maf_filt_crispr, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
@@
 crispr_data$Color_Nonsilent <- factor(crispr_data$Color_Nonsilent)
+
 # Cell line lineages
@@
 crispr_data_g2p$Hugo_Symbol <- factor(crispr_data_g2p$Hugo_Symbol, levels = g2p_genes)
+crispr_data_g2p$Mutation_Status_Nonsilent <- factor(crispr_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
 ```
@@
 crispr_signif_g2p_gene <- readRDS("./data_munging/rds/crispr_signif_g2p_gene.rds")
-
-crispr_signif_g2p_20gene <- as.character(crispr_signif_g2p_gene$Hugo_Symbol[0:20])
-
 knitr::kable(crispr_signif_g2p_gene[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results for Level A point mutations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
@@
 
+```{r}
+unique(crispr_data_signif_g2p_gene$Mutation_Status_Nonsilent)
+```
+
 ```{r fig.height=7, fig.width=12}
-crispr_data_signif_g2p_gene_filt <- filter(crispr_data_ptmuts, Hugo_Symbol %in% crispr_signif_g2p_20gene)
+crispr_data_signif_g2p_gene_filt <- filter(crispr_data_ptmuts, Hugo_Symbol %in% as.character(crispr_signif_g2p_gene$Hugo_Symbol))
 crispr_data_signif_g2p_gene <- merge(crispr_data_signif_g2p_gene_filt, crispr_signif_g2p_gene, by = "Hugo_Symbol")
-crispr_data_signif_g2p_gene$Hugo_Symbol <- ordered(crispr_data_signif_g2p_gene$Hugo_Symbol, levels = crispr_signif_g2p_20gene)
-crispr_data_signif_g2p_gene_color <- as.character(crispr_data_signif_g2p_gene$Color_Nonsilent)
-names(crispr_data_signif_g2p_gene_color) <- crispr_data_signif_g2p_gene$Mutation_Status_Nonsilent
+crispr_data_signif_g2p_gene$Hugo_Symbol <- ordered(crispr_data_signif_g2p_gene$Hugo_Symbol, levels = as.character(crispr_signif_g2p_gene$Hugo_Symbol))
+
 crispr_data_signif_g2p_gene <- merge(crispr_data_signif_g2p_gene, crispr_data_signif_g2p_gene %>% group_by(Hugo_Symbol) %>% summarize(Text_y = max(Score)), by = "Hugo_Symbol")
-
 crispr_data_signif_g2p_gene_text <- unique(data.frame(p.signif = crispr_data_signif_g2p_gene$p.signif, p.signif.adj = crispr_data_signif_g2p_gene$p.signif.adj,  Hugo_Symbol = crispr_data_signif_g2p_gene$Hugo_Symbol, Text_y = crispr_data_signif_g2p_gene$Text_y))
@@
   geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
-  scale_color_manual(values = crispr_data_signif_g2p_gene_color) + 
+  scale_color_manual(values = c("Mutant" = "darkorchid", "Wildtype" = "thistle")) +
   geom_text(data = crispr_data_signif_g2p_gene_text, mapping = aes(x = 1.5, y = Text_y, label = p.signif), nudge_y = 0.2) +
@@
 crispr_data_signif_g2p_lineage$Hugo_Symbol <- ordered(crispr_data_signif_g2p_lineage$Hugo_Symbol, levels = crispr_signif_g2p_20gene)
-crispr_data_signif_g2p_lineage_color <- as.character(crispr_data_signif_g2p_lineage$Color_Nonsilent)
-names(crispr_data_signif_g2p_lineage_color) <- crispr_data_signif_g2p_lineage$Mutation_Status_Nonsilent
+
 crispr_data_signif_g2p_lineage <- merge(crispr_data_signif_g2p_lineage, crispr_data_signif_g2p_lineage %>% group_by(Hugo_Symbol) %>% summarize(Text_y = max(Score)), by = "Hugo_Symbol")
@@
   geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
-  scale_color_manual(values = crispr_data_signif_g2p_lineage_color) +
+  scale_color_manual(values = c("Mutant" = "darkorchid", "Wildtype" = "thistle")) +
   geom_text(data = crispr_data_signif_g2p_lineage_text, mapping = aes(x = group_general_lineage_name, y = Text_y, label = p.signif), angle = 90, vjust = 0.8, nudge_y = 0.1) +
@@
 
-# ggsave("./plots/manuscript/crispr_crispr_data_signif_g2p_lineage_plot.png", crispr_data_signif_g2p_lineage_plot, width = 12, height = 15, units = "in")
+# ggsave("./plots/manuscript/crispr_data_signif_g2p_lineage_plot.png", crispr_data_signif_g2p_lineage_plot, width = 12, height = 15, units = "in")
 ```
@@
 crispr_data_signif_g2p_lineage_summ <- crispr_data_signif_g2p_lineage %>% group_by(Hugo_Symbol, group_general_lineage_name, Mutation_Status_Nonsilent) %>% tally()
+
 # write.table(crispr_data_signif_g2p_lineage_summ, file = "~/Desktop/crispr_data_signif_g2p_lineage_summ_20181005.tsv", quote = FALSE, sep = "\t")
@@
 ### G2P gene and drug
+
 ```{r}
@@
 ccle_signif_g2p <- readRDS("./data_munging/rds/ccle_signif_g2p_gene.rds")
-
 knitr::kable(ccle_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
@@
 ccle_signif_g2p_grid <- readRDS("./data_munging/rds/ccle_signif_g2p_grid.rds")
-
 knitr::kable(ccle_signif_g2p_grid[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
@@
 ctrp_signif_g2p <- readRDS("./data_munging/rds/ctrp_signif_g2p_gene.rds")
-
 knitr::kable(ctrp_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
@@
 ctrp_signif_g2p_grid <- readRDS("./data_munging/rds/ctrp_signif_g2p_grid.rds")
-
 knitr::kable(ctrp_signif_g2p_grid[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
@@
 gdsc_signif_g2p <- readRDS("./data_munging/rds/gdsc_signif_g2p_gene.rds")
-
 knitr::kable(gdsc_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
@@
 gdsc_signif_g2p_grid <- readRDS("./data_munging/rds/gdsc_signif_g2p_grid.rds")
-
 knitr::kable(gdsc_signif_g2p_grid[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
@@
 rownames(crispr_data_g2p_summ) <- NULL
+
 # write.table(crispr_data_g2p_summ, file = "~/Desktop/crispr_data_g2p_summ_20181003.tsv", quote = FALSE, sep = "\t")
@@
 
-```{r}
-g2p_druggene_p_tally <- g2p %>% group_by(Drug_Gene) %>% tally() %>% drop_na()
-range(g2p_druggene_p_tally$n)
-mean(g2p_druggene_p_tally$n)
-sd(g2p_druggene_p_tally$n)
-
-g2p_drug_tally <- g2p %>% group_by(Drug) %>% tally() %>% drop_na()
-range(g2p_drug_tally$n)
-mean(g2p_drug_tally$n)
-sd(g2p_drug_tally$n)
-
-g2p_gene_tally <- g2p %>% group_by(Gene) %>% tally() %>% drop_na()
-range(g2p_gene_tally$n)
-mean(g2p_gene_tally$n)
-sd(g2p_gene_tally$n)
-```
-
 ```{r fig.height=4, fig.width=8}
-g2p_druggene_p_summ <- merge(g2p_druggene_p_tally, ccle_signif_g2p[, c("Drug_Gene", "p")], by = "Drug_Gene", all.x = TRUE)
-g2p_druggene_p_summ <- merge(g2p_druggene_p_summ, ctrp_signif_g2p[, c("Drug_Gene", "p")], by = "Drug_Gene", all.x = TRUE, suffixes = c("_CCLE", "_CTRP"))
-g2p_druggene_p_summ <- merge(g2p_druggene_p_summ, gdsc_signif_g2p[, c("Drug_Gene", "p")], by = "Drug_Gene", all.x = TRUE)
+g2p_druggene_p_summ <- merge(g2p_druggene_p_tally, ccle_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all.x = TRUE)
+g2p_druggene_p_summ <- merge(g2p_druggene_p_summ, ctrp_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all.x = TRUE, suffixes = c("_CCLE", "_CTRP"))
+g2p_druggene_p_summ <- merge(g2p_druggene_p_summ, gdsc_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all.x = TRUE)
 colnames(g2p_druggene_p_summ)[colnames(g2p_druggene_p_summ) == "p_CCLE"] <- "CCLE"
@@
 colnames(g2p_druggene_p_summ)[colnames(g2p_druggene_p_summ) == "p"] <- "GDSC"
+
 g2p_druggene_p_summ_melt <- melt(g2p_druggene_p_summ, id.vars = c("Drug_Gene", "n"), measure.vars = c("CCLE", "CTRP", "GDSC"), variable.name = "Dataset", value.name = "p")
@@
 g2p_druggene_mut_plot
+
 ggsave("./plots/manuscript/g2p_druggene_mut_plot.png", g2p_druggene_mut_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
@@
 g2p_druggene_ge_plot
-# ggsave("./plots/manuscript/g2p_druggene_ge_plot.png", g2p_druggene_ge_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
+
+ggsave("./plots/manuscript/g2p_druggene_ge_plot.png", g2p_druggene_ge_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
 ```
@@
 plot_cn_box$widths <- as.list(p_maxWidth)
-
 g2p_druggene_cn_plot <- cowplot::plot_grid(plot_cn_box, plot_cn_point, nrow = 2, rel_heights = c(1, 4))
 g2p_druggene_cn_plot
-# ggsave("./plots/manuscript/g2p_druggene_cn_plot.png", g2p_druggene_cn_plot, device = "png", dpi = 450, width = 12, height = 5.5, units = "in")
+
+ggsave("./plots/manuscript/g2p_druggene_cn_plot.png", g2p_druggene_cn_plot, device = "png", dpi = 450, width = 12, height = 5.5, units = "in")
 ```
@@
   theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
 plot <- subplot(plot_cn_box, plot_cn_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and copy number"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
@@
 
+G2P summary stats:
+```{r}
+g2p_druggene_p_tally <- g2p %>% group_by(Drug_Gene) %>% tally() %>% drop_na()
+range(g2p_druggene_p_tally$n)
+mean(g2p_druggene_p_tally$n)
+sd(g2p_druggene_p_tally$n)
+
+g2p_drug_tally <- g2p %>% group_by(Drug) %>% tally() %>% drop_na()
+range(g2p_drug_tally$n)
+mean(g2p_drug_tally$n)
+sd(g2p_drug_tally$n)
+
+g2p_gene_tally <- g2p %>% group_by(Gene) %>% tally() %>% drop_na()
+range(g2p_gene_tally$n)
+mean(g2p_gene_tally$n)
+sd(g2p_gene_tally$n)
+```
+
+Mutation status summary stats:
+```{r}
+g2p_druggene_all_summ_stats <- g2p_druggene_all_summ
+g2p_druggene_all_summ_stats$n_true <- TRUE
+g2p_druggene_all_summ_stats <- g2p_druggene_all_summ_stats %>% drop_na(p) %>% group_by(Dataset, InG2P) %>% summarize(p_mean = round(mean(p), 3), p_sd = round(sd(p), 3), n = sum(n_true), n_signif = sum(p < 0.05))
+```
+
+Pearson summary stats:
+```{r fig.height=4, fig.width=5}
+g2p_druggene_pearson_stats <- g2p_druggene_pearson
+g2p_druggene_pearson_stats$n_true <- TRUE
+g2p_druggene_pearson_stats <- g2p_druggene_pearson_stats %>% group_by(Dataset, InG2P) %>% drop_na() %>% summarize(ge_mean = round(mean(Pearson_GE_Abs), 3),
+          ge_sd = round(sd(Pearson_GE_Abs), 3),
+          ge_n = sum(n_true),
+          ge_n_signif = sum(Pearson_Pval_GE < 0.05),
+          cn_mean = round(mean(Pearson_CN_Abs), 3),
+          cn_sd = round(sd(Pearson_CN_Abs), 3),
+          cn_n = sum(n_true),
+          cn_n_signif = sum(Pearson_Pval_CN < 0.05))
+
+ctrp_grid_summary_data <- filter(ctrp_data_g2p_grid, Drug_Gene == "afatinib_ERBB2")
+
+ctrp_grid_summary_mut_corr <- wilcox.test(AUC_zscore ~ Mutation_Status_Nonsilent, data = ctrp_grid_summary_data[!is.na(ctrp_grid_summary_data$Mutation_Status_Nonsilent),], paired = FALSE)
+ctrp_grid_summary_mut_corr_text <- paste0("W = ", ctrp_grid_summary_mut_corr$statistic, ", p = ", round(ctrp_grid_summary_mut_corr$p.value, 3))
+
+ctrp_grid_summary_ge_corr <- cor.test(y = ctrp_grid_summary_data$AUC, x = ctrp_grid_summary_data$RPKM, method = "pearson", use = "complete.obs")
+ctrp_grid_summary_ge_corr_text <- paste0("r = ", round(ctrp_grid_summary_ge_corr$estimate, 3), ", t(", ctrp_grid_summary_ge_corr$parameter, ") = ", round(ctrp_grid_summary_ge_corr$statistic, 2), ", p = ", round(ctrp_grid_summary_ge_corr$p.value, 3))
+
+ctrp_grid_summary_cn_corr <- cor.test(y = ctrp_grid_summary_data$AUC, x = ctrp_grid_summary_data$CN, method = "pearson", use = "complete.obs")
+ctrp_grid_summary_cn_corr_text <- paste0("r = ", round(ctrp_grid_summary_cn_corr$estimate, 3), ", t(", ctrp_grid_summary_cn_corr$parameter, ") = ", round(ctrp_grid_summary_cn_corr$statistic, 2), ", p = ", round(ctrp_grid_summary_cn_corr$p.value, 3))
+
+ctrp_grid_summary_mut_plot <- ggplot(data = ctrp_grid_summary_data[!is.na(ctrp_grid_summary_data$Mutation_Status_Nonsilent),], aes(y = AUC_zscore, x = Mutation_Status_Nonsilent, fill = Mutation_Status_Nonsilent)) +
+  geom_boxplot(outlier.shape = NA, alpha = 0.6) +
+  geom_jitter(width = 0.2, shape = 21) +
+  scale_fill_manual(values = c("Wildtype" = "lightsteelblue1", "Mutant" = "steelblue4")) +
+  annotate(geom = "text", label = ctrp_grid_summary_mut_corr_text, x = 1.5, y = 1.3) +
+  guides(fill = FALSE) +
+  labs(x = "ERBB2 mutation status", y = "Afatinib AUC (z-score)")
+ctrp_grid_summary_mut_plot
+
+ctrp_grid_summary_ge_plot <- ggplot(data = ctrp_grid_summary_data, aes(y = AUC_zscore, x = RPKM)) +
+  geom_point(alpha = 0.25, size = 1.25, color = "gray4") +
+  geom_smooth(method = "lm", se = FALSE, lwd = 0.5, lty = 2) +
+  annotate(geom = "text", label = ctrp_grid_summary_ge_corr_text, x = 1750, y = 1.3) +
+  labs(x = "ERBB2 gene expression (RPKM)", y = "Afatinib AUC (z-score)") +
+  theme(axis.title.y = element_blank())
+ctrp_grid_summary_ge_plot
+
+ctrp_grid_summary_cn_plot <- ggplot(data = ctrp_grid_summary_data, aes(y = AUC_zscore, x = CN)) +
+  geom_point(alpha = 0.25, size = 1.25, color = "gray4") +
+  geom_smooth(method = "lm", se = FALSE, lwd = 0.5, lty = 2) +
+  annotate(geom = "text", label = ctrp_grid_summary_cn_corr_text, x = 4, y = 1.3) +
+  labs(x = "ERBB2 copy number (log2 ratio)") +
+  theme(axis.title.y = element_blank())
+ctrp_grid_summary_cn_plot
+
+ggsave("./plots/manuscript/ctrp_grid_summary_mut_plot.png", ctrp_grid_summary_mut_plot, device = "png", dpi = 450, width = 3, height = 4, units = "in")
+ggsave("./plots/manuscript/ctrp_grid_summary_ge_plot.png", ctrp_grid_summary_ge_plot, device = "png", dpi = 450, width = 5, height = 4, units = "in")
+ggsave("./plots/manuscript/ctrp_grid_summary_cn_plot.png", ctrp_grid_summary_cn_plot, device = "png", dpi = 450, width = 5, height = 4, units = "in")
+```
+
+Big grid plot by lineages:
 ```{r fig.height=20, fig.width=12}

### 2018-11-26 manuscript.Rmd
minor changes to Rmd and plots

@@
 g2p$position <- ifelse(grepl("NA", g2p$position), NA, g2p$position)
-g2p <- subset(g2p, grepl("^CID", g2p$DrugID))
-
-g2p_drug_genes <- unique(g2p$Drug_Gene[!is.na(g2p$Drug_Gene)])
+g2p_filt <- subset(g2p, grepl("^CID", g2p$DrugID))
+
+g2p_drug_genes <- unique(g2p_filt$Drug_Gene[!is.na(g2p_filt$Drug_Gene)])
 g2p_genes <- unique(sapply(strsplit(g2p_drug_genes, "_", fixed = TRUE), function(x) x[2]))
@@
 g2p_genes <- c("EGFR", "KRAS", "ERBB2", "ERBB3", "MET", "ALK", "ROS1", "PDGFRA", "ABL1", "KIT", "PDGFRB", "PDGFB", "BRAF", "G6PD", "RET", "BRCA1", "BRCA2", "UGT1A1", "TSC1", "TSC2", "AKT1", "IDH2", "DPYD", "ESR1", "CYP19A1", "TPMT", "FLT3", "NPM1", "DNMT3A", "PML", "PTCH1", "JAK2", "MYD88", "MGMT")
+```
+
+```{r}
+g2p_nonCID <- subset(g2p, !grepl("^CID", g2p$DrugID))
+summ <- g2p_nonCID %>% group_by(Drug, DrugID) %>% tally() %>% summarize(n = n,
+                                                                percent = n / 402 * 100)
+summ
 ```
@@
 
-```{r}
-unique(crispr_data_signif_g2p_gene$Mutation_Status_Nonsilent)
-```
-
 ```{r fig.height=7, fig.width=12}
@@
 
-```{r fig.height=15, fig.width=15}
+```{r fig.height=15, fig.width=15, eval=FALSE}
 crispr_data_signif_g2p_lineage <- merge(crispr_data_signif_g2p_gene_filt, crispr_signif_g2p_lineage, by = c("Hugo_Symbol", "group_general_lineage_name"))
-crispr_data_signif_g2p_lineage$Hugo_Symbol <- ordered(crispr_data_signif_g2p_lineage$Hugo_Symbol, levels = crispr_signif_g2p_20gene)
+crispr_data_signif_g2p_lineage$Hugo_Symbol <- ordered(crispr_data_signif_g2p_lineage$Hugo_Symbol, levels = as.character(unique((crispr_signif_g2p_lineage$Hugo_Symbol)))
 
@@
 ## Drugscreen: G2P evidence
+
+G2P summary stats:
+```{r}
+g2p_druggene_p_tally <- g2p %>% group_by(Drug_Gene) %>% tally() %>% drop_na()
+range(g2p_druggene_p_tally$n)
+mean(g2p_druggene_p_tally$n)
+sd(g2p_druggene_p_tally$n)
+
+g2p_drug_tally <- g2p %>% group_by(Drug) %>% tally() %>% drop_na()
+range(g2p_drug_tally$n)
+mean(g2p_drug_tally$n)
+sd(g2p_drug_tally$n)
+
+g2p_gene_tally <- g2p %>% group_by(Gene) %>% tally() %>% drop_na()
+range(g2p_gene_tally$n)
+mean(g2p_gene_tally$n)
+sd(g2p_gene_tally$n)
+```
 
@@
 ### All
-
-G2P summary stats:
-```{r}
-g2p_druggene_p_tally <- g2p %>% group_by(Drug_Gene) %>% tally() %>% drop_na()
-range(g2p_druggene_p_tally$n)
-mean(g2p_druggene_p_tally$n)
-sd(g2p_druggene_p_tally$n)
-
-g2p_drug_tally <- g2p %>% group_by(Drug) %>% tally() %>% drop_na()
-range(g2p_drug_tally$n)
-mean(g2p_drug_tally$n)
-sd(g2p_drug_tally$n)
-
-g2p_gene_tally <- g2p %>% group_by(Gene) %>% tally() %>% drop_na()
-range(g2p_gene_tally$n)
-mean(g2p_gene_tally$n)
-sd(g2p_gene_tally$n)
-```
 

### 2018-11-27 manuscript.Rmd
manuscript plots/data update

@@
 ```{r}
-g2p <- read.delim("./data_munging/g2p_full_level_A_dataset_withGroupedLineages.csv", sep = "\t", header = TRUE, row.names = 1)
-g2p <- merge(g2p, lineage_converter, by = "grouped_general_doid", all.x = TRUE)
+g2p <- read.delim("./data_munging/g2p_full_level_A_dataset_NEW_NOV_27.csv", sep = "\t", header = TRUE)
+# g2p <- merge(g2p, lineage_converter, by = "grouped_general_doid", all.x = TRUE)
 g2p$Drug <- tolower(g2p$Drug)
@@
 g2p_drugs <- unique(sapply(strsplit(g2p_drug_genes, "_", fixed = TRUE), function(x) x[1]))
+g2p_drug_genes
 g2p_genes
@@
 # ge_melt_18Q4 <- readRDS("./data_munging/rds/ge_melt_18Q4.rds")
+
+# maf_filt_dan <- filter(maf_df, Hugo_Symbol %in% g2p_genes)
+# write.table(maf_filt_dan, file = "~/Desktop/maf_filt_dan_18Q4_2018112.csv", quote = FALSE, sep = ",", row.names = FALSE)
 ```
@@
 
+```{r}
+test_ccle <- ccle_data_ptmuts %>% group_by(Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()
+test_ctrp <- ctrp_data_ptmuts %>% group_by(Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()
+test_gdsc <- gdsc_data_ptmuts %>% group_by(Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()
+
+```
+
 # Mutation Status Wilcoxon tests
@@
 
-```{r fig.height=15, fig.width=15, eval=FALSE}
+```{r fig.height=18, fig.width=15, eval=TRUE}
 crispr_data_signif_g2p_lineage <- merge(crispr_data_signif_g2p_gene_filt, crispr_signif_g2p_lineage, by = c("Hugo_Symbol", "group_general_lineage_name"))
-crispr_data_signif_g2p_lineage$Hugo_Symbol <- ordered(crispr_data_signif_g2p_lineage$Hugo_Symbol, levels = as.character(unique((crispr_signif_g2p_lineage$Hugo_Symbol)))
+crispr_data_signif_g2p_lineage$Hugo_Symbol <- ordered(crispr_data_signif_g2p_lineage$Hugo_Symbol, levels = as.character(unique((crispr_signif_g2p_lineage$Hugo_Symbol))))
 
@@
 crispr_data_signif_g2p_lineage_plot <- ggplot(data = crispr_data_signif_g2p_lineage, aes(x = group_general_lineage_name, y = Score)) +
-  facet_wrap(~ Hugo_Symbol, nrow = 4, scales = "free_y") +
+  facet_wrap(~ Hugo_Symbol, nrow = 6, scales = "free_y") +
   geom_point(aes(color = Mutation_Status_Nonsilent), alpha = 0.5) +
@@
 
-# ggsave("./plots/manuscript/crispr_data_signif_g2p_lineage_plot.png", crispr_data_signif_g2p_lineage_plot, width = 12, height = 15, units = "in")
+# ggsave("./plots/manuscript/crispr_data_signif_g2p_lineage_plot.png", crispr_data_signif_g2p_lineage_plot, width = 15, height = 18, units = "in")
 ```
@@
 ```{r}
-g2p_druggene_p_tally <- g2p %>% group_by(Drug_Gene) %>% tally() %>% drop_na()
+g2p_druggene_p_tally <- g2p_filt %>% group_by(Drug_Gene) %>% tally() %>% drop_na()
 range(g2p_druggene_p_tally$n)
@@
 
-g2p_drug_tally <- g2p %>% group_by(Drug) %>% tally() %>% drop_na()
+g2p_drug_tally <- g2p_filt %>% group_by(Drug) %>% tally() %>% drop_na()
 range(g2p_drug_tally$n)
@@
 
-g2p_gene_tally <- g2p %>% group_by(Gene) %>% tally() %>% drop_na()
+g2p_gene_tally <- g2p_filt %>% group_by(Gene) %>% tally() %>% drop_na()
 range(g2p_gene_tally$n)
@@
 ccle_p_ttest <- t.test(ccle_druggene_summ$p ~ ccle_druggene_summ$InG2P)
-ccle_p_ttest_res <- paste0("t(", round(ccle_p_ttest$parameter, 1), ") = ", round(ccle_p_ttest$statistic, 2), ", p = ", round(ccle_p_ttest$p.value, 3))
+ccle_p_ttest_res <- paste0("t(", round(ccle_p_ttest$parameter, 0), ") = ", round(ccle_p_ttest$statistic, 2), ", p = ", round(ccle_p_ttest$p.value, 2))
 
@@
 ctrp_p_ttest <- t.test(ctrp_druggene_summ$p ~ ctrp_druggene_summ$InG2P)
-ctrp_p_ttest_res <- paste0("t(", round(ctrp_p_ttest$parameter, 1), ") = ", round(ctrp_p_ttest$statistic, 2), ", p = ", round(ctrp_p_ttest$p.value, 3))
+ctrp_p_ttest_res <- paste0("t(", round(ctrp_p_ttest$parameter, 0), ") = ", round(ctrp_p_ttest$statistic, 2), ", p = ", formatC(ctrp_p_ttest$p.value, digits = 2, format = "f"))
 
@@
 gdsc_p_ttest <- t.test(gdsc_druggene_summ$p ~ gdsc_druggene_summ$InG2P)
-gdsc_p_ttest_res <- paste0("t(", round(gdsc_p_ttest$parameter, 1), ") = ", round(gdsc_p_ttest$statistic, 2), ", p = ", round(gdsc_p_ttest$p.value, 3))
+gdsc_p_ttest_res <- paste0("t(", round(gdsc_p_ttest$parameter, 0), ") = ", round(gdsc_p_ttest$statistic, 2), ", p = ", round(gdsc_p_ttest$p.value, 2))
 
@@
 
-ggsave("./plots/manuscript/g2p_druggene_mut_plot.png", g2p_druggene_mut_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
+# ggsave("./plots/manuscript/g2p_druggene_mut_plot.png", g2p_druggene_mut_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
 ```
@@
 ccle_pearson_ttest_GE <- t.test(ccle_pearson_res$Pearson_Corr_GE ~ ccle_pearson_res$InG2P)
-ccle_pearson_ttest_res_GE <- paste0("t(", round(ccle_pearson_ttest_GE$parameter, 1), ") = ", round(ccle_pearson_ttest_GE$statistic, 2), ", p = ", round(ccle_pearson_ttest_GE$p.value, 3))
+ccle_pearson_ttest_res_GE <- paste0("t(", round(ccle_pearson_ttest_GE$parameter, 0), ") = ", round(ccle_pearson_ttest_GE$statistic, 2), ", p = ", round(ccle_pearson_ttest_GE$p.value, 2))
 ccle_pearson_ttest_CN <- t.test(ccle_pearson_res$Pearson_Corr_CN ~ ccle_pearson_res$InG2P)
-ccle_pearson_ttest_res_CN <- paste0("t(", round(ccle_pearson_ttest_CN$parameter, 1), ") = ", round(ccle_pearson_ttest_CN$statistic, 2), ", p = ", round(ccle_pearson_ttest_CN$p.value, 3))
+ccle_pearson_ttest_res_CN <- paste0("t(", round(ccle_pearson_ttest_CN$parameter, 0), ") = ", round(ccle_pearson_ttest_CN$statistic, 2), ", p = ", round(ccle_pearson_ttest_CN$p.value, 2))
 
@@
 ctrp_pearson_ttest_GE <- t.test(ctrp_pearson_res$Pearson_Corr_GE ~ ctrp_pearson_res$InG2P)
-ctrp_pearson_ttest_res_GE <- paste0("t(", round(ctrp_pearson_ttest_GE$parameter, 1), ") = ", round(ctrp_pearson_ttest_GE$statistic, 2), ", p = ", round(ctrp_pearson_ttest_GE$p.value, 3))
+ctrp_pearson_ttest_res_GE <- paste0("t(", round(ctrp_pearson_ttest_GE$parameter, 0), ") = ", round(ctrp_pearson_ttest_GE$statistic, 2), ", p ", ifelse(round(ctrp_pearson_ttest_GE$p.value, 3) == 0, "< 0.001", paste0("= ", round(ctrp_pearson_ttest_GE$p.value, 3))))
 ctrp_pearson_ttest_CN <- t.test(ctrp_pearson_res$Pearson_Corr_CN ~ ctrp_pearson_res$InG2P)
-ctrp_pearson_ttest_res_CN <- paste0("t(", round(ctrp_pearson_ttest_CN$parameter, 1), ") = ", round(ctrp_pearson_ttest_CN$statistic, 2), ", p = ", round(ctrp_pearson_ttest_CN$p.value, 3))
+ctrp_pearson_ttest_res_CN <- paste0("t(", round(ctrp_pearson_ttest_CN$parameter, 0), ") = ", round(ctrp_pearson_ttest_CN$statistic, 2), ", p = ", round(ctrp_pearson_ttest_CN$p.value, 3))
 
@@
 gdsc_pearson_ttest_GE <- t.test(gdsc_pearson_res$Pearson_Corr_GE ~ gdsc_pearson_res$InG2P)
-gdsc_pearson_ttest_res_GE <- paste0("t(", round(gdsc_pearson_ttest_GE$parameter, 1), ") = ", round(gdsc_pearson_ttest_GE$statistic, 2), ", p = ", round(gdsc_pearson_ttest_GE$p.value, 3))
+gdsc_pearson_ttest_res_GE <- paste0("t(", round(gdsc_pearson_ttest_GE$parameter, 0), ") = ", round(gdsc_pearson_ttest_GE$statistic, 2), ", p = ", round(gdsc_pearson_ttest_GE$p.value, 3))
 gdsc_pearson_ttest_CN <- t.test(gdsc_pearson_res$Pearson_Corr_CN ~ gdsc_pearson_res$InG2P)
-gdsc_pearson_ttest_res_CN <- paste0("t(", round(gdsc_pearson_ttest_CN$parameter, 1), ") = ", round(gdsc_pearson_ttest_CN$statistic, 2), ", p = ", round(gdsc_pearson_ttest_CN$p.value, 3))
+gdsc_pearson_ttest_res_CN <- paste0("t(", round(gdsc_pearson_ttest_CN$parameter, 0), ") = ", round(gdsc_pearson_ttest_CN$statistic, 2), ", p = ", round(gdsc_pearson_ttest_CN$p.value, 3))
 
@@
 
-ggsave("./plots/manuscript/g2p_druggene_ge_plot.png", g2p_druggene_ge_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
+# ggsave("./plots/manuscript/g2p_druggene_ge_plot.png", g2p_druggene_ge_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
 ```
@@
 g2p_druggene_all_summ_stats$n_true <- TRUE
-g2p_druggene_all_summ_stats <- g2p_druggene_all_summ_stats %>% drop_na(p) %>% group_by(Dataset, InG2P) %>% summarize(p_mean = round(mean(p), 3), p_sd = round(sd(p), 3), n = sum(n_true), n_signif = sum(p < 0.05))
+g2p_druggene_all_summ_stats <- g2p_druggene_all_summ_stats %>% drop_na(p) %>% group_by(Dataset, InG2P) %>% summarize(p_mean = round(mean(p), 2), p_sd = round(sd(p), 2), n = sum(n_true), n_signif = sum(p < 0.05))
 ```
@@
 g2p_druggene_pearson_stats$n_true <- TRUE
-g2p_druggene_pearson_stats <- g2p_druggene_pearson_stats %>% group_by(Dataset, InG2P) %>% drop_na() %>% summarize(ge_mean = round(mean(Pearson_GE_Abs), 3),
-          ge_sd = round(sd(Pearson_GE_Abs), 3),
+g2p_druggene_pearson_stats <- g2p_druggene_pearson_stats %>% group_by(Dataset, InG2P) %>% drop_na() %>% summarize(
+          ge_mean = round(mean(Pearson_GE_Abs), 5),
+          ge_sd = round(sd(Pearson_GE_Abs), 5),
           ge_n = sum(n_true),
@@
           cn_mean = round(mean(Pearson_CN_Abs), 3),
-          cn_sd = round(sd(Pearson_CN_Abs), 3),
+          cn_sd = round(sd(Pearson_CN_Abs), 5),
           cn_n = sum(n_true),
@@
 ctrp_grid_summary_mut_corr <- wilcox.test(AUC_zscore ~ Mutation_Status_Nonsilent, data = ctrp_grid_summary_data[!is.na(ctrp_grid_summary_data$Mutation_Status_Nonsilent),], paired = FALSE)
-ctrp_grid_summary_mut_corr_text <- paste0("W = ", ctrp_grid_summary_mut_corr$statistic, ", p = ", round(ctrp_grid_summary_mut_corr$p.value, 3))
+ctrp_grid_summary_mut_corr_text <- paste0("W = ", formatC(ctrp_grid_summary_mut_corr$statistic, format = "d", big.mark = ","), "\np = ", round(ctrp_grid_summary_mut_corr$p.value, 3))
 
 ctrp_grid_summary_ge_corr <- cor.test(y = ctrp_grid_summary_data$AUC, x = ctrp_grid_summary_data$RPKM, method = "pearson", use = "complete.obs")
-ctrp_grid_summary_ge_corr_text <- paste0("r = ", round(ctrp_grid_summary_ge_corr$estimate, 3), ", t(", ctrp_grid_summary_ge_corr$parameter, ") = ", round(ctrp_grid_summary_ge_corr$statistic, 2), ", p = ", round(ctrp_grid_summary_ge_corr$p.value, 3))
+ctrp_grid_summary_ge_corr_text <- paste0("r(", ctrp_grid_summary_ge_corr$parameter, ") = ", round(ctrp_grid_summary_ge_corr$estimate, 2), "\np ", ifelse(round(ctrp_grid_summary_ge_corr$p.value, 3) == 0, "< 0.001", paste0("= ", round(ctrp_grid_summary_ge_corr$p.value, 3))))
 
 ctrp_grid_summary_cn_corr <- cor.test(y = ctrp_grid_summary_data$AUC, x = ctrp_grid_summary_data$CN, method = "pearson", use = "complete.obs")
-ctrp_grid_summary_cn_corr_text <- paste0("r = ", round(ctrp_grid_summary_cn_corr$estimate, 3), ", t(", ctrp_grid_summary_cn_corr$parameter, ") = ", round(ctrp_grid_summary_cn_corr$statistic, 2), ", p = ", round(ctrp_grid_summary_cn_corr$p.value, 3))
+ctrp_grid_summary_cn_corr_text <- paste0("r(", ctrp_grid_summary_cn_corr$parameter, ") = ", formatC(ctrp_grid_summary_cn_corr$estimate, digits = 2, format = "f"), "\np ", ifelse(round(ctrp_grid_summary_cn_corr$p.value, 3) == 0, "< 0.001", paste0("= ", round(ctrp_grid_summary_cn_corr$p.value, 3))))
 
@@
   guides(fill = FALSE) +
-  labs(x = "ERBB2 mutation status", y = "Afatinib AUC (z-score)")
+  labs(x = "ERBB2 mutation status", y = "Afatinib AUC (z-score)") +
+  geom_segment(aes(x = 1, y = 1.5, xend = 1.1, yend = 1.5), lwd = 0.2) +
+  geom_segment(aes(x = 1.9, y = 1.5, xend = 2, yend = 1.5), lwd = 0.2) +
+  geom_segment(aes(x = 1, y = 1.5, xend = 1, yend = 1.35), lwd = 0.2) +
+  geom_segment(aes(x = 2, y = 1.5, xend = 2, yend = 1.35), lwd = 0.2)
 ctrp_grid_summary_mut_plot
@@
   geom_smooth(method = "lm", se = FALSE, lwd = 0.5, lty = 2) +
-  annotate(geom = "text", label = ctrp_grid_summary_ge_corr_text, x = 1750, y = 1.3) +
+  annotate(geom = "text", label = ctrp_grid_summary_ge_corr_text, x = 2000, y = 1.3) +
   labs(x = "ERBB2 gene expression (RPKM)", y = "Afatinib AUC (z-score)") +
-  theme(axis.title.y = element_blank())
+  theme(axis.title.y = element_blank()) +
+  geom_curve(aes(x = 750, y = -1.9, xend = 1720, yend = 1.1), lwd = 0.2, curvature = -0.2, arrow = arrow(length = unit(0.03, "npc")))
 ctrp_grid_summary_ge_plot
@@
   geom_smooth(method = "lm", se = FALSE, lwd = 0.5, lty = 2) +
-  annotate(geom = "text", label = ctrp_grid_summary_cn_corr_text, x = 4, y = 1.3) +
+  annotate(geom = "text", label = ctrp_grid_summary_cn_corr_text, x = 5, y = 1.3) +
   labs(x = "ERBB2 copy number (log2 ratio)") +
-  theme(axis.title.y = element_blank())
+  theme(axis.title.y = element_blank()) +
+  geom_curve(aes(x = 4, y = -2.3, xend = 5, yend = 0.8), lwd = 0.2, curvature = 0.2, arrow = arrow(length = unit(0.03, "npc")))
 ctrp_grid_summary_cn_plot
 
-ggsave("./plots/manuscript/ctrp_grid_summary_mut_plot.png", ctrp_grid_summary_mut_plot, device = "png", dpi = 450, width = 3, height = 4, units = "in")
-ggsave("./plots/manuscript/ctrp_grid_summary_ge_plot.png", ctrp_grid_summary_ge_plot, device = "png", dpi = 450, width = 5, height = 4, units = "in")
-ggsave("./plots/manuscript/ctrp_grid_summary_cn_plot.png", ctrp_grid_summary_cn_plot, device = "png", dpi = 450, width = 5, height = 4, units = "in")
+# ggsave("./plots/manuscript/ctrp_grid_summary_mut_plot.png", ctrp_grid_summary_mut_plot, device = "png", dpi = 450, width = 3, height = 4, units = "in")
+# ggsave("./plots/manuscript/ctrp_grid_summary_ge_plot.png", ctrp_grid_summary_ge_plot, device = "png", dpi = 450, width = 5, height = 4, units = "in")
+# ggsave("./plots/manuscript/ctrp_grid_summary_cn_plot.png", ctrp_grid_summary_cn_plot, device = "png", dpi = 450, width = 5, height = 4, units = "in")
 ```
@@
 
-ggsave("./plots/manuscript/all_druggenelin_summ_plot.png", all_druggenelin_summ_plot, device = "png", dpi = 450, width = 12, height = 40, units = "in")
+# ggsave("./plots/manuscript/all_druggenelin_summ_plot.png", all_druggenelin_summ_plot, device = "png", dpi = 450, width = 12, height = 40, units = "in")
 ```

### 2018-11-28 manuscript.Rmd

@@
 g2p_nonCID <- subset(g2p, !grepl("^CID", g2p$DrugID))
-summ <- g2p_nonCID %>% group_by(Drug, DrugID) %>% tally() %>% summarize(n = n,
-                                                                percent = n / 402 * 100)
+summ <- g2p_nonCID %>% group_by(Drug, DrugID) %>% tally() %>% summarize(DrugID = DrugID, n = n, percent = formatC(n / 402 * 100, digits = 6, format = "f"))
 summ
@@
 test_gdsc <- gdsc_data_ptmuts %>% group_by(Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()
-
 ```

### 2018-11-30 manuscript.Rmd

@@
 g2p <- read.delim("./data_munging/g2p_full_level_A_dataset_NEW_NOV_27.csv", sep = "\t", header = TRUE)
-# g2p <- merge(g2p, lineage_converter, by = "grouped_general_doid", all.x = TRUE)
+colnames(g2p)[colnames(g2p) == "Phenotype.ID"] <- "grouped_general_doid"
+g2p <- merge(g2p, lineage_converter, by = "grouped_general_doid", all.x = TRUE)
+
 g2p$Drug <- tolower(g2p$Drug)

### 2018-12-03 manuscript.Rmd
update rmd

@@
     ccle_ge_ttest <- t.test(use_data_ccle$Pearson_GE_Abs ~ use_data_ccle$InG2P)
-    ccle_ge_res <- paste0("t(", round(ccle_ge_ttest$parameter, 1), ") = ", round(ccle_ge_ttest$statistic, 2), ", p = ", round(ccle_ge_ttest$p.value, 3))
+    ccle_ge_res <- paste0("t(", trunc(ccle_ge_ttest$parameter), ") = ", round(ccle_ge_ttest$statistic, 2), ", p = ", round(ccle_ge_ttest$p.value, 3))
   }
@@
     ccle_cn_ttest <- t.test(use_data_ccle$Pearson_CN_Abs ~ use_data_ccle$InG2P)
-    ccle_cn_res <- paste0("t(", round(ccle_cn_ttest$parameter, 1), ") = ", round(ccle_cn_ttest$statistic, 2), ", p = ", round(ccle_cn_ttest$p.value, 3))
+    ccle_cn_res <- paste0("t(", trunc(ccle_cn_ttest$parameter), ") = ", round(ccle_cn_ttest$statistic, 2), ", p = ", round(ccle_cn_ttest$p.value, 3))
   }
@@
     ctrp_ge_ttest <- t.test(use_data_ctrp$Pearson_GE_Abs ~ use_data_ctrp$InG2P)
-    ctrp_ge_res <- paste0("t(", round(ctrp_ge_ttest$parameter, 1), ") = ", round(ctrp_ge_ttest$statistic, 2), ", p = ", round(ctrp_ge_ttest$p.value, 3))
+    ctrp_ge_res <- paste0("t(", trunc(ctrp_ge_ttest$parameter), ") = ", round(ctrp_ge_ttest$statistic, 2), ", p = ", round(ctrp_ge_ttest$p.value, 3))
   }
@@
     ctrp_cn_ttest <- t.test(use_data_ctrp$Pearson_CN_Abs ~ use_data_ctrp$InG2P)
-    ctrp_cn_res <- paste0("t(", round(ctrp_cn_ttest$parameter, 1), ") = ", round(ctrp_cn_ttest$statistic, 2), ", p = ", round(ctrp_cn_ttest$p.value, 3))
+    ctrp_cn_res <- paste0("t(", trunc(ctrp_cn_ttest$parameter), ") = ", round(ctrp_cn_ttest$statistic, 2), ", p = ", round(ctrp_cn_ttest$p.value, 3))
   }
@@
     gdsc_ge_ttest <- t.test(use_data_gdsc$Pearson_GE_Abs ~ use_data_gdsc$InG2P)
-    gdsc_ge_res <- paste0("t(", round(gdsc_ge_ttest$parameter, 1), ") = ", round(gdsc_ge_ttest$statistic, 2), ", p = ", round(gdsc_ge_ttest$p.value, 3))
+    gdsc_ge_res <- paste0("t(", trunc(gdsc_ge_ttest$parameter), ") = ", round(gdsc_ge_ttest$statistic, 2), ", p = ", round(gdsc_ge_ttest$p.value, 3))
   }
@@
     gdsc_cn_ttest <- t.test(use_data_gdsc$Pearson_CN_Abs ~ use_data_gdsc$InG2P)
-    gdsc_cn_res <- paste0("t(", round(gdsc_cn_ttest$parameter, 1), ") = ", round(gdsc_cn_ttest$statistic, 2), ", p = ", round(gdsc_cn_ttest$p.value, 3))
+    gdsc_cn_res <- paste0("t(", trunc(gdsc_cn_ttest$parameter), ") = ", round(gdsc_cn_ttest$statistic, 2), ", p = ", round(gdsc_cn_ttest$p.value, 3))
   }
@@
                           t_statistic_GE = c(round(ccle_ge_ttest$statistic, 3), round(ctrp_ge_ttest$statistic, 3), round(gdsc_ge_ttest$statistic, 3)),
-                          df_GE = c(round(ccle_ge_ttest$parameter, 3), round(ctrp_ge_ttest$parameter, 3), round(gdsc_ge_ttest$parameter, 3)),
+                          df_GE = c(trunc(ccle_ge_ttest$parameter), trunc(ctrp_ge_ttest$parameter), trunc(gdsc_ge_ttest$parameter)),
                           p_value_GE = c(round(ccle_ge_ttest$p.value, 3), round(ctrp_ge_ttest$p.value, 3), round(gdsc_ge_ttest$p.value, 3)),
@@
                           t_statistic_CN = c(round(ccle_cn_ttest$statistic, 3), round(ctrp_cn_ttest$statistic, 3), round(gdsc_cn_ttest$statistic, 3)),
-                          df_CN = c(round(ccle_cn_ttest$parameter, 3), round(ctrp_cn_ttest$parameter, 3), round(gdsc_cn_ttest$parameter, 3)),
+                          df_CN = c(trunc(ccle_cn_ttest$parameter), trunc(ctrp_cn_ttest$parameter), trunc(gdsc_cn_ttest$parameter)),
                           p_value_CN = c(round(ccle_cn_ttest$p.value, 3), round(ctrp_cn_ttest$p.value, 3), round(gdsc_cn_ttest$p.value, 3)),
@@
 ```{r}
-g2p <- read.delim("./data_munging/g2p_full_level_A_dataset_NEW_NOV_27.csv", sep = "\t", header = TRUE)
-colnames(g2p)[colnames(g2p) == "Phenotype.ID"] <- "grouped_general_doid"
+g2p <- read.delim("./data_munging/g2p_full_level_A_dataset_NEW_DEC_2_2018_withGroupedLineages.csv", sep = "\t", header = TRUE)
+g2p[, 1:2] <- NULL
 g2p <- merge(g2p, lineage_converter, by = "grouped_general_doid", all.x = TRUE)
@@
 crispr_signif_g2p_gene <- readRDS("./data_munging/rds/crispr_signif_g2p_gene.rds")
+crispr_signif_g2p_gene <- rbind(crispr_signif_g2p_gene, c("G6PD", rep(NA, 11)))
 knitr::kable(crispr_signif_g2p_gene[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results for Level A point mutations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
@@
 
+#### CRISPR
+
+```{r fig.height=1.5, fig.width=12}
+crispr_signif_g2p_gene$y_label <- "CRISPR"
+crispr_signif_g2p_gene$Hugo_Symbol <- factor(crispr_signif_g2p_gene$Hugo_Symbol, levels = g2p_genes)
+crispr_signif_g2p_gene$p <- as.numeric(as.character(crispr_signif_g2p_gene$p))
+
+crispr_mut_heatmap_plot <- ggplot(data = crispr_signif_g2p_gene, aes(x = Hugo_Symbol, y = y_label)) +
+  geom_tile(aes(fill = p)) +
+  scale_fill_gradientn(colors = c("darkgreen", "white", "white"), values = c(0, 0.05, 1), na.value = "darksalmon") +
+  scale_x_discrete(drop = FALSE) +
+  theme(axis.title.y = element_blank(), axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 10)) +
+  labs(x = "Gene")
+
+# write.table(crispr_signif_g2p_gene, file = "~/Desktop/crispr_signif_g2p_gene_20181203.csv", quote = FALSE, sep = ",", row.names = FALSE)
+# ggsave("./plots/manuscript/crispr_mut_heatmap_plot_example.png", crispr_mut_heatmap_plot, device = "png", dpi = 450, width = 12, height = 1.5, units = "in")
+```
+
 #### Mutation status
@@
 gdsc_p_ttest <- t.test(gdsc_druggene_summ$p ~ gdsc_druggene_summ$InG2P)
-gdsc_p_ttest_res <- paste0("t(", round(gdsc_p_ttest$parameter, 0), ") = ", round(gdsc_p_ttest$statistic, 2), ", p = ", round(gdsc_p_ttest$p.value, 2))
+gdsc_p_ttest_res <- paste0("t(", round(gdsc_p_ttest$parameter, 0), ") = ", round(gdsc_p_ttest$statistic, 2), ", p = ", formatC(gdsc_p_ttest$p.value, digits = 2, format = "f"))
 
@@
 
-# ggsave("./plots/manuscript/g2p_druggene_mut_plot.png", g2p_druggene_mut_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
+ggsave("./plots/manuscript/g2p_druggene_mut_plot.png", g2p_druggene_mut_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
 ```
@@
 
-ggsave("./plots/manuscript/g2p_druggene_cn_plot.png", g2p_druggene_cn_plot, device = "png", dpi = 450, width = 12, height = 5.5, units = "in")
+# ggsave("./plots/manuscript/g2p_druggene_cn_plot.png", g2p_druggene_cn_plot, device = "png", dpi = 450, width = 12, height = 5.5, units = "in")
 ```
@@
 g2p_druggene_all_summ_stats$n_true <- TRUE
-g2p_druggene_all_summ_stats <- g2p_druggene_all_summ_stats %>% drop_na(p) %>% group_by(Dataset, InG2P) %>% summarize(p_mean = round(mean(p), 2), p_sd = round(sd(p), 2), n = sum(n_true), n_signif = sum(p < 0.05))
+g2p_druggene_all_summ_stats <- g2p_druggene_all_summ_stats %>% drop_na(p) %>% group_by(Dataset, InG2P) %>% summarize(p_mean = round(mean(p), 2), p_sd = round(sd(p), 2), n = sum(n_true), n_signif = sum(p < 0.05), n_sig_perc = n_signif / n * 100)
 ```
@@
           ge_n_signif = sum(Pearson_Pval_GE < 0.05),
+          ge_n_sig_perc = ge_n_signif / ge_n * 100,
           cn_mean = round(mean(Pearson_CN_Abs), 3),
@@
           cn_n = sum(n_true),
-          cn_n_signif = sum(Pearson_Pval_CN < 0.05))
+          cn_n_signif = sum(Pearson_Pval_CN < 0.05),
+          cn_n_sig_perc = cn_n_signif / cn_n * 100)
 

### 2018-12-05 manuscript.Rmd
start on lineage-specific analysis for manuscript

@@
 }
+
 # WilcoxonByDrugAllGenes <- function(melt_file, grid_file, data_name) {
@@
 ```{r}
+# levels(g2p_filt$Phenotype.Description)
+unique(g2p_filt$group_general_lineage_name)
+levels(g2p_filt$group_general_lineage_name)
+
 g2p_nonCID <- subset(g2p, !grepl("^CID", g2p$DrugID))
@@
 ```{r}
+length(unique(ccle_data_g2p_grid$Drug))
+length(unique(ccle_data_g2p_grid$Drug_Gene))
+```
+
+```{r}
 test_ccle <- ccle_data_ptmuts %>% group_by(Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()
@@
 test_gdsc <- gdsc_data_ptmuts %>% group_by(Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()
+```
+
+```{r}
+unique(crispr_data_g2p$lineage_name)
 ```
@@
 crispr_data_signif_g2p_lineage_plot <- ggplot(data = crispr_data_signif_g2p_lineage, aes(x = group_general_lineage_name, y = Score)) +
-  facet_wrap(~ Hugo_Symbol, nrow = 6, scales = "free_y") +
+  facet_wrap(~ Hugo_Symbol, drop = FALSE, nrow = 6, scales = "free_y") +
   geom_point(aes(color = Mutation_Status_Nonsilent), alpha = 0.5) +
@@
 knitr::kable(ccle_signif_g2p_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+
+knitr::kable(ccle_signif_g2p_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 sd(g2p_gene_tally$n)
+
+g2p_druggenelin_tally <- g2p_filt %>% group_by(Drug, Gene, Drug_Gene, group_general_lineage_name) %>% tally() %>% drop_na()
+length(unique(g2p_druggenelin_tally$Drug))
+length(unique(g2p_druggenelin_tally$Gene))
+unique(g2p_filt$Phenotype.Description)
 ```
@@
 
-### All
+### Mut, GE, and CN
+
+#### Lineage-agnostic
 
@@
           cn_n_sig_perc = cn_n_signif / cn_n * 100)
-
+```
+
+Example p-value and Pearson correlation coefficient derivations:
+```{r}
 ctrp_grid_summary_data <- filter(ctrp_data_g2p_grid, Drug_Gene == "afatinib_ERBB2")
@@
 # ggsave("./plots/manuscript/ctrp_grid_summary_cn_plot.png", ctrp_grid_summary_cn_plot, device = "png", dpi = 450, width = 5, height = 4, units = "in")
+```
+
+#### By lineage
+
+Deriving n for Bonferroni correction:
+```{r}
+ttest_summ_res_mut <- g2p_druggenelin_p_ttest_res_list[, c("p_value", "Dataset", "group_general_lineage_name")]
+ttest_summ_res_mut$Metric <- "Mutation Status"
+mut_alphas <- ttest_summ_res_mut %>% drop_na(p_value) %>% group_by(Dataset) %>% tally()
+mut_alphas$alpha_adj <- 0.05 / mut_alphas$n
+
+ttest_summ_res_ge <- druggenelin_pearson_ttest_res_list[, c("p_value_GE", "Dataset", "group_general_lineage_name")]
+colnames(ttest_summ_res_ge) <- c("p_value", "Dataset", "group_general_lineage_name")
+ttest_summ_res_ge$Metric <- "Gene Expression"
+ge_alphas <- ttest_summ_res_ge %>% drop_na(p_value) %>% group_by(Dataset) %>% tally()
+ge_alphas$alpha_adj <- 0.05 / ge_alphas$n
+
+ttest_summ_res_cn <- druggenelin_pearson_ttest_res_list[, c("p_value_CN", "Dataset", "group_general_lineage_name")]
+colnames(ttest_summ_res_cn) <- c("p_value", "Dataset", "group_general_lineage_name")
+ttest_summ_res_cn$Metric <- "Copy Number"
+cn_alphas <- ttest_summ_res_cn %>% drop_na(p_value) %>% group_by(Dataset) %>% tally()
+cn_alphas$alpha_adj <- 0.05 / cn_alphas$n
+```
+
+Facted lineage summaries:
+```{r fig.height=4, fig.width=12}
+ttest_mut_summ_facet <- ggplot(data = ttest_summ_res, aes(x = p_value, fill = Dataset, color = Dataset)) +
+  facet_grid(Metric ~ Dataset) +
+  geom_histogram(bins = 40, binwidth = 0.025, boundary = 0, closed = "left") +
+  scale_y_continuous(breaks = c(0:6), labels = c(0:6)) +
+  scale_x_continuous(breaks = seq(0, 1, by = 0.1), expand = c(0.01, 0.01)) +
+  scale_fill_manual(values = c("CCLE" = "palegreen3", "CTRP" = "slategray3", "GDSC" = "paleturquoise3")) +
+  scale_color_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
+  theme(legend.position = c(0.5, 1.7), legend.direction = "horizontal", panel.grid.minor.y = element_blank()) +
+  labs(x = "P-value", y = "Frquency")
+ttest_mut_summ_facet
+
+# ggsave("./plots/manuscript/all_druggenelin_ttest_summ_facet_plot.png", ttest_mut_summ_facet, device = "png", dpi = 450, width = 12, height = 4, units = "in")
+```
+
+Stacked lineage summaries:
+```{r fig.height=7, fig.width=12}
+# margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
+ttest_summ_res <- rbind(ttest_summ_res_mut, ttest_summ_res_ge, ttest_summ_res_cn)
+ttest_summ_res$Metric <- factor(ttest_summ_res$Metric, levels = c("Mutation Status", "Gene Expression", "Copy Number"))
+
+ttest_mut_summ_plot <- ggplot(data = g2p_druggenelin_p_ttest_res_list, aes(x = p_value)) +
+  geom_histogram(aes(fill = Dataset, color = Dataset), position = "stack", bins = 40, binwidth = 0.025, boundary = 0, closed = "left") +
+  scale_y_continuous(breaks = c(0:6), labels = c(0:6)) +
+  scale_x_continuous(breaks = seq(0, 1, by = 0.05), expand = c(0.01, 0.01)) +
+  scale_fill_manual(values = c("CCLE" = "palegreen3", "CTRP" = "slategray3", "GDSC" = "paleturquoise3")) +
+  scale_color_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
+  theme(legend.position = c(0.5, 1.7), legend.direction = "horizontal", panel.grid.minor.y = element_blank(), panel.grid.minor.x = element_blank(), plot.margin = unit(c(30, 5.5, 1, 5.5), "pt")) +
+  labs(x = "P-value", y = "Frquency", title = "Mutation status")
+
+ttest_ge_summ_plot <- ggplot(data = druggenelin_pearson_ttest_res_list, aes(x = p_value_GE)) +
+  geom_histogram(aes(fill = Dataset, color = Dataset), position = "stack", bins = 40, binwidth = 0.025, boundary = 0, closed = "left") +
+  scale_y_continuous(breaks = c(0:7), labels = c(0:7), expand = c(0.01, 0.01)) +
+  scale_x_continuous(breaks = seq(0, 1, by = 0.05), expand = c(0.01, 0.01)) +
+  scale_fill_manual(values = c("CCLE" = "palegreen3", "CTRP" = "slategray3", "GDSC" = "paleturquoise3")) +
+  scale_color_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
+  theme(legend.position = "none", panel.grid.minor.y = element_blank(), panel.grid.minor.x = element_blank(), plot.margin = unit(c(1, 5.5, 1, 5.5), "pt")) +
+  labs(x = "P-value", y = "Frquency", title = "Gene expression")
+
+ttest_cn_summ_plot <- ggplot(data = druggenelin_pearson_ttest_res_list, aes(x = p_value_CN)) +
+  geom_histogram(aes(fill = Dataset, color = Dataset), position = "stack", bins = 40, binwidth = 0.025, boundary = 0, closed = "left") +
+  scale_y_continuous(breaks = c(0:6), labels = c(0:6), expand = c(0.01, 0.01)) +
+  scale_x_continuous(breaks = seq(0, 1, by = 0.05), expand = c(0.01, 0.01)) +
+  scale_fill_manual(values = c("CCLE" = "palegreen3", "CTRP" = "slategray3", "GDSC" = "paleturquoise3")) +
+  scale_color_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
+  theme(legend.position = "none", panel.grid.minor.y = element_blank(), panel.grid.minor.x = element_blank(), plot.margin = unit(c(1, 5.5, 5.5, 5.5), "pt")) +
+  labs(x = "P-value", y = "Frquency", title = "Copy number")
+
+ttest_mut_summ_plot <- ggplot_gtable(ggplot_build(ttest_mut_summ_plot))
+ttest_ge_summ_plot <- ggplot_gtable(ggplot_build(ttest_ge_summ_plot))
+ttest_cn_summ_plot <- ggplot_gtable(ggplot_build(ttest_cn_summ_plot))
+
+# p_maxWidth <-  grid::unit.pmax(ttest_mut_summ_plot$widths, ttest_ge_summ_plot$widths, ttest_cn_summ_plot$widths)
+# ttest_mut_summ_plot$widths <- as.list(p_maxWidth)
+# ttest_ge_summ_plot$widths <- as.list(p_maxWidth)
+# ttest_cn_summ_plot$widths <- as.list(p_maxWidth)
+
+ttest_summ_plot <- cowplot::plot_grid(ttest_mut_summ_plot, ttest_ge_summ_plot,ttest_cn_summ_plot, nrow = 3, rel_heights = c(1, 1.6, 1.6))
+ttest_summ_plot
+
+# ggsave("./plots/manuscript/all_druggenelin_ttest_summ_plot.png", ttest_summ_plot, device = "png", dpi = 450, width = 12, height = 7, units = "in")
 ```

### 2018-12-06 manuscript.Rmd
g2p DGL stats, new summ plots

@@
 library(bsselectR)
+library(cowplot)
+theme_set(theme_light())
 library(data.table)
@@
 library(ggrepel)
+library(gridExtra)
 library(ggsignif)
@@
 g2p$Drug_Gene <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene), NA, paste0(g2p$Drug, "_", g2p$Gene))
+g2p$Drug_Gene_Lin <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene) | is.na(g2p$group_general_lineage_name), NA, paste0(g2p$Drug, "_", g2p$Gene, "_", g2p$group_general_lineage_name))
 g2p$position <- paste0("g.chr", g2p$Chromosome, ":", g2p$End, g2p$Ref, ">", g2p$Alt)
@@
 
+g2p_druggenelins <-  unique(g2p_filt$Drug_Gene_Lin[!is.na(g2p_filt$Drug_Gene_Lin)])
 g2p_drug_genes <- unique(g2p_filt$Drug_Gene[!is.na(g2p_filt$Drug_Gene)])
@@
 ccle_data$Drug_Gene <- paste0(ccle_data$Drug, "_", ccle_data$Hugo_Symbol)
+ccle_data$Drug_Gene_Lin <- paste0(ccle_data$Drug, "_", ccle_data$Hugo_Symbol, "_", ccle_data$group_general_lineage_name)
 saveRDS(ccle_data, "./data_munging/rds/ccle_data_18Q4_g2pgenes.rds", compress = "xz")
@@
 ctrp_data$Drug_Gene <- paste0(ctrp_data$Drug, "_", ctrp_data$Hugo_Symbol)
+ctrp_data$Drug_Gene_Lin <- paste0(ctrp_data$Drug, "_", ctrp_data$Hugo_Symbol, "_", ctrp_data$group_general_lineage_name)
 saveRDS(ctrp_data, "./data_munging/rds/ctrp_data_18Q4_g2pgenes.rds", compress = "xz")
@@
 gdsc_data$Drug_Gene <- paste0(gdsc_data$Drug, "_", gdsc_data$Hugo_Symbol)
+gdsc_data$Drug_Gene_Lin <- paste0(gdsc_data$Drug, "_", gdsc_data$Hugo_Symbol, "_", gdsc_data$group_general_lineage_name)
 saveRDS(gdsc_data, "./data_munging/rds/gdsc_data_18Q4_g2pgenes.rds", compress = "xz")
@@
 gdsc_data_g2p$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
+
+# Filter drug screen datasets for G2P drug-gene-lineage associations
+ccle_data_g2p_dgl <- filter(ccle_data_ptmuts, Drug_Gene_Lin %in% g2p_druggenelins)
+ccle_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(ccle_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
+ctrp_data_g2p_dgl <- filter(ctrp_data_ptmuts, Drug_Gene_Lin %in% g2p_druggenelins)
+ctrp_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
+gdsc_data_g2p_dgl <- filter(gdsc_data_ptmuts, Drug_Gene_Lin %in% g2p_druggenelins)
+gdsc_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
 
@@
 ```{r, eval=FALSE}
-ccle_signif_g2p_lineage <- lapply(unique(ccle_data_g2p_grid$Drug), WilcoxonByDrug, dataset = ccle_data_g2p_grid, data_name = "ccle", grouping_var = "lineage")
-names(ccle_signif_g2p_lineage) <- unique(ccle_signif_g2p_lineage$Drug)
-ccle_signif_g2p_lineage <- rbindlist(ccle_signif_g2p_lineage, use.names = TRUE)
+ccle_signif_grid_lineage <- lapply(unique(ccle_data_g2p_grid$Drug), WilcoxonByDrug, dataset = ccle_data_g2p_grid, data_name = "ccle", grouping_var = "lineage")
+names(ccle_signif_grid_lineage) <- unique(ccle_signif_grid_lineage$Drug)
+ccle_signif_grid_lineage <- rbindlist(ccle_signif_grid_lineage, use.names = TRUE)
+ccle_signif_grid_lineage <- ccle_signif_grid_lineage[order(ccle_signif_grid_lineage$p),]
+saveRDS(ccle_signif_grid_lineage, "./data_munging/rds/ccle_signif_grid_lineage.rds")
+
+ccle_signif_g2p_lineage <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene_Lin", data = ccle_data_g2p_dgl, method = "wilcox.test", p.adjust.method = "BH")
+ccle_signif_g2p_lineage <- adj_signif(ccle_signif_g2p_lineage)
 ccle_signif_g2p_lineage <- ccle_signif_g2p_lineage[order(ccle_signif_g2p_lineage$p),]
@@
 ccle_signif_g2p_lineage <- readRDS("./data_munging/rds/ccle_signif_g2p_lineage.rds")
-knitr::kable(ccle_signif_g2p_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-
-knitr::kable(ccle_signif_g2p_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+ccle_signif_grid_lineage <- readRDS("./data_munging/rds/ccle_signif_grid_lineage.rds")
+
+knitr::kable(ccle_signif_g2p_lineage[, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+
+knitr::kable(ccle_signif_grid_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 ```{r, eval=FALSE}
-ctrp_signif_g2p_lineage <- lapply(unique(ctrp_data_g2p_grid$Drug), WilcoxonByDrug, dataset = ctrp_data_g2p_grid, data_name = "ctrp", grouping_var = "lineage")
-names(ctrp_signif_g2p_lineage) <- unique(ctrp_signif_g2p_lineage$Drug)
-ctrp_signif_g2p_lineage <- rbindlist(ctrp_signif_g2p_lineage, use.names = TRUE)
+ctrp_signif_grid_lineage <- lapply(unique(ctrp_data_g2p_grid$Drug), WilcoxonByDrug, dataset = ctrp_data_g2p_grid, data_name = "ctrp", grouping_var = "lineage")
+names(ctrp_signif_grid_lineage) <- unique(ctrp_signif_grid_lineage$Drug)
+ctrp_signif_grid_lineage <- rbindlist(ctrp_signif_grid_lineage, use.names = TRUE)
+ctrp_signif_grid_lineage <- ctrp_signif_grid_lineage[order(ctrp_signif_grid_lineage$p),]
+saveRDS(ctrp_signif_grid_lineage, "./data_munging/rds/ctrp_signif_grid_lineage.rds")
+
+ctrp_signif_g2p_lineage <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene_Lin", data = ctrp_data_g2p_dgl, method = "wilcox.test", p.adjust.method = "BH")
+ctrp_signif_g2p_lineage <- adj_signif(ctrp_signif_g2p_lineage)
 ctrp_signif_g2p_lineage <- ctrp_signif_g2p_lineage[order(ctrp_signif_g2p_lineage$p),]
@@
 ctrp_signif_g2p_lineage <- readRDS("./data_munging/rds/ctrp_signif_g2p_lineage.rds")
-knitr::kable(ctrp_signif_g2p_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+ctrp_signif_grid_lineage <- readRDS("./data_munging/rds/ctrp_signif_grid_lineage.rds")
+
+knitr::kable(ctrp_signif_g2p_lineage[, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+
+knitr::kable(ctrp_signif_grid_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 ```{r, eval=FALSE}
-gdsc_signif_g2p_lineage <- lapply(unique(gdsc_data_g2p_grid$Drug), WilcoxonByDrug, dataset = gdsc_data_g2p_grid, data_name = "gdsc", grouping_var = "lineage")
-names(gdsc_signif_g2p_lineage) <- unique(gdsc_signif_g2p_lineage$Drug)
-gdsc_signif_g2p_lineage <- rbindlist(gdsc_signif_g2p_lineage, use.names = TRUE)
+gdsc_signif_grid_lineage <- lapply(unique(gdsc_data_g2p_grid$Drug), WilcoxonByDrug, dataset = gdsc_data_g2p_grid, data_name = "gdsc", grouping_var = "lineage")
+names(gdsc_signif_grid_lineage) <- unique(gdsc_signif_grid_lineage$Drug)
+gdsc_signif_grid_lineage <- rbindlist(gdsc_signif_grid_lineage, use.names = TRUE)
+gdsc_signif_grid_lineage <- gdsc_signif_grid_lineage[order(gdsc_signif_grid_lineage$p),]
+saveRDS(gdsc_signif_grid_lineage, "./data_munging/rds/gdsc_signif_grid_lineage.rds")
+
+gdsc_signif_g2p_lineage <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene_Lin", data = gdsc_data_g2p_dgl, method = "wilcox.test", p.adjust.method = "BH")
+gdsc_signif_g2p_lineage <- adj_signif(gdsc_signif_g2p_lineage)
 gdsc_signif_g2p_lineage <- gdsc_signif_g2p_lineage[order(gdsc_signif_g2p_lineage$p),]
@@
 gdsc_signif_g2p_lineage <- readRDS("./data_munging/rds/gdsc_signif_g2p_lineage.rds")
-knitr::kable(gdsc_signif_g2p_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+gdsc_signif_grid_lineage <- readRDS("./data_munging/rds/gdsc_signif_grid_lineage.rds")
+
+knitr::kable(gdsc_signif_g2p_lineage[, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+
+knitr::kable(gdsc_signif_grid_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
-## Drugscreen: G2P evidence
+## G2P evidence
 
@@
   geom_tile(aes(fill = p)) +
-  scale_fill_gradientn(colors = c("darkgreen", "white", "white"), values = c(0, 0.05, 1), na.value = "darksalmon") +
+  scale_fill_gradientn(colors = c("darkgreen", "honeydew", "white"), values = c(0, 0.05, 1), na.value = "darksalmon") +
   scale_x_discrete(drop = FALSE) +
@@
   labs(x = "Gene")
+crispr_mut_heatmap_plot
 
@@
 # ggsave("./plots/manuscript/crispr_mut_heatmap_plot_example.png", crispr_mut_heatmap_plot, device = "png", dpi = 450, width = 12, height = 1.5, units = "in")
+```
+
+```{r fig.height=5, fig.width=12}
+crispr_res_mut <- select(crispr_signif_g2p_gene, Hugo_Symbol, p)
+crispr_res_mut$corr <- 0
+crispr_res_mut$Metric <- "Mutation Status"
+crispr_res_mut$p_log10 <- -log10(crispr_res_mut$p)
+
+crispr_pearson_res_GE <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>%
+                    summarize(p = cor.test(y = Score, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
+                              corr = cor.test(y = Score, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
+                              Metric = "Gene Expression")
+subset(crispr_pearson_res_GE, p < 0.05)
+
+crispr_pearson_res_CN <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>%
+                    summarize(p = cor.test(y = Score, x = CN, method = "pearson", use = "complete.obs")$p.value,
+                              corr = cor.test(y = Score, x = CN, method = "pearson", use = "complete.obs")$estimate,
+                              Metric = "Copy Number")
+subset(crispr_pearson_res_CN, p < 0.05)
+
+crispr_pearson_res <- rbind(crispr_pearson_res_GE, crispr_pearson_res_CN)
+crispr_pearson_res$Metric <- factor(crispr_pearson_res$Metric, levels = c("Gene Expression", "Copy Number"))
+crispr_pearson_res$p_log10 <- -log10(crispr_pearson_res$p)
+
+crispr_summ_res_mut_plot <- ggplot(data = subset(crispr_res_mut, p < 0.05)) +
+  facet_grid(~ Metric) +
+  scale_y_continuous(breaks = seq(0, 50, by = 5), labels = seq(0, 50, by = 5)) +
+  coord_cartesian(ylim = c(0, 50)) +
+  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
+  geom_label_repel(mapping = aes(y = p_log10, x = corr, label = Hugo_Symbol, color = Metric), force = 10, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
+  theme(legend.position = "none", panel.grid.major.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(5.5, 1.5, 5.5, 5.5), "pt")) +
+  scale_color_manual(values = c("Mutation Status" = "darkorchid4")) +
+  labs(y = "-log10(p-value)")
+
+crispr_summ_res_pearson_plot <- ggplot(data = subset(crispr_pearson_res, p < 0.05)) +
+  facet_grid(~ Metric, scales = "free_x", space = "free") +
+  scale_y_continuous(breaks = seq(0, 50, by = 5), labels = seq(0, 50, by = 5)) +
+  scale_x_continuous(breaks = seq(-0.6, 0.3, by = 0.1), labels = formatC(seq(-0.6, 0.3, by = 0.1), digits = 2, format = "f")) +
+  coord_cartesian(ylim = c(0, 50)) +
+  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
+  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
+  geom_label_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Hugo_Symbol), force = 10, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
+  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
+  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
+  labs(x = "Pearson correlation coefficient (r)")
+
+crispr_genomic_features_summ_plot <- plot_grid(crispr_summ_res_mut_plot, crispr_summ_res_pearson_plot, align = "h", rel_widths = c(1, 5))
+crispr_genomic_features_summ_plot
+
+# ggsave("./plots/manuscript/crispr_genomic_features_summ_plot.png", crispr_genomic_features_summ_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
 ```
@@
 
-g2p_druggene_p_summ_plot <- ggplot(data = g2p_druggene_p_summ_melt, aes(x = p, y = n, shape = Dataset, color = Dataset)) +
-  geom_point(size = 2) +
-  scale_color_manual(values = c("green3", "darkslategray4", "darkturquoise")) +
-  labs(x = "Gene-drug association p-value by mutation status", y = "Number of level A G2P associations")
-g2p_druggene_p_summ_plot
+# g2p_druggene_p_summ_plot <- ggplot(data = g2p_druggene_p_summ_melt, aes(x = p, y = n, shape = Dataset, color = Dataset)) +
+#   geom_point(size = 2) +
+#   scale_color_manual(values = c("green3", "darkslategray4", "darkturquoise")) +
+#   labs(x = "Gene-drug association p-value by mutation status", y = "Number of level A G2P associations")
+# g2p_druggene_p_summ_plot
 # ggsave("./plots/manuscript/g2p_druggene_p_summ_plot.png", g2p_druggene_p_summ_plot, device = "png", dpi = 450, width = 8, height = 4, units = "in")
@@
   facet_wrap(~ Dataset, scales = "free_x") +
-  geom_violin(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.5) +
-  geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.75, width = 0.25) +
+  geom_violin(mapping = aes(color = InG2P, fill = InG2P, y = p, x = InG2P), alpha = 0.35) +
+  geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), width = 0.25) +
   scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
   coord_flip() +
@@
   facet_wrap(~ Dataset) +
-  geom_violin(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.5) +
-  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
+  geom_violin(mapping = aes(color = InG2P, fill = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.35) +
+  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), width = 0.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
   scale_y_continuous(breaks = seq(0, 0.65, by = 0.1), labels = seq(0, 0.65, by = 0.1)) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
   coord_flip(ylim = c(0, 0.65)) +
@@
   facet_wrap(~ Dataset) +
-  geom_violin(mapping = aes(color = InG2P, y = Pearson_CN_Abs, x = InG2P), alpha = 0.5) +
-  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_CN_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
+  geom_violin(mapping = aes(color = InG2P, fill = InG2P, y = Pearson_CN_Abs, x = InG2P), alpha = 0.35) +
+  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_CN_Abs, x = InG2P), width = 0.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
   scale_y_continuous(breaks = seq(0, 0.5, by = 0.1), labels = seq(0, 0.5, by = 0.1)) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
   coord_flip(ylim = c(0, 0.5)) +
@@
 
+#### Summary: Test plots
+
+```{r fig.height=4, fig.width=12}
+ccle_res_mut <- select(ccle_signif_g2p, Drug_Gene, p, Drug_Gene_Ordered)
+ccle_res_mut$corr <- 0
+ccle_res_mut$Metric <- "Mutation Status"
+ccle_res_mut$p_log10 <- -log10(ccle_res_mut$p)
+ccle_res_mut$Dataset <- "CCLE"
+ccle_pearson_res_GE <- select(filter(ccle_pearson_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_GE, Pearson_Pval_GE, Dataset)
+colnames(ccle_pearson_res_GE) <- c("Drug_Gene", "corr", "p", "Dataset")
+ccle_pearson_res_GE$Metric <- "Gene Expression"
+subset(ccle_pearson_res_GE, p < 0.05)
+ccle_pearson_res_CN <- select(filter(ccle_pearson_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_CN, Pearson_Pval_CN, Dataset)
+colnames(ccle_pearson_res_CN) <- c("Drug_Gene", "corr", "p", "Dataset")
+ccle_pearson_res_CN$Metric <- "Copy Number"
+subset(ccle_pearson_res_CN, p < 0.05)
+ccle_pearson_res_filt <- rbind(ccle_pearson_res_GE, ccle_pearson_res_CN)
+ccle_pearson_res_filt$Metric <- factor(ccle_pearson_res_filt$Metric, levels = c("Gene Expression", "Copy Number"))
+ccle_pearson_res_filt$p_log10 <- -log10(ccle_pearson_res_filt$p)
+
+ccle_summ_res_mut_plot <- ggplot(data = subset(ccle_res_mut, p < 0.05)) +
+  facet_grid(Dataset ~ Metric) +
+  scale_y_continuous(breaks = seq(0, 35, by = 5), labels = seq(0, 35, by = 5)) +
+  coord_cartesian(ylim = c(0, 35)) +
+  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
+  geom_label_repel(mapping = aes(y = p_log10, x = corr, label = Drug_Gene, color = Metric), force = 10, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
+  theme(legend.position = "none", panel.grid.major.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(5.5, 1.5, 5.5, 5.5), "pt"), strip.background.y = element_blank(), strip.text.y = element_blank()) +
+  scale_color_manual(values = c("Mutation Status" = "darkorchid4")) +
+  labs(y = "-log10(p-value)")
+
+ccle_summ_res_pearson_plot <- ggplot(data = subset(ccle_pearson_res_filt, p < 0.05)) +
+  facet_grid(Dataset ~ Metric) +
+  coord_cartesian(ylim = c(0, 35)) +
+  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
+  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
+  geom_label_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 10, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
+  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
+  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
+  labs(x = "Pearson correlation coefficient (r)")
+
+ccle_genomic_features_summ_plot <- plot_grid(ccle_summ_res_mut_plot, ccle_summ_res_pearson_plot, align = "h", rel_widths = c(1, 5))
+ccle_genomic_features_summ_plot
+
+# ggsave("./plots/manuscript/ccle_genomic_features_summ_plot.png", ccle_genomic_features_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
+```
+
+```{r fig.height=6, fig.width=12}
+ctrp_res_mut <- select(ctrp_signif_g2p, Drug_Gene, p, Drug_Gene_Ordered)
+ctrp_res_mut$corr <- 0
+ctrp_res_mut$Metric <- "Mutation Status"
+ctrp_res_mut$p_log10 <- -log10(ctrp_res_mut$p)
+ctrp_res_mut$Dataset <- "CTRP"
+ctrp_pearson_res_GE <- select(filter(ctrp_pearson_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_GE, Pearson_Pval_GE, Dataset)
+colnames(ctrp_pearson_res_GE) <- c("Drug_Gene", "corr", "p", "Dataset")
+ctrp_pearson_res_GE$Metric <- "Gene Expression"
+subset(ctrp_pearson_res_GE, p < 0.05)
+ctrp_pearson_res_CN <- select(filter(ctrp_pearson_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_CN, Pearson_Pval_CN, Dataset)
+colnames(ctrp_pearson_res_CN) <- c("Drug_Gene", "corr", "p", "Dataset")
+ctrp_pearson_res_CN$Metric <- "Copy Number"
+subset(ctrp_pearson_res_CN, p < 0.05)
+ctrp_pearson_res_filt <- rbind(ctrp_pearson_res_GE, ctrp_pearson_res_CN)
+ctrp_pearson_res_filt$Metric <- factor(ctrp_pearson_res_filt$Metric, levels = c("Gene Expression", "Copy Number"))
+ctrp_pearson_res_filt$p_log10 <- -log10(ctrp_pearson_res_filt$p)
+
+ctrp_summ_res_mut_plot <- ggplot(data = subset(ctrp_res_mut, p < 0.05)) +
+  facet_grid(Dataset ~ Metric) +
+  # scale_y_continuous(breaks = seq(0, 30, by = 5), labels = seq(0, 30, by = 5)) +
+  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
+  geom_label_repel(mapping = aes(y = p_log10, x = corr, label = Drug_Gene_Ordered, color = Metric), force = 10, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 1) +
+  theme(legend.position = "none", panel.grid.major.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(5.5, 1.5, 5.5, 5.5), "pt"), strip.background.y = element_blank(), strip.text.y = element_blank()) +
+  scale_color_manual(values = c("Mutation Status" = "darkorchid4")) +
+  labs(y = "-log10(p-value)")
+
+ctrp_summ_res_pearson_plot <- ggplot(data = subset(ctrp_pearson_res_filt, p < 0.05)) +
+  facet_grid(Dataset ~ Metric) +
+  scale_y_continuous(breaks = seq(0, 30, by = 5), labels = seq(0, 30, by = 5)) +
+  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
+  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
+  geom_label_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 10, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
+  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
+  theme(legend.position = "none", plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
+  labs(x = "Pearson correlation coefficient (r)")
+
+ctrp_genomic_features_summ_plot <- plot_grid(ctrp_summ_res_mut_plot, ctrp_summ_res_pearson_plot, align = "h", rel_widths = c(1, 5))
+ctrp_genomic_features_summ_plot
+
+# ggsave("./plots/manuscript/ccle_genomic_features_summ_plot.png", ccle_genomic_features_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
+```
+
 ### By lineage
@@
 cn_alphas$alpha_adj <- 0.05 / cn_alphas$n
+
+ttest_summ_res <- rbind(ttest_summ_res_mut, ttest_summ_res_ge, ttest_summ_res_cn)
+ttest_summ_res$Metric <- factor(ttest_summ_res$Metric, levels = c("Mutation Status", "Gene Expression", "Copy Number"))
 ```
@@
 ```{r fig.height=7, fig.width=12}
-# margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
-ttest_summ_res <- rbind(ttest_summ_res_mut, ttest_summ_res_ge, ttest_summ_res_cn)
-ttest_summ_res$Metric <- factor(ttest_summ_res$Metric, levels = c("Mutation Status", "Gene Expression", "Copy Number"))
+# plot.margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
 

### 2018-12-07 manuscript.Rmd
remade all lineage plotlys/pngs, updated signif Rds files

@@
 library(ggrepel)
+library(ggsignif)
+library(gplots)
 library(gridExtra)
-library(ggsignif)
 library(htmlwidgets)
@@
 library(tidyverse)
+library(VennDiagram)
 ```
@@
   print(paste0("Lineage: ", toupper(lineage)))
-  use_data <- filter(signif_all_lin, group_general_lineage_name == lineage)
+  use_data <- filter(signif_lin_g2p_grid, group_general_lineage_name == lineage)
   use_data$Dataset <- factor(use_data$Dataset, levels = c("CCLE", "CTRP", "GDSC"))
@@
 
-knitr::kable(ccle_signif_g2p_lineage[, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(ccle_signif_g2p_lineage[, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 
@@
 
-knitr::kable(ctrp_signif_g2p_lineage[, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(ctrp_signif_g2p_lineage[, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 
@@
 
-knitr::kable(gdsc_signif_g2p_lineage[, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(gdsc_signif_g2p_lineage[, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 
@@
 crispr_res_mut$p_log10 <- -log10(crispr_res_mut$p)
+subset(crispr_res_mut, p < 0.05)
 
@@
   geom_label_repel(mapping = aes(y = p_log10, x = corr, label = Hugo_Symbol, color = Metric), force = 10, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
-  theme(legend.position = "none", panel.grid.major.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(5.5, 1.5, 5.5, 5.5), "pt")) +
+  theme(legend.position = "none", panel.grid.major.x = element_blank(), panel.grid.minor.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(5.5, 1.5, 5.5, 5.5), "pt")) +
   scale_color_manual(values = c("Mutation Status" = "darkorchid4")) +
@@
 
-#### Summary: Test plots
+#### Summary: Drug screen test plots
 
 ```{r fig.height=4, fig.width=12}
-ccle_res_mut <- select(ccle_signif_g2p, Drug_Gene, p, Drug_Gene_Ordered)
+ccle_res_mut <- select(ccle_signif_g2p, Drug_Gene, p)
 ccle_res_mut$corr <- 0
@@
 ```{r fig.height=6, fig.width=12}
-ctrp_res_mut <- select(ctrp_signif_g2p, Drug_Gene, p, Drug_Gene_Ordered)
+ctrp_res_mut <- select(ctrp_signif_g2p, Drug_Gene, p)
 ctrp_res_mut$corr <- 0
@@
   geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_label_repel(mapping = aes(y = p_log10, x = corr, label = Drug_Gene_Ordered, color = Metric), force = 10, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 1) +
+  geom_label_repel(mapping = aes(y = p_log10, x = corr, label = Drug_Gene, color = Metric), force = 10, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 1) +
   theme(legend.position = "none", panel.grid.major.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(5.5, 1.5, 5.5, 5.5), "pt"), strip.background.y = element_blank(), strip.text.y = element_blank()) +
@@
 ```{r}
-ccle_druggenelin_summ <- ccle_signif_g2p_lineage
+ccle_druggenelin_summ <- ccle_signif_grid_lineage
 ccle_druggenelin_summ$Drug_Gene <- paste0(ccle_druggenelin_summ$Drug, "_", ccle_druggenelin_summ$Hugo_Symbol)
@@
 
-ctrp_druggenelin_summ <- ctrp_signif_g2p_lineage
+ctrp_druggenelin_summ <- ctrp_signif_grid_lineage
 ctrp_druggenelin_summ$Drug_Gene <- paste0(ctrp_druggenelin_summ$Drug, "_", ctrp_druggenelin_summ$Hugo_Symbol)
@@
 
-gdsc_druggenelin_summ <- gdsc_signif_g2p_lineage
+gdsc_druggenelin_summ <- gdsc_signif_grid_lineage
 gdsc_druggenelin_summ$Drug_Gene <- paste0(gdsc_druggenelin_summ$Drug, "_", gdsc_druggenelin_summ$Hugo_Symbol)
@@
 
+DGL overlap:
+```{r}
+dgl_overlap_test_list <- list(CCLE = unique(ccle_data_g2p_dgl$Drug_Gene_Lin),
+                              CTRP = unique(ctrp_data_g2p_dgl$Drug_Gene_Lin),
+                              GDSC = unique(gdsc_data_g2p_dgl$Drug_Gene_Lin))
+
+ItemsList <- venn(dgl_overlap_test_list, show.plot=TRUE)
+```
+
+Test the 102 level-A G2P drug-gene-lineage combinations:
+```{r, eval=FALSE}
+ccle_lineages4pearson <- as.character(unique(ccle_data_g2p_dgl$group_general_lineage_name))[!is.na(as.character(unique(ccle_data_g2p_dgl$group_general_lineage_name)))]
+ccle_signif_ge <- lapply(ccle_lineages4pearson, PearsonByLineage, variable = "GE", dataset = ccle_data_g2p_dgl)
+ccle_signif_ge_all_lin <- rbindlist(ccle_signif_ge, use.names = TRUE)
+ccle_signif_ge_all_lin$Dataset <- "CCLE"
+ccle_signif_cn <- lapply(ccle_lineages4pearson, PearsonByLineage, variable = "CN", dataset = ccle_data_g2p_dgl)
+ccle_signif_cn_all_lin <- rbindlist(ccle_signif_cn, use.names = TRUE)
+ccle_signif_cn_all_lin$Dataset <- "CCLE"
+ccle_signif_all_lin <- merge(ccle_signif_ge_all_lin, ccle_signif_cn_all_lin, by = c("Drug_Gene", "group_general_lineage_name", "n", "Dataset"), all = TRUE)
+
+ctrp_lineages4pearson <- as.character(unique(ctrp_data_g2p_dgl$group_general_lineage_name))[!is.na(as.character(unique(ctrp_data_g2p_dgl$group_general_lineage_name)))]
+ctrp_signif_ge <- lapply(ctrp_lineages4pearson, PearsonByLineage, variable = "GE", dataset = ctrp_data_g2p_dgl)
+ctrp_signif_ge_all_lin <- rbindlist(ctrp_signif_ge, use.names = TRUE)
+ctrp_signif_ge_all_lin$Dataset <- "CTRP"
+ctrp_signif_cn <- lapply(ctrp_lineages4pearson, PearsonByLineage, variable = "CN", dataset = ctrp_data_g2p_dgl)
+ctrp_signif_cn_all_lin <- rbindlist(ctrp_signif_cn, use.names = TRUE)
+ctrp_signif_cn_all_lin$Dataset <- "CTRP"
+ctrp_signif_all_lin <- merge(ctrp_signif_ge_all_lin, ctrp_signif_cn_all_lin, by = c("Drug_Gene", "group_general_lineage_name", "n", "Dataset"), all = TRUE)
+
+gdsc_lineages4pearson <- as.character(unique(gdsc_data_g2p_dgl$group_general_lineage_name))[!is.na(as.character(unique(gdsc_data_g2p_dgl$group_general_lineage_name)))]
+gdsc_signif_ge <- lapply(gdsc_lineages4pearson, PearsonByLineage, variable = "GE", dataset = gdsc_data_g2p_dgl)
+gdsc_signif_ge_all_lin <- rbindlist(gdsc_signif_ge, use.names = TRUE)
+gdsc_signif_ge_all_lin$Dataset <- "GDSC"
+gdsc_signif_cn <- lapply(gdsc_lineages4pearson, PearsonByLineage, variable = "CN", dataset = gdsc_data_g2p_dgl)
+gdsc_signif_cn_all_lin <- rbindlist(gdsc_signif_cn, use.names = TRUE)
+gdsc_signif_cn_all_lin$Dataset <- "GDSC"
+gdsc_signif_all_lin <- merge(gdsc_signif_ge_all_lin, gdsc_signif_cn_all_lin, by = c("Drug_Gene", "group_general_lineage_name", "n", "Dataset"), all = TRUE)
+
+signif_all_lin <- rbind(ccle_signif_all_lin, ctrp_signif_all_lin, gdsc_signif_all_lin)
+signif_all_lin$n <- ifelse(is.na(signif_all_lin$n), 0, signif_all_lin$n)
+signif_all_lin$InG2P <- ifelse(signif_all_lin$n != 0, "Yes", "No")
+signif_all_lin$Drug_Gene_Lin <- paste0(signif_all_lin$Drug_Gene, "_", signif_all_lin$group_general_lineage_name)
+saveRDS(signif_all_lin, "./data_munging/rds/signif_lin_g2p_dgl.rds")
+```
+
+```{r}
+signif_lin_g2p_dgl <- readRDS("./data_munging/rds/signif_lin_g2p_dgl.rds")
+
+# CCLE mut, n = 7
+ccle_mut <- filter(select(ccle_signif_g2p_lineage, Drug_Gene_Lin, p), p < 0.05)
+ccle_mut_n <- nrow(select(ccle_signif_g2p_lineage, Drug_Gene_Lin, p))
+# CCLE GE/CN, n = 9
+ccle_ge <- select(subset(filter(signif_lin_g2p_dgl, Dataset == "CCLE"), Pearson_Pval_GE < 0.05), Drug_Gene_Lin, Pearson_Pval_GE, Pearson_Corr_GE)
+ccle_cn <- select(subset(filter(signif_lin_g2p_dgl, Dataset == "CCLE"), Pearson_Pval_CN < 0.05), Drug_Gene_Lin, Pearson_Pval_CN, Pearson_Corr_CN)
+ccle_Pear_n <- nrow(filter(signif_lin_g2p_dgl, Dataset == "CCLE"))
+ccle_dgl_summ <- merge(ccle_mut, merge(ccle_ge, ccle_cn, by = "Drug_Gene_Lin", all = TRUE), all = TRUE)
+ccle_dgl_summ <- with(ccle_dgl_summ, cbind(colsplit(Drug_Gene_Lin, pattern = "_", names = c("Drug", "Gene", "Lineage")), 
+                                           CCLE_p = p,
+                                           CCLE_p_Bonf = ifelse(p < 0.05 / ccle_mut_n, "Sig", NA),
+                                           CCLE_r_GE = Pearson_Corr_GE,
+                                           CCLE_p_GE = Pearson_Pval_GE,
+                                           CCLE_p_GE_Bonf = ifelse(Pearson_Pval_GE < 0.05 / ccle_Pear_n, "Sig", NA),
+                                           CCLE_r_CN = Pearson_Corr_CN,
+                                           CCLE_p_CN = Pearson_Pval_CN,
+                                           CCLE_p_CN_Bonf = ifelse(Pearson_Pval_CN < 0.05 / ccle_Pear_n, "Sig", NA)))
+
+# CTRP mut, n = 48
+ctrp_mut <- filter(select(ctrp_signif_g2p_lineage, Drug_Gene_Lin, p), p < 0.05)
+ctrp_mut_n <- nrow(select(ctrp_signif_g2p_lineage, Drug_Gene_Lin, p))
+# CTRP GE/CN, n = 61
+ctrp_ge <- select(subset(filter(signif_lin_g2p_dgl, Dataset == "CTRP"), Pearson_Pval_GE < 0.05), Drug_Gene_Lin, Pearson_Pval_GE, Pearson_Corr_GE)
+ctrp_cn <- select(subset(filter(signif_lin_g2p_dgl, Dataset == "CTRP"), Pearson_Pval_CN < 0.05), Drug_Gene_Lin, Pearson_Pval_CN, Pearson_Corr_CN)
+ctrp_Pear_n <- nrow(filter(signif_lin_g2p_dgl, Dataset == "CTRP"))
+ctrp_dgl_summ <- merge(ctrp_mut, merge(ctrp_ge, ctrp_cn, by = "Drug_Gene_Lin", all = TRUE), all = TRUE)
+ctrp_dgl_summ <- with(ctrp_dgl_summ, cbind(colsplit(Drug_Gene_Lin, pattern = "_", names = c("Drug", "Gene", "Lineage")), 
+                                           CTRP_p = p,
+                                           CTRP_p_Bonf = ifelse(p < 0.05 / ctrp_mut_n, "Sig", NA),
+                                           CTRP_r_GE = Pearson_Corr_GE,
+                                           CTRP_p_GE = Pearson_Pval_GE,
+                                           CTRP_p_GE_Bonf = ifelse(Pearson_Pval_GE < 0.05 / ctrp_Pear_n, "Sig", NA),
+                                           CTRP_r_CN = Pearson_Corr_CN,
+                                           CTRP_p_CN = Pearson_Pval_CN,
+                                           CTRP_p_CN_Bonf = ifelse(Pearson_Pval_CN < 0.05 / ctrp_Pear_n, "Sig", NA)))
+
+# GDSC mut, n = 39
+gdsc_mut <- filter(select(gdsc_signif_g2p_lineage, Drug_Gene_Lin, p), p < 0.05)
+gdsc_mut_n <- nrow(select(gdsc_signif_g2p_lineage, Drug_Gene_Lin, p))
+# GDSC GE/CN, n = 53
+gdsc_ge <- select(subset(filter(signif_lin_g2p_dgl, Dataset == "GDSC"), Pearson_Pval_GE < 0.05), Drug_Gene_Lin, Pearson_Pval_GE, Pearson_Corr_GE)
+gdsc_cn <- select(subset(filter(signif_lin_g2p_dgl, Dataset == "GDSC"), Pearson_Pval_CN < 0.05), Drug_Gene_Lin, Pearson_Pval_CN, Pearson_Corr_CN)
+gdsc_Pear_n <- nrow(filter(signif_lin_g2p_dgl, Dataset == "GDSC"))
+gdsc_dgl_summ <- merge(gdsc_mut, merge(gdsc_ge, gdsc_cn, by = "Drug_Gene_Lin", all = TRUE), all = TRUE)
+gdsc_dgl_summ <- with(gdsc_dgl_summ, cbind(colsplit(Drug_Gene_Lin, pattern = "_", names = c("Drug", "Gene", "Lineage")), 
+                                           GDSC_p = p,
+                                           GDSC_p_Bonf = ifelse(p < 0.05 / gdsc_mut_n, "Sig", NA),
+                                           GDSC_r_GE = Pearson_Corr_GE,
+                                           GDSC_p_GE = Pearson_Pval_GE,
+                                           GDSC_p_GE_Bonf = ifelse(Pearson_Pval_GE < 0.05 / gdsc_Pear_n, "Sig", NA),
+                                           GDSC_r_CN = Pearson_Corr_CN,
+                                           GDSC_p_CN = Pearson_Pval_CN,
+                                           GDSC_p_CN_Bonf = ifelse(Pearson_Pval_CN < 0.05 / gdsc_Pear_n, "Sig", NA)))
+
+dgl_summ <- merge(merge(ccle_dgl_summ, ctrp_dgl_summ, by = c("Drug", "Gene", "Lineage"), all = TRUE), gdsc_dgl_summ, by = c("Drug", "Gene", "Lineage"), all = TRUE)
+```
+
+Test all combinations of G2P drugs and genes in all lineages. InG2P indicates G2P drug-gene associations test across all lineages.
 ```{r, eval=FALSE}
@@
 signif_all_lin$InG2P <- ifelse(signif_all_lin$n != 0, "Yes", "No")
-saveRDS(signif_all_lin, "./data_munging/rds/signif_all_lin.rds")
-```
-
-```{r}
-signif_all_lin <- readRDS("./data_munging/rds/signif_all_lin.rds")
+signif_all_lin$Drug_Gene_Lin <- paste0(signif_all_lin$Drug_Gene, "_", signif_all_lin$group_general_lineage_name)
+saveRDS(signif_all_lin, "./data_munging/rds/signif_lin_g2p_grid.rds")
+```
+
+```{r}
+signif_lin_g2p_grid <- readRDS("./data_munging/rds/signif_lin_g2p_grid.rds")
 ```
@@
 ```{r, results='hide', eval=FALSE}
-druggenelin_pearson_ttest_res <- lapply(as.character(unique(signif_all_lin$group_general_lineage_name)), PearsonPlotlyByLineage)
+druggenelin_pearson_ttest_res <- lapply(as.character(unique(signif_lin_g2p_grid$group_general_lineage_name)), PearsonPlotlyByLineage)
 druggenelin_pearson_ttest_res_list <- rbindlist(druggenelin_pearson_ttest_res, use.names = TRUE)
@@
 
-Facted lineage summaries:
+Faceted lineage summaries:
 ```{r fig.height=4, fig.width=12}

### 2018-12-10 manuscript.Rmd

@@
 
-```{r}
-unique(crispr_data_g2p$lineage_name)
-```
-
 # Mutation Status Wilcoxon tests
@@
 
-# ggsave("./plots/manuscript/ccle_genomic_features_summ_plot.png", ccle_genomic_features_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
+# ggsave("./plots/manuscript/ctrp_genomic_features_summ_plot.png", ctrp_genomic_features_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
+```
+
+```{r fig.height=6, fig.width=12}
+gdsc_res_mut <- select(gdsc_signif_g2p, Drug_Gene, p)
+gdsc_res_mut$corr <- 0
+gdsc_res_mut$Metric <- "Mutation Status"
+gdsc_res_mut$p_log10 <- -log10(gdsc_res_mut$p)
+gdsc_res_mut$Dataset <- "GDSC"
+gdsc_pearson_res_GE <- select(filter(gdsc_pearson_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_GE, Pearson_Pval_GE, Dataset)
+colnames(gdsc_pearson_res_GE) <- c("Drug_Gene", "corr", "p", "Dataset")
+gdsc_pearson_res_GE$Metric <- "Gene Expression"
+subset(gdsc_pearson_res_GE, p < 0.05)
+gdsc_pearson_res_CN <- select(filter(gdsc_pearson_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_CN, Pearson_Pval_CN, Dataset)
+colnames(gdsc_pearson_res_CN) <- c("Drug_Gene", "corr", "p", "Dataset")
+gdsc_pearson_res_CN$Metric <- "Copy Number"
+subset(gdsc_pearson_res_CN, p < 0.05)
+gdsc_pearson_res_filt <- rbind(gdsc_pearson_res_GE, gdsc_pearson_res_CN)
+gdsc_pearson_res_filt$Metric <- factor(gdsc_pearson_res_filt$Metric, levels = c("Gene Expression", "Copy Number"))
+gdsc_pearson_res_filt$p_log10 <- -log10(gdsc_pearson_res_filt$p)
+
+gdsc_summ_res_mut_plot <- ggplot(data = subset(gdsc_res_mut, p < 0.05)) +
+  facet_grid(Dataset ~ Metric) +
+  # scale_y_continuous(breaks = seq(0, 30, by = 5), labels = seq(0, 30, by = 5)) +
+  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
+  geom_text_repel(mapping = aes(y = p_log10, x = corr, label = Drug_Gene, color = Metric), box.padding = 0.75, force = 15, size = 2.5, segment.size = 0.2, segment.colour = "grey50") +
+  theme(legend.position = "none", panel.grid.major.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(5.5, 1.5, 5.5, 5.5), "pt"), strip.background.y = element_blank(), strip.text.y = element_blank()) +
+  scale_color_manual(values = c("Mutation Status" = "darkorchid4")) +
+  labs(y = "-log10(p-value)")
+
+gdsc_summ_res_pearson_plot <- ggplot(data = subset(gdsc_pearson_res_filt, p < 0.05)) +
+  facet_grid(Dataset ~ Metric) +
+  # scale_y_continuous(breaks = seq(0, 30, by = 5), labels = seq(0, 30, by = 5)) +
+  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
+  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
+  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 10, nudge_y = 2.5, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
+  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
+  theme(legend.position = "none", plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
+  labs(x = "Pearson correlation coefficient (r)", y = "-log10(p-value)")
+
+gdsc_genomic_features_summ_plot <- plot_grid(gdsc_summ_res_mut_plot, gdsc_summ_res_pearson_plot, align = "h", rel_widths = c(1, 5))
+gdsc_genomic_features_summ_plot
+
+# ggsave("./plots/manuscript/gdsc_genomic_features_summ_plot.png", gdsc_genomic_features_summ_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
+```
+
+```{r fig.height=4, fig.width=8}
+all_res_mut <- rbind(ccle_res_mut, ctrp_res_mut, gdsc_res_mut)
+
+all_summ_res_plot <- ggplot(data = subset(all_res_mut, p < 0.05)) +
+  facet_grid(~ Dataset) +
+  geom_point(aes(x = corr, y = p_log10, color = Dataset), alpha = 0.5) +
+  scale_y_continuous(breaks = seq(0, 12, by = 2), labels = seq(0, 12, by = 2)) +
+  scale_x_continuous(breaks = seq(0, 0.1, by = 0.1), labels = seq(0, 0.1, by = 0.1)) +
+  coord_cartesian(xlim = c(0, 0.05)) +
+  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Dataset, label = Drug_Gene), nudge_x = 0.05, direction = "y", hjust = 0, size = 2.5, segment.size = 0.1, segment.colour = "grey50", box.padding = 0.6) +
+  scale_color_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
+  theme(legend.position = "none", plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt"), panel.grid.major.x = element_blank(), panel.grid.minor.x = element_blank(), axis.title.x = element_blank(), axis.ticks.x = element_blank(), axis.text.x = element_blank()) +
+  labs(y = "-log10(p-value)")
+all_summ_res_plot
+
+# ggsave("./plots/manuscript/all_summ_mut_plot.png", all_summ_res_plot, device = "png", dpi = 450, width = 12, height = 6, units = "in")
+```
+
+```{r fig.height=12, fig.width=12}
+all_pearson_res <- rbind(ccle_pearson_res_filt, ctrp_pearson_res_filt, gdsc_pearson_res_filt)
+
+all_summ_res_pearson_plot <- ggplot(data = subset(all_pearson_res, p < 0.05)) +
+  facet_grid(Dataset ~ Metric, scales = "free", space = "free") +
+  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
+  geom_point(aes(x = corr, y = p_log10, color = Dataset), alpha = 0.5) +
+  scale_y_continuous(breaks = seq(0, 60, by = 10), labels = seq(0, 60, by = 10)) +
+  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Dataset, label = Drug_Gene), force = 10, nudge_y = 3, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
+  scale_color_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
+  theme(legend.position = "none", plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
+  labs(x = "Pearson correlation coefficient (r)", y = "-log10(p-value)")
+all_summ_res_pearson_plot
+
+# ggsave("./plots/manuscript/all_summ_res_pearson_plot.png", all_summ_res_pearson_plot, device = "png", dpi = 450, width = 12, height = 10, units = "in")
+```
+
+```{r}
+levels(all_pearson_res$Dataset)
 ```
@@
 
-all_druggenelin_ge <- select(signif_all_lin, Drug_Gene, group_general_lineage_name, n, Pearson_GE_Abs, InG2P, Dataset, Pearson_GE_Sign)
+all_druggenelin_ge <- select(signif_lin_g2p_grid, Drug_Gene, group_general_lineage_name, n, Pearson_GE_Abs, InG2P, Dataset, Pearson_GE_Sign)
 all_druggenelin_ge$Measure <- "Gene Expression"
@@
 
-all_druggenelin_cn <- select(signif_all_lin, Drug_Gene, group_general_lineage_name, n, Pearson_CN_Abs, InG2P, Dataset, Pearson_CN_Sign)
+all_druggenelin_cn <- select(signif_lin_g2p_grid, Drug_Gene, group_general_lineage_name, n, Pearson_CN_Abs, InG2P, Dataset, Pearson_CN_Sign)
 all_druggenelin_cn$Measure <- "Copy Number"

### 2018-12-12 manuscript.Rmd
update Rmd
update lineage plots

@@
 
-# Set up
+# SET UP
 
@@
 
-# Functions {.tabset .tabset-fade .tabset-pills}
+# FUNCTIONS {.tabset .tabset-fade .tabset-pills}
 
@@
 
-## Make G2P lineage mutation status plotly
-```{r}
-MutPlotlyByLineage <- function(lineage_name) {
-  use_data <- filter(g2p_druggenelin_all_summ, group_general_lineage_name == lineage_name)
+## Make lineage mut plots
+
+```{r}
+MutPlotsByLineage <- function(lineage_name) {
+
+  use_data <- filter(dgl_mut_grid_summ, group_general_lineage_name == lineage_name)
   use_data$Dataset <- factor(use_data$Dataset, levels = c("CCLE", "CTRP", "GDSC"))
@@
     ccle_lin_p_ttest <- t.test(use_data_ccle$p ~ use_data_ccle$InG2P)
-    ccle_lin_p_ttest_res <- paste0("t(", round(ccle_lin_p_ttest$parameter, 1), ") = ", round(ccle_lin_p_ttest$statistic, 2), ", p = ", round(ccle_lin_p_ttest$p.value, 3))
+    ccle_lin_p_ttest_res <- paste0("t(", trunc(ccle_lin_p_ttest$parameter), ") = ", round(ccle_lin_p_ttest$statistic, 2), ", p = ", round(ccle_lin_p_ttest$p.value, 3))
   }
@@
     ctrp_lin_p_ttest <- t.test(use_data_ctrp$p ~ use_data_ctrp$InG2P)
-    ctrp_lin_p_ttest_res <- paste0("t(", round(ctrp_lin_p_ttest$parameter, 1), ") = ", round(ctrp_lin_p_ttest$statistic, 2), ", p = ", round(ctrp_lin_p_ttest$p.value, 3))
+    ctrp_lin_p_ttest_res <- paste0("t(", trunc(ctrp_lin_p_ttest$parameter), ") = ", round(ctrp_lin_p_ttest$statistic, 2), ", p = ", round(ctrp_lin_p_ttest$p.value, 3))
   }
@@
     gdsc_lin_p_ttest <- t.test(use_data_gdsc$p ~ use_data_gdsc$InG2P)
-    gdsc_lin_p_ttest_res <- paste0("t(", round(gdsc_lin_p_ttest$parameter, 1), ") = ", round(gdsc_lin_p_ttest$statistic, 2), ", p = ", round(gdsc_lin_p_ttest$p.value, 3))
-  }
-
-  y_value <- ifelse(ticker == 3, 10, max(use_data$n) + 1)
+    gdsc_lin_p_ttest_res <- paste0("t(", trunc(gdsc_lin_p_ttest$parameter), ") = ", round(gdsc_lin_p_ttest$statistic, 2), ", p = ", round(gdsc_lin_p_ttest$p.value, 3))
+  }
+
+  y_value <- ifelse(ticker == 3, 10, max(use_data$n) + max(use_data$n) * 0.1)
+
   summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"),
@@
                           t_statistic = c(round(ccle_lin_p_ttest$statistic, 3), round(ctrp_lin_p_ttest$statistic, 3), round(gdsc_lin_p_ttest$statistic, 3)),
-                          df = c(round(ccle_lin_p_ttest$parameter, 3), round(ctrp_lin_p_ttest$parameter, 3), round(gdsc_lin_p_ttest$parameter, 3)),
+                          df = c(trunc(ccle_lin_p_ttest$parameter), trunc(ctrp_lin_p_ttest$parameter), trunc(gdsc_lin_p_ttest$parameter)),
                           p_value = c(round(ccle_lin_p_ttest$p.value, 3), round(ctrp_lin_p_ttest$p.value, 3), round(gdsc_lin_p_ttest$p.value, 3)),
@@
     scale_y_continuous(breaks = pretty_breaks()) +
-    geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = p, y = n), alpha = 0.5, position = position_jitter(width = 0, height = 0.15)) +
+    geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = p, y = n), alpha = 0.5) +
     scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
@@
 
-  saveWidgetFix(widget = plot, file = paste0("./plots/manuscript/plotlys_mut_by_lineage/", lineage_name, "_mut_plotly.html"))
-
   plot_point <- ggplot_gtable(ggplot_build(plot_point))
@@
                      rel_heights = c(1, 4))
-  ggsave(paste0("./plots/manuscript/pngs_mut_by_lineage/", lineage_name, "_mut_plot.png"), mut_plot, device = "png", dpi = 450, width = 12, height = 6, units =   "in")
+
+  saveWidgetFix(widget = plot, file = paste0("./plots/manuscript/plotlys_mut_by_lineage_grid/", lineage_name, "_mut_plotly_grid.html"))
+  ggsave(paste0("./plots/manuscript/pngs_mut_by_lineage_grid/", lineage_name, "_mut_plot_grid.png"), mut_plot, device = "png", dpi = 450, width = 12, height = 6, units =   "in")
 
@@
 
-## Make G2P lineage Pearson plotlys
-```{r}
-PearsonPlotlyByLineage <- function(lineage) {
+## Make lineage GE/CN plots
+
+```{r}
+PearsonPlotsByLineage <- function(lineage) {
   print(paste0("Lineage: ", toupper(lineage)))
-  use_data <- filter(signif_lin_g2p_grid, group_general_lineage_name == lineage)
+  use_data <- filter(dgl_signif_pearson_g2p_grid, group_general_lineage_name == lineage)
   use_data$Dataset <- factor(use_data$Dataset, levels = c("CCLE", "CTRP", "GDSC"))
@@
 
-  y_value_ge <- ifelse(ticker_ge == 3, 10, max(use_data$n) + 1)
-  y_value_cn <- ifelse(ticker_cn == 3, 10, max(use_data$n) + 1)
+  y_value_ge <- ifelse(ticker_ge == 3, 10, max(use_data$n) + max(use_data$n) * 0.1)
+  y_value_cn <- ifelse(ticker_cn == 3, 10, max(use_data$n) + max(use_data$n) * 0.1)
+
   summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"),
@@
       scale_y_continuous(breaks = pretty_breaks()) +
-      geom_point(mapping = aes(label = Pearson_GE_Label, color = InG2P, fill = InG2P, shape = Pearson_GE_Sign, x = Pearson_GE_Abs, y = n), alpha = 0.5, position = position_jitter(width = 0, height = 0.15)) +
+      geom_point(mapping = aes(label = Pearson_GE_Label, color = InG2P, fill = InG2P, shape = Pearson_GE_Sign, x = Pearson_GE_Abs, y = n), alpha = 0.5) +
       scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
@@
       scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-      geom_text_repel(data = subset(use_data, InG2P == "Yes"), aes(label = Drug_Gene, x = Pearson_GE_Abs, y = n), size = 3, segment.size = 0.2, segment.color = "grey50") +
+      geom_text_repel(data = subset(use_data, InG2P == "Yes" & n > 10), aes(label = Drug_Gene, x = Pearson_GE_Abs, y = n), size = 3, segment.size = 0.2, segment.color = "grey50") +
       geom_text(data = summ_text, mapping = aes(x = 0.5, y = y_value_ge, label = Test_Results_GE), nudge_y = 1) +
@@
       theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
+
     plot_ge <- subplot(plot_ge_box, plot_ge_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>%
@@
                       yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
-    saveWidgetFix(widget = plot_ge, file = paste0("./plots/manuscript/plotlys_ge_by_lineage/", lineage, "_ge_plotly.html"))
-    print("Gene expression plotly: DONE")
 
@@
     png_ge
-    ggsave(paste0("./plots/manuscript/pngs_ge_by_lineage/", lineage, "_ge_plot.png"), png_ge, device = "png", dpi = 450, width = 12, height = 6, units = "in")
-    print("Gene expression plot: DONE")
+
+    saveWidgetFix(widget = plot_ge, file = paste0("./plots/manuscript/plotlys_ge_by_lineage_grid/", lineage, "_ge_plotly_grid.html"))
+    ggsave(paste0("./plots/manuscript/pngs_ge_by_lineage_grid/", lineage, "_ge_plot_grid.png"), png_ge, device = "png", dpi = 450, width = 12, height = 6, units = "in")
+    print("Gene expression plots: DONE")
   }
@@
       scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-      geom_text_repel(data = subset(use_data, InG2P == "Yes"), aes(label = Drug_Gene, x = Pearson_CN_Abs, y = n), size = 3, segment.size = 0.2, segment.color = "grey50") +
+      geom_text_repel(data = subset(use_data, InG2P == "Yes"  & n > 10), aes(label = Drug_Gene, x = Pearson_CN_Abs, y = n), size = 3, segment.size = 0.2, segment.color = "grey50") +
       geom_text(data = summ_text, mapping = aes(x = 0.5, y = y_value_cn, label = Test_Results_CN), nudge_y = 1) +
@@
       theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
+
     plot_cn <- subplot(plot_cn_box, plot_cn_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>%
@@
                       yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
-    saveWidgetFix(widget = plot_cn, file = paste0("./plots/manuscript/plotlys_cn_by_lineage/", lineage, "_cn_plotly.html"))
-    print("Copy number plotly: DONE")
 
@@
     png_cn
-    ggsave(paste0("./plots/manuscript/pngs_cn_by_lineage/", lineage, "_cn_plot.png"), png_cn, device = "png", dpi = 450, width = 12, height = 6, units = "in")
-    print("Copy number plot: DONE")
+
+    saveWidgetFix(widget = plot_cn, file = paste0("./plots/manuscript/plotlys_cn_by_lineage_grid/", lineage, "_cn_plotly_grid.html"))
+    ggsave(paste0("./plots/manuscript/pngs_cn_by_lineage_grid/", lineage, "_cn_plot_grid.png"), png_cn, device = "png", dpi = 450, width = 12, height = 6, units = "in")
+    print("Copy number plots: DONE")
   }
@@
 
-# Data management {.tabset .tabset-fade .tabset-pills}
+# DATA MANAGEMENT {.tabset .tabset-fade .tabset-pills}
 
@@
 
-## Genomic annotations
-
-### CCLE MAF file
+## CCLE genomic annotations
+
+### Mutation status (Mut)
 
@@
 
-### CCLE copy number file
+### Copy number (CN)
 
@@
 
-### CCLE gene expression file
+### Gene expression (GE)
 
@@
 
-## CRISPR
-
-### DepMap dependency probabilities
-
-```{r, eval=FALSE}
-dep <- read.delim("./data_munging/18Q4/gene_dependency_18Q4_20181115.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
-# Remove Entrez gene IDs from colnames
-colnames(dep) <- gsub(" .*", "", colnames(dep))
-```
-
-### Merge CRISPR data and annotations
-
-The latest CRISPR CERES score data (18Q3, August 2018) was pulled from the [DepMap Data Portal](https://depmap.org/portal/download/) (Broad Institute Cancer Dependency Map 2018, Meyers et al. 2017).
-```{r, eval=FALSE}
-crispr <- read.delim("./data_munging/18Q4/gene_effect_18Q4_20181115.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
-# Remove Entrez gene IDs from colnames
-colnames(crispr) <- gsub(" .*", "", colnames(crispr))
-```
-
-Merge annotation data:
-```{r, eval=FALSE}
-# Melt CRISPR dataset for merging
-crispr_melt <- melt(crispr, id.vars = "DepMap_ID", measure.vars = colnames(crispr)[2:ncol(crispr)], variable.name = "Hugo_Symbol", value.name = "Score")
-# Melt dependency probabilities dataset for merging
-dep_melt <- melt(dep, id.vars = "DepMap_ID", measure.vars = colnames(dep)[2:ncol(dep)], variable.name = "Hugo_Symbol", value.name = "Dep_Prob")
-# Merge dependency probabilities
-crispr_melt <- merge(crispr_melt, dep_melt, by = c("DepMap_ID", "Hugo_Symbol"), all.x = TRUE)
-# Merge cell line metadata
-crispr_melt <- merge(crispr_melt, ccl_info, by = "DepMap_ID", all.x = TRUE)
-crispr_melt <- merge(crispr_melt, crispr_meta, by = c("CCLE_Name", "DepMap_ID"), all.x = TRUE)
-
-# Merge mutation annotations
-maf_filt_crispr <- filter(maf_df, Hugo_Symbol %in% as.character(unique(crispr_melt$Hugo_Symbol)))
-crispr_muts <- merge(crispr_melt, maf_filt_crispr, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
-crispr_muts$Hugo_Symbol <- factor(crispr_muts$Hugo_Symbol)
-crispr_muts <- crispr_muts %>% mutate(Mutation_Status_Nonsilent = if_else(is.na(Mutation_Status_Nonsilent), "Wildtype", Mutation_Status_Nonsilent))
-# Summarize number of mutant and Wildtype cell lines
-crispr_muts_summ <- crispr_muts %>% group_by(Hugo_Symbol) %>%
-  summarize(N_Nonsilent_Wildtype = sum(Mutation_Status_Nonsilent == "Wildtype"),
-            N_Nonsilent_Mutant = sum(Mutation_Status_Nonsilent == "Mutant"))
-# Merge test results back into full dataset, which restores information lost in the summarization
-crispr_data <- merge(crispr_muts_summ, crispr_muts, by = "Hugo_Symbol")
-# Add Color columns
-crispr_data$Color_Nonsilent <- ifelse(crispr_data$Mutation_Status_Nonsilent == "Wildtype", "thistle", "darkorchid")
-crispr_data$Color_Nonsilent <- factor(crispr_data$Color_Nonsilent)
-
-# Cell line lineages
-crispr_data <- merge(crispr_data, ccl_converter, by = c("CCLE_Name", "DepMap_ID"), all.x = TRUE)
-levels(crispr_data$lineage_name) <- sort(levels(crispr_data$lineage_name), decreasing = TRUE)
-# Copy number
-crispr_data <- merge(crispr_data, cn_melt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
-# Gene expression (RPKM)
-ge_crispr_18Q3 <- filter(ge_melt_18Q3, Hugo_Symbol %in% as.character(unique(crispr_melt$Hugo_Symbol)))
-# ge_crispr_18Q4 <- filter(ge_melt_18Q4, Hugo_Symbol %in% as.character(unique(crispr_melt$Hugo_Symbol)))
-crispr_data <- merge(crispr_data, ge_crispr_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
-# crispr_data <- merge(crispr_data, ge_crispr_18Q4, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
-saveRDS(crispr_data, "./../htscreen_lineages_giant_files/crispr_data_18Q4.rds", compress = "xz")
-```
-
-```{r}
-crispr_data <- readRDS("./../htscreen_lineages_giant_files/crispr_data_18Q4.rds")
-crispr_data_ptmuts <- filter(crispr_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
-crispr_data_ptmuts$Keep_PtMut_Tests <- ifelse(crispr_data_ptmuts$Reference_Allele_Length == 1 | is.na(crispr_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(crispr_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
-crispr_data_ptmuts <- filter(crispr_data_ptmuts, Keep_PtMut_Tests == TRUE)
-
-# Filter CRISPR for G2P genes in G2P
-crispr_data_g2p <- filter(crispr_data_ptmuts, Hugo_Symbol %in% g2p_genes)
-crispr_data_g2p$Hugo_Symbol <- factor(crispr_data_g2p$Hugo_Symbol, levels = g2p_genes)
-crispr_data_g2p$Mutation_Status_Nonsilent <- factor(crispr_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-```
-
 ## Drug screens
+
+### Merge drug data and annotations
 
@@
 
+### Filter drug data
+
 ```{r}
@@
 ```{r}
-length(unique(ccle_data_g2p_grid$Drug))
-length(unique(ccle_data_g2p_grid$Drug_Gene))
-```
-
-```{r}
 test_ccle <- ccle_data_ptmuts %>% group_by(Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()
@@
 
-# Mutation Status Wilcoxon tests
+## CRISPR
+
+### DepMap dependency probabilities
+
+```{r, eval=FALSE}
+dep <- read.delim("./data_munging/18Q4/gene_dependency_18Q4_20181115.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
+# Remove Entrez gene IDs from colnames
+colnames(dep) <- gsub(" .*", "", colnames(dep))
+```
+
+### Merge CRISPR data and annotations
+
+The latest CRISPR CERES score data (18Q3, August 2018) was pulled from the [DepMap Data Portal](https://depmap.org/portal/download/) (Broad Institute Cancer Dependency Map 2018, Meyers et al. 2017).
+```{r, eval=FALSE}
+crispr <- read.delim("./data_munging/18Q4/gene_effect_18Q4_20181115.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
+# Remove Entrez gene IDs from colnames
+colnames(crispr) <- gsub(" .*", "", colnames(crispr))
+```
+
+Merge annotation data:
+```{r, eval=FALSE}
+# Melt CRISPR dataset for merging
+crispr_melt <- melt(crispr, id.vars = "DepMap_ID", measure.vars = colnames(crispr)[2:ncol(crispr)], variable.name = "Hugo_Symbol", value.name = "Score")
+# Melt dependency probabilities dataset for merging
+dep_melt <- melt(dep, id.vars = "DepMap_ID", measure.vars = colnames(dep)[2:ncol(dep)], variable.name = "Hugo_Symbol", value.name = "Dep_Prob")
+# Merge dependency probabilities
+crispr_melt <- merge(crispr_melt, dep_melt, by = c("DepMap_ID", "Hugo_Symbol"), all.x = TRUE)
+# Merge cell line metadata
+crispr_melt <- merge(crispr_melt, ccl_info, by = "DepMap_ID", all.x = TRUE)
+crispr_melt <- merge(crispr_melt, crispr_meta, by = c("CCLE_Name", "DepMap_ID"), all.x = TRUE)
+
+# Merge mutation annotations
+maf_filt_crispr <- filter(maf_df, Hugo_Symbol %in% as.character(unique(crispr_melt$Hugo_Symbol)))
+crispr_muts <- merge(crispr_melt, maf_filt_crispr, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
+crispr_muts$Hugo_Symbol <- factor(crispr_muts$Hugo_Symbol)
+crispr_muts <- crispr_muts %>% mutate(Mutation_Status_Nonsilent = if_else(is.na(Mutation_Status_Nonsilent), "Wildtype", Mutation_Status_Nonsilent))
+# Summarize number of mutant and Wildtype cell lines
+crispr_muts_summ <- crispr_muts %>% group_by(Hugo_Symbol) %>%
+  summarize(N_Nonsilent_Wildtype = sum(Mutation_Status_Nonsilent == "Wildtype"),
+            N_Nonsilent_Mutant = sum(Mutation_Status_Nonsilent == "Mutant"))
+# Merge test results back into full dataset, which restores information lost in the summarization
+crispr_data <- merge(crispr_muts_summ, crispr_muts, by = "Hugo_Symbol")
+# Add Color columns
+crispr_data$Color_Nonsilent <- ifelse(crispr_data$Mutation_Status_Nonsilent == "Wildtype", "thistle", "darkorchid")
+crispr_data$Color_Nonsilent <- factor(crispr_data$Color_Nonsilent)
+
+# Cell line lineages
+crispr_data <- merge(crispr_data, ccl_converter, by = c("CCLE_Name", "DepMap_ID"), all.x = TRUE)
+levels(crispr_data$lineage_name) <- sort(levels(crispr_data$lineage_name), decreasing = TRUE)
+# Copy number
+crispr_data <- merge(crispr_data, cn_melt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
+# Gene expression (RPKM)
+ge_crispr_18Q3 <- filter(ge_melt_18Q3, Hugo_Symbol %in% as.character(unique(crispr_melt$Hugo_Symbol)))
+# ge_crispr_18Q4 <- filter(ge_melt_18Q4, Hugo_Symbol %in% as.character(unique(crispr_melt$Hugo_Symbol)))
+crispr_data <- merge(crispr_data, ge_crispr_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
+# crispr_data <- merge(crispr_data, ge_crispr_18Q4, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
+saveRDS(crispr_data, "./../htscreen_lineages_giant_files/crispr_data_18Q4.rds", compress = "xz")
+```
+
+```{r}
+crispr_data <- readRDS("./../htscreen_lineages_giant_files/crispr_data_18Q4.rds")
+crispr_data_ptmuts <- filter(crispr_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
+crispr_data_ptmuts$Keep_PtMut_Tests <- ifelse(crispr_data_ptmuts$Reference_Allele_Length == 1 | is.na(crispr_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(crispr_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
+crispr_data_ptmuts <- filter(crispr_data_ptmuts, Keep_PtMut_Tests == TRUE)
+
+# Filter CRISPR for G2P genes in G2P
+crispr_data_g2p <- filter(crispr_data_ptmuts, Hugo_Symbol %in% g2p_genes)
+crispr_data_g2p$Hugo_Symbol <- factor(crispr_data_g2p$Hugo_Symbol, levels = g2p_genes)
+crispr_data_g2p$Mutation_Status_Nonsilent <- factor(crispr_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
+```
+
+# WILCOXON TESTS
 
@@
 
+Wilcoxon tests for assessing effect of mutation status on gene essentiality scores (CRISPR) and AUC (CCLE, CTRP, and GDSC).
+
 ## CRISPR
 
-### G2P genes
-
+Test G2P genes in lineage-agnostic context:
 ```{r, eval=FALSE}
@@
 
+Plot results of `crispr_signif_g2p_gene` tests:
 ```{r fig.height=7, fig.width=12}
@@
 
-### Gene
-
+Test G2P genes in lineage-grouped context:
 ```{r, eval=FALSE}
@@
 
+Plot results of `crispr_signif_g2p_lineage` tests:
 ```{r fig.height=18, fig.width=15, eval=TRUE}
@@
 
+Count mutant/wildtype calls in each gene-lineage group:
 ```{r}
@@
 ## CCLE
-
-### G2P gene and drug
-
-```{r}
-test_ccle <- ccle_data_g2p_grid %>% group_by(Hugo_Symbol, Drug) %>% tally()
-```
-
-```{r, eval=FALSE}
-# G2P drug-gene associations only
-ccle_signif_g2p <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene", data = ccle_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
-ccle_signif_g2p <- adj_signif(ccle_signif_g2p)
-ccle_signif_g2p <- ccle_signif_g2p[order(ccle_signif_g2p$p),]
-saveRDS(ccle_signif_g2p, "./data_munging/rds/ccle_signif_g2p_gene.rds")
-
-# Grid comparisons of G2P drugs and genes
-ccle_signif_g2p_grid <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "Drug"), ref.group = "Wildtype", data = ccle_data_g2p_grid, method = "wilcox.test", p.adjust.method = "BH")
-ccle_signif_g2p_grid <- adj_signif(ccle_signif_g2p_grid)
-ccle_signif_g2p_grid <- ccle_signif_g2p_grid[order(ccle_signif_g2p_grid$p),]
-ccle_signif_g2p_grid$Drug_Gene <- paste0(ccle_signif_g2p_grid$Drug, "_", ccle_signif_g2p_grid$Hugo_Symbol)
-saveRDS(ccle_signif_g2p_grid, "./data_munging/rds/ccle_signif_g2p_grid.rds")
-```
-
-```{r}
-ccle_signif_g2p <- readRDS("./data_munging/rds/ccle_signif_g2p_gene.rds")
-knitr::kable(ccle_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-
-ccle_signif_g2p_grid <- readRDS("./data_munging/rds/ccle_signif_g2p_grid.rds")
-knitr::kable(ccle_signif_g2p_grid[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-### G2P gene, drug, and lineage
-
-```{r, eval=FALSE}
-ccle_signif_grid_lineage <- lapply(unique(ccle_data_g2p_grid$Drug), WilcoxonByDrug, dataset = ccle_data_g2p_grid, data_name = "ccle", grouping_var = "lineage")
-names(ccle_signif_grid_lineage) <- unique(ccle_signif_grid_lineage$Drug)
-ccle_signif_grid_lineage <- rbindlist(ccle_signif_grid_lineage, use.names = TRUE)
-ccle_signif_grid_lineage <- ccle_signif_grid_lineage[order(ccle_signif_grid_lineage$p),]
-saveRDS(ccle_signif_grid_lineage, "./data_munging/rds/ccle_signif_grid_lineage.rds")
-
-ccle_signif_g2p_lineage <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene_Lin", data = ccle_data_g2p_dgl, method = "wilcox.test", p.adjust.method = "BH")
-ccle_signif_g2p_lineage <- adj_signif(ccle_signif_g2p_lineage)
-ccle_signif_g2p_lineage <- ccle_signif_g2p_lineage[order(ccle_signif_g2p_lineage$p),]
-saveRDS(ccle_signif_g2p_lineage, "./data_munging/rds/ccle_signif_g2p_lineage.rds")
-```
-
-```{r}
-ccle_signif_g2p_lineage <- readRDS("./data_munging/rds/ccle_signif_g2p_lineage.rds")
-ccle_signif_grid_lineage <- readRDS("./data_munging/rds/ccle_signif_grid_lineage.rds")
-
-knitr::kable(ccle_signif_g2p_lineage[, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-
-knitr::kable(ccle_signif_grid_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-## CTRP
-
-### G2P gene and drug
-
-```{r, eval=FALSE}
-ctrp_signif_g2p <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene", data = ctrp_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
-ctrp_signif_g2p <- adj_signif(ctrp_signif_g2p)
-ctrp_signif_g2p <- ctrp_signif_g2p[order(ctrp_signif_g2p$p),]
-saveRDS(ctrp_signif_g2p, "./data_munging/rds/ctrp_signif_g2p_gene.rds")
-
-# Grid comparisons of G2P drugs and genes
-ctrp_signif_g2p_grid <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "Drug"), data = ctrp_data_g2p_grid, method = "wilcox.test", p.adjust.method = "BH")
-ctrp_signif_g2p_grid <- adj_signif(ctrp_signif_g2p_grid)
-ctrp_signif_g2p_grid <- ctrp_signif_g2p_grid[order(ctrp_signif_g2p_grid$p),]
-ctrp_signif_g2p_grid$Drug_Gene <- paste0(ctrp_signif_g2p_grid$Drug, "_", ctrp_signif_g2p_grid$Hugo_Symbol)
-saveRDS(ctrp_signif_g2p_grid, "./data_munging/rds/ctrp_signif_g2p_grid.rds")
-```
-
-```{r}
-ctrp_signif_g2p <- readRDS("./data_munging/rds/ctrp_signif_g2p_gene.rds")
-knitr::kable(ctrp_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-
-ctrp_signif_g2p_grid <- readRDS("./data_munging/rds/ctrp_signif_g2p_grid.rds")
-knitr::kable(ctrp_signif_g2p_grid[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-### G2P gene, drug, and lineage
-
-```{r, eval=FALSE}
-ctrp_signif_grid_lineage <- lapply(unique(ctrp_data_g2p_grid$Drug), WilcoxonByDrug, dataset = ctrp_data_g2p_grid, data_name = "ctrp", grouping_var = "lineage")
-names(ctrp_signif_grid_lineage) <- unique(ctrp_signif_grid_lineage$Drug)
-ctrp_signif_grid_lineage <- rbindlist(ctrp_signif_grid_lineage, use.names = TRUE)
-ctrp_signif_grid_lineage <- ctrp_signif_grid_lineage[order(ctrp_signif_grid_lineage$p),]
-saveRDS(ctrp_signif_grid_lineage, "./data_munging/rds/ctrp_signif_grid_lineage.rds")
-
-ctrp_signif_g2p_lineage <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene_Lin", data = ctrp_data_g2p_dgl, method = "wilcox.test", p.adjust.method = "BH")
-ctrp_signif_g2p_lineage <- adj_signif(ctrp_signif_g2p_lineage)
-ctrp_signif_g2p_lineage <- ctrp_signif_g2p_lineage[order(ctrp_signif_g2p_lineage$p),]
-saveRDS(ctrp_signif_g2p_lineage, "./data_munging/rds/ctrp_signif_g2p_lineage.rds")
-```
-
-```{r}
-ctrp_signif_g2p_lineage <- readRDS("./data_munging/rds/ctrp_signif_g2p_lineage.rds")
-ctrp_signif_grid_lineage <- readRDS("./data_munging/rds/ctrp_signif_grid_lineage.rds")
-
-knitr::kable(ctrp_signif_g2p_lineage[, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-
-knitr::kable(ctrp_signif_grid_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-## GDSC
-
-### G2P gene and drug
-
-```{r, eval=FALSE}
-gdsc_signif_g2p <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene", data = gdsc_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
-gdsc_signif_g2p <- adj_signif(gdsc_signif_g2p)
-gdsc_signif_g2p <- gdsc_signif_g2p[order(gdsc_signif_g2p$p),]
-saveRDS(gdsc_signif_g2p, "./data_munging/rds/gdsc_signif_g2p_gene.rds")
-
-# Grid comparisons of G2P drugs and genes
-gdsc_signif_g2p_grid <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "Drug"), data = gdsc_data_g2p_grid, method = "wilcox.test", p.adjust.method = "BH")
-gdsc_signif_g2p_grid <- adj_signif(gdsc_signif_g2p_grid)
-gdsc_signif_g2p_grid <- gdsc_signif_g2p_grid[order(gdsc_signif_g2p_grid$p),]
-gdsc_signif_g2p_grid$Drug_Gene <- paste0(gdsc_signif_g2p_grid$Drug, "_", gdsc_signif_g2p_grid$Hugo_Symbol)
-saveRDS(gdsc_signif_g2p_grid, "./data_munging/rds/gdsc_signif_g2p_grid.rds")
-```
-
-```{r}
-gdsc_signif_g2p <- readRDS("./data_munging/rds/gdsc_signif_g2p_gene.rds")
-knitr::kable(gdsc_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-
-gdsc_signif_g2p_grid <- readRDS("./data_munging/rds/gdsc_signif_g2p_grid.rds")
-knitr::kable(gdsc_signif_g2p_grid[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-### G2P gene, drug, and lineage
-
-```{r, eval=FALSE}
-gdsc_signif_grid_lineage <- lapply(unique(gdsc_data_g2p_grid$Drug), WilcoxonByDrug, dataset = gdsc_data_g2p_grid, data_name = "gdsc", grouping_var = "lineage")
-names(gdsc_signif_grid_lineage) <- unique(gdsc_signif_grid_lineage$Drug)
-gdsc_signif_grid_lineage <- rbindlist(gdsc_signif_grid_lineage, use.names = TRUE)
-gdsc_signif_grid_lineage <- gdsc_signif_grid_lineage[order(gdsc_signif_grid_lineage$p),]
-saveRDS(gdsc_signif_grid_lineage, "./data_munging/rds/gdsc_signif_grid_lineage.rds")
-
-gdsc_signif_g2p_lineage <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene_Lin", data = gdsc_data_g2p_dgl, method = "wilcox.test", p.adjust.method = "BH")
-gdsc_signif_g2p_lineage <- adj_signif(gdsc_signif_g2p_lineage)
-gdsc_signif_g2p_lineage <- gdsc_signif_g2p_lineage[order(gdsc_signif_g2p_lineage$p),]
-saveRDS(gdsc_signif_g2p_lineage, "./data_munging/rds/gdsc_signif_g2p_lineage.rds")
-```
-
-```{r}
-gdsc_signif_g2p_lineage <- readRDS("./data_munging/rds/gdsc_signif_g2p_lineage.rds")
-gdsc_signif_grid_lineage <- readRDS("./data_munging/rds/gdsc_signif_grid_lineage.rds")
-
-knitr::kable(gdsc_signif_g2p_lineage[, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-
-knitr::kable(gdsc_signif_grid_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-## Drug screens: All CRISPR genes
 
@@
 
-CCLE:
-
-user   system  elapsed 
-1483.399  262.649 1901.698
-
+Test all CRISPR genes in lineage-agnostic context:
 ```{r, eval=FALSE}
@@
 saveRDS(ccle_data_allgenes, "./data_munging/rds/ccle_data_18Q3_allgenes.rds", compress = "xz")
+
+# user   system  elapsed 
+# 1483.399  262.649 1901.698 
 ```
@@
 
-CTRP:
+Test G2P genes in lineage-agnostic context:
+```{r, eval=FALSE}
+# G2P drug-gene associations only
+ccle_signif_g2p <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene", data = ccle_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
+ccle_signif_g2p <- adj_signif(ccle_signif_g2p)
+ccle_signif_g2p <- ccle_signif_g2p[order(ccle_signif_g2p$p),]
+saveRDS(ccle_signif_g2p, "./data_munging/rds/ccle_signif_g2p_gene.rds")
+
+# Grid comparisons of G2P drugs and genes
+ccle_signif_g2p_grid <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = c("Drug_Gene"), data = ccle_data_g2p_grid, method = "wilcox.test", p.adjust.method = "BH")
+ccle_signif_g2p_grid <- adj_signif(ccle_signif_g2p_grid)
+ccle_signif_g2p_grid <- ccle_signif_g2p_grid[order(ccle_signif_g2p_grid$p),]
+saveRDS(ccle_signif_g2p_grid, "./data_munging/rds/ccle_signif_g2p_grid.rds")
+```
+
+```{r}
+ccle_signif_g2p <- readRDS("./data_munging/rds/ccle_signif_g2p_gene.rds")
+knitr::kable(ccle_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+
+ccle_signif_g2p_grid <- readRDS("./data_munging/rds/ccle_signif_g2p_grid.rds")
+knitr::kable(ccle_signif_g2p_grid[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+Test G2P genes in lineage-grouped context:
+```{r, eval=FALSE}
+ccle_signif_grid_lineage <- lapply(unique(ccle_data_g2p_grid$Drug), WilcoxonByDrug, dataset = ccle_data_g2p_grid, data_name = "ccle", grouping_var = "lineage")
+names(ccle_signif_grid_lineage) <- unique(ccle_signif_grid_lineage$Drug)
+ccle_signif_grid_lineage <- rbindlist(ccle_signif_grid_lineage, use.names = TRUE)
+ccle_signif_grid_lineage <- ccle_signif_grid_lineage[order(ccle_signif_grid_lineage$p),]
+saveRDS(ccle_signif_grid_lineage, "./data_munging/rds/ccle_signif_grid_lineage.rds")
+
+ccle_signif_g2p_lineage <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene_Lin", data = ccle_data_g2p_dgl, method = "wilcox.test", p.adjust.method = "BH")
+ccle_signif_g2p_lineage <- adj_signif(ccle_signif_g2p_lineage)
+ccle_signif_g2p_lineage <- ccle_signif_g2p_lineage[order(ccle_signif_g2p_lineage$p),]
+saveRDS(ccle_signif_g2p_lineage, "./data_munging/rds/ccle_signif_g2p_lineage.rds")
+```
+
+```{r}
+ccle_signif_g2p_lineage <- readRDS("./data_munging/rds/ccle_signif_g2p_lineage.rds")
+ccle_signif_grid_lineage <- readRDS("./data_munging/rds/ccle_signif_grid_lineage.rds")
+
+knitr::kable(ccle_signif_g2p_lineage[, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+
+knitr::kable(ccle_signif_grid_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+## CTRP
+
+Test all CRISPR genes in lineage-agnostic context:
 ```{r, eval=FALSE}
@@
 
-GDSC:
+Test G2P genes in lineage-agnostic context:
+```{r, eval=FALSE}
+ctrp_signif_g2p <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene", data = ctrp_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
+ctrp_signif_g2p <- adj_signif(ctrp_signif_g2p)
+ctrp_signif_g2p <- ctrp_signif_g2p[order(ctrp_signif_g2p$p),]
+saveRDS(ctrp_signif_g2p, "./data_munging/rds/ctrp_signif_g2p_gene.rds")
+
+# Grid comparisons of G2P drugs and genes
+ctrp_signif_g2p_grid <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene", data = ctrp_data_g2p_grid, method = "wilcox.test", p.adjust.method = "BH")
+ctrp_signif_g2p_grid <- adj_signif(ctrp_signif_g2p_grid)
+ctrp_signif_g2p_grid <- ctrp_signif_g2p_grid[order(ctrp_signif_g2p_grid$p),]
+saveRDS(ctrp_signif_g2p_grid, "./data_munging/rds/ctrp_signif_g2p_grid.rds")
+```
+
+```{r}
+ctrp_signif_g2p <- readRDS("./data_munging/rds/ctrp_signif_g2p_gene.rds")
+knitr::kable(ctrp_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+
+ctrp_signif_g2p_grid <- readRDS("./data_munging/rds/ctrp_signif_g2p_grid.rds")
+knitr::kable(ctrp_signif_g2p_grid[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+Test G2P genes in lineage-grouped context:
+```{r, eval=FALSE}
+ctrp_signif_grid_lineage <- lapply(unique(ctrp_data_g2p_grid$Drug), WilcoxonByDrug, dataset = ctrp_data_g2p_grid, data_name = "ctrp", grouping_var = "lineage")
+names(ctrp_signif_grid_lineage) <- unique(ctrp_signif_grid_lineage$Drug)
+ctrp_signif_grid_lineage <- rbindlist(ctrp_signif_grid_lineage, use.names = TRUE)
+ctrp_signif_grid_lineage <- ctrp_signif_grid_lineage[order(ctrp_signif_grid_lineage$p),]
+saveRDS(ctrp_signif_grid_lineage, "./data_munging/rds/ctrp_signif_grid_lineage.rds")
+
+ctrp_signif_g2p_lineage <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene_Lin", data = ctrp_data_g2p_dgl, method = "wilcox.test", p.adjust.method = "BH")
+ctrp_signif_g2p_lineage <- adj_signif(ctrp_signif_g2p_lineage)
+ctrp_signif_g2p_lineage <- ctrp_signif_g2p_lineage[order(ctrp_signif_g2p_lineage$p),]
+saveRDS(ctrp_signif_g2p_lineage, "./data_munging/rds/ctrp_signif_g2p_lineage.rds")
+```
+
+```{r}
+ctrp_signif_g2p_lineage <- readRDS("./data_munging/rds/ctrp_signif_g2p_lineage.rds")
+ctrp_signif_grid_lineage <- readRDS("./data_munging/rds/ctrp_signif_grid_lineage.rds")
+
+knitr::kable(ctrp_signif_g2p_lineage[, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+
+knitr::kable(ctrp_signif_grid_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+## GDSC
+
+Test all CRISPR genes in lineage-agnostic context:
 ```{r, eval=FALSE}
@@
 
-# Dataset summaries
+Test G2P genes in lineage-agnostic context:
+```{r, eval=FALSE}
+gdsc_signif_g2p <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene", data = gdsc_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
+gdsc_signif_g2p <- adj_signif(gdsc_signif_g2p)
+gdsc_signif_g2p <- gdsc_signif_g2p[order(gdsc_signif_g2p$p),]
+saveRDS(gdsc_signif_g2p, "./data_munging/rds/gdsc_signif_g2p_gene.rds")
+
+# Grid comparisons of G2P drugs and genes
+gdsc_signif_g2p_grid <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene", data = gdsc_data_g2p_grid, method = "wilcox.test", p.adjust.method = "BH")
+gdsc_signif_g2p_grid <- adj_signif(gdsc_signif_g2p_grid)
+gdsc_signif_g2p_grid <- gdsc_signif_g2p_grid[order(gdsc_signif_g2p_grid$p),]
+saveRDS(gdsc_signif_g2p_grid, "./data_munging/rds/gdsc_signif_g2p_grid.rds")
+```
+
+```{r}
+gdsc_signif_g2p <- readRDS("./data_munging/rds/gdsc_signif_g2p_gene.rds")
+knitr::kable(gdsc_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+
+gdsc_signif_g2p_grid <- readRDS("./data_munging/rds/gdsc_signif_g2p_grid.rds")
+knitr::kable(gdsc_signif_g2p_grid[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+Test G2P genes in lineage-grouped context:
+```{r, eval=FALSE}
+gdsc_signif_grid_lineage <- lapply(unique(gdsc_data_g2p_grid$Drug), WilcoxonByDrug, dataset = gdsc_data_g2p_grid, data_name = "gdsc", grouping_var = "lineage")
+names(gdsc_signif_grid_lineage) <- unique(gdsc_signif_grid_lineage$Drug)
+gdsc_signif_grid_lineage <- rbindlist(gdsc_signif_grid_lineage, use.names = TRUE)
+gdsc_signif_grid_lineage <- gdsc_signif_grid_lineage[order(gdsc_signif_grid_lineage$p),]
+saveRDS(gdsc_signif_grid_lineage, "./data_munging/rds/gdsc_signif_grid_lineage.rds")
+
+gdsc_signif_g2p_lineage <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene_Lin", data = gdsc_data_g2p_dgl, method = "wilcox.test", p.adjust.method = "BH")
+gdsc_signif_g2p_lineage <- adj_signif(gdsc_signif_g2p_lineage)
+gdsc_signif_g2p_lineage <- gdsc_signif_g2p_lineage[order(gdsc_signif_g2p_lineage$p),]
+saveRDS(gdsc_signif_g2p_lineage, "./data_munging/rds/gdsc_signif_g2p_lineage.rds")
+```
+
+```{r}
+gdsc_signif_g2p_lineage <- readRDS("./data_munging/rds/gdsc_signif_g2p_lineage.rds")
+gdsc_signif_grid_lineage <- readRDS("./data_munging/rds/gdsc_signif_grid_lineage.rds")
+
+knitr::kable(gdsc_signif_g2p_lineage[, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+
+knitr::kable(gdsc_signif_grid_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+# PEARSON CORRELATIONS
 
@@
 
-## CRISPR: Mutation status counts
-
-```{r}
-crispr_data_g2p_summ <- unique(crispr_data_g2p[, c("Hugo_Symbol", "N_Nonsilent_Mutant", "N_Nonsilent_Wildtype")])
-crispr_data_g2p_summ$Percent_Mutant <- crispr_data_g2p_summ$N_Nonsilent_Mutant / (crispr_data_g2p_summ$N_Nonsilent_Mutant + crispr_data_g2p_summ$N_Nonsilent_Wildtype) * 100
-rownames(crispr_data_g2p_summ) <- NULL
-
-# write.table(crispr_data_g2p_summ, file = "~/Desktop/crispr_data_g2p_summ_20181003.tsv", quote = FALSE, sep = "\t")
-
-knitr::kable(crispr_data_g2p_summ, caption = "CRISPR: Level A G2P genes mutation status summary") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-## G2P evidence
-
-G2P summary stats:
-```{r}
-g2p_druggene_p_tally <- g2p_filt %>% group_by(Drug_Gene) %>% tally() %>% drop_na()
-range(g2p_druggene_p_tally$n)
-mean(g2p_druggene_p_tally$n)
-sd(g2p_druggene_p_tally$n)
-
-g2p_drug_tally <- g2p_filt %>% group_by(Drug) %>% tally() %>% drop_na()
-range(g2p_drug_tally$n)
-mean(g2p_drug_tally$n)
-sd(g2p_drug_tally$n)
-
-g2p_gene_tally <- g2p_filt %>% group_by(Gene) %>% tally() %>% drop_na()
-range(g2p_gene_tally$n)
-mean(g2p_gene_tally$n)
-sd(g2p_gene_tally$n)
-
-g2p_druggenelin_tally <- g2p_filt %>% group_by(Drug, Gene, Drug_Gene, group_general_lineage_name) %>% tally() %>% drop_na()
-length(unique(g2p_druggenelin_tally$Drug))
-length(unique(g2p_druggenelin_tally$Gene))
-unique(g2p_filt$Phenotype.Description)
-```
-
-### Lineage-agnostic
-
-#### CRISPR
-
-```{r fig.height=1.5, fig.width=12}
-crispr_signif_g2p_gene$y_label <- "CRISPR"
-crispr_signif_g2p_gene$Hugo_Symbol <- factor(crispr_signif_g2p_gene$Hugo_Symbol, levels = g2p_genes)
-crispr_signif_g2p_gene$p <- as.numeric(as.character(crispr_signif_g2p_gene$p))
-
-crispr_mut_heatmap_plot <- ggplot(data = crispr_signif_g2p_gene, aes(x = Hugo_Symbol, y = y_label)) +
-  geom_tile(aes(fill = p)) +
-  scale_fill_gradientn(colors = c("darkgreen", "honeydew", "white"), values = c(0, 0.05, 1), na.value = "darksalmon") +
-  scale_x_discrete(drop = FALSE) +
-  theme(axis.title.y = element_blank(), axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 10)) +
-  labs(x = "Gene")
-crispr_mut_heatmap_plot
-
-# write.table(crispr_signif_g2p_gene, file = "~/Desktop/crispr_signif_g2p_gene_20181203.csv", quote = FALSE, sep = ",", row.names = FALSE)
-# ggsave("./plots/manuscript/crispr_mut_heatmap_plot_example.png", crispr_mut_heatmap_plot, device = "png", dpi = 450, width = 12, height = 1.5, units = "in")
-```
-
-```{r fig.height=5, fig.width=12}
-crispr_res_mut <- select(crispr_signif_g2p_gene, Hugo_Symbol, p)
-crispr_res_mut$corr <- 0
-crispr_res_mut$Metric <- "Mutation Status"
-crispr_res_mut$p_log10 <- -log10(crispr_res_mut$p)
-subset(crispr_res_mut, p < 0.05)
-
+Pearson correlations for assessing effect of gene expression and copy number on gene essentiality score and AUC.
+
+## CRISPR
+
+```{r}
 crispr_pearson_res_GE <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>%
@@
                               Metric = "Gene Expression")
-subset(crispr_pearson_res_GE, p < 0.05)
 
@@
                               Metric = "Copy Number")
-subset(crispr_pearson_res_CN, p < 0.05)
-
-crispr_pearson_res <- rbind(crispr_pearson_res_GE, crispr_pearson_res_CN)
-crispr_pearson_res$Metric <- factor(crispr_pearson_res$Metric, levels = c("Gene Expression", "Copy Number"))
-crispr_pearson_res$p_log10 <- -log10(crispr_pearson_res$p)
-
-crispr_summ_res_mut_plot <- ggplot(data = subset(crispr_res_mut, p < 0.05)) +
-  facet_grid(~ Metric) +
-  scale_y_continuous(breaks = seq(0, 50, by = 5), labels = seq(0, 50, by = 5)) +
-  coord_cartesian(ylim = c(0, 50)) +
-  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_label_repel(mapping = aes(y = p_log10, x = corr, label = Hugo_Symbol, color = Metric), force = 10, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
-  theme(legend.position = "none", panel.grid.major.x = element_blank(), panel.grid.minor.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(5.5, 1.5, 5.5, 5.5), "pt")) +
-  scale_color_manual(values = c("Mutation Status" = "darkorchid4")) +
-  labs(y = "-log10(p-value)")
-
-crispr_summ_res_pearson_plot <- ggplot(data = subset(crispr_pearson_res, p < 0.05)) +
-  facet_grid(~ Metric, scales = "free_x", space = "free") +
-  scale_y_continuous(breaks = seq(0, 50, by = 5), labels = seq(0, 50, by = 5)) +
-  scale_x_continuous(breaks = seq(-0.6, 0.3, by = 0.1), labels = formatC(seq(-0.6, 0.3, by = 0.1), digits = 2, format = "f")) +
-  coord_cartesian(ylim = c(0, 50)) +
-  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
-  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_label_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Hugo_Symbol), force = 10, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
-  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
-  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
-  labs(x = "Pearson correlation coefficient (r)")
-
-crispr_genomic_features_summ_plot <- plot_grid(crispr_summ_res_mut_plot, crispr_summ_res_pearson_plot, align = "h", rel_widths = c(1, 5))
-crispr_genomic_features_summ_plot
-
-# ggsave("./plots/manuscript/crispr_genomic_features_summ_plot.png", crispr_genomic_features_summ_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
-```
-
-#### Mutation status
-
-```{r fig.height=4, fig.width=8}
-g2p_druggene_p_summ <- merge(g2p_druggene_p_tally, ccle_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all.x = TRUE)
-g2p_druggene_p_summ <- merge(g2p_druggene_p_summ, ctrp_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all.x = TRUE, suffixes = c("_CCLE", "_CTRP"))
-g2p_druggene_p_summ <- merge(g2p_druggene_p_summ, gdsc_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all.x = TRUE)
-colnames(g2p_druggene_p_summ)[colnames(g2p_druggene_p_summ) == "p_CCLE"] <- "CCLE"
-colnames(g2p_druggene_p_summ)[colnames(g2p_druggene_p_summ) == "p_CTRP"] <- "CTRP"
-colnames(g2p_druggene_p_summ)[colnames(g2p_druggene_p_summ) == "p"] <- "GDSC"
-
-g2p_druggene_p_summ_melt <- melt(g2p_druggene_p_summ, id.vars = c("Drug_Gene", "n"), measure.vars = c("CCLE", "CTRP", "GDSC"), variable.name = "Dataset", value.name = "p")
-
-# g2p_druggene_p_summ_plot <- ggplot(data = g2p_druggene_p_summ_melt, aes(x = p, y = n, shape = Dataset, color = Dataset)) +
-#   geom_point(size = 2) +
-#   scale_color_manual(values = c("green3", "darkslategray4", "darkturquoise")) +
-#   labs(x = "Gene-drug association p-value by mutation status", y = "Number of level A G2P associations")
-# g2p_druggene_p_summ_plot
-# ggsave("./plots/manuscript/g2p_druggene_p_summ_plot.png", g2p_druggene_p_summ_plot, device = "png", dpi = 450, width = 8, height = 4, units = "in")
-```
-
-```
-for_dan <- with(g2p_druggene_p_summ, cbind(n, CCLE, CTRP, GDSC, colsplit(Drug_Gene, pattern = "_", names = c("Drug", "Hugo_Symbol"))))
-write.table(for_dan, file = "~/Desktop/for_dan.tsv", sep = "\t")
-```
-
-```{r}
-ccle_druggene_summ <- merge(g2p_druggene_p_tally, ccle_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
-ccle_druggene_summ$n <- ifelse(is.na(ccle_druggene_summ$n), 0, ccle_druggene_summ$n)
-ccle_druggene_summ$InG2P <- ifelse(ccle_druggene_summ$n != 0, "Yes", "No")
-ccle_druggene_summ$Dataset <- "CCLE"
-ccle_p_ttest <- t.test(ccle_druggene_summ$p ~ ccle_druggene_summ$InG2P)
-ccle_p_ttest_res <- paste0("t(", round(ccle_p_ttest$parameter, 0), ") = ", round(ccle_p_ttest$statistic, 2), ", p = ", round(ccle_p_ttest$p.value, 2))
-
-ctrp_druggene_summ <- merge(g2p_druggene_p_tally, ctrp_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
-ctrp_druggene_summ$n <- ifelse(is.na(ctrp_druggene_summ$n), 0, ctrp_druggene_summ$n)
-ctrp_druggene_summ$InG2P <- ifelse(ctrp_druggene_summ$n != 0, "Yes", "No")
-ctrp_druggene_summ$Dataset <- "CTRP"
-ctrp_p_ttest <- t.test(ctrp_druggene_summ$p ~ ctrp_druggene_summ$InG2P)
-ctrp_p_ttest_res <- paste0("t(", round(ctrp_p_ttest$parameter, 0), ") = ", round(ctrp_p_ttest$statistic, 2), ", p = ", formatC(ctrp_p_ttest$p.value, digits = 2, format = "f"))
-
-gdsc_druggene_summ <- merge(g2p_druggene_p_tally, gdsc_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
-gdsc_druggene_summ$n <- ifelse(is.na(gdsc_druggene_summ$n), 0, gdsc_druggene_summ$n)
-gdsc_druggene_summ$InG2P <- ifelse(gdsc_druggene_summ$n != 0, "Yes", "No")
-gdsc_druggene_summ$Dataset <- "GDSC"
-gdsc_p_ttest <- t.test(gdsc_druggene_summ$p ~ gdsc_druggene_summ$InG2P)
-gdsc_p_ttest_res <- paste0("t(", round(gdsc_p_ttest$parameter, 0), ") = ", round(gdsc_p_ttest$statistic, 2), ", p = ", formatC(gdsc_p_ttest$p.value, digits = 2, format = "f"))
-
-g2p_druggene_all_summ <- rbind(ccle_druggene_summ, ctrp_druggene_summ, gdsc_druggene_summ)
-g2p_druggene_all_summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"), Test_Results_p = c(ccle_p_ttest_res, ctrp_p_ttest_res, gdsc_p_ttest_res))
-g2p_druggene_all_summ$Drug_Gene_Ordered <- factor(g2p_druggene_all_summ$Drug_Gene, levels = as.character(unique(g2p_druggene_all_summ$Drug_Gene)), labels = sapply(strsplit(x = as.character(unique(g2p_druggene_all_summ$Drug_Gene)), split = "_"), function(x) paste0(x[1], "\n", x[2])))
-```
-
-```{r fig.height=5, fig.width=12}
-plot_p_point <- ggplot(data = g2p_druggene_all_summ, aes(x = p, y = n, label = Drug_Gene)) +
-  facet_wrap(~ Dataset, scales = "free_x") +
-  geom_point(mapping = aes(color = InG2P), alpha = 0.5) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
-  geom_text_repel(data = subset(g2p_druggene_all_summ, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
-  geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = 0.5, y = 115, label = Test_Results_p)) +
-  labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations") +
-  theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
-
-plot_p_box <- ggplot(data = g2p_druggene_all_summ) +
-  facet_wrap(~ Dataset, scales = "free_x") +
-  geom_violin(mapping = aes(color = InG2P, fill = InG2P, y = p, x = InG2P), alpha = 0.35) +
-  geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), width = 0.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  coord_flip() +
-  labs(x = "In G2P?") +
-  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
-plot_p_point <- ggplot_gtable(ggplot_build(plot_p_point))
-plot_p_box <- ggplot_gtable(ggplot_build(plot_p_box))
-p_maxWidth <-  grid::unit.pmax(plot_p_point$widths, plot_p_box$widths)
-plot_p_point$widths <- as.list(p_maxWidth)
-plot_p_box$widths <- as.list(p_maxWidth)
-g2p_druggene_mut_plot <- cowplot::plot_grid(plot_p_box,
-                   plot_p_point,
-                   nrow = 2,
-                   rel_heights = c(1, 4))
-g2p_druggene_mut_plot
-
-# ggsave("./plots/manuscript/g2p_druggene_mut_plot.png", g2p_druggene_mut_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
-```
-
-```{r, eval=FALSE}
-plot_p_point <- ggplot(data = g2p_druggene_all_summ) +
-  facet_wrap(~ Dataset, scales = "free_x") +
-  geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = p, y = n), alpha = 0.5) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
-  geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = 0.5, y = 115, label = Test_Results_p)) +
-  labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations") +
-  theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
-
-plot_p_box <- ggplot(data = g2p_druggene_all_summ) +
-  facet_wrap(~ Dataset, scales = "free_x") +
-  geom_violin(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.5) +
-  geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.75, width = 0.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  coord_flip() +
-  labs(x = "Level A G2P\nassociation") +
-  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
-plot <- subplot(plot_p_box, plot_p_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Gene-drug association p-value between mutation groups"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
-
-saveWidgetFix(widget = plot, file = "./plots/manuscript/g2p_druggene_mut_plot.html")
-```
-
-#### GE and CN
-
-```{r}
+```
+
+## Drug screens
+
+```{r}
+g2p_druggene_p_tally <- g2p_filt %>% group_by(Drug_Gene) %>% tally() %>% drop_na()
 ccle_pearson_res <- ccle_data_g2p_grid %>% group_by(Drug_Gene) %>%
@@
 gdsc_pearson_ttest_res_CN <- paste0("t(", round(gdsc_pearson_ttest_CN$parameter, 0), ") = ", round(gdsc_pearson_ttest_CN$statistic, 2), ", p = ", round(gdsc_pearson_ttest_CN$p.value, 3))
-
+```
+
+# SUMMARIES
+
+--------------------------------------------------------------------------------
+
+## CRISPR: Mutation status counts
+
+```{r}
+crispr_data_g2p_summ <- unique(crispr_data_g2p[, c("Hugo_Symbol", "N_Nonsilent_Mutant", "N_Nonsilent_Wildtype")])
+crispr_data_g2p_summ$Percent_Mutant <- crispr_data_g2p_summ$N_Nonsilent_Mutant / (crispr_data_g2p_summ$N_Nonsilent_Mutant + crispr_data_g2p_summ$N_Nonsilent_Wildtype) * 100
+rownames(crispr_data_g2p_summ) <- NULL
+
+# write.table(crispr_data_g2p_summ, file = "~/Desktop/crispr_data_g2p_summ_20181003.tsv", quote = FALSE, sep = "\t")
+
+knitr::kable(crispr_data_g2p_summ, caption = "CRISPR: Level A G2P genes mutation status summary") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+## G2P tallies and summary stats
+
+```{r}
+print("Drug-Gene")
+g2p_druggene_p_tally <- g2p_filt %>% group_by(Drug_Gene) %>% tally() %>% drop_na()
+nrow(g2p_druggene_p_tally)
+range(g2p_druggene_p_tally$n)
+mean(g2p_druggene_p_tally$n)
+sd(g2p_druggene_p_tally$n)
+
+print("Drug")
+g2p_drug_tally <- g2p_filt %>% group_by(Drug) %>% tally() %>% drop_na()
+range(g2p_drug_tally$n)
+mean(g2p_drug_tally$n)
+sd(g2p_drug_tally$n)
+
+print("Gene")
+g2p_gene_tally <- g2p_filt %>% group_by(Gene) %>% tally() %>% drop_na()
+range(g2p_gene_tally$n)
+mean(g2p_gene_tally$n)
+sd(g2p_gene_tally$n)
+
+print("Drug-Gene-Lineage")
+g2p_druggenelin_tally <- g2p_filt %>% group_by(Drug, Gene, Drug_Gene, group_general_lineage_name) %>% tally() %>% drop_na()
+nrow(g2p_druggenelin_tally)
+length(unique(g2p_druggenelin_tally$Drug))
+length(unique(g2p_druggenelin_tally$Gene))
+unique(g2p_filt$Phenotype.Description)
+```
+
+## Lineage-agnostic
+
+### Mut
+
+CRISPR mutation status plots of p-values:
+```{r fig.height=1.5, fig.width=12}
+crispr_signif_g2p_gene$y_label <- "CRISPR"
+crispr_signif_g2p_gene$Hugo_Symbol <- factor(crispr_signif_g2p_gene$Hugo_Symbol, levels = g2p_genes)
+crispr_signif_g2p_gene$p <- as.numeric(as.character(crispr_signif_g2p_gene$p))
+
+crispr_mut_heatmap_plot <- ggplot(data = crispr_signif_g2p_gene, aes(x = Hugo_Symbol, y = y_label)) +
+  geom_tile(aes(fill = p)) +
+  scale_fill_gradientn(colors = c("darkgreen", "honeydew", "white"), values = c(0, 0.05, 1), na.value = "darksalmon") +
+  scale_x_discrete(drop = FALSE) +
+  theme(axis.title.y = element_blank(), axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 10)) +
+  labs(x = "Gene")
+crispr_mut_heatmap_plot
+
+# write.table(crispr_signif_g2p_gene, file = "~/Desktop/crispr_signif_g2p_gene_20181203.csv", quote = FALSE, sep = ",", row.names = FALSE)
+# ggsave("./plots/manuscript/crispr_mut_heatmap_plot_example.png", crispr_mut_heatmap_plot, device = "png", dpi = 450, width = 12, height = 1.5, units = "in")
+```
+
+Drug screen test plot for G2P associations vs. p-value plot:
+```{r fig.height=4, fig.width=8}
+g2p_druggene_p_summ <- merge(g2p_druggene_p_tally, ccle_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all.x = TRUE)
+g2p_druggene_p_summ <- merge(g2p_druggene_p_summ, ctrp_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all.x = TRUE, suffixes = c("_CCLE", "_CTRP"))
+g2p_druggene_p_summ <- merge(g2p_druggene_p_summ, gdsc_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all.x = TRUE)
+colnames(g2p_druggene_p_summ)[colnames(g2p_druggene_p_summ) == "p_CCLE"] <- "CCLE"
+colnames(g2p_druggene_p_summ)[colnames(g2p_druggene_p_summ) == "p_CTRP"] <- "CTRP"
+colnames(g2p_druggene_p_summ)[colnames(g2p_druggene_p_summ) == "p"] <- "GDSC"
+
+g2p_druggene_p_summ_melt <- melt(g2p_druggene_p_summ, id.vars = c("Drug_Gene", "n"), measure.vars = c("CCLE", "CTRP", "GDSC"), variable.name = "Dataset", value.name = "p")
+
+g2p_druggene_p_summ_plot <- ggplot(data = g2p_druggene_p_summ_melt, aes(x = p, y = n, shape = Dataset, color = Dataset)) +
+  geom_point(size = 2) +
+  scale_color_manual(values = c("green3", "darkslategray4", "darkturquoise")) +
+  labs(x = "Gene-drug association p-value by mutation status", y = "Number of level A G2P associations")
+g2p_druggene_p_summ_plot
+# ggsave("./plots/manuscript/g2p_druggene_p_summ_plot.png", g2p_druggene_p_summ_plot, device = "png", dpi = 450, width = 8, height = 4, units = "in")
+```
+
+Code to write out dataframe of p-values for Dan to make green heatmaps:
+```{r}
+# for_dan <- with(g2p_druggene_p_summ, cbind(n, CCLE, CTRP, GDSC, colsplit(Drug_Gene, pattern = "_", names = c("Drug", "Hugo_Symbol"))))
+# write.table(for_dan, file = "~/Desktop/for_dan.tsv", sep = "\t")
+```
+
+```{r}
+ccle_druggene_summ <- merge(g2p_druggene_p_tally, ccle_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
+ccle_druggene_summ$n <- ifelse(is.na(ccle_druggene_summ$n), 0, ccle_druggene_summ$n)
+ccle_druggene_summ$InG2P <- ifelse(ccle_druggene_summ$n != 0, "Yes", "No")
+ccle_druggene_summ$Dataset <- "CCLE"
+ccle_p_ttest <- t.test(ccle_druggene_summ$p ~ ccle_druggene_summ$InG2P)
+ccle_p_ttest_res <- paste0("t(", round(ccle_p_ttest$parameter, 0), ") = ", round(ccle_p_ttest$statistic, 2), ", p = ", round(ccle_p_ttest$p.value, 2))
+
+ctrp_druggene_summ <- merge(g2p_druggene_p_tally, ctrp_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
+ctrp_druggene_summ$n <- ifelse(is.na(ctrp_druggene_summ$n), 0, ctrp_druggene_summ$n)
+ctrp_druggene_summ$InG2P <- ifelse(ctrp_druggene_summ$n != 0, "Yes", "No")
+ctrp_druggene_summ$Dataset <- "CTRP"
+ctrp_p_ttest <- t.test(ctrp_druggene_summ$p ~ ctrp_druggene_summ$InG2P)
+ctrp_p_ttest_res <- paste0("t(", round(ctrp_p_ttest$parameter, 0), ") = ", round(ctrp_p_ttest$statistic, 2), ", p = ", formatC(ctrp_p_ttest$p.value, digits = 2, format = "f"))
+
+gdsc_druggene_summ <- merge(g2p_druggene_p_tally, gdsc_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
+gdsc_druggene_summ$n <- ifelse(is.na(gdsc_druggene_summ$n), 0, gdsc_druggene_summ$n)
+gdsc_druggene_summ$InG2P <- ifelse(gdsc_druggene_summ$n != 0, "Yes", "No")
+gdsc_druggene_summ$Dataset <- "GDSC"
+gdsc_p_ttest <- t.test(gdsc_druggene_summ$p ~ gdsc_druggene_summ$InG2P)
+gdsc_p_ttest_res <- paste0("t(", round(gdsc_p_ttest$parameter, 0), ") = ", round(gdsc_p_ttest$statistic, 2), ", p = ", formatC(gdsc_p_ttest$p.value, digits = 2, format = "f"))
+
+g2p_druggene_all_summ <- rbind(ccle_druggene_summ, ctrp_druggene_summ, gdsc_druggene_summ)
+g2p_druggene_all_summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"), Test_Results_p = c(ccle_p_ttest_res, ctrp_p_ttest_res, gdsc_p_ttest_res))
+g2p_druggene_all_summ$Drug_Gene_Ordered <- factor(g2p_druggene_all_summ$Drug_Gene, levels = as.character(unique(g2p_druggene_all_summ$Drug_Gene)), labels = sapply(strsplit(x = as.character(unique(g2p_druggene_all_summ$Drug_Gene)), split = "_"), function(x) paste0(x[1], "\n", x[2])))
+```
+
+```{r fig.height=5, fig.width=12}
+plot_p_point <- ggplot(data = g2p_druggene_all_summ, aes(x = p, y = n, label = Drug_Gene)) +
+  facet_wrap(~ Dataset, scales = "free_x") +
+  geom_point(mapping = aes(color = InG2P), alpha = 0.5) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
+  geom_text_repel(data = subset(g2p_druggene_all_summ, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
+  geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = 0.5, y = 115, label = Test_Results_p)) +
+  labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations") +
+  theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
+
+plot_p_box <- ggplot(data = g2p_druggene_all_summ) +
+  facet_wrap(~ Dataset, scales = "free_x") +
+  geom_violin(mapping = aes(color = InG2P, fill = InG2P, y = p, x = InG2P), alpha = 0.35) +
+  geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), width = 0.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  coord_flip() +
+  labs(x = "In G2P?") +
+  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
+
+plot_p_point <- ggplot_gtable(ggplot_build(plot_p_point))
+plot_p_box <- ggplot_gtable(ggplot_build(plot_p_box))
+p_maxWidth <-  grid::unit.pmax(plot_p_point$widths, plot_p_box$widths)
+plot_p_point$widths <- as.list(p_maxWidth)
+plot_p_box$widths <- as.list(p_maxWidth)
+g2p_druggene_mut_plot <- cowplot::plot_grid(plot_p_box,
+                   plot_p_point,
+                   nrow = 2,
+                   rel_heights = c(1, 4))
+g2p_druggene_mut_plot
+
+# ggsave("./plots/manuscript/g2p_druggene_mut_plot.png", g2p_druggene_mut_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
+```
+
+```{r, eval=FALSE}
+plot_p_point <- ggplot(data = g2p_druggene_all_summ) +
+  facet_wrap(~ Dataset, scales = "free_x") +
+  geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = p, y = n), alpha = 0.5) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
+  geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = 0.5, y = 115, label = Test_Results_p)) +
+  labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations") +
+  theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
+
+plot_p_box <- ggplot(data = g2p_druggene_all_summ) +
+  facet_wrap(~ Dataset, scales = "free_x") +
+  geom_violin(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.5) +
+  geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.75, width = 0.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  coord_flip() +
+  labs(x = "Level A G2P\nassociation") +
+  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
+
+plot <- subplot(plot_p_box, plot_p_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Gene-drug association p-value between mutation groups"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
+
+saveWidgetFix(widget = plot, file = "./plots/manuscript/g2p_druggene_mut_plot.html")
+```
+
+### GE
+
+```{r}
 g2p_druggene_pearson <- rbind(ccle_pearson_res, ctrp_pearson_res, gdsc_pearson_res)
@@
 
-Gene expression:
 ```{r fig.height=5, fig.width=12}
@@
 
-Copy number:
+### CN
+
 ```{r fig.height=5.5, fig.width=12}
@@
 
-#### Summary: Drug screen test plots
-
+## G2P associations
+
+This section contains summary plots for the Wilcoxon tests and Pearson correlations done for only level A G2P drug-gene associations (i.e.
+not the grid tests) and G2P genes in the case of the CRISPR dataset.
+
+### CRISPR
+
+```{r fig.height=5, fig.width=12}
+crispr_res_mut <- select(crispr_signif_g2p_gene, Hugo_Symbol, p)
+crispr_res_mut$corr <- 0
+crispr_res_mut$Metric <- "Mutation Status"
+crispr_res_mut$p_log10 <- -log10(crispr_res_mut$p)
+subset(crispr_res_mut, p < 0.05)
+
+subset(crispr_pearson_res_GE, p < 0.05)
+subset(crispr_pearson_res_CN, p < 0.05)
+
+crispr_pearson_res <- rbind(crispr_pearson_res_GE, crispr_pearson_res_CN)
+crispr_pearson_res$Metric <- factor(crispr_pearson_res$Metric, levels = c("Gene Expression", "Copy Number"))
+crispr_pearson_res$p_log10 <- -log10(crispr_pearson_res$p)
+
+crispr_summ_res_mut_plot <- ggplot(data = subset(crispr_res_mut, p < 0.05)) +
+  facet_grid(~ Metric) +
+  scale_y_continuous(breaks = seq(0, 50, by = 5), labels = seq(0, 50, by = 5)) +
+  coord_cartesian(ylim = c(0, 50)) +
+  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
+  geom_label_repel(mapping = aes(y = p_log10, x = corr, label = Hugo_Symbol, color = Metric), force = 10, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
+  theme(legend.position = "none", panel.grid.major.x = element_blank(), panel.grid.minor.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(5.5, 1.5, 5.5, 5.5), "pt")) +
+  scale_color_manual(values = c("Mutation Status" = "darkorchid4")) +
+  labs(y = "-log10(p-value)")
+
+crispr_summ_res_pearson_plot <- ggplot(data = subset(crispr_pearson_res, p < 0.05)) +
+  facet_grid(~ Metric, scales = "free_x", space = "free") +
+  scale_y_continuous(breaks = seq(0, 50, by = 5), labels = seq(0, 50, by = 5)) +
+  scale_x_continuous(breaks = seq(-0.6, 0.3, by = 0.1), labels = formatC(seq(-0.6, 0.3, by = 0.1), digits = 2, format = "f")) +
+  coord_cartesian(ylim = c(0, 50)) +
+  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
+  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
+  geom_label_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Hugo_Symbol), force = 10, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
+  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
+  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
+  labs(x = "Pearson correlation coefficient (r)")
+
+crispr_genomic_features_summ_plot <- plot_grid(crispr_summ_res_mut_plot, crispr_summ_res_pearson_plot, align = "h", rel_widths = c(1, 5))
+crispr_genomic_features_summ_plot
+
+# ggsave("./plots/manuscript/crispr_genomic_features_summ_plot.png", crispr_genomic_features_summ_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
+```
+
+### CCLE
+
+G2P drug-gene associations with a significant effect on AUC by mutation status, gene expression, and copy number:
 ```{r fig.height=4, fig.width=12}
@@
 
+### CTRP
+
+G2P drug-gene associations with a significant effect on AUC by mutation status, gene expression, and copy number:
 ```{r fig.height=6, fig.width=12}
@@
   geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_label_repel(mapping = aes(y = p_log10, x = corr, label = Drug_Gene, color = Metric), force = 10, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 1) +
+  geom_text_repel(mapping = aes(y = p_log10, x = corr, label = Drug_Gene, color = Metric), force = 10, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 1) +
   theme(legend.position = "none", panel.grid.major.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(5.5, 1.5, 5.5, 5.5), "pt"), strip.background.y = element_blank(), strip.text.y = element_blank()) +
@@
   geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_label_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 10, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
+  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 10, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
   scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
@@
 
+### GDSC
+
+G2P drug-gene associations with a significant effect on AUC by mutation status, gene expression, and copy number:
 ```{r fig.height=6, fig.width=12}
@@
 
+### Drug: Mut
+
+G2P drug-gene associations with a significant effect on AUC by mutation status:
 ```{r fig.height=4, fig.width=8}
@@
 
+### Drug: GE and CN
+
+G2P drug-gene associations with a significant effect on AUC by gene expression and copy number:
 ```{r fig.height=12, fig.width=12}
@@
 
-```{r}
-levels(all_pearson_res$Dataset)
-```
-
-### By lineage
-
-#### Mutation Status
-
+## Lineage-grouped
+
+### Mut: Grid
+
+Summarize the Wilcoxon test p-values of the grid tests by mutation status. Grid tests were all lineage-agnostic G2P drug-gene associations tested across all screened lineages in each dataset:
 ```{r}
 g2p_druggenelin_p_tally <- g2p %>% group_by(Drug_Gene, group_general_lineage_name) %>% tally()
-```
-
-```{r}
+
 ccle_druggenelin_summ <- ccle_signif_grid_lineage
@@
 ccle_druggenelin_summ <- merge(g2p_druggenelin_p_tally, ccle_druggenelin_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
+ccle_druggenelin_summ$Drug_Gene_Lin <- paste0(ccle_druggenelin_summ$Drug_Gene, "_", ccle_druggenelin_summ$group_general_lineage_name)
 ccle_druggenelin_summ$n <- ifelse(is.na(ccle_druggenelin_summ$n), 0, ccle_druggenelin_summ$n)
@@
 ctrp_druggenelin_summ <- merge(g2p_druggenelin_p_tally, ctrp_druggenelin_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
+ctrp_druggenelin_summ$Drug_Gene_Lin <- paste0(ctrp_druggenelin_summ$Drug_Gene, "_", ctrp_druggenelin_summ$group_general_lineage_name)
 ctrp_druggenelin_summ$n <- ifelse(is.na(ctrp_druggenelin_summ$n), 0, ctrp_druggenelin_summ$n)
@@
 gdsc_druggenelin_summ <- merge(g2p_druggenelin_p_tally, gdsc_druggenelin_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
+gdsc_druggenelin_summ$Drug_Gene_Lin <- paste0(gdsc_druggenelin_summ$Drug_Gene, "_", gdsc_druggenelin_summ$group_general_lineage_name)
 gdsc_druggenelin_summ$n <- ifelse(is.na(gdsc_druggenelin_summ$n), 0, gdsc_druggenelin_summ$n)
@@
 gdsc_druggenelin_summ$Dataset <- "GDSC"
-g2p_druggenelin_all_summ <- rbind(ccle_druggenelin_summ, ctrp_druggenelin_summ, gdsc_druggenelin_summ)
-g2p_druggenelin_all_summ$InG2P <- factor(g2p_druggenelin_all_summ$InG2P, levels = c("Yes", "No"))
-# test <- filter(filter(g2p_druggenelin_all_summ, group_general_lineage_name == "breast cancer"), Dataset == "CCLE")
-# test <- test[-39,]
-```
-
+
+dgl_mut_grid_summ <- rbind(ccle_druggenelin_summ, ctrp_druggenelin_summ, gdsc_druggenelin_summ)
+```
+
+Make summary plots of mutation status tests by lineage and return a dataframe of all t-test results from comparing the p-value distributions of G2P and non-G2P drug-gene associaions:
 ```{r, eval=FALSE, results = 'hide'}
-g2p_druggenelin_p_ttest_res <- lapply(as.character(unique(g2p_druggenelin_all_summ$group_general_lineage_name)), MutPlotlyByLineage)
-g2p_druggenelin_p_ttest_res_list <- rbindlist(g2p_druggenelin_p_ttest_res, use.names = TRUE)
-g2p_druggenelin_p_ttest_res_list <- g2p_druggenelin_p_ttest_res_list[order(g2p_druggenelin_p_ttest_res_list$p_value),]
-saveRDS(g2p_druggenelin_p_ttest_res_list, "./data_munging/rds/g2p_druggenelin_p_ttest_res.rds")
-# test <- filter(g2p_druggenelin_all_summ, Dataset == "CCLE")
-# test <- filter(g2p_druggenelin_all_summ, group_general_lineage_name == "biliary tract cancer")
-# test_summ <- test %>% count(InG2P)
-# test2 <- filter(g2p_druggenelin_all_summ, Dataset == "CTRP")
-# test2_summ <- test2 %>% count(group_general_lineage_name, InG2P)
-# test3 <- filter(g2p_druggenelin_all_summ, Dataset == "GDSC")
-# test3_summ <- test3 %>% count(group_general_lineage_name, InG2P)
-```
-
-```{r}
-g2p_druggenelin_p_ttest_res_list <- readRDS("./data_munging/rds/g2p_druggenelin_p_ttest_res.rds")
-knitr::kable(g2p_druggenelin_p_ttest_res_list, caption = "Mutation status: T-test results for level A G2P drug-gene associations across lineages") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-#### GE and CN
-
-DGL overlap:
+dgl_mut_g2p_grid_ttest_res <- lapply(as.character(unique(dgl_mut_grid_summ$group_general_lineage_name)), MutPlotsByLineage)
+dgl_mut_g2p_grid_ttest_res_list <- rbindlist(dgl_mut_g2p_grid_ttest_res, use.names = TRUE)
+dgl_mut_g2p_grid_ttest_res_list <- dgl_mut_g2p_grid_ttest_res_list[order(dgl_mut_g2p_grid_ttest_res_list$p_value),]
+saveRDS(dgl_mut_g2p_grid_ttest_res_list, "./data_munging/rds/dgl_mut_g2p_grid_ttest_res_list.rds")
+```
+
+```{r}
+dgl_mut_g2p_grid_ttest_res_list <- readRDS("./data_munging/rds/dgl_mut_g2p_grid_ttest_res_list.rds")
+knitr::kable(dgl_mut_g2p_grid_ttest_res_list, caption = "Mutation status: T-test results for level A G2P drug-gene associations across lineages") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+### GE/CN: G2P
+
+Drug-gene-lineage (DGL) overlaps between CCLE, CTRP, and GDSC:
 ```{r}
@@
 
-Test the 102 level-A G2P drug-gene-lineage combinations:
+Test the 102 level-A G2P DGL combinations:
 ```{r, eval=FALSE}
@@
 signif_all_lin$Drug_Gene_Lin <- paste0(signif_all_lin$Drug_Gene, "_", signif_all_lin$group_general_lineage_name)
-saveRDS(signif_all_lin, "./data_munging/rds/signif_lin_g2p_dgl.rds")
-```
-
-```{r}
-signif_lin_g2p_dgl <- readRDS("./data_munging/rds/signif_lin_g2p_dgl.rds")
-
+saveRDS(signif_all_lin, "./data_munging/rds/dgl_signif_pearson_g2p.rds")
+```
+
+```{r}
+dgl_signif_pearson_g2p <- readRDS("./data_munging/rds/dgl_signif_pearson_g2p.rds")
+```
+
+```{r}
 # CCLE mut, n = 7
@@
 # CCLE GE/CN, n = 9
-ccle_ge <- select(subset(filter(signif_lin_g2p_dgl, Dataset == "CCLE"), Pearson_Pval_GE < 0.05), Drug_Gene_Lin, Pearson_Pval_GE, Pearson_Corr_GE)
-ccle_cn <- select(subset(filter(signif_lin_g2p_dgl, Dataset == "CCLE"), Pearson_Pval_CN < 0.05), Drug_Gene_Lin, Pearson_Pval_CN, Pearson_Corr_CN)
-ccle_Pear_n <- nrow(filter(signif_lin_g2p_dgl, Dataset == "CCLE"))
+ccle_ge <- select(subset(filter(dgl_signif_pearson_g2p, Dataset == "CCLE"), Pearson_Pval_GE < 0.05), Drug_Gene_Lin, Pearson_Pval_GE, Pearson_Corr_GE)
+ccle_cn <- select(subset(filter(dgl_signif_pearson_g2p, Dataset == "CCLE"), Pearson_Pval_CN < 0.05), Drug_Gene_Lin, Pearson_Pval_CN, Pearson_Corr_CN)
+ccle_Pear_n <- nrow(filter(dgl_signif_pearson_g2p, Dataset == "CCLE"))
 ccle_dgl_summ <- merge(ccle_mut, merge(ccle_ge, ccle_cn, by = "Drug_Gene_Lin", all = TRUE), all = TRUE)
@@
 # CTRP GE/CN, n = 61
-ctrp_ge <- select(subset(filter(signif_lin_g2p_dgl, Dataset == "CTRP"), Pearson_Pval_GE < 0.05), Drug_Gene_Lin, Pearson_Pval_GE, Pearson_Corr_GE)
-ctrp_cn <- select(subset(filter(signif_lin_g2p_dgl, Dataset == "CTRP"), Pearson_Pval_CN < 0.05), Drug_Gene_Lin, Pearson_Pval_CN, Pearson_Corr_CN)
-ctrp_Pear_n <- nrow(filter(signif_lin_g2p_dgl, Dataset == "CTRP"))
+ctrp_ge <- select(subset(filter(dgl_signif_pearson_g2p, Dataset == "CTRP"), Pearson_Pval_GE < 0.05), Drug_Gene_Lin, Pearson_Pval_GE, Pearson_Corr_GE)
+ctrp_cn <- select(subset(filter(dgl_signif_pearson_g2p, Dataset == "CTRP"), Pearson_Pval_CN < 0.05), Drug_Gene_Lin, Pearson_Pval_CN, Pearson_Corr_CN)
+ctrp_Pear_n <- nrow(filter(dgl_signif_pearson_g2p, Dataset == "CTRP"))
 ctrp_dgl_summ <- merge(ctrp_mut, merge(ctrp_ge, ctrp_cn, by = "Drug_Gene_Lin", all = TRUE), all = TRUE)
@@
 # GDSC GE/CN, n = 53
-gdsc_ge <- select(subset(filter(signif_lin_g2p_dgl, Dataset == "GDSC"), Pearson_Pval_GE < 0.05), Drug_Gene_Lin, Pearson_Pval_GE, Pearson_Corr_GE)
-gdsc_cn <- select(subset(filter(signif_lin_g2p_dgl, Dataset == "GDSC"), Pearson_Pval_CN < 0.05), Drug_Gene_Lin, Pearson_Pval_CN, Pearson_Corr_CN)
-gdsc_Pear_n <- nrow(filter(signif_lin_g2p_dgl, Dataset == "GDSC"))
+gdsc_ge <- select(subset(filter(dgl_signif_pearson_g2p, Dataset == "GDSC"), Pearson_Pval_GE < 0.05), Drug_Gene_Lin, Pearson_Pval_GE, Pearson_Corr_GE)
+gdsc_cn <- select(subset(filter(dgl_signif_pearson_g2p, Dataset == "GDSC"), Pearson_Pval_CN < 0.05), Drug_Gene_Lin, Pearson_Pval_CN, Pearson_Corr_CN)
+gdsc_Pear_n <- nrow(filter(dgl_signif_pearson_g2p, Dataset == "GDSC"))
 gdsc_dgl_summ <- merge(gdsc_mut, merge(gdsc_ge, gdsc_cn, by = "Drug_Gene_Lin", all = TRUE), all = TRUE)
@@
 
-dgl_summ <- merge(merge(ccle_dgl_summ, ctrp_dgl_summ, by = c("Drug", "Gene", "Lineage"), all = TRUE), gdsc_dgl_summ, by = c("Drug", "Gene", "Lineage"), all = TRUE)
-```
+g2p_dgl_summ <- merge(merge(ccle_dgl_summ, ctrp_dgl_summ, by = c("Drug", "Gene", "Lineage"), all = TRUE), gdsc_dgl_summ, by = c("Drug", "Gene", "Lineage"), all = TRUE)
+```
+
+### GE/CN: Grid
 
@@
 signif_all_lin$Drug_Gene_Lin <- paste0(signif_all_lin$Drug_Gene, "_", signif_all_lin$group_general_lineage_name)
-saveRDS(signif_all_lin, "./data_munging/rds/signif_lin_g2p_grid.rds")
-```
-
-```{r}
-signif_lin_g2p_grid <- readRDS("./data_munging/rds/signif_lin_g2p_grid.rds")
+saveRDS(signif_all_lin, "./data_munging/rds/dgl_signif_pearson_g2p_grid.rds")
+```
+
+```{r}
+dgl_signif_pearson_g2p_grid <- readRDS("./data_munging/rds/dgl_signif_pearson_g2p_grid.rds")
 ```
@@
 ```{r, results='hide', eval=FALSE}
-druggenelin_pearson_ttest_res <- lapply(as.character(unique(signif_lin_g2p_grid$group_general_lineage_name)), PearsonPlotlyByLineage)
-druggenelin_pearson_ttest_res_list <- rbindlist(druggenelin_pearson_ttest_res, use.names = TRUE)
-saveRDS(druggenelin_pearson_ttest_res_list, "./data_munging/rds/druggenelin_pearson_ttest_res_list.rds")
-```
-
-```{r}
-druggenelin_pearson_ttest_res_list <- readRDS("./data_munging/rds/druggenelin_pearson_ttest_res_list.rds")
-
-knitr::kable(druggenelin_pearson_ttest_res_list[order(druggenelin_pearson_ttest_res_list$p_value_GE), c("Dataset", "group_general_lineage_name", "t_statistic_GE", "df_GE", "p_value_GE")], caption = "Gene expression: T-test results for level A G2P drug-gene/gene expression associations across lineages") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-
-knitr::kable(druggenelin_pearson_ttest_res_list[order(druggenelin_pearson_ttest_res_list$p_value_CN), c("Dataset", "group_general_lineage_name", "t_statistic_CN", "df_CN", "p_value_CN")], caption = "Copy number: T-test results for level A G2P drug-gene/gene expression associations across lineages") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-### Mut, GE, and CN
+dgl_pearson_g2p_grid_ttest_res <- lapply(as.character(unique(dgl_signif_pearson_g2p_grid$group_general_lineage_name)), PearsonPlotsByLineage)
+dgl_pearson_g2p_grid_ttest_res_list <- rbindlist(dgl_pearson_g2p_grid_ttest_res, use.names = TRUE)
+saveRDS(dgl_pearson_g2p_grid_ttest_res_list, "./data_munging/rds/dgl_pearson_g2p_grid_ttest_res_list.rds")
+```
+
+```{r}
+dgl_pearson_g2p_grid_ttest_res_list <- readRDS("./data_munging/rds/dgl_pearson_g2p_grid_ttest_res_list.rds")
+
+knitr::kable(dgl_pearson_g2p_grid_ttest_res_list[order(dgl_pearson_g2p_grid_ttest_res_list$p_value_GE), c("Dataset", "group_general_lineage_name", "t_statistic_GE", "df_GE", "p_value_GE")], caption = "Gene expression: T-test results for level A G2P drug-gene/gene expression associations across lineages") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+
+knitr::kable(dgl_pearson_g2p_grid_ttest_res_list[order(dgl_pearson_g2p_grid_ttest_res_list$p_value_CN), c("Dataset", "group_general_lineage_name", "t_statistic_CN", "df_CN", "p_value_CN")], caption = "Copy number: T-test results for level A G2P drug-gene/gene expression associations across lineages") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+## Mut, Ge, and CN
 
@@
 
-Example p-value and Pearson correlation coefficient derivations:
+Example p-value and Pearson correlation coefficient derivations for afatinib and ERBB2 in the CTRP dataset:
 ```{r}
@@
 
-#### By lineage
+### Lineage-grouped
 
@@
 ```{r}
-ttest_summ_res_mut <- g2p_druggenelin_p_ttest_res_list[, c("p_value", "Dataset", "group_general_lineage_name")]
+ttest_summ_res_mut <- dgl_mut_g2p_grid_ttest_res_list[, c("p_value", "Dataset", "group_general_lineage_name")]
 ttest_summ_res_mut$Metric <- "Mutation Status"
@@
 
-ttest_summ_res_ge <- druggenelin_pearson_ttest_res_list[, c("p_value_GE", "Dataset", "group_general_lineage_name")]
+ttest_summ_res_ge <- dgl_pearson_g2p_grid_ttest_res_list[, c("p_value_GE", "Dataset", "group_general_lineage_name")]
 colnames(ttest_summ_res_ge) <- c("p_value", "Dataset", "group_general_lineage_name")
@@
 
-ttest_summ_res_cn <- druggenelin_pearson_ttest_res_list[, c("p_value_CN", "Dataset", "group_general_lineage_name")]
+ttest_summ_res_cn <- dgl_pearson_g2p_grid_ttest_res_list[, c("p_value_CN", "Dataset", "group_general_lineage_name")]
 colnames(ttest_summ_res_cn) <- c("p_value", "Dataset", "group_general_lineage_name")
@@
 
-ttest_mut_summ_plot <- ggplot(data = g2p_druggenelin_p_ttest_res_list, aes(x = p_value)) +
+ttest_mut_summ_plot <- ggplot(data = dgl_mut_g2p_grid_ttest_res_list, aes(x = p_value)) +
   geom_histogram(aes(fill = Dataset, color = Dataset), position = "stack", bins = 40, binwidth = 0.025, boundary = 0, closed = "left") +
@@
 
-ttest_ge_summ_plot <- ggplot(data = druggenelin_pearson_ttest_res_list, aes(x = p_value_GE)) +
+ttest_ge_summ_plot <- ggplot(data = dgl_pearson_g2p_grid_ttest_res_list, aes(x = p_value_GE)) +
   geom_histogram(aes(fill = Dataset, color = Dataset), position = "stack", bins = 40, binwidth = 0.025, boundary = 0, closed = "left") +
@@
 
-ttest_cn_summ_plot <- ggplot(data = druggenelin_pearson_ttest_res_list, aes(x = p_value_CN)) +
+ttest_cn_summ_plot <- ggplot(data = dgl_pearson_g2p_grid_ttest_res_list, aes(x = p_value_CN)) +
   geom_histogram(aes(fill = Dataset, color = Dataset), position = "stack", bins = 40, binwidth = 0.025, boundary = 0, closed = "left") +
@@
 ```{r fig.height=20, fig.width=12}
-all_druggenelin_mut <- g2p_druggenelin_all_summ
-all_druggenelin_mut$Sign <- "None"
-all_druggenelin_mut$Measure <- "Mutation Status"
-colnames(all_druggenelin_mut)[colnames(all_druggenelin_mut) == "p"] <- "Statistic"
-
-all_druggenelin_ge <- select(signif_lin_g2p_grid, Drug_Gene, group_general_lineage_name, n, Pearson_GE_Abs, InG2P, Dataset, Pearson_GE_Sign)
-all_druggenelin_ge$Measure <- "Gene Expression"
-colnames(all_druggenelin_ge)[colnames(all_druggenelin_ge) == "Pearson_GE_Abs"] <- "Statistic"
-colnames(all_druggenelin_ge)[colnames(all_druggenelin_ge) == "Pearson_GE_Sign"] <- "Sign"
-
-all_druggenelin_cn <- select(signif_lin_g2p_grid, Drug_Gene, group_general_lineage_name, n, Pearson_CN_Abs, InG2P, Dataset, Pearson_CN_Sign)
-all_druggenelin_cn$Measure <- "Copy Number"
-colnames(all_druggenelin_cn)[colnames(all_druggenelin_cn) == "Pearson_CN_Abs"] <- "Statistic"
-colnames(all_druggenelin_cn)[colnames(all_druggenelin_cn) == "Pearson_CN_Sign"] <- "Sign"
-
-all_druggenelin_summ <- rbind(all_druggenelin_mut, all_druggenelin_ge, all_druggenelin_cn)
-all_druggenelin_summ$Sign <- ifelse(is.na(all_druggenelin_summ$Sign), "None", all_druggenelin_summ$Sign)
-
-all_druggenelin_summ_plot <- ggplot(data = all_druggenelin_summ, aes(x = InG2P, y = Statistic)) +
+dgl_mut <- dgl_mut_grid_summ
+dgl_mut$Sign <- "None"
+dgl_mut$Measure <- "Mutation Status"
+colnames(dgl_mut)[colnames(dgl_mut) == "p"] <- "Statistic"
+dgl_mut$Drug_Gene_Lin <- NULL
+
+dgl_ge <- select(dgl_signif_pearson_g2p_grid, Drug_Gene, group_general_lineage_name, n, Pearson_GE_Abs, InG2P, Dataset, Pearson_GE_Sign)
+dgl_ge$Measure <- "Gene Expression"
+colnames(dgl_ge)[colnames(dgl_ge) == "Pearson_GE_Abs"] <- "Statistic"
+colnames(dgl_ge)[colnames(dgl_ge) == "Pearson_GE_Sign"] <- "Sign"
+
+dgl_cn <- select(dgl_signif_pearson_g2p_grid, Drug_Gene, group_general_lineage_name, n, Pearson_CN_Abs, InG2P, Dataset, Pearson_CN_Sign)
+dgl_cn$Measure <- "Copy Number"
+colnames(dgl_cn)[colnames(dgl_cn) == "Pearson_CN_Abs"] <- "Statistic"
+colnames(dgl_cn)[colnames(dgl_cn) == "Pearson_CN_Sign"] <- "Sign"
+
+dgl_all <- rbind(dgl_mut, dgl_ge, dgl_cn)
+dgl_all$Sign <- ifelse(is.na(dgl_all$Sign), "None", dgl_all$Sign)
+
+dgl_all_plot <- ggplot(data = dgl_all, aes(x = InG2P, y = Statistic)) +
   facet_grid(group_general_lineage_name ~ Measure * Dataset) +
@@
 
-# ggsave("./plots/manuscript/all_druggenelin_summ_plot.png", all_druggenelin_summ_plot, device = "png", dpi = 450, width = 12, height = 40, units = "in")
-```
-
-```
-plot_cn_box <- ggplot(data = g2p_druggene_pearson) +
-  facet_wrap(~ Dataset) +
-  geom_violin(mapping = aes(color = InG2P, y = Pearson_CN_Abs, x = InG2P), alpha = 0.5) +
-  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_CN_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  coord_flip() +
-  labs(x = "In G2P?") +
-  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-```
-
-## Cell line overlap
+# ggsave("./plots/manuscript/dgl_all_plot.png", dgl_all_plot, device = "png", dpi = 450, width = 12, height = 40, units = "in")
+```
+
+## DO THIS: Cell line overlap
 
@@
 
-# Boxplots
+# BOXPLOTS
 
@@
 
-# CRISPR: Point mutation mapping
+# CRISPR: POINT MUT MAPPING
 
@@
 
-# References
+# REFERENCES
 
@@
 
-# Session information
+# SESSION INFORMATION
 

### 2018-12-13 manuscript.Rmd

@@
 
+# write.table(crispr_data_signif_g2p_lineage, file = "~/Desktop/crispr_data_signif_g2p_lineage_20181213.tsv", quote = FALSE, sep = "\t")
 # ggsave("./plots/manuscript/crispr_data_signif_g2p_lineage_plot.png", crispr_data_signif_g2p_lineage_plot, width = 15, height = 18, units = "in")
@@
 ccle_signif_g2p_grid <- readRDS("./data_munging/rds/ccle_signif_g2p_grid.rds")
-knitr::kable(ccle_signif_g2p_grid[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(ccle_signif_g2p_grid[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 ctrp_signif_g2p_grid <- readRDS("./data_munging/rds/ctrp_signif_g2p_grid.rds")
-knitr::kable(ctrp_signif_g2p_grid[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(ctrp_signif_g2p_grid[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 gdsc_signif_g2p_grid <- readRDS("./data_munging/rds/gdsc_signif_g2p_grid.rds")
-knitr::kable(gdsc_signif_g2p_grid[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+knitr::kable(gdsc_signif_g2p_grid[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
   facet_grid(Dataset ~ Metric) +
-  # scale_y_continuous(breaks = seq(0, 30, by = 5), labels = seq(0, 30, by = 5)) +
+  scale_y_continuous(breaks = seq(0, 10, by = 1), labels = seq(0, 10, by = 1)) +
   geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_text_repel(mapping = aes(y = p_log10, x = corr, label = Drug_Gene, color = Metric), force = 10, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 1) +
+  geom_text_repel(mapping = aes(y = p_log10, x = corr, label = Drug_Gene, color = Metric), force = 50, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 1.5) +
   theme(legend.position = "none", panel.grid.major.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(5.5, 1.5, 5.5, 5.5), "pt"), strip.background.y = element_blank(), strip.text.y = element_blank()) +
@@
   scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
-  theme(legend.position = "none", plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
+  theme(legend.position = "none", plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt"), axis.title.y = element_blank()) +
   labs(x = "Pearson correlation coefficient (r)")
@@
   facet_grid(Dataset ~ Metric) +
-  # scale_y_continuous(breaks = seq(0, 30, by = 5), labels = seq(0, 30, by = 5)) +
+  scale_y_continuous(breaks = seq(0, 16, by = 1), labels = seq(0, 16, by = 1)) +
   geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_text_repel(mapping = aes(y = p_log10, x = corr, label = Drug_Gene, color = Metric), box.padding = 0.75, force = 15, size = 2.5, segment.size = 0.2, segment.colour = "grey50") +
+  geom_text_repel(mapping = aes(y = p_log10, x = corr, label = Drug_Gene, color = Metric), box.padding = 1, nudge_y = 0.75, force = 20, size = 2.5, segment.size = 0.2, segment.colour = "grey50") +
   theme(legend.position = "none", panel.grid.major.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(5.5, 1.5, 5.5, 5.5), "pt"), strip.background.y = element_blank(), strip.text.y = element_blank()) +
@@
   facet_grid(Dataset ~ Metric) +
-  # scale_y_continuous(breaks = seq(0, 30, by = 5), labels = seq(0, 30, by = 5)) +
+  scale_y_continuous(breaks = seq(0, 100, by = 10), labels = seq(0, 100, by = 10)) +
   geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
@@
   scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
-  theme(legend.position = "none", plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
+  theme(legend.position = "none", plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt"), axis.title.y = element_blank()) +
   labs(x = "Pearson correlation coefficient (r)", y = "-log10(p-value)")
@@
 
-ItemsList <- venn(dgl_overlap_test_list, show.plot=TRUE)
+ItemsList <- venn(dgl_overlap_test_list, show.plot = TRUE)
+ItemsList
 ```
@@
 
-g2p_dgl_summ <- merge(merge(ccle_dgl_summ, ctrp_dgl_summ, by = c("Drug", "Gene", "Lineage"), all = TRUE), gdsc_dgl_summ, by = c("Drug", "Gene", "Lineage"), all = TRUE)
+g2p_dgl_sig_summ <- merge(merge(ccle_dgl_summ, ctrp_dgl_summ, by = c("Drug", "Gene", "Lineage"), all = TRUE), gdsc_dgl_summ, by = c("Drug", "Gene", "Lineage"), all = TRUE)
 ```

### 2018-12-17 manuscript.Rmd
added new summ plots and spearman corr plots, renamed files accordingly

@@
 
-# PEARSON CORRELATIONS
+# PEARSON/SPEARMAN CORRELATIONS
 
@@
                               Metric = "Copy Number")
+
+crispr_spearman_res_GE <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>%
+                    summarize(p = cor.test(y = Score, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
+                              corr = cor.test(y = Score, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
+                              Metric = "Gene Expression")
+
+crispr_spearman_res_CN <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>%
+                    summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value,
+                              corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate,
+                              Metric = "Copy Number")
 ```
@@
 g2p_druggene_p_tally <- g2p_filt %>% group_by(Drug_Gene) %>% tally() %>% drop_na()
-ccle_pearson_res <- ccle_data_g2p_grid %>% group_by(Drug_Gene) %>%
+ccle_cor_res <- ccle_data_g2p_grid %>% group_by(Drug_Gene) %>%
                     summarize(Pearson_Corr_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
@@
                               Pearson_Corr_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$estimate,
-                              Pearson_Pval_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$p.value)
-ccle_pearson_res <- merge(g2p_druggene_p_tally, ccle_pearson_res, by = "Drug_Gene", all.y = TRUE)
-ccle_pearson_res$n <- ifelse(is.na(ccle_pearson_res$n), 0, ccle_pearson_res$n)
-ccle_pearson_res$InG2P <- ifelse(ccle_pearson_res$n != 0, "Yes", "No")
-ccle_pearson_res$Dataset <- "CCLE"
-ccle_pearson_ttest_GE <- t.test(ccle_pearson_res$Pearson_Corr_GE ~ ccle_pearson_res$InG2P)
+                              Pearson_Pval_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$p.value,
+                              Spearman_Corr_GE = cor.test(y = AUC, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
+                              Spearman_Pval_GE = cor.test(y = AUC, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
+                              Spearman_Corr_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$estimate,
+                              Spearman_Pval_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$p.value)
+ccle_cor_res <- merge(g2p_druggene_p_tally, ccle_cor_res, by = "Drug_Gene", all.y = TRUE)
+ccle_cor_res$n <- ifelse(is.na(ccle_cor_res$n), 0, ccle_cor_res$n)
+ccle_cor_res$InG2P <- ifelse(ccle_cor_res$n != 0, "Yes", "No")
+ccle_cor_res$Dataset <- "CCLE"
+ccle_pearson_ttest_GE <- t.test(ccle_cor_res$Pearson_Corr_GE ~ ccle_cor_res$InG2P)
 ccle_pearson_ttest_res_GE <- paste0("t(", round(ccle_pearson_ttest_GE$parameter, 0), ") = ", round(ccle_pearson_ttest_GE$statistic, 2), ", p = ", round(ccle_pearson_ttest_GE$p.value, 2))
-ccle_pearson_ttest_CN <- t.test(ccle_pearson_res$Pearson_Corr_CN ~ ccle_pearson_res$InG2P)
+ccle_pearson_ttest_CN <- t.test(ccle_cor_res$Pearson_Corr_CN ~ ccle_cor_res$InG2P)
 ccle_pearson_ttest_res_CN <- paste0("t(", round(ccle_pearson_ttest_CN$parameter, 0), ") = ", round(ccle_pearson_ttest_CN$statistic, 2), ", p = ", round(ccle_pearson_ttest_CN$p.value, 2))
-
-ctrp_pearson_res <- ctrp_data_g2p_grid %>% group_by(Drug_Gene) %>%
+ccle_spearman_ttest_GE <- t.test(ccle_cor_res$Spearman_Corr_GE ~ ccle_cor_res$InG2P)
+ccle_spearman_ttest_res_GE <- paste0("t(", round(ccle_spearman_ttest_GE$parameter, 0), ") = ", round(ccle_spearman_ttest_GE$statistic, 2), ", p = ", round(ccle_spearman_ttest_GE$p.value, 2))
+ccle_spearman_ttest_CN <- t.test(ccle_cor_res$Spearman_Corr_CN ~ ccle_cor_res$InG2P)
+ccle_spearman_ttest_res_CN <- paste0("t(", round(ccle_spearman_ttest_CN$parameter, 0), ") = ", round(ccle_spearman_ttest_CN$statistic, 2), ", p = ", formatC(ccle_spearman_ttest_CN$p.value, 2, format = "f"))
+
+ctrp_cor_res <- ctrp_data_g2p_grid %>% group_by(Drug_Gene) %>%
                     summarize(Pearson_Corr_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
@@
                               Pearson_Corr_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$estimate,
-                              Pearson_Pval_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$p.value)
-ctrp_pearson_res <- merge(g2p_druggene_p_tally, ctrp_pearson_res, by = "Drug_Gene", all.y = TRUE)
-ctrp_pearson_res$n <- ifelse(is.na(ctrp_pearson_res$n), 0, ctrp_pearson_res$n)
-ctrp_pearson_res$InG2P <- ifelse(ctrp_pearson_res$n != 0, "Yes", "No")
-ctrp_pearson_res$Dataset <- "CTRP"
-ctrp_pearson_ttest_GE <- t.test(ctrp_pearson_res$Pearson_Corr_GE ~ ctrp_pearson_res$InG2P)
+                              Pearson_Pval_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$p.value,
+                              Spearman_Corr_GE = cor.test(y = AUC, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
+                              Spearman_Pval_GE = cor.test(y = AUC, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
+                              Spearman_Corr_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$estimate,
+                              Spearman_Pval_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$p.value)
+ctrp_cor_res <- merge(g2p_druggene_p_tally, ctrp_cor_res, by = "Drug_Gene", all.y = TRUE)
+ctrp_cor_res$n <- ifelse(is.na(ctrp_cor_res$n), 0, ctrp_cor_res$n)
+ctrp_cor_res$InG2P <- ifelse(ctrp_cor_res$n != 0, "Yes", "No")
+ctrp_cor_res$Dataset <- "CTRP"
+ctrp_pearson_ttest_GE <- t.test(ctrp_cor_res$Pearson_Corr_GE ~ ctrp_cor_res$InG2P)
 ctrp_pearson_ttest_res_GE <- paste0("t(", round(ctrp_pearson_ttest_GE$parameter, 0), ") = ", round(ctrp_pearson_ttest_GE$statistic, 2), ", p ", ifelse(round(ctrp_pearson_ttest_GE$p.value, 3) == 0, "< 0.001", paste0("= ", round(ctrp_pearson_ttest_GE$p.value, 3))))
-ctrp_pearson_ttest_CN <- t.test(ctrp_pearson_res$Pearson_Corr_CN ~ ctrp_pearson_res$InG2P)
+ctrp_pearson_ttest_CN <- t.test(ctrp_cor_res$Pearson_Corr_CN ~ ctrp_cor_res$InG2P)
 ctrp_pearson_ttest_res_CN <- paste0("t(", round(ctrp_pearson_ttest_CN$parameter, 0), ") = ", round(ctrp_pearson_ttest_CN$statistic, 2), ", p = ", round(ctrp_pearson_ttest_CN$p.value, 3))
-
-gdsc_pearson_res <- gdsc_data_g2p_grid %>% group_by(Drug_Gene) %>%
+ctrp_spearman_ttest_GE <- t.test(ctrp_cor_res$Spearman_Corr_GE ~ ctrp_cor_res$InG2P)
+ctrp_spearman_ttest_res_GE <- paste0("t(", round(ctrp_spearman_ttest_GE$parameter, 0), ") = ", round(ctrp_spearman_ttest_GE$statistic, 2), ", p = ", round(ctrp_spearman_ttest_GE$p.value, 2))
+ctrp_spearman_ttest_CN <- t.test(ctrp_cor_res$Spearman_Corr_CN ~ ctrp_cor_res$InG2P)
+ctrp_spearman_ttest_res_CN <- paste0("t(", round(ctrp_spearman_ttest_CN$parameter, 0), ") = ", round(ctrp_spearman_ttest_CN$statistic, 2), ", p = ", round(ctrp_spearman_ttest_CN$p.value, 2))
+
+gdsc_cor_res <- gdsc_data_g2p_grid %>% group_by(Drug_Gene) %>%
                     summarize(Pearson_Corr_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
@@
                               Pearson_Corr_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$estimate,
-                              Pearson_Pval_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$p.value)
-gdsc_pearson_res <- merge(g2p_druggene_p_tally, gdsc_pearson_res, by = "Drug_Gene", all.y = TRUE)
-gdsc_pearson_res$n <- ifelse(is.na(gdsc_pearson_res$n), 0, gdsc_pearson_res$n)
-gdsc_pearson_res$InG2P <- ifelse(gdsc_pearson_res$n != 0, "Yes", "No")
-gdsc_pearson_res$Dataset <- "GDSC"
-gdsc_pearson_ttest_GE <- t.test(gdsc_pearson_res$Pearson_Corr_GE ~ gdsc_pearson_res$InG2P)
+                              Pearson_Pval_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$p.value,
+                              Spearman_Corr_GE = cor.test(y = AUC, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
+                              Spearman_Pval_GE = cor.test(y = AUC, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
+                              Spearman_Corr_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$estimate,
+                              Spearman_Pval_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$p.value)
+gdsc_cor_res <- merge(g2p_druggene_p_tally, gdsc_cor_res, by = "Drug_Gene", all.y = TRUE)
+gdsc_cor_res$n <- ifelse(is.na(gdsc_cor_res$n), 0, gdsc_cor_res$n)
+gdsc_cor_res$InG2P <- ifelse(gdsc_cor_res$n != 0, "Yes", "No")
+gdsc_cor_res$Dataset <- "GDSC"
+gdsc_pearson_ttest_GE <- t.test(gdsc_cor_res$Pearson_Corr_GE ~ gdsc_cor_res$InG2P)
 gdsc_pearson_ttest_res_GE <- paste0("t(", round(gdsc_pearson_ttest_GE$parameter, 0), ") = ", round(gdsc_pearson_ttest_GE$statistic, 2), ", p = ", round(gdsc_pearson_ttest_GE$p.value, 3))
-gdsc_pearson_ttest_CN <- t.test(gdsc_pearson_res$Pearson_Corr_CN ~ gdsc_pearson_res$InG2P)
+gdsc_pearson_ttest_CN <- t.test(gdsc_cor_res$Pearson_Corr_CN ~ gdsc_cor_res$InG2P)
 gdsc_pearson_ttest_res_CN <- paste0("t(", round(gdsc_pearson_ttest_CN$parameter, 0), ") = ", round(gdsc_pearson_ttest_CN$statistic, 2), ", p = ", round(gdsc_pearson_ttest_CN$p.value, 3))
+gdsc_spearman_ttest_GE <- t.test(gdsc_cor_res$Spearman_Corr_GE ~ gdsc_cor_res$InG2P)
+gdsc_spearman_ttest_res_GE <- paste0("t(", round(gdsc_spearman_ttest_GE$parameter, 0), ") = ", round(gdsc_spearman_ttest_GE$statistic, 2), ", p = ", round(gdsc_spearman_ttest_GE$p.value, 2))
+gdsc_spearman_ttest_CN <- t.test(gdsc_cor_res$Spearman_Corr_CN ~ gdsc_cor_res$InG2P)
+gdsc_spearman_ttest_res_CN <- paste0("t(", round(gdsc_spearman_ttest_CN$parameter, 0), ") = ", round(gdsc_spearman_ttest_CN$statistic, 2), ", p = ", round(gdsc_spearman_ttest_CN$p.value, 2))
+
+g2p_cor <- rbind(ccle_cor_res, ctrp_cor_res, gdsc_cor_res)
+g2p_cor$Pearson_GE_Abs <- abs(g2p_cor$Pearson_Corr_GE)
+g2p_cor$Pearson_GE_Sign <- ifelse(sign(g2p_cor$Pearson_Corr_GE) == 1, "+", ifelse(sign(g2p_cor$Pearson_Corr_GE) == -1, "-", "0"))
+g2p_cor$Pearson_CN_Abs <- abs(g2p_cor$Pearson_Corr_CN)
+g2p_cor$Pearson_CN_Sign <- ifelse(sign(g2p_cor$Pearson_Corr_CN) == 1, "+", ifelse(sign(g2p_cor$Pearson_Corr_CN) == -1, "-", "0"))
+g2p_cor$Spearman_GE_Abs <- abs(g2p_cor$Spearman_Corr_GE)
+g2p_cor$Spearman_GE_Sign <- ifelse(sign(g2p_cor$Spearman_Corr_GE) == 1, "+", ifelse(sign(g2p_cor$Spearman_Corr_GE) == -1, "-", "0"))
+g2p_cor$Spearman_CN_Abs <- abs(g2p_cor$Spearman_Corr_CN)
+g2p_cor$Spearman_CN_Sign <- ifelse(sign(g2p_cor$Spearman_Corr_CN) == 1, "+", ifelse(sign(g2p_cor$Spearman_Corr_CN) == -1, "-", "0"))
+
+g2p_cor_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"),
+                               Pearson_Test_Results_GE = c(ccle_pearson_ttest_res_GE, ctrp_pearson_ttest_res_GE, gdsc_pearson_ttest_res_GE),
+                               Pearson_Test_Results_CN = c(ccle_pearson_ttest_res_CN, ctrp_pearson_ttest_res_CN, gdsc_pearson_ttest_res_CN),
+                               Spearman_Test_Results_GE = c(ccle_spearman_ttest_res_GE, ctrp_spearman_ttest_res_GE, gdsc_spearman_ttest_res_GE),
+                               Spearman_Test_Results_CN = c(ccle_spearman_ttest_res_CN, ctrp_spearman_ttest_res_CN, gdsc_spearman_ttest_res_CN))
 ```
@@
 ```{r fig.height=4, fig.width=8}
-g2p_druggene_p_summ <- merge(g2p_druggene_p_tally, ccle_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all.x = TRUE)
-g2p_druggene_p_summ <- merge(g2p_druggene_p_summ, ctrp_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all.x = TRUE, suffixes = c("_CCLE", "_CTRP"))
-g2p_druggene_p_summ <- merge(g2p_druggene_p_summ, gdsc_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all.x = TRUE)
-colnames(g2p_druggene_p_summ)[colnames(g2p_druggene_p_summ) == "p_CCLE"] <- "CCLE"
-colnames(g2p_druggene_p_summ)[colnames(g2p_druggene_p_summ) == "p_CTRP"] <- "CTRP"
-colnames(g2p_druggene_p_summ)[colnames(g2p_druggene_p_summ) == "p"] <- "GDSC"
-
-g2p_druggene_p_summ_melt <- melt(g2p_druggene_p_summ, id.vars = c("Drug_Gene", "n"), measure.vars = c("CCLE", "CTRP", "GDSC"), variable.name = "Dataset", value.name = "p")
-
-g2p_druggene_p_summ_plot <- ggplot(data = g2p_druggene_p_summ_melt, aes(x = p, y = n, shape = Dataset, color = Dataset)) +
+g2p_mut_summ <- merge(g2p_druggene_p_tally, ccle_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all.x = TRUE)
+g2p_mut_summ <- merge(g2p_mut_summ, ctrp_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all.x = TRUE, suffixes = c("_CCLE", "_CTRP"))
+g2p_mut_summ <- merge(g2p_mut_summ, gdsc_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all.x = TRUE)
+colnames(g2p_mut_summ)[colnames(g2p_mut_summ) == "p_CCLE"] <- "CCLE"
+colnames(g2p_mut_summ)[colnames(g2p_mut_summ) == "p_CTRP"] <- "CTRP"
+colnames(g2p_mut_summ)[colnames(g2p_mut_summ) == "p"] <- "GDSC"
+
+g2p_mut_summ_melt <- melt(g2p_mut_summ, id.vars = c("Drug_Gene", "n"), measure.vars = c("CCLE", "CTRP", "GDSC"), variable.name = "Dataset", value.name = "p")
+
+g2p_mut_summ_plot <- ggplot(data = g2p_mut_summ_melt, aes(x = p, y = n, shape = Dataset, color = Dataset)) +
   geom_point(size = 2) +
@@
   labs(x = "Gene-drug association p-value by mutation status", y = "Number of level A G2P associations")
-g2p_druggene_p_summ_plot
-# ggsave("./plots/manuscript/g2p_druggene_p_summ_plot.png", g2p_druggene_p_summ_plot, device = "png", dpi = 450, width = 8, height = 4, units = "in")
+g2p_mut_summ_plot
+# ggsave("./plots/manuscript/g2p_mut_summ_plot.png", g2p_mut_summ_plot, device = "png", dpi = 450, width = 8, height = 4, units = "in")
 ```
@@
 ```{r}
-ccle_druggene_summ <- merge(g2p_druggene_p_tally, ccle_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
-ccle_druggene_summ$n <- ifelse(is.na(ccle_druggene_summ$n), 0, ccle_druggene_summ$n)
-ccle_druggene_summ$InG2P <- ifelse(ccle_druggene_summ$n != 0, "Yes", "No")
-ccle_druggene_summ$Dataset <- "CCLE"
-ccle_p_ttest <- t.test(ccle_druggene_summ$p ~ ccle_druggene_summ$InG2P)
+ccle_mut_summ <- merge(g2p_druggene_p_tally, ccle_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
+ccle_mut_summ$n <- ifelse(is.na(ccle_mut_summ$n), 0, ccle_mut_summ$n)
+ccle_mut_summ$InG2P <- ifelse(ccle_mut_summ$n != 0, "Yes", "No")
+ccle_mut_summ$Dataset <- "CCLE"
+ccle_p_ttest <- t.test(ccle_mut_summ$p ~ ccle_mut_summ$InG2P)
 ccle_p_ttest_res <- paste0("t(", round(ccle_p_ttest$parameter, 0), ") = ", round(ccle_p_ttest$statistic, 2), ", p = ", round(ccle_p_ttest$p.value, 2))
 
-ctrp_druggene_summ <- merge(g2p_druggene_p_tally, ctrp_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
-ctrp_druggene_summ$n <- ifelse(is.na(ctrp_druggene_summ$n), 0, ctrp_druggene_summ$n)
-ctrp_druggene_summ$InG2P <- ifelse(ctrp_druggene_summ$n != 0, "Yes", "No")
-ctrp_druggene_summ$Dataset <- "CTRP"
-ctrp_p_ttest <- t.test(ctrp_druggene_summ$p ~ ctrp_druggene_summ$InG2P)
+ctrp_mut_summ <- merge(g2p_druggene_p_tally, ctrp_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
+ctrp_mut_summ$n <- ifelse(is.na(ctrp_mut_summ$n), 0, ctrp_mut_summ$n)
+ctrp_mut_summ$InG2P <- ifelse(ctrp_mut_summ$n != 0, "Yes", "No")
+ctrp_mut_summ$Dataset <- "CTRP"
+ctrp_p_ttest <- t.test(ctrp_mut_summ$p ~ ctrp_mut_summ$InG2P)
 ctrp_p_ttest_res <- paste0("t(", round(ctrp_p_ttest$parameter, 0), ") = ", round(ctrp_p_ttest$statistic, 2), ", p = ", formatC(ctrp_p_ttest$p.value, digits = 2, format = "f"))
 
-gdsc_druggene_summ <- merge(g2p_druggene_p_tally, gdsc_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
-gdsc_druggene_summ$n <- ifelse(is.na(gdsc_druggene_summ$n), 0, gdsc_druggene_summ$n)
-gdsc_druggene_summ$InG2P <- ifelse(gdsc_druggene_summ$n != 0, "Yes", "No")
-gdsc_druggene_summ$Dataset <- "GDSC"
-gdsc_p_ttest <- t.test(gdsc_druggene_summ$p ~ gdsc_druggene_summ$InG2P)
+gdsc_mut_summ <- merge(g2p_druggene_p_tally, gdsc_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
+gdsc_mut_summ$n <- ifelse(is.na(gdsc_mut_summ$n), 0, gdsc_mut_summ$n)
+gdsc_mut_summ$InG2P <- ifelse(gdsc_mut_summ$n != 0, "Yes", "No")
+gdsc_mut_summ$Dataset <- "GDSC"
+gdsc_p_ttest <- t.test(gdsc_mut_summ$p ~ gdsc_mut_summ$InG2P)
 gdsc_p_ttest_res <- paste0("t(", round(gdsc_p_ttest$parameter, 0), ") = ", round(gdsc_p_ttest$statistic, 2), ", p = ", formatC(gdsc_p_ttest$p.value, digits = 2, format = "f"))
 
-g2p_druggene_all_summ <- rbind(ccle_druggene_summ, ctrp_druggene_summ, gdsc_druggene_summ)
-g2p_druggene_all_summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"), Test_Results_p = c(ccle_p_ttest_res, ctrp_p_ttest_res, gdsc_p_ttest_res))
-g2p_druggene_all_summ$Drug_Gene_Ordered <- factor(g2p_druggene_all_summ$Drug_Gene, levels = as.character(unique(g2p_druggene_all_summ$Drug_Gene)), labels = sapply(strsplit(x = as.character(unique(g2p_druggene_all_summ$Drug_Gene)), split = "_"), function(x) paste0(x[1], "\n", x[2])))
+g2p_mut_all_summ <- rbind(ccle_mut_summ, ctrp_mut_summ, gdsc_mut_summ)
+g2p_mut_all_summ$p_log10 <- -log10(g2p_mut_all_summ$p)
+g2p_mut_all_summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"), Test_Results_p = c(ccle_p_ttest_res, ctrp_p_ttest_res, gdsc_p_ttest_res))
+g2p_mut_all_summ$Drug_Gene_Ordered <- factor(g2p_mut_all_summ$Drug_Gene, levels = as.character(unique(g2p_mut_all_summ$Drug_Gene)), labels = sapply(strsplit(x = as.character(unique(g2p_mut_all_summ$Drug_Gene)), split = "_"), function(x) paste0(x[1], "\n", x[2])))
 ```
@@
 ```{r fig.height=5, fig.width=12}
-plot_p_point <- ggplot(data = g2p_druggene_all_summ, aes(x = p, y = n, label = Drug_Gene)) +
+plot_p_point <- ggplot(data = g2p_mut_all_summ, aes(x = p, y = n, label = Drug_Gene)) +
   facet_wrap(~ Dataset, scales = "free_x") +
@@
 
-plot_p_box <- ggplot(data = g2p_druggene_all_summ) +
+plot_p_box <- ggplot(data = g2p_mut_all_summ) +
   facet_wrap(~ Dataset, scales = "free_x") +
@@
 plot_p_box$widths <- as.list(p_maxWidth)
-g2p_druggene_mut_plot <- cowplot::plot_grid(plot_p_box,
+g2p_mut_plot <- cowplot::plot_grid(plot_p_box,
                    plot_p_point,
@@
                    rel_heights = c(1, 4))
-g2p_druggene_mut_plot
-
-# ggsave("./plots/manuscript/g2p_druggene_mut_plot.png", g2p_druggene_mut_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
-```
-
-```{r, eval=FALSE}
-plot_p_point <- ggplot(data = g2p_druggene_all_summ) +
+g2p_mut_plot
+
+# ggsave("./plots/manuscript/g2p_mut_plot.png", g2p_mut_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
+```
+
+```{r, eval=FALSE}
+plot_p_point <- ggplot(data = g2p_mut_all_summ) +
   facet_wrap(~ Dataset, scales = "free_x") +
@@
 
-saveWidgetFix(widget = plot, file = "./plots/manuscript/g2p_druggene_mut_plot.html")
+saveWidgetFix(widget = plot, file = "./plots/manuscript/g2p_mut_plot.html")
 ```
@@
 
-```{r}
-g2p_druggene_pearson <- rbind(ccle_pearson_res, ctrp_pearson_res, gdsc_pearson_res)
-g2p_druggene_pearson$Pearson_GE_Abs <- abs(g2p_druggene_pearson$Pearson_Corr_GE)
-g2p_druggene_pearson$Pearson_GE_Sign <- ifelse(sign(g2p_druggene_pearson$Pearson_Corr_GE) == 1, "+",
-                                           ifelse(sign(g2p_druggene_pearson$Pearson_Corr_GE) == -1, "-", "0"))
-g2p_druggene_pearson$Pearson_CN_Abs <- abs(g2p_druggene_pearson$Pearson_Corr_CN)
-g2p_druggene_pearson$Pearson_CN_Sign <- ifelse(sign(g2p_druggene_pearson$Pearson_Corr_CN) == 1, "+",
-                                           ifelse(sign(g2p_druggene_pearson$Pearson_Corr_CN) == -1, "-", "0"))
-g2p_druggene_pearson_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"),
-                                        Test_Results_GE = c(ccle_pearson_ttest_res_GE, ctrp_pearson_ttest_res_GE, gdsc_pearson_ttest_res_GE),
-                                        Test_Results_CN = c(ccle_pearson_ttest_res_CN, ctrp_pearson_ttest_res_CN, gdsc_pearson_ttest_res_CN))
-```
+#### Pearson
 
 ```{r fig.height=5, fig.width=12}
-plot_ge_point <- ggplot(data = g2p_druggene_pearson, aes(x = Pearson_GE_Abs, y = n, label = Drug_Gene)) +
+plot_ge_pearson_point <- ggplot(data = g2p_cor, aes(x = Pearson_GE_Abs, y = n, label = Drug_Gene)) +
   facet_wrap(~ Dataset) +
@@
   scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
-  geom_text_repel(data = subset(g2p_druggene_pearson, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
-  geom_text(data = g2p_druggene_pearson_text, mapping = aes(x = 0.325, y = 115, label = Test_Results_GE)) +
-  labs(x = "Pearson correlation coefficient between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +
+  geom_text_repel(data = subset(g2p_cor, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
+  geom_text(data = g2p_cor_text, mapping = aes(x = 0.325, y = 115, label = Pearson_Test_Results_GE)) +
+  labs(x = "Pearson correlation coefficient (r) between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +
   theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
@@
 
-plot_ge_box <- ggplot(data = g2p_druggene_pearson) +
+plot_ge_pearson_box <- ggplot(data = g2p_cor) +
   facet_wrap(~ Dataset) +
@@
   theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-plot_ge_point <- ggplot_gtable(ggplot_build(plot_ge_point))
-plot_ge_box <- ggplot_gtable(ggplot_build(plot_ge_box))
-p_maxWidth <-  grid::unit.pmax(plot_ge_point$widths[2:3], plot_ge_box$widths[2:3])
-plot_ge_point$widths[2:3] <- p_maxWidth
-plot_ge_box$widths[2:3] <- p_maxWidth
-
-g2p_druggene_ge_plot <- cowplot::plot_grid(plot_ge_box, plot_ge_point, nrow = 2, rel_heights = c(1, 4))
-g2p_druggene_ge_plot
-
-# ggsave("./plots/manuscript/g2p_druggene_ge_plot.png", g2p_druggene_ge_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
-```
-
-```{r, eval=FALSE}
-plot_ge_point <- ggplot(data = g2p_druggene_pearson) +
+
+plot_ge_pearson_point <- ggplot_gtable(ggplot_build(plot_ge_pearson_point))
+plot_ge_pearson_box <- ggplot_gtable(ggplot_build(plot_ge_pearson_box))
+p_maxWidth <-  grid::unit.pmax(plot_ge_pearson_point$widths[2:3], plot_ge_pearson_box$widths[2:3])
+plot_ge_pearson_point$widths[2:3] <- p_maxWidth
+plot_ge_pearson_box$widths[2:3] <- p_maxWidth
+
+g2p_ge_pearson_plot <- cowplot::plot_grid(plot_ge_pearson_box, plot_ge_pearson_point, nrow = 2, rel_heights = c(1, 4))
+g2p_ge_pearson_plot
+
+# ggsave("./plots/manuscript/g2p_ge_pearson_plot.png", g2p_ge_pearson_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
+```
+
+```{r, eval=FALSE}
+plot_ge_point <- ggplot(data = g2p_cor) +
   facet_wrap(~ Dataset) +
@@
   scale_x_continuous(breaks = pretty_breaks()) +
-  geom_text(data = g2p_druggene_pearson_text, mapping = aes(x = 0.3, y = 115, label = Test_Results_GE)) +
-  labs(x = "Pearson correlation coefficient between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +
+  geom_text(data = g2p_cor_text, mapping = aes(x = 0.3, y = 115, label = Pearson_Test_Results_GE)) +
+  labs(x = "Pearson correlation coefficient (r) between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +
   theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
@@
 
-plot_ge_box <- ggplot(data = g2p_druggene_pearson) +
+plot_ge_box <- ggplot(data = g2p_cor) +
   facet_wrap(~ Dataset) +
@@
 
-plot <- subplot(plot_ge_box, plot_ge_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and gene expression"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
-
-saveWidgetFix(widget = plot, file = "./plots/manuscript/g2p_druggene_ge_plot.html")
+ge_pearson_plot <- subplot(plot_ge_box, plot_ge_point, nrows = 2, heights = c(0.2, 0.8), titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and gene expression"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
+
+saveWidgetFix(widget = ge_pearson_plot, file = "./plots/manuscript/g2p_ge_pearson_plot.html")
+```
+
+#### Spearman
+
+```{r fig.height=5, fig.width=12}
+plot_ge_spearman_point <- ggplot(data = g2p_cor, aes(x = Spearman_GE_Abs, y = n, label = Drug_Gene)) +
+  facet_wrap(~ Dataset) +
+  geom_point(mapping = aes(fill = InG2P, color = InG2P, shape = Spearman_GE_Sign), alpha = 0.5, size = 1.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
+  scale_x_continuous(breaks = seq(0, 0.65, by = 0.1), labels = seq(0, 0.65, by = 0.1)) +
+  coord_cartesian(xlim = c(0, 0.6)) +
+  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
+  geom_text_repel(data = subset(g2p_cor, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
+  geom_text(data = g2p_cor_text, mapping = aes(x = 0.3, y = 115, label = Spearman_Test_Results_GE)) +
+  labs(x = "Spearman correlation coefficient (r_s) between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +
+  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
+  guides(color = FALSE, fill = FALSE, shape = FALSE)
+
+plot_ge_spearman_box <- ggplot(data = g2p_cor) +
+  facet_wrap(~ Dataset) +
+  geom_violin(mapping = aes(color = InG2P, fill = InG2P, y = Spearman_GE_Abs, x = InG2P), alpha = 0.35) +
+  geom_boxplot(mapping = aes(color = InG2P, y = Spearman_GE_Abs, x = InG2P), width = 0.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_y_continuous(breaks = seq(0, 0.65, by = 0.1), labels = seq(0, 0.65, by = 0.1)) +
+  coord_flip(ylim = c(0, 0.6)) +
+  labs(x = "In G2P?") +
+  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
+
+plot_ge_spearman_point <- ggplot_gtable(ggplot_build(plot_ge_spearman_point))
+plot_ge_spearman_box <- ggplot_gtable(ggplot_build(plot_ge_spearman_box))
+p_maxWidth <-  grid::unit.pmax(plot_ge_spearman_point$widths[2:3], plot_ge_spearman_box$widths[2:3])
+plot_ge_spearman_point$widths[2:3] <- p_maxWidth
+plot_ge_spearman_box$widths[2:3] <- p_maxWidth
+
+g2p_ge_spearman_plot <- cowplot::plot_grid(plot_ge_spearman_box, plot_ge_spearman_point, nrow = 2, rel_heights = c(1, 4))
+g2p_ge_spearman_plot
+
+# ggsave("./plots/manuscript/g2p_ge_spearman_plot.png", g2p_ge_spearman_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
+```
+
+```{r, eval=FALSE}
+plot_ge_point <- ggplot(data = g2p_cor) +
+  facet_wrap(~ Dataset) +
+  geom_point(mapping = aes(label = Drug_Gene, fill = InG2P, color = InG2P, shape = Spearman_GE_Sign, x = Spearman_GE_Abs, y = n, size = Spearman_Pval_GE), alpha = 0.5, size = 1.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
+  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
+  scale_x_continuous(breaks = pretty_breaks()) +
+  geom_text(data = g2p_cor_text, mapping = aes(x = 0.3, y = 115, label = Spearman_Test_Results_GE)) +
+  labs(x = "Spearman correlation coefficient (r_s) between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +
+  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
+  guides(color = FALSE, fill = FALSE) +
+  labs(shape = NULL)
+
+plot_ge_box <- ggplot(data = g2p_cor) +
+  facet_wrap(~ Dataset) +
+  geom_violin(mapping = aes(color = InG2P, y = Spearman_GE_Abs, x = InG2P), alpha = 0.5) +
+  geom_boxplot(mapping = aes(color = InG2P, y = Spearman_GE_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  coord_flip() +
+  labs(x = "In G2P?") +
+  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
+
+ge_spearman_plot <- subplot(plot_ge_box, plot_ge_point, nrows = 2, heights = c(0.2, 0.8), titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Spearman correlation coefficient between drug-gene AUC and gene expression"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
+
+saveWidgetFix(widget = ge_spearman_plot, file = "./plots/manuscript/g2p_ge_spearman_plot.html")
 ```
@@
 
-```{r fig.height=5.5, fig.width=12}
-plot_cn_point <- ggplot(data = g2p_druggene_pearson, aes(x = Pearson_CN_Abs, y = n, label = Drug_Gene)) +
+#### Pearson
+
+```{r fig.height=5, fig.width=12}
+plot_cn_pearson_point <- ggplot(data = g2p_cor, aes(x = Pearson_CN_Abs, y = n, label = Drug_Gene)) +
   facet_wrap(~ Dataset) +
@@
   scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
-  scale_x_continuous(breaks = seq(0, 0.5, by = 0.1), labels = seq(0, 0.5, by = 0.1)) +
+  scale_x_continuous(breaks = seq(0, 0.65, by = 0.1), labels = seq(0, 0.65, by = 0.1)) +
   coord_cartesian(xlim = c(0, 0.5)) +
   scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
-  geom_text_repel(data = subset(g2p_druggene_pearson, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
-  geom_text(data = g2p_druggene_pearson_text, mapping = aes(x = 0.25, y = 115, label = Test_Results_CN)) +
-  labs(x = "Pearson correlation coefficient between drug-gene AUC and copy number", y = "Number of level A G2P associations", shape = "Direction of correlation:", color = "Level A G2P association:") +
+  geom_text_repel(data = subset(g2p_cor, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
+  geom_text(data = g2p_cor_text, mapping = aes(x = 0.25, y = 115, label = Pearson_Test_Results_CN)) +
+  labs(x = "Pearson correlation coefficient (r) between drug-gene AUC and copy number", y = "Number of level A G2P associations") +
   theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
-  guides(color = guide_legend(override.aes = list(size = 4, shape = 15)), shape = guide_legend(override.aes = list(size = 3)), fill = FALSE)
-
-plot_cn_box <- ggplot(data = g2p_druggene_pearson) +
+  guides(color = FALSE, fill = FALSE, shape = FALSE)
+
+plot_cn_pearson_box <- ggplot(data = g2p_cor) +
   facet_wrap(~ Dataset) +
@@
   scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_y_continuous(breaks = seq(0, 0.5, by = 0.1), labels = seq(0, 0.5, by = 0.1)) +
+  scale_y_continuous(breaks = seq(0, 0.65, by = 0.1), labels = seq(0, 0.65, by = 0.1)) +
   coord_flip(ylim = c(0, 0.5)) +
@@
 
-plot_cn_point <- ggplot_gtable(ggplot_build(plot_cn_point))
-plot_cn_box <- ggplot_gtable(ggplot_build(plot_cn_box))
-p_maxWidth <-  grid::unit.pmax(plot_cn_point$widths, plot_cn_box$widths)
-plot_cn_point$widths <- as.list(p_maxWidth)
-plot_cn_box$widths <- as.list(p_maxWidth)
-g2p_druggene_cn_plot <- cowplot::plot_grid(plot_cn_box, plot_cn_point, nrow = 2, rel_heights = c(1, 4))
-g2p_druggene_cn_plot
-
-# ggsave("./plots/manuscript/g2p_druggene_cn_plot.png", g2p_druggene_cn_plot, device = "png", dpi = 450, width = 12, height = 5.5, units = "in")
-```
-
-```{r, eval=FALSE}
-plot_cn_point <- ggplot(data = g2p_druggene_pearson) +
+plot_cn_pearson_point <- ggplot_gtable(ggplot_build(plot_cn_pearson_point))
+plot_cn_pearson_box <- ggplot_gtable(ggplot_build(plot_cn_pearson_box))
+p_maxWidth <-  grid::unit.pmax(plot_cn_pearson_point$widths[2:3], plot_cn_pearson_box$widths[2:3])
+plot_cn_pearson_point$widths[2:3] <- p_maxWidth
+plot_cn_pearson_box$widths[2:3] <- p_maxWidth
+
+g2p_cn_pearson_plot <- cowplot::plot_grid(plot_cn_pearson_box, plot_cn_pearson_point, nrow = 2, rel_heights = c(1, 4))
+g2p_cn_pearson_plot
+
+# ggsave("./plots/manuscript/g2p_cn_pearson_plot.png", g2p_cn_pearson_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
+```
+
+```{r, eval=FALSE}
+plot_cn_point <- ggplot(data = g2p_cor) +
   facet_wrap(~ Dataset) +
-  geom_point(mapping = aes(label = Drug_Gene, fill = InG2P, color = InG2P, shape = Pearson_CN_Sign, x = Pearson_CN_Abs, y = n), alpha = 0.5, size = 1.25) +
+  geom_point(mapping = aes(label = Drug_Gene, fill = InG2P, color = InG2P, shape = Pearson_CN_Sign, x = Pearson_CN_Abs, y = n, size = Pearson_Pval_CN), alpha = 0.5, size = 1.25) +
   scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
@@
   scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
-  scale_y_continuous(breaks = seq(0, 110, by = 10), labels = seq(0, 110, by = 10)) +
+  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
   scale_x_continuous(breaks = pretty_breaks()) +
-  geom_text(data = g2p_druggene_pearson_text, mapping = aes(x = 0.3, y = 110, label = Test_Results_GE)) +
-  labs(x = "Pearson correlation coefficient between drug-gene AUC and copy number", y = "Number of level A G2P associations") +
+  geom_text(data = g2p_cor_text, mapping = aes(x = 0.3, y = 115, label = Pearson_Test_Results_CN)) +
+  labs(x = "Pearson correlation coefficient (r) between drug-gene AUC and copy number", y = "Number of level A G2P associations") +
   theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
-  guides(color = guide_legend(override.aes = list(size = 4, shape = 15)), shape = guide_legend(override.aes = list(size = 3)), fill = FALSE) +
+  guides(color = FALSE, fill = FALSE) +
   labs(shape = NULL)
-plot_cn_box <- ggplot(data = g2p_druggene_pearson) +
+
+plot_cn_box <- ggplot(data = g2p_cor) +
   facet_wrap(~ Dataset) +
@@
   theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-plot <- subplot(plot_cn_box, plot_cn_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and copy number"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
-
-saveWidgetFix(widget = plot, file = "./plots/manuscript/g2p_druggene_cn_plot.html")
-```
-
-## G2P associations
-
-This section contains summary plots for the Wilcoxon tests and Pearson correlations done for only level A G2P drug-gene associations (i.e.
+
+cn_pearson_plot <- subplot(plot_cn_box, plot_cn_point, nrows = 2, heights = c(0.2, 0.8), titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and copy number"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
+
+saveWidgetFix(widget = ge_pearson_plot, file = "./plots/manuscript/g2p_cn_pearson_plot.html")
+```
+
+#### Spearman
+
+```{r fig.height=5, fig.width=12}
+plot_cn_spearman_point <- ggplot(data = g2p_cor, aes(x = Spearman_CN_Abs, y = n, label = Drug_Gene)) +
+  facet_wrap(~ Dataset) +
+  geom_point(mapping = aes(fill = InG2P, color = InG2P, shape = Spearman_CN_Sign), alpha = 0.5, size = 1.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
+  scale_x_continuous(breaks = seq(0, 0.4, by = 0.05), labels = seq(0, 0.4, by = 0.05)) +
+  coord_cartesian(xlim = c(0, 0.35)) +
+  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
+  geom_text_repel(data = subset(g2p_cor, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
+  geom_text(data = g2p_cor_text, mapping = aes(x = 0.175, y = 115, label = Spearman_Test_Results_CN)) +
+  labs(x = "Spearman correlation coefficient (r_s) between drug-gene AUC and copy number", y = "Number of level A G2P associations") +
+  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
+  guides(color = FALSE, fill = FALSE, shape = FALSE)
+
+plot_cn_spearman_box <- ggplot(data = g2p_cor) +
+  facet_wrap(~ Dataset) +
+  geom_violin(mapping = aes(color = InG2P, fill = InG2P, y = Spearman_CN_Abs, x = InG2P), alpha = 0.35) +
+  geom_boxplot(mapping = aes(color = InG2P, y = Spearman_CN_Abs, x = InG2P), width = 0.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_y_continuous(breaks = seq(0, 0.4, by = 0.05), labels = seq(0, 0.4, by = 0.05)) +
+  coord_flip(ylim = c(0, 0.35)) +
+  labs(x = "In G2P?") +
+  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
+
+plot_cn_spearman_point <- ggplot_gtable(ggplot_build(plot_cn_spearman_point))
+plot_cn_spearman_box <- ggplot_gtable(ggplot_build(plot_cn_spearman_box))
+p_maxWidth <-  grid::unit.pmax(plot_cn_spearman_point$widths[2:3], plot_cn_spearman_box$widths[2:3])
+plot_cn_spearman_point$widths[2:3] <- p_maxWidth
+plot_cn_spearman_box$widths[2:3] <- p_maxWidth
+
+g2p_cn_spearman_plot <- cowplot::plot_grid(plot_cn_spearman_box, plot_cn_spearman_point, nrow = 2, rel_heights = c(1, 4))
+g2p_cn_spearman_plot
+
+# ggsave("./plots/manuscript/g2p_cn_spearman_plot.png", g2p_cn_spearman_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
+```
+
+```{r, eval=FALSE}
+plot_cn_point <- ggplot(data = g2p_cor) +
+  facet_wrap(~ Dataset) +
+  geom_point(mapping = aes(label = Drug_Gene, fill = InG2P, color = InG2P, shape = Spearman_CN_Sign, x = Spearman_CN_Abs, y = n, size = Spearman_Pval_CN), alpha = 0.5, size = 1.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
+  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
+  scale_x_continuous(breaks = pretty_breaks()) +
+  geom_text(data = g2p_cor_text, mapping = aes(x = 0.175, y = 115, label = Spearman_Test_Results_CN)) +
+  labs(x = "Spearman correlation coefficient (r_s) between drug-gene AUC and copy number", y = "Number of level A G2P associations") +
+  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
+  guides(color = FALSE, fill = FALSE) +
+  labs(shape = NULL)
+
+plot_cn_box <- ggplot(data = g2p_cor) +
+  facet_wrap(~ Dataset) +
+  geom_violin(mapping = aes(color = InG2P, y = Spearman_CN_Abs, x = InG2P), alpha = 0.5) +
+  geom_boxplot(mapping = aes(color = InG2P, y = Spearman_CN_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  coord_flip() +
+  labs(x = "In G2P?") +
+  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
+
+cn_spearman_plot <- subplot(plot_cn_box, plot_cn_point, nrows = 2, heights = c(0.2, 0.8), titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Spearman correlation coefficient between drug-gene AUC and copy number"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
+
+saveWidgetFix(widget = cn_spearman_plot, file = "./plots/manuscript/g2p_cn_spearman_plot.html")
+```
+
+### Genomic features supplementary plots
+
+This section contains summary plots for the Wilcoxon tests and Pearson/Spearman correlations done for only level A G2P drug-gene associations (i.e.
 not the grid tests) and G2P genes in the case of the CRISPR dataset.
 
-### CRISPR
-
+#### CRISPR
+
+G2P genes with a significant effect on CERES score by mutation status, gene expression, and copy number. Summary plot using Pearson correlation coefficient for GE and CN:
 ```{r fig.height=5, fig.width=12}
@@
 
-crispr_genomic_features_summ_plot <- plot_grid(crispr_summ_res_mut_plot, crispr_summ_res_pearson_plot, align = "h", rel_widths = c(1, 5))
-crispr_genomic_features_summ_plot
-
-# ggsave("./plots/manuscript/crispr_genomic_features_summ_plot.png", crispr_genomic_features_summ_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
-```
-
-### CCLE
-
-G2P drug-gene associations with a significant effect on AUC by mutation status, gene expression, and copy number:
+crispr_genomic_features_pearson_summ_plot <- plot_grid(crispr_summ_res_mut_plot, crispr_summ_res_pearson_plot, align = "h", rel_widths = c(1, 5))
+crispr_genomic_features_pearson_summ_plot
+
+# ggsave("./plots/manuscript/crispr_genomic_features_pearson_summ_plot.png", crispr_genomic_features_pearson_summ_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
+```
+
+Summary plot using Spearman correlation coefficient for GE and CN:
+```{r fig.height=5, fig.width=12}
+subset(crispr_spearman_res_GE, p < 0.05)
+subset(crispr_spearman_res_CN, p < 0.05)
+
+crispr_spearman_res <- rbind(crispr_spearman_res_GE, crispr_spearman_res_CN)
+crispr_spearman_res$Metric <- factor(crispr_spearman_res$Metric, levels = c("Gene Expression", "Copy Number"))
+crispr_spearman_res$p_log10 <- -log10(crispr_spearman_res$p)
+
+crispr_summ_res_spearman_plot <- ggplot(data = subset(crispr_spearman_res, p < 0.05)) +
+  facet_grid(~ Metric, scales = "free_x", space = "free") +
+  scale_y_continuous(breaks = seq(0, 50, by = 5), labels = seq(0, 50, by = 5)) +
+  scale_x_continuous(breaks = seq(-0.6, 0.3, by = 0.1), labels = formatC(seq(-0.6, 0.3, by = 0.1), digits = 2, format = "f")) +
+  coord_cartesian(ylim = c(0, 50)) +
+  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
+  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
+  geom_label_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Hugo_Symbol), force = 10, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
+  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
+  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
+  labs(x = "Spearman's rank correlation coefficient (r_s)")
+
+crispr_genomic_features_spearman_summ_plot <- plot_grid(crispr_summ_res_mut_plot, crispr_summ_res_spearman_plot, align = "h", rel_widths = c(1, 5))
+crispr_genomic_features_spearman_summ_plot
+
+# ggsave("./plots/manuscript/crispr_genomic_features_spearman_summ_plot.png", crispr_genomic_features_spearman_summ_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
+```
+
+#### CCLE
+
+G2P drug-gene associations with a significant effect on AUC by mutation status, gene expression, and copy number. Summary plot using Pearson correlation coefficient for GE and CN:
 ```{r fig.height=4, fig.width=12}
@@
 ccle_res_mut$Dataset <- "CCLE"
-ccle_pearson_res_GE <- select(filter(ccle_pearson_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_GE, Pearson_Pval_GE, Dataset)
+
+ccle_pearson_res_GE <- select(filter(ccle_cor_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_GE, Pearson_Pval_GE, Dataset)
 colnames(ccle_pearson_res_GE) <- c("Drug_Gene", "corr", "p", "Dataset")
@@
 subset(ccle_pearson_res_GE, p < 0.05)
-ccle_pearson_res_CN <- select(filter(ccle_pearson_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_CN, Pearson_Pval_CN, Dataset)
+
+ccle_pearson_res_CN <- select(filter(ccle_cor_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_CN, Pearson_Pval_CN, Dataset)
 colnames(ccle_pearson_res_CN) <- c("Drug_Gene", "corr", "p", "Dataset")
@@
 subset(ccle_pearson_res_CN, p < 0.05)
+
 ccle_pearson_res_filt <- rbind(ccle_pearson_res_GE, ccle_pearson_res_CN)
@@
 
-ccle_genomic_features_summ_plot <- plot_grid(ccle_summ_res_mut_plot, ccle_summ_res_pearson_plot, align = "h", rel_widths = c(1, 5))
-ccle_genomic_features_summ_plot
-
-# ggsave("./plots/manuscript/ccle_genomic_features_summ_plot.png", ccle_genomic_features_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
-```
-
-### CTRP
-
-G2P drug-gene associations with a significant effect on AUC by mutation status, gene expression, and copy number:
-```{r fig.height=6, fig.width=12}
+ccle_genomic_features_pearson_summ_plot <- plot_grid(ccle_summ_res_mut_plot, ccle_summ_res_pearson_plot, align = "h", rel_widths = c(1, 5))
+ccle_genomic_features_pearson_summ_plot
+
+# ggsave("./plots/manuscript/ccle_genomic_features_pearson_summ_plot.png", ccle_genomic_features_pearson_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
+```
+
+Summary plot using Spearman correlation coefficient for GE and CN:
+```{r fig.height=4, fig.width=12}
+ccle_spearman_res_GE <- select(filter(ccle_cor_res, InG2P == "Yes"), Drug_Gene, Spearman_Corr_GE, Spearman_Pval_GE, Dataset)
+colnames(ccle_spearman_res_GE) <- c("Drug_Gene", "corr", "p", "Dataset")
+ccle_spearman_res_GE$Metric <- "Gene Expression"
+subset(ccle_spearman_res_GE, p < 0.05)
+
+ccle_spearman_res_CN <- select(filter(ccle_cor_res, InG2P == "Yes"), Drug_Gene, Spearman_Corr_CN, Spearman_Pval_CN, Dataset)
+colnames(ccle_spearman_res_CN) <- c("Drug_Gene", "corr", "p", "Dataset")
+ccle_spearman_res_CN$Metric <- "Copy Number"
+subset(ccle_spearman_res_CN, p < 0.05)
+
+ccle_spearman_res_filt <- rbind(ccle_spearman_res_GE, ccle_spearman_res_CN)
+ccle_spearman_res_filt$Metric <- factor(ccle_spearman_res_filt$Metric, levels = c("Gene Expression", "Copy Number"))
+ccle_spearman_res_filt$p_log10 <- -log10(ccle_spearman_res_filt$p)
+
+ccle_summ_res_spearman_plot <- ggplot(data = subset(ccle_spearman_res_filt, p < 0.05)) +
+  facet_grid(Dataset ~ Metric) +
+  coord_cartesian(ylim = c(0, 35)) +
+  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
+  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
+  geom_label_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 10, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
+  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
+  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
+  labs(x = "Spearman's rank correlation coefficient (r_s)")
+
+ccle_genomic_features_spearman_summ_plot <- plot_grid(ccle_summ_res_mut_plot, ccle_summ_res_spearman_plot, align = "h", rel_widths = c(1, 5))
+ccle_genomic_features_spearman_summ_plot
+
+# ggsave("./plots/manuscript/ccle_genomic_features_spearman_summ_plot.png", ccle_genomic_features_spearman_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
+```
+
+#### CTRP
+
+G2P drug-gene associations with a significant effect on AUC by mutation status, gene expression, and copy number. Summary plot using Pearson correlation coefficient for GE and CN:
+```{r fig.height=4, fig.width=12}
 ctrp_res_mut <- select(ctrp_signif_g2p, Drug_Gene, p)
@@
 ctrp_res_mut$Dataset <- "CTRP"
-ctrp_pearson_res_GE <- select(filter(ctrp_pearson_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_GE, Pearson_Pval_GE, Dataset)
+
+ctrp_pearson_res_GE <- select(filter(ctrp_cor_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_GE, Pearson_Pval_GE, Dataset)
 colnames(ctrp_pearson_res_GE) <- c("Drug_Gene", "corr", "p", "Dataset")
@@
 subset(ctrp_pearson_res_GE, p < 0.05)
-ctrp_pearson_res_CN <- select(filter(ctrp_pearson_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_CN, Pearson_Pval_CN, Dataset)
+
+ctrp_pearson_res_CN <- select(filter(ctrp_cor_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_CN, Pearson_Pval_CN, Dataset)
 colnames(ctrp_pearson_res_CN) <- c("Drug_Gene", "corr", "p", "Dataset")
@@
 subset(ctrp_pearson_res_CN, p < 0.05)
+
 ctrp_pearson_res_filt <- rbind(ctrp_pearson_res_GE, ctrp_pearson_res_CN)
@@
   facet_grid(Dataset ~ Metric) +
-  scale_y_continuous(breaks = seq(0, 10, by = 1), labels = seq(0, 10, by = 1)) +
+  scale_y_continuous(breaks = seq(0, 35, by = 5), labels = seq(0, 35, by = 5)) +
+  coord_cartesian(ylim = c(0, 35)) +
   geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_text_repel(mapping = aes(y = p_log10, x = corr, label = Drug_Gene, color = Metric), force = 50, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 1.5) +
+  geom_text_repel(mapping = aes(y = p_log10, x = corr, label = Drug_Gene, color = Metric), force = 15, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.9) +
   theme(legend.position = "none", panel.grid.major.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(5.5, 1.5, 5.5, 5.5), "pt"), strip.background.y = element_blank(), strip.text.y = element_blank()) +
@@
   facet_grid(Dataset ~ Metric) +
-  scale_y_continuous(breaks = seq(0, 30, by = 5), labels = seq(0, 30, by = 5)) +
+  coord_cartesian(ylim = c(0, 35)) +
   geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
@@
   scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
-  theme(legend.position = "none", plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt"), axis.title.y = element_blank()) +
+  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
   labs(x = "Pearson correlation coefficient (r)")
 
-ctrp_genomic_features_summ_plot <- plot_grid(ctrp_summ_res_mut_plot, ctrp_summ_res_pearson_plot, align = "h", rel_widths = c(1, 5))
-ctrp_genomic_features_summ_plot
-
-# ggsave("./plots/manuscript/ctrp_genomic_features_summ_plot.png", ctrp_genomic_features_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
-```
-
-### GDSC
-
-G2P drug-gene associations with a significant effect on AUC by mutation status, gene expression, and copy number:
-```{r fig.height=6, fig.width=12}
+ctrp_genomic_features_pearson_summ_plot <- plot_grid(ctrp_summ_res_mut_plot, ctrp_summ_res_pearson_plot, align = "h", rel_widths = c(1, 5))
+ctrp_genomic_features_pearson_summ_plot
+
+# ggsave("./plots/manuscript/ctrp_genomic_features_pearson_summ_plot.png", ctrp_genomic_features_pearson_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
+```
+
+Summary plot using Spearman correlation coefficient for GE and CN:
+```{r fig.height=4, fig.width=12}
+ctrp_spearman_res_GE <- select(filter(ctrp_cor_res, InG2P == "Yes"), Drug_Gene, Spearman_Corr_GE, Spearman_Pval_GE, Dataset)
+colnames(ctrp_spearman_res_GE) <- c("Drug_Gene", "corr", "p", "Dataset")
+ctrp_spearman_res_GE$Metric <- "Gene Expression"
+subset(ctrp_spearman_res_GE, p < 0.05)
+
+ctrp_spearman_res_CN <- select(filter(ctrp_cor_res, InG2P == "Yes"), Drug_Gene, Spearman_Corr_CN, Spearman_Pval_CN, Dataset)
+colnames(ctrp_spearman_res_CN) <- c("Drug_Gene", "corr", "p", "Dataset")
+ctrp_spearman_res_CN$Metric <- "Copy Number"
+subset(ctrp_spearman_res_CN, p < 0.05)
+
+ctrp_spearman_res_filt <- rbind(ctrp_spearman_res_GE, ctrp_spearman_res_CN)
+ctrp_spearman_res_filt$Metric <- factor(ctrp_spearman_res_filt$Metric, levels = c("Gene Expression", "Copy Number"))
+ctrp_spearman_res_filt$p_log10 <- -log10(ctrp_spearman_res_filt$p)
+
+ctrp_summ_res_spearman_plot <- ggplot(data = subset(ctrp_spearman_res_filt, p < 0.05)) +
+  facet_grid(Dataset ~ Metric) +
+  coord_cartesian(ylim = c(0, 35)) +
+  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
+  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
+  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 20, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
+  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
+  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
+  labs(x = "Spearman's rank correlation coefficient (r_s)")
+
+ctrp_genomic_features_spearman_summ_plot <- plot_grid(ctrp_summ_res_mut_plot, ctrp_summ_res_spearman_plot, align = "h", rel_widths = c(1, 5))
+ctrp_genomic_features_spearman_summ_plot
+
+# ggsave("./plots/manuscript/ctrp_genomic_features_spearman_summ_plot.png", ctrp_genomic_features_spearman_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
+```
+
+#### GDSC
+
+G2P drug-gene associations with a significant effect on AUC by mutation status, gene expression, and copy number. Summary plot using Pearson correlation coefficient for GE and CN:
+```{r fig.height=4, fig.width=12}
 gdsc_res_mut <- select(gdsc_signif_g2p, Drug_Gene, p)
@@
 gdsc_res_mut$Dataset <- "GDSC"
-gdsc_pearson_res_GE <- select(filter(gdsc_pearson_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_GE, Pearson_Pval_GE, Dataset)
+
+gdsc_pearson_res_GE <- select(filter(gdsc_cor_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_GE, Pearson_Pval_GE, Dataset)
 colnames(gdsc_pearson_res_GE) <- c("Drug_Gene", "corr", "p", "Dataset")
@@
 subset(gdsc_pearson_res_GE, p < 0.05)
-gdsc_pearson_res_CN <- select(filter(gdsc_pearson_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_CN, Pearson_Pval_CN, Dataset)
+
+gdsc_pearson_res_CN <- select(filter(gdsc_cor_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_CN, Pearson_Pval_CN, Dataset)
 colnames(gdsc_pearson_res_CN) <- c("Drug_Gene", "corr", "p", "Dataset")
@@
 subset(gdsc_pearson_res_CN, p < 0.05)
+
 gdsc_pearson_res_filt <- rbind(gdsc_pearson_res_GE, gdsc_pearson_res_CN)
@@
   geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_text_repel(mapping = aes(y = p_log10, x = corr, label = Drug_Gene, color = Metric), box.padding = 1, nudge_y = 0.75, force = 20, size = 2.5, segment.size = 0.2, segment.colour = "grey50") +
+  geom_text_repel(mapping = aes(y = p_log10, x = corr, label = Drug_Gene, color = Metric), force = 15, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.9) +
   theme(legend.position = "none", panel.grid.major.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(5.5, 1.5, 5.5, 5.5), "pt"), strip.background.y = element_blank(), strip.text.y = element_blank()) +
@@
   geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 10, nudge_y = 2.5, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
+  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 10, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
   scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
-  theme(legend.position = "none", plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt"), axis.title.y = element_blank()) +
-  labs(x = "Pearson correlation coefficient (r)", y = "-log10(p-value)")
-
-gdsc_genomic_features_summ_plot <- plot_grid(gdsc_summ_res_mut_plot, gdsc_summ_res_pearson_plot, align = "h", rel_widths = c(1, 5))
-gdsc_genomic_features_summ_plot
-
-# ggsave("./plots/manuscript/gdsc_genomic_features_summ_plot.png", gdsc_genomic_features_summ_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
-```
-
-### Drug: Mut
+  theme(legend.position = "none", axis.title.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
+  labs(x = "Pearson correlation coefficient (r)")
+
+gdsc_genomic_features_pearson_summ_plot <- plot_grid(gdsc_summ_res_mut_plot, gdsc_summ_res_pearson_plot, align = "h", rel_widths = c(1, 5))
+gdsc_genomic_features_pearson_summ_plot
+
+# ggsave("./plots/manuscript/gdsc_genomic_features_pearson_summ_plot.png", gdsc_genomic_features_pearson_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
+```
+
+Summary plot using Spearman correlation coefficient for GE and CN:
+```{r fig.height=4, fig.width=12}
+gdsc_spearman_res_GE <- select(filter(gdsc_cor_res, InG2P == "Yes"), Drug_Gene, Spearman_Corr_GE, Spearman_Pval_GE, Dataset)
+colnames(gdsc_spearman_res_GE) <- c("Drug_Gene", "corr", "p", "Dataset")
+gdsc_spearman_res_GE$Metric <- "Gene Expression"
+subset(gdsc_spearman_res_GE, p < 0.05)
+
+gdsc_spearman_res_CN <- select(filter(gdsc_cor_res, InG2P == "Yes"), Drug_Gene, Spearman_Corr_CN, Spearman_Pval_CN, Dataset)
+colnames(gdsc_spearman_res_CN) <- c("Drug_Gene", "corr", "p", "Dataset")
+gdsc_spearman_res_CN$Metric <- "Copy Number"
+subset(gdsc_spearman_res_CN, p < 0.05)
+
+gdsc_spearman_res_filt <- rbind(gdsc_spearman_res_GE, gdsc_spearman_res_CN)
+gdsc_spearman_res_filt$Metric <- factor(gdsc_spearman_res_filt$Metric, levels = c("Gene Expression", "Copy Number"))
+gdsc_spearman_res_filt$p_log10 <- -log10(gdsc_spearman_res_filt$p)
+
+gdsc_summ_res_spearman_plot <- ggplot(data = subset(gdsc_spearman_res_filt, p < 0.05)) +
+  facet_grid(Dataset ~ Metric) +
+  scale_y_continuous(breaks = seq(0, 50, by = 5), labels = seq(0, 50, by = 5)) +
+  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
+  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
+  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 20, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
+  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
+  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
+  labs(x = "Spearman's rank correlation coefficient (r_s)")
+
+gdsc_genomic_features_spearman_summ_plot <- plot_grid(gdsc_summ_res_mut_plot, gdsc_summ_res_spearman_plot, align = "h", rel_widths = c(1, 5))
+gdsc_genomic_features_spearman_summ_plot
+
+# ggsave("./plots/manuscript/gdsc_genomic_features_spearman_summ_plot.png", gdsc_genomic_features_spearman_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
+```
+
+#### Drug: Mut
 
@@
 ```{r fig.height=4, fig.width=8}
-all_res_mut <- rbind(ccle_res_mut, ctrp_res_mut, gdsc_res_mut)
-
-all_summ_res_plot <- ggplot(data = subset(all_res_mut, p < 0.05)) +
+all_mut_res <- rbind(ccle_res_mut, ctrp_res_mut, gdsc_res_mut)
+
+all_mut_summ_plot <- ggplot(data = subset(all_res_mut, p < 0.05)) +
   facet_grid(~ Dataset) +
@@
   labs(y = "-log10(p-value)")
-all_summ_res_plot
-
-# ggsave("./plots/manuscript/all_summ_mut_plot.png", all_summ_res_plot, device = "png", dpi = 450, width = 12, height = 6, units = "in")
-```
-
-### Drug: GE and CN
+all_mut_summ_plot
+
+# ggsave("./plots/manuscript/all_mut_summ_plot.png", all_mut_summ_plot, device = "png", dpi = 450, width = 12, height = 6, units = "in")
+```
+
+#### Drug: GE and CN
 
@@
 all_pearson_res <- rbind(ccle_pearson_res_filt, ctrp_pearson_res_filt, gdsc_pearson_res_filt)
-
-all_summ_res_pearson_plot <- ggplot(data = subset(all_pearson_res, p < 0.05)) +
+all_pearson_summ_plot <- ggplot(data = subset(all_pearson_res, p < 0.05)) +
   facet_grid(Dataset ~ Metric, scales = "free", space = "free") +
@@
   labs(x = "Pearson correlation coefficient (r)", y = "-log10(p-value)")
-all_summ_res_pearson_plot
-
-# ggsave("./plots/manuscript/all_summ_res_pearson_plot.png", all_summ_res_pearson_plot, device = "png", dpi = 450, width = 12, height = 10, units = "in")
+all_pearson_summ_plot
+# ggsave("./plots/manuscript/all_pearson_summ_plot.png", all_pearson_summ_plot, device = "png", dpi = 450, width = 12, height = 10, units = "in")
+
+all_spearman_res <- rbind(ccle_spearman_res_filt, ctrp_spearman_res_filt, gdsc_spearman_res_filt)
+all_spearman_summ_plot <- ggplot(data = subset(all_spearman_res, p < 0.05)) +
+  facet_grid(Dataset ~ Metric, scales = "free", space = "free") +
+  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
+  geom_point(aes(x = corr, y = p_log10, color = Dataset), alpha = 0.5) +
+  scale_y_continuous(breaks = seq(0, 60, by = 10), labels = seq(0, 60, by = 10)) +
+  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Dataset, label = Drug_Gene), force = 10, nudge_y = 1, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
+  scale_color_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
+  theme(legend.position = "none", plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
+  labs(x = "Pearson correlation coefficient (r)", y = "-log10(p-value)")
+all_spearman_summ_plot
+# ggsave("./plots/manuscript/all_spearman_summ_plot.png", all_spearman_summ_plot, device = "png", dpi = 450, width = 12, height = 10, units = "in")
 ```
@@
 
-## Mut, Ge, and CN
-
-#### Lineage-agnostic
+## Mut/GE/CN
+
+### Lineage-agnostic
 
@@
 ```{r fig.height=4, fig.width=5}
-g2p_druggene_pearson_stats <- g2p_druggene_pearson
-g2p_druggene_pearson_stats$n_true <- TRUE
-g2p_druggene_pearson_stats <- g2p_druggene_pearson_stats %>% group_by(Dataset, InG2P) %>% drop_na() %>% summarize(
+g2p_mut_cor_stats <- g2p_mut_cor
+g2p_mut_cor_stats$n_true <- TRUE
+g2p_mut_cor_stats <- g2p_mut_cor_stats %>% group_by(Dataset, InG2P) %>% drop_na() %>% summarize(
           ge_mean = round(mean(Pearson_GE_Abs), 5),
@@
           cn_n_sig_perc = cn_n_signif / cn_n * 100)
+```
+
+```{r fig.height=6, fig.width=12}
+pval_summ_mut <- g2p_mut_all_summ
+pval_summ_mut$Measure <- "Mutation Status"
+pval_summ_mut$Drug_Gene_Ordered <- NULL
+
+pval_summ_ge <- select(g2p_cor, Drug_Gene, n, Pearson_Pval_GE, InG2P, Dataset)
+colnames(pval_summ_ge)[colnames(pval_summ_ge) == "Pearson_Pval_GE"] <- "p"
+pval_summ_ge$p_log10 <- -log10(pval_summ_ge$p)
+pval_summ_ge$Measure <- "Gene Expression"
+
+pval_summ_cn <- select(g2p_cor, Drug_Gene, n, Pearson_Pval_CN, InG2P, Dataset)
+colnames(pval_summ_cn)[colnames(pval_summ_cn) == "Pearson_Pval_CN"] <- "p"
+pval_summ_cn$p_log10 <- -log10(pval_summ_cn$p)
+pval_summ_cn$Measure <- "Copy Number"
+
+pval_summ <- rbind(pval_summ_mut, pval_summ_ge, pval_summ_cn)
+pval_summ$Measure <- factor(pval_summ$Measure, levels = c("Mutation Status", "Gene Expression", "Copy Number"))
+
+pval_summ_plot <- ggplot(data = pval_summ, aes(x = p_log10, y = n, color = Dataset, shape = Dataset, label = Drug_Gene)) +
+  facet_wrap(~ Measure, scales = "free_x") +
+  geom_point(alpha = 0.7) +
+  scale_color_manual(values = c("green3", "darkslategray4", "darkturquoise")) +
+  geom_text_repel(data = filter(pval_summ, n > 20 & Measure == "Mutation Status"), mapping = aes(x = p_log10, y = n, color = Dataset, label = Drug_Gene), direction = "y", nudge_x = 9, hjust = 0, size = 2.5, segment.size = 0.1, segment.colour = "grey50", box.padding = 0.6, show.legend = FALSE) +
+  geom_text_repel(data = filter(pval_summ, n > 20 & Measure == "Gene Expression"), mapping = aes(x = p_log10, y = n, color = Dataset, label = Drug_Gene), direction = "y", nudge_x = 50, hjust = 0, size = 2.5, segment.size = 0.1, segment.colour = "grey50", box.padding = 0.6, show.legend = FALSE) +
+  geom_text_repel(data = filter(pval_summ, n > 20 & Measure == "Copy Number"), mapping = aes(x = p_log10, y = n, color = Dataset, label = Drug_Gene), direction = "y", nudge_x = 20, hjust = 0, size = 2.5, segment.size = 0.1, segment.colour = "grey50", box.padding = 0.6, show.legend = FALSE) +
+  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
+  labs(x = "-log10(p-value)", y = "Number of level A G2P associations") +
+  theme(legend.position = "bottom")
+pval_summ_plot
+
+# ggsave("./plots/manuscript/all_pval_summ_plot.png", pval_summ_plot, device = "png", dpi = 450, width = 12, height = 6, units = "in")
 ```
@@
 
-# ggsave("./plots/manuscript/all_druggenelin_ttest_summ_facet_plot.png", ttest_mut_summ_facet, device = "png", dpi = 450, width = 12, height = 4, units = "in")
+# ggsave("./plots/manuscript/all_dgl_ttest_summ_facet_plot.png", ttest_mut_summ_facet, device = "png", dpi = 450, width = 12, height = 4, units = "in")
 ```
@@
 
-# ggsave("./plots/manuscript/all_druggenelin_ttest_summ_plot.png", ttest_summ_plot, device = "png", dpi = 450, width = 12, height = 7, units = "in")
+# ggsave("./plots/manuscript/all_dgl_ttest_summ_plot.png", ttest_summ_plot, device = "png", dpi = 450, width = 12, height = 7, units = "in")
 ```
@@
 
-# ggsave("./plots/manuscript/dgl_all_plot.png", dgl_all_plot, device = "png", dpi = 450, width = 12, height = 40, units = "in")
+# ggsave("./plots/manuscript/all_dgl_plot.png", dgl_all_plot, device = "png", dpi = 450, width = 12, height = 40, units = "in")
 ```

### 2018-12-17 manuscript.Rmd
update Rmd

@@
       pearson_res <- use_data_filt %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$estimate, Pearson_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$p.value)
-      pearson_res <- merge(g2p_druggene_p_tally, pearson_res, all.y = TRUE)
+      pearson_res <- merge(g2p_druggene_tally, pearson_res, all.y = TRUE)
       pearson_res$group_general_lineage_name <- lin
@@
       pearson_res <- use_data_filt %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$estimate, Pearson_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$p.value)
-      pearson_res <- merge(g2p_druggene_p_tally, pearson_res, all.y = TRUE)
+      pearson_res <- merge(g2p_druggene_tally, pearson_res, all.y = TRUE)
       pearson_res$group_general_lineage_name <- lin
@@
 
-g2p_druggenelins <-  unique(g2p_filt$Drug_Gene_Lin[!is.na(g2p_filt$Drug_Gene_Lin)])
-g2p_drug_genes <- unique(g2p_filt$Drug_Gene[!is.na(g2p_filt$Drug_Gene)])
+g2p_dgls <-  unique(g2p_filt$Drug_Gene_Lin[!is.na(g2p_filt$Drug_Gene_Lin)])
+g2p_druggenes <- unique(g2p_filt$Drug_Gene[!is.na(g2p_filt$Drug_Gene)])
 g2p_genes <- unique(sapply(strsplit(g2p_drug_genes, "_", fixed = TRUE), function(x) x[2]))
 g2p_drugs <- unique(sapply(strsplit(g2p_drug_genes, "_", fixed = TRUE), function(x) x[1]))
-g2p_drug_genes
+g2p_druggenes
 g2p_genes
@@
 # Filter drug screen datasets for G2P drug-gene-lineage associations
-ccle_data_g2p_dgl <- filter(ccle_data_ptmuts, Drug_Gene_Lin %in% g2p_druggenelins)
+ccle_data_g2p_dgl <- filter(ccle_data_ptmuts, Drug_Gene_Lin %in% g2p_dgls)
 ccle_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(ccle_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-ctrp_data_g2p_dgl <- filter(ctrp_data_ptmuts, Drug_Gene_Lin %in% g2p_druggenelins)
+ctrp_data_g2p_dgl <- filter(ctrp_data_ptmuts, Drug_Gene_Lin %in% g2p_dgls)
 ctrp_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-gdsc_data_g2p_dgl <- filter(gdsc_data_ptmuts, Drug_Gene_Lin %in% g2p_druggenelins)
+gdsc_data_g2p_dgl <- filter(gdsc_data_ptmuts, Drug_Gene_Lin %in% g2p_dgls)
 gdsc_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
@@
                                    Metric = "Gene Expression")
-
 crispr_pearson_res_CN <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>%
@@
                                    Metric = "Copy Number")
-
 crispr_spearman_res_GE <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>%
@@
                                     Metric = "Gene Expression")
-
 crispr_spearman_res_CN <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>%
@@
 ```{r}
-g2p_druggene_p_tally <- g2p_filt %>% group_by(Drug_Gene) %>% tally() %>% drop_na()
+g2p_druggene_tally <- g2p_filt %>% group_by(Drug_Gene) %>% tally() %>% drop_na()
+
+# CCLE
 ccle_cor_res <- ccle_data_g2p_grid %>% group_by(Drug_Gene) %>%
@@
                               Spearman_Pval_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$p.value)
-ccle_cor_res <- merge(g2p_druggene_p_tally, ccle_cor_res, by = "Drug_Gene", all.y = TRUE)
+ccle_cor_res <- merge(g2p_druggene_tally, ccle_cor_res, by = "Drug_Gene", all.y = TRUE)
 ccle_cor_res$n <- ifelse(is.na(ccle_cor_res$n), 0, ccle_cor_res$n)
@@
 
+# CTRP
 ctrp_cor_res <- ctrp_data_g2p_grid %>% group_by(Drug_Gene) %>%
@@
                               Spearman_Pval_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$p.value)
-ctrp_cor_res <- merge(g2p_druggene_p_tally, ctrp_cor_res, by = "Drug_Gene", all.y = TRUE)
+ctrp_cor_res <- merge(g2p_druggene_tally, ctrp_cor_res, by = "Drug_Gene", all.y = TRUE)
 ctrp_cor_res$n <- ifelse(is.na(ctrp_cor_res$n), 0, ctrp_cor_res$n)
@@
 
+# GDSC
 gdsc_cor_res <- gdsc_data_g2p_grid %>% group_by(Drug_Gene) %>%
@@
                               Spearman_Pval_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$p.value)
-gdsc_cor_res <- merge(g2p_druggene_p_tally, gdsc_cor_res, by = "Drug_Gene", all.y = TRUE)
+gdsc_cor_res <- merge(g2p_druggene_tally, gdsc_cor_res, by = "Drug_Gene", all.y = TRUE)
 gdsc_cor_res$n <- ifelse(is.na(gdsc_cor_res$n), 0, gdsc_cor_res$n)
@@
 
+# All
 g2p_cor <- rbind(ccle_cor_res, ctrp_cor_res, gdsc_cor_res)
@@
 g2p_cor$Spearman_CN_Sign <- ifelse(sign(g2p_cor$Spearman_Corr_CN) == 1, "+", ifelse(sign(g2p_cor$Spearman_Corr_CN) == -1, "-", "0"))
-
 g2p_cor_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"),
@@
 print("Drug-Gene")
-g2p_druggene_p_tally <- g2p_filt %>% group_by(Drug_Gene) %>% tally() %>% drop_na()
-nrow(g2p_druggene_p_tally)
-range(g2p_druggene_p_tally$n)
-mean(g2p_druggene_p_tally$n)
-sd(g2p_druggene_p_tally$n)
+g2p_druggene_tally <- g2p_filt %>% group_by(Drug_Gene) %>% tally() %>% drop_na()
+nrow(g2p_druggene_tally)
+range(g2p_druggene_tally$n)
+mean(g2p_druggene_tally$n)
+sd(g2p_druggene_tally$n)
 
@@
 print("Drug-Gene-Lineage")
-g2p_druggenelin_tally <- g2p_filt %>% group_by(Drug, Gene, Drug_Gene, group_general_lineage_name) %>% tally() %>% drop_na()
-nrow(g2p_druggenelin_tally)
-length(unique(g2p_druggenelin_tally$Drug))
-length(unique(g2p_druggenelin_tally$Gene))
+g2p_dgl_tally <- g2p_filt %>% group_by(Drug, Gene, Drug_Gene, group_general_lineage_name) %>% tally() %>% drop_na()
+nrow(g2p_dgl_tally)
+length(unique(g2p_dgl_tally$Drug))
+length(unique(g2p_dgl_tally$Gene))
 unique(g2p_filt$Phenotype.Description)
@@
 
-Drug screen test plot for G2P associations vs. p-value plot:
-```{r fig.height=4, fig.width=8}
-g2p_mut_summ <- merge(g2p_druggene_p_tally, ccle_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all.x = TRUE)
-g2p_mut_summ <- merge(g2p_mut_summ, ctrp_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all.x = TRUE, suffixes = c("_CCLE", "_CTRP"))
-g2p_mut_summ <- merge(g2p_mut_summ, gdsc_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all.x = TRUE)
-colnames(g2p_mut_summ)[colnames(g2p_mut_summ) == "p_CCLE"] <- "CCLE"
-colnames(g2p_mut_summ)[colnames(g2p_mut_summ) == "p_CTRP"] <- "CTRP"
-colnames(g2p_mut_summ)[colnames(g2p_mut_summ) == "p"] <- "GDSC"
-
-g2p_mut_summ_melt <- melt(g2p_mut_summ, id.vars = c("Drug_Gene", "n"), measure.vars = c("CCLE", "CTRP", "GDSC"), variable.name = "Dataset", value.name = "p")
-
-g2p_mut_summ_plot <- ggplot(data = g2p_mut_summ_melt, aes(x = p, y = n, shape = Dataset, color = Dataset)) +
-  geom_point(size = 2) +
-  scale_color_manual(values = c("green3", "darkslategray4", "darkturquoise")) +
-  labs(x = "Gene-drug association p-value by mutation status", y = "Number of level A G2P associations")
-g2p_mut_summ_plot
-# ggsave("./plots/manuscript/g2p_mut_summ_plot.png", g2p_mut_summ_plot, device = "png", dpi = 450, width = 8, height = 4, units = "in")
-```
-
-Code to write out dataframe of p-values for Dan to make green heatmaps:
-```{r}
-# for_dan <- with(g2p_druggene_p_summ, cbind(n, CCLE, CTRP, GDSC, colsplit(Drug_Gene, pattern = "_", names = c("Drug", "Hugo_Symbol"))))
-# write.table(for_dan, file = "~/Desktop/for_dan.tsv", sep = "\t")
-```
-
-```{r}
-ccle_mut_summ <- merge(g2p_druggene_p_tally, ccle_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
+```{r}
+ccle_mut_summ <- merge(g2p_druggene_tally, ccle_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
 ccle_mut_summ$n <- ifelse(is.na(ccle_mut_summ$n), 0, ccle_mut_summ$n)
@@
 
-ctrp_mut_summ <- merge(g2p_druggene_p_tally, ctrp_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
+ctrp_mut_summ <- merge(g2p_druggene_tally, ctrp_signif_g2p_grid[, c("`Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
 ctrp_mut_summ$n <- ifelse(is.na(ctrp_mut_summ$n), 0, ctrp_mut_summ$n)
@@
 
-gdsc_mut_summ <- merge(g2p_druggene_p_tally, gdsc_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
+gdsc_mut_summ <- merge(g2p_druggene_tally, gdsc_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
 gdsc_mut_summ$n <- ifelse(is.na(gdsc_mut_summ$n), 0, gdsc_mut_summ$n)
@@
 
-### Genomic features supplementary plots
-
-This section contains summary plots for the Wilcoxon tests and Pearson/Spearman correlations done for only level A G2P drug-gene associations (i.e.
-not the grid tests) and G2P genes in the case of the CRISPR dataset.
-
-#### CRISPR
-
-G2P genes with a significant effect on CERES score by mutation status, gene expression, and copy number. Summary plot using Pearson correlation coefficient for GE and CN:
-```{r fig.height=5, fig.width=12}
-crispr_res_mut <- select(crispr_signif_g2p_gene, Hugo_Symbol, p)
-crispr_res_mut$corr <- 0
-crispr_res_mut$Metric <- "Mutation Status"
-crispr_res_mut$p_log10 <- -log10(crispr_res_mut$p)
-subset(crispr_res_mut, p < 0.05)
-
-subset(crispr_pearson_res_GE, p < 0.05)
-subset(crispr_pearson_res_CN, p < 0.05)
-
-crispr_pearson_res <- rbind(crispr_pearson_res_GE, crispr_pearson_res_CN)
-crispr_pearson_res$Metric <- factor(crispr_pearson_res$Metric, levels = c("Gene Expression", "Copy Number"))
-crispr_pearson_res$p_log10 <- -log10(crispr_pearson_res$p)
-
-crispr_summ_res_mut_plot <- ggplot(data = subset(crispr_res_mut, p < 0.05)) +
-  facet_grid(~ Metric) +
-  scale_y_continuous(breaks = seq(0, 50, by = 5), labels = seq(0, 50, by = 5)) +
-  coord_cartesian(ylim = c(0, 50)) +
-  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_label_repel(mapping = aes(y = p_log10, x = corr, label = Hugo_Symbol, color = Metric), force = 10, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
-  theme(legend.position = "none", panel.grid.major.x = element_blank(), panel.grid.minor.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(5.5, 1.5, 5.5, 5.5), "pt")) +
-  scale_color_manual(values = c("Mutation Status" = "darkorchid4")) +
-  labs(y = "-log10(p-value)")
-
-crispr_summ_res_pearson_plot <- ggplot(data = subset(crispr_pearson_res, p < 0.05)) +
-  facet_grid(~ Metric, scales = "free_x", space = "free") +
-  scale_y_continuous(breaks = seq(0, 50, by = 5), labels = seq(0, 50, by = 5)) +
-  scale_x_continuous(breaks = seq(-0.6, 0.3, by = 0.1), labels = formatC(seq(-0.6, 0.3, by = 0.1), digits = 2, format = "f")) +
-  coord_cartesian(ylim = c(0, 50)) +
-  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
-  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_label_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Hugo_Symbol), force = 10, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
-  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
-  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
-  labs(x = "Pearson correlation coefficient (r)")
-
-crispr_genomic_features_pearson_summ_plot <- plot_grid(crispr_summ_res_mut_plot, crispr_summ_res_pearson_plot, align = "h", rel_widths = c(1, 5))
-crispr_genomic_features_pearson_summ_plot
-
-# ggsave("./plots/manuscript/crispr_genomic_features_pearson_summ_plot.png", crispr_genomic_features_pearson_summ_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
-```
-
-Summary plot using Spearman correlation coefficient for GE and CN:
-```{r fig.height=5, fig.width=12}
-subset(crispr_spearman_res_GE, p < 0.05)
-subset(crispr_spearman_res_CN, p < 0.05)
-
-crispr_spearman_res <- rbind(crispr_spearman_res_GE, crispr_spearman_res_CN)
-crispr_spearman_res$Metric <- factor(crispr_spearman_res$Metric, levels = c("Gene Expression", "Copy Number"))
-crispr_spearman_res$p_log10 <- -log10(crispr_spearman_res$p)
-
-crispr_summ_res_spearman_plot <- ggplot(data = subset(crispr_spearman_res, p < 0.05)) +
-  facet_grid(~ Metric, scales = "free_x", space = "free") +
-  scale_y_continuous(breaks = seq(0, 50, by = 5), labels = seq(0, 50, by = 5)) +
-  scale_x_continuous(breaks = seq(-0.6, 0.3, by = 0.1), labels = formatC(seq(-0.6, 0.3, by = 0.1), digits = 2, format = "f")) +
-  coord_cartesian(ylim = c(0, 50)) +
-  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
-  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_label_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Hugo_Symbol), force = 10, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
-  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
-  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
-  labs(x = "Spearman's rank correlation coefficient (r_s)")
-
-crispr_genomic_features_spearman_summ_plot <- plot_grid(crispr_summ_res_mut_plot, crispr_summ_res_spearman_plot, align = "h", rel_widths = c(1, 5))
-crispr_genomic_features_spearman_summ_plot
-
-# ggsave("./plots/manuscript/crispr_genomic_features_spearman_summ_plot.png", crispr_genomic_features_spearman_summ_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
-```
-
-#### CCLE
-
-G2P drug-gene associations with a significant effect on AUC by mutation status, gene expression, and copy number. Summary plot using Pearson correlation coefficient for GE and CN:
-```{r fig.height=4, fig.width=12}
-ccle_res_mut <- select(ccle_signif_g2p, Drug_Gene, p)
-ccle_res_mut$corr <- 0
-ccle_res_mut$Metric <- "Mutation Status"
-ccle_res_mut$p_log10 <- -log10(ccle_res_mut$p)
-ccle_res_mut$Dataset <- "CCLE"
-
-ccle_pearson_res_GE <- select(filter(ccle_cor_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_GE, Pearson_Pval_GE, Dataset)
-colnames(ccle_pearson_res_GE) <- c("Drug_Gene", "corr", "p", "Dataset")
-ccle_pearson_res_GE$Metric <- "Gene Expression"
-subset(ccle_pearson_res_GE, p < 0.05)
-
-ccle_pearson_res_CN <- select(filter(ccle_cor_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_CN, Pearson_Pval_CN, Dataset)
-colnames(ccle_pearson_res_CN) <- c("Drug_Gene", "corr", "p", "Dataset")
-ccle_pearson_res_CN$Metric <- "Copy Number"
-subset(ccle_pearson_res_CN, p < 0.05)
-
-ccle_pearson_res_filt <- rbind(ccle_pearson_res_GE, ccle_pearson_res_CN)
-ccle_pearson_res_filt$Metric <- factor(ccle_pearson_res_filt$Metric, levels = c("Gene Expression", "Copy Number"))
-ccle_pearson_res_filt$p_log10 <- -log10(ccle_pearson_res_filt$p)
-
-ccle_summ_res_mut_plot <- ggplot(data = subset(ccle_res_mut, p < 0.05)) +
-  facet_grid(Dataset ~ Metric) +
-  scale_y_continuous(breaks = seq(0, 35, by = 5), labels = seq(0, 35, by = 5)) +
-  coord_cartesian(ylim = c(0, 35)) +
-  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_label_repel(mapping = aes(y = p_log10, x = corr, label = Drug_Gene, color = Metric), force = 10, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
-  theme(legend.position = "none", panel.grid.major.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(5.5, 1.5, 5.5, 5.5), "pt"), strip.background.y = element_blank(), strip.text.y = element_blank()) +
-  scale_color_manual(values = c("Mutation Status" = "darkorchid4")) +
-  labs(y = "-log10(p-value)")
-
-ccle_summ_res_pearson_plot <- ggplot(data = subset(ccle_pearson_res_filt, p < 0.05)) +
-  facet_grid(Dataset ~ Metric) +
-  coord_cartesian(ylim = c(0, 35)) +
-  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
-  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_label_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 10, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
-  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
-  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
-  labs(x = "Pearson correlation coefficient (r)")
-
-ccle_genomic_features_pearson_summ_plot <- plot_grid(ccle_summ_res_mut_plot, ccle_summ_res_pearson_plot, align = "h", rel_widths = c(1, 5))
-ccle_genomic_features_pearson_summ_plot
-
-# ggsave("./plots/manuscript/ccle_genomic_features_pearson_summ_plot.png", ccle_genomic_features_pearson_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
-```
-
-Summary plot using Spearman correlation coefficient for GE and CN:
-```{r fig.height=4, fig.width=12}
-ccle_spearman_res_GE <- select(filter(ccle_cor_res, InG2P == "Yes"), Drug_Gene, Spearman_Corr_GE, Spearman_Pval_GE, Dataset)
-colnames(ccle_spearman_res_GE) <- c("Drug_Gene", "corr", "p", "Dataset")
-ccle_spearman_res_GE$Metric <- "Gene Expression"
-subset(ccle_spearman_res_GE, p < 0.05)
-
-ccle_spearman_res_CN <- select(filter(ccle_cor_res, InG2P == "Yes"), Drug_Gene, Spearman_Corr_CN, Spearman_Pval_CN, Dataset)
-colnames(ccle_spearman_res_CN) <- c("Drug_Gene", "corr", "p", "Dataset")
-ccle_spearman_res_CN$Metric <- "Copy Number"
-subset(ccle_spearman_res_CN, p < 0.05)
-
-ccle_spearman_res_filt <- rbind(ccle_spearman_res_GE, ccle_spearman_res_CN)
-ccle_spearman_res_filt$Metric <- factor(ccle_spearman_res_filt$Metric, levels = c("Gene Expression", "Copy Number"))
-ccle_spearman_res_filt$p_log10 <- -log10(ccle_spearman_res_filt$p)
-
-ccle_summ_res_spearman_plot <- ggplot(data = subset(ccle_spearman_res_filt, p < 0.05)) +
-  facet_grid(Dataset ~ Metric) +
-  coord_cartesian(ylim = c(0, 35)) +
-  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
-  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_label_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 10, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
-  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
-  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
-  labs(x = "Spearman's rank correlation coefficient (r_s)")
-
-ccle_genomic_features_spearman_summ_plot <- plot_grid(ccle_summ_res_mut_plot, ccle_summ_res_spearman_plot, align = "h", rel_widths = c(1, 5))
-ccle_genomic_features_spearman_summ_plot
-
-# ggsave("./plots/manuscript/ccle_genomic_features_spearman_summ_plot.png", ccle_genomic_features_spearman_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
-```
-
-#### CTRP
-
-G2P drug-gene associations with a significant effect on AUC by mutation status, gene expression, and copy number. Summary plot using Pearson correlation coefficient for GE and CN:
-```{r fig.height=4, fig.width=12}
-ctrp_res_mut <- select(ctrp_signif_g2p, Drug_Gene, p)
-ctrp_res_mut$corr <- 0
-ctrp_res_mut$Metric <- "Mutation Status"
-ctrp_res_mut$p_log10 <- -log10(ctrp_res_mut$p)
-ctrp_res_mut$Dataset <- "CTRP"
-
-ctrp_pearson_res_GE <- select(filter(ctrp_cor_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_GE, Pearson_Pval_GE, Dataset)
-colnames(ctrp_pearson_res_GE) <- c("Drug_Gene", "corr", "p", "Dataset")
-ctrp_pearson_res_GE$Metric <- "Gene Expression"
-subset(ctrp_pearson_res_GE, p < 0.05)
-
-ctrp_pearson_res_CN <- select(filter(ctrp_cor_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_CN, Pearson_Pval_CN, Dataset)
-colnames(ctrp_pearson_res_CN) <- c("Drug_Gene", "corr", "p", "Dataset")
-ctrp_pearson_res_CN$Metric <- "Copy Number"
-subset(ctrp_pearson_res_CN, p < 0.05)
-
-ctrp_pearson_res_filt <- rbind(ctrp_pearson_res_GE, ctrp_pearson_res_CN)
-ctrp_pearson_res_filt$Metric <- factor(ctrp_pearson_res_filt$Metric, levels = c("Gene Expression", "Copy Number"))
-ctrp_pearson_res_filt$p_log10 <- -log10(ctrp_pearson_res_filt$p)
-
-ctrp_summ_res_mut_plot <- ggplot(data = subset(ctrp_res_mut, p < 0.05)) +
-  facet_grid(Dataset ~ Metric) +
-  scale_y_continuous(breaks = seq(0, 35, by = 5), labels = seq(0, 35, by = 5)) +
-  coord_cartesian(ylim = c(0, 35)) +
-  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_text_repel(mapping = aes(y = p_log10, x = corr, label = Drug_Gene, color = Metric), force = 15, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.9) +
-  theme(legend.position = "none", panel.grid.major.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(5.5, 1.5, 5.5, 5.5), "pt"), strip.background.y = element_blank(), strip.text.y = element_blank()) +
-  scale_color_manual(values = c("Mutation Status" = "darkorchid4")) +
-  labs(y = "-log10(p-value)")
-
-ctrp_summ_res_pearson_plot <- ggplot(data = subset(ctrp_pearson_res_filt, p < 0.05)) +
-  facet_grid(Dataset ~ Metric) +
-  coord_cartesian(ylim = c(0, 35)) +
-  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
-  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 10, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
-  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
-  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
-  labs(x = "Pearson correlation coefficient (r)")
-
-ctrp_genomic_features_pearson_summ_plot <- plot_grid(ctrp_summ_res_mut_plot, ctrp_summ_res_pearson_plot, align = "h", rel_widths = c(1, 5))
-ctrp_genomic_features_pearson_summ_plot
-
-# ggsave("./plots/manuscript/ctrp_genomic_features_pearson_summ_plot.png", ctrp_genomic_features_pearson_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
-```
-
-Summary plot using Spearman correlation coefficient for GE and CN:
-```{r fig.height=4, fig.width=12}
-ctrp_spearman_res_GE <- select(filter(ctrp_cor_res, InG2P == "Yes"), Drug_Gene, Spearman_Corr_GE, Spearman_Pval_GE, Dataset)
-colnames(ctrp_spearman_res_GE) <- c("Drug_Gene", "corr", "p", "Dataset")
-ctrp_spearman_res_GE$Metric <- "Gene Expression"
-subset(ctrp_spearman_res_GE, p < 0.05)
-
-ctrp_spearman_res_CN <- select(filter(ctrp_cor_res, InG2P == "Yes"), Drug_Gene, Spearman_Corr_CN, Spearman_Pval_CN, Dataset)
-colnames(ctrp_spearman_res_CN) <- c("Drug_Gene", "corr", "p", "Dataset")
-ctrp_spearman_res_CN$Metric <- "Copy Number"
-subset(ctrp_spearman_res_CN, p < 0.05)
-
-ctrp_spearman_res_filt <- rbind(ctrp_spearman_res_GE, ctrp_spearman_res_CN)
-ctrp_spearman_res_filt$Metric <- factor(ctrp_spearman_res_filt$Metric, levels = c("Gene Expression", "Copy Number"))
-ctrp_spearman_res_filt$p_log10 <- -log10(ctrp_spearman_res_filt$p)
-
-ctrp_summ_res_spearman_plot <- ggplot(data = subset(ctrp_spearman_res_filt, p < 0.05)) +
-  facet_grid(Dataset ~ Metric) +
-  coord_cartesian(ylim = c(0, 35)) +
-  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
-  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 20, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
-  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
-  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
-  labs(x = "Spearman's rank correlation coefficient (r_s)")
-
-ctrp_genomic_features_spearman_summ_plot <- plot_grid(ctrp_summ_res_mut_plot, ctrp_summ_res_spearman_plot, align = "h", rel_widths = c(1, 5))
-ctrp_genomic_features_spearman_summ_plot
-
-# ggsave("./plots/manuscript/ctrp_genomic_features_spearman_summ_plot.png", ctrp_genomic_features_spearman_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
-```
-
-#### GDSC
-
-G2P drug-gene associations with a significant effect on AUC by mutation status, gene expression, and copy number. Summary plot using Pearson correlation coefficient for GE and CN:
-```{r fig.height=4, fig.width=12}
-gdsc_res_mut <- select(gdsc_signif_g2p, Drug_Gene, p)
-gdsc_res_mut$corr <- 0
-gdsc_res_mut$Metric <- "Mutation Status"
-gdsc_res_mut$p_log10 <- -log10(gdsc_res_mut$p)
-gdsc_res_mut$Dataset <- "GDSC"
-
-gdsc_pearson_res_GE <- select(filter(gdsc_cor_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_GE, Pearson_Pval_GE, Dataset)
-colnames(gdsc_pearson_res_GE) <- c("Drug_Gene", "corr", "p", "Dataset")
-gdsc_pearson_res_GE$Metric <- "Gene Expression"
-subset(gdsc_pearson_res_GE, p < 0.05)
-
-gdsc_pearson_res_CN <- select(filter(gdsc_cor_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_CN, Pearson_Pval_CN, Dataset)
-colnames(gdsc_pearson_res_CN) <- c("Drug_Gene", "corr", "p", "Dataset")
-gdsc_pearson_res_CN$Metric <- "Copy Number"
-subset(gdsc_pearson_res_CN, p < 0.05)
-
-gdsc_pearson_res_filt <- rbind(gdsc_pearson_res_GE, gdsc_pearson_res_CN)
-gdsc_pearson_res_filt$Metric <- factor(gdsc_pearson_res_filt$Metric, levels = c("Gene Expression", "Copy Number"))
-gdsc_pearson_res_filt$p_log10 <- -log10(gdsc_pearson_res_filt$p)
-
-gdsc_summ_res_mut_plot <- ggplot(data = subset(gdsc_res_mut, p < 0.05)) +
-  facet_grid(Dataset ~ Metric) +
-  scale_y_continuous(breaks = seq(0, 16, by = 1), labels = seq(0, 16, by = 1)) +
-  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_text_repel(mapping = aes(y = p_log10, x = corr, label = Drug_Gene, color = Metric), force = 15, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.9) +
-  theme(legend.position = "none", panel.grid.major.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(5.5, 1.5, 5.5, 5.5), "pt"), strip.background.y = element_blank(), strip.text.y = element_blank()) +
-  scale_color_manual(values = c("Mutation Status" = "darkorchid4")) +
-  labs(y = "-log10(p-value)")
-
-gdsc_summ_res_pearson_plot <- ggplot(data = subset(gdsc_pearson_res_filt, p < 0.05)) +
-  facet_grid(Dataset ~ Metric) +
-  scale_y_continuous(breaks = seq(0, 100, by = 10), labels = seq(0, 100, by = 10)) +
-  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
-  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 10, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
-  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
-  theme(legend.position = "none", axis.title.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
-  labs(x = "Pearson correlation coefficient (r)")
-
-gdsc_genomic_features_pearson_summ_plot <- plot_grid(gdsc_summ_res_mut_plot, gdsc_summ_res_pearson_plot, align = "h", rel_widths = c(1, 5))
-gdsc_genomic_features_pearson_summ_plot
-
-# ggsave("./plots/manuscript/gdsc_genomic_features_pearson_summ_plot.png", gdsc_genomic_features_pearson_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
-```
-
-Summary plot using Spearman correlation coefficient for GE and CN:
-```{r fig.height=4, fig.width=12}
-gdsc_spearman_res_GE <- select(filter(gdsc_cor_res, InG2P == "Yes"), Drug_Gene, Spearman_Corr_GE, Spearman_Pval_GE, Dataset)
-colnames(gdsc_spearman_res_GE) <- c("Drug_Gene", "corr", "p", "Dataset")
-gdsc_spearman_res_GE$Metric <- "Gene Expression"
-subset(gdsc_spearman_res_GE, p < 0.05)
-
-gdsc_spearman_res_CN <- select(filter(gdsc_cor_res, InG2P == "Yes"), Drug_Gene, Spearman_Corr_CN, Spearman_Pval_CN, Dataset)
-colnames(gdsc_spearman_res_CN) <- c("Drug_Gene", "corr", "p", "Dataset")
-gdsc_spearman_res_CN$Metric <- "Copy Number"
-subset(gdsc_spearman_res_CN, p < 0.05)
-
-gdsc_spearman_res_filt <- rbind(gdsc_spearman_res_GE, gdsc_spearman_res_CN)
-gdsc_spearman_res_filt$Metric <- factor(gdsc_spearman_res_filt$Metric, levels = c("Gene Expression", "Copy Number"))
-gdsc_spearman_res_filt$p_log10 <- -log10(gdsc_spearman_res_filt$p)
-
-gdsc_summ_res_spearman_plot <- ggplot(data = subset(gdsc_spearman_res_filt, p < 0.05)) +
-  facet_grid(Dataset ~ Metric) +
-  scale_y_continuous(breaks = seq(0, 50, by = 5), labels = seq(0, 50, by = 5)) +
-  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
-  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 20, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
-  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
-  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
-  labs(x = "Spearman's rank correlation coefficient (r_s)")
-
-gdsc_genomic_features_spearman_summ_plot <- plot_grid(gdsc_summ_res_mut_plot, gdsc_summ_res_spearman_plot, align = "h", rel_widths = c(1, 5))
-gdsc_genomic_features_spearman_summ_plot
-
-# ggsave("./plots/manuscript/gdsc_genomic_features_spearman_summ_plot.png", gdsc_genomic_features_spearman_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
-```
-
-#### Drug: Mut
-
-G2P drug-gene associations with a significant effect on AUC by mutation status:
-```{r fig.height=4, fig.width=8}
-all_mut_res <- rbind(ccle_res_mut, ctrp_res_mut, gdsc_res_mut)
-
-all_mut_summ_plot <- ggplot(data = subset(all_res_mut, p < 0.05)) +
-  facet_grid(~ Dataset) +
-  geom_point(aes(x = corr, y = p_log10, color = Dataset), alpha = 0.5) +
-  scale_y_continuous(breaks = seq(0, 12, by = 2), labels = seq(0, 12, by = 2)) +
-  scale_x_continuous(breaks = seq(0, 0.1, by = 0.1), labels = seq(0, 0.1, by = 0.1)) +
-  coord_cartesian(xlim = c(0, 0.05)) +
-  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Dataset, label = Drug_Gene), nudge_x = 0.05, direction = "y", hjust = 0, size = 2.5, segment.size = 0.1, segment.colour = "grey50", box.padding = 0.6) +
-  scale_color_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
-  theme(legend.position = "none", plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt"), panel.grid.major.x = element_blank(), panel.grid.minor.x = element_blank(), axis.title.x = element_blank(), axis.ticks.x = element_blank(), axis.text.x = element_blank()) +
-  labs(y = "-log10(p-value)")
-all_mut_summ_plot
-
-# ggsave("./plots/manuscript/all_mut_summ_plot.png", all_mut_summ_plot, device = "png", dpi = 450, width = 12, height = 6, units = "in")
-```
-
-#### Drug: GE and CN
-
-G2P drug-gene associations with a significant effect on AUC by gene expression and copy number:
-```{r fig.height=12, fig.width=12}
-all_pearson_res <- rbind(ccle_pearson_res_filt, ctrp_pearson_res_filt, gdsc_pearson_res_filt)
-all_pearson_summ_plot <- ggplot(data = subset(all_pearson_res, p < 0.05)) +
-  facet_grid(Dataset ~ Metric, scales = "free", space = "free") +
-  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
-  geom_point(aes(x = corr, y = p_log10, color = Dataset), alpha = 0.5) +
-  scale_y_continuous(breaks = seq(0, 60, by = 10), labels = seq(0, 60, by = 10)) +
-  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Dataset, label = Drug_Gene), force = 10, nudge_y = 3, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
-  scale_color_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
-  theme(legend.position = "none", plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
-  labs(x = "Pearson correlation coefficient (r)", y = "-log10(p-value)")
-all_pearson_summ_plot
-# ggsave("./plots/manuscript/all_pearson_summ_plot.png", all_pearson_summ_plot, device = "png", dpi = 450, width = 12, height = 10, units = "in")
-
-all_spearman_res <- rbind(ccle_spearman_res_filt, ctrp_spearman_res_filt, gdsc_spearman_res_filt)
-all_spearman_summ_plot <- ggplot(data = subset(all_spearman_res, p < 0.05)) +
-  facet_grid(Dataset ~ Metric, scales = "free", space = "free") +
-  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
-  geom_point(aes(x = corr, y = p_log10, color = Dataset), alpha = 0.5) +
-  scale_y_continuous(breaks = seq(0, 60, by = 10), labels = seq(0, 60, by = 10)) +
-  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Dataset, label = Drug_Gene), force = 10, nudge_y = 1, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
-  scale_color_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
-  theme(legend.position = "none", plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
-  labs(x = "Pearson correlation coefficient (r)", y = "-log10(p-value)")
-all_spearman_summ_plot
-# ggsave("./plots/manuscript/all_spearman_summ_plot.png", all_spearman_summ_plot, device = "png", dpi = 450, width = 12, height = 10, units = "in")
-```
-
 ## Lineage-grouped
@@
 ```{r}
-g2p_druggenelin_p_tally <- g2p %>% group_by(Drug_Gene, group_general_lineage_name) %>% tally()
-
-ccle_druggenelin_summ <- ccle_signif_grid_lineage
-ccle_druggenelin_summ$Drug_Gene <- paste0(ccle_druggenelin_summ$Drug, "_", ccle_druggenelin_summ$Hugo_Symbol)
-ccle_druggenelin_summ <- merge(g2p_druggenelin_p_tally, ccle_druggenelin_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
-ccle_druggenelin_summ$Drug_Gene_Lin <- paste0(ccle_druggenelin_summ$Drug_Gene, "_", ccle_druggenelin_summ$group_general_lineage_name)
-ccle_druggenelin_summ$n <- ifelse(is.na(ccle_druggenelin_summ$n), 0, ccle_druggenelin_summ$n)
-ccle_druggenelin_summ$InG2P <- ifelse(ccle_druggenelin_summ$n != 0, "Yes", "No")
-ccle_druggenelin_summ$Dataset <- "CCLE"
-
-ctrp_druggenelin_summ <- ctrp_signif_grid_lineage
-ctrp_druggenelin_summ$Drug_Gene <- paste0(ctrp_druggenelin_summ$Drug, "_", ctrp_druggenelin_summ$Hugo_Symbol)
-ctrp_druggenelin_summ <- merge(g2p_druggenelin_p_tally, ctrp_druggenelin_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
-ctrp_druggenelin_summ$Drug_Gene_Lin <- paste0(ctrp_druggenelin_summ$Drug_Gene, "_", ctrp_druggenelin_summ$group_general_lineage_name)
-ctrp_druggenelin_summ$n <- ifelse(is.na(ctrp_druggenelin_summ$n), 0, ctrp_druggenelin_summ$n)
-ctrp_druggenelin_summ$InG2P <- ifelse(ctrp_druggenelin_summ$n != 0, "Yes", "No")
-ctrp_druggenelin_summ$Dataset <- "CTRP"
-
-gdsc_druggenelin_summ <- gdsc_signif_grid_lineage
-gdsc_druggenelin_summ$Drug_Gene <- paste0(gdsc_druggenelin_summ$Drug, "_", gdsc_druggenelin_summ$Hugo_Symbol)
-gdsc_druggenelin_summ <- merge(g2p_druggenelin_p_tally, gdsc_druggenelin_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
-gdsc_druggenelin_summ$Drug_Gene_Lin <- paste0(gdsc_druggenelin_summ$Drug_Gene, "_", gdsc_druggenelin_summ$group_general_lineage_name)
-gdsc_druggenelin_summ$n <- ifelse(is.na(gdsc_druggenelin_summ$n), 0, gdsc_druggenelin_summ$n)
-gdsc_druggenelin_summ$InG2P <- ifelse(gdsc_druggenelin_summ$n != 0, "Yes", "No")
-gdsc_druggenelin_summ$Dataset <- "GDSC"
-
-dgl_mut_grid_summ <- rbind(ccle_druggenelin_summ, ctrp_druggenelin_summ, gdsc_druggenelin_summ)
+g2p_dgl_mut_tally <- g2p %>% group_by(Drug_Gene, group_general_lineage_name) %>% tally()
+
+ccle_dgl_summ <- ccle_signif_grid_lineage
+ccle_dgl_summ$Drug_Gene <- paste0(ccle_dgl_summ$Drug, "_", ccle_dgl_summ$Hugo_Symbol)
+ccle_dgl_summ <- merge(g2p_dgl_mut_tally, ccle_dgl_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
+ccle_dgl_summ$Drug_Gene_Lin <- paste0(ccle_dgl_summ$Drug_Gene, "_", ccle_dgl_summ$group_general_lineage_name)
+ccle_dgl_summ$n <- ifelse(is.na(ccle_dgl_summ$n), 0, ccle_dgl_summ$n)
+ccle_dgl_summ$InG2P <- ifelse(ccle_dgl_summ$n != 0, "Yes", "No")
+ccle_dgl_summ$Dataset <- "CCLE"
+
+ctrp_dgl_summ <- ctrp_signif_grid_lineage
+ctrp_dgl_summ$Drug_Gene <- paste0(ctrp_dgl_summ$Drug, "_", ctrp_dgl_summ$Hugo_Symbol)
+ctrp_dgl_summ <- merge(g2p_dgl_mut_tally, ctrp_dgl_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
+ctrp_dgl_summ$Drug_Gene_Lin <- paste0(ctrp_dgl_summ$Drug_Gene, "_", ctrp_dgl_summ$group_general_lineage_name)
+ctrp_dgl_summ$n <- ifelse(is.na(ctrp_dgl_summ$n), 0, ctrp_dgl_summ$n)
+ctrp_dgl_summ$InG2P <- ifelse(ctrp_dgl_summ$n != 0, "Yes", "No")
+ctrp_dgl_summ$Dataset <- "CTRP"
+
+gdsc_dgl_summ <- gdsc_signif_grid_lineage
+gdsc_dgl_summ$Drug_Gene <- paste0(gdsc_dgl_summ$Drug, "_", gdsc_dgl_summ$Hugo_Symbol)
+gdsc_dgl_summ <- merge(g2p_dgl_mut_tally, gdsc_dgl_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
+gdsc_dgl_summ$Drug_Gene_Lin <- paste0(gdsc_dgl_summ$Drug_Gene, "_", gdsc_dgl_summ$group_general_lineage_name)
+gdsc_dgl_summ$n <- ifelse(is.na(gdsc_dgl_summ$n), 0, gdsc_dgl_summ$n)
+gdsc_dgl_summ$InG2P <- ifelse(gdsc_dgl_summ$n != 0, "Yes", "No")
+gdsc_dgl_summ$Dataset <- "GDSC"
+
+dgl_mut_grid_summ <- rbind(ccle_dgl_summ, ctrp_dgl_summ, gdsc_dgl_summ)
 ```
@@
 
-Mutation status summary stats:
-```{r}
+This section contains summary plots for the Wilcoxon tests and Pearson/Spearman correlations done for only level A G2P drug-gene associations (i.e.
+not the grid tests) and G2P genes in the case of the CRISPR dataset.
+
+#### CRISPR
+
+G2P genes with a significant effect on CERES score by mutation status, gene expression, and copy number. Summary plot using Pearson correlation coefficient for GE and CN:
+```{r fig.height=5, fig.width=12}
+crispr_res_mut <- select(crispr_signif_g2p_gene, Hugo_Symbol, p)
+crispr_res_mut$corr <- 0
+crispr_res_mut$Metric <- "Mutation Status"
+crispr_res_mut$p_log10 <- -log10(crispr_res_mut$p)
+subset(crispr_res_mut, p < 0.05)
+
+subset(crispr_pearson_res_GE, p < 0.05)
+subset(crispr_pearson_res_CN, p < 0.05)
+
+crispr_pearson_res <- rbind(crispr_pearson_res_GE, crispr_pearson_res_CN)
+crispr_pearson_res$Metric <- factor(crispr_pearson_res$Metric, levels = c("Gene Expression", "Copy Number"))
+crispr_pearson_res$p_log10 <- -log10(crispr_pearson_res$p)
+
+crispr_summ_res_mut_plot <- ggplot(data = subset(crispr_res_mut, p < 0.05)) +
+  facet_grid(~ Metric) +
+  scale_y_continuous(breaks = seq(0, 50, by = 5), labels = seq(0, 50, by = 5)) +
+  coord_cartesian(ylim = c(0, 50)) +
+  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
+  geom_label_repel(mapping = aes(y = p_log10, x = corr, label = Hugo_Symbol, color = Metric), force = 10, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
+  theme(legend.position = "none", panel.grid.major.x = element_blank(), panel.grid.minor.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(5.5, 1.5, 5.5, 5.5), "pt")) +
+  scale_color_manual(values = c("Mutation Status" = "darkorchid4")) +
+  labs(y = "-log10(p-value)")
+
+crispr_summ_res_pearson_plot <- ggplot(data = subset(crispr_pearson_res, p < 0.05)) +
+  facet_grid(~ Metric, scales = "free_x", space = "free") +
+  scale_y_continuous(breaks = seq(0, 50, by = 5), labels = seq(0, 50, by = 5)) +
+  scale_x_continuous(breaks = seq(-0.6, 0.3, by = 0.1), labels = formatC(seq(-0.6, 0.3, by = 0.1), digits = 2, format = "f")) +
+  coord_cartesian(ylim = c(0, 50)) +
+  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
+  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
+  geom_label_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Hugo_Symbol), force = 10, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
+  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
+  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
+  labs(x = "Pearson correlation coefficient (r)")
+
+crispr_genomic_features_pearson_summ_plot <- plot_grid(crispr_summ_res_mut_plot, crispr_summ_res_pearson_plot, align = "h", rel_widths = c(1, 5))
+crispr_genomic_features_pearson_summ_plot
+
+# ggsave("./plots/manuscript/crispr_genomic_features_pearson_summ_plot.png", crispr_genomic_features_pearson_summ_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
+```
+
+Summary plot using Spearman correlation coefficient for GE and CN:
+```{r fig.height=5, fig.width=12}
+subset(crispr_spearman_res_GE, p < 0.05)
+subset(crispr_spearman_res_CN, p < 0.05)
+
+crispr_spearman_res <- rbind(crispr_spearman_res_GE, crispr_spearman_res_CN)
+crispr_spearman_res$Metric <- factor(crispr_spearman_res$Metric, levels = c("Gene Expression", "Copy Number"))
+crispr_spearman_res$p_log10 <- -log10(crispr_spearman_res$p)
+
+crispr_summ_res_spearman_plot <- ggplot(data = subset(crispr_spearman_res, p < 0.05)) +
+  facet_grid(~ Metric, scales = "free_x", space = "free") +
+  scale_y_continuous(breaks = seq(0, 50, by = 5), labels = seq(0, 50, by = 5)) +
+  scale_x_continuous(breaks = seq(-0.6, 0.3, by = 0.1), labels = formatC(seq(-0.6, 0.3, by = 0.1), digits = 2, format = "f")) +
+  coord_cartesian(ylim = c(0, 50)) +
+  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
+  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
+  geom_label_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Hugo_Symbol), force = 10, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
+  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
+  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
+  labs(x = "Spearman's rank correlation coefficient (r_s)")
+
+crispr_genomic_features_spearman_summ_plot <- plot_grid(crispr_summ_res_mut_plot, crispr_summ_res_spearman_plot, align = "h", rel_widths = c(1, 5))
+crispr_genomic_features_spearman_summ_plot
+
+# ggsave("./plots/manuscript/crispr_genomic_features_spearman_summ_plot.png", crispr_genomic_features_spearman_summ_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
+```
+
+#### CCLE
+
+G2P drug-gene associations with a significant effect on AUC by mutation status, gene expression, and copy number. Summary plot using Pearson correlation coefficient for GE and CN:
+```{r fig.height=4, fig.width=12}
+ccle_res_mut <- select(ccle_signif_g2p, Drug_Gene, p)
+ccle_res_mut$corr <- 0
+ccle_res_mut$Metric <- "Mutation Status"
+ccle_res_mut$p_log10 <- -log10(ccle_res_mut$p)
+ccle_res_mut$Dataset <- "CCLE"
+
+ccle_pearson_res_GE <- select(filter(ccle_cor_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_GE, Pearson_Pval_GE, Dataset)
+colnames(ccle_pearson_res_GE) <- c("Drug_Gene", "corr", "p", "Dataset")
+ccle_pearson_res_GE$Metric <- "Gene Expression"
+subset(ccle_pearson_res_GE, p < 0.05)
+
+ccle_pearson_res_CN <- select(filter(ccle_cor_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_CN, Pearson_Pval_CN, Dataset)
+colnames(ccle_pearson_res_CN) <- c("Drug_Gene", "corr", "p", "Dataset")
+ccle_pearson_res_CN$Metric <- "Copy Number"
+subset(ccle_pearson_res_CN, p < 0.05)
+
+ccle_pearson_res_filt <- rbind(ccle_pearson_res_GE, ccle_pearson_res_CN)
+ccle_pearson_res_filt$Metric <- factor(ccle_pearson_res_filt$Metric, levels = c("Gene Expression", "Copy Number"))
+ccle_pearson_res_filt$p_log10 <- -log10(ccle_pearson_res_filt$p)
+
+ccle_summ_res_mut_plot <- ggplot(data = subset(ccle_res_mut, p < 0.05)) +
+  facet_grid(Dataset ~ Metric) +
+  scale_y_continuous(breaks = seq(0, 35, by = 5), labels = seq(0, 35, by = 5)) +
+  coord_cartesian(ylim = c(0, 35)) +
+  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
+  geom_label_repel(mapping = aes(y = p_log10, x = corr, label = Drug_Gene, color = Metric), force = 10, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
+  theme(legend.position = "none", panel.grid.major.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(5.5, 1.5, 5.5, 5.5), "pt"), strip.background.y = element_blank(), strip.text.y = element_blank()) +
+  scale_color_manual(values = c("Mutation Status" = "darkorchid4")) +
+  labs(y = "-log10(p-value)")
+
+ccle_summ_res_pearson_plot <- ggplot(data = subset(ccle_pearson_res_filt, p < 0.05)) +
+  facet_grid(Dataset ~ Metric) +
+  coord_cartesian(ylim = c(0, 35)) +
+  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
+  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
+  geom_label_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 10, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
+  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
+  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
+  labs(x = "Pearson correlation coefficient (r)")
+
+ccle_genomic_features_pearson_summ_plot <- plot_grid(ccle_summ_res_mut_plot, ccle_summ_res_pearson_plot, align = "h", rel_widths = c(1, 5))
+ccle_genomic_features_pearson_summ_plot
+
+# ggsave("./plots/manuscript/ccle_genomic_features_pearson_summ_plot.png", ccle_genomic_features_pearson_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
+```
+
+Summary plot using Spearman correlation coefficient for GE and CN:
+```{r fig.height=4, fig.width=12}
+ccle_spearman_res_GE <- select(filter(ccle_cor_res, InG2P == "Yes"), Drug_Gene, Spearman_Corr_GE, Spearman_Pval_GE, Dataset)
+colnames(ccle_spearman_res_GE) <- c("Drug_Gene", "corr", "p", "Dataset")
+ccle_spearman_res_GE$Metric <- "Gene Expression"
+subset(ccle_spearman_res_GE, p < 0.05)
+
+ccle_spearman_res_CN <- select(filter(ccle_cor_res, InG2P == "Yes"), Drug_Gene, Spearman_Corr_CN, Spearman_Pval_CN, Dataset)
+colnames(ccle_spearman_res_CN) <- c("Drug_Gene", "corr", "p", "Dataset")
+ccle_spearman_res_CN$Metric <- "Copy Number"
+subset(ccle_spearman_res_CN, p < 0.05)
+
+ccle_spearman_res_filt <- rbind(ccle_spearman_res_GE, ccle_spearman_res_CN)
+ccle_spearman_res_filt$Metric <- factor(ccle_spearman_res_filt$Metric, levels = c("Gene Expression", "Copy Number"))
+ccle_spearman_res_filt$p_log10 <- -log10(ccle_spearman_res_filt$p)
+
+ccle_summ_res_spearman_plot <- ggplot(data = subset(ccle_spearman_res_filt, p < 0.05)) +
+  facet_grid(Dataset ~ Metric) +
+  coord_cartesian(ylim = c(0, 35)) +
+  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
+  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
+  geom_label_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 10, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
+  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
+  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
+  labs(x = "Spearman's rank correlation coefficient (r_s)")
+
+ccle_genomic_features_spearman_summ_plot <- plot_grid(ccle_summ_res_mut_plot, ccle_summ_res_spearman_plot, align = "h", rel_widths = c(1, 5))
+ccle_genomic_features_spearman_summ_plot
+
+# ggsave("./plots/manuscript/ccle_genomic_features_spearman_summ_plot.png", ccle_genomic_features_spearman_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
+```
+
+#### CTRP
+
+G2P drug-gene associations with a significant effect on AUC by mutation status, gene expression, and copy number. Summary plot using Pearson correlation coefficient for GE and CN:
+```{r fig.height=4, fig.width=12}
+ctrp_res_mut <- select(ctrp_signif_g2p, Drug_Gene, p)
+ctrp_res_mut$corr <- 0
+ctrp_res_mut$Metric <- "Mutation Status"
+ctrp_res_mut$p_log10 <- -log10(ctrp_res_mut$p)
+ctrp_res_mut$Dataset <- "CTRP"
+
+ctrp_pearson_res_GE <- select(filter(ctrp_cor_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_GE, Pearson_Pval_GE, Dataset)
+colnames(ctrp_pearson_res_GE) <- c("Drug_Gene", "corr", "p", "Dataset")
+ctrp_pearson_res_GE$Metric <- "Gene Expression"
+subset(ctrp_pearson_res_GE, p < 0.05)
+
+ctrp_pearson_res_CN <- select(filter(ctrp_cor_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_CN, Pearson_Pval_CN, Dataset)
+colnames(ctrp_pearson_res_CN) <- c("Drug_Gene", "corr", "p", "Dataset")
+ctrp_pearson_res_CN$Metric <- "Copy Number"
+subset(ctrp_pearson_res_CN, p < 0.05)
+
+ctrp_pearson_res_filt <- rbind(ctrp_pearson_res_GE, ctrp_pearson_res_CN)
+ctrp_pearson_res_filt$Metric <- factor(ctrp_pearson_res_filt$Metric, levels = c("Gene Expression", "Copy Number"))
+ctrp_pearson_res_filt$p_log10 <- -log10(ctrp_pearson_res_filt$p)
+
+ctrp_summ_res_mut_plot <- ggplot(data = subset(ctrp_res_mut, p < 0.05)) +
+  facet_grid(Dataset ~ Metric) +
+  scale_y_continuous(breaks = seq(0, 35, by = 5), labels = seq(0, 35, by = 5)) +
+  coord_cartesian(ylim = c(0, 35)) +
+  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
+  geom_text_repel(mapping = aes(y = p_log10, x = corr, label = Drug_Gene, color = Metric), force = 15, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.9) +
+  theme(legend.position = "none", panel.grid.major.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(5.5, 1.5, 5.5, 5.5), "pt"), strip.background.y = element_blank(), strip.text.y = element_blank()) +
+  scale_color_manual(values = c("Mutation Status" = "darkorchid4")) +
+  labs(y = "-log10(p-value)")
+
+ctrp_summ_res_pearson_plot <- ggplot(data = subset(ctrp_pearson_res_filt, p < 0.05)) +
+  facet_grid(Dataset ~ Metric) +
+  coord_cartesian(ylim = c(0, 35)) +
+  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
+  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
+  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 10, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
+  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
+  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
+  labs(x = "Pearson correlation coefficient (r)")
+
+ctrp_genomic_features_pearson_summ_plot <- plot_grid(ctrp_summ_res_mut_plot, ctrp_summ_res_pearson_plot, align = "h", rel_widths = c(1, 5))
+ctrp_genomic_features_pearson_summ_plot
+
+# ggsave("./plots/manuscript/ctrp_genomic_features_pearson_summ_plot.png", ctrp_genomic_features_pearson_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
+```
+
+Summary plot using Spearman correlation coefficient for GE and CN:
+```{r fig.height=4, fig.width=12}
+ctrp_spearman_res_GE <- select(filter(ctrp_cor_res, InG2P == "Yes"), Drug_Gene, Spearman_Corr_GE, Spearman_Pval_GE, Dataset)
+colnames(ctrp_spearman_res_GE) <- c("Drug_Gene", "corr", "p", "Dataset")
+ctrp_spearman_res_GE$Metric <- "Gene Expression"
+subset(ctrp_spearman_res_GE, p < 0.05)
+
+ctrp_spearman_res_CN <- select(filter(ctrp_cor_res, InG2P == "Yes"), Drug_Gene, Spearman_Corr_CN, Spearman_Pval_CN, Dataset)
+colnames(ctrp_spearman_res_CN) <- c("Drug_Gene", "corr", "p", "Dataset")
+ctrp_spearman_res_CN$Metric <- "Copy Number"
+subset(ctrp_spearman_res_CN, p < 0.05)
+
+ctrp_spearman_res_filt <- rbind(ctrp_spearman_res_GE, ctrp_spearman_res_CN)
+ctrp_spearman_res_filt$Metric <- factor(ctrp_spearman_res_filt$Metric, levels = c("Gene Expression", "Copy Number"))
+ctrp_spearman_res_filt$p_log10 <- -log10(ctrp_spearman_res_filt$p)
+
+ctrp_summ_res_spearman_plot <- ggplot(data = subset(ctrp_spearman_res_filt, p < 0.05)) +
+  facet_grid(Dataset ~ Metric) +
+  coord_cartesian(ylim = c(0, 35)) +
+  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
+  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
+  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 20, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
+  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
+  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
+  labs(x = "Spearman's rank correlation coefficient (r_s)")
+
+ctrp_genomic_features_spearman_summ_plot <- plot_grid(ctrp_summ_res_mut_plot, ctrp_summ_res_spearman_plot, align = "h", rel_widths = c(1, 5))
+ctrp_genomic_features_spearman_summ_plot
+
+# ggsave("./plots/manuscript/ctrp_genomic_features_spearman_summ_plot.png", ctrp_genomic_features_spearman_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
+```
+
+#### GDSC
+
+G2P drug-gene associations with a significant effect on AUC by mutation status, gene expression, and copy number. Summary plot using Pearson correlation coefficient for GE and CN:
+```{r fig.height=4, fig.width=12}
+gdsc_res_mut <- select(gdsc_signif_g2p, Drug_Gene, p)
+gdsc_res_mut$corr <- 0
+gdsc_res_mut$Metric <- "Mutation Status"
+gdsc_res_mut$p_log10 <- -log10(gdsc_res_mut$p)
+gdsc_res_mut$Dataset <- "GDSC"
+
+gdsc_pearson_res_GE <- select(filter(gdsc_cor_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_GE, Pearson_Pval_GE, Dataset)
+colnames(gdsc_pearson_res_GE) <- c("Drug_Gene", "corr", "p", "Dataset")
+gdsc_pearson_res_GE$Metric <- "Gene Expression"
+subset(gdsc_pearson_res_GE, p < 0.05)
+
+gdsc_pearson_res_CN <- select(filter(gdsc_cor_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_CN, Pearson_Pval_CN, Dataset)
+colnames(gdsc_pearson_res_CN) <- c("Drug_Gene", "corr", "p", "Dataset")
+gdsc_pearson_res_CN$Metric <- "Copy Number"
+subset(gdsc_pearson_res_CN, p < 0.05)
+
+gdsc_pearson_res_filt <- rbind(gdsc_pearson_res_GE, gdsc_pearson_res_CN)
+gdsc_pearson_res_filt$Metric <- factor(gdsc_pearson_res_filt$Metric, levels = c("Gene Expression", "Copy Number"))
+gdsc_pearson_res_filt$p_log10 <- -log10(gdsc_pearson_res_filt$p)
+
+gdsc_summ_res_mut_plot <- ggplot(data = subset(gdsc_res_mut, p < 0.05)) +
+  facet_grid(Dataset ~ Metric) +
+  scale_y_continuous(breaks = seq(0, 16, by = 1), labels = seq(0, 16, by = 1)) +
+  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
+  geom_text_repel(mapping = aes(y = p_log10, x = corr, label = Drug_Gene, color = Metric), force = 15, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.9) +
+  theme(legend.position = "none", panel.grid.major.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(5.5, 1.5, 5.5, 5.5), "pt"), strip.background.y = element_blank(), strip.text.y = element_blank()) +
+  scale_color_manual(values = c("Mutation Status" = "darkorchid4")) +
+  labs(y = "-log10(p-value)")
+
+gdsc_summ_res_pearson_plot <- ggplot(data = subset(gdsc_pearson_res_filt, p < 0.05)) +
+  facet_grid(Dataset ~ Metric) +
+  scale_y_continuous(breaks = seq(0, 100, by = 10), labels = seq(0, 100, by = 10)) +
+  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
+  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
+  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 10, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
+  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
+  theme(legend.position = "none", axis.title.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
+  labs(x = "Pearson correlation coefficient (r)")
+
+gdsc_genomic_features_pearson_summ_plot <- plot_grid(gdsc_summ_res_mut_plot, gdsc_summ_res_pearson_plot, align = "h", rel_widths = c(1, 5))
+gdsc_genomic_features_pearson_summ_plot
+
+# ggsave("./plots/manuscript/gdsc_genomic_features_pearson_summ_plot.png", gdsc_genomic_features_pearson_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
+```
+
+Summary plot using Spearman correlation coefficient for GE and CN:
+```{r fig.height=4, fig.width=12}
+gdsc_spearman_res_GE <- select(filter(gdsc_cor_res, InG2P == "Yes"), Drug_Gene, Spearman_Corr_GE, Spearman_Pval_GE, Dataset)
+colnames(gdsc_spearman_res_GE) <- c("Drug_Gene", "corr", "p", "Dataset")
+gdsc_spearman_res_GE$Metric <- "Gene Expression"
+subset(gdsc_spearman_res_GE, p < 0.05)
+
+gdsc_spearman_res_CN <- select(filter(gdsc_cor_res, InG2P == "Yes"), Drug_Gene, Spearman_Corr_CN, Spearman_Pval_CN, Dataset)
+colnames(gdsc_spearman_res_CN) <- c("Drug_Gene", "corr", "p", "Dataset")
+gdsc_spearman_res_CN$Metric <- "Copy Number"
+subset(gdsc_spearman_res_CN, p < 0.05)
+
+gdsc_spearman_res_filt <- rbind(gdsc_spearman_res_GE, gdsc_spearman_res_CN)
+gdsc_spearman_res_filt$Metric <- factor(gdsc_spearman_res_filt$Metric, levels = c("Gene Expression", "Copy Number"))
+gdsc_spearman_res_filt$p_log10 <- -log10(gdsc_spearman_res_filt$p)
+
+gdsc_summ_res_spearman_plot <- ggplot(data = subset(gdsc_spearman_res_filt, p < 0.05)) +
+  facet_grid(Dataset ~ Metric) +
+  scale_y_continuous(breaks = seq(0, 50, by = 5), labels = seq(0, 50, by = 5)) +
+  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
+  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
+  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 20, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
+  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
+  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
+  labs(x = "Spearman's rank correlation coefficient (r_s)")
+
+gdsc_genomic_features_spearman_summ_plot <- plot_grid(gdsc_summ_res_mut_plot, gdsc_summ_res_spearman_plot, align = "h", rel_widths = c(1, 5))
+gdsc_genomic_features_spearman_summ_plot
+
+# ggsave("./plots/manuscript/gdsc_genomic_features_spearman_summ_plot.png", gdsc_genomic_features_spearman_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
+```
+
+#### Drug: Mut
+
+G2P drug-gene associations with a significant effect on AUC by mutation status:
+```{r fig.height=4, fig.width=8}
+all_mut_res <- rbind(ccle_res_mut, ctrp_res_mut, gdsc_res_mut)
+
+all_mut_summ_plot <- ggplot(data = subset(all_res_mut, p < 0.05)) +
+  facet_grid(~ Dataset) +
+  geom_point(aes(x = corr, y = p_log10, color = Dataset), alpha = 0.5) +
+  scale_y_continuous(breaks = seq(0, 12, by = 2), labels = seq(0, 12, by = 2)) +
+  scale_x_continuous(breaks = seq(0, 0.1, by = 0.1), labels = seq(0, 0.1, by = 0.1)) +
+  coord_cartesian(xlim = c(0, 0.05)) +
+  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Dataset, label = Drug_Gene), nudge_x = 0.05, direction = "y", hjust = 0, size = 2.5, segment.size = 0.1, segment.colour = "grey50", box.padding = 0.6) +
+  scale_color_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
+  theme(legend.position = "none", plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt"), panel.grid.major.x = element_blank(), panel.grid.minor.x = element_blank(), axis.title.x = element_blank(), axis.ticks.x = element_blank(), axis.text.x = element_blank()) +
+  labs(y = "-log10(p-value)")
+all_mut_summ_plot
+
+# ggsave("./plots/manuscript/all_mut_summ_plot.png", all_mut_summ_plot, device = "png", dpi = 450, width = 12, height = 6, units = "in")
+```
+
+#### Drug: GE and CN
+
+G2P drug-gene associations with a significant effect on AUC by gene expression and copy number:
+```{r fig.height=12, fig.width=12}
+all_pearson_res <- rbind(ccle_pearson_res_filt, ctrp_pearson_res_filt, gdsc_pearson_res_filt)
+all_pearson_summ_plot <- ggplot(data = subset(all_pearson_res, p < 0.05)) +
+  facet_grid(Dataset ~ Metric, scales = "free", space = "free") +
+  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
+  geom_point(aes(x = corr, y = p_log10, color = Dataset), alpha = 0.5) +
+  scale_y_continuous(breaks = seq(0, 60, by = 10), labels = seq(0, 60, by = 10)) +
+  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Dataset, label = Drug_Gene), force = 10, nudge_y = 3, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
+  scale_color_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
+  theme(legend.position = "none", plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
+  labs(x = "Pearson correlation coefficient (r)", y = "-log10(p-value)")
+all_pearson_summ_plot
+# ggsave("./plots/manuscript/all_pearson_summ_plot.png", all_pearson_summ_plot, device = "png", dpi = 450, width = 12, height = 10, units = "in")
+
+all_spearman_res <- rbind(ccle_spearman_res_filt, ctrp_spearman_res_filt, gdsc_spearman_res_filt)
+all_spearman_summ_plot <- ggplot(data = subset(all_spearman_res, p < 0.05)) +
+  facet_grid(Dataset ~ Metric, scales = "free", space = "free") +
+  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
+  geom_point(aes(x = corr, y = p_log10, color = Dataset), alpha = 0.5) +
+  scale_y_continuous(breaks = seq(0, 60, by = 10), labels = seq(0, 60, by = 10)) +
+  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Dataset, label = Drug_Gene), force = 10, nudge_y = 1, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
+  scale_color_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
+  theme(legend.position = "none", plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
+  labs(x = "Pearson correlation coefficient (r)", y = "-log10(p-value)")
+all_spearman_summ_plot
+# ggsave("./plots/manuscript/all_spearman_summ_plot.png", all_spearman_summ_plot, device = "png", dpi = 450, width = 12, height = 10, units = "in")
+```
+
+#### Drug: P-values
+
+```{r fig.height=6, fig.width=12}
+pval_summ_mut <- g2p_mut_all_summ
+pval_summ_mut$Measure <- "Mutation Status"
+pval_summ_mut$Drug_Gene_Ordered <- NULL
+
+pval_summ_ge <- select(g2p_cor, Drug_Gene, n, Pearson_Pval_GE, InG2P, Dataset)
+colnames(pval_summ_ge)[colnames(pval_summ_ge) == "Pearson_Pval_GE"] <- "p"
+pval_summ_ge$p_log10 <- -log10(pval_summ_ge$p)
+pval_summ_ge$Measure <- "Gene Expression"
+
+pval_summ_cn <- select(g2p_cor, Drug_Gene, n, Pearson_Pval_CN, InG2P, Dataset)
+colnames(pval_summ_cn)[colnames(pval_summ_cn) == "Pearson_Pval_CN"] <- "p"
+pval_summ_cn$p_log10 <- -log10(pval_summ_cn$p)
+pval_summ_cn$Measure <- "Copy Number"
+
+pval_summ <- rbind(pval_summ_mut, pval_summ_ge, pval_summ_cn)
+pval_summ$Measure <- factor(pval_summ$Measure, levels = c("Mutation Status", "Gene Expression", "Copy Number"))
+
+pval_summ_plot <- ggplot(data = pval_summ, aes(x = p_log10, y = n, color = Dataset, shape = Dataset, label = Drug_Gene)) +
+  facet_wrap(~ Measure, scales = "free_x") +
+  geom_point(alpha = 0.7) +
+  scale_color_manual(values = c("green3", "darkslategray4", "darkturquoise")) +
+  geom_text_repel(data = filter(pval_summ, n > 20 & Measure == "Mutation Status"), mapping = aes(x = p_log10, y = n, color = Dataset, label = Drug_Gene), direction = "y", nudge_x = 9, hjust = 0, size = 2.5, segment.size = 0.1, segment.colour = "grey50", box.padding = 0.6, show.legend = FALSE) +
+  geom_text_repel(data = filter(pval_summ, n > 20 & Measure == "Gene Expression"), mapping = aes(x = p_log10, y = n, color = Dataset, label = Drug_Gene), direction = "y", nudge_x = 50, hjust = 0, size = 2.5, segment.size = 0.1, segment.colour = "grey50", box.padding = 0.6, show.legend = FALSE) +
+  geom_text_repel(data = filter(pval_summ, n > 20 & Measure == "Copy Number"), mapping = aes(x = p_log10, y = n, color = Dataset, label = Drug_Gene), direction = "y", nudge_x = 20, hjust = 0, size = 2.5, segment.size = 0.1, segment.colour = "grey50", box.padding = 0.6, show.legend = FALSE) +
+  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
+  labs(x = "-log10(p-value)", y = "Number of level A G2P associations") +
+  theme(legend.position = "bottom")
+pval_summ_plot
+
+# ggsave("./plots/manuscript/all_pval_summ_plot.png", pval_summ_plot, device = "png", dpi = 450, width = 12, height = 6, units = "in")
+```
+
+#### Summary stats
+
+```{r}
+# Mutation status
 g2p_druggene_all_summ_stats <- g2p_druggene_all_summ
@@
 g2p_druggene_all_summ_stats <- g2p_druggene_all_summ_stats %>% drop_na(p) %>% group_by(Dataset, InG2P) %>% summarize(p_mean = round(mean(p), 2), p_sd = round(sd(p), 2), n = sum(n_true), n_signif = sum(p < 0.05), n_sig_perc = n_signif / n * 100)
-```
-
-Pearson summary stats:
-```{r fig.height=4, fig.width=5}
+
+# Pearson correlations
 g2p_mut_cor_stats <- g2p_mut_cor
@@
 
-```{r fig.height=6, fig.width=12}
-pval_summ_mut <- g2p_mut_all_summ
-pval_summ_mut$Measure <- "Mutation Status"
-pval_summ_mut$Drug_Gene_Ordered <- NULL
-
-pval_summ_ge <- select(g2p_cor, Drug_Gene, n, Pearson_Pval_GE, InG2P, Dataset)
-colnames(pval_summ_ge)[colnames(pval_summ_ge) == "Pearson_Pval_GE"] <- "p"
-pval_summ_ge$p_log10 <- -log10(pval_summ_ge$p)
-pval_summ_ge$Measure <- "Gene Expression"
-
-pval_summ_cn <- select(g2p_cor, Drug_Gene, n, Pearson_Pval_CN, InG2P, Dataset)
-colnames(pval_summ_cn)[colnames(pval_summ_cn) == "Pearson_Pval_CN"] <- "p"
-pval_summ_cn$p_log10 <- -log10(pval_summ_cn$p)
-pval_summ_cn$Measure <- "Copy Number"
-
-pval_summ <- rbind(pval_summ_mut, pval_summ_ge, pval_summ_cn)
-pval_summ$Measure <- factor(pval_summ$Measure, levels = c("Mutation Status", "Gene Expression", "Copy Number"))
-
-pval_summ_plot <- ggplot(data = pval_summ, aes(x = p_log10, y = n, color = Dataset, shape = Dataset, label = Drug_Gene)) +
-  facet_wrap(~ Measure, scales = "free_x") +
-  geom_point(alpha = 0.7) +
-  scale_color_manual(values = c("green3", "darkslategray4", "darkturquoise")) +
-  geom_text_repel(data = filter(pval_summ, n > 20 & Measure == "Mutation Status"), mapping = aes(x = p_log10, y = n, color = Dataset, label = Drug_Gene), direction = "y", nudge_x = 9, hjust = 0, size = 2.5, segment.size = 0.1, segment.colour = "grey50", box.padding = 0.6, show.legend = FALSE) +
-  geom_text_repel(data = filter(pval_summ, n > 20 & Measure == "Gene Expression"), mapping = aes(x = p_log10, y = n, color = Dataset, label = Drug_Gene), direction = "y", nudge_x = 50, hjust = 0, size = 2.5, segment.size = 0.1, segment.colour = "grey50", box.padding = 0.6, show.legend = FALSE) +
-  geom_text_repel(data = filter(pval_summ, n > 20 & Measure == "Copy Number"), mapping = aes(x = p_log10, y = n, color = Dataset, label = Drug_Gene), direction = "y", nudge_x = 20, hjust = 0, size = 2.5, segment.size = 0.1, segment.colour = "grey50", box.padding = 0.6, show.legend = FALSE) +
-  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
-  labs(x = "-log10(p-value)", y = "Number of level A G2P associations") +
-  theme(legend.position = "bottom")
-pval_summ_plot
-
-# ggsave("./plots/manuscript/all_pval_summ_plot.png", pval_summ_plot, device = "png", dpi = 450, width = 12, height = 6, units = "in")
-```
+#### CTRP example derivation
 
@@
 
-## DO THIS: Cell line overlap
+## Cell line overlap
 

### 2018-12-18 manuscript.Rmd
added g2p lin/non-g2p lin analyses

@@
 g2p_druggenes <- unique(g2p_filt$Drug_Gene[!is.na(g2p_filt$Drug_Gene)])
-g2p_genes <- unique(sapply(strsplit(g2p_drug_genes, "_", fixed = TRUE), function(x) x[2]))
-g2p_drugs <- unique(sapply(strsplit(g2p_drug_genes, "_", fixed = TRUE), function(x) x[1]))
+g2p_genes <- unique(sapply(strsplit(g2p_druggenes, "_", fixed = TRUE), function(x) x[2]))
+g2p_drugs <- unique(sapply(strsplit(g2p_druggenes, "_", fixed = TRUE), function(x) x[1]))
 g2p_druggenes
@@
 # Filter drug screen datasets for G2P drug-gene associations
-ccle_data_g2p <- filter(ccle_data_ptmuts, Drug_Gene %in% g2p_drug_genes)
+ccle_data_g2p <- filter(ccle_data_ptmuts, Drug_Gene %in% g2p_druggenes)
 ccle_data_g2p$Mutation_Status_Nonsilent <- factor(ccle_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-ctrp_data_g2p <- filter(ctrp_data_ptmuts, Drug_Gene %in% g2p_drug_genes)
+ctrp_data_g2p <- filter(ctrp_data_ptmuts, Drug_Gene %in% g2p_druggenes)
 ctrp_data_g2p$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-gdsc_data_g2p <- filter(gdsc_data_ptmuts, Drug_Gene %in% g2p_drug_genes)
+gdsc_data_g2p <- filter(gdsc_data_ptmuts, Drug_Gene %in% g2p_druggenes)
 gdsc_data_g2p$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
@@
 
-## Lineage-agnostic
-
-### Mut
+# PANCANCER
+
+--------------------------------------------------------------------------------
+
+## Mut
 
@@
 
-ctrp_mut_summ <- merge(g2p_druggene_tally, ctrp_signif_g2p_grid[, c("`Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
+ctrp_mut_summ <- merge(g2p_druggene_tally, ctrp_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
 ctrp_mut_summ$n <- ifelse(is.na(ctrp_mut_summ$n), 0, ctrp_mut_summ$n)
@@
   scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
-  geom_text_repel(data = subset(g2p_druggene_all_summ, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
-  geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = 0.5, y = 115, label = Test_Results_p)) +
+  geom_text_repel(data = subset(g2p_mut_all_summ, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
+  geom_text(data = g2p_mut_all_summ_text, mapping = aes(x = 0.5, y = 115, label = Test_Results_p)) +
   labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations") +
@@
   scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
-  geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = 0.5, y = 115, label = Test_Results_p)) +
+  geom_text(data = g2p_mut_all_summ_text, mapping = aes(x = 0.5, y = 115, label = Test_Results_p)) +
   labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations") +
@@
 
-### GE
-
-#### Pearson
+## GE
+
+### Pearson
 
@@
 
-#### Spearman
+### Spearman
 
@@
 
-### CN
-
-#### Pearson
+## CN
+
+### Pearson
 
@@
 
-## Lineage-grouped
-
-### Mut: Grid
+# BY LINEAGE
+
+--------------------------------------------------------------------------------
+
+## Mut: Grid
 
@@
 
-### GE/CN: G2P
+## GE/CN: G2P
 
@@
 
-### GE/CN: Grid
+## GE/CN: Grid
 
@@
 
-## Mut/GE/CN
-
-### Lineage-agnostic
+# MUT/GE/CN
+
+--------------------------------------------------------------------------------
+
+## Pancancer
 
@@
 
-#### CRISPR
+### CRISPR
 
@@
 
-#### CCLE
+### CCLE
 
@@
 
-#### CTRP
+### CTRP
 
@@
 
-#### GDSC
+### GDSC
 
@@
 
-#### Drug: Mut
+### Drug: Mut
 
@@
 
-all_mut_summ_plot <- ggplot(data = subset(all_res_mut, p < 0.05)) +
+all_mut_summ_plot <- ggplot(data = subset(all_mut_res, p < 0.05)) +
   facet_grid(~ Dataset) +
@@
 
-#### Drug: GE and CN
+### Drug: GE and CN
 
@@
 
-#### Drug: P-values
+### Drug: P-values
 
@@
 
-#### Summary stats
+### Summary stats
 
@@
 # Mutation status
-g2p_druggene_all_summ_stats <- g2p_druggene_all_summ
-g2p_druggene_all_summ_stats$n_true <- TRUE
-g2p_druggene_all_summ_stats <- g2p_druggene_all_summ_stats %>% drop_na(p) %>% group_by(Dataset, InG2P) %>% summarize(p_mean = round(mean(p), 2), p_sd = round(sd(p), 2), n = sum(n_true), n_signif = sum(p < 0.05), n_sig_perc = n_signif / n * 100)
+g2p_mut_all_summ_stats <- g2p_mut_all_summ
+g2p_mut_all_summ_stats$n_true <- TRUE
+g2p_mut_all_summ_stats <- g2p_mut_all_summ_stats %>% drop_na(p) %>% group_by(Dataset, InG2P) %>% summarize(p_mean = round(mean(p), 2), p_sd = round(sd(p), 2), n = sum(n_true), n_signif = sum(p < 0.05), n_sig_perc = n_signif / n * 100)
 
 # Pearson correlations
-g2p_mut_cor_stats <- g2p_mut_cor
-g2p_mut_cor_stats$n_true <- TRUE
-g2p_mut_cor_stats <- g2p_mut_cor_stats %>% group_by(Dataset, InG2P) %>% drop_na() %>% summarize(
+g2p_cor_stats <- g2p_cor
+g2p_cor_stats$n_true <- TRUE
+g2p_cor_stats <- g2p_cor_stats %>% group_by(Dataset, InG2P) %>% drop_na() %>% summarize(
           ge_mean = round(mean(Pearson_GE_Abs), 5),
@@
 
-#### CTRP example derivation
+### CTRP example derivation
 
@@
 
-### Lineage-grouped
-
-Deriving n for Bonferroni correction:
-```{r}
+## By lineage
+
+### Kolmogorov-Smirnov tests
+
+```{r}
+MakeCorrResSummaryTable <- function(df_list, dataset_name) {
+  res_full <- data.frame(matrix(ncol = 8, nrow = 0))
+  for(i in 1:length(df_list)) {
+    corr_res <- df_list[[i]] %>% group_by(G2P_DGL) %>% summarize(Dataset = dataset_name,
+                Drug_Gene = names(df_list)[i],
+                Lineages = paste(as.character(unique(group_general_lineage_name)), collapse = ", "),
+                N_Lineages = length(as.character(unique(group_general_lineage_name))),
+                Pearson_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
+                Pearson_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$estimate,
+                Spearman_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
+                Spearman_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$estimate)
+    corr_res <- merge(corr_res, compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, data = df_list[[i]], group.by = "G2P_DGL", method = "wilcox.test")[, c("G2P_DGL", "p")], by = "G2P_DGL", all = TRUE)
+    corr_res$Mut_Signif <- ifelse(corr_res$p < 0.05, 1, 0)
+    res_full <- rbind(res_full, corr_res)
+  }
+  return(res_full)
+}
+```
+
+```{r}
+ccle_data_g2p$G2P_DGL <- ifelse(ccle_data_g2p$Drug_Gene_Lin %in% g2p_dgls, "Yes", "No")
+ccle_data_g2p_split <- split(ccle_data_g2p, f = ccle_data_g2p$Drug_Gene)
+ccle_corr_all <- MakeCorrResSummaryTable(ccle_data_g2p_split, dataset_name = "CCLE")
+
+ctrp_data_g2p$G2P_DGL <- ifelse(ctrp_data_g2p$Drug_Gene_Lin %in% g2p_dgls, "Yes", "No")
+ctrp_data_g2p_split <- split(ctrp_data_g2p, f = ctrp_data_g2p$Drug_Gene)
+ctrp_corr_all <- MakeCorrResSummaryTable(ctrp_data_g2p_split, dataset_name = "CTRP")
+
+gdsc_data_g2p$G2P_DGL <- ifelse(gdsc_data_g2p$Drug_Gene_Lin %in% g2p_dgls, "Yes", "No")
+gdsc_data_g2p_split <- split(gdsc_data_g2p, f = gdsc_data_g2p$Drug_Gene)
+gdsc_corr_all <- MakeCorrResSummaryTable(gdsc_data_g2p_split, dataset_name = "GDSC")
+
+g2p_corr_all <- rbind(ccle_corr_all, ctrp_corr_all, gdsc_corr_all)
+```
+
+```{r}
+G2PCorr_KStest <- function(dataset, dataset_name) {
+  Metric <- colnames(dataset)[6:9]
+  D_stat <- NULL
+  pval <- NULL
+  signif <- NULL
+
+  yes <- dataset[dataset$G2P_DGL == "Yes",]
+  no <- dataset[dataset$G2P_DGL == "No",]
+
+  for(i in 6:9) {
+    # print(yes[[colnames(yes)[i]]])
+    # print(no[[colnames(no)[i]]])
+    test <- ks.test(yes[[colnames(yes)[i]]], no[[colnames(no)[i]]])
+    D_stat <- c(D_stat, test$statistic)
+    pval <- c(pval, test$p.value)
+    signif <- c(signif, ifelse(test$p.value < 0.001, "***", ifelse(test$p.value < 0.01, "**", ifelse(test$p.value < 0.05, "*", NA))))
+  }
+  df <- data.frame(Metric, D_stat, pval, signif)
+  df$Dataset <- dataset_name
+  return(df)
+}
+```
+
+```{r}
+ccle_corr_stats <- G2PCorr_KStest(ccle_corr_all, "CCLE")
+ctrp_corr_stats <- G2PCorr_KStest(ctrp_corr_all, "CTRP")
+gdsc_corr_stats <- G2PCorr_KStest(gdsc_corr_all, "GDSC")
+g2p_corr_stats <- rbind(ccle_corr_stats, ctrp_corr_stats, gdsc_corr_stats)
+g2p_corr_stats
+
+g2p_mut_stats <- g2p_corr_all %>% group_by(Dataset, G2P_DGL) %>% drop_na(Mut_Signif) %>% summarize(N_Signif_Muts = sum(Mut_Signif),
+                                                                                                   Total_Tests = length(Mut_Signif),
+                                                                                                   Perc_Signif = N_Signif_Muts / Total_Tests * 100)
+g2p_mut_stats
+```
+
+### Grid t-test summaries
+
+Faceted lineage summaries:
+```{r fig.height=4, fig.width=12}
 ttest_summ_res_mut <- dgl_mut_g2p_grid_ttest_res_list[, c("p_value", "Dataset", "group_general_lineage_name")]
 ttest_summ_res_mut$Metric <- "Mutation Status"
-mut_alphas <- ttest_summ_res_mut %>% drop_na(p_value) %>% group_by(Dataset) %>% tally()
-mut_alphas$alpha_adj <- 0.05 / mut_alphas$n
 
@@
 ttest_summ_res_ge$Metric <- "Gene Expression"
-ge_alphas <- ttest_summ_res_ge %>% drop_na(p_value) %>% group_by(Dataset) %>% tally()
-ge_alphas$alpha_adj <- 0.05 / ge_alphas$n
 
@@
 ttest_summ_res_cn$Metric <- "Copy Number"
-cn_alphas <- ttest_summ_res_cn %>% drop_na(p_value) %>% group_by(Dataset) %>% tally()
-cn_alphas$alpha_adj <- 0.05 / cn_alphas$n
 
@@
 ttest_summ_res$Metric <- factor(ttest_summ_res$Metric, levels = c("Mutation Status", "Gene Expression", "Copy Number"))
-```
-
-Faceted lineage summaries:
-```{r fig.height=4, fig.width=12}
+
 ttest_mut_summ_facet <- ggplot(data = ttest_summ_res, aes(x = p_value, fill = Dataset, color = Dataset)) +
@@
 # plot.margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
-
 ttest_mut_summ_plot <- ggplot(data = dgl_mut_g2p_grid_ttest_res_list, aes(x = p_value)) +
@@
 
-# BOXPLOTS
+# OLD: BOXPLOTS
 
@@
 
-# CRISPR: POINT MUT MAPPING
+# OLD: CRISPR POINT MUT MAPPING
 

### 2018-12-19 manuscript.Rmd
set up papaja manuscript.Rmd for reproducibility

--- 2018-12-17 manuscript.Rmd
@@
 ---
-title: "Manuscript"
-author: "Sally Claridge"
-date: "`r format(Sys.time(), '%d %B %Y')`"
-output:
-  html_document:
-    theme: cerulean
-    number_sections: true
-    toc: true
-    toc_depth: 3
-    toc_float:
-      collapsed: true
-    code_folding: hide
-    pandoc_args: [
-      "+RTS", "-K2048m",
-      "-RTS"
-    ]
+title             : "Manuscript"
+shorttitle        : "Subtitle"
+
+author: 
+  - name          : "Sally E. Claridge"
+    affiliation   : "1"
+  - name          : "Daniel M. Charytonowicz"
+    affiliation   : "1"
+  - name          : "Adam A. Margolin"
+    affiliation   : "1, 2"
+    corresponding : yes    # Define only one corresponding author
+    address       : "Icahn School of Medicine at Mount Sinai, Deparment of Genetics and Genomic Sciences, One Gustave L. Levy Place, Box 1498, New York, NY 10029"
+    email         : "adam.margolin@mssm.edu"
+
+affiliation:
+  - id            : "1"
+    institution   : "Department of Genetics and Genomic Sciences, Icahn Institute for Data Science and Genomic Technology, Icahn School of Medicine at Mount Sinai, New York, NY"
+  - id            : "2"
+    institution   : "Cancer Target Discovery and Development Network (Oregon Health and Science University, Portland, OR), National Cancer Institute, National Institutes of Health"
+
+authornote: |
+  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
+
+  Enter author note here.
+
+abstract: |
+  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
+
+  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
+
+  One sentence clearly stating the **general problem** being addressed by  this particular study.
+
+  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
+
+  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
+
+  One or two sentences to put the results into a more **general context**.
+
+  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
+
+  <!-- https://tinyurl.com/ybremelq -->
+
+keywords          : "keywords"
+wordcount         : "X"
+
+bibliography      : ["manuscript.bib"]
+
+floatsintext      : no
+figurelist        : no
+tablelist         : no
+footnotelist      : no
+linenumbers       : yes
+mask              : no
+draft             : no
+
+documentclass     : "apa6"
+classoption       : "man"
+biblio-style      : "apa"
+output            :
+  papaja::apa6_pdf:
+    citation_package: biblatex
 ---
 
-Analysis of the Broad's Avana CRISPR (Broad Institute Cancer Dependency Map 2018, Meyers et al.
-2017) and the Broad and Dana-Farber Cancer Institite's Achilles shRNA (MacFarland et al.
-2018, Data Science 2018).
-
-The Avana screen produced results using [CERES](https://depmap.org/ceres/) (Meyers et al.
-2017) ([GitHub](https://github.com/cancerdatasci/ceres)), which generates gene dependency scores from sgRNA depletion scores from gene essentiality screens and eliminates bias arising from the effect of copy number variation on Cas9 DNA cleavage.
-The lower the CERES score, the higher the likelihood that the gene is essential in the associated cell line.
-Scores are scaled per cell line such that a score of 0 is the median effect of nonessential genes and -1 is the median effect of common core essential genes.
-
-All annotation files (copy number, mutation status, and gene expression) (Consortium and Consortium 2015, Barretina et al.
-2012) were downloaded from the [DepMap Data Portal](https://depmap.org/portal/download/).
-
-# SET UP
-
---------------------------------------------------------------------------------
-
-```{r setup, include=FALSE}
-set.seed(1234)
-knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
-# num_cores <- parallel::detectCores()
-options(mc.cores = parallel::detectCores(), expressions = 5e5)
+```{r setup, include = FALSE}
+library("papaja")
+# install.packages("tinytex")
+# tinytex::install_tinytex()
+# install.packages("citr")
 ```
 
-Edited `.Renviron` to avoid "Error: memory exhausted (limit reached?)" when melting the GE dataset, as per the suggestion from [StackOverflow](https://stackoverflow.com/questions/51295402/r-on-macos-error-vector-memory-exhausted-limit-reached)
-```
-cd ~
-touch .Renviron
-open .Renviron
-# Added following line to .Renviron:
-R_MAX_VSIZE=100Gb
+```{r analysis-preferences}
+# Seed for random number generation
+set.seed(42)
+knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
 ```
 
-```{r}
-library(bsselectR)
-library(cowplot)
-theme_set(theme_light())
-library(data.table)
-library(ggpubr)
-library(ggrepel)
-library(ggsignif)
-library(gplots)
-library(gridExtra)
-library(htmlwidgets)
-library(kableExtra)
-library(plotly)
-library(reshape2)
-library(scales)
-library(tidyverse)
-library(VennDiagram)
+[@aksoy2017]
+
+# Introduction
+
+# Results
+
+# Discussion
+
+\newpage
+
+# Methods
+
+We used `r cite_r("manuscript_r_references.bib")` for all our analyses.
+
+\newpage
+
+# References
+
+```{r create_r-references}
+r_refs(file = "manuscript_r_references.bib")
 ```
 
-# FUNCTIONS {.tabset .tabset-fade .tabset-pills}
+\begingroup
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
 
---------------------------------------------------------------------------------
+Finally, the APA guidelines require a note at the start of the reference section that explains what an asterisk means. This note can be added at the end of the document as follows.
 
-## Significance thresholding
-
-```{r}
-adj_signif <- function(df) {
-  # Takes df from compare_means and creates a signif code column for adjusted p-vals
-  df$p.signif <- ifelse(df$p.signif == "ns", NA, df$p.signif)
-  df$p.signif.adj <- ifelse(df$p.adj <= 0.0001, "****",
-                     ifelse(df$p.adj <= 0.001, "***",
-                     ifelse(df$p.adj <= 0.01, "**",
-                     ifelse(df$p.adj <= 0.05, "*", NA))))
-  df$p.short <- formatC(df$p, format = "g", digits =  2)
-  df$p.adj.short <- formatC(df$p.adj, format = "g", digits =  2)
-
-  return(df)
-}
-```
-
-## Wilcoxon tests by drug
-
-```{r}
-WilcoxonByDrug <- function(drug, dataset, data_name, grouping_var) {
-  if(grouping_var == "lineage") {
-    grouper <- c("Hugo_Symbol", "group_general_lineage_name")
-  }
-  else if(grouping_var == "gene") {
-    grouper <- "Hugo_Symbol"
-  }
-  use_data <- filter(dataset, Drug == drug)
-  sig <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = grouper, data = use_data, method = "wilcox.test", p.adjust.method = "BH")
-  sig <- adj_signif(sig)
-  sig <- sig[order(sig$p),]
-  sig$Drug <- drug
-  sig$Dataset <- toupper(data_name)
-  return(sig)
-}
-
-# WilcoxonByDrugAllGenes <- function(melt_file, grid_file, data_name) {
-#   druglist <- as.character(unique(melt_file$Drug))
-#   sig_df <- NULL
-#   for(i in 1:length(druglist)) {
-#     print(paste0("Current drug in process: ", druglist[i], " (drug ", i, " of ", length(druglist), ")."))
-#     flush.console()
-#     melted <- filter(melt_file, Drug == druglist[i])
-#     use_data <- merge(grid_file, melted, by = "accession_id", all.x = TRUE)
-#     use_data <- merge(use_data, ccl_converter, by = "accession_id", all.x = TRUE)
-#     use_data <- merge(use_data, maf_df, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
-#     use_data$Mutation_Status_Nonsilent <- ifelse(is.na(use_data$Mutation_Status_Nonsilent), "Wildtype", use_data$Mutation_Status_Nonsilent)
-#     use_data$Hugo_Symbol <- factor(use_data$Hugo_Symbol)
-#     use_data$AUC <- as.numeric(use_data$AUC)
-#     use_data <- filter(use_data, !is.na(use_data$AUC))
-#     use_data$Drug_Gene <- paste0(use_data$Drug, "_", use_data$Hugo_Symbol)
-#     use_data_ptmuts <- filter(use_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
-#     use_data_ptmuts$Keep_PtMut_Tests <- ifelse(use_data_ptmuts$Reference_Allele_Length == 1 | is.na(use_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(use_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
-#     use_data_ptmuts <- filter(use_data_ptmuts, Keep_PtMut_Tests == TRUE)
-#     
-#     sig <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = "Hugo_Symbol", data = use_data_ptmuts, method = "wilcox.test", p.adjust.method = "BH")
-#     sig <- adj_signif(sig)
-#     sig <- sig[order(sig$p),]
-#     sig <- filter(sig, p <= 0.05)
-#     sig$Drug <- druglist[i]
-#     sig$Dataset <- toupper(data_name)
-#     sig_df <- rbind(sig_df, sig)
-#   }
-#   return(sig_df)
-# }
-```
-
-## Pearson correlation by lineage
-```{r}
-PearsonByLineage <- function(lin, dataset, variable) {
-  use_data <- filter(dataset, group_general_lineage_name == lin)
-  if(variable == "GE") {
-    use_data <- filter(use_data, !is.na(RPKM))
-    use_data_summ <- use_data %>% count(Drug_Gene)
-    use_data_summ <- filter(use_data_summ, n >= 3) # cor.test requires at least 3 non-NA data points
-    use_data_filt <- filter(use_data, Drug_Gene %in% as.character(unique(use_data_summ$Drug_Gene)))
-    if(nrow(use_data_filt) > 0) {
-      pearson_res <- use_data_filt %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$estimate, Pearson_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$p.value)
-      pearson_res <- merge(g2p_druggene_tally, pearson_res, all.y = TRUE)
-      pearson_res$group_general_lineage_name <- lin
-      pearson_res$Pearson_GE_Abs <- abs(pearson_res$Pearson_Corr_GE)
-      pearson_res$Pearson_GE_Sign <- ifelse(sign(pearson_res$Pearson_Corr_GE) == 1, "+",
-                                              ifelse(sign(pearson_res$Pearson_Corr_GE) == -1, "-", "0"))
-      return(pearson_res)
-    }
-  }
-  else if(variable == "CN") {
-    use_data <- filter(use_data, !is.na(CN))
-    use_data_summ <- use_data %>% count(Drug_Gene)
-    use_data_summ <- filter(use_data_summ, n >= 3) # cor.test requires at least 3 non-NA data points
-    use_data_filt <- filter(use_data, Drug_Gene %in% as.character(unique(use_data_summ$Drug_Gene)))
-    if(nrow(use_data_filt) > 0) {
-      pearson_res <- use_data_filt %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$estimate, Pearson_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$p.value)
-      pearson_res <- merge(g2p_druggene_tally, pearson_res, all.y = TRUE)
-      pearson_res$group_general_lineage_name <- lin
-      pearson_res$Pearson_CN_Abs <- abs(pearson_res$Pearson_Corr_CN)
-      pearson_res$Pearson_CN_Sign <- ifelse(sign(pearson_res$Pearson_Corr_CN) == 1, "+",
-                                              ifelse(sign(pearson_res$Pearson_Corr_CN) == -1, "-", "0"))
-      return(pearson_res)
-    }
-  }
-}
-```
-
-## Save widget to new directory
-```{r}
-saveWidgetFix <- function (widget , file, ...) {
-  ## A wrapper to saveWidget which compensates for arguable BUG in
-  ## saveWidget which requires `file` to be in current working
-  ## directory.
-  wd <- getwd()
-  on.exit(setwd(wd))
-  outDir <- dirname(file)
-  file <- basename(file)
-  setwd(outDir);
-  saveWidget(widget, file = file,...)
-}
-```
-
-## Make lineage mut plots
-
-```{r}
-MutPlotsByLineage <- function(lineage_name) {
-
-  use_data <- filter(dgl_mut_grid_summ, group_general_lineage_name == lineage_name)
-  use_data$Dataset <- factor(use_data$Dataset, levels = c("CCLE", "CTRP", "GDSC"))
-  ticker <- 0
-
-  use_data_ccle <- filter(use_data, Dataset == "CCLE")
-  use_data_ccle_summ <- use_data_ccle %>% count(InG2P)
-  ccle_lin_p_ttest <- data.frame(statistic = NA,
-                                 parameter =  NA,
-                                 p.value = NA)
-  if(nrow(use_data_ccle_summ) <= 1) {
-    ccle_lin_p_ttest_res <-  NA
-    ticker <- ticker + 1
-    }
-  else if(use_data_ccle_summ[use_data_ccle_summ$InG2P == "Yes",]$nn < 2) { ccle_lin_p_ttest_res <-  NA }
-  else if(use_data_ccle_summ[use_data_ccle_summ$InG2P == "Yes",]$nn >= 2) {
-    ccle_lin_p_ttest <- t.test(use_data_ccle$p ~ use_data_ccle$InG2P)
-    ccle_lin_p_ttest_res <- paste0("t(", trunc(ccle_lin_p_ttest$parameter), ") = ", round(ccle_lin_p_ttest$statistic, 2), ", p = ", round(ccle_lin_p_ttest$p.value, 3))
-  }
-
-  use_data_ctrp <- filter(use_data, Dataset == "CTRP")
-  use_data_ctrp_summ <- use_data_ctrp %>% count(InG2P)
-  ctrp_lin_p_ttest <- data.frame(statistic = NA,
-                                 parameter =  NA,
-                                 p.value = NA)
-  if(nrow(use_data_ctrp_summ) <= 1) {
-    ctrp_lin_p_ttest_res <-  NA
-    ticker <- ticker + 1
-    }
-  else if(use_data_ctrp_summ[use_data_ctrp_summ$InG2P == "Yes",]$nn < 2) { ctrp_lin_p_ttest_res <-  NA }
-  else if(use_data_ctrp_summ[use_data_ctrp_summ$InG2P == "Yes",]$nn >= 2) {
-    ctrp_lin_p_ttest <- t.test(use_data_ctrp$p ~ use_data_ctrp$InG2P)
-    ctrp_lin_p_ttest_res <- paste0("t(", trunc(ctrp_lin_p_ttest$parameter), ") = ", round(ctrp_lin_p_ttest$statistic, 2), ", p = ", round(ctrp_lin_p_ttest$p.value, 3))
-  }
-
-  use_data_gdsc <- filter(use_data, Dataset == "GDSC")
-  use_data_gdsc_summ <- use_data_gdsc %>% count(InG2P)
-  gdsc_lin_p_ttest <- data.frame(statistic = NA,
-                                 parameter =  NA,
-                                 p.value = NA)
-  if(nrow(use_data_gdsc_summ) <= 1) {
-    gdsc_lin_p_ttest_res <-  NA
-    ticker <- ticker + 1
-    }
-  else if(use_data_gdsc_summ[use_data_gdsc_summ$InG2P == "Yes",]$nn < 2) { gdsc_lin_p_ttest_res <-  NA }
-  else if(use_data_gdsc_summ[use_data_gdsc_summ$InG2P == "Yes",]$nn >= 2) {
-    gdsc_lin_p_ttest <- t.test(use_data_gdsc$p ~ use_data_gdsc$InG2P)
-    gdsc_lin_p_ttest_res <- paste0("t(", trunc(gdsc_lin_p_ttest$parameter), ") = ", round(gdsc_lin_p_ttest$statistic, 2), ", p = ", round(gdsc_lin_p_ttest$p.value, 3))
-  }
-
-  y_value <- ifelse(ticker == 3, 10, max(use_data$n) + max(use_data$n) * 0.1)
-
-  summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"),
-                          Test_Results_p = c(ccle_lin_p_ttest_res, ctrp_lin_p_ttest_res, gdsc_lin_p_ttest_res),
-                          t_statistic = c(round(ccle_lin_p_ttest$statistic, 3), round(ctrp_lin_p_ttest$statistic, 3), round(gdsc_lin_p_ttest$statistic, 3)),
-                          df = c(trunc(ccle_lin_p_ttest$parameter), trunc(ctrp_lin_p_ttest$parameter), trunc(gdsc_lin_p_ttest$parameter)),
-                          p_value = c(round(ccle_lin_p_ttest$p.value, 3), round(ctrp_lin_p_ttest$p.value, 3), round(gdsc_lin_p_ttest$p.value, 3)),
-                          group_general_lineage_name = lineage_name)
-  plot_point <- ggplot(data = use_data) +
-    facet_wrap(~ Dataset, drop = FALSE) +
-    coord_cartesian(xlim = c(0, 1), ylim = c(0, y_value)) +
-    scale_x_continuous(breaks = seq(0, 1, by = 0.1), labels = seq(0, 1, by = 0.1)) +
-    scale_y_continuous(breaks = pretty_breaks()) +
-    geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = p, y = n), alpha = 0.5) +
-    scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-    geom_text_repel(data = subset(use_data, InG2P == "Yes"), mapping = aes(x = p, y = n, label = Drug_Gene), size = 3, segment.size = 0.2, segment.color = "grey50") +
-    geom_text(data = summ_text, mapping = aes(x = 0.5, y = y_value, label = Test_Results_p), nudge_y = 0.1) +
-    labs(x = "Drug-gene association p-value between mutation groups", y = "Number of level A G2P associations") +
-    theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
-  plot_box <- ggplot(data = use_data) +
-    facet_wrap(~ Dataset, drop = FALSE) +
-    coord_cartesian(ylim = c(0, 1)) +
-    scale_y_continuous(breaks = seq(0, 1, by = 0.1), labels = seq(0, 1, by = 0.1)) +
-    geom_violin(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.5) +
-    geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.75, width = 0.25) +
-    scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-    coord_flip() +
-    labs(x = "In G2P?", title = toupper(lineage_name)) +
-    theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-  plot <- subplot(plot_box, plot_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(title = toupper(lineage_name), margin = list(t = 75, l = 75), xaxis5 = list(title = "Gene-drug association p-value between mutation groups"), yaxis = list(title = "Level A G2P\nassociation", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
-
-  plot_point <- ggplot_gtable(ggplot_build(plot_point))
-  plot_box <- ggplot_gtable(ggplot_build(plot_box))
-  p_maxWidth <-  grid::unit.pmax(plot_point$widths, plot_box$widths)
-  plot_point$widths <- as.list(p_maxWidth)
-  plot_box$widths <- as.list(p_maxWidth)
-
-  mut_plot <- cowplot::plot_grid(plot_box,
-                     plot_point,
-                     nrow = 2,
-                     rel_heights = c(1, 4))
-
-  saveWidgetFix(widget = plot, file = paste0("./plots/manuscript/plotlys_mut_by_lineage_grid/", lineage_name, "_mut_plotly_grid.html"))
-  ggsave(paste0("./plots/manuscript/pngs_mut_by_lineage_grid/", lineage_name, "_mut_plot_grid.png"), mut_plot, device = "png", dpi = 450, width = 12, height = 6, units =   "in")
-
-  return(summ_text)
-}
-```
-
-## Make lineage GE/CN plots
-
-```{r}
-PearsonPlotsByLineage <- function(lineage) {
-  print(paste0("Lineage: ", toupper(lineage)))
-  use_data <- filter(dgl_signif_pearson_g2p_grid, group_general_lineage_name == lineage)
-  use_data$Dataset <- factor(use_data$Dataset, levels = c("CCLE", "CTRP", "GDSC"))
-  use_data$Pearson_GE_Label <- paste0(round(use_data$Pearson_Pval_GE, 3), "\nDrug_Gene: ", use_data$Drug_Gene)
-  use_data$Pearson_CN_Label <- paste0(round(use_data$Pearson_Pval_CN, 3), "\nDrug_Gene: ", use_data$Drug_Gene)
-  ticker_ge <- 0
-  ticker_cn <- 0
-  ticker <- 0
-
-  use_data_ccle <- filter(use_data, Dataset == "CCLE")
-  use_data_ccle_ge_summ <- use_data_ccle[!is.na(use_data_ccle$Pearson_GE_Abs),] %>% count(InG2P)
-  use_data_ccle_cn_summ <- use_data_ccle[!is.na(use_data_ccle$Pearson_CN_Abs),] %>% count(InG2P)
-  ccle_ge_ttest <- data.frame(statistic = NA, parameter = NA, p.value = NA)
-  ccle_cn_ttest <- data.frame(statistic = NA, parameter = NA, p.value = NA)
-  if(nrow(use_data_ccle_ge_summ) <= 1) {
-    ccle_ge_res <-  NA
-    ticker_ge <- ticker_ge + 1
-  }
-  else if(use_data_ccle_ge_summ[use_data_ccle_ge_summ$InG2P == "Yes",]$nn < 2) {
-    ccle_ge_res <-  NA
-  }
-  else if(use_data_ccle_ge_summ[use_data_ccle_ge_summ$InG2P == "Yes",]$nn >= 2) {
-    ccle_ge_ttest <- t.test(use_data_ccle$Pearson_GE_Abs ~ use_data_ccle$InG2P)
-    ccle_ge_res <- paste0("t(", trunc(ccle_ge_ttest$parameter), ") = ", round(ccle_ge_ttest$statistic, 2), ", p = ", round(ccle_ge_ttest$p.value, 3))
-  }
-  if(nrow(use_data_ccle_cn_summ) <= 1) {
-    ccle_cn_res <-  NA
-    ticker_cn <- ticker_cn + 1
-  }
-  else if(use_data_ccle_cn_summ[use_data_ccle_cn_summ$InG2P == "Yes",]$nn < 2) {
-    ccle_cn_res <-  NA
-  }
-  else if(use_data_ccle_cn_summ[use_data_ccle_cn_summ$InG2P == "Yes",]$nn >= 2) {
-    ccle_cn_ttest <- t.test(use_data_ccle$Pearson_CN_Abs ~ use_data_ccle$InG2P)
-    ccle_cn_res <- paste0("t(", trunc(ccle_cn_ttest$parameter), ") = ", round(ccle_cn_ttest$statistic, 2), ", p = ", round(ccle_cn_ttest$p.value, 3))
-  }
-  print("CCLE testing: DONE")
-
-  use_data_ctrp <- filter(use_data, Dataset == "CTRP")
-  use_data_ctrp_ge_summ <- use_data_ctrp[!is.na(use_data_ctrp$Pearson_GE_Abs),] %>% count(InG2P)
-  use_data_ctrp_cn_summ <- use_data_ctrp[!is.na(use_data_ctrp$Pearson_CN_Abs),] %>% count(InG2P)
-  ctrp_ge_ttest <- data.frame(statistic = NA, parameter = NA, p.value = NA)
-  ctrp_cn_ttest <- data.frame(statistic = NA, parameter = NA, p.value = NA)
-  if(nrow(use_data_ctrp_ge_summ) <= 1) {
-    ctrp_ge_res <-  NA
-    ticker_ge <- ticker_ge + 1
-  }
-  else if(use_data_ctrp_ge_summ[use_data_ctrp_ge_summ$InG2P == "Yes",]$nn < 2) {
-    ctrp_ge_res <-  NA
-  }
-  else if(use_data_ctrp_ge_summ[use_data_ctrp_ge_summ$InG2P == "Yes",]$nn >= 2) {
-    ctrp_ge_ttest <- t.test(use_data_ctrp$Pearson_GE_Abs ~ use_data_ctrp$InG2P)
-    ctrp_ge_res <- paste0("t(", trunc(ctrp_ge_ttest$parameter), ") = ", round(ctrp_ge_ttest$statistic, 2), ", p = ", round(ctrp_ge_ttest$p.value, 3))
-  }
-  if(nrow(use_data_ctrp_cn_summ) <= 1) {
-    ctrp_cn_res <-  NA
-    ticker_cn <- ticker_cn + 1
-  }
-  else if(use_data_ctrp_cn_summ[use_data_ctrp_cn_summ$InG2P == "Yes",]$nn < 2) {
-    ctrp_cn_res <-  NA
-  }
-  else if(use_data_ctrp_cn_summ[use_data_ctrp_cn_summ$InG2P == "Yes",]$nn >= 2) {
-    ctrp_cn_ttest <- t.test(use_data_ctrp$Pearson_CN_Abs ~ use_data_ctrp$InG2P)
-    ctrp_cn_res <- paste0("t(", trunc(ctrp_cn_ttest$parameter), ") = ", round(ctrp_cn_ttest$statistic, 2), ", p = ", round(ctrp_cn_ttest$p.value, 3))
-  }
-  print("CTRP testing: DONE")
-
-  use_data_gdsc <- filter(use_data, Dataset == "GDSC")
-  use_data_gdsc_ge_summ <- use_data_gdsc[!is.na(use_data_gdsc$Pearson_GE_Abs),] %>% count(InG2P)
-  use_data_gdsc_cn_summ <- use_data_gdsc[!is.na(use_data_gdsc$Pearson_CN_Abs),] %>% count(InG2P)
-  gdsc_ge_ttest <- data.frame(statistic = NA, parameter = NA, p.value = NA)
-  gdsc_cn_ttest <- data.frame(statistic = NA, parameter = NA, p.value = NA)
-  if(nrow(use_data_gdsc_ge_summ) <= 1) {
-    gdsc_ge_res <-  NA
-    ticker_ge <- ticker_ge + 1
-  }
-  else if(use_data_gdsc_ge_summ[use_data_gdsc_ge_summ$InG2P == "Yes",]$nn < 2) {
-    gdsc_ge_res <-  NA
-  }
-  else if(use_data_gdsc_ge_summ[use_data_gdsc_ge_summ$InG2P == "Yes",]$nn >= 2) {
-    gdsc_ge_ttest <- t.test(use_data_gdsc$Pearson_GE_Abs ~ use_data_gdsc$InG2P)
-    gdsc_ge_res <- paste0("t(", trunc(gdsc_ge_ttest$parameter), ") = ", round(gdsc_ge_ttest$statistic, 2), ", p = ", round(gdsc_ge_ttest$p.value, 3))
-  }
-  if(nrow(use_data_gdsc_cn_summ) <= 1) {
-    gdsc_cn_res <-  NA
-    ticker_cn <- ticker_cn + 1
-  }
-  else if(use_data_gdsc_cn_summ[use_data_gdsc_cn_summ$InG2P == "Yes",]$nn < 2) {
-    gdsc_cn_res <-  NA
-  }
-  else if(use_data_gdsc_cn_summ[use_data_gdsc_cn_summ$InG2P == "Yes",]$nn >= 2) {
-    gdsc_cn_ttest <- t.test(use_data_gdsc$Pearson_CN_Abs ~ use_data_gdsc$InG2P)
-    gdsc_cn_res <- paste0("t(", trunc(gdsc_cn_ttest$parameter), ") = ", round(gdsc_cn_ttest$statistic, 2), ", p = ", round(gdsc_cn_ttest$p.value, 3))
-  }
-  print("GDSC testing: DONE")
-
-  y_value_ge <- ifelse(ticker_ge == 3, 10, max(use_data$n) + max(use_data$n) * 0.1)
-  y_value_cn <- ifelse(ticker_cn == 3, 10, max(use_data$n) + max(use_data$n) * 0.1)
-
-  summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"),
-                          Test_Results_GE = c(ccle_ge_res, ctrp_ge_res, gdsc_ge_res),
-                          t_statistic_GE = c(round(ccle_ge_ttest$statistic, 3), round(ctrp_ge_ttest$statistic, 3), round(gdsc_ge_ttest$statistic, 3)),
-                          df_GE = c(trunc(ccle_ge_ttest$parameter), trunc(ctrp_ge_ttest$parameter), trunc(gdsc_ge_ttest$parameter)),
-                          p_value_GE = c(round(ccle_ge_ttest$p.value, 3), round(ctrp_ge_ttest$p.value, 3), round(gdsc_ge_ttest$p.value, 3)),
-                          Test_Results_CN = c(ccle_cn_res, ctrp_cn_res, gdsc_cn_res),
-                          t_statistic_CN = c(round(ccle_cn_ttest$statistic, 3), round(ctrp_cn_ttest$statistic, 3), round(gdsc_cn_ttest$statistic, 3)),
-                          df_CN = c(trunc(ccle_cn_ttest$parameter), trunc(ctrp_cn_ttest$parameter), trunc(gdsc_cn_ttest$parameter)),
-                          p_value_CN = c(round(ccle_cn_ttest$p.value, 3), round(ctrp_cn_ttest$p.value, 3), round(gdsc_cn_ttest$p.value, 3)),
-                          group_general_lineage_name = lineage)
-
-  ## Gene expression
-  if(sum(!is.na(use_data$Pearson_GE_Abs)) > 0) {
-    plot_ge_point <- ggplot(data = use_data) +
-      facet_wrap(~ Dataset, drop = FALSE) +
-      scale_y_continuous(breaks = pretty_breaks()) +
-      geom_point(mapping = aes(label = Pearson_GE_Label, color = InG2P, fill = InG2P, shape = Pearson_GE_Sign, x = Pearson_GE_Abs, y = n), alpha = 0.5) +
-      scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
-      scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-      scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-      geom_text_repel(data = subset(use_data, InG2P == "Yes" & n > 10), aes(label = Drug_Gene, x = Pearson_GE_Abs, y = n), size = 3, segment.size = 0.2, segment.color = "grey50") +
-      geom_text(data = summ_text, mapping = aes(x = 0.5, y = y_value_ge, label = Test_Results_GE), nudge_y = 1) +
-      labs(y = "Number of level A G2P associations", x = "Pearson correlation coefficient between drug-gene AUC and gene expression") +
-      theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
-    plot_ge_box <- ggplot(data = use_data) +
-      facet_wrap(~ Dataset, drop = FALSE) +
-      geom_violin(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.5) +
-      geom_boxplot(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
-      scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-      coord_flip() +
-      labs(x = "In G2P?", title = toupper(lineage)) +
-      theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
-    plot_ge <- subplot(plot_ge_box, plot_ge_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>%
-               layout(title = lineage, margin = list(t = 75, l = 75),
-                      xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and gene expression"),
-                      yaxis = list(title = "In G2P?", domain = c(0.8, 1)),
-                      yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
-
-    png_ge_point <- ggplot_gtable(ggplot_build(plot_ge_point))
-    png_ge_box <- ggplot_gtable(ggplot_build(plot_ge_box))
-    p_maxWidth <-  grid::unit.pmax(png_ge_point$widths, png_ge_box$widths)
-    png_ge_point$widths <- as.list(p_maxWidth)
-    png_ge_box$widths <- as.list(p_maxWidth)
-
-    png_ge <- cowplot::plot_grid(png_ge_box, png_ge_point, nrow = 2, rel_heights = c(1, 4))
-    png_ge
-
-    saveWidgetFix(widget = plot_ge, file = paste0("./plots/manuscript/plotlys_ge_by_lineage_grid/", lineage, "_ge_plotly_grid.html"))
-    ggsave(paste0("./plots/manuscript/pngs_ge_by_lineage_grid/", lineage, "_ge_plot_grid.png"), png_ge, device = "png", dpi = 450, width = 12, height = 6, units = "in")
-    print("Gene expression plots: DONE")
-  }
-  else if(sum(!is.na(use_data$Pearson_GE_Abs)) == 0) { print("Gene expression plots: None") }
-
-  ## Copy number
-  if(sum(!is.na(use_data$Pearson_CN_Abs)) > 0) {
-    plot_cn_point <- ggplot(data = use_data) +
-      facet_wrap(~ Dataset, drop = FALSE) +
-      scale_y_continuous(breaks = pretty_breaks()) +
-      geom_point(mapping = aes(label = Pearson_CN_Label, color = InG2P, fill = InG2P, shape = Pearson_CN_Sign, x = Pearson_CN_Abs, y = n), alpha = 0.5, position = position_jitter(width = 0, height = 0.15)) +
-      scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
-      scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-      scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-      geom_text_repel(data = subset(use_data, InG2P == "Yes"  & n > 10), aes(label = Drug_Gene, x = Pearson_CN_Abs, y = n), size = 3, segment.size = 0.2, segment.color = "grey50") +
-      geom_text(data = summ_text, mapping = aes(x = 0.5, y = y_value_cn, label = Test_Results_CN), nudge_y = 1) +
-      labs(y = "Number of level A G2P associations", x = "Pearson correlation coefficient between drug-gene AUC and copy number") +
-      theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
-    plot_cn_box <- ggplot(data = use_data) +
-      facet_wrap(~ Dataset, drop = FALSE) +
-      geom_violin(mapping = aes(color = InG2P, y = Pearson_CN_Abs, x = InG2P), alpha = 0.5) +
-      geom_boxplot(mapping = aes(color = InG2P, y = Pearson_CN_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
-      scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-      coord_flip() +
-      labs(x = "In G2P?", title = toupper(lineage)) +
-      theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
-    plot_cn <- subplot(plot_cn_box, plot_cn_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>%
-               layout(title = lineage, margin = list(t = 75, l = 75),
-                      xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and copy number"),
-                      yaxis = list(title = "In G2P?", domain = c(0.8, 1)),
-                      yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
-
-    png_cn_point <- ggplot_gtable(ggplot_build(plot_cn_point))
-    png_cn_box <- ggplot_gtable(ggplot_build(plot_cn_box))
-    p_maxWidth <-  grid::unit.pmax(png_cn_point$widths, png_cn_box$widths)
-    png_cn_point$widths <- as.list(p_maxWidth)
-    png_cn_box$widths <- as.list(p_maxWidth)
-
-    png_cn <- cowplot::plot_grid(png_cn_box, png_cn_point, nrow = 2, rel_heights = c(1, 4))
-    png_cn
-
-    saveWidgetFix(widget = plot_cn, file = paste0("./plots/manuscript/plotlys_cn_by_lineage_grid/", lineage, "_cn_plotly_grid.html"))
-    ggsave(paste0("./plots/manuscript/pngs_cn_by_lineage_grid/", lineage, "_cn_plot_grid.png"), png_cn, device = "png", dpi = 450, width = 12, height = 6, units = "in")
-    print("Copy number plots: DONE")
-  }
-  else if(sum(!is.na(use_data$Pearson_CN_Abs)) == 0) { print("Copy number plots: None") }
-
-  return(summ_text)
-}
-```
-
-## Make per-drug boxplots
-```{r}
-makeDrugBoxplots <- function(drug, dataset) {
-  if(dataset == "CCLE" | dataset == "ccle") {
-    use_data <- filter(ccle_data_ptmuts, Drug == drug)
-    use_color <- as.character(use_data$Color_Nonsilent)
-    names(use_color) <- use_data$Mutation_Status_Nonsilent
-    sig <- ccle_signif_g2p_ByDrug[[drug]]
-    label_text <- data.frame(p.signif = sig$p.signif, p.signif.adj = sig$p.signif.adj, Hugo_Symbol = sig$Hugo_Symbol)
-    label_text$Hugo_Symbol <- factor(label_text$Hugo_Symbol, levels = g2p_genes)
-  }
-  else if(dataset == "CTRP" | dataset == "ctrp") {
-    use_data <- filter(ctrp_data_ptmuts, Drug == drug)
-    use_color <- as.character(use_data$Color_Nonsilent)
-    names(use_color) <- use_data$Mutation_Status_Nonsilent
-    sig <- ctrp_signif_g2p_ByDrug[[drug]]
-    label_text <- data.frame(p.signif = sig$p.signif, p.signif.adj = sig$p.signif.adj, Hugo_Symbol = sig$Hugo_Symbol)
-    label_text$Hugo_Symbol <- factor(label_text$Hugo_Symbol, levels = g2p_genes)
-  }
-  else if(dataset == "GDSC" | dataset == "gdsc") {
-    use_data <- filter(gdsc_data_ptmuts, Drug == drug)
-    use_color <- as.character(use_data$Color_Nonsilent)
-    names(use_color) <- use_data$Mutation_Status_Nonsilent
-    sig <- gdsc_signif_g2p_ByDrug[[drug]]
-    label_text <- data.frame(p.signif = sig$p.signif, p.signif.adj = sig$p.signif.adj, Hugo_Symbol = sig$Hugo_Symbol)
-    label_text$Hugo_Symbol <- factor(label_text$Hugo_Symbol, levels = g2p_genes)
-  }
-  else { return("Error: Invalid dataset.") }
-
-  plot <- ggplot(data = use_data, aes(x = Mutation_Status_Nonsilent, y = AUC)) +
-    facet_wrap(~ Hugo_Symbol, drop = FALSE, nrow = 1) +
-    geom_boxplot(mapping = aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85), outlier.shape = 3, outlier.size = 0.5) +
-    scale_fill_manual(values = use_color) +
-    guides(color = FALSE) +
-    geom_text(data = label_text, mapping = aes(x = 1.5, y = max(use_data$AUC), label = p.signif), nudge_y = 0.2) +
-    theme(strip.text.x = element_text(size = 10, angle = 45), legend.position = "top", axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
-    labs(fill = "Mutation Status", y = "AUC", x = "Mutation Status", title = paste0(toupper(dataset), ": ", drug))
-  return(plot)
-}
-```
-
-# DATA MANAGEMENT {.tabset .tabset-fade .tabset-pills}
-
---------------------------------------------------------------------------------
-
-## D. Charytonowicz cell line converter
-
-This comprehensive cancer cell line information curated by Daniel Charytonowicz.
-```{r}
-ccl_converter <- read.delim("./data_munging/cell_line_database_v1_20180911.tsv", row.names = 1, sep = "\t", header = TRUE)
-lineage_converter <- unique(ccl_converter[, c("grouped_general_doid", "group_general_lineage_name")])
-colnames(ccl_converter)[colnames(ccl_converter) == "Broad_ID"] <- "DepMap_ID"
-```
-
-## DepMap cell line metadata
-
-```{r}
-ccl_info <- read.delim("./data_munging/18Q4/DepMap-2018q4-celllines_20181115.csv", sep = ",", header = TRUE, na.strings = c("", NA))
-ccl_info$Primary.Disease <- gsub("\\\\", "", ccl_info$Primary.Disease)
-ccl_info$Primary.Disease <- gsub("Ewings", "Ewing's", ccl_info$Primary.Disease)
-# From figshare
-crispr_meta <- read.delim("./data_munging/18Q4/sample_info_18Q4_crispr_20181115.csv", sep = ",", header = TRUE, na.strings = c("", NA))
-colnames(crispr_meta)[7] <- "CCLE_Name"
-```
-
-## CCLE genomic annotations
-
-### Mutation status (Mut)
-
-For mutation calling, get paired gene name and cell line fields in a data frame.
-For this analysis, we don't care about how many mutations there are per gene or what type of mutations there are, so I didn't save more information.
-I took unique gene-cell line combinations since we only cared about mutation presence/absence.
-Add a `Mutation_Status` column denoting all entries in MAF files as mutations present in the associated cell lines.
-
-Merged mutation calls (coding region, germline filtered):
-```{r, eval=FALSE}
-maf_raw <- read.delim("./data_munging/18Q4/depmap_18Q4_mutation_calls_20181114.csv.gz", header = TRUE, sep = ",", row.names = 1)
-colnames(maf_raw)[colnames(maf_raw) == "Tumor_Sample_Barcode"] <- "CCLE_Name"
-# Select columns
-maf_df <- subset(maf_raw, select = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID", "Variant_Classification", "Reference_Allele", "Tumor_Seq_Allele1", "Genome_Change"))
-maf_df$Reference_Allele_Length <- ifelse(maf_df$Reference_Allele == "-", 0, nchar(as.character(maf_df$Reference_Allele)))
-maf_df$Tumor_Seq_Allele1_Length <- nchar(as.character(maf_df$Tumor_Seq_Allele1))
-# Add Mutation_Status column
-maf_df$Mutation_Status_Nonsilent <- ifelse(maf_df$Variant_Classification == "Silent", "Wildtype", "Mutant")
-maf_df <- unique(maf_df)
-saveRDS(maf_df, "./data_munging/rds/maf_df_18Q4.rds", compress = "xz")
-```
-
-### Copy number (CN)
-
-DepMap WES CN Data:
-```{r, eval=FALSE}
-cn <- read.delim("./data_munging/18Q4/public_18Q4_gene_cn_20181115.csv.gz", sep = ",", check.names = FALSE, header = TRUE)
-# Remove Entrez gene IDs from colnames
-# Format: Hugo_Symbol (Entrez ID)
-colnames(cn) <- gsub(" .*", "", colnames(cn))
-# Melt
-cn_melt <- melt(data = cn, id.vars = "DepMap_ID", measure.vars = colnames(cn[2:ncol(cn)]), variable.name = "Hugo_Symbol", value.name = "CN")
-saveRDS(cn_melt, "./data_munging/rds/cn_melt_18Q4.rds", compress = "xz")
-```
-
-### Gene expression (GE)
-
-18Q3, Gene expression data (Reads Per Kilobase of transcript, per Million mapped reads, RPKM).
-```{r, eval=FALSE}
-ge_18Q3 <- read.delim("./../htscreen_lineages_giant_files/CCLE_DepMap_18q3_RNAseq_RPKM_20180718.gct.gz", skip = 2, header = TRUE, sep = "\t", check.names = FALSE)
-# Edit columns
-ge_18Q3$Name <- NULL
-colnames(ge_18Q3)[1] <- "Hugo_Symbol"
-# Melt
-ge_melt_18Q3 <- melt(data = ge_18Q3, id.vars = "Hugo_Symbol", measure.vars = colnames(ge_18Q3[2:ncol(ge_18Q3)]), value.name = "RPKM")
-## Split variable column
-ge_melt_18Q3 <- with(ge_melt_18Q3, cbind(Hugo_Symbol, colsplit(variable, pattern = " ", names = c("CCLE_Name", "DepMap_ID")), RPKM))
-## Remove parentheses around Broad IDs
-ge_melt_18Q3$DepMap_ID <- gsub("\\(|\\)", "", ge_melt_18Q3$DepMap_ID)
-saveRDS(ge_melt_18Q3, "./../htscreen_lineages_giant_files/ge_melt_18Q3.rds", compress = "xz")
-```
-
-18Q4, CCLE RNAseq gene expression data (log2(TPM+1)):
-```{r, eval=FALSE}
-ge_18Q4 <- read.delim("./../htscreen_lineages_giant_files/CCLE_depMap_18Q4_TPM_v2_20181115.csv.gz", header = TRUE, sep = ",", check.names = FALSE)
-# Remove Entrez gene IDs from colnames
-# Format: Hugo_Symbol (Entrez ID)
-colnames(ge_18Q4) <- gsub(" .*", "", colnames(ge_18Q4))
-colnames(ge_18Q4)[1] <- "DepMap_ID"
-# Melt
-ge_melt_18Q4_all <- melt(ge_18Q4, id.vars = "DepMap_ID", measure.vars = colnames(ge_18Q4)[2:ncol(ge_18Q4)], variable.name = "Hugo_Symbol", value.name = "TPM")
-ge_melt_18Q4 <- unique(ge_melt_18Q4)
-saveRDS(ge_melt_18Q4, "./data_munging/rds/ge_melt_18Q4.rds", compress = "xz")
-```
-
-## G2P
-
-```{r}
-g2p <- read.delim("./data_munging/g2p_full_level_A_dataset_NEW_DEC_2_2018_withGroupedLineages.csv", sep = "\t", header = TRUE)
-g2p[, 1:2] <- NULL
-g2p <- merge(g2p, lineage_converter, by = "grouped_general_doid", all.x = TRUE)
-
-g2p$Drug <- tolower(g2p$Drug)
-g2p[g2p == -1] <- NA
-g2p$Ref[g2p$Ref == "None"] <- NA
-g2p$Alt[g2p$Alt == "None"] <- NA
-g2p$Drug_Gene <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene), NA, paste0(g2p$Drug, "_", g2p$Gene))
-g2p$Drug_Gene_Lin <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene) | is.na(g2p$group_general_lineage_name), NA, paste0(g2p$Drug, "_", g2p$Gene, "_", g2p$group_general_lineage_name))
-g2p$position <- paste0("g.chr", g2p$Chromosome, ":", g2p$End, g2p$Ref, ">", g2p$Alt)
-g2p$position <- ifelse(grepl("NA", g2p$position), NA, g2p$position)
-g2p_filt <- subset(g2p, grepl("^CID", g2p$DrugID))
-
-g2p_dgls <-  unique(g2p_filt$Drug_Gene_Lin[!is.na(g2p_filt$Drug_Gene_Lin)])
-g2p_druggenes <- unique(g2p_filt$Drug_Gene[!is.na(g2p_filt$Drug_Gene)])
-g2p_genes <- unique(sapply(strsplit(g2p_drug_genes, "_", fixed = TRUE), function(x) x[2]))
-g2p_drugs <- unique(sapply(strsplit(g2p_drug_genes, "_", fixed = TRUE), function(x) x[1]))
-g2p_druggenes
-g2p_genes
-g2p_drugs
-# Order and genes taken from pink heatmapo from Daniel's analyses
-g2p_genes <- c("EGFR", "KRAS", "ERBB2", "ERBB3", "MET", "ALK", "ROS1", "PDGFRA", "ABL1", "KIT", "PDGFRB", "PDGFB", "BRAF", "G6PD", "RET", "BRCA1", "BRCA2", "UGT1A1", "TSC1", "TSC2", "AKT1", "IDH2", "DPYD", "ESR1", "CYP19A1", "TPMT", "FLT3", "NPM1", "DNMT3A", "PML", "PTCH1", "JAK2", "MYD88", "MGMT")
-```
-
-```{r}
-# levels(g2p_filt$Phenotype.Description)
-unique(g2p_filt$group_general_lineage_name)
-levels(g2p_filt$group_general_lineage_name)
-
-g2p_nonCID <- subset(g2p, !grepl("^CID", g2p$DrugID))
-summ <- g2p_nonCID %>% group_by(Drug, DrugID) %>% tally() %>% summarize(DrugID = DrugID, n = n, percent = formatC(n / 402 * 100, digits = 6, format = "f"))
-summ
-```
-
-```{r, eval=FALSE}
-maf_df <- readRDS("./data_munging/rds/maf_df_18Q4.rds")
-cn_melt <- readRDS("./data_munging/rds/cn_melt_18Q4.rds")
-ge_melt_18Q3 <- readRDS("./../htscreen_lineages_giant_files/ge_melt_18Q3.rds")
-# ge_melt_18Q4 <- readRDS("./data_munging/rds/ge_melt_18Q4.rds")
-
-# maf_filt_dan <- filter(maf_df, Hugo_Symbol %in% g2p_genes)
-# write.table(maf_filt_dan, file = "~/Desktop/maf_filt_dan_18Q4_2018112.csv", quote = FALSE, sep = ",", row.names = FALSE)
-```
-
-## Drug screens
-
-### Merge drug data and annotations
-
-```{r, eval=FALSE}
-# Drug metadata
-drug_meta <- read.delim("./data_munging/drug_id_drug_name_table_10_12_2018.tsv", sep = "\t", header = FALSE)
-colnames(drug_meta) <- c("CID", "Drug")
-drug_meta$Drug <- tolower(drug_meta$Drug)
-maf_df_g2p <- filter(maf_df, Hugo_Symbol %in% g2p_genes)
-ge_filt_18Q3 <- filter(ge_melt_18Q3, Hugo_Symbol %in% g2p_genes)
-# ge_filt_18Q4 <- filter(ge_melt_18Q4, Hugo_Symbol %in% g2p_genes)
-cn_filt <- filter(cn_melt, Hugo_Symbol %in% g2p_genes)
-
-# CCLE
-ccle <- read.delim("./data_munging/data_drug_auc_ccle_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
-ccle <- merge(drug_meta, ccle, by = "CID")
-ccle_melt <- melt(ccle, id.vars = c("CID", "Drug"), measure.vars = colnames(ccle)[3:ncol(ccle)], variable.name = "accession_id", value.name = "ActArea")
-ccle_grid <- expand.grid("accession_id" = unique(ccle_melt$accession_id), "Hugo_Symbol" = g2p_genes)
-ccle_data <- merge(ccle_grid, ccle_melt, by = "accession_id", all.x = TRUE)
-ccle_data <- merge(ccle_data, ccl_converter, by = "accession_id", all.x = TRUE)
-ccle_data <- merge(ccle_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
-ccle_data$Mutation_Status_Nonsilent <- ifelse(is.na(ccle_data$Mutation_Status_Nonsilent), "Wildtype", ccle_data$Mutation_Status_Nonsilent)
-ccle_data <- merge(ccle_data, ge_filt_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
-# ccle_data <- merge(ccle_data, ge_filt_18Q4, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
-ccle_data <- merge(ccle_data, cn_filt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
-ccle_data$Hugo_Symbol <- factor(ccle_data$Hugo_Symbol)
-ccle_data$ActArea <- as.numeric(ccle_data$ActArea)
-# CCLE AUC is actually AOC
-# assuming scale is 0-8, transform to range between 0 and 1
-# get AUC by 1 - AOC
-ccle_data$AUC <- 1 - (ccle_data$ActArea / 8)
-ccle_data <- filter(ccle_data, !is.na(ccle_data$AUC))
-ccle_data$AUC_zscore <- (ccle_data$AUC - mean(ccle_data$AUC)) / sd(ccle_data$AUC)
-ccle_data$Color_Nonsilent <- ifelse(ccle_data$Mutation_Status_Nonsilent == "Wildtype", "palegreen3", "springgreen4")
-ccle_data$Color_Nonsilent <- factor(ccle_data$Color_Nonsilent)
-ccle_data$Drug_Gene <- paste0(ccle_data$Drug, "_", ccle_data$Hugo_Symbol)
-ccle_data$Drug_Gene_Lin <- paste0(ccle_data$Drug, "_", ccle_data$Hugo_Symbol, "_", ccle_data$group_general_lineage_name)
-saveRDS(ccle_data, "./data_munging/rds/ccle_data_18Q4_g2pgenes.rds", compress = "xz")
-
-# CTRP
-ctrp <- read.delim("./data_munging/data_drug_auc_ctrp_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
-ctrp <- merge(drug_meta, ctrp, by = "CID")
-ctrp_melt <- melt(ctrp, id.vars = c("CID", "Drug"), measure.vars = colnames(ctrp)[3:ncol(ctrp)], variable.name = "accession_id", value.name = "AUC")
-ctrp_grid <- expand.grid("accession_id" = unique(ctrp_melt$accession_id), "Hugo_Symbol" = g2p_genes)
-ctrp_data <- merge(ctrp_grid, ctrp_melt, by = "accession_id", all.x = TRUE)
-ctrp_data <- merge(ctrp_data, ccl_converter, by = "accession_id", all.x = TRUE)
-ctrp_data <- merge(ctrp_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
-ctrp_data$Mutation_Status_Nonsilent <- ifelse(is.na(ctrp_data$Mutation_Status_Nonsilent), "Wildtype", ctrp_data$Mutation_Status_Nonsilent)
-ctrp_data <- merge(ctrp_data, ge_filt_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
-# ctrp_data <- merge(ctrp_data, ge_filt_18Q4, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
-ctrp_data <- merge(ctrp_data, cn_filt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
-ctrp_data$Hugo_Symbol <- factor(ctrp_data$Hugo_Symbol)
-ctrp_data$AUC <- as.numeric(ctrp_data$AUC)
-ctrp_data <- filter(ctrp_data, !is.na(ctrp_data$AUC))
-ctrp_data$AUC_zscore <- (ctrp_data$AUC - mean(ctrp_data$AUC)) / sd(ctrp_data$AUC)
-ctrp_data$Color_Nonsilent <- ifelse(ctrp_data$Mutation_Status_Nonsilent == "Wildtype", "slategray3", "steelblue4")
-ctrp_data$Color_Nonsilent <- factor(ctrp_data$Color_Nonsilent)
-ctrp_data$Drug_Gene <- paste0(ctrp_data$Drug, "_", ctrp_data$Hugo_Symbol)
-ctrp_data$Drug_Gene_Lin <- paste0(ctrp_data$Drug, "_", ctrp_data$Hugo_Symbol, "_", ctrp_data$group_general_lineage_name)
-saveRDS(ctrp_data, "./data_munging/rds/ctrp_data_18Q4_g2pgenes.rds", compress = "xz")
-
-# GDSC
-gdsc <- read.delim("./data_munging/data_drug_auc_gdsc_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
-gdsc <- merge(drug_meta, gdsc, by = "CID")
-gdsc_melt <- melt(gdsc, id.vars = c("CID", "Drug"), measure.vars = colnames(gdsc)[3:ncol(gdsc)], variable.name = "accession_id", value.name = "AUC")
-gdsc_grid <- expand.grid("accession_id" = unique(gdsc_melt$accession_id), "Hugo_Symbol" = g2p_genes)
-gdsc_data <- merge(gdsc_grid, gdsc_melt, by = "accession_id", all.x = TRUE)
-gdsc_data <- merge(gdsc_data, ccl_converter, by = "accession_id", all.x = TRUE)
-gdsc_data <- merge(gdsc_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
-gdsc_data$Mutation_Status_Nonsilent <- ifelse(is.na(gdsc_data$Mutation_Status_Nonsilent), "Wildtype", gdsc_data$Mutation_Status_Nonsilent)
-gdsc_data <- merge(gdsc_data, ge_filt_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
-# gdsc_data <- merge(gdsc_data, ge_filt_18Q4, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
-gdsc_data <- merge(gdsc_data, cn_filt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
-gdsc_data$Hugo_Symbol <- factor(gdsc_data$Hugo_Symbol)
-gdsc_data$AUC <- as.numeric(gdsc_data$AUC)
-gdsc_data <- filter(gdsc_data, !is.na(gdsc_data$AUC))
-gdsc_data$AUC_zscore <- (gdsc_data$AUC - mean(gdsc_data$AUC)) / sd(gdsc_data$AUC)
-gdsc_data$Color_Nonsilent <- ifelse(gdsc_data$Mutation_Status_Nonsilent == "Wildtype", "paleturquoise3", "turquoise4")
-gdsc_data$Color_Nonsilent <- factor(gdsc_data$Color_Nonsilent)
-gdsc_data$Drug_Gene <- paste0(gdsc_data$Drug, "_", gdsc_data$Hugo_Symbol)
-gdsc_data$Drug_Gene_Lin <- paste0(gdsc_data$Drug, "_", gdsc_data$Hugo_Symbol, "_", gdsc_data$group_general_lineage_name)
-saveRDS(gdsc_data, "./data_munging/rds/gdsc_data_18Q4_g2pgenes.rds", compress = "xz")
-```
-
-### Filter drug data
-
-```{r}
-ccle_data <- readRDS("./data_munging/rds/ccle_data_18Q4_g2pgenes.rds")
-ccle_data_ptmuts <- filter(ccle_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
-ccle_data_ptmuts$Keep_PtMut_Tests <- ifelse(ccle_data_ptmuts$Reference_Allele_Length == 1 | is.na(ccle_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(ccle_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
-ccle_data_ptmuts <- filter(ccle_data_ptmuts, Keep_PtMut_Tests == TRUE)
-ccle_data_ptmuts$Dataset <- "CCLE"
-ccle_data_ptmuts$Hugo_Symbol <- ordered(ccle_data_ptmuts$Hugo_Symbol, levels = g2p_genes)
-
-ctrp_data <- readRDS("./data_munging/rds/ctrp_data_18Q4_g2pgenes.rds")
-ctrp_data_ptmuts <- filter(ctrp_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
-ctrp_data_ptmuts$Keep_PtMut_Tests <- ifelse(ctrp_data_ptmuts$Reference_Allele_Length == 1 | is.na(ctrp_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(ctrp_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
-ctrp_data_ptmuts <- filter(ctrp_data_ptmuts, Keep_PtMut_Tests == TRUE)
-ctrp_data_ptmuts$Dataset <- "CTRP"
-ctrp_data_ptmuts$Hugo_Symbol <- ordered(ctrp_data_ptmuts$Hugo_Symbol, levels = g2p_genes)
-
-gdsc_data <- readRDS("./data_munging/rds/gdsc_data_18Q4_g2pgenes.rds")
-gdsc_data_ptmuts <- filter(gdsc_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
-gdsc_data_ptmuts$Keep_PtMut_Tests <- ifelse(gdsc_data_ptmuts$Reference_Allele_Length == 1 | is.na(gdsc_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(gdsc_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
-gdsc_data_ptmuts <- filter(gdsc_data_ptmuts, Keep_PtMut_Tests == TRUE)
-gdsc_data_ptmuts$Dataset <- "GDSC"
-gdsc_data_ptmuts$Hugo_Symbol <- ordered(gdsc_data_ptmuts$Hugo_Symbol, levels = g2p_genes)
-
-# Filter drug screen datasets for G2P drug-gene associations
-ccle_data_g2p <- filter(ccle_data_ptmuts, Drug_Gene %in% g2p_drug_genes)
-ccle_data_g2p$Mutation_Status_Nonsilent <- factor(ccle_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-ctrp_data_g2p <- filter(ctrp_data_ptmuts, Drug_Gene %in% g2p_drug_genes)
-ctrp_data_g2p$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-gdsc_data_g2p <- filter(gdsc_data_ptmuts, Drug_Gene %in% g2p_drug_genes)
-gdsc_data_g2p$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-
-# Filter drug screen datasets for G2P drug-gene-lineage associations
-ccle_data_g2p_dgl <- filter(ccle_data_ptmuts, Drug_Gene_Lin %in% g2p_dgls)
-ccle_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(ccle_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-ctrp_data_g2p_dgl <- filter(ctrp_data_ptmuts, Drug_Gene_Lin %in% g2p_dgls)
-ctrp_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-gdsc_data_g2p_dgl <- filter(gdsc_data_ptmuts, Drug_Gene_Lin %in% g2p_dgls)
-gdsc_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-
-# Filter drug screen datasets for G2P drugs and genes
-ccle_data_g2p_grid <- filter(ccle_data_ptmuts, Drug %in% g2p_drugs)
-ccle_data_g2p_grid$Mutation_Status_Nonsilent <- factor(ccle_data_g2p_grid$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-ctrp_data_g2p_grid <- filter(ctrp_data_ptmuts, Drug %in% g2p_drugs)
-ctrp_data_g2p_grid$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p_grid$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-gdsc_data_g2p_grid <- filter(gdsc_data_ptmuts, Drug %in% g2p_drugs)
-gdsc_data_g2p_grid$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p_grid$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-```
-
-```{r}
-test_ccle <- ccle_data_ptmuts %>% group_by(Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()
-test_ctrp <- ctrp_data_ptmuts %>% group_by(Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()
-test_gdsc <- gdsc_data_ptmuts %>% group_by(Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()
-```
-
-## CRISPR
-
-### DepMap dependency probabilities
-
-```{r, eval=FALSE}
-dep <- read.delim("./data_munging/18Q4/gene_dependency_18Q4_20181115.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
-# Remove Entrez gene IDs from colnames
-colnames(dep) <- gsub(" .*", "", colnames(dep))
-```
-
-### Merge CRISPR data and annotations
-
-The latest CRISPR CERES score data (18Q3, August 2018) was pulled from the [DepMap Data Portal](https://depmap.org/portal/download/) (Broad Institute Cancer Dependency Map 2018, Meyers et al. 2017).
-```{r, eval=FALSE}
-crispr <- read.delim("./data_munging/18Q4/gene_effect_18Q4_20181115.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
-# Remove Entrez gene IDs from colnames
-colnames(crispr) <- gsub(" .*", "", colnames(crispr))
-```
-
-Merge annotation data:
-```{r, eval=FALSE}
-# Melt CRISPR dataset for merging
-crispr_melt <- melt(crispr, id.vars = "DepMap_ID", measure.vars = colnames(crispr)[2:ncol(crispr)], variable.name = "Hugo_Symbol", value.name = "Score")
-# Melt dependency probabilities dataset for merging
-dep_melt <- melt(dep, id.vars = "DepMap_ID", measure.vars = colnames(dep)[2:ncol(dep)], variable.name = "Hugo_Symbol", value.name = "Dep_Prob")
-# Merge dependency probabilities
-crispr_melt <- merge(crispr_melt, dep_melt, by = c("DepMap_ID", "Hugo_Symbol"), all.x = TRUE)
-# Merge cell line metadata
-crispr_melt <- merge(crispr_melt, ccl_info, by = "DepMap_ID", all.x = TRUE)
-crispr_melt <- merge(crispr_melt, crispr_meta, by = c("CCLE_Name", "DepMap_ID"), all.x = TRUE)
-
-# Merge mutation annotations
-maf_filt_crispr <- filter(maf_df, Hugo_Symbol %in% as.character(unique(crispr_melt$Hugo_Symbol)))
-crispr_muts <- merge(crispr_melt, maf_filt_crispr, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
-crispr_muts$Hugo_Symbol <- factor(crispr_muts$Hugo_Symbol)
-crispr_muts <- crispr_muts %>% mutate(Mutation_Status_Nonsilent = if_else(is.na(Mutation_Status_Nonsilent), "Wildtype", Mutation_Status_Nonsilent))
-# Summarize number of mutant and Wildtype cell lines
-crispr_muts_summ <- crispr_muts %>% group_by(Hugo_Symbol) %>%
-  summarize(N_Nonsilent_Wildtype = sum(Mutation_Status_Nonsilent == "Wildtype"),
-            N_Nonsilent_Mutant = sum(Mutation_Status_Nonsilent == "Mutant"))
-# Merge test results back into full dataset, which restores information lost in the summarization
-crispr_data <- merge(crispr_muts_summ, crispr_muts, by = "Hugo_Symbol")
-# Add Color columns
-crispr_data$Color_Nonsilent <- ifelse(crispr_data$Mutation_Status_Nonsilent == "Wildtype", "thistle", "darkorchid")
-crispr_data$Color_Nonsilent <- factor(crispr_data$Color_Nonsilent)
-
-# Cell line lineages
-crispr_data <- merge(crispr_data, ccl_converter, by = c("CCLE_Name", "DepMap_ID"), all.x = TRUE)
-levels(crispr_data$lineage_name) <- sort(levels(crispr_data$lineage_name), decreasing = TRUE)
-# Copy number
-crispr_data <- merge(crispr_data, cn_melt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
-# Gene expression (RPKM)
-ge_crispr_18Q3 <- filter(ge_melt_18Q3, Hugo_Symbol %in% as.character(unique(crispr_melt$Hugo_Symbol)))
-# ge_crispr_18Q4 <- filter(ge_melt_18Q4, Hugo_Symbol %in% as.character(unique(crispr_melt$Hugo_Symbol)))
-crispr_data <- merge(crispr_data, ge_crispr_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
-# crispr_data <- merge(crispr_data, ge_crispr_18Q4, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
-saveRDS(crispr_data, "./../htscreen_lineages_giant_files/crispr_data_18Q4.rds", compress = "xz")
-```
-
-```{r}
-crispr_data <- readRDS("./../htscreen_lineages_giant_files/crispr_data_18Q4.rds")
-crispr_data_ptmuts <- filter(crispr_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
-crispr_data_ptmuts$Keep_PtMut_Tests <- ifelse(crispr_data_ptmuts$Reference_Allele_Length == 1 | is.na(crispr_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(crispr_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
-crispr_data_ptmuts <- filter(crispr_data_ptmuts, Keep_PtMut_Tests == TRUE)
-
-# Filter CRISPR for G2P genes in G2P
-crispr_data_g2p <- filter(crispr_data_ptmuts, Hugo_Symbol %in% g2p_genes)
-crispr_data_g2p$Hugo_Symbol <- factor(crispr_data_g2p$Hugo_Symbol, levels = g2p_genes)
-crispr_data_g2p$Mutation_Status_Nonsilent <- factor(crispr_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-```
-
-# WILCOXON TESTS
-
---------------------------------------------------------------------------------
-
-Wilcoxon tests for assessing effect of mutation status on gene essentiality scores (CRISPR) and AUC (CCLE, CTRP, and GDSC).
-
-## CRISPR
-
-Test G2P genes in lineage-agnostic context:
-```{r, eval=FALSE}
-crispr_signif_g2p_gene <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol"), data = crispr_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
-crispr_signif_g2p_gene <- adj_signif(crispr_signif_g2p_gene)
-crispr_signif_g2p_gene <- crispr_signif_g2p_gene[order(crispr_signif_g2p_gene$p),]
-saveRDS(crispr_signif_g2p_gene, "./data_munging/rds/crispr_signif_g2p_gene.rds")
-```
-
-```{r}
-crispr_signif_g2p_gene <- readRDS("./data_munging/rds/crispr_signif_g2p_gene.rds")
-crispr_signif_g2p_gene <- rbind(crispr_signif_g2p_gene, c("G6PD", rep(NA, 11)))
-knitr::kable(crispr_signif_g2p_gene[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results for Level A point mutations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-Plot results of `crispr_signif_g2p_gene` tests:
-```{r fig.height=7, fig.width=12}
-crispr_data_signif_g2p_gene_filt <- filter(crispr_data_ptmuts, Hugo_Symbol %in% as.character(crispr_signif_g2p_gene$Hugo_Symbol))
-crispr_data_signif_g2p_gene <- merge(crispr_data_signif_g2p_gene_filt, crispr_signif_g2p_gene, by = "Hugo_Symbol")
-crispr_data_signif_g2p_gene$Hugo_Symbol <- ordered(crispr_data_signif_g2p_gene$Hugo_Symbol, levels = as.character(crispr_signif_g2p_gene$Hugo_Symbol))
-
-crispr_data_signif_g2p_gene <- merge(crispr_data_signif_g2p_gene, crispr_data_signif_g2p_gene %>% group_by(Hugo_Symbol) %>% summarize(Text_y = max(Score)), by = "Hugo_Symbol")
-crispr_data_signif_g2p_gene_text <- unique(data.frame(p.signif = crispr_data_signif_g2p_gene$p.signif, p.signif.adj = crispr_data_signif_g2p_gene$p.signif.adj,  Hugo_Symbol = crispr_data_signif_g2p_gene$Hugo_Symbol, Text_y = crispr_data_signif_g2p_gene$Text_y))
-
-crispr_data_signif_g2p_gene_plot <- ggplot(data = crispr_data_signif_g2p_gene, aes(x = Mutation_Status_Nonsilent, y = Score)) +
-  facet_wrap(~ Hugo_Symbol, drop = FALSE, nrow = 2, scales = "free_y") +
-  geom_jitter(aes(color = Mutation_Status_Nonsilent), alpha = 0.5, width = 0.3) +
-  geom_boxplot(color = "black", fill = NA, outlier.shape = NA) +
-  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
-  scale_color_manual(values = c("Mutant" = "darkorchid", "Wildtype" = "thistle")) +
-  geom_text(data = crispr_data_signif_g2p_gene_text, mapping = aes(x = 1.5, y = Text_y, label = p.signif), nudge_y = 0.2) +
-  theme(legend.position = "top", axis.text.x = element_blank(), axis.ticks.x = element_blank(), axis.title.x = element_blank()) +
-  labs(y = "CERES Score",
-       color = "Mutation Status",
-       title = "CERES scores for select Level A G2P genes",
-       subtitle = "Genes are sorted by increasing p-value.")
-crispr_data_signif_g2p_gene_plot
-
-# ggsave("./plots/manuscript/crispr_data_signif_g2p_gene_plot.png", crispr_data_signif_g2p_gene_plot, width = 12, height = 7, units = "in")
-```
-
-Test G2P genes in lineage-grouped context:
-```{r, eval=FALSE}
-crispr_signif_g2p_lineage <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "group_general_lineage_name"), data = crispr_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
-crispr_signif_g2p_lineage <- adj_signif(crispr_signif_g2p_lineage)
-crispr_signif_g2p_lineage <- crispr_signif_g2p_lineage[order(crispr_signif_g2p_lineage$p),]
-saveRDS(crispr_signif_g2p_lineage, "./data_munging/rds/crispr_signif_g2p_lineage.rds")
-# write.table(crispr_signif_g2p_lineage, file = "~/Desktop/crispr_signif_g2p_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
-```
-
-```{r}
-crispr_signif_g2p_lineage <- readRDS("./data_munging/rds/crispr_signif_g2p_lineage.rds")
-knitr::kable(filter(crispr_signif_g2p_lineage, p < 0.1)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant vs wildtype cell lines by lineage, p < 0.1 (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-Plot results of `crispr_signif_g2p_lineage` tests:
-```{r fig.height=18, fig.width=15, eval=TRUE}
-crispr_data_signif_g2p_lineage <- merge(crispr_data_signif_g2p_gene_filt, crispr_signif_g2p_lineage, by = c("Hugo_Symbol", "group_general_lineage_name"))
-crispr_data_signif_g2p_lineage$Hugo_Symbol <- ordered(crispr_data_signif_g2p_lineage$Hugo_Symbol, levels = as.character(unique((crispr_signif_g2p_lineage$Hugo_Symbol))))
-
-crispr_data_signif_g2p_lineage <- merge(crispr_data_signif_g2p_lineage, crispr_data_signif_g2p_lineage %>% group_by(Hugo_Symbol) %>% summarize(Text_y = max(Score)), by = "Hugo_Symbol")
-
-crispr_data_signif_g2p_lineage_text <- unique(data.frame(p.signif = crispr_data_signif_g2p_lineage$p.signif, p.signif.adj = crispr_data_signif_g2p_lineage$p.signif.adj,  group_general_lineage_name = crispr_data_signif_g2p_lineage$group_general_lineage_name, Hugo_Symbol = crispr_data_signif_g2p_lineage$Hugo_Symbol, Text_y = crispr_data_signif_g2p_lineage$Text_y))
-
-crispr_data_signif_g2p_lineage_plot <- ggplot(data = crispr_data_signif_g2p_lineage, aes(x = group_general_lineage_name, y = Score)) +
-  facet_wrap(~ Hugo_Symbol, drop = FALSE, nrow = 6, scales = "free_y") +
-  geom_point(aes(color = Mutation_Status_Nonsilent), alpha = 0.5) +
-  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
-  scale_color_manual(values = c("Mutant" = "darkorchid", "Wildtype" = "thistle")) +
-  geom_text(data = crispr_data_signif_g2p_lineage_text, mapping = aes(x = group_general_lineage_name, y = Text_y, label = p.signif), angle = 90, vjust = 0.8, nudge_y = 0.1) +
-  theme(legend.position = "top", axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 10)) +
-  labs(y = "CERES Score",
-       x = "Lineage",
-       color = "Mutation Status",
-       title = "CERES score by cell line lineage for significant Level A G2P genes",
-       subtitle = "* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001\nGenes are sorted by increasing lineage-agnostic p-value.")
-crispr_data_signif_g2p_lineage_plot
-
-# write.table(crispr_data_signif_g2p_lineage, file = "~/Desktop/crispr_data_signif_g2p_lineage_20181213.tsv", quote = FALSE, sep = "\t")
-# ggsave("./plots/manuscript/crispr_data_signif_g2p_lineage_plot.png", crispr_data_signif_g2p_lineage_plot, width = 15, height = 18, units = "in")
-```
-
-Count mutant/wildtype calls in each gene-lineage group:
-```{r}
-crispr_data_signif_g2p_lineage_summ <- crispr_data_signif_g2p_lineage %>% group_by(Hugo_Symbol, group_general_lineage_name, Mutation_Status_Nonsilent) %>% tally()
-
-# write.table(crispr_data_signif_g2p_lineage_summ, file = "~/Desktop/crispr_data_signif_g2p_lineage_summ_20181005.tsv", quote = FALSE, sep = "\t")
-
-knitr::kable(crispr_data_signif_g2p_lineage_summ, caption = "Mutant/Wildtype counts for gene-lineage combinations") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-## CCLE
-
-Drug metadata:
-```{r}
-drug_meta <- read.delim("./data_munging/drug_id_drug_name_table_10_12_2018.tsv", sep = "\t", header = FALSE)
-colnames(drug_meta) <- c("CID", "Drug")
-drug_meta$Drug <- tolower(drug_meta$Drug)
-```
-
-Test all CRISPR genes in lineage-agnostic context:
-```{r, eval=FALSE}
-ccle <- read.delim("./data_munging/data_drug_auc_ccle_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
-ccle <- merge(drug_meta, ccle, by = "CID")
-ccle_melt <- melt(ccle, id.vars = c("CID", "Drug"), measure.vars = colnames(ccle)[3:ncol(ccle)], variable.name = "accession_id", value.name = "AUC")
-ccle_grid <- expand.grid("accession_id" = unique(ccle_melt$accession_id), "Hugo_Symbol" = as.character(unique(crispr_data$Hugo_Symbol)))
-system.time({ ccle_data_allgenes <- WilcoxonByDrugAllGenes(ccle_melt, ccle_grid, "CCLE") })
-saveRDS(ccle_data_allgenes, "./data_munging/rds/ccle_data_18Q3_allgenes.rds", compress = "xz")
-
-# user   system  elapsed 
-# 1483.399  262.649 1901.698 
-```
-
-```{r}
-ccle_data_allgenes <- readRDS("./data_munging/rds/ccle_data_18Q3_allgenes.rds")
-ccle_data_allgenes <- ccle_data_allgenes[order(ccle_data_allgenes$p),]
-knitr::kable(ccle_data_allgenes[1:1000, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: by-drug Wilcoxon test results for point mutations in genes targeted in CRISPR screen (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-Test G2P genes in lineage-agnostic context:
-```{r, eval=FALSE}
-# G2P drug-gene associations only
-ccle_signif_g2p <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene", data = ccle_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
-ccle_signif_g2p <- adj_signif(ccle_signif_g2p)
-ccle_signif_g2p <- ccle_signif_g2p[order(ccle_signif_g2p$p),]
-saveRDS(ccle_signif_g2p, "./data_munging/rds/ccle_signif_g2p_gene.rds")
-
-# Grid comparisons of G2P drugs and genes
-ccle_signif_g2p_grid <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = c("Drug_Gene"), data = ccle_data_g2p_grid, method = "wilcox.test", p.adjust.method = "BH")
-ccle_signif_g2p_grid <- adj_signif(ccle_signif_g2p_grid)
-ccle_signif_g2p_grid <- ccle_signif_g2p_grid[order(ccle_signif_g2p_grid$p),]
-saveRDS(ccle_signif_g2p_grid, "./data_munging/rds/ccle_signif_g2p_grid.rds")
-```
-
-```{r}
-ccle_signif_g2p <- readRDS("./data_munging/rds/ccle_signif_g2p_gene.rds")
-knitr::kable(ccle_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-
-ccle_signif_g2p_grid <- readRDS("./data_munging/rds/ccle_signif_g2p_grid.rds")
-knitr::kable(ccle_signif_g2p_grid[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-Test G2P genes in lineage-grouped context:
-```{r, eval=FALSE}
-ccle_signif_grid_lineage <- lapply(unique(ccle_data_g2p_grid$Drug), WilcoxonByDrug, dataset = ccle_data_g2p_grid, data_name = "ccle", grouping_var = "lineage")
-names(ccle_signif_grid_lineage) <- unique(ccle_signif_grid_lineage$Drug)
-ccle_signif_grid_lineage <- rbindlist(ccle_signif_grid_lineage, use.names = TRUE)
-ccle_signif_grid_lineage <- ccle_signif_grid_lineage[order(ccle_signif_grid_lineage$p),]
-saveRDS(ccle_signif_grid_lineage, "./data_munging/rds/ccle_signif_grid_lineage.rds")
-
-ccle_signif_g2p_lineage <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene_Lin", data = ccle_data_g2p_dgl, method = "wilcox.test", p.adjust.method = "BH")
-ccle_signif_g2p_lineage <- adj_signif(ccle_signif_g2p_lineage)
-ccle_signif_g2p_lineage <- ccle_signif_g2p_lineage[order(ccle_signif_g2p_lineage$p),]
-saveRDS(ccle_signif_g2p_lineage, "./data_munging/rds/ccle_signif_g2p_lineage.rds")
-```
-
-```{r}
-ccle_signif_g2p_lineage <- readRDS("./data_munging/rds/ccle_signif_g2p_lineage.rds")
-ccle_signif_grid_lineage <- readRDS("./data_munging/rds/ccle_signif_grid_lineage.rds")
-
-knitr::kable(ccle_signif_g2p_lineage[, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-
-knitr::kable(ccle_signif_grid_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-## CTRP
-
-Test all CRISPR genes in lineage-agnostic context:
-```{r, eval=FALSE}
-ctrp <- read.delim("./data_munging/data_drug_auc_ctrp_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
-ctrp <- merge(drug_meta, ctrp, by = "CID")
-ctrp_melt <- melt(ctrp, id.var  s = c("CID", "Drug"), measure.vars = colnames(ctrp)[3:ncol(ctrp)], variable.name = "accession_id", value.name = "AUC")
-ctrp_grid <- expand.grid("accession_id" = unique(ctrp_melt$accession_id), "Hugo_Symbol" = as.character(unique(crispr_data$Hugo_Symbol)))
-ctrp_data_allgenes <- WilcoxonByDrugAllGenes(ctrp_melt, ctrp_grid, "CTRP")
-saveRDS(ctrp_data_allgenes, "./data_munging/rds/ctrp_data_18Q3_allgenes.rds", compress = "xz")
-```
-
-```{r}
-ctrp_data_allgenes <- readRDS("./data_munging/rds/ctrp_data_18Q3_allgenes.rds")
-ctrp_data_allgenes <- ctrp_data_allgenes[order(ctrp_data_allgenes$p),]
-knitr::kable(ctrp_data_allgenes[1:1000, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: by-drug Wilcoxon test results for point mutations in genes targeted in CRISPR screen (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-Test G2P genes in lineage-agnostic context:
-```{r, eval=FALSE}
-ctrp_signif_g2p <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene", data = ctrp_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
-ctrp_signif_g2p <- adj_signif(ctrp_signif_g2p)
-ctrp_signif_g2p <- ctrp_signif_g2p[order(ctrp_signif_g2p$p),]
-saveRDS(ctrp_signif_g2p, "./data_munging/rds/ctrp_signif_g2p_gene.rds")
-
-# Grid comparisons of G2P drugs and genes
-ctrp_signif_g2p_grid <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene", data = ctrp_data_g2p_grid, method = "wilcox.test", p.adjust.method = "BH")
-ctrp_signif_g2p_grid <- adj_signif(ctrp_signif_g2p_grid)
-ctrp_signif_g2p_grid <- ctrp_signif_g2p_grid[order(ctrp_signif_g2p_grid$p),]
-saveRDS(ctrp_signif_g2p_grid, "./data_munging/rds/ctrp_signif_g2p_grid.rds")
-```
-
-```{r}
-ctrp_signif_g2p <- readRDS("./data_munging/rds/ctrp_signif_g2p_gene.rds")
-knitr::kable(ctrp_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-
-ctrp_signif_g2p_grid <- readRDS("./data_munging/rds/ctrp_signif_g2p_grid.rds")
-knitr::kable(ctrp_signif_g2p_grid[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-Test G2P genes in lineage-grouped context:
-```{r, eval=FALSE}
-ctrp_signif_grid_lineage <- lapply(unique(ctrp_data_g2p_grid$Drug), WilcoxonByDrug, dataset = ctrp_data_g2p_grid, data_name = "ctrp", grouping_var = "lineage")
-names(ctrp_signif_grid_lineage) <- unique(ctrp_signif_grid_lineage$Drug)
-ctrp_signif_grid_lineage <- rbindlist(ctrp_signif_grid_lineage, use.names = TRUE)
-ctrp_signif_grid_lineage <- ctrp_signif_grid_lineage[order(ctrp_signif_grid_lineage$p),]
-saveRDS(ctrp_signif_grid_lineage, "./data_munging/rds/ctrp_signif_grid_lineage.rds")
-
-ctrp_signif_g2p_lineage <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene_Lin", data = ctrp_data_g2p_dgl, method = "wilcox.test", p.adjust.method = "BH")
-ctrp_signif_g2p_lineage <- adj_signif(ctrp_signif_g2p_lineage)
-ctrp_signif_g2p_lineage <- ctrp_signif_g2p_lineage[order(ctrp_signif_g2p_lineage$p),]
-saveRDS(ctrp_signif_g2p_lineage, "./data_munging/rds/ctrp_signif_g2p_lineage.rds")
-```
-
-```{r}
-ctrp_signif_g2p_lineage <- readRDS("./data_munging/rds/ctrp_signif_g2p_lineage.rds")
-ctrp_signif_grid_lineage <- readRDS("./data_munging/rds/ctrp_signif_grid_lineage.rds")
-
-knitr::kable(ctrp_signif_g2p_lineage[, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-
-knitr::kable(ctrp_signif_grid_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-## GDSC
-
-Test all CRISPR genes in lineage-agnostic context:
-```{r, eval=FALSE}
-gdsc <- read.delim("./data_munging/data_drug_auc_gdsc_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
-gdsc <- merge(drug_meta, gdsc, by = "CID")
-gdsc_melt <- melt(gdsc, id.vars = c("CID", "Drug"), measure.vars = colnames(gdsc)[3:ncol(gdsc)], variable.name = "accession_id", value.name = "AUC")
-gdsc_grid <- expand.grid("accession_id" = unique(gdsc_melt$accession_id), "Hugo_Symbol" = as.character(unique(crispr_data$Hugo_Symbol)))
-system.time({ gdsc_data_allgenes <- WilcoxonByDrugAllGenes(gdsc_melt, gdsc_grid, "GDSC") })
-saveRDS(gdsc_data_allgenes, "./data_munging/rds/gdsc_data_18Q3_allgenes.rds", compress = "xz")
-```
-
-```{r}
-gdsc_data_allgenes <- readRDS("./data_munging/rds/gdsc_data_18Q3_allgenes.rds")
-gdsc_data_allgenes <- gdsc_data_allgenes[order(gdsc_data_allgenes$p),]
-knitr::kable(gdsc_data_allgenes[1:1000, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: by-drug Wilcoxon test results for point mutations in genes targeted in CRISPR screen (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-Test G2P genes in lineage-agnostic context:
-```{r, eval=FALSE}
-gdsc_signif_g2p <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene", data = gdsc_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
-gdsc_signif_g2p <- adj_signif(gdsc_signif_g2p)
-gdsc_signif_g2p <- gdsc_signif_g2p[order(gdsc_signif_g2p$p),]
-saveRDS(gdsc_signif_g2p, "./data_munging/rds/gdsc_signif_g2p_gene.rds")
-
-# Grid comparisons of G2P drugs and genes
-gdsc_signif_g2p_grid <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene", data = gdsc_data_g2p_grid, method = "wilcox.test", p.adjust.method = "BH")
-gdsc_signif_g2p_grid <- adj_signif(gdsc_signif_g2p_grid)
-gdsc_signif_g2p_grid <- gdsc_signif_g2p_grid[order(gdsc_signif_g2p_grid$p),]
-saveRDS(gdsc_signif_g2p_grid, "./data_munging/rds/gdsc_signif_g2p_grid.rds")
-```
-
-```{r}
-gdsc_signif_g2p <- readRDS("./data_munging/rds/gdsc_signif_g2p_gene.rds")
-knitr::kable(gdsc_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-
-gdsc_signif_g2p_grid <- readRDS("./data_munging/rds/gdsc_signif_g2p_grid.rds")
-knitr::kable(gdsc_signif_g2p_grid[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-Test G2P genes in lineage-grouped context:
-```{r, eval=FALSE}
-gdsc_signif_grid_lineage <- lapply(unique(gdsc_data_g2p_grid$Drug), WilcoxonByDrug, dataset = gdsc_data_g2p_grid, data_name = "gdsc", grouping_var = "lineage")
-names(gdsc_signif_grid_lineage) <- unique(gdsc_signif_grid_lineage$Drug)
-gdsc_signif_grid_lineage <- rbindlist(gdsc_signif_grid_lineage, use.names = TRUE)
-gdsc_signif_grid_lineage <- gdsc_signif_grid_lineage[order(gdsc_signif_grid_lineage$p),]
-saveRDS(gdsc_signif_grid_lineage, "./data_munging/rds/gdsc_signif_grid_lineage.rds")
-
-gdsc_signif_g2p_lineage <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene_Lin", data = gdsc_data_g2p_dgl, method = "wilcox.test", p.adjust.method = "BH")
-gdsc_signif_g2p_lineage <- adj_signif(gdsc_signif_g2p_lineage)
-gdsc_signif_g2p_lineage <- gdsc_signif_g2p_lineage[order(gdsc_signif_g2p_lineage$p),]
-saveRDS(gdsc_signif_g2p_lineage, "./data_munging/rds/gdsc_signif_g2p_lineage.rds")
-```
-
-```{r}
-gdsc_signif_g2p_lineage <- readRDS("./data_munging/rds/gdsc_signif_g2p_lineage.rds")
-gdsc_signif_grid_lineage <- readRDS("./data_munging/rds/gdsc_signif_grid_lineage.rds")
-
-knitr::kable(gdsc_signif_g2p_lineage[, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-
-knitr::kable(gdsc_signif_grid_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-# PEARSON/SPEARMAN CORRELATIONS
-
---------------------------------------------------------------------------------
-
-Pearson correlations for assessing effect of gene expression and copy number on gene essentiality score and AUC.
-
-## CRISPR
-
-```{r}
-crispr_pearson_res_GE <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>%
-                         summarize(p = cor.test(y = Score, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
-                                   corr = cor.test(y = Score, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
-                                   Metric = "Gene Expression")
-crispr_pearson_res_CN <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>%
-                         summarize(p = cor.test(y = Score, x = CN, method = "pearson", use = "complete.obs")$p.value,
-                                   corr = cor.test(y = Score, x = CN, method = "pearson", use = "complete.obs")$estimate,
-                                   Metric = "Copy Number")
-crispr_spearman_res_GE <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>%
-                          summarize(p = cor.test(y = Score, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
-                                    corr = cor.test(y = Score, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
-                                    Metric = "Gene Expression")
-crispr_spearman_res_CN <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>%
-                          summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value,
-                                    corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate,
-                                    Metric = "Copy Number")
-```
-
-## Drug screens
-
-```{r}
-g2p_druggene_tally <- g2p_filt %>% group_by(Drug_Gene) %>% tally() %>% drop_na()
-
-# CCLE
-ccle_cor_res <- ccle_data_g2p_grid %>% group_by(Drug_Gene) %>%
-                    summarize(Pearson_Corr_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
-                              Pearson_Pval_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
-                              Pearson_Corr_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$estimate,
-                              Pearson_Pval_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$p.value,
-                              Spearman_Corr_GE = cor.test(y = AUC, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
-                              Spearman_Pval_GE = cor.test(y = AUC, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
-                              Spearman_Corr_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$estimate,
-                              Spearman_Pval_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$p.value)
-ccle_cor_res <- merge(g2p_druggene_tally, ccle_cor_res, by = "Drug_Gene", all.y = TRUE)
-ccle_cor_res$n <- ifelse(is.na(ccle_cor_res$n), 0, ccle_cor_res$n)
-ccle_cor_res$InG2P <- ifelse(ccle_cor_res$n != 0, "Yes", "No")
-ccle_cor_res$Dataset <- "CCLE"
-ccle_pearson_ttest_GE <- t.test(ccle_cor_res$Pearson_Corr_GE ~ ccle_cor_res$InG2P)
-ccle_pearson_ttest_res_GE <- paste0("t(", round(ccle_pearson_ttest_GE$parameter, 0), ") = ", round(ccle_pearson_ttest_GE$statistic, 2), ", p = ", round(ccle_pearson_ttest_GE$p.value, 2))
-ccle_pearson_ttest_CN <- t.test(ccle_cor_res$Pearson_Corr_CN ~ ccle_cor_res$InG2P)
-ccle_pearson_ttest_res_CN <- paste0("t(", round(ccle_pearson_ttest_CN$parameter, 0), ") = ", round(ccle_pearson_ttest_CN$statistic, 2), ", p = ", round(ccle_pearson_ttest_CN$p.value, 2))
-ccle_spearman_ttest_GE <- t.test(ccle_cor_res$Spearman_Corr_GE ~ ccle_cor_res$InG2P)
-ccle_spearman_ttest_res_GE <- paste0("t(", round(ccle_spearman_ttest_GE$parameter, 0), ") = ", round(ccle_spearman_ttest_GE$statistic, 2), ", p = ", round(ccle_spearman_ttest_GE$p.value, 2))
-ccle_spearman_ttest_CN <- t.test(ccle_cor_res$Spearman_Corr_CN ~ ccle_cor_res$InG2P)
-ccle_spearman_ttest_res_CN <- paste0("t(", round(ccle_spearman_ttest_CN$parameter, 0), ") = ", round(ccle_spearman_ttest_CN$statistic, 2), ", p = ", formatC(ccle_spearman_ttest_CN$p.value, 2, format = "f"))
-
-# CTRP
-ctrp_cor_res <- ctrp_data_g2p_grid %>% group_by(Drug_Gene) %>%
-                    summarize(Pearson_Corr_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
-                              Pearson_Pval_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
-                              Pearson_Corr_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$estimate,
-                              Pearson_Pval_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$p.value,
-                              Spearman_Corr_GE = cor.test(y = AUC, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
-                              Spearman_Pval_GE = cor.test(y = AUC, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
-                              Spearman_Corr_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$estimate,
-                              Spearman_Pval_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$p.value)
-ctrp_cor_res <- merge(g2p_druggene_tally, ctrp_cor_res, by = "Drug_Gene", all.y = TRUE)
-ctrp_cor_res$n <- ifelse(is.na(ctrp_cor_res$n), 0, ctrp_cor_res$n)
-ctrp_cor_res$InG2P <- ifelse(ctrp_cor_res$n != 0, "Yes", "No")
-ctrp_cor_res$Dataset <- "CTRP"
-ctrp_pearson_ttest_GE <- t.test(ctrp_cor_res$Pearson_Corr_GE ~ ctrp_cor_res$InG2P)
-ctrp_pearson_ttest_res_GE <- paste0("t(", round(ctrp_pearson_ttest_GE$parameter, 0), ") = ", round(ctrp_pearson_ttest_GE$statistic, 2), ", p ", ifelse(round(ctrp_pearson_ttest_GE$p.value, 3) == 0, "< 0.001", paste0("= ", round(ctrp_pearson_ttest_GE$p.value, 3))))
-ctrp_pearson_ttest_CN <- t.test(ctrp_cor_res$Pearson_Corr_CN ~ ctrp_cor_res$InG2P)
-ctrp_pearson_ttest_res_CN <- paste0("t(", round(ctrp_pearson_ttest_CN$parameter, 0), ") = ", round(ctrp_pearson_ttest_CN$statistic, 2), ", p = ", round(ctrp_pearson_ttest_CN$p.value, 3))
-ctrp_spearman_ttest_GE <- t.test(ctrp_cor_res$Spearman_Corr_GE ~ ctrp_cor_res$InG2P)
-ctrp_spearman_ttest_res_GE <- paste0("t(", round(ctrp_spearman_ttest_GE$parameter, 0), ") = ", round(ctrp_spearman_ttest_GE$statistic, 2), ", p = ", round(ctrp_spearman_ttest_GE$p.value, 2))
-ctrp_spearman_ttest_CN <- t.test(ctrp_cor_res$Spearman_Corr_CN ~ ctrp_cor_res$InG2P)
-ctrp_spearman_ttest_res_CN <- paste0("t(", round(ctrp_spearman_ttest_CN$parameter, 0), ") = ", round(ctrp_spearman_ttest_CN$statistic, 2), ", p = ", round(ctrp_spearman_ttest_CN$p.value, 2))
-
-# GDSC
-gdsc_cor_res <- gdsc_data_g2p_grid %>% group_by(Drug_Gene) %>%
-                    summarize(Pearson_Corr_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
-                              Pearson_Pval_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
-                              Pearson_Corr_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$estimate,
-                              Pearson_Pval_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$p.value,
-                              Spearman_Corr_GE = cor.test(y = AUC, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
-                              Spearman_Pval_GE = cor.test(y = AUC, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
-                              Spearman_Corr_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$estimate,
-                              Spearman_Pval_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$p.value)
-gdsc_cor_res <- merge(g2p_druggene_tally, gdsc_cor_res, by = "Drug_Gene", all.y = TRUE)
-gdsc_cor_res$n <- ifelse(is.na(gdsc_cor_res$n), 0, gdsc_cor_res$n)
-gdsc_cor_res$InG2P <- ifelse(gdsc_cor_res$n != 0, "Yes", "No")
-gdsc_cor_res$Dataset <- "GDSC"
-gdsc_pearson_ttest_GE <- t.test(gdsc_cor_res$Pearson_Corr_GE ~ gdsc_cor_res$InG2P)
-gdsc_pearson_ttest_res_GE <- paste0("t(", round(gdsc_pearson_ttest_GE$parameter, 0), ") = ", round(gdsc_pearson_ttest_GE$statistic, 2), ", p = ", round(gdsc_pearson_ttest_GE$p.value, 3))
-gdsc_pearson_ttest_CN <- t.test(gdsc_cor_res$Pearson_Corr_CN ~ gdsc_cor_res$InG2P)
-gdsc_pearson_ttest_res_CN <- paste0("t(", round(gdsc_pearson_ttest_CN$parameter, 0), ") = ", round(gdsc_pearson_ttest_CN$statistic, 2), ", p = ", round(gdsc_pearson_ttest_CN$p.value, 3))
-gdsc_spearman_ttest_GE <- t.test(gdsc_cor_res$Spearman_Corr_GE ~ gdsc_cor_res$InG2P)
-gdsc_spearman_ttest_res_GE <- paste0("t(", round(gdsc_spearman_ttest_GE$parameter, 0), ") = ", round(gdsc_spearman_ttest_GE$statistic, 2), ", p = ", round(gdsc_spearman_ttest_GE$p.value, 2))
-gdsc_spearman_ttest_CN <- t.test(gdsc_cor_res$Spearman_Corr_CN ~ gdsc_cor_res$InG2P)
-gdsc_spearman_ttest_res_CN <- paste0("t(", round(gdsc_spearman_ttest_CN$parameter, 0), ") = ", round(gdsc_spearman_ttest_CN$statistic, 2), ", p = ", round(gdsc_spearman_ttest_CN$p.value, 2))
-
-# All
-g2p_cor <- rbind(ccle_cor_res, ctrp_cor_res, gdsc_cor_res)
-g2p_cor$Pearson_GE_Abs <- abs(g2p_cor$Pearson_Corr_GE)
-g2p_cor$Pearson_GE_Sign <- ifelse(sign(g2p_cor$Pearson_Corr_GE) == 1, "+", ifelse(sign(g2p_cor$Pearson_Corr_GE) == -1, "-", "0"))
-g2p_cor$Pearson_CN_Abs <- abs(g2p_cor$Pearson_Corr_CN)
-g2p_cor$Pearson_CN_Sign <- ifelse(sign(g2p_cor$Pearson_Corr_CN) == 1, "+", ifelse(sign(g2p_cor$Pearson_Corr_CN) == -1, "-", "0"))
-g2p_cor$Spearman_GE_Abs <- abs(g2p_cor$Spearman_Corr_GE)
-g2p_cor$Spearman_GE_Sign <- ifelse(sign(g2p_cor$Spearman_Corr_GE) == 1, "+", ifelse(sign(g2p_cor$Spearman_Corr_GE) == -1, "-", "0"))
-g2p_cor$Spearman_CN_Abs <- abs(g2p_cor$Spearman_Corr_CN)
-g2p_cor$Spearman_CN_Sign <- ifelse(sign(g2p_cor$Spearman_Corr_CN) == 1, "+", ifelse(sign(g2p_cor$Spearman_Corr_CN) == -1, "-", "0"))
-g2p_cor_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"),
-                               Pearson_Test_Results_GE = c(ccle_pearson_ttest_res_GE, ctrp_pearson_ttest_res_GE, gdsc_pearson_ttest_res_GE),
-                               Pearson_Test_Results_CN = c(ccle_pearson_ttest_res_CN, ctrp_pearson_ttest_res_CN, gdsc_pearson_ttest_res_CN),
-                               Spearman_Test_Results_GE = c(ccle_spearman_ttest_res_GE, ctrp_spearman_ttest_res_GE, gdsc_spearman_ttest_res_GE),
-                               Spearman_Test_Results_CN = c(ccle_spearman_ttest_res_CN, ctrp_spearman_ttest_res_CN, gdsc_spearman_ttest_res_CN))
-```
-
-# SUMMARIES
-
---------------------------------------------------------------------------------
-
-## CRISPR: Mutation status counts
-
-```{r}
-crispr_data_g2p_summ <- unique(crispr_data_g2p[, c("Hugo_Symbol", "N_Nonsilent_Mutant", "N_Nonsilent_Wildtype")])
-crispr_data_g2p_summ$Percent_Mutant <- crispr_data_g2p_summ$N_Nonsilent_Mutant / (crispr_data_g2p_summ$N_Nonsilent_Mutant + crispr_data_g2p_summ$N_Nonsilent_Wildtype) * 100
-rownames(crispr_data_g2p_summ) <- NULL
-
-# write.table(crispr_data_g2p_summ, file = "~/Desktop/crispr_data_g2p_summ_20181003.tsv", quote = FALSE, sep = "\t")
-
-knitr::kable(crispr_data_g2p_summ, caption = "CRISPR: Level A G2P genes mutation status summary") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-## G2P tallies and summary stats
-
-```{r}
-print("Drug-Gene")
-g2p_druggene_tally <- g2p_filt %>% group_by(Drug_Gene) %>% tally() %>% drop_na()
-nrow(g2p_druggene_tally)
-range(g2p_druggene_tally$n)
-mean(g2p_druggene_tally$n)
-sd(g2p_druggene_tally$n)
-
-print("Drug")
-g2p_drug_tally <- g2p_filt %>% group_by(Drug) %>% tally() %>% drop_na()
-range(g2p_drug_tally$n)
-mean(g2p_drug_tally$n)
-sd(g2p_drug_tally$n)
-
-print("Gene")
-g2p_gene_tally <- g2p_filt %>% group_by(Gene) %>% tally() %>% drop_na()
-range(g2p_gene_tally$n)
-mean(g2p_gene_tally$n)
-sd(g2p_gene_tally$n)
-
-print("Drug-Gene-Lineage")
-g2p_dgl_tally <- g2p_filt %>% group_by(Drug, Gene, Drug_Gene, group_general_lineage_name) %>% tally() %>% drop_na()
-nrow(g2p_dgl_tally)
-length(unique(g2p_dgl_tally$Drug))
-length(unique(g2p_dgl_tally$Gene))
-unique(g2p_filt$Phenotype.Description)
-```
-
-## Lineage-agnostic
-
-### Mut
-
-CRISPR mutation status plots of p-values:
-```{r fig.height=1.5, fig.width=12}
-crispr_signif_g2p_gene$y_label <- "CRISPR"
-crispr_signif_g2p_gene$Hugo_Symbol <- factor(crispr_signif_g2p_gene$Hugo_Symbol, levels = g2p_genes)
-crispr_signif_g2p_gene$p <- as.numeric(as.character(crispr_signif_g2p_gene$p))
-
-crispr_mut_heatmap_plot <- ggplot(data = crispr_signif_g2p_gene, aes(x = Hugo_Symbol, y = y_label)) +
-  geom_tile(aes(fill = p)) +
-  scale_fill_gradientn(colors = c("darkgreen", "honeydew", "white"), values = c(0, 0.05, 1), na.value = "darksalmon") +
-  scale_x_discrete(drop = FALSE) +
-  theme(axis.title.y = element_blank(), axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 10)) +
-  labs(x = "Gene")
-crispr_mut_heatmap_plot
-
-# write.table(crispr_signif_g2p_gene, file = "~/Desktop/crispr_signif_g2p_gene_20181203.csv", quote = FALSE, sep = ",", row.names = FALSE)
-# ggsave("./plots/manuscript/crispr_mut_heatmap_plot_example.png", crispr_mut_heatmap_plot, device = "png", dpi = 450, width = 12, height = 1.5, units = "in")
-```
-
-```{r}
-ccle_mut_summ <- merge(g2p_druggene_tally, ccle_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
-ccle_mut_summ$n <- ifelse(is.na(ccle_mut_summ$n), 0, ccle_mut_summ$n)
-ccle_mut_summ$InG2P <- ifelse(ccle_mut_summ$n != 0, "Yes", "No")
-ccle_mut_summ$Dataset <- "CCLE"
-ccle_p_ttest <- t.test(ccle_mut_summ$p ~ ccle_mut_summ$InG2P)
-ccle_p_ttest_res <- paste0("t(", round(ccle_p_ttest$parameter, 0), ") = ", round(ccle_p_ttest$statistic, 2), ", p = ", round(ccle_p_ttest$p.value, 2))
-
-ctrp_mut_summ <- merge(g2p_druggene_tally, ctrp_signif_g2p_grid[, c("`Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
-ctrp_mut_summ$n <- ifelse(is.na(ctrp_mut_summ$n), 0, ctrp_mut_summ$n)
-ctrp_mut_summ$InG2P <- ifelse(ctrp_mut_summ$n != 0, "Yes", "No")
-ctrp_mut_summ$Dataset <- "CTRP"
-ctrp_p_ttest <- t.test(ctrp_mut_summ$p ~ ctrp_mut_summ$InG2P)
-ctrp_p_ttest_res <- paste0("t(", round(ctrp_p_ttest$parameter, 0), ") = ", round(ctrp_p_ttest$statistic, 2), ", p = ", formatC(ctrp_p_ttest$p.value, digits = 2, format = "f"))
-
-gdsc_mut_summ <- merge(g2p_druggene_tally, gdsc_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
-gdsc_mut_summ$n <- ifelse(is.na(gdsc_mut_summ$n), 0, gdsc_mut_summ$n)
-gdsc_mut_summ$InG2P <- ifelse(gdsc_mut_summ$n != 0, "Yes", "No")
-gdsc_mut_summ$Dataset <- "GDSC"
-gdsc_p_ttest <- t.test(gdsc_mut_summ$p ~ gdsc_mut_summ$InG2P)
-gdsc_p_ttest_res <- paste0("t(", round(gdsc_p_ttest$parameter, 0), ") = ", round(gdsc_p_ttest$statistic, 2), ", p = ", formatC(gdsc_p_ttest$p.value, digits = 2, format = "f"))
-
-g2p_mut_all_summ <- rbind(ccle_mut_summ, ctrp_mut_summ, gdsc_mut_summ)
-g2p_mut_all_summ$p_log10 <- -log10(g2p_mut_all_summ$p)
-g2p_mut_all_summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"), Test_Results_p = c(ccle_p_ttest_res, ctrp_p_ttest_res, gdsc_p_ttest_res))
-g2p_mut_all_summ$Drug_Gene_Ordered <- factor(g2p_mut_all_summ$Drug_Gene, levels = as.character(unique(g2p_mut_all_summ$Drug_Gene)), labels = sapply(strsplit(x = as.character(unique(g2p_mut_all_summ$Drug_Gene)), split = "_"), function(x) paste0(x[1], "\n", x[2])))
-```
-
-```{r fig.height=5, fig.width=12}
-plot_p_point <- ggplot(data = g2p_mut_all_summ, aes(x = p, y = n, label = Drug_Gene)) +
-  facet_wrap(~ Dataset, scales = "free_x") +
-  geom_point(mapping = aes(color = InG2P), alpha = 0.5) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
-  geom_text_repel(data = subset(g2p_druggene_all_summ, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
-  geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = 0.5, y = 115, label = Test_Results_p)) +
-  labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations") +
-  theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
-
-plot_p_box <- ggplot(data = g2p_mut_all_summ) +
-  facet_wrap(~ Dataset, scales = "free_x") +
-  geom_violin(mapping = aes(color = InG2P, fill = InG2P, y = p, x = InG2P), alpha = 0.35) +
-  geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), width = 0.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  coord_flip() +
-  labs(x = "In G2P?") +
-  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
-plot_p_point <- ggplot_gtable(ggplot_build(plot_p_point))
-plot_p_box <- ggplot_gtable(ggplot_build(plot_p_box))
-p_maxWidth <-  grid::unit.pmax(plot_p_point$widths, plot_p_box$widths)
-plot_p_point$widths <- as.list(p_maxWidth)
-plot_p_box$widths <- as.list(p_maxWidth)
-g2p_mut_plot <- cowplot::plot_grid(plot_p_box,
-                   plot_p_point,
-                   nrow = 2,
-                   rel_heights = c(1, 4))
-g2p_mut_plot
-
-# ggsave("./plots/manuscript/g2p_mut_plot.png", g2p_mut_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
-```
-
-```{r, eval=FALSE}
-plot_p_point <- ggplot(data = g2p_mut_all_summ) +
-  facet_wrap(~ Dataset, scales = "free_x") +
-  geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = p, y = n), alpha = 0.5) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
-  geom_text(data = g2p_druggene_all_summ_text, mapping = aes(x = 0.5, y = 115, label = Test_Results_p)) +
-  labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations") +
-  theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
-
-plot_p_box <- ggplot(data = g2p_mut_all_summ) +
-  facet_wrap(~ Dataset, scales = "free_x") +
-  geom_violin(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.5) +
-  geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.75, width = 0.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  coord_flip() +
-  labs(x = "Level A G2P\nassociation") +
-  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
-plot <- subplot(plot_p_box, plot_p_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Gene-drug association p-value between mutation groups"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
-
-saveWidgetFix(widget = plot, file = "./plots/manuscript/g2p_mut_plot.html")
-```
-
-### GE
-
-#### Pearson
-
-```{r fig.height=5, fig.width=12}
-plot_ge_pearson_point <- ggplot(data = g2p_cor, aes(x = Pearson_GE_Abs, y = n, label = Drug_Gene)) +
-  facet_wrap(~ Dataset) +
-  geom_point(mapping = aes(fill = InG2P, color = InG2P, shape = Pearson_GE_Sign), alpha = 0.5, size = 1.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
-  scale_x_continuous(breaks = seq(0, 0.65, by = 0.1), labels = seq(0, 0.65, by = 0.1)) +
-  coord_cartesian(xlim = c(0, 0.65)) +
-  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
-  geom_text_repel(data = subset(g2p_cor, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
-  geom_text(data = g2p_cor_text, mapping = aes(x = 0.325, y = 115, label = Pearson_Test_Results_GE)) +
-  labs(x = "Pearson correlation coefficient (r) between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +
-  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
-  guides(color = FALSE, fill = FALSE, shape = FALSE)
-
-plot_ge_pearson_box <- ggplot(data = g2p_cor) +
-  facet_wrap(~ Dataset) +
-  geom_violin(mapping = aes(color = InG2P, fill = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.35) +
-  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), width = 0.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_y_continuous(breaks = seq(0, 0.65, by = 0.1), labels = seq(0, 0.65, by = 0.1)) +
-  coord_flip(ylim = c(0, 0.65)) +
-  labs(x = "In G2P?") +
-  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
-plot_ge_pearson_point <- ggplot_gtable(ggplot_build(plot_ge_pearson_point))
-plot_ge_pearson_box <- ggplot_gtable(ggplot_build(plot_ge_pearson_box))
-p_maxWidth <-  grid::unit.pmax(plot_ge_pearson_point$widths[2:3], plot_ge_pearson_box$widths[2:3])
-plot_ge_pearson_point$widths[2:3] <- p_maxWidth
-plot_ge_pearson_box$widths[2:3] <- p_maxWidth
-
-g2p_ge_pearson_plot <- cowplot::plot_grid(plot_ge_pearson_box, plot_ge_pearson_point, nrow = 2, rel_heights = c(1, 4))
-g2p_ge_pearson_plot
-
-# ggsave("./plots/manuscript/g2p_ge_pearson_plot.png", g2p_ge_pearson_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
-```
-
-```{r, eval=FALSE}
-plot_ge_point <- ggplot(data = g2p_cor) +
-  facet_wrap(~ Dataset) +
-  geom_point(mapping = aes(label = Drug_Gene, fill = InG2P, color = InG2P, shape = Pearson_GE_Sign, x = Pearson_GE_Abs, y = n, size = Pearson_Pval_GE), alpha = 0.5, size = 1.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
-  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
-  scale_x_continuous(breaks = pretty_breaks()) +
-  geom_text(data = g2p_cor_text, mapping = aes(x = 0.3, y = 115, label = Pearson_Test_Results_GE)) +
-  labs(x = "Pearson correlation coefficient (r) between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +
-  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
-  guides(color = FALSE, fill = FALSE) +
-  labs(shape = NULL)
-
-plot_ge_box <- ggplot(data = g2p_cor) +
-  facet_wrap(~ Dataset) +
-  geom_violin(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.5) +
-  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  coord_flip() +
-  labs(x = "In G2P?") +
-  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
-ge_pearson_plot <- subplot(plot_ge_box, plot_ge_point, nrows = 2, heights = c(0.2, 0.8), titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and gene expression"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
-
-saveWidgetFix(widget = ge_pearson_plot, file = "./plots/manuscript/g2p_ge_pearson_plot.html")
-```
-
-#### Spearman
-
-```{r fig.height=5, fig.width=12}
-plot_ge_spearman_point <- ggplot(data = g2p_cor, aes(x = Spearman_GE_Abs, y = n, label = Drug_Gene)) +
-  facet_wrap(~ Dataset) +
-  geom_point(mapping = aes(fill = InG2P, color = InG2P, shape = Spearman_GE_Sign), alpha = 0.5, size = 1.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
-  scale_x_continuous(breaks = seq(0, 0.65, by = 0.1), labels = seq(0, 0.65, by = 0.1)) +
-  coord_cartesian(xlim = c(0, 0.6)) +
-  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
-  geom_text_repel(data = subset(g2p_cor, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
-  geom_text(data = g2p_cor_text, mapping = aes(x = 0.3, y = 115, label = Spearman_Test_Results_GE)) +
-  labs(x = "Spearman correlation coefficient (r_s) between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +
-  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
-  guides(color = FALSE, fill = FALSE, shape = FALSE)
-
-plot_ge_spearman_box <- ggplot(data = g2p_cor) +
-  facet_wrap(~ Dataset) +
-  geom_violin(mapping = aes(color = InG2P, fill = InG2P, y = Spearman_GE_Abs, x = InG2P), alpha = 0.35) +
-  geom_boxplot(mapping = aes(color = InG2P, y = Spearman_GE_Abs, x = InG2P), width = 0.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_y_continuous(breaks = seq(0, 0.65, by = 0.1), labels = seq(0, 0.65, by = 0.1)) +
-  coord_flip(ylim = c(0, 0.6)) +
-  labs(x = "In G2P?") +
-  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
-plot_ge_spearman_point <- ggplot_gtable(ggplot_build(plot_ge_spearman_point))
-plot_ge_spearman_box <- ggplot_gtable(ggplot_build(plot_ge_spearman_box))
-p_maxWidth <-  grid::unit.pmax(plot_ge_spearman_point$widths[2:3], plot_ge_spearman_box$widths[2:3])
-plot_ge_spearman_point$widths[2:3] <- p_maxWidth
-plot_ge_spearman_box$widths[2:3] <- p_maxWidth
-
-g2p_ge_spearman_plot <- cowplot::plot_grid(plot_ge_spearman_box, plot_ge_spearman_point, nrow = 2, rel_heights = c(1, 4))
-g2p_ge_spearman_plot
-
-# ggsave("./plots/manuscript/g2p_ge_spearman_plot.png", g2p_ge_spearman_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
-```
-
-```{r, eval=FALSE}
-plot_ge_point <- ggplot(data = g2p_cor) +
-  facet_wrap(~ Dataset) +
-  geom_point(mapping = aes(label = Drug_Gene, fill = InG2P, color = InG2P, shape = Spearman_GE_Sign, x = Spearman_GE_Abs, y = n, size = Spearman_Pval_GE), alpha = 0.5, size = 1.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
-  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
-  scale_x_continuous(breaks = pretty_breaks()) +
-  geom_text(data = g2p_cor_text, mapping = aes(x = 0.3, y = 115, label = Spearman_Test_Results_GE)) +
-  labs(x = "Spearman correlation coefficient (r_s) between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +
-  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
-  guides(color = FALSE, fill = FALSE) +
-  labs(shape = NULL)
-
-plot_ge_box <- ggplot(data = g2p_cor) +
-  facet_wrap(~ Dataset) +
-  geom_violin(mapping = aes(color = InG2P, y = Spearman_GE_Abs, x = InG2P), alpha = 0.5) +
-  geom_boxplot(mapping = aes(color = InG2P, y = Spearman_GE_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  coord_flip() +
-  labs(x = "In G2P?") +
-  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
-ge_spearman_plot <- subplot(plot_ge_box, plot_ge_point, nrows = 2, heights = c(0.2, 0.8), titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Spearman correlation coefficient between drug-gene AUC and gene expression"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
-
-saveWidgetFix(widget = ge_spearman_plot, file = "./plots/manuscript/g2p_ge_spearman_plot.html")
-```
-
-### CN
-
-#### Pearson
-
-```{r fig.height=5, fig.width=12}
-plot_cn_pearson_point <- ggplot(data = g2p_cor, aes(x = Pearson_CN_Abs, y = n, label = Drug_Gene)) +
-  facet_wrap(~ Dataset) +
-  geom_point(mapping = aes(fill = InG2P, color = InG2P, shape = Pearson_CN_Sign), alpha = 0.5, size = 1.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
-  scale_x_continuous(breaks = seq(0, 0.65, by = 0.1), labels = seq(0, 0.65, by = 0.1)) +
-  coord_cartesian(xlim = c(0, 0.5)) +
-  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
-  geom_text_repel(data = subset(g2p_cor, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
-  geom_text(data = g2p_cor_text, mapping = aes(x = 0.25, y = 115, label = Pearson_Test_Results_CN)) +
-  labs(x = "Pearson correlation coefficient (r) between drug-gene AUC and copy number", y = "Number of level A G2P associations") +
-  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
-  guides(color = FALSE, fill = FALSE, shape = FALSE)
-
-plot_cn_pearson_box <- ggplot(data = g2p_cor) +
-  facet_wrap(~ Dataset) +
-  geom_violin(mapping = aes(color = InG2P, fill = InG2P, y = Pearson_CN_Abs, x = InG2P), alpha = 0.35) +
-  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_CN_Abs, x = InG2P), width = 0.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_y_continuous(breaks = seq(0, 0.65, by = 0.1), labels = seq(0, 0.65, by = 0.1)) +
-  coord_flip(ylim = c(0, 0.5)) +
-  labs(x = "In G2P?") +
-  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
-plot_cn_pearson_point <- ggplot_gtable(ggplot_build(plot_cn_pearson_point))
-plot_cn_pearson_box <- ggplot_gtable(ggplot_build(plot_cn_pearson_box))
-p_maxWidth <-  grid::unit.pmax(plot_cn_pearson_point$widths[2:3], plot_cn_pearson_box$widths[2:3])
-plot_cn_pearson_point$widths[2:3] <- p_maxWidth
-plot_cn_pearson_box$widths[2:3] <- p_maxWidth
-
-g2p_cn_pearson_plot <- cowplot::plot_grid(plot_cn_pearson_box, plot_cn_pearson_point, nrow = 2, rel_heights = c(1, 4))
-g2p_cn_pearson_plot
-
-# ggsave("./plots/manuscript/g2p_cn_pearson_plot.png", g2p_cn_pearson_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
-```
-
-```{r, eval=FALSE}
-plot_cn_point <- ggplot(data = g2p_cor) +
-  facet_wrap(~ Dataset) +
-  geom_point(mapping = aes(label = Drug_Gene, fill = InG2P, color = InG2P, shape = Pearson_CN_Sign, x = Pearson_CN_Abs, y = n, size = Pearson_Pval_CN), alpha = 0.5, size = 1.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
-  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
-  scale_x_continuous(breaks = pretty_breaks()) +
-  geom_text(data = g2p_cor_text, mapping = aes(x = 0.3, y = 115, label = Pearson_Test_Results_CN)) +
-  labs(x = "Pearson correlation coefficient (r) between drug-gene AUC and copy number", y = "Number of level A G2P associations") +
-  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
-  guides(color = FALSE, fill = FALSE) +
-  labs(shape = NULL)
-
-plot_cn_box <- ggplot(data = g2p_cor) +
-  facet_wrap(~ Dataset) +
-  geom_violin(mapping = aes(color = InG2P, y = Pearson_CN_Abs, x = InG2P), alpha = 0.5) +
-  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_CN_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  coord_flip() +
-  labs(x = "In G2P?") +
-  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
-cn_pearson_plot <- subplot(plot_cn_box, plot_cn_point, nrows = 2, heights = c(0.2, 0.8), titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and copy number"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
-
-saveWidgetFix(widget = ge_pearson_plot, file = "./plots/manuscript/g2p_cn_pearson_plot.html")
-```
-
-#### Spearman
-
-```{r fig.height=5, fig.width=12}
-plot_cn_spearman_point <- ggplot(data = g2p_cor, aes(x = Spearman_CN_Abs, y = n, label = Drug_Gene)) +
-  facet_wrap(~ Dataset) +
-  geom_point(mapping = aes(fill = InG2P, color = InG2P, shape = Spearman_CN_Sign), alpha = 0.5, size = 1.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
-  scale_x_continuous(breaks = seq(0, 0.4, by = 0.05), labels = seq(0, 0.4, by = 0.05)) +
-  coord_cartesian(xlim = c(0, 0.35)) +
-  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
-  geom_text_repel(data = subset(g2p_cor, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
-  geom_text(data = g2p_cor_text, mapping = aes(x = 0.175, y = 115, label = Spearman_Test_Results_CN)) +
-  labs(x = "Spearman correlation coefficient (r_s) between drug-gene AUC and copy number", y = "Number of level A G2P associations") +
-  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
-  guides(color = FALSE, fill = FALSE, shape = FALSE)
-
-plot_cn_spearman_box <- ggplot(data = g2p_cor) +
-  facet_wrap(~ Dataset) +
-  geom_violin(mapping = aes(color = InG2P, fill = InG2P, y = Spearman_CN_Abs, x = InG2P), alpha = 0.35) +
-  geom_boxplot(mapping = aes(color = InG2P, y = Spearman_CN_Abs, x = InG2P), width = 0.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_y_continuous(breaks = seq(0, 0.4, by = 0.05), labels = seq(0, 0.4, by = 0.05)) +
-  coord_flip(ylim = c(0, 0.35)) +
-  labs(x = "In G2P?") +
-  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
-plot_cn_spearman_point <- ggplot_gtable(ggplot_build(plot_cn_spearman_point))
-plot_cn_spearman_box <- ggplot_gtable(ggplot_build(plot_cn_spearman_box))
-p_maxWidth <-  grid::unit.pmax(plot_cn_spearman_point$widths[2:3], plot_cn_spearman_box$widths[2:3])
-plot_cn_spearman_point$widths[2:3] <- p_maxWidth
-plot_cn_spearman_box$widths[2:3] <- p_maxWidth
-
-g2p_cn_spearman_plot <- cowplot::plot_grid(plot_cn_spearman_box, plot_cn_spearman_point, nrow = 2, rel_heights = c(1, 4))
-g2p_cn_spearman_plot
-
-# ggsave("./plots/manuscript/g2p_cn_spearman_plot.png", g2p_cn_spearman_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
-```
-
-```{r, eval=FALSE}
-plot_cn_point <- ggplot(data = g2p_cor) +
-  facet_wrap(~ Dataset) +
-  geom_point(mapping = aes(label = Drug_Gene, fill = InG2P, color = InG2P, shape = Spearman_CN_Sign, x = Spearman_CN_Abs, y = n, size = Spearman_Pval_CN), alpha = 0.5, size = 1.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
-  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
-  scale_x_continuous(breaks = pretty_breaks()) +
-  geom_text(data = g2p_cor_text, mapping = aes(x = 0.175, y = 115, label = Spearman_Test_Results_CN)) +
-  labs(x = "Spearman correlation coefficient (r_s) between drug-gene AUC and copy number", y = "Number of level A G2P associations") +
-  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
-  guides(color = FALSE, fill = FALSE) +
-  labs(shape = NULL)
-
-plot_cn_box <- ggplot(data = g2p_cor) +
-  facet_wrap(~ Dataset) +
-  geom_violin(mapping = aes(color = InG2P, y = Spearman_CN_Abs, x = InG2P), alpha = 0.5) +
-  geom_boxplot(mapping = aes(color = InG2P, y = Spearman_CN_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  coord_flip() +
-  labs(x = "In G2P?") +
-  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
-cn_spearman_plot <- subplot(plot_cn_box, plot_cn_point, nrows = 2, heights = c(0.2, 0.8), titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Spearman correlation coefficient between drug-gene AUC and copy number"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
-
-saveWidgetFix(widget = cn_spearman_plot, file = "./plots/manuscript/g2p_cn_spearman_plot.html")
-```
-
-## Lineage-grouped
-
-### Mut: Grid
-
-Summarize the Wilcoxon test p-values of the grid tests by mutation status. Grid tests were all lineage-agnostic G2P drug-gene associations tested across all screened lineages in each dataset:
-```{r}
-g2p_dgl_mut_tally <- g2p %>% group_by(Drug_Gene, group_general_lineage_name) %>% tally()
-
-ccle_dgl_summ <- ccle_signif_grid_lineage
-ccle_dgl_summ$Drug_Gene <- paste0(ccle_dgl_summ$Drug, "_", ccle_dgl_summ$Hugo_Symbol)
-ccle_dgl_summ <- merge(g2p_dgl_mut_tally, ccle_dgl_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
-ccle_dgl_summ$Drug_Gene_Lin <- paste0(ccle_dgl_summ$Drug_Gene, "_", ccle_dgl_summ$group_general_lineage_name)
-ccle_dgl_summ$n <- ifelse(is.na(ccle_dgl_summ$n), 0, ccle_dgl_summ$n)
-ccle_dgl_summ$InG2P <- ifelse(ccle_dgl_summ$n != 0, "Yes", "No")
-ccle_dgl_summ$Dataset <- "CCLE"
-
-ctrp_dgl_summ <- ctrp_signif_grid_lineage
-ctrp_dgl_summ$Drug_Gene <- paste0(ctrp_dgl_summ$Drug, "_", ctrp_dgl_summ$Hugo_Symbol)
-ctrp_dgl_summ <- merge(g2p_dgl_mut_tally, ctrp_dgl_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
-ctrp_dgl_summ$Drug_Gene_Lin <- paste0(ctrp_dgl_summ$Drug_Gene, "_", ctrp_dgl_summ$group_general_lineage_name)
-ctrp_dgl_summ$n <- ifelse(is.na(ctrp_dgl_summ$n), 0, ctrp_dgl_summ$n)
-ctrp_dgl_summ$InG2P <- ifelse(ctrp_dgl_summ$n != 0, "Yes", "No")
-ctrp_dgl_summ$Dataset <- "CTRP"
-
-gdsc_dgl_summ <- gdsc_signif_grid_lineage
-gdsc_dgl_summ$Drug_Gene <- paste0(gdsc_dgl_summ$Drug, "_", gdsc_dgl_summ$Hugo_Symbol)
-gdsc_dgl_summ <- merge(g2p_dgl_mut_tally, gdsc_dgl_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
-gdsc_dgl_summ$Drug_Gene_Lin <- paste0(gdsc_dgl_summ$Drug_Gene, "_", gdsc_dgl_summ$group_general_lineage_name)
-gdsc_dgl_summ$n <- ifelse(is.na(gdsc_dgl_summ$n), 0, gdsc_dgl_summ$n)
-gdsc_dgl_summ$InG2P <- ifelse(gdsc_dgl_summ$n != 0, "Yes", "No")
-gdsc_dgl_summ$Dataset <- "GDSC"
-
-dgl_mut_grid_summ <- rbind(ccle_dgl_summ, ctrp_dgl_summ, gdsc_dgl_summ)
-```
-
-Make summary plots of mutation status tests by lineage and return a dataframe of all t-test results from comparing the p-value distributions of G2P and non-G2P drug-gene associaions:
-```{r, eval=FALSE, results = 'hide'}
-dgl_mut_g2p_grid_ttest_res <- lapply(as.character(unique(dgl_mut_grid_summ$group_general_lineage_name)), MutPlotsByLineage)
-dgl_mut_g2p_grid_ttest_res_list <- rbindlist(dgl_mut_g2p_grid_ttest_res, use.names = TRUE)
-dgl_mut_g2p_grid_ttest_res_list <- dgl_mut_g2p_grid_ttest_res_list[order(dgl_mut_g2p_grid_ttest_res_list$p_value),]
-saveRDS(dgl_mut_g2p_grid_ttest_res_list, "./data_munging/rds/dgl_mut_g2p_grid_ttest_res_list.rds")
-```
-
-```{r}
-dgl_mut_g2p_grid_ttest_res_list <- readRDS("./data_munging/rds/dgl_mut_g2p_grid_ttest_res_list.rds")
-knitr::kable(dgl_mut_g2p_grid_ttest_res_list, caption = "Mutation status: T-test results for level A G2P drug-gene associations across lineages") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-### GE/CN: G2P
-
-Drug-gene-lineage (DGL) overlaps between CCLE, CTRP, and GDSC:
-```{r}
-dgl_overlap_test_list <- list(CCLE = unique(ccle_data_g2p_dgl$Drug_Gene_Lin),
-                              CTRP = unique(ctrp_data_g2p_dgl$Drug_Gene_Lin),
-                              GDSC = unique(gdsc_data_g2p_dgl$Drug_Gene_Lin))
-
-ItemsList <- venn(dgl_overlap_test_list, show.plot = TRUE)
-ItemsList
-```
-
-Test the 102 level-A G2P DGL combinations:
-```{r, eval=FALSE}
-ccle_lineages4pearson <- as.character(unique(ccle_data_g2p_dgl$group_general_lineage_name))[!is.na(as.character(unique(ccle_data_g2p_dgl$group_general_lineage_name)))]
-ccle_signif_ge <- lapply(ccle_lineages4pearson, PearsonByLineage, variable = "GE", dataset = ccle_data_g2p_dgl)
-ccle_signif_ge_all_lin <- rbindlist(ccle_signif_ge, use.names = TRUE)
-ccle_signif_ge_all_lin$Dataset <- "CCLE"
-ccle_signif_cn <- lapply(ccle_lineages4pearson, PearsonByLineage, variable = "CN", dataset = ccle_data_g2p_dgl)
-ccle_signif_cn_all_lin <- rbindlist(ccle_signif_cn, use.names = TRUE)
-ccle_signif_cn_all_lin$Dataset <- "CCLE"
-ccle_signif_all_lin <- merge(ccle_signif_ge_all_lin, ccle_signif_cn_all_lin, by = c("Drug_Gene", "group_general_lineage_name", "n", "Dataset"), all = TRUE)
-
-ctrp_lineages4pearson <- as.character(unique(ctrp_data_g2p_dgl$group_general_lineage_name))[!is.na(as.character(unique(ctrp_data_g2p_dgl$group_general_lineage_name)))]
-ctrp_signif_ge <- lapply(ctrp_lineages4pearson, PearsonByLineage, variable = "GE", dataset = ctrp_data_g2p_dgl)
-ctrp_signif_ge_all_lin <- rbindlist(ctrp_signif_ge, use.names = TRUE)
-ctrp_signif_ge_all_lin$Dataset <- "CTRP"
-ctrp_signif_cn <- lapply(ctrp_lineages4pearson, PearsonByLineage, variable = "CN", dataset = ctrp_data_g2p_dgl)
-ctrp_signif_cn_all_lin <- rbindlist(ctrp_signif_cn, use.names = TRUE)
-ctrp_signif_cn_all_lin$Dataset <- "CTRP"
-ctrp_signif_all_lin <- merge(ctrp_signif_ge_all_lin, ctrp_signif_cn_all_lin, by = c("Drug_Gene", "group_general_lineage_name", "n", "Dataset"), all = TRUE)
-
-gdsc_lineages4pearson <- as.character(unique(gdsc_data_g2p_dgl$group_general_lineage_name))[!is.na(as.character(unique(gdsc_data_g2p_dgl$group_general_lineage_name)))]
-gdsc_signif_ge <- lapply(gdsc_lineages4pearson, PearsonByLineage, variable = "GE", dataset = gdsc_data_g2p_dgl)
-gdsc_signif_ge_all_lin <- rbindlist(gdsc_signif_ge, use.names = TRUE)
-gdsc_signif_ge_all_lin$Dataset <- "GDSC"
-gdsc_signif_cn <- lapply(gdsc_lineages4pearson, PearsonByLineage, variable = "CN", dataset = gdsc_data_g2p_dgl)
-gdsc_signif_cn_all_lin <- rbindlist(gdsc_signif_cn, use.names = TRUE)
-gdsc_signif_cn_all_lin$Dataset <- "GDSC"
-gdsc_signif_all_lin <- merge(gdsc_signif_ge_all_lin, gdsc_signif_cn_all_lin, by = c("Drug_Gene", "group_general_lineage_name", "n", "Dataset"), all = TRUE)
-
-signif_all_lin <- rbind(ccle_signif_all_lin, ctrp_signif_all_lin, gdsc_signif_all_lin)
-signif_all_lin$n <- ifelse(is.na(signif_all_lin$n), 0, signif_all_lin$n)
-signif_all_lin$InG2P <- ifelse(signif_all_lin$n != 0, "Yes", "No")
-signif_all_lin$Drug_Gene_Lin <- paste0(signif_all_lin$Drug_Gene, "_", signif_all_lin$group_general_lineage_name)
-saveRDS(signif_all_lin, "./data_munging/rds/dgl_signif_pearson_g2p.rds")
-```
-
-```{r}
-dgl_signif_pearson_g2p <- readRDS("./data_munging/rds/dgl_signif_pearson_g2p.rds")
-```
-
-```{r}
-# CCLE mut, n = 7
-ccle_mut <- filter(select(ccle_signif_g2p_lineage, Drug_Gene_Lin, p), p < 0.05)
-ccle_mut_n <- nrow(select(ccle_signif_g2p_lineage, Drug_Gene_Lin, p))
-# CCLE GE/CN, n = 9
-ccle_ge <- select(subset(filter(dgl_signif_pearson_g2p, Dataset == "CCLE"), Pearson_Pval_GE < 0.05), Drug_Gene_Lin, Pearson_Pval_GE, Pearson_Corr_GE)
-ccle_cn <- select(subset(filter(dgl_signif_pearson_g2p, Dataset == "CCLE"), Pearson_Pval_CN < 0.05), Drug_Gene_Lin, Pearson_Pval_CN, Pearson_Corr_CN)
-ccle_Pear_n <- nrow(filter(dgl_signif_pearson_g2p, Dataset == "CCLE"))
-ccle_dgl_summ <- merge(ccle_mut, merge(ccle_ge, ccle_cn, by = "Drug_Gene_Lin", all = TRUE), all = TRUE)
-ccle_dgl_summ <- with(ccle_dgl_summ, cbind(colsplit(Drug_Gene_Lin, pattern = "_", names = c("Drug", "Gene", "Lineage")), 
-                                           CCLE_p = p,
-                                           CCLE_p_Bonf = ifelse(p < 0.05 / ccle_mut_n, "Sig", NA),
-                                           CCLE_r_GE = Pearson_Corr_GE,
-                                           CCLE_p_GE = Pearson_Pval_GE,
-                                           CCLE_p_GE_Bonf = ifelse(Pearson_Pval_GE < 0.05 / ccle_Pear_n, "Sig", NA),
-                                           CCLE_r_CN = Pearson_Corr_CN,
-                                           CCLE_p_CN = Pearson_Pval_CN,
-                                           CCLE_p_CN_Bonf = ifelse(Pearson_Pval_CN < 0.05 / ccle_Pear_n, "Sig", NA)))
-
-# CTRP mut, n = 48
-ctrp_mut <- filter(select(ctrp_signif_g2p_lineage, Drug_Gene_Lin, p), p < 0.05)
-ctrp_mut_n <- nrow(select(ctrp_signif_g2p_lineage, Drug_Gene_Lin, p))
-# CTRP GE/CN, n = 61
-ctrp_ge <- select(subset(filter(dgl_signif_pearson_g2p, Dataset == "CTRP"), Pearson_Pval_GE < 0.05), Drug_Gene_Lin, Pearson_Pval_GE, Pearson_Corr_GE)
-ctrp_cn <- select(subset(filter(dgl_signif_pearson_g2p, Dataset == "CTRP"), Pearson_Pval_CN < 0.05), Drug_Gene_Lin, Pearson_Pval_CN, Pearson_Corr_CN)
-ctrp_Pear_n <- nrow(filter(dgl_signif_pearson_g2p, Dataset == "CTRP"))
-ctrp_dgl_summ <- merge(ctrp_mut, merge(ctrp_ge, ctrp_cn, by = "Drug_Gene_Lin", all = TRUE), all = TRUE)
-ctrp_dgl_summ <- with(ctrp_dgl_summ, cbind(colsplit(Drug_Gene_Lin, pattern = "_", names = c("Drug", "Gene", "Lineage")), 
-                                           CTRP_p = p,
-                                           CTRP_p_Bonf = ifelse(p < 0.05 / ctrp_mut_n, "Sig", NA),
-                                           CTRP_r_GE = Pearson_Corr_GE,
-                                           CTRP_p_GE = Pearson_Pval_GE,
-                                           CTRP_p_GE_Bonf = ifelse(Pearson_Pval_GE < 0.05 / ctrp_Pear_n, "Sig", NA),
-                                           CTRP_r_CN = Pearson_Corr_CN,
-                                           CTRP_p_CN = Pearson_Pval_CN,
-                                           CTRP_p_CN_Bonf = ifelse(Pearson_Pval_CN < 0.05 / ctrp_Pear_n, "Sig", NA)))
-
-# GDSC mut, n = 39
-gdsc_mut <- filter(select(gdsc_signif_g2p_lineage, Drug_Gene_Lin, p), p < 0.05)
-gdsc_mut_n <- nrow(select(gdsc_signif_g2p_lineage, Drug_Gene_Lin, p))
-# GDSC GE/CN, n = 53
-gdsc_ge <- select(subset(filter(dgl_signif_pearson_g2p, Dataset == "GDSC"), Pearson_Pval_GE < 0.05), Drug_Gene_Lin, Pearson_Pval_GE, Pearson_Corr_GE)
-gdsc_cn <- select(subset(filter(dgl_signif_pearson_g2p, Dataset == "GDSC"), Pearson_Pval_CN < 0.05), Drug_Gene_Lin, Pearson_Pval_CN, Pearson_Corr_CN)
-gdsc_Pear_n <- nrow(filter(dgl_signif_pearson_g2p, Dataset == "GDSC"))
-gdsc_dgl_summ <- merge(gdsc_mut, merge(gdsc_ge, gdsc_cn, by = "Drug_Gene_Lin", all = TRUE), all = TRUE)
-gdsc_dgl_summ <- with(gdsc_dgl_summ, cbind(colsplit(Drug_Gene_Lin, pattern = "_", names = c("Drug", "Gene", "Lineage")), 
-                                           GDSC_p = p,
-                                           GDSC_p_Bonf = ifelse(p < 0.05 / gdsc_mut_n, "Sig", NA),
-                                           GDSC_r_GE = Pearson_Corr_GE,
-                                           GDSC_p_GE = Pearson_Pval_GE,
-                                           GDSC_p_GE_Bonf = ifelse(Pearson_Pval_GE < 0.05 / gdsc_Pear_n, "Sig", NA),
-                                           GDSC_r_CN = Pearson_Corr_CN,
-                                           GDSC_p_CN = Pearson_Pval_CN,
-                                           GDSC_p_CN_Bonf = ifelse(Pearson_Pval_CN < 0.05 / gdsc_Pear_n, "Sig", NA)))
-
-g2p_dgl_sig_summ <- merge(merge(ccle_dgl_summ, ctrp_dgl_summ, by = c("Drug", "Gene", "Lineage"), all = TRUE), gdsc_dgl_summ, by = c("Drug", "Gene", "Lineage"), all = TRUE)
-```
-
-### GE/CN: Grid
-
-Test all combinations of G2P drugs and genes in all lineages. InG2P indicates G2P drug-gene associations test across all lineages.
-```{r, eval=FALSE}
-ccle_lineages4pearson <- as.character(unique(ccle_data_g2p_grid$group_general_lineage_name))[!is.na(as.character(unique(ccle_data_g2p_grid$group_general_lineage_name)))]
-ccle_signif_ge <- lapply(ccle_lineages4pearson, PearsonByLineage, variable = "GE", dataset = ccle_data_g2p_grid)
-ccle_signif_ge_all_lin <- rbindlist(ccle_signif_ge, use.names = TRUE)
-ccle_signif_ge_all_lin$Dataset <- "CCLE"
-ccle_signif_cn <- lapply(ccle_lineages4pearson, PearsonByLineage, variable = "CN", dataset = ccle_data_g2p_grid)
-ccle_signif_cn_all_lin <- rbindlist(ccle_signif_cn, use.names = TRUE)
-ccle_signif_cn_all_lin$Dataset <- "CCLE"
-ccle_signif_all_lin <- merge(ccle_signif_ge_all_lin, ccle_signif_cn_all_lin, by = c("Drug_Gene", "group_general_lineage_name", "n", "Dataset"), all = TRUE)
-
-ctrp_lineages4pearson <- as.character(unique(ctrp_data_g2p_grid$group_general_lineage_name))[!is.na(as.character(unique(ctrp_data_g2p_grid$group_general_lineage_name)))]
-ctrp_signif_ge <- lapply(ctrp_lineages4pearson, PearsonByLineage, variable = "GE", dataset = ctrp_data_g2p_grid)
-ctrp_signif_ge_all_lin <- rbindlist(ctrp_signif_ge, use.names = TRUE)
-ctrp_signif_ge_all_lin$Dataset <- "CTRP"
-ctrp_signif_cn <- lapply(ctrp_lineages4pearson, PearsonByLineage, variable = "CN", dataset = ctrp_data_g2p_grid)
-ctrp_signif_cn_all_lin <- rbindlist(ctrp_signif_cn, use.names = TRUE)
-ctrp_signif_cn_all_lin$Dataset <- "CTRP"
-ctrp_signif_all_lin <- merge(ctrp_signif_ge_all_lin, ctrp_signif_cn_all_lin, by = c("Drug_Gene", "group_general_lineage_name", "n", "Dataset"), all = TRUE)
-
-gdsc_lineages4pearson <- as.character(unique(gdsc_data_g2p_grid$group_general_lineage_name))[!is.na(as.character(unique(gdsc_data_g2p_grid$group_general_lineage_name)))]
-gdsc_signif_ge <- lapply(gdsc_lineages4pearson, PearsonByLineage, variable = "GE", dataset = gdsc_data_g2p_grid)
-gdsc_signif_ge_all_lin <- rbindlist(gdsc_signif_ge, use.names = TRUE)
-gdsc_signif_ge_all_lin$Dataset <- "GDSC"
-gdsc_signif_cn <- lapply(gdsc_lineages4pearson, PearsonByLineage, variable = "CN", dataset = gdsc_data_g2p_grid)
-gdsc_signif_cn_all_lin <- rbindlist(gdsc_signif_cn, use.names = TRUE)
-gdsc_signif_cn_all_lin$Dataset <- "GDSC"
-gdsc_signif_all_lin <- merge(gdsc_signif_ge_all_lin, gdsc_signif_cn_all_lin, by = c("Drug_Gene", "group_general_lineage_name", "n", "Dataset"), all = TRUE)
-
-signif_all_lin <- rbind(ccle_signif_all_lin, ctrp_signif_all_lin, gdsc_signif_all_lin)
-signif_all_lin$n <- ifelse(is.na(signif_all_lin$n), 0, signif_all_lin$n)
-signif_all_lin$InG2P <- ifelse(signif_all_lin$n != 0, "Yes", "No")
-signif_all_lin$Drug_Gene_Lin <- paste0(signif_all_lin$Drug_Gene, "_", signif_all_lin$group_general_lineage_name)
-saveRDS(signif_all_lin, "./data_munging/rds/dgl_signif_pearson_g2p_grid.rds")
-```
-
-```{r}
-dgl_signif_pearson_g2p_grid <- readRDS("./data_munging/rds/dgl_signif_pearson_g2p_grid.rds")
-```
-
-```{r, results='hide', eval=FALSE}
-dgl_pearson_g2p_grid_ttest_res <- lapply(as.character(unique(dgl_signif_pearson_g2p_grid$group_general_lineage_name)), PearsonPlotsByLineage)
-dgl_pearson_g2p_grid_ttest_res_list <- rbindlist(dgl_pearson_g2p_grid_ttest_res, use.names = TRUE)
-saveRDS(dgl_pearson_g2p_grid_ttest_res_list, "./data_munging/rds/dgl_pearson_g2p_grid_ttest_res_list.rds")
-```
-
-```{r}
-dgl_pearson_g2p_grid_ttest_res_list <- readRDS("./data_munging/rds/dgl_pearson_g2p_grid_ttest_res_list.rds")
-
-knitr::kable(dgl_pearson_g2p_grid_ttest_res_list[order(dgl_pearson_g2p_grid_ttest_res_list$p_value_GE), c("Dataset", "group_general_lineage_name", "t_statistic_GE", "df_GE", "p_value_GE")], caption = "Gene expression: T-test results for level A G2P drug-gene/gene expression associations across lineages") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-
-knitr::kable(dgl_pearson_g2p_grid_ttest_res_list[order(dgl_pearson_g2p_grid_ttest_res_list$p_value_CN), c("Dataset", "group_general_lineage_name", "t_statistic_CN", "df_CN", "p_value_CN")], caption = "Copy number: T-test results for level A G2P drug-gene/gene expression associations across lineages") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-## Mut/GE/CN
-
-### Lineage-agnostic
-
-This section contains summary plots for the Wilcoxon tests and Pearson/Spearman correlations done for only level A G2P drug-gene associations (i.e.
-not the grid tests) and G2P genes in the case of the CRISPR dataset.
-
-#### CRISPR
-
-G2P genes with a significant effect on CERES score by mutation status, gene expression, and copy number. Summary plot using Pearson correlation coefficient for GE and CN:
-```{r fig.height=5, fig.width=12}
-crispr_res_mut <- select(crispr_signif_g2p_gene, Hugo_Symbol, p)
-crispr_res_mut$corr <- 0
-crispr_res_mut$Metric <- "Mutation Status"
-crispr_res_mut$p_log10 <- -log10(crispr_res_mut$p)
-subset(crispr_res_mut, p < 0.05)
-
-subset(crispr_pearson_res_GE, p < 0.05)
-subset(crispr_pearson_res_CN, p < 0.05)
-
-crispr_pearson_res <- rbind(crispr_pearson_res_GE, crispr_pearson_res_CN)
-crispr_pearson_res$Metric <- factor(crispr_pearson_res$Metric, levels = c("Gene Expression", "Copy Number"))
-crispr_pearson_res$p_log10 <- -log10(crispr_pearson_res$p)
-
-crispr_summ_res_mut_plot <- ggplot(data = subset(crispr_res_mut, p < 0.05)) +
-  facet_grid(~ Metric) +
-  scale_y_continuous(breaks = seq(0, 50, by = 5), labels = seq(0, 50, by = 5)) +
-  coord_cartesian(ylim = c(0, 50)) +
-  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_label_repel(mapping = aes(y = p_log10, x = corr, label = Hugo_Symbol, color = Metric), force = 10, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
-  theme(legend.position = "none", panel.grid.major.x = element_blank(), panel.grid.minor.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(5.5, 1.5, 5.5, 5.5), "pt")) +
-  scale_color_manual(values = c("Mutation Status" = "darkorchid4")) +
-  labs(y = "-log10(p-value)")
-
-crispr_summ_res_pearson_plot <- ggplot(data = subset(crispr_pearson_res, p < 0.05)) +
-  facet_grid(~ Metric, scales = "free_x", space = "free") +
-  scale_y_continuous(breaks = seq(0, 50, by = 5), labels = seq(0, 50, by = 5)) +
-  scale_x_continuous(breaks = seq(-0.6, 0.3, by = 0.1), labels = formatC(seq(-0.6, 0.3, by = 0.1), digits = 2, format = "f")) +
-  coord_cartesian(ylim = c(0, 50)) +
-  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
-  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_label_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Hugo_Symbol), force = 10, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
-  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
-  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
-  labs(x = "Pearson correlation coefficient (r)")
-
-crispr_genomic_features_pearson_summ_plot <- plot_grid(crispr_summ_res_mut_plot, crispr_summ_res_pearson_plot, align = "h", rel_widths = c(1, 5))
-crispr_genomic_features_pearson_summ_plot
-
-# ggsave("./plots/manuscript/crispr_genomic_features_pearson_summ_plot.png", crispr_genomic_features_pearson_summ_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
-```
-
-Summary plot using Spearman correlation coefficient for GE and CN:
-```{r fig.height=5, fig.width=12}
-subset(crispr_spearman_res_GE, p < 0.05)
-subset(crispr_spearman_res_CN, p < 0.05)
-
-crispr_spearman_res <- rbind(crispr_spearman_res_GE, crispr_spearman_res_CN)
-crispr_spearman_res$Metric <- factor(crispr_spearman_res$Metric, levels = c("Gene Expression", "Copy Number"))
-crispr_spearman_res$p_log10 <- -log10(crispr_spearman_res$p)
-
-crispr_summ_res_spearman_plot <- ggplot(data = subset(crispr_spearman_res, p < 0.05)) +
-  facet_grid(~ Metric, scales = "free_x", space = "free") +
-  scale_y_continuous(breaks = seq(0, 50, by = 5), labels = seq(0, 50, by = 5)) +
-  scale_x_continuous(breaks = seq(-0.6, 0.3, by = 0.1), labels = formatC(seq(-0.6, 0.3, by = 0.1), digits = 2, format = "f")) +
-  coord_cartesian(ylim = c(0, 50)) +
-  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
-  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_label_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Hugo_Symbol), force = 10, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
-  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
-  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
-  labs(x = "Spearman's rank correlation coefficient (r_s)")
-
-crispr_genomic_features_spearman_summ_plot <- plot_grid(crispr_summ_res_mut_plot, crispr_summ_res_spearman_plot, align = "h", rel_widths = c(1, 5))
-crispr_genomic_features_spearman_summ_plot
-
-# ggsave("./plots/manuscript/crispr_genomic_features_spearman_summ_plot.png", crispr_genomic_features_spearman_summ_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
-```
-
-#### CCLE
-
-G2P drug-gene associations with a significant effect on AUC by mutation status, gene expression, and copy number. Summary plot using Pearson correlation coefficient for GE and CN:
-```{r fig.height=4, fig.width=12}
-ccle_res_mut <- select(ccle_signif_g2p, Drug_Gene, p)
-ccle_res_mut$corr <- 0
-ccle_res_mut$Metric <- "Mutation Status"
-ccle_res_mut$p_log10 <- -log10(ccle_res_mut$p)
-ccle_res_mut$Dataset <- "CCLE"
-
-ccle_pearson_res_GE <- select(filter(ccle_cor_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_GE, Pearson_Pval_GE, Dataset)
-colnames(ccle_pearson_res_GE) <- c("Drug_Gene", "corr", "p", "Dataset")
-ccle_pearson_res_GE$Metric <- "Gene Expression"
-subset(ccle_pearson_res_GE, p < 0.05)
-
-ccle_pearson_res_CN <- select(filter(ccle_cor_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_CN, Pearson_Pval_CN, Dataset)
-colnames(ccle_pearson_res_CN) <- c("Drug_Gene", "corr", "p", "Dataset")
-ccle_pearson_res_CN$Metric <- "Copy Number"
-subset(ccle_pearson_res_CN, p < 0.05)
-
-ccle_pearson_res_filt <- rbind(ccle_pearson_res_GE, ccle_pearson_res_CN)
-ccle_pearson_res_filt$Metric <- factor(ccle_pearson_res_filt$Metric, levels = c("Gene Expression", "Copy Number"))
-ccle_pearson_res_filt$p_log10 <- -log10(ccle_pearson_res_filt$p)
-
-ccle_summ_res_mut_plot <- ggplot(data = subset(ccle_res_mut, p < 0.05)) +
-  facet_grid(Dataset ~ Metric) +
-  scale_y_continuous(breaks = seq(0, 35, by = 5), labels = seq(0, 35, by = 5)) +
-  coord_cartesian(ylim = c(0, 35)) +
-  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_label_repel(mapping = aes(y = p_log10, x = corr, label = Drug_Gene, color = Metric), force = 10, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
-  theme(legend.position = "none", panel.grid.major.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(5.5, 1.5, 5.5, 5.5), "pt"), strip.background.y = element_blank(), strip.text.y = element_blank()) +
-  scale_color_manual(values = c("Mutation Status" = "darkorchid4")) +
-  labs(y = "-log10(p-value)")
-
-ccle_summ_res_pearson_plot <- ggplot(data = subset(ccle_pearson_res_filt, p < 0.05)) +
-  facet_grid(Dataset ~ Metric) +
-  coord_cartesian(ylim = c(0, 35)) +
-  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
-  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_label_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 10, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
-  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
-  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
-  labs(x = "Pearson correlation coefficient (r)")
-
-ccle_genomic_features_pearson_summ_plot <- plot_grid(ccle_summ_res_mut_plot, ccle_summ_res_pearson_plot, align = "h", rel_widths = c(1, 5))
-ccle_genomic_features_pearson_summ_plot
-
-# ggsave("./plots/manuscript/ccle_genomic_features_pearson_summ_plot.png", ccle_genomic_features_pearson_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
-```
-
-Summary plot using Spearman correlation coefficient for GE and CN:
-```{r fig.height=4, fig.width=12}
-ccle_spearman_res_GE <- select(filter(ccle_cor_res, InG2P == "Yes"), Drug_Gene, Spearman_Corr_GE, Spearman_Pval_GE, Dataset)
-colnames(ccle_spearman_res_GE) <- c("Drug_Gene", "corr", "p", "Dataset")
-ccle_spearman_res_GE$Metric <- "Gene Expression"
-subset(ccle_spearman_res_GE, p < 0.05)
-
-ccle_spearman_res_CN <- select(filter(ccle_cor_res, InG2P == "Yes"), Drug_Gene, Spearman_Corr_CN, Spearman_Pval_CN, Dataset)
-colnames(ccle_spearman_res_CN) <- c("Drug_Gene", "corr", "p", "Dataset")
-ccle_spearman_res_CN$Metric <- "Copy Number"
-subset(ccle_spearman_res_CN, p < 0.05)
-
-ccle_spearman_res_filt <- rbind(ccle_spearman_res_GE, ccle_spearman_res_CN)
-ccle_spearman_res_filt$Metric <- factor(ccle_spearman_res_filt$Metric, levels = c("Gene Expression", "Copy Number"))
-ccle_spearman_res_filt$p_log10 <- -log10(ccle_spearman_res_filt$p)
-
-ccle_summ_res_spearman_plot <- ggplot(data = subset(ccle_spearman_res_filt, p < 0.05)) +
-  facet_grid(Dataset ~ Metric) +
-  coord_cartesian(ylim = c(0, 35)) +
-  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
-  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_label_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 10, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
-  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
-  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
-  labs(x = "Spearman's rank correlation coefficient (r_s)")
-
-ccle_genomic_features_spearman_summ_plot <- plot_grid(ccle_summ_res_mut_plot, ccle_summ_res_spearman_plot, align = "h", rel_widths = c(1, 5))
-ccle_genomic_features_spearman_summ_plot
-
-# ggsave("./plots/manuscript/ccle_genomic_features_spearman_summ_plot.png", ccle_genomic_features_spearman_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
-```
-
-#### CTRP
-
-G2P drug-gene associations with a significant effect on AUC by mutation status, gene expression, and copy number. Summary plot using Pearson correlation coefficient for GE and CN:
-```{r fig.height=4, fig.width=12}
-ctrp_res_mut <- select(ctrp_signif_g2p, Drug_Gene, p)
-ctrp_res_mut$corr <- 0
-ctrp_res_mut$Metric <- "Mutation Status"
-ctrp_res_mut$p_log10 <- -log10(ctrp_res_mut$p)
-ctrp_res_mut$Dataset <- "CTRP"
-
-ctrp_pearson_res_GE <- select(filter(ctrp_cor_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_GE, Pearson_Pval_GE, Dataset)
-colnames(ctrp_pearson_res_GE) <- c("Drug_Gene", "corr", "p", "Dataset")
-ctrp_pearson_res_GE$Metric <- "Gene Expression"
-subset(ctrp_pearson_res_GE, p < 0.05)
-
-ctrp_pearson_res_CN <- select(filter(ctrp_cor_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_CN, Pearson_Pval_CN, Dataset)
-colnames(ctrp_pearson_res_CN) <- c("Drug_Gene", "corr", "p", "Dataset")
-ctrp_pearson_res_CN$Metric <- "Copy Number"
-subset(ctrp_pearson_res_CN, p < 0.05)
-
-ctrp_pearson_res_filt <- rbind(ctrp_pearson_res_GE, ctrp_pearson_res_CN)
-ctrp_pearson_res_filt$Metric <- factor(ctrp_pearson_res_filt$Metric, levels = c("Gene Expression", "Copy Number"))
-ctrp_pearson_res_filt$p_log10 <- -log10(ctrp_pearson_res_filt$p)
-
-ctrp_summ_res_mut_plot <- ggplot(data = subset(ctrp_res_mut, p < 0.05)) +
-  facet_grid(Dataset ~ Metric) +
-  scale_y_continuous(breaks = seq(0, 35, by = 5), labels = seq(0, 35, by = 5)) +
-  coord_cartesian(ylim = c(0, 35)) +
-  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_text_repel(mapping = aes(y = p_log10, x = corr, label = Drug_Gene, color = Metric), force = 15, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.9) +
-  theme(legend.position = "none", panel.grid.major.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(5.5, 1.5, 5.5, 5.5), "pt"), strip.background.y = element_blank(), strip.text.y = element_blank()) +
-  scale_color_manual(values = c("Mutation Status" = "darkorchid4")) +
-  labs(y = "-log10(p-value)")
-
-ctrp_summ_res_pearson_plot <- ggplot(data = subset(ctrp_pearson_res_filt, p < 0.05)) +
-  facet_grid(Dataset ~ Metric) +
-  coord_cartesian(ylim = c(0, 35)) +
-  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
-  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 10, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
-  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
-  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
-  labs(x = "Pearson correlation coefficient (r)")
-
-ctrp_genomic_features_pearson_summ_plot <- plot_grid(ctrp_summ_res_mut_plot, ctrp_summ_res_pearson_plot, align = "h", rel_widths = c(1, 5))
-ctrp_genomic_features_pearson_summ_plot
-
-# ggsave("./plots/manuscript/ctrp_genomic_features_pearson_summ_plot.png", ctrp_genomic_features_pearson_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
-```
-
-Summary plot using Spearman correlation coefficient for GE and CN:
-```{r fig.height=4, fig.width=12}
-ctrp_spearman_res_GE <- select(filter(ctrp_cor_res, InG2P == "Yes"), Drug_Gene, Spearman_Corr_GE, Spearman_Pval_GE, Dataset)
-colnames(ctrp_spearman_res_GE) <- c("Drug_Gene", "corr", "p", "Dataset")
-ctrp_spearman_res_GE$Metric <- "Gene Expression"
-subset(ctrp_spearman_res_GE, p < 0.05)
-
-ctrp_spearman_res_CN <- select(filter(ctrp_cor_res, InG2P == "Yes"), Drug_Gene, Spearman_Corr_CN, Spearman_Pval_CN, Dataset)
-colnames(ctrp_spearman_res_CN) <- c("Drug_Gene", "corr", "p", "Dataset")
-ctrp_spearman_res_CN$Metric <- "Copy Number"
-subset(ctrp_spearman_res_CN, p < 0.05)
-
-ctrp_spearman_res_filt <- rbind(ctrp_spearman_res_GE, ctrp_spearman_res_CN)
-ctrp_spearman_res_filt$Metric <- factor(ctrp_spearman_res_filt$Metric, levels = c("Gene Expression", "Copy Number"))
-ctrp_spearman_res_filt$p_log10 <- -log10(ctrp_spearman_res_filt$p)
-
-ctrp_summ_res_spearman_plot <- ggplot(data = subset(ctrp_spearman_res_filt, p < 0.05)) +
-  facet_grid(Dataset ~ Metric) +
-  coord_cartesian(ylim = c(0, 35)) +
-  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
-  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 20, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
-  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
-  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
-  labs(x = "Spearman's rank correlation coefficient (r_s)")
-
-ctrp_genomic_features_spearman_summ_plot <- plot_grid(ctrp_summ_res_mut_plot, ctrp_summ_res_spearman_plot, align = "h", rel_widths = c(1, 5))
-ctrp_genomic_features_spearman_summ_plot
-
-# ggsave("./plots/manuscript/ctrp_genomic_features_spearman_summ_plot.png", ctrp_genomic_features_spearman_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
-```
-
-#### GDSC
-
-G2P drug-gene associations with a significant effect on AUC by mutation status, gene expression, and copy number. Summary plot using Pearson correlation coefficient for GE and CN:
-```{r fig.height=4, fig.width=12}
-gdsc_res_mut <- select(gdsc_signif_g2p, Drug_Gene, p)
-gdsc_res_mut$corr <- 0
-gdsc_res_mut$Metric <- "Mutation Status"
-gdsc_res_mut$p_log10 <- -log10(gdsc_res_mut$p)
-gdsc_res_mut$Dataset <- "GDSC"
-
-gdsc_pearson_res_GE <- select(filter(gdsc_cor_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_GE, Pearson_Pval_GE, Dataset)
-colnames(gdsc_pearson_res_GE) <- c("Drug_Gene", "corr", "p", "Dataset")
-gdsc_pearson_res_GE$Metric <- "Gene Expression"
-subset(gdsc_pearson_res_GE, p < 0.05)
-
-gdsc_pearson_res_CN <- select(filter(gdsc_cor_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_CN, Pearson_Pval_CN, Dataset)
-colnames(gdsc_pearson_res_CN) <- c("Drug_Gene", "corr", "p", "Dataset")
-gdsc_pearson_res_CN$Metric <- "Copy Number"
-subset(gdsc_pearson_res_CN, p < 0.05)
-
-gdsc_pearson_res_filt <- rbind(gdsc_pearson_res_GE, gdsc_pearson_res_CN)
-gdsc_pearson_res_filt$Metric <- factor(gdsc_pearson_res_filt$Metric, levels = c("Gene Expression", "Copy Number"))
-gdsc_pearson_res_filt$p_log10 <- -log10(gdsc_pearson_res_filt$p)
-
-gdsc_summ_res_mut_plot <- ggplot(data = subset(gdsc_res_mut, p < 0.05)) +
-  facet_grid(Dataset ~ Metric) +
-  scale_y_continuous(breaks = seq(0, 16, by = 1), labels = seq(0, 16, by = 1)) +
-  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_text_repel(mapping = aes(y = p_log10, x = corr, label = Drug_Gene, color = Metric), force = 15, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.9) +
-  theme(legend.position = "none", panel.grid.major.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(5.5, 1.5, 5.5, 5.5), "pt"), strip.background.y = element_blank(), strip.text.y = element_blank()) +
-  scale_color_manual(values = c("Mutation Status" = "darkorchid4")) +
-  labs(y = "-log10(p-value)")
-
-gdsc_summ_res_pearson_plot <- ggplot(data = subset(gdsc_pearson_res_filt, p < 0.05)) +
-  facet_grid(Dataset ~ Metric) +
-  scale_y_continuous(breaks = seq(0, 100, by = 10), labels = seq(0, 100, by = 10)) +
-  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
-  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 10, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
-  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
-  theme(legend.position = "none", axis.title.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
-  labs(x = "Pearson correlation coefficient (r)")
-
-gdsc_genomic_features_pearson_summ_plot <- plot_grid(gdsc_summ_res_mut_plot, gdsc_summ_res_pearson_plot, align = "h", rel_widths = c(1, 5))
-gdsc_genomic_features_pearson_summ_plot
-
-# ggsave("./plots/manuscript/gdsc_genomic_features_pearson_summ_plot.png", gdsc_genomic_features_pearson_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
-```
-
-Summary plot using Spearman correlation coefficient for GE and CN:
-```{r fig.height=4, fig.width=12}
-gdsc_spearman_res_GE <- select(filter(gdsc_cor_res, InG2P == "Yes"), Drug_Gene, Spearman_Corr_GE, Spearman_Pval_GE, Dataset)
-colnames(gdsc_spearman_res_GE) <- c("Drug_Gene", "corr", "p", "Dataset")
-gdsc_spearman_res_GE$Metric <- "Gene Expression"
-subset(gdsc_spearman_res_GE, p < 0.05)
-
-gdsc_spearman_res_CN <- select(filter(gdsc_cor_res, InG2P == "Yes"), Drug_Gene, Spearman_Corr_CN, Spearman_Pval_CN, Dataset)
-colnames(gdsc_spearman_res_CN) <- c("Drug_Gene", "corr", "p", "Dataset")
-gdsc_spearman_res_CN$Metric <- "Copy Number"
-subset(gdsc_spearman_res_CN, p < 0.05)
-
-gdsc_spearman_res_filt <- rbind(gdsc_spearman_res_GE, gdsc_spearman_res_CN)
-gdsc_spearman_res_filt$Metric <- factor(gdsc_spearman_res_filt$Metric, levels = c("Gene Expression", "Copy Number"))
-gdsc_spearman_res_filt$p_log10 <- -log10(gdsc_spearman_res_filt$p)
-
-gdsc_summ_res_spearman_plot <- ggplot(data = subset(gdsc_spearman_res_filt, p < 0.05)) +
-  facet_grid(Dataset ~ Metric) +
-  scale_y_continuous(breaks = seq(0, 50, by = 5), labels = seq(0, 50, by = 5)) +
-  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
-  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 20, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
-  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
-  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
-  labs(x = "Spearman's rank correlation coefficient (r_s)")
-
-gdsc_genomic_features_spearman_summ_plot <- plot_grid(gdsc_summ_res_mut_plot, gdsc_summ_res_spearman_plot, align = "h", rel_widths = c(1, 5))
-gdsc_genomic_features_spearman_summ_plot
-
-# ggsave("./plots/manuscript/gdsc_genomic_features_spearman_summ_plot.png", gdsc_genomic_features_spearman_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
-```
-
-#### Drug: Mut
-
-G2P drug-gene associations with a significant effect on AUC by mutation status:
-```{r fig.height=4, fig.width=8}
-all_mut_res <- rbind(ccle_res_mut, ctrp_res_mut, gdsc_res_mut)
-
-all_mut_summ_plot <- ggplot(data = subset(all_res_mut, p < 0.05)) +
-  facet_grid(~ Dataset) +
-  geom_point(aes(x = corr, y = p_log10, color = Dataset), alpha = 0.5) +
-  scale_y_continuous(breaks = seq(0, 12, by = 2), labels = seq(0, 12, by = 2)) +
-  scale_x_continuous(breaks = seq(0, 0.1, by = 0.1), labels = seq(0, 0.1, by = 0.1)) +
-  coord_cartesian(xlim = c(0, 0.05)) +
-  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Dataset, label = Drug_Gene), nudge_x = 0.05, direction = "y", hjust = 0, size = 2.5, segment.size = 0.1, segment.colour = "grey50", box.padding = 0.6) +
-  scale_color_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
-  theme(legend.position = "none", plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt"), panel.grid.major.x = element_blank(), panel.grid.minor.x = element_blank(), axis.title.x = element_blank(), axis.ticks.x = element_blank(), axis.text.x = element_blank()) +
-  labs(y = "-log10(p-value)")
-all_mut_summ_plot
-
-# ggsave("./plots/manuscript/all_mut_summ_plot.png", all_mut_summ_plot, device = "png", dpi = 450, width = 12, height = 6, units = "in")
-```
-
-#### Drug: GE and CN
-
-G2P drug-gene associations with a significant effect on AUC by gene expression and copy number:
-```{r fig.height=12, fig.width=12}
-all_pearson_res <- rbind(ccle_pearson_res_filt, ctrp_pearson_res_filt, gdsc_pearson_res_filt)
-all_pearson_summ_plot <- ggplot(data = subset(all_pearson_res, p < 0.05)) +
-  facet_grid(Dataset ~ Metric, scales = "free", space = "free") +
-  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
-  geom_point(aes(x = corr, y = p_log10, color = Dataset), alpha = 0.5) +
-  scale_y_continuous(breaks = seq(0, 60, by = 10), labels = seq(0, 60, by = 10)) +
-  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Dataset, label = Drug_Gene), force = 10, nudge_y = 3, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
-  scale_color_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
-  theme(legend.position = "none", plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
-  labs(x = "Pearson correlation coefficient (r)", y = "-log10(p-value)")
-all_pearson_summ_plot
-# ggsave("./plots/manuscript/all_pearson_summ_plot.png", all_pearson_summ_plot, device = "png", dpi = 450, width = 12, height = 10, units = "in")
-
-all_spearman_res <- rbind(ccle_spearman_res_filt, ctrp_spearman_res_filt, gdsc_spearman_res_filt)
-all_spearman_summ_plot <- ggplot(data = subset(all_spearman_res, p < 0.05)) +
-  facet_grid(Dataset ~ Metric, scales = "free", space = "free") +
-  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
-  geom_point(aes(x = corr, y = p_log10, color = Dataset), alpha = 0.5) +
-  scale_y_continuous(breaks = seq(0, 60, by = 10), labels = seq(0, 60, by = 10)) +
-  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Dataset, label = Drug_Gene), force = 10, nudge_y = 1, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
-  scale_color_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
-  theme(legend.position = "none", plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
-  labs(x = "Pearson correlation coefficient (r)", y = "-log10(p-value)")
-all_spearman_summ_plot
-# ggsave("./plots/manuscript/all_spearman_summ_plot.png", all_spearman_summ_plot, device = "png", dpi = 450, width = 12, height = 10, units = "in")
-```
-
-#### Drug: P-values
-
-```{r fig.height=6, fig.width=12}
-pval_summ_mut <- g2p_mut_all_summ
-pval_summ_mut$Measure <- "Mutation Status"
-pval_summ_mut$Drug_Gene_Ordered <- NULL
-
-pval_summ_ge <- select(g2p_cor, Drug_Gene, n, Pearson_Pval_GE, InG2P, Dataset)
-colnames(pval_summ_ge)[colnames(pval_summ_ge) == "Pearson_Pval_GE"] <- "p"
-pval_summ_ge$p_log10 <- -log10(pval_summ_ge$p)
-pval_summ_ge$Measure <- "Gene Expression"
-
-pval_summ_cn <- select(g2p_cor, Drug_Gene, n, Pearson_Pval_CN, InG2P, Dataset)
-colnames(pval_summ_cn)[colnames(pval_summ_cn) == "Pearson_Pval_CN"] <- "p"
-pval_summ_cn$p_log10 <- -log10(pval_summ_cn$p)
-pval_summ_cn$Measure <- "Copy Number"
-
-pval_summ <- rbind(pval_summ_mut, pval_summ_ge, pval_summ_cn)
-pval_summ$Measure <- factor(pval_summ$Measure, levels = c("Mutation Status", "Gene Expression", "Copy Number"))
-
-pval_summ_plot <- ggplot(data = pval_summ, aes(x = p_log10, y = n, color = Dataset, shape = Dataset, label = Drug_Gene)) +
-  facet_wrap(~ Measure, scales = "free_x") +
-  geom_point(alpha = 0.7) +
-  scale_color_manual(values = c("green3", "darkslategray4", "darkturquoise")) +
-  geom_text_repel(data = filter(pval_summ, n > 20 & Measure == "Mutation Status"), mapping = aes(x = p_log10, y = n, color = Dataset, label = Drug_Gene), direction = "y", nudge_x = 9, hjust = 0, size = 2.5, segment.size = 0.1, segment.colour = "grey50", box.padding = 0.6, show.legend = FALSE) +
-  geom_text_repel(data = filter(pval_summ, n > 20 & Measure == "Gene Expression"), mapping = aes(x = p_log10, y = n, color = Dataset, label = Drug_Gene), direction = "y", nudge_x = 50, hjust = 0, size = 2.5, segment.size = 0.1, segment.colour = "grey50", box.padding = 0.6, show.legend = FALSE) +
-  geom_text_repel(data = filter(pval_summ, n > 20 & Measure == "Copy Number"), mapping = aes(x = p_log10, y = n, color = Dataset, label = Drug_Gene), direction = "y", nudge_x = 20, hjust = 0, size = 2.5, segment.size = 0.1, segment.colour = "grey50", box.padding = 0.6, show.legend = FALSE) +
-  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
-  labs(x = "-log10(p-value)", y = "Number of level A G2P associations") +
-  theme(legend.position = "bottom")
-pval_summ_plot
-
-# ggsave("./plots/manuscript/all_pval_summ_plot.png", pval_summ_plot, device = "png", dpi = 450, width = 12, height = 6, units = "in")
-```
-
-#### Summary stats
-
-```{r}
-# Mutation status
-g2p_druggene_all_summ_stats <- g2p_druggene_all_summ
-g2p_druggene_all_summ_stats$n_true <- TRUE
-g2p_druggene_all_summ_stats <- g2p_druggene_all_summ_stats %>% drop_na(p) %>% group_by(Dataset, InG2P) %>% summarize(p_mean = round(mean(p), 2), p_sd = round(sd(p), 2), n = sum(n_true), n_signif = sum(p < 0.05), n_sig_perc = n_signif / n * 100)
-
-# Pearson correlations
-g2p_mut_cor_stats <- g2p_mut_cor
-g2p_mut_cor_stats$n_true <- TRUE
-g2p_mut_cor_stats <- g2p_mut_cor_stats %>% group_by(Dataset, InG2P) %>% drop_na() %>% summarize(
-          ge_mean = round(mean(Pearson_GE_Abs), 5),
-          ge_sd = round(sd(Pearson_GE_Abs), 5),
-          ge_n = sum(n_true),
-          ge_n_signif = sum(Pearson_Pval_GE < 0.05),
-          ge_n_sig_perc = ge_n_signif / ge_n * 100,
-          cn_mean = round(mean(Pearson_CN_Abs), 3),
-          cn_sd = round(sd(Pearson_CN_Abs), 5),
-          cn_n = sum(n_true),
-          cn_n_signif = sum(Pearson_Pval_CN < 0.05),
-          cn_n_sig_perc = cn_n_signif / cn_n * 100)
-```
-
-#### CTRP example derivation
-
-Example p-value and Pearson correlation coefficient derivations for afatinib and ERBB2 in the CTRP dataset:
-```{r}
-ctrp_grid_summary_data <- filter(ctrp_data_g2p_grid, Drug_Gene == "afatinib_ERBB2")
-
-ctrp_grid_summary_mut_corr <- wilcox.test(AUC_zscore ~ Mutation_Status_Nonsilent, data = ctrp_grid_summary_data[!is.na(ctrp_grid_summary_data$Mutation_Status_Nonsilent),], paired = FALSE)
-ctrp_grid_summary_mut_corr_text <- paste0("W = ", formatC(ctrp_grid_summary_mut_corr$statistic, format = "d", big.mark = ","), "\np = ", round(ctrp_grid_summary_mut_corr$p.value, 3))
-
-ctrp_grid_summary_ge_corr <- cor.test(y = ctrp_grid_summary_data$AUC, x = ctrp_grid_summary_data$RPKM, method = "pearson", use = "complete.obs")
-ctrp_grid_summary_ge_corr_text <- paste0("r(", ctrp_grid_summary_ge_corr$parameter, ") = ", round(ctrp_grid_summary_ge_corr$estimate, 2), "\np ", ifelse(round(ctrp_grid_summary_ge_corr$p.value, 3) == 0, "< 0.001", paste0("= ", round(ctrp_grid_summary_ge_corr$p.value, 3))))
-
-ctrp_grid_summary_cn_corr <- cor.test(y = ctrp_grid_summary_data$AUC, x = ctrp_grid_summary_data$CN, method = "pearson", use = "complete.obs")
-ctrp_grid_summary_cn_corr_text <- paste0("r(", ctrp_grid_summary_cn_corr$parameter, ") = ", formatC(ctrp_grid_summary_cn_corr$estimate, digits = 2, format = "f"), "\np ", ifelse(round(ctrp_grid_summary_cn_corr$p.value, 3) == 0, "< 0.001", paste0("= ", round(ctrp_grid_summary_cn_corr$p.value, 3))))
-
-ctrp_grid_summary_mut_plot <- ggplot(data = ctrp_grid_summary_data[!is.na(ctrp_grid_summary_data$Mutation_Status_Nonsilent),], aes(y = AUC_zscore, x = Mutation_Status_Nonsilent, fill = Mutation_Status_Nonsilent)) +
-  geom_boxplot(outlier.shape = NA, alpha = 0.6) +
-  geom_jitter(width = 0.2, shape = 21) +
-  scale_fill_manual(values = c("Wildtype" = "lightsteelblue1", "Mutant" = "steelblue4")) +
-  annotate(geom = "text", label = ctrp_grid_summary_mut_corr_text, x = 1.5, y = 1.3) +
-  guides(fill = FALSE) +
-  labs(x = "ERBB2 mutation status", y = "Afatinib AUC (z-score)") +
-  geom_segment(aes(x = 1, y = 1.5, xend = 1.1, yend = 1.5), lwd = 0.2) +
-  geom_segment(aes(x = 1.9, y = 1.5, xend = 2, yend = 1.5), lwd = 0.2) +
-  geom_segment(aes(x = 1, y = 1.5, xend = 1, yend = 1.35), lwd = 0.2) +
-  geom_segment(aes(x = 2, y = 1.5, xend = 2, yend = 1.35), lwd = 0.2)
-ctrp_grid_summary_mut_plot
-
-ctrp_grid_summary_ge_plot <- ggplot(data = ctrp_grid_summary_data, aes(y = AUC_zscore, x = RPKM)) +
-  geom_point(alpha = 0.25, size = 1.25, color = "gray4") +
-  geom_smooth(method = "lm", se = FALSE, lwd = 0.5, lty = 2) +
-  annotate(geom = "text", label = ctrp_grid_summary_ge_corr_text, x = 2000, y = 1.3) +
-  labs(x = "ERBB2 gene expression (RPKM)", y = "Afatinib AUC (z-score)") +
-  theme(axis.title.y = element_blank()) +
-  geom_curve(aes(x = 750, y = -1.9, xend = 1720, yend = 1.1), lwd = 0.2, curvature = -0.2, arrow = arrow(length = unit(0.03, "npc")))
-ctrp_grid_summary_ge_plot
-
-ctrp_grid_summary_cn_plot <- ggplot(data = ctrp_grid_summary_data, aes(y = AUC_zscore, x = CN)) +
-  geom_point(alpha = 0.25, size = 1.25, color = "gray4") +
-  geom_smooth(method = "lm", se = FALSE, lwd = 0.5, lty = 2) +
-  annotate(geom = "text", label = ctrp_grid_summary_cn_corr_text, x = 5, y = 1.3) +
-  labs(x = "ERBB2 copy number (log2 ratio)") +
-  theme(axis.title.y = element_blank()) +
-  geom_curve(aes(x = 4, y = -2.3, xend = 5, yend = 0.8), lwd = 0.2, curvature = 0.2, arrow = arrow(length = unit(0.03, "npc")))
-ctrp_grid_summary_cn_plot
-
-# ggsave("./plots/manuscript/ctrp_grid_summary_mut_plot.png", ctrp_grid_summary_mut_plot, device = "png", dpi = 450, width = 3, height = 4, units = "in")
-# ggsave("./plots/manuscript/ctrp_grid_summary_ge_plot.png", ctrp_grid_summary_ge_plot, device = "png", dpi = 450, width = 5, height = 4, units = "in")
-# ggsave("./plots/manuscript/ctrp_grid_summary_cn_plot.png", ctrp_grid_summary_cn_plot, device = "png", dpi = 450, width = 5, height = 4, units = "in")
-```
-
-### Lineage-grouped
-
-Deriving n for Bonferroni correction:
-```{r}
-ttest_summ_res_mut <- dgl_mut_g2p_grid_ttest_res_list[, c("p_value", "Dataset", "group_general_lineage_name")]
-ttest_summ_res_mut$Metric <- "Mutation Status"
-mut_alphas <- ttest_summ_res_mut %>% drop_na(p_value) %>% group_by(Dataset) %>% tally()
-mut_alphas$alpha_adj <- 0.05 / mut_alphas$n
-
-ttest_summ_res_ge <- dgl_pearson_g2p_grid_ttest_res_list[, c("p_value_GE", "Dataset", "group_general_lineage_name")]
-colnames(ttest_summ_res_ge) <- c("p_value", "Dataset", "group_general_lineage_name")
-ttest_summ_res_ge$Metric <- "Gene Expression"
-ge_alphas <- ttest_summ_res_ge %>% drop_na(p_value) %>% group_by(Dataset) %>% tally()
-ge_alphas$alpha_adj <- 0.05 / ge_alphas$n
-
-ttest_summ_res_cn <- dgl_pearson_g2p_grid_ttest_res_list[, c("p_value_CN", "Dataset", "group_general_lineage_name")]
-colnames(ttest_summ_res_cn) <- c("p_value", "Dataset", "group_general_lineage_name")
-ttest_summ_res_cn$Metric <- "Copy Number"
-cn_alphas <- ttest_summ_res_cn %>% drop_na(p_value) %>% group_by(Dataset) %>% tally()
-cn_alphas$alpha_adj <- 0.05 / cn_alphas$n
-
-ttest_summ_res <- rbind(ttest_summ_res_mut, ttest_summ_res_ge, ttest_summ_res_cn)
-ttest_summ_res$Metric <- factor(ttest_summ_res$Metric, levels = c("Mutation Status", "Gene Expression", "Copy Number"))
-```
-
-Faceted lineage summaries:
-```{r fig.height=4, fig.width=12}
-ttest_mut_summ_facet <- ggplot(data = ttest_summ_res, aes(x = p_value, fill = Dataset, color = Dataset)) +
-  facet_grid(Metric ~ Dataset) +
-  geom_histogram(bins = 40, binwidth = 0.025, boundary = 0, closed = "left") +
-  scale_y_continuous(breaks = c(0:6), labels = c(0:6)) +
-  scale_x_continuous(breaks = seq(0, 1, by = 0.1), expand = c(0.01, 0.01)) +
-  scale_fill_manual(values = c("CCLE" = "palegreen3", "CTRP" = "slategray3", "GDSC" = "paleturquoise3")) +
-  scale_color_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
-  theme(legend.position = c(0.5, 1.7), legend.direction = "horizontal", panel.grid.minor.y = element_blank()) +
-  labs(x = "P-value", y = "Frquency")
-ttest_mut_summ_facet
-
-# ggsave("./plots/manuscript/all_dgl_ttest_summ_facet_plot.png", ttest_mut_summ_facet, device = "png", dpi = 450, width = 12, height = 4, units = "in")
-```
-
-Stacked lineage summaries:
-```{r fig.height=7, fig.width=12}
-# plot.margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
-
-ttest_mut_summ_plot <- ggplot(data = dgl_mut_g2p_grid_ttest_res_list, aes(x = p_value)) +
-  geom_histogram(aes(fill = Dataset, color = Dataset), position = "stack", bins = 40, binwidth = 0.025, boundary = 0, closed = "left") +
-  scale_y_continuous(breaks = c(0:6), labels = c(0:6)) +
-  scale_x_continuous(breaks = seq(0, 1, by = 0.05), expand = c(0.01, 0.01)) +
-  scale_fill_manual(values = c("CCLE" = "palegreen3", "CTRP" = "slategray3", "GDSC" = "paleturquoise3")) +
-  scale_color_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
-  theme(legend.position = c(0.5, 1.7), legend.direction = "horizontal", panel.grid.minor.y = element_blank(), panel.grid.minor.x = element_blank(), plot.margin = unit(c(30, 5.5, 1, 5.5), "pt")) +
-  labs(x = "P-value", y = "Frquency", title = "Mutation status")
-
-ttest_ge_summ_plot <- ggplot(data = dgl_pearson_g2p_grid_ttest_res_list, aes(x = p_value_GE)) +
-  geom_histogram(aes(fill = Dataset, color = Dataset), position = "stack", bins = 40, binwidth = 0.025, boundary = 0, closed = "left") +
-  scale_y_continuous(breaks = c(0:7), labels = c(0:7), expand = c(0.01, 0.01)) +
-  scale_x_continuous(breaks = seq(0, 1, by = 0.05), expand = c(0.01, 0.01)) +
-  scale_fill_manual(values = c("CCLE" = "palegreen3", "CTRP" = "slategray3", "GDSC" = "paleturquoise3")) +
-  scale_color_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
-  theme(legend.position = "none", panel.grid.minor.y = element_blank(), panel.grid.minor.x = element_blank(), plot.margin = unit(c(1, 5.5, 1, 5.5), "pt")) +
-  labs(x = "P-value", y = "Frquency", title = "Gene expression")
-
-ttest_cn_summ_plot <- ggplot(data = dgl_pearson_g2p_grid_ttest_res_list, aes(x = p_value_CN)) +
-  geom_histogram(aes(fill = Dataset, color = Dataset), position = "stack", bins = 40, binwidth = 0.025, boundary = 0, closed = "left") +
-  scale_y_continuous(breaks = c(0:6), labels = c(0:6), expand = c(0.01, 0.01)) +
-  scale_x_continuous(breaks = seq(0, 1, by = 0.05), expand = c(0.01, 0.01)) +
-  scale_fill_manual(values = c("CCLE" = "palegreen3", "CTRP" = "slategray3", "GDSC" = "paleturquoise3")) +
-  scale_color_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
-  theme(legend.position = "none", panel.grid.minor.y = element_blank(), panel.grid.minor.x = element_blank(), plot.margin = unit(c(1, 5.5, 5.5, 5.5), "pt")) +
-  labs(x = "P-value", y = "Frquency", title = "Copy number")
-
-ttest_mut_summ_plot <- ggplot_gtable(ggplot_build(ttest_mut_summ_plot))
-ttest_ge_summ_plot <- ggplot_gtable(ggplot_build(ttest_ge_summ_plot))
-ttest_cn_summ_plot <- ggplot_gtable(ggplot_build(ttest_cn_summ_plot))
-
-# p_maxWidth <-  grid::unit.pmax(ttest_mut_summ_plot$widths, ttest_ge_summ_plot$widths, ttest_cn_summ_plot$widths)
-# ttest_mut_summ_plot$widths <- as.list(p_maxWidth)
-# ttest_ge_summ_plot$widths <- as.list(p_maxWidth)
-# ttest_cn_summ_plot$widths <- as.list(p_maxWidth)
-
-ttest_summ_plot <- cowplot::plot_grid(ttest_mut_summ_plot, ttest_ge_summ_plot,ttest_cn_summ_plot, nrow = 3, rel_heights = c(1, 1.6, 1.6))
-ttest_summ_plot
-
-# ggsave("./plots/manuscript/all_dgl_ttest_summ_plot.png", ttest_summ_plot, device = "png", dpi = 450, width = 12, height = 7, units = "in")
-```
-
-Big grid plot by lineages:
-```{r fig.height=20, fig.width=12}
-dgl_mut <- dgl_mut_grid_summ
-dgl_mut$Sign <- "None"
-dgl_mut$Measure <- "Mutation Status"
-colnames(dgl_mut)[colnames(dgl_mut) == "p"] <- "Statistic"
-dgl_mut$Drug_Gene_Lin <- NULL
-
-dgl_ge <- select(dgl_signif_pearson_g2p_grid, Drug_Gene, group_general_lineage_name, n, Pearson_GE_Abs, InG2P, Dataset, Pearson_GE_Sign)
-dgl_ge$Measure <- "Gene Expression"
-colnames(dgl_ge)[colnames(dgl_ge) == "Pearson_GE_Abs"] <- "Statistic"
-colnames(dgl_ge)[colnames(dgl_ge) == "Pearson_GE_Sign"] <- "Sign"
-
-dgl_cn <- select(dgl_signif_pearson_g2p_grid, Drug_Gene, group_general_lineage_name, n, Pearson_CN_Abs, InG2P, Dataset, Pearson_CN_Sign)
-dgl_cn$Measure <- "Copy Number"
-colnames(dgl_cn)[colnames(dgl_cn) == "Pearson_CN_Abs"] <- "Statistic"
-colnames(dgl_cn)[colnames(dgl_cn) == "Pearson_CN_Sign"] <- "Sign"
-
-dgl_all <- rbind(dgl_mut, dgl_ge, dgl_cn)
-dgl_all$Sign <- ifelse(is.na(dgl_all$Sign), "None", dgl_all$Sign)
-
-dgl_all_plot <- ggplot(data = dgl_all, aes(x = InG2P, y = Statistic)) +
-  facet_grid(group_general_lineage_name ~ Measure * Dataset) +
-  geom_jitter(mapping = aes(shape = Sign, fill = InG2P, color = InG2P), width = 0.4, alpha = 0.5, size = 1) +
-  geom_boxplot(width = 0.25, fill = NA, outlier.shape = NA) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_shape_manual(values = c(25, 24, 4), labels = c("Negative", "Positive", "NA")) +
-  theme(legend.position = "top") +
-  guides(color = FALSE, fill = FALSE)
-
-# ggsave("./plots/manuscript/all_dgl_plot.png", dgl_all_plot, device = "png", dpi = 450, width = 12, height = 40, units = "in")
-```
-
-## Cell line overlap
-
-```{r, eval=FALSE}
-crispr_ccl <- unique(select(crispr_data, DepMap_ID, CCLE_Name))
-ccle_ccl <- unique(select(ccle_data, DepMap_ID, CCLE_Name, accession_id))
-ctrp_ccl <- unique(select(ctrp_data, DepMap_ID, CCLE_Name, accession_id))
-gdsc_ccl <- unique(select(gdsc_data, DepMap_ID, CCLE_Name, accession_id))
-# all_ccl <- merge(ccle_ccl, ctrp_ccl, by = c("DepMap_ID", "CCLE_Name", "accession_id"), all = TRUE)
-```
-
-# BOXPLOTS
-
---------------------------------------------------------------------------------
-
-Mutation status boxplots for genes identified in G2P.
-
-## G2P genes
-
-Boxplots ordered by gene based on frequency of G2P associations.
-
-### CRISPR
-
-```{r fig.height=5, fig.width=20}
-crispr_data_g2p$Hugo_Symbol <- factor(crispr_data_g2p$Hugo_Symbol, levels = g2p_genes)
-crispr_data_g2p_color <- as.character(crispr_data_g2p$Color_Nonsilent)
-names(crispr_data_g2p_color) <- crispr_data_g2p$Mutation_Status_Nonsilent
-crispr_label_text <- data.frame(p.signif.adj = crispr_signif_g2p_gene$p.signif.adj, p.signif = crispr_signif_g2p_gene$p.signif, Hugo_Symbol = crispr_signif_g2p_gene$Hugo_Symbol)
-crispr_label_text <- filter(crispr_label_text, Hugo_Symbol %in% g2p_genes)
-crispr_label_text$Hugo_Symbol <- factor(crispr_label_text$Hugo_Symbol, levels = g2p_genes)
-crispr_data_g2p_plot <- ggplot(data = crispr_data_g2p, aes(x = Mutation_Status_Nonsilent, y = Score)) +
-  facet_wrap(~ Hugo_Symbol, drop = FALSE, nrow = 1) +
-  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
-  geom_boxplot(mapping = aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85)) +
-  scale_fill_manual(values = crispr_data_g2p_color) +
-  guides(color = FALSE) +
-  geom_text(data = crispr_label_text, mapping = aes(x = 1.5, y = 2, label = p.signif), nudge_y = 0.1) +
-  theme(strip.text.x = element_text(size = 10, angle = 45), legend.position = "top", axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
-  labs(title = "CRISPR", fill = "Mutation Status", y = "CERES Score", x = "Mutation Status")
-crispr_data_g2p_plot
-
-# ggsave("./plots/manuscript/crispr_data_g2p_plot.png", crispr_data_g2p_plot, device = "png", dpi = 450, width = 20, height = 5, units = "in")
-```
-
-### CCLE
-
-Plot code:
-```{r, eval=FALSE}
-ccle_drugs <- as.character(unique(ccle_data_ptmuts$Drug))
-ccle_g2p_drugboxplots <- lapply(ccle_drugs, makeDrugBoxplots, dataset = "CCLE")
-ccle_g2p_drugboxplots_paths <- paste0(ccle_drugs, "_ccle_drugboxplots.png")
-pwalk(list(ccle_g2p_drugboxplots_paths, ccle_g2p_drugboxplots), ggsave, path = "./plots/manuscript/ccle_g2p_drugboxplots", dpi = 450, width = 20, height = 5, units = "in")
-```
-
-Data management:
-```{r, eval=FALSE}
-ccle_g2p_drugboxplots <- paste0(list.files("./plots/manuscript/ccle_g2p_drugboxplots", full.names = TRUE))
-names(ccle_g2p_drugboxplots) <- str_replace_all(ccle_g2p_drugboxplots, c("_ccle_drugboxplots.png" = "", "./plots/manuscript/ccle_g2p_drugboxplots/" = ""))
-bsselect(ccle_g2p_drugboxplots, type = "img", live_search = TRUE, show_tick = TRUE, height = 100)
-```
-
-### CTRP
-
-Plot code:
-```{r, eval=FALSE}
-ctrp_drugs <- as.character(unique(ctrp_data_ptmuts$Drug))
-ctrp_g2p_drugboxplots <- lapply(ctrp_drugs, makeDrugBoxplots, dataset = "ctrp")
-ctrp_g2p_drugboxplots_paths <- paste0(ctrp_drugs, "_ctrp_drugboxplots.png")
-pwalk(list(ctrp_g2p_drugboxplots_paths, ctrp_g2p_drugboxplots), ggsave, path = "./plots/manuscript/ctrp_g2p_drugboxplots", dpi = 450, width = 20, height = 5, units = "in")
-```
-
-Data management:
-```{r, eval=FALSE}
-ctrp_g2p_drugboxplots <- paste0(list.files("./plots/manuscript/ctrp_g2p_drugboxplots", full.names = TRUE))
-names(ctrp_g2p_drugboxplots) <- str_replace_all(ctrp_g2p_drugboxplots, c("_ctrp_drugboxplots.png" = "", "./plots/manuscript/ctrp_g2p_drugboxplots/" = ""))
-bsselect(ctrp_g2p_drugboxplots, type = "img", live_search = TRUE, show_tick = TRUE, height = 100)
-```
-
-### GDSC
-
-Plot code:
-```{r, eval=FALSE}
-gdsc_drugs <- as.character(unique(gdsc_data_ptmuts$Drug))
-gdsc_g2p_drugboxplots <- lapply(gdsc_drugs, makeDrugBoxplots, dataset = "gdsc")
-gdsc_g2p_drugboxplots_paths <- paste0(gdsc_drugs, "_gdsc_drugboxplots.png")
-pwalk(list(gdsc_g2p_drugboxplots_paths, gdsc_g2p_drugboxplots), ggsave, path = "./plots/manuscript/gdsc_g2p_drugboxplots", dpi = 450, width = 20, height = 5, units = "in")
-```
-
-Data management:
-```{r, eval=FALSE}
-gdsc_g2p_drugboxplots <- paste0(list.files("./plots/manuscript/gdsc_g2p_drugboxplots", full.names = TRUE))
-names(gdsc_g2p_drugboxplots) <- str_replace_all(gdsc_g2p_drugboxplots, c("_gdsc_drugboxplots.png" = "", "./plots/manuscript/gdsc_g2p_drugboxplots/" = ""))
-bsselect(gdsc_g2p_drugboxplots, type = "img", live_search = TRUE, show_tick = TRUE, height = 100)
-```
-
-## G2P level A drug-gene associations only
-
-### CCLE
-
-```{r fig.height=4, fig.width=12}
-ccle_g2p_order <- as.character(ccle_signif_g2p$Drug_Gene)
-ccle_data_g2p$Drug_Gene_Ordered <- factor(ccle_data_g2p$Drug_Gene, levels = ccle_g2p_order, labels = sapply(strsplit(x = ccle_g2p_order, split = "_"), function(x) paste0(x[1], "\n", x[2])))
-ccle_signif_g2p$Drug_Gene_Ordered <- factor(ccle_signif_g2p$Drug_Gene, levels = ccle_g2p_order, labels = sapply(strsplit(x = ccle_g2p_order, split = "_"), function(x) paste0(x[1], "\n", x[2])))
-ccle_data_g2p_color <- as.character(ccle_data_g2p$Color_Nonsilent)
-names(ccle_data_g2p_color) <- ccle_data_g2p$Mutation_Status_Nonsilent
-ccle_label_text <- data.frame(p.signif.adj = ccle_signif_g2p$p.signif.adj, p.signif = ccle_signif_g2p$p.signif, Drug_Gene_Ordered = ccle_signif_g2p$Drug_Gene_Ordered)
-ccle_data_g2p_plot <- ggplot(data = ccle_data_g2p, aes(x = Mutation_Status_Nonsilent, y = AUC)) +
-  facet_wrap(~ Drug_Gene_Ordered, drop = FALSE, nrow = 1) +
-  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
-  geom_boxplot(mapping = aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85), outlier.shape = 3, outlier.size = 0.5) +
-  scale_fill_manual(values = ccle_data_g2p_color) +
-  guides(color = FALSE) +
-  geom_text(data = ccle_label_text, mapping = aes(x = 1.5, y = 7, label = p.signif), nudge_y = 0.1) +
-  theme(legend.position = "top", axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
-  labs(title = "CCLE", fill = "Mutation Status", y = "AUC", x = "Mutation Status")
-ccle_data_g2p_plot
-
-# ggsave("./plots/manuscript/ccle_data_g2p_plot.png", ccle_data_g2p_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
-```
-
-### CTRP
-
-```{r fig.height=7, fig.width=12}
-ctrp_g2p_order <- as.character(ctrp_signif_g2p$Drug_Gene)
-ctrp_data_g2p$Drug_Gene_Ordered <- factor(ctrp_data_g2p$Drug_Gene, levels = ctrp_g2p_order, labels = sapply(strsplit(x = ctrp_g2p_order, split = "_"), function(x) paste0(x[1], "\n", x[2])))
-ctrp_signif_g2p$Drug_Gene_Ordered <- factor(ctrp_signif_g2p$Drug_Gene, levels = ctrp_g2p_order, labels = sapply(strsplit(x = ctrp_g2p_order, split = "_"), function(x) paste0(x[1], "\n", x[2])))
-ctrp_data_g2p_color <- as.character(ctrp_data_g2p$Color_Nonsilent)
-names(ctrp_data_g2p_color) <- ctrp_data_g2p$Mutation_Status_Nonsilent
-ctrp_label_text <- data.frame(p.signif.adj = ctrp_signif_g2p$p.signif.adj, p.signif = ctrp_signif_g2p$p.signif, Drug_Gene_Ordered = ctrp_signif_g2p$Drug_Gene_Ordered)
-ctrp_data_g2p_plot <- ggplot(data = ctrp_data_g2p, aes(x = Mutation_Status_Nonsilent, y = AUC)) +
-  facet_wrap(~ Drug_Gene_Ordered, drop = FALSE, nrow = 3) +
-  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
-  geom_boxplot(mapping = aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85), outlier.shape = 3, outlier.size = 0.5) +
-  scale_fill_manual(values = ctrp_data_g2p_color) +
-  guides(color = FALSE) +
-  geom_text(data = ctrp_label_text, mapping = aes(x = 1.5, y = 22.5, label = p.signif), nudge_y = 0.1) +
-  theme(legend.position = "top", axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
-  labs(title = "CTRP", fill = "Mutation Status", y = "AUC", x = "Mutation Status")
-ctrp_data_g2p_plot
-
-# ggsave("./plots/manuscript/ctrp_data_g2p_plot.png", ctrp_data_g2p_plot, device = "png", dpi = 450, width = 12, height = 7, units = "in")
-```
-
-### GDSC
-
-```{r fig.height=7, fig.width=12}
-gdsc_g2p_order <- as.character(gdsc_signif_g2p$Drug_Gene)
-gdsc_data_g2p$Drug_Gene_Ordered <- factor(gdsc_data_g2p$Drug_Gene, levels = gdsc_g2p_order, labels = sapply(strsplit(x = gdsc_g2p_order, split = "_"), function(x) paste0(x[1], "\n", x[2])))
-gdsc_signif_g2p$Drug_Gene_Ordered <- factor(gdsc_signif_g2p$Drug_Gene, levels = gdsc_g2p_order, labels = sapply(strsplit(x = gdsc_g2p_order, split = "_"), function(x) paste0(x[1], "\n", x[2])))
-gdsc_data_g2p_color <- as.character(gdsc_data_g2p$Color_Nonsilent)
-names(gdsc_data_g2p_color) <- gdsc_data_g2p$Mutation_Status_Nonsilent
-gdsc_label_text <- data.frame(p.signif.adj = gdsc_signif_g2p$p.signif.adj, p.signif = gdsc_signif_g2p$p.signif, Drug_Gene_Ordered = gdsc_signif_g2p$Drug_Gene_Ordered)
-gdsc_data_g2p_plot <- ggplot(data = gdsc_data_g2p, aes(x = Mutation_Status_Nonsilent, y = AUC)) +
-  facet_wrap(~ Drug_Gene_Ordered, drop = FALSE, nrow = 3) +
-  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
-  geom_boxplot(mapping = aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85), outlier.shape = 3, outlier.size = 0.5) +
-  scale_fill_manual(values = gdsc_data_g2p_color) +
-  guides(color = FALSE) +
-  geom_text(data = gdsc_label_text, mapping = aes(x = 1.5, y = 1, label = p.signif), nudge_y = 0.1) +
-  theme(legend.position = "top", axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
-  labs(title = "GDSC", fill = "Mutation Status", y = "AUC", x = "Mutation Status")
-gdsc_data_g2p_plot
-
-# ggsave("./plots/manuscript/gdsc_data_g2p_plot.png", gdsc_data_g2p_plot, device = "png", dpi = 450, width = 12, height = 7, units = "in")
-```
-
-# CRISPR: POINT MUT MAPPING
-
---------------------------------------------------------------------------------
-
-Match specific point mutations.
-```{r fig.height=5, fig.width=20, eval=FALSE}
-g2p_indications <- filter(read.delim("./data_munging/data_mutation_associations_appended.csv", sep = "\t", header = TRUE), Evidence.Level == "A")
-maf_g2p_indications <- filter(maf_raw, Genome_Change %in% g2p_indications$MutationName)
-crispr_g2p_indications <- merge(crispr_data_ptmuts, maf_g2p_indications, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
-crispr_g2p_indications$Mutation_Status_Nonsilent <- ifelse(is.na(crispr_g2p_indications$Mutation_Status_Nonsilent), "Wildtype", crispr_g2p_indications$Mutation_Status_Nonsilent)
-dup_g2p_indications <- filter(crispr_g2p_indications[, c("Hugo_Symbol", "CCLE_Name", "DepMap_ID")] %>% group_by(Hugo_Symbol, CCLE_Name, DepMap_ID) %>% tally(), n > 1)
-crispr_g2p_indications <- merge(crispr_g2p_indications, dup_g2p_indications, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
-crispr_g2p_indications$Genome_Change <- factor(crispr_g2p_indications$Genome_Change, levels = unique(crispr_g2p_indications$Genome_Change))
-crispr_g2p_indications_nonNA <- filter(crispr_g2p_indications, is.na(n))
-crispr_g2p_indications_plot <- ggplot(crispr_g2p_indications, aes(x = Hugo_Symbol, y = Score)) +
-  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
-  geom_boxplot(alpha = 0.5, color = "lightgray", outlier.shape = NA) +
-  geom_jitter(width = 0.3, mapping = aes(color = Mutation_Status_Nonsilent), size = 1) +
-  theme_light() +
-  theme(legend.title = element_blank()) +
-  labs(x = "Gene", y = "CERES Score")
-crispr_g2p_indications_plot
-crispr_g2p_indications_muts_plot <- ggplot(crispr_g2p_indications, aes(x = Protein_Change, y = Score)) +
-  facet_grid(~ Hugo_Symbol, scales = "free_x", space = "free") +
-  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
-  geom_boxplot(alpha = 0.5, color = "lightgray", outlier.shape = NA) +
-  geom_jitter(width = 0.1, mapping = aes(color = Mutation_Status_Nonsilent), size = 1) +
-  theme_light() +
-  theme(legend.title = element_blank(), axis.text.x = element_text(angle = 90, hjust = 1)) +
-  labs(x = "Gene", y = "CERES Score")
-crispr_g2p_indications_muts_plot
-
-# ggsave("./plots/manuscript/crispr_g2p_indications_plot_test.png", crispr_g2p_indications_plot, width = 12, height = 5, units = "in")
-# ggsave("./plots/manuscript/crispr_g2p_indications_muts_plot_test.png", crispr_g2p_indications_muts_plot, width = 20, height = 5, units = "in")
-```
-
-# REFERENCES
-
---------------------------------------------------------------------------------
-
-Barretina, J., Caponigro, G., Stransky, N., Venkatesan, K., Margolin, A.
-A., Kim, S., … Garraway, L.
-A.
-(2012).
-The Cancer Cell Line Encyclopedia enables predictive modelling of anticancer drug sensitivity.
-Nature, 483(7391), 603–607.
-https://doi.org/10.1038/nature11003
-
-Broad Institute Cancer Dependency Map; Cancer Data Science (2018): Cancer Dependency Map, CRISPR Avana dataset 18Q3 (Avana_public_18Q3). figshare. Fileset. doi:10.6084/m9.figshare.6931364.v1
-
-Consortium, T. C. C. L. E., & Consortium, T. G. of D. S. in C. (2015). Pharmacogenomic agreement between two cancer cell line data sets. Nature, 528(7580), 84–87. https://doi.org/10.1038/nature15736
-
-Data Science, Cancer (2018): DEMETER2 data. figshare. Fileset. doi:10.6084/m9.figshare.6025238.v2
-
-Doench, J.
-G., Fusi, N., Sullender, M., Hegde, M., Vaimberg, E.
-W., Donovan, K.
-F., … Root, D.
-E.
-(2016).
-Optimized sgRNA design to maximize activity and minimize off-target effects of CRISPR-Cas9.
-Nature Biotechnology, 34(2), 184–191.
-https://doi.org/10.1038/nbt.3437
-
-Meyers, R.
-M., Bryan, J.
-G., McFarland, J.
-M., Weir, B.
-A., Sizemore, A.
-E., Xu, H., … Tsherniak, A.
-(2017).
-Computational correction of copy-number effect improves specificity of CRISPR-Cas9 essentiality screens in cancer cells.
-Nature Genetics, 49(12), 1779–1784.
-https://doi.org/10.1038/ng.3984
-
-McFarland, J.
-M., Ho, Z.
-V., Kugener, G., Dempster, J.
-M., Montgomery, P.
-G., Bryan, J.
-G., … Tsherniak, A.
-(2018).
-Improved estimation of cancer dependencies from large-scale RNAi screens using model-based normalization and data integration.
-https://doi.org/10.1101/305656
-
-# SESSION INFORMATION
-
---------------------------------------------------------------------------------
-
-```{r}
-print(sessionInfo())
-```
+<div id = "refs"></div>
+\endgroup

### 2018-12-19 manuscript.tex
set up papaja manuscript.Rmd for reproducibility

\documentclass[man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Manuscript},
            pdfauthor={Sally E. Claridge, Daniel M. Charytonowicz, \& Adam A. Margolin},
            pdfkeywords={keywords},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage[style=apa]{biblatex}

\addbibresource{manuscript.bib}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

  \title{Manuscript}
    \author{Sally E. Claridge\textsuperscript{1}, Daniel M.
Charytonowicz\textsuperscript{1}, \& Adam A.
Margolin\textsuperscript{1, 2}}
    \date{}

\shorttitle{Subtitle}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Department of Genetics and Genomic Sciences, Icahn Institute for Data Science and Genomic Technology, Icahn School of Medicine at Mount Sinai, New York, NY\\\textsuperscript{2} Cancer Target Discovery and Development Network (Oregon Health and Science University, Portland, OR), National Cancer Institute, National Institutes of Health}
\keywords{keywords\newline\indent Word count: X}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

\usepackage{longtable}
\usepackage{lscape}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage[flushleft]{threeparttable}
\usepackage{threeparttablex}

\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers

\authornote{Add complete departmental affiliations for each
author here. Each new line herein must be indented, like this line.

Enter author note here.

Correspondence concerning this article should be addressed to Adam A.
Margolin, Icahn School of Medicine at Mount Sinai, Deparment of Genetics
and Genomic Sciences, One Gustave L. Levy Place, Box 1498, New York, NY
10029. E-mail:
\href{mailto:adam.margolin@mssm.edu}{\nolinkurl{adam.margolin@mssm.edu}}}

\abstract{
One or two sentences providing a \textbf{basic introduction} to the
field, comprehensible to a scientist in any discipline.

Two to three sentences of \textbf{more detailed background},
comprehensible to scientists in related disciplines.

One sentence clearly stating the \textbf{general problem} being
addressed by this particular study.

One sentence summarizing the main result (with the words ``\textbf{here
we show}'' or their equivalent).

Two or three sentences explaining what the \textbf{main result} reveals
in direct comparison to what was thought to be the case previously, or
how the main result adds to previous knowledge.

One or two sentences to put the results into a more \textbf{general
context}.

Two or three sentences to provide a \textbf{broader perspective},
readily comprehensible to a scientist in any discipline.

}

\begin{document}
\maketitle

\autocite{aksoy2017}

\section{Introduction}\label{introduction}

\section{Results}\label{results}

\section{Discussion}\label{discussion}

\newpage

\section{Methods}\label{methods}

We used R \autocite[Version 3.5.0;][]{R-base} and the R-packages
\emph{bsselectR} \autocite[Version 0.1.0;][]{R-bsselectR},
\emph{cowplot} \autocite[Version 0.9.3;][]{R-cowplot}, \emph{data.table}
\autocite[Version 1.11.4;][]{R-data.table}, \emph{dplyr}
\autocite[Version 0.7.8;][]{R-dplyr}, \emph{forcats} \autocite[Version
0.3.0;][]{R-forcats}, \emph{futile.logger} \autocite[Version
1.4.3;][]{R-futile.logger}, \emph{ggplot2} \autocite[Version
3.0.0;][]{R-ggplot2}, \emph{ggpubr} \autocite[Version
0.1.7.999;][]{R-ggpubr}, \emph{ggrepel} \autocite[Version
0.8.0;][]{R-ggrepel}, \emph{ggsignif} \autocite[Version
0.4.0;][]{R-ggsignif}, \emph{gplots} \autocite[Version
3.0.1;][]{R-gplots}, \emph{gridExtra} \autocite[Version
2.3;][]{R-gridExtra}, \emph{htmlwidgets} \autocite[Version
1.2;][]{R-htmlwidgets}, \emph{kableExtra} \autocite[Version
0.9.0;][]{R-kableExtra}, \emph{magrittr} \autocite[Version
1.5;][]{R-magrittr}, \emph{papaja} \autocite[Version
0.1.0.9842;][]{R-papaja}, \emph{plotly} \autocite[Version
4.8.0;][]{R-plotly}, \emph{purrr} \autocite[Version 0.2.5;][]{R-purrr},
\emph{readr} \autocite[Version 1.1.1;][]{R-readr}, \emph{reshape2}
\autocite[Version 1.4.3;][]{R-reshape2}, \emph{scales} \autocite[Version
1.0.0;][]{R-scales}, \emph{shiny} \autocite[Version 1.1.0;][]{R-shiny},
\emph{stringr} \autocite[Version 1.3.1;][]{R-stringr}, \emph{tibble}
\autocite[Version 1.4.2;][]{R-tibble}, \emph{tidyr} \autocite[Version
0.8.2;][]{R-tidyr}, \emph{tidyverse} \autocite[Version
1.2.1;][]{R-tidyverse}, and \emph{VennDiagram} \autocite[Version
1.6.20;][]{R-VennDiagram} for all our analyses.

\newpage

\section{References}\label{references}

\begingroup
\setlength{\parindent}{-0.5in} \setlength{\leftskip}{0.5in}

Finally, the APA guidelines require a note at the start of the reference
section that explains what an asterisk means. This note can be added at
the end of the document as follows.

\hypertarget{refs}{}

\endgroup

\printbibliography

\end{document}

### 2018-12-19 manuscript.tex
move manuscript from Google doc to Rmd

@@
 \urlstyle{same}  % don't use monospace font for urls
-\usepackage[style=apa]{biblatex}
-
-\addbibresource{manuscript.bib}
 \usepackage{graphicx,grffile}
@@
 \abstract{
-One or two sentences providing a \textbf{basic introduction} to the
-field, comprehensible to a scientist in any discipline.
-
-Two to three sentences of \textbf{more detailed background},
-comprehensible to scientists in related disciplines.
-
-One sentence clearly stating the \textbf{general problem} being
-addressed by this particular study.
-
-One sentence summarizing the main result (with the words ``\textbf{here
-we show}'' or their equivalent).
-
-Two or three sentences explaining what the \textbf{main result} reveals
-in direct comparison to what was thought to be the case previously, or
-how the main result adds to previous knowledge.
-
-One or two sentences to put the results into a more \textbf{general
-context}.
-
-Two or three sentences to provide a \textbf{broader perspective},
-readily comprehensible to a scientist in any discipline.
+Multiple high-throughput functional screens in cancer cell lines have
+generated large amounts of information on drug efficacy in a variety of
+genomic contexts and cancer lineages. Inconsistencies between datasets
+have led us to investigate whether these large-scale screens reproduce
+established clinical drug-gene associations and if genomic features
+particular to specific genes improve said reproducibility. We evaluated
+three large-scale, small-molecule drug screens and one CRISPR/Cas9 gene
+essentiality screen, all within the context of clinical interpretations
+derived from a new cancer variant annotation resource published by the
+Variant Interpretation for Cancer Consortium (VICC). We identified low
+levels of concordance between the three drug screen datasets and
+clinical drug-gene associations using mutation status, gene expression,
+and copy number as genomic indicators. Less than half of the clinical
+drug-gene cancer associations from the VICC resource were identified in
+these three drug screen datasets, suggesting a barrier to translating
+findings from these large-scale screens into the clinic.
 
@@
 
-\autocite{aksoy2017}
+\section{Introduction}\label{introduction}
 
-\section{Introduction}\label{introduction}
+Cancer cell lines are a long-standing model for systematic testing of
+candidate therapeutics, beginning with the National Cancer Institute 60
+(NCI60) assay from the late 1980s (M. C. Alley et al., 1988; R. H.
+Shoemaker, 2006; Stinson et al., 1992), which has been used to screen
+over 100,000 compounds as of 2010 (Holbeck, Collins, \& Doroshow, 2010).
+Since then, numerous small-molecule and gene essentiality screens of
+various scales and study aims have been conducted in cell lines, from
+grouping drugs by therapeutic target similarity (Greshock et al., 2010)
+to screening only near-haploid cell lines to generate genome-level
+insights into gene essentiality (T. Wang et al., 2015) to broadly
+identifying cancer dependencies with large-scale screens in multiple
+cancer types (McDonald et al., 2017; J. M. McFarland et al., 2018;
+Meyers et al., 2017; Patel et al., 2017) or select lineages (Heiser et
+al., 2009; Marcotte et al., 2012; Patel et al., 2017). Despite their
+widespread use, cancer cell lines are known to have issues with
+inconsistent naming conventions and contamination (M. Yu et al., 2015),
+and some cell lines have been shown to vary widely at the genetic level
+and in response to drug treatment across strains (Ben-David et al.,
+2018). Additionally, comparisons between cancer cell lines and tumors
+indicate that cell lines have higher numbers of genomic aberrations
+(Domcke, Sinha, Levine, Sander, \& Schultz, 2013; Mouradov et al., 2014;
+Neve et al., 2006) and tend to be hypermethylated (Paz et al., 2003;
+Varley et al., 2013), which could prove an impediment to translating
+cell line discoveries into the clinic.
+
+There have also been debates over consistency between drug screen
+datasets, namely the Broad Institute's and Novartis Institutes for
+Biomedical Research's Cancer Cell Line Encyclopedia (CCLE) (J. Barretina
+et al., 2012; T. C. C. L. E. Consortium \& Consortium, 2015) and the
+Genomics of Drug Sensitivity in Cancer (GDSC) from the Cancer Genome
+Project at the Wellcome Sanger Institute and the Center for Molecular
+Therapeutics at Massachusetts General Hospital Cancer Center (Garnett et
+al., 2012; Yang et al., 2012). The GDSC has also been referred to as the
+Cancer Genome Project (CGP) and the Sanger dataset. Studies have shown
+that drug-gene interactions matched between CCLE and GDSC exhibited poor
+correlation and inconsistencies (Haibe-Kains et al., 2013; Jang, Neto,
+Guinney, Friend, \& Margolin, 2014), prompting other groups to join the
+debate on how best correct for experimental and methodological variation
+between the original drug screens and subsequent computational analysis
+(T. C. C. L. E. Consortium \& Consortium, 2015; Geeleher, Cox, \& Huang,
+2016; Geeleher, Gamazon, Seoighe, Cox, \& Huang, 2016; Hatzis et al.,
+2014; Haverty et al., 2016; Safikhani et al., 2016, 2017).
+
+The prevalence and importance of cancer cell lines in large-scale
+therapeutic research and the apparent inconsistencies between the GDSC
+and CCLE encouraged us to compare the results from these functional
+screens to clinical drug-gene associations. An outstanding question
+concerning studies based on cancer cell lines is whether these the cell
+line systems can accurately model tumor dynamics or recapitulate
+clinical cancer vulnerabilities, and many large-scale grants and
+clinical trials are fundamentally anchored by results from screens
+conducted in cancer cell lines. Thus, our goal was to evaluate how well
+these functional screens recapitulate known drug, gene, and tumor type
+associations that are currently used in clinical decision-making.
+
+We derived our clinical associations from a new project conducted by the
+Variant Interpretation for Cancer Consortium (VICC;
+\url{https://cancervariants.org/}), a Driver Project for the Global
+Alliance for Genomics and Health (GA4GH) (Genomics \& Health, 2016). The
+VICC has curated annotations of known cancer variants at varying levels
+of evidence from multiple resources (A. H. Wagner et al., 2018): the
+Precision Medicine Knowledgebase (L. Huang et al., 2016), MolecularMatch
+(\url{https://www.molecularmatch.com/index.html}), OncoKB (Chakravarty
+et al., 2017), Jackson Labs Clinical Knowledgebase (S. E. Patterson et
+al., 2016), Clinical Interpretations of Variance in Cancers (CIViC)
+(Griffith et al., 2017), and the Cancer Genome Interpreter (CGI)
+(Tamborero et al., 2018). These harmonized variants are hosted on an
+ElasticSearch (Kibana v6.0) platform called Genotype to Phenotype (G2P,
+\url{https://search.cancervariants.org/\#*}) that allows users to query
+and filter aggregated evidence from the various databases listed above
+as well as the GA4GH beacon service
+(\url{http://beacon-network.org/\#/}), which yields access to genetic
+mutation data from over 200 datasets as of 2016 (Genomics \& Health,
+2016). For drug screen datasets, we focus on three well-known,
+large-scale drug projects: the CCLE and GDSC, which were mentioned
+above, and the Center for the Science of Therapeutics at the Broad
+Institute's Cancer Therapeutics Response Portal (CTRP) dataset (Basu et
+al., 2013; M. G. Rees et al., 2016; B. Seashore-Ludlow et al., 2015). We
+also analyzed the results from a large-scale CRISPR/Cas9 screen
+conducted by the Broad Institute's Cancer Dependency Map project
+(DepMap) using the Avana knockout library (Doench et al., 2016; Meyers
+et al., 2017), which will address whether gene essentiality screens via
+CRISPR yield results comparable to functional drug screens.
 
@@
 
+\subsection{Comparison of G2P drug-gene associations and CCLE, CTRP, and
+GDSC}\label{comparison-of-g2p-drug-gene-associations-and-ccle-ctrp-and-gdsc}
+
+G2P designed a set of standards for stratifying their database's cancer
+variant interpretations, ranging from preclinical data at the
+low-evidence end (level D) to clinically actionable interpretations at
+the high-evidence end (level A). To test only these clinically
+actionable associations, we filtered the G2P dataset for only level-A
+G2P interpretations, of which there were 1,296 (see Methods). All
+compounds screened within the GDSC, CTRP, and CCLE datasets are
+considered \enquote{small molecules} and are respectively linked to
+Compound (CID) numbers used for indexing in the PubChem database
+(\url{https://pubchem.ncbi.nlm.nih.gov/}). As a result, non-small
+molecules, which include proteins and biologics (i.e.~monoclonal
+antibodies), that had level-A G2P evidence could not be included in our
+comparisons. Thus, G2P interpretations for which the compound did not
+have a matching CID code were excluded from further analysis as were
+interpretations that did not have an associated compound, resulting in
+removal of 402 interpretations (Table 1). It should be noted that
+cisplatin, a small molecule, was excluded due to its being indexed with
+a ChEMBLdb identifier (\url{https://www.ebi.ac.uk/chembl/}), which we
+did not manually re-index to a CID to avoid accidental
+mischaracterization.
+
+After filtering, 894 level-A G2P interpretations were carried forward in
+subsequent analyses, constituting 57 unique drugs and 34 unique genes in
+88 distinct level-A combinations (Figure 1A). The number of level-A
+interpretations per drug ranged from 1 to 176 (M = 15.7, SD = 34.6),
+from 1 to 264 (M = 26.2, SD = 61.6) per gene, and for each level-A
+drug-gene combination, the range was 1 to 103 (M = 10.1, SD = 19.8).
+These unique drugs, genes, and combinations are hereafter referred to as
+G2P drugs, G2P genes, and G2P associations. Of the 57 unique G2P drugs,
+37 of them were screened in at least one of the drug screen datasets, 14
+were screened in two of the three datasets, and only three drugs were
+screened in all three datasets. The remaining 20 un-screened G2P drugs
+suggests an incompleteness of these drug screens, though these projects
+frequently release new screening data that may include these drugs in
+future releases.
+
+Using cell-line-specific point mutation annotations from the CCLE, we
+compared z-score-transformed area under the dose-response curve (AUC)
+distributions between mutant and wildtype cell lines for all G2P genes
+for each G2P drug tested in the CCLE, CTRP, and GDSC drug screens
+(Figures 1B and 2A). At uncorrected \(\alpha\) = 0.05, Wilcoxon rank-sum
+tests revealed that in CCLE, the AUC distributions of mutant and
+wildtype groups for 10 out of 170 (5.88\%) tested drug-gene combinations
+were significantly different, 91 out of 918 (9.91\%) were significantly
+different for CTRP, and 61 out of 850 (7.18\%) for GDSC. We observe
+little concordance between the number of interpretations for each G2P
+association and the significance of mutation status on AUC for said G2P
+association, suggesting that mutation status alone is not a robust
+predictor of clinically actionable genetic targets. This led us to
+examine the correlations between AUC and gene expression and AUC and
+copy number, two other genomic features that are known to associate with
+cancer and drug response.
+
+\subsection{Do small-molecule screens in cancer cell lines recapitulate
+clinical drug-gene
+associations?}\label{do-small-molecule-screens-in-cancer-cell-lines-recapitulate-clinical-drug-gene-associations}
+
+We compared the distribution of level-A G2P associations (Figure 1A) and
+the associated p-values from the mutation status comparisons (Figure 1B)
+with a null distribution of p-values derived from all pairwise
+combinations of G2P genes and the G2P drugs tested in each dataset, less
+any of the 88 distinct combinations with G2P interpretations, i.e.~the
+non-gray squares in the right heatmap of Figure 1A (Figure 3A). To
+formally test concordance between clinically actionable variants and
+drug screen results, we conducted an independent, two-group t-test to
+compare the distributions of p-values of drug-gene combinations that
+either were or were not represented with level-A evidence in G2P, which
+indicated that the distributions of p-values did not significantly
+differ for CCLE {[}t(9) = 0.25, p = 0.81{]}, CTRP {[}t(51) = 0.85, p =
+0.40{]}, nor GDSC {[}t(47) = -0.56, p = 0.58{]} (Table 2). This further
+supports that mutation status is not a robust genomic feature for
+predicting therapeutic responses.
+
+Similar tests were conducted for the distributions of Pearson
+correlation coefficients (r) between the number of level-A G2P
+associations and gene expression (RPKM) and copy number (log2 ratio) of
+the gene in the association (Figures 3B-C). Example r derivations are
+shown in Figures 2B-C. Absolute values of r were used to simplify
+extreme values in both directions for testing. The difference in the
+CCLE \textbar{}r\textbar{} distributions for both gene expression
+{[}t(8) = 1.43, p = 0.19{]} and copy number {[}t(8) = 2.48, p = 0.23{]}
+were non-significant, which is likely explained by the small sample size
+since only five G2P drugs were screened in the CCLE dataset. For both
+the CTRP and GDSC screens, \textbar{}r\textbar{} values for gene
+expression correlations were significantly greater for the level-A G2P
+associations than the null distribution {[}tCTRP(49) = 3.79, pCTRP
+\textless{} 0.001; tGDSC(44) = 2.97, pGDSC = 0.005{]}. The
+\textbar{}r\textbar{} distributions using copy number were also
+significantly different for CTRP {[}t(49) = 2.48, p = 0.017{]} but not
+for GDSC {[}t(44) = 1.95, p = 0.058{]}.
+
+In all three datasets for both level-A G2P associations and null
+distribution associations, there are more significant
+\textbar{}r\textbar{} values when using gene expression as the genomic
+feature than when using copy number (Table 2), which corresponds with
+previous work showing that gene expression is an informative molecular
+feature when assessing drug sensitivity (Jang et al., 2014; Sirota et
+al., 2011). Additionally, in all cases, there are more significant r
+values when using copy number than there are significant p-values from
+the mutation status comparisons. Though observational, these results
+suggest an order of predictive robustness for these three genomic
+features when used in isolation: Gene expression \textgreater{} copy
+number \textgreater{} mutation status. Additionally, across all three
+genomic features, CTRP consistently identified a higher percentage of
+its possible level-A G2P associations than GDSC, and similarly, GDSC
+identified a higher percentage than CCLE. In the CCLE-GDSC debate,
+inconsistency between the datasets was attributed to the groups using
+two very different assays for generating AUC measurements though it was
+undecided which was more accurate (Haibe-Kains et al., 2013; Jang et
+al., 2014; Weinstein \& Lorenzi, 2013). Our results provide very
+preliminary evidence that GDSC is more accurate than CCLE in regards to
+reproducing clinical associations. However, CTRP may be even more
+accurate than both GDSC and CCLE.
+
+\subsection{Do these pancancer drug-gene associations penetrate to the
+lineage-specific
+level?}\label{do-these-pancancer-drug-gene-associations-penetrate-to-the-lineage-specific-level}
+
+\begin{itemize}
+\tightlist
+\item
+  What do these correlations with mutation status, gene expression, and
+  copy number look like when you constrict to a specific lineage?
+\item
+  When you restrict, do the correlations become more distinct?
+\item
+  Are the lineage-specific results approximately the same as the
+  pancancer results?
+\item
+  Looking at a histogram of p-values, if the histogram is flat, then
+  nothing is significant (note from meeting on 11/16)
+\end{itemize}
+
+In the 894 level-A G2P interpretations, there was a wide variation in
+the specificity of cancer description, ranging from \enquote{Waldenström
+macroglobulinemia} and \enquote{hyper eosinophilic advanced syndrome} on
+the more detailed end to \enquote{cancer} on the broad end. Similarly,
+the drug screen datasets had a wide range in lineage specificity,
+e.g.~CCLE, GTRP, and GDSC all had lineages labeled \enquote{leukemia}
+and \enquote{T-cell childhood acute lymphocytic leukemia} and the CRISPR
+dataset had cell lines labeled \enquote{Epstein-Barr virus-related
+Burkitt lymphoma} and \enquote{lymphoma.} To more easily conduct
+comparative analyses in a cancer-specific manner, we developed a more
+general lineage grouping method derived from the Human Disease Ontology
+identity codes (DOIDs, \url{http://disease-ontology.org/}) (Schriml et
+al., 2019) assigned to each cell line, yielding 27 unique lineage
+groupings. This custom lineage grouping was included in our harmonized
+cancer cell line database (see METHODS).
+
+In the level-A G2P interpretations, there were 102 unique
+drug-gene-lineage combinations (DGLs), representing seven of our curated
+cancer lineages: cancer, breast cancer, leukemia, lung cancer, ovarian
+cancer, skin cancer, and thyroid cancer. CCLE had data for nine DGLs,
+CTRP had data for 61, and GDSC had data for 53, yielding a total of 73
+unique DGLs across all three datasets.
+
+At an alpha of 0.05, no DGLs were identified in the CCLE screen when
+using mutation status as a correlate (n = 7), but CTRP and GDSC
+identified six and five, respectively, in skin cancer, lung cancer, and
+cancer. These significant associations did not hold after Bonferroni
+correction in CTRP (n = 48, \(\alpha\)adjusted = 0.001) or GDSC (n = 39,
+\(\alpha\)adjusted = 0.001).
+
+When using gene expression as the genomic feature, three CCLE DGLs had
+significant correlations at an adjusted alpha of 0.006 (n = 9). Two of
+these three DGLs were also significantly correlated with copy number (n
+= 9, \(\alpha\)adjusted = 0.006).
+
+In CTRP, AUC of 19 DGLs significantly correlated with gene expression,
+12 of which were significant after correction (n = 61,
+\(\alpha\)adjusted = 0.0008). Copy number correlations were significant
+for 12 DGLs, with three DGLs significant post-correction (n = 61,
+\(\alpha\)adjusted = 0.0008).
+
+AUC of 16 DGLs in GDSC significantly correlated with gene expression. At
+an adjusted alpha of 0.0009 (n = 53) eight of them were significant.
+Fewer DGLs were significant when correlating AUC with copy number with 6
+significant at an alpha of 0.05 and 1 significant at an adjusted alpha
+of 0.0009 (n = 53).
+
+Interestingly, when we test the effect of mutation status on drug
+response for the DGLs derived from all pairwise combinations of G2P
+drugs and genes\ldots{} (Figure \#\#1).
+
+\subsection{Are CRISPR/Cas9 gene essentiality results comparable to
+those of functional drug
+screens?}\label{are-crisprcas9-gene-essentiality-results-comparable-to-those-of-functional-drug-screens}
+
+The CRISPR screen from the Broad Institute reports gene dependency using
+CERES scores (Meyers et al., 2017), which are generated from sgRNA
+depletion scores and eliminate bias arising from the effect of copy
+number variation on Cas9 DNA cleavage. The lower the CERES score, the
+higher the likelihood that the gene is essential in the associated cell
+line. Scores are scaled per cell line such that a score of 0 is the
+median effect of nonessential genes and -1 is the median effect of
+common core essential genes. Of the 34 G2P genes, only G6PD was not
+targeted by an sgRNA in the CRISPR dataset.
+
+When we don't account for lineage, Wilcoxon rank-sum tests revealed that
+mutations in eight of the 33 (24.2\%) G2P genes significantly correlated
+with CERES score (\(\alpha\) = 0.05): KRAS (p \textless{} 0.001), BRAF
+(p \textless{} 0.001), BRCA2 (p \textless{} 0.001), CYP19A1 (p = 0.004),
+TSC2 (p = 0.005), JAK2 (p = 0.031), DPYD (p = 0.042), and UGT1A1 (p =
+0.048). Gene expression (RPKM) of 17 (51.5\%) G2P genes significantly
+correlated with CERES score, as did copy number (log2-ratio) for 14
+(42.4\%) G2P genes (Figure \#\#2). For the purpose of comparison to the
+drug screen data, if we treat CRISPR knockdown like a small-molecule
+drug, then these results are similar to the results from CCLE, CTRP, and
+GDSC (Table 2).
+
+\begin{itemize}
+\tightlist
+\item
+  Lineage?
+\end{itemize}
+
+\subsection{Are known copy number driven associations recapitulated in
+the drug and CRISPR
+screens?}\label{are-known-copy-number-driven-associations-recapitulated-in-the-drug-and-crispr-screens}
+
+If a gene's response to is copy number driven, we would expect copy
+number to significantly correlate with AUC and gene essentiality scores,
+as would gene expression is expression and copy number are associated.
+
+In a lineage-agnostic context of the CRISPR screen, ERBB2 gene
+essentiality score had a significant negative correlation with ERBB2
+gene expression (p \textless{} 10-12, r = -0.31) and ERBB2 copy number
+(p \textless{} 10-15, r = -0.34) (Figure \#\#2). Similarly, MET gene
+essentiality also correlated with both MET gene expression (p
+\textless{} 10-12, r = -0.31) and copy number (p \textless{} 10-8, r =
+-0.25). Notably, BRCA1 also significantly correlated with both gene
+expression (p \textless{} 0.001, r = 0.16) and copy number (p
+\textless{} 0.01, r = 0.14). BRCA2 significantly correlated with all
+three of the genomic features tested: gene expression (p \textless{}
+0.05, r = 0.10), copy number (p \textless{} 10-7, r = 0.23), and
+mutation status (p \textless{} 0.001).
+
+\subsection{Which genomic features drive KRAS, EGFR, and BRAF drug-gene
+associations?}\label{which-genomic-features-drive-kras-egfr-and-braf-drug-gene-associations}
+
 \section{Discussion}\label{discussion}
+
+Level-A G2P interpretations correspond to clinical evidence that
+suggests efficacy of gene targets and/or drugs, and this work questions
+whether these relationships manifest themselves in in vitro drug
+screens. We have demonstrated that on its own, mutation status is not a
+robust predictor of drug efficacy and that copy number and gene
+expression fare better as predictors. However, for these three genomic
+features in all three datasets, only 11.1\% (mutation status, 1 of 9,
+CCLE) to 47.9\% (gene expression, 23 of 48, CTRP) (Table 2), of the
+level-A G2P drug-gene associations in the respective dataset were
+significant at an uncorrected \(\alpha\) = 0.05. This suggests that
+while the drug screens successfully identify some clinically relevant
+drug-gene associations, many associations are also missed, which raises
+the question of the extent to which clinical researchers can rely on in
+vitro drug screens when attempting to develop and select therapeutics
+for cancer patients.
+
+These results also highlight the need to account for the complex
+differences inherent between data generated in clinical scenarios and
+data captured in highly controlled, artificial in vitro environments.
+Potential sources of variation and error include the fact that cells
+growing in a laboratory as opposed to those, even of the same tissue
+type, growing in a multicellular organism are exposed to differing sets
+of stressors and signals that can significantly impact intracellular
+signaling pathways, irrespective of shared genomic profiles. These
+differences can include, but are not be limited to, immunologic
+reactions, both adaptive and intrinsic (e.g.~cytokine signaling,
+inflammation), endocrine (e.g.~stress hormones), and nervous system
+stimulation, all of which can have significant downstream implications
+on cellular behavior in the context of therapeutic efficacy. Similarly,
+a laboratory environment and in vitro cell culture introduce abnormal
+growth conditions with respect to extracellular matrix composition,
+nutrient availability, and cell density, all of which have the potential
+to alter cellular signaling and thus render a drug ineffective during
+screening despite would-be in vivo activity.
+
+In the era of precision medicine, the ultimate boon would be that the
+unique omics signatures of a patient's individual cancer can be used to
+guide treatment. High-throughput, in vitro screens of targeted cancer
+agents against cell lines with known omics profiles are beneficial for
+testing hypotheses concerning the mechanisms of action for these agents
+and they allow for scalability and systematic screening. However,
+extrapolating the potential downstream effects of inhibiting a major
+growth pathway (e.g.~MAPK, IP-DAG) to predict the clinical prognosis and
+progression of a multicellular tumor mass growing in a complex
+environment, compounded with the cross-reacting effects of tumor genomic
+heterogeneity, make it a questionable statement that one can safely
+predict clinical consequences from suppressing a single pathway in a
+model system, as evidenced by our findings of fewer than half of the
+known clinical associations in the three drug screen datasets. The
+benefits of these cancer cell line models, in contrast, lie in their
+ability to assess the big-picture effects of these agents. In order to
+fully understand therapeutic drug response, a higher degree of
+granularity is needed. Additional effort to combine more cell line
+information such as gene expression, epigenetic profiles, and proteomic
+data with mutational profiles is essential to improving the efficacy and
+validity of in vitro cell line screens. Further benefit could be derived
+from conducting these screens in environments that are more in line with
+the clinical scenarios we are trying to predict. This would include
+things such a 3-dimensional cell culture, coculturing with stromal cells
+to mimic the tumor microenvironment, as well as other modalities that
+can attempt to better replicate in vivo environments.
+
+As a next step to improve the informational granularity of the analysis
+presented here, our subsequent goal will be to assess the extent to
+which these drug-gene associations are specific to individual cancer
+cell line lineages, which are available and annotated in the data sets
+analyzed within this report. By evaluating how many clinically
+actionable associations are identified in these large-scale functional
+screens, we can begin to address best practices for translating
+discoveries from these tumor models into clinical trials.
 
@@
 
-We used R \autocite[Version 3.5.0;][]{R-base} and the R-packages
-\emph{bsselectR} \autocite[Version 0.1.0;][]{R-bsselectR},
-\emph{cowplot} \autocite[Version 0.9.3;][]{R-cowplot}, \emph{data.table}
-\autocite[Version 1.11.4;][]{R-data.table}, \emph{dplyr}
-\autocite[Version 0.7.8;][]{R-dplyr}, \emph{forcats} \autocite[Version
-0.3.0;][]{R-forcats}, \emph{futile.logger} \autocite[Version
-1.4.3;][]{R-futile.logger}, \emph{ggplot2} \autocite[Version
-3.0.0;][]{R-ggplot2}, \emph{ggpubr} \autocite[Version
-0.1.7.999;][]{R-ggpubr}, \emph{ggrepel} \autocite[Version
-0.8.0;][]{R-ggrepel}, \emph{ggsignif} \autocite[Version
-0.4.0;][]{R-ggsignif}, \emph{gplots} \autocite[Version
-3.0.1;][]{R-gplots}, \emph{gridExtra} \autocite[Version
-2.3;][]{R-gridExtra}, \emph{htmlwidgets} \autocite[Version
-1.2;][]{R-htmlwidgets}, \emph{kableExtra} \autocite[Version
-0.9.0;][]{R-kableExtra}, \emph{magrittr} \autocite[Version
-1.5;][]{R-magrittr}, \emph{papaja} \autocite[Version
-0.1.0.9842;][]{R-papaja}, \emph{plotly} \autocite[Version
-4.8.0;][]{R-plotly}, \emph{purrr} \autocite[Version 0.2.5;][]{R-purrr},
-\emph{readr} \autocite[Version 1.1.1;][]{R-readr}, \emph{reshape2}
-\autocite[Version 1.4.3;][]{R-reshape2}, \emph{scales} \autocite[Version
-1.0.0;][]{R-scales}, \emph{shiny} \autocite[Version 1.1.0;][]{R-shiny},
-\emph{stringr} \autocite[Version 1.3.1;][]{R-stringr}, \emph{tibble}
-\autocite[Version 1.4.2;][]{R-tibble}, \emph{tidyr} \autocite[Version
-0.8.2;][]{R-tidyr}, \emph{tidyverse} \autocite[Version
-1.2.1;][]{R-tidyverse}, and \emph{VennDiagram} \autocite[Version
-1.6.20;][]{R-VennDiagram} for all our analyses.
+\subsection{G2P cancer variants}\label{g2p-cancer-variants}
+
+Cancer variants with the highest level of evidence (i.e.~level A) in the
+Genotype to Phenotype (G2P) database were retrieved from the Variant
+Interpretation for Cancer Consortium (VICC) portal
+(\url{https://search.cancervariants.org/\#*}) (A. H. Wagner et al.,
+2018) using a customized JSON-query script. All JSON queries were passed
+to the available application program interface (API) where a request was
+made for all drug-gene associations with level-A evidence via the G2P
+evidence label, i.e.~association.evidence\_label. From manual inspection
+using G2P's front-end Kibana interface, it was known that, at the time
+of the last query, 27 November 2018, there were 1,297 known level-A
+associations. Due to the limited request processing capabilities of the
+G2P JSON API, queries were batched into packets of 10 data points, for a
+total of 130 requests made in succession. Each returned request was
+processed as JSON object and searched to identify any existing key:value
+pairs for the following variables: evidence level, mutation, gene,
+chromosome, start, end, ref, alt, direction, phenotype description,
+phenotype family, phenotype ID, drug, drug ID, feature names, and
+sequence ID. For any evidence point where a given key:value pair was not
+found or unavailable, a value of -1 was assigned. One of the 1,297
+level-A entries was irretrievable, yielding a final dataset of 1,296
+level-A G2P interpretations, which were stored in a pandas data table
+and exported in CSV format. The VICC's methods for the harvesting and
+harmonizing of cancer variants is available in a GitHub repository from
+Oregon Health \& Science University
+(\url{https://github.com/ohsu-comp-bio/g2p-aggregator}).
+
+\subsection{DepMap data retrieval and
+processing}\label{depmap-data-retrieval-and-processing}
+
+CRISPR/Cas9, CCLE mutation calls, and CCLE copy number data were all
+retrieved from the Broad Institute's Cancer Dependency Map (DepMap)
+Public 18Q4 release via the DepMap data portal
+(\url{https://depmap.org/portal/download/}) (DepMap, 2018). Gene
+expression data was retrieved from the DepMap Public 18Q3 release (Broad
+DepMap, 2018) from the same data portal. For cell lines with no CCLE
+annotation, the DepMap group drew raw copy number and mutation data from
+whole exome sequencing data produced by the Wellcome Trust Sanger
+Institute {[}Catalogue Of Somatic Mutations In Cancer (COSMIC,
+\url{https://cancer.sanger.ac.uk/cell_lines}) (S. Bamford et al., 2004;
+S. A. Forbes et al., 2017); European Genome-phenome Archive (Lappalainen
+et al., 2015), accession number EGAD00001001039{]} and processed the
+data following the CCLE pipelines to ensure consistency.
+
+\subsubsection{CRISPR/Cas9 screen}\label{crisprcas9-screen}
+
+Gene effect scores for 17,634 genes in 517 cell lines were inferred from
+a CRISPR/Cas9 (clustered regularly interspaced short palindromic
+repeats/CRISPR-associated 9) screen using the Broad Institute's Avana
+knockout library (Doench et al., 2016). The Broad Institute's data
+processing and screening methods are available from the figshare record
+(DepMap, 2018) and the original publication of CERES, the algorithm that
+computes inferred gene dependency scores (Meyers et al., 2017). The
+DepMap releases new data quarterly, with the current data set being the
+18Q4 release. This release has 175 more cell lines than the original
+data release that was published with CERES (dataset: gene\_effect.csv,
+accessed 15 November 2018).
+
+\subsubsection{Mutation calls}\label{mutation-calls}
+
+The CCLE provided mutation annotations in 19,280 genes across 1,596 cell
+lines (dataset: depmap\_18Q4\_mutation\_calls.csv, accessed 14 November
+2018). CCLE called substitutions using MuTect (Cibulskis et al., 2013)
+and annotated variants using Oncotator (Ramos et al., 2015) and indels
+using Indelocator
+(\url{https://software.broadinstitute.org/cancer/cga/indelocator}). We
+filtered mutation calls for point mutations, defined as
+single-nucleotide insertions, deletions, and substitutions, regardless
+of result, i.e.~frameshift or missense mutation. For this analysis, cell
+lines harboring non-silent point mutations were considered
+\enquote{mutant} for the gene in question. All other mutations and genes
+without annotation in the Mutation Annotation Format (MAF) file were
+considered \enquote{wildtype.} \enquote{Mutant} and \enquote{wildtype}
+calls were binarily encoded per-gene/per-cell line, regardless of
+quantity of harbored mutations per gene in a given cell line.
+
+\subsubsection{Copy number data}\label{copy-number-data}
+
+The CCLE generated genomic copy number (CN) data using the Affymetrix
+Genome-Wide Human SNP Array 6.0 and GenePattern pipeline (Network, 2008)
+and normalized segmented CN log2-ratios for 23,299 genes across 1,098
+cell lines using circular binary segmentation (Olshen, Venkatraman,
+Lucito, \& Wigler, 2004) (dataset: public\_18Q4\_gene\_cn.csv, accessed
+15 November 2018).
+
+\subsubsection{Gene expression data}\label{gene-expression-data}
+
+The CCLE reports gene expression in RPKM (reads per kilobase per million
+mapped reads) for 54,356 genes across 1,156 cell lines, generated on the
+GeneChip Human Genome U133 Plus 2.0 Array (dataset:
+CCLE\_DepMap\_18q3\_RNAseq\_RPKM\_20180718.gct, accessed 18 July 2018).
+
+\subsection{Drug screen dataset retrieval and
+harmonization}\label{drug-screen-dataset-retrieval-and-harmonization}
+
+The Cancer Therapeutics Response Portal (CTRP) drug screen dataset (v2)
+(Basu et al., 2013; M. G. Rees et al., 2016; B. Seashore-Ludlow et al.,
+2015) was retrieved from the National Cancer Institute's Cancer Target
+Discovery and Development (CTD2) Network's data portal
+(\url{https://ocg.cancer.gov/programs/ctd2/data-portal}, accessed 6 June
+2018). The Genomics of Drug Sensitivity in Cancer (GDSC) drug screen
+dataset (Garnett et al., 2012; Yang et al., 2012) was retrieved from the
+data portal at (\url{https://www.cancerrxgene.org/downloads}, accessed
+19 June 2018). The Cancer Cell Line Encyclopedia (CCLE) drug screen
+dataset (J. Barretina et al., 2012; T. C. C. L. E. Consortium \&
+Consortium, 2015) was retrieved from the Broad Institute's data portal
+(\url{https://portals.broadinstitute.org/ccle}, accessed 20 June 2018).
+
+\subsubsection{Cell line harmonization}\label{cell-line-harmonization}
+
+In an effort to compare CCLE, CTRP, GDSC and CRISPR results and include
+lineage specificity, it was necessary to consolidate cell lines screened
+in each dataset. Given that unique identifiers can be used between
+studies, it was necessary to standardize the identity of each cell line
+with a common source. To achieve this, a freely available cell line
+database called Cellosaurus (v26.0, 14 May 2018) (Bairoch, 2018) was
+downloaded and merged with the Broad Institute's DepMap cell line data
+(accessed 8 June 2018) to create a harmonized cancer cell line database
+containing synonymous identifiers that enabled consolidation of all cell
+lines used in CCLE, CTRP, GDSC and CRISPR into a common framework.
+Subsequent additions to this database include the merging of DepMap IDs
+used in the 18Q3 and 18Q4 DepMap data releases. We curated missing
+synonyms and identifiers, and we manually annotated the granularity of
+lineage labeling for all cell lines analyzed in this study based on
+their Human Disease Ontology identity codes (DOIDs,
+\url{http://disease-ontology.org/}) (Schriml et al., 2019), resulting in
+27 unique lineages. For ease of comparison between datasets, we labeled
+all cell lines with custom, randomized identifiers.
+
+\subsubsection{AUC harmonization}\label{auc-harmonization}
+
+The CCLE reports cell line sensitivity to small molecules as an activity
+area measured above the dose-response curve (ActArea), while both CTRP
+and GDSC report small molecule activity as area under the dose-response
+curve (AUC). Since ActArea is reported with a scale of 0 to 8, we
+converted CCLE's ActArea values to AUC via:
+
+\[AUC=1- \frac{ActArea}{8}\]
+
+All AUC values across the three drug screen datasets were z-score
+transformed:
+
+\[z = \frac{AUC - \mu_{AUC}}{\sigma_{AUC}}\]
+
+where AUC is the mean AUC across all drug-cell line combinations in the
+dataset and AUC is the standard deviation.
+
+\subsection{Computational}\label{computational}
+
+For Figure 1, all data were imported and manipulated using pandas
+(v0.23.0) (McKinney, 2011) and plotted using seaborn (v0.90) (Waskom,
+2012), which sat on top of matplotlib (v2.2.2) (Hunter, 2007) and was
+executed on Python (v2.7.15) (Python Software Foundation,
+\url{https://www.python.org/}) in an IPython (v5.5.0) (Pérez \& Granger,
+2007) kernel within a localhost Jupyter (v5.2.2) notebook (Kluyver et
+al., 2016). All other analyses were conducted in R (v3.5.0) (R
+Foundation for Statistical Computing, \url{https://www.R-project.org/})
+in an RStudio environment (v1.1.447) (RStudio, 2012). All other plots
+were drawn using the ggplot2 (v3.0.0) R package (Wickham, 2016).
+
+\subsubsection{Statistics}\label{statistics}
+
+Wilcoxon tests were computed using the ggpubr (v.) R package
+(Kassambara, 2018).
+
+For computing Pearson correlation coefficients, if there were three or
+fewer data points, then the correlation was not done and a value of NA
+was supplied.
 
@@
 \hypertarget{refs}{}
+\hypertarget{ref-alley1988}{}
+Alley, M. C., Scudiere, D. A., Monks, A., Hursey, M. L., Czerwinski, M.
+J., Fine, D. L., \ldots{} Boyd, M. R. (1988). Feasibility of Drug
+Screening with Panels of Human Tumor Cell Lines Using a Microculture
+Tetrazolium Assay. \emph{Cancer Research}, \emph{48}, 589--601.
+
+\hypertarget{ref-bairoch2018}{}
+Bairoch, A. (2018). The Cellosaurus, a Cell-Line Knowledge Resource.
+\emph{Journal of Biomolecular Techniques : JBT}, \emph{29}(2), 25--38.
+doi:\href{https://doi.org/10.7171/jbt.18-2902-002}{10.7171/jbt.18-2902-002}
+
+\hypertarget{ref-bamford2004}{}
+Bamford, S., Dawson, E., Forbes, S., Clements, J., Pettett, R., Dogan,
+A., \ldots{} Wooster, R. (2004). The COSMIC (Catalogue of Somatic
+Mutations in Cancer) database and website. \emph{British Journal of
+Cancer}, \emph{91}(2), 355--358.
+doi:\href{https://doi.org/10.1038/sj.bjc.6601894}{10.1038/sj.bjc.6601894}
+
+\hypertarget{ref-barretina2012}{}
+Barretina, J., Caponigro, G., Stransky, N., Venkatesan, K., Margolin, A.
+A., Kim, S., \ldots{} Garraway, L. A. (2012). The Cancer Cell Line
+Encyclopedia enables predictive modelling of anticancer drug
+sensitivity. \emph{Nature}, \emph{483}(7391), 603--607.
+doi:\href{https://doi.org/10.1038/nature11003}{10.1038/nature11003}
+
+\hypertarget{ref-basu2013}{}
+Basu, A., Bodycombe, N. E., Cheah, J. H., Price, E. V., Liu, K.,
+Schaefer, G. I., \ldots{} Schreiber, S. L. (2013). An interactive
+resource to identify cancer genetic and lineage dependencies targeted by
+small molecules. \emph{Cell, Cell}, \emph{154, 154}(5, 5), 1151,
+1151--1161.
+doi:\href{https://doi.org/10.1016/j.cell.2013.08.003,\%2010.1016/j.cell.2013.08.003}{10.1016/j.cell.2013.08.003, 10.1016/j.cell.2013.08.003}
+
+\hypertarget{ref-ben-david2018}{}
+Ben-David, U., Siranosian, B., Ha, G., Tang, H., Oren, Y., Hinohara, K.,
+\ldots{} Golub, T. R. (2018). Genetic and transcriptional evolution
+alters cancer cell line drug response. \emph{Nature}, \emph{560}(7718),
+325--330.
+doi:\href{https://doi.org/10.1038/s41586-018-0409-3}{10.1038/s41586-018-0409-3}
+
+\hypertarget{ref-broaddepmap2018}{}
+Broad DepMap. (2018, January 8). DepMap Achilles 18Q3 public. Figshare.
+Retrieved from
+\url{https://figshare.com/articles/DepMap_Achilles_18Q3_public/6931364}
+
+\hypertarget{ref-chakravarty2017}{}
+Chakravarty, D., Gao, J., Phillips, S., Kundra, R., Zhang, H., Wang, J.,
+\ldots{} Schultz, N. (2017). OncoKB: A Precision Oncology Knowledge
+Base. \emph{JCO Precision Oncology}, (1), 1--16.
+doi:\href{https://doi.org/10.1200/PO.17.00011}{10.1200/PO.17.00011}
+
+\hypertarget{ref-cibulskis2013}{}
+Cibulskis, K., Lawrence, M. S., Carter, S. L., Sivachenko, A., Jaffe,
+D., Sougnez, C., \ldots{} Getz, G. (2013). Sensitive detection of
+somatic point mutations in impure and heterogeneous cancer samples.
+\emph{Nature Biotechnology}, \emph{31}(3), 213--219.
+doi:\href{https://doi.org/10.1038/nbt.2514}{10.1038/nbt.2514}
+
+\hypertarget{ref-consortium2015}{}
+Consortium, T. C. C. L. E., \& Consortium, T. G. of D. S. in C. (2015).
+Pharmacogenomic agreement between two cancer cell line data sets.
+\emph{Nature}, \emph{528}(7580), 84--87.
+doi:\href{https://doi.org/10.1038/nature15736}{10.1038/nature15736}
+
+\hypertarget{ref-broaddepmap2018a}{}
+DepMap, B. (2018, January 11). DepMap Achilles 18Q4 public. Figshare.
+Retrieved from
+\url{https://figshare.com/articles/DepMap_Achilles_18Q4_public/7270880}
+
+\hypertarget{ref-doench2016a}{}
+Doench, J. G., Fusi, N., Sullender, M., Hegde, M., Vaimberg, E. W.,
+Donovan, K. F., \ldots{} Root, D. E. (2016). Optimized sgRNA design to
+maximize activity and minimize off-target effects of CRISPR-Cas9.
+\emph{Nature Biotechnology}, \emph{34}(2), 184--191.
+doi:\href{https://doi.org/10.1038/nbt.3437}{10.1038/nbt.3437}
+
+\hypertarget{ref-domcke2013}{}
+Domcke, S., Sinha, R., Levine, D. A., Sander, C., \& Schultz, N. (2013).
+Evaluating cell lines as tumour models by comparison of genomic
+profiles. \emph{Nature Communications}, \emph{4}.
+doi:\href{https://doi.org/10.1038/ncomms3126}{10.1038/ncomms3126}
+
+\hypertarget{ref-forbes2017}{}
+Forbes, S. A., Beare, D., Boutselakis, H., Bamford, S., Bindal, N.,
+Tate, J., \ldots{} Campbell, P. J. (2017). COSMIC: Somatic cancer
+genetics at high-resolution. \emph{Nucleic Acids Research},
+\emph{45}(D1), D777--D783.
+doi:\href{https://doi.org/10.1093/nar/gkw1121}{10.1093/nar/gkw1121}
+
+\hypertarget{ref-garnett2012}{}
+Garnett, M. J., Edelman, E. J., Heidorn, S. J., Greenman, C. D., Dastur,
+A., Lau, K. W., \ldots{} Benes, C. H. (2012). Systematic identification
+of genomic markers of drug sensitivity in cancer cells. \emph{Nature},
+\emph{483}(7391), 570--575.
+doi:\href{https://doi.org/10.1038/nature11005}{10.1038/nature11005}
+
+\hypertarget{ref-geeleher2016}{}
+Geeleher, P., Cox, N. J., \& Huang, R. S. (2016). Cancer biomarker
+discovery is improved by accounting for variability in general levels of
+drug sensitivity in pre-clinical models. \emph{Genome Biology},
+\emph{17}, 190.
+doi:\href{https://doi.org/10.1186/s13059-016-1050-9}{10.1186/s13059-016-1050-9}
+
+\hypertarget{ref-geeleher2016a}{}
+Geeleher, P., Gamazon, E. R., Seoighe, C., Cox, N. J., \& Huang, R. S.
+(2016). Consistency in large pharmacogenomic studies. \emph{Nature},
+\emph{540}(7631), E1--E2.
+doi:\href{https://doi.org/10.1038/nature19838}{10.1038/nature19838}
+
+\hypertarget{ref-theglobalallianceforgenomicsandhealth2016}{}
+Genomics, T. G. A. for, \& Health. (2016). A federated ecosystem for
+sharing genomic, clinical data. \emph{Science}, \emph{352}(6291),
+1278--1280.
+doi:\href{https://doi.org/10.1126/science.aaf6162}{10.1126/science.aaf6162}
+
+\hypertarget{ref-greshock2010}{}
+Greshock, J., Bachman, K. E., Degenhardt, Y. Y., Jing, J., Wen, Y. H.,
+Eastman, S., \ldots{} Wooster, R. (2010). Molecular Target Class Is
+Predictive of In vitro Response Profile. \emph{Cancer Research},
+\emph{70}(9), 3677--3686.
+doi:\href{https://doi.org/10.1158/0008-5472.CAN-09-3788}{10.1158/0008-5472.CAN-09-3788}
+
+\hypertarget{ref-griffith2017}{}
+Griffith, M., Spies, N. C., Krysiak, K., McMichael, J. F., Coffman, A.
+C., Danos, A. M., \ldots{} Griffith, O. L. (2017). CIViC is a community
+knowledgebase for expert crowdsourcing the clinical interpretation of
+variants in cancer. \emph{Nature Genetics}, \emph{49}(2), 170--174.
+doi:\href{https://doi.org/10.1038/ng.3774}{10.1038/ng.3774}
+
+\hypertarget{ref-haibe-kains2013}{}
+Haibe-Kains, B., El-Hachem, N., Birkbak, N. J., Jin, A. C., Beck, A. H.,
+Aerts, H. J. W. L., \& Quackenbush, J. (2013). Inconsistency in large
+pharmacogenomic studies. \emph{Nature}, \emph{504}(7480), 389--393.
+doi:\href{https://doi.org/10.1038/nature12831}{10.1038/nature12831}
+
+\hypertarget{ref-hatzis2014}{}
+Hatzis, C., Bedard, P. L., Juul Birkbak, N., Beck, A. H., Aerts, H. J.
+W. L., Stern, D. F., \ldots{} Haibe-Kains, B. (2014). Enhancing
+Reproducibility in Cancer Drug Screening: How Do We Move Forward?
+\emph{Cancer Research}, \emph{74}(15), 4016--4023.
+doi:\href{https://doi.org/10.1158/0008-5472.CAN-14-0725}{10.1158/0008-5472.CAN-14-0725}
+
+\hypertarget{ref-haverty2016}{}
+Haverty, P. M., Lin, E., Tan, J., Yu, Y., Lam, B., Lianoglou, S.,
+\ldots{} Bourgon, R. (2016). Reproducible pharmacogenomic profiling of
+cancer cell line panels. \emph{Nature}, \emph{533}(7603), 333--337.
+doi:\href{https://doi.org/10.1038/nature17987}{10.1038/nature17987}
+
+\hypertarget{ref-heiser2009}{}
+Heiser, L. M., Wang, N. J., Talcott, C. L., Laderoute, K. R., Knapp, M.,
+Guan, Y., \ldots{} Spellman, P. T. (2009). Integrated analysis of breast
+cancer cell lines reveals unique signaling pathways. \emph{Genome
+Biology}, \emph{10}(3), R31.
+doi:\href{https://doi.org/10.1186/gb-2009-10-3-r31}{10.1186/gb-2009-10-3-r31}
+
+\hypertarget{ref-holbeck2010}{}
+Holbeck, S. L., Collins, J. M., \& Doroshow, J. H. (2010). Analysis of
+FDA-Approved Anti-Cancer Agents in the NCI60 Panel of Human Tumor Cell
+Lines. \emph{Molecular Cancer Therapeutics}, \emph{9}(5), 1451--1460.
+doi:\href{https://doi.org/10.1158/1535-7163.MCT-10-0106}{10.1158/1535-7163.MCT-10-0106}
+
+\hypertarget{ref-huang2016}{}
+Huang, L., Fernandes, H., Zia, H., Tavassoli, P., Rennert, H., Pisapia,
+D., \ldots{} Elemento, O. (2016). The cancer precision medicine
+knowledge base for structured clinical-grade mutations and
+interpretations. \emph{Journal of the American Medical Informatics
+Association : JAMIA}, \emph{24}(3), 513--519.
+doi:\href{https://doi.org/10.1093/jamia/ocw148}{10.1093/jamia/ocw148}
+
+\hypertarget{ref-hunter2007}{}
+Hunter, J. (2007). Matplotlib: A 2D graphics environment, \emph{9}(3),
+90--95.
+doi:\href{https://doi.org/10.5281/zenodo.1202077}{10.5281/zenodo.1202077}
+
+\hypertarget{ref-jang2014}{}
+Jang, I. S., Neto, E. C., Guinney, J., Friend, S. H., \& Margolin, A. A.
+(2014). Systematic assessment of analytical methods for drug sensitivity
+prediction from cancer cell line data. \emph{Pacific Symposium on
+Biocomputing. Pacific Symposium on Biocomputing}, 63--74. Retrieved from
+\url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3995541/}
+
+\hypertarget{ref-kassambara2018}{}
+Kassambara, A. (2018). Ggpubr: 'Ggplot2' Based Publication Ready Plots
+(Version 0.1.7.999). Retrieved from
+\url{https://cran.r-project.org/web/packages/ggpubr/index.html}
+
+\hypertarget{ref-kluyver2016}{}
+Kluyver, T., Ragan-Kelley, B., Pérez, F., Granger, B., Bussonnier, M.,
+Frederic, J., \ldots{} Team, J. D. (2016). Jupyter Notebooks - a
+publishing format for reproducible computational workflows. In F.
+Loizides \& B. Schmidt (Eds.), \emph{Positioning and Power in Academic
+Publishing: Players, Agents and Agendas} (pp. 87--90). IOS Press.
+
+\hypertarget{ref-lappalainen2015}{}
+Lappalainen, I., Almeida-King, J., Kumanduri, V., Senf, A., Spalding, J.
+D., ur-Rehman, S., \ldots{} Flicek, P. (2015). The European
+Genome-phenome Archive of human data consented for biomedical research.
+\emph{Nature Genetics}, \emph{47}(7), 692--695.
+doi:\href{https://doi.org/10.1038/ng.3312}{10.1038/ng.3312}
+
+\hypertarget{ref-marcotte2012}{}
+Marcotte, R., Brown, K. R., Suarez, F., Sayad, A., Karamboulas, K.,
+Krzyzanowski, P. M., \ldots{} Moffat, J. (2012). Essential gene profiles
+in breast, pancreas and ovarian cancer cells. \emph{Cancer Discovery},
+\emph{2}(2), 172--189.
+doi:\href{https://doi.org/10.1158/2159-8290.CD-11-0224}{10.1158/2159-8290.CD-11-0224}
+
+\hypertarget{ref-mcdonald2017}{}
+McDonald, E. R., de Weck, A., Schlabach, M. R., Billy, E., Mavrakis, K.
+J., Hoffman, G. R., \ldots{} Sellers, W. R. (2017). Project DRIVE: A
+Compendium of Cancer Dependencies and Synthetic Lethal Relationships
+Uncovered by Large-Scale, Deep RNAi Screening. \emph{Cell},
+\emph{170}(3), 577--592.e10.
+doi:\href{https://doi.org/10.1016/j.cell.2017.07.005}{10.1016/j.cell.2017.07.005}
+
+\hypertarget{ref-mcfarland2018}{}
+McFarland, J. M., Ho, Z. V., Kugener, G., Dempster, J. M., Montgomery,
+P. G., Bryan, J. G., \ldots{} Tsherniak, A. (2018). Improved estimation
+of cancer dependencies from large-scale RNAi screens using model-based
+normalization and data integration.
+doi:\href{https://doi.org/10.1101/305656}{10.1101/305656}
+
+\hypertarget{ref-mckinney2011}{}
+McKinney, W. (2011). Pandas: A Foundational Python Library for Data
+Analysis and Statistics. Retrieved from \url{http://pandas.pydata.org/}
+
+\hypertarget{ref-meyers2017}{}
+Meyers, R. M., Bryan, J. G., McFarland, J. M., Weir, B. A., Sizemore, A.
+E., Xu, H., \ldots{} Tsherniak, A. (2017). Computational correction of
+copy-number effect improves specificity of CRISPR-Cas9 essentiality
+screens in cancer cells. \emph{Nature Genetics}, \emph{49}(12),
+1779--1784. doi:\href{https://doi.org/10.1038/ng.3984}{10.1038/ng.3984}
+
+\hypertarget{ref-mouradov2014}{}
+Mouradov, D., Sloggett, C., Jorissen, R. N., Love, C. G., Li, S.,
+Burgess, A. W., \ldots{} Sieber, O. M. (2014). Colorectal Cancer Cell
+Lines Are Representative Models of the Main Molecular Subtypes of
+Primary Cancer. \emph{Cancer Research}, \emph{74}(12), 3238--3247.
+doi:\href{https://doi.org/10.1158/0008-5472.CAN-14-0013}{10.1158/0008-5472.CAN-14-0013}
+
+\hypertarget{ref-thecancergenomeatlasresearchnetwork2008}{}
+Network, T. C. G. A. R. (2008). Comprehensive genomic characterization
+defines human glioblastoma genes and core pathways, \emph{455},
+1061--1068.
+doi:\href{https://doi.org/10.1038/nature07385}{10.1038/nature07385}
+
+\hypertarget{ref-neve2006}{}
+Neve, R. M., Chin, K., Fridlyand, J., Yeh, J., Baehner, F. L., Fevr, T.,
+\ldots{} Gray, J. W. (2006). A collection of breast cancer cell lines
+for the study of functionally distinct cancer subtypes. \emph{Cancer
+Cell}, \emph{10}(6), 515--527.
+doi:\href{https://doi.org/10.1016/j.ccr.2006.10.008}{10.1016/j.ccr.2006.10.008}
+
+\hypertarget{ref-olshen2004}{}
+Olshen, A. B., Venkatraman, E. S., Lucito, R., \& Wigler, M. (2004).
+Circular binary segmentation for the analysis of array-based DNA copy
+number data. \emph{Biostatistics}, \emph{5}(4), 557--572.
+doi:\href{https://doi.org/10.1093/biostatistics/kxh008}{10.1093/biostatistics/kxh008}
+
+\hypertarget{ref-patel2017}{}
+Patel, S. J., Sanjana, N. E., Kishton, R. J., Eidizadeh, A., Vodnala, S.
+K., Cam, M., \ldots{} Restifo, N. P. (2017). Identification of essential
+genes for cancer immunotherapy. \emph{Nature}, \emph{548}(7669),
+537--542.
+doi:\href{https://doi.org/10.1038/nature23477}{10.1038/nature23477}
+
+\hypertarget{ref-patterson2016}{}
+Patterson, S. E., Liu, R., Statz, C. M., Durkin, D., Lakshminarayana,
+A., \& Mockus, S. M. (2016). The clinical trial landscape in oncology
+and connectivity of somatic mutational profiles to targeted therapies.
+\emph{Human Genomics}, \emph{10}(1).
+doi:\href{https://doi.org/10.1186/s40246-016-0061-7}{10.1186/s40246-016-0061-7}
+
+\hypertarget{ref-paz2003}{}
+Paz, M. F., Fraga, M. F., Avila, S., Guo, M., Pollan, M., Herman, J. G.,
+\& Esteller, M. (2003). A Systematic Profile of DNA Methylation in Human
+Cancer Cell Lines, \emph{63}, 1114--1121.
+
+\hypertarget{ref-perez2007}{}
+Pérez, F., \& Granger, B. (2007). IPython: A System for Interactive
+Scientific Computing, \emph{9}(3), 21--29.
+doi:\href{https://doi.org/10.1109/MCSE.2007.53}{10.1109/MCSE.2007.53}
+
+\hypertarget{ref-ramos2015a}{}
+Ramos, A. H., Lichtenstein, L., Gupta, M., Lawrence, M. S., Pugh, T. J.,
+Saksena, G., \ldots{} Getz, G. (2015). Oncotator: Cancer Variant
+Annotation Tool. \emph{Human Mutation}, \emph{36}(4), E2423--E2429.
+doi:\href{https://doi.org/10.1002/humu.22771}{10.1002/humu.22771}
+
+\hypertarget{ref-rees2016}{}
+Rees, M. G., Seashore-Ludlow, B., Cheah, J. H., Adams, D. J., Price, E.
+V., Gill, S., \ldots{} Schreiber, S. L. (2016). Correlating chemical
+sensitivity and basal gene expression reveals mechanism of action.
+\emph{Nature Chemical Biology}, \emph{12}(2), 109--116.
+doi:\href{https://doi.org/10.1038/nchembio.1986}{10.1038/nchembio.1986}
+
+\hypertarget{ref-rstudio2012}{}
+RStudio. (2012). RStudio: Integrated development environment for R
+(Version 1.1.447). Boston, MA: RStudio.
+
+\hypertarget{ref-safikhani2016}{}
+Safikhani, Z., El-Hachem, N., Smirnov, P., Freeman, M., Goldenberg, A.,
+Birkbak, N. J., \ldots{} Haibe-Kains, B. (2016). Safikhani et al. reply.
+\emph{Nature}, \emph{540}(7631), E2--E4.
+doi:\href{https://doi.org/10.1038/nature19839}{10.1038/nature19839}
+
+\hypertarget{ref-safikhani2017}{}
+Safikhani, Z., Smirnov, P., Freeman, M., El-Hachem, N., She, A., Rene,
+Q., \ldots{} Haibe-Kains, B. (2017). Revisiting inconsistency in large
+pharmacogenomic studies. \emph{F1000Research}, \emph{5}.
+doi:\href{https://doi.org/10.12688/f1000research.9611.3}{10.12688/f1000research.9611.3}
+
+\hypertarget{ref-schriml2019}{}
+Schriml, L. M., Mitraka, E., Munro, J., Tauber, B., Schor, M., Nickle,
+L., \ldots{} Greene, C. (2019). Human Disease Ontology 2018 update:
+Classification, content and workflow expansion, 1--8.
+doi:\href{https://doi.org/10.1093/nar/gky1032}{10.1093/nar/gky1032}
+
+\hypertarget{ref-seashore-ludlow2015}{}
+Seashore-Ludlow, B., Rees, M. G., Cheah, J. H., Cokol, M., Price, E. V.,
+Coletti, M. E., \ldots{} Schreiber, S. L. (2015). Harnessing
+Connectivity in a Large-Scale Small-Molecule Sensitivity Dataset.
+\emph{Cancer Discovery, Cancer Discovery}, \emph{5, 5}(11, 11), 1210,
+1210--1223.
+doi:\href{https://doi.org/10.1158/2159-8290.CD-15-0235,\%2010.1158/2159-8290.CD-15-0235}{10.1158/2159-8290.CD-15-0235, 10.1158/2159-8290.CD-15-0235}
+
+\hypertarget{ref-shoemaker2006}{}
+Shoemaker, R. H. (2006). The NCI60 human tumour cell line anticancer
+drug screen. \emph{Nature Reviews Cancer}, \emph{6}(10), 813--823.
+doi:\href{https://doi.org/10.1038/nrc1951}{10.1038/nrc1951}
+
+\hypertarget{ref-stinson1992}{}
+Stinson, S., Alley, M., Kopp, W., Fiebig, H., Mullendore, L., Pittman,
+A., \ldots{} Boyd, M. (1992). Morphological and immunocytochemical
+characteristics of human tumor cell lines for use in a disease-oriented
+anticancer drug screen, \emph{12}(4), 1035--1053.
+
+\hypertarget{ref-tamborero2018}{}
+Tamborero, D., Rubio-Perez, C., Deu-Pons, J., Schroeder, M. P.,
+Vivancos, A., Rovira, A., \ldots{} Lopez-Bigas, N. (2018). Cancer Genome
+Interpreter annotates the biological and clinical relevance of tumor
+alterations. \emph{Genome Medicine}, \emph{10}.
+doi:\href{https://doi.org/10.1186/s13073-018-0531-8}{10.1186/s13073-018-0531-8}
+
+\hypertarget{ref-varley2013}{}
+Varley, K. E., Gertz, J., Bowling, K. M., Parker, S. L., Reddy, T. E.,
+Pauli-Behn, F., \ldots{} Myers, R. M. (2013). Dynamic DNA methylation
+across diverse human cell lines and tissues. \emph{Genome Research},
+\emph{23}(3), 555--567.
+doi:\href{https://doi.org/10.1101/gr.147942.112}{10.1101/gr.147942.112}
+
+\hypertarget{ref-wagner2018}{}
+Wagner, A. H., Walsh, B., Mayfield, G., Tamborero, D., Sonkin, D.,
+Krysiak, K., \ldots{} Margolin, A. (2018). A harmonized
+meta-knowledgebase of clinical interpretations of cancer genomic
+variants. doi:\href{https://doi.org/10.1101/366856}{10.1101/366856}
+
+\hypertarget{ref-wang2015a}{}
+Wang, T., Birsoy, K., Hughes, N. W., Krupczak, K. M., Post, Y., Wei, J.
+J., \ldots{} Sabatini, D. M. (2015). Identification and characterization
+of essential genes in the human genome. \emph{Science (New York, N.Y.)},
+\emph{350}(6264), 1096--1101.
+doi:\href{https://doi.org/10.1126/science.aac7041}{10.1126/science.aac7041}
+
+\hypertarget{ref-waskom2012}{}
+Waskom, M. (2012). Seaborn: Statistical data visualization (Version
+0.9.0). Retrieved from \url{http://seaborn.pydata.org/}
+
+\hypertarget{ref-wickham2016}{}
+Wickham, H. (2016). Ggplot2: Elegant Graphics for Data Analysis (Version
+3.0.0). Retrieved from \url{http://ggplot2.org}
+
+\hypertarget{ref-yang2012}{}
+Yang, W., Soares, J., Greninger, P., Edelman, E. J., Lightfoot, H.,
+Forbes, S., \ldots{} Garnett, M. J. (2012). Genomics of Drug Sensitivity
+in Cancer (GDSC): A resource for therapeutic biomarker discovery in
+cancer cells. \emph{Nucleic Acids Research}, \emph{41}(D1), D955--D961.
+doi:\href{https://doi.org/10.1093/nar/gks1111}{10.1093/nar/gks1111}
+
+\hypertarget{ref-yu2015}{}
+Yu, M., Selvaraj, S. K., Liang-Chu, M. M. Y., Aghajani, S., Busse, M.,
+Yuan, J., \ldots{} Neve, R. M. (2015). A resource for cell line
+authentication, annotation and quality control. \emph{Nature},
+\emph{520}(7547), 307--311.
+doi:\href{https://doi.org/10.1038/nature14397}{10.1038/nature14397}
 
@@
 
-\printbibliography
-
 \end{document}

### 2018-12-19 manuscript.Rmd

@@
 abstract: |
-  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
-
-  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
-
-  One sentence clearly stating the **general problem** being addressed by  this particular study.
-
-  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
-
-  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
-
-  One or two sentences to put the results into a more **general context**.
-
-  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
-
-  <!-- https://tinyurl.com/ybremelq -->
+  Multiple high-throughput functional screens in cancer cell lines have generated large amounts of information on drug efficacy in a variety of genomic contexts and cancer lineages.
+Inconsistencies between datasets have led us to investigate whether these large-scale screens reproduce established clinical drug-gene associations and if genomic features particular to specific genes improve said reproducibility.
+We evaluated three large-scale, small-molecule drug screens and one CRISPR/Cas9 gene essentiality screen, all within the context of clinical interpretations derived from a new cancer variant annotation resource published by the Variant Interpretation for Cancer Consortium (VICC).
+We identified low levels of concordance between the three drug screen datasets and clinical drug-gene associations using mutation status, gene expression, and copy number as genomic indicators.
+Less than half of the clinical drug-gene cancer associations from the VICC resource were identified in these three drug screen datasets, suggesting a barrier to translating findings from these large-scale screens into the clinic.
 
@@
 biblio-style      : "apa"
-output            :
-  papaja::apa6_pdf:
-    citation_package: biblatex
+output            : papaja::apa6_pdf
 ---
@@
 ```{r setup, include = FALSE}
-library("papaja")
+# library("papaja")
 # install.packages("tinytex")
@@
 # install.packages("citr")
+# devtools::install_github("benmarwick/wordcountaddin", type = "source", dependencies = TRUE)
+# update wordcount in Addins
 ```
@@
 
-[@aksoy2017]
+# Introduction
 
-# Introduction
+Cancer cell lines are a long-standing model for systematic testing of candidate therapeutics, beginning with the National Cancer Institute 60 (NCI60) assay from the late 1980s [@alley1988; @shoemaker2006; @stinson1992], which has been used to screen over 100,000 compounds as of 2010 [@holbeck2010].
+Since then, numerous small-molecule and gene essentiality screens of various scales and study aims have been conducted in cell lines, from grouping drugs by therapeutic target similarity [@greshock2010] to screening only near-haploid cell lines to generate genome-level insights into gene essentiality [@wang2015a] to broadly identifying cancer dependencies with large-scale screens in multiple cancer types [@mcdonald2017; @mcfarland2018; @meyers2017; @patel2017] or select lineages [@heiser2009; @marcotte2012; @patel2017].
+Despite their widespread use, cancer cell lines are known to have issues with inconsistent naming conventions and contamination [@yu2015], and some cell lines have been shown to vary widely at the genetic level and in response to drug treatment across strains [@ben-david2018].
+Additionally, comparisons between cancer cell lines and tumors indicate that cell lines have higher numbers of genomic aberrations [@domcke2013; @mouradov2014; @neve2006] and tend to be hypermethylated [@paz2003; @varley2013], which could prove an impediment to translating cell line discoveries into the clinic.
+
+There have also been debates over consistency between drug screen datasets, namely the Broad Institute’s and Novartis Institutes for Biomedical Research’s Cancer Cell Line Encyclopedia (CCLE) [@barretina2012; @consortium2015] and the Genomics of Drug Sensitivity in Cancer (GDSC) from the Cancer Genome Project at the Wellcome Sanger Institute and the Center for Molecular Therapeutics at Massachusetts General Hospital Cancer Center [@garnett2012; @yang2012].
+The GDSC has also been referred to as the Cancer Genome Project (CGP) and the Sanger dataset.
+Studies have shown that drug-gene interactions matched between CCLE and GDSC exhibited poor correlation and inconsistencies [@haibe-kains2013; @jang2014], prompting other groups to join the debate on how best correct for experimental and methodological variation between the original drug screens and subsequent computational analysis [@consortium2015; @geeleher2016; @geeleher2016a; @hatzis2014; @haverty2016; @safikhani2016; @safikhani2017].
+
+The prevalence and importance of cancer cell lines in large-scale therapeutic research and the apparent inconsistencies between the GDSC and CCLE encouraged us to compare the results from these functional screens to clinical drug-gene associations.
+An outstanding question concerning studies based on cancer cell lines is whether these the cell line systems can accurately model tumor dynamics or recapitulate clinical cancer vulnerabilities, and many large-scale grants and clinical trials are fundamentally anchored by results from screens conducted in cancer cell lines.
+Thus, our goal was to evaluate how well these functional screens recapitulate known drug, gene, and tumor type associations that are currently used in clinical decision-making.
+
+We derived our clinical associations from a new project conducted by the Variant Interpretation for Cancer Consortium (VICC; https://cancervariants.org/), a Driver Project for the Global Alliance for Genomics and Health (GA4GH) [@theglobalallianceforgenomicsandhealth2016].
+The VICC has curated annotations of known cancer variants at varying levels of evidence from multiple resources [@wagner2018]: the Precision Medicine Knowledgebase [@huang2016], MolecularMatch (https://www.molecularmatch.com/index.html), OncoKB [@chakravarty2017], Jackson Labs Clinical Knowledgebase [@patterson2016], Clinical Interpretations of Variance in Cancers (CIViC) [@griffith2017], and the Cancer Genome Interpreter (CGI) [@tamborero2018].
+These harmonized variants are hosted on an ElasticSearch (Kibana v6.0) platform called Genotype to Phenotype (G2P, https://search.cancervariants.org/#*) that allows users to query and filter aggregated evidence from the various databases listed above as well as the GA4GH beacon service (http://beacon-network.org/#/), which yields access to genetic mutation data from over 200 datasets as of 2016 [@theglobalallianceforgenomicsandhealth2016].
+For drug screen datasets, we focus on three well-known, large-scale drug projects: the CCLE and GDSC, which were mentioned above, and the Center for the Science of Therapeutics at the Broad Institute’s Cancer Therapeutics Response Portal (CTRP) dataset [@basu2013; @rees2016; @seashore-ludlow2015].
+We also analyzed the results from a large-scale CRISPR/Cas9 screen conducted by the Broad Institute’s Cancer Dependency Map project (DepMap) using the Avana knockout library [@doench2016a; @meyers2017], which will address whether gene essentiality screens via CRISPR yield results comparable to functional drug screens.
 
@@
 
+## Comparison of G2P drug-gene associations and CCLE, CTRP, and GDSC
+
+G2P designed a set of standards for stratifying their database’s cancer variant interpretations, ranging from preclinical data at the low-evidence end (level D) to clinically actionable interpretations at the high-evidence end (level A).
+To test only these clinically actionable associations, we filtered the G2P dataset for only level-A G2P interpretations, of which there were 1,296 (see Methods).
+All compounds screened within the GDSC, CTRP, and CCLE datasets are considered “small molecules” and are respectively linked to Compound (CID) numbers used for indexing in the PubChem database (https://pubchem.ncbi.nlm.nih.gov/).
+As a result, non-small molecules, which include proteins and biologics (i.e.
+monoclonal antibodies), that had level-A G2P evidence could not be included in our comparisons.
+Thus, G2P interpretations for which the compound did not have a matching CID code were excluded from further analysis as were interpretations that did not have an associated compound, resulting in removal of 402 interpretations (Table 1).
+It should be noted that cisplatin, a small molecule, was excluded due to its being indexed with a ChEMBLdb identifier (https://www.ebi.ac.uk/chembl/), which we did not manually re-index to a CID to avoid accidental mischaracterization.
+
+After filtering, 894 level-A G2P interpretations were carried forward in subsequent analyses, constituting 57 unique drugs and 34 unique genes in 88 distinct level-A combinations (Figure 1A).
+The number of level-A interpretations per drug ranged from 1 to 176 (M = 15.7, SD = 34.6), from 1 to 264 (M = 26.2, SD = 61.6) per gene, and for each level-A drug-gene combination, the range was 1 to 103 (M = 10.1, SD = 19.8).
+These unique drugs, genes, and combinations are hereafter referred to as G2P drugs, G2P genes, and G2P associations.
+Of the 57 unique G2P drugs, 37 of them were screened in at least one of the drug screen datasets, 14 were screened in two of the three datasets, and only three drugs were screened in all three datasets.
+The remaining 20 un-screened G2P drugs suggests an incompleteness of these drug screens, though these projects frequently release new screening data that may include these drugs in future releases.
+
+Using cell-line-specific point mutation annotations from the CCLE, we compared z-score-transformed area under the dose-response curve (AUC) distributions between mutant and wildtype cell lines for all G2P genes for each G2P drug tested in the CCLE, CTRP, and GDSC drug screens (Figures 1B and 2A).
+At uncorrected $\alpha$ = 0.05, Wilcoxon rank-sum tests revealed that in CCLE, the AUC distributions of mutant and wildtype groups for 10 out of 170 (5.88%) tested drug-gene combinations were significantly different, 91 out of 918 (9.91%) were significantly different for CTRP, and 61 out of 850 (7.18%) for GDSC.
+We observe little concordance between the number of interpretations for each G2P association and the significance of mutation status on AUC for said G2P association, suggesting that mutation status alone is not a robust predictor of clinically actionable genetic targets.
+This led us to examine the correlations between AUC and gene expression and AUC and copy number, two other genomic features that are known to associate with cancer and drug response.
+
+## Do small-molecule screens in cancer cell lines recapitulate clinical drug-gene associations?
+
+We compared the distribution of level-A G2P associations (Figure 1A) and the associated p-values from the mutation status comparisons (Figure 1B) with a null distribution of p-values derived from all pairwise combinations of G2P genes and the G2P drugs tested in each dataset, less any of the 88 distinct combinations with G2P interpretations, i.e.
+the non-gray squares in the right heatmap of Figure 1A (Figure 3A).
+To formally test concordance between clinically actionable variants and drug screen results, we conducted an independent, two-group t-test to compare the distributions of p-values of drug-gene combinations that either were or were not represented with level-A evidence in G2P, which indicated that the distributions of p-values did not significantly differ for CCLE [t(9) = 0.25, p = 0.81], CTRP [t(51) = 0.85, p = 0.40], nor GDSC [t(47) = -0.56, p = 0.58]  (Table 2).
+This further supports that mutation status is not a robust genomic feature for predicting therapeutic responses.
+
+Similar tests were conducted for the distributions of Pearson correlation coefficients (r) between the number of level-A G2P associations and gene expression (RPKM) and copy number (log2 ratio) of the gene in the association (Figures 3B-C).
+Example r derivations are shown in Figures 2B-C.
+Absolute values of r were used to simplify extreme values in both directions for testing.
+The difference in the CCLE |r| distributions for both gene expression [t(8) = 1.43, p = 0.19] and copy number [t(8) = 2.48, p = 0.23] were non-significant, which is likely explained by the small sample size since only five G2P drugs were screened in the CCLE dataset.
+For both the CTRP and GDSC screens, |r| values for gene expression correlations were significantly greater for the level-A G2P associations than the null distribution [tCTRP(49) = 3.79, pCTRP < 0.001; tGDSC(44) = 2.97, pGDSC = 0.005].
+The |r| distributions using copy number were also significantly different for CTRP [t(49) = 2.48, p = 0.017] but not for GDSC [t(44) = 1.95, p = 0.058].
+
+In all three datasets for both level-A G2P associations and null distribution associations, there are more significant |r| values when using gene expression as the genomic feature than when using copy number (Table 2), which corresponds with previous work showing that gene expression is an informative molecular feature when assessing drug sensitivity (Jang et al., 2014; Sirota et al., 2011).
+Additionally, in all cases, there are more significant r values when using copy number than there are significant p-values from the mutation status comparisons.
+Though observational, these results suggest an order of predictive robustness for these three genomic features when used in isolation: Gene expression > copy number > mutation status.
+Additionally, across all three genomic features, CTRP consistently identified a higher percentage of its possible level-A G2P associations than GDSC, and similarly, GDSC identified a higher percentage than CCLE.
+In the CCLE-GDSC debate, inconsistency between the datasets was attributed to the groups using two very different assays for generating AUC measurements though it was undecided which was more accurate (Haibe-Kains et al., 2013; Jang et al., 2014; Weinstein & Lorenzi, 2013).
+Our results provide very preliminary evidence that GDSC is more accurate than CCLE in regards to reproducing clinical associations.
+However, CTRP may be even more accurate than both GDSC and CCLE.
+
+## Do these pancancer drug-gene associations penetrate to the lineage-specific level?
+
+- What do these correlations with mutation status, gene expression, and copy number look like when you constrict to a specific lineage?
+- When you restrict, do the correlations become more distinct?
+- Are the lineage-specific results approximately the same as the pancancer results?
+- Looking at a histogram of p-values, if the histogram is flat, then nothing is significant (note from meeting on 11/16)
+
+In the 894 level-A G2P interpretations, there was a wide variation in the specificity of cancer description, ranging from “Waldenström macroglobulinemia” and “hyper eosinophilic advanced syndrome” on the more detailed end to “cancer” on the broad end.
+Similarly, the drug screen datasets had a wide range in lineage specificity, e.g.
+CCLE, GTRP, and GDSC all had lineages labeled “leukemia” and “T-cell childhood acute lymphocytic leukemia” and the CRISPR dataset had cell lines labeled “Epstein-Barr virus-related Burkitt lymphoma” and “lymphoma.” To more easily conduct comparative analyses in a cancer-specific manner, we developed a more general lineage grouping method derived from the Human Disease Ontology identity codes (DOIDs, http://disease-ontology.org/) (Schriml et al., 2019) assigned to each cell line, yielding 27 unique lineage groupings.
+This custom lineage grouping was included in our harmonized cancer cell line database (see METHODS).
+
+In the level-A G2P interpretations, there were 102 unique drug-gene-lineage combinations (DGLs), representing seven of our curated cancer lineages: cancer, breast cancer, leukemia, lung cancer, ovarian cancer, skin cancer, and thyroid cancer.
+CCLE had data for nine DGLs, CTRP had data for 61, and GDSC had data for 53, yielding a total of 73 unique DGLs across all three datasets.
+
+At an alpha of 0.05, no DGLs were identified in the CCLE screen when using mutation status as a correlate (n = 7), but CTRP and GDSC identified six and five, respectively, in skin cancer, lung cancer, and cancer.
+These significant associations did not hold after Bonferroni correction in CTRP (n = 48, $\alpha$adjusted = 0.001) or GDSC (n = 39, $\alpha$adjusted = 0.001).
+
+When using gene expression as the genomic feature, three CCLE DGLs had significant correlations at an adjusted alpha of 0.006 (n = 9).
+Two of these three DGLs were also significantly correlated with copy number (n = 9, $\alpha$adjusted = 0.006).
+
+In CTRP, AUC of 19 DGLs significantly correlated with gene expression, 12 of which were significant after correction (n = 61, $\alpha$adjusted = 0.0008).
+Copy number correlations were significant for 12 DGLs, with three DGLs significant post-correction (n = 61, $\alpha$adjusted = 0.0008).
+
+AUC of 16 DGLs in GDSC significantly correlated with gene expression.
+At an adjusted alpha of 0.0009 (n = 53) eight of them were significant.
+Fewer DGLs were significant when correlating AUC with copy number with 6 significant at an alpha of 0.05 and 1 significant at an adjusted alpha of 0.0009 (n = 53).
+
+Interestingly, when we test the effect of mutation status on drug response for the DGLs derived from all pairwise combinations of G2P drugs and genes… (Figure ##1).
+
+## Are CRISPR/Cas9 gene essentiality results comparable to those of functional drug screens?
+
+The CRISPR screen from the Broad Institute reports gene dependency using CERES scores (Meyers et al., 2017), which are generated from sgRNA depletion scores and eliminate bias arising from the effect of copy number variation on Cas9 DNA cleavage.
+The lower the CERES score, the higher the likelihood that the gene is essential in the associated cell line.
+Scores are scaled per cell line such that a score of 0 is the median effect of nonessential genes and -1 is the median effect of common core essential genes.
+Of the 34 G2P genes, only G6PD was not targeted by an sgRNA in the CRISPR dataset.
+
+When we don’t account for lineage, Wilcoxon rank-sum tests revealed that mutations in eight of the 33 (24.2%) G2P genes significantly correlated with CERES score ($\alpha$ = 0.05): KRAS (p < 0.001), BRAF (p < 0.001), BRCA2  (p < 0.001), CYP19A1 (p = 0.004), TSC2 (p = 0.005), JAK2 (p = 0.031), DPYD (p = 0.042), and UGT1A1 (p = 0.048).
+Gene expression (RPKM) of 17 (51.5%) G2P genes significantly correlated with CERES score, as did copy number (log2-ratio) for 14 (42.4%) G2P genes (Figure ##2).
+For the purpose of comparison to the drug screen data, if we treat CRISPR knockdown like a small-molecule drug, then these results are similar to the results from CCLE, CTRP, and GDSC (Table 2).
+
+- Lineage?
+
+## Are known copy number driven associations recapitulated in the drug and CRISPR screens?
+
+If a gene’s response to is copy number driven, we would expect copy number to significantly correlate with AUC and gene essentiality scores, as would gene expression is expression and copy number are associated.
+
+In a lineage-agnostic context of the CRISPR screen, ERBB2 gene essentiality score had a significant negative correlation with ERBB2 gene expression (p < 10-12, r = -0.31) and ERBB2 copy number (p < 10-15, r = -0.34) (Figure ##2).
+Similarly, MET gene essentiality also correlated with both MET gene expression (p < 10-12, r = -0.31) and copy number (p < 10-8, r = -0.25).
+Notably, BRCA1 also significantly correlated with both gene expression (p < 0.001, r = 0.16) and copy number (p < 0.01, r = 0.14).
+BRCA2 significantly correlated with all three of the genomic features tested: gene expression (p < 0.05, r = 0.10), copy number (p < 10-7, r = 0.23), and mutation status (p < 0.001).
+
+## Which genomic features drive KRAS, EGFR, and BRAF drug-gene associations?
+
 # Discussion
+
+Level-A G2P interpretations correspond to clinical evidence that suggests efficacy of gene targets and/or drugs, and this work questions whether these relationships manifest themselves in in vitro drug screens.
+We have demonstrated that on its own, mutation status is not a robust predictor of drug efficacy and that copy number and gene expression fare better as predictors.
+However, for these three genomic features in all three datasets, only 11.1% (mutation status, 1 of 9, CCLE) to 47.9% (gene expression, 23 of 48, CTRP) (Table 2), of the level-A G2P drug-gene associations in the respective dataset were significant at an uncorrected $\alpha$ = 0.05.
+This suggests that while the drug screens successfully identify some clinically relevant drug-gene associations, many associations are also missed, which raises the question of the extent to which clinical researchers can rely on in vitro drug screens when attempting to develop and select therapeutics for cancer patients.
+
+These results also highlight the need to account for the complex differences inherent between data generated in clinical scenarios and data captured in highly controlled, artificial in vitro environments.
+Potential sources of variation and error include the fact that cells growing in a laboratory as opposed to those, even of the same tissue type, growing in a multicellular organism are exposed to differing sets of stressors and signals that can significantly impact intracellular signaling pathways, irrespective of shared genomic profiles.
+These differences can include, but are not be limited to, immunologic reactions, both adaptive and intrinsic (e.g.
+cytokine signaling, inflammation), endocrine (e.g.
+stress hormones), and nervous system stimulation, all of which can have significant downstream implications on cellular behavior in the context of therapeutic efficacy.
+Similarly, a laboratory environment and in vitro cell culture introduce abnormal growth conditions with respect to extracellular matrix composition, nutrient availability, and cell density, all of which have the potential to alter cellular signaling and thus render a drug ineffective during screening despite would-be in vivo activity.
+
+In the era of precision medicine, the ultimate boon would be that the unique omics signatures of a patient’s individual cancer can be used to guide treatment.
+High-throughput, in vitro screens of targeted cancer agents against cell lines with known omics profiles are beneficial for testing hypotheses concerning the mechanisms of action for these agents and they allow for scalability and systematic screening.
+However, extrapolating the potential downstream effects of inhibiting a major growth pathway (e.g.
+MAPK, IP-DAG) to predict the clinical prognosis and progression of a multicellular tumor mass growing in a complex environment, compounded with the cross-reacting effects of tumor genomic heterogeneity, make it a questionable statement that one can safely predict clinical consequences from suppressing a single pathway in a model system, as evidenced by our findings of fewer than half of the known clinical associations in the three drug screen datasets.
+The benefits of these cancer cell line models, in contrast, lie in their ability to assess the big-picture effects of these agents.
+In order to fully understand therapeutic drug response, a higher degree of granularity is needed.
+Additional effort to combine more cell line information such as gene expression, epigenetic profiles, and proteomic data with mutational profiles is essential to improving the efficacy and validity of in vitro cell line screens.
+Further benefit could be derived from conducting these screens in environments that are more in line with the clinical scenarios we are trying to predict.
+This would include things such a 3-dimensional cell culture, coculturing with stromal cells to mimic the tumor microenvironment, as well as other modalities that can attempt to better replicate in vivo environments.
+
+As a next step to improve the informational granularity of the analysis presented here, our subsequent goal will be to assess the extent to which these drug-gene associations are specific to individual cancer cell line lineages, which are available and annotated in the data sets analyzed within this report.
+By evaluating how many clinically actionable associations are identified in these large-scale functional screens, we can begin to address best practices for translating discoveries from these tumor models into clinical trials.
 
@@
 
-We used `r cite_r("manuscript_r_references.bib")` for all our analyses.
+## G2P cancer variants
+
+Cancer variants with the highest level of evidence (i.e.
+level A) in the Genotype to Phenotype (G2P) database were retrieved from the Variant Interpretation for Cancer Consortium (VICC) portal (https://search.cancervariants.org/#*) [@wagner2018] using a customized JSON-query script.
+All JSON queries were passed to the available application program interface (API) where a request was made for all drug-gene associations with level-A evidence via the G2P evidence label, i.e.
+association.evidence_label.
+From manual inspection using G2P’s front-end Kibana interface, it was known that, at the time of the last query, 27 November 2018, there were 1,297 known level-A associations.
+Due to the limited request processing capabilities of the G2P JSON API, queries were batched into packets of 10 data points, for a total of 130 requests made in succession.
+Each returned request was processed as JSON object and searched to identify any existing key:value pairs for the following variables: evidence level, mutation, gene, chromosome, start, end, ref, alt, direction, phenotype description, phenotype family, phenotype ID, drug, drug ID, feature names, and sequence ID.
+For any evidence point where a given key:value pair was not found or unavailable, a value of -1 was assigned.
+One of the 1,297 level-A entries was irretrievable, yielding a final dataset of 1,296 level-A G2P interpretations, which were stored in a pandas data table and exported in CSV format.
+The VICC’s methods for the harvesting and harmonizing of cancer variants is available in a GitHub repository from Oregon Health & Science University (https://github.com/ohsu-comp-bio/g2p-aggregator).
+
+## DepMap data retrieval and processing
+
+CRISPR/Cas9, CCLE mutation calls, and CCLE copy number data were all retrieved from the Broad Institute’s Cancer Dependency Map (DepMap) Public 18Q4 release via the DepMap data portal (https://depmap.org/portal/download/) [@broaddepmap2018a].
+Gene expression data was retrieved from the DepMap Public 18Q3 release [@broaddepmap2018] from the same data portal.
+For cell lines with no CCLE annotation, the DepMap group drew raw copy number and mutation data from whole exome sequencing data produced by the Wellcome Trust Sanger Institute [Catalogue Of Somatic Mutations In Cancer (COSMIC, https://cancer.sanger.ac.uk/cell_lines) [@bamford2004; @forbes2017]; European Genome-phenome Archive [@lappalainen2015], accession number EGAD00001001039] and processed the data following the CCLE pipelines to ensure consistency.
+
+### CRISPR/Cas9 screen
+
+Gene effect scores for 17,634 genes in 517 cell lines were inferred from a CRISPR/Cas9 (clustered regularly interspaced short palindromic repeats/CRISPR-associated 9) screen using the Broad Institute’s Avana knockout library [@doench2016a].
+The Broad Institute’s data processing and screening methods are available from the figshare record [@broaddepmap2018a] and the original publication of CERES, the algorithm that computes inferred gene dependency scores [@meyers2017].
+The DepMap releases new data quarterly, with the current data set being the 18Q4 release.
+This release has 175 more cell lines than the original data release that was published with CERES (dataset: gene_effect.csv, accessed 15 November 2018).
+
+### Mutation calls
+
+The CCLE provided mutation annotations in 19,280 genes across 1,596 cell lines (dataset: depmap_18Q4_mutation_calls.csv, accessed 14 November 2018).
+CCLE called substitutions using MuTect [@cibulskis2013] and annotated variants using Oncotator [@ramos2015a] and indels using Indelocator (https://software.broadinstitute.org/cancer/cga/indelocator).
+We filtered mutation calls for point mutations, defined as single-nucleotide insertions, deletions, and substitutions, regardless of result, i.e.
+frameshift or missense mutation.
+For this analysis, cell lines harboring non-silent point mutations were considered “mutant” for the gene in question.
+All other mutations and genes without annotation in the Mutation Annotation Format (MAF) file were considered “wildtype.” “Mutant” and “wildtype” calls were binarily encoded per-gene/per-cell line, regardless of quantity of harbored mutations per gene in a given cell line.
+
+### Copy number data
+
+The CCLE generated genomic copy number (CN) data using the Affymetrix Genome-Wide Human SNP Array 6.0 and GenePattern pipeline [@thecancergenomeatlasresearchnetwork2008] and normalized segmented CN log2-ratios for 23,299 genes across 1,098 cell lines using circular binary segmentation [@olshen2004] (dataset: public_18Q4_gene_cn.csv, accessed 15 November 2018).
+
+### Gene expression data
+
+The CCLE reports gene expression in RPKM (reads per kilobase per million mapped reads) for 54,356 genes across 1,156 cell lines, generated on the GeneChip Human Genome U133 Plus 2.0 Array (dataset: CCLE_DepMap_18q3_RNAseq_RPKM_20180718.gct, accessed 18 July 2018).
+
+## Drug screen dataset retrieval and harmonization
+
+The Cancer Therapeutics Response Portal (CTRP) drug screen dataset (v2) [@basu2013; @rees2016; @seashore-ludlow2015] was retrieved from the National Cancer Institute’s Cancer Target Discovery and Development (CTD2) Network’s data portal (https://ocg.cancer.gov/programs/ctd2/data-portal, accessed 6 June 2018).
+The Genomics of Drug Sensitivity in Cancer (GDSC) drug screen dataset [@garnett2012; @yang2012] was retrieved from the data portal at (https://www.cancerrxgene.org/downloads, accessed 19 June 2018).
+The Cancer Cell Line Encyclopedia (CCLE) drug screen dataset [@barretina2012; @consortium2015] was retrieved from the Broad Institute’s data portal (https://portals.broadinstitute.org/ccle, accessed 20 June 2018).
+
+### Cell line harmonization
+
+In an effort to compare CCLE, CTRP, GDSC and CRISPR results and include lineage specificity, it was necessary to consolidate cell lines screened in each dataset.
+Given that unique identifiers can be used between studies, it was necessary to standardize the identity of each cell line with a common source.
+To achieve this, a freely available cell line database called Cellosaurus (v26.0, 14 May 2018) [@bairoch2018] was downloaded and merged with the Broad Institute’s DepMap cell line data (accessed 8 June 2018) to create a harmonized cancer cell line database containing synonymous identifiers that enabled consolidation of all cell lines used in CCLE, CTRP, GDSC and CRISPR into a common framework.
+Subsequent additions to this database include the merging of DepMap IDs used in the 18Q3 and 18Q4 DepMap data releases.
+We curated missing synonyms and identifiers, and we manually annotated the granularity of lineage labeling for all cell lines analyzed in this study based on their Human Disease Ontology identity codes (DOIDs, http://disease-ontology.org/) [@schriml2019], resulting in 27 unique lineages.
+For ease of comparison between datasets, we labeled all cell lines with custom, randomized identifiers.
+
+### AUC harmonization
+
+The CCLE reports cell line sensitivity to small molecules as an activity area measured above the dose-response curve (ActArea), while both CTRP and GDSC report small molecule activity as area under the dose-response curve (AUC).
+Since ActArea is reported with a scale of 0 to 8, we converted CCLE’s ActArea values to AUC via:
+
+$$AUC=1- \frac{ActArea}{8}$$
+
+All AUC values across the three drug screen datasets were z-score transformed:
+
+$$z = \frac{AUC - \mu_{AUC}}{\sigma_{AUC}}$$
+
+where AUC is the mean AUC across all drug-cell line combinations in the dataset and AUC is the standard deviation.
+
+## Computational
+
+For Figure 1, all data were imported and manipulated using pandas (v0.23.0) [@mckinney2011] and plotted using seaborn (v0.90) [@waskom2012], which sat on top of matplotlib (v2.2.2) [@hunter2007] and was executed on Python (v2.7.15) (Python Software Foundation, https://www.python.org/) in an IPython (v5.5.0) [@perez2007] kernel within a localhost Jupyter (v5.2.2) notebook [@kluyver2016].
+All other analyses were conducted in R (v3.5.0) (R Foundation for Statistical Computing, https://www.R-project.org/) in an RStudio environment (v1.1.447) [@rstudio2012].
+All other plots were drawn using the ggplot2 (v3.0.0) R package [@wickham2016].
+
+### Statistics
+
+Wilcoxon tests were computed using the ggpubr (v.`r print(packageVersion("ggpubr"))`) R package [@kassambara2018].
+
+For computing Pearson correlation coefficients, if there were three or fewer data points, then the correlation was not done and a value of NA was supplied.
 
@@
 # References
-
-```{r create_r-references}
-r_refs(file = "manuscript_r_references.bib")
-```
 

### 2018-12-19 manuscript_analysis.Rmd

---
title: "Manuscript"
author: "Sally Claridge"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    theme: cerulean
    number_sections: true
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: true
    code_folding: hide
    pandoc_args: [
      "+RTS", "-K2048m",
      "-RTS"
    ]
---

Analysis of the Broad's Avana CRISPR (Broad Institute Cancer Dependency Map 2018, Meyers et al. 2017) and the Broad and Dana-Farber Cancer Institite's Achilles shRNA (MacFarland et al. 2018, Data Science 2018).

The Avana screen produced results using [CERES](https://depmap.org/ceres/) (Meyers et al. 2017) ([GitHub](https://github.com/cancerdatasci/ceres)), which generates gene dependency scores from sgRNA depletion scores from gene essentiality screens and eliminates bias arising from the effect of copy number variation on Cas9 DNA cleavage. The lower the CERES score, the higher the likelihood that the gene is essential in the associated cell line. Scores are scaled per cell line such that a score of 0 is the median effect of nonessential genes and -1 is the median effect of common core essential genes.

All annotation files (copy number, mutation status, and gene expression) (Consortium and Consortium 2015, Barretina et al. 2012) were downloaded from the [DepMap Data Portal](https://depmap.org/portal/download/).

# SET UP

--------------------------------------------------------------------------------

```{r setup, include=FALSE}
set.seed(1234)
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
# num_cores <- parallel::detectCores()
options(mc.cores = parallel::detectCores(), expressions = 5e5)
```

Edited `.Renviron` to avoid "Error: memory exhausted (limit reached?)" when melting the GE dataset, as per the suggestion from [StackOverflow](https://stackoverflow.com/questions/51295402/r-on-macos-error-vector-memory-exhausted-limit-reached)
```
cd ~
touch .Renviron
open .Renviron
# Added following line to .Renviron:
R_MAX_VSIZE=100Gb
```

```{r}
library(bsselectR)
library(cowplot)
theme_set(theme_light())
library(data.table)
library(ggpubr)
library(ggrepel)
library(ggsignif)
library(gplots)
library(gridExtra)
library(htmlwidgets)
library(kableExtra)
library(papaja)
library(plotly)
library(reshape2)
library(scales)
library(tidyverse)
library(VennDiagram)
# devtools::install_github("crsh/papaja")
```

# FUNCTIONS {.tabset .tabset-fade .tabset-pills}

--------------------------------------------------------------------------------

## Significance thresholding

```{r}
adj_signif <- function(df) {
  # Takes df from compare_means and creates a signif code column for adjusted p-vals
  df$p.signif <- ifelse(df$p.signif == "ns", NA, df$p.signif)
  df$p.signif.adj <- ifelse(df$p.adj <= 0.0001, "****",
                     ifelse(df$p.adj <= 0.001, "***",
                     ifelse(df$p.adj <= 0.01, "**",
                     ifelse(df$p.adj <= 0.05, "*", NA))))
  df$p.short <- formatC(df$p, format = "g", digits =  2)
  df$p.adj.short <- formatC(df$p.adj, format = "g", digits =  2)

  return(df)
}
```

## Wilcoxon tests by drug

```{r}
WilcoxonByDrug <- function(drug, dataset, data_name, grouping_var) {
  if(grouping_var == "lineage") {
    grouper <- c("Hugo_Symbol", "group_general_lineage_name")
  }
  else if(grouping_var == "gene") {
    grouper <- "Hugo_Symbol"
  }
  use_data <- filter(dataset, Drug == drug)
  sig <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = grouper, data = use_data, method = "wilcox.test", p.adjust.method = "BH")
  sig <- adj_signif(sig)
  sig <- sig[order(sig$p),]
  sig$Drug <- drug
  sig$Dataset <- toupper(data_name)
  return(sig)
}

# WilcoxonByDrugAllGenes <- function(melt_file, grid_file, data_name) {
#   druglist <- as.character(unique(melt_file$Drug))
#   sig_df <- NULL
#   for(i in 1:length(druglist)) {
#     print(paste0("Current drug in process: ", druglist[i], " (drug ", i, " of ", length(druglist), ")."))
#     flush.console()
#     melted <- filter(melt_file, Drug == druglist[i])
#     use_data <- merge(grid_file, melted, by = "accession_id", all.x = TRUE)
#     use_data <- merge(use_data, ccl_converter, by = "accession_id", all.x = TRUE)
#     use_data <- merge(use_data, maf_df, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
#     use_data$Mutation_Status_Nonsilent <- ifelse(is.na(use_data$Mutation_Status_Nonsilent), "Wildtype", use_data$Mutation_Status_Nonsilent)
#     use_data$Hugo_Symbol <- factor(use_data$Hugo_Symbol)
#     use_data$AUC <- as.numeric(use_data$AUC)
#     use_data <- filter(use_data, !is.na(use_data$AUC))
#     use_data$Drug_Gene <- paste0(use_data$Drug, "_", use_data$Hugo_Symbol)
#     use_data_ptmuts <- filter(use_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
#     use_data_ptmuts$Keep_PtMut_Tests <- ifelse(use_data_ptmuts$Reference_Allele_Length == 1 | is.na(use_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(use_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
#     use_data_ptmuts <- filter(use_data_ptmuts, Keep_PtMut_Tests == TRUE)
#     
#     sig <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = "Hugo_Symbol", data = use_data_ptmuts, method = "wilcox.test", p.adjust.method = "BH")
#     sig <- adj_signif(sig)
#     sig <- sig[order(sig$p),]
#     sig <- filter(sig, p <= 0.05)
#     sig$Drug <- druglist[i]
#     sig$Dataset <- toupper(data_name)
#     sig_df <- rbind(sig_df, sig)
#   }
#   return(sig_df)
# }
```

## Pearson correlation by lineage
```{r}
PearsonByLineage <- function(lin, dataset, variable) {
  use_data <- filter(dataset, group_general_lineage_name == lin)
  if(variable == "GE") {
    use_data <- filter(use_data, !is.na(RPKM))
    use_data_summ <- use_data %>% count(Drug_Gene)
    use_data_summ <- filter(use_data_summ, n >= 3) # cor.test requires at least 3 non-NA data points
    use_data_filt <- filter(use_data, Drug_Gene %in% as.character(unique(use_data_summ$Drug_Gene)))
    if(nrow(use_data_filt) > 0) {
      pearson_res <- use_data_filt %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$estimate, Pearson_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$p.value)
      pearson_res <- merge(g2p_druggene_tally, pearson_res, all.y = TRUE)
      pearson_res$group_general_lineage_name <- lin
      pearson_res$Pearson_GE_Abs <- abs(pearson_res$Pearson_Corr_GE)
      pearson_res$Pearson_GE_Sign <- ifelse(sign(pearson_res$Pearson_Corr_GE) == 1, "+",
                                              ifelse(sign(pearson_res$Pearson_Corr_GE) == -1, "-", "0"))
      return(pearson_res)
    }
  }
  else if(variable == "CN") {
    use_data <- filter(use_data, !is.na(CN))
    use_data_summ <- use_data %>% count(Drug_Gene)
    use_data_summ <- filter(use_data_summ, n >= 3) # cor.test requires at least 3 non-NA data points
    use_data_filt <- filter(use_data, Drug_Gene %in% as.character(unique(use_data_summ$Drug_Gene)))
    if(nrow(use_data_filt) > 0) {
      pearson_res <- use_data_filt %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$estimate, Pearson_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$p.value)
      pearson_res <- merge(g2p_druggene_tally, pearson_res, all.y = TRUE)
      pearson_res$group_general_lineage_name <- lin
      pearson_res$Pearson_CN_Abs <- abs(pearson_res$Pearson_Corr_CN)
      pearson_res$Pearson_CN_Sign <- ifelse(sign(pearson_res$Pearson_Corr_CN) == 1, "+",
                                              ifelse(sign(pearson_res$Pearson_Corr_CN) == -1, "-", "0"))
      return(pearson_res)
    }
  }
}
```

## Save widget to new directory
```{r}
saveWidgetFix <- function (widget , file, ...) {
  ## A wrapper to saveWidget which compensates for arguable BUG in
  ## saveWidget which requires `file` to be in current working
  ## directory.
  wd <- getwd()
  on.exit(setwd(wd))
  outDir <- dirname(file)
  file <- basename(file)
  setwd(outDir);
  saveWidget(widget, file = file,...)
}
```

## Make lineage mut plots

```{r}
MutPlotsByLineage <- function(lineage_name) {

  use_data <- filter(dgl_mut_grid_summ, group_general_lineage_name == lineage_name)
  use_data$Dataset <- factor(use_data$Dataset, levels = c("CCLE", "CTRP", "GDSC"))
  ticker <- 0

  use_data_ccle <- filter(use_data, Dataset == "CCLE")
  use_data_ccle_summ <- use_data_ccle %>% count(InG2P)
  ccle_lin_p_ttest <- data.frame(statistic = NA,
                                 parameter =  NA,
                                 p.value = NA)
  if(nrow(use_data_ccle_summ) <= 1) {
    ccle_lin_p_ttest_res <-  NA
    ticker <- ticker + 1
    }
  else if(use_data_ccle_summ[use_data_ccle_summ$InG2P == "Yes",]$nn < 2) { ccle_lin_p_ttest_res <-  NA }
  else if(use_data_ccle_summ[use_data_ccle_summ$InG2P == "Yes",]$nn >= 2) {
    ccle_lin_p_ttest <- t.test(use_data_ccle$p ~ use_data_ccle$InG2P)
    ccle_lin_p_ttest_res <- paste0("t(", trunc(ccle_lin_p_ttest$parameter), ") = ", round(ccle_lin_p_ttest$statistic, 2), ", p = ", round(ccle_lin_p_ttest$p.value, 3))
  }

  use_data_ctrp <- filter(use_data, Dataset == "CTRP")
  use_data_ctrp_summ <- use_data_ctrp %>% count(InG2P)
  ctrp_lin_p_ttest <- data.frame(statistic = NA,
                                 parameter =  NA,
                                 p.value = NA)
  if(nrow(use_data_ctrp_summ) <= 1) {
    ctrp_lin_p_ttest_res <-  NA
    ticker <- ticker + 1
    }
  else if(use_data_ctrp_summ[use_data_ctrp_summ$InG2P == "Yes",]$nn < 2) { ctrp_lin_p_ttest_res <-  NA }
  else if(use_data_ctrp_summ[use_data_ctrp_summ$InG2P == "Yes",]$nn >= 2) {
    ctrp_lin_p_ttest <- t.test(use_data_ctrp$p ~ use_data_ctrp$InG2P)
    ctrp_lin_p_ttest_res <- paste0("t(", trunc(ctrp_lin_p_ttest$parameter), ") = ", round(ctrp_lin_p_ttest$statistic, 2), ", p = ", round(ctrp_lin_p_ttest$p.value, 3))
  }

  use_data_gdsc <- filter(use_data, Dataset == "GDSC")
  use_data_gdsc_summ <- use_data_gdsc %>% count(InG2P)
  gdsc_lin_p_ttest <- data.frame(statistic = NA,
                                 parameter =  NA,
                                 p.value = NA)
  if(nrow(use_data_gdsc_summ) <= 1) {
    gdsc_lin_p_ttest_res <-  NA
    ticker <- ticker + 1
    }
  else if(use_data_gdsc_summ[use_data_gdsc_summ$InG2P == "Yes",]$nn < 2) { gdsc_lin_p_ttest_res <-  NA }
  else if(use_data_gdsc_summ[use_data_gdsc_summ$InG2P == "Yes",]$nn >= 2) {
    gdsc_lin_p_ttest <- t.test(use_data_gdsc$p ~ use_data_gdsc$InG2P)
    gdsc_lin_p_ttest_res <- paste0("t(", trunc(gdsc_lin_p_ttest$parameter), ") = ", round(gdsc_lin_p_ttest$statistic, 2), ", p = ", round(gdsc_lin_p_ttest$p.value, 3))
  }

  y_value <- ifelse(ticker == 3, 10, max(use_data$n) + max(use_data$n) * 0.1)

  summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"),
                          Test_Results_p = c(ccle_lin_p_ttest_res, ctrp_lin_p_ttest_res, gdsc_lin_p_ttest_res),
                          t_statistic = c(round(ccle_lin_p_ttest$statistic, 3), round(ctrp_lin_p_ttest$statistic, 3), round(gdsc_lin_p_ttest$statistic, 3)),
                          df = c(trunc(ccle_lin_p_ttest$parameter), trunc(ctrp_lin_p_ttest$parameter), trunc(gdsc_lin_p_ttest$parameter)),
                          p_value = c(round(ccle_lin_p_ttest$p.value, 3), round(ctrp_lin_p_ttest$p.value, 3), round(gdsc_lin_p_ttest$p.value, 3)),
                          group_general_lineage_name = lineage_name)
  plot_point <- ggplot(data = use_data) +
    facet_wrap(~ Dataset, drop = FALSE) +
    coord_cartesian(xlim = c(0, 1), ylim = c(0, y_value)) +
    scale_x_continuous(breaks = seq(0, 1, by = 0.1), labels = seq(0, 1, by = 0.1)) +
    scale_y_continuous(breaks = pretty_breaks()) +
    geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = p, y = n), alpha = 0.5) +
    scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
    geom_text_repel(data = subset(use_data, InG2P == "Yes"), mapping = aes(x = p, y = n, label = Drug_Gene), size = 3, segment.size = 0.2, segment.color = "grey50") +
    geom_text(data = summ_text, mapping = aes(x = 0.5, y = y_value, label = Test_Results_p), nudge_y = 0.1) +
    labs(x = "Drug-gene association p-value between mutation groups", y = "Number of level A G2P associations") +
    theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
  plot_box <- ggplot(data = use_data) +
    facet_wrap(~ Dataset, drop = FALSE) +
    coord_cartesian(ylim = c(0, 1)) +
    scale_y_continuous(breaks = seq(0, 1, by = 0.1), labels = seq(0, 1, by = 0.1)) +
    geom_violin(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.5) +
    geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.75, width = 0.25) +
    scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
    coord_flip() +
    labs(x = "In G2P?", title = toupper(lineage_name)) +
    theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
  plot <- subplot(plot_box, plot_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(title = toupper(lineage_name), margin = list(t = 75, l = 75), xaxis5 = list(title = "Gene-drug association p-value between mutation groups"), yaxis = list(title = "Level A G2P\nassociation", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))

  plot_point <- ggplot_gtable(ggplot_build(plot_point))
  plot_box <- ggplot_gtable(ggplot_build(plot_box))
  p_maxWidth <-  grid::unit.pmax(plot_point$widths, plot_box$widths)
  plot_point$widths <- as.list(p_maxWidth)
  plot_box$widths <- as.list(p_maxWidth)

  mut_plot <- cowplot::plot_grid(plot_box,
                     plot_point,
                     nrow = 2,
                     rel_heights = c(1, 4))

  saveWidgetFix(widget = plot, file = paste0("./plots/manuscript/plotlys_mut_by_lineage_grid/", lineage_name, "_mut_plotly_grid.html"))
  ggsave(paste0("./plots/manuscript/pngs_mut_by_lineage_grid/", lineage_name, "_mut_plot_grid.png"), mut_plot, device = "png", dpi = 450, width = 12, height = 6, units =   "in")

  return(summ_text)
}
```

## Make lineage GE/CN plots

```{r}
PearsonPlotsByLineage <- function(lineage) {
  print(paste0("Lineage: ", toupper(lineage)))
  use_data <- filter(dgl_signif_pearson_g2p_grid, group_general_lineage_name == lineage)
  use_data$Dataset <- factor(use_data$Dataset, levels = c("CCLE", "CTRP", "GDSC"))
  use_data$Pearson_GE_Label <- paste0(round(use_data$Pearson_Pval_GE, 3), "\nDrug_Gene: ", use_data$Drug_Gene)
  use_data$Pearson_CN_Label <- paste0(round(use_data$Pearson_Pval_CN, 3), "\nDrug_Gene: ", use_data$Drug_Gene)
  ticker_ge <- 0
  ticker_cn <- 0
  ticker <- 0

  use_data_ccle <- filter(use_data, Dataset == "CCLE")
  use_data_ccle_ge_summ <- use_data_ccle[!is.na(use_data_ccle$Pearson_GE_Abs),] %>% count(InG2P)
  use_data_ccle_cn_summ <- use_data_ccle[!is.na(use_data_ccle$Pearson_CN_Abs),] %>% count(InG2P)
  ccle_ge_ttest <- data.frame(statistic = NA, parameter = NA, p.value = NA)
  ccle_cn_ttest <- data.frame(statistic = NA, parameter = NA, p.value = NA)
  if(nrow(use_data_ccle_ge_summ) <= 1) {
    ccle_ge_res <-  NA
    ticker_ge <- ticker_ge + 1
  }
  else if(use_data_ccle_ge_summ[use_data_ccle_ge_summ$InG2P == "Yes",]$nn < 2) {
    ccle_ge_res <-  NA
  }
  else if(use_data_ccle_ge_summ[use_data_ccle_ge_summ$InG2P == "Yes",]$nn >= 2) {
    ccle_ge_ttest <- t.test(use_data_ccle$Pearson_GE_Abs ~ use_data_ccle$InG2P)
    ccle_ge_res <- paste0("t(", trunc(ccle_ge_ttest$parameter), ") = ", round(ccle_ge_ttest$statistic, 2), ", p = ", round(ccle_ge_ttest$p.value, 3))
  }
  if(nrow(use_data_ccle_cn_summ) <= 1) {
    ccle_cn_res <-  NA
    ticker_cn <- ticker_cn + 1
  }
  else if(use_data_ccle_cn_summ[use_data_ccle_cn_summ$InG2P == "Yes",]$nn < 2) {
    ccle_cn_res <-  NA
  }
  else if(use_data_ccle_cn_summ[use_data_ccle_cn_summ$InG2P == "Yes",]$nn >= 2) {
    ccle_cn_ttest <- t.test(use_data_ccle$Pearson_CN_Abs ~ use_data_ccle$InG2P)
    ccle_cn_res <- paste0("t(", trunc(ccle_cn_ttest$parameter), ") = ", round(ccle_cn_ttest$statistic, 2), ", p = ", round(ccle_cn_ttest$p.value, 3))
  }
  print("CCLE testing: DONE")

  use_data_ctrp <- filter(use_data, Dataset == "CTRP")
  use_data_ctrp_ge_summ <- use_data_ctrp[!is.na(use_data_ctrp$Pearson_GE_Abs),] %>% count(InG2P)
  use_data_ctrp_cn_summ <- use_data_ctrp[!is.na(use_data_ctrp$Pearson_CN_Abs),] %>% count(InG2P)
  ctrp_ge_ttest <- data.frame(statistic = NA, parameter = NA, p.value = NA)
  ctrp_cn_ttest <- data.frame(statistic = NA, parameter = NA, p.value = NA)
  if(nrow(use_data_ctrp_ge_summ) <= 1) {
    ctrp_ge_res <-  NA
    ticker_ge <- ticker_ge + 1
  }
  else if(use_data_ctrp_ge_summ[use_data_ctrp_ge_summ$InG2P == "Yes",]$nn < 2) {
    ctrp_ge_res <-  NA
  }
  else if(use_data_ctrp_ge_summ[use_data_ctrp_ge_summ$InG2P == "Yes",]$nn >= 2) {
    ctrp_ge_ttest <- t.test(use_data_ctrp$Pearson_GE_Abs ~ use_data_ctrp$InG2P)
    ctrp_ge_res <- paste0("t(", trunc(ctrp_ge_ttest$parameter), ") = ", round(ctrp_ge_ttest$statistic, 2), ", p = ", round(ctrp_ge_ttest$p.value, 3))
  }
  if(nrow(use_data_ctrp_cn_summ) <= 1) {
    ctrp_cn_res <-  NA
    ticker_cn <- ticker_cn + 1
  }
  else if(use_data_ctrp_cn_summ[use_data_ctrp_cn_summ$InG2P == "Yes",]$nn < 2) {
    ctrp_cn_res <-  NA
  }
  else if(use_data_ctrp_cn_summ[use_data_ctrp_cn_summ$InG2P == "Yes",]$nn >= 2) {
    ctrp_cn_ttest <- t.test(use_data_ctrp$Pearson_CN_Abs ~ use_data_ctrp$InG2P)
    ctrp_cn_res <- paste0("t(", trunc(ctrp_cn_ttest$parameter), ") = ", round(ctrp_cn_ttest$statistic, 2), ", p = ", round(ctrp_cn_ttest$p.value, 3))
  }
  print("CTRP testing: DONE")

  use_data_gdsc <- filter(use_data, Dataset == "GDSC")
  use_data_gdsc_ge_summ <- use_data_gdsc[!is.na(use_data_gdsc$Pearson_GE_Abs),] %>% count(InG2P)
  use_data_gdsc_cn_summ <- use_data_gdsc[!is.na(use_data_gdsc$Pearson_CN_Abs),] %>% count(InG2P)
  gdsc_ge_ttest <- data.frame(statistic = NA, parameter = NA, p.value = NA)
  gdsc_cn_ttest <- data.frame(statistic = NA, parameter = NA, p.value = NA)
  if(nrow(use_data_gdsc_ge_summ) <= 1) {
    gdsc_ge_res <-  NA
    ticker_ge <- ticker_ge + 1
  }
  else if(use_data_gdsc_ge_summ[use_data_gdsc_ge_summ$InG2P == "Yes",]$nn < 2) {
    gdsc_ge_res <-  NA
  }
  else if(use_data_gdsc_ge_summ[use_data_gdsc_ge_summ$InG2P == "Yes",]$nn >= 2) {
    gdsc_ge_ttest <- t.test(use_data_gdsc$Pearson_GE_Abs ~ use_data_gdsc$InG2P)
    gdsc_ge_res <- paste0("t(", trunc(gdsc_ge_ttest$parameter), ") = ", round(gdsc_ge_ttest$statistic, 2), ", p = ", round(gdsc_ge_ttest$p.value, 3))
  }
  if(nrow(use_data_gdsc_cn_summ) <= 1) {
    gdsc_cn_res <-  NA
    ticker_cn <- ticker_cn + 1
  }
  else if(use_data_gdsc_cn_summ[use_data_gdsc_cn_summ$InG2P == "Yes",]$nn < 2) {
    gdsc_cn_res <-  NA
  }
  else if(use_data_gdsc_cn_summ[use_data_gdsc_cn_summ$InG2P == "Yes",]$nn >= 2) {
    gdsc_cn_ttest <- t.test(use_data_gdsc$Pearson_CN_Abs ~ use_data_gdsc$InG2P)
    gdsc_cn_res <- paste0("t(", trunc(gdsc_cn_ttest$parameter), ") = ", round(gdsc_cn_ttest$statistic, 2), ", p = ", round(gdsc_cn_ttest$p.value, 3))
  }
  print("GDSC testing: DONE")

  y_value_ge <- ifelse(ticker_ge == 3, 10, max(use_data$n) + max(use_data$n) * 0.1)
  y_value_cn <- ifelse(ticker_cn == 3, 10, max(use_data$n) + max(use_data$n) * 0.1)

  summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"),
                          Test_Results_GE = c(ccle_ge_res, ctrp_ge_res, gdsc_ge_res),
                          t_statistic_GE = c(round(ccle_ge_ttest$statistic, 3), round(ctrp_ge_ttest$statistic, 3), round(gdsc_ge_ttest$statistic, 3)),
                          df_GE = c(trunc(ccle_ge_ttest$parameter), trunc(ctrp_ge_ttest$parameter), trunc(gdsc_ge_ttest$parameter)),
                          p_value_GE = c(round(ccle_ge_ttest$p.value, 3), round(ctrp_ge_ttest$p.value, 3), round(gdsc_ge_ttest$p.value, 3)),
                          Test_Results_CN = c(ccle_cn_res, ctrp_cn_res, gdsc_cn_res),
                          t_statistic_CN = c(round(ccle_cn_ttest$statistic, 3), round(ctrp_cn_ttest$statistic, 3), round(gdsc_cn_ttest$statistic, 3)),
                          df_CN = c(trunc(ccle_cn_ttest$parameter), trunc(ctrp_cn_ttest$parameter), trunc(gdsc_cn_ttest$parameter)),
                          p_value_CN = c(round(ccle_cn_ttest$p.value, 3), round(ctrp_cn_ttest$p.value, 3), round(gdsc_cn_ttest$p.value, 3)),
                          group_general_lineage_name = lineage)

  ## Gene expression
  if(sum(!is.na(use_data$Pearson_GE_Abs)) > 0) {
    plot_ge_point <- ggplot(data = use_data) +
      facet_wrap(~ Dataset, drop = FALSE) +
      scale_y_continuous(breaks = pretty_breaks()) +
      geom_point(mapping = aes(label = Pearson_GE_Label, color = InG2P, fill = InG2P, shape = Pearson_GE_Sign, x = Pearson_GE_Abs, y = n), alpha = 0.5) +
      scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
      scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
      scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
      geom_text_repel(data = subset(use_data, InG2P == "Yes" & n > 10), aes(label = Drug_Gene, x = Pearson_GE_Abs, y = n), size = 3, segment.size = 0.2, segment.color = "grey50") +
      geom_text(data = summ_text, mapping = aes(x = 0.5, y = y_value_ge, label = Test_Results_GE), nudge_y = 1) +
      labs(y = "Number of level A G2P associations", x = "Pearson correlation coefficient between drug-gene AUC and gene expression") +
      theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
    plot_ge_box <- ggplot(data = use_data) +
      facet_wrap(~ Dataset, drop = FALSE) +
      geom_violin(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.5) +
      geom_boxplot(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
      scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
      coord_flip() +
      labs(x = "In G2P?", title = toupper(lineage)) +
      theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))

    plot_ge <- subplot(plot_ge_box, plot_ge_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>%
               layout(title = lineage, margin = list(t = 75, l = 75),
                      xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and gene expression"),
                      yaxis = list(title = "In G2P?", domain = c(0.8, 1)),
                      yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))

    png_ge_point <- ggplot_gtable(ggplot_build(plot_ge_point))
    png_ge_box <- ggplot_gtable(ggplot_build(plot_ge_box))
    p_maxWidth <-  grid::unit.pmax(png_ge_point$widths, png_ge_box$widths)
    png_ge_point$widths <- as.list(p_maxWidth)
    png_ge_box$widths <- as.list(p_maxWidth)

    png_ge <- cowplot::plot_grid(png_ge_box, png_ge_point, nrow = 2, rel_heights = c(1, 4))
    png_ge

    saveWidgetFix(widget = plot_ge, file = paste0("./plots/manuscript/plotlys_ge_by_lineage_grid/", lineage, "_ge_plotly_grid.html"))
    ggsave(paste0("./plots/manuscript/pngs_ge_by_lineage_grid/", lineage, "_ge_plot_grid.png"), png_ge, device = "png", dpi = 450, width = 12, height = 6, units = "in")
    print("Gene expression plots: DONE")
  }
  else if(sum(!is.na(use_data$Pearson_GE_Abs)) == 0) { print("Gene expression plots: None") }

  ## Copy number
  if(sum(!is.na(use_data$Pearson_CN_Abs)) > 0) {
    plot_cn_point <- ggplot(data = use_data) +
      facet_wrap(~ Dataset, drop = FALSE) +
      scale_y_continuous(breaks = pretty_breaks()) +
      geom_point(mapping = aes(label = Pearson_CN_Label, color = InG2P, fill = InG2P, shape = Pearson_CN_Sign, x = Pearson_CN_Abs, y = n), alpha = 0.5, position = position_jitter(width = 0, height = 0.15)) +
      scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
      scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
      scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
      geom_text_repel(data = subset(use_data, InG2P == "Yes"  & n > 10), aes(label = Drug_Gene, x = Pearson_CN_Abs, y = n), size = 3, segment.size = 0.2, segment.color = "grey50") +
      geom_text(data = summ_text, mapping = aes(x = 0.5, y = y_value_cn, label = Test_Results_CN), nudge_y = 1) +
      labs(y = "Number of level A G2P associations", x = "Pearson correlation coefficient between drug-gene AUC and copy number") +
      theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
    plot_cn_box <- ggplot(data = use_data) +
      facet_wrap(~ Dataset, drop = FALSE) +
      geom_violin(mapping = aes(color = InG2P, y = Pearson_CN_Abs, x = InG2P), alpha = 0.5) +
      geom_boxplot(mapping = aes(color = InG2P, y = Pearson_CN_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
      scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
      coord_flip() +
      labs(x = "In G2P?", title = toupper(lineage)) +
      theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))

    plot_cn <- subplot(plot_cn_box, plot_cn_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>%
               layout(title = lineage, margin = list(t = 75, l = 75),
                      xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and copy number"),
                      yaxis = list(title = "In G2P?", domain = c(0.8, 1)),
                      yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))

    png_cn_point <- ggplot_gtable(ggplot_build(plot_cn_point))
    png_cn_box <- ggplot_gtable(ggplot_build(plot_cn_box))
    p_maxWidth <-  grid::unit.pmax(png_cn_point$widths, png_cn_box$widths)
    png_cn_point$widths <- as.list(p_maxWidth)
    png_cn_box$widths <- as.list(p_maxWidth)

    png_cn <- cowplot::plot_grid(png_cn_box, png_cn_point, nrow = 2, rel_heights = c(1, 4))
    png_cn

    saveWidgetFix(widget = plot_cn, file = paste0("./plots/manuscript/plotlys_cn_by_lineage_grid/", lineage, "_cn_plotly_grid.html"))
    ggsave(paste0("./plots/manuscript/pngs_cn_by_lineage_grid/", lineage, "_cn_plot_grid.png"), png_cn, device = "png", dpi = 450, width = 12, height = 6, units = "in")
    print("Copy number plots: DONE")
  }
  else if(sum(!is.na(use_data$Pearson_CN_Abs)) == 0) { print("Copy number plots: None") }

  return(summ_text)
}
```

## Make per-drug boxplots
```{r}
makeDrugBoxplots <- function(drug, dataset) {
  if(dataset == "CCLE" | dataset == "ccle") {
    use_data <- filter(ccle_data_ptmuts, Drug == drug)
    use_color <- as.character(use_data$Color_Nonsilent)
    names(use_color) <- use_data$Mutation_Status_Nonsilent
    sig <- ccle_signif_g2p_ByDrug[[drug]]
    label_text <- data.frame(p.signif = sig$p.signif, p.signif.adj = sig$p.signif.adj, Hugo_Symbol = sig$Hugo_Symbol)
    label_text$Hugo_Symbol <- factor(label_text$Hugo_Symbol, levels = g2p_genes)
  }
  else if(dataset == "CTRP" | dataset == "ctrp") {
    use_data <- filter(ctrp_data_ptmuts, Drug == drug)
    use_color <- as.character(use_data$Color_Nonsilent)
    names(use_color) <- use_data$Mutation_Status_Nonsilent
    sig <- ctrp_signif_g2p_ByDrug[[drug]]
    label_text <- data.frame(p.signif = sig$p.signif, p.signif.adj = sig$p.signif.adj, Hugo_Symbol = sig$Hugo_Symbol)
    label_text$Hugo_Symbol <- factor(label_text$Hugo_Symbol, levels = g2p_genes)
  }
  else if(dataset == "GDSC" | dataset == "gdsc") {
    use_data <- filter(gdsc_data_ptmuts, Drug == drug)
    use_color <- as.character(use_data$Color_Nonsilent)
    names(use_color) <- use_data$Mutation_Status_Nonsilent
    sig <- gdsc_signif_g2p_ByDrug[[drug]]
    label_text <- data.frame(p.signif = sig$p.signif, p.signif.adj = sig$p.signif.adj, Hugo_Symbol = sig$Hugo_Symbol)
    label_text$Hugo_Symbol <- factor(label_text$Hugo_Symbol, levels = g2p_genes)
  }
  else { return("Error: Invalid dataset.") }

  plot <- ggplot(data = use_data, aes(x = Mutation_Status_Nonsilent, y = AUC)) +
    facet_wrap(~ Hugo_Symbol, drop = FALSE, nrow = 1) +
    geom_boxplot(mapping = aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85), outlier.shape = 3, outlier.size = 0.5) +
    scale_fill_manual(values = use_color) +
    guides(color = FALSE) +
    geom_text(data = label_text, mapping = aes(x = 1.5, y = max(use_data$AUC), label = p.signif), nudge_y = 0.2) +
    theme(strip.text.x = element_text(size = 10, angle = 45), legend.position = "top", axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
    labs(fill = "Mutation Status", y = "AUC", x = "Mutation Status", title = paste0(toupper(dataset), ": ", drug))
  return(plot)
}
```

# DATA MANAGEMENT {.tabset .tabset-fade .tabset-pills}

--------------------------------------------------------------------------------

## D. Charytonowicz cell line converter

This comprehensive cancer cell line information curated by Daniel Charytonowicz.
```{r}
ccl_converter <- read.delim("./data_munging/cell_line_database_v1_20180911.tsv", row.names = 1, sep = "\t", header = TRUE)
lineage_converter <- unique(ccl_converter[, c("grouped_general_doid", "group_general_lineage_name")])
colnames(ccl_converter)[colnames(ccl_converter) == "Broad_ID"] <- "DepMap_ID"
```

## DepMap cell line metadata

```{r}
ccl_info <- read.delim("./data_munging/18Q4/DepMap-2018q4-celllines_20181115.csv", sep = ",", header = TRUE, na.strings = c("", NA))
ccl_info$Primary.Disease <- gsub("\\\\", "", ccl_info$Primary.Disease)
ccl_info$Primary.Disease <- gsub("Ewings", "Ewing's", ccl_info$Primary.Disease)
# From figshare
crispr_meta <- read.delim("./data_munging/18Q4/sample_info_18Q4_crispr_20181115.csv", sep = ",", header = TRUE, na.strings = c("", NA))
colnames(crispr_meta)[7] <- "CCLE_Name"
```

## CCLE genomic annotations

### Mutation status (Mut)

For mutation calling, get paired gene name and cell line fields in a data frame. For this analysis, we don't care about how many mutations there are per gene or what type of mutations there are, so I didn't save more information. I took unique gene-cell line combinations since we only cared about mutation presence/absence. Add a `Mutation_Status` column denoting all entries in MAF files as mutations present in the associated cell lines.

Merged mutation calls (coding region, germline filtered):
```{r, eval=FALSE}
maf_raw <- read.delim("./data_munging/18Q4/depmap_18Q4_mutation_calls_20181114.csv.gz", header = TRUE, sep = ",", row.names = 1)
colnames(maf_raw)[colnames(maf_raw) == "Tumor_Sample_Barcode"] <- "CCLE_Name"
# Select columns
maf_df <- subset(maf_raw, select = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID", "Variant_Classification", "Reference_Allele", "Tumor_Seq_Allele1", "Genome_Change"))
maf_df$Reference_Allele_Length <- ifelse(maf_df$Reference_Allele == "-", 0, nchar(as.character(maf_df$Reference_Allele)))
maf_df$Tumor_Seq_Allele1_Length <- nchar(as.character(maf_df$Tumor_Seq_Allele1))
# Add Mutation_Status column
maf_df$Mutation_Status_Nonsilent <- ifelse(maf_df$Variant_Classification == "Silent", "Wildtype", "Mutant")
maf_df <- unique(maf_df)
saveRDS(maf_df, "./data_munging/rds/maf_df_18Q4.rds", compress = "xz")
```

### Copy number (CN)

DepMap WES CN Data:
```{r, eval=FALSE}
cn <- read.delim("./data_munging/18Q4/public_18Q4_gene_cn_20181115.csv.gz", sep = ",", check.names = FALSE, header = TRUE)
# Remove Entrez gene IDs from colnames
# Format: Hugo_Symbol (Entrez ID)
colnames(cn) <- gsub(" .*", "", colnames(cn))
# Melt
cn_melt <- melt(data = cn, id.vars = "DepMap_ID", measure.vars = colnames(cn[2:ncol(cn)]), variable.name = "Hugo_Symbol", value.name = "CN")
saveRDS(cn_melt, "./data_munging/rds/cn_melt_18Q4.rds", compress = "xz")
```

### Gene expression (GE)

18Q3, Gene expression data (Reads Per Kilobase of transcript, per Million mapped reads, RPKM).
```{r, eval=FALSE}
ge_18Q3 <- read.delim("./../htscreens_giant_files/CCLE_DepMap_18q3_RNAseq_RPKM_20180718.gct.gz", skip = 2, header = TRUE, sep = "\t", check.names = FALSE)
# Edit columns
ge_18Q3$Name <- NULL
colnames(ge_18Q3)[1] <- "Hugo_Symbol"
# Melt
ge_melt_18Q3 <- melt(data = ge_18Q3, id.vars = "Hugo_Symbol", measure.vars = colnames(ge_18Q3[2:ncol(ge_18Q3)]), value.name = "RPKM")
## Split variable column
ge_melt_18Q3 <- with(ge_melt_18Q3, cbind(Hugo_Symbol, colsplit(variable, pattern = " ", names = c("CCLE_Name", "DepMap_ID")), RPKM))
## Remove parentheses around Broad IDs
ge_melt_18Q3$DepMap_ID <- gsub("\\(|\\)", "", ge_melt_18Q3$DepMap_ID)
saveRDS(ge_melt_18Q3, "./../htscreens_giant_files/ge_melt_18Q3.rds", compress = "xz")
```

18Q4, CCLE RNAseq gene expression data (log2(TPM+1)):
```{r, eval=FALSE}
ge_18Q4 <- read.delim("./../htscreens_giant_files/CCLE_depMap_18Q4_TPM_v2_20181115.csv.gz", header = TRUE, sep = ",", check.names = FALSE)
# Remove Entrez gene IDs from colnames
# Format: Hugo_Symbol (Entrez ID)
colnames(ge_18Q4) <- gsub(" .*", "", colnames(ge_18Q4))
colnames(ge_18Q4)[1] <- "DepMap_ID"
# Melt
ge_melt_18Q4_all <- melt(ge_18Q4, id.vars = "DepMap_ID", measure.vars = colnames(ge_18Q4)[2:ncol(ge_18Q4)], variable.name = "Hugo_Symbol", value.name = "TPM")
ge_melt_18Q4 <- unique(ge_melt_18Q4)
saveRDS(ge_melt_18Q4, "./data_munging/rds/ge_melt_18Q4.rds", compress = "xz")
```

## G2P

```{r}
g2p <- read.delim("./data_munging/g2p_full_level_A_dataset_NEW_DEC_2_2018_withGroupedLineages.csv", sep = "\t", header = TRUE)
g2p[, 1:2] <- NULL
g2p <- merge(g2p, lineage_converter, by = "grouped_general_doid", all.x = TRUE)

g2p$Drug <- tolower(g2p$Drug)
g2p[g2p == -1] <- NA
g2p$Ref[g2p$Ref == "None"] <- NA
g2p$Alt[g2p$Alt == "None"] <- NA
g2p$Drug_Gene <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene), NA, paste0(g2p$Drug, "_", g2p$Gene))
g2p$Drug_Gene_Lin <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene) | is.na(g2p$group_general_lineage_name), NA, paste0(g2p$Drug, "_", g2p$Gene, "_", g2p$group_general_lineage_name))
g2p$position <- paste0("g.chr", g2p$Chromosome, ":", g2p$End, g2p$Ref, ">", g2p$Alt)
g2p$position <- ifelse(grepl("NA", g2p$position), NA, g2p$position)
g2p_filt <- subset(g2p, grepl("^CID", g2p$DrugID))

g2p_dgls <-  unique(g2p_filt$Drug_Gene_Lin[!is.na(g2p_filt$Drug_Gene_Lin)])
g2p_druggenes <- unique(g2p_filt$Drug_Gene[!is.na(g2p_filt$Drug_Gene)])
g2p_genes <- unique(sapply(strsplit(g2p_druggenes, "_", fixed = TRUE), function(x) x[2]))
g2p_drugs <- unique(sapply(strsplit(g2p_druggenes, "_", fixed = TRUE), function(x) x[1]))
g2p_druggenes
g2p_genes
g2p_drugs
# Order and genes taken from pink heatmapo from Daniel's analyses
g2p_genes <- c("EGFR", "KRAS", "ERBB2", "ERBB3", "MET", "ALK", "ROS1", "PDGFRA", "ABL1", "KIT", "PDGFRB", "PDGFB", "BRAF", "G6PD", "RET", "BRCA1", "BRCA2", "UGT1A1", "TSC1", "TSC2", "AKT1", "IDH2", "DPYD", "ESR1", "CYP19A1", "TPMT", "FLT3", "NPM1", "DNMT3A", "PML", "PTCH1", "JAK2", "MYD88", "MGMT")
```

```{r}
# levels(g2p_filt$Phenotype.Description)
unique(g2p_filt$group_general_lineage_name)
levels(g2p_filt$group_general_lineage_name)

g2p_nonCID <- subset(g2p, !grepl("^CID", g2p$DrugID))
summ <- g2p_nonCID %>% group_by(Drug, DrugID) %>% tally() %>% summarize(DrugID = DrugID, n = n, percent = formatC(n / 402 * 100, digits = 6, format = "f"))
summ
```

```{r, eval=FALSE}
maf_df <- readRDS("./data_munging/rds/maf_df_18Q4.rds")
cn_melt <- readRDS("./data_munging/rds/cn_melt_18Q4.rds")
ge_melt_18Q3 <- readRDS("./../htscreens_giant_files/ge_melt_18Q3.rds")
# ge_melt_18Q4 <- readRDS("./data_munging/rds/ge_melt_18Q4.rds")

# maf_filt_dan <- filter(maf_df, Hugo_Symbol %in% g2p_genes)
# write.table(maf_filt_dan, file = "~/Desktop/maf_filt_dan_18Q4_2018112.csv", quote = FALSE, sep = ",", row.names = FALSE)
```

## Drug screens

### Merge drug data and annotations

```{r, eval=FALSE}
# Drug metadata
drug_meta <- read.delim("./data_munging/drug_id_drug_name_table_10_12_2018.tsv", sep = "\t", header = FALSE)
colnames(drug_meta) <- c("CID", "Drug")
drug_meta$Drug <- tolower(drug_meta$Drug)
maf_df_g2p <- filter(maf_df, Hugo_Symbol %in% g2p_genes)
ge_filt_18Q3 <- filter(ge_melt_18Q3, Hugo_Symbol %in% g2p_genes)
# ge_filt_18Q4 <- filter(ge_melt_18Q4, Hugo_Symbol %in% g2p_genes)
cn_filt <- filter(cn_melt, Hugo_Symbol %in% g2p_genes)

# CCLE
ccle <- read.delim("./data_munging/data_drug_auc_ccle_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
ccle <- merge(drug_meta, ccle, by = "CID")
ccle_melt <- melt(ccle, id.vars = c("CID", "Drug"), measure.vars = colnames(ccle)[3:ncol(ccle)], variable.name = "accession_id", value.name = "ActArea")
ccle_grid <- expand.grid("accession_id" = unique(ccle_melt$accession_id), "Hugo_Symbol" = g2p_genes)
ccle_data <- merge(ccle_grid, ccle_melt, by = "accession_id", all.x = TRUE)
ccle_data <- merge(ccle_data, ccl_converter, by = "accession_id", all.x = TRUE)
ccle_data <- merge(ccle_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
ccle_data$Mutation_Status_Nonsilent <- ifelse(is.na(ccle_data$Mutation_Status_Nonsilent), "Wildtype", ccle_data$Mutation_Status_Nonsilent)
ccle_data <- merge(ccle_data, ge_filt_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
# ccle_data <- merge(ccle_data, ge_filt_18Q4, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
ccle_data <- merge(ccle_data, cn_filt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
ccle_data$Hugo_Symbol <- factor(ccle_data$Hugo_Symbol)
ccle_data$ActArea <- as.numeric(ccle_data$ActArea)
# CCLE AUC is actually AOC
# assuming scale is 0-8, transform to range between 0 and 1
# get AUC by 1 - AOC
ccle_data$AUC <- 1 - (ccle_data$ActArea / 8)
ccle_data <- filter(ccle_data, !is.na(ccle_data$AUC))
ccle_data$AUC_zscore <- (ccle_data$AUC - mean(ccle_data$AUC)) / sd(ccle_data$AUC)
ccle_data$Color_Nonsilent <- ifelse(ccle_data$Mutation_Status_Nonsilent == "Wildtype", "palegreen3", "springgreen4")
ccle_data$Color_Nonsilent <- factor(ccle_data$Color_Nonsilent)
ccle_data$Drug_Gene <- paste0(ccle_data$Drug, "_", ccle_data$Hugo_Symbol)
ccle_data$Drug_Gene_Lin <- paste0(ccle_data$Drug, "_", ccle_data$Hugo_Symbol, "_", ccle_data$group_general_lineage_name)
saveRDS(ccle_data, "./data_munging/rds/ccle_data_18Q4_g2pgenes.rds", compress = "xz")

# CTRP
ctrp <- read.delim("./data_munging/data_drug_auc_ctrp_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
ctrp <- merge(drug_meta, ctrp, by = "CID")
ctrp_melt <- melt(ctrp, id.vars = c("CID", "Drug"), measure.vars = colnames(ctrp)[3:ncol(ctrp)], variable.name = "accession_id", value.name = "AUC")
ctrp_grid <- expand.grid("accession_id" = unique(ctrp_melt$accession_id), "Hugo_Symbol" = g2p_genes)
ctrp_data <- merge(ctrp_grid, ctrp_melt, by = "accession_id", all.x = TRUE)
ctrp_data <- merge(ctrp_data, ccl_converter, by = "accession_id", all.x = TRUE)
ctrp_data <- merge(ctrp_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
ctrp_data$Mutation_Status_Nonsilent <- ifelse(is.na(ctrp_data$Mutation_Status_Nonsilent), "Wildtype", ctrp_data$Mutation_Status_Nonsilent)
ctrp_data <- merge(ctrp_data, ge_filt_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
# ctrp_data <- merge(ctrp_data, ge_filt_18Q4, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
ctrp_data <- merge(ctrp_data, cn_filt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
ctrp_data$Hugo_Symbol <- factor(ctrp_data$Hugo_Symbol)
ctrp_data$AUC <- as.numeric(ctrp_data$AUC)
ctrp_data <- filter(ctrp_data, !is.na(ctrp_data$AUC))
ctrp_data$AUC_zscore <- (ctrp_data$AUC - mean(ctrp_data$AUC)) / sd(ctrp_data$AUC)
ctrp_data$Color_Nonsilent <- ifelse(ctrp_data$Mutation_Status_Nonsilent == "Wildtype", "slategray3", "steelblue4")
ctrp_data$Color_Nonsilent <- factor(ctrp_data$Color_Nonsilent)
ctrp_data$Drug_Gene <- paste0(ctrp_data$Drug, "_", ctrp_data$Hugo_Symbol)
ctrp_data$Drug_Gene_Lin <- paste0(ctrp_data$Drug, "_", ctrp_data$Hugo_Symbol, "_", ctrp_data$group_general_lineage_name)
saveRDS(ctrp_data, "./data_munging/rds/ctrp_data_18Q4_g2pgenes.rds", compress = "xz")

# GDSC
gdsc <- read.delim("./data_munging/data_drug_auc_gdsc_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
gdsc <- merge(drug_meta, gdsc, by = "CID")
gdsc_melt <- melt(gdsc, id.vars = c("CID", "Drug"), measure.vars = colnames(gdsc)[3:ncol(gdsc)], variable.name = "accession_id", value.name = "AUC")
gdsc_grid <- expand.grid("accession_id" = unique(gdsc_melt$accession_id), "Hugo_Symbol" = g2p_genes)
gdsc_data <- merge(gdsc_grid, gdsc_melt, by = "accession_id", all.x = TRUE)
gdsc_data <- merge(gdsc_data, ccl_converter, by = "accession_id", all.x = TRUE)
gdsc_data <- merge(gdsc_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
gdsc_data$Mutation_Status_Nonsilent <- ifelse(is.na(gdsc_data$Mutation_Status_Nonsilent), "Wildtype", gdsc_data$Mutation_Status_Nonsilent)
gdsc_data <- merge(gdsc_data, ge_filt_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
# gdsc_data <- merge(gdsc_data, ge_filt_18Q4, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
gdsc_data <- merge(gdsc_data, cn_filt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
gdsc_data$Hugo_Symbol <- factor(gdsc_data$Hugo_Symbol)
gdsc_data$AUC <- as.numeric(gdsc_data$AUC)
gdsc_data <- filter(gdsc_data, !is.na(gdsc_data$AUC))
gdsc_data$AUC_zscore <- (gdsc_data$AUC - mean(gdsc_data$AUC)) / sd(gdsc_data$AUC)
gdsc_data$Color_Nonsilent <- ifelse(gdsc_data$Mutation_Status_Nonsilent == "Wildtype", "paleturquoise3", "turquoise4")
gdsc_data$Color_Nonsilent <- factor(gdsc_data$Color_Nonsilent)
gdsc_data$Drug_Gene <- paste0(gdsc_data$Drug, "_", gdsc_data$Hugo_Symbol)
gdsc_data$Drug_Gene_Lin <- paste0(gdsc_data$Drug, "_", gdsc_data$Hugo_Symbol, "_", gdsc_data$group_general_lineage_name)
saveRDS(gdsc_data, "./data_munging/rds/gdsc_data_18Q4_g2pgenes.rds", compress = "xz")
```

### Filter drug data

```{r}
ccle_data <- readRDS("./data_munging/rds/ccle_data_18Q4_g2pgenes.rds")
ccle_data_ptmuts <- filter(ccle_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
ccle_data_ptmuts$Keep_PtMut_Tests <- ifelse(ccle_data_ptmuts$Reference_Allele_Length == 1 | is.na(ccle_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(ccle_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
ccle_data_ptmuts <- filter(ccle_data_ptmuts, Keep_PtMut_Tests == TRUE)
ccle_data_ptmuts$Dataset <- "CCLE"
ccle_data_ptmuts$Hugo_Symbol <- ordered(ccle_data_ptmuts$Hugo_Symbol, levels = g2p_genes)

ctrp_data <- readRDS("./data_munging/rds/ctrp_data_18Q4_g2pgenes.rds")
ctrp_data_ptmuts <- filter(ctrp_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
ctrp_data_ptmuts$Keep_PtMut_Tests <- ifelse(ctrp_data_ptmuts$Reference_Allele_Length == 1 | is.na(ctrp_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(ctrp_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
ctrp_data_ptmuts <- filter(ctrp_data_ptmuts, Keep_PtMut_Tests == TRUE)
ctrp_data_ptmuts$Dataset <- "CTRP"
ctrp_data_ptmuts$Hugo_Symbol <- ordered(ctrp_data_ptmuts$Hugo_Symbol, levels = g2p_genes)

gdsc_data <- readRDS("./data_munging/rds/gdsc_data_18Q4_g2pgenes.rds")
gdsc_data_ptmuts <- filter(gdsc_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
gdsc_data_ptmuts$Keep_PtMut_Tests <- ifelse(gdsc_data_ptmuts$Reference_Allele_Length == 1 | is.na(gdsc_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(gdsc_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
gdsc_data_ptmuts <- filter(gdsc_data_ptmuts, Keep_PtMut_Tests == TRUE)
gdsc_data_ptmuts$Dataset <- "GDSC"
gdsc_data_ptmuts$Hugo_Symbol <- ordered(gdsc_data_ptmuts$Hugo_Symbol, levels = g2p_genes)

# Filter drug screen datasets for G2P drug-gene associations
ccle_data_g2p <- filter(ccle_data_ptmuts, Drug_Gene %in% g2p_druggenes)
ccle_data_g2p$Mutation_Status_Nonsilent <- factor(ccle_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
ctrp_data_g2p <- filter(ctrp_data_ptmuts, Drug_Gene %in% g2p_druggenes)
ctrp_data_g2p$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
gdsc_data_g2p <- filter(gdsc_data_ptmuts, Drug_Gene %in% g2p_druggenes)
gdsc_data_g2p$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))

# Filter drug screen datasets for G2P drug-gene-lineage associations
ccle_data_g2p_dgl <- filter(ccle_data_ptmuts, Drug_Gene_Lin %in% g2p_dgls)
ccle_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(ccle_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
ctrp_data_g2p_dgl <- filter(ctrp_data_ptmuts, Drug_Gene_Lin %in% g2p_dgls)
ctrp_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
gdsc_data_g2p_dgl <- filter(gdsc_data_ptmuts, Drug_Gene_Lin %in% g2p_dgls)
gdsc_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))

# Filter drug screen datasets for G2P drugs and genes
ccle_data_g2p_grid <- filter(ccle_data_ptmuts, Drug %in% g2p_drugs)
ccle_data_g2p_grid$Mutation_Status_Nonsilent <- factor(ccle_data_g2p_grid$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
ctrp_data_g2p_grid <- filter(ctrp_data_ptmuts, Drug %in% g2p_drugs)
ctrp_data_g2p_grid$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p_grid$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
gdsc_data_g2p_grid <- filter(gdsc_data_ptmuts, Drug %in% g2p_drugs)
gdsc_data_g2p_grid$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p_grid$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
```

```{r}
test_ccle <- ccle_data_ptmuts %>% group_by(Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()
test_ctrp <- ctrp_data_ptmuts %>% group_by(Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()
test_gdsc <- gdsc_data_ptmuts %>% group_by(Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()
```

## CRISPR

### DepMap dependency probabilities

```{r, eval=FALSE}
dep <- read.delim("./data_munging/18Q4/gene_dependency_18Q4_20181115.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
# Remove Entrez gene IDs from colnames
colnames(dep) <- gsub(" .*", "", colnames(dep))
```

### Merge CRISPR data and annotations

The latest CRISPR CERES score data (18Q3, August 2018) was pulled from the [DepMap Data Portal](https://depmap.org/portal/download/) (Broad Institute Cancer Dependency Map 2018, Meyers et al. 2017).
```{r, eval=FALSE}
crispr <- read.delim("./data_munging/18Q4/gene_effect_18Q4_20181115.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
# Remove Entrez gene IDs from colnames
colnames(crispr) <- gsub(" .*", "", colnames(crispr))
```

Merge annotation data:
```{r, eval=FALSE}
# Melt CRISPR dataset for merging
crispr_melt <- melt(crispr, id.vars = "DepMap_ID", measure.vars = colnames(crispr)[2:ncol(crispr)], variable.name = "Hugo_Symbol", value.name = "Score")
# Melt dependency probabilities dataset for merging
dep_melt <- melt(dep, id.vars = "DepMap_ID", measure.vars = colnames(dep)[2:ncol(dep)], variable.name = "Hugo_Symbol", value.name = "Dep_Prob")
# Merge dependency probabilities
crispr_melt <- merge(crispr_melt, dep_melt, by = c("DepMap_ID", "Hugo_Symbol"), all.x = TRUE)
# Merge cell line metadata
crispr_melt <- merge(crispr_melt, ccl_info, by = "DepMap_ID", all.x = TRUE)
crispr_melt <- merge(crispr_melt, crispr_meta, by = c("CCLE_Name", "DepMap_ID"), all.x = TRUE)

# Merge mutation annotations
maf_filt_crispr <- filter(maf_df, Hugo_Symbol %in% as.character(unique(crispr_melt$Hugo_Symbol)))
crispr_muts <- merge(crispr_melt, maf_filt_crispr, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
crispr_muts$Hugo_Symbol <- factor(crispr_muts$Hugo_Symbol)
crispr_muts <- crispr_muts %>% mutate(Mutation_Status_Nonsilent = if_else(is.na(Mutation_Status_Nonsilent), "Wildtype", Mutation_Status_Nonsilent))
# Summarize number of mutant and Wildtype cell lines
crispr_muts_summ <- crispr_muts %>% group_by(Hugo_Symbol) %>%
  summarize(N_Nonsilent_Wildtype = sum(Mutation_Status_Nonsilent == "Wildtype"),
            N_Nonsilent_Mutant = sum(Mutation_Status_Nonsilent == "Mutant"))
# Merge test results back into full dataset, which restores information lost in the summarization
crispr_data <- merge(crispr_muts_summ, crispr_muts, by = "Hugo_Symbol")
# Add Color columns
crispr_data$Color_Nonsilent <- ifelse(crispr_data$Mutation_Status_Nonsilent == "Wildtype", "thistle", "darkorchid")
crispr_data$Color_Nonsilent <- factor(crispr_data$Color_Nonsilent)

# Cell line lineages
crispr_data <- merge(crispr_data, ccl_converter, by = c("CCLE_Name", "DepMap_ID"), all.x = TRUE)
levels(crispr_data$lineage_name) <- sort(levels(crispr_data$lineage_name), decreasing = TRUE)
# Copy number
crispr_data <- merge(crispr_data, cn_melt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
# Gene expression (RPKM)
ge_crispr_18Q3 <- filter(ge_melt_18Q3, Hugo_Symbol %in% as.character(unique(crispr_melt$Hugo_Symbol)))
# ge_crispr_18Q4 <- filter(ge_melt_18Q4, Hugo_Symbol %in% as.character(unique(crispr_melt$Hugo_Symbol)))
crispr_data <- merge(crispr_data, ge_crispr_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
# crispr_data <- merge(crispr_data, ge_crispr_18Q4, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
saveRDS(crispr_data, "./../htscreens_giant_files/crispr_data_18Q4.rds", compress = "xz")
```

```{r}
crispr_data <- readRDS("./../htscreens_giant_files/crispr_data_18Q4.rds")
crispr_data_ptmuts <- filter(crispr_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
crispr_data_ptmuts$Keep_PtMut_Tests <- ifelse(crispr_data_ptmuts$Reference_Allele_Length == 1 | is.na(crispr_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(crispr_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
crispr_data_ptmuts <- filter(crispr_data_ptmuts, Keep_PtMut_Tests == TRUE)

# Filter CRISPR for G2P genes in G2P
crispr_data_g2p <- filter(crispr_data_ptmuts, Hugo_Symbol %in% g2p_genes)
crispr_data_g2p$Hugo_Symbol <- factor(crispr_data_g2p$Hugo_Symbol, levels = g2p_genes)
crispr_data_g2p$Mutation_Status_Nonsilent <- factor(crispr_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
```

# WILCOXON TESTS

--------------------------------------------------------------------------------

Wilcoxon tests for assessing effect of mutation status on gene essentiality scores (CRISPR) and AUC (CCLE, CTRP, and GDSC).

## CRISPR

Test G2P genes in lineage-agnostic context:
```{r, eval=FALSE}
crispr_signif_g2p_gene <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol"), data = crispr_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
crispr_signif_g2p_gene <- adj_signif(crispr_signif_g2p_gene)
crispr_signif_g2p_gene <- crispr_signif_g2p_gene[order(crispr_signif_g2p_gene$p),]
saveRDS(crispr_signif_g2p_gene, "./data_munging/rds/crispr_signif_g2p_gene.rds")
```

```{r}
crispr_signif_g2p_gene <- readRDS("./data_munging/rds/crispr_signif_g2p_gene.rds")
crispr_signif_g2p_gene <- rbind(crispr_signif_g2p_gene, c("G6PD", rep(NA, 11)))
knitr::kable(crispr_signif_g2p_gene[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results for Level A point mutations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

Plot results of `crispr_signif_g2p_gene` tests:
```{r fig.height=7, fig.width=12}
crispr_data_signif_g2p_gene_filt <- filter(crispr_data_ptmuts, Hugo_Symbol %in% as.character(crispr_signif_g2p_gene$Hugo_Symbol))
crispr_data_signif_g2p_gene <- merge(crispr_data_signif_g2p_gene_filt, crispr_signif_g2p_gene, by = "Hugo_Symbol")
crispr_data_signif_g2p_gene$Hugo_Symbol <- ordered(crispr_data_signif_g2p_gene$Hugo_Symbol, levels = as.character(crispr_signif_g2p_gene$Hugo_Symbol))

crispr_data_signif_g2p_gene <- merge(crispr_data_signif_g2p_gene, crispr_data_signif_g2p_gene %>% group_by(Hugo_Symbol) %>% summarize(Text_y = max(Score)), by = "Hugo_Symbol")
crispr_data_signif_g2p_gene_text <- unique(data.frame(p.signif = crispr_data_signif_g2p_gene$p.signif, p.signif.adj = crispr_data_signif_g2p_gene$p.signif.adj,  Hugo_Symbol = crispr_data_signif_g2p_gene$Hugo_Symbol, Text_y = crispr_data_signif_g2p_gene$Text_y))

crispr_data_signif_g2p_gene_plot <- ggplot(data = crispr_data_signif_g2p_gene, aes(x = Mutation_Status_Nonsilent, y = Score)) +
  facet_wrap(~ Hugo_Symbol, drop = FALSE, nrow = 2, scales = "free_y") +
  geom_jitter(aes(color = Mutation_Status_Nonsilent), alpha = 0.5, width = 0.3) +
  geom_boxplot(color = "black", fill = NA, outlier.shape = NA) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  scale_color_manual(values = c("Mutant" = "darkorchid", "Wildtype" = "thistle")) +
  geom_text(data = crispr_data_signif_g2p_gene_text, mapping = aes(x = 1.5, y = Text_y, label = p.signif), nudge_y = 0.2) +
  theme(legend.position = "top", axis.text.x = element_blank(), axis.ticks.x = element_blank(), axis.title.x = element_blank()) +
  labs(y = "CERES Score",
       color = "Mutation Status",
       title = "CERES scores for select Level A G2P genes",
       subtitle = "Genes are sorted by increasing p-value.")
crispr_data_signif_g2p_gene_plot

# ggsave("./plots/manuscript/crispr_data_signif_g2p_gene_plot.png", crispr_data_signif_g2p_gene_plot, width = 12, height = 7, units = "in")
```

Test G2P genes in lineage-grouped context:
```{r, eval=FALSE}
crispr_signif_g2p_lineage <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "group_general_lineage_name"), data = crispr_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
crispr_signif_g2p_lineage <- adj_signif(crispr_signif_g2p_lineage)
crispr_signif_g2p_lineage <- crispr_signif_g2p_lineage[order(crispr_signif_g2p_lineage$p),]
saveRDS(crispr_signif_g2p_lineage, "./data_munging/rds/crispr_signif_g2p_lineage.rds")
# write.table(crispr_signif_g2p_lineage, file = "~/Desktop/crispr_signif_g2p_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
```

```{r}
crispr_signif_g2p_lineage <- readRDS("./data_munging/rds/crispr_signif_g2p_lineage.rds")
knitr::kable(filter(crispr_signif_g2p_lineage, p < 0.1)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant vs wildtype cell lines by lineage, p < 0.1 (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

Plot results of `crispr_signif_g2p_lineage` tests:
```{r fig.height=18, fig.width=15, eval=TRUE}
crispr_data_signif_g2p_lineage <- merge(crispr_data_signif_g2p_gene_filt, crispr_signif_g2p_lineage, by = c("Hugo_Symbol", "group_general_lineage_name"))
crispr_data_signif_g2p_lineage$Hugo_Symbol <- ordered(crispr_data_signif_g2p_lineage$Hugo_Symbol, levels = as.character(unique((crispr_signif_g2p_lineage$Hugo_Symbol))))

crispr_data_signif_g2p_lineage <- merge(crispr_data_signif_g2p_lineage, crispr_data_signif_g2p_lineage %>% group_by(Hugo_Symbol) %>% summarize(Text_y = max(Score)), by = "Hugo_Symbol")

crispr_data_signif_g2p_lineage_text <- unique(data.frame(p.signif = crispr_data_signif_g2p_lineage$p.signif, p.signif.adj = crispr_data_signif_g2p_lineage$p.signif.adj,  group_general_lineage_name = crispr_data_signif_g2p_lineage$group_general_lineage_name, Hugo_Symbol = crispr_data_signif_g2p_lineage$Hugo_Symbol, Text_y = crispr_data_signif_g2p_lineage$Text_y))

crispr_data_signif_g2p_lineage_plot <- ggplot(data = crispr_data_signif_g2p_lineage, aes(x = group_general_lineage_name, y = Score)) +
  facet_wrap(~ Hugo_Symbol, drop = FALSE, nrow = 6, scales = "free_y") +
  geom_point(aes(color = Mutation_Status_Nonsilent), alpha = 0.5) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  scale_color_manual(values = c("Mutant" = "darkorchid", "Wildtype" = "thistle")) +
  geom_text(data = crispr_data_signif_g2p_lineage_text, mapping = aes(x = group_general_lineage_name, y = Text_y, label = p.signif), angle = 90, vjust = 0.8, nudge_y = 0.1) +
  theme(legend.position = "top", axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 10)) +
  labs(y = "CERES Score",
       x = "Lineage",
       color = "Mutation Status",
       title = "CERES score by cell line lineage for significant Level A G2P genes",
       subtitle = "* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001\nGenes are sorted by increasing lineage-agnostic p-value.")
crispr_data_signif_g2p_lineage_plot

# write.table(crispr_data_signif_g2p_lineage, file = "~/Desktop/crispr_data_signif_g2p_lineage_20181213.tsv", quote = FALSE, sep = "\t")
# ggsave("./plots/manuscript/crispr_data_signif_g2p_lineage_plot.png", crispr_data_signif_g2p_lineage_plot, width = 15, height = 18, units = "in")
```

Count mutant/wildtype calls in each gene-lineage group:
```{r}
crispr_data_signif_g2p_lineage_summ <- crispr_data_signif_g2p_lineage %>% group_by(Hugo_Symbol, group_general_lineage_name, Mutation_Status_Nonsilent) %>% tally()

# write.table(crispr_data_signif_g2p_lineage_summ, file = "~/Desktop/crispr_data_signif_g2p_lineage_summ_20181005.tsv", quote = FALSE, sep = "\t")

knitr::kable(crispr_data_signif_g2p_lineage_summ, caption = "Mutant/Wildtype counts for gene-lineage combinations") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

## CCLE

Drug metadata:
```{r}
drug_meta <- read.delim("./data_munging/drug_id_drug_name_table_10_12_2018.tsv", sep = "\t", header = FALSE)
colnames(drug_meta) <- c("CID", "Drug")
drug_meta$Drug <- tolower(drug_meta$Drug)
```

Test all CRISPR genes in lineage-agnostic context:
```{r, eval=FALSE}
ccle <- read.delim("./data_munging/data_drug_auc_ccle_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
ccle <- merge(drug_meta, ccle, by = "CID")
ccle_melt <- melt(ccle, id.vars = c("CID", "Drug"), measure.vars = colnames(ccle)[3:ncol(ccle)], variable.name = "accession_id", value.name = "AUC")
ccle_grid <- expand.grid("accession_id" = unique(ccle_melt$accession_id), "Hugo_Symbol" = as.character(unique(crispr_data$Hugo_Symbol)))
system.time({ ccle_data_allgenes <- WilcoxonByDrugAllGenes(ccle_melt, ccle_grid, "CCLE") })
saveRDS(ccle_data_allgenes, "./data_munging/rds/ccle_data_18Q3_allgenes.rds", compress = "xz")

# user   system  elapsed 
# 1483.399  262.649 1901.698 
```

```{r}
ccle_data_allgenes <- readRDS("./data_munging/rds/ccle_data_18Q3_allgenes.rds")
ccle_data_allgenes <- ccle_data_allgenes[order(ccle_data_allgenes$p),]
knitr::kable(ccle_data_allgenes[1:1000, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: by-drug Wilcoxon test results for point mutations in genes targeted in CRISPR screen (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

Test G2P genes in lineage-agnostic context:
```{r, eval=FALSE}
# G2P drug-gene associations only
ccle_signif_g2p <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene", data = ccle_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
ccle_signif_g2p <- adj_signif(ccle_signif_g2p)
ccle_signif_g2p <- ccle_signif_g2p[order(ccle_signif_g2p$p),]
saveRDS(ccle_signif_g2p, "./data_munging/rds/ccle_signif_g2p_gene.rds")

# Grid comparisons of G2P drugs and genes
ccle_signif_g2p_grid <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = c("Drug_Gene"), data = ccle_data_g2p_grid, method = "wilcox.test", p.adjust.method = "BH")
ccle_signif_g2p_grid <- adj_signif(ccle_signif_g2p_grid)
ccle_signif_g2p_grid <- ccle_signif_g2p_grid[order(ccle_signif_g2p_grid$p),]
saveRDS(ccle_signif_g2p_grid, "./data_munging/rds/ccle_signif_g2p_grid.rds")
```

```{r}
ccle_signif_g2p <- readRDS("./data_munging/rds/ccle_signif_g2p_gene.rds")
knitr::kable(ccle_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")

ccle_signif_g2p_grid <- readRDS("./data_munging/rds/ccle_signif_g2p_grid.rds")
knitr::kable(ccle_signif_g2p_grid[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

Test G2P genes in lineage-grouped context:
```{r, eval=FALSE}
ccle_signif_grid_lineage <- lapply(unique(ccle_data_g2p_grid$Drug), WilcoxonByDrug, dataset = ccle_data_g2p_grid, data_name = "ccle", grouping_var = "lineage")
names(ccle_signif_grid_lineage) <- unique(ccle_signif_grid_lineage$Drug)
ccle_signif_grid_lineage <- rbindlist(ccle_signif_grid_lineage, use.names = TRUE)
ccle_signif_grid_lineage <- ccle_signif_grid_lineage[order(ccle_signif_grid_lineage$p),]
saveRDS(ccle_signif_grid_lineage, "./data_munging/rds/ccle_signif_grid_lineage.rds")

ccle_signif_g2p_lineage <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene_Lin", data = ccle_data_g2p_dgl, method = "wilcox.test", p.adjust.method = "BH")
ccle_signif_g2p_lineage <- adj_signif(ccle_signif_g2p_lineage)
ccle_signif_g2p_lineage <- ccle_signif_g2p_lineage[order(ccle_signif_g2p_lineage$p),]
saveRDS(ccle_signif_g2p_lineage, "./data_munging/rds/ccle_signif_g2p_lineage.rds")
```

```{r}
ccle_signif_g2p_lineage <- readRDS("./data_munging/rds/ccle_signif_g2p_lineage.rds")
ccle_signif_grid_lineage <- readRDS("./data_munging/rds/ccle_signif_grid_lineage.rds")

knitr::kable(ccle_signif_g2p_lineage[, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")

knitr::kable(ccle_signif_grid_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

## CTRP

Test all CRISPR genes in lineage-agnostic context:
```{r, eval=FALSE}
ctrp <- read.delim("./data_munging/data_drug_auc_ctrp_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
ctrp <- merge(drug_meta, ctrp, by = "CID")
ctrp_melt <- melt(ctrp, id.var  s = c("CID", "Drug"), measure.vars = colnames(ctrp)[3:ncol(ctrp)], variable.name = "accession_id", value.name = "AUC")
ctrp_grid <- expand.grid("accession_id" = unique(ctrp_melt$accession_id), "Hugo_Symbol" = as.character(unique(crispr_data$Hugo_Symbol)))
ctrp_data_allgenes <- WilcoxonByDrugAllGenes(ctrp_melt, ctrp_grid, "CTRP")
saveRDS(ctrp_data_allgenes, "./data_munging/rds/ctrp_data_18Q3_allgenes.rds", compress = "xz")
```

```{r}
ctrp_data_allgenes <- readRDS("./data_munging/rds/ctrp_data_18Q3_allgenes.rds")
ctrp_data_allgenes <- ctrp_data_allgenes[order(ctrp_data_allgenes$p),]
knitr::kable(ctrp_data_allgenes[1:1000, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: by-drug Wilcoxon test results for point mutations in genes targeted in CRISPR screen (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

Test G2P genes in lineage-agnostic context:
```{r, eval=FALSE}
ctrp_signif_g2p <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene", data = ctrp_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
ctrp_signif_g2p <- adj_signif(ctrp_signif_g2p)
ctrp_signif_g2p <- ctrp_signif_g2p[order(ctrp_signif_g2p$p),]
saveRDS(ctrp_signif_g2p, "./data_munging/rds/ctrp_signif_g2p_gene.rds")

# Grid comparisons of G2P drugs and genes
ctrp_signif_g2p_grid <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene", data = ctrp_data_g2p_grid, method = "wilcox.test", p.adjust.method = "BH")
ctrp_signif_g2p_grid <- adj_signif(ctrp_signif_g2p_grid)
ctrp_signif_g2p_grid <- ctrp_signif_g2p_grid[order(ctrp_signif_g2p_grid$p),]
saveRDS(ctrp_signif_g2p_grid, "./data_munging/rds/ctrp_signif_g2p_grid.rds")
```

```{r}
ctrp_signif_g2p <- readRDS("./data_munging/rds/ctrp_signif_g2p_gene.rds")
knitr::kable(ctrp_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")

ctrp_signif_g2p_grid <- readRDS("./data_munging/rds/ctrp_signif_g2p_grid.rds")
knitr::kable(ctrp_signif_g2p_grid[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

Test G2P genes in lineage-grouped context:
```{r, eval=FALSE}
ctrp_signif_grid_lineage <- lapply(unique(ctrp_data_g2p_grid$Drug), WilcoxonByDrug, dataset = ctrp_data_g2p_grid, data_name = "ctrp", grouping_var = "lineage")
names(ctrp_signif_grid_lineage) <- unique(ctrp_signif_grid_lineage$Drug)
ctrp_signif_grid_lineage <- rbindlist(ctrp_signif_grid_lineage, use.names = TRUE)
ctrp_signif_grid_lineage <- ctrp_signif_grid_lineage[order(ctrp_signif_grid_lineage$p),]
saveRDS(ctrp_signif_grid_lineage, "./data_munging/rds/ctrp_signif_grid_lineage.rds")

ctrp_signif_g2p_lineage <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene_Lin", data = ctrp_data_g2p_dgl, method = "wilcox.test", p.adjust.method = "BH")
ctrp_signif_g2p_lineage <- adj_signif(ctrp_signif_g2p_lineage)
ctrp_signif_g2p_lineage <- ctrp_signif_g2p_lineage[order(ctrp_signif_g2p_lineage$p),]
saveRDS(ctrp_signif_g2p_lineage, "./data_munging/rds/ctrp_signif_g2p_lineage.rds")
```

```{r}
ctrp_signif_g2p_lineage <- readRDS("./data_munging/rds/ctrp_signif_g2p_lineage.rds")
ctrp_signif_grid_lineage <- readRDS("./data_munging/rds/ctrp_signif_grid_lineage.rds")

knitr::kable(ctrp_signif_g2p_lineage[, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")

knitr::kable(ctrp_signif_grid_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

## GDSC

Test all CRISPR genes in lineage-agnostic context:
```{r, eval=FALSE}
gdsc <- read.delim("./data_munging/data_drug_auc_gdsc_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
gdsc <- merge(drug_meta, gdsc, by = "CID")
gdsc_melt <- melt(gdsc, id.vars = c("CID", "Drug"), measure.vars = colnames(gdsc)[3:ncol(gdsc)], variable.name = "accession_id", value.name = "AUC")
gdsc_grid <- expand.grid("accession_id" = unique(gdsc_melt$accession_id), "Hugo_Symbol" = as.character(unique(crispr_data$Hugo_Symbol)))
system.time({ gdsc_data_allgenes <- WilcoxonByDrugAllGenes(gdsc_melt, gdsc_grid, "GDSC") })
saveRDS(gdsc_data_allgenes, "./data_munging/rds/gdsc_data_18Q3_allgenes.rds", compress = "xz")
```

```{r}
gdsc_data_allgenes <- readRDS("./data_munging/rds/gdsc_data_18Q3_allgenes.rds")
gdsc_data_allgenes <- gdsc_data_allgenes[order(gdsc_data_allgenes$p),]
knitr::kable(gdsc_data_allgenes[1:1000, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: by-drug Wilcoxon test results for point mutations in genes targeted in CRISPR screen (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

Test G2P genes in lineage-agnostic context:
```{r, eval=FALSE}
gdsc_signif_g2p <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene", data = gdsc_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
gdsc_signif_g2p <- adj_signif(gdsc_signif_g2p)
gdsc_signif_g2p <- gdsc_signif_g2p[order(gdsc_signif_g2p$p),]
saveRDS(gdsc_signif_g2p, "./data_munging/rds/gdsc_signif_g2p_gene.rds")

# Grid comparisons of G2P drugs and genes
gdsc_signif_g2p_grid <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene", data = gdsc_data_g2p_grid, method = "wilcox.test", p.adjust.method = "BH")
gdsc_signif_g2p_grid <- adj_signif(gdsc_signif_g2p_grid)
gdsc_signif_g2p_grid <- gdsc_signif_g2p_grid[order(gdsc_signif_g2p_grid$p),]
saveRDS(gdsc_signif_g2p_grid, "./data_munging/rds/gdsc_signif_g2p_grid.rds")
```

```{r}
gdsc_signif_g2p <- readRDS("./data_munging/rds/gdsc_signif_g2p_gene.rds")
knitr::kable(gdsc_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")

gdsc_signif_g2p_grid <- readRDS("./data_munging/rds/gdsc_signif_g2p_grid.rds")
knitr::kable(gdsc_signif_g2p_grid[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

Test G2P genes in lineage-grouped context:
```{r, eval=FALSE}
gdsc_signif_grid_lineage <- lapply(unique(gdsc_data_g2p_grid$Drug), WilcoxonByDrug, dataset = gdsc_data_g2p_grid, data_name = "gdsc", grouping_var = "lineage")
names(gdsc_signif_grid_lineage) <- unique(gdsc_signif_grid_lineage$Drug)
gdsc_signif_grid_lineage <- rbindlist(gdsc_signif_grid_lineage, use.names = TRUE)
gdsc_signif_grid_lineage <- gdsc_signif_grid_lineage[order(gdsc_signif_grid_lineage$p),]
saveRDS(gdsc_signif_grid_lineage, "./data_munging/rds/gdsc_signif_grid_lineage.rds")

gdsc_signif_g2p_lineage <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene_Lin", data = gdsc_data_g2p_dgl, method = "wilcox.test", p.adjust.method = "BH")
gdsc_signif_g2p_lineage <- adj_signif(gdsc_signif_g2p_lineage)
gdsc_signif_g2p_lineage <- gdsc_signif_g2p_lineage[order(gdsc_signif_g2p_lineage$p),]
saveRDS(gdsc_signif_g2p_lineage, "./data_munging/rds/gdsc_signif_g2p_lineage.rds")
```

```{r}
gdsc_signif_g2p_lineage <- readRDS("./data_munging/rds/gdsc_signif_g2p_lineage.rds")
gdsc_signif_grid_lineage <- readRDS("./data_munging/rds/gdsc_signif_grid_lineage.rds")

knitr::kable(gdsc_signif_g2p_lineage[, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")

knitr::kable(gdsc_signif_grid_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

# PEARSON/SPEARMAN CORRELATIONS

--------------------------------------------------------------------------------

Pearson correlations for assessing effect of gene expression and copy number on gene essentiality score and AUC.

## CRISPR

```{r}
crispr_pearson_res_GE <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>%
                         summarize(p = cor.test(y = Score, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
                                   corr = cor.test(y = Score, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
                                   Metric = "Gene Expression")
crispr_pearson_res_CN <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>%
                         summarize(p = cor.test(y = Score, x = CN, method = "pearson", use = "complete.obs")$p.value,
                                   corr = cor.test(y = Score, x = CN, method = "pearson", use = "complete.obs")$estimate,
                                   Metric = "Copy Number")
crispr_spearman_res_GE <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>%
                          summarize(p = cor.test(y = Score, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
                                    corr = cor.test(y = Score, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
                                    Metric = "Gene Expression")
crispr_spearman_res_CN <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>%
                          summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value,
                                    corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate,
                                    Metric = "Copy Number")
```

## Drug screens

```{r}
g2p_druggene_tally <- g2p_filt %>% group_by(Drug_Gene) %>% tally() %>% drop_na()

# CCLE
ccle_cor_res <- ccle_data_g2p_grid %>% group_by(Drug_Gene) %>%
                    summarize(Pearson_Corr_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
                              Pearson_Corr_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$p.value,
                              Spearman_Corr_GE = cor.test(y = AUC, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_GE = cor.test(y = AUC, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
                              Spearman_Corr_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$p.value)
ccle_cor_res <- merge(g2p_druggene_tally, ccle_cor_res, by = "Drug_Gene", all.y = TRUE)
ccle_cor_res$n <- ifelse(is.na(ccle_cor_res$n), 0, ccle_cor_res$n)
ccle_cor_res$InG2P <- ifelse(ccle_cor_res$n != 0, "Yes", "No")
ccle_cor_res$Dataset <- "CCLE"
ccle_pearson_ttest_GE <- t.test(ccle_cor_res$Pearson_Corr_GE ~ ccle_cor_res$InG2P)
ccle_pearson_ttest_res_GE <- paste0("t(", round(ccle_pearson_ttest_GE$parameter, 0), ") = ", round(ccle_pearson_ttest_GE$statistic, 2), ", p = ", round(ccle_pearson_ttest_GE$p.value, 2))
ccle_pearson_ttest_CN <- t.test(ccle_cor_res$Pearson_Corr_CN ~ ccle_cor_res$InG2P)
ccle_pearson_ttest_res_CN <- paste0("t(", round(ccle_pearson_ttest_CN$parameter, 0), ") = ", round(ccle_pearson_ttest_CN$statistic, 2), ", p = ", round(ccle_pearson_ttest_CN$p.value, 2))
ccle_spearman_ttest_GE <- t.test(ccle_cor_res$Spearman_Corr_GE ~ ccle_cor_res$InG2P)
ccle_spearman_ttest_res_GE <- paste0("t(", round(ccle_spearman_ttest_GE$parameter, 0), ") = ", round(ccle_spearman_ttest_GE$statistic, 2), ", p = ", round(ccle_spearman_ttest_GE$p.value, 2))
ccle_spearman_ttest_CN <- t.test(ccle_cor_res$Spearman_Corr_CN ~ ccle_cor_res$InG2P)
ccle_spearman_ttest_res_CN <- paste0("t(", round(ccle_spearman_ttest_CN$parameter, 0), ") = ", round(ccle_spearman_ttest_CN$statistic, 2), ", p = ", formatC(ccle_spearman_ttest_CN$p.value, 2, format = "f"))

# CTRP
ctrp_cor_res <- ctrp_data_g2p_grid %>% group_by(Drug_Gene) %>%
                    summarize(Pearson_Corr_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
                              Pearson_Corr_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$p.value,
                              Spearman_Corr_GE = cor.test(y = AUC, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_GE = cor.test(y = AUC, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
                              Spearman_Corr_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$p.value)
ctrp_cor_res <- merge(g2p_druggene_tally, ctrp_cor_res, by = "Drug_Gene", all.y = TRUE)
ctrp_cor_res$n <- ifelse(is.na(ctrp_cor_res$n), 0, ctrp_cor_res$n)
ctrp_cor_res$InG2P <- ifelse(ctrp_cor_res$n != 0, "Yes", "No")
ctrp_cor_res$Dataset <- "CTRP"
ctrp_pearson_ttest_GE <- t.test(ctrp_cor_res$Pearson_Corr_GE ~ ctrp_cor_res$InG2P)
ctrp_pearson_ttest_res_GE <- paste0("t(", round(ctrp_pearson_ttest_GE$parameter, 0), ") = ", round(ctrp_pearson_ttest_GE$statistic, 2), ", p ", ifelse(round(ctrp_pearson_ttest_GE$p.value, 3) == 0, "< 0.001", paste0("= ", round(ctrp_pearson_ttest_GE$p.value, 3))))
ctrp_pearson_ttest_CN <- t.test(ctrp_cor_res$Pearson_Corr_CN ~ ctrp_cor_res$InG2P)
ctrp_pearson_ttest_res_CN <- paste0("t(", round(ctrp_pearson_ttest_CN$parameter, 0), ") = ", round(ctrp_pearson_ttest_CN$statistic, 2), ", p = ", round(ctrp_pearson_ttest_CN$p.value, 3))
ctrp_spearman_ttest_GE <- t.test(ctrp_cor_res$Spearman_Corr_GE ~ ctrp_cor_res$InG2P)
ctrp_spearman_ttest_res_GE <- paste0("t(", round(ctrp_spearman_ttest_GE$parameter, 0), ") = ", round(ctrp_spearman_ttest_GE$statistic, 2), ", p = ", round(ctrp_spearman_ttest_GE$p.value, 2))
ctrp_spearman_ttest_CN <- t.test(ctrp_cor_res$Spearman_Corr_CN ~ ctrp_cor_res$InG2P)
ctrp_spearman_ttest_res_CN <- paste0("t(", round(ctrp_spearman_ttest_CN$parameter, 0), ") = ", round(ctrp_spearman_ttest_CN$statistic, 2), ", p = ", round(ctrp_spearman_ttest_CN$p.value, 2))

# GDSC
gdsc_cor_res <- gdsc_data_g2p_grid %>% group_by(Drug_Gene) %>%
                    summarize(Pearson_Corr_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
                              Pearson_Corr_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$p.value,
                              Spearman_Corr_GE = cor.test(y = AUC, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_GE = cor.test(y = AUC, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
                              Spearman_Corr_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$p.value)
gdsc_cor_res <- merge(g2p_druggene_tally, gdsc_cor_res, by = "Drug_Gene", all.y = TRUE)
gdsc_cor_res$n <- ifelse(is.na(gdsc_cor_res$n), 0, gdsc_cor_res$n)
gdsc_cor_res$InG2P <- ifelse(gdsc_cor_res$n != 0, "Yes", "No")
gdsc_cor_res$Dataset <- "GDSC"
gdsc_pearson_ttest_GE <- t.test(gdsc_cor_res$Pearson_Corr_GE ~ gdsc_cor_res$InG2P)
gdsc_pearson_ttest_res_GE <- paste0("t(", round(gdsc_pearson_ttest_GE$parameter, 0), ") = ", round(gdsc_pearson_ttest_GE$statistic, 2), ", p = ", round(gdsc_pearson_ttest_GE$p.value, 3))
gdsc_pearson_ttest_CN <- t.test(gdsc_cor_res$Pearson_Corr_CN ~ gdsc_cor_res$InG2P)
gdsc_pearson_ttest_res_CN <- paste0("t(", round(gdsc_pearson_ttest_CN$parameter, 0), ") = ", round(gdsc_pearson_ttest_CN$statistic, 2), ", p = ", round(gdsc_pearson_ttest_CN$p.value, 3))
gdsc_spearman_ttest_GE <- t.test(gdsc_cor_res$Spearman_Corr_GE ~ gdsc_cor_res$InG2P)
gdsc_spearman_ttest_res_GE <- paste0("t(", round(gdsc_spearman_ttest_GE$parameter, 0), ") = ", round(gdsc_spearman_ttest_GE$statistic, 2), ", p = ", round(gdsc_spearman_ttest_GE$p.value, 2))
gdsc_spearman_ttest_CN <- t.test(gdsc_cor_res$Spearman_Corr_CN ~ gdsc_cor_res$InG2P)
gdsc_spearman_ttest_res_CN <- paste0("t(", round(gdsc_spearman_ttest_CN$parameter, 0), ") = ", round(gdsc_spearman_ttest_CN$statistic, 2), ", p = ", round(gdsc_spearman_ttest_CN$p.value, 2))

# All
g2p_cor <- rbind(ccle_cor_res, ctrp_cor_res, gdsc_cor_res)
g2p_cor$Pearson_GE_Abs <- abs(g2p_cor$Pearson_Corr_GE)
g2p_cor$Pearson_GE_Sign <- ifelse(sign(g2p_cor$Pearson_Corr_GE) == 1, "+", ifelse(sign(g2p_cor$Pearson_Corr_GE) == -1, "-", "0"))
g2p_cor$Pearson_CN_Abs <- abs(g2p_cor$Pearson_Corr_CN)
g2p_cor$Pearson_CN_Sign <- ifelse(sign(g2p_cor$Pearson_Corr_CN) == 1, "+", ifelse(sign(g2p_cor$Pearson_Corr_CN) == -1, "-", "0"))
g2p_cor$Spearman_GE_Abs <- abs(g2p_cor$Spearman_Corr_GE)
g2p_cor$Spearman_GE_Sign <- ifelse(sign(g2p_cor$Spearman_Corr_GE) == 1, "+", ifelse(sign(g2p_cor$Spearman_Corr_GE) == -1, "-", "0"))
g2p_cor$Spearman_CN_Abs <- abs(g2p_cor$Spearman_Corr_CN)
g2p_cor$Spearman_CN_Sign <- ifelse(sign(g2p_cor$Spearman_Corr_CN) == 1, "+", ifelse(sign(g2p_cor$Spearman_Corr_CN) == -1, "-", "0"))
g2p_cor_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"),
                               Pearson_Test_Results_GE = c(ccle_pearson_ttest_res_GE, ctrp_pearson_ttest_res_GE, gdsc_pearson_ttest_res_GE),
                               Pearson_Test_Results_CN = c(ccle_pearson_ttest_res_CN, ctrp_pearson_ttest_res_CN, gdsc_pearson_ttest_res_CN),
                               Spearman_Test_Results_GE = c(ccle_spearman_ttest_res_GE, ctrp_spearman_ttest_res_GE, gdsc_spearman_ttest_res_GE),
                               Spearman_Test_Results_CN = c(ccle_spearman_ttest_res_CN, ctrp_spearman_ttest_res_CN, gdsc_spearman_ttest_res_CN))
```

# SUMMARIES

--------------------------------------------------------------------------------

## CRISPR: Mutation status counts

```{r}
crispr_data_g2p_summ <- unique(crispr_data_g2p[, c("Hugo_Symbol", "N_Nonsilent_Mutant", "N_Nonsilent_Wildtype")])
crispr_data_g2p_summ$Percent_Mutant <- crispr_data_g2p_summ$N_Nonsilent_Mutant / (crispr_data_g2p_summ$N_Nonsilent_Mutant + crispr_data_g2p_summ$N_Nonsilent_Wildtype) * 100
rownames(crispr_data_g2p_summ) <- NULL

# write.table(crispr_data_g2p_summ, file = "~/Desktop/crispr_data_g2p_summ_20181003.tsv", quote = FALSE, sep = "\t")

knitr::kable(crispr_data_g2p_summ, caption = "CRISPR: Level A G2P genes mutation status summary") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

## G2P tallies and summary stats

```{r}
print("Drug-Gene")
g2p_druggene_tally <- g2p_filt %>% group_by(Drug_Gene) %>% tally() %>% drop_na()
nrow(g2p_druggene_tally)
range(g2p_druggene_tally$n)
mean(g2p_druggene_tally$n)
sd(g2p_druggene_tally$n)

print("Drug")
g2p_drug_tally <- g2p_filt %>% group_by(Drug) %>% tally() %>% drop_na()
range(g2p_drug_tally$n)
mean(g2p_drug_tally$n)
sd(g2p_drug_tally$n)

print("Gene")
g2p_gene_tally <- g2p_filt %>% group_by(Gene) %>% tally() %>% drop_na()
range(g2p_gene_tally$n)
mean(g2p_gene_tally$n)
sd(g2p_gene_tally$n)

print("Drug-Gene-Lineage")
g2p_dgl_tally <- g2p_filt %>% group_by(Drug, Gene, Drug_Gene, group_general_lineage_name) %>% tally() %>% drop_na()
nrow(g2p_dgl_tally)
length(unique(g2p_dgl_tally$Drug))
length(unique(g2p_dgl_tally$Gene))
unique(g2p_filt$Phenotype.Description)
```

# PANCANCER

--------------------------------------------------------------------------------

## Mut

CRISPR mutation status plots of p-values:
```{r fig.height=1.5, fig.width=12}
crispr_signif_g2p_gene$y_label <- "CRISPR"
crispr_signif_g2p_gene$Hugo_Symbol <- factor(crispr_signif_g2p_gene$Hugo_Symbol, levels = g2p_genes)
crispr_signif_g2p_gene$p <- as.numeric(as.character(crispr_signif_g2p_gene$p))

crispr_mut_heatmap_plot <- ggplot(data = crispr_signif_g2p_gene, aes(x = Hugo_Symbol, y = y_label)) +
  geom_tile(aes(fill = p)) +
  scale_fill_gradientn(colors = c("darkgreen", "honeydew", "white"), values = c(0, 0.05, 1), na.value = "darksalmon") +
  scale_x_discrete(drop = FALSE) +
  theme(axis.title.y = element_blank(), axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 10)) +
  labs(x = "Gene")
crispr_mut_heatmap_plot

# write.table(crispr_signif_g2p_gene, file = "~/Desktop/crispr_signif_g2p_gene_20181203.csv", quote = FALSE, sep = ",", row.names = FALSE)
# ggsave("./plots/manuscript/crispr_mut_heatmap_plot_example.png", crispr_mut_heatmap_plot, device = "png", dpi = 450, width = 12, height = 1.5, units = "in")
```

```{r}
ccle_mut_summ <- merge(g2p_druggene_tally, ccle_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
ccle_mut_summ$n <- ifelse(is.na(ccle_mut_summ$n), 0, ccle_mut_summ$n)
ccle_mut_summ$InG2P <- ifelse(ccle_mut_summ$n != 0, "Yes", "No")
ccle_mut_summ$Dataset <- "CCLE"
ccle_p_ttest <- t.test(ccle_mut_summ$p ~ ccle_mut_summ$InG2P)
ccle_p_ttest_res <- paste0("t(", round(ccle_p_ttest$parameter, 0), ") = ", round(ccle_p_ttest$statistic, 2), ", p = ", round(ccle_p_ttest$p.value, 2))

ctrp_mut_summ <- merge(g2p_druggene_tally, ctrp_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
ctrp_mut_summ$n <- ifelse(is.na(ctrp_mut_summ$n), 0, ctrp_mut_summ$n)
ctrp_mut_summ$InG2P <- ifelse(ctrp_mut_summ$n != 0, "Yes", "No")
ctrp_mut_summ$Dataset <- "CTRP"
ctrp_p_ttest <- t.test(ctrp_mut_summ$p ~ ctrp_mut_summ$InG2P)
ctrp_p_ttest_res <- paste0("t(", round(ctrp_p_ttest$parameter, 0), ") = ", round(ctrp_p_ttest$statistic, 2), ", p = ", formatC(ctrp_p_ttest$p.value, digits = 2, format = "f"))

gdsc_mut_summ <- merge(g2p_druggene_tally, gdsc_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
gdsc_mut_summ$n <- ifelse(is.na(gdsc_mut_summ$n), 0, gdsc_mut_summ$n)
gdsc_mut_summ$InG2P <- ifelse(gdsc_mut_summ$n != 0, "Yes", "No")
gdsc_mut_summ$Dataset <- "GDSC"
gdsc_p_ttest <- t.test(gdsc_mut_summ$p ~ gdsc_mut_summ$InG2P)
gdsc_p_ttest_res <- paste0("t(", round(gdsc_p_ttest$parameter, 0), ") = ", round(gdsc_p_ttest$statistic, 2), ", p = ", formatC(gdsc_p_ttest$p.value, digits = 2, format = "f"))

g2p_mut_all_summ <- rbind(ccle_mut_summ, ctrp_mut_summ, gdsc_mut_summ)
g2p_mut_all_summ$p_log10 <- -log10(g2p_mut_all_summ$p)
g2p_mut_all_summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"), Test_Results_p = c(ccle_p_ttest_res, ctrp_p_ttest_res, gdsc_p_ttest_res))
g2p_mut_all_summ$Drug_Gene_Ordered <- factor(g2p_mut_all_summ$Drug_Gene, levels = as.character(unique(g2p_mut_all_summ$Drug_Gene)), labels = sapply(strsplit(x = as.character(unique(g2p_mut_all_summ$Drug_Gene)), split = "_"), function(x) paste0(x[1], "\n", x[2])))
```

```{r fig.height=5, fig.width=12}
plot_p_point <- ggplot(data = g2p_mut_all_summ, aes(x = p, y = n, label = Drug_Gene)) +
  facet_wrap(~ Dataset, scales = "free_x") +
  geom_point(mapping = aes(color = InG2P), alpha = 0.5) +
  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
  geom_text_repel(data = subset(g2p_mut_all_summ, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
  geom_text(data = g2p_mut_all_summ_text, mapping = aes(x = 0.5, y = 115, label = Test_Results_p)) +
  labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations") +
  theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())

plot_p_box <- ggplot(data = g2p_mut_all_summ) +
  facet_wrap(~ Dataset, scales = "free_x") +
  geom_violin(mapping = aes(color = InG2P, fill = InG2P, y = p, x = InG2P), alpha = 0.35) +
  geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), width = 0.25) +
  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
  coord_flip() +
  labs(x = "In G2P?") +
  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))

plot_p_point <- ggplot_gtable(ggplot_build(plot_p_point))
plot_p_box <- ggplot_gtable(ggplot_build(plot_p_box))
p_maxWidth <-  grid::unit.pmax(plot_p_point$widths, plot_p_box$widths)
plot_p_point$widths <- as.list(p_maxWidth)
plot_p_box$widths <- as.list(p_maxWidth)
g2p_mut_plot <- cowplot::plot_grid(plot_p_box,
                   plot_p_point,
                   nrow = 2,
                   rel_heights = c(1, 4))
g2p_mut_plot

# ggsave("./plots/manuscript/g2p_mut_plot.png", g2p_mut_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
```

```{r, eval=FALSE}
plot_p_point <- ggplot(data = g2p_mut_all_summ) +
  facet_wrap(~ Dataset, scales = "free_x") +
  geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = p, y = n), alpha = 0.5) +
  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
  geom_text(data = g2p_mut_all_summ_text, mapping = aes(x = 0.5, y = 115, label = Test_Results_p)) +
  labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations") +
  theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())

plot_p_box <- ggplot(data = g2p_mut_all_summ) +
  facet_wrap(~ Dataset, scales = "free_x") +
  geom_violin(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.5) +
  geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.75, width = 0.25) +
  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
  coord_flip() +
  labs(x = "Level A G2P\nassociation") +
  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))

plot <- subplot(plot_p_box, plot_p_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Gene-drug association p-value between mutation groups"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))

saveWidgetFix(widget = plot, file = "./plots/manuscript/g2p_mut_plot.html")
```

## GE

### Pearson

```{r fig.height=5, fig.width=12}
plot_ge_pearson_point <- ggplot(data = g2p_cor, aes(x = Pearson_GE_Abs, y = n, label = Drug_Gene)) +
  facet_wrap(~ Dataset) +
  geom_point(mapping = aes(fill = InG2P, color = InG2P, shape = Pearson_GE_Sign), alpha = 0.5, size = 1.25) +
  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
  scale_x_continuous(breaks = seq(0, 0.65, by = 0.1), labels = seq(0, 0.65, by = 0.1)) +
  coord_cartesian(xlim = c(0, 0.65)) +
  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
  geom_text_repel(data = subset(g2p_cor, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
  geom_text(data = g2p_cor_text, mapping = aes(x = 0.325, y = 115, label = Pearson_Test_Results_GE)) +
  labs(x = "Pearson correlation coefficient (r) between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +
  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
  guides(color = FALSE, fill = FALSE, shape = FALSE)

plot_ge_pearson_box <- ggplot(data = g2p_cor) +
  facet_wrap(~ Dataset) +
  geom_violin(mapping = aes(color = InG2P, fill = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.35) +
  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), width = 0.25) +
  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
  scale_y_continuous(breaks = seq(0, 0.65, by = 0.1), labels = seq(0, 0.65, by = 0.1)) +
  coord_flip(ylim = c(0, 0.65)) +
  labs(x = "In G2P?") +
  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))

plot_ge_pearson_point <- ggplot_gtable(ggplot_build(plot_ge_pearson_point))
plot_ge_pearson_box <- ggplot_gtable(ggplot_build(plot_ge_pearson_box))
p_maxWidth <-  grid::unit.pmax(plot_ge_pearson_point$widths[2:3], plot_ge_pearson_box$widths[2:3])
plot_ge_pearson_point$widths[2:3] <- p_maxWidth
plot_ge_pearson_box$widths[2:3] <- p_maxWidth

g2p_ge_pearson_plot <- cowplot::plot_grid(plot_ge_pearson_box, plot_ge_pearson_point, nrow = 2, rel_heights = c(1, 4))
g2p_ge_pearson_plot

# ggsave("./plots/manuscript/g2p_ge_pearson_plot.png", g2p_ge_pearson_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
```

```{r, eval=FALSE}
plot_ge_point <- ggplot(data = g2p_cor) +
  facet_wrap(~ Dataset) +
  geom_point(mapping = aes(label = Drug_Gene, fill = InG2P, color = InG2P, shape = Pearson_GE_Sign, x = Pearson_GE_Abs, y = n, size = Pearson_Pval_GE), alpha = 0.5, size = 1.25) +
  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
  scale_x_continuous(breaks = pretty_breaks()) +
  geom_text(data = g2p_cor_text, mapping = aes(x = 0.3, y = 115, label = Pearson_Test_Results_GE)) +
  labs(x = "Pearson correlation coefficient (r) between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +
  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
  guides(color = FALSE, fill = FALSE) +
  labs(shape = NULL)

plot_ge_box <- ggplot(data = g2p_cor) +
  facet_wrap(~ Dataset) +
  geom_violin(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.5) +
  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
  coord_flip() +
  labs(x = "In G2P?") +
  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))

ge_pearson_plot <- subplot(plot_ge_box, plot_ge_point, nrows = 2, heights = c(0.2, 0.8), titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and gene expression"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))

saveWidgetFix(widget = ge_pearson_plot, file = "./plots/manuscript/g2p_ge_pearson_plot.html")
```

### Spearman

```{r fig.height=5, fig.width=12}
plot_ge_spearman_point <- ggplot(data = g2p_cor, aes(x = Spearman_GE_Abs, y = n, label = Drug_Gene)) +
  facet_wrap(~ Dataset) +
  geom_point(mapping = aes(fill = InG2P, color = InG2P, shape = Spearman_GE_Sign), alpha = 0.5, size = 1.25) +
  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
  scale_x_continuous(breaks = seq(0, 0.65, by = 0.1), labels = seq(0, 0.65, by = 0.1)) +
  coord_cartesian(xlim = c(0, 0.6)) +
  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
  geom_text_repel(data = subset(g2p_cor, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
  geom_text(data = g2p_cor_text, mapping = aes(x = 0.3, y = 115, label = Spearman_Test_Results_GE)) +
  labs(x = "Spearman correlation coefficient (r_s) between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +
  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
  guides(color = FALSE, fill = FALSE, shape = FALSE)

plot_ge_spearman_box <- ggplot(data = g2p_cor) +
  facet_wrap(~ Dataset) +
  geom_violin(mapping = aes(color = InG2P, fill = InG2P, y = Spearman_GE_Abs, x = InG2P), alpha = 0.35) +
  geom_boxplot(mapping = aes(color = InG2P, y = Spearman_GE_Abs, x = InG2P), width = 0.25) +
  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
  scale_y_continuous(breaks = seq(0, 0.65, by = 0.1), labels = seq(0, 0.65, by = 0.1)) +
  coord_flip(ylim = c(0, 0.6)) +
  labs(x = "In G2P?") +
  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))

plot_ge_spearman_point <- ggplot_gtable(ggplot_build(plot_ge_spearman_point))
plot_ge_spearman_box <- ggplot_gtable(ggplot_build(plot_ge_spearman_box))
p_maxWidth <-  grid::unit.pmax(plot_ge_spearman_point$widths[2:3], plot_ge_spearman_box$widths[2:3])
plot_ge_spearman_point$widths[2:3] <- p_maxWidth
plot_ge_spearman_box$widths[2:3] <- p_maxWidth

g2p_ge_spearman_plot <- cowplot::plot_grid(plot_ge_spearman_box, plot_ge_spearman_point, nrow = 2, rel_heights = c(1, 4))
g2p_ge_spearman_plot

# ggsave("./plots/manuscript/g2p_ge_spearman_plot.png", g2p_ge_spearman_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
```

```{r, eval=FALSE}
plot_ge_point <- ggplot(data = g2p_cor) +
  facet_wrap(~ Dataset) +
  geom_point(mapping = aes(label = Drug_Gene, fill = InG2P, color = InG2P, shape = Spearman_GE_Sign, x = Spearman_GE_Abs, y = n, size = Spearman_Pval_GE), alpha = 0.5, size = 1.25) +
  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
  scale_x_continuous(breaks = pretty_breaks()) +
  geom_text(data = g2p_cor_text, mapping = aes(x = 0.3, y = 115, label = Spearman_Test_Results_GE)) +
  labs(x = "Spearman correlation coefficient (r_s) between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +
  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
  guides(color = FALSE, fill = FALSE) +
  labs(shape = NULL)

plot_ge_box <- ggplot(data = g2p_cor) +
  facet_wrap(~ Dataset) +
  geom_violin(mapping = aes(color = InG2P, y = Spearman_GE_Abs, x = InG2P), alpha = 0.5) +
  geom_boxplot(mapping = aes(color = InG2P, y = Spearman_GE_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
  coord_flip() +
  labs(x = "In G2P?") +
  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))

ge_spearman_plot <- subplot(plot_ge_box, plot_ge_point, nrows = 2, heights = c(0.2, 0.8), titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Spearman correlation coefficient between drug-gene AUC and gene expression"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))

saveWidgetFix(widget = ge_spearman_plot, file = "./plots/manuscript/g2p_ge_spearman_plot.html")
```

## CN

### Pearson

```{r fig.height=5, fig.width=12}
plot_cn_pearson_point <- ggplot(data = g2p_cor, aes(x = Pearson_CN_Abs, y = n, label = Drug_Gene)) +
  facet_wrap(~ Dataset) +
  geom_point(mapping = aes(fill = InG2P, color = InG2P, shape = Pearson_CN_Sign), alpha = 0.5, size = 1.25) +
  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
  scale_x_continuous(breaks = seq(0, 0.65, by = 0.1), labels = seq(0, 0.65, by = 0.1)) +
  coord_cartesian(xlim = c(0, 0.5)) +
  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
  geom_text_repel(data = subset(g2p_cor, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
  geom_text(data = g2p_cor_text, mapping = aes(x = 0.25, y = 115, label = Pearson_Test_Results_CN)) +
  labs(x = "Pearson correlation coefficient (r) between drug-gene AUC and copy number", y = "Number of level A G2P associations") +
  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
  guides(color = FALSE, fill = FALSE, shape = FALSE)

plot_cn_pearson_box <- ggplot(data = g2p_cor) +
  facet_wrap(~ Dataset) +
  geom_violin(mapping = aes(color = InG2P, fill = InG2P, y = Pearson_CN_Abs, x = InG2P), alpha = 0.35) +
  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_CN_Abs, x = InG2P), width = 0.25) +
  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
  scale_y_continuous(breaks = seq(0, 0.65, by = 0.1), labels = seq(0, 0.65, by = 0.1)) +
  coord_flip(ylim = c(0, 0.5)) +
  labs(x = "In G2P?") +
  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))

plot_cn_pearson_point <- ggplot_gtable(ggplot_build(plot_cn_pearson_point))
plot_cn_pearson_box <- ggplot_gtable(ggplot_build(plot_cn_pearson_box))
p_maxWidth <-  grid::unit.pmax(plot_cn_pearson_point$widths[2:3], plot_cn_pearson_box$widths[2:3])
plot_cn_pearson_point$widths[2:3] <- p_maxWidth
plot_cn_pearson_box$widths[2:3] <- p_maxWidth

g2p_cn_pearson_plot <- cowplot::plot_grid(plot_cn_pearson_box, plot_cn_pearson_point, nrow = 2, rel_heights = c(1, 4))
g2p_cn_pearson_plot

# ggsave("./plots/manuscript/g2p_cn_pearson_plot.png", g2p_cn_pearson_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
```

```{r, eval=FALSE}
plot_cn_point <- ggplot(data = g2p_cor) +
  facet_wrap(~ Dataset) +
  geom_point(mapping = aes(label = Drug_Gene, fill = InG2P, color = InG2P, shape = Pearson_CN_Sign, x = Pearson_CN_Abs, y = n, size = Pearson_Pval_CN), alpha = 0.5, size = 1.25) +
  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
  scale_x_continuous(breaks = pretty_breaks()) +
  geom_text(data = g2p_cor_text, mapping = aes(x = 0.3, y = 115, label = Pearson_Test_Results_CN)) +
  labs(x = "Pearson correlation coefficient (r) between drug-gene AUC and copy number", y = "Number of level A G2P associations") +
  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
  guides(color = FALSE, fill = FALSE) +
  labs(shape = NULL)

plot_cn_box <- ggplot(data = g2p_cor) +
  facet_wrap(~ Dataset) +
  geom_violin(mapping = aes(color = InG2P, y = Pearson_CN_Abs, x = InG2P), alpha = 0.5) +
  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_CN_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
  coord_flip() +
  labs(x = "In G2P?") +
  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))

cn_pearson_plot <- subplot(plot_cn_box, plot_cn_point, nrows = 2, heights = c(0.2, 0.8), titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and copy number"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))

saveWidgetFix(widget = ge_pearson_plot, file = "./plots/manuscript/g2p_cn_pearson_plot.html")
```

### Spearman

```{r fig.height=5, fig.width=12}
plot_cn_spearman_point <- ggplot(data = g2p_cor, aes(x = Spearman_CN_Abs, y = n, label = Drug_Gene)) +
  facet_wrap(~ Dataset) +
  geom_point(mapping = aes(fill = InG2P, color = InG2P, shape = Spearman_CN_Sign), alpha = 0.5, size = 1.25) +
  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
  scale_x_continuous(breaks = seq(0, 0.4, by = 0.05), labels = seq(0, 0.4, by = 0.05)) +
  coord_cartesian(xlim = c(0, 0.35)) +
  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
  geom_text_repel(data = subset(g2p_cor, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
  geom_text(data = g2p_cor_text, mapping = aes(x = 0.175, y = 115, label = Spearman_Test_Results_CN)) +
  labs(x = "Spearman correlation coefficient (r_s) between drug-gene AUC and copy number", y = "Number of level A G2P associations") +
  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
  guides(color = FALSE, fill = FALSE, shape = FALSE)

plot_cn_spearman_box <- ggplot(data = g2p_cor) +
  facet_wrap(~ Dataset) +
  geom_violin(mapping = aes(color = InG2P, fill = InG2P, y = Spearman_CN_Abs, x = InG2P), alpha = 0.35) +
  geom_boxplot(mapping = aes(color = InG2P, y = Spearman_CN_Abs, x = InG2P), width = 0.25) +
  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
  scale_y_continuous(breaks = seq(0, 0.4, by = 0.05), labels = seq(0, 0.4, by = 0.05)) +
  coord_flip(ylim = c(0, 0.35)) +
  labs(x = "In G2P?") +
  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))

plot_cn_spearman_point <- ggplot_gtable(ggplot_build(plot_cn_spearman_point))
plot_cn_spearman_box <- ggplot_gtable(ggplot_build(plot_cn_spearman_box))
p_maxWidth <-  grid::unit.pmax(plot_cn_spearman_point$widths[2:3], plot_cn_spearman_box$widths[2:3])
plot_cn_spearman_point$widths[2:3] <- p_maxWidth
plot_cn_spearman_box$widths[2:3] <- p_maxWidth

g2p_cn_spearman_plot <- cowplot::plot_grid(plot_cn_spearman_box, plot_cn_spearman_point, nrow = 2, rel_heights = c(1, 4))
g2p_cn_spearman_plot

# ggsave("./plots/manuscript/g2p_cn_spearman_plot.png", g2p_cn_spearman_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
```

```{r, eval=FALSE}
plot_cn_point <- ggplot(data = g2p_cor) +
  facet_wrap(~ Dataset) +
  geom_point(mapping = aes(label = Drug_Gene, fill = InG2P, color = InG2P, shape = Spearman_CN_Sign, x = Spearman_CN_Abs, y = n, size = Spearman_Pval_CN), alpha = 0.5, size = 1.25) +
  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
  scale_x_continuous(breaks = pretty_breaks()) +
  geom_text(data = g2p_cor_text, mapping = aes(x = 0.175, y = 115, label = Spearman_Test_Results_CN)) +
  labs(x = "Spearman correlation coefficient (r_s) between drug-gene AUC and copy number", y = "Number of level A G2P associations") +
  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
  guides(color = FALSE, fill = FALSE) +
  labs(shape = NULL)

plot_cn_box <- ggplot(data = g2p_cor) +
  facet_wrap(~ Dataset) +
  geom_violin(mapping = aes(color = InG2P, y = Spearman_CN_Abs, x = InG2P), alpha = 0.5) +
  geom_boxplot(mapping = aes(color = InG2P, y = Spearman_CN_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
  coord_flip() +
  labs(x = "In G2P?") +
  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))

cn_spearman_plot <- subplot(plot_cn_box, plot_cn_point, nrows = 2, heights = c(0.2, 0.8), titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Spearman correlation coefficient between drug-gene AUC and copy number"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))

saveWidgetFix(widget = cn_spearman_plot, file = "./plots/manuscript/g2p_cn_spearman_plot.html")
```

# BY LINEAGE

--------------------------------------------------------------------------------

## Mut: Grid

Summarize the Wilcoxon test p-values of the grid tests by mutation status. Grid tests were all lineage-agnostic G2P drug-gene associations tested across all screened lineages in each dataset:
```{r}
g2p_dgl_mut_tally <- g2p %>% group_by(Drug_Gene, group_general_lineage_name) %>% tally()

ccle_dgl_summ <- ccle_signif_grid_lineage
ccle_dgl_summ$Drug_Gene <- paste0(ccle_dgl_summ$Drug, "_", ccle_dgl_summ$Hugo_Symbol)
ccle_dgl_summ <- merge(g2p_dgl_mut_tally, ccle_dgl_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
ccle_dgl_summ$Drug_Gene_Lin <- paste0(ccle_dgl_summ$Drug_Gene, "_", ccle_dgl_summ$group_general_lineage_name)
ccle_dgl_summ$n <- ifelse(is.na(ccle_dgl_summ$n), 0, ccle_dgl_summ$n)
ccle_dgl_summ$InG2P <- ifelse(ccle_dgl_summ$n != 0, "Yes", "No")
ccle_dgl_summ$Dataset <- "CCLE"

ctrp_dgl_summ <- ctrp_signif_grid_lineage
ctrp_dgl_summ$Drug_Gene <- paste0(ctrp_dgl_summ$Drug, "_", ctrp_dgl_summ$Hugo_Symbol)
ctrp_dgl_summ <- merge(g2p_dgl_mut_tally, ctrp_dgl_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
ctrp_dgl_summ$Drug_Gene_Lin <- paste0(ctrp_dgl_summ$Drug_Gene, "_", ctrp_dgl_summ$group_general_lineage_name)
ctrp_dgl_summ$n <- ifelse(is.na(ctrp_dgl_summ$n), 0, ctrp_dgl_summ$n)
ctrp_dgl_summ$InG2P <- ifelse(ctrp_dgl_summ$n != 0, "Yes", "No")
ctrp_dgl_summ$Dataset <- "CTRP"

gdsc_dgl_summ <- gdsc_signif_grid_lineage
gdsc_dgl_summ$Drug_Gene <- paste0(gdsc_dgl_summ$Drug, "_", gdsc_dgl_summ$Hugo_Symbol)
gdsc_dgl_summ <- merge(g2p_dgl_mut_tally, gdsc_dgl_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
gdsc_dgl_summ$Drug_Gene_Lin <- paste0(gdsc_dgl_summ$Drug_Gene, "_", gdsc_dgl_summ$group_general_lineage_name)
gdsc_dgl_summ$n <- ifelse(is.na(gdsc_dgl_summ$n), 0, gdsc_dgl_summ$n)
gdsc_dgl_summ$InG2P <- ifelse(gdsc_dgl_summ$n != 0, "Yes", "No")
gdsc_dgl_summ$Dataset <- "GDSC"

dgl_mut_grid_summ <- rbind(ccle_dgl_summ, ctrp_dgl_summ, gdsc_dgl_summ)
```

Make summary plots of mutation status tests by lineage and return a dataframe of all t-test results from comparing the p-value distributions of G2P and non-G2P drug-gene associaions:
```{r, eval=FALSE, results = 'hide'}
dgl_mut_g2p_grid_ttest_res <- lapply(as.character(unique(dgl_mut_grid_summ$group_general_lineage_name)), MutPlotsByLineage)
dgl_mut_g2p_grid_ttest_res_list <- rbindlist(dgl_mut_g2p_grid_ttest_res, use.names = TRUE)
dgl_mut_g2p_grid_ttest_res_list <- dgl_mut_g2p_grid_ttest_res_list[order(dgl_mut_g2p_grid_ttest_res_list$p_value),]
saveRDS(dgl_mut_g2p_grid_ttest_res_list, "./data_munging/rds/dgl_mut_g2p_grid_ttest_res_list.rds")
```

```{r}
dgl_mut_g2p_grid_ttest_res_list <- readRDS("./data_munging/rds/dgl_mut_g2p_grid_ttest_res_list.rds")
knitr::kable(dgl_mut_g2p_grid_ttest_res_list, caption = "Mutation status: T-test results for level A G2P drug-gene associations across lineages") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

## GE/CN: G2P

Drug-gene-lineage (DGL) overlaps between CCLE, CTRP, and GDSC:
```{r}
dgl_overlap_test_list <- list(CCLE = unique(ccle_data_g2p_dgl$Drug_Gene_Lin),
                              CTRP = unique(ctrp_data_g2p_dgl$Drug_Gene_Lin),
                              GDSC = unique(gdsc_data_g2p_dgl$Drug_Gene_Lin))

ItemsList <- venn(dgl_overlap_test_list, show.plot = TRUE)
ItemsList
```

Test the 102 level-A G2P DGL combinations:
```{r, eval=FALSE}
ccle_lineages4pearson <- as.character(unique(ccle_data_g2p_dgl$group_general_lineage_name))[!is.na(as.character(unique(ccle_data_g2p_dgl$group_general_lineage_name)))]
ccle_signif_ge <- lapply(ccle_lineages4pearson, PearsonByLineage, variable = "GE", dataset = ccle_data_g2p_dgl)
ccle_signif_ge_all_lin <- rbindlist(ccle_signif_ge, use.names = TRUE)
ccle_signif_ge_all_lin$Dataset <- "CCLE"
ccle_signif_cn <- lapply(ccle_lineages4pearson, PearsonByLineage, variable = "CN", dataset = ccle_data_g2p_dgl)
ccle_signif_cn_all_lin <- rbindlist(ccle_signif_cn, use.names = TRUE)
ccle_signif_cn_all_lin$Dataset <- "CCLE"
ccle_signif_all_lin <- merge(ccle_signif_ge_all_lin, ccle_signif_cn_all_lin, by = c("Drug_Gene", "group_general_lineage_name", "n", "Dataset"), all = TRUE)

ctrp_lineages4pearson <- as.character(unique(ctrp_data_g2p_dgl$group_general_lineage_name))[!is.na(as.character(unique(ctrp_data_g2p_dgl$group_general_lineage_name)))]
ctrp_signif_ge <- lapply(ctrp_lineages4pearson, PearsonByLineage, variable = "GE", dataset = ctrp_data_g2p_dgl)
ctrp_signif_ge_all_lin <- rbindlist(ctrp_signif_ge, use.names = TRUE)
ctrp_signif_ge_all_lin$Dataset <- "CTRP"
ctrp_signif_cn <- lapply(ctrp_lineages4pearson, PearsonByLineage, variable = "CN", dataset = ctrp_data_g2p_dgl)
ctrp_signif_cn_all_lin <- rbindlist(ctrp_signif_cn, use.names = TRUE)
ctrp_signif_cn_all_lin$Dataset <- "CTRP"
ctrp_signif_all_lin <- merge(ctrp_signif_ge_all_lin, ctrp_signif_cn_all_lin, by = c("Drug_Gene", "group_general_lineage_name", "n", "Dataset"), all = TRUE)

gdsc_lineages4pearson <- as.character(unique(gdsc_data_g2p_dgl$group_general_lineage_name))[!is.na(as.character(unique(gdsc_data_g2p_dgl$group_general_lineage_name)))]
gdsc_signif_ge <- lapply(gdsc_lineages4pearson, PearsonByLineage, variable = "GE", dataset = gdsc_data_g2p_dgl)
gdsc_signif_ge_all_lin <- rbindlist(gdsc_signif_ge, use.names = TRUE)
gdsc_signif_ge_all_lin$Dataset <- "GDSC"
gdsc_signif_cn <- lapply(gdsc_lineages4pearson, PearsonByLineage, variable = "CN", dataset = gdsc_data_g2p_dgl)
gdsc_signif_cn_all_lin <- rbindlist(gdsc_signif_cn, use.names = TRUE)
gdsc_signif_cn_all_lin$Dataset <- "GDSC"
gdsc_signif_all_lin <- merge(gdsc_signif_ge_all_lin, gdsc_signif_cn_all_lin, by = c("Drug_Gene", "group_general_lineage_name", "n", "Dataset"), all = TRUE)

signif_all_lin <- rbind(ccle_signif_all_lin, ctrp_signif_all_lin, gdsc_signif_all_lin)
signif_all_lin$n <- ifelse(is.na(signif_all_lin$n), 0, signif_all_lin$n)
signif_all_lin$InG2P <- ifelse(signif_all_lin$n != 0, "Yes", "No")
signif_all_lin$Drug_Gene_Lin <- paste0(signif_all_lin$Drug_Gene, "_", signif_all_lin$group_general_lineage_name)
saveRDS(signif_all_lin, "./data_munging/rds/dgl_signif_pearson_g2p.rds")
```

```{r}
dgl_signif_pearson_g2p <- readRDS("./data_munging/rds/dgl_signif_pearson_g2p.rds")
```

```{r}
# CCLE mut, n = 7
ccle_mut <- filter(select(ccle_signif_g2p_lineage, Drug_Gene_Lin, p), p < 0.05)
ccle_mut_n <- nrow(select(ccle_signif_g2p_lineage, Drug_Gene_Lin, p))
# CCLE GE/CN, n = 9
ccle_ge <- select(subset(filter(dgl_signif_pearson_g2p, Dataset == "CCLE"), Pearson_Pval_GE < 0.05), Drug_Gene_Lin, Pearson_Pval_GE, Pearson_Corr_GE)
ccle_cn <- select(subset(filter(dgl_signif_pearson_g2p, Dataset == "CCLE"), Pearson_Pval_CN < 0.05), Drug_Gene_Lin, Pearson_Pval_CN, Pearson_Corr_CN)
ccle_Pear_n <- nrow(filter(dgl_signif_pearson_g2p, Dataset == "CCLE"))
ccle_dgl_summ <- merge(ccle_mut, merge(ccle_ge, ccle_cn, by = "Drug_Gene_Lin", all = TRUE), all = TRUE)
ccle_dgl_summ <- with(ccle_dgl_summ, cbind(colsplit(Drug_Gene_Lin, pattern = "_", names = c("Drug", "Gene", "Lineage")), 
                                           CCLE_p = p,
                                           CCLE_p_Bonf = ifelse(p < 0.05 / ccle_mut_n, "Sig", NA),
                                           CCLE_r_GE = Pearson_Corr_GE,
                                           CCLE_p_GE = Pearson_Pval_GE,
                                           CCLE_p_GE_Bonf = ifelse(Pearson_Pval_GE < 0.05 / ccle_Pear_n, "Sig", NA),
                                           CCLE_r_CN = Pearson_Corr_CN,
                                           CCLE_p_CN = Pearson_Pval_CN,
                                           CCLE_p_CN_Bonf = ifelse(Pearson_Pval_CN < 0.05 / ccle_Pear_n, "Sig", NA)))

# CTRP mut, n = 48
ctrp_mut <- filter(select(ctrp_signif_g2p_lineage, Drug_Gene_Lin, p), p < 0.05)
ctrp_mut_n <- nrow(select(ctrp_signif_g2p_lineage, Drug_Gene_Lin, p))
# CTRP GE/CN, n = 61
ctrp_ge <- select(subset(filter(dgl_signif_pearson_g2p, Dataset == "CTRP"), Pearson_Pval_GE < 0.05), Drug_Gene_Lin, Pearson_Pval_GE, Pearson_Corr_GE)
ctrp_cn <- select(subset(filter(dgl_signif_pearson_g2p, Dataset == "CTRP"), Pearson_Pval_CN < 0.05), Drug_Gene_Lin, Pearson_Pval_CN, Pearson_Corr_CN)
ctrp_Pear_n <- nrow(filter(dgl_signif_pearson_g2p, Dataset == "CTRP"))
ctrp_dgl_summ <- merge(ctrp_mut, merge(ctrp_ge, ctrp_cn, by = "Drug_Gene_Lin", all = TRUE), all = TRUE)
ctrp_dgl_summ <- with(ctrp_dgl_summ, cbind(colsplit(Drug_Gene_Lin, pattern = "_", names = c("Drug", "Gene", "Lineage")), 
                                           CTRP_p = p,
                                           CTRP_p_Bonf = ifelse(p < 0.05 / ctrp_mut_n, "Sig", NA),
                                           CTRP_r_GE = Pearson_Corr_GE,
                                           CTRP_p_GE = Pearson_Pval_GE,
                                           CTRP_p_GE_Bonf = ifelse(Pearson_Pval_GE < 0.05 / ctrp_Pear_n, "Sig", NA),
                                           CTRP_r_CN = Pearson_Corr_CN,
                                           CTRP_p_CN = Pearson_Pval_CN,
                                           CTRP_p_CN_Bonf = ifelse(Pearson_Pval_CN < 0.05 / ctrp_Pear_n, "Sig", NA)))

# GDSC mut, n = 39
gdsc_mut <- filter(select(gdsc_signif_g2p_lineage, Drug_Gene_Lin, p), p < 0.05)
gdsc_mut_n <- nrow(select(gdsc_signif_g2p_lineage, Drug_Gene_Lin, p))
# GDSC GE/CN, n = 53
gdsc_ge <- select(subset(filter(dgl_signif_pearson_g2p, Dataset == "GDSC"), Pearson_Pval_GE < 0.05), Drug_Gene_Lin, Pearson_Pval_GE, Pearson_Corr_GE)
gdsc_cn <- select(subset(filter(dgl_signif_pearson_g2p, Dataset == "GDSC"), Pearson_Pval_CN < 0.05), Drug_Gene_Lin, Pearson_Pval_CN, Pearson_Corr_CN)
gdsc_Pear_n <- nrow(filter(dgl_signif_pearson_g2p, Dataset == "GDSC"))
gdsc_dgl_summ <- merge(gdsc_mut, merge(gdsc_ge, gdsc_cn, by = "Drug_Gene_Lin", all = TRUE), all = TRUE)
gdsc_dgl_summ <- with(gdsc_dgl_summ, cbind(colsplit(Drug_Gene_Lin, pattern = "_", names = c("Drug", "Gene", "Lineage")), 
                                           GDSC_p = p,
                                           GDSC_p_Bonf = ifelse(p < 0.05 / gdsc_mut_n, "Sig", NA),
                                           GDSC_r_GE = Pearson_Corr_GE,
                                           GDSC_p_GE = Pearson_Pval_GE,
                                           GDSC_p_GE_Bonf = ifelse(Pearson_Pval_GE < 0.05 / gdsc_Pear_n, "Sig", NA),
                                           GDSC_r_CN = Pearson_Corr_CN,
                                           GDSC_p_CN = Pearson_Pval_CN,
                                           GDSC_p_CN_Bonf = ifelse(Pearson_Pval_CN < 0.05 / gdsc_Pear_n, "Sig", NA)))

g2p_dgl_sig_summ <- merge(merge(ccle_dgl_summ, ctrp_dgl_summ, by = c("Drug", "Gene", "Lineage"), all = TRUE), gdsc_dgl_summ, by = c("Drug", "Gene", "Lineage"), all = TRUE)
```

## GE/CN: Grid

Test all combinations of G2P drugs and genes in all lineages. InG2P indicates G2P drug-gene associations test across all lineages.
```{r, eval=FALSE}
ccle_lineages4pearson <- as.character(unique(ccle_data_g2p_grid$group_general_lineage_name))[!is.na(as.character(unique(ccle_data_g2p_grid$group_general_lineage_name)))]
ccle_signif_ge <- lapply(ccle_lineages4pearson, PearsonByLineage, variable = "GE", dataset = ccle_data_g2p_grid)
ccle_signif_ge_all_lin <- rbindlist(ccle_signif_ge, use.names = TRUE)
ccle_signif_ge_all_lin$Dataset <- "CCLE"
ccle_signif_cn <- lapply(ccle_lineages4pearson, PearsonByLineage, variable = "CN", dataset = ccle_data_g2p_grid)
ccle_signif_cn_all_lin <- rbindlist(ccle_signif_cn, use.names = TRUE)
ccle_signif_cn_all_lin$Dataset <- "CCLE"
ccle_signif_all_lin <- merge(ccle_signif_ge_all_lin, ccle_signif_cn_all_lin, by = c("Drug_Gene", "group_general_lineage_name", "n", "Dataset"), all = TRUE)

ctrp_lineages4pearson <- as.character(unique(ctrp_data_g2p_grid$group_general_lineage_name))[!is.na(as.character(unique(ctrp_data_g2p_grid$group_general_lineage_name)))]
ctrp_signif_ge <- lapply(ctrp_lineages4pearson, PearsonByLineage, variable = "GE", dataset = ctrp_data_g2p_grid)
ctrp_signif_ge_all_lin <- rbindlist(ctrp_signif_ge, use.names = TRUE)
ctrp_signif_ge_all_lin$Dataset <- "CTRP"
ctrp_signif_cn <- lapply(ctrp_lineages4pearson, PearsonByLineage, variable = "CN", dataset = ctrp_data_g2p_grid)
ctrp_signif_cn_all_lin <- rbindlist(ctrp_signif_cn, use.names = TRUE)
ctrp_signif_cn_all_lin$Dataset <- "CTRP"
ctrp_signif_all_lin <- merge(ctrp_signif_ge_all_lin, ctrp_signif_cn_all_lin, by = c("Drug_Gene", "group_general_lineage_name", "n", "Dataset"), all = TRUE)

gdsc_lineages4pearson <- as.character(unique(gdsc_data_g2p_grid$group_general_lineage_name))[!is.na(as.character(unique(gdsc_data_g2p_grid$group_general_lineage_name)))]
gdsc_signif_ge <- lapply(gdsc_lineages4pearson, PearsonByLineage, variable = "GE", dataset = gdsc_data_g2p_grid)
gdsc_signif_ge_all_lin <- rbindlist(gdsc_signif_ge, use.names = TRUE)
gdsc_signif_ge_all_lin$Dataset <- "GDSC"
gdsc_signif_cn <- lapply(gdsc_lineages4pearson, PearsonByLineage, variable = "CN", dataset = gdsc_data_g2p_grid)
gdsc_signif_cn_all_lin <- rbindlist(gdsc_signif_cn, use.names = TRUE)
gdsc_signif_cn_all_lin$Dataset <- "GDSC"
gdsc_signif_all_lin <- merge(gdsc_signif_ge_all_lin, gdsc_signif_cn_all_lin, by = c("Drug_Gene", "group_general_lineage_name", "n", "Dataset"), all = TRUE)

signif_all_lin <- rbind(ccle_signif_all_lin, ctrp_signif_all_lin, gdsc_signif_all_lin)
signif_all_lin$n <- ifelse(is.na(signif_all_lin$n), 0, signif_all_lin$n)
signif_all_lin$InG2P <- ifelse(signif_all_lin$n != 0, "Yes", "No")
signif_all_lin$Drug_Gene_Lin <- paste0(signif_all_lin$Drug_Gene, "_", signif_all_lin$group_general_lineage_name)
saveRDS(signif_all_lin, "./data_munging/rds/dgl_signif_pearson_g2p_grid.rds")
```

```{r}
dgl_signif_pearson_g2p_grid <- readRDS("./data_munging/rds/dgl_signif_pearson_g2p_grid.rds")
```

```{r, results='hide', eval=FALSE}
dgl_pearson_g2p_grid_ttest_res <- lapply(as.character(unique(dgl_signif_pearson_g2p_grid$group_general_lineage_name)), PearsonPlotsByLineage)
dgl_pearson_g2p_grid_ttest_res_list <- rbindlist(dgl_pearson_g2p_grid_ttest_res, use.names = TRUE)
saveRDS(dgl_pearson_g2p_grid_ttest_res_list, "./data_munging/rds/dgl_pearson_g2p_grid_ttest_res_list.rds")
```

```{r}
dgl_pearson_g2p_grid_ttest_res_list <- readRDS("./data_munging/rds/dgl_pearson_g2p_grid_ttest_res_list.rds")

knitr::kable(dgl_pearson_g2p_grid_ttest_res_list[order(dgl_pearson_g2p_grid_ttest_res_list$p_value_GE), c("Dataset", "group_general_lineage_name", "t_statistic_GE", "df_GE", "p_value_GE")], caption = "Gene expression: T-test results for level A G2P drug-gene/gene expression associations across lineages") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")

knitr::kable(dgl_pearson_g2p_grid_ttest_res_list[order(dgl_pearson_g2p_grid_ttest_res_list$p_value_CN), c("Dataset", "group_general_lineage_name", "t_statistic_CN", "df_CN", "p_value_CN")], caption = "Copy number: T-test results for level A G2P drug-gene/gene expression associations across lineages") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

# MUT/GE/CN

--------------------------------------------------------------------------------

## Pancancer

This section contains summary plots for the Wilcoxon tests and Pearson/Spearman correlations done for only level A G2P drug-gene associations (i.e. not the grid tests) and G2P genes in the case of the CRISPR dataset.

### CRISPR

G2P genes with a significant effect on CERES score by mutation status, gene expression, and copy number. Summary plot using Pearson correlation coefficient for GE and CN:
```{r fig.height=5, fig.width=12}
crispr_res_mut <- select(crispr_signif_g2p_gene, Hugo_Symbol, p)
crispr_res_mut$corr <- 0
crispr_res_mut$Metric <- "Mutation Status"
crispr_res_mut$p_log10 <- -log10(crispr_res_mut$p)
subset(crispr_res_mut, p < 0.05)

subset(crispr_pearson_res_GE, p < 0.05)
subset(crispr_pearson_res_CN, p < 0.05)

crispr_pearson_res <- rbind(crispr_pearson_res_GE, crispr_pearson_res_CN)
crispr_pearson_res$Metric <- factor(crispr_pearson_res$Metric, levels = c("Gene Expression", "Copy Number"))
crispr_pearson_res$p_log10 <- -log10(crispr_pearson_res$p)

crispr_summ_res_mut_plot <- ggplot(data = subset(crispr_res_mut, p < 0.05)) +
  facet_grid(~ Metric) +
  scale_y_continuous(breaks = seq(0, 50, by = 5), labels = seq(0, 50, by = 5)) +
  coord_cartesian(ylim = c(0, 50)) +
  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
  geom_label_repel(mapping = aes(y = p_log10, x = corr, label = Hugo_Symbol, color = Metric), force = 10, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
  theme(legend.position = "none", panel.grid.major.x = element_blank(), panel.grid.minor.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(5.5, 1.5, 5.5, 5.5), "pt")) +
  scale_color_manual(values = c("Mutation Status" = "darkorchid4")) +
  labs(y = "-log10(p-value)")

crispr_summ_res_pearson_plot <- ggplot(data = subset(crispr_pearson_res, p < 0.05)) +
  facet_grid(~ Metric, scales = "free_x", space = "free") +
  scale_y_continuous(breaks = seq(0, 50, by = 5), labels = seq(0, 50, by = 5)) +
  scale_x_continuous(breaks = seq(-0.6, 0.3, by = 0.1), labels = formatC(seq(-0.6, 0.3, by = 0.1), digits = 2, format = "f")) +
  coord_cartesian(ylim = c(0, 50)) +
  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
  geom_label_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Hugo_Symbol), force = 10, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
  labs(x = "Pearson correlation coefficient (r)")

crispr_genomic_features_pearson_summ_plot <- plot_grid(crispr_summ_res_mut_plot, crispr_summ_res_pearson_plot, align = "h", rel_widths = c(1, 5))
crispr_genomic_features_pearson_summ_plot

# ggsave("./plots/manuscript/crispr_genomic_features_pearson_summ_plot.png", crispr_genomic_features_pearson_summ_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
```

Summary plot using Spearman correlation coefficient for GE and CN:
```{r fig.height=5, fig.width=12}
subset(crispr_spearman_res_GE, p < 0.05)
subset(crispr_spearman_res_CN, p < 0.05)

crispr_spearman_res <- rbind(crispr_spearman_res_GE, crispr_spearman_res_CN)
crispr_spearman_res$Metric <- factor(crispr_spearman_res$Metric, levels = c("Gene Expression", "Copy Number"))
crispr_spearman_res$p_log10 <- -log10(crispr_spearman_res$p)

crispr_summ_res_spearman_plot <- ggplot(data = subset(crispr_spearman_res, p < 0.05)) +
  facet_grid(~ Metric, scales = "free_x", space = "free") +
  scale_y_continuous(breaks = seq(0, 50, by = 5), labels = seq(0, 50, by = 5)) +
  scale_x_continuous(breaks = seq(-0.6, 0.3, by = 0.1), labels = formatC(seq(-0.6, 0.3, by = 0.1), digits = 2, format = "f")) +
  coord_cartesian(ylim = c(0, 50)) +
  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
  geom_label_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Hugo_Symbol), force = 10, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
  labs(x = "Spearman's rank correlation coefficient (r_s)")

crispr_genomic_features_spearman_summ_plot <- plot_grid(crispr_summ_res_mut_plot, crispr_summ_res_spearman_plot, align = "h", rel_widths = c(1, 5))
crispr_genomic_features_spearman_summ_plot

# ggsave("./plots/manuscript/crispr_genomic_features_spearman_summ_plot.png", crispr_genomic_features_spearman_summ_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
```

### CCLE

G2P drug-gene associations with a significant effect on AUC by mutation status, gene expression, and copy number. Summary plot using Pearson correlation coefficient for GE and CN:
```{r fig.height=4, fig.width=12}
ccle_res_mut <- select(ccle_signif_g2p, Drug_Gene, p)
ccle_res_mut$corr <- 0
ccle_res_mut$Metric <- "Mutation Status"
ccle_res_mut$p_log10 <- -log10(ccle_res_mut$p)
ccle_res_mut$Dataset <- "CCLE"

ccle_pearson_res_GE <- select(filter(ccle_cor_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_GE, Pearson_Pval_GE, Dataset)
colnames(ccle_pearson_res_GE) <- c("Drug_Gene", "corr", "p", "Dataset")
ccle_pearson_res_GE$Metric <- "Gene Expression"
subset(ccle_pearson_res_GE, p < 0.05)

ccle_pearson_res_CN <- select(filter(ccle_cor_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_CN, Pearson_Pval_CN, Dataset)
colnames(ccle_pearson_res_CN) <- c("Drug_Gene", "corr", "p", "Dataset")
ccle_pearson_res_CN$Metric <- "Copy Number"
subset(ccle_pearson_res_CN, p < 0.05)

ccle_pearson_res_filt <- rbind(ccle_pearson_res_GE, ccle_pearson_res_CN)
ccle_pearson_res_filt$Metric <- factor(ccle_pearson_res_filt$Metric, levels = c("Gene Expression", "Copy Number"))
ccle_pearson_res_filt$p_log10 <- -log10(ccle_pearson_res_filt$p)

ccle_summ_res_mut_plot <- ggplot(data = subset(ccle_res_mut, p < 0.05)) +
  facet_grid(Dataset ~ Metric) +
  scale_y_continuous(breaks = seq(0, 35, by = 5), labels = seq(0, 35, by = 5)) +
  coord_cartesian(ylim = c(0, 35)) +
  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
  geom_label_repel(mapping = aes(y = p_log10, x = corr, label = Drug_Gene, color = Metric), force = 10, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
  theme(legend.position = "none", panel.grid.major.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(5.5, 1.5, 5.5, 5.5), "pt"), strip.background.y = element_blank(), strip.text.y = element_blank()) +
  scale_color_manual(values = c("Mutation Status" = "darkorchid4")) +
  labs(y = "-log10(p-value)")

ccle_summ_res_pearson_plot <- ggplot(data = subset(ccle_pearson_res_filt, p < 0.05)) +
  facet_grid(Dataset ~ Metric) +
  coord_cartesian(ylim = c(0, 35)) +
  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
  geom_label_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 10, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
  labs(x = "Pearson correlation coefficient (r)")

ccle_genomic_features_pearson_summ_plot <- plot_grid(ccle_summ_res_mut_plot, ccle_summ_res_pearson_plot, align = "h", rel_widths = c(1, 5))
ccle_genomic_features_pearson_summ_plot

# ggsave("./plots/manuscript/ccle_genomic_features_pearson_summ_plot.png", ccle_genomic_features_pearson_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
```

Summary plot using Spearman correlation coefficient for GE and CN:
```{r fig.height=4, fig.width=12}
ccle_spearman_res_GE <- select(filter(ccle_cor_res, InG2P == "Yes"), Drug_Gene, Spearman_Corr_GE, Spearman_Pval_GE, Dataset)
colnames(ccle_spearman_res_GE) <- c("Drug_Gene", "corr", "p", "Dataset")
ccle_spearman_res_GE$Metric <- "Gene Expression"
subset(ccle_spearman_res_GE, p < 0.05)

ccle_spearman_res_CN <- select(filter(ccle_cor_res, InG2P == "Yes"), Drug_Gene, Spearman_Corr_CN, Spearman_Pval_CN, Dataset)
colnames(ccle_spearman_res_CN) <- c("Drug_Gene", "corr", "p", "Dataset")
ccle_spearman_res_CN$Metric <- "Copy Number"
subset(ccle_spearman_res_CN, p < 0.05)

ccle_spearman_res_filt <- rbind(ccle_spearman_res_GE, ccle_spearman_res_CN)
ccle_spearman_res_filt$Metric <- factor(ccle_spearman_res_filt$Metric, levels = c("Gene Expression", "Copy Number"))
ccle_spearman_res_filt$p_log10 <- -log10(ccle_spearman_res_filt$p)

ccle_summ_res_spearman_plot <- ggplot(data = subset(ccle_spearman_res_filt, p < 0.05)) +
  facet_grid(Dataset ~ Metric) +
  coord_cartesian(ylim = c(0, 35)) +
  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
  geom_label_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 10, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
  labs(x = "Spearman's rank correlation coefficient (r_s)")

ccle_genomic_features_spearman_summ_plot <- plot_grid(ccle_summ_res_mut_plot, ccle_summ_res_spearman_plot, align = "h", rel_widths = c(1, 5))
ccle_genomic_features_spearman_summ_plot

# ggsave("./plots/manuscript/ccle_genomic_features_spearman_summ_plot.png", ccle_genomic_features_spearman_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
```

### CTRP

G2P drug-gene associations with a significant effect on AUC by mutation status, gene expression, and copy number. Summary plot using Pearson correlation coefficient for GE and CN:
```{r fig.height=4, fig.width=12}
ctrp_res_mut <- select(ctrp_signif_g2p, Drug_Gene, p)
ctrp_res_mut$corr <- 0
ctrp_res_mut$Metric <- "Mutation Status"
ctrp_res_mut$p_log10 <- -log10(ctrp_res_mut$p)
ctrp_res_mut$Dataset <- "CTRP"

ctrp_pearson_res_GE <- select(filter(ctrp_cor_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_GE, Pearson_Pval_GE, Dataset)
colnames(ctrp_pearson_res_GE) <- c("Drug_Gene", "corr", "p", "Dataset")
ctrp_pearson_res_GE$Metric <- "Gene Expression"
subset(ctrp_pearson_res_GE, p < 0.05)

ctrp_pearson_res_CN <- select(filter(ctrp_cor_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_CN, Pearson_Pval_CN, Dataset)
colnames(ctrp_pearson_res_CN) <- c("Drug_Gene", "corr", "p", "Dataset")
ctrp_pearson_res_CN$Metric <- "Copy Number"
subset(ctrp_pearson_res_CN, p < 0.05)

ctrp_pearson_res_filt <- rbind(ctrp_pearson_res_GE, ctrp_pearson_res_CN)
ctrp_pearson_res_filt$Metric <- factor(ctrp_pearson_res_filt$Metric, levels = c("Gene Expression", "Copy Number"))
ctrp_pearson_res_filt$p_log10 <- -log10(ctrp_pearson_res_filt$p)

ctrp_summ_res_mut_plot <- ggplot(data = subset(ctrp_res_mut, p < 0.05)) +
  facet_grid(Dataset ~ Metric) +
  scale_y_continuous(breaks = seq(0, 35, by = 5), labels = seq(0, 35, by = 5)) +
  coord_cartesian(ylim = c(0, 35)) +
  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
  geom_text_repel(mapping = aes(y = p_log10, x = corr, label = Drug_Gene, color = Metric), force = 15, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.9) +
  theme(legend.position = "none", panel.grid.major.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(5.5, 1.5, 5.5, 5.5), "pt"), strip.background.y = element_blank(), strip.text.y = element_blank()) +
  scale_color_manual(values = c("Mutation Status" = "darkorchid4")) +
  labs(y = "-log10(p-value)")

ctrp_summ_res_pearson_plot <- ggplot(data = subset(ctrp_pearson_res_filt, p < 0.05)) +
  facet_grid(Dataset ~ Metric) +
  coord_cartesian(ylim = c(0, 35)) +
  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 10, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
  labs(x = "Pearson correlation coefficient (r)")

ctrp_genomic_features_pearson_summ_plot <- plot_grid(ctrp_summ_res_mut_plot, ctrp_summ_res_pearson_plot, align = "h", rel_widths = c(1, 5))
ctrp_genomic_features_pearson_summ_plot

# ggsave("./plots/manuscript/ctrp_genomic_features_pearson_summ_plot.png", ctrp_genomic_features_pearson_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
```

Summary plot using Spearman correlation coefficient for GE and CN:
```{r fig.height=4, fig.width=12}
ctrp_spearman_res_GE <- select(filter(ctrp_cor_res, InG2P == "Yes"), Drug_Gene, Spearman_Corr_GE, Spearman_Pval_GE, Dataset)
colnames(ctrp_spearman_res_GE) <- c("Drug_Gene", "corr", "p", "Dataset")
ctrp_spearman_res_GE$Metric <- "Gene Expression"
subset(ctrp_spearman_res_GE, p < 0.05)

ctrp_spearman_res_CN <- select(filter(ctrp_cor_res, InG2P == "Yes"), Drug_Gene, Spearman_Corr_CN, Spearman_Pval_CN, Dataset)
colnames(ctrp_spearman_res_CN) <- c("Drug_Gene", "corr", "p", "Dataset")
ctrp_spearman_res_CN$Metric <- "Copy Number"
subset(ctrp_spearman_res_CN, p < 0.05)

ctrp_spearman_res_filt <- rbind(ctrp_spearman_res_GE, ctrp_spearman_res_CN)
ctrp_spearman_res_filt$Metric <- factor(ctrp_spearman_res_filt$Metric, levels = c("Gene Expression", "Copy Number"))
ctrp_spearman_res_filt$p_log10 <- -log10(ctrp_spearman_res_filt$p)

ctrp_summ_res_spearman_plot <- ggplot(data = subset(ctrp_spearman_res_filt, p < 0.05)) +
  facet_grid(Dataset ~ Metric) +
  coord_cartesian(ylim = c(0, 35)) +
  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 20, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
  labs(x = "Spearman's rank correlation coefficient (r_s)")

ctrp_genomic_features_spearman_summ_plot <- plot_grid(ctrp_summ_res_mut_plot, ctrp_summ_res_spearman_plot, align = "h", rel_widths = c(1, 5))
ctrp_genomic_features_spearman_summ_plot

# ggsave("./plots/manuscript/ctrp_genomic_features_spearman_summ_plot.png", ctrp_genomic_features_spearman_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
```

### GDSC

G2P drug-gene associations with a significant effect on AUC by mutation status, gene expression, and copy number. Summary plot using Pearson correlation coefficient for GE and CN:
```{r fig.height=4, fig.width=12}
gdsc_res_mut <- select(gdsc_signif_g2p, Drug_Gene, p)
gdsc_res_mut$corr <- 0
gdsc_res_mut$Metric <- "Mutation Status"
gdsc_res_mut$p_log10 <- -log10(gdsc_res_mut$p)
gdsc_res_mut$Dataset <- "GDSC"

gdsc_pearson_res_GE <- select(filter(gdsc_cor_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_GE, Pearson_Pval_GE, Dataset)
colnames(gdsc_pearson_res_GE) <- c("Drug_Gene", "corr", "p", "Dataset")
gdsc_pearson_res_GE$Metric <- "Gene Expression"
subset(gdsc_pearson_res_GE, p < 0.05)

gdsc_pearson_res_CN <- select(filter(gdsc_cor_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_CN, Pearson_Pval_CN, Dataset)
colnames(gdsc_pearson_res_CN) <- c("Drug_Gene", "corr", "p", "Dataset")
gdsc_pearson_res_CN$Metric <- "Copy Number"
subset(gdsc_pearson_res_CN, p < 0.05)

gdsc_pearson_res_filt <- rbind(gdsc_pearson_res_GE, gdsc_pearson_res_CN)
gdsc_pearson_res_filt$Metric <- factor(gdsc_pearson_res_filt$Metric, levels = c("Gene Expression", "Copy Number"))
gdsc_pearson_res_filt$p_log10 <- -log10(gdsc_pearson_res_filt$p)

gdsc_summ_res_mut_plot <- ggplot(data = subset(gdsc_res_mut, p < 0.05)) +
  facet_grid(Dataset ~ Metric) +
  scale_y_continuous(breaks = seq(0, 16, by = 1), labels = seq(0, 16, by = 1)) +
  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
  geom_text_repel(mapping = aes(y = p_log10, x = corr, label = Drug_Gene, color = Metric), force = 15, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.9) +
  theme(legend.position = "none", panel.grid.major.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(5.5, 1.5, 5.5, 5.5), "pt"), strip.background.y = element_blank(), strip.text.y = element_blank()) +
  scale_color_manual(values = c("Mutation Status" = "darkorchid4")) +
  labs(y = "-log10(p-value)")

gdsc_summ_res_pearson_plot <- ggplot(data = subset(gdsc_pearson_res_filt, p < 0.05)) +
  facet_grid(Dataset ~ Metric) +
  scale_y_continuous(breaks = seq(0, 100, by = 10), labels = seq(0, 100, by = 10)) +
  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 10, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
  theme(legend.position = "none", axis.title.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
  labs(x = "Pearson correlation coefficient (r)")

gdsc_genomic_features_pearson_summ_plot <- plot_grid(gdsc_summ_res_mut_plot, gdsc_summ_res_pearson_plot, align = "h", rel_widths = c(1, 5))
gdsc_genomic_features_pearson_summ_plot

# ggsave("./plots/manuscript/gdsc_genomic_features_pearson_summ_plot.png", gdsc_genomic_features_pearson_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
```

Summary plot using Spearman correlation coefficient for GE and CN:
```{r fig.height=4, fig.width=12}
gdsc_spearman_res_GE <- select(filter(gdsc_cor_res, InG2P == "Yes"), Drug_Gene, Spearman_Corr_GE, Spearman_Pval_GE, Dataset)
colnames(gdsc_spearman_res_GE) <- c("Drug_Gene", "corr", "p", "Dataset")
gdsc_spearman_res_GE$Metric <- "Gene Expression"
subset(gdsc_spearman_res_GE, p < 0.05)

gdsc_spearman_res_CN <- select(filter(gdsc_cor_res, InG2P == "Yes"), Drug_Gene, Spearman_Corr_CN, Spearman_Pval_CN, Dataset)
colnames(gdsc_spearman_res_CN) <- c("Drug_Gene", "corr", "p", "Dataset")
gdsc_spearman_res_CN$Metric <- "Copy Number"
subset(gdsc_spearman_res_CN, p < 0.05)

gdsc_spearman_res_filt <- rbind(gdsc_spearman_res_GE, gdsc_spearman_res_CN)
gdsc_spearman_res_filt$Metric <- factor(gdsc_spearman_res_filt$Metric, levels = c("Gene Expression", "Copy Number"))
gdsc_spearman_res_filt$p_log10 <- -log10(gdsc_spearman_res_filt$p)

gdsc_summ_res_spearman_plot <- ggplot(data = subset(gdsc_spearman_res_filt, p < 0.05)) +
  facet_grid(Dataset ~ Metric) +
  scale_y_continuous(breaks = seq(0, 50, by = 5), labels = seq(0, 50, by = 5)) +
  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 20, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
  labs(x = "Spearman's rank correlation coefficient (r_s)")

gdsc_genomic_features_spearman_summ_plot <- plot_grid(gdsc_summ_res_mut_plot, gdsc_summ_res_spearman_plot, align = "h", rel_widths = c(1, 5))
gdsc_genomic_features_spearman_summ_plot

# ggsave("./plots/manuscript/gdsc_genomic_features_spearman_summ_plot.png", gdsc_genomic_features_spearman_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
```

### Drug: Mut

G2P drug-gene associations with a significant effect on AUC by mutation status:
```{r fig.height=4, fig.width=8}
all_mut_res <- rbind(ccle_res_mut, ctrp_res_mut, gdsc_res_mut)

all_mut_summ_plot <- ggplot(data = subset(all_mut_res, p < 0.05)) +
  facet_grid(~ Dataset) +
  geom_point(aes(x = corr, y = p_log10, color = Dataset), alpha = 0.5) +
  scale_y_continuous(breaks = seq(0, 12, by = 2), labels = seq(0, 12, by = 2)) +
  scale_x_continuous(breaks = seq(0, 0.1, by = 0.1), labels = seq(0, 0.1, by = 0.1)) +
  coord_cartesian(xlim = c(0, 0.05)) +
  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Dataset, label = Drug_Gene), nudge_x = 0.05, direction = "y", hjust = 0, size = 2.5, segment.size = 0.1, segment.colour = "grey50", box.padding = 0.6) +
  scale_color_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
  theme(legend.position = "none", plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt"), panel.grid.major.x = element_blank(), panel.grid.minor.x = element_blank(), axis.title.x = element_blank(), axis.ticks.x = element_blank(), axis.text.x = element_blank()) +
  labs(y = "-log10(p-value)")
all_mut_summ_plot

# ggsave("./plots/manuscript/all_mut_summ_plot.png", all_mut_summ_plot, device = "png", dpi = 450, width = 12, height = 6, units = "in")
```

### Drug: GE and CN

G2P drug-gene associations with a significant effect on AUC by gene expression and copy number:
```{r fig.height=12, fig.width=12}
all_pearson_res <- rbind(ccle_pearson_res_filt, ctrp_pearson_res_filt, gdsc_pearson_res_filt)
all_pearson_summ_plot <- ggplot(data = subset(all_pearson_res, p < 0.05)) +
  facet_grid(Dataset ~ Metric, scales = "free", space = "free") +
  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
  geom_point(aes(x = corr, y = p_log10, color = Dataset), alpha = 0.5) +
  scale_y_continuous(breaks = seq(0, 60, by = 10), labels = seq(0, 60, by = 10)) +
  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Dataset, label = Drug_Gene), force = 10, nudge_y = 3, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
  scale_color_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
  theme(legend.position = "none", plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
  labs(x = "Pearson correlation coefficient (r)", y = "-log10(p-value)")
all_pearson_summ_plot
# ggsave("./plots/manuscript/all_pearson_summ_plot.png", all_pearson_summ_plot, device = "png", dpi = 450, width = 12, height = 10, units = "in")

all_spearman_res <- rbind(ccle_spearman_res_filt, ctrp_spearman_res_filt, gdsc_spearman_res_filt)
all_spearman_summ_plot <- ggplot(data = subset(all_spearman_res, p < 0.05)) +
  facet_grid(Dataset ~ Metric, scales = "free", space = "free") +
  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
  geom_point(aes(x = corr, y = p_log10, color = Dataset), alpha = 0.5) +
  scale_y_continuous(breaks = seq(0, 60, by = 10), labels = seq(0, 60, by = 10)) +
  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Dataset, label = Drug_Gene), force = 10, nudge_y = 1, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
  scale_color_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
  theme(legend.position = "none", plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
  labs(x = "Pearson correlation coefficient (r)", y = "-log10(p-value)")
all_spearman_summ_plot
# ggsave("./plots/manuscript/all_spearman_summ_plot.png", all_spearman_summ_plot, device = "png", dpi = 450, width = 12, height = 10, units = "in")
```

### Drug: P-values

```{r fig.height=6, fig.width=12}
pval_summ_mut <- g2p_mut_all_summ
pval_summ_mut$Measure <- "Mutation Status"
pval_summ_mut$Drug_Gene_Ordered <- NULL

pval_summ_ge <- select(g2p_cor, Drug_Gene, n, Pearson_Pval_GE, InG2P, Dataset)
colnames(pval_summ_ge)[colnames(pval_summ_ge) == "Pearson_Pval_GE"] <- "p"
pval_summ_ge$p_log10 <- -log10(pval_summ_ge$p)
pval_summ_ge$Measure <- "Gene Expression"

pval_summ_cn <- select(g2p_cor, Drug_Gene, n, Pearson_Pval_CN, InG2P, Dataset)
colnames(pval_summ_cn)[colnames(pval_summ_cn) == "Pearson_Pval_CN"] <- "p"
pval_summ_cn$p_log10 <- -log10(pval_summ_cn$p)
pval_summ_cn$Measure <- "Copy Number"

pval_summ <- rbind(pval_summ_mut, pval_summ_ge, pval_summ_cn)
pval_summ$Measure <- factor(pval_summ$Measure, levels = c("Mutation Status", "Gene Expression", "Copy Number"))

pval_summ_plot <- ggplot(data = pval_summ, aes(x = p_log10, y = n, color = Dataset, shape = Dataset, label = Drug_Gene)) +
  facet_wrap(~ Measure, scales = "free_x") +
  geom_point(alpha = 0.7) +
  scale_color_manual(values = c("green3", "darkslategray4", "darkturquoise")) +
  geom_text_repel(data = filter(pval_summ, n > 20 & Measure == "Mutation Status"), mapping = aes(x = p_log10, y = n, color = Dataset, label = Drug_Gene), direction = "y", nudge_x = 9, hjust = 0, size = 2.5, segment.size = 0.1, segment.colour = "grey50", box.padding = 0.6, show.legend = FALSE) +
  geom_text_repel(data = filter(pval_summ, n > 20 & Measure == "Gene Expression"), mapping = aes(x = p_log10, y = n, color = Dataset, label = Drug_Gene), direction = "y", nudge_x = 50, hjust = 0, size = 2.5, segment.size = 0.1, segment.colour = "grey50", box.padding = 0.6, show.legend = FALSE) +
  geom_text_repel(data = filter(pval_summ, n > 20 & Measure == "Copy Number"), mapping = aes(x = p_log10, y = n, color = Dataset, label = Drug_Gene), direction = "y", nudge_x = 20, hjust = 0, size = 2.5, segment.size = 0.1, segment.colour = "grey50", box.padding = 0.6, show.legend = FALSE) +
  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
  labs(x = "-log10(p-value)", y = "Number of level A G2P associations") +
  theme(legend.position = "bottom")
pval_summ_plot

# ggsave("./plots/manuscript/all_pval_summ_plot.png", pval_summ_plot, device = "png", dpi = 450, width = 12, height = 6, units = "in")

pval_summ_plot2 <- ggplot(data = pval_summ, aes(x = p_log10, y = n, color = Dataset, shape = Dataset, label = Drug_Gene)) +
  facet_wrap(~ Measure, scales = "free_x") +
  geom_point(alpha = 0.7) +
  scale_color_manual(values = c("green3", "darkslategray4", "darkturquoise")) +
  geom_text_repel(data = filter(pval_summ, p_log10 > 5 & Measure == "Mutation Status"), mapping = aes(x = p_log10, y = n, color = Dataset, label = Drug_Gene), direction = "y", nudge_y = 10, hjust = 0, size = 2.5, segment.size = 0.1, segment.colour = "grey50", box.padding = 0.6, show.legend = FALSE) +
  geom_text_repel(data = filter(pval_summ, p_log10 > 20 & Measure == "Gene Expression"), mapping = aes(x = p_log10, y = n, color = Dataset, label = Drug_Gene), direction = "y", nudge_y = 10, hjust = 0, size = 2.5, segment.size = 0.1, segment.colour = "grey50", box.padding = 0.6, show.legend = FALSE) +
  geom_text_repel(data = filter(pval_summ, p_log10 > 7.5 & Measure == "Copy Number"), mapping = aes(x = p_log10, y = n, color = Dataset, label = Drug_Gene), direction = "y", nudge_y = 10, hjust = 0, size = 2.5, segment.size = 0.1, segment.colour = "grey50", box.padding = 0.6, show.legend = FALSE) +
  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
  labs(x = "-log10(p-value)", y = "Number of level A G2P associations") +
  theme(legend.position = "bottom")
pval_summ_plot2

# ggsave("./plots/manuscript/all_pval_summ_plot2.png", pval_summ_plot2, device = "png", dpi = 450, width = 12, height = 6, units = "in")
```

### Summary stats

```{r}
# Mutation status
g2p_mut_all_summ_stats <- g2p_mut_all_summ
g2p_mut_all_summ_stats$n_true <- TRUE
g2p_mut_all_summ_stats <- g2p_mut_all_summ_stats %>% drop_na(p) %>% group_by(Dataset, InG2P) %>% summarize(p_mean = round(mean(p), 2), p_sd = round(sd(p), 2), n = sum(n_true), n_signif = sum(p < 0.05), n_sig_perc = n_signif / n * 100)

# Pearson correlations
g2p_cor_stats <- g2p_cor
g2p_cor_stats$n_true <- TRUE
g2p_cor_stats <- g2p_cor_stats %>% group_by(Dataset, InG2P) %>% drop_na() %>% summarize(
          ge_mean = round(mean(Pearson_GE_Abs), 5),
          ge_sd = round(sd(Pearson_GE_Abs), 5),
          ge_n = sum(n_true),
          ge_n_signif = sum(Pearson_Pval_GE < 0.05),
          ge_n_sig_perc = ge_n_signif / ge_n * 100,
          cn_mean = round(mean(Pearson_CN_Abs), 3),
          cn_sd = round(sd(Pearson_CN_Abs), 5),
          cn_n = sum(n_true),
          cn_n_signif = sum(Pearson_Pval_CN < 0.05),
          cn_n_sig_perc = cn_n_signif / cn_n * 100)
```

### CTRP example derivation

Example p-value and Pearson correlation coefficient derivations for afatinib and ERBB2 in the CTRP dataset:
```{r}
ctrp_grid_summary_data <- filter(ctrp_data_g2p_grid, Drug_Gene == "afatinib_ERBB2")

ctrp_grid_summary_mut_corr <- wilcox.test(AUC_zscore ~ Mutation_Status_Nonsilent, data = ctrp_grid_summary_data[!is.na(ctrp_grid_summary_data$Mutation_Status_Nonsilent),], paired = FALSE)
ctrp_grid_summary_mut_corr_text <- paste0("W = ", formatC(ctrp_grid_summary_mut_corr$statistic, format = "d", big.mark = ","), "\np = ", round(ctrp_grid_summary_mut_corr$p.value, 3))

ctrp_grid_summary_ge_corr <- cor.test(y = ctrp_grid_summary_data$AUC, x = ctrp_grid_summary_data$RPKM, method = "pearson", use = "complete.obs")
ctrp_grid_summary_ge_corr_text <- paste0("r(", ctrp_grid_summary_ge_corr$parameter, ") = ", round(ctrp_grid_summary_ge_corr$estimate, 2), "\np ", ifelse(round(ctrp_grid_summary_ge_corr$p.value, 3) == 0, "< 0.001", paste0("= ", round(ctrp_grid_summary_ge_corr$p.value, 3))))

ctrp_grid_summary_cn_corr <- cor.test(y = ctrp_grid_summary_data$AUC, x = ctrp_grid_summary_data$CN, method = "pearson", use = "complete.obs")
ctrp_grid_summary_cn_corr_text <- paste0("r(", ctrp_grid_summary_cn_corr$parameter, ") = ", formatC(ctrp_grid_summary_cn_corr$estimate, digits = 2, format = "f"), "\np ", ifelse(round(ctrp_grid_summary_cn_corr$p.value, 3) == 0, "< 0.001", paste0("= ", round(ctrp_grid_summary_cn_corr$p.value, 3))))

ctrp_grid_summary_mut_plot <- ggplot(data = ctrp_grid_summary_data[!is.na(ctrp_grid_summary_data$Mutation_Status_Nonsilent),], aes(y = AUC_zscore, x = Mutation_Status_Nonsilent, fill = Mutation_Status_Nonsilent)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.6) +
  geom_jitter(width = 0.2, shape = 21) +
  scale_fill_manual(values = c("Wildtype" = "lightsteelblue1", "Mutant" = "steelblue4")) +
  annotate(geom = "text", label = ctrp_grid_summary_mut_corr_text, x = 1.5, y = 1.3) +
  guides(fill = FALSE) +
  labs(x = "ERBB2 mutation status", y = "Afatinib AUC (z-score)") +
  geom_segment(aes(x = 1, y = 1.5, xend = 1.1, yend = 1.5), lwd = 0.2) +
  geom_segment(aes(x = 1.9, y = 1.5, xend = 2, yend = 1.5), lwd = 0.2) +
  geom_segment(aes(x = 1, y = 1.5, xend = 1, yend = 1.35), lwd = 0.2) +
  geom_segment(aes(x = 2, y = 1.5, xend = 2, yend = 1.35), lwd = 0.2)
ctrp_grid_summary_mut_plot

ctrp_grid_summary_ge_plot <- ggplot(data = ctrp_grid_summary_data, aes(y = AUC_zscore, x = RPKM)) +
  geom_point(alpha = 0.25, size = 1.25, color = "gray4") +
  geom_smooth(method = "lm", se = FALSE, lwd = 0.5, lty = 2) +
  annotate(geom = "text", label = ctrp_grid_summary_ge_corr_text, x = 2000, y = 1.3) +
  labs(x = "ERBB2 gene expression (RPKM)", y = "Afatinib AUC (z-score)") +
  theme(axis.title.y = element_blank()) +
  geom_curve(aes(x = 750, y = -1.9, xend = 1720, yend = 1.1), lwd = 0.2, curvature = -0.2, arrow = arrow(length = unit(0.03, "npc")))
ctrp_grid_summary_ge_plot

ctrp_grid_summary_cn_plot <- ggplot(data = ctrp_grid_summary_data, aes(y = AUC_zscore, x = CN)) +
  geom_point(alpha = 0.25, size = 1.25, color = "gray4") +
  geom_smooth(method = "lm", se = FALSE, lwd = 0.5, lty = 2) +
  annotate(geom = "text", label = ctrp_grid_summary_cn_corr_text, x = 5, y = 1.3) +
  labs(x = "ERBB2 copy number (log2 ratio)") +
  theme(axis.title.y = element_blank()) +
  geom_curve(aes(x = 4, y = -2.3, xend = 5, yend = 0.8), lwd = 0.2, curvature = 0.2, arrow = arrow(length = unit(0.03, "npc")))
ctrp_grid_summary_cn_plot

# ggsave("./plots/manuscript/ctrp_grid_summary_mut_plot.png", ctrp_grid_summary_mut_plot, device = "png", dpi = 450, width = 3, height = 4, units = "in")
# ggsave("./plots/manuscript/ctrp_grid_summary_ge_plot.png", ctrp_grid_summary_ge_plot, device = "png", dpi = 450, width = 5, height = 4, units = "in")
# ggsave("./plots/manuscript/ctrp_grid_summary_cn_plot.png", ctrp_grid_summary_cn_plot, device = "png", dpi = 450, width = 5, height = 4, units = "in")
```

## By lineage

### Kolmogorov-Smirnov tests

```{r}
MakeCorrResSummaryTable <- function(df_list, dataset_name) {
  res_full <- data.frame(matrix(ncol = 8, nrow = 0))
  for(i in 1:length(df_list)) {
    corr_res <- df_list[[i]] %>% group_by(G2P_DGL) %>% summarize(Dataset = dataset_name,
                Drug_Gene = names(df_list)[i],
                Lineages = paste(as.character(unique(group_general_lineage_name)), collapse = ", "),
                N_Lineages = length(as.character(unique(group_general_lineage_name))),
                Pearson_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
                Pearson_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$estimate,
                Spearman_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
                Spearman_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$estimate)
    corr_res <- merge(corr_res, compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, data = df_list[[i]], group.by = "G2P_DGL", method = "wilcox.test")[, c("G2P_DGL", "p")], by = "G2P_DGL", all = TRUE)
    corr_res$Mut_Signif <- ifelse(corr_res$p < 0.05, 1, 0)
    res_full <- rbind(res_full, corr_res)
  }
  return(res_full)
}
```

```{r}
ccle_data_g2p$G2P_DGL <- ifelse(ccle_data_g2p$Drug_Gene_Lin %in% g2p_dgls, "Yes", "No")
ccle_data_g2p_split <- split(ccle_data_g2p, f = ccle_data_g2p$Drug_Gene)
ccle_corr_all <- MakeCorrResSummaryTable(ccle_data_g2p_split, dataset_name = "CCLE")

ctrp_data_g2p$G2P_DGL <- ifelse(ctrp_data_g2p$Drug_Gene_Lin %in% g2p_dgls, "Yes", "No")
ctrp_data_g2p_split <- split(ctrp_data_g2p, f = ctrp_data_g2p$Drug_Gene)
ctrp_corr_all <- MakeCorrResSummaryTable(ctrp_data_g2p_split, dataset_name = "CTRP")

gdsc_data_g2p$G2P_DGL <- ifelse(gdsc_data_g2p$Drug_Gene_Lin %in% g2p_dgls, "Yes", "No")
gdsc_data_g2p_split <- split(gdsc_data_g2p, f = gdsc_data_g2p$Drug_Gene)
gdsc_corr_all <- MakeCorrResSummaryTable(gdsc_data_g2p_split, dataset_name = "GDSC")

g2p_corr_all <- rbind(ccle_corr_all, ctrp_corr_all, gdsc_corr_all)
```

```{r}
G2PCorr_KStest <- function(dataset, dataset_name) {
  Metric <- colnames(dataset)[6:9]
  D_stat <- NULL
  pval <- NULL
  signif <- NULL

  yes <- dataset[dataset$G2P_DGL == "Yes",]
  no <- dataset[dataset$G2P_DGL == "No",]

  for(i in 6:9) {
    # print(yes[[colnames(yes)[i]]])
    # print(no[[colnames(no)[i]]])
    test <- ks.test(yes[[colnames(yes)[i]]], no[[colnames(no)[i]]])
    D_stat <- c(D_stat, test$statistic)
    pval <- c(pval, test$p.value)
    signif <- c(signif, ifelse(test$p.value < 0.001, "***", ifelse(test$p.value < 0.01, "**", ifelse(test$p.value < 0.05, "*", NA))))
  }
  df <- data.frame(Metric, D_stat, pval, signif)
  df$Dataset <- dataset_name
  return(df)
}
```

```{r}
ccle_corr_stats <- G2PCorr_KStest(ccle_corr_all, "CCLE")
ctrp_corr_stats <- G2PCorr_KStest(ctrp_corr_all, "CTRP")
gdsc_corr_stats <- G2PCorr_KStest(gdsc_corr_all, "GDSC")
g2p_corr_stats <- rbind(ccle_corr_stats, ctrp_corr_stats, gdsc_corr_stats)
g2p_corr_stats

g2p_mut_stats <- g2p_corr_all %>% group_by(Dataset, G2P_DGL) %>% drop_na(Mut_Signif) %>% summarize(N_Signif_Muts = sum(Mut_Signif),
                                                                                                   Total_Tests = length(Mut_Signif),
                                                                                                   Perc_Signif = N_Signif_Muts / Total_Tests * 100)
g2p_mut_stats
```

### Grid t-test summaries

Figure #. Histograms of p-values from t-tests comparing distributions of summary statistics for CCLE, CTRP, and GDSC drug screen results in the context of G2P level A evidence and lineage. Each p-value is derived from comparisons similar to those shown in Figure 2, but for these p-values, the data is grouped by lineage prior to conducting the t-test rather than the test being lineage-agnostic. To produce these p-values, AUC was correlated with each genomic feature for all possible pairwise combinations of G2P drugs and genes in all lineages represented in each dataset. For each lineage, t-tests were used to compare distributions of p-values (mutation status) or Pearson correlation coefficients (gene expression and copy number) that were grouped by whether or not the underlying drug-gene combination had level-A G2P evidence. For each dataset, if there were two or more correlation results in each G2P presence/absence group in a specific lineage, a t-test was conducted and the p-value appears in the appropriate histogram. Mutation status histograms are sparse due to limited mutation annotations for many of the G2P genes in all screened cell lines.
```{r fig.height=4, fig.width=12}
ttest_summ_res_mut <- dgl_mut_g2p_grid_ttest_res_list[, c("p_value", "Dataset", "group_general_lineage_name")]
ttest_summ_res_mut$Metric <- "Mutation Status"

ttest_summ_res_ge <- dgl_pearson_g2p_grid_ttest_res_list[, c("p_value_GE", "Dataset", "group_general_lineage_name")]
colnames(ttest_summ_res_ge) <- c("p_value", "Dataset", "group_general_lineage_name")
ttest_summ_res_ge$Metric <- "Gene Expression"

ttest_summ_res_cn <- dgl_pearson_g2p_grid_ttest_res_list[, c("p_value_CN", "Dataset", "group_general_lineage_name")]
colnames(ttest_summ_res_cn) <- c("p_value", "Dataset", "group_general_lineage_name")
ttest_summ_res_cn$Metric <- "Copy Number"

ttest_summ_res <- rbind(ttest_summ_res_mut, ttest_summ_res_ge, ttest_summ_res_cn)
ttest_summ_res$Metric <- factor(ttest_summ_res$Metric, levels = c("Mutation Status", "Gene Expression", "Copy Number"))

ttest_mut_summ_facet <- ggplot(data = ttest_summ_res, aes(x = p_value, fill = Dataset, color = Dataset)) +
  facet_grid(Metric ~ Dataset) +
  geom_histogram(bins = 40, binwidth = 0.025, boundary = 0, closed = "left") +
  scale_y_continuous(breaks = c(0:6), labels = c(0:6)) +
  scale_x_continuous(breaks = seq(0, 1, by = 0.1), expand = c(0.01, 0.01)) +
  scale_fill_manual(values = c("CCLE" = "palegreen3", "CTRP" = "slategray3", "GDSC" = "paleturquoise3")) +
  scale_color_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
  theme(legend.position = c(0.5, 1.7), legend.direction = "horizontal", panel.grid.minor.y = element_blank()) +
  labs(x = "P-value", y = "Frquency")
ttest_mut_summ_facet

# ggsave("./plots/manuscript/all_dgl_ttest_summ_facet_plot.png", ttest_mut_summ_facet, device = "png", dpi = 450, width = 12, height = 4, units = "in")
```

Big grid plot by lineages:
```{r fig.height=20, fig.width=12}
dgl_mut <- dgl_mut_grid_summ
dgl_mut$Sign <- "None"
dgl_mut$Measure <- "Mutation Status"
colnames(dgl_mut)[colnames(dgl_mut) == "p"] <- "Statistic"
dgl_mut$Drug_Gene_Lin <- NULL

dgl_ge <- select(dgl_signif_pearson_g2p_grid, Drug_Gene, group_general_lineage_name, n, Pearson_GE_Abs, InG2P, Dataset, Pearson_GE_Sign)
dgl_ge$Measure <- "Gene Expression"
colnames(dgl_ge)[colnames(dgl_ge) == "Pearson_GE_Abs"] <- "Statistic"
colnames(dgl_ge)[colnames(dgl_ge) == "Pearson_GE_Sign"] <- "Sign"

dgl_cn <- select(dgl_signif_pearson_g2p_grid, Drug_Gene, group_general_lineage_name, n, Pearson_CN_Abs, InG2P, Dataset, Pearson_CN_Sign)
dgl_cn$Measure <- "Copy Number"
colnames(dgl_cn)[colnames(dgl_cn) == "Pearson_CN_Abs"] <- "Statistic"
colnames(dgl_cn)[colnames(dgl_cn) == "Pearson_CN_Sign"] <- "Sign"

dgl_all <- rbind(dgl_mut, dgl_ge, dgl_cn)
dgl_all$Sign <- ifelse(is.na(dgl_all$Sign), "None", dgl_all$Sign)

dgl_all_plot <- ggplot(data = dgl_all, aes(x = InG2P, y = Statistic)) +
  facet_grid(group_general_lineage_name ~ Measure * Dataset) +
  geom_jitter(mapping = aes(shape = Sign, fill = InG2P, color = InG2P), width = 0.4, alpha = 0.5, size = 1) +
  geom_boxplot(width = 0.25, fill = NA, outlier.shape = NA) +
  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
  scale_shape_manual(values = c(25, 24, 4), labels = c("Negative", "Positive", "NA")) +
  theme(legend.position = "top") +
  guides(color = FALSE, fill = FALSE)

# ggsave("./plots/manuscript/all_dgl_plot.png", dgl_all_plot, device = "png", dpi = 450, width = 12, height = 40, units = "in")
```

## Cell line overlap

```{r, eval=FALSE}
crispr_ccl <- unique(select(crispr_data, DepMap_ID, CCLE_Name))
ccle_ccl <- unique(select(ccle_data, DepMap_ID, CCLE_Name, accession_id))
ctrp_ccl <- unique(select(ctrp_data, DepMap_ID, CCLE_Name, accession_id))
gdsc_ccl <- unique(select(gdsc_data, DepMap_ID, CCLE_Name, accession_id))
# all_ccl <- merge(ccle_ccl, ctrp_ccl, by = c("DepMap_ID", "CCLE_Name", "accession_id"), all = TRUE)
```

# OLD: BOXPLOTS

--------------------------------------------------------------------------------

Mutation status boxplots for genes identified in G2P.

## G2P genes

Boxplots ordered by gene based on frequency of G2P associations.

### CRISPR

```{r fig.height=5, fig.width=20}
crispr_data_g2p$Hugo_Symbol <- factor(crispr_data_g2p$Hugo_Symbol, levels = g2p_genes)
crispr_data_g2p_color <- as.character(crispr_data_g2p$Color_Nonsilent)
names(crispr_data_g2p_color) <- crispr_data_g2p$Mutation_Status_Nonsilent
crispr_label_text <- data.frame(p.signif.adj = crispr_signif_g2p_gene$p.signif.adj, p.signif = crispr_signif_g2p_gene$p.signif, Hugo_Symbol = crispr_signif_g2p_gene$Hugo_Symbol)
crispr_label_text <- filter(crispr_label_text, Hugo_Symbol %in% g2p_genes)
crispr_label_text$Hugo_Symbol <- factor(crispr_label_text$Hugo_Symbol, levels = g2p_genes)
crispr_data_g2p_plot <- ggplot(data = crispr_data_g2p, aes(x = Mutation_Status_Nonsilent, y = Score)) +
  facet_wrap(~ Hugo_Symbol, drop = FALSE, nrow = 1) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  geom_boxplot(mapping = aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85)) +
  scale_fill_manual(values = crispr_data_g2p_color) +
  guides(color = FALSE) +
  geom_text(data = crispr_label_text, mapping = aes(x = 1.5, y = 2, label = p.signif), nudge_y = 0.1) +
  theme(strip.text.x = element_text(size = 10, angle = 45), legend.position = "top", axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
  labs(title = "CRISPR", fill = "Mutation Status", y = "CERES Score", x = "Mutation Status")
crispr_data_g2p_plot

# ggsave("./plots/manuscript/crispr_data_g2p_plot.png", crispr_data_g2p_plot, device = "png", dpi = 450, width = 20, height = 5, units = "in")
```

### CCLE

Plot code:
```{r, eval=FALSE}
ccle_drugs <- as.character(unique(ccle_data_ptmuts$Drug))
ccle_g2p_drugboxplots <- lapply(ccle_drugs, makeDrugBoxplots, dataset = "CCLE")
ccle_g2p_drugboxplots_paths <- paste0(ccle_drugs, "_ccle_drugboxplots.png")
pwalk(list(ccle_g2p_drugboxplots_paths, ccle_g2p_drugboxplots), ggsave, path = "./plots/manuscript/ccle_g2p_drugboxplots", dpi = 450, width = 20, height = 5, units = "in")
```

Data management:
```{r, eval=FALSE}
ccle_g2p_drugboxplots <- paste0(list.files("./plots/manuscript/ccle_g2p_drugboxplots", full.names = TRUE))
names(ccle_g2p_drugboxplots) <- str_replace_all(ccle_g2p_drugboxplots, c("_ccle_drugboxplots.png" = "", "./plots/manuscript/ccle_g2p_drugboxplots/" = ""))
bsselect(ccle_g2p_drugboxplots, type = "img", live_search = TRUE, show_tick = TRUE, height = 100)
```

### CTRP

Plot code:
```{r, eval=FALSE}
ctrp_drugs <- as.character(unique(ctrp_data_ptmuts$Drug))
ctrp_g2p_drugboxplots <- lapply(ctrp_drugs, makeDrugBoxplots, dataset = "ctrp")
ctrp_g2p_drugboxplots_paths <- paste0(ctrp_drugs, "_ctrp_drugboxplots.png")
pwalk(list(ctrp_g2p_drugboxplots_paths, ctrp_g2p_drugboxplots), ggsave, path = "./plots/manuscript/ctrp_g2p_drugboxplots", dpi = 450, width = 20, height = 5, units = "in")
```

Data management:
```{r, eval=FALSE}
ctrp_g2p_drugboxplots <- paste0(list.files("./plots/manuscript/ctrp_g2p_drugboxplots", full.names = TRUE))
names(ctrp_g2p_drugboxplots) <- str_replace_all(ctrp_g2p_drugboxplots, c("_ctrp_drugboxplots.png" = "", "./plots/manuscript/ctrp_g2p_drugboxplots/" = ""))
bsselect(ctrp_g2p_drugboxplots, type = "img", live_search = TRUE, show_tick = TRUE, height = 100)
```

### GDSC

Plot code:
```{r, eval=FALSE}
gdsc_drugs <- as.character(unique(gdsc_data_ptmuts$Drug))
gdsc_g2p_drugboxplots <- lapply(gdsc_drugs, makeDrugBoxplots, dataset = "gdsc")
gdsc_g2p_drugboxplots_paths <- paste0(gdsc_drugs, "_gdsc_drugboxplots.png")
pwalk(list(gdsc_g2p_drugboxplots_paths, gdsc_g2p_drugboxplots), ggsave, path = "./plots/manuscript/gdsc_g2p_drugboxplots", dpi = 450, width = 20, height = 5, units = "in")
```

Data management:
```{r, eval=FALSE}
gdsc_g2p_drugboxplots <- paste0(list.files("./plots/manuscript/gdsc_g2p_drugboxplots", full.names = TRUE))
names(gdsc_g2p_drugboxplots) <- str_replace_all(gdsc_g2p_drugboxplots, c("_gdsc_drugboxplots.png" = "", "./plots/manuscript/gdsc_g2p_drugboxplots/" = ""))
bsselect(gdsc_g2p_drugboxplots, type = "img", live_search = TRUE, show_tick = TRUE, height = 100)
```

## G2P level A drug-gene associations only

### CCLE

```{r fig.height=4, fig.width=12}
ccle_g2p_order <- as.character(ccle_signif_g2p$Drug_Gene)
ccle_data_g2p$Drug_Gene_Ordered <- factor(ccle_data_g2p$Drug_Gene, levels = ccle_g2p_order, labels = sapply(strsplit(x = ccle_g2p_order, split = "_"), function(x) paste0(x[1], "\n", x[2])))
ccle_signif_g2p$Drug_Gene_Ordered <- factor(ccle_signif_g2p$Drug_Gene, levels = ccle_g2p_order, labels = sapply(strsplit(x = ccle_g2p_order, split = "_"), function(x) paste0(x[1], "\n", x[2])))
ccle_data_g2p_color <- as.character(ccle_data_g2p$Color_Nonsilent)
names(ccle_data_g2p_color) <- ccle_data_g2p$Mutation_Status_Nonsilent
ccle_label_text <- data.frame(p.signif.adj = ccle_signif_g2p$p.signif.adj, p.signif = ccle_signif_g2p$p.signif, Drug_Gene_Ordered = ccle_signif_g2p$Drug_Gene_Ordered)
ccle_data_g2p_plot <- ggplot(data = ccle_data_g2p, aes(x = Mutation_Status_Nonsilent, y = AUC)) +
  facet_wrap(~ Drug_Gene_Ordered, drop = FALSE, nrow = 1) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  geom_boxplot(mapping = aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85), outlier.shape = 3, outlier.size = 0.5) +
  scale_fill_manual(values = ccle_data_g2p_color) +
  guides(color = FALSE) +
  geom_text(data = ccle_label_text, mapping = aes(x = 1.5, y = 7, label = p.signif), nudge_y = 0.1) +
  theme(legend.position = "top", axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
  labs(title = "CCLE", fill = "Mutation Status", y = "AUC", x = "Mutation Status")
ccle_data_g2p_plot

# ggsave("./plots/manuscript/ccle_data_g2p_plot.png", ccle_data_g2p_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
```

### CTRP

```{r fig.height=7, fig.width=12}
ctrp_g2p_order <- as.character(ctrp_signif_g2p$Drug_Gene)
ctrp_data_g2p$Drug_Gene_Ordered <- factor(ctrp_data_g2p$Drug_Gene, levels = ctrp_g2p_order, labels = sapply(strsplit(x = ctrp_g2p_order, split = "_"), function(x) paste0(x[1], "\n", x[2])))
ctrp_signif_g2p$Drug_Gene_Ordered <- factor(ctrp_signif_g2p$Drug_Gene, levels = ctrp_g2p_order, labels = sapply(strsplit(x = ctrp_g2p_order, split = "_"), function(x) paste0(x[1], "\n", x[2])))
ctrp_data_g2p_color <- as.character(ctrp_data_g2p$Color_Nonsilent)
names(ctrp_data_g2p_color) <- ctrp_data_g2p$Mutation_Status_Nonsilent
ctrp_label_text <- data.frame(p.signif.adj = ctrp_signif_g2p$p.signif.adj, p.signif = ctrp_signif_g2p$p.signif, Drug_Gene_Ordered = ctrp_signif_g2p$Drug_Gene_Ordered)
ctrp_data_g2p_plot <- ggplot(data = ctrp_data_g2p, aes(x = Mutation_Status_Nonsilent, y = AUC)) +
  facet_wrap(~ Drug_Gene_Ordered, drop = FALSE, nrow = 3) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  geom_boxplot(mapping = aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85), outlier.shape = 3, outlier.size = 0.5) +
  scale_fill_manual(values = ctrp_data_g2p_color) +
  guides(color = FALSE) +
  geom_text(data = ctrp_label_text, mapping = aes(x = 1.5, y = 22.5, label = p.signif), nudge_y = 0.1) +
  theme(legend.position = "top", axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
  labs(title = "CTRP", fill = "Mutation Status", y = "AUC", x = "Mutation Status")
ctrp_data_g2p_plot

# ggsave("./plots/manuscript/ctrp_data_g2p_plot.png", ctrp_data_g2p_plot, device = "png", dpi = 450, width = 12, height = 7, units = "in")
```

### GDSC

```{r fig.height=7, fig.width=12}
gdsc_g2p_order <- as.character(gdsc_signif_g2p$Drug_Gene)
gdsc_data_g2p$Drug_Gene_Ordered <- factor(gdsc_data_g2p$Drug_Gene, levels = gdsc_g2p_order, labels = sapply(strsplit(x = gdsc_g2p_order, split = "_"), function(x) paste0(x[1], "\n", x[2])))
gdsc_signif_g2p$Drug_Gene_Ordered <- factor(gdsc_signif_g2p$Drug_Gene, levels = gdsc_g2p_order, labels = sapply(strsplit(x = gdsc_g2p_order, split = "_"), function(x) paste0(x[1], "\n", x[2])))
gdsc_data_g2p_color <- as.character(gdsc_data_g2p$Color_Nonsilent)
names(gdsc_data_g2p_color) <- gdsc_data_g2p$Mutation_Status_Nonsilent
gdsc_label_text <- data.frame(p.signif.adj = gdsc_signif_g2p$p.signif.adj, p.signif = gdsc_signif_g2p$p.signif, Drug_Gene_Ordered = gdsc_signif_g2p$Drug_Gene_Ordered)
gdsc_data_g2p_plot <- ggplot(data = gdsc_data_g2p, aes(x = Mutation_Status_Nonsilent, y = AUC)) +
  facet_wrap(~ Drug_Gene_Ordered, drop = FALSE, nrow = 3) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  geom_boxplot(mapping = aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85), outlier.shape = 3, outlier.size = 0.5) +
  scale_fill_manual(values = gdsc_data_g2p_color) +
  guides(color = FALSE) +
  geom_text(data = gdsc_label_text, mapping = aes(x = 1.5, y = 1, label = p.signif), nudge_y = 0.1) +
  theme(legend.position = "top", axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
  labs(title = "GDSC", fill = "Mutation Status", y = "AUC", x = "Mutation Status")
gdsc_data_g2p_plot

# ggsave("./plots/manuscript/gdsc_data_g2p_plot.png", gdsc_data_g2p_plot, device = "png", dpi = 450, width = 12, height = 7, units = "in")
```

# OLD: CRISPR POINT MUT MAPPING

--------------------------------------------------------------------------------

Match specific point mutations.
```{r fig.height=5, fig.width=20, eval=FALSE}
g2p_indications <- filter(read.delim("./data_munging/data_mutation_associations_appended.csv", sep = "\t", header = TRUE), Evidence.Level == "A")
maf_g2p_indications <- filter(maf_raw, Genome_Change %in% g2p_indications$MutationName)
crispr_g2p_indications <- merge(crispr_data_ptmuts, maf_g2p_indications, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
crispr_g2p_indications$Mutation_Status_Nonsilent <- ifelse(is.na(crispr_g2p_indications$Mutation_Status_Nonsilent), "Wildtype", crispr_g2p_indications$Mutation_Status_Nonsilent)
dup_g2p_indications <- filter(crispr_g2p_indications[, c("Hugo_Symbol", "CCLE_Name", "DepMap_ID")] %>% group_by(Hugo_Symbol, CCLE_Name, DepMap_ID) %>% tally(), n > 1)
crispr_g2p_indications <- merge(crispr_g2p_indications, dup_g2p_indications, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
crispr_g2p_indications$Genome_Change <- factor(crispr_g2p_indications$Genome_Change, levels = unique(crispr_g2p_indications$Genome_Change))
crispr_g2p_indications_nonNA <- filter(crispr_g2p_indications, is.na(n))
crispr_g2p_indications_plot <- ggplot(crispr_g2p_indications, aes(x = Hugo_Symbol, y = Score)) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  geom_boxplot(alpha = 0.5, color = "lightgray", outlier.shape = NA) +
  geom_jitter(width = 0.3, mapping = aes(color = Mutation_Status_Nonsilent), size = 1) +
  theme_light() +
  theme(legend.title = element_blank()) +
  labs(x = "Gene", y = "CERES Score")
crispr_g2p_indications_plot
crispr_g2p_indications_muts_plot <- ggplot(crispr_g2p_indications, aes(x = Protein_Change, y = Score)) +
  facet_grid(~ Hugo_Symbol, scales = "free_x", space = "free") +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  geom_boxplot(alpha = 0.5, color = "lightgray", outlier.shape = NA) +
  geom_jitter(width = 0.1, mapping = aes(color = Mutation_Status_Nonsilent), size = 1) +
  theme_light() +
  theme(legend.title = element_blank(), axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(x = "Gene", y = "CERES Score")
crispr_g2p_indications_muts_plot

# ggsave("./plots/manuscript/crispr_g2p_indications_plot_test.png", crispr_g2p_indications_plot, width = 12, height = 5, units = "in")
# ggsave("./plots/manuscript/crispr_g2p_indications_muts_plot_test.png", crispr_g2p_indications_muts_plot, width = 20, height = 5, units = "in")
```

# REFERENCES

--------------------------------------------------------------------------------

Barretina, J., Caponigro, G., Stransky, N., Venkatesan, K., Margolin, A. A., Kim, S., … Garraway, L. A. (2012). The Cancer Cell Line Encyclopedia enables predictive modelling of anticancer drug sensitivity. Nature, 483(7391), 603–607. https://doi.org/10.1038/nature11003

Broad Institute Cancer Dependency Map; Cancer Data Science (2018): Cancer Dependency Map, CRISPR Avana dataset 18Q3 (Avana_public_18Q3). figshare. Fileset. doi:10.6084/m9.figshare.6931364.v1

Consortium, T. C. C. L. E., & Consortium, T. G. of D. S. in C. (2015). Pharmacogenomic agreement between two cancer cell line data sets. Nature, 528(7580), 84–87. https://doi.org/10.1038/nature15736

Data Science, Cancer (2018): DEMETER2 data. figshare. Fileset. doi:10.6084/m9.figshare.6025238.v2

Doench, J. G., Fusi, N., Sullender, M., Hegde, M., Vaimberg, E. W., Donovan, K. F., … Root, D. E. (2016). Optimized sgRNA design to maximize activity and minimize off-target effects of CRISPR-Cas9. Nature Biotechnology, 34(2), 184–191. https://doi.org/10.1038/nbt.3437

Meyers, R. M., Bryan, J. G., McFarland, J. M., Weir, B. A., Sizemore, A. E., Xu, H., … Tsherniak, A. (2017). Computational correction of copy-number effect improves specificity of CRISPR-Cas9 essentiality screens in cancer cells. Nature Genetics, 49(12), 1779–1784. https://doi.org/10.1038/ng.3984

McFarland, J. M., Ho, Z. V., Kugener, G., Dempster, J. M., Montgomery, P. G., Bryan, J. G., … Tsherniak, A. (2018). Improved estimation of cancer dependencies from large-scale RNAi screens using model-based normalization and data integration. https://doi.org/10.1101/305656

# SESSION INFORMATION

--------------------------------------------------------------------------------

```{r}
print(sessionInfo())
```

### 2018-12-20 manuscript_analysis.Rmd

@@
 g2p_druggenes <- unique(g2p_filt$Drug_Gene[!is.na(g2p_filt$Drug_Gene)])
-g2p_genes <- unique(sapply(strsplit(g2p_druggenes, "_", fixed = TRUE), function(x) x[2]))
-g2p_drugs <- unique(sapply(strsplit(g2p_druggenes, "_", fixed = TRUE), function(x) x[1]))
+g2p_drugs <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[1]))
+g2p_genes <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[2]))
+g2p_lins <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[3]))
 g2p_druggenes
+g2p_drugs
 g2p_genes
-g2p_drugs
+g2p_lins
+
 # Order and genes taken from pink heatmapo from Daniel's analyses
@@
 
+Pearson correlations for gene expression and copy number:
+```{r fig.height=6, fig.width=12}
+crispr_pearson_res_GE <- transform(crispr_pearson_res_GE, Hugo_Symbol = reorder(Hugo_Symbol, corr)) 
+crispr_pearson_res_GE$p_log10 <- -log10(crispr_pearson_res_GE$p)
+crispr_pearson_res_CN <- transform(crispr_pearson_res_CN, Hugo_Symbol = reorder(Hugo_Symbol, corr)) 
+crispr_pearson_res_CN$p_log10 <- -log10(crispr_pearson_res_CN$p)
+
+crispr_ge_pearson_corr_plot <- ggplot(data = crispr_pearson_res_GE, aes(x = Hugo_Symbol, y = corr)) +
+  geom_point(aes(fill = p_log10), pch = 21, size = 5) +
+  scale_fill_gradient2(low = "white", mid = "white", high = "darkorchid4", midpoint = 1.3010299957) +
+  coord_cartesian(ylim = c(-0.65, 0.25)) +
+  theme(legend.position = "bottom", axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 10)) +
+  labs(fill = "-log10(p)", x = "Gene", y = "Pearson Correlation Coefficient (r_s)", subtitle = "CRISPR: Correlation between AUC z-score and gene expression")
+crispr_cn_pearson_corr_plot <- ggplot(data = crispr_pearson_res_CN, aes(x = Hugo_Symbol, y = corr)) +
+  geom_point(aes(fill = p_log10), pch = 21, size = 5) +
+  scale_fill_gradient2(low = "white", mid = "white", high = "darkorchid4", midpoint = 1.3010299957) +
+  coord_cartesian(ylim = c(-0.65, 0.25)) +
+  theme(legend.position = "bottom", axis.title.y = element_blank(), axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 10)) +
+  labs(fill = "-log10(p)", x = "Gene", y = "Pearson Correlation Coefficient (r_s)", subtitle = "CRISPR: Correlation between AUC z-score and copy number")
+
+crispr_pearson_corr_plot <- plot_grid(crispr_ge_pearson_corr_plot, crispr_cn_pearson_corr_plot, align = "h")
+crispr_pearson_corr_plot
+# ggsave("./plots/manuscript/crispr_pearson_corr_plot.png", crispr_pearson_corr_plot, device = "png", dpi = 450, width = 12, height = 6, units = "in")
+```
+
+Spearman correlations for gene expression and copy number:
+```{r fig.height=6, fig.width=12}
+crispr_spearman_res_GE <- transform(crispr_spearman_res_GE, Hugo_Symbol = reorder(Hugo_Symbol, corr)) 
+crispr_spearman_res_GE$p_log10 <- -log10(crispr_spearman_res_GE$p)
+crispr_spearman_res_CN <- transform(crispr_spearman_res_CN, Hugo_Symbol = reorder(Hugo_Symbol, corr)) 
+crispr_spearman_res_CN$p_log10 <- -log10(crispr_spearman_res_CN$p)
+
+crispr_ge_spearman_corr_plot <- ggplot(data = crispr_spearman_res_GE, aes(x = Hugo_Symbol, y = corr)) +
+  geom_point(aes(fill = p_log10), pch = 21, size = 5) +
+  scale_fill_gradient2(low = "white", mid = "white", high = "darkorchid4", midpoint = 1.3010299957) +
+  coord_cartesian(ylim = c(-0.45, 0.2)) +
+  theme(legend.position = "bottom", axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 10)) +
+  labs(fill = "-log10(p)", x = "Gene", y = "Spearman Correlation Coefficient (r_s)", subtitle = "CRISPR: Correlation between AUC z-score and gene expression")
+crispr_cn_spearman_corr_plot <- ggplot(data = crispr_spearman_res_CN, aes(x = Hugo_Symbol, y = corr)) +
+  geom_point(aes(fill = p_log10), pch = 21, size = 5) +
+  scale_fill_gradient2(low = "white", mid = "white", high = "darkorchid4", midpoint = 1.3010299957) +
+  coord_cartesian(ylim = c(-0.45, 0.2)) +
+  theme(legend.position = "bottom", axis.title.y = element_blank(), axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 10)) +
+  labs(fill = "-log10(p)", x = "Gene", y = "Spearman Correlation Coefficient (r_s)", subtitle = "CRISPR: Correlation between AUC z-score and copy number")
+
+crispr_spearman_corr_plot <- plot_grid(crispr_ge_spearman_corr_plot, crispr_cn_spearman_corr_plot, align = "h")
+crispr_spearman_corr_plot
+# ggsave("./plots/manuscript/crispr_spearman_corr_plot.png", crispr_spearman_corr_plot, device = "png", dpi = 450, width = 12, height = 6, units = "in")
+```
+
 ### CCLE
@@
 }
-```
-
-```{r}
-ccle_data_g2p$G2P_DGL <- ifelse(ccle_data_g2p$Drug_Gene_Lin %in% g2p_dgls, "Yes", "No")
-ccle_data_g2p_split <- split(ccle_data_g2p, f = ccle_data_g2p$Drug_Gene)
-ccle_corr_all <- MakeCorrResSummaryTable(ccle_data_g2p_split, dataset_name = "CCLE")
-
-ctrp_data_g2p$G2P_DGL <- ifelse(ctrp_data_g2p$Drug_Gene_Lin %in% g2p_dgls, "Yes", "No")
-ctrp_data_g2p_split <- split(ctrp_data_g2p, f = ctrp_data_g2p$Drug_Gene)
-ctrp_corr_all <- MakeCorrResSummaryTable(ctrp_data_g2p_split, dataset_name = "CTRP")
-
-gdsc_data_g2p$G2P_DGL <- ifelse(gdsc_data_g2p$Drug_Gene_Lin %in% g2p_dgls, "Yes", "No")
-gdsc_data_g2p_split <- split(gdsc_data_g2p, f = gdsc_data_g2p$Drug_Gene)
-gdsc_corr_all <- MakeCorrResSummaryTable(gdsc_data_g2p_split, dataset_name = "GDSC")
-
-g2p_corr_all <- rbind(ccle_corr_all, ctrp_corr_all, gdsc_corr_all)
-```
-
-```{r}
+
 G2PCorr_KStest <- function(dataset, dataset_name) {
@@
 ```{r}
+ccle_data_g2p$G2P_DGL <- ifelse(ccle_data_g2p$Drug_Gene_Lin %in% g2p_dgls, "Yes", "No")
+ccle_data_g2p_split <- split(ccle_data_g2p, f = ccle_data_g2p$Drug_Gene)
+ccle_corr_all <- MakeCorrResSummaryTable(ccle_data_g2p_split, dataset_name = "CCLE")
+
+ctrp_data_g2p$G2P_DGL <- ifelse(ctrp_data_g2p$Drug_Gene_Lin %in% g2p_dgls, "Yes", "No")
+ctrp_data_g2p_split <- split(ctrp_data_g2p, f = ctrp_data_g2p$Drug_Gene)
+ctrp_corr_all <- MakeCorrResSummaryTable(ctrp_data_g2p_split, dataset_name = "CTRP")
+
+gdsc_data_g2p$G2P_DGL <- ifelse(gdsc_data_g2p$Drug_Gene_Lin %in% g2p_dgls, "Yes", "No")
+gdsc_data_g2p_split <- split(gdsc_data_g2p, f = gdsc_data_g2p$Drug_Gene)
+gdsc_corr_all <- MakeCorrResSummaryTable(gdsc_data_g2p_split, dataset_name = "GDSC")
+
+g2p_corr_all <- rbind(ccle_corr_all, ctrp_corr_all, gdsc_corr_all)
+
 ccle_corr_stats <- G2PCorr_KStest(ccle_corr_all, "CCLE")
@@
 g2p_corr_stats <- rbind(ccle_corr_stats, ctrp_corr_stats, gdsc_corr_stats)
+g2p_corr_stats <- g2p_corr_stats %>% separate(col = Metric, into = c("Correlation_Method", "corr", "Metric"), sep = "_")
 g2p_corr_stats
@@
 g2p_mut_stats
+```
+
+Plot of Kolmogorov-Smirnov test results comparing correlations between CN/GE and AUC z-score in G2P and non-G2P lineages:
+```{r fig.height=6, fig.width=12}
+g2p_corr_4plot <- g2p_corr_all
+g2p_corr_4plot$p <- NULL
+g2p_corr_4plot$Mut_Signif <- NULL
+g2p_corr_4plot <- melt(g2p_corr_4plot, id.vars = colnames(g2p_corr_4plot)[1:5], measure.vars = colnames(g2p_corr_4plot)[6:9], value.name = "Correlation")
+g2p_corr_4plot <- g2p_corr_4plot %>% separate(col = variable, into = c("Correlation_Method", "corr", "Metric"), sep = "_", remove = FALSE)
+
+g2p_ks_res_plot <- ggplot(data = g2p_corr_4plot) +
+  facet_grid(Correlation_Method ~ Metric * Dataset) +
+  geom_violin(aes(y = Correlation, x = G2P_DGL, fill = G2P_DGL, color = G2P_DGL), alpha = 0.3) +
+  geom_boxplot(width = 0.075, aes(y = Correlation, x = G2P_DGL, color = G2P_DGL)) +
+  geom_jitter(width = 0.3, alpha = 0.7, aes(y = Correlation, x = G2P_DGL, color = G2P_DGL)) +
+  theme(legend.position = "none") +
+  coord_cartesian(ylim = c(-1, 1)) +
+  geom_text(data = g2p_corr_stats, aes(x = 1.5, y = 0.8, label = paste0("D = ", formatC(D_stat, digits = 2, format = "f"), ", p = ", ifelse(pval > 0.1, round(pval, 2), round(pval, 3)), "\n", ifelse(is.na(signif), "", signif)))) +
+  labs(x = "Is the lineage in a G2P DGL?", y = "Correlation Coefficint", subtitle = "Kolmogorov-Smirnov test results comparing correlations between CN/GE and AUC z-score in G2P and non-G2P lineages.")
+g2p_ks_res_plot
+
+# ggsave("./plots/manuscript/g2p_ks_res_plot.png", g2p_ks_res_plot, device = "png", dpi = 450, width = 12, height = 6, units = "in")
 ```
@@
 # ggsave("./plots/manuscript/all_dgl_plot.png", dgl_all_plot, device = "png", dpi = 450, width = 12, height = 40, units = "in")
+```
+
+## Pancancer vs. Lineage
+
+```{r}
+compare_grid <- expand.grid(g2p_druggenes, unique(ccl_converter$group_general_lineage_name), c("CCLE", "CTRP", "GDSC"), c("Gene Expression", "Copy Number", "Mutation Status"))
+colnames(compare_grid) <- c("Drug_Gene", "group_general_lineage_name", "Dataset", "Metric")
+
+pancan_ge <- select(filter(all_pearson_res, Metric == "Gene Expression"), Drug_Gene, p, Dataset, p_log10)
+colnames(pancan_ge)[colnames(pancan_ge) == "p"] <- "p_pancan"
+colnames(pancan_ge)[colnames(pancan_ge) == "p_log10"] <- "p_log10_pancan"
+compare_ge <- select(dgl_signif_pearson_g2p_grid, Drug_Gene, group_general_lineage_name, n, Pearson_Pval_GE, Drug_Gene_Lin, InG2P, Dataset)
+colnames(compare_ge)[colnames(compare_ge) == "Pearson_Pval_GE"] <- "p"
+compare_ge$p_log10 <- -log10(compare_ge$p)
+compare_ge <- merge(compare_ge, pancan_ge, by = c("Drug_Gene", "Dataset"), all = TRUE)
+compare_ge$Compare_Pvals <- ifelse(compare_ge$p_log10 < compare_ge$p_log10_pancan, "Under", "Above")
+compare_ge$Metric <- "Gene Expression"
+
+pancan_cn <- select(filter(all_pearson_res, Metric == "Copy Number"), Drug_Gene, p, Dataset, p_log10)
+colnames(pancan_cn)[colnames(pancan_cn) == "p"] <- "p_pancan"
+colnames(pancan_cn)[colnames(pancan_cn) == "p_log10"] <- "p_log10_pancan"
+compare_cn <- select(dgl_signif_pearson_g2p_grid, Drug_Gene, group_general_lineage_name, n, Pearson_Pval_CN, Drug_Gene_Lin, InG2P, Dataset)
+colnames(compare_cn)[colnames(compare_cn) == "Pearson_Pval_CN"] <- "p"
+compare_cn$p_log10 <- -log10(compare_cn$p)
+compare_cn <- merge(compare_cn, pancan_cn, by = c("Drug_Gene", "Dataset"), all = TRUE)
+compare_cn$Compare_Pvals <- ifelse(compare_cn$p_log10 < compare_cn$p_log10_pancan, "Under", "Above")
+compare_cn$Metric <- "Copy Number"
+
+pancan_mut <- all_mut_res
+pancan_mut$Metric <- NULL
+pancan_mut$corr <- NULL
+colnames(pancan_mut)[colnames(pancan_mut) == "p"] <- "p_pancan"
+colnames(pancan_mut)[colnames(pancan_mut) == "p_log10"] <- "p_log10_pancan"
+compare_mut <- dgl_mut_grid_summ
+compare_mut$p_log10 <- -log10(compare_mut$p)
+compare_mut <- merge(compare_mut, pancan_mut, by = c("Drug_Gene", "Dataset"), all = TRUE)
+compare_mut$Compare_Pvals <- ifelse(compare_mut$p_log10 < compare_mut$p_log10_pancan, "Under", "Above")
+compare_mut$Metric <- "Mutation Status"
+
+compare_data <- filter(rbind(compare_ge, compare_cn, compare_mut), Drug_Gene %in% g2p_druggenes)
+compare_data <- merge(compare_grid, compare_data, by = c("Drug_Gene", "group_general_lineage_name", "Dataset", "Metric"), all.x = TRUE)
+```
+
+```{r}
+compare_data_stats <- compare_data %>% count(Metric, Compare_Pvals)
+compare_data_stats
+```
+
+```{r fig.height=12, fig.width=12}
+compare_mut_plot <- ggplot(data = filter(compare_data, Metric == "Mutation Status"), aes(x = group_general_lineage_name, y = Drug_Gene)) +
+  facet_wrap(~ Dataset) +
+  geom_point(aes(shape = Compare_Pvals, fill = p_log10), color = "gray50") +
+  scale_fill_gradient2(low = "white", mid = "white", high = "darkorchid4", midpoint = 1.3010299957) +
+  scale_shape_manual(values = c(25, 24), labels = c("Below", "Above")) +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4), legend.position = "top") +
+  labs(title = "Mutation Status",
+       subtitle = paste0("Above: ", filter(compare_data_stats, Metric == "Mutation Status" & Compare_Pvals == "Above")$nn, "\n",
+                         "Under: ", filter(compare_data_stats, Metric == "Mutation Status" & Compare_Pvals == "Under")$nn, "\n",
+                         "Not tested: ", filter(compare_data_stats, Metric == "Mutation Status" & is.na(Compare_Pvals))$nn),
+       x = "Lineage", y = "Drug-Gene", shape = "Compare linege p-value to pancancer p-value:", fill = "-log10(p)")
+# ggsave("./plots/manuscript/compare_mut_plot.png", compare_mut_plot, device = "png", dpi = 450, width = 12, height = 12, units = "in")
+
+compare_ge_plot <- ggplot(data = filter(compare_data, Metric == "Gene Expression"), aes(x = group_general_lineage_name, y = Drug_Gene)) +
+  facet_wrap(~ Dataset) +
+  geom_point(aes(shape = Compare_Pvals, fill = p_log10), color = "gray50") +
+  scale_fill_gradient2(low = "white", mid = "white", high = "darkorchid4", midpoint = 1.3010299957) +
+  scale_shape_manual(values = c(25, 24), labels = c("Below", "Above")) +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4), legend.position = "top") +
+  labs(title = "Gene Expression",
+       subtitle = paste0("Above: ", filter(compare_data_stats, Metric == "Gene Expression" & Compare_Pvals == "Above")$nn, "\n",
+                         "Under: ", filter(compare_data_stats, Metric == "Gene Expression" & Compare_Pvals == "Under")$nn, "\n",
+                         "Not tested: ", filter(compare_data_stats, Metric == "Gene Expression" & is.na(Compare_Pvals))$nn),
+       x = "Lineage", y = "Drug-Gene", shape = "Compare linege p-value to pancancer p-value:", fill = "-log10(p)")
+# ggsave("./plots/manuscript/compare_ge_plot.png", compare_ge_plot, device = "png", dpi = 450, width = 12, height = 12, units = "in")
+
+compare_cn_plot <- ggplot(data = filter(compare_data, Metric == "Copy Number"), aes(x = group_general_lineage_name, y = Drug_Gene)) +
+  facet_wrap(~ Dataset) +
+  geom_point(aes(shape = Compare_Pvals, fill = p_log10), color = "gray50") +
+  scale_fill_gradient2(low = "white", mid = "white", high = "darkorchid4", midpoint = 1.3010299957) +
+  scale_shape_manual(values = c(25, 24), labels = c("Below", "Above")) +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4), legend.position = "top") +
+  labs(title = "Copy Number",
+       subtitle = paste0("Above: ", filter(compare_data_stats, Metric == "Copy Number" & Compare_Pvals == "Above")$nn, "\n",
+                         "Under: ", filter(compare_data_stats, Metric == "Copy Number" & Compare_Pvals == "Under")$nn, "\n",
+                         "Not tested: ", filter(compare_data_stats, Metric == "Copy Number" & is.na(Compare_Pvals))$nn),
+       x = "Lineage", y = "Drug-Gene", shape = "Compare linege p-value to pancancer p-value:", fill = "-log10(p)")
+# ggsave("./plots/manuscript/compare_cn_plot.png", compare_cn_plot, device = "png", dpi = 450, width = 12, height = 12, units = "in")
+```
+
+```{r}
+test <- filter(compare_mut, Drug_Gene == "nilotinib_ABL1" & Dataset == "CCLE" & group_general_lineage_name == "bone cancer")
 ```

### 2018-12-21 manuscript.Rmd
work on manuscript updates

@@
 
-```{r setup, include = FALSE}
-# library("papaja")
+```{r setup, include=FALSE}
+library(tidyverse)
+library(ggpubr)
+library(papaja)
 # install.packages("tinytex")
@@
 
+```{r g2p-data, include=FALSE}
+ccl_converter <- read.delim("./data_munging/cell_line_database_v1_20180911.tsv", row.names = 1, sep = "\t", header = TRUE)
+lineage_converter <- unique(ccl_converter[, c("grouped_general_doid", "group_general_lineage_name")])
+colnames(ccl_converter)[colnames(ccl_converter) == "Broad_ID"] <- "DepMap_ID"
+
+g2p <- read.delim("./data_munging/g2p_full_level_A_dataset_NEW_DEC_2_2018_withGroupedLineages.csv", sep = "\t", header = TRUE)
+g2p[, 1:2] <- NULL
+g2p <- merge(g2p, lineage_converter, by = "grouped_general_doid", all.x = TRUE)
+
+g2p$Drug <- tolower(g2p$Drug)
+g2p[g2p == -1] <- NA
+g2p$Ref[g2p$Ref == "None"] <- NA
+g2p$Alt[g2p$Alt == "None"] <- NA
+g2p$Drug_Gene <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene), NA, paste0(g2p$Drug, "_", g2p$Gene))
+g2p$Drug_Gene_Lin <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene) | is.na(g2p$group_general_lineage_name), NA, paste0(g2p$Drug, "_", g2p$Gene, "_", g2p$group_general_lineage_name))
+g2p$position <- paste0("g.chr", g2p$Chromosome, ":", g2p$End, g2p$Ref, ">", g2p$Alt)
+g2p$position <- ifelse(grepl("NA", g2p$position), NA, g2p$position)
+g2p_filt <- subset(g2p, grepl("^CID", g2p$DrugID))
+g2p_dgls <-  unique(g2p_filt$Drug_Gene_Lin[!is.na(g2p_filt$Drug_Gene_Lin)])
+g2p_druggenes <- unique(g2p_filt$Drug_Gene[!is.na(g2p_filt$Drug_Gene)])
+g2p_drugs <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[1]))
+g2p_genes <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[2]))
+g2p_lins <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[3]))
+
+# Order and genes taken from pink heatmapo from Daniel's analyses
+g2p_genes <- c("EGFR", "KRAS", "ERBB2", "ERBB3", "MET", "ALK", "ROS1", "PDGFRA", "ABL1", "KIT", "PDGFRB", "PDGFB", "BRAF", "G6PD", "RET", "BRCA1", "BRCA2", "UGT1A1", "TSC1", "TSC2", "AKT1", "IDH2", "DPYD", "ESR1", "CYP19A1", "TPMT", "FLT3", "NPM1", "DNMT3A", "PML", "PTCH1", "JAK2", "MYD88", "MGMT")
+
+g2p_nonCID <- subset(g2p, !grepl("^CID", g2p$DrugID))
+
+# print("Drug-Gene")
+g2p_druggene_tally <- g2p_filt %>% group_by(Drug_Gene) %>% tally() %>% drop_na()
+nrow(g2p_druggene_tally)
+range(g2p_druggene_tally$n)
+mean(g2p_druggene_tally$n)
+sd(g2p_druggene_tally$n)
+
+# print("Drug")
+g2p_drug_tally <- g2p_filt %>% group_by(Drug) %>% tally() %>% drop_na()
+range(g2p_drug_tally$n)
+mean(g2p_drug_tally$n)
+sd(g2p_drug_tally$n)
+
+# print("Gene")
+g2p_gene_tally <- g2p_filt %>% group_by(Gene) %>% tally() %>% drop_na()
+range(g2p_gene_tally$n)
+mean(g2p_gene_tally$n)
+sd(g2p_gene_tally$n)
+
+# print("Drug-Gene-Lineage")
+g2p_dgl_tally <- g2p_filt %>% group_by(Drug, Gene, Drug_Gene, group_general_lineage_name) %>% tally() %>% drop_na()
+nrow(g2p_dgl_tally)
+length(unique(g2p_dgl_tally$Drug))
+length(unique(g2p_dgl_tally$Gene))
+unique(g2p_filt$Phenotype.Description)
+```
+
+```{r table-g2p-nonCID, echo=FALSE, results='asis'}
+summ <- g2p_nonCID %>% group_by(Drug, DrugID) %>% tally() %>% summarize("Compound identifier" = DrugID, "Number of G2P interpretations" = n, "Proportion of excluded interpretations (%)" = printnum(n / 402 * 100))
+colnames(summ)[colnames(summ) == "Drug"] <- "Compound"
+summ$Compound[summ$Compound == "egfr"] <- "EGFR"
+summ$Compound[summ$Compound == "mab"] <- "mAb"
+
+apa_table(summ, caption = "Distribution of level-A G2P drugs excluded from analyses",
+          note = "mAb = monoclonal antibody; NA indicates G2P interpretation does not have an associated compound")
+```
+
 G2P designed a set of standards for stratifying their database’s cancer variant interpretations, ranging from preclinical data at the low-evidence end (level D) to clinically actionable interpretations at the high-evidence end (level A).
-To test only these clinically actionable associations, we filtered the G2P dataset for only level-A G2P interpretations, of which there were 1,296 (see Methods).
+To test only these clinically actionable associations, we filtered the G2P dataset for only level-A G2P interpretations, of which there were `r formatC(nrow(g2p), big.mark = ",", big.interval = 3L)` (see Methods).
 All compounds screened within the GDSC, CTRP, and CCLE datasets are considered “small molecules” and are respectively linked to Compound (CID) numbers used for indexing in the PubChem database (https://pubchem.ncbi.nlm.nih.gov/).
@@
 monoclonal antibodies), that had level-A G2P evidence could not be included in our comparisons.
-Thus, G2P interpretations for which the compound did not have a matching CID code were excluded from further analysis as were interpretations that did not have an associated compound, resulting in removal of 402 interpretations (Table 1).
+Thus, G2P interpretations for which the compound did not have a matching CID code were excluded from further analysis as were interpretations that did not have an associated compound, resulting in removal of `r nrow(g2p_nonCID)` interpretations (Table\ \@ref(tab:table-g2p-nonCID)).
 It should be noted that cisplatin, a small molecule, was excluded due to its being indexed with a ChEMBLdb identifier (https://www.ebi.ac.uk/chembl/), which we did not manually re-index to a CID to avoid accidental mischaracterization.
 
-After filtering, 894 level-A G2P interpretations were carried forward in subsequent analyses, constituting 57 unique drugs and 34 unique genes in 88 distinct level-A combinations (Figure 1A).
-The number of level-A interpretations per drug ranged from 1 to 176 (M = 15.7, SD = 34.6), from 1 to 264 (M = 26.2, SD = 61.6) per gene, and for each level-A drug-gene combination, the range was 1 to 103 (M = 10.1, SD = 19.8).
+After filtering, `r nrow(g2p_filt)` level-A G2P interpretations were carried forward in subsequent analyses, constituting `r length(g2p_drugs)` unique drugs and `r length(g2p_genes)` unique genes in `r length(g2p_druggenes)` distinct level-A combinations (*Figure 1A*).
+The number of level-A interpretations per drug ranged from `r range(g2p_drug_tally$n)[1]` to `r range(g2p_drug_tally$n)[2]` ($M =$ `r printnum(mean(g2p_drug_tally$n))`, $SD =$ `r printnum(sd(g2p_drug_tally$n))`), `r range(g2p_gene_tally$n)[1]` to `r range(g2p_gene_tally$n)[2]` ($M =$ `r printnum(mean(g2p_gene_tally$n))`, $SD =$ `r printnum(sd(g2p_gene_tally$n))`) per gene, and for each level-A drug-gene combination, the range was `r range(g2p_druggene_tally$n)[1]` to `r range(g2p_druggene_tally$n)[2]` ($M =$ `r printnum(mean(g2p_druggene_tally$n))`, $SD =$ `r printnum(sd(g2p_druggene_tally$n))`).
 These unique drugs, genes, and combinations are hereafter referred to as G2P drugs, G2P genes, and G2P associations.
-Of the 57 unique G2P drugs, 37 of them were screened in at least one of the drug screen datasets, 14 were screened in two of the three datasets, and only three drugs were screened in all three datasets.
+Of the `r length(g2p_drugs)` unique G2P drugs, 37 of them were screened in at least one of the drug screen datasets, 14 were screened in two of the three datasets, and only three drugs were screened in all three datasets.
 The remaining 20 un-screened G2P drugs suggests an incompleteness of these drug screens, though these projects frequently release new screening data that may include these drugs in future releases.
 
-Using cell-line-specific point mutation annotations from the CCLE, we compared z-score-transformed area under the dose-response curve (AUC) distributions between mutant and wildtype cell lines for all G2P genes for each G2P drug tested in the CCLE, CTRP, and GDSC drug screens (Figures 1B and 2A).
-At uncorrected $\alpha$ = 0.05, Wilcoxon rank-sum tests revealed that in CCLE, the AUC distributions of mutant and wildtype groups for 10 out of 170 (5.88%) tested drug-gene combinations were significantly different, 91 out of 918 (9.91%) were significantly different for CTRP, and 61 out of 850 (7.18%) for GDSC.
+```{r}
+ccle_signif_g2p_grid <- readRDS("./data_munging/rds/ccle_signif_g2p_grid.rds")
+ctrp_signif_g2p_grid <- readRDS("./data_munging/rds/ctrp_signif_g2p_grid.rds")
+gdsc_signif_g2p_grid <- readRDS("./data_munging/rds/gdsc_signif_g2p_grid.rds")
+```
+
+Using cell-line-specific point mutation annotations from the CCLE, we compared z-score-transformed area under the dose-response curve (AUC) distributions between mutant and wildtype cell lines for all G2P genes for each G2P drug tested in the CCLE, CTRP, and GDSC drug screens (*Figures 1B and 2A*).
+At uncorrected $\alpha = 0.05$, Wilcoxon rank-sum tests revealed that in CCLE, the AUC distributions of mutant and wildtype groups for `r nrow(filter(ccle_signif_g2p_grid, p < 0.05))` out of `r nrow(ccle_signif_g2p_grid)` (`r printnum(nrow(filter(ccle_signif_g2p_grid, p < 0.05)) / nrow(ccle_signif_g2p_grid) * 100)`%) tested drug-gene combinations were significantly different, `r nrow(filter(ctrp_signif_g2p_grid, p < 0.05))` out of `r nrow(ctrp_signif_g2p_grid)` (`r printnum(nrow(filter(ctrp_signif_g2p_grid, p < 0.05)) / nrow(ctrp_signif_g2p_grid) * 100)`%) were significantly different for CTRP, and `r nrow(filter(gdsc_signif_g2p_grid, p < 0.05))` out of `r nrow(gdsc_signif_g2p_grid)` (`r printnum(nrow(filter(gdsc_signif_g2p_grid, p < 0.05)) / nrow(gdsc_signif_g2p_grid) * 100)`%) for GDSC.
 We observe little concordance between the number of interpretations for each G2P association and the significance of mutation status on AUC for said G2P association, suggesting that mutation status alone is not a robust predictor of clinically actionable genetic targets.
@@
 
-We compared the distribution of level-A G2P associations (Figure 1A) and the associated p-values from the mutation status comparisons (Figure 1B) with a null distribution of p-values derived from all pairwise combinations of G2P genes and the G2P drugs tested in each dataset, less any of the 88 distinct combinations with G2P interpretations, i.e.
-the non-gray squares in the right heatmap of Figure 1A (Figure 3A).
+We compared the distribution of level-A G2P associations (*Figure 1A*) and the associated p-values from the mutation status comparisons (*Figure 1B*) with a null distribution of p-values derived from all pairwise combinations of G2P genes and the G2P drugs tested in each dataset, less any of the 88 distinct combinations with G2P interpretations, i.e.
+the non-gray squares in the right heatmap of *Figure 1A (Figure 3A*).
 To formally test concordance between clinically actionable variants and drug screen results, we conducted an independent, two-group t-test to compare the distributions of p-values of drug-gene combinations that either were or were not represented with level-A evidence in G2P, which indicated that the distributions of p-values did not significantly differ for CCLE [t(9) = 0.25, p = 0.81], CTRP [t(51) = 0.85, p = 0.40], nor GDSC [t(47) = -0.56, p = 0.58]  (Table 2).
@@
 
-Similar tests were conducted for the distributions of Pearson correlation coefficients (r) between the number of level-A G2P associations and gene expression (RPKM) and copy number (log2 ratio) of the gene in the association (Figures 3B-C).
-Example r derivations are shown in Figures 2B-C.
+Similar tests were conducted for the distributions of Pearson correlation coefficients (r) between the number of level-A G2P associations and gene expression (RPKM) and copy number (log2 ratio) of the gene in the association (*Figures 3B-C*).
+Example r derivations are shown in *Figures 2B-C*.
 Absolute values of r were used to simplify extreme values in both directions for testing.
@@
 
-In all three datasets for both level-A G2P associations and null distribution associations, there are more significant |r| values when using gene expression as the genomic feature than when using copy number (Table 2), which corresponds with previous work showing that gene expression is an informative molecular feature when assessing drug sensitivity (Jang et al., 2014; Sirota et al., 2011).
+In all three datasets for both level-A G2P associations and null distribution associations, there are more significant |r| values when using gene expression as the genomic feature than when using copy number (Table 2), which corresponds with previous work showing that gene expression is an informative molecular feature when assessing drug sensitivity [@jang2014; @sirota2011].
 Additionally, in all cases, there are more significant r values when using copy number than there are significant p-values from the mutation status comparisons.
@@
 Additionally, across all three genomic features, CTRP consistently identified a higher percentage of its possible level-A G2P associations than GDSC, and similarly, GDSC identified a higher percentage than CCLE.
-In the CCLE-GDSC debate, inconsistency between the datasets was attributed to the groups using two very different assays for generating AUC measurements though it was undecided which was more accurate (Haibe-Kains et al., 2013; Jang et al., 2014; Weinstein & Lorenzi, 2013).
+In the CCLE-GDSC debate, inconsistency between the datasets was attributed to the groups using two very different assays for generating AUC measurements though it was undecided which was more accurate[@haibe-kains2013; @jang2014; @weinstein2013].
 Our results provide very preliminary evidence that GDSC is more accurate than CCLE in regards to reproducing clinical associations.
@@
 
-In the 894 level-A G2P interpretations, there was a wide variation in the specificity of cancer description, ranging from “Waldenström macroglobulinemia” and “hyper eosinophilic advanced syndrome” on the more detailed end to “cancer” on the broad end.
+In the `r nrow(g2p_filt)` level-A G2P interpretations, there was a wide variation in the specificity of cancer description, ranging from “Waldenström macroglobulinemia” and “hyper eosinophilic advanced syndrome” on the more detailed end to “cancer” on the broad end.
 Similarly, the drug screen datasets had a wide range in lineage specificity, e.g.
-CCLE, GTRP, and GDSC all had lineages labeled “leukemia” and “T-cell childhood acute lymphocytic leukemia” and the CRISPR dataset had cell lines labeled “Epstein-Barr virus-related Burkitt lymphoma” and “lymphoma.” To more easily conduct comparative analyses in a cancer-specific manner, we developed a more general lineage grouping method derived from the Human Disease Ontology identity codes (DOIDs, http://disease-ontology.org/) (Schriml et al., 2019) assigned to each cell line, yielding 27 unique lineage groupings.
+CCLE, GTRP, and GDSC all had lineages labeled “leukemia” and “T-cell childhood acute lymphocytic leukemia” and the CRISPR dataset had cell lines labeled “Epstein-Barr virus-related Burkitt lymphoma” and “lymphoma.” To more easily conduct comparative analyses in a cancer-specific manner, we developed a more general lineage grouping method derived from the Human Disease Ontology identity codes (DOIDs, http://disease-ontology.org/) [@schriml2019] assigned to each cell line, yielding 27 unique lineage groupings.
 This custom lineage grouping was included in our harmonized cancer cell line database (see METHODS).
 
-In the level-A G2P interpretations, there were 102 unique drug-gene-lineage combinations (DGLs), representing seven of our curated cancer lineages: cancer, breast cancer, leukemia, lung cancer, ovarian cancer, skin cancer, and thyroid cancer.
+In the level-A G2P interpretations, there were `r nrow(g2p_dgl_tally)` unique drug-gene-lineage combinations (DGLs), representing seven of our curated cancer lineages: cancer, breast cancer, leukemia, lung cancer, ovarian cancer, skin cancer, and thyroid cancer.
 CCLE had data for nine DGLs, CTRP had data for 61, and GDSC had data for 53, yielding a total of 73 unique DGLs across all three datasets.
 
-At an alpha of 0.05, no DGLs were identified in the CCLE screen when using mutation status as a correlate (n = 7), but CTRP and GDSC identified six and five, respectively, in skin cancer, lung cancer, and cancer.
-These significant associations did not hold after Bonferroni correction in CTRP (n = 48, $\alpha$adjusted = 0.001) or GDSC (n = 39, $\alpha$adjusted = 0.001).
+At an $\alpha =  0.05$, no DGLs were identified in the CCLE screen when using mutation status as a correlate (n = 7), but CTRP and GDSC identified six and five, respectively, in skin cancer, lung cancer, and cancer.
+These significant associations did not hold after Bonferroni correction in CTRP ($n = 48$, $\alpha_{adjusted} = 0.001$) or GDSC ($n = 39$, $\alpha_{adjusted} = 0.001$).
 
-When using gene expression as the genomic feature, three CCLE DGLs had significant correlations at an adjusted alpha of 0.006 (n = 9).
-Two of these three DGLs were also significantly correlated with copy number (n = 9, $\alpha$adjusted = 0.006).
+When using gene expression as the genomic feature, three CCLE DGLs had significant correlations at an adjusted $\alpha =  0.006$ ($n = 9$).
+Two of these three DGLs were also significantly correlated with copy number ($n = 9$, $\alpha_{adjusted} = 0.006$).
 
-In CTRP, AUC of 19 DGLs significantly correlated with gene expression, 12 of which were significant after correction (n = 61, $\alpha$adjusted = 0.0008).
-Copy number correlations were significant for 12 DGLs, with three DGLs significant post-correction (n = 61, $\alpha$adjusted = 0.0008).
+In CTRP, AUC of 19 DGLs significantly correlated with gene expression, 12 of which were significant after correction ($n = 61$, $\alpha_{adjusted} = 0.0008$).
+Copy number correlations were significant for 12 DGLs, with three DGLs significant post-correction ($n = 61$, $\alpha_{adjusted} = 0.0008$).
 
 AUC of 16 DGLs in GDSC significantly correlated with gene expression.
-At an adjusted alpha of 0.0009 (n = 53) eight of them were significant.
-Fewer DGLs were significant when correlating AUC with copy number with 6 significant at an alpha of 0.05 and 1 significant at an adjusted alpha of 0.0009 (n = 53).
+At an adjusted $\alpha$ of 0.0009 ($n = 53$) eight of them were significant.
+Fewer DGLs were significant when correlating AUC with copy number with 6 significant at an $\alpha$ of 0.05 and 1 significant at an adjusted $\alpha$ of 0.0009 ($n = 53$).
 
-Interestingly, when we test the effect of mutation status on drug response for the DGLs derived from all pairwise combinations of G2P drugs and genes… (Figure ##1).
+Interestingly, when we test the effect of mutation status on drug response for the DGLs derived from all pairwise combinations of G2P drugs and genes… (*Figure ##1*).
 
@@
 
-The CRISPR screen from the Broad Institute reports gene dependency using CERES scores (Meyers et al., 2017), which are generated from sgRNA depletion scores and eliminate bias arising from the effect of copy number variation on Cas9 DNA cleavage.
+The CRISPR screen from the Broad Institute reports gene dependency using CERES scores [@meyers2017], which are generated from sgRNA depletion scores and eliminate bias arising from the effect of copy number variation on Cas9 DNA cleavage.
 The lower the CERES score, the higher the likelihood that the gene is essential in the associated cell line.
@@
 
-When we don’t account for lineage, Wilcoxon rank-sum tests revealed that mutations in eight of the 33 (24.2%) G2P genes significantly correlated with CERES score ($\alpha$ = 0.05): KRAS (p < 0.001), BRAF (p < 0.001), BRCA2  (p < 0.001), CYP19A1 (p = 0.004), TSC2 (p = 0.005), JAK2 (p = 0.031), DPYD (p = 0.042), and UGT1A1 (p = 0.048).
+When we don’t account for lineage, Wilcoxon rank-sum tests revealed that mutations in eight of the 33 (24.2%) G2P genes significantly correlated with CERES score ($\alpha = 0.05$): KRAS ($p < 0.001$), BRAF ($p < 0.001$), BRCA2  ($p < 0.001$), CYP19A1 ($p = 0.004$), TSC2 ($p = 0.005$), JAK2 ($p = 0.031$), DPYD ($p = 0.042$), and UGT1A1 ($p = 0.048$).
 Gene expression (RPKM) of 17 (51.5%) G2P genes significantly correlated with CERES score, as did copy number (log2-ratio) for 14 (42.4%) G2P genes (Figure ##2).
@@
 
-In a lineage-agnostic context of the CRISPR screen, ERBB2 gene essentiality score had a significant negative correlation with ERBB2 gene expression (p < 10-12, r = -0.31) and ERBB2 copy number (p < 10-15, r = -0.34) (Figure ##2).
-Similarly, MET gene essentiality also correlated with both MET gene expression (p < 10-12, r = -0.31) and copy number (p < 10-8, r = -0.25).
-Notably, BRCA1 also significantly correlated with both gene expression (p < 0.001, r = 0.16) and copy number (p < 0.01, r = 0.14).
-BRCA2 significantly correlated with all three of the genomic features tested: gene expression (p < 0.05, r = 0.10), copy number (p < 10-7, r = 0.23), and mutation status (p < 0.001).
+In a lineage-agnostic context of the CRISPR screen, ERBB2 gene essentiality score had a significant negative correlation with ERBB2 gene expression ($p < 10^{-12}$, $r = -0.31$) and ERBB2 copy number ($p < 10^{-15}$, $r = -0.34$) (*Figure ##2*).
+Similarly, MET gene essentiality also correlated with both MET gene expression ($p < 10^{-12}$, $r = -0.31$) and copy number ($p < 10^{-8}$, $r = -0.25$).
+Notably, BRCA1 also significantly correlated with both gene expression ($p < 0.001$, $r = 0.16$) and copy number ($p < 0.01$, $r = 0.14$).
+BRCA2 significantly correlated with all three of the genomic features tested: gene expression ($p < 0.05$, $r = 0.10$), copy number ($p < 10^{-7}$, $r = 0.23$), and mutation status ($p < 0.001$).
 
 ## Which genomic features drive KRAS, EGFR, and BRAF drug-gene associations?
+
+**Should we do this?**
 
@@
 We have demonstrated that on its own, mutation status is not a robust predictor of drug efficacy and that copy number and gene expression fare better as predictors.
-However, for these three genomic features in all three datasets, only 11.1% (mutation status, 1 of 9, CCLE) to 47.9% (gene expression, 23 of 48, CTRP) (Table 2), of the level-A G2P drug-gene associations in the respective dataset were significant at an uncorrected $\alpha$ = 0.05.
+However, for these three genomic features in all three datasets, only 11.1% (mutation status, 1 of 9, CCLE) to 47.9% (gene expression, 23 of 48, CTRP) (Table 2), of the level-A G2P drug-gene associations in the respective dataset were significant at an uncorrected $\alpha = 0.05$.
 This suggests that while the drug screens successfully identify some clinically relevant drug-gene associations, many associations are also missed, which raises the question of the extent to which clinical researchers can rely on in vitro drug screens when attempting to develop and select therapeutics for cancer patients.
@@
 
+To preclude variation in genomic feature calls across the datasets, we used identical annotations from CCLE for all cell lines screened in the three datasets.
 The CCLE provided mutation annotations in 19,280 genes across 1,596 cell lines (dataset: depmap_18Q4_mutation_calls.csv, accessed 14 November 2018).
@@
 The CCLE reports cell line sensitivity to small molecules as an activity area measured above the dose-response curve (ActArea), while both CTRP and GDSC report small molecule activity as area under the dose-response curve (AUC).
-Since ActArea is reported with a scale of 0 to 8, we converted CCLE’s ActArea values to AUC via:
+Since ActArea is reported with a scale of 0 to 8, we converted CCLE’s ActArea values to AUC via
 
@@
 
-For Figure 1, all data were imported and manipulated using pandas (v0.23.0) [@mckinney2011] and plotted using seaborn (v0.90) [@waskom2012], which sat on top of matplotlib (v2.2.2) [@hunter2007] and was executed on Python (v2.7.15) (Python Software Foundation, https://www.python.org/) in an IPython (v5.5.0) [@perez2007] kernel within a localhost Jupyter (v5.2.2) notebook [@kluyver2016].
+For *Figure 1*, all data were imported and manipulated using pandas (v0.23.0) [@mckinney2011] and plotted using seaborn (v0.90) [@waskom2012], which sat on top of matplotlib (v2.2.2) [@hunter2007] and was executed on Python (v2.7.15) (Python Software Foundation, https://www.python.org/) in an IPython (v5.5.0) [@perez2007] kernel within a localhost Jupyter (v5.2.2) notebook [@kluyver2016].
 All other analyses were conducted in R (v3.5.0) (R Foundation for Statistical Computing, https://www.R-project.org/) in an RStudio environment (v1.1.447) [@rstudio2012].

### 2018-12-21 manuscript.tex
work on manuscript updates

@@
 
+\begin{table}[tbp]
+\begin{center}
+\begin{threeparttable}
+\caption{\label{tab:table-g2p-nonCID}Distribution of level-A G2P drugs excluded from analyses}
+\begin{tabular}{llll}
+\toprule
+Compound & \multicolumn{1}{c}{Compound identifier} & \multicolumn{1}{c}{Number of G2P interpretations} & \multicolumn{1}{c}{Proportion of excluded interpretations (\%)}\\
+\midrule
+cetuximab & CHEMBL1201577 & 74 & 18.41\\
+cisplatin & CHEMBL2068237 & 3 & 0.75\\
+egfr & SID160769799 & 1 & 0.25\\
+ipilimumab & CHEMBL1789844 & 2 & 0.50\\
+mab & CHEMBL2109423 & 16 & 3.98\\
+nivolumab & CHEMBL2108738 & 4 & 1.00\\
+panitumumab & CHEMBL1201827 & 75 & 18.66\\
+pembrolizumab & CHEMBL3137343 & 3 & 0.75\\
+pertuzumab & CHEMBL2007641 & 1 & 0.25\\
+trastuzumab & CHEMBL1201585 & 9 & 2.24\\
+NA & NA & 214 & 53.23\\
+\bottomrule
+\addlinespace
+\end{tabular}
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} mAb = monoclonal antibody; NA indicates G2P interpretation does not have an associated compound}
+\end{tablenotes}
+\end{threeparttable}
+\end{center}
+\end{table}
+
 G2P designed a set of standards for stratifying their database's cancer
@@
 interpretations that did not have an associated compound, resulting in
-removal of 402 interpretations (Table 1). It should be noted that
-cisplatin, a small molecule, was excluded due to its being indexed with
-a ChEMBLdb identifier (\url{https://www.ebi.ac.uk/chembl/}), which we
-did not manually re-index to a CID to avoid accidental
-mischaracterization.
+removal of 402 interpretations Table~\ref{tab:table-g2p-nonCID}. It
+should be noted that cisplatin, a small molecule, was excluded due to
+its being indexed with a ChEMBLdb identifier
+(\url{https://www.ebi.ac.uk/chembl/}), which we did not manually
+re-index to a CID to avoid accidental mischaracterization.
 
@@
 subsequent analyses, constituting 57 unique drugs and 34 unique genes in
-88 distinct level-A combinations (Figure 1A). The number of level-A
-interpretations per drug ranged from 1 to 176 (M = 15.7, SD = 34.6),
-from 1 to 264 (M = 26.2, SD = 61.6) per gene, and for each level-A
-drug-gene combination, the range was 1 to 103 (M = 10.1, SD = 19.8).
-These unique drugs, genes, and combinations are hereafter referred to as
-G2P drugs, G2P genes, and G2P associations. Of the 57 unique G2P drugs,
-37 of them were screened in at least one of the drug screen datasets, 14
-were screened in two of the three datasets, and only three drugs were
-screened in all three datasets. The remaining 20 un-screened G2P drugs
-suggests an incompleteness of these drug screens, though these projects
-frequently release new screening data that may include these drugs in
-future releases.
+88 distinct level-A combinations (\emph{Figure 1A}). The number of
+level-A interpretations per drug ranged from 1 to 176 (\(M =\) 15.68,
+\(SD =\) 34.63), 1 to 264 (\(M =\) 26.24, \(SD =\) 61.58) per gene, and
+for each level-A drug-gene combination, the range was 1 to 103 (\(M =\)
+10.14, \(SD =\) 19.80). These unique drugs, genes, and combinations are
+hereafter referred to as G2P drugs, G2P genes, and G2P associations. Of
+the 57 unique G2P drugs, 37 of them were screened in at least one of the
+drug screen datasets, 14 were screened in two of the three datasets, and
+only three drugs were screened in all three datasets. The remaining 20
+un-screened G2P drugs suggests an incompleteness of these drug screens,
+though these projects frequently release new screening data that may
+include these drugs in future releases.
 
@@
 for each G2P drug tested in the CCLE, CTRP, and GDSC drug screens
-(Figures 1B and 2A). At uncorrected \(\alpha\) = 0.05, Wilcoxon rank-sum
-tests revealed that in CCLE, the AUC distributions of mutant and
-wildtype groups for 10 out of 170 (5.88\%) tested drug-gene combinations
-were significantly different, 91 out of 918 (9.91\%) were significantly
-different for CTRP, and 61 out of 850 (7.18\%) for GDSC. We observe
-little concordance between the number of interpretations for each G2P
-association and the significance of mutation status on AUC for said G2P
-association, suggesting that mutation status alone is not a robust
-predictor of clinically actionable genetic targets. This led us to
-examine the correlations between AUC and gene expression and AUC and
+(\emph{Figures 1B and 2A}). At uncorrected \(\alpha = 0.05\), Wilcoxon
+rank-sum tests revealed that in CCLE, the AUC distributions of mutant
+and wildtype groups for 10 out of 170 (5.88\%) tested drug-gene
+combinations were significantly different, 91 out of 918 (9.91\%) were
+significantly different for CTRP, and 61 out of 850 (7.18\%) for GDSC.
+We observe little concordance between the number of interpretations for
+each G2P association and the significance of mutation status on AUC for
+said G2P association, suggesting that mutation status alone is not a
+robust predictor of clinically actionable genetic targets. This led us
+to examine the correlations between AUC and gene expression and AUC and
 copy number, two other genomic features that are known to associate with
@@
 
-We compared the distribution of level-A G2P associations (Figure 1A) and
-the associated p-values from the mutation status comparisons (Figure 1B)
-with a null distribution of p-values derived from all pairwise
-combinations of G2P genes and the G2P drugs tested in each dataset, less
-any of the 88 distinct combinations with G2P interpretations, i.e.~the
-non-gray squares in the right heatmap of Figure 1A (Figure 3A). To
-formally test concordance between clinically actionable variants and
-drug screen results, we conducted an independent, two-group t-test to
-compare the distributions of p-values of drug-gene combinations that
-either were or were not represented with level-A evidence in G2P, which
-indicated that the distributions of p-values did not significantly
-differ for CCLE {[}t(9) = 0.25, p = 0.81{]}, CTRP {[}t(51) = 0.85, p =
-0.40{]}, nor GDSC {[}t(47) = -0.56, p = 0.58{]} (Table 2). This further
-supports that mutation status is not a robust genomic feature for
-predicting therapeutic responses.
+We compared the distribution of level-A G2P associations (\emph{Figure
+1A}) and the associated p-values from the mutation status comparisons
+(\emph{Figure 1B}) with a null distribution of p-values derived from all
+pairwise combinations of G2P genes and the G2P drugs tested in each
+dataset, less any of the 88 distinct combinations with G2P
+interpretations, i.e.~the non-gray squares in the right heatmap of
+\emph{Figure 1A (Figure 3A}). To formally test concordance between
+clinically actionable variants and drug screen results, we conducted an
+independent, two-group t-test to compare the distributions of p-values
+of drug-gene combinations that either were or were not represented with
+level-A evidence in G2P, which indicated that the distributions of
+p-values did not significantly differ for CCLE {[}t(9) = 0.25, p =
+0.81{]}, CTRP {[}t(51) = 0.85, p = 0.40{]}, nor GDSC {[}t(47) = -0.56, p
+= 0.58{]} (Table 2). This further supports that mutation status is not a
+robust genomic feature for predicting therapeutic responses.
 
@@
 associations and gene expression (RPKM) and copy number (log2 ratio) of
-the gene in the association (Figures 3B-C). Example r derivations are
-shown in Figures 2B-C. Absolute values of r were used to simplify
-extreme values in both directions for testing. The difference in the
-CCLE \textbar{}r\textbar{} distributions for both gene expression
+the gene in the association (\emph{Figures 3B-C}). Example r derivations
+are shown in \emph{Figures 2B-C}. Absolute values of r were used to
+simplify extreme values in both directions for testing. The difference
+in the CCLE \textbar{}r\textbar{} distributions for both gene expression
 {[}t(8) = 1.43, p = 0.19{]} and copy number {[}t(8) = 2.48, p = 0.23{]}
@@
 two very different assays for generating AUC measurements though it was
-undecided which was more accurate (Haibe-Kains et al., 2013; Jang et
-al., 2014; Weinstein \& Lorenzi, 2013). Our results provide very
-preliminary evidence that GDSC is more accurate than CCLE in regards to
-reproducing clinical associations. However, CTRP may be even more
-accurate than both GDSC and CCLE.
+undecided which was more accurate(Haibe-Kains et al., 2013; Jang et al.,
+2014; Weinstein \& Lorenzi, 2013). Our results provide very preliminary
+evidence that GDSC is more accurate than CCLE in regards to reproducing
+clinical associations. However, CTRP may be even more accurate than both
+GDSC and CCLE.
 
@@
 
-At an alpha of 0.05, no DGLs were identified in the CCLE screen when
+At an \(\alpha = 0.05\), no DGLs were identified in the CCLE screen when
 using mutation status as a correlate (n = 7), but CTRP and GDSC
@@
 cancer. These significant associations did not hold after Bonferroni
-correction in CTRP (n = 48, \(\alpha\)adjusted = 0.001) or GDSC (n = 39,
-\(\alpha\)adjusted = 0.001).
+correction in CTRP (\(n = 48\), \(\alpha_{adjusted} = 0.001\)) or GDSC
+(\(n = 39\), \(\alpha_{adjusted} = 0.001\)).
 
 When using gene expression as the genomic feature, three CCLE DGLs had
-significant correlations at an adjusted alpha of 0.006 (n = 9). Two of
-these three DGLs were also significantly correlated with copy number (n
-= 9, \(\alpha\)adjusted = 0.006).
+significant correlations at an adjusted \(\alpha = 0.006\) (\(n = 9\)).
+Two of these three DGLs were also significantly correlated with copy
+number (\(n = 9\), \(\alpha_{adjusted} = 0.006\)).
 
 In CTRP, AUC of 19 DGLs significantly correlated with gene expression,
-12 of which were significant after correction (n = 61,
-\(\alpha\)adjusted = 0.0008). Copy number correlations were significant
-for 12 DGLs, with three DGLs significant post-correction (n = 61,
-\(\alpha\)adjusted = 0.0008).
+12 of which were significant after correction (\(n = 61\),
+\(\alpha_{adjusted} = 0.0008\)). Copy number correlations were
+significant for 12 DGLs, with three DGLs significant post-correction
+(\(n = 61\), \(\alpha_{adjusted} = 0.0008\)).
 
 AUC of 16 DGLs in GDSC significantly correlated with gene expression. At
-an adjusted alpha of 0.0009 (n = 53) eight of them were significant.
-Fewer DGLs were significant when correlating AUC with copy number with 6
-significant at an alpha of 0.05 and 1 significant at an adjusted alpha
-of 0.0009 (n = 53).
+an adjusted \(\alpha\) of 0.0009 (\(n = 53\)) eight of them were
+significant. Fewer DGLs were significant when correlating AUC with copy
+number with 6 significant at an \(\alpha\) of 0.05 and 1 significant at
+an adjusted \(\alpha\) of 0.0009 (\(n = 53\)).
 
@@
 response for the DGLs derived from all pairwise combinations of G2P
-drugs and genes\ldots{} (Figure \#\#1).
+drugs and genes\ldots{} (\emph{Figure \#\#1}).
 
@@
 mutations in eight of the 33 (24.2\%) G2P genes significantly correlated
-with CERES score (\(\alpha\) = 0.05): KRAS (p \textless{} 0.001), BRAF
-(p \textless{} 0.001), BRCA2 (p \textless{} 0.001), CYP19A1 (p = 0.004),
-TSC2 (p = 0.005), JAK2 (p = 0.031), DPYD (p = 0.042), and UGT1A1 (p =
-0.048). Gene expression (RPKM) of 17 (51.5\%) G2P genes significantly
-correlated with CERES score, as did copy number (log2-ratio) for 14
-(42.4\%) G2P genes (Figure \#\#2). For the purpose of comparison to the
-drug screen data, if we treat CRISPR knockdown like a small-molecule
-drug, then these results are similar to the results from CCLE, CTRP, and
-GDSC (Table 2).
+with CERES score (\(\alpha = 0.05\)): KRAS (\(p < 0.001\)), BRAF
+(\(p < 0.001\)), BRCA2 (\(p < 0.001\)), CYP19A1 (\(p = 0.004\)), TSC2
+(\(p = 0.005\)), JAK2 (\(p = 0.031\)), DPYD (\(p = 0.042\)), and UGT1A1
+(\(p = 0.048\)). Gene expression (RPKM) of 17 (51.5\%) G2P genes
+significantly correlated with CERES score, as did copy number
+(log2-ratio) for 14 (42.4\%) G2P genes (Figure \#\#2). For the purpose
+of comparison to the drug screen data, if we treat CRISPR knockdown like
+a small-molecule drug, then these results are similar to the results
+from CCLE, CTRP, and GDSC (Table 2).
 
@@
 essentiality score had a significant negative correlation with ERBB2
-gene expression (p \textless{} 10-12, r = -0.31) and ERBB2 copy number
-(p \textless{} 10-15, r = -0.34) (Figure \#\#2). Similarly, MET gene
-essentiality also correlated with both MET gene expression (p
-\textless{} 10-12, r = -0.31) and copy number (p \textless{} 10-8, r =
--0.25). Notably, BRCA1 also significantly correlated with both gene
-expression (p \textless{} 0.001, r = 0.16) and copy number (p
-\textless{} 0.01, r = 0.14). BRCA2 significantly correlated with all
-three of the genomic features tested: gene expression (p \textless{}
-0.05, r = 0.10), copy number (p \textless{} 10-7, r = 0.23), and
-mutation status (p \textless{} 0.001).
+gene expression (\(p < 10^{-12}\), \(r = -0.31\)) and ERBB2 copy number
+(\(p < 10^{-15}\), \(r = -0.34\)) (\emph{Figure \#\#2}). Similarly, MET
+gene essentiality also correlated with both MET gene expression
+(\(p < 10^{-12}\), \(r = -0.31\)) and copy number (\(p < 10^{-8}\),
+\(r = -0.25\)). Notably, BRCA1 also significantly correlated with both
+gene expression (\(p < 0.001\), \(r = 0.16\)) and copy number
+(\(p < 0.01\), \(r = 0.14\)). BRCA2 significantly correlated with all
+three of the genomic features tested: gene expression (\(p < 0.05\),
+\(r = 0.10\)), copy number (\(p < 10^{-7}\), \(r = 0.23\)), and mutation
+status (\(p < 0.001\)).
 
@@
 associations?}\label{which-genomic-features-drive-kras-egfr-and-braf-drug-gene-associations}
+
+\textbf{Should we do this?}
 
@@
 level-A G2P drug-gene associations in the respective dataset were
-significant at an uncorrected \(\alpha\) = 0.05. This suggests that
+significant at an uncorrected \(\alpha = 0.05\). This suggests that
 while the drug screens successfully identify some clinically relevant
@@
 
-The CCLE provided mutation annotations in 19,280 genes across 1,596 cell
-lines (dataset: depmap\_18Q4\_mutation\_calls.csv, accessed 14 November
-2018). CCLE called substitutions using MuTect (Cibulskis et al., 2013)
-and annotated variants using Oncotator (Ramos et al., 2015) and indels
-using Indelocator
+To preclude variation in genomic feature calls across the datasets, we
+used identical annotations from CCLE for all cell lines screened in the
+three datasets. The CCLE provided mutation annotations in 19,280 genes
+across 1,596 cell lines (dataset: depmap\_18Q4\_mutation\_calls.csv,
+accessed 14 November 2018). CCLE called substitutions using MuTect
+(Cibulskis et al., 2013) and annotated variants using Oncotator (Ramos
+et al., 2015) and indels using Indelocator
 (\url{https://software.broadinstitute.org/cancer/cga/indelocator}). We
@@
 curve (AUC). Since ActArea is reported with a scale of 0 to 8, we
-converted CCLE's ActArea values to AUC via:
+converted CCLE's ActArea values to AUC via
 
@@
 
-For Figure 1, all data were imported and manipulated using pandas
+For \emph{Figure 1}, all data were imported and manipulated using pandas
 (v0.23.0) (McKinney, 2011) and plotted using seaborn (v0.90) (Waskom,
@@
 
+\hypertarget{ref-sirota2011}{}
+Sirota, M., Dudley, J. T., Kim, J., Chiang, A. P., Morgan, A. A.,
+Sweet-Cordero, A., \ldots{} Butte, A. J. (2011). Discovery and
+preclinical validation of drug indications using compendia of public
+gene expression data. \emph{Science Translational Medicine},
+\emph{3}(96), 96ra77.
+doi:\href{https://doi.org/10.1126/scitranslmed.3001318}{10.1126/scitranslmed.3001318}
+
 \hypertarget{ref-stinson1992}{}
@@
 
+\hypertarget{ref-weinstein2013}{}
+Weinstein, J. N., \& Lorenzi, P. L. (2013). Discrepancies in drug
+sensitivity, \emph{504}(7480), 381--313.
+doi:\href{https://doi.org/10.1038/504383a}{10.1038/504383a}
+
 \hypertarget{ref-wickham2016}{}

### 2019-01-02 manuscript_analysis.Rmd
updated stats with AUC_zscore instead of AUC

@@
 ccle_cor_res <- ccle_data_g2p_grid %>% group_by(Drug_Gene) %>%
-                    summarize(Pearson_Corr_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
-                              Pearson_Pval_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
-                              Pearson_Corr_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$estimate,
-                              Pearson_Pval_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$p.value,
-                              Spearman_Corr_GE = cor.test(y = AUC, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
-                              Spearman_Pval_GE = cor.test(y = AUC, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
-                              Spearman_Corr_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$estimate,
-                              Spearman_Pval_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$p.value)
+                    summarize(Pearson_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
+                              Pearson_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
+                              Pearson_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$estimate,
+                              Pearson_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$p.value,
+                              Spearman_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
+                              Spearman_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
+                              Spearman_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$estimate,
+                              Spearman_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$p.value)
 ccle_cor_res <- merge(g2p_druggene_tally, ccle_cor_res, by = "Drug_Gene", all.y = TRUE)
@@
 ctrp_cor_res <- ctrp_data_g2p_grid %>% group_by(Drug_Gene) %>%
-                    summarize(Pearson_Corr_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
-                              Pearson_Pval_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
-                              Pearson_Corr_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$estimate,
-                              Pearson_Pval_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$p.value,
-                              Spearman_Corr_GE = cor.test(y = AUC, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
-                              Spearman_Pval_GE = cor.test(y = AUC, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
-                              Spearman_Corr_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$estimate,
-                              Spearman_Pval_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$p.value)
+                    summarize(Pearson_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
+                              Pearson_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
+                              Pearson_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$estimate,
+                              Pearson_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$p.value,
+                              Spearman_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
+                              Spearman_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
+                              Spearman_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$estimate,
+                              Spearman_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$p.value)
 ctrp_cor_res <- merge(g2p_druggene_tally, ctrp_cor_res, by = "Drug_Gene", all.y = TRUE)
@@
 gdsc_cor_res <- gdsc_data_g2p_grid %>% group_by(Drug_Gene) %>%
-                    summarize(Pearson_Corr_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
-                              Pearson_Pval_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
-                              Pearson_Corr_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$estimate,
-                              Pearson_Pval_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$p.value,
-                              Spearman_Corr_GE = cor.test(y = AUC, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
-                              Spearman_Pval_GE = cor.test(y = AUC, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
-                              Spearman_Corr_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$estimate,
-                              Spearman_Pval_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$p.value)
+                    summarize(Pearson_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
+                              Pearson_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
+                              Pearson_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$estimate,
+                              Pearson_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$p.value,
+                              Spearman_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
+                              Spearman_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
+                              Spearman_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$estimate,
+                              Spearman_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$p.value)
 gdsc_cor_res <- merge(g2p_druggene_tally, gdsc_cor_res, by = "Drug_Gene", all.y = TRUE)

### 2019-01-04 manuscript.Rmd
update manuscript.Rmd for reproducibility in results sections

@@
 ---
-title             : "Manuscript"
+title             : "Manuscript Draft"
 shorttitle        : "Subtitle"
@@
 
-```{r g2p-data, include=FALSE}
+```{r g2p-data, echo=FALSE, include=FALSE}
 ccl_converter <- read.delim("./data_munging/cell_line_database_v1_20180911.tsv", row.names = 1, sep = "\t", header = TRUE)
@@
 length(unique(g2p_dgl_tally$Gene))
-unique(g2p_filt$Phenotype.Description)
+g2p_lins <- as.character(unique(g2p_dgl_tally$group_general_lineage_name))
+```
+
+```{r drug-data, echo=FALSE, include=FALSE}
+ccle_data <- readRDS("./data_munging/rds/ccle_data_18Q4_g2pgenes.rds")
+ccle_data_ptmuts <- filter(ccle_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
+ccle_data_ptmuts$Keep_PtMut_Tests <- ifelse(ccle_data_ptmuts$Reference_Allele_Length == 1 | is.na(ccle_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(ccle_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
+ccle_data_ptmuts <- filter(ccle_data_ptmuts, Keep_PtMut_Tests == TRUE)
+ccle_data_ptmuts$Dataset <- "CCLE"
+ccle_data_ptmuts$Hugo_Symbol <- ordered(ccle_data_ptmuts$Hugo_Symbol, levels = g2p_genes)
+
+ctrp_data <- readRDS("./data_munging/rds/ctrp_data_18Q4_g2pgenes.rds")
+ctrp_data_ptmuts <- filter(ctrp_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
+ctrp_data_ptmuts$Keep_PtMut_Tests <- ifelse(ctrp_data_ptmuts$Reference_Allele_Length == 1 | is.na(ctrp_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(ctrp_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
+ctrp_data_ptmuts <- filter(ctrp_data_ptmuts, Keep_PtMut_Tests == TRUE)
+ctrp_data_ptmuts$Dataset <- "CTRP"
+ctrp_data_ptmuts$Hugo_Symbol <- ordered(ctrp_data_ptmuts$Hugo_Symbol, levels = g2p_genes)
+
+gdsc_data <- readRDS("./data_munging/rds/gdsc_data_18Q4_g2pgenes.rds")
+gdsc_data_ptmuts <- filter(gdsc_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
+gdsc_data_ptmuts$Keep_PtMut_Tests <- ifelse(gdsc_data_ptmuts$Reference_Allele_Length == 1 | is.na(gdsc_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(gdsc_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
+gdsc_data_ptmuts <- filter(gdsc_data_ptmuts, Keep_PtMut_Tests == TRUE)
+gdsc_data_ptmuts$Dataset <- "GDSC"
+gdsc_data_ptmuts$Hugo_Symbol <- ordered(gdsc_data_ptmuts$Hugo_Symbol, levels = g2p_genes)
+
+# Filter drug screen datasets for G2P drug-gene associations
+ccle_data_g2p <- filter(ccle_data_ptmuts, Drug_Gene %in% g2p_druggenes)
+ccle_data_g2p$Mutation_Status_Nonsilent <- factor(ccle_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
+ctrp_data_g2p <- filter(ctrp_data_ptmuts, Drug_Gene %in% g2p_druggenes)
+ctrp_data_g2p$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
+gdsc_data_g2p <- filter(gdsc_data_ptmuts, Drug_Gene %in% g2p_druggenes)
+gdsc_data_g2p$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
+
+# Filter drug screen datasets for G2P drug-gene-lineage associations
+ccle_data_g2p_dgl <- filter(ccle_data_ptmuts, Drug_Gene_Lin %in% g2p_dgls)
+ccle_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(ccle_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
+ctrp_data_g2p_dgl <- filter(ctrp_data_ptmuts, Drug_Gene_Lin %in% g2p_dgls)
+ctrp_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
+gdsc_data_g2p_dgl <- filter(gdsc_data_ptmuts, Drug_Gene_Lin %in% g2p_dgls)
+gdsc_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
+
+# Filter drug screen datasets for G2P drugs and genes
+ccle_data_g2p_grid <- filter(ccle_data_ptmuts, Drug %in% g2p_drugs)
+ccle_data_g2p_grid$Mutation_Status_Nonsilent <- factor(ccle_data_g2p_grid$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
+ctrp_data_g2p_grid <- filter(ctrp_data_ptmuts, Drug %in% g2p_drugs)
+ctrp_data_g2p_grid$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p_grid$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
+gdsc_data_g2p_grid <- filter(gdsc_data_ptmuts, Drug %in% g2p_drugs)
+gdsc_data_g2p_grid$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p_grid$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
+
+# Dataset counts
+drug_summ <- data.frame(Drug = character(), Dataset_Count = integer(), stringsAsFactors = FALSE)
+for(drug in g2p_drugs) {
+  counter = 0
+  if(drug %in% as.character(unique(ccle_data_g2p$Drug))) { counter <- counter + 1 }
+  if(drug %in% as.character(unique(ctrp_data_g2p$Drug))) { counter <- counter + 1 }
+  if(drug %in% as.character(unique(gdsc_data_g2p$Drug))) { counter <- counter + 1 }
+  drug_summ <- rbind(drug_summ, data.frame(Drug = drug, Dataset_Count = counter))
+}
 ```
@@
           note = "mAb = monoclonal antibody; NA indicates G2P interpretation does not have an associated compound")
+```
+
+```{r ccldb, echo=FALSE, include=FALSE}
+ccl_converter <- read.delim("./data_munging/cell_line_database_v1_20180911.tsv", row.names = 1, sep = "\t", header = TRUE)
 ```
@@
 These unique drugs, genes, and combinations are hereafter referred to as G2P drugs, G2P genes, and G2P associations.
-Of the `r length(g2p_drugs)` unique G2P drugs, 37 of them were screened in at least one of the drug screen datasets, 14 were screened in two of the three datasets, and only three drugs were screened in all three datasets.
-The remaining 20 un-screened G2P drugs suggests an incompleteness of these drug screens, though these projects frequently release new screening data that may include these drugs in future releases.
+Filtering our screening datasets by these clinical criteria yields panels of potentially clinically relevant omic features.
+Of the `r length(g2p_drugs)` unique G2P drugs, `r nrow(drug_summ[drug_summ$Dataset_Count >= 1,])` of them were screened in at least one of the drug screen datasets, `r nrow(drug_summ[drug_summ$Dataset_Count >= 2,])` drugs were screened in at least two of the three datasets, and only `r nrow(drug_summ[drug_summ$Dataset_Count >= 3,])` were screened in all three datasets.
+The remaining `r nrow(drug_summ[drug_summ$Dataset_Count == 0,])` un-screened G2P drugs suggests an incompleteness of these drug screens, though these projects frequently release new screening data that may include these drugs in future releases.
 
-```{r}
+```{r grid-wilcox-res, echo = FALSE}
 ccle_signif_g2p_grid <- readRDS("./data_munging/rds/ccle_signif_g2p_grid.rds")
@@
 Similarly, the drug screen datasets had a wide range in lineage specificity, e.g.
-CCLE, GTRP, and GDSC all had lineages labeled “leukemia” and “T-cell childhood acute lymphocytic leukemia” and the CRISPR dataset had cell lines labeled “Epstein-Barr virus-related Burkitt lymphoma” and “lymphoma.” To more easily conduct comparative analyses in a cancer-specific manner, we developed a more general lineage grouping method derived from the Human Disease Ontology identity codes (DOIDs, http://disease-ontology.org/) [@schriml2019] assigned to each cell line, yielding 27 unique lineage groupings.
+CCLE, GTRP, and GDSC all had lineages labeled “leukemia” and “T-cell childhood acute lymphocytic leukemia” and the CRISPR dataset had cell lines labeled “Epstein-Barr virus-related Burkitt lymphoma” and “lymphoma.” To more easily conduct comparative analyses in a cancer-specific manner, we developed a more general lineage grouping method derived from the Human Disease Ontology identity codes (DOIDs, http://disease-ontology.org/) [@schriml2019] assigned to each cell line, yielding `r length(unique(ccl_converter$group_general_lineage_name))` unique lineage groupings.
 This custom lineage grouping was included in our harmonized cancer cell line database (see METHODS).
 
-In the level-A G2P interpretations, there were `r nrow(g2p_dgl_tally)` unique drug-gene-lineage combinations (DGLs), representing seven of our curated cancer lineages: cancer, breast cancer, leukemia, lung cancer, ovarian cancer, skin cancer, and thyroid cancer.
-CCLE had data for nine DGLs, CTRP had data for 61, and GDSC had data for 53, yielding a total of 73 unique DGLs across all three datasets.
+In the level-A G2P interpretations, there were `r nrow(g2p_dgl_tally)` unique drug-gene-lineage combinations (DGLs), representing seven of our curated cancer lineages: `r paste(g2p_lins[1:length(g2p_lins) -1], collapse = ", ")`, and `r g2p_lins[length(g2p_lins)]`.
+CCLE had data for `r length(unique(ccle_data_g2p_dgl$Drug_Gene_Lin))` DGLs, CTRP had data for `r length(unique(ctrp_data_g2p_dgl$Drug_Gene_Lin))`, and GDSC had data for `r length(unique(gdsc_data_g2p_dgl$Drug_Gene_Lin))`, yielding a total of `r length(union(union(unique(ccle_data_g2p_dgl$Drug_Gene_Lin), unique(ctrp_data_g2p_dgl$Drug_Gene_Lin)), unique(gdsc_data_g2p_dgl$Drug_Gene_Lin)))` unique DGLs across all three datasets.
+Only `r length(intersect(intersect(unique(ccle_data_g2p_dgl$Drug_Gene_Lin), unique(ctrp_data_g2p_dgl$Drug_Gene_Lin)), unique(gdsc_data_g2p_dgl$Drug_Gene_Lin)))` DGLs were screened in all three datasets,
 
@@
 We filtered mutation calls for point mutations, defined as single-nucleotide insertions, deletions, and substitutions, regardless of result, i.e.
-frameshift or missense mutation.
+frameshift, missense, or nonsense mutation.
 For this analysis, cell lines harboring non-silent point mutations were considered “mutant” for the gene in question.
@@
 
+```{r}
+r_v <- paste0("v", getRversion())
+# rstudio_v <- paste0("v", RStudio.Version()$version)
+ggplot_v <- paste0("v", packageVersion("ggplot2"))
+ggpubr_v <- paste0("v", packageVersion("ggpubr"))
+```
+
 For *Figure 1*, all data were imported and manipulated using pandas (v0.23.0) [@mckinney2011] and plotted using seaborn (v0.90) [@waskom2012], which sat on top of matplotlib (v2.2.2) [@hunter2007] and was executed on Python (v2.7.15) (Python Software Foundation, https://www.python.org/) in an IPython (v5.5.0) [@perez2007] kernel within a localhost Jupyter (v5.2.2) notebook [@kluyver2016].
-All other analyses were conducted in R (v3.5.0) (R Foundation for Statistical Computing, https://www.R-project.org/) in an RStudio environment (v1.1.447) [@rstudio2012].
-All other plots were drawn using the ggplot2 (v3.0.0) R package [@wickham2016].
+All other analyses were conducted in R (`r r_v`) [@rdevelopmentcoreteam2010, https://www.R-project.org/] in an RStudio environment (v1.1.447) [@rstudio2012].
+All other plots were drawn using the ggplot2 (`r ggplot_v`) R package [@wickham2016].
 
@@
 
-Wilcoxon tests were computed using the ggpubr (v.`r print(packageVersion("ggpubr"))`) R package [@kassambara2018].
+Wilcoxon tests were computed using the ggpubr (`r ggpubr_v`) R package [@kassambara2018].
 

### 2019-01-04 manuscript.tex

@@
 \hypersetup{unicode=true,
-            pdftitle={Manuscript},
+            pdftitle={Manuscript Draft},
             pdfauthor={Sally E. Claridge, Daniel M. Charytonowicz, \& Adam A. Margolin},
@@
 
-  \title{Manuscript}
+  \title{Manuscript Draft}
     \author{Sally E. Claridge\textsuperscript{1}, Daniel M.
@@
 \url{https://cancervariants.org/}), a Driver Project for the Global
-Alliance for Genomics and Health (GA4GH) (Genomics \& Health, 2016). The
-VICC has curated annotations of known cancer variants at varying levels
-of evidence from multiple resources (A. H. Wagner et al., 2018): the
-Precision Medicine Knowledgebase (L. Huang et al., 2016), MolecularMatch
+Alliance for Genomics and Health (GA4GH) (The Global Alliance for
+Genomics and Health, 2016). The VICC has curated annotations of known
+cancer variants at varying levels of evidence from multiple resources
+(A. H. Wagner et al., 2018): the Precision Medicine Knowledgebase (L.
+Huang et al., 2016), MolecularMatch
 (\url{https://www.molecularmatch.com/index.html}), OncoKB (Chakravarty
@@
 (\url{http://beacon-network.org/\#/}), which yields access to genetic
-mutation data from over 200 datasets as of 2016 (Genomics \& Health,
-2016). For drug screen datasets, we focus on three well-known,
-large-scale drug projects: the CCLE and GDSC, which were mentioned
-above, and the Center for the Science of Therapeutics at the Broad
-Institute's Cancer Therapeutics Response Portal (CTRP) dataset (Basu et
-al., 2013; M. G. Rees et al., 2016; B. Seashore-Ludlow et al., 2015). We
-also analyzed the results from a large-scale CRISPR/Cas9 screen
-conducted by the Broad Institute's Cancer Dependency Map project
+mutation data from over 200 datasets as of 2016 (The Global Alliance for
+Genomics and Health, 2016). For drug screen datasets, we focus on three
+well-known, large-scale drug projects: the CCLE and GDSC, which were
+mentioned above, and the Center for the Science of Therapeutics at the
+Broad Institute's Cancer Therapeutics Response Portal (CTRP) dataset
+(Basu et al., 2013; M. G. Rees et al., 2016; B. Seashore-Ludlow et al.,
+2015). We also analyzed the results from a large-scale CRISPR/Cas9
+screen conducted by the Broad Institute's Cancer Dependency Map project
 (DepMap) using the Avana knockout library (Doench et al., 2016; Meyers
@@
 cisplatin & CHEMBL2068237 & 3 & 0.75\\
-egfr & SID160769799 & 1 & 0.25\\
+EGFR & SID160769799 & 1 & 0.25\\
 ipilimumab & CHEMBL1789844 & 2 & 0.50\\
-mab & CHEMBL2109423 & 16 & 3.98\\
+mAb & CHEMBL2109423 & 16 & 3.98\\
 nivolumab & CHEMBL2108738 & 4 & 1.00\\
@@
 interpretations that did not have an associated compound, resulting in
-removal of 402 interpretations Table~\ref{tab:table-g2p-nonCID}. It
+removal of 402 interpretations (Table~\ref{tab:table-g2p-nonCID}). It
 should be noted that cisplatin, a small molecule, was excluded due to
@@
 10.14, \(SD =\) 19.80). These unique drugs, genes, and combinations are
-hereafter referred to as G2P drugs, G2P genes, and G2P associations. Of
-the 57 unique G2P drugs, 37 of them were screened in at least one of the
-drug screen datasets, 14 were screened in two of the three datasets, and
-only three drugs were screened in all three datasets. The remaining 20
-un-screened G2P drugs suggests an incompleteness of these drug screens,
-though these projects frequently release new screening data that may
-include these drugs in future releases.
+hereafter referred to as G2P drugs, G2P genes, and G2P associations.
+Filtering our screening datasets by these clinical criteria yields
+panels of potentially clinically relevant omic features. Of the 57
+unique G2P drugs, 37 of them were screened in at least one of the drug
+screen datasets, 17 drugs were screened in at least two of the three
+datasets, and only 3 were screened in all three datasets. The remaining
+20 un-screened G2P drugs suggests an incompleteness of these drug
+screens, though these projects frequently release new screening data
+that may include these drugs in future releases.
 
@@
 rank-sum tests revealed that in CCLE, the AUC distributions of mutant
-and wildtype groups for 10 out of 170 (5.88\%) tested drug-gene
-combinations were significantly different, 91 out of 918 (9.91\%) were
-significantly different for CTRP, and 61 out of 850 (7.18\%) for GDSC.
+and wildtype groups for 18 out of 170 (10.59\%) tested drug-gene
+combinations were significantly different, 135 out of 918 (14.71\%) were
+significantly different for CTRP, and 89 out of 850 (10.47\%) for GDSC.
 We observe little concordance between the number of interpretations for
@@
 drug-gene-lineage combinations (DGLs), representing seven of our curated
-cancer lineages: cancer, breast cancer, leukemia, lung cancer, ovarian
-cancer, skin cancer, and thyroid cancer. CCLE had data for nine DGLs,
-CTRP had data for 61, and GDSC had data for 53, yielding a total of 73
-unique DGLs across all three datasets.
+cancer lineages: cancer, lung cancer, breast cancer, leukemia, thyroid
+cancer, skin cancer, and ovarian cancer. CCLE had data for 9 DGLs, CTRP
+had data for 61, and GDSC had data for 53, yielding a total of 73 unique
+DGLs across all three datasets. Only 7 DGLs were screened in all three
+datasets,
 
@@
 Public 18Q4 release via the DepMap data portal
-(\url{https://depmap.org/portal/download/}) (DepMap, 2018). Gene
+(\url{https://depmap.org/portal/download/}) (Broad DepMap, 2018). Gene
 expression data was retrieved from the DepMap Public 18Q3 release (Broad
@@
 processing and screening methods are available from the figshare record
-(DepMap, 2018) and the original publication of CERES, the algorithm that
-computes inferred gene dependency scores (Meyers et al., 2017). The
-DepMap releases new data quarterly, with the current data set being the
-18Q4 release. This release has 175 more cell lines than the original
-data release that was published with CERES (dataset: gene\_effect.csv,
-accessed 15 November 2018).
+(Broad DepMap, 2018) and the original publication of CERES, the
+algorithm that computes inferred gene dependency scores (Meyers et al.,
+2017). The DepMap releases new data quarterly, with the current data set
+being the 18Q4 release. This release has 175 more cell lines than the
+original data release that was published with CERES (dataset:
+gene\_effect.csv, accessed 15 November 2018).
 
@@
 single-nucleotide insertions, deletions, and substitutions, regardless
-of result, i.e.~frameshift or missense mutation. For this analysis, cell
-lines harboring non-silent point mutations were considered
-\enquote{mutant} for the gene in question. All other mutations and genes
-without annotation in the Mutation Annotation Format (MAF) file were
-considered \enquote{wildtype.} \enquote{Mutant} and \enquote{wildtype}
-calls were binarily encoded per-gene/per-cell line, regardless of
-quantity of harbored mutations per gene in a given cell line.
+of result, i.e.~frameshift, missense, or nonsense mutation. For this
+analysis, cell lines harboring non-silent point mutations were
+considered \enquote{mutant} for the gene in question. All other
+mutations and genes without annotation in the Mutation Annotation Format
+(MAF) file were considered \enquote{wildtype.} \enquote{Mutant} and
+\enquote{wildtype} calls were binarily encoded per-gene/per-cell line,
+regardless of quantity of harbored mutations per gene in a given cell
+line.
 
@@
 The CCLE generated genomic copy number (CN) data using the Affymetrix
-Genome-Wide Human SNP Array 6.0 and GenePattern pipeline (Network, 2008)
-and normalized segmented CN log2-ratios for 23,299 genes across 1,098
-cell lines using circular binary segmentation (Olshen, Venkatraman,
-Lucito, \& Wigler, 2004) (dataset: public\_18Q4\_gene\_cn.csv, accessed
-15 November 2018).
+Genome-Wide Human SNP Array 6.0 and GenePattern pipeline (The Cancer
+Genome Atlas Research Network, 2008) and normalized segmented CN
+log2-ratios for 23,299 genes across 1,098 cell lines using circular
+binary segmentation (Olshen, Venkatraman, Lucito, \& Wigler, 2004)
+(dataset: public\_18Q4\_gene\_cn.csv, accessed 15 November 2018).
 
@@
 al., 2016). All other analyses were conducted in R (v3.5.0) (R
-Foundation for Statistical Computing, \url{https://www.R-project.org/})
-in an RStudio environment (v1.1.447) (RStudio, 2012). All other plots
-were drawn using the ggplot2 (v3.0.0) R package (Wickham, 2016).
+Development Core Team, 2010, \url{https://www.R-project.org/}) in an
+RStudio environment (v1.1.447) (RStudio, 2012). All other plots were
+drawn using the ggplot2 (v3.0.0) R package (Wickham, 2016).
 
@@
 
-Wilcoxon tests were computed using the ggpubr (v.) R package
+Wilcoxon tests were computed using the ggpubr (v0.1.7.999) R package
 (Kassambara, 2018).
@@
 Bairoch, A. (2018). The Cellosaurus, a Cell-Line Knowledge Resource.
-\emph{Journal of Biomolecular Techniques : JBT}, \emph{29}(2), 25--38.
+\emph{J Biomol Tech}, \emph{29}(2), 25--38.
 doi:\href{https://doi.org/10.7171/jbt.18-2902-002}{10.7171/jbt.18-2902-002}
@@
 resource to identify cancer genetic and lineage dependencies targeted by
-small molecules. \emph{Cell, Cell}, \emph{154, 154}(5, 5), 1151,
-1151--1161.
+small molecules. \emph{Cell}, \emph{154, 154}(5, 5), 1151, 1151--1161.
 doi:\href{https://doi.org/10.1016/j.cell.2013.08.003,\%2010.1016/j.cell.2013.08.003}{10.1016/j.cell.2013.08.003, 10.1016/j.cell.2013.08.003}
@@
 
+\hypertarget{ref-broaddepmap2018a}{}
+Broad DepMap. (2018, January 11). DepMap Achilles 18Q4 public. Figshare.
+Retrieved from
+\url{https://figshare.com/articles/DepMap_Achilles_18Q4_public/7270880}
+
 \hypertarget{ref-broaddepmap2018}{}
@@
 
-\hypertarget{ref-broaddepmap2018a}{}
-DepMap, B. (2018, January 11). DepMap Achilles 18Q4 public. Figshare.
-Retrieved from
-\url{https://figshare.com/articles/DepMap_Achilles_18Q4_public/7270880}
-
 \hypertarget{ref-doench2016a}{}
@@
 Evaluating cell lines as tumour models by comparison of genomic
-profiles. \emph{Nature Communications}, \emph{4}.
+profiles. \emph{Nat Commun}, \emph{4}.
 doi:\href{https://doi.org/10.1038/ncomms3126}{10.1038/ncomms3126}
@@
 Tate, J., \ldots{} Campbell, P. J. (2017). COSMIC: Somatic cancer
-genetics at high-resolution. \emph{Nucleic Acids Research},
-\emph{45}(D1), D777--D783.
+genetics at high-resolution. \emph{Nucleic Acids Res}, \emph{45}(D1),
+D777--D783.
 doi:\href{https://doi.org/10.1093/nar/gkw1121}{10.1093/nar/gkw1121}
@@
 
-\hypertarget{ref-theglobalallianceforgenomicsandhealth2016}{}
-Genomics, T. G. A. for, \& Health. (2016). A federated ecosystem for
-sharing genomic, clinical data. \emph{Science}, \emph{352}(6291),
-1278--1280.
-doi:\href{https://doi.org/10.1126/science.aaf6162}{10.1126/science.aaf6162}
-
 \hypertarget{ref-greshock2010}{}
@@
 Reproducibility in Cancer Drug Screening: How Do We Move Forward?
-\emph{Cancer Research}, \emph{74}(15), 4016--4023.
+\emph{Cancer Res}, \emph{74}(15), 4016--4023.
 doi:\href{https://doi.org/10.1158/0008-5472.CAN-14-0725}{10.1158/0008-5472.CAN-14-0725}
@@
 Guan, Y., \ldots{} Spellman, P. T. (2009). Integrated analysis of breast
-cancer cell lines reveals unique signaling pathways. \emph{Genome
-Biology}, \emph{10}(3), R31.
+cancer cell lines reveals unique signaling pathways. \emph{Genome Biol},
+\emph{10}(3), R31.
 doi:\href{https://doi.org/10.1186/gb-2009-10-3-r31}{10.1186/gb-2009-10-3-r31}
@@
 FDA-Approved Anti-Cancer Agents in the NCI60 Panel of Human Tumor Cell
-Lines. \emph{Molecular Cancer Therapeutics}, \emph{9}(5), 1451--1460.
+Lines. \emph{Mol Cancer Ther}, \emph{9}(5), 1451--1460.
 doi:\href{https://doi.org/10.1158/1535-7163.MCT-10-0106}{10.1158/1535-7163.MCT-10-0106}
@@
 knowledge base for structured clinical-grade mutations and
-interpretations. \emph{Journal of the American Medical Informatics
-Association : JAMIA}, \emph{24}(3), 513--519.
+interpretations. \emph{J Am Med Inform Assoc}, \emph{24}(3), 513--519.
 doi:\href{https://doi.org/10.1093/jamia/ocw148}{10.1093/jamia/ocw148}
@@
 (2014). Systematic assessment of analytical methods for drug sensitivity
-prediction from cancer cell line data. \emph{Pacific Symposium on
-Biocomputing. Pacific Symposium on Biocomputing}, 63--74. Retrieved from
+prediction from cancer cell line data. \emph{Pac Symp Biocomput},
+63--74. Retrieved from
 \url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3995541/}
@@
 Genome-phenome Archive of human data consented for biomedical research.
-\emph{Nature Genetics}, \emph{47}(7), 692--695.
+\emph{Nat Genet}, \emph{47}(7), 692--695.
 doi:\href{https://doi.org/10.1038/ng.3312}{10.1038/ng.3312}
@@
 Krzyzanowski, P. M., \ldots{} Moffat, J. (2012). Essential gene profiles
-in breast, pancreas and ovarian cancer cells. \emph{Cancer Discovery},
+in breast, pancreas and ovarian cancer cells. \emph{Cancer Discov},
 \emph{2}(2), 172--189.
@@
 copy-number effect improves specificity of CRISPR-Cas9 essentiality
-screens in cancer cells. \emph{Nature Genetics}, \emph{49}(12),
-1779--1784. doi:\href{https://doi.org/10.1038/ng.3984}{10.1038/ng.3984}
+screens in cancer cells. \emph{Nat Genet}, \emph{49}(12), 1779--1784.
+doi:\href{https://doi.org/10.1038/ng.3984}{10.1038/ng.3984}
 
@@
 
-\hypertarget{ref-thecancergenomeatlasresearchnetwork2008}{}
-Network, T. C. G. A. R. (2008). Comprehensive genomic characterization
-defines human glioblastoma genes and core pathways, \emph{455},
-1061--1068.
-doi:\href{https://doi.org/10.1038/nature07385}{10.1038/nature07385}
-
 \hypertarget{ref-neve2006}{}
@@
 
+\hypertarget{ref-rdevelopmentcoreteam2010}{}
+R Development Core Team. (2010). \emph{R: A Language and Environment for
+Statistical Computing}. Vienna, Austria: R Foundation for Statistical
+Computing. Retrieved from \url{https://www.R-project.org/}
+
 \hypertarget{ref-ramos2015a}{}
@@
 sensitivity and basal gene expression reveals mechanism of action.
-\emph{Nature Chemical Biology}, \emph{12}(2), 109--116.
+\emph{Nat Chem Biol}, \emph{12}(2), 109--116.
 doi:\href{https://doi.org/10.1038/nchembio.1986}{10.1038/nchembio.1986}
@@
 Q., \ldots{} Haibe-Kains, B. (2017). Revisiting inconsistency in large
-pharmacogenomic studies. \emph{F1000Research}, \emph{5}.
+pharmacogenomic studies. \emph{F1000Res}, \emph{5}.
 doi:\href{https://doi.org/10.12688/f1000research.9611.3}{10.12688/f1000research.9611.3}
@@
 Connectivity in a Large-Scale Small-Molecule Sensitivity Dataset.
-\emph{Cancer Discovery, Cancer Discovery}, \emph{5, 5}(11, 11), 1210,
-1210--1223.
+\emph{Cancer Discov}, \emph{5, 5}(11, 11), 1210, 1210--1223.
 doi:\href{https://doi.org/10.1158/2159-8290.CD-15-0235,\%2010.1158/2159-8290.CD-15-0235}{10.1158/2159-8290.CD-15-0235, 10.1158/2159-8290.CD-15-0235}
@@
 preclinical validation of drug indications using compendia of public
-gene expression data. \emph{Science Translational Medicine},
-\emph{3}(96), 96ra77.
+gene expression data. \emph{Sci Transl Med}, \emph{3}(96), 96ra77.
 doi:\href{https://doi.org/10.1126/scitranslmed.3001318}{10.1126/scitranslmed.3001318}
@@
 Interpreter annotates the biological and clinical relevance of tumor
-alterations. \emph{Genome Medicine}, \emph{10}.
+alterations. \emph{Genome Med}, \emph{10}.
 doi:\href{https://doi.org/10.1186/s13073-018-0531-8}{10.1186/s13073-018-0531-8}
+
+\hypertarget{ref-thecancergenomeatlasresearchnetwork2008}{}
+The Cancer Genome Atlas Research Network. (2008). Comprehensive genomic
+characterization defines human glioblastoma genes and core pathways,
+\emph{455}, 1061--1068.
+doi:\href{https://doi.org/10.1038/nature07385}{10.1038/nature07385}
+
+\hypertarget{ref-theglobalallianceforgenomicsandhealth2016}{}
+The Global Alliance for Genomics and Health. (2016). A federated
+ecosystem for sharing genomic, clinical data. \emph{Science},
+\emph{352}(6291), 1278--1280.
+doi:\href{https://doi.org/10.1126/science.aaf6162}{10.1126/science.aaf6162}
 
@@
 Pauli-Behn, F., \ldots{} Myers, R. M. (2013). Dynamic DNA methylation
-across diverse human cell lines and tissues. \emph{Genome Research},
+across diverse human cell lines and tissues. \emph{Genome Res},
 \emph{23}(3), 555--567.
@@
 J., \ldots{} Sabatini, D. M. (2015). Identification and characterization
-of essential genes in the human genome. \emph{Science (New York, N.Y.)},
+of essential genes in the human genome. \emph{Science},
 \emph{350}(6264), 1096--1101.
@@
 in Cancer (GDSC): A resource for therapeutic biomarker discovery in
-cancer cells. \emph{Nucleic Acids Research}, \emph{41}(D1), D955--D961.
+cancer cells. \emph{Nucleic Acids Res}, \emph{41}(D1), D955--D961.
 doi:\href{https://doi.org/10.1093/nar/gks1111}{10.1093/nar/gks1111}

### 2019-01-04 manuscript_analysis.Rmd

@@
 test_gdsc <- gdsc_data_ptmuts %>% group_by(Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()
+
+# drug_summ <- data.frame(Drug = g2p_drugs, Dataset_Count = 0)
+```
+
+```{r}
+drug_summ <- data.frame(Drug = character(), Dataset_Count = integer(), stringsAsFactors = FALSE)
+
+for(drug in g2p_drugs) {
+  counter = 0
+  if(drug %in% as.character(unique(ccle_data_g2p$Drug))) { counter <- counter + 1 }
+  if(drug %in% as.character(unique(ctrp_data_g2p$Drug))) { counter <- counter + 1 }
+  if(drug %in% as.character(unique(gdsc_data_g2p$Drug))) { counter <- counter + 1 }
+  drug_summ <- rbind(drug_summ, data.frame(Drug = drug, Dataset_Count = counter))
+}
 ```
@@
 
-knitr::kable(crispr_data_signif_g2p_lineage_summ, caption = "Mutant/Wildtype counts for gene-lineage combinations") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+crispr_data_signif_g2p_lineage_summ_kable <- knitr::kable(crispr_data_signif_g2p_lineage_summ, caption = "Mutant/Wildtype counts for gene-lineage combinations") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 ccle_data_allgenes <- ccle_data_allgenes[order(ccle_data_allgenes$p),]
-knitr::kable(ccle_data_allgenes[1:1000, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: by-drug Wilcoxon test results for point mutations in genes targeted in CRISPR screen (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+ccle_data_allgenes_kable <- knitr::kable(ccle_data_allgenes[1:1000, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: by-drug Wilcoxon test results for point mutations in genes targeted in CRISPR screen (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 ccle_signif_g2p <- readRDS("./data_munging/rds/ccle_signif_g2p_gene.rds")
-knitr::kable(ccle_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+ccle_signif_g2p_kable <- knitr::kable(ccle_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 
 ccle_signif_g2p_grid <- readRDS("./data_munging/rds/ccle_signif_g2p_grid.rds")
-knitr::kable(ccle_signif_g2p_grid[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+ccle_signif_g2p_grid_kable <- knitr::kable(ccle_signif_g2p_grid[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
-knitr::kable(ccle_signif_g2p_lineage[, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-
-knitr::kable(ccle_signif_grid_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+ccle_signif_g2p_lineage_kable <- knitr::kable(ccle_signif_g2p_lineage[, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+
+ccle_signif_grid_lineage_kable <- knitr::kable(ccle_signif_grid_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 ctrp_data_allgenes <- ctrp_data_allgenes[order(ctrp_data_allgenes$p),]
-knitr::kable(ctrp_data_allgenes[1:1000, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: by-drug Wilcoxon test results for point mutations in genes targeted in CRISPR screen (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+ctrp_data_allgenes_kable <- knitr::kable(ctrp_data_allgenes[1:1000, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: by-drug Wilcoxon test results for point mutations in genes targeted in CRISPR screen (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 ctrp_signif_g2p <- readRDS("./data_munging/rds/ctrp_signif_g2p_gene.rds")
-knitr::kable(ctrp_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+ctrp_signif_g2p_kable <- knitr::kable(ctrp_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 
 ctrp_signif_g2p_grid <- readRDS("./data_munging/rds/ctrp_signif_g2p_grid.rds")
-knitr::kable(ctrp_signif_g2p_grid[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+ctrp_signif_g2p_grid_kable <- knitr::kable(ctrp_signif_g2p_grid[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
-knitr::kable(ctrp_signif_g2p_lineage[, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-
-knitr::kable(ctrp_signif_grid_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+ctrp_signif_g2p_lineage_kable <- knitr::kable(ctrp_signif_g2p_lineage[, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+
+ctrp_signif_grid_lineage_kable <- knitr::kable(ctrp_signif_grid_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 gdsc_data_allgenes <- gdsc_data_allgenes[order(gdsc_data_allgenes$p),]
-knitr::kable(gdsc_data_allgenes[1:1000, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: by-drug Wilcoxon test results for point mutations in genes targeted in CRISPR screen (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+gdsc_data_allgenes_kable <- knitr::kable(gdsc_data_allgenes[1:1000, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: by-drug Wilcoxon test results for point mutations in genes targeted in CRISPR screen (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 gdsc_signif_g2p <- readRDS("./data_munging/rds/gdsc_signif_g2p_gene.rds")
-knitr::kable(gdsc_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+gdsc_signif_g2p_kabl <- knitr::kable(gdsc_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 
 gdsc_signif_g2p_grid <- readRDS("./data_munging/rds/gdsc_signif_g2p_grid.rds")
-knitr::kable(gdsc_signif_g2p_grid[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+gdsc_signif_g2p_grid_kable <- knitr::kable(gdsc_signif_g2p_grid[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
-knitr::kable(gdsc_signif_g2p_lineage[, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-
-knitr::kable(gdsc_signif_grid_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+gdsc_signif_g2p_lineage_kable <- knitr::kable(gdsc_signif_g2p_lineage[, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+
+gdsc_signif_grid_lineage_kable <- knitr::kable(gdsc_signif_grid_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
-knitr::kable(crispr_data_g2p_summ, caption = "CRISPR: Level A G2P genes mutation status summary") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+crispr_data_g2p_summ_kable <- knitr::kable(crispr_data_g2p_summ, caption = "CRISPR: Level A G2P genes mutation status summary") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 length(unique(g2p_dgl_tally$Gene))
-unique(g2p_filt$Phenotype.Description)
-```
-
-# PANCANCER
-
---------------------------------------------------------------------------------
-
-## Mut
-
-CRISPR mutation status plots of p-values:
-```{r fig.height=1.5, fig.width=12}
-crispr_signif_g2p_gene$y_label <- "CRISPR"
-crispr_signif_g2p_gene$Hugo_Symbol <- factor(crispr_signif_g2p_gene$Hugo_Symbol, levels = g2p_genes)
-crispr_signif_g2p_gene$p <- as.numeric(as.character(crispr_signif_g2p_gene$p))
-
-crispr_mut_heatmap_plot <- ggplot(data = crispr_signif_g2p_gene, aes(x = Hugo_Symbol, y = y_label)) +
-  geom_tile(aes(fill = p)) +
-  scale_fill_gradientn(colors = c("darkgreen", "honeydew", "white"), values = c(0, 0.05, 1), na.value = "darksalmon") +
-  scale_x_discrete(drop = FALSE) +
-  theme(axis.title.y = element_blank(), axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 10)) +
-  labs(x = "Gene")
-crispr_mut_heatmap_plot
-
-# write.table(crispr_signif_g2p_gene, file = "~/Desktop/crispr_signif_g2p_gene_20181203.csv", quote = FALSE, sep = ",", row.names = FALSE)
-# ggsave("./plots/manuscript/crispr_mut_heatmap_plot_example.png", crispr_mut_heatmap_plot, device = "png", dpi = 450, width = 12, height = 1.5, units = "in")
-```
-
-```{r}
-ccle_mut_summ <- merge(g2p_druggene_tally, ccle_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
-ccle_mut_summ$n <- ifelse(is.na(ccle_mut_summ$n), 0, ccle_mut_summ$n)
-ccle_mut_summ$InG2P <- ifelse(ccle_mut_summ$n != 0, "Yes", "No")
-ccle_mut_summ$Dataset <- "CCLE"
-ccle_p_ttest <- t.test(ccle_mut_summ$p ~ ccle_mut_summ$InG2P)
-ccle_p_ttest_res <- paste0("t(", round(ccle_p_ttest$parameter, 0), ") = ", round(ccle_p_ttest$statistic, 2), ", p = ", round(ccle_p_ttest$p.value, 2))
-
-ctrp_mut_summ <- merge(g2p_druggene_tally, ctrp_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
-ctrp_mut_summ$n <- ifelse(is.na(ctrp_mut_summ$n), 0, ctrp_mut_summ$n)
-ctrp_mut_summ$InG2P <- ifelse(ctrp_mut_summ$n != 0, "Yes", "No")
-ctrp_mut_summ$Dataset <- "CTRP"
-ctrp_p_ttest <- t.test(ctrp_mut_summ$p ~ ctrp_mut_summ$InG2P)
-ctrp_p_ttest_res <- paste0("t(", round(ctrp_p_ttest$parameter, 0), ") = ", round(ctrp_p_ttest$statistic, 2), ", p = ", formatC(ctrp_p_ttest$p.value, digits = 2, format = "f"))
-
-gdsc_mut_summ <- merge(g2p_druggene_tally, gdsc_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
-gdsc_mut_summ$n <- ifelse(is.na(gdsc_mut_summ$n), 0, gdsc_mut_summ$n)
-gdsc_mut_summ$InG2P <- ifelse(gdsc_mut_summ$n != 0, "Yes", "No")
-gdsc_mut_summ$Dataset <- "GDSC"
-gdsc_p_ttest <- t.test(gdsc_mut_summ$p ~ gdsc_mut_summ$InG2P)
-gdsc_p_ttest_res <- paste0("t(", round(gdsc_p_ttest$parameter, 0), ") = ", round(gdsc_p_ttest$statistic, 2), ", p = ", formatC(gdsc_p_ttest$p.value, digits = 2, format = "f"))
-
-g2p_mut_all_summ <- rbind(ccle_mut_summ, ctrp_mut_summ, gdsc_mut_summ)
-g2p_mut_all_summ$p_log10 <- -log10(g2p_mut_all_summ$p)
-g2p_mut_all_summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"), Test_Results_p = c(ccle_p_ttest_res, ctrp_p_ttest_res, gdsc_p_ttest_res))
-g2p_mut_all_summ$Drug_Gene_Ordered <- factor(g2p_mut_all_summ$Drug_Gene, levels = as.character(unique(g2p_mut_all_summ$Drug_Gene)), labels = sapply(strsplit(x = as.character(unique(g2p_mut_all_summ$Drug_Gene)), split = "_"), function(x) paste0(x[1], "\n", x[2])))
-```
-
-```{r fig.height=5, fig.width=12}
-plot_p_point <- ggplot(data = g2p_mut_all_summ, aes(x = p, y = n, label = Drug_Gene)) +
-  facet_wrap(~ Dataset, scales = "free_x") +
-  geom_point(mapping = aes(color = InG2P), alpha = 0.5) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
-  geom_text_repel(data = subset(g2p_mut_all_summ, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
-  geom_text(data = g2p_mut_all_summ_text, mapping = aes(x = 0.5, y = 115, label = Test_Results_p)) +
-  labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations") +
-  theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
-
-plot_p_box <- ggplot(data = g2p_mut_all_summ) +
-  facet_wrap(~ Dataset, scales = "free_x") +
-  geom_violin(mapping = aes(color = InG2P, fill = InG2P, y = p, x = InG2P), alpha = 0.35) +
-  geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), width = 0.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  coord_flip() +
-  labs(x = "In G2P?") +
-  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
-plot_p_point <- ggplot_gtable(ggplot_build(plot_p_point))
-plot_p_box <- ggplot_gtable(ggplot_build(plot_p_box))
-p_maxWidth <-  grid::unit.pmax(plot_p_point$widths, plot_p_box$widths)
-plot_p_point$widths <- as.list(p_maxWidth)
-plot_p_box$widths <- as.list(p_maxWidth)
-g2p_mut_plot <- cowplot::plot_grid(plot_p_box,
-                   plot_p_point,
-                   nrow = 2,
-                   rel_heights = c(1, 4))
-g2p_mut_plot
-
-# ggsave("./plots/manuscript/g2p_mut_plot.png", g2p_mut_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
-```
-
-```{r, eval=FALSE}
-plot_p_point <- ggplot(data = g2p_mut_all_summ) +
-  facet_wrap(~ Dataset, scales = "free_x") +
-  geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = p, y = n), alpha = 0.5) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
-  geom_text(data = g2p_mut_all_summ_text, mapping = aes(x = 0.5, y = 115, label = Test_Results_p)) +
-  labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations") +
-  theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
-
-plot_p_box <- ggplot(data = g2p_mut_all_summ) +
-  facet_wrap(~ Dataset, scales = "free_x") +
-  geom_violin(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.5) +
-  geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.75, width = 0.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  coord_flip() +
-  labs(x = "Level A G2P\nassociation") +
-  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
-plot <- subplot(plot_p_box, plot_p_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Gene-drug association p-value between mutation groups"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
-
-saveWidgetFix(widget = plot, file = "./plots/manuscript/g2p_mut_plot.html")
-```
-
-## GE
-
-### Pearson
-
-```{r fig.height=5, fig.width=12}
-plot_ge_pearson_point <- ggplot(data = g2p_cor, aes(x = Pearson_GE_Abs, y = n, label = Drug_Gene)) +
-  facet_wrap(~ Dataset) +
-  geom_point(mapping = aes(fill = InG2P, color = InG2P, shape = Pearson_GE_Sign), alpha = 0.5, size = 1.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
-  scale_x_continuous(breaks = seq(0, 0.65, by = 0.1), labels = seq(0, 0.65, by = 0.1)) +
-  coord_cartesian(xlim = c(0, 0.65)) +
-  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
-  geom_text_repel(data = subset(g2p_cor, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
-  geom_text(data = g2p_cor_text, mapping = aes(x = 0.325, y = 115, label = Pearson_Test_Results_GE)) +
-  labs(x = "Pearson correlation coefficient (r) between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +
-  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
-  guides(color = FALSE, fill = FALSE, shape = FALSE)
-
-plot_ge_pearson_box <- ggplot(data = g2p_cor) +
-  facet_wrap(~ Dataset) +
-  geom_violin(mapping = aes(color = InG2P, fill = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.35) +
-  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), width = 0.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_y_continuous(breaks = seq(0, 0.65, by = 0.1), labels = seq(0, 0.65, by = 0.1)) +
-  coord_flip(ylim = c(0, 0.65)) +
-  labs(x = "In G2P?") +
-  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
-plot_ge_pearson_point <- ggplot_gtable(ggplot_build(plot_ge_pearson_point))
-plot_ge_pearson_box <- ggplot_gtable(ggplot_build(plot_ge_pearson_box))
-p_maxWidth <-  grid::unit.pmax(plot_ge_pearson_point$widths[2:3], plot_ge_pearson_box$widths[2:3])
-plot_ge_pearson_point$widths[2:3] <- p_maxWidth
-plot_ge_pearson_box$widths[2:3] <- p_maxWidth
-
-g2p_ge_pearson_plot <- cowplot::plot_grid(plot_ge_pearson_box, plot_ge_pearson_point, nrow = 2, rel_heights = c(1, 4))
-g2p_ge_pearson_plot
-
-# ggsave("./plots/manuscript/g2p_ge_pearson_plot.png", g2p_ge_pearson_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
-```
-
-```{r, eval=FALSE}
-plot_ge_point <- ggplot(data = g2p_cor) +
-  facet_wrap(~ Dataset) +
-  geom_point(mapping = aes(label = Drug_Gene, fill = InG2P, color = InG2P, shape = Pearson_GE_Sign, x = Pearson_GE_Abs, y = n, size = Pearson_Pval_GE), alpha = 0.5, size = 1.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
-  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
-  scale_x_continuous(breaks = pretty_breaks()) +
-  geom_text(data = g2p_cor_text, mapping = aes(x = 0.3, y = 115, label = Pearson_Test_Results_GE)) +
-  labs(x = "Pearson correlation coefficient (r) between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +
-  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
-  guides(color = FALSE, fill = FALSE) +
-  labs(shape = NULL)
-
-plot_ge_box <- ggplot(data = g2p_cor) +
-  facet_wrap(~ Dataset) +
-  geom_violin(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.5) +
-  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  coord_flip() +
-  labs(x = "In G2P?") +
-  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
-ge_pearson_plot <- subplot(plot_ge_box, plot_ge_point, nrows = 2, heights = c(0.2, 0.8), titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and gene expression"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
-
-saveWidgetFix(widget = ge_pearson_plot, file = "./plots/manuscript/g2p_ge_pearson_plot.html")
-```
-
-### Spearman
-
-```{r fig.height=5, fig.width=12}
-plot_ge_spearman_point <- ggplot(data = g2p_cor, aes(x = Spearman_GE_Abs, y = n, label = Drug_Gene)) +
-  facet_wrap(~ Dataset) +
-  geom_point(mapping = aes(fill = InG2P, color = InG2P, shape = Spearman_GE_Sign), alpha = 0.5, size = 1.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
-  scale_x_continuous(breaks = seq(0, 0.65, by = 0.1), labels = seq(0, 0.65, by = 0.1)) +
-  coord_cartesian(xlim = c(0, 0.6)) +
-  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
-  geom_text_repel(data = subset(g2p_cor, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
-  geom_text(data = g2p_cor_text, mapping = aes(x = 0.3, y = 115, label = Spearman_Test_Results_GE)) +
-  labs(x = "Spearman correlation coefficient (r_s) between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +
-  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
-  guides(color = FALSE, fill = FALSE, shape = FALSE)
-
-plot_ge_spearman_box <- ggplot(data = g2p_cor) +
-  facet_wrap(~ Dataset) +
-  geom_violin(mapping = aes(color = InG2P, fill = InG2P, y = Spearman_GE_Abs, x = InG2P), alpha = 0.35) +
-  geom_boxplot(mapping = aes(color = InG2P, y = Spearman_GE_Abs, x = InG2P), width = 0.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_y_continuous(breaks = seq(0, 0.65, by = 0.1), labels = seq(0, 0.65, by = 0.1)) +
-  coord_flip(ylim = c(0, 0.6)) +
-  labs(x = "In G2P?") +
-  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
-plot_ge_spearman_point <- ggplot_gtable(ggplot_build(plot_ge_spearman_point))
-plot_ge_spearman_box <- ggplot_gtable(ggplot_build(plot_ge_spearman_box))
-p_maxWidth <-  grid::unit.pmax(plot_ge_spearman_point$widths[2:3], plot_ge_spearman_box$widths[2:3])
-plot_ge_spearman_point$widths[2:3] <- p_maxWidth
-plot_ge_spearman_box$widths[2:3] <- p_maxWidth
-
-g2p_ge_spearman_plot <- cowplot::plot_grid(plot_ge_spearman_box, plot_ge_spearman_point, nrow = 2, rel_heights = c(1, 4))
-g2p_ge_spearman_plot
-
-# ggsave("./plots/manuscript/g2p_ge_spearman_plot.png", g2p_ge_spearman_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
-```
-
-```{r, eval=FALSE}
-plot_ge_point <- ggplot(data = g2p_cor) +
-  facet_wrap(~ Dataset) +
-  geom_point(mapping = aes(label = Drug_Gene, fill = InG2P, color = InG2P, shape = Spearman_GE_Sign, x = Spearman_GE_Abs, y = n, size = Spearman_Pval_GE), alpha = 0.5, size = 1.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
-  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
-  scale_x_continuous(breaks = pretty_breaks()) +
-  geom_text(data = g2p_cor_text, mapping = aes(x = 0.3, y = 115, label = Spearman_Test_Results_GE)) +
-  labs(x = "Spearman correlation coefficient (r_s) between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +
-  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
-  guides(color = FALSE, fill = FALSE) +
-  labs(shape = NULL)
-
-plot_ge_box <- ggplot(data = g2p_cor) +
-  facet_wrap(~ Dataset) +
-  geom_violin(mapping = aes(color = InG2P, y = Spearman_GE_Abs, x = InG2P), alpha = 0.5) +
-  geom_boxplot(mapping = aes(color = InG2P, y = Spearman_GE_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  coord_flip() +
-  labs(x = "In G2P?") +
-  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
-ge_spearman_plot <- subplot(plot_ge_box, plot_ge_point, nrows = 2, heights = c(0.2, 0.8), titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Spearman correlation coefficient between drug-gene AUC and gene expression"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
-
-saveWidgetFix(widget = ge_spearman_plot, file = "./plots/manuscript/g2p_ge_spearman_plot.html")
-```
-
-## CN
-
-### Pearson
-
-```{r fig.height=5, fig.width=12}
-plot_cn_pearson_point <- ggplot(data = g2p_cor, aes(x = Pearson_CN_Abs, y = n, label = Drug_Gene)) +
-  facet_wrap(~ Dataset) +
-  geom_point(mapping = aes(fill = InG2P, color = InG2P, shape = Pearson_CN_Sign), alpha = 0.5, size = 1.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
-  scale_x_continuous(breaks = seq(0, 0.65, by = 0.1), labels = seq(0, 0.65, by = 0.1)) +
-  coord_cartesian(xlim = c(0, 0.5)) +
-  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
-  geom_text_repel(data = subset(g2p_cor, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
-  geom_text(data = g2p_cor_text, mapping = aes(x = 0.25, y = 115, label = Pearson_Test_Results_CN)) +
-  labs(x = "Pearson correlation coefficient (r) between drug-gene AUC and copy number", y = "Number of level A G2P associations") +
-  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
-  guides(color = FALSE, fill = FALSE, shape = FALSE)
-
-plot_cn_pearson_box <- ggplot(data = g2p_cor) +
-  facet_wrap(~ Dataset) +
-  geom_violin(mapping = aes(color = InG2P, fill = InG2P, y = Pearson_CN_Abs, x = InG2P), alpha = 0.35) +
-  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_CN_Abs, x = InG2P), width = 0.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_y_continuous(breaks = seq(0, 0.65, by = 0.1), labels = seq(0, 0.65, by = 0.1)) +
-  coord_flip(ylim = c(0, 0.5)) +
-  labs(x = "In G2P?") +
-  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
-plot_cn_pearson_point <- ggplot_gtable(ggplot_build(plot_cn_pearson_point))
-plot_cn_pearson_box <- ggplot_gtable(ggplot_build(plot_cn_pearson_box))
-p_maxWidth <-  grid::unit.pmax(plot_cn_pearson_point$widths[2:3], plot_cn_pearson_box$widths[2:3])
-plot_cn_pearson_point$widths[2:3] <- p_maxWidth
-plot_cn_pearson_box$widths[2:3] <- p_maxWidth
-
-g2p_cn_pearson_plot <- cowplot::plot_grid(plot_cn_pearson_box, plot_cn_pearson_point, nrow = 2, rel_heights = c(1, 4))
-g2p_cn_pearson_plot
-
-# ggsave("./plots/manuscript/g2p_cn_pearson_plot.png", g2p_cn_pearson_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
-```
-
-```{r, eval=FALSE}
-plot_cn_point <- ggplot(data = g2p_cor) +
-  facet_wrap(~ Dataset) +
-  geom_point(mapping = aes(label = Drug_Gene, fill = InG2P, color = InG2P, shape = Pearson_CN_Sign, x = Pearson_CN_Abs, y = n, size = Pearson_Pval_CN), alpha = 0.5, size = 1.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
-  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
-  scale_x_continuous(breaks = pretty_breaks()) +
-  geom_text(data = g2p_cor_text, mapping = aes(x = 0.3, y = 115, label = Pearson_Test_Results_CN)) +
-  labs(x = "Pearson correlation coefficient (r) between drug-gene AUC and copy number", y = "Number of level A G2P associations") +
-  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
-  guides(color = FALSE, fill = FALSE) +
-  labs(shape = NULL)
-
-plot_cn_box <- ggplot(data = g2p_cor) +
-  facet_wrap(~ Dataset) +
-  geom_violin(mapping = aes(color = InG2P, y = Pearson_CN_Abs, x = InG2P), alpha = 0.5) +
-  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_CN_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  coord_flip() +
-  labs(x = "In G2P?") +
-  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
-cn_pearson_plot <- subplot(plot_cn_box, plot_cn_point, nrows = 2, heights = c(0.2, 0.8), titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and copy number"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
-
-saveWidgetFix(widget = ge_pearson_plot, file = "./plots/manuscript/g2p_cn_pearson_plot.html")
-```
-
-### Spearman
-
-```{r fig.height=5, fig.width=12}
-plot_cn_spearman_point <- ggplot(data = g2p_cor, aes(x = Spearman_CN_Abs, y = n, label = Drug_Gene)) +
-  facet_wrap(~ Dataset) +
-  geom_point(mapping = aes(fill = InG2P, color = InG2P, shape = Spearman_CN_Sign), alpha = 0.5, size = 1.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
-  scale_x_continuous(breaks = seq(0, 0.4, by = 0.05), labels = seq(0, 0.4, by = 0.05)) +
-  coord_cartesian(xlim = c(0, 0.35)) +
-  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
-  geom_text_repel(data = subset(g2p_cor, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
-  geom_text(data = g2p_cor_text, mapping = aes(x = 0.175, y = 115, label = Spearman_Test_Results_CN)) +
-  labs(x = "Spearman correlation coefficient (r_s) between drug-gene AUC and copy number", y = "Number of level A G2P associations") +
-  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
-  guides(color = FALSE, fill = FALSE, shape = FALSE)
-
-plot_cn_spearman_box <- ggplot(data = g2p_cor) +
-  facet_wrap(~ Dataset) +
-  geom_violin(mapping = aes(color = InG2P, fill = InG2P, y = Spearman_CN_Abs, x = InG2P), alpha = 0.35) +
-  geom_boxplot(mapping = aes(color = InG2P, y = Spearman_CN_Abs, x = InG2P), width = 0.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_y_continuous(breaks = seq(0, 0.4, by = 0.05), labels = seq(0, 0.4, by = 0.05)) +
-  coord_flip(ylim = c(0, 0.35)) +
-  labs(x = "In G2P?") +
-  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
-plot_cn_spearman_point <- ggplot_gtable(ggplot_build(plot_cn_spearman_point))
-plot_cn_spearman_box <- ggplot_gtable(ggplot_build(plot_cn_spearman_box))
-p_maxWidth <-  grid::unit.pmax(plot_cn_spearman_point$widths[2:3], plot_cn_spearman_box$widths[2:3])
-plot_cn_spearman_point$widths[2:3] <- p_maxWidth
-plot_cn_spearman_box$widths[2:3] <- p_maxWidth
-
-g2p_cn_spearman_plot <- cowplot::plot_grid(plot_cn_spearman_box, plot_cn_spearman_point, nrow = 2, rel_heights = c(1, 4))
-g2p_cn_spearman_plot
-
-# ggsave("./plots/manuscript/g2p_cn_spearman_plot.png", g2p_cn_spearman_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
-```
-
-```{r, eval=FALSE}
-plot_cn_point <- ggplot(data = g2p_cor) +
-  facet_wrap(~ Dataset) +
-  geom_point(mapping = aes(label = Drug_Gene, fill = InG2P, color = InG2P, shape = Spearman_CN_Sign, x = Spearman_CN_Abs, y = n, size = Spearman_Pval_CN), alpha = 0.5, size = 1.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
-  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
-  scale_x_continuous(breaks = pretty_breaks()) +
-  geom_text(data = g2p_cor_text, mapping = aes(x = 0.175, y = 115, label = Spearman_Test_Results_CN)) +
-  labs(x = "Spearman correlation coefficient (r_s) between drug-gene AUC and copy number", y = "Number of level A G2P associations") +
-  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
-  guides(color = FALSE, fill = FALSE) +
-  labs(shape = NULL)
-
-plot_cn_box <- ggplot(data = g2p_cor) +
-  facet_wrap(~ Dataset) +
-  geom_violin(mapping = aes(color = InG2P, y = Spearman_CN_Abs, x = InG2P), alpha = 0.5) +
-  geom_boxplot(mapping = aes(color = InG2P, y = Spearman_CN_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  coord_flip() +
-  labs(x = "In G2P?") +
-  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
-cn_spearman_plot <- subplot(plot_cn_box, plot_cn_point, nrows = 2, heights = c(0.2, 0.8), titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Spearman correlation coefficient between drug-gene AUC and copy number"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
-
-saveWidgetFix(widget = cn_spearman_plot, file = "./plots/manuscript/g2p_cn_spearman_plot.html")
+# unique(g2p_filt$Phenotype.Description)
+```
+
+## Cell line overlap
+
+```{r, eval=FALSE}
+crispr_ccl <- unique(select(crispr_data, DepMap_ID, CCLE_Name))
+ccle_ccl <- unique(select(ccle_data, DepMap_ID, CCLE_Name, accession_id))
+ctrp_ccl <- unique(select(ctrp_data, DepMap_ID, CCLE_Name, accession_id))
+gdsc_ccl <- unique(select(gdsc_data, DepMap_ID, CCLE_Name, accession_id))
+# all_ccl <- merge(ccle_ccl, ctrp_ccl, by = c("DepMap_ID", "CCLE_Name", "accession_id"), all = TRUE)
 ```
@@
 dgl_mut_grid_summ <- rbind(ccle_dgl_summ, ctrp_dgl_summ, gdsc_dgl_summ)
-```
-
-Make summary plots of mutation status tests by lineage and return a dataframe of all t-test results from comparing the p-value distributions of G2P and non-G2P drug-gene associaions:
-```{r, eval=FALSE, results = 'hide'}
-dgl_mut_g2p_grid_ttest_res <- lapply(as.character(unique(dgl_mut_grid_summ$group_general_lineage_name)), MutPlotsByLineage)
-dgl_mut_g2p_grid_ttest_res_list <- rbindlist(dgl_mut_g2p_grid_ttest_res, use.names = TRUE)
-dgl_mut_g2p_grid_ttest_res_list <- dgl_mut_g2p_grid_ttest_res_list[order(dgl_mut_g2p_grid_ttest_res_list$p_value),]
-saveRDS(dgl_mut_g2p_grid_ttest_res_list, "./data_munging/rds/dgl_mut_g2p_grid_ttest_res_list.rds")
-```
-
-```{r}
-dgl_mut_g2p_grid_ttest_res_list <- readRDS("./data_munging/rds/dgl_mut_g2p_grid_ttest_res_list.rds")
-knitr::kable(dgl_mut_g2p_grid_ttest_res_list, caption = "Mutation status: T-test results for level A G2P drug-gene associations across lineages") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 
-```{r, results='hide', eval=FALSE}
-dgl_pearson_g2p_grid_ttest_res <- lapply(as.character(unique(dgl_signif_pearson_g2p_grid$group_general_lineage_name)), PearsonPlotsByLineage)
-dgl_pearson_g2p_grid_ttest_res_list <- rbindlist(dgl_pearson_g2p_grid_ttest_res, use.names = TRUE)
-saveRDS(dgl_pearson_g2p_grid_ttest_res_list, "./data_munging/rds/dgl_pearson_g2p_grid_ttest_res_list.rds")
-```
-
-```{r}
-dgl_pearson_g2p_grid_ttest_res_list <- readRDS("./data_munging/rds/dgl_pearson_g2p_grid_ttest_res_list.rds")
-
-knitr::kable(dgl_pearson_g2p_grid_ttest_res_list[order(dgl_pearson_g2p_grid_ttest_res_list$p_value_GE), c("Dataset", "group_general_lineage_name", "t_statistic_GE", "df_GE", "p_value_GE")], caption = "Gene expression: T-test results for level A G2P drug-gene/gene expression associations across lineages") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-
-knitr::kable(dgl_pearson_g2p_grid_ttest_res_list[order(dgl_pearson_g2p_grid_ttest_res_list$p_value_CN), c("Dataset", "group_general_lineage_name", "t_statistic_CN", "df_CN", "p_value_CN")], caption = "Copy number: T-test results for level A G2P drug-gene/gene expression associations across lineages") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-# MUT/GE/CN
+# MUT/GE/CN: Pancancer
 
 --------------------------------------------------------------------------------
-
-## Pancancer
 
@@
 
-### CRISPR
+## CRISPR
 
@@
 
+## Summaries by dataset
+
 ### CCLE
@@
 
-### Drug: Mut
+## Summaries by feature
+
+### Mut
 
@@
 
-### Drug: GE and CN
+### GE and CN
 
@@
 
-### Drug: P-values
+## P-values
 
@@
 
-### Summary stats
+## Summary stats
 
@@
 g2p_mut_all_summ_stats <- g2p_mut_all_summ_stats %>% drop_na(p) %>% group_by(Dataset, InG2P) %>% summarize(p_mean = round(mean(p), 2), p_sd = round(sd(p), 2), n = sum(n_true), n_signif = sum(p < 0.05), n_sig_perc = n_signif / n * 100)
+g2p_mut_all_summ_stats
 
@@
           cn_n_sig_perc = cn_n_signif / cn_n * 100)
-```
-
-### CTRP example derivation
+g2p_cor_stats
+```
+
+## CTRP example derivation
 
@@
 
-## By lineage
-
-### Kolmogorov-Smirnov tests
+# MUT/GE/CN: By lineage
+
+--------------------------------------------------------------------------------
+
+## Big grid summary plot
+
+Big grid plot by lineages:
+```{r fig.height=20, fig.width=12}
+dgl_mut <- dgl_mut_grid_summ
+dgl_mut$Sign <- "None"
+dgl_mut$Measure <- "Mutation Status"
+colnames(dgl_mut)[colnames(dgl_mut) == "p"] <- "Statistic"
+dgl_mut$Drug_Gene_Lin <- NULL
+
+dgl_ge <- select(dgl_signif_pearson_g2p_grid, Drug_Gene, group_general_lineage_name, n, Pearson_GE_Abs, InG2P, Dataset, Pearson_GE_Sign)
+dgl_ge$Measure <- "Gene Expression"
+colnames(dgl_ge)[colnames(dgl_ge) == "Pearson_GE_Abs"] <- "Statistic"
+colnames(dgl_ge)[colnames(dgl_ge) == "Pearson_GE_Sign"] <- "Sign"
+
+dgl_cn <- select(dgl_signif_pearson_g2p_grid, Drug_Gene, group_general_lineage_name, n, Pearson_CN_Abs, InG2P, Dataset, Pearson_CN_Sign)
+dgl_cn$Measure <- "Copy Number"
+colnames(dgl_cn)[colnames(dgl_cn) == "Pearson_CN_Abs"] <- "Statistic"
+colnames(dgl_cn)[colnames(dgl_cn) == "Pearson_CN_Sign"] <- "Sign"
+
+dgl_all <- rbind(dgl_mut, dgl_ge, dgl_cn)
+dgl_all$Sign <- ifelse(is.na(dgl_all$Sign), "None", dgl_all$Sign)
+
+dgl_all_plot <- ggplot(data = dgl_all, aes(x = InG2P, y = Statistic)) +
+  facet_grid(group_general_lineage_name ~ Measure * Dataset) +
+  geom_jitter(mapping = aes(shape = Sign, fill = InG2P, color = InG2P), width = 0.4, alpha = 0.5, size = 1) +
+  geom_boxplot(width = 0.25, fill = NA, outlier.shape = NA) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_shape_manual(values = c(25, 24, 4), labels = c("Negative", "Positive", "NA")) +
+  theme(legend.position = "top") +
+  guides(color = FALSE, fill = FALSE)
+
+# ggsave("./plots/manuscript/all_dgl_plot.png", dgl_all_plot, device = "png", dpi = 450, width = 12, height = 40, units = "in")
+```
+
+## Kolmogorov-Smirnov tests
 
@@
 
-### Grid t-test summaries
-
-Figure #.
-Histograms of p-values from t-tests comparing distributions of summary statistics for CCLE, CTRP, and GDSC drug screen results in the context of G2P level A evidence and lineage.
-Each p-value is derived from comparisons similar to those shown in Figure 2, but for these p-values, the data is grouped by lineage prior to conducting the t-test rather than the test being lineage-agnostic.
-To produce these p-values, AUC was correlated with each genomic feature for all possible pairwise combinations of G2P drugs and genes in all lineages represented in each dataset.
-For each lineage, t-tests were used to compare distributions of p-values (mutation status) or Pearson correlation coefficients (gene expression and copy number) that were grouped by whether or not the underlying drug-gene combination had level-A G2P evidence.
-For each dataset, if there were two or more correlation results in each G2P presence/absence group in a specific lineage, a t-test was conducted and the p-value appears in the appropriate histogram.
-Mutation status histograms are sparse due to limited mutation annotations for many of the G2P genes in all screened cell lines.
-```{r fig.height=4, fig.width=12}
-ttest_summ_res_mut <- dgl_mut_g2p_grid_ttest_res_list[, c("p_value", "Dataset", "group_general_lineage_name")]
-ttest_summ_res_mut$Metric <- "Mutation Status"
-
-ttest_summ_res_ge <- dgl_pearson_g2p_grid_ttest_res_list[, c("p_value_GE", "Dataset", "group_general_lineage_name")]
-colnames(ttest_summ_res_ge) <- c("p_value", "Dataset", "group_general_lineage_name")
-ttest_summ_res_ge$Metric <- "Gene Expression"
-
-ttest_summ_res_cn <- dgl_pearson_g2p_grid_ttest_res_list[, c("p_value_CN", "Dataset", "group_general_lineage_name")]
-colnames(ttest_summ_res_cn) <- c("p_value", "Dataset", "group_general_lineage_name")
-ttest_summ_res_cn$Metric <- "Copy Number"
-
-ttest_summ_res <- rbind(ttest_summ_res_mut, ttest_summ_res_ge, ttest_summ_res_cn)
-ttest_summ_res$Metric <- factor(ttest_summ_res$Metric, levels = c("Mutation Status", "Gene Expression", "Copy Number"))
-
-ttest_mut_summ_facet <- ggplot(data = ttest_summ_res, aes(x = p_value, fill = Dataset, color = Dataset)) +
-  facet_grid(Metric ~ Dataset) +
-  geom_histogram(bins = 40, binwidth = 0.025, boundary = 0, closed = "left") +
-  scale_y_continuous(breaks = c(0:6), labels = c(0:6)) +
-  scale_x_continuous(breaks = seq(0, 1, by = 0.1), expand = c(0.01, 0.01)) +
-  scale_fill_manual(values = c("CCLE" = "palegreen3", "CTRP" = "slategray3", "GDSC" = "paleturquoise3")) +
-  scale_color_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
-  theme(legend.position = c(0.5, 1.7), legend.direction = "horizontal", panel.grid.minor.y = element_blank()) +
-  labs(x = "P-value", y = "Frquency")
-ttest_mut_summ_facet
-
-# ggsave("./plots/manuscript/all_dgl_ttest_summ_facet_plot.png", ttest_mut_summ_facet, device = "png", dpi = 450, width = 12, height = 4, units = "in")
-```
-
-Big grid plot by lineages:
-```{r fig.height=20, fig.width=12}
-dgl_mut <- dgl_mut_grid_summ
-dgl_mut$Sign <- "None"
-dgl_mut$Measure <- "Mutation Status"
-colnames(dgl_mut)[colnames(dgl_mut) == "p"] <- "Statistic"
-dgl_mut$Drug_Gene_Lin <- NULL
-
-dgl_ge <- select(dgl_signif_pearson_g2p_grid, Drug_Gene, group_general_lineage_name, n, Pearson_GE_Abs, InG2P, Dataset, Pearson_GE_Sign)
-dgl_ge$Measure <- "Gene Expression"
-colnames(dgl_ge)[colnames(dgl_ge) == "Pearson_GE_Abs"] <- "Statistic"
-colnames(dgl_ge)[colnames(dgl_ge) == "Pearson_GE_Sign"] <- "Sign"
-
-dgl_cn <- select(dgl_signif_pearson_g2p_grid, Drug_Gene, group_general_lineage_name, n, Pearson_CN_Abs, InG2P, Dataset, Pearson_CN_Sign)
-dgl_cn$Measure <- "Copy Number"
-colnames(dgl_cn)[colnames(dgl_cn) == "Pearson_CN_Abs"] <- "Statistic"
-colnames(dgl_cn)[colnames(dgl_cn) == "Pearson_CN_Sign"] <- "Sign"
-
-dgl_all <- rbind(dgl_mut, dgl_ge, dgl_cn)
-dgl_all$Sign <- ifelse(is.na(dgl_all$Sign), "None", dgl_all$Sign)
-
-dgl_all_plot <- ggplot(data = dgl_all, aes(x = InG2P, y = Statistic)) +
-  facet_grid(group_general_lineage_name ~ Measure * Dataset) +
-  geom_jitter(mapping = aes(shape = Sign, fill = InG2P, color = InG2P), width = 0.4, alpha = 0.5, size = 1) +
-  geom_boxplot(width = 0.25, fill = NA, outlier.shape = NA) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_shape_manual(values = c(25, 24, 4), labels = c("Negative", "Positive", "NA")) +
-  theme(legend.position = "top") +
-  guides(color = FALSE, fill = FALSE)
-
-# ggsave("./plots/manuscript/all_dgl_plot.png", dgl_all_plot, device = "png", dpi = 450, width = 12, height = 40, units = "in")
-```
-
-## Pancancer vs. Lineage
+# Pancancer vs. Lineage
+
+--------------------------------------------------------------------------------
 
@@
 
-## Cell line overlap
-
-```{r, eval=FALSE}
-crispr_ccl <- unique(select(crispr_data, DepMap_ID, CCLE_Name))
-ccle_ccl <- unique(select(ccle_data, DepMap_ID, CCLE_Name, accession_id))
-ctrp_ccl <- unique(select(ctrp_data, DepMap_ID, CCLE_Name, accession_id))
-gdsc_ccl <- unique(select(gdsc_data, DepMap_ID, CCLE_Name, accession_id))
-# all_ccl <- merge(ccle_ccl, ctrp_ccl, by = c("DepMap_ID", "CCLE_Name", "accession_id"), all = TRUE)
-```
-
-# OLD: BOXPLOTS
+# OLD: Distribution t-tests
+
+--------------------------------------------------------------------------------
+
+## Mut
+
+CRISPR mutation status plots of p-values:
+```{r fig.height=1.5, fig.width=12}
+crispr_signif_g2p_gene$y_label <- "CRISPR"
+crispr_signif_g2p_gene$Hugo_Symbol <- factor(crispr_signif_g2p_gene$Hugo_Symbol, levels = g2p_genes)
+crispr_signif_g2p_gene$p <- as.numeric(as.character(crispr_signif_g2p_gene$p))
+
+crispr_mut_heatmap_plot <- ggplot(data = crispr_signif_g2p_gene, aes(x = Hugo_Symbol, y = y_label)) +
+  geom_tile(aes(fill = p)) +
+  scale_fill_gradientn(colors = c("darkgreen", "honeydew", "white"), values = c(0, 0.05, 1), na.value = "darksalmon") +
+  scale_x_discrete(drop = FALSE) +
+  theme(axis.title.y = element_blank(), axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 10)) +
+  labs(x = "Gene")
+crispr_mut_heatmap_plot
+
+# write.table(crispr_signif_g2p_gene, file = "~/Desktop/crispr_signif_g2p_gene_20181203.csv", quote = FALSE, sep = ",", row.names = FALSE)
+# ggsave("./plots/manuscript/crispr_mut_heatmap_plot_example.png", crispr_mut_heatmap_plot, device = "png", dpi = 450, width = 12, height = 1.5, units = "in")
+```
+
+```{r}
+ccle_mut_summ <- merge(g2p_druggene_tally, ccle_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
+ccle_mut_summ$n <- ifelse(is.na(ccle_mut_summ$n), 0, ccle_mut_summ$n)
+ccle_mut_summ$InG2P <- ifelse(ccle_mut_summ$n != 0, "Yes", "No")
+ccle_mut_summ$Dataset <- "CCLE"
+ccle_p_ttest <- t.test(ccle_mut_summ$p ~ ccle_mut_summ$InG2P)
+ccle_p_ttest_res <- paste0("t(", round(ccle_p_ttest$parameter, 0), ") = ", round(ccle_p_ttest$statistic, 2), ", p = ", round(ccle_p_ttest$p.value, 2))
+
+ctrp_mut_summ <- merge(g2p_druggene_tally, ctrp_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
+ctrp_mut_summ$n <- ifelse(is.na(ctrp_mut_summ$n), 0, ctrp_mut_summ$n)
+ctrp_mut_summ$InG2P <- ifelse(ctrp_mut_summ$n != 0, "Yes", "No")
+ctrp_mut_summ$Dataset <- "CTRP"
+ctrp_p_ttest <- t.test(ctrp_mut_summ$p ~ ctrp_mut_summ$InG2P)
+ctrp_p_ttest_res <- paste0("t(", round(ctrp_p_ttest$parameter, 0), ") = ", round(ctrp_p_ttest$statistic, 2), ", p = ", formatC(ctrp_p_ttest$p.value, digits = 2, format = "f"))
+
+gdsc_mut_summ <- merge(g2p_druggene_tally, gdsc_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
+gdsc_mut_summ$n <- ifelse(is.na(gdsc_mut_summ$n), 0, gdsc_mut_summ$n)
+gdsc_mut_summ$InG2P <- ifelse(gdsc_mut_summ$n != 0, "Yes", "No")
+gdsc_mut_summ$Dataset <- "GDSC"
+gdsc_p_ttest <- t.test(gdsc_mut_summ$p ~ gdsc_mut_summ$InG2P)
+gdsc_p_ttest_res <- paste0("t(", round(gdsc_p_ttest$parameter, 0), ") = ", round(gdsc_p_ttest$statistic, 2), ", p = ", formatC(gdsc_p_ttest$p.value, digits = 2, format = "f"))
+
+g2p_mut_all_summ <- rbind(ccle_mut_summ, ctrp_mut_summ, gdsc_mut_summ)
+g2p_mut_all_summ$p_log10 <- -log10(g2p_mut_all_summ$p)
+g2p_mut_all_summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"), Test_Results_p = c(ccle_p_ttest_res, ctrp_p_ttest_res, gdsc_p_ttest_res))
+g2p_mut_all_summ$Drug_Gene_Ordered <- factor(g2p_mut_all_summ$Drug_Gene, levels = as.character(unique(g2p_mut_all_summ$Drug_Gene)), labels = sapply(strsplit(x = as.character(unique(g2p_mut_all_summ$Drug_Gene)), split = "_"), function(x) paste0(x[1], "\n", x[2])))
+```
+
+```{r fig.height=5, fig.width=12}
+plot_p_point <- ggplot(data = g2p_mut_all_summ, aes(x = p, y = n, label = Drug_Gene)) +
+  facet_wrap(~ Dataset, scales = "free_x") +
+  geom_point(mapping = aes(color = InG2P), alpha = 0.5) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
+  geom_text_repel(data = subset(g2p_mut_all_summ, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
+  geom_text(data = g2p_mut_all_summ_text, mapping = aes(x = 0.5, y = 115, label = Test_Results_p)) +
+  labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations") +
+  theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
+
+plot_p_box <- ggplot(data = g2p_mut_all_summ) +
+  facet_wrap(~ Dataset, scales = "free_x") +
+  geom_violin(mapping = aes(color = InG2P, fill = InG2P, y = p, x = InG2P), alpha = 0.35) +
+  geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), width = 0.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  coord_flip() +
+  labs(x = "In G2P?") +
+  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
+
+plot_p_point <- ggplot_gtable(ggplot_build(plot_p_point))
+plot_p_box <- ggplot_gtable(ggplot_build(plot_p_box))
+p_maxWidth <-  grid::unit.pmax(plot_p_point$widths, plot_p_box$widths)
+plot_p_point$widths <- as.list(p_maxWidth)
+plot_p_box$widths <- as.list(p_maxWidth)
+g2p_mut_plot <- cowplot::plot_grid(plot_p_box,
+                   plot_p_point,
+                   nrow = 2,
+                   rel_heights = c(1, 4))
+g2p_mut_plot
+
+# ggsave("./plots/manuscript/g2p_mut_plot.png", g2p_mut_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
+```
+
+```{r, eval=FALSE}
+plot_p_point <- ggplot(data = g2p_mut_all_summ) +
+  facet_wrap(~ Dataset, scales = "free_x") +
+  geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = p, y = n), alpha = 0.5) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
+  geom_text(data = g2p_mut_all_summ_text, mapping = aes(x = 0.5, y = 115, label = Test_Results_p)) +
+  labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations") +
+  theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
+
+plot_p_box <- ggplot(data = g2p_mut_all_summ) +
+  facet_wrap(~ Dataset, scales = "free_x") +
+  geom_violin(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.5) +
+  geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.75, width = 0.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  coord_flip() +
+  labs(x = "Level A G2P\nassociation") +
+  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
+
+plot <- subplot(plot_p_box, plot_p_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Gene-drug association p-value between mutation groups"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
+
+saveWidgetFix(widget = plot, file = "./plots/manuscript/g2p_mut_plot.html")
+```
+
+## GE
+
+### Pearson
+
+```{r fig.height=5, fig.width=12}
+plot_ge_pearson_point <- ggplot(data = g2p_cor, aes(x = Pearson_GE_Abs, y = n, label = Drug_Gene)) +
+  facet_wrap(~ Dataset) +
+  geom_point(mapping = aes(fill = InG2P, color = InG2P, shape = Pearson_GE_Sign), alpha = 0.5, size = 1.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
+  scale_x_continuous(breaks = seq(0, 0.65, by = 0.1), labels = seq(0, 0.65, by = 0.1)) +
+  coord_cartesian(xlim = c(0, 0.65)) +
+  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
+  geom_text_repel(data = subset(g2p_cor, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
+  geom_text(data = g2p_cor_text, mapping = aes(x = 0.325, y = 115, label = Pearson_Test_Results_GE)) +
+  labs(x = "Pearson correlation coefficient (r) between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +
+  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
+  guides(color = FALSE, fill = FALSE, shape = FALSE)
+
+plot_ge_pearson_box <- ggplot(data = g2p_cor) +
+  facet_wrap(~ Dataset) +
+  geom_violin(mapping = aes(color = InG2P, fill = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.35) +
+  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), width = 0.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_y_continuous(breaks = seq(0, 0.65, by = 0.1), labels = seq(0, 0.65, by = 0.1)) +
+  coord_flip(ylim = c(0, 0.65)) +
+  labs(x = "In G2P?") +
+  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
+
+plot_ge_pearson_point <- ggplot_gtable(ggplot_build(plot_ge_pearson_point))
+plot_ge_pearson_box <- ggplot_gtable(ggplot_build(plot_ge_pearson_box))
+p_maxWidth <-  grid::unit.pmax(plot_ge_pearson_point$widths[2:3], plot_ge_pearson_box$widths[2:3])
+plot_ge_pearson_point$widths[2:3] <- p_maxWidth
+plot_ge_pearson_box$widths[2:3] <- p_maxWidth
+
+g2p_ge_pearson_plot <- cowplot::plot_grid(plot_ge_pearson_box, plot_ge_pearson_point, nrow = 2, rel_heights = c(1, 4))
+g2p_ge_pearson_plot
+
+# ggsave("./plots/manuscript/g2p_ge_pearson_plot.png", g2p_ge_pearson_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
+```
+
+```{r, eval=FALSE}
+plot_ge_point <- ggplot(data = g2p_cor) +
+  facet_wrap(~ Dataset) +
+  geom_point(mapping = aes(label = Drug_Gene, fill = InG2P, color = InG2P, shape = Pearson_GE_Sign, x = Pearson_GE_Abs, y = n, size = Pearson_Pval_GE), alpha = 0.5, size = 1.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
+  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
+  scale_x_continuous(breaks = pretty_breaks()) +
+  geom_text(data = g2p_cor_text, mapping = aes(x = 0.3, y = 115, label = Pearson_Test_Results_GE)) +
+  labs(x = "Pearson correlation coefficient (r) between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +
+  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
+  guides(color = FALSE, fill = FALSE) +
+  labs(shape = NULL)
+
+plot_ge_box <- ggplot(data = g2p_cor) +
+  facet_wrap(~ Dataset) +
+  geom_violin(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.5) +
+  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  coord_flip() +
+  labs(x = "In G2P?") +
+  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
+
+ge_pearson_plot <- subplot(plot_ge_box, plot_ge_point, nrows = 2, heights = c(0.2, 0.8), titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and gene expression"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
+
+saveWidgetFix(widget = ge_pearson_plot, file = "./plots/manuscript/g2p_ge_pearson_plot.html")
+```
+
+### Spearman
+
+```{r fig.height=5, fig.width=12}
+plot_ge_spearman_point <- ggplot(data = g2p_cor, aes(x = Spearman_GE_Abs, y = n, label = Drug_Gene)) +
+  facet_wrap(~ Dataset) +
+  geom_point(mapping = aes(fill = InG2P, color = InG2P, shape = Spearman_GE_Sign), alpha = 0.5, size = 1.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
+  scale_x_continuous(breaks = seq(0, 0.65, by = 0.1), labels = seq(0, 0.65, by = 0.1)) +
+  coord_cartesian(xlim = c(0, 0.6)) +
+  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
+  geom_text_repel(data = subset(g2p_cor, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
+  geom_text(data = g2p_cor_text, mapping = aes(x = 0.3, y = 115, label = Spearman_Test_Results_GE)) +
+  labs(x = "Spearman correlation coefficient (r_s) between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +
+  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
+  guides(color = FALSE, fill = FALSE, shape = FALSE)
+
+plot_ge_spearman_box <- ggplot(data = g2p_cor) +
+  facet_wrap(~ Dataset) +
+  geom_violin(mapping = aes(color = InG2P, fill = InG2P, y = Spearman_GE_Abs, x = InG2P), alpha = 0.35) +
+  geom_boxplot(mapping = aes(color = InG2P, y = Spearman_GE_Abs, x = InG2P), width = 0.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_y_continuous(breaks = seq(0, 0.65, by = 0.1), labels = seq(0, 0.65, by = 0.1)) +
+  coord_flip(ylim = c(0, 0.6)) +
+  labs(x = "In G2P?") +
+  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
+
+plot_ge_spearman_point <- ggplot_gtable(ggplot_build(plot_ge_spearman_point))
+plot_ge_spearman_box <- ggplot_gtable(ggplot_build(plot_ge_spearman_box))
+p_maxWidth <-  grid::unit.pmax(plot_ge_spearman_point$widths[2:3], plot_ge_spearman_box$widths[2:3])
+plot_ge_spearman_point$widths[2:3] <- p_maxWidth
+plot_ge_spearman_box$widths[2:3] <- p_maxWidth
+
+g2p_ge_spearman_plot <- cowplot::plot_grid(plot_ge_spearman_box, plot_ge_spearman_point, nrow = 2, rel_heights = c(1, 4))
+g2p_ge_spearman_plot
+
+# ggsave("./plots/manuscript/g2p_ge_spearman_plot.png", g2p_ge_spearman_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
+```
+
+```{r, eval=FALSE}
+plot_ge_point <- ggplot(data = g2p_cor) +
+  facet_wrap(~ Dataset) +
+  geom_point(mapping = aes(label = Drug_Gene, fill = InG2P, color = InG2P, shape = Spearman_GE_Sign, x = Spearman_GE_Abs, y = n, size = Spearman_Pval_GE), alpha = 0.5, size = 1.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
+  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
+  scale_x_continuous(breaks = pretty_breaks()) +
+  geom_text(data = g2p_cor_text, mapping = aes(x = 0.3, y = 115, label = Spearman_Test_Results_GE)) +
+  labs(x = "Spearman correlation coefficient (r_s) between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +
+  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
+  guides(color = FALSE, fill = FALSE) +
+  labs(shape = NULL)
+
+plot_ge_box <- ggplot(data = g2p_cor) +
+  facet_wrap(~ Dataset) +
+  geom_violin(mapping = aes(color = InG2P, y = Spearman_GE_Abs, x = InG2P), alpha = 0.5) +
+  geom_boxplot(mapping = aes(color = InG2P, y = Spearman_GE_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  coord_flip() +
+  labs(x = "In G2P?") +
+  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
+
+ge_spearman_plot <- subplot(plot_ge_box, plot_ge_point, nrows = 2, heights = c(0.2, 0.8), titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Spearman correlation coefficient between drug-gene AUC and gene expression"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
+
+saveWidgetFix(widget = ge_spearman_plot, file = "./plots/manuscript/g2p_ge_spearman_plot.html")
+```
+
+## CN
+
+### Pearson
+
+```{r fig.height=5, fig.width=12}
+plot_cn_pearson_point <- ggplot(data = g2p_cor, aes(x = Pearson_CN_Abs, y = n, label = Drug_Gene)) +
+  facet_wrap(~ Dataset) +
+  geom_point(mapping = aes(fill = InG2P, color = InG2P, shape = Pearson_CN_Sign), alpha = 0.5, size = 1.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
+  scale_x_continuous(breaks = seq(0, 0.65, by = 0.1), labels = seq(0, 0.65, by = 0.1)) +
+  coord_cartesian(xlim = c(0, 0.5)) +
+  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
+  geom_text_repel(data = subset(g2p_cor, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
+  geom_text(data = g2p_cor_text, mapping = aes(x = 0.25, y = 115, label = Pearson_Test_Results_CN)) +
+  labs(x = "Pearson correlation coefficient (r) between drug-gene AUC and copy number", y = "Number of level A G2P associations") +
+  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
+  guides(color = FALSE, fill = FALSE, shape = FALSE)
+
+plot_cn_pearson_box <- ggplot(data = g2p_cor) +
+  facet_wrap(~ Dataset) +
+  geom_violin(mapping = aes(color = InG2P, fill = InG2P, y = Pearson_CN_Abs, x = InG2P), alpha = 0.35) +
+  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_CN_Abs, x = InG2P), width = 0.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_y_continuous(breaks = seq(0, 0.65, by = 0.1), labels = seq(0, 0.65, by = 0.1)) +
+  coord_flip(ylim = c(0, 0.5)) +
+  labs(x = "In G2P?") +
+  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
+
+plot_cn_pearson_point <- ggplot_gtable(ggplot_build(plot_cn_pearson_point))
+plot_cn_pearson_box <- ggplot_gtable(ggplot_build(plot_cn_pearson_box))
+p_maxWidth <-  grid::unit.pmax(plot_cn_pearson_point$widths[2:3], plot_cn_pearson_box$widths[2:3])
+plot_cn_pearson_point$widths[2:3] <- p_maxWidth
+plot_cn_pearson_box$widths[2:3] <- p_maxWidth
+
+g2p_cn_pearson_plot <- cowplot::plot_grid(plot_cn_pearson_box, plot_cn_pearson_point, nrow = 2, rel_heights = c(1, 4))
+g2p_cn_pearson_plot
+
+# ggsave("./plots/manuscript/g2p_cn_pearson_plot.png", g2p_cn_pearson_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
+```
+
+```{r, eval=FALSE}
+plot_cn_point <- ggplot(data = g2p_cor) +
+  facet_wrap(~ Dataset) +
+  geom_point(mapping = aes(label = Drug_Gene, fill = InG2P, color = InG2P, shape = Pearson_CN_Sign, x = Pearson_CN_Abs, y = n, size = Pearson_Pval_CN), alpha = 0.5, size = 1.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
+  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
+  scale_x_continuous(breaks = pretty_breaks()) +
+  geom_text(data = g2p_cor_text, mapping = aes(x = 0.3, y = 115, label = Pearson_Test_Results_CN)) +
+  labs(x = "Pearson correlation coefficient (r) between drug-gene AUC and copy number", y = "Number of level A G2P associations") +
+  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
+  guides(color = FALSE, fill = FALSE) +
+  labs(shape = NULL)
+
+plot_cn_box <- ggplot(data = g2p_cor) +
+  facet_wrap(~ Dataset) +
+  geom_violin(mapping = aes(color = InG2P, y = Pearson_CN_Abs, x = InG2P), alpha = 0.5) +
+  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_CN_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  coord_flip() +
+  labs(x = "In G2P?") +
+  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
+
+cn_pearson_plot <- subplot(plot_cn_box, plot_cn_point, nrows = 2, heights = c(0.2, 0.8), titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and copy number"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
+
+saveWidgetFix(widget = ge_pearson_plot, file = "./plots/manuscript/g2p_cn_pearson_plot.html")
+```
+
+### Spearman
+
+```{r fig.height=5, fig.width=12}
+plot_cn_spearman_point <- ggplot(data = g2p_cor, aes(x = Spearman_CN_Abs, y = n, label = Drug_Gene)) +
+  facet_wrap(~ Dataset) +
+  geom_point(mapping = aes(fill = InG2P, color = InG2P, shape = Spearman_CN_Sign), alpha = 0.5, size = 1.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
+  scale_x_continuous(breaks = seq(0, 0.4, by = 0.05), labels = seq(0, 0.4, by = 0.05)) +
+  coord_cartesian(xlim = c(0, 0.35)) +
+  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
+  geom_text_repel(data = subset(g2p_cor, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
+  geom_text(data = g2p_cor_text, mapping = aes(x = 0.175, y = 115, label = Spearman_Test_Results_CN)) +
+  labs(x = "Spearman correlation coefficient (r_s) between drug-gene AUC and copy number", y = "Number of level A G2P associations") +
+  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
+  guides(color = FALSE, fill = FALSE, shape = FALSE)
+
+plot_cn_spearman_box <- ggplot(data = g2p_cor) +
+  facet_wrap(~ Dataset) +
+  geom_violin(mapping = aes(color = InG2P, fill = InG2P, y = Spearman_CN_Abs, x = InG2P), alpha = 0.35) +
+  geom_boxplot(mapping = aes(color = InG2P, y = Spearman_CN_Abs, x = InG2P), width = 0.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_y_continuous(breaks = seq(0, 0.4, by = 0.05), labels = seq(0, 0.4, by = 0.05)) +
+  coord_flip(ylim = c(0, 0.35)) +
+  labs(x = "In G2P?") +
+  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
+
+plot_cn_spearman_point <- ggplot_gtable(ggplot_build(plot_cn_spearman_point))
+plot_cn_spearman_box <- ggplot_gtable(ggplot_build(plot_cn_spearman_box))
+p_maxWidth <-  grid::unit.pmax(plot_cn_spearman_point$widths[2:3], plot_cn_spearman_box$widths[2:3])
+plot_cn_spearman_point$widths[2:3] <- p_maxWidth
+plot_cn_spearman_box$widths[2:3] <- p_maxWidth
+
+g2p_cn_spearman_plot <- cowplot::plot_grid(plot_cn_spearman_box, plot_cn_spearman_point, nrow = 2, rel_heights = c(1, 4))
+g2p_cn_spearman_plot
+
+# ggsave("./plots/manuscript/g2p_cn_spearman_plot.png", g2p_cn_spearman_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
+```
+
+```{r, eval=FALSE}
+plot_cn_point <- ggplot(data = g2p_cor) +
+  facet_wrap(~ Dataset) +
+  geom_point(mapping = aes(label = Drug_Gene, fill = InG2P, color = InG2P, shape = Spearman_CN_Sign, x = Spearman_CN_Abs, y = n, size = Spearman_Pval_CN), alpha = 0.5, size = 1.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
+  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
+  scale_x_continuous(breaks = pretty_breaks()) +
+  geom_text(data = g2p_cor_text, mapping = aes(x = 0.175, y = 115, label = Spearman_Test_Results_CN)) +
+  labs(x = "Spearman correlation coefficient (r_s) between drug-gene AUC and copy number", y = "Number of level A G2P associations") +
+  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
+  guides(color = FALSE, fill = FALSE) +
+  labs(shape = NULL)
+
+plot_cn_box <- ggplot(data = g2p_cor) +
+  facet_wrap(~ Dataset) +
+  geom_violin(mapping = aes(color = InG2P, y = Spearman_CN_Abs, x = InG2P), alpha = 0.5) +
+  geom_boxplot(mapping = aes(color = InG2P, y = Spearman_CN_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
+  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
+  coord_flip() +
+  labs(x = "In G2P?") +
+  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
+
+cn_spearman_plot <- subplot(plot_cn_box, plot_cn_point, nrows = 2, heights = c(0.2, 0.8), titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Spearman correlation coefficient between drug-gene AUC and copy number"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
+
+saveWidgetFix(widget = cn_spearman_plot, file = "./plots/manuscript/g2p_cn_spearman_plot.html")
+```
+
+## By lineage
+
+Make summary plots of mutation status tests by lineage and return a dataframe of all t-test results from comparing the p-value distributions of G2P and non-G2P drug-gene associaions:
+```{r, eval=FALSE, results = 'hide'}
+dgl_mut_g2p_grid_ttest_res <- lapply(as.character(unique(dgl_mut_grid_summ$group_general_lineage_name)), MutPlotsByLineage)
+dgl_mut_g2p_grid_ttest_res_list <- rbindlist(dgl_mut_g2p_grid_ttest_res, use.names = TRUE)
+dgl_mut_g2p_grid_ttest_res_list <- dgl_mut_g2p_grid_ttest_res_list[order(dgl_mut_g2p_grid_ttest_res_list$p_value),]
+saveRDS(dgl_mut_g2p_grid_ttest_res_list, "./data_munging/rds/dgl_mut_g2p_grid_ttest_res_list.rds")
+```
+
+```{r}
+dgl_mut_g2p_grid_ttest_res_list <- readRDS("./data_munging/rds/dgl_mut_g2p_grid_ttest_res_list.rds")
+dgl_mut_g2p_grid_ttest_res_list_kable <- knitr::kable(dgl_mut_g2p_grid_ttest_res_list, caption = "Mutation status: T-test results for level A G2P drug-gene associations across lineages") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+Make summary plots of gene expression and copy number tests by lineage and return a dataframe of all t-test results from comparing the p-value distributions of G2P and non-G2P drug-gene associaions:
+```{r, results='hide', eval=FALSE}
+dgl_pearson_g2p_grid_ttest_res <- lapply(as.character(unique(dgl_signif_pearson_g2p_grid$group_general_lineage_name)), PearsonPlotsByLineage)
+dgl_pearson_g2p_grid_ttest_res_list <- rbindlist(dgl_pearson_g2p_grid_ttest_res, use.names = TRUE)
+saveRDS(dgl_pearson_g2p_grid_ttest_res_list, "./data_munging/rds/dgl_pearson_g2p_grid_ttest_res_list.rds")
+```
+
+```{r}
+dgl_pearson_g2p_grid_ttest_res_list <- readRDS("./data_munging/rds/dgl_pearson_g2p_grid_ttest_res_list.rds")
+
+dgl_ge_g2p_grid_ttest_res_list_kable <- knitr::kable(dgl_pearson_g2p_grid_ttest_res_list[order(dgl_pearson_g2p_grid_ttest_res_list$p_value_GE), c("Dataset", "group_general_lineage_name", "t_statistic_GE", "df_GE", "p_value_GE")], caption = "Gene expression: T-test results for level A G2P drug-gene/gene expression associations across lineages") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+
+dgl_cn_g2p_grid_ttest_res_list_kable <- knitr::kable(dgl_pearson_g2p_grid_ttest_res_list[order(dgl_pearson_g2p_grid_ttest_res_list$p_value_CN), c("Dataset", "group_general_lineage_name", "t_statistic_CN", "df_CN", "p_value_CN")], caption = "Copy number: T-test results for level A G2P drug-gene/gene expression associations across lineages") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+### Grid t-test summaries
+
+Figure #.
+Histograms of p-values from t-tests comparing distributions of summary statistics for CCLE, CTRP, and GDSC drug screen results in the context of G2P level A evidence and lineage.
+Each p-value is derived from comparisons similar to those shown in Figure 2, but for these p-values, the data is grouped by lineage prior to conducting the t-test rather than the test being lineage-agnostic.
+To produce these p-values, AUC was correlated with each genomic feature for all possible pairwise combinations of G2P drugs and genes in all lineages represented in each dataset.
+For each lineage, t-tests were used to compare distributions of p-values (mutation status) or Pearson correlation coefficients (gene expression and copy number) that were grouped by whether or not the underlying drug-gene combination had level-A G2P evidence.
+For each dataset, if there were two or more correlation results in each G2P presence/absence group in a specific lineage, a t-test was conducted and the p-value appears in the appropriate histogram.
+Mutation status histograms are sparse due to limited mutation annotations for many of the G2P genes in all screened cell lines.
+```{r fig.height=4, fig.width=12}
+ttest_summ_res_mut <- dgl_mut_g2p_grid_ttest_res_list[, c("p_value", "Dataset", "group_general_lineage_name")]
+ttest_summ_res_mut$Metric <- "Mutation Status"
+
+ttest_summ_res_ge <- dgl_pearson_g2p_grid_ttest_res_list[, c("p_value_GE", "Dataset", "group_general_lineage_name")]
+colnames(ttest_summ_res_ge) <- c("p_value", "Dataset", "group_general_lineage_name")
+ttest_summ_res_ge$Metric <- "Gene Expression"
+
+ttest_summ_res_cn <- dgl_pearson_g2p_grid_ttest_res_list[, c("p_value_CN", "Dataset", "group_general_lineage_name")]
+colnames(ttest_summ_res_cn) <- c("p_value", "Dataset", "group_general_lineage_name")
+ttest_summ_res_cn$Metric <- "Copy Number"
+
+ttest_summ_res <- rbind(ttest_summ_res_mut, ttest_summ_res_ge, ttest_summ_res_cn)
+ttest_summ_res$Metric <- factor(ttest_summ_res$Metric, levels = c("Mutation Status", "Gene Expression", "Copy Number"))
+
+ttest_mut_summ_facet <- ggplot(data = ttest_summ_res, aes(x = p_value, fill = Dataset, color = Dataset)) +
+  facet_grid(Metric ~ Dataset) +
+  geom_histogram(bins = 40, binwidth = 0.025, boundary = 0, closed = "left") +
+  scale_y_continuous(breaks = c(0:6), labels = c(0:6)) +
+  scale_x_continuous(breaks = seq(0, 1, by = 0.1), expand = c(0.01, 0.01)) +
+  scale_fill_manual(values = c("CCLE" = "palegreen3", "CTRP" = "slategray3", "GDSC" = "paleturquoise3")) +
+  scale_color_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
+  theme(legend.position = c(0.5, 1.7), legend.direction = "horizontal", panel.grid.minor.y = element_blank()) +
+  labs(x = "P-value", y = "Frquency")
+ttest_mut_summ_facet
+
+# ggsave("./plots/manuscript/all_dgl_ttest_summ_facet_plot.png", ttest_mut_summ_facet, device = "png", dpi = 450, width = 12, height = 4, units = "in")
+```
+
+# OLD: Boxplots
 
@@
 
-# OLD: CRISPR POINT MUT MAPPING
+# OLD: CRISPR point mut mapping
 

### 2019-01-07 manuscript_analysis.Rmd
spearman/pearson overlap

@@
 crispr_signif_g2p_gene <- rbind(crispr_signif_g2p_gene, c("G6PD", rep(NA, 11)))
-knitr::kable(crispr_signif_g2p_gene[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results for Level A point mutations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+crispr_signif_g2p_gene_kable <- knitr::kable(crispr_signif_g2p_gene[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results for Level A point mutations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 crispr_signif_g2p_lineage <- readRDS("./data_munging/rds/crispr_signif_g2p_lineage.rds")
-knitr::kable(filter(crispr_signif_g2p_lineage, p < 0.1)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant vs wildtype cell lines by lineage, p < 0.1 (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+crispr_signif_g2p_lineage_kable <- knitr::kable(filter(crispr_signif_g2p_lineage, p < 0.1)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant vs wildtype cell lines by lineage, p < 0.1 (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 crispr_res_mut$Metric <- "Mutation Status"
-crispr_res_mut$p_log10 <- -log10(crispr_res_mut$p)
+crispr_res_mut$p_log10 <- -log10(as.numeric(crispr_res_mut$p))
 subset(crispr_res_mut, p < 0.05)
@@
 
+Mutation summaries for G2P gri comparisons:
+```{r}
+ccle_mut_summ <- merge(g2p_druggene_tally, ccle_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
+ccle_mut_summ$n <- ifelse(is.na(ccle_mut_summ$n), 0, ccle_mut_summ$n)
+ccle_mut_summ$InG2P <- ifelse(ccle_mut_summ$n != 0, "Yes", "No")
+ccle_mut_summ$Dataset <- "CCLE"
+
+ctrp_mut_summ <- merge(g2p_druggene_tally, ctrp_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
+ctrp_mut_summ$n <- ifelse(is.na(ctrp_mut_summ$n), 0, ctrp_mut_summ$n)
+ctrp_mut_summ$InG2P <- ifelse(ctrp_mut_summ$n != 0, "Yes", "No")
+ctrp_mut_summ$Dataset <- "CTRP"
+
+gdsc_mut_summ <- merge(g2p_druggene_tally, gdsc_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
+gdsc_mut_summ$n <- ifelse(is.na(gdsc_mut_summ$n), 0, gdsc_mut_summ$n)
+gdsc_mut_summ$InG2P <- ifelse(gdsc_mut_summ$n != 0, "Yes", "No")
+gdsc_mut_summ$Dataset <- "GDSC"
+
+g2p_mut_all_summ <- rbind(ccle_mut_summ, ctrp_mut_summ, gdsc_mut_summ)
+g2p_mut_all_summ$p_log10 <- -log10(g2p_mut_all_summ$p)
+```
+
 ```{r fig.height=6, fig.width=12}
@@
 # ggsave("./plots/manuscript/all_pval_summ_plot2.png", pval_summ_plot2, device = "png", dpi = 450, width = 12, height = 6, units = "in")
+```
+
+## Pearson/Spearman comparison
+
+Compare significant Pearson and Spearman correlations:
+```{r}
+corr_summ_ge <- select(g2p_cor, Drug_Gene, n, Pearson_Pval_GE, Spearman_Pval_GE, InG2P, Dataset)
+corr_summ_ge$Pearson_Pval_GE_log10 <- -log10(corr_summ_ge$Pearson_Pval_GE)
+corr_summ_ge$Spearman_Pval_GE_log10 <- -log10(corr_summ_ge$Spearman_Pval_GE)
+corr_summ_ge$Overlap_Status <- ifelse(corr_summ_ge$Pearson_Pval_GE < 0.05 & corr_summ_ge$Spearman_Pval_GE < 0.05, "Both", ifelse(corr_summ_ge$Pearson_Pval_GE < 0.05, "Pearson", ifelse(corr_summ_ge$Spearman_Pval_GE < 0.05, "Spearman", NA)))
+corr_summ_ge$Overlap_Status_Bonf <- ifelse(corr_summ_ge$Pearson_Pval_GE < 0.05 / nrow(corr_summ_ge) & corr_summ_ge$Spearman_Pval_GE < 0.05 / nrow(corr_summ_ge), "Both", ifelse(corr_summ_ge$Pearson_Pval_GE < 0.05 / nrow(corr_summ_ge), "Pearson", ifelse(corr_summ_ge$Spearman_Pval_GE < 0.05 / nrow(corr_summ_ge), "Spearman", NA)))
+corr_summ_ge %>% count(Overlap_Status)
+corr_summ_ge %>% count(Overlap_Status_Bonf)
+
+corr_summ_cn <- select(g2p_cor, Drug_Gene, n, Pearson_Pval_CN, Spearman_Pval_CN, InG2P, Dataset)
+corr_summ_cn$Pearson_Pval_CN_log10 <- -log10(corr_summ_cn$Pearson_Pval_CN)
+corr_summ_cn$Spearman_Pval_CN_log10 <- -log10(corr_summ_cn$Spearman_Pval_CN)
+corr_summ_cn$Overlap_Status <- ifelse(corr_summ_cn$Pearson_Pval_CN < 0.05 & corr_summ_cn$Spearman_Pval_CN < 0.05, "Both", ifelse(corr_summ_cn$Pearson_Pval_CN < 0.05, "Pearson", ifelse(corr_summ_cn$Spearman_Pval_CN < 0.05, "Spearman", NA)))
+corr_summ_cn$Overlap_Status_Bonf <- ifelse(corr_summ_cn$Pearson_Pval_CN < 0.05 / nrow(corr_summ_cn) & corr_summ_cn$Spearman_Pval_CN < 0.05 / nrow(corr_summ_cn), "Both", ifelse(corr_summ_cn$Pearson_Pval_CN < 0.05 / nrow(corr_summ_cn), "Pearson", ifelse(corr_summ_cn$Spearman_Pval_CN < 0.05 / nrow(corr_summ_cn), "Spearman", NA)))
+corr_summ_cn %>% count(Overlap_Status)
+corr_summ_cn %>% count(Overlap_Status_Bonf)
 ```

### 2019-01-07 manuscript.Rmd

@@
 
-At an $\alpha =  0.05$, no DGLs were identified in the CCLE screen when using mutation status as a correlate (n = 7), but CTRP and GDSC identified six and five, respectively, in skin cancer, lung cancer, and cancer.
+At an $\alpha =  0.05$, no DGLs were identified in the CCLE screen when using mutation status as a correlate (*n = 7*), but CTRP and GDSC identified *six* and *five*, respectively, in skin cancer, lung cancer, and cancer.
 These significant associations did not hold after Bonferroni correction in CTRP ($n = 48$, $\alpha_{adjusted} = 0.001$) or GDSC ($n = 39$, $\alpha_{adjusted} = 0.001$).

### 2019-01-08 manuscript.Rmd
update rmds

--- 2019-01-04 manuscript.Rmd
@@
 
-```{r grid-wilcox-res, echo = FALSE}
+```{r grid-dg-wilcox, echo = FALSE}
 ccle_signif_g2p_grid <- readRDS("./data_munging/rds/ccle_signif_g2p_grid.rds")
@@
 ## Do small-molecule screens in cancer cell lines recapitulate clinical drug-gene associations?
+
+**Cut this analysis since we are comparing distributions of p-values?**
 
@@
 
+```{r grid-dgl-wilcox, echo = FALSE}
+ccle_signif_g2p_lineage <- readRDS("./data_munging/rds/ccle_signif_g2p_lineage.rds")
+ccle_signif_grid_lineage <- readRDS("./data_munging/rds/ccle_signif_grid_lineage.rds")
+
+ctrp_signif_g2p_lineage <- readRDS("./data_munging/rds/ctrp_signif_g2p_lineage.rds")
+ctrp_signif_grid_lineage <- readRDS("./data_munging/rds/ctrp_signif_grid_lineage.rds")
+
+gdsc_signif_g2p_lineage <- readRDS("./data_munging/rds/gdsc_signif_g2p_lineage.rds")
+gdsc_signif_grid_lineage <- readRDS("./data_munging/rds/gdsc_signif_grid_lineage.rds")
+```
+
 - What do these correlations with mutation status, gene expression, and copy number look like when you constrict to a specific lineage?
@@
 CCLE, GTRP, and GDSC all had lineages labeled “leukemia” and “T-cell childhood acute lymphocytic leukemia” and the CRISPR dataset had cell lines labeled “Epstein-Barr virus-related Burkitt lymphoma” and “lymphoma.” To more easily conduct comparative analyses in a cancer-specific manner, we developed a more general lineage grouping method derived from the Human Disease Ontology identity codes (DOIDs, http://disease-ontology.org/) [@schriml2019] assigned to each cell line, yielding `r length(unique(ccl_converter$group_general_lineage_name))` unique lineage groupings.
-This custom lineage grouping was included in our harmonized cancer cell line database (see METHODS).
+This custom lineage grouping was included in our harmonized cancer cell line database (see Methods).
 
@@
 
-At an $\alpha =  0.05$, no DGLs were identified in the CCLE screen when using mutation status as a correlate (n = 7), but CTRP and GDSC identified six and five, respectively, in skin cancer, lung cancer, and cancer.
-These significant associations did not hold after Bonferroni correction in CTRP ($n = 48$, $\alpha_{adjusted} = 0.001$) or GDSC ($n = 39$, $\alpha_{adjusted} = 0.001$).
+Prior to correction for an FDR of 5%, no DGLs were identified in the CCLE screen when using mutation status as a correlate ($n =$ `r nrow(ccle_signif_g2p_lineage)`, `r length(unique(ccle_data_g2p_dgl$Drug_Gene_Lin)) - nrow(ccle_signif_g2p_lineage)` DGLs were not analyzed due to lack of mutation annotations in *UGT1A1* in "cancer" lineages), but CTRP ($n =$ `r nrow(ctrp_signif_g2p_lineage)`) and GDSC ($n =$ `r nrow(gdsc_signif_g2p_lineage)`) identified `r nrow(filter(ctrp_signif_g2p_lineage, !is.na(p.signif)))` and `r nrow(filter(gdsc_signif_g2p_lineage, !is.na(p.signif)))`, respectively, in skin cancer, lung cancer, and cancer.
+After Benjamini-Hochberg FDR correction, none of the datasets yielded significant DGL interactions.
 
+**BAD ANALYSIS, keep for reference:** These significant associations did not hold after Bonferroni correction in CTRP ($n = 48$, $\alpha_{adjusted} = 0.001$) or GDSC ($n = 39$, $\alpha_{adjusted} = 0.001$).
 When using gene expression as the genomic feature, three CCLE DGLs had significant correlations at an adjusted $\alpha =  0.006$ ($n = 9$).
 Two of these three DGLs were also significantly correlated with copy number ($n = 9$, $\alpha_{adjusted} = 0.006$).
-
 In CTRP, AUC of 19 DGLs significantly correlated with gene expression, 12 of which were significant after correction ($n = 61$, $\alpha_{adjusted} = 0.0008$).
 Copy number correlations were significant for 12 DGLs, with three DGLs significant post-correction ($n = 61$, $\alpha_{adjusted} = 0.0008$).
-
 AUC of 16 DGLs in GDSC significantly correlated with gene expression.
@@
 Fewer DGLs were significant when correlating AUC with copy number with 6 significant at an $\alpha$ of 0.05 and 1 significant at an adjusted $\alpha$ of 0.0009 ($n = 53$).
-
-Interestingly, when we test the effect of mutation status on drug response for the DGLs derived from all pairwise combinations of G2P drugs and genes… (*Figure ##1*).
 

### 2019-01-08 manuscript.tex
update rmds

@@
 
+\textbf{Cut this analysis since we are comparing distributions of
+p-values?}
+
 We compared the distribution of level-A G2P associations (\emph{Figure
@@
 groupings. This custom lineage grouping was included in our harmonized
-cancer cell line database (see METHODS).
+cancer cell line database (see Methods).
 
@@
 
-At an \(\alpha = 0.05\), no DGLs were identified in the CCLE screen when
-using mutation status as a correlate (n = 7), but CTRP and GDSC
-identified six and five, respectively, in skin cancer, lung cancer, and
-cancer. These significant associations did not hold after Bonferroni
-correction in CTRP (\(n = 48\), \(\alpha_{adjusted} = 0.001\)) or GDSC
-(\(n = 39\), \(\alpha_{adjusted} = 0.001\)).
-
-When using gene expression as the genomic feature, three CCLE DGLs had
-significant correlations at an adjusted \(\alpha = 0.006\) (\(n = 9\)).
-Two of these three DGLs were also significantly correlated with copy
-number (\(n = 9\), \(\alpha_{adjusted} = 0.006\)).
-
-In CTRP, AUC of 19 DGLs significantly correlated with gene expression,
-12 of which were significant after correction (\(n = 61\),
-\(\alpha_{adjusted} = 0.0008\)). Copy number correlations were
-significant for 12 DGLs, with three DGLs significant post-correction
-(\(n = 61\), \(\alpha_{adjusted} = 0.0008\)).
-
-AUC of 16 DGLs in GDSC significantly correlated with gene expression. At
-an adjusted \(\alpha\) of 0.0009 (\(n = 53\)) eight of them were
+Prior to correction for an FDR of 5\%, no DGLs were identified in the
+CCLE screen when using mutation status as a correlate (\(n =\) 7, 2 DGLs
+were not analyzed due to lack of mutation annotations in \emph{UGT1A1}
+in \enquote{cancer} lineages), but CTRP (\(n =\) 48) and GDSC (\(n =\)
+39) identified 6 and 5, respectively, in skin cancer, lung cancer, and
+cancer.
+
+\textbf{BAD ANALYSIS, keep for reference:} These significant
+associations did not hold after Bonferroni correction in CTRP
+(\(n = 48\), \(\alpha_{adjusted} = 0.001\)) or GDSC (\(n = 39\),
+\(\alpha_{adjusted} = 0.001\)). When using gene expression as the
+genomic feature, three CCLE DGLs had significant correlations at an
+adjusted \(\alpha = 0.006\) (\(n = 9\)). Two of these three DGLs were
+also significantly correlated with copy number (\(n = 9\),
+\(\alpha_{adjusted} = 0.006\)). In CTRP, AUC of 19 DGLs significantly
+correlated with gene expression, 12 of which were significant after
+correction (\(n = 61\), \(\alpha_{adjusted} = 0.0008\)). Copy number
+correlations were significant for 12 DGLs, with three DGLs significant
+post-correction (\(n = 61\), \(\alpha_{adjusted} = 0.0008\)). AUC of 16
+DGLs in GDSC significantly correlated with gene expression. At an
+adjusted \(\alpha\) of 0.0009 (\(n = 53\)) eight of them were
 significant. Fewer DGLs were significant when correlating AUC with copy
@@
 an adjusted \(\alpha\) of 0.0009 (\(n = 53\)).
-
-Interestingly, when we test the effect of mutation status on drug
-response for the DGLs derived from all pairwise combinations of G2P
-drugs and genes\ldots{} (\emph{Figure \#\#1}).
 

### 2019-01-08 manuscript_analysis.Rmd

@@
 ```{r}
-adj_signif <- function(df) {
-  # Takes df from compare_means and creates a signif code column for adjusted p-vals
+adj_signif <- function(df, alpha) {
+  # Takes df from compare_means and creates a signif code column for FDR-adjusted p-vals for provided alpha
+  a <- alpha
+  i <- seq(along.with = df$p)
+  m <- nrow(df)
+  x <- sort(df$p) < i / m * a
+  if(length(unique(x)) == 2) {
+    k <- max(which(sort(df$p) < i/ m * a))
+    cutoff <- sort(df$p)[k]
+  }
+  else {
+    k <- NA
+    cutoff <- NA
+  }
+  df$p.signif.adj <- ifelse(df$p.adj <= cutoff, "*", NA)
   df$p.signif <- ifelse(df$p.signif == "ns", NA, df$p.signif)
-  df$p.signif.adj <- ifelse(df$p.adj <= 0.0001, "****",
-                     ifelse(df$p.adj <= 0.001, "***",
-                     ifelse(df$p.adj <= 0.01, "**",
-                     ifelse(df$p.adj <= 0.05, "*", NA))))
   df$p.short <- formatC(df$p, format = "g", digits =  2)
   df$p.adj.short <- formatC(df$p.adj, format = "g", digits =  2)
-
+  df$k <- k
+  df$FDR_cutoff <- cutoff
   return(df)
@@
 
+```{r}
+test <- adj_signif(ccle_signif_grid_lineage, alpha = 0.05)
+length(unique(test))
+```
+
 ## Wilcoxon tests by drug
@@
 ```{r}
-WilcoxonByDrug <- function(drug, dataset, data_name, grouping_var) {
-  if(grouping_var == "lineage") {
-    grouper <- c("Hugo_Symbol", "group_general_lineage_name")
-  }
-  else if(grouping_var == "gene") {
-    grouper <- "Hugo_Symbol"
-  }
-  use_data <- filter(dataset, Drug == drug)
-  sig <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = grouper, data = use_data, method = "wilcox.test", p.adjust.method = "BH")
-  sig <- adj_signif(sig)
-  sig <- sig[order(sig$p),]
-  sig$Drug <- drug
-  sig$Dataset <- toupper(data_name)
-  return(sig)
-}
-
 # WilcoxonByDrugAllGenes <- function(melt_file, grid_file, data_name) {
@@
 crispr_signif_g2p_gene <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol"), data = crispr_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
-crispr_signif_g2p_gene <- adj_signif(crispr_signif_g2p_gene)
+crispr_signif_g2p_gene <- adj_signif(crispr_signif_g2p_gene, alpha = 0.05)
 crispr_signif_g2p_gene <- crispr_signif_g2p_gene[order(crispr_signif_g2p_gene$p),]
@@
 crispr_signif_g2p_gene <- rbind(crispr_signif_g2p_gene, c("G6PD", rep(NA, 11)))
-crispr_signif_g2p_gene_kable <- knitr::kable(crispr_signif_g2p_gene[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results for Level A point mutations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+crispr_signif_g2p_gene_kable <- knitr::kable(crispr_signif_g2p_gene[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj", "FDR_cutoff")], caption = "Wilcoxon test results for Level A point mutations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 crispr_signif_g2p_lineage <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "group_general_lineage_name"), data = crispr_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
-crispr_signif_g2p_lineage <- adj_signif(crispr_signif_g2p_lineage)
+crispr_signif_g2p_lineage <- adj_signif(crispr_signif_g2p_lineage, alpha = 0.05)
 crispr_signif_g2p_lineage <- crispr_signif_g2p_lineage[order(crispr_signif_g2p_lineage$p),]
@@
 crispr_signif_g2p_lineage <- readRDS("./data_munging/rds/crispr_signif_g2p_lineage.rds")
-crispr_signif_g2p_lineage_kable <- knitr::kable(filter(crispr_signif_g2p_lineage, p < 0.1)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant vs wildtype cell lines by lineage, p < 0.1 (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+crispr_signif_g2p_lineage_kable <- knitr::kable(filter(crispr_signif_g2p_lineage, p < 0.1)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj", "FDR_cutoff")], caption = "Wilcoxon test results comparing non-silent mutant vs wildtype cell lines by lineage, p < 0.1 (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 ccle_signif_g2p <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene", data = ccle_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
-ccle_signif_g2p <- adj_signif(ccle_signif_g2p)
+ccle_signif_g2p <- adj_signif(ccle_signif_g2p, alpha = 0.05)
 ccle_signif_g2p <- ccle_signif_g2p[order(ccle_signif_g2p$p),]
@@
 ccle_signif_g2p_grid <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = c("Drug_Gene"), data = ccle_data_g2p_grid, method = "wilcox.test", p.adjust.method = "BH")
-ccle_signif_g2p_grid <- adj_signif(ccle_signif_g2p_grid)
+ccle_signif_g2p_grid <- adj_signif(ccle_signif_g2p_grid, alpha = 0.05)
 ccle_signif_g2p_grid <- ccle_signif_g2p_grid[order(ccle_signif_g2p_grid$p),]
@@
 ccle_signif_g2p <- readRDS("./data_munging/rds/ccle_signif_g2p_gene.rds")
-ccle_signif_g2p_kable <- knitr::kable(ccle_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+ccle_signif_g2p_kable <- knitr::kable(ccle_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj", "FDR_cutoff")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 
 ccle_signif_g2p_grid <- readRDS("./data_munging/rds/ccle_signif_g2p_grid.rds")
-ccle_signif_g2p_grid_kable <- knitr::kable(ccle_signif_g2p_grid[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+ccle_signif_g2p_grid_kable <- knitr::kable(ccle_signif_g2p_grid[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj", "FDR_cutoff")], caption = "CCLE: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 ```{r, eval=FALSE}
-ccle_signif_grid_lineage <- lapply(unique(ccle_data_g2p_grid$Drug), WilcoxonByDrug, dataset = ccle_data_g2p_grid, data_name = "ccle", grouping_var = "lineage")
-names(ccle_signif_grid_lineage) <- unique(ccle_signif_grid_lineage$Drug)
-ccle_signif_grid_lineage <- rbindlist(ccle_signif_grid_lineage, use.names = TRUE)
+ccle_signif_grid_lineage <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene_Lin", data = ccle_data_g2p_grid, method = "wilcox.test", p.adjust.method = "BH")
+ccle_signif_grid_lineage <- adj_signif(ccle_signif_grid_lineage, alpha = 0.05)
 ccle_signif_grid_lineage <- ccle_signif_grid_lineage[order(ccle_signif_grid_lineage$p),]
@@
 ccle_signif_g2p_lineage <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene_Lin", data = ccle_data_g2p_dgl, method = "wilcox.test", p.adjust.method = "BH")
-ccle_signif_g2p_lineage <- adj_signif(ccle_signif_g2p_lineage)
+ccle_signif_g2p_lineage <- adj_signif(ccle_signif_g2p_lineage, alpha = 0.05)
 ccle_signif_g2p_lineage <- ccle_signif_g2p_lineage[order(ccle_signif_g2p_lineage$p),]
@@
 
-ccle_signif_g2p_lineage_kable <- knitr::kable(ccle_signif_g2p_lineage[, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-
-ccle_signif_grid_lineage_kable <- knitr::kable(ccle_signif_grid_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+ccle_signif_g2p_lineage_kable <- knitr::kable(ccle_signif_g2p_lineage[, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj", "FDR_cutoff")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+
+ccle_signif_grid_lineage_kable <- knitr::kable(ccle_signif_grid_lineage[1:500, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj", "FDR_cutoff")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 ctrp_signif_g2p <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene", data = ctrp_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
-ctrp_signif_g2p <- adj_signif(ctrp_signif_g2p)
+ctrp_signif_g2p <- adj_signif(ctrp_signif_g2p, alpha = 0.05)
 ctrp_signif_g2p <- ctrp_signif_g2p[order(ctrp_signif_g2p$p),]
@@
 ctrp_signif_g2p_grid <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene", data = ctrp_data_g2p_grid, method = "wilcox.test", p.adjust.method = "BH")
-ctrp_signif_g2p_grid <- adj_signif(ctrp_signif_g2p_grid)
+ctrp_signif_g2p_grid <- adj_signif(ctrp_signif_g2p_grid, alpha = 0.05)
 ctrp_signif_g2p_grid <- ctrp_signif_g2p_grid[order(ctrp_signif_g2p_grid$p),]
@@
 ctrp_signif_g2p <- readRDS("./data_munging/rds/ctrp_signif_g2p_gene.rds")
-ctrp_signif_g2p_kable <- knitr::kable(ctrp_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+ctrp_signif_g2p_kable <- knitr::kable(ctrp_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj", "FDR_cutoff")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 
 ctrp_signif_g2p_grid <- readRDS("./data_munging/rds/ctrp_signif_g2p_grid.rds")
-ctrp_signif_g2p_grid_kable <- knitr::kable(ctrp_signif_g2p_grid[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+ctrp_signif_g2p_grid_kable <- knitr::kable(ctrp_signif_g2p_grid[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj", "FDR_cutoff")], caption = "CTRP: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 ```{r, eval=FALSE}
-ctrp_signif_grid_lineage <- lapply(unique(ctrp_data_g2p_grid$Drug), WilcoxonByDrug, dataset = ctrp_data_g2p_grid, data_name = "ctrp", grouping_var = "lineage")
-names(ctrp_signif_grid_lineage) <- unique(ctrp_signif_grid_lineage$Drug)
-ctrp_signif_grid_lineage <- rbindlist(ctrp_signif_grid_lineage, use.names = TRUE)
+ctrp_signif_grid_lineage <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene_Lin", data = ctrp_data_g2p_grid, method = "wilcox.test", p.adjust.method = "BH")
+ctrp_signif_grid_lineage <- adj_signif(ctrp_signif_grid_lineage, alpha = 0.05)
 ctrp_signif_grid_lineage <- ctrp_signif_grid_lineage[order(ctrp_signif_grid_lineage$p),]
@@
 ctrp_signif_g2p_lineage <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene_Lin", data = ctrp_data_g2p_dgl, method = "wilcox.test", p.adjust.method = "BH")
-ctrp_signif_g2p_lineage <- adj_signif(ctrp_signif_g2p_lineage)
+ctrp_signif_g2p_lineage <- adj_signif(ctrp_signif_g2p_lineage, alpha = 0.05)
 ctrp_signif_g2p_lineage <- ctrp_signif_g2p_lineage[order(ctrp_signif_g2p_lineage$p),]
@@
 
-ctrp_signif_g2p_lineage_kable <- knitr::kable(ctrp_signif_g2p_lineage[, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-
-ctrp_signif_grid_lineage_kable <- knitr::kable(ctrp_signif_grid_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+ctrp_signif_g2p_lineage_kable <- knitr::kable(ctrp_signif_g2p_lineage[, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj", "FDR_cutoff")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+
+ctrp_signif_grid_lineage_kable <- knitr::kable(ctrp_signif_grid_lineage[1:500, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj", "FDR_cutoff")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 gdsc_signif_g2p <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene", data = gdsc_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
-gdsc_signif_g2p <- adj_signif(gdsc_signif_g2p)
+gdsc_signif_g2p <- adj_signif(gdsc_signif_g2p, alpha = 0.05)
 gdsc_signif_g2p <- gdsc_signif_g2p[order(gdsc_signif_g2p$p),]
@@
 gdsc_signif_g2p_grid <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene", data = gdsc_data_g2p_grid, method = "wilcox.test", p.adjust.method = "BH")
-gdsc_signif_g2p_grid <- adj_signif(gdsc_signif_g2p_grid)
+gdsc_signif_g2p_grid <- adj_signif(gdsc_signif_g2p_grid, alpha = 0.05)
 gdsc_signif_g2p_grid <- gdsc_signif_g2p_grid[order(gdsc_signif_g2p_grid$p),]
@@
 gdsc_signif_g2p_grid <- readRDS("./data_munging/rds/gdsc_signif_g2p_grid.rds")
-gdsc_signif_g2p_grid_kable <- knitr::kable(gdsc_signif_g2p_grid[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+gdsc_signif_g2p_grid_kable <- knitr::kable(gdsc_signif_g2p_grid[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj", "FDR_cutoff")], caption = "GDSC: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 ```{r, eval=FALSE}
-gdsc_signif_grid_lineage <- lapply(unique(gdsc_data_g2p_grid$Drug), WilcoxonByDrug, dataset = gdsc_data_g2p_grid, data_name = "gdsc", grouping_var = "lineage")
-names(gdsc_signif_grid_lineage) <- unique(gdsc_signif_grid_lineage$Drug)
-gdsc_signif_grid_lineage <- rbindlist(gdsc_signif_grid_lineage, use.names = TRUE)
+gdsc_signif_grid_lineage <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene_Lin", data = gdsc_data_g2p_grid, method = "wilcox.test", p.adjust.method = "BH")
+gdsc_signif_grid_lineage <- adj_signif(gdsc_signif_grid_lineage, alpha = 0.05)
 gdsc_signif_grid_lineage <- gdsc_signif_grid_lineage[order(gdsc_signif_grid_lineage$p),]
@@
 gdsc_signif_g2p_lineage <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene_Lin", data = gdsc_data_g2p_dgl, method = "wilcox.test", p.adjust.method = "BH")
-gdsc_signif_g2p_lineage <- adj_signif(gdsc_signif_g2p_lineage)
+gdsc_signif_g2p_lineage <- adj_signif(gdsc_signif_g2p_lineage, alpha = 0.05)
 gdsc_signif_g2p_lineage <- gdsc_signif_g2p_lineage[order(gdsc_signif_g2p_lineage$p),]
@@
 
-gdsc_signif_g2p_lineage_kable <- knitr::kable(gdsc_signif_g2p_lineage[, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-
-gdsc_signif_grid_lineage_kable <- knitr::kable(gdsc_signif_grid_lineage[1:500, c("Hugo_Symbol", "Drug", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+gdsc_signif_g2p_lineage_kable <- knitr::kable(gdsc_signif_g2p_lineage[, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj", "FDR_cutoff")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+
+gdsc_signif_grid_lineage_kable <- knitr::kable(gdsc_signif_grid_lineage[1:500, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj", "FDR_cutoff")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```

### 2019-01-09 manuscript_analysis.Rmd
p.adj and rewriting, add code to papaja doc

@@
 crispr_signif_g2p_gene <- rbind(crispr_signif_g2p_gene, c("G6PD", rep(NA, 11)))
-crispr_signif_g2p_gene_kable <- knitr::kable(crispr_signif_g2p_gene[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj", "FDR_cutoff")], caption = "Wilcoxon test results for Level A point mutations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+crispr_signif_g2p_gene_kable <- knitr::kable(crispr_signif_g2p_gene[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj", "k", "FDR_cutoff")], caption = "Wilcoxon test results for Level A point mutations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
 ccle_signif_g2p_grid_kable <- knitr::kable(ccle_signif_g2p_grid[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj", "FDR_cutoff")], caption = "CCLE: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+```
+
+```{r}
+test <- p.adjust(ccle_signif_g2p$p, method = "BH")
 ```
@@
 ccle_cor_res$Dataset <- "CCLE"
-ccle_pearson_ttest_GE <- t.test(ccle_cor_res$Pearson_Corr_GE ~ ccle_cor_res$InG2P)
-ccle_pearson_ttest_res_GE <- paste0("t(", round(ccle_pearson_ttest_GE$parameter, 0), ") = ", round(ccle_pearson_ttest_GE$statistic, 2), ", p = ", round(ccle_pearson_ttest_GE$p.value, 2))
-ccle_pearson_ttest_CN <- t.test(ccle_cor_res$Pearson_Corr_CN ~ ccle_cor_res$InG2P)
-ccle_pearson_ttest_res_CN <- paste0("t(", round(ccle_pearson_ttest_CN$parameter, 0), ") = ", round(ccle_pearson_ttest_CN$statistic, 2), ", p = ", round(ccle_pearson_ttest_CN$p.value, 2))
-ccle_spearman_ttest_GE <- t.test(ccle_cor_res$Spearman_Corr_GE ~ ccle_cor_res$InG2P)
-ccle_spearman_ttest_res_GE <- paste0("t(", round(ccle_spearman_ttest_GE$parameter, 0), ") = ", round(ccle_spearman_ttest_GE$statistic, 2), ", p = ", round(ccle_spearman_ttest_GE$p.value, 2))
-ccle_spearman_ttest_CN <- t.test(ccle_cor_res$Spearman_Corr_CN ~ ccle_cor_res$InG2P)
-ccle_spearman_ttest_res_CN <- paste0("t(", round(ccle_spearman_ttest_CN$parameter, 0), ") = ", round(ccle_spearman_ttest_CN$statistic, 2), ", p = ", formatC(ccle_spearman_ttest_CN$p.value, 2, format = "f"))
+# ccle_pearson_ttest_GE <- t.test(ccle_cor_res$Pearson_Corr_GE ~ ccle_cor_res$InG2P)
+# ccle_pearson_ttest_res_GE <- paste0("t(", round(ccle_pearson_ttest_GE$parameter, 0), ") = ", round(ccle_pearson_ttest_GE$statistic, 2), ", p = ", round(ccle_pearson_ttest_GE$p.value, 2))
+# ccle_pearson_ttest_CN <- t.test(ccle_cor_res$Pearson_Corr_CN ~ ccle_cor_res$InG2P)
+# ccle_pearson_ttest_res_CN <- paste0("t(", round(ccle_pearson_ttest_CN$parameter, 0), ") = ", round(ccle_pearson_ttest_CN$statistic, 2), ", p = ", round(ccle_pearson_ttest_CN$p.value, 2))
+# ccle_spearman_ttest_GE <- t.test(ccle_cor_res$Spearman_Corr_GE ~ ccle_cor_res$InG2P)
+# ccle_spearman_ttest_res_GE <- paste0("t(", round(ccle_spearman_ttest_GE$parameter, 0), ") = ", round(ccle_spearman_ttest_GE$statistic, 2), ", p = ", round(ccle_spearman_ttest_GE$p.value, 2))
+# ccle_spearman_ttest_CN <- t.test(ccle_cor_res$Spearman_Corr_CN ~ ccle_cor_res$InG2P)
+# ccle_spearman_ttest_res_CN <- paste0("t(", round(ccle_spearman_ttest_CN$parameter, 0), ") = ", round(ccle_spearman_ttest_CN$statistic, 2), ", p = ", formatC(ccle_spearman_ttest_CN$p.value, 2, format = "f"))
 
@@
 ctrp_cor_res$Dataset <- "CTRP"
-ctrp_pearson_ttest_GE <- t.test(ctrp_cor_res$Pearson_Corr_GE ~ ctrp_cor_res$InG2P)
-ctrp_pearson_ttest_res_GE <- paste0("t(", round(ctrp_pearson_ttest_GE$parameter, 0), ") = ", round(ctrp_pearson_ttest_GE$statistic, 2), ", p ", ifelse(round(ctrp_pearson_ttest_GE$p.value, 3) == 0, "< 0.001", paste0("= ", round(ctrp_pearson_ttest_GE$p.value, 3))))
-ctrp_pearson_ttest_CN <- t.test(ctrp_cor_res$Pearson_Corr_CN ~ ctrp_cor_res$InG2P)
-ctrp_pearson_ttest_res_CN <- paste0("t(", round(ctrp_pearson_ttest_CN$parameter, 0), ") = ", round(ctrp_pearson_ttest_CN$statistic, 2), ", p = ", round(ctrp_pearson_ttest_CN$p.value, 3))
-ctrp_spearman_ttest_GE <- t.test(ctrp_cor_res$Spearman_Corr_GE ~ ctrp_cor_res$InG2P)
-ctrp_spearman_ttest_res_GE <- paste0("t(", round(ctrp_spearman_ttest_GE$parameter, 0), ") = ", round(ctrp_spearman_ttest_GE$statistic, 2), ", p = ", round(ctrp_spearman_ttest_GE$p.value, 2))
-ctrp_spearman_ttest_CN <- t.test(ctrp_cor_res$Spearman_Corr_CN ~ ctrp_cor_res$InG2P)
-ctrp_spearman_ttest_res_CN <- paste0("t(", round(ctrp_spearman_ttest_CN$parameter, 0), ") = ", round(ctrp_spearman_ttest_CN$statistic, 2), ", p = ", round(ctrp_spearman_ttest_CN$p.value, 2))
+# ctrp_pearson_ttest_GE <- t.test(ctrp_cor_res$Pearson_Corr_GE ~ ctrp_cor_res$InG2P)
+# ctrp_pearson_ttest_res_GE <- paste0("t(", round(ctrp_pearson_ttest_GE$parameter, 0), ") = ", round(ctrp_pearson_ttest_GE$statistic, 2), ", p ", ifelse(round(ctrp_pearson_ttest_GE$p.value, 3) == 0, "< 0.001", paste0("= ", round(ctrp_pearson_ttest_GE$p.value, 3))))
+# ctrp_pearson_ttest_CN <- t.test(ctrp_cor_res$Pearson_Corr_CN ~ ctrp_cor_res$InG2P)
+# ctrp_pearson_ttest_res_CN <- paste0("t(", round(ctrp_pearson_ttest_CN$parameter, 0), ") = ", round(ctrp_pearson_ttest_CN$statistic, 2), ", p = ", round(ctrp_pearson_ttest_CN$p.value, 3))
+# ctrp_spearman_ttest_GE <- t.test(ctrp_cor_res$Spearman_Corr_GE ~ ctrp_cor_res$InG2P)
+# ctrp_spearman_ttest_res_GE <- paste0("t(", round(ctrp_spearman_ttest_GE$parameter, 0), ") = ", round(ctrp_spearman_ttest_GE$statistic, 2), ", p = ", round(ctrp_spearman_ttest_GE$p.value, 2))
+# ctrp_spearman_ttest_CN <- t.test(ctrp_cor_res$Spearman_Corr_CN ~ ctrp_cor_res$InG2P)
+# ctrp_spearman_ttest_res_CN <- paste0("t(", round(ctrp_spearman_ttest_CN$parameter, 0), ") = ", round(ctrp_spearman_ttest_CN$statistic, 2), ", p = ", round(ctrp_spearman_ttest_CN$p.value, 2))
 
@@
 gdsc_cor_res$Dataset <- "GDSC"
-gdsc_pearson_ttest_GE <- t.test(gdsc_cor_res$Pearson_Corr_GE ~ gdsc_cor_res$InG2P)
-gdsc_pearson_ttest_res_GE <- paste0("t(", round(gdsc_pearson_ttest_GE$parameter, 0), ") = ", round(gdsc_pearson_ttest_GE$statistic, 2), ", p = ", round(gdsc_pearson_ttest_GE$p.value, 3))
-gdsc_pearson_ttest_CN <- t.test(gdsc_cor_res$Pearson_Corr_CN ~ gdsc_cor_res$InG2P)
-gdsc_pearson_ttest_res_CN <- paste0("t(", round(gdsc_pearson_ttest_CN$parameter, 0), ") = ", round(gdsc_pearson_ttest_CN$statistic, 2), ", p = ", round(gdsc_pearson_ttest_CN$p.value, 3))
-gdsc_spearman_ttest_GE <- t.test(gdsc_cor_res$Spearman_Corr_GE ~ gdsc_cor_res$InG2P)
-gdsc_spearman_ttest_res_GE <- paste0("t(", round(gdsc_spearman_ttest_GE$parameter, 0), ") = ", round(gdsc_spearman_ttest_GE$statistic, 2), ", p = ", round(gdsc_spearman_ttest_GE$p.value, 2))
-gdsc_spearman_ttest_CN <- t.test(gdsc_cor_res$Spearman_Corr_CN ~ gdsc_cor_res$InG2P)
-gdsc_spearman_ttest_res_CN <- paste0("t(", round(gdsc_spearman_ttest_CN$parameter, 0), ") = ", round(gdsc_spearman_ttest_CN$statistic, 2), ", p = ", round(gdsc_spearman_ttest_CN$p.value, 2))
+# gdsc_pearson_ttest_GE <- t.test(gdsc_cor_res$Pearson_Corr_GE ~ gdsc_cor_res$InG2P)
+# gdsc_pearson_ttest_res_GE <- paste0("t(", round(gdsc_pearson_ttest_GE$parameter, 0), ") = ", round(gdsc_pearson_ttest_GE$statistic, 2), ", p = ", round(gdsc_pearson_ttest_GE$p.value, 3))
+# gdsc_pearson_ttest_CN <- t.test(gdsc_cor_res$Pearson_Corr_CN ~ gdsc_cor_res$InG2P)
+# gdsc_pearson_ttest_res_CN <- paste0("t(", round(gdsc_pearson_ttest_CN$parameter, 0), ") = ", round(gdsc_pearson_ttest_CN$statistic, 2), ", p = ", round(gdsc_pearson_ttest_CN$p.value, 3))
+# gdsc_spearman_ttest_GE <- t.test(gdsc_cor_res$Spearman_Corr_GE ~ gdsc_cor_res$InG2P)
+# gdsc_spearman_ttest_res_GE <- paste0("t(", round(gdsc_spearman_ttest_GE$parameter, 0), ") = ", round(gdsc_spearman_ttest_GE$statistic, 2), ", p = ", round(gdsc_spearman_ttest_GE$p.value, 2))
+# gdsc_spearman_ttest_CN <- t.test(gdsc_cor_res$Spearman_Corr_CN ~ gdsc_cor_res$InG2P)
+# gdsc_spearman_ttest_res_CN <- paste0("t(", round(gdsc_spearman_ttest_CN$parameter, 0), ") = ", round(gdsc_spearman_ttest_CN$statistic, 2), ", p = ", round(gdsc_spearman_ttest_CN$p.value, 2))
 
@@
 g2p_cor$Spearman_CN_Sign <- ifelse(sign(g2p_cor$Spearman_Corr_CN) == 1, "+", ifelse(sign(g2p_cor$Spearman_Corr_CN) == -1, "-", "0"))
-g2p_cor_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"),
-                               Pearson_Test_Results_GE = c(ccle_pearson_ttest_res_GE, ctrp_pearson_ttest_res_GE, gdsc_pearson_ttest_res_GE),
-                               Pearson_Test_Results_CN = c(ccle_pearson_ttest_res_CN, ctrp_pearson_ttest_res_CN, gdsc_pearson_ttest_res_CN),
-                               Spearman_Test_Results_GE = c(ccle_spearman_ttest_res_GE, ctrp_spearman_ttest_res_GE, gdsc_spearman_ttest_res_GE),
-                               Spearman_Test_Results_CN = c(ccle_spearman_ttest_res_CN, ctrp_spearman_ttest_res_CN, gdsc_spearman_ttest_res_CN))
+# g2p_cor_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"),
+#                                Pearson_Test_Results_GE = c(ccle_pearson_ttest_res_GE, ctrp_pearson_ttest_res_GE, gdsc_pearson_ttest_res_GE),
+#                                Pearson_Test_Results_CN = c(ccle_pearson_ttest_res_CN, ctrp_pearson_ttest_res_CN, gdsc_pearson_ttest_res_CN),
+#                                Spearman_Test_Results_GE = c(ccle_spearman_ttest_res_GE, ctrp_spearman_ttest_res_GE, gdsc_spearman_ttest_res_GE),
+#                                Spearman_Test_Results_CN = c(ccle_spearman_ttest_res_CN, ctrp_spearman_ttest_res_CN, gdsc_spearman_ttest_res_CN))
 ```
@@
 
-ccle_dgl_summ <- ccle_signif_grid_lineage
+ccle_dgl_summ <- ccle_signif_grid_lineage %>% separate(Drug_Gene_Lin, c("Drug", "Hugo_Symbol", "group_general_lineage_name"), "_")
 ccle_dgl_summ$Drug_Gene <- paste0(ccle_dgl_summ$Drug, "_", ccle_dgl_summ$Hugo_Symbol)
@@
 
-ctrp_dgl_summ <- ctrp_signif_grid_lineage
+ctrp_dgl_summ <- ctrp_signif_grid_lineage %>% separate(Drug_Gene_Lin, c("Drug", "Hugo_Symbol", "group_general_lineage_name"), "_")
 ctrp_dgl_summ$Drug_Gene <- paste0(ctrp_dgl_summ$Drug, "_", ctrp_dgl_summ$Hugo_Symbol)
@@
 
-gdsc_dgl_summ <- gdsc_signif_grid_lineage
+gdsc_dgl_summ <- gdsc_signif_grid_lineage %>% separate(Drug_Gene_Lin, c("Drug", "Hugo_Symbol", "group_general_lineage_name"), "_")
 gdsc_dgl_summ$Drug_Gene <- paste0(gdsc_dgl_summ$Drug, "_", gdsc_dgl_summ$Hugo_Symbol)

### 2019-01-09 manuscript.Rmd

@@
 floatsintext      : no
+figuresintext     : yes
 figurelist        : no
@@
 ## Comparison of G2P drug-gene associations and CCLE, CTRP, and GDSC
+
+```{r functions, echo=FALSE, include=FALSE}
+e2exp_converter <- function(string) {
+  e <- formatC(as.numeric(string), format = "e", digits = 0)
+  exp <- sub("(\\d)e-0(\\d)", "$p_k < \\1^{-\\2}$", e, perl = TRUE)
+  return(exp)
+}
+```
 
@@
 
+# Wilcoxon test results
+ccle_signif_g2p <- readRDS("./data_munging/rds/ccle_signif_g2p_gene.rds")
+ccle_signif_g2p_exp <- e2exp_converter(ccle_signif_g2p$FDR_cutoff[1])
+ccle_signif_g2p_grid <- readRDS("./data_munging/rds/ccle_signif_g2p_grid.rds")
+ccle_signif_g2p_grid_exp <- e2exp_converter(ccle_signif_g2p_grid$FDR_cutoff[1])
+ccle_signif_g2p_lineage <- readRDS("./data_munging/rds/ccle_signif_g2p_lineage.rds")
+ccle_signif_g2p_lineage_exp <- e2exp_converter(ccle_signif_g2p_lineage$FDR_cutoff[1])
+ccle_signif_grid_lineage <- readRDS("./data_munging/rds/ccle_signif_grid_lineage.rds")
+ccle_signif_grid_lineage_exp <- e2exp_converter(ccle_signif_grid_lineage$FDR_cutoff[1])
+
+ctrp_signif_g2p <- readRDS("./data_munging/rds/ctrp_signif_g2p_gene.rds")
+ctrp_signif_g2p_exp <- e2exp_converter(ctrp_signif_g2p$FDR_cutoff[1])
+ctrp_signif_g2p_grid <- readRDS("./data_munging/rds/ctrp_signif_g2p_grid.rds")
+ctrp_signif_g2p_grid_exp <- e2exp_converter(ctrp_signif_g2p_grid$FDR_cutoff[1])
+ctrp_signif_g2p_lineage <- readRDS("./data_munging/rds/ctrp_signif_g2p_lineage.rds")
+ctrp_signif_g2p_lineage_exp <- e2exp_converter(ctrp_signif_g2p_lineage$FDR_cutoff[1])
+ctrp_signif_grid_lineage <- readRDS("./data_munging/rds/ctrp_signif_grid_lineage.rds")
+ctrp_signif_grid_lineage_exp <- e2exp_converter(ctrp_signif_grid_lineage$FDR_cutoff[1])
+
+gdsc_signif_g2p <- readRDS("./data_munging/rds/gdsc_signif_g2p_gene.rds")
+gdsc_signif_g2p_exp <- e2exp_converter(gdsc_signif_g2p$FDR_cutoff[1])
+gdsc_signif_g2p_grid <- readRDS("./data_munging/rds/gdsc_signif_g2p_grid.rds")
+gdsc_signif_g2p_grid_exp <- e2exp_converter(gdsc_signif_g2p_grid$FDR_cutoff[1])
+gdsc_signif_g2p_lineage <- readRDS("./data_munging/rds/gdsc_signif_g2p_lineage.rds")
+gdsc_signif_g2p_lineage_exp <- e2exp_converter(gdsc_signif_g2p_lineage$FDR_cutoff[1])
+gdsc_signif_grid_lineage <- readRDS("./data_munging/rds/gdsc_signif_grid_lineage.rds")
+gdsc_signif_grid_lineage_exp <- e2exp_converter(gdsc_signif_grid_lineage$FDR_cutoff[1])
+
+# CCLE: GE/CN correlations
+ccle_cor_res <- ccle_data_g2p_grid %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs", exact = FALSE)$estimate, Pearson_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs", exact = FALSE)$p.value, Pearson_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs", exact = FALSE)$estimate, Pearson_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs", exact = FALSE)$p.value, Spearman_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs", exact = FALSE)$estimate, Spearman_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs", exact = FALSE)$p.value, Spearman_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs", exact = FALSE)$estimate, Spearman_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs", exact = FALSE)$p.value)
+ccle_cor_res <- merge(g2p_druggene_tally, ccle_cor_res, by = "Drug_Gene", all.y = TRUE)
+ccle_cor_res$n <- ifelse(is.na(ccle_cor_res$n), 0, ccle_cor_res$n)
+ccle_cor_res$InG2P <- ifelse(ccle_cor_res$n != 0, "Yes", "No")
+ccle_cor_res$Dataset <- "CCLE"
+
+# CTRP: GE/CN correlations
+ctrp_cor_res <- ctrp_data_g2p_grid %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs", exact = FALSE)$estimate, Pearson_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs", exact = FALSE)$p.value, Pearson_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs", exact = FALSE)$estimate, Pearson_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs", exact = FALSE)$p.value, Spearman_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs", exact = FALSE)$estimate, Spearman_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs", exact = FALSE)$p.value, Spearman_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs", exact = FALSE)$estimate, Spearman_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs", exact = FALSE)$p.value)
+ctrp_cor_res <- merge(g2p_druggene_tally, ctrp_cor_res, by = "Drug_Gene", all.y = TRUE)
+ctrp_cor_res$n <- ifelse(is.na(ctrp_cor_res$n), 0, ctrp_cor_res$n)
+ctrp_cor_res$InG2P <- ifelse(ctrp_cor_res$n != 0, "Yes", "No")
+ctrp_cor_res$Dataset <- "CTRP"
+
+# GDSC: GE/CN correlations
+gdsc_cor_res <- gdsc_data_g2p_grid %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs", exact = FALSE)$estimate, Pearson_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs", exact = FALSE)$p.value, Pearson_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs", exact = FALSE)$estimate, Pearson_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs", exact = FALSE)$p.value, Spearman_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs", exact = FALSE)$estimate, Spearman_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs", exact = FALSE)$p.value, Spearman_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs", exact = FALSE)$estimate, Spearman_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs", exact = FALSE)$p.value)
+gdsc_cor_res <- merge(g2p_druggene_tally, gdsc_cor_res, by = "Drug_Gene", all.y = TRUE)
+gdsc_cor_res$n <- ifelse(is.na(gdsc_cor_res$n), 0, gdsc_cor_res$n)
+gdsc_cor_res$InG2P <- ifelse(gdsc_cor_res$n != 0, "Yes", "No")
+gdsc_cor_res$Dataset <- "GDSC"
+
 # Dataset counts
@@
 
-```{r ccldb, echo=FALSE, include=FALSE}
-ccl_converter <- read.delim("./data_munging/cell_line_database_v1_20180911.tsv", row.names = 1, sep = "\t", header = TRUE)
-```
-
 G2P designed a set of standards for stratifying their database’s cancer variant interpretations, ranging from preclinical data at the low-evidence end (level D) to clinically actionable interpretations at the high-evidence end (level A).
@@
 
-```{r grid-dg-wilcox, echo = FALSE}
-ccle_signif_g2p_grid <- readRDS("./data_munging/rds/ccle_signif_g2p_grid.rds")
-ctrp_signif_g2p_grid <- readRDS("./data_munging/rds/ctrp_signif_g2p_grid.rds")
-gdsc_signif_g2p_grid <- readRDS("./data_munging/rds/gdsc_signif_g2p_grid.rds")
-```
+Using cell-line-specific point mutation annotations from the CCLE, we compared z-score-transformed area under the dose-response curve (AUC) distributions between mutant and wildtype cell lines for all G2P genes for each G2P drug tested in the CCLE, CTRP, and GDSC drug screens (*Figures 1B and 2A*).
+At an unadjusted $\alpha = 0.05$, Wilcoxon rank-sum tests revealed that in CCLE, the AUC distributions of mutant and wildtype groups for `r nrow(filter(ccle_signif_g2p_grid, p < 0.05))` out of `r nrow(ccle_signif_g2p_grid)` (`r printnum(nrow(filter(ccle_signif_g2p_grid, p < 0.05)) / nrow(ccle_signif_g2p_grid) * 100)`%) tested drug-gene combinations were significantly different, `r nrow(filter(ctrp_signif_g2p_grid, p < 0.05))` out of `r nrow(ctrp_signif_g2p_grid)` (`r printnum(nrow(filter(ctrp_signif_g2p_grid, p < 0.05)) / nrow(ctrp_signif_g2p_grid) * 100)`%) were significantly different for CTRP, and `r nrow(filter(gdsc_signif_g2p_grid, p < 0.05))` out of `r nrow(gdsc_signif_g2p_grid)` (`r printnum(nrow(filter(gdsc_signif_g2p_grid, p < 0.05)) / nrow(gdsc_signif_g2p_grid) * 100)`%) for GDSC.
 
-Using cell-line-specific point mutation annotations from the CCLE, we compared z-score-transformed area under the dose-response curve (AUC) distributions between mutant and wildtype cell lines for all G2P genes for each G2P drug tested in the CCLE, CTRP, and GDSC drug screens (*Figures 1B and 2A*).
-At uncorrected $\alpha = 0.05$, Wilcoxon rank-sum tests revealed that in CCLE, the AUC distributions of mutant and wildtype groups for `r nrow(filter(ccle_signif_g2p_grid, p < 0.05))` out of `r nrow(ccle_signif_g2p_grid)` (`r printnum(nrow(filter(ccle_signif_g2p_grid, p < 0.05)) / nrow(ccle_signif_g2p_grid) * 100)`%) tested drug-gene combinations were significantly different, `r nrow(filter(ctrp_signif_g2p_grid, p < 0.05))` out of `r nrow(ctrp_signif_g2p_grid)` (`r printnum(nrow(filter(ctrp_signif_g2p_grid, p < 0.05)) / nrow(ctrp_signif_g2p_grid) * 100)`%) were significantly different for CTRP, and `r nrow(filter(gdsc_signif_g2p_grid, p < 0.05))` out of `r nrow(gdsc_signif_g2p_grid)` (`r printnum(nrow(filter(gdsc_signif_g2p_grid, p < 0.05)) / nrow(gdsc_signif_g2p_grid) * 100)`%) for GDSC.
+Controlling for a false discovery rate (FDR) < 5%, selumetinib-*BRAF* ($p$ `r printp(ccle_signif_g2p_grid[ccle_signif_g2p_grid$Drug_Gene == "selumetinib_BRAF",]$p.adj)`) was the only significant drug-gene combination tested in CCLE (`r ccle_signif_g2p_grid_exp`).
+CTRP (`r ctrp_signif_g2p_grid_exp`) yielded `r nrow(ctrp_signif_g2p_grid)` significant combinations, one of which was selumetinib-*BRAF*.
+
 We observe little concordance between the number of interpretations for each G2P association and the significance of mutation status on AUC for said G2P association, suggesting that mutation status alone is not a robust predictor of clinically actionable genetic targets.
 This led us to examine the correlations between AUC and gene expression and AUC and copy number, two other genomic features that are known to associate with cancer and drug response.
+
+We computed Spearman correlation coefficients ($r_s$) between AUC of each drug-gene association and gene expression (RPKM) and copy number (log$_2$ ratio) of the gene in the association
 
@@
 Additionally, across all three genomic features, CTRP consistently identified a higher percentage of its possible level-A G2P associations than GDSC, and similarly, GDSC identified a higher percentage than CCLE.
-In the CCLE-GDSC debate, inconsistency between the datasets was attributed to the groups using two very different assays for generating AUC measurements though it was undecided which was more accurate[@haibe-kains2013; @jang2014; @weinstein2013].
+In the CCLE-GDSC debate, inconsistency between the datasets was attributed to the groups using two very different assays for generating AUC measurements though it was undecided which was more accurate [@haibe-kains2013; @jang2014; @weinstein2013].
 Our results provide very preliminary evidence that GDSC is more accurate than CCLE in regards to reproducing clinical associations.
@@
 ## Do these pancancer drug-gene associations penetrate to the lineage-specific level?
-
-```{r grid-dgl-wilcox, echo = FALSE}
-ccle_signif_g2p_lineage <- readRDS("./data_munging/rds/ccle_signif_g2p_lineage.rds")
-ccle_signif_grid_lineage <- readRDS("./data_munging/rds/ccle_signif_grid_lineage.rds")
-
-ctrp_signif_g2p_lineage <- readRDS("./data_munging/rds/ctrp_signif_g2p_lineage.rds")
-ctrp_signif_grid_lineage <- readRDS("./data_munging/rds/ctrp_signif_grid_lineage.rds")
-
-gdsc_signif_g2p_lineage <- readRDS("./data_munging/rds/gdsc_signif_g2p_lineage.rds")
-gdsc_signif_grid_lineage <- readRDS("./data_munging/rds/gdsc_signif_grid_lineage.rds")
-```
 
@@
 
-**BAD ANALYSIS, keep for reference:** These significant associations did not hold after Bonferroni correction in CTRP ($n = 48$, $\alpha_{adjusted} = 0.001$) or GDSC ($n = 39$, $\alpha_{adjusted} = 0.001$).
-When using gene expression as the genomic feature, three CCLE DGLs had significant correlations at an adjusted $\alpha =  0.006$ ($n = 9$).
-Two of these three DGLs were also significantly correlated with copy number ($n = 9$, $\alpha_{adjusted} = 0.006$).
-In CTRP, AUC of 19 DGLs significantly correlated with gene expression, 12 of which were significant after correction ($n = 61$, $\alpha_{adjusted} = 0.0008$).
-Copy number correlations were significant for 12 DGLs, with three DGLs significant post-correction ($n = 61$, $\alpha_{adjusted} = 0.0008$).
-AUC of 16 DGLs in GDSC significantly correlated with gene expression.
-At an adjusted $\alpha$ of 0.0009 ($n = 53$) eight of them were significant.
-Fewer DGLs were significant when correlating AUC with copy number with 6 significant at an $\alpha$ of 0.05 and 1 significant at an adjusted $\alpha$ of 0.0009 ($n = 53$).
+## Are CRISPR/Cas9 gene essentiality results comparable to those of functional drug screens?
 
-## Are CRISPR/Cas9 gene essentiality results comparable to those of functional drug screens?
+```{r crispr-data, echo = FALSE, warning = FALSE, message = FALSE}
+crispr_data <- readRDS("./../htscreens_giant_files/crispr_data_18Q4.rds")
+crispr_data_ptmuts <- filter(crispr_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
+crispr_data_ptmuts$Keep_PtMut_Tests <- ifelse(crispr_data_ptmuts$Reference_Allele_Length == 1 | is.na(crispr_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(crispr_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
+crispr_data_ptmuts <- filter(crispr_data_ptmuts, Keep_PtMut_Tests == TRUE)
+
+# Filter CRISPR for G2P genes in G2P
+crispr_data_g2p <- filter(crispr_data_ptmuts, Hugo_Symbol %in% g2p_genes)
+crispr_data_g2p$Hugo_Symbol <- factor(crispr_data_g2p$Hugo_Symbol, levels = g2p_genes)
+crispr_data_g2p$Mutation_Status_Nonsilent <- factor(crispr_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
+
+# Wilcoxon test results
+crispr_signif_g2p_gene <- readRDS("./data_munging/rds/crispr_signif_g2p_gene.rds")
+crispr_signif_g2p_gene_exp <- e2exp_converter(crispr_signif_g2p_gene$FDR_cutoff[1])
+crispr_signif_g2p_gene_sig <- filter(crispr_signif_g2p_gene, !is.na(p.signif.adj))
+
+# GE/CN correlations
+crispr_spearman_res_GE <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>% summarize(p = cor.test(y = Score, x = RPKM, method = "spearman", use = "complete.obs", exact = FALSE)$p.value, corr = cor.test(y = Score, x = RPKM, method = "spearman", use = "complete.obs", exact = FALSE)$estimate, Metric = "Gene Expression")
+crispr_spearman_res_GE_sig <- filter(crispr_spearman_res_GE, p < 0.05)
+
+crispr_spearman_res_CN <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>% summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs", exact = FALSE)$p.value, corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs", exact = FALSE)$estimate, Metric = "Copy Number")
+crispr_spearman_res_CN_sig <- filter(crispr_spearman_res_CN, p < 0.05)
+```
 
@@
 Scores are scaled per cell line such that a score of 0 is the median effect of nonessential genes and -1 is the median effect of common core essential genes.
-Of the 34 G2P genes, only G6PD was not targeted by an sgRNA in the CRISPR dataset.
+Of the `r length(g2p_genes)` G2P genes, only *`r setdiff(g2p_genes, as.character(crispr_signif_g2p_gene$Hugo_Symbol))`* was not targeted by an sgRNA in the CRISPR dataset.
 
-When we don’t account for lineage, Wilcoxon rank-sum tests revealed that mutations in eight of the 33 (24.2%) G2P genes significantly correlated with CERES score ($\alpha = 0.05$): KRAS ($p < 0.001$), BRAF ($p < 0.001$), BRCA2  ($p < 0.001$), CYP19A1 ($p = 0.004$), TSC2 ($p = 0.005$), JAK2 ($p = 0.031$), DPYD ($p = 0.042$), and UGT1A1 ($p = 0.048$).
-Gene expression (RPKM) of 17 (51.5%) G2P genes significantly correlated with CERES score, as did copy number (log2-ratio) for 14 (42.4%) G2P genes (Figure ##2).
+When we don’t account for lineage, Wilcoxon rank-sum tests (`r crispr_signif_g2p_gene_exp`, FDR < 5%) revealed that mutations in `r nrow(crispr_signif_g2p_gene_sig)` genes significantly correlated with CERES score: *`r as.character(crispr_signif_g2p_gene_sig$Hugo_Symbol)[1]`* ($p$ `r printp(crispr_signif_g2p_gene_sig$p.adj[1])`) and *`r as.character(crispr_signif_g2p_gene_sig$Hugo_Symbol)[2]`* ($p$ `r printp(crispr_signif_g2p_gene_sig$p.adj[2])`).
+
+Gene expression (RPKM) of `r nrow(crispr_spearman_res_GE_sig)` out of `r nrow(crispr_spearman_res_GE)` (`r printnum(nrow(crispr_spearman_res_GE_sig) / nrow(crispr_spearman_res_GE) * 100)`%) G2P genes significantly correlated with CERES score, as did copy number (log2-ratio) for `r nrow(crispr_spearman_res_CN_sig)` out of `r nrow(crispr_spearman_res_CN)` (`r printnum(nrow(crispr_spearman_res_CN_sig) / nrow(crispr_spearman_res_CN) * 100)`%) G2P genes.
+
 For the purpose of comparison to the drug screen data, if we treat CRISPR knockdown like a small-molecule drug, then these results are similar to the results from CCLE, CTRP, and GDSC (Table 2).
@@
 
-Wilcoxon tests were computed using the ggpubr (`r ggpubr_v`) R package [@kassambara2018].
+Wilcoxon tests were conducted using the `compare_means` function in the ggpubr (`r ggpubr_v`) R package [@kassambara2018].
+`compare_means` does Benjamini-Hochberg p-value adjustment using the `p,adjust` function from the `stats` base R package.
 
-For computing Pearson correlation coefficients, if there were three or fewer data points, then the correlation was not done and a value of NA was supplied.
+For computing Spearman correlation coefficients. If there were 3 or fewer data points, then the correlation was not done and a value of NA was supplied.
 

### 2019-01-09 manuscript.tex

@@
 for each G2P drug tested in the CCLE, CTRP, and GDSC drug screens
-(\emph{Figures 1B and 2A}). At uncorrected \(\alpha = 0.05\), Wilcoxon
+(\emph{Figures 1B and 2A}). At an unadjusted \(\alpha = 0.05\), Wilcoxon
 rank-sum tests revealed that in CCLE, the AUC distributions of mutant
@@
 significantly different for CTRP, and 89 out of 850 (10.47\%) for GDSC.
+
+Controlling for a false discovery rate (FDR) \textless{} 5\%,
+selumetinib-\emph{BRAF} (\(p\) \textless{} .001) was the only
+significant drug-gene combination tested in CCLE (\(p_k < 8^{-4}\)).
+CTRP (\(p_k < 7^{-4}\)) yielded 918 significant combinations, one of
+which was selumetinib-\emph{BRAF}.
+
 We observe little concordance between the number of interpretations for
@@
 cancer and drug response.
+
+We computed Spearman correlation coefficients (\(r_s\)) between AUC of
+each drug-gene association and gene expression (RPKM) and copy number
+(log\(_2\) ratio) of the gene in the association
 
@@
 two very different assays for generating AUC measurements though it was
-undecided which was more accurate(Haibe-Kains et al., 2013; Jang et al.,
-2014; Weinstein \& Lorenzi, 2013). Our results provide very preliminary
-evidence that GDSC is more accurate than CCLE in regards to reproducing
-clinical associations. However, CTRP may be even more accurate than both
-GDSC and CCLE.
+undecided which was more accurate (Haibe-Kains et al., 2013; Jang et
+al., 2014; Weinstein \& Lorenzi, 2013). Our results provide very
+preliminary evidence that GDSC is more accurate than CCLE in regards to
+reproducing clinical associations. However, CTRP may be even more
+accurate than both GDSC and CCLE.
 
@@
 39) identified 6 and 5, respectively, in skin cancer, lung cancer, and
-cancer.
-
-\textbf{BAD ANALYSIS, keep for reference:} These significant
-associations did not hold after Bonferroni correction in CTRP
-(\(n = 48\), \(\alpha_{adjusted} = 0.001\)) or GDSC (\(n = 39\),
-\(\alpha_{adjusted} = 0.001\)). When using gene expression as the
-genomic feature, three CCLE DGLs had significant correlations at an
-adjusted \(\alpha = 0.006\) (\(n = 9\)). Two of these three DGLs were
-also significantly correlated with copy number (\(n = 9\),
-\(\alpha_{adjusted} = 0.006\)). In CTRP, AUC of 19 DGLs significantly
-correlated with gene expression, 12 of which were significant after
-correction (\(n = 61\), \(\alpha_{adjusted} = 0.0008\)). Copy number
-correlations were significant for 12 DGLs, with three DGLs significant
-post-correction (\(n = 61\), \(\alpha_{adjusted} = 0.0008\)). AUC of 16
-DGLs in GDSC significantly correlated with gene expression. At an
-adjusted \(\alpha\) of 0.0009 (\(n = 53\)) eight of them were
-significant. Fewer DGLs were significant when correlating AUC with copy
-number with 6 significant at an \(\alpha\) of 0.05 and 1 significant at
-an adjusted \(\alpha\) of 0.0009 (\(n = 53\)).
+cancer. After Benjamini-Hochberg FDR correction, none of the datasets
+yielded significant DGL interactions.
 
@@
 median effect of nonessential genes and -1 is the median effect of
-common core essential genes. Of the 34 G2P genes, only G6PD was not
-targeted by an sgRNA in the CRISPR dataset.
-
-When we don't account for lineage, Wilcoxon rank-sum tests revealed that
-mutations in eight of the 33 (24.2\%) G2P genes significantly correlated
-with CERES score (\(\alpha = 0.05\)): KRAS (\(p < 0.001\)), BRAF
-(\(p < 0.001\)), BRCA2 (\(p < 0.001\)), CYP19A1 (\(p = 0.004\)), TSC2
-(\(p = 0.005\)), JAK2 (\(p = 0.031\)), DPYD (\(p = 0.042\)), and UGT1A1
-(\(p = 0.048\)). Gene expression (RPKM) of 17 (51.5\%) G2P genes
-significantly correlated with CERES score, as did copy number
-(log2-ratio) for 14 (42.4\%) G2P genes (Figure \#\#2). For the purpose
-of comparison to the drug screen data, if we treat CRISPR knockdown like
-a small-molecule drug, then these results are similar to the results
-from CCLE, CTRP, and GDSC (Table 2).
+common core essential genes. Of the 34 G2P genes, only \emph{G6PD} was
+not targeted by an sgRNA in the CRISPR dataset.
+
+When we don't account for lineage, Wilcoxon rank-sum tests
+(\(p_k < 5^{-3}\), FDR \textless{} 5\%) revealed that mutations in 2
+genes significantly correlated with CERES score: \emph{KRAS} (\(p\)
+\textless{} .001) and \emph{BRAF} (\(p\) \textless{} .001).
+
+Gene expression (RPKM) of 12 out of 33 (36.36\%) G2P genes significantly
+correlated with CERES score, as did copy number (log2-ratio) for 12 out
+of 33 (36.36\%) G2P genes.
+
+For the purpose of comparison to the drug screen data, if we treat
+CRISPR knockdown like a small-molecule drug, then these results are
+similar to the results from CCLE, CTRP, and GDSC (Table 2).
 
@@
 
-Wilcoxon tests were computed using the ggpubr (v0.1.7.999) R package
-(Kassambara, 2018).
-
-For computing Pearson correlation coefficients, if there were three or
+Wilcoxon tests were conducted using the \texttt{compare\_means} function
+in the ggpubr (v0.1.7.999) R package (Kassambara, 2018).
+\texttt{compare\_means} does Benjamini-Hochberg p-value adjustment using
+the \texttt{p,adjust} function from the \texttt{stats} base R package.
+
+For computing Spearman correlation coefficients. If there were 3 or
 fewer data points, then the correlation was not done and a value of NA

### 2019-01-10 manuscript.Rmd
update manuscript, fix table, venndiagrams

@@
 
-floatsintext      : no
-figuresintext     : yes
+floatsintext      : yes
+figsintext        : yes
 figurelist        : no
@@
 library(papaja)
+library(bookdown)
+library(VennDiagram)
 # install.packages("tinytex")
@@
 
-## Comparison of G2P drug-gene associations and CCLE, CTRP, and GDSC
+## Do small-molecule screens in cancer cell lines recapitulate clinical drug-gene associations?
 
 ```{r functions, echo=FALSE, include=FALSE}
-e2exp_converter <- function(string) {
-  e <- formatC(as.numeric(string), format = "e", digits = 0)
-  exp <- sub("(\\d)e-0(\\d)", "$p_k < \\1^{-\\2}$", e, perl = TRUE)
+e2exp_converter <- function(string, p_type) {
+  e <- formatC(as.numeric(string), format = "e", digits = 1)
+  if(p_type == "pk") {
+    if(grepl("(\\d+)e-([1-9]+)", e)) {
+      exp <- sub("(.+)e-(\\d+)", "$p_k = \\1^{-\\2}$", e, perl = TRUE)
+    }
+    if(!grepl("(\\d+)e-([1-9]+)", e)) {
+      exp <- sub("(.+)e-0(\\d)", "$p_k = \\1^{-\\2}$", e, perl = TRUE)
+    }
+  }
+  if(p_type == "p") {
+    if(grepl("(\\d+)e-([1-9]+)", e)) {
+      exp <- sub("(.+)e-(\\d+)", "$p = \\1^{-\\2}$", e, perl = TRUE)
+    }
+    if(!grepl("(\\d+)e-([1-9]+)", e)) {
+      exp <- sub("(.+)e-0(\\d)", "$p = \\1^{-\\2}$", e, perl = TRUE)
+    }
+  }
+  if(p_type == "padj") {
+    if(grepl("(\\d+)e-([1-9]+)", e)) {
+      exp <- sub("(.+)e-(\\d+)", "$p_{adj} = \\1^{-\\2}$", e, perl = TRUE)
+    }
+    if(!grepl("(\\d+)e-([1-9]+)", e)) {
+      exp <- sub("(.+)e-0(\\d)", "$p_{adj} = \\1^{-\\2}$", e, perl = TRUE)
+    }
+  }
   return(exp)
@@
 ccle_signif_g2p <- readRDS("./data_munging/rds/ccle_signif_g2p_gene.rds")
-ccle_signif_g2p_exp <- e2exp_converter(ccle_signif_g2p$FDR_cutoff[1])
+ccle_signif_g2p_exp <- e2exp_converter(ccle_signif_g2p$FDR_cutoff[1], p_type = "pk")
 ccle_signif_g2p_grid <- readRDS("./data_munging/rds/ccle_signif_g2p_grid.rds")
-ccle_signif_g2p_grid_exp <- e2exp_converter(ccle_signif_g2p_grid$FDR_cutoff[1])
+ccle_signif_g2p_grid_exp <- e2exp_converter(ccle_signif_g2p_grid$FDR_cutoff[1], p_type = "pk")
 ccle_signif_g2p_lineage <- readRDS("./data_munging/rds/ccle_signif_g2p_lineage.rds")
-ccle_signif_g2p_lineage_exp <- e2exp_converter(ccle_signif_g2p_lineage$FDR_cutoff[1])
+ccle_signif_g2p_lineage_exp <- e2exp_converter(ccle_signif_g2p_lineage$FDR_cutoff[1], p_type = "pk")
 ccle_signif_grid_lineage <- readRDS("./data_munging/rds/ccle_signif_grid_lineage.rds")
-ccle_signif_grid_lineage_exp <- e2exp_converter(ccle_signif_grid_lineage$FDR_cutoff[1])
+ccle_signif_grid_lineage_exp <- e2exp_converter(ccle_signif_grid_lineage$FDR_cutoff[1], p_type = "pk")
 
 ctrp_signif_g2p <- readRDS("./data_munging/rds/ctrp_signif_g2p_gene.rds")
-ctrp_signif_g2p_exp <- e2exp_converter(ctrp_signif_g2p$FDR_cutoff[1])
+ctrp_signif_g2p_exp <- e2exp_converter(ctrp_signif_g2p$FDR_cutoff[1], p_type = "pk")
 ctrp_signif_g2p_grid <- readRDS("./data_munging/rds/ctrp_signif_g2p_grid.rds")
-ctrp_signif_g2p_grid_exp <- e2exp_converter(ctrp_signif_g2p_grid$FDR_cutoff[1])
+ctrp_signif_g2p_grid_exp <- e2exp_converter(ctrp_signif_g2p_grid$FDR_cutoff[1], p_type = "pk")
 ctrp_signif_g2p_lineage <- readRDS("./data_munging/rds/ctrp_signif_g2p_lineage.rds")
-ctrp_signif_g2p_lineage_exp <- e2exp_converter(ctrp_signif_g2p_lineage$FDR_cutoff[1])
+ctrp_signif_g2p_lineage_exp <- e2exp_converter(ctrp_signif_g2p_lineage$FDR_cutoff[1], p_type = "pk")
 ctrp_signif_grid_lineage <- readRDS("./data_munging/rds/ctrp_signif_grid_lineage.rds")
-ctrp_signif_grid_lineage_exp <- e2exp_converter(ctrp_signif_grid_lineage$FDR_cutoff[1])
+ctrp_signif_grid_lineage_exp <- e2exp_converter(ctrp_signif_grid_lineage$FDR_cutoff[1], p_type = "pk")
 
 gdsc_signif_g2p <- readRDS("./data_munging/rds/gdsc_signif_g2p_gene.rds")
-gdsc_signif_g2p_exp <- e2exp_converter(gdsc_signif_g2p$FDR_cutoff[1])
+gdsc_signif_g2p_exp <- e2exp_converter(gdsc_signif_g2p$FDR_cutoff[1], p_type = "pk")
 gdsc_signif_g2p_grid <- readRDS("./data_munging/rds/gdsc_signif_g2p_grid.rds")
-gdsc_signif_g2p_grid_exp <- e2exp_converter(gdsc_signif_g2p_grid$FDR_cutoff[1])
+gdsc_signif_g2p_grid_exp <- e2exp_converter(gdsc_signif_g2p_grid$FDR_cutoff[1], p_type = "pk")
 gdsc_signif_g2p_lineage <- readRDS("./data_munging/rds/gdsc_signif_g2p_lineage.rds")
-gdsc_signif_g2p_lineage_exp <- e2exp_converter(gdsc_signif_g2p_lineage$FDR_cutoff[1])
+gdsc_signif_g2p_lineage_exp <- e2exp_converter(gdsc_signif_g2p_lineage$FDR_cutoff[1], p_type = "pk")
 gdsc_signif_grid_lineage <- readRDS("./data_munging/rds/gdsc_signif_grid_lineage.rds")
-gdsc_signif_grid_lineage_exp <- e2exp_converter(gdsc_signif_grid_lineage$FDR_cutoff[1])
+gdsc_signif_grid_lineage_exp <- e2exp_converter(gdsc_signif_grid_lineage$FDR_cutoff[1], p_type = "pk")
 
@@
 
-```{r table-g2p-nonCID, echo=FALSE, results='asis'}
-summ <- g2p_nonCID %>% group_by(Drug, DrugID) %>% tally() %>% summarize("Compound identifier" = DrugID, "Number of G2P interpretations" = n, "Proportion of excluded interpretations (%)" = printnum(n / 402 * 100))
+```{r table-g2p-nonCID, results="asis"}
+summ <- g2p_nonCID %>% group_by(Drug, DrugID) %>% tally() %>% summarize("CID" = DrugID, "N_G2P" = n, "%" = printnum(n / nrow(g2p_nonCID) * 100))
 colnames(summ)[colnames(summ) == "Drug"] <- "Compound"
@@
 summ$Compound[summ$Compound == "mab"] <- "mAb"
+summ <- summ[order(summ$N_G2P),]
 
-apa_table(summ, caption = "Distribution of level-A G2P drugs excluded from analyses",
-          note = "mAb = monoclonal antibody; NA indicates G2P interpretation does not have an associated compound")
+apa_table(summ, align = "c", font_size = "small", caption = "Level-A G2P interpretations excluded from analyses", note = "N_G2P (%) = number of associated G2P interpretations, % is out of column total; mAb = monoclonal antibody; NA indicates G2P interpretation does not have an associated compound.")
 ```
@@
 
-Using cell-line-specific point mutation annotations from the CCLE, we compared z-score-transformed area under the dose-response curve (AUC) distributions between mutant and wildtype cell lines for all G2P genes for each G2P drug tested in the CCLE, CTRP, and GDSC drug screens (*Figures 1B and 2A*).
-At an unadjusted $\alpha = 0.05$, Wilcoxon rank-sum tests revealed that in CCLE, the AUC distributions of mutant and wildtype groups for `r nrow(filter(ccle_signif_g2p_grid, p < 0.05))` out of `r nrow(ccle_signif_g2p_grid)` (`r printnum(nrow(filter(ccle_signif_g2p_grid, p < 0.05)) / nrow(ccle_signif_g2p_grid) * 100)`%) tested drug-gene combinations were significantly different, `r nrow(filter(ctrp_signif_g2p_grid, p < 0.05))` out of `r nrow(ctrp_signif_g2p_grid)` (`r printnum(nrow(filter(ctrp_signif_g2p_grid, p < 0.05)) / nrow(ctrp_signif_g2p_grid) * 100)`%) were significantly different for CTRP, and `r nrow(filter(gdsc_signif_g2p_grid, p < 0.05))` out of `r nrow(gdsc_signif_g2p_grid)` (`r printnum(nrow(filter(gdsc_signif_g2p_grid, p < 0.05)) / nrow(gdsc_signif_g2p_grid) * 100)`%) for GDSC.
+**Describe why we compare all pairwise combos rather than filtering for just the drug-gene combos in G2P**
 
-Controlling for a false discovery rate (FDR) < 5%, selumetinib-*BRAF* ($p$ `r printp(ccle_signif_g2p_grid[ccle_signif_g2p_grid$Drug_Gene == "selumetinib_BRAF",]$p.adj)`) was the only significant drug-gene combination tested in CCLE (`r ccle_signif_g2p_grid_exp`).
-CTRP (`r ctrp_signif_g2p_grid_exp`) yielded `r nrow(ctrp_signif_g2p_grid)` significant combinations, one of which was selumetinib-*BRAF*.
+Using cell-line-specific point mutation annotations from the CCLE, we compared z-score-transformed area under the dose-response curve (AUC) distributions between mutant and wildtype cell lines for all pairwise combinations of G2P genes and drugs tested in the CCLE, CTRP, and GDSC drug screens (*Figures 1B and 2A*).
+At an unadjusted $\alpha = 0.05$, Wilcoxon rank-sum tests revealed that in CCLE, AUC significantly correlated with mutation status for `r nrow(filter(ccle_signif_g2p_grid, p < 0.05))` out of `r nrow(ccle_signif_g2p_grid)` (`r printnum(nrow(filter(ccle_signif_g2p_grid, p < 0.05)) / nrow(ccle_signif_g2p_grid) * 100)`%) tested drug-gene combinations were significantly different, `r nrow(filter(ctrp_signif_g2p_grid, p < 0.05))` out of `r nrow(ctrp_signif_g2p_grid)` (`r printnum(nrow(filter(ctrp_signif_g2p_grid, p < 0.05)) / nrow(ctrp_signif_g2p_grid) * 100)`%) were significantly different for CTRP, and `r nrow(filter(gdsc_signif_g2p_grid, p < 0.05))` out of `r nrow(gdsc_signif_g2p_grid)` (`r printnum(nrow(filter(gdsc_signif_g2p_grid, p < 0.05)) / nrow(gdsc_signif_g2p_grid) * 100)`%) for GDSC.
+
+Controlling for a false discovery rate (FDR) < 5%, selumetinib-*BRAF* (`r e2exp_converter(ccle_signif_g2p_grid[ccle_signif_g2p_grid$Drug_Gene == "selumetinib_BRAF",]$p.adj, p_type = "padj")`) was the only significant drug-gene combination tested in CCLE (`r ccle_signif_g2p_grid_exp`).
+CTRP (`r ctrp_signif_g2p_grid_exp`) yielded `r nrow(ctrp_signif_g2p_grid[!is.na(ctrp_signif_g2p_grid$p.signif.adj),])` significant combinations, one of which was selumetinib-*BRAF*.
+There were `r nrow(gdsc_signif_g2p_grid[!is.na(gdsc_signif_g2p_grid$p.signif.adj),])` significant G2P associations in the GDSC dataset (`r gdsc_signif_g2p_grid_exp`), Of all the significant correlations between mutation status and AUC across datasets, the only genes represented were *KRAS* and *BRAF* (Figure\ \@ref(fig:drug-venn)).
+
+```{r drug-venn, echo = FALSE, message=FALSE, warning=FALSE}
+futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
+
+ccle_dgs <- as.character(ccle_signif_g2p_grid[!is.na(ccle_signif_g2p_grid$p.signif.adj),]$Drug_Gene)
+ctrp_dgs <- as.character(ctrp_signif_g2p_grid[!is.na(ctrp_signif_g2p_grid$p.signif.adj),]$Drug_Gene)
+gdsc_dgs <- as.character(gdsc_signif_g2p_grid[!is.na(gdsc_signif_g2p_grid$p.signif.adj),]$Drug_Gene)
+
+drug_venn <- venn.diagram(list("CCLE" = ccle_dgs, "CTRP" = ctrp_dgs, "GDSC" = gdsc_dgs), lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 50, 120), cat.dist = c(0.001, 0.02, 0.0001), cat.cex = 1.5, cex = 1, filename = NULL)
+# in GDSC only
+drug_venn[[7]]$label  <- paste(sort(setdiff(setdiff(gdsc_dgs, ctrp_dgs), ccle_dgs)), collapse = "\n")
+# in GDSC and CTRP only
+drug_venn[[8]]$label <- paste(intersect(gdsc_dgs, ctrp_dgs), collapse = "\n")
+# in CTRP only
+drug_venn[[9]]$label <- paste(sort(setdiff(setdiff(ctrp_dgs, gdsc_dgs), ccle_dgs)), collapse = "\n")
+# in CTRP and CCLE only
+drug_venn[[10]]$label <- intersect(ccle_dgs, ctrp_dgs)
+
+grid.newpage()
+grid.draw(drug_venn)
+```
 
@@
 
-We computed Spearman correlation coefficients ($r_s$) between AUC of each drug-gene association and gene expression (RPKM) and copy number (log$_2$ ratio) of the gene in the association
-
-## Do small-molecule screens in cancer cell lines recapitulate clinical drug-gene associations?
+We computed Spearman correlation coefficients ($r_s$) between AUC of each drug-gene association and gene expression (RPKM) and copy number (log$_2$ ratio) of the gene in the association...
 
@@
 - Looking at a histogram of p-values, if the histogram is flat, then nothing is significant (note from meeting on 11/16)
+- KS test results
 
@@
 
-```{r crispr-data, echo = FALSE, warning = FALSE, message = FALSE}
+```{r crispr-data, echo = FALSE, include = FALSE, warning = FALSE, message = FALSE}
 crispr_data <- readRDS("./../htscreens_giant_files/crispr_data_18Q4.rds")
@@
 crispr_signif_g2p_gene <- readRDS("./data_munging/rds/crispr_signif_g2p_gene.rds")
-crispr_signif_g2p_gene_exp <- e2exp_converter(crispr_signif_g2p_gene$FDR_cutoff[1])
+crispr_signif_g2p_gene_exp <- e2exp_converter(crispr_signif_g2p_gene$FDR_cutoff[1], p_type = "pk")
 crispr_signif_g2p_gene_sig <- filter(crispr_signif_g2p_gene, !is.na(p.signif.adj))
@@
 
+```{r crispr-venn, echo = FALSE}
+crispr_venn <- venn.diagram(list("Gene Expression" = as.character(crispr_spearman_res_GE_sig$Hugo_Symbol), "Copy Number" = as.character(crispr_spearman_res_CN_sig$Hugo_Symbol)), fill = c("darkorchid4", "mediumorchid1"), lty = rep("blank", 2), alpha = c(0.5, 0.5), cat.pos = c(-2, 5), cat.cex = 1.5, cex = 1, filename = NULL)
+
+# in GE only
+crispr_venn[[5]]$label  <- paste(sort(setdiff(as.character(crispr_spearman_res_GE_sig$Hugo_Symbol), as.character(crispr_spearman_res_CN_sig$Hugo_Symbol))), collapse = "\n")
+# in CN only
+crispr_venn[[6]]$label <- paste(sort(setdiff(as.character(crispr_spearman_res_CN_sig$Hugo_Symbol), as.character(crispr_spearman_res_GE_sig$Hugo_Symbol))), collapse = "\n")
+# intesection
+crispr_venn[[7]]$label <- paste(sort(intersect(as.character(crispr_spearman_res_CN_sig$Hugo_Symbol), as.character(crispr_spearman_res_GE_sig$Hugo_Symbol))), collapse = "\n")
+
+grid.newpage()
+grid.draw(crispr_venn)
+```
+
 The CRISPR screen from the Broad Institute reports gene dependency using CERES scores [@meyers2017], which are generated from sgRNA depletion scores and eliminate bias arising from the effect of copy number variation on Cas9 DNA cleavage.
@@
 
-When we don’t account for lineage, Wilcoxon rank-sum tests (`r crispr_signif_g2p_gene_exp`, FDR < 5%) revealed that mutations in `r nrow(crispr_signif_g2p_gene_sig)` genes significantly correlated with CERES score: *`r as.character(crispr_signif_g2p_gene_sig$Hugo_Symbol)[1]`* ($p$ `r printp(crispr_signif_g2p_gene_sig$p.adj[1])`) and *`r as.character(crispr_signif_g2p_gene_sig$Hugo_Symbol)[2]`* ($p$ `r printp(crispr_signif_g2p_gene_sig$p.adj[2])`).
+When we don’t account for lineage, Wilcoxon rank-sum tests (`r crispr_signif_g2p_gene_exp`, FDR < 5%) revealed that mutations in `r nrow(crispr_signif_g2p_gene_sig)` genes significantly correlated with CERES score: *`r as.character(crispr_signif_g2p_gene_sig$Hugo_Symbol)[1]`* (`r e2exp_converter(crispr_signif_g2p_gene_sig$p.adj[1], p_type = "padj")`) and *`r as.character(crispr_signif_g2p_gene_sig$Hugo_Symbol)[2]`* (`r e2exp_converter(crispr_signif_g2p_gene_sig$p.adj[2], p_type = "padj")`).
+Gene expression (RPKM) of `r nrow(crispr_spearman_res_GE_sig)` out of `r nrow(crispr_spearman_res_GE)` (`r printnum(nrow(crispr_spearman_res_GE_sig) / nrow(crispr_spearman_res_GE) * 100)`%) G2P genes significantly correlated with CERES score, as did copy number (log2-ratio) for `r nrow(crispr_spearman_res_CN_sig)` out of `r nrow(crispr_spearman_res_CN)` (`r printnum(nrow(crispr_spearman_res_CN_sig) / nrow(crispr_spearman_res_CN) * 100)`%) G2P genes (Figure\ \@ref(fig:crispr-venn)).
 
-Gene expression (RPKM) of `r nrow(crispr_spearman_res_GE_sig)` out of `r nrow(crispr_spearman_res_GE)` (`r printnum(nrow(crispr_spearman_res_GE_sig) / nrow(crispr_spearman_res_GE) * 100)`%) G2P genes significantly correlated with CERES score, as did copy number (log2-ratio) for `r nrow(crispr_spearman_res_CN_sig)` out of `r nrow(crispr_spearman_res_CN)` (`r printnum(nrow(crispr_spearman_res_CN_sig) / nrow(crispr_spearman_res_CN) * 100)`%) G2P genes.
-
-For the purpose of comparison to the drug screen data, if we treat CRISPR knockdown like a small-molecule drug, then these results are similar to the results from CCLE, CTRP, and GDSC (Table 2).
+For the purpose of comparison to the drug screen data, if we treat CRISPR knockdown like a small-molecule drug, then these results are more comprehensive than the results from CCLE, CTRP, and GDSC (Table 2).
 

### 2019-01-10 manuscript.tex
update manuscript, fix table, venndiagrams

@@
-\documentclass[man]{apa6}
+\documentclass[man,floatsintext]{apa6}
 \usepackage{lmodern}
@@
 
-\DeclareDelayedFloatFlavor{ThreePartTable}{table}
-\DeclareDelayedFloatFlavor{lltable}{table}
-\DeclareDelayedFloatFlavor*{longtable}{table}
-\makeatletter
-\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
-\makeatother
 \usepackage{lineno}
@@
 
-\subsection{Comparison of G2P drug-gene associations and CCLE, CTRP, and
-GDSC}\label{comparison-of-g2p-drug-gene-associations-and-ccle-ctrp-and-gdsc}
+\subsection{Do small-molecule screens in cancer cell lines recapitulate
+clinical drug-gene
+associations?}\label{do-small-molecule-screens-in-cancer-cell-lines-recapitulate-clinical-drug-gene-associations}
 
@@
 \begin{threeparttable}
-\caption{\label{tab:table-g2p-nonCID}Distribution of level-A G2P drugs excluded from analyses}
-\begin{tabular}{llll}
+\caption{\label{tab:table-g2p-nonCID}Level-A G2P interpretations excluded from analyses}
+\small{
+\begin{tabular}{cccc}
 \toprule
-Compound & \multicolumn{1}{c}{Compound identifier} & \multicolumn{1}{c}{Number of G2P interpretations} & \multicolumn{1}{c}{Proportion of excluded interpretations (\%)}\\
+Compound & \multicolumn{1}{c}{CID} & \multicolumn{1}{c}{N\_G2P} & \multicolumn{1}{c}{\%}\\
 \midrule
+EGFR & SID160769799 & 1 & 0.25\\
+pertuzumab & CHEMBL2007641 & 1 & 0.25\\
+ipilimumab & CHEMBL1789844 & 2 & 0.50\\
+cisplatin & CHEMBL2068237 & 3 & 0.75\\
+pembrolizumab & CHEMBL3137343 & 3 & 0.75\\
+nivolumab & CHEMBL2108738 & 4 & 1.00\\
+trastuzumab & CHEMBL1201585 & 9 & 2.24\\
+mAb & CHEMBL2109423 & 16 & 3.98\\
 cetuximab & CHEMBL1201577 & 74 & 18.41\\
-cisplatin & CHEMBL2068237 & 3 & 0.75\\
-EGFR & SID160769799 & 1 & 0.25\\
-ipilimumab & CHEMBL1789844 & 2 & 0.50\\
-mAb & CHEMBL2109423 & 16 & 3.98\\
-nivolumab & CHEMBL2108738 & 4 & 1.00\\
 panitumumab & CHEMBL1201827 & 75 & 18.66\\
-pembrolizumab & CHEMBL3137343 & 3 & 0.75\\
-pertuzumab & CHEMBL2007641 & 1 & 0.25\\
-trastuzumab & CHEMBL1201585 & 9 & 2.24\\
 NA & NA & 214 & 53.23\\
@@
 \end{tabular}
+}
 \begin{tablenotes}[para]
-\normalsize{\textit{Note.} mAb = monoclonal antibody; NA indicates G2P interpretation does not have an associated compound}
+\normalsize{\textit{Note.} N\_G2P (\%) = number of associated G2P interpretations, \% is out of column total; mAb = monoclonal antibody; NA indicates G2P interpretation does not have an associated compound.}
 \end{tablenotes}
@@
 
+\textbf{Describe why we compare all pairwise combos rather than
+filtering for just the drug-gene combos in G2P}
+
 Using cell-line-specific point mutation annotations from the CCLE, we
 compared z-score-transformed area under the dose-response curve (AUC)
-distributions between mutant and wildtype cell lines for all G2P genes
-for each G2P drug tested in the CCLE, CTRP, and GDSC drug screens
-(\emph{Figures 1B and 2A}). At an unadjusted \(\alpha = 0.05\), Wilcoxon
-rank-sum tests revealed that in CCLE, the AUC distributions of mutant
-and wildtype groups for 18 out of 170 (10.59\%) tested drug-gene
-combinations were significantly different, 135 out of 918 (14.71\%) were
-significantly different for CTRP, and 89 out of 850 (10.47\%) for GDSC.
+distributions between mutant and wildtype cell lines for all pairwise
+combinations of G2P genes and drugs tested in the CCLE, CTRP, and GDSC
+drug screens (\emph{Figures 1B and 2A}). At an unadjusted
+\(\alpha = 0.05\), Wilcoxon rank-sum tests revealed that in CCLE, AUC
+significantly correlated with mutation status for 18 out of 170
+(10.59\%) tested drug-gene combinations were significantly different,
+135 out of 918 (14.71\%) were significantly different for CTRP, and 89
+out of 850 (10.47\%) for GDSC.
 
 Controlling for a false discovery rate (FDR) \textless{} 5\%,
-selumetinib-\emph{BRAF} (\(p\) \textless{} .001) was the only
-significant drug-gene combination tested in CCLE (\(p_k < 8^{-4}\)).
-CTRP (\(p_k < 7^{-4}\)) yielded 918 significant combinations, one of
-which was selumetinib-\emph{BRAF}.
+selumetinib-\emph{BRAF} (\(p_{adj} = 1.4^{-10}\)) was the only
+significant drug-gene combination tested in CCLE (\(p_k = 7.9^{-4}\)).
+CTRP (\(p_k = 6.5^{-4}\)) yielded 5 significant combinations, one of
+which was selumetinib-\emph{BRAF}. There were 3 significant G2P
+associations in the GDSC dataset (\(p_k = 9.5^{-5}\)), Of all the
+significant correlations between mutation status and AUC across
+datasets, the only genes represented were \emph{KRAS} and \emph{BRAF}
+(Figure~\ref{fig:drug-venn}).
+
+\begin{verbatim}
+## NULL
+\end{verbatim}
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/drug-venn-1.pdf}
+\caption{}
+\end{figure}
 
@@
 each drug-gene association and gene expression (RPKM) and copy number
-(log\(_2\) ratio) of the gene in the association
-
-\subsection{Do small-molecule screens in cancer cell lines recapitulate
-clinical drug-gene
-associations?}\label{do-small-molecule-screens-in-cancer-cell-lines-recapitulate-clinical-drug-gene-associations}
+(log\(_2\) ratio) of the gene in the association\ldots{}
 
@@
   nothing is significant (note from meeting on 11/16)
+\item
+  KS test results
 \end{itemize}
@@
 
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/crispr-venn-1.pdf}
+\caption{}
+\end{figure}
+
 The CRISPR screen from the Broad Institute reports gene dependency using
@@
 When we don't account for lineage, Wilcoxon rank-sum tests
-(\(p_k < 5^{-3}\), FDR \textless{} 5\%) revealed that mutations in 2
-genes significantly correlated with CERES score: \emph{KRAS} (\(p\)
-\textless{} .001) and \emph{BRAF} (\(p\) \textless{} .001).
-
+(\(p_k = 5.1^{-3}\), FDR \textless{} 5\%) revealed that mutations in 2
+genes significantly correlated with CERES score: \emph{KRAS}
+(\(p_{adj} = 2.6^{-37}\)) and \emph{BRAF} (\(p_{adj} = 8.2^{-18}\)).
 Gene expression (RPKM) of 12 out of 33 (36.36\%) G2P genes significantly
 correlated with CERES score, as did copy number (log2-ratio) for 12 out
-of 33 (36.36\%) G2P genes.
+of 33 (36.36\%) G2P genes (Figure~\ref{fig:crispr-venn}).
 

### 2019-01-10 manuscript_analysis.Rmd

@@
 
+## Tests
+
+```{r}
+ccle_pearson_ttest_GE <- t.test(ccle_cor_res$Pearson_Corr_GE ~ ccle_cor_res$InG2P)
+ccle_pearson_ttest_res_GE <- paste0("t(", round(ccle_pearson_ttest_GE$parameter, 0), ") = ", round(ccle_pearson_ttest_GE$statistic, 2), ", p = ", round(ccle_pearson_ttest_GE$p.value, 2))
+ccle_pearson_ttest_CN <- t.test(ccle_cor_res$Pearson_Corr_CN ~ ccle_cor_res$InG2P)
+ccle_pearson_ttest_res_CN <- paste0("t(", round(ccle_pearson_ttest_CN$parameter, 0), ") = ", round(ccle_pearson_ttest_CN$statistic, 2), ", p = ", round(ccle_pearson_ttest_CN$p.value, 2))
+ccle_spearman_ttest_GE <- t.test(ccle_cor_res$Spearman_Corr_GE ~ ccle_cor_res$InG2P)
+ccle_spearman_ttest_res_GE <- paste0("t(", round(ccle_spearman_ttest_GE$parameter, 0), ") = ", round(ccle_spearman_ttest_GE$statistic, 2), ", p = ", round(ccle_spearman_ttest_GE$p.value, 2))
+ccle_spearman_ttest_CN <- t.test(ccle_cor_res$Spearman_Corr_CN ~ ccle_cor_res$InG2P)
+ccle_spearman_ttest_res_CN <- paste0("t(", round(ccle_spearman_ttest_CN$parameter, 0), ") = ", round(ccle_spearman_ttest_CN$statistic, 2), ", p = ", formatC(ccle_spearman_ttest_CN$p.value, 2, format = "f"))
+
+ctrp_pearson_ttest_GE <- t.test(ctrp_cor_res$Pearson_Corr_GE ~ ctrp_cor_res$InG2P)
+ctrp_pearson_ttest_res_GE <- paste0("t(", round(ctrp_pearson_ttest_GE$parameter, 0), ") = ", round(ctrp_pearson_ttest_GE$statistic, 2), ", p ", ifelse(round(ctrp_pearson_ttest_GE$p.value, 3) == 0, "< 0.001", paste0("= ", round(ctrp_pearson_ttest_GE$p.value, 3))))
+ctrp_pearson_ttest_CN <- t.test(ctrp_cor_res$Pearson_Corr_CN ~ ctrp_cor_res$InG2P)
+ctrp_pearson_ttest_res_CN <- paste0("t(", round(ctrp_pearson_ttest_CN$parameter, 0), ") = ", round(ctrp_pearson_ttest_CN$statistic, 2), ", p = ", round(ctrp_pearson_ttest_CN$p.value, 3))
+ctrp_spearman_ttest_GE <- t.test(ctrp_cor_res$Spearman_Corr_GE ~ ctrp_cor_res$InG2P)
+ctrp_spearman_ttest_res_GE <- paste0("t(", round(ctrp_spearman_ttest_GE$parameter, 0), ") = ", round(ctrp_spearman_ttest_GE$statistic, 2), ", p = ", round(ctrp_spearman_ttest_GE$p.value, 2))
+ctrp_spearman_ttest_CN <- t.test(ctrp_cor_res$Spearman_Corr_CN ~ ctrp_cor_res$InG2P)
+ctrp_spearman_ttest_res_CN <- paste0("t(", round(ctrp_spearman_ttest_CN$parameter, 0), ") = ", round(ctrp_spearman_ttest_CN$statistic, 2), ", p = ", round(ctrp_spearman_ttest_CN$p.value, 2))
+
+gdsc_pearson_ttest_GE <- t.test(gdsc_cor_res$Pearson_Corr_GE ~ gdsc_cor_res$InG2P)
+gdsc_pearson_ttest_res_GE <- paste0("t(", round(gdsc_pearson_ttest_GE$parameter, 0), ") = ", round(gdsc_pearson_ttest_GE$statistic, 2), ", p = ", round(gdsc_pearson_ttest_GE$p.value, 3))
+gdsc_pearson_ttest_CN <- t.test(gdsc_cor_res$Pearson_Corr_CN ~ gdsc_cor_res$InG2P)
+gdsc_pearson_ttest_res_CN <- paste0("t(", round(gdsc_pearson_ttest_CN$parameter, 0), ") = ", round(gdsc_pearson_ttest_CN$statistic, 2), ", p = ", round(gdsc_pearson_ttest_CN$p.value, 3))
+gdsc_spearman_ttest_GE <- t.test(gdsc_cor_res$Spearman_Corr_GE ~ gdsc_cor_res$InG2P)
+gdsc_spearman_ttest_res_GE <- paste0("t(", round(gdsc_spearman_ttest_GE$parameter, 0), ") = ", round(gdsc_spearman_ttest_GE$statistic, 2), ", p = ", round(gdsc_spearman_ttest_GE$p.value, 2))
+gdsc_spearman_ttest_CN <- t.test(gdsc_cor_res$Spearman_Corr_CN ~ gdsc_cor_res$InG2P)
+gdsc_spearman_ttest_res_CN <- paste0("t(", round(gdsc_spearman_ttest_CN$parameter, 0), ") = ", round(gdsc_spearman_ttest_CN$statistic, 2), ", p = ", round(gdsc_spearman_ttest_CN$p.value, 2))
+
+g2p_cor_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"), Pearson_Test_Results_GE = c(ccle_pearson_ttest_res_GE, ctrp_pearson_ttest_res_GE, gdsc_pearson_ttest_res_GE), Pearson_Test_Results_CN = c(ccle_pearson_ttest_res_CN, ctrp_pearson_ttest_res_CN, gdsc_pearson_ttest_res_CN), Spearman_Test_Results_GE = c(ccle_spearman_ttest_res_GE, ctrp_spearman_ttest_res_GE, gdsc_spearman_ttest_res_GE), Spearman_Test_Results_CN = c(ccle_spearman_ttest_res_CN, ctrp_spearman_ttest_res_CN, gdsc_spearman_ttest_res_CN))
+```
+
 ## Mut

### 2019-01-11 manuscript.Rmd
work on manuscript, mut results, venn diagrams

@@
 floatsintext      : yes
-figsintext        : yes
+figsintext        : no
 figurelist        : no
@@
 library(VennDiagram)
+library(lettercase)
 # install.packages("tinytex")
@@
 e2exp_converter <- function(string, p_type) {
+  # Convert p-vals in scientific format to latex-equation style p-vals with exponent
   e <- formatC(as.numeric(string), format = "e", digits = 1)
@@
   return(exp)
+}
+
+dg2intext_converter <- function(drug_gene) {
+  # Convert drug-gene strings to have italic gene name
+  d_g <- strsplit(drug_gene, split = "_")
+  dg <- paste0(d_g[[1]][1], "-*", d_g[[1]][2], "*")
+  return(dg)
 }
@@
 
+# Mut summaries
+drug_grid_shared_dg <- union(ccle_signif_g2p_grid[!is.na(ccle_signif_g2p_grid$p.signif.adj),]$Drug_Gene, union(ctrp_signif_g2p_grid[!is.na(ctrp_signif_g2p_grid$p.signif.adj),]$Drug_Gene, gdsc_signif_g2p_grid[!is.na(gdsc_signif_g2p_grid$p.signif.adj),]$Drug_Gene))
+
 # CCLE: GE/CN correlations
-ccle_cor_res <- ccle_data_g2p_grid %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs", exact = FALSE)$estimate, Pearson_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs", exact = FALSE)$p.value, Pearson_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs", exact = FALSE)$estimate, Pearson_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs", exact = FALSE)$p.value, Spearman_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs", exact = FALSE)$estimate, Spearman_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs", exact = FALSE)$p.value, Spearman_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs", exact = FALSE)$estimate, Spearman_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs", exact = FALSE)$p.value)
+ccle_cor_res <- ccle_data_g2p_grid %>% group_by(Drug_Gene) %>% summarize(
+  Pearson_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs", exact = FALSE)$estimate,
+  Pearson_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs", exact = FALSE)$p.value,
+  Pearson_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs", exact = FALSE)$estimate,
+  Pearson_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs", exact = FALSE)$p.value,
+  Spearman_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs", exact = FALSE)$estimate,
+  Spearman_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs", exact = FALSE)$p.value,
+  Spearman_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs", exact = FALSE)$estimate,
+  Spearman_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs", exact = FALSE)$p.value)
 ccle_cor_res <- merge(g2p_druggene_tally, ccle_cor_res, by = "Drug_Gene", all.y = TRUE)
@@
 
-**Describe why we compare all pairwise combos rather than filtering for just the drug-gene combos in G2P**
+Using cell-line-specific point mutation annotations from the CCLE, we compared z-score-transformed area under the dose-response curve (AUC) distributions between mutant and wildtype cell lines for all G2P associations tested in the CCLE, CTRP, and GDSC drug screens.
+Of the `r length(g2p_druggenes)` G2P associations, data was available for `r length(ccle_signif_g2p$Drug_Gene)` associations in CCLE, `r length(ctrp_signif_g2p$Drug_Gene)` in CTRP, and `r length(gdsc_signif_g2p$Drug_Gene)` in GDSC.
+Controlling for a false discovery rate (FDR) < 5%, CCLE yielded no significant correlations (Wilcoxon rank-sum tests, `r ccle_signif_g2p_exp`), though the most significant G2P association was `r dg2intext_converter(ccle_signif_g2p$Drug_Gene[1])` (`r e2exp_converter(ccle_signif_g2p$p.adj[1], p_type = "padj")`).
+In CTRP, AUC from `r nrow(filter(ctrp_signif_g2p[!is.na(ctrp_signif_g2p$p.signif.adj),]))` drug-gene associations correlated with the gene's mutation status (`r ctrp_signif_g2p_exp`): `r dg2intext_converter(ctrp_signif_g2p$Drug_Gene[1])` (`r e2exp_converter(ctrp_signif_g2p$p.adj[1], p_type = "padj")`), `r dg2intext_converter(ctrp_signif_g2p$Drug_Gene[2])` (`r e2exp_converter(ctrp_signif_g2p$p.adj[2], p_type = "padj")`), and `r dg2intext_converter(ctrp_signif_g2p$Drug_Gene[3])` (`r e2exp_converter(ctrp_signif_g2p$p.adj[3], p_type = "padj")`).
+`r str_ucfirst(dg2intext_converter(gdsc_signif_g2p$Drug_Gene[1]))` (`r e2exp_converter(gdsc_signif_g2p$p.adj[1], p_type = "padj")`) and `r dg2intext_converter(gdsc_signif_g2p$Drug_Gene[2])` (`r e2exp_converter(gdsc_signif_g2p$p.adj[2], p_type = "padj")`) were significant in GDSC (`r gdsc_signif_g2p_exp`).
 
-Using cell-line-specific point mutation annotations from the CCLE, we compared z-score-transformed area under the dose-response curve (AUC) distributions between mutant and wildtype cell lines for all pairwise combinations of G2P genes and drugs tested in the CCLE, CTRP, and GDSC drug screens (*Figures 1B and 2A*).
-At an unadjusted $\alpha = 0.05$, Wilcoxon rank-sum tests revealed that in CCLE, AUC significantly correlated with mutation status for `r nrow(filter(ccle_signif_g2p_grid, p < 0.05))` out of `r nrow(ccle_signif_g2p_grid)` (`r printnum(nrow(filter(ccle_signif_g2p_grid, p < 0.05)) / nrow(ccle_signif_g2p_grid) * 100)`%) tested drug-gene combinations were significantly different, `r nrow(filter(ctrp_signif_g2p_grid, p < 0.05))` out of `r nrow(ctrp_signif_g2p_grid)` (`r printnum(nrow(filter(ctrp_signif_g2p_grid, p < 0.05)) / nrow(ctrp_signif_g2p_grid) * 100)`%) were significantly different for CTRP, and `r nrow(filter(gdsc_signif_g2p_grid, p < 0.05))` out of `r nrow(gdsc_signif_g2p_grid)` (`r printnum(nrow(filter(gdsc_signif_g2p_grid, p < 0.05)) / nrow(gdsc_signif_g2p_grid) * 100)`%) for GDSC.
+> **(???) Describe why we compare all pairwise combos rather than filtering for just the drug-gene combos in G2P?**
 
-Controlling for a false discovery rate (FDR) < 5%, selumetinib-*BRAF* (`r e2exp_converter(ccle_signif_g2p_grid[ccle_signif_g2p_grid$Drug_Gene == "selumetinib_BRAF",]$p.adj, p_type = "padj")`) was the only significant drug-gene combination tested in CCLE (`r ccle_signif_g2p_grid_exp`).
+To test for potentially novel drug-gene associations, we conducted similar Wilcoxon rank-sum tests for all pairwise combinations of G2P genes and drugs tested in the three drug screens (*Figures 1B and 2A*).
+At an unadjusted $\alpha = 0.05$, the tests revealed that in CCLE, AUC significantly correlated with mutation status for `r nrow(filter(ccle_signif_g2p_grid, p < 0.05))` out of `r nrow(ccle_signif_g2p_grid)` (`r printnum(nrow(filter(ccle_signif_g2p_grid, p < 0.05)) / nrow(ccle_signif_g2p_grid) * 100)`%) tested drug-gene combinations were significantly different, `r nrow(filter(ctrp_signif_g2p_grid, p < 0.05))` out of `r nrow(ctrp_signif_g2p_grid)` (`r printnum(nrow(filter(ctrp_signif_g2p_grid, p < 0.05)) / nrow(ctrp_signif_g2p_grid) * 100)`%) were significantly different for CTRP, and `r nrow(filter(gdsc_signif_g2p_grid, p < 0.05))` out of `r nrow(gdsc_signif_g2p_grid)` (`r printnum(nrow(filter(gdsc_signif_g2p_grid, p < 0.05)) / nrow(gdsc_signif_g2p_grid) * 100)`%) for GDSC.
+
+Controlling for a FDR < 5%, `r dg2intext_converter(ccle_signif_g2p_grid$Drug_Gene[1])` (`r e2exp_converter(ccle_signif_g2p_grid$p.adj[1], p_type = "padj")`) was the only significant drug-gene combination tested in CCLE (`r ccle_signif_g2p_grid_exp`).
 CTRP (`r ctrp_signif_g2p_grid_exp`) yielded `r nrow(ctrp_signif_g2p_grid[!is.na(ctrp_signif_g2p_grid$p.signif.adj),])` significant combinations, one of which was selumetinib-*BRAF*.
-There were `r nrow(gdsc_signif_g2p_grid[!is.na(gdsc_signif_g2p_grid$p.signif.adj),])` significant G2P associations in the GDSC dataset (`r gdsc_signif_g2p_grid_exp`), Of all the significant correlations between mutation status and AUC across datasets, the only genes represented were *KRAS* and *BRAF* (Figure\ \@ref(fig:drug-venn)).
+There were `r nrow(gdsc_signif_g2p_grid[!is.na(gdsc_signif_g2p_grid$p.signif.adj),])` significant G2P associations in the GDSC dataset (`r gdsc_signif_g2p_grid_exp`).
+Of all the significant correlations between mutation status and AUC across datasets, the only genes represented were *KRAS* and *BRAF* (Figure\ \@ref(fig:drug-venn)).
+Of the `r length(drug_grid_shared_dg)` significant drug-gene associations across datasets, `r length(intersect(drug_grid_shared_dg, g2p_druggenes))` were G2P associations.
+The remaining `r length(drug_grid_shared_dg) - length(intersect(drug_grid_shared_dg, g2p_druggenes))` associations were `r dg2intext_converter(setdiff(drug_grid_shared_dg, g2p_druggenes)[1])`, `r dg2intext_converter(setdiff(drug_grid_shared_dg, g2p_druggenes)[2])`, and `r dg2intext_converter(setdiff(drug_grid_shared_dg, g2p_druggenes)[3])`.
+
+> **(???) Trametinib and selumetinib are both *MEK* inhibitors, and pazopanib is a *VEGFR* inhibitor.
+VEGF signaling can influence the MAPK/ERK signaling pathway, which promotes cell proliferation and survival.
+This pathway includes *RAS*, *BRAF*, and *MEK* proteins.
+These results underscore the importance of the MAPK/ERK signaling pathway in cancer.**
+
+However, taking these results as a whole, we observe little concordance between G2P associations and the correlation of mutation status and AUC for said G2P association, suggesting that mutation status alone is not a robust predictor of clinically actionable genetic targets.
+This led us to examine the correlations between AUC and gene expression and AUC and copy number, two other genomic features that are known to associate with cancer and drug response.
+We computed Spearman correlation coefficients ($r_s$) between AUC of each drug-gene association and gene expression (RPKM) and copy number (log$_2$ ratio) of the gene in the association...
 
 ```{r drug-venn, echo = FALSE, message=FALSE, warning=FALSE}
-futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
-
-ccle_dgs <- as.character(ccle_signif_g2p_grid[!is.na(ccle_signif_g2p_grid$p.signif.adj),]$Drug_Gene)
-ctrp_dgs <- as.character(ctrp_signif_g2p_grid[!is.na(ctrp_signif_g2p_grid$p.signif.adj),]$Drug_Gene)
-gdsc_dgs <- as.character(gdsc_signif_g2p_grid[!is.na(gdsc_signif_g2p_grid$p.signif.adj),]$Drug_Gene)
-
-drug_venn <- venn.diagram(list("CCLE" = ccle_dgs, "CTRP" = ctrp_dgs, "GDSC" = gdsc_dgs), lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 50, 120), cat.dist = c(0.001, 0.02, 0.0001), cat.cex = 1.5, cex = 1, filename = NULL)
-# in GDSC only
-drug_venn[[7]]$label  <- paste(sort(setdiff(setdiff(gdsc_dgs, ctrp_dgs), ccle_dgs)), collapse = "\n")
-# in GDSC and CTRP only
-drug_venn[[8]]$label <- paste(intersect(gdsc_dgs, ctrp_dgs), collapse = "\n")
-# in CTRP only
-drug_venn[[9]]$label <- paste(sort(setdiff(setdiff(ctrp_dgs, gdsc_dgs), ccle_dgs)), collapse = "\n")
-# in CTRP and CCLE only
-drug_venn[[10]]$label <- intersect(ccle_dgs, ctrp_dgs)
-
-grid.newpage()
-grid.draw(drug_venn)
+knitr::include_graphics("./plots/manuscript/drugscreen_venn.png")
 ```
 
-We observe little concordance between the number of interpretations for each G2P association and the significance of mutation status on AUC for said G2P association, suggesting that mutation status alone is not a robust predictor of clinically actionable genetic targets.
-This led us to examine the correlations between AUC and gene expression and AUC and copy number, two other genomic features that are known to associate with cancer and drug response.
-
-We computed Spearman correlation coefficients ($r_s$) between AUC of each drug-gene association and gene expression (RPKM) and copy number (log$_2$ ratio) of the gene in the association...
-
-**Cut this analysis since we are comparing distributions of p-values?**
+> **(???) Cut this analysis since we are comparing distributions of p-values?**
 
@@
 CCLE had data for `r length(unique(ccle_data_g2p_dgl$Drug_Gene_Lin))` DGLs, CTRP had data for `r length(unique(ctrp_data_g2p_dgl$Drug_Gene_Lin))`, and GDSC had data for `r length(unique(gdsc_data_g2p_dgl$Drug_Gene_Lin))`, yielding a total of `r length(union(union(unique(ccle_data_g2p_dgl$Drug_Gene_Lin), unique(ctrp_data_g2p_dgl$Drug_Gene_Lin)), unique(gdsc_data_g2p_dgl$Drug_Gene_Lin)))` unique DGLs across all three datasets.
-Only `r length(intersect(intersect(unique(ccle_data_g2p_dgl$Drug_Gene_Lin), unique(ctrp_data_g2p_dgl$Drug_Gene_Lin)), unique(gdsc_data_g2p_dgl$Drug_Gene_Lin)))` DGLs were screened in all three datasets,
+Only `r length(intersect(intersect(unique(ccle_data_g2p_dgl$Drug_Gene_Lin), unique(ctrp_data_g2p_dgl$Drug_Gene_Lin)), unique(gdsc_data_g2p_dgl$Drug_Gene_Lin)))` DGLs were screened in all three datasets.
 
@@
 After Benjamini-Hochberg FDR correction, none of the datasets yielded significant DGL interactions.
+
+> **(???) KS test results**
+
+(Figure\ \@ref(fig:ksplot))
+
+```{r ksplot, echo = FALSE, warning = FALSE, message = FALSE, fig.cap="Comparison of Spearman correlation coefficients derived from copy number (log$_2$ ratio), gene expression (RPKM), and AUC z-scores from G2P drug-gene associations.
+Coefficients were grouped by whether or not the associated lineage for each comparison was in a G2P drug-gene-lineage association or not.
+Distributions of these grouped coefficients were compared using Kolmogorov-Smirnov tests."}
+knitr::include_graphics("./plots/manuscript/g2p_spearman_ks_res_plot.png")
+```
 
@@
 
-```{r crispr-venn, echo = FALSE}
-crispr_venn <- venn.diagram(list("Gene Expression" = as.character(crispr_spearman_res_GE_sig$Hugo_Symbol), "Copy Number" = as.character(crispr_spearman_res_CN_sig$Hugo_Symbol)), fill = c("darkorchid4", "mediumorchid1"), lty = rep("blank", 2), alpha = c(0.5, 0.5), cat.pos = c(-2, 5), cat.cex = 1.5, cex = 1, filename = NULL)
-
-# in GE only
-crispr_venn[[5]]$label  <- paste(sort(setdiff(as.character(crispr_spearman_res_GE_sig$Hugo_Symbol), as.character(crispr_spearman_res_CN_sig$Hugo_Symbol))), collapse = "\n")
-# in CN only
-crispr_venn[[6]]$label <- paste(sort(setdiff(as.character(crispr_spearman_res_CN_sig$Hugo_Symbol), as.character(crispr_spearman_res_GE_sig$Hugo_Symbol))), collapse = "\n")
-# intesection
-crispr_venn[[7]]$label <- paste(sort(intersect(as.character(crispr_spearman_res_CN_sig$Hugo_Symbol), as.character(crispr_spearman_res_GE_sig$Hugo_Symbol))), collapse = "\n")
-
-grid.newpage()
-grid.draw(crispr_venn)
+```{r crispr-venn, echo = FALSE, message=FALSE, warning=FALSE}
+knitr::include_graphics("./plots/manuscript/crispr_venn.png")
 ```
@@
 Wilcoxon tests were conducted using the `compare_means` function in the ggpubr (`r ggpubr_v`) R package [@kassambara2018].
-`compare_means` does Benjamini-Hochberg p-value adjustment using the `p,adjust` function from the `stats` base R package.
+`compare_means` does Benjamini-Hochberg p-value adjustment using the `p.adjust` function from the `stats` base R package.
 
-For computing Spearman correlation coefficients. If there were 3 or fewer data points, then the correlation was not done and a value of NA was supplied.
+For computing Spearman correlation coefficients, we used the `cor.test` base R package. If there were 3 or fewer data points, then the correlation was not done and a value of `NA` was supplied.
 

### 2019-01-11 manuscript_analysis.Rmd
work on manuscript, mut results, venn diagrams

@@
 
+Venn diagram between GE and CN:
+```{r}
+futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
+crispr_venn <- venn.diagram(list("Gene Expression" = as.character(crispr_spearman_res_GE_sig$Hugo_Symbol), "Copy Number" = as.character(crispr_spearman_res_CN_sig$Hugo_Symbol)), fill = c("darkorchid4", "mediumorchid1"), lty = rep("blank", 2), alpha = c(0.5, 0.5), cat.pos = c(-2, 5), cat.cex = 1.5, cex = 1, filename = NULL)
+
+# in GE only
+crispr_venn[[5]]$label  <- paste(sort(setdiff(as.character(crispr_spearman_res_GE_sig$Hugo_Symbol), as.character(crispr_spearman_res_CN_sig$Hugo_Symbol))), collapse = "\n")
+# in CN only
+crispr_venn[[6]]$label <- paste(sort(setdiff(as.character(crispr_spearman_res_CN_sig$Hugo_Symbol), as.character(crispr_spearman_res_GE_sig$Hugo_Symbol))), collapse = "\n")
+# intesection
+crispr_venn[[7]]$label <- paste(sort(intersect(as.character(crispr_spearman_res_CN_sig$Hugo_Symbol), as.character(crispr_spearman_res_GE_sig$Hugo_Symbol))), collapse = "\n")
+
+png("./plots/manuscript/crispr_venn.png")
+grid.newpage()
+grid.draw(crispr_venn)
+dev.off()
+```
+
 G2P genes with a significant effect on CERES score by mutation status, gene expression, and copy number. Summary plot using Pearson correlation coefficient for GE and CN:
@@
 ### Mut
+
+Venn diagram of drug-gene associations:
+```{r}
+futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
+
+ccle_dgs <- as.character(ccle_signif_g2p_grid[!is.na(ccle_signif_g2p_grid$p.signif.adj),]$Drug_Gene)
+ctrp_dgs <- as.character(ctrp_signif_g2p_grid[!is.na(ctrp_signif_g2p_grid$p.signif.adj),]$Drug_Gene)
+gdsc_dgs <- as.character(gdsc_signif_g2p_grid[!is.na(gdsc_signif_g2p_grid$p.signif.adj),]$Drug_Gene)
+
+drug_venn <- venn.diagram(list("CCLE" = ccle_dgs, "CTRP" = ctrp_dgs, "GDSC" = gdsc_dgs), lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 50, 120), cat.dist = c(0.001, 0.02, 0.0001), cat.cex = 1.5, cex = 1, filename = NULL)
+# in GDSC only
+drug_venn[[7]]$label  <- paste(sort(setdiff(setdiff(gdsc_dgs, ctrp_dgs), ccle_dgs)), collapse = "\n")
+# in GDSC and CTRP only
+drug_venn[[8]]$label <- paste(intersect(gdsc_dgs, ctrp_dgs), collapse = "\n")
+# in CTRP only
+drug_venn[[9]]$label <- paste(sort(setdiff(setdiff(ctrp_dgs, gdsc_dgs), ccle_dgs)), collapse = "\n")
+# in CTRP and CCLE only
+drug_venn[[10]]$label <- intersect(ccle_dgs, ctrp_dgs)
+
+png("./plots/manuscript/drugscreen_venn.png")
+grid.newpage()
+grid.draw(drug_venn)
+dev.off()
+```
 
@@
 g2p_corr_stats <- g2p_corr_stats %>% separate(col = Metric, into = c("Correlation_Method", "corr", "Metric"), sep = "_")
+g2p_corr_stats$Metric <- ifelse(g2p_corr_stats$Metric == "GE", "Gene Expression", "Copy Number")
 g2p_corr_stats
@@
 g2p_corr_4plot <- g2p_corr_4plot %>% separate(col = variable, into = c("Correlation_Method", "corr", "Metric"), sep = "_", remove = FALSE)
+g2p_corr_4plot$Metric <- ifelse(g2p_corr_4plot$Metric == "GE", "Gene Expression", "Copy Number")
 
@@
 # ggsave("./plots/manuscript/g2p_ks_res_plot.png", g2p_ks_res_plot, device = "png", dpi = 450, width = 12, height = 6, units = "in")
+```
+
+```{r fig.height=6, fig.width=12}
+g2p_ks_res_plot_spearman <- ggplot(data = filter(g2p_corr_4plot, Correlation_Method == "Spearman")) +
+  facet_grid(Metric ~ Dataset, labeller = labeller(yfacet = c('CN' = "Copy Number", 'GE' = "Gene Expression"))) +
+  geom_violin(aes(y = Correlation, x = G2P_DGL, fill = Dataset, color = Dataset, alpha = G2P_DGL)) +
+  geom_boxplot(width = 0.075, aes(y = Correlation, x = G2P_DGL, color = Dataset)) +
+  geom_jitter(width = 0.3, alpha = 0.8, aes(y = Correlation, x = G2P_DGL, color = Dataset)) +
+  theme(legend.position = "none") +
+  scale_alpha_manual(values = c("Yes" = 0.6, "No" = 0.2)) +
+  scale_fill_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
+  scale_color_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4", "CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
+  coord_cartesian(ylim = c(-1, 1)) +
+  geom_text(data = filter(g2p_corr_stats, Correlation_Method == "Spearman"), aes(x = 1.5, y = 0.8, label = paste0("D = ", formatC(D_stat, digits = 2, format = "f"), ", p = ", ifelse(pval > 0.1, round(pval, 2), round(pval, 3)), "\n", ifelse(is.na(signif), "", signif)))) +
+  labs(x = "Is the lineage in a G2P DGL?", y = "Spearman Correlation Coefficient")
+g2p_ks_res_plot_spearman
+
+# ggsave("./plots/manuscript/g2p_spearman_ks_res_plot.png", g2p_ks_res_plot_spearman, device = "png", dpi = 450, width = 12, height = 6, units = "in")
 ```

### 2019-01-11 manuscript.tex

@@
 
+\DeclareDelayedFloatFlavor{ThreePartTable}{table}
+\DeclareDelayedFloatFlavor{lltable}{table}
+\DeclareDelayedFloatFlavor*{longtable}{table}
+\makeatletter
+\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
+\makeatother
 \usepackage{lineno}
@@
 
-\textbf{Describe why we compare all pairwise combos rather than
-filtering for just the drug-gene combos in G2P}
-
 Using cell-line-specific point mutation annotations from the CCLE, we
 compared z-score-transformed area under the dose-response curve (AUC)
-distributions between mutant and wildtype cell lines for all pairwise
-combinations of G2P genes and drugs tested in the CCLE, CTRP, and GDSC
-drug screens (\emph{Figures 1B and 2A}). At an unadjusted
-\(\alpha = 0.05\), Wilcoxon rank-sum tests revealed that in CCLE, AUC
-significantly correlated with mutation status for 18 out of 170
-(10.59\%) tested drug-gene combinations were significantly different,
-135 out of 918 (14.71\%) were significantly different for CTRP, and 89
-out of 850 (10.47\%) for GDSC.
-
-Controlling for a false discovery rate (FDR) \textless{} 5\%,
-selumetinib-\emph{BRAF} (\(p_{adj} = 1.4^{-10}\)) was the only
-significant drug-gene combination tested in CCLE (\(p_k = 7.9^{-4}\)).
-CTRP (\(p_k = 6.5^{-4}\)) yielded 5 significant combinations, one of
-which was selumetinib-\emph{BRAF}. There were 3 significant G2P
-associations in the GDSC dataset (\(p_k = 9.5^{-5}\)), Of all the
-significant correlations between mutation status and AUC across
-datasets, the only genes represented were \emph{KRAS} and \emph{BRAF}
-(Figure~\ref{fig:drug-venn}).
-
-\begin{verbatim}
-## NULL
-\end{verbatim}
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/drug-venn-1.pdf}
-\caption{}
-\end{figure}
-
-We observe little concordance between the number of interpretations for
-each G2P association and the significance of mutation status on AUC for
-said G2P association, suggesting that mutation status alone is not a
+distributions between mutant and wildtype cell lines for all G2P
+associations tested in the CCLE, CTRP, and GDSC drug screens. Of the 88
+G2P associations, data was available for 9 associations in CCLE, 48 in
+CTRP, and 44 in GDSC. Controlling for a false discovery rate (FDR)
+\textless{} 5\%, CCLE yielded no significant correlations (Wilcoxon
+rank-sum tests, \(p_k = 2.1^{-4}\)), though the most significant G2P
+association was selumetinib-\emph{KRAS} (\(p_{adj} = 1.9^{-3}\)). In
+CTRP, AUC from 3 drug-gene associations correlated with the gene's
+mutation status (\(p_k = 4.5^{-3}\)): selumetinib-\emph{KRAS}
+(\(p_{adj} = 4.4^{-8}\)), vemurafenib-\emph{BRAF}
+(\(p_{adj} = 4.4^{-8}\)), and dabrafenib-\emph{BRAF}
+(\(p_{adj} = 7.7^{-5}\)). Dabrafenib-\emph{BRAF}
+(\(p_{adj} = 8.6^{-11}\)) and trametinib-\emph{BRAF}
+(\(p_{adj} = 4.2^{-6}\)) were significant in GDSC (\(p_k = 2.3^{-3}\)).
+
+\begin{quote}
+\textbf{(???) Describe why we compare all pairwise combos rather than
+filtering for just the drug-gene combos in G2P?}
+\end{quote}
+
+To test for potentially novel drug-gene associations, we conducted
+similar Wilcoxon rank-sum tests for all pairwise combinations of G2P
+genes and drugs tested in the three drug screens (\emph{Figures 1B and
+2A}). At an unadjusted \(\alpha = 0.05\), the tests revealed that in
+CCLE, AUC significantly correlated with mutation status for 18 out of
+170 (10.59\%) tested drug-gene combinations were significantly
+different, 135 out of 918 (14.71\%) were significantly different for
+CTRP, and 89 out of 850 (10.47\%) for GDSC.
+
+Controlling for a FDR \textless{} 5\%, selumetinib-\emph{BRAF}
+(\(p_{adj} = 1.4^{-10}\)) was the only significant drug-gene combination
+tested in CCLE (\(p_k = 7.9^{-4}\)). CTRP (\(p_k = 6.5^{-4}\)) yielded 5
+significant combinations, one of which was selumetinib-\emph{BRAF}.
+There were 3 significant G2P associations in the GDSC dataset
+(\(p_k = 9.5^{-5}\)). Of all the significant correlations between
+mutation status and AUC across datasets, the only genes represented were
+\emph{KRAS} and \emph{BRAF} (Figure~\ref{fig:drug-venn}). Of the 7
+significant drug-gene associations across datasets, 4 were G2P
+associations. The remaining 3 associations were selumetinib-\emph{BRAF},
+trametinib-\emph{KRAS}, and pazopanib-\emph{BRAF}.
+
+\begin{quote}
+\textbf{(???) Trametinib and selumetinib are both \emph{MEK} inhibitors,
+and pazopanib is a \emph{VEGFR} inhibitor. VEGF signaling can influence
+the MAPK/ERK signaling pathway, which promotes cell proliferation and
+survival. This pathway includes \emph{RAS}, \emph{BRAF}, and \emph{MEK}
+proteins. These results underscore the importance of the MAPK/ERK
+signaling pathway in cancer.}
+\end{quote}
+
+However, taking these results as a whole, we observe little concordance
+between G2P associations and the correlation of mutation status and AUC
+for said G2P association, suggesting that mutation status alone is not a
 robust predictor of clinically actionable genetic targets. This led us
@@
 copy number, two other genomic features that are known to associate with
-cancer and drug response.
-
-We computed Spearman correlation coefficients (\(r_s\)) between AUC of
-each drug-gene association and gene expression (RPKM) and copy number
-(log\(_2\) ratio) of the gene in the association\ldots{}
-
-\textbf{Cut this analysis since we are comparing distributions of
+cancer and drug response. We computed Spearman correlation coefficients
+(\(r_s\)) between AUC of each drug-gene association and gene expression
+(RPKM) and copy number (log\(_2\) ratio) of the gene in the
+association\ldots{}
+
+\begin{figure}
+\centering
+\includegraphics{./plots/manuscript/drugscreen_venn.png}
+\caption{}
+\end{figure}
+
+\begin{quote}
+\textbf{(???) Cut this analysis since we are comparing distributions of
 p-values?}
+\end{quote}
 
@@
 DGLs across all three datasets. Only 7 DGLs were screened in all three
-datasets,
+datasets.
 
@@
 
+\begin{quote}
+\textbf{(???) KS test results}
+\end{quote}
+
+(Figure~\ref{fig:ksplot})
+
+\begin{figure}
+\centering
+\includegraphics{./plots/manuscript/g2p_spearman_ks_res_plot.png}
+\caption{\label{fig:ksplot}Comparison of Spearman correlation coefficients
+derived from copy number (log\(_2\) ratio), gene expression (RPKM), and
+AUC z-scores from G2P drug-gene associations. Coefficients were grouped
+by whether or not the associated lineage for each comparison was in a
+G2P drug-gene-lineage association or not. Distributions of these grouped
+coefficients were compared using Kolmogorov-Smirnov tests.}
+\end{figure}
+
 \subsection{Are CRISPR/Cas9 gene essentiality results comparable to
@@
 \centering
-\includegraphics{manuscript_files/figure-latex/crispr-venn-1.pdf}
+\includegraphics{./plots/manuscript/crispr_venn.png}
 \caption{}
@@
 For the purpose of comparison to the drug screen data, if we treat
-CRISPR knockdown like a small-molecule drug, then these results are
-similar to the results from CCLE, CTRP, and GDSC (Table 2).
+CRISPR knockdown like a small-molecule drug, then these results are more
+comprehensive than the results from CCLE, CTRP, and GDSC (Table 2).
 
@@
 \texttt{compare\_means} does Benjamini-Hochberg p-value adjustment using
-the \texttt{p,adjust} function from the \texttt{stats} base R package.
-
-For computing Spearman correlation coefficients. If there were 3 or
-fewer data points, then the correlation was not done and a value of NA
-was supplied.
+the \texttt{p.adjust} function from the \texttt{stats} base R package.
+
+For computing Spearman correlation coefficients, we used the
+\texttt{cor.test} base R package. If there were 3 or fewer data points,
+then the correlation was not done and a value of \texttt{NA} was
+supplied.
 

### 2019-01-16 manuscript.Rmd
updated papaja doc and made new venn diagrams

@@
 VEGF signaling can influence the MAPK/ERK signaling pathway, which promotes cell proliferation and survival.
-This pathway includes *RAS*, *BRAF*, and *MEK* proteins.
-These results underscore the importance of the MAPK/ERK signaling pathway in cancer.**
+This pathway includes *RAS*, *BRAF*, and *MEK* proteins.**
 
@@
 This led us to examine the correlations between AUC and gene expression and AUC and copy number, two other genomic features that are known to associate with cancer and drug response.
-We computed Spearman correlation coefficients ($r_s$) between AUC of each drug-gene association and gene expression (RPKM) and copy number (log$_2$ ratio) of the gene in the association...
+We computed Spearman correlation coefficients ($r_s$) between AUC of each drug-gene association and gene expression (RPKM) and copy number (log$_2$ ratio) of the gene in the association...**(???) need to complete this thought/analysis**
 
-```{r drug-venn, echo = FALSE, message=FALSE, warning=FALSE}
-knitr::include_graphics("./plots/manuscript/drugscreen_venn.png")
+(ref:drug-venn) Overlap of drug-gene associations drawn from all pairwise combinations of G2P drugs and G2P genes whose drug effects significantly correlated with (**A**) mutation status, (**B**) gene expression, and (**C**) copy number across CCLE, CTRP, and GDSC.
+
+```{r drug-venn, echo = FALSE, message=FALSE, warning=FALSE, fig.cap='(ref:drug-venn)'}
+knitr::include_graphics("./plots/manuscript/drugscreen_venns.pdf")
 ```
 
-> **(???) Cut this analysis since we are comparing distributions of p-values?**
+> **(???) Cut these next three paragraphs since we cut the analysis, but keep for future reference**
 
@@
 
-```{r ksplot, echo = FALSE, warning = FALSE, message = FALSE, fig.cap="Comparison of Spearman correlation coefficients derived from copy number (log$_2$ ratio), gene expression (RPKM), and AUC z-scores from G2P drug-gene associations.
+(ref:ksplot) Comparison of Spearman correlation coefficients ($r_s$) derived from copy number (log$_2$ ratio), gene expression (RPKM), and AUC z-scores from G2P drug-gene associations.
 Coefficients were grouped by whether or not the associated lineage for each comparison was in a G2P drug-gene-lineage association or not.
-Distributions of these grouped coefficients were compared using Kolmogorov-Smirnov tests."}
-knitr::include_graphics("./plots/manuscript/g2p_spearman_ks_res_plot.png")
+Distributions of these grouped coefficients were compared using Kolmogorov-Smirnov tests.
+
+```{r ksplot, echo = FALSE, warning = FALSE, message = FALSE, fig.cap='(ref:ksplot)'}
+knitr::include_graphics("./plots/manuscript/g2p_spearman_ks_res_plot.pdf")
 ```
@@
 
-```{r crispr-venn, echo = FALSE, message=FALSE, warning=FALSE}
-knitr::include_graphics("./plots/manuscript/crispr_venn.png")
+(ref:crispr-venn) Overlap of genes whose gene expression and/or copy number significantly correlated with CERES score.
+
+```{r crispr-venn, echo = FALSE, message=FALSE, warning=FALSE, fig.cap='(ref:crispr-venn)'}
+knitr::include_graphics("./plots/manuscript/crispr_venn.pdf")
 ```

### 2019-01-16 manuscript.tex

@@
 survival. This pathway includes \emph{RAS}, \emph{BRAF}, and \emph{MEK}
-proteins. These results underscore the importance of the MAPK/ERK
-signaling pathway in cancer.}
+proteins.}
 \end{quote}
@@
 (RPKM) and copy number (log\(_2\) ratio) of the gene in the
-association\ldots{}
+association\ldots{}\textbf{(???) need to complete this thought/analysis}
 
@@
 \centering
-\includegraphics{./plots/manuscript/drugscreen_venn.png}
-\caption{}
+\includegraphics{./plots/manuscript/drugscreen_venns.pdf}
+\caption{\label{fig:drug-venn}Overlap of drug-gene associations drawn from all
+pairwise combinations of G2P drugs and G2P genes whose drug effects
+significantly correlated with (\textbf{A}) mutation status, (\textbf{B})
+gene expression, and (\textbf{C}) copy number across CCLE, CTRP, and
+GDSC.}
 \end{figure}
@@
 \begin{quote}
-\textbf{(???) Cut this analysis since we are comparing distributions of
-p-values?}
+\textbf{(???) Cut these next three paragraphs since we cut the analysis,
+but keep for future reference}
 \end{quote}
@@
 \centering
-\includegraphics{./plots/manuscript/g2p_spearman_ks_res_plot.png}
-\caption{\label{fig:ksplot}Comparison of Spearman correlation coefficients
+\includegraphics{./plots/manuscript/g2p_spearman_ks_res_plot.pdf}
+\caption{\label{fig:ksplot}Comparison of Spearman correlation coefficients (\(r_s\))
 derived from copy number (log\(_2\) ratio), gene expression (RPKM), and
@@
 \centering
-\includegraphics{./plots/manuscript/crispr_venn.png}
-\caption{}
+\includegraphics{./plots/manuscript/crispr_venn.pdf}
+\caption{\label{fig:crispr-venn}Overlap of genes whose gene expression and/or copy
+number significantly correlated with CERES score.}
 \end{figure}

### 2019-01-16 manuscript_analysis.Rmd

@@
 }
-```
-
-```{r}
-test <- adj_signif(ccle_signif_grid_lineage, alpha = 0.05)
-length(unique(test))
 ```
@@
 ccle_cor_res$Dataset <- "CCLE"
-# ccle_pearson_ttest_GE <- t.test(ccle_cor_res$Pearson_Corr_GE ~ ccle_cor_res$InG2P)
-# ccle_pearson_ttest_res_GE <- paste0("t(", round(ccle_pearson_ttest_GE$parameter, 0), ") = ", round(ccle_pearson_ttest_GE$statistic, 2), ", p = ", round(ccle_pearson_ttest_GE$p.value, 2))
-# ccle_pearson_ttest_CN <- t.test(ccle_cor_res$Pearson_Corr_CN ~ ccle_cor_res$InG2P)
-# ccle_pearson_ttest_res_CN <- paste0("t(", round(ccle_pearson_ttest_CN$parameter, 0), ") = ", round(ccle_pearson_ttest_CN$statistic, 2), ", p = ", round(ccle_pearson_ttest_CN$p.value, 2))
-# ccle_spearman_ttest_GE <- t.test(ccle_cor_res$Spearman_Corr_GE ~ ccle_cor_res$InG2P)
-# ccle_spearman_ttest_res_GE <- paste0("t(", round(ccle_spearman_ttest_GE$parameter, 0), ") = ", round(ccle_spearman_ttest_GE$statistic, 2), ", p = ", round(ccle_spearman_ttest_GE$p.value, 2))
-# ccle_spearman_ttest_CN <- t.test(ccle_cor_res$Spearman_Corr_CN ~ ccle_cor_res$InG2P)
-# ccle_spearman_ttest_res_CN <- paste0("t(", round(ccle_spearman_ttest_CN$parameter, 0), ") = ", round(ccle_spearman_ttest_CN$statistic, 2), ", p = ", formatC(ccle_spearman_ttest_CN$p.value, 2, format = "f"))
 
@@
 ctrp_cor_res$Dataset <- "CTRP"
-# ctrp_pearson_ttest_GE <- t.test(ctrp_cor_res$Pearson_Corr_GE ~ ctrp_cor_res$InG2P)
-# ctrp_pearson_ttest_res_GE <- paste0("t(", round(ctrp_pearson_ttest_GE$parameter, 0), ") = ", round(ctrp_pearson_ttest_GE$statistic, 2), ", p ", ifelse(round(ctrp_pearson_ttest_GE$p.value, 3) == 0, "< 0.001", paste0("= ", round(ctrp_pearson_ttest_GE$p.value, 3))))
-# ctrp_pearson_ttest_CN <- t.test(ctrp_cor_res$Pearson_Corr_CN ~ ctrp_cor_res$InG2P)
-# ctrp_pearson_ttest_res_CN <- paste0("t(", round(ctrp_pearson_ttest_CN$parameter, 0), ") = ", round(ctrp_pearson_ttest_CN$statistic, 2), ", p = ", round(ctrp_pearson_ttest_CN$p.value, 3))
-# ctrp_spearman_ttest_GE <- t.test(ctrp_cor_res$Spearman_Corr_GE ~ ctrp_cor_res$InG2P)
-# ctrp_spearman_ttest_res_GE <- paste0("t(", round(ctrp_spearman_ttest_GE$parameter, 0), ") = ", round(ctrp_spearman_ttest_GE$statistic, 2), ", p = ", round(ctrp_spearman_ttest_GE$p.value, 2))
-# ctrp_spearman_ttest_CN <- t.test(ctrp_cor_res$Spearman_Corr_CN ~ ctrp_cor_res$InG2P)
-# ctrp_spearman_ttest_res_CN <- paste0("t(", round(ctrp_spearman_ttest_CN$parameter, 0), ") = ", round(ctrp_spearman_ttest_CN$statistic, 2), ", p = ", round(ctrp_spearman_ttest_CN$p.value, 2))
 
@@
 gdsc_cor_res$Dataset <- "GDSC"
-# gdsc_pearson_ttest_GE <- t.test(gdsc_cor_res$Pearson_Corr_GE ~ gdsc_cor_res$InG2P)
-# gdsc_pearson_ttest_res_GE <- paste0("t(", round(gdsc_pearson_ttest_GE$parameter, 0), ") = ", round(gdsc_pearson_ttest_GE$statistic, 2), ", p = ", round(gdsc_pearson_ttest_GE$p.value, 3))
-# gdsc_pearson_ttest_CN <- t.test(gdsc_cor_res$Pearson_Corr_CN ~ gdsc_cor_res$InG2P)
-# gdsc_pearson_ttest_res_CN <- paste0("t(", round(gdsc_pearson_ttest_CN$parameter, 0), ") = ", round(gdsc_pearson_ttest_CN$statistic, 2), ", p = ", round(gdsc_pearson_ttest_CN$p.value, 3))
-# gdsc_spearman_ttest_GE <- t.test(gdsc_cor_res$Spearman_Corr_GE ~ gdsc_cor_res$InG2P)
-# gdsc_spearman_ttest_res_GE <- paste0("t(", round(gdsc_spearman_ttest_GE$parameter, 0), ") = ", round(gdsc_spearman_ttest_GE$statistic, 2), ", p = ", round(gdsc_spearman_ttest_GE$p.value, 2))
-# gdsc_spearman_ttest_CN <- t.test(gdsc_cor_res$Spearman_Corr_CN ~ gdsc_cor_res$InG2P)
-# gdsc_spearman_ttest_res_CN <- paste0("t(", round(gdsc_spearman_ttest_CN$parameter, 0), ") = ", round(gdsc_spearman_ttest_CN$statistic, 2), ", p = ", round(gdsc_spearman_ttest_CN$p.value, 2))
 
@@
 g2p_cor$Spearman_CN_Sign <- ifelse(sign(g2p_cor$Spearman_Corr_CN) == 1, "+", ifelse(sign(g2p_cor$Spearman_Corr_CN) == -1, "-", "0"))
+```
+
+Deprecated: T-tests of G2P presence/absence distributions
+```{r}
+# ccle_pearson_ttest_GE <- t.test(ccle_cor_res$Pearson_Corr_GE ~ ccle_cor_res$InG2P)
+# ccle_pearson_ttest_res_GE <- paste0("t(", round(ccle_pearson_ttest_GE$parameter, 0), ") = ", round(ccle_pearson_ttest_GE$statistic, 2), ", p = ", round(ccle_pearson_ttest_GE$p.value, 2))
+# ccle_pearson_ttest_CN <- t.test(ccle_cor_res$Pearson_Corr_CN ~ ccle_cor_res$InG2P)
+# ccle_pearson_ttest_res_CN <- paste0("t(", round(ccle_pearson_ttest_CN$parameter, 0), ") = ", round(ccle_pearson_ttest_CN$statistic, 2), ", p = ", round(ccle_pearson_ttest_CN$p.value, 2))
+# ccle_spearman_ttest_GE <- t.test(ccle_cor_res$Spearman_Corr_GE ~ ccle_cor_res$InG2P)
+# ccle_spearman_ttest_res_GE <- paste0("t(", round(ccle_spearman_ttest_GE$parameter, 0), ") = ", round(ccle_spearman_ttest_GE$statistic, 2), ", p = ", round(ccle_spearman_ttest_GE$p.value, 2))
+# ccle_spearman_ttest_CN <- t.test(ccle_cor_res$Spearman_Corr_CN ~ ccle_cor_res$InG2P)
+# ccle_spearman_ttest_res_CN <- paste0("t(", round(ccle_spearman_ttest_CN$parameter, 0), ") = ", round(ccle_spearman_ttest_CN$statistic, 2), ", p = ", formatC(ccle_spearman_ttest_CN$p.value, 2, format = "f"))
+
+# ctrp_pearson_ttest_GE <- t.test(ctrp_cor_res$Pearson_Corr_GE ~ ctrp_cor_res$InG2P)
+# ctrp_pearson_ttest_res_GE <- paste0("t(", round(ctrp_pearson_ttest_GE$parameter, 0), ") = ", round(ctrp_pearson_ttest_GE$statistic, 2), ", p ", ifelse(round(ctrp_pearson_ttest_GE$p.value, 3) == 0, "< 0.001", paste0("= ", round(ctrp_pearson_ttest_GE$p.value, 3))))
+# ctrp_pearson_ttest_CN <- t.test(ctrp_cor_res$Pearson_Corr_CN ~ ctrp_cor_res$InG2P)
+# ctrp_pearson_ttest_res_CN <- paste0("t(", round(ctrp_pearson_ttest_CN$parameter, 0), ") = ", round(ctrp_pearson_ttest_CN$statistic, 2), ", p = ", round(ctrp_pearson_ttest_CN$p.value, 3))
+# ctrp_spearman_ttest_GE <- t.test(ctrp_cor_res$Spearman_Corr_GE ~ ctrp_cor_res$InG2P)
+# ctrp_spearman_ttest_res_GE <- paste0("t(", round(ctrp_spearman_ttest_GE$parameter, 0), ") = ", round(ctrp_spearman_ttest_GE$statistic, 2), ", p = ", round(ctrp_spearman_ttest_GE$p.value, 2))
+# ctrp_spearman_ttest_CN <- t.test(ctrp_cor_res$Spearman_Corr_CN ~ ctrp_cor_res$InG2P)
+# ctrp_spearman_ttest_res_CN <- paste0("t(", round(ctrp_spearman_ttest_CN$parameter, 0), ") = ", round(ctrp_spearman_ttest_CN$statistic, 2), ", p = ", round(ctrp_spearman_ttest_CN$p.value, 2))
+
+# gdsc_pearson_ttest_GE <- t.test(gdsc_cor_res$Pearson_Corr_GE ~ gdsc_cor_res$InG2P)
+# gdsc_pearson_ttest_res_GE <- paste0("t(", round(gdsc_pearson_ttest_GE$parameter, 0), ") = ", round(gdsc_pearson_ttest_GE$statistic, 2), ", p = ", round(gdsc_pearson_ttest_GE$p.value, 3))
+# gdsc_pearson_ttest_CN <- t.test(gdsc_cor_res$Pearson_Corr_CN ~ gdsc_cor_res$InG2P)
+# gdsc_pearson_ttest_res_CN <- paste0("t(", round(gdsc_pearson_ttest_CN$parameter, 0), ") = ", round(gdsc_pearson_ttest_CN$statistic, 2), ", p = ", round(gdsc_pearson_ttest_CN$p.value, 3))
+# gdsc_spearman_ttest_GE <- t.test(gdsc_cor_res$Spearman_Corr_GE ~ gdsc_cor_res$InG2P)
+# gdsc_spearman_ttest_res_GE <- paste0("t(", round(gdsc_spearman_ttest_GE$parameter, 0), ") = ", round(gdsc_spearman_ttest_GE$statistic, 2), ", p = ", round(gdsc_spearman_ttest_GE$p.value, 2))
+# gdsc_spearman_ttest_CN <- t.test(gdsc_cor_res$Spearman_Corr_CN ~ gdsc_cor_res$InG2P)
+# gdsc_spearman_ttest_res_CN <- paste0("t(", round(gdsc_spearman_ttest_CN$parameter, 0), ") = ", round(gdsc_spearman_ttest_CN$statistic, 2), ", p = ", round(gdsc_spearman_ttest_CN$p.value, 2))
+
 # g2p_cor_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"),
@@
 futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
+crispr_spearman_res_GE_sig <- filter(crispr_spearman_res_GE, p < 0.05)
+crispr_spearman_res_CN_sig <- filter(crispr_spearman_res_CN, p < 0.05)
 crispr_venn <- venn.diagram(list("Gene Expression" = as.character(crispr_spearman_res_GE_sig$Hugo_Symbol), "Copy Number" = as.character(crispr_spearman_res_CN_sig$Hugo_Symbol)), fill = c("darkorchid4", "mediumorchid1"), lty = rep("blank", 2), alpha = c(0.5, 0.5), cat.pos = c(-2, 5), cat.cex = 1.5, cex = 1, filename = NULL)
@@
 
-png("./plots/manuscript/crispr_venn.png")
-grid.newpage()
-grid.draw(crispr_venn)
-dev.off()
+ggsave("./plots/manuscript/crispr_venn.pdf", crispr_venn)
 ```
@@
 ### Mut
-
-Venn diagram of drug-gene associations:
-```{r}
-futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
-
-ccle_dgs <- as.character(ccle_signif_g2p_grid[!is.na(ccle_signif_g2p_grid$p.signif.adj),]$Drug_Gene)
-ctrp_dgs <- as.character(ctrp_signif_g2p_grid[!is.na(ctrp_signif_g2p_grid$p.signif.adj),]$Drug_Gene)
-gdsc_dgs <- as.character(gdsc_signif_g2p_grid[!is.na(gdsc_signif_g2p_grid$p.signif.adj),]$Drug_Gene)
-
-drug_venn <- venn.diagram(list("CCLE" = ccle_dgs, "CTRP" = ctrp_dgs, "GDSC" = gdsc_dgs), lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 50, 120), cat.dist = c(0.001, 0.02, 0.0001), cat.cex = 1.5, cex = 1, filename = NULL)
-# in GDSC only
-drug_venn[[7]]$label  <- paste(sort(setdiff(setdiff(gdsc_dgs, ctrp_dgs), ccle_dgs)), collapse = "\n")
-# in GDSC and CTRP only
-drug_venn[[8]]$label <- paste(intersect(gdsc_dgs, ctrp_dgs), collapse = "\n")
-# in CTRP only
-drug_venn[[9]]$label <- paste(sort(setdiff(setdiff(ctrp_dgs, gdsc_dgs), ccle_dgs)), collapse = "\n")
-# in CTRP and CCLE only
-drug_venn[[10]]$label <- intersect(ccle_dgs, ctrp_dgs)
-
-png("./plots/manuscript/drugscreen_venn.png")
-grid.newpage()
-grid.draw(drug_venn)
-dev.off()
-```
 
@@
 # ggsave("./plots/manuscript/all_spearman_summ_plot.png", all_spearman_summ_plot, device = "png", dpi = 450, width = 12, height = 10, units = "in")
+```
+
+### Venn diagrams
+
+Venn diagram of drug-gene associations:
+```{r}
+futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
+
+ccle_mut_dgs <- as.character(ccle_signif_g2p_grid[!is.na(ccle_signif_g2p_grid$p.signif.adj),]$Drug_Gene)
+ctrp_mut_dgs <- as.character(ctrp_signif_g2p_grid[!is.na(ctrp_signif_g2p_grid$p.signif.adj),]$Drug_Gene)
+gdsc_mut_dgs <- as.character(gdsc_signif_g2p_grid[!is.na(gdsc_signif_g2p_grid$p.signif.adj),]$Drug_Gene)
+
+ccle_ge_dgs <- as.character(ccle_cor_res[ccle_cor_res$Spearman_Pval_GE < 0.05,]$Drug_Gene)
+ctrp_ge_dgs <- as.character(ctrp_cor_res[ctrp_cor_res$Spearman_Pval_GE < 0.05,]$Drug_Gene)
+gdsc_ge_dgs <- as.character(gdsc_cor_res[gdsc_cor_res$Spearman_Pval_GE < 0.05,]$Drug_Gene)
+
+ccle_cn_dgs <- as.character(ccle_cor_res[ccle_cor_res$Spearman_Pval_CN < 0.05,]$Drug_Gene)
+ctrp_cn_dgs <- as.character(ctrp_cor_res[ctrp_cor_res$Spearman_Pval_CN < 0.05,]$Drug_Gene)
+gdsc_cn_dgs <- as.character(gdsc_cor_res[gdsc_cor_res$Spearman_Pval_CN < 0.05,]$Drug_Gene)
+
+drug_venn_mut <- venn.diagram(list("CCLE" = ccle_mut_dgs, "CTRP" = ctrp_mut_dgs, "GDSC" = gdsc_mut_dgs), resolution = 5000, main = "A", main.pos = c(0, 1), main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 50, 120), cat.dist = c(0.001, 0.02, 0.0001), cat.cex = 1.5, cex = 1, filename = NULL, height = 4000)
+# in GDSC only
+drug_venn_mut[[7]]$label  <- paste(sort(setdiff(setdiff(gdsc_dgs, ctrp_dgs), ccle_dgs)), collapse = "\n")
+# in GDSC and CTRP only
+drug_venn_mut[[8]]$label <- paste(intersect(gdsc_dgs, ctrp_dgs), collapse = "\n")
+# in CTRP only
+drug_venn_mut[[9]]$label <- paste(sort(setdiff(setdiff(ctrp_dgs, gdsc_dgs), ccle_dgs)), collapse = "\n")
+# in CTRP and CCLE only
+drug_venn_mut[[10]]$label <- intersect(ccle_dgs, ctrp_dgs)
+
+drug_venn_ge <- venn.diagram(list("CCLE" = ccle_ge_dgs, "CTRP" = ctrp_ge_dgs, "GDSC" = gdsc_ge_dgs), resolution = 5000, main = "B", main.pos = c(0, 1), main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.001, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
+
+drug_venn_cn <- venn.diagram(list("CCLE" = ccle_cn_dgs, "CTRP" = ctrp_cn_dgs, "GDSC" = gdsc_cn_dgs), resolution = 5000, main = "C", main.pos = c(0, 1), main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(0, 0, 0), cat.dist = c(0.11, 0.11, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
+
+grid.arrange(grobTree(drug_venn_mut),
+             grobTree(drug_venn_ge),
+             grobTree(drug_venn_cn),
+             ncol = 1, 
+             heights = c(2/5, 2/5, 1/5))
+
+drugscreen_venns <- arrangeGrob(grobTree(drug_venn_mut),
+             grobTree(drug_venn_ge),
+             grobTree(drug_venn_cn),
+             ncol = 1, 
+             heights = c(2/5, 2/5, 1/5))
+ # ggsave(file = "./plots/manuscript/drugscreen_venns.pdf", drugscreen_venns) #saves g
+
+# png("./plots/manuscript/drugscreen_venn_mut.png")
+# grid.newpage()
+# grid.draw(drug_venn_mut)
+# dev.off()
 ```
@@
 
-# ggsave("./plots/manuscript/g2p_spearman_ks_res_plot.png", g2p_ks_res_plot_spearman, device = "png", dpi = 450, width = 12, height = 6, units = "in")
+# ggsave("./plots/manuscript/g2p_spearman_ks_res_plot.pdf", g2p_ks_res_plot_spearman, device = "pdf", dpi = 500, width = 12, height = 6, units = "in")
 ```

### 2019-01-22 manuscript_analysis.Rmd
identified data duplications due to manual MAF annotations, need to fix

@@
 
-Merged mutation calls (coding region, germline filtered):
+Mutation calls (coding region, germline filtered):
 ```{r, eval=FALSE}
@@
 ### Merge drug data and annotations
+
+457/3462 gene-cell line combinations have more than one mutation in the MAF file. **FIX THIS**
+```{r}
+# test <- maf_df_g2p %>% count(Hugo_Symbol, CCLE_Name)
+# test <- test[order(test$n, decreasing = TRUE),]
+```
 
@@
 
-Pearson correlations for assessing effect of gene expression and copy number on gene essentiality score and AUC.
+Pearson and Spearman correlations for assessing effect of gene expression and copy number on gene essentiality score and AUC.
+
+Example of how to describe Spearman correaltion results: ""A Spearman's correlation was run to determine the relationship between 23 groundwater uranium and TDS values.
+There was a strong, positive monotonic correlation between Uranium and TDS ( = .71, n = 23, p < .001)."
 
@@
 
-ggsave("./plots/manuscript/crispr_venn.pdf", crispr_venn)
+# ggsave("./plots/manuscript/crispr_venn.pdf", crispr_venn)
 ```
@@
 crispr_spearman_res_CN$p_log10 <- -log10(crispr_spearman_res_CN$p)
+spearman_KRAS <- rbind(filter(crispr_data_g2p, Hugo_Symbol == "KRAS") %>% summarize(p = cor.test(y = Score, x = RPKM, method = "spearman", use = "complete.obs")$p.value, corr = cor.test(y = Score, x = RPKM, method = "spearman", use = "complete.obs")$estimate, Metric = "Gene Expression"), filter(crispr_data_g2p, Hugo_Symbol == "KRAS") %>% summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value, corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate, Metric = "Copy Number"))
+
+crispr_ge_spearman_corr_inset <- ggplot(filter(crispr_data_g2p, Hugo_Symbol == "KRAS"), aes(x = RPKM, y = Score)) +
+  geom_point(pch = 21, fill = "cadetblue3", alpha = 0.6) +
+  labs(x = "KRAS Gene Expression (RPKM)", y = "CERES Score", subtitle = paste0("Spearman correlation coefficient = ", round(spearman_KRAS$corr[1], 2), " (", printp(spearman_KRAS$p[1]), ")"))
+
+crispr_cn_spearman_corr_inset <- ggplot(filter(crispr_data_g2p, Hugo_Symbol == "KRAS"), aes(x = CN, y = Score)) +
+  geom_point(pch = 21, fill = "palegreen2", alpha = 0.6) +
+  labs(x = "KRAS Copy Number (log2 ratio)", y = "CERES Score", subtitle = paste0("Spearman correlation coefficient = ", round(spearman_KRAS$corr[2], 2), " (", printp(spearman_KRAS$p[2]), ")"))
 
@@
   geom_point(aes(fill = p_log10), pch = 21, size = 5) +
-  scale_fill_gradient2(low = "white", mid = "white", high = "darkorchid4", midpoint = 1.3010299957) +
+  scale_fill_gradient2(low = "white", mid = "white", high = "deepskyblue4", midpoint = 1.3010299957) +
   coord_cartesian(ylim = c(-0.45, 0.2)) +
   theme(legend.position = "bottom", axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 10)) +
-  labs(fill = "-log10(p)", x = "Gene", y = "Spearman Correlation Coefficient (r_s)", subtitle = "CRISPR: Correlation between AUC z-score and gene expression")
+  labs(fill = "-log10(p)", x = "Gene", y = "Spearman Correlation Coefficient (r_s)") +
+  annotation_custom(ggplotGrob(crispr_ge_spearman_corr_inset), xmin = 12, xmax = 32, ymin = -0.15, ymax = -0.45) +
+  geom_curve(aes(x = 3.5, y = -0.285, xend = 13, yend = -0.16), color = "lightgray", curvature = -0.2, arrow = arrow(length = unit(0.03, "npc")))
+
 crispr_cn_spearman_corr_plot <- ggplot(data = crispr_spearman_res_CN, aes(x = Hugo_Symbol, y = corr)) +
   geom_point(aes(fill = p_log10), pch = 21, size = 5) +
-  scale_fill_gradient2(low = "white", mid = "white", high = "darkorchid4", midpoint = 1.3010299957) +
+  scale_fill_gradient2(low = "white", mid = "white", high = "green4", midpoint = 1.3010299957) +
   coord_cartesian(ylim = c(-0.45, 0.2)) +
   theme(legend.position = "bottom", axis.title.y = element_blank(), axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 10)) +
-  labs(fill = "-log10(p)", x = "Gene", y = "Spearman Correlation Coefficient (r_s)", subtitle = "CRISPR: Correlation between AUC z-score and copy number")
+  labs(fill = "-log10(p)", x = "Gene", y = "Spearman Correlation Coefficient (r_s)") +
+  annotation_custom(ggplotGrob(crispr_cn_spearman_corr_inset), xmin = 12, xmax = 32, ymin = -0.15, ymax = -0.45) +
+  geom_curve(aes(x = 2.5, y = -0.232, xend = 13, yend = -0.16), color = "lightgray", curvature = -0.2, arrow = arrow(length = unit(0.03, "npc")))
 
@@
 # in GDSC only
-drug_venn_mut[[7]]$label  <- paste(sort(setdiff(setdiff(gdsc_dgs, ctrp_dgs), ccle_dgs)), collapse = "\n")
+drug_venn_mut[[7]]$label  <- paste(sort(setdiff(setdiff(gdsc_mut_dgs, ctrp_mut_dgs), ccle_mut_dgs)), collapse = "\n")
 # in GDSC and CTRP only
-drug_venn_mut[[8]]$label <- paste(intersect(gdsc_dgs, ctrp_dgs), collapse = "\n")
+drug_venn_mut[[8]]$label <- paste(intersect(gdsc_mut_dgs, ctrp_mut_dgs), collapse = "\n")
 # in CTRP only
-drug_venn_mut[[9]]$label <- paste(sort(setdiff(setdiff(ctrp_dgs, gdsc_dgs), ccle_dgs)), collapse = "\n")
+drug_venn_mut[[9]]$label <- paste(sort(setdiff(setdiff(ctrp_mut_dgs, gdsc_mut_dgs), ccle_mut_dgs)), collapse = "\n")
 # in CTRP and CCLE only
-drug_venn_mut[[10]]$label <- intersect(ccle_dgs, ctrp_dgs)
+drug_venn_mut[[10]]$label <- intersect(ccle_mut_dgs, ctrp_mut_dgs)
 
@@
 
-# Pancancer vs. Lineage
+# Comopare pancancer vs. lineage
 

### 2019-01-24 manuscript_analysis.Rmd

@@
 maf_df <- subset(maf_raw, select = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID", "Variant_Classification", "Reference_Allele", "Tumor_Seq_Allele1", "Genome_Change"))
-maf_df$Reference_Allele_Length <- ifelse(maf_df$Reference_Allele == "-", 0, nchar(as.character(maf_df$Reference_Allele)))
-maf_df$Tumor_Seq_Allele1_Length <- nchar(as.character(maf_df$Tumor_Seq_Allele1))
+maf_df$Reference_Allele <- ifelse(maf_df$Reference_Allele == "-", 0, nchar(as.character(maf_df$Reference_Allele)))
+maf_df$Tumor_Seq_Allele1 <- nchar(as.character(maf_df$Tumor_Seq_Allele1))
+maf_df <- maf_df[maf_df$Variant_Classification != "Silent",]
 # Add Mutation_Status column
-maf_df$Mutation_Status_Nonsilent <- ifelse(maf_df$Variant_Classification == "Silent", "Wildtype", "Mutant")
-maf_df <- unique(maf_df)
+maf_df$Mutation_Status_Nonsilent <- "Mutant"
+
 saveRDS(maf_df, "./data_munging/rds/maf_df_18Q4.rds", compress = "xz")
@@
 
-```{r}
+```{r, eval=FALSE}
 ccle_data <- readRDS("./data_munging/rds/ccle_data_18Q4_g2pgenes.rds")
-ccle_data_ptmuts <- filter(ccle_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
-ccle_data_ptmuts$Keep_PtMut_Tests <- ifelse(ccle_data_ptmuts$Reference_Allele_Length == 1 | is.na(ccle_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(ccle_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
+ccle_data_ptmuts <- filter(ccle_data, Reference_Allele == 1 | Reference_Allele == 0 | is.na(Reference_Allele))
+ccle_data_ptmuts$Keep_PtMut_Tests <- ifelse(ccle_data_ptmuts$Reference_Allele == 1 | is.na(ccle_data_ptmuts$Reference_Allele), TRUE, ifelse(ccle_data_ptmuts$Tumor_Seq_Allele1 == 1, TRUE, FALSE))
 ccle_data_ptmuts <- filter(ccle_data_ptmuts, Keep_PtMut_Tests == TRUE)
+ccle_data_ptmuts <- subset(ccle_data_ptmuts, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, Genome_Change, Keep_PtMut_Tests))
 ccle_data_ptmuts$Dataset <- "CCLE"
 ccle_data_ptmuts$Hugo_Symbol <- ordered(ccle_data_ptmuts$Hugo_Symbol, levels = g2p_genes)
+ccle_data_ptmuts <- unique(ccle_data_ptmuts)
+saveRDS(ccle_data_ptmuts, "./data_munging/rds/ccle_data_18Q4_g2pgenes_ptmuts.rds", compress = "xz")
 
 ctrp_data <- readRDS("./data_munging/rds/ctrp_data_18Q4_g2pgenes.rds")
-ctrp_data_ptmuts <- filter(ctrp_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
-ctrp_data_ptmuts$Keep_PtMut_Tests <- ifelse(ctrp_data_ptmuts$Reference_Allele_Length == 1 | is.na(ctrp_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(ctrp_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
+ctrp_data_ptmuts <- filter(ctrp_data, Reference_Allele == 1 | Reference_Allele == 0 | is.na(Reference_Allele))
+ctrp_data_ptmuts$Keep_PtMut_Tests <- ifelse(ctrp_data_ptmuts$Reference_Allele == 1 | is.na(ctrp_data_ptmuts$Reference_Allele), TRUE, ifelse(ctrp_data_ptmuts$Tumor_Seq_Allele1 == 1, TRUE, FALSE))
 ctrp_data_ptmuts <- filter(ctrp_data_ptmuts, Keep_PtMut_Tests == TRUE)
+ctrp_data_ptmuts <- subset(ctrp_data_ptmuts, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, Genome_Change, Keep_PtMut_Tests))
 ctrp_data_ptmuts$Dataset <- "CTRP"
 ctrp_data_ptmuts$Hugo_Symbol <- ordered(ctrp_data_ptmuts$Hugo_Symbol, levels = g2p_genes)
+ctrp_data_ptmuts <- unique(ctrp_data_ptmuts)
+saveRDS(ctrp_data_ptmuts, "./data_munging/rds/ctrp_data_18Q4_g2pgenes_ptmuts.rds", compress = "xz")
 
 gdsc_data <- readRDS("./data_munging/rds/gdsc_data_18Q4_g2pgenes.rds")
-gdsc_data_ptmuts <- filter(gdsc_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
-gdsc_data_ptmuts$Keep_PtMut_Tests <- ifelse(gdsc_data_ptmuts$Reference_Allele_Length == 1 | is.na(gdsc_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(gdsc_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
+gdsc_data_ptmuts <- filter(gdsc_data, Reference_Allele == 1 | Reference_Allele == 0 | is.na(Reference_Allele))
+gdsc_data_ptmuts$Keep_PtMut_Tests <- ifelse(gdsc_data_ptmuts$Reference_Allele == 1 | is.na(gdsc_data_ptmuts$Reference_Allele), TRUE, ifelse(gdsc_data_ptmuts$Tumor_Seq_Allele1 == 1, TRUE, FALSE))
 gdsc_data_ptmuts <- filter(gdsc_data_ptmuts, Keep_PtMut_Tests == TRUE)
+gdsc_data_ptmuts <- subset(gdsc_data_ptmuts, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, Genome_Change, Keep_PtMut_Tests))
 gdsc_data_ptmuts$Dataset <- "GDSC"
 gdsc_data_ptmuts$Hugo_Symbol <- ordered(gdsc_data_ptmuts$Hugo_Symbol, levels = g2p_genes)
+gdsc_data_ptmuts <- unique(gdsc_data_ptmuts)
+saveRDS(gdsc_data_ptmuts, "./data_munging/rds/gdsc_data_18Q4_g2pgenes_ptmuts.rds", compress = "xz")
+```
+
+```{r}
+ccle_data_ptmuts <- readRDS("./data_munging/rds/ccle_data_18Q4_g2pgenes_ptmuts.rds")
+ctrp_data_ptmuts <- readRDS("./data_munging/rds/ctrp_data_18Q4_g2pgenes_ptmuts.rds")
+gdsc_data_ptmuts <- readRDS("./data_munging/rds/gdsc_data_18Q4_g2pgenes_ptmuts.rds")
 
@@
 gdsc_data_g2p_grid$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p_grid$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-```
-
-```{r}
+
+# Testing
 test_ccle <- ccle_data_ptmuts %>% group_by(Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()
@@
 
+How many datasets screen each G2P drug?
 ```{r}
@@
 saveRDS(crispr_data, "./../htscreens_giant_files/crispr_data_18Q4.rds", compress = "xz")
+
+# Takes a really long time to run (4+ hours)
+# crispr_data_ptmuts <- filter(crispr_data, Reference_Allele == 1 | Reference_Allele == 0 | is.na(Reference_Allele))
+# crispr_data_ptmuts$Keep_PtMut_Tests <- ifelse(crispr_data_ptmuts$Reference_Allele == 1 | is.na(crispr_data_ptmuts$Reference_Allele), TRUE, ifelse(crispr_data_ptmuts$Tumor_Seq_Allele1 == 1, TRUE, FALSE))
+# crispr_data_ptmuts <- filter(crispr_data_ptmuts, Keep_PtMut_Tests == TRUE)
+# crispr_data_ptmuts <- subset(crispr_data_ptmuts, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, Genome_Change, Keep_PtMut_Tests))
+# crispr_data_ptmuts <- unique(crispr_data_ptmuts)
+# saveRDS(crispr_data_ptmuts, "./data_munging/rds/crispr_data_18Q4_ptmuts.rds", compress = "xz")
 ```
@@
 crispr_data <- readRDS("./../htscreens_giant_files/crispr_data_18Q4.rds")
-crispr_data_ptmuts <- filter(crispr_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
-crispr_data_ptmuts$Keep_PtMut_Tests <- ifelse(crispr_data_ptmuts$Reference_Allele_Length == 1 | is.na(crispr_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(crispr_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
-crispr_data_ptmuts <- filter(crispr_data_ptmuts, Keep_PtMut_Tests == TRUE)
+# crispr_data_ptmuts <- readRDS("./../htscreens_giant_files/crispr_data_18Q4_ptmuts.rds")
+# 
+# crispr_data_ptmuts <- filter(crispr_data, Hugo_Symbol %in% g2p_genes)
+# crispr_data_ptmuts <- filter(crispr_data_ptmuts, Reference_Allele == 1 | Reference_Allele == 0 | is.na(Reference_Allele))
+# crispr_data_ptmuts$Keep_PtMut_Tests <- ifelse(crispr_data_ptmuts$Reference_Allele == 1 | is.na(crispr_data_ptmuts$Reference_Allele), TRUE, ifelse(crispr_data_ptmuts$Tumor_Seq_Allele1 == 1, TRUE, FALSE))
+# crispr_data_ptmuts <- filter(crispr_data_ptmuts, Keep_PtMut_Tests == TRUE)
+# crispr_data_ptmuts <- subset(crispr_data_ptmuts, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, Genome_Change, Keep_PtMut_Tests))
+# crispr_data_ptmuts <- unique(crispr_data_ptmuts)
 

### 2019-01-24 manuscript_analysis.Rmd
updated analyses in Rmd

@@
 ```{r}
+ccle_data <- readRDS("./data_munging/rds/ccle_data_18Q4_g2pgenes.rds")
+ctrp_data <- readRDS("./data_munging/rds/ctrp_data_18Q4_g2pgenes.rds")
+gdsc_data <- readRDS("./data_munging/rds/gdsc_data_18Q4_g2pgenes.rds")
 ccle_data_ptmuts <- readRDS("./data_munging/rds/ccle_data_18Q4_g2pgenes_ptmuts.rds")
@@
 crispr_data <- readRDS("./../htscreens_giant_files/crispr_data_18Q4.rds")
+# Run next two lines only if the file was made (see end of the last chunk)
 # crispr_data_ptmuts <- readRDS("./../htscreens_giant_files/crispr_data_18Q4_ptmuts.rds")
-# 
-# crispr_data_ptmuts <- filter(crispr_data, Hugo_Symbol %in% g2p_genes)
-# crispr_data_ptmuts <- filter(crispr_data_ptmuts, Reference_Allele == 1 | Reference_Allele == 0 | is.na(Reference_Allele))
-# crispr_data_ptmuts$Keep_PtMut_Tests <- ifelse(crispr_data_ptmuts$Reference_Allele == 1 | is.na(crispr_data_ptmuts$Reference_Allele), TRUE, ifelse(crispr_data_ptmuts$Tumor_Seq_Allele1 == 1, TRUE, FALSE))
-# crispr_data_ptmuts <- filter(crispr_data_ptmuts, Keep_PtMut_Tests == TRUE)
-# crispr_data_ptmuts <- subset(crispr_data_ptmuts, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, Genome_Change, Keep_PtMut_Tests))
-# crispr_data_ptmuts <- unique(crispr_data_ptmuts)
+# crispr_data_g2p <- filter(crispr_data_ptmuts, Hugo_Symbol %in% g2p_genes)
 
 # Filter CRISPR for G2P genes in G2P
-crispr_data_g2p <- filter(crispr_data_ptmuts, Hugo_Symbol %in% g2p_genes)
+crispr_data_ptmuts <- filter(crispr_data, Hugo_Symbol %in% g2p_genes)
+# Filter G2P CRISPR for point mutations
+crispr_data_ptmuts <- filter(crispr_data_ptmuts, Reference_Allele == 1 | Reference_Allele == 0 | is.na(Reference_Allele))
+crispr_data_ptmuts$Keep_PtMut_Tests <- ifelse(crispr_data_ptmuts$Reference_Allele == 1 | is.na(crispr_data_ptmuts$Reference_Allele), TRUE, ifelse(crispr_data_ptmuts$Tumor_Seq_Allele1 == 1, TRUE, FALSE))
+crispr_data_ptmuts <- filter(crispr_data_ptmuts, Keep_PtMut_Tests == TRUE)
+crispr_data_ptmuts <- subset(crispr_data_ptmuts, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, Genome_Change, Keep_PtMut_Tests))
+crispr_data_g2p <- unique(crispr_data_ptmuts)
 crispr_data_g2p$Hugo_Symbol <- factor(crispr_data_g2p$Hugo_Symbol, levels = g2p_genes)
@@
 ```{r, eval=FALSE}
-ccle <- read.delim("./data_munging/data_drug_auc_ccle_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
-ccle <- merge(drug_meta, ccle, by = "CID")
-ccle_melt <- melt(ccle, id.vars = c("CID", "Drug"), measure.vars = colnames(ccle)[3:ncol(ccle)], variable.name = "accession_id", value.name = "AUC")
-ccle_grid <- expand.grid("accession_id" = unique(ccle_melt$accession_id), "Hugo_Symbol" = as.character(unique(crispr_data$Hugo_Symbol)))
-system.time({ ccle_data_allgenes <- WilcoxonByDrugAllGenes(ccle_melt, ccle_grid, "CCLE") })
-saveRDS(ccle_data_allgenes, "./data_munging/rds/ccle_data_18Q3_allgenes.rds", compress = "xz")
+# ccle <- read.delim("./data_munging/data_drug_auc_ccle_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
+# ccle <- merge(drug_meta, ccle, by = "CID")
+# ccle_melt <- melt(ccle, id.vars = c("CID", "Drug"), measure.vars = colnames(ccle)[3:ncol(ccle)], variable.name = "accession_id", value.name = "AUC")
+# ccle_grid <- expand.grid("accession_id" = unique(ccle_melt$accession_id), "Hugo_Symbol" = as.character(unique(crispr_data$Hugo_Symbol)))
+# system.time({ ccle_data_allgenes <- WilcoxonByDrugAllGenes(ccle_melt, ccle_grid, "CCLE") })
+# saveRDS(ccle_data_allgenes, "./data_munging/rds/ccle_data_18Q3_allgenes.rds", compress = "xz")
 
@@
 
-```{r}
-test <- p.adjust(ccle_signif_g2p$p, method = "BH")
-```
-
 Test G2P genes in lineage-grouped context:
@@
 ```{r, eval=FALSE}
-ctrp <- read.delim("./data_munging/data_drug_auc_ctrp_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
-ctrp <- merge(drug_meta, ctrp, by = "CID")
-ctrp_melt <- melt(ctrp, id.var  s = c("CID", "Drug"), measure.vars = colnames(ctrp)[3:ncol(ctrp)], variable.name = "accession_id", value.name = "AUC")
-ctrp_grid <- expand.grid("accession_id" = unique(ctrp_melt$accession_id), "Hugo_Symbol" = as.character(unique(crispr_data$Hugo_Symbol)))
-ctrp_data_allgenes <- WilcoxonByDrugAllGenes(ctrp_melt, ctrp_grid, "CTRP")
-saveRDS(ctrp_data_allgenes, "./data_munging/rds/ctrp_data_18Q3_allgenes.rds", compress = "xz")
+# ctrp <- read.delim("./data_munging/data_drug_auc_ctrp_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
+# ctrp <- merge(drug_meta, ctrp, by = "CID")
+# ctrp_melt <- melt(ctrp, id.var  s = c("CID", "Drug"), measure.vars = colnames(ctrp)[3:ncol(ctrp)], variable.name = "accession_id", value.name = "AUC")
+# ctrp_grid <- expand.grid("accession_id" = unique(ctrp_melt$accession_id), "Hugo_Symbol" = as.character(unique(crispr_data$Hugo_Symbol)))
+# ctrp_data_allgenes <- WilcoxonByDrugAllGenes(ctrp_melt, ctrp_grid, "CTRP")
+# saveRDS(ctrp_data_allgenes, "./data_munging/rds/ctrp_data_18Q3_allgenes.rds", compress = "xz")
 ```
@@
 ```{r, eval=FALSE}
-gdsc <- read.delim("./data_munging/data_drug_auc_gdsc_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
-gdsc <- merge(drug_meta, gdsc, by = "CID")
-gdsc_melt <- melt(gdsc, id.vars = c("CID", "Drug"), measure.vars = colnames(gdsc)[3:ncol(gdsc)], variable.name = "accession_id", value.name = "AUC")
-gdsc_grid <- expand.grid("accession_id" = unique(gdsc_melt$accession_id), "Hugo_Symbol" = as.character(unique(crispr_data$Hugo_Symbol)))
-system.time({ gdsc_data_allgenes <- WilcoxonByDrugAllGenes(gdsc_melt, gdsc_grid, "GDSC") })
-saveRDS(gdsc_data_allgenes, "./data_munging/rds/gdsc_data_18Q3_allgenes.rds", compress = "xz")
+# gdsc <- read.delim("./data_munging/data_drug_auc_gdsc_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
+# gdsc <- merge(drug_meta, gdsc, by = "CID")
+# gdsc_melt <- melt(gdsc, id.vars = c("CID", "Drug"), measure.vars = colnames(gdsc)[3:ncol(gdsc)], variable.name = "accession_id", value.name = "AUC")
+# gdsc_grid <- expand.grid("accession_id" = unique(gdsc_melt$accession_id), "Hugo_Symbol" = as.character(unique(crispr_data$Hugo_Symbol)))
+# system.time({ gdsc_data_allgenes <- WilcoxonByDrugAllGenes(gdsc_melt, gdsc_grid, "GDSC") })
+# saveRDS(gdsc_data_allgenes, "./data_munging/rds/gdsc_data_18Q3_allgenes.rds", compress = "xz")
 ```
@@
 
-```{r}
+```{r, warning=FALSE}
 crispr_pearson_res_GE <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>%
@@
 
-```{r}
+```{r, warning=FALSE}
 g2p_druggene_tally <- g2p_filt %>% group_by(Drug_Gene) %>% tally() %>% drop_na()
@@
 
-# ggsave("./plots/manuscript/crispr_venn.pdf", crispr_venn)
+ggsave("./plots/manuscript/crispr_venn.pdf", crispr_venn)
 ```
@@
 Spearman correlations for gene expression and copy number:
-```{r fig.height=6, fig.width=12}
+```{r fig.height=8, fig.width=16}
 crispr_spearman_res_GE <- transform(crispr_spearman_res_GE, Hugo_Symbol = reorder(Hugo_Symbol, corr)) 
@@
   annotation_custom(ggplotGrob(crispr_ge_spearman_corr_inset), xmin = 12, xmax = 32, ymin = -0.15, ymax = -0.45) +
-  geom_curve(aes(x = 3.5, y = -0.285, xend = 13, yend = -0.16), color = "lightgray", curvature = -0.2, arrow = arrow(length = unit(0.03, "npc")))
+  geom_curve(aes(x = 3.5, y = -0.27, xend = 14, yend = -0.165), color = "lightgray", curvature = -0.2, arrow = arrow(length = unit(0.03, "npc")))
 
@@
   annotation_custom(ggplotGrob(crispr_cn_spearman_corr_inset), xmin = 12, xmax = 32, ymin = -0.15, ymax = -0.45) +
-  geom_curve(aes(x = 2.5, y = -0.232, xend = 13, yend = -0.16), color = "lightgray", curvature = -0.2, arrow = arrow(length = unit(0.03, "npc")))
+  geom_curve(aes(x = 2.5, y = -0.232, xend = 14, yend = -0.165), color = "lightgray", curvature = -0.2, arrow = arrow(length = unit(0.03, "npc")))
 
@@
 crispr_spearman_corr_plot
-# ggsave("./plots/manuscript/crispr_spearman_corr_plot.png", crispr_spearman_corr_plot, device = "png", dpi = 450, width = 12, height = 6, units = "in")
+# ggsave("./plots/manuscript/crispr_spearman_corr_plot.png", crispr_spearman_corr_plot, device = "png", dpi = 450, width = 16, height = 8, units = "in")
 ```
@@
   scale_y_continuous(breaks = seq(0, 35, by = 5), labels = seq(0, 35, by = 5)) +
-  coord_cartesian(ylim = c(0, 35)) +
+  coord_cartesian(ylim = c(0, 25)) +
   geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
@@
   facet_grid(Dataset ~ Metric) +
-  coord_cartesian(ylim = c(0, 35)) +
+  coord_cartesian(ylim = c(0, 25)) +
   geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
@@
   facet_grid(Dataset ~ Metric) +
+  coord_cartesian(ylim = c(0, 30)) +
   scale_y_continuous(breaks = seq(0, 50, by = 5), labels = seq(0, 50, by = 5)) +
@@
   scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
-  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
+  theme(legend.position = "none", axis.title.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
+  annotate(geom = "text", x = 0, y = 30, label = c("afatinib_ERBB2 and lapatinib_ERBB2\n-log10(p-value) >> 100", ""), size = 3) +
   labs(x = "Spearman's rank correlation coefficient (r_s)")
@@
   theme(legend.position = "none", plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
+  annotate(geom = "text", x = 0, y = 30, label = c("", "", "", "", "afatinib_ERBB2 and lapatinib_ERBB2\n-log10(p-value) >> 100", ""), size = 3) +
   labs(x = "Pearson correlation coefficient (r)", y = "-log10(p-value)")
@@
 ctrp_grid_summary_ge_corr <- cor.test(y = ctrp_grid_summary_data$AUC, x = ctrp_grid_summary_data$RPKM, method = "pearson", use = "complete.obs")
-ctrp_grid_summary_ge_corr_text <- paste0("r(", ctrp_grid_summary_ge_corr$parameter, ") = ", round(ctrp_grid_summary_ge_corr$estimate, 2), "\np ", ifelse(round(ctrp_grid_summary_ge_corr$p.value, 3) == 0, "< 0.001", paste0("= ", round(ctrp_grid_summary_ge_corr$p.value, 3))))
+ctrp_grid_summary_ge_corr_text <- paste0("r(", ctrp_grid_summary_ge_corr$parameter, ") = ", formatC(ctrp_grid_summary_ge_corr$estimate, digits = 2, format = "f"), "\np ", ifelse(round(ctrp_grid_summary_ge_corr$p.value, 3) == 0, "< 0.001", paste0("= ", round(ctrp_grid_summary_ge_corr$p.value, 3))))
 
@@
 
-```{r}
+```{r, warning=FALSE}
+# cannot compute exact p-value with ties??????
+
 ccle_data_g2p$G2P_DGL <- ifelse(ccle_data_g2p$Drug_Gene_Lin %in% g2p_dgls, "Yes", "No")
@@
 
-# Comopare pancancer vs. lineage
+# Compare pancancer vs. lineage
 
@@
 # ggsave("./plots/manuscript/compare_cn_plot.png", compare_cn_plot, device = "png", dpi = 450, width = 12, height = 12, units = "in")
-```
-
-```{r}
-test <- filter(compare_mut, Drug_Gene == "nilotinib_ABL1" & Dataset == "CCLE" & group_general_lineage_name == "bone cancer")
 ```

### 2019-01-24 manuscript.tex
updated manuscript_analysis and manuscript

@@
 
-We derived our clinical associations from a new project conducted by the
+To curate an evidence-based list of these clinical biomarkers, we
+utilized a new oncological data aggregation project conducted by the
 Variant Interpretation for Cancer Consortium (VICC;
@@
 subsequent analyses, constituting 57 unique drugs and 34 unique genes in
-88 distinct level-A combinations (\emph{Figure 1A}). The number of
-level-A interpretations per drug ranged from 1 to 176 (\(M =\) 15.68,
-\(SD =\) 34.63), 1 to 264 (\(M =\) 26.24, \(SD =\) 61.58) per gene, and
-for each level-A drug-gene combination, the range was 1 to 103 (\(M =\)
-10.14, \(SD =\) 19.80). These unique drugs, genes, and combinations are
-hereafter referred to as G2P drugs, G2P genes, and G2P associations.
-Filtering our screening datasets by these clinical criteria yields
-panels of potentially clinically relevant omic features. Of the 57
-unique G2P drugs, 37 of them were screened in at least one of the drug
-screen datasets, 17 drugs were screened in at least two of the three
-datasets, and only 3 were screened in all three datasets. The remaining
-20 un-screened G2P drugs suggests an incompleteness of these drug
-screens, though these projects frequently release new screening data
-that may include these drugs in future releases.
+88 distinct level-A combinations (\emph{Figure 1A: Pink heatmap}). The
+number of level-A interpretations per drug ranged from 1 to 176 (\(M =\)
+15.68, \(SD =\) 34.63), 1 to 264 (\(M =\) 26.24, \(SD =\) 61.58) per
+gene, and for each level-A drug-gene combination, the range was 1 to 103
+(\(M =\) 10.14, \(SD =\) 19.80). These unique drugs, genes, and
+combinations are hereafter referred to as G2P drugs, G2P genes, and G2P
+associations. Filtering our screening datasets by these clinical
+criteria yields panels of potentially clinically relevant omic features.
+Of the 57 unique G2P drugs, 37 of them were screened in at least one of
+the drug screen datasets, 17 drugs were screened in at least two of the
+three datasets, and only 3 were screened in all three datasets. The
+remaining 20 un-screened G2P drugs suggests an incompleteness of these
+drug screens, though these projects frequently release new screening
+data that may include these drugs in future releases.
 
@@
 \textless{} 5\%, CCLE yielded no significant correlations (Wilcoxon
-rank-sum tests, \(p_k = 2.1^{-4}\)), though the most significant G2P
-association was selumetinib-\emph{KRAS} (\(p_{adj} = 1.9^{-3}\)). In
+rank-sum tests, \(p_k = 1.2^{-4}\)), though the most significant G2P
+association was selumetinib-\emph{KRAS} (\(p_{adj} = 1.1^{-3}\)). In
 CTRP, AUC from 3 drug-gene associations correlated with the gene's
-mutation status (\(p_k = 4.5^{-3}\)): selumetinib-\emph{KRAS}
-(\(p_{adj} = 4.4^{-8}\)), vemurafenib-\emph{BRAF}
-(\(p_{adj} = 4.4^{-8}\)), and dabrafenib-\emph{BRAF}
-(\(p_{adj} = 7.7^{-5}\)). Dabrafenib-\emph{BRAF}
-(\(p_{adj} = 8.6^{-11}\)) and trametinib-\emph{BRAF}
-(\(p_{adj} = 4.2^{-6}\)) were significant in GDSC (\(p_k = 2.3^{-3}\)).
+mutation status (\(p_k = 2.6^{-3}\)): vemurafenib-\emph{BRAF}
+(\(p_{adj} = 5.8^{-9}\)), selumetinib-\emph{KRAS}
+(\(p_{adj} = 4.6^{-8}\)), and dabrafenib-\emph{BRAF}
+(\(p_{adj} = 8.3^{-5}\)). Dabrafenib-\emph{BRAF}
+(\(p_{adj} = 3.2^{-11}\)) was the only significant association in GDSC
+(\(p_k = 2.6^{-6}\)).
 
@@
 similar Wilcoxon rank-sum tests for all pairwise combinations of G2P
-genes and drugs tested in the three drug screens (\emph{Figures 1B and
-2A}). At an unadjusted \(\alpha = 0.05\), the tests revealed that in
-CCLE, AUC significantly correlated with mutation status for 18 out of
-170 (10.59\%) tested drug-gene combinations were significantly
-different, 135 out of 918 (14.71\%) were significantly different for
-CTRP, and 89 out of 850 (10.47\%) for GDSC.
+genes and drugs tested in the three drug screens (\emph{Figures 1B:
+Green heatmaps}). At an unadjusted \(\alpha = 0.05\), the tests revealed
+that in CCLE, AUC significantly correlated with mutation status for 14
+out of 170 (8.24\%) tested drug-gene combinations were significantly
+different, 93 out of 918 (10.13\%) were significantly different for
+CTRP, and 72 out of 850 (8.47\%) for GDSC.
 
 Controlling for a FDR \textless{} 5\%, selumetinib-\emph{BRAF}
-(\(p_{adj} = 1.4^{-10}\)) was the only significant drug-gene combination
-tested in CCLE (\(p_k = 7.9^{-4}\)). CTRP (\(p_k = 6.5^{-4}\)) yielded 5
+(\(p_{adj} = 2.9^{-10}\)) was the only significant drug-gene combination
+tested in CCLE (\(p_k = 1.2^{-4}\)). CTRP (\(p_k = 3.9^{-4}\)) yielded 4
 significant combinations, one of which was selumetinib-\emph{BRAF}.
-There were 3 significant G2P associations in the GDSC dataset
-(\(p_k = 9.5^{-5}\)). Of all the significant correlations between
+There were 2 significant G2P associations in the GDSC dataset
+(\(p_k = 2.3^{-4}\)). Of all the significant correlations between
 mutation status and AUC across datasets, the only genes represented were
-\emph{KRAS} and \emph{BRAF} (Figure~\ref{fig:drug-venn}). Of the 7
-significant drug-gene associations across datasets, 4 were G2P
-associations. The remaining 3 associations were selumetinib-\emph{BRAF},
-trametinib-\emph{KRAS}, and pazopanib-\emph{BRAF}.
+\emph{KRAS} and \emph{BRAF} (Figure~\ref{fig:drug-venn}). Of the 5
+significant drug-gene associations across datasets, 3 were G2P
+associations. The remaining 2 associations were selumetinib-\emph{BRAF}
+and trametinib-\emph{KRAS}.
 
@@
 \includegraphics{./plots/manuscript/drugscreen_venns.pdf}
-\caption{\label{fig:drug-venn}Overlap of drug-gene associations drawn from all
-pairwise combinations of G2P drugs and G2P genes whose drug effects
+\caption{\label{fig:drug-venn}\textbf{Overlap of significant drug-gene associations
+from CCLE, CTRP, and GDSC}. Overlap of drug-gene associations drawn from
+all pairwise combinations of G2P drugs and G2P genes whose drug effects
 significantly correlated with (\textbf{A}) mutation status, (\textbf{B})
@@
 
-Prior to correction for an FDR of 5\%, no DGLs were identified in the
-CCLE screen when using mutation status as a correlate (\(n =\) 7, 2 DGLs
-were not analyzed due to lack of mutation annotations in \emph{UGT1A1}
-in \enquote{cancer} lineages), but CTRP (\(n =\) 48) and GDSC (\(n =\)
-39) identified 6 and 5, respectively, in skin cancer, lung cancer, and
-cancer. After Benjamini-Hochberg FDR correction, none of the datasets
-yielded significant DGL interactions.
+Prior to correction for an FDR of 5\%, 1 DGL,
+selumetinib-\emph{KRAS}-lung cancer, was identified in the CCLE screen
+when using mutation status as a correlate (\(n =\) 7, 2 DGLs were not
+analyzed due to lack of mutation annotations in \emph{UGT1A1} in
+\enquote{cancer} lineages), but CTRP (\(n =\) 48) and GDSC (\(n =\) 39)
+identified 5 and 4, respectively, in skin cancer, lung cancer, and
+cancer lineages. After Benjamini-Hochberg FDR correction, none of the
+datasets yielded significant DGL interactions.
 
 \begin{quote}
-\textbf{(???) KS test results}
+\textbf{(???) KS test results: Need to flesh out this section}
 \end{quote}
@@
 \includegraphics{./plots/manuscript/g2p_spearman_ks_res_plot.pdf}
-\caption{\label{fig:ksplot}Comparison of Spearman correlation coefficients (\(r_s\))
-derived from copy number (log\(_2\) ratio), gene expression (RPKM), and
-AUC z-scores from G2P drug-gene associations. Coefficients were grouped
-by whether or not the associated lineage for each comparison was in a
-G2P drug-gene-lineage association or not. Distributions of these grouped
-coefficients were compared using Kolmogorov-Smirnov tests.}
+\caption{\label{fig:ksplot}\textbf{Comparison of drug-gene AUC vs.~gene expression and
+vs.~copy number in G2P and non-G2P cell lines}. Comparison of Spearman
+correlation coefficients (\(r_s\)) derived from copy number (log\(_2\)
+ratio) vs.~AUC z-scores and gene expression (RPKM) vs.~AUC z-scores for
+G2P drug-gene associations. Correlation coefficients were grouped by
+whether or not the associated lineage for each comparison was in a
+level-A G2P drug-gene-lineage association or not. The distributions of
+these grouped coefficients were compared using Kolmogorov-Smirnov tests
+to identify whether correlations in G2P lineages were distinct from
+correlations in non-G2P lineages.}
 \end{figure}
@@
 \centering
+\includegraphics{./plots/manuscript/crispr_spearman_corr_plot.pdf}
+\caption{\label{fig:crispr-waterfall}Stuff stuff stuff!}
+\end{figure}
+
+\begin{figure}
+\centering
 \includegraphics{./plots/manuscript/crispr_venn.pdf}
-\caption{\label{fig:crispr-venn}Overlap of genes whose gene expression and/or copy
-number significantly correlated with CERES score.}
+\caption{\label{fig:crispr-venn}\textbf{CRISPR sceen results}. Overlap of genes whose
+gene expression and/or copy number significantly correlated with CERES
+score (Spearman rank-order correlations).}
 \end{figure}
@@
 When we don't account for lineage, Wilcoxon rank-sum tests
-(\(p_k = 5.1^{-3}\), FDR \textless{} 5\%) revealed that mutations in 2
-genes significantly correlated with CERES score: \emph{KRAS}
-(\(p_{adj} = 2.6^{-37}\)) and \emph{BRAF} (\(p_{adj} = 8.2^{-18}\)).
-Gene expression (RPKM) of 12 out of 33 (36.36\%) G2P genes significantly
+(\(p_k = 4.1^{-17}\), FDR \textless{} 5\%) revealed that mutations in 1
+gene significantly correlated with CERES score: \emph{KRAS}
+(\(p_{adj} = 3.7^{-37}\)). Gene expression (RPKM) of 13 out of 33
+(39.39\%, Spearman rank-order correlations) G2P genes significantly
 correlated with CERES score, as did copy number (log2-ratio) for 12 out
-of 33 (36.36\%) G2P genes (Figure~\ref{fig:crispr-venn}).
-
-For the purpose of comparison to the drug screen data, if we treat
-CRISPR knockdown like a small-molecule drug, then these results are more
-comprehensive than the results from CCLE, CTRP, and GDSC (Table 2).
-
-\begin{itemize}
-\tightlist
-\item
-  Lineage?
-\end{itemize}
+of 33 (36.36\%, Spearman rank-order correlations) G2P genes
+(Figure~\ref{fig:crispr-waterfall}). We see moderate overlap between
+these genes whose CERES scores significantly correlated with gene
+expression and with copy number (Figure~\ref{fig:crispr-venn}). For the
+purpose of comparison to the drug screen data, if we treat CRISPR
+knockdown like a small-molecule drug, then these results are more
+comprehensive than the results from CCLE, CTRP, and GDSC.
+
+\begin{quote}
+\textbf{(???) Lineage????}
+\end{quote}
 
@@
 
-In a lineage-agnostic context of the CRISPR screen, ERBB2 gene
-essentiality score had a significant negative correlation with ERBB2
-gene expression (\(p < 10^{-12}\), \(r = -0.31\)) and ERBB2 copy number
-(\(p < 10^{-15}\), \(r = -0.34\)) (\emph{Figure \#\#2}). Similarly, MET
-gene essentiality also correlated with both MET gene expression
-(\(p < 10^{-12}\), \(r = -0.31\)) and copy number (\(p < 10^{-8}\),
-\(r = -0.25\)). Notably, BRCA1 also significantly correlated with both
-gene expression (\(p < 0.001\), \(r = 0.16\)) and copy number
-(\(p < 0.01\), \(r = 0.14\)). BRCA2 significantly correlated with all
-three of the genomic features tested: gene expression (\(p < 0.05\),
-\(r = 0.10\)), copy number (\(p < 10^{-7}\), \(r = 0.23\)), and mutation
-status (\(p < 0.001\)).
+In a lineage-agnostic context of the CRISPR screen, \emph{ERBB2} gene
+essentiality score had significant negative correlations with
+\emph{ERBB2} gene expression (\(p = 8.3^{-12}\), \(r_s =\) -0.30) and
+\emph{ERBB2} copy number (\(p = 3.8^{-10}\), \(r_s =\) -0.27)
+(\emph{Figure \#\#2}). Notably, gene essentiality of \emph{MET}, which
+is known to have copy number alterations in some cancers (An et al.,
+2014; J. H. Kim, Kim, \& Kim, 2018), did not significantly correlate
+with \emph{MET} gene expression nor \emph{MET} copy number. \emph{BRCA1}
+gene essentiality also significantly correlated with both \emph{BRCA1}
+gene expression (\(p = 4.7^{-6}\), \(r_s =\) 0.20) and \emph{BRCA1} copy
+number (\(p = 1.1^{-3}\), \(r_s =\) 0.14). \emph{BRCA2} gene
+essentiality significantly correlated \emph{BRCA2} gene expression
+(\(p = 6.6^{-7}\), \(r_s =\) 0.22) but not \emph{BRCA2} copy number.
 
@@
 
-\textbf{Should we do this?}
+\begin{quote}
+\textbf{(???) Should we do this?}
+\end{quote}
 
@@
 Public 18Q4 release via the DepMap data portal
-(\url{https://depmap.org/portal/download/}) (Broad DepMap, 2018). Gene
+(\url{https://depmap.org/portal/download/}) (DepMap, 2018). Gene
 expression data was retrieved from the DepMap Public 18Q3 release (Broad
@@
 processing and screening methods are available from the figshare record
-(Broad DepMap, 2018) and the original publication of CERES, the
-algorithm that computes inferred gene dependency scores (Meyers et al.,
-2017). The DepMap releases new data quarterly, with the current data set
-being the 18Q4 release. This release has 175 more cell lines than the
-original data release that was published with CERES (dataset:
-gene\_effect.csv, accessed 15 November 2018).
+(DepMap, 2018) and the original publication of CERES, the algorithm that
+computes inferred gene dependency scores (Meyers et al., 2017). The
+DepMap releases new data quarterly, with the current data set being the
+18Q4 release. This release has 175 more cell lines than the original
+data release that was published with CERES (dataset: gene\_effect.csv,
+accessed 15 November 2018).
 
@@
 The CCLE generated genomic copy number (CN) data using the Affymetrix
-Genome-Wide Human SNP Array 6.0 and GenePattern pipeline (The Cancer
-Genome Atlas Research Network, 2008) and normalized segmented CN
-log2-ratios for 23,299 genes across 1,098 cell lines using circular
-binary segmentation (Olshen, Venkatraman, Lucito, \& Wigler, 2004)
-(dataset: public\_18Q4\_gene\_cn.csv, accessed 15 November 2018).
+Genome-Wide Human SNP Array 6.0 and GenePattern pipeline (Network, 2008)
+and normalized segmented CN log2-ratios for 23,299 genes across 1,098
+cell lines using circular binary segmentation (Olshen, Venkatraman,
+Lucito, \& Wigler, 2004) (dataset: public\_18Q4\_gene\_cn.csv, accessed
+15 November 2018).
 
@@
 2007) kernel within a localhost Jupyter (v5.2.2) notebook (Kluyver et
-al., 2016). All other analyses were conducted in R (v3.5.0) (R
-Development Core Team, 2010, \url{https://www.R-project.org/}) in an
-RStudio environment (v1.1.447) (RStudio, 2012). All other plots were
-drawn using the ggplot2 (v3.0.0) R package (Wickham, 2016).
+al., 2016). All other analyses were conducted in R (v3.5.0) (R. D. C.
+Team, 2010, \url{https://www.R-project.org/}) in an RStudio environment
+(v1.1.447) (RStudio, 2012). All other plots were drawn using the ggplot2
+(v3.0.0) R package (Wickham, 2016).
 
@@
 For computing Spearman correlation coefficients, we used the
-\texttt{cor.test} base R package. If there were 3 or fewer data points,
-then the correlation was not done and a value of \texttt{NA} was
-supplied.
+\texttt{cor.test} function from the \texttt{stats} package. If there
+were 3 or fewer data points, then the correlation was not done and a
+value of \texttt{NA} was supplied.
 
@@
 
+\hypertarget{ref-an2014}{}
+An, X., Wang, F., Shao, Q., Wang, F.-H., Wang, Z.-Q., Chen, C., \ldots{}
+Li, Y.-H. (2014). MET amplification is not rare and predicts unfavorable
+clinical outcomes in patients with recurrent/metastatic gastric cancer
+after chemotherapy. \emph{Cancer}, \emph{120}(5), 675--682.
+doi:\href{https://doi.org/10.1002/cncr.28454}{10.1002/cncr.28454}
+
 \hypertarget{ref-bairoch2018}{}
@@
 
-\hypertarget{ref-broaddepmap2018a}{}
-Broad DepMap. (2018, January 11). DepMap Achilles 18Q4 public. Figshare.
-Retrieved from
-\url{https://figshare.com/articles/DepMap_Achilles_18Q4_public/7270880}
-
 \hypertarget{ref-broaddepmap2018}{}
@@
 
+\hypertarget{ref-broaddepmap2018a}{}
+DepMap, B. (2018, January 11). DepMap Achilles 18Q4 public. Figshare.
+Retrieved from
+\url{https://figshare.com/articles/DepMap_Achilles_18Q4_public/7270880}
+
 \hypertarget{ref-doench2016a}{}
@@
 \url{https://cran.r-project.org/web/packages/ggpubr/index.html}
+
+\hypertarget{ref-kim2018}{}
+Kim, J. H., Kim, H. S., \& Kim, B. J. (2018). Prognostic value of MET
+copy number gain in non-small-cell lung cancer: An updated
+meta-analysis. \emph{J Cancer}, \emph{9}(10), 1836--1845.
+doi:\href{https://doi.org/10.7150/jca.24980}{10.7150/jca.24980}
 
@@
 
+\hypertarget{ref-thecancergenomeatlasresearchnetwork2008}{}
+Network, T. C. G. A. R. (2008). Comprehensive genomic characterization
+defines human glioblastoma genes and core pathways, \emph{455},
+1061--1068.
+doi:\href{https://doi.org/10.1038/nature07385}{10.1038/nature07385}
+
 \hypertarget{ref-neve2006}{}
@@
 
-\hypertarget{ref-rdevelopmentcoreteam2010}{}
-R Development Core Team. (2010). \emph{R: A Language and Environment for
-Statistical Computing}. Vienna, Austria: R Foundation for Statistical
-Computing. Retrieved from \url{https://www.R-project.org/}
-
 \hypertarget{ref-ramos2015a}{}
@@
 
-\hypertarget{ref-thecancergenomeatlasresearchnetwork2008}{}
-The Cancer Genome Atlas Research Network. (2008). Comprehensive genomic
-characterization defines human glioblastoma genes and core pathways,
-\emph{455}, 1061--1068.
-doi:\href{https://doi.org/10.1038/nature07385}{10.1038/nature07385}
+\hypertarget{ref-rdevelopmentcoreteam2010}{}
+Team, R. D. C. (2010). \emph{R: A Language and Environment for
+Statistical Computing}. Vienna, Austria: R Foundation for Statistical
+Computing. Retrieved from \url{https://www.R-project.org/}
 

### 2019-01-24 manuscript_analysis.Rmd
updated manuscript_analysis and manuscript

@@
   geom_point(pch = 21, fill = "cadetblue3", alpha = 0.6) +
-  labs(x = "KRAS Gene Expression (RPKM)", y = "CERES Score", subtitle = paste0("Spearman correlation coefficient = ", round(spearman_KRAS$corr[1], 2), " (", printp(spearman_KRAS$p[1]), ")"))
+  labs(x = "KRAS Gene Expression (RPKM)", y = "CERES Score", subtitle = paste0("Spearman correlation coefficient = ", round(spearman_KRAS$corr[1], 2), " (p = ", formatC(as.numeric(spearman_KRAS$p[1]), format = "e", digits = 1), ")"))
 
@@
   geom_point(pch = 21, fill = "palegreen2", alpha = 0.6) +
-  labs(x = "KRAS Copy Number (log2 ratio)", y = "CERES Score", subtitle = paste0("Spearman correlation coefficient = ", round(spearman_KRAS$corr[2], 2), " (", printp(spearman_KRAS$p[2]), ")"))
+  labs(x = "KRAS Copy Number (log2 ratio)", y = "CERES Score", subtitle = paste0("Spearman correlation coefficient = ", round(spearman_KRAS$corr[2], 2), " (p = ", formatC(as.numeric(spearman_KRAS$p[2]), format = "e", digits = 1), ")"))
 
@@
   theme(legend.position = "bottom", axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 10)) +
-  labs(fill = "-log10(p)", x = "Gene", y = "Spearman Correlation Coefficient (r_s)") +
+  labs(fill = "-log10(p)", x = "Gene", y = expression("Spearman Correlation Coefficient"~(r[s]))) +
   annotation_custom(ggplotGrob(crispr_ge_spearman_corr_inset), xmin = 12, xmax = 32, ymin = -0.15, ymax = -0.45) +
@@
 crispr_spearman_corr_plot
-# ggsave("./plots/manuscript/crispr_spearman_corr_plot.png", crispr_spearman_corr_plot, device = "png", dpi = 450, width = 16, height = 8, units = "in")
+
+# ggsave("./plots/manuscript/crispr_spearman_corr_plot.pdf", crispr_spearman_corr_plot, device = "pdf", dpi = 450, width = 16, height = 8, units = "in")
 ```

### 2019-01-24 manuscript.Rmd

@@
 
-We derived our clinical associations from a new project conducted by the Variant Interpretation for Cancer Consortium (VICC; https://cancervariants.org/), a Driver Project for the Global Alliance for Genomics and Health (GA4GH) [@theglobalallianceforgenomicsandhealth2016].
+To curate an evidence-based list of these clinical biomarkers, we utilized a new oncological data aggregation project conducted by the Variant Interpretation for Cancer Consortium (VICC; https://cancervariants.org/), a Driver Project for the Global Alliance for Genomics and Health (GA4GH) [@theglobalallianceforgenomicsandhealth2016].
 The VICC has curated annotations of known cancer variants at varying levels of evidence from multiple resources [@wagner2018]: the Precision Medicine Knowledgebase [@huang2016], MolecularMatch (https://www.molecularmatch.com/index.html), OncoKB [@chakravarty2017], Jackson Labs Clinical Knowledgebase [@patterson2016], Clinical Interpretations of Variance in Cancers (CIViC) [@griffith2017], and the Cancer Genome Interpreter (CGI) [@tamborero2018].
@@
 
-dg2intext_converter <- function(drug_gene) {
-  # Convert drug-gene strings to have italic gene name
-  d_g <- strsplit(drug_gene, split = "_")
-  dg <- paste0(d_g[[1]][1], "-*", d_g[[1]][2], "*")
-  return(dg)
+drugstring2intext_converter <- function(string, type) {
+  # Convert drug-gene/drug-gene-lineage strings to have italic gene name
+  if(type == "dg") {
+    d_g <- strsplit(string, split = "_")
+    text <- paste0(d_g[[1]][1], "-*", d_g[[1]][2], "*")
+  }
+  if(type == "dgl") {
+    d_g_l <- strsplit(string, split = "_")
+    text <- paste0(d_g_l[[1]][1], "-*", d_g_l[[1]][2], "*-", d_g_l[[1]][3])
+  }  
+  return(text)
 }
@@
 ```{r drug-data, echo=FALSE, include=FALSE}
-ccle_data <- readRDS("./data_munging/rds/ccle_data_18Q4_g2pgenes.rds")
-ccle_data_ptmuts <- filter(ccle_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
-ccle_data_ptmuts$Keep_PtMut_Tests <- ifelse(ccle_data_ptmuts$Reference_Allele_Length == 1 | is.na(ccle_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(ccle_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
-ccle_data_ptmuts <- filter(ccle_data_ptmuts, Keep_PtMut_Tests == TRUE)
-ccle_data_ptmuts$Dataset <- "CCLE"
-ccle_data_ptmuts$Hugo_Symbol <- ordered(ccle_data_ptmuts$Hugo_Symbol, levels = g2p_genes)
-
-ctrp_data <- readRDS("./data_munging/rds/ctrp_data_18Q4_g2pgenes.rds")
-ctrp_data_ptmuts <- filter(ctrp_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
-ctrp_data_ptmuts$Keep_PtMut_Tests <- ifelse(ctrp_data_ptmuts$Reference_Allele_Length == 1 | is.na(ctrp_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(ctrp_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
-ctrp_data_ptmuts <- filter(ctrp_data_ptmuts, Keep_PtMut_Tests == TRUE)
-ctrp_data_ptmuts$Dataset <- "CTRP"
-ctrp_data_ptmuts$Hugo_Symbol <- ordered(ctrp_data_ptmuts$Hugo_Symbol, levels = g2p_genes)
-
-gdsc_data <- readRDS("./data_munging/rds/gdsc_data_18Q4_g2pgenes.rds")
-gdsc_data_ptmuts <- filter(gdsc_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
-gdsc_data_ptmuts$Keep_PtMut_Tests <- ifelse(gdsc_data_ptmuts$Reference_Allele_Length == 1 | is.na(gdsc_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(gdsc_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
-gdsc_data_ptmuts <- filter(gdsc_data_ptmuts, Keep_PtMut_Tests == TRUE)
-gdsc_data_ptmuts$Dataset <- "GDSC"
-gdsc_data_ptmuts$Hugo_Symbol <- ordered(gdsc_data_ptmuts$Hugo_Symbol, levels = g2p_genes)
+ccle_data_ptmuts <- readRDS("./data_munging/rds/ccle_data_18Q4_g2pgenes_ptmuts.rds")
+ctrp_data_ptmuts <- readRDS("./data_munging/rds/ctrp_data_18Q4_g2pgenes_ptmuts.rds")
+gdsc_data_ptmuts <- readRDS("./data_munging/rds/gdsc_data_18Q4_g2pgenes_ptmuts.rds")
 
@@
 
-After filtering, `r nrow(g2p_filt)` level-A G2P interpretations were carried forward in subsequent analyses, constituting `r length(g2p_drugs)` unique drugs and `r length(g2p_genes)` unique genes in `r length(g2p_druggenes)` distinct level-A combinations (*Figure 1A*).
+After filtering, `r nrow(g2p_filt)` level-A G2P interpretations were carried forward in subsequent analyses, constituting `r length(g2p_drugs)` unique drugs and `r length(g2p_genes)` unique genes in `r length(g2p_druggenes)` distinct level-A combinations (*Figure 1A: Pink heatmap*).
 The number of level-A interpretations per drug ranged from `r range(g2p_drug_tally$n)[1]` to `r range(g2p_drug_tally$n)[2]` ($M =$ `r printnum(mean(g2p_drug_tally$n))`, $SD =$ `r printnum(sd(g2p_drug_tally$n))`), `r range(g2p_gene_tally$n)[1]` to `r range(g2p_gene_tally$n)[2]` ($M =$ `r printnum(mean(g2p_gene_tally$n))`, $SD =$ `r printnum(sd(g2p_gene_tally$n))`) per gene, and for each level-A drug-gene combination, the range was `r range(g2p_druggene_tally$n)[1]` to `r range(g2p_druggene_tally$n)[2]` ($M =$ `r printnum(mean(g2p_druggene_tally$n))`, $SD =$ `r printnum(sd(g2p_druggene_tally$n))`).
@@
 Of the `r length(g2p_druggenes)` G2P associations, data was available for `r length(ccle_signif_g2p$Drug_Gene)` associations in CCLE, `r length(ctrp_signif_g2p$Drug_Gene)` in CTRP, and `r length(gdsc_signif_g2p$Drug_Gene)` in GDSC.
-Controlling for a false discovery rate (FDR) < 5%, CCLE yielded no significant correlations (Wilcoxon rank-sum tests, `r ccle_signif_g2p_exp`), though the most significant G2P association was `r dg2intext_converter(ccle_signif_g2p$Drug_Gene[1])` (`r e2exp_converter(ccle_signif_g2p$p.adj[1], p_type = "padj")`).
-In CTRP, AUC from `r nrow(filter(ctrp_signif_g2p[!is.na(ctrp_signif_g2p$p.signif.adj),]))` drug-gene associations correlated with the gene's mutation status (`r ctrp_signif_g2p_exp`): `r dg2intext_converter(ctrp_signif_g2p$Drug_Gene[1])` (`r e2exp_converter(ctrp_signif_g2p$p.adj[1], p_type = "padj")`), `r dg2intext_converter(ctrp_signif_g2p$Drug_Gene[2])` (`r e2exp_converter(ctrp_signif_g2p$p.adj[2], p_type = "padj")`), and `r dg2intext_converter(ctrp_signif_g2p$Drug_Gene[3])` (`r e2exp_converter(ctrp_signif_g2p$p.adj[3], p_type = "padj")`).
-`r str_ucfirst(dg2intext_converter(gdsc_signif_g2p$Drug_Gene[1]))` (`r e2exp_converter(gdsc_signif_g2p$p.adj[1], p_type = "padj")`) and `r dg2intext_converter(gdsc_signif_g2p$Drug_Gene[2])` (`r e2exp_converter(gdsc_signif_g2p$p.adj[2], p_type = "padj")`) were significant in GDSC (`r gdsc_signif_g2p_exp`).
+Controlling for a false discovery rate (FDR) < 5%, CCLE yielded no significant correlations (Wilcoxon rank-sum tests, `r ccle_signif_g2p_exp`), though the most significant G2P association was `r drugstring2intext_converter(ccle_signif_g2p$Drug_Gene[1], "dg")` (`r e2exp_converter(ccle_signif_g2p$p.adj[1], p_type = "padj")`).
+In CTRP, AUC from `r nrow(filter(ctrp_signif_g2p[!is.na(ctrp_signif_g2p$p.signif.adj),]))` drug-gene associations correlated with the gene's mutation status (`r ctrp_signif_g2p_exp`): `r drugstring2intext_converter(ctrp_signif_g2p$Drug_Gene[1], "dg")` (`r e2exp_converter(ctrp_signif_g2p$p.adj[1], p_type = "padj")`), `r drugstring2intext_converter(ctrp_signif_g2p$Drug_Gene[2], "dg")` (`r e2exp_converter(ctrp_signif_g2p$p.adj[2], p_type = "padj")`), and `r drugstring2intext_converter(ctrp_signif_g2p$Drug_Gene[3], "dg")` (`r e2exp_converter(ctrp_signif_g2p$p.adj[3], p_type = "padj")`).
+`r str_ucfirst(drugstring2intext_converter(gdsc_signif_g2p$Drug_Gene[1], "dg"))` (`r e2exp_converter(gdsc_signif_g2p$p.adj[1], p_type = "padj")`) was the only significant association in GDSC (`r gdsc_signif_g2p_exp`).
 
@@
 
-To test for potentially novel drug-gene associations, we conducted similar Wilcoxon rank-sum tests for all pairwise combinations of G2P genes and drugs tested in the three drug screens (*Figures 1B and 2A*).
+To test for potentially novel drug-gene associations, we conducted similar Wilcoxon rank-sum tests for all pairwise combinations of G2P genes and drugs tested in the three drug screens (*Figures 1B: Green heatmaps*).
 At an unadjusted $\alpha = 0.05$, the tests revealed that in CCLE, AUC significantly correlated with mutation status for `r nrow(filter(ccle_signif_g2p_grid, p < 0.05))` out of `r nrow(ccle_signif_g2p_grid)` (`r printnum(nrow(filter(ccle_signif_g2p_grid, p < 0.05)) / nrow(ccle_signif_g2p_grid) * 100)`%) tested drug-gene combinations were significantly different, `r nrow(filter(ctrp_signif_g2p_grid, p < 0.05))` out of `r nrow(ctrp_signif_g2p_grid)` (`r printnum(nrow(filter(ctrp_signif_g2p_grid, p < 0.05)) / nrow(ctrp_signif_g2p_grid) * 100)`%) were significantly different for CTRP, and `r nrow(filter(gdsc_signif_g2p_grid, p < 0.05))` out of `r nrow(gdsc_signif_g2p_grid)` (`r printnum(nrow(filter(gdsc_signif_g2p_grid, p < 0.05)) / nrow(gdsc_signif_g2p_grid) * 100)`%) for GDSC.
 
-Controlling for a FDR < 5%, `r dg2intext_converter(ccle_signif_g2p_grid$Drug_Gene[1])` (`r e2exp_converter(ccle_signif_g2p_grid$p.adj[1], p_type = "padj")`) was the only significant drug-gene combination tested in CCLE (`r ccle_signif_g2p_grid_exp`).
+Controlling for a FDR < 5%, `r drugstring2intext_converter(ccle_signif_g2p_grid$Drug_Gene[1], "dg")` (`r e2exp_converter(ccle_signif_g2p_grid$p.adj[1], p_type = "padj")`) was the only significant drug-gene combination tested in CCLE (`r ccle_signif_g2p_grid_exp`).
 CTRP (`r ctrp_signif_g2p_grid_exp`) yielded `r nrow(ctrp_signif_g2p_grid[!is.na(ctrp_signif_g2p_grid$p.signif.adj),])` significant combinations, one of which was selumetinib-*BRAF*.
@@
 Of the `r length(drug_grid_shared_dg)` significant drug-gene associations across datasets, `r length(intersect(drug_grid_shared_dg, g2p_druggenes))` were G2P associations.
-The remaining `r length(drug_grid_shared_dg) - length(intersect(drug_grid_shared_dg, g2p_druggenes))` associations were `r dg2intext_converter(setdiff(drug_grid_shared_dg, g2p_druggenes)[1])`, `r dg2intext_converter(setdiff(drug_grid_shared_dg, g2p_druggenes)[2])`, and `r dg2intext_converter(setdiff(drug_grid_shared_dg, g2p_druggenes)[3])`.
+The remaining `r length(drug_grid_shared_dg) - length(intersect(drug_grid_shared_dg, g2p_druggenes))` associations were `r drugstring2intext_converter(setdiff(drug_grid_shared_dg, g2p_druggenes)[1], "dg")` and `r drugstring2intext_converter(setdiff(drug_grid_shared_dg, g2p_druggenes)[2], "dg")`.
 
@@
 
-(ref:drug-venn) Overlap of drug-gene associations drawn from all pairwise combinations of G2P drugs and G2P genes whose drug effects significantly correlated with (**A**) mutation status, (**B**) gene expression, and (**C**) copy number across CCLE, CTRP, and GDSC.
+(ref:drug-venn) **Overlap of significant drug-gene associations from CCLE, CTRP, and GDSC**.
+Overlap of drug-gene associations drawn from all pairwise combinations of G2P drugs and G2P genes whose drug effects significantly correlated with (**A**) mutation status, (**B**) gene expression, and (**C**) copy number across CCLE, CTRP, and GDSC.
 
@@
 
-Prior to correction for an FDR of 5%, no DGLs were identified in the CCLE screen when using mutation status as a correlate ($n =$ `r nrow(ccle_signif_g2p_lineage)`, `r length(unique(ccle_data_g2p_dgl$Drug_Gene_Lin)) - nrow(ccle_signif_g2p_lineage)` DGLs were not analyzed due to lack of mutation annotations in *UGT1A1* in "cancer" lineages), but CTRP ($n =$ `r nrow(ctrp_signif_g2p_lineage)`) and GDSC ($n =$ `r nrow(gdsc_signif_g2p_lineage)`) identified `r nrow(filter(ctrp_signif_g2p_lineage, !is.na(p.signif)))` and `r nrow(filter(gdsc_signif_g2p_lineage, !is.na(p.signif)))`, respectively, in skin cancer, lung cancer, and cancer.
+Prior to correction for an FDR of 5%, 1 DGL, `r drugstring2intext_converter(ccle_signif_g2p_lineage$Drug_Gene_Lin[1], "dgl")`, was identified in the CCLE screen when using mutation status as a correlate ($n =$ `r nrow(ccle_signif_g2p_lineage)`, `r length(unique(ccle_data_g2p_dgl$Drug_Gene_Lin)) - nrow(ccle_signif_g2p_lineage)` DGLs were not analyzed due to lack of mutation annotations in *UGT1A1* in "cancer" lineages), but CTRP ($n =$ `r nrow(ctrp_signif_g2p_lineage)`) and GDSC ($n =$ `r nrow(gdsc_signif_g2p_lineage)`) identified `r nrow(filter(ctrp_signif_g2p_lineage, !is.na(p.signif)))` and `r nrow(filter(gdsc_signif_g2p_lineage, !is.na(p.signif)))`, respectively, in skin cancer, lung cancer, and cancer lineages.
 After Benjamini-Hochberg FDR correction, none of the datasets yielded significant DGL interactions.
 
-> **(???) KS test results**
+> **(???) KS test results: Need to flesh out this section**
 
@@
 
-(ref:ksplot) Comparison of Spearman correlation coefficients ($r_s$) derived from copy number (log$_2$ ratio), gene expression (RPKM), and AUC z-scores from G2P drug-gene associations.
-Coefficients were grouped by whether or not the associated lineage for each comparison was in a G2P drug-gene-lineage association or not.
-Distributions of these grouped coefficients were compared using Kolmogorov-Smirnov tests.
+(ref:ksplot) **Comparison of drug-gene AUC vs.
+gene expression and vs.
+copy number in G2P and non-G2P cell lines**.
+Comparison of Spearman correlation coefficients ($r_s$) derived from copy number (log$_2$ ratio) vs.
+AUC z-scores and gene expression (RPKM) vs.
+AUC z-scores for G2P drug-gene associations.
+Correlation coefficients were grouped by whether or not the associated lineage for each comparison was in a level-A G2P drug-gene-lineage association or not.
+The distributions of these grouped coefficients were compared using Kolmogorov-Smirnov tests to identify whether correlations in G2P lineages were distinct from correlations in non-G2P lineages.
 
@@
 crispr_data <- readRDS("./../htscreens_giant_files/crispr_data_18Q4.rds")
-crispr_data_ptmuts <- filter(crispr_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
-crispr_data_ptmuts$Keep_PtMut_Tests <- ifelse(crispr_data_ptmuts$Reference_Allele_Length == 1 | is.na(crispr_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(crispr_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
+# Filter CRISPR for G2P genes in G2P
+crispr_data_ptmuts <- filter(crispr_data, Hugo_Symbol %in% g2p_genes)
+# Filter G2P CRISPR for point mutations
+crispr_data_ptmuts <- filter(crispr_data_ptmuts, Reference_Allele == 1 | Reference_Allele == 0 | is.na(Reference_Allele))
+crispr_data_ptmuts$Keep_PtMut_Tests <- ifelse(crispr_data_ptmuts$Reference_Allele == 1 | is.na(crispr_data_ptmuts$Reference_Allele), TRUE, ifelse(crispr_data_ptmuts$Tumor_Seq_Allele1 == 1, TRUE, FALSE))
 crispr_data_ptmuts <- filter(crispr_data_ptmuts, Keep_PtMut_Tests == TRUE)
-
-# Filter CRISPR for G2P genes in G2P
-crispr_data_g2p <- filter(crispr_data_ptmuts, Hugo_Symbol %in% g2p_genes)
+crispr_data_ptmuts <- subset(crispr_data_ptmuts, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, Genome_Change, Keep_PtMut_Tests))
+crispr_data_g2p <- unique(crispr_data_ptmuts)
 crispr_data_g2p$Hugo_Symbol <- factor(crispr_data_g2p$Hugo_Symbol, levels = g2p_genes)
@@
 
-(ref:crispr-venn) Overlap of genes whose gene expression and/or copy number significantly correlated with CERES score.
+(ref:crispr-waterfall) Stuff stuff stuff!
+
+```{r crispr-waterfall, echo = FALSE, message=FALSE, warning=FALSE, fig.cap='(ref:crispr-waterfall)'}
+knitr::include_graphics("./plots/manuscript/crispr_spearman_corr_plot.pdf")
+```
+
+(ref:crispr-venn) **CRISPR sceen results**. Overlap of genes whose gene expression and/or copy number significantly correlated with CERES score (Spearman rank-order correlations).
 
@@
 
-When we don’t account for lineage, Wilcoxon rank-sum tests (`r crispr_signif_g2p_gene_exp`, FDR < 5%) revealed that mutations in `r nrow(crispr_signif_g2p_gene_sig)` genes significantly correlated with CERES score: *`r as.character(crispr_signif_g2p_gene_sig$Hugo_Symbol)[1]`* (`r e2exp_converter(crispr_signif_g2p_gene_sig$p.adj[1], p_type = "padj")`) and *`r as.character(crispr_signif_g2p_gene_sig$Hugo_Symbol)[2]`* (`r e2exp_converter(crispr_signif_g2p_gene_sig$p.adj[2], p_type = "padj")`).
-Gene expression (RPKM) of `r nrow(crispr_spearman_res_GE_sig)` out of `r nrow(crispr_spearman_res_GE)` (`r printnum(nrow(crispr_spearman_res_GE_sig) / nrow(crispr_spearman_res_GE) * 100)`%) G2P genes significantly correlated with CERES score, as did copy number (log2-ratio) for `r nrow(crispr_spearman_res_CN_sig)` out of `r nrow(crispr_spearman_res_CN)` (`r printnum(nrow(crispr_spearman_res_CN_sig) / nrow(crispr_spearman_res_CN) * 100)`%) G2P genes (Figure\ \@ref(fig:crispr-venn)).
+When we don’t account for lineage, Wilcoxon rank-sum tests (`r crispr_signif_g2p_gene_exp`, FDR < 5%) revealed that mutations in `r nrow(crispr_signif_g2p_gene_sig)` gene significantly correlated with CERES score: *`r as.character(crispr_signif_g2p_gene_sig$Hugo_Symbol)[1]`* (`r e2exp_converter(crispr_signif_g2p_gene_sig$p.adj[1], p_type = "padj")`).
+Gene expression (RPKM) of `r nrow(crispr_spearman_res_GE_sig)` out of `r nrow(crispr_spearman_res_GE)` (`r printnum(nrow(crispr_spearman_res_GE_sig) / nrow(crispr_spearman_res_GE) * 100)`%, Spearman rank-order correlations) G2P genes significantly correlated with CERES score, as did copy number (log2-ratio) for `r nrow(crispr_spearman_res_CN_sig)` out of `r nrow(crispr_spearman_res_CN)` (`r printnum(nrow(crispr_spearman_res_CN_sig) / nrow(crispr_spearman_res_CN) * 100)`%, Spearman rank-order correlations) G2P genes (Figure\ \@ref(fig:crispr-waterfall)).
+We see moderate overlap between these genes whose CERES scores significantly correlated with gene expression and with copy number (Figure\ \@ref(fig:crispr-venn)).
+For the purpose of comparison to the drug screen data, if we treat CRISPR knockdown like a small-molecule drug, then these results are more comprehensive than the results from CCLE, CTRP, and GDSC.
 
-For the purpose of comparison to the drug screen data, if we treat CRISPR knockdown like a small-molecule drug, then these results are more comprehensive than the results from CCLE, CTRP, and GDSC (Table 2).
-
-- Lineage?
+> **(???) Lineage????**
 
@@
 
-In a lineage-agnostic context of the CRISPR screen, ERBB2 gene essentiality score had a significant negative correlation with ERBB2 gene expression ($p < 10^{-12}$, $r = -0.31$) and ERBB2 copy number ($p < 10^{-15}$, $r = -0.34$) (*Figure ##2*).
-Similarly, MET gene essentiality also correlated with both MET gene expression ($p < 10^{-12}$, $r = -0.31$) and copy number ($p < 10^{-8}$, $r = -0.25$).
-Notably, BRCA1 also significantly correlated with both gene expression ($p < 0.001$, $r = 0.16$) and copy number ($p < 0.01$, $r = 0.14$).
-BRCA2 significantly correlated with all three of the genomic features tested: gene expression ($p < 0.05$, $r = 0.10$), copy number ($p < 10^{-7}$, $r = 0.23$), and mutation status ($p < 0.001$).
+In a lineage-agnostic context of the CRISPR screen, *ERBB2* gene essentiality score had significant negative correlations with *ERBB2* gene expression (`r e2exp_converter(crispr_spearman_res_GE_sig$p[which(crispr_spearman_res_GE_sig$Hugo_Symbol == "ERBB2")], "p")`, $r_s =$ `r printnum(crispr_spearman_res_GE_sig$corr[which(crispr_spearman_res_GE_sig$Hugo_Symbol == "ERBB2")])`) and *ERBB2* copy number (`r e2exp_converter(crispr_spearman_res_CN_sig$p[which(crispr_spearman_res_CN_sig$Hugo_Symbol == "ERBB2")], "p")`, $r_s =$ `r printnum(crispr_spearman_res_CN_sig$corr[which(crispr_spearman_res_CN_sig$Hugo_Symbol == "ERBB2")])`) (*Figure ##2*).
+Notably, gene essentiality of *MET*, which is known to have copy number alterations in some cancers [@an2014; @kim2018], did not significantly correlate with *MET* gene expression nor *MET* copy number.
+*BRCA1* gene essentiality also significantly correlated with both *BRCA1* gene expression (`r e2exp_converter(crispr_spearman_res_GE_sig$p[which(crispr_spearman_res_GE_sig$Hugo_Symbol == "BRCA1")], "p")`, $r_s =$ `r printnum(crispr_spearman_res_GE_sig$corr[which(crispr_spearman_res_GE_sig$Hugo_Symbol == "BRCA1")])`) and *BRCA1* copy number (`r e2exp_converter(crispr_spearman_res_CN_sig$p[which(crispr_spearman_res_CN_sig$Hugo_Symbol == "BRCA1")], "p")`, $r_s =$ `r printnum(crispr_spearman_res_CN_sig$corr[which(crispr_spearman_res_CN_sig$Hugo_Symbol == "BRCA1")])`).
+*BRCA2* gene essentiality significantly correlated *BRCA2* gene expression (`r e2exp_converter(crispr_spearman_res_CN_sig$p[which(crispr_spearman_res_CN_sig$Hugo_Symbol == "BRCA2")], "p")`, $r_s =$ `r printnum(crispr_spearman_res_CN_sig$corr[which(crispr_spearman_res_CN_sig$Hugo_Symbol == "BRCA2")])`) but not *BRCA2* copy number.
 
@@
 
-**Should we do this?**
+> **(???) Should we do this?**
 
@@
 
-For computing Spearman correlation coefficients, we used the `cor.test` base R package. If there were 3 or fewer data points, then the correlation was not done and a value of `NA` was supplied.
+For computing Spearman correlation coefficients, we used the `cor.test` function from the `stats` package.
+If there were 3 or fewer data points, then the correlation was not done and a value of `NA` was supplied.
 

### 2019-01-25 manuscript.Rmd

@@
 floatsintext      : yes
-figsintext        : no
+figsintext        : yes
 figurelist        : no
@@
 
-(ref:crispr-waterfall) Stuff stuff stuff!
+(ref:crispr-waterfall) **CRISPR screen correlations between  dependencey score, gene expression, and copy number**.
+Significance of Spearman correlation coefficients ($r_s$) derived from comparisons of CERES score/gene expression and CERES score/copy number for the `r length(crispr_signif_g2p_gene$Hugo_Symbol)` G2P genes screened in the CRISPR dataset.
+Inset plots show example derivations of Spearman correlation coefficients using *KRAS* gene expression (left) and copy number (right).
+In both inset plots, each point represents data from one cell line.
 

### 2019-02-14 multivariate_regression.Rmd
initiated mvr Rmd

---
title: "Multivariate Regression"
author: "Sally Claridge"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    theme: cerulean
    number_sections: true
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: true
    code_folding: hide
    pandoc_args: [
      "+RTS", "-K2048m",
      "-RTS"
    ]
---

This is part of the ongoing [Variant Interpretation for Cancer Consortium Meta-Knowledgebase (G2P)](https://search.cancervariants.org/#*) project. This part of the project is mentored by Denise Duma, PhD, in which we aim to use a partial least squares (PLS) multivariate regression model to (**1**) determine the feature modules that best explain the drug responses observed in the [Cancer Cell Line Encyclopedia (CCLE)](https://portals.broadinstitute.org/ccle), [Cancer Therapeutics Response Portal (CTRP)](https://portals.broadinstitute.org/ctrp/), and [Genomics of Drug Senstitivity in Cancer (GDSC)](https://www.cancerrxgene.org/) pharmacogenomics screens in cancer cell lines, and (**2**) develop a robust predictive model for linking multiple omics features to drug sensitivity across these hundreds of cell lines of various cancer lineages. We utillize gene expression, copy number, and mutation status data collected by the CCLE for nearly all of these cell lines and distributed via the [Cancer Dependency Map (DepMap)](https://depmap.org/portal/), a collaborative project helmed by the Broad Institute and Wellcome Trust Sanger Institute.

# SET UP

--------------------------------------------------------------------------------

```{r setup, include=FALSE}
set.seed(1234)
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
# num_cores <- parallel::detectCores()
options(mc.cores = parallel::detectCores(), expressions = 5e5, digits = 4)
```

```{r libraries}
library(tidyverse)
library(pls)
```

# Introduction to the `pls` package

--------------------------------------------------------------------------------

These examples are derived from "Introduction to `pls` Package" by Bjorn Mevik and Ron Wehrens (2018).

Load example data sets:
```{r}
data(yarn)
data(oliveoil)
data(gasoline)
```

## `gasoline` example

Divide data into test and training sets:
```{r}
gasTrain <- gasoline[1:50,]
gasTest <- gasoline[51:60,]
```

Fit a PLSR model. Note that validation is presented as RMSEP, which is Root Mean Squared Error of Prediction. `CV` are ordinary crossvalidation estimates, and `adjCV` are bias-corrected crossvalidation estimates.
```{r}
gas1 <- plsr(octane ~ NIR, ncomp = 10, data = gasTrain, validation = "LOO")

summary(gas1)
```

The first plot is of the the RMSEP curves for gasoline data, grouped by `CV` and `adjCV` as functions of the number of components. Visually, we see the main inflection point occurs at 2 components. Using those 2 components, make a prediction plot. This plots the cross-validated predictions with two components versus measured values. The plots fall along the target $y = 1$ line and we do not observe any curvature or abnormalities.
```{r}
par(mfrow = c(1, 2))
plot(RMSEP(gas1), legendpos = "topright")
# plot(gas1, plottype = "validation", legendpos = "topright")
plot(gas1, ncomp = 2, asp = 1, line = TRUE)
par(mfrow = c(1, 1))
```

This is a pairwise plot of the score values for the first 3 coponents, which can be used to look for patterns, groups, or outliers in the data.
```{r}
plot(gas1, plottype = "scores", comps = 1:3)
```

The percents in parentheses above indicate the relative amount of X variance explained by each component. These explained variances can be extracted:
```{r}
explvar(gas1)
```

Loading plots are frequently used for interpretation purposes.
```{r}
plot(gas1, "loadings", comps = 1:2, legendpos = "topleft", labels = "numbers", xlab = "nm")
```

Using the `gas1` model, we can predict response values of new observations. Since we know the true response values for these samples, we can calculate the RMSEP for the test set. We se that for 2 components, we get 0.2445, which is close to the crossvalidated RMSEP (0.297).
```{r}
predict(gas1, ncomp = 2, newdata = gasTest)
RMSEP(gas1, newdata = gasTest)
```

## Model fitting examples

When the response term is a matrix, a multi-response model is fit:
```{r}
dim(oliveoil$sensory)
dim(oliveoil$chemical)
plsr(sensory ~ chemical, data = oliveoil)
```

You can use `update()` to refit a prevoous model using new parameters or new/different observations:
```{r}
dens1 <- plsr(density ~ NIR, ncomp = 5, data = yarn)
trainid <- which(yarn$train == TRUE)
dens2 <- update(dens1, subset = trainid)
dens3 <- update(dens1, ncomp = 10)
```

In PLS, predictor variables are always centered as part of the fit algorithm. If `scale = TRUE`, then each variable is standardized by dividing it by its standard deviation, and if `scale` is a numeric vector, each variable is divided by the corresponding number.
```{r}
olive1 <- plsr(sensory ~ chemical, scale = TRUE, data = oliveoil)
```

## Choosing the number of components with crossvalidation

There are two component selection strategies in `seelctNcomp`. (1) Is the one-sigma heuristic that consists of choosing the model with the fewest components that is still less than one standard error away from the overall best model. (2) Uses a permutation approach that tests whether adding a new component is beneficial by taking the global minimum of the crossvalidation curve and reducing the number of components one by one as long as no significant deterioration in performance is found (default is $\alpha = 0.01$).
```{r}
par(mfrow = c(1, 2))
ncomp.onesigma <- selectNcomp(gas1, method = "onesigma", plot = TRUE, main = "One-Sigma")
ncomp.permut <- selectNcomp(gas1, method = "randomization", plot = TRUE, main = "Permutation")
par(mfrow = c(1, 1))
```

The `crossval` function takes an `mvr` object and performs crossvalidation such that the pre-treatment is done for each segment. Applying MSC in this case leads to nearly identical crossvalidation estimates of prediction error. Whe n the scaling does not depend on dividing the data into segments, `crossval`, though slower, gives the same results as `mvrCv`.
```{r}
gas2 <- plsr(octane ~ msc(NIR), ncomp = 10, data = gasTrain) # msc is domain-sepcific to NIR
gas2.cv <- crossval(gas2, segments = 10)
plot(MSEP(gas2.cv), legendpos = "topright")
summary(gas2.cv, what = "validation")
```

### 2019-02-18 multivariate_regression.Rmd

@@
 
-This is a pairwise plot of the score values for the first 3 coponents, which can be used to look for patterns, groups, or outliers in the data.
+This is a pairwise plot of the score values for the first 3 coponents, which can be used to look for patterns, groups, or outliers in the data (can use `scoreplot` function).
 ```{r}
@@
 
-Loading plots are frequently used for interpretation purposes.
+Loading plots are frequently used for interpretation purposes (can use `loadingplot` function).
 ```{r}
@@
 ```
+
+## Inspecting fitted models
+
+### Plots
+
+Prediction plots (`predplot`) can be used to compare predicted vs.
+measured values.
+Test data predictions are used if the `newdata` argument is called, crossvalidated predictions are used if the model was built using crossvalidation, and the default is to use predictions from the training set.
+
+We can use a validation plot (`validationplot`) to visually assess the optimal number of components.
+The y-axis is RMSEP, MSEP, or R^2^, and the x-axis is the number of components.
+Usually, you take the first locak minimum rather than the absolute minimum to avoid overfitting.
+
+We can look at the loadings and scores using `loadingplot` and `scoreplot` functions (examples of these plots are above).
+
+We can also visualize the regression coefficients using `coefplot` or as below.
+We can plot the regression vectors for multiple components simultaneously.
+Coefficients for component 2 and 3 look similar becasue component 3 contributes little to the predictions.
+```{r}
+plot(gas1, plottype = "coef", ncomp = 1:3, legendpos = "bottomleft", labels = "numbers", xlab = "nm")
+```
+
+A correlation loadings plot (`corrplot` function) shows correlations between each variable and specified components. From the manual:
+
+>These plots are scatter plots of two sets of scores with concentric circles of radii given by `radii`.
+Each point corresponds to an X variable.
+The squared distance between the point and the origin equals the fraction of the variance of the variable explained by the components in the panel.
+The default values for radii correspond to 50% and 100% explained variance, respectively.
+
+```{r}
+plot(gas1, plottype = "correlation", comps = 1:3)
+```
+
+### Extraction
+
+Using `coef`, you can extract the regression coefficients from the model. You can modify how many components to take into account and whether or not an intercept is necessary (default is `FALSE`).
+
+Scores and loadings can be extracted via `scores` and `loadings` for X and `Yscores` and `Yloadings` for Y.
+The `loading.weights` function can extract the weights from a PLSR model but not a PCA model.
+
+## Predicting new observations
+
+The `predict` method is used to predict future observations.
+Standard form is `predict(mymodel, ncomp = myncomp, newdata = mynewdata)`, where `mymodel` is a fitted model, `myncomp` specifies the model size to be used, and `mynewdata` is a data frame or matrix of new X observations and can contain new Y data to compare against the predictions or to estimate the predictive ability of the model.
+You can also make predictions using specific components with the `comps` argument.
+`predict` returns a three-dimensional array, in which entry (*i*, *j*, *k*) is the predicted value for observation *i*, response *j*, and model size *k*.
+When `comps` is used, the *k* dimension is dropped because the results are always from a single model.
+`drop` drops singleton dimensions.
+You can use `predplot` to view the predictions comparing predicted and measured values.
+```{r}
+drop(predict(gas1, ncomp = 2:3, newdata = gasTest[1:5,]))
+predplot(gas1, ncomp = 2:3, newdata = gasTest, asp = 1, line = TRUE)
+```
+
+##

### 2019-02-28 manuscript_analysis.Rmd

@@
 ```{r, eval=FALSE}
-maf_df <- readRDS("./data_munging/rds/maf_df_18Q4.rds")
 cn_melt <- readRDS("./data_munging/rds/cn_melt_18Q4.rds")
@@
 
-457/3462 gene-cell line combinations have more than one mutation in the MAF file. **FIX THIS**
-```{r}
-# test <- maf_df_g2p %>% count(Hugo_Symbol, CCLE_Name)
-# test <- test[order(test$n, decreasing = TRUE),]
-```
+```{r}
+maf_df <- readRDS("./data_munging/rds/maf_df_18Q4.rds")
+test <- filter(maf_df, Hugo_Symbol %in% g2p_genes) %>% count(Hugo_Symbol, CCLE_Name)
+test <- test[order(test$n, decreasing = TRUE),]
+```
+
+`r nrow(filter(test, n == 1))`/`r nrow(test)` gene-cell line combinations have more than one mutation in the MAF file. This is corrected in the point mutation filtering done below.
 
@@
 ccle_data_ptmuts <- filter(ccle_data_ptmuts, Keep_PtMut_Tests == TRUE)
+# Remove columns that lead to duplicate mutation entries
 ccle_data_ptmuts <- subset(ccle_data_ptmuts, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, Genome_Change, Keep_PtMut_Tests))
@@
 ctrp_data_ptmuts <- filter(ctrp_data_ptmuts, Keep_PtMut_Tests == TRUE)
+# Remove columns that lead to duplicate mutation entries
 ctrp_data_ptmuts <- subset(ctrp_data_ptmuts, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, Genome_Change, Keep_PtMut_Tests))
@@
 gdsc_data_ptmuts <- filter(gdsc_data_ptmuts, Keep_PtMut_Tests == TRUE)
+# Remove columns that lead to duplicate mutation entries
 gdsc_data_ptmuts <- subset(gdsc_data_ptmuts, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, Genome_Change, Keep_PtMut_Tests))
@@
 gdsc_signif_g2p <- readRDS("./data_munging/rds/gdsc_signif_g2p_gene.rds")
-gdsc_signif_g2p_kabl <- knitr::kable(gdsc_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
+gdsc_signif_g2p_kable <- knitr::kable(gdsc_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 
@@
 
-Example of how to describe Spearman correaltion results: ""A Spearman's correlation was run to determine the relationship between 23 groundwater uranium and TDS values.
+Example of how to describe Spearman correaltion results: A Spearman's correlation was run to determine the relationship between 23 groundwater uranium and TDS values.
 There was a strong, positive monotonic correlation between Uranium and TDS ( = .71, n = 23, p < .001)."
@@
 rownames(crispr_data_g2p_summ) <- NULL
-
+crispr_data_g2p_summ <- crispr_data_g2p_summ[order(crispr_data_g2p_summ$Percent_Mutant, decreasing = TRUE),]
 # write.table(crispr_data_g2p_summ, file = "~/Desktop/crispr_data_g2p_summ_20181003.tsv", quote = FALSE, sep = "\t")
@@
 ccle_dgl_summ <- with(ccle_dgl_summ, cbind(colsplit(Drug_Gene_Lin, pattern = "_", names = c("Drug", "Gene", "Lineage")), 
-                                           CCLE_p = p,
-                                           CCLE_p_Bonf = ifelse(p < 0.05 / ccle_mut_n, "Sig", NA),
+                                           CCLE_p_mut = p,
+                                           CCLE_p_mut_Bonf = ifelse(p < 0.05 / ccle_mut_n, "Sig", NA),
                                            CCLE_r_GE = Pearson_Corr_GE,
@@
 ctrp_dgl_summ <- with(ctrp_dgl_summ, cbind(colsplit(Drug_Gene_Lin, pattern = "_", names = c("Drug", "Gene", "Lineage")), 
-                                           CTRP_p = p,
-                                           CTRP_p_Bonf = ifelse(p < 0.05 / ctrp_mut_n, "Sig", NA),
+                                           CTRP_p_mut = p,
+                                           CTRP_p_mut_Bonf = ifelse(p < 0.05 / ctrp_mut_n, "Sig", NA),
                                            CTRP_r_GE = Pearson_Corr_GE,
@@
 gdsc_dgl_summ <- with(gdsc_dgl_summ, cbind(colsplit(Drug_Gene_Lin, pattern = "_", names = c("Drug", "Gene", "Lineage")), 
-                                           GDSC_p = p,
-                                           GDSC_p_Bonf = ifelse(p < 0.05 / gdsc_mut_n, "Sig", NA),
+                                           GDSC_p_mut = p,
+                                           GDSC_p_mut_Bonf = ifelse(p < 0.05 / gdsc_mut_n, "Sig", NA),
                                            GDSC_r_GE = Pearson_Corr_GE,
@@
 g2p_dgl_sig_summ <- merge(merge(ccle_dgl_summ, ctrp_dgl_summ, by = c("Drug", "Gene", "Lineage"), all = TRUE), gdsc_dgl_summ, by = c("Drug", "Gene", "Lineage"), all = TRUE)
+```
+
+```{r}
+g2p_dgl_sig_summ_labels <- c("CCLE_mut", "CCLE_GE", "CCLE_CN",
+                             "CTRP_mut", "CTRP_GE", "CTRP_CN",
+                             "GDSC_mut", "GDSC_GE", "GDSC_CN")
+
+g2p_dgl_sig_summ_n <- c(sum(!is.na(g2p_dgl_sig_summ$CCLE_p_mut)),
+                        sum(!is.na(g2p_dgl_sig_summ$CCLE_p_GE)),
+                        sum(!is.na(g2p_dgl_sig_summ$CCLE_p_CN)),
+                        sum(!is.na(g2p_dgl_sig_summ$CTRP_p_mut)),
+                        sum(!is.na(g2p_dgl_sig_summ$CTRP_p_GE)),
+                        sum(!is.na(g2p_dgl_sig_summ$CTRP_p_CN)),
+                        sum(!is.na(g2p_dgl_sig_summ$GDSC_p_mut)),
+                        sum(!is.na(g2p_dgl_sig_summ$GDSC_p_GE)),
+                        sum(!is.na(g2p_dgl_sig_summ$GDSC_p_CN)))
+
+g2p_dgl_sig_summ_percents <- c(sum(!is.na(g2p_dgl_sig_summ$CCLE_p_mut_Bonf)) / sum(!is.na(g2p_dgl_sig_summ$CCLE_p_mut)) * 100,
+sum(!is.na(g2p_dgl_sig_summ$CCLE_p_GE_Bonf)) / sum(!is.na(g2p_dgl_sig_summ$CCLE_p_GE)) * 100,
+sum(!is.na(g2p_dgl_sig_summ$CCLE_p_CN_Bonf)) / sum(!is.na(g2p_dgl_sig_summ$CCLE_p_CN)) * 100,
+sum(!is.na(g2p_dgl_sig_summ$CTRP_p_mut_Bonf)) / sum(!is.na(g2p_dgl_sig_summ$CTRP_p_mut)) * 100,
+sum(!is.na(g2p_dgl_sig_summ$CTRP_p_GE_Bonf)) / sum(!is.na(g2p_dgl_sig_summ$CTRP_p_GE)) * 100,
+sum(!is.na(g2p_dgl_sig_summ$CTRP_p_CN_Bonf)) / sum(!is.na(g2p_dgl_sig_summ$CTRP_p_CN)) * 100,
+sum(!is.na(g2p_dgl_sig_summ$GDSC_p_mut_Bonf)) / sum(!is.na(g2p_dgl_sig_summ$GDSC_p_mut)) * 100,
+sum(!is.na(g2p_dgl_sig_summ$GDSC_p_GE_Bonf)) / sum(!is.na(g2p_dgl_sig_summ$GDSC_p_GE)) * 100,
+sum(!is.na(g2p_dgl_sig_summ$GDSC_p_CN_Bonf)) / sum(!is.na(g2p_dgl_sig_summ$GDSC_p_CN)) * 100)
+
+g2p_dgl_sig_summ_stats <- data.frame("Dataset_Feature" = g2p_dgl_sig_summ_labels, "n_measured" = g2p_dgl_sig_summ_n, "Percent_Sig_Bonf" = g2p_dgl_sig_summ_percents)
 ```
@@
 
-Mutation summaries for G2P gri comparisons:
+Mutation summaries for G2P grid comparisons:
 ```{r}
@@
 
-# Pearson correlations
-g2p_cor_stats <- g2p_cor
-g2p_cor_stats$n_true <- TRUE
-g2p_cor_stats <- g2p_cor_stats %>% group_by(Dataset, InG2P) %>% drop_na() %>% summarize(
-          ge_mean = round(mean(Pearson_GE_Abs), 5),
-          ge_sd = round(sd(Pearson_GE_Abs), 5),
+# Spearman correlations
+g2p_spearman_stats <- g2p_cor
+g2p_spearman_stats$n_true <- TRUE
+g2p_spearman_stats <- g2p_spearman_stats %>% group_by(Dataset, InG2P) %>% drop_na() %>% summarize(
+          ge_mean = round(mean(Spearman_GE_Abs), 5),
+          ge_sd = round(sd(Spearman_GE_Abs), 5),
           ge_n = sum(n_true),
-          ge_n_signif = sum(Pearson_Pval_GE < 0.05),
+          ge_n_signif = sum(Spearman_Pval_GE < 0.05),
           ge_n_sig_perc = ge_n_signif / ge_n * 100,
-          cn_mean = round(mean(Pearson_CN_Abs), 3),
-          cn_sd = round(sd(Pearson_CN_Abs), 5),
+          cn_mean = round(mean(Spearman_CN_Abs), 3),
+          cn_sd = round(sd(Spearman_CN_Abs), 5),
           cn_n = sum(n_true),
-          cn_n_signif = sum(Pearson_Pval_CN < 0.05),
+          cn_n_signif = sum(Spearman_Pval_CN < 0.05),
           cn_n_sig_perc = cn_n_signif / cn_n * 100)
-g2p_cor_stats
+
+g2p_cor_stats <- merge(g2p_mut_all_summ_stats, g2p_spearman_stats, by = c("Dataset", "InG2P"))
+g2p_cor_stats_kable <- knitr::kable(g2p_cor_stats, caption = "Summary of number of features with significant correlations with drug response, both in G2P and not") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```
@@
                 N_Lineages = length(as.character(unique(group_general_lineage_name))),
-                Pearson_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
-                Pearson_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$estimate,
-                Spearman_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
-                Spearman_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$estimate)
+                Pearson_Corr_GE = cor.test(y = AUC_zscore,
+                                           x = RPKM, method = "pearson",
+                                           use = "complete.obs")$estimate,
+                Pearson_Corr_CN = cor.test(y = AUC_zscore,
+                                           x = CN, method = "pearson",
+                                           use = "complete.obs")$estimate,
+                Spearman_Corr_GE = cor.test(y = AUC_zscore,
+                                            x = RPKM, method = "spearman",
+                                            use = "complete.obs")$estimate,
+                Spearman_Corr_CN = cor.test(y = AUC_zscore,
+                                            x = CN, method = "spearman",
+                                            use = "complete.obs")$estimate)
     corr_res <- merge(corr_res, compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, data = df_list[[i]], group.by = "G2P_DGL", method = "wilcox.test")[, c("G2P_DGL", "p")], by = "G2P_DGL", all = TRUE)
@@
   scale_fill_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
-  scale_color_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4", "CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
+  scale_color_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
   coord_cartesian(ylim = c(-1, 1)) +
@@
 ```{r}
-compare_grid <- expand.grid(g2p_druggenes, unique(ccl_converter$group_general_lineage_name), c("CCLE", "CTRP", "GDSC"), c("Gene Expression", "Copy Number", "Mutation Status"))
-colnames(compare_grid) <- c("Drug_Gene", "group_general_lineage_name", "Dataset", "Metric")
-
 pancan_ge <- select(filter(all_pearson_res, Metric == "Gene Expression"), Drug_Gene, p, Dataset, p_log10)
@@
 compare_ge <- merge(compare_ge, pancan_ge, by = c("Drug_Gene", "Dataset"), all = TRUE)
-compare_ge$Compare_Pvals <- ifelse(compare_ge$p_log10 < compare_ge$p_log10_pancan, "Under", "Above")
+compare_ge$Compare_Pvals <- ifelse(compare_ge$p < compare_ge$p_pancan, "lineage more sig", "pancan more sig")
 compare_ge$Metric <- "Gene Expression"
@@
 compare_cn <- merge(compare_cn, pancan_cn, by = c("Drug_Gene", "Dataset"), all = TRUE)
-compare_cn$Compare_Pvals <- ifelse(compare_cn$p_log10 < compare_cn$p_log10_pancan, "Under", "Above")
+compare_cn$Compare_Pvals <- ifelse(compare_cn$p < compare_cn$p_pancan, "lineage more sig", "pancan more sig")
 compare_cn$Metric <- "Copy Number"
@@
 compare_mut <- merge(compare_mut, pancan_mut, by = c("Drug_Gene", "Dataset"), all = TRUE)
-compare_mut$Compare_Pvals <- ifelse(compare_mut$p_log10 < compare_mut$p_log10_pancan, "Under", "Above")
+compare_mut$Compare_Pvals <- ifelse(compare_mut$p < compare_mut$p_pancan, "lineage more sig", "pancan more sig")
 compare_mut$Metric <- "Mutation Status"
@@
 compare_data <- filter(rbind(compare_ge, compare_cn, compare_mut), Drug_Gene %in% g2p_druggenes)
-compare_data <- merge(compare_grid, compare_data, by = c("Drug_Gene", "group_general_lineage_name", "Dataset", "Metric"), all.x = TRUE)
-```
-
-```{r}
-compare_data_stats <- compare_data %>% count(Metric, Compare_Pvals)
-compare_data_stats
+compare_data$Compare_Pvals <- ifelse(is.na(compare_data$Compare_Pvals), "in G2P but not measured", compare_data$Compare_Pvals)
+
+# Add grid entries for counting non-G2P drug-gene associations
+# compare_grid <- expand.grid(g2p_druggenes, unique(ccl_converter$group_general_lineage_name), c("CCLE", "CTRP", "GDSC"), c("Gene Expression", "Copy Number", "Mutation Status"))
+# colnames(compare_grid) <- c("Drug_Gene", "group_general_lineage_name", "Dataset", "Metric")
+# compare_data <- merge(compare_grid, compare_data, by = c("Drug_Gene", "group_general_lineage_name", "Dataset", "Metric"), all.x = TRUE)
+# compare_data$Compare_Pvals <- ifelse(is.na(compare_data$Compare_Pvals), "not in G2P", compare_data$Compare_Pvals)
+```
+
+```{r}
+compare_data_stats <- compare_data %>% count(Dataset, Metric, Compare_Pvals)
+compare_data_stats_kable <- knitr::kable(compare_data_stats, caption = "Comparison of lineage-specific and pancancer p-values for G2P drug-gene associations") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
 ```

### 2019-02-28 multivariate_regression.Rmd
test plsr on CCLE+CTRP data w/ GE

@@
 ```{r libraries}
+library(reshape2)
 library(tidyverse)
@@
 
-There are two component selection strategies in `seelctNcomp`.
+There are two component selection strategies in `selectNcomp`.
 (1) Is the one-sigma heuristic that consists of choosing the model with the fewest components that is still less than one standard error away from the overall best model.
@@
 
-##
+# Test `pls` with drugscreen data
+
+--------------------------------------------------------------------------------
+
+## Global data files
+
+Load in G2P data for gene filtering:
+```{r}
+ccl_converter <- read.delim("./data_munging/cell_line_database_v1_20180911.tsv", row.names = 1, sep = "\t", header = TRUE)
+colnames(ccl_converter)[colnames(ccl_converter) == "Broad_ID"] <- "DepMap_ID"
+ach2cvcl <- select(ccl_converter, accession_id, DepMap_ID)
+lineage_converter <- unique(ccl_converter[, c("grouped_general_doid", "group_general_lineage_name")])
+
+g2p <- read.delim("./data_munging/g2p_full_level_A_dataset_NEW_DEC_2_2018_withGroupedLineages.csv", sep = "\t", header = TRUE)
+g2p[, 1:2] <- NULL
+g2p <- merge(g2p, lineage_converter, by = "grouped_general_doid", all.x = TRUE)
+
+g2p$Drug <- tolower(g2p$Drug)
+g2p[g2p == -1] <- NA
+g2p$Ref[g2p$Ref == "None"] <- NA
+g2p$Alt[g2p$Alt == "None"] <- NA
+g2p$Drug_Gene <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene), NA, paste0(g2p$Drug, "_", g2p$Gene))
+g2p$Drug_Gene_Lin <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene) | is.na(g2p$group_general_lineage_name), NA, paste0(g2p$Drug, "_", g2p$Gene, "_", g2p$group_general_lineage_name))
+g2p$position <- paste0("g.chr", g2p$Chromosome, ":", g2p$End, g2p$Ref, ">", g2p$Alt)
+g2p$position <- ifelse(grepl("NA", g2p$position), NA, g2p$position)
+g2p_filt <- subset(g2p, grepl("^CID", g2p$DrugID))
+
+g2p_dgls <-  unique(g2p_filt$Drug_Gene_Lin[!is.na(g2p_filt$Drug_Gene_Lin)])
+g2p_druggenes <- unique(g2p_filt$Drug_Gene[!is.na(g2p_filt$Drug_Gene)])
+g2p_drugs <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[1]))
+g2p_genes <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[2]))
+g2p_lins <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[3]))
+# g2p_druggenes
+# g2p_drugs
+# g2p_genes
+# g2p_lins
+
+# Order and genes taken from pink heatmapo from Daniel's analyses
+g2p_genes <- c("EGFR", "KRAS", "ERBB2", "ERBB3", "MET", "ALK", "ROS1", "PDGFRA", "ABL1", "KIT", "PDGFRB", "PDGFB", "BRAF", "G6PD", "RET", "BRCA1", "BRCA2", "UGT1A1", "TSC1", "TSC2", "AKT1", "IDH2", "DPYD", "ESR1", "CYP19A1", "TPMT", "FLT3", "NPM1", "DNMT3A", "PML", "PTCH1", "JAK2", "MYD88", "MGMT")
+```
+
+Drug metadata and gene expression data:
+```{r}
+drug_meta <- read.delim("./data_munging/drug_id_drug_name_table_10_12_2018.tsv", sep = "\t", header = FALSE)
+colnames(drug_meta) <- c("CID", "Drug")
+drug_meta$Drug <- tolower(drug_meta$Drug)
+
+ge_melt_18Q3 <- readRDS("./../htscreens_giant_files/ge_melt_18Q3.rds")
+# ge <- filter(ge_melt_18Q3, DepMap_ID %in% ach2cvcl$DepMap_ID)
+# ge <- dcast(ge[sample(nrow(ge), 5000),], CCLE_Name + DepMap_ID ~ Hugo_Symbol, value.var = "RPKM")
+ge <- filter(ge_melt_18Q3, Hugo_Symbol %in% g2p_genes)
+ge <- dcast(ge, CCLE_Name + DepMap_ID ~ Hugo_Symbol, value.var = "RPKM")
+ge <- merge(ach2cvcl, ge, by = "DepMap_ID")
+rownames(ge) <- ge$accession_id
+ge[, 1:3] <- NULL
+ge[] <- sapply(ge, function(x) log2(x + 0.25))
+```
+
+## CCLE
+
+```{r}
+ccle <- read.delim("./data_munging/data_drug_auc_ccle_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
+ccle <- merge(drug_meta, ccle, by = "CID")
+ccle <- filter(ccle, Drug %in% g2p_drugs)
+rownames(ccle) <- ccle$Drug
+ccle$Drug <- NULL
+ccle$CID <- NULL
+ccle$Dataset <- NULL
+ccle[] <- sapply(ccle, function(x) as.numeric(as.character(x)))
+ccle <- t(ccle)
+
+ccle <- ccle[intersect(rownames(ccle), rownames(ge)),]
+ge_ccle <- ge[intersect(rownames(ccle), rownames(ge)),]
+
+# Test only erlotinib
+ccle_eqn <- data.frame(depy = I(as.matrix(ccle[,2])), indx = I(as.matrix(ge_ccle))) 
+ccle_plsr1 <- plsr(depy ~ indx, data = ccle_eqn, validation = "LOO")
+summary(ccle_plsr1)
+
+par(mfrow = c(1, 2))
+ccle_erlot_ncomp.onesigma <- selectNcomp(ccle_plsr1, method = "onesigma", plot = TRUE, main = "One-Sigma")
+ccle_erlot_ncomp.permut <- selectNcomp(ccle_plsr1, method = "randomization", plot = TRUE, main = "Permutation")
+par(mfrow = c(1, 1))
+```
+
+```{r}
+plot(RMSEP(ccle_plsr1))
+plot(ccle_plsr1, ncomp = ccle_erlot_ncomp.onesigma, asp = 1, line = TRUE)
+plot(ccle_plsr1, plottype = "scores", comps = 1:5)
+plot(ccle_plsr1, plottype = "loadings", comps = 1:5, legendpos = "topright")
+plot(ccle_plsr1, plottype = "correlation", comps = 1:5)
+plot(ccle_plsr1, plottype = "coef", ncomp = 1:5, legendpos = "topright")
+```
+
+## CTRP
+
+```{r}
+ctrp <- read.delim("./data_munging/data_drug_auc_ctrp_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
+ctrp <- merge(drug_meta, ctrp, by = "CID")
+ctrp <- filter(ctrp, Drug %in% g2p_drugs)
+rownames(ctrp) <- ctrp$Drug
+ctrp$Drug <- NULL
+ctrp$CID <- NULL
+ctrp$Dataset <- NULL
+ctrp[] <- sapply(ctrp, function(x) as.numeric(as.character(x)))
+ctrp <- t(ctrp)
+
+ctrp <- ctrp[intersect(rownames(ctrp), rownames(ge)),]
+ge_ctrp <- ge[intersect(rownames(ctrp), rownames(ge)),]
+
+ctrp_eqn <- data.frame(depy = I(as.matrix(ctrp[,6])), indx = I(as.matrix(ge_ctrp))) 
+ctrp_plsr1 <- plsr(depy ~ indx, data = ctrp_eqn, validation = "LOO")
+summary(ctrp_plsr1)
+```
+
+```{r, eval=FALSE}
+ctrp_plsr <- list()
+for(i in 1:ncol(ctrp)) {
+  ctrp_eqn <- data.frame(depy = I(as.matrix(ctrp[,i])), indx = I(as.matrix(ge_ctrp)))
+  ctrp_plsr_new <- plsr(depy ~ indx, data = ctrp_eqn, validation = "LOO")
+  ctrp_plsr[[i]] <- ctrp_plsr_new
+  # summary(ctrp_plsr1)
+}
+names(ctrp_plsr) <- colnames(ctrp)
+
+test <- selectNcomp(ctrp_plsr[["fluorouracil"]], method = "randomization", plot = TRUE)
+```

### 2019-03-05 19Q1.Rmd
renamed Rmds to separate DepMap releases more clearly

--- 2019-01-24 manuscript_analysis.Rmd
@@
 ---
-title: "Manuscript"
+title: "19Q1"
 author: "Sally Claridge"
@@
 ```
-
-# FUNCTIONS {.tabset .tabset-fade .tabset-pills}
-
---------------------------------------------------------------------------------
-
-## Significance thresholding
-
-```{r}
-adj_signif <- function(df, alpha) {
-  # Takes df from compare_means and creates a signif code column for FDR-adjusted p-vals for provided alpha
-  a <- alpha
-  i <- seq(along.with = df$p)
-  m <- nrow(df)
-  x <- sort(df$p) < i / m * a
-  if(length(unique(x)) == 2) {
-    k <- max(which(sort(df$p) < i/ m * a))
-    cutoff <- sort(df$p)[k]
-  }
-  else {
-    k <- NA
-    cutoff <- NA
-  }
-  df$p.signif.adj <- ifelse(df$p.adj <= cutoff, "*", NA)
-  df$p.signif <- ifelse(df$p.signif == "ns", NA, df$p.signif)
-  df$p.short <- formatC(df$p, format = "g", digits =  2)
-  df$p.adj.short <- formatC(df$p.adj, format = "g", digits =  2)
-  df$k <- k
-  df$FDR_cutoff <- cutoff
-  return(df)
-}
-```
-
-## Wilcoxon tests by drug
-
-```{r}
-# WilcoxonByDrugAllGenes <- function(melt_file, grid_file, data_name) {
-#   druglist <- as.character(unique(melt_file$Drug))
-#   sig_df <- NULL
-#   for(i in 1:length(druglist)) {
-#     print(paste0("Current drug in process: ", druglist[i], " (drug ", i, " of ", length(druglist), ")."))
-#     flush.console()
-#     melted <- filter(melt_file, Drug == druglist[i])
-#     use_data <- merge(grid_file, melted, by = "accession_id", all.x = TRUE)
-#     use_data <- merge(use_data, ccl_converter, by = "accession_id", all.x = TRUE)
-#     use_data <- merge(use_data, maf_df, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
-#     use_data$Mutation_Status_Nonsilent <- ifelse(is.na(use_data$Mutation_Status_Nonsilent), "Wildtype", use_data$Mutation_Status_Nonsilent)
-#     use_data$Hugo_Symbol <- factor(use_data$Hugo_Symbol)
-#     use_data$AUC <- as.numeric(use_data$AUC)
-#     use_data <- filter(use_data, !is.na(use_data$AUC))
-#     use_data$Drug_Gene <- paste0(use_data$Drug, "_", use_data$Hugo_Symbol)
-#     use_data_ptmuts <- filter(use_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
-#     use_data_ptmuts$Keep_PtMut_Tests <- ifelse(use_data_ptmuts$Reference_Allele_Length == 1 | is.na(use_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(use_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
-#     use_data_ptmuts <- filter(use_data_ptmuts, Keep_PtMut_Tests == TRUE)
-#     
-#     sig <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = "Hugo_Symbol", data = use_data_ptmuts, method = "wilcox.test", p.adjust.method = "BH")
-#     sig <- adj_signif(sig)
-#     sig <- sig[order(sig$p),]
-#     sig <- filter(sig, p <= 0.05)
-#     sig$Drug <- druglist[i]
-#     sig$Dataset <- toupper(data_name)
-#     sig_df <- rbind(sig_df, sig)
-#   }
-#   return(sig_df)
-# }
-```
-
-## Pearson correlation by lineage
-```{r}
-PearsonByLineage <- function(lin, dataset, variable) {
-  use_data <- filter(dataset, group_general_lineage_name == lin)
-  if(variable == "GE") {
-    use_data <- filter(use_data, !is.na(RPKM))
-    use_data_summ <- use_data %>% count(Drug_Gene)
-    use_data_summ <- filter(use_data_summ, n >= 3) # cor.test requires at least 3 non-NA data points
-    use_data_filt <- filter(use_data, Drug_Gene %in% as.character(unique(use_data_summ$Drug_Gene)))
-    if(nrow(use_data_filt) > 0) {
-      pearson_res <- use_data_filt %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$estimate, Pearson_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$p.value)
-      pearson_res <- merge(g2p_druggene_tally, pearson_res, all.y = TRUE)
-      pearson_res$group_general_lineage_name <- lin
-      pearson_res$Pearson_GE_Abs <- abs(pearson_res$Pearson_Corr_GE)
-      pearson_res$Pearson_GE_Sign <- ifelse(sign(pearson_res$Pearson_Corr_GE) == 1, "+",
-                                              ifelse(sign(pearson_res$Pearson_Corr_GE) == -1, "-", "0"))
-      return(pearson_res)
-    }
-  }
-  else if(variable == "CN") {
-    use_data <- filter(use_data, !is.na(CN))
-    use_data_summ <- use_data %>% count(Drug_Gene)
-    use_data_summ <- filter(use_data_summ, n >= 3) # cor.test requires at least 3 non-NA data points
-    use_data_filt <- filter(use_data, Drug_Gene %in% as.character(unique(use_data_summ$Drug_Gene)))
-    if(nrow(use_data_filt) > 0) {
-      pearson_res <- use_data_filt %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$estimate, Pearson_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$p.value)
-      pearson_res <- merge(g2p_druggene_tally, pearson_res, all.y = TRUE)
-      pearson_res$group_general_lineage_name <- lin
-      pearson_res$Pearson_CN_Abs <- abs(pearson_res$Pearson_Corr_CN)
-      pearson_res$Pearson_CN_Sign <- ifelse(sign(pearson_res$Pearson_Corr_CN) == 1, "+",
-                                              ifelse(sign(pearson_res$Pearson_Corr_CN) == -1, "-", "0"))
-      return(pearson_res)
-    }
-  }
-}
-```
-
-## Save widget to new directory
-```{r}
-saveWidgetFix <- function (widget , file, ...) {
-  ## A wrapper to saveWidget which compensates for arguable BUG in
-  ## saveWidget which requires `file` to be in current working
-  ## directory.
-  wd <- getwd()
-  on.exit(setwd(wd))
-  outDir <- dirname(file)
-  file <- basename(file)
-  setwd(outDir);
-  saveWidget(widget, file = file,...)
-}
-```
-
-## Make lineage mut plots
-
-```{r}
-MutPlotsByLineage <- function(lineage_name) {
-
-  use_data <- filter(dgl_mut_grid_summ, group_general_lineage_name == lineage_name)
-  use_data$Dataset <- factor(use_data$Dataset, levels = c("CCLE", "CTRP", "GDSC"))
-  ticker <- 0
-
-  use_data_ccle <- filter(use_data, Dataset == "CCLE")
-  use_data_ccle_summ <- use_data_ccle %>% count(InG2P)
-  ccle_lin_p_ttest <- data.frame(statistic = NA,
-                                 parameter =  NA,
-                                 p.value = NA)
-  if(nrow(use_data_ccle_summ) <= 1) {
-    ccle_lin_p_ttest_res <-  NA
-    ticker <- ticker + 1
-    }
-  else if(use_data_ccle_summ[use_data_ccle_summ$InG2P == "Yes",]$nn < 2) { ccle_lin_p_ttest_res <-  NA }
-  else if(use_data_ccle_summ[use_data_ccle_summ$InG2P == "Yes",]$nn >= 2) {
-    ccle_lin_p_ttest <- t.test(use_data_ccle$p ~ use_data_ccle$InG2P)
-    ccle_lin_p_ttest_res <- paste0("t(", trunc(ccle_lin_p_ttest$parameter), ") = ", round(ccle_lin_p_ttest$statistic, 2), ", p = ", round(ccle_lin_p_ttest$p.value, 3))
-  }
-
-  use_data_ctrp <- filter(use_data, Dataset == "CTRP")
-  use_data_ctrp_summ <- use_data_ctrp %>% count(InG2P)
-  ctrp_lin_p_ttest <- data.frame(statistic = NA,
-                                 parameter =  NA,
-                                 p.value = NA)
-  if(nrow(use_data_ctrp_summ) <= 1) {
-    ctrp_lin_p_ttest_res <-  NA
-    ticker <- ticker + 1
-    }
-  else if(use_data_ctrp_summ[use_data_ctrp_summ$InG2P == "Yes",]$nn < 2) { ctrp_lin_p_ttest_res <-  NA }
-  else if(use_data_ctrp_summ[use_data_ctrp_summ$InG2P == "Yes",]$nn >= 2) {
-    ctrp_lin_p_ttest <- t.test(use_data_ctrp$p ~ use_data_ctrp$InG2P)
-    ctrp_lin_p_ttest_res <- paste0("t(", trunc(ctrp_lin_p_ttest$parameter), ") = ", round(ctrp_lin_p_ttest$statistic, 2), ", p = ", round(ctrp_lin_p_ttest$p.value, 3))
-  }
-
-  use_data_gdsc <- filter(use_data, Dataset == "GDSC")
-  use_data_gdsc_summ <- use_data_gdsc %>% count(InG2P)
-  gdsc_lin_p_ttest <- data.frame(statistic = NA,
-                                 parameter =  NA,
-                                 p.value = NA)
-  if(nrow(use_data_gdsc_summ) <= 1) {
-    gdsc_lin_p_ttest_res <-  NA
-    ticker <- ticker + 1
-    }
-  else if(use_data_gdsc_summ[use_data_gdsc_summ$InG2P == "Yes",]$nn < 2) { gdsc_lin_p_ttest_res <-  NA }
-  else if(use_data_gdsc_summ[use_data_gdsc_summ$InG2P == "Yes",]$nn >= 2) {
-    gdsc_lin_p_ttest <- t.test(use_data_gdsc$p ~ use_data_gdsc$InG2P)
-    gdsc_lin_p_ttest_res <- paste0("t(", trunc(gdsc_lin_p_ttest$parameter), ") = ", round(gdsc_lin_p_ttest$statistic, 2), ", p = ", round(gdsc_lin_p_ttest$p.value, 3))
-  }
-
-  y_value <- ifelse(ticker == 3, 10, max(use_data$n) + max(use_data$n) * 0.1)
-
-  summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"),
-                          Test_Results_p = c(ccle_lin_p_ttest_res, ctrp_lin_p_ttest_res, gdsc_lin_p_ttest_res),
-                          t_statistic = c(round(ccle_lin_p_ttest$statistic, 3), round(ctrp_lin_p_ttest$statistic, 3), round(gdsc_lin_p_ttest$statistic, 3)),
-                          df = c(trunc(ccle_lin_p_ttest$parameter), trunc(ctrp_lin_p_ttest$parameter), trunc(gdsc_lin_p_ttest$parameter)),
-                          p_value = c(round(ccle_lin_p_ttest$p.value, 3), round(ctrp_lin_p_ttest$p.value, 3), round(gdsc_lin_p_ttest$p.value, 3)),
-                          group_general_lineage_name = lineage_name)
-  plot_point <- ggplot(data = use_data) +
-    facet_wrap(~ Dataset, drop = FALSE) +
-    coord_cartesian(xlim = c(0, 1), ylim = c(0, y_value)) +
-    scale_x_continuous(breaks = seq(0, 1, by = 0.1), labels = seq(0, 1, by = 0.1)) +
-    scale_y_continuous(breaks = pretty_breaks()) +
-    geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = p, y = n), alpha = 0.5) +
-    scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-    geom_text_repel(data = subset(use_data, InG2P == "Yes"), mapping = aes(x = p, y = n, label = Drug_Gene), size = 3, segment.size = 0.2, segment.color = "grey50") +
-    geom_text(data = summ_text, mapping = aes(x = 0.5, y = y_value, label = Test_Results_p), nudge_y = 0.1) +
-    labs(x = "Drug-gene association p-value between mutation groups", y = "Number of level A G2P associations") +
-    theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
-  plot_box <- ggplot(data = use_data) +
-    facet_wrap(~ Dataset, drop = FALSE) +
-    coord_cartesian(ylim = c(0, 1)) +
-    scale_y_continuous(breaks = seq(0, 1, by = 0.1), labels = seq(0, 1, by = 0.1)) +
-    geom_violin(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.5) +
-    geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.75, width = 0.25) +
-    scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-    coord_flip() +
-    labs(x = "In G2P?", title = toupper(lineage_name)) +
-    theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-  plot <- subplot(plot_box, plot_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(title = toupper(lineage_name), margin = list(t = 75, l = 75), xaxis5 = list(title = "Gene-drug association p-value between mutation groups"), yaxis = list(title = "Level A G2P\nassociation", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
-
-  plot_point <- ggplot_gtable(ggplot_build(plot_point))
-  plot_box <- ggplot_gtable(ggplot_build(plot_box))
-  p_maxWidth <-  grid::unit.pmax(plot_point$widths, plot_box$widths)
-  plot_point$widths <- as.list(p_maxWidth)
-  plot_box$widths <- as.list(p_maxWidth)
-
-  mut_plot <- cowplot::plot_grid(plot_box,
-                     plot_point,
-                     nrow = 2,
-                     rel_heights = c(1, 4))
-
-  saveWidgetFix(widget = plot, file = paste0("./plots/manuscript/plotlys_mut_by_lineage_grid/", lineage_name, "_mut_plotly_grid.html"))
-  ggsave(paste0("./plots/manuscript/pngs_mut_by_lineage_grid/", lineage_name, "_mut_plot_grid.png"), mut_plot, device = "png", dpi = 450, width = 12, height = 6, units =   "in")
-
-  return(summ_text)
-}
-```
-
-## Make lineage GE/CN plots
-
-```{r}
-PearsonPlotsByLineage <- function(lineage) {
-  print(paste0("Lineage: ", toupper(lineage)))
-  use_data <- filter(dgl_signif_pearson_g2p_grid, group_general_lineage_name == lineage)
-  use_data$Dataset <- factor(use_data$Dataset, levels = c("CCLE", "CTRP", "GDSC"))
-  use_data$Pearson_GE_Label <- paste0(round(use_data$Pearson_Pval_GE, 3), "\nDrug_Gene: ", use_data$Drug_Gene)
-  use_data$Pearson_CN_Label <- paste0(round(use_data$Pearson_Pval_CN, 3), "\nDrug_Gene: ", use_data$Drug_Gene)
-  ticker_ge <- 0
-  ticker_cn <- 0
-  ticker <- 0
-
-  use_data_ccle <- filter(use_data, Dataset == "CCLE")
-  use_data_ccle_ge_summ <- use_data_ccle[!is.na(use_data_ccle$Pearson_GE_Abs),] %>% count(InG2P)
-  use_data_ccle_cn_summ <- use_data_ccle[!is.na(use_data_ccle$Pearson_CN_Abs),] %>% count(InG2P)
-  ccle_ge_ttest <- data.frame(statistic = NA, parameter = NA, p.value = NA)
-  ccle_cn_ttest <- data.frame(statistic = NA, parameter = NA, p.value = NA)
-  if(nrow(use_data_ccle_ge_summ) <= 1) {
-    ccle_ge_res <-  NA
-    ticker_ge <- ticker_ge + 1
-  }
-  else if(use_data_ccle_ge_summ[use_data_ccle_ge_summ$InG2P == "Yes",]$nn < 2) {
-    ccle_ge_res <-  NA
-  }
-  else if(use_data_ccle_ge_summ[use_data_ccle_ge_summ$InG2P == "Yes",]$nn >= 2) {
-    ccle_ge_ttest <- t.test(use_data_ccle$Pearson_GE_Abs ~ use_data_ccle$InG2P)
-    ccle_ge_res <- paste0("t(", trunc(ccle_ge_ttest$parameter), ") = ", round(ccle_ge_ttest$statistic, 2), ", p = ", round(ccle_ge_ttest$p.value, 3))
-  }
-  if(nrow(use_data_ccle_cn_summ) <= 1) {
-    ccle_cn_res <-  NA
-    ticker_cn <- ticker_cn + 1
-  }
-  else if(use_data_ccle_cn_summ[use_data_ccle_cn_summ$InG2P == "Yes",]$nn < 2) {
-    ccle_cn_res <-  NA
-  }
-  else if(use_data_ccle_cn_summ[use_data_ccle_cn_summ$InG2P == "Yes",]$nn >= 2) {
-    ccle_cn_ttest <- t.test(use_data_ccle$Pearson_CN_Abs ~ use_data_ccle$InG2P)
-    ccle_cn_res <- paste0("t(", trunc(ccle_cn_ttest$parameter), ") = ", round(ccle_cn_ttest$statistic, 2), ", p = ", round(ccle_cn_ttest$p.value, 3))
-  }
-  print("CCLE testing: DONE")
-
-  use_data_ctrp <- filter(use_data, Dataset == "CTRP")
-  use_data_ctrp_ge_summ <- use_data_ctrp[!is.na(use_data_ctrp$Pearson_GE_Abs),] %>% count(InG2P)
-  use_data_ctrp_cn_summ <- use_data_ctrp[!is.na(use_data_ctrp$Pearson_CN_Abs),] %>% count(InG2P)
-  ctrp_ge_ttest <- data.frame(statistic = NA, parameter = NA, p.value = NA)
-  ctrp_cn_ttest <- data.frame(statistic = NA, parameter = NA, p.value = NA)
-  if(nrow(use_data_ctrp_ge_summ) <= 1) {
-    ctrp_ge_res <-  NA
-    ticker_ge <- ticker_ge + 1
-  }
-  else if(use_data_ctrp_ge_summ[use_data_ctrp_ge_summ$InG2P == "Yes",]$nn < 2) {
-    ctrp_ge_res <-  NA
-  }
-  else if(use_data_ctrp_ge_summ[use_data_ctrp_ge_summ$InG2P == "Yes",]$nn >= 2) {
-    ctrp_ge_ttest <- t.test(use_data_ctrp$Pearson_GE_Abs ~ use_data_ctrp$InG2P)
-    ctrp_ge_res <- paste0("t(", trunc(ctrp_ge_ttest$parameter), ") = ", round(ctrp_ge_ttest$statistic, 2), ", p = ", round(ctrp_ge_ttest$p.value, 3))
-  }
-  if(nrow(use_data_ctrp_cn_summ) <= 1) {
-    ctrp_cn_res <-  NA
-    ticker_cn <- ticker_cn + 1
-  }
-  else if(use_data_ctrp_cn_summ[use_data_ctrp_cn_summ$InG2P == "Yes",]$nn < 2) {
-    ctrp_cn_res <-  NA
-  }
-  else if(use_data_ctrp_cn_summ[use_data_ctrp_cn_summ$InG2P == "Yes",]$nn >= 2) {
-    ctrp_cn_ttest <- t.test(use_data_ctrp$Pearson_CN_Abs ~ use_data_ctrp$InG2P)
-    ctrp_cn_res <- paste0("t(", trunc(ctrp_cn_ttest$parameter), ") = ", round(ctrp_cn_ttest$statistic, 2), ", p = ", round(ctrp_cn_ttest$p.value, 3))
-  }
-  print("CTRP testing: DONE")
-
-  use_data_gdsc <- filter(use_data, Dataset == "GDSC")
-  use_data_gdsc_ge_summ <- use_data_gdsc[!is.na(use_data_gdsc$Pearson_GE_Abs),] %>% count(InG2P)
-  use_data_gdsc_cn_summ <- use_data_gdsc[!is.na(use_data_gdsc$Pearson_CN_Abs),] %>% count(InG2P)
-  gdsc_ge_ttest <- data.frame(statistic = NA, parameter = NA, p.value = NA)
-  gdsc_cn_ttest <- data.frame(statistic = NA, parameter = NA, p.value = NA)
-  if(nrow(use_data_gdsc_ge_summ) <= 1) {
-    gdsc_ge_res <-  NA
-    ticker_ge <- ticker_ge + 1
-  }
-  else if(use_data_gdsc_ge_summ[use_data_gdsc_ge_summ$InG2P == "Yes",]$nn < 2) {
-    gdsc_ge_res <-  NA
-  }
-  else if(use_data_gdsc_ge_summ[use_data_gdsc_ge_summ$InG2P == "Yes",]$nn >= 2) {
-    gdsc_ge_ttest <- t.test(use_data_gdsc$Pearson_GE_Abs ~ use_data_gdsc$InG2P)
-    gdsc_ge_res <- paste0("t(", trunc(gdsc_ge_ttest$parameter), ") = ", round(gdsc_ge_ttest$statistic, 2), ", p = ", round(gdsc_ge_ttest$p.value, 3))
-  }
-  if(nrow(use_data_gdsc_cn_summ) <= 1) {
-    gdsc_cn_res <-  NA
-    ticker_cn <- ticker_cn + 1
-  }
-  else if(use_data_gdsc_cn_summ[use_data_gdsc_cn_summ$InG2P == "Yes",]$nn < 2) {
-    gdsc_cn_res <-  NA
-  }
-  else if(use_data_gdsc_cn_summ[use_data_gdsc_cn_summ$InG2P == "Yes",]$nn >= 2) {
-    gdsc_cn_ttest <- t.test(use_data_gdsc$Pearson_CN_Abs ~ use_data_gdsc$InG2P)
-    gdsc_cn_res <- paste0("t(", trunc(gdsc_cn_ttest$parameter), ") = ", round(gdsc_cn_ttest$statistic, 2), ", p = ", round(gdsc_cn_ttest$p.value, 3))
-  }
-  print("GDSC testing: DONE")
-
-  y_value_ge <- ifelse(ticker_ge == 3, 10, max(use_data$n) + max(use_data$n) * 0.1)
-  y_value_cn <- ifelse(ticker_cn == 3, 10, max(use_data$n) + max(use_data$n) * 0.1)
-
-  summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"),
-                          Test_Results_GE = c(ccle_ge_res, ctrp_ge_res, gdsc_ge_res),
-                          t_statistic_GE = c(round(ccle_ge_ttest$statistic, 3), round(ctrp_ge_ttest$statistic, 3), round(gdsc_ge_ttest$statistic, 3)),
-                          df_GE = c(trunc(ccle_ge_ttest$parameter), trunc(ctrp_ge_ttest$parameter), trunc(gdsc_ge_ttest$parameter)),
-                          p_value_GE = c(round(ccle_ge_ttest$p.value, 3), round(ctrp_ge_ttest$p.value, 3), round(gdsc_ge_ttest$p.value, 3)),
-                          Test_Results_CN = c(ccle_cn_res, ctrp_cn_res, gdsc_cn_res),
-                          t_statistic_CN = c(round(ccle_cn_ttest$statistic, 3), round(ctrp_cn_ttest$statistic, 3), round(gdsc_cn_ttest$statistic, 3)),
-                          df_CN = c(trunc(ccle_cn_ttest$parameter), trunc(ctrp_cn_ttest$parameter), trunc(gdsc_cn_ttest$parameter)),
-                          p_value_CN = c(round(ccle_cn_ttest$p.value, 3), round(ctrp_cn_ttest$p.value, 3), round(gdsc_cn_ttest$p.value, 3)),
-                          group_general_lineage_name = lineage)
-
-  ## Gene expression
-  if(sum(!is.na(use_data$Pearson_GE_Abs)) > 0) {
-    plot_ge_point <- ggplot(data = use_data) +
-      facet_wrap(~ Dataset, drop = FALSE) +
-      scale_y_continuous(breaks = pretty_breaks()) +
-      geom_point(mapping = aes(label = Pearson_GE_Label, color = InG2P, fill = InG2P, shape = Pearson_GE_Sign, x = Pearson_GE_Abs, y = n), alpha = 0.5) +
-      scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
-      scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-      scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-      geom_text_repel(data = subset(use_data, InG2P == "Yes" & n > 10), aes(label = Drug_Gene, x = Pearson_GE_Abs, y = n), size = 3, segment.size = 0.2, segment.color = "grey50") +
-      geom_text(data = summ_text, mapping = aes(x = 0.5, y = y_value_ge, label = Test_Results_GE), nudge_y = 1) +
-      labs(y = "Number of level A G2P associations", x = "Pearson correlation coefficient between drug-gene AUC and gene expression") +
-      theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
-    plot_ge_box <- ggplot(data = use_data) +
-      facet_wrap(~ Dataset, drop = FALSE) +
-      geom_violin(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.5) +
-      geom_boxplot(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
-      scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-      coord_flip() +
-      labs(x = "In G2P?", title = toupper(lineage)) +
-      theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
-    plot_ge <- subplot(plot_ge_box, plot_ge_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>%
-               layout(title = lineage, margin = list(t = 75, l = 75),
-                      xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and gene expression"),
-                      yaxis = list(title = "In G2P?", domain = c(0.8, 1)),
-                      yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
-
-    png_ge_point <- ggplot_gtable(ggplot_build(plot_ge_point))
-    png_ge_box <- ggplot_gtable(ggplot_build(plot_ge_box))
-    p_maxWidth <-  grid::unit.pmax(png_ge_point$widths, png_ge_box$widths)
-    png_ge_point$widths <- as.list(p_maxWidth)
-    png_ge_box$widths <- as.list(p_maxWidth)
-
-    png_ge <- cowplot::plot_grid(png_ge_box, png_ge_point, nrow = 2, rel_heights = c(1, 4))
-    png_ge
-
-    saveWidgetFix(widget = plot_ge, file = paste0("./plots/manuscript/plotlys_ge_by_lineage_grid/", lineage, "_ge_plotly_grid.html"))
-    ggsave(paste0("./plots/manuscript/pngs_ge_by_lineage_grid/", lineage, "_ge_plot_grid.png"), png_ge, device = "png", dpi = 450, width = 12, height = 6, units = "in")
-    print("Gene expression plots: DONE")
-  }
-  else if(sum(!is.na(use_data$Pearson_GE_Abs)) == 0) { print("Gene expression plots: None") }
-
-  ## Copy number
-  if(sum(!is.na(use_data$Pearson_CN_Abs)) > 0) {
-    plot_cn_point <- ggplot(data = use_data) +
-      facet_wrap(~ Dataset, drop = FALSE) +
-      scale_y_continuous(breaks = pretty_breaks()) +
-      geom_point(mapping = aes(label = Pearson_CN_Label, color = InG2P, fill = InG2P, shape = Pearson_CN_Sign, x = Pearson_CN_Abs, y = n), alpha = 0.5, position = position_jitter(width = 0, height = 0.15)) +
-      scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
-      scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-      scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-      geom_text_repel(data = subset(use_data, InG2P == "Yes"  & n > 10), aes(label = Drug_Gene, x = Pearson_CN_Abs, y = n), size = 3, segment.size = 0.2, segment.color = "grey50") +
-      geom_text(data = summ_text, mapping = aes(x = 0.5, y = y_value_cn, label = Test_Results_CN), nudge_y = 1) +
-      labs(y = "Number of level A G2P associations", x = "Pearson correlation coefficient between drug-gene AUC and copy number") +
-      theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
-    plot_cn_box <- ggplot(data = use_data) +
-      facet_wrap(~ Dataset, drop = FALSE) +
-      geom_violin(mapping = aes(color = InG2P, y = Pearson_CN_Abs, x = InG2P), alpha = 0.5) +
-      geom_boxplot(mapping = aes(color = InG2P, y = Pearson_CN_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
-      scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-      coord_flip() +
-      labs(x = "In G2P?", title = toupper(lineage)) +
-      theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
-    plot_cn <- subplot(plot_cn_box, plot_cn_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>%
-               layout(title = lineage, margin = list(t = 75, l = 75),
-                      xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and copy number"),
-                      yaxis = list(title = "In G2P?", domain = c(0.8, 1)),
-                      yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
-
-    png_cn_point <- ggplot_gtable(ggplot_build(plot_cn_point))
-    png_cn_box <- ggplot_gtable(ggplot_build(plot_cn_box))
-    p_maxWidth <-  grid::unit.pmax(png_cn_point$widths, png_cn_box$widths)
-    png_cn_point$widths <- as.list(p_maxWidth)
-    png_cn_box$widths <- as.list(p_maxWidth)
-
-    png_cn <- cowplot::plot_grid(png_cn_box, png_cn_point, nrow = 2, rel_heights = c(1, 4))
-    png_cn
-
-    saveWidgetFix(widget = plot_cn, file = paste0("./plots/manuscript/plotlys_cn_by_lineage_grid/", lineage, "_cn_plotly_grid.html"))
-    ggsave(paste0("./plots/manuscript/pngs_cn_by_lineage_grid/", lineage, "_cn_plot_grid.png"), png_cn, device = "png", dpi = 450, width = 12, height = 6, units = "in")
-    print("Copy number plots: DONE")
-  }
-  else if(sum(!is.na(use_data$Pearson_CN_Abs)) == 0) { print("Copy number plots: None") }
-
-  return(summ_text)
-}
-```
-
-## Make per-drug boxplots
-```{r}
-makeDrugBoxplots <- function(drug, dataset) {
-  if(dataset == "CCLE" | dataset == "ccle") {
-    use_data <- filter(ccle_data_ptmuts, Drug == drug)
-    use_color <- as.character(use_data$Color_Nonsilent)
-    names(use_color) <- use_data$Mutation_Status_Nonsilent
-    sig <- ccle_signif_g2p_ByDrug[[drug]]
-    label_text <- data.frame(p.signif = sig$p.signif, p.signif.adj = sig$p.signif.adj, Hugo_Symbol = sig$Hugo_Symbol)
-    label_text$Hugo_Symbol <- factor(label_text$Hugo_Symbol, levels = g2p_genes)
-  }
-  else if(dataset == "CTRP" | dataset == "ctrp") {
-    use_data <- filter(ctrp_data_ptmuts, Drug == drug)
-    use_color <- as.character(use_data$Color_Nonsilent)
-    names(use_color) <- use_data$Mutation_Status_Nonsilent
-    sig <- ctrp_signif_g2p_ByDrug[[drug]]
-    label_text <- data.frame(p.signif = sig$p.signif, p.signif.adj = sig$p.signif.adj, Hugo_Symbol = sig$Hugo_Symbol)
-    label_text$Hugo_Symbol <- factor(label_text$Hugo_Symbol, levels = g2p_genes)
-  }
-  else if(dataset == "GDSC" | dataset == "gdsc") {
-    use_data <- filter(gdsc_data_ptmuts, Drug == drug)
-    use_color <- as.character(use_data$Color_Nonsilent)
-    names(use_color) <- use_data$Mutation_Status_Nonsilent
-    sig <- gdsc_signif_g2p_ByDrug[[drug]]
-    label_text <- data.frame(p.signif = sig$p.signif, p.signif.adj = sig$p.signif.adj, Hugo_Symbol = sig$Hugo_Symbol)
-    label_text$Hugo_Symbol <- factor(label_text$Hugo_Symbol, levels = g2p_genes)
-  }
-  else { return("Error: Invalid dataset.") }
-
-  plot <- ggplot(data = use_data, aes(x = Mutation_Status_Nonsilent, y = AUC)) +
-    facet_wrap(~ Hugo_Symbol, drop = FALSE, nrow = 1) +
-    geom_boxplot(mapping = aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85), outlier.shape = 3, outlier.size = 0.5) +
-    scale_fill_manual(values = use_color) +
-    guides(color = FALSE) +
-    geom_text(data = label_text, mapping = aes(x = 1.5, y = max(use_data$AUC), label = p.signif), nudge_y = 0.2) +
-    theme(strip.text.x = element_text(size = 10, angle = 45), legend.position = "top", axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
-    labs(fill = "Mutation Status", y = "AUC", x = "Mutation Status", title = paste0(toupper(dataset), ": ", drug))
-  return(plot)
-}
-```
-
-# DATA MANAGEMENT {.tabset .tabset-fade .tabset-pills}
-
---------------------------------------------------------------------------------
-
-## D. Charytonowicz cell line converter
-
-This comprehensive cancer cell line information curated by Daniel Charytonowicz.
-```{r}
-ccl_converter <- read.delim("./data_munging/cell_line_database_v1_20180911.tsv", row.names = 1, sep = "\t", header = TRUE)
-lineage_converter <- unique(ccl_converter[, c("grouped_general_doid", "group_general_lineage_name")])
-colnames(ccl_converter)[colnames(ccl_converter) == "Broad_ID"] <- "DepMap_ID"
-```
-
-## DepMap cell line metadata
-
-```{r}
-ccl_info <- read.delim("./data_munging/18Q4/DepMap-2018q4-celllines_20181115.csv", sep = ",", header = TRUE, na.strings = c("", NA))
-ccl_info$Primary.Disease <- gsub("\\\\", "", ccl_info$Primary.Disease)
-ccl_info$Primary.Disease <- gsub("Ewings", "Ewing's", ccl_info$Primary.Disease)
-# From figshare
-crispr_meta <- read.delim("./data_munging/18Q4/sample_info_18Q4_crispr_20181115.csv", sep = ",", header = TRUE, na.strings = c("", NA))
-colnames(crispr_meta)[7] <- "CCLE_Name"
-```
-
-## CCLE genomic annotations
-
-### Mutation status (Mut)
-
-For mutation calling, get paired gene name and cell line fields in a data frame.
-For this analysis, we don't care about how many mutations there are per gene or what type of mutations there are, so I didn't save more information.
-I took unique gene-cell line combinations since we only cared about mutation presence/absence.
-Add a `Mutation_Status` column denoting all entries in MAF files as mutations present in the associated cell lines.
-
-Mutation calls (coding region, germline filtered):
-```{r, eval=FALSE}
-maf_raw <- read.delim("./data_munging/18Q4/depmap_18Q4_mutation_calls_20181114.csv.gz", header = TRUE, sep = ",", row.names = 1)
-colnames(maf_raw)[colnames(maf_raw) == "Tumor_Sample_Barcode"] <- "CCLE_Name"
-# Select columns
-maf_df <- subset(maf_raw, select = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID", "Variant_Classification", "Reference_Allele", "Tumor_Seq_Allele1", "Genome_Change"))
-maf_df$Reference_Allele <- ifelse(maf_df$Reference_Allele == "-", 0, nchar(as.character(maf_df$Reference_Allele)))
-maf_df$Tumor_Seq_Allele1 <- nchar(as.character(maf_df$Tumor_Seq_Allele1))
-maf_df <- maf_df[maf_df$Variant_Classification != "Silent",]
-# Add Mutation_Status column
-maf_df$Mutation_Status_Nonsilent <- "Mutant"
-
-saveRDS(maf_df, "./data_munging/rds/maf_df_18Q4.rds", compress = "xz")
-```
-
-### Copy number (CN)
-
-DepMap WES CN Data:
-```{r, eval=FALSE}
-cn <- read.delim("./data_munging/18Q4/public_18Q4_gene_cn_20181115.csv.gz", sep = ",", check.names = FALSE, header = TRUE)
-# Remove Entrez gene IDs from colnames
-# Format: Hugo_Symbol (Entrez ID)
-colnames(cn) <- gsub(" .*", "", colnames(cn))
-# Melt
-cn_melt <- melt(data = cn, id.vars = "DepMap_ID", measure.vars = colnames(cn[2:ncol(cn)]), variable.name = "Hugo_Symbol", value.name = "CN")
-saveRDS(cn_melt, "./data_munging/rds/cn_melt_18Q4.rds", compress = "xz")
-```
-
-### Gene expression (GE)
-
-18Q3, Gene expression data (Reads Per Kilobase of transcript, per Million mapped reads, RPKM).
-```{r, eval=FALSE}
-ge_18Q3 <- read.delim("./../htscreens_giant_files/CCLE_DepMap_18q3_RNAseq_RPKM_20180718.gct.gz", skip = 2, header = TRUE, sep = "\t", check.names = FALSE)
-# Edit columns
-ge_18Q3$Name <- NULL
-colnames(ge_18Q3)[1] <- "Hugo_Symbol"
-# Melt
-ge_melt_18Q3 <- melt(data = ge_18Q3, id.vars = "Hugo_Symbol", measure.vars = colnames(ge_18Q3[2:ncol(ge_18Q3)]), value.name = "RPKM")
-## Split variable column
-ge_melt_18Q3 <- with(ge_melt_18Q3, cbind(Hugo_Symbol, colsplit(variable, pattern = " ", names = c("CCLE_Name", "DepMap_ID")), RPKM))
-## Remove parentheses around Broad IDs
-ge_melt_18Q3$DepMap_ID <- gsub("\\(|\\)", "", ge_melt_18Q3$DepMap_ID)
-saveRDS(ge_melt_18Q3, "./../htscreens_giant_files/ge_melt_18Q3.rds", compress = "xz")
-```
-
-18Q4, CCLE RNAseq gene expression data (log2(TPM+1)):
-```{r, eval=FALSE}
-ge_18Q4 <- read.delim("./../htscreens_giant_files/CCLE_depMap_18Q4_TPM_v2_20181115.csv.gz", header = TRUE, sep = ",", check.names = FALSE)
-# Remove Entrez gene IDs from colnames
-# Format: Hugo_Symbol (Entrez ID)
-colnames(ge_18Q4) <- gsub(" .*", "", colnames(ge_18Q4))
-colnames(ge_18Q4)[1] <- "DepMap_ID"
-# Melt
-ge_melt_18Q4_all <- melt(ge_18Q4, id.vars = "DepMap_ID", measure.vars = colnames(ge_18Q4)[2:ncol(ge_18Q4)], variable.name = "Hugo_Symbol", value.name = "TPM")
-ge_melt_18Q4 <- unique(ge_melt_18Q4)
-saveRDS(ge_melt_18Q4, "./data_munging/rds/ge_melt_18Q4.rds", compress = "xz")
-```
-
-## G2P
-
-```{r}
-g2p <- read.delim("./data_munging/g2p_full_level_A_dataset_NEW_DEC_2_2018_withGroupedLineages.csv", sep = "\t", header = TRUE)
-g2p[, 1:2] <- NULL
-g2p <- merge(g2p, lineage_converter, by = "grouped_general_doid", all.x = TRUE)
-
-g2p$Drug <- tolower(g2p$Drug)
-g2p[g2p == -1] <- NA
-g2p$Ref[g2p$Ref == "None"] <- NA
-g2p$Alt[g2p$Alt == "None"] <- NA
-g2p$Drug_Gene <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene), NA, paste0(g2p$Drug, "_", g2p$Gene))
-g2p$Drug_Gene_Lin <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene) | is.na(g2p$group_general_lineage_name), NA, paste0(g2p$Drug, "_", g2p$Gene, "_", g2p$group_general_lineage_name))
-g2p$position <- paste0("g.chr", g2p$Chromosome, ":", g2p$End, g2p$Ref, ">", g2p$Alt)
-g2p$position <- ifelse(grepl("NA", g2p$position), NA, g2p$position)
-g2p_filt <- subset(g2p, grepl("^CID", g2p$DrugID))
-
-g2p_dgls <-  unique(g2p_filt$Drug_Gene_Lin[!is.na(g2p_filt$Drug_Gene_Lin)])
-g2p_druggenes <- unique(g2p_filt$Drug_Gene[!is.na(g2p_filt$Drug_Gene)])
-g2p_drugs <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[1]))
-g2p_genes <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[2]))
-g2p_lins <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[3]))
-g2p_druggenes
-g2p_drugs
-g2p_genes
-g2p_lins
-
-# Order and genes taken from pink heatmapo from Daniel's analyses
-g2p_genes <- c("EGFR", "KRAS", "ERBB2", "ERBB3", "MET", "ALK", "ROS1", "PDGFRA", "ABL1", "KIT", "PDGFRB", "PDGFB", "BRAF", "G6PD", "RET", "BRCA1", "BRCA2", "UGT1A1", "TSC1", "TSC2", "AKT1", "IDH2", "DPYD", "ESR1", "CYP19A1", "TPMT", "FLT3", "NPM1", "DNMT3A", "PML", "PTCH1", "JAK2", "MYD88", "MGMT")
-```
-
-```{r}
-# levels(g2p_filt$Phenotype.Description)
-unique(g2p_filt$group_general_lineage_name)
-levels(g2p_filt$group_general_lineage_name)
-
-g2p_nonCID <- subset(g2p, !grepl("^CID", g2p$DrugID))
-summ <- g2p_nonCID %>% group_by(Drug, DrugID) %>% tally() %>% summarize(DrugID = DrugID, n = n, percent = formatC(n / 402 * 100, digits = 6, format = "f"))
-summ
-```
-
-```{r, eval=FALSE}
-maf_df <- readRDS("./data_munging/rds/maf_df_18Q4.rds")
-cn_melt <- readRDS("./data_munging/rds/cn_melt_18Q4.rds")
-ge_melt_18Q3 <- readRDS("./../htscreens_giant_files/ge_melt_18Q3.rds")
-# ge_melt_18Q4 <- readRDS("./data_munging/rds/ge_melt_18Q4.rds")
-
-# maf_filt_dan <- filter(maf_df, Hugo_Symbol %in% g2p_genes)
-# write.table(maf_filt_dan, file = "~/Desktop/maf_filt_dan_18Q4_2018112.csv", quote = FALSE, sep = ",", row.names = FALSE)
-```
-
-## Drug screens
-
-### Merge drug data and annotations
-
-457/3462 gene-cell line combinations have more than one mutation in the MAF file. **FIX THIS**
-```{r}
-# test <- maf_df_g2p %>% count(Hugo_Symbol, CCLE_Name)
-# test <- test[order(test$n, decreasing = TRUE),]
-```
-
-```{r, eval=FALSE}
-# Drug metadata
-drug_meta <- read.delim("./data_munging/drug_id_drug_name_table_10_12_2018.tsv", sep = "\t", header = FALSE)
-colnames(drug_meta) <- c("CID", "Drug")
-drug_meta$Drug <- tolower(drug_meta$Drug)
-maf_df_g2p <- filter(maf_df, Hugo_Symbol %in% g2p_genes)
-ge_filt_18Q3 <- filter(ge_melt_18Q3, Hugo_Symbol %in% g2p_genes)
-# ge_filt_18Q4 <- filter(ge_melt_18Q4, Hugo_Symbol %in% g2p_genes)
-cn_filt <- filter(cn_melt, Hugo_Symbol %in% g2p_genes)
-
-# CCLE
-ccle <- read.delim("./data_munging/data_drug_auc_ccle_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
-ccle <- merge(drug_meta, ccle, by = "CID")
-ccle_melt <- melt(ccle, id.vars = c("CID", "Drug"), measure.vars = colnames(ccle)[3:ncol(ccle)], variable.name = "accession_id", value.name = "ActArea")
-ccle_grid <- expand.grid("accession_id" = unique(ccle_melt$accession_id), "Hugo_Symbol" = g2p_genes)
-ccle_data <- merge(ccle_grid, ccle_melt, by = "accession_id", all.x = TRUE)
-ccle_data <- merge(ccle_data, ccl_converter, by = "accession_id", all.x = TRUE)
-ccle_data <- merge(ccle_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
-ccle_data$Mutation_Status_Nonsilent <- ifelse(is.na(ccle_data$Mutation_Status_Nonsilent), "Wildtype", ccle_data$Mutation_Status_Nonsilent)
-ccle_data <- merge(ccle_data, ge_filt_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
-# ccle_data <- merge(ccle_data, ge_filt_18Q4, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
-ccle_data <- merge(ccle_data, cn_filt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
-ccle_data$Hugo_Symbol <- factor(ccle_data$Hugo_Symbol)
-ccle_data$ActArea <- as.numeric(ccle_data$ActArea)
-# CCLE AUC is actually AOC
-# assuming scale is 0-8, transform to range between 0 and 1
-# get AUC by 1 - AOC
-ccle_data$AUC <- 1 - (ccle_data$ActArea / 8)
-ccle_data <- filter(ccle_data, !is.na(ccle_data$AUC))
-ccle_data$AUC_zscore <- (ccle_data$AUC - mean(ccle_data$AUC)) / sd(ccle_data$AUC)
-ccle_data$Color_Nonsilent <- ifelse(ccle_data$Mutation_Status_Nonsilent == "Wildtype", "palegreen3", "springgreen4")
-ccle_data$Color_Nonsilent <- factor(ccle_data$Color_Nonsilent)
-ccle_data$Drug_Gene <- paste0(ccle_data$Drug, "_", ccle_data$Hugo_Symbol)
-ccle_data$Drug_Gene_Lin <- paste0(ccle_data$Drug, "_", ccle_data$Hugo_Symbol, "_", ccle_data$group_general_lineage_name)
-saveRDS(ccle_data, "./data_munging/rds/ccle_data_18Q4_g2pgenes.rds", compress = "xz")
-
-# CTRP
-ctrp <- read.delim("./data_munging/data_drug_auc_ctrp_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
-ctrp <- merge(drug_meta, ctrp, by = "CID")
-ctrp_melt <- melt(ctrp, id.vars = c("CID", "Drug"), measure.vars = colnames(ctrp)[3:ncol(ctrp)], variable.name = "accession_id", value.name = "AUC")
-ctrp_grid <- expand.grid("accession_id" = unique(ctrp_melt$accession_id), "Hugo_Symbol" = g2p_genes)
-ctrp_data <- merge(ctrp_grid, ctrp_melt, by = "accession_id", all.x = TRUE)
-ctrp_data <- merge(ctrp_data, ccl_converter, by = "accession_id", all.x = TRUE)
-ctrp_data <- merge(ctrp_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
-ctrp_data$Mutation_Status_Nonsilent <- ifelse(is.na(ctrp_data$Mutation_Status_Nonsilent), "Wildtype", ctrp_data$Mutation_Status_Nonsilent)
-ctrp_data <- merge(ctrp_data, ge_filt_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
-# ctrp_data <- merge(ctrp_data, ge_filt_18Q4, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
-ctrp_data <- merge(ctrp_data, cn_filt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
-ctrp_data$Hugo_Symbol <- factor(ctrp_data$Hugo_Symbol)
-ctrp_data$AUC <- as.numeric(ctrp_data$AUC)
-ctrp_data <- filter(ctrp_data, !is.na(ctrp_data$AUC))
-ctrp_data$AUC_zscore <- (ctrp_data$AUC - mean(ctrp_data$AUC)) / sd(ctrp_data$AUC)
-ctrp_data$Color_Nonsilent <- ifelse(ctrp_data$Mutation_Status_Nonsilent == "Wildtype", "slategray3", "steelblue4")
-ctrp_data$Color_Nonsilent <- factor(ctrp_data$Color_Nonsilent)
-ctrp_data$Drug_Gene <- paste0(ctrp_data$Drug, "_", ctrp_data$Hugo_Symbol)
-ctrp_data$Drug_Gene_Lin <- paste0(ctrp_data$Drug, "_", ctrp_data$Hugo_Symbol, "_", ctrp_data$group_general_lineage_name)
-saveRDS(ctrp_data, "./data_munging/rds/ctrp_data_18Q4_g2pgenes.rds", compress = "xz")
-
-# GDSC
-gdsc <- read.delim("./data_munging/data_drug_auc_gdsc_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
-gdsc <- merge(drug_meta, gdsc, by = "CID")
-gdsc_melt <- melt(gdsc, id.vars = c("CID", "Drug"), measure.vars = colnames(gdsc)[3:ncol(gdsc)], variable.name = "accession_id", value.name = "AUC")
-gdsc_grid <- expand.grid("accession_id" = unique(gdsc_melt$accession_id), "Hugo_Symbol" = g2p_genes)
-gdsc_data <- merge(gdsc_grid, gdsc_melt, by = "accession_id", all.x = TRUE)
-gdsc_data <- merge(gdsc_data, ccl_converter, by = "accession_id", all.x = TRUE)
-gdsc_data <- merge(gdsc_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
-gdsc_data$Mutation_Status_Nonsilent <- ifelse(is.na(gdsc_data$Mutation_Status_Nonsilent), "Wildtype", gdsc_data$Mutation_Status_Nonsilent)
-gdsc_data <- merge(gdsc_data, ge_filt_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
-# gdsc_data <- merge(gdsc_data, ge_filt_18Q4, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
-gdsc_data <- merge(gdsc_data, cn_filt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
-gdsc_data$Hugo_Symbol <- factor(gdsc_data$Hugo_Symbol)
-gdsc_data$AUC <- as.numeric(gdsc_data$AUC)
-gdsc_data <- filter(gdsc_data, !is.na(gdsc_data$AUC))
-gdsc_data$AUC_zscore <- (gdsc_data$AUC - mean(gdsc_data$AUC)) / sd(gdsc_data$AUC)
-gdsc_data$Color_Nonsilent <- ifelse(gdsc_data$Mutation_Status_Nonsilent == "Wildtype", "paleturquoise3", "turquoise4")
-gdsc_data$Color_Nonsilent <- factor(gdsc_data$Color_Nonsilent)
-gdsc_data$Drug_Gene <- paste0(gdsc_data$Drug, "_", gdsc_data$Hugo_Symbol)
-gdsc_data$Drug_Gene_Lin <- paste0(gdsc_data$Drug, "_", gdsc_data$Hugo_Symbol, "_", gdsc_data$group_general_lineage_name)
-saveRDS(gdsc_data, "./data_munging/rds/gdsc_data_18Q4_g2pgenes.rds", compress = "xz")
-```
-
-### Filter drug data
-
-```{r, eval=FALSE}
-ccle_data <- readRDS("./data_munging/rds/ccle_data_18Q4_g2pgenes.rds")
-ccle_data_ptmuts <- filter(ccle_data, Reference_Allele == 1 | Reference_Allele == 0 | is.na(Reference_Allele))
-ccle_data_ptmuts$Keep_PtMut_Tests <- ifelse(ccle_data_ptmuts$Reference_Allele == 1 | is.na(ccle_data_ptmuts$Reference_Allele), TRUE, ifelse(ccle_data_ptmuts$Tumor_Seq_Allele1 == 1, TRUE, FALSE))
-ccle_data_ptmuts <- filter(ccle_data_ptmuts, Keep_PtMut_Tests == TRUE)
-ccle_data_ptmuts <- subset(ccle_data_ptmuts, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, Genome_Change, Keep_PtMut_Tests))
-ccle_data_ptmuts$Dataset <- "CCLE"
-ccle_data_ptmuts$Hugo_Symbol <- ordered(ccle_data_ptmuts$Hugo_Symbol, levels = g2p_genes)
-ccle_data_ptmuts <- unique(ccle_data_ptmuts)
-saveRDS(ccle_data_ptmuts, "./data_munging/rds/ccle_data_18Q4_g2pgenes_ptmuts.rds", compress = "xz")
-
-ctrp_data <- readRDS("./data_munging/rds/ctrp_data_18Q4_g2pgenes.rds")
-ctrp_data_ptmuts <- filter(ctrp_data, Reference_Allele == 1 | Reference_Allele == 0 | is.na(Reference_Allele))
-ctrp_data_ptmuts$Keep_PtMut_Tests <- ifelse(ctrp_data_ptmuts$Reference_Allele == 1 | is.na(ctrp_data_ptmuts$Reference_Allele), TRUE, ifelse(ctrp_data_ptmuts$Tumor_Seq_Allele1 == 1, TRUE, FALSE))
-ctrp_data_ptmuts <- filter(ctrp_data_ptmuts, Keep_PtMut_Tests == TRUE)
-ctrp_data_ptmuts <- subset(ctrp_data_ptmuts, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, Genome_Change, Keep_PtMut_Tests))
-ctrp_data_ptmuts$Dataset <- "CTRP"
-ctrp_data_ptmuts$Hugo_Symbol <- ordered(ctrp_data_ptmuts$Hugo_Symbol, levels = g2p_genes)
-ctrp_data_ptmuts <- unique(ctrp_data_ptmuts)
-saveRDS(ctrp_data_ptmuts, "./data_munging/rds/ctrp_data_18Q4_g2pgenes_ptmuts.rds", compress = "xz")
-
-gdsc_data <- readRDS("./data_munging/rds/gdsc_data_18Q4_g2pgenes.rds")
-gdsc_data_ptmuts <- filter(gdsc_data, Reference_Allele == 1 | Reference_Allele == 0 | is.na(Reference_Allele))
-gdsc_data_ptmuts$Keep_PtMut_Tests <- ifelse(gdsc_data_ptmuts$Reference_Allele == 1 | is.na(gdsc_data_ptmuts$Reference_Allele), TRUE, ifelse(gdsc_data_ptmuts$Tumor_Seq_Allele1 == 1, TRUE, FALSE))
-gdsc_data_ptmuts <- filter(gdsc_data_ptmuts, Keep_PtMut_Tests == TRUE)
-gdsc_data_ptmuts <- subset(gdsc_data_ptmuts, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, Genome_Change, Keep_PtMut_Tests))
-gdsc_data_ptmuts$Dataset <- "GDSC"
-gdsc_data_ptmuts$Hugo_Symbol <- ordered(gdsc_data_ptmuts$Hugo_Symbol, levels = g2p_genes)
-gdsc_data_ptmuts <- unique(gdsc_data_ptmuts)
-saveRDS(gdsc_data_ptmuts, "./data_munging/rds/gdsc_data_18Q4_g2pgenes_ptmuts.rds", compress = "xz")
-```
-
-```{r}
-ccle_data <- readRDS("./data_munging/rds/ccle_data_18Q4_g2pgenes.rds")
-ctrp_data <- readRDS("./data_munging/rds/ctrp_data_18Q4_g2pgenes.rds")
-gdsc_data <- readRDS("./data_munging/rds/gdsc_data_18Q4_g2pgenes.rds")
-ccle_data_ptmuts <- readRDS("./data_munging/rds/ccle_data_18Q4_g2pgenes_ptmuts.rds")
-ctrp_data_ptmuts <- readRDS("./data_munging/rds/ctrp_data_18Q4_g2pgenes_ptmuts.rds")
-gdsc_data_ptmuts <- readRDS("./data_munging/rds/gdsc_data_18Q4_g2pgenes_ptmuts.rds")
-
-# Filter drug screen datasets for G2P drug-gene associations
-ccle_data_g2p <- filter(ccle_data_ptmuts, Drug_Gene %in% g2p_druggenes)
-ccle_data_g2p$Mutation_Status_Nonsilent <- factor(ccle_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-ctrp_data_g2p <- filter(ctrp_data_ptmuts, Drug_Gene %in% g2p_druggenes)
-ctrp_data_g2p$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-gdsc_data_g2p <- filter(gdsc_data_ptmuts, Drug_Gene %in% g2p_druggenes)
-gdsc_data_g2p$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-
-# Filter drug screen datasets for G2P drug-gene-lineage associations
-ccle_data_g2p_dgl <- filter(ccle_data_ptmuts, Drug_Gene_Lin %in% g2p_dgls)
-ccle_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(ccle_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-ctrp_data_g2p_dgl <- filter(ctrp_data_ptmuts, Drug_Gene_Lin %in% g2p_dgls)
-ctrp_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-gdsc_data_g2p_dgl <- filter(gdsc_data_ptmuts, Drug_Gene_Lin %in% g2p_dgls)
-gdsc_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-
-# Filter drug screen datasets for G2P drugs and genes
-ccle_data_g2p_grid <- filter(ccle_data_ptmuts, Drug %in% g2p_drugs)
-ccle_data_g2p_grid$Mutation_Status_Nonsilent <- factor(ccle_data_g2p_grid$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-ctrp_data_g2p_grid <- filter(ctrp_data_ptmuts, Drug %in% g2p_drugs)
-ctrp_data_g2p_grid$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p_grid$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-gdsc_data_g2p_grid <- filter(gdsc_data_ptmuts, Drug %in% g2p_drugs)
-gdsc_data_g2p_grid$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p_grid$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-
-# Testing
-test_ccle <- ccle_data_ptmuts %>% group_by(Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()
-test_ctrp <- ctrp_data_ptmuts %>% group_by(Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()
-test_gdsc <- gdsc_data_ptmuts %>% group_by(Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()
-
-# drug_summ <- data.frame(Drug = g2p_drugs, Dataset_Count = 0)
-```
-
-How many datasets screen each G2P drug?
-```{r}
-drug_summ <- data.frame(Drug = character(), Dataset_Count = integer(), stringsAsFactors = FALSE)
-
-for(drug in g2p_drugs) {
-  counter = 0
-  if(drug %in% as.character(unique(ccle_data_g2p$Drug))) { counter <- counter + 1 }
-  if(drug %in% as.character(unique(ctrp_data_g2p$Drug))) { counter <- counter + 1 }
-  if(drug %in% as.character(unique(gdsc_data_g2p$Drug))) { counter <- counter + 1 }
-  drug_summ <- rbind(drug_summ, data.frame(Drug = drug, Dataset_Count = counter))
-}
-```
-
-## CRISPR
-
-### DepMap dependency probabilities
-
-```{r, eval=FALSE}
-dep <- read.delim("./data_munging/18Q4/gene_dependency_18Q4_20181115.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
-# Remove Entrez gene IDs from colnames
-colnames(dep) <- gsub(" .*", "", colnames(dep))
-```
-
-### Merge CRISPR data and annotations
-
-The latest CRISPR CERES score data (18Q3, August 2018) was pulled from the [DepMap Data Portal](https://depmap.org/portal/download/) (Broad Institute Cancer Dependency Map 2018, Meyers et al. 2017).
-```{r, eval=FALSE}
-crispr <- read.delim("./data_munging/18Q4/gene_effect_18Q4_20181115.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
-# Remove Entrez gene IDs from colnames
-colnames(crispr) <- gsub(" .*", "", colnames(crispr))
-```
-
-Merge annotation data:
-```{r, eval=FALSE}
-# Melt CRISPR dataset for merging
-crispr_melt <- melt(crispr, id.vars = "DepMap_ID", measure.vars = colnames(crispr)[2:ncol(crispr)], variable.name = "Hugo_Symbol", value.name = "Score")
-# Melt dependency probabilities dataset for merging
-dep_melt <- melt(dep, id.vars = "DepMap_ID", measure.vars = colnames(dep)[2:ncol(dep)], variable.name = "Hugo_Symbol", value.name = "Dep_Prob")
-# Merge dependency probabilities
-crispr_melt <- merge(crispr_melt, dep_melt, by = c("DepMap_ID", "Hugo_Symbol"), all.x = TRUE)
-# Merge cell line metadata
-crispr_melt <- merge(crispr_melt, ccl_info, by = "DepMap_ID", all.x = TRUE)
-crispr_melt <- merge(crispr_melt, crispr_meta, by = c("CCLE_Name", "DepMap_ID"), all.x = TRUE)
-
-# Merge mutation annotations
-maf_filt_crispr <- filter(maf_df, Hugo_Symbol %in% as.character(unique(crispr_melt$Hugo_Symbol)))
-crispr_muts <- merge(crispr_melt, maf_filt_crispr, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
-crispr_muts$Hugo_Symbol <- factor(crispr_muts$Hugo_Symbol)
-crispr_muts <- crispr_muts %>% mutate(Mutation_Status_Nonsilent = if_else(is.na(Mutation_Status_Nonsilent), "Wildtype", Mutation_Status_Nonsilent))
-# Summarize number of mutant and Wildtype cell lines
-crispr_muts_summ <- crispr_muts %>% group_by(Hugo_Symbol) %>%
-  summarize(N_Nonsilent_Wildtype = sum(Mutation_Status_Nonsilent == "Wildtype"),
-            N_Nonsilent_Mutant = sum(Mutation_Status_Nonsilent == "Mutant"))
-# Merge test results back into full dataset, which restores information lost in the summarization
-crispr_data <- merge(crispr_muts_summ, crispr_muts, by = "Hugo_Symbol")
-# Add Color columns
-crispr_data$Color_Nonsilent <- ifelse(crispr_data$Mutation_Status_Nonsilent == "Wildtype", "thistle", "darkorchid")
-crispr_data$Color_Nonsilent <- factor(crispr_data$Color_Nonsilent)
-
-# Cell line lineages
-crispr_data <- merge(crispr_data, ccl_converter, by = c("CCLE_Name", "DepMap_ID"), all.x = TRUE)
-levels(crispr_data$lineage_name) <- sort(levels(crispr_data$lineage_name), decreasing = TRUE)
-# Copy number
-crispr_data <- merge(crispr_data, cn_melt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
-# Gene expression (RPKM)
-ge_crispr_18Q3 <- filter(ge_melt_18Q3, Hugo_Symbol %in% as.character(unique(crispr_melt$Hugo_Symbol)))
-# ge_crispr_18Q4 <- filter(ge_melt_18Q4, Hugo_Symbol %in% as.character(unique(crispr_melt$Hugo_Symbol)))
-crispr_data <- merge(crispr_data, ge_crispr_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
-# crispr_data <- merge(crispr_data, ge_crispr_18Q4, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
-saveRDS(crispr_data, "./../htscreens_giant_files/crispr_data_18Q4.rds", compress = "xz")
-
-# Takes a really long time to run (4+ hours)
-# crispr_data_ptmuts <- filter(crispr_data, Reference_Allele == 1 | Reference_Allele == 0 | is.na(Reference_Allele))
-# crispr_data_ptmuts$Keep_PtMut_Tests <- ifelse(crispr_data_ptmuts$Reference_Allele == 1 | is.na(crispr_data_ptmuts$Reference_Allele), TRUE, ifelse(crispr_data_ptmuts$Tumor_Seq_Allele1 == 1, TRUE, FALSE))
-# crispr_data_ptmuts <- filter(crispr_data_ptmuts, Keep_PtMut_Tests == TRUE)
-# crispr_data_ptmuts <- subset(crispr_data_ptmuts, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, Genome_Change, Keep_PtMut_Tests))
-# crispr_data_ptmuts <- unique(crispr_data_ptmuts)
-# saveRDS(crispr_data_ptmuts, "./data_munging/rds/crispr_data_18Q4_ptmuts.rds", compress = "xz")
-```
-
-```{r}
-crispr_data <- readRDS("./../htscreens_giant_files/crispr_data_18Q4.rds")
-# Run next two lines only if the file was made (see end of the last chunk)
-# crispr_data_ptmuts <- readRDS("./../htscreens_giant_files/crispr_data_18Q4_ptmuts.rds")
-# crispr_data_g2p <- filter(crispr_data_ptmuts, Hugo_Symbol %in% g2p_genes)
-
-# Filter CRISPR for G2P genes in G2P
-crispr_data_ptmuts <- filter(crispr_data, Hugo_Symbol %in% g2p_genes)
-# Filter G2P CRISPR for point mutations
-crispr_data_ptmuts <- filter(crispr_data_ptmuts, Reference_Allele == 1 | Reference_Allele == 0 | is.na(Reference_Allele))
-crispr_data_ptmuts$Keep_PtMut_Tests <- ifelse(crispr_data_ptmuts$Reference_Allele == 1 | is.na(crispr_data_ptmuts$Reference_Allele), TRUE, ifelse(crispr_data_ptmuts$Tumor_Seq_Allele1 == 1, TRUE, FALSE))
-crispr_data_ptmuts <- filter(crispr_data_ptmuts, Keep_PtMut_Tests == TRUE)
-crispr_data_ptmuts <- subset(crispr_data_ptmuts, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, Genome_Change, Keep_PtMut_Tests))
-crispr_data_g2p <- unique(crispr_data_ptmuts)
-crispr_data_g2p$Hugo_Symbol <- factor(crispr_data_g2p$Hugo_Symbol, levels = g2p_genes)
-crispr_data_g2p$Mutation_Status_Nonsilent <- factor(crispr_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-```
-
-# WILCOXON TESTS
-
---------------------------------------------------------------------------------
-
-Wilcoxon tests for assessing effect of mutation status on gene essentiality scores (CRISPR) and AUC (CCLE, CTRP, and GDSC).
-
-## CRISPR
-
-Test G2P genes in lineage-agnostic context:
-```{r, eval=FALSE}
-crispr_signif_g2p_gene <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol"), data = crispr_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
-crispr_signif_g2p_gene <- adj_signif(crispr_signif_g2p_gene, alpha = 0.05)
-crispr_signif_g2p_gene <- crispr_signif_g2p_gene[order(crispr_signif_g2p_gene$p),]
-saveRDS(crispr_signif_g2p_gene, "./data_munging/rds/crispr_signif_g2p_gene.rds")
-```
-
-```{r}
-crispr_signif_g2p_gene <- readRDS("./data_munging/rds/crispr_signif_g2p_gene.rds")
-crispr_signif_g2p_gene <- rbind(crispr_signif_g2p_gene, c("G6PD", rep(NA, 11)))
-crispr_signif_g2p_gene_kable <- knitr::kable(crispr_signif_g2p_gene[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj", "k", "FDR_cutoff")], caption = "Wilcoxon test results for Level A point mutations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-Plot results of `crispr_signif_g2p_gene` tests:
-```{r fig.height=7, fig.width=12}
-crispr_data_signif_g2p_gene_filt <- filter(crispr_data_ptmuts, Hugo_Symbol %in% as.character(crispr_signif_g2p_gene$Hugo_Symbol))
-crispr_data_signif_g2p_gene <- merge(crispr_data_signif_g2p_gene_filt, crispr_signif_g2p_gene, by = "Hugo_Symbol")
-crispr_data_signif_g2p_gene$Hugo_Symbol <- ordered(crispr_data_signif_g2p_gene$Hugo_Symbol, levels = as.character(crispr_signif_g2p_gene$Hugo_Symbol))
-
-crispr_data_signif_g2p_gene <- merge(crispr_data_signif_g2p_gene, crispr_data_signif_g2p_gene %>% group_by(Hugo_Symbol) %>% summarize(Text_y = max(Score)), by = "Hugo_Symbol")
-crispr_data_signif_g2p_gene_text <- unique(data.frame(p.signif = crispr_data_signif_g2p_gene$p.signif, p.signif.adj = crispr_data_signif_g2p_gene$p.signif.adj,  Hugo_Symbol = crispr_data_signif_g2p_gene$Hugo_Symbol, Text_y = crispr_data_signif_g2p_gene$Text_y))
-
-crispr_data_signif_g2p_gene_plot <- ggplot(data = crispr_data_signif_g2p_gene, aes(x = Mutation_Status_Nonsilent, y = Score)) +
-  facet_wrap(~ Hugo_Symbol, drop = FALSE, nrow = 2, scales = "free_y") +
-  geom_jitter(aes(color = Mutation_Status_Nonsilent), alpha = 0.5, width = 0.3) +
-  geom_boxplot(color = "black", fill = NA, outlier.shape = NA) +
-  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
-  scale_color_manual(values = c("Mutant" = "darkorchid", "Wildtype" = "thistle")) +
-  geom_text(data = crispr_data_signif_g2p_gene_text, mapping = aes(x = 1.5, y = Text_y, label = p.signif), nudge_y = 0.2) +
-  theme(legend.position = "top", axis.text.x = element_blank(), axis.ticks.x = element_blank(), axis.title.x = element_blank()) +
-  labs(y = "CERES Score",
-       color = "Mutation Status",
-       title = "CERES scores for select Level A G2P genes",
-       subtitle = "Genes are sorted by increasing p-value.")
-crispr_data_signif_g2p_gene_plot
-
-# ggsave("./plots/manuscript/crispr_data_signif_g2p_gene_plot.png", crispr_data_signif_g2p_gene_plot, width = 12, height = 7, units = "in")
-```
-
-Test G2P genes in lineage-grouped context:
-```{r, eval=FALSE}
-crispr_signif_g2p_lineage <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "group_general_lineage_name"), data = crispr_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
-crispr_signif_g2p_lineage <- adj_signif(crispr_signif_g2p_lineage, alpha = 0.05)
-crispr_signif_g2p_lineage <- crispr_signif_g2p_lineage[order(crispr_signif_g2p_lineage$p),]
-saveRDS(crispr_signif_g2p_lineage, "./data_munging/rds/crispr_signif_g2p_lineage.rds")
-# write.table(crispr_signif_g2p_lineage, file = "~/Desktop/crispr_signif_g2p_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
-```
-
-```{r}
-crispr_signif_g2p_lineage <- readRDS("./data_munging/rds/crispr_signif_g2p_lineage.rds")
-crispr_signif_g2p_lineage_kable <- knitr::kable(filter(crispr_signif_g2p_lineage, p < 0.1)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj", "FDR_cutoff")], caption = "Wilcoxon test results comparing non-silent mutant vs wildtype cell lines by lineage, p < 0.1 (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-Plot results of `crispr_signif_g2p_lineage` tests:
-```{r fig.height=18, fig.width=15, eval=TRUE}
-crispr_data_signif_g2p_lineage <- merge(crispr_data_signif_g2p_gene_filt, crispr_signif_g2p_lineage, by = c("Hugo_Symbol", "group_general_lineage_name"))
-crispr_data_signif_g2p_lineage$Hugo_Symbol <- ordered(crispr_data_signif_g2p_lineage$Hugo_Symbol, levels = as.character(unique((crispr_signif_g2p_lineage$Hugo_Symbol))))
-
-crispr_data_signif_g2p_lineage <- merge(crispr_data_signif_g2p_lineage, crispr_data_signif_g2p_lineage %>% group_by(Hugo_Symbol) %>% summarize(Text_y = max(Score)), by = "Hugo_Symbol")
-
-crispr_data_signif_g2p_lineage_text <- unique(data.frame(p.signif = crispr_data_signif_g2p_lineage$p.signif, p.signif.adj = crispr_data_signif_g2p_lineage$p.signif.adj,  group_general_lineage_name = crispr_data_signif_g2p_lineage$group_general_lineage_name, Hugo_Symbol = crispr_data_signif_g2p_lineage$Hugo_Symbol, Text_y = crispr_data_signif_g2p_lineage$Text_y))
-
-crispr_data_signif_g2p_lineage_plot <- ggplot(data = crispr_data_signif_g2p_lineage, aes(x = group_general_lineage_name, y = Score)) +
-  facet_wrap(~ Hugo_Symbol, drop = FALSE, nrow = 6, scales = "free_y") +
-  geom_point(aes(color = Mutation_Status_Nonsilent), alpha = 0.5) +
-  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
-  scale_color_manual(values = c("Mutant" = "darkorchid", "Wildtype" = "thistle")) +
-  geom_text(data = crispr_data_signif_g2p_lineage_text, mapping = aes(x = group_general_lineage_name, y = Text_y, label = p.signif), angle = 90, vjust = 0.8, nudge_y = 0.1) +
-  theme(legend.position = "top", axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 10)) +
-  labs(y = "CERES Score",
-       x = "Lineage",
-       color = "Mutation Status",
-       title = "CERES score by cell line lineage for significant Level A G2P genes",
-       subtitle = "* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001\nGenes are sorted by increasing lineage-agnostic p-value.")
-crispr_data_signif_g2p_lineage_plot
-
-# write.table(crispr_data_signif_g2p_lineage, file = "~/Desktop/crispr_data_signif_g2p_lineage_20181213.tsv", quote = FALSE, sep = "\t")
-# ggsave("./plots/manuscript/crispr_data_signif_g2p_lineage_plot.png", crispr_data_signif_g2p_lineage_plot, width = 15, height = 18, units = "in")
-```
-
-Count mutant/wildtype calls in each gene-lineage group:
-```{r}
-crispr_data_signif_g2p_lineage_summ <- crispr_data_signif_g2p_lineage %>% group_by(Hugo_Symbol, group_general_lineage_name, Mutation_Status_Nonsilent) %>% tally()
-
-# write.table(crispr_data_signif_g2p_lineage_summ, file = "~/Desktop/crispr_data_signif_g2p_lineage_summ_20181005.tsv", quote = FALSE, sep = "\t")
-
-crispr_data_signif_g2p_lineage_summ_kable <- knitr::kable(crispr_data_signif_g2p_lineage_summ, caption = "Mutant/Wildtype counts for gene-lineage combinations") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-## CCLE
-
-Drug metadata:
-```{r}
-drug_meta <- read.delim("./data_munging/drug_id_drug_name_table_10_12_2018.tsv", sep = "\t", header = FALSE)
-colnames(drug_meta) <- c("CID", "Drug")
-drug_meta$Drug <- tolower(drug_meta$Drug)
-```
-
-Test all CRISPR genes in lineage-agnostic context:
-```{r, eval=FALSE}
-# ccle <- read.delim("./data_munging/data_drug_auc_ccle_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
-# ccle <- merge(drug_meta, ccle, by = "CID")
-# ccle_melt <- melt(ccle, id.vars = c("CID", "Drug"), measure.vars = colnames(ccle)[3:ncol(ccle)], variable.name = "accession_id", value.name = "AUC")
-# ccle_grid <- expand.grid("accession_id" = unique(ccle_melt$accession_id), "Hugo_Symbol" = as.character(unique(crispr_data$Hugo_Symbol)))
-# system.time({ ccle_data_allgenes <- WilcoxonByDrugAllGenes(ccle_melt, ccle_grid, "CCLE") })
-# saveRDS(ccle_data_allgenes, "./data_munging/rds/ccle_data_18Q3_allgenes.rds", compress = "xz")
-
-# user   system  elapsed 
-# 1483.399  262.649 1901.698 
-```
-
-```{r}
-ccle_data_allgenes <- readRDS("./data_munging/rds/ccle_data_18Q3_allgenes.rds")
-ccle_data_allgenes <- ccle_data_allgenes[order(ccle_data_allgenes$p),]
-ccle_data_allgenes_kable <- knitr::kable(ccle_data_allgenes[1:1000, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: by-drug Wilcoxon test results for point mutations in genes targeted in CRISPR screen (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-Test G2P genes in lineage-agnostic context:
-```{r, eval=FALSE}
-# G2P drug-gene associations only
-ccle_signif_g2p <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene", data = ccle_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
-ccle_signif_g2p <- adj_signif(ccle_signif_g2p, alpha = 0.05)
-ccle_signif_g2p <- ccle_signif_g2p[order(ccle_signif_g2p$p),]
-saveRDS(ccle_signif_g2p, "./data_munging/rds/ccle_signif_g2p_gene.rds")
-
-# Grid comparisons of G2P drugs and genes
-ccle_signif_g2p_grid <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = c("Drug_Gene"), data = ccle_data_g2p_grid, method = "wilcox.test", p.adjust.method = "BH")
-ccle_signif_g2p_grid <- adj_signif(ccle_signif_g2p_grid, alpha = 0.05)
-ccle_signif_g2p_grid <- ccle_signif_g2p_grid[order(ccle_signif_g2p_grid$p),]
-saveRDS(ccle_signif_g2p_grid, "./data_munging/rds/ccle_signif_g2p_grid.rds")
-```
-
-```{r}
-ccle_signif_g2p <- readRDS("./data_munging/rds/ccle_signif_g2p_gene.rds")
-ccle_signif_g2p_kable <- knitr::kable(ccle_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj", "FDR_cutoff")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-
-ccle_signif_g2p_grid <- readRDS("./data_munging/rds/ccle_signif_g2p_grid.rds")
-ccle_signif_g2p_grid_kable <- knitr::kable(ccle_signif_g2p_grid[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj", "FDR_cutoff")], caption = "CCLE: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-Test G2P genes in lineage-grouped context:
-```{r, eval=FALSE}
-ccle_signif_grid_lineage <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene_Lin", data = ccle_data_g2p_grid, method = "wilcox.test", p.adjust.method = "BH")
-ccle_signif_grid_lineage <- adj_signif(ccle_signif_grid_lineage, alpha = 0.05)
-ccle_signif_grid_lineage <- ccle_signif_grid_lineage[order(ccle_signif_grid_lineage$p),]
-saveRDS(ccle_signif_grid_lineage, "./data_munging/rds/ccle_signif_grid_lineage.rds")
-
-ccle_signif_g2p_lineage <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene_Lin", data = ccle_data_g2p_dgl, method = "wilcox.test", p.adjust.method = "BH")
-ccle_signif_g2p_lineage <- adj_signif(ccle_signif_g2p_lineage, alpha = 0.05)
-ccle_signif_g2p_lineage <- ccle_signif_g2p_lineage[order(ccle_signif_g2p_lineage$p),]
-saveRDS(ccle_signif_g2p_lineage, "./data_munging/rds/ccle_signif_g2p_lineage.rds")
-```
-
-```{r}
-ccle_signif_g2p_lineage <- readRDS("./data_munging/rds/ccle_signif_g2p_lineage.rds")
-ccle_signif_grid_lineage <- readRDS("./data_munging/rds/ccle_signif_grid_lineage.rds")
-
-ccle_signif_g2p_lineage_kable <- knitr::kable(ccle_signif_g2p_lineage[, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj", "FDR_cutoff")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-
-ccle_signif_grid_lineage_kable <- knitr::kable(ccle_signif_grid_lineage[1:500, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj", "FDR_cutoff")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-## CTRP
-
-Test all CRISPR genes in lineage-agnostic context:
-```{r, eval=FALSE}
-# ctrp <- read.delim("./data_munging/data_drug_auc_ctrp_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
-# ctrp <- merge(drug_meta, ctrp, by = "CID")
-# ctrp_melt <- melt(ctrp, id.var  s = c("CID", "Drug"), measure.vars = colnames(ctrp)[3:ncol(ctrp)], variable.name = "accession_id", value.name = "AUC")
-# ctrp_grid <- expand.grid("accession_id" = unique(ctrp_melt$accession_id), "Hugo_Symbol" = as.character(unique(crispr_data$Hugo_Symbol)))
-# ctrp_data_allgenes <- WilcoxonByDrugAllGenes(ctrp_melt, ctrp_grid, "CTRP")
-# saveRDS(ctrp_data_allgenes, "./data_munging/rds/ctrp_data_18Q3_allgenes.rds", compress = "xz")
-```
-
-```{r}
-ctrp_data_allgenes <- readRDS("./data_munging/rds/ctrp_data_18Q3_allgenes.rds")
-ctrp_data_allgenes <- ctrp_data_allgenes[order(ctrp_data_allgenes$p),]
-ctrp_data_allgenes_kable <- knitr::kable(ctrp_data_allgenes[1:1000, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: by-drug Wilcoxon test results for point mutations in genes targeted in CRISPR screen (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-Test G2P genes in lineage-agnostic context:
-```{r, eval=FALSE}
-ctrp_signif_g2p <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene", data = ctrp_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
-ctrp_signif_g2p <- adj_signif(ctrp_signif_g2p, alpha = 0.05)
-ctrp_signif_g2p <- ctrp_signif_g2p[order(ctrp_signif_g2p$p),]
-saveRDS(ctrp_signif_g2p, "./data_munging/rds/ctrp_signif_g2p_gene.rds")
-
-# Grid comparisons of G2P drugs and genes
-ctrp_signif_g2p_grid <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene", data = ctrp_data_g2p_grid, method = "wilcox.test", p.adjust.method = "BH")
-ctrp_signif_g2p_grid <- adj_signif(ctrp_signif_g2p_grid, alpha = 0.05)
-ctrp_signif_g2p_grid <- ctrp_signif_g2p_grid[order(ctrp_signif_g2p_grid$p),]
-saveRDS(ctrp_signif_g2p_grid, "./data_munging/rds/ctrp_signif_g2p_grid.rds")
-```
-
-```{r}
-ctrp_signif_g2p <- readRDS("./data_munging/rds/ctrp_signif_g2p_gene.rds")
-ctrp_signif_g2p_kable <- knitr::kable(ctrp_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj", "FDR_cutoff")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-
-ctrp_signif_g2p_grid <- readRDS("./data_munging/rds/ctrp_signif_g2p_grid.rds")
-ctrp_signif_g2p_grid_kable <- knitr::kable(ctrp_signif_g2p_grid[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj", "FDR_cutoff")], caption = "CTRP: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-Test G2P genes in lineage-grouped context:
-```{r, eval=FALSE}
-ctrp_signif_grid_lineage <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene_Lin", data = ctrp_data_g2p_grid, method = "wilcox.test", p.adjust.method = "BH")
-ctrp_signif_grid_lineage <- adj_signif(ctrp_signif_grid_lineage, alpha = 0.05)
-ctrp_signif_grid_lineage <- ctrp_signif_grid_lineage[order(ctrp_signif_grid_lineage$p),]
-saveRDS(ctrp_signif_grid_lineage, "./data_munging/rds/ctrp_signif_grid_lineage.rds")
-
-ctrp_signif_g2p_lineage <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene_Lin", data = ctrp_data_g2p_dgl, method = "wilcox.test", p.adjust.method = "BH")
-ctrp_signif_g2p_lineage <- adj_signif(ctrp_signif_g2p_lineage, alpha = 0.05)
-ctrp_signif_g2p_lineage <- ctrp_signif_g2p_lineage[order(ctrp_signif_g2p_lineage$p),]
-saveRDS(ctrp_signif_g2p_lineage, "./data_munging/rds/ctrp_signif_g2p_lineage.rds")
-```
-
-```{r}
-ctrp_signif_g2p_lineage <- readRDS("./data_munging/rds/ctrp_signif_g2p_lineage.rds")
-ctrp_signif_grid_lineage <- readRDS("./data_munging/rds/ctrp_signif_grid_lineage.rds")
-
-ctrp_signif_g2p_lineage_kable <- knitr::kable(ctrp_signif_g2p_lineage[, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj", "FDR_cutoff")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-
-ctrp_signif_grid_lineage_kable <- knitr::kable(ctrp_signif_grid_lineage[1:500, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj", "FDR_cutoff")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-## GDSC
-
-Test all CRISPR genes in lineage-agnostic context:
-```{r, eval=FALSE}
-# gdsc <- read.delim("./data_munging/data_drug_auc_gdsc_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
-# gdsc <- merge(drug_meta, gdsc, by = "CID")
-# gdsc_melt <- melt(gdsc, id.vars = c("CID", "Drug"), measure.vars = colnames(gdsc)[3:ncol(gdsc)], variable.name = "accession_id", value.name = "AUC")
-# gdsc_grid <- expand.grid("accession_id" = unique(gdsc_melt$accession_id), "Hugo_Symbol" = as.character(unique(crispr_data$Hugo_Symbol)))
-# system.time({ gdsc_data_allgenes <- WilcoxonByDrugAllGenes(gdsc_melt, gdsc_grid, "GDSC") })
-# saveRDS(gdsc_data_allgenes, "./data_munging/rds/gdsc_data_18Q3_allgenes.rds", compress = "xz")
-```
-
-```{r}
-gdsc_data_allgenes <- readRDS("./data_munging/rds/gdsc_data_18Q3_allgenes.rds")
-gdsc_data_allgenes <- gdsc_data_allgenes[order(gdsc_data_allgenes$p),]
-gdsc_data_allgenes_kable <- knitr::kable(gdsc_data_allgenes[1:1000, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: by-drug Wilcoxon test results for point mutations in genes targeted in CRISPR screen (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-Test G2P genes in lineage-agnostic context:
-```{r, eval=FALSE}
-gdsc_signif_g2p <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene", data = gdsc_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
-gdsc_signif_g2p <- adj_signif(gdsc_signif_g2p, alpha = 0.05)
-gdsc_signif_g2p <- gdsc_signif_g2p[order(gdsc_signif_g2p$p),]
-saveRDS(gdsc_signif_g2p, "./data_munging/rds/gdsc_signif_g2p_gene.rds")
-
-# Grid comparisons of G2P drugs and genes
-gdsc_signif_g2p_grid <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene", data = gdsc_data_g2p_grid, method = "wilcox.test", p.adjust.method = "BH")
-gdsc_signif_g2p_grid <- adj_signif(gdsc_signif_g2p_grid, alpha = 0.05)
-gdsc_signif_g2p_grid <- gdsc_signif_g2p_grid[order(gdsc_signif_g2p_grid$p),]
-saveRDS(gdsc_signif_g2p_grid, "./data_munging/rds/gdsc_signif_g2p_grid.rds")
-```
-
-```{r}
-gdsc_signif_g2p <- readRDS("./data_munging/rds/gdsc_signif_g2p_gene.rds")
-gdsc_signif_g2p_kabl <- knitr::kable(gdsc_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-
-gdsc_signif_g2p_grid <- readRDS("./data_munging/rds/gdsc_signif_g2p_grid.rds")
-gdsc_signif_g2p_grid_kable <- knitr::kable(gdsc_signif_g2p_grid[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj", "FDR_cutoff")], caption = "GDSC: Wilcoxon test results for point mutations in level A G2P genes and drugs (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-Test G2P genes in lineage-grouped context:
-```{r, eval=FALSE}
-gdsc_signif_grid_lineage <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene_Lin", data = gdsc_data_g2p_grid, method = "wilcox.test", p.adjust.method = "BH")
-gdsc_signif_grid_lineage <- adj_signif(gdsc_signif_grid_lineage, alpha = 0.05)
-gdsc_signif_grid_lineage <- gdsc_signif_grid_lineage[order(gdsc_signif_grid_lineage$p),]
-saveRDS(gdsc_signif_grid_lineage, "./data_munging/rds/gdsc_signif_grid_lineage.rds")
-
-gdsc_signif_g2p_lineage <- compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene_Lin", data = gdsc_data_g2p_dgl, method = "wilcox.test", p.adjust.method = "BH")
-gdsc_signif_g2p_lineage <- adj_signif(gdsc_signif_g2p_lineage, alpha = 0.05)
-gdsc_signif_g2p_lineage <- gdsc_signif_g2p_lineage[order(gdsc_signif_g2p_lineage$p),]
-saveRDS(gdsc_signif_g2p_lineage, "./data_munging/rds/gdsc_signif_g2p_lineage.rds")
-```
-
-```{r}
-gdsc_signif_g2p_lineage <- readRDS("./data_munging/rds/gdsc_signif_g2p_lineage.rds")
-gdsc_signif_grid_lineage <- readRDS("./data_munging/rds/gdsc_signif_grid_lineage.rds")
-
-gdsc_signif_g2p_lineage_kable <- knitr::kable(gdsc_signif_g2p_lineage[, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj", "FDR_cutoff")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-
-gdsc_signif_grid_lineage_kable <- knitr::kable(gdsc_signif_grid_lineage[1:500, c("Drug_Gene_Lin", "p", "p.adj", "p.format", "p.signif", "p.signif.adj", "FDR_cutoff")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations across lineages (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-# PEARSON/SPEARMAN CORRELATIONS
-
---------------------------------------------------------------------------------
-
-Pearson and Spearman correlations for assessing effect of gene expression and copy number on gene essentiality score and AUC.
-
-Example of how to describe Spearman correaltion results: ""A Spearman's correlation was run to determine the relationship between 23 groundwater uranium and TDS values.
-There was a strong, positive monotonic correlation between Uranium and TDS ( = .71, n = 23, p < .001)."
-
-## CRISPR
-
-```{r, warning=FALSE}
-crispr_pearson_res_GE <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>%
-                         summarize(p = cor.test(y = Score, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
-                                   corr = cor.test(y = Score, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
-                                   Metric = "Gene Expression")
-crispr_pearson_res_CN <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>%
-                         summarize(p = cor.test(y = Score, x = CN, method = "pearson", use = "complete.obs")$p.value,
-                                   corr = cor.test(y = Score, x = CN, method = "pearson", use = "complete.obs")$estimate,
-                                   Metric = "Copy Number")
-crispr_spearman_res_GE <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>%
-                          summarize(p = cor.test(y = Score, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
-                                    corr = cor.test(y = Score, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
-                                    Metric = "Gene Expression")
-crispr_spearman_res_CN <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>%
-                          summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value,
-                                    corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate,
-                                    Metric = "Copy Number")
-```
-
-## Drug screens
-
-```{r, warning=FALSE}
-g2p_druggene_tally <- g2p_filt %>% group_by(Drug_Gene) %>% tally() %>% drop_na()
-
-# CCLE
-ccle_cor_res <- ccle_data_g2p_grid %>% group_by(Drug_Gene) %>%
-                    summarize(Pearson_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
-                              Pearson_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
-                              Pearson_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$estimate,
-                              Pearson_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$p.value,
-                              Spearman_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
-                              Spearman_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
-                              Spearman_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$estimate,
-                              Spearman_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$p.value)
-ccle_cor_res <- merge(g2p_druggene_tally, ccle_cor_res, by = "Drug_Gene", all.y = TRUE)
-ccle_cor_res$n <- ifelse(is.na(ccle_cor_res$n), 0, ccle_cor_res$n)
-ccle_cor_res$InG2P <- ifelse(ccle_cor_res$n != 0, "Yes", "No")
-ccle_cor_res$Dataset <- "CCLE"
-
-# CTRP
-ctrp_cor_res <- ctrp_data_g2p_grid %>% group_by(Drug_Gene) %>%
-                    summarize(Pearson_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
-                              Pearson_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
-                              Pearson_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$estimate,
-                              Pearson_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$p.value,
-                              Spearman_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
-                              Spearman_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
-                              Spearman_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$estimate,
-                              Spearman_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$p.value)
-ctrp_cor_res <- merge(g2p_druggene_tally, ctrp_cor_res, by = "Drug_Gene", all.y = TRUE)
-ctrp_cor_res$n <- ifelse(is.na(ctrp_cor_res$n), 0, ctrp_cor_res$n)
-ctrp_cor_res$InG2P <- ifelse(ctrp_cor_res$n != 0, "Yes", "No")
-ctrp_cor_res$Dataset <- "CTRP"
-
-# GDSC
-gdsc_cor_res <- gdsc_data_g2p_grid %>% group_by(Drug_Gene) %>%
-                    summarize(Pearson_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
-                              Pearson_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
-                              Pearson_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$estimate,
-                              Pearson_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$p.value,
-                              Spearman_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
-                              Spearman_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
-                              Spearman_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$estimate,
-                              Spearman_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$p.value)
-gdsc_cor_res <- merge(g2p_druggene_tally, gdsc_cor_res, by = "Drug_Gene", all.y = TRUE)
-gdsc_cor_res$n <- ifelse(is.na(gdsc_cor_res$n), 0, gdsc_cor_res$n)
-gdsc_cor_res$InG2P <- ifelse(gdsc_cor_res$n != 0, "Yes", "No")
-gdsc_cor_res$Dataset <- "GDSC"
-
-# All
-g2p_cor <- rbind(ccle_cor_res, ctrp_cor_res, gdsc_cor_res)
-g2p_cor$Pearson_GE_Abs <- abs(g2p_cor$Pearson_Corr_GE)
-g2p_cor$Pearson_GE_Sign <- ifelse(sign(g2p_cor$Pearson_Corr_GE) == 1, "+", ifelse(sign(g2p_cor$Pearson_Corr_GE) == -1, "-", "0"))
-g2p_cor$Pearson_CN_Abs <- abs(g2p_cor$Pearson_Corr_CN)
-g2p_cor$Pearson_CN_Sign <- ifelse(sign(g2p_cor$Pearson_Corr_CN) == 1, "+", ifelse(sign(g2p_cor$Pearson_Corr_CN) == -1, "-", "0"))
-g2p_cor$Spearman_GE_Abs <- abs(g2p_cor$Spearman_Corr_GE)
-g2p_cor$Spearman_GE_Sign <- ifelse(sign(g2p_cor$Spearman_Corr_GE) == 1, "+", ifelse(sign(g2p_cor$Spearman_Corr_GE) == -1, "-", "0"))
-g2p_cor$Spearman_CN_Abs <- abs(g2p_cor$Spearman_Corr_CN)
-g2p_cor$Spearman_CN_Sign <- ifelse(sign(g2p_cor$Spearman_Corr_CN) == 1, "+", ifelse(sign(g2p_cor$Spearman_Corr_CN) == -1, "-", "0"))
-```
-
-Deprecated: T-tests of G2P presence/absence distributions
-```{r}
-# ccle_pearson_ttest_GE <- t.test(ccle_cor_res$Pearson_Corr_GE ~ ccle_cor_res$InG2P)
-# ccle_pearson_ttest_res_GE <- paste0("t(", round(ccle_pearson_ttest_GE$parameter, 0), ") = ", round(ccle_pearson_ttest_GE$statistic, 2), ", p = ", round(ccle_pearson_ttest_GE$p.value, 2))
-# ccle_pearson_ttest_CN <- t.test(ccle_cor_res$Pearson_Corr_CN ~ ccle_cor_res$InG2P)
-# ccle_pearson_ttest_res_CN <- paste0("t(", round(ccle_pearson_ttest_CN$parameter, 0), ") = ", round(ccle_pearson_ttest_CN$statistic, 2), ", p = ", round(ccle_pearson_ttest_CN$p.value, 2))
-# ccle_spearman_ttest_GE <- t.test(ccle_cor_res$Spearman_Corr_GE ~ ccle_cor_res$InG2P)
-# ccle_spearman_ttest_res_GE <- paste0("t(", round(ccle_spearman_ttest_GE$parameter, 0), ") = ", round(ccle_spearman_ttest_GE$statistic, 2), ", p = ", round(ccle_spearman_ttest_GE$p.value, 2))
-# ccle_spearman_ttest_CN <- t.test(ccle_cor_res$Spearman_Corr_CN ~ ccle_cor_res$InG2P)
-# ccle_spearman_ttest_res_CN <- paste0("t(", round(ccle_spearman_ttest_CN$parameter, 0), ") = ", round(ccle_spearman_ttest_CN$statistic, 2), ", p = ", formatC(ccle_spearman_ttest_CN$p.value, 2, format = "f"))
-
-# ctrp_pearson_ttest_GE <- t.test(ctrp_cor_res$Pearson_Corr_GE ~ ctrp_cor_res$InG2P)
-# ctrp_pearson_ttest_res_GE <- paste0("t(", round(ctrp_pearson_ttest_GE$parameter, 0), ") = ", round(ctrp_pearson_ttest_GE$statistic, 2), ", p ", ifelse(round(ctrp_pearson_ttest_GE$p.value, 3) == 0, "< 0.001", paste0("= ", round(ctrp_pearson_ttest_GE$p.value, 3))))
-# ctrp_pearson_ttest_CN <- t.test(ctrp_cor_res$Pearson_Corr_CN ~ ctrp_cor_res$InG2P)
-# ctrp_pearson_ttest_res_CN <- paste0("t(", round(ctrp_pearson_ttest_CN$parameter, 0), ") = ", round(ctrp_pearson_ttest_CN$statistic, 2), ", p = ", round(ctrp_pearson_ttest_CN$p.value, 3))
-# ctrp_spearman_ttest_GE <- t.test(ctrp_cor_res$Spearman_Corr_GE ~ ctrp_cor_res$InG2P)
-# ctrp_spearman_ttest_res_GE <- paste0("t(", round(ctrp_spearman_ttest_GE$parameter, 0), ") = ", round(ctrp_spearman_ttest_GE$statistic, 2), ", p = ", round(ctrp_spearman_ttest_GE$p.value, 2))
-# ctrp_spearman_ttest_CN <- t.test(ctrp_cor_res$Spearman_Corr_CN ~ ctrp_cor_res$InG2P)
-# ctrp_spearman_ttest_res_CN <- paste0("t(", round(ctrp_spearman_ttest_CN$parameter, 0), ") = ", round(ctrp_spearman_ttest_CN$statistic, 2), ", p = ", round(ctrp_spearman_ttest_CN$p.value, 2))
-
-# gdsc_pearson_ttest_GE <- t.test(gdsc_cor_res$Pearson_Corr_GE ~ gdsc_cor_res$InG2P)
-# gdsc_pearson_ttest_res_GE <- paste0("t(", round(gdsc_pearson_ttest_GE$parameter, 0), ") = ", round(gdsc_pearson_ttest_GE$statistic, 2), ", p = ", round(gdsc_pearson_ttest_GE$p.value, 3))
-# gdsc_pearson_ttest_CN <- t.test(gdsc_cor_res$Pearson_Corr_CN ~ gdsc_cor_res$InG2P)
-# gdsc_pearson_ttest_res_CN <- paste0("t(", round(gdsc_pearson_ttest_CN$parameter, 0), ") = ", round(gdsc_pearson_ttest_CN$statistic, 2), ", p = ", round(gdsc_pearson_ttest_CN$p.value, 3))
-# gdsc_spearman_ttest_GE <- t.test(gdsc_cor_res$Spearman_Corr_GE ~ gdsc_cor_res$InG2P)
-# gdsc_spearman_ttest_res_GE <- paste0("t(", round(gdsc_spearman_ttest_GE$parameter, 0), ") = ", round(gdsc_spearman_ttest_GE$statistic, 2), ", p = ", round(gdsc_spearman_ttest_GE$p.value, 2))
-# gdsc_spearman_ttest_CN <- t.test(gdsc_cor_res$Spearman_Corr_CN ~ gdsc_cor_res$InG2P)
-# gdsc_spearman_ttest_res_CN <- paste0("t(", round(gdsc_spearman_ttest_CN$parameter, 0), ") = ", round(gdsc_spearman_ttest_CN$statistic, 2), ", p = ", round(gdsc_spearman_ttest_CN$p.value, 2))
-
-# g2p_cor_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"),
-#                                Pearson_Test_Results_GE = c(ccle_pearson_ttest_res_GE, ctrp_pearson_ttest_res_GE, gdsc_pearson_ttest_res_GE),
-#                                Pearson_Test_Results_CN = c(ccle_pearson_ttest_res_CN, ctrp_pearson_ttest_res_CN, gdsc_pearson_ttest_res_CN),
-#                                Spearman_Test_Results_GE = c(ccle_spearman_ttest_res_GE, ctrp_spearman_ttest_res_GE, gdsc_spearman_ttest_res_GE),
-#                                Spearman_Test_Results_CN = c(ccle_spearman_ttest_res_CN, ctrp_spearman_ttest_res_CN, gdsc_spearman_ttest_res_CN))
-```
-
-# SUMMARIES
-
---------------------------------------------------------------------------------
-
-## CRISPR: Mutation status counts
-
-```{r}
-crispr_data_g2p_summ <- unique(crispr_data_g2p[, c("Hugo_Symbol", "N_Nonsilent_Mutant", "N_Nonsilent_Wildtype")])
-crispr_data_g2p_summ$Percent_Mutant <- crispr_data_g2p_summ$N_Nonsilent_Mutant / (crispr_data_g2p_summ$N_Nonsilent_Mutant + crispr_data_g2p_summ$N_Nonsilent_Wildtype) * 100
-rownames(crispr_data_g2p_summ) <- NULL
-
-# write.table(crispr_data_g2p_summ, file = "~/Desktop/crispr_data_g2p_summ_20181003.tsv", quote = FALSE, sep = "\t")
-
-crispr_data_g2p_summ_kable <- knitr::kable(crispr_data_g2p_summ, caption = "CRISPR: Level A G2P genes mutation status summary") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-## G2P tallies and summary stats
-
-```{r}
-print("Drug-Gene")
-g2p_druggene_tally <- g2p_filt %>% group_by(Drug_Gene) %>% tally() %>% drop_na()
-nrow(g2p_druggene_tally)
-range(g2p_druggene_tally$n)
-mean(g2p_druggene_tally$n)
-sd(g2p_druggene_tally$n)
-
-print("Drug")
-g2p_drug_tally <- g2p_filt %>% group_by(Drug) %>% tally() %>% drop_na()
-range(g2p_drug_tally$n)
-mean(g2p_drug_tally$n)
-sd(g2p_drug_tally$n)
-
-print("Gene")
-g2p_gene_tally <- g2p_filt %>% group_by(Gene) %>% tally() %>% drop_na()
-range(g2p_gene_tally$n)
-mean(g2p_gene_tally$n)
-sd(g2p_gene_tally$n)
-
-print("Drug-Gene-Lineage")
-g2p_dgl_tally <- g2p_filt %>% group_by(Drug, Gene, Drug_Gene, group_general_lineage_name) %>% tally() %>% drop_na()
-nrow(g2p_dgl_tally)
-length(unique(g2p_dgl_tally$Drug))
-length(unique(g2p_dgl_tally$Gene))
-# unique(g2p_filt$Phenotype.Description)
-```
-
-## Cell line overlap
-
-```{r, eval=FALSE}
-crispr_ccl <- unique(select(crispr_data, DepMap_ID, CCLE_Name))
-ccle_ccl <- unique(select(ccle_data, DepMap_ID, CCLE_Name, accession_id))
-ctrp_ccl <- unique(select(ctrp_data, DepMap_ID, CCLE_Name, accession_id))
-gdsc_ccl <- unique(select(gdsc_data, DepMap_ID, CCLE_Name, accession_id))
-# all_ccl <- merge(ccle_ccl, ctrp_ccl, by = c("DepMap_ID", "CCLE_Name", "accession_id"), all = TRUE)
-```
-
-# BY LINEAGE
-
---------------------------------------------------------------------------------
-
-## Mut: Grid
-
-Summarize the Wilcoxon test p-values of the grid tests by mutation status. Grid tests were all lineage-agnostic G2P drug-gene associations tested across all screened lineages in each dataset:
-```{r}
-g2p_dgl_mut_tally <- g2p %>% group_by(Drug_Gene, group_general_lineage_name) %>% tally()
-
-ccle_dgl_summ <- ccle_signif_grid_lineage %>% separate(Drug_Gene_Lin, c("Drug", "Hugo_Symbol", "group_general_lineage_name"), "_")
-ccle_dgl_summ$Drug_Gene <- paste0(ccle_dgl_summ$Drug, "_", ccle_dgl_summ$Hugo_Symbol)
-ccle_dgl_summ <- merge(g2p_dgl_mut_tally, ccle_dgl_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
-ccle_dgl_summ$Drug_Gene_Lin <- paste0(ccle_dgl_summ$Drug_Gene, "_", ccle_dgl_summ$group_general_lineage_name)
-ccle_dgl_summ$n <- ifelse(is.na(ccle_dgl_summ$n), 0, ccle_dgl_summ$n)
-ccle_dgl_summ$InG2P <- ifelse(ccle_dgl_summ$n != 0, "Yes", "No")
-ccle_dgl_summ$Dataset <- "CCLE"
-
-ctrp_dgl_summ <- ctrp_signif_grid_lineage %>% separate(Drug_Gene_Lin, c("Drug", "Hugo_Symbol", "group_general_lineage_name"), "_")
-ctrp_dgl_summ$Drug_Gene <- paste0(ctrp_dgl_summ$Drug, "_", ctrp_dgl_summ$Hugo_Symbol)
-ctrp_dgl_summ <- merge(g2p_dgl_mut_tally, ctrp_dgl_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
-ctrp_dgl_summ$Drug_Gene_Lin <- paste0(ctrp_dgl_summ$Drug_Gene, "_", ctrp_dgl_summ$group_general_lineage_name)
-ctrp_dgl_summ$n <- ifelse(is.na(ctrp_dgl_summ$n), 0, ctrp_dgl_summ$n)
-ctrp_dgl_summ$InG2P <- ifelse(ctrp_dgl_summ$n != 0, "Yes", "No")
-ctrp_dgl_summ$Dataset <- "CTRP"
-
-gdsc_dgl_summ <- gdsc_signif_grid_lineage %>% separate(Drug_Gene_Lin, c("Drug", "Hugo_Symbol", "group_general_lineage_name"), "_")
-gdsc_dgl_summ$Drug_Gene <- paste0(gdsc_dgl_summ$Drug, "_", gdsc_dgl_summ$Hugo_Symbol)
-gdsc_dgl_summ <- merge(g2p_dgl_mut_tally, gdsc_dgl_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
-gdsc_dgl_summ$Drug_Gene_Lin <- paste0(gdsc_dgl_summ$Drug_Gene, "_", gdsc_dgl_summ$group_general_lineage_name)
-gdsc_dgl_summ$n <- ifelse(is.na(gdsc_dgl_summ$n), 0, gdsc_dgl_summ$n)
-gdsc_dgl_summ$InG2P <- ifelse(gdsc_dgl_summ$n != 0, "Yes", "No")
-gdsc_dgl_summ$Dataset <- "GDSC"
-
-dgl_mut_grid_summ <- rbind(ccle_dgl_summ, ctrp_dgl_summ, gdsc_dgl_summ)
-```
-
-## GE/CN: G2P
-
-Drug-gene-lineage (DGL) overlaps between CCLE, CTRP, and GDSC:
-```{r}
-dgl_overlap_test_list <- list(CCLE = unique(ccle_data_g2p_dgl$Drug_Gene_Lin),
-                              CTRP = unique(ctrp_data_g2p_dgl$Drug_Gene_Lin),
-                              GDSC = unique(gdsc_data_g2p_dgl$Drug_Gene_Lin))
-
-ItemsList <- venn(dgl_overlap_test_list, show.plot = TRUE)
-ItemsList
-```
-
-Test the 102 level-A G2P DGL combinations:
-```{r, eval=FALSE}
-ccle_lineages4pearson <- as.character(unique(ccle_data_g2p_dgl$group_general_lineage_name))[!is.na(as.character(unique(ccle_data_g2p_dgl$group_general_lineage_name)))]
-ccle_signif_ge <- lapply(ccle_lineages4pearson, PearsonByLineage, variable = "GE", dataset = ccle_data_g2p_dgl)
-ccle_signif_ge_all_lin <- rbindlist(ccle_signif_ge, use.names = TRUE)
-ccle_signif_ge_all_lin$Dataset <- "CCLE"
-ccle_signif_cn <- lapply(ccle_lineages4pearson, PearsonByLineage, variable = "CN", dataset = ccle_data_g2p_dgl)
-ccle_signif_cn_all_lin <- rbindlist(ccle_signif_cn, use.names = TRUE)
-ccle_signif_cn_all_lin$Dataset <- "CCLE"
-ccle_signif_all_lin <- merge(ccle_signif_ge_all_lin, ccle_signif_cn_all_lin, by = c("Drug_Gene", "group_general_lineage_name", "n", "Dataset"), all = TRUE)
-
-ctrp_lineages4pearson <- as.character(unique(ctrp_data_g2p_dgl$group_general_lineage_name))[!is.na(as.character(unique(ctrp_data_g2p_dgl$group_general_lineage_name)))]
-ctrp_signif_ge <- lapply(ctrp_lineages4pearson, PearsonByLineage, variable = "GE", dataset = ctrp_data_g2p_dgl)
-ctrp_signif_ge_all_lin <- rbindlist(ctrp_signif_ge, use.names = TRUE)
-ctrp_signif_ge_all_lin$Dataset <- "CTRP"
-ctrp_signif_cn <- lapply(ctrp_lineages4pearson, PearsonByLineage, variable = "CN", dataset = ctrp_data_g2p_dgl)
-ctrp_signif_cn_all_lin <- rbindlist(ctrp_signif_cn, use.names = TRUE)
-ctrp_signif_cn_all_lin$Dataset <- "CTRP"
-ctrp_signif_all_lin <- merge(ctrp_signif_ge_all_lin, ctrp_signif_cn_all_lin, by = c("Drug_Gene", "group_general_lineage_name", "n", "Dataset"), all = TRUE)
-
-gdsc_lineages4pearson <- as.character(unique(gdsc_data_g2p_dgl$group_general_lineage_name))[!is.na(as.character(unique(gdsc_data_g2p_dgl$group_general_lineage_name)))]
-gdsc_signif_ge <- lapply(gdsc_lineages4pearson, PearsonByLineage, variable = "GE", dataset = gdsc_data_g2p_dgl)
-gdsc_signif_ge_all_lin <- rbindlist(gdsc_signif_ge, use.names = TRUE)
-gdsc_signif_ge_all_lin$Dataset <- "GDSC"
-gdsc_signif_cn <- lapply(gdsc_lineages4pearson, PearsonByLineage, variable = "CN", dataset = gdsc_data_g2p_dgl)
-gdsc_signif_cn_all_lin <- rbindlist(gdsc_signif_cn, use.names = TRUE)
-gdsc_signif_cn_all_lin$Dataset <- "GDSC"
-gdsc_signif_all_lin <- merge(gdsc_signif_ge_all_lin, gdsc_signif_cn_all_lin, by = c("Drug_Gene", "group_general_lineage_name", "n", "Dataset"), all = TRUE)
-
-signif_all_lin <- rbind(ccle_signif_all_lin, ctrp_signif_all_lin, gdsc_signif_all_lin)
-signif_all_lin$n <- ifelse(is.na(signif_all_lin$n), 0, signif_all_lin$n)
-signif_all_lin$InG2P <- ifelse(signif_all_lin$n != 0, "Yes", "No")
-signif_all_lin$Drug_Gene_Lin <- paste0(signif_all_lin$Drug_Gene, "_", signif_all_lin$group_general_lineage_name)
-saveRDS(signif_all_lin, "./data_munging/rds/dgl_signif_pearson_g2p.rds")
-```
-
-```{r}
-dgl_signif_pearson_g2p <- readRDS("./data_munging/rds/dgl_signif_pearson_g2p.rds")
-```
-
-```{r}
-# CCLE mut, n = 7
-ccle_mut <- filter(select(ccle_signif_g2p_lineage, Drug_Gene_Lin, p), p < 0.05)
-ccle_mut_n <- nrow(select(ccle_signif_g2p_lineage, Drug_Gene_Lin, p))
-# CCLE GE/CN, n = 9
-ccle_ge <- select(subset(filter(dgl_signif_pearson_g2p, Dataset == "CCLE"), Pearson_Pval_GE < 0.05), Drug_Gene_Lin, Pearson_Pval_GE, Pearson_Corr_GE)
-ccle_cn <- select(subset(filter(dgl_signif_pearson_g2p, Dataset == "CCLE"), Pearson_Pval_CN < 0.05), Drug_Gene_Lin, Pearson_Pval_CN, Pearson_Corr_CN)
-ccle_Pear_n <- nrow(filter(dgl_signif_pearson_g2p, Dataset == "CCLE"))
-ccle_dgl_summ <- merge(ccle_mut, merge(ccle_ge, ccle_cn, by = "Drug_Gene_Lin", all = TRUE), all = TRUE)
-ccle_dgl_summ <- with(ccle_dgl_summ, cbind(colsplit(Drug_Gene_Lin, pattern = "_", names = c("Drug", "Gene", "Lineage")), 
-                                           CCLE_p = p,
-                                           CCLE_p_Bonf = ifelse(p < 0.05 / ccle_mut_n, "Sig", NA),
-                                           CCLE_r_GE = Pearson_Corr_GE,
-                                           CCLE_p_GE = Pearson_Pval_GE,
-                                           CCLE_p_GE_Bonf = ifelse(Pearson_Pval_GE < 0.05 / ccle_Pear_n, "Sig", NA),
-                                           CCLE_r_CN = Pearson_Corr_CN,
-                                           CCLE_p_CN = Pearson_Pval_CN,
-                                           CCLE_p_CN_Bonf = ifelse(Pearson_Pval_CN < 0.05 / ccle_Pear_n, "Sig", NA)))
-
-# CTRP mut, n = 48
-ctrp_mut <- filter(select(ctrp_signif_g2p_lineage, Drug_Gene_Lin, p), p < 0.05)
-ctrp_mut_n <- nrow(select(ctrp_signif_g2p_lineage, Drug_Gene_Lin, p))
-# CTRP GE/CN, n = 61
-ctrp_ge <- select(subset(filter(dgl_signif_pearson_g2p, Dataset == "CTRP"), Pearson_Pval_GE < 0.05), Drug_Gene_Lin, Pearson_Pval_GE, Pearson_Corr_GE)
-ctrp_cn <- select(subset(filter(dgl_signif_pearson_g2p, Dataset == "CTRP"), Pearson_Pval_CN < 0.05), Drug_Gene_Lin, Pearson_Pval_CN, Pearson_Corr_CN)
-ctrp_Pear_n <- nrow(filter(dgl_signif_pearson_g2p, Dataset == "CTRP"))
-ctrp_dgl_summ <- merge(ctrp_mut, merge(ctrp_ge, ctrp_cn, by = "Drug_Gene_Lin", all = TRUE), all = TRUE)
-ctrp_dgl_summ <- with(ctrp_dgl_summ, cbind(colsplit(Drug_Gene_Lin, pattern = "_", names = c("Drug", "Gene", "Lineage")), 
-                                           CTRP_p = p,
-                                           CTRP_p_Bonf = ifelse(p < 0.05 / ctrp_mut_n, "Sig", NA),
-                                           CTRP_r_GE = Pearson_Corr_GE,
-                                           CTRP_p_GE = Pearson_Pval_GE,
-                                           CTRP_p_GE_Bonf = ifelse(Pearson_Pval_GE < 0.05 / ctrp_Pear_n, "Sig", NA),
-                                           CTRP_r_CN = Pearson_Corr_CN,
-                                           CTRP_p_CN = Pearson_Pval_CN,
-                                           CTRP_p_CN_Bonf = ifelse(Pearson_Pval_CN < 0.05 / ctrp_Pear_n, "Sig", NA)))
-
-# GDSC mut, n = 39
-gdsc_mut <- filter(select(gdsc_signif_g2p_lineage, Drug_Gene_Lin, p), p < 0.05)
-gdsc_mut_n <- nrow(select(gdsc_signif_g2p_lineage, Drug_Gene_Lin, p))
-# GDSC GE/CN, n = 53
-gdsc_ge <- select(subset(filter(dgl_signif_pearson_g2p, Dataset == "GDSC"), Pearson_Pval_GE < 0.05), Drug_Gene_Lin, Pearson_Pval_GE, Pearson_Corr_GE)
-gdsc_cn <- select(subset(filter(dgl_signif_pearson_g2p, Dataset == "GDSC"), Pearson_Pval_CN < 0.05), Drug_Gene_Lin, Pearson_Pval_CN, Pearson_Corr_CN)
-gdsc_Pear_n <- nrow(filter(dgl_signif_pearson_g2p, Dataset == "GDSC"))
-gdsc_dgl_summ <- merge(gdsc_mut, merge(gdsc_ge, gdsc_cn, by = "Drug_Gene_Lin", all = TRUE), all = TRUE)
-gdsc_dgl_summ <- with(gdsc_dgl_summ, cbind(colsplit(Drug_Gene_Lin, pattern = "_", names = c("Drug", "Gene", "Lineage")), 
-                                           GDSC_p = p,
-                                           GDSC_p_Bonf = ifelse(p < 0.05 / gdsc_mut_n, "Sig", NA),
-                                           GDSC_r_GE = Pearson_Corr_GE,
-                                           GDSC_p_GE = Pearson_Pval_GE,
-                                           GDSC_p_GE_Bonf = ifelse(Pearson_Pval_GE < 0.05 / gdsc_Pear_n, "Sig", NA),
-                                           GDSC_r_CN = Pearson_Corr_CN,
-                                           GDSC_p_CN = Pearson_Pval_CN,
-                                           GDSC_p_CN_Bonf = ifelse(Pearson_Pval_CN < 0.05 / gdsc_Pear_n, "Sig", NA)))
-
-g2p_dgl_sig_summ <- merge(merge(ccle_dgl_summ, ctrp_dgl_summ, by = c("Drug", "Gene", "Lineage"), all = TRUE), gdsc_dgl_summ, by = c("Drug", "Gene", "Lineage"), all = TRUE)
-```
-
-## GE/CN: Grid
-
-Test all combinations of G2P drugs and genes in all lineages. InG2P indicates G2P drug-gene associations test across all lineages.
-```{r, eval=FALSE}
-ccle_lineages4pearson <- as.character(unique(ccle_data_g2p_grid$group_general_lineage_name))[!is.na(as.character(unique(ccle_data_g2p_grid$group_general_lineage_name)))]
-ccle_signif_ge <- lapply(ccle_lineages4pearson, PearsonByLineage, variable = "GE", dataset = ccle_data_g2p_grid)
-ccle_signif_ge_all_lin <- rbindlist(ccle_signif_ge, use.names = TRUE)
-ccle_signif_ge_all_lin$Dataset <- "CCLE"
-ccle_signif_cn <- lapply(ccle_lineages4pearson, PearsonByLineage, variable = "CN", dataset = ccle_data_g2p_grid)
-ccle_signif_cn_all_lin <- rbindlist(ccle_signif_cn, use.names = TRUE)
-ccle_signif_cn_all_lin$Dataset <- "CCLE"
-ccle_signif_all_lin <- merge(ccle_signif_ge_all_lin, ccle_signif_cn_all_lin, by = c("Drug_Gene", "group_general_lineage_name", "n", "Dataset"), all = TRUE)
-
-ctrp_lineages4pearson <- as.character(unique(ctrp_data_g2p_grid$group_general_lineage_name))[!is.na(as.character(unique(ctrp_data_g2p_grid$group_general_lineage_name)))]
-ctrp_signif_ge <- lapply(ctrp_lineages4pearson, PearsonByLineage, variable = "GE", dataset = ctrp_data_g2p_grid)
-ctrp_signif_ge_all_lin <- rbindlist(ctrp_signif_ge, use.names = TRUE)
-ctrp_signif_ge_all_lin$Dataset <- "CTRP"
-ctrp_signif_cn <- lapply(ctrp_lineages4pearson, PearsonByLineage, variable = "CN", dataset = ctrp_data_g2p_grid)
-ctrp_signif_cn_all_lin <- rbindlist(ctrp_signif_cn, use.names = TRUE)
-ctrp_signif_cn_all_lin$Dataset <- "CTRP"
-ctrp_signif_all_lin <- merge(ctrp_signif_ge_all_lin, ctrp_signif_cn_all_lin, by = c("Drug_Gene", "group_general_lineage_name", "n", "Dataset"), all = TRUE)
-
-gdsc_lineages4pearson <- as.character(unique(gdsc_data_g2p_grid$group_general_lineage_name))[!is.na(as.character(unique(gdsc_data_g2p_grid$group_general_lineage_name)))]
-gdsc_signif_ge <- lapply(gdsc_lineages4pearson, PearsonByLineage, variable = "GE", dataset = gdsc_data_g2p_grid)
-gdsc_signif_ge_all_lin <- rbindlist(gdsc_signif_ge, use.names = TRUE)
-gdsc_signif_ge_all_lin$Dataset <- "GDSC"
-gdsc_signif_cn <- lapply(gdsc_lineages4pearson, PearsonByLineage, variable = "CN", dataset = gdsc_data_g2p_grid)
-gdsc_signif_cn_all_lin <- rbindlist(gdsc_signif_cn, use.names = TRUE)
-gdsc_signif_cn_all_lin$Dataset <- "GDSC"
-gdsc_signif_all_lin <- merge(gdsc_signif_ge_all_lin, gdsc_signif_cn_all_lin, by = c("Drug_Gene", "group_general_lineage_name", "n", "Dataset"), all = TRUE)
-
-signif_all_lin <- rbind(ccle_signif_all_lin, ctrp_signif_all_lin, gdsc_signif_all_lin)
-signif_all_lin$n <- ifelse(is.na(signif_all_lin$n), 0, signif_all_lin$n)
-signif_all_lin$InG2P <- ifelse(signif_all_lin$n != 0, "Yes", "No")
-signif_all_lin$Drug_Gene_Lin <- paste0(signif_all_lin$Drug_Gene, "_", signif_all_lin$group_general_lineage_name)
-saveRDS(signif_all_lin, "./data_munging/rds/dgl_signif_pearson_g2p_grid.rds")
-```
-
-```{r}
-dgl_signif_pearson_g2p_grid <- readRDS("./data_munging/rds/dgl_signif_pearson_g2p_grid.rds")
-```
-
-# MUT/GE/CN: Pancancer
-
---------------------------------------------------------------------------------
-
-This section contains summary plots for the Wilcoxon tests and Pearson/Spearman correlations done for only level A G2P drug-gene associations (i.e.
-not the grid tests) and G2P genes in the case of the CRISPR dataset.
-
-## CRISPR
-
-Venn diagram between GE and CN:
-```{r}
-futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
-crispr_spearman_res_GE_sig <- filter(crispr_spearman_res_GE, p < 0.05)
-crispr_spearman_res_CN_sig <- filter(crispr_spearman_res_CN, p < 0.05)
-crispr_venn <- venn.diagram(list("Gene Expression" = as.character(crispr_spearman_res_GE_sig$Hugo_Symbol), "Copy Number" = as.character(crispr_spearman_res_CN_sig$Hugo_Symbol)), fill = c("darkorchid4", "mediumorchid1"), lty = rep("blank", 2), alpha = c(0.5, 0.5), cat.pos = c(-2, 5), cat.cex = 1.5, cex = 1, filename = NULL)
-
-# in GE only
-crispr_venn[[5]]$label  <- paste(sort(setdiff(as.character(crispr_spearman_res_GE_sig$Hugo_Symbol), as.character(crispr_spearman_res_CN_sig$Hugo_Symbol))), collapse = "\n")
-# in CN only
-crispr_venn[[6]]$label <- paste(sort(setdiff(as.character(crispr_spearman_res_CN_sig$Hugo_Symbol), as.character(crispr_spearman_res_GE_sig$Hugo_Symbol))), collapse = "\n")
-# intesection
-crispr_venn[[7]]$label <- paste(sort(intersect(as.character(crispr_spearman_res_CN_sig$Hugo_Symbol), as.character(crispr_spearman_res_GE_sig$Hugo_Symbol))), collapse = "\n")
-
-ggsave("./plots/manuscript/crispr_venn.pdf", crispr_venn)
-```
-
-G2P genes with a significant effect on CERES score by mutation status, gene expression, and copy number. Summary plot using Pearson correlation coefficient for GE and CN:
-```{r fig.height=5, fig.width=12}
-crispr_res_mut <- select(crispr_signif_g2p_gene, Hugo_Symbol, p)
-crispr_res_mut$corr <- 0
-crispr_res_mut$Metric <- "Mutation Status"
-crispr_res_mut$p_log10 <- -log10(as.numeric(crispr_res_mut$p))
-subset(crispr_res_mut, p < 0.05)
-
-subset(crispr_pearson_res_GE, p < 0.05)
-subset(crispr_pearson_res_CN, p < 0.05)
-
-crispr_pearson_res <- rbind(crispr_pearson_res_GE, crispr_pearson_res_CN)
-crispr_pearson_res$Metric <- factor(crispr_pearson_res$Metric, levels = c("Gene Expression", "Copy Number"))
-crispr_pearson_res$p_log10 <- -log10(crispr_pearson_res$p)
-
-crispr_summ_res_mut_plot <- ggplot(data = subset(crispr_res_mut, p < 0.05)) +
-  facet_grid(~ Metric) +
-  scale_y_continuous(breaks = seq(0, 50, by = 5), labels = seq(0, 50, by = 5)) +
-  coord_cartesian(ylim = c(0, 50)) +
-  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_label_repel(mapping = aes(y = p_log10, x = corr, label = Hugo_Symbol, color = Metric), force = 10, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
-  theme(legend.position = "none", panel.grid.major.x = element_blank(), panel.grid.minor.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(5.5, 1.5, 5.5, 5.5), "pt")) +
-  scale_color_manual(values = c("Mutation Status" = "darkorchid4")) +
-  labs(y = "-log10(p-value)")
-
-crispr_summ_res_pearson_plot <- ggplot(data = subset(crispr_pearson_res, p < 0.05)) +
-  facet_grid(~ Metric, scales = "free_x", space = "free") +
-  scale_y_continuous(breaks = seq(0, 50, by = 5), labels = seq(0, 50, by = 5)) +
-  scale_x_continuous(breaks = seq(-0.6, 0.3, by = 0.1), labels = formatC(seq(-0.6, 0.3, by = 0.1), digits = 2, format = "f")) +
-  coord_cartesian(ylim = c(0, 50)) +
-  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
-  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_label_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Hugo_Symbol), force = 10, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
-  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
-  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
-  labs(x = "Pearson correlation coefficient (r)")
-
-crispr_genomic_features_pearson_summ_plot <- plot_grid(crispr_summ_res_mut_plot, crispr_summ_res_pearson_plot, align = "h", rel_widths = c(1, 5))
-crispr_genomic_features_pearson_summ_plot
-
-# ggsave("./plots/manuscript/crispr_genomic_features_pearson_summ_plot.png", crispr_genomic_features_pearson_summ_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
-```
-
-Summary plot using Spearman correlation coefficient for GE and CN:
-```{r fig.height=5, fig.width=12}
-subset(crispr_spearman_res_GE, p < 0.05)
-subset(crispr_spearman_res_CN, p < 0.05)
-
-crispr_spearman_res <- rbind(crispr_spearman_res_GE, crispr_spearman_res_CN)
-crispr_spearman_res$Metric <- factor(crispr_spearman_res$Metric, levels = c("Gene Expression", "Copy Number"))
-crispr_spearman_res$p_log10 <- -log10(crispr_spearman_res$p)
-
-crispr_summ_res_spearman_plot <- ggplot(data = subset(crispr_spearman_res, p < 0.05)) +
-  facet_grid(~ Metric, scales = "free_x", space = "free") +
-  scale_y_continuous(breaks = seq(0, 50, by = 5), labels = seq(0, 50, by = 5)) +
-  scale_x_continuous(breaks = seq(-0.6, 0.3, by = 0.1), labels = formatC(seq(-0.6, 0.3, by = 0.1), digits = 2, format = "f")) +
-  coord_cartesian(ylim = c(0, 50)) +
-  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
-  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_label_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Hugo_Symbol), force = 10, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
-  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
-  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
-  labs(x = "Spearman's rank correlation coefficient (r_s)")
-
-crispr_genomic_features_spearman_summ_plot <- plot_grid(crispr_summ_res_mut_plot, crispr_summ_res_spearman_plot, align = "h", rel_widths = c(1, 5))
-crispr_genomic_features_spearman_summ_plot
-
-# ggsave("./plots/manuscript/crispr_genomic_features_spearman_summ_plot.png", crispr_genomic_features_spearman_summ_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
-```
-
-Pearson correlations for gene expression and copy number:
-```{r fig.height=6, fig.width=12}
-crispr_pearson_res_GE <- transform(crispr_pearson_res_GE, Hugo_Symbol = reorder(Hugo_Symbol, corr)) 
-crispr_pearson_res_GE$p_log10 <- -log10(crispr_pearson_res_GE$p)
-crispr_pearson_res_CN <- transform(crispr_pearson_res_CN, Hugo_Symbol = reorder(Hugo_Symbol, corr)) 
-crispr_pearson_res_CN$p_log10 <- -log10(crispr_pearson_res_CN$p)
-
-crispr_ge_pearson_corr_plot <- ggplot(data = crispr_pearson_res_GE, aes(x = Hugo_Symbol, y = corr)) +
-  geom_point(aes(fill = p_log10), pch = 21, size = 5) +
-  scale_fill_gradient2(low = "white", mid = "white", high = "darkorchid4", midpoint = 1.3010299957) +
-  coord_cartesian(ylim = c(-0.65, 0.25)) +
-  theme(legend.position = "bottom", axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 10)) +
-  labs(fill = "-log10(p)", x = "Gene", y = "Pearson Correlation Coefficient (r_s)", subtitle = "CRISPR: Correlation between AUC z-score and gene expression")
-crispr_cn_pearson_corr_plot <- ggplot(data = crispr_pearson_res_CN, aes(x = Hugo_Symbol, y = corr)) +
-  geom_point(aes(fill = p_log10), pch = 21, size = 5) +
-  scale_fill_gradient2(low = "white", mid = "white", high = "darkorchid4", midpoint = 1.3010299957) +
-  coord_cartesian(ylim = c(-0.65, 0.25)) +
-  theme(legend.position = "bottom", axis.title.y = element_blank(), axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 10)) +
-  labs(fill = "-log10(p)", x = "Gene", y = "Pearson Correlation Coefficient (r_s)", subtitle = "CRISPR: Correlation between AUC z-score and copy number")
-
-crispr_pearson_corr_plot <- plot_grid(crispr_ge_pearson_corr_plot, crispr_cn_pearson_corr_plot, align = "h")
-crispr_pearson_corr_plot
-# ggsave("./plots/manuscript/crispr_pearson_corr_plot.png", crispr_pearson_corr_plot, device = "png", dpi = 450, width = 12, height = 6, units = "in")
-```
-
-Spearman correlations for gene expression and copy number:
-```{r fig.height=8, fig.width=16}
-crispr_spearman_res_GE <- transform(crispr_spearman_res_GE, Hugo_Symbol = reorder(Hugo_Symbol, corr)) 
-crispr_spearman_res_GE$p_log10 <- -log10(crispr_spearman_res_GE$p)
-crispr_spearman_res_CN <- transform(crispr_spearman_res_CN, Hugo_Symbol = reorder(Hugo_Symbol, corr)) 
-crispr_spearman_res_CN$p_log10 <- -log10(crispr_spearman_res_CN$p)
-spearman_KRAS <- rbind(filter(crispr_data_g2p, Hugo_Symbol == "KRAS") %>% summarize(p = cor.test(y = Score, x = RPKM, method = "spearman", use = "complete.obs")$p.value, corr = cor.test(y = Score, x = RPKM, method = "spearman", use = "complete.obs")$estimate, Metric = "Gene Expression"), filter(crispr_data_g2p, Hugo_Symbol == "KRAS") %>% summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value, corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate, Metric = "Copy Number"))
-
-crispr_ge_spearman_corr_inset <- ggplot(filter(crispr_data_g2p, Hugo_Symbol == "KRAS"), aes(x = RPKM, y = Score)) +
-  geom_point(pch = 21, fill = "cadetblue3", alpha = 0.6) +
-  labs(x = "KRAS Gene Expression (RPKM)", y = "CERES Score", subtitle = paste0("Spearman correlation coefficient = ", round(spearman_KRAS$corr[1], 2), " (", printp(spearman_KRAS$p[1]), ")"))
-
-crispr_cn_spearman_corr_inset <- ggplot(filter(crispr_data_g2p, Hugo_Symbol == "KRAS"), aes(x = CN, y = Score)) +
-  geom_point(pch = 21, fill = "palegreen2", alpha = 0.6) +
-  labs(x = "KRAS Copy Number (log2 ratio)", y = "CERES Score", subtitle = paste0("Spearman correlation coefficient = ", round(spearman_KRAS$corr[2], 2), " (", printp(spearman_KRAS$p[2]), ")"))
-
-crispr_ge_spearman_corr_plot <- ggplot(data = crispr_spearman_res_GE, aes(x = Hugo_Symbol, y = corr)) +
-  geom_point(aes(fill = p_log10), pch = 21, size = 5) +
-  scale_fill_gradient2(low = "white", mid = "white", high = "deepskyblue4", midpoint = 1.3010299957) +
-  coord_cartesian(ylim = c(-0.45, 0.2)) +
-  theme(legend.position = "bottom", axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 10)) +
-  labs(fill = "-log10(p)", x = "Gene", y = "Spearman Correlation Coefficient (r_s)") +
-  annotation_custom(ggplotGrob(crispr_ge_spearman_corr_inset), xmin = 12, xmax = 32, ymin = -0.15, ymax = -0.45) +
-  geom_curve(aes(x = 3.5, y = -0.27, xend = 14, yend = -0.165), color = "lightgray", curvature = -0.2, arrow = arrow(length = unit(0.03, "npc")))
-
-crispr_cn_spearman_corr_plot <- ggplot(data = crispr_spearman_res_CN, aes(x = Hugo_Symbol, y = corr)) +
-  geom_point(aes(fill = p_log10), pch = 21, size = 5) +
-  scale_fill_gradient2(low = "white", mid = "white", high = "green4", midpoint = 1.3010299957) +
-  coord_cartesian(ylim = c(-0.45, 0.2)) +
-  theme(legend.position = "bottom", axis.title.y = element_blank(), axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 10)) +
-  labs(fill = "-log10(p)", x = "Gene", y = "Spearman Correlation Coefficient (r_s)") +
-  annotation_custom(ggplotGrob(crispr_cn_spearman_corr_inset), xmin = 12, xmax = 32, ymin = -0.15, ymax = -0.45) +
-  geom_curve(aes(x = 2.5, y = -0.232, xend = 14, yend = -0.165), color = "lightgray", curvature = -0.2, arrow = arrow(length = unit(0.03, "npc")))
-
-crispr_spearman_corr_plot <- plot_grid(crispr_ge_spearman_corr_plot, crispr_cn_spearman_corr_plot, align = "h")
-crispr_spearman_corr_plot
-# ggsave("./plots/manuscript/crispr_spearman_corr_plot.png", crispr_spearman_corr_plot, device = "png", dpi = 450, width = 16, height = 8, units = "in")
-```
-
-## Summaries by dataset
-
-### CCLE
-
-G2P drug-gene associations with a significant effect on AUC by mutation status, gene expression, and copy number. Summary plot using Pearson correlation coefficient for GE and CN:
-```{r fig.height=4, fig.width=12}
-ccle_res_mut <- select(ccle_signif_g2p, Drug_Gene, p)
-ccle_res_mut$corr <- 0
-ccle_res_mut$Metric <- "Mutation Status"
-ccle_res_mut$p_log10 <- -log10(ccle_res_mut$p)
-ccle_res_mut$Dataset <- "CCLE"
-
-ccle_pearson_res_GE <- select(filter(ccle_cor_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_GE, Pearson_Pval_GE, Dataset)
-colnames(ccle_pearson_res_GE) <- c("Drug_Gene", "corr", "p", "Dataset")
-ccle_pearson_res_GE$Metric <- "Gene Expression"
-subset(ccle_pearson_res_GE, p < 0.05)
-
-ccle_pearson_res_CN <- select(filter(ccle_cor_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_CN, Pearson_Pval_CN, Dataset)
-colnames(ccle_pearson_res_CN) <- c("Drug_Gene", "corr", "p", "Dataset")
-ccle_pearson_res_CN$Metric <- "Copy Number"
-subset(ccle_pearson_res_CN, p < 0.05)
-
-ccle_pearson_res_filt <- rbind(ccle_pearson_res_GE, ccle_pearson_res_CN)
-ccle_pearson_res_filt$Metric <- factor(ccle_pearson_res_filt$Metric, levels = c("Gene Expression", "Copy Number"))
-ccle_pearson_res_filt$p_log10 <- -log10(ccle_pearson_res_filt$p)
-
-ccle_summ_res_mut_plot <- ggplot(data = subset(ccle_res_mut, p < 0.05)) +
-  facet_grid(Dataset ~ Metric) +
-  scale_y_continuous(breaks = seq(0, 35, by = 5), labels = seq(0, 35, by = 5)) +
-  coord_cartesian(ylim = c(0, 25)) +
-  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_label_repel(mapping = aes(y = p_log10, x = corr, label = Drug_Gene, color = Metric), force = 10, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
-  theme(legend.position = "none", panel.grid.major.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(5.5, 1.5, 5.5, 5.5), "pt"), strip.background.y = element_blank(), strip.text.y = element_blank()) +
-  scale_color_manual(values = c("Mutation Status" = "darkorchid4")) +
-  labs(y = "-log10(p-value)")
-
-ccle_summ_res_pearson_plot <- ggplot(data = subset(ccle_pearson_res_filt, p < 0.05)) +
-  facet_grid(Dataset ~ Metric) +
-  coord_cartesian(ylim = c(0, 25)) +
-  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
-  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_label_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 10, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
-  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
-  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
-  labs(x = "Pearson correlation coefficient (r)")
-
-ccle_genomic_features_pearson_summ_plot <- plot_grid(ccle_summ_res_mut_plot, ccle_summ_res_pearson_plot, align = "h", rel_widths = c(1, 5))
-ccle_genomic_features_pearson_summ_plot
-
-# ggsave("./plots/manuscript/ccle_genomic_features_pearson_summ_plot.png", ccle_genomic_features_pearson_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
-```
-
-Summary plot using Spearman correlation coefficient for GE and CN:
-```{r fig.height=4, fig.width=12}
-ccle_spearman_res_GE <- select(filter(ccle_cor_res, InG2P == "Yes"), Drug_Gene, Spearman_Corr_GE, Spearman_Pval_GE, Dataset)
-colnames(ccle_spearman_res_GE) <- c("Drug_Gene", "corr", "p", "Dataset")
-ccle_spearman_res_GE$Metric <- "Gene Expression"
-subset(ccle_spearman_res_GE, p < 0.05)
-
-ccle_spearman_res_CN <- select(filter(ccle_cor_res, InG2P == "Yes"), Drug_Gene, Spearman_Corr_CN, Spearman_Pval_CN, Dataset)
-colnames(ccle_spearman_res_CN) <- c("Drug_Gene", "corr", "p", "Dataset")
-ccle_spearman_res_CN$Metric <- "Copy Number"
-subset(ccle_spearman_res_CN, p < 0.05)
-
-ccle_spearman_res_filt <- rbind(ccle_spearman_res_GE, ccle_spearman_res_CN)
-ccle_spearman_res_filt$Metric <- factor(ccle_spearman_res_filt$Metric, levels = c("Gene Expression", "Copy Number"))
-ccle_spearman_res_filt$p_log10 <- -log10(ccle_spearman_res_filt$p)
-
-ccle_summ_res_spearman_plot <- ggplot(data = subset(ccle_spearman_res_filt, p < 0.05)) +
-  facet_grid(Dataset ~ Metric) +
-  coord_cartesian(ylim = c(0, 25)) +
-  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
-  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_label_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 10, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
-  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
-  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
-  labs(x = "Spearman's rank correlation coefficient (r_s)")
-
-ccle_genomic_features_spearman_summ_plot <- plot_grid(ccle_summ_res_mut_plot, ccle_summ_res_spearman_plot, align = "h", rel_widths = c(1, 5))
-ccle_genomic_features_spearman_summ_plot
-
-# ggsave("./plots/manuscript/ccle_genomic_features_spearman_summ_plot.png", ccle_genomic_features_spearman_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
-```
-
-### CTRP
-
-G2P drug-gene associations with a significant effect on AUC by mutation status, gene expression, and copy number. Summary plot using Pearson correlation coefficient for GE and CN:
-```{r fig.height=4, fig.width=12}
-ctrp_res_mut <- select(ctrp_signif_g2p, Drug_Gene, p)
-ctrp_res_mut$corr <- 0
-ctrp_res_mut$Metric <- "Mutation Status"
-ctrp_res_mut$p_log10 <- -log10(ctrp_res_mut$p)
-ctrp_res_mut$Dataset <- "CTRP"
-
-ctrp_pearson_res_GE <- select(filter(ctrp_cor_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_GE, Pearson_Pval_GE, Dataset)
-colnames(ctrp_pearson_res_GE) <- c("Drug_Gene", "corr", "p", "Dataset")
-ctrp_pearson_res_GE$Metric <- "Gene Expression"
-subset(ctrp_pearson_res_GE, p < 0.05)
-
-ctrp_pearson_res_CN <- select(filter(ctrp_cor_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_CN, Pearson_Pval_CN, Dataset)
-colnames(ctrp_pearson_res_CN) <- c("Drug_Gene", "corr", "p", "Dataset")
-ctrp_pearson_res_CN$Metric <- "Copy Number"
-subset(ctrp_pearson_res_CN, p < 0.05)
-
-ctrp_pearson_res_filt <- rbind(ctrp_pearson_res_GE, ctrp_pearson_res_CN)
-ctrp_pearson_res_filt$Metric <- factor(ctrp_pearson_res_filt$Metric, levels = c("Gene Expression", "Copy Number"))
-ctrp_pearson_res_filt$p_log10 <- -log10(ctrp_pearson_res_filt$p)
-
-ctrp_summ_res_mut_plot <- ggplot(data = subset(ctrp_res_mut, p < 0.05)) +
-  facet_grid(Dataset ~ Metric) +
-  scale_y_continuous(breaks = seq(0, 35, by = 5), labels = seq(0, 35, by = 5)) +
-  coord_cartesian(ylim = c(0, 35)) +
-  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_text_repel(mapping = aes(y = p_log10, x = corr, label = Drug_Gene, color = Metric), force = 15, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.9) +
-  theme(legend.position = "none", panel.grid.major.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(5.5, 1.5, 5.5, 5.5), "pt"), strip.background.y = element_blank(), strip.text.y = element_blank()) +
-  scale_color_manual(values = c("Mutation Status" = "darkorchid4")) +
-  labs(y = "-log10(p-value)")
-
-ctrp_summ_res_pearson_plot <- ggplot(data = subset(ctrp_pearson_res_filt, p < 0.05)) +
-  facet_grid(Dataset ~ Metric) +
-  coord_cartesian(ylim = c(0, 35)) +
-  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
-  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 10, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
-  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
-  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
-  labs(x = "Pearson correlation coefficient (r)")
-
-ctrp_genomic_features_pearson_summ_plot <- plot_grid(ctrp_summ_res_mut_plot, ctrp_summ_res_pearson_plot, align = "h", rel_widths = c(1, 5))
-ctrp_genomic_features_pearson_summ_plot
-
-# ggsave("./plots/manuscript/ctrp_genomic_features_pearson_summ_plot.png", ctrp_genomic_features_pearson_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
-```
-
-Summary plot using Spearman correlation coefficient for GE and CN:
-```{r fig.height=4, fig.width=12}
-ctrp_spearman_res_GE <- select(filter(ctrp_cor_res, InG2P == "Yes"), Drug_Gene, Spearman_Corr_GE, Spearman_Pval_GE, Dataset)
-colnames(ctrp_spearman_res_GE) <- c("Drug_Gene", "corr", "p", "Dataset")
-ctrp_spearman_res_GE$Metric <- "Gene Expression"
-subset(ctrp_spearman_res_GE, p < 0.05)
-
-ctrp_spearman_res_CN <- select(filter(ctrp_cor_res, InG2P == "Yes"), Drug_Gene, Spearman_Corr_CN, Spearman_Pval_CN, Dataset)
-colnames(ctrp_spearman_res_CN) <- c("Drug_Gene", "corr", "p", "Dataset")
-ctrp_spearman_res_CN$Metric <- "Copy Number"
-subset(ctrp_spearman_res_CN, p < 0.05)
-
-ctrp_spearman_res_filt <- rbind(ctrp_spearman_res_GE, ctrp_spearman_res_CN)
-ctrp_spearman_res_filt$Metric <- factor(ctrp_spearman_res_filt$Metric, levels = c("Gene Expression", "Copy Number"))
-ctrp_spearman_res_filt$p_log10 <- -log10(ctrp_spearman_res_filt$p)
-
-ctrp_summ_res_spearman_plot <- ggplot(data = subset(ctrp_spearman_res_filt, p < 0.05)) +
-  facet_grid(Dataset ~ Metric) +
-  coord_cartesian(ylim = c(0, 35)) +
-  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
-  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 20, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
-  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
-  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
-  labs(x = "Spearman's rank correlation coefficient (r_s)")
-
-ctrp_genomic_features_spearman_summ_plot <- plot_grid(ctrp_summ_res_mut_plot, ctrp_summ_res_spearman_plot, align = "h", rel_widths = c(1, 5))
-ctrp_genomic_features_spearman_summ_plot
-
-# ggsave("./plots/manuscript/ctrp_genomic_features_spearman_summ_plot.png", ctrp_genomic_features_spearman_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
-```
-
-### GDSC
-
-G2P drug-gene associations with a significant effect on AUC by mutation status, gene expression, and copy number. Summary plot using Pearson correlation coefficient for GE and CN:
-```{r fig.height=4, fig.width=12}
-gdsc_res_mut <- select(gdsc_signif_g2p, Drug_Gene, p)
-gdsc_res_mut$corr <- 0
-gdsc_res_mut$Metric <- "Mutation Status"
-gdsc_res_mut$p_log10 <- -log10(gdsc_res_mut$p)
-gdsc_res_mut$Dataset <- "GDSC"
-
-gdsc_pearson_res_GE <- select(filter(gdsc_cor_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_GE, Pearson_Pval_GE, Dataset)
-colnames(gdsc_pearson_res_GE) <- c("Drug_Gene", "corr", "p", "Dataset")
-gdsc_pearson_res_GE$Metric <- "Gene Expression"
-subset(gdsc_pearson_res_GE, p < 0.05)
-
-gdsc_pearson_res_CN <- select(filter(gdsc_cor_res, InG2P == "Yes"), Drug_Gene, Pearson_Corr_CN, Pearson_Pval_CN, Dataset)
-colnames(gdsc_pearson_res_CN) <- c("Drug_Gene", "corr", "p", "Dataset")
-gdsc_pearson_res_CN$Metric <- "Copy Number"
-subset(gdsc_pearson_res_CN, p < 0.05)
-
-gdsc_pearson_res_filt <- rbind(gdsc_pearson_res_GE, gdsc_pearson_res_CN)
-gdsc_pearson_res_filt$Metric <- factor(gdsc_pearson_res_filt$Metric, levels = c("Gene Expression", "Copy Number"))
-gdsc_pearson_res_filt$p_log10 <- -log10(gdsc_pearson_res_filt$p)
-
-gdsc_summ_res_mut_plot <- ggplot(data = subset(gdsc_res_mut, p < 0.05)) +
-  facet_grid(Dataset ~ Metric) +
-  scale_y_continuous(breaks = seq(0, 16, by = 1), labels = seq(0, 16, by = 1)) +
-  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_text_repel(mapping = aes(y = p_log10, x = corr, label = Drug_Gene, color = Metric), force = 15, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.9) +
-  theme(legend.position = "none", panel.grid.major.x = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(5.5, 1.5, 5.5, 5.5), "pt"), strip.background.y = element_blank(), strip.text.y = element_blank()) +
-  scale_color_manual(values = c("Mutation Status" = "darkorchid4")) +
-  labs(y = "-log10(p-value)")
-
-gdsc_summ_res_pearson_plot <- ggplot(data = subset(gdsc_pearson_res_filt, p < 0.05)) +
-  facet_grid(Dataset ~ Metric) +
-  scale_y_continuous(breaks = seq(0, 100, by = 10), labels = seq(0, 100, by = 10)) +
-  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
-  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 10, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
-  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
-  theme(legend.position = "none", axis.title.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
-  labs(x = "Pearson correlation coefficient (r)")
-
-gdsc_genomic_features_pearson_summ_plot <- plot_grid(gdsc_summ_res_mut_plot, gdsc_summ_res_pearson_plot, align = "h", rel_widths = c(1, 5))
-gdsc_genomic_features_pearson_summ_plot
-
-# ggsave("./plots/manuscript/gdsc_genomic_features_pearson_summ_plot.png", gdsc_genomic_features_pearson_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
-```
-
-Summary plot using Spearman correlation coefficient for GE and CN:
-```{r fig.height=4, fig.width=12}
-gdsc_spearman_res_GE <- select(filter(gdsc_cor_res, InG2P == "Yes"), Drug_Gene, Spearman_Corr_GE, Spearman_Pval_GE, Dataset)
-colnames(gdsc_spearman_res_GE) <- c("Drug_Gene", "corr", "p", "Dataset")
-gdsc_spearman_res_GE$Metric <- "Gene Expression"
-subset(gdsc_spearman_res_GE, p < 0.05)
-
-gdsc_spearman_res_CN <- select(filter(gdsc_cor_res, InG2P == "Yes"), Drug_Gene, Spearman_Corr_CN, Spearman_Pval_CN, Dataset)
-colnames(gdsc_spearman_res_CN) <- c("Drug_Gene", "corr", "p", "Dataset")
-gdsc_spearman_res_CN$Metric <- "Copy Number"
-subset(gdsc_spearman_res_CN, p < 0.05)
-
-gdsc_spearman_res_filt <- rbind(gdsc_spearman_res_GE, gdsc_spearman_res_CN)
-gdsc_spearman_res_filt$Metric <- factor(gdsc_spearman_res_filt$Metric, levels = c("Gene Expression", "Copy Number"))
-gdsc_spearman_res_filt$p_log10 <- -log10(gdsc_spearman_res_filt$p)
-
-gdsc_summ_res_spearman_plot <- ggplot(data = subset(gdsc_spearman_res_filt, p < 0.05)) +
-  facet_grid(Dataset ~ Metric) +
-  coord_cartesian(ylim = c(0, 30)) +
-  scale_y_continuous(breaks = seq(0, 50, by = 5), labels = seq(0, 50, by = 5)) +
-  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
-  geom_point(aes(x = corr, y = p_log10, color = Metric), alpha = 0.5) +
-  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Metric, label = Drug_Gene), force = 20, nudge_y = 2, nudge_x = 0.05, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
-  scale_color_manual(values = c("Gene Expression" = "darkorchid1", "Copy Number" = "mediumorchid1")) +
-  theme(legend.position = "none", axis.title.y = element_blank(), plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
-  annotate(geom = "text", x = 0, y = 30, label = c("afatinib_ERBB2 and lapatinib_ERBB2\n-log10(p-value) >> 100", ""), size = 3) +
-  labs(x = "Spearman's rank correlation coefficient (r_s)")
-
-gdsc_genomic_features_spearman_summ_plot <- plot_grid(gdsc_summ_res_mut_plot, gdsc_summ_res_spearman_plot, align = "h", rel_widths = c(1, 5))
-gdsc_genomic_features_spearman_summ_plot
-
-# ggsave("./plots/manuscript/gdsc_genomic_features_spearman_summ_plot.png", gdsc_genomic_features_spearman_summ_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
-```
-
-## Summaries by feature
-
-### Mut
-
-G2P drug-gene associations with a significant effect on AUC by mutation status:
-```{r fig.height=4, fig.width=8}
-all_mut_res <- rbind(ccle_res_mut, ctrp_res_mut, gdsc_res_mut)
-
-all_mut_summ_plot <- ggplot(data = subset(all_mut_res, p < 0.05)) +
-  facet_grid(~ Dataset) +
-  geom_point(aes(x = corr, y = p_log10, color = Dataset), alpha = 0.5) +
-  scale_y_continuous(breaks = seq(0, 12, by = 2), labels = seq(0, 12, by = 2)) +
-  scale_x_continuous(breaks = seq(0, 0.1, by = 0.1), labels = seq(0, 0.1, by = 0.1)) +
-  coord_cartesian(xlim = c(0, 0.05)) +
-  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Dataset, label = Drug_Gene), nudge_x = 0.05, direction = "y", hjust = 0, size = 2.5, segment.size = 0.1, segment.colour = "grey50", box.padding = 0.6) +
-  scale_color_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
-  theme(legend.position = "none", plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt"), panel.grid.major.x = element_blank(), panel.grid.minor.x = element_blank(), axis.title.x = element_blank(), axis.ticks.x = element_blank(), axis.text.x = element_blank()) +
-  labs(y = "-log10(p-value)")
-all_mut_summ_plot
-
-# ggsave("./plots/manuscript/all_mut_summ_plot.png", all_mut_summ_plot, device = "png", dpi = 450, width = 12, height = 6, units = "in")
-```
-
-### GE and CN
-
-G2P drug-gene associations with a significant effect on AUC by gene expression and copy number:
-```{r fig.height=12, fig.width=12}
-all_pearson_res <- rbind(ccle_pearson_res_filt, ctrp_pearson_res_filt, gdsc_pearson_res_filt)
-all_pearson_summ_plot <- ggplot(data = subset(all_pearson_res, p < 0.05)) +
-  facet_grid(Dataset ~ Metric, scales = "free", space = "free") +
-  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
-  geom_point(aes(x = corr, y = p_log10, color = Dataset), alpha = 0.5) +
-  scale_y_continuous(breaks = seq(0, 60, by = 10), labels = seq(0, 60, by = 10)) +
-  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Dataset, label = Drug_Gene), force = 10, nudge_y = 3, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
-  scale_color_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
-  theme(legend.position = "none", plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
-  labs(x = "Pearson correlation coefficient (r)", y = "-log10(p-value)")
-all_pearson_summ_plot
-# ggsave("./plots/manuscript/all_pearson_summ_plot.png", all_pearson_summ_plot, device = "png", dpi = 450, width = 12, height = 10, units = "in")
-
-all_spearman_res <- rbind(ccle_spearman_res_filt, ctrp_spearman_res_filt, gdsc_spearman_res_filt)
-all_spearman_summ_plot <- ggplot(data = subset(all_spearman_res, p < 0.05)) +
-  facet_grid(Dataset ~ Metric, scales = "free", space = "free") +
-  geom_vline(xintercept = 0, color = "grey50", lty = 2, lwd = 0.3) +
-  geom_point(aes(x = corr, y = p_log10, color = Dataset), alpha = 0.5) +
-  scale_y_continuous(breaks = seq(0, 60, by = 10), labels = seq(0, 60, by = 10)) +
-  geom_text_repel(mapping = aes(y = p_log10, x = corr, color = Dataset, label = Drug_Gene), force = 10, nudge_y = 1, size = 2.5, segment.size = 0.2, segment.colour = "grey50", box.padding = 0.6) +
-  scale_color_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
-  theme(legend.position = "none", plot.margin = unit(c(5.5, 5.5, 5.5, 1.5), "pt")) +
-  annotate(geom = "text", x = 0, y = 30, label = c("", "", "", "", "afatinib_ERBB2 and lapatinib_ERBB2\n-log10(p-value) >> 100", ""), size = 3) +
-  labs(x = "Pearson correlation coefficient (r)", y = "-log10(p-value)")
-all_spearman_summ_plot
-# ggsave("./plots/manuscript/all_spearman_summ_plot.png", all_spearman_summ_plot, device = "png", dpi = 450, width = 12, height = 10, units = "in")
-```
-
-### Venn diagrams
-
-Venn diagram of drug-gene associations:
-```{r}
-futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
-
-ccle_mut_dgs <- as.character(ccle_signif_g2p_grid[!is.na(ccle_signif_g2p_grid$p.signif.adj),]$Drug_Gene)
-ctrp_mut_dgs <- as.character(ctrp_signif_g2p_grid[!is.na(ctrp_signif_g2p_grid$p.signif.adj),]$Drug_Gene)
-gdsc_mut_dgs <- as.character(gdsc_signif_g2p_grid[!is.na(gdsc_signif_g2p_grid$p.signif.adj),]$Drug_Gene)
-
-ccle_ge_dgs <- as.character(ccle_cor_res[ccle_cor_res$Spearman_Pval_GE < 0.05,]$Drug_Gene)
-ctrp_ge_dgs <- as.character(ctrp_cor_res[ctrp_cor_res$Spearman_Pval_GE < 0.05,]$Drug_Gene)
-gdsc_ge_dgs <- as.character(gdsc_cor_res[gdsc_cor_res$Spearman_Pval_GE < 0.05,]$Drug_Gene)
-
-ccle_cn_dgs <- as.character(ccle_cor_res[ccle_cor_res$Spearman_Pval_CN < 0.05,]$Drug_Gene)
-ctrp_cn_dgs <- as.character(ctrp_cor_res[ctrp_cor_res$Spearman_Pval_CN < 0.05,]$Drug_Gene)
-gdsc_cn_dgs <- as.character(gdsc_cor_res[gdsc_cor_res$Spearman_Pval_CN < 0.05,]$Drug_Gene)
-
-drug_venn_mut <- venn.diagram(list("CCLE" = ccle_mut_dgs, "CTRP" = ctrp_mut_dgs, "GDSC" = gdsc_mut_dgs), resolution = 5000, main = "A", main.pos = c(0, 1), main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 50, 120), cat.dist = c(0.001, 0.02, 0.0001), cat.cex = 1.5, cex = 1, filename = NULL, height = 4000)
-# in GDSC only
-drug_venn_mut[[7]]$label  <- paste(sort(setdiff(setdiff(gdsc_mut_dgs, ctrp_mut_dgs), ccle_mut_dgs)), collapse = "\n")
-# in GDSC and CTRP only
-drug_venn_mut[[8]]$label <- paste(intersect(gdsc_mut_dgs, ctrp_mut_dgs), collapse = "\n")
-# in CTRP only
-drug_venn_mut[[9]]$label <- paste(sort(setdiff(setdiff(ctrp_mut_dgs, gdsc_mut_dgs), ccle_mut_dgs)), collapse = "\n")
-# in CTRP and CCLE only
-drug_venn_mut[[10]]$label <- intersect(ccle_mut_dgs, ctrp_mut_dgs)
-
-drug_venn_ge <- venn.diagram(list("CCLE" = ccle_ge_dgs, "CTRP" = ctrp_ge_dgs, "GDSC" = gdsc_ge_dgs), resolution = 5000, main = "B", main.pos = c(0, 1), main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.001, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
-
-drug_venn_cn <- venn.diagram(list("CCLE" = ccle_cn_dgs, "CTRP" = ctrp_cn_dgs, "GDSC" = gdsc_cn_dgs), resolution = 5000, main = "C", main.pos = c(0, 1), main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(0, 0, 0), cat.dist = c(0.11, 0.11, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
-
-grid.arrange(grobTree(drug_venn_mut),
-             grobTree(drug_venn_ge),
-             grobTree(drug_venn_cn),
-             ncol = 1, 
-             heights = c(2/5, 2/5, 1/5))
-
-drugscreen_venns <- arrangeGrob(grobTree(drug_venn_mut),
-             grobTree(drug_venn_ge),
-             grobTree(drug_venn_cn),
-             ncol = 1, 
-             heights = c(2/5, 2/5, 1/5))
-# ggsave(file = "./plots/manuscript/drugscreen_venns.pdf", drugscreen_venns) #saves g
-
-# png("./plots/manuscript/drugscreen_venn_mut.png")
-# grid.newpage()
-# grid.draw(drug_venn_mut)
-# dev.off()
-```
-
-## P-values
-
-Mutation summaries for G2P gri comparisons:
-```{r}
-ccle_mut_summ <- merge(g2p_druggene_tally, ccle_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
-ccle_mut_summ$n <- ifelse(is.na(ccle_mut_summ$n), 0, ccle_mut_summ$n)
-ccle_mut_summ$InG2P <- ifelse(ccle_mut_summ$n != 0, "Yes", "No")
-ccle_mut_summ$Dataset <- "CCLE"
-
-ctrp_mut_summ <- merge(g2p_druggene_tally, ctrp_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
-ctrp_mut_summ$n <- ifelse(is.na(ctrp_mut_summ$n), 0, ctrp_mut_summ$n)
-ctrp_mut_summ$InG2P <- ifelse(ctrp_mut_summ$n != 0, "Yes", "No")
-ctrp_mut_summ$Dataset <- "CTRP"
-
-gdsc_mut_summ <- merge(g2p_druggene_tally, gdsc_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
-gdsc_mut_summ$n <- ifelse(is.na(gdsc_mut_summ$n), 0, gdsc_mut_summ$n)
-gdsc_mut_summ$InG2P <- ifelse(gdsc_mut_summ$n != 0, "Yes", "No")
-gdsc_mut_summ$Dataset <- "GDSC"
-
-g2p_mut_all_summ <- rbind(ccle_mut_summ, ctrp_mut_summ, gdsc_mut_summ)
-g2p_mut_all_summ$p_log10 <- -log10(g2p_mut_all_summ$p)
-```
-
-```{r fig.height=6, fig.width=12}
-pval_summ_mut <- g2p_mut_all_summ
-pval_summ_mut$Measure <- "Mutation Status"
-pval_summ_mut$Drug_Gene_Ordered <- NULL
-
-pval_summ_ge <- select(g2p_cor, Drug_Gene, n, Pearson_Pval_GE, InG2P, Dataset)
-colnames(pval_summ_ge)[colnames(pval_summ_ge) == "Pearson_Pval_GE"] <- "p"
-pval_summ_ge$p_log10 <- -log10(pval_summ_ge$p)
-pval_summ_ge$Measure <- "Gene Expression"
-
-pval_summ_cn <- select(g2p_cor, Drug_Gene, n, Pearson_Pval_CN, InG2P, Dataset)
-colnames(pval_summ_cn)[colnames(pval_summ_cn) == "Pearson_Pval_CN"] <- "p"
-pval_summ_cn$p_log10 <- -log10(pval_summ_cn$p)
-pval_summ_cn$Measure <- "Copy Number"
-
-pval_summ <- rbind(pval_summ_mut, pval_summ_ge, pval_summ_cn)
-pval_summ$Measure <- factor(pval_summ$Measure, levels = c("Mutation Status", "Gene Expression", "Copy Number"))
-
-pval_summ_plot <- ggplot(data = pval_summ, aes(x = p_log10, y = n, color = Dataset, shape = Dataset, label = Drug_Gene)) +
-  facet_wrap(~ Measure, scales = "free_x") +
-  geom_point(alpha = 0.7) +
-  scale_color_manual(values = c("green3", "darkslategray4", "darkturquoise")) +
-  geom_text_repel(data = filter(pval_summ, n > 20 & Measure == "Mutation Status"), mapping = aes(x = p_log10, y = n, color = Dataset, label = Drug_Gene), direction = "y", nudge_x = 9, hjust = 0, size = 2.5, segment.size = 0.1, segment.colour = "grey50", box.padding = 0.6, show.legend = FALSE) +
-  geom_text_repel(data = filter(pval_summ, n > 20 & Measure == "Gene Expression"), mapping = aes(x = p_log10, y = n, color = Dataset, label = Drug_Gene), direction = "y", nudge_x = 50, hjust = 0, size = 2.5, segment.size = 0.1, segment.colour = "grey50", box.padding = 0.6, show.legend = FALSE) +
-  geom_text_repel(data = filter(pval_summ, n > 20 & Measure == "Copy Number"), mapping = aes(x = p_log10, y = n, color = Dataset, label = Drug_Gene), direction = "y", nudge_x = 20, hjust = 0, size = 2.5, segment.size = 0.1, segment.colour = "grey50", box.padding = 0.6, show.legend = FALSE) +
-  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
-  labs(x = "-log10(p-value)", y = "Number of level A G2P associations") +
-  theme(legend.position = "bottom")
-pval_summ_plot
-
-# ggsave("./plots/manuscript/all_pval_summ_plot.png", pval_summ_plot, device = "png", dpi = 450, width = 12, height = 6, units = "in")
-
-pval_summ_plot2 <- ggplot(data = pval_summ, aes(x = p_log10, y = n, color = Dataset, shape = Dataset, label = Drug_Gene)) +
-  facet_wrap(~ Measure, scales = "free_x") +
-  geom_point(alpha = 0.7) +
-  scale_color_manual(values = c("green3", "darkslategray4", "darkturquoise")) +
-  geom_text_repel(data = filter(pval_summ, p_log10 > 5 & Measure == "Mutation Status"), mapping = aes(x = p_log10, y = n, color = Dataset, label = Drug_Gene), direction = "y", nudge_y = 10, hjust = 0, size = 2.5, segment.size = 0.1, segment.colour = "grey50", box.padding = 0.6, show.legend = FALSE) +
-  geom_text_repel(data = filter(pval_summ, p_log10 > 20 & Measure == "Gene Expression"), mapping = aes(x = p_log10, y = n, color = Dataset, label = Drug_Gene), direction = "y", nudge_y = 10, hjust = 0, size = 2.5, segment.size = 0.1, segment.colour = "grey50", box.padding = 0.6, show.legend = FALSE) +
-  geom_text_repel(data = filter(pval_summ, p_log10 > 7.5 & Measure == "Copy Number"), mapping = aes(x = p_log10, y = n, color = Dataset, label = Drug_Gene), direction = "y", nudge_y = 10, hjust = 0, size = 2.5, segment.size = 0.1, segment.colour = "grey50", box.padding = 0.6, show.legend = FALSE) +
-  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
-  labs(x = "-log10(p-value)", y = "Number of level A G2P associations") +
-  theme(legend.position = "bottom")
-pval_summ_plot2
-
-# ggsave("./plots/manuscript/all_pval_summ_plot2.png", pval_summ_plot2, device = "png", dpi = 450, width = 12, height = 6, units = "in")
-```
-
-## Pearson/Spearman comparison
-
-Compare significant Pearson and Spearman correlations:
-```{r}
-corr_summ_ge <- select(g2p_cor, Drug_Gene, n, Pearson_Pval_GE, Spearman_Pval_GE, InG2P, Dataset)
-corr_summ_ge$Pearson_Pval_GE_log10 <- -log10(corr_summ_ge$Pearson_Pval_GE)
-corr_summ_ge$Spearman_Pval_GE_log10 <- -log10(corr_summ_ge$Spearman_Pval_GE)
-corr_summ_ge$Overlap_Status <- ifelse(corr_summ_ge$Pearson_Pval_GE < 0.05 & corr_summ_ge$Spearman_Pval_GE < 0.05, "Both", ifelse(corr_summ_ge$Pearson_Pval_GE < 0.05, "Pearson", ifelse(corr_summ_ge$Spearman_Pval_GE < 0.05, "Spearman", NA)))
-corr_summ_ge$Overlap_Status_Bonf <- ifelse(corr_summ_ge$Pearson_Pval_GE < 0.05 / nrow(corr_summ_ge) & corr_summ_ge$Spearman_Pval_GE < 0.05 / nrow(corr_summ_ge), "Both", ifelse(corr_summ_ge$Pearson_Pval_GE < 0.05 / nrow(corr_summ_ge), "Pearson", ifelse(corr_summ_ge$Spearman_Pval_GE < 0.05 / nrow(corr_summ_ge), "Spearman", NA)))
-corr_summ_ge %>% count(Overlap_Status)
-corr_summ_ge %>% count(Overlap_Status_Bonf)
-
-corr_summ_cn <- select(g2p_cor, Drug_Gene, n, Pearson_Pval_CN, Spearman_Pval_CN, InG2P, Dataset)
-corr_summ_cn$Pearson_Pval_CN_log10 <- -log10(corr_summ_cn$Pearson_Pval_CN)
-corr_summ_cn$Spearman_Pval_CN_log10 <- -log10(corr_summ_cn$Spearman_Pval_CN)
-corr_summ_cn$Overlap_Status <- ifelse(corr_summ_cn$Pearson_Pval_CN < 0.05 & corr_summ_cn$Spearman_Pval_CN < 0.05, "Both", ifelse(corr_summ_cn$Pearson_Pval_CN < 0.05, "Pearson", ifelse(corr_summ_cn$Spearman_Pval_CN < 0.05, "Spearman", NA)))
-corr_summ_cn$Overlap_Status_Bonf <- ifelse(corr_summ_cn$Pearson_Pval_CN < 0.05 / nrow(corr_summ_cn) & corr_summ_cn$Spearman_Pval_CN < 0.05 / nrow(corr_summ_cn), "Both", ifelse(corr_summ_cn$Pearson_Pval_CN < 0.05 / nrow(corr_summ_cn), "Pearson", ifelse(corr_summ_cn$Spearman_Pval_CN < 0.05 / nrow(corr_summ_cn), "Spearman", NA)))
-corr_summ_cn %>% count(Overlap_Status)
-corr_summ_cn %>% count(Overlap_Status_Bonf)
-```
-
-## Summary stats
-
-```{r}
-# Mutation status
-g2p_mut_all_summ_stats <- g2p_mut_all_summ
-g2p_mut_all_summ_stats$n_true <- TRUE
-g2p_mut_all_summ_stats <- g2p_mut_all_summ_stats %>% drop_na(p) %>% group_by(Dataset, InG2P) %>% summarize(p_mean = round(mean(p), 2), p_sd = round(sd(p), 2), n = sum(n_true), n_signif = sum(p < 0.05), n_sig_perc = n_signif / n * 100)
-g2p_mut_all_summ_stats
-
-# Pearson correlations
-g2p_cor_stats <- g2p_cor
-g2p_cor_stats$n_true <- TRUE
-g2p_cor_stats <- g2p_cor_stats %>% group_by(Dataset, InG2P) %>% drop_na() %>% summarize(
-          ge_mean = round(mean(Pearson_GE_Abs), 5),
-          ge_sd = round(sd(Pearson_GE_Abs), 5),
-          ge_n = sum(n_true),
-          ge_n_signif = sum(Pearson_Pval_GE < 0.05),
-          ge_n_sig_perc = ge_n_signif / ge_n * 100,
-          cn_mean = round(mean(Pearson_CN_Abs), 3),
-          cn_sd = round(sd(Pearson_CN_Abs), 5),
-          cn_n = sum(n_true),
-          cn_n_signif = sum(Pearson_Pval_CN < 0.05),
-          cn_n_sig_perc = cn_n_signif / cn_n * 100)
-g2p_cor_stats
-```
-
-## CTRP example derivation
-
-Example p-value and Pearson correlation coefficient derivations for afatinib and ERBB2 in the CTRP dataset:
-```{r}
-ctrp_grid_summary_data <- filter(ctrp_data_g2p_grid, Drug_Gene == "afatinib_ERBB2")
-
-ctrp_grid_summary_mut_corr <- wilcox.test(AUC_zscore ~ Mutation_Status_Nonsilent, data = ctrp_grid_summary_data[!is.na(ctrp_grid_summary_data$Mutation_Status_Nonsilent),], paired = FALSE)
-ctrp_grid_summary_mut_corr_text <- paste0("W = ", formatC(ctrp_grid_summary_mut_corr$statistic, format = "d", big.mark = ","), "\np = ", round(ctrp_grid_summary_mut_corr$p.value, 3))
-
-ctrp_grid_summary_ge_corr <- cor.test(y = ctrp_grid_summary_data$AUC, x = ctrp_grid_summary_data$RPKM, method = "pearson", use = "complete.obs")
-ctrp_grid_summary_ge_corr_text <- paste0("r(", ctrp_grid_summary_ge_corr$parameter, ") = ", formatC(ctrp_grid_summary_ge_corr$estimate, digits = 2, format = "f"), "\np ", ifelse(round(ctrp_grid_summary_ge_corr$p.value, 3) == 0, "< 0.001", paste0("= ", round(ctrp_grid_summary_ge_corr$p.value, 3))))
-
-ctrp_grid_summary_cn_corr <- cor.test(y = ctrp_grid_summary_data$AUC, x = ctrp_grid_summary_data$CN, method = "pearson", use = "complete.obs")
-ctrp_grid_summary_cn_corr_text <- paste0("r(", ctrp_grid_summary_cn_corr$parameter, ") = ", formatC(ctrp_grid_summary_cn_corr$estimate, digits = 2, format = "f"), "\np ", ifelse(round(ctrp_grid_summary_cn_corr$p.value, 3) == 0, "< 0.001", paste0("= ", round(ctrp_grid_summary_cn_corr$p.value, 3))))
-
-ctrp_grid_summary_mut_plot <- ggplot(data = ctrp_grid_summary_data[!is.na(ctrp_grid_summary_data$Mutation_Status_Nonsilent),], aes(y = AUC_zscore, x = Mutation_Status_Nonsilent, fill = Mutation_Status_Nonsilent)) +
-  geom_boxplot(outlier.shape = NA, alpha = 0.6) +
-  geom_jitter(width = 0.2, shape = 21) +
-  scale_fill_manual(values = c("Wildtype" = "lightsteelblue1", "Mutant" = "steelblue4")) +
-  annotate(geom = "text", label = ctrp_grid_summary_mut_corr_text, x = 1.5, y = 1.3) +
-  guides(fill = FALSE) +
-  labs(x = "ERBB2 mutation status", y = "Afatinib AUC (z-score)") +
-  geom_segment(aes(x = 1, y = 1.5, xend = 1.1, yend = 1.5), lwd = 0.2) +
-  geom_segment(aes(x = 1.9, y = 1.5, xend = 2, yend = 1.5), lwd = 0.2) +
-  geom_segment(aes(x = 1, y = 1.5, xend = 1, yend = 1.35), lwd = 0.2) +
-  geom_segment(aes(x = 2, y = 1.5, xend = 2, yend = 1.35), lwd = 0.2)
-ctrp_grid_summary_mut_plot
-
-ctrp_grid_summary_ge_plot <- ggplot(data = ctrp_grid_summary_data, aes(y = AUC_zscore, x = RPKM)) +
-  geom_point(alpha = 0.25, size = 1.25, color = "gray4") +
-  geom_smooth(method = "lm", se = FALSE, lwd = 0.5, lty = 2) +
-  annotate(geom = "text", label = ctrp_grid_summary_ge_corr_text, x = 2000, y = 1.3) +
-  labs(x = "ERBB2 gene expression (RPKM)", y = "Afatinib AUC (z-score)") +
-  theme(axis.title.y = element_blank()) +
-  geom_curve(aes(x = 750, y = -1.9, xend = 1720, yend = 1.1), lwd = 0.2, curvature = -0.2, arrow = arrow(length = unit(0.03, "npc")))
-ctrp_grid_summary_ge_plot
-
-ctrp_grid_summary_cn_plot <- ggplot(data = ctrp_grid_summary_data, aes(y = AUC_zscore, x = CN)) +
-  geom_point(alpha = 0.25, size = 1.25, color = "gray4") +
-  geom_smooth(method = "lm", se = FALSE, lwd = 0.5, lty = 2) +
-  annotate(geom = "text", label = ctrp_grid_summary_cn_corr_text, x = 5, y = 1.3) +
-  labs(x = "ERBB2 copy number (log2 ratio)") +
-  theme(axis.title.y = element_blank()) +
-  geom_curve(aes(x = 4, y = -2.3, xend = 5, yend = 0.8), lwd = 0.2, curvature = 0.2, arrow = arrow(length = unit(0.03, "npc")))
-ctrp_grid_summary_cn_plot
-
-# ggsave("./plots/manuscript/ctrp_grid_summary_mut_plot.png", ctrp_grid_summary_mut_plot, device = "png", dpi = 450, width = 3, height = 4, units = "in")
-# ggsave("./plots/manuscript/ctrp_grid_summary_ge_plot.png", ctrp_grid_summary_ge_plot, device = "png", dpi = 450, width = 5, height = 4, units = "in")
-# ggsave("./plots/manuscript/ctrp_grid_summary_cn_plot.png", ctrp_grid_summary_cn_plot, device = "png", dpi = 450, width = 5, height = 4, units = "in")
-```
-
-# MUT/GE/CN: By lineage
-
---------------------------------------------------------------------------------
-
-## Big grid summary plot
-
-Big grid plot by lineages:
-```{r fig.height=20, fig.width=12}
-dgl_mut <- dgl_mut_grid_summ
-dgl_mut$Sign <- "None"
-dgl_mut$Measure <- "Mutation Status"
-colnames(dgl_mut)[colnames(dgl_mut) == "p"] <- "Statistic"
-dgl_mut$Drug_Gene_Lin <- NULL
-
-dgl_ge <- select(dgl_signif_pearson_g2p_grid, Drug_Gene, group_general_lineage_name, n, Pearson_GE_Abs, InG2P, Dataset, Pearson_GE_Sign)
-dgl_ge$Measure <- "Gene Expression"
-colnames(dgl_ge)[colnames(dgl_ge) == "Pearson_GE_Abs"] <- "Statistic"
-colnames(dgl_ge)[colnames(dgl_ge) == "Pearson_GE_Sign"] <- "Sign"
-
-dgl_cn <- select(dgl_signif_pearson_g2p_grid, Drug_Gene, group_general_lineage_name, n, Pearson_CN_Abs, InG2P, Dataset, Pearson_CN_Sign)
-dgl_cn$Measure <- "Copy Number"
-colnames(dgl_cn)[colnames(dgl_cn) == "Pearson_CN_Abs"] <- "Statistic"
-colnames(dgl_cn)[colnames(dgl_cn) == "Pearson_CN_Sign"] <- "Sign"
-
-dgl_all <- rbind(dgl_mut, dgl_ge, dgl_cn)
-dgl_all$Sign <- ifelse(is.na(dgl_all$Sign), "None", dgl_all$Sign)
-
-dgl_all_plot <- ggplot(data = dgl_all, aes(x = InG2P, y = Statistic)) +
-  facet_grid(group_general_lineage_name ~ Measure * Dataset) +
-  geom_jitter(mapping = aes(shape = Sign, fill = InG2P, color = InG2P), width = 0.4, alpha = 0.5, size = 1) +
-  geom_boxplot(width = 0.25, fill = NA, outlier.shape = NA) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_shape_manual(values = c(25, 24, 4), labels = c("Negative", "Positive", "NA")) +
-  theme(legend.position = "top") +
-  guides(color = FALSE, fill = FALSE)
-
-# ggsave("./plots/manuscript/all_dgl_plot.png", dgl_all_plot, device = "png", dpi = 450, width = 12, height = 40, units = "in")
-```
-
-## Kolmogorov-Smirnov tests
-
-```{r}
-MakeCorrResSummaryTable <- function(df_list, dataset_name) {
-  res_full <- data.frame(matrix(ncol = 8, nrow = 0))
-  for(i in 1:length(df_list)) {
-    corr_res <- df_list[[i]] %>% group_by(G2P_DGL) %>% summarize(Dataset = dataset_name,
-                Drug_Gene = names(df_list)[i],
-                Lineages = paste(as.character(unique(group_general_lineage_name)), collapse = ", "),
-                N_Lineages = length(as.character(unique(group_general_lineage_name))),
-                Pearson_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
-                Pearson_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$estimate,
-                Spearman_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
-                Spearman_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$estimate)
-    corr_res <- merge(corr_res, compare_means(AUC_zscore ~ Mutation_Status_Nonsilent, data = df_list[[i]], group.by = "G2P_DGL", method = "wilcox.test")[, c("G2P_DGL", "p")], by = "G2P_DGL", all = TRUE)
-    corr_res$Mut_Signif <- ifelse(corr_res$p < 0.05, 1, 0)
-    res_full <- rbind(res_full, corr_res)
-  }
-  return(res_full)
-}
-
-G2PCorr_KStest <- function(dataset, dataset_name) {
-  Metric <- colnames(dataset)[6:9]
-  D_stat <- NULL
-  pval <- NULL
-  signif <- NULL
-
-  yes <- dataset[dataset$G2P_DGL == "Yes",]
-  no <- dataset[dataset$G2P_DGL == "No",]
-
-  for(i in 6:9) {
-    # print(yes[[colnames(yes)[i]]])
-    # print(no[[colnames(no)[i]]])
-    test <- ks.test(yes[[colnames(yes)[i]]], no[[colnames(no)[i]]])
-    D_stat <- c(D_stat, test$statistic)
-    pval <- c(pval, test$p.value)
-    signif <- c(signif, ifelse(test$p.value < 0.001, "***", ifelse(test$p.value < 0.01, "**", ifelse(test$p.value < 0.05, "*", NA))))
-  }
-  df <- data.frame(Metric, D_stat, pval, signif)
-  df$Dataset <- dataset_name
-  return(df)
-}
-```
-
-```{r, warning=FALSE}
-# cannot compute exact p-value with ties??????
-
-ccle_data_g2p$G2P_DGL <- ifelse(ccle_data_g2p$Drug_Gene_Lin %in% g2p_dgls, "Yes", "No")
-ccle_data_g2p_split <- split(ccle_data_g2p, f = ccle_data_g2p$Drug_Gene)
-ccle_corr_all <- MakeCorrResSummaryTable(ccle_data_g2p_split, dataset_name = "CCLE")
-
-ctrp_data_g2p$G2P_DGL <- ifelse(ctrp_data_g2p$Drug_Gene_Lin %in% g2p_dgls, "Yes", "No")
-ctrp_data_g2p_split <- split(ctrp_data_g2p, f = ctrp_data_g2p$Drug_Gene)
-ctrp_corr_all <- MakeCorrResSummaryTable(ctrp_data_g2p_split, dataset_name = "CTRP")
-
-gdsc_data_g2p$G2P_DGL <- ifelse(gdsc_data_g2p$Drug_Gene_Lin %in% g2p_dgls, "Yes", "No")
-gdsc_data_g2p_split <- split(gdsc_data_g2p, f = gdsc_data_g2p$Drug_Gene)
-gdsc_corr_all <- MakeCorrResSummaryTable(gdsc_data_g2p_split, dataset_name = "GDSC")
-
-g2p_corr_all <- rbind(ccle_corr_all, ctrp_corr_all, gdsc_corr_all)
-
-ccle_corr_stats <- G2PCorr_KStest(ccle_corr_all, "CCLE")
-ctrp_corr_stats <- G2PCorr_KStest(ctrp_corr_all, "CTRP")
-gdsc_corr_stats <- G2PCorr_KStest(gdsc_corr_all, "GDSC")
-g2p_corr_stats <- rbind(ccle_corr_stats, ctrp_corr_stats, gdsc_corr_stats)
-g2p_corr_stats <- g2p_corr_stats %>% separate(col = Metric, into = c("Correlation_Method", "corr", "Metric"), sep = "_")
-g2p_corr_stats$Metric <- ifelse(g2p_corr_stats$Metric == "GE", "Gene Expression", "Copy Number")
-g2p_corr_stats
-
-g2p_mut_stats <- g2p_corr_all %>% group_by(Dataset, G2P_DGL) %>% drop_na(Mut_Signif) %>% summarize(N_Signif_Muts = sum(Mut_Signif),
-                                                                                                   Total_Tests = length(Mut_Signif),
-                                                                                                   Perc_Signif = N_Signif_Muts / Total_Tests * 100)
-g2p_mut_stats
-```
-
-Plot of Kolmogorov-Smirnov test results comparing correlations between CN/GE and AUC z-score in G2P and non-G2P lineages:
-```{r fig.height=6, fig.width=12}
-g2p_corr_4plot <- g2p_corr_all
-g2p_corr_4plot$p <- NULL
-g2p_corr_4plot$Mut_Signif <- NULL
-g2p_corr_4plot <- melt(g2p_corr_4plot, id.vars = colnames(g2p_corr_4plot)[1:5], measure.vars = colnames(g2p_corr_4plot)[6:9], value.name = "Correlation")
-g2p_corr_4plot <- g2p_corr_4plot %>% separate(col = variable, into = c("Correlation_Method", "corr", "Metric"), sep = "_", remove = FALSE)
-g2p_corr_4plot$Metric <- ifelse(g2p_corr_4plot$Metric == "GE", "Gene Expression", "Copy Number")
-
-g2p_ks_res_plot <- ggplot(data = g2p_corr_4plot) +
-  facet_grid(Correlation_Method ~ Metric * Dataset) +
-  geom_violin(aes(y = Correlation, x = G2P_DGL, fill = G2P_DGL, color = G2P_DGL), alpha = 0.3) +
-  geom_boxplot(width = 0.075, aes(y = Correlation, x = G2P_DGL, color = G2P_DGL)) +
-  geom_jitter(width = 0.3, alpha = 0.7, aes(y = Correlation, x = G2P_DGL, color = G2P_DGL)) +
-  theme(legend.position = "none") +
-  coord_cartesian(ylim = c(-1, 1)) +
-  geom_text(data = g2p_corr_stats, aes(x = 1.5, y = 0.8, label = paste0("D = ", formatC(D_stat, digits = 2, format = "f"), ", p = ", ifelse(pval > 0.1, round(pval, 2), round(pval, 3)), "\n", ifelse(is.na(signif), "", signif)))) +
-  labs(x = "Is the lineage in a G2P DGL?", y = "Correlation Coefficint", subtitle = "Kolmogorov-Smirnov test results comparing correlations between CN/GE and AUC z-score in G2P and non-G2P lineages.")
-g2p_ks_res_plot
-
-# ggsave("./plots/manuscript/g2p_ks_res_plot.png", g2p_ks_res_plot, device = "png", dpi = 450, width = 12, height = 6, units = "in")
-```
-
-```{r fig.height=6, fig.width=12}
-g2p_ks_res_plot_spearman <- ggplot(data = filter(g2p_corr_4plot, Correlation_Method == "Spearman")) +
-  facet_grid(Metric ~ Dataset, labeller = labeller(yfacet = c('CN' = "Copy Number", 'GE' = "Gene Expression"))) +
-  geom_violin(aes(y = Correlation, x = G2P_DGL, fill = Dataset, color = Dataset, alpha = G2P_DGL)) +
-  geom_boxplot(width = 0.075, aes(y = Correlation, x = G2P_DGL, color = Dataset)) +
-  geom_jitter(width = 0.3, alpha = 0.8, aes(y = Correlation, x = G2P_DGL, color = Dataset)) +
-  theme(legend.position = "none") +
-  scale_alpha_manual(values = c("Yes" = 0.6, "No" = 0.2)) +
-  scale_fill_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
-  scale_color_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4", "CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
-  coord_cartesian(ylim = c(-1, 1)) +
-  geom_text(data = filter(g2p_corr_stats, Correlation_Method == "Spearman"), aes(x = 1.5, y = 0.8, label = paste0("D = ", formatC(D_stat, digits = 2, format = "f"), ", p = ", ifelse(pval > 0.1, round(pval, 2), round(pval, 3)), "\n", ifelse(is.na(signif), "", signif)))) +
-  labs(x = "Is the lineage in a G2P DGL?", y = "Spearman Correlation Coefficient")
-g2p_ks_res_plot_spearman
-
-# ggsave("./plots/manuscript/g2p_spearman_ks_res_plot.pdf", g2p_ks_res_plot_spearman, device = "pdf", dpi = 500, width = 12, height = 6, units = "in")
-```
-
-# Compare pancancer vs. lineage
-
---------------------------------------------------------------------------------
-
-```{r}
-compare_grid <- expand.grid(g2p_druggenes, unique(ccl_converter$group_general_lineage_name), c("CCLE", "CTRP", "GDSC"), c("Gene Expression", "Copy Number", "Mutation Status"))
-colnames(compare_grid) <- c("Drug_Gene", "group_general_lineage_name", "Dataset", "Metric")
-
-pancan_ge <- select(filter(all_pearson_res, Metric == "Gene Expression"), Drug_Gene, p, Dataset, p_log10)
-colnames(pancan_ge)[colnames(pancan_ge) == "p"] <- "p_pancan"
-colnames(pancan_ge)[colnames(pancan_ge) == "p_log10"] <- "p_log10_pancan"
-compare_ge <- select(dgl_signif_pearson_g2p_grid, Drug_Gene, group_general_lineage_name, n, Pearson_Pval_GE, Drug_Gene_Lin, InG2P, Dataset)
-colnames(compare_ge)[colnames(compare_ge) == "Pearson_Pval_GE"] <- "p"
-compare_ge$p_log10 <- -log10(compare_ge$p)
-compare_ge <- merge(compare_ge, pancan_ge, by = c("Drug_Gene", "Dataset"), all = TRUE)
-compare_ge$Compare_Pvals <- ifelse(compare_ge$p_log10 < compare_ge$p_log10_pancan, "Under", "Above")
-compare_ge$Metric <- "Gene Expression"
-
-pancan_cn <- select(filter(all_pearson_res, Metric == "Copy Number"), Drug_Gene, p, Dataset, p_log10)
-colnames(pancan_cn)[colnames(pancan_cn) == "p"] <- "p_pancan"
-colnames(pancan_cn)[colnames(pancan_cn) == "p_log10"] <- "p_log10_pancan"
-compare_cn <- select(dgl_signif_pearson_g2p_grid, Drug_Gene, group_general_lineage_name, n, Pearson_Pval_CN, Drug_Gene_Lin, InG2P, Dataset)
-colnames(compare_cn)[colnames(compare_cn) == "Pearson_Pval_CN"] <- "p"
-compare_cn$p_log10 <- -log10(compare_cn$p)
-compare_cn <- merge(compare_cn, pancan_cn, by = c("Drug_Gene", "Dataset"), all = TRUE)
-compare_cn$Compare_Pvals <- ifelse(compare_cn$p_log10 < compare_cn$p_log10_pancan, "Under", "Above")
-compare_cn$Metric <- "Copy Number"
-
-pancan_mut <- all_mut_res
-pancan_mut$Metric <- NULL
-pancan_mut$corr <- NULL
-colnames(pancan_mut)[colnames(pancan_mut) == "p"] <- "p_pancan"
-colnames(pancan_mut)[colnames(pancan_mut) == "p_log10"] <- "p_log10_pancan"
-compare_mut <- dgl_mut_grid_summ
-compare_mut$p_log10 <- -log10(compare_mut$p)
-compare_mut <- merge(compare_mut, pancan_mut, by = c("Drug_Gene", "Dataset"), all = TRUE)
-compare_mut$Compare_Pvals <- ifelse(compare_mut$p_log10 < compare_mut$p_log10_pancan, "Under", "Above")
-compare_mut$Metric <- "Mutation Status"
-
-compare_data <- filter(rbind(compare_ge, compare_cn, compare_mut), Drug_Gene %in% g2p_druggenes)
-compare_data <- merge(compare_grid, compare_data, by = c("Drug_Gene", "group_general_lineage_name", "Dataset", "Metric"), all.x = TRUE)
-```
-
-```{r}
-compare_data_stats <- compare_data %>% count(Metric, Compare_Pvals)
-compare_data_stats
-```
-
-```{r fig.height=12, fig.width=12}
-compare_mut_plot <- ggplot(data = filter(compare_data, Metric == "Mutation Status"), aes(x = group_general_lineage_name, y = Drug_Gene)) +
-  facet_wrap(~ Dataset) +
-  geom_point(aes(shape = Compare_Pvals, fill = p_log10), color = "gray50") +
-  scale_fill_gradient2(low = "white", mid = "white", high = "darkorchid4", midpoint = 1.3010299957) +
-  scale_shape_manual(values = c(25, 24), labels = c("Below", "Above")) +
-  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4), legend.position = "top") +
-  labs(title = "Mutation Status",
-       subtitle = paste0("Above: ", filter(compare_data_stats, Metric == "Mutation Status" & Compare_Pvals == "Above")$nn, "\n",
-                         "Under: ", filter(compare_data_stats, Metric == "Mutation Status" & Compare_Pvals == "Under")$nn, "\n",
-                         "Not tested: ", filter(compare_data_stats, Metric == "Mutation Status" & is.na(Compare_Pvals))$nn),
-       x = "Lineage", y = "Drug-Gene", shape = "Compare linege p-value to pancancer p-value:", fill = "-log10(p)")
-# ggsave("./plots/manuscript/compare_mut_plot.png", compare_mut_plot, device = "png", dpi = 450, width = 12, height = 12, units = "in")
-
-compare_ge_plot <- ggplot(data = filter(compare_data, Metric == "Gene Expression"), aes(x = group_general_lineage_name, y = Drug_Gene)) +
-  facet_wrap(~ Dataset) +
-  geom_point(aes(shape = Compare_Pvals, fill = p_log10), color = "gray50") +
-  scale_fill_gradient2(low = "white", mid = "white", high = "darkorchid4", midpoint = 1.3010299957) +
-  scale_shape_manual(values = c(25, 24), labels = c("Below", "Above")) +
-  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4), legend.position = "top") +
-  labs(title = "Gene Expression",
-       subtitle = paste0("Above: ", filter(compare_data_stats, Metric == "Gene Expression" & Compare_Pvals == "Above")$nn, "\n",
-                         "Under: ", filter(compare_data_stats, Metric == "Gene Expression" & Compare_Pvals == "Under")$nn, "\n",
-                         "Not tested: ", filter(compare_data_stats, Metric == "Gene Expression" & is.na(Compare_Pvals))$nn),
-       x = "Lineage", y = "Drug-Gene", shape = "Compare linege p-value to pancancer p-value:", fill = "-log10(p)")
-# ggsave("./plots/manuscript/compare_ge_plot.png", compare_ge_plot, device = "png", dpi = 450, width = 12, height = 12, units = "in")
-
-compare_cn_plot <- ggplot(data = filter(compare_data, Metric == "Copy Number"), aes(x = group_general_lineage_name, y = Drug_Gene)) +
-  facet_wrap(~ Dataset) +
-  geom_point(aes(shape = Compare_Pvals, fill = p_log10), color = "gray50") +
-  scale_fill_gradient2(low = "white", mid = "white", high = "darkorchid4", midpoint = 1.3010299957) +
-  scale_shape_manual(values = c(25, 24), labels = c("Below", "Above")) +
-  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4), legend.position = "top") +
-  labs(title = "Copy Number",
-       subtitle = paste0("Above: ", filter(compare_data_stats, Metric == "Copy Number" & Compare_Pvals == "Above")$nn, "\n",
-                         "Under: ", filter(compare_data_stats, Metric == "Copy Number" & Compare_Pvals == "Under")$nn, "\n",
-                         "Not tested: ", filter(compare_data_stats, Metric == "Copy Number" & is.na(Compare_Pvals))$nn),
-       x = "Lineage", y = "Drug-Gene", shape = "Compare linege p-value to pancancer p-value:", fill = "-log10(p)")
-# ggsave("./plots/manuscript/compare_cn_plot.png", compare_cn_plot, device = "png", dpi = 450, width = 12, height = 12, units = "in")
-```
-
-# OLD: Distribution t-tests
-
---------------------------------------------------------------------------------
-
-## Tests
-
-```{r}
-ccle_pearson_ttest_GE <- t.test(ccle_cor_res$Pearson_Corr_GE ~ ccle_cor_res$InG2P)
-ccle_pearson_ttest_res_GE <- paste0("t(", round(ccle_pearson_ttest_GE$parameter, 0), ") = ", round(ccle_pearson_ttest_GE$statistic, 2), ", p = ", round(ccle_pearson_ttest_GE$p.value, 2))
-ccle_pearson_ttest_CN <- t.test(ccle_cor_res$Pearson_Corr_CN ~ ccle_cor_res$InG2P)
-ccle_pearson_ttest_res_CN <- paste0("t(", round(ccle_pearson_ttest_CN$parameter, 0), ") = ", round(ccle_pearson_ttest_CN$statistic, 2), ", p = ", round(ccle_pearson_ttest_CN$p.value, 2))
-ccle_spearman_ttest_GE <- t.test(ccle_cor_res$Spearman_Corr_GE ~ ccle_cor_res$InG2P)
-ccle_spearman_ttest_res_GE <- paste0("t(", round(ccle_spearman_ttest_GE$parameter, 0), ") = ", round(ccle_spearman_ttest_GE$statistic, 2), ", p = ", round(ccle_spearman_ttest_GE$p.value, 2))
-ccle_spearman_ttest_CN <- t.test(ccle_cor_res$Spearman_Corr_CN ~ ccle_cor_res$InG2P)
-ccle_spearman_ttest_res_CN <- paste0("t(", round(ccle_spearman_ttest_CN$parameter, 0), ") = ", round(ccle_spearman_ttest_CN$statistic, 2), ", p = ", formatC(ccle_spearman_ttest_CN$p.value, 2, format = "f"))
-
-ctrp_pearson_ttest_GE <- t.test(ctrp_cor_res$Pearson_Corr_GE ~ ctrp_cor_res$InG2P)
-ctrp_pearson_ttest_res_GE <- paste0("t(", round(ctrp_pearson_ttest_GE$parameter, 0), ") = ", round(ctrp_pearson_ttest_GE$statistic, 2), ", p ", ifelse(round(ctrp_pearson_ttest_GE$p.value, 3) == 0, "< 0.001", paste0("= ", round(ctrp_pearson_ttest_GE$p.value, 3))))
-ctrp_pearson_ttest_CN <- t.test(ctrp_cor_res$Pearson_Corr_CN ~ ctrp_cor_res$InG2P)
-ctrp_pearson_ttest_res_CN <- paste0("t(", round(ctrp_pearson_ttest_CN$parameter, 0), ") = ", round(ctrp_pearson_ttest_CN$statistic, 2), ", p = ", round(ctrp_pearson_ttest_CN$p.value, 3))
-ctrp_spearman_ttest_GE <- t.test(ctrp_cor_res$Spearman_Corr_GE ~ ctrp_cor_res$InG2P)
-ctrp_spearman_ttest_res_GE <- paste0("t(", round(ctrp_spearman_ttest_GE$parameter, 0), ") = ", round(ctrp_spearman_ttest_GE$statistic, 2), ", p = ", round(ctrp_spearman_ttest_GE$p.value, 2))
-ctrp_spearman_ttest_CN <- t.test(ctrp_cor_res$Spearman_Corr_CN ~ ctrp_cor_res$InG2P)
-ctrp_spearman_ttest_res_CN <- paste0("t(", round(ctrp_spearman_ttest_CN$parameter, 0), ") = ", round(ctrp_spearman_ttest_CN$statistic, 2), ", p = ", round(ctrp_spearman_ttest_CN$p.value, 2))
-
-gdsc_pearson_ttest_GE <- t.test(gdsc_cor_res$Pearson_Corr_GE ~ gdsc_cor_res$InG2P)
-gdsc_pearson_ttest_res_GE <- paste0("t(", round(gdsc_pearson_ttest_GE$parameter, 0), ") = ", round(gdsc_pearson_ttest_GE$statistic, 2), ", p = ", round(gdsc_pearson_ttest_GE$p.value, 3))
-gdsc_pearson_ttest_CN <- t.test(gdsc_cor_res$Pearson_Corr_CN ~ gdsc_cor_res$InG2P)
-gdsc_pearson_ttest_res_CN <- paste0("t(", round(gdsc_pearson_ttest_CN$parameter, 0), ") = ", round(gdsc_pearson_ttest_CN$statistic, 2), ", p = ", round(gdsc_pearson_ttest_CN$p.value, 3))
-gdsc_spearman_ttest_GE <- t.test(gdsc_cor_res$Spearman_Corr_GE ~ gdsc_cor_res$InG2P)
-gdsc_spearman_ttest_res_GE <- paste0("t(", round(gdsc_spearman_ttest_GE$parameter, 0), ") = ", round(gdsc_spearman_ttest_GE$statistic, 2), ", p = ", round(gdsc_spearman_ttest_GE$p.value, 2))
-gdsc_spearman_ttest_CN <- t.test(gdsc_cor_res$Spearman_Corr_CN ~ gdsc_cor_res$InG2P)
-gdsc_spearman_ttest_res_CN <- paste0("t(", round(gdsc_spearman_ttest_CN$parameter, 0), ") = ", round(gdsc_spearman_ttest_CN$statistic, 2), ", p = ", round(gdsc_spearman_ttest_CN$p.value, 2))
-
-g2p_cor_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"), Pearson_Test_Results_GE = c(ccle_pearson_ttest_res_GE, ctrp_pearson_ttest_res_GE, gdsc_pearson_ttest_res_GE), Pearson_Test_Results_CN = c(ccle_pearson_ttest_res_CN, ctrp_pearson_ttest_res_CN, gdsc_pearson_ttest_res_CN), Spearman_Test_Results_GE = c(ccle_spearman_ttest_res_GE, ctrp_spearman_ttest_res_GE, gdsc_spearman_ttest_res_GE), Spearman_Test_Results_CN = c(ccle_spearman_ttest_res_CN, ctrp_spearman_ttest_res_CN, gdsc_spearman_ttest_res_CN))
-```
-
-## Mut
-
-CRISPR mutation status plots of p-values:
-```{r fig.height=1.5, fig.width=12}
-crispr_signif_g2p_gene$y_label <- "CRISPR"
-crispr_signif_g2p_gene$Hugo_Symbol <- factor(crispr_signif_g2p_gene$Hugo_Symbol, levels = g2p_genes)
-crispr_signif_g2p_gene$p <- as.numeric(as.character(crispr_signif_g2p_gene$p))
-
-crispr_mut_heatmap_plot <- ggplot(data = crispr_signif_g2p_gene, aes(x = Hugo_Symbol, y = y_label)) +
-  geom_tile(aes(fill = p)) +
-  scale_fill_gradientn(colors = c("darkgreen", "honeydew", "white"), values = c(0, 0.05, 1), na.value = "darksalmon") +
-  scale_x_discrete(drop = FALSE) +
-  theme(axis.title.y = element_blank(), axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 10)) +
-  labs(x = "Gene")
-crispr_mut_heatmap_plot
-
-# write.table(crispr_signif_g2p_gene, file = "~/Desktop/crispr_signif_g2p_gene_20181203.csv", quote = FALSE, sep = ",", row.names = FALSE)
-# ggsave("./plots/manuscript/crispr_mut_heatmap_plot_example.png", crispr_mut_heatmap_plot, device = "png", dpi = 450, width = 12, height = 1.5, units = "in")
-```
-
-```{r}
-ccle_mut_summ <- merge(g2p_druggene_tally, ccle_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
-ccle_mut_summ$n <- ifelse(is.na(ccle_mut_summ$n), 0, ccle_mut_summ$n)
-ccle_mut_summ$InG2P <- ifelse(ccle_mut_summ$n != 0, "Yes", "No")
-ccle_mut_summ$Dataset <- "CCLE"
-ccle_p_ttest <- t.test(ccle_mut_summ$p ~ ccle_mut_summ$InG2P)
-ccle_p_ttest_res <- paste0("t(", round(ccle_p_ttest$parameter, 0), ") = ", round(ccle_p_ttest$statistic, 2), ", p = ", round(ccle_p_ttest$p.value, 2))
-
-ctrp_mut_summ <- merge(g2p_druggene_tally, ctrp_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
-ctrp_mut_summ$n <- ifelse(is.na(ctrp_mut_summ$n), 0, ctrp_mut_summ$n)
-ctrp_mut_summ$InG2P <- ifelse(ctrp_mut_summ$n != 0, "Yes", "No")
-ctrp_mut_summ$Dataset <- "CTRP"
-ctrp_p_ttest <- t.test(ctrp_mut_summ$p ~ ctrp_mut_summ$InG2P)
-ctrp_p_ttest_res <- paste0("t(", round(ctrp_p_ttest$parameter, 0), ") = ", round(ctrp_p_ttest$statistic, 2), ", p = ", formatC(ctrp_p_ttest$p.value, digits = 2, format = "f"))
-
-gdsc_mut_summ <- merge(g2p_druggene_tally, gdsc_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
-gdsc_mut_summ$n <- ifelse(is.na(gdsc_mut_summ$n), 0, gdsc_mut_summ$n)
-gdsc_mut_summ$InG2P <- ifelse(gdsc_mut_summ$n != 0, "Yes", "No")
-gdsc_mut_summ$Dataset <- "GDSC"
-gdsc_p_ttest <- t.test(gdsc_mut_summ$p ~ gdsc_mut_summ$InG2P)
-gdsc_p_ttest_res <- paste0("t(", round(gdsc_p_ttest$parameter, 0), ") = ", round(gdsc_p_ttest$statistic, 2), ", p = ", formatC(gdsc_p_ttest$p.value, digits = 2, format = "f"))
-
-g2p_mut_all_summ <- rbind(ccle_mut_summ, ctrp_mut_summ, gdsc_mut_summ)
-g2p_mut_all_summ$p_log10 <- -log10(g2p_mut_all_summ$p)
-g2p_mut_all_summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"), Test_Results_p = c(ccle_p_ttest_res, ctrp_p_ttest_res, gdsc_p_ttest_res))
-g2p_mut_all_summ$Drug_Gene_Ordered <- factor(g2p_mut_all_summ$Drug_Gene, levels = as.character(unique(g2p_mut_all_summ$Drug_Gene)), labels = sapply(strsplit(x = as.character(unique(g2p_mut_all_summ$Drug_Gene)), split = "_"), function(x) paste0(x[1], "\n", x[2])))
-```
-
-```{r fig.height=5, fig.width=12}
-plot_p_point <- ggplot(data = g2p_mut_all_summ, aes(x = p, y = n, label = Drug_Gene)) +
-  facet_wrap(~ Dataset, scales = "free_x") +
-  geom_point(mapping = aes(color = InG2P), alpha = 0.5) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
-  geom_text_repel(data = subset(g2p_mut_all_summ, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
-  geom_text(data = g2p_mut_all_summ_text, mapping = aes(x = 0.5, y = 115, label = Test_Results_p)) +
-  labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations") +
-  theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
-
-plot_p_box <- ggplot(data = g2p_mut_all_summ) +
-  facet_wrap(~ Dataset, scales = "free_x") +
-  geom_violin(mapping = aes(color = InG2P, fill = InG2P, y = p, x = InG2P), alpha = 0.35) +
-  geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), width = 0.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  coord_flip() +
-  labs(x = "In G2P?") +
-  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
-plot_p_point <- ggplot_gtable(ggplot_build(plot_p_point))
-plot_p_box <- ggplot_gtable(ggplot_build(plot_p_box))
-p_maxWidth <-  grid::unit.pmax(plot_p_point$widths, plot_p_box$widths)
-plot_p_point$widths <- as.list(p_maxWidth)
-plot_p_box$widths <- as.list(p_maxWidth)
-g2p_mut_plot <- cowplot::plot_grid(plot_p_box,
-                   plot_p_point,
-                   nrow = 2,
-                   rel_heights = c(1, 4))
-g2p_mut_plot
-
-# ggsave("./plots/manuscript/g2p_mut_plot.png", g2p_mut_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
-```
-
-```{r, eval=FALSE}
-plot_p_point <- ggplot(data = g2p_mut_all_summ) +
-  facet_wrap(~ Dataset, scales = "free_x") +
-  geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = p, y = n), alpha = 0.5) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
-  geom_text(data = g2p_mut_all_summ_text, mapping = aes(x = 0.5, y = 115, label = Test_Results_p)) +
-  labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations") +
-  theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
-
-plot_p_box <- ggplot(data = g2p_mut_all_summ) +
-  facet_wrap(~ Dataset, scales = "free_x") +
-  geom_violin(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.5) +
-  geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.75, width = 0.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  coord_flip() +
-  labs(x = "Level A G2P\nassociation") +
-  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
-plot <- subplot(plot_p_box, plot_p_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Gene-drug association p-value between mutation groups"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
-
-saveWidgetFix(widget = plot, file = "./plots/manuscript/g2p_mut_plot.html")
-```
-
-## GE
-
-### Pearson
-
-```{r fig.height=5, fig.width=12}
-plot_ge_pearson_point <- ggplot(data = g2p_cor, aes(x = Pearson_GE_Abs, y = n, label = Drug_Gene)) +
-  facet_wrap(~ Dataset) +
-  geom_point(mapping = aes(fill = InG2P, color = InG2P, shape = Pearson_GE_Sign), alpha = 0.5, size = 1.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
-  scale_x_continuous(breaks = seq(0, 0.65, by = 0.1), labels = seq(0, 0.65, by = 0.1)) +
-  coord_cartesian(xlim = c(0, 0.65)) +
-  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
-  geom_text_repel(data = subset(g2p_cor, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
-  geom_text(data = g2p_cor_text, mapping = aes(x = 0.325, y = 115, label = Pearson_Test_Results_GE)) +
-  labs(x = "Pearson correlation coefficient (r) between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +
-  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
-  guides(color = FALSE, fill = FALSE, shape = FALSE)
-
-plot_ge_pearson_box <- ggplot(data = g2p_cor) +
-  facet_wrap(~ Dataset) +
-  geom_violin(mapping = aes(color = InG2P, fill = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.35) +
-  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), width = 0.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_y_continuous(breaks = seq(0, 0.65, by = 0.1), labels = seq(0, 0.65, by = 0.1)) +
-  coord_flip(ylim = c(0, 0.65)) +
-  labs(x = "In G2P?") +
-  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
-plot_ge_pearson_point <- ggplot_gtable(ggplot_build(plot_ge_pearson_point))
-plot_ge_pearson_box <- ggplot_gtable(ggplot_build(plot_ge_pearson_box))
-p_maxWidth <-  grid::unit.pmax(plot_ge_pearson_point$widths[2:3], plot_ge_pearson_box$widths[2:3])
-plot_ge_pearson_point$widths[2:3] <- p_maxWidth
-plot_ge_pearson_box$widths[2:3] <- p_maxWidth
-
-g2p_ge_pearson_plot <- cowplot::plot_grid(plot_ge_pearson_box, plot_ge_pearson_point, nrow = 2, rel_heights = c(1, 4))
-g2p_ge_pearson_plot
-
-# ggsave("./plots/manuscript/g2p_ge_pearson_plot.png", g2p_ge_pearson_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
-```
-
-```{r, eval=FALSE}
-plot_ge_point <- ggplot(data = g2p_cor) +
-  facet_wrap(~ Dataset) +
-  geom_point(mapping = aes(label = Drug_Gene, fill = InG2P, color = InG2P, shape = Pearson_GE_Sign, x = Pearson_GE_Abs, y = n, size = Pearson_Pval_GE), alpha = 0.5, size = 1.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
-  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
-  scale_x_continuous(breaks = pretty_breaks()) +
-  geom_text(data = g2p_cor_text, mapping = aes(x = 0.3, y = 115, label = Pearson_Test_Results_GE)) +
-  labs(x = "Pearson correlation coefficient (r) between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +
-  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
-  guides(color = FALSE, fill = FALSE) +
-  labs(shape = NULL)
-
-plot_ge_box <- ggplot(data = g2p_cor) +
-  facet_wrap(~ Dataset) +
-  geom_violin(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.5) +
-  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  coord_flip() +
-  labs(x = "In G2P?") +
-  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
-ge_pearson_plot <- subplot(plot_ge_box, plot_ge_point, nrows = 2, heights = c(0.2, 0.8), titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and gene expression"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
-
-saveWidgetFix(widget = ge_pearson_plot, file = "./plots/manuscript/g2p_ge_pearson_plot.html")
-```
-
-### Spearman
-
-```{r fig.height=5, fig.width=12}
-plot_ge_spearman_point <- ggplot(data = g2p_cor, aes(x = Spearman_GE_Abs, y = n, label = Drug_Gene)) +
-  facet_wrap(~ Dataset) +
-  geom_point(mapping = aes(fill = InG2P, color = InG2P, shape = Spearman_GE_Sign), alpha = 0.5, size = 1.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
-  scale_x_continuous(breaks = seq(0, 0.65, by = 0.1), labels = seq(0, 0.65, by = 0.1)) +
-  coord_cartesian(xlim = c(0, 0.6)) +
-  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
-  geom_text_repel(data = subset(g2p_cor, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
-  geom_text(data = g2p_cor_text, mapping = aes(x = 0.3, y = 115, label = Spearman_Test_Results_GE)) +
-  labs(x = "Spearman correlation coefficient (r_s) between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +
-  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
-  guides(color = FALSE, fill = FALSE, shape = FALSE)
-
-plot_ge_spearman_box <- ggplot(data = g2p_cor) +
-  facet_wrap(~ Dataset) +
-  geom_violin(mapping = aes(color = InG2P, fill = InG2P, y = Spearman_GE_Abs, x = InG2P), alpha = 0.35) +
-  geom_boxplot(mapping = aes(color = InG2P, y = Spearman_GE_Abs, x = InG2P), width = 0.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_y_continuous(breaks = seq(0, 0.65, by = 0.1), labels = seq(0, 0.65, by = 0.1)) +
-  coord_flip(ylim = c(0, 0.6)) +
-  labs(x = "In G2P?") +
-  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
-plot_ge_spearman_point <- ggplot_gtable(ggplot_build(plot_ge_spearman_point))
-plot_ge_spearman_box <- ggplot_gtable(ggplot_build(plot_ge_spearman_box))
-p_maxWidth <-  grid::unit.pmax(plot_ge_spearman_point$widths[2:3], plot_ge_spearman_box$widths[2:3])
-plot_ge_spearman_point$widths[2:3] <- p_maxWidth
-plot_ge_spearman_box$widths[2:3] <- p_maxWidth
-
-g2p_ge_spearman_plot <- cowplot::plot_grid(plot_ge_spearman_box, plot_ge_spearman_point, nrow = 2, rel_heights = c(1, 4))
-g2p_ge_spearman_plot
-
-# ggsave("./plots/manuscript/g2p_ge_spearman_plot.png", g2p_ge_spearman_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
-```
-
-```{r, eval=FALSE}
-plot_ge_point <- ggplot(data = g2p_cor) +
-  facet_wrap(~ Dataset) +
-  geom_point(mapping = aes(label = Drug_Gene, fill = InG2P, color = InG2P, shape = Spearman_GE_Sign, x = Spearman_GE_Abs, y = n, size = Spearman_Pval_GE), alpha = 0.5, size = 1.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
-  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
-  scale_x_continuous(breaks = pretty_breaks()) +
-  geom_text(data = g2p_cor_text, mapping = aes(x = 0.3, y = 115, label = Spearman_Test_Results_GE)) +
-  labs(x = "Spearman correlation coefficient (r_s) between drug-gene AUC and gene expression", y = "Number of level A G2P associations") +
-  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
-  guides(color = FALSE, fill = FALSE) +
-  labs(shape = NULL)
-
-plot_ge_box <- ggplot(data = g2p_cor) +
-  facet_wrap(~ Dataset) +
-  geom_violin(mapping = aes(color = InG2P, y = Spearman_GE_Abs, x = InG2P), alpha = 0.5) +
-  geom_boxplot(mapping = aes(color = InG2P, y = Spearman_GE_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  coord_flip() +
-  labs(x = "In G2P?") +
-  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
-ge_spearman_plot <- subplot(plot_ge_box, plot_ge_point, nrows = 2, heights = c(0.2, 0.8), titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Spearman correlation coefficient between drug-gene AUC and gene expression"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
-
-saveWidgetFix(widget = ge_spearman_plot, file = "./plots/manuscript/g2p_ge_spearman_plot.html")
-```
-
-## CN
-
-### Pearson
-
-```{r fig.height=5, fig.width=12}
-plot_cn_pearson_point <- ggplot(data = g2p_cor, aes(x = Pearson_CN_Abs, y = n, label = Drug_Gene)) +
-  facet_wrap(~ Dataset) +
-  geom_point(mapping = aes(fill = InG2P, color = InG2P, shape = Pearson_CN_Sign), alpha = 0.5, size = 1.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
-  scale_x_continuous(breaks = seq(0, 0.65, by = 0.1), labels = seq(0, 0.65, by = 0.1)) +
-  coord_cartesian(xlim = c(0, 0.5)) +
-  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
-  geom_text_repel(data = subset(g2p_cor, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
-  geom_text(data = g2p_cor_text, mapping = aes(x = 0.25, y = 115, label = Pearson_Test_Results_CN)) +
-  labs(x = "Pearson correlation coefficient (r) between drug-gene AUC and copy number", y = "Number of level A G2P associations") +
-  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
-  guides(color = FALSE, fill = FALSE, shape = FALSE)
-
-plot_cn_pearson_box <- ggplot(data = g2p_cor) +
-  facet_wrap(~ Dataset) +
-  geom_violin(mapping = aes(color = InG2P, fill = InG2P, y = Pearson_CN_Abs, x = InG2P), alpha = 0.35) +
-  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_CN_Abs, x = InG2P), width = 0.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_y_continuous(breaks = seq(0, 0.65, by = 0.1), labels = seq(0, 0.65, by = 0.1)) +
-  coord_flip(ylim = c(0, 0.5)) +
-  labs(x = "In G2P?") +
-  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
-plot_cn_pearson_point <- ggplot_gtable(ggplot_build(plot_cn_pearson_point))
-plot_cn_pearson_box <- ggplot_gtable(ggplot_build(plot_cn_pearson_box))
-p_maxWidth <-  grid::unit.pmax(plot_cn_pearson_point$widths[2:3], plot_cn_pearson_box$widths[2:3])
-plot_cn_pearson_point$widths[2:3] <- p_maxWidth
-plot_cn_pearson_box$widths[2:3] <- p_maxWidth
-
-g2p_cn_pearson_plot <- cowplot::plot_grid(plot_cn_pearson_box, plot_cn_pearson_point, nrow = 2, rel_heights = c(1, 4))
-g2p_cn_pearson_plot
-
-# ggsave("./plots/manuscript/g2p_cn_pearson_plot.png", g2p_cn_pearson_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
-```
-
-```{r, eval=FALSE}
-plot_cn_point <- ggplot(data = g2p_cor) +
-  facet_wrap(~ Dataset) +
-  geom_point(mapping = aes(label = Drug_Gene, fill = InG2P, color = InG2P, shape = Pearson_CN_Sign, x = Pearson_CN_Abs, y = n, size = Pearson_Pval_CN), alpha = 0.5, size = 1.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
-  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
-  scale_x_continuous(breaks = pretty_breaks()) +
-  geom_text(data = g2p_cor_text, mapping = aes(x = 0.3, y = 115, label = Pearson_Test_Results_CN)) +
-  labs(x = "Pearson correlation coefficient (r) between drug-gene AUC and copy number", y = "Number of level A G2P associations") +
-  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
-  guides(color = FALSE, fill = FALSE) +
-  labs(shape = NULL)
-
-plot_cn_box <- ggplot(data = g2p_cor) +
-  facet_wrap(~ Dataset) +
-  geom_violin(mapping = aes(color = InG2P, y = Pearson_CN_Abs, x = InG2P), alpha = 0.5) +
-  geom_boxplot(mapping = aes(color = InG2P, y = Pearson_CN_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  coord_flip() +
-  labs(x = "In G2P?") +
-  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
-cn_pearson_plot <- subplot(plot_cn_box, plot_cn_point, nrows = 2, heights = c(0.2, 0.8), titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and copy number"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
-
-saveWidgetFix(widget = ge_pearson_plot, file = "./plots/manuscript/g2p_cn_pearson_plot.html")
-```
-
-### Spearman
-
-```{r fig.height=5, fig.width=12}
-plot_cn_spearman_point <- ggplot(data = g2p_cor, aes(x = Spearman_CN_Abs, y = n, label = Drug_Gene)) +
-  facet_wrap(~ Dataset) +
-  geom_point(mapping = aes(fill = InG2P, color = InG2P, shape = Spearman_CN_Sign), alpha = 0.5, size = 1.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
-  scale_x_continuous(breaks = seq(0, 0.4, by = 0.05), labels = seq(0, 0.4, by = 0.05)) +
-  coord_cartesian(xlim = c(0, 0.35)) +
-  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
-  geom_text_repel(data = subset(g2p_cor, InG2P == "Yes" & n > 10), size = 3, segment.size = 0.2, segment.color = "grey50") +
-  geom_text(data = g2p_cor_text, mapping = aes(x = 0.175, y = 115, label = Spearman_Test_Results_CN)) +
-  labs(x = "Spearman correlation coefficient (r_s) between drug-gene AUC and copy number", y = "Number of level A G2P associations") +
-  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
-  guides(color = FALSE, fill = FALSE, shape = FALSE)
-
-plot_cn_spearman_box <- ggplot(data = g2p_cor) +
-  facet_wrap(~ Dataset) +
-  geom_violin(mapping = aes(color = InG2P, fill = InG2P, y = Spearman_CN_Abs, x = InG2P), alpha = 0.35) +
-  geom_boxplot(mapping = aes(color = InG2P, y = Spearman_CN_Abs, x = InG2P), width = 0.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_y_continuous(breaks = seq(0, 0.4, by = 0.05), labels = seq(0, 0.4, by = 0.05)) +
-  coord_flip(ylim = c(0, 0.35)) +
-  labs(x = "In G2P?") +
-  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
-plot_cn_spearman_point <- ggplot_gtable(ggplot_build(plot_cn_spearman_point))
-plot_cn_spearman_box <- ggplot_gtable(ggplot_build(plot_cn_spearman_box))
-p_maxWidth <-  grid::unit.pmax(plot_cn_spearman_point$widths[2:3], plot_cn_spearman_box$widths[2:3])
-plot_cn_spearman_point$widths[2:3] <- p_maxWidth
-plot_cn_spearman_box$widths[2:3] <- p_maxWidth
-
-g2p_cn_spearman_plot <- cowplot::plot_grid(plot_cn_spearman_box, plot_cn_spearman_point, nrow = 2, rel_heights = c(1, 4))
-g2p_cn_spearman_plot
-
-# ggsave("./plots/manuscript/g2p_cn_spearman_plot.png", g2p_cn_spearman_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
-```
-
-```{r, eval=FALSE}
-plot_cn_point <- ggplot(data = g2p_cor) +
-  facet_wrap(~ Dataset) +
-  geom_point(mapping = aes(label = Drug_Gene, fill = InG2P, color = InG2P, shape = Spearman_CN_Sign, x = Spearman_CN_Abs, y = n, size = Spearman_Pval_CN), alpha = 0.5, size = 1.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
-  scale_y_continuous(breaks = seq(0, 120, by = 10), labels = seq(0, 120, by = 10)) +
-  scale_x_continuous(breaks = pretty_breaks()) +
-  geom_text(data = g2p_cor_text, mapping = aes(x = 0.175, y = 115, label = Spearman_Test_Results_CN)) +
-  labs(x = "Spearman correlation coefficient (r_s) between drug-gene AUC and copy number", y = "Number of level A G2P associations") +
-  theme(legend.position = "bottom", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank()) +
-  guides(color = FALSE, fill = FALSE) +
-  labs(shape = NULL)
-
-plot_cn_box <- ggplot(data = g2p_cor) +
-  facet_wrap(~ Dataset) +
-  geom_violin(mapping = aes(color = InG2P, y = Spearman_CN_Abs, x = InG2P), alpha = 0.5) +
-  geom_boxplot(mapping = aes(color = InG2P, y = Spearman_CN_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
-  scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
-  coord_flip() +
-  labs(x = "In G2P?") +
-  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
-
-cn_spearman_plot <- subplot(plot_cn_box, plot_cn_point, nrows = 2, heights = c(0.2, 0.8), titleX = TRUE, titleY = TRUE) %>% layout(margin = list(l = 75), xaxis5 = list(title = "Spearman correlation coefficient between drug-gene AUC and copy number"), yaxis = list(title = "In G2P?", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
-
-saveWidgetFix(widget = cn_spearman_plot, file = "./plots/manuscript/g2p_cn_spearman_plot.html")
-```
-
-## By lineage
-
-Make summary plots of mutation status tests by lineage and return a dataframe of all t-test results from comparing the p-value distributions of G2P and non-G2P drug-gene associaions:
-```{r, eval=FALSE, results = 'hide'}
-dgl_mut_g2p_grid_ttest_res <- lapply(as.character(unique(dgl_mut_grid_summ$group_general_lineage_name)), MutPlotsByLineage)
-dgl_mut_g2p_grid_ttest_res_list <- rbindlist(dgl_mut_g2p_grid_ttest_res, use.names = TRUE)
-dgl_mut_g2p_grid_ttest_res_list <- dgl_mut_g2p_grid_ttest_res_list[order(dgl_mut_g2p_grid_ttest_res_list$p_value),]
-saveRDS(dgl_mut_g2p_grid_ttest_res_list, "./data_munging/rds/dgl_mut_g2p_grid_ttest_res_list.rds")
-```
-
-```{r}
-dgl_mut_g2p_grid_ttest_res_list <- readRDS("./data_munging/rds/dgl_mut_g2p_grid_ttest_res_list.rds")
-dgl_mut_g2p_grid_ttest_res_list_kable <- knitr::kable(dgl_mut_g2p_grid_ttest_res_list, caption = "Mutation status: T-test results for level A G2P drug-gene associations across lineages") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-Make summary plots of gene expression and copy number tests by lineage and return a dataframe of all t-test results from comparing the p-value distributions of G2P and non-G2P drug-gene associaions:
-```{r, results='hide', eval=FALSE}
-dgl_pearson_g2p_grid_ttest_res <- lapply(as.character(unique(dgl_signif_pearson_g2p_grid$group_general_lineage_name)), PearsonPlotsByLineage)
-dgl_pearson_g2p_grid_ttest_res_list <- rbindlist(dgl_pearson_g2p_grid_ttest_res, use.names = TRUE)
-saveRDS(dgl_pearson_g2p_grid_ttest_res_list, "./data_munging/rds/dgl_pearson_g2p_grid_ttest_res_list.rds")
-```
-
-```{r}
-dgl_pearson_g2p_grid_ttest_res_list <- readRDS("./data_munging/rds/dgl_pearson_g2p_grid_ttest_res_list.rds")
-
-dgl_ge_g2p_grid_ttest_res_list_kable <- knitr::kable(dgl_pearson_g2p_grid_ttest_res_list[order(dgl_pearson_g2p_grid_ttest_res_list$p_value_GE), c("Dataset", "group_general_lineage_name", "t_statistic_GE", "df_GE", "p_value_GE")], caption = "Gene expression: T-test results for level A G2P drug-gene/gene expression associations across lineages") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-
-dgl_cn_g2p_grid_ttest_res_list_kable <- knitr::kable(dgl_pearson_g2p_grid_ttest_res_list[order(dgl_pearson_g2p_grid_ttest_res_list$p_value_CN), c("Dataset", "group_general_lineage_name", "t_statistic_CN", "df_CN", "p_value_CN")], caption = "Copy number: T-test results for level A G2P drug-gene/gene expression associations across lineages") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
-```
-
-### Grid t-test summaries
-
-Figure #.
-Histograms of p-values from t-tests comparing distributions of summary statistics for CCLE, CTRP, and GDSC drug screen results in the context of G2P level A evidence and lineage.
-Each p-value is derived from comparisons similar to those shown in Figure 2, but for these p-values, the data is grouped by lineage prior to conducting the t-test rather than the test being lineage-agnostic.
-To produce these p-values, AUC was correlated with each genomic feature for all possible pairwise combinations of G2P drugs and genes in all lineages represented in each dataset.
-For each lineage, t-tests were used to compare distributions of p-values (mutation status) or Pearson correlation coefficients (gene expression and copy number) that were grouped by whether or not the underlying drug-gene combination had level-A G2P evidence.
-For each dataset, if there were two or more correlation results in each G2P presence/absence group in a specific lineage, a t-test was conducted and the p-value appears in the appropriate histogram.
-Mutation status histograms are sparse due to limited mutation annotations for many of the G2P genes in all screened cell lines.
-```{r fig.height=4, fig.width=12}
-ttest_summ_res_mut <- dgl_mut_g2p_grid_ttest_res_list[, c("p_value", "Dataset", "group_general_lineage_name")]
-ttest_summ_res_mut$Metric <- "Mutation Status"
-
-ttest_summ_res_ge <- dgl_pearson_g2p_grid_ttest_res_list[, c("p_value_GE", "Dataset", "group_general_lineage_name")]
-colnames(ttest_summ_res_ge) <- c("p_value", "Dataset", "group_general_lineage_name")
-ttest_summ_res_ge$Metric <- "Gene Expression"
-
-ttest_summ_res_cn <- dgl_pearson_g2p_grid_ttest_res_list[, c("p_value_CN", "Dataset", "group_general_lineage_name")]
-colnames(ttest_summ_res_cn) <- c("p_value", "Dataset", "group_general_lineage_name")
-ttest_summ_res_cn$Metric <- "Copy Number"
-
-ttest_summ_res <- rbind(ttest_summ_res_mut, ttest_summ_res_ge, ttest_summ_res_cn)
-ttest_summ_res$Metric <- factor(ttest_summ_res$Metric, levels = c("Mutation Status", "Gene Expression", "Copy Number"))
-
-ttest_mut_summ_facet <- ggplot(data = ttest_summ_res, aes(x = p_value, fill = Dataset, color = Dataset)) +
-  facet_grid(Metric ~ Dataset) +
-  geom_histogram(bins = 40, binwidth = 0.025, boundary = 0, closed = "left") +
-  scale_y_continuous(breaks = c(0:6), labels = c(0:6)) +
-  scale_x_continuous(breaks = seq(0, 1, by = 0.1), expand = c(0.01, 0.01)) +
-  scale_fill_manual(values = c("CCLE" = "palegreen3", "CTRP" = "slategray3", "GDSC" = "paleturquoise3")) +
-  scale_color_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
-  theme(legend.position = c(0.5, 1.7), legend.direction = "horizontal", panel.grid.minor.y = element_blank()) +
-  labs(x = "P-value", y = "Frquency")
-ttest_mut_summ_facet
-
-# ggsave("./plots/manuscript/all_dgl_ttest_summ_facet_plot.png", ttest_mut_summ_facet, device = "png", dpi = 450, width = 12, height = 4, units = "in")
-```
-
-# OLD: Boxplots
-
---------------------------------------------------------------------------------
-
-Mutation status boxplots for genes identified in G2P.
-
-## G2P genes
-
-Boxplots ordered by gene based on frequency of G2P associations.
-
-### CRISPR
-
-```{r fig.height=5, fig.width=20}
-crispr_data_g2p$Hugo_Symbol <- factor(crispr_data_g2p$Hugo_Symbol, levels = g2p_genes)
-crispr_data_g2p_color <- as.character(crispr_data_g2p$Color_Nonsilent)
-names(crispr_data_g2p_color) <- crispr_data_g2p$Mutation_Status_Nonsilent
-crispr_label_text <- data.frame(p.signif.adj = crispr_signif_g2p_gene$p.signif.adj, p.signif = crispr_signif_g2p_gene$p.signif, Hugo_Symbol = crispr_signif_g2p_gene$Hugo_Symbol)
-crispr_label_text <- filter(crispr_label_text, Hugo_Symbol %in% g2p_genes)
-crispr_label_text$Hugo_Symbol <- factor(crispr_label_text$Hugo_Symbol, levels = g2p_genes)
-crispr_data_g2p_plot <- ggplot(data = crispr_data_g2p, aes(x = Mutation_Status_Nonsilent, y = Score)) +
-  facet_wrap(~ Hugo_Symbol, drop = FALSE, nrow = 1) +
-  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
-  geom_boxplot(mapping = aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85)) +
-  scale_fill_manual(values = crispr_data_g2p_color) +
-  guides(color = FALSE) +
-  geom_text(data = crispr_label_text, mapping = aes(x = 1.5, y = 2, label = p.signif), nudge_y = 0.1) +
-  theme(strip.text.x = element_text(size = 10, angle = 45), legend.position = "top", axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
-  labs(title = "CRISPR", fill = "Mutation Status", y = "CERES Score", x = "Mutation Status")
-crispr_data_g2p_plot
-
-# ggsave("./plots/manuscript/crispr_data_g2p_plot.png", crispr_data_g2p_plot, device = "png", dpi = 450, width = 20, height = 5, units = "in")
-```
-
-### CCLE
-
-Plot code:
-```{r, eval=FALSE}
-ccle_drugs <- as.character(unique(ccle_data_ptmuts$Drug))
-ccle_g2p_drugboxplots <- lapply(ccle_drugs, makeDrugBoxplots, dataset = "CCLE")
-ccle_g2p_drugboxplots_paths <- paste0(ccle_drugs, "_ccle_drugboxplots.png")
-pwalk(list(ccle_g2p_drugboxplots_paths, ccle_g2p_drugboxplots), ggsave, path = "./plots/manuscript/ccle_g2p_drugboxplots", dpi = 450, width = 20, height = 5, units = "in")
-```
-
-Data management:
-```{r, eval=FALSE}
-ccle_g2p_drugboxplots <- paste0(list.files("./plots/manuscript/ccle_g2p_drugboxplots", full.names = TRUE))
-names(ccle_g2p_drugboxplots) <- str_replace_all(ccle_g2p_drugboxplots, c("_ccle_drugboxplots.png" = "", "./plots/manuscript/ccle_g2p_drugboxplots/" = ""))
-bsselect(ccle_g2p_drugboxplots, type = "img", live_search = TRUE, show_tick = TRUE, height = 100)
-```
-
-### CTRP
-
-Plot code:
-```{r, eval=FALSE}
-ctrp_drugs <- as.character(unique(ctrp_data_ptmuts$Drug))
-ctrp_g2p_drugboxplots <- lapply(ctrp_drugs, makeDrugBoxplots, dataset = "ctrp")
-ctrp_g2p_drugboxplots_paths <- paste0(ctrp_drugs, "_ctrp_drugboxplots.png")
-pwalk(list(ctrp_g2p_drugboxplots_paths, ctrp_g2p_drugboxplots), ggsave, path = "./plots/manuscript/ctrp_g2p_drugboxplots", dpi = 450, width = 20, height = 5, units = "in")
-```
-
-Data management:
-```{r, eval=FALSE}
-ctrp_g2p_drugboxplots <- paste0(list.files("./plots/manuscript/ctrp_g2p_drugboxplots", full.names = TRUE))
-names(ctrp_g2p_drugboxplots) <- str_replace_all(ctrp_g2p_drugboxplots, c("_ctrp_drugboxplots.png" = "", "./plots/manuscript/ctrp_g2p_drugboxplots/" = ""))
-bsselect(ctrp_g2p_drugboxplots, type = "img", live_search = TRUE, show_tick = TRUE, height = 100)
-```
-
-### GDSC
-
-Plot code:
-```{r, eval=FALSE}
-gdsc_drugs <- as.character(unique(gdsc_data_ptmuts$Drug))
-gdsc_g2p_drugboxplots <- lapply(gdsc_drugs, makeDrugBoxplots, dataset = "gdsc")
-gdsc_g2p_drugboxplots_paths <- paste0(gdsc_drugs, "_gdsc_drugboxplots.png")
-pwalk(list(gdsc_g2p_drugboxplots_paths, gdsc_g2p_drugboxplots), ggsave, path = "./plots/manuscript/gdsc_g2p_drugboxplots", dpi = 450, width = 20, height = 5, units = "in")
-```
-
-Data management:
-```{r, eval=FALSE}
-gdsc_g2p_drugboxplots <- paste0(list.files("./plots/manuscript/gdsc_g2p_drugboxplots", full.names = TRUE))
-names(gdsc_g2p_drugboxplots) <- str_replace_all(gdsc_g2p_drugboxplots, c("_gdsc_drugboxplots.png" = "", "./plots/manuscript/gdsc_g2p_drugboxplots/" = ""))
-bsselect(gdsc_g2p_drugboxplots, type = "img", live_search = TRUE, show_tick = TRUE, height = 100)
-```
-
-## G2P level A drug-gene associations only
-
-### CCLE
-
-```{r fig.height=4, fig.width=12}
-ccle_g2p_order <- as.character(ccle_signif_g2p$Drug_Gene)
-ccle_data_g2p$Drug_Gene_Ordered <- factor(ccle_data_g2p$Drug_Gene, levels = ccle_g2p_order, labels = sapply(strsplit(x = ccle_g2p_order, split = "_"), function(x) paste0(x[1], "\n", x[2])))
-ccle_signif_g2p$Drug_Gene_Ordered <- factor(ccle_signif_g2p$Drug_Gene, levels = ccle_g2p_order, labels = sapply(strsplit(x = ccle_g2p_order, split = "_"), function(x) paste0(x[1], "\n", x[2])))
-ccle_data_g2p_color <- as.character(ccle_data_g2p$Color_Nonsilent)
-names(ccle_data_g2p_color) <- ccle_data_g2p$Mutation_Status_Nonsilent
-ccle_label_text <- data.frame(p.signif.adj = ccle_signif_g2p$p.signif.adj, p.signif = ccle_signif_g2p$p.signif, Drug_Gene_Ordered = ccle_signif_g2p$Drug_Gene_Ordered)
-ccle_data_g2p_plot <- ggplot(data = ccle_data_g2p, aes(x = Mutation_Status_Nonsilent, y = AUC)) +
-  facet_wrap(~ Drug_Gene_Ordered, drop = FALSE, nrow = 1) +
-  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
-  geom_boxplot(mapping = aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85), outlier.shape = 3, outlier.size = 0.5) +
-  scale_fill_manual(values = ccle_data_g2p_color) +
-  guides(color = FALSE) +
-  geom_text(data = ccle_label_text, mapping = aes(x = 1.5, y = 7, label = p.signif), nudge_y = 0.1) +
-  theme(legend.position = "top", axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
-  labs(title = "CCLE", fill = "Mutation Status", y = "AUC", x = "Mutation Status")
-ccle_data_g2p_plot
-
-# ggsave("./plots/manuscript/ccle_data_g2p_plot.png", ccle_data_g2p_plot, device = "png", dpi = 450, width = 12, height = 4, units = "in")
-```
-
-### CTRP
-
-```{r fig.height=7, fig.width=12}
-ctrp_g2p_order <- as.character(ctrp_signif_g2p$Drug_Gene)
-ctrp_data_g2p$Drug_Gene_Ordered <- factor(ctrp_data_g2p$Drug_Gene, levels = ctrp_g2p_order, labels = sapply(strsplit(x = ctrp_g2p_order, split = "_"), function(x) paste0(x[1], "\n", x[2])))
-ctrp_signif_g2p$Drug_Gene_Ordered <- factor(ctrp_signif_g2p$Drug_Gene, levels = ctrp_g2p_order, labels = sapply(strsplit(x = ctrp_g2p_order, split = "_"), function(x) paste0(x[1], "\n", x[2])))
-ctrp_data_g2p_color <- as.character(ctrp_data_g2p$Color_Nonsilent)
-names(ctrp_data_g2p_color) <- ctrp_data_g2p$Mutation_Status_Nonsilent
-ctrp_label_text <- data.frame(p.signif.adj = ctrp_signif_g2p$p.signif.adj, p.signif = ctrp_signif_g2p$p.signif, Drug_Gene_Ordered = ctrp_signif_g2p$Drug_Gene_Ordered)
-ctrp_data_g2p_plot <- ggplot(data = ctrp_data_g2p, aes(x = Mutation_Status_Nonsilent, y = AUC)) +
-  facet_wrap(~ Drug_Gene_Ordered, drop = FALSE, nrow = 3) +
-  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
-  geom_boxplot(mapping = aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85), outlier.shape = 3, outlier.size = 0.5) +
-  scale_fill_manual(values = ctrp_data_g2p_color) +
-  guides(color = FALSE) +
-  geom_text(data = ctrp_label_text, mapping = aes(x = 1.5, y = 22.5, label = p.signif), nudge_y = 0.1) +
-  theme(legend.position = "top", axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
-  labs(title = "CTRP", fill = "Mutation Status", y = "AUC", x = "Mutation Status")
-ctrp_data_g2p_plot
-
-# ggsave("./plots/manuscript/ctrp_data_g2p_plot.png", ctrp_data_g2p_plot, device = "png", dpi = 450, width = 12, height = 7, units = "in")
-```
-
-### GDSC
-
-```{r fig.height=7, fig.width=12}
-gdsc_g2p_order <- as.character(gdsc_signif_g2p$Drug_Gene)
-gdsc_data_g2p$Drug_Gene_Ordered <- factor(gdsc_data_g2p$Drug_Gene, levels = gdsc_g2p_order, labels = sapply(strsplit(x = gdsc_g2p_order, split = "_"), function(x) paste0(x[1], "\n", x[2])))
-gdsc_signif_g2p$Drug_Gene_Ordered <- factor(gdsc_signif_g2p$Drug_Gene, levels = gdsc_g2p_order, labels = sapply(strsplit(x = gdsc_g2p_order, split = "_"), function(x) paste0(x[1], "\n", x[2])))
-gdsc_data_g2p_color <- as.character(gdsc_data_g2p$Color_Nonsilent)
-names(gdsc_data_g2p_color) <- gdsc_data_g2p$Mutation_Status_Nonsilent
-gdsc_label_text <- data.frame(p.signif.adj = gdsc_signif_g2p$p.signif.adj, p.signif = gdsc_signif_g2p$p.signif, Drug_Gene_Ordered = gdsc_signif_g2p$Drug_Gene_Ordered)
-gdsc_data_g2p_plot <- ggplot(data = gdsc_data_g2p, aes(x = Mutation_Status_Nonsilent, y = AUC)) +
-  facet_wrap(~ Drug_Gene_Ordered, drop = FALSE, nrow = 3) +
-  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
-  geom_boxplot(mapping = aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85), outlier.shape = 3, outlier.size = 0.5) +
-  scale_fill_manual(values = gdsc_data_g2p_color) +
-  guides(color = FALSE) +
-  geom_text(data = gdsc_label_text, mapping = aes(x = 1.5, y = 1, label = p.signif), nudge_y = 0.1) +
-  theme(legend.position = "top", axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
-  labs(title = "GDSC", fill = "Mutation Status", y = "AUC", x = "Mutation Status")
-gdsc_data_g2p_plot
-
-# ggsave("./plots/manuscript/gdsc_data_g2p_plot.png", gdsc_data_g2p_plot, device = "png", dpi = 450, width = 12, height = 7, units = "in")
-```
-
-# OLD: CRISPR point mut mapping
-
---------------------------------------------------------------------------------
-
-Match specific point mutations.
-```{r fig.height=5, fig.width=20, eval=FALSE}
-g2p_indications <- filter(read.delim("./data_munging/data_mutation_associations_appended.csv", sep = "\t", header = TRUE), Evidence.Level == "A")
-maf_g2p_indications <- filter(maf_raw, Genome_Change %in% g2p_indications$MutationName)
-crispr_g2p_indications <- merge(crispr_data_ptmuts, maf_g2p_indications, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
-crispr_g2p_indications$Mutation_Status_Nonsilent <- ifelse(is.na(crispr_g2p_indications$Mutation_Status_Nonsilent), "Wildtype", crispr_g2p_indications$Mutation_Status_Nonsilent)
-dup_g2p_indications <- filter(crispr_g2p_indications[, c("Hugo_Symbol", "CCLE_Name", "DepMap_ID")] %>% group_by(Hugo_Symbol, CCLE_Name, DepMap_ID) %>% tally(), n > 1)
-crispr_g2p_indications <- merge(crispr_g2p_indications, dup_g2p_indications, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
-crispr_g2p_indications$Genome_Change <- factor(crispr_g2p_indications$Genome_Change, levels = unique(crispr_g2p_indications$Genome_Change))
-crispr_g2p_indications_nonNA <- filter(crispr_g2p_indications, is.na(n))
-crispr_g2p_indications_plot <- ggplot(crispr_g2p_indications, aes(x = Hugo_Symbol, y = Score)) +
-  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
-  geom_boxplot(alpha = 0.5, color = "lightgray", outlier.shape = NA) +
-  geom_jitter(width = 0.3, mapping = aes(color = Mutation_Status_Nonsilent), size = 1) +
-  theme_light() +
-  theme(legend.title = element_blank()) +
-  labs(x = "Gene", y = "CERES Score")
-crispr_g2p_indications_plot
-crispr_g2p_indications_muts_plot <- ggplot(crispr_g2p_indications, aes(x = Protein_Change, y = Score)) +
-  facet_grid(~ Hugo_Symbol, scales = "free_x", space = "free") +
-  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
-  geom_boxplot(alpha = 0.5, color = "lightgray", outlier.shape = NA) +
-  geom_jitter(width = 0.1, mapping = aes(color = Mutation_Status_Nonsilent), size = 1) +
-  theme_light() +
-  theme(legend.title = element_blank(), axis.text.x = element_text(angle = 90, hjust = 1)) +
-  labs(x = "Gene", y = "CERES Score")
-crispr_g2p_indications_muts_plot
-
-# ggsave("./plots/manuscript/crispr_g2p_indications_plot_test.png", crispr_g2p_indications_plot, width = 12, height = 5, units = "in")
-# ggsave("./plots/manuscript/crispr_g2p_indications_muts_plot_test.png", crispr_g2p_indications_muts_plot, width = 20, height = 5, units = "in")
-```
-
-# REFERENCES
-
---------------------------------------------------------------------------------
-
-Barretina, J., Caponigro, G., Stransky, N., Venkatesan, K., Margolin, A.
-A., Kim, S., … Garraway, L.
-A.
-(2012).
-The Cancer Cell Line Encyclopedia enables predictive modelling of anticancer drug sensitivity.
-Nature, 483(7391), 603–607.
-https://doi.org/10.1038/nature11003
-
-Broad Institute Cancer Dependency Map; Cancer Data Science (2018): Cancer Dependency Map, CRISPR Avana dataset 18Q3 (Avana_public_18Q3). figshare. Fileset. doi:10.6084/m9.figshare.6931364.v1
-
-Consortium, T. C. C. L. E., & Consortium, T. G. of D. S. in C. (2015). Pharmacogenomic agreement between two cancer cell line data sets. Nature, 528(7580), 84–87. https://doi.org/10.1038/nature15736
-
-Data Science, Cancer (2018): DEMETER2 data. figshare. Fileset. doi:10.6084/m9.figshare.6025238.v2
-
-Doench, J.
-G., Fusi, N., Sullender, M., Hegde, M., Vaimberg, E.
-W., Donovan, K.
-F., … Root, D.
-E.
-(2016).
-Optimized sgRNA design to maximize activity and minimize off-target effects of CRISPR-Cas9.
-Nature Biotechnology, 34(2), 184–191.
-https://doi.org/10.1038/nbt.3437
-
-Meyers, R.
-M., Bryan, J.
-G., McFarland, J.
-M., Weir, B.
-A., Sizemore, A.
-E., Xu, H., … Tsherniak, A.
-(2017).
-Computational correction of copy-number effect improves specificity of CRISPR-Cas9 essentiality screens in cancer cells.
-Nature Genetics, 49(12), 1779–1784.
-https://doi.org/10.1038/ng.3984
-
-McFarland, J.
-M., Ho, Z.
-V., Kugener, G., Dempster, J.
-M., Montgomery, P.
-G., Bryan, J.
-G., … Tsherniak, A.
-(2018).
-Improved estimation of cancer dependencies from large-scale RNAi screens using model-based normalization and data integration.
-https://doi.org/10.1101/305656
-
-# SESSION INFORMATION
-
---------------------------------------------------------------------------------
-
-```{r}
-print(sessionInfo())
-```

### 2019-03-05 19Q1.Rmd
update 18Q4 and 19Q1 Rmds

@@
 
-Analysis of the Broad's Avana CRISPR (Broad Institute Cancer Dependency Map 2018, Meyers et al.
-2017) and the Broad and Dana-Farber Cancer Institite's Achilles shRNA (MacFarland et al.
-2018, Data Science 2018).
+Analysis of the [Broad's Avana CRISPR](https://depmap.org/portal/download/) (Broad Institute Cancer Dependency Map 2018, Meyers et al.
+2017), the [Cancer Therapeutics Response Portal](https://ocg.cancer.gov/programs/ctd2/data-portal) (CTRP) drug screen dataset (v2) (Basu et al., 2013; M.
+G.
+Rees et al., 2016; B.
+Seashore-Ludlow et al., 2015), the [Genomics of Drug Sensitivity in Cancer](https://www.cancerrxgene.org/downloads) (GDSC) drug screen dataset (Garnett et al., 2012; Yang et al., 2012) , and the [Cancer Cell Line Encyclopedia](https://portals.broadinstitute.org/ccle) (CCLE) drug screen dataset (J.
+Barretina et al., 2012; T.
+C.
+C.
+L.
+E.
+Consortium & Consortium, 2015).
 
@@
 
-Edited `.Renviron` to avoid "Error: memory exhausted (limit reached?)" when melting the GE dataset, as per the suggestion from [StackOverflow](https://stackoverflow.com/questions/51295402/r-on-macos-error-vector-memory-exhausted-limit-reached)
+Edited `.Renviron` to avoid "Error: memory exhausted (limit reached?)" when melting the GE dataset, as per the suggestion from [StackOverflow](https://stackoverflow.com/questions/51295402/r-on-macos-error-vector-memory-exhausted-limit-reached):å
 ```
@@
 ```{r}
-library(bsselectR)
-library(cowplot)
-theme_set(theme_light())
-library(data.table)
 library(ggpubr)
@@
 library(ggsignif)
-library(gplots)
-library(gridExtra)
-library(htmlwidgets)
 library(kableExtra)
-library(papaja)
-library(plotly)
 library(reshape2)
-library(scales)
 library(tidyverse)
-library(VennDiagram)
-# devtools::install_github("crsh/papaja")
+theme_set(theme_light())
 ```
+
+# DATA MANAGEMENT {.tabset .tabset-fade .tabset-pills}
+
+--------------------------------------------------------------------------------
+
+## D. Charytonowicz cell line converter
+
+This comprehensive cancer cell line information was curated by both Daniel Charytonowicz and myself.
+```{r}
+ccl_converter <- read.delim("./data_munging/cell_line_database_v1_20180911.tsv", row.names = 1, sep = "\t", header = TRUE)
+lineage_converter <- unique(ccl_converter[, c("grouped_general_doid", "group_general_lineage_name")])
+colnames(ccl_converter)[colnames(ccl_converter) == "Broad_ID"] <- "DepMap_ID"
+```
+
+## DepMap cell line metadata
+
+```{r}
+ccl_info <- read.delim("./data_munging/19Q1/DepMap-2019Q1-celllines_20181115.csv", sep = ",", header = TRUE, na.strings = c("", NA))
+ccl_info$Primary.Disease <- gsub("\\\\", "", ccl_info$Primary.Disease)
+ccl_info$Primary.Disease <- gsub("Ewings", "Ewing's", ccl_info$Primary.Disease)
+# From figshare
+crispr_meta <- read.delim("./data_munging/19Q1/sample_info_19Q1_crispr_20181115.csv", sep = ",", header = TRUE, na.strings = c("", NA))
+colnames(crispr_meta)[7] <- "CCLE_Name"
+```
+
+## CCLE genomic annotations
+
+### Mutation status (Mut)
+
+For mutation calling, get paired gene name and cell line fields in a data frame.
+For this analysis, we don't care about how many mutations there are per gene or what type of mutations there are, so I didn't save more information.
+I took unique gene-cell line combinations since we only cared about mutation presence/absence.
+Add a `Mutation_Status` column denoting all entries in MAF files as mutations present in the associated cell lines.
+
+Mutation calls (coding region, germline filtered):
+```{r, eval=FALSE}
+maf_raw <- read.delim("./data_munging/19Q1/depmap_19Q1_mutation_calls_20181114.csv.gz", header = TRUE, sep = ",", row.names = 1)
+colnames(maf_raw)[colnames(maf_raw) == "Tumor_Sample_Barcode"] <- "CCLE_Name"
+# Select columns
+maf_df <- subset(maf_raw, select = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID", "Variant_Classification", "Reference_Allele", "Tumor_Seq_Allele1", "Genome_Change"))
+maf_df$Reference_Allele <- ifelse(maf_df$Reference_Allele == "-", 0, nchar(as.character(maf_df$Reference_Allele)))
+maf_df$Tumor_Seq_Allele1 <- nchar(as.character(maf_df$Tumor_Seq_Allele1))
+maf_df <- maf_df[maf_df$Variant_Classification != "Silent",]
+# Add Mutation_Status column
+maf_df$Mutation_Status_Nonsilent <- "Mutant"
+
+saveRDS(maf_df, "./data_munging/rds/maf_df_19Q1.rds", compress = "xz")
+```
+
+### Copy number (CN)
+
+DepMap WES CN Data:
+```{r, eval=FALSE}
+cn <- read.delim("./data_munging/19Q1/public_19Q1_gene_cn_20181115.csv.gz", sep = ",", check.names = FALSE, header = TRUE)
+# Remove Entrez gene IDs from colnames
+# Format: Hugo_Symbol (Entrez ID)
+colnames(cn) <- gsub(" .*", "", colnames(cn))
+# Melt
+cn_melt <- melt(data = cn, id.vars = "DepMap_ID", measure.vars = colnames(cn[2:ncol(cn)]), variable.name = "Hugo_Symbol", value.name = "CN")
+saveRDS(cn_melt, "./data_munging/rds/cn_melt_19Q1.rds", compress = "xz")
+```
+
+### Gene expression (GE)
+
+18Q3, Gene expression data (Reads Per Kilobase of transcript, per Million mapped reads, RPKM).
+```{r, eval=FALSE}
+ge_18Q3 <- read.delim("./../htscreens_giant_files/CCLE_DepMap_18q3_RNAseq_RPKM_20180718.gct.gz", skip = 2, header = TRUE, sep = "\t", check.names = FALSE)
+# Edit columns
+ge_18Q3$Name <- NULL
+colnames(ge_18Q3)[1] <- "Hugo_Symbol"
+# Melt
+ge_melt_18Q3 <- melt(data = ge_18Q3, id.vars = "Hugo_Symbol", measure.vars = colnames(ge_18Q3[2:ncol(ge_18Q3)]), value.name = "RPKM")
+## Split variable column
+ge_melt_18Q3 <- with(ge_melt_18Q3, cbind(Hugo_Symbol, colsplit(variable, pattern = " ", names = c("CCLE_Name", "DepMap_ID")), RPKM))
+## Remove parentheses around Broad IDs
+ge_melt_18Q3$DepMap_ID <- gsub("\\(|\\)", "", ge_melt_18Q3$DepMap_ID)
+saveRDS(ge_melt_18Q3, "./../htscreens_giant_files/ge_melt_18Q3.rds", compress = "xz")
+```
+
+19Q1, CCLE RNAseq gene expression data (log2(TPM+1)):
+```{r, eval=FALSE}
+ge_19Q1 <- read.delim("./../htscreens_giant_files/CCLE_depMap_19Q1_TPM_v2_20181115.csv.gz", header = TRUE, sep = ",", check.names = FALSE)
+# Remove Entrez gene IDs from colnames
+# Format: Hugo_Symbol (Entrez ID)
+colnames(ge_19Q1) <- gsub(" .*", "", colnames(ge_19Q1))
+colnames(ge_19Q1)[1] <- "DepMap_ID"
+# Melt
+ge_melt_19Q1_all <- melt(ge_19Q1, id.vars = "DepMap_ID", measure.vars = colnames(ge_19Q1)[2:ncol(ge_19Q1)], variable.name = "Hugo_Symbol", value.name = "TPM")
+ge_melt_19Q1 <- unique(ge_melt_19Q1)
+saveRDS(ge_melt_19Q1, "./data_munging/rds/ge_melt_19Q1.rds", compress = "xz")
+```
+
+## G2P
+
+```{r}
+g2p <- read.delim("./data_munging/g2p_full_level_A_dataset_NEW_DEC_2_2018_withGroupedLineages.csv", sep = "\t", header = TRUE)
+g2p[, 1:2] <- NULL
+g2p <- merge(g2p, lineage_converter, by = "grouped_general_doid", all.x = TRUE)
+
+g2p$Drug <- tolower(g2p$Drug)
+g2p[g2p == -1] <- NA
+g2p$Ref[g2p$Ref == "None"] <- NA
+g2p$Alt[g2p$Alt == "None"] <- NA
+g2p$Drug_Gene <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene), NA, paste0(g2p$Drug, "_", g2p$Gene))
+g2p$Drug_Gene_Lin <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene) | is.na(g2p$group_general_lineage_name), NA, paste0(g2p$Drug, "_", g2p$Gene, "_", g2p$group_general_lineage_name))
+g2p$position <- paste0("g.chr", g2p$Chromosome, ":", g2p$End, g2p$Ref, ">", g2p$Alt)
+g2p$position <- ifelse(grepl("NA", g2p$position), NA, g2p$position)
+g2p_filt <- subset(g2p, grepl("^CID", g2p$DrugID))
+
+g2p_dgls <-  unique(g2p_filt$Drug_Gene_Lin[!is.na(g2p_filt$Drug_Gene_Lin)])
+g2p_druggenes <- unique(g2p_filt$Drug_Gene[!is.na(g2p_filt$Drug_Gene)])
+g2p_drugs <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[1]))
+g2p_genes <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[2]))
+g2p_lins <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[3]))
+g2p_druggenes
+g2p_drugs
+g2p_genes
+g2p_lins
+
+# Order and genes taken from pink heatmapo from Daniel's analyses
+g2p_genes <- c("EGFR", "KRAS", "ERBB2", "ERBB3", "MET", "ALK", "ROS1", "PDGFRA", "ABL1", "KIT", "PDGFRB", "PDGFB", "BRAF", "G6PD", "RET", "BRCA1", "BRCA2", "UGT1A1", "TSC1", "TSC2", "AKT1", "IDH2", "DPYD", "ESR1", "CYP19A1", "TPMT", "FLT3", "NPM1", "DNMT3A", "PML", "PTCH1", "JAK2", "MYD88", "MGMT")
+```
+
+```{r}
+# levels(g2p_filt$Phenotype.Description)
+unique(g2p_filt$group_generals_lineage_name)
+levels(g2p_filt$group_general_lineage_name)
+
+g2p_nonCID <- subset(g2p, !grepl("^CID", g2p$DrugID))
+summ <- g2p_nonCID %>% group_by(Drug, DrugID) %>% tally() %>% summarize(DrugID = DrugID, n = n, percent = formatC(n / 402 * 100, digits = 6, format = "f"))
+summ
+```
+
+```{r, eval=FALSE}
+cn_melt <- readRDS("./data_munging/rds/cn_melt_19Q1.rds")
+ge_melt_18Q3 <- readRDS("./../htscreens_giant_files/ge_melt_18Q3.rds")
+# ge_melt_19Q1 <- readRDS("./data_munging/rds/ge_melt_19Q1.rds")
+
+# maf_filt_dan <- filter(maf_df, Hugo_Symbol %in% g2p_genes)
+# write.table(maf_filt_dan, file = "~/Desktop/maf_filt_dan_19Q1_2018112.csv", quote = FALSE, sep = ",", row.names = FALSE)
+```
+
+## Drug screens
+
+### Merge drug data and annotations
+
+```{r}
+maf_df <- readRDS("./data_munging/rds/maf_df_19Q1.rds")
+test <- filter(maf_df, Hugo_Symbol %in% g2p_genes) %>% count(Hugo_Symbol, CCLE_Name)
+test <- test[order(test$n, decreasing = TRUE),]
+```
+
+`r nrow(filter(test, n == 1))`/`r nrow(test)` gene-cell line combinations have more than one mutation in the MAF file. This is corrected in the point mutation filtering done below.
+
+```{r, eval=FALSE}
+# Drug metadata
+drug_meta <- read.delim("./data_munging/drug_id_drug_name_table_10_12_2018.tsv", sep = "\t", header = FALSE)
+colnames(drug_meta) <- c("CID", "Drug")
+drug_meta$Drug <- tolower(drug_meta$Drug)
+maf_df_g2p <- filter(maf_df, Hugo_Symbol %in% g2p_genes)
+ge_filt_18Q3 <- filter(ge_melt_18Q3, Hugo_Symbol %in% g2p_genes)
+# ge_filt_19Q1 <- filter(ge_melt_19Q1, Hugo_Symbol %in% g2p_genes)
+cn_filt <- filter(cn_melt, Hugo_Symbol %in% g2p_genes)
+
+# CCLE
+ccle <- read.delim("./data_munging/data_drug_auc_ccle_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
+ccle <- merge(drug_meta, ccle, by = "CID")
+ccle_melt <- melt(ccle, id.vars = c("CID", "Drug"), measure.vars = colnames(ccle)[3:ncol(ccle)], variable.name = "accession_id", value.name = "ActArea")
+ccle_grid <- expand.grid("accession_id" = unique(ccle_melt$accession_id), "Hugo_Symbol" = g2p_genes)
+ccle_data <- merge(ccle_grid, ccle_melt, by = "accession_id", all.x = TRUE)
+ccle_data <- merge(ccle_data, ccl_converter, by = "accession_id", all.x = TRUE)
+ccle_data <- merge(ccle_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
+ccle_data$Mutation_Status_Nonsilent <- ifelse(is.na(ccle_data$Mutation_Status_Nonsilent), "Wildtype", ccle_data$Mutation_Status_Nonsilent)
+ccle_data <- merge(ccle_data, ge_filt_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
+# ccle_data <- merge(ccle_data, ge_filt_19Q1, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
+ccle_data <- merge(ccle_data, cn_filt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
+ccle_data$Hugo_Symbol <- factor(ccle_data$Hugo_Symbol)
+ccle_data$ActArea <- as.numeric(ccle_data$ActArea)
+# CCLE AUC is actually AOC
+# assuming scale is 0-8, transform to range between 0 and 1
+# get AUC by 1 - AOC
+ccle_data$AUC <- 1 - (ccle_data$ActArea / 8)
+ccle_data <- filter(ccle_data, !is.na(ccle_data$AUC))
+ccle_data$AUC_zscore <- (ccle_data$AUC - mean(ccle_data$AUC)) / sd(ccle_data$AUC)
+ccle_data$Color_Nonsilent <- ifelse(ccle_data$Mutation_Status_Nonsilent == "Wildtype", "palegreen3", "springgreen4")
+ccle_data$Color_Nonsilent <- factor(ccle_data$Color_Nonsilent)
+ccle_data$Drug_Gene <- paste0(ccle_data$Drug, "_", ccle_data$Hugo_Symbol)
+ccle_data$Drug_Gene_Lin <- paste0(ccle_data$Drug, "_", ccle_data$Hugo_Symbol, "_", ccle_data$group_general_lineage_name)
+saveRDS(ccle_data, "./data_munging/rds/ccle_data_19Q1_g2pgenes.rds", compress = "xz")
+
+# CTRP
+ctrp <- read.delim("./data_munging/data_drug_auc_ctrp_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
+ctrp <- merge(drug_meta, ctrp, by = "CID")
+ctrp_melt <- melt(ctrp, id.vars = c("CID", "Drug"), measure.vars = colnames(ctrp)[3:ncol(ctrp)], variable.name = "accession_id", value.name = "AUC")
+ctrp_grid <- expand.grid("accession_id" = unique(ctrp_melt$accession_id), "Hugo_Symbol" = g2p_genes)
+ctrp_data <- merge(ctrp_grid, ctrp_melt, by = "accession_id", all.x = TRUE)
+ctrp_data <- merge(ctrp_data, ccl_converter, by = "accession_id", all.x = TRUE)
+ctrp_data <- merge(ctrp_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
+ctrp_data$Mutation_Status_Nonsilent <- ifelse(is.na(ctrp_data$Mutation_Status_Nonsilent), "Wildtype", ctrp_data$Mutation_Status_Nonsilent)
+ctrp_data <- merge(ctrp_data, ge_filt_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
+# ctrp_data <- merge(ctrp_data, ge_filt_19Q1, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
+ctrp_data <- merge(ctrp_data, cn_filt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
+ctrp_data$Hugo_Symbol <- factor(ctrp_data$Hugo_Symbol)
+ctrp_data$AUC <- as.numeric(ctrp_data$AUC)
+ctrp_data <- filter(ctrp_data, !is.na(ctrp_data$AUC))
+ctrp_data$AUC_zscore <- (ctrp_data$AUC - mean(ctrp_data$AUC)) / sd(ctrp_data$AUC)
+ctrp_data$Color_Nonsilent <- ifelse(ctrp_data$Mutation_Status_Nonsilent == "Wildtype", "slategray3", "steelblue4")
+ctrp_data$Color_Nonsilent <- factor(ctrp_data$Color_Nonsilent)
+ctrp_data$Drug_Gene <- paste0(ctrp_data$Drug, "_", ctrp_data$Hugo_Symbol)
+ctrp_data$Drug_Gene_Lin <- paste0(ctrp_data$Drug, "_", ctrp_data$Hugo_Symbol, "_", ctrp_data$group_general_lineage_name)
+saveRDS(ctrp_data, "./data_munging/rds/ctrp_data_19Q1_g2pgenes.rds", compress = "xz")
+
+# GDSC
+gdsc <- read.delim("./data_munging/data_drug_auc_gdsc_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
+gdsc <- merge(drug_meta, gdsc, by = "CID")
+gdsc_melt <- melt(gdsc, id.vars = c("CID", "Drug"), measure.vars = colnames(gdsc)[3:ncol(gdsc)], variable.name = "accession_id", value.name = "AUC")
+gdsc_grid <- expand.grid("accession_id" = unique(gdsc_melt$accession_id), "Hugo_Symbol" = g2p_genes)
+gdsc_data <- merge(gdsc_grid, gdsc_melt, by = "accession_id", all.x = TRUE)
+gdsc_data <- merge(gdsc_data, ccl_converter, by = "accession_id", all.x = TRUE)
+gdsc_data <- merge(gdsc_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
+gdsc_data$Mutation_Status_Nonsilent <- ifelse(is.na(gdsc_data$Mutation_Status_Nonsilent), "Wildtype", gdsc_data$Mutation_Status_Nonsilent)
+gdsc_data <- merge(gdsc_data, ge_filt_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
+# gdsc_data <- merge(gdsc_data, ge_filt_19Q1, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
+gdsc_data <- merge(gdsc_data, cn_filt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
+gdsc_data$Hugo_Symbol <- factor(gdsc_data$Hugo_Symbol)
+gdsc_data$AUC <- as.numeric(gdsc_data$AUC)
+gdsc_data <- filter(gdsc_data, !is.na(gdsc_data$AUC))
+gdsc_data$AUC_zscore <- (gdsc_data$AUC - mean(gdsc_data$AUC)) / sd(gdsc_data$AUC)
+gdsc_data$Color_Nonsilent <- ifelse(gdsc_data$Mutation_Status_Nonsilent == "Wildtype", "paleturquoise3", "turquoise4")
+gdsc_data$Color_Nonsilent <- factor(gdsc_data$Color_Nonsilent)
+gdsc_data$Drug_Gene <- paste0(gdsc_data$Drug, "_", gdsc_data$Hugo_Symbol)
+gdsc_data$Drug_Gene_Lin <- paste0(gdsc_data$Drug, "_", gdsc_data$Hugo_Symbol, "_", gdsc_data$group_general_lineage_name)
+saveRDS(gdsc_data, "./data_munging/rds/gdsc_data_19Q1_g2pgenes.rds", compress = "xz")
+```
+
+### Filter drug data
+
+```{r, eval=FALSE}
+ccle_data <- readRDS("./data_munging/rds/ccle_data_19Q1_g2pgenes.rds")
+ccle_data_ptmuts <- filter(ccle_data, Reference_Allele == 1 | Reference_Allele == 0 | is.na(Reference_Allele))
+ccle_data_ptmuts$Keep_PtMut_Tests <- ifelse(ccle_data_ptmuts$Reference_Allele == 1 | is.na(ccle_data_ptmuts$Reference_Allele), TRUE, ifelse(ccle_data_ptmuts$Tumor_Seq_Allele1 == 1, TRUE, FALSE))
+ccle_data_ptmuts <- filter(ccle_data_ptmuts, Keep_PtMut_Tests == TRUE)
+# Remove columns that lead to duplicate mutation entries
+ccle_data_ptmuts <- subset(ccle_data_ptmuts, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, Genome_Change, Keep_PtMut_Tests))
+ccle_data_ptmuts$Dataset <- "CCLE"
+ccle_data_ptmuts$Hugo_Symbol <- ordered(ccle_data_ptmuts$Hugo_Symbol, levels = g2p_genes)
+ccle_data_ptmuts <- unique(ccle_data_ptmuts)
+saveRDS(ccle_data_ptmuts, "./data_munging/rds/ccle_data_19Q1_g2pgenes_ptmuts.rds", compress = "xz")
+
+ctrp_data <- readRDS("./data_munging/rds/ctrp_data_19Q1_g2pgenes.rds")
+ctrp_data_ptmuts <- filter(ctrp_data, Reference_Allele == 1 | Reference_Allele == 0 | is.na(Reference_Allele))
+ctrp_data_ptmuts$Keep_PtMut_Tests <- ifelse(ctrp_data_ptmuts$Reference_Allele == 1 | is.na(ctrp_data_ptmuts$Reference_Allele), TRUE, ifelse(ctrp_data_ptmuts$Tumor_Seq_Allele1 == 1, TRUE, FALSE))
+ctrp_data_ptmuts <- filter(ctrp_data_ptmuts, Keep_PtMut_Tests == TRUE)
+# Remove columns that lead to duplicate mutation entries
+ctrp_data_ptmuts <- subset(ctrp_data_ptmuts, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, Genome_Change, Keep_PtMut_Tests))
+ctrp_data_ptmuts$Dataset <- "CTRP"
+ctrp_data_ptmuts$Hugo_Symbol <- ordered(ctrp_data_ptmuts$Hugo_Symbol, levels = g2p_genes)
+ctrp_data_ptmuts <- unique(ctrp_data_ptmuts)
+saveRDS(ctrp_data_ptmuts, "./data_munging/rds/ctrp_data_19Q1_g2pgenes_ptmuts.rds", compress = "xz")
+
+gdsc_data <- readRDS("./data_munging/rds/gdsc_data_19Q1_g2pgenes.rds")
+gdsc_data_ptmuts <- filter(gdsc_data, Reference_Allele == 1 | Reference_Allele == 0 | is.na(Reference_Allele))
+gdsc_data_ptmuts$Keep_PtMut_Tests <- ifelse(gdsc_data_ptmuts$Reference_Allele == 1 | is.na(gdsc_data_ptmuts$Reference_Allele), TRUE, ifelse(gdsc_data_ptmuts$Tumor_Seq_Allele1 == 1, TRUE, FALSE))
+gdsc_data_ptmuts <- filter(gdsc_data_ptmuts, Keep_PtMut_Tests == TRUE)
+# Remove columns that lead to duplicate mutation entries
+gdsc_data_ptmuts <- subset(gdsc_data_ptmuts, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, Genome_Change, Keep_PtMut_Tests))
+gdsc_data_ptmuts$Dataset <- "GDSC"
+gdsc_data_ptmuts$Hugo_Symbol <- ordered(gdsc_data_ptmuts$Hugo_Symbol, levels = g2p_genes)
+gdsc_data_ptmuts <- unique(gdsc_data_ptmuts)
+saveRDS(gdsc_data_ptmuts, "./data_munging/rds/gdsc_data_19Q1_g2pgenes_ptmuts.rds", compress = "xz")
+```
+
+```{r}
+ccle_data <- readRDS("./data_munging/rds/ccle_data_19Q1_g2pgenes.rds")
+ctrp_data <- readRDS("./data_munging/rds/ctrp_data_19Q1_g2pgenes.rds")
+gdsc_data <- readRDS("./data_munging/rds/gdsc_data_19Q1_g2pgenes.rds")
+ccle_data_ptmuts <- readRDS("./data_munging/rds/ccle_data_19Q1_g2pgenes_ptmuts.rds")
+ctrp_data_ptmuts <- readRDS("./data_munging/rds/ctrp_data_19Q1_g2pgenes_ptmuts.rds")
+gdsc_data_ptmuts <- readRDS("./data_munging/rds/gdsc_data_19Q1_g2pgenes_ptmuts.rds")
+
+# Filter drug screen datasets for G2P drug-gene associations
+ccle_data_g2p <- filter(ccle_data_ptmuts, Drug_Gene %in% g2p_druggenes)
+ccle_data_g2p$Mutation_Status_Nonsilent <- factor(ccle_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
+ctrp_data_g2p <- filter(ctrp_data_ptmuts, Drug_Gene %in% g2p_druggenes)
+ctrp_data_g2p$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
+gdsc_data_g2p <- filter(gdsc_data_ptmuts, Drug_Gene %in% g2p_druggenes)
+gdsc_data_g2p$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
+
+# Filter drug screen datasets for G2P drug-gene-lineage associations
+ccle_data_g2p_dgl <- filter(ccle_data_ptmuts, Drug_Gene_Lin %in% g2p_dgls)
+ccle_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(ccle_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
+ctrp_data_g2p_dgl <- filter(ctrp_data_ptmuts, Drug_Gene_Lin %in% g2p_dgls)
+ctrp_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
+gdsc_data_g2p_dgl <- filter(gdsc_data_ptmuts, Drug_Gene_Lin %in% g2p_dgls)
+gdsc_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
+
+# Filter drug screen datasets for G2P drugs and genes
+ccle_data_g2p_grid <- filter(ccle_data_ptmuts, Drug %in% g2p_drugs)
+ccle_data_g2p_grid$Mutation_Status_Nonsilent <- factor(ccle_data_g2p_grid$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
+ctrp_data_g2p_grid <- filter(ctrp_data_ptmuts, Drug %in% g2p_drugs)
+ctrp_data_g2p_grid$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p_grid$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
+gdsc_data_g2p_grid <- filter(gdsc_data_ptmuts, Drug %in% g2p_drugs)
+gdsc_data_g2p_grid$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p_grid$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
+
+# Testing
+test_ccle <- ccle_data_ptmuts %>% group_by(Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()
+test_ctrp <- ctrp_data_ptmuts %>% group_by(Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()
+test_gdsc <- gdsc_data_ptmuts %>% group_by(Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()
+
+# drug_summ <- data.frame(Drug = g2p_drugs, Dataset_Count = 0)
+```

### 2019-03-05 18Q4.Rmd
renamed Rmds to separate DepMap releases more clearly

--- 2019-02-28 manuscript_analysis.Rmd
@@
 ---
-title: "Manuscript"
+title: "18Q4"
 author: "Sally Claridge"
@@
 Analysis of the Broad's Avana CRISPR (Broad Institute Cancer Dependency Map 2018, Meyers et al.
-2017) and the Broad and Dana-Farber Cancer Institite's Achilles shRNA (MacFarland et al.
-2018, Data Science 2018).
+2017), the Cancer Therapeutics Response Portal (CTRP) drug screen dataset (v2) (Basu et al., 2013; M.
+G.
+Rees et al., 2016; B.
+Seashore-Ludlow et al., 2015), the Genomics of Drug Sensitivity in Cancer (GDSC) drug screen dataset (Garnett et al., 2012; Yang et al., 2012) , and the Cancer Cell Line Encyclopedia (CCLE) drug screen dataset (J.
+Barretina et al., 2012; T.
+C.
+C.
+L.
+E.
+Consortium & Consortium, 2015).
 
@@
 
-This comprehensive cancer cell line information curated by Daniel Charytonowicz.
+This comprehensive cancer cell line information was curated by both Daniel Charytonowicz and myself.
 ```{r}

### 2019-03-06 19Q1.Rmd
add 19Q1 cn and maf processed Rds

@@
 
+Note that the new 19Q1 release made multiple changes to variable names:
+
+- They reverted back to "Broad_ID" from 18Q3 rather than "DepMap_ID" that was used in 18Q4
+- Primary.Disease column of the cell line metadata file is more consistently named (Subtype.Disease now has the specific disease annotations), though there are a couple capitalization inconsistencies
+- MAF file no longer has "CCLE_Name" column and has a duplicate column of the Broad IDs (DepMap_ID and Tumor_Sample_Barcode)
+
+And data (the following is taken from the [data portal](https://depmap.org/portal/download/)):
+
+- **Expression**: We use the GTEx pipeline. Since last release, there have been some updates to the versions of different components of the pipeline and minor bug fixes on GTEx's end.
+- **Mutation**: In this release, we additionally process DepMap WES samples through the CGA mutation calling pipeline adapted for cell lines and available on FireCloud.
+We have added a column for the allele counts from this pipeline run (CGA_WES_AC).
+Previously, the WES_AC column was generated from running the Van Allen mutation calling pipeline for SNPs + Mutect2 for INDELs.
+This column is now named VA_WES_AC.
+- **Copy Number**: We have moved to using the newest version of the GATK pipeline.
+
 ## D. Charytonowicz cell line converter
@@
 lineage_converter <- unique(ccl_converter[, c("grouped_general_doid", "group_general_lineage_name")])
-colnames(ccl_converter)[colnames(ccl_converter) == "Broad_ID"] <- "DepMap_ID"
 ```
@@
 
+19Q1 update fixed almost all of the inconsistencies of the Primary.Disease column, though there were come capitalization inconsistencies.
 ```{r}
-ccl_info <- read.delim("./data_munging/19Q1/DepMap-2019Q1-celllines_20181115.csv", sep = ",", header = TRUE, na.strings = c("", NA))
-ccl_info$Primary.Disease <- gsub("\\\\", "", ccl_info$Primary.Disease)
-ccl_info$Primary.Disease <- gsub("Ewings", "Ewing's", ccl_info$Primary.Disease)
-# From figshare
-crispr_meta <- read.delim("./data_munging/19Q1/sample_info_19Q1_crispr_20181115.csv", sep = ",", header = TRUE, na.strings = c("", NA))
-colnames(crispr_meta)[7] <- "CCLE_Name"
+ccl_info <- read.delim("./data_munging/19Q1/DepMap-2019q1-celllines_v2_20190305.csv", sep = ",", header = TRUE, na.strings = c("", NA))
+# Convert Primary.Disease entries to all lower case to fix factorization
+ccl_info$Primary.Disease <- as.factor(tolower(ccl_info$Primary.Disease))
+# Harmonize ID column name
+colnames(ccl_info)[colnames(ccl_info) == "DepMap_ID"] <- "Broad_ID"
+
+# Sample info from figshare
+crispr_meta <- read.delim("./data_munging/19Q1/sample_info_20190306.csv", sep = ",", header = TRUE, na.strings = c("", NA))
+colnames(crispr_meta)[colnames(crispr_meta) == "CCLE_name"] <- "CCLE_Name"
 ```
@@
 ```{r, eval=FALSE}
-maf_raw <- read.delim("./data_munging/19Q1/depmap_19Q1_mutation_calls_20181114.csv.gz", header = TRUE, sep = ",", row.names = 1)
-colnames(maf_raw)[colnames(maf_raw) == "Tumor_Sample_Barcode"] <- "CCLE_Name"
+maf_raw <- read.delim("./data_munging/19Q1/depmap_19Q1_mutation_calls_20190305.csv.gz", header = TRUE, sep = ",", row.names = 1)
+# Harmonize ID column name
+colnames(maf_raw)[colnames(maf_raw) == "DepMap_ID"] <- "Broad_ID"
 # Select columns
-maf_df <- subset(maf_raw, select = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID", "Variant_Classification", "Reference_Allele", "Tumor_Seq_Allele1", "Genome_Change"))
+maf_df <- subset(maf_raw, select = c("Hugo_Symbol", "Broad_ID", "Variant_Classification", "Reference_Allele", "Tumor_Seq_Allele1", "Genome_Change"))
 maf_df$Reference_Allele <- ifelse(maf_df$Reference_Allele == "-", 0, nchar(as.character(maf_df$Reference_Allele)))
@@
 ```{r, eval=FALSE}
-cn <- read.delim("./data_munging/19Q1/public_19Q1_gene_cn_20181115.csv.gz", sep = ",", check.names = FALSE, header = TRUE)
-# Remove Entrez gene IDs from colnames
-# Format: Hugo_Symbol (Entrez ID)
+cn <- read.delim("./data_munging/19Q1/public_19Q1_gene_cn_20190305.csv.gz", sep = ",", check.names = FALSE, header = TRUE)
+# Remove Entrez gene IDs from colnames, format is "Hugo_Symbol (Entrez ID)"
 colnames(cn) <- gsub(" .*", "", colnames(cn))
+colnames(cn)[1] <- "Broad_ID"
 # Melt
-cn_melt <- melt(data = cn, id.vars = "DepMap_ID", measure.vars = colnames(cn[2:ncol(cn)]), variable.name = "Hugo_Symbol", value.name = "CN")
+cn_melt <- melt(data = cn, id.vars = "Broad_ID", measure.vars = colnames(cn[2:ncol(cn)]), variable.name = "Hugo_Symbol", value.name = "CN")
 saveRDS(cn_melt, "./data_munging/rds/cn_melt_19Q1.rds", compress = "xz")
@@
 ```{r, eval=FALSE}
-ge_18Q3 <- read.delim("./../htscreens_giant_files/CCLE_DepMap_18q3_RNAseq_RPKM_20180718.gct.gz", skip = 2, header = TRUE, sep = "\t", check.names = FALSE)
-# Edit columns
-ge_18Q3$Name <- NULL
-colnames(ge_18Q3)[1] <- "Hugo_Symbol"
-# Melt
-ge_melt_18Q3 <- melt(data = ge_18Q3, id.vars = "Hugo_Symbol", measure.vars = colnames(ge_18Q3[2:ncol(ge_18Q3)]), value.name = "RPKM")
-## Split variable column
-ge_melt_18Q3 <- with(ge_melt_18Q3, cbind(Hugo_Symbol, colsplit(variable, pattern = " ", names = c("CCLE_Name", "DepMap_ID")), RPKM))
-## Remove parentheses around Broad IDs
-ge_melt_18Q3$DepMap_ID <- gsub("\\(|\\)", "", ge_melt_18Q3$DepMap_ID)
-saveRDS(ge_melt_18Q3, "./../htscreens_giant_files/ge_melt_18Q3.rds", compress = "xz")
+# ge_18Q3 <- read.delim("./../htscreens_giant_files/CCLE_depMap_19Q1_TPM_20190305.csv.gz", skip = 2, header = TRUE, sep = "\t", check.names = FALSE)
+# # Edit columns
+# ge_18Q3$Name <- NULL
+# colnames(ge_18Q3)[1] <- "Hugo_Symbol"
+# # Melt
+# ge_melt_18Q3 <- melt(data = ge_18Q3, id.vars = "Hugo_Symbol", measure.vars = colnames(ge_18Q3[2:ncol(ge_18Q3)]), value.name = "RPKM")
+# ## Split variable column
+# ge_melt_18Q3 <- with(ge_melt_18Q3, cbind(Hugo_Symbol, colsplit(variable, pattern = " ", names = c("CCLE_Name", "DepMap_ID")), RPKM))
+# ## Remove parentheses around Broad IDs
+# ge_melt_18Q3$DepMap_ID <- gsub("\\(|\\)", "", ge_melt_18Q3$DepMap_ID)
+# saveRDS(ge_melt_18Q3, "./../htscreens_giant_files/ge_melt_18Q3.rds", compress = "xz")
 ```
@@
 ```{r, eval=FALSE}
-ge_19Q1 <- read.delim("./../htscreens_giant_files/CCLE_depMap_19Q1_TPM_v2_20181115.csv.gz", header = TRUE, sep = ",", check.names = FALSE)
-# Remove Entrez gene IDs from colnames
-# Format: Hugo_Symbol (Entrez ID)
+ge_19Q1 <- read.delim("./../htscreens_giant_files/CCLE_depMap_19Q1_TPM_20190305.csv.gz", header = TRUE, sep = ",", check.names = FALSE)
+# Remove Entrez gene IDs from colnames, format is "Hugo_Symbol (Entrez ID)"
 colnames(ge_19Q1) <- gsub(" .*", "", colnames(ge_19Q1))
-colnames(ge_19Q1)[1] <- "DepMap_ID"
+colnames(ge_19Q1)[1] <- "Broad_ID"
 # Melt
-ge_melt_19Q1_all <- melt(ge_19Q1, id.vars = "DepMap_ID", measure.vars = colnames(ge_19Q1)[2:ncol(ge_19Q1)], variable.name = "Hugo_Symbol", value.name = "TPM")
-ge_melt_19Q1 <- unique(ge_melt_19Q1)
+ge_melt_19Q1_all <- melt(ge_19Q1, id.vars = "Broad_ID", measure.vars = colnames(ge_19Q1)[2:ncol(ge_19Q1)], variable.name = "Hugo_Symbol", value.name = "TPM")
+# ge_melt_19Q1 <- unique(ge_melt_19Q1_all)
 saveRDS(ge_melt_19Q1, "./data_munging/rds/ge_melt_19Q1.rds", compress = "xz")

### 2019-03-06 19Q1.Rmd

@@
 
-saveRDS(maf_df, "./data_munging/rds/maf_df_19Q1.rds", compress = "xz")
+saveRDS(maf_df, "./data_munging/19Q1/maf_df_19Q1.rds", compress = "xz")
 ```
@@
 cn_melt <- melt(data = cn, id.vars = "Broad_ID", measure.vars = colnames(cn[2:ncol(cn)]), variable.name = "Hugo_Symbol", value.name = "CN")
-saveRDS(cn_melt, "./data_munging/rds/cn_melt_19Q1.rds", compress = "xz")
+saveRDS(cn_melt, "./data_munging/19Q1/cn_melt_19Q1.rds", compress = "xz")
 ```
@@
 # Melt
-ge_melt_19Q1_all <- melt(ge_19Q1, id.vars = "Broad_ID", measure.vars = colnames(ge_19Q1)[2:ncol(ge_19Q1)], variable.name = "Hugo_Symbol", value.name = "TPM")
+ge_melt_19Q1 <- melt(ge_19Q1, id.vars = "Broad_ID", measure.vars = colnames(ge_19Q1)[2:ncol(ge_19Q1)], variable.name = "Hugo_Symbol", value.name = "TPM")
 # ge_melt_19Q1 <- unique(ge_melt_19Q1_all)
-saveRDS(ge_melt_19Q1, "./data_munging/rds/ge_melt_19Q1.rds", compress = "xz")
+saveRDS(ge_melt_19Q1, "./data_munging/19Q1/ge_melt_19Q1.rds", compress = "xz")
 ```
@@
 ```{r, eval=FALSE}
-cn_melt <- readRDS("./data_munging/rds/cn_melt_19Q1.rds")
+cn_melt <- readRDS("./data_munging/19Q1/cn_melt_19Q1.rds")
 ge_melt_18Q3 <- readRDS("./../htscreens_giant_files/ge_melt_18Q3.rds")
-# ge_melt_19Q1 <- readRDS("./data_munging/rds/ge_melt_19Q1.rds")
+# ge_melt_19Q1 <- readRDS("./data_munging/19Q1/ge_melt_19Q1.rds")
 
@@
 ```{r}
-maf_df <- readRDS("./data_munging/rds/maf_df_19Q1.rds")
+maf_df <- readRDS("./data_munging/19Q1/maf_df_19Q1.rds")
 test <- filter(maf_df, Hugo_Symbol %in% g2p_genes) %>% count(Hugo_Symbol, CCLE_Name)
@@
 ccle_data$Drug_Gene_Lin <- paste0(ccle_data$Drug, "_", ccle_data$Hugo_Symbol, "_", ccle_data$group_general_lineage_name)
-saveRDS(ccle_data, "./data_munging/rds/ccle_data_19Q1_g2pgenes.rds", compress = "xz")
+saveRDS(ccle_data, "./data_munging/19Q1/ccle_data_19Q1_g2pgenes.rds", compress = "xz")
 
@@
 ctrp_data$Drug_Gene_Lin <- paste0(ctrp_data$Drug, "_", ctrp_data$Hugo_Symbol, "_", ctrp_data$group_general_lineage_name)
-saveRDS(ctrp_data, "./data_munging/rds/ctrp_data_19Q1_g2pgenes.rds", compress = "xz")
+saveRDS(ctrp_data, "./data_munging/19Q1/ctrp_data_19Q1_g2pgenes.rds", compress = "xz")
 
@@
 gdsc_data$Drug_Gene_Lin <- paste0(gdsc_data$Drug, "_", gdsc_data$Hugo_Symbol, "_", gdsc_data$group_general_lineage_name)
-saveRDS(gdsc_data, "./data_munging/rds/gdsc_data_19Q1_g2pgenes.rds", compress = "xz")
+saveRDS(gdsc_data, "./data_munging/19Q1/gdsc_data_19Q1_g2pgenes.rds", compress = "xz")
 ```
@@
 ```{r, eval=FALSE}
-ccle_data <- readRDS("./data_munging/rds/ccle_data_19Q1_g2pgenes.rds")
+ccle_data <- readRDS("./data_munging/19Q1/ccle_data_19Q1_g2pgenes.rds")
 ccle_data_ptmuts <- filter(ccle_data, Reference_Allele == 1 | Reference_Allele == 0 | is.na(Reference_Allele))
@@
 ccle_data_ptmuts <- unique(ccle_data_ptmuts)
-saveRDS(ccle_data_ptmuts, "./data_munging/rds/ccle_data_19Q1_g2pgenes_ptmuts.rds", compress = "xz")
+saveRDS(ccle_data_ptmuts, "./data_munging/19Q1/ccle_data_19Q1_g2pgenes_ptmuts.rds", compress = "xz")
 
-ctrp_data <- readRDS("./data_munging/rds/ctrp_data_19Q1_g2pgenes.rds")
+ctrp_data <- readRDS("./data_munging/19Q1/ctrp_data_19Q1_g2pgenes.rds")
 ctrp_data_ptmuts <- filter(ctrp_data, Reference_Allele == 1 | Reference_Allele == 0 | is.na(Reference_Allele))
@@
 ctrp_data_ptmuts <- unique(ctrp_data_ptmuts)
-saveRDS(ctrp_data_ptmuts, "./data_munging/rds/ctrp_data_19Q1_g2pgenes_ptmuts.rds", compress = "xz")
+saveRDS(ctrp_data_ptmuts, "./data_munging/19Q1/ctrp_data_19Q1_g2pgenes_ptmuts.rds", compress = "xz")
 
-gdsc_data <- readRDS("./data_munging/rds/gdsc_data_19Q1_g2pgenes.rds")
+gdsc_data <- readRDS("./data_munging/19Q1/gdsc_data_19Q1_g2pgenes.rds")
 gdsc_data_ptmuts <- filter(gdsc_data, Reference_Allele == 1 | Reference_Allele == 0 | is.na(Reference_Allele))
@@
 gdsc_data_ptmuts <- unique(gdsc_data_ptmuts)
-saveRDS(gdsc_data_ptmuts, "./data_munging/rds/gdsc_data_19Q1_g2pgenes_ptmuts.rds", compress = "xz")
+saveRDS(gdsc_data_ptmuts, "./data_munging/19Q1/gdsc_data_19Q1_g2pgenes_ptmuts.rds", compress = "xz")
 ```
@@
 ```{r}
-ccle_data <- readRDS("./data_munging/rds/ccle_data_19Q1_g2pgenes.rds")
-ctrp_data <- readRDS("./data_munging/rds/ctrp_data_19Q1_g2pgenes.rds")
-gdsc_data <- readRDS("./data_munging/rds/gdsc_data_19Q1_g2pgenes.rds")
-ccle_data_ptmuts <- readRDS("./data_munging/rds/ccle_data_19Q1_g2pgenes_ptmuts.rds")
-ctrp_data_ptmuts <- readRDS("./data_munging/rds/ctrp_data_19Q1_g2pgenes_ptmuts.rds")
-gdsc_data_ptmuts <- readRDS("./data_munging/rds/gdsc_data_19Q1_g2pgenes_ptmuts.rds")
+ccle_data <- readRDS("./data_munging/19Q1/ccle_data_19Q1_g2pgenes.rds")
+ctrp_data <- readRDS("./data_munging/19Q1/ctrp_data_19Q1_g2pgenes.rds")
+gdsc_data <- readRDS("./data_munging/19Q1/gdsc_data_19Q1_g2pgenes.rds")
+ccle_data_ptmuts <- readRDS("./data_munging/19Q1/ccle_data_19Q1_g2pgenes_ptmuts.rds")
+ctrp_data_ptmuts <- readRDS("./data_munging/19Q1/ctrp_data_19Q1_g2pgenes_ptmuts.rds")
+gdsc_data_ptmuts <- readRDS("./data_munging/19Q1/gdsc_data_19Q1_g2pgenes_ptmuts.rds")
 

### 2019-03-07 19Q1.Rmd
work on GCN dataframe

@@
 ```
+
+## Denise's GCN dataframes
+
+Code for Denise's graph convolutional networks analyses (see meeting notes from 6 March 2019).
+- Convert drug/compound names to all capitalized for harmonization.
+
+```{r, eval=FALSE}
+maf_df <- readRDS("./data_munging/19Q1/maf_df_19Q1.rds")
+cn_melt <- readRDS("./data_munging/19Q1/cn_melt_19Q1.rds")
+ge_melt <- readRDS("./data_munging/19Q1/ge_melt_19Q1.rds")
+
+ctrp <- read.delim("./data_munging/pharmacogenomics_raw_files/CTRP_v20.data.curves_post_qc.txt.gz", sep = "\t", header  = TRUE, check.names = FALSE) 
+# area_under_curve: integrated area under the sigmoid-fit concentration-response curve
+ctrp_filt <- ctrp[, c("experiment_id", "area_under_curve", "master_cpd_id")]
+ctrp_meta_ccl <- select(read.delim("./data_munging/pharmacogenomics_raw_files/CTRP_v20.meta.per_cell_line_20190306.txt"), master_ccl_id, ccl_name, ccle_primary_site)
+ctrp_meta_exp <- select(read.delim("./data_munging/pharmacogenomics_raw_files/CTRP_v20.meta.per_experiment_20190306.txt"), experiment_id, master_ccl_id)
+ctrp_meta_cpd <- select(read.delim("./data_munging/pharmacogenomics_raw_files/CTRP_v20.meta.per_compound_20190306.txt"), master_cpd_id, cpd_name)
+ctrp_keep <- merge(merge(ctrp_meta_ccl, ctrp_meta_exp, by = "master_ccl_id", all = TRUE), merge(ctrp_meta_cpd, ctrp_filt, by = "master_cpd_id", all = TRUE), by = "experiment_id", all = TRUE)
+ctrp_keep$cpd_name <- toupper(ctrp_keep$cpd_name)
+ctrp_keep$ccle_primary_site <- ifelse(as.character(ctrp_keep$ccle_primary_site) == "", NA, as.character(ctrp_keep$ccle_primary_site))
+ctrp4harm_long <- select(ctrp_keep, ccl_name, ccle_primary_site, cpd_name, area_under_curve)
+colnames(ctrp4harm_long) <- c("source_ccl_name", "source_histology", "compound_name", "AUC")
+ctrp4harm_long$source <- "CTRP"
+ctrp4harm_long$sample_id <- with(ctrp4harm_long, paste(source, source_ccl_name, source_histology, sep = "_"))
+ctrp4harm <- dcast(ctrp4harm_long, source + source_ccl_name + source_histology + sample_id ~ compound_name, value.var = "AUC", fill = 0)
+```

### 2019-03-08 19Q1.Rmd
concat CCLE, CTRP, and GDSC AUC data--Needs editing

--- 2019-03-06 19Q1.Rmd
@@
 library(tidyverse)
+library(naniar)
 theme_set(theme_light())
@@
 
-18Q3, Gene expression data (Reads Per Kilobase of transcript, per Million mapped reads, RPKM).
-```{r, eval=FALSE}
-# ge_18Q3 <- read.delim("./../htscreens_giant_files/CCLE_depMap_19Q1_TPM_20190305.csv.gz", skip = 2, header = TRUE, sep = "\t", check.names = FALSE)
-# # Edit columns
-# ge_18Q3$Name <- NULL
-# colnames(ge_18Q3)[1] <- "Hugo_Symbol"
-# # Melt
-# ge_melt_18Q3 <- melt(data = ge_18Q3, id.vars = "Hugo_Symbol", measure.vars = colnames(ge_18Q3[2:ncol(ge_18Q3)]), value.name = "RPKM")
-# ## Split variable column
-# ge_melt_18Q3 <- with(ge_melt_18Q3, cbind(Hugo_Symbol, colsplit(variable, pattern = " ", names = c("CCLE_Name", "DepMap_ID")), RPKM))
-# ## Remove parentheses around Broad IDs
-# ge_melt_18Q3$DepMap_ID <- gsub("\\(|\\)", "", ge_melt_18Q3$DepMap_ID)
-# saveRDS(ge_melt_18Q3, "./../htscreens_giant_files/ge_melt_18Q3.rds", compress = "xz")
-```
-
 19Q1, CCLE RNAseq gene expression data (log2(TPM+1)):
@@
 
-## G2P
+## Denise's GCN dataframes
 
-```{r}
-g2p <- read.delim("./data_munging/g2p_full_level_A_dataset_NEW_DEC_2_2018_withGroupedLineages.csv", sep = "\t", header = TRUE)
-g2p[, 1:2] <- NULL
-g2p <- merge(g2p, lineage_converter, by = "grouped_general_doid", all.x = TRUE)
+Code for Denise's graph convolutional networks analyses (see meeting notes from 6 March 2019).
+- Convert drug/compound names to all capitalized for harmonization.
 
-g2p$Drug <- tolower(g2p$Drug)
-g2p[g2p == -1] <- NA
-g2p$Ref[g2p$Ref == "None"] <- NA
-g2p$Alt[g2p$Alt == "None"] <- NA
-g2p$Drug_Gene <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene), NA, paste0(g2p$Drug, "_", g2p$Gene))
-g2p$Drug_Gene_Lin <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene) | is.na(g2p$group_general_lineage_name), NA, paste0(g2p$Drug, "_", g2p$Gene, "_", g2p$group_general_lineage_name))
-g2p$position <- paste0("g.chr", g2p$Chromosome, ":", g2p$End, g2p$Ref, ">", g2p$Alt)
-g2p$position <- ifelse(grepl("NA", g2p$position), NA, g2p$position)
-g2p_filt <- subset(g2p, grepl("^CID", g2p$DrugID))
+```{r, eval=TRUE}
+maf_df <- readRDS("./data_munging/19Q1/maf_df_19Q1.rds")
+cn_melt <- readRDS("./data_munging/19Q1/cn_melt_19Q1.rds")
+ge_melt <- readRDS("./data_munging/19Q1/ge_melt_19Q1.rds")
 
-g2p_dgls <-  unique(g2p_filt$Drug_Gene_Lin[!is.na(g2p_filt$Drug_Gene_Lin)])
-g2p_druggenes <- unique(g2p_filt$Drug_Gene[!is.na(g2p_filt$Drug_Gene)])
-g2p_drugs <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[1]))
-g2p_genes <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[2]))
-g2p_lins <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[3]))
-g2p_druggenes
-g2p_drugs
-g2p_genes
-g2p_lins
+ccle <- read.delim("./data_munging/pharmacogenomics_raw_files/CCLE_NP24.2009_Drug_data_2015.02.24_20190307.csv", sep = ",", header  = TRUE, check.names = FALSE)
+ctrp <- read.delim("./data_munging/pharmacogenomics_raw_files/CTRP_v20.data.curves_post_qc.txt.gz", sep = "\t", header  = TRUE, check.names = FALSE)
+gdsc <- read.delim("./data_munging/pharmacogenomics_raw_files/GDSC_v17.3_fitted_dose_response_20190306.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
 
-# Order and genes taken from pink heatmapo from Daniel's analyses
-g2p_genes <- c("EGFR", "KRAS", "ERBB2", "ERBB3", "MET", "ALK", "ROS1", "PDGFRA", "ABL1", "KIT", "PDGFRB", "PDGFB", "BRAF", "G6PD", "RET", "BRCA1", "BRCA2", "UGT1A1", "TSC1", "TSC2", "AKT1", "IDH2", "DPYD", "ESR1", "CYP19A1", "TPMT", "FLT3", "NPM1", "DNMT3A", "PML", "PTCH1", "JAK2", "MYD88", "MGMT")
+## CCLE
+# Note that ActArea is NOT an AUC value
+ccle_filt <- ccle[, c("CCLE Cell Line Name", "ActArea", "Compound")]
+ccle_filt$source_ccl_name <- sapply(strsplit(as.character(ccle_filt$`CCLE Cell Line Name`), split = "_"), function(x) x[1])
+ccle_filt$source_histology <- tolower(gsub("^[a-z0-9]*_", "", ccle_filt$`CCLE Cell Line Name`, ignore.case = TRUE))
+ccle_filt$source_histology <- ifelse(as.character(ccle_filt$source_histology) == "", NA, as.character(ccle_filt$source_histology))
+ccle_filt$compound_name <- toupper(ccle_filt$Compound)
+colnames(ccle_filt)[colnames(ccle_filt) == "ActArea"] <- "AUC"
+ccle4harm_long <- select(ccle_filt, source_ccl_name, source_histology, compound_name, AUC)
+ccle4harm_long$source <- "CCLE"
+ccle4harm_long$sample_id <- with(ccle4harm_long, paste(source, source_ccl_name, source_histology, sep = "_"))
+ccle4harm <- dcast(ccle4harm_long, source + source_ccl_name + source_histology + sample_id ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
+ccle4harm[, 5:ncol(ccle4harm)] <- ccle4harm[, 5:ncol(ccle4harm)] %>% replace_with_na_all(condition = ~.x == 10000)
+
+## CTRP
+# area_under_curve: integrated area under the sigmoid-fit concentration-response curve
+ctrp_filt <- ctrp[, c("experiment_id", "area_under_curve", "master_cpd_id")]
+ctrp_meta_ccl <- select(read.delim("./data_munging/pharmacogenomics_raw_files/CTRP_v20.meta.per_cell_line_20190306.txt"), master_ccl_id, ccl_name, ccle_primary_site)
+ctrp_meta_exp <- select(read.delim("./data_munging/pharmacogenomics_raw_files/CTRP_v20.meta.per_experiment_20190306.txt"), experiment_id, master_ccl_id)
+ctrp_meta_cpd <- select(read.delim("./data_munging/pharmacogenomics_raw_files/CTRP_v20.meta.per_compound_20190306.txt"), master_cpd_id, cpd_name)
+ctrp_keep <- merge(merge(ctrp_meta_ccl, ctrp_meta_exp, by = "master_ccl_id", all = TRUE), merge(ctrp_meta_cpd, ctrp_filt, by = "master_cpd_id", all = TRUE), by = "experiment_id", all = TRUE)
+ctrp_keep$cpd_name <- toupper(ctrp_keep$cpd_name)
+ctrp_keep$ccle_primary_site <- ifelse(as.character(ctrp_keep$ccle_primary_site) == "", NA, as.character(ctrp_keep$ccle_primary_site))
+ctrp4harm_long <- select(ctrp_keep, ccl_name, ccle_primary_site, cpd_name, area_under_curve)
+colnames(ctrp4harm_long) <- c("source_ccl_name", "source_histology", "compound_name", "AUC")
+ctrp4harm_long$source <- "CTRP"
+ctrp4harm_long$sample_id <- with(ctrp4harm_long, paste(source, source_ccl_name, source_histology, sep = "_"))
+ctrp4harm <- dcast(ctrp4harm_long, source + source_ccl_name + source_histology + sample_id ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
+ctrp4harm[, 5:ncol(ctrp4harm)] <- ctrp4harm[, 5:ncol(ctrp4harm)] %>% replace_with_na_all(condition = ~.x == 10000)
+
+## GDSC
+gdsc_meta_ccl <- select(read.delim("./data_munging/pharmacogenomics_raw_files/GDSC_Cell_Lines_Details.csv", sep = ","), Line, Site)
+gdsc_filt <- gdsc[, c("CELL_LINE_NAME", "DRUG_NAME", "AUC")]
+gdsc_filt$DRUG_NAME <- toupper(gdsc_filt$DRUG_NAME)
+colnames(gdsc_filt)[colnames(gdsc_filt) ==  "CELL_LINE_NAME"] <- "Line"
+gdsc_filt <- merge(gdsc_filt, gdsc_meta_ccl, by = "Line", all = TRUE)
+gdsc4harm_long <- select(gdsc_filt, Line, Site, DRUG_NAME, AUC)
+colnames(gdsc4harm_long) <- c("source_ccl_name", "source_histology", "compound_name", "AUC")
+gdsc4harm_long$source <- "GDSC"
+gdsc4harm_long$sample_id <- with(gdsc4harm_long, paste(source, source_ccl_name, source_histology, sep = "_"))
+gdsc4harm <- dcast(gdsc4harm_long, source + source_ccl_name + source_histology + sample_id ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
+gdsc4harm[, 5:ncol(gdsc4harm)] <- gdsc4harm[, 5:ncol(gdsc4harm)] %>% replace_with_na_all(condition = ~.x == 10000)
+
+## BIND ALL
+pgx_harm_list <- list(ccle4harm, ctrp4harm, gdsc4harm)
+pgx_harm_names <- unique(unlist(lapply(pgx_harm_list, names)))
+pgx_harm <- do.call(rbind,
+                    c(lapply(pgx_harm_list,
+                             function(x) data.frame(c(x,
+                                                      sapply(setdiff(pgx_harm_names, names(x)),
+                                                             function(y) NA)
+                                                      )
+                                                    )
+                             )
+                      )
+                    )
 ```
-
-```{r}
-# levels(g2p_filt$Phenotype.Description)
-unique(g2p_filt$group_generals_lineage_name)
-levels(g2p_filt$group_general_lineage_name)
-
-g2p_nonCID <- subset(g2p, !grepl("^CID", g2p$DrugID))
-summ <- g2p_nonCID %>% group_by(Drug, DrugID) %>% tally() %>% summarize(DrugID = DrugID, n = n, percent = formatC(n / 402 * 100, digits = 6, format = "f"))
-summ
-```
-
-```{r, eval=FALSE}
-cn_melt <- readRDS("./data_munging/19Q1/cn_melt_19Q1.rds")
-ge_melt_18Q3 <- readRDS("./../htscreens_giant_files/ge_melt_18Q3.rds")
-# ge_melt_19Q1 <- readRDS("./data_munging/19Q1/ge_melt_19Q1.rds")
-
-# maf_filt_dan <- filter(maf_df, Hugo_Symbol %in% g2p_genes)
-# write.table(maf_filt_dan, file = "~/Desktop/maf_filt_dan_19Q1_2018112.csv", quote = FALSE, sep = ",", row.names = FALSE)
-```
-
-## Drug screens
-
-### Merge drug data and annotations
-
-```{r}
-maf_df <- readRDS("./data_munging/19Q1/maf_df_19Q1.rds")
-test <- filter(maf_df, Hugo_Symbol %in% g2p_genes) %>% count(Hugo_Symbol, CCLE_Name)
-test <- test[order(test$n, decreasing = TRUE),]
-```
-
-`r nrow(filter(test, n == 1))`/`r nrow(test)` gene-cell line combinations have more than one mutation in the MAF file. This is corrected in the point mutation filtering done below.
-
-```{r, eval=FALSE}
-# Drug metadata
-drug_meta <- read.delim("./data_munging/drug_id_drug_name_table_10_12_2018.tsv", sep = "\t", header = FALSE)
-colnames(drug_meta) <- c("CID", "Drug")
-drug_meta$Drug <- tolower(drug_meta$Drug)
-maf_df_g2p <- filter(maf_df, Hugo_Symbol %in% g2p_genes)
-ge_filt_18Q3 <- filter(ge_melt_18Q3, Hugo_Symbol %in% g2p_genes)
-# ge_filt_19Q1 <- filter(ge_melt_19Q1, Hugo_Symbol %in% g2p_genes)
-cn_filt <- filter(cn_melt, Hugo_Symbol %in% g2p_genes)
-
-# CCLE
-ccle <- read.delim("./data_munging/data_drug_auc_ccle_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
-ccle <- merge(drug_meta, ccle, by = "CID")
-ccle_melt <- melt(ccle, id.vars = c("CID", "Drug"), measure.vars = colnames(ccle)[3:ncol(ccle)], variable.name = "accession_id", value.name = "ActArea")
-ccle_grid <- expand.grid("accession_id" = unique(ccle_melt$accession_id), "Hugo_Symbol" = g2p_genes)
-ccle_data <- merge(ccle_grid, ccle_melt, by = "accession_id", all.x = TRUE)
-ccle_data <- merge(ccle_data, ccl_converter, by = "accession_id", all.x = TRUE)
-ccle_data <- merge(ccle_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
-ccle_data$Mutation_Status_Nonsilent <- ifelse(is.na(ccle_data$Mutation_Status_Nonsilent), "Wildtype", ccle_data$Mutation_Status_Nonsilent)
-ccle_data <- merge(ccle_data, ge_filt_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
-# ccle_data <- merge(ccle_data, ge_filt_19Q1, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
-ccle_data <- merge(ccle_data, cn_filt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
-ccle_data$Hugo_Symbol <- factor(ccle_data$Hugo_Symbol)
-ccle_data$ActArea <- as.numeric(ccle_data$ActArea)
-# CCLE AUC is actually AOC
-# assuming scale is 0-8, transform to range between 0 and 1
-# get AUC by 1 - AOC
-ccle_data$AUC <- 1 - (ccle_data$ActArea / 8)
-ccle_data <- filter(ccle_data, !is.na(ccle_data$AUC))
-ccle_data$AUC_zscore <- (ccle_data$AUC - mean(ccle_data$AUC)) / sd(ccle_data$AUC)
-ccle_data$Color_Nonsilent <- ifelse(ccle_data$Mutation_Status_Nonsilent == "Wildtype", "palegreen3", "springgreen4")
-ccle_data$Color_Nonsilent <- factor(ccle_data$Color_Nonsilent)
-ccle_data$Drug_Gene <- paste0(ccle_data$Drug, "_", ccle_data$Hugo_Symbol)
-ccle_data$Drug_Gene_Lin <- paste0(ccle_data$Drug, "_", ccle_data$Hugo_Symbol, "_", ccle_data$group_general_lineage_name)
-saveRDS(ccle_data, "./data_munging/19Q1/ccle_data_19Q1_g2pgenes.rds", compress = "xz")
-
-# CTRP
-ctrp <- read.delim("./data_munging/data_drug_auc_ctrp_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
-ctrp <- merge(drug_meta, ctrp, by = "CID")
-ctrp_melt <- melt(ctrp, id.vars = c("CID", "Drug"), measure.vars = colnames(ctrp)[3:ncol(ctrp)], variable.name = "accession_id", value.name = "AUC")
-ctrp_grid <- expand.grid("accession_id" = unique(ctrp_melt$accession_id), "Hugo_Symbol" = g2p_genes)
-ctrp_data <- merge(ctrp_grid, ctrp_melt, by = "accession_id", all.x = TRUE)
-ctrp_data <- merge(ctrp_data, ccl_converter, by = "accession_id", all.x = TRUE)
-ctrp_data <- merge(ctrp_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
-ctrp_data$Mutation_Status_Nonsilent <- ifelse(is.na(ctrp_data$Mutation_Status_Nonsilent), "Wildtype", ctrp_data$Mutation_Status_Nonsilent)
-ctrp_data <- merge(ctrp_data, ge_filt_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
-# ctrp_data <- merge(ctrp_data, ge_filt_19Q1, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
-ctrp_data <- merge(ctrp_data, cn_filt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
-ctrp_data$Hugo_Symbol <- factor(ctrp_data$Hugo_Symbol)
-ctrp_data$AUC <- as.numeric(ctrp_data$AUC)
-ctrp_data <- filter(ctrp_data, !is.na(ctrp_data$AUC))
-ctrp_data$AUC_zscore <- (ctrp_data$AUC - mean(ctrp_data$AUC)) / sd(ctrp_data$AUC)
-ctrp_data$Color_Nonsilent <- ifelse(ctrp_data$Mutation_Status_Nonsilent == "Wildtype", "slategray3", "steelblue4")
-ctrp_data$Color_Nonsilent <- factor(ctrp_data$Color_Nonsilent)
-ctrp_data$Drug_Gene <- paste0(ctrp_data$Drug, "_", ctrp_data$Hugo_Symbol)
-ctrp_data$Drug_Gene_Lin <- paste0(ctrp_data$Drug, "_", ctrp_data$Hugo_Symbol, "_", ctrp_data$group_general_lineage_name)
-saveRDS(ctrp_data, "./data_munging/19Q1/ctrp_data_19Q1_g2pgenes.rds", compress = "xz")
-
-# GDSC
-gdsc <- read.delim("./data_munging/data_drug_auc_gdsc_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
-gdsc <- merge(drug_meta, gdsc, by = "CID")
-gdsc_melt <- melt(gdsc, id.vars = c("CID", "Drug"), measure.vars = colnames(gdsc)[3:ncol(gdsc)], variable.name = "accession_id", value.name = "AUC")
-gdsc_grid <- expand.grid("accession_id" = unique(gdsc_melt$accession_id), "Hugo_Symbol" = g2p_genes)
-gdsc_data <- merge(gdsc_grid, gdsc_melt, by = "accession_id", all.x = TRUE)
-gdsc_data <- merge(gdsc_data, ccl_converter, by = "accession_id", all.x = TRUE)
-gdsc_data <- merge(gdsc_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
-gdsc_data$Mutation_Status_Nonsilent <- ifelse(is.na(gdsc_data$Mutation_Status_Nonsilent), "Wildtype", gdsc_data$Mutation_Status_Nonsilent)
-gdsc_data <- merge(gdsc_data, ge_filt_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
-# gdsc_data <- merge(gdsc_data, ge_filt_19Q1, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
-gdsc_data <- merge(gdsc_data, cn_filt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
-gdsc_data$Hugo_Symbol <- factor(gdsc_data$Hugo_Symbol)
-gdsc_data$AUC <- as.numeric(gdsc_data$AUC)
-gdsc_data <- filter(gdsc_data, !is.na(gdsc_data$AUC))
-gdsc_data$AUC_zscore <- (gdsc_data$AUC - mean(gdsc_data$AUC)) / sd(gdsc_data$AUC)
-gdsc_data$Color_Nonsilent <- ifelse(gdsc_data$Mutation_Status_Nonsilent == "Wildtype", "paleturquoise3", "turquoise4")
-gdsc_data$Color_Nonsilent <- factor(gdsc_data$Color_Nonsilent)
-gdsc_data$Drug_Gene <- paste0(gdsc_data$Drug, "_", gdsc_data$Hugo_Symbol)
-gdsc_data$Drug_Gene_Lin <- paste0(gdsc_data$Drug, "_", gdsc_data$Hugo_Symbol, "_", gdsc_data$group_general_lineage_name)
-saveRDS(gdsc_data, "./data_munging/19Q1/gdsc_data_19Q1_g2pgenes.rds", compress = "xz")
-```
-
-### Filter drug data
-
-```{r, eval=FALSE}
-ccle_data <- readRDS("./data_munging/19Q1/ccle_data_19Q1_g2pgenes.rds")
-ccle_data_ptmuts <- filter(ccle_data, Reference_Allele == 1 | Reference_Allele == 0 | is.na(Reference_Allele))
-ccle_data_ptmuts$Keep_PtMut_Tests <- ifelse(ccle_data_ptmuts$Reference_Allele == 1 | is.na(ccle_data_ptmuts$Reference_Allele), TRUE, ifelse(ccle_data_ptmuts$Tumor_Seq_Allele1 == 1, TRUE, FALSE))
-ccle_data_ptmuts <- filter(ccle_data_ptmuts, Keep_PtMut_Tests == TRUE)
-# Remove columns that lead to duplicate mutation entries
-ccle_data_ptmuts <- subset(ccle_data_ptmuts, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, Genome_Change, Keep_PtMut_Tests))
-ccle_data_ptmuts$Dataset <- "CCLE"
-ccle_data_ptmuts$Hugo_Symbol <- ordered(ccle_data_ptmuts$Hugo_Symbol, levels = g2p_genes)
-ccle_data_ptmuts <- unique(ccle_data_ptmuts)
-saveRDS(ccle_data_ptmuts, "./data_munging/19Q1/ccle_data_19Q1_g2pgenes_ptmuts.rds", compress = "xz")
-
-ctrp_data <- readRDS("./data_munging/19Q1/ctrp_data_19Q1_g2pgenes.rds")
-ctrp_data_ptmuts <- filter(ctrp_data, Reference_Allele == 1 | Reference_Allele == 0 | is.na(Reference_Allele))
-ctrp_data_ptmuts$Keep_PtMut_Tests <- ifelse(ctrp_data_ptmuts$Reference_Allele == 1 | is.na(ctrp_data_ptmuts$Reference_Allele), TRUE, ifelse(ctrp_data_ptmuts$Tumor_Seq_Allele1 == 1, TRUE, FALSE))
-ctrp_data_ptmuts <- filter(ctrp_data_ptmuts, Keep_PtMut_Tests == TRUE)
-# Remove columns that lead to duplicate mutation entries
-ctrp_data_ptmuts <- subset(ctrp_data_ptmuts, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, Genome_Change, Keep_PtMut_Tests))
-ctrp_data_ptmuts$Dataset <- "CTRP"
-ctrp_data_ptmuts$Hugo_Symbol <- ordered(ctrp_data_ptmuts$Hugo_Symbol, levels = g2p_genes)
-ctrp_data_ptmuts <- unique(ctrp_data_ptmuts)
-saveRDS(ctrp_data_ptmuts, "./data_munging/19Q1/ctrp_data_19Q1_g2pgenes_ptmuts.rds", compress = "xz")
-
-gdsc_data <- readRDS("./data_munging/19Q1/gdsc_data_19Q1_g2pgenes.rds")
-gdsc_data_ptmuts <- filter(gdsc_data, Reference_Allele == 1 | Reference_Allele == 0 | is.na(Reference_Allele))
-gdsc_data_ptmuts$Keep_PtMut_Tests <- ifelse(gdsc_data_ptmuts$Reference_Allele == 1 | is.na(gdsc_data_ptmuts$Reference_Allele), TRUE, ifelse(gdsc_data_ptmuts$Tumor_Seq_Allele1 == 1, TRUE, FALSE))
-gdsc_data_ptmuts <- filter(gdsc_data_ptmuts, Keep_PtMut_Tests == TRUE)
-# Remove columns that lead to duplicate mutation entries
-gdsc_data_ptmuts <- subset(gdsc_data_ptmuts, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, Genome_Change, Keep_PtMut_Tests))
-gdsc_data_ptmuts$Dataset <- "GDSC"
-gdsc_data_ptmuts$Hugo_Symbol <- ordered(gdsc_data_ptmuts$Hugo_Symbol, levels = g2p_genes)
-gdsc_data_ptmuts <- unique(gdsc_data_ptmuts)
-saveRDS(gdsc_data_ptmuts, "./data_munging/19Q1/gdsc_data_19Q1_g2pgenes_ptmuts.rds", compress = "xz")
-```
-
-```{r}
-ccle_data <- readRDS("./data_munging/19Q1/ccle_data_19Q1_g2pgenes.rds")
-ctrp_data <- readRDS("./data_munging/19Q1/ctrp_data_19Q1_g2pgenes.rds")
-gdsc_data <- readRDS("./data_munging/19Q1/gdsc_data_19Q1_g2pgenes.rds")
-ccle_data_ptmuts <- readRDS("./data_munging/19Q1/ccle_data_19Q1_g2pgenes_ptmuts.rds")
-ctrp_data_ptmuts <- readRDS("./data_munging/19Q1/ctrp_data_19Q1_g2pgenes_ptmuts.rds")
-gdsc_data_ptmuts <- readRDS("./data_munging/19Q1/gdsc_data_19Q1_g2pgenes_ptmuts.rds")
-
-# Filter drug screen datasets for G2P drug-gene associations
-ccle_data_g2p <- filter(ccle_data_ptmuts, Drug_Gene %in% g2p_druggenes)
-ccle_data_g2p$Mutation_Status_Nonsilent <- factor(ccle_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-ctrp_data_g2p <- filter(ctrp_data_ptmuts, Drug_Gene %in% g2p_druggenes)
-ctrp_data_g2p$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-gdsc_data_g2p <- filter(gdsc_data_ptmuts, Drug_Gene %in% g2p_druggenes)
-gdsc_data_g2p$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-
-# Filter drug screen datasets for G2P drug-gene-lineage associations
-ccle_data_g2p_dgl <- filter(ccle_data_ptmuts, Drug_Gene_Lin %in% g2p_dgls)
-ccle_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(ccle_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-ctrp_data_g2p_dgl <- filter(ctrp_data_ptmuts, Drug_Gene_Lin %in% g2p_dgls)
-ctrp_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-gdsc_data_g2p_dgl <- filter(gdsc_data_ptmuts, Drug_Gene_Lin %in% g2p_dgls)
-gdsc_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-
-# Filter drug screen datasets for G2P drugs and genes
-ccle_data_g2p_grid <- filter(ccle_data_ptmuts, Drug %in% g2p_drugs)
-ccle_data_g2p_grid$Mutation_Status_Nonsilent <- factor(ccle_data_g2p_grid$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-ctrp_data_g2p_grid <- filter(ctrp_data_ptmuts, Drug %in% g2p_drugs)
-ctrp_data_g2p_grid$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p_grid$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-gdsc_data_g2p_grid <- filter(gdsc_data_ptmuts, Drug %in% g2p_drugs)
-gdsc_data_g2p_grid$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p_grid$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-
-# Testing
-test_ccle <- ccle_data_ptmuts %>% group_by(Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()
-test_ctrp <- ctrp_data_ptmuts %>% group_by(Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()
-test_gdsc <- gdsc_data_ptmuts %>% group_by(Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()
-
-# drug_summ <- data.frame(Drug = g2p_drugs, Dataset_Count = 0)
-```

### 2019-03-11 19Q1.Rmd
summary analyses of PGx data for Denise

@@
 
-All annotation files (copy number, mutation status, and gene expression) (Consortium and Consortium 2015, Barretina et al.
+Annotation files for mutation status, copy number, and gene expression of the CCLE and CTRP datasets (Consortium and Consortium 2015, Barretina et al.
 2012) were downloaded from the [DepMap Data Portal](https://depmap.org/portal/download/).
+Note that the group that conducted the GDSC screen also collected their own genomic annotation information for mutation status, copy number, and gene expression, but we did not use it.
 
@@
 library(naniar)
+library(VennDiagram)
 theme_set(theme_light())
@@
 
-Note that the new 19Q1 release made multiple changes to variable names:
+Note that the new DepMap 19Q1 release made multiple changes to variable names:
 
-- They reverted back to "Broad_ID" from 18Q3 rather than "DepMap_ID" that was used in 18Q4
-- Primary.Disease column of the cell line metadata file is more consistently named (Subtype.Disease now has the specific disease annotations), though there are a couple capitalization inconsistencies
-- MAF file no longer has "CCLE_Name" column and has a duplicate column of the Broad IDs (DepMap_ID and Tumor_Sample_Barcode)
+- For their universal ccancer cell line nomenclature, they reverted back to `Broad_ID` from 18Q3 rather than `DepMap_ID` that was used in 18Q4
+- The `Primary.Disease` column of the cell line metadata file is more consistently named (`Subtype.Disease` now has the specific disease annotations), though there are a couple capitalization inconsistencies
+- MAF file no longer has `CCLE_Name` column and has a duplicate column of the Broad IDs (i.e. `DepMap_ID` and `Tumor_Sample_Barcode`)
 
-And data (the following is taken from the [data portal](https://depmap.org/portal/download/)):
+And changes to the data processing pipelines (the following is taken verbatim from the [DepMap data portal](https://depmap.org/portal/download/)):
 
@@
 - Convert drug/compound names to all capitalized for harmonization.
+- Convert all cell line histologies to lower case with words separated by an underscore
+- Maintain same rows across all four data frames, filling with NAs as necessary
+- For each dataframe, maintain same columns for all three source datasets
+- Columns in final dataframes: `source`, `source_ccl_name`, `source_histology`, `sample_id`, and `genes[p]`
+
+### AUC
 
@@
 
-## CCLE
-# Note that ActArea is NOT an AUC value
+# CCLE
+## Note that ActArea is NOT an AUC value
 ccle_filt <- ccle[, c("CCLE Cell Line Name", "ActArea", "Compound")]
@@
 colnames(ccle_filt)[colnames(ccle_filt) == "ActArea"] <- "AUC"
-ccle4harm_long <- select(ccle_filt, source_ccl_name, source_histology, compound_name, AUC)
-ccle4harm_long$source <- "CCLE"
-ccle4harm_long$sample_id <- with(ccle4harm_long, paste(source, source_ccl_name, source_histology, sep = "_"))
-ccle4harm <- dcast(ccle4harm_long, source + source_ccl_name + source_histology + sample_id ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
-ccle4harm[, 5:ncol(ccle4harm)] <- ccle4harm[, 5:ncol(ccle4harm)] %>% replace_with_na_all(condition = ~.x == 10000)
+ccle_auc_long <- select(ccle_filt, source_ccl_name, source_histology, compound_name, AUC)
+ccle_auc_long$source <- "CCLE"
+ccle_auc_long$sample_id <- with(ccle_auc_long, paste(source, source_ccl_name, source_histology, sep = "_"))
+ccle_auc <- dcast(ccle_auc_long, source + source_ccl_name + source_histology + sample_id ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
+ccle_auc[, 5:ncol(ccle_auc)] <- ccle_auc[, 5:ncol(ccle_auc)] %>% replace_with_na_all(condition = ~.x == 10000)
 
-## CTRP
-# area_under_curve: integrated area under the sigmoid-fit concentration-response curve
+# CTRP
+## area_under_curve: integrated area under the sigmoid-fit concentration-response curve
 ctrp_filt <- ctrp[, c("experiment_id", "area_under_curve", "master_cpd_id")]
@@
 ctrp_keep$ccle_primary_site <- ifelse(as.character(ctrp_keep$ccle_primary_site) == "", NA, as.character(ctrp_keep$ccle_primary_site))
-ctrp4harm_long <- select(ctrp_keep, ccl_name, ccle_primary_site, cpd_name, area_under_curve)
-colnames(ctrp4harm_long) <- c("source_ccl_name", "source_histology", "compound_name", "AUC")
-ctrp4harm_long$source <- "CTRP"
-ctrp4harm_long$sample_id <- with(ctrp4harm_long, paste(source, source_ccl_name, source_histology, sep = "_"))
-ctrp4harm <- dcast(ctrp4harm_long, source + source_ccl_name + source_histology + sample_id ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
-ctrp4harm[, 5:ncol(ctrp4harm)] <- ctrp4harm[, 5:ncol(ctrp4harm)] %>% replace_with_na_all(condition = ~.x == 10000)
-
-## GDSC
+ctrp_auc_long <- select(ctrp_keep, ccl_name, ccle_primary_site, cpd_name, area_under_curve)
+colnames(ctrp_auc_long) <- c("source_ccl_name", "source_histology", "compound_name", "AUC")
+ctrp_auc_long$source <- "CTRP"
+ctrp_auc_long$sample_id <- with(ctrp_auc_long, paste(source, source_ccl_name, source_histology, sep = "_"))
+ctrp_auc <- dcast(ctrp_auc_long, source + source_ccl_name + source_histology + sample_id ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
+ctrp_auc[, 5:ncol(ctrp_auc)] <- ctrp_auc[, 5:ncol(ctrp_auc)] %>% replace_with_na_all(condition = ~.x = GDSC
 gdsc_meta_ccl <- select(read.delim("./data_munging/pharmacogenomics_raw_files/GDSC_Cell_Lines_Details.csv", sep = ","), Line, Site)
@@
 gdsc_filt <- merge(gdsc_filt, gdsc_meta_ccl, by = "Line", all = TRUE)
-gdsc4harm_long <- select(gdsc_filt, Line, Site, DRUG_NAME, AUC)
-colnames(gdsc4harm_long) <- c("source_ccl_name", "source_histology", "compound_name", "AUC")
-gdsc4harm_long$source <- "GDSC"
-gdsc4harm_long$sample_id <- with(gdsc4harm_long, paste(source, source_ccl_name, source_histology, sep = "_"))
-gdsc4harm <- dcast(gdsc4harm_long, source + source_ccl_name + source_histology + sample_id ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
-gdsc4harm[, 5:ncol(gdsc4harm)] <- gdsc4harm[, 5:ncol(gdsc4harm)] %>% replace_with_na_all(condition = ~.x == 10000)
+gdsc_auc_long <- select(gdsc_filt, Line, Site, DRUG_NAME, AUC)
+colnames(gdsc_auc_long) <- c("source_ccl_name", "source_histology", "compound_name", "AUC")
+gdsc_auc_long$source <- "GDSC"
+gdsc_auc_long$sample_id <- with(gdsc_auc_long, paste(source, source_ccl_name, source_histology, sep = "_"))
+gdsc_auc <- dcast(gdsc_auc_long, source + source_ccl_name + source_histology + sample_id ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
+gdsc_auc[, 5:ncol(gdsc_auc)] <- gdsc_auc[, 5:ncol(gdsc_auc)] %>% replace_with_na_all(condition = ~.x == 10000)
 
-## BIND ALL
-pgx_harm_list <- list(ccle4harm, ctrp4harm, gdsc4harm)
-pgx_harm_names <- unique(unlist(lapply(pgx_harm_list, names)))
-pgx_harm <- do.call(rbind,
-                    c(lapply(pgx_harm_list,
-                             function(x) data.frame(c(x,
-                                                      sapply(setdiff(pgx_harm_names, names(x)),
-                                                             function(y) NA)
-                                                      )
-                                                    )
-                             )
-                      )
-                    )
+# Bind all AUC
+pgx_auc_list <- list(ccle_auc, ctrp_auc, gdsc_auc)
+pgx_auc_names <- unique(unlist(lapply(pgx_auc_list, names)))
+pgx_all_auc <- do.call(rbind, c(lapply(pgx_auc_list, function(x) data.frame(c(x, sapply(setdiff(pgx_auc_names, names(x)), function(y) NA)), check.names = FALSE))))
+
+# Bind all AUC long files for plotting
+ctrp_auc_long_div <- ctrp_auc_long
+ctrp_auc_long_div$AUC <- ctrp_auc_long_div$AUC / 100
+pgx_auc_long <- rbind(ccle_auc_long, ctrp_auc_long_div, gdsc_auc_long)
 ```
+
+Plots for Denise:
+```{r, eval=FALSE}
+hist_auc_ccle <- ggplot(data = ccle_auc_long) +
+  geom_histogram(mapping = aes(x = AUC, fill = source), color = "black", binwidth = 0.25, boundary = 0, closed = "left") +
+  scale_x_continuous(breaks = seq(0, 8, by = 1), labels = seq(0, 8, by = 1)) +
+  scale_fill_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
+  labs(title = "Distributions of AUC/ActArea values for all drug-cell line combinations", subtitle = "CCLE", y = "Frequency", x = "ActArea") +
+  guides(fill = FALSE)
+hist_auc_ctrp <- ggplot(data = ctrp_auc_long_div) +
+  geom_histogram(mapping = aes(x = AUC, fill = source), color = "black", binwidth = 0.0125, boundary = 0, closed = "left") +
+  scale_x_continuous(breaks = seq(0, 0.3, by = 0.025), labels = seq(0, 0.3, by = 0.025)) +
+  scale_fill_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
+  labs(y = "Frequency", x = "AUC", subtitle = "CTRP", caption = "CTRP AUC values were divided by 100 prior to plotting.") +
+  guides(fill = FALSE)
+hist_auc_gdsc <- ggplot(data = gdsc_auc_long) +
+  geom_histogram(mapping = aes(x = AUC, fill = source), color = "black", binwidth = 0.025, boundary = 0, closed = "left") +
+  scale_x_continuous(breaks = seq(0, 1, by = 0.1), labels = seq(0, 1, by = 0.1)) +
+  scale_fill_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
+  labs(y = "Frequency", x = "AUC", subtitle = "GDSC") +
+  guides(fill = FALSE)
+hist_auc_ccle <- ggplot_gtable(ggplot_build(hist_auc_ccle))
+hist_auc_ctrp <- ggplot_gtable(ggplot_build(hist_auc_ctrp))
+hist_auc_gdsc <- ggplot_gtable(ggplot_build(hist_auc_gdsc))
+p_maxWidth <-  grid::unit.pmax(hist_auc_ccle$widths[2:3], hist_auc_ctrp$widths[2:3], hist_auc_gdsc$widths[2:3])
+hist_auc_ccle$widths[2:3] <- p_maxWidth
+hist_auc_ctrp$widths[2:3] <- p_maxWidth
+hist_auc_gdsc$widths[2:3] <- p_maxWidth
+hist_auc_all <- cowplot::plot_grid(hist_auc_ccle, hist_auc_ctrp, hist_auc_gdsc, nrow = 3, rel_heights = c(9, 9, 8))
+ggsave("./gcn_denise/hist_auc_all.png", hist_auc_all, device = "png", dpi = 450, width = 12, height = 8, units = "in")
+
+venn_ccl <- venn.diagram(list("CCLE" = unique(ccle_auc_long$source_ccl_name), "CTRP" = unique(ctrp_auc_long$source_ccl_name), "GDSC" = unique(gdsc_auc_long$source_ccl_name)), resolution = 5000, main = "Overlap of cancer cell lines (CCLs) screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.001, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
+png("./gcn_denise/venn_ccl.png")
+grid.newpage()
+grid.draw(venn_ccl)
+dev.off()
+
+venn_histology <- venn.diagram(list("CCLE" = unique(na.omit(ccle_auc_long$source_histology)), "CTRP" = unique(na.omit(ctrp_auc_long$source_histology)), "GDSC" = unique(na.omit(gdsc_auc_long$source_histology))), resolution = 5000, main = "Overlap of cancer cell line histologies screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.001, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
+png("./gcn_denise/venn_histology.png")
+grid.newpage()
+grid.draw(venn_histology)
+dev.off()
+
+venn_compound <- venn.diagram(list("CCLE" = unique(na.omit(ccle_auc_long$compound_name)), "CTRP" = unique(na.omit(ctrp_auc_long$compound_name)), "GDSC" = unique(na.omit(gdsc_auc_long$compound_name))), resolution = 5000, main = "Overlap of compounds screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.001, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
+png("./gcn_denise/venn_compound.png")
+grid.newpage()
+grid.draw(venn_compound)
+dev.off()
+```

### 2019-03-12 19Q1.Rmd
update 19Q1 rmd

@@
 ccle_filt$source_histology <- tolower(gsub("^[a-z0-9]*_", "", ccle_filt$`CCLE Cell Line Name`, ignore.case = TRUE))
+# FIX CCL NAMES BEING PUT INTO HISTOLOGY COLUMN
+# ccle_filt$source_histology <- ifelse(grepl("^[a-z0-9]*", ccle_filt$source_histology), NA, ccle_filt$source_histology)
 ccle_filt$source_histology <- ifelse(as.character(ccle_filt$source_histology) == "", NA, as.character(ccle_filt$source_histology))
@@
 ctrp_auc <- dcast(ctrp_auc_long, source + source_ccl_name + source_histology + sample_id ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
-ctrp_auc[, 5:ncol(ctrp_auc)] <- ctrp_auc[, 5:ncol(ctrp_auc)] %>% replace_with_na_all(condition = ~.x = GDSC
+ctrp_auc[, 5:ncol(ctrp_auc)] <- ctrp_auc[, 5:ncol(ctrp_auc)] %>% replace_with_na_all(condition = ~.x == 10000)
+
+# GDSC
 gdsc_meta_ccl <- select(read.delim("./data_munging/pharmacogenomics_raw_files/GDSC_Cell_Lines_Details.csv", sep = ","), Line, Site)

### 2019-03-13 19Q1.Rmd
fix histology mis-labeling in GDSC+CCLE, Venn with all CCLE cell lines

--- 2019-03-08 19Q1.Rmd
@@
 ccl_info <- read.delim("./data_munging/19Q1/DepMap-2019q1-celllines_v2_20190305.csv", sep = ",", header = TRUE, na.strings = c("", NA))
-# Convert Primary.Disease entries to all lower case to fix factorization
+ccl_info$source_ccl_name <- strsplit(as.character(ccl_info$CCLE_Name), split = "_")
+ccl_info$source_ccl_name <- as.character(lapply(ccl_info$source_ccl_name, function(x) ifelse("[MERGED" %in% x || "NORMAL" %in% x, NA, x[1])))
+ccl_info$source_ccl_name[ccl_info$source_ccl_name == "NA"] <- NA
+# Convert Primary.Disease entries to all lower case to fix factorization issue
 ccl_info$Primary.Disease <- as.factor(tolower(ccl_info$Primary.Disease))
@@
 ccle_filt$source_histology <- tolower(gsub("^[a-z0-9]*_", "", ccle_filt$`CCLE Cell Line Name`, ignore.case = TRUE))
-ccle_filt$source_histology <- ifelse(as.character(ccle_filt$source_histology) == "", NA, as.character(ccle_filt$source_histology))
+ccle_filt$source_histology <- ifelse(ccle_filt$`CCLE Cell Line Name` == ccle_filt$source_ccl_name, NA, ccle_filt$source_histology)
 ccle_filt$compound_name <- toupper(ccle_filt$Compound)
 colnames(ccle_filt)[colnames(ccle_filt) == "ActArea"] <- "AUC"
-ccle4harm_long <- select(ccle_filt, source_ccl_name, source_histology, compound_name, AUC)
-ccle4harm_long$source <- "CCLE"
-ccle4harm_long$sample_id <- with(ccle4harm_long, paste(source, source_ccl_name, source_histology, sep = "_"))
-ccle4harm <- dcast(ccle4harm_long, source + source_ccl_name + source_histology + sample_id ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
-ccle4harm[, 5:ncol(ccle4harm)] <- ccle4harm[, 5:ncol(ccle4harm)] %>% replace_with_na_all(condition = ~.x == 10000)
+ccle_auc_long <- select(ccle_filt, source_ccl_name, source_histology, compound_name, AUC)
+ccle_auc_long$source <- "CCLE"
+ccle_auc_long$sample_id <- with(ccle_auc_long, paste(source, source_ccl_name, source_histology, sep = "_"))
+ccle_auc <- dcast(ccle_auc_long, source + source_ccl_name + source_histology + sample_id ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
+ccle_auc[, 5:ncol(ccle_auc)] <- ccle_auc[, 5:ncol(ccle_auc)] %>% replace_with_na_all(condition = ~.x == 10000)
 
-## CTRP
-# area_under_curve: integrated area under the sigmoid-fit concentration-response curve
+# CTRP
+## area_under_curve: integrated area under the sigmoid-fit concentration-response curve
 ctrp_filt <- ctrp[, c("experiment_id", "area_under_curve", "master_cpd_id")]
@@
 ctrp_keep <- merge(merge(ctrp_meta_ccl, ctrp_meta_exp, by = "master_ccl_id", all = TRUE), merge(ctrp_meta_cpd, ctrp_filt, by = "master_cpd_id", all = TRUE), by = "experiment_id", all = TRUE)
+ctrp_keep$ccl_name <- gsub("-", "", ctrp_keep$ccl_name, ignore.case = TRUE)
 ctrp_keep$cpd_name <- toupper(ctrp_keep$cpd_name)
 ctrp_keep$ccle_primary_site <- ifelse(as.character(ctrp_keep$ccle_primary_site) == "", NA, as.character(ctrp_keep$ccle_primary_site))
-ctrp4harm_long <- select(ctrp_keep, ccl_name, ccle_primary_site, cpd_name, area_under_curve)
-colnames(ctrp4harm_long) <- c("source_ccl_name", "source_histology", "compound_name", "AUC")
-ctrp4harm_long$source <- "CTRP"
-ctrp4harm_long$sample_id <- with(ctrp4harm_long, paste(source, source_ccl_name, source_histology, sep = "_"))
-ctrp4harm <- dcast(ctrp4harm_long, source + source_ccl_name + source_histology + sample_id ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
-ctrp4harm[, 5:ncol(ctrp4harm)] <- ctrp4harm[, 5:ncol(ctrp4harm)] %>% replace_with_na_all(condition = ~.x == 10000)
+ctrp_auc_long <- select(ctrp_keep, ccl_name, ccle_primary_site, cpd_name, area_under_curve)
+colnames(ctrp_auc_long) <- c("source_ccl_name", "source_histology", "compound_name", "AUC")
+ctrp_auc_long$source <- "CTRP"
+ctrp_auc_long$sample_id <- with(ctrp_auc_long, paste(source, source_ccl_name, source_histology, sep = "_"))
+ctrp_auc_long_div <- ctrp_auc_long
+ctrp_auc_long_div$AUC <- ctrp_auc_long_div$AUC / 100
+ctrp_auc <- dcast(ctrp_auc_long, source + source_ccl_name + source_histology + sample_id ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
+ctrp_auc[, 5:ncol(ctrp_auc)] <- ctrp_auc[, 5:ncol(ctrp_auc)] %>% replace_with_na_all(condition = ~.x == 10000)
 
-## GDSC
+# GDSC
 gdsc_meta_ccl <- select(read.delim("./data_munging/pharmacogenomics_raw_files/GDSC_Cell_Lines_Details.csv", sep = ","), Line, Site)
+## For following 4 Lines, Site == "NS"
+## Assigned new Sites by looking up cell lines in GDSC cell line portal (https://www.cancerrxgene.org/translation/CellLine#t-all)
+gdsc_meta_ccl$Site[gdsc_meta_ccl$Line == "COR-L321"] <- "lung"
+gdsc_meta_ccl$Site[gdsc_meta_ccl$Line == "SU-DHL-8"] <- "haematopoietic_and_lymphoid_tissue"
+gdsc_meta_ccl$Site[gdsc_meta_ccl$Line == "CRO-AP3"] <- "haematopoietic_and_lymphoid_tissue"
+gdsc_meta_ccl$Site[gdsc_meta_ccl$Line == "Hep_3B2_1-7"] <- "liver"
 gdsc_filt <- gdsc[, c("CELL_LINE_NAME", "DRUG_NAME", "AUC")]
@@
 gdsc_filt <- merge(gdsc_filt, gdsc_meta_ccl, by = "Line", all = TRUE)
-gdsc4harm_long <- select(gdsc_filt, Line, Site, DRUG_NAME, AUC)
-colnames(gdsc4harm_long) <- c("source_ccl_name", "source_histology", "compound_name", "AUC")
-gdsc4harm_long$source <- "GDSC"
-gdsc4harm_long$sample_id <- with(gdsc4harm_long, paste(source, source_ccl_name, source_histology, sep = "_"))
-gdsc4harm <- dcast(gdsc4harm_long, source + source_ccl_name + source_histology + sample_id ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
-gdsc4harm[, 5:ncol(gdsc4harm)] <- gdsc4harm[, 5:ncol(gdsc4harm)] %>% replace_with_na_all(condition = ~.x == 10000)
+gdsc_filt$Line <- gsub("-", "", gdsc_filt$Line, ignore.case = TRUE)
+gdsc_auc_long <- select(gdsc_filt, Line, Site, DRUG_NAME, AUC)
+colnames(gdsc_auc_long) <- c("source_ccl_name", "source_histology", "compound_name", "AUC")
+gdsc_auc_long$source <- "GDSC"
+gdsc_auc_long$sample_id <- with(gdsc_auc_long, paste(source, source_ccl_name, source_histology, sep = "_"))
+gdsc_auc <- dcast(gdsc_auc_long, source + source_ccl_name + source_histology + sample_id ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
+gdsc_auc[, 5:ncol(gdsc_auc)] <- gdsc_auc[, 5:ncol(gdsc_auc)] %>% replace_with_na_all(condition = ~.x == 10000)
 
-## BIND ALL
-pgx_harm_list <- list(ccle4harm, ctrp4harm, gdsc4harm)
-pgx_harm_names <- unique(unlist(lapply(pgx_harm_list, names)))
-pgx_harm <- do.call(rbind,
-                    c(lapply(pgx_harm_list,
-                             function(x) data.frame(c(x,
-                                                      sapply(setdiff(pgx_harm_names, names(x)),
-                                                             function(y) NA)
-                                                      )
-                                                    )
-                             )
-                      )
-                    )
+# Bind all AUC
+pgx_auc_list <- list(ccle_auc, ctrp_auc, gdsc_auc)
+pgx_auc_names <- unique(unlist(lapply(pgx_auc_list, names)))
+pgx_all_auc <- do.call(rbind, c(lapply(pgx_auc_list, function(x) data.frame(c(x, sapply(setdiff(pgx_auc_names, names(x)), function(y) NA)), check.names = FALSE))))
 ```
+
+Compare histology representation for CCLE, CTRP, and GDSC:
+```{r}
+sort(unique(na.omit(gdsc_auc_long$source_histology)))
+# Histologies represented in GDSC but not CTRP
+setdiff(unique(na.omit(gdsc_auc_long$source_histology)), unique(na.omit(ctrp_auc_long$source_histology)))
+# Histologies represented in GDSC but not CCLE
+setdiff(unique(na.omit(gdsc_auc_long$source_histology)), unique(na.omit(ccle_auc_long$source_histology)))
+```
+
+### Summary figures
+
+```{r, eval=FALSE}
+hist_auc_ccle <- ggplot(data = ccle_auc_long) +
+  geom_histogram(mapping = aes(x = AUC, fill = source), color = "black", binwidth = 0.25, boundary = 0, closed = "left") +
+  scale_x_continuous(breaks = seq(0, 8, by = 1), labels = seq(0, 8, by = 1)) +
+  scale_fill_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
+  labs(title = "Distributions of AUC/ActArea values for all drug-cell line combinations", subtitle = "CCLE", y = "Frequency", x = "ActArea") +
+  guides(fill = FALSE)
+hist_auc_ctrp <- ggplot(data = ctrp_auc_long_div) +
+  geom_histogram(mapping = aes(x = AUC, fill = source), color = "black", binwidth = 0.0125, boundary = 0, closed = "left") +
+  scale_x_continuous(breaks = seq(0, 0.3, by = 0.025), labels = seq(0, 0.3, by = 0.025)) +
+  scale_fill_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
+  labs(y = "Frequency", x = "AUC", subtitle = "CTRP", caption = "CTRP AUC values were divided by 100 prior to plotting.") +
+  guides(fill = FALSE)
+hist_auc_gdsc <- ggplot(data = gdsc_auc_long) +
+  geom_histogram(mapping = aes(x = AUC, fill = source), color = "black", binwidth = 0.025, boundary = 0, closed = "left") +
+  scale_x_continuous(breaks = seq(0, 1, by = 0.1), labels = seq(0, 1, by = 0.1)) +
+  scale_fill_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
+  labs(y = "Frequency", x = "AUC", subtitle = "GDSC") +
+  guides(fill = FALSE)
+hist_auc_ccle <- ggplot_gtable(ggplot_build(hist_auc_ccle))
+hist_auc_ctrp <- ggplot_gtable(ggplot_build(hist_auc_ctrp))
+hist_auc_gdsc <- ggplot_gtable(ggplot_build(hist_auc_gdsc))
+p_maxWidth <-  grid::unit.pmax(hist_auc_ccle$widths[2:3], hist_auc_ctrp$widths[2:3], hist_auc_gdsc$widths[2:3])
+hist_auc_ccle$widths[2:3] <- p_maxWidth
+hist_auc_ctrp$widths[2:3] <- p_maxWidth
+hist_auc_gdsc$widths[2:3] <- p_maxWidth
+hist_auc_all <- cowplot::plot_grid(hist_auc_ccle, hist_auc_ctrp, hist_auc_gdsc, nrow = 3, rel_heights = c(9, 9, 8))
+ggsave("./gcn_denise/hist_auc_all.png", hist_auc_all, device = "png", dpi = 450, width = 12, height = 8, units = "in")
+
+venn_ccl <- venn.diagram(list("CCLE" = unique(na.omit(ccl_info$source_ccl_name)), "CTRP" = unique(ctrp_auc_long$source_ccl_name), "GDSC" = unique(gdsc_auc_long$source_ccl_name)), resolution = 5000, main = "Overlap of cancer cell lines (CCLs) screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 0), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
+png("./gcn_denise/venn_ccl.png")
+grid.newpage()
+grid.draw(venn_ccl)
+dev.off()
+
+venn_histology <- venn.diagram(list("CCLE" = unique(na.omit(ccle_auc_long$source_histology)), "CTRP" = unique(na.omit(ctrp_auc_long$source_histology)), "GDSC" = unique(na.omit(gdsc_auc_long$source_histology))), resolution = 5000, main = "Overlap of cancer cell line histologies screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 0), cat.dist = c(-0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
+png("./gcn_denise/venn_histology.png")
+grid.newpage()
+grid.draw(venn_histology)
+dev.off()
+
+venn_compound <- venn.diagram(list("CCLE" = unique(na.omit(ccle_auc_long$compound_name)), "CTRP" = unique(na.omit(ctrp_auc_long$compound_name)), "GDSC" = unique(na.omit(gdsc_auc_long$compound_name))), resolution = 5000, main = "Overlap of compounds screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.001, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
+png("./gcn_denise/venn_compound.png")
+grid.newpage()
+grid.draw(venn_compound)
+dev.off()
+```

### 2019-03-13 19Q1.Rmd

@@
 ```{r}
+library(crunch)
 library(ggpubr)
@@
 library(kableExtra)
+library(naniar)
 library(reshape2)
 library(tidyverse)
-library(naniar)
 library(VennDiagram)
@@
 ccl_info <- read.delim("./data_munging/19Q1/DepMap-2019q1-celllines_v2_20190305.csv", sep = ",", header = TRUE, na.strings = c("", NA))
+ccl_info$source <- "CCLE"
 ccl_info$source_ccl_name <- strsplit(as.character(ccl_info$CCLE_Name), split = "_")
@@
 ccl_info$source_ccl_name[ccl_info$source_ccl_name == "NA"] <- NA
+ccl_info$source_histology <- tolower(gsub("^[a-z0-9]*_", "", ccl_info$CCLE_Name, ignore.case = TRUE))
+ccl_info$source_histology <- ifelse(ccl_info$CCLE_Name == ccl_info$source_ccl_name, NA, ccl_info$source_histology)
+ccl_info$sample_id <- with(ccl_info, paste(source, source_ccl_name, source_histology, sep = "_"))
+# This CCL had a histology of "primary": Looking at the DepMap reference, this is an immortalize epithelial line from the CNS (https://depmap.org/portal/cell_line/NHAHTDD_PRIMARY), so I chanegd the histology accordingly
+ccl_info$source_histology[ccl_info$source_ccl_name == "NHAHTDD"] <- "central_nervous_system"
 # Convert Primary.Disease entries to all lower case to fix factorization issue
@@
 colnames(ge_19Q1)[1] <- "Broad_ID"
+
+pgx_ccle_ge <- merge(select(ccl_info, source, source_ccl_name, source_histology, sample_id, Broad_ID), ge_19Q1, by = "Broad_ID", all = TRUE)
+
 # Melt
@@
 # ge_melt_19Q1 <- unique(ge_melt_19Q1_all)
+
+saveRDS(pgx_ccle_ge, "./data_munging/19Q1/pgx_ccle_ge.rds", compress = "xz")
 saveRDS(ge_melt_19Q1, "./data_munging/19Q1/ge_melt_19Q1.rds", compress = "xz")
@@
 - For each dataframe, maintain same columns for all three source datasets
-- Columns in final dataframes: `source`, `source_ccl_name`, `source_histology`, `sample_id`, and `genes[p]`
+- Columns in final dataframes: `source`, `source_ccl_name`, `source_histology`, `sample_id`, and `genes/compounds/mutations[p]`
 
@@
 
+Column descriptions for `pgx_all_auc`:
+
+- `source`: the dataset from which the data comes from (either CCLE, CTRP, or GDSC)
+- `source_ccl_name`: the name of the cancer cell line (CCL) included in the source dataset
+    - Note that all CCLs (excluding matched normal tissues and "merged" CCLs) from the CCLE dataset (N = 1,645) were included in `pgx_all_auc` for imputation
+- `source_histology`: the general histology/tissue type of the CCL
+- `sample_id`: custom identifiers for our datasets that are concatenations of the `source`, `source_ccl_name`, and `source_histology`
+- All other columns: compound and drug names that were screened in at least one CCL in at least one source dataset
+    - NA values indictate that compound wasn't screened in the respective CCL in the respective source dataset
+
 ```{r, eval=TRUE}
-maf_df <- readRDS("./data_munging/19Q1/maf_df_19Q1.rds")
-cn_melt <- readRDS("./data_munging/19Q1/cn_melt_19Q1.rds")
-ge_melt <- readRDS("./data_munging/19Q1/ge_melt_19Q1.rds")
-
 ccle <- read.delim("./data_munging/pharmacogenomics_raw_files/CCLE_NP24.2009_Drug_data_2015.02.24_20190307.csv", sep = ",", header  = TRUE, check.names = FALSE)
@@
 ccle_filt$source_histology <- ifelse(ccle_filt$`CCLE Cell Line Name` == ccle_filt$source_ccl_name, NA, ccle_filt$source_histology)
+ccle_filt <- merge(select(ccl_info, source, source_ccl_name, source_histology, sample_id), ccle_filt, by = c("source_ccl_name", "source_histology"), all = TRUE)
 ccle_filt$compound_name <- toupper(ccle_filt$Compound)
 colnames(ccle_filt)[colnames(ccle_filt) == "ActArea"] <- "AUC"
-ccle_auc_long <- select(ccle_filt, source_ccl_name, source_histology, compound_name, AUC)
-ccle_auc_long$source <- "CCLE"
-ccle_auc_long$sample_id <- with(ccle_auc_long, paste(source, source_ccl_name, source_histology, sep = "_"))
+ccle_auc_long <- select(ccle_filt, source, source_ccl_name, source_histology, sample_id, compound_name, AUC)
+# ccle_auc_long$source <- "CCLE"
+# ccle_auc_long$sample_id <- with(ccle_auc_long, paste(source, source_ccl_name, source_histology, sep = "_"))
 ccle_auc <- dcast(ccle_auc_long, source + source_ccl_name + source_histology + sample_id ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
@@
 gdsc_meta_ccl$Site[gdsc_meta_ccl$Line == "Hep_3B2_1-7"] <- "liver"
+## For tollowing line, Site did not match CCLE notation, so I changed it to CCLE notation
+gdsc_meta_ccl$Site[gdsc_meta_ccl$Line == "SW13"] <- "adrenal_cortex"
 gdsc_filt <- gdsc[, c("CELL_LINE_NAME", "DRUG_NAME", "AUC")]
@@
 gdsc_auc_long$sample_id <- with(gdsc_auc_long, paste(source, source_ccl_name, source_histology, sep = "_"))
+gdsc_auc_long$source_histology <- as.character(gdsc_auc_long$source_histology)
 gdsc_auc <- dcast(gdsc_auc_long, source + source_ccl_name + source_histology + sample_id ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
@@
 pgx_all_auc <- do.call(rbind, c(lapply(pgx_auc_list, function(x) data.frame(c(x, sapply(setdiff(pgx_auc_names, names(x)), function(y) NA)), check.names = FALSE))))
+# saveRDS(pgx_all_auc, "./data_munging/19Q1/pgx_all_auc.rds", compress = "xz")
+# write.csv.gz(pgx_all_auc, "./data_munging/19Q1/pgx_all_auc.csv.gz", row.names = FALSE)
 ```
@@
 ```{r}
+sort(unique(na.omit(ccle_auc_long$source_histology)))
+sort(unique(na.omit(ctrp_auc_long$source_histology)))
 sort(unique(na.omit(gdsc_auc_long$source_histology)))
-# Histologies represented in GDSC but not CTRP
+
+setdiff(unique(na.omit(ccle_auc_long$source_histology)), unique(na.omit(gdsc_auc_long$source_histology)))
 setdiff(unique(na.omit(gdsc_auc_long$source_histology)), unique(na.omit(ctrp_auc_long$source_histology)))
-# Histologies represented in GDSC but not CCLE
-setdiff(unique(na.omit(gdsc_auc_long$source_histology)), unique(na.omit(ccle_auc_long$source_histology)))
+```
+
+### GE
+
+```{r, eval=FALSE}
+ge_melt <- readRDS("./data_munging/19Q1/ge_melt_19Q1.rds")
+ge_merged <- merge(select(ccl_info, Broad_ID, source_histology, source_ccl_name), ge_melt, by = "Broad_ID", all = TRUE)
+```
+
+### CN
+
+```{r, eval=FALSE}
+cn_melt <- readRDS("./data_munging/19Q1/cn_melt_19Q1.rds")
+```
+
+### Mut
+
+```{r, eval=FALSE}
+maf_df <- readRDS("./data_munging/19Q1/maf_df_19Q1.rds")
 ```
@@
 
+futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
 venn_ccl <- venn.diagram(list("CCLE" = unique(na.omit(ccl_info$source_ccl_name)), "CTRP" = unique(ctrp_auc_long$source_ccl_name), "GDSC" = unique(gdsc_auc_long$source_ccl_name)), resolution = 5000, main = "Overlap of cancer cell lines (CCLs) screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 0), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
@@
 
-venn_histology <- venn.diagram(list("CCLE" = unique(na.omit(ccle_auc_long$source_histology)), "CTRP" = unique(na.omit(ctrp_auc_long$source_histology)), "GDSC" = unique(na.omit(gdsc_auc_long$source_histology))), resolution = 5000, main = "Overlap of cancer cell line histologies screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 0), cat.dist = c(-0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
+futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
+venn_histology <- venn.diagram(list("CCLE" = unique(na.omit(ccle_auc_long$source_histology)), "CTRP" = unique(na.omit(ctrp_auc_long$source_histology)), "GDSC" = unique(na.omit(gdsc_auc_long$source_histology))), resolution = 5000, main = "Overlap of cancer cell line histologies screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(0, 0, 0), cat.dist = c(0.001, 0.001, -0.01), cat.cex = 1.5, cex = 1, filename = NULL)
 png("./gcn_denise/venn_histology.png")
@@
 
+futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
 venn_compound <- venn.diagram(list("CCLE" = unique(na.omit(ccle_auc_long$compound_name)), "CTRP" = unique(na.omit(ctrp_auc_long$compound_name)), "GDSC" = unique(na.omit(gdsc_auc_long$compound_name))), resolution = 5000, main = "Overlap of compounds screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.001, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)

### 2019-03-15 19Q1.Rmd

@@
 ccl_info$source_histology <- ifelse(ccl_info$CCLE_Name == ccl_info$source_ccl_name, NA, ccl_info$source_histology)
-ccl_info$sample_id <- with(ccl_info, paste(source, source_ccl_name, source_histology, sep = "_"))
+ccl_info$sample_ID <- with(ccl_info, paste(source, source_ccl_name, source_histology, sep = "_"))
 # This CCL had a histology of "primary": Looking at the DepMap reference, this is an immortalize epithelial line from the CNS (https://depmap.org/portal/cell_line/NHAHTDD_PRIMARY), so I chanegd the histology accordingly
@@
 ccl_info$Primary.Disease <- as.factor(tolower(ccl_info$Primary.Disease))
-# Harmonize ID column name
+# Harmonize ID column name and rename CCLE_Name column to fit with dataframe style
+colnames(ccl_info)[colnames(ccl_info) == "CCLE_Name"] <- "CCLE_ccl_name"
 colnames(ccl_info)[colnames(ccl_info) == "DepMap_ID"] <- "Broad_ID"
@@
 
-pgx_ccle_ge <- merge(select(ccl_info, source, source_ccl_name, source_histology, sample_id, Broad_ID), ge_19Q1, by = "Broad_ID", all = TRUE)
+# For Denise's GCN
+pgx_ccle_ge <- merge(select(ccl_info, source, source_ccl_name, source_histology, sample_ID, CCLE_ccl_name, Broad_ID), ge_19Q1, by = "Broad_ID", all = TRUE)
+saveRDS(pgx_ccle_ge, "./data_munging/19Q1/pgx_ccle_ge.rds", compress = "xz")
 
@@
 # ge_melt_19Q1 <- unique(ge_melt_19Q1_all)
-
-saveRDS(pgx_ccle_ge, "./data_munging/19Q1/pgx_ccle_ge.rds", compress = "xz")
 saveRDS(ge_melt_19Q1, "./data_munging/19Q1/ge_melt_19Q1.rds", compress = "xz")
@@
 - For each dataframe, maintain same columns for all three source datasets
-- Columns in final dataframes: `source`, `source_ccl_name`, `source_histology`, `sample_id`, and `genes/compounds/mutations[p]`
+- Columns in final dataframes: `source`, `source_ccl_name`, `source_histology`, `sample_ID`, and `genes/compounds/mutations[p]`
 
@@
 - `source_histology`: the general histology/tissue type of the CCL
-- `sample_id`: custom identifiers for our datasets that are concatenations of the `source`, `source_ccl_name`, and `source_histology`
+- `sample_ID`: custom identifiers for our datasets that are concatenations of the `source`, `source_ccl_name`, and `source_histology`
+- `CCLE_ccl_name`: the cell line name using CCLE nomenclature, which is a concatenation of the cell line name with the CCLE-annotated histology in all caps, separated by underscores
+- `Broad_ID`: the custom identifiers (formatted as ACH-######) used by the Broad's Cancer Dependency Map project to ease cell line name harmonization efforts 
 - All other columns: compound and drug names that were screened in at least one CCL in at least one source dataset
@@
 ccle_filt$source_histology <- ifelse(ccle_filt$`CCLE Cell Line Name` == ccle_filt$source_ccl_name, NA, ccle_filt$source_histology)
-ccle_filt <- merge(select(ccl_info, source, source_ccl_name, source_histology, sample_id), ccle_filt, by = c("source_ccl_name", "source_histology"), all = TRUE)
+colnames(ccle_filt)[colnames(ccle_filt) == "CCLE Cell Line Name"] <- "CCLE_ccl_name"
+ccle_filt <- merge(select(ccl_info, source, source_ccl_name, source_histology, sample_ID, CCLE_ccl_name, Broad_ID), ccle_filt, by = c("source_ccl_name", "source_histology", "CCLE_ccl_name"), all = TRUE)
 ccle_filt$compound_name <- toupper(ccle_filt$Compound)
 colnames(ccle_filt)[colnames(ccle_filt) == "ActArea"] <- "AUC"
-ccle_auc_long <- select(ccle_filt, source, source_ccl_name, source_histology, sample_id, compound_name, AUC)
-# ccle_auc_long$source <- "CCLE"
-# ccle_auc_long$sample_id <- with(ccle_auc_long, paste(source, source_ccl_name, source_histology, sep = "_"))
-ccle_auc <- dcast(ccle_auc_long, source + source_ccl_name + source_histology + sample_id ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
-ccle_auc[, 5:ncol(ccle_auc)] <- ccle_auc[, 5:ncol(ccle_auc)] %>% replace_with_na_all(condition = ~.x == 10000)
+ccle_auc_long <- select(ccle_filt, source, source_ccl_name, source_histology, sample_ID, CCLE_ccl_name, Broad_ID, compound_name, AUC)
+ccle_auc <- dcast(ccle_auc_long, source + source_ccl_name + source_histology + sample_ID + CCLE_ccl_name + Broad_ID ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
+ccle_auc[, 7:ncol(ccle_auc)] <- ccle_auc[, 7:ncol(ccle_auc)] %>% replace_with_na_all(condition = ~.x == 10000)
 
@@
 ctrp_auc_long$source <- "CTRP"
-ctrp_auc_long$sample_id <- with(ctrp_auc_long, paste(source, source_ccl_name, source_histology, sep = "_"))
+ctrp_auc_long$sample_ID <- with(ctrp_auc_long, paste(source, source_ccl_name, source_histology, sep = "_"))
+ctrp_auc_long <- merge(ctrp_auc_long, select(ccl_info, source_ccl_name, source_histology, CCLE_ccl_name, Broad_ID), by = c("source_ccl_name", "source_histology"), all.x = TRUE)
 ctrp_auc_long_div <- ctrp_auc_long
 ctrp_auc_long_div$AUC <- ctrp_auc_long_div$AUC / 100
-ctrp_auc <- dcast(ctrp_auc_long, source + source_ccl_name + source_histology + sample_id ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
-ctrp_auc[, 5:ncol(ctrp_auc)] <- ctrp_auc[, 5:ncol(ctrp_auc)] %>% replace_with_na_all(condition = ~.x == 10000)
+ctrp_auc <- dcast(ctrp_auc_long, source + source_ccl_name + source_histology + sample_ID + CCLE_ccl_name + Broad_ID ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
+ctrp_auc[, 7:ncol(ctrp_auc)] <- ctrp_auc[, 7:ncol(ctrp_auc)] %>% replace_with_na_all(condition = ~.x == 10000)
 
@@
 gdsc_auc_long$source <- "GDSC"
-gdsc_auc_long$sample_id <- with(gdsc_auc_long, paste(source, source_ccl_name, source_histology, sep = "_"))
+gdsc_auc_long$sample_ID <- with(gdsc_auc_long, paste(source, source_ccl_name, source_histology, sep = "_"))
 gdsc_auc_long$source_histology <- as.character(gdsc_auc_long$source_histology)
-gdsc_auc <- dcast(gdsc_auc_long, source + source_ccl_name + source_histology + sample_id ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
-gdsc_auc[, 5:ncol(gdsc_auc)] <- gdsc_auc[, 5:ncol(gdsc_auc)] %>% replace_with_na_all(condition = ~.x == 10000)
+gdsc_auc_long <- merge(gdsc_auc_long, select(ccl_info, source_ccl_name, source_histology, CCLE_ccl_name, Broad_ID), by = c("source_ccl_name", "source_histology"), all.x = TRUE)
+gdsc_auc <- dcast(gdsc_auc_long, source + source_ccl_name + source_histology + sample_ID + CCLE_ccl_name + Broad_ID ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
+gdsc_auc[, 7:ncol(gdsc_auc)] <- gdsc_auc[, 7:ncol(gdsc_auc)] %>% replace_with_na_all(condition = ~.x == 10000)
 
@@
 setdiff(unique(na.omit(gdsc_auc_long$source_histology)), unique(na.omit(ctrp_auc_long$source_histology)))
-```
-
-### GE
-
-```{r, eval=FALSE}
-ge_melt <- readRDS("./data_munging/19Q1/ge_melt_19Q1.rds")
-ge_merged <- merge(select(ccl_info, Broad_ID, source_histology, source_ccl_name), ge_melt, by = "Broad_ID", all = TRUE)
-```
-
-### CN
-
-```{r, eval=FALSE}
-cn_melt <- readRDS("./data_munging/19Q1/cn_melt_19Q1.rds")
-```
-
-### Mut
-
-```{r, eval=FALSE}
-maf_df <- readRDS("./data_munging/19Q1/maf_df_19Q1.rds")
 ```
@@
 ```
+
+### Pozdeyev et al. (2016)
+
+```{r}
+ccl_histologies <- select(ccl_info, source_ccl_name, source_histology) %>% drop_na(source_ccl_name)
+colnames(ccl_histologies)[colnames(ccl_histologies) == "source_ccl_name"] <- "Cell_line" 
+auc <- read.delim("./data_munging/pharmacogenomics_raw_files/celline_stack.csv.gz", sep = ",")
+auc <- merge(ccl_histologies, auc, by = "Cell_line", all.y = TRUE)
+num_auc_per_db <- auc %>% count(Database)
+num_ccl_per_db <- unique(select(auc, Database, Cell_line)) %>% count(Database)
+# only CCLs represetented in 2 or 3 databases were included
+num_db_per_ccl <- unique(select(auc, Database, Cell_line)) %>% count(Cell_line)
+```
+
+There were `r length(setdiff(unique(ccl_histologies$Cell_line), unique(auc$Cell_line)))` cell lines not represented in the Pozdeyev et al. harmonized dataset.
+
+Plots:
+```{r}
+futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
+venn_ccl_pozdeyev <- venn.diagram(list("CCLE" = unique(filter(ccl_per_db, Database == "CCLE"))$Cell_line, "CTRP" = unique(filter(ccl_per_db, Database == "CTRP"))$Cell_line, "GDSC" = unique(filter(ccl_per_db, Database == "GDSC"))$Cell_line), resolution = 5000, main = "Overlap of cancer cell lines (CCLs) screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
+png("./gcn_denise/pozdeyev_venn_ccl.png")
+grid.newpage()
+grid.draw(venn_ccl_pozdeyev)
+dev.off()
+
+num_ccl_per_db_bar <- ggplot(data = unique(select(auc, Database, Cell_line))) +
+  geom_bar(aes(x = Database, fill = Database), alpha = 0.7) +
+  scale_fill_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) + 
+  guides(fill = "none") +
+  scale_y_continuous(breaks = seq(0, 700, by = 50), labels = seq(0, 700, by = 50)) +
+  geom_text(data = num_ccl_per_db, aes(x = Database, y = n + 20, label = n)) +
+  labs(y = "Number of cell lines", title = "Number of unique cell lines per dataset")
+ggsave("./gcn_denise/pozdeyev_ccl_per_db.png", num_ccl_per_db_bar, device = "png", dpi = 450, width = 12, height = 8, units = "in")
+
+num_ccl_per_hist_bar <- ggplot(data = unique(select(auc, Database, Cell_line, source_histology))) +
+  facet_wrap(~ Database, scales = "free_y") +
+  geom_bar(aes(x = source_histology, fill = source_histology), alpha = 0.7) +
+  guides(fill = "none") +
+  coord_cartesian(ylim = c(0, 130)) +
+  scale_y_continuous(breaks = seq(0, 130, by = 10), labels = seq(0, 130, by = 10)) +
+  labs(x = "Histology", y = "Number of cell lines", title = "Number of unique cell lines per histology") +
+  theme(axis.text.x = element_text(angle = 60, hjust = 1))
+ggsave("./gcn_denise/pozdeyev_ccl_per_histology.png", num_ccl_per_hist_bar, device = "png", dpi = 450, width = 12, height = 6, units = "in")
+
+auc_per_db_dist <- ggplot(data = auc) +
+  facet_wrap(~ Database) +
+  geom_histogram(aes(x = AUC_IC50, fill = Database), color = "black", alpha = 0.7, binwidth = 0.025, boundary = 0, closed = "left") +
+  scale_fill_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
+  guides(fill = "none") +
+  geom_text(data = num_auc_per_db, aes(x = 0.5, y = 4750, label = paste0("n = ", formatC(n, format = "d", big.mark = ",")))) +
+  scale_y_continuous(breaks = seq(0, 5000, by = 500), labels = seq(0, 5000, by = 500)) +
+  labs(x = "AUC IC50", y = "Frequency", title = "Distributions of AUC IC50 values for all drugs in each dataset")
+ggsave("./gcn_denise/pozdeyev_aucic50_per_db_dist.png", auc_per_db_dist, device = "png", dpi = 450, width = 12, height = 6, units = "in")
+```

### 2019-03-18 19Q1.Rmd
update 19Q1 rmd w/ pozdeyev exploration

@@
 hist_auc_all <- cowplot::plot_grid(hist_auc_ccle, hist_auc_ctrp, hist_auc_gdsc, nrow = 3, rel_heights = c(9, 9, 8))
-ggsave("./gcn_denise/hist_auc_all.png", hist_auc_all, device = "png", dpi = 450, width = 12, height = 8, units = "in")
+hist_auc_all
+# ggsave("./gcn_denise/hist_auc_all.png", hist_auc_all, device = "png", dpi = 450, width = 12, height = 8, units = "in")
 
@@
 venn_ccl <- venn.diagram(list("CCLE" = unique(na.omit(ccl_info$source_ccl_name)), "CTRP" = unique(ctrp_auc_long$source_ccl_name), "GDSC" = unique(gdsc_auc_long$source_ccl_name)), resolution = 5000, main = "Overlap of cancer cell lines (CCLs) screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 0), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
-png("./gcn_denise/venn_ccl.png")
-grid.newpage()
-grid.draw(venn_ccl)
-dev.off()
+# png("./gcn_denise/venn_ccl.png")
+# grid.newpage()
+# grid.draw(venn_ccl)
+# dev.off()
 
@@
 venn_histology <- venn.diagram(list("CCLE" = unique(na.omit(ccle_auc_long$source_histology)), "CTRP" = unique(na.omit(ctrp_auc_long$source_histology)), "GDSC" = unique(na.omit(gdsc_auc_long$source_histology))), resolution = 5000, main = "Overlap of cancer cell line histologies screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(0, 0, 0), cat.dist = c(0.001, 0.001, -0.01), cat.cex = 1.5, cex = 1, filename = NULL)
-png("./gcn_denise/venn_histology.png")
-grid.newpage()
-grid.draw(venn_histology)
-dev.off()
+# png("./gcn_denise/venn_histology.png")
+# grid.newpage()
+# grid.draw(venn_histology)
+# dev.off()
 
@@
 venn_compound <- venn.diagram(list("CCLE" = unique(na.omit(ccle_auc_long$compound_name)), "CTRP" = unique(na.omit(ctrp_auc_long$compound_name)), "GDSC" = unique(na.omit(gdsc_auc_long$compound_name))), resolution = 5000, main = "Overlap of compounds screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.001, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
-png("./gcn_denise/venn_compound.png")
-grid.newpage()
-grid.draw(venn_compound)
-dev.off()
+# png("./gcn_denise/venn_compound.png")
+# grid.newpage()
+# grid.draw(venn_compound)
+# dev.off()
 ```
 
-### Pozdeyev et al. (2016)
+# Pozdeyev et al. (2016) summary
+
+--------------------------------------------------------------------------------
+
+## Matched data
 
@@
 num_auc_per_db <- auc %>% count(Database)
+ccl_per_db <- unique(select(auc, Database, Cell_line))
 num_ccl_per_db <- unique(select(auc, Database, Cell_line)) %>% count(Database)
@@
 
-Plots:
+## Unmatched data
+
+```{r}
+CCLE_drug_response_metrics <- as.data.frame(get(load("./../../../Desktop/Drug_Sensitvity_Metrics/data/CCLE_drug_response_metrics.RData")))
+CTRP_drug_response_metrics <- as.data.frame(get(load("./../../../Desktop/Drug_Sensitvity_Metrics/data/CTRP_drug_response_metrics.RData")))
+GDSC_drug_response_metrics <- as.data.frame(get(load("./../../../Desktop/Drug_Sensitvity_Metrics/data/GDSC_drug_response_metrics.RData")))
+
+ccle_test <- merge(select(CCLE_drug_response_metrics, Drug_name, Cell_line, AUC_IC50), select(filter(auc, Database == "CCLE"), Drug_name, Cell_line, AUC_IC50), by = c("Drug_name", "Cell_line"), suffixes = c("_unmatched", "_matched_all_pairs"), all = TRUE)
+
+ctrp_test <- merge(select(CTRP_drug_response_metrics, Drug_name, Cell_line, AUC_IC50), select(filter(auc, Database == "CTRP"), Drug_name, Cell_line, AUC_IC50), by = c("Drug_name", "Cell_line"), suffixes = c("_unmatched", "_matched_all_pairs"), all = TRUE)
+
+gdsc_test <- merge(select(GDSC_drug_response_metrics, Drug_name, Cell_line, AUC_IC50), select(filter(auc, Database == "GDSC"), Drug_name, Cell_line, AUC_IC50), by = c("Drug_name", "Cell_line"), suffixes = c("_unmatched", "_matched_all_pairs"), all = TRUE)
+
+auc_unmatched <- rbind(CCLE_drug_response_metrics, CTRP_drug_response_metrics, GDSC_drug_response_metrics)
+auc_unmatched$AUC_EC50 <- as.numeric(as.character(auc_unmatched$AUC_EC50))
+auc_unmatched$AUC_IC50 <- as.numeric(as.character(auc_unmatched$AUC_IC50))
+num_auc_unmatched_per_db <- auc_unmatched %>% count(Database)
+```
+
+## Plots
+
+Unmatched: 
 ```{r}
 futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
-venn_ccl_pozdeyev <- venn.diagram(list("CCLE" = unique(filter(ccl_per_db, Database == "CCLE"))$Cell_line, "CTRP" = unique(filter(ccl_per_db, Database == "CTRP"))$Cell_line, "GDSC" = unique(filter(ccl_per_db, Database == "GDSC"))$Cell_line), resolution = 5000, main = "Overlap of cancer cell lines (CCLs) screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
-png("./gcn_denise/pozdeyev_venn_ccl.png")
-grid.newpage()
-grid.draw(venn_ccl_pozdeyev)
-dev.off()
+venn_all_ccl_pozdeyev <- venn.diagram(list("CCLE" = unique(ccle_test$Cell_line), "CTRP" = unique(ctrp_test$Cell_line), "GDSC" = unique(gdsc_test$Cell_line)), resolution = 5000, main = "Overlap of cancer cell lines (CCLs) screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
+# png("./gcn_denise/pozdeyev_venn_all_ccl.png", res = 500, units = "in", width = 6, height = 6)
+# grid.newpage()
+# grid.draw(venn_all_ccl_pozdeyev)
+# dev.off()
+
+futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
+venn_all_drugs_pozdeyev <- venn.diagram(list("CCLE" = unique(ccle_test$Drug_name), "CTRP" = unique(ctrp_test$Drug_name), "GDSC" = unique(gdsc_test$Drug_name)), resolution = 5000, main = "Overlap of cancer cell lines (CCLs) screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
+# png("./gcn_denise/pozdeyev_venn_all_drugs.png", res = 500, units = "in", width = 6, height = 6)
+# grid.newpage()
+# grid.draw(venn_all_drugs_pozdeyev)
+# dev.off()
+
+aucic50_unmatched_per_db_dist <- ggplot(data = auc_unmatched) +
+  facet_wrap(~ Database, scales = "free_y") +
+  geom_histogram(aes(x = AUC_IC50, fill = Database), color = "black", alpha = 0.7, binwidth = 0.025, boundary = 0, closed = "left") +
+  scale_fill_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
+  guides(fill = "none") +
+  labs(x = "AUC IC50", y = "Frequency", title = "Distributions of AUC IC50 values for all drugs in each dataset (unmatched)")
+aucic50_unmatched_per_db_dist
+# ggsave("./gcn_denise/pozdeyev_aucic50_unmatched_per_db_dist.png", aucic50_unmatched_per_db_dist, device = "png", dpi = 450, width = 12, height = 6, units = "in")
+
+aucec50_unmatched_per_db_dist <- ggplot(data = auc_unmatched) +
+  facet_wrap(~ Database, scale = "free_y") +
+  geom_histogram(aes(x = AUC_EC50, fill = Database), color = "black", alpha = 0.7, binwidth = 0.025, boundary = 0, closed = "left") +
+  scale_fill_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
+  guides(fill = "none") +
+  labs(x = "AUC EC50", y = "Frequency", title = "Distributions of AUC EC50 values for all drugs in each dataset (unmatched)")
+aucec50_unmatched_per_db_dist
+# ggsave("./gcn_denise/pozdeyev_aucec50_unmatched_per_db_dist.png", aucec50_unmatched_per_db_dist, device = "png", dpi = 450, width = 12, height = 6, units = "in")
+```
+
+Matched:
+```{r}
+futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
+venn_ccl_pozdeyev <- venn.diagram(list("CCLE" = unique(filter(ccl_per_db, Database == "CCLE"))$Cell_line, "CTRP" = unique(filter(ccl_per_db, Database == "CTRP"))$Cell_line, "GDSC" = unique(filter(ccl_per_db, Database == "GDSC"))$Cell_line), resolution = 5000, main = "Overlap of cancer cell lines (CCLs) screened in matched_all_pairs dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
+# png("./gcn_denise/pozdeyev_venn_ccl.png", res = 500, units = "in", width = 6, height = 6)
+# grid.newpage()
+# grid.draw(venn_ccl_pozdeyev)
+# dev.off()
 
@@
   labs(y = "Number of cell lines", title = "Number of unique cell lines per dataset")
-ggsave("./gcn_denise/pozdeyev_ccl_per_db.png", num_ccl_per_db_bar, device = "png", dpi = 450, width = 12, height = 8, units = "in")
+num_ccl_per_db_bar
+# ggsave("./gcn_denise/pozdeyev_ccl_per_db.png", num_ccl_per_db_bar, device = "png", dpi = 450, width = 12, height = 8, units = "in")
 
-num_ccl_per_hist_bar <- ggplot(data = unique(select(auc, Database, Cell_line, source_histology))) +
+num_ccl_per_hist_per_db_bar <- ggplot(data = unique(select(auc, Database, Cell_line, source_histology))) +
   facet_wrap(~ Database, scales = "free_y") +
@@
   scale_y_continuous(breaks = seq(0, 130, by = 10), labels = seq(0, 130, by = 10)) +
-  labs(x = "Histology", y = "Number of cell lines", title = "Number of unique cell lines per histology") +
+  labs(x = "Histology", y = "Number of cell lines", title = "Number of unique cell lines per histology, grouped by database") +
   theme(axis.text.x = element_text(angle = 60, hjust = 1))
-ggsave("./gcn_denise/pozdeyev_ccl_per_histology.png", num_ccl_per_hist_bar, device = "png", dpi = 450, width = 12, height = 6, units = "in")
+num_ccl_per_hist_per_db_bar
+# ggsave("./gcn_denise/pozdeyev_ccl_per_histology_per_db.png", num_ccl_per_hist_per_db_bar, device = "png", dpi = 450, width = 12, height = 8, units = "in")
 
-auc_per_db_dist <- ggplot(data = auc) +
+num_ccl_per_hist_bar <- ggplot(data = unique(select(auc, Cell_line, source_histology))) +
+  geom_bar(aes(x = source_histology, fill = source_histology), alpha = 0.7) +
+  guides(fill = "none") +
+  coord_cartesian(ylim = c(0, 130)) +
+  scale_y_continuous(breaks = seq(0, 130, by = 10), labels = seq(0, 130, by = 10)) +
+  labs(x = "Histology", y = "Number of cell lines", title = "Number of unique cell lines per histology across all three databases") +
+  theme(axis.text.x = element_text(angle = 60, hjust = 1))
+num_ccl_per_hist_bar
+# ggsave("./gcn_denise/pozdeyev_ccl_per_histology.png", num_ccl_per_hist_bar, device = "png", dpi = 450, width = 12, height = 8, units = "in")
+
+aucic50_per_db_dist <- ggplot(data = auc) +
   facet_wrap(~ Database) +
@@
   scale_y_continuous(breaks = seq(0, 5000, by = 500), labels = seq(0, 5000, by = 500)) +
-  labs(x = "AUC IC50", y = "Frequency", title = "Distributions of AUC IC50 values for all drugs in each dataset")
-ggsave("./gcn_denise/pozdeyev_aucic50_per_db_dist.png", auc_per_db_dist, device = "png", dpi = 450, width = 12, height = 6, units = "in")
+  labs(x = "AUC IC50", y = "Frequency", title = "Distributions of AUC IC50 values for all drugs in each dataset (filtered by matching)")
+aucic50_per_db_dist
+# ggsave("./gcn_denise/pozdeyev_aucic50_per_db_dist.png", aucic50_per_db_dist, device = "png", dpi = 450, width = 12, height = 6, units = "in")
+
+aucec50_per_db_dist <- ggplot(data = auc) +
+  facet_wrap(~ Database) +
+  geom_histogram(aes(x = AUC_EC50, fill = Database), color = "black", alpha = 0.7, binwidth = 0.025, boundary = 0, closed = "left") +
+  scale_fill_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
+  guides(fill = "none") +
+  geom_text(data = num_auc_per_db, aes(x = 0.5, y = 4750, label = paste0("n = ", formatC(n, format = "d", big.mark = ",")))) +
+  scale_y_continuous(breaks = seq(0, 5000, by = 500), labels = seq(0, 5000, by = 500)) +
+  labs(x = "AUC EC50", y = "Frequency", title = "Distributions of AUC EC50 values for all drugs in each dataset (filtered by matching)")
+aucec50_per_db_dist
+# ggsave("./gcn_denise/pozdeyev_aucec50_per_db_dist.png", aucec50_per_db_dist, device = "png", dpi = 450, width = 12, height = 6, units = "in")
 ```

### 2019-03-19 19Q1.Rmd
Rmd changes

@@
 Compare histology representation for CCLE, CTRP, and GDSC:
-```{r}
+```{r, eval=FALSE}
 sort(unique(na.omit(ccle_auc_long$source_histology)))
@@
 
+```{r}
+ccl_histologies <- select(ccl_info, source_ccl_name, source_histology, CCLE_ccl_name, Broad_ID) %>% drop_na(source_ccl_name)
+colnames(ccl_histologies)[colnames(ccl_histologies) == "source_ccl_name"] <- "Cell_line" 
+colnames(ccl_histologies)[colnames(ccl_histologies) == "source_histology"] <- "Histology"
+
+# Accout for cell line aliases and missing histologies
+auc_unmatched_na_histologies <- read.delim("./data_munging/pozdeyev2016/auc_unmatched_na_histologies.csv", sep = ",", row.names = 1)
+auc_unmatched_na_histologies$accession_id <- NULL
+auc_unmatched_na_histologies$Notes <- NULL
+auc_unmatched_na_histologies$Histology <- ifelse(auc_unmatched_na_histologies$Histology == "", NA, as.character(auc_unmatched_na_histologies$Histology))
+auc_unmatched_na_histologies$CCLE_ccl_name <- ifelse(auc_unmatched_na_histologies$CCLE_ccl_name  == "", NA, as.character(auc_unmatched_na_histologies$CCLE_ccl_name ))
+auc_unmatched_na_histologies$Broad_ID <- ifelse(auc_unmatched_na_histologies$Broad_ID == "", NA, as.character(auc_unmatched_na_histologies$Broad_ID))
+
+# Bind DepMap histologies and curated histologies
+ccl_histologies <- bind_rows(ccl_histologies, auc_unmatched_na_histologies)
+```
+
+For plotting:
+
+- `c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")`
+- `c("springgreen4", "steelblue4", "turquoise4")`
+
 ## Matched data
 
-```{r}
-ccl_histologies <- select(ccl_info, source_ccl_name, source_histology) %>% drop_na(source_ccl_name)
-colnames(ccl_histologies)[colnames(ccl_histologies) == "source_ccl_name"] <- "Cell_line" 
-auc <- read.delim("./data_munging/pharmacogenomics_raw_files/celline_stack.csv.gz", sep = ",")
-auc <- merge(ccl_histologies, auc, by = "Cell_line", all.y = TRUE)
-num_auc_per_db <- auc %>% count(Database)
-ccl_per_db <- unique(select(auc, Database, Cell_line))
-num_ccl_per_db <- unique(select(auc, Database, Cell_line)) %>% count(Database)
+```{r, eval=TRUE}
+auc_matched <- read.delim("./data_munging/pharmacogenomics_raw_files/celline_stack.csv.gz", sep = ",")
+auc_matched <- merge(ccl_histologies, auc_matched , by = "Cell_line", all.y = TRUE)
+num_auc_per_db_matched <- auc_matched %>% count(Database)
+ccl_per_db_matched <- unique(select(auc_matched , Database, Cell_line))
+num_ccl_per_db_matched <- unique(select(auc_matched , Database, Cell_line)) %>% count(Database)
 # only CCLs represetented in 2 or 3 databases were included
-num_db_per_ccl <- unique(select(auc, Database, Cell_line)) %>% count(Cell_line)
+num_db_per_ccl_matched <- unique(select(auc_matched , Database, Cell_line)) %>% count(Cell_line)
 ```
 
-There were `r length(setdiff(unique(ccl_histologies$Cell_line), unique(auc$Cell_line)))` cell lines not represented in the Pozdeyev et al. harmonized dataset.
+There were `r length(setdiff(unique(ccl_histologies$Cell_line), unique(auc_matched $Cell_line)))` cell lines not represented in the Pozdeyev et al. harmonized dataset.
+
+Plots:
+```{r, eval=FALSE}
+futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
+venn_ccl_matched_poz <- venn.diagram(list("CCLE" = unique(filter(ccl_per_db_matched, Database == "CCLE"))$Cell_line, "CTRP" = unique(filter(ccl_per_db_matched, Database == "CTRP"))$Cell_line, "GDSC" = unique(filter(ccl_per_db_matched, Database == "GDSC"))$Cell_line), resolution = 5000, main = "Overlap of cancer cell lines (CCLs) screened in matched_all_pairs dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
+png("./gcn_denise/pozdeyev_matched/pozdeyev_venn_ccl_matched.png", res = 500, units = "in", width = 6, height = 6)
+grid.newpage()
+grid.draw(venn_ccl_matched_poz)
+dev.off()
+
+num_ccl_per_db_matched_bar <- ggplot(data = unique(select(auc_matched , Database, Cell_line))) +
+  geom_bar(aes(x = Database, fill = Database), alpha = 0.7) +
+  scale_fill_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) + 
+  guides(fill = "none") +
+  scale_y_continuous(breaks = seq(0, 700, by = 50), labels = seq(0, 700, by = 50)) +
+  geom_text(data = num_ccl_per_db_matched, aes(x = Database, y = n + 20, label = n)) +
+  labs(y = "Number of cell lines", title = "Number of unique cell lines per dataset")
+num_ccl_per_db_matched_bar
+ggsave("./gcn_denise/pozdeyev_matched/pozdeyev_ccl_per_db_matched.png", num_ccl_per_db_matched_bar, device = "png", dpi = 450, width = 12, height = 8, units = "in")
+
+num_ccl_per_hist_per_db_matched_bar <- ggplot(data = unique(select(auc_matched , Database, Cell_line, Histology))) +
+  facet_wrap(~ Database, scales = "free_y") +
+  geom_bar(aes(x = Histology, fill = Histology), alpha = 0.7) +
+  guides(fill = "none") +
+  coord_cartesian(ylim = c(0, 130)) +
+  scale_y_continuous(breaks = seq(0, 130, by = 10), labels = seq(0, 130, by = 10)) +
+  labs(y = "Number of cell lines", title = "Number of unique cell lines per histology, grouped by database") +
+  theme(axis.text.x = element_text(angle = 60, hjust = 1))
+num_ccl_per_hist_per_db_matched_bar
+ggsave("./gcn_denise/pozdeyev_matched/pozdeyev_ccl_per_histology_per_db_matched.png", num_ccl_per_hist_per_db_matched_bar, device = "png", dpi = 450, width = 12, height = 8, units = "in")
+
+num_ccl_per_hist_matched_bar <- ggplot(data = unique(select(auc_matched , Cell_line, Histology))) +
+  geom_bar(aes(x = Histology, fill = Histology), alpha = 0.7) +
+  guides(fill = "none") +
+  coord_cartesian(ylim = c(0, 130)) +
+  scale_y_continuous(breaks = seq(0, 130, by = 10), labels = seq(0, 130, by = 10)) +
+  labs(y = "Number of cell lines", title = "Number of unique cell lines per histology across all three databases") +
+  theme(axis.text.x = element_text(angle = 60, hjust = 1))
+num_ccl_per_hist_matched_bar
+ggsave("./gcn_denise/pozdeyev_matched/pozdeyev_ccl_per_histology_matched.png", num_ccl_per_hist_matched_bar, device = "png", dpi = 450, width = 12, height = 8, units = "in")
+
+aucic50_per_db_matched <- ggplot(data = auc_matched ) +
+  facet_wrap(~ Database) +
+  geom_histogram(aes(x = AUC_IC50, fill = Database), color = "black", alpha = 0.7, binwidth = 0.025, boundary = 0, closed = "left") +
+  scale_fill_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
+  guides(fill = "none") +
+  geom_text(data = num_auc_per_db_matched, aes(x = 0.5, y = 4750, label = paste0("n = ", formatC(n, format = "d", big.mark = ",")))) +
+  scale_y_continuous(breaks = seq(0, 5000, by = 500), labels = seq(0, 5000, by = 500)) +
+  labs(x = "AUC IC50", y = "Frequency", title = "Distributions of AUC IC50 values for all drugs in each dataset (filtered by matching)")
+aucic50_per_db_matched
+ggsave("./gcn_denise/pozdeyev_matched/pozdeyev_aucic50_per_db_matched.png", aucic50_per_db_matched, device = "png", dpi = 450, width = 12, height = 6, units = "in")
+```
 
@@
 ```{r}
-CCLE_drug_response_metrics <- as.data.frame(get(load("./../../../Desktop/Drug_Sensitvity_Metrics/data/CCLE_drug_response_metrics.RData")))
-CTRP_drug_response_metrics <- as.data.frame(get(load("./../../../Desktop/Drug_Sensitvity_Metrics/data/CTRP_drug_response_metrics.RData")))
-GDSC_drug_response_metrics <- as.data.frame(get(load("./../../../Desktop/Drug_Sensitvity_Metrics/data/GDSC_drug_response_metrics.RData")))
+ccle_poz <- read.delim("./data_munging/pozdeyev2016/CCLE_drug_response_metrics.csv.gz", sep = ",")
+ccle_poz <- merge(ccl_histologies, ccle_poz, by = "Cell_line", all.y = TRUE)
+# ccle_test <- merge(select(ccle_poz, Drug_name, Cell_line, AUC_IC50), select(filter(auc, Database == "CCLE"), Drug_name, Cell_line, AUC_IC50), by = c("Drug_name", "Cell_line"), suffixes = c("_unmatched", "_matched_all_pairs"), all = TRUE)
 
-ccle_test <- merge(select(CCLE_drug_response_metrics, Drug_name, Cell_line, AUC_IC50), select(filter(auc, Database == "CCLE"), Drug_name, Cell_line, AUC_IC50), by = c("Drug_name", "Cell_line"), suffixes = c("_unmatched", "_matched_all_pairs"), all = TRUE)
+ctrp_poz <- read.delim("./../htscreens_giant_files/pozdeyev2016/CTRP_drug_response_metrics.csv.gz", sep = ",")
+ctrp_poz <- merge(ccl_histologies, ctrp_poz, by = "Cell_line", all.y = TRUE)
+# ctrp_test <- merge(select(ctrp_poz, Drug_name, Cell_line, AUC_IC50), select(filter(auc, Database == "CTRP"), Drug_name, Cell_line, AUC_IC50), by = c("Drug_name", "Cell_line"), suffixes = c("_unmatched", "_matched_all_pairs"), all = TRUE)
 
-ctrp_test <- merge(select(CTRP_drug_response_metrics, Drug_name, Cell_line, AUC_IC50), select(filter(auc, Database == "CTRP"), Drug_name, Cell_line, AUC_IC50), by = c("Drug_name", "Cell_line"), suffixes = c("_unmatched", "_matched_all_pairs"), all = TRUE)
+gdsc_poz <- read.delim("./data_munging/pozdeyev2016/GDSC_drug_response_metrics.csv.gz", sep = ",")
+gdsc_poz <- merge(ccl_histologies, gdsc_poz, by = "Cell_line", all.y = TRUE)
+# gdsc_test <- merge(select(gdsc_poz, Drug_name, Cell_line, AUC_IC50), select(filter(auc, Database == "GDSC"), Drug_name, Cell_line, AUC_IC50), by = c("Drug_name", "Cell_line"), suffixes = c("_unmatched", "_matched_all_pairs"), all = TRUE)
 
-gdsc_test <- merge(select(GDSC_drug_response_metrics, Drug_name, Cell_line, AUC_IC50), select(filter(auc, Database == "GDSC"), Drug_name, Cell_line, AUC_IC50), by = c("Drug_name", "Cell_line"), suffixes = c("_unmatched", "_matched_all_pairs"), all = TRUE)
-
-auc_unmatched <- rbind(CCLE_drug_response_metrics, CTRP_drug_response_metrics, GDSC_drug_response_metrics)
+auc_unmatched <- bind_rows(ccle_poz, ctrp_poz, gdsc_poz)
 auc_unmatched$AUC_EC50 <- as.numeric(as.character(auc_unmatched$AUC_EC50))
 auc_unmatched$AUC_IC50 <- as.numeric(as.character(auc_unmatched$AUC_IC50))
-num_auc_unmatched_per_db <- auc_unmatched %>% count(Database)
+auc_unmatched$sample_ID <- with(auc_unmatched, paste(Database, Cell_line, Histology, sep = "_"))
+num_auc_per_db_unmatched <- auc_unmatched %>% count(Database)
+
+# Identify cell lines without histology indications. Write to file to edit for merging back to ccl_histologies file
+# test <- filter(auc_unmatched, is.na(Histology))[, 1:10]
+# auc_unmatched_na_hists <- filter(auc_unmatched, is.na(Histology))$Cell_line
+# write.csv(auc_unmatched_na_hists, "./data_munging/pozdeyev2016/auc_unmatched_na_histologies.csv")
+
+# Create merged dataset with sample_ids in the rows and drugs across the columns
+auc_unmatched_wide <- dcast(auc_unmatched, Database + Cell_line + Histology + sample_ID + CCLE_ccl_name + Broad_ID ~ Drug_name, value.var = "AUC_IC50", fun.aggregate = mean, fill = 1000000)
+auc_unmatched_wide[, 7:ncol(auc_unmatched_wide)] <- auc_unmatched_wide[, 7:ncol(auc_unmatched_wide)] %>% replace_with_na_all(condition = ~.x == 1000000)
+# write.csv.gz(auc_unmatched_wide, file = "./data_munging/pozdeyev2016/merged_auc_v20190319.2.csv.gz", row.names = FALSE, na = "NA")
 ```
 
-## Plots
+Data source:
+- Pozdeyev, N., Yoo, M., Mackie, R., Schweppe, R.
+E., Tan, A.
+C., & Haugen, B.
+R.
+(2016).
+Integrating heterogeneous drug sensitivity data from cancer pharmacogenomic studies.
+Oncotarget, 7(32), 51619–51625.
+https://doi.org/10.18632/oncotarget.10010
+- Online visualization tool: http://tanlab.ucdenver.edu/QAPC/
+- Zipped file containing their R scripts and full datasets can be downloaded here: http://tanlab.ucdenver.edu/QAPC/Downloads/Drug_Sensitvity_Metrics.zip
 
-Unmatched: 
+Column descriptions in merged_auc_v20190319.1.csv.gz:
+- `Database`: the dataset from which the data comes from (either CCLE, CTRP, or GDSC)
+- `Cell_line`: the name of the cancer cell line (CCL), harmonized across datasets by Pozdeyev et al. (2016)
+- `Histology`: the general histology/tissue type of the CCL according to the CCLE annotations (see DepMap-2019q1-celllines_v2.csv file from the DepMap Data Portal)
+- `sample_ID`: custom identifiers for this dataset that are concatenations of the `Database`, `Cell_line`, and `Histology`, separated by underscores
+- `CCLE_ccl_name`: the cell line name using CCLE nomenclature, which is a concatenation of the cell line name with the CCLE-annotated histology in all caps, separated by underscores
+- `Broad_ID`: the custom identifiers (formatted as ACH-######) used by the Broad's Cancer Dependency Map project to ease cell line name harmonization efforts 
+- All other columns: compound and drug names that were screened in at least one CCL in at least one database
+    - NA values indictate that compound wasn't screened in the respective CCL in the respective source dataset
+    - Values are in AUC_IC50, the area under rhe dose response curve calculated from IC50 model
+
+Plots:
 ```{r}
 futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
-venn_all_ccl_pozdeyev <- venn.diagram(list("CCLE" = unique(ccle_test$Cell_line), "CTRP" = unique(ctrp_test$Cell_line), "GDSC" = unique(gdsc_test$Cell_line)), resolution = 5000, main = "Overlap of cancer cell lines (CCLs) screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
-# png("./gcn_denise/pozdeyev_venn_all_ccl.png", res = 500, units = "in", width = 6, height = 6)
+venn_all_ccl_unmatched_pozdeyev <- venn.diagram(list("CCLE" = unique(ccle_poz$Cell_line), "CTRP" = unique(ctrp_poz$Cell_line), "GDSC" = unique(gdsc_poz$Cell_line)), resolution = 5000, main = "Overlap of cancer cell lines (CCLs) screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
+# png("./gcn_denise/pozdeyev_unmatched/pozdeyev_venn_all_ccl_unmatched.png", res = 500, units = "in", width = 6, height = 6)
 # grid.newpage()
-# grid.draw(venn_all_ccl_pozdeyev)
+# grid.draw(venn_all_ccl_unmatched_pozdeyev)
 # dev.off()
@@
 futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
-venn_all_drugs_pozdeyev <- venn.diagram(list("CCLE" = unique(ccle_test$Drug_name), "CTRP" = unique(ctrp_test$Drug_name), "GDSC" = unique(gdsc_test$Drug_name)), resolution = 5000, main = "Overlap of cancer cell lines (CCLs) screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
-# png("./gcn_denise/pozdeyev_venn_all_drugs.png", res = 500, units = "in", width = 6, height = 6)
+venn_all_drugs_unmatched_pozdeyev <- venn.diagram(list("CCLE" = unique(ccle_poz$Drug_name), "CTRP" = unique(ctrp_poz$Drug_name), "GDSC" = unique(gdsc_poz$Drug_name)), resolution = 5000, main = "Overlap of cancer cell lines (CCLs) screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
+# png("./gcn_denise/pozdeyev_unmatched/pozdeyev_venn_all_drugs_unmatched.png", res = 500, units = "in", width = 6, height = 6)
 # grid.newpage()
-# grid.draw(venn_all_drugs_pozdeyev)
+# grid.draw(venn_all_drugs_unmatched_pozdeyev)
 # dev.off()
 
-aucic50_unmatched_per_db_dist <- ggplot(data = auc_unmatched) +
+num_ccl_per_hist_per_db_unmatched_bar <- ggplot(data = unique(select(auc_unmatched, Database, Cell_line, Histology))) +
+  facet_wrap(~ Database) +
+  geom_bar(aes(x = Histology, fill = Histology), alpha = 0.7) +
+  guides(fill = "none") +
+  # coord_cartesian(ylim = c(0, 130)) +
+  scale_y_continuous(breaks = seq(0, 160, by = 20), labels = seq(0, 160, by = 20)) +
+  labs(y = "Number of cell lines", title = "Number of unique cell lines per histology, grouped by database") +
+  theme(axis.text.x = element_text(angle = 60, hjust = 1))
+num_ccl_per_hist_per_db_unmatched_bar
+# ggsave("./gcn_denise/pozdeyev_unmatched/pozdeyev_ccl_per_histology_per_db_unmatched.png", num_ccl_per_hist_per_db_unmatched_bar, device = "png", dpi = 450, width = 12, height = 8, units = "in")
+
+num_ccl_per_hist_unmatched_bar <- ggplot(data = unique(select(auc_unmatched, Cell_line, Histology))) +
+  geom_bar(aes(x = Histology, fill = Histology), alpha = 0.7) +
+  guides(fill = "none") +
+  scale_y_continuous(breaks = seq(0, 220, by = 20), labels = seq(0, 220, by = 20)) +
+  labs(y = "Number of cell lines", title = "Number of unique cell lines per histology across all three databases") +
+  theme(axis.text.x = element_text(angle = 60, hjust = 1))
+num_ccl_per_hist_unmatched_bar
+# ggsave("./gcn_denise/pozdeyev_unmatched/pozdeyev_ccl_per_histology_unmatched.png", num_ccl_per_hist_unmatched_bar, device = "png", dpi = 450, width = 12, height = 8, units = "in")
+
+aucic50_per_db_unmatched <- ggplot(data = auc_unmatched) +
   facet_wrap(~ Database, scales = "free_y") +
@@
   labs(x = "AUC IC50", y = "Frequency", title = "Distributions of AUC IC50 values for all drugs in each dataset (unmatched)")
-aucic50_unmatched_per_db_dist
-# ggsave("./gcn_denise/pozdeyev_aucic50_unmatched_per_db_dist.png", aucic50_unmatched_per_db_dist, device = "png", dpi = 450, width = 12, height = 6, units = "in")
-
-aucec50_unmatched_per_db_dist <- ggplot(data = auc_unmatched) +
-  facet_wrap(~ Database, scale = "free_y") +
-  geom_histogram(aes(x = AUC_EC50, fill = Database), color = "black", alpha = 0.7, binwidth = 0.025, boundary = 0, closed = "left") +
-  scale_fill_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
-  guides(fill = "none") +
-  labs(x = "AUC EC50", y = "Frequency", title = "Distributions of AUC EC50 values for all drugs in each dataset (unmatched)")
-aucec50_unmatched_per_db_dist
-# ggsave("./gcn_denise/pozdeyev_aucec50_unmatched_per_db_dist.png", aucec50_unmatched_per_db_dist, device = "png", dpi = 450, width = 12, height = 6, units = "in")
+aucic50_per_db_unmatched
+# ggsave("./gcn_denise/pozdeyev_unmatched/pozdeyev_aucic50_per_db_unmatched.png", aucic50_per_db_unmatched, device = "png", dpi = 450, width = 12, height = 6, units = "in")
 ```
-
-Matched:
-```{r}
-futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
-venn_ccl_pozdeyev <- venn.diagram(list("CCLE" = unique(filter(ccl_per_db, Database == "CCLE"))$Cell_line, "CTRP" = unique(filter(ccl_per_db, Database == "CTRP"))$Cell_line, "GDSC" = unique(filter(ccl_per_db, Database == "GDSC"))$Cell_line), resolution = 5000, main = "Overlap of cancer cell lines (CCLs) screened in matched_all_pairs dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
-# png("./gcn_denise/pozdeyev_venn_ccl.png", res = 500, units = "in", width = 6, height = 6)
-# grid.newpage()
-# grid.draw(venn_ccl_pozdeyev)
-# dev.off()
-
-num_ccl_per_db_bar <- ggplot(data = unique(select(auc, Database, Cell_line))) +
-  geom_bar(aes(x = Database, fill = Database), alpha = 0.7) +
-  scale_fill_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) + 
-  guides(fill = "none") +
-  scale_y_continuous(breaks = seq(0, 700, by = 50), labels = seq(0, 700, by = 50)) +
-  geom_text(data = num_ccl_per_db, aes(x = Database, y = n + 20, label = n)) +
-  labs(y = "Number of cell lines", title = "Number of unique cell lines per dataset")
-num_ccl_per_db_bar
-# ggsave("./gcn_denise/pozdeyev_ccl_per_db.png", num_ccl_per_db_bar, device = "png", dpi = 450, width = 12, height = 8, units = "in")
-
-num_ccl_per_hist_per_db_bar <- ggplot(data = unique(select(auc, Database, Cell_line, source_histology))) +
-  facet_wrap(~ Database, scales = "free_y") +
-  geom_bar(aes(x = source_histology, fill = source_histology), alpha = 0.7) +
-  guides(fill = "none") +
-  coord_cartesian(ylim = c(0, 130)) +
-  scale_y_continuous(breaks = seq(0, 130, by = 10), labels = seq(0, 130, by = 10)) +
-  labs(x = "Histology", y = "Number of cell lines", title = "Number of unique cell lines per histology, grouped by database") +
-  theme(axis.text.x = element_text(angle = 60, hjust = 1))
-num_ccl_per_hist_per_db_bar
-# ggsave("./gcn_denise/pozdeyev_ccl_per_histology_per_db.png", num_ccl_per_hist_per_db_bar, device = "png", dpi = 450, width = 12, height = 8, units = "in")
-
-num_ccl_per_hist_bar <- ggplot(data = unique(select(auc, Cell_line, source_histology))) +
-  geom_bar(aes(x = source_histology, fill = source_histology), alpha = 0.7) +
-  guides(fill = "none") +
-  coord_cartesian(ylim = c(0, 130)) +
-  scale_y_continuous(breaks = seq(0, 130, by = 10), labels = seq(0, 130, by = 10)) +
-  labs(x = "Histology", y = "Number of cell lines", title = "Number of unique cell lines per histology across all three databases") +
-  theme(axis.text.x = element_text(angle = 60, hjust = 1))
-num_ccl_per_hist_bar
-# ggsave("./gcn_denise/pozdeyev_ccl_per_histology.png", num_ccl_per_hist_bar, device = "png", dpi = 450, width = 12, height = 8, units = "in")
-
-aucic50_per_db_dist <- ggplot(data = auc) +
-  facet_wrap(~ Database) +
-  geom_histogram(aes(x = AUC_IC50, fill = Database), color = "black", alpha = 0.7, binwidth = 0.025, boundary = 0, closed = "left") +
-  scale_fill_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
-  guides(fill = "none") +
-  geom_text(data = num_auc_per_db, aes(x = 0.5, y = 4750, label = paste0("n = ", formatC(n, format = "d", big.mark = ",")))) +
-  scale_y_continuous(breaks = seq(0, 5000, by = 500), labels = seq(0, 5000, by = 500)) +
-  labs(x = "AUC IC50", y = "Frequency", title = "Distributions of AUC IC50 values for all drugs in each dataset (filtered by matching)")
-aucic50_per_db_dist
-# ggsave("./gcn_denise/pozdeyev_aucic50_per_db_dist.png", aucic50_per_db_dist, device = "png", dpi = 450, width = 12, height = 6, units = "in")
-
-aucec50_per_db_dist <- ggplot(data = auc) +
-  facet_wrap(~ Database) +
-  geom_histogram(aes(x = AUC_EC50, fill = Database), color = "black", alpha = 0.7, binwidth = 0.025, boundary = 0, closed = "left") +
-  scale_fill_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
-  guides(fill = "none") +
-  geom_text(data = num_auc_per_db, aes(x = 0.5, y = 4750, label = paste0("n = ", formatC(n, format = "d", big.mark = ",")))) +
-  scale_y_continuous(breaks = seq(0, 5000, by = 500), labels = seq(0, 5000, by = 500)) +
-  labs(x = "AUC EC50", y = "Frequency", title = "Distributions of AUC EC50 values for all drugs in each dataset (filtered by matching)")
-aucec50_per_db_dist
-# ggsave("./gcn_denise/pozdeyev_aucec50_per_db_dist.png", aucec50_per_db_dist, device = "png", dpi = 450, width = 12, height = 6, units = "in")
-```

### 2019-03-25 19Q1.Rmd
update poz to use unique CCLs as rows

@@
 
-# Accout for cell line aliases and missing histologies
+# Account for cell line aliases and missing histologies
 auc_unmatched_na_histologies <- read.delim("./data_munging/pozdeyev2016/auc_unmatched_na_histologies.csv", sep = ",", row.names = 1)
@@
 ccle_poz <- merge(ccl_histologies, ccle_poz, by = "Cell_line", all.y = TRUE)
+ccle_poz$InCCLE <- 1
+ccle_poz$InCTRP <- 0
+ccle_poz$InGDSC <- 0
+
 # ccle_test <- merge(select(ccle_poz, Drug_name, Cell_line, AUC_IC50), select(filter(auc, Database == "CCLE"), Drug_name, Cell_line, AUC_IC50), by = c("Drug_name", "Cell_line"), suffixes = c("_unmatched", "_matched_all_pairs"), all = TRUE)
@@
 ctrp_poz <- merge(ccl_histologies, ctrp_poz, by = "Cell_line", all.y = TRUE)
+ctrp_poz$InCCLE <- 0
+ctrp_poz$InCTRP <- 1
+ctrp_poz$InGDSC <- 0
 # ctrp_test <- merge(select(ctrp_poz, Drug_name, Cell_line, AUC_IC50), select(filter(auc, Database == "CTRP"), Drug_name, Cell_line, AUC_IC50), by = c("Drug_name", "Cell_line"), suffixes = c("_unmatched", "_matched_all_pairs"), all = TRUE)
@@
 gdsc_poz <- merge(ccl_histologies, gdsc_poz, by = "Cell_line", all.y = TRUE)
+gdsc_poz$InCCLE <- 0
+gdsc_poz$InCTRP <- 0
+gdsc_poz$InGDSC <- 1
 # gdsc_test <- merge(select(gdsc_poz, Drug_name, Cell_line, AUC_IC50), select(filter(auc, Database == "GDSC"), Drug_name, Cell_line, AUC_IC50), by = c("Drug_name", "Cell_line"), suffixes = c("_unmatched", "_matched_all_pairs"), all = TRUE)
@@
 auc_unmatched <- bind_rows(ccle_poz, ctrp_poz, gdsc_poz)
-auc_unmatched$AUC_EC50 <- as.numeric(as.character(auc_unmatched$AUC_EC50))
+# auc_unmatched$AUC_EC50 <- as.numeric(as.character(auc_unmatched$AUC_EC50))
 auc_unmatched$AUC_IC50 <- as.numeric(as.character(auc_unmatched$AUC_IC50))
-auc_unmatched$sample_ID <- with(auc_unmatched, paste(Database, Cell_line, Histology, sep = "_"))
+# auc_unmatched$sample_ID <- with(auc_unmatched, paste(Database, Cell_line, Histology, sep = "_"))
+auc_unmatched$Database_Drug_name <- with(auc_unmatched, paste(Database, Drug_name, sep = "_"))
+
 num_auc_per_db_unmatched <- auc_unmatched %>% count(Database)
@@
 # Create merged dataset with sample_ids in the rows and drugs across the columns
-auc_unmatched_wide <- dcast(auc_unmatched, Database + Cell_line + Histology + sample_ID + CCLE_ccl_name + Broad_ID ~ Drug_name, value.var = "AUC_IC50", fun.aggregate = mean, fill = 1000000)
-auc_unmatched_wide[, 7:ncol(auc_unmatched_wide)] <- auc_unmatched_wide[, 7:ncol(auc_unmatched_wide)] %>% replace_with_na_all(condition = ~.x == 1000000)
-# write.csv.gz(auc_unmatched_wide, file = "./data_munging/pozdeyev2016/merged_auc_v20190319.2.csv.gz", row.names = FALSE, na = "NA")
+auc_unmatched_wide <- dcast(auc_unmatched, Cell_line + Histology + CCLE_ccl_name + Broad_ID + InCCLE + InCTRP + InGDSC ~ Database_Drug_name, value.var = "AUC_IC50", fun.aggregate = mean, fill = 1000000)
+auc_unmatched_wide[, 8:ncol(auc_unmatched_wide)] <- auc_unmatched_wide[, 8:ncol(auc_unmatched_wide)] %>% replace_with_na_all(condition = ~.x == 1000000)
+# auc_unmatched_wide <- aggregate(. ~ colnames(auc_unmatched_wide)[c(1:4)], data = auc_unmatched_wide, FUN = na.omit, na.action = "na.pass")
+# write.csv.gz(auc_unmatched_wide, file = "./data_munging/pozdeyev2016/merged_auc_vCHANGEDATE.3.csv.gz", row.names = FALSE, na = "NA")
+```
+
+```{r}
+
 ```
@@
 
-Plots:
-```{r}
+Exploratory plots:
+```{r, eval=FALSE}
 futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")

### 2019-03-26 19Q1.Rmd

@@
 ccle_poz <- merge(ccl_histologies, ccle_poz, by = "Cell_line", all.y = TRUE)
-ccle_poz$InCCLE <- 1
-ccle_poz$InCTRP <- 0
-ccle_poz$InGDSC <- 0
+ccle_poz$InCCLE <- "1"
+ccle_poz$InCTRP <- ""
+ccle_poz$InGDSC <- ""
 
@@
 ctrp_poz <- merge(ccl_histologies, ctrp_poz, by = "Cell_line", all.y = TRUE)
-ctrp_poz$InCCLE <- 0
-ctrp_poz$InCTRP <- 1
-ctrp_poz$InGDSC <- 0
+ctrp_poz$InCCLE <- ""
+ctrp_poz$InCTRP <- "1"
+ctrp_poz$InGDSC <- ""
 # ctrp_test <- merge(select(ctrp_poz, Drug_name, Cell_line, AUC_IC50), select(filter(auc, Database == "CTRP"), Drug_name, Cell_line, AUC_IC50), by = c("Drug_name", "Cell_line"), suffixes = c("_unmatched", "_matched_all_pairs"), all = TRUE)
@@
 gdsc_poz <- merge(ccl_histologies, gdsc_poz, by = "Cell_line", all.y = TRUE)
-gdsc_poz$InCCLE <- 0
-gdsc_poz$InCTRP <- 0
-gdsc_poz$InGDSC <- 1
+gdsc_poz$InCCLE <- ""
+gdsc_poz$InCTRP <- ""
+gdsc_poz$InGDSC <- "1"
 # gdsc_test <- merge(select(gdsc_poz, Drug_name, Cell_line, AUC_IC50), select(filter(auc, Database == "GDSC"), Drug_name, Cell_line, AUC_IC50), by = c("Drug_name", "Cell_line"), suffixes = c("_unmatched", "_matched_all_pairs"), all = TRUE)
@@
 # auc_unmatched$sample_ID <- with(auc_unmatched, paste(Database, Cell_line, Histology, sep = "_"))
-auc_unmatched$Database_Drug_name <- with(auc_unmatched, paste(Database, Drug_name, sep = "_"))
+auc_unmatched$Drug_name_Database <- with(auc_unmatched, paste(Drug_name, Database, sep = "_"))
 
@@
 # Create merged dataset with sample_ids in the rows and drugs across the columns
-auc_unmatched_wide <- dcast(auc_unmatched, Cell_line + Histology + CCLE_ccl_name + Broad_ID + InCCLE + InCTRP + InGDSC ~ Database_Drug_name, value.var = "AUC_IC50", fun.aggregate = mean, fill = 1000000)
-auc_unmatched_wide[, 8:ncol(auc_unmatched_wide)] <- auc_unmatched_wide[, 8:ncol(auc_unmatched_wide)] %>% replace_with_na_all(condition = ~.x == 1000000)
-# auc_unmatched_wide <- aggregate(. ~ colnames(auc_unmatched_wide)[c(1:4)], data = auc_unmatched_wide, FUN = na.omit, na.action = "na.pass")
+auc_unmatched_wide <- dcast(auc_unmatched, Cell_line + Histology + CCLE_ccl_name + Broad_ID + InCCLE + InCTRP + InGDSC ~ Drug_name_Database, value.var = "AUC_IC50", fun.aggregate = mean, fill = 1000000)
+auc_unmatched_wide[auc_unmatched_wide == 1000000] <- ""
+auc_unmatched_wide <- auc_unmatched_wide %>% group_by(Cell_line, Histology, CCLE_ccl_name, Broad_ID) %>% summarise_all(funs(trimws(paste(., collapse = ''))))
+auc_unmatched_wide$InCCLE[auc_unmatched_wide == ""] <- 0
+auc_unmatched_wide$InCTRP[auc_unmatched_wide == ""] <- 0
+auc_unmatched_wide$InGDSC[auc_unmatched_wide == ""] <- 0
+auc_unmatched_wide[auc_unmatched_wide == ""] <- NA
+
 # write.csv.gz(auc_unmatched_wide, file = "./data_munging/pozdeyev2016/merged_auc_vCHANGEDATE.3.csv.gz", row.names = FALSE, na = "NA")
@@
 ```{r}
-
+# test <- auc_unmatched_wide_test$InCCLE
+# rm_numerics <- function(x) {
+#   col_new <- c()
+#   for(i in 1:length(x))
+#     print(i)
+#     x_unlist <- unlist(x[i])
+#     print(x_unlist)
+#     x_new <- ifelse(is.na(x_unlist[1]), 1000000, x_unlist[1])
+#     print(x_new)
+#     col_new <- c(col_new, x_new)
+#     print(col_new)
+#   return(col_new)
+# }
+# test2 <- rm_numerics(test)
 ```

### 2019-03-27 19Q1.Rmd

@@
 
-## Denise's GCN dataframes
-
-Code for Denise's graph convolutional networks analyses (see meeting notes from 6 March 2019).
-- Convert drug/compound names to all capitalized for harmonization.
-- Convert all cell line histologies to lower case with words separated by an underscore
-- Maintain same rows across all four data frames, filling with NAs as necessary
-- For each dataframe, maintain same columns for all three source datasets
-- Columns in final dataframes: `source`, `source_ccl_name`, `source_histology`, `sample_ID`, and `genes/compounds/mutations[p]`
-
-### AUC
-
-Column descriptions for `pgx_all_auc`:
-
-- `source`: the dataset from which the data comes from (either CCLE, CTRP, or GDSC)
-- `source_ccl_name`: the name of the cancer cell line (CCL) included in the source dataset
-    - Note that all CCLs (excluding matched normal tissues and "merged" CCLs) from the CCLE dataset (N = 1,645) were included in `pgx_all_auc` for imputation
-- `source_histology`: the general histology/tissue type of the CCL
-- `sample_ID`: custom identifiers for our datasets that are concatenations of the `source`, `source_ccl_name`, and `source_histology`
-- `CCLE_ccl_name`: the cell line name using CCLE nomenclature, which is a concatenation of the cell line name with the CCLE-annotated histology in all caps, separated by underscores
-- `Broad_ID`: the custom identifiers (formatted as ACH-######) used by the Broad's Cancer Dependency Map project to ease cell line name harmonization efforts 
-- All other columns: compound and drug names that were screened in at least one CCL in at least one source dataset
-    - NA values indictate that compound wasn't screened in the respective CCL in the respective source dataset
-
-```{r, eval=TRUE}
-ccle <- read.delim("./data_munging/pharmacogenomics_raw_files/CCLE_NP24.2009_Drug_data_2015.02.24_20190307.csv", sep = ",", header  = TRUE, check.names = FALSE)
-ctrp <- read.delim("./data_munging/pharmacogenomics_raw_files/CTRP_v20.data.curves_post_qc.txt.gz", sep = "\t", header  = TRUE, check.names = FALSE)
-gdsc <- read.delim("./data_munging/pharmacogenomics_raw_files/GDSC_v17.3_fitted_dose_response_20190306.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
-
-# CCLE
-## Note that ActArea is NOT an AUC value
-ccle_filt <- ccle[, c("CCLE Cell Line Name", "ActArea", "Compound")]
-ccle_filt$source_ccl_name <- sapply(strsplit(as.character(ccle_filt$`CCLE Cell Line Name`), split = "_"), function(x) x[1])
-ccle_filt$source_histology <- tolower(gsub("^[a-z0-9]*_", "", ccle_filt$`CCLE Cell Line Name`, ignore.case = TRUE))
-ccle_filt$source_histology <- ifelse(ccle_filt$`CCLE Cell Line Name` == ccle_filt$source_ccl_name, NA, ccle_filt$source_histology)
-colnames(ccle_filt)[colnames(ccle_filt) == "CCLE Cell Line Name"] <- "CCLE_ccl_name"
-ccle_filt <- merge(select(ccl_info, source, source_ccl_name, source_histology, sample_ID, CCLE_ccl_name, Broad_ID), ccle_filt, by = c("source_ccl_name", "source_histology", "CCLE_ccl_name"), all = TRUE)
-ccle_filt$compound_name <- toupper(ccle_filt$Compound)
-colnames(ccle_filt)[colnames(ccle_filt) == "ActArea"] <- "AUC"
-ccle_auc_long <- select(ccle_filt, source, source_ccl_name, source_histology, sample_ID, CCLE_ccl_name, Broad_ID, compound_name, AUC)
-ccle_auc <- dcast(ccle_auc_long, source + source_ccl_name + source_histology + sample_ID + CCLE_ccl_name + Broad_ID ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
-ccle_auc[, 7:ncol(ccle_auc)] <- ccle_auc[, 7:ncol(ccle_auc)] %>% replace_with_na_all(condition = ~.x == 10000)
-
-# CTRP
-## area_under_curve: integrated area under the sigmoid-fit concentration-response curve
-ctrp_filt <- ctrp[, c("experiment_id", "area_under_curve", "master_cpd_id")]
-ctrp_meta_ccl <- select(read.delim("./data_munging/pharmacogenomics_raw_files/CTRP_v20.meta.per_cell_line_20190306.txt"), master_ccl_id, ccl_name, ccle_primary_site)
-ctrp_meta_exp <- select(read.delim("./data_munging/pharmacogenomics_raw_files/CTRP_v20.meta.per_experiment_20190306.txt"), experiment_id, master_ccl_id)
-ctrp_meta_cpd <- select(read.delim("./data_munging/pharmacogenomics_raw_files/CTRP_v20.meta.per_compound_20190306.txt"), master_cpd_id, cpd_name)
-ctrp_keep <- merge(merge(ctrp_meta_ccl, ctrp_meta_exp, by = "master_ccl_id", all = TRUE), merge(ctrp_meta_cpd, ctrp_filt, by = "master_cpd_id", all = TRUE), by = "experiment_id", all = TRUE)
-ctrp_keep$ccl_name <- gsub("-", "", ctrp_keep$ccl_name, ignore.case = TRUE)
-ctrp_keep$cpd_name <- toupper(ctrp_keep$cpd_name)
-ctrp_keep$ccle_primary_site <- ifelse(as.character(ctrp_keep$ccle_primary_site) == "", NA, as.character(ctrp_keep$ccle_primary_site))
-ctrp_auc_long <- select(ctrp_keep, ccl_name, ccle_primary_site, cpd_name, area_under_curve)
-colnames(ctrp_auc_long) <- c("source_ccl_name", "source_histology", "compound_name", "AUC")
-ctrp_auc_long$source <- "CTRP"
-ctrp_auc_long$sample_ID <- with(ctrp_auc_long, paste(source, source_ccl_name, source_histology, sep = "_"))
-ctrp_auc_long <- merge(ctrp_auc_long, select(ccl_info, source_ccl_name, source_histology, CCLE_ccl_name, Broad_ID), by = c("source_ccl_name", "source_histology"), all.x = TRUE)
-ctrp_auc_long_div <- ctrp_auc_long
-ctrp_auc_long_div$AUC <- ctrp_auc_long_div$AUC / 100
-ctrp_auc <- dcast(ctrp_auc_long, source + source_ccl_name + source_histology + sample_ID + CCLE_ccl_name + Broad_ID ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
-ctrp_auc[, 7:ncol(ctrp_auc)] <- ctrp_auc[, 7:ncol(ctrp_auc)] %>% replace_with_na_all(condition = ~.x == 10000)
-
-# GDSC
-gdsc_meta_ccl <- select(read.delim("./data_munging/pharmacogenomics_raw_files/GDSC_Cell_Lines_Details.csv", sep = ","), Line, Site)
-## For following 4 Lines, Site == "NS"
-## Assigned new Sites by looking up cell lines in GDSC cell line portal (https://www.cancerrxgene.org/translation/CellLine#t-all)
-gdsc_meta_ccl$Site[gdsc_meta_ccl$Line == "COR-L321"] <- "lung"
-gdsc_meta_ccl$Site[gdsc_meta_ccl$Line == "SU-DHL-8"] <- "haematopoietic_and_lymphoid_tissue"
-gdsc_meta_ccl$Site[gdsc_meta_ccl$Line == "CRO-AP3"] <- "haematopoietic_and_lymphoid_tissue"
-gdsc_meta_ccl$Site[gdsc_meta_ccl$Line == "Hep_3B2_1-7"] <- "liver"
-## For tollowing line, Site did not match CCLE notation, so I changed it to CCLE notation
-gdsc_meta_ccl$Site[gdsc_meta_ccl$Line == "SW13"] <- "adrenal_cortex"
-gdsc_filt <- gdsc[, c("CELL_LINE_NAME", "DRUG_NAME", "AUC")]
-gdsc_filt$DRUG_NAME <- toupper(gdsc_filt$DRUG_NAME)
-colnames(gdsc_filt)[colnames(gdsc_filt) ==  "CELL_LINE_NAME"] <- "Line"
-gdsc_filt <- merge(gdsc_filt, gdsc_meta_ccl, by = "Line", all = TRUE)
-gdsc_filt$Line <- gsub("-", "", gdsc_filt$Line, ignore.case = TRUE)
-gdsc_auc_long <- select(gdsc_filt, Line, Site, DRUG_NAME, AUC)
-colnames(gdsc_auc_long) <- c("source_ccl_name", "source_histology", "compound_name", "AUC")
-gdsc_auc_long$source <- "GDSC"
-gdsc_auc_long$sample_ID <- with(gdsc_auc_long, paste(source, source_ccl_name, source_histology, sep = "_"))
-gdsc_auc_long$source_histology <- as.character(gdsc_auc_long$source_histology)
-gdsc_auc_long <- merge(gdsc_auc_long, select(ccl_info, source_ccl_name, source_histology, CCLE_ccl_name, Broad_ID), by = c("source_ccl_name", "source_histology"), all.x = TRUE)
-gdsc_auc <- dcast(gdsc_auc_long, source + source_ccl_name + source_histology + sample_ID + CCLE_ccl_name + Broad_ID ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
-gdsc_auc[, 7:ncol(gdsc_auc)] <- gdsc_auc[, 7:ncol(gdsc_auc)] %>% replace_with_na_all(condition = ~.x == 10000)
-
-# Bind all AUC
-pgx_auc_list <- list(ccle_auc, ctrp_auc, gdsc_auc)
-pgx_auc_names <- unique(unlist(lapply(pgx_auc_list, names)))
-pgx_all_auc <- do.call(rbind, c(lapply(pgx_auc_list, function(x) data.frame(c(x, sapply(setdiff(pgx_auc_names, names(x)), function(y) NA)), check.names = FALSE))))
-# saveRDS(pgx_all_auc, "./data_munging/19Q1/pgx_all_auc.rds", compress = "xz")
-# write.csv.gz(pgx_all_auc, "./data_munging/19Q1/pgx_all_auc.csv.gz", row.names = FALSE)
-```
-
-Compare histology representation for CCLE, CTRP, and GDSC:
-```{r, eval=FALSE}
-sort(unique(na.omit(ccle_auc_long$source_histology)))
-sort(unique(na.omit(ctrp_auc_long$source_histology)))
-sort(unique(na.omit(gdsc_auc_long$source_histology)))
-
-setdiff(unique(na.omit(ccle_auc_long$source_histology)), unique(na.omit(gdsc_auc_long$source_histology)))
-setdiff(unique(na.omit(gdsc_auc_long$source_histology)), unique(na.omit(ctrp_auc_long$source_histology)))
-```
-
-### Summary figures
+## CRISPR
 
 ```{r, eval=FALSE}
-hist_auc_ccle <- ggplot(data = ccle_auc_long) +
-  geom_histogram(mapping = aes(x = AUC, fill = source), color = "black", binwidth = 0.25, boundary = 0, closed = "left") +
-  scale_x_continuous(breaks = seq(0, 8, by = 1), labels = seq(0, 8, by = 1)) +
-  scale_fill_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
-  labs(title = "Distributions of AUC/ActArea values for all drug-cell line combinations", subtitle = "CCLE", y = "Frequency", x = "ActArea") +
-  guides(fill = FALSE)
-hist_auc_ctrp <- ggplot(data = ctrp_auc_long_div) +
-  geom_histogram(mapping = aes(x = AUC, fill = source), color = "black", binwidth = 0.0125, boundary = 0, closed = "left") +
-  scale_x_continuous(breaks = seq(0, 0.3, by = 0.025), labels = seq(0, 0.3, by = 0.025)) +
-  scale_fill_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
-  labs(y = "Frequency", x = "AUC", subtitle = "CTRP", caption = "CTRP AUC values were divided by 100 prior to plotting.") +
-  guides(fill = FALSE)
-hist_auc_gdsc <- ggplot(data = gdsc_auc_long) +
-  geom_histogram(mapping = aes(x = AUC, fill = source), color = "black", binwidth = 0.025, boundary = 0, closed = "left") +
-  scale_x_continuous(breaks = seq(0, 1, by = 0.1), labels = seq(0, 1, by = 0.1)) +
-  scale_fill_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
-  labs(y = "Frequency", x = "AUC", subtitle = "GDSC") +
-  guides(fill = FALSE)
-hist_auc_ccle <- ggplot_gtable(ggplot_build(hist_auc_ccle))
-hist_auc_ctrp <- ggplot_gtable(ggplot_build(hist_auc_ctrp))
-hist_auc_gdsc <- ggplot_gtable(ggplot_build(hist_auc_gdsc))
-p_maxWidth <-  grid::unit.pmax(hist_auc_ccle$widths[2:3], hist_auc_ctrp$widths[2:3], hist_auc_gdsc$widths[2:3])
-hist_auc_ccle$widths[2:3] <- p_maxWidth
-hist_auc_ctrp$widths[2:3] <- p_maxWidth
-hist_auc_gdsc$widths[2:3] <- p_maxWidth
-hist_auc_all <- cowplot::plot_grid(hist_auc_ccle, hist_auc_ctrp, hist_auc_gdsc, nrow = 3, rel_heights = c(9, 9, 8))
-hist_auc_all
-# ggsave("./gcn_denise/hist_auc_all.png", hist_auc_all, device = "png", dpi = 450, width = 12, height = 8, units = "in")
-
-futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
-venn_ccl <- venn.diagram(list("CCLE" = unique(na.omit(ccl_info$source_ccl_name)), "CTRP" = unique(ctrp_auc_long$source_ccl_name), "GDSC" = unique(gdsc_auc_long$source_ccl_name)), resolution = 5000, main = "Overlap of cancer cell lines (CCLs) screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 0), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
-# png("./gcn_denise/venn_ccl.png")
-# grid.newpage()
-# grid.draw(venn_ccl)
-# dev.off()
-
-futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
-venn_histology <- venn.diagram(list("CCLE" = unique(na.omit(ccle_auc_long$source_histology)), "CTRP" = unique(na.omit(ctrp_auc_long$source_histology)), "GDSC" = unique(na.omit(gdsc_auc_long$source_histology))), resolution = 5000, main = "Overlap of cancer cell line histologies screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(0, 0, 0), cat.dist = c(0.001, 0.001, -0.01), cat.cex = 1.5, cex = 1, filename = NULL)
-# png("./gcn_denise/venn_histology.png")
-# grid.newpage()
-# grid.draw(venn_histology)
-# dev.off()
-
-futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
-venn_compound <- venn.diagram(list("CCLE" = unique(na.omit(ccle_auc_long$compound_name)), "CTRP" = unique(na.omit(ctrp_auc_long$compound_name)), "GDSC" = unique(na.omit(gdsc_auc_long$compound_name))), resolution = 5000, main = "Overlap of compounds screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.001, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
-# png("./gcn_denise/venn_compound.png")
-# grid.newpage()
-# grid.draw(venn_compound)
-# dev.off()
+crispr <- read.delim("./data_munging/19Q1/gene_effect_corrected_20190305.csv.gz", sep = ",", check.names = FALSE, header = TRUE)
 ```
@@
 
-```{r}
+```{r, eval=FALSE}
 ccle_poz <- read.delim("./data_munging/pozdeyev2016/CCLE_drug_response_metrics.csv.gz", sep = ",")
@@
 auc_unmatched <- bind_rows(ccle_poz, ctrp_poz, gdsc_poz)
+auc_unmatched$WasDrugScreened <- 1
 # auc_unmatched$AUC_EC50 <- as.numeric(as.character(auc_unmatched$AUC_EC50))
@@
 # Create merged dataset with sample_ids in the rows and drugs across the columns
-auc_unmatched_wide <- dcast(auc_unmatched, Cell_line + Histology + CCLE_ccl_name + Broad_ID + InCCLE + InCTRP + InGDSC ~ Drug_name_Database, value.var = "AUC_IC50", fun.aggregate = mean, fill = 1000000)
+auc_unmatched_wide <- dcast(auc_unmatched, Cell_line + Histology + CCLE_ccl_name + Broad_ID + InCCLE + InCTRP + InGDSC + WasDrugScreened ~ Drug_name_Database, value.var = "AUC_IC50", fun.aggregate = mean, fill = 1000000)
 auc_unmatched_wide[auc_unmatched_wide == 1000000] <- ""
-auc_unmatched_wide <- auc_unmatched_wide %>% group_by(Cell_line, Histology, CCLE_ccl_name, Broad_ID) %>% summarise_all(funs(trimws(paste(., collapse = ''))))
-auc_unmatched_wide$InCCLE[auc_unmatched_wide == ""] <- 0
-auc_unmatched_wide$InCTRP[auc_unmatched_wide == ""] <- 0
-auc_unmatched_wide$InGDSC[auc_unmatched_wide == ""] <- 0
+auc_unmatched_wide <- auc_unmatched_wide %>% group_by(Cell_line, Histology, CCLE_ccl_name, Broad_ID, WasDrugScreened) %>% summarise_all(funs(trimws(paste(., collapse = ""))))
+auc_unmatched_wide$InCCLE[auc_unmatched_wide$InCCLE == ""] <- 0
+auc_unmatched_wide$InCTRP[auc_unmatched_wide$InCTRP == ""] <- 0
+auc_unmatched_wide$InGDSC[auc_unmatched_wide$InGDSC == ""] <- 0
 auc_unmatched_wide[auc_unmatched_wide == ""] <- NA
+auc_unmatched_wide <- add_column(auc_unmatched_wide, WasCRISPRScreened = NA, .after = "WasDrugScreened")
+auc_unmatched_wide <- add_column(auc_unmatched_wide, HasCopyNumberData = NA, .after = "WasCRISPRScreened")
+auc_unmatched_wide <- add_column(auc_unmatched_wide, HasGeneExpressionData = NA, .after = "WasCRISPRScreened")
+auc_unmatched_wide <- add_column(auc_unmatched_wide, HasMutationData = NA, .after = "WasCRISPRScreened")
 
-# write.csv.gz(auc_unmatched_wide, file = "./data_munging/pozdeyev2016/merged_auc_vCHANGEDATE.3.csv.gz", row.names = FALSE, na = "NA")
+ccls_not_drugscreened <- filter(ccl_histologies, Cell_line %in% setdiff(ccl_histologies$Cell_line, auc_unmatched_wide$Cell_line))
+ccls_not_drugscreened$WasDrugScreened <- 0
+
+maf_df <- readRDS("./data_munging/19Q1/maf_df_19Q1.rds")
+cn_melt <- readRDS("./data_munging/19Q1/cn_melt_19Q1.rds")
+ge_melt <- readRDS("./data_munging/19Q1/ge_melt_19Q1.rds")
+
+auc_all_ccls <- bind_rows(auc_unmatched_wide, ccls_not_drugscreened)
+auc_all_ccls$HasMutationData <- with(auc_all_ccls, ifelse(Broad_ID %in% maf_df$Broad_ID, 1, 0))
+auc_all_ccls$HasCopyNumberData <- with(auc_all_ccls, ifelse(Broad_ID %in% cn_melt$Broad_ID, 1, 0))
+auc_all_ccls$HasGeneExpressionData <- with(auc_all_ccls, ifelse(Broad_ID %in% ge_melt$Broad_ID, 1, 0))
+auc_all_ccls$WasCRISPRScreened <- with(auc_all_ccls, ifelse(Broad_ID %in% crispr_meta$Broad_ID, 1, 0))
+auc_all_ccls$InCCLE <- with(auc_all_ccls, ifelse(WasDrugScreened == 0, 0, InCCLE))
+auc_all_ccls$InCTRP <- with(auc_all_ccls, ifelse(WasDrugScreened == 0, 0, InCTRP))
+auc_all_ccls$InGDSC <- with(auc_all_ccls, ifelse(WasDrugScreened == 0, 0, InGDSC))
+auc_all_ccls[, -c(1:4)] <- apply(auc_all_ccls[, -c(1:4)], MARGIN = 2, FUN = as.numeric)
+auc_all_ccls <- subset(auc_all_ccls, !(WasDrugScreened == 0 & WasCRISPRScreened == 0 & HasMutationData == 0 & HasGeneExpressionData == 0 & HasCopyNumberData == 0))
+# write.csv.gz(auc_all_ccls, file = "./data_munging/pozdeyev2016/merged_auc_v20190327.3.csv.gz", row.names = FALSE, na = "NA")
 ```
@@
 ```{r}
-# test <- auc_unmatched_wide_test$InCCLE
-# rm_numerics <- function(x) {
-#   col_new <- c()
-#   for(i in 1:length(x))
-#     print(i)
-#     x_unlist <- unlist(x[i])
-#     print(x_unlist)
-#     x_new <- ifelse(is.na(x_unlist[1]), 1000000, x_unlist[1])
-#     print(x_new)
-#     col_new <- c(col_new, x_new)
-#     print(col_new)
-#   return(col_new)
-# }
-# test2 <- rm_numerics(test)
+# test <- as.data.frame(table(auc_all_ccls$Cell_line))
+# test <- filter(auc_all_ccls, Cell_line %in% c("KMH2", "MS1", "TT"))[, 1:12]
+
+length(unique(sapply(strsplit(as.character(colnames(auc_all_ccls)[13:length(colnames(auc_all_ccls))]), split = "_"), function(x) x[1])))
 ```
+
+### README
 
@@
 Column descriptions in merged_auc_v20190319.1.csv.gz:
-- `Database`: the dataset from which the data comes from (either CCLE, CTRP, or GDSC)
-- `Cell_line`: the name of the cancer cell line (CCL), harmonized across datasets by Pozdeyev et al. (2016)
-- `Histology`: the general histology/tissue type of the CCL according to the CCLE annotations (see DepMap-2019q1-celllines_v2.csv file from the DepMap Data Portal)
-- `sample_ID`: custom identifiers for this dataset that are concatenations of the `Database`, `Cell_line`, and `Histology`, separated by underscores
-- `CCLE_ccl_name`: the cell line name using CCLE nomenclature, which is a concatenation of the cell line name with the CCLE-annotated histology in all caps, separated by underscores
-- `Broad_ID`: the custom identifiers (formatted as ACH-######) used by the Broad's Cancer Dependency Map project to ease cell line name harmonization efforts 
-- All other columns: compound and drug names that were screened in at least one CCL in at least one database
+- Cell_line: the name of the cancer cell line (CCL), harmonized across datasets by Pozdeyev et al. (2016)
+- Histology: the general histology/tissue type of the CCL according to the CCLE annotations (see DepMap-2019q1-celllines_v2.csv file from the DepMap Data Portal)
+- CCLE_ccl_name: the cell line name using CCLE nomenclature, which is a concatenation of the cell line name with the CCLE-annotated histology in all caps, separated by underscores
+- Broad_ID: the custom identifiers (formatted as ACH-######) used by the Broad's Cancer Dependency Map project to ease cell line name harmonization efforts 
+- WasDrugScreened: 1 means the cell was screened in at least one pharmacogenomic screens, and 0 means it was not screened in any of the pharmacogenomic screens
+- WasCRISPRScreened: 1 means the cell line was screened in the Avana CRISPR screen, and 0 means it was not
+- HasMutationData: 1 means the cell line had at least one recorded mutation in the MAF file (see file version below), and 0 means it was not annotated in the MAF file
+- HasGeneExpressionData: 1 means gene expression data is available for the cell line (see file version below), and 0 means it does not have gene expression information
+- HasCopyNumberData: 1 means copy number data is available for the cell line (see file version below), and 0 means it does not have copy number information
+- InCCLE: 1 means the cell line was screened in CCLE, 0 means it was not
+- InCTRP: 1 means the cell line was screened in CTRP, 0 means it was not
+- InGDSC: 1 means the cell line was screened in GDSC, 0 means it was not
+- All other columns: compound and drug names that were screened in at least one CCL in at least one database, formatted as Drug_DatabaseName
     - NA values indictate that compound wasn't screened in the respective CCL in the respective source dataset
     - Values are in AUC_IC50, the area under rhe dose response curve calculated from IC50 model
+
+merged_auc_v20190319.1.csv.gz
+merged_auc_v20190319.2.csv.gz:
+- NAs in Histology column (excluding most of the cell lines indicated as being from a "collaborator" in CTRP) hand-curated by searches in DepMap, COSMIC, Cellosaurus, ATCC, canSAR Black, and Cell Model Passports
+merged_auc_v20190327.3.csv.gz:
+- Reformatted to have only unique cell lines in rows
+- Cancer cell lines screened in more than one database have multiple AUC columns (column names are formatted as Drug_DatabaseName)
+- Added information on binary presence/absencee of omic annotations for each cell line (i.e. mutations, copy number, gene expression)
+- Added binary columns indicating presence in CCLE, CTRP, GDSC, drug screens in general (in 1, 2, or 3), and the Avana CRISPR screen
+- Added cell lines that have at least one type of omic data but are not in the CRISPR or pharmacogenomic screens
 
@@
 ```
+
+# Denise's GCN dataframes (Deprected)
+
+--------------------------------------------------------------------------------
+
+Code for Denise's graph convolutional networks analyses (see meeting notes from 6 March 2019).
+- Convert drug/compound names to all capitalized for harmonization.
+- Convert all cell line histologies to lower case with words separated by an underscore
+- Maintain same rows across all four data frames, filling with NAs as necessary
+- For each dataframe, maintain same columns for all three source datasets
+- Columns in final dataframes: `source`, `source_ccl_name`, `source_histology`, `sample_ID`, and `genes/compounds/mutations[p]`
+
+## AUC
+
+Column descriptions for `pgx_all_auc`:
+
+- `source`: the dataset from which the data comes from (either CCLE, CTRP, or GDSC)
+- `source_ccl_name`: the name of the cancer cell line (CCL) included in the source dataset
+    - Note that all CCLs (excluding matched normal tissues and "merged" CCLs) from the CCLE dataset (N = 1,645) were included in `pgx_all_auc` for imputation
+- `source_histology`: the general histology/tissue type of the CCL
+- `sample_ID`: custom identifiers for our datasets that are concatenations of the `source`, `source_ccl_name`, and `source_histology`
+- `CCLE_ccl_name`: the cell line name using CCLE nomenclature, which is a concatenation of the cell line name with the CCLE-annotated histology in all caps, separated by underscores
+- `Broad_ID`: the custom identifiers (formatted as ACH-######) used by the Broad's Cancer Dependency Map project to ease cell line name harmonization efforts 
+- All other columns: compound and drug names that were screened in at least one CCL in at least one source dataset
+    - NA values indictate that compound wasn't screened in the respective CCL in the respective source dataset
+
+```{r, eval=TRUE}
+ccle <- read.delim("./data_munging/pharmacogenomics_raw_files/CCLE_NP24.2009_Drug_data_2015.02.24_20190307.csv", sep = ",", header  = TRUE, check.names = FALSE)
+ctrp <- read.delim("./data_munging/pharmacogenomics_raw_files/CTRP_v20.data.curves_post_qc.txt.gz", sep = "\t", header  = TRUE, check.names = FALSE)
+gdsc <- read.delim("./data_munging/pharmacogenomics_raw_files/GDSC_v17.3_fitted_dose_response_20190306.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
+
+# CCLE
+## Note that ActArea is NOT an AUC value
+ccle_filt <- ccle[, c("CCLE Cell Line Name", "ActArea", "Compound")]
+ccle_filt$source_ccl_name <- sapply(strsplit(as.character(ccle_filt$`CCLE Cell Line Name`), split = "_"), function(x) x[1])
+ccle_filt$source_histology <- tolower(gsub("^[a-z0-9]*_", "", ccle_filt$`CCLE Cell Line Name`, ignore.case = TRUE))
+ccle_filt$source_histology <- ifelse(ccle_filt$`CCLE Cell Line Name` == ccle_filt$source_ccl_name, NA, ccle_filt$source_histology)
+colnames(ccle_filt)[colnames(ccle_filt) == "CCLE Cell Line Name"] <- "CCLE_ccl_name"
+ccle_filt <- merge(select(ccl_info, source, source_ccl_name, source_histology, sample_ID, CCLE_ccl_name, Broad_ID), ccle_filt, by = c("source_ccl_name", "source_histology", "CCLE_ccl_name"), all = TRUE)
+ccle_filt$compound_name <- toupper(ccle_filt$Compound)
+colnames(ccle_filt)[colnames(ccle_filt) == "ActArea"] <- "AUC"
+ccle_auc_long <- select(ccle_filt, source, source_ccl_name, source_histology, sample_ID, CCLE_ccl_name, Broad_ID, compound_name, AUC)
+ccle_auc <- dcast(ccle_auc_long, source + source_ccl_name + source_histology + sample_ID + CCLE_ccl_name + Broad_ID ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
+ccle_auc[, 7:ncol(ccle_auc)] <- ccle_auc[, 7:ncol(ccle_auc)] %>% replace_with_na_all(condition = ~.x == 10000)
+
+# CTRP
+## area_under_curve: integrated area under the sigmoid-fit concentration-response curve
+ctrp_filt <- ctrp[, c("experiment_id", "area_under_curve", "master_cpd_id")]
+ctrp_meta_ccl <- select(read.delim("./data_munging/pharmacogenomics_raw_files/CTRP_v20.meta.per_cell_line_20190306.txt"), master_ccl_id, ccl_name, ccle_primary_site)
+ctrp_meta_exp <- select(read.delim("./data_munging/pharmacogenomics_raw_files/CTRP_v20.meta.per_experiment_20190306.txt"), experiment_id, master_ccl_id)
+ctrp_meta_cpd <- select(read.delim("./data_munging/pharmacogenomics_raw_files/CTRP_v20.meta.per_compound_20190306.txt"), master_cpd_id, cpd_name)
+ctrp_keep <- merge(merge(ctrp_meta_ccl, ctrp_meta_exp, by = "master_ccl_id", all = TRUE), merge(ctrp_meta_cpd, ctrp_filt, by = "master_cpd_id", all = TRUE), by = "experiment_id", all = TRUE)
+ctrp_keep$ccl_name <- gsub("-", "", ctrp_keep$ccl_name, ignore.case = TRUE)
+ctrp_keep$cpd_name <- toupper(ctrp_keep$cpd_name)
+ctrp_keep$ccle_primary_site <- ifelse(as.character(ctrp_keep$ccle_primary_site) == "", NA, as.character(ctrp_keep$ccle_primary_site))
+ctrp_auc_long <- select(ctrp_keep, ccl_name, ccle_primary_site, cpd_name, area_under_curve)
+colnames(ctrp_auc_long) <- c("source_ccl_name", "source_histology", "compound_name", "AUC")
+ctrp_auc_long$source <- "CTRP"
+ctrp_auc_long$sample_ID <- with(ctrp_auc_long, paste(source, source_ccl_name, source_histology, sep = "_"))
+ctrp_auc_long <- merge(ctrp_auc_long, select(ccl_info, source_ccl_name, source_histology, CCLE_ccl_name, Broad_ID), by = c("source_ccl_name", "source_histology"), all.x = TRUE)
+ctrp_auc_long_div <- ctrp_auc_long
+ctrp_auc_long_div$AUC <- ctrp_auc_long_div$AUC / 100
+ctrp_auc <- dcast(ctrp_auc_long, source + source_ccl_name + source_histology + sample_ID + CCLE_ccl_name + Broad_ID ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
+ctrp_auc[, 7:ncol(ctrp_auc)] <- ctrp_auc[, 7:ncol(ctrp_auc)] %>% replace_with_na_all(condition = ~.x == 10000)
+
+# GDSC
+gdsc_meta_ccl <- select(read.delim("./data_munging/pharmacogenomics_raw_files/GDSC_Cell_Lines_Details.csv", sep = ","), Line, Site)
+## For following 4 Lines, Site == "NS"
+## Assigned new Sites by looking up cell lines in GDSC cell line portal (https://www.cancerrxgene.org/translation/CellLine#t-all)
+gdsc_meta_ccl$Site[gdsc_meta_ccl$Line == "COR-L321"] <- "lung"
+gdsc_meta_ccl$Site[gdsc_meta_ccl$Line == "SU-DHL-8"] <- "haematopoietic_and_lymphoid_tissue"
+gdsc_meta_ccl$Site[gdsc_meta_ccl$Line == "CRO-AP3"] <- "haematopoietic_and_lymphoid_tissue"
+gdsc_meta_ccl$Site[gdsc_meta_ccl$Line == "Hep_3B2_1-7"] <- "liver"
+## For tollowing line, Site did not match CCLE notation, so I changed it to CCLE notation
+gdsc_meta_ccl$Site[gdsc_meta_ccl$Line == "SW13"] <- "adrenal_cortex"
+gdsc_filt <- gdsc[, c("CELL_LINE_NAME", "DRUG_NAME", "AUC")]
+gdsc_filt$DRUG_NAME <- toupper(gdsc_filt$DRUG_NAME)
+colnames(gdsc_filt)[colnames(gdsc_filt) ==  "CELL_LINE_NAME"] <- "Line"
+gdsc_filt <- merge(gdsc_filt, gdsc_meta_ccl, by = "Line", all = TRUE)
+gdsc_filt$Line <- gsub("-", "", gdsc_filt$Line, ignore.case = TRUE)
+gdsc_auc_long <- select(gdsc_filt, Line, Site, DRUG_NAME, AUC)
+colnames(gdsc_auc_long) <- c("source_ccl_name", "source_histology", "compound_name", "AUC")
+gdsc_auc_long$source <- "GDSC"
+gdsc_auc_long$sample_ID <- with(gdsc_auc_long, paste(source, source_ccl_name, source_histology, sep = "_"))
+gdsc_auc_long$source_histology <- as.character(gdsc_auc_long$source_histology)
+gdsc_auc_long <- merge(gdsc_auc_long, select(ccl_info, source_ccl_name, source_histology, CCLE_ccl_name, Broad_ID), by = c("source_ccl_name", "source_histology"), all.x = TRUE)
+gdsc_auc <- dcast(gdsc_auc_long, source + source_ccl_name + source_histology + sample_ID + CCLE_ccl_name + Broad_ID ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
+gdsc_auc[, 7:ncol(gdsc_auc)] <- gdsc_auc[, 7:ncol(gdsc_auc)] %>% replace_with_na_all(condition = ~.x == 10000)
+
+# Bind all AUC
+pgx_auc_list <- list(ccle_auc, ctrp_auc, gdsc_auc)
+pgx_auc_names <- unique(unlist(lapply(pgx_auc_list, names)))
+pgx_all_auc <- do.call(rbind, c(lapply(pgx_auc_list, function(x) data.frame(c(x, sapply(setdiff(pgx_auc_names, names(x)), function(y) NA)), check.names = FALSE))))
+# saveRDS(pgx_all_auc, "./data_munging/19Q1/pgx_all_auc.rds", compress = "xz")
+# write.csv.gz(pgx_all_auc, "./data_munging/19Q1/pgx_all_auc.csv.gz", row.names = FALSE)
+```
+
+Compare histology representation for CCLE, CTRP, and GDSC:
+```{r, eval=FALSE}
+sort(unique(na.omit(ccle_auc_long$source_histology)))
+sort(unique(na.omit(ctrp_auc_long$source_histology)))
+sort(unique(na.omit(gdsc_auc_long$source_histology)))
+
+setdiff(unique(na.omit(ccle_auc_long$source_histology)), unique(na.omit(gdsc_auc_long$source_histology)))
+setdiff(unique(na.omit(gdsc_auc_long$source_histology)), unique(na.omit(ctrp_auc_long$source_histology)))
+```
+
+## Summary figures
+
+```{r, eval=FALSE}
+hist_auc_ccle <- ggplot(data = ccle_auc_long) +
+  geom_histogram(mapping = aes(x = AUC, fill = source), color = "black", binwidth = 0.25, boundary = 0, closed = "left") +
+  scale_x_continuous(breaks = seq(0, 8, by = 1), labels = seq(0, 8, by = 1)) +
+  scale_fill_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
+  labs(title = "Distributions of AUC/ActArea values for all drug-cell line combinations", subtitle = "CCLE", y = "Frequency", x = "ActArea") +
+  guides(fill = FALSE)
+hist_auc_ctrp <- ggplot(data = ctrp_auc_long_div) +
+  geom_histogram(mapping = aes(x = AUC, fill = source), color = "black", binwidth = 0.0125, boundary = 0, closed = "left") +
+  scale_x_continuous(breaks = seq(0, 0.3, by = 0.025), labels = seq(0, 0.3, by = 0.025)) +
+  scale_fill_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
+  labs(y = "Frequency", x = "AUC", subtitle = "CTRP", caption = "CTRP AUC values were divided by 100 prior to plotting.") +
+  guides(fill = FALSE)
+hist_auc_gdsc <- ggplot(data = gdsc_auc_long) +
+  geom_histogram(mapping = aes(x = AUC, fill = source), color = "black", binwidth = 0.025, boundary = 0, closed = "left") +
+  scale_x_continuous(breaks = seq(0, 1, by = 0.1), labels = seq(0, 1, by = 0.1)) +
+  scale_fill_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
+  labs(y = "Frequency", x = "AUC", subtitle = "GDSC") +
+  guides(fill = FALSE)
+hist_auc_ccle <- ggplot_gtable(ggplot_build(hist_auc_ccle))
+hist_auc_ctrp <- ggplot_gtable(ggplot_build(hist_auc_ctrp))
+hist_auc_gdsc <- ggplot_gtable(ggplot_build(hist_auc_gdsc))
+p_maxWidth <-  grid::unit.pmax(hist_auc_ccle$widths[2:3], hist_auc_ctrp$widths[2:3], hist_auc_gdsc$widths[2:3])
+hist_auc_ccle$widths[2:3] <- p_maxWidth
+hist_auc_ctrp$widths[2:3] <- p_maxWidth
+hist_auc_gdsc$widths[2:3] <- p_maxWidth
+hist_auc_all <- cowplot::plot_grid(hist_auc_ccle, hist_auc_ctrp, hist_auc_gdsc, nrow = 3, rel_heights = c(9, 9, 8))
+hist_auc_all
+# ggsave("./gcn_denise/hist_auc_all.png", hist_auc_all, device = "png", dpi = 450, width = 12, height = 8, units = "in")
+
+futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
+venn_ccl <- venn.diagram(list("CCLE" = unique(na.omit(ccl_info$source_ccl_name)), "CTRP" = unique(ctrp_auc_long$source_ccl_name), "GDSC" = unique(gdsc_auc_long$source_ccl_name)), resolution = 5000, main = "Overlap of cancer cell lines (CCLs) screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 0), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
+# png("./gcn_denise/venn_ccl.png")
+# grid.newpage()
+# grid.draw(venn_ccl)
+# dev.off()
+
+futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
+venn_histology <- venn.diagram(list("CCLE" = unique(na.omit(ccle_auc_long$source_histology)), "CTRP" = unique(na.omit(ctrp_auc_long$source_histology)), "GDSC" = unique(na.omit(gdsc_auc_long$source_histology))), resolution = 5000, main = "Overlap of cancer cell line histologies screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(0, 0, 0), cat.dist = c(0.001, 0.001, -0.01), cat.cex = 1.5, cex = 1, filename = NULL)
+# png("./gcn_denise/venn_histology.png")
+# grid.newpage()
+# grid.draw(venn_histology)
+# dev.off()
+
+futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
+venn_compound <- venn.diagram(list("CCLE" = unique(na.omit(ccle_auc_long$compound_name)), "CTRP" = unique(na.omit(ctrp_auc_long$compound_name)), "GDSC" = unique(na.omit(gdsc_auc_long$compound_name))), resolution = 5000, main = "Overlap of compounds screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.001, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
+# png("./gcn_denise/venn_compound.png")
+# grid.newpage()
+# grid.draw(venn_compound)
+# dev.off()
+```

### 2019-03-28 19Q1.Rmd
start CN comparisons

@@
 # write.csv.gz(auc_all_ccls, file = "./data_munging/pozdeyev2016/merged_auc_v20190327.3.csv.gz", row.names = FALSE, na = "NA")
-```
 
-```{r}
 # test <- as.data.frame(table(auc_all_ccls$Cell_line))
@@
 
-length(unique(sapply(strsplit(as.character(colnames(auc_all_ccls)[13:length(colnames(auc_all_ccls))]), split = "_"), function(x) x[1])))
+# length(unique(sapply(strsplit(as.character(colnames(auc_all_ccls)[13:length(colnames(auc_all_ccls))]), split = "_"), function(x) x[1])))
+```
+
+### Compar to TCGA
+
+```{r}
+cn_seg <- read.delim("./data_munging/19Q1/copy_number_20190328.csv.gz", sep = ",")
+cn_seg <- merge(ccl_histologies, cn_seg, by = "Broad_ID", all.y = TRUE)
+cn_seg_lung <- filter(cn_seg, Histology == "lung")
 ```

### 2019-04-01 19Q1.Rmd
update Poz Venns, update slides for meeting, update unmatched histologies

@@
 
+ccl_histologies <- subset(ccl_histologies, !(Broad_ID %in% auc_unmatched_na_histologies$Broad_ID))
 # Bind DepMap histologies and curated histologies
@@
 - `c("springgreen4", "steelblue4", "turquoise4")`
-
-## Matched data
-
-```{r, eval=TRUE}
-auc_matched <- read.delim("./data_munging/pharmacogenomics_raw_files/celline_stack.csv.gz", sep = ",")
-auc_matched <- merge(ccl_histologies, auc_matched , by = "Cell_line", all.y = TRUE)
-num_auc_per_db_matched <- auc_matched %>% count(Database)
-ccl_per_db_matched <- unique(select(auc_matched , Database, Cell_line))
-num_ccl_per_db_matched <- unique(select(auc_matched , Database, Cell_line)) %>% count(Database)
-# only CCLs represetented in 2 or 3 databases were included
-num_db_per_ccl_matched <- unique(select(auc_matched , Database, Cell_line)) %>% count(Cell_line)
-```
-
-There were `r length(setdiff(unique(ccl_histologies$Cell_line), unique(auc_matched $Cell_line)))` cell lines not represented in the Pozdeyev et al. harmonized dataset.
-
-Plots:
-```{r, eval=FALSE}
-futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
-venn_ccl_matched_poz <- venn.diagram(list("CCLE" = unique(filter(ccl_per_db_matched, Database == "CCLE"))$Cell_line, "CTRP" = unique(filter(ccl_per_db_matched, Database == "CTRP"))$Cell_line, "GDSC" = unique(filter(ccl_per_db_matched, Database == "GDSC"))$Cell_line), resolution = 5000, main = "Overlap of cancer cell lines (CCLs) screened in matched_all_pairs dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
-png("./gcn_denise/pozdeyev_matched/pozdeyev_venn_ccl_matched.png", res = 500, units = "in", width = 6, height = 6)
-grid.newpage()
-grid.draw(venn_ccl_matched_poz)
-dev.off()
-
-num_ccl_per_db_matched_bar <- ggplot(data = unique(select(auc_matched , Database, Cell_line))) +
-  geom_bar(aes(x = Database, fill = Database), alpha = 0.7) +
-  scale_fill_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) + 
-  guides(fill = "none") +
-  scale_y_continuous(breaks = seq(0, 700, by = 50), labels = seq(0, 700, by = 50)) +
-  geom_text(data = num_ccl_per_db_matched, aes(x = Database, y = n + 20, label = n)) +
-  labs(y = "Number of cell lines", title = "Number of unique cell lines per dataset")
-num_ccl_per_db_matched_bar
-ggsave("./gcn_denise/pozdeyev_matched/pozdeyev_ccl_per_db_matched.png", num_ccl_per_db_matched_bar, device = "png", dpi = 450, width = 12, height = 8, units = "in")
-
-num_ccl_per_hist_per_db_matched_bar <- ggplot(data = unique(select(auc_matched , Database, Cell_line, Histology))) +
-  facet_wrap(~ Database, scales = "free_y") +
-  geom_bar(aes(x = Histology, fill = Histology), alpha = 0.7) +
-  guides(fill = "none") +
-  coord_cartesian(ylim = c(0, 130)) +
-  scale_y_continuous(breaks = seq(0, 130, by = 10), labels = seq(0, 130, by = 10)) +
-  labs(y = "Number of cell lines", title = "Number of unique cell lines per histology, grouped by database") +
-  theme(axis.text.x = element_text(angle = 60, hjust = 1))
-num_ccl_per_hist_per_db_matched_bar
-ggsave("./gcn_denise/pozdeyev_matched/pozdeyev_ccl_per_histology_per_db_matched.png", num_ccl_per_hist_per_db_matched_bar, device = "png", dpi = 450, width = 12, height = 8, units = "in")
-
-num_ccl_per_hist_matched_bar <- ggplot(data = unique(select(auc_matched , Cell_line, Histology))) +
-  geom_bar(aes(x = Histology, fill = Histology), alpha = 0.7) +
-  guides(fill = "none") +
-  coord_cartesian(ylim = c(0, 130)) +
-  scale_y_continuous(breaks = seq(0, 130, by = 10), labels = seq(0, 130, by = 10)) +
-  labs(y = "Number of cell lines", title = "Number of unique cell lines per histology across all three databases") +
-  theme(axis.text.x = element_text(angle = 60, hjust = 1))
-num_ccl_per_hist_matched_bar
-ggsave("./gcn_denise/pozdeyev_matched/pozdeyev_ccl_per_histology_matched.png", num_ccl_per_hist_matched_bar, device = "png", dpi = 450, width = 12, height = 8, units = "in")
-
-aucic50_per_db_matched <- ggplot(data = auc_matched ) +
-  facet_wrap(~ Database) +
-  geom_histogram(aes(x = AUC_IC50, fill = Database), color = "black", alpha = 0.7, binwidth = 0.025, boundary = 0, closed = "left") +
-  scale_fill_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
-  guides(fill = "none") +
-  geom_text(data = num_auc_per_db_matched, aes(x = 0.5, y = 4750, label = paste0("n = ", formatC(n, format = "d", big.mark = ",")))) +
-  scale_y_continuous(breaks = seq(0, 5000, by = 500), labels = seq(0, 5000, by = 500)) +
-  labs(x = "AUC IC50", y = "Frequency", title = "Distributions of AUC IC50 values for all drugs in each dataset (filtered by matching)")
-aucic50_per_db_matched
-ggsave("./gcn_denise/pozdeyev_matched/pozdeyev_aucic50_per_db_matched.png", aucic50_per_db_matched, device = "png", dpi = 450, width = 12, height = 6, units = "in")
-```
 
@@
 auc_all_ccls <- subset(auc_all_ccls, !(WasDrugScreened == 0 & WasCRISPRScreened == 0 & HasMutationData == 0 & HasGeneExpressionData == 0 & HasCopyNumberData == 0))
-# write.csv.gz(auc_all_ccls, file = "./data_munging/pozdeyev2016/merged_auc_v20190327.3.csv.gz", row.names = FALSE, na = "NA")
+# write.csv.gz(auc_all_ccls, file = "./data_munging/pozdeyev2016/merged_auc_v20190401.4.csv.gz", row.names = FALSE, na = "NA")
 
@@
 
-### Compar to TCGA
+```{r}
+auc_all_ccls <- read.delim("./data_munging/pozdeyev2016/merged_auc_v20190401.4.csv.gz", sep = ",")
+
+sum(auc_all_ccls$HasCopyNumberData)
+sum(auc_all_ccls$HasMutationData)
+sum(auc_all_ccls$HasGeneExpressionData)
+sum(auc_all_ccls$WasDrugScreened)
+
+pgx_ccls <- filter(auc_all_ccls, WasDrugScreened == 1)
+crispr_ccls <- filter(auc_all_ccls, WasCRISPRScreened == 1)
+unscreened_ccls <- filter(auc_all_ccls, WasCRISPRScreened == 0 & WasDrugScreened == 0)
+
+ge_ccls <- filter(auc_all_ccls, HasGeneExpressionData == 1)
+cn_ccls <- filter(auc_all_ccls, HasCopyNumberData == 1)
+mut_ccls <- filter(auc_all_ccls, HasMutationData == 1)
+
+all_omics_ccls <- intersect(intersect(unique(ge_ccls$Cell_line), unique(cn_ccls$Cell_line)), unique(mut_ccls$Cell_line))
+sum(filter(auc_all_ccls, Cell_line %in% all_omics_ccls)$WasDrugScreened)
+
+ccle_ccls <- filter(auc_all_ccls, InCCLE == 1)
+ctrp_ccls <- filter(auc_all_ccls, InCTRP == 1)
+gdsc_ccls <- filter(auc_all_ccls, InGDSC == 1)
+
+auc_all_ccls %>% count(Histology)
+```
 
 ```{r}
+test <- mut_ccls[, 1:20]
+test2 <- test %>% count(Broad_ID)
+```
+
+### Summary figures
+
+```{r, eval=FALSE}
+futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
+venn_pgx_crispr_overlap <- venn.diagram(list("CRISPR" = unique(crispr_ccls$Cell_line), "Drug Screen" = unique(pgx_ccls$Cell_line), "Unscreened" = unique(unscreened_ccls$Cell_line)), resolution = 5000, main = "Overlap of cancer cell lines (CCLs) screened via small-molecule and CRISPR", main.fontface = "bold", lty = rep("blank", 3), fill = c("mediumpurple1", "turquoise4", "slategray3"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
+png("./gcn_denise/pozdeyev_unmatched/venn_pgx_crispr_overlap.png", res = 500, units = "in", width = 6, height = 6)
+grid.newpage()
+grid.draw(venn_pgx_crispr_overlap)
+dev.off()
+
+futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
+venn_ccl_overlap <- venn.diagram(list("CCLE" = unique(ccle_ccls$Cell_line), "CTRP" = unique(ctrp_ccls$Cell_line), "GDSC" = unique(gdsc_ccls$Cell_line)), resolution = 5000, main = "Overlap of cancer cell lines (CCLs) screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
+# png("./gcn_denise/pozdeyev_unmatched/pozdeyev_venn_all_ccl_unmatched.png", res = 500, units = "in", width = 6, height = 6)
+# grid.newpage()
+# grid.draw(venn_ccl_overlap)
+# dev.off()
+
+futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
+venn_omics_overlap <- venn.diagram(list("Gene Expression" = unique(ge_ccls$Cell_line), "Copy Number" = unique(cn_ccls$Cell_line), "Mutation" = unique(mut_ccls$Cell_line)), resolution = 5000, main = "Overlapping omic annotations in cancer cell lines (CCLs)", main.fontface = "bold", lty = rep("blank", 3), fill = c("yellow2", "orange", "tomato"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
+png("./gcn_denise/pozdeyev_unmatched/pozdeyev_venn_omics_overlap.png", res = 500, units = "in", width = 6, height = 6)
+grid.newpage()
+grid.draw(venn_omics_overlap)
+dev.off()
+
+num_ccl_per_hist_unmatched_bar <- ggplot(data = unique(select(auc_all_ccls, Cell_line, Histology))) +
+  geom_bar(aes(x = Histology, fill = Histology), alpha = 0.7) +
+  guides(fill = "none") +
+  scale_y_continuous(breaks = seq(0, 300, by = 25), labels = seq(0, 300, by = 25)) +
+  labs(y = "Number of cell lines", title = "Number of unique cell lines per histology across all cell lines") +
+  theme(axis.text.x = element_text(angle = 60, hjust = 1))
+num_ccl_per_hist_unmatched_bar
+# ggsave("./gcn_denise/pozdeyev_unmatched/pozdeyev_ccl_per_histology_unmatched.png", num_ccl_per_hist_unmatched_bar, device = "png", dpi = 450, width = 12, height = 6, units = "in")
+```
+
+### Compare to TCGA
+Quality check: cluster TCGA samples and cell lines—verify that same tumor types cluster together rather than clustering by cell lines and tumor samples
+
+Calculate Pearson correlations between data sets and create a heatmap (also look at Barretina et al. supplement for PCA and mutation load correlations)
+
+```{r, eval=FALSE}
 cn_seg <- read.delim("./data_munging/19Q1/copy_number_20190328.csv.gz", sep = ",")
-cn_seg <- merge(ccl_histologies, cn_seg, by = "Broad_ID", all.y = TRUE)
-cn_seg_lung <- filter(cn_seg, Histology == "lung")
+tcga_pancan <- read.delim("~/Desktop/GDC-PANCAN.masked_cnv.tsv.gz", sep = "\t")
+
+ggplot(cn_seg, aes(x = log2(Segment_Mean/2))) + 
+  geom_density()
+
+ggplot(tcga_pancan, aes(x = value)) + 
+  geom_density()
 ```
@@
 
-# Denise's GCN dataframes (Deprected)
+# (OLD) Pozdeyev et al (2016) matched data
+
+--------------------------------------------------------------------------------
+
+```{r, eval=FALSE}
+auc_matched <- read.delim("./data_munging/pharmacogenomics_raw_files/celline_stack.csv.gz", sep = ",")
+auc_matched <- merge(ccl_histologies, auc_matched , by = "Cell_line", all.y = TRUE)
+num_auc_per_db_matched <- auc_matched %>% count(Database)
+ccl_per_db_matched <- unique(select(auc_matched , Database, Cell_line))
+num_ccl_per_db_matched <- unique(select(auc_matched , Database, Cell_line)) %>% count(Database)
+# only CCLs represetented in 2 or 3 databases were included
+num_db_per_ccl_matched <- unique(select(auc_matched , Database, Cell_line)) %>% count(Cell_line)
+```
+
+There were `r length(setdiff(unique(ccl_histologies$Cell_line), unique(auc_matched $Cell_line)))` cell lines not represented in the Pozdeyev et al. harmonized dataset.
+
+Plots:
+```{r, eval=FALSE}
+futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
+venn_ccl_matched_poz <- venn.diagram(list("CCLE" = unique(filter(ccl_per_db_matched, Database == "CCLE"))$Cell_line, "CTRP" = unique(filter(ccl_per_db_matched, Database == "CTRP"))$Cell_line, "GDSC" = unique(filter(ccl_per_db_matched, Database == "GDSC"))$Cell_line), resolution = 5000, main = "Overlap of cancer cell lines (CCLs) screened in matched_all_pairs dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
+png("./gcn_denise/pozdeyev_matched/pozdeyev_venn_ccl_matched.png", res = 500, units = "in", width = 6, height = 6)
+grid.newpage()
+grid.draw(venn_ccl_matched_poz)
+dev.off()
+
+num_ccl_per_db_matched_bar <- ggplot(data = unique(select(auc_matched , Database, Cell_line))) +
+  geom_bar(aes(x = Database, fill = Database), alpha = 0.7) +
+  scale_fill_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) + 
+  guides(fill = "none") +
+  scale_y_continuous(breaks = seq(0, 700, by = 50), labels = seq(0, 700, by = 50)) +
+  geom_text(data = num_ccl_per_db_matched, aes(x = Database, y = n + 20, label = n)) +
+  labs(y = "Number of cell lines", title = "Number of unique cell lines per dataset")
+num_ccl_per_db_matched_bar
+ggsave("./gcn_denise/pozdeyev_matched/pozdeyev_ccl_per_db_matched.png", num_ccl_per_db_matched_bar, device = "png", dpi = 450, width = 12, height = 8, units = "in")
+
+num_ccl_per_hist_per_db_matched_bar <- ggplot(data = unique(select(auc_matched , Database, Cell_line, Histology))) +
+  facet_wrap(~ Database, scales = "free_y") +
+  geom_bar(aes(x = Histology, fill = Histology), alpha = 0.7) +
+  guides(fill = "none") +
+  coord_cartesian(ylim = c(0, 130)) +
+  scale_y_continuous(breaks = seq(0, 130, by = 10), labels = seq(0, 130, by = 10)) +
+  labs(y = "Number of cell lines", title = "Number of unique cell lines per histology, grouped by database") +
+  theme(axis.text.x = element_text(angle = 60, hjust = 1))
+num_ccl_per_hist_per_db_matched_bar
+ggsave("./gcn_denise/pozdeyev_matched/pozdeyev_ccl_per_histology_per_db_matched.png", num_ccl_per_hist_per_db_matched_bar, device = "png", dpi = 450, width = 12, height = 8, units = "in")
+
+num_ccl_per_hist_matched_bar <- ggplot(data = unique(select(auc_matched , Cell_line, Histology))) +
+  geom_bar(aes(x = Histology, fill = Histology), alpha = 0.7) +
+  guides(fill = "none") +
+  coord_cartesian(ylim = c(0, 130)) +
+  scale_y_continuous(breaks = seq(0, 130, by = 10), labels = seq(0, 130, by = 10)) +
+  labs(y = "Number of cell lines", title = "Number of unique cell lines per histology across all three databases") +
+  theme(axis.text.x = element_text(angle = 60, hjust = 1))
+num_ccl_per_hist_matched_bar
+ggsave("./gcn_denise/pozdeyev_matched/pozdeyev_ccl_per_histology_matched.png", num_ccl_per_hist_matched_bar, device = "png", dpi = 450, width = 12, height = 8, units = "in")
+
+aucic50_per_db_matched <- ggplot(data = auc_matched ) +
+  facet_wrap(~ Database) +
+  geom_histogram(aes(x = AUC_IC50, fill = Database), color = "black", alpha = 0.7, binwidth = 0.025, boundary = 0, closed = "left") +
+  scale_fill_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
+  guides(fill = "none") +
+  geom_text(data = num_auc_per_db_matched, aes(x = 0.5, y = 4750, label = paste0("n = ", formatC(n, format = "d", big.mark = ",")))) +
+  scale_y_continuous(breaks = seq(0, 5000, by = 500), labels = seq(0, 5000, by = 500)) +
+  labs(x = "AUC IC50", y = "Frequency", title = "Distributions of AUC IC50 values for all drugs in each dataset (filtered by matching)")
+aucic50_per_db_matched
+ggsave("./gcn_denise/pozdeyev_matched/pozdeyev_aucic50_per_db_matched.png", aucic50_per_db_matched, device = "png", dpi = 450, width = 12, height = 6, units = "in")
+```
+
+# (OLD) Denise's GCN dataframes
 

### 2019-04-02 19Q1.Rmd
update 19Q1.Rmd and knit to HTML

--- 2019-03-27 19Q1.Rmd
@@
 
-## CCLE genomic annotations
-
-### Mutation status (Mut)
+## Omics
 
@@
 
-### Copy number (CN)
-
 DepMap WES CN Data:
@@
 ```
-
-### Gene expression (GE)
 
@@
 
+Load Rds:
+```{r}
+maf_df <- readRDS("./data_munging/19Q1/maf_df_19Q1.rds")
+cn_melt <- readRDS("./data_munging/19Q1/cn_melt_19Q1.rds")
+ge_melt <- readRDS("./data_munging/19Q1/ge_melt_19Q1.rds")
+```
+
 ## CRISPR
@@
 # Account for cell line aliases and missing histologies
-auc_unmatched_na_histologies <- read.delim("./data_munging/pozdeyev2016/auc_unmatched_na_histologies.csv", sep = ",", row.names = 1)
-auc_unmatched_na_histologies$accession_id <- NULL
-auc_unmatched_na_histologies$Notes <- NULL
-auc_unmatched_na_histologies$Histology <- ifelse(auc_unmatched_na_histologies$Histology == "", NA, as.character(auc_unmatched_na_histologies$Histology))
-auc_unmatched_na_histologies$CCLE_ccl_name <- ifelse(auc_unmatched_na_histologies$CCLE_ccl_name  == "", NA, as.character(auc_unmatched_na_histologies$CCLE_ccl_name ))
-auc_unmatched_na_histologies$Broad_ID <- ifelse(auc_unmatched_na_histologies$Broad_ID == "", NA, as.character(auc_unmatched_na_histologies$Broad_ID))
+auc_na_histologies <- read.delim("./data_munging/pozdeyev2016/auc_na_histologies.csv", sep = ",", row.names = 1)
 
+auc_na_histologies$accession_id <- NULL
+auc_na_histologies$Notes <- NULL
+auc_na_histologies$Histology <- ifelse(auc_na_histologies$Histology == "", NA, as.character(auc_na_histologies$Histology))
+auc_na_histologies$CCLE_ccl_name <- ifelse(auc_na_histologies$CCLE_ccl_name  == "", NA, as.character(auc_na_histologies$CCLE_ccl_name ))
+auc_na_histologies$Broad_ID <- ifelse(auc_na_histologies$Broad_ID == "", NA, as.character(auc_na_histologies$Broad_ID))
+
+ccl_histologies <- subset(ccl_histologies, !(Broad_ID %in% auc_na_histologies$Broad_ID))
 # Bind DepMap histologies and curated histologies
-ccl_histologies <- bind_rows(ccl_histologies, auc_unmatched_na_histologies)
+ccl_histologies <- bind_rows(ccl_histologies, auc_na_histologies)
 ```
@@
 
-## Matched data
+## Data wrangling
 
-```{r, eval=TRUE}
+```{r, eval=FALSE}
+ccle_poz <- read.delim("./data_munging/pozdeyev2016/CCLE_drug_response_metrics.csv.gz", sep = ",")
+
+# ccle_test <- merge(select(ccle_poz, Drug_name, Cell_line, AUC_IC50), select(filter(auc, Database == "CCLE"), Drug_name, Cell_line, AUC_IC50), by = c("Drug_name", "Cell_line"), suffixes = c("_unmatched", "_matched_all_pairs"), all = TRUE)
+
+ctrp_poz <- read.delim("./../htscreens_giant_files/pozdeyev2016/CTRP_drug_response_metrics.csv.gz", sep = ",")
+# ctrp_test <- merge(select(ctrp_poz, Drug_name, Cell_line, AUC_IC50), select(filter(auc, Database == "CTRP"), Drug_name, Cell_line, AUC_IC50), by = c("Drug_name", "Cell_line"), suffixes = c("_unmatched", "_matched_all_pairs"), all = TRUE)
+
+gdsc_poz <- read.delim("./data_munging/pozdeyev2016/GDSC_drug_response_metrics.csv.gz", sep = ",")
+# gdsc_test <- merge(select(gdsc_poz, Drug_name, Cell_line, AUC_IC50), select(filter(auc, Database == "GDSC"), Drug_name, Cell_line, AUC_IC50), by = c("Drug_name", "Cell_line"), suffixes = c("_unmatched", "_matched_all_pairs"), all = TRUE)
+
+auc <- bind_rows(ccle_poz, ctrp_poz, gdsc_poz)
+
+# Harmonize Pozdeyev cell line names with DepMap
+auc$Cell_line <- toupper(gsub("-", "", auc$Cell_line))
+auc$Cell_line <- ifelse(auc$Cell_line == "K052", "KO52", auc$Cell_line)
+auc$Cell_line <- ifelse(auc$Cell_line == "OVCAR3", "NIHOVCAR3", auc$Cell_line)
+auc$Cell_line <- ifelse(auc$Cell_line == "OVCAR3", "NIHOVCAR3", auc$Cell_line)
+auc$Cell_line <- ifelse(auc$Cell_line == "TI73", "T173", auc$Cell_line)
+auc <- merge(ccl_histologies, auc, by = "Cell_line", all.y = TRUE)
+
+auc$WasDrugScreened <- 1
+ccls_not_drugscreened <- filter(ccl_histologies, Cell_line %in% setdiff(ccl_histologies$Cell_line, auc_wide$Cell_line))
+ccls_not_drugscreened$WasDrugScreened <- 0
+
+auc$AUC_IC50 <- as.numeric(as.character(auc$AUC_IC50))
+# auc$sample_ID <- with(auc, paste(Database, Cell_line, Histology, sep = "_"))
+auc$Drug_name_Database <- with(auc, paste(Drug_name, Database, sep = "_"))
+
+num_auc_per_db <- auc %>% count(Database)
+
+# Identify cell lines without histology indications. Write to file to edit for merging back to ccl_histologies file
+# test <- filter(auc, is.na(Histology))[, 1:10]
+# auc_na_hists <- unique(filter(auc, is.na(Histology))$Cell_linet)
+# write.csv(auc_na_hists, "./data_munging/pozdeyev2016/auc_na_histologies.csv")
+
+# Create merged dataset with sample_ids in the rows and drugs across the columns
+auc_wide <- dcast(auc, Cell_line + Histology + CCLE_ccl_name + Broad_ID + WasDrugScreened ~ Drug_name_Database, value.var = "AUC_IC50", fun.aggregate = mean, fill = 1000000)
+auc_wide[auc_wide == 1000000] <- ""
+auc_wide <- auc_wide %>% group_by(Cell_line, Histology, CCLE_ccl_name, Broad_ID, WasDrugScreened) %>% summarise_all(funs(trimws(paste(., collapse = ""))))
+auc_wide[auc_wide == ""] <- NA
+
+auc_all <- bind_rows(auc_wide, ccls_not_drugscreened)
+
+auc_all <- add_column(auc_all, InCCLE = ifelse(auc_all$Cell_line %in% unique(ccle_poz$Cell_line), 1, 0), .after = "Broad_ID")
+auc_all <- add_column(auc_all, InCTRP = ifelse(auc_all$Cell_line %in% unique(ctrp_poz$Cell_line), 1, 0), .after = "Broad_ID")
+auc_all <- add_column(auc_all, InGDSC = ifelse(auc_all$Cell_line %in% unique(gdsc_poz$Cell_line), 1, 0), .after = "Broad_ID")
+
+auc_all <- add_column(auc_all, WasCRISPRScreened = ifelse(auc_all$Broad_ID %in% crispr_meta$Broad_ID, 1, 0), .after = "WasDrugScreened")
+auc_all <- add_column(auc_all, HasCopyNumberData = ifelse(auc_all$Broad_ID %in% unique(cn_melt$Broad_ID)[!is.na(unique(cn_melt$Broad_ID))], 1, 0), .after = "WasCRISPRScreened")
+auc_all <- add_column(auc_all, HasGeneExpressionData = ifelse(auc_all$Broad_ID %in% unique(ge_melt$Broad_ID)[!is.na(unique(ge_melt$Broad_ID))], 1, 0), .after = "WasCRISPRScreened")
+auc_all <- add_column(auc_all, HasMutationData = ifelse(auc_all$Broad_ID %in% unique(maf_df$Broad_ID)[!is.na(unique(maf_df$Broad_ID))], 1, 0), .after = "WasCRISPRScreened")
+
+# auc_all[, -c(1:4)] <- apply(auc_all[, -c(1:4)], MARGIN = 2, FUN = as.numeric)
+auc_all <- subset(auc_all, !(WasDrugScreened == 0 & WasCRISPRScreened == 0 & HasMutationData == 0 & HasGeneExpressionData == 0 & HasCopyNumberData == 0))
+# write.csv.gz(auc_all, file = "./data_munging/pozdeyev2016/merged_auc_v20190402.4.csv.gz", row.names = FALSE, na = "NA")
+
+# test <- as.data.frame(table(auc_all$Cell_line))
+# test <- filter(auc_all, Cell_line %in% c("KMH2", "MS1", "TT"))[, 1:12]
+```
+
+```{r}
+auc_all <- read.delim("./data_munging/pozdeyev2016/merged_auc_v20190402.4.csv.gz", sep = ",", check.names = FALSE)
+
+# Unique drugs across all datasets
+length(unique(sapply(strsplit(as.character(colnames(auc_all)[13:length(colnames(auc_all))]), split = "_"), function(x) x[1])))
+
+sum(auc_all$HasCopyNumberData)
+sum(auc_all$HasMutationData)
+sum(auc_all$HasGeneExpressionData)
+sum(auc_all$WasDrugScreened)
+
+test <- filter(auc_all, HasMutationData == 1)[, 1:12]
+
+pgx_ccls <- filter(auc_all, WasDrugScreened == 1)
+crispr_ccls <- filter(auc_all, WasCRISPRScreened == 1)
+unscreened_ccls <- filter(auc_all, WasCRISPRScreened == 0 & WasDrugScreened == 0)
+
+ge_ccls <- filter(auc_all, HasGeneExpressionData == 1)
+cn_ccls <- filter(auc_all, HasCopyNumberData == 1)
+mut_ccls <- filter(auc_all, HasMutationData == 1)
+
+all_omics_ccls <- intersect(intersect(unique(ge_ccls$Cell_line), unique(cn_ccls$Cell_line)), unique(mut_ccls$Cell_line))
+sum(filter(auc_all, Cell_line %in% all_omics_ccls)$WasDrugScreened)
+
+ccle_ccls <- filter(auc_all, InCCLE == 1)
+ctrp_ccls <- filter(auc_all, InCTRP == 1)
+gdsc_ccls <- filter(auc_all, InGDSC == 1)
+
+auc_all %>% count(Histology)
+```
+
+## Plots
+
+```{r, eval=FALSE}
+futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
+venn_pgx_crispr_overlap <- venn.diagram(list("CRISPR" = unique(crispr_ccls$Cell_line), "Drug Screen" = unique(pgx_ccls$Cell_line), "Unscreened" = unique(unscreened_ccls$Cell_line)), resolution = 5000, main = "Overlap of cancer cell lines (CCLs) screened via small-molecule and CRISPR", main.fontface = "bold", lty = rep("blank", 3), fill = c("mediumpurple1", "turquoise4", "slategray3"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
+png("./gcn_denise/pozdeyev_unmatched/venn_pgx_crispr_overlap.png", res = 500, units = "in", width = 6, height = 6)
+grid.newpage()
+grid.draw(venn_pgx_crispr_overlap)
+dev.off()
+
+futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
+venn_ccl_overlap <- venn.diagram(list("CCLE" = unique(ccle_ccls$Cell_line), "CTRP" = unique(ctrp_ccls$Cell_line), "GDSC" = unique(gdsc_ccls$Cell_line)), resolution = 5000, main = "Overlap of cancer cell lines (CCLs) screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
+png("./gcn_denise/pozdeyev_unmatched/venn_ccl_overlap.png", res = 500, units = "in", width = 6, height = 6)
+grid.newpage()
+grid.draw(venn_ccl_overlap)
+dev.off()
+
+futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
+venn_omics_overlap <- venn.diagram(list("Gene Expression" = unique(ge_ccls$Cell_line), "Copy Number" = unique(cn_ccls$Cell_line), "Mutation" = unique(mut_ccls$Cell_line)), resolution = 5000, main = "Overlapping omic annotations in cancer cell lines (CCLs)", main.fontface = "bold", lty = rep("blank", 3), fill = c("yellow2", "orange", "tomato"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
+png("./gcn_denise/pozdeyev_unmatched/venn_omics_overlap.png", res = 500, units = "in", width = 6, height = 6)
+grid.newpage()
+grid.draw(venn_omics_overlap)
+dev.off()
+
+bar_ccl_per_hist <- ggplot(data = unique(select(auc_all, Cell_line, Histology))) +
+  geom_bar(aes(x = Histology, fill = Histology), alpha = 0.7) +
+  guides(fill = "none") +
+  scale_y_continuous(breaks = seq(0, 300, by = 25), labels = seq(0, 300, by = 25)) +
+  labs(y = "Number of cell lines", title = "Number of unique cell lines per histology across all cell lines") +
+  theme(axis.text.x = element_text(angle = 60, hjust = 1))
+bar_ccl_per_hist
+ggsave("./gcn_denise/pozdeyev_unmatched/barplot_ccl_per_histology.png", bar_ccl_per_hist, device = "png", dpi = 450, width = 12, height = 6, units = "in")
+
+futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
+venn_drugs_overlap <- venn.diagram(list("CCLE" = unique(ccle_poz$Drug_name), "CTRP" = unique(ctrp_poz$Drug_name), "GDSC" = unique(gdsc_poz$Drug_name)), resolution = 5000, main = "Overlap of cancer cell lines (CCLs) screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
+png("./gcn_denise/pozdeyev_unmatched/venn_drugs_overlap.png", res = 500, units = "in", width = 6, height = 6)
+grid.newpage()
+grid.draw(venn_drugs_overlap)
+dev.off()
+
+bar_ccl_per_hist_per_db <- ggplot(data = unique(select(auc, Database, Cell_line, Histology))) +
+  facet_wrap(~ Database) +
+  geom_bar(aes(x = Histology, fill = Histology), alpha = 0.7) +
+  guides(fill = "none") +
+  # coord_cartesian(ylim = c(0, 130)) +
+  scale_y_continuous(breaks = seq(0, 160, by = 20), labels = seq(0, 160, by = 20)) +
+  labs(y = "Number of cell lines", title = "Number of unique cell lines per histology, grouped by database") +
+  theme(axis.text.x = element_text(angle = 60, hjust = 1))
+bar_ccl_per_hist_per_db
+ggsave("./gcn_denise/pozdeyev_unmatched/barplot_ccl_per_histology_per_db.png", bar_ccl_per_hist_per_db, device = "png", dpi = 450, width = 12, height = 8, units = "in")
+
+bar_ccl_per_hist <- ggplot(data = unique(select(auc_all, Cell_line, Histology))) +
+  geom_bar(aes(x = Histology, fill = Histology), alpha = 0.7) +
+  guides(fill = "none") +
+  scale_y_continuous(breaks = seq(0, 220, by = 20), labels = seq(0, 220, by = 20)) +
+  labs(y = "Number of cell lines", title = "Number of unique cell lines per histology across all annotated cell lines") +
+  theme(axis.text.x = element_text(angle = 60, hjust = 1))
+bar_ccl_per_hist
+ggsave("./gcn_denise/pozdeyev_unmatched/barplot_ccl_per_histology.png", bar_ccl_per_hist, device = "png", dpi = 450, width = 12, height = 8, units = "in")
+
+histo_aucic50_per_db <- ggplot(data = auc) +
+  facet_wrap(~ Database, scales = "free_y") +
+  geom_histogram(aes(x = AUC_IC50, fill = Database), color = "black", alpha = 0.7, binwidth = 0.025, boundary = 0, closed = "left") +
+  scale_fill_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
+  guides(fill = "none") +
+  labs(x = "AUC IC50", y = "Frequency", title = "Distributions of AUC IC50 values for all drugs in each dataset (unmatched)")
+histo_aucic50_per_db
+ggsave("./gcn_denise/pozdeyev_unmatched/histogram_aucic50_per_db.png", histo_aucic50_per_db, device = "png", dpi = 450, width = 12, height = 6, units = "in")
+```
+
+## README
+
+DATA SOURCE
+
+- Pozdeyev, N., Yoo, M., Mackie, R., Schweppe, R.
+E., Tan, A.
+C., & Haugen, B.
+R.
+(2016).
+Integrating heterogeneous drug sensitivity data from cancer pharmacogenomic studies.
+Oncotarget, 7(32), 51619–51625.
+https://doi.org/10.18632/oncotarget.10010
+- Online visualization tool: http://tanlab.ucdenver.edu/QAPC/
+- Zipped file containing their R scripts and full datasets can be downloaded here: http://tanlab.ucdenver.edu/QAPC/Downloads/Drug_Sensitvity_Metrics.zip
+
+COLUMN DESCRIPTIONS
+
+For latest version of merged_auc dataframe:
+
+- Cell_line: the name of the cancer cell line (CCL), harmonized across datasets by Pozdeyev et al. (2016)
+- Histology: the general histology/tissue type of the CCL according to the CCLE annotations (see DepMap-2019q1-celllines_v2.csv file from the DepMap Data Portal)
+- CCLE_ccl_name: the cell line name using CCLE nomenclature, which is a concatenation of the cell line name with the CCLE-annotated histology in all caps, separated by underscores
+- Broad_ID: the custom identifiers (formatted as ACH-######) used by the Broad's Cancer Dependency Map project to ease cell line name harmonization efforts 
+- InCCLE: 1 means the cell line was screened in CCLE, 0 means it was not
+- InCTRP: 1 means the cell line was screened in CTRP, 0 means it was not
+- InGDSC: 1 means the cell line was screened in GDSC, 0 means it was not
+- WasDrugScreened: 1 means the cell was screened in at least one pharmacogenomic screens, and 0 means it was not screened in any of the pharmacogenomic screens
+- WasCRISPRScreened: 1 means the cell line was screened in the Avana CRISPR screen, and 0 means it was not
+- HasMutationData: 1 means the cell line had at least one recorded mutation in the MAF file (see file version below), and 0 means it was not annotated in the MAF file
+- HasGeneExpressionData: 1 means gene expression data is available for the cell line (see file version below), and 0 means it does not have gene expression information
+- HasCopyNumberData: 1 means copy number data is available for the cell line (see file version below), and 0 means it does not have copy number information
+- All other columns: compound and drug names that were screened in at least one CCL in at least one database, formatted as Drug_DatabaseName
+    - NA values indictate that compound wasn't screened in the respective CCL in the respective source dataset
+    - Values are in AUC_IC50, the area under rhe dose response curve calculated from IC50 model
+
+CHANGE LOG FOR MERGED_AUC DATAFRAME
+
+merged_auc_v20190319.1.csv.gz
+
+merged_auc_v20190319.2.csv.gz:
+- NAs in Histology column (excluding most of the cell lines indicated as being from a "collaborator" in CTRP) hand-curated by searches in DepMap, COSMIC, Cellosaurus, ATCC, canSAR Black, and Cell Model Passports
+
+merged_auc_v20190327.3.csv.gz:
+- Reformatted to have only unique cell lines in rows
+- Cancer cell lines screened in more than one database have multiple AUC columns (column names are formatted as Drug_DatabaseName)
+- Added information on binary presence/absencee of omic annotations for each cell line (i.e. mutations, copy number, gene expression)
+- Added binary columns indicating presence in CCLE, CTRP, GDSC, drug screens in general (in 1, 2, or 3), and the Avana CRISPR screen
+- Added cell lines that have at least one type of omic data but are not in the CRISPR or pharmacogenomic screens
+
+merged_auc_v20190402.4.csv.gz:
+- Fixed duplicate cell line rows derived from manually curating some of the CCL histologies that had been added in merged_auc_v20190319.2.csv.gz
+- Fixed HasMutationData, HasCopyNumberData, and HasGeneExpression data columns
+- Reordered columns
+
+# Compare to TCGA
+
+--------------------------------------------------------------------------------
+
+Quality check: cluster TCGA samples and cell lines—verify that same tumor types cluster together rather than clustering by cell lines and tumor samples (Kaiqiao)
+
+Calculate Pearson correlations between data sets and create a heatmap (also look at Barretina et al. supplement for PCA and mutation load correlations)
+
+```{r, eval=FALSE}
+cn_seg <- read.delim("./data_munging/19Q1/copy_number_20190328.csv.gz", sep = ",")
+tcga_pancan <- read.delim("~/Desktop/GDC-PANCAN.masked_cnv.tsv.gz", sep = "\t")
+
+ggplot(cn_seg, aes(x = log2(Segment_Mean/2))) + 
+  geom_density()
+
+ggplot(tcga_pancan, aes(x = value)) + 
+  geom_density()
+```
+
+# (OLD) Pozdeyev et al (2016) matched data
+
+--------------------------------------------------------------------------------
+
+```{r, eval=FALSE}
 auc_matched <- read.delim("./data_munging/pharmacogenomics_raw_files/celline_stack.csv.gz", sep = ",")
@@
 ```
-
-There were `r length(setdiff(unique(ccl_histologies$Cell_line), unique(auc_matched $Cell_line)))` cell lines not represented in the Pozdeyev et al. harmonized dataset.
 
@@
 
-## Unmatched data
-
-```{r, eval=FALSE}
-ccle_poz <- read.delim("./data_munging/pozdeyev2016/CCLE_drug_response_metrics.csv.gz", sep = ",")
-ccle_poz <- merge(ccl_histologies, ccle_poz, by = "Cell_line", all.y = TRUE)
-ccle_poz$InCCLE <- "1"
-ccle_poz$InCTRP <- ""
-ccle_poz$InGDSC <- ""
-
-# ccle_test <- merge(select(ccle_poz, Drug_name, Cell_line, AUC_IC50), select(filter(auc, Database == "CCLE"), Drug_name, Cell_line, AUC_IC50), by = c("Drug_name", "Cell_line"), suffixes = c("_unmatched", "_matched_all_pairs"), all = TRUE)
-
-ctrp_poz <- read.delim("./../htscreens_giant_files/pozdeyev2016/CTRP_drug_response_metrics.csv.gz", sep = ",")
-ctrp_poz <- merge(ccl_histologies, ctrp_poz, by = "Cell_line", all.y = TRUE)
-ctrp_poz$InCCLE <- ""
-ctrp_poz$InCTRP <- "1"
-ctrp_poz$InGDSC <- ""
-# ctrp_test <- merge(select(ctrp_poz, Drug_name, Cell_line, AUC_IC50), select(filter(auc, Database == "CTRP"), Drug_name, Cell_line, AUC_IC50), by = c("Drug_name", "Cell_line"), suffixes = c("_unmatched", "_matched_all_pairs"), all = TRUE)
-
-gdsc_poz <- read.delim("./data_munging/pozdeyev2016/GDSC_drug_response_metrics.csv.gz", sep = ",")
-gdsc_poz <- merge(ccl_histologies, gdsc_poz, by = "Cell_line", all.y = TRUE)
-gdsc_poz$InCCLE <- ""
-gdsc_poz$InCTRP <- ""
-gdsc_poz$InGDSC <- "1"
-# gdsc_test <- merge(select(gdsc_poz, Drug_name, Cell_line, AUC_IC50), select(filter(auc, Database == "GDSC"), Drug_name, Cell_line, AUC_IC50), by = c("Drug_name", "Cell_line"), suffixes = c("_unmatched", "_matched_all_pairs"), all = TRUE)
-
-auc_unmatched <- bind_rows(ccle_poz, ctrp_poz, gdsc_poz)
-auc_unmatched$WasDrugScreened <- 1
-# auc_unmatched$AUC_EC50 <- as.numeric(as.character(auc_unmatched$AUC_EC50))
-auc_unmatched$AUC_IC50 <- as.numeric(as.character(auc_unmatched$AUC_IC50))
-# auc_unmatched$sample_ID <- with(auc_unmatched, paste(Database, Cell_line, Histology, sep = "_"))
-auc_unmatched$Drug_name_Database <- with(auc_unmatched, paste(Drug_name, Database, sep = "_"))
-
-num_auc_per_db_unmatched <- auc_unmatched %>% count(Database)
-
-# Identify cell lines without histology indications. Write to file to edit for merging back to ccl_histologies file
-# test <- filter(auc_unmatched, is.na(Histology))[, 1:10]
-# auc_unmatched_na_hists <- filter(auc_unmatched, is.na(Histology))$Cell_line
-# write.csv(auc_unmatched_na_hists, "./data_munging/pozdeyev2016/auc_unmatched_na_histologies.csv")
-
-# Create merged dataset with sample_ids in the rows and drugs across the columns
-auc_unmatched_wide <- dcast(auc_unmatched, Cell_line + Histology + CCLE_ccl_name + Broad_ID + InCCLE + InCTRP + InGDSC + WasDrugScreened ~ Drug_name_Database, value.var = "AUC_IC50", fun.aggregate = mean, fill = 1000000)
-auc_unmatched_wide[auc_unmatched_wide == 1000000] <- ""
-auc_unmatched_wide <- auc_unmatched_wide %>% group_by(Cell_line, Histology, CCLE_ccl_name, Broad_ID, WasDrugScreened) %>% summarise_all(funs(trimws(paste(., collapse = ""))))
-auc_unmatched_wide$InCCLE[auc_unmatched_wide$InCCLE == ""] <- 0
-auc_unmatched_wide$InCTRP[auc_unmatched_wide$InCTRP == ""] <- 0
-auc_unmatched_wide$InGDSC[auc_unmatched_wide$InGDSC == ""] <- 0
-auc_unmatched_wide[auc_unmatched_wide == ""] <- NA
-auc_unmatched_wide <- add_column(auc_unmatched_wide, WasCRISPRScreened = NA, .after = "WasDrugScreened")
-auc_unmatched_wide <- add_column(auc_unmatched_wide, HasCopyNumberData = NA, .after = "WasCRISPRScreened")
-auc_unmatched_wide <- add_column(auc_unmatched_wide, HasGeneExpressionData = NA, .after = "WasCRISPRScreened")
-auc_unmatched_wide <- add_column(auc_unmatched_wide, HasMutationData = NA, .after = "WasCRISPRScreened")
-
-ccls_not_drugscreened <- filter(ccl_histologies, Cell_line %in% setdiff(ccl_histologies$Cell_line, auc_unmatched_wide$Cell_line))
-ccls_not_drugscreened$WasDrugScreened <- 0
-
-maf_df <- readRDS("./data_munging/19Q1/maf_df_19Q1.rds")
-cn_melt <- readRDS("./data_munging/19Q1/cn_melt_19Q1.rds")
-ge_melt <- readRDS("./data_munging/19Q1/ge_melt_19Q1.rds")
-
-auc_all_ccls <- bind_rows(auc_unmatched_wide, ccls_not_drugscreened)
-auc_all_ccls$HasMutationData <- with(auc_all_ccls, ifelse(Broad_ID %in% maf_df$Broad_ID, 1, 0))
-auc_all_ccls$HasCopyNumberData <- with(auc_all_ccls, ifelse(Broad_ID %in% cn_melt$Broad_ID, 1, 0))
-auc_all_ccls$HasGeneExpressionData <- with(auc_all_ccls, ifelse(Broad_ID %in% ge_melt$Broad_ID, 1, 0))
-auc_all_ccls$WasCRISPRScreened <- with(auc_all_ccls, ifelse(Broad_ID %in% crispr_meta$Broad_ID, 1, 0))
-auc_all_ccls$InCCLE <- with(auc_all_ccls, ifelse(WasDrugScreened == 0, 0, InCCLE))
-auc_all_ccls$InCTRP <- with(auc_all_ccls, ifelse(WasDrugScreened == 0, 0, InCTRP))
-auc_all_ccls$InGDSC <- with(auc_all_ccls, ifelse(WasDrugScreened == 0, 0, InGDSC))
-auc_all_ccls[, -c(1:4)] <- apply(auc_all_ccls[, -c(1:4)], MARGIN = 2, FUN = as.numeric)
-auc_all_ccls <- subset(auc_all_ccls, !(WasDrugScreened == 0 & WasCRISPRScreened == 0 & HasMutationData == 0 & HasGeneExpressionData == 0 & HasCopyNumberData == 0))
-# write.csv.gz(auc_all_ccls, file = "./data_munging/pozdeyev2016/merged_auc_v20190327.3.csv.gz", row.names = FALSE, na = "NA")
-```
-
-```{r}
-# test <- as.data.frame(table(auc_all_ccls$Cell_line))
-# test <- filter(auc_all_ccls, Cell_line %in% c("KMH2", "MS1", "TT"))[, 1:12]
-
-length(unique(sapply(strsplit(as.character(colnames(auc_all_ccls)[13:length(colnames(auc_all_ccls))]), split = "_"), function(x) x[1])))
-```
-
-### README
-
-Data source:
-- Pozdeyev, N., Yoo, M., Mackie, R., Schweppe, R.
-E., Tan, A.
-C., & Haugen, B.
-R.
-(2016).
-Integrating heterogeneous drug sensitivity data from cancer pharmacogenomic studies.
-Oncotarget, 7(32), 51619–51625.
-https://doi.org/10.18632/oncotarget.10010
-- Online visualization tool: http://tanlab.ucdenver.edu/QAPC/
-- Zipped file containing their R scripts and full datasets can be downloaded here: http://tanlab.ucdenver.edu/QAPC/Downloads/Drug_Sensitvity_Metrics.zip
-
-Column descriptions in merged_auc_v20190319.1.csv.gz:
-- Cell_line: the name of the cancer cell line (CCL), harmonized across datasets by Pozdeyev et al. (2016)
-- Histology: the general histology/tissue type of the CCL according to the CCLE annotations (see DepMap-2019q1-celllines_v2.csv file from the DepMap Data Portal)
-- CCLE_ccl_name: the cell line name using CCLE nomenclature, which is a concatenation of the cell line name with the CCLE-annotated histology in all caps, separated by underscores
-- Broad_ID: the custom identifiers (formatted as ACH-######) used by the Broad's Cancer Dependency Map project to ease cell line name harmonization efforts 
-- WasDrugScreened: 1 means the cell was screened in at least one pharmacogenomic screens, and 0 means it was not screened in any of the pharmacogenomic screens
-- WasCRISPRScreened: 1 means the cell line was screened in the Avana CRISPR screen, and 0 means it was not
-- HasMutationData: 1 means the cell line had at least one recorded mutation in the MAF file (see file version below), and 0 means it was not annotated in the MAF file
-- HasGeneExpressionData: 1 means gene expression data is available for the cell line (see file version below), and 0 means it does not have gene expression information
-- HasCopyNumberData: 1 means copy number data is available for the cell line (see file version below), and 0 means it does not have copy number information
-- InCCLE: 1 means the cell line was screened in CCLE, 0 means it was not
-- InCTRP: 1 means the cell line was screened in CTRP, 0 means it was not
-- InGDSC: 1 means the cell line was screened in GDSC, 0 means it was not
-- All other columns: compound and drug names that were screened in at least one CCL in at least one database, formatted as Drug_DatabaseName
-    - NA values indictate that compound wasn't screened in the respective CCL in the respective source dataset
-    - Values are in AUC_IC50, the area under rhe dose response curve calculated from IC50 model
-
-merged_auc_v20190319.1.csv.gz
-merged_auc_v20190319.2.csv.gz:
-- NAs in Histology column (excluding most of the cell lines indicated as being from a "collaborator" in CTRP) hand-curated by searches in DepMap, COSMIC, Cellosaurus, ATCC, canSAR Black, and Cell Model Passports
-merged_auc_v20190327.3.csv.gz:
-- Reformatted to have only unique cell lines in rows
-- Cancer cell lines screened in more than one database have multiple AUC columns (column names are formatted as Drug_DatabaseName)
-- Added information on binary presence/absencee of omic annotations for each cell line (i.e. mutations, copy number, gene expression)
-- Added binary columns indicating presence in CCLE, CTRP, GDSC, drug screens in general (in 1, 2, or 3), and the Avana CRISPR screen
-- Added cell lines that have at least one type of omic data but are not in the CRISPR or pharmacogenomic screens
-
-Exploratory plots:
-```{r, eval=FALSE}
-futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
-venn_all_ccl_unmatched_pozdeyev <- venn.diagram(list("CCLE" = unique(ccle_poz$Cell_line), "CTRP" = unique(ctrp_poz$Cell_line), "GDSC" = unique(gdsc_poz$Cell_line)), resolution = 5000, main = "Overlap of cancer cell lines (CCLs) screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
-# png("./gcn_denise/pozdeyev_unmatched/pozdeyev_venn_all_ccl_unmatched.png", res = 500, units = "in", width = 6, height = 6)
-# grid.newpage()
-# grid.draw(venn_all_ccl_unmatched_pozdeyev)
-# dev.off()
-
-futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
-venn_all_drugs_unmatched_pozdeyev <- venn.diagram(list("CCLE" = unique(ccle_poz$Drug_name), "CTRP" = unique(ctrp_poz$Drug_name), "GDSC" = unique(gdsc_poz$Drug_name)), resolution = 5000, main = "Overlap of cancer cell lines (CCLs) screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
-# png("./gcn_denise/pozdeyev_unmatched/pozdeyev_venn_all_drugs_unmatched.png", res = 500, units = "in", width = 6, height = 6)
-# grid.newpage()
-# grid.draw(venn_all_drugs_unmatched_pozdeyev)
-# dev.off()
-
-num_ccl_per_hist_per_db_unmatched_bar <- ggplot(data = unique(select(auc_unmatched, Database, Cell_line, Histology))) +
-  facet_wrap(~ Database) +
-  geom_bar(aes(x = Histology, fill = Histology), alpha = 0.7) +
-  guides(fill = "none") +
-  # coord_cartesian(ylim = c(0, 130)) +
-  scale_y_continuous(breaks = seq(0, 160, by = 20), labels = seq(0, 160, by = 20)) +
-  labs(y = "Number of cell lines", title = "Number of unique cell lines per histology, grouped by database") +
-  theme(axis.text.x = element_text(angle = 60, hjust = 1))
-num_ccl_per_hist_per_db_unmatched_bar
-# ggsave("./gcn_denise/pozdeyev_unmatched/pozdeyev_ccl_per_histology_per_db_unmatched.png", num_ccl_per_hist_per_db_unmatched_bar, device = "png", dpi = 450, width = 12, height = 8, units = "in")
-
-num_ccl_per_hist_unmatched_bar <- ggplot(data = unique(select(auc_unmatched, Cell_line, Histology))) +
-  geom_bar(aes(x = Histology, fill = Histology), alpha = 0.7) +
-  guides(fill = "none") +
-  scale_y_continuous(breaks = seq(0, 220, by = 20), labels = seq(0, 220, by = 20)) +
-  labs(y = "Number of cell lines", title = "Number of unique cell lines per histology across all three databases") +
-  theme(axis.text.x = element_text(angle = 60, hjust = 1))
-num_ccl_per_hist_unmatched_bar
-# ggsave("./gcn_denise/pozdeyev_unmatched/pozdeyev_ccl_per_histology_unmatched.png", num_ccl_per_hist_unmatched_bar, device = "png", dpi = 450, width = 12, height = 8, units = "in")
-
-aucic50_per_db_unmatched <- ggplot(data = auc_unmatched) +
-  facet_wrap(~ Database, scales = "free_y") +
-  geom_histogram(aes(x = AUC_IC50, fill = Database), color = "black", alpha = 0.7, binwidth = 0.025, boundary = 0, closed = "left") +
-  scale_fill_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
-  guides(fill = "none") +
-  labs(x = "AUC IC50", y = "Frequency", title = "Distributions of AUC IC50 values for all drugs in each dataset (unmatched)")
-aucic50_per_db_unmatched
-# ggsave("./gcn_denise/pozdeyev_unmatched/pozdeyev_aucic50_per_db_unmatched.png", aucic50_per_db_unmatched, device = "png", dpi = 450, width = 12, height = 6, units = "in")
-```
-
-# Denise's GCN dataframes (Deprected)
+# (OLD) Denise's GCN dataframes
 
@@
 
-```{r, eval=TRUE}
+```{r, eval=FALSE}
 ccle <- read.delim("./data_munging/pharmacogenomics_raw_files/CCLE_NP24.2009_Drug_data_2015.02.24_20190307.csv", sep = ",", header  = TRUE, check.names = FALSE)

### 2019-04-03 19Q1.Rmd

@@
 
-# Sample info from figshare
-crispr_meta <- read.delim("./data_munging/19Q1/sample_info_20190306.csv", sep = ",", header = TRUE, na.strings = c("", NA))
-colnames(crispr_meta)[colnames(crispr_meta) == "CCLE_name"] <- "CCLE_Name"
+tcga_hist_converter <- read.delim("./data_munging/TCGA/ge_cancer_map_20190403.csv", sep = ",")
+tcga_hist_converter$Cell_line <- toupper(gsub("-", "", tcga_hist_converter$Cell_line))
+tcga_hist_converter %>% count(TCGA_classification)
 ```
@@
 ```{r, eval=FALSE}
+# Sample info from figshare
+crispr_meta <- read.delim("./data_munging/19Q1/sample_info_20190306.csv", sep = ",", header = TRUE, na.strings = c("", NA))
+colnames(crispr_meta)[colnames(crispr_meta) == "CCLE_name"] <- "CCLE_Name"
+
 crispr <- read.delim("./data_munging/19Q1/gene_effect_corrected_20190305.csv.gz", sep = ",", check.names = FALSE, header = TRUE)
@@
 ```{r, eval=FALSE}
-cn_seg <- read.delim("./data_munging/19Q1/copy_number_20190328.csv.gz", sep = ",")
-tcga_pancan <- read.delim("~/Desktop/GDC-PANCAN.masked_cnv.tsv.gz", sep = "\t")
+# Seg data is only for cell lines in teh CRISPR screen
+cn_seg <- read.delim("./data_munging/19Q1/depmap_19Q1_cn_seg_20190403.csv", sep = ",")
+cn_seg <- merge(select(ccl_histologies, Histology, Broad_ID), cn_seg, by = "Broad_ID", all.y = TRUE)
+
+tcga_seg <- read.delim("./data_munging/TCGA/GDC-PANCAN.masked_cnv.ucscxena_seg_20190403.tsv.gz", sep = "\t")
 
@@
 
-ggplot(tcga_pancan, aes(x = value)) + 
+ggplot(tcga_seg, aes(x = value)) + 
   geom_density()

### 2019-04-05 omix.Rmd
rename Denise's work to omix

--- 2019-04-03 19Q1.Rmd
@@
 library(naniar)
+library(openxlsx)
 library(reshape2)
@@
 library(VennDiagram)
+
 theme_set(theme_light())
@@
 
-## DepMap cell line metadata
+## Cell line metadata
 
-19Q1 update fixed almost all of the inconsistencies of the Primary.Disease column, though there were come capitalization inconsistencies.
+DepMap 19Q1 update fixed almost all of the inconsistencies of the Primary.Disease column, though there were come capitalization inconsistencies.
 ```{r}
@@
 ccl_info$source <- "CCLE"
-ccl_info$source_ccl_name <- strsplit(as.character(ccl_info$CCLE_Name), split = "_")
-ccl_info$source_ccl_name <- as.character(lapply(ccl_info$source_ccl_name, function(x) ifelse("[MERGED" %in% x || "NORMAL" %in% x, NA, x[1])))
-ccl_info$source_ccl_name[ccl_info$source_ccl_name == "NA"] <- NA
+ccl_info$Cell_line <- strsplit(as.character(ccl_info$CCLE_Name), split = "_")
+ccl_info$Cell_line <- as.character(lapply(ccl_info$Cell_line, function(x) ifelse("[MERGED" %in% x || "NORMAL" %in% x, NA, x[1])))
+ccl_info$Cell_line[ccl_info$Cell_line == "NA"] <- NA
 ccl_info$source_histology <- tolower(gsub("^[a-z0-9]*_", "", ccl_info$CCLE_Name, ignore.case = TRUE))
-ccl_info$source_histology <- ifelse(ccl_info$CCLE_Name == ccl_info$source_ccl_name, NA, ccl_info$source_histology)
-ccl_info$sample_ID <- with(ccl_info, paste(source, source_ccl_name, source_histology, sep = "_"))
+ccl_info$source_histology <- ifelse(ccl_info$CCLE_Name == ccl_info$CCLE_Name, NA, ccl_info$source_histology)
+
 # This CCL had a histology of "primary": Looking at the DepMap reference, this is an immortalize epithelial line from the CNS (https://depmap.org/portal/cell_line/NHAHTDD_PRIMARY), so I chanegd the histology accordingly
-ccl_info$source_histology[ccl_info$source_ccl_name == "NHAHTDD"] <- "central_nervous_system"
+ccl_info$source_histology[ccl_info$Cell_line == "NHAHTDD"] <- "central_nervous_system"
 # Convert Primary.Disease entries to all lower case to fix factorization issue
@@
 colnames(ccl_info)[colnames(ccl_info) == "DepMap_ID"] <- "Broad_ID"
+```
 
-tcga_hist_converter <- read.delim("./data_munging/TCGA/ge_cancer_map_20190403.csv", sep = ",")
-tcga_hist_converter$Cell_line <- toupper(gsub("-", "", tcga_hist_converter$Cell_line))
-tcga_hist_converter %>% count(TCGA_classification)
+Adding TCGA labels:
+```{r, eval=FALSE}
+tcga_hist_converter <- read.xlsx("./data_munging/TCGA/cell_line_annotation.xlsx", sheet = 1, startRow = 1, colNames = TRUE, rowNames = FALSE)
+tcga_hist_converter <- add_column(.data = tcga_hist_converter, TCGA_manual = NA, .after = "TCGA_combine")
+tcga_hist_converter <- tcga_hist_converter[with(tcga_hist_converter, order(primary_DepMap, subtype_DepMap, primary_site_CTRP, primary_hist_CTRP, subtype_CTRP, tissue1_GDSC)),]
+
+# For manual curation of TCGA labels
+# ccls_for_manual_tcga_curation <- filter(tcga_hist_converter, is.na(TCGA_combine))
+# ccls_for_manual_tcga_curation <- ccls_for_manual_tcga_curation[with(ccls_for_manual_tcga_curation, order(primary_DepMap, subtype_DepMap, primary_site_CTRP, primary_hist_CTRP, subtype_CTRP, tissue1_GDSC)),]
+# write.csv(ccls_for_manual_tcga_curation, "./data_munging/TCGA/cell_line_annotation_noTCGA.csv")
+tcga_hist_converter <- filter(tcga_hist_converter, !is.na(TCGA_combine))
+ccls_curated <- read.delim("./data_munging/TCGA/cell_line_annotation_noTCGA_curated.csv", sep = ",", row.names = 1)
+tcga_histsconverter <- bind_rows(tcga_hist_converter, ccls_curated)
+tcga_hist_converter$TCGA_combine <- with(tcga_hist_converter, ifelse(is.na(TCGA_combine), as.character(TCGA_manual), TCGA_combine))
+# write.csv(tcga_hist_converter, "./data_munging/TCGA/cell_line_annotation_curated_sally_20190404.csv")
 ```
@@
 ```{r}
-ccl_histologies <- select(ccl_info, source_ccl_name, source_histology, CCLE_ccl_name, Broad_ID) %>% drop_na(source_ccl_name)
-colnames(ccl_histologies)[colnames(ccl_histologies) == "source_ccl_name"] <- "Cell_line" 
+ccl_histologies <- select(ccl_info, Cell_line, source_histology, CCLE_ccl_name, Broad_ID) %>% drop_na(Cell_line)
 colnames(ccl_histologies)[colnames(ccl_histologies) == "source_histology"] <- "Histology"
@@
 ```{r, eval=FALSE}
+ccl_info$sample_ID <- with(ccl_info, paste(source, source_ccl_name, source_histology, sep = "_"))
+
 ccle <- read.delim("./data_munging/pharmacogenomics_raw_files/CCLE_NP24.2009_Drug_data_2015.02.24_20190307.csv", sep = ",", header  = TRUE, check.names = FALSE)

### 2019-04-05 19Q1.Rmd
created 19Q1.Rmd for htscreens work

--- 2019-04-02 19Q1.Rmd
@@
 
-Edited `.Renviron` to avoid "Error: memory exhausted (limit reached?)" when melting the GE dataset, as per the suggestion from [StackOverflow](https://stackoverflow.com/questions/51295402/r-on-macos-error-vector-memory-exhausted-limit-reached):å
-```
-cd ~
-touch .Renviron
-open .Renviron
-# Added following line to .Renviron:
-R_MAX_VSIZE=100Gb
-```
-
 ```{r}
@@
 
-# DATA MANAGEMENT {.tabset .tabset-fade .tabset-pills}
+# DATA
 
@@
 
-- For their universal ccancer cell line nomenclature, they reverted back to `Broad_ID` from 18Q3 rather than `DepMap_ID` that was used in 18Q4
+- For their universal ccancer cell line nomenclature, they reverted back to `Broad_ID` from 18Q3 rather than `DepMap_ID` that was used in 19Q1
 - The `Primary.Disease` column of the cell line metadata file is more consistently named (`Subtype.Disease` now has the specific disease annotations), though there are a couple capitalization inconsistencies
@@
 colnames(ccl_info)[colnames(ccl_info) == "DepMap_ID"] <- "Broad_ID"
+```
 
-# Sample info from figshare
-crispr_meta <- read.delim("./data_munging/19Q1/sample_info_20190306.csv", sep = ",", header = TRUE, na.strings = c("", NA))
-colnames(crispr_meta)[colnames(crispr_meta) == "CCLE_name"] <- "CCLE_Name"
+Adding TCGA labels:
+```{r, eval=FALSE}
+tcga_hist_converter <- read.xlsx("./data_munging/TCGA/cell_line_annotation.xlsx", sheet = 1, startRow = 1, colNames = TRUE, rowNames = FALSE)
+tcga_hist_converter <- add_column(.data = tcga_hist_converter, TCGA_manual = NA, .after = "TCGA_combine")
+tcga_hist_converter <- tcga_hist_converter[with(tcga_hist_converter, order(primary_DepMap, subtype_DepMap, primary_site_CTRP, primary_hist_CTRP, subtype_CTRP, tissue1_GDSC)),]
+
+# For manual curation of TCGA labels
+# ccls_for_manual_tcga_curation <- filter(tcga_hist_converter, is.na(TCGA_combine))
+# ccls_for_manual_tcga_curation <- ccls_for_manual_tcga_curation[with(ccls_for_manual_tcga_curation, order(primary_DepMap, subtype_DepMap, primary_site_CTRP, primary_hist_CTRP, subtype_CTRP, tissue1_GDSC)),]
+# write.csv(ccls_for_manual_tcga_curation, "./data_munging/TCGA/cell_line_annotation_noTCGA.csv")
+tcga_hist_converter <- filter(tcga_hist_converter, !is.na(TCGA_combine))
+ccls_curated <- read.delim("./data_munging/TCGA/cell_line_annotation_noTCGA_curated.csv", sep = ",", row.names = 1)
+tcga_histsconverter <- bind_rows(tcga_hist_converter, ccls_curated)
+tcga_hist_converter$TCGA_combine <- with(tcga_hist_converter, ifelse(is.na(TCGA_combine), as.character(TCGA_manual), TCGA_combine))
+# write.csv(tcga_hist_converter, "./data_munging/TCGA/cell_line_annotation_curated_sally_20190404.csv")
+```
+
+## G2P
+
+```{r}
+g2p <- read.delim("./data_munging/g2p_full_level_A_dataset_NEW_DEC_2_2018_withGroupedLineages.csv", sep = "\t", header = TRUE)
+g2p[, 1:2] <- NULL
+g2p <- merge(g2p, lineage_converter, by = "grouped_general_doid", all.x = TRUE)
+
+g2p$Drug <- tolower(g2p$Drug)
+g2p[g2p == -1] <- NA
+g2p$Ref[g2p$Ref == "None"] <- NA
+g2p$Alt[g2p$Alt == "None"] <- NA
+g2p$Drug_Gene <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene), NA, paste0(g2p$Drug, "_", g2p$Gene))
+g2p$Drug_Gene_Lin <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene) | is.na(g2p$group_general_lineage_name), NA, paste0(g2p$Drug, "_", g2p$Gene, "_", g2p$group_general_lineage_name))
+g2p$position <- paste0("g.chr", g2p$Chromosome, ":", g2p$End, g2p$Ref, ">", g2p$Alt)
+g2p$position <- ifelse(grepl("NA", g2p$position), NA, g2p$position)
+g2p_filt <- subset(g2p, grepl("^CID", g2p$DrugID))
+
+g2p_dgls <-  unique(g2p_filt$Drug_Gene_Lin[!is.na(g2p_filt$Drug_Gene_Lin)])
+g2p_druggenes <- unique(g2p_filt$Drug_Gene[!is.na(g2p_filt$Drug_Gene)])
+g2p_drugs <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[1]))
+g2p_genes <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[2]))
+g2p_lins <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[3]))
+g2p_druggenes
+g2p_drugs
+g2p_genes
+g2p_lins
+
+# Order and genes taken from pink heatmapo from Daniel's analyses
+g2p_genes <- c("EGFR", "KRAS", "ERBB2", "ERBB3", "MET", "ALK", "ROS1", "PDGFRA", "ABL1", "KIT", "PDGFRB", "PDGFB", "BRAF", "G6PD", "RET", "BRCA1", "BRCA2", "UGT1A1", "TSC1", "TSC2", "AKT1", "IDH2", "DPYD", "ESR1", "CYP19A1", "TPMT", "FLT3", "NPM1", "DNMT3A", "PML", "PTCH1", "JAK2", "MYD88", "MGMT")
+```
+
+```{r}
+# levels(g2p_filt$Phenotype.Description)
+unique(g2p_filt$group_general_lineage_name)
+levels(g2p_filt$group_general_lineage_name)
+
+g2p_nonCID <- subset(g2p, !grepl("^CID", g2p$DrugID))
+summ <- g2p_nonCID %>% group_by(Drug, DrugID) %>% tally() %>% summarize(DrugID = DrugID, n = n, percent = formatC(n / 402 * 100, digits = 6, format = "f"))
+summ
 ```
@@
 
-## CRISPR
+## Drug screens
+
+### Merge drug data and annotations
+
+```{r}
+test <- filter(maf_df, Hugo_Symbol %in% g2p_genes) %>% count(Hugo_Symbol, CCLE_Name)
+test <- test[order(test$n, decreasing = TRUE),]
+```
+
+`r nrow(filter(test, n == 1))`/`r nrow(test)` gene-cell line combinations have more than one mutation in the MAF file. This is corrected in the point mutation filtering done below.
 
 ```{r, eval=FALSE}
-crispr <- read.delim("./data_munging/19Q1/gene_effect_corrected_20190305.csv.gz", sep = ",", check.names = FALSE, header = TRUE)
+# Drug metadata
+drug_meta <- read.delim("./data_munging/drug_id_drug_name_table_10_12_2018.tsv", sep = "\t", header = FALSE)
+colnames(drug_meta) <- c("CID", "Drug")
+drug_meta$Drug <- tolower(drug_meta$Drug)
+maf_df_g2p <- filter(maf_df, Hugo_Symbol %in% g2p_genes)
+ge_filt_18Q3 <- filter(ge_melt_18Q3, Hugo_Symbol %in% g2p_genes)
+# ge_filt_19Q1 <- filter(ge_melt_19Q1, Hugo_Symbol %in% g2p_genes)
+cn_filt <- filter(cn_melt, Hugo_Symbol %in% g2p_genes)
+
+# CCLE
+ccle <- read.delim("./data_munging/data_drug_auc_ccle_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
+ccle <- merge(drug_meta, ccle, by = "CID")
+ccle_melt <- melt(ccle, id.vars = c("CID", "Drug"), measure.vars = colnames(ccle)[3:ncol(ccle)], variable.name = "accession_id", value.name = "ActArea")
+ccle_grid <- expand.grid("accession_id" = unique(ccle_melt$accession_id), "Hugo_Symbol" = g2p_genes)
+ccle_data <- merge(ccle_grid, ccle_melt, by = "accession_id", all.x = TRUE)
+ccle_data <- merge(ccle_data, ccl_converter, by = "accession_id", all.x = TRUE)
+ccle_data <- merge(ccle_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
+ccle_data$Mutation_Status_Nonsilent <- ifelse(is.na(ccle_data$Mutation_Status_Nonsilent), "Wildtype", ccle_data$Mutation_Status_Nonsilent)
+ccle_data <- merge(ccle_data, ge_filt_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
+# ccle_data <- merge(ccle_data, ge_filt_19Q1, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
+ccle_data <- merge(ccle_data, cn_filt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
+ccle_data$Hugo_Symbol <- factor(ccle_data$Hugo_Symbol)
+ccle_data$ActArea <- as.numeric(ccle_data$ActArea)
+# CCLE AUC is actually AOC
+# assuming scale is 0-8, transform to range between 0 and 1
+# get AUC by 1 - AOC
+ccle_data$AUC <- 1 - (ccle_data$ActArea / 8)
+ccle_data <- filter(ccle_data, !is.na(ccle_data$AUC))
+ccle_data$AUC_zscore <- (ccle_data$AUC - mean(ccle_data$AUC)) / sd(ccle_data$AUC)
+ccle_data$Color_Nonsilent <- ifelse(ccle_data$Mutation_Status_Nonsilent == "Wildtype", "palegreen3", "springgreen4")
+ccle_data$Color_Nonsilent <- factor(ccle_data$Color_Nonsilent)
+ccle_data$Drug_Gene <- paste0(ccle_data$Drug, "_", ccle_data$Hugo_Symbol)
+ccle_data$Drug_Gene_Lin <- paste0(ccle_data$Drug, "_", ccle_data$Hugo_Symbol, "_", ccle_data$group_general_lineage_name)
+saveRDS(ccle_data, "./data_munging/rds/ccle_data_19Q1_g2pgenes.rds", compress = "xz")
+
+# CTRP
+ctrp <- read.delim("./data_munging/data_drug_auc_ctrp_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
+ctrp <- merge(drug_meta, ctrp, by = "CID")
+ctrp_melt <- melt(ctrp, id.vars = c("CID", "Drug"), measure.vars = colnames(ctrp)[3:ncol(ctrp)], variable.name = "accession_id", value.name = "AUC")
+ctrp_grid <- expand.grid("accession_id" = unique(ctrp_melt$accession_id), "Hugo_Symbol" = g2p_genes)
+ctrp_data <- merge(ctrp_grid, ctrp_melt, by = "accession_id", all.x = TRUE)
+ctrp_data <- merge(ctrp_data, ccl_converter, by = "accession_id", all.x = TRUE)
+ctrp_data <- merge(ctrp_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
+ctrp_data$Mutation_Status_Nonsilent <- ifelse(is.na(ctrp_data$Mutation_Status_Nonsilent), "Wildtype", ctrp_data$Mutation_Status_Nonsilent)
+ctrp_data <- merge(ctrp_data, ge_filt_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
+# ctrp_data <- merge(ctrp_data, ge_filt_19Q1, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
+ctrp_data <- merge(ctrp_data, cn_filt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
+ctrp_data$Hugo_Symbol <- factor(ctrp_data$Hugo_Symbol)
+ctrp_data$AUC <- as.numeric(ctrp_data$AUC)
+ctrp_data <- filter(ctrp_data, !is.na(ctrp_data$AUC))
+ctrp_data$AUC_zscore <- (ctrp_data$AUC - mean(ctrp_data$AUC)) / sd(ctrp_data$AUC)
+ctrp_data$Color_Nonsilent <- ifelse(ctrp_data$Mutation_Status_Nonsilent == "Wildtype", "slategray3", "steelblue4")
+ctrp_data$Color_Nonsilent <- factor(ctrp_data$Color_Nonsilent)
+ctrp_data$Drug_Gene <- paste0(ctrp_data$Drug, "_", ctrp_data$Hugo_Symbol)
+ctrp_data$Drug_Gene_Lin <- paste0(ctrp_data$Drug, "_", ctrp_data$Hugo_Symbol, "_", ctrp_data$group_general_lineage_name)
+saveRDS(ctrp_data, "./data_munging/rds/ctrp_data_19Q1_g2pgenes.rds", compress = "xz")
+
+# GDSC
+gdsc <- read.delim("./data_munging/data_drug_auc_gdsc_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
+gdsc <- merge(drug_meta, gdsc, by = "CID")
+gdsc_melt <- melt(gdsc, id.vars = c("CID", "Drug"), measure.vars = colnames(gdsc)[3:ncol(gdsc)], variable.name = "accession_id", value.name = "AUC")
+gdsc_grid <- expand.grid("accession_id" = unique(gdsc_melt$accession_id), "Hugo_Symbol" = g2p_genes)
+gdsc_data <- merge(gdsc_grid, gdsc_melt, by = "accession_id", all.x = TRUE)
+gdsc_data <- merge(gdsc_data, ccl_converter, by = "accession_id", all.x = TRUE)
+gdsc_data <- merge(gdsc_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
+gdsc_data$Mutation_Status_Nonsilent <- ifelse(is.na(gdsc_data$Mutation_Status_Nonsilent), "Wildtype", gdsc_data$Mutation_Status_Nonsilent)
+gdsc_data <- merge(gdsc_data, ge_filt_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
+# gdsc_data <- merge(gdsc_data, ge_filt_19Q1, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
+gdsc_data <- merge(gdsc_data, cn_filt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
+gdsc_data$Hugo_Symbol <- factor(gdsc_data$Hugo_Symbol)
+gdsc_data$AUC <- as.numeric(gdsc_data$AUC)
+gdsc_data <- filter(gdsc_data, !is.na(gdsc_data$AUC))
+gdsc_data$AUC_zscore <- (gdsc_data$AUC - mean(gdsc_data$AUC)) / sd(gdsc_data$AUC)
+gdsc_data$Color_Nonsilent <- ifelse(gdsc_data$Mutation_Status_Nonsilent == "Wildtype", "paleturquoise3", "turquoise4")
+gdsc_data$Color_Nonsilent <- factor(gdsc_data$Color_Nonsilent)
+gdsc_data$Drug_Gene <- paste0(gdsc_data$Drug, "_", gdsc_data$Hugo_Symbol)
+gdsc_data$Drug_Gene_Lin <- paste0(gdsc_data$Drug, "_", gdsc_data$Hugo_Symbol, "_", gdsc_data$group_general_lineage_name)
+saveRDS(gdsc_data, "./data_munging/rds/gdsc_data_19Q1_g2pgenes.rds", compress = "xz")
 ```
 
-# Pozdeyev et al. (2016) summary
-
---------------------------------------------------------------------------------
-
-```{r}
-ccl_histologies <- select(ccl_info, source_ccl_name, source_histology, CCLE_ccl_name, Broad_ID) %>% drop_na(source_ccl_name)
-colnames(ccl_histologies)[colnames(ccl_histologies) == "source_ccl_name"] <- "Cell_line" 
-colnames(ccl_histologies)[colnames(ccl_histologies) == "source_histology"] <- "Histology"
-
-# Account for cell line aliases and missing histologies
-auc_na_histologies <- read.delim("./data_munging/pozdeyev2016/auc_na_histologies.csv", sep = ",", row.names = 1)
-
-auc_na_histologies$accession_id <- NULL
-auc_na_histologies$Notes <- NULL
-auc_na_histologies$Histology <- ifelse(auc_na_histologies$Histology == "", NA, as.character(auc_na_histologies$Histology))
-auc_na_histologies$CCLE_ccl_name <- ifelse(auc_na_histologies$CCLE_ccl_name  == "", NA, as.character(auc_na_histologies$CCLE_ccl_name ))
-auc_na_histologies$Broad_ID <- ifelse(auc_na_histologies$Broad_ID == "", NA, as.character(auc_na_histologies$Broad_ID))
-
-ccl_histologies <- subset(ccl_histologies, !(Broad_ID %in% auc_na_histologies$Broad_ID))
-# Bind DepMap histologies and curated histologies
-ccl_histologies <- bind_rows(ccl_histologies, auc_na_histologies)
-```
-
-For plotting:
-
-- `c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")`
-- `c("springgreen4", "steelblue4", "turquoise4")`
-
-## Data wrangling
+### Filter drug data
 
 ```{r, eval=FALSE}
-ccle_poz <- read.delim("./data_munging/pozdeyev2016/CCLE_drug_response_metrics.csv.gz", sep = ",")
+ccle_data <- readRDS("./data_munging/rds/ccle_data_19Q1_g2pgenes.rds")
+ccle_data_ptmuts <- filter(ccle_data, Reference_Allele == 1 | Reference_Allele == 0 | is.na(Reference_Allele))
+ccle_data_ptmuts$Keep_PtMut_Tests <- ifelse(ccle_data_ptmuts$Reference_Allele == 1 | is.na(ccle_data_ptmuts$Reference_Allele), TRUE, ifelse(ccle_data_ptmuts$Tumor_Seq_Allele1 == 1, TRUE, FALSE))
+ccle_data_ptmuts <- filter(ccle_data_ptmuts, Keep_PtMut_Tests == TRUE)
+# Remove columns that lead to duplicate mutation entries
+ccle_data_ptmuts <- subset(ccle_data_ptmuts, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, Genome_Change, Keep_PtMut_Tests))
+ccle_data_ptmuts$Dataset <- "CCLE"
+ccle_data_ptmuts$Hugo_Symbol <- ordered(ccle_data_ptmuts$Hugo_Symbol, levels = g2p_genes)
+ccle_data_ptmuts <- unique(ccle_data_ptmuts)
+saveRDS(ccle_data_ptmuts, "./data_munging/rds/ccle_data_19Q1_g2pgenes_ptmuts.rds", compress = "xz")
 
-# ccle_test <- merge(select(ccle_poz, Drug_name, Cell_line, AUC_IC50), select(filter(auc, Database == "CCLE"), Drug_name, Cell_line, AUC_IC50), by = c("Drug_name", "Cell_line"), suffixes = c("_unmatched", "_matched_all_pairs"), all = TRUE)
+ctrp_data <- readRDS("./data_munging/rds/ctrp_data_19Q1_g2pgenes.rds")
+ctrp_data_ptmuts <- filter(ctrp_data, Reference_Allele == 1 | Reference_Allele == 0 | is.na(Reference_Allele))
+ctrp_data_ptmuts$Keep_PtMut_Tests <- ifelse(ctrp_data_ptmuts$Reference_Allele == 1 | is.na(ctrp_data_ptmuts$Reference_Allele), TRUE, ifelse(ctrp_data_ptmuts$Tumor_Seq_Allele1 == 1, TRUE, FALSE))
+ctrp_data_ptmuts <- filter(ctrp_data_ptmuts, Keep_PtMut_Tests == TRUE)
+# Remove columns that lead to duplicate mutation entries
+ctrp_data_ptmuts <- subset(ctrp_data_ptmuts, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, Genome_Change, Keep_PtMut_Tests))
+ctrp_data_ptmuts$Dataset <- "CTRP"
+ctrp_data_ptmuts$Hugo_Symbol <- ordered(ctrp_data_ptmuts$Hugo_Symbol, levels = g2p_genes)
+ctrp_data_ptmuts <- unique(ctrp_data_ptmuts)
+saveRDS(ctrp_data_ptmuts, "./data_munging/rds/ctrp_data_19Q1_g2pgenes_ptmuts.rds", compress = "xz")
 
-ctrp_poz <- read.delim("./../htscreens_giant_files/pozdeyev2016/CTRP_drug_response_metrics.csv.gz", sep = ",")
-# ctrp_test <- merge(select(ctrp_poz, Drug_name, Cell_line, AUC_IC50), select(filter(auc, Database == "CTRP"), Drug_name, Cell_line, AUC_IC50), by = c("Drug_name", "Cell_line"), suffixes = c("_unmatched", "_matched_all_pairs"), all = TRUE)
-
-gdsc_poz <- read.delim("./data_munging/pozdeyev2016/GDSC_drug_response_metrics.csv.gz", sep = ",")
-# gdsc_test <- merge(select(gdsc_poz, Drug_name, Cell_line, AUC_IC50), select(filter(auc, Database == "GDSC"), Drug_name, Cell_line, AUC_IC50), by = c("Drug_name", "Cell_line"), suffixes = c("_unmatched", "_matched_all_pairs"), all = TRUE)
-
-auc <- bind_rows(ccle_poz, ctrp_poz, gdsc_poz)
-
-# Harmonize Pozdeyev cell line names with DepMap
-auc$Cell_line <- toupper(gsub("-", "", auc$Cell_line))
-auc$Cell_line <- ifelse(auc$Cell_line == "K052", "KO52", auc$Cell_line)
-auc$Cell_line <- ifelse(auc$Cell_line == "OVCAR3", "NIHOVCAR3", auc$Cell_line)
-auc$Cell_line <- ifelse(auc$Cell_line == "OVCAR3", "NIHOVCAR3", auc$Cell_line)
-auc$Cell_line <- ifelse(auc$Cell_line == "TI73", "T173", auc$Cell_line)
-auc <- merge(ccl_histologies, auc, by = "Cell_line", all.y = TRUE)
-
-auc$WasDrugScreened <- 1
-ccls_not_drugscreened <- filter(ccl_histologies, Cell_line %in% setdiff(ccl_histologies$Cell_line, auc_wide$Cell_line))
-ccls_not_drugscreened$WasDrugScreened <- 0
-
-auc$AUC_IC50 <- as.numeric(as.character(auc$AUC_IC50))
-# auc$sample_ID <- with(auc, paste(Database, Cell_line, Histology, sep = "_"))
-auc$Drug_name_Database <- with(auc, paste(Drug_name, Database, sep = "_"))
-
-num_auc_per_db <- auc %>% count(Database)
-
-# Identify cell lines without histology indications. Write to file to edit for merging back to ccl_histologies file
-# test <- filter(auc, is.na(Histology))[, 1:10]
-# auc_na_hists <- unique(filter(auc, is.na(Histology))$Cell_linet)
-# write.csv(auc_na_hists, "./data_munging/pozdeyev2016/auc_na_histologies.csv")
-
-# Create merged dataset with sample_ids in the rows and drugs across the columns
-auc_wide <- dcast(auc, Cell_line + Histology + CCLE_ccl_name + Broad_ID + WasDrugScreened ~ Drug_name_Database, value.var = "AUC_IC50", fun.aggregate = mean, fill = 1000000)
-auc_wide[auc_wide == 1000000] <- ""
-auc_wide <- auc_wide %>% group_by(Cell_line, Histology, CCLE_ccl_name, Broad_ID, WasDrugScreened) %>% summarise_all(funs(trimws(paste(., collapse = ""))))
-auc_wide[auc_wide == ""] <- NA
-
-auc_all <- bind_rows(auc_wide, ccls_not_drugscreened)
-
-auc_all <- add_column(auc_all, InCCLE = ifelse(auc_all$Cell_line %in% unique(ccle_poz$Cell_line), 1, 0), .after = "Broad_ID")
-auc_all <- add_column(auc_all, InCTRP = ifelse(auc_all$Cell_line %in% unique(ctrp_poz$Cell_line), 1, 0), .after = "Broad_ID")
-auc_all <- add_column(auc_all, InGDSC = ifelse(auc_all$Cell_line %in% unique(gdsc_poz$Cell_line), 1, 0), .after = "Broad_ID")
-
-auc_all <- add_column(auc_all, WasCRISPRScreened = ifelse(auc_all$Broad_ID %in% crispr_meta$Broad_ID, 1, 0), .after = "WasDrugScreened")
-auc_all <- add_column(auc_all, HasCopyNumberData = ifelse(auc_all$Broad_ID %in% unique(cn_melt$Broad_ID)[!is.na(unique(cn_melt$Broad_ID))], 1, 0), .after = "WasCRISPRScreened")
-auc_all <- add_column(auc_all, HasGeneExpressionData = ifelse(auc_all$Broad_ID %in% unique(ge_melt$Broad_ID)[!is.na(unique(ge_melt$Broad_ID))], 1, 0), .after = "WasCRISPRScreened")
-auc_all <- add_column(auc_all, HasMutationData = ifelse(auc_all$Broad_ID %in% unique(maf_df$Broad_ID)[!is.na(unique(maf_df$Broad_ID))], 1, 0), .after = "WasCRISPRScreened")
-
-# auc_all[, -c(1:4)] <- apply(auc_all[, -c(1:4)], MARGIN = 2, FUN = as.numeric)
-auc_all <- subset(auc_all, !(WasDrugScreened == 0 & WasCRISPRScreened == 0 & HasMutationData == 0 & HasGeneExpressionData == 0 & HasCopyNumberData == 0))
-# write.csv.gz(auc_all, file = "./data_munging/pozdeyev2016/merged_auc_v20190402.4.csv.gz", row.names = FALSE, na = "NA")
-
-# test <- as.data.frame(table(auc_all$Cell_line))
-# test <- filter(auc_all, Cell_line %in% c("KMH2", "MS1", "TT"))[, 1:12]
+gdsc_data <- readRDS("./data_munging/rds/gdsc_data_19Q1_g2pgenes.rds")
+gdsc_data_ptmuts <- filter(gdsc_data, Reference_Allele == 1 | Reference_Allele == 0 | is.na(Reference_Allele))
+gdsc_data_ptmuts$Keep_PtMut_Tests <- ifelse(gdsc_data_ptmuts$Reference_Allele == 1 | is.na(gdsc_data_ptmuts$Reference_Allele), TRUE, ifelse(gdsc_data_ptmuts$Tumor_Seq_Allele1 == 1, TRUE, FALSE))
+gdsc_data_ptmuts <- filter(gdsc_data_ptmuts, Keep_PtMut_Tests == TRUE)
+# Remove columns that lead to duplicate mutation entries
+gdsc_data_ptmuts <- subset(gdsc_data_ptmuts, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, Genome_Change, Keep_PtMut_Tests))
+gdsc_data_ptmuts$Dataset <- "GDSC"
+gdsc_data_ptmuts$Hugo_Symbol <- ordered(gdsc_data_ptmuts$Hugo_Symbol, levels = g2p_genes)
+gdsc_data_ptmuts <- unique(gdsc_data_ptmuts)
+saveRDS(gdsc_data_ptmuts, "./data_munging/rds/gdsc_data_19Q1_g2pgenes_ptmuts.rds", compress = "xz")
 ```
@@
 ```{r}
-auc_all <- read.delim("./data_munging/pozdeyev2016/merged_auc_v20190402.4.csv.gz", sep = ",", check.names = FALSE)
+ccle_data <- readRDS("./data_munging/rds/ccle_data_19Q1_g2pgenes.rds")
+ctrp_data <- readRDS("./data_munging/rds/ctrp_data_19Q1_g2pgenes.rds")
+gdsc_data <- readRDS("./data_munging/rds/gdsc_data_19Q1_g2pgenes.rds")
+ccle_data_ptmuts <- readRDS("./data_munging/rds/ccle_data_19Q1_g2pgenes_ptmuts.rds")
+ctrp_data_ptmuts <- readRDS("./data_munging/rds/ctrp_data_19Q1_g2pgenes_ptmuts.rds")
+gdsc_data_ptmuts <- readRDS("./data_munging/rds/gdsc_data_19Q1_g2pgenes_ptmuts.rds")
 
-# Unique drugs across all datasets
-length(unique(sapply(strsplit(as.character(colnames(auc_all)[13:length(colnames(auc_all))]), split = "_"), function(x) x[1])))
+# Filter drug screen datasets for G2P drug-gene associations
+ccle_data_g2p <- filter(ccle_data_ptmuts, Drug_Gene %in% g2p_druggenes)
+ccle_data_g2p$Mutation_Status_Nonsilent <- factor(ccle_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
+ctrp_data_g2p <- filter(ctrp_data_ptmuts, Drug_Gene %in% g2p_druggenes)
+ctrp_data_g2p$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
+gdsc_data_g2p <- filter(gdsc_data_ptmuts, Drug_Gene %in% g2p_druggenes)
+gdsc_data_g2p$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
 
-sum(auc_all$HasCopyNumberData)
-sum(auc_all$HasMutationData)
-sum(auc_all$HasGeneExpressionData)
-sum(auc_all$WasDrugScreened)
+# Filter drug screen datasets for G2P drug-gene-lineage associations
+ccle_data_g2p_dgl <- filter(ccle_data_ptmuts, Drug_Gene_Lin %in% g2p_dgls)
+ccle_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(ccle_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
+ctrp_data_g2p_dgl <- filter(ctrp_data_ptmuts, Drug_Gene_Lin %in% g2p_dgls)
+ctrp_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
+gdsc_data_g2p_dgl <- filter(gdsc_data_ptmuts, Drug_Gene_Lin %in% g2p_dgls)
+gdsc_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
 
-test <- filter(auc_all, HasMutationData == 1)[, 1:12]
+# Filter drug screen datasets for G2P drugs and genes
+ccle_data_g2p_grid <- filter(ccle_data_ptmuts, Drug %in% g2p_drugs)
+ccle_data_g2p_grid$Mutation_Status_Nonsilent <- factor(ccle_data_g2p_grid$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
+ctrp_data_g2p_grid <- filter(ctrp_data_ptmuts, Drug %in% g2p_drugs)
+ctrp_data_g2p_grid$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p_grid$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
+gdsc_data_g2p_grid <- filter(gdsc_data_ptmuts, Drug %in% g2p_drugs)
+gdsc_data_g2p_grid$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p_grid$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
 
-pgx_ccls <- filter(auc_all, WasDrugScreened == 1)
-crispr_ccls <- filter(auc_all, WasCRISPRScreened == 1)
-unscreened_ccls <- filter(auc_all, WasCRISPRScreened == 0 & WasDrugScreened == 0)
+# Testing
+test_ccle <- ccle_data_ptmuts %>% group_by(Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()
+test_ctrp <- ctrp_data_ptmuts %>% group_by(Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()
+test_gdsc <- gdsc_data_ptmuts %>% group_by(Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()
 
-ge_ccls <- filter(auc_all, HasGeneExpressionData == 1)
-cn_ccls <- filter(auc_all, HasCopyNumberData == 1)
-mut_ccls <- filter(auc_all, HasMutationData == 1)
-
-all_omics_ccls <- intersect(intersect(unique(ge_ccls$Cell_line), unique(cn_ccls$Cell_line)), unique(mut_ccls$Cell_line))
-sum(filter(auc_all, Cell_line %in% all_omics_ccls)$WasDrugScreened)
-
-ccle_ccls <- filter(auc_all, InCCLE == 1)
-ctrp_ccls <- filter(auc_all, InCTRP == 1)
-gdsc_ccls <- filter(auc_all, InGDSC == 1)
-
-auc_all %>% count(Histology)
+# drug_summ <- data.frame(Drug = g2p_drugs, Dataset_Count = 0)
 ```
 
-## Plots
+How many datasets screen each G2P drug?
+```{r}
+drug_summ <- data.frame(Drug = character(), Dataset_Count = integer(), stringsAsFactors = FALSE)
+
+for(drug in g2p_drugs) {
+  counter = 0
+  if(drug %in% as.character(unique(ccle_data_g2p$Drug))) { counter <- counter + 1 }
+  if(drug %in% as.character(unique(ctrp_data_g2p$Drug))) { counter <- counter + 1 }
+  if(drug %in% as.character(unique(gdsc_data_g2p$Drug))) { counter <- counter + 1 }
+  drug_summ <- rbind(drug_summ, data.frame(Drug = drug, Dataset_Count = counter))
+}
+```
+
+## CRISPR
+
+### DepMap dependency probabilities
 
 ```{r, eval=FALSE}
-futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
-venn_pgx_crispr_overlap <- venn.diagram(list("CRISPR" = unique(crispr_ccls$Cell_line), "Drug Screen" = unique(pgx_ccls$Cell_line), "Unscreened" = unique(unscreened_ccls$Cell_line)), resolution = 5000, main = "Overlap of cancer cell lines (CCLs) screened via small-molecule and CRISPR", main.fontface = "bold", lty = rep("blank", 3), fill = c("mediumpurple1", "turquoise4", "slategray3"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
-png("./gcn_denise/pozdeyev_unmatched/venn_pgx_crispr_overlap.png", res = 500, units = "in", width = 6, height = 6)
-grid.newpage()
-grid.draw(venn_pgx_crispr_overlap)
-dev.off()
-
-futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
-venn_ccl_overlap <- venn.diagram(list("CCLE" = unique(ccle_ccls$Cell_line), "CTRP" = unique(ctrp_ccls$Cell_line), "GDSC" = unique(gdsc_ccls$Cell_line)), resolution = 5000, main = "Overlap of cancer cell lines (CCLs) screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
-png("./gcn_denise/pozdeyev_unmatched/venn_ccl_overlap.png", res = 500, units = "in", width = 6, height = 6)
-grid.newpage()
-grid.draw(venn_ccl_overlap)
-dev.off()
-
-futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
-venn_omics_overlap <- venn.diagram(list("Gene Expression" = unique(ge_ccls$Cell_line), "Copy Number" = unique(cn_ccls$Cell_line), "Mutation" = unique(mut_ccls$Cell_line)), resolution = 5000, main = "Overlapping omic annotations in cancer cell lines (CCLs)", main.fontface = "bold", lty = rep("blank", 3), fill = c("yellow2", "orange", "tomato"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
-png("./gcn_denise/pozdeyev_unmatched/venn_omics_overlap.png", res = 500, units = "in", width = 6, height = 6)
-grid.newpage()
-grid.draw(venn_omics_overlap)
-dev.off()
-
-bar_ccl_per_hist <- ggplot(data = unique(select(auc_all, Cell_line, Histology))) +
-  geom_bar(aes(x = Histology, fill = Histology), alpha = 0.7) +
-  guides(fill = "none") +
-  scale_y_continuous(breaks = seq(0, 300, by = 25), labels = seq(0, 300, by = 25)) +
-  labs(y = "Number of cell lines", title = "Number of unique cell lines per histology across all cell lines") +
-  theme(axis.text.x = element_text(angle = 60, hjust = 1))
-bar_ccl_per_hist
-ggsave("./gcn_denise/pozdeyev_unmatched/barplot_ccl_per_histology.png", bar_ccl_per_hist, device = "png", dpi = 450, width = 12, height = 6, units = "in")
-
-futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
-venn_drugs_overlap <- venn.diagram(list("CCLE" = unique(ccle_poz$Drug_name), "CTRP" = unique(ctrp_poz$Drug_name), "GDSC" = unique(gdsc_poz$Drug_name)), resolution = 5000, main = "Overlap of cancer cell lines (CCLs) screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
-png("./gcn_denise/pozdeyev_unmatched/venn_drugs_overlap.png", res = 500, units = "in", width = 6, height = 6)
-grid.newpage()
-grid.draw(venn_drugs_overlap)
-dev.off()
-
-bar_ccl_per_hist_per_db <- ggplot(data = unique(select(auc, Database, Cell_line, Histology))) +
-  facet_wrap(~ Database) +
-  geom_bar(aes(x = Histology, fill = Histology), alpha = 0.7) +
-  guides(fill = "none") +
-  # coord_cartesian(ylim = c(0, 130)) +
-  scale_y_continuous(breaks = seq(0, 160, by = 20), labels = seq(0, 160, by = 20)) +
-  labs(y = "Number of cell lines", title = "Number of unique cell lines per histology, grouped by database") +
-  theme(axis.text.x = element_text(angle = 60, hjust = 1))
-bar_ccl_per_hist_per_db
-ggsave("./gcn_denise/pozdeyev_unmatched/barplot_ccl_per_histology_per_db.png", bar_ccl_per_hist_per_db, device = "png", dpi = 450, width = 12, height = 8, units = "in")
-
-bar_ccl_per_hist <- ggplot(data = unique(select(auc_all, Cell_line, Histology))) +
-  geom_bar(aes(x = Histology, fill = Histology), alpha = 0.7) +
-  guides(fill = "none") +
-  scale_y_continuous(breaks = seq(0, 220, by = 20), labels = seq(0, 220, by = 20)) +
-  labs(y = "Number of cell lines", title = "Number of unique cell lines per histology across all annotated cell lines") +
-  theme(axis.text.x = element_text(angle = 60, hjust = 1))
-bar_ccl_per_hist
-ggsave("./gcn_denise/pozdeyev_unmatched/barplot_ccl_per_histology.png", bar_ccl_per_hist, device = "png", dpi = 450, width = 12, height = 8, units = "in")
-
-histo_aucic50_per_db <- ggplot(data = auc) +
-  facet_wrap(~ Database, scales = "free_y") +
-  geom_histogram(aes(x = AUC_IC50, fill = Database), color = "black", alpha = 0.7, binwidth = 0.025, boundary = 0, closed = "left") +
-  scale_fill_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
-  guides(fill = "none") +
-  labs(x = "AUC IC50", y = "Frequency", title = "Distributions of AUC IC50 values for all drugs in each dataset (unmatched)")
-histo_aucic50_per_db
-ggsave("./gcn_denise/pozdeyev_unmatched/histogram_aucic50_per_db.png", histo_aucic50_per_db, device = "png", dpi = 450, width = 12, height = 6, units = "in")
+dep <- read.delim("./data_munging/19Q1/gene_dependency_19Q1_20181115.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
+# Remove Entrez gene IDs from colnames
+colnames(dep) <- gsub(" .*", "", colnames(dep))
 ```
 
-## README
-
-DATA SOURCE
-
-- Pozdeyev, N., Yoo, M., Mackie, R., Schweppe, R.
-E., Tan, A.
-C., & Haugen, B.
-R.
-(2016).
-Integrating heterogeneous drug sensitivity data from cancer pharmacogenomic studies.
-Oncotarget, 7(32), 51619–51625.
-https://doi.org/10.18632/oncotarget.10010
-- Online visualization tool: http://tanlab.ucdenver.edu/QAPC/
-- Zipped file containing their R scripts and full datasets can be downloaded here: http://tanlab.ucdenver.edu/QAPC/Downloads/Drug_Sensitvity_Metrics.zip
-
-COLUMN DESCRIPTIONS
-
-For latest version of merged_auc dataframe:
-
-- Cell_line: the name of the cancer cell line (CCL), harmonized across datasets by Pozdeyev et al. (2016)
-- Histology: the general histology/tissue type of the CCL according to the CCLE annotations (see DepMap-2019q1-celllines_v2.csv file from the DepMap Data Portal)
-- CCLE_ccl_name: the cell line name using CCLE nomenclature, which is a concatenation of the cell line name with the CCLE-annotated histology in all caps, separated by underscores
-- Broad_ID: the custom identifiers (formatted as ACH-######) used by the Broad's Cancer Dependency Map project to ease cell line name harmonization efforts 
-- InCCLE: 1 means the cell line was screened in CCLE, 0 means it was not
-- InCTRP: 1 means the cell line was screened in CTRP, 0 means it was not
-- InGDSC: 1 means the cell line was screened in GDSC, 0 means it was not
-- WasDrugScreened: 1 means the cell was screened in at least one pharmacogenomic screens, and 0 means it was not screened in any of the pharmacogenomic screens
-- WasCRISPRScreened: 1 means the cell line was screened in the Avana CRISPR screen, and 0 means it was not
-- HasMutationData: 1 means the cell line had at least one recorded mutation in the MAF file (see file version below), and 0 means it was not annotated in the MAF file
-- HasGeneExpressionData: 1 means gene expression data is available for the cell line (see file version below), and 0 means it does not have gene expression information
-- HasCopyNumberData: 1 means copy number data is available for the cell line (see file version below), and 0 means it does not have copy number information
-- All other columns: compound and drug names that were screened in at least one CCL in at least one database, formatted as Drug_DatabaseName
-    - NA values indictate that compound wasn't screened in the respective CCL in the respective source dataset
-    - Values are in AUC_IC50, the area under rhe dose response curve calculated from IC50 model
-
-CHANGE LOG FOR MERGED_AUC DATAFRAME
-
-merged_auc_v20190319.1.csv.gz
-
-merged_auc_v20190319.2.csv.gz:
-- NAs in Histology column (excluding most of the cell lines indicated as being from a "collaborator" in CTRP) hand-curated by searches in DepMap, COSMIC, Cellosaurus, ATCC, canSAR Black, and Cell Model Passports
-
-merged_auc_v20190327.3.csv.gz:
-- Reformatted to have only unique cell lines in rows
-- Cancer cell lines screened in more than one database have multiple AUC columns (column names are formatted as Drug_DatabaseName)
-- Added information on binary presence/absencee of omic annotations for each cell line (i.e. mutations, copy number, gene expression)
-- Added binary columns indicating presence in CCLE, CTRP, GDSC, drug screens in general (in 1, 2, or 3), and the Avana CRISPR screen
-- Added cell lines that have at least one type of omic data but are not in the CRISPR or pharmacogenomic screens
-
-merged_auc_v20190402.4.csv.gz:
-- Fixed duplicate cell line rows derived from manually curating some of the CCL histologies that had been added in merged_auc_v20190319.2.csv.gz
-- Fixed HasMutationData, HasCopyNumberData, and HasGeneExpression data columns
-- Reordered columns
-
-# Compare to TCGA
-
---------------------------------------------------------------------------------
-
-Quality check: cluster TCGA samples and cell lines—verify that same tumor types cluster together rather than clustering by cell lines and tumor samples (Kaiqiao)
-
-Calculate Pearson correlations between data sets and create a heatmap (also look at Barretina et al. supplement for PCA and mutation load correlations)
+### Merge CRISPR data and annotations
 
 ```{r, eval=FALSE}
-cn_seg <- read.delim("./data_munging/19Q1/copy_number_20190328.csv.gz", sep = ",")
-tcga_pancan <- read.delim("~/Desktop/GDC-PANCAN.masked_cnv.tsv.gz", sep = "\t")
-
-ggplot(cn_seg, aes(x = log2(Segment_Mean/2))) + 
-  geom_density()
-
-ggplot(tcga_pancan, aes(x = value)) + 
-  geom_density()
+crispr <- read.delim("./data_munging/19Q1/gene_effect_19Q1_20181115.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
+# Remove Entrez gene IDs from colnames
+colnames(crispr) <- gsub(" .*", "", colnames(crispr))
 ```
 
-# (OLD) Pozdeyev et al (2016) matched data
+Merge annotation data:
+```{r, eval=FALSE}
+# Melt CRISPR dataset for merging
+crispr_melt <- melt(crispr, id.vars = "DepMap_ID", measure.vars = colnames(crispr)[2:ncol(crispr)], variable.name = "Hugo_Symbol", value.name = "Score")
+# Melt dependency probabilities dataset for merging
+dep_melt <- melt(dep, id.vars = "DepMap_ID", measure.vars = colnames(dep)[2:ncol(dep)], variable.name = "Hugo_Symbol", value.name = "Dep_Prob")
+# Merge dependency probabilities
+crispr_melt <- merge(crispr_melt, dep_melt, by = c("DepMap_ID", "Hugo_Symbol"), all.x = TRUE)
+# Merge cell line metadata
+crispr_melt <- merge(crispr_melt, ccl_info, by = "DepMap_ID", all.x = TRUE)
+crispr_melt <- merge(crispr_melt, crispr_meta, by = c("CCLE_Name", "DepMap_ID"), all.x = TRUE)
 
---------------------------------------------------------------------------------
+# Merge mutation annotations
+maf_filt_crispr <- filter(maf_df, Hugo_Symbol %in% as.character(unique(crispr_melt$Hugo_Symbol)))
+crispr_muts <- merge(crispr_melt, maf_filt_crispr, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
+crispr_muts$Hugo_Symbol <- factor(crispr_muts$Hugo_Symbol)
+crispr_muts <- crispr_muts %>% mutate(Mutation_Status_Nonsilent = if_else(is.na(Mutation_Status_Nonsilent), "Wildtype", Mutation_Status_Nonsilent))
+# Summarize number of mutant and Wildtype cell lines
+crispr_muts_summ <- crispr_muts %>% group_by(Hugo_Symbol) %>%
+  summarize(N_Nonsilent_Wildtype = sum(Mutation_Status_Nonsilent == "Wildtype"),
+            N_Nonsilent_Mutant = sum(Mutation_Status_Nonsilent == "Mutant"))
+# Merge test results back into full dataset, which restores information lost in the summarization
+crispr_data <- merge(crispr_muts_summ, crispr_muts, by = "Hugo_Symbol")
+# Add Color columns
+crispr_data$Color_Nonsilent <- ifelse(crispr_data$Mutation_Status_Nonsilent == "Wildtype", "thistle", "darkorchid")
+crispr_data$Color_Nonsilent <- factor(crispr_data$Color_Nonsilent)
 
-```{r, eval=FALSE}
-auc_matched <- read.delim("./data_munging/pharmacogenomics_raw_files/celline_stack.csv.gz", sep = ",")
-auc_matched <- merge(ccl_histologies, auc_matched , by = "Cell_line", all.y = TRUE)
-num_auc_per_db_matched <- auc_matched %>% count(Database)
-ccl_per_db_matched <- unique(select(auc_matched , Database, Cell_line))
-num_ccl_per_db_matched <- unique(select(auc_matched , Database, Cell_line)) %>% count(Database)
-# only CCLs represetented in 2 or 3 databases were included
-num_db_per_ccl_matched <- unique(select(auc_matched , Database, Cell_line)) %>% count(Cell_line)
+# Cell line lineages
+crispr_data <- merge(crispr_data, ccl_converter, by = c("CCLE_Name", "DepMap_ID"), all.x = TRUE)
+levels(crispr_data$lineage_name) <- sort(levels(crispr_data$lineage_name), decreasing = TRUE)
+# Copy number
+crispr_data <- merge(crispr_data, cn_melt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
+# Gene expression (RPKM)
+ge_crispr_18Q3 <- filter(ge_melt_18Q3, Hugo_Symbol %in% as.character(unique(crispr_melt$Hugo_Symbol)))
+# ge_crispr_19Q1 <- filter(ge_melt_19Q1, Hugo_Symbol %in% as.character(unique(crispr_melt$Hugo_Symbol)))
+crispr_data <- merge(crispr_data, ge_crispr_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
+# crispr_data <- merge(crispr_data, ge_crispr_19Q1, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
+saveRDS(crispr_data, "./../htscreens_giant_files/crispr_data_19Q1.rds", compress = "xz")
+
+# Takes a really long time to run (4+ hours)
+# crispr_data_ptmuts <- filter(crispr_data, Reference_Allele == 1 | Reference_Allele == 0 | is.na(Reference_Allele))
+# crispr_data_ptmuts$Keep_PtMut_Tests <- ifelse(crispr_data_ptmuts$Reference_Allele == 1 | is.na(crispr_data_ptmuts$Reference_Allele), TRUE, ifelse(crispr_data_ptmuts$Tumor_Seq_Allele1 == 1, TRUE, FALSE))
+# crispr_data_ptmuts <- filter(crispr_data_ptmuts, Keep_PtMut_Tests == TRUE)
+# crispr_data_ptmuts <- subset(crispr_data_ptmuts, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, Genome_Change, Keep_PtMut_Tests))
+# crispr_data_ptmuts <- unique(crispr_data_ptmuts)
+# saveRDS(crispr_data_ptmuts, "./data_munging/rds/crispr_data_19Q1_ptmuts.rds", compress = "xz")
 ```
 
-Plots:
-```{r, eval=FALSE}
-futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
-venn_ccl_matched_poz <- venn.diagram(list("CCLE" = unique(filter(ccl_per_db_matched, Database == "CCLE"))$Cell_line, "CTRP" = unique(filter(ccl_per_db_matched, Database == "CTRP"))$Cell_line, "GDSC" = unique(filter(ccl_per_db_matched, Database == "GDSC"))$Cell_line), resolution = 5000, main = "Overlap of cancer cell lines (CCLs) screened in matched_all_pairs dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
-png("./gcn_denise/pozdeyev_matched/pozdeyev_venn_ccl_matched.png", res = 500, units = "in", width = 6, height = 6)
-grid.newpage()
-grid.draw(venn_ccl_matched_poz)
-dev.off()
+```{r}
+crispr_data <- readRDS("./../htscreens_giant_files/crispr_data_19Q1.rds")
+# Run next two lines only if the file was made (see end of the last chunk)
+# crispr_data_ptmuts <- readRDS("./../htscreens_giant_files/crispr_data_19Q1_ptmuts.rds")
+# crispr_data_g2p <- filter(crispr_data_ptmuts, Hugo_Symbol %in% g2p_genes)
 
-num_ccl_per_db_matched_bar <- ggplot(data = unique(select(auc_matched , Database, Cell_line))) +
-  geom_bar(aes(x = Database, fill = Database), alpha = 0.7) +
-  scale_fill_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) + 
-  guides(fill = "none") +
-  scale_y_continuous(breaks = seq(0, 700, by = 50), labels = seq(0, 700, by = 50)) +
-  geom_text(data = num_ccl_per_db_matched, aes(x = Database, y = n + 20, label = n)) +
-  labs(y = "Number of cell lines", title = "Number of unique cell lines per dataset")
-num_ccl_per_db_matched_bar
-ggsave("./gcn_denise/pozdeyev_matched/pozdeyev_ccl_per_db_matched.png", num_ccl_per_db_matched_bar, device = "png", dpi = 450, width = 12, height = 8, units = "in")
-
-num_ccl_per_hist_per_db_matched_bar <- ggplot(data = unique(select(auc_matched , Database, Cell_line, Histology))) +
-  facet_wrap(~ Database, scales = "free_y") +
-  geom_bar(aes(x = Histology, fill = Histology), alpha = 0.7) +
-  guides(fill = "none") +
-  coord_cartesian(ylim = c(0, 130)) +
-  scale_y_continuous(breaks = seq(0, 130, by = 10), labels = seq(0, 130, by = 10)) +
-  labs(y = "Number of cell lines", title = "Number of unique cell lines per histology, grouped by database") +
-  theme(axis.text.x = element_text(angle = 60, hjust = 1))
-num_ccl_per_hist_per_db_matched_bar
-ggsave("./gcn_denise/pozdeyev_matched/pozdeyev_ccl_per_histology_per_db_matched.png", num_ccl_per_hist_per_db_matched_bar, device = "png", dpi = 450, width = 12, height = 8, units = "in")
-
-num_ccl_per_hist_matched_bar <- ggplot(data = unique(select(auc_matched , Cell_line, Histology))) +
-  geom_bar(aes(x = Histology, fill = Histology), alpha = 0.7) +
-  guides(fill = "none") +
-  coord_cartesian(ylim = c(0, 130)) +
-  scale_y_continuous(breaks = seq(0, 130, by = 10), labels = seq(0, 130, by = 10)) +
-  labs(y = "Number of cell lines", title = "Number of unique cell lines per histology across all three databases") +
-  theme(axis.text.x = element_text(angle = 60, hjust = 1))
-num_ccl_per_hist_matched_bar
-ggsave("./gcn_denise/pozdeyev_matched/pozdeyev_ccl_per_histology_matched.png", num_ccl_per_hist_matched_bar, device = "png", dpi = 450, width = 12, height = 8, units = "in")
-
-aucic50_per_db_matched <- ggplot(data = auc_matched ) +
-  facet_wrap(~ Database) +
-  geom_histogram(aes(x = AUC_IC50, fill = Database), color = "black", alpha = 0.7, binwidth = 0.025, boundary = 0, closed = "left") +
-  scale_fill_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
-  guides(fill = "none") +
-  geom_text(data = num_auc_per_db_matched, aes(x = 0.5, y = 4750, label = paste0("n = ", formatC(n, format = "d", big.mark = ",")))) +
-  scale_y_continuous(breaks = seq(0, 5000, by = 500), labels = seq(0, 5000, by = 500)) +
-  labs(x = "AUC IC50", y = "Frequency", title = "Distributions of AUC IC50 values for all drugs in each dataset (filtered by matching)")
-aucic50_per_db_matched
-ggsave("./gcn_denise/pozdeyev_matched/pozdeyev_aucic50_per_db_matched.png", aucic50_per_db_matched, device = "png", dpi = 450, width = 12, height = 6, units = "in")
+# Filter CRISPR for G2P genes in G2P
+crispr_data_ptmuts <- filter(crispr_data, Hugo_Symbol %in% g2p_genes)
+# Filter G2P CRISPR for point mutations
+crispr_data_ptmuts <- filter(crispr_data_ptmuts, Reference_Allele == 1 | Reference_Allele == 0 | is.na(Reference_Allele))
+crispr_data_ptmuts$Keep_PtMut_Tests <- ifelse(crispr_data_ptmuts$Reference_Allele == 1 | is.na(crispr_data_ptmuts$Reference_Allele), TRUE, ifelse(crispr_data_ptmuts$Tumor_Seq_Allele1 == 1, TRUE, FALSE))
+crispr_data_ptmuts <- filter(crispr_data_ptmuts, Keep_PtMut_Tests == TRUE)
+crispr_data_ptmuts <- subset(crispr_data_ptmuts, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, Genome_Change, Keep_PtMut_Tests))
+crispr_data_g2p <- unique(crispr_data_ptmuts)
+crispr_data_g2p$Hugo_Symbol <- factor(crispr_data_g2p$Hugo_Symbol, levels = g2p_genes)
+crispr_data_g2p$Mutation_Status_Nonsilent <- factor(crispr_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
 ```
-
-# (OLD) Denise's GCN dataframes
-
---------------------------------------------------------------------------------
-
-Code for Denise's graph convolutional networks analyses (see meeting notes from 6 March 2019).
-- Convert drug/compound names to all capitalized for harmonization.
-- Convert all cell line histologies to lower case with words separated by an underscore
-- Maintain same rows across all four data frames, filling with NAs as necessary
-- For each dataframe, maintain same columns for all three source datasets
-- Columns in final dataframes: `source`, `source_ccl_name`, `source_histology`, `sample_ID`, and `genes/compounds/mutations[p]`
-
-## AUC
-
-Column descriptions for `pgx_all_auc`:
-
-- `source`: the dataset from which the data comes from (either CCLE, CTRP, or GDSC)
-- `source_ccl_name`: the name of the cancer cell line (CCL) included in the source dataset
-    - Note that all CCLs (excluding matched normal tissues and "merged" CCLs) from the CCLE dataset (N = 1,645) were included in `pgx_all_auc` for imputation
-- `source_histology`: the general histology/tissue type of the CCL
-- `sample_ID`: custom identifiers for our datasets that are concatenations of the `source`, `source_ccl_name`, and `source_histology`
-- `CCLE_ccl_name`: the cell line name using CCLE nomenclature, which is a concatenation of the cell line name with the CCLE-annotated histology in all caps, separated by underscores
-- `Broad_ID`: the custom identifiers (formatted as ACH-######) used by the Broad's Cancer Dependency Map project to ease cell line name harmonization efforts 
-- All other columns: compound and drug names that were screened in at least one CCL in at least one source dataset
-    - NA values indictate that compound wasn't screened in the respective CCL in the respective source dataset
-
-```{r, eval=FALSE}
-ccle <- read.delim("./data_munging/pharmacogenomics_raw_files/CCLE_NP24.2009_Drug_data_2015.02.24_20190307.csv", sep = ",", header  = TRUE, check.names = FALSE)
-ctrp <- read.delim("./data_munging/pharmacogenomics_raw_files/CTRP_v20.data.curves_post_qc.txt.gz", sep = "\t", header  = TRUE, check.names = FALSE)
-gdsc <- read.delim("./data_munging/pharmacogenomics_raw_files/GDSC_v17.3_fitted_dose_response_20190306.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
-
-# CCLE
-## Note that ActArea is NOT an AUC value
-ccle_filt <- ccle[, c("CCLE Cell Line Name", "ActArea", "Compound")]
-ccle_filt$source_ccl_name <- sapply(strsplit(as.character(ccle_filt$`CCLE Cell Line Name`), split = "_"), function(x) x[1])
-ccle_filt$source_histology <- tolower(gsub("^[a-z0-9]*_", "", ccle_filt$`CCLE Cell Line Name`, ignore.case = TRUE))
-ccle_filt$source_histology <- ifelse(ccle_filt$`CCLE Cell Line Name` == ccle_filt$source_ccl_name, NA, ccle_filt$source_histology)
-colnames(ccle_filt)[colnames(ccle_filt) == "CCLE Cell Line Name"] <- "CCLE_ccl_name"
-ccle_filt <- merge(select(ccl_info, source, source_ccl_name, source_histology, sample_ID, CCLE_ccl_name, Broad_ID), ccle_filt, by = c("source_ccl_name", "source_histology", "CCLE_ccl_name"), all = TRUE)
-ccle_filt$compound_name <- toupper(ccle_filt$Compound)
-colnames(ccle_filt)[colnames(ccle_filt) == "ActArea"] <- "AUC"
-ccle_auc_long <- select(ccle_filt, source, source_ccl_name, source_histology, sample_ID, CCLE_ccl_name, Broad_ID, compound_name, AUC)
-ccle_auc <- dcast(ccle_auc_long, source + source_ccl_name + source_histology + sample_ID + CCLE_ccl_name + Broad_ID ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
-ccle_auc[, 7:ncol(ccle_auc)] <- ccle_auc[, 7:ncol(ccle_auc)] %>% replace_with_na_all(condition = ~.x == 10000)
-
-# CTRP
-## area_under_curve: integrated area under the sigmoid-fit concentration-response curve
-ctrp_filt <- ctrp[, c("experiment_id", "area_under_curve", "master_cpd_id")]
-ctrp_meta_ccl <- select(read.delim("./data_munging/pharmacogenomics_raw_files/CTRP_v20.meta.per_cell_line_20190306.txt"), master_ccl_id, ccl_name, ccle_primary_site)
-ctrp_meta_exp <- select(read.delim("./data_munging/pharmacogenomics_raw_files/CTRP_v20.meta.per_experiment_20190306.txt"), experiment_id, master_ccl_id)
-ctrp_meta_cpd <- select(read.delim("./data_munging/pharmacogenomics_raw_files/CTRP_v20.meta.per_compound_20190306.txt"), master_cpd_id, cpd_name)
-ctrp_keep <- merge(merge(ctrp_meta_ccl, ctrp_meta_exp, by = "master_ccl_id", all = TRUE), merge(ctrp_meta_cpd, ctrp_filt, by = "master_cpd_id", all = TRUE), by = "experiment_id", all = TRUE)
-ctrp_keep$ccl_name <- gsub("-", "", ctrp_keep$ccl_name, ignore.case = TRUE)
-ctrp_keep$cpd_name <- toupper(ctrp_keep$cpd_name)
-ctrp_keep$ccle_primary_site <- ifelse(as.character(ctrp_keep$ccle_primary_site) == "", NA, as.character(ctrp_keep$ccle_primary_site))
-ctrp_auc_long <- select(ctrp_keep, ccl_name, ccle_primary_site, cpd_name, area_under_curve)
-colnames(ctrp_auc_long) <- c("source_ccl_name", "source_histology", "compound_name", "AUC")
-ctrp_auc_long$source <- "CTRP"
-ctrp_auc_long$sample_ID <- with(ctrp_auc_long, paste(source, source_ccl_name, source_histology, sep = "_"))
-ctrp_auc_long <- merge(ctrp_auc_long, select(ccl_info, source_ccl_name, source_histology, CCLE_ccl_name, Broad_ID), by = c("source_ccl_name", "source_histology"), all.x = TRUE)
-ctrp_auc_long_div <- ctrp_auc_long
-ctrp_auc_long_div$AUC <- ctrp_auc_long_div$AUC / 100
-ctrp_auc <- dcast(ctrp_auc_long, source + source_ccl_name + source_histology + sample_ID + CCLE_ccl_name + Broad_ID ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
-ctrp_auc[, 7:ncol(ctrp_auc)] <- ctrp_auc[, 7:ncol(ctrp_auc)] %>% replace_with_na_all(condition = ~.x == 10000)
-
-# GDSC
-gdsc_meta_ccl <- select(read.delim("./data_munging/pharmacogenomics_raw_files/GDSC_Cell_Lines_Details.csv", sep = ","), Line, Site)
-## For following 4 Lines, Site == "NS"
-## Assigned new Sites by looking up cell lines in GDSC cell line portal (https://www.cancerrxgene.org/translation/CellLine#t-all)
-gdsc_meta_ccl$Site[gdsc_meta_ccl$Line == "COR-L321"] <- "lung"
-gdsc_meta_ccl$Site[gdsc_meta_ccl$Line == "SU-DHL-8"] <- "haematopoietic_and_lymphoid_tissue"
-gdsc_meta_ccl$Site[gdsc_meta_ccl$Line == "CRO-AP3"] <- "haematopoietic_and_lymphoid_tissue"
-gdsc_meta_ccl$Site[gdsc_meta_ccl$Line == "Hep_3B2_1-7"] <- "liver"
-## For tollowing line, Site did not match CCLE notation, so I changed it to CCLE notation
-gdsc_meta_ccl$Site[gdsc_meta_ccl$Line == "SW13"] <- "adrenal_cortex"
-gdsc_filt <- gdsc[, c("CELL_LINE_NAME", "DRUG_NAME", "AUC")]
-gdsc_filt$DRUG_NAME <- toupper(gdsc_filt$DRUG_NAME)
-colnames(gdsc_filt)[colnames(gdsc_filt) ==  "CELL_LINE_NAME"] <- "Line"
-gdsc_filt <- merge(gdsc_filt, gdsc_meta_ccl, by = "Line", all = TRUE)
-gdsc_filt$Line <- gsub("-", "", gdsc_filt$Line, ignore.case = TRUE)
-gdsc_auc_long <- select(gdsc_filt, Line, Site, DRUG_NAME, AUC)
-colnames(gdsc_auc_long) <- c("source_ccl_name", "source_histology", "compound_name", "AUC")
-gdsc_auc_long$source <- "GDSC"
-gdsc_auc_long$sample_ID <- with(gdsc_auc_long, paste(source, source_ccl_name, source_histology, sep = "_"))
-gdsc_auc_long$source_histology <- as.character(gdsc_auc_long$source_histology)
-gdsc_auc_long <- merge(gdsc_auc_long, select(ccl_info, source_ccl_name, source_histology, CCLE_ccl_name, Broad_ID), by = c("source_ccl_name", "source_histology"), all.x = TRUE)
-gdsc_auc <- dcast(gdsc_auc_long, source + source_ccl_name + source_histology + sample_ID + CCLE_ccl_name + Broad_ID ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
-gdsc_auc[, 7:ncol(gdsc_auc)] <- gdsc_auc[, 7:ncol(gdsc_auc)] %>% replace_with_na_all(condition = ~.x == 10000)
-
-# Bind all AUC
-pgx_auc_list <- list(ccle_auc, ctrp_auc, gdsc_auc)
-pgx_auc_names <- unique(unlist(lapply(pgx_auc_list, names)))
-pgx_all_auc <- do.call(rbind, c(lapply(pgx_auc_list, function(x) data.frame(c(x, sapply(setdiff(pgx_auc_names, names(x)), function(y) NA)), check.names = FALSE))))
-# saveRDS(pgx_all_auc, "./data_munging/19Q1/pgx_all_auc.rds", compress = "xz")
-# write.csv.gz(pgx_all_auc, "./data_munging/19Q1/pgx_all_auc.csv.gz", row.names = FALSE)
-```
-
-Compare histology representation for CCLE, CTRP, and GDSC:
-```{r, eval=FALSE}
-sort(unique(na.omit(ccle_auc_long$source_histology)))
-sort(unique(na.omit(ctrp_auc_long$source_histology)))
-sort(unique(na.omit(gdsc_auc_long$source_histology)))
-
-setdiff(unique(na.omit(ccle_auc_long$source_histology)), unique(na.omit(gdsc_auc_long$source_histology)))
-setdiff(unique(na.omit(gdsc_auc_long$source_histology)), unique(na.omit(ctrp_auc_long$source_histology)))
-```
-
-## Summary figures
-
-```{r, eval=FALSE}
-hist_auc_ccle <- ggplot(data = ccle_auc_long) +
-  geom_histogram(mapping = aes(x = AUC, fill = source), color = "black", binwidth = 0.25, boundary = 0, closed = "left") +
-  scale_x_continuous(breaks = seq(0, 8, by = 1), labels = seq(0, 8, by = 1)) +
-  scale_fill_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
-  labs(title = "Distributions of AUC/ActArea values for all drug-cell line combinations", subtitle = "CCLE", y = "Frequency", x = "ActArea") +
-  guides(fill = FALSE)
-hist_auc_ctrp <- ggplot(data = ctrp_auc_long_div) +
-  geom_histogram(mapping = aes(x = AUC, fill = source), color = "black", binwidth = 0.0125, boundary = 0, closed = "left") +
-  scale_x_continuous(breaks = seq(0, 0.3, by = 0.025), labels = seq(0, 0.3, by = 0.025)) +
-  scale_fill_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
-  labs(y = "Frequency", x = "AUC", subtitle = "CTRP", caption = "CTRP AUC values were divided by 100 prior to plotting.") +
-  guides(fill = FALSE)
-hist_auc_gdsc <- ggplot(data = gdsc_auc_long) +
-  geom_histogram(mapping = aes(x = AUC, fill = source), color = "black", binwidth = 0.025, boundary = 0, closed = "left") +
-  scale_x_continuous(breaks = seq(0, 1, by = 0.1), labels = seq(0, 1, by = 0.1)) +
-  scale_fill_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
-  labs(y = "Frequency", x = "AUC", subtitle = "GDSC") +
-  guides(fill = FALSE)
-hist_auc_ccle <- ggplot_gtable(ggplot_build(hist_auc_ccle))
-hist_auc_ctrp <- ggplot_gtable(ggplot_build(hist_auc_ctrp))
-hist_auc_gdsc <- ggplot_gtable(ggplot_build(hist_auc_gdsc))
-p_maxWidth <-  grid::unit.pmax(hist_auc_ccle$widths[2:3], hist_auc_ctrp$widths[2:3], hist_auc_gdsc$widths[2:3])
-hist_auc_ccle$widths[2:3] <- p_maxWidth
-hist_auc_ctrp$widths[2:3] <- p_maxWidth
-hist_auc_gdsc$widths[2:3] <- p_maxWidth
-hist_auc_all <- cowplot::plot_grid(hist_auc_ccle, hist_auc_ctrp, hist_auc_gdsc, nrow = 3, rel_heights = c(9, 9, 8))
-hist_auc_all
-# ggsave("./gcn_denise/hist_auc_all.png", hist_auc_all, device = "png", dpi = 450, width = 12, height = 8, units = "in")
-
-futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
-venn_ccl <- venn.diagram(list("CCLE" = unique(na.omit(ccl_info$source_ccl_name)), "CTRP" = unique(ctrp_auc_long$source_ccl_name), "GDSC" = unique(gdsc_auc_long$source_ccl_name)), resolution = 5000, main = "Overlap of cancer cell lines (CCLs) screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 0), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
-# png("./gcn_denise/venn_ccl.png")
-# grid.newpage()
-# grid.draw(venn_ccl)
-# dev.off()
-
-futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
-venn_histology <- venn.diagram(list("CCLE" = unique(na.omit(ccle_auc_long$source_histology)), "CTRP" = unique(na.omit(ctrp_auc_long$source_histology)), "GDSC" = unique(na.omit(gdsc_auc_long$source_histology))), resolution = 5000, main = "Overlap of cancer cell line histologies screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(0, 0, 0), cat.dist = c(0.001, 0.001, -0.01), cat.cex = 1.5, cex = 1, filename = NULL)
-# png("./gcn_denise/venn_histology.png")
-# grid.newpage()
-# grid.draw(venn_histology)
-# dev.off()
-
-futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
-venn_compound <- venn.diagram(list("CCLE" = unique(na.omit(ccle_auc_long$compound_name)), "CTRP" = unique(na.omit(ctrp_auc_long$compound_name)), "GDSC" = unique(na.omit(gdsc_auc_long$compound_name))), resolution = 5000, main = "Overlap of compounds screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.001, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
-# png("./gcn_denise/venn_compound.png")
-# grid.newpage()
-# grid.draw(venn_compound)
-# dev.off()
-```

### 2019-04-05 omix.Rmd
created 19Q1.Rmd for htscreens work

@@
 ---
-title: "19Q1"
+title: "Omix"
 author: "Sally Claridge"

### 2019-04-05 19Q1.Rmd
add TCGA converter file and update ccl_meta processing in 19Q1

@@
 
-## D. Charytonowicz cell line converter
+## Cell line metadata
+
+**D. Charytonowicz cell line converter**
 
 This comprehensive cancer cell line information was curated by both Daniel Charytonowicz and myself.
+
+**Might not need this anymore due to increased care taken by DepMap to harmonize disease names**
 ```{r}
-ccl_converter <- read.delim("./data_munging/cell_line_database_v1_20180911.tsv", row.names = 1, sep = "\t", header = TRUE)
-lineage_converter <- unique(ccl_converter[, c("grouped_general_doid", "group_general_lineage_name")])
+# ccl_converter <- read.delim("./data_munging/cell_line_database_v1_20180911.tsv", row.names = 1, sep = "\t", header = TRUE)
+# lineage_converter <- unique(ccl_converter[, c("grouped_general_doid", "group_general_lineage_name")])
 ```
 
-## Cell line metadata
+**DepMap metadata**
 
@@
 ```{r}
-ccl_info <- read.delim("./data_munging/19Q1/DepMap-2019q1-celllines_v2_20190305.csv", sep = ",", header = TRUE, na.strings = c("", NA))
-ccl_info$source <- "CCLE"
-ccl_info$Cell_line <- strsplit(as.character(ccl_info$CCLE_Name), split = "_")
-ccl_info$Cell_line <- as.character(lapply(ccl_info$Cell_line, function(x) ifelse("[MERGED" %in% x || "NORMAL" %in% x, NA, x[1])))
-ccl_info$Cell_line[ccl_info$Cell_line == "NA"] <- NA
-ccl_info$source_histology <- tolower(gsub("^[a-z0-9]*_", "", ccl_info$CCLE_Name, ignore.case = TRUE))
-ccl_info$source_histology <- ifelse(ccl_info$CCLE_Name == ccl_info$CCLE_Name, NA, ccl_info$source_histology)
-
-# This CCL had a histology of "primary": Looking at the DepMap reference, this is an immortalize epithelial line from the CNS (https://depmap.org/portal/cell_line/NHAHTDD_PRIMARY), so I chanegd the histology accordingly
-ccl_info$source_histology[ccl_info$Cell_line == "NHAHTDD"] <- "central_nervous_system"
+ccl_meta <- read.delim("./data_munging/19Q1/DepMap-2019q1-celllines_v2_20190305.csv", sep = ",", header = TRUE, na.strings = c("", NA))
+ccl_meta$Primary.Disease <- tolower(ccl_meta$Primary.Disease)
+ccl_meta <- subset(ccl_meta, Primary.Disease != "unknown" & Primary.Disease != "primary cells" & !grepl("MERGED", CCLE_Name, fixed = TRUE))
+ccl_meta$Cell_line <- as.character(lapply(ccl_meta$CCLE_Name, function(x) strsplit(as.character(x), split = "_")[[1]][1]))
+ccl_meta$histology <- tolower(gsub("^[a-z0-9]*_", "", ccl_meta$CCLE_Name, ignore.case = TRUE))
 # Convert Primary.Disease entries to all lower case to fix factorization issue
-ccl_info$Primary.Disease <- as.factor(tolower(ccl_info$Primary.Disease))
+ccl_meta$Primary.Disease <- as.factor(tolower(ccl_meta$Primary.Disease))
 # Harmonize ID column name and rename CCLE_Name column to fit with dataframe style
-colnames(ccl_info)[colnames(ccl_info) == "CCLE_Name"] <- "CCLE_ccl_name"
-colnames(ccl_info)[colnames(ccl_info) == "DepMap_ID"] <- "Broad_ID"
-```
-
-Adding TCGA labels:
-```{r, eval=FALSE}
-tcga_hist_converter <- read.xlsx("./data_munging/TCGA/cell_line_annotation.xlsx", sheet = 1, startRow = 1, colNames = TRUE, rowNames = FALSE)
-tcga_hist_converter <- add_column(.data = tcga_hist_converter, TCGA_manual = NA, .after = "TCGA_combine")
-tcga_hist_converter <- tcga_hist_converter[with(tcga_hist_converter, order(primary_DepMap, subtype_DepMap, primary_site_CTRP, primary_hist_CTRP, subtype_CTRP, tissue1_GDSC)),]
-
-# For manual curation of TCGA labels
-# ccls_for_manual_tcga_curation <- filter(tcga_hist_converter, is.na(TCGA_combine))
-# ccls_for_manual_tcga_curation <- ccls_for_manual_tcga_curation[with(ccls_for_manual_tcga_curation, order(primary_DepMap, subtype_DepMap, primary_site_CTRP, primary_hist_CTRP, subtype_CTRP, tissue1_GDSC)),]
-# write.csv(ccls_for_manual_tcga_curation, "./data_munging/TCGA/cell_line_annotation_noTCGA.csv")
-tcga_hist_converter <- filter(tcga_hist_converter, !is.na(TCGA_combine))
-ccls_curated <- read.delim("./data_munging/TCGA/cell_line_annotation_noTCGA_curated.csv", sep = ",", row.names = 1)
-tcga_histsconverter <- bind_rows(tcga_hist_converter, ccls_curated)
-tcga_hist_converter$TCGA_combine <- with(tcga_hist_converter, ifelse(is.na(TCGA_combine), as.character(TCGA_manual), TCGA_combine))
-# write.csv(tcga_hist_converter, "./data_munging/TCGA/cell_line_annotation_curated_sally_20190404.csv")
+colnames(ccl_meta)[colnames(ccl_meta) == "CCLE_Name"] <- "CCLE_ccl_name"
+colnames(ccl_meta)[colnames(ccl_meta) == "DepMap_ID"] <- "Broad_ID"
 ```
@@
 
-# For Denise's GCN
-pgx_ccle_ge <- merge(select(ccl_info, source, source_ccl_name, source_histology, sample_ID, CCLE_ccl_name, Broad_ID), ge_19Q1, by = "Broad_ID", all = TRUE)
-saveRDS(pgx_ccle_ge, "./data_munging/19Q1/pgx_ccle_ge.rds", compress = "xz")
-
 # Melt
@@
 maf_df_g2p <- filter(maf_df, Hugo_Symbol %in% g2p_genes)
-ge_filt_18Q3 <- filter(ge_melt_18Q3, Hugo_Symbol %in% g2p_genes)
-# ge_filt_19Q1 <- filter(ge_melt_19Q1, Hugo_Symbol %in% g2p_genes)
+ge_filt <- filter(ge_melt, Hugo_Symbol %in% g2p_genes)
 cn_filt <- filter(cn_melt, Hugo_Symbol %in% g2p_genes)
@@
 
-### DepMap dependency probabilities
-
-```{r, eval=FALSE}
-dep <- read.delim("./data_munging/19Q1/gene_dependency_19Q1_20181115.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
-# Remove Entrez gene IDs from colnames
-colnames(dep) <- gsub(" .*", "", colnames(dep))
-```
-
 ### Merge CRISPR data and annotations
@@
 crispr_melt <- melt(crispr, id.vars = "DepMap_ID", measure.vars = colnames(crispr)[2:ncol(crispr)], variable.name = "Hugo_Symbol", value.name = "Score")
-# Melt dependency probabilities dataset for merging
-dep_melt <- melt(dep, id.vars = "DepMap_ID", measure.vars = colnames(dep)[2:ncol(dep)], variable.name = "Hugo_Symbol", value.name = "Dep_Prob")
-# Merge dependency probabilities
-crispr_melt <- merge(crispr_melt, dep_melt, by = c("DepMap_ID", "Hugo_Symbol"), all.x = TRUE)
 # Merge cell line metadata
-crispr_melt <- merge(crispr_melt, ccl_info, by = "DepMap_ID", all.x = TRUE)
+crispr_melt <- merge(crispr_melt, ccl_meta, by = "DepMap_ID", all.x = TRUE)
 crispr_melt <- merge(crispr_melt, crispr_meta, by = c("CCLE_Name", "DepMap_ID"), all.x = TRUE)

### 2019-04-08 omix/omix.Rmd
reorg omix files

--- 2019-04-05 omix.Rmd
@@
 set.seed(1234)
+setwd("/Users/claris01/Box\ Sync/SallyProjects/htscreens/omix")
+
 knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
@@
 
-## D. Charytonowicz cell line converter
-
-This comprehensive cancer cell line information was curated by both Daniel Charytonowicz and myself.
-```{r}
-ccl_converter <- read.delim("./data_munging/cell_line_database_v1_20180911.tsv", row.names = 1, sep = "\t", header = TRUE)
-lineage_converter <- unique(ccl_converter[, c("grouped_general_doid", "group_general_lineage_name")])
-```
-
 ## Cell line metadata
@@
 ```{r}
-ccl_info <- read.delim("./data_munging/19Q1/DepMap-2019q1-celllines_v2_20190305.csv", sep = ",", header = TRUE, na.strings = c("", NA))
-ccl_info$source <- "CCLE"
-ccl_info$Cell_line <- strsplit(as.character(ccl_info$CCLE_Name), split = "_")
-ccl_info$Cell_line <- as.character(lapply(ccl_info$Cell_line, function(x) ifelse("[MERGED" %in% x || "NORMAL" %in% x, NA, x[1])))
-ccl_info$Cell_line[ccl_info$Cell_line == "NA"] <- NA
-ccl_info$source_histology <- tolower(gsub("^[a-z0-9]*_", "", ccl_info$CCLE_Name, ignore.case = TRUE))
-ccl_info$source_histology <- ifelse(ccl_info$CCLE_Name == ccl_info$CCLE_Name, NA, ccl_info$source_histology)
+ccl_info <- read.delim("./data/DepMap/DepMap-2019q1-celllines_v2_20190305.csv", sep = ",", header = TRUE, na.strings = c("", NA))
 
-# This CCL had a histology of "primary": Looking at the DepMap reference, this is an immortalize epithelial line from the CNS (https://depmap.org/portal/cell_line/NHAHTDD_PRIMARY), so I chanegd the histology accordingly
-ccl_info$source_histology[ccl_info$Cell_line == "NHAHTDD"] <- "central_nervous_system"
+ccl_info <- subset(ccl_info, Primary.Disease != "unknown" & Primary.Disease != "primary cells" & !grepl("MERGED", CCLE_Name, fixed = TRUE))
+ccl_info$Cell_line <- as.character(lapply(ccl_info$CCLE_Name, function(x) strsplit(as.character(x), split = "_")[[1]][1]))
+ccl_info$Histology <- tolower(gsub("^[a-z0-9]*_", "", ccl_info$CCLE_Name, ignore.case = TRUE))
+
 # Convert Primary.Disease entries to all lower case to fix factorization issue
 ccl_info$Primary.Disease <- as.factor(tolower(ccl_info$Primary.Disease))
-# Harmonize ID column name and rename CCLE_Name column to fit with dataframe style
-colnames(ccl_info)[colnames(ccl_info) == "CCLE_Name"] <- "CCLE_ccl_name"
+
+# Harmonize ID column name
 colnames(ccl_info)[colnames(ccl_info) == "DepMap_ID"] <- "Broad_ID"
+
+# Remove two rows that contain cell lines with two different histologies
+# The histologies that are kept are verified through matching in Cellosaurus and Cell Model Passports
+# KMH2, haematopoietic_and_lymphoid: https://web.expasy.org/cellosaurus/CVCL_1330, https://cellmodelpassports.sanger.ac.uk/passports/SIDM01018
+# MS1, lung: https://web.expasy.org/cellosaurus/CVCL_1429, https://cellmodelpassports.sanger.ac.uk/passports/SIDM00245
+ccl_info <- subset(ccl_info, CCLE_Name != "KMH2_THYROID" & CCLE_Name != "MS1_SKIN")
 ```
@@
 Adding TCGA labels:
-```{r, eval=FALSE}
-tcga_hist_converter <- read.xlsx("./data_munging/TCGA/cell_line_annotation.xlsx", sheet = 1, startRow = 1, colNames = TRUE, rowNames = FALSE)
-tcga_hist_converter <- add_column(.data = tcga_hist_converter, TCGA_manual = NA, .after = "TCGA_combine")
-tcga_hist_converter <- tcga_hist_converter[with(tcga_hist_converter, order(primary_DepMap, subtype_DepMap, primary_site_CTRP, primary_hist_CTRP, subtype_CTRP, tissue1_GDSC)),]
+```{r}
+tcga_hist_converter <- read.xlsx("./data/TCGA/Histology_DepMap_Xena_04052019.xlsx", sheet = 3, startRow = 1, colNames = TRUE, rowNames = FALSE)
+tcga_hist_converter$data_source <- NULL
 
-# For manual curation of TCGA labels
-# ccls_for_manual_tcga_curation <- filter(tcga_hist_converter, is.na(TCGA_combine))
-# ccls_for_manual_tcga_curation <- ccls_for_manual_tcga_curation[with(ccls_for_manual_tcga_curation, order(primary_DepMap, subtype_DepMap, primary_site_CTRP, primary_hist_CTRP, subtype_CTRP, tissue1_GDSC)),]
-# write.csv(ccls_for_manual_tcga_curation, "./data_munging/TCGA/cell_line_annotation_noTCGA.csv")
-tcga_hist_converter <- filter(tcga_hist_converter, !is.na(TCGA_combine))
-ccls_curated <- read.delim("./data_munging/TCGA/cell_line_annotation_noTCGA_curated.csv", sep = ",", row.names = 1)
-tcga_histsconverter <- bind_rows(tcga_hist_converter, ccls_curated)
-tcga_hist_converter$TCGA_combine <- with(tcga_hist_converter, ifelse(is.na(TCGA_combine), as.character(TCGA_manual), TCGA_combine))
-# write.csv(tcga_hist_converter, "./data_munging/TCGA/cell_line_annotation_curated_sally_20190404.csv")
+tcga_hist_converter_depmap <- filter(tcga_hist_converter, grepl("^ACH", sample_ID))
+tcga_hist_converter_tcga <- filter(tcga_hist_converter, grepl("^TCGA", sample_ID))
+colnames(tcga_hist_converter_depmap) <- c("Broad_ID", "TCGA_classification")
+colnames(tcga_hist_converter_tcga) <- c("sample", "TCGA_classification")
+
+ccl_info <- merge(ccl_info, tcga_hist_converter_depmap, by = "Broad_ID", all.x = TRUE)
 ```
-
-## Omics
 
@@
 ```{r, eval=FALSE}
-maf_raw <- read.delim("./data_munging/19Q1/depmap_19Q1_mutation_calls_20190305.csv.gz", header = TRUE, sep = ",", row.names = 1)
+maf_raw <- read.delim("./../data_munging/19Q1/depmap_19Q1_mutation_calls_20190305.csv.gz", header = TRUE, sep = ",", row.names = 1)
 # Harmonize ID column name
@@
 
-saveRDS(maf_df, "./data_munging/19Q1/maf_df_19Q1.rds", compress = "xz")
+saveRDS(maf_df, "./../data_munging/19Q1/maf_df_19Q1.rds", compress = "xz")
 ```
@@
 ```{r, eval=FALSE}
-cn <- read.delim("./data_munging/19Q1/public_19Q1_gene_cn_20190305.csv.gz", sep = ",", check.names = FALSE, header = TRUE)
+cn <- read.delim("./../data_munging/19Q1/public_19Q1_gene_cn_20190305.csv.gz", sep = ",", check.names = FALSE, header = TRUE)
 # Remove Entrez gene IDs from colnames, format is "Hugo_Symbol (Entrez ID)"
@@
 cn_melt <- melt(data = cn, id.vars = "Broad_ID", measure.vars = colnames(cn[2:ncol(cn)]), variable.name = "Hugo_Symbol", value.name = "CN")
-saveRDS(cn_melt, "./data_munging/19Q1/cn_melt_19Q1.rds", compress = "xz")
+saveRDS(cn_melt, "./../data_munging/19Q1/cn_melt_19Q1.rds", compress = "xz")
 ```
@@
 ```{r, eval=FALSE}
-ge_19Q1 <- read.delim("./../htscreens_giant_files/CCLE_depMap_19Q1_TPM_20190305.csv.gz", header = TRUE, sep = ",", check.names = FALSE)
+ge_19Q1 <- read.delim("./../../htscreens_giant_files/CCLE_depMap_19Q1_TPM_20190305.csv.gz", header = TRUE, sep = ",", check.names = FALSE)
 # Remove Entrez gene IDs from colnames, format is "Hugo_Symbol (Entrez ID)"
@@
 # For Denise's GCN
-pgx_ccle_ge <- merge(select(ccl_info, source, source_ccl_name, source_histology, sample_ID, CCLE_ccl_name, Broad_ID), ge_19Q1, by = "Broad_ID", all = TRUE)
-saveRDS(pgx_ccle_ge, "./data_munging/19Q1/pgx_ccle_ge.rds", compress = "xz")
+# pgx_ccle_ge <- merge(select(ccl_info, source, source_ccl_name, source_histology, sample_ID, CCLE_ccl_name, Broad_ID), ge_19Q1, by = "Broad_ID", all = TRUE)
+# saveRDS(pgx_ccle_ge, "./data_munging/19Q1/pgx_ccle_ge.rds", compress = "xz")
 
@@
 # ge_melt_19Q1 <- unique(ge_melt_19Q1_all)
-saveRDS(ge_melt_19Q1, "./data_munging/19Q1/ge_melt_19Q1.rds", compress = "xz")
+saveRDS(ge_melt_19Q1, "./../data_munging/19Q1/ge_melt_19Q1.rds", compress = "xz")
 ```
 
-Load Rds:
+Load omics RDS:
 ```{r}
-maf_df <- readRDS("./data_munging/19Q1/maf_df_19Q1.rds")
-cn_melt <- readRDS("./data_munging/19Q1/cn_melt_19Q1.rds")
-ge_melt <- readRDS("./data_munging/19Q1/ge_melt_19Q1.rds")
+maf_df <- readRDS("./../data_munging/19Q1/maf_df_19Q1.rds")
+cn_melt <- readRDS("./../data_munging/19Q1/cn_melt_19Q1.rds")
+ge_melt <- readRDS("./../data_munging/19Q1/ge_melt_19Q1.rds")
 ```
@@
 
-```{r, eval=FALSE}
+```{r, eval=TRUE}
 # Sample info from figshare
-crispr_meta <- read.delim("./data_munging/19Q1/sample_info_20190306.csv", sep = ",", header = TRUE, na.strings = c("", NA))
+crispr_meta <- read.delim("./data/DepMap/sample_info_20190306.csv", sep = ",", header = TRUE, na.strings = c("", NA))
 colnames(crispr_meta)[colnames(crispr_meta) == "CCLE_name"] <- "CCLE_Name"
 
-crispr <- read.delim("./data_munging/19Q1/gene_effect_corrected_20190305.csv.gz", sep = ",", check.names = FALSE, header = TRUE)
+# crispr <- read.delim("./../data_munging/19Q1/gene_effect_corrected_20190305.csv.gz", sep = ",", check.names = FALSE, header = TRUE)
 ```
 
-# Pozdeyev et al. (2016) summary
+# POZDEYEV ET AL (2016) SUMMARY
 
@@
 ```{r}
-ccl_histologies <- select(ccl_info, Cell_line, source_histology, CCLE_ccl_name, Broad_ID) %>% drop_na(Cell_line)
-colnames(ccl_histologies)[colnames(ccl_histologies) == "source_histology"] <- "Histology"
+ccl_histologies <- select(ccl_info, Cell_line, Histology, TCGA_classification, CCLE_Name, Broad_ID) %>% drop_na(Cell_line)
 
 # Account for cell line aliases and missing histologies
-auc_na_histologies <- read.delim("./data_munging/pozdeyev2016/auc_na_histologies.csv", sep = ",", row.names = 1)
-
+auc_na_histologies <- read.delim("./data/pozdeyev2016/auc_na_histologies.csv", sep = ",", row.names = 1)
 auc_na_histologies$accession_id <- NULL
 auc_na_histologies$Notes <- NULL
+
 auc_na_histologies$Histology <- ifelse(auc_na_histologies$Histology == "", NA, as.character(auc_na_histologies$Histology))
-auc_na_histologies$CCLE_ccl_name <- ifelse(auc_na_histologies$CCLE_ccl_name  == "", NA, as.character(auc_na_histologies$CCLE_ccl_name ))
+auc_na_histologies$CCLE_Name <- ifelse(auc_na_histologies$CCLE_Name  == "", NA, as.character(auc_na_histologies$CCLE_Name ))
 auc_na_histologies$Broad_ID <- ifelse(auc_na_histologies$Broad_ID == "", NA, as.character(auc_na_histologies$Broad_ID))
@@
 ```{r, eval=FALSE}
-ccle_poz <- read.delim("./data_munging/pozdeyev2016/CCLE_drug_response_metrics.csv.gz", sep = ",")
-
+ccle_poz <- read.delim("./data/pozdeyev2016/CCLE_drug_response_metrics.csv.gz", sep = ",")
 # ccle_test <- merge(select(ccle_poz, Drug_name, Cell_line, AUC_IC50), select(filter(auc, Database == "CCLE"), Drug_name, Cell_line, AUC_IC50), by = c("Drug_name", "Cell_line"), suffixes = c("_unmatched", "_matched_all_pairs"), all = TRUE)
 
-ctrp_poz <- read.delim("./../htscreens_giant_files/pozdeyev2016/CTRP_drug_response_metrics.csv.gz", sep = ",")
+ctrp_poz <- read.delim("./../../htscreens_giant_files/omix/pozdeyev2016/CTRP_drug_response_metrics.csv.gz", sep = ",")
 # ctrp_test <- merge(select(ctrp_poz, Drug_name, Cell_line, AUC_IC50), select(filter(auc, Database == "CTRP"), Drug_name, Cell_line, AUC_IC50), by = c("Drug_name", "Cell_line"), suffixes = c("_unmatched", "_matched_all_pairs"), all = TRUE)
 
-gdsc_poz <- read.delim("./data_munging/pozdeyev2016/GDSC_drug_response_metrics.csv.gz", sep = ",")
+gdsc_poz <- read.delim("./data/pozdeyev2016/GDSC_drug_response_metrics.csv.gz", sep = ",")
 # gdsc_test <- merge(select(gdsc_poz, Drug_name, Cell_line, AUC_IC50), select(filter(auc, Database == "GDSC"), Drug_name, Cell_line, AUC_IC50), by = c("Drug_name", "Cell_line"), suffixes = c("_unmatched", "_matched_all_pairs"), all = TRUE)
@@
 auc$WasDrugScreened <- 1
-ccls_not_drugscreened <- filter(ccl_histologies, Cell_line %in% setdiff(ccl_histologies$Cell_line, auc_wide$Cell_line))
+ccls_not_drugscreened <- filter(ccl_histologies, Cell_line %in% setdiff(ccl_histologies$Cell_line, auc$Cell_line))
 ccls_not_drugscreened$WasDrugScreened <- 0
@@
 # test <- filter(auc, is.na(Histology))[, 1:10]
-# auc_na_hists <- unique(filter(auc, is.na(Histology))$Cell_linet)
-# write.csv(auc_na_hists, "./data_munging/pozdeyev2016/auc_na_histologies.csv")
+# auc_na_hists <- unique(filter(auc, is.na(Histology))$Cell_line)
+# write.csv(auc_na_hists, "./data/pozdeyev2016/auc_na_histologies.csv")
 
 # Create merged dataset with sample_ids in the rows and drugs across the columns
-auc_wide <- dcast(auc, Cell_line + Histology + CCLE_ccl_name + Broad_ID + WasDrugScreened ~ Drug_name_Database, value.var = "AUC_IC50", fun.aggregate = mean, fill = 1000000)
+auc_wide <- dcast(auc, Cell_line + Histology + TCGA_classification + CCLE_Name + Broad_ID + WasDrugScreened ~ Drug_name_Database, value.var = "AUC_IC50", fun.aggregate = mean, fill = 1000000)
 auc_wide[auc_wide == 1000000] <- ""
-auc_wide <- auc_wide %>% group_by(Cell_line, Histology, CCLE_ccl_name, Broad_ID, WasDrugScreened) %>% summarise_all(funs(trimws(paste(., collapse = ""))))
 auc_wide[auc_wide == ""] <- NA
@@
 auc_all <- subset(auc_all, !(WasDrugScreened == 0 & WasCRISPRScreened == 0 & HasMutationData == 0 & HasGeneExpressionData == 0 & HasCopyNumberData == 0))
-# write.csv.gz(auc_all, file = "./data_munging/pozdeyev2016/merged_auc_v20190402.4.csv.gz", row.names = FALSE, na = "NA")
+write.csv.gz(auc_all, file = "./data/pozdeyev2016/merged_auc_v20190408.5.csv.gz", row.names = FALSE, na = "NA")
 
@@
 ```{r}
-auc_all <- read.delim("./data_munging/pozdeyev2016/merged_auc_v20190402.4.csv.gz", sep = ",", check.names = FALSE)
+auc_all <- read.delim("./data/pozdeyev2016/merged_auc_v20190408.5.csv.gz", sep = ",", check.names = FALSE)
 
@@
 
-## Plots
+## Exploratory plots
 
@@
 venn_pgx_crispr_overlap <- venn.diagram(list("CRISPR" = unique(crispr_ccls$Cell_line), "Drug Screen" = unique(pgx_ccls$Cell_line), "Unscreened" = unique(unscreened_ccls$Cell_line)), resolution = 5000, main = "Overlap of cancer cell lines (CCLs) screened via small-molecule and CRISPR", main.fontface = "bold", lty = rep("blank", 3), fill = c("mediumpurple1", "turquoise4", "slategray3"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
-png("./gcn_denise/pozdeyev_unmatched/venn_pgx_crispr_overlap.png", res = 500, units = "in", width = 6, height = 6)
+png("./pozdeyev_unmatched/venn_pgx_crispr_overlap.png", res = 500, units = "in", width = 6, height = 6)
 grid.newpage()
@@
 venn_ccl_overlap <- venn.diagram(list("CCLE" = unique(ccle_ccls$Cell_line), "CTRP" = unique(ctrp_ccls$Cell_line), "GDSC" = unique(gdsc_ccls$Cell_line)), resolution = 5000, main = "Overlap of cancer cell lines (CCLs) screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
-png("./gcn_denise/pozdeyev_unmatched/venn_ccl_overlap.png", res = 500, units = "in", width = 6, height = 6)
+png("./pozdeyev_unmatched/venn_ccl_overlap.png", res = 500, units = "in", width = 6, height = 6)
 grid.newpage()
@@
 venn_omics_overlap <- venn.diagram(list("Gene Expression" = unique(ge_ccls$Cell_line), "Copy Number" = unique(cn_ccls$Cell_line), "Mutation" = unique(mut_ccls$Cell_line)), resolution = 5000, main = "Overlapping omic annotations in cancer cell lines (CCLs)", main.fontface = "bold", lty = rep("blank", 3), fill = c("yellow2", "orange", "tomato"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
-png("./gcn_denise/pozdeyev_unmatched/venn_omics_overlap.png", res = 500, units = "in", width = 6, height = 6)
+png("./pozdeyev_unmatched/venn_omics_overlap.png", res = 500, units = "in", width = 6, height = 6)
 grid.newpage()
@@
 bar_ccl_per_hist
-ggsave("./gcn_denise/pozdeyev_unmatched/barplot_ccl_per_histology.png", bar_ccl_per_hist, device = "png", dpi = 450, width = 12, height = 6, units = "in")
+ggsave("./pozdeyev_unmatched/barplot_ccl_per_histology.png", bar_ccl_per_hist, device = "png", dpi = 450, width = 12, height = 6, units = "in")
 
@@
 venn_drugs_overlap <- venn.diagram(list("CCLE" = unique(ccle_poz$Drug_name), "CTRP" = unique(ctrp_poz$Drug_name), "GDSC" = unique(gdsc_poz$Drug_name)), resolution = 5000, main = "Overlap of cancer cell lines (CCLs) screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
-png("./gcn_denise/pozdeyev_unmatched/venn_drugs_overlap.png", res = 500, units = "in", width = 6, height = 6)
+png("./pozdeyev_unmatched/venn_drugs_overlap.png", res = 500, units = "in", width = 6, height = 6)
 grid.newpage()
@@
 bar_ccl_per_hist_per_db
-ggsave("./gcn_denise/pozdeyev_unmatched/barplot_ccl_per_histology_per_db.png", bar_ccl_per_hist_per_db, device = "png", dpi = 450, width = 12, height = 8, units = "in")
+ggsave("./pozdeyev_unmatched/barplot_ccl_per_histology_per_db.png", bar_ccl_per_hist_per_db, device = "png", dpi = 450, width = 12, height = 8, units = "in")
 
@@
   guides(fill = "none") +
-  scale_y_continuous(breaks = seq(0, 220, by = 20), labels = seq(0, 220, by = 20)) +
+  scale_y_continuous(breaks = seq(0, 375, by = 25), labels = seq(0, 375, by = 25)) +
   labs(y = "Number of cell lines", title = "Number of unique cell lines per histology across all annotated cell lines") +
@@
 bar_ccl_per_hist
-ggsave("./gcn_denise/pozdeyev_unmatched/barplot_ccl_per_histology.png", bar_ccl_per_hist, device = "png", dpi = 450, width = 12, height = 8, units = "in")
+ggsave("./pozdeyev_unmatched/barplot_ccl_per_histology.png", bar_ccl_per_hist, device = "png", dpi = 450, width = 12, height = 8, units = "in")
 
@@
 histo_aucic50_per_db
-ggsave("./gcn_denise/pozdeyev_unmatched/histogram_aucic50_per_db.png", histo_aucic50_per_db, device = "png", dpi = 450, width = 12, height = 6, units = "in")
+ggsave("./pozdeyev_unmatched/histogram_aucic50_per_db.png", histo_aucic50_per_db, device = "png", dpi = 450, width = 12, height = 6, units = "in")
 ```
 
-## README
+## README text
 
@@
 - Histology: the general histology/tissue type of the CCL according to the CCLE annotations (see DepMap-2019q1-celllines_v2.csv file from the DepMap Data Portal)
-- CCLE_ccl_name: the cell line name using CCLE nomenclature, which is a concatenation of the cell line name with the CCLE-annotated histology in all caps, separated by underscores
+- TCGA_classification: curated TCGA labels derived from CCLE, GDSC, or manual assignment by Kaiqiao Li and Sally Claridge; note that some TCGA project labels have been combined into more general categories, e.g.
+COAD and READ are grouped into COADREAD
+- CCLE_Name: the cell line name using CCLE nomenclature, which is a concatenation of the cell line name with the CCLE-annotated histology in all caps, separated by underscores
 - Broad_ID: the custom identifiers (formatted as ACH-######) used by the Broad's Cancer Dependency Map project to ease cell line name harmonization efforts 
@@
 
-# Compare to TCGA
+merged_auc_v20190408.5.csv.gz:
+- Removed duplicate cell line entries for KMH2 and MS1 that had incorrect histology entries
+- Added TCGA classifications for all cell lines possible (classifications were manually curated by Kaiqiao Li and Sally Claridge by combining CCLE and GDSC TCGA annotations and two-fold manual comparison)
+- Changed CCLE_ccl_name column to CCLE_Name
+
+# COMPARE TO TCGA
 
@@
 ```{r, eval=FALSE}
-# Seg data is only for cell lines in teh CRISPR screen
-cn_seg <- read.delim("./data_munging/19Q1/depmap_19Q1_cn_seg_20190403.csv", sep = ",")
-cn_seg <- merge(select(ccl_histologies, Histology, Broad_ID), cn_seg, by = "Broad_ID", all.y = TRUE)
+# DepMap gene expression
+ge_depmap <- read.delim("./../../htscreens_giant_files/omix/GE/GE_DepMap_filter.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
+colnames(ge_depmap)[colnames(ge_depmap) == "cancer"] <- "TCGA_classification"
+# Mean center scale
+ge_depmap[, 4:ncol(ge_depmap)] <- apply(ge_depmap[, 4:ncol(ge_depmap)], MARGIN = 2, FUN = scale, center = TRUE, scale = TRUE)
+# Melt
+ge_depmap_melt <- melt(ge_depmap, id.vars = c("sample_ID", "TCGA_classification"), measure.vars = colnames(ge_depmap)[4:length(colnames(ge_depmap))], variable.name = "Gene", value.name = "TPM_scaled")
+# Average scaled TPM per gene per TCGA classification
+ge_depmap_avg <- ge_depmap_melt %>% group_by(TCGA_classification, Gene) %>% summarise(Mean_TPM = mean(TPM_scaled))
+# Make wide
+ge_depmap_wide <- dcast(data = ge_depmap_avg, formula = Gene ~ TCGA_classification, fun.aggregate = mean)
+rownames(ge_depmap_wide) <- ge_depmap_wide$Gene
+ge_depmap_wide$Gene <- NULL
+colnames(ge_depmap_wide) <- paste(colnames(ge_depmap_wide), "DepMap", sep = "_")
 
-tcga_seg <- read.delim("./data_munging/TCGA/GDC-PANCAN.masked_cnv.ucscxena_seg_20190403.tsv.gz", sep = "\t")
+# TCGA gene expression
+ge_tcga <- read.delim("./../../htscreens_giant_files/omix/GE/GE_Xena_filter.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
+colnames(ge_tcga)[colnames(ge_tcga) == "cancer"] <- "TCGA_classification"
+# Mean center scale
+ge_tcga[, 4:ncol(ge_tcga)] <- apply(ge_tcga[, 4:ncol(ge_tcga)], MARGIN = 2, FUN = scale, center = TRUE, scale = TRUE)
+# Melt
+ge_tcga_melt <- melt(ge_tcga, id.vars = c("sample_ID", "TCGA_classification"), measure.vars = colnames(ge_tcga)[4:length(colnames(ge_tcga))], variable.name = "Gene", value.name = "TPM_scaled")
+# Average scaled TPM per gene per TCGA classification
+ge_tcga_avg <- ge_tcga_melt %>% group_by(TCGA_classification, Gene) %>% summarise(Mean_TPM = mean(TPM_scaled))
+# Make wide
+ge_tcga_wide <- dcast(data = ge_tcga_avg, formula = Gene ~ TCGA_classification, fun.aggregate = mean)
+rownames(ge_tcga_wide) <- ge_tcga_wide$Gene
+ge_tcga_wide$Gene <- NULL
+colnames(ge_tcga_wide) <- paste(colnames(ge_tcga_wide), "TCGA", sep = "_")
 
-ggplot(cn_seg, aes(x = log2(Segment_Mean/2))) + 
-  geom_density()
+ge_wide <- bind_cols(ge_depmap_wide, ge_tcga_wide)
 
-ggplot(tcga_seg, aes(x = value)) + 
-  geom_density()
+ge_corr <- ge_wide %>% as.matrix %>% cor(method = "pearson") %>% as.data.frame %>% rownames_to_column(var = "var1") %>% gather(var2, value, -var1)
+ge_corr <- filter(ge_corr, !(grepl("DepMap", var1) & grepl("DepMap", var2)) & !(grepl("TCGA", var1) & grepl("TCGA", var2)))
+ge_corr_wide <- dcast(ge_corr, formula = var1 ~ var2, fun.aggregate = mean)
+# ge_wide_corr <- apply(ge_wide_corr, 2, function(x) gsub("_TCGA|_DepMap","", x))
+
+# ge4corr <- merge(ge_depmap_avg, ge_tcga_avg, by = c("TCGA_classification", "Gene"), all = TRUE)
+# ge_corr <- ge4corr %>% group_by(TCGA_classification) %>% summarize(corr = cor.test(y = Mean_TPM_TCGA, x = Mean_TPM_DepMap, method = "pearson", use = "complete.obs")$estimate)
+```
+
+# (OLD) Data management
+
+--------------------------------------------------------------------------------
+
+```{r, eval=FALSE}
+tcga_hist_converter <- read.xlsx("./data/TCGA/cell_line_annotation.xlsx", sheet = 1, startRow = 1, colNames = TRUE, rowNames = FALSE)
+tcga_hist_converter <- add_column(.data = tcga_hist_converter, TCGA_manual = NA, .after = "TCGA_combine")
+tcga_hist_converter <- tcga_hist_converter[with(tcga_hist_converter, order(primary_DepMap, subtype_DepMap, primary_site_CTRP, primary_hist_CTRP, subtype_CTRP, tissue1_GDSC)),]
+
+# For manual curation of TCGA labels
+ccls_for_manual_tcga_curation <- filter(tcga_hist_converter, is.na(TCGA_combine))
+ccls_for_manual_tcga_curation <- ccls_for_manual_tcga_curation[with(ccls_for_manual_tcga_curation, order(primary_DepMap, subtype_DepMap, primary_site_CTRP, primary_hist_CTRP, subtype_CTRP, tissue1_GDSC)),]
+write.csv(ccls_for_manual_tcga_curation, "./data/TCGA/cell_line_annotation_noTCGA.csv")
+tcga_hist_converter <- filter(tcga_hist_converter, !is.na(TCGA_combine))
+ccls_curated <- read.delim("./data/TCGA/cell_line_annotation_noTCGA_curated.csv", sep = ",", row.names = 1)
+tcga_histsconverter <- bind_rows(tcga_hist_converter, ccls_curated)
+tcga_hist_converter$TCGA_combine <- with(tcga_hist_converter, ifelse(is.na(TCGA_combine), as.character(TCGA_manual), TCGA_combine))
+# write.csv(tcga_hist_converter, "./data/TCGA/cell_line_annotation_curated_sally_20190404.csv")
 ```

### 2019-04-09 intro_to_pls.Rmd
renamed multivariate_regression to intro_to_pls

--- 2019-02-28 multivariate_regression.Rmd
@@
 ---
-title: "Multivariate Regression"
+title: "Introduction to PLS"
 author: "Sally Claridge"

### 2019-04-09 omix/omix.Rmd
updated omix Rmd and html

@@
 
+# NOTES
+
+--------------------------------------------------------------------------------
+
+- Quality check: cluster TCGA samples and cell lines—verify that same tumor types cluster together rather than clustering by cell lines and tumor samples (Kaiqiao)
+- Calculate Pearson correlations between DepMap and TCGA feature sets and create heatmaps (CN, GE, mutation frequency), see Barretina et al. (2016) supplement for example methods and plots
+- Look at Barretina et al. supplement for PCA and mutation load correlations)
+
 # SET UP
@@
 
-Edited `.Renviron` to avoid "Error: memory exhausted (limit reached?)" when melting the GE dataset, as per the suggestion from [StackOverflow](https://stackoverflow.com/questions/51295402/r-on-macos-error-vector-memory-exhausted-limit-reached):å
+Edited `.Renviron` to avoid "Error: memory exhausted (limit reached?)" when melting the GE dataset, as per the suggestion from [StackOverflow](https://stackoverflow.com/questions/51295402/r-on-macos-error-vector-memory-exhausted-limit-reached):
 ```
@@
 ```{r}
+library(circlize)
+library(ComplexHeatmap)
 library(crunch)
@@
 theme_set(theme_light())
+```
+
+```{r}
+unfactorize <- function(df){
+  for(i in which(sapply(df, class) == "factor")) {
+    df[[i]] = as.character(df[[i]])
+  }
+  return(df)
+}
 ```
@@
 ccl_info <- subset(ccl_info, CCLE_Name != "KMH2_THYROID" & CCLE_Name != "MS1_SKIN")
-```
 
-Adding TCGA labels:
-```{r}
-tcga_hist_converter <- read.xlsx("./data/TCGA/Histology_DepMap_Xena_04052019.xlsx", sheet = 3, startRow = 1, colNames = TRUE, rowNames = FALSE)
-tcga_hist_converter$data_source <- NULL
+# Add TCGA labels
+tcga_hist_converter_depmap <- filter(read.xlsx("./data/TCGA/Histology_DepMap_Xena_04052019.xlsx", sheet = 3, startRow = 1, colNames = TRUE, rowNames = FALSE), data_source == "DepMap")
+colnames(tcga_hist_converter_depmap) <- c("Broad_ID", "TCGA_classification", "data_source")
 
-tcga_hist_converter_depmap <- filter(tcga_hist_converter, grepl("^ACH", sample_ID))
-tcga_hist_converter_tcga <- filter(tcga_hist_converter, grepl("^TCGA", sample_ID))
-colnames(tcga_hist_converter_depmap) <- c("Broad_ID", "TCGA_classification")
-colnames(tcga_hist_converter_tcga) <- c("sample", "TCGA_classification")
+tcga_hist_converter_tcga <- filter(read.xlsx("./data/TCGA/Histology_DepMap_Xena_04052019.xlsx", sheet = 3, startRow = 1, colNames = TRUE, rowNames = FALSE), data_source == "Xena_TCGA")
+colnames(tcga_hist_converter_tcga) <- c("sample", "TCGA_classification", "data_source")
 
 ccl_info <- merge(ccl_info, tcga_hist_converter_depmap, by = "Broad_ID", all.x = TRUE)
+
+# Using Pozdeyev filtering
+ccl_histologies <- select(ccl_info, Cell_line, Histology, TCGA_classification, CCLE_Name, Broad_ID) %>% drop_na(Cell_line)
+
+# Account for cell line aliases and missing histologies
+auc_na_histologies <- read.delim("./data/pozdeyev2016/auc_na_histologies.csv", sep = ",", row.names = 1)
+auc_na_histologies$accession_id <- NULL
+auc_na_histologies$Notes <- NULL
+
+auc_na_histologies$Histology <- ifelse(auc_na_histologies$Histology == "", NA, as.character(auc_na_histologies$Histology))
+auc_na_histologies$CCLE_Name <- ifelse(auc_na_histologies$CCLE_Name  == "", NA, as.character(auc_na_histologies$CCLE_Name ))
+auc_na_histologies$Broad_ID <- ifelse(auc_na_histologies$Broad_ID == "", NA, as.character(auc_na_histologies$Broad_ID))
+auc_na_histologies <- unfactorize(auc_na_histologies)
+
+ccl_histologies <- subset(ccl_histologies, !(Broad_ID %in% auc_na_histologies$Broad_ID))
+ccl_histologies <- unfactorize(ccl_histologies)
+# Bind DepMap histologies and curated histologies
+ccl_histologies <- bind_rows(ccl_histologies, auc_na_histologies)
 ```
@@
 --------------------------------------------------------------------------------
-
-```{r}
-ccl_histologies <- select(ccl_info, Cell_line, Histology, TCGA_classification, CCLE_Name, Broad_ID) %>% drop_na(Cell_line)
-
-# Account for cell line aliases and missing histologies
-auc_na_histologies <- read.delim("./data/pozdeyev2016/auc_na_histologies.csv", sep = ",", row.names = 1)
-auc_na_histologies$accession_id <- NULL
-auc_na_histologies$Notes <- NULL
-
-auc_na_histologies$Histology <- ifelse(auc_na_histologies$Histology == "", NA, as.character(auc_na_histologies$Histology))
-auc_na_histologies$CCLE_Name <- ifelse(auc_na_histologies$CCLE_Name  == "", NA, as.character(auc_na_histologies$CCLE_Name ))
-auc_na_histologies$Broad_ID <- ifelse(auc_na_histologies$Broad_ID == "", NA, as.character(auc_na_histologies$Broad_ID))
-
-ccl_histologies <- subset(ccl_histologies, !(Broad_ID %in% auc_na_histologies$Broad_ID))
-# Bind DepMap histologies and curated histologies
-ccl_histologies <- bind_rows(ccl_histologies, auc_na_histologies)
-```
 
@@
 
-sum(auc_all$HasCopyNumberData)
-sum(auc_all$HasMutationData)
-sum(auc_all$HasGeneExpressionData)
-sum(auc_all$WasDrugScreened)
-
-test <- filter(auc_all, HasMutationData == 1)[, 1:12]
-
-pgx_ccls <- filter(auc_all, WasDrugScreened == 1)
-crispr_ccls <- filter(auc_all, WasCRISPRScreened == 1)
-unscreened_ccls <- filter(auc_all, WasCRISPRScreened == 0 & WasDrugScreened == 0)
-
-ge_ccls <- filter(auc_all, HasGeneExpressionData == 1)
-cn_ccls <- filter(auc_all, HasCopyNumberData == 1)
-mut_ccls <- filter(auc_all, HasMutationData == 1)
-
-all_omics_ccls <- intersect(intersect(unique(ge_ccls$Cell_line), unique(cn_ccls$Cell_line)), unique(mut_ccls$Cell_line))
-sum(filter(auc_all, Cell_line %in% all_omics_ccls)$WasDrugScreened)
-
-ccle_ccls <- filter(auc_all, InCCLE == 1)
-ctrp_ccls <- filter(auc_all, InCTRP == 1)
-gdsc_ccls <- filter(auc_all, InGDSC == 1)
+auc_all_summary <- t(auc_all %>% select(InGDSC, InCTRP, InCCLE, HasCopyNumberData, HasMutationData, HasGeneExpressionData, WasDrugScreened, WasCRISPRScreened) %>% summarise_each(funs(count = sum)))
+auc_all_summary
 
@@
 ```{r, eval=FALSE}
+# Data subsetting for easier tracking throughout plots
+pgx_ccls <- filter(auc_all, WasDrugScreened == 1)
+crispr_ccls <- filter(auc_all, WasCRISPRScreened == 1)
+unscreened_ccls <- filter(auc_all, WasCRISPRScreened == 0 & WasDrugScreened == 0)
+ge_ccls <- filter(auc_all, HasGeneExpressionData == 1)
+cn_ccls <- filter(auc_all, HasCopyNumberData == 1)
+mut_ccls <- filter(auc_all, HasMutationData == 1)
+ccle_ccls <- filter(auc_all, InCCLE == 1)
+ctrp_ccls <- filter(auc_all, InCTRP == 1)
+gdsc_ccls <- filter(auc_all, InGDSC == 1)
+
 futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
 venn_pgx_crispr_overlap <- venn.diagram(list("CRISPR" = unique(crispr_ccls$Cell_line), "Drug Screen" = unique(pgx_ccls$Cell_line), "Unscreened" = unique(unscreened_ccls$Cell_line)), resolution = 5000, main = "Overlap of cancer cell lines (CCLs) screened via small-molecule and CRISPR", main.fontface = "bold", lty = rep("blank", 3), fill = c("mediumpurple1", "turquoise4", "slategray3"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
-png("./pozdeyev_unmatched/venn_pgx_crispr_overlap.png", res = 500, units = "in", width = 6, height = 6)
+png("./figures/venn_pgx_crispr_overlap.png", res = 500, units = "in", width = 6, height = 6)
 grid.newpage()
@@
 venn_ccl_overlap <- venn.diagram(list("CCLE" = unique(ccle_ccls$Cell_line), "CTRP" = unique(ctrp_ccls$Cell_line), "GDSC" = unique(gdsc_ccls$Cell_line)), resolution = 5000, main = "Overlap of cancer cell lines (CCLs) screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
-png("./pozdeyev_unmatched/venn_ccl_overlap.png", res = 500, units = "in", width = 6, height = 6)
+png("./figures/venn_ccl_overlap.png", res = 500, units = "in", width = 6, height = 6)
 grid.newpage()
@@
 venn_omics_overlap <- venn.diagram(list("Gene Expression" = unique(ge_ccls$Cell_line), "Copy Number" = unique(cn_ccls$Cell_line), "Mutation" = unique(mut_ccls$Cell_line)), resolution = 5000, main = "Overlapping omic annotations in cancer cell lines (CCLs)", main.fontface = "bold", lty = rep("blank", 3), fill = c("yellow2", "orange", "tomato"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
-png("./pozdeyev_unmatched/venn_omics_overlap.png", res = 500, units = "in", width = 6, height = 6)
+png("./figures/venn_omics_overlap.png", res = 500, units = "in", width = 6, height = 6)
 grid.newpage()
@@
 bar_ccl_per_hist
-ggsave("./pozdeyev_unmatched/barplot_ccl_per_histology.png", bar_ccl_per_hist, device = "png", dpi = 450, width = 12, height = 6, units = "in")
+ggsave("./figures/barplot_ccl_per_histology.png", bar_ccl_per_hist, device = "png", dpi = 450, width = 12, height = 6, units = "in")
 
@@
 venn_drugs_overlap <- venn.diagram(list("CCLE" = unique(ccle_poz$Drug_name), "CTRP" = unique(ctrp_poz$Drug_name), "GDSC" = unique(gdsc_poz$Drug_name)), resolution = 5000, main = "Overlap of cancer cell lines (CCLs) screened in each dataset", main.fontface = "bold", lty = rep("blank", 3), fill = c("springgreen4", "steelblue4", "turquoise4"), alpha = c(0.5, 0.5, 0.5), cat.pos = c(-30, 30, 180), cat.dist = c(0.01, 0.001, 0.001), cat.cex = 1.5, cex = 1, filename = NULL)
-png("./pozdeyev_unmatched/venn_drugs_overlap.png", res = 500, units = "in", width = 6, height = 6)
+png("./figures/venn_drugs_overlap.png", res = 500, units = "in", width = 6, height = 6)
 grid.newpage()
@@
 bar_ccl_per_hist_per_db
-ggsave("./pozdeyev_unmatched/barplot_ccl_per_histology_per_db.png", bar_ccl_per_hist_per_db, device = "png", dpi = 450, width = 12, height = 8, units = "in")
+ggsave("./figures/barplot_ccl_per_histology_per_db.png", bar_ccl_per_hist_per_db, device = "png", dpi = 450, width = 12, height = 8, units = "in")
 
@@
 bar_ccl_per_hist
-ggsave("./pozdeyev_unmatched/barplot_ccl_per_histology.png", bar_ccl_per_hist, device = "png", dpi = 450, width = 12, height = 8, units = "in")
+ggsave("./figures/barplot_ccl_per_histology.png", bar_ccl_per_hist, device = "png", dpi = 450, width = 12, height = 8, units = "in")
 
@@
 histo_aucic50_per_db
-ggsave("./pozdeyev_unmatched/histogram_aucic50_per_db.png", histo_aucic50_per_db, device = "png", dpi = 450, width = 12, height = 6, units = "in")
+ggsave("./figures/histogram_aucic50_per_db.png", histo_aucic50_per_db, device = "png", dpi = 450, width = 12, height = 6, units = "in")
 ```
@@
 
-merged_auc_v20190319.1.csv.gz
-
-merged_auc_v20190319.2.csv.gz:
+- merged_auc_v20190319.1.csv.gz
+- merged_auc_v20190319.2.csv.gz
     - NAs in Histology column (excluding most of the cell lines indicated as being from a "collaborator" in CTRP) hand-curated by searches in DepMap, COSMIC, Cellosaurus, ATCC, canSAR Black, and Cell Model Passports
-
-merged_auc_v20190327.3.csv.gz:
+    - merged_auc_v20190327.3.csv.gz
     - Reformatted to have only unique cell lines in rows
@@
     - Added cell lines that have at least one type of omic data but are not in the CRISPR or pharmacogenomic screens
-
-merged_auc_v20190402.4.csv.gz:
+- merged_auc_v20190402.4.csv.gz
     - Fixed duplicate cell line rows derived from manually curating some of the CCL histologies that had been added in merged_auc_v20190319.2.csv.gz
@@
     - Reordered columns
-
-merged_auc_v20190408.5.csv.gz:
+- merged_auc_v20190408.5.csv.gz
     - Removed duplicate cell line entries for KMH2 and MS1 that had incorrect histology entries
@@
 
-# COMPARE TO TCGA
+# DEPMAP/TCGA: Heatmaps
 
@@
 
-Quality check: cluster TCGA samples and cell lines—verify that same tumor types cluster together rather than clustering by cell lines and tumor samples (Kaiqiao)
+Cancer cell lines and tumor samples are directly incomparable by nature, so the correlation matrices are asymmetric.
+The top left shows how well the features of the DepMap cancer cell lines correlate with those of the TCGA tumor samples, and the bottom right shows the reverse.
+The diagonal of the heatmap shows the comparison of matched TCGA classifications.
 
-Calculate Pearson correlations between data sets and create a heatmap (also look at Barretina et al. supplement for PCA and mutation load correlations)
+## GE
 
-```{r, eval=FALSE}
+Data wrangling and processing:
+```{r ge_heatmap_data, eval=FALSE}
 # DepMap gene expression
@@
 
+# Correlate all against all
 ge_wide <- bind_cols(ge_depmap_wide, ge_tcga_wide)
-
-ge_corr <- ge_wide %>% as.matrix %>% cor(method = "pearson") %>% as.data.frame %>% rownames_to_column(var = "var1") %>% gather(var2, value, -var1)
-ge_corr <- filter(ge_corr, !(grepl("DepMap", var1) & grepl("DepMap", var2)) & !(grepl("TCGA", var1) & grepl("TCGA", var2)))
-ge_corr_wide <- dcast(ge_corr, formula = var1 ~ var2, fun.aggregate = mean)
-# ge_wide_corr <- apply(ge_wide_corr, 2, function(x) gsub("_TCGA|_DepMap","", x))
-
-# ge4corr <- merge(ge_depmap_avg, ge_tcga_avg, by = c("TCGA_classification", "Gene"), all = TRUE)
-# ge_corr <- ge4corr %>% group_by(TCGA_classification) %>% summarize(corr = cor.test(y = Mean_TPM_TCGA, x = Mean_TPM_DepMap, method = "pearson", use = "complete.obs")$estimate)
+ge_corr <- ge_wide %>% as.matrix %>% cor(method = "spearman") %>% as.data.frame %>% rownames_to_column(var = "var1") %>% gather(var2, value, -var1)
+# Filter self-comparisons and eliminate duplicate correlations
+ge_corr <- filter(ge_corr, !(grepl("DepMap", var1) & grepl("DepMap", var2)) & !(grepl("TCGA", var1) & grepl("TCGA", var2)) & grepl("TCGA", var2))
+# Data management
+colnames(ge_corr) <- c("DepMap", "TCGA", "r")
+ge_corr <- data.frame(apply(ge_corr, 2, function(x) gsub("_TCGA|_DepMap","", x)))
+ge_corr$r <- as.numeric(as.character(ge_corr$r))
+# Set up coprrelation dataframe for plotting
+ge_corr_wide <- dcast(ge_corr, DepMap ~ TCGA)
+rownames(ge_corr_wide) <- ge_corr_wide$DepMap
+ge_corr_wide$DepMap <- NULL
 ```
 
-# (OLD) Data management
+Pseudo-figure caption: This is comparison of gene expression profiles between DepMap cancer cell lines and TCGA tumor samples, both classified by TCGA project.
+In each dataset and for each TCGA classification, gene expression (in TPM) for each of the 5,000 most variable genes shared between the two datasets were averaged across samples.
+The dataset averages per TCGA classification were correlated against each other, and these Pearson correlations (r) between TCGA and DepMap gene expression feature sets are shown in the heatmap.
+
+Make heatmaps:
+```{r ge_heatmap, eval=FALSE, fig.height=4, fig.width=3.75}
+col_fun <- colorRamp2(c(-0.5, 0, 0.5, 1), c("black", "red3", "yellow", "white"))
+ge_ht4order <- Heatmap(ge_corr_wide, cluster_rows = FALSE)
+
+ge_ht_legend_list <- list(legend_direction = "horizontal", title_position = "lefttop", legend_width = unit(1.5, "in"), border = "black")
+
+ge_ht <- Heatmap(ge_corr_wide, 
+                 name = "Expression correlation",
+                 col = col_fun, 
+                 rect_gp = gpar(col = "black"),
+                 heatmap_legend_param = ge_ht_legend_list,
+                 row_order = rev(column_order(ge_ht4order)), 
+                 show_column_dend = FALSE, 
+                 cluster_rows = FALSE, 
+                 row_names_side = "left",
+                 row_title = "DepMap cancer cell lines",
+                 column_title = "TCGA tumor samples", 
+                 column_title_side = "bottom")
+png(filename = "./figures/ge_depmap_tcga_heatmap_spearman.png", width = 7.5, height = 8, units = "in", res = 500)
+draw(ge_ht, heatmap_legend_side = "top")
+dev.off()
+```
+
+## CN
+
+Data wrangling and processing:
+
+**DO NOT RUN UNTIL ADDED TCGA TO CN AND GE DATASETS**
+```{r cn_heatmap_data, eval=FALSE}
+# TCGA copy number
+cn_tcga <- read.delim("./data/CN/CN_GDC_filter.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
+colnames(cn_tcga)[colnames(cn_tcga) == "cancer"] <- "TCGA_classification"
+# Melt
+cn_tcga_melt <- melt(cn_tcga, id.vars = c("sample_ID", "TCGA_classification"), measure.vars = colnames(cn_tcga)[4:length(colnames(cn_tcga))], variable.name = "Gene", value.name = "CN")
+# Average scaled TPM per gene per TCGA classification
+cn_tcga_avg <- cn_tcga_melt %>% group_by(TCGA_classification, Gene) %>% summarise(Mean_CN = mean(CN))
+# Make wide
+cn_tcga_wide <- dcast(data = cn_tcga_avg, formula = Gene ~ TCGA_classification, fun.aggregate = mean)
+rownames(cn_tcga_wide) <- cn_tcga_wide$Gene
+cn_tcga_wide$Gene <- NULL
+colnames(cn_tcga_wide) <- paste(colnames(cn_tcga_wide), "TCGA", sep = "_")
+
+## 18Q4
+
+# DepMap copy number (18Q4)
+cn_depmap <- read.delim("./data/CN/CN_DepMap_filter.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
+colnames(cn_depmap)[colnames(cn_depmap) == "cancer"] <- "TCGA_classification"
+# Melt
+cn_depmap_melt <- melt(cn_depmap, id.vars = c("sample_ID", "TCGA_classification"), measure.vars = colnames(cn_depmap)[4:length(colnames(cn_depmap))], variable.name = "Gene", value.name = "CN")
+# Average CN levels per gene per TCGA classification
+cn_depmap_avg <- cn_depmap_melt %>% group_by(TCGA_classification, Gene) %>% summarise(Mean_CN = mean(CN))
+# Make wide
+cn_depmap_wide <- dcast(data = cn_depmap_avg, formula = Gene ~ TCGA_classification, fun.aggregate = mean)
+rownames(cn_depmap_wide) <- cn_depmap_wide$Gene
+cn_depmap_wide$Gene <- NULL
+colnames(cn_depmap_wide) <- paste(colnames(cn_depmap_wide), "DepMap", sep = "_")
+
+# Correlate all against all (18Q4)
+cn_wide <- bind_cols(cn_depmap_wide, cn_tcga_wide)
+cn_corr <- cn_wide %>% as.matrix %>% cor(method = "spearman") %>% as.data.frame %>% rownames_to_column(var = "var1") %>% gather(var2, value, -var1)
+# Filter self-comparisons and eliminate duplicate correlations
+cn_corr <- filter(cn_corr, !(grepl("DepMap", var1) & grepl("DepMap", var2)) & !(grepl("TCGA", var1) & grepl("TCGA", var2)) & grepl("TCGA", var2))
+# Data management
+colnames(cn_corr) <- c("DepMap", "TCGA", "r")
+cn_corr <- data.frame(apply(cn_corr, 2, function(x) gsub("_TCGA|_DepMap","", x)))
+cn_corr$r <- as.numeric(as.character(cn_corr$r))
+# Set up coprrelation dataframe for plotting
+cn_corr_wide <- dcast(cn_corr, DepMap ~ TCGA)
+rownames(cn_corr_wide) <- cn_corr_wide$DepMap
+cn_corr_wide$DepMap <- NULL
+
+## 19Q1
+
+# DepMap copy number (19Q1)
+# Filter for genes and TCGA classifications in TCGA CN dataset
+cn_filt <- filter(cn_melt, Hugo_Symbol %in% unique(cn_tcga_melt$Gene) & TCGA_classification %in% unique(cn_tcga_melt$TCGA_classification))
+colnames(cn_filt)[colnames(cn_filt) == "Hugo_Symbol"] <- "Gene"
+# Assign CN levels
+cn_19Q1$CN <- with(cn_19Q1, ifelse(CN > 0.3, 1, ifelse(CN < -0.3, -1, 0)))
+# Average CN levels per gene per TCGA classification
+cn_19Q1_avg <- cn_19Q1 %>% group_by(TCGA_classification, Gene) %>% summarise(Mean_CN = mean(CN))
+# Make wide
+cn_19Q1_wide <- dcast(data = cn_19Q1_avg, formula = Gene ~ TCGA_classification, fun.aggregate = mean)
+rownames(cn_19Q1_wide) <- cn_19Q1_wide$Gene
+cn_19Q1_wide$Gene <- NULL
+colnames(cn_19Q1_wide) <- paste(colnames(cn_19Q1_wide), "DepMap", sep = "_")
+
+# Correlate all against all (19Q1)
+cn_wide_19Q1 <- bind_cols(cn_19Q1_wide, cn_tcga_wide)
+cn_corr_19Q1 <- cn_wide_19Q1 %>% as.matrix %>% cor(method = "spearman") %>% as.data.frame %>% rownames_to_column(var = "var1") %>% gather(var2, value, -var1)
+# Filter self-comparisons and eliminate duplicate correlations
+cn_corr_19Q1 <- filter(cn_corr_19Q1, !(grepl("DepMap", var1) & grepl("DepMap", var2)) & !(grepl("TCGA", var1) & grepl("TCGA", var2)) & grepl("TCGA", var2))
+# Data management
+colnames(cn_corr_19Q1) <- c("DepMap", "TCGA", "r")
+cn_corr_19Q1 <- data.frame(apply(cn_corr_19Q1, 2, function(x) gsub("_TCGA|_DepMap","", x)))
+cn_corr_19Q1$r <- as.numeric(as.character(cn_corr_19Q1$r))
+# Set up coprrelation dataframe for plotting
+cn_corr_19Q1_wide <- dcast(cn_corr_19Q1, DepMap ~ TCGA)
+rownames(cn_corr_19Q1_wide) <- cn_corr_19Q1_wide$DepMap
+cn_corr_19Q1_wide$DepMap <- NULL
+```
+
+Pseudo-figure caption: This is comparison of thresholded copy number profiles between DepMap cancer cell lines and TCGA tumor samples, both classified by TCGA project.
+Levels are -1 for copuy number loss, 0 for neutral, and 1 for gain.
+In each dataset and for each TCGA classification, these numeric copy number levels across all genes shared between the two datasets were averaged, and the datasets were correlated against each other.
+Pearson correlations (r) between TCGA and DepMap copy number feature sets are shown in the heatmap.
+
+Make heatmaps:
+```{r cn_heatmaps, eval=FALSE, fig.height=4, fig.width=3.75}
+col_fun <- colorRamp2(c(-0.5, 0, 0.5, 1), c("black", "red3", "yellow", "white"))
+cn_ht_legend_list <- list(legend_direction = "horizontal", title_position = "lefttop", legend_width = unit(1.5, "in"), border = "black")
+
+# 18Q4
+cn_ht4order <- Heatmap(cn_corr_wide, cluster_rows = FALSE)
+cn_ht <- Heatmap(cn_corr_wide, 
+                 name = "Expression correlation",
+                 col = col_fun, 
+                 rect_gp = gpar(col = "black"),
+                 heatmap_legend_param = cn_ht_legend_list,
+                 row_order = rev(column_order(cn_ht4order)), 
+                 show_column_dend = FALSE, 
+                 cluster_rows = FALSE, 
+                 row_names_side = "left",
+                 row_title = "DepMap cancer cell lines",
+                 column_title = "TCGA tumor samples", 
+                 column_title_side = "bottom")
+# png(filename = "./figures/cn_depmap_tcga_heatmap_spearman.png", width = 7.5, height = 8, units = "in", res = 500)
+draw(cn_ht, heatmap_legend_side = "top")
+# dev.off()
+
+# 19Q1
+cn_19Q1_ht4order <- Heatmap(cn_corr_19Q1_wide, cluster_rows = FALSE)
+
+cn_19Q1_ht <- Heatmap(cn_corr_19Q1_wide, 
+                 name = "Expression correlation",
+                 col = col_fun, 
+                 rect_gp = gpar(col = "black"),
+                 heatmap_legend_param = cn_ht_legend_list,
+                 row_order = rev(column_order(cn_19Q1_ht4order)), 
+                 show_column_dend = FALSE, 
+                 cluster_rows = FALSE, 
+                 row_names_side = "left",
+                 row_title = "DepMap cancer cell lines",
+                 column_title = "TCGA tumor samples", 
+                 column_title_side = "bottom")
+# png(filename = "./figures/cn_depmap_19Q1_tcga_heatmap_spearman.png", width = 7.5, height = 8, units = "in", res = 500)
+draw(cn_19Q1_ht, heatmap_legend_side = "top")
+# dev.off()
+```
+
+## Mut
+
+```{r mut_heatmap_data, eval=FALSE}
+
+```
+
+# OLD
 
 --------------------------------------------------------------------------------
+
+## Data management
 
@@
 
-# (OLD) Pozdeyev et al (2016) matched data
-
---------------------------------------------------------------------------------
+## Pozdeyev et al (2016) matched data
 
@@
 
-# (OLD) Denise's GCN dataframes
-
---------------------------------------------------------------------------------
+## Denise's GCN dataframes
 
@@
 
-## AUC
+### AUC
 
@@
 
-## Summary figures
+### Summary figures
 
@@
 ```
+
+# SESSION INFO
+
+--------------------------------------------------------------------------------
+
+```{r}
+sessionInfo()
+```

### 2019-04-10 omix/omix.Rmd
updated Rmd w/ mutation DepMap/TCGA comparison

@@
 
-```{r}
+```{r load_libraries}
 library(circlize)
@@
 
-```{r}
+```{r functions}
 unfactorize <- function(df){
@@
 DepMap 19Q1 update fixed almost all of the inconsistencies of the Primary.Disease column, though there were come capitalization inconsistencies.
-```{r}
+```{r ccl_info_processing, eval=FALSE}
 ccl_info <- read.delim("./data/DepMap/DepMap-2019q1-celllines_v2_20190305.csv", sep = ",", header = TRUE, na.strings = c("", NA))
@@
 ccl_histologies <- bind_rows(ccl_histologies, auc_na_histologies)
+write.csv(ccl_histologies, "./data/ccl_histologies_metadata.csv")
+```
+
+Load cell line metadata file:
+```{r}
+ccl_histologies <- read.delim("./data/ccl_histologies_metadata.csv", sep = ",", header = TRUE, row.names = 1)
 ```
@@
 Mutation calls (coding region, germline filtered):
-```{r, eval=FALSE}
+```{r mutation, eval=FALSE}
 maf_raw <- read.delim("./../data_munging/19Q1/depmap_19Q1_mutation_calls_20190305.csv.gz", header = TRUE, sep = ",", row.names = 1)
@@
 colnames(maf_raw)[colnames(maf_raw) == "DepMap_ID"] <- "Broad_ID"
+colnames(maf_raw)[colnames(maf_raw) == "Hugo_Symbol"] <- "Gene"
+# Merge CCL metadata
+maf_raw <- merge(select(ccl_histologies, Broad_ID, TCGA_classification), maf_raw, by = "Broad_ID", all.y = TRUE)
 # Select columns
-maf_df <- subset(maf_raw, select = c("Hugo_Symbol", "Broad_ID", "Variant_Classification", "Reference_Allele", "Tumor_Seq_Allele1", "Genome_Change"))
+maf_df <- subset(maf_raw, select = c("Gene", "Broad_ID", "TCGA_classification", "Variant_Classification", "Reference_Allele", "Tumor_Seq_Allele1", "Genome_Change"))
 maf_df$Reference_Allele <- ifelse(maf_df$Reference_Allele == "-", 0, nchar(as.character(maf_df$Reference_Allele)))
@@
 # Add Mutation_Status column
-maf_df$Mutation_Status_Nonsilent <- "Mutant"
+maf_df$Mutation_Status <- 1
 
@@
 DepMap WES CN Data:
-```{r, eval=FALSE}
+```{r copy_number, eval=FALSE}
 cn <- read.delim("./../data_munging/19Q1/public_19Q1_gene_cn_20190305.csv.gz", sep = ",", check.names = FALSE, header = TRUE)
@@
 colnames(cn)[1] <- "Broad_ID"
+# Merge CCL metadata with TCGA labels
+cn <- merge(select(ccl_histologies, Broad_ID, TCGA_classification), cn, by = "Broad_ID", all.y = TRUE)
 # Melt
-cn_melt <- melt(data = cn, id.vars = "Broad_ID", measure.vars = colnames(cn[2:ncol(cn)]), variable.name = "Hugo_Symbol", value.name = "CN")
+cn_melt <- melt(data = cn, id.vars = c("Broad_ID", "TCGA_classification"), measure.vars = colnames(cn[3:ncol(cn)]), variable.name = "Gene", value.name = "CN")
 saveRDS(cn_melt, "./../data_munging/19Q1/cn_melt_19Q1.rds", compress = "xz")
@@
 19Q1, CCLE RNAseq gene expression data (log2(TPM+1)):
-```{r, eval=FALSE}
-ge_19Q1 <- read.delim("./../../htscreens_giant_files/CCLE_depMap_19Q1_TPM_20190305.csv.gz", header = TRUE, sep = ",", check.names = FALSE)
+```{r gene_expression, eval=FALSE}
+ge <- read.delim("./../../htscreens_giant_files/CCLE_depMap_19Q1_TPM_20190305.csv.gz", header = TRUE, sep = ",", check.names = FALSE)
 # Remove Entrez gene IDs from colnames, format is "Hugo_Symbol (Entrez ID)"
-colnames(ge_19Q1) <- gsub(" .*", "", colnames(ge_19Q1))
-colnames(ge_19Q1)[1] <- "Broad_ID"
-
-# For Denise's GCN
-# pgx_ccle_ge <- merge(select(ccl_info, source, source_ccl_name, source_histology, sample_ID, CCLE_ccl_name, Broad_ID), ge_19Q1, by = "Broad_ID", all = TRUE)
-# saveRDS(pgx_ccle_ge, "./data_munging/19Q1/pgx_ccle_ge.rds", compress = "xz")
-
+colnames(ge) <- gsub(" .*", "", colnames(ge))
+colnames(ge)[1] <- "Broad_ID"
+# Merge CCL metadata with TCGA labels
+ge <- merge(select(ccl_histologies, Broad_ID, TCGA_classification), ge, by = "Broad_ID", all.y = TRUE)
 # Melt
-ge_melt_19Q1 <- melt(ge_19Q1, id.vars = "Broad_ID", measure.vars = colnames(ge_19Q1)[2:ncol(ge_19Q1)], variable.name = "Hugo_Symbol", value.name = "TPM")
-# ge_melt_19Q1 <- unique(ge_melt_19Q1_all)
-saveRDS(ge_melt_19Q1, "./../data_munging/19Q1/ge_melt_19Q1.rds", compress = "xz")
+ge_melt <- melt(ge, id.vars = c("Broad_ID", "TCGA_classification"), measure.vars = colnames(ge)[3:ncol(ge)], variable.name = "Gene", value.name = "TPM")
+saveRDS(ge_melt, "./../data_munging/19Q1/ge_melt_19Q1.rds", compress = "xz")
 ```
@@
 Load omics RDS:
-```{r}
+```{r load_omics_rds}
 maf_df <- readRDS("./../data_munging/19Q1/maf_df_19Q1.rds")
@@
 
-```{r, eval=TRUE}
+```{r crispr, eval=TRUE}
 # Sample info from figshare
@@
 
-```{r, eval=FALSE}
+```{r pozdeyev_processing, eval=FALSE}
 ccle_poz <- read.delim("./data/pozdeyev2016/CCLE_drug_response_metrics.csv.gz", sep = ",")
@@
 
-```{r}
+```{r pozdeyev_summaries}
 auc_all <- read.delim("./data/pozdeyev2016/merged_auc_v20190408.5.csv.gz", sep = ",", check.names = FALSE)
@@
 
-```{r, eval=FALSE}
+```{r exploratory_plots, eval=FALSE}
 # Data subsetting for easier tracking throughout plots
@@
 Data wrangling and processing:
-```{r ge_heatmap_data, eval=FALSE}
+```{r ge_heatmap_data, eval=FALSE, warning=FALSE}
 # DepMap gene expression
@@
 In each dataset and for each TCGA classification, gene expression (in TPM) for each of the 5,000 most variable genes shared between the two datasets were averaged across samples.
-The dataset averages per TCGA classification were correlated against each other, and these Pearson correlations (r) between TCGA and DepMap gene expression feature sets are shown in the heatmap.
+The dataset averages per TCGA classification were correlated against each other, and these Pearson/Spearman correlations (r) between TCGA and DepMap gene expression feature sets are shown in the heatmap.
 
@@
 Data wrangling and processing:
-
-**DO NOT RUN UNTIL ADDED TCGA TO CN AND GE DATASETS**
-```{r cn_heatmap_data, eval=FALSE}
+```{r cn_heatmap_data, eval=FALSE, warning=FALSE}
 # TCGA copy number
@@
 colnames(cn_tcga_wide) <- paste(colnames(cn_tcga_wide), "TCGA", sep = "_")
-
-## 18Q4
 
@@
 cn_wide <- bind_cols(cn_depmap_wide, cn_tcga_wide)
-cn_corr <- cn_wide %>% as.matrix %>% cor(method = "spearman") %>% as.data.frame %>% rownames_to_column(var = "var1") %>% gather(var2, value, -var1)
+cn_corr <- cn_wide %>% as.matrix %>% cor(method = "pearson") %>% as.data.frame %>% rownames_to_column(var = "var1") %>% gather(var2, value, -var1)
 # Filter self-comparisons and eliminate duplicate correlations
@@
 cn_corr_wide$DepMap <- NULL
-
-## 19Q1
-
-# DepMap copy number (19Q1)
-# Filter for genes and TCGA classifications in TCGA CN dataset
-cn_filt <- filter(cn_melt, Hugo_Symbol %in% unique(cn_tcga_melt$Gene) & TCGA_classification %in% unique(cn_tcga_melt$TCGA_classification))
-colnames(cn_filt)[colnames(cn_filt) == "Hugo_Symbol"] <- "Gene"
-# Assign CN levels
-cn_19Q1$CN <- with(cn_19Q1, ifelse(CN > 0.3, 1, ifelse(CN < -0.3, -1, 0)))
-# Average CN levels per gene per TCGA classification
-cn_19Q1_avg <- cn_19Q1 %>% group_by(TCGA_classification, Gene) %>% summarise(Mean_CN = mean(CN))
-# Make wide
-cn_19Q1_wide <- dcast(data = cn_19Q1_avg, formula = Gene ~ TCGA_classification, fun.aggregate = mean)
-rownames(cn_19Q1_wide) <- cn_19Q1_wide$Gene
-cn_19Q1_wide$Gene <- NULL
-colnames(cn_19Q1_wide) <- paste(colnames(cn_19Q1_wide), "DepMap", sep = "_")
-
-# Correlate all against all (19Q1)
-cn_wide_19Q1 <- bind_cols(cn_19Q1_wide, cn_tcga_wide)
-cn_corr_19Q1 <- cn_wide_19Q1 %>% as.matrix %>% cor(method = "spearman") %>% as.data.frame %>% rownames_to_column(var = "var1") %>% gather(var2, value, -var1)
-# Filter self-comparisons and eliminate duplicate correlations
-cn_corr_19Q1 <- filter(cn_corr_19Q1, !(grepl("DepMap", var1) & grepl("DepMap", var2)) & !(grepl("TCGA", var1) & grepl("TCGA", var2)) & grepl("TCGA", var2))
-# Data management
-colnames(cn_corr_19Q1) <- c("DepMap", "TCGA", "r")
-cn_corr_19Q1 <- data.frame(apply(cn_corr_19Q1, 2, function(x) gsub("_TCGA|_DepMap","", x)))
-cn_corr_19Q1$r <- as.numeric(as.character(cn_corr_19Q1$r))
-# Set up coprrelation dataframe for plotting
-cn_corr_19Q1_wide <- dcast(cn_corr_19Q1, DepMap ~ TCGA)
-rownames(cn_corr_19Q1_wide) <- cn_corr_19Q1_wide$DepMap
-cn_corr_19Q1_wide$DepMap <- NULL
 ```
@@
 Pseudo-figure caption: This is comparison of thresholded copy number profiles between DepMap cancer cell lines and TCGA tumor samples, both classified by TCGA project.
-Levels are -1 for copuy number loss, 0 for neutral, and 1 for gain.
+Levels are -1 for copy number loss, 0 for neutral, and 1 for gain.
 In each dataset and for each TCGA classification, these numeric copy number levels across all genes shared between the two datasets were averaged, and the datasets were correlated against each other.
-Pearson correlations (r) between TCGA and DepMap copy number feature sets are shown in the heatmap.
+Pearson/Spearman correlations (r) between TCGA and DepMap copy number feature sets are shown in the heatmap.
 
@@
 ```{r cn_heatmaps, eval=FALSE, fig.height=4, fig.width=3.75}
-col_fun <- colorRamp2(c(-0.5, 0, 0.5, 1), c("black", "red3", "yellow", "white"))
+col_fun <- colorRamp2(c(0, 0.25, 0.5, 0.75), c("black", "red3", "yellow", "white"))
 cn_ht_legend_list <- list(legend_direction = "horizontal", title_position = "lefttop", legend_width = unit(1.5, "in"), border = "black")
@@
 cn_ht <- Heatmap(cn_corr_wide, 
-                 name = "Expression correlation",
+                 name = "Copy number correlation",
                  col = col_fun, 
@@
                  column_title_side = "bottom")
-# png(filename = "./figures/cn_depmap_tcga_heatmap_spearman.png", width = 7.5, height = 8, units = "in", res = 500)
+# png(filename = "./figures/cn_depmap_tcga_heatmap_pearson.png", width = 7.5, height = 8, units = "in", res = 500)
 draw(cn_ht, heatmap_legend_side = "top")
 # dev.off()
+```
 
-# 19Q1
-cn_19Q1_ht4order <- Heatmap(cn_corr_19Q1_wide, cluster_rows = FALSE)
+## Mut
 
-cn_19Q1_ht <- Heatmap(cn_corr_19Q1_wide, 
-                 name = "Expression correlation",
+Data wrangling and processing:
+```{r mut_heatmap_data, eval=FALSE}
+# TCGA
+mut_tcga <- read.delim("./data/mutation/mutation_Xena_filter.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
+mut_tcga <- unfactorize(mut_tcga)
+mut_tcga[, 4:ncol(mut_tcga)] <- apply(mut_tcga[, 4:ncol(mut_tcga)], 2, function(x) ifelse(x > 1, 1, x))
+colnames(mut_tcga)[colnames(mut_tcga) == "cancer"] <- "TCGA_classification"
+# Melt
+mut_tcga_melt <- melt(mut_tcga, id.vars = c("sample_ID", "TCGA_classification"), measure.vars = colnames(mut_tcga)[4:length(colnames(mut_tcga))], variable.name = "Gene", value.name = "Mutation_Status")
+# Average CN levels per gene per TCGA classification
+mut_tcga_prop <- mut_tcga_melt %>% group_by(TCGA_classification, Gene) %>% summarise(Proportion_Mut = sum(Mutation_Status)/n())
+# Make wide
+mut_tcga_wide <- dcast(data = mut_tcga_prop, formula = Gene ~ TCGA_classification, fun.aggregate = mean)
+rownames(mut_tcga_wide) <- mut_tcga_wide$Gene
+mut_tcga_wide$Gene <- NULL
+colnames(mut_tcga_wide) <- paste(colnames(mut_tcga_wide), "TCGA", sep = "_")
+
+# DepMap
+mut_depmap <- read.delim("./data/mutation/mutation_DepMap_filter.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
+mut_depmap <- unfactorize(mut_depmap)
+mut_depmap[, 4:ncol(mut_depmap)] <- apply(mut_depmap[, 4:ncol(mut_depmap)], 2, function(x) ifelse(x > 1, 1, x))
+colnames(mut_depmap)[colnames(mut_depmap) == "cancer"] <- "TCGA_classification"
+# Melt
+mut_depmap_melt <- melt(mut_depmap, id.vars = c("sample_ID", "TCGA_classification"), measure.vars = colnames(mut_depmap)[4:length(colnames(mut_depmap))], variable.name = "Gene", value.name = "Mutation_Status")
+# Average CN levels per gene per TCGA classification
+mut_depmap_prop <- mut_depmap_melt %>% group_by(TCGA_classification, Gene) %>% summarise(Proportion_Mut = sum(Mutation_Status)/n())
+# Make wide
+mut_depmap_wide <- dcast(data = mut_depmap_prop, formula = Gene ~ TCGA_classification, fun.aggregate = mean)
+rownames(mut_depmap_wide) <- mut_depmap_wide$Gene
+mut_depmap_wide$Gene <- NULL
+colnames(mut_depmap_wide) <- paste(colnames(mut_depmap_wide), "DepMap", sep = "_")
+
+# Correlate all against all (18Q4)
+mut_wide <- bind_cols(mut_depmap_wide, mut_tcga_wide)
+mut_corr <- mut_wide %>% as.matrix %>% cor(method = "spearman") %>% as.data.frame %>% rownames_to_column(var = "var1") %>% gather(var2, value, -var1)
+# Filter self-comparisons and eliminate duplicate correlations
+mut_corr <- filter(mut_corr, !(grepl("DepMap", var1) & grepl("DepMap", var2)) & !(grepl("TCGA", var1) & grepl("TCGA", var2)) & grepl("TCGA", var2))
+# Data management
+colnames(mut_corr) <- c("DepMap", "TCGA", "r")
+mut_corr <- data.frame(apply(mut_corr, 2, function(x) gsub("_TCGA|_DepMap","", x)))
+mut_corr$r <- as.numeric(as.character(mut_corr$r))
+# Set up coprrelation dataframe for plotting
+mut_corr_wide <- dcast(mut_corr, DepMap ~ TCGA)
+rownames(mut_corr_wide) <- mut_corr_wide$DepMap
+mut_corr_wide$DepMap <- NULL
+```
+
+Pseudo-figure caption: This is comparison of binary gene-level mutation frequency profiles between DepMap cancer cell lines and TCGA tumor samples, both classified by TCGA project.
+In each dataset and for each TCGA classification, the proportion of samples containing at least one mutation was calculated for all genes shared between the two datasets, and the proportions were correlated against each other.
+Pearson/Spearman correlations (r) between TCGA and DepMap copy number feature sets are shown in the heatmap.
+
+Genes in the TCGA mutation dataset were analyzed if they were mutated in >=4% annotated samples and had a mutaiton in at least one cancer cell line from DepMap.
+
+Make heatmaps:
+```{r cn_heatmaps, eval=FALSE, fig.height=4, fig.width=3.75}
+col_fun <- colorRamp2(c(0, 0.15, 0.35, 0.5), c("black", "red3", "yellow", "white"))
+mut_ht_legend_list <- list(legend_direction = "horizontal", title_position = "lefttop", legend_width = unit(1.5, "in"), border = "black")
+
+# 18Q4
+mut_ht4order <- Heatmap(mut_corr_wide, cluster_rows = FALSE)
+mut_ht <- Heatmap(mut_corr_wide, 
+                 name = "Mutation correlation",
                  col = col_fun, 
                  rect_gp = gpar(col = "black"),
-                 heatmap_legend_param = cn_ht_legend_list,
-                 row_order = rev(column_order(cn_19Q1_ht4order)), 
+                 heatmap_legend_param = mut_ht_legend_list,
+                 row_order = rev(column_order(mut_ht4order)), 
                  show_column_dend = FALSE, 
@@
                  column_title_side = "bottom")
-# png(filename = "./figures/cn_depmap_19Q1_tcga_heatmap_spearman.png", width = 7.5, height = 8, units = "in", res = 500)
-draw(cn_19Q1_ht, heatmap_legend_side = "top")
+# png(filename = "./figures/mut_depmap_tcga_heatmap_spearman.png", width = 7.5, height = 8, units = "in", res = 500)
+draw(mut_ht, heatmap_legend_side = "top")
 # dev.off()
-```
-
-## Mut
-
-```{r mut_heatmap_data, eval=FALSE}
-
 ```

### 2019-04-11 omix/omix.Rmd

@@
 library(kableExtra)
+library(lemon)
 library(naniar)
@@
 theme_set(theme_light())
+# install.packages("lemon")
 ```
@@
 
-# DEPMAP/TCGA: Heatmaps
+# DEPMAP/TCGA
 
@@
 
-## GE
+```{r}
+tcga_classifications_16 <- c("BLCA", "BRCA", "COADREAD", "ESCA", "GBMLGG", "HNSC", "KIRC", "LIHC", "LUAD", "LUSC", "OV", "PAAD", "SARC", "SKCM", "STAD", "UCEC")
+```
+
+## Heatmaps
+
+### GE
 
@@
 
-## CN
-
-Data wrangling and processing:
-```{r cn_heatmap_data, eval=FALSE, warning=FALSE}
+### CN
+
+Continuous CN estimate data wrangling and processing:
+```{r cn_heatmap_data_continuous, eval=FALSE, warning=FALSE}
+# DepMap copy number
+cn_depmap <- read.delim("./../../htscreens_giant_files/omix/CN/CN_cont_DepMap_filter.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
+colnames(cn_depmap)[colnames(cn_depmap) == "cancer"] <- "TCGA_classification"
+# Mean center scale
+cn_depmap[, 4:ncol(cn_depmap)] <- apply(cn_depmap[, 4:ncol(cn_depmap)], MARGIN = 2, FUN = scale, center = TRUE, scale = TRUE)
+# Melt
+cn_depmap_melt <- melt(cn_depmap, id.vars = c("sample_ID", "TCGA_classification"), measure.vars = colnames(cn_depmap)[4:length(colnames(cn_depmap))], variable.name = "Gene", value.name = "CN_scaled")
+cn_depmap_melt <- filter(cn_depmap_melt, TCGA_classification %in% tcga_classifications_16)
+# Average scaled TPM per gene per TCGA classification
+cn_depmap_avg <- cn_depmap_melt %>% group_by(TCGA_classification, Gene) %>% summarise(Mean_CN = mean(CN_scaled))
+# Make wide
+cn_depmap_wide <- dcast(data = cn_depmap_avg, formula = Gene ~ TCGA_classification, fun.aggregate = mean)
+rownames(cn_depmap_wide) <- cn_depmap_wide$Gene
+cn_depmap_wide$Gene <- NULL
+colnames(cn_depmap_wide) <- paste(colnames(cn_depmap_wide), "DepMap", sep = "_")
+
+# TCGA cop number
+cn_tcga <- read.delim("./../../htscreens_giant_files/omix/CN/CN_cont_Xena_filter.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
+colnames(cn_tcga)[colnames(cn_tcga) == "cancer"] <- "TCGA_classification"
+# Mean center scale
+cn_tcga[, 4:ncol(cn_tcga)] <- apply(cn_tcga[, 4:ncol(cn_tcga)], MARGIN = 2, FUN = scale, center = TRUE, scale = TRUE)
+# Melt
+cn_tcga_melt <- melt(cn_tcga, id.vars = c("sample_ID", "TCGA_classification"), measure.vars = colnames(cn_tcga)[4:length(colnames(cn_tcga))], variable.name = "Gene", value.name = "CN_scaled")
+cn_tcga_melt <- filter(cn_tcga_melt, TCGA_classification %in% tcga_classifications_16)
+# Average scaled TPM per gene per TCGA classification
+cn_tcga_avg <- cn_tcga_melt %>% group_by(TCGA_classification, Gene) %>% summarise(Mean_CN = mean(CN_scaled))
+# Make wide
+cn_tcga_wide <- dcast(data = cn_tcga_avg, formula = Gene ~ TCGA_classification, fun.aggregate = mean)
+rownames(cn_tcga_wide) <- cn_tcga_wide$Gene
+cn_tcga_wide$Gene <- NULL
+colnames(cn_tcga_wide) <- paste(colnames(cn_tcga_wide), "TCGA", sep = "_")
+
+# Correlate all against all
+cn_wide <- bind_cols(cn_depmap_wide, cn_tcga_wide)
+cn_corr <- cn_wide %>% as.matrix %>% cor(method = "pearson") %>% as.data.frame %>% rownames_to_column(var = "var1") %>% gather(var2, value, -var1)
+# Filter self-comparisons and eliminate duplicate correlations
+cn_corr <- filter(cn_corr, !(grepl("DepMap", var1) & grepl("DepMap", var2)) & !(grepl("TCGA", var1) & grepl("TCGA", var2)) & grepl("TCGA", var2))
+# Data management
+colnames(cn_corr) <- c("DepMap", "TCGA", "r")
+cn_corr <- data.frame(apply(cn_corr, 2, function(x) gsub("_TCGA|_DepMap","", x)))
+cn_corr$r <- as.numeric(as.character(cn_corr$r))
+# cn_corr <- filter(cn_corr, DepMap %in% tcga_classifications_16 & TCGA %in% tcga_classifications_16)
+# Set up coprrelation dataframe for plotting
+cn_corr_wide <- dcast(cn_corr, DepMap ~ TCGA)
+rownames(cn_corr_wide) <- cn_corr_wide$DepMap
+cn_corr_wide$DepMap <- NULL
+```
+
+Thresholded CN estimate data wrangling and processing:
+```{r cn_heatmap_data_thresholded, eval=FALSE, warning=FALSE}
 # TCGA copy number
@@
 
-Pseudo-figure caption: This is comparison of thresholded copy number profiles between DepMap cancer cell lines and TCGA tumor samples, both classified by TCGA project.
+Pseudo-figure caption for thresholded data: This is comparison of thresholded copy number profiles between DepMap cancer cell lines and TCGA tumor samples, both classified by TCGA project.
 Levels are -1 for copy number loss, 0 for neutral, and 1 for gain.
@@
 ```{r cn_heatmaps, eval=FALSE, fig.height=4, fig.width=3.75}
-col_fun <- colorRamp2(c(0, 0.25, 0.5, 0.75), c("black", "red3", "yellow", "white"))
+col_fun <- colorRamp2(c(-0.5, 0, 0.25, 0.75), c("black", "red3", "yellow", "white"))
 cn_ht_legend_list <- list(legend_direction = "horizontal", title_position = "lefttop", legend_width = unit(1.5, "in"), border = "black")
@@
                  column_title_side = "bottom")
-# png(filename = "./figures/cn_depmap_tcga_heatmap_pearson.png", width = 7.5, height = 8, units = "in", res = 500)
+# png(filename = "./figures/cn_depmap_tcga_heatmap_pearson_continuous.png", width = 7.5, height = 8, units = "in", res = 500)
 draw(cn_ht, heatmap_legend_side = "top")
@@
 
-## Mut
+### Mut
 
@@
 mut_tcga_melt <- melt(mut_tcga, id.vars = c("sample_ID", "TCGA_classification"), measure.vars = colnames(mut_tcga)[4:length(colnames(mut_tcga))], variable.name = "Gene", value.name = "Mutation_Status")
-# Average CN levels per gene per TCGA classification
-mut_tcga_prop <- mut_tcga_melt %>% group_by(TCGA_classification, Gene) %>% summarise(Proportion_Mut = sum(Mutation_Status)/n())
+# Calce proportion mutated per gene per TCGA classification
+mut_tcga_prop <- mut_tcga_melt %>% group_by(TCGA_classification, Gene) %>% summarise(Proportion_Mut = sum(Mutation_Status) / n())
 # Make wide
 mut_tcga_wide <- dcast(data = mut_tcga_prop, formula = Gene ~ TCGA_classification, fun.aggregate = mean)
+mut_tcga_wide <- mut_tcga_wide[mut_tcga_wide$Gene != "TP53", ]
 rownames(mut_tcga_wide) <- mut_tcga_wide$Gene
@@
 mut_depmap_melt <- melt(mut_depmap, id.vars = c("sample_ID", "TCGA_classification"), measure.vars = colnames(mut_depmap)[4:length(colnames(mut_depmap))], variable.name = "Gene", value.name = "Mutation_Status")
-# Average CN levels per gene per TCGA classification
-mut_depmap_prop <- mut_depmap_melt %>% group_by(TCGA_classification, Gene) %>% summarise(Proportion_Mut = sum(Mutation_Status)/n())
+# Calce proportion mutated per gene per TCGA classification
+mut_depmap_prop <- mut_depmap_melt %>% group_by(TCGA_classification, Gene) %>% summarise(Proportion_Mut = sum(Mutation_Status) / n())
 # Make wide
 mut_depmap_wide <- dcast(data = mut_depmap_prop, formula = Gene ~ TCGA_classification, fun.aggregate = mean)
+mut_depmap_wide <- mut_depmap_wide[mut_depmap_wide$Gene != "TP53", ]
 rownames(mut_depmap_wide) <- mut_depmap_wide$Gene
@@
 In each dataset and for each TCGA classification, the proportion of samples containing at least one mutation was calculated for all genes shared between the two datasets, and the proportions were correlated against each other.
-Pearson/Spearman correlations (r) between TCGA and DepMap copy number feature sets are shown in the heatmap.
-
-Genes in the TCGA mutation dataset were analyzed if they were mutated in >=4% annotated samples and had a mutaiton in at least one cancer cell line from DepMap.
+Pearson/Spearman correlations (r) between TCGA and DepMap mutation feature sets are shown in the heatmap.
+
+For plots labeled as "5000", the 5,000 mosr variable genes analyzed in the gene expression heatmap were selected for the mutation analyses.
+Alternatively, for the plots labeled as "252", the genes in the TCGA mutation dataset were analyzed if they were mutated in >=4% annotated samples and had a mutation in at least one cancer cell line from DepMap.
+TP53 was removed from the heatmap, as was done in Barretina et al.
+(2012).
+For the scatterplots, TP53 was retained.
 
@@
 ```{r cn_heatmaps, eval=FALSE, fig.height=4, fig.width=3.75}
-col_fun <- colorRamp2(c(0, 0.15, 0.35, 0.5), c("black", "red3", "yellow", "white"))
+col_fun <- colorRamp2(c(0, 0.2, 0.5, 0.7), c("black", "red3", "yellow", "white"))
 mut_ht_legend_list <- list(legend_direction = "horizontal", title_position = "lefttop", legend_width = unit(1.5, "in"), border = "black")
@@
                  column_title_side = "bottom")
-# png(filename = "./figures/mut_depmap_tcga_heatmap_spearman.png", width = 7.5, height = 8, units = "in", res = 500)
+# png(filename = "./figures/mut_depmap_tcga_heatmap_spearman_252.png", width = 7.5, height = 8, units = "in", res = 500)
 draw(mut_ht, heatmap_legend_side = "top")
 # dev.off()
+```
+
+## Scatterplots
+
+### CN
+
+```{r cn_scatters_data, eval=FALSE}
+# For both datasets: CN_Status encoded as 1 is non-neutral (-1 or +1) and 0 is neutral
+
+# TCGA
+# Calc proportion of non-neutral CN per gene per TCGA classification
+cn_tcga_prop <- cn_tcga_melt
+cn_tcga_prop$CN_Status <- with(cn_tcga_prop, ifelse(CN != 0, 1, CN))
+cn_tcga_prop <- cn_tcga_prop %>% group_by(TCGA_classification, Gene) %>% summarise(Proportion_NonNeutral_CN = sum(CN_Status) / n(), N = n())
+
+# DepMap
+# Calc proportion of non-neutral CN per gene per TCGA classification
+cn_depmap_prop <- cn_depmap_melt
+cn_depmap_prop$CN_Status <- with(cn_depmap_prop, ifelse(CN != 0, 1, CN))
+cn_depmap_prop <- cn_depmap_prop %>% group_by(TCGA_classification, Gene) %>% summarise(Proportion_NonNeutral_CN = sum(CN_Status) / n(), N = n())
+
+# Merge non-neutral CN proportion dataframes for plotting
+cn_props <- merge(cn_depmap_prop, cn_tcga_prop, by = c("TCGA_classification", "Gene"), all = TRUE, suffixes = c("_DepMap","_TCGA"))
+```
+
+Pseudo-caption: This is a comparison of proportions of non-neutral copy number samples between cancer cell lines and TCGA samples in our 16 TCGA classification categories.
+Each point corresponds to a single gene in the associated cancer type.
+For these plots, thresholded copy number levels of -1 (loss) and +1 (gain) were recoded as "non-neutral."
+
+```{r cn_scatters, fig.height=8, fig.width=8, eval=FALSE}
+cn_props_scatters <- ggplot(data = cn_props, aes(x = Proportion_NonNeutral_CN_TCGA, y = Proportion_NonNeutral_CN_DepMap)) +
+  facet_wrap(~ TCGA_classification, nrow = 4) +
+  geom_point(alpha = 0.3, color = "darkcyan") +
+  scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
+  scale_x_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
+  coord_cartesian(ylim = c(0, 1), xlim = c(0, 1)) +
+  geom_smooth(method = "lm", se = FALSE, lwd = 0.5, color = "darkgray") +
+  stat_cor(method = "pearson", label.x = 0.85, label.y = 0.15, label.sep = "\n") +
+  # geom_text_repel(data = subset(cn_props, Proportion_NonNeutral_CN_TCGA > 0.4 & Proportion_NonNeutral_CN_DepMap > 0.6), aes(x = Proportion_NonNeutral_CN_DepMap, y = Proportion_NonNeutral_CN_DepMap, label = Gene), size = 3) +
+  labs(x = "TCGA non-neutral CN frequency", y = "DepMap non-neutral CN frequency", caption = paste0(formatC(x = length(unique(cn_props$Gene)), format = "d", big.mark = ","), " genes compared."))
+
+ggsave("./figures/cn_depmap_tcga_scatter_pearson.png", cn_props_scatters, device = "png", dpi = 450, width = 12, height = 12, units = "in")
+```
+
+### Mut
+
+```{r mut_scatters_data, eval=FALSE}
+# Merge mutation proportion dataframes for plotting
+mut_props <- merge(mut_depmap_prop, mut_tcga_prop, by = c("TCGA_classification", "Gene"), all = TRUE, suffixes = c("_DepMap","_TCGA"))
+```
+
+Pseudo-caption: This is a comparison of proportions of mutated samples between cancer cell lines and TCGA samples in our 16 TCGA classification categories.
+Each point corresponds to a single gene in the associated cancer type.
+
+```{r mut_scatters, fig.height=8, fig.width=8, eval=FALSE}
+mut_props_scatters <- ggplot(data = mut_props, aes(x = Proportion_Mut_TCGA, y = Proportion_Mut_DepMap)) +
+  facet_wrap(~ TCGA_classification, nrow = 4) +
+  geom_point(alpha = 0.3, color = "darkcyan") +
+  scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
+  scale_x_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
+  coord_cartesian(ylim = c(0, 1), xlim = c(0, 1)) +
+  geom_smooth(method = "lm", se = FALSE, lwd = 0.5, color = "gainsboro") +
+  stat_cor(method = "pearson", label.x = 0.85, label.y = 0.15, label.sep = "\n") +
+  geom_text_repel(data = subset(mut_props, Proportion_Mut_TCGA > 0.3 & Proportion_Mut_DepMap > 0.3), aes(x = Proportion_Mut_TCGA, y = Proportion_Mut_DepMap, label = Gene), size = 3) +
+  labs(x = "TCGA mutation frequency", y = "DepMap mutation frequency", caption = paste0(formatC(x = length(unique(mut_props$Gene)), format = "d", big.mark = ","), " genes compared."))
+
+ggsave("./figures/mut_depmap_tcga_scatter_pearson.png", mut_props_scatters, device = "png", dpi = 450, width = 12, height = 12, units = "in")
 ```

### 2019-04-12 omix/omix.Rmd
functionalized most data processing and plotting of omics features{

--- 2019-04-10 omix/omix.Rmd
@@
 }
+
+DepMapTCGAMakeWideDF <- function(melted_df, output_type, data_source, exclusions) {
+  # Input is a 4-column melted dataframe of omic features
+  # Rename columns: sample_ID, TCGA_classification, Gene, Value
+  colnames(df) <- c("sample_ID", "TCGA_classification", "Gene", "Value")
+  if(tolower(output_type) == "average" | tolower(output_type) == "avg") {
+    # Average feature values per gene per TCGA classification
+    df_avg <- df %>%
+              group_by(TCGA_classification, Gene) %>%
+              summarise(Mean_Value = mean(Value))
+    # Make wide
+    df_wide <- dcast(data = df_avg,
+                     formula = Gene ~ TCGA_classification,
+                     value.var = "Mean_Value",
+                     fun.aggregate = mean)
+    # Remove genes if argument exists
+    if(!missing(exclusions)) { df_wide <- df_wide[df_wide$Gene != exclusions, ] }
+    rownames(df_wide) <- df_wide$Gene
+    df_wide$Gene <- NULL
+    colnames(df_wide) <- paste(colnames(df_wide), data_source, sep = "_")
+  }  
+  if(tolower(output_type) == "proportion" | tolower(output_type) == "prop") {
+    # Calc proportion of 1s over 1s + 0s per gene per TCGA classification
+    df_prop <- df %>% 
+               group_by(TCGA_classification, Gene) %>%
+               summarise(Proportion = sum(Value) / n())
+    # Make wide
+    df_wide <- dcast(data = df_prop,
+                     formula = Gene ~ TCGA_classification,
+                     value.var = "Proportion",
+                     fun.aggregate = mean)
+    # Remove genes if argument exists
+    if(!missing(exclusions)) { df_wide <- df_wide[df_wide$Gene != exclusions, ] }
+    rownames(df_wide) <- df_wide$Gene
+    df_wide$Gene <- NULL
+    colnames(df_wide) <- paste(colnames(df_wide), data_source, sep = "_")
+  }
+  return(df_wide)
+}
+
+DepMapTCGACorrMatrix <- function(DepMap_wide_df, TCGA_wide_df, corr_method) {
+  # Input is the output from DepMapTCGAMakeWideDF function for DepMap and TCGA
+  wide <- bind_cols(DepMap_wide_df, TCGA_wide_df)
+  # Correlate all against all
+  corr <- wide %>% as.matrix %>% cor(method = corr_method) %>% as.data.frame %>% rownames_to_column(var = "var1") %>% gather(var2, value, -var1)
+  # Filter self-comparisons and eliminate duplicate correlations
+  corr <- filter(corr, !(grepl("DepMap", var1) & grepl("DepMap", var2)) & !(grepl("TCGA", var1) & grepl("TCGA", var2)) & grepl("TCGA", var2))
+  # Data management
+  colnames(corr) <- c("DepMap", "TCGA", "r")
+  corr <- data.frame(apply(corr, 2, function(x) gsub("_TCGA|_DepMap","", x)))
+  corr$r <- as.numeric(as.character(corr$r))
+  # Set up coprrelation dataframe for plotting
+  corr_wide <- dcast(corr, DepMap ~ TCGA, value.var = "r")
+  rownames(corr_wide) <- corr_wide$DepMap
+  corr_wide$DepMap <- NULL
+  return(corr_wide)
+}
+
+DepMapTCGACorrHeatmap <- function(corr_wide_df, out_filepath, legend_title, color_breaks) {
+  # Libraries
+  require(ComplexHeatmap)
+  require(circlize)
+  # Define color scale
+  col_fun <- colorRamp2(color_breaks, c("black", "red3", "yellow", "white"))
+  # Legend properties list
+  ht_legend_list <- list(legend_direction = "horizontal", title_position = "lefttop", legend_width = unit(1.5, "in"), border = "black")
+  # Get column order to have symmetrically ordered axes
+  ht4order <- Heatmap(corr_wide_df, cluster_rows = FALSE)
+  # Make heatmap
+  ht <- Heatmap(corr_wide_df, 
+                name = legend_title,
+                col = col_fun, 
+                rect_gp = gpar(col = "black"),
+                heatmap_legend_param = ht_legend_list,
+                row_order = rev(column_order(ht4order)), 
+                show_column_dend = FALSE, 
+                cluster_rows = FALSE, 
+                row_names_side = "left",
+                row_title = "DepMap cancer cell lines",
+                column_title = "TCGA tumor samples", 
+                column_title_side = "bottom")
+  # Save to file
+  png(filename = out_filepath, width = 7.5, height = 8, units = "in", res = 500)
+  draw(ht, heatmap_legend_side = "top")
+  dev.off()
+  # Return heatmap object for in-line rendering
+  return(ht)
+}
+
+DepMapTCGAPropsScatterplots <- function(DepMap_melted_df, TCGA_melted_df, out_filepath) {
+  # Input is the 4-column melted dataframe of omic features from DepMap and TCGA
+  # Rename columns: sample_ID, TCGA_classification, Gene, Value
+  colnames(DepMap_melted_df) <- c("sample_ID", "TCGA_classification", "Gene", "Value")
+  colnames(TCGA_melted_df) <- c("sample_ID", "TCGA_classification", "Gene", "Value")
+  # Calculate proportions
+  DepMap_prop <- DepMap_melted_df %>% group_by(TCGA_classification, Gene) %>% summarise(Proportion = sum(Value) / n())
+  TCGA_prop <- TCGA_melted_df %>% group_by(TCGA_classification, Gene) %>% summarise(Proportion = sum(Value) / n())
+  # Merge proportions from DepMap and TCGA
+  props <- merge(DepMap_prop, TCGA_prop, by = c("TCGA_classification", "Gene"), all = TRUE, suffixes = c("_DepMap","_TCGA"))
+  # Plot faceted scatterplots
+  props_scatters <- ggplot(data = props, aes(x = Proportion_TCGA, y = Proportion_DepMap)) +
+    facet_wrap(~ TCGA_classification, nrow = 4) +
+    geom_point(alpha = 0.3, color = "darkcyan") +
+    scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
+    scale_x_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
+    coord_cartesian(ylim = c(0, 1), xlim = c(0, 1)) +
+    geom_smooth(method = "lm", se = FALSE, lwd = 0.5, color = "darkgray") +
+    stat_cor(method = "pearson", label.x = 0.85, label.y = 0.15, label.sep = "\n") +
+    labs(x = "TCGA frequency", y = "DepMap frequency", caption = paste0(formatC(x = length(unique(props$Gene)), format = "d", big.mark = ","), " genes compared."))
+  # Save to file
+  ggsave(out_filepath, props_scatters, device = "png", dpi = 450, width = 12, height = 12, units = "in")
+  # Return for in-line rendering
+  return(props_scatters)
+}
 ```
@@
 DepMap 19Q1 update fixed almost all of the inconsistencies of the Primary.Disease column, though there were come capitalization inconsistencies.
-```{r ccl_info_processing, eval=FALSE}
+```{r ccl_info_processing, eval = FALSE}
 ccl_info <- read.delim("./data/DepMap/DepMap-2019q1-celllines_v2_20190305.csv", sep = ",", header = TRUE, na.strings = c("", NA))
@@
 Mutation calls (coding region, germline filtered):
-```{r mutation, eval=FALSE}
+```{r mutation, eval = FALSE}
 maf_raw <- read.delim("./../data_munging/19Q1/depmap_19Q1_mutation_calls_20190305.csv.gz", header = TRUE, sep = ",", row.names = 1)
@@
 DepMap WES CN Data:
-```{r copy_number, eval=FALSE}
+```{r copy_number, eval = FALSE}
 cn <- read.delim("./../data_munging/19Q1/public_19Q1_gene_cn_20190305.csv.gz", sep = ",", check.names = FALSE, header = TRUE)
@@
 19Q1, CCLE RNAseq gene expression data (log2(TPM+1)):
-```{r gene_expression, eval=FALSE}
+```{r gene_expression, eval = FALSE}
 ge <- read.delim("./../../htscreens_giant_files/CCLE_depMap_19Q1_TPM_20190305.csv.gz", header = TRUE, sep = ",", check.names = FALSE)
@@
 
-```{r crispr, eval=TRUE}
+```{r crispr}
 # Sample info from figshare
@@
 
-```{r pozdeyev_processing, eval=FALSE}
+```{r pozdeyev_processing, eval = FALSE}
 ccle_poz <- read.delim("./data/pozdeyev2016/CCLE_drug_response_metrics.csv.gz", sep = ",")
@@
 
-```{r exploratory_plots, eval=FALSE}
+```{r exploratory_plots, eval = FALSE}
 # Data subsetting for easier tracking throughout plots
@@
 
+```{r}
+tcga_classifications_16 <- c("BLCA", "BRCA", "COADREAD", "ESCA", "GBMLGG", "HNSC", "KIRC", "LIHC", "LUAD", "LUSC", "OV", "PAAD", "SARC", "SKCM", "STAD", "UCEC")
+```
+
 ## GE
@@
 ```{r ge_heatmap_data, eval=FALSE, warning=FALSE}
-# DepMap gene expression
+# DepMap
+# TPM
 ge_depmap <- read.delim("./../../htscreens_giant_files/omix/GE/GE_DepMap_filter.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
 colnames(ge_depmap)[colnames(ge_depmap) == "cancer"] <- "TCGA_classification"
-# Mean center scale
+# Mean-center scale
 ge_depmap[, 4:ncol(ge_depmap)] <- apply(ge_depmap[, 4:ncol(ge_depmap)], MARGIN = 2, FUN = scale, center = TRUE, scale = TRUE)
@@
 ge_depmap_melt <- melt(ge_depmap, id.vars = c("sample_ID", "TCGA_classification"), measure.vars = colnames(ge_depmap)[4:length(colnames(ge_depmap))], variable.name = "Gene", value.name = "TPM_scaled")
-# Average scaled TPM per gene per TCGA classification
-ge_depmap_avg <- ge_depmap_melt %>% group_by(TCGA_classification, Gene) %>% summarise(Mean_TPM = mean(TPM_scaled))
-# Make wide
-ge_depmap_wide <- dcast(data = ge_depmap_avg, formula = Gene ~ TCGA_classification, fun.aggregate = mean)
-rownames(ge_depmap_wide) <- ge_depmap_wide$Gene
-ge_depmap_wide$Gene <- NULL
-colnames(ge_depmap_wide) <- paste(colnames(ge_depmap_wide), "DepMap", sep = "_")
+# Make wide
+ge_depmap_wide <- DepMapTCGAMakeWideDF(df = ge_depmap_melt, output_type = "average", data_source = "DepMap")
 
@@
 ge_tcga_melt <- melt(ge_tcga, id.vars = c("sample_ID", "TCGA_classification"), measure.vars = colnames(ge_tcga)[4:length(colnames(ge_tcga))], variable.name = "Gene", value.name = "TPM_scaled")
-# Average scaled TPM per gene per TCGA classification
-ge_tcga_avg <- ge_tcga_melt %>% group_by(TCGA_classification, Gene) %>% summarise(Mean_TPM = mean(TPM_scaled))
-# Make wide
-ge_tcga_wide <- dcast(data = ge_tcga_avg, formula = Gene ~ TCGA_classification, fun.aggregate = mean)
-rownames(ge_tcga_wide) <- ge_tcga_wide$Gene
-ge_tcga_wide$Gene <- NULL
-colnames(ge_tcga_wide) <- paste(colnames(ge_tcga_wide), "TCGA", sep = "_")
+# Make wide
+ge_tcga_wide <- DepMapTCGAMakeWideDF(df = ge_tcga_melt, output_type = "average", data_source = "TCGA")
 
 # Correlate all against all
-ge_wide <- bind_cols(ge_depmap_wide, ge_tcga_wide)
-ge_corr <- ge_wide %>% as.matrix %>% cor(method = "spearman") %>% as.data.frame %>% rownames_to_column(var = "var1") %>% gather(var2, value, -var1)
-# Filter self-comparisons and eliminate duplicate correlations
-ge_corr <- filter(ge_corr, !(grepl("DepMap", var1) & grepl("DepMap", var2)) & !(grepl("TCGA", var1) & grepl("TCGA", var2)) & grepl("TCGA", var2))
-# Data management
-colnames(ge_corr) <- c("DepMap", "TCGA", "r")
-ge_corr <- data.frame(apply(ge_corr, 2, function(x) gsub("_TCGA|_DepMap","", x)))
-ge_corr$r <- as.numeric(as.character(ge_corr$r))
-# Set up coprrelation dataframe for plotting
-ge_corr_wide <- dcast(ge_corr, DepMap ~ TCGA)
-rownames(ge_corr_wide) <- ge_corr_wide$DepMap
-ge_corr_wide$DepMap <- NULL
+ge_corr_wide_pearson <- DepMapTCGACorrMatrix(DepMap_wide_df = ge_depmap_wide, TCGA_wide_df = ge_tcga_wide, corr_method = "pearson")
+ge_corr_wide_spearman <- DepMapTCGACorrMatrix(DepMap_wide_df = ge_depmap_wide, TCGA_wide_df = ge_tcga_wide, corr_method = "spearman")
 ```
@@
 ```{r ge_heatmap, eval=FALSE, fig.height=4, fig.width=3.75}
-col_fun <- colorRamp2(c(-0.5, 0, 0.5, 1), c("black", "red3", "yellow", "white"))
-ge_ht4order <- Heatmap(ge_corr_wide, cluster_rows = FALSE)
-
-ge_ht_legend_list <- list(legend_direction = "horizontal", title_position = "lefttop", legend_width = unit(1.5, "in"), border = "black")
-
-ge_ht <- Heatmap(ge_corr_wide, 
-                 name = "Expression correlation",
-                 col = col_fun, 
-                 rect_gp = gpar(col = "black"),
-                 heatmap_legend_param = ge_ht_legend_list,
-                 row_order = rev(column_order(ge_ht4order)), 
-                 show_column_dend = FALSE, 
-                 cluster_rows = FALSE, 
-                 row_names_side = "left",
-                 row_title = "DepMap cancer cell lines",
-                 column_title = "TCGA tumor samples", 
-                 column_title_side = "bottom")
-png(filename = "./figures/ge_depmap_tcga_heatmap_spearman.png", width = 7.5, height = 8, units = "in", res = 500)
-draw(ge_ht, heatmap_legend_side = "top")
-dev.off()
-```
-
-## CN
-
-Data wrangling and processing:
-```{r cn_heatmap_data, eval=FALSE, warning=FALSE}
-# TCGA copy number
-cn_tcga <- read.delim("./data/CN/CN_GDC_filter.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
-colnames(cn_tcga)[colnames(cn_tcga) == "cancer"] <- "TCGA_classification"
-# Melt
-cn_tcga_melt <- melt(cn_tcga, id.vars = c("sample_ID", "TCGA_classification"), measure.vars = colnames(cn_tcga)[4:length(colnames(cn_tcga))], variable.name = "Gene", value.name = "CN")
-# Average scaled TPM per gene per TCGA classification
-cn_tcga_avg <- cn_tcga_melt %>% group_by(TCGA_classification, Gene) %>% summarise(Mean_CN = mean(CN))
-# Make wide
-cn_tcga_wide <- dcast(data = cn_tcga_avg, formula = Gene ~ TCGA_classification, fun.aggregate = mean)
-rownames(cn_tcga_wide) <- cn_tcga_wide$Gene
-cn_tcga_wide$Gene <- NULL
-colnames(cn_tcga_wide) <- paste(colnames(cn_tcga_wide), "TCGA", sep = "_")
-
-# DepMap copy number (18Q4)
-cn_depmap <- read.delim("./data/CN/CN_DepMap_filter.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
-colnames(cn_depmap)[colnames(cn_depmap) == "cancer"] <- "TCGA_classification"
-# Melt
-cn_depmap_melt <- melt(cn_depmap, id.vars = c("sample_ID", "TCGA_classification"), measure.vars = colnames(cn_depmap)[4:length(colnames(cn_depmap))], variable.name = "Gene", value.name = "CN")
-# Average CN levels per gene per TCGA classification
-cn_depmap_avg <- cn_depmap_melt %>% group_by(TCGA_classification, Gene) %>% summarise(Mean_CN = mean(CN))
-# Make wide
-cn_depmap_wide <- dcast(data = cn_depmap_avg, formula = Gene ~ TCGA_classification, fun.aggregate = mean)
-rownames(cn_depmap_wide) <- cn_depmap_wide$Gene
-cn_depmap_wide$Gene <- NULL
-colnames(cn_depmap_wide) <- paste(colnames(cn_depmap_wide), "DepMap", sep = "_")
-
-# Correlate all against all (18Q4)
-cn_wide <- bind_cols(cn_depmap_wide, cn_tcga_wide)
-cn_corr <- cn_wide %>% as.matrix %>% cor(method = "pearson") %>% as.data.frame %>% rownames_to_column(var = "var1") %>% gather(var2, value, -var1)
-# Filter self-comparisons and eliminate duplicate correlations
-cn_corr <- filter(cn_corr, !(grepl("DepMap", var1) & grepl("DepMap", var2)) & !(grepl("TCGA", var1) & grepl("TCGA", var2)) & grepl("TCGA", var2))
-# Data management
-colnames(cn_corr) <- c("DepMap", "TCGA", "r")
-cn_corr <- data.frame(apply(cn_corr, 2, function(x) gsub("_TCGA|_DepMap","", x)))
-cn_corr$r <- as.numeric(as.character(cn_corr$r))
-# Set up coprrelation dataframe for plotting
-cn_corr_wide <- dcast(cn_corr, DepMap ~ TCGA)
-rownames(cn_corr_wide) <- cn_corr_wide$DepMap
-cn_corr_wide$DepMap <- NULL
-```
-
-Pseudo-figure caption: This is comparison of thresholded copy number profiles between DepMap cancer cell lines and TCGA tumor samples, both classified by TCGA project.
-Levels are -1 for copy number loss, 0 for neutral, and 1 for gain.
-In each dataset and for each TCGA classification, these numeric copy number levels across all genes shared between the two datasets were averaged, and the datasets were correlated against each other.
-Pearson/Spearman correlations (r) between TCGA and DepMap copy number feature sets are shown in the heatmap.
-
-Make heatmaps:
-```{r cn_heatmaps, eval=FALSE, fig.height=4, fig.width=3.75}
-col_fun <- colorRamp2(c(0, 0.25, 0.5, 0.75), c("black", "red3", "yellow", "white"))
-cn_ht_legend_list <- list(legend_direction = "horizontal", title_position = "lefttop", legend_width = unit(1.5, "in"), border = "black")
-
-# 18Q4
-cn_ht4order <- Heatmap(cn_corr_wide, cluster_rows = FALSE)
-cn_ht <- Heatmap(cn_corr_wide, 
-                 name = "Copy number correlation",
-                 col = col_fun, 
-                 rect_gp = gpar(col = "black"),
-                 heatmap_legend_param = cn_ht_legend_list,
-                 row_order = rev(column_order(cn_ht4order)), 
-                 show_column_dend = FALSE, 
-                 cluster_rows = FALSE, 
-                 row_names_side = "left",
-                 row_title = "DepMap cancer cell lines",
-                 column_title = "TCGA tumor samples", 
-                 column_title_side = "bottom")
-# png(filename = "./figures/cn_depmap_tcga_heatmap_pearson.png", width = 7.5, height = 8, units = "in", res = 500)
-draw(cn_ht, heatmap_legend_side = "top")
-# dev.off()
+ge_ht_p <- DepMapTCGACorrHeatmap(corr_wide_df = ge_corr_wide_pearson, out_filepath = "./figures/ge_depmap_tcga_heatmap_pearson.png", legend_title = "Expression Pearson correlation", color_breaks = c(-0.5, 0, 0.5, 1))
+# draw(ge_ht_p, heatmap_legend_side = "top")
+
+ge_ht_s <- DepMapTCGACorrHeatmap(corr_wide_df = ge_corr_wide_spearman, out_filepath = "./figures/ge_depmap_tcga_heatmap_spearman.png", legend_title = "Expression Spearman correlation", color_breaks = c(-0.5, 0, 0.5, 1))
+# draw(ge_ht_s, heatmap_legend_side = "top")
 ```
@@
 ```{r mut_heatmap_data, eval=FALSE}
+# DepMap
+mut_depmap <- read.delim("./data/mutation/mutation_DepMap_filter.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
+mut_depmap <- unfactorize(mut_depmap)
+mut_depmap[, 4:ncol(mut_depmap)] <- apply(mut_depmap[, 4:ncol(mut_depmap)], 2, function(x) ifelse(x > 1, 1, x))
+colnames(mut_depmap)[colnames(mut_depmap) == "cancer"] <- "TCGA_classification"
+# Melt
+mut_depmap_melt <- melt(mut_depmap, id.vars = c("sample_ID", "TCGA_classification"), measure.vars = colnames(mut_depmap)[4:length(colnames(mut_depmap))], variable.name = "Gene", value.name = "Mutation_Status")
+# Make wide
+mut_depmap_wide <- DepMapTCGAMakeWideDF(df = mut_depmap_melt, output_type = "proportion", data_source = "DepMap", exclusions = c("TP53"))
+
 # TCGA
@@
 mut_tcga_melt <- melt(mut_tcga, id.vars = c("sample_ID", "TCGA_classification"), measure.vars = colnames(mut_tcga)[4:length(colnames(mut_tcga))], variable.name = "Gene", value.name = "Mutation_Status")
-# Average CN levels per gene per TCGA classification
-mut_tcga_prop <- mut_tcga_melt %>% group_by(TCGA_classification, Gene) %>% summarise(Proportion_Mut = sum(Mutation_Status)/n())
-# Make wide
-mut_tcga_wide <- dcast(data = mut_tcga_prop, formula = Gene ~ TCGA_classification, fun.aggregate = mean)
-rownames(mut_tcga_wide) <- mut_tcga_wide$Gene
-mut_tcga_wide$Gene <- NULL
-colnames(mut_tcga_wide) <- paste(colnames(mut_tcga_wide), "TCGA", sep = "_")
-
-# DepMap
-mut_depmap <- read.delim("./data/mutation/mutation_DepMap_filter.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
-mut_depmap <- unfactorize(mut_depmap)
-mut_depmap[, 4:ncol(mut_depmap)] <- apply(mut_depmap[, 4:ncol(mut_depmap)], 2, function(x) ifelse(x > 1, 1, x))
-colnames(mut_depmap)[colnames(mut_depmap) == "cancer"] <- "TCGA_classification"
-# Melt
-mut_depmap_melt <- melt(mut_depmap, id.vars = c("sample_ID", "TCGA_classification"), measure.vars = colnames(mut_depmap)[4:length(colnames(mut_depmap))], variable.name = "Gene", value.name = "Mutation_Status")
-# Average CN levels per gene per TCGA classification
-mut_depmap_prop <- mut_depmap_melt %>% group_by(TCGA_classification, Gene) %>% summarise(Proportion_Mut = sum(Mutation_Status)/n())
-# Make wide
-mut_depmap_wide <- dcast(data = mut_depmap_prop, formula = Gene ~ TCGA_classification, fun.aggregate = mean)
-rownames(mut_depmap_wide) <- mut_depmap_wide$Gene
-mut_depmap_wide$Gene <- NULL
-colnames(mut_depmap_wide) <- paste(colnames(mut_depmap_wide), "DepMap", sep = "_")
-
-# Correlate all against all (18Q4)
-mut_wide <- bind_cols(mut_depmap_wide, mut_tcga_wide)
-mut_corr <- mut_wide %>% as.matrix %>% cor(method = "spearman") %>% as.data.frame %>% rownames_to_column(var = "var1") %>% gather(var2, value, -var1)
-# Filter self-comparisons and eliminate duplicate correlations
-mut_corr <- filter(mut_corr, !(grepl("DepMap", var1) & grepl("DepMap", var2)) & !(grepl("TCGA", var1) & grepl("TCGA", var2)) & grepl("TCGA", var2))
-# Data management
-colnames(mut_corr) <- c("DepMap", "TCGA", "r")
-mut_corr <- data.frame(apply(mut_corr, 2, function(x) gsub("_TCGA|_DepMap","", x)))
-mut_corr$r <- as.numeric(as.character(mut_corr$r))
-# Set up coprrelation dataframe for plotting
-mut_corr_wide <- dcast(mut_corr, DepMap ~ TCGA)
-rownames(mut_corr_wide) <- mut_corr_wide$DepMap
-mut_corr_wide$DepMap <- NULL
+# Make wide
+mut_tcga_wide <- DepMapTCGAMakeWideDF(df = mut_tcga_melt, output_type = "proportion", data_source = "TCGA", exclusions = c("TP53"))
+
+# Correlate all against all
+mut_corr_wide_pearson <- DepMapTCGACorrMatrix(DepMap_wide_df = mut_depmap_wide, TCGA_wide_df = mut_tcga_wide, corr_method = "pearson")
+mut_corr_wide_spearman <- DepMapTCGACorrMatrix(DepMap_wide_df = mut_depmap_wide, TCGA_wide_df = mut_tcga_wide, corr_method = "spearman")
 ```
@@
 In each dataset and for each TCGA classification, the proportion of samples containing at least one mutation was calculated for all genes shared between the two datasets, and the proportions were correlated against each other.
+Pearson/Spearman correlations (r) between TCGA and DepMap mutation feature sets are shown in the heatmap.
+
+For plots labeled as "5000", the 5,000 most variable genes analyzed in the gene expression heatmap were selected for the mutation analyses.
+Alternatively, for the plots labeled as "252", the genes in the TCGA mutation dataset were analyzed if they were mutated in >=4% annotated samples and had a mutation in at least one cancer cell line from DepMap.
+TP53 was removed from the heatmap, as was done in Barretina et al.
+(2012).
+For the scatterplots, TP53 was retained.
+
+Pseudo-caption for scatterplots: This is a comparison of proportions of mutated samples between cancer cell lines and TCGA samples in our 16 TCGA classification categories.
+Each point corresponds to a single gene in the associated cancer type.
+
+Make plots:
+```{r mut_plots, eval=FALSE, fig.height=4, fig.width=3.75}
+mut_ht_p <- DepMapTCGACorrHeatmap(corr_wide_df = mut_corr_wide_pearson, out_filepath = "./figures/mut_depmap_tcga_heatmap_pearson_252.png", legend_title = "Mutation Pearson correlation", color_breaks = c(0, 0.3, 0.6, 0.9))
+# draw(mut_ht_p, heatmap_legend_side = "top")
+
+mut_ht_s <- DepMapTCGACorrHeatmap(corr_wide_df = mut_corr_wide_spearman, out_filepath = "./figures/mut_depmap_tcga_heatmap_spearman_252.png", legend_title = "Mutation Spearman correlation", color_breaks = c(0, 0.3, 0.5, 0.7))
+# draw(mut_ht_s, heatmap_legend_side = "top")
+
+mut_props_scatters <- DepMapTCGAPropsScatterplots(DepMap_melted_df = mut_depmap_melt, TCGA_melted_df = mut_tcga_melt, out_filepath = "./figures/mut_depmap_tcga_scatter_pearson_253.png")
+```
+
+## CN
+
+### Continuous
+
+Continuous CN estimate data wrangling and processing:
+```{r cn_heatmap_data_continuous, eval=FALSE, warning=FALSE}
+# DepMap copy number
+cn_depmap <- read.delim("./../../htscreens_giant_files/omix/CN/CN_cont_DepMap_filter.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
+colnames(cn_depmap)[colnames(cn_depmap) == "cancer"] <- "TCGA_classification"
+# Mean center scale
+cn_depmap[, 4:ncol(cn_depmap)] <- apply(cn_depmap[, 4:ncol(cn_depmap)], MARGIN = 2, FUN = scale, center = TRUE, scale = TRUE)
+# Melt
+cn_depmap_melt <- melt(cn_depmap, id.vars = c("sample_ID", "TCGA_classification"), measure.vars = colnames(cn_depmap)[4:length(colnames(cn_depmap))], variable.name = "Gene", value.name = "CN_scaled")
+cn_depmap_melt <- filter(cn_depmap_melt, TCGA_classification %in% tcga_classifications_16)
+# Make wide
+cn_depmap_wide <- DepMapTCGAMakeWideDF(df = cn_depmap_melt, output_type = "average", data_source = "DepMap")
+
+# TCGA cop number
+cn_tcga <- read.delim("./../../htscreens_giant_files/omix/CN/CN_cont_Xena_filter.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
+colnames(cn_tcga)[colnames(cn_tcga) == "cancer"] <- "TCGA_classification"
+# Mean center scale
+cn_tcga[, 4:ncol(cn_tcga)] <- apply(cn_tcga[, 4:ncol(cn_tcga)], MARGIN = 2, FUN = scale, center = TRUE, scale = TRUE)
+# Melt
+cn_tcga_melt <- melt(cn_tcga, id.vars = c("sample_ID", "TCGA_classification"), measure.vars = colnames(cn_tcga)[4:length(colnames(cn_tcga))], variable.name = "Gene", value.name = "CN_scaled")
+cn_tcga_melt <- filter(cn_tcga_melt, TCGA_classification %in% tcga_classifications_16)
+# Make wide
+cn_tcga_wide <- DepMapTCGAMakeWideDF(df = cn_tcga_melt, output_type = "proportion", data_source = "TCGA")
+
+# Correlate all against all
+cn_corr_wide_pearson <- DepMapTCGACorrMatrix(DepMap_wide_df = cn_depmap_wide, TCGA_wide_df = cn_tcga_wide, corr_method = "pearson")
+cn_corr_wide_spearman <- DepMapTCGACorrMatrix(DepMap_wide_df = cn_depmap_wide, TCGA_wide_df = cn_tcga_wide, corr_method = "spearman")
+```
+
+### -1, 0, +1
+
+Thresholded tertiary CN estimate data wrangling and processing:
+```{r cn_heatmap_data_thresholded3, eval=FALSE, warning=FALSE}
+# DepMap copy number (18Q4)
+cn_depmap <- read.delim("./data/CN/CN_DepMap_filter.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
+colnames(cn_depmap)[colnames(cn_depmap) == "cancer"] <- "TCGA_classification"
+# Melt
+cn_depmap_melt <- melt(cn_depmap, id.vars = c("sample_ID", "TCGA_classification"), measure.vars = colnames(cn_depmap)[4:length(colnames(cn_depmap))], variable.name = "Gene", value.name = "CN")
+# Make wide
+cn_depmap_wide <- DepMapTCGAMakeWideDF(df = cn_depmap_melt, output_type = "average", data_source = "DepMap")
+
+# TCGA copy number
+cn_tcga <- read.delim("./data/CN/CN_GDC_filter.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
+colnames(cn_tcga)[colnames(cn_tcga) == "cancer"] <- "TCGA_classification"
+# Melt
+cn_tcga_melt <- melt(cn_tcga, id.vars = c("sample_ID", "TCGA_classification"), measure.vars = colnames(cn_tcga)[4:length(colnames(cn_tcga))], variable.name = "Gene", value.name = "CN")
+# Make wide
+cn_tcga_wide <- DepMapTCGAMakeWideDF(df = cn_tcga_melt, output_type = "proportion", data_source = "TCGA")
+
+# Correlate all against all
+cn_corr_wide_pearson <- DepMapTCGACorrMatrix(DepMap_wide_df = cn_depmap_wide, TCGA_wide_df = cn_tcga_wide, corr_method = "pearson")
+cn_corr_wide_spearman <- DepMapTCGACorrMatrix(DepMap_wide_df = cn_depmap_wide, TCGA_wide_df = cn_tcga_wide, corr_method = "spearman")
+```
+
+### ±1, 0
+
+Thresholded binary CN estimate data wrangling and processing (for both datasets, CN_Status is encoded as 1 is non-neutral (-1 or +1) and 0 is neutral):
+```{r cn_heatmap_data_thresholded2, eval=FALSE, warning=FALSE}
+# DepMap
+cn_depmap <- read.delim("./data/CN/CN_DepMap_filter.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
+colnames(cn_depmap)[colnames(cn_depmap) == "cancer"] <- "TCGA_classification"
+# Melt
+cn_depmap_melt <- melt(cn_depmap, id.vars = c("sample_ID", "TCGA_classification"), measure.vars = colnames(cn_depmap)[4:length(colnames(cn_depmap))], variable.name = "Gene", value.name = "CN")
+# Calc proportion of non-neutral CN per gene per TCGA classification
+cn_depmap_melt$CN_Status <- with(cn_depmap_melt, ifelse(CN != 0, 1, CN))
+cn_depmap_melt$CN <- NULL
+# Make wide
+cn_depmap_wide <- DepMapTCGAMakeWideDF(df = cn_depmap_melt, output_type = "average", data_source = "DepMap")
+
+# TCGA
+cn_tcga <- read.delim("./data/CN/CN_GDC_filter.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
+colnames(cn_tcga)[colnames(cn_tcga) == "cancer"] <- "TCGA_classification"
+# Melt
+cn_tcga_melt <- melt(cn_tcga, id.vars = c("sample_ID", "TCGA_classification"), measure.vars = colnames(cn_tcga)[4:length(colnames(cn_tcga))], variable.name = "Gene", value.name = "CN")
+# Calc proportion of non-neutral CN per gene per TCGA classification
+cn_tcga_melt$CN_Status <- with(cn_tcga_melt, ifelse(CN != 0, 1, CN))
+cn_tcga_melt$CN <- NULL
+# Make wide
+cn_tcga_wide <- DepMapTCGAMakeWideDF(df = cn_tcga_melt, output_type = "proportion", data_source = "TCGA")
+
+# Correlate all against all
+cn_corr_wide_pearson <- DepMapTCGACorrMatrix(DepMap_wide_df = cn_depmap_wide, TCGA_wide_df = cn_tcga_wide, corr_method = "pearson")
+cn_corr_wide_spearman <- DepMapTCGACorrMatrix(DepMap_wide_df = cn_depmap_wide, TCGA_wide_df = cn_tcga_wide, corr_method = "spearman")
+```
+
+### -1/0, +1
+
+Thresholded binary CN gain/non-gain estimate data wrangling and processing:
+```{r cn_heatmap_data_thresholdedgain, eval=FALSE, warning=FALSE}
+# DepMap
+cn_depmap <- read.delim("./data/CN/CN_DepMap_filter.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
+colnames(cn_depmap)[colnames(cn_depmap) == "cancer"] <- "TCGA_classification"
+# Melt
+cn_depmap_melt <- melt(cn_depmap, id.vars = c("sample_ID", "TCGA_classification"), measure.vars = colnames(cn_depmap)[4:length(colnames(cn_depmap))], variable.name = "Gene", value.name = "CN")
+# Calc proportion of non-neutral CN per gene per TCGA classification
+cn_depmap_melt$CN_Status <- with(cn_depmap_melt, ifelse(CN != 1, 0, CN))
+cn_depmap_melt$CN <- NULL
+# Make wide
+cn_depmap_wide <- DepMapTCGAMakeWideDF(df = cn_depmap_melt, output_type = "average", data_source = "DepMap")
+
+# TCGA
+cn_tcga <- read.delim("./data/CN/CN_GDC_filter.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
+colnames(cn_tcga)[colnames(cn_tcga) == "cancer"] <- "TCGA_classification"
+# Melt
+cn_tcga_melt <- melt(cn_tcga, id.vars = c("sample_ID", "TCGA_classification"), measure.vars = colnames(cn_tcga)[4:length(colnames(cn_tcga))], variable.name = "Gene", value.name = "CN")
+# Calc proportion of non-neutral CN per gene per TCGA classification
+cn_tcga_melt$CN_Status <- with(cn_tcga_melt, ifelse(CN != 1, 0, CN))
+cn_tcga_melt$CN <- NULL
+# Make wide
+cn_tcga_wide <- DepMapTCGAMakeWideDF(df = cn_tcga_melt, output_type = "proportion", data_source = "TCGA")
+
+# Correlate all against all
+cn_corr_wide_pearson <- DepMapTCGACorrMatrix(DepMap_wide_df = cn_depmap_wide, TCGA_wide_df = cn_tcga_wide, corr_method = "pearson")
+cn_corr_wide_spearman <- DepMapTCGACorrMatrix(DepMap_wide_df = cn_depmap_wide, TCGA_wide_df = cn_tcga_wide, corr_method = "spearman")
+```
+
+### -1, 0/+1
+
+Thresholded binary CN loss/non-loss estimate data wrangling and processing:
+```{r cn_heatmap_data_thresholdedloss, eval=FALSE, warning=FALSE}
+# DepMap
+cn_depmap <- read.delim("./data/CN/CN_DepMap_filter.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
+colnames(cn_depmap)[colnames(cn_depmap) == "cancer"] <- "TCGA_classification"
+# Melt
+cn_depmap_melt <- melt(cn_depmap, id.vars = c("sample_ID", "TCGA_classification"), measure.vars = colnames(cn_depmap)[4:length(colnames(cn_depmap))], variable.name = "Gene", value.name = "CN")
+# Calc proportion of non-neutral CN per gene per TCGA classification
+cn_depmap_melt$CN_Status <- with(cn_depmap_melt, ifelse(CN != -1, 0, CN))
+cn_depmap_melt$CN <- NULL
+# Make wide
+cn_depmap_wide <- DepMapTCGAMakeWideDF(df = cn_depmap_melt, output_type = "average", data_source = "DepMap")
+
+# TCGA
+cn_tcga <- read.delim("./data/CN/CN_GDC_filter.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
+colnames(cn_tcga)[colnames(cn_tcga) == "cancer"] <- "TCGA_classification"
+# Melt
+cn_tcga_melt <- melt(cn_tcga, id.vars = c("sample_ID", "TCGA_classification"), measure.vars = colnames(cn_tcga)[4:length(colnames(cn_tcga))], variable.name = "Gene", value.name = "CN")
+# Calc proportion of non-neutral CN per gene per TCGA classification
+cn_tcga_melt$CN_Status <- with(cn_tcga_melt, ifelse(CN != -1, 0, CN))
+cn_tcga_melt$CN <- NULL
+# Make wide
+cn_tcga_wide <- DepMapTCGAMakeWideDF(df = cn_tcga_melt, output_type = "proportion", data_source = "TCGA")
+
+# Correlate all against all
+cn_corr_wide_pearson <- DepMapTCGACorrMatrix(DepMap_wide_df = cn_depmap_wide, TCGA_wide_df = cn_tcga_wide, corr_method = "pearson")
+cn_corr_wide_spearman <- DepMapTCGACorrMatrix(DepMap_wide_df = cn_depmap_wide, TCGA_wide_df = cn_tcga_wide, corr_method = "spearman")
+```
+
+### Plots
+
+Pseudo-figure caption for thresholded data: This is comparison of thresholded copy number profiles between DepMap cancer cell lines and TCGA tumor samples, both classified by TCGA project.
+Levels are -1 for copy number loss, 0 for neutral, and 1 for gain.
+In each dataset and for each TCGA classification, these numeric copy number levels across all genes shared between the two datasets were averaged, and the datasets were correlated against each other.
 Pearson/Spearman correlations (r) between TCGA and DepMap copy number feature sets are shown in the heatmap.
 
-Genes in the TCGA mutation dataset were analyzed if they were mutated in >=4% annotated samples and had a mutaiton in at least one cancer cell line from DepMap.
-
-Make heatmaps:
-```{r cn_heatmaps, eval=FALSE, fig.height=4, fig.width=3.75}
-col_fun <- colorRamp2(c(0, 0.15, 0.35, 0.5), c("black", "red3", "yellow", "white"))
-mut_ht_legend_list <- list(legend_direction = "horizontal", title_position = "lefttop", legend_width = unit(1.5, "in"), border = "black")
-
-# 18Q4
-mut_ht4order <- Heatmap(mut_corr_wide, cluster_rows = FALSE)
-mut_ht <- Heatmap(mut_corr_wide, 
-                 name = "Mutation correlation",
-                 col = col_fun, 
-                 rect_gp = gpar(col = "black"),
-                 heatmap_legend_param = mut_ht_legend_list,
-                 row_order = rev(column_order(mut_ht4order)), 
-                 show_column_dend = FALSE, 
-                 cluster_rows = FALSE, 
-                 row_names_side = "left",
-                 row_title = "DepMap cancer cell lines",
-                 column_title = "TCGA tumor samples", 
-                 column_title_side = "bottom")
-# png(filename = "./figures/mut_depmap_tcga_heatmap_spearman.png", width = 7.5, height = 8, units = "in", res = 500)
-draw(mut_ht, heatmap_legend_side = "top")
-# dev.off()
+Pseudo-caption for scatterplots: This is a comparison of proportions of non-neutral copy number samples between cancer cell lines and TCGA samples in our 16 TCGA classification categories.
+Each point corresponds to a single gene in the associated cancer type.
+For these plots, thresholded copy number levels of -1 (loss) and +1 (gain) were recoded as "non-neutral."
+
+Make plots:
+```{r cn_plots, eval=TRUE, fig.height=4, fig.width=3.75}
+cn_ht_p <- DepMapTCGACorrHeatmap(corr_wide_df = cn_corr_wide_pearson, out_filepath = "./figures/cn_depmap_tcga_heatmap_pearson_thresholdedloss.png", legend_title = "Copy number Pearson correlation", color_breaks = c(0, 0.2, 0.4, 0.6))
+# draw(cn_ht_p, heatmap_legend_side = "top")
+
+cn_ht_s <- DepMapTCGACorrHeatmap(corr_wide_df = cn_corr_wide_spearman, out_filepath = "./figures/cn_depmap_tcga_heatmap_spearman_thresholdedloss.png", legend_title = "Copy number Spearman correlation", color_breaks = c(0, 0.2, 0.4, 0.6))
+# draw(cn_ht_s, heatmap_legend_side = "top")
+
+cn_props_scatters <- DepMapTCGAPropsScatterplots(DepMap_melted_df = cn_depmap_melt, TCGA_melted_df = cn_tcga_melt, out_filepath = "./figures/cn_depmap_tcga_scatter_pearson_thresholdedloss.png")
 ```
@@
 
-```{r, eval=FALSE}
+```{r, eval = FALSE}
 tcga_hist_converter <- read.xlsx("./data/TCGA/cell_line_annotation.xlsx", sheet = 1, startRow = 1, colNames = TRUE, rowNames = FALSE)
@@
 
-```{r, eval=FALSE}
+```{r, eval = FALSE}
 auc_matched <- read.delim("./data_munging/pharmacogenomics_raw_files/celline_stack.csv.gz", sep = ",")
@@
 Plots:
-```{r, eval=FALSE}
+```{r, eval = FALSE}
 futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
@@
 
-```{r, eval=FALSE}
+```{r, eval = FALSE}
 ccl_info$sample_ID <- with(ccl_info, paste(source, source_ccl_name, source_histology, sep = "_"))
@@
 Compare histology representation for CCLE, CTRP, and GDSC:
-```{r, eval=FALSE}
+```{r, eval = FALSE}
 sort(unique(na.omit(ccle_auc_long$source_histology)))
@@
 
-```{r, eval=FALSE}
+```{r, eval = FALSE}
 hist_auc_ccle <- ggplot(data = ccle_auc_long) +

### 2019-04-15 omix/omix.Rmd
update omix.Rmd

@@
   # Rename columns: sample_ID, TCGA_classification, Gene, Value
-  colnames(df) <- c("sample_ID", "TCGA_classification", "Gene", "Value")
+  colnames(melted_df) <- c("sample_ID", "TCGA_classification", "Gene", "Value")
   if(tolower(output_type) == "average" | tolower(output_type) == "avg") {
     # Average feature values per gene per TCGA classification
-    df_avg <- df %>%
+    df_avg <- melted_df %>%
               group_by(TCGA_classification, Gene) %>%
@@
     # Calc proportion of 1s over 1s + 0s per gene per TCGA classification
-    df_prop <- df %>% 
+    df_prop <- melted_df %>% 
                group_by(TCGA_classification, Gene) %>%
@@
 
-DepMapTCGACorrMatrix <- function(DepMap_wide_df, TCGA_wide_df, corr_method) {
+DepMapTCGACorrMatrix <- function(DepMap_wide_df, TCGA_wide_df, corr_method, data_format) {
   # Input is the output from DepMapTCGAMakeWideDF function for DepMap and TCGA
@@
   # Correlate all against all
-  corr <- wide %>% as.matrix %>% cor(method = corr_method) %>% as.data.frame %>% rownames_to_column(var = "var1") %>% gather(var2, value, -var1)
+  corr <- wide %>% as.matrix %>% cor(method = corr_method, use = "pairwise.complete.obs") %>% as.data.frame %>% rownames_to_column(var = "var1") %>% gather(var2, value, -var1)
   # Filter self-comparisons and eliminate duplicate correlations
@@
   corr$r <- as.numeric(as.character(corr$r))
-  # Set up coprrelation dataframe for plotting
-  corr_wide <- dcast(corr, DepMap ~ TCGA, value.var = "r")
-  rownames(corr_wide) <- corr_wide$DepMap
-  corr_wide$DepMap <- NULL
-  return(corr_wide)
+  if(data_format == "long") {
+    # Leave dataframe in long format (for plotting with GGPlot)
+    corr_df <- corr
+  }
+  if(data_format == "wide") {
+    # Make wide dataframe (for plotting with ComplexHeatmap)
+    corr_df <- dcast(corr, DepMap ~ TCGA, value.var = "r")
+    rownames(corr_df) <- corr_df$DepMap
+    corr_df$DepMap <- NULL
+  }
+  return(corr_df)
 }
@@
   ht_legend_list <- list(legend_direction = "horizontal", title_position = "lefttop", legend_width = unit(1.5, "in"), border = "black")
-  # Get column order to have symmetrically ordered axes
+  # Get clustered column order to have symmetrically ordered axes
+  # By default, clustering is performed by hclust()
   ht4order <- Heatmap(corr_wide_df, cluster_rows = FALSE)
@@
   # Calculate proportions
-  DepMap_prop <- DepMap_melted_df %>% group_by(TCGA_classification, Gene) %>% summarise(Proportion = sum(Value) / n())
-  TCGA_prop <- TCGA_melted_df %>% group_by(TCGA_classification, Gene) %>% summarise(Proportion = sum(Value) / n())
+  DepMap_prop <- DepMap_melted_df %>% group_by(TCGA_classification, Gene) %>% summarise(Proportion = sum(Value) / n(), N = n())
+  TCGA_prop <- TCGA_melted_df %>% group_by(TCGA_classification, Gene) %>% summarise(Proportion = sum(Value) / n(), N = n())
   # Merge proportions from DepMap and TCGA
   props <- merge(DepMap_prop, TCGA_prop, by = c("TCGA_classification", "Gene"), all = TRUE, suffixes = c("_DepMap","_TCGA"))
+  props$N_summary <- with(props, paste0("N_DepMap = ", N_DepMap, ", N_TCGA = ", N_TCGA))
   # Plot faceted scatterplots
   props_scatters <- ggplot(data = props, aes(x = Proportion_TCGA, y = Proportion_DepMap)) +
-    facet_wrap(~ TCGA_classification, nrow = 4) +
+    facet_wrap(~ TCGA_classification * N_summary, nrow = 4) +
     geom_point(alpha = 0.3, color = "darkcyan") +
@@
     stat_cor(method = "pearson", label.x = 0.85, label.y = 0.15, label.sep = "\n") +
+    theme(strip.text.x = element_text(size = 12), axis.title = element_text(size = 14)) +
     labs(x = "TCGA frequency", y = "DepMap frequency", caption = paste0(formatC(x = length(unique(props$Gene)), format = "d", big.mark = ","), " genes compared."))
   # Save to file
-  ggsave(out_filepath, props_scatters, device = "png", dpi = 450, width = 12, height = 12, units = "in")
+  ggsave(out_filepath, props_scatters, device = "png", dpi = 450, width = 12, height = 13, units = "in")
   # Return for in-line rendering
@@
 # Make wide
-ge_depmap_wide <- DepMapTCGAMakeWideDF(df = ge_depmap_melt, output_type = "average", data_source = "DepMap")
+ge_depmap_wide <- DepMapTCGAMakeWideDF(melted_df = ge_depmap_melt, output_type = "average", data_source = "DepMap")
 
@@
 # Make wide
-ge_tcga_wide <- DepMapTCGAMakeWideDF(df = ge_tcga_melt, output_type = "average", data_source = "TCGA")
+ge_tcga_wide <- DepMapTCGAMakeWideDF(melted_df = ge_tcga_melt, output_type = "average", data_source = "TCGA")
 
 # Correlate all against all
-ge_corr_wide_pearson <- DepMapTCGACorrMatrix(DepMap_wide_df = ge_depmap_wide, TCGA_wide_df = ge_tcga_wide, corr_method = "pearson")
-ge_corr_wide_spearman <- DepMapTCGACorrMatrix(DepMap_wide_df = ge_depmap_wide, TCGA_wide_df = ge_tcga_wide, corr_method = "spearman")
+ge_corr_wide_pearson <- DepMapTCGACorrMatrix(DepMap_wide_df = ge_depmap_wide, TCGA_wide_df = ge_tcga_wide, corr_method = "pearson", data_format = "wide")
 ```
@@
 # draw(ge_ht_p, heatmap_legend_side = "top")
-
-ge_ht_s <- DepMapTCGACorrHeatmap(corr_wide_df = ge_corr_wide_spearman, out_filepath = "./figures/ge_depmap_tcga_heatmap_spearman.png", legend_title = "Expression Spearman correlation", color_breaks = c(-0.5, 0, 0.5, 1))
-# draw(ge_ht_s, heatmap_legend_side = "top")
 ```
@@
 # Make wide
-mut_depmap_wide <- DepMapTCGAMakeWideDF(df = mut_depmap_melt, output_type = "proportion", data_source = "DepMap", exclusions = c("TP53"))
+mut_depmap_wide <- DepMapTCGAMakeWideDF(melted_df = mut_depmap_melt, output_type = "proportion", data_source = "DepMap", exclusions = c("TP53"))
+mut_depmap_wide_wTP53 <- DepMapTCGAMakeWideDF(melted_df = mut_depmap_melt, output_type = "proportion", data_source = "DepMap")
 
@@
 # Make wide
-mut_tcga_wide <- DepMapTCGAMakeWideDF(df = mut_tcga_melt, output_type = "proportion", data_source = "TCGA", exclusions = c("TP53"))
+mut_tcga_wide <- DepMapTCGAMakeWideDF(melted_df = mut_tcga_melt, output_type = "proportion", data_source = "TCGA", exclusions = c("TP53"))
+mut_tcga_wide_wTP53 <- DepMapTCGAMakeWideDF(melted_df = mut_tcga_melt, output_type = "proportion", data_source = "TCGA")
 
 # Correlate all against all
-mut_corr_wide_pearson <- DepMapTCGACorrMatrix(DepMap_wide_df = mut_depmap_wide, TCGA_wide_df = mut_tcga_wide, corr_method = "pearson")
-mut_corr_wide_spearman <- DepMapTCGACorrMatrix(DepMap_wide_df = mut_depmap_wide, TCGA_wide_df = mut_tcga_wide, corr_method = "spearman")
+mut_corr_wide_pearson <- DepMapTCGACorrMatrix(DepMap_wide_df = mut_depmap_wide, TCGA_wide_df = mut_tcga_wide, corr_method = "pearson", data_format = "wide")
+# mut_corr_wide_pearson <- DepMapTCGACorrMatrix(DepMap_wide_df = mut_depmap_wide_wTP53, TCGA_wide_df = mut_tcga_wide_wTP53, corr_method = "pearson", data_format = "wide")
 ```
@@
 For plots labeled as "5000", the 5,000 most variable genes analyzed in the gene expression heatmap were selected for the mutation analyses.
-Alternatively, for the plots labeled as "252", the genes in the TCGA mutation dataset were analyzed if they were mutated in >=4% annotated samples and had a mutation in at least one cancer cell line from DepMap.
-TP53 was removed from the heatmap, as was done in Barretina et al.
+Alternatively, for the plots labeled as "252" or "253", the genes in the TCGA mutation dataset were analyzed if they were mutated in >=4% annotated samples and had a mutation in at least one cancer cell line from DepMap.
+TP53 was removed from the heatmap (n = 252), as was done in Barretina et al.
 (2012).
-For the scatterplots, TP53 was retained.
+For the scatterplots, TP53 was retained (n = 253).
 
@@
 ```{r mut_plots, eval=FALSE, fig.height=4, fig.width=3.75}
-mut_ht_p <- DepMapTCGACorrHeatmap(corr_wide_df = mut_corr_wide_pearson, out_filepath = "./figures/mut_depmap_tcga_heatmap_pearson_252.png", legend_title = "Mutation Pearson correlation", color_breaks = c(0, 0.3, 0.6, 0.9))
+mut_ht_p <- DepMapTCGACorrHeatmap(corr_wide_df = mut_corr_wide_pearson, out_filepath = "./figures/mut_depmap_tcga_heatmap_pearson_253.png", legend_title = "Mutation Pearson correlation (incl.
+TP53)", color_breaks = c(0.15, 0.35, 0.55, 0.85))
 # draw(mut_ht_p, heatmap_legend_side = "top")
 
-mut_ht_s <- DepMapTCGACorrHeatmap(corr_wide_df = mut_corr_wide_spearman, out_filepath = "./figures/mut_depmap_tcga_heatmap_spearman_252.png", legend_title = "Mutation Spearman correlation", color_breaks = c(0, 0.3, 0.5, 0.7))
-# draw(mut_ht_s, heatmap_legend_side = "top")
-
 mut_props_scatters <- DepMapTCGAPropsScatterplots(DepMap_melted_df = mut_depmap_melt, TCGA_melted_df = mut_tcga_melt, out_filepath = "./figures/mut_depmap_tcga_scatter_pearson_253.png")
@@
 
-### Continuous
+### Continuous (GISTIC2 TCGA)
 
 Continuous CN estimate data wrangling and processing:
-```{r cn_heatmap_data_continuous, eval=FALSE, warning=FALSE}
+```{r cn_heatmap_data_continuous_GISTIC2, eval=FALSE, warning=FALSE}
 # DepMap copy number
@@
 # Make wide
-cn_depmap_wide <- DepMapTCGAMakeWideDF(df = cn_depmap_melt, output_type = "average", data_source = "DepMap")
-
-# TCGA cop number
+cn_depmap_wide <- DepMapTCGAMakeWideDF(melted_df = cn_depmap_melt, output_type = "average", data_source = "DepMap")
+
+# TCGA copy number
+# GISTIC2 estimate
+# https://xenabrowser.net/datapages/?dataset=TCGA.PANCAN.sampleMap%2FGistic2_CopyNumber_Gistic2_all_data_by_genes&host=https%3A%2F%2Ftcga.xenahubs.net&removeHub=https%3A%2F%2Fxena.treehouse.gi.ucsc.edu%3A443
 cn_tcga <- read.delim("./../../htscreens_giant_files/omix/CN/CN_cont_Xena_filter.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
@@
 # Make wide
-cn_tcga_wide <- DepMapTCGAMakeWideDF(df = cn_tcga_melt, output_type = "proportion", data_source = "TCGA")
+cn_tcga_wide <- DepMapTCGAMakeWideDF(melted_df = cn_tcga_melt, output_type = "proportion", data_source = "TCGA")
 
 # Correlate all against all
-cn_corr_wide_pearson <- DepMapTCGACorrMatrix(DepMap_wide_df = cn_depmap_wide, TCGA_wide_df = cn_tcga_wide, corr_method = "pearson")
-cn_corr_wide_spearman <- DepMapTCGACorrMatrix(DepMap_wide_df = cn_depmap_wide, TCGA_wide_df = cn_tcga_wide, corr_method = "spearman")
+cn_corr_wide_pearson <- DepMapTCGACorrMatrix(DepMap_wide_df = cn_depmap_wide, TCGA_wide_df = cn_tcga_wide, corr_method = "pearson", data_format = "wide")
+```
+
+### Continuous (log(tumor/normal) TCGA)
+
+Continuous CN estimate data wrangling and processing:
+```{r cn_heatmap_data_continuous, eval=FALSE, warning=FALSE}
+# DepMap copy number
+cn_depmap <- read.delim("./../../htscreens_giant_files/omix/CN/CN_germ_del_DepMap_filter.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
+colnames(cn_depmap)[colnames(cn_depmap) == "cancer"] <- "TCGA_classification"
+# Mean center scale
+cn_depmap[, 4:ncol(cn_depmap)] <- apply(cn_depmap[, 4:ncol(cn_depmap)], MARGIN = 2, FUN = scale, center = TRUE, scale = TRUE)
+# Melt
+cn_depmap_melt <- melt(cn_depmap, id.vars = c("sample_ID", "TCGA_classification"), measure.vars = colnames(cn_depmap)[4:length(colnames(cn_depmap))], variable.name = "Gene", value.name = "CN_scaled")
+cn_depmap_melt <- filter(cn_depmap_melt, TCGA_classification %in% tcga_classifications_16)
+# Make wide
+cn_depmap_wide <- DepMapTCGAMakeWideDF(melted_df = cn_depmap_melt, output_type = "average", data_source = "DepMap")
+
+# TCGA copy number
+# log(tumor/normal) estimate
+# https://xenabrowser.net/datapages/?dataset=broad.mit.edu_PANCAN_Genome_Wide_SNP_6_whitelisted.gene.xena&host=https%3A%2F%2Fpancanatlas.xenahubs.net&removeHub=https%3A%2F%2Fxena.treehouse.gi.ucsc.edu%3A443
+cn_tcga <- read.delim("./../../htscreens_giant_files/omix/CN/CN_germ_del_Xena_filter.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
+colnames(cn_tcga)[colnames(cn_tcga) == "cancer"] <- "TCGA_classification"
+# Mean center scale
+cn_tcga[, 4:ncol(cn_tcga)] <- apply(cn_tcga[, 4:ncol(cn_tcga)], MARGIN = 2, FUN = scale, center = TRUE, scale = TRUE)
+# Melt
+cn_tcga_melt <- melt(cn_tcga, id.vars = c("sample_ID", "TCGA_classification"), measure.vars = colnames(cn_tcga)[4:length(colnames(cn_tcga))], variable.name = "Gene", value.name = "CN_scaled")
+cn_tcga_melt <- filter(cn_tcga_melt, TCGA_classification %in% tcga_classifications_16)
+# Make wide
+cn_tcga_wide <- DepMapTCGAMakeWideDF(melted_df = cn_tcga_melt, output_type = "proportion", data_source = "TCGA")
+
+# Correlate all against all
+cn_corr_wide_pearson <- DepMapTCGACorrMatrix(DepMap_wide_df = cn_depmap_wide, TCGA_wide_df = cn_tcga_wide, corr_method = "pearson", data_format = "wide")
 ```
@@
 # Make wide
-cn_depmap_wide <- DepMapTCGAMakeWideDF(df = cn_depmap_melt, output_type = "average", data_source = "DepMap")
+cn_depmap_wide <- DepMapTCGAMakeWideDF(melted_df = cn_depmap_melt, output_type = "average", data_source = "DepMap")
 
@@
 # Make wide
-cn_tcga_wide <- DepMapTCGAMakeWideDF(df = cn_tcga_melt, output_type = "proportion", data_source = "TCGA")
+cn_tcga_wide <- DepMapTCGAMakeWideDF(melted_df = cn_tcga_melt, output_type = "proportion", data_source = "TCGA")
 
 # Correlate all against all
-cn_corr_wide_pearson <- DepMapTCGACorrMatrix(DepMap_wide_df = cn_depmap_wide, TCGA_wide_df = cn_tcga_wide, corr_method = "pearson")
-cn_corr_wide_spearman <- DepMapTCGACorrMatrix(DepMap_wide_df = cn_depmap_wide, TCGA_wide_df = cn_tcga_wide, corr_method = "spearman")
+cn_corr_wide_pearson <- DepMapTCGACorrMatrix(DepMap_wide_df = cn_depmap_wide, TCGA_wide_df = cn_tcga_wide, corr_method = "pearson", data_format = "wide")
 ```
@@
 Make plots:
-```{r cn_plots, eval=TRUE, fig.height=4, fig.width=3.75}
-cn_ht_p <- DepMapTCGACorrHeatmap(corr_wide_df = cn_corr_wide_pearson, out_filepath = "./figures/cn_depmap_tcga_heatmap_pearson_thresholdedloss.png", legend_title = "Copy number Pearson correlation", color_breaks = c(0, 0.2, 0.4, 0.6))
+```{r cn_plots, eval=FALSE, fig.height=4, fig.width=3.75}
+cn_ht_p <- DepMapTCGACorrHeatmap(corr_wide_df = cn_corr_wide_pearson, out_filepath = "./figures/cn_depmap_tcga_heatmap_pearson_continuous.png", legend_title = "Copy number Pearson correlation", color_breaks = c(-0.5, 0, 0.5, 1.0))
 # draw(cn_ht_p, heatmap_legend_side = "top")
-
-cn_ht_s <- DepMapTCGACorrHeatmap(corr_wide_df = cn_corr_wide_spearman, out_filepath = "./figures/cn_depmap_tcga_heatmap_spearman_thresholdedloss.png", legend_title = "Copy number Spearman correlation", color_breaks = c(0, 0.2, 0.4, 0.6))
-# draw(cn_ht_s, heatmap_legend_side = "top")
 

### 2019-04-16 19Q1.Rmd
rm celline_stack old file and updated 19Q1

@@
 
+```{r functions}
+unfactorize <- function(df){
+  for(i in which(sapply(df, class) == "factor")) {
+    df[[i]] = as.character(df[[i]])
+  }
+  return(df)
+}
+```
+
 # DATA
@@
 ```{r}
-# ccl_converter <- read.delim("./data_munging/cell_line_database_v1_20180911.tsv", row.names = 1, sep = "\t", header = TRUE)
-# lineage_converter <- unique(ccl_converter[, c("grouped_general_doid", "group_general_lineage_name")])
+ccl_converter <- read.delim("./data_munging/cell_line_database_v1_20180911.tsv", row.names = 1, sep = "\t", header = TRUE)
+lineage_converter <- unique(ccl_converter[, c("Broad_ID", "grouped_general_doid", "group_general_lineage_name")])
 ```
@@
 ccl_meta$Primary.Disease <- as.factor(tolower(ccl_meta$Primary.Disease))
-# Harmonize ID column name and rename CCLE_Name column to fit with dataframe style
-colnames(ccl_meta)[colnames(ccl_meta) == "CCLE_Name"] <- "CCLE_ccl_name"
+# Harmonize ID column name
 colnames(ccl_meta)[colnames(ccl_meta) == "DepMap_ID"] <- "Broad_ID"
+
+# Remove two rows that contain cell lines with two different histologies
+# The histologies that are kept are verified through matching in Cellosaurus and Cell Model Passports
+# KMH2, haematopoietic_and_lymphoid: https://web.expasy.org/cellosaurus/CVCL_1330, https://cellmodelpassports.sanger.ac.uk/passports/SIDM01018
+# MS1, lung: https://web.expasy.org/cellosaurus/CVCL_1429, https://cellmodelpassports.sanger.ac.uk/passports/SIDM00245
+ccl_meta <- subset(ccl_meta, CCLE_Name != "KMH2_THYROID" & CCLE_Name != "MS1_SKIN")
 ```
@@
 
-# Order and genes taken from pink heatmapo from Daniel's analyses
-g2p_genes <- c("EGFR", "KRAS", "ERBB2", "ERBB3", "MET", "ALK", "ROS1", "PDGFRA", "ABL1", "KIT", "PDGFRB", "PDGFB", "BRAF", "G6PD", "RET", "BRCA1", "BRCA2", "UGT1A1", "TSC1", "TSC2", "AKT1", "IDH2", "DPYD", "ESR1", "CYP19A1", "TPMT", "FLT3", "NPM1", "DNMT3A", "PML", "PTCH1", "JAK2", "MYD88", "MGMT")
+# Order and genes taken from pink heatmap from Daniel's analyses
+# g2p_genes <- c("EGFR", "KRAS", "ERBB2", "ERBB3", "MET", "ALK", "ROS1", "PDGFRA", "ABL1", "KIT", "PDGFRB", "PDGFB", "BRAF", "G6PD", "RET", "BRCA1", "BRCA2", "UGT1A1", "TSC1", "TSC2", "AKT1", "IDH2", "DPYD", "ESR1", "CYP19A1", "TPMT", "FLT3", "NPM1", "DNMT3A", "PML", "PTCH1", "JAK2", "MYD88", "MGMT")
 ```
 
-```{r}
+```{r, eval=FALSE}
 # levels(g2p_filt$Phenotype.Description)
@@
 `r nrow(filter(test, n == 1))`/`r nrow(test)` gene-cell line combinations have more than one mutation in the MAF file. This is corrected in the point mutation filtering done below.
+
+**UPDATE WITH POZDEYEV AUC DATA**
+
+```{r}
+ccle <- read.delim("./../htscreens_giant_files/pozdeyev_data/CCLE_drug_response_metrics.csv.gz", sep = ",")
+ctrp <- read.delim("./../htscreens_giant_files/pozdeyev_data/CTRP_drug_response_metrics.csv.gz", sep = ",")
+gdsc <- read.delim("./../htscreens_giant_files/pozdeyev_data/GDSC_drug_response_metrics.csv.gz", sep = ",")
+```
 

### 2019-04-21 19Q1.Rmd
update omics and rds

@@
 }
+
+MergeOmicsG2P <- function(database, outfile) {
+  # Merge mutation status, CN, and GE omics data with drugscreen results and metadata
+  filt <- auc %>% filter(Database == database) %>% select(Cell_line, Histology, TCGA_classification, CCLE_Name, Broad_ID, Drug, AUC_IC50)
+  print(paste0("Filtered for ", database, "."))
+
+  # Get all G2Pgene-cell line combinations
+  grid <- expand.grid("Cell_line" = unique(filt$Cell_line), "Gene" = g2p_genes)
+  data <-  merge(filt, grid, by = "Cell_line", all.y = TRUE)
+  print("Merged grid.")
+
+  # Merge metadata
+  data <-  merge(data, select(ccl_meta, Cell_line, Histology, CCLE_Name, Broad_ID, Primary.Disease), by = c("Cell_line", "Histology", "CCLE_Name", "Broad_ID"), all.x = TRUE)
+  ## Add columns for G2P drug-gene and drug-gene-lineage sorting
+  data$Drug_Gene <- paste0(data$Drug, "_", data$Gene)
+  data$Drug_Gene_Lin <- paste0(data$Drug, "_", data$Gene, "_", data$Primary.Disease)
+  print("Merged metadata.")
+
+  # Merge mutation calls
+  data <- merge(data, maf_df_filt, by = c("Gene", "Broad_ID"), all.x = TRUE)
+  data$Mutation_Status <- ifelse(is.na(data$Mutation_Status), 0, data$Mutation_Status)
+  ## Identify point mutations
+  data$Keep_PtMut_Tests <- with(data, ifelse(Reference_Allele == 1 | is.na(Reference_Allele), TRUE, ifelse(Reference_Allele == 0 & Tumor_Seq_Allele1 == 1, TRUE, FALSE)))
+  ## Add color columns for plotting
+  if(database == "CCLE") {
+    data$Color <- ifelse(data$Mutation_Status == 0, "palegreen3", "springgreen4")
+    data$Color <- factor(data$Color)
+  }
+  if(database == "CTRP") {
+    data$Color <- ifelse(data$Mutation_Status == 0, "slategray3", "steelblue4")
+    data$Color <- factor(data$Color)
+  }
+  if(database == "GDSC") {
+    data$Color <- ifelse(data$Mutation_Status == 0, "paleturquoise3", "turquoise4")
+    data$Color <- factor(data$Color)
+  }
+  print("Merged mutation calls.")
+
+  # Merge GE data
+  data <- merge(data, ge_filt, by = c("Gene", "Broad_ID"), all.x = TRUE)
+  print("Merged gene expression data.")
+
+  # Merge CN data
+  data <- merge(data, cn_filt, by = c("Gene", "Broad_ID"), all.x = TRUE)
+  print("Merged copy number data.")
+
+  # Factorize gene
+  data$Gene <- factor(data$Gene)
+
+  # Save and return dataframe
+  saveRDS(data, outfile, compress = "xz")
+  return(data)
+}
+
+FilterForPointMuts <- function(dataframe, outfile) {
+  # Filter for point mutations
+  ptmuts <- filter(dataframe, Keep_PtMut_Tests == TRUE)
+  # Remove columns that lead to duplicate mutation entries
+  ptmuts <- subset(ptmuts, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, Keep_PtMut_Tests))
+  ptmuts$Gene <- ordered(ptmuts$Gene, levels = g2p_genes)
+  ptmuts <- unique(ptmuts)
+  saveRDS(ptmuts, outfile, compress = "xz")
+  return(ptmuts)
+}s
 ```
@@
 This comprehensive cancer cell line information was curated by both Daniel Charytonowicz and myself.
-
-**Might not need this anymore due to increased care taken by DepMap to harmonize disease names**
 ```{r}
@@
 lineage_converter <- unique(ccl_converter[, c("Broad_ID", "grouped_general_doid", "group_general_lineage_name")])
+ccl_histologies <- read.delim("./data_munging/ccl_histologies_metadata.csv", sep = ",", header = TRUE, row.names = 1)
 ```
@@
 ccl_meta$Primary.Disease <- tolower(ccl_meta$Primary.Disease)
+ccl_meta$Primary.Disease <- with(ccl_meta, ifelse(Primary.Disease == "colon/colorectal cancer", "colorectal cancer", Primary.Disease))
 ccl_meta <- subset(ccl_meta, Primary.Disease != "unknown" & Primary.Disease != "primary cells" & !grepl("MERGED", CCLE_Name, fixed = TRUE))
 ccl_meta$Cell_line <- as.character(lapply(ccl_meta$CCLE_Name, function(x) strsplit(as.character(x), split = "_")[[1]][1]))
-ccl_meta$histology <- tolower(gsub("^[a-z0-9]*_", "", ccl_meta$CCLE_Name, ignore.case = TRUE))
+ccl_meta$Histology <- tolower(gsub("^[a-z0-9]*_", "", ccl_meta$CCLE_Name, ignore.case = TRUE))
 # Convert Primary.Disease entries to all lower case to fix factorization issue
@@
 colnames(maf_raw)[colnames(maf_raw) == "DepMap_ID"] <- "Broad_ID"
+colnames(maf_raw)[colnames(maf_raw) == "Hugo_Symbol"] <- "Gene"
 # Select columns
-maf_df <- subset(maf_raw, select = c("Hugo_Symbol", "Broad_ID", "Variant_Classification", "Reference_Allele", "Tumor_Seq_Allele1", "Genome_Change"))
+maf_df <- subset(maf_raw, select = c("Gene", "Broad_ID", "Variant_Classification", "Reference_Allele", "Tumor_Seq_Allele1"))
 maf_df$Reference_Allele <- ifelse(maf_df$Reference_Allele == "-", 0, nchar(as.character(maf_df$Reference_Allele)))
@@
 cn <- read.delim("./data_munging/19Q1/public_19Q1_gene_cn_20190305.csv.gz", sep = ",", check.names = FALSE, header = TRUE)
-# Remove Entrez gene IDs from colnames, format is "Hugo_Symbol (Entrez ID)"
+# Remove Entrez gene IDs from colnames, format is "Gene (Entrez ID)"
 colnames(cn) <- gsub(" .*", "", colnames(cn))
@@
 # Melt
-cn_melt <- melt(data = cn, id.vars = "Broad_ID", measure.vars = colnames(cn[2:ncol(cn)]), variable.name = "Hugo_Symbol", value.name = "CN")
+cn_melt <- melt(data = cn, id.vars = "Broad_ID", measure.vars = colnames(cn[2:ncol(cn)]), variable.name = "Gene", value.name = "CN")
+
 saveRDS(cn_melt, "./data_munging/19Q1/cn_melt_19Q1.rds", compress = "xz")
@@
 ```{r, eval=FALSE}
-ge_19Q1 <- read.delim("./../htscreens_giant_files/CCLE_depMap_19Q1_TPM_20190305.csv.gz", header = TRUE, sep = ",", check.names = FALSE)
-# Remove Entrez gene IDs from colnames, format is "Hugo_Symbol (Entrez ID)"
-colnames(ge_19Q1) <- gsub(" .*", "", colnames(ge_19Q1))
-colnames(ge_19Q1)[1] <- "Broad_ID"
+ge <- read.delim("./../htscreens_giant_files/CCLE_depMap_19Q1_TPM_20190305.csv.gz", header = TRUE, sep = ",", check.names = FALSE)
+# Remove Entrez gene IDs from colnames, format is "Gene (Entrez ID)"
+colnames(ge) <- gsub(" .*", "", colnames(ge_19Q1))
+colnames(ge)[1] <- "Broad_ID"
+# Melt
+ge_melt <- melt(ge, id.vars = "Broad_ID", measure.vars = colnames(ge_19Q1)[2:ncol(ge_19Q1)], variable.name = "Gene", value.name = "TPM")
 
-# Melt
-ge_melt_19Q1 <- melt(ge_19Q1, id.vars = "Broad_ID", measure.vars = colnames(ge_19Q1)[2:ncol(ge_19Q1)], variable.name = "Hugo_Symbol", value.name = "TPM")
-# ge_melt_19Q1 <- unique(ge_melt_19Q1_all)
-saveRDS(ge_melt_19Q1, "./data_munging/19Q1/ge_melt_19Q1.rds", compress = "xz")
+saveRDS(ge_melt, "./data_munging/19Q1/ge_melt_19Q1.rds", compress = "xz")
 ```
@@
 
-### Merge drug data and annotations
+### Merge omics
 
 ```{r}
-test <- filter(maf_df, Hugo_Symbol %in% g2p_genes) %>% count(Hugo_Symbol, CCLE_Name)
+test <- filter(maf_df, Gene %in% g2p_genes) %>% count(Gene, Broad_ID)
 test <- test[order(test$n, decreasing = TRUE),]
@@
 
-`r nrow(filter(test, n == 1))`/`r nrow(test)` gene-cell line combinations have more than one mutation in the MAF file. This is corrected in the point mutation filtering done below.
+`r nrow(filter(test, n != 1))`/`r nrow(test)` gene-cell line combinations have more than one mutation in the MAF file. This is corrected in the point mutation filtering done below.
+```{r, eval=FALSE}
+# Load in Pozdeyev et al. (2016) data
+ccle_all <- read.delim("./../htscreens_giant_files/pozdeyev_data/CCLE_drug_response_metrics.csv.gz", sep = ",")
+ctrp_all <- read.delim("./../htscreens_giant_files/pozdeyev_data/CTRP_drug_response_metrics.csv.gz", sep = ",")
+gdsc_all <- read.delim("./../htscreens_giant_files/pozdeyev_data/GDSC_drug_response_metrics.csv.gz", sep = ",")
 
-**UPDATE WITH POZDEYEV AUC DATA**
+auc <- bind_rows(ccle_all, ctrp_all, gdsc_all)
+
+# Harmonize Pozdeyev cell line names with DepMap
+auc$Drug <- tolower(auc$Drug_name)
+auc$Cell_line <- toupper(gsub("-", "", auc$Cell_line))
+auc$Cell_line <- ifelse(auc$Cell_line == "K052", "KO52", auc$Cell_line)
+auc$Cell_line <- ifelse(auc$Cell_line == "OVCAR3", "NIHOVCAR3", auc$Cell_line)
+auc$Cell_line <- ifelse(auc$Cell_line == "OVCAR3", "NIHOVCAR3", auc$Cell_line)
+auc$Cell_line <- ifelse(auc$Cell_line == "TI73", "T173", auc$Cell_line)
+auc <- merge(ccl_histologies, auc, by = "Cell_line", all.y = TRUE)
+
+# Omics metadata
+maf_df_filt <- filter(maf_df, Gene %in% g2p_genes)
+ge_filt <- filter(ge_melt, Gene %in% g2p_genes)
+cn_filt <- filter(cn_melt, Gene %in% g2p_genes)
+
+ccle <- MergeOmicsG2P(database = "CCLE", outfile = "./data_munging/rds/ccle_data_19Q1_g2pgenes.rds")
+ctrp <- MergeOmicsG2P(database = "CTRP", outfile = "./data_munging/rds/ctrp_data_19Q1_g2pgenes.rds")
+gdsc <- MergeOmicsG2P(database = "GDSC", outfile = "./data_munging/rds/gdsc_data_19Q1_g2pgenes.rds")
+
+ccle_ptmuts <- FilterForPointMuts(dataframe = ccle, outfile = "./data_munging/rds/ccle_data_19Q1_g2pgenes_ptmuts.rds")
+ctrp_ptmuts <- FilterForPointMuts(dataframe = ctrp, outfile = "./data_munging/rds/ctrp_data_19Q1_g2pgenes_ptmuts.rds")
+gdsc_ptmuts <- FilterForPointMuts(dataframe = gdsc, outfile = "./data_munging/rds/gdsc_data_19Q1_g2pgenes_ptmuts.rds")
+```
+
+### Summaries
 
 ```{r}
-ccle <- read.delim("./../htscreens_giant_files/pozdeyev_data/CCLE_drug_response_metrics.csv.gz", sep = ",")
-ctrp <- read.delim("./../htscreens_giant_files/pozdeyev_data/CTRP_drug_response_metrics.csv.gz", sep = ",")
-gdsc <- read.delim("./../htscreens_giant_files/pozdeyev_data/GDSC_drug_response_metrics.csv.gz", sep = ",")
-```
-
-```{r, eval=FALSE}
-# Drug metadata
-drug_meta <- read.delim("./data_munging/drug_id_drug_name_table_10_12_2018.tsv", sep = "\t", header = FALSE)
-colnames(drug_meta) <- c("CID", "Drug")
-drug_meta$Drug <- tolower(drug_meta$Drug)
-maf_df_g2p <- filter(maf_df, Hugo_Symbol %in% g2p_genes)
-ge_filt <- filter(ge_melt, Hugo_Symbol %in% g2p_genes)
-cn_filt <- filter(cn_melt, Hugo_Symbol %in% g2p_genes)
-
-# CCLE
-ccle <- read.delim("./data_munging/data_drug_auc_ccle_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
-ccle <- merge(drug_meta, ccle, by = "CID")
-ccle_melt <- melt(ccle, id.vars = c("CID", "Drug"), measure.vars = colnames(ccle)[3:ncol(ccle)], variable.name = "accession_id", value.name = "ActArea")
-ccle_grid <- expand.grid("accession_id" = unique(ccle_melt$accession_id), "Hugo_Symbol" = g2p_genes)
-ccle_data <- merge(ccle_grid, ccle_melt, by = "accession_id", all.x = TRUE)
-ccle_data <- merge(ccle_data, ccl_converter, by = "accession_id", all.x = TRUE)
-ccle_data <- merge(ccle_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
-ccle_data$Mutation_Status_Nonsilent <- ifelse(is.na(ccle_data$Mutation_Status_Nonsilent), "Wildtype", ccle_data$Mutation_Status_Nonsilent)
-ccle_data <- merge(ccle_data, ge_filt_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
-# ccle_data <- merge(ccle_data, ge_filt_19Q1, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
-ccle_data <- merge(ccle_data, cn_filt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
-ccle_data$Hugo_Symbol <- factor(ccle_data$Hugo_Symbol)
-ccle_data$ActArea <- as.numeric(ccle_data$ActArea)
-# CCLE AUC is actually AOC
-# assuming scale is 0-8, transform to range between 0 and 1
-# get AUC by 1 - AOC
-ccle_data$AUC <- 1 - (ccle_data$ActArea / 8)
-ccle_data <- filter(ccle_data, !is.na(ccle_data$AUC))
-ccle_data$AUC_zscore <- (ccle_data$AUC - mean(ccle_data$AUC)) / sd(ccle_data$AUC)
-ccle_data$Color_Nonsilent <- ifelse(ccle_data$Mutation_Status_Nonsilent == "Wildtype", "palegreen3", "springgreen4")
-ccle_data$Color_Nonsilent <- factor(ccle_data$Color_Nonsilent)
-ccle_data$Drug_Gene <- paste0(ccle_data$Drug, "_", ccle_data$Hugo_Symbol)
-ccle_data$Drug_Gene_Lin <- paste0(ccle_data$Drug, "_", ccle_data$Hugo_Symbol, "_", ccle_data$group_general_lineage_name)
-saveRDS(ccle_data, "./data_munging/rds/ccle_data_19Q1_g2pgenes.rds", compress = "xz")
-
-# CTRP
-ctrp <- read.delim("./data_munging/data_drug_auc_ctrp_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
-ctrp <- merge(drug_meta, ctrp, by = "CID")
-ctrp_melt <- melt(ctrp, id.vars = c("CID", "Drug"), measure.vars = colnames(ctrp)[3:ncol(ctrp)], variable.name = "accession_id", value.name = "AUC")
-ctrp_grid <- expand.grid("accession_id" = unique(ctrp_melt$accession_id), "Hugo_Symbol" = g2p_genes)
-ctrp_data <- merge(ctrp_grid, ctrp_melt, by = "accession_id", all.x = TRUE)
-ctrp_data <- merge(ctrp_data, ccl_converter, by = "accession_id", all.x = TRUE)
-ctrp_data <- merge(ctrp_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
-ctrp_data$Mutation_Status_Nonsilent <- ifelse(is.na(ctrp_data$Mutation_Status_Nonsilent), "Wildtype", ctrp_data$Mutation_Status_Nonsilent)
-ctrp_data <- merge(ctrp_data, ge_filt_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
-# ctrp_data <- merge(ctrp_data, ge_filt_19Q1, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
-ctrp_data <- merge(ctrp_data, cn_filt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
-ctrp_data$Hugo_Symbol <- factor(ctrp_data$Hugo_Symbol)
-ctrp_data$AUC <- as.numeric(ctrp_data$AUC)
-ctrp_data <- filter(ctrp_data, !is.na(ctrp_data$AUC))
-ctrp_data$AUC_zscore <- (ctrp_data$AUC - mean(ctrp_data$AUC)) / sd(ctrp_data$AUC)
-ctrp_data$Color_Nonsilent <- ifelse(ctrp_data$Mutation_Status_Nonsilent == "Wildtype", "slategray3", "steelblue4")
-ctrp_data$Color_Nonsilent <- factor(ctrp_data$Color_Nonsilent)
-ctrp_data$Drug_Gene <- paste0(ctrp_data$Drug, "_", ctrp_data$Hugo_Symbol)
-ctrp_data$Drug_Gene_Lin <- paste0(ctrp_data$Drug, "_", ctrp_data$Hugo_Symbol, "_", ctrp_data$group_general_lineage_name)
-saveRDS(ctrp_data, "./data_munging/rds/ctrp_data_19Q1_g2pgenes.rds", compress = "xz")
-
-# GDSC
-gdsc <- read.delim("./data_munging/data_drug_auc_gdsc_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
-gdsc <- merge(drug_meta, gdsc, by = "CID")
-gdsc_melt <- melt(gdsc, id.vars = c("CID", "Drug"), measure.vars = colnames(gdsc)[3:ncol(gdsc)], variable.name = "accession_id", value.name = "AUC")
-gdsc_grid <- expand.grid("accession_id" = unique(gdsc_melt$accession_id), "Hugo_Symbol" = g2p_genes)
-gdsc_data <- merge(gdsc_grid, gdsc_melt, by = "accession_id", all.x = TRUE)
-gdsc_data <- merge(gdsc_data, ccl_converter, by = "accession_id", all.x = TRUE)
-gdsc_data <- merge(gdsc_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
-gdsc_data$Mutation_Status_Nonsilent <- ifelse(is.na(gdsc_data$Mutation_Status_Nonsilent), "Wildtype", gdsc_data$Mutation_Status_Nonsilent)
-gdsc_data <- merge(gdsc_data, ge_filt_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
-# gdsc_data <- merge(gdsc_data, ge_filt_19Q1, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
-gdsc_data <- merge(gdsc_data, cn_filt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
-gdsc_data$Hugo_Symbol <- factor(gdsc_data$Hugo_Symbol)
-gdsc_data$AUC <- as.numeric(gdsc_data$AUC)
-gdsc_data <- filter(gdsc_data, !is.na(gdsc_data$AUC))
-gdsc_data$AUC_zscore <- (gdsc_data$AUC - mean(gdsc_data$AUC)) / sd(gdsc_data$AUC)
-gdsc_data$Color_Nonsilent <- ifelse(gdsc_data$Mutation_Status_Nonsilent == "Wildtype", "paleturquoise3", "turquoise4")
-gdsc_data$Color_Nonsilent <- factor(gdsc_data$Color_Nonsilent)
-gdsc_data$Drug_Gene <- paste0(gdsc_data$Drug, "_", gdsc_data$Hugo_Symbol)
-gdsc_data$Drug_Gene_Lin <- paste0(gdsc_data$Drug, "_", gdsc_data$Hugo_Symbol, "_", gdsc_data$group_general_lineage_name)
-saveRDS(gdsc_data, "./data_munging/rds/gdsc_data_19Q1_g2pgenes.rds", compress = "xz")
-```
-
-### Filter drug data
-
-```{r, eval=FALSE}
-ccle_data <- readRDS("./data_munging/rds/ccle_data_19Q1_g2pgenes.rds")
-ccle_data_ptmuts <- filter(ccle_data, Reference_Allele == 1 | Reference_Allele == 0 | is.na(Reference_Allele))
-ccle_data_ptmuts$Keep_PtMut_Tests <- ifelse(ccle_data_ptmuts$Reference_Allele == 1 | is.na(ccle_data_ptmuts$Reference_Allele), TRUE, ifelse(ccle_data_ptmuts$Tumor_Seq_Allele1 == 1, TRUE, FALSE))
-ccle_data_ptmuts <- filter(ccle_data_ptmuts, Keep_PtMut_Tests == TRUE)
-# Remove columns that lead to duplicate mutation entries
-ccle_data_ptmuts <- subset(ccle_data_ptmuts, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, Genome_Change, Keep_PtMut_Tests))
-ccle_data_ptmuts$Dataset <- "CCLE"
-ccle_data_ptmuts$Hugo_Symbol <- ordered(ccle_data_ptmuts$Hugo_Symbol, levels = g2p_genes)
-ccle_data_ptmuts <- unique(ccle_data_ptmuts)
-saveRDS(ccle_data_ptmuts, "./data_munging/rds/ccle_data_19Q1_g2pgenes_ptmuts.rds", compress = "xz")
-
-ctrp_data <- readRDS("./data_munging/rds/ctrp_data_19Q1_g2pgenes.rds")
-ctrp_data_ptmuts <- filter(ctrp_data, Reference_Allele == 1 | Reference_Allele == 0 | is.na(Reference_Allele))
-ctrp_data_ptmuts$Keep_PtMut_Tests <- ifelse(ctrp_data_ptmuts$Reference_Allele == 1 | is.na(ctrp_data_ptmuts$Reference_Allele), TRUE, ifelse(ctrp_data_ptmuts$Tumor_Seq_Allele1 == 1, TRUE, FALSE))
-ctrp_data_ptmuts <- filter(ctrp_data_ptmuts, Keep_PtMut_Tests == TRUE)
-# Remove columns that lead to duplicate mutation entries
-ctrp_data_ptmuts <- subset(ctrp_data_ptmuts, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, Genome_Change, Keep_PtMut_Tests))
-ctrp_data_ptmuts$Dataset <- "CTRP"
-ctrp_data_ptmuts$Hugo_Symbol <- ordered(ctrp_data_ptmuts$Hugo_Symbol, levels = g2p_genes)
-ctrp_data_ptmuts <- unique(ctrp_data_ptmuts)
-saveRDS(ctrp_data_ptmuts, "./data_munging/rds/ctrp_data_19Q1_g2pgenes_ptmuts.rds", compress = "xz")
-
-gdsc_data <- readRDS("./data_munging/rds/gdsc_data_19Q1_g2pgenes.rds")
-gdsc_data_ptmuts <- filter(gdsc_data, Reference_Allele == 1 | Reference_Allele == 0 | is.na(Reference_Allele))
-gdsc_data_ptmuts$Keep_PtMut_Tests <- ifelse(gdsc_data_ptmuts$Reference_Allele == 1 | is.na(gdsc_data_ptmuts$Reference_Allele), TRUE, ifelse(gdsc_data_ptmuts$Tumor_Seq_Allele1 == 1, TRUE, FALSE))
-gdsc_data_ptmuts <- filter(gdsc_data_ptmuts, Keep_PtMut_Tests == TRUE)
-# Remove columns that lead to duplicate mutation entries
-gdsc_data_ptmuts <- subset(gdsc_data_ptmuts, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, Genome_Change, Keep_PtMut_Tests))
-gdsc_data_ptmuts$Dataset <- "GDSC"
-gdsc_data_ptmuts$Hugo_Symbol <- ordered(gdsc_data_ptmuts$Hugo_Symbol, levels = g2p_genes)
-gdsc_data_ptmuts <- unique(gdsc_data_ptmuts)
-saveRDS(gdsc_data_ptmuts, "./data_munging/rds/gdsc_data_19Q1_g2pgenes_ptmuts.rds", compress = "xz")
-```
-
-```{r}
-ccle_data <- readRDS("./data_munging/rds/ccle_data_19Q1_g2pgenes.rds")
-ctrp_data <- readRDS("./data_munging/rds/ctrp_data_19Q1_g2pgenes.rds")
-gdsc_data <- readRDS("./data_munging/rds/gdsc_data_19Q1_g2pgenes.rds")
-ccle_data_ptmuts <- readRDS("./data_munging/rds/ccle_data_19Q1_g2pgenes_ptmuts.rds")
-ctrp_data_ptmuts <- readRDS("./data_munging/rds/ctrp_data_19Q1_g2pgenes_ptmuts.rds")
-gdsc_data_ptmuts <- readRDS("./data_munging/rds/gdsc_data_19Q1_g2pgenes_ptmuts.rds")
-
-# Filter drug screen datasets for G2P drug-gene associations
-ccle_data_g2p <- filter(ccle_data_ptmuts, Drug_Gene %in% g2p_druggenes)
-ccle_data_g2p$Mutation_Status_Nonsilent <- factor(ccle_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-ctrp_data_g2p <- filter(ctrp_data_ptmuts, Drug_Gene %in% g2p_druggenes)
-ctrp_data_g2p$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-gdsc_data_g2p <- filter(gdsc_data_ptmuts, Drug_Gene %in% g2p_druggenes)
-gdsc_data_g2p$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-
-# Filter drug screen datasets for G2P drug-gene-lineage associations
-ccle_data_g2p_dgl <- filter(ccle_data_ptmuts, Drug_Gene_Lin %in% g2p_dgls)
-ccle_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(ccle_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-ctrp_data_g2p_dgl <- filter(ctrp_data_ptmuts, Drug_Gene_Lin %in% g2p_dgls)
-ctrp_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-gdsc_data_g2p_dgl <- filter(gdsc_data_ptmuts, Drug_Gene_Lin %in% g2p_dgls)
-gdsc_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-
-# Filter drug screen datasets for G2P drugs and genes
-ccle_data_g2p_grid <- filter(ccle_data_ptmuts, Drug %in% g2p_drugs)
-ccle_data_g2p_grid$Mutation_Status_Nonsilent <- factor(ccle_data_g2p_grid$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-ctrp_data_g2p_grid <- filter(ctrp_data_ptmuts, Drug %in% g2p_drugs)
-ctrp_data_g2p_grid$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p_grid$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-gdsc_data_g2p_grid <- filter(gdsc_data_ptmuts, Drug %in% g2p_drugs)
-gdsc_data_g2p_grid$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p_grid$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
+ccle <- readRDS("./data_munging/rds/ccle_data_19Q1_g2pgenes.rds")
+ctrp <- readRDS("./data_munging/rds/ctrp_data_19Q1_g2pgenes.rds")
+gdsc <- readRDS("./data_munging/rds/gdsc_data_19Q1_g2pgenes.rds")
+ccle_ptmuts <- readRDS("./data_munging/rds/ccle_data_19Q1_g2pgenes_ptmuts.rds")
+ctrp_ptmuts <- readRDS("./data_munging/rds/ctrp_data_19Q1_g2pgenes_ptmuts.rds")
+gdsc_ptmuts <- readRDS("./data_munging/rds/gdsc_data_19Q1_g2pgenes_ptmuts.rds")
 
 # Testing
-test_ccle <- ccle_data_ptmuts %>% group_by(Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()
-test_ctrp <- ctrp_data_ptmuts %>% group_by(Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()
-test_gdsc <- gdsc_data_ptmuts %>% group_by(Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()
-
-# drug_summ <- data.frame(Drug = g2p_drugs, Dataset_Count = 0)
+test_ccle <- ccle_ptmuts %>% group_by(Gene, Mutation_Status_Nonsilent) %>% tally()
+test_ctrp <- ctrp_ptmuts %>% group_by(Gene, Mutation_Status_Nonsilent) %>% tally()
+test_gdsc <- gdsc_ptmuts %>% group_by(Gene, Mutation_Status_Nonsilent) %>% tally()
 ```
@@
 How many datasets screen each G2P drug?
-```{r}
+```{r, eval=FALSE}
 drug_summ <- data.frame(Drug = character(), Dataset_Count = integer(), stringsAsFactors = FALSE)
@@
 # Melt CRISPR dataset for merging
-crispr_melt <- melt(crispr, id.vars = "DepMap_ID", measure.vars = colnames(crispr)[2:ncol(crispr)], variable.name = "Hugo_Symbol", value.name = "Score")
+crispr_melt <- melt(crispr, id.vars = "DepMap_ID", measure.vars = colnames(crispr)[2:ncol(crispr)], variable.name = "Gene", value.name = "Score")
 # Merge cell line metadata
@@
 # Merge mutation annotations
-maf_filt_crispr <- filter(maf_df, Hugo_Symbol %in% as.character(unique(crispr_melt$Hugo_Symbol)))
-crispr_muts <- merge(crispr_melt, maf_filt_crispr, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
-crispr_muts$Hugo_Symbol <- factor(crispr_muts$Hugo_Symbol)
+maf_filt_crispr <- filter(maf_df, Gene %in% as.character(unique(crispr_melt$Gene)))
+crispr_muts <- merge(crispr_melt, maf_filt_crispr, by = c("Gene", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
+crispr_muts$Gene <- factor(crispr_muts$Gene)
 crispr_muts <- crispr_muts %>% mutate(Mutation_Status_Nonsilent = if_else(is.na(Mutation_Status_Nonsilent), "Wildtype", Mutation_Status_Nonsilent))
 # Summarize number of mutant and Wildtype cell lines
-crispr_muts_summ <- crispr_muts %>% group_by(Hugo_Symbol) %>%
+crispr_muts_summ <- crispr_muts %>% group_by(Gene) %>%
   summarize(N_Nonsilent_Wildtype = sum(Mutation_Status_Nonsilent == "Wildtype"),
@@
 # Merge test results back into full dataset, which restores information lost in the summarization
-crispr_data <- merge(crispr_muts_summ, crispr_muts, by = "Hugo_Symbol")
+crispr_data <- merge(crispr_muts_summ, crispr_muts, by = "Gene")
 # Add Color columns
@@
 # Copy number
-crispr_data <- merge(crispr_data, cn_melt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
+crispr_data <- merge(crispr_data, cn_melt, by = c("Gene", "DepMap_ID"), all.x = TRUE)
 # Gene expression (RPKM)
-ge_crispr_18Q3 <- filter(ge_melt_18Q3, Hugo_Symbol %in% as.character(unique(crispr_melt$Hugo_Symbol)))
-# ge_crispr_19Q1 <- filter(ge_melt_19Q1, Hugo_Symbol %in% as.character(unique(crispr_melt$Hugo_Symbol)))
-crispr_data <- merge(crispr_data, ge_crispr_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
-# crispr_data <- merge(crispr_data, ge_crispr_19Q1, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
+ge_crispr_18Q3 <- filter(ge_melt_18Q3, Gene %in% as.character(unique(crispr_melt$Gene)))
+# ge_crispr_19Q1 <- filter(ge_melt_19Q1, Gene %in% as.character(unique(crispr_melt$Gene)))
+crispr_data <- merge(crispr_data, ge_crispr_18Q3, by = c("Gene", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
+# crispr_data <- merge(crispr_data, ge_crispr_19Q1, by = c("Gene", "DepMap_ID"), all.x = TRUE)
 saveRDS(crispr_data, "./../htscreens_giant_files/crispr_data_19Q1.rds", compress = "xz")
@@
 
-```{r}
+```{r, eval=FALSE}
 crispr_data <- readRDS("./../htscreens_giant_files/crispr_data_19Q1.rds")
@@
 # crispr_data_ptmuts <- readRDS("./../htscreens_giant_files/crispr_data_19Q1_ptmuts.rds")
-# crispr_data_g2p <- filter(crispr_data_ptmuts, Hugo_Symbol %in% g2p_genes)
+# crispr_data_g2p <- filter(crispr_data_ptmuts, Gene %in% g2p_genes)
 
 # Filter CRISPR for G2P genes in G2P
-crispr_data_ptmuts <- filter(crispr_data, Hugo_Symbol %in% g2p_genes)
+crispr_data_ptmuts <- filter(crispr_data, Gene %in% g2p_genes)
 # Filter G2P CRISPR for point mutations
@@
 crispr_data_g2p <- unique(crispr_data_ptmuts)
-crispr_data_g2p$Hugo_Symbol <- factor(crispr_data_g2p$Hugo_Symbol, levels = g2p_genes)
+crispr_data_g2p$Gene <- factor(crispr_data_g2p$Gene, levels = g2p_genes)
 crispr_data_g2p$Mutation_Status_Nonsilent <- factor(crispr_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))

### 2019-04-22 19Q1.Rmd

@@
   ## Identify point mutations
-  data$Keep_PtMut_Tests <- with(data, ifelse(Reference_Allele == 1 | is.na(Reference_Allele), TRUE, ifelse(Reference_Allele == 0 & Tumor_Seq_Allele1 == 1, TRUE, FALSE)))
+  data$PointMutation <- ifelse(is.na(data$PointMutation), 0, data$PointMutation)
   ## Add color columns for plotting
@@
   # Filter for point mutations
-  ptmuts <- filter(dataframe, Keep_PtMut_Tests == TRUE)
+  ptmuts <- filter(dataframe, PointMutation == 1)
   # Remove columns that lead to duplicate mutation entries
-  ptmuts <- subset(ptmuts, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, Keep_PtMut_Tests))
+  ptmuts <- subset(ptmuts, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, PointMutation))
   ptmuts$Gene <- ordered(ptmuts$Gene, levels = g2p_genes)
@@
   return(ptmuts)
-}s
+}
 ```
@@
 maf_df$Mutation_Status <- 1
+maf_df$PointMutation <- with(maf_df, ifelse(Reference_Allele == 1 | is.na(Reference_Allele), TRUE, ifelse(Reference_Allele == 0 & Tumor_Seq_Allele1 == 1, 1, 0)))
 
@@
 
-ccle <- MergeOmicsG2P(database = "CCLE", outfile = "./data_munging/rds/ccle_data_19Q1_g2pgenes.rds")
-ctrp <- MergeOmicsG2P(database = "CTRP", outfile = "./data_munging/rds/ctrp_data_19Q1_g2pgenes.rds")
-gdsc <- MergeOmicsG2P(database = "GDSC", outfile = "./data_munging/rds/gdsc_data_19Q1_g2pgenes.rds")
+# ccle <- MergeOmicsG2P(database = "CCLE", outfile = "./data_munging/rds/ccle_data_19Q1_g2pgenes.rds")
+# ctrp <- MergeOmicsG2P(database = "CTRP", outfile = "./data_munging/rds/ctrp_data_19Q1_g2pgenes.rds")
+# gdsc <- MergeOmicsG2P(database = "GDSC", outfile = "./data_munging/rds/gdsc_data_19Q1_g2pgenes.rds")
 
-ccle_ptmuts <- FilterForPointMuts(dataframe = ccle, outfile = "./data_munging/rds/ccle_data_19Q1_g2pgenes_ptmuts.rds")
-ctrp_ptmuts <- FilterForPointMuts(dataframe = ctrp, outfile = "./data_munging/rds/ctrp_data_19Q1_g2pgenes_ptmuts.rds")
+# ccle_ptmuts <- FilterForPointMuts(dataframe = ccle, outfile = "./data_munging/rds/ccle_data_19Q1_g2pgenes_ptmuts.rds")
+# ctrp_ptmuts <- FilterForPointMuts(dataframe = ctrp, outfile = "./data_munging/rds/ctrp_data_19Q1_g2pgenes_ptmuts.rds")
 gdsc_ptmuts <- FilterForPointMuts(dataframe = gdsc, outfile = "./data_munging/rds/gdsc_data_19Q1_g2pgenes_ptmuts.rds")
@@
 
-```{r}
+```{r, eval=FALSE}
 ccle <- readRDS("./data_munging/rds/ccle_data_19Q1_g2pgenes.rds")
-ctrp <- readRDS("./data_munging/rds/ctrp_data_19Q1_g2pgenes.rds")
+ctrp <- readRDS("./../htscreens_giant_files/ctrp_data_19Q1_g2pgenes.rds")
 gdsc <- readRDS("./data_munging/rds/gdsc_data_19Q1_g2pgenes.rds")
 ccle_ptmuts <- readRDS("./data_munging/rds/ccle_data_19Q1_g2pgenes_ptmuts.rds")
-ctrp_ptmuts <- readRDS("./data_munging/rds/ctrp_data_19Q1_g2pgenes_ptmuts.rds")
+ctrp_ptmuts <- readRDS("./../htscreens_giant_files/ctrp_data_19Q1_g2pgenes_ptmuts.rds")
 gdsc_ptmuts <- readRDS("./data_munging/rds/gdsc_data_19Q1_g2pgenes_ptmuts.rds")
@@
 ```{r, eval=FALSE}
-crispr <- read.delim("./data_munging/19Q1/gene_effect_19Q1_20181115.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
+crispr <- read.delim("./data_munging/19Q1/gene_effect_corrected_20190305.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
 # Remove Entrez gene IDs from colnames
 colnames(crispr) <- gsub(" .*", "", colnames(crispr))
-```
-
-Merge annotation data:
-```{r, eval=FALSE}
+colnames(crispr)[1] <- "Broad_ID"
 # Melt CRISPR dataset for merging
-crispr_melt <- melt(crispr, id.vars = "DepMap_ID", measure.vars = colnames(crispr)[2:ncol(crispr)], variable.name = "Gene", value.name = "Score")
+crispr_melt <- melt(crispr, id.vars = "Broad_ID", measure.vars = colnames(crispr)[2:ncol(crispr)], variable.name = "Gene", value.name = "Score")
 # Merge cell line metadata
-crispr_melt <- merge(crispr_melt, ccl_meta, by = "DepMap_ID", all.x = TRUE)
-crispr_melt <- merge(crispr_melt, crispr_meta, by = c("CCLE_Name", "DepMap_ID"), all.x = TRUE)
-
+crispr_melt <- merge(crispr_melt, ccl_meta, by = "Broad_ID", all.x = TRUE)
 # Merge mutation annotations
 maf_filt_crispr <- filter(maf_df, Gene %in% as.character(unique(crispr_melt$Gene)))
-crispr_muts <- merge(crispr_melt, maf_filt_crispr, by = c("Gene", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
+maf_filt_crispr <- subset(maf_filt_crispr, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1))
+maf_filt_crispr <- unique(maf_filt_crispr)
+crispr_muts <- merge(crispr_melt, maf_filt_crispr, by = c("Gene","Broad_ID"), all.x = TRUE)
 crispr_muts$Gene <- factor(crispr_muts$Gene)
-crispr_muts <- crispr_muts %>% mutate(Mutation_Status_Nonsilent = if_else(is.na(Mutation_Status_Nonsilent), "Wildtype", Mutation_Status_Nonsilent))
+crispr_muts$Mutation_Status <- ifelse(is.na(crispr_muts$Mutation_Status), 0, crispr_muts$Mutation_Status)
+## Identify point mutations and wildtypes for testing
+crispr_muts$PointMutation <- ifelse(is.na(crispr_muts$PointMutation), 1, crispr_muts$PointMutation)
 # Summarize number of mutant and Wildtype cell lines
 crispr_muts_summ <- crispr_muts %>% group_by(Gene) %>%
-  summarize(N_Nonsilent_Wildtype = sum(Mutation_Status_Nonsilent == "Wildtype"),
-            N_Nonsilent_Mutant = sum(Mutation_Status_Nonsilent == "Mutant"))
+  summarize(N_Wildtype = length(Mutation_Status) - sum(Mutation_Status == 1),
+            N_Mutant = sum(Mutation_Status == 1))
 # Merge test results back into full dataset, which restores information lost in the summarization
@@
 # Add Color columns
-crispr_data$Color_Nonsilent <- ifelse(crispr_data$Mutation_Status_Nonsilent == "Wildtype", "thistle", "darkorchid")
-crispr_data$Color_Nonsilent <- factor(crispr_data$Color_Nonsilent)
+crispr_data$Color <- ifelse(crispr_data$Mutation_Status == 0, "thistle", "darkorchid")
+crispr_data$Color <- factor(crispr_data$Color)
 
 # Cell line lineages
-crispr_data <- merge(crispr_data, ccl_converter, by = c("CCLE_Name", "DepMap_ID"), all.x = TRUE)
-levels(crispr_data$lineage_name) <- sort(levels(crispr_data$lineage_name), decreasing = TRUE)
+# crispr_data <- merge(crispr_data, ccl_converter, by = c("CCLE_Name", "Broad_ID"), all.x = TRUE)
+# levels(crispr_data$lineage_name) <- sort(levels(crispr_data$lineage_name), decreasing = TRUE)
 # Copy number
-crispr_data <- merge(crispr_data, cn_melt, by = c("Gene", "DepMap_ID"), all.x = TRUE)
+crispr_data <- merge(crispr_data, cn_melt, by = c("Gene", "Broad_ID"), all.x = TRUE)
 # Gene expression (RPKM)
-ge_crispr_18Q3 <- filter(ge_melt_18Q3, Gene %in% as.character(unique(crispr_melt$Gene)))
+ge_crispr <- filter(ge_melt, Gene %in% as.character(unique(crispr_melt$Gene)))
 # ge_crispr_19Q1 <- filter(ge_melt_19Q1, Gene %in% as.character(unique(crispr_melt$Gene)))
-crispr_data <- merge(crispr_data, ge_crispr_18Q3, by = c("Gene", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
-# crispr_data <- merge(crispr_data, ge_crispr_19Q1, by = c("Gene", "DepMap_ID"), all.x = TRUE)
+crispr_data <- merge(crispr_data, ge_crispr, by = c("Gene", "Broad_ID"), all.x = TRUE)
+# crispr_data <- merge(crispr_data, ge_crispr_19Q1, by = c("Gene", "Broad_ID"), all.x = TRUE)
 saveRDS(crispr_data, "./../htscreens_giant_files/crispr_data_19Q1.rds", compress = "xz")
-
-# Takes a really long time to run (4+ hours)
-# crispr_data_ptmuts <- filter(crispr_data, Reference_Allele == 1 | Reference_Allele == 0 | is.na(Reference_Allele))
-# crispr_data_ptmuts$Keep_PtMut_Tests <- ifelse(crispr_data_ptmuts$Reference_Allele == 1 | is.na(crispr_data_ptmuts$Reference_Allele), TRUE, ifelse(crispr_data_ptmuts$Tumor_Seq_Allele1 == 1, TRUE, FALSE))
-# crispr_data_ptmuts <- filter(crispr_data_ptmuts, Keep_PtMut_Tests == TRUE)
-# crispr_data_ptmuts <- subset(crispr_data_ptmuts, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, Genome_Change, Keep_PtMut_Tests))
-# crispr_data_ptmuts <- unique(crispr_data_ptmuts)
-# saveRDS(crispr_data_ptmuts, "./data_munging/rds/crispr_data_19Q1_ptmuts.rds", compress = "xz")
 ```
 
-```{r, eval=FALSE}
+```{r, eval=TRUE}
 crispr_data <- readRDS("./../htscreens_giant_files/crispr_data_19Q1.rds")
@@
 # crispr_data_ptmuts <- readRDS("./../htscreens_giant_files/crispr_data_19Q1_ptmuts.rds")
-# crispr_data_g2p <- filter(crispr_data_ptmuts, Gene %in% g2p_genes)
 
+# Filter G2P CRISPR for point mutations
+crispr_data_ptmuts <- filter(crispr_data, PointMutation == 1)
+crispr_data_ptmuts <- subset(crispr_data_ptmuts, select = -c(PointMutation))
 # Filter CRISPR for G2P genes in G2P
-crispr_data_ptmuts <- filter(crispr_data, Gene %in% g2p_genes)
-# Filter G2P CRISPR for point mutations
-crispr_data_ptmuts <- filter(crispr_data_ptmuts, Reference_Allele == 1 | Reference_Allele == 0 | is.na(Reference_Allele))
-crispr_data_ptmuts$Keep_PtMut_Tests <- ifelse(crispr_data_ptmuts$Reference_Allele == 1 | is.na(crispr_data_ptmuts$Reference_Allele), TRUE, ifelse(crispr_data_ptmuts$Tumor_Seq_Allele1 == 1, TRUE, FALSE))
-crispr_data_ptmuts <- filter(crispr_data_ptmuts, Keep_PtMut_Tests == TRUE)
-crispr_data_ptmuts <- subset(crispr_data_ptmuts, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, Genome_Change, Keep_PtMut_Tests))
-crispr_data_g2p <- unique(crispr_data_ptmuts)
+crispr_data_g2p <- filter(crispr_data_ptmuts, Gene %in% g2p_genes)
+crispr_data_g2p <- unique(crispr_data_g2p)
 crispr_data_g2p$Gene <- factor(crispr_data_g2p$Gene, levels = g2p_genes)
-crispr_data_g2p$Mutation_Status_Nonsilent <- factor(crispr_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
+crispr_data_g2p$Mutation_Status <- factor(crispr_data_g2p$Mutation_Status)
 ```

### 2019-04-23 19Q1.Rmd

@@
   print(paste0("Filtered for ", database, "."))
+  colnames(filt)[colnames(filt) == "AUC_IC50"] <- "Score"
 
@@
   ## Identify point mutations
-  data$PointMutation <- ifelse(is.na(data$PointMutation), 0, data$PointMutation)
+  data$PointMutation <- ifelse(is.na(data$PointMutation), 1, data$PointMutation)
   ## Add color columns for plotting
@@
 
+  # Drop cell lines not in DepMap
+  data <- filter(data, !is.na(Broad_ID))
+
   # Factorize gene
@@
   return(ptmuts)
+}
+
+adj_signif <- function(df, alpha) {
+  # Takes df from compare_means and creates a signif code column for FDR-adjusted p-vals
+  df$p.signif.adj <- ifelse(df$p.adj <= alpha, "*", NA)
+  df$p.signif <- ifelse(df$p.signif == "ns", NA, df$p.signif)
+  df$p.short <- formatC(df$p, format = "g", digits =  2)
+  df$p.adj.short <- formatC(df$p.adj, format = "g", digits =  2)
+  return(df)
+}
+
+WilcoxonTestDF <- function(dataframe, measure_var, grouping, outfile) {
+  require(ggpubr)
+  signif <- compare_means(Score ~ Mutation_Status, group.by = grouping, data = dataframe, method = "wilcox.test", p.adjust.method = "BH")
+  signif <- adj_signif(signif, alpha = 0.05)
+  signif <- signif[order(signif$p),]
+  saveRDS(signif, outfile)
+  return(signif)
 }
@@
 
-# ccle <- MergeOmicsG2P(database = "CCLE", outfile = "./data_munging/rds/ccle_data_19Q1_g2pgenes.rds")
-# ctrp <- MergeOmicsG2P(database = "CTRP", outfile = "./data_munging/rds/ctrp_data_19Q1_g2pgenes.rds")
-# gdsc <- MergeOmicsG2P(database = "GDSC", outfile = "./data_munging/rds/gdsc_data_19Q1_g2pgenes.rds")
+ccle <- MergeOmicsG2P(database = "CCLE", outfile = "./data_munging/rds/ccle_data_19Q1_g2pgenes.rds")
+ctrp <- MergeOmicsG2P(database = "CTRP", outfile = "./../htscreens_giant_files/ctrp_data_19Q1_g2pgenes.rds")
+gdsc <- MergeOmicsG2P(database = "GDSC", outfile = "./data_munging/rds/gdsc_data_19Q1_g2pgenes.rds")
 
-# ccle_ptmuts <- FilterForPointMuts(dataframe = ccle, outfile = "./data_munging/rds/ccle_data_19Q1_g2pgenes_ptmuts.rds")
+ccle_ptmuts <- FilterForPointMuts(dataframe = ccle, outfile = "./data_munging/rds/ccle_data_19Q1_g2pgenes_ptmuts.rds")
 # ctrp_ptmuts <- FilterForPointMuts(dataframe = ctrp, outfile = "./data_munging/rds/ctrp_data_19Q1_g2pgenes_ptmuts.rds")
@@
 ccle <- readRDS("./data_munging/rds/ccle_data_19Q1_g2pgenes.rds")
-ctrp <- readRDS("./../htscreens_giant_files/ctrp_data_19Q1_g2pgenes.rds")
+# ctrp <- readRDS("./../htscreens_giant_files/ctrp_data_19Q1_g2pgenes.rds")
 gdsc <- readRDS("./data_munging/rds/gdsc_data_19Q1_g2pgenes.rds")
 ccle_ptmuts <- readRDS("./data_munging/rds/ccle_data_19Q1_g2pgenes_ptmuts.rds")
-ctrp_ptmuts <- readRDS("./../htscreens_giant_files/ctrp_data_19Q1_g2pgenes_ptmuts.rds")
+# ctrp_ptmuts <- readRDS("./../htscreens_giant_files/ctrp_data_19Q1_g2pgenes_ptmuts.rds")
 gdsc_ptmuts <- readRDS("./data_munging/rds/gdsc_data_19Q1_g2pgenes_ptmuts.rds")
@@
 # Testing
-test_ccle <- ccle_ptmuts %>% group_by(Gene, Mutation_Status_Nonsilent) %>% tally()
-test_ctrp <- ctrp_ptmuts %>% group_by(Gene, Mutation_Status_Nonsilent) %>% tally()
-test_gdsc <- gdsc_ptmuts %>% group_by(Gene, Mutation_Status_Nonsilent) %>% tally()
+test_ccle <- ccle_ptmuts %>% count(Gene, Mutation_Status)
+# test_ctrp <- ctrp_ptmuts %>% count(Gene, Mutation_Status)
+test_gdsc <- gdsc_ptmuts %>% count(Gene, Mutation_Status)
 ```
@@
 colnames(crispr)[1] <- "Broad_ID"
+
 # Melt CRISPR dataset for merging
 crispr_melt <- melt(crispr, id.vars = "Broad_ID", measure.vars = colnames(crispr)[2:ncol(crispr)], variable.name = "Gene", value.name = "Score")
+
 # Merge cell line metadata
 crispr_melt <- merge(crispr_melt, ccl_meta, by = "Broad_ID", all.x = TRUE)
+
 # Merge mutation annotations
@@
 crispr_muts$PointMutation <- ifelse(is.na(crispr_muts$PointMutation), 1, crispr_muts$PointMutation)
+
 # Summarize number of mutant and Wildtype cell lines
-crispr_muts_summ <- crispr_muts %>% group_by(Gene) %>%
-  summarize(N_Wildtype = length(Mutation_Status) - sum(Mutation_Status == 1),
-            N_Mutant = sum(Mutation_Status == 1))
-# Merge test results back into full dataset, which restores information lost in the summarization
+crispr_muts_summ <- crispr_muts %>% group_by(Gene) %>% summarize(N_Wildtype = length(Mutation_Status) - sum(Mutation_Status == 1), N_Mutant = sum(Mutation_Status == 1))
+## Merge test results back into full dataset, which restores information lost in the summarization
 crispr_data <- merge(crispr_muts_summ, crispr_muts, by = "Gene")
-# Add Color columns
+## Add Color column
 crispr_data$Color <- ifelse(crispr_data$Mutation_Status == 0, "thistle", "darkorchid")
@@
 # Cell line lineages
-# crispr_data <- merge(crispr_data, ccl_converter, by = c("CCLE_Name", "Broad_ID"), all.x = TRUE)
-# levels(crispr_data$lineage_name) <- sort(levels(crispr_data$lineage_name), decreasing = TRUE)
-# Copy number
 crispr_data <- merge(crispr_data, cn_melt, by = c("Gene", "Broad_ID"), all.x = TRUE)
+
 # Gene expression (RPKM)
 ge_crispr <- filter(ge_melt, Gene %in% as.character(unique(crispr_melt$Gene)))
-# ge_crispr_19Q1 <- filter(ge_melt_19Q1, Gene %in% as.character(unique(crispr_melt$Gene)))
 crispr_data <- merge(crispr_data, ge_crispr, by = c("Gene", "Broad_ID"), all.x = TRUE)
-# crispr_data <- merge(crispr_data, ge_crispr_19Q1, by = c("Gene", "Broad_ID"), all.x = TRUE)
 saveRDS(crispr_data, "./../htscreens_giant_files/crispr_data_19Q1.rds", compress = "xz")
@@
 crispr_data_g2p <- unique(crispr_data_g2p)
-crispr_data_g2p$Gene <- factor(crispr_data_g2p$Gene, levels = g2p_genes)
+crispr_data_g2p$Gene <- factor(crispr_data_g2p$Gene)
 crispr_data_g2p$Mutation_Status <- factor(crispr_data_g2p$Mutation_Status)
+crispr_data_g2p$Primary.Disease <- factor(crispr_data_g2p$Primary.Disease)
 ```
+
+# WILCOXON TESTS
+
+--------------------------------------------------------------------------------
+
+```{r, eval=FALSE}
+crispr_signif_gene <- WilcoxonTestDF(dataframe = crispr_data_g2p, grouping = "Gene", outfile = "./data_munging/rds/crispr_signif_g2p_gene.rds")
+crispr_signif_lineage <- WilcoxonTestDF(dataframe = crispr_data_g2p, grouping = c("Gene", "Primary.Disease"), outfile = "./data_munging/rds/crispr_signif_g2p_lineage.rds")
+
+ccle_signif_gene <- WilcoxonTestDF(dataframe = ccle_ptmuts, grouping = "Gene", outfile = "./data_munging/rds/ccle_signif_g2p_gene.rds")
+ccle_signif_lineage <- WilcoxonTestDF(dataframe = ccle_ptmuts, grouping = c("Gene", "Primary.Disease"), outfile = "./data_munging/rds/ccle_signif_g2p_lineage.rds")
+```
+
+# SESSION INFORMATION
+
+--------------------------------------------------------------------------------
+
+```{r}
+print(sessionInfo())
+```

### 2019-04-24 19Q1.Rmd
Wilcoxon tests for CRISPR, CCLE, and CTRP

@@
 
-```{r, eval=FALSE}
+```{r, eval=TRUE}
 ccle <- readRDS("./data_munging/rds/ccle_data_19Q1_g2pgenes.rds")
@@
 
-ccle_signif_gene <- WilcoxonTestDF(dataframe = ccle_ptmuts, grouping = "Gene", outfile = "./data_munging/rds/ccle_signif_g2p_gene.rds")
-ccle_signif_lineage <- WilcoxonTestDF(dataframe = ccle_ptmuts, grouping = c("Gene", "Primary.Disease"), outfile = "./data_munging/rds/ccle_signif_g2p_lineage.rds")
+ccle_signif_gene <- WilcoxonTestDF(dataframe = ccle_ptmuts, grouping = "Drug_Gene", outfile = "./data_munging/rds/ccle_signif_g2p_gene.rds")
+ccle_signif_gene$G2P_Drug_Gene <- ifelse(ccle_signif_gene$Drug_Gene %in% g2p_druggenes, TRUE, FALSE)
+ccle_signif_lineage <- WilcoxonTestDF(dataframe = filter(ccle_ptmuts, Drug_Gene_Lin %in% g2p_dgls), grouping = "Drug_Gene_Lin", outfile = "./data_munging/rds/ccle_signif_g2p_lineage.rds")
+
+# ctrp_signif_gene <- WilcoxonTestDF(dataframe = ctrp_ptmuts, grouping = "Drug_Gene", outfile = "./data_munging/rds/ctrp_signif_g2p_gene.rds")
+# ctrp_signif_gene$G2P_Drug_Gene <- ifelse(ctrp_signif_gene$Drug_Gene %in% g2p_druggenes, TRUE, FALSE)
+# ctrp_signif_lineage <- WilcoxonTestDF(dataframe = filter(ctrp_ptmuts, Drug_Gene_Lin %in% g2p_dgls), grouping = "Drug_Gene_Lin", outfile = "./data_munging/rds/ctrp_signif_g2p_lineage.rds")
+
+gdsc_signif_gene <- WilcoxonTestDF(dataframe = gdsc_ptmuts, grouping = "Drug_Gene", outfile = "./data_munging/rds/gdsc_signif_g2p_gene.rds")
+gdsc_signif_gene$G2P_Drug_Gene <- ifelse(gdsc_signif_gene$Drug_Gene %in% g2p_druggenes, TRUE, FALSE)
+gdsc_signif_lineage <- WilcoxonTestDF(dataframe = filter(gdsc_ptmuts, Drug_Gene_Lin %in% g2p_dgls), grouping = "Drug_Gene_Lin", outfile = "./data_munging/rds/gdsc_signif_g2p_lineage.rds")
+```
+
+```{r}
+test <- gdsc_ptmuts %>% count(Drug_Gene_Lin, Mutation_Status)
 ```

### 2019-04-26 18Q4.Rmd
updated 18Q4 and 19Q1 Rmds, test CRISPR merging function and normalization testing

@@
 ```{r, eval=FALSE}
-cn_melt <- readRDS("./data_munging/rds/cn_melt_18Q4.rds")
+cn_melt <- readRDS("./data_munging/18Q4/cn_melt_18Q4.rds")
 ge_melt_18Q3 <- readRDS("./../htscreens_giant_files/ge_melt_18Q3.rds")
@@
 ```{r}
-maf_df <- readRDS("./data_munging/rds/maf_df_18Q4.rds")
+maf_df <- readRDS("./data_munging/18Q4/maf_df_18Q4.rds")
 test <- filter(maf_df, Hugo_Symbol %in% g2p_genes) %>% count(Hugo_Symbol, CCLE_Name)

### 2019-04-26 19Q1.Rmd
updated 18Q4 and 19Q1 Rmds, test CRISPR merging function and normalization testing

@@
   # Merge mutation status, CN, and GE omics data with drugscreen results and metadata
+  if(database %in% c("CCLE", "CTRP", "GDSC")) {
     filt <- auc %>% filter(Database == database) %>% select(Cell_line, Histology, TCGA_classification, CCLE_Name, Broad_ID, Drug, AUC_IC50)
-  print(paste0("Filtered for ", database, "."))
+    print(paste0("Processing ", database, " data."))
     colnames(filt)[colnames(filt) == "AUC_IC50"] <- "Score"
@@
     print("Merged grid.")
-
     # Merge metadata
@@
     print("Merged metadata.")
+  if(database == "CRISPR") {
+    print(paste0("Processing ", database, " data."))
+    # Melt CRISPR dataset for merging
+    data <- melt(crispr, id.vars = "Broad_ID", measure.vars = colnames(crispr)[2:ncol(crispr)], variable.name = "Gene", value.name = "Score")
+    # Merge cell line metadata
+    data <- merge(data, select(ccl_meta, Cell_line, Histology, CCLE_Name, Broad_ID, Primary.Disease), by = "Broad_ID", all.x = TRUE)
+    data$Drug_Gene <- paste0(data$Drug, "_", data$Gene)
+    data$Drug_Gene_Lin <- paste0(data$Drug, "_", data$Gene, "_", data$Primary.Disease)
+    print("Merged metadata.")
+  }
 
@@
   data$PointMutation <- ifelse(is.na(data$PointMutation), 1, data$PointMutation)
+  # Summarize number of mutant and Wildtype cell lines
+  data_muts_summ <- data %>% group_by(Gene) %>% summarize(N_Wildtype = length(Mutation_Status) - sum(Mutation_Status == 1), N_Mutant = sum(Mutation_Status == 1))
+  ## Merge test results back into full dataset, which restores information lost in the summarization
+  data <- merge(data_muts_summ, data, by = "Gene")
   ## Add color columns for plotting
@@
     data$Color <- ifelse(data$Mutation_Status == 0, "paleturquoise3", "turquoise4")
+    data$Color <- factor(data$Color)
+  }
+  if(database == "CRISPR") {
+    data$Color <- ifelse(data$Mutation_Status == 0, "thistle", "darkorchid")
     data$Color <- factor(data$Color)
@@
 `r nrow(filter(test, n != 1))`/`r nrow(test)` gene-cell line combinations have more than one mutation in the MAF file. This is corrected in the point mutation filtering done below.
+
+**NEED TO RUN CTRP OVER WEEKEND**
 ```{r, eval=FALSE}
@@
 ```{r, eval=FALSE}
-crispr <- read.delim("./data_munging/19Q1/gene_effect_corrected_20190305.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
+crispr_all <- read.delim("./data_munging/19Q1/gene_effect_corrected_20190305.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
 # Remove Entrez gene IDs from colnames
-colnames(crispr) <- gsub(" .*", "", colnames(crispr))
-colnames(crispr)[1] <- "Broad_ID"
+colnames(crispr_all) <- gsub(" .*", "", colnames(crispr_all))
+colnames(crispr_all)[1] <- "Broad_ID"
 
 # Melt CRISPR dataset for merging
-crispr_melt <- melt(crispr, id.vars = "Broad_ID", measure.vars = colnames(crispr)[2:ncol(crispr)], variable.name = "Gene", value.name = "Score")
+crispr_melt <- melt(crispr_all, id.vars = "Broad_ID", measure.vars = colnames(crispr_all)[2:ncol(crispr_all)], variable.name = "Gene", value.name = "Score")
 
@@
 
+Test merging and filtering functions on CRISPR data:
+```{r, eval=FALSE}
+crispr <- MergeOmicsG2P(database = "CRISPR", outfile = "./../htscreens_giant_files/crispr_data_19Q1_g2pgenes.rds")
+crispr_ptmuts <- FilterForPointMuts(dataframe = crispr, outfile = "./../htscreens_giant_files/crispr_data_19Q1_g2pgenes_ptmuts.rds")
+```
+
 # WILCOXON TESTS
@@
 
+# SANDBOX
+
+--------------------------------------------------------------------------------
+
+Filter for BRCA1/2 mutations to see if we catch non-germline mutations/CN variants:
 ```{r}
-test <- gdsc_ptmuts %>% count(Drug_Gene_Lin, Mutation_Status)
+test <- filter(maf_df, Gene == "BRCA1" | Gene == "BRCA2")
+test2 <- filter(cn_melt, Gene == "BRCA1" | Gene == "BRCA2")
+```
+
+Test out standardization/normalization methods on Pozdeyev data. This yields evidence that the AUC values are already normalized.
+```{r, eval=FALSE}
+ccle_all <- read.delim("./../htscreens_giant_files/pozdeyev_data/CCLE_drug_response_metrics.csv.gz", sep = ",")
+ccle_all$AUC_IC50_standardized <- scale(ccle_all$AUC_IC50, center = TRUE, scale = TRUE)
+ccle_all$AUC_IC50_normalized <- scale(ccle_all$AUC_IC50, center = min(ccle_all$AUC_IC50[!is.na(ccle_all$AUC_IC50)]), scale = max(ccle_all$AUC_IC50[!is.na(ccle_all$AUC_IC50)]) - min(ccle_all$AUC_IC50[!is.na(ccle_all$AUC_IC50)]))
+ctrp_all <- read.delim("./../htscreens_giant_files/pozdeyev_data/CTRP_drug_response_metrics.csv.gz", sep = ",")
+ctrp_all$AUC_IC50_standardized <- scale(ctrp_all$AUC_IC50, center = TRUE, scale = TRUE)
+ctrp_all$AUC_IC50_normalized <- scale(ctrp_all$AUC_IC50, center = min(ctrp_all$AUC_IC50[!is.na(ctrp_all$AUC_IC50)]), scale = max(ctrp_all$AUC_IC50[!is.na(ctrp_all$AUC_IC50)]) - min(ctrp_all$AUC_IC50[!is.na(ctrp_all$AUC_IC50)]))
+gdsc_all <- read.delim("./../htscreens_giant_files/pozdeyev_data/GDSC_drug_response_metrics.csv.gz", sep = ",")
+gdsc_all$AUC_IC50_standardized <- scale(gdsc_all$AUC_IC50, center = TRUE, scale = TRUE)
+gdsc_all$AUC_IC50_normalized <- scale(gdsc_all$AUC_IC50, center = min(gdsc_all$AUC_IC50[!is.na(gdsc_all$AUC_IC50)]), scale = max(gdsc_all$AUC_IC50[!is.na(gdsc_all$AUC_IC50)]) - min(gdsc_all$AUC_IC50[!is.na(gdsc_all$AUC_IC50)]))
+
+auc_test <- bind_rows(ccle_all, ctrp_all, gdsc_all)
+
+ggplot(data = auc_test) +
+  geom_histogram(aes(x = AUC_IC50)) +
+  facet_wrap(~ Database, ncol = 3, scales = "free_y")
+ggplot(data = auc_test) +
+  geom_histogram(aes(x = AUC_IC50_normalized)) +
+  facet_wrap(~ Database, ncol = 3, scales = "free_y")
+ggplot(data = auc_test) +
+  geom_histogram(aes(x = AUC_IC50_standardized)) +
+  facet_wrap(~ Database, ncol = 3, scales = "free_y")
 ```

### 2019-04-26 18Q4.Rmd
updated 18Q4.Rmd for clarity

@@
 ```{r, warning=FALSE}
-crispr_pearson_res_GE <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>%
-                         summarize(p = cor.test(y = Score, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
-                                   corr = cor.test(y = Score, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
-                                   Metric = "Gene Expression")
-crispr_pearson_res_CN <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>%
-                         summarize(p = cor.test(y = Score, x = CN, method = "pearson", use = "complete.obs")$p.value,
-                                   corr = cor.test(y = Score, x = CN, method = "pearson", use = "complete.obs")$estimate,
-                                   Metric = "Copy Number")
-crispr_spearman_res_GE <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>%
-                          summarize(p = cor.test(y = Score, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
-                                    corr = cor.test(y = Score, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
-                                    Metric = "Gene Expression")
-crispr_spearman_res_CN <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>%
-                          summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value,
-                                    corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate,
-                                    Metric = "Copy Number")
+crispr_pearson_res_GE <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>% summarize(p = cor.test(y = Score, x = RPKM, method = "pearson", use = "complete.obs")$p.value, corr = cor.test(y = Score, x = RPKM, method = "pearson", use = "complete.obs")$estimate, Metric = "Gene Expression")
+crispr_pearson_res_CN <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>% summarize(p = cor.test(y = Score, x = CN, method = "pearson", use = "complete.obs")$p.value, corr = cor.test(y = Score, x = CN, method = "pearson", use = "complete.obs")$estimate, Metric = "Copy Number")
+crispr_spearman_res_GE <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>%summarize(p = cor.test(y = Score, x = RPKM, method = "spearman", use = "complete.obs")$p.value, corr = cor.test(y = Score, x = RPKM, method = "spearman", use = "complete.obs")$estimate, Metric = "Gene Expression")
+crispr_spearman_res_CN <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>% summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value, corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate, Metric = "Copy Number")
 ```
@@
 
-g2p_mut_stats <- g2p_corr_all %>% group_by(Dataset, G2P_DGL) %>% drop_na(Mut_Signif) %>% summarize(N_Signif_Muts = sum(Mut_Signif),
-                                                                                                   Total_Tests = length(Mut_Signif),
-                                                                                                   Perc_Signif = N_Signif_Muts / Total_Tests * 100)
+g2p_mut_stats <- g2p_corr_all %>% group_by(Dataset, G2P_DGL) %>% drop_na(Mut_Signif) %>% summarize(N_Signif_Muts = sum(Mut_Signif), Total_Tests = length(Mut_Signif), Perc_Signif = N_Signif_Muts / Total_Tests * 100)
 g2p_mut_stats

### 2019-04-26 19Q1.Rmd

@@
 
-# SET UP
+# Set up
 
@@
     data$Drug_Gene <- paste0(data$Drug, "_", data$Gene)
+    data$G2P_Drug_Gene <- ifelse(data$Drug_Gene %in% g2p_druggenes, "Yes", "No")
     data$Drug_Gene_Lin <- paste0(data$Drug, "_", data$Gene, "_", data$Primary.Disease)
+    data$G2P_Drug_Gene_Lin <- ifelse(data$Drug_Gene_Lin %in% g2p_dgls, "Yes", "No")
     print("Merged metadata.")
+  }
   if(database == "CRISPR") {
@@
   data$PointMutation <- ifelse(is.na(data$PointMutation), 1, data$PointMutation)
-  # Summarize number of mutant and Wildtype cell lines
+  ## Summarize number of mutant and Wildtype cell lines
   data_muts_summ <- data %>% group_by(Gene) %>% summarize(N_Wildtype = length(Mutation_Status) - sum(Mutation_Status == 1), N_Mutant = sum(Mutation_Status == 1))
@@
     data$Color <- ifelse(data$Mutation_Status == 0, "palegreen3", "springgreen4")
-    data$Color <- factor(data$Color)
   }
@@
     data$Color <- ifelse(data$Mutation_Status == 0, "slategray3", "steelblue4")
-    data$Color <- factor(data$Color)
   }
@@
     data$Color <- ifelse(data$Mutation_Status == 0, "paleturquoise3", "turquoise4")
-    data$Color <- factor(data$Color)
   }
@@
     data$Color <- ifelse(data$Mutation_Status == 0, "thistle", "darkorchid")
+  }
   data$Color <- factor(data$Color)
-  }
   print("Merged mutation calls.")
@@
 
-# DATA
+# Data
 
@@
 ccle <- MergeOmicsG2P(database = "CCLE", outfile = "./data_munging/rds/ccle_data_19Q1_g2pgenes.rds")
-ctrp <- MergeOmicsG2P(database = "CTRP", outfile = "./../htscreens_giant_files/ctrp_data_19Q1_g2pgenes.rds")
-gdsc <- MergeOmicsG2P(database = "GDSC", outfile = "./data_munging/rds/gdsc_data_19Q1_g2pgenes.rds")
+# ctrp <- MergeOmicsG2P(database = "CTRP", outfile = "./../htscreens_giant_files/ctrp_data_19Q1_g2pgenes.rds")
+# gdsc <- MergeOmicsG2P(database = "GDSC", outfile = "./data_munging/rds/gdsc_data_19Q1_g2pgenes.rds")
 
@@
 # ctrp_ptmuts <- FilterForPointMuts(dataframe = ctrp, outfile = "./data_munging/rds/ctrp_data_19Q1_g2pgenes_ptmuts.rds")
-gdsc_ptmuts <- FilterForPointMuts(dataframe = gdsc, outfile = "./data_munging/rds/gdsc_data_19Q1_g2pgenes_ptmuts.rds")
+# gdsc_ptmuts <- FilterForPointMuts(dataframe = gdsc, outfile = "./data_munging/rds/gdsc_data_19Q1_g2pgenes_ptmuts.rds")
 ```
@@
 ```{r, eval=TRUE}
-crispr_data <- readRDS("./../htscreens_giant_files/crispr_data_19Q1.rds")
-# Run next two lines only if the file was made (see end of the last chunk)
-# crispr_data_ptmuts <- readRDS("./../htscreens_giant_files/crispr_data_19Q1_ptmuts.rds")
+crispr_all <- readRDS("./../htscreens_giant_files/crispr_data_19Q1.rds")
 
 # Filter G2P CRISPR for point mutations
-crispr_data_ptmuts <- filter(crispr_data, PointMutation == 1)
-crispr_data_ptmuts <- subset(crispr_data_ptmuts, select = -c(PointMutation))
+crispr_ptmuts <- filter(crispr_data, PointMutation == 1)
+crispr_ptmuts <- subset(crispr_data_ptmuts, select = -c(PointMutation))
 # Filter CRISPR for G2P genes in G2P
-crispr_data_g2p <- filter(crispr_data_ptmuts, Gene %in% g2p_genes)
+crispr_data_g2p <- filter(crispr_ptmuts, Gene %in% g2p_genes)
 crispr_data_g2p <- unique(crispr_data_g2p)
@@
 
-# WILCOXON TESTS
+# Wilcoxon tests
 
@@
 
-# SANDBOX
+# Spearman correlations
+
+--------------------------------------------------------------------------------
+
+Spearman correlations for gene expression and copy number:
+```{r fig.height=8, fig.width=16}
+crispr_spear_ge <- transform(crispr_data_g2p %>% group_by(Gene) %>% summarize(p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value, p_log10 = -log10(p), corr = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate, Metric = "Gene Expression"), Gene = reorder(Gene, corr))
+crispr_spear_cn <- transform(crispr_data_g2p %>% group_by(Gene) %>% summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value, p_log10 = -log10(p), corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate, Metric = "Copy Number"), Gene = reorder(Gene, corr))
+
+spearman_KRAS <- rbind(filter(crispr_data_g2p, Gene == "KRAS") %>% summarize(p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value, corr = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate, Metric = "Gene Expression"), filter(crispr_data_g2p, Gene == "KRAS") %>% summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value, corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate, Metric = "Copy Number"))
+
+crispr_ge_spearman_corr_inset <- ggplot(filter(crispr_data_g2p, Gene == "KRAS"), aes(x = TPM, y = Score)) +
+  geom_point(pch = 21, fill = "cadetblue3", alpha = 0.6) +
+  labs(x = "KRAS Gene Expression (TPM)", y = "CERES Score", subtitle = paste0("Spearman correlation coefficient = ", round(spearman_KRAS$corr[1], 2), " (p = ", formatC(as.numeric(spearman_KRAS$p[1]), format = "e", digits = 1), ")"))
+
+crispr_cn_spearman_corr_inset <- ggplot(filter(crispr_data_g2p, Gene == "KRAS"), aes(x = CN, y = Score)) +
+  geom_point(pch = 21, fill = "palegreen2", alpha = 0.6) +
+  labs(x = "KRAS Copy Number (log2 ratio)", y = "CERES Score", subtitle = paste0("Spearman correlation coefficient = ", round(spearman_KRAS$corr[2], 2), " (p = ", formatC(as.numeric(spearman_KRAS$p[2]), format = "e", digits = 1), ")"))
+
+crispr_ge_spearman_corr_plot <- ggplot(data = crispr_spear_ge, aes(x = Gene, y = corr)) +
+  geom_point(aes(fill = p_log10), pch = 21, size = 5) +
+  scale_fill_gradient2(low = "white", mid = "white", high = "deepskyblue4", midpoint = 1.3010299957) +
+  coord_cartesian(ylim = c(-0.45, 0.2)) +
+  theme(legend.position = "bottom", axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 10)) +
+  labs(fill = "-log10(p)", x = "Gene", y = expression("Spearman Correlation Coefficient"~(r[s]))) +
+  annotation_custom(ggplotGrob(crispr_ge_spearman_corr_inset), xmin = 12, xmax = 32, ymin = -0.15, ymax = -0.45) +
+  geom_curve(aes(x = 3.5, y = -0.27, xend = 14, yend = -0.165), color = "lightgray", curvature = -0.2, arrow = arrow(length = unit(0.03, "npc")))
+
+crispr_cn_spearman_corr_plot <- ggplot(data = crispr_spear_cn, aes(x = Gene, y = corr)) +
+  geom_point(aes(fill = p_log10), pch = 21, size = 5) +
+  scale_fill_gradient2(low = "white", mid = "white", high = "green4", midpoint = 1.3010299957) +
+  coord_cartesian(ylim = c(-0.45, 0.2)) +
+  theme(legend.position = "bottom", axis.title.y = element_blank(), axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 10)) +
+  labs(fill = "-log10(p)", x = "Gene", y = "Spearman Correlation Coefficient (r_s)") +
+  annotation_custom(ggplotGrob(crispr_cn_spearman_corr_inset), xmin = 12, xmax = 32, ymin = -0.15, ymax = -0.45) +
+  geom_curve(aes(x = 2.5, y = -0.232, xend = 14, yend = -0.165), color = "lightgray", curvature = -0.2, arrow = arrow(length = unit(0.03, "npc")))
+
+crispr_spearman_corr_plot <- plot_grid(crispr_ge_spearman_corr_plot, crispr_cn_spearman_corr_plot, align = "h")
+crispr_spearman_corr_plot
+
+# ggsave("./plots/manuscript/crispr_spearman_corr_plot.pdf", crispr_spearman_corr_plot, device = "pdf", dpi = 450, width = 16, height = 8, units = "in")
+```
+
+# DGL KS tests
+
+--------------------------------------------------------------------------------
+
+```{r KS_functions}
+MakeCorrResSummaryTable <- function(df_list, dataset_name) {
+  # Input: list of dataframes corresponding to Drug_Gene groupings in the drugscreen datasets filtered for point mutations
+  CorrResSummaryTable <- data.frame(matrix(ncol = 6, nrow = 0))
+  for(i in 1:length(df_list)) {
+    corr_res <- df_list[[i]] %>% group_by(G2P_Drug_Gene_Lin) %>% summarize(Dataset = dataset_name,
+                Drug_Gene = names(df_list)[i],
+                Lineages = paste(as.character(unique(Primary.Disease)), collapse = ", "),
+                N_Lineages = length(as.character(unique(Primary.Disease))),
+                Spearman_Corr_GE = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate,
+                Spearman_Corr_CN = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate)
+    dgl_signif <- compare_means(Score ~ Mutation_Status, data = df_list[[i]], group.by = "G2P_Drug_Gene_Lin", method = "wilcox.test")[, c("G2P_Drug_Gene_Lin", "p")]
+    corr_res <- merge(corr_res, dgl_signif, by = "G2P_Drug_Gene_Lin", all = TRUE)
+    corr_res$Mut_Signif <- ifelse(corr_res$p < 0.05, 1, 0)
+    CorrResSummaryTable <- rbind(CorrResSummaryTable, corr_res)
+  }
+  return(CorrResSummaryTable)
+}
+
+G2PCorrKStest <- function(dataset, dataset_name) {
+  # Input: CorrResSummaryTable created by the MakeCorrResSummaryTable function
+  Metric <- colnames(dataset)[6:9]
+  D_stat <- NULL
+  pval <- NULL
+  signif <- NULL
+
+  yes <- dataset[dataset$G2P_Drug_Gene_Lin == "Yes",]
+  no <- dataset[dataset$G2P_Drug_Gene_Lin == "No",]
+
+  for(i in 6:9) {
+    test <- ks.test(yes[[colnames(yes)[i]]], no[[colnames(no)[i]]])
+    D_stat <- c(D_stat, test$statistic)
+    pval <- c(pval, test$p.value)
+    signif <- c(signif, ifelse(test$p.value < 0.001, "***", ifelse(test$p.value < 0.01, "**", ifelse(test$p.value < 0.05, "*", NA))))
+  }
+  df <- data.frame(Metric, D_stat, pval, signif)
+  df$Dataset <- dataset_name
+  return(df)
+}
+
+G2PCorrTables <- function(table_type) {
+  # CCLE
+  ccle_split <- split(ccle_ptmuts, f = ccle_ptmuts$Drug_Gene)
+  ccle_corr_all <- MakeCorrResSummaryTable(ccle_split, dataset_name = "CCLE")
+  # CTRP
+  ctrp_split <- split(ctrp_ptmuts, f = ctrp_ptmuts$Drug_Gene)
+  ctrp_corr_all <- MakeCorrResSummaryTable(ctrp_split, dataset_name = "CTRP")
+  # GDSC
+  gdsc_split <- split(gdsc_ptmuts, f = gdsc_ptmuts$Drug_Gene)
+  gdsc_corr_all <- MakeCorrResSummaryTable(gdsc_split, dataset_name = "GDSC")
+
+  g2p_corr_all <- rbind(ccle_corr_all, ctrp_corr_all, gdsc_corr_all)
+
+  if(table_type == "correlation" | table_type == "corr" ) {
+    return(g2p_corr_all)
+  }  
+  if(table_type == "mutation" | table_type == "mut" ) {
+    g2p_mut_stats <- g2p_corr_all %>% group_by(Dataset, G2P_Drug_Gene_lin) %>% drop_na(Mut_Signif) %>% summarize(N_Signif_Muts = sum(Mut_Signif),   Total_Tests = length(Mut_Signif), Perc_Signif = N_Signif_Muts / Total_Tests * 100)
+    return(g2p_mut_stats)
+  }
+  if(table_type == "KS" | table_type == "ks") {
+    ccle_corr_stats <- G2PCorrKStest(ccle_corr_all, "CCLE")
+    ctrp_corr_stats <- G2PCorrKStest(ctrp_corr_all, "CTRP")
+    gdsc_corr_stats <- G2PCorrKStest(gdsc_corr_all, "GDSC")
+    g2p_corr_stats <- rbind(ccle_corr_stats, ctrp_corr_stats, gdsc_corr_stats)
+    g2p_corr_stats <- g2p_corr_stats %>% separate(col = Metric, into = c("Correlation_Method", "corr", "Metric"), sep = "_")
+    g2p_corr_stats$Metric <- ifelse(g2p_corr_stats$Metric == "GE", "Gene Expression", "Copy Number")
+    return(g2p_corr_stats)
+  }
+}
+```
+
+Kolmogorov-Smirnov tests comparing DGLs that are in a G2P DGL and not.
+
+**RUN THIS WHEN ALL DRUGSCREEN DATA HAS BEEN MERGED**
+```{r, eval=FALSE, fig.height=6, fig.width=12}
+g2p_mut_stats <- G2PCorrTables(table_type = "mutation")
+g2p_corr_all <- G2PCorrTables(table_type = "correlation")
+g2p_corr_stats <- G2PCorrTables(table_type = "KS")
+
+g2p_corr_4plot <- g2p_corr_all
+g2p_corr_4plot$p <- NULL
+g2p_corr_4plot$Mut_Signif <- NULL
+g2p_corr_4plot <- melt(g2p_corr_4plot, id.vars = colnames(g2p_corr_4plot)[1:5], measure.vars = colnames(g2p_corr_4plot)[6:9], value.name = "Correlation")
+g2p_corr_4plot <- g2p_corr_4plot %>% separate(col = variable, into = c("Correlation_Method", "corr", "Metric"), sep = "_", remove = FALSE)
+g2p_corr_4plot$Metric <- ifelse(g2p_corr_4plot$Metric == "GE", "Gene Expression", "Copy Number")
+
+g2p_ks_res_plot_spearman <- ggplot(data = filter(g2p_corr_4plot, Correlation_Method == "Spearman")) +
+  facet_grid(Metric ~ Dataset, labeller = labeller(yfacet = c('CN' = "Copy Number", 'GE' = "Gene Expression"))) +
+  geom_violin(aes(y = Correlation, x = G2P_Drug_Gene_Lin, fill = Dataset, color = Dataset, alpha = G2P_Drug_Gene_Lin)) +
+  geom_boxplot(width = 0.075, aes(y = Correlation, x = G2P_Drug_Gene_Lin, color = Dataset)) +
+  geom_jitter(width = 0.3, alpha = 0.8, aes(y = Correlation, x = G2P_Drug_Gene_Lin, color = Dataset)) +
+  theme(legend.position = "none") +
+  scale_alpha_manual(values = c("Yes" = 0.6, "No" = 0.2)) +
+  scale_fill_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
+  scale_color_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
+  coord_cartesian(ylim = c(-1, 1)) +
+  geom_text(data = filter(g2p_corr_stats, Correlation_Method == "Spearman"), aes(x = 1.5, y = 0.8, label = paste0("D = ", formatC(D_stat, digits = 2, format = "f"), ", p = ", ifelse(pval > 0.1, round(pval, 2), round(pval, 3)), "\n", ifelse(is.na(signif), "", signif)))) +
+  labs(x = "Is the lineage in a G2P DGL?", y = "Spearman Correlation Coefficient")
+g2p_ks_res_plot_spearman
+
+# ggsave("./plots/manuscript/g2p_spearman_ks_res_plot.pdf", g2p_ks_res_plot_spearman, device = "pdf", dpi = 500, width = 12, height = 6, units = "in")
+```
+
+# Sandbox
 
@@
 
-# SESSION INFORMATION
+# Session information
 

### 2019-04-29 19Q1.Rmd
updated Rmd

@@
     # Melt CRISPR dataset for merging
-    data <- melt(crispr, id.vars = "Broad_ID", measure.vars = colnames(crispr)[2:ncol(crispr)], variable.name = "Gene", value.name = "Score")
+    data <- melt(crispr_all, id.vars = "Broad_ID", measure.vars = colnames(crispr_all)[2:ncol(crispr_all)], variable.name = "Gene", value.name = "Score")
     # Merge cell line metadata
@@
 ccle <- MergeOmicsG2P(database = "CCLE", outfile = "./data_munging/rds/ccle_data_19Q1_g2pgenes.rds")
-# ctrp <- MergeOmicsG2P(database = "CTRP", outfile = "./../htscreens_giant_files/ctrp_data_19Q1_g2pgenes.rds")
-# gdsc <- MergeOmicsG2P(database = "GDSC", outfile = "./data_munging/rds/gdsc_data_19Q1_g2pgenes.rds")
+ctrp <- MergeOmicsG2P(database = "CTRP", outfile = "./../htscreens_giant_files/ctrp_data_19Q1_g2pgenes.rds")
+gdsc <- MergeOmicsG2P(database = "GDSC", outfile = "./data_munging/rds/gdsc_data_19Q1_g2pgenes.rds")
 
 ccle_ptmuts <- FilterForPointMuts(dataframe = ccle, outfile = "./data_munging/rds/ccle_data_19Q1_g2pgenes_ptmuts.rds")
-# ctrp_ptmuts <- FilterForPointMuts(dataframe = ctrp, outfile = "./data_munging/rds/ctrp_data_19Q1_g2pgenes_ptmuts.rds")
-# gdsc_ptmuts <- FilterForPointMuts(dataframe = gdsc, outfile = "./data_munging/rds/gdsc_data_19Q1_g2pgenes_ptmuts.rds")
+ctrp_ptmuts <- FilterForPointMuts(dataframe = ctrp, outfile = "./../htscreens_giant_files/ctrp_data_19Q1_g2pgenes_ptmuts.rds")
+gdsc_ptmuts <- FilterForPointMuts(dataframe = gdsc, outfile = "./data_munging/rds/gdsc_data_19Q1_g2pgenes_ptmuts.rds")
 ```
@@
 
-```{r, eval=TRUE}
+```{r, eval=FALSE}
 ccle <- readRDS("./data_munging/rds/ccle_data_19Q1_g2pgenes.rds")
-# ctrp <- readRDS("./../htscreens_giant_files/ctrp_data_19Q1_g2pgenes.rds")
+ctrp <- readRDS("./../htscreens_giant_files/ctrp_data_19Q1_g2pgenes.rds")
 gdsc <- readRDS("./data_munging/rds/gdsc_data_19Q1_g2pgenes.rds")
 ccle_ptmuts <- readRDS("./data_munging/rds/ccle_data_19Q1_g2pgenes_ptmuts.rds")
-# ctrp_ptmuts <- readRDS("./../htscreens_giant_files/ctrp_data_19Q1_g2pgenes_ptmuts.rds")
+ctrp_ptmuts <- readRDS("./../htscreens_giant_files/ctrp_data_19Q1_g2pgenes_ptmuts.rds")
 gdsc_ptmuts <- readRDS("./data_munging/rds/gdsc_data_19Q1_g2pgenes_ptmuts.rds")
@@
 test_ccle <- ccle_ptmuts %>% count(Gene, Mutation_Status)
-# test_ctrp <- ctrp_ptmuts %>% count(Gene, Mutation_Status)
+test_ctrp <- ctrp_ptmuts %>% count(Gene, Mutation_Status)
 test_gdsc <- gdsc_ptmuts %>% count(Gene, Mutation_Status)
@@
 ```{r, eval=TRUE}
-crispr_all <- readRDS("./../htscreens_giant_files/crispr_data_19Q1.rds")
+crispr_data <- readRDS("./../htscreens_giant_files/crispr_data_19Q1.rds")
 
@@
 crispr_ptmuts <- filter(crispr_data, PointMutation == 1)
-crispr_ptmuts <- subset(crispr_data_ptmuts, select = -c(PointMutation))
+crispr_ptmuts <- subset(crispr_ptmuts, select = -c(PointMutation))
 # Filter CRISPR for G2P genes in G2P
-crispr_data_g2p <- filter(crispr_ptmuts, Gene %in% g2p_genes)
-crispr_data_g2p <- unique(crispr_data_g2p)
-crispr_data_g2p$Gene <- factor(crispr_data_g2p$Gene)
-crispr_data_g2p$Mutation_Status <- factor(crispr_data_g2p$Mutation_Status)
-crispr_data_g2p$Primary.Disease <- factor(crispr_data_g2p$Primary.Disease)
+crispr_g2p <- filter(crispr_ptmuts, Gene %in% g2p_genes)
+crispr_g2p <- unique(crispr_g2p)
+crispr_g2p$Gene <- factor(crispr_g2p$Gene)
+crispr_g2p$Mutation_Status <- factor(crispr_g2p$Mutation_Status)
+crispr_g2p$Primary.Disease <- factor(crispr_g2p$Primary.Disease)
 ```
@@
 ```{r, eval=FALSE}
-crispr <- MergeOmicsG2P(database = "CRISPR", outfile = "./../htscreens_giant_files/crispr_data_19Q1_g2pgenes.rds")
-crispr_ptmuts <- FilterForPointMuts(dataframe = crispr, outfile = "./../htscreens_giant_files/crispr_data_19Q1_g2pgenes_ptmuts.rds")
+# crispr_all <- read.delim("./data_munging/19Q1/gene_effect_corrected_20190305.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
+# # Remove Entrez gene IDs from colnames
+# colnames(crispr_all) <- gsub(" .*", "", colnames(crispr_all))
+# colnames(crispr_all)[1] <- "Broad_ID"
+
+# Omics metadata
+maf_df_filt <- filter(maf_df, Gene %in% g2p_genes)
+ge_filt <- filter(ge_melt, Gene %in% g2p_genes)
+cn_filt <- filter(cn_melt, Gene %in% g2p_genes)
+
+crispr_fxn <- MergeOmicsG2P(database = "CRISPR", outfile = "./../htscreens_giant_files/crispr_data_19Q1_g2pgenes_fxn.rds")
+crispr_ptmuts_fxn <- FilterForPointMuts(dataframe = crispr_fxn, outfile = "./../htscreens_giant_files/crispr_data_19Q1_g2pgenes_ptmuts_fxn.rds")
 ```
@@
 
-```{r, eval=FALSE}
+```{r, eval=TRUE}
 crispr_signif_gene <- WilcoxonTestDF(dataframe = crispr_data_g2p, grouping = "Gene", outfile = "./data_munging/rds/crispr_signif_g2p_gene.rds")
@@
 
-# ctrp_signif_gene <- WilcoxonTestDF(dataframe = ctrp_ptmuts, grouping = "Drug_Gene", outfile = "./data_munging/rds/ctrp_signif_g2p_gene.rds")
-# ctrp_signif_gene$G2P_Drug_Gene <- ifelse(ctrp_signif_gene$Drug_Gene %in% g2p_druggenes, TRUE, FALSE)
-# ctrp_signif_lineage <- WilcoxonTestDF(dataframe = filter(ctrp_ptmuts, Drug_Gene_Lin %in% g2p_dgls), grouping = "Drug_Gene_Lin", outfile = "./data_munging/rds/ctrp_signif_g2p_lineage.rds")
+ctrp_signif_gene <- WilcoxonTestDF(dataframe = ctrp_ptmuts, grouping = "Drug_Gene", outfile = "./data_munging/rds/ctrp_signif_g2p_gene.rds")
+ctrp_signif_gene$G2P_Drug_Gene <- ifelse(ctrp_signif_gene$Drug_Gene %in% g2p_druggenes, TRUE, FALSE)
+ctrp_signif_lineage <- WilcoxonTestDF(dataframe = filter(ctrp_ptmuts, Drug_Gene_Lin %in% g2p_dgls), grouping = "Drug_Gene_Lin", outfile = "./data_munging/rds/ctrp_signif_g2p_lineage.rds")
 

### 2019-04-29 19Q1.Rmd
updated Rmd

@@
 ```{r}
+library(cowplot)
 library(crunch)
@@
   return(ptmuts)
-}
-
-adj_signif <- function(df, alpha) {
-  # Takes df from compare_means and creates a signif code column for FDR-adjusted p-vals
-  df$p.signif.adj <- ifelse(df$p.adj <= alpha, "*", NA)
-  df$p.signif <- ifelse(df$p.signif == "ns", NA, df$p.signif)
-  df$p.short <- formatC(df$p, format = "g", digits =  2)
-  df$p.adj.short <- formatC(df$p.adj, format = "g", digits =  2)
-  return(df)
-}
-
-WilcoxonTestDF <- function(dataframe, measure_var, grouping, outfile) {
-  require(ggpubr)
-  signif <- compare_means(Score ~ Mutation_Status, group.by = grouping, data = dataframe, method = "wilcox.test", p.adjust.method = "BH")
-  signif <- adj_signif(signif, alpha = 0.05)
-  signif <- signif[order(signif$p),]
-  saveRDS(signif, outfile)
-  return(signif)
 }
@@
   counter = 0
-  if(drug %in% as.character(unique(ccle_data_g2p$Drug))) { counter <- counter + 1 }
-  if(drug %in% as.character(unique(ctrp_data_g2p$Drug))) { counter <- counter + 1 }
-  if(drug %in% as.character(unique(gdsc_data_g2p$Drug))) { counter <- counter + 1 }
+  if(drug %in% as.character(unique(ccle$Drug))) { counter <- counter + 1 }
+  if(drug %in% as.character(unique(ctrp$Drug))) { counter <- counter + 1 }
+  if(drug %in% as.character(unique(gdsc$Drug))) { counter <- counter + 1 }
   drug_summ <- rbind(drug_summ, data.frame(Drug = drug, Dataset_Count = counter))
@@
 
+```{r}
+crispr_fxn <- readRDS("./../htscreens_giant_files/crispr_data_19Q1_g2pgenes_fxn.rds")
+crispr_ptmuts_fxn <- readRDS("./../htscreens_giant_files/crispr_data_19Q1_g2pgenes_ptmuts_fxn.rds")
+```
+
 # Wilcoxon tests
@@
 
-```{r, eval=TRUE}
-crispr_signif_gene <- WilcoxonTestDF(dataframe = crispr_data_g2p, grouping = "Gene", outfile = "./data_munging/rds/crispr_signif_g2p_gene.rds")
-crispr_signif_lineage <- WilcoxonTestDF(dataframe = crispr_data_g2p, grouping = c("Gene", "Primary.Disease"), outfile = "./data_munging/rds/crispr_signif_g2p_lineage.rds")
+```{r wilcoxon_functions}
+adj_signif <- function(df, alpha) {
+  # Takes df from compare_means and creates a signif code column for FDR-adjusted p-vals
+  df$p.signif.adj <- ifelse(df$p.adj <= alpha, "*", NA)
+  df$p.signif <- ifelse(df$p.signif == "ns", NA, df$p.signif)
+  df$p.short <- formatC(df$p, format = "g", digits =  2)
+  df$p.adj.short <- formatC(df$p.adj, format = "g", digits =  2)
+  return(df)
+}
+
+WilcoxonTestDF <- function(dataframe, measure_var, grouping, outfile) {
+  require(ggpubr)
+  signif <- compare_means(Score ~ Mutation_Status, group.by = grouping, data = dataframe, method = "wilcox.test", p.adjust.method = "BH")
+  signif <- adj_signif(signif, alpha = 0.05)
+  signif <- signif[order(signif$p),]
+  saveRDS(signif, outfile)
+  return(signif)
+}
+```
+
+```{r, eval=FALSE}
+crispr_signif_gene <- WilcoxonTestDF(dataframe = crispr_g2p, grouping = "Gene", outfile = "./data_munging/rds/crispr_signif_g2p_gene.rds")
+crispr_signif_lineage <- WilcoxonTestDF(dataframe = crispr_g2p, grouping = c("Gene", "Primary.Disease"), outfile = "./data_munging/rds/crispr_signif_g2p_lineage.rds")
 
@@
 Spearman correlations for gene expression and copy number:
-```{r fig.height=8, fig.width=16}
-crispr_spear_ge <- transform(crispr_data_g2p %>% group_by(Gene) %>% summarize(p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value, p_log10 = -log10(p), corr = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate, Metric = "Gene Expression"), Gene = reorder(Gene, corr))
-crispr_spear_cn <- transform(crispr_data_g2p %>% group_by(Gene) %>% summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value, p_log10 = -log10(p), corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate, Metric = "Copy Number"), Gene = reorder(Gene, corr))
+```{r fig.height=6, fig.width=12}
+crispr_spear_ge <- transform(crispr_g2p %>% group_by(Gene) %>% summarize(p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value, p_log10 = -log10(p), corr = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate, Metric = "Gene Expression"), Gene = reorder(Gene, corr))
+crispr_spear_cn <- transform(crispr_g2p %>% group_by(Gene) %>% summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value, p_log10 = -log10(p), corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate, Metric = "Copy Number"), Gene = reorder(Gene, corr))
 
-spearman_KRAS <- rbind(filter(crispr_data_g2p, Gene == "KRAS") %>% summarize(p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value, corr = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate, Metric = "Gene Expression"), filter(crispr_data_g2p, Gene == "KRAS") %>% summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value, corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate, Metric = "Copy Number"))
+spearman_KRAS <- rbind(filter(crispr_g2p, Gene == "KRAS") %>% summarize(p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value, corr = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate, Metric = "Gene Expression"), filter(crispr_g2p, Gene == "KRAS") %>% summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value, corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate, Metric = "Copy Number"))
 
-crispr_ge_spearman_corr_inset <- ggplot(filter(crispr_data_g2p, Gene == "KRAS"), aes(x = TPM, y = Score)) +
+crispr_ge_spearman_corr_inset <- ggplot(filter(crispr_g2p, Gene == "KRAS"), aes(x = TPM, y = Score)) +
   geom_point(pch = 21, fill = "cadetblue3", alpha = 0.6) +
@@
 
-crispr_cn_spearman_corr_inset <- ggplot(filter(crispr_data_g2p, Gene == "KRAS"), aes(x = CN, y = Score)) +
+crispr_cn_spearman_corr_inset <- ggplot(filter(crispr_g2p, Gene == "KRAS"), aes(x = CN, y = Score)) +
   geom_point(pch = 21, fill = "palegreen2", alpha = 0.6) +
-  labs(x = "KRAS Copy Number (log2 ratio)", y = "CERES Score", subtitle = paste0("Spearman correlation coefficient = ", round(spearman_KRAS$corr[2], 2), " (p = ", formatC(as.numeric(spearman_KRAS$p[2]), format = "e", digits = 1), ")"))
+  labs(x = expression("KRAS Copy Number"~(log[2]-ratio)), y = "CERES Score", subtitle = paste0("Spearman correlation coefficient = ", round(spearman_KRAS$corr[2], 2), " (p = ", formatC(as.numeric(spearman_KRAS$p[2]), format = "e", digits = 1), ")"))
 
@@
   geom_point(aes(fill = p_log10), pch = 21, size = 5) +
-  scale_fill_gradient2(low = "white", mid = "white", high = "deepskyblue4", midpoint = 1.3010299957) +
-  coord_cartesian(ylim = c(-0.45, 0.2)) +
-  theme(legend.position = "bottom", axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 10)) +
-  labs(fill = "-log10(p)", x = "Gene", y = expression("Spearman Correlation Coefficient"~(r[s]))) +
-  annotation_custom(ggplotGrob(crispr_ge_spearman_corr_inset), xmin = 12, xmax = 32, ymin = -0.15, ymax = -0.45) +
-  geom_curve(aes(x = 3.5, y = -0.27, xend = 14, yend = -0.165), color = "lightgray", curvature = -0.2, arrow = arrow(length = unit(0.03, "npc")))
+  scale_fill_gradientn(colours = c("white", "deepskyblue4"), breaks = c(0, 3, 6, 9, 12, 15), labels = c(0, 3, 6, 9, 12, 15), limits = c(0, 15)) +
+  coord_cartesian(ylim = c(-0.325, 0.325)) +
+  scale_y_continuous(breaks = seq(-0.4, 0.4, by = 0.05), labels = seq(-0.4, 0.4, by = 0.05)) +
+  theme(legend.position = c(0.15, 0.95), legend.direction = "horizontal", legend.key.size = unit(0.05, "npc"), axis.text.x = element_text(angle = 65, hjust = 1, vjust = 1, size = 10)) +
+  labs(title = "Gene Expression", fill = expression(-log[10](p)), x = "Gene", y = expression("Spearman Correlation Coefficient"~(r[s]))) +
+  annotation_custom(ggplotGrob(crispr_ge_spearman_corr_inset), xmin = 12, xmax = 32, ymin = -0.325, ymax = -0.1) +
+  geom_curve(aes(x = 2, y = -0.262, xend = 13.7, yend = -0.112), color = "lightgray", curvature = -0.45, arrow = arrow(length = unit(0.03, "npc")))
 
@@
   geom_point(aes(fill = p_log10), pch = 21, size = 5) +
-  scale_fill_gradient2(low = "white", mid = "white", high = "green4", midpoint = 1.3010299957) +
-  coord_cartesian(ylim = c(-0.45, 0.2)) +
-  theme(legend.position = "bottom", axis.title.y = element_blank(), axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 10)) +
-  labs(fill = "-log10(p)", x = "Gene", y = "Spearman Correlation Coefficient (r_s)") +
-  annotation_custom(ggplotGrob(crispr_cn_spearman_corr_inset), xmin = 12, xmax = 32, ymin = -0.15, ymax = -0.45) +
-  geom_curve(aes(x = 2.5, y = -0.232, xend = 14, yend = -0.165), color = "lightgray", curvature = -0.2, arrow = arrow(length = unit(0.03, "npc")))
+  scale_fill_gradientn(colours = c("white", "green4"), breaks = c(0, 3, 6, 9, 12, 15), labels = c(0, 3, 6, 9, 12, 15), limits = c(0, 15)) +
+  coord_cartesian(ylim = c(-0.325, 0.325)) +
+  scale_y_continuous(breaks = seq(-0.4, 0.4, by = 0.05), labels = seq(-0.4, 0.4, by = 0.05)) +
+  theme(legend.position = c(0.15, 0.95), legend.direction = "horizontal", legend.key.size = unit(0.05, "npc"), axis.title.y = element_blank(), axis.text.x = element_text(angle = 65, hjust = 1, vjust = 1, size = 10)) +
+  labs(title = "Copy Number", fill = expression(-log[10](p)), x = "Gene", y = expression("Spearman Correlation Coefficient"~(r[s]))) +
+  annotation_custom(ggplotGrob(crispr_cn_spearman_corr_inset), xmin = 12, xmax = 32, ymin = -0.325, ymax = -0.1) +
+  geom_curve(aes(x = 2, y = -0.255, xend = 13.7, yend = -0.112), color = "lightgray", curvature = -0.2, arrow = arrow(length = unit(0.03, "npc")))
 
@@
 
-# ggsave("./plots/manuscript/crispr_spearman_corr_plot.pdf", crispr_spearman_corr_plot, device = "pdf", dpi = 450, width = 16, height = 8, units = "in")
+ggsave("./plots/manuscript/crispr_spearman_corr_plot.pdf", crispr_spearman_corr_plot, device = "pdf", dpi = 450, width = 20, height = 10, units = "in")
 ```
@@
   # Input: list of dataframes corresponding to Drug_Gene groupings in the drugscreen datasets filtered for point mutations
-  CorrResSummaryTable <- data.frame(matrix(ncol = 6, nrow = 0))
+  CorrResSummaryTable <- data.frame(matrix(ncol = 7, nrow = 0))
   for(i in 1:length(df_list)) {
-    corr_res <- df_list[[i]] %>% group_by(G2P_Drug_Gene_Lin) %>% summarize(Dataset = dataset_name,
+    corr_res <- df_list[[i]] %>% group_by(G2P_Drug_Gene_Lin) %>% summarize(
+                Dataset = dataset_name,
                 Drug_Gene = names(df_list)[i],
+                G2P_Drug_Gene = ifelse(Drug_Gene %in% g2p_druggenes, "Yes", "No"),
                 Lineages = paste(as.character(unique(Primary.Disease)), collapse = ", "),
@@
                 Spearman_Corr_CN = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate)
+    print(names(df_list)[i])
+
+    if(length(unique(df_list[[i]]$Mutation_Status)) == 2) {
       dgl_signif <- compare_means(Score ~ Mutation_Status, data = df_list[[i]], group.by = "G2P_Drug_Gene_Lin", method = "wilcox.test")[, c("G2P_Drug_Gene_Lin", "p")]
+    }
+    if(length(unique(df_list[[i]]$Mutation_Status)) == 1) {
+      dgl_signif <- data.frame("G2P_Drug_Gene_Lin" = NA, "p" = NA)
+    }
+
     corr_res <- merge(corr_res, dgl_signif, by = "G2P_Drug_Gene_Lin", all = TRUE)
@@
   }
+  CorrResSummaryTable <- CorrResSummaryTable[!is.na(CorrResSummaryTable$G2P_Drug_Gene_Lin), ]
   return(CorrResSummaryTable)
@@
   # Input: CorrResSummaryTable created by the MakeCorrResSummaryTable function
-  Metric <- colnames(dataset)[6:9]
+  Metric <- colnames(dataset)[7:8]
   D_stat <- NULL
@@
 
-  for(i in 6:9) {
+  for(i in 7:8) {
     test <- ks.test(yes[[colnames(yes)[i]]], no[[colnames(no)[i]]])
@@
 
-G2PCorrTables <- function(table_type) {
+G2PCorrTable <- function(ccle_ptmuts_df, ctrp_ptmuts_df, gdsc_ptmuts_df) {
   # CCLE
-  ccle_split <- split(ccle_ptmuts, f = ccle_ptmuts$Drug_Gene)
+  ccle_split <- split(ccle_ptmuts_df, f = ccle_ptmuts_df$Drug_Gene)
   ccle_corr_all <- MakeCorrResSummaryTable(ccle_split, dataset_name = "CCLE")
+  print("CCLE correlations: Complete.")
   # CTRP
-  ctrp_split <- split(ctrp_ptmuts, f = ctrp_ptmuts$Drug_Gene)
+  ctrp_split <- split(ctrp_ptmuts_df, f = ctrp_ptmuts_df$Drug_Gene)
   ctrp_corr_all <- MakeCorrResSummaryTable(ctrp_split, dataset_name = "CTRP")
+  print("CTRP correlations: Complete.")
   # GDSC
-  gdsc_split <- split(gdsc_ptmuts, f = gdsc_ptmuts$Drug_Gene)
+  gdsc_split <- split(gdsc_ptmuts_df, f = gdsc_ptmuts_df$Drug_Gene)
   gdsc_corr_all <- MakeCorrResSummaryTable(gdsc_split, dataset_name = "GDSC")
+  print("GDSC correlations: Complete.")
 
@@
 
-  if(table_type == "correlation" | table_type == "corr" ) {
   return(g2p_corr_all)
 }
+
+G2PCorrStatsTables<- function(corr_df, table_type) {  
   if(table_type == "mutation" | table_type == "mut" ) {
-    g2p_mut_stats <- g2p_corr_all %>% group_by(Dataset, G2P_Drug_Gene_lin) %>% drop_na(Mut_Signif) %>% summarize(N_Signif_Muts = sum(Mut_Signif),   Total_Tests = length(Mut_Signif), Perc_Signif = N_Signif_Muts / Total_Tests * 100)
-    return(g2p_mut_stats)
+    mut_stats <- corr_df %>% group_by(G2P_Drug_Gene_Lin, Dataset) %>% drop_na(Mut_Signif) %>% summarize(N_Signif_Muts = sum(Mut_Signif), Total_Tests = length(Mut_Signif), Perc_Signif = N_Signif_Muts / Total_Tests * 100)
+    print("Returning mutation statistics.")
+    return(mut_stats)
   }
   if(table_type == "KS" | table_type == "ks") {
-    ccle_corr_stats <- G2PCorrKStest(ccle_corr_all, "CCLE")
-    ctrp_corr_stats <- G2PCorrKStest(ctrp_corr_all, "CTRP")
-    gdsc_corr_stats <- G2PCorrKStest(gdsc_corr_all, "GDSC")
-    g2p_corr_stats <- rbind(ccle_corr_stats, ctrp_corr_stats, gdsc_corr_stats)
-    g2p_corr_stats <- g2p_corr_stats %>% separate(col = Metric, into = c("Correlation_Method", "corr", "Metric"), sep = "_")
-    g2p_corr_stats$Metric <- ifelse(g2p_corr_stats$Metric == "GE", "Gene Expression", "Copy Number")
-    return(g2p_corr_stats)
+    ccle_corr_stats <- G2PCorrKStest(filter(corr_df, Dataset == "CCLE"), "CCLE")
+    ctrp_corr_stats <- G2PCorrKStest(filter(corr_df, Dataset == "CTRP"), "CTRP")
+    gdsc_corr_stats <- G2PCorrKStest(filter(corr_df, Dataset == "GDSC"), "GDSC")
+    corr_stats <- rbind(ccle_corr_stats, ctrp_corr_stats, gdsc_corr_stats)
+    corr_stats <- corr_stats %>% separate(col = Metric, into = c("Correlation_Method", "corr", "Metric"), sep = "_")
+    corr_stats$Metric <- ifelse(corr_stats$Metric == "GE", "Gene Expression", "Copy Number")
+    print("Returning KS test results.")
+    return(corr_stats)
   }
@@
 Kolmogorov-Smirnov tests comparing DGLs that are in a G2P DGL and not.
-
-**RUN THIS WHEN ALL DRUGSCREEN DATA HAS BEEN MERGED**
 ```{r, eval=FALSE, fig.height=6, fig.width=12}
-g2p_mut_stats <- G2PCorrTables(table_type = "mutation")
-g2p_corr_all <- G2PCorrTables(table_type = "correlation")
-g2p_corr_stats <- G2PCorrTables(table_type = "KS")
+g2p_corr_all <- G2PCorrTable(ccle_ptmuts_df = ccle_ptmuts, ctrp_ptmuts_df = ctrp_ptmuts, gdsc_ptmuts_df = gdsc_ptmuts)
+g2p_mut_stats <- G2PCorrStatsTables(corr_df = g2p_corr_all, table_type = "mutation")
+g2p_corr_stats <- G2PCorrStatsTables(corr_df = g2p_corr_all, table_type = "KS")
 
@@
 g2p_corr_4plot$Mut_Signif <- NULL
-g2p_corr_4plot <- melt(g2p_corr_4plot, id.vars = colnames(g2p_corr_4plot)[1:5], measure.vars = colnames(g2p_corr_4plot)[6:9], value.name = "Correlation")
+g2p_corr_4plot <- melt(g2p_corr_4plot, id.vars = colnames(g2p_corr_4plot)[1:5], measure.vars = colnames(g2p_corr_4plot)[6:7], value.name = "Correlation")
 g2p_corr_4plot <- g2p_corr_4plot %>% separate(col = variable, into = c("Correlation_Method", "corr", "Metric"), sep = "_", remove = FALSE)

### 2019-04-30 19Q1.Rmd
updated Rmd

@@
 
-ggsave("./plots/manuscript/crispr_spearman_corr_plot.pdf", crispr_spearman_corr_plot, device = "pdf", dpi = 450, width = 20, height = 10, units = "in")
+# ggsave("./plots/manuscript/crispr_spearman_corr_plot.pdf", crispr_spearman_corr_plot, device = "pdf", dpi = 450, width = 20, height = 10, units = "in")
 ```
@@
 ```{r, eval=FALSE, fig.height=6, fig.width=12}
-g2p_corr_all <- G2PCorrTable(ccle_ptmuts_df = ccle_ptmuts, ctrp_ptmuts_df = ctrp_ptmuts, gdsc_ptmuts_df = gdsc_ptmuts)
+# g2p_corr_all <- G2PCorrTable(ccle_ptmuts_df = ccle_ptmuts, ctrp_ptmuts_df = ctrp_ptmuts, gdsc_ptmuts_df = gdsc_ptmuts)
+# saveRDS(g2p_corr_all, "./data_munging/rds/g2p_corr_all.rds")
+g2p_corr_all <- readRDS("./data_munging/rds/g2p_corr_all.rds")
 g2p_mut_stats <- G2PCorrStatsTables(corr_df = g2p_corr_all, table_type = "mutation")
@@
 g2p_corr_4plot$Mut_Signif <- NULL
-g2p_corr_4plot <- melt(g2p_corr_4plot, id.vars = colnames(g2p_corr_4plot)[1:5], measure.vars = colnames(g2p_corr_4plot)[6:7], value.name = "Correlation")
+g2p_corr_4plot <- melt(g2p_corr_4plot, id.vars = colnames(g2p_corr_4plot)[1:6], measure.vars = colnames(g2p_corr_4plot)[7:8], value.name = "Correlation")
 g2p_corr_4plot <- g2p_corr_4plot %>% separate(col = variable, into = c("Correlation_Method", "corr", "Metric"), sep = "_", remove = FALSE)

### 2019-04-30 19Q1.Rmd
re-organized plots dir

@@
 
+```{r}
+crispr_signif_gene <- readRDS("./data_munging/rds/crispr_signif_g2p_gene.rds")
+crispr_signif_lineage <- readRDS("./data_munging/rds/crispr_signif_g2p_lineage.rds")
+ccle_signif_gene <- readRDS("./data_munging/rds/ccle_signif_g2p_gene.rds")
+ccle_signif_lineage <- readRDS("./data_munging/rds/ccle_signif_g2p_lineage.rds")
+ctrp_signif_gene <- readRDS("./data_munging/rds/ctrp_signif_g2p_gene.rds")
+ctrp_signif_lineage <- readRDS("./data_munging/rds/ctrp_signif_g2p_lineage.rds")
+gdsc_signif_gene <- readRDS("./data_munging/rds/gdsc_signif_g2p_gene.rds")
+gdsc_signif_lineage <- readRDS("./data_munging/rds/gdsc_signif_g2p_lineage.rds")
+```
+
 # Spearman correlations
@@
   geom_point(aes(fill = p_log10), pch = 21, size = 5) +
-  scale_fill_gradientn(colours = c("white", "deepskyblue4"), breaks = c(0, 3, 6, 9, 12, 15), labels = c(0, 3, 6, 9, 12, 15), limits = c(0, 15)) +
+  scale_fill_gradientn(colours = c("white", "deepskyblue4"),
+                       breaks = c(0, 3, 6, 9, 12, 15),
+                       labels = c(0, 3, 6, 9, 12, 15),
+                       limits = c(0, 15)) +
   coord_cartesian(ylim = c(-0.325, 0.325)) +
-  scale_y_continuous(breaks = seq(-0.4, 0.4, by = 0.05), labels = seq(-0.4, 0.4, by = 0.05)) +
-  theme(legend.position = c(0.15, 0.95), legend.direction = "horizontal", legend.key.size = unit(0.05, "npc"), axis.text.x = element_text(angle = 65, hjust = 1, vjust = 1, size = 10)) +
-  labs(title = "Gene Expression", fill = expression(-log[10](p)), x = "Gene", y = expression("Spearman Correlation Coefficient"~(r[s]))) +
-  annotation_custom(ggplotGrob(crispr_ge_spearman_corr_inset), xmin = 12, xmax = 32, ymin = -0.325, ymax = -0.1) +
-  geom_curve(aes(x = 2, y = -0.262, xend = 13.7, yend = -0.112), color = "lightgray", curvature = -0.45, arrow = arrow(length = unit(0.03, "npc")))
+  scale_y_continuous(breaks = seq(-0.4, 0.4, by = 0.05),
+                     labels = seq(-0.4, 0.4, by = 0.05)) +
+  theme(legend.position = c(0.15, 0.95),
+        legend.direction = "horizontal",
+        legend.key.size = unit(0.05, "npc"),
+        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 10)) +
+  labs(title = "Gene Expression",
+       fill = expression(-log[10](p)),
+       x = "Gene",
+       y = expression("Spearman Correlation Coefficient"~(r[s]))) +
+  annotation_custom(ggplotGrob(crispr_ge_spearman_corr_inset),
+                    xmin = 12, xmax = 32, ymin = -0.325, ymax = -0.1) +
+  geom_curve(aes(x = 2, y = -0.262, xend = 13.7, yend = -0.112),
+             color = "lightgray", curvature = -0.45,
+             arrow = arrow(length = unit(0.03, "npc")))
 
@@
   geom_point(aes(fill = p_log10), pch = 21, size = 5) +
-  scale_fill_gradientn(colours = c("white", "green4"), breaks = c(0, 3, 6, 9, 12, 15), labels = c(0, 3, 6, 9, 12, 15), limits = c(0, 15)) +
+  scale_fill_gradientn(colours = c("white", "green4"),
+                       breaks = c(0, 3, 6, 9, 12, 15),
+                       labels = c(0, 3, 6, 9, 12, 15),
+                       limits = c(0, 15)) +
   coord_cartesian(ylim = c(-0.325, 0.325)) +
-  scale_y_continuous(breaks = seq(-0.4, 0.4, by = 0.05), labels = seq(-0.4, 0.4, by = 0.05)) +
-  theme(legend.position = c(0.15, 0.95), legend.direction = "horizontal", legend.key.size = unit(0.05, "npc"), axis.title.y = element_blank(), axis.text.x = element_text(angle = 65, hjust = 1, vjust = 1, size = 10)) +
-  labs(title = "Copy Number", fill = expression(-log[10](p)), x = "Gene", y = expression("Spearman Correlation Coefficient"~(r[s]))) +
-  annotation_custom(ggplotGrob(crispr_cn_spearman_corr_inset), xmin = 12, xmax = 32, ymin = -0.325, ymax = -0.1) +
-  geom_curve(aes(x = 2, y = -0.255, xend = 13.7, yend = -0.112), color = "lightgray", curvature = -0.2, arrow = arrow(length = unit(0.03, "npc")))
+  scale_y_continuous(breaks = seq(-0.4, 0.4, by = 0.05),
+                     labels = seq(-0.4, 0.4, by = 0.05)) +
+  theme(legend.position = c(0.15, 0.95),
+        legend.direction = "horizontal",
+        legend.key.size = unit(0.05, "npc"),
+        axis.title.y = element_blank(),
+        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 10)) +
+  labs(title = "Copy Number",
+       fill = expression(-log[10](p)),
+       x = "Gene",
+       y = expression("Spearman Correlation Coefficient"~(r[s]))) +
+  annotation_custom(ggplotGrob(crispr_cn_spearman_corr_inset),
+                    xmin = 12, xmax = 32, ymin = -0.325, ymax = -0.1) +
+  geom_curve(aes(x = 2, y = -0.255, xend = 13.7, yend = -0.112),
+             color = "lightgray", curvature = -0.2,
+             arrow = arrow(length = unit(0.03, "npc")))
 
@@
 
-# ggsave("./plots/manuscript/crispr_spearman_corr_plot.pdf", crispr_spearman_corr_plot, device = "pdf", dpi = 450, width = 20, height = 10, units = "in")
+ggsave("./plots/manuscript/crispr_spearman_corr_plot.png", crispr_spearman_corr_plot, device = "png", dpi = 450, width = 20, height = 10, units = "in")
 ```
@@
 Kolmogorov-Smirnov tests comparing DGLs that are in a G2P DGL and not.
-```{r, eval=FALSE, fig.height=6, fig.width=12}
+```{r, eval=TRUE, fig.height=6, fig.width=12}
 # g2p_corr_all <- G2PCorrTable(ccle_ptmuts_df = ccle_ptmuts, ctrp_ptmuts_df = ctrp_ptmuts, gdsc_ptmuts_df = gdsc_ptmuts)

### 2019-04-30 19Q1.Rmd
update rmd, start on re-making Fig1

@@
 ```{r}
+library(circlize)
+library(ComplexHeatmap)
 library(cowplot)
@@
 
-```{r functions}
+```{r general_functions}
 unfactorize <- function(df){
@@
 }
+```
 
+# Import data
+
+--------------------------------------------------------------------------------
+
+Note that the new DepMap 19Q1 release made multiple changes to variable names:
+
+- For their universal ccancer cell line nomenclature, they reverted back to `Broad_ID` from 18Q3 rather than `DepMap_ID` that was used in 19Q1
+- The `Primary.Disease` column of the cell line metadata file is more consistently named (`Subtype.Disease` now has the specific disease annotations), though there are a couple capitalization inconsistencies
+- MAF file no longer has `CCLE_Name` column and has a duplicate column of the Broad IDs (i.e. `DepMap_ID` and `Tumor_Sample_Barcode`)
+
+And changes to the data processing pipelines (the following is taken verbatim from the [DepMap data portal](https://depmap.org/portal/download/)):
+
+- **Expression**: We use the GTEx pipeline. Since last release, there have been some updates to the versions of different components of the pipeline and minor bug fixes on GTEx's end.
+- **Mutation**: In this release, we additionally process DepMap WES samples through the CGA mutation calling pipeline adapted for cell lines and available on FireCloud.
+We have added a column for the allele counts from this pipeline run (CGA_WES_AC).
+Previously, the WES_AC column was generated from running the Van Allen mutation calling pipeline for SNPs + Mutect2 for INDELs.
+This column is now named VA_WES_AC.
+- **Copy Number**: We have moved to using the newest version of the GATK pipeline.
+
+## Cell line metadata
+
+**D. Charytonowicz cell line converter**
+
+This comprehensive cancer cell line information was curated by both Daniel Charytonowicz and myself.
+```{r}
+ccl_converter <- read.delim("./data_munging/cell_line_database_v1_20180911.tsv", row.names = 1, sep = "\t", header = TRUE)
+lineage_converter <- unique(ccl_converter[, c("Broad_ID", "grouped_general_doid", "group_general_lineage_name")])
+ccl_histologies <- read.delim("./data_munging/ccl_histologies_metadata.csv", sep = ",", header = TRUE, row.names = 1)
+```
+
+**DepMap metadata**
+
+DepMap 19Q1 update fixed almost all of the inconsistencies of the Primary.Disease column, though there were come capitalization inconsistencies.
+```{r}
+ccl_meta <- read.delim("./data_munging/19Q1/DepMap-2019q1-celllines_v2_20190305.csv", sep = ",", header = TRUE, na.strings = c("", NA))
+ccl_meta$Primary.Disease <- tolower(ccl_meta$Primary.Disease)
+ccl_meta$Primary.Disease <- with(ccl_meta, ifelse(Primary.Disease == "colon/colorectal cancer", "colorectal cancer", Primary.Disease))
+ccl_meta <- subset(ccl_meta, Primary.Disease != "unknown" & Primary.Disease != "primary cells" & !grepl("MERGED", CCLE_Name, fixed = TRUE))
+ccl_meta$Cell_line <- as.character(lapply(ccl_meta$CCLE_Name, function(x) strsplit(as.character(x), split = "_")[[1]][1]))
+ccl_meta$Histology <- tolower(gsub("^[a-z0-9]*_", "", ccl_meta$CCLE_Name, ignore.case = TRUE))
+# Convert Primary.Disease entries to all lower case to fix factorization issue
+ccl_meta$Primary.Disease <- as.factor(tolower(ccl_meta$Primary.Disease))
+# Harmonize ID column name
+colnames(ccl_meta)[colnames(ccl_meta) == "DepMap_ID"] <- "Broad_ID"
+
+# Remove two rows that contain cell lines with two different histologies
+# The histologies that are kept are verified through matching in Cellosaurus and Cell Model Passports
+# KMH2, haematopoietic_and_lymphoid: https://web.expasy.org/cellosaurus/CVCL_1330, https://cellmodelpassports.sanger.ac.uk/passports/SIDM01018
+# MS1, lung: https://web.expasy.org/cellosaurus/CVCL_1429, https://cellmodelpassports.sanger.ac.uk/passports/SIDM00245
+ccl_meta <- subset(ccl_meta, CCLE_Name != "KMH2_THYROID" & CCLE_Name != "MS1_SKIN")
+```
+
+## G2P
+
+```{r}
+g2p_all <- read.delim("./data_munging/g2p_full_level_A_dataset_NEW_DEC_2_2018_withGroupedLineages.csv", sep = "\t", header = TRUE)
+g2p_all[, 1:2] <- NULL
+g2p_all$Drug <- tolower(g2p_all$Drug)
+g2p_all[g2p_all == -1] <- NA
+g2p_all$Ref[g2p_all$Ref == "None"] <- NA
+g2p_all$Alt[g2p_all$Alt == "None"] <- NA
+g2p_all <- subset(g2p_all, grepl("^CID", g2p_all$DrugID))
+g2p <- merge(g2p_all, lineage_converter, by = "grouped_general_doid", all.x = TRUE)
+
+g2p$Drug_Gene <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene), NA, paste0(g2p$Drug, "_", g2p$Gene))
+g2p$Drug_Gene_Lin <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene) | is.na(g2p$group_general_lineage_name), NA, paste0(g2p$Drug, "_", g2p$Gene, "_", g2p$group_general_lineage_name))
+g2p$position <- paste0("g.chr", g2p$Chromosome, ":", g2p$End, g2p$Ref, ">", g2p$Alt)
+g2p$position <- ifelse(grepl("NA", g2p$position), NA, g2p$position)
+
+g2p_dgls <-  unique(g2p$Drug_Gene_Lin[!is.na(g2p$Drug_Gene_Lin)])
+g2p_druggenes <- unique(g2p$Drug_Gene[!is.na(g2p$Drug_Gene)])
+g2p_drugs <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[1]))
+g2p_genes <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[2]))
+g2p_lins <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[3]))
+g2p_druggenes
+g2p_drugs
+g2p_genes
+g2p_lins
+
+# Order and genes taken from pink heatmap from Daniel's analyses
+# g2p_genes <- c("EGFR", "KRAS", "ERBB2", "ERBB3", "MET", "ALK", "ROS1", "PDGFRA", "ABL1", "KIT", "PDGFRB", "PDGFB", "BRAF", "G6PD", "RET", "BRCA1", "BRCA2", "UGT1A1", "TSC1", "TSC2", "AKT1", "IDH2", "DPYD", "ESR1", "CYP19A1", "TPMT", "FLT3", "NPM1", "DNMT3A", "PML", "PTCH1", "JAK2", "MYD88", "MGMT")
+```
+
+```{r, eval=FALSE}
+unique(g2p$group_general_lineage_name)
+levels(g2p$group_general_lineage_name)
+
+g2p_nonCID <- subset(g2p_all, !grepl("^CID", g2p_all$DrugID))
+summ <- g2p_nonCID %>% group_by(Drug, DrugID) %>% tally() %>% summarize(DrugID = DrugID, n = n, percent = formatC(n / 402 * 100, digits = 6, format = "f"))
+summ
+```
+
+## Omics
+
+For mutation calling, get paired gene name and cell line fields in a data frame.
+For this analysis, we don't care about how many mutations there are per gene or what type of mutations there are, so I didn't save more information.
+I took unique gene-cell line combinations since we only cared about mutation presence/absence.
+Add a `Mutation_Status` column denoting all entries in MAF files as mutations present in the associated cell lines.
+
+Mutation calls (coding region, germline filtered):
+```{r, eval=FALSE}
+maf_raw <- read.delim("./data_munging/19Q1/depmap_19Q1_mutation_calls_20190305.csv.gz", header = TRUE, sep = ",", row.names = 1)
+# Harmonize ID column name
+colnames(maf_raw)[colnames(maf_raw) == "DepMap_ID"] <- "Broad_ID"
+colnames(maf_raw)[colnames(maf_raw) == "Hugo_Symbol"] <- "Gene"
+# Select columns
+maf_df <- subset(maf_raw, select = c("Gene", "Broad_ID", "Variant_Classification", "Reference_Allele", "Tumor_Seq_Allele1"))
+maf_df$Reference_Allele <- ifelse(maf_df$Reference_Allele == "-", 0, nchar(as.character(maf_df$Reference_Allele)))
+maf_df$Tumor_Seq_Allele1 <- nchar(as.character(maf_df$Tumor_Seq_Allele1))
+maf_df <- maf_df[maf_df$Variant_Classification != "Silent",]
+# Add Mutation_Status column
+maf_df$Mutation_Status <- 1
+maf_df$PointMutation <- with(maf_df, ifelse(Reference_Allele == 1 | is.na(Reference_Allele), TRUE, ifelse(Reference_Allele == 0 & Tumor_Seq_Allele1 == 1, 1, 0)))
+
+saveRDS(maf_df, "./data_munging/19Q1/maf_df_19Q1.rds", compress = "xz")
+```
+
+DepMap WES CN Data:
+```{r, eval=FALSE}
+cn <- read.delim("./data_munging/19Q1/public_19Q1_gene_cn_20190305.csv.gz", sep = ",", check.names = FALSE, header = TRUE)
+# Remove Entrez gene IDs from colnames, format is "Gene (Entrez ID)"
+colnames(cn) <- gsub(" .*", "", colnames(cn))
+colnames(cn)[1] <- "Broad_ID"
+# Melt
+cn_melt <- melt(data = cn, id.vars = "Broad_ID", measure.vars = colnames(cn[2:ncol(cn)]), variable.name = "Gene", value.name = "CN")
+
+saveRDS(cn_melt, "./data_munging/19Q1/cn_melt_19Q1.rds", compress = "xz")
+```
+
+19Q1, CCLE RNAseq gene expression data (log2(TPM+1)):
+```{r, eval=FALSE}
+ge <- read.delim("./../htscreens_giant_files/CCLE_depMap_19Q1_TPM_20190305.csv.gz", header = TRUE, sep = ",", check.names = FALSE)
+# Remove Entrez gene IDs from colnames, format is "Gene (Entrez ID)"
+colnames(ge) <- gsub(" .*", "", colnames(ge_19Q1))
+colnames(ge)[1] <- "Broad_ID"
+# Melt
+ge_melt <- melt(ge, id.vars = "Broad_ID", measure.vars = colnames(ge_19Q1)[2:ncol(ge_19Q1)], variable.name = "Gene", value.name = "TPM")
+
+saveRDS(ge_melt, "./data_munging/19Q1/ge_melt_19Q1.rds", compress = "xz")
+```
+
+Load Rds:
+```{r}
+maf_df <- readRDS("./data_munging/19Q1/maf_df_19Q1.rds")
+cn_melt <- readRDS("./data_munging/19Q1/cn_melt_19Q1.rds")
+ge_melt <- readRDS("./data_munging/19Q1/ge_melt_19Q1.rds")
+```
+
+# Merge omics
+
+--------------------------------------------------------------------------------
+
+```{r omics_functions}
 MergeOmicsG2P <- function(database, outfile) {
@@
 
-# Data
-
---------------------------------------------------------------------------------
-
-Note that the new DepMap 19Q1 release made multiple changes to variable names:
-
-- For their universal ccancer cell line nomenclature, they reverted back to `Broad_ID` from 18Q3 rather than `DepMap_ID` that was used in 19Q1
-- The `Primary.Disease` column of the cell line metadata file is more consistently named (`Subtype.Disease` now has the specific disease annotations), though there are a couple capitalization inconsistencies
-- MAF file no longer has `CCLE_Name` column and has a duplicate column of the Broad IDs (i.e. `DepMap_ID` and `Tumor_Sample_Barcode`)
-
-And changes to the data processing pipelines (the following is taken verbatim from the [DepMap data portal](https://depmap.org/portal/download/)):
-
-- **Expression**: We use the GTEx pipeline. Since last release, there have been some updates to the versions of different components of the pipeline and minor bug fixes on GTEx's end.
-- **Mutation**: In this release, we additionally process DepMap WES samples through the CGA mutation calling pipeline adapted for cell lines and available on FireCloud.
-We have added a column for the allele counts from this pipeline run (CGA_WES_AC).
-Previously, the WES_AC column was generated from running the Van Allen mutation calling pipeline for SNPs + Mutect2 for INDELs.
-This column is now named VA_WES_AC.
-- **Copy Number**: We have moved to using the newest version of the GATK pipeline.
-
-## Cell line metadata
-
-**D. Charytonowicz cell line converter**
-
-This comprehensive cancer cell line information was curated by both Daniel Charytonowicz and myself.
-```{r}
-ccl_converter <- read.delim("./data_munging/cell_line_database_v1_20180911.tsv", row.names = 1, sep = "\t", header = TRUE)
-lineage_converter <- unique(ccl_converter[, c("Broad_ID", "grouped_general_doid", "group_general_lineage_name")])
-ccl_histologies <- read.delim("./data_munging/ccl_histologies_metadata.csv", sep = ",", header = TRUE, row.names = 1)
-```
-
-**DepMap metadata**
-
-DepMap 19Q1 update fixed almost all of the inconsistencies of the Primary.Disease column, though there were come capitalization inconsistencies.
-```{r}
-ccl_meta <- read.delim("./data_munging/19Q1/DepMap-2019q1-celllines_v2_20190305.csv", sep = ",", header = TRUE, na.strings = c("", NA))
-ccl_meta$Primary.Disease <- tolower(ccl_meta$Primary.Disease)
-ccl_meta$Primary.Disease <- with(ccl_meta, ifelse(Primary.Disease == "colon/colorectal cancer", "colorectal cancer", Primary.Disease))
-ccl_meta <- subset(ccl_meta, Primary.Disease != "unknown" & Primary.Disease != "primary cells" & !grepl("MERGED", CCLE_Name, fixed = TRUE))
-ccl_meta$Cell_line <- as.character(lapply(ccl_meta$CCLE_Name, function(x) strsplit(as.character(x), split = "_")[[1]][1]))
-ccl_meta$Histology <- tolower(gsub("^[a-z0-9]*_", "", ccl_meta$CCLE_Name, ignore.case = TRUE))
-# Convert Primary.Disease entries to all lower case to fix factorization issue
-ccl_meta$Primary.Disease <- as.factor(tolower(ccl_meta$Primary.Disease))
-# Harmonize ID column name
-colnames(ccl_meta)[colnames(ccl_meta) == "DepMap_ID"] <- "Broad_ID"
-
-# Remove two rows that contain cell lines with two different histologies
-# The histologies that are kept are verified through matching in Cellosaurus and Cell Model Passports
-# KMH2, haematopoietic_and_lymphoid: https://web.expasy.org/cellosaurus/CVCL_1330, https://cellmodelpassports.sanger.ac.uk/passports/SIDM01018
-# MS1, lung: https://web.expasy.org/cellosaurus/CVCL_1429, https://cellmodelpassports.sanger.ac.uk/passports/SIDM00245
-ccl_meta <- subset(ccl_meta, CCLE_Name != "KMH2_THYROID" & CCLE_Name != "MS1_SKIN")
-```
-
-## G2P
-
-```{r}
-g2p <- read.delim("./data_munging/g2p_full_level_A_dataset_NEW_DEC_2_2018_withGroupedLineages.csv", sep = "\t", header = TRUE)
-g2p[, 1:2] <- NULL
-g2p <- merge(g2p, lineage_converter, by = "grouped_general_doid", all.x = TRUE)
-
-g2p$Drug <- tolower(g2p$Drug)
-g2p[g2p == -1] <- NA
-g2p$Ref[g2p$Ref == "None"] <- NA
-g2p$Alt[g2p$Alt == "None"] <- NA
-g2p$Drug_Gene <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene), NA, paste0(g2p$Drug, "_", g2p$Gene))
-g2p$Drug_Gene_Lin <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene) | is.na(g2p$group_general_lineage_name), NA, paste0(g2p$Drug, "_", g2p$Gene, "_", g2p$group_general_lineage_name))
-g2p$position <- paste0("g.chr", g2p$Chromosome, ":", g2p$End, g2p$Ref, ">", g2p$Alt)
-g2p$position <- ifelse(grepl("NA", g2p$position), NA, g2p$position)
-g2p_filt <- subset(g2p, grepl("^CID", g2p$DrugID))
-
-g2p_dgls <-  unique(g2p_filt$Drug_Gene_Lin[!is.na(g2p_filt$Drug_Gene_Lin)])
-g2p_druggenes <- unique(g2p_filt$Drug_Gene[!is.na(g2p_filt$Drug_Gene)])
-g2p_drugs <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[1]))
-g2p_genes <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[2]))
-g2p_lins <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[3]))
-g2p_druggenes
-g2p_drugs
-g2p_genes
-g2p_lins
-
-# Order and genes taken from pink heatmap from Daniel's analyses
-# g2p_genes <- c("EGFR", "KRAS", "ERBB2", "ERBB3", "MET", "ALK", "ROS1", "PDGFRA", "ABL1", "KIT", "PDGFRB", "PDGFB", "BRAF", "G6PD", "RET", "BRCA1", "BRCA2", "UGT1A1", "TSC1", "TSC2", "AKT1", "IDH2", "DPYD", "ESR1", "CYP19A1", "TPMT", "FLT3", "NPM1", "DNMT3A", "PML", "PTCH1", "JAK2", "MYD88", "MGMT")
-```
-
-```{r, eval=FALSE}
-# levels(g2p_filt$Phenotype.Description)
-unique(g2p_filt$group_general_lineage_name)
-levels(g2p_filt$group_general_lineage_name)
-
-g2p_nonCID <- subset(g2p, !grepl("^CID", g2p$DrugID))
-summ <- g2p_nonCID %>% group_by(Drug, DrugID) %>% tally() %>% summarize(DrugID = DrugID, n = n, percent = formatC(n / 402 * 100, digits = 6, format = "f"))
-summ
-```
-
-## Omics
-
-For mutation calling, get paired gene name and cell line fields in a data frame.
-For this analysis, we don't care about how many mutations there are per gene or what type of mutations there are, so I didn't save more information.
-I took unique gene-cell line combinations since we only cared about mutation presence/absence.
-Add a `Mutation_Status` column denoting all entries in MAF files as mutations present in the associated cell lines.
-
-Mutation calls (coding region, germline filtered):
-```{r, eval=FALSE}
-maf_raw <- read.delim("./data_munging/19Q1/depmap_19Q1_mutation_calls_20190305.csv.gz", header = TRUE, sep = ",", row.names = 1)
-# Harmonize ID column name
-colnames(maf_raw)[colnames(maf_raw) == "DepMap_ID"] <- "Broad_ID"
-colnames(maf_raw)[colnames(maf_raw) == "Hugo_Symbol"] <- "Gene"
-# Select columns
-maf_df <- subset(maf_raw, select = c("Gene", "Broad_ID", "Variant_Classification", "Reference_Allele", "Tumor_Seq_Allele1"))
-maf_df$Reference_Allele <- ifelse(maf_df$Reference_Allele == "-", 0, nchar(as.character(maf_df$Reference_Allele)))
-maf_df$Tumor_Seq_Allele1 <- nchar(as.character(maf_df$Tumor_Seq_Allele1))
-maf_df <- maf_df[maf_df$Variant_Classification != "Silent",]
-# Add Mutation_Status column
-maf_df$Mutation_Status <- 1
-maf_df$PointMutation <- with(maf_df, ifelse(Reference_Allele == 1 | is.na(Reference_Allele), TRUE, ifelse(Reference_Allele == 0 & Tumor_Seq_Allele1 == 1, 1, 0)))
-
-saveRDS(maf_df, "./data_munging/19Q1/maf_df_19Q1.rds", compress = "xz")
-```
-
-DepMap WES CN Data:
-```{r, eval=FALSE}
-cn <- read.delim("./data_munging/19Q1/public_19Q1_gene_cn_20190305.csv.gz", sep = ",", check.names = FALSE, header = TRUE)
-# Remove Entrez gene IDs from colnames, format is "Gene (Entrez ID)"
-colnames(cn) <- gsub(" .*", "", colnames(cn))
-colnames(cn)[1] <- "Broad_ID"
-# Melt
-cn_melt <- melt(data = cn, id.vars = "Broad_ID", measure.vars = colnames(cn[2:ncol(cn)]), variable.name = "Gene", value.name = "CN")
-
-saveRDS(cn_melt, "./data_munging/19Q1/cn_melt_19Q1.rds", compress = "xz")
-```
-
-19Q1, CCLE RNAseq gene expression data (log2(TPM+1)):
-```{r, eval=FALSE}
-ge <- read.delim("./../htscreens_giant_files/CCLE_depMap_19Q1_TPM_20190305.csv.gz", header = TRUE, sep = ",", check.names = FALSE)
-# Remove Entrez gene IDs from colnames, format is "Gene (Entrez ID)"
-colnames(ge) <- gsub(" .*", "", colnames(ge_19Q1))
-colnames(ge)[1] <- "Broad_ID"
-# Melt
-ge_melt <- melt(ge, id.vars = "Broad_ID", measure.vars = colnames(ge_19Q1)[2:ncol(ge_19Q1)], variable.name = "Gene", value.name = "TPM")
-
-saveRDS(ge_melt, "./data_munging/19Q1/ge_melt_19Q1.rds", compress = "xz")
-```
-
-Load Rds:
-```{r}
-maf_df <- readRDS("./data_munging/19Q1/maf_df_19Q1.rds")
-cn_melt <- readRDS("./data_munging/19Q1/cn_melt_19Q1.rds")
-ge_melt <- readRDS("./data_munging/19Q1/ge_melt_19Q1.rds")
-```
-
 ## Drug screens
-
-### Merge omics
 
@@
 `r nrow(filter(test, n != 1))`/`r nrow(test)` gene-cell line combinations have more than one mutation in the MAF file. This is corrected in the point mutation filtering done below.
-
-**NEED TO RUN CTRP OVER WEEKEND**
 ```{r, eval=FALSE}
@@
 
-### Summaries
-
 ```{r, eval=TRUE}
@@
 ## CRISPR
-
-### Merge CRISPR data and annotations
 
@@
 
-# Wilcoxon tests
+# G2P summary figures
+
+--------------------------------------------------------------------------------
+
+```{r fig.height=6, fig.width=12}
+g2p_dg_counts <- g2p_all %>% count(Drug, , Gene) %>% filter(!is.na(Drug), !is.na(Gene))
+g2p_dg_counts <- dcast(g2p_dg_counts, Gene ~ Drug, value.var = "n", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
+g2p_dg_counts <- g2p_dg_counts[order(rowSums(-g2p_dg_counts)), order(colSums(-g2p_dg_counts))]
+g2p_dg_counts[g2p_dg_counts == 0] <- NA
+
+# Define color scale
+col_fun <- colorRamp2(c(0, 103), c("mistyrose", "purple4"))
+# Legend properties list
+ht_legend_list <- list(legend_direction = "horizontal", title_position = "lefttop", legend_width = unit(6, "in"), border = "black")
+ht <- Heatmap(g2p_dg_counts, 
+              name = "Frequency",
+              col = col_fun,
+              na_col = "white",
+              rect_gp = gpar(col = "gray88"),
+              heatmap_legend_param = ht_legend_list,
+              cluster_rows = FALSE, 
+              cluster_columns = FALSE, 
+              row_names_side = "left",
+              row_title = "Genes",
+              column_title = "Drugs", 
+              column_title_side = "bottom")
+
+# png(filename = out_filepath, width = 7.5, height = 8, units = "in", res = 500)
+draw(ht, heatmap_legend_side = "top")
+# dev.off()
+```
+
+# Wilcoxon tests (mut)
 
@@
 
-# Spearman correlations
+# Spearman (CN, GE)
 
@@
 Spearman correlations for gene expression and copy number:
-```{r fig.height=6, fig.width=12}
+```{r}
 crispr_spear_ge <- transform(crispr_g2p %>% group_by(Gene) %>% summarize(p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value, p_log10 = -log10(p), corr = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate, Metric = "Gene Expression"), Gene = reorder(Gene, corr))
 crispr_spear_cn <- transform(crispr_g2p %>% group_by(Gene) %>% summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value, p_log10 = -log10(p), corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate, Metric = "Copy Number"), Gene = reorder(Gene, corr))
+```
 
+Create CRISPR two-column, KRAS-inset plot for CN and GE:
+```{r fig.height=6, fig.width=12}
 spearman_KRAS <- rbind(filter(crispr_g2p, Gene == "KRAS") %>% summarize(p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value, corr = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate, Metric = "Gene Expression"), filter(crispr_g2p, Gene == "KRAS") %>% summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value, corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate, Metric = "Copy Number"))
@@
 Kolmogorov-Smirnov tests comparing DGLs that are in a G2P DGL and not.
+
+**NEED TO FILTER FOR ONLY G2P DRUG-GENE COMBINATIONS PRIOR TO KS TEST**
+
 ```{r, eval=TRUE, fig.height=6, fig.width=12}
@@
 g2p_mut_stats <- G2PCorrStatsTables(corr_df = g2p_corr_all, table_type = "mutation")
-g2p_corr_stats <- G2PCorrStatsTables(corr_df = g2p_corr_all, table_type = "KS")
 
-g2p_corr_4plot <- g2p_corr_all
+g2p_corr_4plot <- filter(g2p_corr_all, G2P_Drug_Gene == "Yes")
+g2p_corr_stats <- G2PCorrStatsTables(corr_df = g2p_corr_4plot, table_type = "KS")
 g2p_corr_4plot$p <- NULL
@@
   coord_cartesian(ylim = c(-1, 1)) +
-  geom_text(data = filter(g2p_corr_stats, Correlation_Method == "Spearman"), aes(x = 1.5, y = 0.8, label = paste0("D = ", formatC(D_stat, digits = 2, format = "f"), ", p = ", ifelse(pval > 0.1, round(pval, 2), round(pval, 3)), "\n", ifelse(is.na(signif), "", signif)))) +
-  labs(x = "Is the lineage in a G2P DGL?", y = "Spearman Correlation Coefficient")
+  geom_text(data = filter(g2p_corr_stats, Correlation_Method == "Spearman"),
+            aes(x = 1.5, y = 0.8,
+                label = paste0("D = ", formatC(D_stat, digits = 2, format = "f"),
+                               ", p = ", ifelse(pval > 0.1, round(pval, 2), ifelse(pval < 0.001, formatC(pval, digits = 1, format = "e"), round(pval, 3))),
+                               "\n", ifelse(is.na(signif), "", signif)))) +
+  labs(x = "Is the lineage in a G2P DGL?",
+       y = expression("Spearman Correlation Coefficient"~(r[s])))
 g2p_ks_res_plot_spearman
 
-# ggsave("./plots/manuscript/g2p_spearman_ks_res_plot.pdf", g2p_ks_res_plot_spearman, device = "pdf", dpi = 500, width = 12, height = 6, units = "in")
+ggsave("./plots/manuscript/g2p_spearman_ks_res_plot.png", g2p_ks_res_plot_spearman, device = "png", dpi = 500, width = 12, height = 6, units = "in")
 ```

### 2019-05-01 19Q1.Rmd
updated Rmd

@@
 
-    # Get all G2Pgene-cell line combinations
+    # Get all G2P gene-cell line combinations
     grid <- expand.grid("Cell_line" = unique(filt$Cell_line), "Gene" = g2p_genes)
@@
     data <- melt(crispr_all, id.vars = "Broad_ID", measure.vars = colnames(crispr_all)[2:ncol(crispr_all)], variable.name = "Gene", value.name = "Score")
+    # Get all G2P gene-cell line combinations
+    data <-  filter(data, Gene %in% g2p_genes)
     # Merge cell line metadata
@@
 
+Merge all CRISPR genes:
 ```{r, eval=FALSE}
@@
 crispr_ptmuts <- subset(crispr_ptmuts, select = -c(PointMutation))
-# Filter CRISPR for G2P genes in G2P
-crispr_g2p <- filter(crispr_ptmuts, Gene %in% g2p_genes)
-crispr_g2p <- unique(crispr_g2p)
-crispr_g2p$Gene <- factor(crispr_g2p$Gene)
-crispr_g2p$Mutation_Status <- factor(crispr_g2p$Mutation_Status)
-crispr_g2p$Primary.Disease <- factor(crispr_g2p$Primary.Disease)
+crispr_ptmuts <- filter(crispr_ptmuts, Gene %in% g2p_genes)
 ```
 
-Test merging and filtering functions on CRISPR data:
-```{r, eval=FALSE}
-# crispr_all <- read.delim("./data_munging/19Q1/gene_effect_corrected_20190305.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
-# # Remove Entrez gene IDs from colnames
-# colnames(crispr_all) <- gsub(" .*", "", colnames(crispr_all))
-# colnames(crispr_all)[1] <- "Broad_ID"
-
-# Omics metadata
-maf_df_filt <- filter(maf_df, Gene %in% g2p_genes)
-ge_filt <- filter(ge_melt, Gene %in% g2p_genes)
-cn_filt <- filter(cn_melt, Gene %in% g2p_genes)
-
-crispr_fxn <- MergeOmicsG2P(database = "CRISPR", outfile = "./../htscreens_giant_files/crispr_data_19Q1_g2pgenes_fxn.rds")
-crispr_ptmuts_fxn <- FilterForPointMuts(dataframe = crispr_fxn, outfile = "./../htscreens_giant_files/crispr_data_19Q1_g2pgenes_ptmuts_fxn.rds")
-```
-
-```{r}
-crispr_fxn <- readRDS("./../htscreens_giant_files/crispr_data_19Q1_g2pgenes_fxn.rds")
-crispr_ptmuts_fxn <- readRDS("./../htscreens_giant_files/crispr_data_19Q1_g2pgenes_ptmuts_fxn.rds")
-```
-
-# G2P summary figures
+# G2P summary heatmap
 
@@
 
-```{r fig.height=6, fig.width=12}
-g2p_dg_counts <- g2p_all %>% count(Drug, , Gene) %>% filter(!is.na(Drug), !is.na(Gene))
-g2p_dg_counts <- dcast(g2p_dg_counts, Gene ~ Drug, value.var = "n", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
+```{r fig.height=6, fig.width=8}
+g2p_dg_counts <- g2p_all %>% count(Drug, Gene) %>% filter(!is.na(Drug), !is.na(Gene))
+g2p_dg_counts <- dcast(g2p_dg_counts, Drug ~ Gene, value.var = "n", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Drug)
 g2p_dg_counts <- g2p_dg_counts[order(rowSums(-g2p_dg_counts)), order(colSums(-g2p_dg_counts))]
@@
 
+# Create annotation layer
+hta_data <- data.frame(Drug = rownames(g2p_dg_counts), CCLE = NA, CTRP = NA, GDSC = NA)
+hta_data$CCLE <- ifelse(hta_data$Drug %in% unique(ccle_ptmuts$Drug), "Screened", "Not screened")
+hta_data$CTRP <- ifelse(hta_data$Drug %in% unique(ctrp_ptmuts$Drug), "Screened", "Not screened")
+hta_data$GDSC <- ifelse(hta_data$Drug %in% unique(gdsc_ptmuts$Drug), "Screened", "Not screened")
+rownames(hta_data) <- hta_data$Drug
+hta_data$Drug <- NULL
+
+hta_annot <- HeatmapAnnotation(text = anno_text(colnames(hta_data), offset = unit(0.1, "in"), gp = gpar(fontsize = 10)))
+hta_legend_list <- list(legend_direction = "horizontal", border = "gray70", nrow = 2)
+hta <- Heatmap(hta_data,
+               name = "Functional screen status           ",
+               col = c("Screened" = "purple4", "Not screened" = "gray97"), 
+               rect_gp = gpar(col = "gray70"),
+               top_annotation = hta_annot,
+               heatmap_legend_param = hta_legend_list,
+               row_names_side = "left",
+               row_names_gp = gpar(fontsize = 10),
+               column_names_side = "top",
+               column_names_gp = gpar(fontsize = 10),
+               show_column_names = FALSE,
+               cluster_rows = FALSE, 
+               cluster_columns = FALSE,
+               row_title = "Drugs",
+               row_title_gp = gpar(fontface = "bold", fontsize = 14),
+               column_title = "Dataset",
+               column_title_gp = gpar(fontface = "bold", fontsize = 14),
+               width = unit(1.5, "in"))
+
 # Define color scale
-col_fun <- colorRamp2(c(0, 103), c("mistyrose", "purple4"))
+col_fun <- colorRamp2(c(0, 100), c("mistyrose", "purple4"))
 # Legend properties list
-ht_legend_list <- list(legend_direction = "horizontal", title_position = "lefttop", legend_width = unit(6, "in"), border = "black")
+ht_legend_list <- list(legend_direction = "horizontal", legend_width = unit(2.5, "in"), border = "gray70")
 ht <- Heatmap(g2p_dg_counts, 
-              name = "Frequency",
+              name = "Number of G2P interpretations",
               col = col_fun,
-              na_col = "white",
-              rect_gp = gpar(col = "gray88"),
+              na_col = "gray97",
+              rect_gp = gpar(col = "gray70"),
               heatmap_legend_param = ht_legend_list,
@@
               cluster_columns = FALSE, 
+              show_row_names = FALSE,
               row_names_side = "left",
-              row_title = "Genes",
-              column_title = "Drugs", 
+              row_names_gp = gpar(fontsize = 10),
+              column_names_side = "bottom",
+              column_names_gp = gpar(fontsize = 10),
+              row_title = "Drugs",
+              row_title_gp = gpar(fontface = "bold", fontsize = 14),
+              column_title = "Genes", 
+              column_title_gp = gpar(fontface = "bold", fontsize = 14),
               column_title_side = "bottom")
 
-# png(filename = out_filepath, width = 7.5, height = 8, units = "in", res = 500)
-draw(ht, heatmap_legend_side = "top")
+# png(filename = "./plots/manuscript/g2p_summary_heatmap.png", width = 12, height = 10, units = "in", res = 500)
+draw(hta + ht, gap = unit(5, "mm"), heatmap_legend_side = "top")
 # dev.off()
@@
 
+## Plots
+
 # Spearman (CN, GE)
@@
 Spearman correlations for gene expression and copy number:
-```{r}
-crispr_spear_ge <- transform(crispr_g2p %>% group_by(Gene) %>% summarize(p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value, p_log10 = -log10(p), corr = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate, Metric = "Gene Expression"), Gene = reorder(Gene, corr))
-crispr_spear_cn <- transform(crispr_g2p %>% group_by(Gene) %>% summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value, p_log10 = -log10(p), corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate, Metric = "Copy Number"), Gene = reorder(Gene, corr))
+```{r, warning=FALSE}
+crispr_spear_ge <- transform(crispr_ptmuts %>% group_by(Gene) %>% summarize(p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value, p_log10 = -log10(p), corr = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate, Metric = "Gene Expression"), Gene = reorder(Gene, corr))
+crispr_spear_cn <- transform(crispr_ptmuts %>% group_by(Gene) %>% summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value, p_log10 = -log10(p), corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate, Metric = "Copy Number"), Gene = reorder(Gene, corr))
 ```
+
+## Plots
 
@@
 ```{r fig.height=6, fig.width=12}
-spearman_KRAS <- rbind(filter(crispr_g2p, Gene == "KRAS") %>% summarize(p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value, corr = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate, Metric = "Gene Expression"), filter(crispr_g2p, Gene == "KRAS") %>% summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value, corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate, Metric = "Copy Number"))
+spearman_KRAS <- rbind(filter(crispr_ptmuts, Gene == "KRAS") %>% summarize(p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value, corr = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate, Metric = "Gene Expression"), filter(crispr_ptmuts, Gene == "KRAS") %>% summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value, corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate, Metric = "Copy Number"))
 
-crispr_ge_spearman_corr_inset <- ggplot(filter(crispr_g2p, Gene == "KRAS"), aes(x = TPM, y = Score)) +
+crispr_ge_spearman_corr_inset <- ggplot(filter(crispr_ptmuts, Gene == "KRAS"), aes(x = TPM, y = Score)) +
   geom_point(pch = 21, fill = "cadetblue3", alpha = 0.6) +
@@
 
-crispr_cn_spearman_corr_inset <- ggplot(filter(crispr_g2p, Gene == "KRAS"), aes(x = CN, y = Score)) +
+crispr_cn_spearman_corr_inset <- ggplot(filter(crispr_ptmuts, Gene == "KRAS"), aes(x = CN, y = Score)) +
   geom_point(pch = 21, fill = "palegreen2", alpha = 0.6) +
@@
 
-ggsave("./plots/manuscript/crispr_spearman_corr_plot.png", crispr_spearman_corr_plot, device = "png", dpi = 450, width = 20, height = 10, units = "in")
+# ggsave("./plots/manuscript/crispr_spearman_corr_plot.png", crispr_spearman_corr_plot, device = "png", dpi = 450, width = 20, height = 10, units = "in")
 ```
@@
 Kolmogorov-Smirnov tests comparing DGLs that are in a G2P DGL and not.
-
-**NEED TO FILTER FOR ONLY G2P DRUG-GENE COMBINATIONS PRIOR TO KS TEST**
-
 ```{r, eval=TRUE, fig.height=6, fig.width=12}
@@
 
-ggsave("./plots/manuscript/g2p_spearman_ks_res_plot.png", g2p_ks_res_plot_spearman, device = "png", dpi = 500, width = 12, height = 6, units = "in")
+# ggsave("./plots/manuscript/g2p_spearman_ks_res_plot.png", g2p_ks_res_plot_spearman, device = "png", dpi = 500, width = 12, height = 6, units = "in")
 ```
@@
 test2 <- filter(cn_melt, Gene == "BRCA1" | Gene == "BRCA2")
+```
+
+Test filtering CRISPR data for G2P genes using function:
+```{r, eval=FALSE}
+crispr_all <- read.delim("./data_munging/19Q1/gene_effect_corrected_20190305.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
+# Remove Entrez gene IDs from colnames
+colnames(crispr_all) <- gsub(" .*", "", colnames(crispr_all))
+colnames(crispr_all)[1] <- "Broad_ID"
+
+# Omics metadata
+maf_df_filt <- filter(maf_df, Gene %in% g2p_genes)
+ge_filt <- filter(ge_melt, Gene %in% g2p_genes)
+cn_filt <- filter(cn_melt, Gene %in% g2p_genes)
+
+crispr_fxn <- MergeOmicsG2P(database = "CRISPR", outfile = "./../htscreens_giant_files/crispr_data_19Q1_g2pgenes_fxn.rds")
+crispr_ptmuts_fxn <- FilterForPointMuts(dataframe = crispr_fxn, outfile = "./../htscreens_giant_files/crispr_data_19Q1_g2pgenes_ptmuts_fxn.rds")
+```
+
+```{r, eval=FALSE}
+crispr_fxn <- readRDS("./../htscreens_giant_files/crispr_data_19Q1_g2pgenes_fxn.rds")
+crispr_ptmuts_fxn <- readRDS("./../htscreens_giant_files/crispr_data_19Q1_g2pgenes_ptmuts_fxn.rds")
 ```

### 2019-05-02 19Q1.Rmd
updated Rmd

@@
 
-```{r}
+```{r libraries}
 library(circlize)
@@
 
-# Import data
+# DATA
 
@@
 This comprehensive cancer cell line information was curated by both Daniel Charytonowicz and myself.
-```{r}
+```{r dan_ccl_database}
 ccl_converter <- read.delim("./data_munging/cell_line_database_v1_20180911.tsv", row.names = 1, sep = "\t", header = TRUE)
-lineage_converter <- unique(ccl_converter[, c("Broad_ID", "grouped_general_doid", "group_general_lineage_name")])
+ccl_lineage_converter <- unique(ccl_converter[, c("Broad_ID", "grouped_general_doid", "group_general_lineage_name")])
+lineage_converter <- unique(select(lineage_converter, grouped_general_doid, group_general_lineage_name))
 ccl_histologies <- read.delim("./data_munging/ccl_histologies_metadata.csv", sep = ",", header = TRUE, row.names = 1)
@@
 DepMap 19Q1 update fixed almost all of the inconsistencies of the Primary.Disease column, though there were come capitalization inconsistencies.
-```{r}
+```{r depmap_metadata}
 ccl_meta <- read.delim("./data_munging/19Q1/DepMap-2019q1-celllines_v2_20190305.csv", sep = ",", header = TRUE, na.strings = c("", NA))
@@
 
-```{r}
-g2p_all <- read.delim("./data_munging/g2p_full_level_A_dataset_NEW_DEC_2_2018_withGroupedLineages.csv", sep = "\t", header = TRUE)
-g2p_all[, 1:2] <- NULL
-g2p_all$Drug <- tolower(g2p_all$Drug)
-g2p_all[g2p_all == -1] <- NA
-g2p_all$Ref[g2p_all$Ref == "None"] <- NA
-g2p_all$Alt[g2p_all$Alt == "None"] <- NA
-g2p_all <- subset(g2p_all, grepl("^CID", g2p_all$DrugID))
-g2p <- merge(g2p_all, lineage_converter, by = "grouped_general_doid", all.x = TRUE)
-
+```{r g2p_interpretations}
+g2p <- read.delim("./data_munging/g2p_full_level_A_dataset_NEW_DEC_2_2018_withGroupedLineages.csv", sep = "\t", header = TRUE)
+g2p[, 1:2] <- NULL
+g2p$Drug <- tolower(g2p$Drug)
+g2p[g2p == -1] <- NA
+g2p$Ref[g2p$Ref == "None"] <- NA
+g2p$Alt[g2p$Alt == "None"] <- NA
+g2p <- subset(g2p, grepl("^CID", g2p$DrugID))
 g2p$Drug_Gene <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene), NA, paste0(g2p$Drug, "_", g2p$Gene))
-g2p$Drug_Gene_Lin <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene) | is.na(g2p$group_general_lineage_name), NA, paste0(g2p$Drug, "_", g2p$Gene, "_", g2p$group_general_lineage_name))
 g2p$position <- paste0("g.chr", g2p$Chromosome, ":", g2p$End, g2p$Ref, ">", g2p$Alt)
 g2p$position <- ifelse(grepl("NA", g2p$position), NA, g2p$position)
+g2p <- merge(g2p, lineage_converter, by = "grouped_general_doid", all.x = TRUE)
+g2p$Drug_Gene_Lin <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene) | is.na(g2p$group_general_lineage_name), NA, paste0(g2p$Drug, "_", g2p$Gene, "_", g2p$group_general_lineage_name))
 
@@
 
-```{r, eval=FALSE}
+```{r testing, eval=FALSE}
 unique(g2p$group_general_lineage_name)
@@
 
-g2p_nonCID <- subset(g2p_all, !grepl("^CID", g2p_all$DrugID))
+g2p_nonCID <- subset(g2p, !grepl("^CID", g2p$DrugID))
 summ <- g2p_nonCID %>% group_by(Drug, DrugID) %>% tally() %>% summarize(DrugID = DrugID, n = n, percent = formatC(n / 402 * 100, digits = 6, format = "f"))
@@
 Mutation calls (coding region, germline filtered):
-```{r, eval=FALSE}
+```{r mutation_status, eval=FALSE}
 maf_raw <- read.delim("./data_munging/19Q1/depmap_19Q1_mutation_calls_20190305.csv.gz", header = TRUE, sep = ",", row.names = 1)
@@
 DepMap WES CN Data:
-```{r, eval=FALSE}
+```{r copy_number, eval=FALSE}
 cn <- read.delim("./data_munging/19Q1/public_19Q1_gene_cn_20190305.csv.gz", sep = ",", check.names = FALSE, header = TRUE)
@@
 19Q1, CCLE RNAseq gene expression data (log2(TPM+1)):
-```{r, eval=FALSE}
+```{r gene_expression, eval=FALSE}
 ge <- read.delim("./../htscreens_giant_files/CCLE_depMap_19Q1_TPM_20190305.csv.gz", header = TRUE, sep = ",", check.names = FALSE)
@@
 Load Rds:
-```{r}
+```{r load_omics_rds}
 maf_df <- readRDS("./data_munging/19Q1/maf_df_19Q1.rds")
@@
 
-# Merge omics
+```{r omics_testing, eval=FALSE}
+test <- filter(maf_df, Gene %in% g2p_genes) %>% count(Gene, Broad_ID)
+test <- test[order(test$n, decreasing = TRUE),]
+```
+
+# MERGE OMICS
 
@@
 
-```{r}
-test <- filter(maf_df, Gene %in% g2p_genes) %>% count(Gene, Broad_ID)
-test <- test[order(test$n, decreasing = TRUE),]
-```
-
 `r nrow(filter(test, n != 1))`/`r nrow(test)` gene-cell line combinations have more than one mutation in the MAF file. This is corrected in the point mutation filtering done below.
-```{r, eval=FALSE}
+```{r merge_filter_drug_data, eval=FALSE}
 # Load in Pozdeyev et al. (2016) data
@@
 
-```{r, eval=TRUE}
+```{r load_drug_rds, eval=TRUE}
 ccle <- readRDS("./data_munging/rds/ccle_data_19Q1_g2pgenes.rds")
@@
 How many datasets screen each G2P drug?
-```{r, eval=FALSE}
+```{r drug_testing, eval=FALSE}
 drug_summ <- data.frame(Drug = character(), Dataset_Count = integer(), stringsAsFactors = FALSE)
@@
 Merge all CRISPR genes:
-```{r, eval=FALSE}
+```{r merge_crispr_data, eval=FALSE}
 crispr_all <- read.delim("./data_munging/19Q1/gene_effect_corrected_20190305.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
@@
 
-```{r, eval=TRUE}
+```{r load_crispr_filter, eval=TRUE}
 crispr_data <- readRDS("./../htscreens_giant_files/crispr_data_19Q1.rds")
@@
 crispr_ptmuts <- filter(crispr_ptmuts, Gene %in% g2p_genes)
+crispr_ptmuts$Gene <- factor(crispr_ptmuts$Gene)
+crispr_ptmuts$Primary.Disease <- factor(crispr_ptmuts$Primary.Disease)
 ```
 
-# G2P summary heatmap
+# DATA SUMMARY FIGURES
 
@@
 
-```{r fig.height=6, fig.width=8}
-g2p_dg_counts <- g2p_all %>% count(Drug, Gene) %>% filter(!is.na(Drug), !is.na(Gene))
+## Cell line and drug overlaps
+
+```{r ccl_venn, eval=FALSE}
+ccle_ccls <- unique(ccle_ptmuts$Broad_ID)
+ctrp_ccls <- unique(ctrp_ptmuts$Broad_ID)
+gdsc_ccls <- unique(gdsc_ptmuts$Broad_ID)
+crispr_ccls <- unique(crispr_ptmuts$Broad_ID)
+
+futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
+venn.diagram(x = list(ccle_ccls, ctrp_ccls, gdsc_ccls, crispr_ccls),
+             filename = "./plots/manuscript/venn_ccls.png",
+             output = TRUE, imagetype = "png",
+             height = 2000, width = 2000, resolution = 500,
+             lwd = 1, cex = 1,
+             category.names = c("CCLE", "CTRP", "GDSC", "CRISPR"),
+             cat.cex = 1.4, cat.fontface = "bold", cat.default.pos = "outer",
+             # cat.dist = c(0.06, 0.06, 0.035),
+             fill = c("springgreen4", "steelblue4", "turquoise4", "darkorchid"))
+```
+
+```{r drug_venn, eval=FALSE}
+ccle_drugs <- unique(ccle_ptmuts$Drug)
+ctrp_drugs <- unique(ctrp_ptmuts$Drug)
+gdsc_drugs <- unique(gdsc_ptmuts$Drug)
+
+futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
+venn.diagram(x = list(ccle_drugs, ctrp_drugs, gdsc_drugs),
+             filename = "./plots/manuscript/venn_drugs.png",
+             output = TRUE, imagetype = "png",
+             height = 2000, width = 2000, resolution = 500,
+             lwd = 1, cex = 1.4,
+             category.names = c("CCLE", "CTRP", "GDSC"),
+             cat.cex = 1.4, cat.fontface = "bold", cat.default.pos = "outer",
+             cat.dist = c(0.06, 0.06, 0.035),
+             fill = c("palegreen3", "slategray3", "paleturquoise3"))
+```
+
+**RUN THIS IN TEH EVENING**
+```{r, eval=FALSE}
+ccle_hists <- unique(select(ccle_ptmuts, Broad_ID, Primary.Disease)) %>% count(Primary.Disease)
+ccle_hists$Perc <- ccle_hists$n / sum(ccle_hists$n) * 100
+ccle_hists$Dataset <- "CCLE"
+ctrp_hists <- unique(select(ctrp_ptmuts, Broad_ID, Primary.Disease)) %>% count(Primary.Disease)
+ctrp_hists$Perc <- ctrp_hists$n / sum(ctrp_hists$n) * 100
+ctrp_hists$Dataset <- "CTRP"
+gdsc_hists <- unique(select(gdsc_ptmuts, Broad_ID, Primary.Disease)) %>% count(Primary.Disease)
+gdsc_hists$Perc <- gdsc_hists$n / sum(gdsc_hists$n) * 100
+gdsc_hists$Dataset <- "GDSC"
+
+drug_hists <- rbind(ccle_hists, ctrp_hists, gdsc_hists)
+drug_hists$Primary.Disease <- as.character(drug_hists$Primary.Disease)
+
+ggplot(drug_hists, aes(x = Dataset, y = n, fill = Primary.Disease)) +
+  geom_bar(stat = "identity", color = "black")
+```
+
+## G2P summary heatmap
+
+```{r dg_heatmap, fig.height=6, fig.width=8}
+g2p_dg_counts <- g2p %>% count(Drug, Gene) %>% filter(!is.na(Drug), !is.na(Gene))
 g2p_dg_counts <- dcast(g2p_dg_counts, Drug ~ Gene, value.var = "n", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Drug)
@@
 
-# Wilcoxon tests (mut)
+# WILCOXON (MUT)
 
@@
 
-WilcoxonTestDF <- function(dataframe, measure_var, grouping, outfile) {
+WilcoxonTestDF <- function(dataframe, grouping, outfile) {
   require(ggpubr)
-  signif <- compare_means(Score ~ Mutation_Status, group.by = grouping, data = dataframe, method = "wilcox.test", p.adjust.method = "BH")
+  if(grouping == "Drug_Gene_Lin") {
+    # Filter out DGLs with too few samples in at least one mutation status category
+    count <- ctrp_ptmuts %>% count(Drug_Gene_Lin, Mutation_Status)
+    count2 <- count %>% count(Drug_Gene_Lin)
+    count3 <- merge(count, count2, by = "Drug_Gene_Lin", suffixes = c("_sub3", "_1mut")) %>% filter(n_1mut == 2)
+    count3$n_sub3 <- ifelse(count3$n_sub3 >= 3, TRUE, FALSE)
+    count4 <- count3 %>% filter(n_sub3) %>% count(Drug_Gene_Lin) %>% filter(n == 2)
+    dataframe <- filter(dataframe, Drug_Gene_Lin %in% unique(count4$Drug_Gene_Lin))
+    dataframe$Drug_Gene_Lin <- factor(dataframe$Drug_Gene_Lin)
+  }
+  signif <- compare_means(Score ~ Mutation_Status, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
   signif <- adj_signif(signif, alpha = 0.05)
   signif <- signif[order(signif$p),]
+  if(grouping == "Drug_Gene") {
+    signif$InG2P <- ifelse(signif$Drug_Gene %in% g2p_druggenes, "Yes", "No")
+  }
+  if(grouping == "Drug_Gene_Lin") {
+    signif$InG2P <- ifelse(signif$Drug_Gene_Lin %in% g2p_dgls, "Yes", "No")
+  }
   saveRDS(signif, outfile)
@@
 
-```{r, eval=FALSE}
-crispr_signif_gene <- WilcoxonTestDF(dataframe = crispr_g2p, grouping = "Gene", outfile = "./data_munging/rds/crispr_signif_g2p_gene.rds")
-crispr_signif_lineage <- WilcoxonTestDF(dataframe = crispr_g2p, grouping = c("Gene", "Primary.Disease"), outfile = "./data_munging/rds/crispr_signif_g2p_lineage.rds")
+```{r wilcoxon_tests, eval=FALSE}
+crispr_signif_gene <- WilcoxonTestDF(dataframe = crispr_ptmuts, grouping = "Gene", outfile = "./data_munging/rds/crispr_signif_g2p_gene.rds")
+crispr_signif_lineage <- WilcoxonTestDF(dataframe = crispr_ptmuts, grouping = c("Gene", "Primary.Disease"), outfile = "./data_munging/rds/crispr_signif_g2p_lineage.rds")
 
 ccle_signif_gene <- WilcoxonTestDF(dataframe = ccle_ptmuts, grouping = "Drug_Gene", outfile = "./data_munging/rds/ccle_signif_g2p_gene.rds")
-ccle_signif_gene$G2P_Drug_Gene <- ifelse(ccle_signif_gene$Drug_Gene %in% g2p_druggenes, TRUE, FALSE)
-ccle_signif_lineage <- WilcoxonTestDF(dataframe = filter(ccle_ptmuts, Drug_Gene_Lin %in% g2p_dgls), grouping = "Drug_Gene_Lin", outfile = "./data_munging/rds/ccle_signif_g2p_lineage.rds")
+ccle_signif_lineage <- WilcoxonTestDF(dataframe = ccle_ptmuts, grouping = "Drug_Gene_Lin", outfile = "./data_munging/rds/ccle_signif_g2p_lineage.rds")
 
 ctrp_signif_gene <- WilcoxonTestDF(dataframe = ctrp_ptmuts, grouping = "Drug_Gene", outfile = "./data_munging/rds/ctrp_signif_g2p_gene.rds")
-ctrp_signif_gene$G2P_Drug_Gene <- ifelse(ctrp_signif_gene$Drug_Gene %in% g2p_druggenes, TRUE, FALSE)
-ctrp_signif_lineage <- WilcoxonTestDF(dataframe = filter(ctrp_ptmuts, Drug_Gene_Lin %in% g2p_dgls), grouping = "Drug_Gene_Lin", outfile = "./data_munging/rds/ctrp_signif_g2p_lineage.rds")
+ctrp_signif_lineage <- WilcoxonTestDF(dataframe = ctrp_ptmuts, grouping = "Drug_Gene_Lin", outfile = "./data_munging/rds/ctrp_signif_g2p_lineage.rds")
 
 gdsc_signif_gene <- WilcoxonTestDF(dataframe = gdsc_ptmuts, grouping = "Drug_Gene", outfile = "./data_munging/rds/gdsc_signif_g2p_gene.rds")
-gdsc_signif_gene$G2P_Drug_Gene <- ifelse(gdsc_signif_gene$Drug_Gene %in% g2p_druggenes, TRUE, FALSE)
-gdsc_signif_lineage <- WilcoxonTestDF(dataframe = filter(gdsc_ptmuts, Drug_Gene_Lin %in% g2p_dgls), grouping = "Drug_Gene_Lin", outfile = "./data_munging/rds/gdsc_signif_g2p_lineage.rds")
+gdsc_signif_lineage <- WilcoxonTestDF(dataframe = gdsc_ptmuts, grouping = "Drug_Gene_Lin", outfile = "./data_munging/rds/gdsc_signif_g2p_lineage.rds")
 ```
 
-```{r}
+```{r load_wilcoxon_rds}
 crispr_signif_gene <- readRDS("./data_munging/rds/crispr_signif_g2p_gene.rds")
@@
 
-# Spearman (CN, GE)
+# SPEARMAN (CN, GE)
 
@@
 
+## Drugscreens
+
+```{r drug_spear_calc, warning=FALSE}
+g2p_druggene_tally <- g2p %>% group_by(Drug_Gene) %>% tally() %>% drop_na()
+
+# CCLE
+ccle_cor_res <- ccle_ptmuts %>% group_by(Drug_Gene) %>%summarize(
+                GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate,
+                GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value,
+                CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate,
+                CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value)
+ccle_cor_res <- merge(g2p_druggene_tally, ccle_cor_res, by = "Drug_Gene", all.y = TRUE)
+ccle_cor_res$n <- ifelse(is.na(ccle_cor_res$n), 0, ccle_cor_res$n)
+ccle_cor_res$InG2P <- ifelse(ccle_cor_res$n != 0, "Yes", "No")
+ccle_cor_res$Dataset <- "CCLE"
+
+# CTRP
+ctrp_cor_res <- ctrp_ptmuts %>% group_by(Drug_Gene) %>%summarize(
+                GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate,
+                GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value,
+                CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate,
+                CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value)
+ctrp_cor_res <- merge(g2p_druggene_tally, ctrp_cor_res, by = "Drug_Gene", all.y = TRUE)
+ctrp_cor_res$n <- ifelse(is.na(ctrp_cor_res$n), 0, ctrp_cor_res$n)
+ctrp_cor_res$InG2P <- ifelse(ctrp_cor_res$n != 0, "Yes", "No")
+ctrp_cor_res$Dataset <- "CTRP"
+
+# GDSC
+gdsc_cor_res <- gdsc_ptmuts %>% group_by(Drug_Gene) %>%summarize(
+                GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate,
+                GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value,
+                CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate,
+                CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value)
+gdsc_cor_res <- merge(g2p_druggene_tally, gdsc_cor_res, by = "Drug_Gene", all.y = TRUE)
+gdsc_cor_res$n <- ifelse(is.na(gdsc_cor_res$n), 0, gdsc_cor_res$n)
+gdsc_cor_res$InG2P <- ifelse(gdsc_cor_res$n != 0, "Yes", "No")
+gdsc_cor_res$Dataset <- "GDSC"
+
+# All
+g2p_cor <- rbind(ccle_cor_res, ctrp_cor_res, gdsc_cor_res)
+```
+
+## CRISPR
+
 Spearman correlations for gene expression and copy number:
-```{r, warning=FALSE}
+```{r crispr_spear_calc, warning=FALSE}
 crispr_spear_ge <- transform(crispr_ptmuts %>% group_by(Gene) %>% summarize(p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value, p_log10 = -log10(p), corr = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate, Metric = "Gene Expression"), Gene = reorder(Gene, corr))
@@
 
-## Plots
-
 Create CRISPR two-column, KRAS-inset plot for CN and GE:
-```{r fig.height=6, fig.width=12}
+```{r crispr_spear_plot, fig.height=6, fig.width=12}
 spearman_KRAS <- rbind(filter(crispr_ptmuts, Gene == "KRAS") %>% summarize(p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value, corr = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate, Metric = "Gene Expression"), filter(crispr_ptmuts, Gene == "KRAS") %>% summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value, corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate, Metric = "Copy Number"))
@@
 
-# DGL KS tests
+# DGL KS TESTS
 
@@
                 Spearman_Corr_CN = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate)
-    print(names(df_list)[i])
+    # print(names(df_list)[i])
 
@@
 Kolmogorov-Smirnov tests comparing DGLs that are in a G2P DGL and not.
-```{r, eval=TRUE, fig.height=6, fig.width=12}
+```{r drug_KS_tests, eval=TRUE, warning=FALSE, fig.height=6, fig.width=12}
 # g2p_corr_all <- G2PCorrTable(ccle_ptmuts_df = ccle_ptmuts, ctrp_ptmuts_df = ctrp_ptmuts, gdsc_ptmuts_df = gdsc_ptmuts)
-# saveRDS(g2p_corr_all, "./data_munging/rds/g2p_corr_all.rds")
+saveRDS(g2p_corr_all, "./data_munging/rds/g2p_corr_all.rds")
 g2p_corr_all <- readRDS("./data_munging/rds/g2p_corr_all.rds")
@@
 
-# Sandbox
+# SANDBOX
 
@@
 Filter for BRCA1/2 mutations to see if we catch non-germline mutations/CN variants:
-```{r}
+```{r brca_test, eval=FALSE}
 test <- filter(maf_df, Gene == "BRCA1" | Gene == "BRCA2")
@@
 Test filtering CRISPR data for G2P genes using function:
-```{r, eval=FALSE}
+```{r crispr_fnx_test, eval=FALSE}
 crispr_all <- read.delim("./data_munging/19Q1/gene_effect_corrected_20190305.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
@@
 
-```{r, eval=FALSE}
+```{r load_crispr_fnx_test_rds, eval=FALSE}
 crispr_fxn <- readRDS("./../htscreens_giant_files/crispr_data_19Q1_g2pgenes_fxn.rds")
@@
 Test out standardization/normalization methods on Pozdeyev data. This yields evidence that the AUC values are already normalized.
-```{r, eval=FALSE}
+```{r pozdeyev_norm_testing, eval=FALSE}
 ccle_all <- read.delim("./../htscreens_giant_files/pozdeyev_data/CCLE_drug_response_metrics.csv.gz", sep = ",")
@@
 
-```{r}
+```{r session_info}
 print(sessionInfo())

### 2019-05-03 19Q1.Rmd
update Rmd

@@
 ccl_lineage_converter <- unique(ccl_converter[, c("Broad_ID", "grouped_general_doid", "group_general_lineage_name")])
-lineage_converter <- unique(select(lineage_converter, grouped_general_doid, group_general_lineage_name))
+lineage_converter <- unique(select(ccl_lineage_converter, grouped_general_doid, group_general_lineage_name))
 ccl_histologies <- read.delim("./data_munging/ccl_histologies_metadata.csv", sep = ",", header = TRUE, row.names = 1)
@@
 
-**RUN THIS IN TEH EVENING**
-```{r, eval=FALSE}
+## Histology distributions
+
+```{r histology_dists_data, eval=FALSE}
 ccle_hists <- unique(select(ccle_ptmuts, Broad_ID, Primary.Disease)) %>% count(Primary.Disease)
@@
 gdsc_hists$Dataset <- "GDSC"
+crispr_hists <- unique(select(crispr_ptmuts, Broad_ID, Primary.Disease)) %>% count(Primary.Disease)
+crispr_hists$Perc <- crispr_hists$n / sum(crispr_hists$n) * 100
+crispr_hists$Dataset <- "CRISPR"
 
-drug_hists <- rbind(ccle_hists, ctrp_hists, gdsc_hists)
+drug_hists <- rbind(ccle_hists, ctrp_hists, gdsc_hists, crispr_hists) %>% drop_na(Primary.Disease)
+drug_hists$Dataset <- factor(drug_hists$Dataset, levels = c("CCLE", "CTRP", "GDSC", "CRISPR"))
 drug_hists$Primary.Disease <- as.character(drug_hists$Primary.Disease)
+drug_hists$Primary.Disease <- gsub(" cancer", "", drug_hists$Primary.Disease)
+# saveRDS(drug_hists, "./data_munging/rds/histology_distributions.rds")
+```
 
+```{r histology_dists, fig.height=4.5, fig.width=4}
+drug_hists <- readRDS("./data_munging/rds/histology_distributions.rds")
+png(filename = "./plots/manuscript/histology_distributions.png", width = 8, height = 9, units = "in", res = 500)
 ggplot(drug_hists, aes(x = Dataset, y = n, fill = Primary.Disease)) +
-  geom_bar(stat = "identity", color = "black")
+  geom_bar(stat = "identity", color = "black") +
+  scale_y_continuous(breaks = seq(0, 850, by = 50), labels = seq(0, 850, by = 50)) +
+  guides(fill = guide_legend(title = "Histology", ncol = 1)) +
+  labs(y = "Count")
+dev.off()
 ```
@@
 # g2p_corr_all <- G2PCorrTable(ccle_ptmuts_df = ccle_ptmuts, ctrp_ptmuts_df = ctrp_ptmuts, gdsc_ptmuts_df = gdsc_ptmuts)
-saveRDS(g2p_corr_all, "./data_munging/rds/g2p_corr_all.rds")
+# saveRDS(g2p_corr_all, "./data_munging/rds/g2p_corr_all.rds")
 g2p_corr_all <- readRDS("./data_munging/rds/g2p_corr_all.rds")

### 2019-05-03 19Q1.Rmd
added CRISPR Wilcoxon test plot code

@@
 crispr_data <- merge(crispr_muts_summ, crispr_muts, by = "Gene")
+crispr_ptmuts$Mutation_Status <- factor(crispr_ptmuts$Mutation_Status)
 ## Add Color column
@@
 crispr_data <- merge(crispr_data, ge_crispr, by = c("Gene", "Broad_ID"), all.x = TRUE)
-saveRDS(crispr_data, "./../htscreens_giant_files/crispr_data_19Q1.rds", compress = "xz")
-```
 
-```{r load_crispr_filter, eval=TRUE}
-crispr_data <- readRDS("./../htscreens_giant_files/crispr_data_19Q1.rds")
+saveRDS(crispr_data, "./data_munging/rds/crispr_data_19Q1.rds", compress = "xz")
 
@@
 crispr_ptmuts <- filter(crispr_ptmuts, Gene %in% g2p_genes)
-crispr_ptmuts$Gene <- factor(crispr_ptmuts$Gene)
 crispr_ptmuts$Primary.Disease <- factor(crispr_ptmuts$Primary.Disease)
+crispr_ptmuts$Mutation_Status <- factor(crispr_ptmuts$Mutation_Status)
+saveRDS(crispr_ptmuts, "./data_munging/rds/crispr_data_19Q1_g2pgenes_ptmuts.rds", compress = "xz")
+```
+
+```{r load_crispr_filter, eval=TRUE}
+crispr_data <- readRDS("./data_munging/rds/crispr_data_19Q1.rds")
+crispr_ptmuts <- readRDS("./data_munging/rds/crispr_data_19Q1_g2pgenes_ptmuts.rds")
 ```
@@
 ## Plots
+
+```{r crispr_mut_gene_plot, fig.height=4, fig.width=8}
+crispr_signif_gene$Gene <- factor(crispr_signif_gene$Gene, levels = g2p_genes)
+crispr_ptmuts$Gene <- factor(crispr_ptmuts$Gene, levels = g2p_genes)
+
+crispr_gene_mut_plot <- ggplot(data = crispr_ptmuts) +
+  facet_wrap(~ Gene, nrow = 2, drop = FALSE) +
+  scale_color_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "darkorchid", "0" = "thistle")) +
+  geom_jitter(aes(x = Mutation_Status, y = Score, color = Mutation_Status), width = 0.2, alpha = 0.5, size = 0.6) +
+  geom_boxplot(aes(x = Mutation_Status, y = Score), fill = "transparent", outlier.shape = NA, lwd = 0.3) +
+  geom_text(data = crispr_signif_gene, aes(x = 1.5, y = 1.75, label = p.signif.adj)) +
+  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
+  theme(legend.position = "top", legend.direction = "horizontal") +
+  guides(color = guide_legend(override.aes = list(size = 3))) +
+  labs(y = "CERES Score")
+crispr_gene_mut_plot
+
+# ggsave("./plots/manuscript/crispr_gene_mut_plot.png", crispr_gene_mut_plot, width = 12, height = 6, units = "in")
+```
+
+```{r crispr_mut_lin_plot, fig.height=12, fig.width=8}
+crispr_signif_lineage$Gene <- factor(crispr_signif_lineage$Gene, levels = g2p_genes)
+
+crispr_gene_lin_plot <- ggplot(data = crispr_ptmuts) +
+  facet_wrap(~ Primary.Disease, nrow = 7, scales = "free_x") +
+  scale_color_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "darkorchid", "0" = "thistle")) +
+  geom_point(aes(x = Gene, y = Score, color = Mutation_Status), alpha = 0.5, size = 0.6) +
+  geom_text(data = crispr_signif_lineage, aes(x = Gene, y = 1.75, label = p.signif.adj)) +
+  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
+  theme(legend.position = "top", legend.direction = "horizontal", axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 10)) +
+  guides(color = guide_legend(override.aes = list(size = 3))) +
+  ylab("CERES Score") +
+  scale_x_discrete(name = "Mutation Status", labels = c("0" = "WT", "1" = "Mut"))
+crispr_gene_lin_plot
+
+# ggsave("./plots/manuscript/crispr_gene_lineage_plot.png", crispr_gene_lin_plot, width = 16, height = 20, units = "in")
+```
 

### 2019-05-03 19Q1.Rmd

@@
 
-```{r dg_heatmap, fig.height=6, fig.width=8}
+```{r dg_heatmap, fig.height=6, fig.width=8, warning=FALSE}
 g2p_dg_counts <- g2p %>% count(Drug, Gene) %>% filter(!is.na(Drug), !is.na(Gene))
@@
 g2p_dg_counts[g2p_dg_counts == 0] <- NA
+
+g2p_gene_order <- colnames(g2p_dg_counts)
+g2p_drug_order <- rownames(g2p_dg_counts)
 
@@
               column_names_gp = gpar(fontsize = 10),
+              show_column_names = FALSE,
+              bottom_annotation = HeatmapAnnotation(
+                  text = anno_text(colnames(g2p_dg_counts),
+                                   rot = 45,
+                                   gp = gpar(fontsize = 10),
+                                   offset = unit(1, "npc"),
+                                   just = "right"),
+                  annotation_height = unit(0.45, "in")),
               row_title = "Drugs",
@@
 
-# png(filename = "./plots/manuscript/g2p_summary_heatmap.png", width = 12, height = 10, units = "in", res = 500)
+# png(filename = "./plots/manuscript/g2p_summary_heatmap.png", width = 10, height = 9, units = "in", res = 500)
 draw(hta + ht, gap = unit(5, "mm"), heatmap_legend_side = "top")
@@
 ccle_signif_gene <- WilcoxonTestDF(dataframe = ccle_ptmuts, grouping = "Drug_Gene", outfile = "./data_munging/rds/ccle_signif_g2p_gene.rds")
+ccle_signif_g2p_druggene <- WilcoxonTestDF(dataframe = filter(ccle_ptmuts, Drug %in% g2p_drugs & Gene %in% g2p_genes), grouping = "Drug_Gene", outfile = "./data_munging/rds/ccle_signif_g2p_druggene.rds")
 ccle_signif_lineage <- WilcoxonTestDF(dataframe = ccle_ptmuts, grouping = "Drug_Gene_Lin", outfile = "./data_munging/rds/ccle_signif_g2p_lineage.rds")
@@
 ctrp_signif_gene <- WilcoxonTestDF(dataframe = ctrp_ptmuts, grouping = "Drug_Gene", outfile = "./data_munging/rds/ctrp_signif_g2p_gene.rds")
+ctrp_signif_g2p_druggene <- WilcoxonTestDF(dataframe = filter(ctrp_ptmuts, Drug %in% g2p_drugs & Gene %in% g2p_genes), grouping = "Drug_Gene", outfile = "./data_munging/rds/ctrp_signif_g2p_druggene.rds")
 ctrp_signif_lineage <- WilcoxonTestDF(dataframe = ctrp_ptmuts, grouping = "Drug_Gene_Lin", outfile = "./data_munging/rds/ctrp_signif_g2p_lineage.rds")
@@
 gdsc_signif_gene <- WilcoxonTestDF(dataframe = gdsc_ptmuts, grouping = "Drug_Gene", outfile = "./data_munging/rds/gdsc_signif_g2p_gene.rds")
+gdsc_signif_g2p_druggene <- WilcoxonTestDF(dataframe = filter(gdsc_ptmuts, Drug %in% g2p_drugs & Gene %in% g2p_genes), grouping = "Drug_Gene", outfile = "./data_munging/rds/gdsc_signif_g2p_druggene.rds")
 gdsc_signif_lineage <- WilcoxonTestDF(dataframe = gdsc_ptmuts, grouping = "Drug_Gene_Lin", outfile = "./data_munging/rds/gdsc_signif_g2p_lineage.rds")
@@
 crispr_signif_lineage <- readRDS("./data_munging/rds/crispr_signif_g2p_lineage.rds")
+
 ccle_signif_gene <- readRDS("./data_munging/rds/ccle_signif_g2p_gene.rds")
+ccle_signif_g2p_druggene <- readRDS("./data_munging/rds/ccle_signif_g2p_druggene.rds")
 ccle_signif_lineage <- readRDS("./data_munging/rds/ccle_signif_g2p_lineage.rds")
+
 ctrp_signif_gene <- readRDS("./data_munging/rds/ctrp_signif_g2p_gene.rds")
+ctrp_signif_g2p_druggene <- readRDS("./data_munging/rds/ctrp_signif_g2p_druggene.rds")
 ctrp_signif_lineage <- readRDS("./data_munging/rds/ctrp_signif_g2p_lineage.rds")
+
 gdsc_signif_gene <- readRDS("./data_munging/rds/gdsc_signif_g2p_gene.rds")
+gdsc_signif_g2p_druggene <- readRDS("./data_munging/rds/gdsc_signif_g2p_druggene.rds")
 gdsc_signif_lineage <- readRDS("./data_munging/rds/gdsc_signif_g2p_lineage.rds")
@@
 # ggsave("./plots/manuscript/crispr_gene_lineage_plot.png", crispr_gene_lin_plot, width = 16, height = 20, units = "in")
+```
+
+```{r heatmap_function}
+MakeMutHeatmap <- function(signif_g2p_druggene, row_names, col_title, color, legend_title) {
+  signif_g2p_druggene$Drug <- sapply(strsplit(signif_g2p_druggene$Drug_Gene, "_", fixed = TRUE), function(x) x[1])
+  signif_g2p_druggene$Gene <- sapply(strsplit(signif_g2p_druggene$Drug_Gene, "_", fixed = TRUE), function(x) x[2])
+
+  signif_grid <- dcast(signif_g2p_druggene, Gene ~ Drug, value.var = "p", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
+  signif_grid <- signif_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
+  signif_grid <- signif_grid[complete.cases(signif_grid), ]
+  signif_grid[signif_grid > 0.05] <- NA
+
+  signif_grid_annot <- dcast(signif_g2p_druggene, Gene ~ Drug, value.var = "InG2P", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
+  signif_grid_annot <- signif_grid_annot[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
+  signif_grid_annot <- signif_grid_annot[complete.cases(signif_grid_annot), ]
+  signif_grid_annot[signif_grid_annot == "No"] <- ""
+  signif_grid_annot[signif_grid_annot == "Yes"] <- "*"
+
+  col_fun <- colorRamp2(c(0, 0.05), c(color, "gray97"))
+  # Legend properties list
+  ht_legend_list <- list(title = legend_title, title_position = "topleft", legend_direction = "horizontal", legend_width = unit(2, "in"), border = "gray70",   at = seq(0, 0.05, by = 0.01), labels = seq(0, 0.05, by = 0.01))
+  ht <- Heatmap(signif_grid,
+                col = col_fun,
+                na_col = "gray97",
+                rect_gp = gpar(col = "gray70"),
+                heatmap_legend_param = ht_legend_list,
+                cluster_rows = FALSE, 
+                cluster_columns = FALSE, 
+                show_row_names = as.logical(row_names),
+                row_names_side = "left",
+                row_names_gp = gpar(fontsize = 10),
+                column_names_side = "bottom",
+                column_names_gp = gpar(fontsize = 10),
+                show_column_names = FALSE,
+                bottom_annotation = HeatmapAnnotation(
+                  text = anno_text(colnames(signif_grid),
+                                   rot = 45,
+                                   gp = gpar(fontsize = 11),
+                                   offset = unit(1, "npc"),
+                                   just = "right"),
+                  annotation_height = unit(0.85, "in")),
+                  # annotation_height = max_text_width(colnames(signif_grid))),
+                row_title = "Genes",
+                row_title_gp = gpar(fontface = "bold", fontsize = 14),
+                column_title = col_title, 
+                column_title_gp = gpar(fontface = "bold", fontsize = 14),
+                column_title_side = "bottom",
+                cell_fun = function(j, i, x, y, width, height, fill) { grid.text(signif_grid_annot[i, j], x, y, gp = gpar(fontsize = 20)) })
+  return(ht)
+}
+```
+
+```{r mut_heatmaps, eval=FALSE}
+ht_ccle <- MakeMutHeatmap(signif_g2p_druggene = ccle_signif_g2p_druggene, legend_title = "P-value", row_names = TRUE, color = "darkgreen", col_title = "Drugs")
+png(filename = "./plots/manuscript/ccle_mut_heatmap.png", width = 3, height = 10, units = "in", res = 500)
+draw(ht_ccle, heatmap_legend_side = "top")
+dev.off()
+
+ht_ctrp <- MakeMutHeatmap(signif_g2p_druggene = ctrp_signif_g2p_druggene, legend_title = "P-value", row_names = TRUE, color = "steelblue4", col_title = "Drugs")
+png(filename = "./plots/manuscript/ctrp_mut_heatmap.png", width = 9.5, height = 10, units = "in", res = 500)
+draw(ht_ctrp, heatmap_legend_side = "top")
+dev.off()
+
+ht_gdsc <- MakeMutHeatmap(signif_g2p_druggene = gdsc_signif_g2p_druggene, legend_title = "P-value", row_names = TRUE, color = "turquoise4", col_title = "Drugs")
+png(filename = "./plots/manuscript/gdsc_mut_heatmap.png", width = 5, height = 10, units = "in", res = 500)
+draw(ht_gdsc, heatmap_legend_side = "top")
+dev.off()
+
+ht_ccle2 <- MakeMutHeatmap(signif_g2p_druggene = ccle_signif_g2p_druggene, legend_title = "CCLE p-value                                                                               ", row_names = TRUE, color = "darkgreen", col_title = "")
+ht_ctrp2 <- MakeMutHeatmap(signif_g2p_druggene = ctrp_signif_g2p_druggene, legend_title = "CTRP p-value                                                                              ", row_names = FALSE, color = "steelblue4", col_title = "Drugs")
+ht_gdsc2 <- MakeMutHeatmap(signif_g2p_druggene = gdsc_signif_g2p_druggene, legend_title = "GDSC p-value", row_names = FALSE, color = "turquoise4", col_title = "")
+png(filename = "./plots/manuscript/drug_mut_heatmap.png", width = 13, height = 10, units = "in", res = 500)
+draw(ht_ccle2 + ht_ctrp2 + ht_gdsc2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
+dev.off()
 ```

### 2019-05-06 19Q1.Rmd

@@
   require(ggpubr)
-  if(grouping == "Drug_Gene_Lin") {
+  if("Drug_Gene_Lin" %in% grouping) {
     # Filter out DGLs with too few samples in at least one mutation status category
-    count <- ctrp_ptmuts %>% count(Drug_Gene_Lin, Mutation_Status)
-    count2 <- count %>% count(Drug_Gene_Lin)
-    count3 <- merge(count, count2, by = "Drug_Gene_Lin", suffixes = c("_sub3", "_1mut")) %>% filter(n_1mut == 2)
-    count3$n_sub3 <- ifelse(count3$n_sub3 >= 3, TRUE, FALSE)
-    count4 <- count3 %>% filter(n_sub3) %>% count(Drug_Gene_Lin) %>% filter(n == 2)
-    dataframe <- filter(dataframe, Drug_Gene_Lin %in% unique(count4$Drug_Gene_Lin))
-    dataframe$Drug_Gene_Lin <- factor(dataframe$Drug_Gene_Lin)
+    count_mut_n <- dataframe %>% count(Drug_Gene_Lin, Mutation_Status) %>% filter(n >= 3)
+    count_mut_category <- count_mut_n %>% count(Drug_Gene_Lin) %>% filter(n == 2)
+    dgl_keep <- intersect(count_mut_n$Drug_Gene_Lin, count_mut_category$Drug_Gene_Lin)
+    dataframe <- filter(dataframe, Drug_Gene_Lin %in% dgl_keep)
+    dataframe$Drug_Gene_Lin <- as.character(dataframe$Drug_Gene_Lin)
   }
@@
   signif <- signif[order(signif$p),]
-  if(grouping == "Drug_Gene") {
+  if("Drug_Gene" %in% grouping) {
     signif$InG2P <- ifelse(signif$Drug_Gene %in% g2p_druggenes, "Yes", "No")
   }
-  if(grouping == "Drug_Gene_Lin") {
+  if("Drug_Gene_Lin" %in% grouping) {
     signif$InG2P <- ifelse(signif$Drug_Gene_Lin %in% g2p_dgls, "Yes", "No")
@@
 ```{r wilcoxon_tests, eval=FALSE}
+crispr_ptmuts <- unfactorize(crispr_ptmuts)
 crispr_signif_gene <- WilcoxonTestDF(dataframe = crispr_ptmuts, grouping = "Gene", outfile = "./data_munging/rds/crispr_signif_g2p_gene.rds")
@@
 
-ccle_signif_gene <- WilcoxonTestDF(dataframe = ccle_ptmuts, grouping = "Drug_Gene", outfile = "./data_munging/rds/ccle_signif_g2p_gene.rds")
-ccle_signif_g2p_druggene <- WilcoxonTestDF(dataframe = filter(ccle_ptmuts, Drug %in% g2p_drugs & Gene %in% g2p_genes), grouping = "Drug_Gene", outfile = "./data_munging/rds/ccle_signif_g2p_druggene.rds")
-ccle_signif_lineage <- WilcoxonTestDF(dataframe = ccle_ptmuts, grouping = "Drug_Gene_Lin", outfile = "./data_munging/rds/ccle_signif_g2p_lineage.rds")
-
-ctrp_signif_gene <- WilcoxonTestDF(dataframe = ctrp_ptmuts, grouping = "Drug_Gene", outfile = "./data_munging/rds/ctrp_signif_g2p_gene.rds")
-ctrp_signif_g2p_druggene <- WilcoxonTestDF(dataframe = filter(ctrp_ptmuts, Drug %in% g2p_drugs & Gene %in% g2p_genes), grouping = "Drug_Gene", outfile = "./data_munging/rds/ctrp_signif_g2p_druggene.rds")
-ctrp_signif_lineage <- WilcoxonTestDF(dataframe = ctrp_ptmuts, grouping = "Drug_Gene_Lin", outfile = "./data_munging/rds/ctrp_signif_g2p_lineage.rds")
-
-gdsc_signif_gene <- WilcoxonTestDF(dataframe = gdsc_ptmuts, grouping = "Drug_Gene", outfile = "./data_munging/rds/gdsc_signif_g2p_gene.rds")
-gdsc_signif_g2p_druggene <- WilcoxonTestDF(dataframe = filter(gdsc_ptmuts, Drug %in% g2p_drugs & Gene %in% g2p_genes), grouping = "Drug_Gene", outfile = "./data_munging/rds/gdsc_signif_g2p_druggene.rds")
-gdsc_signif_lineage <- WilcoxonTestDF(dataframe = gdsc_ptmuts, grouping = "Drug_Gene_Lin", outfile = "./data_munging/rds/gdsc_signif_g2p_lineage.rds")
+ccle_ptmuts_filt <- filter(ccle_ptmuts, Drug %in% g2p_drugs)
+ccle_ptmuts_filt$Gene <- factor(ccle_ptmuts_filt$Gene, ordered = FALSE)
+ccle_ptmuts_filt <- unfactorize(ccle_ptmuts_filt)
+ccle_signif_gene <- WilcoxonTestDF(dataframe = ccle_ptmuts, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/ccle_signif_g2p_gene.rds")
+ccle_signif_g2p_druggene <- WilcoxonTestDF(dataframe = filter(ccle_ptmuts, Drug %in% g2p_drugs & Gene %in% g2p_genes), grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/ccle_signif_g2p_druggene.rds")
+ccle_signif_lineage <- WilcoxonTestDF(dataframe = ccle_ptmuts_filt, grouping = c("Drug", "Gene", "Primary.Disease", "Drug_Gene_Lin"), outfile = "./data_munging/rds/ccle_signif_g2p_lineage.rds")
+
+ctrp_ptmuts_filt <- filter(ctrp_ptmuts, Drug %in% g2p_drugs)
+ctrp_ptmuts_filt$Gene <- factor(ctrp_ptmuts_filt$Gene, ordered = FALSE)
+ctrp_ptmuts_filt <- unfactorize(ctrp_ptmuts_filt)
+ctrp_signif_gene <- WilcoxonTestDF(dataframe = ctrp_ptmuts, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/ctrp_signif_g2p_gene.rds")
+ctrp_signif_g2p_druggene <- WilcoxonTestDF(dataframe = filter(ctrp_ptmuts, Drug %in% g2p_drugs & Gene %in% g2p_genes), grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/ctrp_signif_g2p_druggene.rds")
+ctrp_signif_lineage <- WilcoxonTestDF(dataframe = ctrp_ptmuts_filt, grouping = c("Drug", "Gene", "Primary.Disease", "Drug_Gene_Lin"), outfile = "./data_munging/rds/ctrp_signif_g2p_lineage.rds")
+
+gdsc_ptmuts_filt <- filter(gdsc_ptmuts, Drug %in% g2p_drugs)
+gdsc_ptmuts_filt$Gene <- factor(gdsc_ptmuts_filt$Gene, ordered = FALSE)
+gdsc_ptmuts_filt <- unfactorize(gdsc_ptmuts_filt)
+gdsc_signif_gene <- WilcoxonTestDF(dataframe = gdsc_ptmuts, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/gdsc_signif_g2p_gene.rds")
+gdsc_signsif_g2p_druggene <- WilcoxonTestDF(dataframe = filter(gdsc_ptmuts, Drug %in% g2p_drugs & Gene %in% g2p_genes), grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/gdsc_signif_g2p_druggene.rds")
+gdsc_signif_lineage <- WilcoxonTestDF(dataframe = gdsc_ptmuts_filt, grouping = c("Drug", "Gene", "Primary.Disease", "Drug_Gene_Lin"), outfile = "./data_munging/rds/gdsc_signif_g2p_lineage.rds")
 ```
@@
   scale_color_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "darkorchid", "0" = "thistle")) +
+  scale_x_discrete(name = "Mutation Status", labels = c("0" = "WT", "1" = "Mut")) +
   geom_jitter(aes(x = Mutation_Status, y = Score, color = Mutation_Status), width = 0.2, alpha = 0.5, size = 0.6) +
@@
   labs(y = "CERES Score")
-crispr_gene_mut_plot
+# crispr_gene_mut_plot
 
@@
 
-```{r heatmap_function}
+```{r mut_heatmap_function}
 MakeMutHeatmap <- function(signif_g2p_druggene, row_names, col_title, color, legend_title) {
-  signif_g2p_druggene$Drug <- sapply(strsplit(signif_g2p_druggene$Drug_Gene, "_", fixed = TRUE), function(x) x[1])
-  signif_g2p_druggene$Gene <- sapply(strsplit(signif_g2p_druggene$Drug_Gene, "_", fixed = TRUE), function(x) x[2])
+  # signif_g2p_druggene$Drug <- sapply(strsplit(signif_g2p_druggene$Drug_Gene, "_", fixed = TRUE), function(x) x[1])
+  # signif_g2p_druggene$Gene <- sapply(strsplit(signif_g2p_druggene$Drug_Gene, "_", fixed = TRUE), function(x) x[2])
 
@@
 
-## Drugscreens
-
 ```{r drug_spear_calc, warning=FALSE}
@@
 # CCLE
-ccle_cor_res <- ccle_ptmuts %>% group_by(Drug_Gene) %>%summarize(
+ccle_cor_res <- ccle_ptmuts %>% group_by(Drug, Gene, Drug_Gene) %>% summarize(
                 GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate,
@@
 # CTRP
-ctrp_cor_res <- ctrp_ptmuts %>% group_by(Drug_Gene) %>%summarize(
+ctrp_cor_res <- ctrp_ptmuts %>% group_by(Drug, Gene, Drug_Gene) %>% summarize(
                 GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate,
@@
 # GDSC
-gdsc_cor_res <- gdsc_ptmuts %>% group_by(Drug_Gene) %>%summarize(
+gdsc_cor_res <- gdsc_ptmuts %>% group_by(Drug, Gene, Drug_Gene) %>% summarize(
                 GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate,
@@
 g2p_cor <- rbind(ccle_cor_res, ctrp_cor_res, gdsc_cor_res)
-```
-
-## CRISPR
+
+saveRDS(g2p_cor, "./data_munging/rds/drug_cor.rds")
+```
+
+```{r load_drug_spear}
+g2p_cor <- readRDS("./data_munging/rds/drug_cor.rds")
+```
 
@@
 ```
+
+## Plots
 
@@
 
+```{r corr_heatmap_function}
+MakeCorrHeatmap <- function(drug_cor_res, row_names, col_title, color, legend_title) {
+  # drug_cor_res$Drug <- sapply(strsplit(signif_g2p_druggene$Drug_Gene, "_", fixed = TRUE), function(x) x[1])
+  # drug_cor_res$Gene <- sapply(strsplit(signif_g2p_druggene$Drug_Gene, "_", fixed = TRUE), function(x) x[2])
+
+  signif_grid <- dcast(signif_g2p_druggene, Gene ~ Drug, value.var = "p", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
+  signif_grid <- signif_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
+  signif_grid <- signif_grid[complete.cases(signif_grid), ]
+  signif_grid[signif_grid > 0.05] <- NA
+
+  # signif_grid_annot <- dcast(signif_g2p_druggene, Gene ~ Drug, value.var = "InG2P", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
+  # signif_grid_annot <- signif_grid_annot[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
+  # signif_grid_annot <- signif_grid_annot[complete.cases(signif_grid_annot), ]
+  # signif_grid_annot[signif_grid_annot == "No"] <- ""
+  # signif_grid_annot[signif_grid_annot == "Yes"] <- "*"
+
+  col_fun <- colorRamp2(c(0, 0.05), c(color, "gray97"))
+  # Legend properties list
+  ht_legend_list <- list(title = legend_title, title_position = "topleft", legend_direction = "horizontal", legend_width = unit(2, "in"), border = "gray70",   at = seq(0, 0.05, by = 0.01), labels = seq(0, 0.05, by = 0.01))
+  ht <- Heatmap(signif_grid,
+                col = col_fun,
+                na_col = "gray97",
+                rect_gp = gpar(col = "gray70"),
+                heatmap_legend_param = ht_legend_list,
+                cluster_rows = FALSE, 
+                cluster_columns = FALSE, 
+                show_row_names = as.logical(row_names),
+                row_names_side = "left",
+                row_names_gp = gpar(fontsize = 10),
+                column_names_side = "bottom",
+                column_names_gp = gpar(fontsize = 10),
+                show_column_names = FALSE,
+                bottom_annotation = HeatmapAnnotation(
+                  text = anno_text(colnames(signif_grid),
+                                   rot = 45,
+                                   gp = gpar(fontsize = 11),
+                                   offset = unit(1, "npc"),
+                                   just = "right"),
+                  annotation_height = unit(0.85, "in")),
+                  # annotation_height = max_text_width(colnames(signif_grid))),
+                row_title = "Genes",
+                row_title_gp = gpar(fontface = "bold", fontsize = 14),
+                column_title = col_title, 
+                column_title_gp = gpar(fontface = "bold", fontsize = 14),
+                column_title_side = "bottom",
+                # cell_fun = function(j, i, x, y, width, height, fill) { grid.text(signif_grid_annot[i, j], x, y, gp = gpar(fontsize = 20)) }
+                )
+  return(ht)
+}
+```
+
+```{r drug_spear_plot}
+
+```
+
 # DGL KS TESTS
@@
 # g2p_corr_all <- G2PCorrTable(ccle_ptmuts_df = ccle_ptmuts, ctrp_ptmuts_df = ctrp_ptmuts, gdsc_ptmuts_df = gdsc_ptmuts)
-# saveRDS(g2p_corr_all, "./data_munging/rds/g2p_corr_all.rds")
-g2p_corr_all <- readRDS("./data_munging/rds/g2p_corr_all.rds")
+# saveRDS(g2p_corr_all, "./data_munging/rds/g2p_dgl_corr.rds")
+g2p_corr_all <- readRDS("./data_munging/rds/g2p_dgl_corr.rds")
 g2p_mut_stats <- G2PCorrStatsTables(corr_df = g2p_corr_all, table_type = "mutation")

### 2019-05-07 19Q1.Rmd
create drugscreen CN and GE heatmaps

@@
 
-```{r drug_spear_calc, warning=FALSE}
+```{r drug_spear_calc, warning=FALSE, eval=FALSE}
 g2p_druggene_tally <- g2p %>% group_by(Drug_Gene) %>% tally() %>% drop_na()
@@
 ```{r corr_heatmap_function}
-MakeCorrHeatmap <- function(drug_cor_res, row_names, col_title, color, legend_title) {
+MakeCorrHeatmap <- function(drug_cor_res, row_names, col_title, color_range, legend_title, metric) {
   # drug_cor_res$Drug <- sapply(strsplit(signif_g2p_druggene$Drug_Gene, "_", fixed = TRUE), function(x) x[1])
   # drug_cor_res$Gene <- sapply(strsplit(signif_g2p_druggene$Drug_Gene, "_", fixed = TRUE), function(x) x[2])
-
-  signif_grid <- dcast(signif_g2p_druggene, Gene ~ Drug, value.var = "p", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
+  if(toupper(metric) == "CN" | toupper(metric) == "COPY NUMBER") {
+    signif_grid <- dcast(drug_cor_res, Gene ~ Drug, value.var = "CN_p", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
     signif_grid <- signif_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
     signif_grid <- signif_grid[complete.cases(signif_grid), ]
-  signif_grid[signif_grid > 0.05] <- NA
-
-  # signif_grid_annot <- dcast(signif_g2p_druggene, Gene ~ Drug, value.var = "InG2P", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
-  # signif_grid_annot <- signif_grid_annot[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
-  # signif_grid_annot <- signif_grid_annot[complete.cases(signif_grid_annot), ]
-  # signif_grid_annot[signif_grid_annot == "No"] <- ""
-  # signif_grid_annot[signif_grid_annot == "Yes"] <- "*"
-
-  col_fun <- colorRamp2(c(0, 0.05), c(color, "gray97"))
+    signif_grid[signif_grid >= 0.05] <- ""
+    signif_grid[signif_grid != ""] <- "*"
+
+    corr_grid <- dcast(drug_cor_res, Gene ~ Drug, value.var = "CN_r", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
+    corr_grid <- corr_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(corr_grid))]
+    corr_grid <- corr_grid[complete.cases(corr_grid), ]
+  }
+
+  if(toupper(metric) == "GE" | toupper(metric) == "GENE EXPRESSION") {
+    signif_grid <- dcast(drug_cor_res, Gene ~ Drug, value.var = "GE_p", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
+    signif_grid <- signif_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
+    signif_grid <- signif_grid[complete.cases(signif_grid), ]
+    signif_grid[signif_grid >= 0.05] <- ""
+    signif_grid[signif_grid != ""] <- "*"
+
+    corr_grid <- dcast(drug_cor_res, Gene ~ Drug, value.var = "GE_r", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
+    corr_grid <- corr_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(corr_grid))]
+    corr_grid <- corr_grid[complete.cases(corr_grid), ]
+  }
+
+  annot_grid <- dcast(drug_cor_res, Gene ~ Drug, value.var = "InG2P", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
+  annot_grid <- annot_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
+  annot_grid <- annot_grid[complete.cases(annot_grid), ]
+  annot_grid[annot_grid == "No"] <- ""
+  annot_grid[annot_grid == "Yes"] <- "*"
+
+  col_fun <- colorRamp2(color_range, c("red3", "white", "green4"))
+
   # Legend properties list
-  ht_legend_list <- list(title = legend_title, title_position = "topleft", legend_direction = "horizontal", legend_width = unit(2, "in"), border = "gray70",   at = seq(0, 0.05, by = 0.01), labels = seq(0, 0.05, by = 0.01))
-  ht <- Heatmap(signif_grid,
+  ht_legend_list <- list(title_position = "topleft", legend_direction = "horizontal", legend_width = unit(2, "in"), border = "gray70", at = seq(color_range[1], color_range[3], by = 0.2), labels = seq(color_range[1], color_range[3], by = 0.2))
+  ht <- Heatmap(corr_grid,
                 col = col_fun,
+                name = legend_title,
                 na_col = "gray97",
@@
                 column_title_gp = gpar(fontface = "bold", fontsize = 14),
-                column_title_side = "bottom",
-                # cell_fun = function(j, i, x, y, width, height, fill) { grid.text(signif_grid_annot[i, j], x, y, gp = gpar(fontsize = 20)) }
+                column_title_side = "top",
+                cell_fun = function(j, i, x, y, width, height, fill) { grid.text(signif_grid[i, j], x, y, gp = gpar(fontsize = 20)) }
                 )
@@
 
-```{r drug_spear_plot}
-
+```{r drug_spear_plots, eval=FALSE}
+# Copy number
+ccle_cor <- unfactorize(filter(g2p_cor, Dataset == "CCLE"))
+ccle_cn_ht <- MakeCorrHeatmap(drug_cor_res = ccle_cor, row_names = TRUE, col_title = "CCLE", color_range = c(-0.25, 0, 0.25), legend_title = "CCLE Spearman correlation", metric = "CN")
+png(filename = "./plots/manuscript/ccle_cn_heatmap.png", width = 3, height = 10, units = "in", res = 500)
+draw(ccle_cn_ht, heatmap_legend_side = "top")
+dev.off()
+
+ctrp_cor <- unfactorize(filter(g2p_cor, Dataset == "CTRP"))
+ctrp_cn_ht <- MakeCorrHeatmap(drug_cor_res = ctrp_cor, row_names = TRUE, col_title = "CTRP", color_range = c(-0.35, 0, 0.35), legend_title = "CTRP Spearman correlation", metric = "CN")
+png(filename = "./plots/manuscript/ctrp_cn_heatmap.png", width = 9.5, height = 10, units = "in", res = 500)
+draw(ctrp_cn_ht, heatmap_legend_side = "top")
+dev.off()
+
+gdsc_cor <- unfactorize(filter(g2p_cor, Dataset == "GDSC"))
+gdsc_cn_ht <- MakeCorrHeatmap(drug_cor_res = gdsc_cor, row_names = TRUE, col_title = "GDSC", color_range = c(-0.25, 0, 0.25), legend_title = "GDSC Spearman correlation", metric = "CN")
+png(filename = "./plots/manuscript/gdsc_cn_heatmap.png", width = 5, height = 10, units = "in", res = 500)
+draw(gdsc_cn_ht, heatmap_legend_side = "top")
+dev.off()
+
+ccle_cn_ht2 <- MakeCorrHeatmap(drug_cor_res = ccle_cor, row_names = TRUE, col_title = "CCLE", color_range = c(-0.35, 0, 0.35), legend_title = "Copy num. Spearman correlation", metric = "CN")
+ctrp_cn_ht2 <- MakeCorrHeatmap(drug_cor_res = ctrp_cor, row_names = FALSE, col_title = "CTRP", color_range = c(-0.35, 0, 0.35), legend_title = "Copy num. Spearman correlation", metric = "CN")
+gdsc_cn_ht2 <- MakeCorrHeatmap(drug_cor_res = gdsc_cor, row_names = FALSE, col_title = "GDSC", color_range = c(-0.35, 0, 0.35), legend_title = "Copy num. Spearman correlation", metric = "CN")
+png(filename = "./plots/manuscript/drug_cn_heatmap.png", width = 13, height = 10, units = "in", res = 500)
+draw(ccle_cn_ht2 + ctrp_cn_ht2 + gdsc_cn_ht2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
+dev.off()
+
+# Gene expression
+ccle_ge_ht <- MakeCorrHeatmap(drug_cor_res = ccle_cor, row_names = TRUE, col_title = "CCLE", color_range = c(-0.5, 0, 0.5), legend_title = "CCLE Spearman correlation", metric = "GE")
+png(filename = "./plots/manuscript/ccle_ge_heatmap.png", width = 3, height = 10, units = "in", res = 500)
+draw(ccle_ge_ht, heatmap_legend_side = "top")
+dev.off()
+
+ctrp_ge_ht <- MakeCorrHeatmap(drug_cor_res = ctrp_cor, row_names = TRUE, col_title = "CTRP", color_range = c(-0.5, 0, 0.5), legend_title = "CTRP Spearman correlation", metric = "GE")
+png(filename = "./plots/manuscript/ctrp_ge_heatmap.png", width = 9.5, height = 10, units = "in", res = 500)
+draw(ctrp_ge_ht, heatmap_legend_side = "top")
+dev.off()
+
+gdsc_ge_ht <- MakeCorrHeatmap(drug_cor_res = gdsc_cor, row_names = TRUE, col_title = "GDSC", color_range = c(-0.5, 0, 0.5), legend_title = "GDSC Spearman correlation", metric = "GE")
+png(filename = "./plots/manuscript/gdsc_ge_heatmap.png", width = 5, height = 10, units = "in", res = 500)
+draw(gdsc_ge_ht, heatmap_legend_side = "top")
+dev.off()
+
+ccle_ge_ht2 <- MakeCorrHeatmap(drug_cor_res = ccle_cor, row_names = TRUE, col_title = "CCLE", color_range = c(-0.5, 0, 0.5), legend_title = "Gene expr. Spearman correlation", metric = "GE")
+ctrp_ge_ht2 <- MakeCorrHeatmap(druwg_cor_res = ctrp_cor, row_names = FALSE, col_title = "CTRP", color_range = c(-0.5, 0, 0.5), legend_title = "Gene expr. Spearman correlation", metric = "GE")
+gdsc_ge_ht2 <- MakeCorrHeatmap(drug_cor_res = gdsc_cor, row_names = FALSE, col_title = "GDSC", color_range = c(-0.5, 0, 0.5), legend_title = "Gene expr. Spearman correlation", metric = "GE")
+png(filename = "./plots/manuscript/drug_ge_heatmap.png", width = 13, height = 10, units = "in", res = 500)
+draw(ccle_ge_ht2 + ctrp_ge_ht2 + gdsc_ge_ht2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
+dev.off()
 ```

### 2019-05-08 19Q1.Rmd
updated Rmd

@@
 maf_df$PointMutation <- with(maf_df, ifelse(Reference_Allele == 1 | is.na(Reference_Allele), TRUE, ifelse(Reference_Allele == 0 & Tumor_Seq_Allele1 == 1, 1, 0)))
+maf_df <- unfactorize(maf_df)
 
@@
 cn_melt <- melt(data = cn, id.vars = "Broad_ID", measure.vars = colnames(cn[2:ncol(cn)]), variable.name = "Gene", value.name = "CN")
+cn_melt <- unfactorize(cn_melt)
 
@@
 # Remove Entrez gene IDs from colnames, format is "Gene (Entrez ID)"
-colnames(ge) <- gsub(" .*", "", colnames(ge_19Q1))
+colnames(ge) <- gsub(" .*", "", colnames(ge))
 colnames(ge)[1] <- "Broad_ID"
 # Melt
-ge_melt <- melt(ge, id.vars = "Broad_ID", measure.vars = colnames(ge_19Q1)[2:ncol(ge_19Q1)], variable.name = "Gene", value.name = "TPM")
+ge_melt <- melt(ge, id.vars = "Broad_ID", measure.vars = colnames(ge)[2:ncol(ge)], variable.name = "Gene", value.name = "TPM")
+ge_melt$TPM <- log2(ge_melt$TPM + 1)
+ge_melt <- unfactorize(ge_melt)
 
@@
     # Merge metadata
-    data <-  merge(data, select(ccl_meta, Cell_line, Histology, CCLE_Name, Broad_ID, Primary.Disease), by = c("Cell_line", "Histology", "CCLE_Name", "Broad_ID"), all.x = TRUE)
+    data <-  merge(data, select(ccl_meta, Cell_line, Histology, CCLE_Name, Broad_ID, Primary.Disease), by = c("Cell_line", "Histology", "CCLE_Name", "Broad_ID"), all.y = TRUE)
     ## Add columns for G2P drug-gene and drug-gene-lineage sorting
@@
     # Merge cell line metadata
-    data <- merge(data, select(ccl_meta, Cell_line, Histology, CCLE_Name, Broad_ID, Primary.Disease), by = "Broad_ID", all.x = TRUE)
+    data <- merge(data, select(ccl_meta, Cell_line, Histology, CCLE_Name, Broad_ID, Primary.Disease), by = "Broad_ID", all.y = TRUE)
     data$Drug_Gene <- paste0(data$Drug, "_", data$Gene)
@@
   # Merge mutation calls
-  data <- merge(data, maf_df_filt, by = c("Gene", "Broad_ID"), all.x = TRUE)
+  data <- unfactorize(data)
+  data <- merge(data, maf_df_ptmuts, by = c("Gene", "Broad_ID"), all.x = TRUE)
   data$Mutation_Status <- ifelse(is.na(data$Mutation_Status), 0, data$Mutation_Status)
   ## Identify point mutations
-  data$PointMutation <- ifelse(is.na(data$PointMutation), 1, data$PointMutation)
+  # data$PointMutation <- ifelse(is.na(data$PointMutation), 1, data$PointMutation)
   ## Summarize number of mutant and Wildtype cell lines
@@
   data <- merge(data_muts_summ, data, by = "Gene")
-  ## Add color columns for plotting
-  if(database == "CCLE") {
-    data$Color <- ifelse(data$Mutation_Status == 0, "palegreen3", "springgreen4")
-  }
-  if(database == "CTRP") {
-    data$Color <- ifelse(data$Mutation_Status == 0, "slategray3", "steelblue4")
-  }
-  if(database == "GDSC") {
-    data$Color <- ifelse(data$Mutation_Status == 0, "paleturquoise3", "turquoise4")
-  }
-  if(database == "CRISPR") {
-    data$Color <- ifelse(data$Mutation_Status == 0, "thistle", "darkorchid")
-  }
-  data$Color <- factor(data$Color)
   print("Merged mutation calls.")
@@
   # Drop cell lines not in DepMap
-  data <- filter(data, !is.na(Broad_ID))
+  data <- filter(data, !is.na(Broad_ID) & !(Broad_ID %in% c("ACH-001182", "ACH-001451")))
 
@@
 
-FilterForPointMuts <- function(dataframe, outfile) {
-  # Filter for point mutations
-  ptmuts <- filter(dataframe, PointMutation == 1)
-  # Remove columns that lead to duplicate mutation entries
-  ptmuts <- subset(ptmuts, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, PointMutation))
-  ptmuts$Gene <- ordered(ptmuts$Gene, levels = g2p_genes)
-  ptmuts <- unique(ptmuts)
-  saveRDS(ptmuts, outfile, compress = "xz")
-  return(ptmuts)
-}
+# FilterForPointMuts <- function(dataframe, outfile) {
+#   # Filter for point mutations
+#   ptmuts <- filter(dataframe, PointMutation == 1)
+#   # Remove columns that lead to duplicate mutation entries
+#   ptmuts <- subset(ptmuts, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, PointMutation))
+#   ptmuts$Gene <- ordered(ptmuts$Gene, levels = g2p_genes)
+#   ptmuts <- unique(ptmuts)
+#   saveRDS(ptmuts, outfile, compress = "xz")
+#   return(ptmuts)
+# }
 ```
@@
 `r nrow(filter(test, n != 1))`/`r nrow(test)` gene-cell line combinations have more than one mutation in the MAF file. This is corrected in the point mutation filtering done below.
+
+**RE-FILTER FOR PTMUTS**
 ```{r merge_filter_drug_data, eval=FALSE}
@@
 # Omics metadata
-maf_df_filt <- filter(maf_df, Gene %in% g2p_genes)
+maf_df_ptmuts <- unique(filter(maf_df, Gene %in% g2p_genes & PointMutation == 1) %>% select(-c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, PointMutation)))
 ge_filt <- filter(ge_melt, Gene %in% g2p_genes)
@@
 
-ccle <- MergeOmicsG2P(database = "CCLE", outfile = "./data_munging/rds/ccle_data_19Q1_g2pgenes.rds")
-ctrp <- MergeOmicsG2P(database = "CTRP", outfile = "./../htscreens_giant_files/ctrp_data_19Q1_g2pgenes.rds")
-gdsc <- MergeOmicsG2P(database = "GDSC", outfile = "./data_munging/rds/gdsc_data_19Q1_g2pgenes.rds")
-
-ccle_ptmuts <- FilterForPointMuts(dataframe = ccle, outfile = "./data_munging/rds/ccle_data_19Q1_g2pgenes_ptmuts.rds")
-ctrp_ptmuts <- FilterForPointMuts(dataframe = ctrp, outfile = "./../htscreens_giant_files/ctrp_data_19Q1_g2pgenes_ptmuts.rds")
-gdsc_ptmuts <- FilterForPointMuts(dataframe = gdsc, outfile = "./data_munging/rds/gdsc_data_19Q1_g2pgenes_ptmuts.rds")
+ccle_ptmuts <- MergeOmicsG2P(database = "CCLE", outfile = "./data_munging/rds/ccle_data_19Q1_g2pgenes_ptmuts.rds")
+ctrp_ptmuts <- MergeOmicsG2P(database = "CTRP", outfile = "./../htscreens_giant_files/ctrp_data_19Q1_g2pgenes_ptmuts.rds")
+gdsc_ptmuts <- MergeOmicsG2P(database = "GDSC", outfile = "./data_munging/rds/gdsc_data_19Q1_g2pgenes_ptmuts.rds")
 ```
@@
 ```{r load_drug_rds, eval=TRUE}
-ccle <- readRDS("./data_munging/rds/ccle_data_19Q1_g2pgenes.rds")
-ctrp <- readRDS("./../htscreens_giant_files/ctrp_data_19Q1_g2pgenes.rds")
-gdsc <- readRDS("./data_munging/rds/gdsc_data_19Q1_g2pgenes.rds")
 ccle_ptmuts <- readRDS("./data_munging/rds/ccle_data_19Q1_g2pgenes_ptmuts.rds")
@@
 Merge all CRISPR genes:
-```{r merge_crispr_data, eval=FALSE}
+```{r merge_crispr_data, eval=TRUE}
 crispr_all <- read.delim("./data_munging/19Q1/gene_effect_corrected_20190305.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
@@
 # Merge mutation annotations
-maf_filt_crispr <- filter(maf_df, Gene %in% as.character(unique(crispr_melt$Gene)))
-maf_filt_crispr <- subset(maf_filt_crispr, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1))
-maf_filt_crispr <- unique(maf_filt_crispr)
+maf_filt_crispr <- unique(filter(maf_df, Gene %in% as.character(unique(crispr_melt$Gene)) & PointMutation == 1) %>% select(-c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, PointMutation)))
 crispr_muts <- merge(crispr_melt, maf_filt_crispr, by = c("Gene","Broad_ID"), all.x = TRUE)
-crispr_muts$Gene <- factor(crispr_muts$Gene)
 crispr_muts$Mutation_Status <- ifelse(is.na(crispr_muts$Mutation_Status), 0, crispr_muts$Mutation_Status)
-## Identify point mutations and wildtypes for testing
-crispr_muts$PointMutation <- ifelse(is.na(crispr_muts$PointMutation), 1, crispr_muts$PointMutation)
 
@@
 
-saveRDS(crispr_data, "./data_munging/rds/crispr_data_19Q1.rds", compress = "xz")
+saveRDS(crispr_data, "./data_munging/rds/crispr_data_19Q1_ptmuts.rds", compress = "xz")
 
 # Filter G2P CRISPR for point mutations
-crispr_ptmuts <- filter(crispr_data, PointMutation == 1)
-crispr_ptmuts <- subset(crispr_ptmuts, select = -c(PointMutation))
-crispr_ptmuts <- filter(crispr_ptmuts, Gene %in% g2p_genes)
-crispr_ptmuts$Primary.Disease <- factor(crispr_ptmuts$Primary.Disease)
-crispr_ptmuts$Mutation_Status <- factor(crispr_ptmuts$Mutation_Status)
-saveRDS(crispr_ptmuts, "./data_munging/rds/crispr_data_19Q1_g2pgenes_ptmuts.rds", compress = "xz")
+# crispr_ptmuts <- filter(crispr_data, PointMutation == 1)
+# crispr_ptmuts <- subset(crispr_ptmuts, select = -c(PointMutation))
+# crispr_ptmuts <- filter(crispr_ptmuts, Gene %in% g2p_genes)
+# crispr_ptmuts$Primary.Disease <- factor(crispr_ptmuts$Primary.Disease)
+# crispr_ptmuts$Mutation_Status <- factor(crispr_ptmuts$Mutation_Status)
+# saveRDS(crispr_ptmuts, "./data_munging/rds/crispr_data_19Q1_g2pgenes_ptmuts.rds", compress = "xz")
 ```
@@
 ```{r load_crispr_filter, eval=TRUE}
-crispr_data <- readRDS("./data_munging/rds/crispr_data_19Q1.rds")
-crispr_ptmuts <- readRDS("./data_munging/rds/crispr_data_19Q1_g2pgenes_ptmuts.rds")
+# crispr_data <- readRDS("./data_munging/rds/crispr_data_19Q1.rds")
+crispr_ptmuts <- readRDS("./data_munging/rds/crispr_data_19Q1_ptmuts.rds")
 ```
@@
 
+## Mutation
+
 ## Cell line and drug overlaps
 
-```{r ccl_venn, eval=FALSE}
+```{r ccl_venn, eval=TRUE}
 ccle_ccls <- unique(ccle_ptmuts$Broad_ID)
@@
 venn.diagram(x = list(ccle_ccls, ctrp_ccls, gdsc_ccls, crispr_ccls),
-             filename = "./plots/manuscript/venn_ccls.png",
+             filename = "./plots/manuscript/all_venn_ccls.png",
              output = TRUE, imagetype = "png",
@@
              fill = c("springgreen4", "steelblue4", "turquoise4", "darkorchid"))
-```
-
-```{r drug_venn, eval=FALSE}
+
+venn.diagram(x = list(ccle_ccls, ctrp_ccls, gdsc_ccls),
+             filename = "./plots/manuscript/drug_venn_ccls.png",
+             output = TRUE, imagetype = "png",
+             height = 2000, width = 2000, resolution = 500,
+             lwd = 1, cex = 1.4,
+             category.names = c("CCLE", "CTRP", "GDSC"),
+             cat.cex = 1.4, cat.fontface = "bold", cat.default.pos = "outer",
+             cat.dist = c(0.06, 0.06, 0.035),
+             fill = c("springgreen4", "steelblue4", "turquoise4"))
+```
+
+```{r drug_venn, eval=TRUE}
 ccle_drugs <- unique(ccle_ptmuts$Drug)
@@
 venn.diagram(x = list(ccle_drugs, ctrp_drugs, gdsc_drugs),
-             filename = "./plots/manuscript/venn_drugs.png",
+             filename = "./plots/manuscript/drug_venn_drugs.png",
              output = TRUE, imagetype = "png",
@@
 
-```{r histology_dists_data, eval=FALSE}
+```{r histology_dists_data, eval=TRUE}
 ccle_hists <- unique(select(ccle_ptmuts, Broad_ID, Primary.Disease)) %>% count(Primary.Disease)
@@
 drug_hists$Primary.Disease <- gsub(" cancer", "", drug_hists$Primary.Disease)
-# saveRDS(drug_hists, "./data_munging/rds/histology_distributions.rds")
+saveRDS(drug_hists, "./data_munging/rds/histology_distributions.rds")
 ```
@@
 drug_hists <- readRDS("./data_munging/rds/histology_distributions.rds")
-png(filename = "./plots/manuscript/histology_distributions.png", width = 8, height = 9, units = "in", res = 500)
+png(filename = "./plots/manuscript/all_histology_distributions.png", width = 8, height = 9, units = "in", res = 500)
 ggplot(drug_hists, aes(x = Dataset, y = n, fill = Primary.Disease)) +
@@
   labs(y = "Count")
+dev.off()
+```
+
+```{r, eval=TRUE}
+ccle_ccls <- unique(ccle_ptmuts$Broad_ID)
+ctrp_ccls <- unique(ctrp_ptmuts$Broad_ID)
+gdsc_ccls <- unique(gdsc_ptmuts$Broad_ID)
+crispr_ccls <- unique(crispr_ptmuts$Broad_ID)
+
+ccls <- data.frame(Broad_ID = union(ccle_ccls, union(ctrp_ccls, gdsc_ccls)))
+all_ccls <- merge(ccls, ccl_meta, by = "Broad_ID")
+all_ccls$Primary.Disease <- gsub(" cancer", "", all_ccls$Primary.Disease)
+
+png(filename = "./plots/manuscript/drug_histology_distributions.png", width = 8, height = 4, units = "in", res = 500)
+ggplot(all_ccls, aes(x = fct_infreq(factor(Primary.Disease)), fill = Primary.Disease)) +
+  geom_bar(color = "black") +
+  scale_y_continuous(breaks = seq(0, 220, by = 40), labels = seq(0, 220, by = 40)) +
+  guides(fill = FALSE) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
+  labs(y = "Number of Cell Lines", x = "Histology", caption = paste0(formatC(nrow(all_ccls), format = "d", big.mark = ","), " cell lines represented."))
 dev.off()
@@
 
-# png(filename = "./plots/manuscript/g2p_summary_heatmap.png", width = 10, height = 9, units = "in", res = 500)
+png(filename = "./plots/manuscript/g2p_summary_heatmap.png", width = 10, height = 9, units = "in", res = 500)
 draw(hta + ht, gap = unit(5, "mm"), heatmap_legend_side = "top")
-# dev.off()
+dev.off()
 ```
@@
 
-```{r wilcoxon_tests, eval=FALSE}
+```{r wilcoxon_tests, eval=TRUE}
 crispr_ptmuts <- unfactorize(crispr_ptmuts)
@@
   geom_boxplot(aes(x = Mutation_Status, y = Score), fill = "transparent", outlier.shape = NA, lwd = 0.3) +
-  geom_text(data = crispr_signif_gene, aes(x = 1.5, y = 1.75, label = p.signif.adj)) +
+  geom_text(data = crispr_signif_gene, aes(x = 1.5, y = 1.75, label = p.signif)) +
   geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
@@
   labs(y = "CERES Score")
-# crispr_gene_mut_plot
-
-# ggsave("./plots/manuscript/crispr_gene_mut_plot.png", crispr_gene_mut_plot, width = 12, height = 6, units = "in")
-```
-
-```{r crispr_mut_lin_plot, fig.height=12, fig.width=8}
+crispr_gene_mut_plot
+
+ggsave("./plots/manuscript/crispr_gene_mut_plot.png", crispr_gene_mut_plot, width = 12, height = 6, units = "in")
+```
+
+```{r crispr_mut_lin_plot}
 crispr_signif_lineage$Gene <- factor(crispr_signif_lineage$Gene, levels = g2p_genes)
@@
 crispr_gene_lin_plot <- ggplot(data = crispr_ptmuts) +
-  facet_wrap(~ Primary.Disease, nrow = 7, scales = "free_x") +
+  facet_wrap(~ Primary.Disease, nrow = 6, scales = "free_x") +
   scale_color_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "darkorchid", "0" = "thistle")) +
   geom_point(aes(x = Gene, y = Score, color = Mutation_Status), alpha = 0.5, size = 0.6) +
-  geom_text(data = crispr_signif_lineage, aes(x = Gene, y = 1.75, label = p.signif.adj)) +
+  geom_text(data = crispr_signif_lineage, aes(x = Gene, y = 1.6, label = p.signif), angle = 90, vjust = 0.8, nudge_y = 0.1, size = 3) +
   geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
-  theme(legend.position = "top", legend.direction = "horizontal", axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 10)) +
+  theme(legend.position = "top", legend.direction = "horizontal", axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 7)) +
   guides(color = guide_legend(override.aes = list(size = 3))) +
@@
 
-# ggsave("./plots/manuscript/crispr_gene_lineage_plot.png", crispr_gene_lin_plot, width = 16, height = 20, units = "in")
+ggsave("./plots/manuscript/crispr_gene_lineage_plot.png", crispr_gene_lin_plot, width = 16, height = 18, units = "in")
 ```
@@
 
-```{r mut_heatmaps, eval=FALSE}
+```{r mut_heatmaps, eval=TRUE}
 ht_ccle <- MakeMutHeatmap(signif_g2p_druggene = ccle_signif_g2p_druggene, legend_title = "P-value", row_names = TRUE, color = "darkgreen", col_title = "Drugs")
@@
 
-```{r drug_spear_calc, warning=FALSE, eval=FALSE}
+```{r drug_spear_calc, warning=FALSE, eval=TRUE}
 g2p_druggene_tally <- g2p %>% group_by(Drug_Gene) %>% tally() %>% drop_na()
@@
 
-# ggsave("./plots/manuscript/crispr_spearman_corr_plot.png", crispr_spearman_corr_plot, device = "png", dpi = 450, width = 20, height = 10, units = "in")
+ggsave("./plots/manuscript/crispr_spearman_corr_plot.png", crispr_spearman_corr_plot, device = "png", dpi = 450, width = 20, height = 10, units = "in")
 ```
@@
 
-```{r drug_spear_plots, eval=FALSE}
+```{r drug_spear_plots, eval=TRUE}
 # Copy number
@@
 ```{r drug_KS_tests, eval=TRUE, warning=FALSE, fig.height=6, fig.width=12}
-# g2p_corr_all <- G2PCorrTable(ccle_ptmuts_df = ccle_ptmuts, ctrp_ptmuts_df = ctrp_ptmuts, gdsc_ptmuts_df = gdsc_ptmuts)
-# saveRDS(g2p_corr_all, "./data_munging/rds/g2p_dgl_corr.rds")
-g2p_corr_all <- readRDS("./data_munging/rds/g2p_dgl_corr.rds")
-g2p_mut_stats <- G2PCorrStatsTables(corr_df = g2p_corr_all, table_type = "mutation")
+g2p_dgl_corr <- G2PCorrTable(ccle_ptmuts_df = ccle_ptmuts, ctrp_ptmuts_df = ctrp_ptmuts, gdsc_ptmuts_df = gdsc_ptmuts)
+saveRDS(g2p_dgl_corr, "./data_munging/rds/g2p_dgl_corr.rds")
+g2p_dgl_corr <- readRDS("./data_munging/rds/g2p_dgl_corr.rds")
+g2p_mut_stats <- G2PCorrStatsTables(corr_df = g2p_dgl_corr, table_type = "mutation")
 
@@
 
-# ggsave("./plots/manuscript/g2p_spearman_ks_res_plot.png", g2p_ks_res_plot_spearman, device = "png", dpi = 500, width = 12, height = 6, units = "in")
+ggsave("./plots/manuscript/g2p_spearman_ks_res_plot.png", g2p_ks_res_plot_spearman, device = "png", dpi = 500, width = 12, height = 6, units = "in")
 ```

### 2019-05-09 19Q1.Rmd
update Rmd

@@
 ```{r load_drug_rds, eval=TRUE}
-ccle_ptmuts <- readRDS("./data_munging/rds/ccle_data_19Q1_g2pgenes_ptmuts.rds")
-ctrp_ptmuts <- readRDS("./../htscreens_giant_files/ctrp_data_19Q1_g2pgenes_ptmuts.rds")
-gdsc_ptmuts <- readRDS("./data_munging/rds/gdsc_data_19Q1_g2pgenes_ptmuts.rds")
+ccle_ptmuts <- readRDS("./data_munging/rds/ccle_data_19Q1_g2pgenes_ptmuts.rds") %>% drop_na(Drug)
+ctrp_ptmuts <- readRDS("./../htscreens_giant_files/ctrp_data_19Q1_g2pgenes_ptmuts.rds") %>% drop_na(Drug)
+gdsc_ptmuts <- readRDS("./data_munging/rds/gdsc_data_19Q1_g2pgenes_ptmuts.rds") %>% drop_na(Drug)
 
 # Testing
-test_ccle <- ccle_ptmuts %>% count(Gene, Mutation_Status)
+test_ccle <- ccle_ptmuts %>% count(Gene, Drug)
 test_ctrp <- ctrp_ptmuts %>% count(Gene, Mutation_Status)
@@
 Merge all CRISPR genes:
-```{r merge_crispr_data, eval=TRUE}
+```{r merge_crispr_data, eval=FALSE}
 crispr_all <- read.delim("./data_munging/19Q1/gene_effect_corrected_20190305.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
@@
 crispr_data <- merge(crispr_muts_summ, crispr_muts, by = "Gene")
-crispr_ptmuts$Mutation_Status <- factor(crispr_ptmuts$Mutation_Status)
+crispr_data$Mutation_Status <- factor(crispr_data$Mutation_Status)
 ## Add Color column
@@
 
-```{r ccl_venn, eval=TRUE}
+```{r ccl_venn, eval=FALSE}
 ccle_ccls <- unique(ccle_ptmuts$Broad_ID)
@@
 
-```{r drug_venn, eval=TRUE}
+```{r drug_venn, eval=FALSE}
 ccle_drugs <- unique(ccle_ptmuts$Drug)
@@
 
-```{r histology_dists_data, eval=TRUE}
+```{r histology_dists_data, eval=FALSE}
 ccle_hists <- unique(select(ccle_ptmuts, Broad_ID, Primary.Disease)) %>% count(Primary.Disease)
@@
 
-```{r, eval=TRUE}
+```{r, eval=FALSE}
 ccle_ccls <- unique(ccle_ptmuts$Broad_ID)
@@
 
-```{r wilcoxon_tests, eval=TRUE}
+```{r wilcoxon_tests, eval=FALSE}
 crispr_ptmuts <- unfactorize(crispr_ptmuts)
@@
 
-```{r mut_heatmaps, eval=TRUE}
+```{r mut_heatmaps, eval=FALSE}
 ht_ccle <- MakeMutHeatmap(signif_g2p_druggene = ccle_signif_g2p_druggene, legend_title = "P-value", row_names = TRUE, color = "darkgreen", col_title = "Drugs")
@@
 
-```{r drug_spear_calc, warning=FALSE, eval=TRUE}
+```{r drug_spear_calc, warning=FALSE, eval=FALSE}
 g2p_druggene_tally <- g2p %>% group_by(Drug_Gene) %>% tally() %>% drop_na()
@@
 
-```{r drug_spear_plots, eval=TRUE}
+```{r drug_spear_plots, eval=FALSE}
 # Copy number
@@
 ccle_ge_ht2 <- MakeCorrHeatmap(drug_cor_res = ccle_cor, row_names = TRUE, col_title = "CCLE", color_range = c(-0.5, 0, 0.5), legend_title = "Gene expr. Spearman correlation", metric = "GE")
-ctrp_ge_ht2 <- MakeCorrHeatmap(druwg_cor_res = ctrp_cor, row_names = FALSE, col_title = "CTRP", color_range = c(-0.5, 0, 0.5), legend_title = "Gene expr. Spearman correlation", metric = "GE")
+ctrp_ge_ht2 <- MakeCorrHeatmap(drug_cor_res = ctrp_cor, row_names = FALSE, col_title = "CTRP", color_range = c(-0.5, 0, 0.5), legend_title = "Gene expr. Spearman correlation", metric = "GE")
 gdsc_ge_ht2 <- MakeCorrHeatmap(drug_cor_res = gdsc_cor, row_names = FALSE, col_title = "GDSC", color_range = c(-0.5, 0, 0.5), legend_title = "Gene expr. Spearman correlation", metric = "GE")
@@
 Kolmogorov-Smirnov tests comparing DGLs that are in a G2P DGL and not.
-```{r drug_KS_tests, eval=TRUE, warning=FALSE, fig.height=6, fig.width=12}
-g2p_dgl_corr <- G2PCorrTable(ccle_ptmuts_df = ccle_ptmuts, ctrp_ptmuts_df = ctrp_ptmuts, gdsc_ptmuts_df = gdsc_ptmuts)
-saveRDS(g2p_dgl_corr, "./data_munging/rds/g2p_dgl_corr.rds")
+```{r drug_KS_tests, eval=FALSE, warning=FALSE, fig.height=6, fig.width=12}
+# g2p_dgl_corr <- G2PCorrTable(ccle_ptmuts_df = ccle_ptmuts, ctrp_ptmuts_df = ctrp_ptmuts, gdsc_ptmuts_df = gdsc_ptmuts)
+# saveRDS(g2p_dgl_corr, "./data_munging/rds/g2p_dgl_corr.rds")
 g2p_dgl_corr <- readRDS("./data_munging/rds/g2p_dgl_corr.rds")
@@
 
-g2p_corr_4plot <- filter(g2p_corr_all, G2P_Drug_Gene == "Yes")
+g2p_corr_4plot <- filter(g2p_dgl_corr, G2P_Drug_Gene == "Yes")
 g2p_corr_stats <- G2PCorrStatsTables(corr_df = g2p_corr_4plot, table_type = "KS")

### 2019-05-09 19Q1.Rmd
update CRISPR plots and Rmd

@@
     print("Merged metadata.")
+    # Merge mutation calls
+    data <- unfactorize(data)
+    data <- merge(data, maf_df_ptmuts, by = c("Gene", "Broad_ID"), all.x = TRUE)
+    data$Mutation_Status <- ifelse(is.na(data$Mutation_Status), 0, data$Mutation_Status)
   }
@@
     print("Merged metadata.")
-  }
-
     # Merge mutation calls
     data <- unfactorize(data)
-  data <- merge(data, maf_df_ptmuts, by = c("Gene", "Broad_ID"), all.x = TRUE)
+    data <- merge(data, maf_df, by = c("Gene", "Broad_ID"), all.x = TRUE)
     data$Mutation_Status <- ifelse(is.na(data$Mutation_Status), 0, data$Mutation_Status)
-  ## Identify point mutations
-  # data$PointMutation <- ifelse(is.na(data$PointMutation), 1, data$PointMutation)
+  }
+
   ## Summarize number of mutant and Wildtype cell lines
@@
 crispr_data$Mutation_Status <- factor(crispr_data$Mutation_Status)
-## Add Color column
-crispr_data$Color <- ifelse(crispr_data$Mutation_Status == 0, "thistle", "darkorchid")
-crispr_data$Color <- factor(crispr_data$Color)
 
@@
              fill = c("springgreen4", "steelblue4", "turquoise4", "darkorchid"))
-
+futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
 venn.diagram(x = list(ccle_ccls, ctrp_ccls, gdsc_ccls),
@@
 drug_hists <- readRDS("./data_munging/rds/histology_distributions.rds")
-png(filename = "./plots/manuscript/all_histology_distributions.png", width = 8, height = 9, units = "in", res = 500)
+# png(filename = "./plots/manuscript/all_histology_distributions.png", width = 8, height = 9, units = "in", res = 500)
 ggplot(drug_hists, aes(x = Dataset, y = n, fill = Primary.Disease)) +
@@
   labs(y = "Count")
-dev.off()
+# dev.off()
 ```
@@
 
+## AUC heatmap
+
+```{r}
+ccle_auc_grid <- dcast(filter(ccle_ptmuts, Drug %in% g2p_drugs), Drug ~ Broad_ID, value.var = "Score", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Drug)
+ctrp_auc_grid <- dcast(filter(ctrp_ptmuts, Drug %in% g2p_drugs), Drug ~ Broad_ID, value.var = "Score", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Drug)
+gdsc_auc_grid <- dcast(filter(gdsc_ptmuts, Drug %in% g2p_drugs), Drug ~ Broad_ID, value.var = "Score", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Drug)
+
+ccle_auc_ht <- Heatmap(ccle_auc_grid,
+                       name = "AUC",
+                       show_column_names = FALSE, 
+                       column_title = "CCLE",
+                       column_title_side = "top")
+ctrp_auc_ht <- Heatmap(ctrp_auc_grid,
+                       name = "AUC",
+                       show_column_names = FALSE, 
+                       column_title = "CTRP",
+                       column_title_side = "top")
+gdsc_auc_ht <- Heatmap(gdsc_auc_grid,
+                       name = "AUC",
+                       show_column_names = FALSE, 
+                       column_title = "GDSC",
+                       column_title_side = "top")
+
+draw(ccle_auc_ht)
+draw(ctrp_auc_ht)
+draw(gdsc_auc_ht)
+```
+
 # WILCOXON (MUT)
@@
 crispr_ptmuts <- unfactorize(crispr_ptmuts)
-crispr_signif_gene <- WilcoxonTestDF(dataframe = crispr_ptmuts, grouping = "Gene", outfile = "./data_munging/rds/crispr_signif_g2p_gene.rds")
-crispr_signif_lineage <- WilcoxonTestDF(dataframe = crispr_ptmuts, grouping = c("Gene", "Primary.Disease"), outfile = "./data_munging/rds/crispr_signif_g2p_lineage.rds")
+# crispr_signif_all_gene <- WilcoxonTestDF(dataframe = crispr_ptmuts, grouping = "Gene", outfile = "./data_munging/rds/crispr_signif_gene.rds")
+crispr_ptmuts_filt <- filter(crispr_ptmuts, Gene %in% g2p_genes)
+crispr_signif_gene <- WilcoxonTestDF(dataframe = crispr_ptmuts_filt, grouping = "Gene", outfile = "./data_munging/rds/crispr_signif_g2p_gene.rds")
+crispr_signif_lineage <- WilcoxonTestDF(dataframe = crispr_ptmuts_filt, grouping = c("Gene", "Primary.Disease"), outfile = "./data_munging/rds/crispr_signif_g2p_lineage.rds")
 
@@
 crispr_signif_gene$Gene <- factor(crispr_signif_gene$Gene, levels = g2p_genes)
-crispr_ptmuts$Gene <- factor(crispr_ptmuts$Gene, levels = g2p_genes)
-
-crispr_gene_mut_plot <- ggplot(data = crispr_ptmuts) +
+crispr_ptmuts_filt <- filter(crispr_ptmuts, Gene %in% g2p_genes)
+crispr_ptmuts_filt$Gene <- factor(crispr_ptmuts_filt$Gene, levels = g2p_genes)
+crispr_ptmuts_filt$Mutation_Status <- as.character(crispr_ptmuts_filt$Mutation_Status)
+
+crispr_gene_mut_plot <- ggplot(data = crispr_ptmuts_filt) +
   facet_wrap(~ Gene, nrow = 2, drop = FALSE) +
@@
   labs(y = "CERES Score")
-crispr_gene_mut_plot
-
-ggsave("./plots/manuscript/crispr_gene_mut_plot.png", crispr_gene_mut_plot, width = 12, height = 6, units = "in")
+# crispr_gene_mut_plot
+
+# ggsave("./plots/manuscript/crispr_gene_mut_plot.png", crispr_gene_mut_plot, width = 12, height = 6, units = "in")
 ```
@@
 
-crispr_gene_lin_plot <- ggplot(data = crispr_ptmuts) +
+crispr_gene_lin_plot <- ggplot(data = crispr_ptmuts_filt) +
   facet_wrap(~ Primary.Disease, nrow = 6, scales = "free_x") +
@@
   scale_x_discrete(name = "Mutation Status", labels = c("0" = "WT", "1" = "Mut"))
-crispr_gene_lin_plot
-
-ggsave("./plots/manuscript/crispr_gene_lineage_plot.png", crispr_gene_lin_plot, width = 16, height = 18, units = "in")
+# crispr_gene_lin_plot
+
+# ggsave("./plots/manuscript/crispr_gene_lineage_plot.png", crispr_gene_lin_plot, width = 16, height = 18, units = "in")
 ```
@@
 ```{r crispr_spear_calc, warning=FALSE}
-crispr_spear_ge <- transform(crispr_ptmuts %>% group_by(Gene) %>% summarize(p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value, p_log10 = -log10(p), corr = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate, Metric = "Gene Expression"), Gene = reorder(Gene, corr))
-crispr_spear_cn <- transform(crispr_ptmuts %>% group_by(Gene) %>% summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value, p_log10 = -log10(p), corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate, Metric = "Copy Number"), Gene = reorder(Gene, corr))
+crispr_spear_ge <- transform(crispr_ptmuts_filt %>% group_by(Gene) %>% summarize(p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value, p_log10 = -log10(p), corr = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate, Metric = "Gene Expression"), Gene = reorder(Gene, corr))
+crispr_spear_cn <- transform(crispr_ptmuts_filt %>% group_by(Gene) %>% summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value, p_log10 = -log10(p), corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate, Metric = "Copy Number"), Gene = reorder(Gene, corr))
 ```
@@
 ```{r crispr_spear_plot, fig.height=6, fig.width=12}
-spearman_KRAS <- rbind(filter(crispr_ptmuts, Gene == "KRAS") %>% summarize(p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value, corr = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate, Metric = "Gene Expression"), filter(crispr_ptmuts, Gene == "KRAS") %>% summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value, corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate, Metric = "Copy Number"))
-
-crispr_ge_spearman_corr_inset <- ggplot(filter(crispr_ptmuts, Gene == "KRAS"), aes(x = TPM, y = Score)) +
+spearman_KRAS <- rbind(filter(crispr_ptmuts_filt, Gene == "KRAS") %>% summarize(p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value, corr = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate, Metric = "Gene Expression"), filter(crispr_ptmuts_filt, Gene == "KRAS") %>% summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value, corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate, Metric = "Copy Number"))
+
+crispr_ge_spearman_corr_inset <- ggplot(filter(crispr_ptmuts_filt, Gene == "KRAS"), aes(x = TPM, y = Score)) +
   geom_point(pch = 21, fill = "cadetblue3", alpha = 0.6) +
-  labs(x = "KRAS Gene Expression (TPM)", y = "CERES Score", subtitle = paste0("Spearman correlation coefficient = ", round(spearman_KRAS$corr[1], 2), " (p = ", formatC(as.numeric(spearman_KRAS$p[1]), format = "e", digits = 1), ")"))
-
-crispr_cn_spearman_corr_inset <- ggplot(filter(crispr_ptmuts, Gene == "KRAS"), aes(x = CN, y = Score)) +
+  labs(x = expression("KRAS Gene Expression"~(log[2](TPM))), y = "CERES Score", subtitle = paste0("Spearman correlation coefficient = ", round(spearman_KRAS$corr[1], 2), " (p = ", formatC(as.numeric(spearman_KRAS$p[1]), format = "e", digits = 1), ")"))
+
+crispr_cn_spearman_corr_inset <- ggplot(filter(crispr_ptmuts_filt, Gene == "KRAS"), aes(x = CN, y = Score)) +
   geom_point(pch = 21, fill = "palegreen2", alpha = 0.6) +

### 2019-05-10 19Q1.Rmd
updated Rmd

@@
 library(ggsignif)
+library(jsonlite)
 library(kableExtra)
@@
 library(scales)
+library(stringr)
 library(tidyverse)
@@
 
-```{r g2p_interpretations}
+```{r g2p_parsing_functions}
+ExtractBiomarkerType <- function(json_string) {
+  json_string <- as.character(json_string)
+  biomarker_type <- ((str_extract(string = json_string, pattern = "biomarker_type.+") %>% strsplit(split = ","))[[1]][1] %>% str_extract(pattern = "u'.+") %>% str_match("'(.*?)'"))[,2]
+  return(biomarker_type)
+}
+```
+
+```{r g2p_parsing, eval=FALSE}
+# g2p_json <- "./../htscreens_giant_files/g2p_all.json"
+# g2p_all <- fromJSON(sprintf("[%s]", paste(readLines(g2p_json), collapse = ",")), flatten = TRUE)
+# saveRDS(g2p_all, "./../htscreens_giant_files/g2p_all_flattened_json.rds", compress = "xz")
+
 g2p <- read.delim("./data_munging/g2p_full_level_A_dataset_NEW_DEC_2_2018_withGroupedLineages.csv", sep = "\t", header = TRUE)
@@
 g2p <- subset(g2p, grepl("^CID", g2p$DrugID))
+g2p$Direction <- ifelse(g2p$Direction == 1 | g2p$Direction == "", NA, as.character(g2p$Direction))
+g2p$Gene <- ifelse(is.na(g2p$Gene) & g2p$Drug == "daunorubicin", "MLL", as.character(g2p$Gene))
+g2p <- g2p[, c("Drug", "DrugID", "Direction", "Gene", "Ref", "Alt", "Start", "End", "Chromosome", "Feature.Names", "Mutation", "JSON", "Evidence.Level", "Phenotype.Description", "Phenotype.Family", "Phenotype.ID", "Sequence.ID", "grouped_general_doid")]
+g2p <- add_column(g2p, biomarker_type = tolower(sapply(g2p$JSON, ExtractBiomarkerType, simplify = TRUE)), .after = "Feature.Names")
+g2p <- add_column(g2p, biomarker_type_curated = as.character(894), .after = "biomarker_type")
+g2p$biomarker_type_curated <-
+  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = ",")), NA,
+  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "del")), "deletion",
+  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "ins|dup")), "insertion",
+  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "oncogenic mutation|mutant")), "mutation",
+  ifelse(g2p$Feature.Names == "KRAS G12fs*3", "deletion",
+  ifelse(g2p$biomarker_type == "intron variant", "intron variant",
+  ifelse(g2p$biomarker_type == "microsatellite", "microsatellite",
+  ifelse(g2p$biomarker_type == "positive", "positive",
+  ifelse(g2p$biomarker_type == "rearrange", "rearrangement",
+  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "fusion|FUSION|Fusion")), "fusion", 
+  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "[A-Z0-9]-[A-Z0-9]")), "fusion",
+  ifelse(g2p$biomarker_type == "synonymous", "synonymous",
+  ifelse(g2p$biomarker_type == "biallelic inactivation", "biallelic inactivation",       
+  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "[A-Z][0-9]+[A-WYZ]")), "missense",
+  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "[A-Z][0-9]+([X]|[*])")), "nonsense", NA)))))))))))))))
 g2p$Drug_Gene <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene), NA, paste0(g2p$Drug, "_", g2p$Gene))
@@
 g2p$position <- ifelse(grepl("NA", g2p$position), NA, g2p$position)
-g2p <- merge(g2p, lineage_converter, by = "grouped_general_doid", all.x = TRUE)
+g2p <- merge(lineage_converter, g2p, by = "grouped_general_doid", all.y = TRUE)
 g2p$Drug_Gene_Lin <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene) | is.na(g2p$group_general_lineage_name), NA, paste0(g2p$Drug, "_", g2p$Gene, "_", g2p$group_general_lineage_name))
 
-g2p_dgls <-  unique(g2p$Drug_Gene_Lin[!is.na(g2p$Drug_Gene_Lin)])
+write.csv(g2p, "./data_munging/g2p_db_edited.csv")
+
+g2p_dgls <-  unique (g2p$Drug_Gene_Lin[!is.na(g2p$Drug_Gene_Lin)])
 g2p_druggenes <- unique(g2p$Drug_Gene[!is.na(g2p$Drug_Gene)])
@@
 
+!is.na(str_match(string = "ALK L1198F", pattern = "[A-Z][0-9]+[A-WYZ]"))
+
 # Order and genes taken from pink heatmap from Daniel's analyses
@@
 
+```{r g2p}
+g2p <- read.delim("./data_munging/g2p_db_edited.csv", sep = ",", header = TRUE)
+
+g2p_dgls <-  unique (g2p$Drug_Gene_Lin[!is.na(g2p$Drug_Gene_Lin)])
+g2p_druggenes <- unique(g2p$Drug_Gene[!is.na(g2p$Drug_Gene)])
+g2p_drugs <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[1]))
+g2p_genes <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[2]))
+g2p_lins <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[3]))
+```
+
 ```{r testing, eval=FALSE}
+g2p$JSON[1]
+test <- filter(g2p, is.na(Gene))
+test$JSON[2]
+
 unique(g2p$group_general_lineage_name)

### 2019-05-13 19Q1.Rmd
updated Rmd

@@
 g2p[g2p == -1] <- NA
-g2p$Ref[g2p$Ref == "None"] <- NA
-g2p$Alt[g2p$Alt == "None"] <- NA
+g2p$Ref[g2p$Ref == "None" | g2p$Ref == "-" | is.na(g2p$Ref)] <- ""
+g2p$Alt[g2p$Alt == "None" | g2p$Alt == "-" | is.na(g2p$Alt)] <- ""
+g2p <- add_column(g2p, Ref_Length = nchar(as.character(g2p$Ref)), .after = "Ref")
+g2p <- add_column(g2p, Alt_Length = nchar(as.character(g2p$Alt)), .after = "Alt")
+g2p <- add_column(g2p, Variant_Length = NA, .after = "Alt_Length")
+g2p$Variant_Length <-
+  ifelse(g2p$Alt_Length == 1 & g2p$Ref_Length == 1, 1,
+  ifelse(g2p$Alt_Length == 2 & g2p$Ref_Length == 2, 2,
+  ifelse(g2p$Alt_Length == 3 & g2p$Ref_Length == 3, 3,
+  ifelse(g2p$Ref_Length == g2p$Alt_Length & g2p$Ref_Length > 3, g2p$Ref_Length,
+  ifelse(g2p$Ref_Length != g2p$Alt_Length, abs(g2p$Ref_Length - g2p$Alt_Length), NA)))))
+g2p <- add_column(g2p, Variant_Type = NA, .after = "Alt")
+g2p$Variant_Type <-
+  ifelse(g2p$Alt_Length == 1 & g2p$Ref_Length == 1, "SNP",
+  ifelse(g2p$Alt_Length == 2 & g2p$Ref_Length == 2, "DNP",
+  ifelse(g2p$Alt_Length == 3 & g2p$Ref_Length == 3, "TNP",
+  ifelse(g2p$Ref_Length == g2p$Alt_Length & g2p$Ref_Length > 3, "ONP",
+  ifelse(g2p$Ref_Length > g2p$Alt_Length, "DEL",
+  ifelse(g2p$Ref_Length < g2p$Alt_Length, "INS", NA))))))
 g2p <- subset(g2p, grepl("^CID", g2p$DrugID))
@@
 g2p <- add_column(g2p, biomarker_type = tolower(sapply(g2p$JSON, ExtractBiomarkerType, simplify = TRUE)), .after = "Feature.Names")
-g2p <- add_column(g2p, biomarker_type_curated = as.character(894), .after = "biomarker_type")
+g2p <- add_column(g2p, biomarker_type_curated = NA, .after = "biomarker_type")
 g2p$biomarker_type_curated <-
-  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = ",")), NA,
-  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "del")), "deletion",
-  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "ins|dup")), "insertion",
-  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "oncogenic mutation|mutant")), "mutation",
-  ifelse(g2p$Feature.Names == "KRAS G12fs*3", "deletion",
-  ifelse(g2p$biomarker_type == "intron variant", "intron variant",
+  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "[A-Z0-9]+-[A-Z0-9]+^[>|)]")), "fusion",
+  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "[A-Z][0-9]+[A-WYZ]")) | !is.na(str_match(string = g2p$biomarker_type, pattern = "missense")), "Missense_Mutation",
+  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "splice")) | !is.na(str_match(string = g2p$biomarker_type, pattern = "splice")), "Splice_Site",
+  ifelse(!is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "fusion")) | !is.na(str_match(string = tolower(g2p$biomarker_type), pattern = "fusion")), "fusion", 
+  ifelse(!is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "biallelic inactivation")), "biallelic inactivation",
+  ifelse(!is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "amplification")), "amplification",
+  ifelse(!is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "mutant|mutation")), "mutation",
+  ifelse(g2p$Feature.Names == "KRAS G12G" | g2p$Feature.Names == "KRAS G13G", "synonymous",
+  ifelse(g2p$Variant_Type == "DEL" & g2p$Variant_Length %% 3 == 0, "In_Frame_Del",
+  ifelse(g2p$Variant_Type == "DEL" & g2p$Variant_Length %% 3 != 0, "Frame_Shift_Del",
+  ifelse(g2p$Variant_Type == "INS" & g2p$Variant_Length %% 3 == 0, "In_Frame_Ins",
+  ifelse(g2p$Variant_Type == "INS" & g2p$Variant_Length %% 3 != 0, "Frame_Shift_Ins",
+  ifelse(g2p$biomarker_type == "inframe_deletion", "In_Frame_Del",
+  ifelse(g2p$biomarker_type == "inframe_insertion" | !is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "inframe insertion")), "In_Frame_Ins",
+  ifelse(g2p$Feature.Names %in% c("EGFR E746_A750del", "EGFR exon 19 deletions", "Exon 19 deletion/insertion", "Exon 19 deletion"), "In_Frame_Ins",
+  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "[A-Z][0-9]+([X]|[*])")), "Nonsense_Mutation",
+  ifelse(g2p$Feature.Names == "KRAS G12fs*3" | g2p$Feature.Names == "EGFR E746fs*15", "deletion",
+  ifelse(!is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "amplification")), "amplification",
   ifelse(g2p$biomarker_type == "microsatellite", "microsatellite",
-  ifelse(g2p$biomarker_type == "positive", "positive",
+  ifelse(g2p$biomarker_type == "positive" | !is.na(str_match(string = g2p$Feature.Names, pattern = "positive")), "positive",
   ifelse(g2p$biomarker_type == "rearrange", "rearrangement",
-  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "fusion|FUSION|Fusion")), "fusion", 
-  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "[A-Z0-9]-[A-Z0-9]")), "fusion",
-  ifelse(g2p$biomarker_type == "synonymous", "synonymous",
-  ifelse(g2p$biomarker_type == "biallelic inactivation", "biallelic inactivation",       
-  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "[A-Z][0-9]+[A-WYZ]")), "missense",
-  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "[A-Z][0-9]+([X]|[*])")), "nonsense", NA)))))))))))))))
+  ifelse(g2p$biomarker_type == "intron variant", "Intron",
+  ifelse(!is.na(str_match(string = tolower(g2p$biomarker_type), pattern = "mut")), "mutation", g2p$biomarker_type_curated)))))))))))))))))))))))
+
 g2p$Drug_Gene <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene), NA, paste0(g2p$Drug, "_", g2p$Gene))
@@
 
-write.csv(g2p, "./data_munging/g2p_db_edited.csv")
+# write.csv(g2p, "./data_munging/g2p_db_edited.csv")
 
@@
 
-!is.na(str_match(string = "ALK L1198F", pattern = "[A-Z][0-9]+[A-WYZ]"))
-
 # Order and genes taken from pink heatmap from Daniel's analyses
@@
 
-g2p_dgls <-  unique (g2p$Drug_Gene_Lin[!is.na(g2p$Drug_Gene_Lin)])
-g2p_druggenes <- unique(g2p$Drug_Gene[!is.na(g2p$Drug_Gene)])
+g2p_dgls <-  as.character(unique(g2p$Drug_Gene_Lin[!is.na(g2p$Drug_Gene_Lin)]))
+g2p_druggenes <- as.character(unique(g2p$Drug_Gene[!is.na(g2p$Drug_Gene)]))
 g2p_drugs <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[1]))

### 2019-05-14 19Q1.Rmd
updated Rmd

@@
 g2p[, 1:2] <- NULL
+g2p <- unfactorize(g2p)
 g2p$Drug <- tolower(g2p$Drug)
 g2p[g2p == -1] <- NA
+g2p$Gene <- ifelse(is.na(g2p$Gene) & g2p$Drug == "daunorubicin", "MLL", as.character(g2p$Gene))
+g2p$Direction <- ifelse(g2p$Direction == 1 | g2p$Direction == "", NA, as.character(g2p$Direction))
 g2p$Ref[g2p$Ref == "None" | g2p$Ref == "-" | is.na(g2p$Ref)] <- ""
 g2p$Alt[g2p$Alt == "None" | g2p$Alt == "-" | is.na(g2p$Alt)] <- ""
+g2p <- g2p[, c("Drug", "DrugID", "Direction", "Gene", "Ref", "Alt", "Start", "End", "Chromosome", "Feature.Names", "Mutation", "JSON", "Evidence.Level", "Phenotype.Description", "Phenotype.Family", "Phenotype.ID", "Sequence.ID", "grouped_general_doid")]
 g2p <- add_column(g2p, Ref_Length = nchar(as.character(g2p$Ref)), .after = "Ref")
@@
   ifelse(g2p$Ref_Length != g2p$Alt_Length, abs(g2p$Ref_Length - g2p$Alt_Length), NA)))))
-g2p <- add_column(g2p, Variant_Type = NA, .after = "Alt")
+g2p <- add_column(g2p, Variant_Type = NA, .after = "Alt_Length")
 g2p$Variant_Type <-
@@
   ifelse(g2p$Ref_Length > g2p$Alt_Length, "DEL",
-  ifelse(g2p$Ref_Length < g2p$Alt_Length, "INS", NA))))))
+  ifelse(g2p$Ref_Length < g2p$Alt_Length, "INS", "None"))))))
 g2p <- subset(g2p, grepl("^CID", g2p$DrugID))
-g2p$Direction <- ifelse(g2p$Direction == 1 | g2p$Direction == "", NA, as.character(g2p$Direction))
-g2p$Gene <- ifelse(is.na(g2p$Gene) & g2p$Drug == "daunorubicin", "MLL", as.character(g2p$Gene))
-g2p <- g2p[, c("Drug", "DrugID", "Direction", "Gene", "Ref", "Alt", "Start", "End", "Chromosome", "Feature.Names", "Mutation", "JSON", "Evidence.Level", "Phenotype.Description", "Phenotype.Family", "Phenotype.ID", "Sequence.ID", "grouped_general_doid")]
 g2p <- add_column(g2p, biomarker_type = tolower(sapply(g2p$JSON, ExtractBiomarkerType, simplify = TRUE)), .after = "Feature.Names")
 g2p <- add_column(g2p, biomarker_type_curated = NA, .after = "biomarker_type")
-g2p$biomarker_type_curated <-
-  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "[A-Z0-9]+-[A-Z0-9]+^[>|)]")), "fusion",
-  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "[A-Z][0-9]+[A-WYZ]")) | !is.na(str_match(string = g2p$biomarker_type, pattern = "missense")), "Missense_Mutation",
+biomarker_type_curated <-
   ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "splice")) | !is.na(str_match(string = g2p$biomarker_type, pattern = "splice")), "Splice_Site",
+  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "Amplification|amplification")), "amplification",
+  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "^PDGFRA [(]")) | !is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "mutant|mutation|mut")), "mutation",
   ifelse(!is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "fusion")) | !is.na(str_match(string = tolower(g2p$biomarker_type), pattern = "fusion")), "fusion", 
-  ifelse(!is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "biallelic inactivation")), "biallelic inactivation",
-  ifelse(!is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "amplification")), "amplification",
-  ifelse(!is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "mutant|mutation")), "mutation",
-  ifelse(g2p$Feature.Names == "KRAS G12G" | g2p$Feature.Names == "KRAS G13G", "synonymous",
+  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "[A-Z0-9|A-Z]+-[A-Z0-9|A-Z]+")) & is.na(str_match(string = g2p$Feature.Names, pattern = "[0-9]+-[0-9]+")), "fusion",
   ifelse(g2p$Variant_Type == "DEL" & g2p$Variant_Length %% 3 == 0, "In_Frame_Del",
@@
   ifelse(g2p$Variant_Type == "INS" & g2p$Variant_Length %% 3 != 0, "Frame_Shift_Ins",
-  ifelse(g2p$biomarker_type == "inframe_deletion", "In_Frame_Del",
-  ifelse(g2p$biomarker_type == "inframe_insertion" | !is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "inframe insertion")), "In_Frame_Ins",
-  ifelse(g2p$Feature.Names %in% c("EGFR E746_A750del", "EGFR exon 19 deletions", "Exon 19 deletion/insertion", "Exon 19 deletion"), "In_Frame_Ins",
+  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "EGFR E746_A750del")), "In_Frame_Del",
+  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "EGFR H773>PNPY")), "In_Frame_Ins",
+  ifelse(g2p$Feature.Names == "KRAS G12G" | g2p$Feature.Names == "KRAS G13G", "synonymous",
+  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "[A-Z][0-9]+[A-WYZ]")) | !is.na(str_match(string = g2p$biomarker_type, pattern = "missense")), "Missense_Mutation",
   ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "[A-Z][0-9]+([X]|[*])")), "Nonsense_Mutation",
-  ifelse(g2p$Feature.Names == "KRAS G12fs*3" | g2p$Feature.Names == "EGFR E746fs*15", "deletion",
-  ifelse(!is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "amplification")), "amplification",
-  ifelse(g2p$biomarker_type == "microsatellite", "microsatellite",
-  ifelse(g2p$biomarker_type == "positive" | !is.na(str_match(string = g2p$Feature.Names, pattern = "positive")), "positive",
+  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "positive")), "positive",
+  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "expression")), "expression",
   ifelse(g2p$biomarker_type == "rearrange", "rearrangement",
   ifelse(g2p$biomarker_type == "intron variant", "Intron",
-  ifelse(!is.na(str_match(string = tolower(g2p$biomarker_type), pattern = "mut")), "mutation", g2p$biomarker_type_curated)))))))))))))))))))))))
-
+  ifelse(g2p$biomarker_type == "inframe_deletion" | !is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "inframe deletion")), "In_Frame_Del",
+  ifelse(g2p$biomarker_type == "inframe_insertion" | !is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "inframe insertion")), "In_Frame_Ins",
+  ifelse(!is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "biallelic inactivation")), "biallelic inactivation", NA)))))))))))))))))))))
+g2p$biomarker_type_curated <- biomarker_type_curated[,1]
 g2p$Drug_Gene <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene), NA, paste0(g2p$Drug, "_", g2p$Gene))
@@
 
-g2p_dgls <-  unique (g2p$Drug_Gene_Lin[!is.na(g2p$Drug_Gene_Lin)])
-g2p_druggenes <- unique(g2p$Drug_Gene[!is.na(g2p$Drug_Gene)])
-g2p_drugs <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[1]))
-g2p_genes <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[2]))
-g2p_lins <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[3]))
-g2p_druggenes
-g2p_drugs
-g2p_genes
-g2p_lins
+# g2p_dgls <-  unique (g2p$Drug_Gene_Lin[!is.na(g2p$Drug_Gene_Lin)])
+# g2p_druggenes <- unique(g2p$Drug_Gene[!is.na(g2p$Drug_Gene)])
+# g2p_drugs <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[1]))
+# g2p_genes <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[2]))
+# g2p_lins <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[3]))
+# g2p_druggenes
+# g2p_drugs
+# g2p_genes
+# g2p_lins
 
@@
 saveRDS(maf_df, "./data_munging/19Q1/maf_df_19Q1.rds", compress = "xz")
+```
+
+DepMap 19Q2 fusion calls:
+```{r fusion_calls, eval=FALSE}
+fusions <- read.delim("./data_munging/19Q2/CCLE_fusions.csv.gz", header = TRUE, sep = ",")
+fusions$LeftGene <- gsub(" .*", "", fusions$LeftGene)
+fusions$RightGene <- gsub(" .*", "", fusions$RightGene)
+fusions$ <- gsub(" .*", "", fusions$RightGene)
 ```
@@
 
-**RE-FILTER FOR PTMUTS**
 ```{r merge_filter_drug_data, eval=FALSE}
@@
 crispr_melt <- merge(crispr_melt, ccl_meta, by = "Broad_ID", all.x = TRUE)
+test_crispr <- unique(select(crispr_melt, Broad_ID, Histology)) %>% count(Histology)
 

### 2019-05-15 19Q1.Rmd
update 19Q1 Rmd

@@
 
-Annotation files for mutation status, copy number, and gene expression of the CCLE and CTRP datasets (Consortium and Consortium 2015, Barretina et al.
+Annotation files for mutation status, copy number, and gene expression of the CCLE, GDSC, and CTRP datasets (Consortium and Consortium 2015, Barretina et al.
 2012) were downloaded from the [DepMap Data Portal](https://depmap.org/portal/download/).
@@
 g2p <- add_column(g2p, biomarker_type_curated = NA, .after = "biomarker_type")
+# Manually assign biomarker_types based on a combination of biomarker_type derived from the JSON string and patterns in the Feature.Names
 biomarker_type_curated <-
@@
   ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "EGFR H773>PNPY")), "In_Frame_Ins",
-  ifelse(g2p$Feature.Names == "KRAS G12G" | g2p$Feature.Names == "KRAS G13G", "synonymous",
+  ifelse(g2p$Feature.Names == "KRAS G12G" | g2p$Feature.Names == "KRAS G13G", "Silent",
   ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "[A-Z][0-9]+[A-WYZ]")) | !is.na(str_match(string = g2p$biomarker_type, pattern = "missense")), "Missense_Mutation",
@@
 
-DepMap 19Q2 fusion calls:
-```{r fusion_calls, eval=FALSE}
+DepMap 19Q2 fusion calls derived using the [STAR-Fusion pipeline](https://github.com/STAR-Fusion/STAR-Fusion/wiki). Column descriptions:
+
+- *JunctionReads*: the number of RNA-Seq fragments containing a read that aligns as a split read at the site of the putative fusion junction
+- *SpanningFrags*: the number of RNA-Seq fragments that encompass the fusion junction such that one read of the pair aligns to a different gene than the other paired-end read of that fragment
+    - Those predictions that have very few JunctionReads and/or SpanningReads are going to be enriched for false positives.
+Note, depending on the site of the fusion breakpoint and length of the reads, it may not be possible to have SpanningFragments and all evidence may show up in the form of JunctionReads
+- *FFPM (fusion fragments per million total reads)*: normalized measure of the fusion-supporting RNA-seq fragmentS; a filter of 0.1 sum FFPM (meaning at least 1 fusion-supporting RNA-seq fragment per 10M total reads) tends to be effective at excluding fusion artifacts, and is the current default for filtering fusions from the final output
+- *LargeAnchorSupport*: whether there are split reads that provide 'long' (set to length of 25 bases) alignments on both sides of the putative breakpoint
+    - Those fusions supported only by split reads (no spanning fragments) and lack LargeAnchorSupport are often highly suspicious and tend to be false positives
+    - Those with LargeAnchorSupport are labeled as 'YES_LDAS' (where LDAS = long double anchor support)
+- *SpliceType*: whether the proposed breakpoint occurs at reference exon junctions as provided by the reference transcript structure annotations (ex. gencode)
+- *LeftBreakEntropy* and *RightBreakEntropy*: the Shannon entropy of the 15 exonic bases flanking the breakpoint.
+    - The maximum entropy is 2, representing highest complexity, and the lowest would be zero (involving a 15 base mononucleotide run)
+    - Low entropy sites should generally be treated as less confident breakpoints.
+
+```{r fusion_calls_19Q2, eval=FALSE}
 fusions <- read.delim("./data_munging/19Q2/CCLE_fusions.csv.gz", header = TRUE, sep = ",")
@@
 fusions$RightGene <- gsub(" .*", "", fusions$RightGene)
-fusions$ <- gsub(" .*", "", fusions$RightGene)
+fusions$X.FusionName <- gsub("--", "-", fusions$X.FusionName)
+fusions <- select(fusions, DepMap_ID, X.FusionName)
+fusions <- as.data.frame(lapply(fusions, function(x) gsub("IGH@|IGH-@", "IGH", x)))
+colnames(fusions) <- c("Broad_ID", "FusionPair")
 ```
@@
 
-19Q1, CCLE RNAseq gene expression data (log2(TPM+1)):
+19Q1, CCLE RNAseq gene expression data:
 ```{r gene_expression, eval=FALSE}
@@
 ```{r omics_functions}
-MergeOmicsG2P <- function(database, outfile) {
+MergeOmicsG2P <- function(database, maf_df, ge_df, cn_df, outfile) {
   # Merge mutation status, CN, and GE omics data with drugscreen results and metadata
@@
     data <- unfactorize(data)
-    data <- merge(data, maf_df_ptmuts, by = c("Gene", "Broad_ID"), all.x = TRUE)
+    data <- merge(data, maf_df, by = c("Gene", "Broad_ID"), all.x = TRUE)
     data$Mutation_Status <- ifelse(is.na(data$Mutation_Status), 0, data$Mutation_Status)
@@
   # Merge GE data
-  data <- merge(data, ge_filt, by = c("Gene", "Broad_ID"), all.x = TRUE)
+  data <- merge(data, ge_df, by = c("Gene", "Broad_ID"), all.x = TRUE)
   print("Merged gene expression data.")
@@
   # Merge CN data
-  data <- merge(data, cn_filt, by = c("Gene", "Broad_ID"), all.x = TRUE)
+  data <- merge(data, cn_df, by = c("Gene", "Broad_ID"), all.x = TRUE)
   print("Merged copy number data.")
@@
 
+**MERGE WITHOUT G2P AND PTMUT FILTER (5/15)**
 ```{r merge_filter_drug_data, eval=FALSE}
@@
 
+ccle <- MergeOmicsG2P(database = "CCLE", maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, outfile = "./data_munging/rds/ccle_data_19Q1.rds")
+# ctrp <- MergeOmicsG2P(database = "CTRP", maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, outfile = "./../htscreens_giant_files/ctrp_data_19Q1.rds")
+# gdsc <- MergeOmicsG2P(database = "GDSC", maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, outfile = "./data_munging/rds/gdsc_data_19Q1.rds")
+
 # Omics metadata
-maf_df_ptmuts <- unique(filter(maf_df, Gene %in% g2p_genes & PointMutation == 1) %>% select(-c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, PointMutation)))
-ge_filt <- filter(ge_melt, Gene %in% g2p_genes)
-cn_filt <- filter(cn_melt, Gene %in% g2p_genes)
-
-ccle_ptmuts <- MergeOmicsG2P(database = "CCLE", outfile = "./data_munging/rds/ccle_data_19Q1_g2pgenes_ptmuts.rds")
-ctrp_ptmuts <- MergeOmicsG2P(database = "CTRP", outfile = "./../htscreens_giant_files/ctrp_data_19Q1_g2pgenes_ptmuts.rds")
-gdsc_ptmuts <- MergeOmicsG2P(database = "GDSC", outfile = "./data_munging/rds/gdsc_data_19Q1_g2pgenes_ptmuts.rds")
+# maf_df_ptmuts <- unique(filter(maf_df, Gene %in% g2p_genes & PointMutation == 1)
+# ge_filt <- filter(ge_melt, Gene %in% g2p_genes)
+# cn_filt <- filter(cn_melt, Gene %in% g2p_genes)
+# ccle_ptmuts <- MergeOmicsG2P(database = "CCLE", maf_df = maf_df_ptmuts, ge_df = ge_filt, cn_df = cn_filt, outfile = "./data_munging/rds/ccle_data_19Q1_g2pgenes_ptmuts.rds")
+# ctrp_ptmuts <- MergeOmicsG2P(database = "CTRP", maf_df = maf_df_ptmuts, ge_df = ge_filt, cn_df = cn_filt, outfile = "./../htscreens_giant_files/ctrp_data_19Q1_g2pgenes_ptmuts.rds")
+# gdsc_ptmuts <- MergeOmicsG2P(database = "GDSC", maf_df = maf_df_ptmuts, ge_df = ge_filt, cn_df = cn_filt, outfile = "./data_munging/rds/gdsc_data_19Q1_g2pgenes_ptmuts.rds")
+```
+
+```{r}
+ccle_missense <- filter(ccle, Variant_Classification == "Missense_Mutation")
+ccle_missense_grid <- expand.grid("Gene" = unique(ccle_missense$Gene), "Broad_ID" = unique(ccle_missense$Broad_ID))
+ccle_missense_grid$Variant_Classification <- NA
+ccle_missense <- merge(ccle_missense, ccle_missense_grid, by = c("Gene", "Broad_ID", "Variant_Classification"), all = TRUE)
 ```
@@
 # Testing
-test_ccle <- ccle_ptmuts %>% count(Gene, Drug)
-test_ctrp <- ctrp_ptmuts %>% count(Gene, Mutation_Status)
-test_gdsc <- gdsc_ptmuts %>% count(Gene, Mutation_Status)
+test_ccle <- ccle_ptmuts %>% count(Drug)
+test_ctrp <- ctrp_ptmuts %>% count(Drug)
+sum(!is.na(str_match(test_ctrp$Drug, "ratio")))
+test_gdsc <- gdsc_ptmuts %>% count(Drug)
 ```

### 2019-05-15 19Q2.Rmd

--- 2019-05-15 19Q1.Rmd
@@
 ---
-title: "19Q1"
+title: "19Q2"
 author: "Sally Claridge"
@@
 
-Note that the new DepMap 19Q1 release made multiple changes to variable names:
-
-- For their universal ccancer cell line nomenclature, they reverted back to `Broad_ID` from 18Q3 rather than `DepMap_ID` that was used in 19Q1
-- The `Primary.Disease` column of the cell line metadata file is more consistently named (`Subtype.Disease` now has the specific disease annotations), though there are a couple capitalization inconsistencies
-- MAF file no longer has `CCLE_Name` column and has a duplicate column of the Broad IDs (i.e. `DepMap_ID` and `Tumor_Sample_Barcode`)
-
-And changes to the data processing pipelines (the following is taken verbatim from the [DepMap data portal](https://depmap.org/portal/download/)):
-
-- **Expression**: We use the GTEx pipeline. Since last release, there have been some updates to the versions of different components of the pipeline and minor bug fixes on GTEx's end.
-- **Mutation**: In this release, we additionally process DepMap WES samples through the CGA mutation calling pipeline adapted for cell lines and available on FireCloud.
-We have added a column for the allele counts from this pipeline run (CGA_WES_AC).
-Previously, the WES_AC column was generated from running the Van Allen mutation calling pipeline for SNPs + Mutect2 for INDELs.
-This column is now named VA_WES_AC.
-- **Copy Number**: We have moved to using the newest version of the GATK pipeline.
-
 ## Cell line metadata
@@
 ccl_converter <- read.delim("./data_munging/cell_line_database_v1_20180911.tsv", row.names = 1, sep = "\t", header = TRUE)
-ccl_lineage_converter <- unique(ccl_converter[, c("Broad_ID", "grouped_general_doid", "group_general_lineage_name")])
+ccl_lineage_converter <- unique(ccl_converter[, c("DepMap_ID", "grouped_general_doid", "group_general_lineage_name")])
 lineage_converter <- unique(select(ccl_lineage_converter, grouped_general_doid, group_general_lineage_name))
@@
 
-DepMap 19Q1 update fixed almost all of the inconsistencies of the Primary.Disease column, though there were come capitalization inconsistencies.
+DepMap 19Q2 update fixed almost all of the inconsistencies of the Primary.Disease column, though there were come capitalization inconsistencies.
 ```{r depmap_metadata}
-ccl_meta <- read.delim("./data_munging/19Q1/DepMap-2019q1-celllines_v2_20190305.csv", sep = ",", header = TRUE, na.strings = c("", NA))
-ccl_meta$Primary.Disease <- tolower(ccl_meta$Primary.Disease)
-ccl_meta$Primary.Disease <- with(ccl_meta, ifelse(Primary.Disease == "colon/colorectal cancer", "colorectal cancer", Primary.Disease))
-ccl_meta <- subset(ccl_meta, Primary.Disease != "unknown" & Primary.Disease != "primary cells" & !grepl("MERGED", CCLE_Name, fixed = TRUE))
-ccl_meta$Cell_line <- as.character(lapply(ccl_meta$CCLE_Name, function(x) strsplit(as.character(x), split = "_")[[1]][1]))
-ccl_meta$Histology <- tolower(gsub("^[a-z0-9]*_", "", ccl_meta$CCLE_Name, ignore.case = TRUE))
-# Convert Primary.Disease entries to all lower case to fix factorization issue
-ccl_meta$Primary.Disease <- as.factor(tolower(ccl_meta$Primary.Disease))
-# Harmonize ID column name
-colnames(ccl_meta)[colnames(ccl_meta) == "DepMap_ID"] <- "Broad_ID"
-
+ccl_meta <- read.delim("./data_munging/19Q2/sample_info.csv", sep = ",", header = TRUE, na.strings = c("", NA))
+ccl_meta <- select(ccl_meta, DepMap_ID, stripped_cell_line_name, CCLE_name, disease)
+colnames(ccl_meta) <- c("DepMap_ID", "Cell_line", "CCLE_name", "disease")
 # Remove two rows that contain cell lines with two different histologies
@@
 # MS1, lung: https://web.expasy.org/cellosaurus/CVCL_1429, https://cellmodelpassports.sanger.ac.uk/passports/SIDM00245
-ccl_meta <- subset(ccl_meta, CCLE_Name != "KMH2_THYROID" & CCLE_Name != "MS1_SKIN")
+ccl_meta <- subset(ccl_meta, CCLE_name != "KMH2_THYROID" & CCLE_name != "MS1_SKIN")
+ccl_meta <- subset(ccl_meta, !grepl("MERGED", CCLE_name, fixed = TRUE))
+ccl_diseases <- as.character(unique(ccl_meta$disease))[as.character(unique(ccl_meta$disease)) != " "]
+CCLE_histology <- tolower(gsub("^[a-z0-9]*_", "", ccl_meta$CCLE_name, ignore.case = TRUE))
+ccl_meta <- add_column(ccl_meta, CCLE_histology = CCLE_histology, .after = "CCLE_name")
+ccl_meta$disease <- with(ccl_meta, ifelse(disease == " " & Histology %in% ccl_diseases, as.character(Histology), as.character(disease)))
+ccl_meta$disease <- with(ccl_meta, ifelse(disease == "ovary", "ovarian",
+                                   ifelse(disease == " " & Histology == "vulva", "vulva",
+                                   ifelse(disease == " " & Histology == "stomach", "gastric",
+                                   ifelse(disease == " " & Histology == "upper_aerodigestive_tract", "upper_aerodigestive_tract",
+                                   ifelse(disease == " " & Histology == "large_intestine", "colorectal",
+                                   ifelse(disease == " " & Histology == "biliary_tract", "bile_duct",
+                                   ifelse(disease == " " & Histology == "oesophagus", "esophagus",
+                                   ifelse(disease == " " & Histology == "testis", "embryo", disease)))))))))
 ```
@@
 
-```{r g2p_parsing_functions}
-ExtractBiomarkerType <- function(json_string) {
-  json_string <- as.character(json_string)
-  biomarker_type <- ((str_extract(string = json_string, pattern = "biomarker_type.+") %>% strsplit(split = ","))[[1]][1] %>% str_extract(pattern = "u'.+") %>% str_match("'(.*?)'"))[,2]
-  return(biomarker_type)
-}
-```
-
-```{r g2p_parsing, eval=FALSE}
-# g2p_json <- "./../htscreens_giant_files/g2p_all.json"
-# g2p_all <- fromJSON(sprintf("[%s]", paste(readLines(g2p_json), collapse = ",")), flatten = TRUE)
-# saveRDS(g2p_all, "./../htscreens_giant_files/g2p_all_flattened_json.rds", compress = "xz")
-
-g2p <- read.delim("./data_munging/g2p_full_level_A_dataset_NEW_DEC_2_2018_withGroupedLineages.csv", sep = "\t", header = TRUE)
-g2p[, 1:2] <- NULL
-g2p <- unfactorize(g2p)
-g2p$Drug <- tolower(g2p$Drug)
-g2p[g2p == -1] <- NA
-g2p$Gene <- ifelse(is.na(g2p$Gene) & g2p$Drug == "daunorubicin", "MLL", as.character(g2p$Gene))
-g2p$Direction <- ifelse(g2p$Direction == 1 | g2p$Direction == "", NA, as.character(g2p$Direction))
-g2p$Ref[g2p$Ref == "None" | g2p$Ref == "-" | is.na(g2p$Ref)] <- ""
-g2p$Alt[g2p$Alt == "None" | g2p$Alt == "-" | is.na(g2p$Alt)] <- ""
-g2p <- g2p[, c("Drug", "DrugID", "Direction", "Gene", "Ref", "Alt", "Start", "End", "Chromosome", "Feature.Names", "Mutation", "JSON", "Evidence.Level", "Phenotype.Description", "Phenotype.Family", "Phenotype.ID", "Sequence.ID", "grouped_general_doid")]
-g2p <- add_column(g2p, Ref_Length = nchar(as.character(g2p$Ref)), .after = "Ref")
-g2p <- add_column(g2p, Alt_Length = nchar(as.character(g2p$Alt)), .after = "Alt")
-g2p <- add_column(g2p, Variant_Length = NA, .after = "Alt_Length")
-g2p$Variant_Length <-
-  ifelse(g2p$Alt_Length == 1 & g2p$Ref_Length == 1, 1,
-  ifelse(g2p$Alt_Length == 2 & g2p$Ref_Length == 2, 2,
-  ifelse(g2p$Alt_Length == 3 & g2p$Ref_Length == 3, 3,
-  ifelse(g2p$Ref_Length == g2p$Alt_Length & g2p$Ref_Length > 3, g2p$Ref_Length,
-  ifelse(g2p$Ref_Length != g2p$Alt_Length, abs(g2p$Ref_Length - g2p$Alt_Length), NA)))))
-g2p <- add_column(g2p, Variant_Type = NA, .after = "Alt_Length")
-g2p$Variant_Type <-
-  ifelse(g2p$Alt_Length == 1 & g2p$Ref_Length == 1, "SNP",
-  ifelse(g2p$Alt_Length == 2 & g2p$Ref_Length == 2, "DNP",
-  ifelse(g2p$Alt_Length == 3 & g2p$Ref_Length == 3, "TNP",
-  ifelse(g2p$Ref_Length == g2p$Alt_Length & g2p$Ref_Length > 3, "ONP",
-  ifelse(g2p$Ref_Length > g2p$Alt_Length, "DEL",
-  ifelse(g2p$Ref_Length < g2p$Alt_Length, "INS", "None"))))))
-g2p <- subset(g2p, grepl("^CID", g2p$DrugID))
-g2p <- add_column(g2p, biomarker_type = tolower(sapply(g2p$JSON, ExtractBiomarkerType, simplify = TRUE)), .after = "Feature.Names")
-g2p <- add_column(g2p, biomarker_type_curated = NA, .after = "biomarker_type")
-# Manually assign biomarker_types based on a combination of biomarker_type derived from the JSON string and patterns in the Feature.Names
-biomarker_type_curated <-
-  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "splice")) | !is.na(str_match(string = g2p$biomarker_type, pattern = "splice")), "Splice_Site",
-  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "Amplification|amplification")), "amplification",
-  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "^PDGFRA [(]")) | !is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "mutant|mutation|mut")), "mutation",
-  ifelse(!is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "fusion")) | !is.na(str_match(string = tolower(g2p$biomarker_type), pattern = "fusion")), "fusion", 
-  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "[A-Z0-9|A-Z]+-[A-Z0-9|A-Z]+")) & is.na(str_match(string = g2p$Feature.Names, pattern = "[0-9]+-[0-9]+")), "fusion",
-  ifelse(g2p$Variant_Type == "DEL" & g2p$Variant_Length %% 3 == 0, "In_Frame_Del",
-  ifelse(g2p$Variant_Type == "DEL" & g2p$Variant_Length %% 3 != 0, "Frame_Shift_Del",
-  ifelse(g2p$Variant_Type == "INS" & g2p$Variant_Length %% 3 == 0, "In_Frame_Ins",
-  ifelse(g2p$Variant_Type == "INS" & g2p$Variant_Length %% 3 != 0, "Frame_Shift_Ins",
-  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "EGFR E746_A750del")), "In_Frame_Del",
-  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "EGFR H773>PNPY")), "In_Frame_Ins",
-  ifelse(g2p$Feature.Names == "KRAS G12G" | g2p$Feature.Names == "KRAS G13G", "Silent",
-  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "[A-Z][0-9]+[A-WYZ]")) | !is.na(str_match(string = g2p$biomarker_type, pattern = "missense")), "Missense_Mutation",
-  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "[A-Z][0-9]+([X]|[*])")), "Nonsense_Mutation",
-  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "positive")), "positive",
-  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "expression")), "expression",
-  ifelse(g2p$biomarker_type == "rearrange", "rearrangement",
-  ifelse(g2p$biomarker_type == "intron variant", "Intron",
-  ifelse(g2p$biomarker_type == "inframe_deletion" | !is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "inframe deletion")), "In_Frame_Del",
-  ifelse(g2p$biomarker_type == "inframe_insertion" | !is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "inframe insertion")), "In_Frame_Ins",
-  ifelse(!is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "biallelic inactivation")), "biallelic inactivation", NA)))))))))))))))))))))
-g2p$biomarker_type_curated <- biomarker_type_curated[,1]
-g2p$Drug_Gene <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene), NA, paste0(g2p$Drug, "_", g2p$Gene))
-g2p$position <- paste0("g.chr", g2p$Chromosome, ":", g2p$End, g2p$Ref, ">", g2p$Alt)
-g2p$position <- ifelse(grepl("NA", g2p$position), NA, g2p$position)
-g2p <- merge(lineage_converter, g2p, by = "grouped_general_doid", all.y = TRUE)
-g2p$Drug_Gene_Lin <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene) | is.na(g2p$group_general_lineage_name), NA, paste0(g2p$Drug, "_", g2p$Gene, "_", g2p$group_general_lineage_name))
-
-# write.csv(g2p, "./data_munging/g2p_db_edited.csv")
-
-# g2p_dgls <-  unique (g2p$Drug_Gene_Lin[!is.na(g2p$Drug_Gene_Lin)])
-# g2p_druggenes <- unique(g2p$Drug_Gene[!is.na(g2p$Drug_Gene)])
-# g2p_drugs <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[1]))
-# g2p_genes <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[2]))
-# g2p_lins <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[3]))
-# g2p_druggenes
-# g2p_drugs
-# g2p_genes
-# g2p_lins
-
-# Order and genes taken from pink heatmap from Daniel's analyses
-# g2p_genes <- c("EGFR", "KRAS", "ERBB2", "ERBB3", "MET", "ALK", "ROS1", "PDGFRA", "ABL1", "KIT", "PDGFRB", "PDGFB", "BRAF", "G6PD", "RET", "BRCA1", "BRCA2", "UGT1A1", "TSC1", "TSC2", "AKT1", "IDH2", "DPYD", "ESR1", "CYP19A1", "TPMT", "FLT3", "NPM1", "DNMT3A", "PML", "PTCH1", "JAK2", "MYD88", "MGMT")
-```
-
 ```{r g2p}
-g2p <- read.delim("./data_munging/g2p_db_edited.csv", sep = ",", header = TRUE)
+g2p <- read.delim("./data_munging/g2p_db_edited.csv", sep = ",", header = TRUE, row.names = 1)
+g2p$Drug_Gene_Lin <- gsub(pattern = " cancer", "", g2p$Drug_Gene_Lin)
 
@@
 g2p_lins <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[3]))
-```
-
-```{r testing, eval=FALSE}
-g2p$JSON[1]
-test <- filter(g2p, is.na(Gene))
-test$JSON[2]
-
-unique(g2p$group_general_lineage_name)
-levels(g2p$group_general_lineage_name)
-
-g2p_nonCID <- subset(g2p, !grepl("^CID", g2p$DrugID))
-summ <- g2p_nonCID %>% group_by(Drug, DrugID) %>% tally() %>% summarize(DrugID = DrugID, n = n, percent = formatC(n / 402 * 100, digits = 6, format = "f"))
-summ
 ```
@@
 ```{r mutation_status, eval=FALSE}
-maf_raw <- read.delim("./data_munging/19Q1/depmap_19Q1_mutation_calls_20190305.csv.gz", header = TRUE, sep = ",", row.names = 1)
-# Harmonize ID column name
-colnames(maf_raw)[colnames(maf_raw) == "DepMap_ID"] <- "Broad_ID"
+maf_raw <- read.delim("./data_munging/19Q2/CCLE_mutations_20190514.csv.gz", header = TRUE, sep = ",")
+maf_raw[, 1:2] <- NULL
 colnames(maf_raw)[colnames(maf_raw) == "Hugo_Symbol"] <- "Gene"
+maf_raw <- unfactorize(maf_raw)
 # Select columns
-maf_df <- subset(maf_raw, select = c("Gene", "Broad_ID", "Variant_Classification", "Reference_Allele", "Tumor_Seq_Allele1"))
-maf_df$Reference_Allele <- ifelse(maf_df$Reference_Allele == "-", 0, nchar(as.character(maf_df$Reference_Allele)))
-maf_df$Tumor_Seq_Allele1 <- nchar(as.character(maf_df$Tumor_Seq_Allele1))
-maf_df <- maf_df[maf_df$Variant_Classification != "Silent",]
-# Add Mutation_Status column
-maf_df$Mutation_Status <- 1
-maf_df$PointMutation <- with(maf_df, ifelse(Reference_Allele == 1 | is.na(Reference_Allele), TRUE, ifelse(Reference_Allele == 0 & Tumor_Seq_Allele1 == 1, 1, 0)))
-maf_df <- unfactorize(maf_df)
+maf <- subset(maf_raw, select = c("Gene", "DepMap_ID", "Variant_Classification", "Variant_Type"))
+maf <- maf[!is.na(maf$Variant_Classification),]
+maf <- maf[maf$Variant_Classification %in% unique(g2p$biomarker_type_curated),]
+maf$Mutation <- 1
+maf_df <- dcast(maf, Gene + DepMap_ID ~ Variant_Classification, fun.aggregate = mean, fill = 0)
+maf_df_summ <- colSums(maf_df[, 3:ncol(maf_df)])
 
-saveRDS(maf_df, "./data_munging/19Q1/maf_df_19Q1.rds", compress = "xz")
+saveRDS(maf_df, "./data_munging/19Q2/maf_df_19Q2.rds", compress = "xz")
 ```
@@
 
-```{r fusion_calls_19Q2, eval=FALSE}
+```{r fusion_calls, eval=TRUE}
 fusions <- read.delim("./data_munging/19Q2/CCLE_fusions.csv.gz", header = TRUE, sep = ",")
@@
 fusions <- as.data.frame(lapply(fusions, function(x) gsub("IGH@|IGH-@", "IGH", x)))
-colnames(fusions) <- c("Broad_ID", "FusionPair")
+colnames(fusions) <- c("DepMap_ID", "FusionPair")
+fusions <- merge(fusions, ccl_meta, by = "DepMap_ID", all.x = TRUE)
 ```
@@
 ```{r copy_number, eval=FALSE}
-cn <- read.delim("./data_munging/19Q1/public_19Q1_gene_cn_20190305.csv.gz", sep = ",", check.names = FALSE, header = TRUE)
+cn <- read.delim("./data_munging/19Q2/CCLE_gene_cn_20190514.csv.gz", sep = ",", check.names = FALSE, header = TRUE)
 # Remove Entrez gene IDs from colnames, format is "Gene (Entrez ID)"
 colnames(cn) <- gsub(" .*", "", colnames(cn))
-colnames(cn)[1] <- "Broad_ID"
+colnames(cn)[1] <- "DepMap_ID"
 # Melt
-cn_melt <- melt(data = cn, id.vars = "Broad_ID", measure.vars = colnames(cn[2:ncol(cn)]), variable.name = "Gene", value.name = "CN")
+cn_melt <- melt(data = cn, id.vars = "DepMap_ID", measure.vars = colnames(cn[2:ncol(cn)]), variable.name = "Gene", value.name = "CN")
 cn_melt <- unfactorize(cn_melt)
 
-saveRDS(cn_melt, "./data_munging/19Q1/cn_melt_19Q1.rds", compress = "xz")
+saveRDS(cn_melt, "./data_munging/19Q2/cn_melt_19Q2.rds", compress = "xz")
 ```
 
-19Q1, CCLE RNAseq gene expression data:
+19Q2, CCLE RNAseq gene expression data:
 ```{r gene_expression, eval=FALSE}
-ge <- read.delim("./../htscreens_giant_files/CCLE_depMap_19Q1_TPM_20190305.csv.gz", header = TRUE, sep = ",", check.names = FALSE)
+ge <- read.delim("./../htscreens_giant_files/CCLE_depMap_19Q2_TPM_20190305.csv.gz", header = TRUE, sep = ",", check.names = FALSE)
 # Remove Entrez gene IDs from colnames, format is "Gene (Entrez ID)"
 colnames(ge) <- gsub(" .*", "", colnames(ge))
-colnames(ge)[1] <- "Broad_ID"
+colnames(ge)[1] <- "DepMap_ID"
 # Melt
-ge_melt <- melt(ge, id.vars = "Broad_ID", measure.vars = colnames(ge)[2:ncol(ge)], variable.name = "Gene", value.name = "TPM")
+ge_melt <- melt(ge, id.vars = "DepMap_ID", measure.vars = colnames(ge)[2:ncol(ge)], variable.name = "Gene", value.name = "TPM")
 ge_melt$TPM <- log2(ge_melt$TPM + 1)
@@
 
-saveRDS(ge_melt, "./data_munging/19Q1/ge_melt_19Q1.rds", compress = "xz")
+saveRDS(ge_melt, "./data_munging/19Q2/ge_melt_19Q2.rds", compress = "xz")
 ```
@@
 ```{r load_omics_rds}
-maf_df <- readRDS("./data_munging/19Q1/maf_df_19Q1.rds")
-cn_melt <- readRDS("./data_munging/19Q1/cn_melt_19Q1.rds")
-ge_melt <- readRDS("./data_munging/19Q1/ge_melt_19Q1.rds")
-```
-
-```{r omics_testing, eval=FALSE}
-test <- filter(maf_df, Gene %in% g2p_genes) %>% count(Gene, Broad_ID)
-test <- test[order(test$n, decreasing = TRUE),]
+maf_df <- readRDS("./data_munging/19Q2/maf_df_19Q2.rds")
+cn_melt <- readRDS("./data_munging/19Q2/cn_melt_19Q2.rds")
+ge_melt <- readRDS("./data_munging/19Q2/ge_melt_19Q2.rds")
 ```
@@
   if(database %in% c("CCLE", "CTRP", "GDSC")) {
-    filt <- auc %>% filter(Database == database) %>% select(Cell_line, Histology, TCGA_classification, CCLE_Name, Broad_ID, Drug, AUC_IC50)
+    filt <- auc %>% filter(Database == database) %>% select(Cell_line, Histology, TCGA_classification, CCLE_Name, DepMap_ID, Drug, AUC_IC50)
     print(paste0("Processing ", database, " data."))
@@
     # Merge metadata
-    data <-  merge(data, select(ccl_meta, Cell_line, Histology, CCLE_Name, Broad_ID, Primary.Disease), by = c("Cell_line", "Histology", "CCLE_Name", "Broad_ID"), all.y = TRUE)
+    data <-  merge(data, select(ccl_meta, Cell_line, Histology, CCLE_Name, DepMap_ID, Primary.Disease), by = c("Cell_line", "Histology", "CCLE_Name", "DepMap_ID"), all.y = TRUE)
     ## Add columns for G2P drug-gene and drug-gene-lineage sorting
@@
     data <- unfactorize(data)
-    data <- merge(data, maf_df, by = c("Gene", "Broad_ID"), all.x = TRUE)
+    data <- merge(data, maf_df, by = c("Gene", "DepMap_ID"), all.x = TRUE)
     data$Mutation_Status <- ifelse(is.na(data$Mutation_Status), 0, data$Mutation_Status)
@@
     # Melt CRISPR dataset for merging
-    data <- melt(crispr_all, id.vars = "Broad_ID", measure.vars = colnames(crispr_all)[2:ncol(crispr_all)], variable.name = "Gene", value.name = "Score")
+    data <- melt(crispr_all, id.vars = "DepMap_ID", measure.vars = colnames(crispr_all)[2:ncol(crispr_all)], variable.name = "Gene", value.name = "Score")
     # Get all G2P gene-cell line combinations
@@
     # Merge cell line metadata
-    data <- merge(data, select(ccl_meta, Cell_line, Histology, CCLE_Name, Broad_ID, Primary.Disease), by = "Broad_ID", all.y = TRUE)
+    data <- merge(data, select(ccl_meta, Cell_line, Histology, CCLE_Name, DepMap_ID, Primary.Disease), by = "DepMap_ID", all.y = TRUE)
     data$Drug_Gene <- paste0(data$Drug, "_", data$Gene)
@@
   print("Merged mutation calls.")
-
   # Merge GE data
-  data <- merge(data, ge_df, by = c("Gene", "Broad_ID"), all.x = TRUE)
+  data <- merge(data, ge_df, by = c("Gene", "DepMap_ID"), all.x = TRUE)
   print("Merged gene expression data.")
-
   # Merge CN data
-  data <- merge(data, cn_df, by = c("Gene", "Broad_ID"), all.x = TRUE)
+  data <- merge(data, cn_df, by = c("Gene", "DepMap_ID"), all.x = TRUE)
   print("Merged copy number data.")
-
   # Drop cell lines not in DepMap
-  data <- filter(data, !is.na(Broad_ID) & !(Broad_ID %in% c("ACH-001182", "ACH-001451")))
-
-  # Factorize gene
-  data$Gene <- factor(data$Gene)
-
+  data <- filter(data, !is.na(DepMap_ID) & !(DepMap_ID %in% c("ACH-001182", "ACH-001451")))
   # Save and return dataframe
+  data <- unfactorize(data)
   saveRDS(data, outfile, compress = "xz")
@@
 }
-
-# FilterForPointMuts <- function(dataframe, outfile) {
-#   # Filter for point mutations
-#   ptmuts <- filter(dataframe, PointMutation == 1)
-#   # Remove columns that lead to duplicate mutation entries
-#   ptmuts <- subset(ptmuts, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, PointMutation))
-#   ptmuts$Gene <- ordered(ptmuts$Gene, levels = g2p_genes)
-#   ptmuts <- unique(ptmuts)
-#   saveRDS(ptmuts, outfile, compress = "xz")
-#   return(ptmuts)
-# }
 ```
@@
 
-ccle <- MergeOmicsG2P(database = "CCLE", maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, outfile = "./data_munging/rds/ccle_data_19Q1.rds")
-# ctrp <- MergeOmicsG2P(database = "CTRP", maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, outfile = "./../htscreens_giant_files/ctrp_data_19Q1.rds")
-# gdsc <- MergeOmicsG2P(database = "GDSC", maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, outfile = "./data_munging/rds/gdsc_data_19Q1.rds")
-
-# Omics metadata
-# maf_df_ptmuts <- unique(filter(maf_df, Gene %in% g2p_genes & PointMutation == 1)
-# ge_filt <- filter(ge_melt, Gene %in% g2p_genes)
-# cn_filt <- filter(cn_melt, Gene %in% g2p_genes)
-# ccle_ptmuts <- MergeOmicsG2P(database = "CCLE", maf_df = maf_df_ptmuts, ge_df = ge_filt, cn_df = cn_filt, outfile = "./data_munging/rds/ccle_data_19Q1_g2pgenes_ptmuts.rds")
-# ctrp_ptmuts <- MergeOmicsG2P(database = "CTRP", maf_df = maf_df_ptmuts, ge_df = ge_filt, cn_df = cn_filt, outfile = "./../htscreens_giant_files/ctrp_data_19Q1_g2pgenes_ptmuts.rds")
-# gdsc_ptmuts <- MergeOmicsG2P(database = "GDSC", maf_df = maf_df_ptmuts, ge_df = ge_filt, cn_df = cn_filt, outfile = "./data_munging/rds/gdsc_data_19Q1_g2pgenes_ptmuts.rds")
+ccle <- MergeOmicsG2P(database = "CCLE", maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, outfile = "./data_munging/rds/ccle_data_19Q2.rds")
+# ctrp <- MergeOmicsG2P(database = "CTRP", maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, outfile = "./../htscreens_giant_files/ctrp_data_19Q2.rds")
+# gdsc <- MergeOmicsG2P(database = "GDSC", maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, outfile = "./data_munging/rds/gdsc_data_19Q2.rds")
 ```
@@
 ccle_missense <- filter(ccle, Variant_Classification == "Missense_Mutation")
-ccle_missense_grid <- expand.grid("Gene" = unique(ccle_missense$Gene), "Broad_ID" = unique(ccle_missense$Broad_ID))
+ccle_missense_grid <- expand.grid("Gene" = unique(ccle_missense$Gene), "DepMap_ID" = unique(ccle_missense$DepMap_ID))
 ccle_missense_grid$Variant_Classification <- NA
-ccle_missense <- merge(ccle_missense, ccle_missense_grid, by = c("Gene", "Broad_ID", "Variant_Classification"), all = TRUE)
+ccle_missense <- merge(ccle_missense, ccle_missense_grid, by = c("Gene", "DepMap_ID", "Variant_Classification"), all = TRUE)
 ```
@@
 ```{r load_drug_rds, eval=TRUE}
-ccle_ptmuts <- readRDS("./data_munging/rds/ccle_data_19Q1_g2pgenes_ptmuts.rds") %>% drop_na(Drug)
-ctrp_ptmuts <- readRDS("./../htscreens_giant_files/ctrp_data_19Q1_g2pgenes_ptmuts.rds") %>% drop_na(Drug)
-gdsc_ptmuts <- readRDS("./data_munging/rds/gdsc_data_19Q1_g2pgenes_ptmuts.rds") %>% drop_na(Drug)
+ccle_ptmuts <- readRDS("./data_munging/rds/ccle_data_19Q2_g2pgenes_ptmuts.rds") %>% drop_na(Drug)
+ctrp_ptmuts <- readRDS("./../htscreens_giant_files/ctrp_data_19Q2_g2pgenes_ptmuts.rds") %>% drop_na(Drug)
+gdsc_ptmuts <- readRDS("./data_munging/rds/gdsc_data_19Q2_g2pgenes_ptmuts.rds") %>% drop_na(Drug)
 
@@
 
-## CRISPR
-
-Merge all CRISPR genes:
-```{r merge_crispr_data, eval=FALSE}
-crispr_all <- read.delim("./data_munging/19Q1/gene_effect_corrected_20190305.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
-# Remove Entrez gene IDs from colnames
-colnames(crispr_all) <- gsub(" .*", "", colnames(crispr_all))
-colnames(crispr_all)[1] <- "Broad_ID"
-
-# Melt CRISPR dataset for merging
-crispr_melt <- melt(crispr_all, id.vars = "Broad_ID", measure.vars = colnames(crispr_all)[2:ncol(crispr_all)], variable.name = "Gene", value.name = "Score")
-
-# Merge cell line metadata
-crispr_melt <- merge(crispr_melt, ccl_meta, by = "Broad_ID", all.x = TRUE)
-test_crispr <- unique(select(crispr_melt, Broad_ID, Histology)) %>% count(Histology)
-
-# Merge mutation annotations
-maf_filt_crispr <- unique(filter(maf_df, Gene %in% as.character(unique(crispr_melt$Gene)) & PointMutation == 1) %>% select(-c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, PointMutation)))
-crispr_muts <- merge(crispr_melt, maf_filt_crispr, by = c("Gene","Broad_ID"), all.x = TRUE)
-crispr_muts$Mutation_Status <- ifelse(is.na(crispr_muts$Mutation_Status), 0, crispr_muts$Mutation_Status)
-
-# Summarize number of mutant and Wildtype cell lines
-crispr_muts_summ <- crispr_muts %>% group_by(Gene) %>% summarize(N_Wildtype = length(Mutation_Status) - sum(Mutation_Status == 1), N_Mutant = sum(Mutation_Status == 1))
-## Merge test results back into full dataset, which restores information lost in the summarization
-crispr_data <- merge(crispr_muts_summ, crispr_muts, by = "Gene")
-crispr_data$Mutation_Status <- factor(crispr_data$Mutation_Status)
-
-# Cell line lineages
-crispr_data <- merge(crispr_data, cn_melt, by = c("Gene", "Broad_ID"), all.x = TRUE)
-
-# Gene expression (RPKM)
-ge_crispr <- filter(ge_melt, Gene %in% as.character(unique(crispr_melt$Gene)))
-crispr_data <- merge(crispr_data, ge_crispr, by = c("Gene", "Broad_ID"), all.x = TRUE)
-
-saveRDS(crispr_data, "./data_munging/rds/crispr_data_19Q1_ptmuts.rds", compress = "xz")
-
-# Filter G2P CRISPR for point mutations
-# crispr_ptmuts <- filter(crispr_data, PointMutation == 1)
-# crispr_ptmuts <- subset(crispr_ptmuts, select = -c(PointMutation))
-# crispr_ptmuts <- filter(crispr_ptmuts, Gene %in% g2p_genes)
-# crispr_ptmuts$Primary.Disease <- factor(crispr_ptmuts$Primary.Disease)
-# crispr_ptmuts$Mutation_Status <- factor(crispr_ptmuts$Mutation_Status)
-# saveRDS(crispr_ptmuts, "./data_munging/rds/crispr_data_19Q1_g2pgenes_ptmuts.rds", compress = "xz")
-```
-
-```{r load_crispr_filter, eval=TRUE}
-# crispr_data <- readRDS("./data_munging/rds/crispr_data_19Q1.rds")
-crispr_ptmuts <- readRDS("./data_munging/rds/crispr_data_19Q1_ptmuts.rds")
-```
-
-# DATA SUMMARY FIGURES
-
---------------------------------------------------------------------------------
-
-## Mutation
-
-## Cell line and drug overlaps
-
-```{r ccl_venn, eval=FALSE}
-ccle_ccls <- unique(ccle_ptmuts$Broad_ID)
-ctrp_ccls <- unique(ctrp_ptmuts$Broad_ID)
-gdsc_ccls <- unique(gdsc_ptmuts$Broad_ID)
-crispr_ccls <- unique(crispr_ptmuts$Broad_ID)
-
-futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
-venn.diagram(x = list(ccle_ccls, ctrp_ccls, gdsc_ccls, crispr_ccls),
-             filename = "./plots/manuscript/all_venn_ccls.png",
-             output = TRUE, imagetype = "png",
-             height = 2000, width = 2000, resolution = 500,
-             lwd = 1, cex = 1,
-             category.names = c("CCLE", "CTRP", "GDSC", "CRISPR"),
-             cat.cex = 1.4, cat.fontface = "bold", cat.default.pos = "outer",
-             # cat.dist = c(0.06, 0.06, 0.035),
-             fill = c("springgreen4", "steelblue4", "turquoise4", "darkorchid"))
-futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
-venn.diagram(x = list(ccle_ccls, ctrp_ccls, gdsc_ccls),
-             filename = "./plots/manuscript/drug_venn_ccls.png",
-             output = TRUE, imagetype = "png",
-             height = 2000, width = 2000, resolution = 500,
-             lwd = 1, cex = 1.4,
-             category.names = c("CCLE", "CTRP", "GDSC"),
-             cat.cex = 1.4, cat.fontface = "bold", cat.default.pos = "outer",
-             cat.dist = c(0.06, 0.06, 0.035),
-             fill = c("springgreen4", "steelblue4", "turquoise4"))
-```
-
-```{r drug_venn, eval=FALSE}
-ccle_drugs <- unique(ccle_ptmuts$Drug)
-ctrp_drugs <- unique(ctrp_ptmuts$Drug)
-gdsc_drugs <- unique(gdsc_ptmuts$Drug)
-
-futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
-venn.diagram(x = list(ccle_drugs, ctrp_drugs, gdsc_drugs),
-             filename = "./plots/manuscript/drug_venn_drugs.png",
-             output = TRUE, imagetype = "png",
-             height = 2000, width = 2000, resolution = 500,
-             lwd = 1, cex = 1.4,
-             category.names = c("CCLE", "CTRP", "GDSC"),
-             cat.cex = 1.4, cat.fontface = "bold", cat.default.pos = "outer",
-             cat.dist = c(0.06, 0.06, 0.035),
-             fill = c("palegreen3", "slategray3", "paleturquoise3"))
-```
-
-## Histology distributions
-
-```{r histology_dists_data, eval=FALSE}
-ccle_hists <- unique(select(ccle_ptmuts, Broad_ID, Primary.Disease)) %>% count(Primary.Disease)
-ccle_hists$Perc <- ccle_hists$n / sum(ccle_hists$n) * 100
-ccle_hists$Dataset <- "CCLE"
-ctrp_hists <- unique(select(ctrp_ptmuts, Broad_ID, Primary.Disease)) %>% count(Primary.Disease)
-ctrp_hists$Perc <- ctrp_hists$n / sum(ctrp_hists$n) * 100
-ctrp_hists$Dataset <- "CTRP"
-gdsc_hists <- unique(select(gdsc_ptmuts, Broad_ID, Primary.Disease)) %>% count(Primary.Disease)
-gdsc_hists$Perc <- gdsc_hists$n / sum(gdsc_hists$n) * 100
-gdsc_hists$Dataset <- "GDSC"
-crispr_hists <- unique(select(crispr_ptmuts, Broad_ID, Primary.Disease)) %>% count(Primary.Disease)
-crispr_hists$Perc <- crispr_hists$n / sum(crispr_hists$n) * 100
-crispr_hists$Dataset <- "CRISPR"
-
-drug_hists <- rbind(ccle_hists, ctrp_hists, gdsc_hists, crispr_hists) %>% drop_na(Primary.Disease)
-drug_hists$Dataset <- factor(drug_hists$Dataset, levels = c("CCLE", "CTRP", "GDSC", "CRISPR"))
-drug_hists$Primary.Disease <- as.character(drug_hists$Primary.Disease)
-drug_hists$Primary.Disease <- gsub(" cancer", "", drug_hists$Primary.Disease)
-saveRDS(drug_hists, "./data_munging/rds/histology_distributions.rds")
-```
-
-```{r histology_dists, fig.height=4.5, fig.width=4}
-drug_hists <- readRDS("./data_munging/rds/histology_distributions.rds")
-# png(filename = "./plots/manuscript/all_histology_distributions.png", width = 8, height = 9, units = "in", res = 500)
-ggplot(drug_hists, aes(x = Dataset, y = n, fill = Primary.Disease)) +
-  geom_bar(stat = "identity", color = "black") +
-  scale_y_continuous(breaks = seq(0, 850, by = 50), labels = seq(0, 850, by = 50)) +
-  guides(fill = guide_legend(title = "Histology", ncol = 1)) +
-  labs(y = "Count")
-# dev.off()
-```
-
-```{r, eval=FALSE}
-ccle_ccls <- unique(ccle_ptmuts$Broad_ID)
-ctrp_ccls <- unique(ctrp_ptmuts$Broad_ID)
-gdsc_ccls <- unique(gdsc_ptmuts$Broad_ID)
-crispr_ccls <- unique(crispr_ptmuts$Broad_ID)
-
-ccls <- data.frame(Broad_ID = union(ccle_ccls, union(ctrp_ccls, gdsc_ccls)))
-all_ccls <- merge(ccls, ccl_meta, by = "Broad_ID")
-all_ccls$Primary.Disease <- gsub(" cancer", "", all_ccls$Primary.Disease)
-
-png(filename = "./plots/manuscript/drug_histology_distributions.png", width = 8, height = 4, units = "in", res = 500)
-ggplot(all_ccls, aes(x = fct_infreq(factor(Primary.Disease)), fill = Primary.Disease)) +
-  geom_bar(color = "black") +
-  scale_y_continuous(breaks = seq(0, 220, by = 40), labels = seq(0, 220, by = 40)) +
-  guides(fill = FALSE) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
-  labs(y = "Number of Cell Lines", x = "Histology", caption = paste0(formatC(nrow(all_ccls), format = "d", big.mark = ","), " cell lines represented."))
-dev.off()
-```
-
-## G2P summary heatmap
-
-```{r dg_heatmap, fig.height=6, fig.width=8, warning=FALSE}
-g2p_dg_counts <- g2p %>% count(Drug, Gene) %>% filter(!is.na(Drug), !is.na(Gene))
-g2p_dg_counts <- dcast(g2p_dg_counts, Drug ~ Gene, value.var = "n", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Drug)
-g2p_dg_counts <- g2p_dg_counts[order(rowSums(-g2p_dg_counts)), order(colSums(-g2p_dg_counts))]
-g2p_dg_counts[g2p_dg_counts == 0] <- NA
-
-g2p_gene_order <- colnames(g2p_dg_counts)
-g2p_drug_order <- rownames(g2p_dg_counts)
-
-# Create annotation layer
-hta_data <- data.frame(Drug = rownames(g2p_dg_counts), CCLE = NA, CTRP = NA, GDSC = NA)
-hta_data$CCLE <- ifelse(hta_data$Drug %in% unique(ccle_ptmuts$Drug), "Screened", "Not screened")
-hta_data$CTRP <- ifelse(hta_data$Drug %in% unique(ctrp_ptmuts$Drug), "Screened", "Not screened")
-hta_data$GDSC <- ifelse(hta_data$Drug %in% unique(gdsc_ptmuts$Drug), "Screened", "Not screened")
-rownames(hta_data) <- hta_data$Drug
-hta_data$Drug <- NULL
-
-hta_annot <- HeatmapAnnotation(text = anno_text(colnames(hta_data), offset = unit(0.1, "in"), gp = gpar(fontsize = 10)))
-hta_legend_list <- list(legend_direction = "horizontal", border = "gray70", nrow = 2)
-hta <- Heatmap(hta_data,
-               name = "Functional screen status           ",
-               col = c("Screened" = "purple4", "Not screened" = "gray97"), 
-               rect_gp = gpar(col = "gray70"),
-               top_annotation = hta_annot,
-               heatmap_legend_param = hta_legend_list,
-               row_names_side = "left",
-               row_names_gp = gpar(fontsize = 10),
-               column_names_side = "top",
-               column_names_gp = gpar(fontsize = 10),
-               show_column_names = FALSE,
-               cluster_rows = FALSE, 
-               cluster_columns = FALSE,
-               row_title = "Drugs",
-               row_title_gp = gpar(fontface = "bold", fontsize = 14),
-               column_title = "Dataset",
-               column_title_gp = gpar(fontface = "bold", fontsize = 14),
-               width = unit(1.5, "in"))
-
-# Define color scale
-col_fun <- colorRamp2(c(0, 100), c("mistyrose", "purple4"))
-# Legend properties list
-ht_legend_list <- list(legend_direction = "horizontal", legend_width = unit(2.5, "in"), border = "gray70")
-ht <- Heatmap(g2p_dg_counts, 
-              name = "Number of G2P interpretations",
-              col = col_fun,
-              na_col = "gray97",
-              rect_gp = gpar(col = "gray70"),
-              heatmap_legend_param = ht_legend_list,
-              cluster_rows = FALSE, 
-              cluster_columns = FALSE, 
-              show_row_names = FALSE,
-              row_names_side = "left",
-              row_names_gp = gpar(fontsize = 10),
-              column_names_side = "bottom",
-              column_names_gp = gpar(fontsize = 10),
-              show_column_names = FALSE,
-              bottom_annotation = HeatmapAnnotation(
-                  text = anno_text(colnames(g2p_dg_counts),
-                                   rot = 45,
-                                   gp = gpar(fontsize = 10),
-                                   offset = unit(1, "npc"),
-                                   just = "right"),
-                  annotation_height = unit(0.45, "in")),
-              row_title = "Drugs",
-              row_title_gp = gpar(fontface = "bold", fontsize = 14),
-              column_title = "Genes", 
-              column_title_gp = gpar(fontface = "bold", fontsize = 14),
-              column_title_side = "bottom")
-
-png(filename = "./plots/manuscript/g2p_summary_heatmap.png", width = 10, height = 9, units = "in", res = 500)
-draw(hta + ht, gap = unit(5, "mm"), heatmap_legend_side = "top")
-dev.off()
-```
-
-## AUC heatmap
-
-```{r}
-ccle_auc_grid <- dcast(filter(ccle_ptmuts, Drug %in% g2p_drugs), Drug ~ Broad_ID, value.var = "Score", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Drug)
-ctrp_auc_grid <- dcast(filter(ctrp_ptmuts, Drug %in% g2p_drugs), Drug ~ Broad_ID, value.var = "Score", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Drug)
-gdsc_auc_grid <- dcast(filter(gdsc_ptmuts, Drug %in% g2p_drugs), Drug ~ Broad_ID, value.var = "Score", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Drug)
-
-ccle_auc_ht <- Heatmap(ccle_auc_grid,
-                       name = "AUC",
-                       show_column_names = FALSE, 
-                       column_title = "CCLE",
-                       column_title_side = "top")
-ctrp_auc_ht <- Heatmap(ctrp_auc_grid,
-                       name = "AUC",
-                       show_column_names = FALSE, 
-                       column_title = "CTRP",
-                       column_title_side = "top")
-gdsc_auc_ht <- Heatmap(gdsc_auc_grid,
-                       name = "AUC",
-                       show_column_names = FALSE, 
-                       column_title = "GDSC",
-                       column_title_side = "top")
-
-draw(ccle_auc_ht)
-draw(ctrp_auc_ht)
-draw(gdsc_auc_ht)
-```
-
-# WILCOXON (MUT)
-
---------------------------------------------------------------------------------
-
-```{r wilcoxon_functions}
-adj_signif <- function(df, alpha) {
-  # Takes df from compare_means and creates a signif code column for FDR-adjusted p-vals
-  df$p.signif.adj <- ifelse(df$p.adj <= alpha, "*", NA)
-  df$p.signif <- ifelse(df$p.signif == "ns", NA, df$p.signif)
-  df$p.short <- formatC(df$p, format = "g", digits =  2)
-  df$p.adj.short <- formatC(df$p.adj, format = "g", digits =  2)
-  return(df)
-}
-
-WilcoxonTestDF <- function(dataframe, grouping, outfile) {
-  require(ggpubr)
-  if("Drug_Gene_Lin" %in% grouping) {
-    # Filter out DGLs with too few samples in at least one mutation status category
-    count_mut_n <- dataframe %>% count(Drug_Gene_Lin, Mutation_Status) %>% filter(n >= 3)
-    count_mut_category <- count_mut_n %>% count(Drug_Gene_Lin) %>% filter(n == 2)
-    dgl_keep <- intersect(count_mut_n$Drug_Gene_Lin, count_mut_category$Drug_Gene_Lin)
-    dataframe <- filter(dataframe, Drug_Gene_Lin %in% dgl_keep)
-    dataframe$Drug_Gene_Lin <- as.character(dataframe$Drug_Gene_Lin)
-  }
-  signif <- compare_means(Score ~ Mutation_Status, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
-  signif <- adj_signif(signif, alpha = 0.05)
-  signif <- signif[order(signif$p),]
-  if("Drug_Gene" %in% grouping) {
-    signif$InG2P <- ifelse(signif$Drug_Gene %in% g2p_druggenes, "Yes", "No")
-  }
-  if("Drug_Gene_Lin" %in% grouping) {
-    signif$InG2P <- ifelse(signif$Drug_Gene_Lin %in% g2p_dgls, "Yes", "No")
-  }
-  saveRDS(signif, outfile)
-  return(signif)
-}
-```
-
-```{r wilcoxon_tests, eval=FALSE}
-crispr_ptmuts <- unfactorize(crispr_ptmuts)
-# crispr_signif_all_gene <- WilcoxonTestDF(dataframe = crispr_ptmuts, grouping = "Gene", outfile = "./data_munging/rds/crispr_signif_gene.rds")
-crispr_ptmuts_filt <- filter(crispr_ptmuts, Gene %in% g2p_genes)
-crispr_signif_gene <- WilcoxonTestDF(dataframe = crispr_ptmuts_filt, grouping = "Gene", outfile = "./data_munging/rds/crispr_signif_g2p_gene.rds")
-crispr_signif_lineage <- WilcoxonTestDF(dataframe = crispr_ptmuts_filt, grouping = c("Gene", "Primary.Disease"), outfile = "./data_munging/rds/crispr_signif_g2p_lineage.rds")
-
-ccle_ptmuts_filt <- filter(ccle_ptmuts, Drug %in% g2p_drugs)
-ccle_ptmuts_filt$Gene <- factor(ccle_ptmuts_filt$Gene, ordered = FALSE)
-ccle_ptmuts_filt <- unfactorize(ccle_ptmuts_filt)
-ccle_signif_gene <- WilcoxonTestDF(dataframe = ccle_ptmuts, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/ccle_signif_g2p_gene.rds")
-ccle_signif_g2p_druggene <- WilcoxonTestDF(dataframe = filter(ccle_ptmuts, Drug %in% g2p_drugs & Gene %in% g2p_genes), grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/ccle_signif_g2p_druggene.rds")
-ccle_signif_lineage <- WilcoxonTestDF(dataframe = ccle_ptmuts_filt, grouping = c("Drug", "Gene", "Primary.Disease", "Drug_Gene_Lin"), outfile = "./data_munging/rds/ccle_signif_g2p_lineage.rds")
-
-ctrp_ptmuts_filt <- filter(ctrp_ptmuts, Drug %in% g2p_drugs)
-ctrp_ptmuts_filt$Gene <- factor(ctrp_ptmuts_filt$Gene, ordered = FALSE)
-ctrp_ptmuts_filt <- unfactorize(ctrp_ptmuts_filt)
-ctrp_signif_gene <- WilcoxonTestDF(dataframe = ctrp_ptmuts, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/ctrp_signif_g2p_gene.rds")
-ctrp_signif_g2p_druggene <- WilcoxonTestDF(dataframe = filter(ctrp_ptmuts, Drug %in% g2p_drugs & Gene %in% g2p_genes), grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/ctrp_signif_g2p_druggene.rds")
-ctrp_signif_lineage <- WilcoxonTestDF(dataframe = ctrp_ptmuts_filt, grouping = c("Drug", "Gene", "Primary.Disease", "Drug_Gene_Lin"), outfile = "./data_munging/rds/ctrp_signif_g2p_lineage.rds")
-
-gdsc_ptmuts_filt <- filter(gdsc_ptmuts, Drug %in% g2p_drugs)
-gdsc_ptmuts_filt$Gene <- factor(gdsc_ptmuts_filt$Gene, ordered = FALSE)
-gdsc_ptmuts_filt <- unfactorize(gdsc_ptmuts_filt)
-gdsc_signif_gene <- WilcoxonTestDF(dataframe = gdsc_ptmuts, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/gdsc_signif_g2p_gene.rds")
-gdsc_signsif_g2p_druggene <- WilcoxonTestDF(dataframe = filter(gdsc_ptmuts, Drug %in% g2p_drugs & Gene %in% g2p_genes), grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/gdsc_signif_g2p_druggene.rds")
-gdsc_signif_lineage <- WilcoxonTestDF(dataframe = gdsc_ptmuts_filt, grouping = c("Drug", "Gene", "Primary.Disease", "Drug_Gene_Lin"), outfile = "./data_munging/rds/gdsc_signif_g2p_lineage.rds")
-```
-
-```{r load_wilcoxon_rds}
-crispr_signif_gene <- readRDS("./data_munging/rds/crispr_signif_g2p_gene.rds")
-crispr_signif_lineage <- readRDS("./data_munging/rds/crispr_signif_g2p_lineage.rds")
-
-ccle_signif_gene <- readRDS("./data_munging/rds/ccle_signif_g2p_gene.rds")
-ccle_signif_g2p_druggene <- readRDS("./data_munging/rds/ccle_signif_g2p_druggene.rds")
-ccle_signif_lineage <- readRDS("./data_munging/rds/ccle_signif_g2p_lineage.rds")
-
-ctrp_signif_gene <- readRDS("./data_munging/rds/ctrp_signif_g2p_gene.rds")
-ctrp_signif_g2p_druggene <- readRDS("./data_munging/rds/ctrp_signif_g2p_druggene.rds")
-ctrp_signif_lineage <- readRDS("./data_munging/rds/ctrp_signif_g2p_lineage.rds")
-
-gdsc_signif_gene <- readRDS("./data_munging/rds/gdsc_signif_g2p_gene.rds")
-gdsc_signif_g2p_druggene <- readRDS("./data_munging/rds/gdsc_signif_g2p_druggene.rds")
-gdsc_signif_lineage <- readRDS("./data_munging/rds/gdsc_signif_g2p_lineage.rds")
-```
-
-## Plots
-
-```{r crispr_mut_gene_plot, fig.height=4, fig.width=8}
-crispr_signif_gene$Gene <- factor(crispr_signif_gene$Gene, levels = g2p_genes)
-crispr_ptmuts_filt <- filter(crispr_ptmuts, Gene %in% g2p_genes)
-crispr_ptmuts_filt$Gene <- factor(crispr_ptmuts_filt$Gene, levels = g2p_genes)
-crispr_ptmuts_filt$Mutation_Status <- as.character(crispr_ptmuts_filt$Mutation_Status)
-
-crispr_gene_mut_plot <- ggplot(data = crispr_ptmuts_filt) +
-  facet_wrap(~ Gene, nrow = 2, drop = FALSE) +
-  scale_color_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "darkorchid", "0" = "thistle")) +
-  scale_x_discrete(name = "Mutation Status", labels = c("0" = "WT", "1" = "Mut")) +
-  geom_jitter(aes(x = Mutation_Status, y = Score, color = Mutation_Status), width = 0.2, alpha = 0.5, size = 0.6) +
-  geom_boxplot(aes(x = Mutation_Status, y = Score), fill = "transparent", outlier.shape = NA, lwd = 0.3) +
-  geom_text(data = crispr_signif_gene, aes(x = 1.5, y = 1.75, label = p.signif)) +
-  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
-  theme(legend.position = "top", legend.direction = "horizontal") +
-  guides(color = guide_legend(override.aes = list(size = 3))) +
-  labs(y = "CERES Score")
-# crispr_gene_mut_plot
-
-# ggsave("./plots/manuscript/crispr_gene_mut_plot.png", crispr_gene_mut_plot, width = 12, height = 6, units = "in")
-```
-
-```{r crispr_mut_lin_plot}
-crispr_signif_lineage$Gene <- factor(crispr_signif_lineage$Gene, levels = g2p_genes)
-
-crispr_gene_lin_plot <- ggplot(data = crispr_ptmuts_filt) +
-  facet_wrap(~ Primary.Disease, nrow = 6, scales = "free_x") +
-  scale_color_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "darkorchid", "0" = "thistle")) +
-  geom_point(aes(x = Gene, y = Score, color = Mutation_Status), alpha = 0.5, size = 0.6) +
-  geom_text(data = crispr_signif_lineage, aes(x = Gene, y = 1.6, label = p.signif), angle = 90, vjust = 0.8, nudge_y = 0.1, size = 3) +
-  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
-  theme(legend.position = "top", legend.direction = "horizontal", axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 7)) +
-  guides(color = guide_legend(override.aes = list(size = 3))) +
-  ylab("CERES Score") +
-  scale_x_discrete(name = "Mutation Status", labels = c("0" = "WT", "1" = "Mut"))
-# crispr_gene_lin_plot
-
-# ggsave("./plots/manuscript/crispr_gene_lineage_plot.png", crispr_gene_lin_plot, width = 16, height = 18, units = "in")
-```
-
-```{r mut_heatmap_function}
-MakeMutHeatmap <- function(signif_g2p_druggene, row_names, col_title, color, legend_title) {
-  # signif_g2p_druggene$Drug <- sapply(strsplit(signif_g2p_druggene$Drug_Gene, "_", fixed = TRUE), function(x) x[1])
-  # signif_g2p_druggene$Gene <- sapply(strsplit(signif_g2p_druggene$Drug_Gene, "_", fixed = TRUE), function(x) x[2])
-
-  signif_grid <- dcast(signif_g2p_druggene, Gene ~ Drug, value.var = "p", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
-  signif_grid <- signif_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
-  signif_grid <- signif_grid[complete.cases(signif_grid), ]
-  signif_grid[signif_grid > 0.05] <- NA
-
-  signif_grid_annot <- dcast(signif_g2p_druggene, Gene ~ Drug, value.var = "InG2P", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
-  signif_grid_annot <- signif_grid_annot[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
-  signif_grid_annot <- signif_grid_annot[complete.cases(signif_grid_annot), ]
-  signif_grid_annot[signif_grid_annot == "No"] <- ""
-  signif_grid_annot[signif_grid_annot == "Yes"] <- "*"
-
-  col_fun <- colorRamp2(c(0, 0.05), c(color, "gray97"))
-  # Legend properties list
-  ht_legend_list <- list(title = legend_title, title_position = "topleft", legend_direction = "horizontal", legend_width = unit(2, "in"), border = "gray70",   at = seq(0, 0.05, by = 0.01), labels = seq(0, 0.05, by = 0.01))
-  ht <- Heatmap(signif_grid,
-                col = col_fun,
-                na_col = "gray97",
-                rect_gp = gpar(col = "gray70"),
-                heatmap_legend_param = ht_legend_list,
-                cluster_rows = FALSE, 
-                cluster_columns = FALSE, 
-                show_row_names = as.logical(row_names),
-                row_names_side = "left",
-                row_names_gp = gpar(fontsize = 10),
-                column_names_side = "bottom",
-                column_names_gp = gpar(fontsize = 10),
-                show_column_names = FALSE,
-                bottom_annotation = HeatmapAnnotation(
-                  text = anno_text(colnames(signif_grid),
-                                   rot = 45,
-                                   gp = gpar(fontsize = 11),
-                                   offset = unit(1, "npc"),
-                                   just = "right"),
-                  annotation_height = unit(0.85, "in")),
-                  # annotation_height = max_text_width(colnames(signif_grid))),
-                row_title = "Genes",
-                row_title_gp = gpar(fontface = "bold", fontsize = 14),
-                column_title = col_title, 
-                column_title_gp = gpar(fontface = "bold", fontsize = 14),
-                column_title_side = "bottom",
-                cell_fun = function(j, i, x, y, width, height, fill) { grid.text(signif_grid_annot[i, j], x, y, gp = gpar(fontsize = 20)) })
-  return(ht)
-}
-```
-
-```{r mut_heatmaps, eval=FALSE}
-ht_ccle <- MakeMutHeatmap(signif_g2p_druggene = ccle_signif_g2p_druggene, legend_title = "P-value", row_names = TRUE, color = "darkgreen", col_title = "Drugs")
-png(filename = "./plots/manuscript/ccle_mut_heatmap.png", width = 3, height = 10, units = "in", res = 500)
-draw(ht_ccle, heatmap_legend_side = "top")
-dev.off()
-
-ht_ctrp <- MakeMutHeatmap(signif_g2p_druggene = ctrp_signif_g2p_druggene, legend_title = "P-value", row_names = TRUE, color = "steelblue4", col_title = "Drugs")
-png(filename = "./plots/manuscript/ctrp_mut_heatmap.png", width = 9.5, height = 10, units = "in", res = 500)
-draw(ht_ctrp, heatmap_legend_side = "top")
-dev.off()
-
-ht_gdsc <- MakeMutHeatmap(signif_g2p_druggene = gdsc_signif_g2p_druggene, legend_title = "P-value", row_names = TRUE, color = "turquoise4", col_title = "Drugs")
-png(filename = "./plots/manuscript/gdsc_mut_heatmap.png", width = 5, height = 10, units = "in", res = 500)
-draw(ht_gdsc, heatmap_legend_side = "top")
-dev.off()
-
-ht_ccle2 <- MakeMutHeatmap(signif_g2p_druggene = ccle_signif_g2p_druggene, legend_title = "CCLE p-value                                                                               ", row_names = TRUE, color = "darkgreen", col_title = "")
-ht_ctrp2 <- MakeMutHeatmap(signif_g2p_druggene = ctrp_signif_g2p_druggene, legend_title = "CTRP p-value                                                                              ", row_names = FALSE, color = "steelblue4", col_title = "Drugs")
-ht_gdsc2 <- MakeMutHeatmap(signif_g2p_druggene = gdsc_signif_g2p_druggene, legend_title = "GDSC p-value", row_names = FALSE, color = "turquoise4", col_title = "")
-png(filename = "./plots/manuscript/drug_mut_heatmap.png", width = 13, height = 10, units = "in", res = 500)
-draw(ht_ccle2 + ht_ctrp2 + ht_gdsc2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
-dev.off()
-```
-
-# SPEARMAN (CN, GE)
-
---------------------------------------------------------------------------------
-
-```{r drug_spear_calc, warning=FALSE, eval=FALSE}
-g2p_druggene_tally <- g2p %>% group_by(Drug_Gene) %>% tally() %>% drop_na()
-
-# CCLE
-ccle_cor_res <- ccle_ptmuts %>% group_by(Drug, Gene, Drug_Gene) %>% summarize(
-                GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate,
-                GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value,
-                CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate,
-                CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value)
-ccle_cor_res <- merge(g2p_druggene_tally, ccle_cor_res, by = "Drug_Gene", all.y = TRUE)
-ccle_cor_res$n <- ifelse(is.na(ccle_cor_res$n), 0, ccle_cor_res$n)
-ccle_cor_res$InG2P <- ifelse(ccle_cor_res$n != 0, "Yes", "No")
-ccle_cor_res$Dataset <- "CCLE"
-
-# CTRP
-ctrp_cor_res <- ctrp_ptmuts %>% group_by(Drug, Gene, Drug_Gene) %>% summarize(
-                GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate,
-                GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value,
-                CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate,
-                CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value)
-ctrp_cor_res <- merge(g2p_druggene_tally, ctrp_cor_res, by = "Drug_Gene", all.y = TRUE)
-ctrp_cor_res$n <- ifelse(is.na(ctrp_cor_res$n), 0, ctrp_cor_res$n)
-ctrp_cor_res$InG2P <- ifelse(ctrp_cor_res$n != 0, "Yes", "No")
-ctrp_cor_res$Dataset <- "CTRP"
-
-# GDSC
-gdsc_cor_res <- gdsc_ptmuts %>% group_by(Drug, Gene, Drug_Gene) %>% summarize(
-                GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate,
-                GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value,
-                CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate,
-                CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value)
-gdsc_cor_res <- merge(g2p_druggene_tally, gdsc_cor_res, by = "Drug_Gene", all.y = TRUE)
-gdsc_cor_res$n <- ifelse(is.na(gdsc_cor_res$n), 0, gdsc_cor_res$n)
-gdsc_cor_res$InG2P <- ifelse(gdsc_cor_res$n != 0, "Yes", "No")
-gdsc_cor_res$Dataset <- "GDSC"
-
-# All
-g2p_cor <- rbind(ccle_cor_res, ctrp_cor_res, gdsc_cor_res)
-
-saveRDS(g2p_cor, "./data_munging/rds/drug_cor.rds")
-```
-
-```{r load_drug_spear}
-g2p_cor <- readRDS("./data_munging/rds/drug_cor.rds")
-```
-
-Spearman correlations for gene expression and copy number:
-```{r crispr_spear_calc, warning=FALSE}
-crispr_spear_ge <- transform(crispr_ptmuts_filt %>% group_by(Gene) %>% summarize(p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value, p_log10 = -log10(p), corr = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate, Metric = "Gene Expression"), Gene = reorder(Gene, corr))
-crispr_spear_cn <- transform(crispr_ptmuts_filt %>% group_by(Gene) %>% summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value, p_log10 = -log10(p), corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate, Metric = "Copy Number"), Gene = reorder(Gene, corr))
-```
-
-## Plots
-
-Create CRISPR two-column, KRAS-inset plot for CN and GE:
-```{r crispr_spear_plot, fig.height=6, fig.width=12}
-spearman_KRAS <- rbind(filter(crispr_ptmuts_filt, Gene == "KRAS") %>% summarize(p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value, corr = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate, Metric = "Gene Expression"), filter(crispr_ptmuts_filt, Gene == "KRAS") %>% summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value, corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate, Metric = "Copy Number"))
-
-crispr_ge_spearman_corr_inset <- ggplot(filter(crispr_ptmuts_filt, Gene == "KRAS"), aes(x = TPM, y = Score)) +
-  geom_point(pch = 21, fill = "cadetblue3", alpha = 0.6) +
-  labs(x = expression("KRAS Gene Expression"~(log[2](TPM))), y = "CERES Score", subtitle = paste0("Spearman correlation coefficient = ", round(spearman_KRAS$corr[1], 2), " (p = ", formatC(as.numeric(spearman_KRAS$p[1]), format = "e", digits = 1), ")"))
-
-crispr_cn_spearman_corr_inset <- ggplot(filter(crispr_ptmuts_filt, Gene == "KRAS"), aes(x = CN, y = Score)) +
-  geom_point(pch = 21, fill = "palegreen2", alpha = 0.6) +
-  labs(x = expression("KRAS Copy Number"~(log[2]-ratio)), y = "CERES Score", subtitle = paste0("Spearman correlation coefficient = ", round(spearman_KRAS$corr[2], 2), " (p = ", formatC(as.numeric(spearman_KRAS$p[2]), format = "e", digits = 1), ")"))
-
-crispr_ge_spearman_corr_plot <- ggplot(data = crispr_spear_ge, aes(x = Gene, y = corr)) +
-  geom_point(aes(fill = p_log10), pch = 21, size = 5) +
-  scale_fill_gradientn(colours = c("white", "deepskyblue4"),
-                       breaks = c(0, 3, 6, 9, 12, 15),
-                       labels = c(0, 3, 6, 9, 12, 15),
-                       limits = c(0, 15)) +
-  coord_cartesian(ylim = c(-0.325, 0.325)) +
-  scale_y_continuous(breaks = seq(-0.4, 0.4, by = 0.05),
-                     labels = seq(-0.4, 0.4, by = 0.05)) +
-  theme(legend.position = c(0.15, 0.95),
-        legend.direction = "horizontal",
-        legend.key.size = unit(0.05, "npc"),
-        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 10)) +
-  labs(title = "Gene Expression",
-       fill = expression(-log[10](p)),
-       x = "Gene",
-       y = expression("Spearman Correlation Coefficient"~(r[s]))) +
-  annotation_custom(ggplotGrob(crispr_ge_spearman_corr_inset),
-                    xmin = 12, xmax = 32, ymin = -0.325, ymax = -0.1) +
-  geom_curve(aes(x = 2, y = -0.262, xend = 13.7, yend = -0.112),
-             color = "lightgray", curvature = -0.45,
-             arrow = arrow(length = unit(0.03, "npc")))
-
-crispr_cn_spearman_corr_plot <- ggplot(data = crispr_spear_cn, aes(x = Gene, y = corr)) +
-  geom_point(aes(fill = p_log10), pch = 21, size = 5) +
-  scale_fill_gradientn(colours = c("white", "green4"),
-                       breaks = c(0, 3, 6, 9, 12, 15),
-                       labels = c(0, 3, 6, 9, 12, 15),
-                       limits = c(0, 15)) +
-  coord_cartesian(ylim = c(-0.325, 0.325)) +
-  scale_y_continuous(breaks = seq(-0.4, 0.4, by = 0.05),
-                     labels = seq(-0.4, 0.4, by = 0.05)) +
-  theme(legend.position = c(0.15, 0.95),
-        legend.direction = "horizontal",
-        legend.key.size = unit(0.05, "npc"),
-        axis.title.y = element_blank(),
-        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 10)) +
-  labs(title = "Copy Number",
-       fill = expression(-log[10](p)),
-       x = "Gene",
-       y = expression("Spearman Correlation Coefficient"~(r[s]))) +
-  annotation_custom(ggplotGrob(crispr_cn_spearman_corr_inset),
-                    xmin = 12, xmax = 32, ymin = -0.325, ymax = -0.1) +
-  geom_curve(aes(x = 2, y = -0.255, xend = 13.7, yend = -0.112),
-             color = "lightgray", curvature = -0.2,
-             arrow = arrow(length = unit(0.03, "npc")))
-
-crispr_spearman_corr_plot <- plot_grid(crispr_ge_spearman_corr_plot, crispr_cn_spearman_corr_plot, align = "h")
-crispr_spearman_corr_plot
-
-ggsave("./plots/manuscript/crispr_spearman_corr_plot.png", crispr_spearman_corr_plot, device = "png", dpi = 450, width = 20, height = 10, units = "in")
-```
-
-```{r corr_heatmap_function}
-MakeCorrHeatmap <- function(drug_cor_res, row_names, col_title, color_range, legend_title, metric) {
-  # drug_cor_res$Drug <- sapply(strsplit(signif_g2p_druggene$Drug_Gene, "_", fixed = TRUE), function(x) x[1])
-  # drug_cor_res$Gene <- sapply(strsplit(signif_g2p_druggene$Drug_Gene, "_", fixed = TRUE), function(x) x[2])
-  if(toupper(metric) == "CN" | toupper(metric) == "COPY NUMBER") {
-    signif_grid <- dcast(drug_cor_res, Gene ~ Drug, value.var = "CN_p", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
-    signif_grid <- signif_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
-    signif_grid <- signif_grid[complete.cases(signif_grid), ]
-    signif_grid[signif_grid >= 0.05] <- ""
-    signif_grid[signif_grid != ""] <- "*"
-
-    corr_grid <- dcast(drug_cor_res, Gene ~ Drug, value.var = "CN_r", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
-    corr_grid <- corr_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(corr_grid))]
-    corr_grid <- corr_grid[complete.cases(corr_grid), ]
-  }
-
-  if(toupper(metric) == "GE" | toupper(metric) == "GENE EXPRESSION") {
-    signif_grid <- dcast(drug_cor_res, Gene ~ Drug, value.var = "GE_p", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
-    signif_grid <- signif_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
-    signif_grid <- signif_grid[complete.cases(signif_grid), ]
-    signif_grid[signif_grid >= 0.05] <- ""
-    signif_grid[signif_grid != ""] <- "*"
-
-    corr_grid <- dcast(drug_cor_res, Gene ~ Drug, value.var = "GE_r", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
-    corr_grid <- corr_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(corr_grid))]
-    corr_grid <- corr_grid[complete.cases(corr_grid), ]
-  }
-
-  annot_grid <- dcast(drug_cor_res, Gene ~ Drug, value.var = "InG2P", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
-  annot_grid <- annot_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
-  annot_grid <- annot_grid[complete.cases(annot_grid), ]
-  annot_grid[annot_grid == "No"] <- ""
-  annot_grid[annot_grid == "Yes"] <- "*"
-
-  col_fun <- colorRamp2(color_range, c("red3", "white", "green4"))
-
-  # Legend properties list
-  ht_legend_list <- list(title_position = "topleft", legend_direction = "horizontal", legend_width = unit(2, "in"), border = "gray70", at = seq(color_range[1], color_range[3], by = 0.2), labels = seq(color_range[1], color_range[3], by = 0.2))
-  ht <- Heatmap(corr_grid,
-                col = col_fun,
-                name = legend_title,
-                na_col = "gray97",
-                rect_gp = gpar(col = "gray70"),
-                heatmap_legend_param = ht_legend_list,
-                cluster_rows = FALSE, 
-                cluster_columns = FALSE, 
-                show_row_names = as.logical(row_names),
-                row_names_side = "left",
-                row_names_gp = gpar(fontsize = 10),
-                column_names_side = "bottom",
-                column_names_gp = gpar(fontsize = 10),
-                show_column_names = FALSE,
-                bottom_annotation = HeatmapAnnotation(
-                  text = anno_text(colnames(signif_grid),
-                                   rot = 45,
-                                   gp = gpar(fontsize = 11),
-                                   offset = unit(1, "npc"),
-                                   just = "right"),
-                  annotation_height = unit(0.85, "in")),
-                  # annotation_height = max_text_width(colnames(signif_grid))),
-                row_title = "Genes",
-                row_title_gp = gpar(fontface = "bold", fontsize = 14),
-                column_title = col_title, 
-                column_title_gp = gpar(fontface = "bold", fontsize = 14),
-                column_title_side = "top",
-                cell_fun = function(j, i, x, y, width, height, fill) { grid.text(signif_grid[i, j], x, y, gp = gpar(fontsize = 20)) }
-                )
-  return(ht)
-}
-```
-
-```{r drug_spear_plots, eval=FALSE}
-# Copy number
-ccle_cor <- unfactorize(filter(g2p_cor, Dataset == "CCLE"))
-ccle_cn_ht <- MakeCorrHeatmap(drug_cor_res = ccle_cor, row_names = TRUE, col_title = "CCLE", color_range = c(-0.25, 0, 0.25), legend_title = "CCLE Spearman correlation", metric = "CN")
-png(filename = "./plots/manuscript/ccle_cn_heatmap.png", width = 3, height = 10, units = "in", res = 500)
-draw(ccle_cn_ht, heatmap_legend_side = "top")
-dev.off()
-
-ctrp_cor <- unfactorize(filter(g2p_cor, Dataset == "CTRP"))
-ctrp_cn_ht <- MakeCorrHeatmap(drug_cor_res = ctrp_cor, row_names = TRUE, col_title = "CTRP", color_range = c(-0.35, 0, 0.35), legend_title = "CTRP Spearman correlation", metric = "CN")
-png(filename = "./plots/manuscript/ctrp_cn_heatmap.png", width = 9.5, height = 10, units = "in", res = 500)
-draw(ctrp_cn_ht, heatmap_legend_side = "top")
-dev.off()
-
-gdsc_cor <- unfactorize(filter(g2p_cor, Dataset == "GDSC"))
-gdsc_cn_ht <- MakeCorrHeatmap(drug_cor_res = gdsc_cor, row_names = TRUE, col_title = "GDSC", color_range = c(-0.25, 0, 0.25), legend_title = "GDSC Spearman correlation", metric = "CN")
-png(filename = "./plots/manuscript/gdsc_cn_heatmap.png", width = 5, height = 10, units = "in", res = 500)
-draw(gdsc_cn_ht, heatmap_legend_side = "top")
-dev.off()
-
-ccle_cn_ht2 <- MakeCorrHeatmap(drug_cor_res = ccle_cor, row_names = TRUE, col_title = "CCLE", color_range = c(-0.35, 0, 0.35), legend_title = "Copy num. Spearman correlation", metric = "CN")
-ctrp_cn_ht2 <- MakeCorrHeatmap(drug_cor_res = ctrp_cor, row_names = FALSE, col_title = "CTRP", color_range = c(-0.35, 0, 0.35), legend_title = "Copy num. Spearman correlation", metric = "CN")
-gdsc_cn_ht2 <- MakeCorrHeatmap(drug_cor_res = gdsc_cor, row_names = FALSE, col_title = "GDSC", color_range = c(-0.35, 0, 0.35), legend_title = "Copy num. Spearman correlation", metric = "CN")
-png(filename = "./plots/manuscript/drug_cn_heatmap.png", width = 13, height = 10, units = "in", res = 500)
-draw(ccle_cn_ht2 + ctrp_cn_ht2 + gdsc_cn_ht2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
-dev.off()
-
-# Gene expression
-ccle_ge_ht <- MakeCorrHeatmap(drug_cor_res = ccle_cor, row_names = TRUE, col_title = "CCLE", color_range = c(-0.5, 0, 0.5), legend_title = "CCLE Spearman correlation", metric = "GE")
-png(filename = "./plots/manuscript/ccle_ge_heatmap.png", width = 3, height = 10, units = "in", res = 500)
-draw(ccle_ge_ht, heatmap_legend_side = "top")
-dev.off()
-
-ctrp_ge_ht <- MakeCorrHeatmap(drug_cor_res = ctrp_cor, row_names = TRUE, col_title = "CTRP", color_range = c(-0.5, 0, 0.5), legend_title = "CTRP Spearman correlation", metric = "GE")
-png(filename = "./plots/manuscript/ctrp_ge_heatmap.png", width = 9.5, height = 10, units = "in", res = 500)
-draw(ctrp_ge_ht, heatmap_legend_side = "top")
-dev.off()
-
-gdsc_ge_ht <- MakeCorrHeatmap(drug_cor_res = gdsc_cor, row_names = TRUE, col_title = "GDSC", color_range = c(-0.5, 0, 0.5), legend_title = "GDSC Spearman correlation", metric = "GE")
-png(filename = "./plots/manuscript/gdsc_ge_heatmap.png", width = 5, height = 10, units = "in", res = 500)
-draw(gdsc_ge_ht, heatmap_legend_side = "top")
-dev.off()
-
-ccle_ge_ht2 <- MakeCorrHeatmap(drug_cor_res = ccle_cor, row_names = TRUE, col_title = "CCLE", color_range = c(-0.5, 0, 0.5), legend_title = "Gene expr. Spearman correlation", metric = "GE")
-ctrp_ge_ht2 <- MakeCorrHeatmap(drug_cor_res = ctrp_cor, row_names = FALSE, col_title = "CTRP", color_range = c(-0.5, 0, 0.5), legend_title = "Gene expr. Spearman correlation", metric = "GE")
-gdsc_ge_ht2 <- MakeCorrHeatmap(drug_cor_res = gdsc_cor, row_names = FALSE, col_title = "GDSC", color_range = c(-0.5, 0, 0.5), legend_title = "Gene expr. Spearman correlation", metric = "GE")
-png(filename = "./plots/manuscript/drug_ge_heatmap.png", width = 13, height = 10, units = "in", res = 500)
-draw(ccle_ge_ht2 + ctrp_ge_ht2 + gdsc_ge_ht2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
-dev.off()
-```
-
-# DGL KS TESTS
-
---------------------------------------------------------------------------------
-
-```{r KS_functions}
-MakeCorrResSummaryTable <- function(df_list, dataset_name) {
-  # Input: list of dataframes corresponding to Drug_Gene groupings in the drugscreen datasets filtered for point mutations
-  CorrResSummaryTable <- data.frame(matrix(ncol = 7, nrow = 0))
-  for(i in 1:length(df_list)) {
-    corr_res <- df_list[[i]] %>% group_by(G2P_Drug_Gene_Lin) %>% summarize(
-                Dataset = dataset_name,
-                Drug_Gene = names(df_list)[i],
-                G2P_Drug_Gene = ifelse(Drug_Gene %in% g2p_druggenes, "Yes", "No"),
-                Lineages = paste(as.character(unique(Primary.Disease)), collapse = ", "),
-                N_Lineages = length(as.character(unique(Primary.Disease))),
-                Spearman_Corr_GE = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate,
-                Spearman_Corr_CN = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate)
-    # print(names(df_list)[i])
-
-    if(length(unique(df_list[[i]]$Mutation_Status)) == 2) {
-      dgl_signif <- compare_means(Score ~ Mutation_Status, data = df_list[[i]], group.by = "G2P_Drug_Gene_Lin", method = "wilcox.test")[, c("G2P_Drug_Gene_Lin", "p")]
-    }
-    if(length(unique(df_list[[i]]$Mutation_Status)) == 1) {
-      dgl_signif <- data.frame("G2P_Drug_Gene_Lin" = NA, "p" = NA)
-    }
-
-    corr_res <- merge(corr_res, dgl_signif, by = "G2P_Drug_Gene_Lin", all = TRUE)
-    corr_res$Mut_Signif <- ifelse(corr_res$p < 0.05, 1, 0)
-    CorrResSummaryTable <- rbind(CorrResSummaryTable, corr_res)
-  }
-  CorrResSummaryTable <- CorrResSummaryTable[!is.na(CorrResSummaryTable$G2P_Drug_Gene_Lin), ]
-  return(CorrResSummaryTable)
-}
-
-G2PCorrKStest <- function(dataset, dataset_name) {
-  # Input: CorrResSummaryTable created by the MakeCorrResSummaryTable function
-  Metric <- colnames(dataset)[7:8]
-  D_stat <- NULL
-  pval <- NULL
-  signif <- NULL
-
-  yes <- dataset[dataset$G2P_Drug_Gene_Lin == "Yes",]
-  no <- dataset[dataset$G2P_Drug_Gene_Lin == "No",]
-
-  for(i in 7:8) {
-    test <- ks.test(yes[[colnames(yes)[i]]], no[[colnames(no)[i]]])
-    D_stat <- c(D_stat, test$statistic)
-    pval <- c(pval, test$p.value)
-    signif <- c(signif, ifelse(test$p.value < 0.001, "***", ifelse(test$p.value < 0.01, "**", ifelse(test$p.value < 0.05, "*", NA))))
-  }
-  df <- data.frame(Metric, D_stat, pval, signif)
-  df$Dataset <- dataset_name
-  return(df)
-}
-
-G2PCorrTable <- function(ccle_ptmuts_df, ctrp_ptmuts_df, gdsc_ptmuts_df) {
-  # CCLE
-  ccle_split <- split(ccle_ptmuts_df, f = ccle_ptmuts_df$Drug_Gene)
-  ccle_corr_all <- MakeCorrResSummaryTable(ccle_split, dataset_name = "CCLE")
-  print("CCLE correlations: Complete.")
-  # CTRP
-  ctrp_split <- split(ctrp_ptmuts_df, f = ctrp_ptmuts_df$Drug_Gene)
-  ctrp_corr_all <- MakeCorrResSummaryTable(ctrp_split, dataset_name = "CTRP")
-  print("CTRP correlations: Complete.")
-  # GDSC
-  gdsc_split <- split(gdsc_ptmuts_df, f = gdsc_ptmuts_df$Drug_Gene)
-  gdsc_corr_all <- MakeCorrResSummaryTable(gdsc_split, dataset_name = "GDSC")
-  print("GDSC correlations: Complete.")
-
-  g2p_corr_all <- rbind(ccle_corr_all, ctrp_corr_all, gdsc_corr_all)
-
-  return(g2p_corr_all)
-}
-
-G2PCorrStatsTables<- function(corr_df, table_type) {  
-  if(table_type == "mutation" | table_type == "mut" ) {
-    mut_stats <- corr_df %>% group_by(G2P_Drug_Gene_Lin, Dataset) %>% drop_na(Mut_Signif) %>% summarize(N_Signif_Muts = sum(Mut_Signif), Total_Tests = length(Mut_Signif), Perc_Signif = N_Signif_Muts / Total_Tests * 100)
-    print("Returning mutation statistics.")
-    return(mut_stats)
-  }
-  if(table_type == "KS" | table_type == "ks") {
-    ccle_corr_stats <- G2PCorrKStest(filter(corr_df, Dataset == "CCLE"), "CCLE")
-    ctrp_corr_stats <- G2PCorrKStest(filter(corr_df, Dataset == "CTRP"), "CTRP")
-    gdsc_corr_stats <- G2PCorrKStest(filter(corr_df, Dataset == "GDSC"), "GDSC")
-    corr_stats <- rbind(ccle_corr_stats, ctrp_corr_stats, gdsc_corr_stats)
-    corr_stats <- corr_stats %>% separate(col = Metric, into = c("Correlation_Method", "corr", "Metric"), sep = "_")
-    corr_stats$Metric <- ifelse(corr_stats$Metric == "GE", "Gene Expression", "Copy Number")
-    print("Returning KS test results.")
-    return(corr_stats)
-  }
-}
-```
-
-Kolmogorov-Smirnov tests comparing DGLs that are in a G2P DGL and not.
-```{r drug_KS_tests, eval=FALSE, warning=FALSE, fig.height=6, fig.width=12}
-# g2p_dgl_corr <- G2PCorrTable(ccle_ptmuts_df = ccle_ptmuts, ctrp_ptmuts_df = ctrp_ptmuts, gdsc_ptmuts_df = gdsc_ptmuts)
-# saveRDS(g2p_dgl_corr, "./data_munging/rds/g2p_dgl_corr.rds")
-g2p_dgl_corr <- readRDS("./data_munging/rds/g2p_dgl_corr.rds")
-g2p_mut_stats <- G2PCorrStatsTables(corr_df = g2p_dgl_corr, table_type = "mutation")
-
-g2p_corr_4plot <- filter(g2p_dgl_corr, G2P_Drug_Gene == "Yes")
-g2p_corr_stats <- G2PCorrStatsTables(corr_df = g2p_corr_4plot, table_type = "KS")
-g2p_corr_4plot$p <- NULL
-g2p_corr_4plot$Mut_Signif <- NULL
-g2p_corr_4plot <- melt(g2p_corr_4plot, id.vars = colnames(g2p_corr_4plot)[1:6], measure.vars = colnames(g2p_corr_4plot)[7:8], value.name = "Correlation")
-g2p_corr_4plot <- g2p_corr_4plot %>% separate(col = variable, into = c("Correlation_Method", "corr", "Metric"), sep = "_", remove = FALSE)
-g2p_corr_4plot$Metric <- ifelse(g2p_corr_4plot$Metric == "GE", "Gene Expression", "Copy Number")
-
-g2p_ks_res_plot_spearman <- ggplot(data = filter(g2p_corr_4plot, Correlation_Method == "Spearman")) +
-  facet_grid(Metric ~ Dataset, labeller = labeller(yfacet = c('CN' = "Copy Number", 'GE' = "Gene Expression"))) +
-  geom_violin(aes(y = Correlation, x = G2P_Drug_Gene_Lin, fill = Dataset, color = Dataset, alpha = G2P_Drug_Gene_Lin)) +
-  geom_boxplot(width = 0.075, aes(y = Correlation, x = G2P_Drug_Gene_Lin, color = Dataset)) +
-  geom_jitter(width = 0.3, alpha = 0.8, aes(y = Correlation, x = G2P_Drug_Gene_Lin, color = Dataset)) +
-  theme(legend.position = "none") +
-  scale_alpha_manual(values = c("Yes" = 0.6, "No" = 0.2)) +
-  scale_fill_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
-  scale_color_manual(values = c("CCLE" = "springgreen4", "CTRP" = "steelblue4", "GDSC" = "turquoise4")) +
-  coord_cartesian(ylim = c(-1, 1)) +
-  geom_text(data = filter(g2p_corr_stats, Correlation_Method == "Spearman"),
-            aes(x = 1.5, y = 0.8,
-                label = paste0("D = ", formatC(D_stat, digits = 2, format = "f"),
-                               ", p = ", ifelse(pval > 0.1, round(pval, 2), ifelse(pval < 0.001, formatC(pval, digits = 1, format = "e"), round(pval, 3))),
-                               "\n", ifelse(is.na(signif), "", signif)))) +
-  labs(x = "Is the lineage in a G2P DGL?",
-       y = expression("Spearman Correlation Coefficient"~(r[s])))
-g2p_ks_res_plot_spearman
-
-# ggsave("./plots/manuscript/g2p_spearman_ks_res_plot.png", g2p_ks_res_plot_spearman, device = "png", dpi = 500, width = 12, height = 6, units = "in")
-```
-
-# SANDBOX
-
---------------------------------------------------------------------------------
-
-Filter for BRCA1/2 mutations to see if we catch non-germline mutations/CN variants:
-```{r brca_test, eval=FALSE}
-test <- filter(maf_df, Gene == "BRCA1" | Gene == "BRCA2")
-test2 <- filter(cn_melt, Gene == "BRCA1" | Gene == "BRCA2")
-```
-
-Test filtering CRISPR data for G2P genes using function:
-```{r crispr_fnx_test, eval=FALSE}
-crispr_all <- read.delim("./data_munging/19Q1/gene_effect_corrected_20190305.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
-# Remove Entrez gene IDs from colnames
-colnames(crispr_all) <- gsub(" .*", "", colnames(crispr_all))
-colnames(crispr_all)[1] <- "Broad_ID"
-
-# Omics metadata
-maf_df_filt <- filter(maf_df, Gene %in% g2p_genes)
-ge_filt <- filter(ge_melt, Gene %in% g2p_genes)
-cn_filt <- filter(cn_melt, Gene %in% g2p_genes)
-
-crispr_fxn <- MergeOmicsG2P(database = "CRISPR", outfile = "./../htscreens_giant_files/crispr_data_19Q1_g2pgenes_fxn.rds")
-crispr_ptmuts_fxn <- FilterForPointMuts(dataframe = crispr_fxn, outfile = "./../htscreens_giant_files/crispr_data_19Q1_g2pgenes_ptmuts_fxn.rds")
-```
-
-```{r load_crispr_fnx_test_rds, eval=FALSE}
-crispr_fxn <- readRDS("./../htscreens_giant_files/crispr_data_19Q1_g2pgenes_fxn.rds")
-crispr_ptmuts_fxn <- readRDS("./../htscreens_giant_files/crispr_data_19Q1_g2pgenes_ptmuts_fxn.rds")
-```
-
-Test out standardization/normalization methods on Pozdeyev data. This yields evidence that the AUC values are already normalized.
-```{r pozdeyev_norm_testing, eval=FALSE}
-ccle_all <- read.delim("./../htscreens_giant_files/pozdeyev_data/CCLE_drug_response_metrics.csv.gz", sep = ",")
-ccle_all$AUC_IC50_standardized <- scale(ccle_all$AUC_IC50, center = TRUE, scale = TRUE)
-ccle_all$AUC_IC50_normalized <- scale(ccle_all$AUC_IC50, center = min(ccle_all$AUC_IC50[!is.na(ccle_all$AUC_IC50)]), scale = max(ccle_all$AUC_IC50[!is.na(ccle_all$AUC_IC50)]) - min(ccle_all$AUC_IC50[!is.na(ccle_all$AUC_IC50)]))
-ctrp_all <- read.delim("./../htscreens_giant_files/pozdeyev_data/CTRP_drug_response_metrics.csv.gz", sep = ",")
-ctrp_all$AUC_IC50_standardized <- scale(ctrp_all$AUC_IC50, center = TRUE, scale = TRUE)
-ctrp_all$AUC_IC50_normalized <- scale(ctrp_all$AUC_IC50, center = min(ctrp_all$AUC_IC50[!is.na(ctrp_all$AUC_IC50)]), scale = max(ctrp_all$AUC_IC50[!is.na(ctrp_all$AUC_IC50)]) - min(ctrp_all$AUC_IC50[!is.na(ctrp_all$AUC_IC50)]))
-gdsc_all <- read.delim("./../htscreens_giant_files/pozdeyev_data/GDSC_drug_response_metrics.csv.gz", sep = ",")
-gdsc_all$AUC_IC50_standardized <- scale(gdsc_all$AUC_IC50, center = TRUE, scale = TRUE)
-gdsc_all$AUC_IC50_normalized <- scale(gdsc_all$AUC_IC50, center = min(gdsc_all$AUC_IC50[!is.na(gdsc_all$AUC_IC50)]), scale = max(gdsc_all$AUC_IC50[!is.na(gdsc_all$AUC_IC50)]) - min(gdsc_all$AUC_IC50[!is.na(gdsc_all$AUC_IC50)]))
-
-auc_test <- bind_rows(ccle_all, ctrp_all, gdsc_all)
-
-ggplot(data = auc_test) +
-  geom_histogram(aes(x = AUC_IC50)) +
-  facet_wrap(~ Database, ncol = 3, scales = "free_y")
-ggplot(data = auc_test) +
-  geom_histogram(aes(x = AUC_IC50_normalized)) +
-  facet_wrap(~ Database, ncol = 3, scales = "free_y")
-ggplot(data = auc_test) +
-  geom_histogram(aes(x = AUC_IC50_standardized)) +
-  facet_wrap(~ Database, ncol = 3, scales = "free_y")
-```
-
 # SESSION INFORMATION

### 2019-05-16 19Q2.Rmd
consolidate curated G2P biomarker types, include non-drug-assoc interpretations

@@
 ccl_converter <- read.delim("./data_munging/cell_line_database_v1_20180911.tsv", row.names = 1, sep = "\t", header = TRUE)
+colnames(ccl_converter)[colnames(ccl_converter) == "Broad_ID"] <- "DepMap_ID"
 ccl_lineage_converter <- unique(ccl_converter[, c("DepMap_ID", "grouped_general_doid", "group_general_lineage_name")])
@@
 ccl_meta <- add_column(ccl_meta, CCLE_histology = CCLE_histology, .after = "CCLE_name")
-ccl_meta$disease <- with(ccl_meta, ifelse(disease == " " & Histology %in% ccl_diseases, as.character(Histology), as.character(disease)))
+ccl_meta$disease <- with(ccl_meta, ifelse(disease == " " & CCLE_histology %in% ccl_diseases, as.character(CCLE_histology), as.character(disease)))
 ccl_meta$disease <- with(ccl_meta, ifelse(disease == "ovary", "ovarian",
-                                   ifelse(disease == " " & Histology == "vulva", "vulva",
-                                   ifelse(disease == " " & Histology == "stomach", "gastric",
-                                   ifelse(disease == " " & Histology == "upper_aerodigestive_tract", "upper_aerodigestive_tract",
-                                   ifelse(disease == " " & Histology == "large_intestine", "colorectal",
-                                   ifelse(disease == " " & Histology == "biliary_tract", "bile_duct",
-                                   ifelse(disease == " " & Histology == "oesophagus", "esophagus",
-                                   ifelse(disease == " " & Histology == "testis", "embryo", disease)))))))))
+                                   ifelse(disease == " " & CCLE_histology == "vulva", "vulva",
+                                   ifelse(disease == " " & CCLE_histology == "stomach", "gastric",
+                                   ifelse(disease == " " & CCLE_histology == "upper_aerodigestive_tract", "upper_aerodigestive_tract",
+                                   ifelse(disease == " " & CCLE_histology == "large_intestine", "colorectal",
+                                   ifelse(disease == " " & CCLE_histology == "biliary_tract", "bile_duct",
+                                   ifelse(disease == " " & CCLE_histology == "oesophagus", "esophagus",
+                                   ifelse(disease == " " & CCLE_histology == "testis", "embryo", disease)))))))))
 ```
@@
 ## G2P
+
+```{r g2p_parsing_functions}
+ExtractBiomarkerType <- function(json_string) {
+  json_string <- as.character(json_string)
+  biomarker_type <- ((str_extract(string = json_string, pattern = "biomarker_type.+") %>% strsplit(split = ","))[[1]][1] %>% str_extract(pattern = "u'.+") %>% str_match("'(.*?)'"))[,2]
+  biomarker_type <- ifelse(is.na(biomarker_type), "", biomarker_type)
+  return(biomarker_type)
+}
+```
+
+```{r g2p_parsing, eval=FALSE}
+g2p <- read.delim("./data_munging/g2p_full_level_A_dataset_NEW_DEC_2_2018_withGroupedLineages.csv", sep = "\t", header = TRUE)
+g2p[, 1:2] <- NULL
+g2p <- unfactorize(g2p)
+g2p$Drug <- tolower(g2p$Drug)
+g2p[g2p == -1] <- ""
+g2p$Gene <- ifelse(is.na(g2p$Gene) & g2p$Drug == "daunorubicin", "MLL", as.character(g2p$Gene))
+g2p$Direction <- ifelse(g2p$Direction == 1 | g2p$Direction == "", NA, as.character(g2p$Direction))
+g2p$Ref[g2p$Ref == "None" | g2p$Ref == "-" | is.na(g2p$Ref)] <- ""
+g2p$Alt[g2p$Alt == "None" | g2p$Alt == "-" | is.na(g2p$Alt)] <- ""
+g2p <- g2p[, c("Drug", "DrugID", "Direction", "Gene", "Ref", "Alt", "Start", "End", "Chromosome", "Feature.Names", "Mutation", "JSON", "Evidence.Level", "Phenotype.Description", "Phenotype.Family", "Phenotype.ID", "Sequence.ID", "grouped_general_doid")]
+g2p <- add_column(g2p, Ref_Length = nchar(as.character(g2p$Ref)), .after = "Ref")
+g2p <- add_column(g2p, Alt_Length = nchar(as.character(g2p$Alt)), .after = "Alt")
+g2p <- add_column(g2p, Variant_Length = NA, .after = "Alt_Length")
+g2p$Variant_Length <-
+  ifelse(g2p$Alt_Length == 1 & g2p$Ref_Length == 1, 1,
+  ifelse(g2p$Alt_Length == 2 & g2p$Ref_Length == 2, 2,
+  ifelse(g2p$Alt_Length == 3 & g2p$Ref_Length == 3, 3,
+  ifelse(g2p$Ref_Length == g2p$Alt_Length & g2p$Ref_Length > 3, g2p$Ref_Length,
+  ifelse(g2p$Ref_Length != g2p$Alt_Length, abs(g2p$Ref_Length - g2p$Alt_Length), NA)))))
+g2p <- add_column(g2p, Variant_Type = NA, .after = "Alt_Length")
+g2p$Variant_Type <-
+  ifelse(g2p$Alt_Length == 1 & g2p$Ref_Length == 1, "SNP",
+  ifelse(g2p$Alt_Length == 2 & g2p$Ref_Length == 2, "DNP",
+  ifelse(g2p$Alt_Length == 3 & g2p$Ref_Length == 3, "TNP",
+  ifelse(g2p$Ref_Length == g2p$Alt_Length & g2p$Ref_Length > 3, "ONP",
+  ifelse(g2p$Ref_Length > g2p$Alt_Length, "DEL",
+  ifelse(g2p$Ref_Length < g2p$Alt_Length, "INS", "None"))))))
+g2p <- subset(g2p, !grepl("^SID|^CHEMBL", g2p$DrugID))
+g2p <- subset(g2p, !grepl("germline|homozygosity", tolower(g2p$Feature.Names)))
+g2p <- add_column(g2p, biomarker_type = tolower(sapply(g2p$JSON, ExtractBiomarkerType, simplify = TRUE)), .after = "Feature.Names")
+g2p <- add_column(g2p, biomarker_type_curated = NA, .after = "biomarker_type")
+
+# Manually assign biomarker_types based on a combination of biomarker_type derived from the JSON string and patterns in the Feature.Names
+biomarker_type_curated <- 
+  ifelse(!is.na(str_match(string = tolower(g2p$biomarker_type), pattern = "copy number variant|amplification")) | !is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "copy number variant|amplification")), "Amplification/CNV",
+  ifelse(!is.na(str_match(string = toupper(g2p$Feature.Names), pattern = "[A-Z0-9|A-Z]+-[A-Z0-9|A-Z]+|FUSION")) & is.na(str_match(string = g2p$Feature.Names, pattern = "[0-9]+-[0-9]+")) | g2p$biomarker_type == "fusion" | g2p$biomarker_type == "rearrange", "Fusion",
+  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "[A-Z][0-9]+([A-Z]|[*])|[0-9A-Z]+ [A-Z][0-9]+|[A-Z][0-9]+$")), "Mutation",
+  ifelse(!is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "expression|methylation")), "Expression",
+  ifelse(!is.na(str_match(string = g2p$biomarker_type, pattern = "intron|insertion|deletion|mutant")), "Mutation",
+  ifelse(!is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "codon|positive|biallelic inactivation|del|ins|dup|mut|frameshift|missense|variant|[0-9]+fs|>")), "Mutation",
+  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "^KIT$|^BRCA$")), "Mutation", NA)))))))
+g2p$biomarker_type_curated <- biomarker_type_curated[,1]
+g2p[g2p == ""] <- NA
+g2p$Drug_Gene <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene), NA, paste0(g2p$Drug, "_", g2p$Gene))
+g2p <- merge(lineage_converter, g2p, by = "grouped_general_doid", all.y = TRUE)
+g2p$Drug_Gene_Lin <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene) | is.na(g2p$group_general_lineage_name), NA, paste0(g2p$Drug, "_", g2p$Gene, "_", g2p$group_general_lineage_name))
+g2p$Gene_Lin <- ifelse(is.na(g2p$Drug) | !is.na(g2p$Gene) | !is.na(g2p$group_general_lineage_name), paste0(g2p$Gene, "_", g2p$group_general_lineage_name), NA)
+
+# write.csv(g2p, "./data_munging/g2p_db_edited.csv")
+```
 
@@
 # Select columns
-maf <- subset(maf_raw, select = c("Gene", "DepMap_ID", "Variant_Classification", "Variant_Type"))
+maf <- subset(maf_raw, select = c("Gene", "DepMap_ID", "Variant_Classification"))
 maf <- maf[!is.na(maf$Variant_Classification),]
@@
 DepMap WES CN Data:
+
+- gene_cn - NumericalMatrix
+- Gene level copy number data, log2 transformed with a pseudo count 1. This is generated by mapping genes onto the segment level calls.
+- Rows: cell lines (Broad IDs)
+- Columns: genes (HGNC symbol and Entrez ID)
+
 ```{r copy_number, eval=FALSE}
@@
 19Q2, CCLE RNAseq gene expression data:
+
+- expression - NumericalMatrix
+- RNAseq TPM gene expression data for just protein coding genes using RSEM. Log2 transformed, using a pseudo-count of 1.
+- Rows: cell lines (Broad IDs)
+- Columns: genes (HGNC symbol and Entrez ID)
+
 ```{r gene_expression, eval=FALSE}
-ge <- read.delim("./../htscreens_giant_files/CCLE_depMap_19Q2_TPM_20190305.csv.gz", header = TRUE, sep = ",", check.names = FALSE)
+ge <- read.delim("./data_munging/19Q2/CCLE_expression_20190514.csv.gz", header = TRUE, sep = ",", check.names = FALSE)
 # Remove Entrez gene IDs from colnames, format is "Gene (Entrez ID)"
@@
 ge_melt <- melt(ge, id.vars = "DepMap_ID", measure.vars = colnames(ge)[2:ncol(ge)], variable.name = "Gene", value.name = "TPM")
-ge_melt$TPM <- log2(ge_melt$TPM + 1)
+# ge_melt$TPM <- log2(ge_melt$TPM + 1)
 ge_melt <- unfactorize(ge_melt)

### 2019-05-16 19Q2.Rmd
updated 19Q2 MAF df

@@
 g2p$biomarker_type_curated <- biomarker_type_curated[,1]
+
+# Add association columns
 g2p[g2p == ""] <- NA
@@
 
-g2p_dgls <-  as.character(unique(g2p$Drug_Gene_Lin[!is.na(g2p$Drug_Gene_Lin)]))
-g2p_druggenes <- as.character(unique(g2p$Drug_Gene[!is.na(g2p$Drug_Gene)]))
-g2p_drugs <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[1]))
-g2p_genes <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[2]))
-g2p_lins <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[3]))
+g2p_dgl <-  as.character(unique(g2p$Drug_Gene_Lin[!is.na(g2p$Drug_Gene_Lin)]))
+g2p_dg <- as.character(unique(g2p$Drug_Gene[!is.na(g2p$Drug_Gene)]))
+g2p_gl <- as.character(unique(g2p$Drug_Gene[!is.na(g2p$Gene_Lin)]))
+g2p_drugs <- unique(sapply(strsplit(g2p_dgl, "_", fixed = TRUE), function(x) x[1]))
+g2p_genes <- unique(sapply(strsplit(g2p_dgl, "_", fixed = TRUE), function(x) x[2]))
+g2p_lins <- unique(sapply(strsplit(g2p_dgl, "_", fixed = TRUE), function(x) x[3]))
 ```
@@
 # Select columns
-maf <- subset(maf_raw, select = c("Gene", "DepMap_ID", "Variant_Classification"))
-maf <- maf[!is.na(maf$Variant_Classification),]
-maf <- maf[maf$Variant_Classification %in% unique(g2p$biomarker_type_curated),]
+maf <- subset(maf_raw, select = c("Gene", "DepMap_ID"))
 maf$Mutation <- 1
-maf_df <- dcast(maf, Gene + DepMap_ID ~ Variant_Classification, fun.aggregate = mean, fill = 0)
-maf_df_summ <- colSums(maf_df[, 3:ncol(maf_df)])
+maf_grid <- expand.grid("Gene" = unique(maf$Gene), "DepMap_ID" = unique(maf$DepMap_ID))
+maf_df <- merge(maf, maf_grid, by = c("Gene", "DepMap_ID"), all = TRUE)
+maf_df[is.na(maf_df)] <- 0
 

### 2019-05-17 19Q2.Rmd
updated Rmd for merging drug data

@@
 ccl_histologies <- read.delim("./data_munging/ccl_histologies_metadata.csv", sep = ",", header = TRUE, row.names = 1)
+colnames(ccl_histologies) <- c("Cell_line", "CCLE_histology", "TCGA_classification", "CCLE_name", "DepMap_ID")
 ```
@@
 g2p_dg <- as.character(unique(g2p$Drug_Gene[!is.na(g2p$Drug_Gene)]))
-g2p_gl <- as.character(unique(g2p$Drug_Gene[!is.na(g2p$Gene_Lin)]))
-g2p_drugs <- unique(sapply(strsplit(g2p_dgl, "_", fixed = TRUE), function(x) x[1]))
-g2p_genes <- unique(sapply(strsplit(g2p_dgl, "_", fixed = TRUE), function(x) x[2]))
-g2p_lins <- unique(sapply(strsplit(g2p_dgl, "_", fixed = TRUE), function(x) x[3]))
+g2p_gl <- as.character(unique(g2p$Gene_Lin[!is.na(g2p$Gene_Lin)]))
+g2p_drugs <- as.character(unique(g2p$Drug[!is.na(g2p$Drug)]))
+g2p_genes <- as.character(unique(g2p$Gene[!is.na(g2p$Gene)]))
+g2p_lins <- as.character(unique(g2p$group_general_lineage_name[!is.na(g2p$group_general_lineage_name)]))
 ```
@@
 ```{r omics_functions}
-MergeOmicsG2P <- function(database, maf_df, ge_df, cn_df, outfile) {
+MergeOmicsG2P <- function(database, maf_df, ge_df, cn_df, gene_list, outfile) {
   # Merge mutation status, CN, and GE omics data with drugscreen results and metadata
   if(database %in% c("CCLE", "CTRP", "GDSC")) {
-    filt <- auc %>% filter(Database == database) %>% select(Cell_line, Histology, TCGA_classification, CCLE_Name, DepMap_ID, Drug, AUC_IC50)
+    filt <- auc %>% filter(Database == database) %>% select(Cell_line, CCLE_histology, TCGA_classification, CCLE_name, DepMap_ID, Drug, AUC_IC50)
     print(paste0("Processing ", database, " data."))
@@
 
-    # Get all G2P gene-cell line combinations
-    grid <- expand.grid("Cell_line" = unique(filt$Cell_line), "Gene" = g2p_genes)
+    grid <- expand.grid("Cell_line" = unique(filt$Cell_line), "Gene" = gene_list)
     data <-  merge(filt, grid, by = "Cell_line", all.y = TRUE)
@@
     # Merge metadata
-    data <-  merge(data, select(ccl_meta, Cell_line, Histology, CCLE_Name, DepMap_ID, Primary.Disease), by = c("Cell_line", "Histology", "CCLE_Name", "DepMap_ID"), all.y = TRUE)
+    data <-  merge(data, select(ccl_meta, Cell_line, CCLE_histology, CCLE_name, DepMap_ID, disease), by = c("Cell_line", "CCLE_histology", "CCLE_name", "DepMap_ID"), all.y = TRUE)
     ## Add columns for G2P drug-gene and drug-gene-lineage sorting
     data$Drug_Gene <- paste0(data$Drug, "_", data$Gene)
-    data$G2P_Drug_Gene <- ifelse(data$Drug_Gene %in% g2p_druggenes, "Yes", "No")
-    data$Drug_Gene_Lin <- paste0(data$Drug, "_", data$Gene, "_", data$Primary.Disease)
-    data$G2P_Drug_Gene_Lin <- ifelse(data$Drug_Gene_Lin %in% g2p_dgls, "Yes", "No")
+    data$G2P_Drug_Gene <- ifelse(data$Drug_Gene %in% g2p_dg, "Yes", "No")
+    data$Drug_Gene_Lin <- paste0(data$Drug, "_", data$Gene, "_", data$disease)
+    data$G2P_Drug_Gene_Lin <- ifelse(data$Drug_Gene_Lin %in% g2p_dgl, "Yes", "No")
+    data$Gene_Lin <- paste0(data$Gene, "_", data$Gene, "_", data$disease)
+    data$G2P_Gene_Lin <- ifelse(data$Gene_Lin %in% g2p_gl, "Yes", "No")
     print("Merged metadata.")
@@
     data <- merge(data, maf_df, by = c("Gene", "DepMap_ID"), all.x = TRUE)
-    data$Mutation_Status <- ifelse(is.na(data$Mutation_Status), 0, data$Mutation_Status)
+    data$Mutation <- ifelse(is.na(data$Mutation), 0, data$Mutation)
   }
@@
     data <- melt(crispr_all, id.vars = "DepMap_ID", measure.vars = colnames(crispr_all)[2:ncol(crispr_all)], variable.name = "Gene", value.name = "Score")
-    # Get all G2P gene-cell line combinations
-    data <-  filter(data, Gene %in% g2p_genes)
     # Merge cell line metadata
-    data <- merge(data, select(ccl_meta, Cell_line, Histology, CCLE_Name, DepMap_ID, Primary.Disease), by = "DepMap_ID", all.y = TRUE)
-    data$Drug_Gene <- paste0(data$Drug, "_", data$Gene)
-    data$Drug_Gene_Lin <- paste0(data$Drug, "_", data$Gene, "_", data$Primary.Disease)
+    data <- merge(data, select(ccl_meta, Cell_line, CCLE_histology, CCLE_name, DepMap_ID, disease), by = "DepMap_ID", all.y = TRUE)
     print("Merged metadata.")
@@
   ## Summarize number of mutant and Wildtype cell lines
-  data_muts_summ <- data %>% group_by(Gene) %>% summarize(N_Wildtype = length(Mutation_Status) - sum(Mutation_Status == 1), N_Mutant = sum(Mutation_Status == 1))
+  data_muts_summ <- data %>% group_by(Gene) %>% summarize(N_Wildtype = length(Mutation) - sum(Mutation == 1), N_Mutant = sum(Mutation == 1))
   ## Merge test results back into full dataset, which restores information lost in the summarization
@@
 
-ccle <- MergeOmicsG2P(database = "CCLE", maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, outfile = "./data_munging/rds/ccle_data_19Q2.rds")
-# ctrp <- MergeOmicsG2P(database = "CTRP", maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, outfile = "./../htscreens_giant_files/ctrp_data_19Q2.rds")
-# gdsc <- MergeOmicsG2P(database = "GDSC", maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, outfile = "./data_munging/rds/gdsc_data_19Q2.rds")
+ccle <- MergeOmicsG2P(database = "CCLE", maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./../htscreens_giant_files/ccle_data_19Q2.rds")
+ctrp <- MergeOmicsG2P(database = "CTRP", maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./../htscreens_giant_files/ctrp_data_19Q2.rds")
+gdsc <- MergeOmicsG2P(database = "GDSC", maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./../htscreens_giant_files/gdsc_data_19Q2.rds")
+
+# all_genes <- intersect(unique(maf_df$Gene), intersect(unique(cn_melt$Gene), unique(ge_melt$Gene)))
+# ccle <- MergeOmicsG2P(database = "CCLE", maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = all_genes, outfile = "./../htscreens_giant_files/ccle_data_19Q2.rds")
+# ctrp <- MergeOmicsG2P(database = "CTRP", maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = all_genes, outfile = "./../htscreens_giant_files/ctrp_data_19Q2.rds")
+# gdsc <- MergeOmicsG2P(database = "GDSC", maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = all_genes, outfile = "./../htscreens_giant_files/gdsc_data_19Q2.rds")
 ```
 
-```{r}
-ccle_missense <- filter(ccle, Variant_Classification == "Missense_Mutation")
-ccle_missense_grid <- expand.grid("Gene" = unique(ccle_missense$Gene), "DepMap_ID" = unique(ccle_missense$DepMap_ID))
-ccle_missense_grid$Variant_Classification <- NA
-ccle_missense <- merge(ccle_missense, ccle_missense_grid, by = c("Gene", "DepMap_ID", "Variant_Classification"), all = TRUE)
-```
-
-```{r load_drug_rds, eval=TRUE}
-ccle_ptmuts <- readRDS("./data_munging/rds/ccle_data_19Q2_g2pgenes_ptmuts.rds") %>% drop_na(Drug)
-ctrp_ptmuts <- readRDS("./../htscreens_giant_files/ctrp_data_19Q2_g2pgenes_ptmuts.rds") %>% drop_na(Drug)
-gdsc_ptmuts <- readRDS("./data_munging/rds/gdsc_data_19Q2_g2pgenes_ptmuts.rds") %>% drop_na(Drug)
+```{r load_drug_rds, eval=FALSE}
+ccle <- readRDS("./data_munging/rds/ccle_data_19Q2_g2pgenes_ptmuts.rds") %>% drop_na(Drug)
+ctrp <- readRDS("./data_munging/rds/ctrp_data_19Q2_g2pgenes_ptmuts.rds") %>% drop_na(Drug)
+gdsc <- readRDS("./data_munging/rds/gdsc_data_19Q2_g2pgenes_ptmuts.rds") %>% drop_na(Drug)
 

### 2019-05-17 19Q2.Rmd

@@
 ccl_converter <- read.delim("./data_munging/cell_line_database_v1_20180911.tsv", row.names = 1, sep = "\t", header = TRUE)
-colnames(ccl_converter)[colnames(ccl_converter) == "Broad_ID"] <- "DepMap_ID"
+colnames(ccl_converter)[colnames(ccl_converter) == "DepMap_ID"] <- "DepMap_ID"
 ccl_lineage_converter <- unique(ccl_converter[, c("DepMap_ID", "grouped_general_doid", "group_general_lineage_name")])
@@
 g2p[g2p == -1] <- ""
-g2p$Gene <- ifelse(is.na(g2p$Gene) & g2p$Drug == "daunorubicin", "MLL", as.character(g2p$Gene))
+g2p$Gene <- ifelse(g2p$Gene == "" & g2p$Drug == "daunorubicin", "MLL", as.character(g2p$Gene))
 g2p$Direction <- ifelse(g2p$Direction == 1 | g2p$Direction == "", NA, as.character(g2p$Direction))
@@
 
-ccle <- MergeOmicsG2P(database = "CCLE", maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./../htscreens_giant_files/ccle_data_19Q2.rds")
+ccle <- MergeOmicsG2P(database = "CCLE", maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./data_munging/19Q2/ccle_data_19Q2.rds")
+write.csv.gz(ccle %>% drop_na(Score), "./data_munging/19Q2/ccle_data_19Q2.csv.gz")
+
 ctrp <- MergeOmicsG2P(database = "CTRP", maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./../htscreens_giant_files/ctrp_data_19Q2.rds")
-gdsc <- MergeOmicsG2P(database = "GDSC", maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./../htscreens_giant_files/gdsc_data_19Q2.rds")
+write.csv.gz(ctrp %>% drop_na(Score), "./../htscreens_giant_files/ctrp_data_19Q2.csv.gz")
+
+gdsc <- MergeOmicsG2P(database = "GDSC", maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./data_munging/19Q2/gdsc_data_19Q2.rds")
+write.csv.gz(gdsc %>% drop_na(Score), "./../htscreens_giant_files/gdsc_data_19Q2.csv.gz")
 
@@
 
-```{r load_drug_rds, eval=FALSE}
-ccle <- readRDS("./data_munging/rds/ccle_data_19Q2_g2pgenes_ptmuts.rds") %>% drop_na(Drug)
-ctrp <- readRDS("./data_munging/rds/ctrp_data_19Q2_g2pgenes_ptmuts.rds") %>% drop_na(Drug)
-gdsc <- readRDS("./data_munging/rds/gdsc_data_19Q2_g2pgenes_ptmuts.rds") %>% drop_na(Drug)
+```{r load_drug_rds, eval=TRUE}
+ccle <- readRDS("./data_munging/19Q2/ccle_data_19Q2.rds") %>% drop_na(Drug)
+ctrp <- readRDS("./../htscreens_giant_files/ctrp_data_19Q2.rds") %>% drop_na(Drug)
+gdsc <- readRDS("./data_munging/19Q2/gdsc_data_19Q2.rds") %>% drop_na(Drug)
 
 # Testing
-test_ccle <- ccle_ptmuts %>% count(Drug)
-test_ctrp <- ctrp_ptmuts %>% count(Drug)
-sum(!is.na(str_match(test_ctrp$Drug, "ratio")))
-test_gdsc <- gdsc_ptmuts %>% count(Drug)
+test_ccle <- ccle %>% count(Drug)
+test_ctrp <- ctrp %>% count(Drug)
+test_gdsc <- gdsc %>% count(Drug)
 ```
@@
   counter = 0
-  if(drug %in% as.character(unique(ccle$Drug))) { counter <- counter + 1 }
-  if(drug %in% as.character(unique(ctrp$Drug))) { counter <- counter + 1 }
-  if(drug %in% as.character(unique(gdsc$Drug))) { counter <- counter + 1 }
+  if(drug %in% as.character(unique(ccle$Drug[!is.na(ccle$Drug)]))) { counter <- counter + 1 }
+  if(drug %in% as.character(unique(ctrp$Drug[!is.na(ctrp$Drug)]))) { counter <- counter + 1 }
+  if(drug %in% as.character(unique(gdsc$Drug[!is.na(gdsc$Drug)]))) { counter <- counter + 1 }
   drug_summ <- rbind(drug_summ, data.frame(Drug = drug, Dataset_Count = counter))
 }
+```
+
+# EXPLORATORY FIGURES
+
+--------------------------------------------------------------------------------
+
+## Mutation
+
+## Cell line and drug overlaps
+
+```{r ccl_venn, eval=FALSE}
+ccle_ccls <- unique(ccle$DepMap_ID)
+ctrp_ccls <- unique(ctrp$DepMap_ID)
+gdsc_ccls <- unique(gdsc$DepMap_ID)
+# crispr_ccls <- unique(crispr_ccls$DepMap_ID)
+
+# futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
+# venn.diagram(x = list(ccle_ccls, ctrp_ccls, gdsc_ccls, crispr_ccls),
+#              filename = "./plots/manuscript/all_venn_ccls.png",
+#              output = TRUE, imagetype = "png",
+#              height = 2000, width = 2000, resolution = 500,
+#              lwd = 1, cex = 1,
+#              category.names = c("CCLE", "CTRP", "GDSC", "CRISPR"),
+#              cat.cex = 1.4, cat.fontface = "bold", cat.default.pos = "outer",
+#              # cat.dist = c(0.06, 0.06, 0.035),
+#              fill = c("springgreen4", "steelblue4", "turquoise4", "darkorchid"))
+futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
+venn.diagram(x = list(ccle_ccls, ctrp_ccls, gdsc_ccls),
+             filename = "./plots/manuscript/drug_venn_ccls.png",
+             output = TRUE, imagetype = "png",
+             height = 2000, width = 2000, resolution = 500,
+             lwd = 1, cex = 1.4,
+             category.names = c("CCLE", "CTRP", "GDSC"),
+             cat.cex = 1.4, cat.fontface = "bold", cat.default.pos = "outer",
+             cat.dist = c(0.06, 0.06, 0.035),
+             fill = c("springgreen4", "steelblue4", "turquoise4"))
+```
+
+```{r drug_venn, eval=FALSE}
+ccle_drugs <- unique(ccle$Drug)
+ctrp_drugs <- unique(ctrp$Drug)
+gdsc_drugs <- unique(gdsc$Drug)
+
+futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
+venn.diagram(x = list(ccle_drugs, ctrp_drugs, gdsc_drugs),
+             filename = "./plots/manuscript/drug_venn_drugs.png",
+             output = TRUE, imagetype = "png",
+             height = 2000, width = 2000, resolution = 500,
+             lwd = 1, cex = 1.4,
+             category.names = c("CCLE", "CTRP", "GDSC"),
+             cat.cex = 1.4, cat.fontface = "bold", cat.default.pos = "outer",
+             cat.dist = c(0.06, 0.06, 0.035),
+             fill = c("palegreen3", "slategray3", "paleturquoise3"))
+```
+
+## Histology distributions
+
+**RUN THIS WHEN CRISPR IS DONE MERGING (5/17)**
+```{r histology_dists_data, eval=FALSE}
+ccle_hists <- unique(select(ccle, DepMap_ID, disease)) %>% count(disease)
+ccle_hists$Perc <- ccle_hists$n / sum(ccle_hists$n) * 100
+ccle_hists$Dataset <- "CCLE"
+ctrp_hists <- unique(select(ctrp, DepMap_ID, disease)) %>% count(disease)
+ctrp_hists$Perc <- ctrp_hists$n / sum(ctrp_hists$n) * 100
+ctrp_hists$Dataset <- "CTRP"
+gdsc_hists <- unique(select(gdsc, DepMap_ID, disease)) %>% count(disease)
+gdsc_hists$Perc <- gdsc_hists$n / sum(gdsc_hists$n) * 100
+gdsc_hists$Dataset <- "GDSC"
+crispr_hists <- unique(select(crispr, DepMap_ID, disease)) %>% count(disease)
+crispr_hists$Perc <- crispr_hists$n / sum(crispr_hists$n) * 100
+crispr_hists$Dataset <- "CRISPR"
+
+drug_hists <- rbind(ccle_hists, ctrp_hists, gdsc_hists, crispr_hists) %>% drop_na(disease)
+drug_hists$Dataset <- factor(drug_hists$Dataset, levels = c("CCLE", "CTRP", "GDSC", "CRISPR"))
+drug_hists$disease <- as.character(drug_hists$disease)
+drug_hists$disease <- gsub(" cancer", "", drug_hists$disease)
+saveRDS(drug_hists, "./data_munging/rds/histology_distributions.rds")
+```
+
+**RUN THIS WHEN CRISPR IS DONE MERGING (5/17)**
+```{r histology_dists, fig.height=4.5, fig.width=4, eval=FALSE}
+drug_hists <- readRDS("./data_munging/rds/histology_distributions.rds")
+# png(filename = "./plots/manuscript/all_histology_distributions.png", width = 8, height = 9, units = "in", res = 500)
+ggplot(drug_hists, aes(x = Dataset, y = n, fill = disease)) +
+  geom_bar(stat = "identity", color = "black") +
+  scale_y_continuous(breaks = seq(0, 850, by = 50), labels = seq(0, 850, by = 50)) +
+  guides(fill = guide_legend(title = "Histology", ncol = 1)) +
+  labs(y = "Count")
+# dev.off()
+```
+
+**RUN THIS WHEN CRISPR IS DONE MERGING (5/17)**
+```{r, eval=FALSE}
+ccle_ccls <- unique(ccle$DepMap_ID)
+ctrp_ccls <- unique(ctrp$DepMap_ID)
+gdsc_ccls <- unique(gdsc$DepMap_ID)
+crispr_ccls <- unique(crispr$DepMap_ID)
+
+ccls <- data.frame(DepMap_ID = union(ccle_ccls, union(ctrp_ccls, gdsc_ccls)))
+all_ccls <- merge(ccls, ccl_meta, by = "DepMap_ID")
+all_ccls$disease <- gsub(" cancer", "", all_ccls$disease)
+
+png(filename = "./plots/manuscript/drug_histology_distributions.png", width = 8, height = 4, units = "in", res = 500)
+ggplot(all_ccls, aes(x = fct_infreq(factor(disease)), fill = disease)) +
+  geom_bar(color = "black") +
+  scale_y_continuous(breaks = seq(0, 220, by = 40), labels = seq(0, 220, by = 40)) +
+  guides(fill = FALSE) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
+  labs(y = "Number of Cell Lines", x = "Histology", caption = paste0(formatC(nrow(all_ccls), format = "d", big.mark = ","), " cell lines represented."))
+dev.off()
+```
+
+## G2P summary heatmap
+
+```{r dg_heatmap, fig.height=6, fig.width=8, warning=FALSE}
+g2p_dg_counts <- g2p %>% count(Drug, Gene) %>% filter(!is.na(Drug), !is.na(Gene))
+g2p_dg_counts <- dcast(g2p_dg_counts, Drug ~ Gene, value.var = "n", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Drug)
+g2p_dg_counts <- g2p_dg_counts[order(rowSums(-g2p_dg_counts)), order(colSums(-g2p_dg_counts))]
+g2p_dg_counts[g2p_dg_counts == 0] <- NA
+
+g2p_gene_order <- colnames(g2p_dg_counts)
+g2p_drug_order <- rownames(g2p_dg_counts)
+
+# Create annotation layer
+hta_data <- data.frame(Drug = rownames(g2p_dg_counts), CCLE = NA, CTRP = NA, GDSC = NA)
+hta_data$CCLE <- ifelse(hta_data$Drug %in% unique(ccle$Drug), "Screened", "Not screened")
+hta_data$CTRP <- ifelse(hta_data$Drug %in% unique(ctrp$Drug), "Screened", "Not screened")
+hta_data$GDSC <- ifelse(hta_data$Drug %in% unique(gdsc$Drug), "Screened", "Not screened")
+rownames(hta_data) <- hta_data$Drug
+hta_data$Drug <- NULL
+
+hta_annot <- HeatmapAnnotation(text = anno_text(colnames(hta_data), offset = unit(0.1, "in"), gp = gpar(fontsize = 10)))
+hta_legend_list <- list(legend_direction = "horizontal", border = "gray70", nrow = 2)
+hta <- Heatmap(hta_data,
+               name = "Functional screen status           ",
+               col = c("Screened" = "purple4", "Not screened" = "gray97"), 
+               rect_gp = gpar(col = "gray70"),
+               top_annotation = hta_annot,
+               heatmap_legend_param = hta_legend_list,
+               row_names_side = "left",
+               row_names_gp = gpar(fontsize = 10),
+               column_names_side = "top",
+               column_names_gp = gpar(fontsize = 10),
+               show_column_names = FALSE,
+               cluster_rows = FALSE, 
+               cluster_columns = FALSE,
+               row_title = "Drugs",
+               row_title_gp = gpar(fontface = "bold", fontsize = 14),
+               column_title = "Dataset",
+               column_title_gp = gpar(fontface = "bold", fontsize = 14),
+               width = unit(1.5, "in"))
+
+# Define color scale
+col_fun <- colorRamp2(c(0, 100), c("mistyrose", "purple4"))
+# Legend properties list
+ht_legend_list <- list(legend_direction = "horizontal", legend_width = unit(2.5, "in"), border = "gray70")
+ht <- Heatmap(g2p_dg_counts, 
+              name = "Number of G2P interpretations",
+              col = col_fun,
+              na_col = "gray97",
+              rect_gp = gpar(col = "gray70"),
+              heatmap_legend_param = ht_legend_list,
+              cluster_rows = FALSE, 
+              cluster_columns = FALSE, 
+              show_row_names = FALSE,
+              row_names_side = "left",
+              row_names_gp = gpar(fontsize = 10),
+              column_names_side = "bottom",
+              column_names_gp = gpar(fontsize = 10),
+              show_column_names = FALSE,
+              bottom_annotation = HeatmapAnnotation(
+                  text = anno_text(colnames(g2p_dg_counts),
+                                   rot = 45,
+                                   gp = gpar(fontsize = 10),
+                                   offset = unit(1, "npc"),
+                                   just = "right"),
+                  annotation_height = unit(0.45, "in")),
+              row_title = "Drugs",
+              row_title_gp = gpar(fontface = "bold", fontsize = 14),
+              column_title = "Genes", 
+              column_title_gp = gpar(fontface = "bold", fontsize = 14),
+              column_title_side = "bottom")
+
+png(filename = "./plots/manuscript/g2p_summary_heatmap.png", width = 10, height = 9, units = "in", res = 500)
+draw(hta + ht, gap = unit(5, "mm"), heatmap_legend_side = "top")
+dev.off()
+```
+
+## Clustered AUC heatmap
+
+```{r}
+ccle_auc_grid <- dcast(filter(ccle_ptmuts, Drug %in% g2p_drugs), Drug ~ DepMap_ID, value.var = "Score", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Drug)
+ctrp_auc_grid <- dcast(filter(ctrp_ptmuts, Drug %in% g2p_drugs), Drug ~ DepMap_ID, value.var = "Score", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Drug)
+gdsc_auc_grid <- dcast(filter(gdsc_ptmuts, Drug %in% g2p_drugs), Drug ~ DepMap_ID, value.var = "Score", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Drug)
+
+ccle_auc_ht <- Heatmap(ccle_auc_grid,
+                       name = "AUC",
+                       show_column_names = FALSE, 
+                       column_title = "CCLE",
+                       column_title_side = "top")
+ctrp_auc_ht <- Heatmap(ctrp_auc_grid,
+                       name = "AUC",
+                       show_column_names = FALSE, 
+                       column_title = "CTRP",
+                       column_title_side = "top")
+gdsc_auc_ht <- Heatmap(gdsc_auc_grid,
+                       name = "AUC",
+                       show_column_names = FALSE, 
+                       column_title = "GDSC",
+                       column_title_side = "top")
+
+draw(ccle_auc_ht)
+draw(ctrp_auc_ht)
+draw(gdsc_auc_ht)
+```
+
+# WILCOXON (MUT)
+
+--------------------------------------------------------------------------------
+
+```{r wilcoxon_functions}
+adj_signif <- function(df, alpha) {
+  # Takes df from compare_means and creates a signif code column for FDR-adjusted p-vals
+  df$p.signif.adj <- ifelse(df$p.adj <= alpha, "*", NA)
+  df$p.signif <- ifelse(df$p.signif == "ns", NA, df$p.signif)
+  df$p.short <- formatC(df$p, format = "g", digits =  2)
+  df$p.adj.short <- formatC(df$p.adj, format = "g", digits =  2)
+  return(df)
+}
+
+WilcoxonTestDF <- function(dataframe, grouping, outfile) {
+  require(ggpubr)
+  if("Drug_Gene_Lin" %in% grouping) {
+    # Filter out DGLs with too few samples in at least one mutation status category
+    count_mut_n <- dataframe %>% count(Drug_Gene_Lin, Mutation) %>% filter(n >= 3)
+    count_mut_category <- count_mut_n %>% count(Drug_Gene_Lin) %>% filter(n == 2)
+    dgl_keep <- intersect(count_mut_n$Drug_Gene_Lin, count_mut_category$Drug_Gene_Lin)
+    dataframe <- filter(dataframe, Drug_Gene_Lin %in% dgl_keep)
+    dataframe$Drug_Gene_Lin <- as.character(dataframe$Drug_Gene_Lin)
+  }
+  signif <- compare_means(Score ~ Mutation, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
+  signif <- adj_signif(signif, alpha = 0.05)
+  signif <- signif[order(signif$p),]
+  if("Drug_Gene" %in% grouping) {
+    signif$InG2P <- ifelse(signif$Drug_Gene %in% g2p_dg, "Yes", "No")
+  }
+  if("Drug_Gene_Lin" %in% grouping) {
+    signif$InG2P <- ifelse(signif$Drug_Gene_Lin %in% g2p_dgl, "Yes", "No")
+  }
+  saveRDS(signif, outfile)
+  return(signif)
+}
+```
+
+```{r wilcoxon_tests, eval=FALSE}
+# crispr_ptmuts <- unfactorize(crispr_ptmuts)
+# # crispr_signif_all_gene <- WilcoxonTestDF(dataframe = crispr_ptmuts, grouping = "Gene", outfile = "./data_munging/rds/crispr_signif_gene.rds")
+# crispr_ptmuts_filt <- filter(crispr_ptmuts, Gene %in% g2p_genes)
+# crispr_signif_gene <- WilcoxonTestDF(dataframe = crispr_ptmuts_filt, grouping = "Gene", outfile = "./data_munging/rds/crispr_signif_g2p_gene.rds")
+# crispr_signif_lineage <- WilcoxonTestDF(dataframe = crispr_ptmuts_filt, grouping = c("Gene", "Primary.Disease"), outfile = "./data_munging/rds/crispr_signif_g2p_lineage.rds")
+
+ccle_filt <- filter(ccle, Drug %in% g2p_drugs & Gene %in% g2p_genes)
+ccle_filt$Gene <- factor(ccle_filt$Gene, ordered = FALSE)
+ccle_filt <- unfactorize(ccle_filt)
+ccle_signif_dg <- WilcoxonTestDF(dataframe = ccle, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/ccle_signif_dg.rds")
+ccle_signif_g2p_dg <- WilcoxonTestDF(dataframe = ccle_filt, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/ccle_signif_g2p_dg.rds")
+ccle_signif_g2p_dgl <- WilcoxonTestDF(dataframe = ccle_filt, grouping = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), outfile = "./data_munging/rds/ccle_signif_g2p_dgl.rds")
+
+# ctrp_filt <- filter(ctrp, Drug %in% g2p_drugs)
+# ctrp_filt$Gene <- factor(ctrp_filt$Gene, ordered = FALSE)
+# ctrp_filt <- unfactorize(ctrp_filt)
+# ctrp_signif_gene <- WilcoxonTestDF(dataframe = ctrp, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/ctrp_signif_g2p_gene.rds")
+# ctrp_signif_g2p_druggene <- WilcoxonTestDF(dataframe = filter(ctrp, Drug %in% g2p_drugs & Gene %in% g2p_genes), grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/ctrp_signif_g2p_druggene.rds")
+# ctrp_signif_lineage <- WilcoxonTestDF(dataframe = ctrp_filt, grouping = c("Drug", "Gene", "Primary.Disease", "Drug_Gene_Lin"), outfile = "./data_munging/rds/ctrp_signif_g2p_lineage.rds")
+# 
+# gdsc_filt <- filter(gdsc, Drug %in% g2p_drugs)
+# gdsc_filt$Gene <- factor(gdsc_filt$Gene, ordered = FALSE)
+# gdsc_filt <- unfactorize(gdsc_filt)
+# gdsc_signif_gene <- WilcoxonTestDF(dataframe = gdsc, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/gdsc_signif_g2p_gene.rds")
+# gdsc_signsif_g2p_druggene <- WilcoxonTestDF(dataframe = filter(gdsc, Drug %in% g2p_drugs & Gene %in% g2p_genes), grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/gdsc_signif_g2p_druggene.rds")
+# gdsc_signif_lineage <- WilcoxonTestDF(dataframe = gdsc_filt, grouping = c("Drug", "Gene", "Primary.Disease", "Drug_Gene_Lin"), outfile = "./data_munging/rds/gdsc_signif_g2p_lineage.rds")
+```
+
+```{r load_wilcoxon_rds}
+# crispr_signif_gene <- readRDS("./data_munging/rds/crispr_signif_g2p_gene.rds")
+# crispr_signif_lineage <- readRDS("./data_munging/rds/crispr_signif_g2p_lineage.rds")
+
+ccle_signif_gene <- readRDS("./data_munging/rds/ccle_signif_g2p_gene.rds")
+ccle_signif_g2p_druggene <- readRDS("./data_munging/rds/ccle_signif_g2p_druggene.rds")
+ccle_signif_lineage <- readRDS("./data_munging/rds/ccle_signif_g2p_lineage.rds")
+
+ctrp_signif_gene <- readRDS("./data_munging/rds/ctrp_signif_g2p_gene.rds")
+ctrp_signif_g2p_druggene <- readRDS("./data_munging/rds/ctrp_signif_g2p_druggene.rds")
+ctrp_signif_lineage <- readRDS("./data_munging/rds/ctrp_signif_g2p_lineage.rds")
+
+gdsc_signif_gene <- readRDS("./data_munging/rds/gdsc_signif_g2p_gene.rds")
+gdsc_signif_g2p_druggene <- readRDS("./data_munging/rds/gdsc_signif_g2p_druggene.rds")
+gdsc_signif_lineage <- readRDS("./data_munging/rds/gdsc_signif_g2p_lineage.rds")
 ```

### 2019-05-17 19Q2.Rmd

@@
 ccl_converter <- read.delim("./data_munging/cell_line_database_v1_20180911.tsv", row.names = 1, sep = "\t", header = TRUE)
-colnames(ccl_converter)[colnames(ccl_converter) == "DepMap_ID"] <- "DepMap_ID"
+colnames(ccl_converter)[colnames(ccl_converter) == "Broad_ID"] <- "DepMap_ID"
 ccl_lineage_converter <- unique(ccl_converter[, c("DepMap_ID", "grouped_general_doid", "group_general_lineage_name")])
@@
 `r nrow(filter(test, n != 1))`/`r nrow(test)` gene-cell line combinations have more than one mutation in the MAF file. This is corrected in the point mutation filtering done below.
-
-**MERGE WITHOUT G2P AND PTMUT FILTER (5/15)**
-```{r merge_filter_drug_data, eval=FALSE}
+```{r merge_drug_data, eval=FALSE}
 # Load in Pozdeyev et al. (2016) data
@@
 
+## CRISPR
+
+```{r merge_crispr_data, eval=TRUE}
+crispr_all <- read.delim("./data_munging/19Q2/Achilles_gene_effect_20190514.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
+# Remove Entrez gene IDs from colnames
+colnames(crispr_all) <- gsub(" .*", "", colnames(crispr_all))
+colnames(crispr_all)[1] <- "DepMap_ID"
+
+# Melt CRISPR dataset for merging
+# crispr_melt <- melt(crispr_all, id.vars = "DepMap_ID", measure.vars = colnames(crispr_all)[2:ncol(crispr_all)], variable.name = "Gene", value.name = "Score")
+
+crispr <- MergeOmicsG2P(database = "CRISPR", maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./data_munging/19Q2/crispr_data_19Q2.rds")
+write.csv.gz(crispr %>% drop_na(Score), "./data_munging/19Q2/crispr_data_19Q2.csv.gz")
+```
+
 # EXPLORATORY FIGURES
@@
 
-```{r ccl_venn, eval=FALSE}
+```{r ccl_venn, eval=TRUE}
 ccle_ccls <- unique(ccle$DepMap_ID)
@@
 gdsc_ccls <- unique(gdsc$DepMap_ID)
-# crispr_ccls <- unique(crispr_ccls$DepMap_ID)
+crispr_ccls <- unique(crispr_ccls$DepMap_ID)
 
-# futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
-# venn.diagram(x = list(ccle_ccls, ctrp_ccls, gdsc_ccls, crispr_ccls),
-#              filename = "./plots/manuscript/all_venn_ccls.png",
-#              output = TRUE, imagetype = "png",
-#              height = 2000, width = 2000, resolution = 500,
-#              lwd = 1, cex = 1,
-#              category.names = c("CCLE", "CTRP", "GDSC", "CRISPR"),
-#              cat.cex = 1.4, cat.fontface = "bold", cat.default.pos = "outer",
-#              # cat.dist = c(0.06, 0.06, 0.035),
-#              fill = c("springgreen4", "steelblue4", "turquoise4", "darkorchid"))
+futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
+venn.diagram(x = list(ccle_ccls, ctrp_ccls, gdsc_ccls, crispr_ccls),
+             filename = "./plots/manuscript/all_venn_ccls.png",
+             output = TRUE, imagetype = "png",
+             height = 2000, width = 2000, resolution = 500,
+             lwd = 1, cex = 1,
+             category.names = c("CCLE", "CTRP", "GDSC", "CRISPR"),
+             cat.cex = 1.4, cat.fontface = "bold", cat.default.pos = "outer",
+             # cat.dist = c(0.06, 0.06, 0.035),
+             fill = c("springgreen4", "steelblue4", "turquoise4", "darkorchid"))
 futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
@@
 **RUN THIS WHEN CRISPR IS DONE MERGING (5/17)**
-```{r histology_dists_data, eval=FALSE}
+```{r histology_dists_data, eval=TRUE}
 ccle_hists <- unique(select(ccle, DepMap_ID, disease)) %>% count(disease)
@@
 **RUN THIS WHEN CRISPR IS DONE MERGING (5/17)**
-```{r histology_dists, fig.height=4.5, fig.width=4, eval=FALSE}
+```{r histology_dists, fig.height=4.5, fig.width=4, eval=TRUE}
 drug_hists <- readRDS("./data_munging/rds/histology_distributions.rds")
-# png(filename = "./plots/manuscript/all_histology_distributions.png", width = 8, height = 9, units = "in", res = 500)
+png(filename = "./plots/manuscript/all_histology_distributions.png", width = 8, height = 9, units = "in", res = 500)
 ggplot(drug_hists, aes(x = Dataset, y = n, fill = disease)) +
@@
   labs(y = "Count")
-# dev.off()
+dev.off()
 ```
@@
 **RUN THIS WHEN CRISPR IS DONE MERGING (5/17)**
-```{r, eval=FALSE}
+```{r, eval=TRUE}
 ccle_ccls <- unique(ccle$DepMap_ID)
@@
 g2p_dg_counts <- g2p_dg_counts[order(rowSums(-g2p_dg_counts)), order(colSums(-g2p_dg_counts))]
-g2p_dg_counts[g2p_dg_counts == 0] <- NA
+# g2p_dg_counts[g2p_dg_counts == 0] <- NA
 
@@
 # Define color scale
-col_fun <- colorRamp2(c(0, 100), c("mistyrose", "purple4"))
+col_fun <- colorRamp2(c(0, 1, 100), c("gray97", "mistyrose", "purple4"))
 # Legend properties list
@@
 
-```{r}
-ccle_auc_grid <- dcast(filter(ccle_ptmuts, Drug %in% g2p_drugs), Drug ~ DepMap_ID, value.var = "Score", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Drug)
-ctrp_auc_grid <- dcast(filter(ctrp_ptmuts, Drug %in% g2p_drugs), Drug ~ DepMap_ID, value.var = "Score", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Drug)
-gdsc_auc_grid <- dcast(filter(gdsc_ptmuts, Drug %in% g2p_drugs), Drug ~ DepMap_ID, value.var = "Score", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Drug)
+```{r auc_clustered_ht, eval=FALSE}
+ccle_auc_grid <- dcast(ccle, Drug ~ DepMap_ID, value.var = "Score", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Drug)
+ctrp_auc_grid <- dcast(ctrp, Drug ~ DepMap_ID, value.var = "Score", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Drug)
+gdsc_auc_grid <- dcast(gdsc, Drug ~ DepMap_ID, value.var = "Score", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Drug)
 
+ccle_lineages_ha <- merge(data.frame("DepMap_ID" = colnames(ccle_auc_grid)), select(ccl_meta, DepMap_ID, disease), by = "DepMap_ID", all.x = TRUE) %>% `rownames<-`(.[,1]) %>% select(-DepMap_ID)
+ctrp_lineages_ha <- merge(data.frame("DepMap_ID" = colnames(ctrp_auc_grid)), select(ccl_meta, DepMap_ID, disease), by = "DepMap_ID", all.x = TRUE) %>% `rownames<-`(.[,1]) %>% select(-DepMap_ID)
+gdsc_lineages_ha <- merge(data.frame("DepMap_ID" = colnames(gdsc_auc_grid)), select(ccl_meta, DepMap_ID, disease), by = "DepMap_ID", all.x = TRUE) %>% `rownames<-`(.[,1]) %>% select(-DepMap_ID)
+
+ht_legend_list <- list(direction = "horizontal")
+
+ccle_col_fun <- colorRamp2(c(0, 1), c("gray97", "darkgreen"))
+ccle_auc_ha <- HeatmapAnnotation(Lineage = ccle_lineages_ha$disease, annotation_legend_param = list(Lineage = list(direction = "horizontal", nrow = 5)))
 ccle_auc_ht <- Heatmap(ccle_auc_grid,
+                       na_col = "black",
+                       col = ccle_col_fun,
+                       top_annotation = ccle_auc_ha,
+                       heatmap_legend_param = ht_legend_list,
                        name = "AUC",
                        show_column_names = FALSE, 
-                       column_title = "CCLE",
+                       row_title = "Drugs and Small Molecules",
+                       column_title = "Cancer Cell Lines",
                        column_title_side = "top")
+
+ctrp_col_fun <- colorRamp2(c(0, 1), c("gray97", "steelblue4"))
+ctrp_auc_ha <- HeatmapAnnotation(Lineage = ctrp_lineages_ha$disease, annotation_legend_param = list(Lineage = list(direction = "horizontal", nrow = 3)))
 ctrp_auc_ht <- Heatmap(ctrp_auc_grid,
+                       na_col = "black",
+                       col = ctrp_col_fun,
+                       top_annotation = ctrp_auc_ha,
+                       heatmap_legend_param = ht_legend_list,
                        name = "AUC",
                        show_column_names = FALSE, 
-                       column_title = "CTRP",
+                       row_title = "Drugs and Small Molecules",
+                       column_title = "Cancer Cell Lines",
                        column_title_side = "top")
+
+gdsc_col_fun <- colorRamp2(c(0, 1), c("gray97", "turquoise4"))
+gdsc_auc_ha <- HeatmapAnnotation(Lineage = gdsc_lineages_ha$disease, annotation_legend_param = list(Lineage = list(direction = "horizontal", nrow = 3)))
 gdsc_auc_ht <- Heatmap(gdsc_auc_grid,
+                       na_col = "black",
+                       col = gdsc_col_fun,
+                       top_annotation = gdsc_auc_ha,
+                       heatmap_legend_param = ht_legend_list,
                        name = "AUC",
                        show_column_names = FALSE, 
-                       column_title = "GDSC",
+                       row_title = "Drugs and Small Molecules",
+                       column_title = "Cancer Cell Lines",
                        column_title_side = "top")
 
-draw(ccle_auc_ht)
-draw(ctrp_auc_ht)
-draw(gdsc_auc_ht)
+png(filename = "./plots/manuscript/ccle_clustered_heatmap.png", width = 10, height = 8, units = "in", res = 500)
+draw(ccle_auc_ht, merge_legend = TRUE, heatmap_legend_side = "top", annotation_legend_side = "top")
+dev.off()
+
+png(filename = "./plots/manuscript/ctrp_clustered_heatmap.png", width = 22, height = 40, units = "in", res = 500)
+draw(ctrp_auc_ht, merge_legend = TRUE, heatmap_legend_side = "top", annotation_legend_side = "top")
+dev.off()
+
+png(filename = "./plots/manuscript/gdsc_clustered_heatmap.png", width = 18, height = 20, units = "in", res = 500)
+draw(gdsc_auc_ht, merge_legend = TRUE, heatmap_legend_side = "top", annotation_legend_side = "top")
+dev.off()
 ```
@@
 
-```{r wilcoxon_tests, eval=FALSE}
+```{r wilcoxon_tests, eval=TRUE}
 # crispr_ptmuts <- unfactorize(crispr_ptmuts)
@@
 
-ccle_filt <- filter(ccle, Drug %in% g2p_drugs & Gene %in% g2p_genes)
-ccle_filt$Gene <- factor(ccle_filt$Gene, ordered = FALSE)
-ccle_filt <- unfactorize(ccle_filt)
-ccle_signif_dg <- WilcoxonTestDF(dataframe = ccle, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/ccle_signif_dg.rds")
-ccle_signif_g2p_dg <- WilcoxonTestDF(dataframe = ccle_filt, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/ccle_signif_g2p_dg.rds")
-ccle_signif_g2p_dgl <- WilcoxonTestDF(dataframe = ccle_filt, grouping = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), outfile = "./data_munging/rds/ccle_signif_g2p_dgl.rds")
+# ccle_filt <- filter(ccle, Drug %in% g2p_drugs & Gene %in% g2p_genes)
+# ccle_filt$Gene <- factor(ccle_filt$Gene, ordered = FALSE)
+# ccle_filt <- unfactorize(ccle_filt)
+# ccle_signif_dg <- WilcoxonTestDF(dataframe = ccle, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/ccle_signif_dg.rds")
+# ccle_signif_g2p_dg <- WilcoxonTestDF(dataframe = ccle_filt, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/ccle_signif_g2p_dg.rds")
+# ccle_signif_g2p_dgl <- WilcoxonTestDF(dataframe = ccle_filt, grouping = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), outfile = "./data_munging/rds/ccle_signif_g2p_dgl.rds")
 
-# ctrp_filt <- filter(ctrp, Drug %in% g2p_drugs)
-# ctrp_filt$Gene <- factor(ctrp_filt$Gene, ordered = FALSE)
-# ctrp_filt <- unfactorize(ctrp_filt)
-# ctrp_signif_gene <- WilcoxonTestDF(dataframe = ctrp, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/ctrp_signif_g2p_gene.rds")
-# ctrp_signif_g2p_druggene <- WilcoxonTestDF(dataframe = filter(ctrp, Drug %in% g2p_drugs & Gene %in% g2p_genes), grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/ctrp_signif_g2p_druggene.rds")
-# ctrp_signif_lineage <- WilcoxonTestDF(dataframe = ctrp_filt, grouping = c("Drug", "Gene", "Primary.Disease", "Drug_Gene_Lin"), outfile = "./data_munging/rds/ctrp_signif_g2p_lineage.rds")
-# 
-# gdsc_filt <- filter(gdsc, Drug %in% g2p_drugs)
-# gdsc_filt$Gene <- factor(gdsc_filt$Gene, ordered = FALSE)
-# gdsc_filt <- unfactorize(gdsc_filt)
-# gdsc_signif_gene <- WilcoxonTestDF(dataframe = gdsc, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/gdsc_signif_g2p_gene.rds")
-# gdsc_signsif_g2p_druggene <- WilcoxonTestDF(dataframe = filter(gdsc, Drug %in% g2p_drugs & Gene %in% g2p_genes), grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/gdsc_signif_g2p_druggene.rds")
-# gdsc_signif_lineage <- WilcoxonTestDF(dataframe = gdsc_filt, grouping = c("Drug", "Gene", "Primary.Disease", "Drug_Gene_Lin"), outfile = "./data_munging/rds/gdsc_signif_g2p_lineage.rds")
+ctrp_filt <- filter(ctrp, Drug %in% g2p_drugs & Gene %in% g2p_genes)
+ctrp_filt$Gene <- factor(ctrp_filt$Gene, ordered = FALSE)
+ctrp_filt <- unfactorize(ctrp_filt)
+ctrp_signif_dg <- WilcoxonTestDF(dataframe = ctrp, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/ctrp_signif_dg.rds")
+ctrp_signif_g2p_dg <- WilcoxonTestDF(dataframe = ctrp_filt, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/ctrp_signif_g2p_dg.rds")
+ctrp_signif_g2p_dgl <- WilcoxonTestDF(dataframe = ctrp_filt, grouping = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), outfile = "./data_munging/rds/ctrp_signif_g2p_dgl.rds")
+
+gdsc_filt <- filter(gdsc, Drug %in% g2p_drugs & Gene %in% g2p_genes)
+gdsc_filt$Gene <- factor(gdsc_filt$Gene, ordered = FALSE)
+gdsc_filt <- unfactorize(gdsc_filt)
+gdsc_signif_dg <- WilcoxonTestDF(dataframe = gdsc, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/gdsc_signif_dg.rds")
+gdsc_signif_g2p_dg <- WilcoxonTestDF(dataframe = gdsc_filt, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/gdsc_signif_g2p_dg.rds")
+gdsc_signif_g2p_dgl <- WilcoxonTestDF(dataframe = gdsc_filt, grouping = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), outfile = "./data_munging/rds/gdsc_signif_g2p_dgl.rds")
 ```
@@
 
-ccle_signif_gene <- readRDS("./data_munging/rds/ccle_signif_g2p_gene.rds")
-ccle_signif_g2p_druggene <- readRDS("./data_munging/rds/ccle_signif_g2p_druggene.rds")
-ccle_signif_lineage <- readRDS("./data_munging/rds/ccle_signif_g2p_lineage.rds")
+# ccle_signif_gene <- readRDS("./data_munging/rds/ccle_signif_g2p_gene.rds")
+# ccle_signif_g2p_druggene <- readRDS("./data_munging/rds/ccle_signif_g2p_druggene.rds")
+# ccle_signif_lineage <- readRDS("./data_munging/rds/ccle_signif_g2p_lineage.rds")
+# 
+# ctrp_signif_gene <- readRDS("./data_munging/rds/ctrp_signif_g2p_gene.rds")
+# ctrp_signif_g2p_druggene <- readRDS("./data_munging/rds/ctrp_signif_g2p_druggene.rds")
+# ctrp_signif_lineage <- readRDS("./data_munging/rds/ctrp_signif_g2p_lineage.rds")
+# 
+# gdsc_signif_gene <- readRDS("./data_munging/rds/gdsc_signif_g2p_gene.rds")
+# gdsc_signif_g2p_druggene <- readRDS("./data_munging/rds/gdsc_signif_g2p_druggene.rds")
+# gdsc_signif_lineage <- readRDS("./data_munging/rds/gdsc_signif_g2p_lineage.rds")
+```
 
-ctrp_signif_gene <- readRDS("./data_munging/rds/ctrp_signif_g2p_gene.rds")
-ctrp_signif_g2p_druggene <- readRDS("./data_munging/rds/ctrp_signif_g2p_druggene.rds")
-ctrp_signif_lineage <- readRDS("./data_munging/rds/ctrp_signif_g2p_lineage.rds")
+# SPEARMAN (CN, GE)
 
-gdsc_signif_gene <- readRDS("./data_munging/rds/gdsc_signif_g2p_gene.rds")
-gdsc_signif_g2p_druggene <- readRDS("./data_munging/rds/gdsc_signif_g2p_druggene.rds")
-gdsc_signif_lineage <- readRDS("./data_munging/rds/gdsc_signif_g2p_lineage.rds")
+--------------------------------------------------------------------------------
+
+```{r drug_spear_calc, warning=FALSE, eval=TRUE}
+g2p_druggene_tally <- g2p %>% group_by(Drug_Gene) %>% tally() %>% drop_na()
+
+# CCLE
+ccle_cor_res <- ccle %>% group_by(Drug, Gene, Drug_Gene) %>% summarize(
+                GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate,
+                GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value,
+                CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate,
+                CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value)
+ccle_cor_res <- merge(g2p_druggene_tally, ccle_cor_res, by = "Drug_Gene", all.y = TRUE)
+ccle_cor_res$n <- ifelse(is.na(ccle_cor_res$n), 0, ccle_cor_res$n)
+ccle_cor_res$InG2P <- ifelse(ccle_cor_res$n != 0, "Yes", "No")
+ccle_cor_res$Dataset <- "CCLE"
+
+# CTRP
+ctrp_cor_res <- ctrp %>% group_by(Drug, Gene, Drug_Gene) %>% summarize(
+                GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate,
+                GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value,
+                CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate,
+                CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value)
+ctrp_cor_res <- merge(g2p_druggene_tally, ctrp_cor_res, by = "Drug_Gene", all.y = TRUE)
+ctrp_cor_res$n <- ifelse(is.na(ctrp_cor_res$n), 0, ctrp_cor_res$n)
+ctrp_cor_res$InG2P <- ifelse(ctrp_cor_res$n != 0, "Yes", "No")
+ctrp_cor_res$Dataset <- "CTRP"
+
+# GDSC
+gdsc_cor_res <- gdsc %>% group_by(Drug, Gene, Drug_Gene) %>% summarize(
+                GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate,
+                GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value,
+                CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate,
+                CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value)
+gdsc_cor_res <- merge(g2p_druggene_tally, gdsc_cor_res, by = "Drug_Gene", all.y = TRUE)
+gdsc_cor_res$n <- ifelse(is.na(gdsc_cor_res$n), 0, gdsc_cor_res$n)
+gdsc_cor_res$InG2P <- ifelse(gdsc_cor_res$n != 0, "Yes", "No")
+gdsc_cor_res$Dataset <- "GDSC"
+
+# All
+g2p_cor <- rbind(ccle_cor_res, ctrp_cor_res, gdsc_cor_res)
+
+saveRDS(g2p_cor, "./data_munging/rds/drug_cor.rds")
+```
+
+```{r load_drug_spear}
+g2p_cor <- readRDS("./data_munging/rds/drug_cor.rds")
+```
+
+Spearman correlations for gene expression and copy number:
+```{r crispr_spear_calc, warning=FALSE}
+crispr_spear_ge <- transform(crispr_ptmuts_filt %>% group_by(Gene) %>% summarize(p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value, p_log10 = -log10(p), corr = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate, Metric = "Gene Expression"), Gene = reorder(Gene, corr))
+crispr_spear_cn <- transform(crispr_ptmuts_filt %>% group_by(Gene) %>% summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value, p_log10 = -log10(p), corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate, Metric = "Copy Number"), Gene = reorder(Gene, corr))
 ```

### 2019-05-18 19Q2.Rmd
update Rmd

@@
 
-```{r merge_crispr_data, eval=TRUE}
+```{r merge_crispr_data, eval=FALSE}
 crispr_all <- read.delim("./data_munging/19Q2/Achilles_gene_effect_20190514.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
@@
 
-```{r ccl_venn, eval=TRUE}
+```{r ccl_venn, eval=FALSE}
 ccle_ccls <- unique(ccle$DepMap_ID)
@@
 gdsc_ccls <- unique(gdsc$DepMap_ID)
-crispr_ccls <- unique(crispr_ccls$DepMap_ID)
+crispr_ccls <- unique(crispr$DepMap_ID)
 
@@
 **RUN THIS WHEN CRISPR IS DONE MERGING (5/17)**
-```{r histology_dists_data, eval=TRUE}
+```{r histology_dists_data, eval=FALSE}
 ccle_hists <- unique(select(ccle, DepMap_ID, disease)) %>% count(disease)
@@
 
-**RUN THIS WHEN CRISPR IS DONE MERGING (5/17)**
-```{r histology_dists, fig.height=4.5, fig.width=4, eval=TRUE}
+```{r histology_dists, fig.height=4.5, fig.width=4, eval=FALSE}
 drug_hists <- readRDS("./data_munging/rds/histology_distributions.rds")
@@
 **RUN THIS WHEN CRISPR IS DONE MERGING (5/17)**
-```{r, eval=TRUE}
+```{r, eval=FALSE}
 ccle_ccls <- unique(ccle$DepMap_ID)
@@
 ```{r wilcoxon_tests, eval=TRUE}
-# crispr_ptmuts <- unfactorize(crispr_ptmuts)
-# # crispr_signif_all_gene <- WilcoxonTestDF(dataframe = crispr_ptmuts, grouping = "Gene", outfile = "./data_munging/rds/crispr_signif_gene.rds")
-# crispr_ptmuts_filt <- filter(crispr_ptmuts, Gene %in% g2p_genes)
-# crispr_signif_gene <- WilcoxonTestDF(dataframe = crispr_ptmuts_filt, grouping = "Gene", outfile = "./data_munging/rds/crispr_signif_g2p_gene.rds")
-# crispr_signif_lineage <- WilcoxonTestDF(dataframe = crispr_ptmuts_filt, grouping = c("Gene", "Primary.Disease"), outfile = "./data_munging/rds/crispr_signif_g2p_lineage.rds")
+crispr <- unfactorize(crispr)
+crispr_signif_all_gene <- WilcoxonTestDF(dataframe = crispr, grouping = "Gene", outfile = "./data_munging/rds/crispr_signif_g.rds")
+crispr_filt <- filter(crispr, Gene %in% g2p_genes)
+crispr_signif_gene <- WilcoxonTestDF(dataframe = crispr_filt, grouping = "Gene", outfile = "./data_munging/rds/crispr_signif_g2p_g.rds")
+crispr_signif_lineage <- WilcoxonTestDF(dataframe = crispr_filt, grouping = c("Gene", "disease"), outfile = "./data_munging/rds/crispr_signif_g2p_gl.rds")
 
@@
 # ccle_signif_g2p_dgl <- WilcoxonTestDF(dataframe = ccle_filt, grouping = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), outfile = "./data_munging/rds/ccle_signif_g2p_dgl.rds")
-
-ctrp_filt <- filter(ctrp, Drug %in% g2p_drugs & Gene %in% g2p_genes)
-ctrp_filt$Gene <- factor(ctrp_filt$Gene, ordered = FALSE)
-ctrp_filt <- unfactorize(ctrp_filt)
-ctrp_signif_dg <- WilcoxonTestDF(dataframe = ctrp, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/ctrp_signif_dg.rds")
-ctrp_signif_g2p_dg <- WilcoxonTestDF(dataframe = ctrp_filt, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/ctrp_signif_g2p_dg.rds")
-ctrp_signif_g2p_dgl <- WilcoxonTestDF(dataframe = ctrp_filt, grouping = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), outfile = "./data_munging/rds/ctrp_signif_g2p_dgl.rds")
-
-gdsc_filt <- filter(gdsc, Drug %in% g2p_drugs & Gene %in% g2p_genes)
-gdsc_filt$Gene <- factor(gdsc_filt$Gene, ordered = FALSE)
-gdsc_filt <- unfactorize(gdsc_filt)
-gdsc_signif_dg <- WilcoxonTestDF(dataframe = gdsc, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/gdsc_signif_dg.rds")
-gdsc_signif_g2p_dg <- WilcoxonTestDF(dataframe = gdsc_filt, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/gdsc_signif_g2p_dg.rds")
-gdsc_signif_g2p_dgl <- WilcoxonTestDF(dataframe = gdsc_filt, grouping = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), outfile = "./data_munging/rds/gdsc_signif_g2p_dgl.rds")
+# 
+# ctrp_filt <- filter(ctrp, Drug %in% g2p_drugs & Gene %in% g2p_genes)
+# ctrp_filt$Gene <- factor(ctrp_filt$Gene, ordered = FALSE)
+# ctrp_filt <- unfactorize(ctrp_filt)
+# ctrp_signif_dg <- WilcoxonTestDF(dataframe = ctrp, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/ctrp_signif_dg.rds")
+# ctrp_signif_g2p_dg <- WilcoxonTestDF(dataframe = ctrp_filt, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/ctrp_signif_g2p_dg.rds")
+# ctrp_signif_g2p_dgl <- WilcoxonTestDF(dataframe = ctrp_filt, grouping = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), outfile = "./data_munging/rds/ctrp_signif_g2p_dgl.rds")
+# 
+# gdsc_filt <- filter(gdsc, Drug %in% g2p_drugs & Gene %in% g2p_genes)
+# gdsc_filt$Gene <- factor(gdsc_filt$Gene, ordered = FALSE)
+# gdsc_filt <- unfactorize(gdsc_filt)
+# gdsc_signif_dg <- WilcoxonTestDF(dataframe = gdsc, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/gdsc_signif_dg.rds")
+# gdsc_signif_g2p_dg <- WilcoxonTestDF(dataframe = gdsc_filt, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/gdsc_signif_g2p_dg.rds")
+# gdsc_signif_g2p_dgl <- WilcoxonTestDF(dataframe = gdsc_filt, grouping = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), outfile = "./data_munging/rds/gdsc_signif_g2p_dgl.rds")
 ```
@@
 # CCLE
-ccle_cor_res <- ccle %>% group_by(Drug, Gene, Drug_Gene) %>% summarize(
-                GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate,
-                GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value,
-                CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate,
-                CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value)
-ccle_cor_res <- merge(g2p_druggene_tally, ccle_cor_res, by = "Drug_Gene", all.y = TRUE)
+ccle_ge_res <- ccle_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(TPM) %>% summarize(
+                GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$estimate,
+                GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$p.value)
+ccle_cn_res <- ccle_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(CN) %>% summarize(
+                CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$estimate,
+                CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$p.value)
+ccle_cor_res <- merge(g2p_druggene_tally, merge(ccle_ge_res, ccle_cn_res, by = c("Drug", "Gene", "Drug_Gene"), all = TRUE), by = "Drug_Gene", all.y = TRUE)
 ccle_cor_res$n <- ifelse(is.na(ccle_cor_res$n), 0, ccle_cor_res$n)
@@
 # CTRP
-ctrp_cor_res <- ctrp %>% group_by(Drug, Gene, Drug_Gene) %>% summarize(
-                GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate,
-                GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value,
-                CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate,
-                CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value)
-ctrp_cor_res <- merge(g2p_druggene_tally, ctrp_cor_res, by = "Drug_Gene", all.y = TRUE)
+ctrp_ge_res <- ctrp_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(TPM) %>% summarize(
+                GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$estimate,
+                GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$p.value)
+ctrp_cn_res <- ctrp_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(CN) %>% summarize(
+                CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$estimate,
+                CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$p.value)
+ctrp_cor_res <- merge(g2p_druggene_tally, merge(ctrp_ge_res, ctrp_cn_res, by = c("Drug", "Gene", "Drug_Gene"), all = TRUE), by = "Drug_Gene", all.y = TRUE)
 ctrp_cor_res$n <- ifelse(is.na(ctrp_cor_res$n), 0, ctrp_cor_res$n)
@@
 # GDSC
-gdsc_cor_res <- gdsc %>% group_by(Drug, Gene, Drug_Gene) %>% summarize(
-                GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate,
-                GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value,
-                CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate,
-                CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value)
-gdsc_cor_res <- merge(g2p_druggene_tally, gdsc_cor_res, by = "Drug_Gene", all.y = TRUE)
+gdsc_ge_res <- gdsc_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(TPM) %>% summarize(
+                GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$estimate,
+                GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$p.value)
+gdsc_cn_res <- gdsc_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(CN) %>% summarize(
+                CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$estimate,
+                CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$p.value)
+gdsc_cor_res <- merge(g2p_druggene_tally, merge(gdsc_ge_res, gdsc_cn_res, by = c("Drug", "Gene", "Drug_Gene"), all = TRUE), by = "Drug_Gene", all.y = TRUE)
 gdsc_cor_res$n <- ifelse(is.na(gdsc_cor_res$n), 0, gdsc_cor_res$n)
@@
 ```{r crispr_spear_calc, warning=FALSE}
-crispr_spear_ge <- transform(crispr_ptmuts_filt %>% group_by(Gene) %>% summarize(p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value, p_log10 = -log10(p), corr = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate, Metric = "Gene Expression"), Gene = reorder(Gene, corr))
-crispr_spear_cn <- transform(crispr_ptmuts_filt %>% group_by(Gene) %>% summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value, p_log10 = -log10(p), corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate, Metric = "Copy Number"), Gene = reorder(Gene, corr))
+crispr_spear_ge <- transform(crispr %>% group_by(Gene) %>% drop_na(TPM) %>% summarize(p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value, p_log10 = -log10(p), corr = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate, Metric = "Gene Expression"), Gene = reorder(Gene, corr))
+crispr_spear_cn <- transform(crispr %>% group_by(Gene) %>% drop_na(CN) %>% summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value, p_log10 = -log10(p), corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate, Metric = "Copy Number"), Gene = reorder(Gene, corr))
+c("white", "deepskyblue4")
+
+ggplot(data = filter(crispr_spear_cn, Gene %in% g2p_genes)) +
+  geom_point(aes(x = Gene, y = corr, fill = p_log10), pch = 21) +
+  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(), legend.position = "bottom") +
+  scale_fill_gradientn(colours = c("white", "green4"),
+                       breaks = c(0, 4, 8, 12, 16, 20),
+                       labels = c(0, 4, 8, 12, 16, 20),
+                       limits = c(0, 21)) +
+  geom_text_repel(data = filter(crispr_spear_cn, Gene %in% g2p_genes & p < 0.05) , mapping = aes(x = Gene, y = corr, label = Gene)) +
+  labs(title = "Copy Number",
+       fill = expression(-log[10](p)),
+       x = "Gene",
+       y = expression("Spearman Correlation Coefficient"~(r[s])))
 ```

### 2019-05-18 19Q2.Rmd

@@
 crispr <- MergeOmicsG2P(database = "CRISPR", maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./data_munging/19Q2/crispr_data_19Q2.rds")
-write.csv.gz(crispr %>% drop_na(Score), "./data_munging/19Q2/crispr_data_19Q2.csv.gz")
+write.csv.gz(crispr %>% drop_na(Score), "./../htscreens_giant_files/crispr_data_19Q2.csv.gz")
+```
+
+```{r read_crispr_data}
+crispr <- readRDS("./data_munging/19Q2/crispr_data_19Q2.rds")
 ```
@@
 
-```{r wilcoxon_tests, eval=TRUE}
+```{r wilcoxon_tests, eval=FALSE}
 crispr <- unfactorize(crispr)
@@
 
-# ccle_filt <- filter(ccle, Drug %in% g2p_drugs & Gene %in% g2p_genes)
-# ccle_filt$Gene <- factor(ccle_filt$Gene, ordered = FALSE)
-# ccle_filt <- unfactorize(ccle_filt)
-# ccle_signif_dg <- WilcoxonTestDF(dataframe = ccle, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/ccle_signif_dg.rds")
-# ccle_signif_g2p_dg <- WilcoxonTestDF(dataframe = ccle_filt, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/ccle_signif_g2p_dg.rds")
-# ccle_signif_g2p_dgl <- WilcoxonTestDF(dataframe = ccle_filt, grouping = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), outfile = "./data_munging/rds/ccle_signif_g2p_dgl.rds")
-# 
-# ctrp_filt <- filter(ctrp, Drug %in% g2p_drugs & Gene %in% g2p_genes)
-# ctrp_filt$Gene <- factor(ctrp_filt$Gene, ordered = FALSE)
-# ctrp_filt <- unfactorize(ctrp_filt)
-# ctrp_signif_dg <- WilcoxonTestDF(dataframe = ctrp, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/ctrp_signif_dg.rds")
-# ctrp_signif_g2p_dg <- WilcoxonTestDF(dataframe = ctrp_filt, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/ctrp_signif_g2p_dg.rds")
-# ctrp_signif_g2p_dgl <- WilcoxonTestDF(dataframe = ctrp_filt, grouping = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), outfile = "./data_munging/rds/ctrp_signif_g2p_dgl.rds")
-# 
-# gdsc_filt <- filter(gdsc, Drug %in% g2p_drugs & Gene %in% g2p_genes)
-# gdsc_filt$Gene <- factor(gdsc_filt$Gene, ordered = FALSE)
-# gdsc_filt <- unfactorize(gdsc_filt)
-# gdsc_signif_dg <- WilcoxonTestDF(dataframe = gdsc, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/gdsc_signif_dg.rds")
-# gdsc_signif_g2p_dg <- WilcoxonTestDF(dataframe = gdsc_filt, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/gdsc_signif_g2p_dg.rds")
-# gdsc_signif_g2p_dgl <- WilcoxonTestDF(dataframe = gdsc_filt, grouping = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), outfile = "./data_munging/rds/gdsc_signif_g2p_dgl.rds")
+ccle_filt <- filter(ccle, Drug %in% g2p_drugs & Gene %in% g2p_genes)
+ccle_filt$Gene <- factor(ccle_filt$Gene, ordered = FALSE)
+ccle_filt <- unfactorize(ccle_filt)
+ccle_signif_dg <- WilcoxonTestDF(dataframe = ccle, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/ccle_signif_dg.rds")
+ccle_signif_g2p_dg <- WilcoxonTestDF(dataframe = ccle_filt, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/ccle_signif_g2p_dg.rds")
+ccle_signif_g2p_dgl <- WilcoxonTestDF(dataframe = ccle_filt, grouping = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), outfile = "./data_munging/rds/ccle_signif_g2p_dgl.rds")
+
+ctrp_filt <- filter(ctrp, Drug %in% g2p_drugs & Gene %in% g2p_genes)
+ctrp_filt$Gene <- factor(ctrp_filt$Gene, ordered = FALSE)
+ctrp_filt <- unfactorize(ctrp_filt)
+ctrp_signif_dg <- WilcoxonTestDF(dataframe = ctrp, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/ctrp_signif_dg.rds")
+ctrp_signif_g2p_dg <- WilcoxonTestDF(dataframe = ctrp_filt, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/ctrp_signif_g2p_dg.rds")
+ctrp_signif_g2p_dgl <- WilcoxonTestDF(dataframe = ctrp_filt, grouping = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), outfile = "./data_munging/rds/ctrp_signif_g2p_dgl.rds")
+
+gdsc_filt <- filter(gdsc, Drug %in% g2p_drugs & Gene %in% g2p_genes)
+gdsc_filt$Gene <- factor(gdsc_filt$Gene, ordered = FALSE)
+gdsc_filt <- unfactorize(gdsc_filt)
+gdsc_signif_dg <- WilcoxonTestDF(dataframe = gdsc, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/gdsc_signif_dg.rds")
+gdsc_signif_g2p_dg <- WilcoxonTestDF(dataframe = gdsc_filt, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/gdsc_signif_g2p_dg.rds")
+gdsc_signif_g2p_dgl <- WilcoxonTestDF(dataframe = gdsc_filt, grouping = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), outfile = "./data_munging/rds/gdsc_signif_g2p_dgl.rds")
 ```

### 2019-05-20 19Q2.Rmd
update Rmds

@@
 g2p_genes <- as.character(unique(g2p$Gene[!is.na(g2p$Gene)]))
+g2p_dg_genes <- unique(sapply(strsplit(g2p_dgl, "_", fixed = TRUE), function(x) x[2]))
 g2p_lins <- as.character(unique(g2p$group_general_lineage_name[!is.na(g2p$group_general_lineage_name)]))
+
+g2p$biomarker_type_curated <- ifelse(is.na(g2p$biomarker_type_curated), "None", as.character(g2p$biomarker_type_curated))
+g2p_split <- split(g2p, g2p$biomarker_type_curated)
+g2p_amp <- g2p_split[[1]]
+g2p_expr <- g2p_split[[2]]
+g2p_fus <- g2p_split[[3]]
+g2p_fus$FusionPair <- sapply(X = g2p_fus$Feature.Names, function(x) strsplit(as.character(x)," ")[[1]][1])
+g2p_fus$FusionPair <- ifelse(g2p_fus$FusionPair == "Fusions", as.character(g2p_fus$Gene), as.character(g2p_fus$FusionPair))
+g2p_mut <- g2p_split[[4]]
+g2p_mut_genes <- unique(sapply(strsplit(as.character(g2p_mut$Drug_Gene)[!is.na(g2p_mut$Drug_Gene)], "_", fixed = TRUE), function(x) x[2]))
+g2p_no_biomarker <- g2p_split[[4]]
+
+g2p_nodrug <- filter(g2p, is.na(Drug))
 ```
@@
 fusions$X.FusionName <- gsub("--", "-", fusions$X.FusionName)
-fusions <- select(fusions, DepMap_ID, X.FusionName)
+fusions <- select(fusions, DepMap_ID, X.FusionName, LeftGene, RightGene)
 fusions <- as.data.frame(lapply(fusions, function(x) gsub("IGH@|IGH-@", "IGH", x)))
-colnames(fusions) <- c("DepMap_ID", "FusionPair")
+colnames(fusions) <- c("DepMap_ID", "FusionPair", "LeftGene", "RightGene")
 fusions <- merge(fusions, ccl_meta, by = "DepMap_ID", all.x = TRUE)
+fusions$G2P_Fusion <- ifelse(fusions$FusionPair %in% as.character(unique(g2p_fus$FusionPair)) | fusions$LeftGene %in% as.character(unique(g2p_fus$FusionPair)) | fusions$RightGene %in% as.character(unique(g2p_fus$FusionPair)), "Yes", "No")
+fusions_filt <- unique(filter(fusions, G2P_Fusion == "Yes"))
 ```
@@
 }
+```
+
+Merge fusions:
+```{r, eval=FALSE}
+ccle_all <- read.delim("./../htscreens_giant_files/pozdeyev_data/CCLE_drug_response_metrics.csv.gz", sep = ",")
+ctrp_all <- read.delim("./../htscreens_giant_files/pozdeyev_data/CTRP_drug_response_metrics.csv.gz", sep = ",")
+gdsc_all <- read.delim("./../htscreens_giant_files/pozdeyev_data/GDSC_drug_response_metrics.csv.gz", sep = ",")
+
+auc <- bind_rows(ccle_all, ctrp_all, gdsc_all)
+
+# Harmonize Pozdeyev cell line names with DepMap
+auc$Drug <- tolower(auc$Drug_name)
+auc$Cell_line <- toupper(gsub("-", "", auc$Cell_line))
+auc$Cell_line <- ifelse(auc$Cell_line == "K052", "KO52", auc$Cell_line)
+auc$Cell_line <- ifelse(auc$Cell_line == "OVCAR3", "NIHOVCAR3", auc$Cell_line)
+auc$Cell_line <- ifelse(auc$Cell_line == "OVCAR3", "NIHOVCAR3", auc$Cell_line)
+auc$Cell_line <- ifelse(auc$Cell_line == "TI73", "T173", auc$Cell_line)
+auc <- merge(ccl_histologies, auc, by = "Cell_line", all.y = TRUE)
+
+ccle_fus <- auc %>% filter(Database == "CCLE") %>% select(Cell_line, CCLE_histology, TCGA_classification, CCLE_name, DepMap_ID, Drug, AUC_IC50)
+ccle_fus_grid <- expand.grid("DepMap_ID" = unique(ccle_fus$DepMap_ID), "FusionPair" = unique(fusions_filt$FusionPair))
+ccle_fus <- merge(merge(ccle_fus, ccle_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "CCLE_name", "CCLE_histology", "Cell_line", "FusionPair"), all = TRUE)
+ccle_fus$G2P_Fusion <- ifelse(is.na(ccle_fus$G2P_Fusion), "No", as.character(ccle_fus$G2P_Fusion))
+
+ctrp_fus <- auc %>% filter(Database == "CTRP") %>% select(Cell_line, CCLE_histology, TCGA_classification, CCLE_name, DepMap_ID, Drug, AUC_IC50)
+ctrp_fus_grid <- expand.grid("DepMap_ID" = unique(ctrp_fus$DepMap_ID), "FusionPair" = unique(fusions_filt$FusionPair))
+ctrp_fus <- merge(merge(ctrp_fus, ctrp_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "CCLE_name", "CCLE_histology", "Cell_line", "FusionPair"), all = TRUE)
+ctrp_fus$G2P_Fusion <- ifelse(is.na(ctrp_fus$G2P_Fusion), "No", as.character(ctrp_fus$G2P_Fusion))
+
+gdsc_fus <- auc %>% filter(Database == "GDSC") %>% select(Cell_line, CCLE_histology, TCGA_classification, CCLE_name, DepMap_ID, Drug, AUC_IC50)
+gdsc_fus_grid <- expand.grid("DepMap_ID" = unique(gdsc_fus$DepMap_ID), "FusionPair" = unique(fusions_filt$FusionPair))
+gdsc_fus <- merge(merge(gdsc_fus, gdsc_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "CCLE_name", "CCLE_histology", "Cell_line", "FusionPair"), all = TRUE)
+gdsc_fus$G2P_Fusion <- ifelse(is.na(gdsc_fus$G2P_Fusion), "No", as.character(gdsc_fus$G2P_Fusion))
+
+fus <- bind_rows(ccle_fus, ctrp_fus, gdsc_fus)
+saveRDS(fus, "./data_munging/rds/fusions_merged.rds")
+```
+
+```{r}
+fus <- readRDS("./data_munging/rds/fusions_merged.rds") %>% drop_na(Drug)
+fus_summary <- fus %>% count(Drug, FusionPair, G2P_Fusion)
 ```
@@
               column_names_side = "bottom",
-              column_names_gp = gpar(fontsize = 10),
               show_column_names = FALSE,
@@
                                    rot = 45,
-                                   gp = gpar(fontsize = 10),
+                                   gp = gpar(fontsize = 8),
                                    offset = unit(1, "npc"),
@@
 
-WilcoxonTestDF <- function(dataframe, grouping, outfile) {
+WilcoxonTestDF <- function(dataframe, grouping, g2p_list, outfile) {
   require(ggpubr)
@@
   if("Drug_Gene" %in% grouping) {
-    signif$InG2P <- ifelse(signif$Drug_Gene %in% g2p_dg, "Yes", "No")
+    signif$InG2P <- ifelse(signif$Drug_Gene %in% g2p_list, "Yes", "No")
   }
   if("Drug_Gene_Lin" %in% grouping) {
-    signif$InG2P <- ifelse(signif$Drug_Gene_Lin %in% g2p_dgl, "Yes", "No")
+    signif$InG2P <- ifelse(signif$Drug_Gene_Lin %in% g2p_list, "Yes", "No")
   }
@@
 
+```{r}
+test <- unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)]))
+test2 <- unique(as.character(g2p_mut$Drug_Gene_Lin[!is.na(g2p_mut$Drug_Gene_Lin)]))
+```
+
 ```{r wilcoxon_tests, eval=FALSE}
 crispr <- unfactorize(crispr)
-crispr_signif_all_gene <- WilcoxonTestDF(dataframe = crispr, grouping = "Gene", outfile = "./data_munging/rds/crispr_signif_g.rds")
+# crispr_signif_all_gene <- WilcoxonTestDF(dataframe = crispr, grouping = "Gene", outfile = "./data_munging/rds/crispr_signif_g.rds")
 crispr_filt <- filter(crispr, Gene %in% g2p_genes)
@@
 
-ccle_filt <- filter(ccle, Drug %in% g2p_drugs & Gene %in% g2p_genes)
+ccle_filt <- filter(ccle, Drug %in% g2p_drugs & Gene %in% g2p_dg_genes)
 ccle_filt$Gene <- factor(ccle_filt$Gene, ordered = FALSE)
 ccle_filt <- unfactorize(ccle_filt)
-ccle_signif_dg <- WilcoxonTestDF(dataframe = ccle, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/ccle_signif_dg.rds")
-ccle_signif_g2p_dg <- WilcoxonTestDF(dataframe = ccle_filt, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/ccle_signif_g2p_dg.rds")
-ccle_signif_g2p_dgl <- WilcoxonTestDF(dataframe = ccle_filt, grouping = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), outfile = "./data_munging/rds/ccle_signif_g2p_dgl.rds")
+ccle_signif_dg <- WilcoxonTestDF(dataframe = ccle, grouping = c("Drug", "Gene", "Drug_Gene"), g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), outfile = "./data_munging/rds/ccle_signif_dg.rds")
+ccle_signif_g2p_dg <- WilcoxonTestDF(dataframe = ccle_filt, grouping = c("Drug", "Gene", "Drug_Gene"), g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), outfile = "./data_munging/rds/ccle_signif_g2p_dg.rds")
+ccle_signif_g2p_dgl <- WilcoxonTestDF(dataframe = ccle_filt, grouping = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), g2p_list = unique(as.character(g2p_mut$Drug_Gene_Lin[!is.na(g2p_mut$Drug_Gene_Lin)])), outfile = "./data_munging/rds/ccle_signif_g2p_dgl.rds")
 
-ctrp_filt <- filter(ctrp, Drug %in% g2p_drugs & Gene %in% g2p_genes)
+ctrp_filt <- filter(ctrp, Drug %in% g2p_drugs & Gene %in% g2p_dg_genes)
 ctrp_filt$Gene <- factor(ctrp_filt$Gene, ordered = FALSE)
 ctrp_filt <- unfactorize(ctrp_filt)
-ctrp_signif_dg <- WilcoxonTestDF(dataframe = ctrp, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/ctrp_signif_dg.rds")
-ctrp_signif_g2p_dg <- WilcoxonTestDF(dataframe = ctrp_filt, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/ctrp_signif_g2p_dg.rds")
-ctrp_signif_g2p_dgl <- WilcoxonTestDF(dataframe = ctrp_filt, grouping = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), outfile = "./data_munging/rds/ctrp_signif_g2p_dgl.rds")
+# ctrp_signif_dg <- WilcoxonTestDF(dataframe = ctrp, grouping = c("Drug", "Gene", "Drug_Gene"), g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), outfile = "./data_munging/rds/ctrp_signif_dg.rds")
+ctrp_signif_g2p_dg <- WilcoxonTestDF(dataframe = ctrp_filt, grouping = c("Drug", "Gene", "Drug_Gene"), g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), outfile = "./data_munging/rds/ctrp_signif_g2p_dg.rds")
+ctrp_signif_g2p_dgl <- WilcoxonTestDF(dataframe = ctrp_filt, grouping = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), g2p_list = unique(as.character(g2p_mut$Drug_Gene_Lin[!is.na(g2p_mut$Drug_Gene_Lin)])), outfile = "./data_munging/rds/ctrp_signif_g2p_dgl.rds")
 
-gdsc_filt <- filter(gdsc, Drug %in% g2p_drugs & Gene %in% g2p_genes)
+gdsc_filt <- filter(gdsc, Drug %in% g2p_drugs & Gene %in% g2p_dg_genes)
 gdsc_filt$Gene <- factor(gdsc_filt$Gene, ordered = FALSE)
 gdsc_filt <- unfactorize(gdsc_filt)
-gdsc_signif_dg <- WilcoxonTestDF(dataframe = gdsc, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/gdsc_signif_dg.rds")
-gdsc_signif_g2p_dg <- WilcoxonTestDF(dataframe = gdsc_filt, grouping = c("Drug", "Gene", "Drug_Gene"), outfile = "./data_munging/rds/gdsc_signif_g2p_dg.rds")
-gdsc_signif_g2p_dgl <- WilcoxonTestDF(dataframe = gdsc_filt, grouping = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), outfile = "./data_munging/rds/gdsc_signif_g2p_dgl.rds")
+# gdsc_signif_dg <- WilcoxonTestDF(dataframe = gdsc, grouping = c("Drug", "Gene", "Drug_Gene"), g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), outfile = "./data_munging/rds/gdsc_signif_dg.rds")
+gdsc_signif_g2p_dg <- WilcoxonTestDF(dataframe = gdsc_filt, grouping = c("Drug", "Gene", "Drug_Gene"), g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), outfile = "./data_munging/rds/gdsc_signif_g2p_dg.rds")
+gdsc_signif_g2p_dgl <- WilcoxonTestDF(dataframe = gdsc_filt, grouping = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), g2p_list = unique(as.character(g2p_mut$Drug_Gene_Lin[!is.na(g2p_mut$Drug_Gene_Lin)])), outfile = "./data_munging/rds/gdsc_signif_g2p_dgl.rds")
 ```
@@
 ```{r load_wilcoxon_rds}
-# crispr_signif_gene <- readRDS("./data_munging/rds/crispr_signif_g2p_gene.rds")
-# crispr_signif_lineage <- readRDS("./data_munging/rds/crispr_signif_g2p_lineage.rds")
+crispr_signif_g <- readRDS("./data_munging/rds/crispr_signif_g.rds")
+crispr_signif_g2p_g <- readRDS("./data_munging/rds/crispr_signif_g2p_g.rds")
+crispr_signif_lin <- readRDS("./data_munging/rds/crispr_signif_g2p_gl.rds")
 
-# ccle_signif_gene <- readRDS("./data_munging/rds/ccle_signif_g2p_gene.rds")
-# ccle_signif_g2p_druggene <- readRDS("./data_munging/rds/ccle_signif_g2p_druggene.rds")
-# ccle_signif_lineage <- readRDS("./data_munging/rds/ccle_signif_g2p_lineage.rds")
-# 
-# ctrp_signif_gene <- readRDS("./data_munging/rds/ctrp_signif_g2p_gene.rds")
-# ctrp_signif_g2p_druggene <- readRDS("./data_munging/rds/ctrp_signif_g2p_druggene.rds")
-# ctrp_signif_lineage <- readRDS("./data_munging/rds/ctrp_signif_g2p_lineage.rds")
-# 
-# gdsc_signif_gene <- readRDS("./data_munging/rds/gdsc_signif_g2p_gene.rds")
-# gdsc_signif_g2p_druggene <- readRDS("./data_munging/rds/gdsc_signif_g2p_druggene.rds")
-# gdsc_signif_lineage <- readRDS("./data_munging/rds/gdsc_signif_g2p_lineage.rds")
+ccle_signif_dg <- readRDS("./data_munging/rds/ccle_signif_dg.rds")
+ccle_signif_g2p_dg <- readRDS("./data_munging/rds/ccle_signif_g2p_dg.rds")
+ccle_signif_dgl <- readRDS("./data_munging/rds/ccle_signif_g2p_dgl.rds")
+
+# ctrp_signif_g <- readRDS("./data_munging/rds/ctrp_signif_dg.rds")
+ctrp_signif_g2p_dg <- readRDS("./data_munging/rds/ctrp_signif_g2p_dg.rds")
+ctrp_signif_dgl <- readRDS("./data_munging/rds/ctrp_signif_g2p_dgl.rds")
+
+# gdsc_signif_g <- readRDS("./data_munging/rds/gdsc_signif_dg.rds")
+gdsc_signif_g2p_dg <- readRDS("./data_munging/rds/gdsc_signif_g2p_dg.rds")
+gdsc_signif_dgl <- readRDS("./data_munging/rds/gdsc_signif_g2p_dgl.rds")
 ```
+
+## Plots
+
+```{r fig.height=4, fig.width=8}
+crispr_filt <- filter(crispr, Gene %in% g2p_mut_genes)
+crispr_filt$Gene <- factor(crispr_filt$Gene, levels = g2p_mut_genes)
+crispr_filt$Mutation <- as.character(crispr_filt$Mutation)
+crispr_signif_filt <- filter(crispr_signif_g2p_g, Gene %in% g2p_mut_genes)
+crispr_signif_filt$Gene <- factor(crispr_signif_filt$Gene, levels = g2p_mut_genes)
+
+crispr_gene_mut_plot <- ggplot(data = crispr_filt) +
+  facet_wrap(~ Gene, nrow = 2, drop = FALSE) +
+  scale_color_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "darkorchid", "0" = "thistle")) +
+  scale_x_discrete(name = "Mutation Status", labels = c("0" = "WT", "1" = "Mut")) +
+  geom_jitter(aes(x = Mutation, y = Score, color = Mutation), width = 0.2, alpha = 0.5, size = 0.6) +
+  geom_boxplot(aes(x = Mutation, y = Score), fill = "transparent", outlier.shape = NA, lwd = 0.3) +
+  geom_text(data = crispr_signif_filt, aes(x = 1.5, y = 2, label = p.signif)) +
+  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
+  theme(legend.position = "top", legend.direction = "horizontal") +
+  guides(color = guide_legend(override.aes = list(size = 3))) +
+  labs(y = "CERES Score")
+crispr_gene_mut_plot
+
+# ggsave("./plots/manuscript/crispr_gene_mut_plot.png", crispr_gene_mut_plot, width = 12, height = 6, units = "in")
+```
+
+```{r}
+MakeMutHeatmap <- function(signif_g2p_dg, row_names, col_title, color, legend_title) {
+  signif_grid <- dcast(signif_g2p_dg, Gene ~ Drug, value.var = "p", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
+  signif_grid <- signif_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
+  signif_grid <- signif_grid[complete.cases(signif_grid), ]
+  signif_grid[signif_grid > 0.05] <- NA
+
+  signif_grid_annot <- dcast(signif_g2p_dg, Gene ~ Drug, value.var = "InG2P", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
+  signif_grid_annot <- signif_grid_annot[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
+  signif_grid_annot <- signif_grid_annot[complete.cases(signif_grid_annot), ]
+  signif_grid_annot[signif_grid_annot == "No"] <- ""
+  signif_grid_annot[signif_grid_annot == "Yes"] <- "O"
+
+  col_fun <- colorRamp2(c(0, 0.05), c(color, "gray97"))
+  # Legend properties list
+  ht_legend_list <- list(title = legend_title, title_position = "topleft", legend_direction = "horizontal", legend_width = unit(2, "in"), border = "gray70",   at = seq(0, 0.05, by = 0.01), labels = seq(0, 0.05, by = 0.01))
+  ht <- Heatmap(signif_grid,
+                col = col_fun,
+                na_col = "gray97",
+                rect_gp = gpar(col = "gray70"),
+                heatmap_legend_param = ht_legend_list,
+                cluster_rows = FALSE, 
+                cluster_columns = FALSE, 
+                show_row_names = as.logical(row_names),
+                row_names_side = "left",
+                row_names_gp = gpar(fontsize = 10),
+                column_names_side = "bottom",
+                column_names_gp = gpar(fontsize = 10),
+                show_column_names = FALSE,
+                bottom_annotation = HeatmapAnnotation(
+                  text = anno_text(colnames(signif_grid),
+                                   rot = 45,
+                                   gp = gpar(fontsize = 11),
+                                   offset = unit(1, "npc"),
+                                   just = "right"),
+                  annotation_height = unit(0.85, "in")),
+                  # annotation_height = max_text_width(colnames(signif_grid))),
+                row_title = "Genes",
+                row_title_gp = gpar(fontface = "bold", fontsize = 14),
+                column_title = col_title, 
+                column_title_gp = gpar(fontface = "bold", fontsize = 14),
+                column_title_side = "bottom",
+                cell_fun = function(j, i, x, y, width, height, fill) {
+                  grid.text(signif_grid_annot[i, j], x, y, gp = gpar(fontsize = 20))
+                  # if(signif_grid_annot[i, j] == "G") {
+                  #   grid.circle(x = x, y = y, r = 0.02, gp = gpar(fill = "transparent", col = "black"))
+                  # }
+                }
+                )
+  return(ht)
+}
+```
+
+```{r mut_heatmaps, eval=FALSE}
+ht_ccle <- MakeMutHeatmap(signif_g2p_dg = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), legend_title = "P-value", row_names = TRUE, color = "darkgreen", col_title = "Drugs")
+png(filename = "./plots/manuscript/ccle_mut_heatmap.png", width = 3, height = 10, units = "in", res = 500)
+draw(ht_ccle, heatmap_legend_side = "top")
+dev.off()
+
+ht_ctrp <- MakeMutHeatmap(signif_g2p_dg = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), legend_title = "P-value", row_names = TRUE, color = "steelblue4", col_title = "Drugs")
+png(filename = "./plots/manuscript/ctrp_mut_heatmap.png", width = 9.5, height = 10, units = "in", res = 500)
+draw(ht_ctrp, heatmap_legend_side = "top")
+dev.off()
+
+ht_gdsc <- MakeMutHeatmap(signif_g2p_dg = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), legend_title = "P-value", row_names = TRUE, color = "turquoise4", col_title = "Drugs")
+png(filename = "./plots/manuscript/gdsc_mut_heatmap.png", width = 5, height = 10, units = "in", res = 500)
+draw(ht_gdsc, heatmap_legend_side = "top")
+dev.off()
+
+ht_ccle2 <- MakeMutHeatmap(signif_g2p_dg = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), legend_title = "CCLE p-value                                                                               ", row_names = TRUE, color = "darkgreen", col_title = "")
+ht_ctrp2 <- MakeMutHeatmap(signif_g2p_dg = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), legend_title = "CTRP p-value                                                                              ", row_names = FALSE, color = "steelblue4", col_title = "Drugs")
+ht_gdsc2 <- MakeMutHeatmap(signif_g2p_dg = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), legend_title = "GDSC p-value", row_names = FALSE, color = "turquoise4", col_title = "")
+png(filename = "./plots/manuscript/drug_mut_heatmap.png", width = 13, height = 10, units = "in", res = 500)
+draw(ht_ccle2 + ht_ctrp2 + ht_gdsc2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
+dev.off()
+```
+
+# WILCOXON (Fusions)
+
+--------------------------------------------------------------------------------
 
@@
 ```{r drug_spear_calc, warning=FALSE, eval=FALSE}
-g2p_druggene_tally <- g2p %>% group_by(Drug_Gene) %>% tally() %>% drop_na()
-
 # CCLE
-ccle_ge_res <- ccle_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(TPM) %>% summarize(
-                GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$estimate,
-                GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$p.value)
-ccle_cn_res <- ccle_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(CN) %>% summarize(
-                CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$estimate,
-                CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$p.value)
-ccle_cor_res <- merge(g2p_druggene_tally, merge(ccle_ge_res, ccle_cn_res, by = c("Drug", "Gene", "Drug_Gene"), all = TRUE), by = "Drug_Gene", all.y = TRUE)
-ccle_cor_res$n <- ifelse(is.na(ccle_cor_res$n), 0, ccle_cor_res$n)
-ccle_cor_res$InG2P <- ifelse(ccle_cor_res$n != 0, "Yes", "No")
-ccle_cor_res$Dataset <- "CCLE"
+ccle_filt <- filter(ccle, Drug %in% g2p_drugs & Gene %in% g2p_genes)
+ccle_filt$Gene <- factor(ccle_filt$Gene, ordered = FALSE)
+ccle_filt <- unfactorize(ccle_filt)
+ccle_ge_res <- ccle_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(TPM) %>% summarize(GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$estimate, GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$p.value)
+ccle_ge_res$InG2P <- ifelse(ccle_ge_res$Drug_Gene %in% unique(as.character(g2p_expr$Drug_Gene[!is.na(g2p_expr$Drug_Gene)])), "Yes", "No")
+ccle_ge_res$Dataset <- "CCLE"
+ccle_cn_res <- ccle_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(CN) %>% summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$estimate, CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$p.value)
+ccle_cn_res$InG2P <- ifelse(ccle_cn_res$Drug_Gene %in% unique(as.character(g2p_amp$Drug_Gene[!is.na(g2p_amp$Drug_Gene)])), "Yes", "No")
+ccle_cn_res$Dataset <- "CCLE"
 
 # CTRP
-ctrp_ge_res <- ctrp_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(TPM) %>% summarize(
-                GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$estimate,
-                GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$p.value)
-ctrp_cn_res <- ctrp_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(CN) %>% summarize(
-                CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$estimate,
-                CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$p.value)
-ctrp_cor_res <- merge(g2p_druggene_tally, merge(ctrp_ge_res, ctrp_cn_res, by = c("Drug", "Gene", "Drug_Gene"), all = TRUE), by = "Drug_Gene", all.y = TRUE)
-ctrp_cor_res$n <- ifelse(is.na(ctrp_cor_res$n), 0, ctrp_cor_res$n)
-ctrp_cor_res$InG2P <- ifelse(ctrp_cor_res$n != 0, "Yes", "No")
-ctrp_cor_res$Dataset <- "CTRP"
+ctrp_filt <- filter(ctrp, Drug %in% g2p_drugs & Gene %in% g2p_genes)
+ctrp_filt$Gene <- factor(ctrp_filt$Gene, ordered = FALSE)
+ctrp_filt <- unfactorize(ctrp_filt)
+ctrp_ge_res <- ctrp_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(TPM) %>% summarize(GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$estimate, GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$p.value)
+ctrp_ge_res$InG2P <- ifelse(ctrp_ge_res$Drug_Gene %in% unique(as.character(g2p_expr$Drug_Gene[!is.na(g2p_expr$Drug_Gene)])), "Yes", "No")
+ctrp_ge_res$Dataset <- "CTRP"
+ctrp_cn_res <- ctrp_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(CN) %>% summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$estimate, CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$p.value)
+ctrp_cn_res$InG2P <- ifelse(ctrp_cn_res$Drug_Gene %in% unique(as.character(g2p_amp$Drug_Gene[!is.na(g2p_amp$Drug_Gene)])), "Yes", "No")
+ctrp_cn_res$Dataset <- "CTRP"
 
 # GDSC
-gdsc_ge_res <- gdsc_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(TPM) %>% summarize(
-                GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$estimate,
-                GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$p.value)
-gdsc_cn_res <- gdsc_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(CN) %>% summarize(
-                CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$estimate,
-                CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$p.value)
-gdsc_cor_res <- merge(g2p_druggene_tally, merge(gdsc_ge_res, gdsc_cn_res, by = c("Drug", "Gene", "Drug_Gene"), all = TRUE), by = "Drug_Gene", all.y = TRUE)
-gdsc_cor_res$n <- ifelse(is.na(gdsc_cor_res$n), 0, gdsc_cor_res$n)
-gdsc_cor_res$InG2P <- ifelse(gdsc_cor_res$n != 0, "Yes", "No")
-gdsc_cor_res$Dataset <- "GDSC"
+gdsc_filt <- filter(gdsc, Drug %in% g2p_drugs & Gene %in% g2p_genes)
+gdsc_filt$Gene <- factor(gdsc_filt$Gene, ordered = FALSE)
+gdsc_filt <- unfactorize(gdsc_filt)
+gdsc_ge_res <- gdsc_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(TPM) %>% summarize(GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$estimate, GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$p.value)
+gdsc_ge_res$InG2P <- ifelse(gdsc_ge_res$Drug_Gene %in% unique(as.character(g2p_expr$Drug_Gene[!is.na(g2p_expr$Drug_Gene)])), "Yes", "No")
+gdsc_ge_res$Dataset <- "GDSC"
+gdsc_cn_res <- gdsc_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(CN) %>% summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$estimate, CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$p.value)
+gdsc_cn_res$InG2P <- ifelse(gdsc_cn_res$Drug_Gene %in% unique(as.character(g2p_amp$Drug_Gene[!is.na(g2p_amp$Drug_Gene)])), "Yes", "No")
+gdsc_cn_res$Dataset <- "GDSC"
 
 # All
-g2p_cor <- rbind(ccle_cor_res, ctrp_cor_res, gdsc_cor_res)
-
-saveRDS(g2p_cor, "./data_munging/rds/drug_cor.rds")
+cn_cor <- rbind(ccle_cn_res, ctrp_cn_res, gdsc_cn_res)
+saveRDS(cn_cor, "./data_munging/rds/drug_cn_cor.rds")
+ge_cor <- rbind(ccle_ge_res, ctrp_ge_res, gdsc_ge_res)
+saveRDS(ge_cor, "./data_munging/rds/drug_ge_cor.rds")
 ```
@@
 ```{r load_drug_spear}
-g2p_cor <- readRDS("./data_munging/rds/drug_cor.rds")
+cn_cor <- readRDS("./data_munging/rds/drug_cn_cor.rds")
+ge_cor <- readRDS("./data_munging/rds/drug_ge_cor.rds")
 ```
+
+## Plots
 
@@
 
-ggplot(data = filter(crispr_spear_cn, Gene %in% g2p_genes)) +
-  geom_point(aes(x = Gene, y = corr, fill = p_log10), pch = 21) +
-  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(), legend.position = "bottom") +
+crispr_spear_cn_plot <- ggplot(data = filter(crispr_spear_cn, Gene %in% g2p_dg_genes)) +
+  geom_point(aes(x = Gene, y = corr, fill = p_log10), pch = 21, size = 5) +
+  theme(legend.position = "bottom") +
   scale_fill_gradientn(colours = c("white", "green4"),
@@
                        limits = c(0, 21)) +
-  geom_text_repel(data = filter(crispr_spear_cn, Gene %in% g2p_genes & p < 0.05) , mapping = aes(x = Gene, y = corr, label = Gene)) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 10)) +
   labs(title = "Copy Number",
@@
        y = expression("Spearman Correlation Coefficient"~(r[s])))
+
+crispr_spear_ge_plot <- ggplot(data = filter(crispr_spear_ge, Gene %in% g2p_dg_genes)) +
+  geom_point(aes(x = Gene, y = corr, fill = p_log10), pch = 21, size = 5) +
+  theme(legend.position = "bottom") +
+  scale_fill_gradientn(colours = c("white", "deepskyblue4"),
+                       breaks = c(0, 4, 8, 12, 16, 20),
+                       labels = c(0, 4, 8, 12, 16, 20),
+                       limits = c(0, 21)) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 10)) +
+  labs(title = "Gene Expression",
+       fill = expression(-log[10](p)),
+       x = "Gene",
+       y = expression("Spearman Correlation Coefficient"~(r[s])))
+
+crispr_spearman_corr_plot <- plot_grid(crispr_spear_cn_plot, crispr_spear_ge_plot, align = "h")
+crispr_spearman_corr_plot
+
+# ggsave("./plots/manuscript/crispr_spearman_corr_plot.png", crispr_spearman_corr_plot, device = "png", dpi = 450, width = 20, height = 10, units = "in")
+```
+
+```{r corr_heatmap_function}
+MakeCorrHeatmap <- function(drug_cor_res, row_names, col_title, color_range, legend_title, metric, radius) {
+  if(toupper(metric) == "CN" | toupper(metric) == "COPY NUMBER") {
+    signif_grid <- dcast(drug_cor_res, Gene ~ Drug, value.var = "CN_p", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
+    signif_grid <- signif_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
+    signif_grid <- signif_grid[complete.cases(signif_grid), ]
+    signif_grid[signif_grid >= 0.05] <- ""
+    signif_grid[signif_grid != ""] <- "*"
+
+    corr_grid <- dcast(drug_cor_res, Gene ~ Drug, value.var = "CN_r", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
+    corr_grid <- corr_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(corr_grid))]
+    corr_grid <- corr_grid[complete.cases(corr_grid), ]
+  }
+
+  if(toupper(metric) == "GE" | toupper(metric) == "GENE EXPRESSION") {
+    signif_grid <- dcast(drug_cor_res, Gene ~ Drug, value.var = "GE_p", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
+    signif_grid <- signif_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
+    signif_grid <- signif_grid[complete.cases(signif_grid), ]
+    signif_grid[signif_grid >= 0.05] <- ""
+    signif_grid[signif_grid != ""] <- "*"
+
+    corr_grid <- dcast(drug_cor_res, Gene ~ Drug, value.var = "GE_r", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
+    corr_grid <- corr_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(corr_grid))]
+    corr_grid <- corr_grid[complete.cases(corr_grid), ]
+  }
+
+  annot_grid <- dcast(drug_cor_res, Gene ~ Drug, value.var = "InG2P", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
+  annot_grid <- annot_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
+  annot_grid <- annot_grid[complete.cases(annot_grid), ]
+  annot_grid[annot_grid == "No"] <- ""
+  annot_grid[annot_grid == "Yes"] <- "G"
+
+  col_fun <- colorRamp2(color_range, c("red3", "white", "green4"))
+
+  # Legend properties list
+  ht_legend_list <- list(title_position = "topleft", legend_direction = "horizontal", legend_width = unit(3, "in"), border = "gray70", at = seq(color_range[1], color_range[3], by = 0.1), labels = seq(color_range[1], color_range[3], by = 0.1))
+  ht <- Heatmap(corr_grid,
+                col = col_fun,
+                name = legend_title,
+                na_col = "gray97",
+                rect_gp = gpar(col = "gray70"),
+                heatmap_legend_param = ht_legend_list,
+                cluster_rows = FALSE, 
+                cluster_columns = FALSE, 
+                show_row_names = as.logical(row_names),
+                row_names_side = "left",
+                row_names_gp = gpar(fontsize = 10),
+                column_names_side = "bottom",
+                column_names_gp = gpar(fontsize = 10),
+                show_column_names = FALSE,
+                bottom_annotation = HeatmapAnnotation(
+                  text = anno_text(colnames(signif_grid),
+                                   rot = 45,
+                                   gp = gpar(fontsize = 11),
+                                   offset = unit(1, "npc"),
+                                   just = "right"),
+                  annotation_height = unit(0.85, "in")),
+                row_title = "Genes",
+                row_title_gp = gpar(fontface = "bold", fontsize = 14),
+                column_title = col_title, 
+                column_title_gp = gpar(fontface = "bold", fontsize = 14),
+                column_title_side = "top",
+                cell_fun = function(j, i, x, y, width, height, fill) {
+                  grid.text(signif_grid[i, j], x, y, gp = gpar(fontsize = 20))
+                  if(annot_grid[i, j] == "G") {
+                    grid.circle(x = x, y = y, r = radius, gp = gpar(fill = "transparent", col = "black"))
+                  }
+                }
+                )
+  return(ht)
+}
+```
+
+```{r drug_spear_plots, eval=FALSE}
+# Copy number
+ccle_cn_cor <- unfactorize(filter(cn_cor, Dataset == "CCLE" & Gene %in% unique(g2p_amp$Gene)))
+ccle_cn_ht <- MakeCorrHeatmap(drug_cor_res = ccle_cn_cor, row_names = TRUE, col_title = "CCLE", color_range = c(-0.2, 0, 0.2), radius = 0.1, legend_title = "CCLE Spearman correlation", metric = "CN")
+png(filename = "./plots/manuscript/ccle_cn_heatmap.png", width = 3, height = 3, units = "in", res = 500)
+draw(ccle_cn_ht, heatmap_legend_side = "top")
+dev.off()
+
+ctrp_cn_cor <- unfactorize(filter(cn_cor, Dataset == "CTRP" & Gene %in% unique(g2p_amp$Gene)))
+ctrp_cn_ht <- MakeCorrHeatmap(drug_cor_res = ctrp_cn_cor, row_names = TRUE, col_title = "CTRP", color_range = c(-0.2, 0, 0.2), radius = 0.1, legend_title = "CTRP Spearman correlation", metric = "CN")
+png(filename = "./plots/manuscript/ctrp_cn_heatmap.png", width = 8, height = 3, units = "in", res = 500)
+draw(ctrp_cn_ht, heatmap_legend_side = "top")
+dev.off()
+
+gdsc_cn_cor <- unfactorize(filter(cn_cor, Dataset == "GDSC" & Gene %in% unique(g2p_amp$Gene)))
+gdsc_cn_ht <- MakeCorrHeatmap(drug_cor_res = gdsc_cn_cor, row_names = TRUE, col_title = "GDSC", color_range = c(-0.2, 0, 0.2), radius = 0.1, legend_title = "GDSC Spearman correlation", metric = "CN")
+png(filename = "./plots/manuscript/gdsc_cn_heatmap.png", width = 5, height = 3, units = "in", res = 500)
+draw(gdsc_cn_ht, heatmap_legend_side = "top")
+dev.off()
+
+ccle_cn_ht2 <- MakeCorrHeatmap(drug_cor_res = ccle_cn_cor, row_names = TRUE, col_title = "CCLE", color_range = c(-0.2, 0, 0.2), radius = 0.1, legend_title = "Copy num.
+Spearman correlation", metric = "CN")
+ctrp_cn_ht2 <- MakeCorrHeatmap(drug_cor_res = ctrp_cn_cor, row_names = FALSE, col_title = "CTRP", color_range = c(-0.2, 0, 0.2), radius = 0.1, legend_title = "Copy num.
+Spearman correlation", metric = "CN")
+gdsc_cn_ht2 <- MakeCorrHeatmap(drug_cor_res = gdsc_cn_cor, row_names = FALSE, col_title = "GDSC", color_range = c(-0.2, 0, 0.2), radius = 0.1, legend_title = "Copy num.
+Spearman correlation", metric = "CN")
+png(filename = "./plots/manuscript/drug_cn_heatmap.png", width = 13, height = 3, units = "in", res = 500)
+draw(ccle_cn_ht2 + ctrp_cn_ht2 + gdsc_cn_ht2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
+dev.off()
+
+# Gene expression
+ccle_ge_cor <- unfactorize(filter(ge_cor, Dataset == "CCLE" & Gene %in% unique(g2p_expr$Gene)))
+ccle_ge_ht <- MakeCorrHeatmap(drug_cor_res = ccle_ge_cor, row_names = TRUE, col_title = "CCLE", color_range = c(-0.5, 0, 0.5), radius = 0.2, legend_title = "CCLE Spearman correlation", metric = "GE")
+png(filename = "./plots/manuscript/ccle_ge_heatmap.png", width = 3, height = 2.5, units = "in", res = 500)
+draw(ccle_ge_ht, heatmap_legend_side = "top")
+dev.off()
+
+ctrp_ge_cor <- unfactorize(filter(ge_cor, Dataset == "CTRP" & Gene %in% unique(g2p_expr$Gene)))
+ctrp_ge_ht <- MakeCorrHeatmap(drug_cor_res = ctrp_ge_cor, row_names = TRUE, col_title = "CTRP", color_range = c(-0.5, 0, 0.5), radius = 0.2, legend_title = "CTRP Spearman correlation", metric = "GE")
+png(filename = "./plots/manuscript/ctrp_ge_heatmap.png", width = 8, height = 2.5, units = "in", res = 500)
+draw(ctrp_ge_ht, heatmap_legend_side = "top")
+dev.off()
+
+gdsc_ge_cor <- unfactorize(filter(ge_cor, Dataset == "GDSC" & Gene %in% unique(g2p_expr$Gene)))
+gdsc_ge_ht <- MakeCorrHeatmap(drug_cor_res = gdsc_ge_cor, row_names = TRUE, col_title = "GDSC", color_range = c(-0.5, 0, 0.5), radius = 0.2, legend_title = "GDSC Spearman correlation", metric = "GE")
+png(filename = "./plots/manuscript/gdsc_ge_heatmap.png", width = 5, height = 2.5, units = "in", res = 500)
+draw(gdsc_ge_ht, heatmap_legend_side = "top")
+dev.off()
+
+ccle_ge_ht2 <- MakeCorrHeatmap(drug_cor_res = ccle_ge_cor, row_names = TRUE, col_title = "CCLE", color_range = c(-0.5, 0, 0.5), radius = 0.2, legend_title = "Gene expr.
+Spearman correlation", metric = "GE")
+ctrp_ge_ht2 <- MakeCorrHeatmap(drug_cor_res = ctrp_ge_cor, row_names = FALSE, col_title = "CTRP", color_range = c(-0.5, 0, 0.5), radius = 0.2, legend_title = "Gene expr.
+Spearman correlation", metric = "GE")
+gdsc_ge_ht2 <- MakeCorrHeatmap(drug_cor_res = gdsc_ge_cor, row_names = FALSE, col_title = "GDSC", color_range = c(-0.5, 0, 0.5), radius = 0.2, legend_title = "Gene expr.
+Spearman correlation", metric = "GE")
+png(filename = "./plots/manuscript/drug_ge_heatmap.png", width = 13, height = 2.5, units = "in", res = 500)
+draw(ccle_ge_ht2 + ctrp_ge_ht2 + gdsc_ge_ht2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
+dev.off()
 ```

### 2019-05-20 19Q1.Rmd

@@
 g2p <- read.delim("./data_munging/g2p_db_edited.csv", sep = ",", header = TRUE)
+g2p$biomarker_type_curated <- ifelse(is.na(g2p$biomarker_type_curated), "None", g2p$biomarker_type_curated)
 
@@
 g2p_lins <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[3]))
+
+g2p_split <- split(g2p, g2p$biomarker_type_curated)
+g2p_amp <- g2p_split[[1]]
 ```

### 2019-05-30 19Q2.Rmd
update Rmd

@@
 
+# Edit direction column
+g2p <- add_column(g2p, Direction_Curated = NA, .after = "Direction")
+g2p$Direction_Curated <-
+  ifelse(!is.na(str_match(string = tolower(g2p$Direction), pattern = "sensitive|sensitivity||responsive")), "sensitivity",
+         ifelse(!is.na(str_match(string = tolower(g2p$Direction), pattern = "resist")), "resistance", NA))
+
 # Add association columns
@@
 g2p$biomarker_type_curated <- ifelse(is.na(g2p$biomarker_type_curated), "None", as.character(g2p$biomarker_type_curated))
-g2p_split <- split(g2p, g2p$biomarker_type_curated)
+g2p_split <- split(filter(g2p, !is.na(Drug)), g2p$biomarker_type_curated)
 g2p_amp <- g2p_split[[1]]
@@
 g2p_fus$FusionPair <- ifelse(g2p_fus$FusionPair == "Fusions", as.character(g2p_fus$Gene), as.character(g2p_fus$FusionPair))
+g2p_fus$Drug_FusionPair <- ifelse(is.na(g2p_fus$Drug) | is.na(g2p_fus$FusionPair), NA, paste0(g2p_fus$Drug, "_", g2p_fus$FusionPair))
 g2p_mut <- g2p_split[[4]]
 g2p_mut_genes <- unique(sapply(strsplit(as.character(g2p_mut$Drug_Gene)[!is.na(g2p_mut$Drug_Gene)], "_", fixed = TRUE), function(x) x[2]))
-g2p_no_biomarker <- g2p_split[[4]]
+g2p_no_biomarker <- g2p_split[[5]]
 
@@
 fusions <- merge(fusions, ccl_meta, by = "DepMap_ID", all.x = TRUE)
-fusions$G2P_Fusion <- ifelse(fusions$FusionPair %in% as.character(unique(g2p_fus$FusionPair)) | fusions$LeftGene %in% as.character(unique(g2p_fus$FusionPair)) | fusions$RightGene %in% as.character(unique(g2p_fus$FusionPair)), "Yes", "No")
-fusions_filt <- unique(filter(fusions, G2P_Fusion == "Yes"))
 ```
@@
 
-auc <- bind_rows(ccle_all, ctrp_all, gdsc_all)
+auc <- bind_rows(ccle_all, ctrp_all, gdsc_all) %>% drop_na(Drug_name)
 
@@
 
+fusions_filt <- filter(fusions, FusionPair %in% unique(as.character(g2p_fus$FusionPair)))
+
 ccle_fus <- auc %>% filter(Database == "CCLE") %>% select(Cell_line, CCLE_histology, TCGA_classification, CCLE_name, DepMap_ID, Drug, AUC_IC50)
@@
 ccle_fus <- merge(merge(ccle_fus, ccle_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "CCLE_name", "CCLE_histology", "Cell_line", "FusionPair"), all = TRUE)
-ccle_fus$G2P_Fusion <- ifelse(is.na(ccle_fus$G2P_Fusion), "No", as.character(ccle_fus$G2P_Fusion))
+ccle_fus$Fusion_Status <- ifelse(!is.na(ccle_fus$LeftGene), "Yes", "No")
+ccle_fus$Drug_FusionPair <- ifelse(is.na(ccle_fus$Drug) | is.na(ccle_fus$FusionPair), NA, paste0(ccle_fus$Drug, "_", ccle_fus$FusionPair))
+ccle_fus$G2P_Drug_FusionPair <- ifelse(ccle_fus$Drug_FusionPair %in% unique(as.character(g2p_fus$Drug_FusionPair)), "Yes", "No")
+ccle_fus$G2P_Fusion <- ifelse(ccle_fus$FusionPair %in% unique(as.character(g2p_fus$FusionPair)), "Yes", "No")
+ccle_fus$Database <- "CCLE"
 
@@
 ctrp_fus <- merge(merge(ctrp_fus, ctrp_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "CCLE_name", "CCLE_histology", "Cell_line", "FusionPair"), all = TRUE)
-ctrp_fus$G2P_Fusion <- ifelse(is.na(ctrp_fus$G2P_Fusion), "No", as.character(ctrp_fus$G2P_Fusion))
+ctrp_fus$Fusion_Status <- ifelse(!is.na(ctrp_fus$LeftGene), "Yes", "No")
+ctrp_fus$Drug_FusionPair <- ifelse(is.na(ctrp_fus$Drug) | is.na(ctrp_fus$FusionPair), NA, paste0(ctrp_fus$Drug, "_", ctrp_fus$FusionPair))
+ctrp_fus$G2P_Drug_FusionPair <- ifelse(ctrp_fus$Drug_FusionPair %in% unique(as.character(g2p_fus$Drug_FusionPair)), "Yes", "No")
+ctrp_fus$G2P_Fusion <- ifelse(ctrp_fus$FusionPair %in% unique(as.character(g2p_fus$FusionPair)), "Yes", "No")
+ctrp_fus$Database <- "CTRP"
 
@@
 gdsc_fus <- merge(merge(gdsc_fus, gdsc_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "CCLE_name", "CCLE_histology", "Cell_line", "FusionPair"), all = TRUE)
-gdsc_fus$G2P_Fusion <- ifelse(is.na(gdsc_fus$G2P_Fusion), "No", as.character(gdsc_fus$G2P_Fusion))
+gdsc_fus$Fusion_Status <- ifelse(!is.na(gdsc_fus$LeftGene), "Yes", "No")
+gdsc_fus$Drug_FusionPair <- ifelse(is.na(gdsc_fus$Drug) | is.na(gdsc_fus$FusionPair), NA, paste0(gdsc_fus$Drug, "_", gdsc_fus$FusionPair))
+gdsc_fus$G2P_Drug_FusionPair <- ifelse(gdsc_fus$Drug_FusionPair %in% unique(as.character(g2p_fus$Drug_FusionPair)), "Yes", "No")
+gdsc_fus$G2P_Fusion <- ifelse(gdsc_fus$FusionPair %in% unique(as.character(g2p_fus$FusionPair)), "Yes", "No")
+gdsc_fus$Database <- "GDSC"
 
 fus <- bind_rows(ccle_fus, ctrp_fus, gdsc_fus)
+colnames(fus)[colnames(fus) == "AUC_IC50"] <- "Score"
 saveRDS(fus, "./data_munging/rds/fusions_merged.rds")
@@
 fus <- readRDS("./data_munging/rds/fusions_merged.rds") %>% drop_na(Drug)
-fus_summary <- fus %>% count(Drug, FusionPair, G2P_Fusion)
+fus_summary <- fus %>% count(Database, Drug, FusionPair, Fusion_Status)
 ```
@@
 
-# WILCOXON (MUT)
+# WILCOXON TESTS
 
@@
     dataframe$Drug_Gene_Lin <- as.character(dataframe$Drug_Gene_Lin)
-  }
     signif <- compare_means(Score ~ Mutation, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
@@
     signif <- signif[order(signif$p),]
+    signif$InG2P <- ifelse(signif$Drug_Gene_Lin %in% g2p_list, "Yes", "No")
+  }
+  if("FusionPair" %in% grouping) {
+    # Filter out fusions with too few samples in at least one category
+    count_n <- dataframe %>% count(Drug, FusionPair, Drug_FusionPair, Fusion_Status) %>% filter(n >= 3)
+    count_category <- count_n %>% count(Drug, FusionPair, Drug_FusionPair) %>% filter(n == 2)
+    keep <- intersect(count_n$Drug_FusionPair, count_category$Drug_FusionPair)
+    dataframe <- filter(dataframe, Drug_FusionPair %in% keep)
+    dataframe$Drug_FusionPair <- as.character(dataframe$Drug_FusionPair)
+    signif <- compare_means(Score ~ Fusion_Status, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
+    signif <- adj_signif(signif, alpha = 0.05)
+    signif <- signif[order(signif$p),]
+    signif$InG2P <- ifelse(signif$Drug_FusionPair %in% g2p_list, "Yes", "No")
+  }
   if("Drug_Gene" %in% grouping) {
+    signif <- compare_means(Score ~ Mutation, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
+    signif <- adj_signif(signif, alpha = 0.05)
+    signif <- signif[order(signif$p),]
     signif$InG2P <- ifelse(signif$Drug_Gene %in% g2p_list, "Yes", "No")
-  }
-  if("Drug_Gene_Lin" %in% grouping) {
-    signif$InG2P <- ifelse(signif$Drug_Gene_Lin %in% g2p_list, "Yes", "No")
   }
@@
 ```
+
+## Mutation status
 
@@
 gdsc_signif_dgl <- readRDS("./data_munging/rds/gdsc_signif_g2p_dgl.rds")
+```
+
+## Fusions
+
+```{r, eval=FALSE}
+ccle_fus <- filter(fus, Database == "CCLE")
+ccle_fus <- unfactorize(ccle_fus)
+ccle_signif_fus <- WilcoxonTestDF(dataframe = ccle_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair"), g2p_list = unique(as.character(g2p_fus$Drug_FusionPair[!is.na(g2p_fus$Drug_FusionPair)])), outfile = "./data_munging/rds/ccle_signif_fusions.rds")
+
+ctrp_fus <- filter(fus, Database == "CTRP")
+ctrp_fus <- unfactorize(ctrp_fus)
+ctrp_signif_fus <- WilcoxonTestDF(dataframe = ctrp_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair"), g2p_list = unique(as.character(g2p_fus$Drug_FusionPair[!is.na(g2p_fus$Drug_FusionPair)])), outfile = "./data_munging/rds/ctrp_signif_fusions.rds")
+
+gdsc_fus <- filter(fus, Drug %in% g2p_drugs & Database == "GDSC")
+gdsc_fus <- unfactorize(gdsc_fus)
+gdsc_signif_fus <- WilcoxonTestDF(dataframe = gdsc_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair"), g2p_list = unique(as.character(g2p_fus$Drug_FusionPair[!is.na(g2p_fus$Drug_FusionPair)])), outfile = "./data_munging/rds/gdsc_signif_fusions.rds")
 ```
@@
 ```{r}
-MakeMutHeatmap <- function(signif_g2p_dg, row_names, col_title, color, legend_title) {
-  signif_grid <- dcast(signif_g2p_dg, Gene ~ Drug, value.var = "p", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
+MakeWilcoxonHeatmap <- function(signif_df, feature, row_names, col_title, color, legend_title, row_title_txt) {
+  if(!is.na(str_match(string = tolower(feature), pattern = "mut"))) {
+    signif_grid <- dcast(signif_df, Gene ~ Drug, value.var = "p", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
     signif_grid <- signif_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
@@
 
-  signif_grid_annot <- dcast(signif_g2p_dg, Gene ~ Drug, value.var = "InG2P", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
+    signif_grid_annot <- dcast(signif_df, Gene ~ Drug, value.var = "InG2P", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
     signif_grid_annot <- signif_grid_annot[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
@@
     signif_grid_annot[signif_grid_annot == "Yes"] <- "O"
-
+  }
+  if(!is.na(str_match(string = tolower(feature), pattern = "fus"))) {
+    signif_grid <- dcast(signif_df, FusionPair ~ Drug, value.var = "p", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-FusionPair)
+    signif_grid <- signif_grid[, intersect(g2p_drug_order, colnames(signif_grid))]
+    signif_grid <- signif_grid[complete.cases(signif_grid), ]
+    signif_grid[signif_grid > 0.05] <- NA
+
+    signif_grid_annot <- dcast(signif_df, FusionPair ~ Drug, value.var = "InG2P", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-FusionPair)
+    signif_grid_annot <- signif_grid_annot[, intersect(g2p_drug_order, colnames(signif_grid))]
+    signif_grid_annot <- signif_grid_annot[complete.cases(signif_grid_annot), ]
+    signif_grid_annot[signif_grid_annot == "No"] <- ""
+    signif_grid_annot[signif_grid_annot == "Yes"] <- "O"
+  }
   col_fun <- colorRamp2(c(0, 0.05), c(color, "gray97"))
@@
                   # annotation_height = max_text_width(colnames(signif_grid))),
-                row_title = "Genes",
+                row_title = row_title_txt,
                 row_title_gp = gpar(fontface = "bold", fontsize = 14),
@@
                   grid.text(signif_grid_annot[i, j], x, y, gp = gpar(fontsize = 20))
-                  # if(signif_grid_annot[i, j] == "G") {
-                  #   grid.circle(x = x, y = y, r = 0.02, gp = gpar(fill = "transparent", col = "black"))
+                  # if(signif_grid_annot[i, j] == "O") {
+                  #   grid.circle(x = x, y = y, r = min(unit.c(width, height))*0.45, gp = gpar(fill = "transparent", col = "black"))
                   # }
@@
 ```{r mut_heatmaps, eval=FALSE}
-ht_ccle <- MakeMutHeatmap(signif_g2p_dg = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), legend_title = "P-value", row_names = TRUE, color = "darkgreen", col_title = "Drugs")
+ht_ccle <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "P-value", row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Genes")
 png(filename = "./plots/manuscript/ccle_mut_heatmap.png", width = 3, height = 10, units = "in", res = 500)
@@
 
-ht_ctrp <- MakeMutHeatmap(signif_g2p_dg = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), legend_title = "P-value", row_names = TRUE, color = "steelblue4", col_title = "Drugs")
+ht_ctrp <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "P-value", row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes")
 png(filename = "./plots/manuscript/ctrp_mut_heatmap.png", width = 9.5, height = 10, units = "in", res = 500)
@@
 
-ht_gdsc <- MakeMutHeatmap(signif_g2p_dg = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), legend_title = "P-value", row_names = TRUE, color = "turquoise4", col_title = "Drugs")
+ht_gdsc <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "P-value", row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Genes")
 png(filename = "./plots/manuscript/gdsc_mut_heatmap.png", width = 5, height = 10, units = "in", res = 500)
@@
 
-ht_ccle2 <- MakeMutHeatmap(signif_g2p_dg = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), legend_title = "CCLE p-value                                                                               ", row_names = TRUE, color = "darkgreen", col_title = "")
-ht_ctrp2 <- MakeMutHeatmap(signif_g2p_dg = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), legend_title = "CTRP p-value                                                                              ", row_names = FALSE, color = "steelblue4", col_title = "Drugs")
-ht_gdsc2 <- MakeMutHeatmap(signif_g2p_dg = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), legend_title = "GDSC p-value", row_names = FALSE, color = "turquoise4", col_title = "")
+ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "CCLE p-value                                                                               ", row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Genes")
+ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "CTRP p-value                                                                              ", row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes")
+ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "GDSC p-value", row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes")
 png(filename = "./plots/manuscript/drug_mut_heatmap.png", width = 13, height = 10, units = "in", res = 500)
@@
 
-# WILCOXON (Fusions)
-
---------------------------------------------------------------------------------
+```{r fus_heatmaps, eval=FALSE}
+ht_ccle <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "P-value", row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Fusion Pairs")
+png(filename = "./plots/manuscript/ccle_fus_heatmap.png", width = 2.5, height = 3, units = "in", res = 500)
+draw(ht_ccle, heatmap_legend_side = "top")
+dev.off()
+
+ht_ctrp <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "P-value", row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Fusion Pairs")
+png(filename = "./plots/manuscript/ctrp_fus_heatmap.png", width = 6, height = 3, units = "in", res = 500)
+draw(ht_ctrp, heatmap_legend_side = "top")
+dev.off()
+
+ht_gdsc <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "P-value", row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Fusion Pairs")
+png(filename = "./plots/manuscript/gdsc_fus_heatmap.png", width = 5, height = 3, units = "in", res = 500)
+draw(ht_gdsc, heatmap_legend_side = "top")
+dev.off()
+
+ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "CCLE p-value                                                                               ", row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Fusion Pairs")
+ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "CTRP p-value                                                                              ", row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Fusion Pairs")
+ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "GDSC p-value", row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Fusion Pairs")
+png(filename = "./plots/manuscript/drug_fus_heatmap.png", width = 13, height = 2.5, units = "in", res = 500)
+draw(ht_ccle2 + ht_ctrp2 + ht_gdsc2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
+dev.off()
+```
 

### 2019-05-31 19Q2.Rmd
update mut and fus heatmaps w/ -log10(p-values) instead of p-values

@@
 
-```{r}
-test <- unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)]))
-test2 <- unique(as.character(g2p_mut$Drug_Gene_Lin[!is.na(g2p_mut$Drug_Gene_Lin)]))
-```
-
-```{r wilcoxon_tests, eval=FALSE}
+```{r mut_wilcoxon_tests, eval=FALSE}
 crispr <- unfactorize(crispr)
@@
 
-```{r load_wilcoxon_rds}
+```{r load_mut_wilcoxon_rds}
 crispr_signif_g <- readRDS("./data_munging/rds/crispr_signif_g.rds")
@@
 
-```{r, eval=FALSE}
+```{r fusion_data}
 ccle_fus <- filter(fus, Database == "CCLE")
 ccle_fus <- unfactorize(ccle_fus)
-ccle_signif_fus <- WilcoxonTestDF(dataframe = ccle_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair"), g2p_list = unique(as.character(g2p_fus$Drug_FusionPair[!is.na(g2p_fus$Drug_FusionPair)])), outfile = "./data_munging/rds/ccle_signif_fusions.rds")
 
@@
 ctrp_fus <- unfactorize(ctrp_fus)
-ctrp_signif_fus <- WilcoxonTestDF(dataframe = ctrp_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair"), g2p_list = unique(as.character(g2p_fus$Drug_FusionPair[!is.na(g2p_fus$Drug_FusionPair)])), outfile = "./data_munging/rds/ctrp_signif_fusions.rds")
 
@@
 gdsc_fus <- unfactorize(gdsc_fus)
+```
+
+```{r fus_wilcoxon_tests, eval=FALSE}
+ccle_signif_fus <- WilcoxonTestDF(dataframe = ccle_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair"), g2p_list = unique(as.character(g2p_fus$Drug_FusionPair[!is.na(g2p_fus$Drug_FusionPair)])), outfile = "./data_munging/rds/ccle_signif_fusions.rds")
+
+ctrp_signif_fus <- WilcoxonTestDF(dataframe = ctrp_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair"), g2p_list = unique(as.character(g2p_fus$Drug_FusionPair[!is.na(g2p_fus$Drug_FusionPair)])), outfile = "./data_munging/rds/ctrp_signif_fusions.rds")
+
 gdsc_signif_fus <- WilcoxonTestDF(dataframe = gdsc_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair"), g2p_list = unique(as.character(g2p_fus$Drug_FusionPair[!is.na(g2p_fus$Drug_FusionPair)])), outfile = "./data_munging/rds/gdsc_signif_fusions.rds")
@@
 
-## Plots
-
-```{r fig.height=4, fig.width=8}
+```{r load_fus_wilcoxon_rds}
+ccle_signif_fus <- readRDS("./data_munging/rds/ccle_signif_fusions.rds")
+ctrp_signif_fus <- readRDS("./data_munging/rds/ctrp_signif_fusions.rds")
+gdsc_signif_fus <- readRDS("./data_munging/rds/gdsc_signif_fusions.rds")
+```
+
+## Boxplots
+
+```{r fig.height=5, fig.width=10}
 crispr_filt <- filter(crispr, Gene %in% g2p_mut_genes)
@@
 
-```{r}
-MakeWilcoxonHeatmap <- function(signif_df, feature, row_names, col_title, color, legend_title, row_title_txt) {
+```{r fusion_boxplots, fig.height=5, fig.width=8}
+ccle_fus_filt <- filter(ccle_fus, FusionPair %in% c("ABL1-BCR", "BCR-ABL1") & Drug %in% g2p_drugs)
+ccle_fus_filt$Drug_f <- factor(ccle_fus_filt$Drug, levels = intersect(g2p_drug_order, unique(ccle_fus$Drug)))
+ccle_signif_fus_filt <- filter(ccle_signif_fus, Drug %in% g2p_drugs)
+ccle_signif_fus_filt$Drug_f <- factor(ccle_signif_fus_filt$Drug, levels = intersect(g2p_drug_order, unique(ccle_signif_fus$Drug)))
+
+ccle_fus_boxplot <- ggplot(data = ccle_fus_filt) +
+  facet_grid(FusionPair ~ Drug_f) +
+  scale_color_manual(name = "Fusion Status", values = c("Yes" = "springgreen4", "No" = "palegreen3")) +
+  geom_jitter(aes(x = Fusion_Status, y = Score, color = Fusion_Status), width = 0.2, alpha = 0.5, size = 0.6) +
+  geom_boxplot(aes(x = Fusion_Status, y = Score), fill = "transparent", outlier.shape = NA, lwd = 0.3) +
+  coord_cartesian(ylim = c(0, 1.2)) +
+  scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
+  geom_text(data = ccle_signif_fus_filt, aes(x = 1.5, y = 1.1, label = p.signif)) +
+  theme(legend.position = "top", legend.direction = "horizontal", axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
+  guides(color = guide_legend(override.aes = list(size = 3))) +
+  labs(y = "AUC", x = "Fusion Status")
+ccle_fus_boxplot
+```
+
+## Heatmaps
+
+```{r wilcoxon_heatmap_function}
+MakeWilcoxonHeatmap <- function(signif_df, feature, row_names, col_title, color, legend_title, legend_breaks, row_title_txt, radius) {
+  signif_df$p_log10 <- as.numeric(formatC(-log10(signif_df$p), digits = 3, format = "f"))
   if(!is.na(str_match(string = tolower(feature), pattern = "mut"))) {
-    signif_grid <- dcast(signif_df, Gene ~ Drug, value.var = "p", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
+    signif_grid <- dcast(signif_df, Gene ~ Drug, value.var = "p_log10", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
     signif_grid <- signif_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
     signif_grid <- signif_grid[complete.cases(signif_grid), ]
-    signif_grid[signif_grid > 0.05] <- NA
+    signif_grid[signif_grid < -log10(0.05)] <- NA
 
@@
   if(!is.na(str_match(string = tolower(feature), pattern = "fus"))) {
-    signif_grid <- dcast(signif_df, FusionPair ~ Drug, value.var = "p", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-FusionPair)
+    signif_grid <- dcast(signif_df, FusionPair ~ Drug, value.var = "p_log10", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-FusionPair)
     signif_grid <- signif_grid[, intersect(g2p_drug_order, colnames(signif_grid))]
     signif_grid <- signif_grid[complete.cases(signif_grid), ]
-    signif_grid[signif_grid > 0.05] <- NA
+    signif_grid[signif_grid < -log10(0.05)] <- NA
 
@@
   }
-  col_fun <- colorRamp2(c(0, 0.05), c(color, "gray97"))
+  col_fun <- colorRamp2(c(legend_breaks[1], legend_breaks[length(legend_breaks)]), c("gray97", color))
   # Legend properties list
-  ht_legend_list <- list(title = legend_title, title_position = "topleft", legend_direction = "horizontal", legend_width = unit(2, "in"), border = "gray70",   at = seq(0, 0.05, by = 0.01), labels = seq(0, 0.05, by = 0.01))
+  ht_legend_list <- list(title = legend_title, title_position = "topleft", legend_direction = "horizontal", legend_width = unit(2, "in"), border = "gray70", at = legend_breaks, labels = legend_breaks)
   ht <- Heatmap(signif_grid,
@@
                 cell_fun = function(j, i, x, y, width, height, fill) {
-                  grid.text(signif_grid_annot[i, j], x, y, gp = gpar(fontsize = 20))
-                  # if(signif_grid_annot[i, j] == "O") {
-                  #   grid.circle(x = x, y = y, r = min(unit.c(width, height))*0.45, gp = gpar(fill = "transparent", col = "black"))
-                  # }
+                  # grid.text(signif_grid_annot[i, j], x, y, gp = gpar(fontsize = 20))
+                  if(signif_grid_annot[i, j] == "O") {
+                    grid.circle(x = x, y = y, r = radius, gp = gpar(fill = "transparent", col = "black"))
+                  }
                 }
@@
 ```{r mut_heatmaps, eval=FALSE}
-ht_ccle <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "P-value", row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Genes")
+ht_ccle <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "-log10(p-value)", legend_breaks = seq(0, 12, by = 3), row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Genes", radius = 0.07)
 png(filename = "./plots/manuscript/ccle_mut_heatmap.png", width = 3, height = 10, units = "in", res = 500)
@@
 
-ht_ctrp <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "P-value", row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes")
+ht_ctrp <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "-log10(p-value)", legend_breaks = seq(0, 18, by = 3), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.016)
 png(filename = "./plots/manuscript/ctrp_mut_heatmap.png", width = 9.5, height = 10, units = "in", res = 500)
@@
 
-ht_gdsc <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "P-value", row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Genes")
+ht_gdsc <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "-log10(p-value)", legend_breaks = seq(0, 6, by = 1), row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.033)
 png(filename = "./plots/manuscript/gdsc_mut_heatmap.png", width = 5, height = 10, units = "in", res = 500)
@@
 
-ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "CCLE p-value                                                                               ", row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Genes")
-ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "CTRP p-value                                                                              ", row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes")
-ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "GDSC p-value", row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes")
+ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "CCLE -log10(p-value)                                                                     ", legend_breaks = seq(0, 12, by = 3), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Genes", radius = 0.07)
+ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "CTRP -log10(p-value)                                                                    ", legend_breaks = seq(0, 18, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.018)
+ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 6, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes", radius = 0.035)
 png(filename = "./plots/manuscript/drug_mut_heatmap.png", width = 13, height = 10, units = "in", res = 500)
@@
 ```{r fus_heatmaps, eval=FALSE}
-ht_ccle <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "P-value", row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Fusion Pairs")
-png(filename = "./plots/manuscript/ccle_fus_heatmap.png", width = 2.5, height = 3, units = "in", res = 500)
+ht_ccle <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "-log10(p-value)",  legend_breaks = seq(0, 4, by = 1), row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Fusion Pairs", radius = 0.2)
+png(filename = "./plots/manuscript/ccle_fus_heatmap.png", width = 5, height = 3, units = "in", res = 500)
 draw(ht_ccle, heatmap_legend_side = "top")
@@
 
-ht_ctrp <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "P-value", row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Fusion Pairs")
-png(filename = "./plots/manuscript/ctrp_fus_heatmap.png", width = 6, height = 3, units = "in", res = 500)
+ht_ctrp <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "-log10(p-value)", row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Fusion Pairs", radius = 0.2)
+png(filename = "./plots/manuscript/ctrp_fus_heatmap.png", width = 13, height = 3, units = "in", res = 500)
 draw(ht_ctrp, heatmap_legend_side = "top")
@@
 
-ht_gdsc <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "P-value", row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Fusion Pairs")
-png(filename = "./plots/manuscript/gdsc_fus_heatmap.png", width = 5, height = 3, units = "in", res = 500)
+ht_gdsc <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "-log10(p-value)", row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Fusion Pairs", radius = 0.2)
+png(filename = "./plots/manuscript/gdsc_fus_heatmap.png", width = 9, height = 3, units = "in", res = 500)
 draw(ht_gdsc, heatmap_legend_side = "top")
@@
 
-ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "CCLE p-value                                                                               ", row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Fusion Pairs")
-ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "CTRP p-value                                                                              ", row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Fusion Pairs")
-ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "GDSC p-value", row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Fusion Pairs")
+ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "CCLE -log10(p-value)                                                                               ", legend_breaks = seq(0, 4, by = 1), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Fusion Pairs", radius = 0.2)
+ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "CTRP -log10(p-value)                                                                              ", row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Fusion Pairs", radius = 0.2)
+ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "GDSC -log10(p-value)", row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Fusion Pairs", radius = 0.2)
 png(filename = "./plots/manuscript/drug_fus_heatmap.png", width = 13, height = 2.5, units = "in", res = 500)

### 2019-05-31 19Q2.Rmd
update Rmd

@@
 g2p <- add_column(g2p, Direction_Curated = NA, .after = "Direction")
-g2p$Direction_Curated <-
-  ifelse(!is.na(str_match(string = tolower(g2p$Direction), pattern = "sensitive|sensitivity||responsive")), "sensitivity",
-         ifelse(!is.na(str_match(string = tolower(g2p$Direction), pattern = "resist")), "resistance", NA))
+g2p$Direction_Curated <- ifelse(!is.na(str_match(string = tolower(g2p$Direction), pattern = "resist")), "resistance", ifelse(!is.na(str_match(string = tolower(g2p$Direction), pattern = "sensitive|sensitivity||responsive")), "sensitivity", NA))
 
@@
 g2p$biomarker_type_curated <- ifelse(is.na(g2p$biomarker_type_curated), "None", as.character(g2p$biomarker_type_curated))
-g2p_split <- split(filter(g2p, !is.na(Drug)), g2p$biomarker_type_curated)
+g2p_split <- filter(g2p, !is.na(Drug)) %>% group_split(biomarker_type_curated)
 g2p_amp <- g2p_split[[1]]
@@
 g2p_fus$FusionPair <- ifelse(g2p_fus$FusionPair == "Fusions", as.character(g2p_fus$Gene), as.character(g2p_fus$FusionPair))
+g2p_fus$FusionPair <- ifelse(g2p_fus$FusionPair == "BCR-ABL", "BCR-ABL1", as.character(g2p_fus$FusionPair))
 g2p_fus$Drug_FusionPair <- ifelse(is.na(g2p_fus$Drug) | is.na(g2p_fus$FusionPair), NA, paste0(g2p_fus$Drug, "_", g2p_fus$FusionPair))
@@
 g2p_mut_genes <- unique(sapply(strsplit(as.character(g2p_mut$Drug_Gene)[!is.na(g2p_mut$Drug_Gene)], "_", fixed = TRUE), function(x) x[2]))
-g2p_no_biomarker <- g2p_split[[5]]
-
 g2p_nodrug <- filter(g2p, is.na(Drug))
@@
 fus <- readRDS("./data_munging/rds/fusions_merged.rds") %>% drop_na(Drug)
-fus_summary <- fus %>% count(Database, Drug, FusionPair, Fusion_Status)
+fus_summary <- fuqs %>% count(Database, Drug, FusionPair, Fusion_Status)
 ```
@@
   }
+  signif$p_log10 <- as.numeric(formatC(-log10(signif$p), digits = 3, format = "f"))
   saveRDS(signif, outfile)
@@
 
-```{r fusion_boxplots, fig.height=5, fig.width=8}
+```{r fusion_boxplots, fig.height=5, fig.width=12}
+# CCLE
 ccle_fus_filt <- filter(ccle_fus, FusionPair %in% c("ABL1-BCR", "BCR-ABL1") & Drug %in% g2p_drugs)
@@
 ccle_fus_boxplot
+
+# CTRP
+ctrp_fus_filt <- filter(ctrp_fus, FusionPair %in% c("ABL1-BCR", "BCR-ABL1") & Drug %in% g2p_drugs)
+ctrp_fus_filt$Drug_f <- factor(ctrp_fus_filt$Drug, levels = intersect(g2p_drug_order, unique(ctrp_fus$Drug)))
+ctrp_signif_fus_filt <- filter(ctrp_signif_fus, Drug %in% g2p_drugs)
+ctrp_signif_fus_filt$Drug_f <- factor(ctrp_signif_fus_filt$Drug, levels = intersect(g2p_drug_order, unique(ctrp_signif_fus$Drug)))
+
+ctrp_fus_boxplot <- ggplot(data = ctrp_fus_filt) +
+  facet_grid(FusionPair ~ Drug_f) +
+  scale_color_manual(name = "Fusion Status", values = c("Yes" = "steelblue4", "No" = "slategray3")) +
+  geom_jitter(aes(x = Fusion_Status, y = Score, color = Fusion_Status), width = 0.2, alpha = 0.5, size = 0.6) +
+  geom_boxplot(aes(x = Fusion_Status, y = Score), fill = "transparent", outlier.shape = NA, lwd = 0.3) +
+  coord_cartesian(ylim = c(0, 1.2)) +
+  scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
+  geom_text(data = ctrp_signif_fus_filt, aes(x = 1.5, y = 1.1, label = p.signif)) +
+  theme(legend.position = "top", legend.direction = "horizontal", axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
+  guides(color = guide_legend(override.aes = list(size = 3))) +
+  labs(y = "AUC", x = "Fusion Status")
+ctrp_fus_boxplot
+
+# GDSC
+gdsc_fus_filt <- filter(gdsc_fus, FusionPair %in% c("ABL1-BCR", "BCR-ABL1") & Drug %in% g2p_drugs)
+gdsc_fus_filt$Drug_f <- factor(gdsc_fus_filt$Drug, levels = intersect(g2p_drug_order, unique(gdsc_fus$Drug)))
+gdsc_signif_fus_filt <- filter(gdsc_signif_fus, Drug %in% g2p_drugs)
+gdsc_signif_fus_filt$Drug_f <- factor(gdsc_signif_fus_filt$Drug, levels = intersect(g2p_drug_order, unique(gdsc_signif_fus$Drug)))
+
+gdsc_fus_boxplot <- ggplot(data = gdsc_fus_filt) +
+  facet_grid(FusionPair ~ Drug_f) +
+  scale_color_manual(name = "Fusion Status", values = c("Yes" = "turquoise4", "No" = "paleturquoise3")) +
+  geom_jitter(aes(x = Fusion_Status, y = Score, color = Fusion_Status), width = 0.2, alpha = 0.5, size = 0.6) +
+  geom_boxplot(aes(x = Fusion_Status, y = Score), fill = "transparent", outlier.shape = NA, lwd = 0.3) +
+  coord_cartesian(ylim = c(0, 1.2)) +
+  scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
+  geom_text(data = gdsc_signif_fus_filt, aes(x = 1.5, y = 1.1, label = p.signif)) +
+  theme(legend.position = "top", legend.direction = "horizontal", axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
+  guides(color = guide_legend(override.aes = list(size = 3))) +
+  labs(y = "AUC", x = "Fusion Status")
+gdsc_fus_boxplot
 ```
@@
 MakeWilcoxonHeatmap <- function(signif_df, feature, row_names, col_title, color, legend_title, legend_breaks, row_title_txt, radius) {
-  signif_df$p_log10 <- as.numeric(formatC(-log10(signif_df$p), digits = 3, format = "f"))
   if(!is.na(str_match(string = tolower(feature), pattern = "mut"))) {
@@
 
-ht_gdsc <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "-log10(p-value)", legend_breaks = seq(0, 6, by = 1), row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.033)
+ht_gdsc <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "-log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.033)
 png(filename = "./plots/manuscript/gdsc_mut_heatmap.png", width = 5, height = 10, units = "in", res = 500)
@@
 ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "CTRP -log10(p-value)                                                                    ", legend_breaks = seq(0, 18, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.018)
-ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 6, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes", radius = 0.035)
-png(filename = "./plots/manuscript/drug_mut_heatmap.png", width = 13, height = 10, units = "in", res = 500)
+ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes", radius = 0.035)
+png(filename = "./plots/manuscript/drug_mut_heatmap.png", width = 13, height = 9.5, units = "in", res = 500)
 draw(ht_ccle2 + ht_ctrp2 + ht_gdsc2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
@@
 
-ht_ctrp <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "-log10(p-value)", row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Fusion Pairs", radius = 0.2)
+ht_ctrp <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "-log10(p-value)", legend_breaks = seq(0, 10, by = 2), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Fusion Pairs", radius = 0.2)
 png(filename = "./plots/manuscript/ctrp_fus_heatmap.png", width = 13, height = 3, units = "in", res = 500)
@@
 
-ht_gdsc <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "-log10(p-value)", row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Fusion Pairs", radius = 0.2)
+ht_gdsc <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "-log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Fusion Pairs", radius = 0.2)
 png(filename = "./plots/manuscript/gdsc_fus_heatmap.png", width = 9, height = 3, units = "in", res = 500)
@@
 ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "CCLE -log10(p-value)                                                                               ", legend_breaks = seq(0, 4, by = 1), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Fusion Pairs", radius = 0.2)
-ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "CTRP -log10(p-value)                                                                              ", row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Fusion Pairs", radius = 0.2)
-ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "GDSC -log10(p-value)", row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Fusion Pairs", radius = 0.2)
-png(filename = "./plots/manuscript/drug_fus_heatmap.png", width = 13, height = 2.5, units = "in", res = 500)
+ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "CTRP -log10(p-value)                                                                              ", legend_breaks = seq(0, 10, by = 2), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Fusion Pairs", radius = 0.2)
+ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Fusion Pairs", radius = 0.2)
+png(filename = "./plots/manuscript/drug_fus_heatmap.png", width = 13, height = 2.4, units = "in", res = 500)
 draw(ht_ccle2 + ht_ctrp2 + ht_gdsc2, gap = unit(0.25, "in"), heatmap_legend_side = "top")

### 2019-06-03 19Q2.Rmd

@@
 g2p <- add_column(g2p, Direction_Curated = NA, .after = "Direction")
-g2p$Direction_Curated <- ifelse(!is.na(str_match(string = tolower(g2p$Direction), pattern = "resist")), "resistance", ifelse(!is.na(str_match(string = tolower(g2p$Direction), pattern = "sensitive|sensitivity||responsive")), "sensitivity", NA))
+g2p$Direction_Curated <- ifelse(!is.na(str_match(string = tolower(g2p$Direction), pattern = "resist")), "resistance", ifelse(!is.na(str_match(string = tolower(g2p$Direction), pattern = "sensitive|sensitivity|responsive")), "sensitivity", "none"))
 
@@
 
+```{r}
+cgi <- read.delim("./../../../Desktop/cgi_biomarkers_latest/cgi_biomarkers_per_variant.tsv", sep = "\t", header = TRUE)
+```
+
 DepMap 19Q2 fusion calls derived using the [STAR-Fusion pipeline](https://github.com/STAR-Fusion/STAR-Fusion/wiki). Column descriptions:
@@
 fusions <- read.delim("./data_munging/19Q2/CCLE_fusions.csv.gz", header = TRUE, sep = ",")
+fusions_bcr_abl1 <- filter(fusions, X.FusionName %in% c("BCR--ABL1", "ABL1--BCR"))
 fusions$LeftGene <- gsub(" .*", "", fusions$LeftGene)
@@
 fus <- readRDS("./data_munging/rds/fusions_merged.rds") %>% drop_na(Drug)
-fus_summary <- fuqs %>% count(Database, Drug, FusionPair, Fusion_Status)
+fus_summary <- fus %>% count(Database, Drug, FusionPair, Fusion_Status)
 ```
@@
 
+ggpubr's convention for symbols indicating statistical significance:
+
+- ns: p > 0.05
+- *: p <= 0.05
+- **: p <= 0.01
+- ***: p <= 0.001
+- ****: p <= 0.0001
+
 ```{r wilcoxon_functions}
@@
 ```{r mut_wilcoxon_tests, eval=FALSE}
+# CRISPR
 crispr <- unfactorize(crispr)
@@
 
+# CCLE
 ccle_filt <- filter(ccle, Drug %in% g2p_drugs & Gene %in% g2p_dg_genes)
@@
 
+# CTRP
 ctrp_filt <- filter(ctrp, Drug %in% g2p_drugs & Gene %in% g2p_dg_genes)
@@
 
+# GDSC
 gdsc_filt <- filter(gdsc, Drug %in% g2p_drugs & Gene %in% g2p_dg_genes)
@@
 ```{r load_mut_wilcoxon_rds}
+g2p_mut_4merge <- unique(select(g2p_mut, Drug_Gene, Direction_Curated))
+g2p_mut_4merge$Direction_Numeric <- as.numeric(g2p_mut_4merge$Direction_Curated)
+
 crispr_signif_g <- readRDS("./data_munging/rds/crispr_signif_g.rds")
@@
 ccle_signif_g2p_dg <- readRDS("./data_munging/rds/ccle_signif_g2p_dg.rds")
+# ccle_signif_g2p_dg <- merge(ccle_signif_g2p_dg, g2p_mut_4merge, by = "Drug_Gene", all.x = TRUE)
+# ccle_signif_g2p_dg$Direction_Numeric <- ifelse(is.na(ccle_signif_g2p_dg$Direction_Numeric), 4, as.numeric(ccle_signif_g2p_dg$Direction_Numeric))
 ccle_signif_dgl <- readRDS("./data_munging/rds/ccle_signif_g2p_dgl.rds")
@@
 ctrp_signif_g2p_dg <- readRDS("./data_munging/rds/ctrp_signif_g2p_dg.rds")
+# ctrp_signif_g2p_dg <- merge(ctrp_signif_g2p_dg, g2p_mut_4merge, by = "Drug_Gene", all.x = TRUE)
 ctrp_signif_dgl <- readRDS("./data_munging/rds/ctrp_signif_g2p_dgl.rds")
@@
 gdsc_signif_g2p_dg <- readRDS("./data_munging/rds/gdsc_signif_g2p_dg.rds")
+# gdsc_signif_g2p_dg <- merge(gdsc_signif_g2p_dg, g2p_mut_4merge, by = "Drug_Gene", all.x = TRUE)
 gdsc_signif_dgl <- readRDS("./data_munging/rds/gdsc_signif_g2p_dgl.rds")
@@
 ```{r load_fus_wilcoxon_rds}
+g2p_fus_4merge <- unique(select(g2p_fus, Drug_FusionPair, Direction_Curated))
+
 ccle_signif_fus <- readRDS("./data_munging/rds/ccle_signif_fusions.rds")
+# ccle_signif_fus <- merge(ccle_signif_fus, g2p_fus_4merge, by = "Drug_FusionPair", all.x = TRUE)
+
 ctrp_signif_fus <- readRDS("./data_munging/rds/ctrp_signif_fusions.rds")
+# ctrp_signif_fus <- merge(ctrp_signif_fus, g2p_fus_4merge, by = "Drug_FusionPair", all.x = TRUE)
+
 gdsc_signif_fus <- readRDS("./data_munging/rds/gdsc_signif_fusions.rds")
+# gdsc_signif_fus <- merge(gdsc_signif_fus, g2p_fus_4merge, by = "Drug_FusionPair", all.x = TRUE)
 ```
@@
 
-```{r fig.height=5, fig.width=10}
+```{r crispr_mut_boxplots, fig.height=5, fig.width=10}
 crispr_filt <- filter(crispr, Gene %in% g2p_mut_genes)
@@
 ccle_fus_boxplot
+# ggsave("./plots/manuscript/ccle_fus_boxplots.png", ccle_fus_boxplot, width = 8, height = 5, units = "in")
 
@@
 ctrp_fus_boxplot
+# ggsave("./plots/manuscript/ctrp_fus_boxplots.png", ctrp_fus_boxplot, width = 19, height = 5, units = "in")
 
@@
 gdsc_fus_boxplot
+# ggsave("./plots/manuscript/gdsc_fus_boxplots.png", gdsc_fus_boxplot, width = 12, height = 5, units = "in")
 ```
@@
 ## Heatmaps
+
+```{r wilcoxon_heatmap_function_EDIT, eval=FALSE}
+MakeWilcoxonHeatmap <- function(signif_df, feature, row_names, col_title, color, legend_title, legend_breaks, row_title_txt, radius) {
+  if(!is.na(str_match(string = tolower(feature), pattern = "mut"))) {
+    signif_grid <- dcast(signif_df, Gene ~ Drug, value.var = "p_log10", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
+    signif_grid <- signif_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
+    signif_grid <- signif_grid[complete.cases(signif_grid), ]
+    signif_grid[signif_grid < -log10(0.05)] <- NA
+
+    signif_grid_annot <- dcast(signif_df, Gene ~ Drug, value.var = "Direction_Curated", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
+    signif_grid_annot <- signif_grid_annot[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
+    signif_grid_annot <- signif_grid_annot[complete.cases(signif_grid_annot), ]
+    # signif_grid_annot[signif_grid_annot == "No"] <- ""
+    # signif_grid_annot[signif_grid_annot == "Yes"] <- "O"
+  }
+  if(!is.na(str_match(string = tolower(feature), pattern = "fus"))) {
+    signif_grid <- dcast(signif_df, FusionPair ~ Drug, value.var = "p_log10", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-FusionPair)
+    signif_grid <- signif_grid[, intersect(g2p_drug_order, colnames(signif_grid))]
+    signif_grid <- signif_grid[complete.cases(signif_grid), ]
+    signif_grid[signif_grid < -log10(0.05)] <- NA
+
+    signif_grid_annot <- dcast(signif_df, FusionPair ~ Drug, value.var = "Direction_Curated", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-FusionPair)
+    signif_grid_annot <- signif_grid_annot[, intersect(g2p_drug_order, colnames(signif_grid))]
+    signif_grid_annot <- signif_grid_annot[complete.cases(signif_grid_annot), ]
+    # signif_grid_annot[signif_grid_annot == "No"] <- ""
+    # signif_grid_annot[signif_grid_annot == "Yes"] <- "O"
+  }
+  col_fun <- colorRamp2(c(legend_breaks[1], legend_breaks[length(legend_breaks)]), c("gray97", color))
+  # Legend properties list
+  ht_legend_list <- list(title = legend_title, title_position = "topleft", legend_direction = "horizontal", legend_width = unit(2, "in"), border = "gray70", at = legend_breaks, labels = legend_breaks)
+  ht <- Heatmap(signif_grid,
+                col = col_fun,
+                na_col = "gray97",
+                rect_gp = gpar(col = "gray70"),
+                heatmap_legend_param = ht_legend_list,
+                cluster_rows = FALSE, 
+                cluster_columns = FALSE, 
+                show_row_names = as.logical(row_names),
+                row_names_side = "left",
+                row_names_gp = gpar(fontsize = 10),
+                column_names_side = "bottom",
+                column_names_gp = gpar(fontsize = 10),
+                show_column_names = FALSE,
+                bottom_annotation = HeatmapAnnotation(
+                  text = anno_text(colnames(signif_grid),
+                                   rot = 45,
+                                   gp = gpar(fontsize = 11),
+                                   offset = unit(1, "npc"),
+                                   just = "right"),
+                  annotation_height = unit(0.85, "in")),
+                  # annotation_height = max_text_width(colnames(signif_grid))),
+                row_title = row_title_txt,
+                row_title_gp = gpar(fontface = "bold", fontsize = 14),
+                column_title = col_title, 
+                column_title_gp = gpar(fontface = "bold", fontsize = 14),
+                column_title_side = "bottom",
+                cell_fun = function(j, i, x, y, width, height, fill) {
+                  # grid.text(signif_grid_annot[i, j], x, y, gp = gpar(fontsize = 20))
+                  if(signif_grid_annot[i, j] == "none") {
+                    grid.circle(x = x, y = y, r = radius, gp = gpar(fill = "transparent", col = "black"))
+                  }
+                  if(signif_grid_annot[i, j] == "sensitivity") {
+                    grid.polygon(x = c(0, 0.5, 1), y = c(0, 1, 0), default.units = "npc", gp = gpar(fill = "transparent", col = "black"))
+                  }
+                  if(signif_grid_annot[i, j] == "resistance") {
+                    grid.polygon(x = c(0.1, 0.1, 0.9, 0.9), y = c(0.1, 0.9, 0.9, 0.1), default.units = "npc", gp = gpar(fill = "transparent", col = "black"))
+                  }
+                }
+                )
+  return(ht)
+}
+```
 
@@
                   if(signif_grid_annot[i, j] == "O") {
-                    grid.circle(x = x, y = y, r = radius, gp = gpar(fill = "transparent", col = "black"))
+                    grid.circle(x = x - width*0.20, y = y - height*0.20, r = radius, default.units = "npc", gp = gpar(fill = "white", col = "black"))
                   }
@@
 
-```{r mut_heatmaps, eval=FALSE}
-ht_ccle <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "-log10(p-value)", legend_breaks = seq(0, 12, by = 3), row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Genes", radius = 0.07)
+```{r testing, eval=FALSE}
+grid.newpage()
+grid.polygon(x = c(0.1, 0.1, 0.9, 0.9), y = c(0.1, 0.9, 0.9, 0.1), default.units = "npc",
+             gp = gpar(), draw = TRUE, vp = NULL)
+
+signif_df <- filter(ccle_signif_fus, Drug %in% g2p_drugs)
+signif_grid <- dcast(signif_df, FusionPair ~ Drug, value.var = "p_log10", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-FusionPair)
+signif_grid <- signif_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
+signif_grid <- signif_grid[complete.cases(signif_grid), ]
+signif_grid[signif_grid < -log10(0.05)] <- NA
+signif_grid_annot <- dcast(signif_df, FusionPair ~ Drug, value.var = "Direction_Curated", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-FusionPair)
+signif_grid_annot <- signif_grid_annot[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
+signif_grid_annot <- signif_grid_annot[complete.cases(signif_grid_annot), ]
+```
+
+```{r mut_heatmaps, eval=FALSE, fig.height=10, fig.width=3}
+ht_ccle <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "-log10(p-value)", legend_breaks = seq(0, 12, by = 3), row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Genes", radius = 0.03)
 png(filename = "./plots/manuscript/ccle_mut_heatmap.png", width = 3, height = 10, units = "in", res = 500)
@@
 
-ht_ctrp <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "-log10(p-value)", legend_breaks = seq(0, 18, by = 3), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.016)
+ht_ctrp <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "-log10(p-value)", legend_breaks = seq(0, 18, by = 3), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.008)
 png(filename = "./plots/manuscript/ctrp_mut_heatmap.png", width = 9.5, height = 10, units = "in", res = 500)
@@
 
-ht_gdsc <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "-log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.033)
+ht_gdsc <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "-log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.015)
 png(filename = "./plots/manuscript/gdsc_mut_heatmap.png", width = 5, height = 10, units = "in", res = 500)
@@
 
-ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "CCLE -log10(p-value)                                                                     ", legend_breaks = seq(0, 12, by = 3), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Genes", radius = 0.07)
-ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "CTRP -log10(p-value)                                                                    ", legend_breaks = seq(0, 18, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.018)
-ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes", radius = 0.035)
+ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "CCLE -log10(p-value)                                                                     ", legend_breaks = seq(0, 12, by = 3), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Genes", radius = 0.03)
+ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "CTRP -log10(p-value)                                                                    ", legend_breaks = seq(0, 18, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.008)
+ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes", radius = 0.015)
 png(filename = "./plots/manuscript/drug_mut_heatmap.png", width = 13, height = 9.5, units = "in", res = 500)
@@
 ```{r fus_heatmaps, eval=FALSE}
-ht_ccle <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "-log10(p-value)",  legend_breaks = seq(0, 4, by = 1), row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Fusion Pairs", radius = 0.2)
+ht_ccle <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "-log10(p-value)",  legend_breaks = seq(0, 4, by = 1), row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Fusion Pairs", radius = 0.1)
 png(filename = "./plots/manuscript/ccle_fus_heatmap.png", width = 5, height = 3, units = "in", res = 500)
@@
 
-ht_ctrp <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "-log10(p-value)", legend_breaks = seq(0, 10, by = 2), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Fusion Pairs", radius = 0.2)
+ht_ctrp <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "-log10(p-value)", legend_breaks = seq(0, 10, by = 2), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Fusion Pairs", radius = 0.1)
 png(filename = "./plots/manuscript/ctrp_fus_heatmap.png", width = 13, height = 3, units = "in", res = 500)
@@
 
-ht_gdsc <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "-log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Fusion Pairs", radius = 0.2)
+ht_gdsc <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "-log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Fusion Pairs", radius = 0.1)
 png(filename = "./plots/manuscript/gdsc_fus_heatmap.png", width = 9, height = 3, units = "in", res = 500)
@@
 
-ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "CCLE -log10(p-value)                                                                               ", legend_breaks = seq(0, 4, by = 1), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Fusion Pairs", radius = 0.2)
-ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "CTRP -log10(p-value)                                                                              ", legend_breaks = seq(0, 10, by = 2), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Fusion Pairs", radius = 0.2)
-ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Fusion Pairs", radius = 0.2)
+ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "CCLE -log10(p-value)                                                                               ", legend_breaks = seq(0, 4, by = 1), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Fusion Pairs", radius = 0.1)
+ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "CTRP -log10(p-value)                                                                              ", legend_breaks = seq(0, 10, by = 2), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Fusion Pairs", radius = 0.1)
+ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Fusion Pairs", radius = 0.1)
 png(filename = "./plots/manuscript/drug_fus_heatmap.png", width = 13, height = 2.4, units = "in", res = 500)
@@
 ```{r load_drug_spear}
+g2p_amp_4merge <- select(g2p_amp, Drug_Gene, Direction_Curated)
 cn_cor <- readRDS("./data_munging/rds/drug_cn_cor.rds")
+cn_cor <- merge(cn_cor, g2p_amp_4merge, by = "Drug_Gene", all.x = TRUE)
+
+g2p_expr_4merge <- select(g2p_expr, Drug_Gene, Direction_Curated)
 ge_cor <- readRDS("./data_munging/rds/drug_ge_cor.rds")
+ge_cor <- merge(ge_cor, g2p_expr_4merge, by = "Drug_Gene", all.x = TRUE)
 ```
@@
 
-  annot_grid <- dcast(drug_cor_res, Gene ~ Drug, value.var = "InG2P", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
+  annot_grid <- dcast(drug_cor_res, Gene ~ Drug, value.var = "Direction_Curated", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
   annot_grid <- annot_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
   annot_grid <- annot_grid[complete.cases(annot_grid), ]
-  annot_grid[annot_grid == "No"] <- ""
-  annot_grid[annot_grid == "Yes"] <- "G"
-
-  col_fun <- colorRamp2(color_range, c("red3", "white", "green4"))
+  # annot_grid[annot_grid == "No"] <- ""
+  # annot_grid[annot_grid == "Yes"] <- "G"
+
+  col_fun <- colorRamp2(color_range, c("red3", "white", "blue3"))
 
@@
                 cell_fun = function(j, i, x, y, width, height, fill) {
-                  grid.text(signif_grid[i, j], x, y, gp = gpar(fontsize = 20))
-                  if(annot_grid[i, j] == "G") {
-                    grid.circle(x = x, y = y, r = radius, gp = gpar(fill = "transparent", col = "black"))
+                  grid.text(signif_grid[i, j], x = x - width*0.20, y = y, gp = gpar(fontsize = 18))
+                  if(annot_grid[i, j] == "sensitivity") {
+                    grid.circle(x = x - width*0.20, y = y - height*0.20, r = height*0.15, default.units = "npc", gp = gpar(fill = "white", col = "black"))
+                    # grid.circle(x = x, y = y, r = radius, gp = gpar(fill = "transparent", col = "black"))
+                  }
+                  if(annot_grid[i, j] == "resistance") {
+                    grid.circle(x = x - width*0.20, y = y - height*0.20, r = height*0.15, default.units = "npc", gp = gpar(fill = "black", col = "black"))
+                    # grid.text("☐", x, y, just = c(0.5, 0.425), gp = gpar(fontsize = 23, fontface = "bold"))
                   }
@@
 
-ccle_cn_ht2 <- MakeCorrHeatmap(drug_cor_res = ccle_cn_cor, row_names = TRUE, col_title = "CCLE", color_range = c(-0.2, 0, 0.2), radius = 0.1, legend_title = "Copy num.
+ccle_cn_ht2 <- MakeCorrHeatmap(drug_cor_res = ccle_cn_cor, row_names = TRUE, col_title = "CCLE", color_range = c(-0.2, 0, 0.2), radius = 0.025, legend_title = "Copy num.
 Spearman correlation", metric = "CN")
-ctrp_cn_ht2 <- MakeCorrHeatmap(drug_cor_res = ctrp_cn_cor, row_names = FALSE, col_title = "CTRP", color_range = c(-0.2, 0, 0.2), radius = 0.1, legend_title = "Copy num.
+ctrp_cn_ht2 <- MakeCorrHeatmap(drug_cor_res = ctrp_cn_cor, row_names = FALSE, col_title = "CTRP", color_range = c(-0.2, 0, 0.2), radius = 0.025, legend_title = "Copy num.
 Spearman correlation", metric = "CN")
-gdsc_cn_ht2 <- MakeCorrHeatmap(drug_cor_res = gdsc_cn_cor, row_names = FALSE, col_title = "GDSC", color_range = c(-0.2, 0, 0.2), radius = 0.1, legend_title = "Copy num.
+gdsc_cn_ht2 <- MakeCorrHeatmap(drug_cor_res = gdsc_cn_cor, row_names = FALSE, col_title = "GDSC", color_range = c(-0.2, 0, 0.2), radius = 0.025, legend_title = "Copy num.
 Spearman correlation", metric = "CN")

### 2019-06-04 19Q2.Rmd

@@
 biomarker_type_curated <- 
-  ifelse(!is.na(str_match(string = tolower(g2p$biomarker_type), pattern = "copy number variant|amplification")) | !is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "copy number variant|amplification")), "Amplification/CNV",
-  ifelse(!is.na(str_match(string = toupper(g2p$Feature.Names), pattern = "[A-Z0-9|A-Z]+-[A-Z0-9|A-Z]+|FUSION")) & is.na(str_match(string = g2p$Feature.Names, pattern = "[0-9]+-[0-9]+")) | g2p$biomarker_type == "fusion" | g2p$biomarker_type == "rearrange", "Fusion",
-  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "[A-Z][0-9]+([A-Z]|[*])|[0-9A-Z]+ [A-Z][0-9]+|[A-Z][0-9]+$")), "Mutation",
-  ifelse(!is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "expression|methylation")), "Expression",
-  ifelse(!is.na(str_match(string = g2p$biomarker_type, pattern = "intron|insertion|deletion|mutant")), "Mutation",
-  ifelse(!is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "codon|positive|biallelic inactivation|del|ins|dup|mut|frameshift|missense|variant|[0-9]+fs|>")), "Mutation",
-  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "^KIT$|^BRCA$")), "Mutation", NA)))))))
+  ifelse(!is.na(str_match(string = tolower(g2p$biomarker_type), pattern = "copy number variant|amplification")[,1]) | !is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "copy number variant|amplification")), "Amplification/CNV",
+  ifelse(!is.na(str_match(string = toupper(g2p$Feature.Names), pattern = "[A-Z0-9|A-Z]+-[A-Z0-9|A-Z]+|FUSION")[,1]) & is.na(str_match(string = g2p$Feature.Names, pattern = "[0-9]+-[0-9]+")) | g2p$biomarker_type == "fusion" | g2p$biomarker_type == "rearrange", "Fusion",
+  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "[A-Z][0-9]+([A-Z]|[*])|[0-9A-Z]+ [A-Z][0-9]+|[A-Z][0-9]+$")[,1]), "Mutation",
+  ifelse(!is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "expression|methylation")[,1]), "Expression",
+  ifelse(!is.na(str_match(string = g2p$biomarker_type, pattern = "intron|insertion|deletion|mutant")[,1]), "Mutation",
+  ifelse(!is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "codon|positive|biallelic inactivation|del|ins|dup|mut|frameshift|missense|variant|[0-9]+fs|>")[,1]), "Mutation",
+  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "^KIT$|^BRCA$")[,1]), "Mutation", NA)))))))
 g2p$biomarker_type_curated <- biomarker_type_curated[,1]
@@
 g2p <- add_column(g2p, Direction_Curated = NA, .after = "Direction")
-g2p$Direction_Curated <- ifelse(!is.na(str_match(string = tolower(g2p$Direction), pattern = "resist")), "resistance", ifelse(!is.na(str_match(string = tolower(g2p$Direction), pattern = "sensitive|sensitivity|responsive")), "sensitivity", "none"))
+g2p$Direction_Curated <- ifelse(!is.na(str_match(string = tolower(g2p$Direction), pattern = "resist")[,1]), "resistance", ifelse(!is.na(str_match(string = tolower(g2p$Direction), pattern = "sensitive|sensitivity|responsive")[,1]), "sensitivity", "none"))
 
@@
 maf_raw <- unfactorize(maf_raw)
-# Select columns
+
+# Select columns for maf_changes_df
+maf_changes <- select(maf_raw, Gene, DepMap_ID, Protein_Change) %>% drop_na(Protein_Change) %>% filter(Protein_Change != "" & Gene %in% g2p_genes)
+maf_changes <- unique(maf_changes)
+maf_changes$Protein_Change <- gsub(pattern = "^p.", replacement = "", x = maf_changes$Protein_Change)
+maf_changes$Keep <- ifelse(!is.na(str_match(string = maf_changes$Protein_Change, pattern = "[A-Z][0-9]+([A-Z]|[*])")[,1]), "Yes", "No")
+maf_changes_df <- filter(maf_changes, Keep == "Yes")
+maf_changes_df$Keep <- NULL
+maf_changes_df$Gene_Protein_Change <- with(maf_changes_df, paste0(Gene, ":", Protein_Change))
+saveRDS(maf_changes_df, "./data_munging/19Q2/maf_changes_df_19Q2.rds", compress = "xz")
+
+# Select columns for maf_df
 maf <- subset(maf_raw, select = c("Gene", "DepMap_ID"))
@@
 maf_df[is.na(maf_df)] <- 0
-
 saveRDS(maf_df, "./data_munging/19Q2/maf_df_19Q2.rds", compress = "xz")
-```
-
-```{r}
-cgi <- read.delim("./../../../Desktop/cgi_biomarkers_latest/cgi_biomarkers_per_variant.tsv", sep = "\t", header = TRUE)
 ```
@@
 ```{r omics_functions}
-MergeOmicsG2P <- function(database, maf_df, ge_df, cn_df, gene_list, outfile) {
+MergeOmicsG2P <- function(database, dataframe, maf_df, ge_df, cn_df, gene_list, outfile) {
   # Merge mutation status, CN, and GE omics data with drugscreen results and metadata
   if(database %in% c("CCLE", "CTRP", "GDSC")) {
-    filt <- auc %>% filter(Database == database) %>% select(Cell_line, CCLE_histology, TCGA_classification, CCLE_name, DepMap_ID, Drug, AUC_IC50)
     print(paste0("Processing ", database, " data."))
-    colnames(filt)[colnames(filt) == "AUC_IC50"] <- "Score"
-
-    grid <- expand.grid("Cell_line" = unique(filt$Cell_line), "Gene" = gene_list)
-    data <-  merge(filt, grid, by = "Cell_line", all.y = TRUE)
+
+    grid <- expand.grid("Cell_line" = unique(dataframe$Cell_line), "Gene" = gene_list)
+    data <-  merge(dataframe, grid, by = "Cell_line", all.y = TRUE)
     print("Merged grid.")
@@
     # Melt CRISPR dataset for merging
-    data <- melt(crispr_all, id.vars = "DepMap_ID", measure.vars = colnames(crispr_all)[2:ncol(crispr_all)], variable.name = "Gene", value.name = "Score")
+    data <- melt(dataframe, id.vars = "DepMap_ID", measure.vars = colnames(crispr_all)[2:ncol(crispr_all)], variable.name = "Gene", value.name = "Score")
     # Merge cell line metadata
@@
 
-`r nrow(filter(test, n != 1))`/`r nrow(test)` gene-cell line combinations have more than one mutation in the MAF file. This is corrected in the point mutation filtering done below.
-```{r merge_drug_data, eval=FALSE}
-# Load in Pozdeyev et al. (2016) data
+```{r adjust_drugscreen_data, eval=FALSE}
 ccle_all <- read.delim("./../htscreens_giant_files/pozdeyev_data/CCLE_drug_response_metrics.csv.gz", sep = ",")
@@
 
-auc <- bind_rows(ccle_all, ctrp_all, gdsc_all)
-
-# Harmonize Pozdeyev cell line names with DepMap
+auc <- bind_rows(ccle_all, ctrp_all, gdsc_all) %>% drop_na(Drug_name)
 auc$Drug <- tolower(auc$Drug_name)
@@
 auc <- merge(ccl_histologies, auc, by = "Cell_line", all.y = TRUE)
-
-ccle <- MergeOmicsG2P(database = "CCLE", maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./data_munging/19Q2/ccle_data_19Q2.rds")
+colnames(auc)[colnames(auc) == "AUC_IC50"] <- "Score"
+saveRDS(auc, "./../htscreens_giant_files/pozdeyev_data/pozdeyev2016_auc_all.rds", compress = "xz")
+
+ccle_all <- auc %>% filter(Database == "CCLE") %>% select(Cell_line, CCLE_histology, TCGA_classification, CCLE_name, DepMap_ID, Drug, Score)
+saveRDS(ccle_all, "./../htscreens_giant_files/pozdeyev_data/pozdeyev2016_ccle_all_edited.rds", compress = "xz")
+ctrp_all <- auc %>% filter(Database == "CTRP") %>% select(Cell_line, CCLE_histology, TCGA_classification, CCLE_name, DepMap_ID, Drug, Score)
+saveRDS(ctrp_all, "./../htscreens_giant_files/pozdeyev_data/pozdeyev2016_ctrp_all_edited.rds", compress = "xz")
+gdsc_all <- auc %>% filter(Database == "GDSC") %>% select(Cell_line, CCLE_histology, TCGA_classification, CCLE_name, DepMap_ID, Drug, Score)
+saveRDS(gdsc_all, "./../htscreens_giant_files/pozdeyev_data/pozdeyev2016_gdsc_all_edited.rds", compress = "xz")
+```
+
+`r nrow(filter(test, n != 1))`/`r nrow(test)` gene-cell line combinations have more than one mutation in the MAF file. This is corrected in the point mutation filtering done below.
+```{r merge_drug_data, eval=FALSE}
+ccle_all <- readRDS("./../htscreens_giant_files/pozdeyev_data/pozdeyev2016_ccle_all_edited.rds")
+ctrp_all <- readRDS("./../htscreens_giant_files/pozdeyev_data/pozdeyev2016_ctrp_all_edited.rds")
+gdsc_all <- readRDS("./../htscreens_giant_files/pozdeyev_data/pozdeyev2016_gdsc_all_edited.rds")
+
+ccle <- MergeOmicsG2P(database = "CCLE", dataframe = ccle_all, maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./data_munging/19Q2/ccle_data_19Q2.rds")
 write.csv.gz(ccle %>% drop_na(Score), "./data_munging/19Q2/ccle_data_19Q2.csv.gz")
 
-ctrp <- MergeOmicsG2P(database = "CTRP", maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./../htscreens_giant_files/ctrp_data_19Q2.rds")
+ctrp <- MergeOmicsG2P(database = "CTRP", dataframe = ctrp_all, maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./../htscreens_giant_files/ctrp_data_19Q2.rds")
 write.csv.gz(ctrp %>% drop_na(Score), "./../htscreens_giant_files/ctrp_data_19Q2.csv.gz")
 
-gdsc <- MergeOmicsG2P(database = "GDSC", maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./data_munging/19Q2/gdsc_data_19Q2.rds")
+gdsc <- MergeOmicsG2P(database = "GDSC", dataframe = gdsc_all, maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./data_munging/19Q2/gdsc_data_19Q2.rds")
 write.csv.gz(gdsc %>% drop_na(Score), "./../htscreens_giant_files/gdsc_data_19Q2.csv.gz")
@@
 # all_genes <- intersect(unique(maf_df$Gene), intersect(unique(cn_melt$Gene), unique(ge_melt$Gene)))
-# ccle <- MergeOmicsG2P(database = "CCLE", maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = all_genes, outfile = "./../htscreens_giant_files/ccle_data_19Q2.rds")
-# ctrp <- MergeOmicsG2P(database = "CTRP", maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = all_genes, outfile = "./../htscreens_giant_files/ctrp_data_19Q2.rds")
-# gdsc <- MergeOmicsG2P(database = "GDSC", maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = all_genes, outfile = "./../htscreens_giant_files/gdsc_data_19Q2.rds")
+# ccle <- MergeOmicsG2P(database = "CCLE", maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = all_genes, outfile = "./../htscreens_giant_files/ccle_data_allgenes_19Q2.rds")
+# ctrp <- MergeOmicsG2P(database = "CTRP", maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = all_genes, outfile = "./../htscreens_giant_files/ctrp_data_allgenes_19Q2.rds")
+# gdsc <- MergeOmicsG2P(database = "GDSC", maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = all_genes, outfile = "./../htscreens_giant_files/gdsc_data_allgenes_19Q2.rds")
 ```
@@
 Merge fusions:
-```{r, eval=FALSE}
-ccle_all <- read.delim("./../htscreens_giant_files/pozdeyev_data/CCLE_drug_response_metrics.csv.gz", sep = ",")
-ctrp_all <- read.delim("./../htscreens_giant_files/pozdeyev_data/CTRP_drug_response_metrics.csv.gz", sep = ",")
-gdsc_all <- read.delim("./../htscreens_giant_files/pozdeyev_data/GDSC_drug_response_metrics.csv.gz", sep = ",")
-
-auc <- bind_rows(ccle_all, ctrp_all, gdsc_all) %>% drop_na(Drug_name)
-
-# Harmonize Pozdeyev cell line names with DepMap
-auc$Drug <- tolower(auc$Drug_name)
-auc$Cell_line <- toupper(gsub("-", "", auc$Cell_line))
-auc$Cell_line <- ifelse(auc$Cell_line == "K052", "KO52", auc$Cell_line)
-auc$Cell_line <- ifelse(auc$Cell_line == "OVCAR3", "NIHOVCAR3", auc$Cell_line)
-auc$Cell_line <- ifelse(auc$Cell_line == "OVCAR3", "NIHOVCAR3", auc$Cell_line)
-auc$Cell_line <- ifelse(auc$Cell_line == "TI73", "T173", auc$Cell_line)
-auc <- merge(ccl_histologies, auc, by = "Cell_line", all.y = TRUE)
-
+```{r merge_fusions, eval=FALSE}
+ccle_all <- readRDS("./../htscreens_giant_files/pozdeyev_data/pozdeyev2016_ccle_all_edited.rds")
+ctrp_all <- readRDS("./../htscreens_giant_files/pozdeyev_data/pozdeyev2016_ctrp_all_edited.rds")
+gdsc_all <- readRDS("./../htscreens_giant_files/pozdeyev_data/pozdeyev2016_gdsc_all_edited.rds")
 fusions_filt <- filter(fusions, FusionPair %in% unique(as.character(g2p_fus$FusionPair)))
 
-ccle_fus <- auc %>% filter(Database == "CCLE") %>% select(Cell_line, CCLE_histology, TCGA_classification, CCLE_name, DepMap_ID, Drug, AUC_IC50)
-ccle_fus_grid <- expand.grid("DepMap_ID" = unique(ccle_fus$DepMap_ID), "FusionPair" = unique(fusions_filt$FusionPair))
-ccle_fus <- merge(merge(ccle_fus, ccle_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "CCLE_name", "CCLE_histology", "Cell_line", "FusionPair"), all = TRUE)
+ccle_fus_grid <- expand.grid("DepMap_ID" = unique(ccle_all$DepMap_ID), "FusionPair" = unique(fusions_filt$FusionPair))
+ccle_fus <- merge(merge(ccle_all, ccle_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "CCLE_name", "CCLE_histology", "Cell_line", "FusionPair"), all = TRUE)
 ccle_fus$Fusion_Status <- ifelse(!is.na(ccle_fus$LeftGene), "Yes", "No")
@@
 
-ctrp_fus <- auc %>% filter(Database == "CTRP") %>% select(Cell_line, CCLE_histology, TCGA_classification, CCLE_name, DepMap_ID, Drug, AUC_IC50)
-ctrp_fus_grid <- expand.grid("DepMap_ID" = unique(ctrp_fus$DepMap_ID), "FusionPair" = unique(fusions_filt$FusionPair))
-ctrp_fus <- merge(merge(ctrp_fus, ctrp_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "CCLE_name", "CCLE_histology", "Cell_line", "FusionPair"), all = TRUE)
+ctrp_fus_grid <- expand.grid("DepMap_ID" = unique(ctrp_all$DepMap_ID), "FusionPair" = unique(fusions_filt$FusionPair))
+ctrp_fus <- merge(merge(ctrp_all, ctrp_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "CCLE_name", "CCLE_histology", "Cell_line", "FusionPair"), all = TRUE)
 ctrp_fus$Fusion_Status <- ifelse(!is.na(ctrp_fus$LeftGene), "Yes", "No")
@@
 
-gdsc_fus <- auc %>% filter(Database == "GDSC") %>% select(Cell_line, CCLE_histology, TCGA_classification, CCLE_name, DepMap_ID, Drug, AUC_IC50)
-gdsc_fus_grid <- expand.grid("DepMap_ID" = unique(gdsc_fus$DepMap_ID), "FusionPair" = unique(fusions_filt$FusionPair))
-gdsc_fus <- merge(merge(gdsc_fus, gdsc_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "CCLE_name", "CCLE_histology", "Cell_line", "FusionPair"), all = TRUE)
+gdsc_fus_grid <- expand.grid("DepMap_ID" = unique(gdsc_all$DepMap_ID), "FusionPair" = unique(fusions_filt$FusionPair))
+gdsc_fus <- merge(merge(gdsc_all, gdsc_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "CCLE_name", "CCLE_histology", "Cell_line", "FusionPair"), all = TRUE)
 gdsc_fus$Fusion_Status <- ifelse(!is.na(gdsc_fus$LeftGene), "Yes", "No")
@@
 
-```{r}
+```{r load_fusion_data}
 fus <- readRDS("./data_munging/rds/fusions_merged.rds") %>% drop_na(Drug)
 fus_summary <- fus %>% count(Database, Drug, FusionPair, Fusion_Status)
+
+```
+
+Merge protein changes: **NEED TO MAKE G2P_prot DATAFRAME (6/4/19)**
+```{r merge_protein_changes, eval=FALSE}
+ccle_all <- readRDS("./../htscreens_giant_files/pozdeyev_data/pozdeyev2016_ccle_all_edited.rds")
+ctrp_all <- readRDS("./../htscreens_giant_files/pozdeyev_data/pozdeyev2016_ctrp_all_edited.rds")
+gdsc_all <- readRDS("./../htscreens_giant_files/pozdeyev_data/pozdeyev2016_gdsc_all_edited.rds")
+maf_changes_df <- readRDS("./data_munging/19Q2/maf_changes_df_19Q2.rds")
+
+ccle_prot_grid <- expand.grid("DepMap_ID" = unique(ccle_all$DepMap_ID), "Protein_Change" = unique(maf_changes_df$Protein_Change))
+ccle_prot <- merge(merge(ccle_all, ccle_prot_grid, by = "DepMap_ID", all = TRUE), maf_changes_df, by = c("DepMap_ID", "CCLE_name", "CCLE_histology", "Cell_line", "Protein_Change"), all = TRUE)
+ccle_prot$Protein_Change_Status <- ifelse(!is.na(ccle_prot$Protein_Change), "Yes", "No")
+ccle_prot$Drug_Protein_Change <- ifelse(is.na(ccle_prot$Drug) | is.na(ccle_prot$Protein_Change), NA, paste0(ccle_prot$Drug, "_", ccle_prot$Protein_Change))
+# ccle_prot$G2P_Drug_Protein_Change <- ifelse(ccle_prot$Drug_Protein_Change %in% unique(as.character(g2p_prot$Drug_Protein_Change)), "Yes", "No")
+# ccle_prot$G2P_Protein_Change <- ifelse(ccle_prot$Protein_Change %in% unique(as.character(g2p_prot$Protein_Change)), "Yes", "No")
+ccle_prot$Database <- "CCLE"
+
 ```
@@
 
-crispr <- MergeOmicsG2P(database = "CRISPR", maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./data_munging/19Q2/crispr_data_19Q2.rds")
+crispr <- MergeOmicsG2P(database = "CRISPR", dataframe = crispr_all, maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./data_munging/19Q2/crispr_data_19Q2.rds")
 write.csv.gz(crispr %>% drop_na(Score), "./../htscreens_giant_files/crispr_data_19Q2.csv.gz")
@@
     # Filter out DGLs with too few samples in at least one mutation status category
+    # Require at least 3 samples in each category to run the test, else filter out that DGL from testing df
     count_mut_n <- dataframe %>% count(Drug_Gene_Lin, Mutation) %>% filter(n >= 3)
@@
     # Filter out fusions with too few samples in at least one category
+    # Require at least 3 samples in each category to run the test, else filter out that Drug_FusionPair from testing df
     count_n <- dataframe %>% count(Drug, FusionPair, Drug_FusionPair, Fusion_Status) %>% filter(n >= 3)
@@
   if("Drug_Gene" %in% grouping) {
+    # Filter out DGs with too few samples in at least one mutation status category
+    # Require at least 3 samples in each category to run the test, else filter out that DG from testing df
+    count_mut_n <- dataframe %>% count(Drug_Gene, Mutation) %>% filter(n >= 3)
+    count_mut_category <- count_mut_n %>% count(Drug_Gene) %>% filter(n == 2)
+    dgl_keep <- intersect(count_mut_n$Drug_Gene, count_mut_category$Drug_Gene)
+    dataframe <- filter(dataframe, Drug_Gene %in% dgl_keep)
+    dataframe$Drug_Gene <- as.character(dataframe$Drug_Gene)
     signif <- compare_means(Score ~ Mutation, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
@@
 ## Heatmaps
-
-```{r wilcoxon_heatmap_function_EDIT, eval=FALSE}
-MakeWilcoxonHeatmap <- function(signif_df, feature, row_names, col_title, color, legend_title, legend_breaks, row_title_txt, radius) {
-  if(!is.na(str_match(string = tolower(feature), pattern = "mut"))) {
-    signif_grid <- dcast(signif_df, Gene ~ Drug, value.var = "p_log10", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
-    signif_grid <- signif_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
-    signif_grid <- signif_grid[complete.cases(signif_grid), ]
-    signif_grid[signif_grid < -log10(0.05)] <- NA
-
-    signif_grid_annot <- dcast(signif_df, Gene ~ Drug, value.var = "Direction_Curated", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
-    signif_grid_annot <- signif_grid_annot[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
-    signif_grid_annot <- signif_grid_annot[complete.cases(signif_grid_annot), ]
-    # signif_grid_annot[signif_grid_annot == "No"] <- ""
-    # signif_grid_annot[signif_grid_annot == "Yes"] <- "O"
-  }
-  if(!is.na(str_match(string = tolower(feature), pattern = "fus"))) {
-    signif_grid <- dcast(signif_df, FusionPair ~ Drug, value.var = "p_log10", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-FusionPair)
-    signif_grid <- signif_grid[, intersect(g2p_drug_order, colnames(signif_grid))]
-    signif_grid <- signif_grid[complete.cases(signif_grid), ]
-    signif_grid[signif_grid < -log10(0.05)] <- NA
-
-    signif_grid_annot <- dcast(signif_df, FusionPair ~ Drug, value.var = "Direction_Curated", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-FusionPair)
-    signif_grid_annot <- signif_grid_annot[, intersect(g2p_drug_order, colnames(signif_grid))]
-    signif_grid_annot <- signif_grid_annot[complete.cases(signif_grid_annot), ]
-    # signif_grid_annot[signif_grid_annot == "No"] <- ""
-    # signif_grid_annot[signif_grid_annot == "Yes"] <- "O"
-  }
-  col_fun <- colorRamp2(c(legend_breaks[1], legend_breaks[length(legend_breaks)]), c("gray97", color))
-  # Legend properties list
-  ht_legend_list <- list(title = legend_title, title_position = "topleft", legend_direction = "horizontal", legend_width = unit(2, "in"), border = "gray70", at = legend_breaks, labels = legend_breaks)
-  ht <- Heatmap(signif_grid,
-                col = col_fun,
-                na_col = "gray97",
-                rect_gp = gpar(col = "gray70"),
-                heatmap_legend_param = ht_legend_list,
-                cluster_rows = FALSE, 
-                cluster_columns = FALSE, 
-                show_row_names = as.logical(row_names),
-                row_names_side = "left",
-                row_names_gp = gpar(fontsize = 10),
-                column_names_side = "bottom",
-                column_names_gp = gpar(fontsize = 10),
-                show_column_names = FALSE,
-                bottom_annotation = HeatmapAnnotation(
-                  text = anno_text(colnames(signif_grid),
-                                   rot = 45,
-                                   gp = gpar(fontsize = 11),
-                                   offset = unit(1, "npc"),
-                                   just = "right"),
-                  annotation_height = unit(0.85, "in")),
-                  # annotation_height = max_text_width(colnames(signif_grid))),
-                row_title = row_title_txt,
-                row_title_gp = gpar(fontface = "bold", fontsize = 14),
-                column_title = col_title, 
-                column_title_gp = gpar(fontface = "bold", fontsize = 14),
-                column_title_side = "bottom",
-                cell_fun = function(j, i, x, y, width, height, fill) {
-                  # grid.text(signif_grid_annot[i, j], x, y, gp = gpar(fontsize = 20))
-                  if(signif_grid_annot[i, j] == "none") {
-                    grid.circle(x = x, y = y, r = radius, gp = gpar(fill = "transparent", col = "black"))
-                  }
-                  if(signif_grid_annot[i, j] == "sensitivity") {
-                    grid.polygon(x = c(0, 0.5, 1), y = c(0, 1, 0), default.units = "npc", gp = gpar(fill = "transparent", col = "black"))
-                  }
-                  if(signif_grid_annot[i, j] == "resistance") {
-                    grid.polygon(x = c(0.1, 0.1, 0.9, 0.9), y = c(0.1, 0.9, 0.9, 0.1), default.units = "npc", gp = gpar(fill = "transparent", col = "black"))
-                  }
-                }
-                )
-  return(ht)
-}
-```
 
@@
 
-```{r testing, eval=FALSE}
-grid.newpage()
-grid.polygon(x = c(0.1, 0.1, 0.9, 0.9), y = c(0.1, 0.9, 0.9, 0.1), default.units = "npc",
-             gp = gpar(), draw = TRUE, vp = NULL)
-
-signif_df <- filter(ccle_signif_fus, Drug %in% g2p_drugs)
-signif_grid <- dcast(signif_df, FusionPair ~ Drug, value.var = "p_log10", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-FusionPair)
-signif_grid <- signif_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
-signif_grid <- signif_grid[complete.cases(signif_grid), ]
-signif_grid[signif_grid < -log10(0.05)] <- NA
-signif_grid_annot <- dcast(signif_df, FusionPair ~ Drug, value.var = "Direction_Curated", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-FusionPair)
-signif_grid_annot <- signif_grid_annot[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
-signif_grid_annot <- signif_grid_annot[complete.cases(signif_grid_annot), ]
-```
-
 ```{r mut_heatmaps, eval=FALSE, fig.height=10, fig.width=3}

### 2019-06-05 19Q2.Rmd
update Rmd

@@
 g2p <- add_column(g2p, Direction_Curated = NA, .after = "Direction")
-g2p$Direction_Curated <- ifelse(!is.na(str_match(string = tolower(g2p$Direction), pattern = "resist")[,1]), "resistance", ifelse(!is.na(str_match(string = tolower(g2p$Direction), pattern = "sensitive|sensitivity|responsive")[,1]), "sensitivity", "none"))
+g2p$Direction_Curated <- ifelse(!is.na(str_match(string = tolower(g2p$Direction), pattern = "resist|adverse|unfavorable")[,1]), "resistance", ifelse(!is.na(str_match(string = tolower(g2p$Direction), pattern = "sensitive|sensitivity|responsive|better")[,1]), "sensitivity", "none"))
+
+# Edit mutation column
+g2p <- add_column(g2p, Mutation_Curated = NA, .after = "Mutation")
+g2p$Mutation_Curated <- gsub("u'|'| |,|\\[|\\]", "", g2p$Mutation)
+g2p$Mutation_Curated <- ifelse(g2p$Mutation_Curated == "", str_match(string = g2p$Feature.Names, pattern = "^[A-Z][0-9]+([A-Z]|[*])| [A-Z][0-9]+([A-Z]|[*])|:[A-Z][0-9]+([A-Z]|[*])")[,1], as.character(g2p$Mutation_Curated))
+g2p$Mutation_Curated <- gsub(":| |c\\..*", "", g2p$Mutation_Curated)
+g2p$Mutation_Curated <- ifelse(!is.na(str_match(string = tolower(g2p$Mutation_Curated), pattern = "exon|expression|frameshift|fusion|methylation|mutation")[,1]), NA, as.character(g2p$Mutation_Curated))
+g2p$Mutation_Curated <- gsub("^([0-9]+)([A-Z])$", "\\2\\1\\2", g2p$Mutation_Curated)
+g2p$Mutation_Curated <- gsub("^([A-Z])([0-9]+)$", "\\1\\2\\1", g2p$Mutation_Curated)
+g2p <- add_column(g2p, Gene_Protein_Change = NA, .after = "Mutation_Curated")
+g2p$Gene_Protein_Change <- ifelse(!is.na(g2p$Gene) & !is.na(g2p$Mutation_Curated), paste0(as.character(g2p$Gene), ":", as.character(g2p$Mutation_Curated)), NA)
 
@@
 maf_changes$Protein_Change <- gsub(pattern = "^p.", replacement = "", x = maf_changes$Protein_Change)
-maf_changes$Keep <- ifelse(!is.na(str_match(string = maf_changes$Protein_Change, pattern = "[A-Z][0-9]+([A-Z]|[*])")[,1]), "Yes", "No")
-maf_changes_df <- filter(maf_changes, Keep == "Yes")
-maf_changes_df$Keep <- NULL
-maf_changes_df$Gene_Protein_Change <- with(maf_changes_df, paste0(Gene, ":", Protein_Change))
-saveRDS(maf_changes_df, "./data_munging/19Q2/maf_changes_df_19Q2.rds", compress = "xz")
+maf_changes$Gene_Protein_Change <- with(maf_changes, paste0(Gene, ":", Protein_Change))
+saveRDS(maf_changes, "./data_munging/19Q2/maf_changes_df_19Q2.rds", compress = "xz")
 
@@
 maf_df <- readRDS("./data_munging/19Q2/maf_df_19Q2.rds")
+maf_changes_df <- readRDS("./data_munging/19Q2/maf_changes_df_19Q2.rds")
 cn_melt <- readRDS("./data_munging/19Q2/cn_melt_19Q2.rds")
 ge_melt <- readRDS("./data_munging/19Q2/ge_melt_19Q2.rds")
+```
+
+```{r}
+test <- filter(maf_changes_df, Gene_Protein_Change %in% unique(g2p_mut$Gene_Protein_Change))
 ```
@@
 g2p_mut_4merge <- unique(select(g2p_mut, Drug_Gene, Direction_Curated))
-g2p_mut_4merge$Direction_Numeric <- as.numeric(g2p_mut_4merge$Direction_Curated)
+test <- g2p_mut_4merge %>% filter(Direction_Curated != "none") %>% count(Drug_Gene) %>% filter(n == 2)
+extended_mut_ht_dg <- unique(as.character(test$Drug_Gene))
 
@@
 ccle_signif_g2p_dg <- readRDS("./data_munging/rds/ccle_signif_g2p_dg.rds")
-# ccle_signif_g2p_dg <- merge(ccle_signif_g2p_dg, g2p_mut_4merge, by = "Drug_Gene", all.x = TRUE)
-# ccle_signif_g2p_dg$Direction_Numeric <- ifelse(is.na(ccle_signif_g2p_dg$Direction_Numeric), 4, as.numeric(ccle_signif_g2p_dg$Direction_Numeric))
 ccle_signif_dgl <- readRDS("./data_munging/rds/ccle_signif_g2p_dgl.rds")
@@
 ctrp_signif_g2p_dg <- readRDS("./data_munging/rds/ctrp_signif_g2p_dg.rds")
-# ctrp_signif_g2p_dg <- merge(ctrp_signif_g2p_dg, g2p_mut_4merge, by = "Drug_Gene", all.x = TRUE)
 ctrp_signif_dgl <- readRDS("./data_munging/rds/ctrp_signif_g2p_dgl.rds")
@@
 gdsc_signif_g2p_dg <- readRDS("./data_munging/rds/gdsc_signif_g2p_dg.rds")
-# gdsc_signif_g2p_dg <- merge(gdsc_signif_g2p_dg, g2p_mut_4merge, by = "Drug_Gene", all.x = TRUE)
 gdsc_signif_dgl <- readRDS("./data_munging/rds/gdsc_signif_g2p_dgl.rds")

### 2019-06-10 19Q2.Rmd

@@
 # Edit mutation column
-g2p <- add_column(g2p, Mutation_Curated = NA, .after = "Mutation")
-g2p$Mutation_Curated <- gsub("u'|'| |,|\\[|\\]", "", g2p$Mutation)
-g2p$Mutation_Curated <- ifelse(g2p$Mutation_Curated == "", str_match(string = g2p$Feature.Names, pattern = "^[A-Z][0-9]+([A-Z]|[*])| [A-Z][0-9]+([A-Z]|[*])|:[A-Z][0-9]+([A-Z]|[*])")[,1], as.character(g2p$Mutation_Curated))
-g2p$Mutation_Curated <- gsub(":| |c\\..*", "", g2p$Mutation_Curated)
-g2p$Mutation_Curated <- ifelse(!is.na(str_match(string = tolower(g2p$Mutation_Curated), pattern = "exon|expression|frameshift|fusion|methylation|mutation")[,1]), NA, as.character(g2p$Mutation_Curated))
-g2p$Mutation_Curated <- gsub("^([0-9]+)([A-Z])$", "\\2\\1\\2", g2p$Mutation_Curated)
-g2p$Mutation_Curated <- gsub("^([A-Z])([0-9]+)$", "\\1\\2\\1", g2p$Mutation_Curated)
-g2p <- add_column(g2p, Gene_Protein_Change = NA, .after = "Mutation_Curated")
-g2p$Gene_Protein_Change <- ifelse(!is.na(g2p$Gene) & !is.na(g2p$Mutation_Curated), paste0(as.character(g2p$Gene), ":", as.character(g2p$Mutation_Curated)), NA)
+g2p <- add_column(g2p, Protein_Change = NA, .after = "Mutation")
+g2p$Protein_Change <- gsub("u'|'| |,|\\[|\\]", "", g2p$Mutation)
+g2p$Protein_Change <- ifelse(g2p$Protein_Change == "", str_match(string = g2p$Feature.Names, pattern = "^[A-Z][0-9]+([A-Z]|[*])| [A-Z][0-9]+([A-Z]|[*])|:[A-Z][0-9]+([A-Z]|[*])")[,1], as.character(g2p$Protein_Change))
+g2p$Protein_Change <- gsub(":| |c\\..*", "", g2p$Protein_Change)
+g2p$Protein_Change <- ifelse(!is.na(str_match(string = tolower(g2p$Protein_Change), pattern = "exon|expression|frameshift|fusion|methylation|mutation|-")[,1]), NA, as.character(g2p$Protein_Change))
+g2p$Protein_Change <- gsub("^([0-9]+)([A-Z])$", "\\2\\1\\2", g2p$Protein_Change)
+g2p$Protein_Change <- gsub("^([A-Z])([0-9]+)$", "\\1\\2\\1", g2p$Protein_Change)
+g2p <- add_column(g2p, Gene_Protein_Change = NA, .after = "Protein_Change")
+g2p$Gene_Protein_Change <- ifelse(!is.na(g2p$Gene) & !is.na(g2p$Protein_Change), paste0(as.character(g2p$Gene), ":", as.character(g2p$Protein_Change)), NA)
 
@@
 g2p_nodrug <- filter(g2p, is.na(Drug))
+g2p_prot <- unique(filter(g2p, !is.na(Gene_Protein_Change) & !is.na(Drug)) %>% select(group_general_lineage_name, Drug, Direction_Curated, Gene, Protein_Change, Gene_Protein_Change))
+g2p_prot$Drug_Gene_Protein_Change <- with(g2p_prot, paste0(Drug, "_", Gene_Protein_Change))
+g2p_prot$Drug_Gene_Protein_Change_Direction <- with(g2p_prot, paste0(Drug_Gene_Protein_Change, "_", Direction_Curated))
 ```
@@
 fus_summary <- fus %>% count(Database, Drug, FusionPair, Fusion_Status)
-
-```
-
-Merge protein changes: **NEED TO MAKE G2P_prot DATAFRAME (6/4/19)**
+```
+
+Merge protein changes
 ```{r merge_protein_changes, eval=FALSE}
@@
 maf_changes_df <- readRDS("./data_munging/19Q2/maf_changes_df_19Q2.rds")
-
-ccle_prot_grid <- expand.grid("DepMap_ID" = unique(ccle_all$DepMap_ID), "Protein_Change" = unique(maf_changes_df$Protein_Change))
-ccle_prot <- merge(merge(ccle_all, ccle_prot_grid, by = "DepMap_ID", all = TRUE), maf_changes_df, by = c("DepMap_ID", "CCLE_name", "CCLE_histology", "Cell_line", "Protein_Change"), all = TRUE)
-ccle_prot$Protein_Change_Status <- ifelse(!is.na(ccle_prot$Protein_Change), "Yes", "No")
-ccle_prot$Drug_Protein_Change <- ifelse(is.na(ccle_prot$Drug) | is.na(ccle_prot$Protein_Change), NA, paste0(ccle_prot$Drug, "_", ccle_prot$Protein_Change))
-# ccle_prot$G2P_Drug_Protein_Change <- ifelse(ccle_prot$Drug_Protein_Change %in% unique(as.character(g2p_prot$Drug_Protein_Change)), "Yes", "No")
-# ccle_prot$G2P_Protein_Change <- ifelse(ccle_prot$Protein_Change %in% unique(as.character(g2p_prot$Protein_Change)), "Yes", "No")
+maf_changes_filt <- filter(maf_changes_df, Gene_Protein_Change %in% unique(as.character(g2p_prot$Gene_Protein_Change)))
+
+# CCLE
+ccle_prot_grid <- expand.grid("DepMap_ID" = unique(ccle_all$DepMap_ID), "Gene_Protein_Change" = unique(maf_changes_filt$Gene_Protein_Change))
+ccle_prot <- merge(ccle_all, ccle_prot_grid, by = "DepMap_ID", all = TRUE)
+ccle_prot <- merge(ccle_prot, maf_changes_filt, by = c("DepMap_ID", "Gene_Protein_Change"), all = TRUE)
+ccle_prot$Change_Status <- ifelse(!is.na(ccle_prot$Protein_Change), "Yes", "No")
+ccle_prot$Drug_Gene_Protein_Change <- ifelse(is.na(ccle_prot$Drug) | is.na(ccle_prot$Gene_Protein_Change), NA, paste0(ccle_prot$Drug, "_", ccle_prot$Gene_Protein_Change))
+ccle_prot$G2P_Drug_Gene_Protein_Change <- ifelse(ccle_prot$Drug_Gene_Protein_Change %in% unique(as.character(g2p_prot$Drug_Gene_Protein_Change)), "Yes", "No")
+ccle_prot$G2P_Protein_Change <- ifelse(ccle_prot$Gene_Protein_Change %in% unique(as.character(g2p_prot$Gene_Protein_Change)), "Yes", "No")
+ccle_prot <- merge(ccle_prot, unique(select(g2p_prot, Drug_Gene_Protein_Change, Direction_Curated)), by = "Drug_Gene_Protein_Change", all.x = TRUE)
 ccle_prot$Database <- "CCLE"
-
+ccle_prot <- ccle_prot %>% drop_na(Drug)
+
+# CTRP
+ctrp_prot_grid <- expand.grid("DepMap_ID" = unique(ctrp_all$DepMap_ID), "Gene_Protein_Change" = unique(maf_changes_filt$Gene_Protein_Change))
+ctrp_prot <- merge(ctrp_all, ctrp_prot_grid, by = "DepMap_ID", all = TRUE)
+ctrp_prot <- merge(ctrp_prot, maf_changes_filt, by = c("DepMap_ID", "Gene_Protein_Change"), all = TRUE)
+ctrp_prot$Change_Status <- ifelse(!is.na(ctrp_prot$Protein_Change), "Yes", "No")
+ctrp_prot$Drug_Gene_Protein_Change <- ifelse(is.na(ctrp_prot$Drug) | is.na(ctrp_prot$Gene_Protein_Change), NA, paste0(ctrp_prot$Drug, "_", ctrp_prot$Gene_Protein_Change))
+ctrp_prot$G2P_Drug_Gene_Protein_Change <- ifelse(ctrp_prot$Drug_Gene_Protein_Change %in% unique(as.character(g2p_prot$Drug_Gene_Protein_Change)), "Yes", "No")
+ctrp_prot$G2P_Protein_Change <- ifelse(ctrp_prot$Gene_Protein_Change %in% unique(as.character(g2p_prot$Gene_Protein_Change)), "Yes", "No")
+ctrp_prot <- merge(ctrp_prot, unique(select(g2p_prot, Drug_Gene_Protein_Change, Direction_Curated)), by = "Drug_Gene_Protein_Change", all.x = TRUE)
+ctrp_prot$Database <- "CTRP"
+ctrp_prot <- ctrp_prot %>% drop_na(Drug)
+
+# GDSC
+gdsc_prot_grid <- expand.grid("DepMap_ID" = unique(gdsc_all$DepMap_ID), "Gene_Protein_Change" = unique(maf_changes_filt$Gene_Protein_Change))
+gdsc_prot <- merge(gdsc_all, gdsc_prot_grid, by = "DepMap_ID", all = TRUE)
+gdsc_prot <- merge(gdsc_prot, maf_changes_filt, by = c("DepMap_ID", "Gene_Protein_Change"), all = TRUE)
+gdsc_prot$Change_Status <- ifelse(!is.na(gdsc_prot$Protein_Change), "Yes", "No")
+gdsc_prot$Drug_Gene_Protein_Change <- ifelse(is.na(gdsc_prot$Drug) | is.na(gdsc_prot$Gene_Protein_Change), NA, paste0(gdsc_prot$Drug, "_", gdsc_prot$Gene_Protein_Change))
+gdsc_prot$G2P_Drug_Gene_Protein_Change <- ifelse(gdsc_prot$Drug_Gene_Protein_Change %in% unique(as.character(g2p_prot$Drug_Gene_Protein_Change)), "Yes", "No")
+gdsc_prot$G2P_Protein_Change <- ifelse(gdsc_prot$Gene_Protein_Change %in% unique(as.character(g2p_prot$Gene_Protein_Change)), "Yes", "No")
+gdsc_prot <- merge(gdsc_prot, unique(select(g2p_prot, Drug_Gene_Protein_Change, Direction_Curated)), by = "Drug_Gene_Protein_Change", all.x = TRUE)
+gdsc_prot$Database <- "GDSC"
+gdsc_prot <- gdsc_prot %>% drop_na(Drug)
+
+prot <- bind_rows(ccle_prot, ctrp_prot, gdsc_prot)
+saveRDS(prot, "./data_munging/rds/protein_changes_merged.rds")
+```
+
+```{r load_prot_data}
+prot <- readRDS("./data_munging/rds/protein_changes_merged.rds")
+prot_summary <- prot %>% count(Database, Drug, Gene_Protein_Change, Change_Status)
 ```
@@
   }
+  if("Gene_Protein_Change" %in% grouping) {
+    # Filter out Gene:Protein_Changes with too few samples in at least one category
+    # Require at least 3 samples in each category to run the test, else filter out that Gene_Protein_Change from testing df
+    count_n <- dataframe %>% count(Drug, Gene_Protein_Change, Drug_Gene_Protein_Change, Change_Status) %>% filter(n >= 3)
+    count_category <- count_n %>% count(Drug, Gene_Protein_Change, Drug_Gene_Protein_Change) %>% filter(n == 2)
+    keep <- intersect(count_n$Drug_Gene_Protein_Change, count_category$Drug_Gene_Protein_Change)
+    dataframe <- filter(dataframe, Drug_Gene_Protein_Change %in% keep)
+    dataframe$Drug_Gene_Protein_Change <- as.character(dataframe$Drug_Gene_Protein_Change)
+    signif <- compare_means(Score ~ Change_Status, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
+    signif <- adj_signif(signif, alpha = 0.05)
+    signif <- signif[order(signif$p),]
+    signif$InG2P <- ifelse(signif$Drug_Gene_Protein_Change %in% g2p_list, "Yes", "No")
+  }
   if("Drug_Gene" %in% grouping) {
@@
 gdsc_signif_dgl <- readRDS("./data_munging/rds/gdsc_signif_g2p_dgl.rds")
+```
+
+## Protein changes
+
+```{r protein_change_data}
+ccle_prot <- filter(prot, Database == "CCLE")
+ccle_prot <- unfactorize(ccle_prot)
+
+ctrp_prot <- filter(prot, Database == "CTRP")
+ctrp_prot <- unfactorize(ctrp_prot)
+
+gdsc_prot <- filter(prot, Drug %in% g2p_drugs & Database == "GDSC")
+gdsc_prot <- unfactorize(gdsc_prot)
+```
+
+```{r prot_wilcoxon_tests, eval=FALSE}
+ccle_prot <- unfactorize(ccle_prot)
+ccle_signif_prot <- WilcoxonTestDF(dataframe = ccle_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change[!is.na(g2p_prot$Drug_Gene_Protein_Change)])), outfile = "./data_munging/rds/ccle_signif_protein_changes.rds")
+
+ctrp_prot <- unfactorize(ctrp_prot)
+ctrp_signif_prot <- WilcoxonTestDF(dataframe = ctrp_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change[!is.na(g2p_prot$Drug_Gene_Protein_Change)])), outfile = "./data_munging/rds/ctrp_signif_protein_changes.rds")
+
+gdsc_prot <- unfactorize(gdsc_prot)
+gdsc_signif_prot <- WilcoxonTestDF(dataframe = gdsc_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change[!is.na(g2p_prot$Drug_Gene_Protein_Change)])), outfile = "./data_munging/rds/gdsc_signif_protein_changes.rds")
+```
+
+```{r load_prot_wilcoxon_rds}
+ccle_signif_prot <- readRDS("./data_munging/rds/ccle_signif_protein_changes.rds")
+ctrp_signif_prot <- readRDS("./data_munging/rds/ctrp_signif_protein_changes.rds")
+gdsc_signif_prot <- readRDS("./data_munging/rds/gdsc_signif_protein_changes.rds")
 ```
@@
     signif_grid_annot <- signif_grid_annot[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
+    signif_grid_annot <- signif_grid_annot[complete.cases(signif_grid_annot), ]
+    signif_grid_annot[signif_grid_annot == "No"] <- ""
+    signif_grid_annot[signif_grid_annot == "Yes"] <- "O"
+  }
+  if(!is.na(str_match(string = tolower(feature), pattern = "prot"))) {
+    signif_grid <- dcast(signif_df, Gene_Protein_Change ~ Drug, value.var = "p_log10", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene_Protein_Change)
+    signif_grid <- signif_grid[, intersect(g2p_drug_order, colnames(signif_grid))]
+    signif_grid <- signif_grid[complete.cases(signif_grid), ]
+    signif_grid[signif_grid < -log10(0.05)] <- NA
+
+    signif_grid_annot <- dcast(signif_df, Gene_Protein_Change ~ Drug, value.var = "InG2P", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene_Protein_Change)
+    signif_grid_annot <- signif_grid_annot[, intersect(g2p_drug_order, colnames(signif_grid))]
     signif_grid_annot <- signif_grid_annot[complete.cases(signif_grid_annot), ]
@@
 
+```{r prot_heatmaps, eval=FALSE, fig.height=10, fig.width=3}
+ht_ccle <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 12, by = 3), row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Genes", radius = 0.03)
+png(filename = "./plots/manuscript/ccle_prot_heatmap.png", width = 3, height = 5.5, units = "in", res = 500)
+draw(ht_ccle, heatmap_legend_side = "top")
+dev.off()
+
+ht_ctrp <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 18, by = 3), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.008)
+png(filename = "./plots/manuscript/ctrp_prot_heatmap.png", width = 9.5, height = 5.5, units = "in", res = 500)
+draw(ht_ctrp, heatmap_legend_side = "top")
+dev.off()
+
+ht_gdsc <- MakeWilcoxonHeatmap(signif_df = gdsc_signif_prot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.015)
+png(filename = "./plots/manuscript/gdsc_prot_heatmap.png", width = 5, height = 5.5, units = "in", res = 500)
+draw(ht_gdsc, heatmap_legend_side = "top")
+dev.off()
+
+ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot, feature = "protein changes", legend_title = "CCLE -log10(p-value)                                                                     ", legend_breaks = seq(0, 12, by = 3), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Genes", radius = 0.03)
+ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot, feature = "protein changes", legend_title = "CTRP -log10(p-value)                                                                    ", legend_breaks = seq(0, 18, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.008)
+ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = gdsc_signif_prot, feature = "protein changes", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes", radius = 0.015)
+# png(filename = "./plots/manuscript/drug_mut_heatmap.png", width = 13, height = 9.5, units = "in", res = 500)
+# draw(ht_ccle2 + ht_ctrp2 + ht_gdsc2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
+# dev.off()
+```
+
 ```{r fus_heatmaps, eval=FALSE}

### 2019-06-11 19Q2.Rmd
test sensitivity/resistance annotations on prot HT

@@
 ccle_signif_prot <- readRDS("./data_munging/rds/ccle_signif_protein_changes.rds")
+ccle_signif_prot <- merge(ccle_signif_prot, unique(select(ccle_prot, Drug_Gene_Protein_Change, Direction_Curated)), by = "Drug_Gene_Protein_Change", all.x = TRUE)
+
 ctrp_signif_prot <- readRDS("./data_munging/rds/ctrp_signif_protein_changes.rds")
+ctrp_signif_prot <- merge(ctrp_signif_prot, unique(select(ctrp_prot, Drug_Gene_Protein_Change, Direction_Curated)), by = "Drug_Gene_Protein_Change", all.x = TRUE)
+
 gdsc_signif_prot <- readRDS("./data_munging/rds/gdsc_signif_protein_changes.rds")
+gdsc_signif_prot <- merge(gdsc_signif_prot, unique(select(gdsc_prot, Drug_Gene_Protein_Change, Direction_Curated)), by = "Drug_Gene_Protein_Change", all.x = TRUE)
 ```
@@
 
-ht_ctrp <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 18, by = 3), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.008)
+ht_ctrp <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 18, by = 3), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.015)
 png(filename = "./plots/manuscript/ctrp_prot_heatmap.png", width = 9.5, height = 5.5, units = "in", res = 500)
@@
 dev.off()
-
-ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot, feature = "protein changes", legend_title = "CCLE -log10(p-value)                                                                     ", legend_breaks = seq(0, 12, by = 3), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Genes", radius = 0.03)
-ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot, feature = "protein changes", legend_title = "CTRP -log10(p-value)                                                                    ", legend_breaks = seq(0, 18, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.008)
-ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = gdsc_signif_prot, feature = "protein changes", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes", radius = 0.015)
-# png(filename = "./plots/manuscript/drug_mut_heatmap.png", width = 13, height = 9.5, units = "in", res = 500)
-# draw(ht_ccle2 + ht_ctrp2 + ht_gdsc2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
-# dev.off()
 ```

### 2019-06-13 19Q2.Rmd
figure out failed CTRP protein change heatmap

@@
 
+```{r, eval=FALSE}
+ctrp_signif_prot <- readRDS("./data_munging/rds/ctrp_signif_protein_changes.rds")
+ctrp_signif_prot <- merge(ctrp_signif_prot, unique(select(ctrp_prot, Drug_Gene_Protein_Change, Direction_Curated)), by = "Drug_Gene_Protein_Change", all.x = TRUE)
+
+signif_df <- ctrp_signif_prot
+
+signif_grid <- dcast(signif_df, Gene_Protein_Change ~ Drug, value.var = "p_log10", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene_Protein_Change)
+signif_grid <- signif_grid[, intersect(g2p_drug_order, colnames(signif_grid))]
+signif_grid <- signif_grid[complete.cases(signif_grid), ]
+signif_grid[signif_grid < -log10(0.05)] <- NA
+
+signif_grid_annot <- dcast(signif_df, Gene_Protein_Change ~ Drug, value.var = "Direction_Curated", fill = 0)
+%>% `rownames<-`(.[,1]) %>% select(-Gene_Protein_Change)
+signif_grid_annot <- signif_grid_annot[, intersect(g2p_drug_order, colnames(signif_grid))]
+signif_grid_annot <- signif_grid_annot[complete.cases(signif_grid_annot), ]
+signif_grid_annot[signif_grid_annot == "No"] <- ""
+signif_grid_annot[signif_grid_annot == "Yes"] <- "O"
+
+test <- ctrp_signif_prot %>% count(Gene_Protein_Change, Drug)
+```
+
 ```{r prot_heatmaps, eval=FALSE, fig.height=10, fig.width=3}

### 2019-06-14 19Q2.Rmd
update Rmd

--- 2019-06-11 19Q2.Rmd
@@
 g2p <- add_column(g2p, Direction_Curated = NA, .after = "Direction")
-g2p$Direction_Curated <- ifelse(!is.na(str_match(string = tolower(g2p$Direction), pattern = "resist|adverse|unfavorable")[,1]), "resistance", ifelse(!is.na(str_match(string = tolower(g2p$Direction), pattern = "sensitive|sensitivity|responsive|better")[,1]), "sensitivity", "none"))
+g2p$Direction_Curated <- with(g2p, ifelse(!is.na(str_match(string = tolower(Direction), pattern = "adverse|unfavorable|^resistant")[,1]), "resistance",
+                         ifelse(!is.na(str_match(string = tolower(Direction), pattern = "confers resistance")[,1]), "resistance",
+                         ifelse(!is.na(str_match(string = tolower(Direction), pattern = "sensitive|sensitivity|responsive|better")[,1]), "sensitivity", 
+                         ifelse(is.na(Direction) & Drug == "gefitinib" & Feature.Names == "L858R" & Gene == "EGFR", "sensitivity",
+                         ifelse(is.na(Direction) & Drug == "trametinib" & Feature.Names == "V600E" & Gene == "BRAF", "sensitivity", NA))))))
 
@@
 
-# write.csv(g2p, "./data_munging/g2p_db_edited.csv")
+write.csv(g2p, "./data_munging/g2p_db_edited.csv")
 ```
@@
 
-# WILCOXON TESTS
+# WILCOXON: PanCan
 
@@
 ccle_prot <- unfactorize(ccle_prot)
+ccle_prot_count <- ccle_prot %>% count(Gene_Protein_Change, Drug, Change_Status)
 
@@
 ctrp_prot <- unfactorize(ctrp_prot)
+ctrp_prot_count <- ctrp_prot %>% count(Gene_Protein_Change, Drug, Change_Status)
 
@@
 gdsc_prot <- unfactorize(gdsc_prot)
+gdsc_prot_count <- gdsc_prot %>% count(Gene_Protein_Change, Drug, Change_Status)
 ```
@@
 
-```{r fusion_boxplots, fig.height=5, fig.width=12}
+```{r fusion_boxplots, fig.height=5, fig.width=12, eval=FALSE}
 # CCLE
@@
 
-    signif_grid_annot <- dcast(signif_df, Gene_Protein_Change ~ Drug, value.var = "InG2P", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene_Protein_Change)
+    signif_grid_annot <- dcast(signif_df, Gene_Protein_Change ~ Drug, value.var = "Direction_Curated", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene_Protein_Change)
     signif_grid_annot <- signif_grid_annot[, intersect(g2p_drug_order, colnames(signif_grid))]
     signif_grid_annot <- signif_grid_annot[complete.cases(signif_grid_annot), ]
-    signif_grid_annot[signif_grid_annot == "No"] <- ""
-    signif_grid_annot[signif_grid_annot == "Yes"] <- "O"
+    signif_grid_annot[signif_grid_annot == "resistance"] <- "X"
+    signif_grid_annot[signif_grid_annot == "sensitivity"] <- "O"
   }
@@
                   }
+                  if(signif_grid_annot[i, j] == "X") {
+                    grid.circle(x = x - width*0.20, y = y - height*0.20, r = radius, default.units = "npc", gp = gpar(fill = "black", col = "black"))
+                  }
                 }
@@
 ```{r prot_heatmaps, eval=FALSE, fig.height=10, fig.width=3}
-ht_ccle <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 12, by = 3), row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Genes", radius = 0.03)
+ht_ccle <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Gene:Protein Change", radius = 0.03)
 png(filename = "./plots/manuscript/ccle_prot_heatmap.png", width = 3, height = 5.5, units = "in", res = 500)
@@
 
-ht_ctrp <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 18, by = 3), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.015)
+ht_ctrp <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Gene:Protein Change", radius = 0.015)
 png(filename = "./plots/manuscript/ctrp_prot_heatmap.png", width = 9.5, height = 5.5, units = "in", res = 500)
@@
 
-ht_gdsc <- MakeWilcoxonHeatmap(signif_df = gdsc_signif_prot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.015)
+ht_gdsc <- MakeWilcoxonHeatmap(signif_df = gdsc_signif_prot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Gene:Protein Change", radius = 0.015)
 png(filename = "./plots/manuscript/gdsc_prot_heatmap.png", width = 5, height = 5.5, units = "in", res = 500)
@@
 
-# SPEARMAN (CN, GE)
+# SPEARMAN: PanCan
 
 --------------------------------------------------------------------------------
+
+## GE/CN
 
@@
 
+# WATERFALL/GSEA: PanCAn
+
+--------------------------------------------------------------------------------
+
+Consider looking at GSEA rankings.
+
+# WILCOXON: Lineages
+
+--------------------------------------------------------------------------------
+
+# SPEARMAN: Lineages
+
+--------------------------------------------------------------------------------
+
+## GE/CN
+
 # SESSION INFORMATION

### 2019-06-17 19Q2.Rmd
update Rmd

@@
                          ifelse(is.na(Direction) & Drug == "gefitinib" & Feature.Names == "L858R" & Gene == "EGFR", "sensitivity",
-                         ifelse(is.na(Direction) & Drug == "trametinib" & Feature.Names == "V600E" & Gene == "BRAF", "sensitivity", NA))))))
+                         ifelse(is.na(Direction) & Drug == "trametinib" & Feature.Names %in% c("V600E", "V600K") & Gene == "BRAF", "sensitivity",
+                         ifelse(is.na(Direction) & Drug == "cabozantinib" & Feature.Names == "RET C634W", "sensitivity", NA)))))))
 
@@
 g2p_fus$Drug_FusionPair <- ifelse(is.na(g2p_fus$Drug) | is.na(g2p_fus$FusionPair), NA, paste0(g2p_fus$Drug, "_", g2p_fus$FusionPair))
-g2p_mut <- g2p_split[[4]]
+g2p_mut <- g2p_split[[4]] %>% drop_na(Direction_Curated)
 g2p_mut_genes <- unique(sapply(strsplit(as.character(g2p_mut$Drug_Gene)[!is.na(g2p_mut$Drug_Gene)], "_", fixed = TRUE), function(x) x[2]))
@@
 g2p_prot$Drug_Gene_Protein_Change_Direction <- with(g2p_prot, paste0(Drug_Gene_Protein_Change, "_", Direction_Curated))
+g2p_mut_summ <- g2p_mut %>% count(Drug_Gene, Direction_Curated)
+# g2p_mut_test_n <- g2p_mut_summ %>% count(Drug_Gene) %>% filter(n > 1)
+# g2p_mut_test <- filter(g2p_mut, Drug_Gene %in% as.character(g2p_mut_test_n$Drug_Gene))
 ```
@@
 
-```{r load_prot_wilcoxon_rds}
+```{r load_prot_wilcoxon_rds, eval=FALSE}
 ccle_signif_prot <- readRDS("./data_munging/rds/ccle_signif_protein_changes.rds")
-ccle_signif_prot <- merge(ccle_signif_prot, unique(select(ccle_prot, Drug_Gene_Protein_Change, Direction_Curated)), by = "Drug_Gene_Protein_Change", all.x = TRUE)
-
 ctrp_signif_prot <- readRDS("./data_munging/rds/ctrp_signif_protein_changes.rds")
-ctrp_signif_prot <- merge(ctrp_signif_prot, unique(select(ctrp_prot, Drug_Gene_Protein_Change, Direction_Curated)), by = "Drug_Gene_Protein_Change", all.x = TRUE)
-
 gdsc_signif_prot <- readRDS("./data_munging/rds/gdsc_signif_protein_changes.rds")
-gdsc_signif_prot <- merge(gdsc_signif_prot, unique(select(gdsc_prot, Drug_Gene_Protein_Change, Direction_Curated)), by = "Drug_Gene_Protein_Change", all.x = TRUE)
+
+gene_prots <- union(unique(ccle_signif_prot$Gene_Protein_Change), union(unique(ctrp_signif_prot$Gene_Protein_Change), unique(gdsc_signif_prot$Gene_Protein_Change)))
+
+ccle_signif_prot_4plot <- merge(merge(ccle_signif_prot, unique(select(ccle_prot, Drug, Gene_Protein_Change, Direction_Curated)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(ccle_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE)
+ctrp_signif_prot_4plot <- merge(merge(ctrp_signif_prot, unique(select(ctrp_prot, Drug, Gene_Protein_Change, Direction_Curated)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(ctrp_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE)
+gdsc_signif_prot_4plot <- merge(merge(gdsc_signif_prot, unique(select(gdsc_prot, Drug, Gene_Protein_Change, Direction_Curated)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(gdsc_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE)
+
+saveRDS(ccle_signif_prot_4plot, "./data_munging/rds/ccle_signif_protein_changes_4plot.rds")
+saveRDS(ctrp_signif_prot_4plot, "./data_munging/rds/ctrp_signif_protein_changes_4plot.rds")
+saveRDS(gdsc_signif_prot_4plot, "./data_munging/rds/gdsc_signif_protein_changes_4plot.rds")
 ```
@@
     signif_grid <- signif_grid[, intersect(g2p_drug_order, colnames(signif_grid))]
-    signif_grid <- signif_grid[complete.cases(signif_grid), ]
+    # signif_grid <- signif_grid[complete.cases(signif_grid), ]
     signif_grid[signif_grid < -log10(0.05)] <- NA
@@
     signif_grid_annot <- signif_grid_annot[, intersect(g2p_drug_order, colnames(signif_grid))]
-    signif_grid_annot <- signif_grid_annot[complete.cases(signif_grid_annot), ]
+    # signif_grid_annot <- signif_grid_annot[complete.cases(signif_grid_annot), ]
     signif_grid_annot[signif_grid_annot == "resistance"] <- "X"
@@
                 col = col_fun,
-                na_col = "gray97",
+                # na_col = "gray97",
+                na_col = "white",
                 rect_gp = gpar(col = "gray70"),
@@
 ```{r prot_heatmaps, eval=FALSE, fig.height=10, fig.width=3}
-ht_ccle <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Gene:Protein Change", radius = 0.03)
+ht_ccle <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot_4plot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Gene:Protein Change", radius = 0.03)
 png(filename = "./plots/manuscript/ccle_prot_heatmap.png", width = 3, height = 5.5, units = "in", res = 500)
@@
 
-ht_ctrp <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Gene:Protein Change", radius = 0.015)
+ht_ctrp <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot_4plot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Gene:Protein Change", radius = 0.015)
 png(filename = "./plots/manuscript/ctrp_prot_heatmap.png", width = 9.5, height = 5.5, units = "in", res = 500)
@@
 
-ht_gdsc <- MakeWilcoxonHeatmap(signif_df = gdsc_signif_prot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Gene:Protein Change", radius = 0.015)
+ht_gdsc <- MakeWilcoxonHeatmap(signif_df = gdsc_signif_prot_4plot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 8, by = 2), row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Gene:Protein Change", radius = 0.015)
 png(filename = "./plots/manuscript/gdsc_prot_heatmap.png", width = 5, height = 5.5, units = "in", res = 500)
 draw(ht_gdsc, heatmap_legend_side = "top")
+dev.off()
+
+ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot_4plot, feature = "protein changes", legend_title = "CCLE -log10(p-value)                                                                     ", legend_breaks = seq(0, 15, by = 3), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Gene:Protein Change", radius = 0.03)
+ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot_4plot, feature = "protein changes", legend_title = "CTRP -log10(p-value)                                                                    ", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Gene:Protein Change", radius = 0.015)
+ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = gdsc_signif_prot_4plot, feature = "protein changes", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 8, by = 2), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Gene:Protein Change", radius = 0.015)
+png(filename = "./plots/manuscript/drug_prot_heatmap.png", width = 13, height = 5, units = "in", res = 500)
+draw(ht_ccle2 + ht_ctrp2 + ht_gdsc2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
 dev.off()

### 2019-06-19 19Q2.Rmd
update RMD

@@
 prot <- bind_rows(ccle_prot, ctrp_prot, gdsc_prot)
+prot <- separate(data = prot, col = Gene_Protein_Change, into = c("Gene", "Protein_Change"), remove = FALSE, sep = ":")
+prot <- add_column(prot, Drug_Gene = paste0(prot$Drug, "_", prot$Gene), .after = "Drug")
+prot$Direction_Curated <- ifelse(is.na(prot$Direction_Curated), "none", as.character(prot$Direction_Curated))
+prot$Direction_Grouper <- with(prot, paste0(Change_Status, "_", Direction_Curated))
 saveRDS(prot, "./data_munging/rds/protein_changes_merged.rds")
@@
 prot <- readRDS("./data_munging/rds/protein_changes_merged.rds")
-prot_summary <- prot %>% count(Database, Drug, Gene_Protein_Change, Change_Status)
+# prot_summary <- prot %>% count(Database, Drug, Gene_Protein_Change, Change_Status)
 ```
@@
 crispr <- readRDS("./data_munging/19Q2/crispr_data_19Q2.rds")
+```
+
+```{r, eval=FALSE}
+maf_changes_df <- readRDS("./data_munging/19Q2/maf_changes_df_19Q2.rds")
+maf_changes_filt <- filter(maf_changes_df, Gene_Protein_Change %in% unique(as.character(g2p_prot$Gene_Protein_Change)))
+
+# CCLE
+crispr_prot_grid <- expand.grid("DepMap_ID" = unique(crispr_all$DepMap_ID), "Gene_Protein_Change" = unique(maf_changes_filt$Gene_Protein_Change))
+crispr_prot <- merge(crispr_all, crispr_prot_grid, by = "DepMap_ID", all = TRUE)
+crispr_prot <- merge(crispr_prot, maf_changes_filt, by = c("DepMap_ID", "Gene_Protein_Change"), all = TRUE)
+crispr_prot$Change_Status <- ifelse(!is.na(crispr_prot$Protein_Change), "Yes", "No")
+crispr_prot$G2P_Protein_Change <- ifelse(crispr_prot$Gene_Protein_Change %in% unique(as.character(g2p_prot$Gene_Protein_Change)), "Yes", "No")
+crispr_prot <- merge(crispr_prot, unique(select(g2p_prot, Drug_Gene_Protein_Change, Direction_Curated)), by = "Drug_Gene_Protein_Change", all.x = TRUE)
+crispr_prot$Database <- "CRISPR"
+
+crispr_prot <- separate(data = crispr_prot, col = Gene_Protein_Change, into = c("Gene", "Protein_Change"), remove = FALSE, sep = ":")
+crispr_prot <- add_column(crispr_prot, Drug_Gene = paste0("CRISPR_", crispr_prot$Gene), .after = "Gene")
+crispr_prot$Direction_Curated <- ifelse(is.na(crispr_prot$Direction_Curated), "none", as.character(crispr_prot$Direction_Curated))
+crispr_prot$Direction_Grouper <- with(crispr_prot, paste0(Change_Status, "_", Direction_Curated))
+
+saveRDS(crispr_prot, "./data_munging/rds/protein_changes_merged.rds")
 ```
@@
 
-WilcoxonTestDF <- function(dataframe, grouping, g2p_list, outfile) {
+WilcoxonTestDF <- function(dataframe, grouping, g2p_list, type, outfile) {
   require(ggpubr)
-  if("Drug_Gene_Lin" %in% grouping) {
+  if(tolower(type) == "drug_gene_lineage") {
     # Filter out DGLs with too few samples in at least one mutation status category
@@
   }
-  if("FusionPair" %in% grouping) {
+  if(tolower(type) == "fusion") {
     # Filter out fusions with too few samples in at least one category
@@
   }
-  if("Gene_Protein_Change" %in% grouping) {
+  if(tolower(type) == "protein_change") {
     # Filter out Gene:Protein_Changes with too few samples in at least one category
@@
   }
-  if("Drug_Gene" %in% grouping) {
+  if(tolower(type) == "direction") {
+    signif <- compare_means(Score ~ Direction_Grouper, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
+    signif <- adj_signif(signif, alpha = 0.05)
+    signif <- signif[order(signif$p),]
+    # signif$InG2P <- ifelse(signif$Drug_Gene_Protein_Change %in% g2p_list, "Yes", "No")
+  }
+  if(tolower(type) == "drug_gene") {
     # Filter out DGs with too few samples in at least one mutation status category
@@
     count_mut_category <- count_mut_n %>% count(Drug_Gene) %>% filter(n == 2)
-    dgl_keep <- intersect(count_mut_n$Drug_Gene, count_mut_category$Drug_Gene)
-    dataframe <- filter(dataframe, Drug_Gene %in% dgl_keep)
+    dg_keep <- intersect(count_mut_n$Drug_Gene, count_mut_category$Drug_Gene)
+    dataframe <- filter(dataframe, Drug_Gene %in% dg_keep)
     dataframe$Drug_Gene <- as.character(dataframe$Drug_Gene)
@@
 # crispr_signif_all_gene <- WilcoxonTestDF(dataframe = crispr, grouping = "Gene", outfile = "./data_munging/rds/crispr_signif_g.rds")
-crispr_filt <- filter(crispr, Gene %in% g2p_genes)
-crispr_signif_gene <- WilcoxonTestDF(dataframe = crispr_filt, grouping = "Gene", outfile = "./data_munging/rds/crispr_signif_g2p_g.rds")
-crispr_signif_lineage <- WilcoxonTestDF(dataframe = crispr_filt, grouping = c("Gene", "disease"), outfile = "./data_munging/rds/crispr_signif_g2p_gl.rds")
+# crispr_filt <- filter(crispr, Gene %in% g2p_genes)
+# crispr_signif_gene <- WilcoxonTestDF(dataframe = crispr_filt, grouping = "Gene", type = "drug_gene", outfile = "./data_munging/rds/crispr_signif_g2p_g.rds")
+# crispr_signif_lineage <- WilcoxonTestDF(dataframe = crispr_filt, grouping = c("Gene", "disease"), type = "drug_gene_lineage", outfile = "./data_munging/rds/crispr_signif_g2p_gl.rds")
 
@@
 ccle_filt <- unfactorize(ccle_filt)
-ccle_signif_dg <- WilcoxonTestDF(dataframe = ccle, grouping = c("Drug", "Gene", "Drug_Gene"), g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), outfile = "./data_munging/rds/ccle_signif_dg.rds")
-ccle_signif_g2p_dg <- WilcoxonTestDF(dataframe = ccle_filt, grouping = c("Drug", "Gene", "Drug_Gene"), g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), outfile = "./data_munging/rds/ccle_signif_g2p_dg.rds")
-ccle_signif_g2p_dgl <- WilcoxonTestDF(dataframe = ccle_filt, grouping = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), g2p_list = unique(as.character(g2p_mut$Drug_Gene_Lin[!is.na(g2p_mut$Drug_Gene_Lin)])), outfile = "./data_munging/rds/ccle_signif_g2p_dgl.rds")
+ccle_signif_dg <- WilcoxonTestDF(dataframe = ccle, grouping = c("Drug", "Gene", "Drug_Gene"), g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), type = "drug_gene", outfile = "./data_munging/rds/ccle_signif_dg.rds")
+ccle_signif_g2p_dg <- WilcoxonTestDF(dataframe = ccle_filt, grouping = c("Drug", "Gene", "Drug_Gene"), type = "drug_gene", g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), outfile = "./data_munging/rds/ccle_signif_g2p_dg.rds")
+ccle_signif_g2p_dgl <- WilcoxonTestDF(dataframe = ccle_filt, grouping = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), type = "drug_gene_lineage", g2p_list = unique(as.character(g2p_mut$Drug_Gene_Lin[!is.na(g2p_mut$Drug_Gene_Lin)])), outfile = "./data_munging/rds/ccle_signif_g2p_dgl.rds")
 
@@
 ctrp_filt <- unfactorize(ctrp_filt)
-# ctrp_signif_dg <- WilcoxonTestDF(dataframe = ctrp, grouping = c("Drug", "Gene", "Drug_Gene"), g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), outfile = "./data_munging/rds/ctrp_signif_dg.rds")
-ctrp_signif_g2p_dg <- WilcoxonTestDF(dataframe = ctrp_filt, grouping = c("Drug", "Gene", "Drug_Gene"), g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), outfile = "./data_munging/rds/ctrp_signif_g2p_dg.rds")
-ctrp_signif_g2p_dgl <- WilcoxonTestDF(dataframe = ctrp_filt, grouping = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), g2p_list = unique(as.character(g2p_mut$Drug_Gene_Lin[!is.na(g2p_mut$Drug_Gene_Lin)])), outfile = "./data_munging/rds/ctrp_signif_g2p_dgl.rds")
+# ctrp_signif_dg <- WilcoxonTestDF(dataframe = ctrp, grouping = c("Drug", "Gene", "Drug_Gene"), type = "drug_gene", g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), outfile = "./data_munging/rds/ctrp_signif_dg.rds")
+ctrp_signif_g2p_dg <- WilcoxonTestDF(dataframe = ctrp_filt, grouping = c("Drug", "Gene", "Drug_Gene"), type = "drug_gene", g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), outfile = "./data_munging/rds/ctrp_signif_g2p_dg.rds")
+ctrp_signif_g2p_dgl <- WilcoxonTestDF(dataframe = ctrp_filt, grouping = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), type = "drug_gene_lineage", g2p_list = unique(as.character(g2p_mut$Drug_Gene_Lin[!is.na(g2p_mut$Drug_Gene_Lin)])), outfile = "./data_munging/rds/ctrp_signif_g2p_dgl.rds")
 
@@
 gdsc_filt <- unfactorize(gdsc_filt)
-# gdsc_signif_dg <- WilcoxonTestDF(dataframe = gdsc, grouping = c("Drug", "Gene", "Drug_Gene"), g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), outfile = "./data_munging/rds/gdsc_signif_dg.rds")
-gdsc_signif_g2p_dg <- WilcoxonTestDF(dataframe = gdsc_filt, grouping = c("Drug", "Gene", "Drug_Gene"), g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), outfile = "./data_munging/rds/gdsc_signif_g2p_dg.rds")
-gdsc_signif_g2p_dgl <- WilcoxonTestDF(dataframe = gdsc_filt, grouping = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), g2p_list = unique(as.character(g2p_mut$Drug_Gene_Lin[!is.na(g2p_mut$Drug_Gene_Lin)])), outfile = "./data_munging/rds/gdsc_signif_g2p_dgl.rds")
+# gdsc_signif_dg <- WilcoxonTestDF(dataframe = gdsc, grouping = c("Drug", "Gene", "Drug_Gene"), type = "drug_gene", g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), outfile = "./data_munging/rds/gdsc_signif_dg.rds")
+gdsc_signif_g2p_dg <- WilcoxonTestDF(dataframe = gdsc_filt, grouping = c("Drug", "Gene", "Drug_Gene"), type = "drug_gene", g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), outfile = "./data_munging/rds/gdsc_signif_g2p_dg.rds")
+gdsc_signif_g2p_dgl <- WilcoxonTestDF(dataframe = gdsc_filt, grouping = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), type = "drug_gene_lineage", g2p_list = unique(as.character(g2p_mut$Drug_Gene_Lin[!is.na(g2p_mut$Drug_Gene_Lin)])), outfile = "./data_munging/rds/gdsc_signif_g2p_dgl.rds")
 ```
@@
 ccle_prot <- unfactorize(ccle_prot)
-ccle_prot_count <- ccle_prot %>% count(Gene_Protein_Change, Drug, Change_Status)
+# ccle_prot_count <- ccle_prot %>% count(Gene_Protein_Change, Drug, Change_Status)
 
@@
 ctrp_prot <- unfactorize(ctrp_prot)
-ctrp_prot_count <- ctrp_prot %>% count(Gene_Protein_Change, Drug, Change_Status)
+# ctrp_prot_count <- ctrp_prot %>% count(Gene_Protein_Change, Drug, Change_Status)
 
@@
 gdsc_prot <- unfactorize(gdsc_prot)
-gdsc_prot_count <- gdsc_prot %>% count(Gene_Protein_Change, Drug, Change_Status)
-```
+# gdsc_prot_count <- gdsc_prot %>% count(Gene_Protein_Change, Drug, Change_Status)
+```
+
+### Sen vs. Res tests
+
+```{r prot_SvR_wilcoxon_tests, eval=FALSE}
+# CCLE
+ccle_prot_dir <- unique(select(ccle_prot, DepMap_ID, Gene, Cell_line, CCLE_histology, TCGA_classification, CCLE_name, Drug, Drug_Gene, Score, Change_Status, Direction_Curated, Direction_Grouper))
+## Resistance
+ccle_prot_res <- filter(ccle_prot_dir, Direction_Grouper %in% c("No_none", "Yes_none", "No_resistance", "Yes_resistance"))
+ccle_prot_res$Direction_Grouper <- with(ccle_prot_res, ifelse(Direction_Grouper == "Yes_resistance", "Mutated", "Not mutated"))
+ccle_signif_prot_res <- WilcoxonTestDF(dataframe = ccle_prot_res, grouping = c("Drug", "Gene", "Drug_Gene"), type = "direction", outfile = "./data_munging/rds/ccle_signif_protein_changes_resistance.rds")
+## Sensitivity
+ccle_prot_sen <- filter(ccle_prot_dir, Direction_Grouper %in% c("No_none", "Yes_none", "No_sensitivity", "Yes_sensitivity"))
+ccle_prot_sen$Direction_Grouper <- with(ccle_prot_sen, ifelse(Direction_Grouper == "Yes_sensitivity", "Mutated", "Not mutated"))
+ccle_signif_prot_sen <- WilcoxonTestDF(dataframe = ccle_prot_sen, grouping = c("Drug", "Gene", "Drug_Gene"), type = "direction", outfile = "./data_munging/rds/ccle_signif_protein_changes_sensitivity.rds")
+
+# CTRP
+ctrp_prot_dir <- unique(select(ctrp_prot, DepMap_ID, Gene, Cell_line, CCLE_histology, TCGA_classification, CCLE_name, Drug, Drug_Gene, Score, Change_Status, Direction_Curated, Direction_Grouper))
+## Resistance
+ctrp_prot_res <- filter(ctrp_prot_dir, Direction_Grouper %in% c("No_none", "Yes_none", "No_resistance", "Yes_resistance"))
+ctrp_prot_res$Direction_Grouper <- with(ctrp_prot_res, ifelse(Direction_Grouper == "Yes_resistance", "Mutated", "Not mutated"))
+ctrp_signif_prot_res <- WilcoxonTestDF(dataframe = ctrp_prot_res, grouping = c("Drug", "Gene", "Drug_Gene"), type = "direction", outfile = "./data_munging/rds/ctrp_signif_protein_changes_resistance.rds")
+## Sensitivity
+ctrp_prot_sen <- filter(ctrp_prot_dir, Direction_Grouper %in% c("No_none", "Yes_none", "No_sensitivity", "Yes_sensitivity"))
+ctrp_prot_sen$Direction_Grouper <- with(ctrp_prot_sen, ifelse(Direction_Grouper == "Yes_sensitivity", "Mutated", "Not mutated"))
+ctrp_signif_prot_sen <- WilcoxonTestDF(dataframe = ctrp_prot_sen, grouping = c("Drug", "Gene", "Drug_Gene"), type = "direction", outfile = "./data_munging/rds/ctrp_signif_protein_changes_sensitivity.rds")
+
+# GDSC
+gdsc_prot_dir <- unique(select(gdsc_prot, DepMap_ID, Gene, Cell_line, CCLE_histology, TCGA_classification, CCLE_name, Drug, Drug_Gene, Score, Change_Status, Direction_Curated, Direction_Grouper))
+## Resistance
+gdsc_prot_res <- filter(gdsc_prot_dir, Direction_Grouper %in% c("No_none", "Yes_none", "No_resistance", "Yes_resistance"))
+gdsc_prot_res$Direction_Grouper <- with(gdsc_prot_res, ifelse(Direction_Grouper == "Yes_resistance", "Mutated", "Not mutated"))
+gdsc_signif_prot_res <- WilcoxonTestDF(dataframe = gdsc_prot_res, grouping = c("Drug", "Gene", "Drug_Gene"), type = "direction", outfile = "./data_munging/rds/gdsc_signif_protein_changes_resistance.rds")
+## Sensitivity
+gdsc_prot_sen <- filter(gdsc_prot_dir, Direction_Grouper %in% c("No_none", "Yes_none", "No_sensitivity", "Yes_sensitivity"))
+gdsc_prot_sen$Direction_Grouper <- with(gdsc_prot_sen, ifelse(Direction_Grouper == "Yes_sensitivity", "Mutated", "Not mutated"))
+gdsc_signif_prot_sen <- WilcoxonTestDF(dataframe = gdsc_prot_sen, grouping = c("Drug", "Gene", "Drug_Gene"), type = "direction", outfile = "./data_munging/rds/gdsc_signif_protein_changes_sensitivity.rds")
+```
+
+```{r load_prot_SvR_wilcoxon_tests}
+ccle_signif_prot_res <- readRDS("./data_munging/rds/ccle_signif_protein_changes_resistance.rds")
+ccle_signif_prot_res$Direction_Test <- "Resistance"
+ccle_signif_prot_sen <- readRDS("./data_munging/rds/ccle_signif_protein_changes_sensitivity.rds")
+ccle_signif_prot_sen$Direction_Test <- "Sensitivity"
+ccle_signif_prot_dir <- bind_rows(ccle_signif_prot_res, ccle_signif_prot_sen)
+
+ctrp_signif_prot_res <- readRDS("./data_munging/rds/ctrp_signif_protein_changes_resistance.rds")
+ctrp_signif_prot_res$Direction_Test <- "Resistance"
+ctrp_signif_prot_sen <- readRDS("./data_munging/rds/ctrp_signif_protein_changes_sensitivity.rds")
+ctrp_signif_prot_sen$Direction_Test <- "Sensitivity"
+ctrp_signif_prot_dir <- bind_rows(ctrp_signif_prot_res, ctrp_signif_prot_sen)
+
+gdsc_signif_prot_res <- readRDS("./data_munging/rds/gdsc_signif_protein_changes_resistance.rds")
+gdsc_signif_prot_res$Direction_Test <- "Resistance"
+gdsc_signif_prot_sen <- readRDS("./data_munging/rds/gdsc_signif_protein_changes_sensitivity.rds")
+gdsc_signif_prot_sen$Direction_Test <- "Sensitivity"
+gdsc_signif_prot_dir <- bind_rows(gdsc_signif_prot_res, gdsc_signif_prot_sen)
+```
+
+### Exact match tests
 
@@
 ccle_prot <- unfactorize(ccle_prot)
-ccle_signif_prot <- WilcoxonTestDF(dataframe = ccle_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change[!is.na(g2p_prot$Drug_Gene_Protein_Change)])), outfile = "./data_munging/rds/ccle_signif_protein_changes.rds")
+ccle_signif_prot <- WilcoxonTestDF(dataframe = ccle_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change[!is.na(g2p_prot$Drug_Gene_Protein_Change)])), type = "protein_change", outfile = "./data_munging/rds/ccle_signif_protein_changes.rds")
 
 ctrp_prot <- unfactorize(ctrp_prot)
-ctrp_signif_prot <- WilcoxonTestDF(dataframe = ctrp_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change[!is.na(g2p_prot$Drug_Gene_Protein_Change)])), outfile = "./data_munging/rds/ctrp_signif_protein_changes.rds")
+ctrp_signif_prot <- WilcoxonTestDF(dataframe = ctrp_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change[!is.na(g2p_prot$Drug_Gene_Protein_Change)])), type = "protein_change", outfile = "./data_munging/rds/ctrp_signif_protein_changes.rds")
 
 gdsc_prot <- unfactorize(gdsc_prot)
-gdsc_signif_prot <- WilcoxonTestDF(dataframe = gdsc_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change[!is.na(g2p_prot$Drug_Gene_Protein_Change)])), outfile = "./data_munging/rds/gdsc_signif_protein_changes.rds")
+gdsc_signif_prot <- WilcoxonTestDF(dataframe = gdsc_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change[!is.na(g2p_prot$Drug_Gene_Protein_Change)])), type = "protein_change", outfile = "./data_munging/rds/gdsc_signif_protein_changes.rds")
 ```
@@
 
+```{r}
+ccle_signif_prot_4plot <- readRDS("./data_munging/rds/ccle_signif_protein_changes_4plot.rds")
+ctrp_signif_prot_4plot <- readRDS("./data_munging/rds/ctrp_signif_protein_changes_4plot.rds")
+gdsc_signif_prot_4plot <- readRDS("./data_munging/rds/gdsc_signif_protein_changes_4plot.rds")
+```
+
 ## Fusions
@@
 ```{r fus_wilcoxon_tests, eval=FALSE}
-ccle_signif_fus <- WilcoxonTestDF(dataframe = ccle_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair"), g2p_list = unique(as.character(g2p_fus$Drug_FusionPair[!is.na(g2p_fus$Drug_FusionPair)])), outfile = "./data_munging/rds/ccle_signif_fusions.rds")
-
-ctrp_signif_fus <- WilcoxonTestDF(dataframe = ctrp_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair"), g2p_list = unique(as.character(g2p_fus$Drug_FusionPair[!is.na(g2p_fus$Drug_FusionPair)])), outfile = "./data_munging/rds/ctrp_signif_fusions.rds")
-
-gdsc_signif_fus <- WilcoxonTestDF(dataframe = gdsc_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair"), g2p_list = unique(as.character(g2p_fus$Drug_FusionPair[!is.na(g2p_fus$Drug_FusionPair)])), outfile = "./data_munging/rds/gdsc_signif_fusions.rds")
+ccle_signif_fus <- WilcoxonTestDF(dataframe = ccle_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair"), g2p_list = unique(as.character(g2p_fus$Drug_FusionPair[!is.na(g2p_fus$Drug_FusionPair)])), type = "fusion", outfile = "./data_munging/rds/ccle_signif_fusions.rds")
+
+ctrp_signif_fus <- WilcoxonTestDF(dataframe = ctrp_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair"), g2p_list = unique(as.character(g2p_fus$Drug_FusionPair[!is.na(g2p_fus$Drug_FusionPair)])), type = "fusion", outfile = "./data_munging/rds/ctrp_signif_fusions.rds")
+
+gdsc_signif_fus <- WilcoxonTestDF(dataframe = gdsc_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair"), g2p_list = unique(as.character(g2p_fus$Drug_FusionPair[!is.na(g2p_fus$Drug_FusionPair)])), type = "fusion", outfile = "./data_munging/rds/gdsc_signif_fusions.rds")
 ```
@@
 # ggsave("./plots/manuscript/gdsc_fus_boxplots.png", gdsc_fus_boxplot, width = 12, height = 5, units = "in")
+```
+
+```{r direction_boxplots}
+# CCLE
+ggplot(data = filter(ccle_prot_res, Drug_Gene %in% ccle_signif_prot_res$Drug_Gene)) +
+  facet_wrap(~ Drug_Gene, nrow = 1) +
+  scale_color_manual(values = c("Mutated" = "springgreen4", "Not mutated" = "palegreen3")) +
+  geom_boxplot(mapping = aes(x = Direction_Grouper, y = Score, color = Direction_Grouper), outlier.shape = NA) +
+  geom_jitter(aes(x = Direction_Grouper, y = Score, color = Direction_Grouper), width = 0.2, alpha = 0.5, size = 0.6) +
+  geom_text(data = ccle_signif_prot_res, aes(x = 1.5, y = 1.0, label = p.signif)) +
+  coord_cartesian(ylim = c(0, 1.1)) +
+  scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
+  theme(legend.position = "none") +
+  labs(y = "AUC", x = "Resistance mutation in associated gene?")
 ```

### 2019-06-20 19Q2.Rmd

@@
 g2p_prot <- unique(filter(g2p, !is.na(Gene_Protein_Change) & !is.na(Drug)) %>% select(group_general_lineage_name, Drug, Direction_Curated, Gene, Protein_Change, Gene_Protein_Change))
+g2p_prot$Drug_Gene <- with(g2p_prot, paste0(Drug, "_", Gene))
 g2p_prot$Drug_Gene_Protein_Change <- with(g2p_prot, paste0(Drug, "_", Gene_Protein_Change))
@@
 ```{r, eval=FALSE}
+crispr_all <- read.delim("./data_munging/19Q2/Achilles_gene_effect_20190514.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
+# Remove Entrez gene IDs from colnames
+colnames(crispr_all) <- gsub(" .*", "", colnames(crispr_all))
+colnames(crispr_all)[1] <- "DepMap_ID"
 maf_changes_df <- readRDS("./data_munging/19Q2/maf_changes_df_19Q2.rds")
@@
 crispr_prot$G2P_Protein_Change <- ifelse(crispr_prot$Gene_Protein_Change %in% unique(as.character(g2p_prot$Gene_Protein_Change)), "Yes", "No")
-crispr_prot <- merge(crispr_prot, unique(select(g2p_prot, Drug_Gene_Protein_Change, Direction_Curated)), by = "Drug_Gene_Protein_Change", all.x = TRUE)
+crispr_prot <- merge(crispr_prot, unique(select(g2p_prot, Gene_Protein_Change, Direction_Curated)), by = "Gene_Protein_Change", all.x = TRUE)
 crispr_prot$Database <- "CRISPR"
@@
 saveRDS(crispr_prot, "./data_munging/rds/protein_changes_merged.rds")
+```
+
+```{r}
+crispr_prot <- readRDS("./data_munging/rds/protein_changes_merged.rds")
 ```
@@
 
-gdsc_prot <- filter(prot, Drug %in% g2p_drugs & Database == "GDSC")
+gdsc_prot <- filter(prot, Database == "GDSC")
 gdsc_prot <- unfactorize(gdsc_prot)
@@
 
-```{r prot_SvR_wilcoxon_tests, eval=FALSE}
+```{r SvR_direction_datasets, eval=FALSE}
 # CCLE
@@
 ccle_prot_res$Direction_Grouper <- with(ccle_prot_res, ifelse(Direction_Grouper == "Yes_resistance", "Mutated", "Not mutated"))
-ccle_signif_prot_res <- WilcoxonTestDF(dataframe = ccle_prot_res, grouping = c("Drug", "Gene", "Drug_Gene"), type = "direction", outfile = "./data_munging/rds/ccle_signif_protein_changes_resistance.rds")
 ## Sensitivity
@@
 ccle_prot_sen$Direction_Grouper <- with(ccle_prot_sen, ifelse(Direction_Grouper == "Yes_sensitivity", "Mutated", "Not mutated"))
-ccle_signif_prot_sen <- WilcoxonTestDF(dataframe = ccle_prot_sen, grouping = c("Drug", "Gene", "Drug_Gene"), type = "direction", outfile = "./data_munging/rds/ccle_signif_protein_changes_sensitivity.rds")
+saveRDS(ccle_prot_res, "./data_munging/rds/ccle_protein_changes_resistance.rds")
+saveRDS(ccle_prot_sen, "./data_munging/rds/ccle_protein_changes_sensitivity.rds")
 
@@
 ctrp_prot_res$Direction_Grouper <- with(ctrp_prot_res, ifelse(Direction_Grouper == "Yes_resistance", "Mutated", "Not mutated"))
-ctrp_signif_prot_res <- WilcoxonTestDF(dataframe = ctrp_prot_res, grouping = c("Drug", "Gene", "Drug_Gene"), type = "direction", outfile = "./data_munging/rds/ctrp_signif_protein_changes_resistance.rds")
 ## Sensitivity
@@
 ctrp_prot_sen$Direction_Grouper <- with(ctrp_prot_sen, ifelse(Direction_Grouper == "Yes_sensitivity", "Mutated", "Not mutated"))
-ctrp_signif_prot_sen <- WilcoxonTestDF(dataframe = ctrp_prot_sen, grouping = c("Drug", "Gene", "Drug_Gene"), type = "direction", outfile = "./data_munging/rds/ctrp_signif_protein_changes_sensitivity.rds")
+saveRDS(ctrp_prot_res, "./data_munging/rds/ctrp_protein_changes_resistance.rds")
+saveRDS(ctrp_prot_sen, "./data_munging/rds/ctrp_protein_changes_sensitivity.rds")
 
@@
 gdsc_prot_res$Direction_Grouper <- with(gdsc_prot_res, ifelse(Direction_Grouper == "Yes_resistance", "Mutated", "Not mutated"))
-gdsc_signif_prot_res <- WilcoxonTestDF(dataframe = gdsc_prot_res, grouping = c("Drug", "Gene", "Drug_Gene"), type = "direction", outfile = "./data_munging/rds/gdsc_signif_protein_changes_resistance.rds")
 ## Sensitivity
@@
 gdsc_prot_sen$Direction_Grouper <- with(gdsc_prot_sen, ifelse(Direction_Grouper == "Yes_sensitivity", "Mutated", "Not mutated"))
+saveRDS(gdsc_prot_res, "./data_munging/rds/gdsc_protein_changes_resistance.rds")
+saveRDS(gdsc_prot_sen, "./data_munging/rds/gdsc_protein_changes_sensitivity.rds")
+```
+
+```{r prot_SvR_wilcoxon_tests, eval=FALSE}
+# CCLE
+ccle_signif_prot_res <- WilcoxonTestDF(dataframe = ccle_prot_res, grouping = c("Drug", "Gene", "Drug_Gene"), type = "direction", outfile = "./data_munging/rds/ccle_signif_protein_changes_resistance.rds")
+ccle_signif_prot_sen <- WilcoxonTestDF(dataframe = ccle_prot_sen, grouping = c("Drug", "Gene", "Drug_Gene"), type = "direction", outfile = "./data_munging/rds/ccle_signif_protein_changes_sensitivity.rds")
+
+# CTRP
+ctrp_signif_prot_res <- WilcoxonTestDF(dataframe = ctrp_prot_res, grouping = c("Drug", "Gene", "Drug_Gene"), type = "direction", outfile = "./data_munging/rds/ctrp_signif_protein_changes_resistance.rds")
+ctrp_signif_prot_sen <- WilcoxonTestDF(dataframe = ctrp_prot_sen, grouping = c("Drug", "Gene", "Drug_Gene"), type = "direction", outfile = "./data_munging/rds/ctrp_signif_protein_changes_sensitivity.rds")
+
+# GDSC
+gdsc_signif_prot_res <- WilcoxonTestDF(dataframe = gdsc_prot_res, grouping = c("Drug", "Gene", "Drug_Gene"), type = "direction", outfile = "./data_munging/rds/gdsc_signif_protein_changes_resistance.rds")
 gdsc_signif_prot_sen <- WilcoxonTestDF(dataframe = gdsc_prot_sen, grouping = c("Drug", "Gene", "Drug_Gene"), type = "direction", outfile = "./data_munging/rds/gdsc_signif_protein_changes_sensitivity.rds")
@@
 # CCLE
-ggplot(data = filter(ccle_prot_res, Drug_Gene %in% ccle_signif_prot_res$Drug_Gene)) +
-  facet_wrap(~ Drug_Gene, nrow = 1) +
+ccle_res_box <- ggplot(data = filter(ccle_prot_res, Drug_Gene %in% ccle_signif_prot_res$Drug_Gene)) +
+  facet_wrap(~ Drug * Gene, nrow = 1) +
   scale_color_manual(values = c("Mutated" = "springgreen4", "Not mutated" = "palegreen3")) +
@@
   geom_jitter(aes(x = Direction_Grouper, y = Score, color = Direction_Grouper), width = 0.2, alpha = 0.5, size = 0.6) +
-  geom_text(data = ccle_signif_prot_res, aes(x = 1.5, y = 1.0, label = p.signif)) +
+  geom_text(data = ccle_signif_prot_res, aes(x = 1.5, y = 1.05, label = p.signif), size = 7) +
   coord_cartesian(ylim = c(0, 1.1)) +
   scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
-  theme(legend.position = "none") +
-  labs(y = "AUC", x = "Resistance mutation in associated gene?")
+  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
+  labs(y = "AUC", x = "Resistance mutation?")
+
+ccle_sen_box <- ggplot(data = filter(ccle_prot_sen, Drug_Gene %in% ccle_signif_prot_sen$Drug_Gene)) +
+  facet_wrap(~ Drug * Gene, nrow = 1) +
+  scale_color_manual(values = c("Mutated" = "springgreen4", "Not mutated" = "palegreen3")) +
+  geom_boxplot(mapping = aes(x = Direction_Grouper, y = Score, color = Direction_Grouper), outlier.shape = NA) +
+  geom_jitter(aes(x = Direction_Grouper, y = Score, color = Direction_Grouper), width = 0.2, alpha = 0.5, size = 0.6) +
+  geom_text(data = ccle_signif_prot_sen, aes(x = 1.5, y = 1.05, label = p.signif), size = 7) +
+  coord_cartesian(ylim = c(0, 1.1)) +
+  scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
+  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
+  labs(y = "AUC", x = "Sensitivity mutation?")
+ccle_dir_boxes <- plot_grid(ccle_res_box, ccle_sen_box, labels = c("A", "B"), rel_widths = c(3, 1.1))
+ggsave("./plots/manuscript/ccle_direction_boxplots.png", ccle_dir_boxes, device = "png", dpi = 450, width = 12, height = 5, units = "in")
+
+# CTRP
+ctrp_res_box <- ggplot(data = filter(ctrp_prot_res, Drug_Gene %in% ctrp_signif_prot_res$Drug_Gene)) +
+  facet_wrap(~ Drug * Gene, nrow = 1) +
+  scale_color_manual(values = c("Mutated" = "steelblue4", "Not mutated" = "slategray3")) +
+  geom_boxplot(mapping = aes(x = Direction_Grouper, y = Score, color = Direction_Grouper), outlier.shape = NA) +
+  geom_jitter(aes(x = Direction_Grouper, y = Score, color = Direction_Grouper), width = 0.2, alpha = 0.5, size = 0.6) +
+  geom_text(data = ctrp_signif_prot_res, aes(x = 1.5, y = 1.05, label = p.signif), size = 7) +
+  coord_cartesian(ylim = c(0, 1.1)) +
+  scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
+  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
+  labs(y = "AUC", x = "Resistance mutation?")
+
+ctrp_sen_box <- ggplot(data = filter(ctrp_prot_sen, Drug_Gene %in% ctrp_signif_prot_sen$Drug_Gene)) +
+  facet_wrap(~ Drug * Gene, nrow = 1) +
+  scale_color_manual(values = c("Mutated" = "steelblue4", "Not mutated" = "slategray3")) +
+  geom_boxplot(mapping = aes(x = Direction_Grouper, y = Score, color = Direction_Grouper), outlier.shape = NA) +
+  geom_jitter(aes(x = Direction_Grouper, y = Score, color = Direction_Grouper), width = 0.2, alpha = 0.5, size = 0.6) +
+  geom_text(data = ctrp_signif_prot_sen, aes(x = 1.5, y = 1.05, label = p.signif), size = 7) +
+  coord_cartesian(ylim = c(0, 1.1)) +
+  scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
+  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
+  labs(y = "AUC", x = "Sensitivity mutation?")
+ctrp_dir_boxes <- plot_grid(ctrp_res_box, ctrp_sen_box, labels = c("A", "B"), ncol = 1)
+ggsave("./plots/manuscript/ctrp_direction_boxplots.png", ctrp_dir_boxes, device = "png", dpi = 450, width = 12, height = 8, units = "in")
+
+# GDSC
+gdsc_res_box <- ggplot(data = filter(gdsc_prot_res, Drug_Gene %in% gdsc_signif_prot_res$Drug_Gene)) +
+  facet_wrap(~ Drug * Gene, nrow = 1) +
+  scale_color_manual(values = c("Mutated" = "turquoise4", "Not mutated" = "paleturquoise3")) +
+  geom_boxplot(mapping = aes(x = Direction_Grouper, y = Score, color = Direction_Grouper), outlier.shape = NA) +
+  geom_jitter(aes(x = Direction_Grouper, y = Score, color = Direction_Grouper), width = 0.2, alpha = 0.5, size = 0.6) +
+  geom_text(data = gdsc_signif_prot_res, aes(x = 1.5, y = 1.05, label = p.signif), size = 7) +
+  coord_cartesian(ylim = c(0, 1.1)) +
+  scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
+  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
+  labs(y = "AUC", x = "Resistance mutation?")
+
+gdsc_sen_box <- ggplot(data = filter(gdsc_prot_sen, Drug_Gene %in% gdsc_signif_prot_sen$Drug_Gene)) +
+  facet_wrap(~ Drug * Gene, nrow = 1) +
+  scale_color_manual(values = c("Mutated" = "turquoise4", "Not mutated" = "paleturquoise3")) +
+  geom_boxplot(mapping = aes(x = Direction_Grouper, y = Score, color = Direction_Grouper), outlier.shape = NA) +
+  geom_jitter(aes(x = Direction_Grouper, y = Score, color = Direction_Grouper), width = 0.2, alpha = 0.5, size = 0.6) +
+  geom_text(data = gdsc_signif_prot_sen, aes(x = 1.5, y = 1.05, label = p.signif), size = 7) +
+  coord_cartesian(ylim = c(0, 1.1)) +
+  scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
+  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
+  labs(y = "AUC", x = "Sensitivity mutation?")
+gdsc_dir_boxes <- plot_grid(gdsc_res_box, gdsc_sen_box, labels = c("A", "B"), rel_widths = c(2, 1.1))
+ggsave("./plots/manuscript/gdsc_direction_boxplots.png", gdsc_dir_boxes, device = "png", dpi = 450, width = 12, height = 5, units = "in")
 ```

### 2019-07-02 19Q2.Rmd
update prot Rds and ht w/ better dir and NA annots

@@
 gdsc_signif_prot_dir <- bind_rows(gdsc_signif_prot_res, gdsc_signif_prot_sen)
+
+ccle_prot_res <- readRDS("./data_munging/rds/ccle_protein_changes_resistance.rds")
+ccle_prot_sen <- readRDS("./data_munging/rds/ccle_protein_changes_sensitivity.rds")
+ctrp_prot_res <- readRDS("./data_munging/rds/ctrp_protein_changes_resistance.rds")
+ctrp_prot_sen <- readRDS("./data_munging/rds/ctrp_protein_changes_sensitivity.rds")
+gdsc_prot_res <- readRDS("./data_munging/rds/gdsc_protein_changes_resistance.rds")
+gdsc_prot_sen <- readRDS("./data_munging/rds/gdsc_protein_changes_sensitivity.rds")
 ```
@@
 
-ccle_signif_prot_4plot <- merge(merge(ccle_signif_prot, unique(select(ccle_prot, Drug, Gene_Protein_Change, Direction_Curated)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(ccle_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE)
-ctrp_signif_prot_4plot <- merge(merge(ctrp_signif_prot, unique(select(ctrp_prot, Drug, Gene_Protein_Change, Direction_Curated)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(ctrp_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE)
-gdsc_signif_prot_4plot <- merge(merge(gdsc_signif_prot, unique(select(gdsc_prot, Drug, Gene_Protein_Change, Direction_Curated)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(gdsc_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE)
+# all_directions <- unique(rbind(select(ccle_prot, Gene_Protein_Change, Drug, Direction_Curated), select(ctrp_prot, Gene_Protein_Change, Drug, Direction_Curated), select(gdsc_prot, Gene_Protein_Change, Drug, Direction_Curated)))
+# saveRDS(all_directions, "./data_munging/rds/protein_changes_directions.rds")
+all_directions <- readRDS("./data_munging/rds/protein_changes_directions.rds")
+
+ccle_signif_prot_4plot <- merge(merge(merge(ccle_signif_prot, unique(select(ccle_prot, Drug, Gene_Protein_Change)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(ccle_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE), all_directions,  by = c("Drug", "Gene_Protein_Change"), all.x = TRUE)
+ctrp_signif_prot_4plot <- merge(merge(merge(ctrp_signif_prot, unique(select(ctrp_prot, Drug, Gene_Protein_Change)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(ctrp_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE), all_directions,  by = c("Drug", "Gene_Protein_Change"), all.x = TRUE)
+gdsc_signif_prot_4plot <- merge(merge(merge(gdsc_signif_prot, unique(select(gdsc_prot, Drug, Gene_Protein_Change)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(gdsc_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE), all_directions,  by = c("Drug", "Gene_Protein_Change"), all.x = TRUE)
 
@@
 ```{r wilcoxon_heatmap_function}
-MakeWilcoxonHeatmap <- function(signif_df, feature, row_names, col_title, color, legend_title, legend_breaks, row_title_txt, radius) {
+MakeWilcoxonHeatmap <- function(signif_df, feature, row_names, col_title, color, legend_title, legend_breaks, row_title_txt, radius, na_color) {
+  if(missing(na_color)) {
+    na_color <- "white"
+  }
   if(!is.na(str_match(string = tolower(feature), pattern = "mut"))) {
@@
     signif_grid <- signif_grid[, intersect(g2p_drug_order, colnames(signif_grid))]
-    # signif_grid <- signif_grid[complete.cases(signif_grid), ]
-    signif_grid[signif_grid < -log10(0.05)] <- NA
+
+    signif_grid_annot1 <- signif_grid
+    signif_grid_annot1[signif_grid_annot1 <= -log10(0.05) | is.na(signif_grid_annot1)] <- ""
+    signif_grid_annot1[signif_grid_annot1 > -log10(0.05)] <- "*"
 
@@
     signif_grid_annot <- signif_grid_annot[, intersect(g2p_drug_order, colnames(signif_grid))]
-    # signif_grid_annot <- signif_grid_annot[complete.cases(signif_grid_annot), ]
     signif_grid_annot[signif_grid_annot == "resistance"] <- "X"
@@
                 col = col_fun,
-                # na_col = "gray97",
-                na_col = "white",
+                na_col = na_color,
                 rect_gp = gpar(col = "gray70"),
@@
                 cell_fun = function(j, i, x, y, width, height, fill) {
-                  # grid.text(signif_grid_annot[i, j], x, y, gp = gpar(fontsize = 20))
+                  if(!is.na(str_match(string = tolower(feature), pattern = "prot"))) {
+                    grid.text(signif_grid_annot1[i, j], x = x - width*0.20, y = y + height*0.07, gp = gpar(fontsize = 17))
+                  }
                   if(signif_grid_annot[i, j] == "O") {
@@
                   if(signif_grid_annot[i, j] == "X") {
-                    grid.circle(x = x - width*0.20, y = y - height*0.20, r = radius, default.units = "npc", gp = gpar(fill = "black", col = "black"))
+                    grid.circle(x = x - width*0.20, y = y - height*0.20, r = radius, default.units = "npc", gp = gpar(fill = "red", col = "black"))
                   }
@@
 
-ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot_4plot, feature = "protein changes", legend_title = "CCLE -log10(p-value)                                                                     ", legend_breaks = seq(0, 15, by = 3), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Gene:Protein Change", radius = 0.03)
-ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot_4plot, feature = "protein changes", legend_title = "CTRP -log10(p-value)                                                                    ", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Gene:Protein Change", radius = 0.015)
-ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = gdsc_signif_prot_4plot, feature = "protein changes", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 8, by = 2), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Gene:Protein Change", radius = 0.015)
+ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot_4plot, feature = "protein changes", legend_title = "CCLE -log10(p-value)                                                              ", legend_breaks = seq(0, 15, by = 3), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Gene:Protein Change", radius = 0.03, na_color = "black")
+ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot_4plot, feature = "protein changes", legend_title = "CTRP -log10(p-value)                                                                               ", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Gene:Protein Change", radius = 0.015, na_color = "black")
+ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = gdsc_signif_prot_4plot, feature = "protein changes", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 8, by = 2), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Gene:Protein Change", radius = 0.015, na_color = "black")
 png(filename = "./plots/manuscript/drug_prot_heatmap.png", width = 13, height = 5, units = "in", res = 500)

### 2019-07-02 19Q2.Rmd
update Rmd w/ new prot analysis and ht

@@
 
-# Edit direction column
+# Manually curate direction column
 g2p <- add_column(g2p, Direction_Curated = NA, .after = "Direction")
@@
 
-# Edit mutation column
+# Curate protein change column
 g2p <- add_column(g2p, Protein_Change = NA, .after = "Mutation")
@@
 # g2p_mut_test <- filter(g2p_mut, Drug_Gene %in% as.character(g2p_mut_test_n$Drug_Gene))
+```
+
+```{r}
+test <- g2p %>% drop_na(Drug_Gene, Direction_Curated) %>% count(Drug_Gene, Direction_Curated) %>% count(Drug_Gene) %>% filter(n > 1)
+test_g2p <- filter(g2p, Drug_Gene %in% as.character(test$Drug_Gene))
 ```
@@
     signif <- signif[order(signif$p),]
-    # signif$InG2P <- ifelse(signif$Drug_Gene_Protein_Change %in% g2p_list, "Yes", "No")
   }

### 2019-07-08 19Q2.Rmd
phased out papaja for manuscript writing

@@
 DepMap 19Q2 update fixed almost all of the inconsistencies of the Primary.Disease column, though there were come capitalization inconsistencies.
-```{r depmap_metadata}
+```{r depmap_metadata, eval=FALSE}
 ccl_meta <- read.delim("./data_munging/19Q2/sample_info.csv", sep = ",", header = TRUE, na.strings = c("", NA))
@@
                                    ifelse(disease == " " & CCLE_histology == "testis", "embryo", disease)))))))))
+
+write.csv(ccl_meta, "./data_munging/19Q2/sample_info_edit_20190708.csv")
+```
+
+```{r}
+ccl_meta <- read.delim("./data_munging/19Q2/sample_info_edit_20190708.csv", sep = ",", header = TRUE, row.names = 1)
 ```
@@
 
-```{r fusion_calls, eval=TRUE}
+```{r fusion_calls, eval=FALSE}
 fusions <- read.delim("./data_munging/19Q2/CCLE_fusions.csv.gz", header = TRUE, sep = ",")
@@
 fusions <- merge(fusions, ccl_meta, by = "DepMap_ID", all.x = TRUE)
+write.csv.gz(fusions, "./data_munging/19Q2/CCLE_fusions_edit_20190708.csv.gz")
+```
+
+```{r}
+fusions <- read.delim("./data_munging/19Q2/CCLE_fusions_edit_20190708.csv.gz", header = TRUE, sep = ",")
 ```
@@
 ccle <- MergeOmicsG2P(database = "CCLE", dataframe = ccle_all, maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./data_munging/19Q2/ccle_data_19Q2.rds")
-write.csv.gz(ccle %>% drop_na(Score), "./data_munging/19Q2/ccle_data_19Q2.csv.gz")
+# write.csv.gz(ccle %>% drop_na(Score), "./data_munging/19Q2/ccle_data_19Q2.csv.gz")
 
 ctrp <- MergeOmicsG2P(database = "CTRP", dataframe = ctrp_all, maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./../htscreens_giant_files/ctrp_data_19Q2.rds")
-write.csv.gz(ctrp %>% drop_na(Score), "./../htscreens_giant_files/ctrp_data_19Q2.csv.gz")
+# write.csv.gz(ctrp %>% drop_na(Score), "./../htscreens_giant_files/ctrp_data_19Q2.csv.gz")
 
 gdsc <- MergeOmicsG2P(database = "GDSC", dataframe = gdsc_all, maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./data_munging/19Q2/gdsc_data_19Q2.rds")
-write.csv.gz(gdsc %>% drop_na(Score), "./../htscreens_giant_files/gdsc_data_19Q2.csv.gz")
+# write.csv.gz(gdsc %>% drop_na(Score), "./../htscreens_giant_files/gdsc_data_19Q2.csv.gz")
 
@@
 
-```{r, eval=FALSE}
-crispr_all <- read.delim("./data_munging/19Q2/Achilles_gene_effect_20190514.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
-# Remove Entrez gene IDs from colnames
-colnames(crispr_all) <- gsub(" .*", "", colnames(crispr_all))
-colnames(crispr_all)[1] <- "DepMap_ID"
+```{r merge_crispr_fus, eval=FALSE}
+fusions_filt <- filter(fusions, FusionPair %in% unique(as.character(g2p_fus$FusionPair)))
+
+crispr_fus_grid <- expand.grid("DepMap_ID" = unique(crispr$DepMap_ID), "FusionPair" = unique(fusions_filt$FusionPair))
+crispr_fus <- merge(merge(crispr, crispr_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "CCLE_name", "CCLE_histology", "Cell_line", "FusionPair"), all = TRUE)
+crispr_fus$Fusion_Status <- ifelse(!is.na(crispr_fus$LeftGene), "Yes", "No")
+crispr_fus$Drug_FusionPair <- ifelse(is.na(crispr_fus$Drug) | is.na(crispr_fus$FusionPair), NA, paste0(crispr_fus$Drug, "_", crispr_fus$FusionPair))
+crispr_fus$G2P_Drug_FusionPair <- ifelse(crispr_fus$Drug_FusionPair %in% unique(as.character(g2p_fus$Drug_FusionPair)), "Yes", "No")
+crispr_fus$G2P_Fusion <- ifelse(crispr_fus$FusionPair %in% unique(as.character(g2p_fus$FusionPair)), "Yes", "No")
+crispr_fus$Database <- "CRISPR"
+
+colnames(crispr_fus)[colnames(crispr_fus) == "AUC_IC50"] <- "Score"
+saveRDS(crispr_fus, "./data_munging/rds/crispr_fusions.rds")
+```
+
+```{r merge_crispr_prot, eval=FALSE}
 maf_changes_df <- readRDS("./data_munging/19Q2/maf_changes_df_19Q2.rds")
@@
 # CCLE
-crispr_prot_grid <- expand.grid("DepMap_ID" = unique(crispr_all$DepMap_ID), "Gene_Protein_Change" = unique(maf_changes_filt$Gene_Protein_Change))
-crispr_prot <- merge(crispr_all, crispr_prot_grid, by = "DepMap_ID", all = TRUE)
+crispr_prot_grid <- expand.grid("DepMap_ID" = unique(crispr$DepMap_ID), "Gene_Protein_Change" = unique(maf_changes_filt$Gene_Protein_Change))
+crispr_prot <- merge(crispr, crispr_prot_grid, by = "DepMap_ID", all = TRUE)
 crispr_prot <- merge(crispr_prot, maf_changes_filt, by = c("DepMap_ID", "Gene_Protein_Change"), all = TRUE)
@@
 
-saveRDS(crispr_prot, "./data_munging/rds/protein_changes_merged.rds")
+saveRDS(crispr_prot, "./data_munging/rds/crispr_protein_changes.rds")
 ```
@@
 ```{r}
-crispr_prot <- readRDS("./data_munging/rds/protein_changes_merged.rds")
+crispr_fus <- readRDS("./data_munging/rds/crispr_fusions.rds")
+crispr_prot <- readRDS("./data_munging/rds/crispr_protein_changes.rds")
 ```
@@
 
-# WATERFALL/GSEA: PanCAn
-
---------------------------------------------------------------------------------
-
-Consider looking at GSEA rankings.
-
 # WILCOXON: Lineages

### 2019-07-08 manuscript.Rmd
phased out papaja for manuscript writing

--- 2019-01-24 manuscript.Rmd
@@
 ---
+output              :
+  pdf_document      :
+    toc             : true
+    toc_depth       : 2
+    number_sections : true
+    fig_caption     : true
+    df_print        : kable
+    highlight       : tango
+    # citation_package: natbib
 title               : "Manuscript Draft"
-shorttitle        : "Subtitle"
-
-author: 
-  - name          : "Sally E. Claridge"
-    affiliation   : "1"
-  - name          : "Daniel M. Charytonowicz"
-    affiliation   : "1"
-  - name          : "Adam A. Margolin"
-    affiliation   : "1, 2"
-    corresponding : yes    # Define only one corresponding author
-    address       : "Icahn School of Medicine at Mount Sinai, Deparment of Genetics and Genomic Sciences, One Gustave L. Levy Place, Box 1498, New York, NY 10029"
-    email         : "adam.margolin@mssm.edu"
-
-affiliation:
-  - id            : "1"
-    institution   : "Department of Genetics and Genomic Sciences, Icahn Institute for Data Science and Genomic Technology, Icahn School of Medicine at Mount Sinai, New York, NY"
-  - id            : "2"
-    institution   : "Cancer Target Discovery and Development Network (Oregon Health and Science University, Portland, OR), National Cancer Institute, National Institutes of Health"
-
-authornote: |
-  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-  Enter author note here.
-
-abstract: |
-  Multiple high-throughput functional screens in cancer cell lines have generated large amounts of information on drug efficacy in a variety of genomic contexts and cancer lineages.
+author              :
+- Sally E. Claridge
+- Daniel M. Charytonowicz
+- Adam A. Margolin
+date                : "`r format(Sys.time(), '%d %B %Y')`"
+bibliography        : manuscript.bib
+fontsize            : 12pt
+geometry            : margin=1in
+linkcolor           : blue
+urlcolor            : blue
+citecolor           : blue
+abstract            : Multiple high-throughput functional screens in cancer cell lines have generated large amounts of information on drug efficacy in a variety of genomic contexts and cancer lineages.
 Inconsistencies between datasets have led us to investigate whether these large-scale screens reproduce established clinical drug-gene associations and if genomic features particular to specific genes improve said reproducibility.
-We evaluated three large-scale, small-molecule drug screens and one CRISPR/Cas9 gene essentiality screen, all within the context of clinical interpretations derived from a new cancer variant annotation resource published by the Variant Interpretation for Cancer Consortium (VICC).
+We evaluated three large-scale, small-molecule drug screens within the context of clinical interpretations derived from a new cancer variant annotation resource published by the Variant Interpretation for Cancer Consortium (VICC).
 We identified low levels of concordance between the three drug screen datasets and clinical drug-gene associations using mutation status, gene expression, and copy number as genomic indicators.
 Less than half of the clinical drug-gene cancer associations from the VICC resource were identified in these three drug screen datasets, suggesting a barrier to translating findings from these large-scale screens into the clinic.
-
-keywords          : "keywords"
-wordcount         : "X"
-
-bibliography      : ["manuscript.bib"]
-
-floatsintext      : yes
-figsintext        : no
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-linenumbers       : yes
-mask              : no
-draft             : no
-
-documentclass     : "apa6"
-classoption       : "man"
-biblio-style      : "apa"
-output            : papaja::apa6_pdf
 ---
 
+\newpage
+
 ```{r setup, include=FALSE}
+library(ggpubr)
 library(tidyverse)
-library(ggpubr)
-library(papaja)
-library(bookdown)
-library(VennDiagram)
-library(lettercase)
+library(kableExtra)
+
 # install.packages("tinytex")
@@
 
-```{r analysis-preferences}
+```{r analysis-preferences, include=FALSE}
 # Seed for random number generation
@@
 
-```{r drug-data, echo=FALSE, include=FALSE}
-ccle_data_ptmuts <- readRDS("./data_munging/rds/ccle_data_18Q4_g2pgenes_ptmuts.rds")
-ctrp_data_ptmuts <- readRDS("./data_munging/rds/ctrp_data_18Q4_g2pgenes_ptmuts.rds")
-gdsc_data_ptmuts <- readRDS("./data_munging/rds/gdsc_data_18Q4_g2pgenes_ptmuts.rds")
+```{r load-processed-data, echo=FALSE, include=FALSE}
+ccl_meta <- read.delim("./data_munging/19Q2/sample_info_edit_20190708.csv", sep = ",", header = TRUE, row.names = 1)
+maf_df <- readRDS("./data_munging/19Q2/maf_df_19Q2.rds")
+maf_changes_df <- readRDS("./data_munging/19Q2/maf_changes_df_19Q2.rds")
+cn_melt <- readRDS("./data_munging/19Q2/cn_melt_19Q2.rds")
+ge_melt <- readRDS("./data_munging/19Q2/ge_melt_19Q2.rds")
+fusions <- read.delim("./data_munging/19Q2/CCLE_fusions_edit_20190708.csv.gz", header = TRUE, sep = ",")
 
-# Filter drug screen datasets for G2P drug-gene associations
-ccle_data_g2p <- filter(ccle_data_ptmuts, Drug_Gene %in% g2p_druggenes)
-ccle_data_g2p$Mutation_Status_Nonsilent <- factor(ccle_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-ctrp_data_g2p <- filter(ctrp_data_ptmuts, Drug_Gene %in% g2p_druggenes)
-ctrp_data_g2p$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-gdsc_data_g2p <- filter(gdsc_data_ptmuts, Drug_Gene %in% g2p_druggenes)
-gdsc_data_g2p$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
+ccle <- readRDS("./data_munging/19Q2/ccle_data_19Q2.rds") %>% drop_na(Drug)
+ctrp <- readRDS("./../htscreens_giant_files/ctrp_data_19Q2.rds") %>% drop_na(Drug)
+gdsc <- readRDS("./data_munging/19Q2/gdsc_data_19Q2.rds") %>% drop_na(Drug)
+fus <- readRDS("./data_munging/rds/fusions_merged.rds") %>% drop_na(Drug)
+fus_summary <- fus %>% count(Database, Drug, FusionPair, Fusion_Status)
+prot <- readRDS("./data_munging/rds/protein_changes_merged.rds")
 
-# Filter drug screen datasets for G2P drug-gene-lineage associations
-ccle_data_g2p_dgl <- filter(ccle_data_ptmuts, Drug_Gene_Lin %in% g2p_dgls)
-ccle_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(ccle_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-ctrp_data_g2p_dgl <- filter(ctrp_data_ptmuts, Drug_Gene_Lin %in% g2p_dgls)
-ctrp_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-gdsc_data_g2p_dgl <- filter(gdsc_data_ptmuts, Drug_Gene_Lin %in% g2p_dgls)
-gdsc_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
+crispr <- readRDS("./data_munging/19Q2/crispr_data_19Q2.rds")
 
-# Filter drug screen datasets for G2P drugs and genes
-ccle_data_g2p_grid <- filter(ccle_data_ptmuts, Drug %in% g2p_drugs)
-ccle_data_g2p_grid$Mutation_Status_Nonsilent <- factor(ccle_data_g2p_grid$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-ctrp_data_g2p_grid <- filter(ctrp_data_ptmuts, Drug %in% g2p_drugs)
-ctrp_data_g2p_grid$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p_grid$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-gdsc_data_g2p_grid <- filter(gdsc_data_ptmuts, Drug %in% g2p_drugs)
-gdsc_data_g2p_grid$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p_grid$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-
-# Wilcoxon test results
-ccle_signif_g2p <- readRDS("./data_munging/rds/ccle_signif_g2p_gene.rds")
-ccle_signif_g2p_exp <- e2exp_converter(ccle_signif_g2p$FDR_cutoff[1], p_type = "pk")
-ccle_signif_g2p_grid <- readRDS("./data_munging/rds/ccle_signif_g2p_grid.rds")
-ccle_signif_g2p_grid_exp <- e2exp_converter(ccle_signif_g2p_grid$FDR_cutoff[1], p_type = "pk")
-ccle_signif_g2p_lineage <- readRDS("./data_munging/rds/ccle_signif_g2p_lineage.rds")
-ccle_signif_g2p_lineage_exp <- e2exp_converter(ccle_signif_g2p_lineage$FDR_cutoff[1], p_type = "pk")
-ccle_signif_grid_lineage <- readRDS("./data_munging/rds/ccle_signif_grid_lineage.rds")
-ccle_signif_grid_lineage_exp <- e2exp_converter(ccle_signif_grid_lineage$FDR_cutoff[1], p_type = "pk")
-
-ctrp_signif_g2p <- readRDS("./data_munging/rds/ctrp_signif_g2p_gene.rds")
-ctrp_signif_g2p_exp <- e2exp_converter(ctrp_signif_g2p$FDR_cutoff[1], p_type = "pk")
-ctrp_signif_g2p_grid <- readRDS("./data_munging/rds/ctrp_signif_g2p_grid.rds")
-ctrp_signif_g2p_grid_exp <- e2exp_converter(ctrp_signif_g2p_grid$FDR_cutoff[1], p_type = "pk")
-ctrp_signif_g2p_lineage <- readRDS("./data_munging/rds/ctrp_signif_g2p_lineage.rds")
-ctrp_signif_g2p_lineage_exp <- e2exp_converter(ctrp_signif_g2p_lineage$FDR_cutoff[1], p_type = "pk")
-ctrp_signif_grid_lineage <- readRDS("./data_munging/rds/ctrp_signif_grid_lineage.rds")
-ctrp_signif_grid_lineage_exp <- e2exp_converter(ctrp_signif_grid_lineage$FDR_cutoff[1], p_type = "pk")
-
-gdsc_signif_g2p <- readRDS("./data_munging/rds/gdsc_signif_g2p_gene.rds")
-gdsc_signif_g2p_exp <- e2exp_converter(gdsc_signif_g2p$FDR_cutoff[1], p_type = "pk")
-gdsc_signif_g2p_grid <- readRDS("./data_munging/rds/gdsc_signif_g2p_grid.rds")
-gdsc_signif_g2p_grid_exp <- e2exp_converter(gdsc_signif_g2p_grid$FDR_cutoff[1], p_type = "pk")
-gdsc_signif_g2p_lineage <- readRDS("./data_munging/rds/gdsc_signif_g2p_lineage.rds")
-gdsc_signif_g2p_lineage_exp <- e2exp_converter(gdsc_signif_g2p_lineage$FDR_cutoff[1], p_type = "pk")
-gdsc_signif_grid_lineage <- readRDS("./data_munging/rds/gdsc_signif_grid_lineage.rds")
-gdsc_signif_grid_lineage_exp <- e2exp_converter(gdsc_signif_grid_lineage$FDR_cutoff[1], p_type = "pk")
-
-# Mut summaries
-drug_grid_shared_dg <- union(ccle_signif_g2p_grid[!is.na(ccle_signif_g2p_grid$p.signif.adj),]$Drug_Gene, union(ctrp_signif_g2p_grid[!is.na(ctrp_signif_g2p_grid$p.signif.adj),]$Drug_Gene, gdsc_signif_g2p_grid[!is.na(gdsc_signif_g2p_grid$p.signif.adj),]$Drug_Gene))
-
-# CCLE: GE/CN correlations
-ccle_cor_res <- ccle_data_g2p_grid %>% group_by(Drug_Gene) %>% summarize(
-  Pearson_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs", exact = FALSE)$estimate,
-  Pearson_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs", exact = FALSE)$p.value,
-  Pearson_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs", exact = FALSE)$estimate,
-  Pearson_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs", exact = FALSE)$p.value,
-  Spearman_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs", exact = FALSE)$estimate,
-  Spearman_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs", exact = FALSE)$p.value,
-  Spearman_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs", exact = FALSE)$estimate,
-  Spearman_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs", exact = FALSE)$p.value)
-ccle_cor_res <- merge(g2p_druggene_tally, ccle_cor_res, by = "Drug_Gene", all.y = TRUE)
-ccle_cor_res$n <- ifelse(is.na(ccle_cor_res$n), 0, ccle_cor_res$n)
-ccle_cor_res$InG2P <- ifelse(ccle_cor_res$n != 0, "Yes", "No")
-ccle_cor_res$Dataset <- "CCLE"
-
-# CTRP: GE/CN correlations
-ctrp_cor_res <- ctrp_data_g2p_grid %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs", exact = FALSE)$estimate, Pearson_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs", exact = FALSE)$p.value, Pearson_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs", exact = FALSE)$estimate, Pearson_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs", exact = FALSE)$p.value, Spearman_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs", exact = FALSE)$estimate, Spearman_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs", exact = FALSE)$p.value, Spearman_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs", exact = FALSE)$estimate, Spearman_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs", exact = FALSE)$p.value)
-ctrp_cor_res <- merge(g2p_druggene_tally, ctrp_cor_res, by = "Drug_Gene", all.y = TRUE)
-ctrp_cor_res$n <- ifelse(is.na(ctrp_cor_res$n), 0, ctrp_cor_res$n)
-ctrp_cor_res$InG2P <- ifelse(ctrp_cor_res$n != 0, "Yes", "No")
-ctrp_cor_res$Dataset <- "CTRP"
-
-# GDSC: GE/CN correlations
-gdsc_cor_res <- gdsc_data_g2p_grid %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs", exact = FALSE)$estimate, Pearson_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs", exact = FALSE)$p.value, Pearson_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs", exact = FALSE)$estimate, Pearson_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs", exact = FALSE)$p.value, Spearman_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs", exact = FALSE)$estimate, Spearman_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs", exact = FALSE)$p.value, Spearman_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs", exact = FALSE)$estimate, Spearman_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs", exact = FALSE)$p.value)
-gdsc_cor_res <- merge(g2p_druggene_tally, gdsc_cor_res, by = "Drug_Gene", all.y = TRUE)
-gdsc_cor_res$n <- ifelse(is.na(gdsc_cor_res$n), 0, gdsc_cor_res$n)
-gdsc_cor_res$InG2P <- ifelse(gdsc_cor_res$n != 0, "Yes", "No")
-gdsc_cor_res$Dataset <- "GDSC"
-
-# Dataset counts
-drug_summ <- data.frame(Drug = character(), Dataset_Count = integer(), stringsAsFactors = FALSE)
-for(drug in g2p_drugs) {
-  counter = 0
-  if(drug %in% as.character(unique(ccle_data_g2p$Drug))) { counter <- counter + 1 }
-  if(drug %in% as.character(unique(ctrp_data_g2p$Drug))) { counter <- counter + 1 }
-  if(drug %in% as.character(unique(gdsc_data_g2p$Drug))) { counter <- counter + 1 }
-  drug_summ <- rbind(drug_summ, data.frame(Drug = drug, Dataset_Count = counter))
-}
-```
-
-```{r table-g2p-nonCID, results="asis"}
-summ <- g2p_nonCID %>% group_by(Drug, DrugID) %>% tally() %>% summarize("CID" = DrugID, "N_G2P" = n, "%" = printnum(n / nrow(g2p_nonCID) * 100))
-colnames(summ)[colnames(summ) == "Drug"] <- "Compound"
-summ$Compound[summ$Compound == "egfr"] <- "EGFR"
-summ$Compound[summ$Compound == "mab"] <- "mAb"
-summ <- summ[order(summ$N_G2P),]
-
-apa_table(summ, align = "c", font_size = "small", caption = "Level-A G2P interpretations excluded from analyses", note = "N_G2P (%) = number of associated G2P interpretations, % is out of column total; mAb = monoclonal antibody; NA indicates G2P interpretation does not have an associated compound.")
+crispr_prot <- readRDS("./data_munging/rds/protein_changes_merged.rds")
 ```
@@
 After filtering, `r nrow(g2p_filt)` level-A G2P interpretations were carried forward in subsequent analyses, constituting `r length(g2p_drugs)` unique drugs and `r length(g2p_genes)` unique genes in `r length(g2p_druggenes)` distinct level-A combinations (*Figure 1A: Pink heatmap*).
-The number of level-A interpretations per drug ranged from `r range(g2p_drug_tally$n)[1]` to `r range(g2p_drug_tally$n)[2]` ($M =$ `r printnum(mean(g2p_drug_tally$n))`, $SD =$ `r printnum(sd(g2p_drug_tally$n))`), `r range(g2p_gene_tally$n)[1]` to `r range(g2p_gene_tally$n)[2]` ($M =$ `r printnum(mean(g2p_gene_tally$n))`, $SD =$ `r printnum(sd(g2p_gene_tally$n))`) per gene, and for each level-A drug-gene combination, the range was `r range(g2p_druggene_tally$n)[1]` to `r range(g2p_druggene_tally$n)[2]` ($M =$ `r printnum(mean(g2p_druggene_tally$n))`, $SD =$ `r printnum(sd(g2p_druggene_tally$n))`).
+The number of level-A interpretations per drug ranged from `r range(g2p_drug_tally$n)[1]` to `r range(g2p_drug_tally$n)[2]` ($M =$ `r formatC(mean(g2p_drug_tally$n), digits = 2)`, $SD =$ `r formatC(sd(g2p_drug_tally$n), digits = 2)`), `r range(g2p_gene_tally$n)[1]` to `r range(g2p_gene_tally$n)[2]` ($M =$ `r formatC(mean(g2p_gene_tally$n), digits = 2)`, $SD =$ `r formatC(sd(g2p_gene_tally$n), digits = 2)`) per gene, and for each level-A drug-gene combination, the range was `r range(g2p_druggene_tally$n)[1]` to `r range(g2p_druggene_tally$n)[2]` ($M =$ `r formatC(mean(g2p_druggene_tally$n), digits = 2)`, $SD =$ `r formatC(sd(g2p_druggene_tally$n), digits = 2)`).
 These unique drugs, genes, and combinations are hereafter referred to as G2P drugs, G2P genes, and G2P associations.
 Filtering our screening datasets by these clinical criteria yields panels of potentially clinically relevant omic features.
-Of the `r length(g2p_drugs)` unique G2P drugs, `r nrow(drug_summ[drug_summ$Dataset_Count >= 1,])` of them were screened in at least one of the drug screen datasets, `r nrow(drug_summ[drug_summ$Dataset_Count >= 2,])` drugs were screened in at least two of the three datasets, and only `r nrow(drug_summ[drug_summ$Dataset_Count >= 3,])` were screened in all three datasets.
-The remaining `r nrow(drug_summ[drug_summ$Dataset_Count == 0,])` un-screened G2P drugs suggests an incompleteness of these drug screens, though these projects frequently release new screening data that may include these drugs in future releases.
+Of the `r length(g2p_drugs)` unique G2P drugs, N of them were screened in at least one of the drug screen datasets, N drugs were screened in at least two of the three datasets, and only N were screened in all three datasets.
+The remaining N un-screened G2P drugs suggests an incompleteness of these drug screens, though these projects frequently release new screening data that may include these drugs in future releases.
 
-Using cell-line-specific point mutation annotations from the CCLE, we compared z-score-transformed area under the dose-response curve (AUC) distributions between mutant and wildtype cell lines for all G2P associations tested in the CCLE, CTRP, and GDSC drug screens.
-Of the `r length(g2p_druggenes)` G2P associations, data was available for `r length(ccle_signif_g2p$Drug_Gene)` associations in CCLE, `r length(ctrp_signif_g2p$Drug_Gene)` in CTRP, and `r length(gdsc_signif_g2p$Drug_Gene)` in GDSC.
-Controlling for a false discovery rate (FDR) < 5%, CCLE yielded no significant correlations (Wilcoxon rank-sum tests, `r ccle_signif_g2p_exp`), though the most significant G2P association was `r drugstring2intext_converter(ccle_signif_g2p$Drug_Gene[1], "dg")` (`r e2exp_converter(ccle_signif_g2p$p.adj[1], p_type = "padj")`).
-In CTRP, AUC from `r nrow(filter(ctrp_signif_g2p[!is.na(ctrp_signif_g2p$p.signif.adj),]))` drug-gene associations correlated with the gene's mutation status (`r ctrp_signif_g2p_exp`): `r drugstring2intext_converter(ctrp_signif_g2p$Drug_Gene[1], "dg")` (`r e2exp_converter(ctrp_signif_g2p$p.adj[1], p_type = "padj")`), `r drugstring2intext_converter(ctrp_signif_g2p$Drug_Gene[2], "dg")` (`r e2exp_converter(ctrp_signif_g2p$p.adj[2], p_type = "padj")`), and `r drugstring2intext_converter(ctrp_signif_g2p$Drug_Gene[3], "dg")` (`r e2exp_converter(ctrp_signif_g2p$p.adj[3], p_type = "padj")`).
-`r str_ucfirst(drugstring2intext_converter(gdsc_signif_g2p$Drug_Gene[1], "dg"))` (`r e2exp_converter(gdsc_signif_g2p$p.adj[1], p_type = "padj")`) was the only significant association in GDSC (`r gdsc_signif_g2p_exp`).
+> Mutation status
 
-> **(???) Describe why we compare all pairwise combos rather than filtering for just the drug-gene combos in G2P?**
+> Fusions
 
-To test for potentially novel drug-gene associations, we conducted similar Wilcoxon rank-sum tests for all pairwise combinations of G2P genes and drugs tested in the three drug screens (*Figures 1B: Green heatmaps*).
-At an unadjusted $\alpha = 0.05$, the tests revealed that in CCLE, AUC significantly correlated with mutation status for `r nrow(filter(ccle_signif_g2p_grid, p < 0.05))` out of `r nrow(ccle_signif_g2p_grid)` (`r printnum(nrow(filter(ccle_signif_g2p_grid, p < 0.05)) / nrow(ccle_signif_g2p_grid) * 100)`%) tested drug-gene combinations were significantly different, `r nrow(filter(ctrp_signif_g2p_grid, p < 0.05))` out of `r nrow(ctrp_signif_g2p_grid)` (`r printnum(nrow(filter(ctrp_signif_g2p_grid, p < 0.05)) / nrow(ctrp_signif_g2p_grid) * 100)`%) were significantly different for CTRP, and `r nrow(filter(gdsc_signif_g2p_grid, p < 0.05))` out of `r nrow(gdsc_signif_g2p_grid)` (`r printnum(nrow(filter(gdsc_signif_g2p_grid, p < 0.05)) / nrow(gdsc_signif_g2p_grid) * 100)`%) for GDSC.
+> Copy number
 
-Controlling for a FDR < 5%, `r drugstring2intext_converter(ccle_signif_g2p_grid$Drug_Gene[1], "dg")` (`r e2exp_converter(ccle_signif_g2p_grid$p.adj[1], p_type = "padj")`) was the only significant drug-gene combination tested in CCLE (`r ccle_signif_g2p_grid_exp`).
-CTRP (`r ctrp_signif_g2p_grid_exp`) yielded `r nrow(ctrp_signif_g2p_grid[!is.na(ctrp_signif_g2p_grid$p.signif.adj),])` significant combinations, one of which was selumetinib-*BRAF*.
-There were `r nrow(gdsc_signif_g2p_grid[!is.na(gdsc_signif_g2p_grid$p.signif.adj),])` significant G2P associations in the GDSC dataset (`r gdsc_signif_g2p_grid_exp`).
-Of all the significant correlations between mutation status and AUC across datasets, the only genes represented were *KRAS* and *BRAF* (Figure\ \@ref(fig:drug-venn)).
-Of the `r length(drug_grid_shared_dg)` significant drug-gene associations across datasets, `r length(intersect(drug_grid_shared_dg, g2p_druggenes))` were G2P associations.
-The remaining `r length(drug_grid_shared_dg) - length(intersect(drug_grid_shared_dg, g2p_druggenes))` associations were `r drugstring2intext_converter(setdiff(drug_grid_shared_dg, g2p_druggenes)[1], "dg")` and `r drugstring2intext_converter(setdiff(drug_grid_shared_dg, g2p_druggenes)[2], "dg")`.
-
-> **(???) Trametinib and selumetinib are both *MEK* inhibitors, and pazopanib is a *VEGFR* inhibitor.
-VEGF signaling can influence the MAPK/ERK signaling pathway, which promotes cell proliferation and survival.
-This pathway includes *RAS*, *BRAF*, and *MEK* proteins.**
+> Gene expression
 
@@
 We computed Spearman correlation coefficients ($r_s$) between AUC of each drug-gene association and gene expression (RPKM) and copy number (log$_2$ ratio) of the gene in the association...**(???) need to complete this thought/analysis**
-
-(ref:drug-venn) **Overlap of significant drug-gene associations from CCLE, CTRP, and GDSC**.
-Overlap of drug-gene associations drawn from all pairwise combinations of G2P drugs and G2P genes whose drug effects significantly correlated with (**A**) mutation status, (**B**) gene expression, and (**C**) copy number across CCLE, CTRP, and GDSC.
-
-```{r drug-venn, echo = FALSE, message=FALSE, warning=FALSE, fig.cap='(ref:drug-venn)'}
-knitr::include_graphics("./plots/manuscript/drugscreen_venns.pdf")
-```
-
-> **(???) Cut these next three paragraphs since we cut the analysis, but keep for future reference**
-
-We compared the distribution of level-A G2P associations (*Figure 1A*) and the associated p-values from the mutation status comparisons (*Figure 1B*) with a null distribution of p-values derived from all pairwise combinations of G2P genes and the G2P drugs tested in each dataset, less any of the 88 distinct combinations with G2P interpretations, i.e.
-the non-gray squares in the right heatmap of *Figure 1A (Figure 3A*).
-To formally test concordance between clinically actionable variants and drug screen results, we conducted an independent, two-group t-test to compare the distributions of p-values of drug-gene combinations that either were or were not represented with level-A evidence in G2P, which indicated that the distributions of p-values did not significantly differ for CCLE [t(9) = 0.25, p = 0.81], CTRP [t(51) = 0.85, p = 0.40], nor GDSC [t(47) = -0.56, p = 0.58]  (Table 2).
-This further supports that mutation status is not a robust genomic feature for predicting therapeutic responses.
-
-Similar tests were conducted for the distributions of Pearson correlation coefficients (r) between the number of level-A G2P associations and gene expression (RPKM) and copy number (log2 ratio) of the gene in the association (*Figures 3B-C*).
-Example r derivations are shown in *Figures 2B-C*.
-Absolute values of r were used to simplify extreme values in both directions for testing.
-The difference in the CCLE |r| distributions for both gene expression [t(8) = 1.43, p = 0.19] and copy number [t(8) = 2.48, p = 0.23] were non-significant, which is likely explained by the small sample size since only five G2P drugs were screened in the CCLE dataset.
-For both the CTRP and GDSC screens, |r| values for gene expression correlations were significantly greater for the level-A G2P associations than the null distribution [tCTRP(49) = 3.79, pCTRP < 0.001; tGDSC(44) = 2.97, pGDSC = 0.005].
-The |r| distributions using copy number were also significantly different for CTRP [t(49) = 2.48, p = 0.017] but not for GDSC [t(44) = 1.95, p = 0.058].
-
-In all three datasets for both level-A G2P associations and null distribution associations, there are more significant |r| values when using gene expression as the genomic feature than when using copy number (Table 2), which corresponds with previous work showing that gene expression is an informative molecular feature when assessing drug sensitivity [@jang2014; @sirota2011].
-Additionally, in all cases, there are more significant r values when using copy number than there are significant p-values from the mutation status comparisons.
-Though observational, these results suggest an order of predictive robustness for these three genomic features when used in isolation: Gene expression > copy number > mutation status.
-Additionally, across all three genomic features, CTRP consistently identified a higher percentage of its possible level-A G2P associations than GDSC, and similarly, GDSC identified a higher percentage than CCLE.
-In the CCLE-GDSC debate, inconsistency between the datasets was attributed to the groups using two very different assays for generating AUC measurements though it was undecided which was more accurate [@haibe-kains2013; @jang2014; @weinstein2013].
-Our results provide very preliminary evidence that GDSC is more accurate than CCLE in regards to reproducing clinical associations.
-However, CTRP may be even more accurate than both GDSC and CCLE.
 
@@
 
-In the level-A G2P interpretations, there were `r nrow(g2p_dgl_tally)` unique drug-gene-lineage combinations (DGLs), representing seven of our curated cancer lineages: `r paste(g2p_lins[1:length(g2p_lins) -1], collapse = ", ")`, and `r g2p_lins[length(g2p_lins)]`.
-CCLE had data for `r length(unique(ccle_data_g2p_dgl$Drug_Gene_Lin))` DGLs, CTRP had data for `r length(unique(ctrp_data_g2p_dgl$Drug_Gene_Lin))`, and GDSC had data for `r length(unique(gdsc_data_g2p_dgl$Drug_Gene_Lin))`, yielding a total of `r length(union(union(unique(ccle_data_g2p_dgl$Drug_Gene_Lin), unique(ctrp_data_g2p_dgl$Drug_Gene_Lin)), unique(gdsc_data_g2p_dgl$Drug_Gene_Lin)))` unique DGLs across all three datasets.
-Only `r length(intersect(intersect(unique(ccle_data_g2p_dgl$Drug_Gene_Lin), unique(ctrp_data_g2p_dgl$Drug_Gene_Lin)), unique(gdsc_data_g2p_dgl$Drug_Gene_Lin)))` DGLs were screened in all three datasets.
-
-Prior to correction for an FDR of 5%, 1 DGL, `r drugstring2intext_converter(ccle_signif_g2p_lineage$Drug_Gene_Lin[1], "dgl")`, was identified in the CCLE screen when using mutation status as a correlate ($n =$ `r nrow(ccle_signif_g2p_lineage)`, `r length(unique(ccle_data_g2p_dgl$Drug_Gene_Lin)) - nrow(ccle_signif_g2p_lineage)` DGLs were not analyzed due to lack of mutation annotations in *UGT1A1* in "cancer" lineages), but CTRP ($n =$ `r nrow(ctrp_signif_g2p_lineage)`) and GDSC ($n =$ `r nrow(gdsc_signif_g2p_lineage)`) identified `r nrow(filter(ctrp_signif_g2p_lineage, !is.na(p.signif)))` and `r nrow(filter(gdsc_signif_g2p_lineage, !is.na(p.signif)))`, respectively, in skin cancer, lung cancer, and cancer lineages.
-After Benjamini-Hochberg FDR correction, none of the datasets yielded significant DGL interactions.
-
-> **(???) KS test results: Need to flesh out this section**
-
-(Figure\ \@ref(fig:ksplot))
-
-(ref:ksplot) **Comparison of drug-gene AUC vs.
-gene expression and vs.
-copy number in G2P and non-G2P cell lines**.
-Comparison of Spearman correlation coefficients ($r_s$) derived from copy number (log$_2$ ratio) vs.
-AUC z-scores and gene expression (RPKM) vs.
-AUC z-scores for G2P drug-gene associations.
-Correlation coefficients were grouped by whether or not the associated lineage for each comparison was in a level-A G2P drug-gene-lineage association or not.
-The distributions of these grouped coefficients were compared using Kolmogorov-Smirnov tests to identify whether correlations in G2P lineages were distinct from correlations in non-G2P lineages.
-
-```{r ksplot, echo = FALSE, warning = FALSE, message = FALSE, fig.cap='(ref:ksplot)'}
-knitr::include_graphics("./plots/manuscript/g2p_spearman_ks_res_plot.pdf")
-```
-
 ## Are CRISPR/Cas9 gene essentiality results comparable to those of functional drug screens?
-
-```{r crispr-data, echo = FALSE, include = FALSE, warning = FALSE, message = FALSE}
-crispr_data <- readRDS("./../htscreens_giant_files/crispr_data_18Q4.rds")
-# Filter CRISPR for G2P genes in G2P
-crispr_data_ptmuts <- filter(crispr_data, Hugo_Symbol %in% g2p_genes)
-# Filter G2P CRISPR for point mutations
-crispr_data_ptmuts <- filter(crispr_data_ptmuts, Reference_Allele == 1 | Reference_Allele == 0 | is.na(Reference_Allele))
-crispr_data_ptmuts$Keep_PtMut_Tests <- ifelse(crispr_data_ptmuts$Reference_Allele == 1 | is.na(crispr_data_ptmuts$Reference_Allele), TRUE, ifelse(crispr_data_ptmuts$Tumor_Seq_Allele1 == 1, TRUE, FALSE))
-crispr_data_ptmuts <- filter(crispr_data_ptmuts, Keep_PtMut_Tests == TRUE)
-crispr_data_ptmuts <- subset(crispr_data_ptmuts, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, Genome_Change, Keep_PtMut_Tests))
-crispr_data_g2p <- unique(crispr_data_ptmuts)
-crispr_data_g2p$Hugo_Symbol <- factor(crispr_data_g2p$Hugo_Symbol, levels = g2p_genes)
-crispr_data_g2p$Mutation_Status_Nonsilent <- factor(crispr_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
-
-# Wilcoxon test results
-crispr_signif_g2p_gene <- readRDS("./data_munging/rds/crispr_signif_g2p_gene.rds")
-crispr_signif_g2p_gene_exp <- e2exp_converter(crispr_signif_g2p_gene$FDR_cutoff[1], p_type = "pk")
-crispr_signif_g2p_gene_sig <- filter(crispr_signif_g2p_gene, !is.na(p.signif.adj))
-
-# GE/CN correlations
-crispr_spearman_res_GE <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>% summarize(p = cor.test(y = Score, x = RPKM, method = "spearman", use = "complete.obs", exact = FALSE)$p.value, corr = cor.test(y = Score, x = RPKM, method = "spearman", use = "complete.obs", exact = FALSE)$estimate, Metric = "Gene Expression")
-crispr_spearman_res_GE_sig <- filter(crispr_spearman_res_GE, p < 0.05)
-
-crispr_spearman_res_CN <- crispr_data_g2p %>% group_by(Hugo_Symbol) %>% summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs", exact = FALSE)$p.value, corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs", exact = FALSE)$estimate, Metric = "Copy Number")
-crispr_spearman_res_CN_sig <- filter(crispr_spearman_res_CN, p < 0.05)
-```
-
-(ref:crispr-waterfall) Stuff stuff stuff!
-
-```{r crispr-waterfall, echo = FALSE, message=FALSE, warning=FALSE, fig.cap='(ref:crispr-waterfall)'}
-knitr::include_graphics("./plots/manuscript/crispr_spearman_corr_plot.pdf")
-```
-
-(ref:crispr-venn) **CRISPR sceen results**. Overlap of genes whose gene expression and/or copy number significantly correlated with CERES score (Spearman rank-order correlations).
-
-```{r crispr-venn, echo = FALSE, message=FALSE, warning=FALSE, fig.cap='(ref:crispr-venn)'}
-knitr::include_graphics("./plots/manuscript/crispr_venn.pdf")
-```
-
-The CRISPR screen from the Broad Institute reports gene dependency using CERES scores [@meyers2017], which are generated from sgRNA depletion scores and eliminate bias arising from the effect of copy number variation on Cas9 DNA cleavage.
-The lower the CERES score, the higher the likelihood that the gene is essential in the associated cell line.
-Scores are scaled per cell line such that a score of 0 is the median effect of nonessential genes and -1 is the median effect of common core essential genes.
-Of the `r length(g2p_genes)` G2P genes, only *`r setdiff(g2p_genes, as.character(crispr_signif_g2p_gene$Hugo_Symbol))`* was not targeted by an sgRNA in the CRISPR dataset.
-
-When we don’t account for lineage, Wilcoxon rank-sum tests (`r crispr_signif_g2p_gene_exp`, FDR < 5%) revealed that mutations in `r nrow(crispr_signif_g2p_gene_sig)` gene significantly correlated with CERES score: *`r as.character(crispr_signif_g2p_gene_sig$Hugo_Symbol)[1]`* (`r e2exp_converter(crispr_signif_g2p_gene_sig$p.adj[1], p_type = "padj")`).
-Gene expression (RPKM) of `r nrow(crispr_spearman_res_GE_sig)` out of `r nrow(crispr_spearman_res_GE)` (`r printnum(nrow(crispr_spearman_res_GE_sig) / nrow(crispr_spearman_res_GE) * 100)`%, Spearman rank-order correlations) G2P genes significantly correlated with CERES score, as did copy number (log2-ratio) for `r nrow(crispr_spearman_res_CN_sig)` out of `r nrow(crispr_spearman_res_CN)` (`r printnum(nrow(crispr_spearman_res_CN_sig) / nrow(crispr_spearman_res_CN) * 100)`%, Spearman rank-order correlations) G2P genes (Figure\ \@ref(fig:crispr-waterfall)).
-We see moderate overlap between these genes whose CERES scores significantly correlated with gene expression and with copy number (Figure\ \@ref(fig:crispr-venn)).
-For the purpose of comparison to the drug screen data, if we treat CRISPR knockdown like a small-molecule drug, then these results are more comprehensive than the results from CCLE, CTRP, and GDSC.
-
-> **(???) Lineage????**
-
-## Are known copy number driven associations recapitulated in the drug and CRISPR screens?
-
-If a gene’s response to is copy number driven, we would expect copy number to significantly correlate with AUC and gene essentiality scores, as would gene expression is expression and copy number are associated.
-
-In a lineage-agnostic context of the CRISPR screen, *ERBB2* gene essentiality score had significant negative correlations with *ERBB2* gene expression (`r e2exp_converter(crispr_spearman_res_GE_sig$p[which(crispr_spearman_res_GE_sig$Hugo_Symbol == "ERBB2")], "p")`, $r_s =$ `r printnum(crispr_spearman_res_GE_sig$corr[which(crispr_spearman_res_GE_sig$Hugo_Symbol == "ERBB2")])`) and *ERBB2* copy number (`r e2exp_converter(crispr_spearman_res_CN_sig$p[which(crispr_spearman_res_CN_sig$Hugo_Symbol == "ERBB2")], "p")`, $r_s =$ `r printnum(crispr_spearman_res_CN_sig$corr[which(crispr_spearman_res_CN_sig$Hugo_Symbol == "ERBB2")])`) (*Figure ##2*).
-Notably, gene essentiality of *MET*, which is known to have copy number alterations in some cancers [@an2014; @kim2018], did not significantly correlate with *MET* gene expression nor *MET* copy number.
-*BRCA1* gene essentiality also significantly correlated with both *BRCA1* gene expression (`r e2exp_converter(crispr_spearman_res_GE_sig$p[which(crispr_spearman_res_GE_sig$Hugo_Symbol == "BRCA1")], "p")`, $r_s =$ `r printnum(crispr_spearman_res_GE_sig$corr[which(crispr_spearman_res_GE_sig$Hugo_Symbol == "BRCA1")])`) and *BRCA1* copy number (`r e2exp_converter(crispr_spearman_res_CN_sig$p[which(crispr_spearman_res_CN_sig$Hugo_Symbol == "BRCA1")], "p")`, $r_s =$ `r printnum(crispr_spearman_res_CN_sig$corr[which(crispr_spearman_res_CN_sig$Hugo_Symbol == "BRCA1")])`).
-*BRCA2* gene essentiality significantly correlated *BRCA2* gene expression (`r e2exp_converter(crispr_spearman_res_CN_sig$p[which(crispr_spearman_res_CN_sig$Hugo_Symbol == "BRCA2")], "p")`, $r_s =$ `r printnum(crispr_spearman_res_CN_sig$corr[which(crispr_spearman_res_CN_sig$Hugo_Symbol == "BRCA2")])`) but not *BRCA2* copy number.
-
-## Which genomic features drive KRAS, EGFR, and BRAF drug-gene associations?
-
-> **(???) Should we do this?**
 
@@
 By evaluating how many clinically actionable associations are identified in these large-scale functional screens, we can begin to address best practices for translating discoveries from these tumor models into clinical trials.
-
-\newpage
 
@@
 
-## Drug screen dataset retrieval and harmonization
+## Drug screen dataset retrieval
+
+**Need to update with Poz info**
 
@@
 
-### AUC harmonization
-
-The CCLE reports cell line sensitivity to small molecules as an activity area measured above the dose-response curve (ActArea), while both CTRP and GDSC report small molecule activity as area under the dose-response curve (AUC).
-Since ActArea is reported with a scale of 0 to 8, we converted CCLE’s ActArea values to AUC via
-
-$$AUC=1- \frac{ActArea}{8}$$
-
-All AUC values across the three drug screen datasets were z-score transformed:
-
-$$z = \frac{AUC - \mu_{AUC}}{\sigma_{AUC}}$$
-
-where AUC is the mean AUC across all drug-cell line combinations in the dataset and AUC is the standard deviation.
-
 ## Computational
 
-```{r}
+```{r, include=FALSE}
 r_v <- paste0("v", getRversion())
@@
 
-\newpage
-
 # References
-
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-
-Finally, the APA guidelines require a note at the start of the reference section that explains what an asterisk means. This note can be added at the end of the document as follows.
-
-<div id = "refs"></div>
-\endgroup

### 2019-07-09 19Q2.Rmd
rm old manuscript files, test CRISPR fusions and protein change merges

@@
 crispr <- MergeOmicsG2P(database = "CRISPR", dataframe = crispr_all, maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./data_munging/19Q2/crispr_data_19Q2.rds")
-write.csv.gz(crispr %>% drop_na(Score), "./../htscreens_giant_files/crispr_data_19Q2.csv.gz")
+# write.csv.gz(crispr %>% drop_na(Score), "./../htscreens_giant_files/crispr_data_19Q2.csv.gz")
 ```
@@
 
-crispr_fus_grid <- expand.grid("DepMap_ID" = unique(crispr$DepMap_ID), "FusionPair" = unique(fusions_filt$FusionPair))
-crispr_fus <- merge(merge(crispr, crispr_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "CCLE_name", "CCLE_histology", "Cell_line", "FusionPair"), all = TRUE)
-crispr_fus$Fusion_Status <- ifelse(!is.na(crispr_fus$LeftGene), "Yes", "No")
-crispr_fus$Drug_FusionPair <- ifelse(is.na(crispr_fus$Drug) | is.na(crispr_fus$FusionPair), NA, paste0(crispr_fus$Drug, "_", crispr_fus$FusionPair))
-crispr_fus$G2P_Drug_FusionPair <- ifelse(crispr_fus$Drug_FusionPair %in% unique(as.character(g2p_fus$Drug_FusionPair)), "Yes", "No")
-crispr_fus$G2P_Fusion <- ifelse(crispr_fus$FusionPair %in% unique(as.character(g2p_fus$FusionPair)), "Yes", "No")
-crispr_fus$Database <- "CRISPR"
-
-colnames(crispr_fus)[colnames(crispr_fus) == "AUC_IC50"] <- "Score"
 saveRDS(crispr_fus, "./data_munging/rds/crispr_fusions.rds")
@@
 ```{r merge_crispr_prot, eval=FALSE}
+crispr_all <- read.delim("./data_munging/19Q2/Achilles_gene_effect_20190514.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
+# Remove Entrez gene IDs from colnames
+colnames(crispr_all) <- gsub(" .*", "", colnames(crispr_all))
+colnames(crispr_all)[1] <- "DepMap_ID"
+
 maf_changes_df <- readRDS("./data_munging/19Q2/maf_changes_df_19Q2.rds")

### 2019-07-10 19Q2.Rmd
update protein changes in G2P db and subsequent analyses--no diff

@@
 g2p <- add_column(g2p, Protein_Change = NA, .after = "Mutation")
+g2p <- separate_rows(g2p, Mutation, sep = ",")
 g2p$Protein_Change <- gsub("u'|'| |,|\\[|\\]", "", g2p$Mutation)
@@
 g2p$Gene_Lin <- ifelse(is.na(g2p$Drug) | !is.na(g2p$Gene) | !is.na(g2p$group_general_lineage_name), paste0(g2p$Gene, "_", g2p$group_general_lineage_name), NA)
-
+g2p <- unique(g2p)
 write.csv(g2p, "./data_munging/g2p_db_edited.csv")
@@
 
-```{r}
+```{r, eval = FALSE}
 crispr_fus <- readRDS("./data_munging/rds/crispr_fusions.rds")

### 2019-07-10 19Q2.Rmd
fix G2P curation

@@
 
+g2p <- data.frame(apply(g2p, MARGIN = 2, function(x) gsub("^$", NA, trimws(x))))
+
 # Manually assign biomarker_types based on a combination of biomarker_type derived from the JSON string and patterns in the Feature.Names
@@
   ifelse(!is.na(str_match(string = tolower(g2p$biomarker_type), pattern = "copy number variant|amplification")[,1]) | !is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "copy number variant|amplification")), "Amplification/CNV",
-  ifelse(!is.na(str_match(string = toupper(g2p$Feature.Names), pattern = "[A-Z0-9|A-Z]+-[A-Z0-9|A-Z]+|FUSION")[,1]) & is.na(str_match(string = g2p$Feature.Names, pattern = "[0-9]+-[0-9]+")) | g2p$biomarker_type == "fusion" | g2p$biomarker_type == "rearrange", "Fusion",
+  ifelse(!is.na(str_match(string = toupper(g2p$Feature.Names), pattern = "[A-Z0-9|A-Z]+-[A-Z0-9|A-Z]+|FUSION|POSITIVE")[,1]) & is.na(str_match(string = g2p$Feature.Names, pattern = "[0-9]+-[0-9]+")) | g2p$biomarker_type == "fusion" | g2p$biomarker_type == "rearrange", "Fusion",
   ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "[A-Z][0-9]+([A-Z]|[*])|[0-9A-Z]+ [A-Z][0-9]+|[A-Z][0-9]+$")[,1]), "Mutation",
@@
 g2p$Protein_Change <- gsub("u'|'| |,|\\[|\\]", "", g2p$Mutation)
-g2p$Protein_Change <- ifelse(g2p$Protein_Change == "", str_match(string = g2p$Feature.Names, pattern = "^[A-Z][0-9]+([A-Z]|[*])| [A-Z][0-9]+([A-Z]|[*])|:[A-Z][0-9]+([A-Z]|[*])")[,1], as.character(g2p$Protein_Change))
+g2p$Protein_Change <- ifelse(is.na(g2p$Protein_Change), str_match(string = g2p$Feature.Names, pattern = "^[A-Z][0-9]+([A-Z]|[*])| [A-Z][0-9]+([A-Z]|[*])|:[A-Z][0-9]+([A-Z]|[*])")[,1], as.character(g2p$Protein_Change))
 g2p$Protein_Change <- gsub(":| |c\\..*", "", g2p$Protein_Change)
-g2p$Protein_Change <- ifelse(!is.na(str_match(string = tolower(g2p$Protein_Change), pattern = "exon|expression|frameshift|fusion|methylation|mutation|-")[,1]), NA, as.character(g2p$Protein_Change))
-g2p$Protein_Change <- gsub("^([0-9]+)([A-Z])$", "\\2\\1\\2", g2p$Protein_Change)
-g2p$Protein_Change <- gsub("^([A-Z])([0-9]+)$", "\\1\\2\\1", g2p$Protein_Change)
+g2p$Protein_Change <- ifelse(!is.na(str_match(string = tolower(trimws(g2p$Protein_Change)), pattern = "^$|exon|amplification|expression|frameshift|fusion|methylation|mutation|-")[,1]), NA, as.character(g2p$Protein_Change))
+g2p$Protein_Change <- ifelse(g2p$Feature.Names == "ALK inframe insertion (1151T)", "1151T",
+                      ifelse(g2p$Feature.Names == "MET M995Ifs*19", "M995Ifs*19",
+                      ifelse(g2p$Feature.Names == "RET (618,620,634,768,791,891,918,C634W,M918T)", "C634W;M918T",
+                      ifelse(g2p$Protein_Change == "V600E/K", "V600E;V600K", as.character(g2p$Protein_Change)))))
+g2p <- separate_rows(g2p, Protein_Change, sep = ";")
+g2p$Protein_Change <- gsub("^([0-9]+)([A-Z])$|^KRAS ([0-9]+)([A-Z])$", "\\2\\1\\2", g2p$Protein_Change) # Fix synonymous mut formatting, eg 13G
+g2p$Protein_Change <- gsub("^([A-Z])([0-9]+)$|^KRAS ([A-Z])([0-9]+)$", "\\1\\2\\1", g2p$Protein_Change) # Fix synonymous mut formatting, eg G13
 g2p <- add_column(g2p, Gene_Protein_Change = NA, .after = "Protein_Change")
@@
 # Add association columns
-g2p[g2p == ""] <- NA
 g2p$Drug_Gene <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene), NA, paste0(g2p$Drug, "_", g2p$Gene))
@@
 g2p$Drug_Gene_Lin <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene) | is.na(g2p$group_general_lineage_name), NA, paste0(g2p$Drug, "_", g2p$Gene, "_", g2p$group_general_lineage_name))
-g2p$Gene_Lin <- ifelse(is.na(g2p$Drug) | !is.na(g2p$Gene) | !is.na(g2p$group_general_lineage_name), paste0(g2p$Gene, "_", g2p$group_general_lineage_name), NA)
 g2p <- unique(g2p)
@@
 g2p_dg <- as.character(unique(g2p$Drug_Gene[!is.na(g2p$Drug_Gene)]))
-g2p_gl <- as.character(unique(g2p$Gene_Lin[!is.na(g2p$Gene_Lin)]))
 g2p_drugs <- as.character(unique(g2p$Drug[!is.na(g2p$Drug)]))
@@
 g2p_nodrug <- filter(g2p, is.na(Drug))
+
 g2p_prot <- unique(filter(g2p, !is.na(Gene_Protein_Change) & !is.na(Drug)) %>% select(group_general_lineage_name, Drug, Direction_Curated, Gene, Protein_Change, Gene_Protein_Change))
-g2p_prot$Drug_Gene <- with(g2p_prot, paste0(Drug, "_", Gene))
-g2p_prot$Drug_Gene_Protein_Change <- with(g2p_prot, paste0(Drug, "_", Gene_Protein_Change))
-g2p_prot$Drug_Gene_Protein_Change_Direction <- with(g2p_prot, paste0(Drug_Gene_Protein_Change, "_", Direction_Curated))
-g2p_mut_summ <- g2p_mut %>% count(Drug_Gene, Direction_Curated)
-# g2p_mut_test_n <- g2p_mut_summ %>% count(Drug_Gene) %>% filter(n > 1)
-# g2p_mut_test <- filter(g2p_mut, Drug_Gene %in% as.character(g2p_mut_test_n$Drug_Gene))
 ```
@@
 ```{r}
+g2p_mut_test_n <- g2p_mut_summ %>% count(Drug_Gene) %>% filter(n > 1)
+g2p_mut_test <- filter(g2p_mut, Drug_Gene %in% as.character(g2p_mut_test_n$Drug_Gene))
 test <- g2p %>% drop_na(Drug_Gene, Direction_Curated) %>% count(Drug_Gene, Direction_Curated) %>% count(Drug_Gene) %>% filter(n > 1)
@@
 ```{r load_mut_wilcoxon_rds}
-g2p_mut_4merge <- unique(select(g2p_mut, Drug_Gene, Direction_Curated))
-test <- g2p_mut_4merge %>% filter(Direction_Curated != "none") %>% count(Drug_Gene) %>% filter(n == 2)
-extended_mut_ht_dg <- unique(as.character(test$Drug_Gene))
+g2p_mut_summ <- g2p_mut %>% count(Drug, Gene, Direction_Curated) %>% select(-n)
+g2p_mut_summ_n <- g2p_mut_summ %>% count(Drug, Gene)
+g2p_mut_summ <- merge(g2p_mut_summ, g2p_mut_summ_n, by = c("Drug", "Gene"))
+g2p_mut_summ$Direction_Heatmap <- with(g2p_mut_summ, ifelse(n == 2, "both", ifelse(n == 1 & Direction_Curated == "resistance", "resistance", "sensitivity")))
+g2p_mut_summ <- unique(select(g2p_mut_summ, Drug, Gene, Direction_Heatmap))
 
@@
 ccle_signif_g2p_dg <- readRDS("./data_munging/rds/ccle_signif_g2p_dg.rds")
+ccle_signif_g2p_dg <- merge(ccle_signif_g2p_dg, g2p_mut_summ, by = c("Drug", "Gene"), all.x = TRUE)
 ccle_signif_dgl <- readRDS("./data_munging/rds/ccle_signif_g2p_dgl.rds")
@@
 ctrp_signif_g2p_dg <- readRDS("./data_munging/rds/ctrp_signif_g2p_dg.rds")
+ctrp_signif_g2p_dg <- merge(ctrp_signif_g2p_dg, g2p_mut_summ, by = c("Drug", "Gene"), all.x = TRUE)
 ctrp_signif_dgl <- readRDS("./data_munging/rds/ctrp_signif_g2p_dgl.rds")
@@
 gdsc_signif_g2p_dg <- readRDS("./data_munging/rds/gdsc_signif_g2p_dg.rds")
+gdsc_signif_g2p_dg <- merge(gdsc_signif_g2p_dg, g2p_mut_summ, by = c("Drug", "Gene"), all.x = TRUE)
 gdsc_signif_dgl <- readRDS("./data_munging/rds/gdsc_signif_g2p_dgl.rds")
@@
 ```{r load_fus_wilcoxon_rds}
-g2p_fus_4merge <- unique(select(g2p_fus, Drug_FusionPair, Direction_Curated))
-
 ccle_signif_fus <- readRDS("./data_munging/rds/ccle_signif_fusions.rds")
-# ccle_signif_fus <- merge(ccle_signif_fus, g2p_fus_4merge, by = "Drug_FusionPair", all.x = TRUE)
-
 ctrp_signif_fus <- readRDS("./data_munging/rds/ctrp_signif_fusions.rds")
-# ctrp_signif_fus <- merge(ctrp_signif_fus, g2p_fus_4merge, by = "Drug_FusionPair", all.x = TRUE)
-
 gdsc_signif_fus <- readRDS("./data_munging/rds/gdsc_signif_fusions.rds")
-# gdsc_signif_fus <- merge(gdsc_signif_fus, g2p_fus_4merge, by = "Drug_FusionPair", all.x = TRUE)
 ```
@@
 
-    signif_grid_annot <- dcast(signif_df, Gene ~ Drug, value.var = "InG2P", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
+    signif_grid_annot <- dcast(signif_df, Gene ~ Drug, value.var = "Direction_Heatmap", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
     signif_grid_annot <- signif_grid_annot[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
     signif_grid_annot <- signif_grid_annot[complete.cases(signif_grid_annot), ]
-    signif_grid_annot[signif_grid_annot == "No"] <- ""
-    signif_grid_annot[signif_grid_annot == "Yes"] <- "O"
+    signif_grid_annot[signif_grid_annot == "sensitivity"] <- "O"
   }
@@
                     grid.circle(x = x - width*0.20, y = y - height*0.20, r = radius, default.units = "npc", gp = gpar(fill = "red", col = "black"))
+                  }
+                  if(signif_grid_annot[i, j] == "resistance") {
+                    grid.circle(x = x - width*0.20, y = y + height*0.20, r = radius, default.units = "npc", gp = gpar(fill = "red", col = "black"))
+                  }
+                  if(signif_grid_annot[i, j] == "both") {
+                    grid.circle(x = x - width*0.20, y = y + height*0.20, r = radius, default.units = "npc", gp = gpar(fill = "red", col = "black"))
+                    grid.circle(x = x - width*0.20, y = y - height*0.20, r = radius, default.units = "npc", gp = gpar(fill = "white", col = "black"))
                   }

### 2019-07-18 19Q2.Rmd
update Rmd to reflect new ccl_meta formatting and information

@@
 
-**D. Charytonowicz cell line converter**
-
-This comprehensive cancer cell line information was curated by both Daniel Charytonowicz and myself.
-```{r dan_ccl_database}
+A comprehensive cancer cell line information was curated by both Daniel Charytonowicz and myself.
+
+DepMap 19Q2 update fixed almost all of the inconsistencies of the Primary.Disease column, though there were come capitalization inconsistencies.
+```{r depmap_metadata, eval=FALSE}
 ccl_converter <- read.delim("./data_munging/cell_line_database_v1_20180911.tsv", row.names = 1, sep = "\t", header = TRUE)
@@
 colnames(ccl_histologies) <- c("Cell_line", "CCLE_histology", "TCGA_classification", "CCLE_name", "DepMap_ID")
-```
-
-**DepMap metadata**
-
-DepMap 19Q2 update fixed almost all of the inconsistencies of the Primary.Disease column, though there were come capitalization inconsistencies.
-```{r depmap_metadata, eval=FALSE}
+
 ccl_meta <- read.delim("./data_munging/19Q2/sample_info.csv", sep = ",", header = TRUE, na.strings = c("", NA))
@@
 colnames(ccl_meta) <- c("DepMap_ID", "Cell_line", "CCLE_name", "disease")
-# Remove two rows that contain cell lines with two different histologies
-# The histologies that are kept are verified through matching in Cellosaurus and Cell Model Passports
-# KMH2, haematopoietic_and_lymphoid: https://web.expasy.org/cellosaurus/CVCL_1330, https://cellmodelpassports.sanger.ac.uk/passports/SIDM01018
-# MS1, lung: https://web.expasy.org/cellosaurus/CVCL_1429, https://cellmodelpassports.sanger.ac.uk/passports/SIDM00245
-ccl_meta <- subset(ccl_meta, CCLE_name != "KMH2_THYROID" & CCLE_name != "MS1_SKIN")
 ccl_meta <- subset(ccl_meta, !grepl("MERGED", CCLE_name, fixed = TRUE))
@@
 ccl_meta <- add_column(ccl_meta, CCLE_histology = CCLE_histology, .after = "CCLE_name")
-ccl_meta$disease <- with(ccl_meta, ifelse(disease == " " & CCLE_histology %in% ccl_diseases, as.character(CCLE_histology), as.character(disease)))
-ccl_meta$disease <- with(ccl_meta, ifelse(disease == "ovary", "ovarian",
-                                   ifelse(disease == " " & CCLE_histology == "vulva", "vulva",
-                                   ifelse(disease == " " & CCLE_histology == "stomach", "gastric",
-                                   ifelse(disease == " " & CCLE_histology == "upper_aerodigestive_tract", "upper_aerodigestive_tract",
+ccl_meta$disease <- with(ccl_meta, ifelse(disease == " ", as.character(CCLE_histology), as.character(disease)))
+ccl_meta$disease <- with(ccl_meta, ifelse(disease == " " & CCLE_histology == "vulva", "vulva",
+                                   ifelse(disease == " " & CCLE_histology == "upper_aerodigestive_tract", "upper_aerodigestive",
                                    ifelse(disease == " " & CCLE_histology == "large_intestine", "colorectal",
@@
                                    ifelse(disease == " " & CCLE_histology == "oesophagus", "esophagus",
-                                   ifelse(disease == " " & CCLE_histology == "testis", "embryo", disease)))))))))
-
-write.csv(ccl_meta, "./data_munging/19Q2/sample_info_edit_20190708.csv")
+                                   ifelse(disease == "other" & CCLE_histology == "haematopoietic_and_lymphoid_tissue", "haematopoietic_and_lymphoid", disease)))))))
+
+ccl_meta <- merge(ccl_meta, ccl_histologies, by = c("Cell_line", "CCLE_histology", "DepMap_ID"), all = TRUE)
+ccl_meta$disease <- with(ccl_meta, ifelse(is.na(disease) & !is.na(CCLE_histology), CCLE_histology, disease))
+ccl_meta$disease <- with(ccl_meta, ifelse(CCLE_histology == "large_intestine", "colorectal", 
+                                   ifelse(CCLE_histology == "haematopoietic_and_lymphoid_tissue", "haematopoietic_and_lymphoid",
+                                   ifelse(CCLE_histology == "upper_aerodigestive_tract", "upper_aerodigestive",
+                                   ifelse(CCLE_histology == "oesophagus", "esophagus", 
+                                   ifelse(CCLE_histology == "biliary_tract", "bile_duct",
+                                   ifelse(Cell_line == "GT3TKB", "lung",
+                                   ifelse(disease == "stomach" | CCLE_histology == "stomach", "gastric", disease))))))))
+
+write.csv(ccl_meta, "./data_munging/19Q2/sample_info_edit_20190717.csv")
 ```
@@
 ```{r}
-ccl_meta <- read.delim("./data_munging/19Q2/sample_info_edit_20190708.csv", sep = ",", header = TRUE, row.names = 1)
-```
+ccl_meta <- read.delim("./data_munging/19Q2/sample_info_edit_20190717.csv", sep = ",", header = TRUE, row.names = 1)
+ccl_meta <- ccl_meta %>% select(DepMap_ID, Cell_line, disease)
+ccl_meta <- filter(ccl_meta, DepMap_ID != "ACH-002397")
+```
+
+ACH-002397 (KMH2_THYROID) was removed to align with Pozdeyev et al (2016) cell line name harmonization.
+CTRP only screened KMH2_HAEMATOPOIETIC_AND_LYMPHOID_TISSUE, whereas GDSC screend both KMH2_HAEMATOPOIETIC_AND_LYMPHOID_TISSUE (i.e.
+KM-H2) and KMH2_THYROID (i.e.
+KMH-2).
+During their harmonization process, Pozdeyev et al only kept KM-H2 from GDSC.
+Thus, we removed KMH2_THYROID from further analyses.
 
@@
 
-```{r}
-g2p_mut_test_n <- g2p_mut_summ %>% count(Drug_Gene) %>% filter(n > 1)
-g2p_mut_test <- filter(g2p_mut, Drug_Gene %in% as.character(g2p_mut_test_n$Drug_Gene))
-test <- g2p %>% drop_na(Drug_Gene, Direction_Curated) %>% count(Drug_Gene, Direction_Curated) %>% count(Drug_Gene) %>% filter(n > 1)
-test_g2p <- filter(g2p, Drug_Gene %in% as.character(test$Drug_Gene))
-```
-
 ## Omics
@@
     # Merge metadata
-    data <-  merge(data, select(ccl_meta, Cell_line, CCLE_histology, CCLE_name, DepMap_ID, disease), by = c("Cell_line", "CCLE_histology", "CCLE_name", "DepMap_ID"), all.y = TRUE)
+    data <-  merge(data, ccl_meta, by = "DepMap_ID", all.y = TRUE)
     ## Add columns for G2P drug-gene and drug-gene-lineage sorting
@@
     data$G2P_Drug_Gene_Lin <- ifelse(data$Drug_Gene_Lin %in% g2p_dgl, "Yes", "No")
-    data$Gene_Lin <- paste0(data$Gene, "_", data$Gene, "_", data$disease)
-    data$G2P_Gene_Lin <- ifelse(data$Gene_Lin %in% g2p_gl, "Yes", "No")
     print("Merged metadata.")
@@
     # Merge cell line metadata
-    data <- merge(data, select(ccl_meta, Cell_line, CCLE_histology, CCLE_name, DepMap_ID, disease), by = "DepMap_ID", all.y = TRUE)
+    data <- merge(data, ccl_meta, by = "DepMap_ID", all.y = TRUE)
     print("Merged metadata.")
@@
 auc$Cell_line <- ifelse(auc$Cell_line == "TI73", "T173", auc$Cell_line)
-auc <- merge(ccl_histologies, auc, by = "Cell_line", all.y = TRUE)
+auc <- merge(ccl_meta, auc, by = "Cell_line", all.y = TRUE)
 colnames(auc)[colnames(auc) == "AUC_IC50"] <- "Score"
@@
 
-ccle_all <- auc %>% filter(Database == "CCLE") %>% select(Cell_line, CCLE_histology, TCGA_classification, CCLE_name, DepMap_ID, Drug, Score)
+ccle_all <- auc %>% filter(Database == "CCLE") %>% select(Cell_line, disease, DepMap_ID, Drug, Score)
 saveRDS(ccle_all, "./../htscreens_giant_files/pozdeyev_data/pozdeyev2016_ccle_all_edited.rds", compress = "xz")
-ctrp_all <- auc %>% filter(Database == "CTRP") %>% select(Cell_line, CCLE_histology, TCGA_classification, CCLE_name, DepMap_ID, Drug, Score)
+ctrp_all <- auc %>% filter(Database == "CTRP") %>% select(Cell_line, disease, DepMap_ID, Drug, Score)
 saveRDS(ctrp_all, "./../htscreens_giant_files/pozdeyev_data/pozdeyev2016_ctrp_all_edited.rds", compress = "xz")
-gdsc_all <- auc %>% filter(Database == "GDSC") %>% select(Cell_line, CCLE_histology, TCGA_classification, CCLE_name, DepMap_ID, Drug, Score)
+gdsc_all <- auc %>% filter(Database == "GDSC") %>% select(Cell_line, disease, DepMap_ID, Drug, Score)
 saveRDS(gdsc_all, "./../htscreens_giant_files/pozdeyev_data/pozdeyev2016_gdsc_all_edited.rds", compress = "xz")
@@
 
-ccle_lineages_ha <- merge(data.frame("DepMap_ID" = colnames(ccle_auc_grid)), select(ccl_meta, DepMap_ID, disease), by = "DepMap_ID", all.x = TRUE) %>% `rownames<-`(.[,1]) %>% select(-DepMap_ID)
-ctrp_lineages_ha <- merge(data.frame("DepMap_ID" = colnames(ctrp_auc_grid)), select(ccl_meta, DepMap_ID, disease), by = "DepMap_ID", all.x = TRUE) %>% `rownames<-`(.[,1]) %>% select(-DepMap_ID)
-gdsc_lineages_ha <- merge(data.frame("DepMap_ID" = colnames(gdsc_auc_grid)), select(ccl_meta, DepMap_ID, disease), by = "DepMap_ID", all.x = TRUE) %>% `rownames<-`(.[,1]) %>% select(-DepMap_ID)
+ccle_lineages_ha <- merge(data.frame("DepMap_ID" = colnames(ccle_auc_grid)), ccl_meta, by = "DepMap_ID", all.x = TRUE) %>% `rownames<-`(.[,1]) %>% select(-DepMap_ID)
+ctrp_lineages_ha <- merge(data.frame("DepMap_ID" = colnames(ctrp_auc_grid)), ccl_meta, by = "DepMap_ID", all.x = TRUE) %>% `rownames<-`(.[,1]) %>% select(-DepMap_ID)
+gdsc_lineages_ha <- merge(data.frame("DepMap_ID" = colnames(gdsc_auc_grid)), ccl_meta, by = "DepMap_ID", all.x = TRUE) %>% `rownames<-`(.[,1]) %>% select(-DepMap_ID)
 
@@
 
-# WILCOXON: PanCan
+# WILCOXON
 
@@
 ccle_signif_dgl <- readRDS("./data_munging/rds/ccle_signif_g2p_dgl.rds")
+ccle_signif_dgl <- merge(ccle_signif_dgl, g2p_mut_summ, by = c("Drug", "Gene"), all.x = TRUE)
 
@@
 ctrp_signif_dgl <- readRDS("./data_munging/rds/ctrp_signif_g2p_dgl.rds")
+ctrp_signif_dgl <- merge(ctrp_signif_dgl, g2p_mut_summ, by = c("Drug", "Gene"), all.x = TRUE)
 
@@
 gdsc_signif_dgl <- readRDS("./data_munging/rds/gdsc_signif_g2p_dgl.rds")
-```
-
-## Protein changes
+gdsc_signif_dgl <- merge(gdsc_signif_dgl, g2p_mut_summ, by = c("Drug", "Gene"), all.x = TRUE)
+```
+
+```{r}
+ccle_filt <- filter(ccle, Drug %in% g2p_drugs & Gene %in% g2p_dg_genes)
+ccle_filt$Gene <- factor(ccle_filt$Gene, ordered = FALSE)
+ccle_filt <- unfactorize(ccle_filt)
+
+ctrp_filt <- filter(ctrp, Drug %in% g2p_drugs & Gene %in% g2p_dg_genes)
+ctrp_filt$Gene <- factor(ctrp_filt$Gene, ordered = FALSE)
+ctrp_filt <- unfactorize(ctrp_filt)
+
+gdsc_filt <- filter(gdsc, Drug %in% g2p_drugs & Gene %in% g2p_dg_genes)
+gdsc_filt$Gene <- factor(gdsc_filt$Gene, ordered = FALSE)
+gdsc_filt <- unfactorize(gdsc_filt)
+
+lins <- union(unique(ccle_signif_dgl$disease), union(unique(ctrp_signif_dgl$disease), unique(gdsc_signif_dgl$disease)))
+
+drug_gene_lins <- unique(rbind(select(ccle_signif_dgl, Gene, Drug, disease, Direction_Curated), select(ctrp_signif_dgl, Gene, Drug, disease, Direction_Curated), select(gdsc_signif_dgl, Gene, Drug, disease, Direction_Curated)))
+
+ccle_signif_prot_4plot <- merge(merge(merge(ccle_signif_prot, unique(select(ccle_prot, Drug, Gene_Protein_Change)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(ccle_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE), all_directions,  by = c("Drug", "Gene_Protein_Change"), all.x = TRUE)
+
+ctrp_signif_prot_4plot <- merge(merge(merge(ctrp_signif_prot, unique(select(ctrp_prot, Drug, Gene_Protein_Change)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(ctrp_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE), all_directions,  by = c("Drug", "Gene_Protein_Change"), all.x = TRUE)
+gdsc_signif_prot_4plot <- merge(merge(merge(gdsc_signif_prot, unique(select(gdsc_prot, Drug, Gene_Protein_Change)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(gdsc_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE), all_directions,  by = c("Drug", "Gene_Protein_Change"), all.x = TRUE)
+```
+
+### Protein changes
 
@@
 ```
-
-### Sen vs. Res tests
-
-```{r SvR_direction_datasets, eval=FALSE}
-# CCLE
-ccle_prot_dir <- unique(select(ccle_prot, DepMap_ID, Gene, Cell_line, CCLE_histology, TCGA_classification, CCLE_name, Drug, Drug_Gene, Score, Change_Status, Direction_Curated, Direction_Grouper))
-## Resistance
-ccle_prot_res <- filter(ccle_prot_dir, Direction_Grouper %in% c("No_none", "Yes_none", "No_resistance", "Yes_resistance"))
-ccle_prot_res$Direction_Grouper <- with(ccle_prot_res, ifelse(Direction_Grouper == "Yes_resistance", "Mutated", "Not mutated"))
-## Sensitivity
-ccle_prot_sen <- filter(ccle_prot_dir, Direction_Grouper %in% c("No_none", "Yes_none", "No_sensitivity", "Yes_sensitivity"))
-ccle_prot_sen$Direction_Grouper <- with(ccle_prot_sen, ifelse(Direction_Grouper == "Yes_sensitivity", "Mutated", "Not mutated"))
-saveRDS(ccle_prot_res, "./data_munging/rds/ccle_protein_changes_resistance.rds")
-saveRDS(ccle_prot_sen, "./data_munging/rds/ccle_protein_changes_sensitivity.rds")
-
-# CTRP
-ctrp_prot_dir <- unique(select(ctrp_prot, DepMap_ID, Gene, Cell_line, CCLE_histology, TCGA_classification, CCLE_name, Drug, Drug_Gene, Score, Change_Status, Direction_Curated, Direction_Grouper))
-## Resistance
-ctrp_prot_res <- filter(ctrp_prot_dir, Direction_Grouper %in% c("No_none", "Yes_none", "No_resistance", "Yes_resistance"))
-ctrp_prot_res$Direction_Grouper <- with(ctrp_prot_res, ifelse(Direction_Grouper == "Yes_resistance", "Mutated", "Not mutated"))
-## Sensitivity
-ctrp_prot_sen <- filter(ctrp_prot_dir, Direction_Grouper %in% c("No_none", "Yes_none", "No_sensitivity", "Yes_sensitivity"))
-ctrp_prot_sen$Direction_Grouper <- with(ctrp_prot_sen, ifelse(Direction_Grouper == "Yes_sensitivity", "Mutated", "Not mutated"))
-saveRDS(ctrp_prot_res, "./data_munging/rds/ctrp_protein_changes_resistance.rds")
-saveRDS(ctrp_prot_sen, "./data_munging/rds/ctrp_protein_changes_sensitivity.rds")
-
-# GDSC
-gdsc_prot_dir <- unique(select(gdsc_prot, DepMap_ID, Gene, Cell_line, CCLE_histology, TCGA_classification, CCLE_name, Drug, Drug_Gene, Score, Change_Status, Direction_Curated, Direction_Grouper))
-## Resistance
-gdsc_prot_res <- filter(gdsc_prot_dir, Direction_Grouper %in% c("No_none", "Yes_none", "No_resistance", "Yes_resistance"))
-gdsc_prot_res$Direction_Grouper <- with(gdsc_prot_res, ifelse(Direction_Grouper == "Yes_resistance", "Mutated", "Not mutated"))
-## Sensitivity
-gdsc_prot_sen <- filter(gdsc_prot_dir, Direction_Grouper %in% c("No_none", "Yes_none", "No_sensitivity", "Yes_sensitivity"))
-gdsc_prot_sen$Direction_Grouper <- with(gdsc_prot_sen, ifelse(Direction_Grouper == "Yes_sensitivity", "Mutated", "Not mutated"))
-saveRDS(gdsc_prot_res, "./data_munging/rds/gdsc_protein_changes_resistance.rds")
-saveRDS(gdsc_prot_sen, "./data_munging/rds/gdsc_protein_changes_sensitivity.rds")
-```
-
-```{r prot_SvR_wilcoxon_tests, eval=FALSE}
-# CCLE
-ccle_signif_prot_res <- WilcoxonTestDF(dataframe = ccle_prot_res, grouping = c("Drug", "Gene", "Drug_Gene"), type = "direction", outfile = "./data_munging/rds/ccle_signif_protein_changes_resistance.rds")
-ccle_signif_prot_sen <- WilcoxonTestDF(dataframe = ccle_prot_sen, grouping = c("Drug", "Gene", "Drug_Gene"), type = "direction", outfile = "./data_munging/rds/ccle_signif_protein_changes_sensitivity.rds")
-
-# CTRP
-ctrp_signif_prot_res <- WilcoxonTestDF(dataframe = ctrp_prot_res, grouping = c("Drug", "Gene", "Drug_Gene"), type = "direction", outfile = "./data_munging/rds/ctrp_signif_protein_changes_resistance.rds")
-ctrp_signif_prot_sen <- WilcoxonTestDF(dataframe = ctrp_prot_sen, grouping = c("Drug", "Gene", "Drug_Gene"), type = "direction", outfile = "./data_munging/rds/ctrp_signif_protein_changes_sensitivity.rds")
-
-# GDSC
-gdsc_signif_prot_res <- WilcoxonTestDF(dataframe = gdsc_prot_res, grouping = c("Drug", "Gene", "Drug_Gene"), type = "direction", outfile = "./data_munging/rds/gdsc_signif_protein_changes_resistance.rds")
-gdsc_signif_prot_sen <- WilcoxonTestDF(dataframe = gdsc_prot_sen, grouping = c("Drug", "Gene", "Drug_Gene"), type = "direction", outfile = "./data_munging/rds/gdsc_signif_protein_changes_sensitivity.rds")
-```
-
-```{r load_prot_SvR_wilcoxon_tests}
-ccle_signif_prot_res <- readRDS("./data_munging/rds/ccle_signif_protein_changes_resistance.rds")
-ccle_signif_prot_res$Direction_Test <- "Resistance"
-ccle_signif_prot_sen <- readRDS("./data_munging/rds/ccle_signif_protein_changes_sensitivity.rds")
-ccle_signif_prot_sen$Direction_Test <- "Sensitivity"
-ccle_signif_prot_dir <- bind_rows(ccle_signif_prot_res, ccle_signif_prot_sen)
-
-ctrp_signif_prot_res <- readRDS("./data_munging/rds/ctrp_signif_protein_changes_resistance.rds")
-ctrp_signif_prot_res$Direction_Test <- "Resistance"
-ctrp_signif_prot_sen <- readRDS("./data_munging/rds/ctrp_signif_protein_changes_sensitivity.rds")
-ctrp_signif_prot_sen$Direction_Test <- "Sensitivity"
-ctrp_signif_prot_dir <- bind_rows(ctrp_signif_prot_res, ctrp_signif_prot_sen)
-
-gdsc_signif_prot_res <- readRDS("./data_munging/rds/gdsc_signif_protein_changes_resistance.rds")
-gdsc_signif_prot_res$Direction_Test <- "Resistance"
-gdsc_signif_prot_sen <- readRDS("./data_munging/rds/gdsc_signif_protein_changes_sensitivity.rds")
-gdsc_signif_prot_sen$Direction_Test <- "Sensitivity"
-gdsc_signif_prot_dir <- bind_rows(gdsc_signif_prot_res, gdsc_signif_prot_sen)
-
-ccle_prot_res <- readRDS("./data_munging/rds/ccle_protein_changes_resistance.rds")
-ccle_prot_sen <- readRDS("./data_munging/rds/ccle_protein_changes_sensitivity.rds")
-ctrp_prot_res <- readRDS("./data_munging/rds/ctrp_protein_changes_resistance.rds")
-ctrp_prot_sen <- readRDS("./data_munging/rds/ctrp_protein_changes_sensitivity.rds")
-gdsc_prot_res <- readRDS("./data_munging/rds/gdsc_protein_changes_resistance.rds")
-gdsc_prot_sen <- readRDS("./data_munging/rds/gdsc_protein_changes_sensitivity.rds")
-```
-
-### Exact match tests
 
@@
 # ggsave("./plots/manuscript/gdsc_fus_boxplots.png", gdsc_fus_boxplot, width = 12, height = 5, units = "in")
-```
-
-```{r direction_boxplots}
-# CCLE
-ccle_res_box <- ggplot(data = filter(ccle_prot_res, Drug_Gene %in% ccle_signif_prot_res$Drug_Gene)) +
-  facet_wrap(~ Drug * Gene, nrow = 1) +
-  scale_color_manual(values = c("Mutated" = "springgreen4", "Not mutated" = "palegreen3")) +
-  geom_boxplot(mapping = aes(x = Direction_Grouper, y = Score, color = Direction_Grouper), outlier.shape = NA) +
-  geom_jitter(aes(x = Direction_Grouper, y = Score, color = Direction_Grouper), width = 0.2, alpha = 0.5, size = 0.6) +
-  geom_text(data = ccle_signif_prot_res, aes(x = 1.5, y = 1.05, label = p.signif), size = 7) +
-  coord_cartesian(ylim = c(0, 1.1)) +
-  scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
-  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
-  labs(y = "AUC", x = "Resistance mutation?")
-
-ccle_sen_box <- ggplot(data = filter(ccle_prot_sen, Drug_Gene %in% ccle_signif_prot_sen$Drug_Gene)) +
-  facet_wrap(~ Drug * Gene, nrow = 1) +
-  scale_color_manual(values = c("Mutated" = "springgreen4", "Not mutated" = "palegreen3")) +
-  geom_boxplot(mapping = aes(x = Direction_Grouper, y = Score, color = Direction_Grouper), outlier.shape = NA) +
-  geom_jitter(aes(x = Direction_Grouper, y = Score, color = Direction_Grouper), width = 0.2, alpha = 0.5, size = 0.6) +
-  geom_text(data = ccle_signif_prot_sen, aes(x = 1.5, y = 1.05, label = p.signif), size = 7) +
-  coord_cartesian(ylim = c(0, 1.1)) +
-  scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
-  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
-  labs(y = "AUC", x = "Sensitivity mutation?")
-ccle_dir_boxes <- plot_grid(ccle_res_box, ccle_sen_box, labels = c("A", "B"), rel_widths = c(3, 1.1))
-ggsave("./plots/manuscript/ccle_direction_boxplots.png", ccle_dir_boxes, device = "png", dpi = 450, width = 12, height = 5, units = "in")
-
-# CTRP
-ctrp_res_box <- ggplot(data = filter(ctrp_prot_res, Drug_Gene %in% ctrp_signif_prot_res$Drug_Gene)) +
-  facet_wrap(~ Drug * Gene, nrow = 1) +
-  scale_color_manual(values = c("Mutated" = "steelblue4", "Not mutated" = "slategray3")) +
-  geom_boxplot(mapping = aes(x = Direction_Grouper, y = Score, color = Direction_Grouper), outlier.shape = NA) +
-  geom_jitter(aes(x = Direction_Grouper, y = Score, color = Direction_Grouper), width = 0.2, alpha = 0.5, size = 0.6) +
-  geom_text(data = ctrp_signif_prot_res, aes(x = 1.5, y = 1.05, label = p.signif), size = 7) +
-  coord_cartesian(ylim = c(0, 1.1)) +
-  scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
-  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
-  labs(y = "AUC", x = "Resistance mutation?")
-
-ctrp_sen_box <- ggplot(data = filter(ctrp_prot_sen, Drug_Gene %in% ctrp_signif_prot_sen$Drug_Gene)) +
-  facet_wrap(~ Drug * Gene, nrow = 1) +
-  scale_color_manual(values = c("Mutated" = "steelblue4", "Not mutated" = "slategray3")) +
-  geom_boxplot(mapping = aes(x = Direction_Grouper, y = Score, color = Direction_Grouper), outlier.shape = NA) +
-  geom_jitter(aes(x = Direction_Grouper, y = Score, color = Direction_Grouper), width = 0.2, alpha = 0.5, size = 0.6) +
-  geom_text(data = ctrp_signif_prot_sen, aes(x = 1.5, y = 1.05, label = p.signif), size = 7) +
-  coord_cartesian(ylim = c(0, 1.1)) +
-  scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
-  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
-  labs(y = "AUC", x = "Sensitivity mutation?")
-ctrp_dir_boxes <- plot_grid(ctrp_res_box, ctrp_sen_box, labels = c("A", "B"), ncol = 1)
-ggsave("./plots/manuscript/ctrp_direction_boxplots.png", ctrp_dir_boxes, device = "png", dpi = 450, width = 12, height = 8, units = "in")
-
-# GDSC
-gdsc_res_box <- ggplot(data = filter(gdsc_prot_res, Drug_Gene %in% gdsc_signif_prot_res$Drug_Gene)) +
-  facet_wrap(~ Drug * Gene, nrow = 1) +
-  scale_color_manual(values = c("Mutated" = "turquoise4", "Not mutated" = "paleturquoise3")) +
-  geom_boxplot(mapping = aes(x = Direction_Grouper, y = Score, color = Direction_Grouper), outlier.shape = NA) +
-  geom_jitter(aes(x = Direction_Grouper, y = Score, color = Direction_Grouper), width = 0.2, alpha = 0.5, size = 0.6) +
-  geom_text(data = gdsc_signif_prot_res, aes(x = 1.5, y = 1.05, label = p.signif), size = 7) +
-  coord_cartesian(ylim = c(0, 1.1)) +
-  scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
-  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
-  labs(y = "AUC", x = "Resistance mutation?")
-
-gdsc_sen_box <- ggplot(data = filter(gdsc_prot_sen, Drug_Gene %in% gdsc_signif_prot_sen$Drug_Gene)) +
-  facet_wrap(~ Drug * Gene, nrow = 1) +
-  scale_color_manual(values = c("Mutated" = "turquoise4", "Not mutated" = "paleturquoise3")) +
-  geom_boxplot(mapping = aes(x = Direction_Grouper, y = Score, color = Direction_Grouper), outlier.shape = NA) +
-  geom_jitter(aes(x = Direction_Grouper, y = Score, color = Direction_Grouper), width = 0.2, alpha = 0.5, size = 0.6) +
-  geom_text(data = gdsc_signif_prot_sen, aes(x = 1.5, y = 1.05, label = p.signif), size = 7) +
-  coord_cartesian(ylim = c(0, 1.1)) +
-  scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
-  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
-  labs(y = "AUC", x = "Sensitivity mutation?")
-gdsc_dir_boxes <- plot_grid(gdsc_res_box, gdsc_sen_box, labels = c("A", "B"), rel_widths = c(2, 1.1))
-ggsave("./plots/manuscript/gdsc_direction_boxplots.png", gdsc_dir_boxes, device = "png", dpi = 450, width = 12, height = 5, units = "in")
 ```
@@
 
+### Pancan
+
 ```{r mut_heatmaps, eval=FALSE, fig.height=10, fig.width=3}
@@
 dev.off()
+```
+
+### Lieage
+
+```{r}
+MakeWilcoxonLineageHeatmap <- function(all_lin_df, lineage) {
+  use_data <- filter(all_lin_df, Gene %in% unique(g2p_mut$Gene) & disease == lineage)
+  ccle_df <- filter(use_data, Database == "CCLE")
+  ctrp_df <- filter(use_data, Database == "CTRP")
+  gdsc_df <- filter(use_datas, Database == "GDSC")
+
+  ht_ccle <- MakeWilcoxonHeatmap(signif_df = ccle_df, feature = "mutation", legend_title = "CCLE -log10(p-value)                                                                     ", legend_breaks = seq(0, 5, by = 1), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Genes", radius = 0.03)
+
+  ht_ctrp <- MakeWilcoxonHeatmap(signif_df = ctrp_df, feature = "mutation", legend_title = "CTRP -log10(p-value)                                                                    ", legend_breaks = seq(0, 12, by = 2), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.008)
+
+  ht_gdsc <- MakeWilcoxonHeatmap(signif_df = gdsc_df, feature = "mutation", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 6, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes", radius = 0.015)
+
+  ht <- ht_ccle + ht_ctrp + ht_gdsc
+  return(ht)
+}
+```
+
+```
+lin_ht <- lapply(lineages, makeDrugBoxplots, dataset = "CCLE")
+ccle_lvlA_drugboxplot_paths <- paste0(ccle_drugs, "_ccle_boxplots.png")
+pwalk(list(ccle_lvlA_drugboxplot_paths, ccle_lvlA_drugboxplots), ggsave, path = "./plots_18Q3/manuscript/ccle_lvlA_boxplots", dpi = 450, width = 12, height = 7, units = "in")
+
+ draw(ht_ccle2 + ht_ctrp2 + ht_gdsc2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
 ```
@@
 
-# WILCOXON: Lineages
+# SPEARMAN: Lineages
 
@@
 
-# SPEARMAN: Lineages
+## GE/CN
+
+# OLD
 
@@
 
-## GE/CN
+## Mut: Sen vs. Res tests
+
+```{r SvR_direction_datasets, eval=FALSE}
+# CCLE
+ccle_prot_dir <- unique(select(ccle_prot, DepMap_ID, Gene, Cell_line, CCLE_histology, TCGA_classification, CCLE_name, Drug, Drug_Gene, Score, Change_Status, Direction_Curated, Direction_Grouper))
+## Resistance
+ccle_prot_res <- filter(ccle_prot_dir, Direction_Grouper %in% c("No_none", "Yes_none", "No_resistance", "Yes_resistance"))
+ccle_prot_res$Direction_Grouper <- with(ccle_prot_res, ifelse(Direction_Grouper == "Yes_resistance", "Mutated", "Not mutated"))
+## Sensitivity
+ccle_prot_sen <- filter(ccle_prot_dir, Direction_Grouper %in% c("No_none", "Yes_none", "No_sensitivity", "Yes_sensitivity"))
+ccle_prot_sen$Direction_Grouper <- with(ccle_prot_sen, ifelse(Direction_Grouper == "Yes_sensitivity", "Mutated", "Not mutated"))
+saveRDS(ccle_prot_res, "./data_munging/rds/ccle_protein_changes_resistance.rds")
+saveRDS(ccle_prot_sen, "./data_munging/rds/ccle_protein_changes_sensitivity.rds")
+
+# CTRP
+ctrp_prot_dir <- unique(select(ctrp_prot, DepMap_ID, Gene, Cell_line, CCLE_histology, TCGA_classification, CCLE_name, Drug, Drug_Gene, Score, Change_Status, Direction_Curated, Direction_Grouper))
+## Resistance
+ctrp_prot_res <- filter(ctrp_prot_dir, Direction_Grouper %in% c("No_none", "Yes_none", "No_resistance", "Yes_resistance"))
+ctrp_prot_res$Direction_Grouper <- with(ctrp_prot_res, ifelse(Direction_Grouper == "Yes_resistance", "Mutated", "Not mutated"))
+## Sensitivity
+ctrp_prot_sen <- filter(ctrp_prot_dir, Direction_Grouper %in% c("No_none", "Yes_none", "No_sensitivity", "Yes_sensitivity"))
+ctrp_prot_sen$Direction_Grouper <- with(ctrp_prot_sen, ifelse(Direction_Grouper == "Yes_sensitivity", "Mutated", "Not mutated"))
+saveRDS(ctrp_prot_res, "./data_munging/rds/ctrp_protein_changes_resistance.rds")
+saveRDS(ctrp_prot_sen, "./data_munging/rds/ctrp_protein_changes_sensitivity.rds")
+
+# GDSC
+gdsc_prot_dir <- unique(select(gdsc_prot, DepMap_ID, Gene, Cell_line, CCLE_histology, TCGA_classification, CCLE_name, Drug, Drug_Gene, Score, Change_Status, Direction_Curated, Direction_Grouper))
+## Resistance
+gdsc_prot_res <- filter(gdsc_prot_dir, Direction_Grouper %in% c("No_none", "Yes_none", "No_resistance", "Yes_resistance"))
+gdsc_prot_res$Direction_Grouper <- with(gdsc_prot_res, ifelse(Direction_Grouper == "Yes_resistance", "Mutated", "Not mutated"))
+## Sensitivity
+gdsc_prot_sen <- filter(gdsc_prot_dir, Direction_Grouper %in% c("No_none", "Yes_none", "No_sensitivity", "Yes_sensitivity"))
+gdsc_prot_sen$Direction_Grouper <- with(gdsc_prot_sen, ifelse(Direction_Grouper == "Yes_sensitivity", "Mutated", "Not mutated"))
+saveRDS(gdsc_prot_res, "./data_munging/rds/gdsc_protein_changes_resistance.rds")
+saveRDS(gdsc_prot_sen, "./data_munging/rds/gdsc_protein_changes_sensitivity.rds")
+```
+
+```{r prot_SvR_wilcoxon_tests, eval=FALSE}
+# CCLE
+ccle_signif_prot_res <- WilcoxonTestDF(dataframe = ccle_prot_res, grouping = c("Drug", "Gene", "Drug_Gene"), type = "direction", outfile = "./data_munging/rds/ccle_signif_protein_changes_resistance.rds")
+ccle_signif_prot_sen <- WilcoxonTestDF(dataframe = ccle_prot_sen, grouping = c("Drug", "Gene", "Drug_Gene"), type = "direction", outfile = "./data_munging/rds/ccle_signif_protein_changes_sensitivity.rds")
+
+# CTRP
+ctrp_signif_prot_res <- WilcoxonTestDF(dataframe = ctrp_prot_res, grouping = c("Drug", "Gene", "Drug_Gene"), type = "direction", outfile = "./data_munging/rds/ctrp_signif_protein_changes_resistance.rds")
+ctrp_signif_prot_sen <- WilcoxonTestDF(dataframe = ctrp_prot_sen, grouping = c("Drug", "Gene", "Drug_Gene"), type = "direction", outfile = "./data_munging/rds/ctrp_signif_protein_changes_sensitivity.rds")
+
+# GDSC
+gdsc_signif_prot_res <- WilcoxonTestDF(dataframe = gdsc_prot_res, grouping = c("Drug", "Gene", "Drug_Gene"), type = "direction", outfile = "./data_munging/rds/gdsc_signif_protein_changes_resistance.rds")
+gdsc_signif_prot_sen <- WilcoxonTestDF(dataframe = gdsc_prot_sen, grouping = c("Drug", "Gene", "Drug_Gene"), type = "direction", outfile = "./data_munging/rds/gdsc_signif_protein_changes_sensitivity.rds")
+```
+
+```{r load_prot_SvR_wilcoxon_tests}
+ccle_signif_prot_res <- readRDS("./data_munging/rds/ccle_signif_protein_changes_resistance.rds")
+ccle_signif_prot_res$Direction_Test <- "Resistance"
+ccle_signif_prot_sen <- readRDS("./data_munging/rds/ccle_signif_protein_changes_sensitivity.rds")
+ccle_signif_prot_sen$Direction_Test <- "Sensitivity"
+ccle_signif_prot_dir <- bind_rows(ccle_signif_prot_res, ccle_signif_prot_sen)
+
+ctrp_signif_prot_res <- readRDS("./data_munging/rds/ctrp_signif_protein_changes_resistance.rds")
+ctrp_signif_prot_res$Direction_Test <- "Resistance"
+ctrp_signif_prot_sen <- readRDS("./data_munging/rds/ctrp_signif_protein_changes_sensitivity.rds")
+ctrp_signif_prot_sen$Direction_Test <- "Sensitivity"
+ctrp_signif_prot_dir <- bind_rows(ctrp_signif_prot_res, ctrp_signif_prot_sen)
+
+gdsc_signif_prot_res <- readRDS("./data_munging/rds/gdsc_signif_protein_changes_resistance.rds")
+gdsc_signif_prot_res$Direction_Test <- "Resistance"
+gdsc_signif_prot_sen <- readRDS("./data_munging/rds/gdsc_signif_protein_changes_sensitivity.rds")
+gdsc_signif_prot_sen$Direction_Test <- "Sensitivity"
+gdsc_signif_prot_dir <- bind_rows(gdsc_signif_prot_res, gdsc_signif_prot_sen)
+
+ccle_prot_res <- readRDS("./data_munging/rds/ccle_protein_changes_resistance.rds")
+ccle_prot_sen <- readRDS("./data_munging/rds/ccle_protein_changes_sensitivity.rds")
+ctrp_prot_res <- readRDS("./data_munging/rds/ctrp_protein_changes_resistance.rds")
+ctrp_prot_sen <- readRDS("./data_munging/rds/ctrp_protein_changes_sensitivity.rds")
+gdsc_prot_res <- readRDS("./data_munging/rds/gdsc_protein_changes_resistance.rds")
+gdsc_prot_sen <- readRDS("./data_munging/rds/gdsc_protein_changes_sensitivity.rds")
+```
+
+```{r direction_boxplots, eval=FALSE}
+# CCLE
+ccle_res_box <- ggplot(data = filter(ccle_prot_res, Drug_Gene %in% ccle_signif_prot_res$Drug_Gene)) +
+  facet_wrap(~ Drug * Gene, nrow = 1) +
+  scale_color_manual(values = c("Mutated" = "springgreen4", "Not mutated" = "palegreen3")) +
+  geom_boxplot(mapping = aes(x = Direction_Grouper, y = Score, color = Direction_Grouper), outlier.shape = NA) +
+  geom_jitter(aes(x = Direction_Grouper, y = Score, color = Direction_Grouper), width = 0.2, alpha = 0.5, size = 0.6) +
+  geom_text(data = ccle_signif_prot_res, aes(x = 1.5, y = 1.05, label = p.signif), size = 7) +
+  coord_cartesian(ylim = c(0, 1.1)) +
+  scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
+  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
+  labs(y = "AUC", x = "Resistance mutation?")
+
+ccle_sen_box <- ggplot(data = filter(ccle_prot_sen, Drug_Gene %in% ccle_signif_prot_sen$Drug_Gene)) +
+  facet_wrap(~ Drug * Gene, nrow = 1) +
+  scale_color_manual(values = c("Mutated" = "springgreen4", "Not mutated" = "palegreen3")) +
+  geom_boxplot(mapping = aes(x = Direction_Grouper, y = Score, color = Direction_Grouper), outlier.shape = NA) +
+  geom_jitter(aes(x = Direction_Grouper, y = Score, color = Direction_Grouper), width = 0.2, alpha = 0.5, size = 0.6) +
+  geom_text(data = ccle_signif_prot_sen, aes(x = 1.5, y = 1.05, label = p.signif), size = 7) +
+  coord_cartesian(ylim = c(0, 1.1)) +
+  scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
+  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
+  labs(y = "AUC", x = "Sensitivity mutation?")
+ccle_dir_boxes <- plot_grid(ccle_res_box, ccle_sen_box, labels = c("A", "B"), rel_widths = c(3, 1.1))
+ggsave("./plots/manuscript/ccle_direction_boxplots.png", ccle_dir_boxes, device = "png", dpi = 450, width = 12, height = 5, units = "in")
+
+# CTRP
+ctrp_res_box <- ggplot(data = filter(ctrp_prot_res, Drug_Gene %in% ctrp_signif_prot_res$Drug_Gene)) +
+  facet_wrap(~ Drug * Gene, nrow = 1) +
+  scale_color_manual(values = c("Mutated" = "steelblue4", "Not mutated" = "slategray3")) +
+  geom_boxplot(mapping = aes(x = Direction_Grouper, y = Score, color = Direction_Grouper), outlier.shape = NA) +
+  geom_jitter(aes(x = Direction_Grouper, y = Score, color = Direction_Grouper), width = 0.2, alpha = 0.5, size = 0.6) +
+  geom_text(data = ctrp_signif_prot_res, aes(x = 1.5, y = 1.05, label = p.signif), size = 7) +
+  coord_cartesian(ylim = c(0, 1.1)) +
+  scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
+  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
+  labs(y = "AUC", x = "Resistance mutation?")
+
+ctrp_sen_box <- ggplot(data = filter(ctrp_prot_sen, Drug_Gene %in% ctrp_signif_prot_sen$Drug_Gene)) +
+  facet_wrap(~ Drug * Gene, nrow = 1) +
+  scale_color_manual(values = c("Mutated" = "steelblue4", "Not mutated" = "slategray3")) +
+  geom_boxplot(mapping = aes(x = Direction_Grouper, y = Score, color = Direction_Grouper), outlier.shape = NA) +
+  geom_jitter(aes(x = Direction_Grouper, y = Score, color = Direction_Grouper), width = 0.2, alpha = 0.5, size = 0.6) +
+  geom_text(data = ctrp_signif_prot_sen, aes(x = 1.5, y = 1.05, label = p.signif), size = 7) +
+  coord_cartesian(ylim = c(0, 1.1)) +
+  scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
+  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
+  labs(y = "AUC", x = "Sensitivity mutation?")
+ctrp_dir_boxes <- plot_grid(ctrp_res_box, ctrp_sen_box, labels = c("A", "B"), ncol = 1)
+ggsave("./plots/manuscript/ctrp_direction_boxplots.png", ctrp_dir_boxes, device = "png", dpi = 450, width = 12, height = 8, units = "in")
+
+# GDSC
+gdsc_res_box <- ggplot(data = filter(gdsc_prot_res, Drug_Gene %in% gdsc_signif_prot_res$Drug_Gene)) +
+  facet_wrap(~ Drug * Gene, nrow = 1) +
+  scale_color_manual(values = c("Mutated" = "turquoise4", "Not mutated" = "paleturquoise3")) +
+  geom_boxplot(mapping = aes(x = Direction_Grouper, y = Score, color = Direction_Grouper), outlier.shape = NA) +
+  geom_jitter(aes(x = Direction_Grouper, y = Score, color = Direction_Grouper), width = 0.2, alpha = 0.5, size = 0.6) +
+  geom_text(data = gdsc_signif_prot_res, aes(x = 1.5, y = 1.05, label = p.signif), size = 7) +
+  coord_cartesian(ylim = c(0, 1.1)) +
+  scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
+  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
+  labs(y = "AUC", x = "Resistance mutation?")
+
+gdsc_sen_box <- ggplot(data = filter(gdsc_prot_sen, Drug_Gene %in% gdsc_signif_prot_sen$Drug_Gene)) +
+  facet_wrap(~ Drug * Gene, nrow = 1) +
+  scale_color_manual(values = c("Mutated" = "turquoise4", "Not mutated" = "paleturquoise3")) +
+  geom_boxplot(mapping = aes(x = Direction_Grouper, y = Score, color = Direction_Grouper), outlier.shape = NA) +
+  geom_jitter(aes(x = Direction_Grouper, y = Score, color = Direction_Grouper), width = 0.2, alpha = 0.5, size = 0.6) +
+  geom_text(data = gdsc_signif_prot_sen, aes(x = 1.5, y = 1.05, label = p.signif), size = 7) +
+  coord_cartesian(ylim = c(0, 1.1)) +
+  scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
+  theme(legend.position = "none", axis.title.y = element_blank(), axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
+  labs(y = "AUC", x = "Sensitivity mutation?")
+gdsc_dir_boxes <- plot_grid(gdsc_res_box, gdsc_sen_box, labels = c("A", "B"), rel_widths = c(2, 1.1))
+ggsave("./plots/manuscript/gdsc_direction_boxplots.png", gdsc_dir_boxes, device = "png", dpi = 450, width = 12, height = 5, units = "in")
+```
 

### 2019-07-19 19Q2.Rmd
update Rmd

@@
 colnames(ccl_converter)[colnames(ccl_converter) == "Broad_ID"] <- "DepMap_ID"
-ccl_lineage_converter <- unique(ccl_converter[, c("DepMap_ID", "grouped_general_doid", "group_general_lineage_name")])
-lineage_converter <- unique(select(ccl_lineage_converter, grouped_general_doid, group_general_lineage_name))
+lineage_converter <- unique(ccl_converter[, c("DepMap_ID", "grouped_general_doid", "group_general_lineage_name")])
+
+# OLD CCL_META
 ccl_histologies <- read.delim("./data_munging/ccl_histologies_metadata.csv", sep = ",", header = TRUE, row.names = 1)
 colnames(ccl_histologies) <- c("Cell_line", "CCLE_histology", "TCGA_classification", "CCLE_name", "DepMap_ID")
-
 ccl_meta <- read.delim("./data_munging/19Q2/sample_info.csv", sep = ",", header = TRUE, na.strings = c("", NA))
@@
 
-ccl_meta <- merge(ccl_meta, ccl_histologies, by = c("Cell_line", "CCLE_histology", "DepMap_ID"), all = TRUE)
+ccl_meta <- merge(merge(ccl_meta, ccl_histologies, by = c("Cell_line", "CCLE_histology", "CCLE_name", "DepMap_ID"), all = TRUE), lineage_converter, by = "DepMap_ID", all = TRUE)
 ccl_meta$disease <- with(ccl_meta, ifelse(is.na(disease) & !is.na(CCLE_histology), CCLE_histology, disease))
@@
                                    ifelse(disease == "stomach" | CCLE_histology == "stomach", "gastric", disease))))))))
-
-write.csv(ccl_meta, "./data_munging/19Q2/sample_info_edit_20190717.csv")
+write.csv(ccl_meta, "./data_munging/19Q2/sample_info_edit_20190718.csv")
 ```
@@
 ccl_meta <- filter(ccl_meta, DepMap_ID != "ACH-002397")
+ccl_unique <- data.frame(disease = unique(ccl_meta$disease))
 ```
@@
   ifelse(!is.na(str_match(string = tolower(g2p$biomarker_type), pattern = "copy number variant|amplification")[,1]) | !is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "copy number variant|amplification")), "Amplification/CNV",
-  ifelse(!is.na(str_match(string = toupper(g2p$Feature.Names), pattern = "[A-Z0-9|A-Z]+-[A-Z0-9|A-Z]+|FUSION|POSITIVE")[,1]) & is.na(str_match(string = g2p$Feature.Names, pattern = "[0-9]+-[0-9]+")) | g2p$biomarker_type == "fusion" | g2p$biomarker_type == "rearrange", "Fusion",
+  ifelse(!is.na(str_match(string = toupper(g2p$Feature.Names), pattern = "[A-Z0-9|A-Z]+-[A-Z0-9|A-Z]+|FUSION|ALK POSITIVE")[,1]) & is.na(str_match(string = g2p$Feature.Names, pattern = "[0-9]+-[0-9]+")) | g2p$biomarker_type == "fusion" | g2p$biomarker_type == "rearrange", "Fusion",
   ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "[A-Z][0-9]+([A-Z]|[*])|[0-9A-Z]+ [A-Z][0-9]+|[A-Z][0-9]+$")[,1]), "Mutation",
-  ifelse(!is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "expression|methylation")[,1]), "Expression",
+  ifelse(!is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "expression|methylation|erbb2  positive")[,1]), "Expression",
   ifelse(!is.na(str_match(string = g2p$biomarker_type, pattern = "intron|insertion|deletion|mutant")[,1]), "Mutation",
@@
 
+# Curate lineage column
+g2p <- separate_rows(g2p, Phenotype.Description, sep = ";")
+g2p_lineages <- cbind(unique(select(g2p, Phenotype.Description, Phenotype.Family)), disease = NA)
+g2p_lineages$disease <- with(g2p_lineages, ifelse(!is.na(str_match(string = tolower(Phenotype.Family), pattern = "astrocytoma|central nervous system|glioma")[,1]) | !is.na(str_match(string = tolower(Phenotype.Description), pattern = "astrocytoma|glioblastoma|craniopharyngioma|medulloblastoma")[,1]), "central_nervous_system",
+                                           ifelse(Phenotype.Family %in% c("breast cancer") | Phenotype.Description %in% c("breast cancer", "Her2-receptor positive breast cancer", "invasive ductal carcinoma"), "breast",
+                                           ifelse(!is.na(str_match(string = tolower(Phenotype.Family), pattern = "lymphoma|bone marrow|hematologic|immune system|leukemia")[,1]) | !is.na(str_match(string = tolower(Phenotype.Description), pattern = "leukemia|lymphoproliferative|myelodisplasic|systemic mastocytosis|hyper eosinophilic|waldenström macroglobulinemia|langerhans")[,1]), "haematopoietic_and_lymphoid",
+                                           ifelse(Phenotype.Family %in% c("kidney cancer", "Nephrotic syndrome") | !is.na(str_match(string = tolower(Phenotype.Description), pattern = "renal|kidney")[,1]), "kidney",
+                                           ifelse(Phenotype.Family %in% c("liver cancer"), "liver",
+                                           ifelse(Phenotype.Family %in% c("lung cancer", "respiratory system cancer"), "lung",
+                                           ifelse(Phenotype.Description %in% c("congenital fibrosarcoma", "synovial sarcoma", "myxoid liposarcoma", "liposarcoma"), "soft_tissue",
+                                           ifelse(Phenotype.Family %in% c("integumentary system cancer", "skin cancer") | Phenotype.Description %in% c("basal cell carcinoma", "Basal cell carcinoma", "Dermatofibrosarcoma", "dermatofibrosarcoma protuberans", "melanoma", "skin melanoma", "squamous cell carcinoma"), "skin",
+                                           ifelse(Phenotype.Family %in% c("peripheral nervous system neoplasm"), "peripheral_nervous_system",
+                                           ifelse(Phenotype.Family %in% c("urinary bladder cancer"), "urinary_tract", 
+                                           ifelse(!is.na(str_match(string = tolower(Phenotype.Description), pattern = "thyroid|papillary carcinoma")[,1]), "thyroid", 
+                                           ifelse(Phenotype.Description %in% c("ovarian cancer"), "ovary", 
+                                           ifelse(Phenotype.Description %in% c("rectal neoplasm"), "colorectal",
+                                           ifelse(Phenotype.Description %in% c("oropharynx cancer"), "upper_aerodigestive", 
+                                           ifelse(!is.na(str_match(string = tolower(Phenotype.Description), pattern = "gastrointestinal")[,1]), "gastric", NA))))))))))))))))
+
+g2p <- merge(g2p, g2p_lineages, by = c("Phenotype.Description", "Phenotype.Family"), all = TRUE)
+
 # Add association columns
 g2p$Drug_Gene <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene), NA, paste0(g2p$Drug, "_", g2p$Gene))
-g2p <- merge(lineage_converter, g2p, by = "grouped_general_doid", all.y = TRUE)
-g2p$Drug_Gene_Lin <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene) | is.na(g2p$group_general_lineage_name), NA, paste0(g2p$Drug, "_", g2p$Gene, "_", g2p$group_general_lineage_name))
+# g2p <- merge(unique(select(ccl_meta, grouped_general_doid, disease)), g2p, by = "grouped_general_doid", all.y = TRUE)
+g2p$Drug_Gene_Lin <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene) | is.na(g2p$disease), NA, paste0(g2p$Drug, "_", g2p$Gene, "_", g2p$disease))
 g2p <- unique(g2p)
-write.csv(g2p, "./data_munging/g2p_db_edited.csv")
+write.csv(g2p, "./data_munging/g2p_db_edited_20190718.csv")
 ```
@@
 ```{r g2p}
-g2p <- read.delim("./data_munging/g2p_db_edited.csv", sep = ",", header = TRUE, row.names = 1)
+g2p <- read.delim("./data_munging/g2p_db_edited_20190718.csv", sep = ",", header = TRUE, row.names = 1)
 g2p$Drug_Gene_Lin <- gsub(pattern = " cancer", "", g2p$Drug_Gene_Lin)
@@
 g2p_mut_genes <- unique(sapply(strsplit(as.character(g2p_mut$Drug_Gene)[!is.na(g2p_mut$Drug_Gene)], "_", fixed = TRUE), function(x) x[2]))
-g2p_nodrug <- filter(g2p, is.na(Drug))
-
-g2p_prot <- unique(filter(g2p, !is.na(Gene_Protein_Change) & !is.na(Drug)) %>% select(group_general_lineage_name, Drug, Direction_Curated, Gene, Protein_Change, Gene_Protein_Change))
+
+g2p_prot <- unique(filter(g2p, !is.na(Gene_Protein_Change) & !is.na(Drug)) %>% select(disease, Drug, Direction_Curated, Gene, Protein_Change, Gene_Protein_Change))
 ```
@@
 fusions <- merge(fusions, ccl_meta, by = "DepMap_ID", all.x = TRUE)
-write.csv.gz(fusions, "./data_munging/19Q2/CCLE_fusions_edit_20190708.csv.gz")
+write.csv.gz(fusions, "./data_munging/19Q2/CCLE_fusions_edit_20190718.csv.gz")
 ```
@@
 ```{r}
-fusions <- read.delim("./data_munging/19Q2/CCLE_fusions_edit_20190708.csv.gz", header = TRUE, sep = ",")
+fusions <- read.delim("./data_munging/19Q2/CCLE_fusions_edit_20190718.csv.gz", header = TRUE, sep = ",")
 ```
@@
 
-```{r}
+```{r, eval=FALSE}
 ccle_filt <- filter(ccle, Drug %in% g2p_drugs & Gene %in% g2p_dg_genes)
@@
     signif_grid <- signif_grid[complete.cases(signif_grid), ]
-    signif_grid[signif_grid < -log10(0.05)] <- NA
+
+    signif_grid_annot1 <- signif_grid
+    signif_grid_annot1[signif_grid_annot1 <= -log10(0.05) | is.na(signif_grid_annot1)] <- ""
+    signif_grid_annot1[signif_grid_annot1 > -log10(0.05)] <- "*"
 
@@
                 cell_fun = function(j, i, x, y, width, height, fill) {
-                  if(!is.na(str_match(string = tolower(feature), pattern = "prot"))) {
-                    grid.text(signif_grid_annot1[i, j], x = x - width*0.20, y = y + height*0.07, gp = gpar(fontsize = 17))
-                  }
+                  grid.text(signif_grid_annot1[i, j], x = x + width*0.25, y = y + height*0.07, gp = gpar(fontsize = 17))
+
                   if(signif_grid_annot[i, j] == "O") {
@@
 
-### Lieage
+### Lineage
 
@@
 
-  col_fun <- colorRamp2(color_range, c("red3", "white", "blue3"))
+  col_fun <- colorRamp2(color_range, c("forestgreen", "white", "blue3"))
 
@@
                   if(annot_grid[i, j] == "resistance") {
-                    grid.circle(x = x - width*0.20, y = y - height*0.20, r = height*0.15, default.units = "npc", gp = gpar(fill = "black", col = "black"))
+                    grid.circle(x = x - width*0.20, y = y - height*0.20, r = height*0.15, default.units = "npc", gp = gpar(fill = "red", col = "black"))
                     # grid.text("☐", x, y, just = c(0.5, 0.425), gp = gpar(fontsize = 23, fontface = "bold"))

### 2019-07-19 19Q2.Rmd
update w/ new lineage tests and CRISPR merge/tests

@@
 g2p <- read.delim("./data_munging/g2p_db_edited_20190718.csv", sep = ",", header = TRUE, row.names = 1)
-g2p$Drug_Gene_Lin <- gsub(pattern = " cancer", "", g2p$Drug_Gene_Lin)
 
@@
 g2p_fus$Drug_FusionPair <- ifelse(is.na(g2p_fus$Drug) | is.na(g2p_fus$FusionPair), NA, paste0(g2p_fus$Drug, "_", g2p_fus$FusionPair))
+g2p_fus$Drug_Fusion_Lineage <- ifelse(is.na(g2p_fus$Drug) | is.na(g2p_fus$FusionPair) | is.na(g2p_fus$disease), NA, paste0(g2p_fus$Drug, "_", g2p_fus$FusionPair, "_", g2p_fus$disease))
 g2p_mut <- g2p_split[[4]] %>% drop_na(Direction_Curated)
@@
 g2p_prot <- unique(filter(g2p, !is.na(Gene_Protein_Change) & !is.na(Drug)) %>% select(disease, Drug, Direction_Curated, Gene, Protein_Change, Gene_Protein_Change))
+g2p_prot$Drug_Gene_Protein_Change <- with(g2p_prot, ifelse(is.na(Drug) | is.na(Gene_Protein_Change), NA, paste0(Drug, "_", Gene_Protein_Change)))
+g2p_prot$Drug_Gene_Protein_Change_Lineage <- with(g2p_prot, ifelse(is.na(Drug) | is.na(Gene_Protein_Change) | is.na(disease), NA, paste0(Drug, "_", Gene_Protein_Change, "_", disease)))
 ```
@@
     # Merge metadata
-    data <-  merge(data, ccl_meta, by = "DepMap_ID", all.y = TRUE)
     ## Add columns for G2P drug-gene and drug-gene-lineage sorting
@@
     data <- merge(data, ccl_meta, by = "DepMap_ID", all.y = TRUE)
+    data$Drug <- "CRISPR"
+    data$Drug_Gene <- paste0(data$Drug, "_", data$Gene)
+    data$G2P_Drug_Gene <- "No"
+    data$Drug_Gene_Lin <- paste0(data$Drug, "_", data$Gene, "_", data$disease)
+    data$G2P_Drug_Gene_Lin <- "No"
     print("Merged metadata.")
@@
 `r nrow(filter(test, n != 1))`/`r nrow(test)` gene-cell line combinations have more than one mutation in the MAF file. This is corrected in the point mutation filtering done below.
-```{r merge_drug_data, eval=FALSE}
+```{r merge_drug_data, eval=TRUE}
 ccle_all <- readRDS("./../htscreens_giant_files/pozdeyev_data/pozdeyev2016_ccle_all_edited.rds")
@@
 ccle <- MergeOmicsG2P(database = "CCLE", dataframe = ccle_all, maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./data_munging/19Q2/ccle_data_19Q2.rds")
-# write.csv.gz(ccle %>% drop_na(Score), "./data_munging/19Q2/ccle_data_19Q2.csv.gz")
+write.csv.gz(ccle %>% drop_na(Score), "./data_munging/19Q2/ccle_data_19Q2.csv.gz")
 
 ctrp <- MergeOmicsG2P(database = "CTRP", dataframe = ctrp_all, maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./../htscreens_giant_files/ctrp_data_19Q2.rds")
-# write.csv.gz(ctrp %>% drop_na(Score), "./../htscreens_giant_files/ctrp_data_19Q2.csv.gz")
+write.csv.gz(ctrp %>% drop_na(Score), "./../htscreens_giant_files/ctrp_data_19Q2.csv.gz")
 
 gdsc <- MergeOmicsG2P(database = "GDSC", dataframe = gdsc_all, maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./data_munging/19Q2/gdsc_data_19Q2.rds")
-# write.csv.gz(gdsc %>% drop_na(Score), "./../htscreens_giant_files/gdsc_data_19Q2.csv.gz")
-
-# all_genes <- intersect(unique(maf_df$Gene), intersect(unique(cn_melt$Gene), unique(ge_melt$Gene)))
-# ccle <- MergeOmicsG2P(database = "CCLE", maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = all_genes, outfile = "./../htscreens_giant_files/ccle_data_allgenes_19Q2.rds")
-# ctrp <- MergeOmicsG2P(database = "CTRP", maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = all_genes, outfile = "./../htscreens_giant_files/ctrp_data_allgenes_19Q2.rds")
-# gdsc <- MergeOmicsG2P(database = "GDSC", maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = all_genes, outfile = "./../htscreens_giant_files/gdsc_data_allgenes_19Q2.rds")
+write.csv.gz(gdsc %>% drop_na(Score), "./../htscreens_giant_files/gdsc_data_19Q2.csv.gz")
 ```
@@
 ccle_fus_grid <- expand.grid("DepMap_ID" = unique(ccle_all$DepMap_ID), "FusionPair" = unique(fusions_filt$FusionPair))
-ccle_fus <- merge(merge(ccle_all, ccle_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "CCLE_name", "CCLE_histology", "Cell_line", "FusionPair"), all = TRUE)
+ccle_fus <- merge(merge(ccle_all, ccle_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "Cell_line", "FusionPair", "disease"), all = TRUE)
 ccle_fus$Fusion_Status <- ifelse(!is.na(ccle_fus$LeftGene), "Yes", "No")
-ccle_fus$Drug_FusionPair <- ifelse(is.na(ccle_fus$Drug) | is.na(ccle_fus$FusionPair), NA, paste0(ccle_fus$Drug, "_", ccle_fus$FusionPair))
+ccle_fus$Drug_FusionPair <- with(ccle_fus, ifelse(is.na(Drug) | is.na(FusionPair), NA, paste0(Drug, "_", FusionPair)))
+ccle_fus$Drug_Fusion_Lineage <- with(ccle_fus, ifelse(is.na(Drug) | is.na(FusionPair) | is.na(disease), NA, paste0(Drug, "_", FusionPair, "_", disease)))
 ccle_fus$G2P_Drug_FusionPair <- ifelse(ccle_fus$Drug_FusionPair %in% unique(as.character(g2p_fus$Drug_FusionPair)), "Yes", "No")
 ccle_fus$G2P_Fusion <- ifelse(ccle_fus$FusionPair %in% unique(as.character(g2p_fus$FusionPair)), "Yes", "No")
+ccle_fus$G2P_Drug_Fusion_Lineage <- ifelse(ccle_fus$Drug_Fusion_Lineage %in% unique(as.character(g2p_fus$Drug_Fusion_Lineage)), "Yes", "No")
 ccle_fus$Database <- "CCLE"
@@
 ctrp_fus_grid <- expand.grid("DepMap_ID" = unique(ctrp_all$DepMap_ID), "FusionPair" = unique(fusions_filt$FusionPair))
-ctrp_fus <- merge(merge(ctrp_all, ctrp_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "CCLE_name", "CCLE_histology", "Cell_line", "FusionPair"), all = TRUE)
+ctrp_fus <- merge(merge(ctrp_all, ctrp_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "Cell_line", "FusionPair", "disease"), all = TRUE)
 ctrp_fus$Fusion_Status <- ifelse(!is.na(ctrp_fus$LeftGene), "Yes", "No")     
-ctrp_fus$Drug_FusionPair <- ifelse(is.na(ctrp_fus$Drug) | is.na(ctrp_fus$FusionPair), NA, paste0(ctrp_fus$Drug, "_", ctrp_fus$FusionPair))
+ctrp_fus$Drug_FusionPair <- with(ctrp_fus, ifelse(is.na(Drug) | is.na(FusionPair), NA, paste0(Drug, "_", FusionPair)))
+ctrp_fus$Drug_Fusion_Lineage <- with(ctrp_fus, ifelse(is.na(Drug) | is.na(FusionPair) | is.na(disease), NA, paste0(Drug, "_", FusionPair, "_", disease)))
 ctrp_fus$G2P_Drug_FusionPair <- ifelse(ctrp_fus$Drug_FusionPair %in% unique(as.character(g2p_fus$Drug_FusionPair)), "Yes", "No")
 ctrp_fus$G2P_Fusion <- ifelse(ctrp_fus$FusionPair %in% unique(as.character(g2p_fus$FusionPair)), "Yes", "No")
+ctrp_fus$G2P_Drug_Fusion_Lineage <- ifelse(ctrp_fus$Drug_Fusion_Lineage %in% unique(as.character(g2p_fus$Drug_Fusion_Lineage)), "Yes", "No")
 ctrp_fus$Database <- "CTRP"
@@
 gdsc_fus_grid <- expand.grid("DepMap_ID" = unique(gdsc_all$DepMap_ID), "FusionPair" = unique(fusions_filt$FusionPair))
-gdsc_fus <- merge(merge(gdsc_all, gdsc_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "CCLE_name", "CCLE_histology", "Cell_line", "FusionPair"), all = TRUE)
+gdsc_fus <- merge(merge(gdsc_all, gdsc_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "Cell_line", "FusionPair", "disease"), all = TRUE)
 gdsc_fus$Fusion_Status <- ifelse(!is.na(gdsc_fus$LeftGene), "Yes", "No")
-gdsc_fus$Drug_FusionPair <- ifelse(is.na(gdsc_fus$Drug) | is.na(gdsc_fus$FusionPair), NA, paste0(gdsc_fus$Drug, "_", gdsc_fus$FusionPair))
+gdsc_fus$Drug_FusionPair <- with(gdsc_fus, ifelse(is.na(Drug) | is.na(FusionPair), NA, paste0(Drug, "_", FusionPair)))
+gdsc_fus$Drug_Fusion_Lineage <- with(gdsc_fus, ifelse(is.na(Drug) | is.na(FusionPair) | is.na(disease), NA, paste0(Drug, "_", FusionPair, "_", disease)))
 gdsc_fus$G2P_Drug_FusionPair <- ifelse(gdsc_fus$Drug_FusionPair %in% unique(as.character(g2p_fus$Drug_FusionPair)), "Yes", "No")
 gdsc_fus$G2P_Fusion <- ifelse(gdsc_fus$FusionPair %in% unique(as.character(g2p_fus$FusionPair)), "Yes", "No")
+gdsc_fus$G2P_Drug_Fusion_Lineage <- ifelse(gdsc_fus$Drug_Fusion_Lineage %in% unique(as.character(g2p_fus$Drug_Fusion_Lineage)), "Yes", "No")
 gdsc_fus$Database <- "GDSC"
@@
 ccle_prot$Change_Status <- ifelse(!is.na(ccle_prot$Protein_Change), "Yes", "No")
-ccle_prot$Drug_Gene_Protein_Change <- ifelse(is.na(ccle_prot$Drug) | is.na(ccle_prot$Gene_Protein_Change), NA, paste0(ccle_prot$Drug, "_", ccle_prot$Gene_Protein_Change))
+ccle_prot$Drug_Gene_Protein_Change <- with(ccle_prot, ifelse(is.na(Drug) | is.na(Gene_Protein_Change), NA, paste0(Drug, "_", Gene_Protein_Change)))
+ccle_prot$Drug_Gene_Protein_Change_Lineage <- with(ccle_prot, ifelse(is.na(Drug) | is.na(Gene_Protein_Change) | is.na(disease), NA, paste0(Drug, "_", Gene_Protein_Change, "_", disease)))
 ccle_prot$G2P_Drug_Gene_Protein_Change <- ifelse(ccle_prot$Drug_Gene_Protein_Change %in% unique(as.character(g2p_prot$Drug_Gene_Protein_Change)), "Yes", "No")
 ccle_prot$G2P_Protein_Change <- ifelse(ccle_prot$Gene_Protein_Change %in% unique(as.character(g2p_prot$Gene_Protein_Change)), "Yes", "No")
+ccle_prot$G2P_Drug_Gene_Protein_Change_Lineage <- ifelse(ccle_prot$Drug_Gene_Protein_Change_Lineage %in% unique(as.character(g2p_prot$Drug_Gene_Protein_Change_Lineage)), "Yes", "No")
 ccle_prot <- merge(ccle_prot, unique(select(g2p_prot, Drug_Gene_Protein_Change, Direction_Curated)), by = "Drug_Gene_Protein_Change", all.x = TRUE)
@@
 ctrp_prot$Change_Status <- ifelse(!is.na(ctrp_prot$Protein_Change), "Yes", "No")
-ctrp_prot$Drug_Gene_Protein_Change <- ifelse(is.na(ctrp_prot$Drug) | is.na(ctrp_prot$Gene_Protein_Change), NA, paste0(ctrp_prot$Drug, "_", ctrp_prot$Gene_Protein_Change))
+ctrp_prot$Drug_Gene_Protein_Change <- with(ctrp_prot, ifelse(is.na(Drug) | is.na(Gene_Protein_Change), NA, paste0(Drug, "_", Gene_Protein_Change)))
+ctrp_prot$Drug_Gene_Protein_Change_Lineage <- with(ctrp_prot, ifelse(is.na(Drug) | is.na(Gene_Protein_Change) | is.na(disease), NA, paste0(Drug, "_", Gene_Protein_Change, "_", disease)))
 ctrp_prot$G2P_Drug_Gene_Protein_Change <- ifelse(ctrp_prot$Drug_Gene_Protein_Change %in% unique(as.character(g2p_prot$Drug_Gene_Protein_Change)), "Yes", "No")
 ctrp_prot$G2P_Protein_Change <- ifelse(ctrp_prot$Gene_Protein_Change %in% unique(as.character(g2p_prot$Gene_Protein_Change)), "Yes", "No")
+ctrp_prot$G2P_Drug_Gene_Protein_Change_Lineage <- ifelse(ctrp_prot$Drug_Gene_Protein_Change_Lineage %in% unique(as.character(g2p_prot$Drug_Gene_Protein_Change_Lineage)), "Yes", "No")
 ctrp_prot <- merge(ctrp_prot, unique(select(g2p_prot, Drug_Gene_Protein_Change, Direction_Curated)), by = "Drug_Gene_Protein_Change", all.x = TRUE)
@@
 gdsc_prot$Change_Status <- ifelse(!is.na(gdsc_prot$Protein_Change), "Yes", "No")
-gdsc_prot$Drug_Gene_Protein_Change <- ifelse(is.na(gdsc_prot$Drug) | is.na(gdsc_prot$Gene_Protein_Change), NA, paste0(gdsc_prot$Drug, "_", gdsc_prot$Gene_Protein_Change))
+gdsc_prot$Drug_Gene_Protein_Change <- with(gdsc_prot, ifelse(is.na(Drug) | is.na(Gene_Protein_Change), NA, paste0(Drug, "_", Gene_Protein_Change)))
+gdsc_prot$Drug_Gene_Protein_Change_Lineage <- with(gdsc_prot, ifelse(is.na(Drug) | is.na(Gene_Protein_Change) | is.na(disease), NA, paste0(Drug, "_", Gene_Protein_Change, "_", disease)))
 gdsc_prot$G2P_Drug_Gene_Protein_Change <- ifelse(gdsc_prot$Drug_Gene_Protein_Change %in% unique(as.character(g2p_prot$Drug_Gene_Protein_Change)), "Yes", "No")
 gdsc_prot$G2P_Protein_Change <- ifelse(gdsc_prot$Gene_Protein_Change %in% unique(as.character(g2p_prot$Gene_Protein_Change)), "Yes", "No")
+gdsc_prot$G2P_Drug_Gene_Protein_Change_Lineage <- ifelse(gdsc_prot$Drug_Gene_Protein_Change_Lineage %in% unique(as.character(g2p_prot$Drug_Gene_Protein_Change_Lineage)), "Yes", "No")
 gdsc_prot <- merge(gdsc_prot, unique(select(g2p_prot, Drug_Gene_Protein_Change, Direction_Curated)), by = "Drug_Gene_Protein_Change", all.x = TRUE)
@@
 
-```{r merge_crispr_data, eval=FALSE}
+```{r merge_crispr_data, eval=TRUE}
 crispr_all <- read.delim("./data_munging/19Q2/Achilles_gene_effect_20190514.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
@@
 
-```{r merge_crispr_fus, eval=FALSE}
+```{r merge_crispr_fus, eval=TRUE}
 fusions_filt <- filter(fusions, FusionPair %in% unique(as.character(g2p_fus$FusionPair)))
+crispr_fus_grid <- expand.grid("DepMap_ID" = unique(crispr$DepMap_ID), "FusionPair" = unique(fusions_filt$FusionPair))
+crispr_fus <- merge(merge(crispr, crispr_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "Cell_line", "FusionPair", "disease"), all = TRUE)
+crispr_fus$Fusion_Status <- ifelse(!is.na(crispr_fus$LeftGene), "Yes", "No")
+crispr_fus$Drug <- "CRISPR"
+crispr_fus$Drug_FusionPair <- with(crispr_fus, ifelse(is.na(Drug) | is.na(FusionPair), NA, paste0(Drug, "_", FusionPair)))
+crispr_fus$Drug_Fusion_Lineage <- with(crispr_fus, ifelse(is.na(Drug) | is.na(FusionPair) | is.na(disease), NA, paste0(Drug, "_", FusionPair, "_", disease)))
+crispr_fus$G2P_Drug_FusionPair <- "No"
+crispr_fus$G2P_Fusion <- ifelse(crispr_fus$FusionPair %in% unique(as.character(g2p_fus$FusionPair)), "Yes", "No")
+crispr_fus$G2P_Drug_Fusion_Lineage <- "No"
+crispr_fus$Database <- "CRISPR"
 
@@
 
-```{r merge_crispr_prot, eval=FALSE}
+```{r merge_crispr_prot, eval=TRUE}
 crispr_all <- read.delim("./data_munging/19Q2/Achilles_gene_effect_20190514.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
@@
 
-# CCLE
-crispr_prot_grid <- expand.grid("DepMap_ID" = unique(crispr$DepMap_ID), "Gene_Protein_Change" = unique(maf_changes_filt$Gene_Protein_Change))
-crispr_prot <- merge(crispr, crispr_prot_grid, by = "DepMap_ID", all = TRUE)
+crispr_prot_grid <- expand.grid("DepMap_ID" = unique(crispr_all$DepMap_ID), "Gene_Protein_Change" = unique(maf_changes_filt$Gene_Protein_Change))
+crispr_prot <- merge(crispr_all, crispr_prot_grid, by = "DepMap_ID", all = TRUE)
 crispr_prot <- merge(crispr_prot, maf_changes_filt, by = c("DepMap_ID", "Gene_Protein_Change"), all = TRUE)
 crispr_prot$Change_Status <- ifelse(!is.na(crispr_prot$Protein_Change), "Yes", "No")
+crispr_prot$Drug <- "CRISPR"
+crispr_prot$Drug_Gene_Protein_Change <- with(crispr_prot, ifelse(is.na(Drug) | is.na(Gene_Protein_Change), NA, paste0(Drug, "_", Gene_Protein_Change)))
+crispr_prot$Drug_Gene_Protein_Change_Lineage <- with(crispr_prot, ifelse(is.na(Drug) | is.na(Gene_Protein_Change) | is.na(disease), NA, paste0(Drug, "_", Gene_Protein_Change, "_", disease)))
+crispr_prot$G2P_Drug_Gene_Protein_Change <- "No"
 crispr_prot$G2P_Protein_Change <- ifelse(crispr_prot$Gene_Protein_Change %in% unique(as.character(g2p_prot$Gene_Protein_Change)), "Yes", "No")
+crispr_prot$G2P_Drug_Gene_Protein_Change_Lineage <- "No"
 crispr_prot <- merge(crispr_prot, unique(select(g2p_prot, Gene_Protein_Change, Direction_Curated)), by = "Gene_Protein_Change", all.x = TRUE)
 crispr_prot$Database <- "CRISPR"
-
-crispr_prot <- separate(data = crispr_prot, col = Gene_Protein_Change, into = c("Gene", "Protein_Change"), remove = FALSE, sep = ":")
-crispr_prot <- add_column(crispr_prot, Drug_Gene = paste0("CRISPR_", crispr_prot$Gene), .after = "Gene")
-crispr_prot$Direction_Curated <- ifelse(is.na(crispr_prot$Direction_Curated), "none", as.character(crispr_prot$Direction_Curated))
-crispr_prot$Direction_Grouper <- with(crispr_prot, paste0(Change_Status, "_", Direction_Curated))
 
@@
     # Require at least 3 samples in each category to run the test, else filter out that Drug_FusionPair from testing df
-    count_n <- dataframe %>% count(Drug, FusionPair, Drug_FusionPair, Fusion_Status) %>% filter(n >= 3)
-    count_category <- count_n %>% count(Drug, FusionPair, Drug_FusionPair) %>% filter(n == 2)
+    count_n <- dataframe %>% count(Drug_FusionPair, Fusion_Status) %>% filter(n >= 3)
+    count_category <- count_n %>% count(Drug_FusionPair) %>% filter(n == 2)
     keep <- intersect(count_n$Drug_FusionPair, count_category$Drug_FusionPair)
@@
   }
+  if(tolower(type) == "fusion_lineage") {
+    # Filter out fusions with too few samples in at least one category
+    # Require at least 3 samples in each category to run the test, else filter out that Drug_Fusion_Lineage from testing df
+    count_n <- dataframe %>% count(Drug_Fusion_Lineage, Fusion_Status) %>% filter(n >= 3)
+    count_category <- count_n %>% count(Drug_Fusion_Lineage) %>% filter(n == 2)
+    keep <- intersect(count_n$Drug_Fusion_Lineage, count_category$Drug_Fusion_Lineage)
+    dataframe <- filter(dataframe, Drug_Fusion_Lineage %in% keep)
+    dataframe$Drug_Fusion_Lineage <- as.character(dataframe$Drug_Fusion_Lineage)
+    signif <- compare_means(Score ~ Fusion_Status, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
+    signif <- adj_signif(signif, alpha = 0.05)
+    signif <- signif[order(signif$p),]
+    signif$InG2P <- ifelse(signif$Drug_Fusion_Lineage %in% g2p_list, "Yes", "No")
+  }
   if(tolower(type) == "protein_change") {
@@
     # Require at least 3 samples in each category to run the test, else filter out that Gene_Protein_Change from testing df
-    count_n <- dataframe %>% count(Drug, Gene_Protein_Change, Drug_Gene_Protein_Change, Change_Status) %>% filter(n >= 3)
-    count_category <- count_n %>% count(Drug, Gene_Protein_Change, Drug_Gene_Protein_Change) %>% filter(n == 2)
+    count_n <- dataframe %>% count(Drug_Gene_Protein_Change, Change_Status) %>% filter(n >= 3)
+    count_category <- count_n %>% count(Drug_Gene_Protein_Change) %>% filter(n == 2)
     keep <- intersect(count_n$Drug_Gene_Protein_Change, count_category$Drug_Gene_Protein_Change)
@@
     signif$InG2P <- ifelse(signif$Drug_Gene_Protein_Change %in% g2p_list, "Yes", "No")
+  }
+  if(tolower(type) == "protein_change_lineage") {
+    # Filter out Gene:Protein_Changes with too few samples in at least one category
+    # Require at least 3 samples in each category to run the test, else filter out that Drug_Gene_Protein_Change_Lineage from testing df
+    count_n <- dataframe %>% count(Drug_Gene_Protein_Change_Lineage, Change_Status) %>% filter(n >= 3)
+    count_category <- count_n %>% count(Drug_Gene_Protein_Change_Lineage) %>% filter(n == 2)
+    keep <- intersect(count_n$Drug_Gene_Protein_Change_Lineage, count_category$Drug_Gene_Protein_Change_Lineage)
+    dataframe <- filter(dataframe, Drug_Gene_Protein_Change_Lineage %in% keep)
+    dataframe$Drug_Gene_Protein_Change_Lineage <- as.character(dataframe$Drug_Gene_Protein_Change_Lineage)
+    signif <- compare_means(Score ~ Change_Status, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
+    signif <- adj_signif(signif, alpha = 0.05)
+    signif <- signif[order(signif$p),]
+    signif$InG2P <- ifelse(signif$Drug_Gene_Protein_Change_Lineage %in% g2p_list, "Yes", "No")
   }
@@
 
-```{r mut_wilcoxon_tests, eval=FALSE}
+**DO THIS AFTER MERGING (19 July 2019)**
+```{r mut_wilcoxon_tests, eval=TRUE}
 # CRISPR
 crispr <- unfactorize(crispr)
-# crispr_signif_all_gene <- WilcoxonTestDF(dataframe = crispr, grouping = "Gene", outfile = "./data_munging/rds/crispr_signif_g.rds")
-# crispr_filt <- filter(crispr, Gene %in% g2p_genes)
-# crispr_signif_gene <- WilcoxonTestDF(dataframe = crispr_filt, grouping = "Gene", type = "drug_gene", outfile = "./data_munging/rds/crispr_signif_g2p_g.rds")
-# crispr_signif_lineage <- WilcoxonTestDF(dataframe = crispr_filt, grouping = c("Gene", "disease"), type = "drug_gene_lineage", outfile = "./data_munging/rds/crispr_signif_g2p_gl.rds")
+crispr_filt <- filter(crispr, Gene %in% g2p_genes)
+crispr_signif_gene <- WilcoxonTestDF(dataframe = crispr_filt, grouping = "Gene", type = "drug_gene", outfile = "./data_munging/rds/crispr_signif_g2p_g.rds")
+crispr_signif_lineage <- WilcoxonTestDF(dataframe = crispr_filt, grouping = c("Gene", "disease"), type = "drug_gene_lineage", outfile = "./data_munging/rds/crispr_signif_g2p_gl.rds")
 
@@
 ccle_filt <- unfactorize(ccle_filt)
-ccle_signif_dg <- WilcoxonTestDF(dataframe = ccle, grouping = c("Drug", "Gene", "Drug_Gene"), g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), type = "drug_gene", outfile = "./data_munging/rds/ccle_signif_dg.rds")
 ccle_signif_g2p_dg <- WilcoxonTestDF(dataframe = ccle_filt, grouping = c("Drug", "Gene", "Drug_Gene"), type = "drug_gene", g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), outfile = "./data_munging/rds/ccle_signif_g2p_dg.rds")
@@
 ctrp_filt <- unfactorize(ctrp_filt)
-# ctrp_signif_dg <- WilcoxonTestDF(dataframe = ctrp, grouping = c("Drug", "Gene", "Drug_Gene"), type = "drug_gene", g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), outfile = "./data_munging/rds/ctrp_signif_dg.rds")
 ctrp_signif_g2p_dg <- WilcoxonTestDF(dataframe = ctrp_filt, grouping = c("Drug", "Gene", "Drug_Gene"), type = "drug_gene", g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), outfile = "./data_munging/rds/ctrp_signif_g2p_dg.rds")
@@
 gdsc_filt <- unfactorize(gdsc_filt)
-# gdsc_signif_dg <- WilcoxonTestDF(dataframe = gdsc, grouping = c("Drug", "Gene", "Drug_Gene"), type = "drug_gene", g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), outfile = "./data_munging/rds/gdsc_signif_dg.rds")
 gdsc_signif_g2p_dg <- WilcoxonTestDF(dataframe = gdsc_filt, grouping = c("Drug", "Gene", "Drug_Gene"), type = "drug_gene", g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), outfile = "./data_munging/rds/gdsc_signif_g2p_dg.rds")
@@
 
-crispr_signif_g <- readRDS("./data_munging/rds/crispr_signif_g.rds")
 crispr_signif_g2p_g <- readRDS("./data_munging/rds/crispr_signif_g2p_g.rds")
@@
 
-ccle_signif_dg <- readRDS("./data_munging/rds/ccle_signif_dg.rds")
 ccle_signif_g2p_dg <- readRDS("./data_munging/rds/ccle_signif_g2p_dg.rds")
@@
 
-# ctrp_signif_g <- readRDS("./data_munging/rds/ctrp_signif_dg.rds")
 ctrp_signif_g2p_dg <- readRDS("./data_munging/rds/ctrp_signif_g2p_dg.rds")
@@
 
-# gdsc_signif_g <- readRDS("./data_munging/rds/gdsc_signif_dg.rds")
 gdsc_signif_g2p_dg <- readRDS("./data_munging/rds/gdsc_signif_g2p_dg.rds")
@@
 ccle_signif_prot <- WilcoxonTestDF(dataframe = ccle_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change[!is.na(g2p_prot$Drug_Gene_Protein_Change)])), type = "protein_change", outfile = "./data_munging/rds/ccle_signif_protein_changes.rds")
+ccle_signif_prot_lin <- WilcoxonTestDF(dataframe = ccle_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change", "Drug_Gene_Protein_Change_Lineage", "disease"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change_Lineage[!is.na(g2p_prot$Drug_Gene_Protein_Change_Lineage)])), type = "protein_change_lineage", outfile = "./data_munging/rds/ccle_signif_protein_changes_lineage.rds")
 
@@
 ctrp_signif_prot <- WilcoxonTestDF(dataframe = ctrp_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change[!is.na(g2p_prot$Drug_Gene_Protein_Change)])), type = "protein_change", outfile = "./data_munging/rds/ctrp_signif_protein_changes.rds")
+ctrp_signif_prot_lin <- WilcoxonTestDF(dataframe = ctrp_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change", "Drug_Gene_Protein_Change_Lineage", "disease"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change_Lineage[!is.na(g2p_prot$Drug_Gene_Protein_Change_Lineage)])), type = "protein_change_lineage", outfile = "./data_munging/rds/ctrp_signif_protein_changes_lineage.rds")
 
@@
 gdsc_signif_prot <- WilcoxonTestDF(dataframe = gdsc_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change[!is.na(g2p_prot$Drug_Gene_Protein_Change)])), type = "protein_change", outfile = "./data_munging/rds/gdsc_signif_protein_changes.rds")
+gdsc_signif_prot_lin <- WilcoxonTestDF(dataframe = gdsc_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change", "Drug_Gene_Protein_Change_Lineage", "disease"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change_Lineage[!is.na(g2p_prot$Drug_Gene_Protein_Change_Lineage)])), type = "protein_change_lineage", outfile = "./data_munging/rds/gdsc_signif_protein_changes_lineage.rds")
 ```
@@
 ccle_signif_fus <- WilcoxonTestDF(dataframe = ccle_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair"), g2p_list = unique(as.character(g2p_fus$Drug_FusionPair[!is.na(g2p_fus$Drug_FusionPair)])), type = "fusion", outfile = "./data_munging/rds/ccle_signif_fusions.rds")
+ccle_signif_fus_lin <- WilcoxonTestDF(dataframe = ccle_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair", "Drug_Fusion_Lineage"), g2p_list = unique(as.character(g2p_fus$Drug_Fusion_Lineage[!is.na(g2p_fus$Drug_Fusion_Lineage)])), type = "fusion_lineage", outfile = "./data_munging/rds/ccle_signif_fusions_lineage.rds")
 
 ctrp_signif_fus <- WilcoxonTestDF(dataframe = ctrp_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair"), g2p_list = unique(as.character(g2p_fus$Drug_FusionPair[!is.na(g2p_fus$Drug_FusionPair)])), type = "fusion", outfile = "./data_munging/rds/ctrp_signif_fusions.rds")
+ctrp_signif_fus_lin<- WilcoxonTestDF(dataframe = ctrp_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair", "Drug_Fusion_Lineage"), g2p_list = unique(as.character(g2p_fus$Drug_Fusion_Lineage[!is.na(g2p_fus$Drug_Fusion_Lineage)])), type = "fusion_lineage", outfile = "./data_munging/rds/ctrp_signif_fusions_lineage.rds")
 
 gdsc_signif_fus <- WilcoxonTestDF(dataframe = gdsc_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair"), g2p_list = unique(as.character(g2p_fus$Drug_FusionPair[!is.na(g2p_fus$Drug_FusionPair)])), type = "fusion", outfile = "./data_munging/rds/gdsc_signif_fusions.rds")
+gdsc_signif_fus_lin <- WilcoxonTestDF(dataframe = gdsc_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair", "Drug_Fusion_Lineage"), g2p_list = unique(as.character(g2p_fus$Drug_Fusion_Lineage[!is.na(g2p_fus$Drug_Fusion_Lineage)])), type = "fusion_lineage", outfile = "./data_munging/rds/gdsc_signif_fusions_lineage.rds")
 ```

### 2019-07-22 19Q2.Rmd
update Rmd w/ CRISPR merging and testing and new histology annotations

@@
 `r nrow(filter(test, n != 1))`/`r nrow(test)` gene-cell line combinations have more than one mutation in the MAF file. This is corrected in the point mutation filtering done below.
-```{r merge_drug_data, eval=TRUE}
+```{r merge_drug_data, eval=FALSE}
 ccle_all <- readRDS("./../htscreens_giant_files/pozdeyev_data/pozdeyev2016_ccle_all_edited.rds")
@@
 
-# Melt CRISPR dataset for merging
-# crispr_melt <- melt(crispr_all, id.vars = "DepMap_ID", measure.vars = colnames(crispr_all)[2:ncol(crispr_all)], variable.name = "Gene", value.name = "Score")
-
 crispr <- MergeOmicsG2P(database = "CRISPR", dataframe = crispr_all, maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./data_munging/19Q2/crispr_data_19Q2.rds")
@@
 
-```{r merge_crispr_fus, eval=TRUE}
+```{r merge_crispr_fus, eval=FALSE}
 fusions_filt <- filter(fusions, FusionPair %in% unique(as.character(g2p_fus$FusionPair)))
@@
 
-```{r merge_crispr_prot, eval=TRUE}
+```{r merge_crispr_prot, eval=FALSE}
 crispr_all <- read.delim("./data_munging/19Q2/Achilles_gene_effect_20190514.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
@@
 
+# Melt CRISPR dataset for merging
+crispr_melt <- melt(crispr_all, id.vars = "DepMap_ID", measure.vars = colnames(crispr_all)[2:ncol(crispr_all)], variable.name = "Gene", value.name = "Score")
+
 maf_changes_df <- readRDS("./data_munging/19Q2/maf_changes_df_19Q2.rds")
@@
 crispr_prot <- merge(crispr_prot, maf_changes_filt, by = c("DepMap_ID", "Gene_Protein_Change"), all = TRUE)
+crispr_prot <- merge(crispr_prot, ccl_meta, by = "DepMap_ID", all.x = TRUE)
 crispr_prot$Change_Status <- ifelse(!is.na(crispr_prot$Protein_Change), "Yes", "No")
@@
     # Require at least 3 samples in each category to run the test, else filter out that DGL from testing df
+    if(is.na(str_match(pattern = "crispr", string = outfile))) {
       count_mut_n <- dataframe %>% count(Drug_Gene_Lin, Mutation) %>% filter(n >= 3)
@@
       signif$InG2P <- ifelse(signif$Drug_Gene_Lin %in% g2p_list, "Yes", "No")
+    }
+    if(!is.na(str_match(pattern = "crispr", string = outfile))) {
+      count_mut_n <- dataframe %>% count(Drug_Gene_Lin, Mutation) %>% filter(n >= 3)
+      count_mut_category <- count_mut_n %>% count(Drug_Gene_Lin) %>% filter(n == 2)
+      dgl_keep <- intersect(count_mut_n$Drug_Gene_Lin, count_mut_category$Drug_Gene_Lin)
+      dataframe <- filter(dataframe, Drug_Gene_Lin %in% dgl_keep)
+      dataframe$Drug_Gene_Lin <- as.character(dataframe$Drug_Gene_Lin)
+      signif <- compare_means(Score ~ Mutation, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
+      signif <- adj_signif(signif, alpha = 0.05)
+      signif <- signif[order(signif$p),]
+      signif$InG2P <- "No"
+    }
   }
@@
     # Require at least 3 samples in each category to run the test, else filter out that DG from testing df
+    if(!is.na(str_match(pattern = "crispr", string = outfile))) {
+      count_mut_n <- dataframe %>% count(Drug_Gene, Mutation) %>% filter(n >= 3)
+      count_mut_category <- count_mut_n %>% count(Drug_Gene) %>% filter(n == 2)
+      dg_keep <- intersect(count_mut_n$Drug_Gene, count_mut_category$Drug_Gene)
+      dataframe <- filter(dataframe, Drug_Gene %in% dg_keep)
+      dataframe$Drug_Gene <- as.character(dataframe$Drug_Gene)
+      signif <- compare_means(Score ~ Mutation, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
+      signif <- adj_signif(signif, alpha = 0.05)
+      signif <- signif[order(signif$p),]
+      signif$InG2P <- "No"
+    }
+    if(is.na(str_match(pattern = "crispr", string = outfile))) {
       count_mut_n <- dataframe %>% count(Drug_Gene, Mutation) %>% filter(n >= 3)
@@
     }
+  }
   signif$p_log10 <- as.numeric(formatC(-log10(signif$p), digits = 3, format = "f"))
@@
 
-**DO THIS AFTER MERGING (19 July 2019)**
-```{r mut_wilcoxon_tests, eval=TRUE}
+```{r mut_wilcoxon_tests, eval=FALSE}
 # CRISPR

### 2019-07-22 19Q2.Rmd
work on coding lineage mut heatmaps

@@
 
-crispr <- MergeOmicsG2P(database = "CRISPR", dataframe = crispr_all, maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./data_munging/19Q2/crispr_data_19Q2.rds")
+crispr <- MergeOmicsG2P(database = "CRISPR", dataframe = crispr_all, maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./../htscreens_giant_files/crispr_data_19Q2.rds")
 # write.csv.gz(crispr %>% drop_na(Score), "./../htscreens_giant_files/crispr_data_19Q2.csv.gz")
@@
 ```{r read_crispr_data}
-crispr <- readRDS("./data_munging/19Q2/crispr_data_19Q2.rds")
+crispr <- readRDS("./../htscreens_giant_files/crispr_data_19Q2.rds")
 ```
@@
 
+g2p_mut_summ_lin <- g2p_mut %>% count(Drug, Gene, disease, Direction_Curated) %>% select(-n)
+g2p_mut_summ_lin_n <- g2p_mut_summ_lin %>% count(Drug, Gene, disease)
+g2p_mut_summ_lin <- merge(g2p_mut_summ_lin, g2p_mut_summ_lin_n, by = c("Drug", "Gene", "disease"))
+g2p_mut_summ_lin$Direction_Heatmap <- with(g2p_mut_summ_lin, ifelse(n == 2, "both", ifelse(n == 1 & Direction_Curated == "resistance", "resistance", "sensitivity")))
+g2p_mut_summ_lin <- unique(select(g2p_mut_summ_lin, Drug, Gene, disease, Direction_Heatmap))
+
 crispr_signif_g2p_g <- readRDS("./data_munging/rds/crispr_signif_g2p_g.rds")
@@
 ccle_signif_dgl <- readRDS("./data_munging/rds/ccle_signif_g2p_dgl.rds")
-ccle_signif_dgl <- merge(ccle_signif_dgl, g2p_mut_summ, by = c("Drug", "Gene"), all.x = TRUE)
+ccle_signif_dgl <- merge(ccle_signif_dgl, g2p_mut_summ_lin, by = c("Drug", "Gene", "disease"), all.x = TRUE)
 
@@
 ctrp_signif_dgl <- readRDS("./data_munging/rds/ctrp_signif_g2p_dgl.rds")
-ctrp_signif_dgl <- merge(ctrp_signif_dgl, g2p_mut_summ, by = c("Drug", "Gene"), all.x = TRUE)
+ctrp_signif_dgl <- merge(ctrp_signif_dgl, g2p_mut_summ_lin, by = c("Drug", "Gene", "disease"), all.x = TRUE)
 
@@
 gdsc_signif_dgl <- readRDS("./data_munging/rds/gdsc_signif_g2p_dgl.rds")
-gdsc_signif_dgl <- merge(gdsc_signif_dgl, g2p_mut_summ, by = c("Drug", "Gene"), all.x = TRUE)
-```
+gdsc_signif_dgl <- merge(gdsc_signif_dgl, g2p_mut_summ_lin, by = c("Drug", "Gene", "disease"), all.x = TRUE)
+```
+
+### Lineages
 
@@
 
-lins <- union(unique(ccle_signif_dgl$disease), union(unique(ctrp_signif_dgl$disease), unique(gdsc_signif_dgl$disease)))
-
-drug_gene_lins <- unique(rbind(select(ccle_signif_dgl, Gene, Drug, disease, Direction_Curated), select(ctrp_signif_dgl, Gene, Drug, disease, Direction_Curated), select(gdsc_signif_dgl, Gene, Drug, disease, Direction_Curated)))
-
-ccle_signif_prot_4plot <- merge(merge(merge(ccle_signif_prot, unique(select(ccle_prot, Drug, Gene_Protein_Change)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(ccle_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE), all_directions,  by = c("Drug", "Gene_Protein_Change"), all.x = TRUE)
-
-ctrp_signif_prot_4plot <- merge(merge(merge(ctrp_signif_prot, unique(select(ctrp_prot, Drug, Gene_Protein_Change)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(ctrp_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE), all_directions,  by = c("Drug", "Gene_Protein_Change"), all.x = TRUE)
-gdsc_signif_prot_4plot <- merge(merge(merge(gdsc_signif_prot, unique(select(gdsc_prot, Drug, Gene_Protein_Change)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(gdsc_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE), all_directions,  by = c("Drug", "Gene_Protein_Change"), all.x = TRUE)
+genes <- union(unique(ccle_signif_dgl$Gene), union(unique(ctrp_signif_dgl$Gene), unique(gdsc_signif_dgl$Gene)))
+diseases <- union(unique(ccle_signif_dgl$disease), union(unique(ctrp_signif_dgl$disease), unique(gdsc_signif_dgl$disease)))
+
+ccle_signif_dgl_4plot <- merge(merge(ccle_signif_dgl, unique(select(ccle_filt, Drug, Gene, disease)), by = c("Drug", "Gene", "disease"), all.x = TRUE), expand.grid("Drug" = unique(ccle_signif_dgl$Drug), "Gene" = genes, "disease" = diseases), by = c("Drug", "Gene", "disease"), all = TRUE)
+ccle_signif_dgl_4plot$Database <- "CCLE"
+
+ctrp_signif_dgl_4plot <- merge(merge(ctrp_signif_dgl, unique(select(ctrp_filt, Drug, Gene, disease)), by = c("Drug", "Gene", "disease"), all.x = TRUE), expand.grid("Drug" = unique(ctrp_signif_dgl$Drug), "Gene" = genes, "disease" = diseases), by = c("Drug", "Gene", "disease"), all = TRUE)
+ctrp_signif_dgl_4plot$Database <- "CTRP"
+
+gdsc_signif_dgl_4plot <- merge(merge(gdsc_signif_dgl, unique(select(gdsc_filt, Drug, Gene, disease)), by = c("Drug", "Gene", "disease"), all.x = TRUE), expand.grid("Drug" = unique(gdsc_signif_dgl$Drug), "Gene" = genes, "disease" = diseases), by = c("Drug", "Gene", "disease"), all = TRUE)
+gdsc_signif_dgl_4plot$Database <- "GDSC"
 ```
@@
   ctrp_df <- filter(use_data, Database == "CTRP")
-  gdsc_df <- filter(use_datas, Database == "GDSC")
+  gdsc_df <- filter(use_data, Database == "GDSC")
 
@@
 
-  ht_gdsc <- MakeWilcoxonHeatmap(signif_df = gdsc_df, feature = "mutation", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 6, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes", radius = 0.015)
+  ht_gdsc <- MakeWilcoxonHeatmap(signif_df = gdsc_df, feature = "mutation", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 8, by = 2), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes", radius = 0.015)
 
@@
 }
-```
-
-```
-lin_ht <- lapply(lineages, makeDrugBoxplots, dataset = "CCLE")
-ccle_lvlA_drugboxplot_paths <- paste0(ccle_drugs, "_ccle_boxplots.png")
-pwalk(list(ccle_lvlA_drugboxplot_paths, ccle_lvlA_drugboxplots), ggsave, path = "./plots_18Q3/manuscript/ccle_lvlA_boxplots", dpi = 450, width = 12, height = 7, units = "in")
-
- draw(ht_ccle2 + ht_ctrp2 + ht_gdsc2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
+
+SaveWilcoxonLineageHeatmap <- function(ht, outfile) {
+  png(filename = outfile, width = 13, height = 9.5, units = "in", res = 500)
+  draw(ht, gap = unit(0.25, "in"), heatmap_legend_side = "top")
+  dev.off()
+}
+```
+
+```{r, eval=FALSE}
+diseases <- union(unique(ccle_signif_dgl_4plot$disease), union(unique(ctrp_signif_dgl_4plot$disease), unique(gdsc_signif_dgl_4plot$disease)))
+
+drugscreens_all_signif_mut <- rbind(ccle_signif_dgl_4plot, ctrp_signif_dgl_4plot, gdsc_signif_dgl_4plot)
+
+lin_hts <- lapply(diseases, MakeWilcoxonLineageHeatmap, all_lin_df = drugscreens_all_signif_mut)
+lin_ht_paths <- paste0(lins, "_mut_heatmap.png")
+pwalk(list(lin_ht_paths, lin_hts), SaveWilcoxonLineageHeatmap, outfile = "./plots/manuscript/lineage_heatmaps")
 ```

### 2019-07-23 19Q2.Rmd

@@
 
-### Lineages
-
-```{r, eval=FALSE}
-ccle_filt <- filter(ccle, Drug %in% g2p_drugs & Gene %in% g2p_dg_genes)
-ccle_filt$Gene <- factor(ccle_filt$Gene, ordered = FALSE)
-ccle_filt <- unfactorize(ccle_filt)
-
-ctrp_filt <- filter(ctrp, Drug %in% g2p_drugs & Gene %in% g2p_dg_genes)
-ctrp_filt$Gene <- factor(ctrp_filt$Gene, ordered = FALSE)
-ctrp_filt <- unfactorize(ctrp_filt)
-
-gdsc_filt <- filter(gdsc, Drug %in% g2p_drugs & Gene %in% g2p_dg_genes)
-gdsc_filt$Gene <- factor(gdsc_filt$Gene, ordered = FALSE)
-gdsc_filt <- unfactorize(gdsc_filt)
-
-genes <- union(unique(ccle_signif_dgl$Gene), union(unique(ctrp_signif_dgl$Gene), unique(gdsc_signif_dgl$Gene)))
-diseases <- union(unique(ccle_signif_dgl$disease), union(unique(ctrp_signif_dgl$disease), unique(gdsc_signif_dgl$disease)))
-
-ccle_signif_dgl_4plot <- merge(merge(ccle_signif_dgl, unique(select(ccle_filt, Drug, Gene, disease)), by = c("Drug", "Gene", "disease"), all.x = TRUE), expand.grid("Drug" = unique(ccle_signif_dgl$Drug), "Gene" = genes, "disease" = diseases), by = c("Drug", "Gene", "disease"), all = TRUE)
-ccle_signif_dgl_4plot$Database <- "CCLE"
-
-ctrp_signif_dgl_4plot <- merge(merge(ctrp_signif_dgl, unique(select(ctrp_filt, Drug, Gene, disease)), by = c("Drug", "Gene", "disease"), all.x = TRUE), expand.grid("Drug" = unique(ctrp_signif_dgl$Drug), "Gene" = genes, "disease" = diseases), by = c("Drug", "Gene", "disease"), all = TRUE)
-ctrp_signif_dgl_4plot$Database <- "CTRP"
-
-gdsc_signif_dgl_4plot <- merge(merge(gdsc_signif_dgl, unique(select(gdsc_filt, Drug, Gene, disease)), by = c("Drug", "Gene", "disease"), all.x = TRUE), expand.grid("Drug" = unique(gdsc_signif_dgl$Drug), "Gene" = genes, "disease" = diseases), by = c("Drug", "Gene", "disease"), all = TRUE)
-gdsc_signif_dgl_4plot$Database <- "GDSC"
-```
-
 ### Protein changes
@@
 ```{r wilcoxon_heatmap_function}
-MakeWilcoxonHeatmap <- function(signif_df, feature, row_names, col_title, color, legend_title, legend_breaks, row_title_txt, radius, na_color) {
+MakeWilcoxonHeatmap <- function(signif_df, feature, row_names, col_title, color, legend_title, legend_breaks, row_title_txt, na_color) {
   if(missing(na_color)) {
@@
   }
+
   if(!is.na(str_match(string = tolower(feature), pattern = "mut"))) {
@@
                 cell_fun = function(j, i, x, y, width, height, fill) {
+                  if(color == "steelblue4") {
+                    radius <- height*0.18
+                  }
+                  if(color == "darkgreen") {
+                    if(!is.na(str_match(string = tolower(feature), pattern = "fus"))) {
+                      radius <- height*0.18
+                    }
+                    else { radius <- width*0.20 }
+                  }
+                  if(color == "turquoise4") {
+                    if(!is.na(str_match(string = tolower(feature), pattern = "fus|prot"))) {
+                      radius <- height*0.18
+                    }
+                    else { radius <- width*0.20 }
+                  }
+
                   grid.text(signif_grid_annot1[i, j], x = x + width*0.25, y = y + height*0.07, gp = gpar(fontsize = 17))
@@
 ```{r mut_heatmaps, eval=FALSE, fig.height=10, fig.width=3}
-ht_ccle <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "-log10(p-value)", legend_breaks = seq(0, 12, by = 3), row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Genes", radius = 0.03)
+ht_ccle <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "-log10(p-value)", legend_breaks = seq(0, 12, by = 3), row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Genes")
 png(filename = "./plots/manuscript/ccle_mut_heatmap.png", width = 3, height = 10, units = "in", res = 500)
@@
 
-ht_ctrp <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "-log10(p-value)", legend_breaks = seq(0, 18, by = 3), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.008)
+ht_ctrp <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "-log10(p-value)", legend_breaks = seq(0, 18, by = 3), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes")
 png(filename = "./plots/manuscript/ctrp_mut_heatmap.png", width = 9.5, height = 10, units = "in", res = 500)
@@
 
-ht_gdsc <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "-log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.015)
+ht_gdsc <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "-log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Genes")
 png(filename = "./plots/manuscript/gdsc_mut_heatmap.png", width = 5, height = 10, units = "in", res = 500)
@@
 
-ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "CCLE -log10(p-value)                                                                     ", legend_breaks = seq(0, 12, by = 3), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Genes", radius = 0.03)
-ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "CTRP -log10(p-value)                                                                    ", legend_breaks = seq(0, 18, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.008)
-ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes", radius = 0.015)
+ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "CCLE -log10(p-value)                                                                     ", legend_breaks = seq(0, 12, by = 3), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Genes")
+ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "CTRP -log10(p-value)                                                                    ", legend_breaks = seq(0, 18, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes")
+ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes")
 png(filename = "./plots/manuscript/drug_mut_heatmap.png", width = 13, height = 9.5, units = "in", res = 500)
@@
 ```{r prot_heatmaps, eval=FALSE, fig.height=10, fig.width=3}
-ht_ccle <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot_4plot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Gene:Protein Change", radius = 0.03)
+ht_ccle <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot_4plot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Gene:Protein Change")
 png(filename = "./plots/manuscript/ccle_prot_heatmap.png", width = 3, height = 5.5, units = "in", res = 500)
@@
 
-ht_ctrp <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot_4plot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Gene:Protein Change", radius = 0.015)
+ht_ctrp <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot_4plot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Gene:Protein Change")
 png(filename = "./plots/manuscript/ctrp_prot_heatmap.png", width = 9.5, height = 5.5, units = "in", res = 500)
@@
 
-ht_gdsc <- MakeWilcoxonHeatmap(signif_df = gdsc_signif_prot_4plot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 8, by = 2), row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Gene:Protein Change", radius = 0.015)
+ht_gdsc <- MakeWilcoxonHeatmap(signif_df = gdsc_signif_prot_4plot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 8, by = 2), row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Gene:Protein Change")
 png(filename = "./plots/manuscript/gdsc_prot_heatmap.png", width = 5, height = 5.5, units = "in", res = 500)
@@
 
-ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot_4plot, feature = "protein changes", legend_title = "CCLE -log10(p-value)                                                              ", legend_breaks = seq(0, 15, by = 3), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Gene:Protein Change", radius = 0.03, na_color = "black")
-ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot_4plot, feature = "protein changes", legend_title = "CTRP -log10(p-value)                                                                               ", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Gene:Protein Change", radius = 0.015, na_color = "black")
-ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = gdsc_signif_prot_4plot, feature = "protein changes", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 8, by = 2), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Gene:Protein Change", radius = 0.015, na_color = "black")
+ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot_4plot, feature = "protein changes", legend_title = "CCLE -log10(p-value)                                                              ", legend_breaks = seq(0, 15, by = 3), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black")
+ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot_4plot, feature = "protein changes", legend_title = "CTRP -log10(p-value)                                                                               ", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Gene:Protein Change", na_color = "black")
+ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = gdsc_signif_prot_4plot, feature = "protein changes", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 8, by = 2), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black")
 png(filename = "./plots/manuscript/drug_prot_heatmap.png", width = 13, height = 5, units = "in", res = 500)
@@
 ```{r fus_heatmaps, eval=FALSE}
-ht_ccle <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "-log10(p-value)",  legend_breaks = seq(0, 4, by = 1), row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Fusion Pairs", radius = 0.1)
+ht_ccle <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "-log10(p-value)",  legend_breaks = seq(0, 4, by = 1), row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Fusion Pairs")
 png(filename = "./plots/manuscript/ccle_fus_heatmap.png", width = 5, height = 3, units = "in", res = 500)
@@
 
-ht_ctrp <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "-log10(p-value)", legend_breaks = seq(0, 10, by = 2), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Fusion Pairs", radius = 0.1)
+ht_ctrp <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "-log10(p-value)", legend_breaks = seq(0, 10, by = 2), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Fusion Pairs")
 png(filename = "./plots/manuscript/ctrp_fus_heatmap.png", width = 13, height = 3, units = "in", res = 500)
@@
 
-ht_gdsc <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "-log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Fusion Pairs", radius = 0.1)
+ht_gdsc <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "-log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Fusion Pairs")
 png(filename = "./plots/manuscript/gdsc_fus_heatmap.png", width = 9, height = 3, units = "in", res = 500)
@@
 
-ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "CCLE -log10(p-value)                                                                               ", legend_breaks = seq(0, 4, by = 1), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Fusion Pairs", radius = 0.1)
-ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "CTRP -log10(p-value)                                                                              ", legend_breaks = seq(0, 10, by = 2), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Fusion Pairs", radius = 0.1)
-ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Fusion Pairs", radius = 0.1)
+ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "CCLE -log10(p-value)                                                                               ", legend_breaks = seq(0, 4, by = 1), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Fusion Pairs")
+ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "CTRP -log10(p-value)                                                                              ", legend_breaks = seq(0, 10, by = 2), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Fusion Pairs")
+ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Fusion Pairs")
 png(filename = "./plots/manuscript/drug_fus_heatmap.png", width = 13, height = 2.4, units = "in", res = 500)
@@
 
-```{r}
-MakeWilcoxonLineageHeatmap <- function(all_lin_df, lineage) {
-  use_data <- filter(all_lin_df, Gene %in% unique(g2p_mut$Gene) & disease == lineage)
-  ccle_df <- filter(use_data, Database == "CCLE")
-  ctrp_df <- filter(use_data, Database == "CTRP")
-  gdsc_df <- filter(use_data, Database == "GDSC")
-
-  ht_ccle <- MakeWilcoxonHeatmap(signif_df = ccle_df, feature = "mutation", legend_title = "CCLE -log10(p-value)                                                                     ", legend_breaks = seq(0, 5, by = 1), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Genes", radius = 0.03)
-
-  ht_ctrp <- MakeWilcoxonHeatmap(signif_df = ctrp_df, feature = "mutation", legend_title = "CTRP -log10(p-value)                                                                    ", legend_breaks = seq(0, 12, by = 2), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.008)
-
-  ht_gdsc <- MakeWilcoxonHeatmap(signif_df = gdsc_df, feature = "mutation", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 8, by = 2), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes", radius = 0.015)
-
-  ht <- ht_ccle + ht_ctrp + ht_gdsc
+```{r lineage_mut_heatmap_functions}
+MakeWilcoxonLineageHeatmap <- function(df, database, lineage) {
+  plot_colors <- c("CCLE" = "darkgreen", "CTRP" = "steelblue4", "GDSC" = "turquoise4")
+  plot_breaks <- list("CCLE" = seq(0, 5, by = 1), "CTRP" = seq(0, 12, by = 2), "GDSC" = seq(0, 8, by = 2))
+
+  df <- filter(df, disease == lineage)
+
+  ht <- MakeWilcoxonHeatmap(signif_df = df, feature = "mutation", legend_title = paste0(database, "\n", lineage, "\n-log10(p-value)"), legend_breaks = plot_breaks[[database]], row_names = TRUE, color = plot_colors[[database]], col_title = "Drugs", row_title_txt = "Genes")
+
   return(ht)
@@
 
-SaveWilcoxonLineageHeatmap <- function(ht, outfile) {
-  png(filename = outfile, width = 13, height = 9.5, units = "in", res = 500)
-  draw(ht, gap = unit(0.25, "in"), heatmap_legend_side = "top")
-  dev.off()
-}
-```
-
-```{r, eval=FALSE}
-diseases <- union(unique(ccle_signif_dgl_4plot$disease), union(unique(ctrp_signif_dgl_4plot$disease), unique(gdsc_signif_dgl_4plot$disease)))
-
-drugscreens_all_signif_mut <- rbind(ccle_signif_dgl_4plot, ctrp_signif_dgl_4plot, gdsc_signif_dgl_4plot)
-
-lin_hts <- lapply(diseases, MakeWilcoxonLineageHeatmap, all_lin_df = drugscreens_all_signif_mut)
-lin_ht_paths <- paste0(lins, "_mut_heatmap.png")
-pwalk(list(lin_ht_paths, lin_hts), SaveWilcoxonLineageHeatmap, outfile = "./plots/manuscript/lineage_heatmaps")
+SaveWilcoxonLineageHeatmap <- function(database, ht_list, lineage) {
+  ht <- ht_list[[lineage]]
+  out_height <- floor((nrow(ht@matrix) + 1) / 2) + 2
+  out_width <- ncol(ht@matrix) / 2 + 1
+
+  png(filename = paste0("./plots/manuscript/lineage_heatmaps/", tolower(database), "_", lineage, "_mut_heatmap.png"), width = out_width, height = out_height, units = "in", res = 500)
+  draw(ht, heatmap_legend_side = "top")
+  invisible(dev.off())
+}
+```
+
+```{r lineage_mut_heatmaps, eval=FALSE, message=FALSE}
+ccle_hts <- lapply(unique(ccle_signif_dgl$disease), MakeWilcoxonLineageHeatmap, df = ccle_signif_dgl, database = "CCLE")
+names(ccle_hts) <- unique(ccle_signif_dgl$disease)
+lapply(unique(ccle_signif_dgl$disease), SaveWilcoxonLineageHeatmap, ht_list = ccle_hts, database = "CCLE")
+
+ctrp_hts <- lapply(unique(ctrp_signif_dgl$disease), MakeWilcoxonLineageHeatmap, df = ctrp_signif_dgl, database = "CTRP")
+names(ctrp_hts) <- unique(ctrp_signif_dgl$disease)
+lapply(unique(ctrp_signif_dgl$disease), SaveWilcoxonLineageHeatmap, ht_list = ctrp_hts, database = "CTRP")
+
+gdsc_hts <- lapply(unique(gdsc_signif_dgl$disease), MakeWilcoxonLineageHeatmap, df = gdsc_signif_dgl, database = "GDSC")
+names(gdsc_hts) <- unique(gdsc_signif_dgl$disease)
+lapply(unique(gdsc_signif_dgl$disease), SaveWilcoxonLineageHeatmap, ht_list = gdsc_hts, database = "GDSC")
 ```

### 2019-07-24 19Q2.Rmd

@@
 
+g2p_mut_summ_crispr <- g2p_mut %>% count(Gene, Direction_Curated) %>% select(-n)
+g2p_mut_summ_crispr_n <- g2p_mut_summ_crispr %>% count(Gene)
+g2p_mut_summ_crispr <- merge(g2p_mut_summ_crispr, g2p_mut_summ_crispr_n, by = c("Gene"))
+g2p_mut_summ_crispr$Direction_Heatmap <- with(g2p_mut_summ_crispr, ifelse(n == 2, "both", ifelse(n == 1 & Direction_Curated == "resistance", "resistance", "sensitivity")))
+g2p_mut_summ_crispr <- unique(select(g2p_mut_summ_crispr, Gene, Direction_Heatmap))
+
 g2p_mut_summ_lin <- g2p_mut %>% count(Drug, Gene, disease, Direction_Curated) %>% select(-n)
@@
 
+g2p_mut_summ_lin_crispr <- g2p_mut %>% count(Gene, disease, Direction_Curated) %>% select(-n)
+g2p_mut_summ_lin_crispr_n <- g2p_mut_summ_lin_crispr %>% count(Gene, disease)
+g2p_mut_summ_lin_crispr <- merge(g2p_mut_summ_lin_crispr, g2p_mut_summ_lin_crispr_n, by = c("Gene", "disease"))
+g2p_mut_summ_lin_crispr$Direction_Heatmap <- with(g2p_mut_summ_lin_crispr, ifelse(n == 2, "both", ifelse(n == 1 & Direction_Curated == "resistance", "resistance", "sensitivity")))
+g2p_mut_summ_lin_crispr <- unique(select(g2p_mut_summ_lin_crispr, Gene, disease, Direction_Heatmap))
+
 crispr_signif_g2p_g <- readRDS("./data_munging/rds/crispr_signif_g2p_g.rds")
+crispr_signif_g2p_g <- add_column(crispr_signif_g2p_g, Drug = "CRISPR", .after = "Gene")
+crispr_signif_g2p_g <- merge(crispr_signif_g2p_g, g2p_mut_summ_crispr, by = "Gene", all.x = TRUE)
 crispr_signif_lin <- readRDS("./data_munging/rds/crispr_signif_g2p_gl.rds")
+crispr_signif_lin <- add_column(crispr_signif_lin, Drug = "CRISPR", .after = "Gene")
+crispr_signif_lin <- merge(crispr_signif_lin, g2p_mut_summ_lin_crispr, by = c("Gene", "disease"), all.x = TRUE)
 
@@
 
+  if(!is.na(str_match(string = tolower(feature), pattern = "crispr"))) {
+    signif_df <- filter(crispr_signif_g2p_g, Gene %in% unique(g2p_mut$Gene))
+    signif_grid <- dcast(signif_df, Gene ~ Drug, value.var = "p_log10", fun.aggregate = mean, fill = 0)
+    signif_grid <- signif_grid[match(g2p_gene_order, signif_grid$Gene),] %>% drop_na(Gene) %>% `rownames<-`(.[,1]) %>% select(-Gene)
+
+    signif_grid_annot1 <- signif_grid
+    signif_grid_annot1[signif_grid_annot1 <= -log10(0.05) | is.na(signif_grid_annot1)] <- ""
+    signif_grid_annot1[signif_grid_annot1 > -log10(0.05)] <- "*"
+
+    signif_grid_annot <- dcast(signif_df, Gene ~ Drug, value.var = "Direction_Heatmap", fill = 0)
+    signif_grid_annot <- signif_grid_annot[match(g2p_gene_order, signif_grid_annot$Gene),] %>% drop_na(Gene) %>% `rownames<-`(.[,1]) %>% select(-Gene)
+    signif_grid_annot[signif_grid_annot == "sensitivity"] <- "O"
+  }
   if(!is.na(str_match(string = tolower(feature), pattern = "mut"))) {
@@
   # Legend properties list
-  ht_legend_list <- list(title = legend_title, title_position = "topleft", legend_direction = "horizontal", legend_width = unit(2, "in"), border = "gray70", at = legend_breaks, labels = legend_breaks)
+  ht_legend_list <- list(title = legend_title, title_position = "topleft", legend_direction = "horizontal", legend_width = unit(1.5, "in"), border = "gray70", at = legend_breaks, labels = legend_breaks)
+
   ht <- Heatmap(signif_grid,
@@
                 cell_fun = function(j, i, x, y, width, height, fill) {
+                  if(color == "darkorchid4") {
+                    radius <- width*0.20
+                  }
                   if(color == "steelblue4") {
@@
 ```{r mut_heatmaps, eval=FALSE, fig.height=10, fig.width=3}
+ht_crispr <- MakeWilcoxonHeatmap(signif_df = filter(crispr_signif_g2p_g, Gene %in% unique(g2p_mut$Gene)), feature = "crispr", legend_title = "-log10(p-value)", legend_breaks = seq(0, 45, by = 9), row_names = TRUE, color = "darkorchid4", col_title = "", row_title_txt = "Genes")
+png(filename = "./plots/manuscript/crispr_mut_heatmap.png", width = 3, height = 10, units = "in", res = 500)
+draw(ht_crispr, heatmap_legend_side = "top")
+dev.off()
+
 ht_ccle <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "-log10(p-value)", legend_breaks = seq(0, 12, by = 3), row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Genes")
@@
 ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "CTRP -log10(p-value)          ", legend_breaks = seq(0, 18, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes")
-ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes")
-png(filename = "./plots/manuscript/drug_mut_heatmap.png", width = 13, height = 9.5, units = "in", res = 500)
-draw(ht_ccle2 + ht_ctrp2 + ht_gdsc2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
+ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "GDSC -log10(p-value)          ", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes")
+ht_crispr2 <- MakeWilcoxonHeatmap(signif_df = filter(crispr_signif_g2p_g, Gene %in% unique(g2p_mut$Gene)), feature = "crispr", legend_title = "CRISPR -log10(p-value)", legend_breaks = seq(0, 45, by = 9), row_names = FALSE, color = "darkorchid4", col_title = "", row_title_txt = "Genes")
+
+# png(filename = "./plots/manuscript/drug_mut_heatmap.png", width = 13, height = 9.5, units = "in", res = 500)
+# draw(ht_ccle2 + ht_ctrp2 + ht_gdsc2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
+# dev.off()
+
+png(filename = "./plots/manuscript/all_mut_heatmap.png", width = 14, height = 9.5, units = "in", res = 500)
+draw(ht_ccle2 + ht_ctrp2 + ht_gdsc2 + ht_crispr2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
 dev.off()

### 2019-07-25 19Q2.Rmd
update g2p summary ht and Rmd

@@
 ```{r libraries}
+# install_github("jokergoo/ComplexHeatmap")
+library(devtools)
 library(circlize)
@@
 library(kableExtra)
+library(magrittr)
 library(naniar)
@@
 g2p$biomarker_type_curated <- ifelse(is.na(g2p$biomarker_type_curated), "None", as.character(g2p$biomarker_type_curated))
-g2p_split <- filter(g2p, !is.na(Drug)) %>% group_split(biomarker_type_curated)
+g2p_split <- filter(g2p, !is.na(Drug)) %>% split(g2p$biomarker_type_curated)
 g2p_amp <- g2p_split[[1]]

### 2019-07-25 19Q2.Rmd
edit CCLE/GDSC 19Q2 RDS, CTRP in giant files

@@
 ccle <- MergeOmicsG2P(database = "CCLE", dataframe = ccle_all, maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./data_munging/19Q2/ccle_data_19Q2.rds")
-write.csv.gz(ccle %>% drop_na(Score), "./data_munging/19Q2/ccle_data_19Q2.csv.gz")
+# write.csv.gz(ccle %>% drop_na(Score), "./data_munging/19Q2/ccle_data_19Q2.csv.gz")
 
 ctrp <- MergeOmicsG2P(database = "CTRP", dataframe = ctrp_all, maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./../htscreens_giant_files/ctrp_data_19Q2.rds")
-write.csv.gz(ctrp %>% drop_na(Score), "./../htscreens_giant_files/ctrp_data_19Q2.csv.gz")
+# write.csv.gz(ctrp %>% drop_na(Score), "./../htscreens_giant_files/ctrp_data_19Q2.csv.gz")
 
 gdsc <- MergeOmicsG2P(database = "GDSC", dataframe = gdsc_all, maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./data_munging/19Q2/gdsc_data_19Q2.rds")
-write.csv.gz(gdsc %>% drop_na(Score), "./../htscreens_giant_files/gdsc_data_19Q2.csv.gz")
+# write.csv.gz(gdsc %>% drop_na(Score), "./../htscreens_giant_files/gdsc_data_19Q2.csv.gz")
 ```
@@
 ```{r load_drug_rds, eval=TRUE}
+# ccle <- readRDS("./data_munging/19Q2/ccle_data_19Q2_all.rds") %>% drop_na(Drug)
+# ctrp <- readRDS("./../htscreens_giant_files/ctrp_data_19Q2_all.rds") %>% drop_na(Drug)
+# gdsc <- readRDS("./data_munging/19Q2/gdsc_data_19Q2_all.rds") %>% drop_na(Drug)
+# saveRDS(ccle, "./data_munging/19Q2/ccle_data_19Q2.rds", compress = "xz")
+# saveRDS(ctrp, "./../htscreens_giant_files/ctrp_data_19Q2.rds", compress = "xz")
+# saveRDS(gdsc, "./data_munging/19Q2/gdsc_data_19Q2.rds", compress = "xz")
+
 ccle <- readRDS("./data_munging/19Q2/ccle_data_19Q2.rds") %>% drop_na(Drug)

### 2019-09-03 19Q2.Rmd
CRISPR GE/CN correlations

@@
 
-```{r drug_spear_calc, warning=FALSE, eval=FALSE}
+Spearman correlations for gene expression and copy number:
+```{r spear_calc, warning=FALSE, eval=FALSE}
+# CRISPR
+crispr_spear_cn <- transform(crispr %>% group_by(Gene) %>% drop_na(CN) %>% summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value, p_log10 = -log10(p), corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate, Metric = "Copy Number"), Gene = reorder(Gene, corr))
+c("white", "deepskyblue4")
+crispr_spear_cn <- add_column(crispr_spear_cn, Drug = "CRISPR", .after = "Gene")
+saveRDS(crispr_spear_cn, "./data_munging/rds/crispr_cn_cor.rds")
+
+crispr_spear_ge <- transform(crispr %>% group_by(Gene) %>% drop_na(TPM) %>% summarize(p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value, p_log10 = -log10(p), corr = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate, Metric = "Gene Expression"), Gene = reorder(Gene, corr))
+crispr_spear_ge <- add_column(crispr_spear_ge, Drug = "CRISPR", .after = "Gene")
+saveRDS(crispr_spear_ge, "./data_munging/rds/crispr_ge_cor.rds")
+
 # CCLE
@@
 ccle_ge_res$Dataset <- "CCLE"
+
 ccle_cn_res <- ccle_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(CN) %>% summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$estimate, CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$p.value)
@@
 ctrp_ge_res$Dataset <- "CTRP"
+
 ctrp_cn_res <- ctrp_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(CN) %>% summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$estimate, CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$p.value)
@@
 gdsc_ge_res$Dataset <- "GDSC"
+
 gdsc_cn_res <- gdsc_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(CN) %>% summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$estimate, CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$p.value)
@@
 
-```{r load_drug_spear}
+```{r load_spear}
+g2p_amp_crispr_4merge <- select(g2p_amp, Gene, Direction_Curated)
+
+crispr_spear_cn <- readRDS("./data_munging/rds/crispr_cn_cor.rds")
+crispr_spear_ge <- readRDS("./data_munging/rds/crispr_ge_cor.rds")
+
 g2p_amp_4merge <- select(g2p_amp, Drug_Gene, Direction_Curated)
@@
 
-Spearman correlations for gene expression and copy number:
-```{r crispr_spear_calc, warning=FALSE}
-crispr_spear_ge <- transform(crispr %>% group_by(Gene) %>% drop_na(TPM) %>% summarize(p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value, p_log10 = -log10(p), corr = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate, Metric = "Gene Expression"), Gene = reorder(Gene, corr))
-crispr_spear_cn <- transform(crispr %>% group_by(Gene) %>% drop_na(CN) %>% summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value, p_log10 = -log10(p), corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate, Metric = "Copy Number"), Gene = reorder(Gene, corr))
-c("white", "deepskyblue4")
-
+```{r crispr_spear_eda, warning=FALSE}
 crispr_spear_cn_plot <- ggplot(data = filter(crispr_spear_cn, Gene %in% g2p_dg_genes)) +
@@
 
+```{r}
+    signif_df <- filter(crispr_signif_g2p_g, Gene %in% unique(g2p_mut$Gene))
+    signif_grid <- dcast(signif_df, Gene ~ Drug, value.var = "p_log10", fun.aggregate = mean, fill = 0)
+    signif_grid <- signif_grid[match(g2p_gene_order, signif_grid$Gene),] %>% drop_na(Gene) %>% `rownames<-`(.[,1]) %>% select(-Gene)
+
+    signif_grid_annot1 <- signif_grid
+    signif_grid_annot1[signif_grid_annot1 <= -log10(0.05) | is.na(signif_grid_annot1)] <- ""
+    signif_grid_annot1[signif_grid_annot1 > -log10(0.05)] <- "*"
+
+```
+
 ```{r corr_heatmap_function}
-MakeCorrHeatmap <- function(drug_cor_res, row_names, col_title, color_range, legend_title, metric, radius) {
+MakeCorrHeatmap <- function(cor_res, row_names, col_title, color_range, legend_title, metric, radius, crispr) {
   if(toupper(metric) == "CN" | toupper(metric) == "COPY NUMBER") {
-    signif_grid <- dcast(drug_cor_res, Gene ~ Drug, value.var = "CN_p", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
+    if(crispr == TRUE) {
+
+    }
+    if(crispr == FALSE) {
+      signif_grid <- dcast(cor_res, Gene ~ Drug, value.var = "CN_p", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
       signif_grid <- signif_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
@@
 
-    corr_grid <- dcast(drug_cor_res, Gene ~ Drug, value.var = "CN_r", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
+      corr_grid <- dcast(cor_res, Gene ~ Drug, value.var = "CN_r", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
       corr_grid <- corr_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(corr_grid))]
@@
     }
+  }
 
   if(toupper(metric) == "GE" | toupper(metric) == "GENE EXPRESSION") {
-    signif_grid <- dcast(drug_cor_res, Gene ~ Drug, value.var = "GE_p", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
+    if(crispr == TRUE) {
+
+    }
+    if(crispr == FALSE) {
+      signif_grid <- dcast(cor_res, Gene ~ Drug, value.var = "GE_p", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
       signif_grid <- signif_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
@@
 
-    corr_grid <- dcast(drug_cor_res, Gene ~ Drug, value.var = "GE_r", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
+      corr_grid <- dcast(cor_res, Gene ~ Drug, value.var = "GE_r", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
       corr_grid <- corr_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(corr_grid))]
@@
     }
-
-  annot_grid <- dcast(drug_cor_res, Gene ~ Drug, value.var = "Direction_Curated", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
+  }
+  if(crispr == TRUE) {
+    annot_grid <- dcast(cor_res, Gene ~ Drug, value.var = "Direction_Curated", fill = 0)
+    annot_grid <- annot_grid[match(g2p_gene_order, annot_grid$Gene),] %>% drop_na(Gene) %>% `rownames<-`(.[,1]) %>% select(-Gene)
+    # annot_grid[annot_grid == "sensitivity"] <- "O"
+    }
+  if(crispr == FALSE) {
+    annot_grid <- dcast(cor_res, Gene ~ Drug, value.var = "Direction_Curated", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
     annot_grid <- annot_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
     annot_grid <- annot_grid[complete.cases(annot_grid), ]
-  # annot_grid[annot_grid == "No"] <- ""
-  # annot_grid[annot_grid == "Yes"] <- "G"
+  }
 
@@
 ```{r drug_spear_plots, eval=FALSE}
+# CRISPR
+crispr_spear_cn <- unfactorize(filter(crispr_spear_cn, Gene %in% unique(g2p_amp$Gene)))
+crispr_cn_ht <- MakeCorrHeatmap(drug_cor_res = crispr_spear_cn, row_names = TRUE, col_title = "CCLE", color_range = c(-0.2, 0, 0.2), radius = 0.1, legend_title = "CCLE Spearman correlation", metric = "CN")
+png(filename = "./plots/manuscript/crispr_cn_heatmap.png", width = 3, height = 3, units = "in", res = 500)
+draw(crispr_cn_ht, heatmap_legend_side = "top")
+dev.off()
+
 # Copy number

### 2019-09-04 19Q2.Rmd
work on CRISPR fusions and protein changes

@@
 ```{r merge_crispr_fus, eval=FALSE}
-fusions_filt <- filter(fusions, FusionPair %in% unique(as.character(g2p_fus$FusionPair)))
+fusions_filt <- unique(filter(fusions, FusionPair %in% unique(as.character(g2p_fus$FusionPair)))) %>% select(-c("Cell_line", "disease"))
 crispr_fus_grid <- expand.grid("DepMap_ID" = unique(crispr$DepMap_ID), "FusionPair" = unique(fusions_filt$FusionPair))
-crispr_fus <- merge(merge(crispr, crispr_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "Cell_line", "FusionPair", "disease"), all = TRUE)
+crispr_fus <- merge(merge(crispr, crispr_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "FusionPair"), all = TRUE)
 crispr_fus$Fusion_Status <- ifelse(!is.na(crispr_fus$LeftGene), "Yes", "No")
@@
 
-saveRDS(crispr_fus, "./data_munging/rds/crispr_fusions.rds")
+saveRDS(crispr_fus, "./../htscreens_giant_files/crispr_fusions.rds", compress = "xz")
 ```
@@
 
-saveRDS(crispr_prot, "./data_munging/rds/crispr_protein_changes.rds")
+saveRDS(crispr_prot, "./../htscreens_giant_files/crispr_protein_changes.rds", compress = "xz")
 ```
@@
 ```{r, eval = FALSE}
-crispr_fus <- readRDS("./data_munging/rds/crispr_fusions.rds")
-crispr_prot <- readRDS("./data_munging/rds/crispr_protein_changes.rds")
+crispr_fus <- readRDS("./../htscreens_giant_files/crispr_fusions.rds")
+crispr_prot <- readRDS("./../htscreens_giant_files/crispr_protein_changes.rds")
 ```

### 2019-09-20 19Q2.Rmd

@@
 crispr_prot_grid <- expand.grid("DepMap_ID" = unique(crispr_all$DepMap_ID), "Gene_Protein_Change" = unique(maf_changes_filt$Gene_Protein_Change))
-crispr_prot <- merge(crispr_all, crispr_prot_grid, by = "DepMap_ID", all = TRUE)
+crispr_prot <- merge(crispr_melt, crispr_prot_grid, by = "DepMap_ID", all = TRUE)
 crispr_prot <- merge(crispr_prot, maf_changes_filt, by = c("DepMap_ID", "Gene_Protein_Change"), all = TRUE)
@@
 
-```{r, eval = FALSE}
+```{r, eval = TRUE}
 crispr_fus <- readRDS("./../htscreens_giant_files/crispr_fusions.rds")

### 2019-09-25 manuscript.Rmd
create knitting template, edit YAML

@@
 output              :
-  pdf_document      :
+  word_document     :
+    reference_docx  : ./word_reference_template.docx
     toc             : true
     toc_depth       : 2
-    number_sections : true
     fig_caption     : true
     df_print        : kable
-    highlight       : tango
     # citation_package: natbib
@@
 citecolor           : blue
+floatsintext        : yes
+figurelist          : no
+tablelist           : no
+footnotelist        : no
+linenumbers         : yes
 abstract            : Multiple high-throughput functional screens in cancer cell lines have generated large amounts of information on drug efficacy in a variety of genomic contexts and cancer lineages.
-Inconsistencies between datasets have led us to investigate whether these large-scale screens reproduce established clinical drug-gene associations and if genomic features particular to specific genes improve said reproducibility.
+Reported inconsistencies between datasets have led us to investigate whether these large-scale screens reproduce established clinical drug-gene associations and if genomic features particular to specific genes improve said reproducibility.
 We evaluated three large-scale, small-molecule drug screens within the context of clinical interpretations derived from a new cancer variant annotation resource published by the Variant Interpretation for Cancer Consortium (VICC).
@@
 ```{r load-processed-data, echo=FALSE, include=FALSE}
-ccl_meta <- read.delim("./data_munging/19Q2/sample_info_edit_20190708.csv", sep = ",", header = TRUE, row.names = 1)
-maf_df <- readRDS("./data_munging/19Q2/maf_df_19Q2.rds")
-maf_changes_df <- readRDS("./data_munging/19Q2/maf_changes_df_19Q2.rds")
-cn_melt <- readRDS("./data_munging/19Q2/cn_melt_19Q2.rds")
-ge_melt <- readRDS("./data_munging/19Q2/ge_melt_19Q2.rds")
-fusions <- read.delim("./data_munging/19Q2/CCLE_fusions_edit_20190708.csv.gz", header = TRUE, sep = ",")
+# ccl_meta <- read.delim("./data_munging/19Q2/sample_info_edit_20190708.csv", sep = ",", header = TRUE, row.names = 1)
+# maf_df <- readRDS("./data_munging/19Q2/maf_df_19Q2.rds")
+# maf_changes_df <- readRDS("./data_munging/19Q2/maf_changes_df_19Q2.rds")
+# cn_melt <- readRDS("./data_munging/19Q2/cn_melt_19Q2.rds")
+# ge_melt <- readRDS("./data_munging/19Q2/ge_melt_19Q2.rds")
+# fusions <- read.delim("./data_munging/19Q2/CCLE_fusions_edit_20190708.csv.gz", header = TRUE, sep = ",")
+# 
+# ccle <- readRDS("./data_munging/19Q2/ccle_data_19Q2.rds") %>% drop_na(Drug)
+# ctrp <- readRDS("./../htscreens_giant_files/ctrp_data_19Q2.rds") %>% drop_na(Drug)
+# gdsc <- readRDS("./data_munging/19Q2/gdsc_data_19Q2.rds") %>% drop_na(Drug)
+# fus <- readRDS("./data_munging/rds/fusions_merged.rds") %>% drop_na(Drug)
+# fus_summary <- fus %>% count(Database, Drug, FusionPair, Fusion_Status)
+# prot <- readRDS("./data_munging/rds/protein_changes_merged.rds")
+# 
+# crispr <- readRDS("./data_munging/19Q2/crispr_data_19Q2.rds")
 
-ccle <- readRDS("./data_munging/19Q2/ccle_data_19Q2.rds") %>% drop_na(Drug)
-ctrp <- readRDS("./../htscreens_giant_files/ctrp_data_19Q2.rds") %>% drop_na(Drug)
-gdsc <- readRDS("./data_munging/19Q2/gdsc_data_19Q2.rds") %>% drop_na(Drug)
-fus <- readRDS("./data_munging/rds/fusions_merged.rds") %>% drop_na(Drug)
-fus_summary <- fus %>% count(Database, Drug, FusionPair, Fusion_Status)
-prot <- readRDS("./data_munging/rds/protein_changes_merged.rds")
-
-crispr <- readRDS("./data_munging/19Q2/crispr_data_19Q2.rds")
-
-crispr_prot <- readRDS("./data_munging/rds/protein_changes_merged.rds")
+# crispr_prot <- readRDS("./data_munging/rds/protein_changes_merged.rds")
 ```
@@
 To test only these clinically actionable associations, we filtered the G2P dataset for only level-A G2P interpretations, of which there were `r formatC(nrow(g2p), big.mark = ",", big.interval = 3L)` (see Methods).
-All compounds screened within the GDSC, CTRP, and CCLE datasets are considered “small molecules” and are respectively linked to Compound (CID) numbers used for indexing in the PubChem database (https://pubchem.ncbi.nlm.nih.gov/).
+All compounds screened within the GDSC, CTRP, and CCLE datasets are considered "small molecules" and are respectively linked to Compound (CID) numbers used for indexing in the PubChem database (https://pubchem.ncbi.nlm.nih.gov/).
 As a result, non-small molecules, which include proteins and biologics (i.e.
@@
 
-After filtering, `r nrow(g2p_filt)` level-A G2P interpretations were carried forward in subsequent analyses, constituting `r length(g2p_drugs)` unique drugs and `r length(g2p_genes)` unique genes in `r length(g2p_druggenes)` distinct level-A combinations (*Figure 1A: Pink heatmap*).
+<!-- After filtering, `r nrow(g2p_filt)` level-A G2P interpretations were carried forward in subsequent analyses, constituting `r length(g2p_drugs)` unique drugs and `r length(g2p_genes)` unique genes in `r length(g2p_druggenes)` distinct level-A combinations (*Figure 1: Pink heatmap*).
 The number of level-A interpretations per drug ranged from `r range(g2p_drug_tally$n)[1]` to `r range(g2p_drug_tally$n)[2]` ($M =$ `r formatC(mean(g2p_drug_tally$n), digits = 2)`, $SD =$ `r formatC(sd(g2p_drug_tally$n), digits = 2)`), `r range(g2p_gene_tally$n)[1]` to `r range(g2p_gene_tally$n)[2]` ($M =$ `r formatC(mean(g2p_gene_tally$n), digits = 2)`, $SD =$ `r formatC(sd(g2p_gene_tally$n), digits = 2)`) per gene, and for each level-A drug-gene combination, the range was `r range(g2p_druggene_tally$n)[1]` to `r range(g2p_druggene_tally$n)[2]` ($M =$ `r formatC(mean(g2p_druggene_tally$n), digits = 2)`, $SD =$ `r formatC(sd(g2p_druggene_tally$n), digits = 2)`).
@@
 The remaining N un-screened G2P drugs suggests an incompleteness of these drug screens, though these projects frequently release new screening data that may include these drugs in future releases.
+-->
+
+![Summary of G2P data content and concordance with drug sensitivity screens.
+(left) The presence or absence of small molecule drugs analyzed in GDSC, CTRP, and CCLE that were identified with level-A evidence in the G2P database.
+(right) The number of level-A interpretations for each drug-gene combination in the G2P database.
+Both axes are ordered by decreasing number of G2P associations.](./plots/manuscript/g2p_summary_heatmap.png)
 
@@
 - Are the lineage-specific results approximately the same as the pancancer results?
-- Looking at a histogram of p-values, if the histogram is flat, then nothing is significant (note from meeting on 11/16)
-- KS test results
 

### 2019-09-27 19Q2.Rmd
filter CRISPR data for G2P genes, remerge fusions and protein changes, fixing NA problem w/ CRISPR dataframes

--- 2019-09-03 19Q2.Rmd
@@
     # Melt CRISPR dataset for merging
-    data <- melt(dataframe, id.vars = "DepMap_ID", measure.vars = colnames(crispr_all)[2:ncol(crispr_all)], variable.name = "Gene", value.name = "Score")
+    data <- select(dataframe, matches(paste(c("DepMap_ID", gene_list), collapse = "|")))
+    data <- melt(dataframe, id.vars = "DepMap_ID", measure.vars = colnames(data)[2:ncol(data)], variable.name = "Gene", value.name = "Score")
     # Merge cell line metadata
@@
 
-crispr <- MergeOmicsG2P(database = "CRISPR", dataframe = crispr_all, maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./../htscreens_giant_files/crispr_data_19Q2.rds")
+# test <- colnames(crispr_all)[colnames(crispr_all) %in% g2p_genes]
+
+crispr <- MergeOmicsG2P(database = "CRISPR", dataframe = crispr_all, maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./data_munging/19Q2/crispr_data_19Q2.rds")
 # write.csv.gz(crispr %>% drop_na(Score), "./../htscreens_giant_files/crispr_data_19Q2.csv.gz")
@@
 ```{r read_crispr_data}
-crispr <- readRDS("./../htscreens_giant_files/crispr_data_19Q2.rds")
+crispr <- readRDS("./data_munging/19Q2/crispr_data_19Q2.rds") %>% drop_na(Gene)
 ```
@@
 ```{r merge_crispr_fus, eval=FALSE}
-fusions_filt <- filter(fusions, FusionPair %in% unique(as.character(g2p_fus$FusionPair)))
-crispr_fus_grid <- expand.grid("DepMap_ID" = unique(crispr$DepMap_ID), "FusionPair" = unique(fusions_filt$FusionPair))
-crispr_fus <- merge(merge(crispr, crispr_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "Cell_line", "FusionPair", "disease"), all = TRUE)
+fusions_filt <- unfactorize(unique(filter(fusions, FusionPair %in% unique(as.character(g2p_fus$FusionPair)))) %>% select(-c("Cell_line", "disease")))
+crispr_fus_grid <- unfactorize(expand.grid("DepMap_ID" = unique(crispr$DepMap_ID), "FusionPair" = unique(fusions_filt$FusionPair)))
+crispr_fus <- merge(merge(crispr, crispr_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "FusionPair"), all = TRUE)
 crispr_fus$Fusion_Status <- ifelse(!is.na(crispr_fus$LeftGene), "Yes", "No")
@@
 
-saveRDS(crispr_fus, "./data_munging/rds/crispr_fusions.rds")
-```
+saveRDS(crispr_fus, "./data_munging/19Q2/crispr_fusions.rds", compress = "xz")
+```
+
+**NEED TO DO THIS**
 
@@
 
+crispr_all <- select(crispr_all, matches(paste(c("DepMap_ID", g2p_genes), collapse = "|")))
+
 # Melt CRISPR dataset for merging
@@
 maf_changes_df <- readRDS("./data_munging/19Q2/maf_changes_df_19Q2.rds")
-maf_changes_filt <- filter(maf_changes_df, Gene_Protein_Change %in% unique(as.character(g2p_prot$Gene_Protein_Change)))
+maf_changes_filt <- filter(maf_changes_df, Gene_Protein_Change %in% unique(as.character(g2p_prot$Gene_Protein_Change))) %>% select(-Gene)
 
 crispr_prot_grid <- expand.grid("DepMap_ID" = unique(crispr_all$DepMap_ID), "Gene_Protein_Change" = unique(maf_changes_filt$Gene_Protein_Change))
-crispr_prot <- merge(crispr_all, crispr_prot_grid, by = "DepMap_ID", all = TRUE)
+crispr_prot <- merge(crispr_melt, crispr_prot_grid, by = "DepMap_ID", all = TRUE)
 crispr_prot <- merge(crispr_prot, maf_changes_filt, by = c("DepMap_ID", "Gene_Protein_Change"), all = TRUE)
@@
 crispr_prot$Change_Status <- ifelse(!is.na(crispr_prot$Protein_Change), "Yes", "No")
+crispr_prot <- select(crispr_prot, -Protein_Change)
 crispr_prot$Drug <- "CRISPR"
@@
 
-saveRDS(crispr_prot, "./data_munging/rds/crispr_protein_changes.rds")
-```
-
-```{r, eval = FALSE}
-crispr_fus <- readRDS("./data_munging/rds/crispr_fusions.rds")
-crispr_prot <- readRDS("./data_munging/rds/crispr_protein_changes.rds")
+saveRDS(crispr_prot, "./data_munging/19Q2/crispr_protein_changes.rds", compress = "xz")
+```
+
+```{r, eval = TRUE}
+crispr_fus <- readRDS("./data_munging/19Q2/crispr_fusions.rds")
+crispr_prot <- readRDS("./data_munging/19Q2/crispr_protein_changes.rds")
 ```

### 2019-09-27 19Q2.Rmd
Remake histology distributions

@@
 
-**RUN THIS WHEN CRISPR IS DONE MERGING (5/17)**
 ```{r histology_dists_data, eval=FALSE}
@@
 
-**RUN THIS WHEN CRISPR IS DONE MERGING (5/17)**
 ```{r, eval=FALSE}
@@
   guides(fill = FALSE) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
+  theme(axis.text.x = element_text(angle = 70, hjust = 1, vjust = 1)) +
   labs(y = "Number of Cell Lines", x = "Histology", caption = paste0(formatC(nrow(all_ccls), format = "d", big.mark = ","), " cell lines represented."))

### 2019-10-08 19Q2.Rmd

@@
 DepMap 19Q2 update fixed almost all of the inconsistencies of the Primary.Disease column, though there were come capitalization inconsistencies.
+```{r}
+ccle_meta_test <- read.delim("./data_munging/19Q2/sample_info.csv", sep = ",", header = TRUE, na.strings = c("", NA))
+```
+
 ```{r depmap_metadata, eval=FALSE}
@@
 colnames(ccl_histologies) <- c("Cell_line", "CCLE_histology", "TCGA_classification", "CCLE_name", "DepMap_ID")
-ccl_meta <- read.delim("./data_munging/19Q2/sample_info.csv", sep = ",", header = TRUE, na.strings = c("", NA))
-ccl_meta <- select(ccl_meta, DepMap_ID, stripped_cell_line_name, CCLE_name, disease)
-colnames(ccl_meta) <- c("DepMap_ID", "Cell_line", "CCLE_name", "disease")
-ccl_meta <- subset(ccl_meta, !grepl("MERGED", CCLE_name, fixed = TRUE))
+ccl_meta_orig <- read.delim("./data_munging/19Q2/sample_info.csv", sep = ",", header = TRUE, na.strings = c("", NA))
+ccl_meta_orig_filt <- select(ccl_meta_orig, DepMap_ID, stripped_cell_line_name, CCLE_name, disease)
+colnames(ccl_meta_orig_filt) <- c("DepMap_ID", "Cell_line", "CCLE_name", "disease")
+ccl_meta <- subset(ccl_meta_orig_filt, !grepl("MERGED", CCLE_name, fixed = TRUE))
 ccl_diseases <- as.character(unique(ccl_meta$disease))[as.character(unique(ccl_meta$disease)) != " "]
@@
                                    ifelse(disease == "stomach" | CCLE_histology == "stomach", "gastric", disease))))))))
-write.csv(ccl_meta, "./data_munging/19Q2/sample_info_edit_20190718.csv")
-```
-
-```{r}
-ccl_meta <- read.delim("./data_munging/19Q2/sample_info_edit_20190717.csv", sep = ",", header = TRUE, row.names = 1)
-ccl_meta <- ccl_meta %>% select(DepMap_ID, Cell_line, disease)
+# Filter out cell lines without a DepMap ID or a cell line
+ccl_meta <- filter(ccl_meta, !is.na(DepMap_ID) & !is.na(Cell_line))
+# Filter out cell lines that have a CCLE_name not present in the original sample info from DepMap
+ccl_meta <- filter(ccl_meta, CCLE_name %in% ccl_meta_orig$CCLE_name & Cell_line %in% ccl_meta_orig_filt$Cell_line)
+# Remove cell line not used in Pozdeyev
 ccl_meta <- filter(ccl_meta, DepMap_ID != "ACH-002397")
-ccl_unique <- data.frame(disease = unique(ccl_meta$disease))
+write.csv(ccl_meta, "./data_munging/19Q2/sample_info_edit_20191008.csv")
 ```
@@
 Thus, we removed KMH2_THYROID from further analyses.
+
+```{r}
+ccl_meta <- read.delim("./data_munging/19Q2/sample_info_edit_20191008.csv", sep = ",", header = TRUE, row.names = 1)
+ccl_meta <- ccl_meta %>% select(DepMap_ID, Cell_line, disease)
+ccl_unique <- data.frame(disease = unique(ccl_meta$disease))
+```
 
@@
 fusions <- merge(fusions, ccl_meta, by = "DepMap_ID", all.x = TRUE)
-write.csv.gz(fusions, "./data_munging/19Q2/CCLE_fusions_edit_20190718.csv.gz")
+write.csv.gz(fusions, "./data_munging/19Q2/CCLE_fusions_edit_20191008.csv.gz")
 ```
@@
 ```{r}
-fusions <- read.delim("./data_munging/19Q2/CCLE_fusions_edit_20190718.csv.gz", header = TRUE, sep = ",")
+fusions <- read.delim("./data_munging/19Q2/CCLE_fusions_edit_20191008.csv.gz", header = TRUE, sep = ",")
 ```
@@
 ```
-
-**NEED TO DO THIS**
 
@@
 
-```{r dg_heatmap, fig.height=6, fig.width=8, warning=FALSE}
+```{r dg_heatmap, fig.height=6, fig.width=8, warning=FALSE, eval=FALSE}
 g2p_dg_counts <- g2p %>% count(Drug, Gene) %>% filter(!is.na(Drug), !is.na(Gene))
@@
 
-hta_annot <- HeatmapAnnotation(text = anno_text(colnames(hta_data), offset = unit(0.1, "in"), gp = gpar(fontsize = 10)))
+hta_annot <- HeatmapAnnotation(text = anno_text(colnames(hta_data), offset = unit(0.4, "in"), gp = gpar(fontsize = 10)))
 hta_legend_list <- list(legend_direction = "horizontal", border = "gray70", nrow = 2)
@@
 
+**ENDED HERE 10/08**
+
 ## Clustered AUC heatmap
 
-```{r auc_clustered_ht, eval=FALSE}
+```{r auc_clustered_ht, eval=TRUE}
 ccle_auc_grid <- dcast(ccle, Drug ~ DepMap_ID, value.var = "Score", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Drug)
@@
 ```
+
+**10/8 Ran code up to here**
 

### 2019-10-09 19Q2.Rmd
update Rmd

@@
 
-```{r dg_heatmap, fig.height=6, fig.width=8, warning=FALSE, eval=FALSE}
+```{r g2p_gount_summ}
 g2p_dg_counts <- g2p %>% count(Drug, Gene) %>% filter(!is.na(Drug), !is.na(Gene))
@@
 g2p_drug_order <- rownames(g2p_dg_counts)
-
+```
+
+```{r dg_heatmap, fig.height=6, fig.width=8, warning=FALSE, eval=FALSE}
 # Create annotation layer
@@
 
-```{r auc_clustered_ht, eval=TRUE}
+```{r auc_clustered_ht, eval=FALSE}
 ccle_auc_grid <- dcast(ccle, Drug ~ DepMap_ID, value.var = "Score", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Drug)
@@
 ```{r protein_change_data}
+crispr_prot <- unfactorize(crispr_prot)
+
 ccle_prot <- filter(prot, Database == "CCLE")
@@
 
+**10/9 ENDED HERE**
+
 ```{r prot_wilcoxon_tests, eval=FALSE}
+# crispr_prot <- unfactorize(crispr_prot)
+# crispr_signif_prot <- WilcoxonTestDF(dataframe = crispr_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change[!is.na(g2p_prot$Drug_Gene_Protein_Change)])), type = "protein_change", outfile = "./data_munging/rds/crispr_signif_protein_changes.rds")
+# 10/9: Ran above line and got this error: Error in wilcox.test.default(xi, xj, paired = paired, ...) : not enough (finite) 'x' observations
+# crispr_signif_prot_lin <- WilcoxonTestDF(dataframe = crispr_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change", "Drug_Gene_Protein_Change_Lineage", "disease"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change_Lineage[!is.na(g2p_prot$Drug_Gene_Protein_Change_Lineage)])), type = "protein_change_lineage", outfile = "./data_munging/rds/crispr_signif_protein_changes_lineage.rds")
+
 ccle_prot <- unfactorize(ccle_prot)
@@
 ```{r fusion_data}
+crispr_fus <- unfactorize(crispr_fus)
+
 ccle_fus <- filter(fus, Database == "CCLE")
@@
 ccle_fus_boxplot
-# ggsave("./plots/manuscript/ccle_fus_boxplots.png", ccle_fus_boxplot, width = 8, height = 5, units = "in")
+ggsave("./plots/manuscript/ccle_fus_boxplots.png", ccle_fus_boxplot, width = 8, height = 5, units = "in")
 
@@
 ctrp_fus_boxplot
-# ggsave("./plots/manuscript/ctrp_fus_boxplots.png", ctrp_fus_boxplot, width = 19, height = 5, units = "in")
+ggsave("./plots/manuscript/ctrp_fus_boxplots.png", ctrp_fus_boxplot, width = 19, height = 5, units = "in")
 
@@
 gdsc_fus_boxplot
-# ggsave("./plots/manuscript/gdsc_fus_boxplots.png", gdsc_fus_boxplot, width = 12, height = 5, units = "in")
+ggsave("./plots/manuscript/gdsc_fus_boxplots.png", gdsc_fus_boxplot, width = 12, height = 5, units = "in")
 ```
@@
 ```
+
+**10/9 STOPPED HERE BEFORE REALIZING I NEEDED TO RUN CRISPR PROT AND FUS WILCOXON TESTS**
 

### 2019-10-14 19Q2.Rmd
fixed CRISPR fusions and protein drug annots, moved prot to giant_files

@@
 crispr_fus$Fusion_Status <- ifelse(!is.na(crispr_fus$LeftGene), "Yes", "No")
-crispr_fus$Drug <- "CRISPR"
+crispr_fus$Drug <- crispr_fus$Drug_Gene
 crispr_fus$Drug_FusionPair <- with(crispr_fus, ifelse(is.na(Drug) | is.na(FusionPair), NA, paste0(Drug, "_", FusionPair)))
@@
 crispr_prot <- select(crispr_prot, -Protein_Change)
-crispr_prot$Drug <- "CRISPR"
+crispr_prot$Drug <- paste0("CRISPR_", crispr_prot$Gene)
 crispr_prot$Drug_Gene_Protein_Change <- with(crispr_prot, ifelse(is.na(Drug) | is.na(Gene_Protein_Change), NA, paste0(Drug, "_", Gene_Protein_Change)))
@@
 **10/9 ENDED HERE**
+**10/14 ENDED HERE**
+
+Testing:
+```{r}
+dataframe <- crispr_prot
+grouping <- c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change")
+
+count_n <- dataframe %>% count(Drug_Gene_Protein_Change, Change_Status) %>% filter(n >= 3)
+count_category <- count_n %>% count(Drug_Gene_Protein_Change) %>% filter(n == 2)
+keep <- intersect(count_n$Drug_Gene_Protein_Change, count_category$Drug_Gene_Protein_Change)
+dataframe <- filter(dataframe, Drug_Gene_Protein_Change %in% keep)
+dataframe$Drug_Gene_Protein_Change <- as.character(dataframe$Drug_Gene_Protein_Change)
+signif <- compare_means(Score ~ Change_Status, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
+signif <- adj_signif(signif, alpha = 0.05)
+signif <- signif[order(signif$p),]
+signif$InG2P <- ifelse(signif$Drug_Gene_Protein_Change %in% g2p_list, "Yes", "No")
+```
 
@@
 # crispr_prot <- unfactorize(crispr_prot)
-# crispr_signif_prot <- WilcoxonTestDF(dataframe = crispr_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change[!is.na(g2p_prot$Drug_Gene_Protein_Change)])), type = "protein_change", outfile = "./data_munging/rds/crispr_signif_protein_changes.rds")
+crispr_signif_prot <- WilcoxonTestDF(dataframe = crispr_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change[!is.na(g2p_prot$Drug_Gene_Protein_Change)])), type = "protein_change", outfile = "./data_munging/rds/crispr_signif_protein_changes.rds")
 # 10/9: Ran above line and got this error: Error in wilcox.test.default(xi, xj, paired = paired, ...) : not enough (finite) 'x' observations

### 2019-10-15 19Q2.Rmd
Rmd changes

@@
 crispr_fus <- readRDS("./data_munging/19Q2/crispr_fusions.rds")
-crispr_prot <- readRDS("./data_munging/19Q2/crispr_protein_changes.rds")
+crispr_prot <- readRDS("./../htscreens_giant_files/crispr_protein_changes.rds")
 ```
@@
 
-Testing:
-```{r}
-dataframe <- crispr_prot
-grouping <- c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change")
-
-count_n <- dataframe %>% count(Drug_Gene_Protein_Change, Change_Status) %>% filter(n >= 3)
-count_category <- count_n %>% count(Drug_Gene_Protein_Change) %>% filter(n == 2)
-keep <- intersect(count_n$Drug_Gene_Protein_Change, count_category$Drug_Gene_Protein_Change)
-dataframe <- filter(dataframe, Drug_Gene_Protein_Change %in% keep)
-dataframe$Drug_Gene_Protein_Change <- as.character(dataframe$Drug_Gene_Protein_Change)
-signif <- compare_means(Score ~ Change_Status, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
-signif <- adj_signif(signif, alpha = 0.05)
-signif <- signif[order(signif$p),]
-signif$InG2P <- ifelse(signif$Drug_Gene_Protein_Change %in% g2p_list, "Yes", "No")
-```
-
 ```{r prot_wilcoxon_tests, eval=FALSE}
-# crispr_prot <- unfactorize(crispr_prot)
+crispr_prot <- unfactorize(crispr_prot)
 crispr_signif_prot <- WilcoxonTestDF(dataframe = crispr_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change[!is.na(g2p_prot$Drug_Gene_Protein_Change)])), type = "protein_change", outfile = "./data_munging/rds/crispr_signif_protein_changes.rds")
 # 10/9: Ran above line and got this error: Error in wilcox.test.default(xi, xj, paired = paired, ...) : not enough (finite) 'x' observations
-# crispr_signif_prot_lin <- WilcoxonTestDF(dataframe = crispr_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change", "Drug_Gene_Protein_Change_Lineage", "disease"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change_Lineage[!is.na(g2p_prot$Drug_Gene_Protein_Change_Lineage)])), type = "protein_change_lineage", outfile = "./data_munging/rds/crispr_signif_protein_changes_lineage.rds")
+crispr_signif_prot_lin <- WilcoxonTestDF(dataframe = crispr_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change", "Drug_Gene_Protein_Change_Lineage", "disease"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change_Lineage[!is.na(g2p_prot$Drug_Gene_Protein_Change_Lineage)])), type = "protein_change_lineage", outfile = "./data_munging/rds/crispr_signif_protein_changes_lineage.rds")
 
@@
 ```{r load_prot_wilcoxon_rds, eval=FALSE}
+crispr_signif_prot <- readRDS("./data_munging/rds/crispr_signif_protein_changes.rds")
 ccle_signif_prot <- readRDS("./data_munging/rds/ccle_signif_protein_changes.rds")
@@
 
-gene_prots <- union(unique(ccle_signif_prot$Gene_Protein_Change), union(unique(ctrp_signif_prot$Gene_Protein_Change), unique(gdsc_signif_prot$Gene_Protein_Change)))
-
-# all_directions <- unique(rbind(select(ccle_prot, Gene_Protein_Change, Drug, Direction_Curated), select(ctrp_prot, Gene_Protein_Change, Drug, Direction_Curated), select(gdsc_prot, Gene_Protein_Change, Drug, Direction_Curated)))
-# saveRDS(all_directions, "./data_munging/rds/protein_changes_directions.rds")
-all_directions <- readRDS("./data_munging/rds/protein_changes_directions.rds")
-
+gene_prots <- union(union(unique(ccle_signif_prot$Gene_Protein_Change), union(unique(ctrp_signif_prot$Gene_Protein_Change), unique(gdsc_signif_prot$Gene_Protein_Change))), unique(crispr_signif_prot$Gene_Protein_Change))
+
+all_directions <- unique(rbind(select(crispr_prot, Gene_Protein_Change, Drug, Direction_Curated), select(ccle_prot, Gene_Protein_Change, Drug, Direction_Curated), select(ctrp_prot, Gene_Protein_Change, Drug, Direction_Curated), select(gdsc_prot, Gene_Protein_Change, Drug, Direction_Curated)))
+saveRDS(all_directions, "./data_munging/rds/protein_changes_directions.rds")
+# all_directions <- readRDS("./data_munging/rds/protein_changes_directions.rds")
+
+crispr_signif_prot_4plot <- merge(merge(merge(crispr_signif_prot, unique(select(crispr_prot, Drug, Gene_Protein_Change)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(crispr_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE), all_directions,  by = c("Drug", "Gene_Protein_Change"), all.x = TRUE)
 ccle_signif_prot_4plot <- merge(merge(merge(ccle_signif_prot, unique(select(ccle_prot, Drug, Gene_Protein_Change)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(ccle_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE), all_directions,  by = c("Drug", "Gene_Protein_Change"), all.x = TRUE)
@@
 
+saveRDS(crispr_signif_prot_4plot, "./data_munging/rds/crispr_signif_protein_changes_4plot.rds")
 saveRDS(ccle_signif_prot_4plot, "./data_munging/rds/ccle_signif_protein_changes_4plot.rds")
@@
 
+**10/15 FIX FUSION_STATUS COLUMN, ALL "NO"**
+
+```{r}
+dataframe <- crispr_fus
+grouping <- c("FusionPair", "Drug", "Drug_FusionPair")
+
+count_n <- dataframe %>% count(Drug_FusionPair, Fusion_Status) %>% filter(n >= 3)
+count_category <- count_n %>% count(Drug_FusionPair) %>% filter(n == 2)
+# keep <- intersect(count_n$Drug_FusionPair, count_category$Drug_FusionPair)
+# dataframe <- filter(dataframe, Drug_FusionPair %in% keep)
+# dataframe$Drug_FusionPair <- as.character(dataframe$Drug_FusionPair)
+# signif <- compare_means(Score ~ Fusion_Status, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
+```
+
 ```{r fus_wilcoxon_tests, eval=FALSE}
+crispr_signif_fus <- WilcoxonTestDF(dataframe = crispr_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair"), g2p_list = unique(as.character(g2p_fus$Drug_FusionPair[!is.na(g2p_fus$Drug_FusionPair)])), type = "fusion", outfile = "./data_munging/rds/crispr_signif_fusions.rds")
+crispr_signif_fus_lin <- WilcoxonTestDF(dataframe = crispr_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair", "Drug_Fusion_Lineage"), g2p_list = unique(as.character(g2p_fus$Drug_Fusion_Lineage[!is.na(g2p_fus$Drug_Fusion_Lineage)])), type = "fusion_lineage", outfile = "./data_munging/rds/crispr_signif_fusions_lineage.rds")
+
 ccle_signif_fus <- WilcoxonTestDF(dataframe = ccle_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair"), g2p_list = unique(as.character(g2p_fus$Drug_FusionPair[!is.na(g2p_fus$Drug_FusionPair)])), type = "fusion", outfile = "./data_munging/rds/ccle_signif_fusions.rds")
@@
 
+**10/15 NEED TO DO CRISPR FUS BOXPLOTS**
+
 ```{r fusion_boxplots, fig.height=5, fig.width=12, eval=FALSE}
+# CRISPR
+# LOOK AT FUSION PREVALENCE
+# crispr_fus_filt <- filter(crispr_fus, FusionPair %in% c("ABL1-BCR", "BCR-ABL1"))
+# 
+# crispr_fus_boxplot <- ggplot(data = crispr_fus_filt) +
+#   facet_grid(FusionPair ~ Drug) +
+#   scale_color_manual(name = "Fusion Status", values = c("Yes" = "darkorchid4", "No" = "thistle")) +
+#   geom_jitter(aes(x = Fusion_Status, y = Score, color = Fusion_Status), width = 0.2, alpha = 0.5, size = 0.6) +
+#   geom_boxplot(aes(x = Fusion_Status, y = Score), fill = "transparent", outlier.shape = NA, lwd = 0.3) +
+#   # coord_cartesian(ylim = c(0, 1.2)) +
+#   scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
+#   geom_text(data = crispr_signif_fus_filt, aes(x = 1.5, y = 1.1, label = p.signif)) +
+#   theme(legend.position = "top", legend.direction = "horizontal", axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
+#   guides(color = guide_legend(override.aes = list(size = 3))) +
+#   labs(y = "AUC", x = "Fusion Status")
+# crispr_fus_boxplot
+# ggsave("./plots/manuscript/crispr_fus_boxplots.png", crispr_fus_boxplot, width = 8, height = 5, units = "in")
+
 # CCLE
@@
 
-**10/9 STOPPED HERE BEFORE REALIZING I NEEDED TO RUN CRISPR PROT AND FUS WILCOXON TESTS**
+**10/15 NEED TO FIGURE OUT CRISPR HT BELOW**
+
+Ran line 1565:
+```
+Error in seq_len(n%%length(x)) : 
+  argument must be coercible to non-negative integer
+```
 
 ```{r prot_heatmaps, eval=FALSE, fig.height=10, fig.width=3}
+ht_crispr<- MakeWilcoxonHeatmap(signif_df = crispr_signif_prot_4plot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Gene:Protein Change")
+png(filename = "./plots/manuscript/crispr_prot_heatmap.png", width = 3, height = 5.5, units = "in", res = 500)
+draw(ht_crispr, heatmap_legend_side = "top")
+dev.off()
+
 ht_ccle <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot_4plot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Gene:Protein Change")

### 2019-10-16 19Q2.Rmd

@@
     data <- select(dataframe, matches(paste(c("DepMap_ID", gene_list), collapse = "|")))
-    data <- melt(dataframe, id.vars = "DepMap_ID", measure.vars = colnames(data)[2:ncol(data)], variable.name = "Gene", value.name = "Score")
+    data <- melt(dataframe, id.vars = "DepMap_ID", measure.vars = colnames(data)[2:ncol(data)], variable.name = "Drug", value.name = "Score")
+    grid <- expand.grid("DepMap_ID" = unique(data$DepMap_ID), "Gene" = gene_list)
+    data <- merge(data, grid, by = "DepMap_ID", all = TRUE)
     # Merge cell line metadata
     data <- merge(data, ccl_meta, by = "DepMap_ID", all.y = TRUE)
-    data$Drug <- "CRISPR"
+    data$Drug <- paste0("CRISPR_", data$Drug)
     data$Drug_Gene <- paste0(data$Drug, "_", data$Gene)
@@
 
+**10/15 MERGED CRISPR -- NEED TO TEST**
+
 ```{r read_crispr_data}
@@
 crispr_fus_grid <- unfactorize(expand.grid("DepMap_ID" = unique(crispr$DepMap_ID), "FusionPair" = unique(fusions_filt$FusionPair)))
-crispr_fus <- merge(merge(crispr, crispr_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "FusionPair"), all = TRUE)
+crispr_fus <- merge(merge(crispr, crispr_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "FusionPair"), all.x = TRUE)
 crispr_fus$Fusion_Status <- ifelse(!is.na(crispr_fus$LeftGene), "Yes", "No")
@@
 ```
-
-**10/15 FIX FUSION_STATUS COLUMN, ALL "NO"**
 

### 2019-10-22 19Q2.Rmd

--- 2019-10-15 19Q2.Rmd
@@
     # Melt CRISPR dataset for merging
-    data <- select(dataframe, matches(paste(c("DepMap_ID", gene_list), collapse = "|")))
+    data <- dataframe[, names(dataframe) %in% c("DepMap_ID", gene_list)]
     data <- melt(dataframe, id.vars = "DepMap_ID", measure.vars = colnames(data)[2:ncol(data)], variable.name = "Gene", value.name = "Score")
@@
 
-# test <- colnames(crispr_all)[colnames(crispr_all) %in% g2p_genes]
-
 crispr <- MergeOmicsG2P(database = "CRISPR", dataframe = crispr_all, maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./data_munging/19Q2/crispr_data_19Q2.rds")
@@
 crispr_fus_grid <- unfactorize(expand.grid("DepMap_ID" = unique(crispr$DepMap_ID), "FusionPair" = unique(fusions_filt$FusionPair)))
-crispr_fus <- merge(merge(crispr, crispr_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "FusionPair"), all = TRUE)
+crispr_fus <- merge(merge(crispr, crispr_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "FusionPair"), all.x = TRUE)
 crispr_fus$Fusion_Status <- ifelse(!is.na(crispr_fus$LeftGene), "Yes", "No")
-crispr_fus$Drug <- crispr_fus$Drug_Gene
 crispr_fus$Drug_FusionPair <- with(crispr_fus, ifelse(is.na(Drug) | is.na(FusionPair), NA, paste0(Drug, "_", FusionPair)))
@@
 crispr_fus$Database <- "CRISPR"
-
+crispr_fus <- crispr_fus %>% drop_na(Score)
 saveRDS(crispr_fus, "./data_munging/19Q2/crispr_fusions.rds", compress = "xz")
@@
 
-crispr_all <- select(crispr_all, matches(paste(c("DepMap_ID", g2p_genes), collapse = "|")))
+crispr_all <- crispr_all[, names(crispr_all) %in% c("DepMap_ID", g2p_genes)]
+
+maf_changes_df <- readRDS("./data_munging/19Q2/maf_changes_df_19Q2.rds")
+maf_changes_filt <- filter(maf_changes_df, Gene_Protein_Change %in% unique(as.character(g2p_prot$Gene_Protein_Change))) %>% select(-Protein_Change)
+maf_changes_filt$Change_Status <- "Yes"
 
@@
 crispr_melt <- melt(crispr_all, id.vars = "DepMap_ID", measure.vars = colnames(crispr_all)[2:ncol(crispr_all)], variable.name = "Gene", value.name = "Score")
-
-maf_changes_df <- readRDS("./data_munging/19Q2/maf_changes_df_19Q2.rds")
-maf_changes_filt <- filter(maf_changes_df, Gene_Protein_Change %in% unique(as.character(g2p_prot$Gene_Protein_Change))) %>% select(-Gene)
-
-crispr_prot_grid <- expand.grid("DepMap_ID" = unique(crispr_all$DepMap_ID), "Gene_Protein_Change" = unique(maf_changes_filt$Gene_Protein_Change))
-crispr_prot <- merge(crispr_melt, crispr_prot_grid, by = "DepMap_ID", all = TRUE)
-crispr_prot <- merge(crispr_prot, maf_changes_filt, by = c("DepMap_ID", "Gene_Protein_Change"), all = TRUE)
+crispr_melt <- filter(crispr_melt, Gene %in% unique(maf_changes_filt$Gene))
+
+grid <- unfactorize(expand.grid("DepMap_ID" = unique(crispr_melt$DepMap_ID), "Gene_Protein_Change" = unique(g2p_prot$Gene_Protein_Change))) 
+grid <- separate(grid, Gene_Protein_Change, c("Gene", "Protein_Change"), sep = ":", remove = FALSE) %>% select(-Protein_Change)
+
+crispr_prot <- merge(crispr_melt, grid, by = c("DepMap_ID", "Gene"), all = TRUE)
+crispr_prot <- merge(crispr_prot, maf_changes_filt, by = c("DepMap_ID", "Gene", "Gene_Protein_Change"), all = TRUE)  %>% drop_na(Score)
 crispr_prot <- merge(crispr_prot, ccl_meta, by = "DepMap_ID", all.x = TRUE)
-crispr_prot$Change_Status <- ifelse(!is.na(crispr_prot$Protein_Change), "Yes", "No")
-crispr_prot <- select(crispr_prot, -Protein_Change)
-crispr_prot$Drug <- paste0("CRISPR_", crispr_prot$Gene)
+crispr_prot$Change_Status <- ifelse(is.na(crispr_prot$Change_Status), "No", crispr_prot$Change_Status)
+crispr_prot$Drug <- "CRISPR"
+crispr_prot$Gene_Protein_Change_Lineage <- with(crispr_prot, ifelse(is.na(Gene_Protein_Change) | is.na(disease), NA, paste0(Gene_Protein_Change, "_", disease)))
 crispr_prot$Drug_Gene_Protein_Change <- with(crispr_prot, ifelse(is.na(Drug) | is.na(Gene_Protein_Change), NA, paste0(Drug, "_", Gene_Protein_Change)))
@@
 
-saveRDS(crispr_prot, "./data_munging/19Q2/crispr_protein_changes.rds", compress = "xz")
+saveRDS(crispr_prot, "./../htscreens_giant_files/crispr_protein_changes.rds", compress = "xz")
 ```
@@
 
-**ENDED HERE 10/08**
-
 ## Clustered AUC heatmap
@@
 
-**10/8 Ran code up to here**
-
 ## Mutation status
@@
 crispr <- unfactorize(crispr)
-crispr_filt <- filter(crispr, Gene %in% g2p_genes)
-crispr_signif_gene <- WilcoxonTestDF(dataframe = crispr_filt, grouping = "Gene", type = "drug_gene", outfile = "./data_munging/rds/crispr_signif_g2p_g.rds")
-crispr_signif_lineage <- WilcoxonTestDF(dataframe = crispr_filt, grouping = c("Gene", "disease"), type = "drug_gene_lineage", outfile = "./data_munging/rds/crispr_signif_g2p_gl.rds")
+crispr_signif_gene <- WilcoxonTestDF(dataframe = crispr, grouping = c("Drug", "Gene", "Drug_Gene"), type = "drug_gene", outfile = "./data_munging/rds/crispr_signif_g2p_g.rds")
+crispr_signif_lineage <- WilcoxonTestDF(dataframe = crispr, grouping =  c("Drug", "Gene", "disease", "Drug_Gene_Lin"), type = "drug_gene_lineage", outfile = "./data_munging/rds/crispr_signif_g2p_gl.rds")
 
@@
 crispr_signif_g2p_g <- readRDS("./data_munging/rds/crispr_signif_g2p_g.rds")
-crispr_signif_g2p_g <- add_column(crispr_signif_g2p_g, Drug = "CRISPR", .after = "Gene")
 crispr_signif_g2p_g <- merge(crispr_signif_g2p_g, g2p_mut_summ_crispr, by = "Gene", all.x = TRUE)
 crispr_signif_lin <- readRDS("./data_munging/rds/crispr_signif_g2p_gl.rds")
-crispr_signif_lin <- add_column(crispr_signif_lin, Drug = "CRISPR", .after = "Gene")
 crispr_signif_lin <- merge(crispr_signif_lin, g2p_mut_summ_lin_crispr, by = c("Gene", "disease"), all.x = TRUE)
@@
 
-**10/9 ENDED HERE**
-**10/14 ENDED HERE**
-
 ```{r prot_wilcoxon_tests, eval=FALSE}
 crispr_prot <- unfactorize(crispr_prot)
-crispr_signif_prot <- WilcoxonTestDF(dataframe = crispr_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change[!is.na(g2p_prot$Drug_Gene_Protein_Change)])), type = "protein_change", outfile = "./data_munging/rds/crispr_signif_protein_changes.rds")
-# 10/9: Ran above line and got this error: Error in wilcox.test.default(xi, xj, paired = paired, ...) : not enough (finite) 'x' observations
-crispr_signif_prot_lin <- WilcoxonTestDF(dataframe = crispr_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change", "Drug_Gene_Protein_Change_Lineage", "disease"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change_Lineage[!is.na(g2p_prot$Drug_Gene_Protein_Change_Lineage)])), type = "protein_change_lineage", outfile = "./data_munging/rds/crispr_signif_protein_changes_lineage.rds")
+crispr_signif_prot <- WilcoxonTestDF(dataframe = crispr_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change"), g2p_list = unique(as.character(g2p_prot$Gene_Protein_Change[!is.na(g2p_prot$Gene_Protein_Change)])), type = "protein_change", outfile = "./data_munging/rds/crispr_signif_protein_changes.rds")
+crispr_signif_prot_lin <- WilcoxonTestDF(dataframe = crispr_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change", "Drug_Gene_Protein_Change_Lineage", "disease"), g2p_list = unique(as.character(g2p_prot$Gene_Protein_Change_Lineage[!is.na(g2p_prot$Gene_Protein_Change_Lineage)])), type = "protein_change_lineage", outfile = "./data_munging/rds/crispr_signif_protein_changes_lineage.rds")
 
@@
 
-all_directions <- unique(rbind(select(crispr_prot, Gene_Protein_Change, Drug, Direction_Curated), select(ccle_prot, Gene_Protein_Change, Drug, Direction_Curated), select(ctrp_prot, Gene_Protein_Change, Drug, Direction_Curated), select(gdsc_prot, Gene_Protein_Change, Drug, Direction_Curated)))
-saveRDS(all_directions, "./data_munging/rds/protein_changes_directions.rds")
-# all_directions <- readRDS("./data_munging/rds/protein_changes_directions.rds")
+# all_directions <- unique(rbind(select(crispr_prot, Gene_Protein_Change, Drug, Direction_Curated), select(ccle_prot, Gene_Protein_Change, Drug, Direction_Curated), select(ctrp_prot, Gene_Protein_Change, Drug, Direction_Curated), select(gdsc_prot, Gene_Protein_Change, Drug, Direction_Curated)))
+# saveRDS(all_directions, "./data_munging/rds/protein_changes_directions.rds")
+all_directions <- readRDS("./data_munging/rds/protein_changes_directions.rds")
 
@@
 ```{r}
+crispr_signif_prot_4plot <- readRDS("./data_munging/rds/crispr_signif_protein_changes_4plot.rds")
 ccle_signif_prot_4plot <- readRDS("./data_munging/rds/ccle_signif_protein_changes_4plot.rds")
@@
 ```{r fus_wilcoxon_tests, eval=FALSE}
-crispr_signif_fus <- WilcoxonTestDF(dataframe = crispr_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair"), g2p_list = unique(as.character(g2p_fus$Drug_FusionPair[!is.na(g2p_fus$Drug_FusionPair)])), type = "fusion", outfile = "./data_munging/rds/crispr_signif_fusions.rds")
-crispr_signif_fus_lin <- WilcoxonTestDF(dataframe = crispr_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair", "Drug_Fusion_Lineage"), g2p_list = unique(as.character(g2p_fus$Drug_Fusion_Lineage[!is.na(g2p_fus$Drug_Fusion_Lineage)])), type = "fusion_lineage", outfile = "./data_munging/rds/crispr_signif_fusions_lineage.rds")
+crispr_signif_fus <- WilcoxonTestDF(dataframe = crispr_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair", "Drug_Gene"), g2p_list = unique(as.character(g2p_fus$Drug_FusionPair[!is.na(g2p_fus$Drug_FusionPair)])), type = "fusion", outfile = "./data_munging/rds/crispr_signif_fusions.rds")
+crispr_signif_fus_lin <- WilcoxonTestDF(dataframe = crispr_fus, grouping = c("Drug_Gene", "FusionPair", "Drug", "Drug_FusionPair", "Drug_Fusion_Lineage"), g2p_list = unique(as.character(g2p_fus$Drug_Fusion_Lineage[!is.na(g2p_fus$Drug_Fusion_Lineage)])), type = "fusion_lineage", outfile = "./data_munging/rds/crispr_signif_fusions_lineage.rds")
 
@@
 ```{r load_fus_wilcoxon_rds}
+crispr_signif_fus <- readRDS("./data_munging/rds/crispr_signif_fusions.rds")
 ccle_signif_fus <- readRDS("./data_munging/rds/ccle_signif_fusions.rds")
@@
 gdsc_signif_fus <- readRDS("./data_munging/rds/gdsc_signif_fusions.rds")
+
+crispr_signif_fus_lin <- readRDS("./data_munging/rds/crispr_signif_fusions_lineage.rds")
+ccle_signif_fus_lin <- readRDS("./data_munging/rds/ccle_signif_fusions_lineage.rds")
+ctrp_signif_fus_lin <- readRDS("./data_munging/rds/ctrp_signif_fusions_lineage.rds")
+gdsc_signif_fus_lin <- readRDS("./data_munging/rds/gdsc_signif_fusions_lineage.rds")
 ```
@@
 
-```{r crispr_mut_boxplots, fig.height=5, fig.width=10}
+```{r crispr_mut_boxplots, fig.height=5, fig.width=10, eval=FALSE}
 crispr_filt <- filter(crispr, Gene %in% g2p_mut_genes)
@@
 
-**10/15 NEED TO DO CRISPR FUS BOXPLOTS**
-
 ```{r fusion_boxplots, fig.height=5, fig.width=12, eval=FALSE}
 # CRISPR
-# LOOK AT FUSION PREVALENCE
-# crispr_fus_filt <- filter(crispr_fus, FusionPair %in% c("ABL1-BCR", "BCR-ABL1"))
-# 
-# crispr_fus_boxplot <- ggplot(data = crispr_fus_filt) +
-#   facet_grid(FusionPair ~ Drug) +
-#   scale_color_manual(name = "Fusion Status", values = c("Yes" = "darkorchid4", "No" = "thistle")) +
-#   geom_jitter(aes(x = Fusion_Status, y = Score, color = Fusion_Status), width = 0.2, alpha = 0.5, size = 0.6) +
-#   geom_boxplot(aes(x = Fusion_Status, y = Score), fill = "transparent", outlier.shape = NA, lwd = 0.3) +
-#   # coord_cartesian(ylim = c(0, 1.2)) +
+crispr_fus_filt <- filter(crispr_fus, FusionPair %in% c("ABL1-BCR", "BCR-ABL1", "PML-PARA") & Drug_Gene %in% c("CRISPR_ABL1"))
+crispr_signif_fus_filt <- filter(crispr_signif_fus, FusionPair %in% c("ABL1-BCR", "BCR-ABL1", "PML-PARA") & Drug_Gene %in% c("CRISPR_ABL1"))
+
+crispr_fus_boxplot <- ggplot(data = crispr_fus_filt) +
+  facet_grid(FusionPair ~ Drug_Gene) +
+  scale_color_manual(name = "Fusion Status", values = c("Yes" = "darkorchid4", "No" = "thistle")) +
+  geom_jitter(aes(x = Fusion_Status, y = Score, color = Fusion_Status), width = 0.2, alpha = 0.5, size = 0.6) +
+  geom_boxplot(aes(x = Fusion_Status, y = Score), fill = "transparent", outlier.shape = NA, lwd = 0.3) +
+  # coord_cartesian(ylim = c(0, 1.2)) +
   # scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
-#   geom_text(data = crispr_signif_fus_filt, aes(x = 1.5, y = 1.1, label = p.signif)) +
-#   theme(legend.position = "top", legend.direction = "horizontal", axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
-#   guides(color = guide_legend(override.aes = list(size = 3))) +
-#   labs(y = "AUC", x = "Fusion Status")
-# crispr_fus_boxplot
-# ggsave("./plots/manuscript/crispr_fus_boxplots.png", crispr_fus_boxplot, width = 8, height = 5, units = "in")
+  geom_text(data = crispr_signif_fus_filt, aes(x = 1.5, y = 1, label = p.signif)) +
+  theme(legend.position = "top", legend.direction = "horizontal", axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
+  guides(color = guide_legend(override.aes = list(size = 3))) +
+  labs(y = "Score", x = "Fusion Status")
+crispr_fus_boxplot
+ggsave("./plots/manuscript/crispr_fus_boxplots.png", crispr_fus_boxplot, width = 8, height = 5, units = "in")
 
@@
                   if(color == "darkorchid4") {
-                    radius <- width*0.20
+                    radius <- width*0.18
                   }
                   if(color == "steelblue4") {
-                    radius <- height*0.18
+                    radius <- height*0.12
                   }
@@
                     if(!is.na(str_match(string = tolower(feature), pattern = "fus"))) {
-                      radius <- height*0.18
-                    }
-                    else { radius <- width*0.20 }
+                      radius <- height*0.16
+                    }
+                    else { radius <- width*0.18 }
                   }
@@
                     if(!is.na(str_match(string = tolower(feature), pattern = "fus|prot"))) {
-                      radius <- height*0.18
-                    }
-                    else { radius <- width*0.20 }
+                      radius <- height*0.16
+                    }
+                    else { radius <- width*0.18 }
                   }
@@
 
-png(filename = "./plots/manuscript/all_mut_heatmap.png", width = 14, height = 9.5, units = "in", res = 500)
+png(filename = "./plots/manuscript/all_mut_heatmap.png", width = 14, height = 8, units = "in", res = 500)
 draw(ht_ccle2 + ht_ctrp2 + ht_gdsc2 + ht_crispr2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
@@
 
-**10/15 NEED TO FIGURE OUT CRISPR HT BELOW**
+**10/22 STOPPED HERE, NEED TO FIGURE OUT CRISPR HT BELOW**
 

### 2019-10-23 19Q2.Rmd
update Rmd

@@
 # all_directions <- unique(rbind(select(crispr_prot, Gene_Protein_Change, Drug, Direction_Curated), select(ccle_prot, Gene_Protein_Change, Drug, Direction_Curated), select(ctrp_prot, Gene_Protein_Change, Drug, Direction_Curated), select(gdsc_prot, Gene_Protein_Change, Drug, Direction_Curated)))
+# all_directions <- filter(all_directions, !is.na(Direction_Curated))
 # saveRDS(all_directions, "./data_munging/rds/protein_changes_directions.rds")
@@
 
-  if(!is.na(str_match(string = tolower(feature), pattern = "crispr"))) {
+  if(!is.na(str_match(string = tolower(feature), pattern = "crispr")) & is.na(str_match(string = tolower(feature), pattern = "prot"))) {
+    print("Making CRISPR mutation status grid and annotation dataframes.")
     signif_df <- filter(crispr_signif_g2p_g, Gene %in% unique(g2p_mut$Gene))
@@
     signif_grid_annot[signif_grid_annot == "sensitivity"] <- "O"
+    print("Done.")
   }
   if(!is.na(str_match(string = tolower(feature), pattern = "mut"))) {
+    print("Making mutation status grid and annotation dataframes.")
     signif_grid <- dcast(signif_df, Gene ~ Drug, value.var = "p_log10", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
@@
     signif_grid_annot[signif_grid_annot == "sensitivity"] <- "O"
+    print("Done.")
   }
   if(!is.na(str_match(string = tolower(feature), pattern = "prot"))) {
+    if(is.na(str_match(string = tolower(feature), pattern = "crispr"))) {
+      print("Making protein changes grid and annotation dataframes.")
       signif_grid <- dcast(signif_df, Gene_Protein_Change ~ Drug, value.var = "p_log10", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene_Protein_Change)
@@
       signif_grid_annot[signif_grid_annot == "sensitivity"] <- "O"
+      print("Done.")
+    }
+    if(!is.na(str_match(string = tolower(feature), pattern = "crispr"))) {
+      print("Making CRISPR protein changes grid and annotation dataframes.")
+      signif_grid <- dcast(signif_df, Gene_Protein_Change ~ Drug, value.var = "p_log10", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene_Protein_Change)
+
+      signif_grid_annot1 <- signif_grid
+      signif_grid_annot1[signif_grid_annot1 <= -log10(0.05) | is.na(signif_grid_annot1)] <- ""
+      signif_grid_annot1[signif_grid_annot1 > -log10(0.05)] <- "*"
+
+      signif_grid_annot <- dcast(signif_df, Gene_Protein_Change ~ Drug, value.var = "Direction_Curated", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene_Protein_Change)
+      signif_grid_annot[signif_grid_annot == "resistance"] <- "X"
+      signif_grid_annot[signif_grid_annot == "sensitivity"] <- "O"
+      print("Done.")
+    }
   }
   if(!is.na(str_match(string = tolower(feature), pattern = "fus"))) {
+    print("Making fusions grid and annotation dataframes.")
     signif_grid <- dcast(signif_df, FusionPair ~ Drug, value.var = "p_log10", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-FusionPair)
@@
     signif_grid_annot[signif_grid_annot == "Yes"] <- "O"
+    print("Done.")
   }
@@
 
+  print("Making heatmap object.")
   ht <- Heatmap(signif_grid,
@@
                   if(color == "darkorchid4") {
-                    radius <- width*0.18
+                    if(is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*0.18 }
+                    if(!is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*0.16 }
                   }
                   if(color == "steelblue4") {
-                    radius <- height*0.12
+                    if(is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*0.12 }
+                    if(!is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*0.16 }
                   }
@@
                     else { radius <- width*0.18 }
-                  }
-
                   grid.text(signif_grid_annot1[i, j], x = x + width*0.25, y = y + height*0.07, gp = gpar(fontsize = 17))
@@
                 }
-                )
+
+  print("Done.")
   return(ht)
@@
 ### Pancan
+
+**10/23 STOPPED HERE: Was fixing annotation dot sizes on heatmaps**
 
@@
 
-**10/22 STOPPED HERE, NEED TO FIGURE OUT CRISPR HT BELOW**
-
-Ran line 1565:
-```
-Error in seq_len(n%%length(x)) : 
-  argument must be coercible to non-negative integer
-```
-
 ```{r prot_heatmaps, eval=FALSE, fig.height=10, fig.width=3}
-ht_crispr<- MakeWilcoxonHeatmap(signif_df = crispr_signif_prot_4plot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Gene:Protein Change")
+ht_crispr <- MakeWilcoxonHeatmap(signif_df = crispr_signif_prot_4plot, feature = "protein changes CRISPR", legend_title = "-log10(p-value)", legend_breaks = seq(0, 25, by = 5), row_names = TRUE, color = "darkorchid4", col_title = "", row_title_txt = "Gene:Protein Change")
 png(filename = "./plots/manuscript/crispr_prot_heatmap.png", width = 3, height = 5.5, units = "in", res = 500)
@@
 
+ht_crispr2 <- MakeWilcoxonHeatmap(signif_df = crispr_signif_prot_4plot, feature = "protein changes CRISPR", legend_title = "CRISPR -log10(p-value)", legend_breaks = seq(0, 25, by = 5), row_names = FALSE, color = "darkorchid4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black")
 ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot_4plot, feature = "protein changes", legend_title = "CCLE -log10(p-value)                                                              ", legend_breaks = seq(0, 15, by = 3), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black")
 ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot_4plot, feature = "protein changes", legend_title = "CTRP -log10(p-value)                                                                               ", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Gene:Protein Change", na_color = "black")
-ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = gdsc_signif_prot_4plot, feature = "protein changes", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 8, by = 2), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black")
-png(filename = "./plots/manuscript/drug_prot_heatmap.png", width = 13, height = 5, units = "in", res = 500)
-draw(ht_ccle2 + ht_ctrp2 + ht_gdsc2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
+ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = gdsc_signif_prot_4plot, feature = "protein changes", legend_title = "GDSC -log10(p-value)                                ", legend_breaks = seq(0, 8, by = 2), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black")
+png(filename = "./plots/manuscript/all_prot_heatmap.png", width = 14, height = 5, units = "in", res = 500)
+draw(ht_ccle2 + ht_ctrp2 + ht_gdsc2 + ht_crispr2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
 dev.off()

### 2019-10-29 19Q2.Rmd
update Rmd

@@
 
-```{r}
-dataframe <- crispr_fus
-grouping <- c("FusionPair", "Drug", "Drug_FusionPair")
-
-count_n <- dataframe %>% count(Drug_FusionPair, Fusion_Status) %>% filter(n >= 3)
-count_category <- count_n %>% count(Drug_FusionPair) %>% filter(n == 2)
-# keep <- intersect(count_n$Drug_FusionPair, count_category$Drug_FusionPair)
-# dataframe <- filter(dataframe, Drug_FusionPair %in% keep)
-# dataframe$Drug_FusionPair <- as.character(dataframe$Drug_FusionPair)
-# signif <- compare_means(Score ~ Fusion_Status, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
-```
-
 ```{r fus_wilcoxon_tests, eval=FALSE}
@@
 
-  if(!is.na(str_match(string = tolower(feature), pattern = "crispr")) & is.na(str_match(string = tolower(feature), pattern = "prot"))) {
+  if(!is.na(str_match(string = tolower(feature), pattern = "crispr")) & is.na(str_match(string = tolower(feature), pattern = "prot|fus"))) {
     print("Making CRISPR mutation status grid and annotation dataframes.")
@@
   if(!is.na(str_match(string = tolower(feature), pattern = "fus"))) {
+    if(is.na(str_match(string = tolower(feature), pattern = "crispr"))) {
       print("Making fusions grid and annotation dataframes.")
@@
       print("Done.")
+    }
+    if(!is.na(str_match(string = tolower(feature), pattern = "crispr"))) {
+      print("Making CRISPR fusions grid and annotation dataframes.")
+      signif_grid <- dcast(signif_df, FusionPair ~ Drug_Gene, value.var = "p_log10", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-FusionPair)
+
+      signif_grid_annot1 <- signif_grid
+      signif_grid_annot1[signif_grid_annot1 <= -log10(0.05) | is.na(signif_grid_annot1)] <- ""
+      signif_grid_annot1[signif_grid_annot1 > -log10(0.05)] <- "*"
+
+      signif_grid_annot <- dcast(signif_df, FusionPair ~ Drug, value.var = "InG2P", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-FusionPair)
+      signif_grid_annot[signif_grid_annot == "No"] <- ""
+      signif_grid_annot[signif_grid_annot == "Yes"] <- "O"
+      print("Done.")
+    }
   }
@@
                   if(color == "darkorchid4") {
-                    if(is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*0.18 }
+                    if(is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*3.3 }
+                    if(!is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*2 }
+                  }
+                  if(color == "steelblue4") {
+                    if(!is.na(str_match(string = tolower(feature), pattern = "fus"))) { radius <- height*0.20 }
                     if(!is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*0.16 }
-                  }
-                  if(color == "steelblue4") {
-                    if(is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*0.12 }
-                    if(!is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*0.16 }
+                    else { radius <- width*0.18 }
                   }
                   if(color == "darkgreen") {
-                    if(!is.na(str_match(string = tolower(feature), pattern = "fus"))) {
-                      radius <- height*0.16
-                    }
+                    if(!is.na(str_match(string = tolower(feature), pattern = "fus"))) { radius <- height*0.16 }
+                    if(!is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*0.3 }
+                    else { radius <- width*0.17 }
+                  }
+                  if(color == "turquoise4") {
+                    if(!is.na(str_match(string = tolower(feature), pattern = "fus|prot"))) { radius <- height*0.16 }
                     else { radius <- width*0.18 }
                   }
-                  if(color == "turquoise4") {
-                    if(!is.na(str_match(string = tolower(feature), pattern = "fus|prot"))) {
-                      radius <- height*0.16
-                    }
-                    else { radius <- width*0.18 }
-                  grid.text(signif_grid_annot1[i, j], x = x + width*0.25, y = y + height*0.07, gp = gpar(fontsize = 17))
+
+                  grid.text(signif_grid_annot1[i, j], x = x + width*0.25, y = y + height*0.065, gp = gpar(fontsize = 17))
 
@@
                   if(signif_grid_annot[i, j] == "X") {
-                    grid.circle(x = x - width*0.20, y = y - height*0.20, r = radius, default.units = "npc", gp = gpar(fill = "red", col = "black"))
+                    grid.circle(x = x - width*0.20, y = y + height*0.20, r = radius, default.units = "npc", gp = gpar(fill = "red", col = "black"))
                   }
@@
                   }
-                }
+                })
 
@@
 ### Pancan
-
-**10/23 STOPPED HERE: Was fixing annotation dot sizes on heatmaps**
 
@@
 
-ht_crispr2 <- MakeWilcoxonHeatmap(signif_df = crispr_signif_prot_4plot, feature = "protein changes CRISPR", legend_title = "CRISPR -log10(p-value)", legend_breaks = seq(0, 25, by = 5), row_names = FALSE, color = "darkorchid4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black")
 ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot_4plot, feature = "protein changes", legend_title = "CCLE -log10(p-value)          ", legend_breaks = seq(0, 15, by = 3), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black")
@@
 ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = gdsc_signif_prot_4plot, feature = "protein changes", legend_title = "GDSC -log10(p-value)          ", legend_breaks = seq(0, 8, by = 2), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black")
+ht_crispr2 <- MakeWilcoxonHeatmap(signif_df = crispr_signif_prot_4plot, feature = "protein changes CRISPR", legend_title = "CRISPR -log10(p-value)", legend_breaks = seq(0, 25, by = 5), row_names = FALSE, color = "darkorchid4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black")
+
 png(filename = "./plots/manuscript/all_prot_heatmap.png", width = 14, height = 5, units = "in", res = 500)
@@
 
+**10/25 Need to fix InG2P annots on CTRP data**
+
 ```{r fus_heatmaps, eval=FALSE}
+ht_crispr <- MakeWilcoxonHeatmap(signif_df = filter(crispr_signif_fus, Drug_Gene == "CRISPR_ABL1" & FusionPair %in% c("BCR-ABL1", "ABL1-BCR")), feature = "fusion crispr", legend_title = "-log10(p-value)",  legend_breaks = seq(0, 2, by = 0.5), row_names = TRUE, color = "darkorchid4", col_title = "Drugs", row_title_txt = "Fusion Pairs")
+png(filename = "./plots/manuscript/crispr_fus_heatmap.png", width = 3, height = 3, units = "in", res = 500)
+draw(ht_crispr, heatmap_legend_side = "top")
+dev.off()
+
 ht_ccle <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "-log10(p-value)",  legend_breaks = seq(0, 4, by = 1), row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Fusion Pairs")
@@
 ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "CTRP -log10(p-value)          ", legend_breaks = seq(0, 10, by = 2), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Fusion Pairs")
-ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Fusion Pairs")
-png(filename = "./plots/manuscript/drug_fus_heatmap.png", width = 13, height = 2.4, units = "in", res = 500)
-draw(ht_ccle2 + ht_ctrp2 + ht_gdsc2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
-dev.off()
-```
+ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "GDSC -log10(p-value)          ", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Fusion Pairs")
+ht_crispr2 <- MakeWilcoxonHeatmap(signif_df = filter(crispr_signif_fus, Drug_Gene == "CRISPR_ABL1" & FusionPair %in% c("BCR-ABL1", "ABL1-BCR")), feature = "fusion crispr", legend_title = "CRISPR -log10(p-value)",  legend_breaks = seq(0, 2, by = 0.5), row_names = FALSE, color = "darkorchid4", col_title = "", row_title_txt = "Fusion Pairs")
+
+png(filename = "./plots/manuscript/all_fus_heatmap.png", width = 15, height = 2.4, units = "in", res = 500)
+draw(ht_ccle2 + ht_ctrp2 + ht_gdsc2 + ht_crispr2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
+dev.off()
+```
+
+**10/23 MADE PLOTS UP TO HERE**
 
 ### Lineage
+
+**10/23 NEED TO RUN LINEAGE PLOTS**
 
@@
 # CRISPR
-crispr_spear_cn <- transform(crispr %>% group_by(Gene) %>% drop_na(CN) %>% summarize(p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value, p_log10 = -log10(p), corr = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate, Metric = "Copy Number"), Gene = reorder(Gene, corr))
-c("white", "deepskyblue4")
-crispr_spear_cn <- add_column(crispr_spear_cn, Drug = "CRISPR", .after = "Gene")
+crispr_spear_cn <- crispr %>% group_by(Gene) %>% drop_na(CN) %>%
+  summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate,
+            CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value,
+            CN_p_log10 = -log10(CN_p),
+            InG2P = "No",
+            Dataset = "CRISPR",
+            Metric = "Copy Number")
+crispr_spear_cn <- transform(crispr_spear_cn, Gene = reorder(Gene, CN_r))
+crispr_spear_cn <- add_column(crispr_spear_cn, Drug = "CRISPR", .before = "Gene")
+Drug_Gene <- with(crispr_spear_cn, paste0(Drug, "_", Gene))
+crispr_spear_cn <- add_column(crispr_spear_cn, Drug_Gene = Drug_Gene, .before = "Drug")
 saveRDS(crispr_spear_cn, "./data_munging/rds/crispr_cn_cor.rds")
 
-crispr_spear_ge <- transform(crispr %>% group_by(Gene) %>% drop_na(TPM) %>% summarize(p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value, p_log10 = -log10(p), corr = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate, Metric = "Gene Expression"), Gene = reorder(Gene, corr))
-crispr_spear_ge <- add_column(crispr_spear_ge, Drug = "CRISPR", .after = "Gene")
+crispr_spear_ge <- crispr %>% group_by(Gene) %>% drop_na(TPM) %>%
+  summarize(GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate,
+            GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value,
+            GE_p_log10 = -log10(GE_p),
+            InG2P = "No",
+            Dataset = "CRISPR",
+            Metric = "Gene Expression")
+crispr_spear_ge <- transform(crispr_spear_ge, Gene = reorder(Gene, GE_r))
+crispr_spear_ge <- add_column(crispr_spear_ge, Drug = "CRISPR", .before = "Gene")
+Drug_Gene <- with(crispr_spear_ge, paste0(Drug, "_", Gene))
+crispr_spear_ge <- add_column(crispr_spear_ge, Drug_Gene = Drug_Gene, .before = "Drug")
 saveRDS(crispr_spear_ge, "./data_munging/rds/crispr_ge_cor.rds")
@@
 ccle_filt <- unfactorize(ccle_filt)
-ccle_ge_res <- ccle_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(TPM) %>% summarize(GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$estimate, GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$p.value)
+ccle_ge_res <- ccle_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(TPM) %>%
+  summarize(GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$estimate,
+            GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$p.value, 
+            GE_p_log10 = -log10(GE_p))
 ccle_ge_res$InG2P <- ifelse(ccle_ge_res$Drug_Gene %in% unique(as.character(g2p_expr$Drug_Gene[!is.na(g2p_expr$Drug_Gene)])), "Yes", "No")
@@
 
-ccle_cn_res <- ccle_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(CN) %>% summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$estimate, CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$p.value)
+ccle_cn_res <- ccle_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(CN) %>%
+  summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$estimate,
+            CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$p.value,
+            CN_p_log10 = -log10(CN_p))
 ccle_cn_res$InG2P <- ifelse(ccle_cn_res$Drug_Gene %in% unique(as.character(g2p_amp$Drug_Gene[!is.na(g2p_amp$Drug_Gene)])), "Yes", "No")
@@
 ctrp_filt <- unfactorize(ctrp_filt)
-ctrp_ge_res <- ctrp_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(TPM) %>% summarize(GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$estimate, GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$p.value)
+ctrp_ge_res <- ctrp_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(TPM) %>%
+  summarize(GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$estimate,
+            GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$p.value,
+            GE_p_log10 = -log10(GE_p))
 ctrp_ge_res$InG2P <- ifelse(ctrp_ge_res$Drug_Gene %in% unique(as.character(g2p_expr$Drug_Gene[!is.na(g2p_expr$Drug_Gene)])), "Yes", "No")
@@
 
-ctrp_cn_res <- ctrp_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(CN) %>% summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$estimate, CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$p.value)
+ctrp_cn_res <- ctrp_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(CN) %>%
+  summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$estimate,
+            CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$p.value,
+            CN_p_log10 = -log10(CN_p))
 ctrp_cn_res$InG2P <- ifelse(ctrp_cn_res$Drug_Gene %in% unique(as.character(g2p_amp$Drug_Gene[!is.na(g2p_amp$Drug_Gene)])), "Yes", "No")
@@
 gdsc_filt <- unfactorize(gdsc_filt)
-gdsc_ge_res <- gdsc_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(TPM) %>% summarize(GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$estimate, GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$p.value)
+gdsc_ge_res <- gdsc_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(TPM) %>%
+  summarize(GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$estimate,
+            GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$p.value,
+            GE_p_log10 = -log10(GE_p))
 gdsc_ge_res$InG2P <- ifelse(gdsc_ge_res$Drug_Gene %in% unique(as.character(g2p_expr$Drug_Gene[!is.na(g2p_expr$Drug_Gene)])), "Yes", "No")
@@
 
-gdsc_cn_res <- gdsc_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(CN) %>% summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$estimate, CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$p.value)
+gdsc_cn_res <- gdsc_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(CN) %>%
+  summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$estimate,
+            CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$p.value,
+            CN_p_log10 = -log10(CN_p))
 gdsc_cn_res$InG2P <- ifelse(gdsc_cn_res$Drug_Gene %in% unique(as.character(g2p_amp$Drug_Gene[!is.na(g2p_amp$Drug_Gene)])), "Yes", "No")
@@
 ```{r load_spear}
-g2p_amp_crispr_4merge <- select(g2p_amp, Gene, Direction_Curated)
-
+# Drug screens
+## CN
+g2p_amp_4merge <- select(g2p_amp, Drug_Gene, Direction_Curated)
+amp_summ <- g2p_amp_4merge %>% count(Drug_Gene)
+amp_summ <- merge(amp_summ, g2p_amp_4merge, by = "Drug_Gene")
+amp_summ$Direction_Heatmap <- with(amp_summ, ifelse(n == 2, "both", ifelse(n == 1 & Direction_Curated == "resistance", "resistance", "sensitivity")))
+amp_summ <- unique(select(amp_summ, Drug_Gene, Direction_Heatmap))
+cn_cor <- readRDS("./data_munging/rds/drug_cn_cor.rds")
+cn_cor <- merge(cn_cor, amp_summ, by = "Drug_Gene", all.x = TRUE)
+## GE
+g2p_expr_4merge <- select(g2p_expr, Drug_Gene, Direction_Curated)
+expr_summ <- g2p_expr_4merge %>% count(Drug_Gene)
+expr_summ <- merge(expr_summ, g2p_expr_4merge, by = "Drug_Gene")
+expr_summ$Direction_Heatmap <- with(expr_summ, ifelse(n == 2, "both", ifelse(n == 1 & Direction_Curated == "resistance", "resistance", "sensitivity")))
+expr_summ <- unique(select(expr_summ, Drug_Gene, Direction_Heatmap))
+ge_cor <- readRDS("./data_munging/rds/drug_ge_cor.rds")
+ge_cor <- merge(ge_cor, expr_summ, by = "Drug_Gene", all.x = TRUE)
+
+# CRISPR
+## CN
+g2p_cn_crispr_4merge <- unique(select(g2p_amp, Gene, Direction_Curated))
+crispr_cn_summ <- g2p_cn_crispr_4merge %>% count(Gene)
+crispr_cn_summ <- merge(crispr_cn_summ, g2p_cn_crispr_4merge, by = "Gene")
+crispr_cn_summ$Direction_Heatmap <- with(crispr_cn_summ, ifelse(n == 2, "both", ifelse(n == 1 & Direction_Curated == "resistance", "resistance", "sensitivity")))
+crispr_cn_summ <- unique(select(crispr_cn_summ, Gene, Direction_Heatmap))
 crispr_spear_cn <- readRDS("./data_munging/rds/crispr_cn_cor.rds")
+crispr_cn_cor <- merge(crispr_spear_cn, crispr_cn_summ, by = "Gene", all.x = TRUE)
+crispr_cn_cor$Metric <- NULL
+## GE
+g2p_ge_crispr_4merge <- unique(select(g2p_expr, Gene, Direction_Curated))
+crispr_ge_summ <- g2p_ge_crispr_4merge %>% count(Gene)
+crispr_ge_summ <- merge(crispr_ge_summ, g2p_ge_crispr_4merge, by = "Gene")
+crispr_ge_summ$Direction_Heatmap <- with(crispr_ge_summ, ifelse(n == 2, "both", ifelse(n == 1 & Direction_Curated == "resistance", "resistance", "sensitivity")))
+crispr_ge_summ <- unique(select(crispr_ge_summ, Gene, Direction_Heatmap))
 crispr_spear_ge <- readRDS("./data_munging/rds/crispr_ge_cor.rds")
-
-g2p_amp_4merge <- select(g2p_amp, Drug_Gene, Direction_Curated)
-cn_cor <- readRDS("./data_munging/rds/drug_cn_cor.rds")
-cn_cor <- merge(cn_cor, g2p_amp_4merge, by = "Drug_Gene", all.x = TRUE)
-
-g2p_expr_4merge <- select(g2p_expr, Drug_Gene, Direction_Curated)
-ge_cor <- readRDS("./data_munging/rds/drug_ge_cor.rds")
-ge_cor <- merge(ge_cor, g2p_expr_4merge, by = "Drug_Gene", all.x = TRUE)
+crispr_ge_cor <- merge(crispr_spear_ge, crispr_ge_summ, by = "Gene", all.x = TRUE)
+crispr_ge_cor$Drug_Gene <- paste0(crispr_ge_cor$Drug, "_", crispr_ge_cor$Gene)
+crispr_ge_cor$Metric <- NULL
+
+all_cn_cor <- rbind(cn_cor, crispr_cn_cor)
+all_ge_cor <- rbind(ge_cor, crispr_ge_cor)
 ```
@@
 crispr_spear_cn_plot <- ggplot(data = filter(crispr_spear_cn, Gene %in% g2p_dg_genes)) +
-  geom_point(aes(x = Gene, y = corr, fill = p_log10), pch = 21, size = 5) +
+  geom_point(aes(x = Gene, y = CN_r, fill = CN_p_log10), pch = 21, size = 5) +
   theme(legend.position = "bottom") +
   scale_fill_gradientn(colours = c("white", "green4"),
-                       breaks = c(0, 4, 8, 12, 16, 20),
-                       labels = c(0, 4, 8, 12, 16, 20),
-                       limits = c(0, 21)) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 10)) +
+                       breaks = seq(0, 14, by = 2),
+                       labels = seq(0, 14, by = 2),
+                       limits = c(0, 14)) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 10), legend.key.width = unit(0.5, "in")) +
   labs(title = "Copy Number",
@@
 crispr_spear_ge_plot <- ggplot(data = filter(crispr_spear_ge, Gene %in% g2p_dg_genes)) +
-  geom_point(aes(x = Gene, y = corr, fill = p_log10), pch = 21, size = 5) +
+  geom_point(aes(x = Gene, y = GE_r, fill = GE_p_log10), pch = 21, size = 5) +
   theme(legend.position = "bottom") +
   scale_fill_gradientn(colours = c("white", "deepskyblue4"),
-                       breaks = c(0, 4, 8, 12, 16, 20),
-                       labels = c(0, 4, 8, 12, 16, 20),
-                       limits = c(0, 21)) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 10)) +
+                       breaks = seq(0, 14, by = 2),
+                       labels = seq(0, 14, by = 2),
+                       limits = c(0, 14)) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 10), legend.key.width = unit(0.5 , "in")) +
   labs(title = "Gene Expression",
@@
 
-# ggsave("./plots/manuscript/crispr_spearman_corr_plot.png", crispr_spearman_corr_plot, device = "png", dpi = 450, width = 20, height = 10, units = "in")
-```
-
-```{r}
-    signif_df <- filter(crispr_signif_g2p_g, Gene %in% unique(g2p_mut$Gene))
-    signif_grid <- dcast(signif_df, Gene ~ Drug, value.var = "p_log10", fun.aggregate = mean, fill = 0)
-    signif_grid <- signif_grid[match(g2p_gene_order, signif_grid$Gene),] %>% drop_na(Gene) %>% `rownames<-`(.[,1]) %>% select(-Gene)
-
-    signif_grid_annot1 <- signif_grid
-    signif_grid_annot1[signif_grid_annot1 <= -log10(0.05) | is.na(signif_grid_annot1)] <- ""
-    signif_grid_annot1[signif_grid_annot1 > -log10(0.05)] <- "*"
-
-```
+ggsave("./plots/manuscript/crispr_spearman_corr_plot.png", crispr_spearman_corr_plot, device = "png", dpi = 450, width = 20, height = 10, units = "in")
+```
+
+**10/28 FIX CRISPR PART OF corr_heatmap_function**
 
@@
   if(crispr == TRUE) {
-    annot_grid <- dcast(cor_res, Gene ~ Drug, value.var = "Direction_Curated", fill = 0)
+    annot_grid <- dcast(cor_res, Gene ~ Drug, value.var = "Direction_Heatmap", fill = 0)
     annot_grid <- annot_grid[match(g2p_gene_order, annot_grid$Gene),] %>% drop_na(Gene) %>% `rownames<-`(.[,1]) %>% select(-Gene)
@@
   if(crispr == FALSE) {
-    annot_grid <- dcast(cor_res, Gene ~ Drug, value.var = "Direction_Curated", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
+    annot_grid <- dcast(cor_res, Gene ~ Drug, value.var = "Direction_Heatmap", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
     annot_grid <- annot_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
@@
   # Legend properties list
-  ht_legend_list <- list(title_position = "topleft", legend_direction = "horizontal", legend_width = unit(3, "in"), border = "gray70", at = seq(color_range[1], color_range[3], by = 0.1), labels = seq(color_range[1], color_range[3], by = 0.1))
+  if(metric == "CN") { legend_sep <- 0.1 }
+  if(metric == "GE") { legend_sep <- 0.2 }
+  ht_legend_list <- list(title_position = "topleft",
+                         legend_direction = "horizontal",
+                         legend_width = unit(2, "in"),
+                         border = "gray70",
+                         at = seq(color_range[1], color_range[3], by = legend_sep),
+                         labels = seq(color_range[1], color_range[3], by = legend_sep))
+
   ht <- Heatmap(corr_grid,
@@
                 cell_fun = function(j, i, x, y, width, height, fill) {
-                  grid.text(signif_grid[i, j], x = x - width*0.20, y = y, gp = gpar(fontsize = 18))
+                  grid.text(signif_grid[i, j], x = x + width*0.20, y = y + height*0.025, gp = gpar(fontsize = 18))
                   if(annot_grid[i, j] == "sensitivity") {
                     grid.circle(x = x - width*0.20, y = y - height*0.20, r = height*0.15, default.units = "npc", gp = gpar(fill = "white", col = "black"))
-                    # grid.circle(x = x, y = y, r = radius, gp = gpar(fill = "transparent", col = "black"))
                   }
                   if(annot_grid[i, j] == "resistance") {
-                    grid.circle(x = x - width*0.20, y = y - height*0.20, r = height*0.15, default.units = "npc", gp = gpar(fill = "red", col = "black"))
-                    # grid.text("☐", x, y, just = c(0.5, 0.425), gp = gpar(fontsize = 23, fontface = "bold"))
+                    grid.circle(x = x - width*0.20, y = y + height*0.20, r = height*0.15, default.units = "npc", gp = gpar(fill = "red", col = "black"))
+                  }
+                  if(annot_grid[i, j] == "both") {
+                    grid.circle(x = x - width*0.20, y = y + height*0.20, r = height*0.15, default.units = "npc", gp = gpar(fill = "red", col = "black"))
+                    grid.circle(x = x - width*0.20, y = y - height*0.20, r = height*0.15, default.units = "npc", gp = gpar(fill = "white", col = "black"))
                   }
@@
 ```{r drug_spear_plots, eval=FALSE}
-# CRISPR
-crispr_spear_cn <- unfactorize(filter(crispr_spear_cn, Gene %in% unique(g2p_amp$Gene)))
-crispr_cn_ht <- MakeCorrHeatmap(drug_cor_res = crispr_spear_cn, row_names = TRUE, col_title = "CCLE", color_range = c(-0.2, 0, 0.2), radius = 0.1, legend_title = "CCLE Spearman correlation", metric = "CN")
-png(filename = "./plots/manuscript/crispr_cn_heatmap.png", width = 3, height = 3, units = "in", res = 500)
-draw(crispr_cn_ht, heatmap_legend_side = "top")
-dev.off()
-
 # Copy number
-ccle_cn_cor <- unfactorize(filter(cn_cor, Dataset == "CCLE" & Gene %in% unique(g2p_amp$Gene)))
-ccle_cn_ht <- MakeCorrHeatmap(drug_cor_res = ccle_cn_cor, row_names = TRUE, col_title = "CCLE", color_range = c(-0.2, 0, 0.2), radius = 0.1, legend_title = "CCLE Spearman correlation", metric = "CN")
-png(filename = "./plots/manuscript/ccle_cn_heatmap.png", width = 3, height = 3, units = "in", res = 500)
+ccle_cn_cor <- unfactorize(filter(all_cn_cor, Dataset == "CCLE" & Gene %in% unique(g2p_amp$Gene)))
+ccle_cn_ht <- MakeCorrHeatmap(cor_res = ccle_cn_cor, row_names = TRUE, col_title = "CCLE", color_range = c(-0.25, 0, 0.25), radius = 0.1, legend_title = "CCLE Spearman correlation", metric = "CN", crispr =  FALSE)
+png(filename = "./plots/manuscript/ccle_cn_heatmap.png", width = 3, height = 4, units = "in", res = 500)
 draw(ccle_cn_ht, heatmap_legend_side = "top")
@@
 
-ctrp_cn_cor <- unfactorize(filter(cn_cor, Dataset == "CTRP" & Gene %in% unique(g2p_amp$Gene)))
-ctrp_cn_ht <- MakeCorrHeatmap(drug_cor_res = ctrp_cn_cor, row_names = TRUE, col_title = "CTRP", color_range = c(-0.2, 0, 0.2), radius = 0.1, legend_title = "CTRP Spearman correlation", metric = "CN")
+ctrp_cn_cor <- unfactorize(filter(all_cn_cor, Dataset == "CTRP" & Gene %in% unique(g2p_amp$Gene)))
+ctrp_cn_ht <- MakeCorrHeatmap(cor_res = ctrp_cn_cor, row_names = TRUE, col_title = "CTRP", color_range = c(-0.25, 0, 0.25), radius = 0.1, legend_title = "CTRP Spearman correlation", metric = "CN", crispr =  FALSE)
 png(filename = "./plots/manuscript/ctrp_cn_heatmap.png", width = 8, height = 3, units = "in", res = 500)
@@
 
-gdsc_cn_cor <- unfactorize(filter(cn_cor, Dataset == "GDSC" & Gene %in% unique(g2p_amp$Gene)))
-gdsc_cn_ht <- MakeCorrHeatmap(drug_cor_res = gdsc_cn_cor, row_names = TRUE, col_title = "GDSC", color_range = c(-0.2, 0, 0.2), radius = 0.1, legend_title = "GDSC Spearman correlation", metric = "CN")
+gdsc_cn_cor <- unfactorize(filter(all_cn_cor, Dataset == "GDSC" & Gene %in% unique(g2p_amp$Gene)))
+gdsc_cn_ht <- MakeCorrHeatmap(cor_res = gdsc_cn_cor, row_names = TRUE, col_title = "GDSC", color_range = c(-0.25, 0, 0.25), radius = 0.1, legend_title = "GDSC Spearman correlation", metric = "CN",  crispr = FALSE)
 png(filename = "./plots/manuscript/gdsc_cn_heatmap.png", width = 5, height = 3, units = "in", res = 500)
@@
 
-ccle_cn_ht2 <- MakeCorrHeatmap(drug_cor_res = ccle_cn_cor, row_names = TRUE, col_title = "CCLE", color_range = c(-0.2, 0, 0.2), radius = 0.025, legend_title = "Copy num.
-Spearman correlation", metric = "CN")
-ctrp_cn_ht2 <- MakeCorrHeatmap(drug_cor_res = ctrp_cn_cor, row_names = FALSE, col_title = "CTRP", color_range = c(-0.2, 0, 0.2), radius = 0.025, legend_title = "Copy num.
-Spearman correlation", metric = "CN")
-gdsc_cn_ht2 <- MakeCorrHeatmap(drug_cor_res = gdsc_cn_cor, row_names = FALSE, col_title = "GDSC", color_range = c(-0.2, 0, 0.2), radius = 0.025, legend_title = "Copy num.
-Spearman correlation", metric = "CN")
-png(filename = "./plots/manuscript/drug_cn_heatmap.png", width = 13, height = 3, units = "in", res = 500)
+ccle_cn_ht2 <- MakeCorrHeatmap(cor_res = ccle_cn_cor, row_names = TRUE, col_title = "CCLE", color_range = c(-0.25, 0, 0.25), radius = 0.025, legend_title = "Copy num.
+Spearman correlation", metric = "CN", crispr =  FALSE)
+ctrp_cn_ht2 <- MakeCorrHeatmap(cor_res = ctrp_cn_cor, row_names = FALSE, col_title = "CTRP", color_range = c(-0.25, 0, 0.25), radius = 0.025, legend_title = "Copy num.
+Spearman correlation", metric = "CN", crispr =  FALSE)
+gdsc_cn_ht2 <- MakeCorrHeatmap(cor_res = gdsc_cn_cor, row_names = FALSE, col_title = "GDSC", color_range = c(-0.25, 0, 0.25), radius = 0.025, legend_title = "Copy num.
+Spearman correlation", metric = "CN", crispr =  FALSE)
+png(filename = "./plots/manuscript/drug_cn_heatmap.png", width = 13, height = 3.5, units = "in", res = 500)
 draw(ccle_cn_ht2 + ctrp_cn_ht2 + gdsc_cn_ht2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
@@
 # Gene expression
-ccle_ge_cor <- unfactorize(filter(ge_cor, Dataset == "CCLE" & Gene %in% unique(g2p_expr$Gene)))
-ccle_ge_ht <- MakeCorrHeatmap(drug_cor_res = ccle_ge_cor, row_names = TRUE, col_title = "CCLE", color_range = c(-0.5, 0, 0.5), radius = 0.2, legend_title = "CCLE Spearman correlation", metric = "GE")
+ccle_ge_cor <- unfactorize(filter(all_ge_cor, Dataset == "CCLE" & Gene %in% unique(g2p_expr$Gene)))
+ccle_ge_ht <- MakeCorrHeatmap(cor_res = ccle_ge_cor, row_names = TRUE, col_title = "CCLE", color_range = c(-0.5, 0, 0.5), radius = 0.2, legend_title = "CCLE Spearman correlation", metric = "GE", crispr =  FALSE)
 png(filename = "./plots/manuscript/ccle_ge_heatmap.png", width = 3, height = 2.5, units = "in", res = 500)
@@
 
-ctrp_ge_cor <- unfactorize(filter(ge_cor, Dataset == "CTRP" & Gene %in% unique(g2p_expr$Gene)))
-ctrp_ge_ht <- MakeCorrHeatmap(drug_cor_res = ctrp_ge_cor, row_names = TRUE, col_title = "CTRP", color_range = c(-0.5, 0, 0.5), radius = 0.2, legend_title = "CTRP Spearman correlation", metric = "GE")
+ctrp_ge_cor <- unfactorize(filter(all_ge_cor, Dataset == "CTRP" & Gene %in% unique(g2p_expr$Gene)))
+ctrp_ge_ht <- MakeCorrHeatmap(cor_res = ctrp_ge_cor, row_names = TRUE, col_title = "CTRP", color_range = c(-0.5, 0, 0.5), radius = 0.2, legend_title = "CTRP Spearman correlation", metric = "GE", crispr =  FALSE)
 png(filename = "./plots/manuscript/ctrp_ge_heatmap.png", width = 8, height = 2.5, units = "in", res = 500)
@@
 
-gdsc_ge_cor <- unfactorize(filter(ge_cor, Dataset == "GDSC" & Gene %in% unique(g2p_expr$Gene)))
-gdsc_ge_ht <- MakeCorrHeatmap(drug_cor_res = gdsc_ge_cor, row_names = TRUE, col_title = "GDSC", color_range = c(-0.5, 0, 0.5), radius = 0.2, legend_title = "GDSC Spearman correlation", metric = "GE")
+gdsc_ge_cor <- unfactorize(filter(all_ge_cor, Dataset == "GDSC" & Gene %in% unique(g2p_expr$Gene)))
+gdsc_ge_ht <- MakeCorrHeatmap(cor_res = gdsc_ge_cor, row_names = TRUE, col_title = "GDSC", color_range = c(-0.5, 0, 0.5), radius = 0.2, legend_title = "GDSC Spearman correlation", metric = "GE", crispr =  FALSE)
 png(filename = "./plots/manuscript/gdsc_ge_heatmap.png", width = 5, height = 2.5, units = "in", res = 500)
@@
 
-ccle_ge_ht2 <- MakeCorrHeatmap(drug_cor_res = ccle_ge_cor, row_names = TRUE, col_title = "CCLE", color_range = c(-0.5, 0, 0.5), radius = 0.2, legend_title = "Gene expr.
-Spearman correlation", metric = "GE")
-ctrp_ge_ht2 <- MakeCorrHeatmap(drug_cor_res = ctrp_ge_cor, row_names = FALSE, col_title = "CTRP", color_range = c(-0.5, 0, 0.5), radius = 0.2, legend_title = "Gene expr.
-Spearman correlation", metric = "GE")
-gdsc_ge_ht2 <- MakeCorrHeatmap(drug_cor_res = gdsc_ge_cor, row_names = FALSE, col_title = "GDSC", color_range = c(-0.5, 0, 0.5), radius = 0.2, legend_title = "Gene expr.
-Spearman correlation", metric = "GE")
-png(filename = "./plots/manuscript/drug_ge_heatmap.png", width = 13, height = 2.5, units = "in", res = 500)
+ccle_ge_ht2 <- MakeCorrHeatmap(cor_res = ccle_ge_cor, row_names = TRUE, col_title = "CCLE", color_range = c(-0.5, 0, 0.5), radius = 0.2, legend_title = "Gene expr.
+Spearman correlation", metric = "GE", crispr =  FALSE)
+ctrp_ge_ht2 <- MakeCorrHeatmap(cor_res = ctrp_ge_cor, row_names = FALSE, col_title = "CTRP", color_range = c(-0.5, 0, 0.5), radius = 0.2, legend_title = "Gene expr.
+Spearman correlation", metric = "GE", crispr =  FALSE)
+gdsc_ge_ht2 <- MakeCorrHeatmap(cor_res = gdsc_ge_cor, row_names = FALSE, col_title = "GDSC", color_range = c(-0.5, 0, 0.5), radius = 0.2, legend_title = "Gene expr.
+Spearman correlation", metric = "GE", crispr =  FALSE)
+png(filename = "./plots/manuscript/drug_ge_heatmap.png", width = 13, height = 3, units = "in", res = 500)
 draw(ccle_ge_ht2 + ctrp_ge_ht2 + gdsc_ge_ht2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
@@
 ```
+
+**10/28 NEED TO MAKE SPEAR CORR PLOTS WITH CRISPR PANEL**
 

### 2019-10-29 manuscript.Rmd
update manu w/ figs

@@
     # citation_package: natbib
+header-includes:
+- \usepackage{caption}
 title               : "Manuscript Draft"
@@
 
+# Results
+
+## Curating clinical biomarkers
+
 To curate an evidence-based list of these clinical biomarkers, we utilized a new oncological data aggregation project conducted by the Variant Interpretation for Cancer Consortium (VICC; https://cancervariants.org/), a Driver Project for the Global Alliance for Genomics and Health (GA4GH) [@theglobalallianceforgenomicsandhealth2016].
@@
 We also analyzed the results from a large-scale CRISPR/Cas9 screen conducted by the Broad Institute’s Cancer Dependency Map project (DepMap) using the Avana knockout library [@doench2016a; @meyers2017], which will address whether gene essentiality screens via CRISPR yield results comparable to functional drug screens.
-
-# Results
 
@@
 
-> Mutation status
+![Overlap of cancer cell lines in our four datasets.](./plots/manuscript/all_venn_ccls.png)
 
-> Fusions
+### Mutation status
 
-> Copy number
+![Mutation status.](./plots/manuscript/all_mut_heatmap.png)
 
-> Gene expression
+![Protein changes.](./plots/manuscript/all_prot_heatmap.png)
 
-However, taking these results as a whole, we observe little concordance between G2P associations and the correlation of mutation status and AUC for said G2P association, suggesting that mutation status alone is not a robust predictor of clinically actionable genetic targets.
+Taking these results as a whole, we observe little concordance between G2P associations and the correlation of mutation status and AUC for said G2P association, suggesting that mutation status alone is not a robust predicto r of clinically actionable genetic targets.
 This led us to examine the correlations between AUC and gene expression and AUC and copy number, two other genomic features that are known to associate with cancer and drug response.
-We computed Spearman correlation coefficients ($r_s$) between AUC of each drug-gene association and gene expression (RPKM) and copy number (log$_2$ ratio) of the gene in the association...**(???) need to complete this thought/analysis**
+We computed Spearman correlation coefficients ($r_s$) between AUC of each drug-gene association and gene expression (RPKM) and copy number (log$_2$ ratio) of the gene in the association...**need to complete this thought/analysis**
+
+### Fusions
+
+![Fusion status.](./plots/manuscript/all_fus_heatmap.png)
+
+### Copy number
+
+![Correlation between putative copy number and AUC.](./plots/manuscript/drug_cn_heatmap.png)
+
+### Gene expression
+
+![Correlation between gene expression and AUC.](./plots/manuscript/drug_ge_heatmap.png)
 
@@
 - What do these correlations with mutation status, gene expression, and copy number look like when you constrict to a specific lineage?
-- When you restrict, do the correlations become more distinct?
-- Are the lineage-specific results approximately the same as the pancancer results?
+- When you restrict, do the correlations become more distinct or are the lineage-specific results approximately the same as the pancancer results?
 
@@
 
+**Need to update all methods for data processing, these method are current up to ~May 2019**
+
 ## G2P cancer variants
@@
 For this analysis, cell lines harboring non-silent point mutations were considered “mutant” for the gene in question.
-All other mutations and genes without annotation in the Mutation Annotation Format (MAF) file were considered “wildtype.” “Mutant” and “wildtype” calls were binarily encoded per-gene/per-cell line, regardless of quantity of harbored mutations per gene in a given cell line.
+All other mutations and genes without annotation in the Mutation Annotation Format (MAF) file were considered "wildtype." "Mutant" and "wildtype" calls were binarily encoded per-gene/per-cell line, regardless of quantity of harbored mutations per gene in a given cell line.
+
+### Protein changes
+
+### Fusion status
 

### 2019-10-29 19Q2.Rmd

@@
 g2p_fus$FusionPair <- ifelse(g2p_fus$FusionPair == "BCR-ABL", "BCR-ABL1", as.character(g2p_fus$FusionPair))
+g2p_fus <- g2p_fus[grep("-", g2p_fus$FusionPair), ]
 g2p_fus$Drug_FusionPair <- ifelse(is.na(g2p_fus$Drug) | is.na(g2p_fus$FusionPair), NA, paste0(g2p_fus$Drug, "_", g2p_fus$FusionPair))
@@
 
+```{r}
+ccle_signif_dgl %>% count(InG2P)
+filter(ccle_signif_dgl, InG2P == "Yes" & p < 0.05) %>% select(Drug, Gene, disease, p.short, Direction_Heatmap)
+ctrp_signif_dgl %>% count(InG2P)
+filter(ctrp_signif_dgl, InG2P == "Yes" & p < 0.05) %>% select(Drug, Gene, disease, p.short, Direction_Heatmap)
+gdsc_signif_dgl %>% count(InG2P)
+filter(gdsc_signif_dgl, InG2P == "Yes" & p < 0.05) %>% select(Drug, Gene, disease, p.short, Direction_Heatmap)
+```
+
 ### Protein changes
@@
 
+```{r}
+all_directions <- readRDS("./data_munging/rds/protein_changes_directions.rds")
+crispr_signif_prot_lin <- readRDS("./data_munging/rds/crispr_signif_protein_changes_lineage.rds")
+crispr_signif_prot_lin <- merge(crispr_signif_prot_lin, all_directions, by = c("Gene_Protein_Change", "Drug"), all.x = TRUE)
+ccle_signif_prot_lin <- readRDS("./data_munging/rds/ccle_signif_protein_changes_lineage.rds")
+ccle_signif_prot_lin <- merge(ccle_signif_prot_lin, all_directions, by = c("Gene_Protein_Change", "Drug"), all.x = TRUE)
+ctrp_signif_prot_lin <- readRDS("./data_munging/rds/ctrp_signif_protein_changes_lineage.rds")
+ctrp_signif_prot_lin <- merge(ctrp_signif_prot_lin, all_directions, by = c("Gene_Protein_Change", "Drug"), all.x = TRUE)
+gdsc_signif_prot_lin <- readRDS("./data_munging/rds/gdsc_signif_protein_changes_lineage.rds")
+gdsc_signif_prot_lin <- merge(gdsc_signif_prot_lin, all_directions, by = c("Gene_Protein_Change", "Drug"), all.x = TRUE)
+
+ccle_signif_prot_lin %>% count(InG2P)
+filter(ccle_signif_prot_lin, InG2P == "Yes" & p < 0.05) %>% select(Drug, Gene_Protein_Change, disease, p.short, Direction_Curated)
+ctrp_signif_prot_lin %>% count(InG2P)
+filter(ctrp_signif_prot_lin, InG2P == "Yes" & p < 0.05) %>% select(Drug, Gene_Protein_Change, disease, p.short, Direction_Curated)
+gdsc_signif_prot_lin %>% count(InG2P)
+filter(gdsc_signif_prot_lin, InG2P == "Yes" & p < 0.05) %>% select(Drug, Gene_Protein_Change, disease, p.short, Direction_Curated)
+```
+
 ## Fusions
@@
 ccle_fus <- unfactorize(ccle_fus)
+# ccle_fus_summ <- unique(select(ccle_fus, DepMap_ID, FusionPair, Fusion_Status)) %>% count(FusionPair, Fusion_Status)
 
@@
 ctrp_fus <- unfactorize(ctrp_fus)
+# ctrp_fus_summ <- unique(select(ctrp_fus, DepMap_ID, FusionPair, Fusion_Status)) %>% count(FusionPair, Fusion_Status)
 
@@
 gdsc_fus <- unfactorize(gdsc_fus)
+# gdsc_fus_summ <- unique(select(gdsc_fus, DepMap_ID, FusionPair, Fusion_Status)) %>% count(FusionPair, Fusion_Status)
 ```
@@
 ## Heatmaps
+
+**10/29 NEED TO FIX CIRCLE ANNOTS ON FUSION/STEELBLUE4 HEATMAP**
 
@@
                   annotation_height = unit(0.85, "in")),
-                  # annotation_height = max_text_width(colnames(signif_grid))),
                 row_title = row_title_txt,
@@
                 cell_fun = function(j, i, x, y, width, height, fill) {
-                  if(color == "darkorchid4") {
-                    if(is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*3.3 }
-                    if(!is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*2 }
-                  }
-                  if(color == "steelblue4") {
-                    if(!is.na(str_match(string = tolower(feature), pattern = "fus"))) { radius <- height*0.20 }
-                    if(!is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*0.16 }
-                    else { radius <- width*0.18 }
-                  }
                   if(color == "darkgreen") {
@@
                   }
+                  if(color == "steelblue4") {
+                    if(!is.na(str_match(string = tolower(feature), pattern = "fus"))) { radius <- height*0.5 }
+                    if(!is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*0.16 }
+                    else { radius <- width*0.18 }
+                  }
                   if(color == "turquoise4") {
@@
                   }
+                  if(color == "darkorchid4") {
+                    if(is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*3.3 }
+                    if(!is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*2 }
+                  }
 
@@
 }
+
+# ht_ctrp <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "-log10(p-value)", legend_breaks = seq(0, 10, by = 2), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Fusion Pairs")
+# png(filename = "./plots/manuscript/ctrp_fus_heatmap.png", width = 13, height = 3, units = "in", res = 500)
+# draw(ht_ctrp, heatmap_legend_side = "top")
+# dev.off()
+# 
+# ht_ctrp <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot_4plot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Gene:Protein Change")
+# png(filename = "./plots/manuscript/ctrp_prot_heatmap.png", width = 9.5, height = 5.5, units = "in", res = 500)
+# draw(ht_ctrp, heatmap_legend_side = "top")
+# dev.off()
 ```

### 2019-11-11 19Q2.Rmd
Added CRISPR code to GE/CN heatmap function

@@
 ```{r histology_dists_data, eval=FALSE}
-ccle_hists <- unique(select(ccle, DepMap_ID, disease)) %>% count(disease)
-ccle_hists$Perc <- ccle_hists$n / sum(ccle_hists$n) * 100
-ccle_hists$Dataset <- "CCLE"
-ctrp_hists <- unique(select(ctrp, DepMap_ID, disease)) %>% count(disease)
-ctrp_hists$Perc <- ctrp_hists$n / sum(ctrp_hists$n) * 100
-ctrp_hists$Dataset <- "CTRP"
-gdsc_hists <- unique(select(gdsc, DepMap_ID, disease)) %>% count(disease)
-gdsc_hists$Perc <- gdsc_hists$n / sum(gdsc_hists$n) * 100
-gdsc_hists$Dataset <- "GDSC"
-crispr_hists <- unique(select(crispr, DepMap_ID, disease)) %>% count(disease)
-crispr_hists$Perc <- crispr_hists$n / sum(crispr_hists$n) * 100
-crispr_hists$Dataset <- "CRISPR"
+hist_count <- function(df, dataset) {
+  hists <- unique(select(df, DepMap_ID, disease)) %>% count(disease)
+  hists$Percent <- hists$n / sum(hists$n) * 100
+  hists$Dataset <- dataset
+  hists$disease <- gsub(" cancer", "", hists$disease)
+  hists <- hists[order(hists$n, decreasing = T),]
+  return(hists)
+}
+
+ccle_hists <- hist_count(ccle, "CCLE")
+ctrp_hists <- hist_count(ctrp, "CTRP")
+gdsc_hists <- hist_count(gdsc, "GDSC")
+crispr_hists <- hist_count(crispr, "CRISPR")
 
@@
 drug_hists$Dataset <- factor(drug_hists$Dataset, levels = c("CCLE", "CTRP", "GDSC", "CRISPR"))
-drug_hists$disease <- as.character(drug_hists$disease)
-drug_hists$disease <- gsub(" cancer", "", drug_hists$disease)
+# drug_hists$disease <- as.character(drug_hists$disease)
 saveRDS(drug_hists, "./data_munging/rds/histology_distributions.rds")
@@
 drug_hists <- readRDS("./data_munging/rds/histology_distributions.rds")
+
 png(filename = "./plots/manuscript/all_histology_distributions.png", width = 8, height = 9, units = "in", res = 500)
@@
 **10/28 FIX CRISPR PART OF corr_heatmap_function**
+**11/11 Added CRISPR code to function, but R aborted due to misplaced bracket (fixed but did not run)**
 
 ```{r corr_heatmap_function}
-MakeCorrHeatmap <- function(cor_res, row_names, col_title, color_range, legend_title, metric, radius, crispr) {
+MakeCorrHeatmap <- function(cor_res, row_names, col_title, color_range, legend_title, metric, radius) {
   if(toupper(metric) == "CN" | toupper(metric) == "COPY NUMBER") {
-    if(crispr == TRUE) {
-
-    }
-    if(crispr == FALSE) {
+    if(col_title == "CRISPR") {
+      signif_grid <- dcast(cor_res, Gene ~ Drug, value.var = "CN_p", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
+      signif_grid <- signif_grid[g2p_gene_order,]
+      signif_grid[signif_grid >= 0.05] <- ""
+      signif_grid[signif_grid != ""] <- "*"
+
+      corr_grid <- dcast(cor_res, Gene ~ Drug, value.var = "CN_r", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
+      corr_grid <- corr_grid[g2p_gene_order,]
+    }
+    if(col_title != "CRISPR") {
       signif_grid <- dcast(cor_res, Gene ~ Drug, value.var = "CN_p", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
@@
   if(toupper(metric) == "GE" | toupper(metric) == "GENE EXPRESSION") {
-    if(crispr == TRUE) {
-
-    }
-    if(crispr == FALSE) {
+    if(col_title == "CRISPR") {
+      signif_grid <- dcast(cor_res, Gene ~ Drug, value.var = "GE_p", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
+      signif_grid <- signif_grid[g2p_gene_order,]
+      signif_grid[signif_grid >= 0.05] <- ""
+      signif_grid[signif_grid != ""] <- "*"
+
+      corr_grid <- dcast(cor_res, Gene ~ Drug, value.var = "CN_r", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
+      corr_grid <- corr_grid[g2p_gene_order,]
+    }
+    if(col_title != "CRISPR") {
       signif_grid <- dcast(cor_res, Gene ~ Drug, value.var = "GE_p", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
@@
   }
-  if(crispr == TRUE) {
+
+  if(col_title == "CRISPR") {
     annot_grid <- dcast(cor_res, Gene ~ Drug, value.var = "Direction_Heatmap", fill = 0)
     annot_grid <- annot_grid[match(g2p_gene_order, annot_grid$Gene),] %>% drop_na(Gene) %>% `rownames<-`(.[,1]) %>% select(-Gene)
-    # annot_grid[annot_grid == "sensitivity"] <- "O"
-    }
-  if(crispr == FALSE) {
+  }
+  if(col_title != "CRISPR") {
     annot_grid <- dcast(cor_res, Gene ~ Drug, value.var = "Direction_Heatmap", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
@@
 
+crispr_cn_cor <- unfactorize(filter(all_cn_cor, Dataset == "CRISPR" & Gene %in% unique(g2p_amp$Gene)))
+crispr_cn_ht <- MakeCorrHeatmap(cor_res = crispr_cn_cor, row_names = TRUE, col_title = "CRISPR", color_range = c(-0.3, 0, 0.1), radius = 0.1, legend_title = "CRISPR Spearman correlation", metric = "CN")
+png(filename = "./plots/manuscript/gdsc_cn_heatmap.png", width = 5, height = 3, units = "in", res = 500)
+draw(gdsc_cn_ht, heatmap_legend_side = "top")
+dev.off()
+
 ccle_cn_ht2 <- MakeCorrHeatmap(cor_res = ccle_cn_cor, row_names = TRUE, col_title = "CCLE", color_range = c(-0.25, 0, 0.25), radius = 0.025, legend_title = "Copy num.

### 2019-11-18 19Q2.Rmd
make CCLE/CTRP/GDSC/CRISPR mut/prot/fus/ge/cn heatmaps, indiv and all

@@
 
+```{r g2p_count_summ}
+g2p_dg_counts <- g2p %>% count(Drug, Gene) %>% filter(!is.na(Drug), !is.na(Gene))
+g2p_dg_counts <- dcast(g2p_dg_counts, Drug ~ Gene, value.var = "n", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Drug)
+g2p_dg_counts <- g2p_dg_counts[order(rowSums(-g2p_dg_counts)), order(colSums(-g2p_dg_counts))]
+# g2p_dg_counts[g2p_dg_counts == 0] <- NA
+
+g2p_gene_order <- colnames(g2p_dg_counts)
+g2p_drug_order <- rownames(g2p_dg_counts)
+```
+
 ## Omics
@@
 ge_melt <- readRDS("./data_munging/19Q2/ge_melt_19Q2.rds")
-```
-
-```{r}
-test <- filter(maf_changes_df, Gene_Protein_Change %in% unique(g2p_mut$Gene_Protein_Change))
 ```
@@
 
-crispr <- MergeOmicsG2P(database = "CRISPR", dataframe = crispr_all, maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./data_munging/19Q2/crispr_data_19Q2.rds")
+crispr_allgenes <- MergeOmicsG2P(database = "CRISPR", dataframe = crispr_all, maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = colnames(crispr_all)[2:length(colnames(crispr_all))], outfile = "./../htscreens_giant_files/crispr_data_19Q2_allgenes.rds")
+
+# crispr <- MergeOmicsG2P(database = "CRISPR", dataframe = crispr_all, maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./data_munging/19Q2/crispr_data_19Q2.rds")
 # write.csv.gz(crispr %>% drop_na(Score), "./../htscreens_giant_files/crispr_data_19Q2.csv.gz")
@@
 ```{r merge_crispr_fus, eval=FALSE}
+crispr_allgenes <- readRDS("./../htscreens_giant_files/crispr_data_19Q2_allgenes.rds")
+fusions_filt <- unfactorize(unique(filter(fusions, FusionPair %in% unique(as.character(g2p_fus$FusionPair)))) %>% select(-c("Cell_line", "disease")))
+crispr_fus_grid <- unfactorize(expand.grid("DepMap_ID" = unique(crispr_allgenes$DepMap_ID), "FusionPair" = unique(fusions_filt$FusionPair)))
+crispr_fus <- merge(merge(crispr_allgenes, crispr_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "FusionPair"), all.x = TRUE)
+crispr_fus$Fusion_Status <- ifelse(!is.na(crispr_fus$LeftGene), "Yes", "No")
+crispr_fus$Drug_FusionPair <- with(crispr_fus, ifelse(is.na(Drug) | is.na(FusionPair), NA, paste0(Drug, "_", FusionPair)))
+crispr_fus$Drug_Fusion_Lineage <- with(crispr_fus, ifelse(is.na(Drug) | is.na(FusionPair) | is.na(disease), NA, paste0(Drug, "_", FusionPair, "_", disease)))
+crispr_fus$G2P_Drug_FusionPair <- "No"
+crispr_fus$G2P_Fusion <- ifelse(crispr_fus$FusionPair %in% unique(as.character(g2p_fus$FusionPair)), "Yes", "No")
+crispr_fus$G2P_Drug_Fusion_Lineage <- "No"
+crispr_fus$Database <- "CRISPR"
+crispr_fus <- crispr_fus %>% drop_na(Score)
+saveRDS(crispr_fus, "./../htscreens_giant_files/crispr_fusions_allgenes.rds", compress = "xz")
+
 fusions_filt <- unfactorize(unique(filter(fusions, FusionPair %in% unique(as.character(g2p_fus$FusionPair)))) %>% select(-c("Cell_line", "disease")))
@@
 
-saveRDS(crispr_prot, "./../htscreens_giant_files/crispr_protein_changes.rds", compress = "xz")
+saveRDS(crispr_prot, "./../htscreens_giant_files/crispr_protein_changes_allgenes.rds", compress = "xz")
 ```
@@
 crispr_prot <- readRDS("./../htscreens_giant_files/crispr_protein_changes.rds")
+```
+
+```{r, eval = FALSE}
+crispr_allgenes <- readRDS("./../htscreens_giant_files/crispr_data_19Q2_allgenes.rds")
+crispr_fus_all <- readRDS("./../htscreens_giant_files/crispr_fusions_allgenes.rds")
+crispr_prot <- readRDS("./../htscreens_giant_files/crispr_protein_changes_allgenes.rds")
 ```
@@
 ## G2P summary heatmap
-
-```{r g2p_gount_summ}
-g2p_dg_counts <- g2p %>% count(Drug, Gene) %>% filter(!is.na(Drug), !is.na(Gene))
-g2p_dg_counts <- dcast(g2p_dg_counts, Drug ~ Gene, value.var = "n", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Drug)
-g2p_dg_counts <- g2p_dg_counts[order(rowSums(-g2p_dg_counts)), order(colSums(-g2p_dg_counts))]
-# g2p_dg_counts[g2p_dg_counts == 0] <- NA
-
-g2p_gene_order <- colnames(g2p_dg_counts)
-g2p_drug_order <- rownames(g2p_dg_counts)
-```
 
@@
 ```{r wilcoxon_heatmap_function}
-MakeWilcoxonHeatmap <- function(signif_df, feature, row_names, col_title, color, legend_title, legend_breaks, row_title_txt, na_color) {
+MakeWilcoxonHeatmap <- function(signif_df, feature, row_names, col_title, color, legend_title, legend_breaks, row_title_txt, na_color, radius) {
   if(missing(na_color)) {
@@
                 cell_fun = function(j, i, x, y, width, height, fill) {
-                  if(color == "darkgreen") {
-                    if(!is.na(str_match(string = tolower(feature), pattern = "fus"))) { radius <- height*0.16 }
-                    if(!is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*0.3 }
-                    else { radius <- width*0.17 }
-                  }
-                  if(color == "steelblue4") {
-                    if(!is.na(str_match(string = tolower(feature), pattern = "fus"))) { radius <- height*0.5 }
-                    if(!is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*0.16 }
-                    else { radius <- width*0.18 }
-                  }
-                  if(color == "turquoise4") {
-                    if(!is.na(str_match(string = tolower(feature), pattern = "fus|prot"))) { radius <- height*0.16 }
-                    else { radius <- width*0.18 }
-                  }
-                  if(color == "darkorchid4") {
-                    if(is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*3.3 }
-                    if(!is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*2 }
-                  }
-
+                  # if(color == "darkgreen") {
+                  #   if(!is.na(str_match(string = tolower(feature), pattern = "fus"))) { radius <- height*0.16 }
+                  #   if(!is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*0.3 }
+                  #   else { radius <- width*0.17 }
+                  # }
+                  # if(color == "steelblue4") {
+                  #   if(!is.na(str_match(string = tolower(feature), pattern = "fus"))) { radius <- height*0.5 }
+                  #   if(!is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*0.16 }
+                  #   else { radius <- width*0.18 }
+                  # }
+                  # if(color == "turquoise4") {
+                  #   if(!is.na(str_match(string = tolower(feature), pattern = "fus|prot"))) { radius <- height*0.16 }
+                  #   else { radius <- width*0.18 }
+                  # }
+                  # if(color == "darkorchid4") {
+                  #   if(is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*3.3 }
+                  #   if(!is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*2 }
+                  # }
+                  # 
                   grid.text(signif_grid_annot1[i, j], x = x + width*0.25, y = y + height*0.065, gp = gpar(fontsize = 17))
@@
                   }
-                })
+                }
+                )
 
@@
 }
-
-# ht_ctrp <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "-log10(p-value)", legend_breaks = seq(0, 10, by = 2), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Fusion Pairs")
-# png(filename = "./plots/manuscript/ctrp_fus_heatmap.png", width = 13, height = 3, units = "in", res = 500)
-# draw(ht_ctrp, heatmap_legend_side = "top")
-# dev.off()
-# 
-# ht_ctrp <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot_4plot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Gene:Protein Change")
-# png(filename = "./plots/manuscript/ctrp_prot_heatmap.png", width = 9.5, height = 5.5, units = "in", res = 500)
-# draw(ht_ctrp, heatmap_legend_side = "top")
-# dev.off()
 ```
@@
 ```{r mut_heatmaps, eval=FALSE, fig.height=10, fig.width=3}
-ht_crispr <- MakeWilcoxonHeatmap(signif_df = filter(crispr_signif_g2p_g, Gene %in% unique(g2p_mut$Gene)), feature = "crispr", legend_title = "-log10(p-value)", legend_breaks = seq(0, 45, by = 9), row_names = TRUE, color = "darkorchid4", col_title = "", row_title_txt = "Genes")
+ht_crispr <- MakeWilcoxonHeatmap(signif_df = filter(crispr_signif_g2p_g, Gene %in% unique(g2p_mut$Gene)), feature = "crispr", legend_title = "-log10(p-value)", legend_breaks = seq(0, 45, by = 9), row_names = TRUE, color = "darkorchid4", col_title = "", row_title_txt = "Genes", radius = 0.05)
 png(filename = "./plots/manuscript/crispr_mut_heatmap.png", width = 3, height = 10, units = "in", res = 500)
@@
 
-ht_ccle <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "-log10(p-value)", legend_breaks = seq(0, 12, by = 3), row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Genes")
+ht_ccle <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "-log10(p-value)", legend_breaks = seq(0, 12, by = 3), row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Genes", radius = 0.04)
 png(filename = "./plots/manuscript/ccle_mut_heatmap.png", width = 3, height = 10, units = "in", res = 500)
@@
 
-ht_ctrp <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "-log10(p-value)", legend_breaks = seq(0, 18, by = 3), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes")
+ht_ctrp <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "-log10(p-value)", legend_breaks = seq(0, 18, by = 3), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.0075)
 png(filename = "./plots/manuscript/ctrp_mut_heatmap.png", width = 9.5, height = 10, units = "in", res = 500)
@@
 
-ht_gdsc <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "-log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Genes")
+ht_gdsc <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "-log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.01)
 png(filename = "./plots/manuscript/gdsc_mut_heatmap.png", width = 5, height = 10, units = "in", res = 500)
@@
 
-ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "CCLE -log10(p-value)          ", legend_breaks = seq(0, 12, by = 3), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Genes")
-ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "CTRP -log10(p-value)          ", legend_breaks = seq(0, 18, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes")
-ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "GDSC -log10(p-value)          ", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes")
-ht_crispr2 <- MakeWilcoxonHeatmap(signif_df = filter(crispr_signif_g2p_g, Gene %in% unique(g2p_mut$Gene)), feature = "crispr", legend_title = "CRISPR -log10(p-value)", legend_breaks = seq(0, 45, by = 9), row_names = FALSE, color = "darkorchid4", col_title = "", row_title_txt = "Genes")
-
-# png(filename = "./plots/manuscript/drug_mut_heatmap.png", width = 13, height = 9.5, units = "in", res = 500)
-# draw(ht_ccle2 + ht_ctrp2 + ht_gdsc2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
-# dev.off()
-
-png(filename = "./plots/manuscript/all_mut_heatmap.png", width = 14, height = 8, units = "in", res = 500)
-draw(ht_ccle2 + ht_ctrp2 + ht_gdsc2 + ht_crispr2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
+ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "CCLE -log10(p-value)          ", legend_breaks = seq(0, 12, by = 3), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Genes", radius = 0.023)
+ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "CTRP -log10(p-value)          ", legend_breaks = seq(0, 18, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.007)
+ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "GDSC -log10(p-value)          ", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes", radius = 0.011)
+ht_crispr2 <- MakeWilcoxonHeatmap(signif_df = filter(crispr_signif_g2p_g, Gene %in% unique(g2p_mut$Gene)), feature = "crispr", legend_title = "CRISPR -log10(p-value)", legend_breaks = seq(0, 45, by = 9), row_names = FALSE, color = "darkorchid4", col_title = "", row_title_txt = "Genes", radius = 0.15)
+
+png(filename = "./plots/manuscript/all_mut_heatmap.png", width = 14, height = 7.5, units = "in", res = 500)
+draw(ht_crispr2 + ht_ccle2 + ht_ctrp2 + ht_gdsc2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
 dev.off()
@@
 ```{r prot_heatmaps, eval=FALSE, fig.height=10, fig.width=3}
-ht_crispr <- MakeWilcoxonHeatmap(signif_df = crispr_signif_prot_4plot, feature = "protein changes CRISPR", legend_title = "-log10(p-value)", legend_breaks = seq(0, 25, by = 5), row_names = TRUE, color = "darkorchid4", col_title = "", row_title_txt = "Gene:Protein Change")
+ht_crispr <- MakeWilcoxonHeatmap(signif_df = crispr_signif_prot_4plot, feature = "protein changes CRISPR", legend_title = "-log10(p-value)", legend_breaks = seq(0, 25, by = 5), row_names = TRUE, color = "darkorchid4", col_title = "", row_title_txt = "Gene:Protein Change", radius = 0.03)
 png(filename = "./plots/manuscript/crispr_prot_heatmap.png", width = 3, height = 5.5, units = "in", res = 500)
@@
 
-ht_ccle <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot_4plot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Gene:Protein Change")
+ht_ccle <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot_4plot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Gene:Protein Change", radius = 0.03)
 png(filename = "./plots/manuscript/ccle_prot_heatmap.png", width = 3, height = 5.5, units = "in", res = 500)
@@
 
-ht_ctrp <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot_4plot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Gene:Protein Change")
+ht_ctrp <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot_4plot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Gene:Protein Change", radius = 0.01)
 png(filename = "./plots/manuscript/ctrp_prot_heatmap.png", width = 9.5, height = 5.5, units = "in", res = 500)
@@
 
-ht_gdsc <- MakeWilcoxonHeatmap(signif_df = gdsc_signif_prot_4plot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 8, by = 2), row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Gene:Protein Change")
+ht_gdsc <- MakeWilcoxonHeatmap(signif_df = gdsc_signif_prot_4plot, feature = "protein changes", legend_title = "-log10(p-value)", legend_breaks = seq(0, 8, by = 2), row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Gene:Protein Change", radius = 0.01)
 png(filename = "./plots/manuscript/gdsc_prot_heatmap.png", width = 5, height = 5.5, units = "in", res = 500)
@@
 
-ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot_4plot, feature = "protein changes", legend_title = "CCLE -log10(p-value)          ", legend_breaks = seq(0, 15, by = 3), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black")
-ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot_4plot, feature = "protein changes", legend_title = "CTRP -log10(p-value)          ", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Gene:Protein Change", na_color = "black")
-ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = gdsc_signif_prot_4plot, feature = "protein changes", legend_title = "GDSC -log10(p-value)          ", legend_breaks = seq(0, 8, by = 2), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black")
-ht_crispr2 <- MakeWilcoxonHeatmap(signif_df = crispr_signif_prot_4plot, feature = "protein changes CRISPR", legend_title = "CRISPR -log10(p-value)", legend_breaks = seq(0, 25, by = 5), row_names = FALSE, color = "darkorchid4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black")
+ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot_4plot, feature = "protein changes", legend_title = "CCLE -log10(p-value)          ", legend_breaks = seq(0, 15, by = 3), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.021)
+ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot_4plot, feature = "protein changes", legend_title = "CTRP -log10(p-value)          ", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.0125)
+ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = gdsc_signif_prot_4plot, feature = "protein changes", legend_title = "GDSC -log10(p-value)          ", legend_breaks = seq(0, 8, by = 2), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.0125)
+ht_crispr2 <- MakeWilcoxonHeatmap(signif_df = crispr_signif_prot_4plot, feature = "protein changes CRISPR", legend_title = "CRISPR -log10(p-value)", legend_breaks = seq(0, 25, by = 5), row_names = FALSE, color = "darkorchid4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.135)
 
 png(filename = "./plots/manuscript/all_prot_heatmap.png", width = 14, height = 5, units = "in", res = 500)
-draw(ht_ccle2 + ht_ctrp2 + ht_gdsc2 + ht_crispr2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
+draw(ht_crispr2 + ht_ccle2 + ht_ctrp2 + ht_gdsc2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
 dev.off()
@@
 **10/25 Need to fix InG2P annots on CTRP data**
-
+**11/15 Need to fix direction annot on CRISPR!**
 ```{r fus_heatmaps, eval=FALSE}
-ht_crispr <- MakeWilcoxonHeatmap(signif_df = filter(crispr_signif_fus, Drug_Gene == "CRISPR_ABL1" & FusionPair %in% c("BCR-ABL1", "ABL1-BCR")), feature = "fusion crispr", legend_title = "-log10(p-value)",  legend_breaks = seq(0, 2, by = 0.5), row_names = TRUE, color = "darkorchid4", col_title = "Drugs", row_title_txt = "Fusion Pairs")
+ht_crispr <- MakeWilcoxonHeatmap(signif_df = filter(crispr_signif_fus, Drug_Gene == "CRISPR_ABL1" & FusionPair %in% c("BCR-ABL1", "ABL1-BCR")), feature = "fusion crispr", legend_title = "-log10(p-value)",  legend_breaks = seq(0, 2, by = 0.5), row_names = TRUE, color = "darkorchid4", col_title = "Drugs", row_title_txt = "Fusion Pairs", radius = 0.5)
 png(filename = "./plots/manuscript/crispr_fus_heatmap.png", width = 3, height = 3, units = "in", res = 500)
@@
 
-ht_ccle <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "-log10(p-value)",  legend_breaks = seq(0, 4, by = 1), row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Fusion Pairs")
+ht_ccle <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "-log10(p-value)",  legend_breaks = seq(0, 4, by = 1), row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Fusion Pairs", radius = 0.01)
 png(filename = "./plots/manuscript/ccle_fus_heatmap.png", width = 5, height = 3, units = "in", res = 500)
@@
 
-ht_ctrp <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "-log10(p-value)", legend_breaks = seq(0, 10, by = 2), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Fusion Pairs")
+ht_ctrp <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "-log10(p-value)", legend_breaks = seq(0, 10, by = 2), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Fusion Pairs", radius = 0.01)
 png(filename = "./plots/manuscript/ctrp_fus_heatmap.png", width = 13, height = 3, units = "in", res = 500)
@@
 
-ht_gdsc <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "-log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Fusion Pairs")
+ht_gdsc <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "-log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Fusion Pairs", radius = 0.01)
 png(filename = "./plots/manuscript/gdsc_fus_heatmap.png", width = 9, height = 3, units = "in", res = 500)
@@
 
-ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "CCLE -log10(p-value)          ", legend_breaks = seq(0, 4, by = 1), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Fusion Pairs")
-ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "CTRP -log10(p-value)          ", legend_breaks = seq(0, 10, by = 2), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Fusion Pairs")
-ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "GDSC -log10(p-value)          ", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Fusion Pairs")
-ht_crispr2 <- MakeWilcoxonHeatmap(signif_df = filter(crispr_signif_fus, Drug_Gene == "CRISPR_ABL1" & FusionPair %in% c("BCR-ABL1", "ABL1-BCR")), feature = "fusion crispr", legend_title = "CRISPR -log10(p-value)",  legend_breaks = seq(0, 2, by = 0.5), row_names = FALSE, color = "darkorchid4", col_title = "", row_title_txt = "Fusion Pairs")
+ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "CCLE -log10(p-value)          ", legend_breaks = seq(0, 4, by = 1), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Fusion Pairs", radius = 0.01)
+ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "CTRP -log10(p-value)          ", legend_breaks = seq(0, 10, by = 2), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Fusion Pairs", radius = 0.01)
+ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "GDSC -log10(p-value)          ", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Fusion Pairs", radius = 0.01)
+ht_crispr2 <- MakeWilcoxonHeatmap(signif_df = filter(crispr_signif_fus, Drug_Gene == "CRISPR_ABL1" & FusionPair %in% c("BCR-ABL1", "ABL1-BCR")), feature = "fusion crispr", legend_title = "CRISPR -log10(p-value)",  legend_breaks = seq(0, 2, by = 0.5), row_names = FALSE, color = "darkorchid4", col_title = "", row_title_txt = "Fusion Pairs", radius = 0.01)
 
@@
 
-**10/28 FIX CRISPR PART OF corr_heatmap_function**
-**11/11 Added CRISPR code to function, but R aborted due to misplaced bracket (fixed but did not run)**
-
 ```{r corr_heatmap_function}
@@
     if(col_title == "CRISPR") {
-      signif_grid <- dcast(cor_res, Gene ~ Drug, value.var = "CN_p", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
-      signif_grid <- signif_grid[g2p_gene_order,]
+      signif_grid <- dcast(cor_res, Gene ~ Drug, value.var = "CN_p", fun.aggregate = mean, fill = 0)
+      signif_grid <- signif_grid[match(g2p_gene_order, signif_grid$Gene),] %>% drop_na(Gene) %>% `rownames<-`(.[,1]) %>% select(-Gene)
       signif_grid[signif_grid >= 0.05] <- ""
@@
 
-      corr_grid <- dcast(cor_res, Gene ~ Drug, value.var = "CN_r", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
-      corr_grid <- corr_grid[g2p_gene_order,]
+      corr_grid <- dcast(cor_res, Gene ~ Drug, value.var = "CN_r", fun.aggregate = mean, fill = 0)
+      corr_grid <- corr_grid[match(g2p_gene_order, corr_grid$Gene),] %>% drop_na(Gene) %>% `rownames<-`(.[,1]) %>% select(-Gene)
+
+      annot_grid <- dcast(cor_res, Gene ~ Drug, value.var = "Direction_Heatmap", fill = 0)
+      annot_grid <- annot_grid[match(g2p_gene_order, annot_grid$Gene),] %>% drop_na(Gene) %>% `rownames<-`(.[,1]) %>% select(-Gene)
     }
@@
       corr_grid <- corr_grid[complete.cases(corr_grid), ]
+
+      annot_grid <- dcast(cor_res, Gene ~ Drug, value.var = "Direction_Heatmap", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
+      annot_grid <- annot_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
+      annot_grid <- annot_grid[complete.cases(annot_grid), ]
     }
@@
     if(col_title == "CRISPR") {
-      signif_grid <- dcast(cor_res, Gene ~ Drug, value.var = "GE_p", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
-      signif_grid <- signif_grid[g2p_gene_order,]
+      signif_grid <- dcast(cor_res, Gene ~ Drug, value.var = "GE_p", fun.aggregate = mean, fill = 0)
+      signif_grid <- signif_grid[match(g2p_gene_order, signif_grid$Gene),] %>% drop_na(Gene) %>% `rownames<-`(.[,1]) %>% select(-Gene)
       signif_grid[signif_grid >= 0.05] <- ""
@@
 
-      corr_grid <- dcast(cor_res, Gene ~ Drug, value.var = "CN_r", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
-      corr_grid <- corr_grid[g2p_gene_order,]
+      corr_grid <- dcast(cor_res, Gene ~ Drug, value.var = "GE_r", fun.aggregate = mean, fill = 0)
+      corr_grid <- corr_grid[match(g2p_gene_order, corr_grid$Gene),] %>% drop_na(Gene) %>% `rownames<-`(.[,1]) %>% select(-Gene)
+
+      annot_grid <- dcast(cor_res, Gene ~ Drug, value.var = "Direction_Heatmap", fill = 0)
+      annot_grid <- annot_grid[match(g2p_gene_order, annot_grid$Gene),] %>% drop_na(Gene) %>% `rownames<-`(.[,1]) %>% select(-Gene)
     }
@@
       corr_grid <- corr_grid[complete.cases(corr_grid), ]
-    }
-  }
-
-  if(col_title == "CRISPR") {
-    annot_grid <- dcast(cor_res, Gene ~ Drug, value.var = "Direction_Heatmap", fill = 0)
-    annot_grid <- annot_grid[match(g2p_gene_order, annot_grid$Gene),] %>% drop_na(Gene) %>% `rownames<-`(.[,1]) %>% select(-Gene)
-  }
-  if(col_title != "CRISPR") {
+
       annot_grid <- dcast(cor_res, Gene ~ Drug, value.var = "Direction_Heatmap", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
@@
       annot_grid <- annot_grid[complete.cases(annot_grid), ]
+    }
   }
@@
                   if(annot_grid[i, j] == "sensitivity") {
-                    grid.circle(x = x - width*0.20, y = y - height*0.20, r = height*0.15, default.units = "npc", gp = gpar(fill = "white", col = "black"))
+                    grid.circle(x = x - width*0.20, y = y - height*0.20, r = radius, default.units = "npc", gp = gpar(fill = "white", col = "black"))
                   }
                   if(annot_grid[i, j] == "resistance") {
-                    grid.circle(x = x - width*0.20, y = y + height*0.20, r = height*0.15, default.units = "npc", gp = gpar(fill = "red", col = "black"))
+                    grid.circle(x = x - width*0.20, y = y + height*0.20, r = radius, default.units = "npc", gp = gpar(fill = "red", col = "black"))
                   }
                   if(annot_grid[i, j] == "both") {
-                    grid.circle(x = x - width*0.20, y = y + height*0.20, r = height*0.15, default.units = "npc", gp = gpar(fill = "red", col = "black"))
-                    grid.circle(x = x - width*0.20, y = y - height*0.20, r = height*0.15, default.units = "npc", gp = gpar(fill = "white", col = "black"))
+                    grid.circle(x = x - width*0.20, y = y + height*0.20, r = radius, default.units = "npc", gp = gpar(fill = "red", col = "black"))
+                    grid.circle(x = x - width*0.20, y = y - height*0.20, r = radius, default.units = "npc", gp = gpar(fill = "white", col = "black"))
                   }
@@
 
-```{r drug_spear_plots, eval=FALSE}
+```{r spear_plots, eval=FALSE}
 # Copy number
+crispr_cn_cor <- unfactorize(filter(all_cn_cor, Dataset == "CRISPR" & Gene %in% unique(g2p_amp$Gene)))
+crispr_cn_ht <- MakeCorrHeatmap(cor_res = crispr_cn_cor, row_names = TRUE, col_title = "CRISPR", color_range = c(-0.25, 0, 0.25), radius = 0.03, legend_title = "CRISPR Spearman correlation", metric = "CN")
+png(filename = "./plots/manuscript/crispr_cn_heatmap.png", width = 3, height = 3, units = "in", res = 500)
+draw(crispr_cn_ht, heatmap_legend_side = "top")
+dev.off()
+
 ccle_cn_cor <- unfactorize(filter(all_cn_cor, Dataset == "CCLE" & Gene %in% unique(g2p_amp$Gene)))
-ccle_cn_ht <- MakeCorrHeatmap(cor_res = ccle_cn_cor, row_names = TRUE, col_title = "CCLE", color_range = c(-0.25, 0, 0.25), radius = 0.1, legend_title = "CCLE Spearman correlation", metric = "CN", crispr =  FALSE)
+ccle_cn_ht <- MakeCorrHeatmap(cor_res = ccle_cn_cor, row_names = TRUE, col_title = "CCLE", color_range = c(-0.25, 0, 0.25), radius = 0.02, legend_title = "CCLE Spearman correlation", metric = "CN")
 png(filename = "./plots/manuscript/ccle_cn_heatmap.png", width = 3, height = 4, units = "in", res = 500)
@@
 ctrp_cn_cor <- unfactorize(filter(all_cn_cor, Dataset == "CTRP" & Gene %in% unique(g2p_amp$Gene)))
-ctrp_cn_ht <- MakeCorrHeatmap(cor_res = ctrp_cn_cor, row_names = TRUE, col_title = "CTRP", color_range = c(-0.25, 0, 0.25), radius = 0.1, legend_title = "CTRP Spearman correlation", metric = "CN", crispr =  FALSE)
+ctrp_cn_ht <- MakeCorrHeatmap(cor_res = ctrp_cn_cor, row_names = TRUE, col_title = "CTRP", color_range = c(-0.25, 0, 0.25), radius = 0.02, legend_title = "CTRP Spearman correlation", metric = "CN")
 png(filename = "./plots/manuscript/ctrp_cn_heatmap.png", width = 8, height = 3, units = "in", res = 500)
@@
 gdsc_cn_cor <- unfactorize(filter(all_cn_cor, Dataset == "GDSC" & Gene %in% unique(g2p_amp$Gene)))
-gdsc_cn_ht <- MakeCorrHeatmap(cor_res = gdsc_cn_cor, row_names = TRUE, col_title = "GDSC", color_range = c(-0.25, 0, 0.25), radius = 0.1, legend_title = "GDSC Spearman correlation", metric = "CN",  crispr = FALSE)
+gdsc_cn_ht <- MakeCorrHeatmap(cor_res = gdsc_cn_cor, row_names = TRUE, col_title = "GDSC", color_range = c(-0.25, 0, 0.25), radius = 0.02, legend_title = "GDSC Spearman correlation", metric = "CN")
 png(filename = "./plots/manuscript/gdsc_cn_heatmap.png", width = 5, height = 3, units = "in", res = 500)
@@
 
-crispr_cn_cor <- unfactorize(filter(all_cn_cor, Dataset == "CRISPR" & Gene %in% unique(g2p_amp$Gene)))
-crispr_cn_ht <- MakeCorrHeatmap(cor_res = crispr_cn_cor, row_names = TRUE, col_title = "CRISPR", color_range = c(-0.3, 0, 0.1), radius = 0.1, legend_title = "CRISPR Spearman correlation", metric = "CN")
-png(filename = "./plots/manuscript/gdsc_cn_heatmap.png", width = 5, height = 3, units = "in", res = 500)
-draw(gdsc_cn_ht, heatmap_legend_side = "top")
-dev.off()
-
-ccle_cn_ht2 <- MakeCorrHeatmap(cor_res = ccle_cn_cor, row_names = TRUE, col_title = "CCLE", color_range = c(-0.25, 0, 0.25), radius = 0.025, legend_title = "Copy num.
-Spearman correlation", metric = "CN", crispr =  FALSE)
-ctrp_cn_ht2 <- MakeCorrHeatmap(cor_res = ctrp_cn_cor, row_names = FALSE, col_title = "CTRP", color_range = c(-0.25, 0, 0.25), radius = 0.025, legend_title = "Copy num.
-Spearman correlation", metric = "CN", crispr =  FALSE)
-gdsc_cn_ht2 <- MakeCorrHeatmap(cor_res = gdsc_cn_cor, row_names = FALSE, col_title = "GDSC", color_range = c(-0.25, 0, 0.25), radius = 0.025, legend_title = "Copy num.
-Spearman correlation", metric = "CN", crispr =  FALSE)
-png(filename = "./plots/manuscript/drug_cn_heatmap.png", width = 13, height = 3.5, units = "in", res = 500)
-draw(ccle_cn_ht2 + ctrp_cn_ht2 + gdsc_cn_ht2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
+crispr_cn_ht2 <- MakeCorrHeatmap(cor_res = crispr_cn_cor, row_names = TRUE, col_title = "CRISPR", color_range = c(-0.25, 0, 0.25), radius = 0.15, legend_title = "Copy num.
+Spearman correlation", metric = "CN")
+ccle_cn_ht2 <- MakeCorrHeatmap(cor_res = ccle_cn_cor, row_names = TRUE, col_title = "CCLE", color_range = c(-0.25, 0, 0.25), radius = 0.0215, legend_title = "Copy num.
+Spearman correlation", metric = "CN")
+ctrp_cn_ht2 <- MakeCorrHeatmap(cor_res = ctrp_cn_cor, row_names = FALSE, col_title = "CTRP", color_range = c(-0.25, 0, 0.25), radius = 0.0215, legend_title = "Copy num.
+Spearman correlation", metric = "CN")
+gdsc_cn_ht2 <- MakeCorrHeatmap(cor_res = gdsc_cn_cor, row_names = FALSE, col_title = "GDSC", color_range = c(-0.25, 0, 0.25), radius = 0.0215, legend_title = "Copy num.
+Spearman correlation", metric = "CN")
+png(filename = "./plots/manuscript/all_cn_heatmap.png", width = 13, height = 3.5, units = "in", res = 500)
+draw(crispr_cn_ht2 +ccle_cn_ht2 + ctrp_cn_ht2 + gdsc_cn_ht2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
 dev.off()
@@
 # Gene expression
+
+crispr_ge_cor <- unfactorize(filter(all_ge_cor, Dataset == "CRISPR" & Gene %in% unique(g2p_expr$Gene)))
+crispr_ge_ht <- MakeCorrHeatmap(cor_res = crispr_ge_cor, row_names = TRUE, col_title = "CRISPR", color_range = c(-0.5, 0, 0.5), radius = 0.1, legend_title = "CRISPR Spearman correlation", metric = "GE")
+png(filename = "./plots/manuscript/crispr_ge_heatmap.png", width = 3, height = 3, units = "in", res = 500)
+draw(crispr_ge_ht, heatmap_legend_side = "top")
+dev.off()
+
 ccle_ge_cor <- unfactorize(filter(all_ge_cor, Dataset == "CCLE" & Gene %in% unique(g2p_expr$Gene)))
-ccle_ge_ht <- MakeCorrHeatmap(cor_res = ccle_ge_cor, row_names = TRUE, col_title = "CCLE", color_range = c(-0.5, 0, 0.5), radius = 0.2, legend_title = "CCLE Spearman correlation", metric = "GE", crispr =  FALSE)
+ccle_ge_ht <- MakeCorrHeatmap(cor_res = ccle_ge_cor, row_names = TRUE, col_title = "CCLE", color_range = c(-0.5, 0, 0.5), radius = 0.2, legend_title = "CCLE Spearman correlation", metric = "GE")
 png(filename = "./plots/manuscript/ccle_ge_heatmap.png", width = 3, height = 2.5, units = "in", res = 500)
@@
 ctrp_ge_cor <- unfactorize(filter(all_ge_cor, Dataset == "CTRP" & Gene %in% unique(g2p_expr$Gene)))
-ctrp_ge_ht <- MakeCorrHeatmap(cor_res = ctrp_ge_cor, row_names = TRUE, col_title = "CTRP", color_range = c(-0.5, 0, 0.5), radius = 0.2, legend_title = "CTRP Spearman correlation", metric = "GE", crispr =  FALSE)
+ctrp_ge_ht <- MakeCorrHeatmap(cor_res = ctrp_ge_cor, row_names = TRUE, col_title = "CTRP", color_range = c(-0.5, 0, 0.5), radius = 0.2, legend_title = "CTRP Spearman correlation", metric = "GE")
 png(filename = "./plots/manuscript/ctrp_ge_heatmap.png", width = 8, height = 2.5, units = "in", res = 500)
@@
 gdsc_ge_cor <- unfactorize(filter(all_ge_cor, Dataset == "GDSC" & Gene %in% unique(g2p_expr$Gene)))
-gdsc_ge_ht <- MakeCorrHeatmap(cor_res = gdsc_ge_cor, row_names = TRUE, col_title = "GDSC", color_range = c(-0.5, 0, 0.5), radius = 0.2, legend_title = "GDSC Spearman correlation", metric = "GE", crispr =  FALSE)
+gdsc_ge_ht <- MakeCorrHeatmap(cor_res = gdsc_ge_cor, row_names = TRUE, col_title = "GDSC", color_range = c(-0.5, 0, 0.5), radius = 0.2, legend_title = "GDSC Spearman correlation", metric = "GE")
 png(filename = "./plots/manuscript/gdsc_ge_heatmap.png", width = 5, height = 2.5, units = "in", res = 500)
@@
 
-ccle_ge_ht2 <- MakeCorrHeatmap(cor_res = ccle_ge_cor, row_names = TRUE, col_title = "CCLE", color_range = c(-0.5, 0, 0.5), radius = 0.2, legend_title = "Gene expr.
-Spearman correlation", metric = "GE", crispr =  FALSE)
-ctrp_ge_ht2 <- MakeCorrHeatmap(cor_res = ctrp_ge_cor, row_names = FALSE, col_title = "CTRP", color_range = c(-0.5, 0, 0.5), radius = 0.2, legend_title = "Gene expr.
-Spearman correlation", metric = "GE", crispr =  FALSE)
-gdsc_ge_ht2 <- MakeCorrHeatmap(cor_res = gdsc_ge_cor, row_names = FALSE, col_title = "GDSC", color_range = c(-0.5, 0, 0.5), radius = 0.2, legend_title = "Gene expr.
-Spearman correlation", metric = "GE", crispr =  FALSE)
-png(filename = "./plots/manuscript/drug_ge_heatmap.png", width = 13, height = 3, units = "in", res = 500)
-draw(ccle_ge_ht2 + ctrp_ge_ht2 + gdsc_ge_ht2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
-dev.off()
-```
-
-**10/28 NEED TO MAKE SPEAR CORR PLOTS WITH CRISPR PANEL**
+crispr_ge_ht2 <- MakeCorrHeatmap(cor_res = crispr_ge_cor, row_names = TRUE, col_title = "CRISPR", color_range = c(-0.5, 0, 0.5), radius = 0.155, legend_title = "Gene expr.
+Spearman correlation", metric = "GE")
+ccle_ge_ht2 <- MakeCorrHeatmap(cor_res = ccle_ge_cor, row_names = TRUE, col_title = "CCLE", color_range = c(-0.5, 0, 0.5), radius = 0.035, legend_title = "Gene expr.
+Spearman correlation", metric = "GE")
+ctrp_ge_ht2 <- MakeCorrHeatmap(cor_res = ctrp_ge_cor, row_names = FALSE, col_title = "CTRP", color_range = c(-0.5, 0, 0.5), radius = 0.035, legend_title = "Gene expr.
+Spearman correlation", metric = "GE")
+gdsc_ge_ht2 <- MakeCorrHeatmap(cor_res = gdsc_ge_cor, row_names = FALSE, col_title = "GDSC", color_range = c(-0.5, 0, 0.5), radius = 0.035, legend_title = "Gene expr.
+Spearman correlation", metric = "GE")
+png(filename = "./plots/manuscript/all_ge_heatmap.png", width = 13, height = 2.9, units = "in", res = 500)
+draw(crispr_ge_ht2 + ccle_ge_ht2 + ctrp_ge_ht2 + gdsc_ge_ht2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
+dev.off()
+```
 

### 2019-11-18 19Q2.Rmd
run CRISPR mut Wilcoxon tests (lineage and lineage-agnostic) on all genes assayed, need to evaluate output

@@
 
-# crispr <- MergeOmicsG2P(database = "CRISPR", dataframe = crispr_all, maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./data_munging/19Q2/crispr_data_19Q2.rds")
+crispr <- MergeOmicsG2P(database = "CRISPR", dataframe = crispr_all, maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./data_munging/19Q2/crispr_data_19Q2.rds")
 # write.csv.gz(crispr %>% drop_na(Score), "./../htscreens_giant_files/crispr_data_19Q2.csv.gz")
@@
 crispr_allgenes <- readRDS("./../htscreens_giant_files/crispr_data_19Q2_allgenes.rds")
-crispr_fus_all <- readRDS("./../htscreens_giant_files/crispr_fusions_allgenes.rds")
-crispr_prot <- readRDS("./../htscreens_giant_files/crispr_protein_changes_allgenes.rds")
+crispr_fus_allgenes <- readRDS("./../htscreens_giant_files/crispr_fusions_allgenes.rds")
+crispr_prot_allgenes <- readRDS("./../htscreens_giant_files/crispr_protein_changes_allgenes.rds")
 ```
@@
 ## Mutation status
+
+```{r eval=FALSE}
+crispr_allgenes <- unfactorize(crispr_allgenes)
+crispr_signif_gene <- WilcoxonTestDF(dataframe = crispr_allgenes, grouping = c("Drug", "Gene", "Drug_Gene"), type = "drug_gene", outfile = "./data_munging/rds/crispr_signif_g_allgenes.rds")
+crispr_signif_lineage <- WilcoxonTestDF(dataframe = crispr_allgenes, grouping =  c("Drug", "Gene", "disease", "Drug_Gene_Lin"), type = "drug_gene_lineage", outfile = "./data_munging/rds/crispr_signif_gl_allgenes.rds")
+```
 

### 2019-11-20 19Q2.Rmd

@@
   require(ggpubr)
+
+  # Mutation status
+  if(tolower(type) == "drug_gene") {
+    # Filter out DGs with too few samples in at least one mutation status category
+    # Require at least 3 samples in each category to run the test, else filter out that DG from testing df
+    count_mut_n <- dataframe %>% count(Drug_Gene, Mutation) %>% filter(n >= 3)
+    count_mut_category <- count_mut_n %>% count(Drug_Gene) %>% filter(n == 2)
+    dg_keep <- intersect(count_mut_n$Drug_Gene, count_mut_category$Drug_Gene)
+    dataframe <- filter(dataframe, Drug_Gene %in% dg_keep)
+    dataframe$Drug_Gene <- as.character(dataframe$Drug_Gene)
+    signif <- compare_means(Score ~ Mutation, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
+    signif <- adj_signif(signif, alpha = 0.05)
+    signif <- signif[order(signif$p),]
+    if(is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- ifelse(signif$Drug_Gene %in% g2p_list, "Yes", "No") }
+    if(!is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- "No" }
+  }
+
+  # Mutation status and lineage
   if(tolower(type) == "drug_gene_lineage") {
@@
     # Require at least 3 samples in each category to run the test, else filter out that DGL from testing df
-    if(is.na(str_match(pattern = "crispr", string = outfile))) {
     count_mut_n <- dataframe %>% count(Drug_Gene_Lin, Mutation) %>% filter(n >= 3)
@@
     signif <- signif[order(signif$p),]
-      signif$InG2P <- ifelse(signif$Drug_Gene_Lin %in% g2p_list, "Yes", "No")
-    }
-    if(!is.na(str_match(pattern = "crispr", string = outfile))) {
-      count_mut_n <- dataframe %>% count(Drug_Gene_Lin, Mutation) %>% filter(n >= 3)
-      count_mut_category <- count_mut_n %>% count(Drug_Gene_Lin) %>% filter(n == 2)
-      dgl_keep <- intersect(count_mut_n$Drug_Gene_Lin, count_mut_category$Drug_Gene_Lin)
-      dataframe <- filter(dataframe, Drug_Gene_Lin %in% dgl_keep)
-      dataframe$Drug_Gene_Lin <- as.character(dataframe$Drug_Gene_Lin)
-      signif <- compare_means(Score ~ Mutation, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
+    if(is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- ifelse(signif$Drug_Gene_Lin %in% g2p_list, "Yes", "No") }
+    if(!is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- "No" }
+  }
+
+  # Protein changes
+  if(tolower(type) == "protein_change") {
+    # Filter out Gene:Protein_Changes with too few samples in at least one category
+    # Require at least 3 samples in each category to run the test, else filter out that Gene_Protein_Change from testing df
+    count_n <- dataframe %>% count(Drug_Gene_Protein_Change, Change_Status) %>% filter(n >= 3)
+    count_category <- count_n %>% count(Drug_Gene_Protein_Change) %>% filter(n == 2)
+    keep <- intersect(count_n$Drug_Gene_Protein_Change, count_category$Drug_Gene_Protein_Change)
+    dataframe <- filter(dataframe, Drug_Gene_Protein_Change %in% keep)
+    dataframe$Drug_Gene_Protein_Change <- as.character(dataframe$Drug_Gene_Protein_Change)
+    signif <- compare_means(Score ~ Change_Status, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
     signif <- adj_signif(signif, alpha = 0.05)
     signif <- signif[order(signif$p),]
-      signif$InG2P <- "No"
-    }
-  }
+    if(is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- ifelse(signif$Drug_Gene_Protein_Change %in% g2p_list, "Yes", "No") }
+    if(!is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- "No" }
+  }
+
+  # Protein changes and lineage
+  if(tolower(type) == "protein_change_lineage") {
+    # Filter out Gene:Protein_Changes with too few samples in at least one category
+    # Require at least 3 samples in each category to run the test, else filter out that Drug_Gene_Protein_Change_Lineage from testing df
+    count_n <- dataframe %>% count(Drug_Gene_Protein_Change_Lineage, Change_Status) %>% filter(n >= 3)
+    count_category <- count_n %>% count(Drug_Gene_Protein_Change_Lineage) %>% filter(n == 2)
+    keep <- intersect(count_n$Drug_Gene_Protein_Change_Lineage, count_category$Drug_Gene_Protein_Change_Lineage)
+    dataframe <- filter(dataframe, Drug_Gene_Protein_Change_Lineage %in% keep)
+    dataframe$Drug_Gene_Protein_Change_Lineage <- as.character(dataframe$Drug_Gene_Protein_Change_Lineage)
+    signif <- compare_means(Score ~ Change_Status, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
+    signif <- adj_signif(signif, alpha = 0.05)
+    signif <- signif[order(signif$p),]
+    if(is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- ifelse(signif$Drug_Gene_Protein_Change_Lineage %in% g2p_list, "Yes", "No") }
+    if(!is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- "No" }
+  }
+
+  # Fusions
   if(tolower(type) == "fusion") {
@@
     signif <- signif[order(signif$p),]
-    signif$InG2P <- ifelse(signif$Drug_FusionPair %in% g2p_list, "Yes", "No")
-  }
+    if(is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- ifelse(signif$Drug_FusionPair %in% g2p_list, "Yes", "No")  }
+    if(!is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- "No" }
+  }
+
+  # Fusions and lineage
   if(tolower(type) == "fusion_lineage") {
@@
     signif <- signif[order(signif$p),]
-    signif$InG2P <- ifelse(signif$Drug_Fusion_Lineage %in% g2p_list, "Yes", "No")
-  }
-  if(tolower(type) == "protein_change") {
-    # Filter out Gene:Protein_Changes with too few samples in at least one category
-    # Require at least 3 samples in each category to run the test, else filter out that Gene_Protein_Change from testing df
-    count_n <- dataframe %>% count(Drug_Gene_Protein_Change, Change_Status) %>% filter(n >= 3)
-    count_category <- count_n %>% count(Drug_Gene_Protein_Change) %>% filter(n == 2)
-    keep <- intersect(count_n$Drug_Gene_Protein_Change, count_category$Drug_Gene_Protein_Change)
-    dataframe <- filter(dataframe, Drug_Gene_Protein_Change %in% keep)
-    dataframe$Drug_Gene_Protein_Change <- as.character(dataframe$Drug_Gene_Protein_Change)
-    signif <- compare_means(Score ~ Change_Status, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
-    signif <- adj_signif(signif, alpha = 0.05)
-    signif <- signif[order(signif$p),]
-    signif$InG2P <- ifelse(signif$Drug_Gene_Protein_Change %in% g2p_list, "Yes", "No")
-  }
-  if(tolower(type) == "protein_change_lineage") {
-    # Filter out Gene:Protein_Changes with too few samples in at least one category
-    # Require at least 3 samples in each category to run the test, else filter out that Drug_Gene_Protein_Change_Lineage from testing df
-    count_n <- dataframe %>% count(Drug_Gene_Protein_Change_Lineage, Change_Status) %>% filter(n >= 3)
-    count_category <- count_n %>% count(Drug_Gene_Protein_Change_Lineage) %>% filter(n == 2)
-    keep <- intersect(count_n$Drug_Gene_Protein_Change_Lineage, count_category$Drug_Gene_Protein_Change_Lineage)
-    dataframe <- filter(dataframe, Drug_Gene_Protein_Change_Lineage %in% keep)
-    dataframe$Drug_Gene_Protein_Change_Lineage <- as.character(dataframe$Drug_Gene_Protein_Change_Lineage)
-    signif <- compare_means(Score ~ Change_Status, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
-    signif <- adj_signif(signif, alpha = 0.05)
-    signif <- signif[order(signif$p),]
-    signif$InG2P <- ifelse(signif$Drug_Gene_Protein_Change_Lineage %in% g2p_list, "Yes", "No")
-  }
+    if(is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- ifelse(signif$Drug_Fusion_Lineage %in% g2p_list, "Yes", "No") }
+    if(!is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- "No" }
+  }
+
+  # Direction (old)
   if(tolower(type) == "direction") {
@@
   }
-  if(tolower(type) == "drug_gene") {
-    # Filter out DGs with too few samples in at least one mutation status category
-    # Require at least 3 samples in each category to run the test, else filter out that DG from testing df
-    if(!is.na(str_match(pattern = "crispr", string = outfile))) {
-      count_mut_n <- dataframe %>% count(Drug_Gene, Mutation) %>% filter(n >= 3)
-      count_mut_category <- count_mut_n %>% count(Drug_Gene) %>% filter(n == 2)
-      dg_keep <- intersect(count_mut_n$Drug_Gene, count_mut_category$Drug_Gene)
-      dataframe <- filter(dataframe, Drug_Gene %in% dg_keep)
-      dataframe$Drug_Gene <- as.character(dataframe$Drug_Gene)
-      signif <- compare_means(Score ~ Mutation, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
-      signif <- adj_signif(signif, alpha = 0.05)
-      signif <- signif[order(signif$p),]
-      signif$InG2P <- "No"
-    }
-    if(is.na(str_match(pattern = "crispr", string = outfile))) {
-      count_mut_n <- dataframe %>% count(Drug_Gene, Mutation) %>% filter(n >= 3)
-      count_mut_category <- count_mut_n %>% count(Drug_Gene) %>% filter(n == 2)
-      dg_keep <- intersect(count_mut_n$Drug_Gene, count_mut_category$Drug_Gene)
-      dataframe <- filter(dataframe, Drug_Gene %in% dg_keep)
-      dataframe$Drug_Gene <- as.character(dataframe$Drug_Gene)
-      signif <- compare_means(Score ~ Mutation, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
-      signif <- adj_signif(signif, alpha = 0.05)
-      signif <- signif[order(signif$p),]
-      signif$InG2P <- ifelse(signif$Drug_Gene %in% g2p_list, "Yes", "No")
-    }
-  }
+
   signif$p_log10 <- as.numeric(formatC(-log10(signif$p), digits = 3, format = "f"))
@@
 
-```{r eval=FALSE}
-crispr_allgenes <- unfactorize(crispr_allgenes)
-crispr_signif_gene <- WilcoxonTestDF(dataframe = crispr_allgenes, grouping = c("Drug", "Gene", "Drug_Gene"), type = "drug_gene", outfile = "./data_munging/rds/crispr_signif_g_allgenes.rds")
-crispr_signif_lineage <- WilcoxonTestDF(dataframe = crispr_allgenes, grouping =  c("Drug", "Gene", "disease", "Drug_Gene_Lin"), type = "drug_gene_lineage", outfile = "./data_munging/rds/crispr_signif_gl_allgenes.rds")
-```
-
-```{r mut_wilcoxon_tests, eval=FALSE}
-# CRISPR
-crispr <- unfactorize(crispr)
-crispr_signif_gene <- WilcoxonTestDF(dataframe = crispr, grouping = c("Drug", "Gene", "Drug_Gene"), type = "drug_gene", outfile = "./data_munging/rds/crispr_signif_g2p_g.rds")
-crispr_signif_lineage <- WilcoxonTestDF(dataframe = crispr, grouping =  c("Drug", "Gene", "disease", "Drug_Gene_Lin"), type = "drug_gene_lineage", outfile = "./data_munging/rds/crispr_signif_g2p_gl.rds")
-
+```{r mut_wilcoxon_tests, eval=TRUE}
 # CCLE
@@
 
+## Protein changes
+
+```{r protein_change_data}
+ccle_prot <- filter(prot, Database == "CCLE")
+ccle_prot <- unfactorize(ccle_prot)
+# ccle_prot_count <- ccle_prot %>% count(Gene_Protein_Change, Drug, Change_Status)
+
+ctrp_prot <- filter(prot, Database == "CTRP")
+ctrp_prot <- unfactorize(ctrp_prot)
+# ctrp_prot_count <- ctrp_prot %>% count(Gene_Protein_Change, Drug, Change_Status)
+
+gdsc_prot <- filter(prot, Database == "GDSC")
+gdsc_prot <- unfactorize(gdsc_prot)
+# gdsc_prot_count <- gdsc_prot %>% count(Gene_Protein_Change, Drug, Change_Status)
+```
+
+```{r prot_wilcoxon_tests, eval=TRUE}
+# CCLE
+ccle_prot <- unfactorize(ccle_prot)
+ccle_signif_prot <- WilcoxonTestDF(dataframe = ccle_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change[!is.na(g2p_prot$Drug_Gene_Protein_Change)])), type = "protein_change", outfile = "./data_munging/rds/ccle_signif_protein_changes.rds")
+ccle_signif_prot_lin <- WilcoxonTestDF(dataframe = ccle_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change", "Drug_Gene_Protein_Change_Lineage", "disease"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change_Lineage[!is.na(g2p_prot$Drug_Gene_Protein_Change_Lineage)])), type = "protein_change_lineage", outfile = "./data_munging/rds/ccle_signif_protein_changes_lineage.rds")
+
+# CTRP
+ctrp_prot <- unfactorize(ctrp_prot)
+ctrp_signif_prot <- WilcoxonTestDF(dataframe = ctrp_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change[!is.na(g2p_prot$Drug_Gene_Protein_Change)])), type = "protein_change", outfile = "./data_munging/rds/ctrp_signif_protein_changes.rds")
+ctrp_signif_prot_lin <- WilcoxonTestDF(dataframe = ctrp_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change", "Drug_Gene_Protein_Change_Lineage", "disease"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change_Lineage[!is.na(g2p_prot$Drug_Gene_Protein_Change_Lineage)])), type = "protein_change_lineage", outfile = "./data_munging/rds/ctrp_signif_protein_changes_lineage.rds")
+
+# GDSC
+gdsc_prot <- unfactorize(gdsc_prot)
+gdsc_signif_prot <- WilcoxonTestDF(dataframe = gdsc_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change[!is.na(g2p_prot$Drug_Gene_Protein_Change)])), type = "protein_change", outfile = "./data_munging/rds/gdsc_signif_protein_changes.rds")
+gdsc_signif_prot_lin <- WilcoxonTestDF(dataframe = gdsc_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change", "Drug_Gene_Protein_Change_Lineage", "disease"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change_Lineage[!is.na(g2p_prot$Drug_Gene_Protein_Change_Lineage)])), type = "protein_change_lineage", outfile = "./data_munging/rds/gdsc_signif_protein_changes_lineage.rds")
+```
+
+## Fusions
+
+```{r fusion_data}
+ccle_fus <- filter(fus, Database == "CCLE")
+ccle_fus <- unfactorize(ccle_fus)
+# ccle_fus_summ <- unique(select(ccle_fus, DepMap_ID, FusionPair, Fusion_Status)) %>% count(FusionPair, Fusion_Status)
+
+ctrp_fus <- filter(fus, Database == "CTRP")
+ctrp_fus <- unfactorize(ctrp_fus)
+# ctrp_fus_summ <- unique(select(ctrp_fus, DepMap_ID, FusionPair, Fusion_Status)) %>% count(FusionPair, Fusion_Status)
+
+gdsc_fus <- filter(fus, Drug %in% g2p_drugs & Database == "GDSC")
+gdsc_fus <- unfactorize(gdsc_fus)
+# gdsc_fus_summ <- unique(select(gdsc_fus, DepMap_ID, FusionPair, Fusion_Status)) %>% count(FusionPair, Fusion_Status)
+```
+
+```{r fus_wilcoxon_tests, eval=TRUE}
+ccle_signif_fus <- WilcoxonTestDF(dataframe = ccle_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair"), g2p_list = unique(as.character(g2p_fus$Drug_FusionPair[!is.na(g2p_fus$Drug_FusionPair)])), type = "fusion", outfile = "./data_munging/rds/ccle_signif_fusions.rds")
+ccle_signif_fus_lin <- WilcoxonTestDF(dataframe = ccle_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair", "Drug_Fusion_Lineage"), g2p_list = unique(as.character(g2p_fus$Drug_Fusion_Lineage[!is.na(g2p_fus$Drug_Fusion_Lineage)])), type = "fusion_lineage", outfile = "./data_munging/rds/ccle_signif_fusions_lineage.rds")
+
+ctrp_signif_fus <- WilcoxonTestDF(dataframe = ctrp_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair"), g2p_list = unique(as.character(g2p_fus$Drug_FusionPair[!is.na(g2p_fus$Drug_FusionPair)])), type = "fusion", outfile = "./data_munging/rds/ctrp_signif_fusions.rds")
+ctrp_signif_fus_lin<- WilcoxonTestDF(dataframe = ctrp_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair", "Drug_Fusion_Lineage"), g2p_list = unique(as.character(g2p_fus$Drug_Fusion_Lineage[!is.na(g2p_fus$Drug_Fusion_Lineage)])), type = "fusion_lineage", outfile = "./data_munging/rds/ctrp_signif_fusions_lineage.rds")
+
+gdsc_signif_fus <- WilcoxonTestDF(dataframe = gdsc_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair"), g2p_list = unique(as.character(g2p_fus$Drug_FusionPair[!is.na(g2p_fus$Drug_FusionPair)])), type = "fusion", outfile = "./data_munging/rds/gdsc_signif_fusions.rds")
+gdsc_signif_fus_lin <- WilcoxonTestDF(dataframe = gdsc_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair", "Drug_Fusion_Lineage"), g2p_list = unique(as.character(g2p_fus$Drug_Fusion_Lineage[!is.na(g2p_fus$Drug_Fusion_Lineage)])), type = "fusion_lineage", outfile = "./data_munging/rds/gdsc_signif_fusions_lineage.rds")
+```
+
+## CRISPR
+
+**11/19 RAN ALL OF THESE!**
+```{r, eval = FALSE}
+# Mutation status
+## All genes
+crispr_allgenes <- unfactorize(crispr_allgenes)
+crispr_signif_gene_allgenes <- WilcoxonTestDF(dataframe = crispr_allgenes, grouping = c("Drug", "Gene", "Drug_Gene"), type = "drug_gene", outfile = "./data_munging/rds/crispr_signif_g_allgenes.rds")
+crispr_signif_lineage_allgenes <- WilcoxonTestDF(dataframe = crispr_allgenes, grouping =  c("Drug", "Gene", "disease", "Drug_Gene_Lin"), type = "drug_gene_lineage", outfile = "./data_munging/rds/crispr_signif_gl_allgenes.rds")
+## G2P genes
+crispr <- unfactorize(crispr)
+crispr_signif_gene <- WilcoxonTestDF(dataframe = crispr, grouping = c("Drug", "Gene", "Drug_Gene"), type = "drug_gene", outfile = "./data_munging/rds/crispr_signif_g2p_g.rds")
+crispr_signif_lineage <- WilcoxonTestDF(dataframe = crispr, grouping =  c("Drug", "Gene", "disease", "Drug_Gene_Lin"), type = "drug_gene_lineage", outfile = "./data_munging/rds/crispr_signif_g2p_gl.rds")
+
+# Protein changes
+## CRISPR: All genes
+crispr_prot_allgenes <- unfactorize(crispr_prot_allgenes)
+crispr_signif_prot_allgenes <- WilcoxonTestDF(dataframe = crispr_prot_allgenes, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change"), type = "protein_change", outfile = "./data_munging/rds/crispr_signif_protein_changes_allgenes.rds")
+crispr_signif_prot_lin_allgenes <- WilcoxonTestDF(dataframe = crispr_prot_allgenes, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change", "Drug_Gene_Protein_Change_Lineage", "disease"), type = "protein_change_lineage", outfile = "./data_munging/rds/crispr_signif_protein_changes_lineage_allgenes.rds")
+## CRISPR: G2P genes
+crispr_prot <- unfactorize(crispr_prot)
+crispr_signif_prot <- WilcoxonTestDF(dataframe = crispr_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change"), type = "protein_change", outfile = "./data_munging/rds/crispr_signif_protein_changes.rds")
+crispr_signif_prot_lin <- WilcoxonTestDF(dataframe = crispr_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change", "Drug_Gene_Protein_Change_Lineage", "disease"), type = "protein_change_lineage", outfile = "./data_munging/rds/crispr_signif_protein_changes_lineage.rds")
+
+# Fusions
+## CRISPR: All genes
+crispr_fus_allgenes <- unfactorize(crispr_fus_allgenes)
+crispr_signif_fus_allgenes <- WilcoxonTestDF(dataframe = crispr_fus_allgenes, grouping = c("FusionPair", "Drug", "Drug_FusionPair", "Drug_Gene"), type = "fusion", outfile = "./data_munging/rds/crispr_signif_fusions_allgenes.rds")
+crispr_signif_fus_lin_allgenes <- WilcoxonTestDF(dataframe = crispr_fus_allgenes, grouping = c("Drug_Gene", "FusionPair", "Drug", "Drug_FusionPair", "Drug_Fusion_Lineage"), type = "fusion_lineage", outfile = "./data_munging/rds/crispr_signif_fusions_lineage_allgenes.rds")
+## CRISPR: G2P genes\
+crispr_fus <- unfactorize(crispr_fus)
+crispr_signif_fus <- WilcoxonTestDF(dataframe = crispr_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair", "Drug_Gene"), type = "fusion", outfile = "./data_munging/rds/crispr_signif_fusions.rds")
+crispr_signif_fus_lin <- WilcoxonTestDF(dataframe = crispr_fus, grouping = c("Drug_Gene", "FusionPair", "Drug", "Drug_FusionPair", "Drug_Fusion_Lineage"), type = "fusion_lineage", outfile = "./data_munging/rds/crispr_signif_fusions_lineage.rds")
+```
+
+## Load and munge
+
+```{r crispr_mut}
+g2p_mut_summ_crispr <- g2p_mut %>% count(Gene, Direction_Curated) %>% select(-n)
+g2p_mut_summ_crispr_n <- g2p_mut_summ_crispr %>% count(Gene)
+g2p_mut_summ_crispr <- merge(g2p_mut_summ_crispr, g2p_mut_summ_crispr_n, by = c("Gene"))
+g2p_mut_summ_crispr$Direction_Heatmap <- with(g2p_mut_summ_crispr, ifelse(n == 2, "both", ifelse(n == 1 & Direction_Curated == "resistance", "resistance", "sensitivity")))
+g2p_mut_summ_crispr <- unique(select(g2p_mut_summ_crispr, Gene, Direction_Heatmap))
+
+g2p_mut_summ_lin_crispr <- g2p_mut %>% count(Gene, disease, Direction_Curated) %>% select(-n)
+g2p_mut_summ_lin_crispr_n <- g2p_mut_summ_lin_crispr %>% count(Gene, disease)
+g2p_mut_summ_lin_crispr <- merge(g2p_mut_summ_lin_crispr, g2p_mut_summ_lin_crispr_n, by = c("Gene", "disease"))
+g2p_mut_summ_lin_crispr$Direction_Heatmap <- with(g2p_mut_summ_lin_crispr, ifelse(n == 2, "both", ifelse(n == 1 & Direction_Curated == "resistance", "resistance", "sensitivity")))
+g2p_mut_summ_lin_crispr <- unique(select(g2p_mut_summ_lin_crispr, Gene, disease, Direction_Heatmap))
+
+crispr_signif_g2p_g <- readRDS("./data_munging/rds/crispr_signif_g2p_g.rds")
+crispr_signif_g2p_g <- merge(crispr_signif_g2p_g, g2p_mut_summ_crispr, by = "Gene", all.x = TRUE)
+crispr_signif_lin <- readRDS("./data_munging/rds/crispr_signif_g2p_gl.rds")
+crispr_signif_lin <- merge(crispr_signif_lin, g2p_mut_summ_lin_crispr, by = c("Gene", "disease"), all.x = TRUE)
+
+crispr_signif_allgenes <- readRDS("./data_munging/rds/crispr_signif_g_allgenes.rds")
+crispr_signif_lin_allgenes <- readRDS("./data_munging/rds/crispr_signif_gl_allgenes.rds")
+```
+
 ```{r load_mut_wilcoxon_rds}
@@
 
-g2p_mut_summ_crispr <- g2p_mut %>% count(Gene, Direction_Curated) %>% select(-n)
-g2p_mut_summ_crispr_n <- g2p_mut_summ_crispr %>% count(Gene)
-g2p_mut_summ_crispr <- merge(g2p_mut_summ_crispr, g2p_mut_summ_crispr_n, by = c("Gene"))
-g2p_mut_summ_crispr$Direction_Heatmap <- with(g2p_mut_summ_crispr, ifelse(n == 2, "both", ifelse(n == 1 & Direction_Curated == "resistance", "resistance", "sensitivity")))
-g2p_mut_summ_crispr <- unique(select(g2p_mut_summ_crispr, Gene, Direction_Heatmap))
-
 g2p_mut_summ_lin <- g2p_mut %>% count(Drug, Gene, disease, Direction_Curated) %>% select(-n)
@@
 
-g2p_mut_summ_lin_crispr <- g2p_mut %>% count(Gene, disease, Direction_Curated) %>% select(-n)
-g2p_mut_summ_lin_crispr_n <- g2p_mut_summ_lin_crispr %>% count(Gene, disease)
-g2p_mut_summ_lin_crispr <- merge(g2p_mut_summ_lin_crispr, g2p_mut_summ_lin_crispr_n, by = c("Gene", "disease"))
-g2p_mut_summ_lin_crispr$Direction_Heatmap <- with(g2p_mut_summ_lin_crispr, ifelse(n == 2, "both", ifelse(n == 1 & Direction_Curated == "resistance", "resistance", "sensitivity")))
-g2p_mut_summ_lin_crispr <- unique(select(g2p_mut_summ_lin_crispr, Gene, disease, Direction_Heatmap))
-
-crispr_signif_g2p_g <- readRDS("./data_munging/rds/crispr_signif_g2p_g.rds")
-crispr_signif_g2p_g <- merge(crispr_signif_g2p_g, g2p_mut_summ_crispr, by = "Gene", all.x = TRUE)
-crispr_signif_lin <- readRDS("./data_munging/rds/crispr_signif_g2p_gl.rds")
-crispr_signif_lin <- merge(crispr_signif_lin, g2p_mut_summ_lin_crispr, by = c("Gene", "disease"), all.x = TRUE)
-
 ccle_signif_g2p_dg <- readRDS("./data_munging/rds/ccle_signif_g2p_dg.rds")
@@
 gdsc_signif_dgl <- merge(gdsc_signif_dgl, g2p_mut_summ_lin, by = c("Drug", "Gene", "disease"), all.x = TRUE)
-```
-
-```{r}
+
 ccle_signif_dgl %>% count(InG2P)
@@
 
-### Protein changes
-
-```{r protein_change_data}
-crispr_prot <- unfactorize(crispr_prot)
-
-ccle_prot <- filter(prot, Database == "CCLE")
-ccle_prot <- unfactorize(ccle_prot)
-# ccle_prot_count <- ccle_prot %>% count(Gene_Protein_Change, Drug, Change_Status)
-
-ctrp_prot <- filter(prot, Database == "CTRP")
-ctrp_prot <- unfactorize(ctrp_prot)
-# ctrp_prot_count <- ctrp_prot %>% count(Gene_Protein_Change, Drug, Change_Status)
-
-gdsc_prot <- filter(prot, Database == "GDSC")
-gdsc_prot <- unfactorize(gdsc_prot)
-# gdsc_prot_count <- gdsc_prot %>% count(Gene_Protein_Change, Drug, Change_Status)
-```
-
-```{r prot_wilcoxon_tests, eval=FALSE}
-crispr_prot <- unfactorize(crispr_prot)
-crispr_signif_prot <- WilcoxonTestDF(dataframe = crispr_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change"), g2p_list = unique(as.character(g2p_prot$Gene_Protein_Change[!is.na(g2p_prot$Gene_Protein_Change)])), type = "protein_change", outfile = "./data_munging/rds/crispr_signif_protein_changes.rds")
-crispr_signif_prot_lin <- WilcoxonTestDF(dataframe = crispr_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change", "Drug_Gene_Protein_Change_Lineage", "disease"), g2p_list = unique(as.character(g2p_prot$Gene_Protein_Change_Lineage[!is.na(g2p_prot$Gene_Protein_Change_Lineage)])), type = "protein_change_lineage", outfile = "./data_munging/rds/crispr_signif_protein_changes_lineage.rds")
-
-ccle_prot <- unfactorize(ccle_prot)
-ccle_signif_prot <- WilcoxonTestDF(dataframe = ccle_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change[!is.na(g2p_prot$Drug_Gene_Protein_Change)])), type = "protein_change", outfile = "./data_munging/rds/ccle_signif_protein_changes.rds")
-ccle_signif_prot_lin <- WilcoxonTestDF(dataframe = ccle_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change", "Drug_Gene_Protein_Change_Lineage", "disease"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change_Lineage[!is.na(g2p_prot$Drug_Gene_Protein_Change_Lineage)])), type = "protein_change_lineage", outfile = "./data_munging/rds/ccle_signif_protein_changes_lineage.rds")
-
-ctrp_prot <- unfactorize(ctrp_prot)
-ctrp_signif_prot <- WilcoxonTestDF(dataframe = ctrp_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change[!is.na(g2p_prot$Drug_Gene_Protein_Change)])), type = "protein_change", outfile = "./data_munging/rds/ctrp_signif_protein_changes.rds")
-ctrp_signif_prot_lin <- WilcoxonTestDF(dataframe = ctrp_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change", "Drug_Gene_Protein_Change_Lineage", "disease"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change_Lineage[!is.na(g2p_prot$Drug_Gene_Protein_Change_Lineage)])), type = "protein_change_lineage", outfile = "./data_munging/rds/ctrp_signif_protein_changes_lineage.rds")
-
-gdsc_prot <- unfactorize(gdsc_prot)
-gdsc_signif_prot <- WilcoxonTestDF(dataframe = gdsc_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change[!is.na(g2p_prot$Drug_Gene_Protein_Change)])), type = "protein_change", outfile = "./data_munging/rds/gdsc_signif_protein_changes.rds")
-gdsc_signif_prot_lin <- WilcoxonTestDF(dataframe = gdsc_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change", "Drug_Gene_Protein_Change_Lineage", "disease"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change_Lineage[!is.na(g2p_prot$Drug_Gene_Protein_Change_Lineage)])), type = "protein_change_lineage", outfile = "./data_munging/rds/gdsc_signif_protein_changes_lineage.rds")
-```
-
 ```{r load_prot_wilcoxon_rds, eval=FALSE}
@@
 
-```{r}
+```{r prot_munging}
 crispr_signif_prot_4plot <- readRDS("./data_munging/rds/crispr_signif_protein_changes_4plot.rds")
@@
 gdsc_signif_prot_4plot <- readRDS("./data_munging/rds/gdsc_signif_protein_changes_4plot.rds")
-```
-
-```{r}
+
 all_directions <- readRDS("./data_munging/rds/protein_changes_directions.rds")
@@
 
-## Fusions
-
-```{r fusion_data}
-crispr_fus <- unfactorize(crispr_fus)
-
-ccle_fus <- filter(fus, Database == "CCLE")
-ccle_fus <- unfactorize(ccle_fus)
-# ccle_fus_summ <- unique(select(ccle_fus, DepMap_ID, FusionPair, Fusion_Status)) %>% count(FusionPair, Fusion_Status)
-
-ctrp_fus <- filter(fus, Database == "CTRP")
-ctrp_fus <- unfactorize(ctrp_fus)
-# ctrp_fus_summ <- unique(select(ctrp_fus, DepMap_ID, FusionPair, Fusion_Status)) %>% count(FusionPair, Fusion_Status)
-
-gdsc_fus <- filter(fus, Drug %in% g2p_drugs & Database == "GDSC")
-gdsc_fus <- unfactorize(gdsc_fus)
-# gdsc_fus_summ <- unique(select(gdsc_fus, DepMap_ID, FusionPair, Fusion_Status)) %>% count(FusionPair, Fusion_Status)
-```
-
-```{r fus_wilcoxon_tests, eval=FALSE}
-crispr_signif_fus <- WilcoxonTestDF(dataframe = crispr_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair", "Drug_Gene"), g2p_list = unique(as.character(g2p_fus$Drug_FusionPair[!is.na(g2p_fus$Drug_FusionPair)])), type = "fusion", outfile = "./data_munging/rds/crispr_signif_fusions.rds")
-crispr_signif_fus_lin <- WilcoxonTestDF(dataframe = crispr_fus, grouping = c("Drug_Gene", "FusionPair", "Drug", "Drug_FusionPair", "Drug_Fusion_Lineage"), g2p_list = unique(as.character(g2p_fus$Drug_Fusion_Lineage[!is.na(g2p_fus$Drug_Fusion_Lineage)])), type = "fusion_lineage", outfile = "./data_munging/rds/crispr_signif_fusions_lineage.rds")
-
-ccle_signif_fus <- WilcoxonTestDF(dataframe = ccle_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair"), g2p_list = unique(as.character(g2p_fus$Drug_FusionPair[!is.na(g2p_fus$Drug_FusionPair)])), type = "fusion", outfile = "./data_munging/rds/ccle_signif_fusions.rds")
-ccle_signif_fus_lin <- WilcoxonTestDF(dataframe = ccle_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair", "Drug_Fusion_Lineage"), g2p_list = unique(as.character(g2p_fus$Drug_Fusion_Lineage[!is.na(g2p_fus$Drug_Fusion_Lineage)])), type = "fusion_lineage", outfile = "./data_munging/rds/ccle_signif_fusions_lineage.rds")
-
-ctrp_signif_fus <- WilcoxonTestDF(dataframe = ctrp_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair"), g2p_list = unique(as.character(g2p_fus$Drug_FusionPair[!is.na(g2p_fus$Drug_FusionPair)])), type = "fusion", outfile = "./data_munging/rds/ctrp_signif_fusions.rds")
-ctrp_signif_fus_lin<- WilcoxonTestDF(dataframe = ctrp_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair", "Drug_Fusion_Lineage"), g2p_list = unique(as.character(g2p_fus$Drug_Fusion_Lineage[!is.na(g2p_fus$Drug_Fusion_Lineage)])), type = "fusion_lineage", outfile = "./data_munging/rds/ctrp_signif_fusions_lineage.rds")
-
-gdsc_signif_fus <- WilcoxonTestDF(dataframe = gdsc_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair"), g2p_list = unique(as.character(g2p_fus$Drug_FusionPair[!is.na(g2p_fus$Drug_FusionPair)])), type = "fusion", outfile = "./data_munging/rds/gdsc_signif_fusions.rds")
-gdsc_signif_fus_lin <- WilcoxonTestDF(dataframe = gdsc_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair", "Drug_Fusion_Lineage"), g2p_list = unique(as.character(g2p_fus$Drug_Fusion_Lineage[!is.na(g2p_fus$Drug_Fusion_Lineage)])), type = "fusion_lineage", outfile = "./data_munging/rds/gdsc_signif_fusions_lineage.rds")
-```
-
 ```{r load_fus_wilcoxon_rds}
+crispr_signif_fus_allgenes <- readRDS("./data_munging/rds/crispr_signif_fusions_allgenes.rds")
+crispr_signif_fus_lin_allgenes <- readRDS("./data_munging/rds/crispr_signif_fusions_lineage_allgenes.rds")
 crispr_signif_fus <- readRDS("./data_munging/rds/crispr_signif_fusions.rds")
+crispr_signif_fus_lin <- readRDS("./data_munging/rds/crispr_signif_fusions_lineage.rds")
+
 ccle_signif_fus <- readRDS("./data_munging/rds/ccle_signif_fusions.rds")
@@
 
-crispr_signif_fus_lin <- readRDS("./data_munging/rds/crispr_signif_fusions_lineage.rds")
 ccle_signif_fus_lin <- readRDS("./data_munging/rds/ccle_signif_fusions_lineage.rds")

### 2019-11-20 19Q2.Rmd
add Spearman GE/CN lineage code, did not run

@@
 
-# WILCOXON
+# WILCOXON: Mutations
 
@@
 ## Heatmaps
-
-**10/29 NEED TO FIX CIRCLE ANNOTS ON FUSION/STEELBLUE4 HEATMAP**
 
@@
                 cell_fun = function(j, i, x, y, width, height, fill) {
-                  # if(color == "darkgreen") {
-                  #   if(!is.na(str_match(string = tolower(feature), pattern = "fus"))) { radius <- height*0.16 }
-                  #   if(!is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*0.3 }
-                  #   else { radius <- width*0.17 }
-                  # }
-                  # if(color == "steelblue4") {
-                  #   if(!is.na(str_match(string = tolower(feature), pattern = "fus"))) { radius <- height*0.5 }
-                  #   if(!is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*0.16 }
-                  #   else { radius <- width*0.18 }
-                  # }
-                  # if(color == "turquoise4") {
-                  #   if(!is.na(str_match(string = tolower(feature), pattern = "fus|prot"))) { radius <- height*0.16 }
-                  #   else { radius <- width*0.18 }
-                  # }
-                  # if(color == "darkorchid4") {
-                  #   if(is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*3.3 }
-                  #   if(!is.na(str_match(string = tolower(feature), pattern = "prot"))) { radius <- height*2 }
-                  # }
-                  # 
                   grid.text(signif_grid_annot1[i, j], x = x + width*0.25, y = y + height*0.065, gp = gpar(fontsize = 17))
@@
 
-# SPEARMAN: PanCan
+# SPEARMAN: GE and CN
 
@@
 
-## GE/CN
-
-Spearman correlations for gene expression and copy number:
+```{r}
+MakeDrugscreenSpearmanCorrDF <- function(dataset, df, metric, lineage) {
+  df_filt <- filter(df, Drug %in% g2p_drugs & Gene %in% g2p_genes)
+  df_filt$Gene <- factor(df_filt$Gene, ordered = FALSE)
+  df_filt <- unfactorize(df_filt)
+
+  if(metric == "GE") {
+    if(lineage) {
+      res <- df_filt %>% group_by(Drug, Gene, disease, Drug_Gene_Lin) %>% drop_na(TPM) %>%
+        summarize(GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$estimate,
+                  GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$p.value, 
+                  GE_p_log10 = -log10(GE_p))
+      res$InG2P <- ifelse(res$Drug_Gene_Lin %in% unique(as.character(g2p_expr$Drug_Gene_Lin[!is.na(g2p_expr$Drug_Gene_Lin)])),   "Yes", "No")
+    }
+    if(!lineage) {
+      res <- df_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(TPM) %>%
+        summarize(GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$estimate,
+                  GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$p.value, 
+                  GE_p_log10 = -log10(GE_p))
+      res$InG2P <- ifelse(res$Drug_Gene %in% unique(as.character(g2p_expr$Drug_Gene[!is.na(g2p_expr$Drug_Gene)])),   "Yes", "No")
+    }
+  }
+  if(metric == "CN") {
+    if(lineage) {
+      res <- df_filt %>% group_by(Drug, Gene, disease, Drug_Gene_Lin) %>% drop_na(CN) %>%
+        summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$estimate,
+                  CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$p.value,
+                  CN_p_log10 = -log10(CN_p))
+      res$InG2P <- ifelse(res$Drug_Gene_Lin %in% unique(as.character(g2p_amp$Drug_Gene_Lin[!is.na(g2p_amp$Drug_Gene_Lin)])), "Yes", "No")
+    }
+    if(!lineage) {
+      res <- df_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(CN) %>%
+        summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$estimate,
+                  CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$p.value, 
+                  CN_p_log10 = -log10(GE_p))
+      res$InG2P <- ifelse(res$Drug_Gene %in% unique(as.character(g2p_expr$Drug_Gene[!is.na(g2p_expr$Drug_Gene)])),   "Yes", "No")
+    }
+  }
+  res$Dataset <- dataset
+  return(res)
+}
+```
+
+## Lineage-agnostic
+
 ```{r spear_calc, warning=FALSE, eval=FALSE}
 # CRISPR
-crispr_spear_cn <- crispr %>% group_by(Gene) %>% drop_na(CN) %>%
+crispr_spear_cn <- crispr %>% group_by(Gene, disease) %>% drop_na(CN) %>%
   summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate,
@@
 crispr_spear_cn <- add_column(crispr_spear_cn, Drug_Gene = Drug_Gene, .before = "Drug")
-saveRDS(crispr_spear_cn, "./data_munging/rds/crispr_cn_cor.rds")
-
-crispr_spear_ge <- crispr %>% group_by(Gene) %>% drop_na(TPM) %>%
+crispr_spear_cn <- add_column(crispr_spear_cn, Drug_Gene_Lin = paste0(Drug_Gene, "_", disease), .before = "Drug")
+saveRDS(crispr_spear_cn, "./data_munging/rds/crispr_cn_cor_lineage.rds")
+
+crispr_spear_ge <- crispr %>% group_by(Gene, disease) %>% drop_na(TPM) %>%
   summarize(GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate,
@@
 crispr_spear_ge <- add_column(crispr_spear_ge, Drug_Gene = Drug_Gene, .before = "Drug")
-saveRDS(crispr_spear_ge, "./data_munging/rds/crispr_ge_cor.rds")
-
-# CCLE
-ccle_filt <- filter(ccle, Drug %in% g2p_drugs & Gene %in% g2p_genes)
-ccle_filt$Gene <- factor(ccle_filt$Gene, ordered = FALSE)
-ccle_filt <- unfactorize(ccle_filt)
-ccle_ge_res <- ccle_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(TPM) %>%
-  summarize(GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$estimate,
-            GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$p.value, 
-            GE_p_log10 = -log10(GE_p))
-ccle_ge_res$InG2P <- ifelse(ccle_ge_res$Drug_Gene %in% unique(as.character(g2p_expr$Drug_Gene[!is.na(g2p_expr$Drug_Gene)])), "Yes", "No")
-ccle_ge_res$Dataset <- "CCLE"
-
-ccle_cn_res <- ccle_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(CN) %>%
-  summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$estimate,
-            CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$p.value,
-            CN_p_log10 = -log10(CN_p))
-ccle_cn_res$InG2P <- ifelse(ccle_cn_res$Drug_Gene %in% unique(as.character(g2p_amp$Drug_Gene[!is.na(g2p_amp$Drug_Gene)])), "Yes", "No")
-ccle_cn_res$Dataset <- "CCLE"
-
-# CTRP
-ctrp_filt <- filter(ctrp, Drug %in% g2p_drugs & Gene %in% g2p_genes)
-ctrp_filt$Gene <- factor(ctrp_filt$Gene, ordered = FALSE)
-ctrp_filt <- unfactorize(ctrp_filt)
-ctrp_ge_res <- ctrp_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(TPM) %>%
-  summarize(GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$estimate,
-            GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$p.value,
-            GE_p_log10 = -log10(GE_p))
-ctrp_ge_res$InG2P <- ifelse(ctrp_ge_res$Drug_Gene %in% unique(as.character(g2p_expr$Drug_Gene[!is.na(g2p_expr$Drug_Gene)])), "Yes", "No")
-ctrp_ge_res$Dataset <- "CTRP"
-
-ctrp_cn_res <- ctrp_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(CN) %>%
-  summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$estimate,
-            CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$p.value,
-            CN_p_log10 = -log10(CN_p))
-ctrp_cn_res$InG2P <- ifelse(ctrp_cn_res$Drug_Gene %in% unique(as.character(g2p_amp$Drug_Gene[!is.na(g2p_amp$Drug_Gene)])), "Yes", "No")
-ctrp_cn_res$Dataset <- "CTRP"
-
-# GDSC
-gdsc_filt <- filter(gdsc, Drug %in% g2p_drugs & Gene %in% g2p_genes)
-gdsc_filt$Gene <- factor(gdsc_filt$Gene, ordered = FALSE)
-gdsc_filt <- unfactorize(gdsc_filt)
-gdsc_ge_res <- gdsc_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(TPM) %>%
-  summarize(GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$estimate,
-            GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$p.value,
-            GE_p_log10 = -log10(GE_p))
-gdsc_ge_res$InG2P <- ifelse(gdsc_ge_res$Drug_Gene %in% unique(as.character(g2p_expr$Drug_Gene[!is.na(g2p_expr$Drug_Gene)])), "Yes", "No")
-gdsc_ge_res$Dataset <- "GDSC"
-
-gdsc_cn_res <- gdsc_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(CN) %>%
-  summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$estimate,
-            CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$p.value,
-            CN_p_log10 = -log10(CN_p))
-gdsc_cn_res$InG2P <- ifelse(gdsc_cn_res$Drug_Gene %in% unique(as.character(g2p_amp$Drug_Gene[!is.na(g2p_amp$Drug_Gene)])), "Yes", "No")
-gdsc_cn_res$Dataset <- "GDSC"
-
-# All
+crispr_spear_ge <- add_column(crispr_spear_ge, Drug_Gene_Lin = paste0(Drug_Gene, "_", disease), .before = "Drug")
+saveRDS(crispr_spear_ge, "./data_munging/rds/crispr_ge_cor_lineage.rds")
+
+ccle_cn_res <- MakeSpearmanCorrDF(dataset = "CCLE", df = ccle, metric = "CN", lineage = FALSE)
+ctrp_cn_res <- MakeSpearmanCorrDF(dataset = "CTRP", df = ctrp, metric = "CN", lineage = FALSE)
+gdsc_cn_res <- MakeSpearmanCorrDF(dataset = "GDSC", df = gdsc, metric = "CN", lineage = FALSE)
 cn_cor <- rbind(ccle_cn_res, ctrp_cn_res, gdsc_cn_res)
 saveRDS(cn_cor, "./data_munging/rds/drug_cn_cor.rds")
+
+ccle_ge_res <- MakeSpearmanCorrDF(dataset = "CCLE", df = ccle, metric = "GE", lineage = FALSE)
+ctrp_ge_res <- MakeSpearmanCorrDF(dataset = "CTRP", df = ctrp, metric = "GE", lineage = FALSE)
+gdsc_ge_res <- MakeSpearmanCorrDF(dataset = "GDSC", df = gdsc, metric = "GE", lineage = FALSE)
 ge_cor <- rbind(ccle_ge_res, ctrp_ge_res, gdsc_ge_res)
@@
 all_ge_cor <- rbind(ge_cor, crispr_ge_cor)
+```
+
+## Lineage
+
+## Lineage
+
+```{r spear_calc_lin, eval=FALSE}
+# CRISPR
+# crispr_spear_cn <- crispr %>% group_by(Gene) %>% drop_na(CN) %>%
+#   summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate,
+#             CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value,
+#             CN_p_log10 = -log10(CN_p),
+#             InG2P = "No",
+#             Dataset = "CRISPR",
+#             Metric = "Copy Number")
+# crispr_spear_cn <- transform(crispr_spear_cn, Gene = reorder(Gene, CN_r))
+# crispr_spear_cn <- add_column(crispr_spear_cn, Drug = "CRISPR", .before = "Gene")
+# Drug_Gene <- with(crispr_spear_cn, paste0(Drug, "_", Gene))
+# crispr_spear_cn <- add_column(crispr_spear_cn, Drug_Gene = Drug_Gene, .before = "Drug")
+# saveRDS(crispr_spear_cn, "./data_munging/rds/crispr_cn_cor.rds")
+# 
+# crispr_spear_ge <- crispr %>% group_by(Gene) %>% drop_na(TPM) %>%
+#   summarize(GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate,
+#             GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value,
+#             GE_p_log10 = -log10(GE_p),
+#             InG2P = "No",
+#             Dataset = "CRISPR",
+#             Metric = "Gene Expression")
+# crispr_spear_ge <- transform(crispr_spear_ge, Gene = reorder(Gene, GE_r))
+# crispr_spear_ge <- add_column(crispr_spear_ge, Drug = "CRISPR", .before = "Gene")
+# Drug_Gene <- with(crispr_spear_ge, paste0(Drug, "_", Gene))
+# crispr_spear_ge <- add_column(crispr_spear_ge, Drug_Gene = Drug_Gene, .before = "Drug")
+# saveRDS(crispr_spear_ge, "./data_munging/rds/crispr_ge_cor.rds")
+
+ccle_cn_res_lin <- MakeSpearmanCorrDF(dataset = "CCLE", df = ccle, metric = "CN", lineage = TRUE)
+ctrp_cn_res_lin <- MakeSpearmanCorrDF(dataset = "CTRP", df = ctrp, metric = "CN", lineage = TRUE)
+gdsc_cn_res_lin <- MakeSpearmanCorrDF(dataset = "GDSC", df = gdsc, metric = "CN", lineage = TRUE)
+cn_cor_lin <- rbind(ccle_cn_res_lin, ctrp_cn_res_lin, gdsc_cn_res_lin)
+saveRDS(cn_cor_lin, "./data_munging/rds/drug_cn_cor_lineage.rds")
+
+ccle_ge_res_lin <- MakeSpearmanCorrDF(dataset = "CCLE", df = ccle, metric = "GE", lineage = TRUE)
+ctrp_ge_res_lin <- MakeSpearmanCorrDF(dataset = "CTRP", df = ctrp, metric = "GE", lineage = TRUE)
+gdsc_ge_res_lin <- MakeSpearmanCorrDF(dataset = "GDSC", df = gdsc, metric = "GE", lineage = TRUE)
+ge_cor_lin <- rbind(ccle_ge_res_lin, ctrp_ge_res_lin, gdsc_ge_res_lin)
+saveRDS(ge_cor_lin, "./data_munging/rds/drug_ge_cor_lineage.rds")
 ```
@@
 
-# SPEARMAN: Lineages
-
---------------------------------------------------------------------------------
-
-## GE/CN
-
-# OLD
+# OLD CODE
 

### 2019-11-25 19Q2.Rmd
CN/GE Spearman corr fxn, ran corr lineage agnostic and lineage specific

@@
 ```{r}
-MakeDrugscreenSpearmanCorrDF <- function(dataset, df, metric, lineage) {
-  df_filt <- filter(df, Drug %in% g2p_drugs & Gene %in% g2p_genes)
-  df_filt$Gene <- factor(df_filt$Gene, ordered = FALSE)
-  df_filt <- unfactorize(df_filt)
+MakeSpearmanCorrDF <- function(dataset, df, metric, lineage) {
+  df$Gene <- factor(df$Gene, ordered = FALSE)
+  df <- unfactorize(df)
 
@@
     if(lineage) {
-      res <- df_filt %>% group_by(Drug, Gene, disease, Drug_Gene_Lin) %>% drop_na(TPM) %>%
-        summarize(GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$estimate,
-                  GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$p.value, 
+      df_count <- df %>% drop_na(TPM) %>% count(Drug, Gene, disease, Drug_Gene_Lin) %>% filter(n >= 3)
+      df <- filter(df, Drug_Gene_Lin %in% df_count$Drug_Gene_Lin)
+      res <- df %>% group_by(Drug, Gene, disease, Drug_Gene_Lin) %>%
+        summarize(GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs", exact = FALSE)$estimate,
+                  GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs", exact = FALSE)$p.value, 
                   GE_p_log10 = -log10(GE_p))
@@
     if(!lineage) {
-      res <- df_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(TPM) %>%
-        summarize(GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$estimate,
-                  GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "na.or.complete")$p.value, 
+      res <- df %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(TPM) %>%
+        summarize(GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs", exact = FALSE)$estimate,
+                  GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs", exact = FALSE)$p.value, 
                   GE_p_log10 = -log10(GE_p))
@@
     if(lineage) {
-      res <- df_filt %>% group_by(Drug, Gene, disease, Drug_Gene_Lin) %>% drop_na(CN) %>%
-        summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$estimate,
-                  CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$p.value,
+      df_count <- df %>% drop_na(CN) %>% count(Drug, Gene, disease, Drug_Gene_Lin) %>% filter(n >= 3)
+      df <- filter(df, Drug_Gene_Lin %in% df_count$Drug_Gene_Lin)
+      res <- df %>% group_by(Drug, Gene, disease, Drug_Gene_Lin) %>%
+        summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs", exact = FALSE)$estimate,
+                  CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs", exact = FALSE)$p.value,
                   CN_p_log10 = -log10(CN_p))
@@
     if(!lineage) {
-      res <- df_filt %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(CN) %>%
-        summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$estimate,
-                  CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "na.or.complete")$p.value, 
-                  CN_p_log10 = -log10(GE_p))
+      res <- df %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(CN) %>%
+        summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs", exact = FALSE)$estimate,
+                  CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs", exact = FALSE)$p.value, 
+                  CN_p_log10 = -log10(CN_p))
       res$InG2P <- ifelse(res$Drug_Gene %in% unique(as.character(g2p_expr$Drug_Gene[!is.na(g2p_expr$Drug_Gene)])),   "Yes", "No")
@@
   }
+  res$Metric <- metric
   res$Dataset <- dataset
@@
 ```{r spear_calc, warning=FALSE, eval=FALSE}
-# CRISPR
-crispr_spear_cn <- crispr %>% group_by(Gene, disease) %>% drop_na(CN) %>%
-  summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate,
-            CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value,
-            CN_p_log10 = -log10(CN_p),
-            InG2P = "No",
-            Dataset = "CRISPR",
-            Metric = "Copy Number")
-crispr_spear_cn <- transform(crispr_spear_cn, Gene = reorder(Gene, CN_r))
-crispr_spear_cn <- add_column(crispr_spear_cn, Drug = "CRISPR", .before = "Gene")
-Drug_Gene <- with(crispr_spear_cn, paste0(Drug, "_", Gene))
-crispr_spear_cn <- add_column(crispr_spear_cn, Drug_Gene = Drug_Gene, .before = "Drug")
-crispr_spear_cn <- add_column(crispr_spear_cn, Drug_Gene_Lin = paste0(Drug_Gene, "_", disease), .before = "Drug")
-saveRDS(crispr_spear_cn, "./data_munging/rds/crispr_cn_cor_lineage.rds")
-
-crispr_spear_ge <- crispr %>% group_by(Gene, disease) %>% drop_na(TPM) %>%
-  summarize(GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate,
-            GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value,
-            GE_p_log10 = -log10(GE_p),
-            InG2P = "No",
-            Dataset = "CRISPR",
-            Metric = "Gene Expression")
-crispr_spear_ge <- transform(crispr_spear_ge, Gene = reorder(Gene, GE_r))
-crispr_spear_ge <- add_column(crispr_spear_ge, Drug = "CRISPR", .before = "Gene")
-Drug_Gene <- with(crispr_spear_ge, paste0(Drug, "_", Gene))
-crispr_spear_ge <- add_column(crispr_spear_ge, Drug_Gene = Drug_Gene, .before = "Drug")
-crispr_spear_ge <- add_column(crispr_spear_ge, Drug_Gene_Lin = paste0(Drug_Gene, "_", disease), .before = "Drug")
-saveRDS(crispr_spear_ge, "./data_munging/rds/crispr_ge_cor_lineage.rds")
-
+# Ran this chunk on 11/25
+crispr_cn_res <- MakeSpearmanCorrDF(dataset = "CRISPR", df = crispr, metric = "CN", lineage = FALSE)
 ccle_cn_res <- MakeSpearmanCorrDF(dataset = "CCLE", df = ccle, metric = "CN", lineage = FALSE)
@@
 gdsc_cn_res <- MakeSpearmanCorrDF(dataset = "GDSC", df = gdsc, metric = "CN", lineage = FALSE)
-cn_cor <- rbind(ccle_cn_res, ctrp_cn_res, gdsc_cn_res)
-saveRDS(cn_cor, "./data_munging/rds/drug_cn_cor.rds")
-
+cn_cor <- rbind(crispr_spear_cn, ccle_cn_res, ctrp_cn_res, gdsc_cn_res)
+saveRDS(cn_cor, "./data_munging/rds/cn_cor.rds")
+
+crispr_ge_res <- MakeSpearmanCorrDF(dataset = "CRISPR", df = crispr, metric = "GE", lineage = FALSE)
 ccle_ge_res <- MakeSpearmanCorrDF(dataset = "CCLE", df = ccle, metric = "GE", lineage = FALSE)
@@
 gdsc_ge_res <- MakeSpearmanCorrDF(dataset = "GDSC", df = gdsc, metric = "GE", lineage = FALSE)
-ge_cor <- rbind(ccle_ge_res, ctrp_ge_res, gdsc_ge_res)
-saveRDS(ge_cor, "./data_munging/rds/drug_ge_cor.rds")
+ge_cor <- rbind(crispr_ge_res, ccle_ge_res, ctrp_ge_res, gdsc_ge_res)
+saveRDS(ge_cor, "./data_munging/rds/ge_cor.rds")
 ```
@@
 
-## Lineage
-
 ```{r spear_calc_lin, eval=FALSE}
-# CRISPR
-# crispr_spear_cn <- crispr %>% group_by(Gene) %>% drop_na(CN) %>%
-#   summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$estimate,
-#             CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs")$p.value,
-#             CN_p_log10 = -log10(CN_p),
-#             InG2P = "No",
-#             Dataset = "CRISPR",
-#             Metric = "Copy Number")
-# crispr_spear_cn <- transform(crispr_spear_cn, Gene = reorder(Gene, CN_r))
-# crispr_spear_cn <- add_column(crispr_spear_cn, Drug = "CRISPR", .before = "Gene")
-# Drug_Gene <- with(crispr_spear_cn, paste0(Drug, "_", Gene))
-# crispr_spear_cn <- add_column(crispr_spear_cn, Drug_Gene = Drug_Gene, .before = "Drug")
-# saveRDS(crispr_spear_cn, "./data_munging/rds/crispr_cn_cor.rds")
-# 
-# crispr_spear_ge <- crispr %>% group_by(Gene) %>% drop_na(TPM) %>%
-#   summarize(GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$estimate,
-#             GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs")$p.value,
-#             GE_p_log10 = -log10(GE_p),
-#             InG2P = "No",
-#             Dataset = "CRISPR",
-#             Metric = "Gene Expression")
-# crispr_spear_ge <- transform(crispr_spear_ge, Gene = reorder(Gene, GE_r))
-# crispr_spear_ge <- add_column(crispr_spear_ge, Drug = "CRISPR", .before = "Gene")
-# Drug_Gene <- with(crispr_spear_ge, paste0(Drug, "_", Gene))
-# crispr_spear_ge <- add_column(crispr_spear_ge, Drug_Gene = Drug_Gene, .before = "Drug")
-# saveRDS(crispr_spear_ge, "./data_munging/rds/crispr_ge_cor.rds")
-
+crispr_cn_res_lin <- MakeSpearmanCorrDF(dataset = "CRISPR", df = crispr, metric = "CN", lineage = TRUE)
 ccle_cn_res_lin <- MakeSpearmanCorrDF(dataset = "CCLE", df = ccle, metric = "CN", lineage = TRUE)
@@
 gdsc_cn_res_lin <- MakeSpearmanCorrDF(dataset = "GDSC", df = gdsc, metric = "CN", lineage = TRUE)
-cn_cor_lin <- rbind(ccle_cn_res_lin, ctrp_cn_res_lin, gdsc_cn_res_lin)
-saveRDS(cn_cor_lin, "./data_munging/rds/drug_cn_cor_lineage.rds")
-
+cn_cor_lin <- rbind(crispr_cn_res_lin, ccle_cn_res_lin, ctrp_cn_res_lin, gdsc_cn_res_lin) %>% filter(CN_p_log10 == Inf)
+saveRDS(cn_cor_lin, "./data_munging/rds/cn_cor_lineage.rds")
+
+crispr_ge_res <- MakeSpearmanCorrDF(dataset = "CRISPR", df = crispr, metric = "GE", lineage = TRUE)
 ccle_ge_res_lin <- MakeSpearmanCorrDF(dataset = "CCLE", df = ccle, metric = "GE", lineage = TRUE)
@@
 gdsc_ge_res_lin <- MakeSpearmanCorrDF(dataset = "GDSC", df = gdsc, metric = "GE", lineage = TRUE)
-ge_cor_lin <- rbind(ccle_ge_res_lin, ctrp_ge_res_lin, gdsc_ge_res_lin)
-saveRDS(ge_cor_lin, "./data_munging/rds/drug_ge_cor_lineage.rds")
+ge_cor_lin <- rbind(crispr_ge_res, ccle_ge_res_lin, ctrp_ge_res_lin, gdsc_ge_res_lin) %>% filter(GE_p_log10 == Inf)
+saveRDS(ge_cor_lin, "./data_munging/rds/ge_cor_lineage.rds")
 ```

### 2019-12-04 19Q2.Rmd
update CN/GE correlation data and calculation/heatmap functions

@@
 
-## Lineage-agnostic
+## Lineage
 
 ```{r spear_calc, warning=FALSE, eval=FALSE}
-# Ran this chunk on 11/25
+# Ran this chunk on 12/3
 crispr_cn_res <- MakeSpearmanCorrDF(dataset = "CRISPR", df = crispr, metric = "CN", lineage = FALSE)
@@
 gdsc_cn_res <- MakeSpearmanCorrDF(dataset = "GDSC", df = gdsc, metric = "CN", lineage = FALSE)
-cn_cor <- rbind(crispr_spear_cn, ccle_cn_res, ctrp_cn_res, gdsc_cn_res)
-saveRDS(cn_cor, "./data_munging/rds/cn_cor.rds")
+cn_cor <- rbind(crispr_cn_res, ccle_cn_res, ctrp_cn_res, gdsc_cn_res)
+saveRDS(cn_cor, "./data_munging/rds/cn_cor.rds", compress = "xz")
 
@@
 ge_cor <- rbind(crispr_ge_res, ccle_ge_res, ctrp_ge_res, gdsc_ge_res)
-saveRDS(ge_cor, "./data_munging/rds/ge_cor.rds")
+saveRDS(ge_cor, "./data_munging/rds/ge_cor.rds", compress = "xz")
 ```
@@
 ```{r load_spear}
-# Drug screens
-## CN
+# CN
+g2p_amp_crispr_4merge <- unique(select(g2p_amp, Gene, Direction_Curated))
+crispr_amp_summ <- g2p_amp_crispr_4merge %>% count(Gene)
+crispr_amp_summ <- merge(crispr_amp_summ, g2p_amp_crispr_4merge, by = "Gene")
+crispr_amp_summ$Drug_Gene <- paste0("CRISPR_", crispr_amp_summ$Gene)
+crispr_amp_summ$Direction_Heatmap <- with(crispr_amp_summ, ifelse(n == 2, "both", ifelse(n == 1 & Direction_Curated == "resistance", "resistance", "sensitivity")))
+crispr_amp_summ <- unique(select(crispr_amp_summ, Drug_Gene, Direction_Heatmap))
+
 g2p_amp_4merge <- select(g2p_amp, Drug_Gene, Direction_Curated)
@@
 amp_summ <- unique(select(amp_summ, Drug_Gene, Direction_Heatmap))
-cn_cor <- readRDS("./data_munging/rds/drug_cn_cor.rds")
+
+amp_summ <- rbind(amp_summ, crispr_amp_summ)
+cn_cor <- readRDS("./data_munging/rds/cn_cor.rds")
 cn_cor <- merge(cn_cor, amp_summ, by = "Drug_Gene", all.x = TRUE)
-## GE
+
+# GE
+g2p_expr_crispr_4merge <- unique(select(g2p_expr, Gene, Direction_Curated))
+crispr_expr_summ <- g2p_expr_crispr_4merge %>% count(Gene)
+crispr_expr_summ <- merge(crispr_expr_summ, g2p_expr_crispr_4merge, by = "Gene")
+crispr_expr_summ$Drug_Gene <- paste0("CRISPR_", crispr_expr_summ$Gene)
+crispr_expr_summ$Direction_Heatmap <- with(crispr_expr_summ, ifelse(n == 2, "both", ifelse(n == 1 & Direction_Curated == "resistance", "resistance", "sensitivity")))
+crispr_expr_summ <- unique(select(crispr_expr_summ, Drug_Gene, Direction_Heatmap))
+
 g2p_expr_4merge <- select(g2p_expr, Drug_Gene, Direction_Curated)
@@
 expr_summ <- unique(select(expr_summ, Drug_Gene, Direction_Heatmap))
-ge_cor <- readRDS("./data_munging/rds/drug_ge_cor.rds")
+
+expr_summ <- rbind(expr_summ, crispr_expr_summ)
+ge_cor <- readRDS("./data_munging/rds/ge_cor.rds")
 ge_cor <- merge(ge_cor, expr_summ, by = "Drug_Gene", all.x = TRUE)
-
-# CRISPR
-## CN
-g2p_cn_crispr_4merge <- unique(select(g2p_amp, Gene, Direction_Curated))
-crispr_cn_summ <- g2p_cn_crispr_4merge %>% count(Gene)
-crispr_cn_summ <- merge(crispr_cn_summ, g2p_cn_crispr_4merge, by = "Gene")
-crispr_cn_summ$Direction_Heatmap <- with(crispr_cn_summ, ifelse(n == 2, "both", ifelse(n == 1 & Direction_Curated == "resistance", "resistance", "sensitivity")))
-crispr_cn_summ <- unique(select(crispr_cn_summ, Gene, Direction_Heatmap))
-crispr_spear_cn <- readRDS("./data_munging/rds/crispr_cn_cor.rds")
-crispr_cn_cor <- merge(crispr_spear_cn, crispr_cn_summ, by = "Gene", all.x = TRUE)
-crispr_cn_cor$Metric <- NULL
-## GE
-g2p_ge_crispr_4merge <- unique(select(g2p_expr, Gene, Direction_Curated))
-crispr_ge_summ <- g2p_ge_crispr_4merge %>% count(Gene)
-crispr_ge_summ <- merge(crispr_ge_summ, g2p_ge_crispr_4merge, by = "Gene")
-crispr_ge_summ$Direction_Heatmap <- with(crispr_ge_summ, ifelse(n == 2, "both", ifelse(n == 1 & Direction_Curated == "resistance", "resistance", "sensitivity")))
-crispr_ge_summ <- unique(select(crispr_ge_summ, Gene, Direction_Heatmap))
-crispr_spear_ge <- readRDS("./data_munging/rds/crispr_ge_cor.rds")
-crispr_ge_cor <- merge(crispr_spear_ge, crispr_ge_summ, by = "Gene", all.x = TRUE)
-crispr_ge_cor$Drug_Gene <- paste0(crispr_ge_cor$Drug, "_", crispr_ge_cor$Gene)
-crispr_ge_cor$Metric <- NULL
-
-all_cn_cor <- rbind(cn_cor, crispr_cn_cor)
-all_ge_cor <- rbind(ge_cor, crispr_ge_cor)
 ```
@@
 ```{r spear_calc_lin, eval=FALSE}
+# Ran on 12/3
 crispr_cn_res_lin <- MakeSpearmanCorrDF(dataset = "CRISPR", df = crispr, metric = "CN", lineage = TRUE)
@@
 gdsc_cn_res_lin <- MakeSpearmanCorrDF(dataset = "GDSC", df = gdsc, metric = "CN", lineage = TRUE)
-cn_cor_lin <- rbind(crispr_cn_res_lin, ccle_cn_res_lin, ctrp_cn_res_lin, gdsc_cn_res_lin) %>% filter(CN_p_log10 == Inf)
+cn_cor_lin <- rbind(crispr_cn_res_lin, ccle_cn_res_lin, ctrp_cn_res_lin, gdsc_cn_res_lin) %>% filter(CN_p_log10 != Inf)
 saveRDS(cn_cor_lin, "./data_munging/rds/cn_cor_lineage.rds")
@@
 gdsc_ge_res_lin <- MakeSpearmanCorrDF(dataset = "GDSC", df = gdsc, metric = "GE", lineage = TRUE)
-ge_cor_lin <- rbind(crispr_ge_res, ccle_ge_res_lin, ctrp_ge_res_lin, gdsc_ge_res_lin) %>% filter(GE_p_log10 == Inf)
+ge_cor_lin <- rbind(crispr_ge_res, ccle_ge_res_lin, ctrp_ge_res_lin, gdsc_ge_res_lin) %>% filter(GE_p_log10 != Inf)
 saveRDS(ge_cor_lin, "./data_munging/rds/ge_cor_lineage.rds")
@@
   }
+
+  corr_grid <- as.matrix(corr_grid)
 
@@
                                    gp = gpar(fontsize = 11),
-                                   offset = unit(1, "npc"),
+                                   location = unit(1, "npc"),
                                    just = "right"),
@@
 # Copy number
-crispr_cn_cor <- unfactorize(filter(all_cn_cor, Dataset == "CRISPR" & Gene %in% unique(g2p_amp$Gene)))
+crispr_cn_cor <- unfactorize(filter(cn_cor, Dataset == "CRISPR" & Gene %in% unique(g2p_amp$Gene)))
 crispr_cn_ht <- MakeCorrHeatmap(cor_res = crispr_cn_cor, row_names = TRUE, col_title = "CRISPR", color_range = c(-0.25, 0, 0.25), radius = 0.03, legend_title = "CRISPR Spearman correlation", metric = "CN")
@@
 
-ccle_cn_cor <- unfactorize(filter(all_cn_cor, Dataset == "CCLE" & Gene %in% unique(g2p_amp$Gene)))
+ccle_cn_cor <- unfactorize(filter(cn_cor, Dataset == "CCLE" & Gene %in% unique(g2p_amp$Gene)))
 ccle_cn_ht <- MakeCorrHeatmap(cor_res = ccle_cn_cor, row_names = TRUE, col_title = "CCLE", color_range = c(-0.25, 0, 0.25), radius = 0.02, legend_title = "CCLE Spearman correlation", metric = "CN")
@@
 
-ctrp_cn_cor <- unfactorize(filter(all_cn_cor, Dataset == "CTRP" & Gene %in% unique(g2p_amp$Gene)))
+ctrp_cn_cor <- unfactorize(filter(cn_cor, Dataset == "CTRP" & Gene %in% unique(g2p_amp$Gene)))
 ctrp_cn_ht <- MakeCorrHeatmap(cor_res = ctrp_cn_cor, row_names = TRUE, col_title = "CTRP", color_range = c(-0.25, 0, 0.25), radius = 0.02, legend_title = "CTRP Spearman correlation", metric = "CN")
@@
 
-gdsc_cn_cor <- unfactorize(filter(all_cn_cor, Dataset == "GDSC" & Gene %in% unique(g2p_amp$Gene)))
+gdsc_cn_cor <- unfactorize(filter(cn_cor, Dataset == "GDSC" & Gene %in% unique(g2p_amp$Gene)))
 gdsc_cn_ht <- MakeCorrHeatmap(cor_res = gdsc_cn_cor, row_names = TRUE, col_title = "GDSC", color_range = c(-0.25, 0, 0.25), radius = 0.02, legend_title = "GDSC Spearman correlation", metric = "CN")
@@
 # Gene expression
-
-crispr_ge_cor <- unfactorize(filter(all_ge_cor, Dataset == "CRISPR" & Gene %in% unique(g2p_expr$Gene)))
+crispr_ge_cor <- unfactorize(filter(ge_cor, Dataset == "CRISPR" & Gene %in% unique(g2p_expr$Gene)))
 crispr_ge_ht <- MakeCorrHeatmap(cor_res = crispr_ge_cor, row_names = TRUE, col_title = "CRISPR", color_range = c(-0.5, 0, 0.5), radius = 0.1, legend_title = "CRISPR Spearman correlation", metric = "GE")
@@
 
-ccle_ge_cor <- unfactorize(filter(all_ge_cor, Dataset == "CCLE" & Gene %in% unique(g2p_expr$Gene)))
+ccle_ge_cor <- unfactorize(filter(ge_cor, Dataset == "CCLE" & Gene %in% unique(g2p_expr$Gene)))
 ccle_ge_ht <- MakeCorrHeatmap(cor_res = ccle_ge_cor, row_names = TRUE, col_title = "CCLE", color_range = c(-0.5, 0, 0.5), radius = 0.2, legend_title = "CCLE Spearman correlation", metric = "GE")
@@
 
-ctrp_ge_cor <- unfactorize(filter(all_ge_cor, Dataset == "CTRP" & Gene %in% unique(g2p_expr$Gene)))
+ctrp_ge_cor <- unfactorize(filter(ge_cor, Dataset == "CTRP" & Gene %in% unique(g2p_expr$Gene)))
 ctrp_ge_ht <- MakeCorrHeatmap(cor_res = ctrp_ge_cor, row_names = TRUE, col_title = "CTRP", color_range = c(-0.5, 0, 0.5), radius = 0.2, legend_title = "CTRP Spearman correlation", metric = "GE")
@@
 
-gdsc_ge_cor <- unfactorize(filter(all_ge_cor, Dataset == "GDSC" & Gene %in% unique(g2p_expr$Gene)))
+gdsc_ge_cor <- unfactorize(filter(ge_cor, Dataset == "GDSC" & Gene %in% unique(g2p_expr$Gene)))
 gdsc_ge_ht <- MakeCorrHeatmap(cor_res = gdsc_ge_cor, row_names = TRUE, col_title = "GDSC", color_range = c(-0.5, 0, 0.5), radius = 0.2, legend_title = "GDSC Spearman correlation", metric = "GE")

### 2019-12-04 19Q2.Rmd
overhaul manuscript methods, not finished

@@
   for(i in which(sapply(df, class) == "factor")) {
-    df[[i]] = as.character(df[[i]])
+    df[[i]] <- as.character(df[[i]])
   }
@@
 g2p_prot$Drug_Gene_Protein_Change_Lineage <- with(g2p_prot, ifelse(is.na(Drug) | is.na(Gene_Protein_Change) | is.na(disease), NA, paste0(Drug, "_", Gene_Protein_Change, "_", disease)))
-```
-
-```{r g2p_count_summ}
+
+# Counts
 g2p_dg_counts <- g2p %>% count(Drug, Gene) %>% filter(!is.na(Drug), !is.na(Gene))
@@
 g2p_dg_counts <- g2p_dg_counts[order(rowSums(-g2p_dg_counts)), order(colSums(-g2p_dg_counts))]
-# g2p_dg_counts[g2p_dg_counts == 0] <- NA
-
 g2p_gene_order <- colnames(g2p_dg_counts)
@@
 
-Mutation calls (coding region, germline filtered):
+Mutation calls (coding region, germline filtered): **12/4 RUN THIS AND RE-MERGE ALL DATA AND RE-RUN TESTS**
 ```{r mutation_status, eval=FALSE}
@@
 # Select columns for maf_df
-maf <- subset(maf_raw, select = c("Gene", "DepMap_ID"))
+maf_raw_edit <- filter(maf_raw, Variant_Classification != "Silent" & !is.na(Variant_Classification))
+maf <- subset(maf_raw_edit, select = c("Gene", "DepMap_ID"))
 maf$Mutation <- 1
@@
   }
+
+  signif_grid <- as.matrix(signif_grid)
   col_fun <- colorRamp2(c(legend_breaks[1], legend_breaks[length(legend_breaks)]), c("gray97", color))
@@
 
-ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "CCLE -log10(p-value)          ", legend_breaks = seq(0, 4, by = 1), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Fusion Pairs", radius = 0.01)
-ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "CTRP -log10(p-value)          ", legend_breaks = seq(0, 10, by = 2), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Fusion Pairs", radius = 0.01)
-ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "GDSC -log10(p-value)          ", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Fusion Pairs", radius = 0.01)
-ht_crispr2 <- MakeWilcoxonHeatmap(signif_df = filter(crispr_signif_fus, Drug_Gene == "CRISPR_ABL1" & FusionPair %in% c("BCR-ABL1", "ABL1-BCR")), feature = "fusion crispr", legend_title = "CRISPR -log10(p-value)",  legend_breaks = seq(0, 2, by = 0.5), row_names = FALSE, color = "darkorchid4", col_title = "", row_title_txt = "Fusion Pairs", radius = 0.01)
+ht_crispr2 <- MakeWilcoxonHeatmap(signif_df = filter(crispr_signif_fus, Drug_Gene == "CRISPR_ABL1" & FusionPair %in% c("BCR-ABL1", "ABL1-BCR")), feature = "fusion crispr", legend_title = "CRISPR -log10(p-value)          ",  legend_breaks = seq(0, 2, by = 0.5), row_names = TRUE, color = "darkorchid4", col_title = "", row_title_txt = "Fusion Pairs", radius = 0.15)
+ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "CCLE -log10(p-value)          ", legend_breaks = seq(0, 4, by = 1), row_names = FALSE, color = "darkgreen", col_title = "", row_title_txt = "Fusion Pairs", radius = 0.15)
+ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "CTRP -log10(p-value)          ", legend_breaks = seq(0, 10, by = 2), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Fusion Pairs", radius = 0.08)
+ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Fusion Pairs", radius = 0.08)
 
 png(filename = "./plots/manuscript/all_fus_heatmap.png", width = 15, height = 2.4, units = "in", res = 500)
-draw(ht_ccle2 + ht_ctrp2 + ht_gdsc2 + ht_crispr2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
+draw(ht_crispr2 + ht_ccle2 + ht_ctrp2 + ht_gdsc2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
 dev.off()
@@
 ```{r crispr_spear_eda, warning=FALSE}
-crispr_spear_cn_plot <- ggplot(data = filter(crispr_spear_cn, Gene %in% g2p_dg_genes)) +
+crispr_spear_cn <- filter(cn_cor, Dataset == "CRISPR" & Gene %in% g2p_dg_genes)
+crispr_spear_cn$Gene <- with(crispr_spear_cn, reorder(Gene, CN_r, function(x) x))
+crispr_spear_cn_plot <- ggplot(data = crispr_spear_cn) +
   geom_point(aes(x = Gene, y = CN_r, fill = CN_p_log10), pch = 21, size = 5) +
@@
 
-crispr_spear_ge_plot <- ggplot(data = filter(crispr_spear_ge, Gene %in% g2p_dg_genes)) +
+crispr_spear_ge <- filter(ge_cor, Dataset == "CRISPR" & Gene %in% g2p_dg_genes)
+crispr_spear_ge$Gene <- with(crispr_spear_ge, reorder(Gene, GE_r, function(x) x))
+crispr_spear_ge_plot <- ggplot(data = crispr_spear_ge) +
   geom_point(aes(x = Gene, y = GE_r, fill = GE_p_log10), pch = 21, size = 5) +

### 2019-12-04 manuscript.Rmd
overhaul manuscript methods, not finished

@@
 library(kableExtra)
-
+library(reshape2)
 # install.packages("tinytex")
@@
 ```{r g2p-data, echo=FALSE, include=FALSE}
-ccl_converter <- read.delim("./data_munging/cell_line_database_v1_20180911.tsv", row.names = 1, sep = "\t", header = TRUE)
-lineage_converter <- unique(ccl_converter[, c("grouped_general_doid", "group_general_lineage_name")])
-colnames(ccl_converter)[colnames(ccl_converter) == "Broad_ID"] <- "DepMap_ID"
+ccl_meta <- read.delim("./data_munging/19Q2/sample_info_edit_20191008.csv", sep = ",", header = TRUE, row.names = 1)
+ccl_meta <- ccl_meta %>% select(DepMap_ID, Cell_line, disease)
+ccl_unique <- data.frame(disease = unique(ccl_meta$disease))
 
-g2p <- read.delim("./data_munging/g2p_full_level_A_dataset_NEW_DEC_2_2018_withGroupedLineages.csv", sep = "\t", header = TRUE)
-g2p[, 1:2] <- NULL
-g2p <- merge(g2p, lineage_converter, by = "grouped_general_doid", all.x = TRUE)
+g2p <- read.delim("./data_munging/g2p_db_edited_20190718.csv", sep = ",", header = TRUE, row.names = 1)
 
-g2p$Drug <- tolower(g2p$Drug)
-g2p[g2p == -1] <- NA
-g2p$Ref[g2p$Ref == "None"] <- NA
-g2p$Alt[g2p$Alt == "None"] <- NA
-g2p$Drug_Gene <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene), NA, paste0(g2p$Drug, "_", g2p$Gene))
-g2p$Drug_Gene_Lin <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene) | is.na(g2p$group_general_lineage_name), NA, paste0(g2p$Drug, "_", g2p$Gene, "_", g2p$group_general_lineage_name))
-g2p$position <- paste0("g.chr", g2p$Chromosome, ":", g2p$End, g2p$Ref, ">", g2p$Alt)
-g2p$position <- ifelse(grepl("NA", g2p$position), NA, g2p$position)
-g2p_filt <- subset(g2p, grepl("^CID", g2p$DrugID))
-g2p_dgls <-  unique(g2p_filt$Drug_Gene_Lin[!is.na(g2p_filt$Drug_Gene_Lin)])
-g2p_druggenes <- unique(g2p_filt$Drug_Gene[!is.na(g2p_filt$Drug_Gene)])
-g2p_drugs <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[1]))
-g2p_genes <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[2]))
-g2p_lins <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[3]))
+g2p_dgl <-  as.character(unique(g2p$Drug_Gene_Lin[!is.na(g2p$Drug_Gene_Lin)]))
+g2p_dg <- as.character(unique(g2p$Drug_Gene[!is.na(g2p$Drug_Gene)]))
+g2p_drugs <- as.character(unique(g2p$Drug[!is.na(g2p$Drug)]))
+g2p_genes <- as.character(unique(g2p$Gene[!is.na(g2p$Gene)]))
+g2p_dg_genes <- unique(sapply(strsplit(g2p_dgl, "_", fixed = TRUE), function(x) x[2]))
+g2p_lins <- as.character(unique(g2p$group_general_lineage_name[!is.na(g2p$group_general_lineage_name)]))
 
-# Order and genes taken from pink heatmapo from Daniel's analyses
-g2p_genes <- c("EGFR", "KRAS", "ERBB2", "ERBB3", "MET", "ALK", "ROS1", "PDGFRA", "ABL1", "KIT", "PDGFRB", "PDGFB", "BRAF", "G6PD", "RET", "BRCA1", "BRCA2", "UGT1A1", "TSC1", "TSC2", "AKT1", "IDH2", "DPYD", "ESR1", "CYP19A1", "TPMT", "FLT3", "NPM1", "DNMT3A", "PML", "PTCH1", "JAK2", "MYD88", "MGMT")
+g2p$biomarker_type_curated <- ifelse(is.na(g2p$biomarker_type_curated), "None", as.character(g2p$biomarker_type_curated))
+g2p_split <- filter(g2p, !is.na(Drug)) %>% split(g2p$biomarker_type_curated)
+g2p_amp <- g2p_split[[1]]
+g2p_expr <- g2p_split[[2]]
+g2p_fus <- g2p_split[[3]]
+g2p_fus$FusionPair <- sapply(X = g2p_fus$Feature.Names, function(x) strsplit(as.character(x)," ")[[1]][1])
+g2p_fus$FusionPair <- ifelse(g2p_fus$FusionPair == "Fusions", as.character(g2p_fus$Gene), as.character(g2p_fus$FusionPair))
+g2p_fus$FusionPair <- ifelse(g2p_fus$FusionPair == "BCR-ABL", "BCR-ABL1", as.character(g2p_fus$FusionPair))
+g2p_fus <- g2p_fus[grep("-", g2p_fus$FusionPair), ]
+g2p_fus$Drug_FusionPair <- ifelse(is.na(g2p_fus$Drug) | is.na(g2p_fus$FusionPair), NA, paste0(g2p_fus$Drug, "_", g2p_fus$FusionPair))
+g2p_fus$Drug_Fusion_Lineage <- ifelse(is.na(g2p_fus$Drug) | is.na(g2p_fus$FusionPair) | is.na(g2p_fus$disease), NA, paste0(g2p_fus$Drug, "_", g2p_fus$FusionPair, "_", g2p_fus$disease))
+g2p_mut <- g2p_split[[4]] %>% drop_na(Direction_Curated)
+g2p_mut_genes <- unique(sapply(strsplit(as.character(g2p_mut$Drug_Gene)[!is.na(g2p_mut$Drug_Gene)], "_", fixed = TRUE), function(x) x[2]))
 
-g2p_nonCID <- subset(g2p, !grepl("^CID", g2p$DrugID))
+g2p_prot <- unique(filter(g2p, !is.na(Gene_Protein_Change) & !is.na(Drug)) %>% select(disease, Drug, Direction_Curated, Gene, Protein_Change, Gene_Protein_Change))
+g2p_prot$Drug_Gene_Protein_Change <- with(g2p_prot, ifelse(is.na(Drug) | is.na(Gene_Protein_Change), NA, paste0(Drug, "_", Gene_Protein_Change)))
+g2p_prot$Drug_Gene_Protein_Change_Lineage <- with(g2p_prot, ifelse(is.na(Drug) | is.na(Gene_Protein_Change) | is.na(disease), NA, paste0(Drug, "_", Gene_Protein_Change, "_", disease)))
 
-# print("Drug-Gene")
-g2p_druggene_tally <- g2p_filt %>% group_by(Drug_Gene) %>% tally() %>% drop_na()
-nrow(g2p_druggene_tally)
-range(g2p_druggene_tally$n)
-mean(g2p_druggene_tally$n)
-sd(g2p_druggene_tally$n)
-
-# print("Drug")
-g2p_drug_tally <- g2p_filt %>% group_by(Drug) %>% tally() %>% drop_na()
-range(g2p_drug_tally$n)
-mean(g2p_drug_tally$n)
-sd(g2p_drug_tally$n)
-
-# print("Gene")
-g2p_gene_tally <- g2p_filt %>% group_by(Gene) %>% tally() %>% drop_na()
-range(g2p_gene_tally$n)
-mean(g2p_gene_tally$n)
-sd(g2p_gene_tally$n)
-
-# print("Drug-Gene-Lineage")
-g2p_dgl_tally <- g2p_filt %>% group_by(Drug, Gene, Drug_Gene, group_general_lineage_name) %>% tally() %>% drop_na()
-nrow(g2p_dgl_tally)
-length(unique(g2p_dgl_tally$Drug))
-length(unique(g2p_dgl_tally$Gene))
-g2p_lins <- as.character(unique(g2p_dgl_tally$group_general_lineage_name))
-```
-
-```{r load-processed-data, echo=FALSE, include=FALSE}
-# ccl_meta <- read.delim("./data_munging/19Q2/sample_info_edit_20190708.csv", sep = ",", header = TRUE, row.names = 1)
-# maf_df <- readRDS("./data_munging/19Q2/maf_df_19Q2.rds")
-# maf_changes_df <- readRDS("./data_munging/19Q2/maf_changes_df_19Q2.rds")
-# cn_melt <- readRDS("./data_munging/19Q2/cn_melt_19Q2.rds")
-# ge_melt <- readRDS("./data_munging/19Q2/ge_melt_19Q2.rds")
-# fusions <- read.delim("./data_munging/19Q2/CCLE_fusions_edit_20190708.csv.gz", header = TRUE, sep = ",")
-# 
-# ccle <- readRDS("./data_munging/19Q2/ccle_data_19Q2.rds") %>% drop_na(Drug)
-# ctrp <- readRDS("./../htscreens_giant_files/ctrp_data_19Q2.rds") %>% drop_na(Drug)
-# gdsc <- readRDS("./data_munging/19Q2/gdsc_data_19Q2.rds") %>% drop_na(Drug)
-# fus <- readRDS("./data_munging/rds/fusions_merged.rds") %>% drop_na(Drug)
-# fus_summary <- fus %>% count(Database, Drug, FusionPair, Fusion_Status)
-# prot <- readRDS("./data_munging/rds/protein_changes_merged.rds")
-# 
-# crispr <- readRDS("./data_munging/19Q2/crispr_data_19Q2.rds")
-
-# crispr_prot <- readRDS("./data_munging/rds/protein_changes_merged.rds")
+# Counts
+g2p_dg_counts <- g2p %>% count(Drug, Gene) %>% filter(!is.na(Drug), !is.na(Gene))
+g2p_dg_counts <- dcast(g2p_dg_counts, Drug ~ Gene, value.var = "n", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Drug)
+g2p_dg_counts <- g2p_dg_counts[order(rowSums(-g2p_dg_counts)), order(colSums(-g2p_dg_counts))]
+g2p_gene_order <- colnames(g2p_dg_counts)
+g2p_drug_order <- rownames(g2p_dg_counts)
 ```
@@
 To test only these clinically actionable associations, we filtered the G2P dataset for only level-A G2P interpretations, of which there were `r formatC(nrow(g2p), big.mark = ",", big.interval = 3L)` (see Methods).
-All compounds screened within the GDSC, CTRP, and CCLE datasets are considered "small molecules" and are respectively linked to Compound (CID) numbers used for indexing in the PubChem database (https://pubchem.ncbi.nlm.nih.gov/).
-As a result, non-small molecules, which include proteins and biologics (i.e.
-monoclonal antibodies), that had level-A G2P evidence could not be included in our comparisons.
-Thus, G2P interpretations for which the compound did not have a matching CID code were excluded from further analysis as were interpretations that did not have an associated compound, resulting in removal of `r nrow(g2p_nonCID)` interpretations (Table\ \@ref(tab:table-g2p-nonCID)).
-It should be noted that cisplatin, a small molecule, was excluded due to its being indexed with a ChEMBLdb identifier (https://www.ebi.ac.uk/chembl/), which we did not manually re-index to a CID to avoid accidental mischaracterization.
 
@@
 
-![Correlation between putative copy number and AUC.](./plots/manuscript/drug_cn_heatmap.png)
+![Correlation between putative copy number and AUC.](./plots/manuscript/all_cn_heatmap.png)
 
@@
 
-![Correlation between gene expression and AUC.](./plots/manuscript/drug_ge_heatmap.png)
+![Correlation between gene expression and AUC.](./plots/manuscript/all_ge_heatmap.png)
 
@@
 
+## Drug screen dataset retrieval
+**12/4 updated**
+We utilized small molecule screening data from the Cancer Therapeutics Response Portal (CTRP, Broad Institute) [@basu_interactive_2013; @rees_correlating_2016; @seashore-ludlow_harnessing_2015], the Genomics of Drug Sensitivity in Cancer (GDSC, Wellcome Sanger Institute and Massachusetts General Hospital Cancer Center), [@garnett_systematic_2012; @yang_genomics_2012], and the Cancer Cell Line Encyclopedia (CCLE, Broad Institute and Novartis Institutes for Biomedical Research) [@barretina_cancer_2012; @consortium_pharmacogenomic_2015].
+To ensure metric consistency, normalized area under the IC50 curve (AUC) for all three datasets were taken from the Quantitative Analysis of Pharmacogenomics in Cancer (http://tanlab.ucdenver.edu/QAPC/) (QAPC) [@pozdeyev_integrating_2016].
+
+## DepMap data retrieval and processing
+**12/4 updated**
+CRISPR/Cas9 and mutation calls, fusions, gene expression, and copy number data from the CCLE were all retrieved from the Broad Institute’s Cancer Dependency Map (DepMap) Public 19Q2 release via the DepMap data portal (https://depmap.org/portal/download/) [@broad_depmap_depmap_2019-1].
+For cell lines with no CCLE annotation, the DepMap group drew raw copy number and mutation data from whole exome sequencing data produced by the Wellcome Trust Sanger Institute [Catalogue Of Somatic Mutations In Cancer (COSMIC, https://cancer.sanger.ac.uk/cell_lines) [@bamford_cosmic_2004; @forbes_cosmic:_2017]; European Genome-phenome Archive [@lappalainen_european_2015], accession number EGAD00001001039] and processed the data following the CCLE pipelines to ensure consistency.
+
+### CRISPR/Cas9 screen
+
+Gene effect scores were inferred from a CRISPR/Cas9 (clustered regularly interspaced short palindromic repeats/CRISPR-associated 9) screen using the Broad Institute’s Avana knockout library [@doench_optimized_2016].
+The Broad Institute’s data processing and screening methods are available from the figshare record [@broad_depmap_depmap_2019-1] and the original publication of CERES, the algorithm that computes inferred gene dependency scores [@meyers_computational_2017].
+
+### Cell line harmonization
+**12/4 updated**
+In an effort to compare CCLE, CTRP, GDSC and CRISPR results and include lineage specificity, it was necessary to consolidate cell lines screened in each dataset.
+Given that unique identifiers can be used between studies, it was necessary to standardize the identity of each cell line with a common source.
+To achieve this, a freely available cell line database called Cellosaurus (v26.0) [@bairoch_cellosaurus_2018] was downloaded and merged with the Broad Institute’s DepMap cell line data to create a harmonized cancer cell line database containing synonymous identifiers that enabled consolidation of all cell lines used in CCLE, CTRP, GDSC and CRISPR into a common framework.
+Subsequent modifications to this database included the merging of DepMap IDs used in the 19Q2 DepMap data release and harmonization with the consensus cell line names from @pozdeyev_integrating_2016.
+We curated missing synonyms and identifiers, and we manually annotated the granularity of lineage labeling for all cell lines analyzed in this study based on their Human Disease Ontology identity codes (DOIDs, http://disease-ontology.org/) [@schriml_human_2019], resulting in `r length(levels(g2p$disease))` unique lineages.
+
+### Mutation calls
+**12/4 EDIT THIS**
+To preclude variation in genomic feature calls across the datasets, we used identical omics annotations from CCLE for all cell lines screened in the three datasets.
+The CCLE called substitutions using MuTect [@cibulskis_sensitive_2013] and annotated variants using Oncotator [@ramos_oncotator:_2015] and indels using Indelocator (https://software.broadinstitute.org/cancer/cga/indelocator).
+
+We had three different mutation types: binarily encoded mutation status (regardless of quantity of harbored mutations per gene in a given cell line), specific protein changes, and fusion status.
+
+We filtered mutation calls for point mutations, defined as single-nucleotide insertions, deletions, and substitutions, regardless of result, i.e.
+frameshift, missense, or nonsense mutation.
+For this analysis, cell lines harboring non-silent point mutations were considered "mutant" for the gene in question.
+All other mutations and genes without annotation in the Mutation Annotation Format (MAF) file were considered "wildtype." "Mutant" and "wildtype" calls were binarily encoded per-gene/per-cell line, regardless of quantity of harbored mutations per gene in a given cell line.
+
+### Copy number data
+**12/4 EDIT THIS**
+The CCLE generated genomic copy number (CN) data using the Affymetrix Genome-Wide Human SNP Array 6.0 and GenePattern pipeline [@thecancergenomeatlasresearchnetwork2008] and normalized segmented CN log2-ratios for 23,299 genes across 1,098 cell lines using circular binary segmentation [@olshen2004] (dataset: public_18Q4_gene_cn.csv, accessed 15 November 2018).
+
+### Gene expression data
+**12/4 EDIT THIS**
+The CCLE reports gene expression in RPKM (reads per kilobase per million mapped reads) for 54,356 genes across 1,156 cell lines, generated on the GeneChip Human Genome U133 Plus 2.0 Array (dataset: CCLE_DepMap_18q3_RNAseq_RPKM_20180718.gct, accessed 18 July 2018).
+
 ## G2P cancer variants
-
+**12/4 updated**
 Cancer variants with the highest level of evidence (i.e.
-level A) in the Genotype to Phenotype (G2P) database were retrieved from the Variant Interpretation for Cancer Consortium (VICC) portal (https://search.cancervariants.org/#*) [@wagner2018] using a customized JSON-query script.
+level A) in the Genotype to Phenotype (G2P) database were retrieved from the Variant Interpretation for Cancer Consortium (VICC) portal (https://search.cancervariants.org/#*) [@wagner_harmonized_2018] using a customized JSON-query script.
 All JSON queries were passed to the available application program interface (API) where a request was made for all drug-gene associations with level-A evidence via the G2P evidence label, i.e.
-association.evidence_label.
+`association.evidence_label`.
 From manual inspection using G2P’s front-end Kibana interface, it was known that, at the time of the last query, 27 November 2018, there were 1,297 known level-A associations.
@@
 One of the 1,297 level-A entries was irretrievable, yielding a final dataset of 1,296 level-A G2P interpretations, which were stored in a pandas data table and exported in CSV format.
+We split each interpretation by row to isolate drug associations with singular lineages, protein changes, and/or mutation types.
 The VICC’s methods for the harvesting and harmonizing of cancer variants is available in a GitHub repository from Oregon Health & Science University (https://github.com/ohsu-comp-bio/g2p-aggregator).
 
-## DepMap data retrieval and processing
-
-CRISPR/Cas9, CCLE mutation calls, and CCLE copy number data were all retrieved from the Broad Institute’s Cancer Dependency Map (DepMap) Public 18Q4 release via the DepMap data portal (https://depmap.org/portal/download/) [@broaddepmap2018a].
-Gene expression data was retrieved from the DepMap Public 18Q3 release [@broaddepmap2018] from the same data portal.
-For cell lines with no CCLE annotation, the DepMap group drew raw copy number and mutation data from whole exome sequencing data produced by the Wellcome Trust Sanger Institute [Catalogue Of Somatic Mutations In Cancer (COSMIC, https://cancer.sanger.ac.uk/cell_lines) [@bamford2004; @forbes2017]; European Genome-phenome Archive [@lappalainen2015], accession number EGAD00001001039] and processed the data following the CCLE pipelines to ensure consistency.
-
-### CRISPR/Cas9 screen
-
-Gene effect scores for 17,634 genes in 517 cell lines were inferred from a CRISPR/Cas9 (clustered regularly interspaced short palindromic repeats/CRISPR-associated 9) screen using the Broad Institute’s Avana knockout library [@doench2016a].
-The Broad Institute’s data processing and screening methods are available from the figshare record [@broaddepmap2018a] and the original publication of CERES, the algorithm that computes inferred gene dependency scores [@meyers2017].
-The DepMap releases new data quarterly, with the current data set being the 18Q4 release.
-This release has 175 more cell lines than the original data release that was published with CERES (dataset: gene_effect.csv, accessed 15 November 2018).
-
-### Mutation calls
-
-To preclude variation in genomic feature calls across the datasets, we used identical annotations from CCLE for all cell lines screened in the three datasets.
-The CCLE provided mutation annotations in 19,280 genes across 1,596 cell lines (dataset: depmap_18Q4_mutation_calls.csv, accessed 14 November 2018).
-CCLE called substitutions using MuTect [@cibulskis2013] and annotated variants using Oncotator [@ramos2015a] and indels using Indelocator (https://software.broadinstitute.org/cancer/cga/indelocator).
-We filtered mutation calls for point mutations, defined as single-nucleotide insertions, deletions, and substitutions, regardless of result, i.e.
-frameshift, missense, or nonsense mutation.
-For this analysis, cell lines harboring non-silent point mutations were considered “mutant” for the gene in question.
-All other mutations and genes without annotation in the Mutation Annotation Format (MAF) file were considered "wildtype." "Mutant" and "wildtype" calls were binarily encoded per-gene/per-cell line, regardless of quantity of harbored mutations per gene in a given cell line.
-
-### Protein changes
-
-### Fusion status
-
-### Copy number data
-
-The CCLE generated genomic copy number (CN) data using the Affymetrix Genome-Wide Human SNP Array 6.0 and GenePattern pipeline [@thecancergenomeatlasresearchnetwork2008] and normalized segmented CN log2-ratios for 23,299 genes across 1,098 cell lines using circular binary segmentation [@olshen2004] (dataset: public_18Q4_gene_cn.csv, accessed 15 November 2018).
-
-### Gene expression data
-
-The CCLE reports gene expression in RPKM (reads per kilobase per million mapped reads) for 54,356 genes across 1,156 cell lines, generated on the GeneChip Human Genome U133 Plus 2.0 Array (dataset: CCLE_DepMap_18q3_RNAseq_RPKM_20180718.gct, accessed 18 July 2018).
-
-## Drug screen dataset retrieval
-
-**Need to update with Poz info**
-
-The Cancer Therapeutics Response Portal (CTRP) drug screen dataset (v2) [@basu2013; @rees2016; @seashore-ludlow2015] was retrieved from the National Cancer Institute’s Cancer Target Discovery and Development (CTD2) Network’s data portal (https://ocg.cancer.gov/programs/ctd2/data-portal, accessed 6 June 2018).
-The Genomics of Drug Sensitivity in Cancer (GDSC) drug screen dataset [@garnett2012; @yang2012] was retrieved from the data portal at (https://www.cancerrxgene.org/downloads, accessed 19 June 2018).
-The Cancer Cell Line Encyclopedia (CCLE) drug screen dataset [@barretina2012; @consortium2015] was retrieved from the Broad Institute’s data portal (https://portals.broadinstitute.org/ccle, accessed 20 June 2018).
-
-### Cell line harmonization
-
-In an effort to compare CCLE, CTRP, GDSC and CRISPR results and include lineage specificity, it was necessary to consolidate cell lines screened in each dataset.
-Given that unique identifiers can be used between studies, it was necessary to standardize the identity of each cell line with a common source.
-To achieve this, a freely available cell line database called Cellosaurus (v26.0, 14 May 2018) [@bairoch2018] was downloaded and merged with the Broad Institute’s DepMap cell line data (accessed 8 June 2018) to create a harmonized cancer cell line database containing synonymous identifiers that enabled consolidation of all cell lines used in CCLE, CTRP, GDSC and CRISPR into a common framework.
-Subsequent additions to this database include the merging of DepMap IDs used in the 18Q3 and 18Q4 DepMap data releases.
-We curated missing synonyms and identifiers, and we manually annotated the granularity of lineage labeling for all cell lines analyzed in this study based on their Human Disease Ontology identity codes (DOIDs, http://disease-ontology.org/) [@schriml2019], resulting in 27 unique lineages.
-For ease of comparison between datasets, we labeled all cell lines with custom, randomized identifiers.
+All compounds screened within the GDSC, CTRP, and CCLE datasets are considered "small molecules" and are respectively linked to Compound (CID) numbers used for indexing in the PubChem database (https://pubchem.ncbi.nlm.nih.gov/).
+As a result, non-small molecules, which include proteins and biologics (i.e.
+monoclonal antibodies), that had level-A G2P evidence could not be included in our comparisons.
+Thus, G2P interpretations for which the compound did not have a matching CID code were excluded from further analysis as were interpretations that did not have an associated compound.
+It should be noted that cisplatin, a small molecule, was excluded due to its being indexed with a ChEMBLdb identifier (https://www.ebi.ac.uk/chembl/), which we did not manually re-index to a CID to avoid mischaracterization.
 
 ## Computational
-
+**12/4 EDIT THIS**
 ```{r, include=FALSE}
@@
 ### Statistics
-
+**12/4 EDIT THIS**
 Wilcoxon tests were conducted using the `compare_means` function in the ggpubr (`r ggpubr_v`) R package [@kassambara2018].
@@
 
+# Conflicts of interest?
+
+# Grant support?
+
 # References

### 2019-12-11 19Q2.Rmd

@@
 
-Mutation calls (coding region, germline filtered): **12/4 RUN THIS AND RE-MERGE ALL DATA AND RE-RUN TESTS**
+Mutation calls (coding region, germline filtered):
 ```{r mutation_status, eval=FALSE}
@@
 maf_df[is.na(maf_df)] <- 0
-saveRDS(maf_df, "./data_munging/19Q2/maf_df_19Q2.rds", compress = "xz")
+saveRDS(maf_df, "./data_munging/19Q2/maf_df_19Q2_nosilent.rds", compress = "xz")
+# saveRDS(maf_df, "./data_munging/19Q2/maf_df_19Q2.rds", compress = "xz")
 ```
@@
 ```{r load_omics_rds}
-maf_df <- readRDS("./data_munging/19Q2/maf_df_19Q2.rds")
+maf_df <- readRDS("./data_munging/19Q2/maf_df_19Q2_nosilent.rds")
 maf_changes_df <- readRDS("./data_munging/19Q2/maf_changes_df_19Q2.rds")
@@
 
-```{r load_drug_rds, eval=TRUE}
+```{r load_drug_rds}
 # ccle <- readRDS("./data_munging/19Q2/ccle_data_19Q2_all.rds") %>% drop_na(Drug)
@@
 
-```{r, eval = FALSE}
+```{r, eval = TRUE}
 crispr_allgenes <- readRDS("./../htscreens_giant_files/crispr_data_19Q2_allgenes.rds")
@@
 
-```{r mut_wilcoxon_tests, eval=TRUE}
+```{r mut_wilcoxon_tests, eval=FALSE}
 # CCLE
@@
 
-```{r prot_wilcoxon_tests, eval=TRUE}
+```{r prot_wilcoxon_tests, eval=FALSE}
 # CCLE
@@
 
-```{r fus_wilcoxon_tests, eval=TRUE}
+```{r fus_wilcoxon_tests, eval=FALSE}
 ccle_signif_fus <- WilcoxonTestDF(dataframe = ccle_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair"), g2p_list = unique(as.character(g2p_fus$Drug_FusionPair[!is.na(g2p_fus$Drug_FusionPair)])), type = "fusion", outfile = "./data_munging/rds/ccle_signif_fusions.rds")
@@
 
-**11/19 RAN ALL OF THESE!**
+**12/5 RAN ALL OF THESE!**
 ```{r, eval = FALSE}
@@
 
-# ggsave("./plots/manuscript/crispr_gene_mut_plot.png", crispr_gene_mut_plot, width = 12, height = 6, units = "in")
+ggsave("./plots/manuscript/crispr_gene_mut_plot.png", crispr_gene_mut_plot, width = 12, height = 6, units = "in")
 ```
@@
 
-**10/23 MADE PLOTS UP TO HERE**
-
 ### Lineage
-
-**10/23 NEED TO RUN LINEAGE PLOTS**
 

### 2019-12-16 manuscript.Rmd
update references and methods in manuscript

@@
 
-Cancer cell lines are a long-standing model for systematic testing of candidate therapeutics, beginning with the National Cancer Institute 60 (NCI60) assay from the late 1980s [@alley1988; @shoemaker2006; @stinson1992], which has been used to screen over 100,000 compounds as of 2010 [@holbeck2010].
-Since then, numerous small-molecule and gene essentiality screens of various scales and study aims have been conducted in cell lines, from grouping drugs by therapeutic target similarity [@greshock2010] to screening only near-haploid cell lines to generate genome-level insights into gene essentiality [@wang2015a] to broadly identifying cancer dependencies with large-scale screens in multiple cancer types [@mcdonald2017; @mcfarland2018; @meyers2017; @patel2017] or select lineages [@heiser2009; @marcotte2012; @patel2017].
-Despite their widespread use, cancer cell lines are known to have issues with inconsistent naming conventions and contamination [@yu2015], and some cell lines have been shown to vary widely at the genetic level and in response to drug treatment across strains [@ben-david2018].
-Additionally, comparisons between cancer cell lines and tumors indicate that cell lines have higher numbers of genomic aberrations [@domcke2013; @mouradov2014; @neve2006] and tend to be hypermethylated [@paz2003; @varley2013], which could prove an impediment to translating cell line discoveries into the clinic.
+Cancer cell lines are a long-standing model for systematic testing of candidate therapeutics, beginning with the National Cancer Institute 60 (NCI60) assay from the late 1980s [@alley_feasibility_1988; @shoemaker_nci60_2006; @stinson_morphological_1992], which has been used to screen over 100,000 compounds as of 2010 [@holbeck_analysis_2010].
+Since then, numerous small-molecule and gene essentiality screens of various scales and study aims have been conducted in cell lines, from grouping drugs by therapeutic target similarity [@greshock_molecular_2010] to screening only near-haploid cell lines to generate genome-level insights into gene essentiality [@wang_identification_2015] to broadly identifying cancer dependencies with large-scale screens in multiple cancer types [@mcdonald_project_2017; @mcfarland_improved_2018; @meyers_computational_2017; @patel_identification_2017] or select lineages [@heiser_integrated_2009; @marcotte_essential_2012; @patel_identification_2017].
+Despite their widespread use, cancer cell lines are known to have issues with inconsistent naming conventions and contamination [@yu_resource_2015], and some cell lines have been shown to vary widely at the genetic level and in response to drug treatment across strains [@ben-david_genetic_2018].
+Additionally, comparisons between cancer cell lines and tumors indicate that cell lines have higher numbers of genomic aberrations [@domcke_evaluating_2013; @mouradov_colorectal_2014; @neve_collection_2006] and tend to be hypermethylated [@paz_systematic_2003; @varley_dynamic_2013], which could prove an impediment to translating cell line discoveries into the clinic.
 
-There have also been debates over consistency between drug screen datasets, namely the Broad Institute’s and Novartis Institutes for Biomedical Research’s Cancer Cell Line Encyclopedia (CCLE) [@barretina2012; @consortium2015] and the Genomics of Drug Sensitivity in Cancer (GDSC) from the Cancer Genome Project at the Wellcome Sanger Institute and the Center for Molecular Therapeutics at Massachusetts General Hospital Cancer Center [@garnett2012; @yang2012].
+There have also been debates over consistency between drug screen datasets, namely the Broad Institute’s and Novartis Institutes for Biomedical Research’s Cancer Cell Line Encyclopedia (CCLE) [@barretina_cancer_2012; @consortium_pharmacogenomic_2015] and the Genomics of Drug Sensitivity in Cancer (GDSC) from the Cancer Genome Project at the Wellcome Sanger Institute and the Center for Molecular Therapeutics at Massachusetts General Hospital Cancer Center [@garnett_systematic_2012; @yang_genomics_2012].
 The GDSC has also been referred to as the Cancer Genome Project (CGP) and the Sanger dataset.
-Studies have shown that drug-gene interactions matched between CCLE and GDSC exhibited poor correlation and inconsistencies [@haibe-kains2013; @jang2014], prompting other groups to join the debate on how best correct for experimental and methodological variation between the original drug screens and subsequent computational analysis [@consortium2015; @geeleher2016; @geeleher2016a; @hatzis2014; @haverty2016; @safikhani2016; @safikhani2017].
+Studies have shown that drug-gene interactions matched between CCLE and GDSC exhibited poor correlation and inconsistencies [@haibe-kains_inconsistency_2013; @jang_systematic_2014], prompting other groups to join the debate on how best correct for experimental and methodological variation between the original drug screens and subsequent computational analysis [@consortium_pharmacogenomic_2015; @geeleher_cancer_2016; @geeleher_consistency_2016; @hatzis_enhancing_2014; @haverty_reproducible_2016; @safikhani_revisiting_2017; @safikhani_safikhani_2016]
 
@@
 
-To curate an evidence-based list of these clinical biomarkers, we utilized a new oncological data aggregation project conducted by the Variant Interpretation for Cancer Consortium (VICC; https://cancervariants.org/), a Driver Project for the Global Alliance for Genomics and Health (GA4GH) [@theglobalallianceforgenomicsandhealth2016].
-The VICC has curated annotations of known cancer variants at varying levels of evidence from multiple resources [@wagner2018]: the Precision Medicine Knowledgebase [@huang2016], MolecularMatch (https://www.molecularmatch.com/index.html), OncoKB [@chakravarty2017], Jackson Labs Clinical Knowledgebase [@patterson2016], Clinical Interpretations of Variance in Cancers (CIViC) [@griffith2017], and the Cancer Genome Interpreter (CGI) [@tamborero2018].
-These harmonized variants are hosted on an ElasticSearch (Kibana v6.0) platform called Genotype to Phenotype (G2P, https://search.cancervariants.org/#*) that allows users to query and filter aggregated evidence from the various databases listed above as well as the GA4GH beacon service (http://beacon-network.org/#/), which yields access to genetic mutation data from over 200 datasets as of 2016 [@theglobalallianceforgenomicsandhealth2016].
-For drug screen datasets, we focus on three well-known, large-scale drug projects: the CCLE and GDSC, which were mentioned above, and the Center for the Science of Therapeutics at the Broad Institute’s Cancer Therapeutics Response Portal (CTRP) dataset [@basu2013; @rees2016; @seashore-ludlow2015].
-We also analyzed the results from a large-scale CRISPR/Cas9 screen conducted by the Broad Institute’s Cancer Dependency Map project (DepMap) using the Avana knockout library [@doench2016a; @meyers2017], which will address whether gene essentiality screens via CRISPR yield results comparable to functional drug screens.
+To curate an evidence-based list of these clinical biomarkers, we utilized a new oncological data aggregation project conducted by the Variant Interpretation for Cancer Consortium (VICC; https://cancervariants.org/), a Driver Project for the Global Alliance for Genomics and Health (GA4GH) [@global_alliance_for_genomics_and_health_federated_2016].
+The VICC has curated annotations of known cancer variants at varying levels of evidence from multiple resources [@wagner_harmonized_2018]: the Precision Medicine Knowledgebase [@huang_cancer_2016], MolecularMatch (https://www.molecularmatch.com/index.html), OncoKB [@chakravarty_oncokb:_2017], Jackson Labs Clinical Knowledgebase [@patterson_clinical_2016], Clinical Interpretations of Variance in Cancers (CIViC) [@griffith_civic_2017], and the Cancer Genome Interpreter (CGI) [@tamborero_cancer_2018].
+These harmonized variants are hosted on an ElasticSearch (Kibana v6.0) platform called Genotype to Phenotype (G2P, https://search.cancervariants.org/#*) that allows users to query and filter aggregated evidence from the various databases listed above as well as the GA4GH beacon service (http://beacon-network.org/#/), which yields access to genetic mutation data from over 200 datasets as of 2016 [@global_alliance_for_genomics_and_health_federated_2016].
+For drug screen datasets, we focus on three well-known, large-scale drug projects: the CCLE and GDSC, which were mentioned above, and the Center for the Science of Therapeutics at the Broad Institute’s Cancer Therapeutics Response Portal (CTRP) dataset [@basu_interactive_2013; @rees_correlating_2016; @seashore-ludlow_harnessing_2015].
+We also analyzed the results from a large-scale CRISPR/Cas9 screen conducted by the Broad Institute’s Cancer Dependency Map project (DepMap) using the Avana knockout library [@doench_optimized_2016; @meyers_computational_2017], which will address whether gene essentiality screens via CRISPR yield results comparable to functional drug screens.
 
@@
 
-<!-- After filtering, `r nrow(g2p_filt)` level-A G2P interpretations were carried forward in subsequent analyses, constituting `r length(g2p_drugs)` unique drugs and `r length(g2p_genes)` unique genes in `r length(g2p_druggenes)` distinct level-A combinations (*Figure 1: Pink heatmap*).
-The number of level-A interpretations per drug ranged from `r range(g2p_drug_tally$n)[1]` to `r range(g2p_drug_tally$n)[2]` ($M =$ `r formatC(mean(g2p_drug_tally$n), digits = 2)`, $SD =$ `r formatC(sd(g2p_drug_tally$n), digits = 2)`), `r range(g2p_gene_tally$n)[1]` to `r range(g2p_gene_tally$n)[2]` ($M =$ `r formatC(mean(g2p_gene_tally$n), digits = 2)`, $SD =$ `r formatC(sd(g2p_gene_tally$n), digits = 2)`) per gene, and for each level-A drug-gene combination, the range was `r range(g2p_druggene_tally$n)[1]` to `r range(g2p_druggene_tally$n)[2]` ($M =$ `r formatC(mean(g2p_druggene_tally$n), digits = 2)`, $SD =$ `r formatC(sd(g2p_druggene_tally$n), digits = 2)`).
-These unique drugs, genes, and combinations are hereafter referred to as G2P drugs, G2P genes, and G2P associations.
-Filtering our screening datasets by these clinical criteria yields panels of potentially clinically relevant omic features.
-Of the `r length(g2p_drugs)` unique G2P drugs, N of them were screened in at least one of the drug screen datasets, N drugs were screened in at least two of the three datasets, and only N were screened in all three datasets.
-The remaining N un-screened G2P drugs suggests an incompleteness of these drug screens, though these projects frequently release new screening data that may include these drugs in future releases.
--->
-
 ![Summary of G2P data content and concordance with drug sensitivity screens.
@@
 
-In the `r nrow(g2p_filt)` level-A G2P interpretations, there was a wide variation in the specificity of cancer description, ranging from “Waldenström macroglobulinemia” and “hyper eosinophilic advanced syndrome” on the more detailed end to “cancer” on the broad end.
+In the `nrow(g2p_filt)` level-A G2P interpretations, there was a wide variation in the specificity of cancer description, ranging from “Waldenström macroglobulinemia” and “hyper eosinophilic advanced syndrome” on the more detailed end to “cancer” on the broad end.
 Similarly, the drug screen datasets had a wide range in lineage specificity, e.g.
-CCLE, GTRP, and GDSC all had lineages labeled “leukemia” and “T-cell childhood acute lymphocytic leukemia” and the CRISPR dataset had cell lines labeled “Epstein-Barr virus-related Burkitt lymphoma” and “lymphoma.” To more easily conduct comparative analyses in a cancer-specific manner, we developed a more general lineage grouping method derived from the Human Disease Ontology identity codes (DOIDs, http://disease-ontology.org/) [@schriml2019] assigned to each cell line, yielding `r length(unique(ccl_converter$group_general_lineage_name))` unique lineage groupings.
+CCLE, GTRP, and GDSC all had lineages labeled “leukemia” and “T-cell childhood acute lymphocytic leukemia” and the CRISPR dataset had cell lines labeled “Epstein-Barr virus-related Burkitt lymphoma” and “lymphoma.” To more easily conduct comparative analyses in a cancer-specific manner, we developed a more general lineage grouping method derived from the Human Disease Ontology identity codes (DOIDs, http://disease-ontology.org/) [@schriml2019] assigned to each cell line, yielding ___ unique lineage groupings.
 This custom lineage grouping was included in our harmonized cancer cell line database (see Methods).
@@
 # Discussion
+
+**NUMBERS WRONG HERE**
 
@@
 ## Drug screen dataset retrieval
+
 **12/4 updated**
+
 We utilized small molecule screening data from the Cancer Therapeutics Response Portal (CTRP, Broad Institute) [@basu_interactive_2013; @rees_correlating_2016; @seashore-ludlow_harnessing_2015], the Genomics of Drug Sensitivity in Cancer (GDSC, Wellcome Sanger Institute and Massachusetts General Hospital Cancer Center), [@garnett_systematic_2012; @yang_genomics_2012], and the Cancer Cell Line Encyclopedia (CCLE, Broad Institute and Novartis Institutes for Biomedical Research) [@barretina_cancer_2012; @consortium_pharmacogenomic_2015].
@@
 ## DepMap data retrieval and processing
+
 **12/4 updated**
+
 CRISPR/Cas9 and mutation calls, fusions, gene expression, and copy number data from the CCLE were all retrieved from the Broad Institute’s Cancer Dependency Map (DepMap) Public 19Q2 release via the DepMap data portal (https://depmap.org/portal/download/) [@broad_depmap_depmap_2019-1].
@@
 ### Cell line harmonization
+
 **12/4 updated**
+
 In an effort to compare CCLE, CTRP, GDSC and CRISPR results and include lineage specificity, it was necessary to consolidate cell lines screened in each dataset.
@@
 ### Mutation calls
+
 **12/4 EDIT THIS**
+
 To preclude variation in genomic feature calls across the datasets, we used identical omics annotations from CCLE for all cell lines screened in the three datasets.
@@
 ### Copy number data
+
 **12/4 EDIT THIS**
+
 The CCLE generated genomic copy number (CN) data using the Affymetrix Genome-Wide Human SNP Array 6.0 and GenePattern pipeline [@thecancergenomeatlasresearchnetwork2008] and normalized segmented CN log2-ratios for 23,299 genes across 1,098 cell lines using circular binary segmentation [@olshen2004] (dataset: public_18Q4_gene_cn.csv, accessed 15 November 2018).
@@
 ### Gene expression data
+
 **12/4 EDIT THIS**
+
 The CCLE reports gene expression in RPKM (reads per kilobase per million mapped reads) for 54,356 genes across 1,156 cell lines, generated on the GeneChip Human Genome U133 Plus 2.0 Array (dataset: CCLE_DepMap_18q3_RNAseq_RPKM_20180718.gct, accessed 18 July 2018).
@@
 ## G2P cancer variants
+
 **12/4 updated**
+
 Cancer variants with the highest level of evidence (i.e.
@@
 ## Computational
+
 **12/4 EDIT THIS**
@@
 ### Statistics
+
 **12/4 EDIT THIS**
+
 Wilcoxon tests were conducted using the `compare_means` function in the ggpubr (`r ggpubr_v`) R package [@kassambara2018].

### 2019-12-16 19Q2.Rmd
small edits during manuscript discussion w/ Daniel

@@
 
+```{r fig.width=10}
+ggplot(data = ccle_fus) + 
+  geom_boxplot(aes(x = disease, y = Score)) +
+
+```
+
 ```{r crispr_mut_boxplots, fig.height=5, fig.width=10, eval=FALSE}
@@
 
-## Lineage
-
 ```{r spear_calc, warning=FALSE, eval=FALSE}
@@
 
+**12/16 FIX THIS **
 ```{r spear_calc_lin, eval=FALSE}
@@
 saveRDS(ge_cor_lin, "./data_munging/rds/ge_cor_lineage.rds")
+```
+
+```{r}
+cn_cor_lin <- readRDS("./data_munging/rds/cn_cor_lineage.rds")
+ge_cor_lin <- readRDS("./data_munging/rds/ge_cor_lineage.rds")
 ```

### 2019-12-27 19Q2.Rmd
new heatmaps and plots, need to fix all heatmaps

@@
                                    ifelse(disease == "stomach" | CCLE_histology == "stomach", "gastric", disease))))))))
+# Drop matched_normal_tissue cell lines
+ccl_meta <- filter(ccl_meta, disease != "matched_normal_tissue")
 # Filter out cell lines without a DepMap ID or a cell line
@@
 
+# Manually curate rucaparib-BRCA/BRCA1/BRCA2 entry
+g2p$Gene <- ifelse(g2p$Drug == "rucaparib" & is.na(g2p$Gene), "BRCA2;BRCA1;BRCA", as.character(g2p$Gene))
+g2p <- separate_rows(g2p, Gene, sep = ";")
+
 # Manually assign biomarker_types based on a combination of biomarker_type derived from the JSON string and patterns in the Feature.Names
@@
 g2p <- unique(g2p)
-write.csv(g2p, "./data_munging/g2p_db_edited_20190718.csv")
+write.csv(g2p, "./data_munging/g2p_db_edited_20191225.csv")
 ```
@@
 ```{r g2p}
-g2p <- read.delim("./data_munging/g2p_db_edited_20190718.csv", sep = ",", header = TRUE, row.names = 1)
+g2p <- read.delim("./data_munging/g2p_db_edited_20191225.csv", sep = ",", header = TRUE, row.names = 1)
 
@@
   }
-
-  ## Summarize number of mutant and Wildtype cell lines
-  data_muts_summ <- data %>% group_by(Gene) %>% summarize(N_Wildtype = length(Mutation) - sum(Mutation == 1), N_Mutant = sum(Mutation == 1))
-  ## Merge test results back into full dataset, which restores information lost in the summarization
-  data <- merge(data_muts_summ, data, by = "Gene")
   print("Merged mutation calls.")
@@
 ```{r load_drug_rds}
+# ccle_all <- readRDS("./../htscreens_giant_files/pozdeyev_data/pozdeyev2016_ccle_all_edited.rds")
+# ctrp_all <- readRDS("./../htscreens_giant_files/pozdeyev_data/pozdeyev2016_ctrp_all_edited.rds")
+# gdsc_all <- readRDS("./../htscreens_giant_files/pozdeyev_data/pozdeyev2016_gdsc_all_edited.rds")
+
 # ccle <- readRDS("./data_munging/19Q2/ccle_data_19Q2_all.rds") %>% drop_na(Drug)
@@
 ccle_prot$Database <- "CCLE"
-ccle_prot <- ccle_prot %>% drop_na(Drug)
+ccle_prot <- ccle_prot %>% drop_na(Drug, DepMap_ID)
 
@@
 ctrp_prot$Database <- "CTRP"
-ctrp_prot <- ctrp_prot %>% drop_na(Drug)
+ctrp_prot <- ctrp_prot %>% drop_na(Drug, DepMap_ID)
 
@@
 gdsc_prot$Database <- "GDSC"
-gdsc_prot <- gdsc_prot %>% drop_na(Drug)
+gdsc_prot <- gdsc_prot %>% drop_na(Drug, DepMap_ID)
 
@@
 
-crispr_allgenes <- MergeOmicsG2P(database = "CRISPR", dataframe = crispr_all, maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = colnames(crispr_all)[2:length(colnames(crispr_all))], outfile = "./../htscreens_giant_files/crispr_data_19Q2_allgenes.rds")
+# crispr_allgenes <- MergeOmicsG2P(database = "CRISPR", dataframe = crispr_all, maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = colnames(crispr_all)[2:length(colnames(crispr_all))], outfile = "./../htscreens_giant_files/crispr_data_19Q2_allgenes.rds")
 
@@
 ```{r merge_crispr_fus, eval=FALSE}
-crispr_allgenes <- readRDS("./../htscreens_giant_files/crispr_data_19Q2_allgenes.rds")
-fusions_filt <- unfactorize(unique(filter(fusions, FusionPair %in% unique(as.character(g2p_fus$FusionPair)))) %>% select(-c("Cell_line", "disease")))
-crispr_fus_grid <- unfactorize(expand.grid("DepMap_ID" = unique(crispr_allgenes$DepMap_ID), "FusionPair" = unique(fusions_filt$FusionPair)))
-crispr_fus <- merge(merge(crispr_allgenes, crispr_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "FusionPair"), all.x = TRUE)
-crispr_fus$Fusion_Status <- ifelse(!is.na(crispr_fus$LeftGene), "Yes", "No")
-crispr_fus$Drug_FusionPair <- with(crispr_fus, ifelse(is.na(Drug) | is.na(FusionPair), NA, paste0(Drug, "_", FusionPair)))
-crispr_fus$Drug_Fusion_Lineage <- with(crispr_fus, ifelse(is.na(Drug) | is.na(FusionPair) | is.na(disease), NA, paste0(Drug, "_", FusionPair, "_", disease)))
-crispr_fus$G2P_Drug_FusionPair <- "No"
-crispr_fus$G2P_Fusion <- ifelse(crispr_fus$FusionPair %in% unique(as.character(g2p_fus$FusionPair)), "Yes", "No")
-crispr_fus$G2P_Drug_Fusion_Lineage <- "No"
-crispr_fus$Database <- "CRISPR"
-crispr_fus <- crispr_fus %>% drop_na(Score)
-saveRDS(crispr_fus, "./../htscreens_giant_files/crispr_fusions_allgenes.rds", compress = "xz")
+# crispr_allgenes <- readRDS("./../htscreens_giant_files/crispr_data_19Q2_allgenes.rds")
+# fusions_filt <- unfactorize(unique(filter(fusions, FusionPair %in% unique(as.character(g2p_fus$FusionPair)))) %>% select(-c("Cell_line", "disease")))
+# crispr_fus_grid <- unfactorize(expand.grid("DepMap_ID" = unique(crispr_allgenes$DepMap_ID), "FusionPair" = unique(fusions_filt$FusionPair)))
+# crispr_fus <- merge(merge(crispr_allgenes, crispr_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "FusionPair"), all.x = TRUE)
+# crispr_fus$Fusion_Status <- ifelse(!is.na(crispr_fus$LeftGene), "Yes", "No")
+# crispr_fus$Drug_FusionPair <- with(crispr_fus, ifelse(is.na(Drug) | is.na(FusionPair), NA, paste0(Drug, "_", FusionPair)))
+# crispr_fus$Drug_Fusion_Lineage <- with(crispr_fus, ifelse(is.na(Drug) | is.na(FusionPair) | is.na(disease), NA, paste0(Drug, "_", FusionPair, "_", disease)))
+# crispr_fus$G2P_Drug_FusionPair <- "No"
+# crispr_fus$G2P_Fusion <- ifelse(crispr_fus$FusionPair %in% unique(as.character(g2p_fus$FusionPair)), "Yes", "No")
+# crispr_fus$G2P_Drug_Fusion_Lineage <- "No"
+# crispr_fus$Database <- "CRISPR"
+# crispr_fus <- crispr_fus %>% drop_na(Score)
+# saveRDS(crispr_fus, "./../htscreens_giant_files/crispr_fusions_allgenes.rds", compress = "xz")
 
@@
 
-saveRDS(crispr_prot, "./../htscreens_giant_files/crispr_protein_changes_allgenes.rds", compress = "xz")
+saveRDS(crispr_prot, "./../htscreens_giant_files/crispr_protein_changes_20191223.rds", compress = "xz")
 ```
@@
 crispr_fus <- readRDS("./data_munging/19Q2/crispr_fusions.rds")
-crispr_prot <- readRDS("./../htscreens_giant_files/crispr_protein_changes.rds")
-```
-
-```{r, eval = TRUE}
+# crispr_prot <- readRDS("./../htscreens_giant_files/crispr_protein_changes.rds")
+crispr_prot <- readRDS("./../htscreens_giant_files/crispr_protein_changes_20191223.rds")
+```
+
+```{r, eval = FALSE}
 crispr_allgenes <- readRDS("./../htscreens_giant_files/crispr_data_19Q2_allgenes.rds")
@@
     # Require at least 3 samples in each category to run the test, else filter out that DG from testing df
-    count_mut_n <- dataframe %>% count(Drug_Gene, Mutation) %>% filter(n >= 3)
-    count_mut_category <- count_mut_n %>% count(Drug_Gene) %>% filter(n == 2)
-    dg_keep <- intersect(count_mut_n$Drug_Gene, count_mut_category$Drug_Gene)
+    count_n <- dataframe %>% count(Drug_Gene, Mutation)
+    count_n_wide <- dcast(count_n, Drug_Gene ~ Mutation, value.var = "n", fill = 0) %>% separate(Drug_Gene, sep = "_", c("Drug", "Gene"), remove = FALSE)
+    colnames(count_n_wide) <- c("Drug_Gene", "Drug", "Gene", "Mutation_0_count", "Mutation_1_count")
+    count_n_filt <- filter(count_n, n >= 3)
+    count_category <- count_n_filt %>% count(Drug_Gene) %>% filter(n == 2)
+    dg_keep <- intersect(count_n_filt$Drug_Gene, count_category$Drug_Gene)
     dataframe <- filter(dataframe, Drug_Gene %in% dg_keep)
@@
     signif <- signif[order(signif$p),]
+    signif <- merge(signif, count_n_wide, by = grouping, all = TRUE)
     if(is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- ifelse(signif$Drug_Gene %in% g2p_list, "Yes", "No") }
@@
     # Require at least 3 samples in each category to run the test, else filter out that DGL from testing df
-    count_mut_n <- dataframe %>% count(Drug_Gene_Lin, Mutation) %>% filter(n >= 3)
-    count_mut_category <- count_mut_n %>% count(Drug_Gene_Lin) %>% filter(n == 2)
-    dgl_keep <- intersect(count_mut_n$Drug_Gene_Lin, count_mut_category$Drug_Gene_Lin)
-    dataframe <- filter(dataframe, Drug_Gene_Lin %in% dgl_keep)
+    count_n <- dataframe %>% count(Drug_Gene_Lin, Mutation)
+    count_n_wide <- dcast(count_n, Drug_Gene_Lin ~ Mutation, value.var = "n", fill = 0) %>% separate(Drug_Gene_Lin, sep = "_", c("Drug", "Gene", "disease"), remove = FALSE)
+    colnames(count_n_wide) <- c("Drug_Gene_Lin", "Drug", "Gene", "disease", "Mutation_0_count", "Mutation_1_count")
+    count_n_wide <- add_column(count_n_wide, Drug_Gene = paste0(count_n_wide$Drug, "_", count_n_wide$Gene), .after = "Gene")
+    count_n_filt <- filter(count_n, n >= 3)
+    count_category <- count_n_filt %>% count(Drug_Gene_Lin) %>% filter(n == 2)
+    dg_keep <- intersect(count_n_filt$Drug_Gene_Lin, count_category$Drug_Gene_Lin)
+    dataframe <- filter(dataframe, Drug_Gene_Lin %in% dg_keep)
     dataframe$Drug_Gene_Lin <- as.character(dataframe$Drug_Gene_Lin)
@@
     signif <- signif[order(signif$p),]
+    signif <- merge(signif, count_n_wide, by = grouping, all = TRUE)
     if(is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- ifelse(signif$Drug_Gene_Lin %in% g2p_list, "Yes", "No") }
@@
     # Require at least 3 samples in each category to run the test, else filter out that Gene_Protein_Change from testing df
-    count_n <- dataframe %>% count(Drug_Gene_Protein_Change, Change_Status) %>% filter(n >= 3)
-    count_category <- count_n %>% count(Drug_Gene_Protein_Change) %>% filter(n == 2)
-    keep <- intersect(count_n$Drug_Gene_Protein_Change, count_category$Drug_Gene_Protein_Change)
-    dataframe <- filter(dataframe, Drug_Gene_Protein_Change %in% keep)
+    count_n <- dataframe %>% count(Drug_Gene_Protein_Change, Change_Status)
+    count_n_wide <- dcast(count_n, Drug_Gene_Protein_Change ~ Change_Status, value.var = "n", fill = 0) %>% separate(Drug_Gene_Protein_Change, sep = "_", c("Drug", "Gene_Protein_Change"), remove = FALSE)
+    colnames(count_n_wide) <- c("Drug_Gene_Protein_Change", "Drug", "Gene_Protein_Change", "Change_Status_0_count", "Change_Status_1_count")
+    count_n_filt <- filter(count_n, n >= 3)
+    count_category <- count_n_filt %>% count(Drug_Gene_Protein_Change) %>% filter(n == 2)
+    dg_keep <- intersect(count_n_filt$Drug_Gene_Protein_Change, count_category$Drug_Gene_Protein_Change)
+    dataframe <- filter(dataframe, Drug_Gene_Protein_Change %in% dg_keep)
     dataframe$Drug_Gene_Protein_Change <- as.character(dataframe$Drug_Gene_Protein_Change)
@@
     signif <- signif[order(signif$p),]
+    signif <- merge(signif, count_n_wide, by = grouping, all = TRUE)
     if(is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- ifelse(signif$Drug_Gene_Protein_Change %in% g2p_list, "Yes", "No") }
@@
     # Require at least 3 samples in each category to run the test, else filter out that Drug_Gene_Protein_Change_Lineage from testing df
-    count_n <- dataframe %>% count(Drug_Gene_Protein_Change_Lineage, Change_Status) %>% filter(n >= 3)
-    count_category <- count_n %>% count(Drug_Gene_Protein_Change_Lineage) %>% filter(n == 2)
-    keep <- intersect(count_n$Drug_Gene_Protein_Change_Lineage, count_category$Drug_Gene_Protein_Change_Lineage)
-    dataframe <- filter(dataframe, Drug_Gene_Protein_Change_Lineage %in% keep)
+    count_n <- dataframe %>% count(Drug_Gene_Protein_Change_Lineage, Change_Status)
+    count_n_wide <- dcast(count_n, Drug_Gene_Protein_Change_Lineage ~ Change_Status, value.var = "n", fill = 0) %>% separate(Drug_Gene_Protein_Change_Lineage, sep = "_", c("Drug", "Gene_Protein_Change", "disease"), remove = FALSE)
+    colnames(count_n_wide) <- c("Drug_Gene_Protein_Change_Lineage", "Drug", "Gene_Protein_Change", "disease", "Change_Status_0_count", "Change_Status_1_count")
+    count_n_wide <- add_column(count_n_wide, Drug_Gene_Protein_Change = paste0(count_n_wide$Drug, "_", count_n_wide$Gene_Protein_Change), .after = "Gene_Protein_Change")
+    count_n_filt <- filter(count_n, n >= 3)
+    count_category <- count_n_filt %>% count(Drug_Gene_Protein_Change_Lineage) %>% filter(n == 2)
+    dg_keep <- intersect(count_n_filt$Drug_Gene_Protein_Change_Lineage, count_category$Drug_Gene_Protein_Change_Lineage)
+    dataframe <- filter(dataframe, Drug_Gene_Protein_Change_Lineage %in% dg_keep)
     dataframe$Drug_Gene_Protein_Change_Lineage <- as.character(dataframe$Drug_Gene_Protein_Change_Lineage)
@@
     signif <- signif[order(signif$p),]
+    signif <- merge(signif, count_n_wide, by = grouping, all = TRUE)
     if(is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- ifelse(signif$Drug_Gene_Protein_Change_Lineage %in% g2p_list, "Yes", "No") }
@@
     # Require at least 3 samples in each category to run the test, else filter out that Drug_FusionPair from testing df
-    count_n <- dataframe %>% count(Drug_FusionPair, Fusion_Status) %>% filter(n >= 3)
-    count_category <- count_n %>% count(Drug_FusionPair) %>% filter(n == 2)
-    keep <- intersect(count_n$Drug_FusionPair, count_category$Drug_FusionPair)
-    dataframe <- filter(dataframe, Drug_FusionPair %in% keep)
+    count_n <- dataframe %>% count(Drug_FusionPair, Fusion_Status)
+    count_n_wide <- dcast(count_n, Drug_FusionPair ~ Fusion_Status, value.var = "n", fill = 0) %>% separate(Drug_FusionPair, sep = "_", c("Drug", "FusionPair"), remove = FALSE)
+    colnames(count_n_wide) <- c("Drug_FusionPair", "Drug", "FusionPair", "Fusion_Status_0_count", "Fusion_Status_1_count")
+    count_n_filt <- filter(count_n, n >= 3)
+    count_category <- count_n_filt %>% count(Drug_FusionPair) %>% filter(n == 2)
+    dg_keep <- intersect(count_n_filt$Drug_FusionPair, count_category$Drug_FusionPair)
+    dataframe <- filter(dataframe, Drug_FusionPair %in% dg_keep)
     dataframe$Drug_FusionPair <- as.character(dataframe$Drug_FusionPair)
@@
     signif <- signif[order(signif$p),]
+    signif <- merge(signif, count_n_wide, by = grouping, all = TRUE)
     if(is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- ifelse(signif$Drug_FusionPair %in% g2p_list, "Yes", "No")  }
@@
     # Require at least 3 samples in each category to run the test, else filter out that Drug_Fusion_Lineage from testing df
-    count_n <- dataframe %>% count(Drug_Fusion_Lineage, Fusion_Status) %>% filter(n >= 3)
-    count_category <- count_n %>% count(Drug_Fusion_Lineage) %>% filter(n == 2)
-    keep <- intersect(count_n$Drug_Fusion_Lineage, count_category$Drug_Fusion_Lineage)
-    dataframe <- filter(dataframe, Drug_Fusion_Lineage %in% keep)
+    count_n <- dataframe %>% count(Drug_Fusion_Lineage, Fusion_Status)
+    count_n_wide <- dcast(count_n, Drug_Fusion_Lineage ~ Fusion_Status, value.var = "n", fill = 0) %>% separate(Drug_Fusion_Lineage, sep = "_", c("Drug", "FusionPair", "disease"), remove = FALSE)
+    colnames(count_n_wide) <- c("Drug_Fusion_Lineage", "Drug", "FusionPair", "disease", "Fusion_Status_0_count", "Fusion_Status_1_count")
+    count_n_wide <- add_column(count_n_wide, Drug_FusionPair = paste0(count_n_wide$Drug, "_", count_n_wide$FusionPair), .after = "FusionPair")
+    count_n_filt <- filter(count_n, n >= 3)
+    count_category <- count_n_filt %>% count(Drug_Fusion_Lineage) %>% filter(n == 2)
+    dg_keep <- intersect(count_n_filt$Drug_Fusion_Lineage, count_category$Drug_Fusion_Lineage)
+    dataframe <- filter(dataframe, Drug_Fusion_Lineage %in% dg_keep)
     dataframe$Drug_Fusion_Lineage <- as.character(dataframe$Drug_Fusion_Lineage)
@@
     signif <- signif[order(signif$p),]
+    signif <- merge(signif, count_n_wide, by = grouping, all = TRUE)
     if(is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- ifelse(signif$Drug_Fusion_Lineage %in% g2p_list, "Yes", "No") }
@@
 ccle_signif_g2p_dg <- WilcoxonTestDF(dataframe = ccle_filt, grouping = c("Drug", "Gene", "Drug_Gene"), type = "drug_gene", g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), outfile = "./data_munging/rds/ccle_signif_g2p_dg.rds")
-ccle_signif_g2p_dgl <- WilcoxonTestDF(dataframe = ccle_filt, grouping = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), type = "drug_gene_lineage", g2p_list = unique(as.character(g2p_mut$Drug_Gene_Lin[!is.na(g2p_mut$Drug_Gene_Lin)])), outfile = "./data_munging/rds/ccle_signif_g2p_dgl.rds")
+ccle_signif_g2p_dgl <- WilcoxonTestDF(dataframe = ccle_filt, grouping = c("Drug", "Gene", "Drug_Gene", "disease", "Drug_Gene_Lin"), type = "drug_gene_lineage", g2p_list = unique(as.character(g2p_mut$Drug_Gene_Lin[!is.na(g2p_mut$Drug_Gene_Lin)])), outfile = "./data_munging/rds/ccle_signif_g2p_dgl.rds")
 
@@
 ctrp_signif_g2p_dg <- WilcoxonTestDF(dataframe = ctrp_filt, grouping = c("Drug", "Gene", "Drug_Gene"), type = "drug_gene", g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), outfile = "./data_munging/rds/ctrp_signif_g2p_dg.rds")
-ctrp_signif_g2p_dgl <- WilcoxonTestDF(dataframe = ctrp_filt, grouping = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), type = "drug_gene_lineage", g2p_list = unique(as.character(g2p_mut$Drug_Gene_Lin[!is.na(g2p_mut$Drug_Gene_Lin)])), outfile = "./data_munging/rds/ctrp_signif_g2p_dgl.rds")
+ctrp_signif_g2p_dgl <- WilcoxonTestDF(dataframe = ctrp_filt, grouping = c("Drug", "Gene", "Drug_Gene", "disease", "Drug_Gene_Lin"), type = "drug_gene_lineage", g2p_list = unique(as.character(g2p_mut$Drug_Gene_Lin[!is.na(g2p_mut$Drug_Gene_Lin)])), outfile = "./data_munging/rds/ctrp_signif_g2p_dgl.rds")
 
@@
 gdsc_signif_g2p_dg <- WilcoxonTestDF(dataframe = gdsc_filt, grouping = c("Drug", "Gene", "Drug_Gene"), type = "drug_gene", g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), outfile = "./data_munging/rds/gdsc_signif_g2p_dg.rds")
-gdsc_signif_g2p_dgl <- WilcoxonTestDF(dataframe = gdsc_filt, grouping = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), type = "drug_gene_lineage", g2p_list = unique(as.character(g2p_mut$Drug_Gene_Lin[!is.na(g2p_mut$Drug_Gene_Lin)])), outfile = "./data_munging/rds/gdsc_signif_g2p_dgl.rds")
+gdsc_signif_g2p_dgl <- WilcoxonTestDF(dataframe = gdsc_filt, grouping = c("Drug", "Gene", "Drug_Gene", "disease", "Drug_Gene_Lin"), type = "drug_gene_lineage", g2p_list = unique(as.character(g2p_mut$Drug_Gene_Lin[!is.na(g2p_mut$Drug_Gene_Lin)])), outfile = "./data_munging/rds/gdsc_signif_g2p_dgl.rds")
 ```
@@
 # CCLE
-ccle_prot <- unfactorize(ccle_prot)
 ccle_signif_prot <- WilcoxonTestDF(dataframe = ccle_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change[!is.na(g2p_prot$Drug_Gene_Protein_Change)])), type = "protein_change", outfile = "./data_munging/rds/ccle_signif_protein_changes.rds")
-ccle_signif_prot_lin <- WilcoxonTestDF(dataframe = ccle_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change", "Drug_Gene_Protein_Change_Lineage", "disease"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change_Lineage[!is.na(g2p_prot$Drug_Gene_Protein_Change_Lineage)])), type = "protein_change_lineage", outfile = "./data_munging/rds/ccle_signif_protein_changes_lineage.rds")
+ccle_signif_prot_lin <- WilcoxonTestDF(dataframe = ccle_prot, grouping = c("Gene_Protein_Change", "Drug", "disease", "Drug_Gene_Protein_Change", "Drug_Gene_Protein_Change_Lineage"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change_Lineage[!is.na(g2p_prot$Drug_Gene_Protein_Change_Lineage)])), type = "protein_change_lineage", outfile = "./data_munging/rds/ccle_signif_protein_changes_lineage.rds")
 
 # CTRP
-ctrp_prot <- unfactorize(ctrp_prot)
 ctrp_signif_prot <- WilcoxonTestDF(dataframe = ctrp_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change[!is.na(g2p_prot$Drug_Gene_Protein_Change)])), type = "protein_change", outfile = "./data_munging/rds/ctrp_signif_protein_changes.rds")
-ctrp_signif_prot_lin <- WilcoxonTestDF(dataframe = ctrp_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change", "Drug_Gene_Protein_Change_Lineage", "disease"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change_Lineage[!is.na(g2p_prot$Drug_Gene_Protein_Change_Lineage)])), type = "protein_change_lineage", outfile = "./data_munging/rds/ctrp_signif_protein_changes_lineage.rds")
+ctrp_signif_prot_lin <- WilcoxonTestDF(dataframe = ctrp_prot, grouping = c("Gene_Protein_Change", "Drug", "disease", "Drug_Gene_Protein_Change", "Drug_Gene_Protein_Change_Lineage"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change_Lineage[!is.na(g2p_prot$Drug_Gene_Protein_Change_Lineage)])), type = "protein_change_lineage", outfile = "./data_munging/rds/ctrp_signif_protein_changes_lineage.rds")
 
 # GDSC
-gdsc_prot <- unfactorize(gdsc_prot)
 gdsc_signif_prot <- WilcoxonTestDF(dataframe = gdsc_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change[!is.na(g2p_prot$Drug_Gene_Protein_Change)])), type = "protein_change", outfile = "./data_munging/rds/gdsc_signif_protein_changes.rds")
-gdsc_signif_prot_lin <- WilcoxonTestDF(dataframe = gdsc_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change", "Drug_Gene_Protein_Change_Lineage", "disease"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change_Lineage[!is.na(g2p_prot$Drug_Gene_Protein_Change_Lineage)])), type = "protein_change_lineage", outfile = "./data_munging/rds/gdsc_signif_protein_changes_lineage.rds")
+gdsc_signif_prot_lin <- WilcoxonTestDF(dataframe = gdsc_prot, grouping = c("Gene_Protein_Change", "Drug", "disease", "Drug_Gene_Protein_Change", "Drug_Gene_Protein_Change_Lineage"), g2p_list = unique(as.character(g2p_prot$Drug_Gene_Protein_Change_Lineage[!is.na(g2p_prot$Drug_Gene_Protein_Change_Lineage)])), type = "protein_change_lineage", outfile = "./data_munging/rds/gdsc_signif_protein_changes_lineage.rds")
 ```
@@
 ccle_signif_fus <- WilcoxonTestDF(dataframe = ccle_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair"), g2p_list = unique(as.character(g2p_fus$Drug_FusionPair[!is.na(g2p_fus$Drug_FusionPair)])), type = "fusion", outfile = "./data_munging/rds/ccle_signif_fusions.rds")
-ccle_signif_fus_lin <- WilcoxonTestDF(dataframe = ccle_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair", "Drug_Fusion_Lineage"), g2p_list = unique(as.character(g2p_fus$Drug_Fusion_Lineage[!is.na(g2p_fus$Drug_Fusion_Lineage)])), type = "fusion_lineage", outfile = "./data_munging/rds/ccle_signif_fusions_lineage.rds")
+ccle_signif_fus_lin <- WilcoxonTestDF(dataframe = ccle_fus, grouping = c("FusionPair", "Drug", "disease", "Drug_FusionPair", "Drug_Fusion_Lineage"), g2p_list = unique(as.character(g2p_fus$Drug_Fusion_Lineage[!is.na(g2p_fus$Drug_Fusion_Lineage)])), type = "fusion_lineage", outfile = "./data_munging/rds/ccle_signif_fusions_lineage.rds")
 
 ctrp_signif_fus <- WilcoxonTestDF(dataframe = ctrp_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair"), g2p_list = unique(as.character(g2p_fus$Drug_FusionPair[!is.na(g2p_fus$Drug_FusionPair)])), type = "fusion", outfile = "./data_munging/rds/ctrp_signif_fusions.rds")
-ctrp_signif_fus_lin<- WilcoxonTestDF(dataframe = ctrp_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair", "Drug_Fusion_Lineage"), g2p_list = unique(as.character(g2p_fus$Drug_Fusion_Lineage[!is.na(g2p_fus$Drug_Fusion_Lineage)])), type = "fusion_lineage", outfile = "./data_munging/rds/ctrp_signif_fusions_lineage.rds")
+ctrp_signif_fus_lin<- WilcoxonTestDF(dataframe = ctrp_fus, grouping = c("FusionPair", "Drug", "disease", "Drug_FusionPair", "Drug_Fusion_Lineage"), g2p_list = unique(as.character(g2p_fus$Drug_Fusion_Lineage[!is.na(g2p_fus$Drug_Fusion_Lineage)])), type = "fusion_lineage", outfile = "./data_munging/rds/ctrp_signif_fusions_lineage.rds")
 
 gdsc_signif_fus <- WilcoxonTestDF(dataframe = gdsc_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair"), g2p_list = unique(as.character(g2p_fus$Drug_FusionPair[!is.na(g2p_fus$Drug_FusionPair)])), type = "fusion", outfile = "./data_munging/rds/gdsc_signif_fusions.rds")
-gdsc_signif_fus_lin <- WilcoxonTestDF(dataframe = gdsc_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair", "Drug_Fusion_Lineage"), g2p_list = unique(as.character(g2p_fus$Drug_Fusion_Lineage[!is.na(g2p_fus$Drug_Fusion_Lineage)])), type = "fusion_lineage", outfile = "./data_munging/rds/gdsc_signif_fusions_lineage.rds")
+gdsc_signif_fus_lin <- WilcoxonTestDF(dataframe = gdsc_fus, grouping = c("FusionPair", "Drug", "disease", "Drug_FusionPair", "Drug_Fusion_Lineage"), g2p_list = unique(as.character(g2p_fus$Drug_Fusion_Lineage[!is.na(g2p_fus$Drug_Fusion_Lineage)])), type = "fusion_lineage", outfile = "./data_munging/rds/gdsc_signif_fusions_lineage.rds")
+```
+
+```{r}
+ccle_fus_means_df <- select(ccle_fus, FusionPair, Drug, Score) %>% group_by(FusionPair, Drug) %>% summarize(Agnostic_Mean_Score = mean(Score))
+ccle_fus_means_lin_df <- select(ccle_fus, FusionPair, disease, Drug, Score) %>% drop_na(disease) %>% group_by(FusionPair, disease, Drug) %>% summarize(Mean_Score = mean(Score))
+ccle_fus_means <- merge(ccle_fus_means_df, ccle_fus_means_lin_df, by = c("FusionPair", "Drug"), all = TRUE)
+```
+
+```{r}
+# ggplot(ccle_fus_means_df) +
+#   geom_histogram(aes(x = disease, y = Mean_Score)) +
+#   facet_wrap(~ Drug)
 ```
@@
 
-**12/5 RAN ALL OF THESE!**
-```{r, eval = FALSE}
+```{r, eval=FALSE}
 # Mutation status
 ## All genes
-crispr_allgenes <- unfactorize(crispr_allgenes)
-crispr_signif_gene_allgenes <- WilcoxonTestDF(dataframe = crispr_allgenes, grouping = c("Drug", "Gene", "Drug_Gene"), type = "drug_gene", outfile = "./data_munging/rds/crispr_signif_g_allgenes.rds")
-crispr_signif_lineage_allgenes <- WilcoxonTestDF(dataframe = crispr_allgenes, grouping =  c("Drug", "Gene", "disease", "Drug_Gene_Lin"), type = "drug_gene_lineage", outfile = "./data_munging/rds/crispr_signif_gl_allgenes.rds")
+# crispr_allgenes <- unfactorize(crispr_allgenes)
+# crispr_signif_gene_allgenes <- WilcoxonTestDF(dataframe = crispr_allgenes, grouping = c("Drug", "Gene", "Drug_Gene"), type = "drug_gene", outfile = "./data_munging/rds/crispr_signif_g_allgenes.rds")
+# crispr_signif_lineage_allgenes <- WilcoxonTestDF(dataframe = crispr_allgenes, grouping =  c("Drug", "Gene", "disease", "Drug_Gene_Lin"), type = "drug_gene_lineage", outfile = "./data_munging/rds/crispr_signif_gl_allgenes.rds")
 ## G2P genes
@@
 crispr_signif_gene <- WilcoxonTestDF(dataframe = crispr, grouping = c("Drug", "Gene", "Drug_Gene"), type = "drug_gene", outfile = "./data_munging/rds/crispr_signif_g2p_g.rds")
-crispr_signif_lineage <- WilcoxonTestDF(dataframe = crispr, grouping =  c("Drug", "Gene", "disease", "Drug_Gene_Lin"), type = "drug_gene_lineage", outfile = "./data_munging/rds/crispr_signif_g2p_gl.rds")
+crispr_signif_lineage <- WilcoxonTestDF(dataframe = crispr, grouping =  c("Drug", "Gene", "disease", "Drug_Gene", "Drug_Gene_Lin"), type = "drug_gene_lineage", outfile = "./data_munging/rds/crispr_signif_g2p_gl.rds")
 
@@
 ## CRISPR: All genes
-crispr_prot_allgenes <- unfactorize(crispr_prot_allgenes)
-crispr_signif_prot_allgenes <- WilcoxonTestDF(dataframe = crispr_prot_allgenes, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change"), type = "protein_change", outfile = "./data_munging/rds/crispr_signif_protein_changes_allgenes.rds")
-crispr_signif_prot_lin_allgenes <- WilcoxonTestDF(dataframe = crispr_prot_allgenes, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change", "Drug_Gene_Protein_Change_Lineage", "disease"), type = "protein_change_lineage", outfile = "./data_munging/rds/crispr_signif_protein_changes_lineage_allgenes.rds")
+# crispr_prot_allgenes <- unfactorize(crispr_prot_allgenes)
+# crispr_signif_prot_allgenes <- WilcoxonTestDF(dataframe = crispr_prot_allgenes, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change"), type = "protein_change", outfile = "./data_munging/rds/crispr_signif_protein_changes_allgenes.rds")
+# crispr_signif_prot_lin_allgenes <- WilcoxonTestDF(dataframe = crispr_prot_allgenes, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change", "Drug_Gene_Protein_Change_Lineage", "disease"), type = "protein_change_lineage", outfile = "./data_munging/rds/crispr_signif_protein_changes_lineage_allgenes.rds")
 ## CRISPR: G2P genes
@@
 ## CRISPR: All genes
-crispr_fus_allgenes <- unfactorize(crispr_fus_allgenes)
-crispr_signif_fus_allgenes <- WilcoxonTestDF(dataframe = crispr_fus_allgenes, grouping = c("FusionPair", "Drug", "Drug_FusionPair", "Drug_Gene"), type = "fusion", outfile = "./data_munging/rds/crispr_signif_fusions_allgenes.rds")
-crispr_signif_fus_lin_allgenes <- WilcoxonTestDF(dataframe = crispr_fus_allgenes, grouping = c("Drug_Gene", "FusionPair", "Drug", "Drug_FusionPair", "Drug_Fusion_Lineage"), type = "fusion_lineage", outfile = "./data_munging/rds/crispr_signif_fusions_lineage_allgenes.rds")
+# crispr_fus_allgenes <- unfactorize(crispr_fus_allgenes)
+# crispr_signif_fus_allgenes <- WilcoxonTestDF(dataframe = crispr_fus_allgenes, grouping = c("FusionPair", "Drug", "Drug_FusionPair", "Drug_Gene"), type = "fusion", outfile = "./data_munging/rds/crispr_signif_fusions_allgenes.rds")
+# crispr_signif_fus_lin_allgenes <- WilcoxonTestDF(dataframe = crispr_fus_allgenes, grouping = c("Drug_Gene", "FusionPair", "Drug", "Drug_FusionPair", "Drug_Fusion_Lineage"), type = "fusion_lineage", outfile = "./data_munging/rds/crispr_signif_fusions_lineage_allgenes.rds")
 ## CRISPR: G2P genes\
 crispr_fus <- unfactorize(crispr_fus)
-crispr_signif_fus <- WilcoxonTestDF(dataframe = crispr_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair", "Drug_Gene"), type = "fusion", outfile = "./data_munging/rds/crispr_signif_fusions.rds")
-crispr_signif_fus_lin <- WilcoxonTestDF(dataframe = crispr_fus, grouping = c("Drug_Gene", "FusionPair", "Drug", "Drug_FusionPair", "Drug_Fusion_Lineage"), type = "fusion_lineage", outfile = "./data_munging/rds/crispr_signif_fusions_lineage.rds")
+crispr_signif_fus <- WilcoxonTestDF(dataframe = crispr_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair"), type = "fusion", outfile = "./data_munging/rds/crispr_signif_fusions.rds")
+crispr_signif_fus_lin <- WilcoxonTestDF(dataframe = crispr_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair", "disease", "Drug_Fusion_Lineage"), type = "fusion_lineage", outfile = "./data_munging/rds/crispr_signif_fusions_lineage.rds")
 ```
@@
 ```{r load_prot_wilcoxon_rds, eval=FALSE}
+crispr_signif_prot <- readRDS("./data_munging/rds/crispr_signif_protein_changes.rds") %>% filter(Change_Status_1_count >= 3)
+ccle_signif_prot <- readRDS("./data_munging/rds/ccle_signif_protein_changes.rds") %>% filter(Change_Status_1_count >= 3)
+ctrp_signif_prot <- readRDS("./data_munging/rds/ctrp_signif_protein_changes.rds") %>% filter(Change_Status_1_count >= 3)
+gdsc_signif_prot <- readRDS("./data_munging/rds/gdsc_signif_protein_changes.rds") %>% filter(Change_Status_1_count >= 3)
+
+gene_prots <- union(union(unique(ccle_signif_prot$Gene_Protein_Change), union(unique(ctrp_signif_prot$Gene_Protein_Change), unique(gdsc_signif_prot$Gene_Protein_Change))), unique(crispr_signif_prot$Gene_Protein_Change))
+
+# all_directions <- unique(rbind(select(crispr_prot, Gene_Protein_Change, Drug, Direction_Curated), select(ccle_prot, Gene_Protein_Change, Drug, Direction_Curated), select(ctrp_prot, Gene_Protein_Change, Drug, Direction_Curated), select(gdsc_prot, Gene_Protein_Change, Drug, Direction_Curated)))
+# all_directions <- filter(all_directions, !is.na(Direction_Curated))
+# saveRDS(all_directions, "./data_munging/rds/protein_changes_directions.rds")
+all_directions <- readRDS("./data_munging/rds/protein_changes_directions.rds")
+
+crispr_signif_prot_4plot <- merge(merge(merge(crispr_signif_prot, unique(select(crispr_prot, Drug, Gene_Protein_Change)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(crispr_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE), all_directions,  by = c("Drug", "Gene_Protein_Change"), all.x = TRUE)
+ccle_signif_prot_4plot <- merge(merge(merge(ccle_signif_prot, unique(select(ccle_prot, Drug, Gene_Protein_Change)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(ccle_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE), all_directions,  by = c("Drug", "Gene_Protein_Change"), all.x = TRUE)
+ctrp_signif_prot_4plot <- merge(merge(merge(ctrp_signif_prot, unique(select(ctrp_prot, Drug, Gene_Protein_Change)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(ctrp_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE), all_directions,  by = c("Drug", "Gene_Protein_Change"), all.x = TRUE)
+gdsc_signif_prot_4plot <- merge(merge(merge(gdsc_signif_prot, unique(select(gdsc_prot, Drug, Gene_Protein_Change)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(gdsc_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE), all_directions,  by = c("Drug", "Gene_Protein_Change"), all.x = TRUE)
+
+saveRDS(crispr_signif_prot_4plot, "./data_munging/rds/crispr_signif_protein_changes_4plot.rds")
+saveRDS(ccle_signif_prot_4plot, "./data_munging/rds/ccle_signif_protein_changes_4plot.rds")
+saveRDS(ctrp_signif_prot_4plot, "./data_munging/rds/ctrp_signif_protein_changes_4plot.rds")
+saveRDS(gdsc_signif_prot_4plot, "./data_munging/rds/gdsc_signif_protein_changes_4plot.rds")
+```
+
+```{r prot_munging}
 crispr_signif_prot <- readRDS("./data_munging/rds/crispr_signif_protein_changes.rds")
@@
 
-gene_prots <- union(union(unique(ccle_signif_prot$Gene_Protein_Change), union(unique(ctrp_signif_prot$Gene_Protein_Change), unique(gdsc_signif_prot$Gene_Protein_Change))), unique(crispr_signif_prot$Gene_Protein_Change))
-
-# all_directions <- unique(rbind(select(crispr_prot, Gene_Protein_Change, Drug, Direction_Curated), select(ccle_prot, Gene_Protein_Change, Drug, Direction_Curated), select(ctrp_prot, Gene_Protein_Change, Drug, Direction_Curated), select(gdsc_prot, Gene_Protein_Change, Drug, Direction_Curated)))
-# all_directions <- filter(all_directions, !is.na(Direction_Curated))
-# saveRDS(all_directions, "./data_munging/rds/protein_changes_directions.rds")
-all_directions <- readRDS("./data_munging/rds/protein_changes_directions.rds")
-
-crispr_signif_prot_4plot <- merge(merge(merge(crispr_signif_prot, unique(select(crispr_prot, Drug, Gene_Protein_Change)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(crispr_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE), all_directions,  by = c("Drug", "Gene_Protein_Change"), all.x = TRUE)
-ccle_signif_prot_4plot <- merge(merge(merge(ccle_signif_prot, unique(select(ccle_prot, Drug, Gene_Protein_Change)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(ccle_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE), all_directions,  by = c("Drug", "Gene_Protein_Change"), all.x = TRUE)
-ctrp_signif_prot_4plot <- merge(merge(merge(ctrp_signif_prot, unique(select(ctrp_prot, Drug, Gene_Protein_Change)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(ctrp_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE), all_directions,  by = c("Drug", "Gene_Protein_Change"), all.x = TRUE)
-gdsc_signif_prot_4plot <- merge(merge(merge(gdsc_signif_prot, unique(select(gdsc_prot, Drug, Gene_Protein_Change)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(gdsc_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE), all_directions,  by = c("Drug", "Gene_Protein_Change"), all.x = TRUE)
-
-saveRDS(crispr_signif_prot_4plot, "./data_munging/rds/crispr_signif_protein_changes_4plot.rds")
-saveRDS(ccle_signif_prot_4plot, "./data_munging/rds/ccle_signif_protein_changes_4plot.rds")
-saveRDS(ctrp_signif_prot_4plot, "./data_munging/rds/ctrp_signif_protein_changes_4plot.rds")
-saveRDS(gdsc_signif_prot_4plot, "./data_munging/rds/gdsc_signif_protein_changes_4plot.rds")
-```
-
-```{r prot_munging}
 crispr_signif_prot_4plot <- readRDS("./data_munging/rds/crispr_signif_protein_changes_4plot.rds")
@@
 ```{r load_fus_wilcoxon_rds}
-crispr_signif_fus_allgenes <- readRDS("./data_munging/rds/crispr_signif_fusions_allgenes.rds")
-crispr_signif_fus_lin_allgenes <- readRDS("./data_munging/rds/crispr_signif_fusions_lineage_allgenes.rds")
+# crispr_signif_fus_allgenes <- readRDS("./data_munging/rds/crispr_signif_fusions_allgenes.rds")
+# crispr_signif_fus_lin_allgenes <- readRDS("./data_munging/rds/crispr_signif_fusions_lineage_allgenes.rds")
 crispr_signif_fus <- readRDS("./data_munging/rds/crispr_signif_fusions.rds")
@@
 ## Boxplots
-
-```{r fig.width=10}
-ggplot(data = ccle_fus) + 
-  geom_boxplot(aes(x = disease, y = Score)) +
-
-```
 
@@
 ### Pancan
-
+**12/16 Need to make all heatmaps tomorrow**
 ```{r mut_heatmaps, eval=FALSE, fig.height=10, fig.width=3}
-ht_crispr <- MakeWilcoxonHeatmap(signif_df = filter(crispr_signif_g2p_g, Gene %in% unique(g2p_mut$Gene)), feature = "crispr", legend_title = "-log10(p-value)", legend_breaks = seq(0, 45, by = 9), row_names = TRUE, color = "darkorchid4", col_title = "", row_title_txt = "Genes", radius = 0.05)
+ht_crispr <- MakeWilcoxonHeatmap(signif_df = filter(crispr_signif_g2p_g, Gene %in% unique(g2p_mut$Gene) & Mutation_1_Count >= 3), feature = "crispr", legend_title = "-log10(p-value)", legend_breaks = seq(0, 45, by = 9), row_names = TRUE, color = "darkorchid4", col_title = "", row_title_txt = "Genes", radius = 0.05)
 png(filename = "./plots/manuscript/crispr_mut_heatmap.png", width = 3, height = 10, units = "in", res = 500)
@@
 
-ht_ccle <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "-log10(p-value)", legend_breaks = seq(0, 12, by = 3), row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Genes", radius = 0.04)
+ht_ccle <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_Count >= 3), feature = "mutation", legend_title = "-log10(p-value)", legend_breaks = seq(0, 12, by = 3), row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Genes", radius = 0.04)
 png(filename = "./plots/manuscript/ccle_mut_heatmap.png", width = 3, height = 10, units = "in", res = 500)
@@
 
-ht_ctrp <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "-log10(p-value)", legend_breaks = seq(0, 18, by = 3), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.0075)
+ht_ctrp <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_Count >= 3), feature = "mutation", legend_title = "-log10(p-value)", legend_breaks = seq(0, 18, by = 3), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.0075)
 png(filename = "./plots/manuscript/ctrp_mut_heatmap.png", width = 9.5, height = 10, units = "in", res = 500)
@@
 
-ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "CCLE -log10(p-value)          ", legend_breaks = seq(0, 12, by = 3), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Genes", radius = 0.023)
-ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "CTRP -log10(p-value)          ", legend_breaks = seq(0, 18, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.007)
-ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "GDSC -log10(p-value)          ", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes", radius = 0.011)
-ht_crispr2 <- MakeWilcoxonHeatmap(signif_df = filter(crispr_signif_g2p_g, Gene %in% unique(g2p_mut$Gene)), feature = "crispr", legend_title = "CRISPR -log10(p-value)", legend_breaks = seq(0, 45, by = 9), row_names = FALSE, color = "darkorchid4", col_title = "", row_title_txt = "Genes", radius = 0.15)
+ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_Count >= 3), feature = "mutation", legend_title = "CCLE -log10(p-value)          ", legend_breaks = seq(0, 12, by = 3), row_names = FALSE, color = "darkgreen", col_title = "", row_title_txt = "Genes", radius = 0.023)
+ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_Count >= 3), feature = "mutation", legend_title = "CTRP -log10(p-value)          ", legend_breaks = seq(0, 18, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.007)
+ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_Count >= 3), feature = "mutation", legend_title = "GDSC -log10(p-value)          ", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes", radius = 0.011)
+ht_crispr2 <- MakeWilcoxonHeatmap(signif_df = filter(crispr_signif_g2p_g, Gene %in% unique(g2p_mut$Gene) & Mutation_1_Count >= 3), feature = "crispr", legend_title = "CRISPR -log10(p-value)", legend_breaks = seq(0, 45, by = 9), row_names = TRUE, color = "darkorchid4", col_title = "", row_title_txt = "Genes", radius = 0.15)
 
@@
 
-ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot_4plot, feature = "protein changes", legend_title = "CCLE -log10(p-value)          ", legend_breaks = seq(0, 15, by = 3), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.021)
+ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot_4plot, feature = "protein changes", legend_title = "CCLE -log10(p-value)          ", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "darkgreen", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.021)
 ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot_4plot, feature = "protein changes", legend_title = "CTRP -log10(p-value)          ", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.0125)
 ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = gdsc_signif_prot_4plot, feature = "protein changes", legend_title = "GDSC -log10(p-value)          ", legend_breaks = seq(0, 8, by = 2), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.0125)
-ht_crispr2 <- MakeWilcoxonHeatmap(signif_df = crispr_signif_prot_4plot, feature = "protein changes CRISPR", legend_title = "CRISPR -log10(p-value)", legend_breaks = seq(0, 25, by = 5), row_names = FALSE, color = "darkorchid4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.135)
+ht_crispr2 <- MakeWilcoxonHeatmap(signif_df = crispr_signif_prot_4plot, feature = "protein changes CRISPR", legend_title = "CRISPR -log10(p-value)", legend_breaks = seq(0, 25, by = 5), row_names = TRUE, color = "darkorchid4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.135)
 
@@
 
-**10/25 Need to fix InG2P annots on CTRP data**
-**11/15 Need to fix direction annot on CRISPR!**
 ```{r fus_heatmaps, eval=FALSE}
@@
     if(lineage) {
-      df_count <- df %>% drop_na(TPM) %>% count(Drug, Gene, disease, Drug_Gene_Lin) %>% filter(n >= 3)
-      df <- filter(df, Drug_Gene_Lin %in% df_count$Drug_Gene_Lin)
-      res <- df %>% group_by(Drug, Gene, disease, Drug_Gene_Lin) %>%
+      df_count <- df %>% drop_na(TPM) %>% count(Drug, Gene, disease, Drug_Gene_Lin)
+      df_count_filt <- filter(df_count, n >= 3)
+      df_filt <- filter(df, Drug_Gene_Lin %in% df_count_filt$Drug_Gene_Lin)
+      res <- df_filt %>% group_by(Drug, Gene, disease, Drug_Gene_Lin) %>%
         summarize(GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs", exact = FALSE)$estimate,
@@
       res$InG2P <- ifelse(res$Drug_Gene_Lin %in% unique(as.character(g2p_expr$Drug_Gene_Lin[!is.na(g2p_expr$Drug_Gene_Lin)])), "Yes", "No")
+      res <- merge(res, df_count, by = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), all = TRUE)
     }
     if(!lineage) {
+      df_count <- df %>% drop_na(TPM) %>% count(Drug, Gene, Drug_Gene)
       res <- df %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(TPM) %>%
@@
       res$InG2P <- ifelse(res$Drug_Gene %in% unique(as.character(g2p_expr$Drug_Gene[!is.na(g2p_expr$Drug_Gene)])), "Yes", "No")
+      res <- merge(res, df_count, by = c("Drug", "Gene", "Drug_Gene"), all = TRUE)
     }
@@
     if(lineage) {
-      df_count <- df %>% drop_na(CN) %>% count(Drug, Gene, disease, Drug_Gene_Lin) %>% filter(n >= 3)
-      df <- filter(df, Drug_Gene_Lin %in% df_count$Drug_Gene_Lin)
-      res <- df %>% group_by(Drug, Gene, disease, Drug_Gene_Lin) %>%
+      df_count <- df %>% drop_na(CN) %>% count(Drug, Gene, disease, Drug_Gene_Lin)
+      df_count_filt <- filter(df_count, n >= 3)
+      df_filt <- filter(df, Drug_Gene_Lin %in% df_count_filt$Drug_Gene_Lin)
+      res <- df_filt %>% group_by(Drug, Gene, disease, Drug_Gene_Lin) %>%
         summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs", exact = FALSE)$estimate,
@@
       res$InG2P <- ifelse(res$Drug_Gene_Lin %in% unique(as.character(g2p_amp$Drug_Gene_Lin[!is.na(g2p_amp$Drug_Gene_Lin)])), "Yes", "No")
+      res <- merge(res, df_count, by = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), all = TRUE)
     }
     if(!lineage) {
+      df_count <- df %>% drop_na(CN) %>% count(Drug, Gene, Drug_Gene)
       res <- df %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(CN) %>%
@@
 ```{r spear_calc, warning=FALSE, eval=FALSE}
-# Ran this chunk on 12/3
 crispr_cn_res <- MakeSpearmanCorrDF(dataset = "CRISPR", df = crispr, metric = "CN", lineage = FALSE)
@@
 cn_cor_lin <- readRDS("./data_munging/rds/cn_cor_lineage.rds")
+cn_cor_lin_g2p <- filter(cn_cor_lin, InG2P == "Yes")
 ge_cor_lin <- readRDS("./data_munging/rds/ge_cor_lineage.rds")
+ge_cor_lin_g2p <- filter(ge_cor_lin, InG2P == "Yes")
 ```
@@
 
-```{r crispr_spear_eda, warning=FALSE}
+```{r crispr_spear_eda, warning=TRUE}
 crispr_spear_cn <- filter(cn_cor, Dataset == "CRISPR" & Gene %in% g2p_dg_genes)

### 2019-12-27 manuscript.Rmd

@@
 
+- summary paragraph
+- study limitations
+- future directions
+
 **NUMBERS WRONG HERE**
@@
 
-## Computational
-
-**12/4 EDIT THIS**
-```{r, include=FALSE}
-r_v <- paste0("v", getRversion())
-# rstudio_v <- paste0("v", RStudio.Version()$version)
-ggplot_v <- paste0("v", packageVersion("ggplot2"))
-ggpubr_v <- paste0("v", packageVersion("ggpubr"))
-```
-
-For *Figure 1*, all data were imported and manipulated using pandas (v0.23.0) [@mckinney2011] and plotted using seaborn (v0.90) [@waskom2012], which sat on top of matplotlib (v2.2.2) [@hunter2007] and was executed on Python (v2.7.15) (Python Software Foundation, https://www.python.org/) in an IPython (v5.5.0) [@perez2007] kernel within a localhost Jupyter (v5.2.2) notebook [@kluyver2016].
-All other analyses were conducted in R (`r r_v`) [@rdevelopmentcoreteam2010, https://www.R-project.org/] in an RStudio environment (v1.1.447) [@rstudio2012].
-All other plots were drawn using the ggplot2 (`r ggplot_v`) R package [@wickham2016].
-
-### Statistics
-
-**12/4 EDIT THIS**
-
-Wilcoxon tests were conducted using the `compare_means` function in the ggpubr (`r ggpubr_v`) R package [@kassambara2018].
-`compare_means` does Benjamini-Hochberg p-value adjustment using the `p.adjust` function from the `stats` base R package.
-
-For computing Spearman correlation coefficients, we used the `cor.test` function from the `stats` package.
-If there were 3 or fewer data points, then the correlation was not done and a value of `NA` was supplied.
-
 # Conflicts of interest?

### 2019-12-29 19Q2.Rmd

@@
 library(ggsignif)
+library(grid)
+library(gridExtra)
+library(gtable)
 library(jsonlite)
@@
 library(VennDiagram)
-
 theme_set(theme_light())
@@
 g2p$biomarker_type_curated <- ifelse(is.na(g2p$biomarker_type_curated), "None", as.character(g2p$biomarker_type_curated))
+g2p <- unfactorize(g2p)
 g2p_split <- filter(g2p, !is.na(Drug)) %>% split(g2p$biomarker_type_curated)
@@
     count_n <- dataframe %>% count(Drug_Gene, Mutation)
+    count_n_wide <- dcast(count_n, Drug_Gene ~ Mutation, value.var = "n", fill = 0) %>% separate(Drug_Gene, sep = "_", c("Drug", "Gene"), extra = "merge", remove = FALSE)
+    colnames(count_n_wide) <- c("Drug_Gene", "Drug", "Gene", "Mutation_0_count", "Mutation_1_count")
+    count_n_filt <- filter(count_n, n >= 3)
+    count_category <- count_n_filt %>% count(Drug_Gene) %>% filter(n == 2)
+    dg_keep <- intersect(count_n_filt$Drug_Gene, count_category$Drug_Gene)
+    dataframe <- filter(dataframe, Drug_Gene %in% dg_keep)
+    dataframe$Drug_Gene <- as.character(dataframe$Drug_Gene)
+    signif <- compare_means(Score ~ Mutation, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
+    signif <- adj_signif(signif, alpha = 0.05)
+    signif <- signif[order(signif$p),]
+    signif <- merge(signif, count_n_wide, by = grouping, all = TRUE)
+    signif$`n WT/mut` <- with(signif, paste0(Mutation_0_count, "/", Mutation_1_count))
+    if(is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- ifelse(signif$Drug_Gene %in% g2p_list, "Yes", "No") }
+    if(!is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- "No" }
+  }
+
+  # Mutation status and lineage
+  if(tolower(type) == "drug_gene_lineage") {
+    # Filter out DGLs with too few samples in at least one mutation status category
+    # Require at least 3 samples in each category to run the test, else filter out that DGL from testing df
+    count_n <- dataframe %>% count(Drug_Gene_Lin, Mutation)
+    count_n_wide <- dcast(count_n, Drug_Gene_Lin ~ Mutation, value.var = "n", fill = 0) %>% separate(Drug_Gene_Lin, sep = "_", c("Drug", "Gene", "disease"), extra = "merge", remove = FALSE)
+    colnames(count_n_wide) <- c("Drug_Gene_Lin", "Drug", "Gene", "disease", "Mutation_0_count", "Mutation_1_count")
+    count_n_wide <- add_column(count_n_wide, Drug_Gene = paste0(count_n_wide$Drug, "_", count_n_wide$Gene), .after = "Gene")
+    count_n_filt <- filter(count_n, n >= 3)
+    count_category <- count_n_filt %>% count(Drug_Gene_Lin) %>% filter(n == 2)
+    dg_keep <- intersect(count_n_filt$Drug_Gene_Lin, count_category$Drug_Gene_Lin)
+    dataframe <- filter(dataframe, Drug_Gene_Lin %in% dg_keep)
+    dataframe$Drug_Gene_Lin <- as.character(dataframe$Drug_Gene_Lin)
+    signif <- compare_means(Score ~ Mutation, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
+    signif <- adj_signif(signif, alpha = 0.05)
+    signif <- signif[order(signif$p),]
+    signif <- merge(signif, count_n_wide, by = grouping, all = TRUE)
+    signif$`n WT/mut` <- with(signif, paste0(Mutation_0_count, "/", Mutation_1_count))
+    if(is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- ifelse(signif$Drug_Gene_Lin %in% g2p_list, "Yes", "No") }
+    if(!is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- "No" }
+  }
+
+  # Protein changes
+  if(tolower(type) == "protein_change") {
+    # Filter out Gene:Protein_Changes with too few samples in at least one category
+    # Require at least 3 samples in each category to run the test, else filter out that Gene_Protein_Change from testing df
+    count_n <- dataframe %>% count(Drug_Gene_Protein_Change, Change_Status)
+    count_n_wide <- dcast(count_n, Drug_Gene_Protein_Change ~ Change_Status, value.var = "n", fill = 0) %>% separate(Drug_Gene_Protein_Change, sep = "_", c("Drug", "Gene_Protein_Change"), extra = "merge", remove = FALSE)
+    colnames(count_n_wide) <- c("Drug_Gene_Protein_Change", "Drug", "Gene_Protein_Change", "Change_Status_0_count", "Change_Status_1_count")
+    count_n_filt <- filter(count_n, n >= 3)
+    count_category <- count_n_filt %>% count(Drug_Gene_Protein_Change) %>% filter(n == 2)
+    dg_keep <- intersect(count_n_filt$Drug_Gene_Protein_Change, count_category$Drug_Gene_Protein_Change)
+    dataframe <- filter(dataframe, Drug_Gene_Protein_Change %in% dg_keep)
+    dataframe$Drug_Gene_Protein_Change <- as.character(dataframe$Drug_Gene_Protein_Change)
+    signif <- compare_means(Score ~ Change_Status, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
+    signif <- adj_signif(signif, alpha = 0.05)
+    signif <- signif[order(signif$p),]
+    signif <- merge(signif, count_n_wide, by = grouping, all = TRUE)
+    signif$`n WT/mut` <- with(signif, paste0(Change_Status_0_count, "/", Change_Status_1_count))
+    if(is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- ifelse(signif$Drug_Gene_Protein_Change %in% g2p_list, "Yes", "No") }
+    if(!is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- "No" }
+  }
+
+  # Protein changes and lineage
+  if(tolower(type) == "protein_change_lineage") {
+    # Filter out Gene:Protein_Changes with too few samples in at least one category
+    # Require at least 3 samples in each category to run the test, else filter out that Drug_Gene_Protein_Change_Lineage from testing df
+    count_n <- dataframe %>% count(Drug_Gene_Protein_Change_Lineage, Change_Status)
+    count_n_wide <- dcast(count_n, Drug_Gene_Protein_Change_Lineage ~ Change_Status, value.var = "n", fill = 0) %>% separate(Drug_Gene_Protein_Change_Lineage, sep = "_", c("Drug", "Gene_Protein_Change", "disease"), extra = "merge", remove = FALSE)
+    colnames(count_n_wide) <- c("Drug_Gene_Protein_Change_Lineage", "Drug", "Gene_Protein_Change", "disease", "Change_Status_0_count", "Change_Status_1_count")
+    count_n_wide <- add_column(count_n_wide, Drug_Gene_Protein_Change = paste0(count_n_wide$Drug, "_", count_n_wide$Gene_Protein_Change), .after = "Gene_Protein_Change")
+    count_n_filt <- filter(count_n, n >= 3)
+    count_category <- count_n_filt %>% count(Drug_Gene_Protein_Change_Lineage) %>% filter(n == 2)
+    dg_keep <- intersect(count_n_filt$Drug_Gene_Protein_Change_Lineage, count_category$Drug_Gene_Protein_Change_Lineage)
+    dataframe <- filter(dataframe, Drug_Gene_Protein_Change_Lineage %in% dg_keep)
+    dataframe$Drug_Gene_Protein_Change_Lineage <- as.character(dataframe$Drug_Gene_Protein_Change_Lineage)
+    signif <- compare_means(Score ~ Change_Status, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
+    signif <- adj_signif(signif, alpha = 0.05)
+    signif <- signif[order(signif$p),]
+    signif <- merge(signif, count_n_wide, by = grouping, all = TRUE)
+    signif$`n WT/mut` <- with(signif, paste0(Change_Status_0_count, "/", Change_Status_1_count))
+    if(is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- ifelse(signif$Drug_Gene_Protein_Change_Lineage %in% g2p_list, "Yes", "No") }
+    if(!is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- "No" }
+  }
+
+  # Fusions
+  if(tolower(type) == "fusion") {
+    # Filter out fusions with too few samples in at least one category
+    # Require at least 3 samples in each category to run the test, else filter out that Drug_FusionPair from testing df
+    count_n <- dataframe %>% count(Drug_FusionPair, Fusion_Status)
+    count_n_wide <- dcast(count_n, Drug_FusionPair ~ Fusion_Status, value.var = "n", fill = 0) %>% separate(Drug_FusionPair, sep = "_", c("Drug", "FusionPair"), extra = "merge", remove = FALSE)
+    colnames(count_n_wide) <- c("Drug_FusionPair", "Drug", "FusionPair", "Fusion_Status_0_count", "Fusion_Status_1_count")
+    count_n_filt <- filter(count_n, n >= 3)
+    count_category <- count_n_filt %>% count(Drug_FusionPair) %>% filter(n == 2)
+    dg_keep <- intersect(count_n_filt$Drug_FusionPair, count_category$Drug_FusionPair)
+    dataframe <- filter(dataframe, Drug_FusionPair %in% dg_keep)
+    dataframe$Drug_FusionPair <- as.character(dataframe$Drug_FusionPair)
+    signif <- compare_means(Score ~ Fusion_Status, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
+    signif <- adj_signif(signif, alpha = 0.05)
+    signif <- signif[order(signif$p),]
+    signif <- merge(signif, count_n_wide, by = grouping, all = TRUE)
+    signif$`n WT/mut` <- with(signif, paste0(Fusion_Status_0_count, "/", Fusion_Status_1_count))
+    if(is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- ifelse(signif$Drug_FusionPair %in% g2p_list, "Yes", "No")  }
+    if(!is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- "No" }
+  }
+
+  # Fusions and lineage
+  if(tolower(type) == "fusion_lineage") {
+    # Filter out fusions with too few samples in at least one category
+    # Require at least 3 samples in each category to run the test, else filter out that Drug_Fusion_Lineage from testing df
+    count_n <- dataframe %>% count(Drug_Fusion_Lineage, Fusion_Status)
+    count_n_wide <- dcast(count_n, Drug_Fusion_Lineage ~ Fusion_Status, value.var = "n", fill = 0) %>% separate(Drug_Fusion_Lineage, sep = "_", c("Drug", "FusionPair", "disease"), extra = "merge", remove = FALSE)
+    colnames(count_n_wide) <- c("Drug_Fusion_Lineage", "Drug", "FusionPair", "disease", "Fusion_Status_0_count", "Fusion_Status_1_count")
+    count_n_wide <- add_column(count_n_wide, Drug_FusionPair = paste0(count_n_wide$Drug, "_", count_n_wide$FusionPair), .after = "FusionPair")
+    count_n_filt <- filter(count_n, n >= 3)
+    count_category <- count_n_filt %>% count(Drug_Fusion_Lineage) %>% filter(n == 2)
+    dg_keep <- intersect(count_n_filt$Drug_Fusion_Lineage, count_category$Drug_Fusion_Lineage)
+    dataframe <- filter(dataframe, Drug_Fusion_Lineage %in% dg_keep)
+    dataframe$Drug_Fusion_Lineage <- as.character(dataframe$Drug_Fusion_Lineage)
+    signif <- compare_means(Score ~ Fusion_Status, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
+    signif <- adj_signif(signif, alpha = 0.05)
+    signif <- signif[order(signif$p),]
+    signif <- merge(signif, count_n_wide, by = grouping, all = TRUE)
+    signif$`n WT/mut` <- with(signif, paste0(Fusion_Status_0_count, "/", Fusion_Status_1_count))
+    if(is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- ifelse(signif$Drug_Fusion_Lineage %in% g2p_list, "Yes", "No") }
+    if(!is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- "No" }
+  }
+
+  # Direction (old)
+  if(tolower(type) == "direction") {
+    signif <- compare_means(Score ~ Direction_Grouper, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
+    signif <- adj_signif(signif, alpha = 0.05)
+    signif <- signif[order(signif$p),]
+  }
+
+  signif$p_log10 <- as.numeric(formatC(-log10(signif$p), digits = 3, format = "f"))
+  saveRDS(signif, outfile)
+  return(signif)
+}
+```
+
+## Mutation status
+
+NOTE: `tidyr` is now in version 1.0.0 and `unnest()` is deprecated.
+`unnest()` is used in `ggpubr` function `compare_means()`, so will get following error when running my custom `WilcoxonTestDF()` function.
+Output is still the same, but will want to update code/testing when `ggpubr` fixes `unnest()` usage.
+
+Error message: `cols` is now required. Please use `cols = c(p)`
+
+```{r testing, eval=FALSE}
+dataframe <- ccle_filt
+grouping = c("Drug", "Gene", "Drug_Gene")
+g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)]))
+outfile = "./data_munging/rds/ccle_signif_g2p_dg.rds"
+
+count_n <- dataframe %>% count(Drug_Gene, Mutation)
     count_n_wide <- dcast(count_n, Drug_Gene ~ Mutation, value.var = "n", fill = 0) %>% separate(Drug_Gene, sep = "_", c("Drug", "Gene"), remove = FALSE)
@@
     signif <- merge(signif, count_n_wide, by = grouping, all = TRUE)
+    signif$`n WT/mut` <- with(signif, paste0(Mutation_0_count, "/", Mutation_1_count))
     if(is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- ifelse(signif$Drug_Gene %in% g2p_list, "Yes", "No") }
     if(!is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- "No" }
-  }
-
-  # Mutation status and lineage
-  if(tolower(type) == "drug_gene_lineage") {
-    # Filter out DGLs with too few samples in at least one mutation status category
-    # Require at least 3 samples in each category to run the test, else filter out that DGL from testing df
+
+dataframe = ccle_filt
+grouping = c("Drug", "Gene", "Drug_Gene", "disease", "Drug_Gene_Lin")
+g2p_list = unique(as.character(g2p_mut$Drug_Gene_Lin[!is.na(g2p_mut$Drug_Gene_Lin)]))
+outfile = "./data_munging/rds/ccle_signif_g2p_dgl.rds"    
     count_n <- dataframe %>% count(Drug_Gene_Lin, Mutation)
-    count_n_wide <- dcast(count_n, Drug_Gene_Lin ~ Mutation, value.var = "n", fill = 0) %>% separate(Drug_Gene_Lin, sep = "_", c("Drug", "Gene", "disease"), remove = FALSE)
+    count_n_wide <- dcast(count_n, Drug_Gene_Lin ~ Mutation, value.var = "n", fill = 0) %>% separate(Drug_Gene_Lin, sep = "_", c("Drug", "Gene", "disease"), extra = "merge", remove = FALSE)
     colnames(count_n_wide) <- c("Drug_Gene_Lin", "Drug", "Gene", "disease", "Mutation_0_count", "Mutation_1_count")
@@
     signif <- merge(signif, count_n_wide, by = grouping, all = TRUE)
+    signif$`n WT/mut` <- with(signif, paste0(Mutation_0_count, "/", Mutation_1_count))
     if(is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- ifelse(signif$Drug_Gene_Lin %in% g2p_list, "Yes", "No") }
     if(!is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- "No" }
-  }
-
-  # Protein changes
-  if(tolower(type) == "protein_change") {
-    # Filter out Gene:Protein_Changes with too few samples in at least one category
-    # Require at least 3 samples in each category to run the test, else filter out that Gene_Protein_Change from testing df
-    count_n <- dataframe %>% count(Drug_Gene_Protein_Change, Change_Status)
-    count_n_wide <- dcast(count_n, Drug_Gene_Protein_Change ~ Change_Status, value.var = "n", fill = 0) %>% separate(Drug_Gene_Protein_Change, sep = "_", c("Drug", "Gene_Protein_Change"), remove = FALSE)
-    colnames(count_n_wide) <- c("Drug_Gene_Protein_Change", "Drug", "Gene_Protein_Change", "Change_Status_0_count", "Change_Status_1_count")
-    count_n_filt <- filter(count_n, n >= 3)
-    count_category <- count_n_filt %>% count(Drug_Gene_Protein_Change) %>% filter(n == 2)
-    dg_keep <- intersect(count_n_filt$Drug_Gene_Protein_Change, count_category$Drug_Gene_Protein_Change)
-    dataframe <- filter(dataframe, Drug_Gene_Protein_Change %in% dg_keep)
-    dataframe$Drug_Gene_Protein_Change <- as.character(dataframe$Drug_Gene_Protein_Change)
-    signif <- compare_means(Score ~ Change_Status, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
-    signif <- adj_signif(signif, alpha = 0.05)
-    signif <- signif[order(signif$p),]
-    signif <- merge(signif, count_n_wide, by = grouping, all = TRUE)
-    if(is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- ifelse(signif$Drug_Gene_Protein_Change %in% g2p_list, "Yes", "No") }
-    if(!is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- "No" }
-  }
-
-  # Protein changes and lineage
-  if(tolower(type) == "protein_change_lineage") {
-    # Filter out Gene:Protein_Changes with too few samples in at least one category
-    # Require at least 3 samples in each category to run the test, else filter out that Drug_Gene_Protein_Change_Lineage from testing df
-    count_n <- dataframe %>% count(Drug_Gene_Protein_Change_Lineage, Change_Status)
-    count_n_wide <- dcast(count_n, Drug_Gene_Protein_Change_Lineage ~ Change_Status, value.var = "n", fill = 0) %>% separate(Drug_Gene_Protein_Change_Lineage, sep = "_", c("Drug", "Gene_Protein_Change", "disease"), remove = FALSE)
-    colnames(count_n_wide) <- c("Drug_Gene_Protein_Change_Lineage", "Drug", "Gene_Protein_Change", "disease", "Change_Status_0_count", "Change_Status_1_count")
-    count_n_wide <- add_column(count_n_wide, Drug_Gene_Protein_Change = paste0(count_n_wide$Drug, "_", count_n_wide$Gene_Protein_Change), .after = "Gene_Protein_Change")
-    count_n_filt <- filter(count_n, n >= 3)
-    count_category <- count_n_filt %>% count(Drug_Gene_Protein_Change_Lineage) %>% filter(n == 2)
-    dg_keep <- intersect(count_n_filt$Drug_Gene_Protein_Change_Lineage, count_category$Drug_Gene_Protein_Change_Lineage)
-    dataframe <- filter(dataframe, Drug_Gene_Protein_Change_Lineage %in% dg_keep)
-    dataframe$Drug_Gene_Protein_Change_Lineage <- as.character(dataframe$Drug_Gene_Protein_Change_Lineage)
-    signif <- compare_means(Score ~ Change_Status, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
-    signif <- adj_signif(signif, alpha = 0.05)
-    signif <- signif[order(signif$p),]
-    signif <- merge(signif, count_n_wide, by = grouping, all = TRUE)
-    if(is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- ifelse(signif$Drug_Gene_Protein_Change_Lineage %in% g2p_list, "Yes", "No") }
-    if(!is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- "No" }
-  }
-
-  # Fusions
-  if(tolower(type) == "fusion") {
-    # Filter out fusions with too few samples in at least one category
-    # Require at least 3 samples in each category to run the test, else filter out that Drug_FusionPair from testing df
-    count_n <- dataframe %>% count(Drug_FusionPair, Fusion_Status)
-    count_n_wide <- dcast(count_n, Drug_FusionPair ~ Fusion_Status, value.var = "n", fill = 0) %>% separate(Drug_FusionPair, sep = "_", c("Drug", "FusionPair"), remove = FALSE)
-    colnames(count_n_wide) <- c("Drug_FusionPair", "Drug", "FusionPair", "Fusion_Status_0_count", "Fusion_Status_1_count")
-    count_n_filt <- filter(count_n, n >= 3)
-    count_category <- count_n_filt %>% count(Drug_FusionPair) %>% filter(n == 2)
-    dg_keep <- intersect(count_n_filt$Drug_FusionPair, count_category$Drug_FusionPair)
-    dataframe <- filter(dataframe, Drug_FusionPair %in% dg_keep)
-    dataframe$Drug_FusionPair <- as.character(dataframe$Drug_FusionPair)
-    signif <- compare_means(Score ~ Fusion_Status, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
-    signif <- adj_signif(signif, alpha = 0.05)
-    signif <- signif[order(signif$p),]
-    signif <- merge(signif, count_n_wide, by = grouping, all = TRUE)
-    if(is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- ifelse(signif$Drug_FusionPair %in% g2p_list, "Yes", "No")  }
-    if(!is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- "No" }
-  }
-
-  # Fusions and lineage
-  if(tolower(type) == "fusion_lineage") {
-    # Filter out fusions with too few samples in at least one category
-    # Require at least 3 samples in each category to run the test, else filter out that Drug_Fusion_Lineage from testing df
-    count_n <- dataframe %>% count(Drug_Fusion_Lineage, Fusion_Status)
-    count_n_wide <- dcast(count_n, Drug_Fusion_Lineage ~ Fusion_Status, value.var = "n", fill = 0) %>% separate(Drug_Fusion_Lineage, sep = "_", c("Drug", "FusionPair", "disease"), remove = FALSE)
-    colnames(count_n_wide) <- c("Drug_Fusion_Lineage", "Drug", "FusionPair", "disease", "Fusion_Status_0_count", "Fusion_Status_1_count")
-    count_n_wide <- add_column(count_n_wide, Drug_FusionPair = paste0(count_n_wide$Drug, "_", count_n_wide$FusionPair), .after = "FusionPair")
-    count_n_filt <- filter(count_n, n >= 3)
-    count_category <- count_n_filt %>% count(Drug_Fusion_Lineage) %>% filter(n == 2)
-    dg_keep <- intersect(count_n_filt$Drug_Fusion_Lineage, count_category$Drug_Fusion_Lineage)
-    dataframe <- filter(dataframe, Drug_Fusion_Lineage %in% dg_keep)
-    dataframe$Drug_Fusion_Lineage <- as.character(dataframe$Drug_Fusion_Lineage)
-    signif <- compare_means(Score ~ Fusion_Status, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
-    signif <- adj_signif(signif, alpha = 0.05)
-    signif <- signif[order(signif$p),]
-    signif <- merge(signif, count_n_wide, by = grouping, all = TRUE)
-    if(is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- ifelse(signif$Drug_Fusion_Lineage %in% g2p_list, "Yes", "No") }
-    if(!is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- "No" }
-  }
-
-  # Direction (old)
-  if(tolower(type) == "direction") {
-    signif <- compare_means(Score ~ Direction_Grouper, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
-    signif <- adj_signif(signif, alpha = 0.05)
-    signif <- signif[order(signif$p),]
-  }
-
-  signif$p_log10 <- as.numeric(formatC(-log10(signif$p), digits = 3, format = "f"))
-  saveRDS(signif, outfile)
-  return(signif)
-}
-```
-
-## Mutation status
+```
 
@@
 
-g2p_mut_summ_lin_crispr <- g2p_mut %>% count(Gene, disease, Direction_Curated) %>% select(-n)
+g2p_mut_summ_lin_crispr <- g2p_mut %>% count(Gene, disease, Direction_Curated) %>% drop_na(disease) %>% select(-n)
 g2p_mut_summ_lin_crispr_n <- g2p_mut_summ_lin_crispr %>% count(Gene, disease)
@@
 ```{r mut_heatmaps, eval=FALSE, fig.height=10, fig.width=3}
-ht_crispr <- MakeWilcoxonHeatmap(signif_df = filter(crispr_signif_g2p_g, Gene %in% unique(g2p_mut$Gene) & Mutation_1_Count >= 3), feature = "crispr", legend_title = "-log10(p-value)", legend_breaks = seq(0, 45, by = 9), row_names = TRUE, color = "darkorchid4", col_title = "", row_title_txt = "Genes", radius = 0.05)
+ht_crispr <- MakeWilcoxonHeatmap(signif_df = filter(crispr_signif_g2p_g, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "crispr", legend_title = "-log10(p-value)", legend_breaks = seq(0, 45, by = 9), row_names = TRUE, color = "darkorchid4", col_title = "", row_title_txt = "Genes", radius = 0.05)
 png(filename = "./plots/manuscript/crispr_mut_heatmap.png", width = 3, height = 10, units = "in", res = 500)
@@
 
-ht_ccle <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_Count >= 3), feature = "mutation", legend_title = "-log10(p-value)", legend_breaks = seq(0, 12, by = 3), row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Genes", radius = 0.04)
+ht_ccle <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "mutation", legend_title = "-log10(p-value)", legend_breaks = seq(0, 12, by = 3), row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Genes", radius = 0.04)
 png(filename = "./plots/manuscript/ccle_mut_heatmap.png", width = 3, height = 10, units = "in", res = 500)
@@
 
-ht_ctrp <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_Count >= 3), feature = "mutation", legend_title = "-log10(p-value)", legend_breaks = seq(0, 18, by = 3), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.0075)
+ht_ctrp <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "mutation", legend_title = "-log10(p-value)", legend_breaks = seq(0, 18, by = 3), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.0075)
 png(filename = "./plots/manuscript/ctrp_mut_heatmap.png", width = 9.5, height = 10, units = "in", res = 500)
@@
 
-ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_Count >= 3), feature = "mutation", legend_title = "CCLE -log10(p-value)          ", legend_breaks = seq(0, 12, by = 3), row_names = FALSE, color = "darkgreen", col_title = "", row_title_txt = "Genes", radius = 0.023)
-ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_Count >= 3), feature = "mutation", legend_title = "CTRP -log10(p-value)          ", legend_breaks = seq(0, 18, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.007)
-ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_Count >= 3), feature = "mutation", legend_title = "GDSC -log10(p-value)          ", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes", radius = 0.011)
-ht_crispr2 <- MakeWilcoxonHeatmap(signif_df = filter(crispr_signif_g2p_g, Gene %in% unique(g2p_mut$Gene) & Mutation_1_Count >= 3), feature = "crispr", legend_title = "CRISPR -log10(p-value)", legend_breaks = seq(0, 45, by = 9), row_names = TRUE, color = "darkorchid4", col_title = "", row_title_txt = "Genes", radius = 0.15)
+ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "mutation", legend_title = "CCLE -log10(p-value)          ", legend_breaks = seq(0, 12, by = 3), row_names = FALSE, color = "darkgreen", col_title = "", row_title_txt = "Genes", radius = 0.023)
+ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "mutation", legend_title = "CTRP -log10(p-value)          ", legend_breaks = seq(0, 18, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.007)
+ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "mutation", legend_title = "GDSC -log10(p-value)          ", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes", radius = 0.011)
+ht_crispr2 <- MakeWilcoxonHeatmap(signif_df = filter(crispr_signif_g2p_g, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "crispr", legend_title = "CRISPR -log10(p-value)", legend_breaks = seq(0, 45, by = 9), row_names = TRUE, color = "darkorchid4", col_title = "", row_title_txt = "Genes", radius = 0.15)
 
@@
 
+# FIGURES
+
+--------------------------------------------------------------------------------
+
+## Figure 3
+
+```{r Figure3, fig.height=12, fig.width=12, eval=FALSE}
+# A: Heatmap
+ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "mutation", legend_title = "CCLE -log10(p-value)          ", legend_breaks = seq(0, 12, by = 3), row_names = FALSE, color = "darkgreen", col_title = "", row_title_txt = "Genes", radius = 0.023)
+ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "mutation", legend_title = "CTRP -log10(p-value)          ", legend_breaks = seq(0, 18, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.007)
+ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "mutation", legend_title = "GDSC -log10(p-value)          ", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes", radius = 0.011)
+ht_crispr2 <- MakeWilcoxonHeatmap(signif_df = filter(crispr_signif_g2p_g, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "crispr", legend_title = "CRISPR -log10(p-value)", legend_breaks = seq(0, 45, by = 9), row_names = TRUE, color = "darkorchid4", col_title = "", row_title_txt = "Genes", radius = 0.15)
+ht_mut_list <- ht_crispr2 + ht_ccle2 + ht_ctrp2 + ht_gdsc2
+ht_mut_grob <- grid.grabExpr(draw(ht_mut_list, gap = unit(0.25, "in"), heatmap_legend_side = "right"))
+
+# B: CRISPR mutation status (agnostic)
+crispr_mut_tb <- tableGrob(crispr_signif_g2p_g %>% filter(Gene %in% unique(g2p_mut$Gene), p < 0.05) %>% select(Gene, p.format, `n WT/mut`), rows = NULL)
+crispr_mut_title <- textGrob("CRISPR", gp = gpar(fontsize = 20))
+padding <- unit(0.5, "line")
+crispr_mut_tb <- gtable_add_rows(crispr_mut_tb, heights = grobHeight(crispr_mut_title) + padding, pos = 0)
+crispr_mut_tb <- gtable_add_grob(crispr_mut_tb, list(crispr_mut_title), t = 1, l = 1, r = ncol(crispr_mut_tb))
+
+# C: Drug screen mutation status (agnostic)
+ccle_mut_df <- ccle_signif_g2p_dg %>% filter(InG2P == "Yes", p < 0.05) %>% select(Drug, Gene, p.format, `n WT/mut`)
+ccle_mut_df <- add_column(ccle_mut_df, .before = "Drug", Dataset = c("CCLE", rep("", nrow(ccle_mut_df) - 1)))
+ctrp_mut_df <- ctrp_signif_g2p_dg %>% filter(InG2P == "Yes", p < 0.05) %>% select(Drug, Gene, p.format, `n WT/mut`)
+ctrp_mut_df <- add_column(ctrp_mut_df, .before = "Drug", Dataset = c("CTRP", rep("", nrow(ctrp_mut_df) - 1)))
+gdsc_mut_df <- gdsc_signif_g2p_dg %>% filter(InG2P == "Yes", p < 0.05) %>% select(Drug, Gene, p.format, `n WT/mut`)
+gdsc_mut_df <- add_column(gdsc_mut_df, .before = "Drug", Dataset = c("GDSC", rep("", nrow(gdsc_mut_df) - 1)))
+mut_signif_tb <- tableGrob(rbind(ccle_mut_df, ctrp_mut_df, gdsc_mut_df), rows = NULL)
+drug_mut_signif_title <- textGrob("Drug screens", gp = gpar(fontsize = 20))
+padding <- unit(0.5, "line")
+mut_signif_tb <- gtable_add_rows(mut_signif_tb, heights = grobHeight(drug_mut_signif_title) + padding, pos = 0)
+mut_signif_tb <- gtable_add_grob(mut_signif_tb, list(drug_mut_signif_title), t = 1, l = 1, r = ncol(mut_signif_tb))
+
+# D: CRISPR mutation status (lineage)
+crispr_mut_lin_tb <- tableGrob(crispr_signif_lineage %>% filter(Gene %in% unique(g2p_mut$Gene), p < 0.05) %>% select(Gene, disease, p.format, `n WT/mut`), rows = NULL)
+crispr_mut_lin_tb <- gtable_add_rows(crispr_mut_lin_tb, heights = grobHeight(crispr_mut_title) + padding, pos = 0)
+crispr_mut_lin_tb <- gtable_add_grob(crispr_mut_lin_tb, list(crispr_mut_title), t = 1, l = 1, r = ncol(crispr_mut_lin_tb))
+
+# E: Drug screen mutation status (lineage)
+ccle_mut_lin_df <- ccle_signif_g2p_dgl %>% filter(InG2P == "Yes", p < 0.05) %>% select(Drug, Gene, disease, p.format, `n WT/mut`)
+ccle_mut_lin_df <- add_column(ccle_mut_lin_df, .before = "Drug", Dataset = c("CCLE", rep("", nrow(ccle_mut_lin_df) - 1)))
+ctrp_mut_lin_df <- ctrp_signif_g2p_dgl %>% filter(InG2P == "Yes", p < 0.05) %>% select(Drug, Gene, disease, p.format, `n WT/mut`)
+ctrp_mut_lin_df <- add_column(ctrp_mut_lin_df, .before = "Drug", Dataset = c("CTRP", rep("", nrow(ctrp_mut_lin_df) - 1)))
+gdsc_mut_lin_df <- gdsc_signif_g2p_dgl %>% filter(InG2P == "Yes", p < 0.05) %>% select(Drug, Gene, disease, p.format, `n WT/mut`)
+gdsc_mut_lin_df <- add_column(gdsc_mut_lin_df, .before = "Drug", Dataset = c("GDSC", rep("", nrow(gdsc_mut_lin_df) - 1)))
+mut_lin_signif_tb <- tableGrob(rbind(ccle_mut_lin_df, ctrp_mut_lin_df, gdsc_mut_lin_df), rows = NULL)
+mut_lin_signif_tb <- gtable_add_rows(mut_lin_signif_tb, heights = grobHeight(drug_mut_signif_title) + padding, pos = 0)
+mut_lin_signif_tb <- gtable_add_grob(mut_lin_signif_tb, list(drug_mut_signif_title), t = 1, l = 1, r = ncol(mut_lin_signif_tb))
+
+# F: Boxplots
+crispr_mut_filt <- filter(crispr, Gene %in% c("BRAF", "KRAS"))
+crispr_mut_filt_plot <- ggplot(data = crispr_mut_filt, mapping = aes(x = as.character(Mutation), y = Score)) +
+  facet_wrap(~ Gene) +
+  geom_violin() +
+  geom_boxplot(outlier.shape = NA, width = 0.07) +
+  stat_compare_means(method = "wilcox", comparisons = list(c("0", "1"))) +
+  labs(title = "CRISPR, lineage agnostic", x = "Mutation Status")
+
+ctrp_mut_filt <- filter(ctrp, Drug_Gene %in% c("afatinib_KRAS", "dabrafenib_BRAF"))
+ctrp_mut_filt_plot <- ggplot(data = ctrp_mut_filt, mapping = aes(x = as.character(Mutation), y = Score)) +
+  facet_wrap(~ Drug_Gene) +
+  geom_violin() +
+  geom_boxplot(outlier.shape = NA, width = 0.07) +
+  stat_compare_means(method = "wilcox", comparisons = list(c("0", "1"))) +
+  labs(title = "CTRP, lineage agnostic", x = "Mutation Status")
+
+crispr_mut_lin_filt <- filter(crispr, Drug_Gene_Lin %in% c("CRISPR_BRAF_skin", "CRISPR_KRAS_lung"))
+crispr_mut_lin_filt_plot <- ggplot(data = crispr_mut_lin_filt, mapping = aes(x = as.character(Mutation), y = Score)) +
+  facet_wrap(~ Drug_Gene_Lin) +
+  geom_violin() +
+  geom_boxplot(outlier.shape = NA, width = 0.07) +
+  stat_compare_means(method = "wilcox", comparisons = list(c("0", "1"))) +
+  labs(title = "CRISPR, skin", x = "Mutation Status")
+
+# Make figure
+A <- textGrob("A", hjust = 0, vjust = 1, gp = gpar(fontsize = 20, fontface = "bold"))
+space <- textGrob("")
+B <- textGrob("B", hjust = 0, vjust = 1, gp = gpar(fontsize = 20, fontface = "bold"))
+C <- textGrob("C", hjust = 0, vjust = 1, gp = gpar(fontsize = 20, fontface = "bold"))
+D <- textGrob("D", hjust = 0, vjust = 1, gp = gpar(fontsize = 20, fontface = "bold"))
+E <- textGrob("E", hjust = 0, vjust = 1, gp = gpar(fontsize = 20, fontface = "bold"))
+f <- textGrob("F", hjust = 0, vjust = 1, gp = gpar(fontsize = 20, fontface = "bold"))
+
+lay <- rbind(c(1, 2, 2, 2),
+             c(3, 3, 3, 3),
+             c(3, 3, 3, 3),
+             c(3, 3, 3, 3),
+             c(3, 3, 3, 3),
+             c(3, 3, 3, 3),
+             c(3, 3, 3, 3),
+             c(3, 3, 3, 3),
+             c(3, 3, 3, 3),
+             c(4, 5, 6, 7),
+             c(8, 9, 10, 11),
+             c(8, 9, 10, 11),
+             c(8, 9, 10, 11),
+             c(8, 9, 10, 11),
+             c(12, 2, 2, 2),
+             c(13, 13, 13, 13),
+             c(13, 13, 13, 13),
+             c(13, 13, 13, 13),
+             c(13, 13, 13, 13),
+             c(13, 13, 13, 13))
+
+png(filename = "./plots/manuscript/figure3.png", width = 25, height = 25, units = "in", res = 500)
+grid.arrange(A, space,
+             ht_mut_grob,
+             B, C, D, E,
+             crispr_mut_tb, mut_signif_tb, crispr_mut_lin_tb, mut_lin_signif_tb,
+             f,
+             arrangeGrob(ggplotGrob(crispr_mut_filt_plot),
+                         ggplotGrob(ctrp_mut_filt_plot),
+                         ggplotGrob(crispr_mut_lin_filt_plot),
+                         nrow = 1),
+             layout_matrix = lay)
+dev.off()
+```
+
 # OLD CODE

### 2020-01-03 19Q2.Rmd

@@
 g2p$biomarker_type_curated <- ifelse(is.na(g2p$biomarker_type_curated), "None", as.character(g2p$biomarker_type_curated))
-g2p <- unfactorize(g2p)
-g2p_split <- filter(g2p, !is.na(Drug)) %>% split(g2p$biomarker_type_curated)
+g2p <- unfactorize(g2p) %>% drop_na(Drug)
+g2p_split <- split(x = g2p, f = g2p$biomarker_type_curated)
+
 g2p_amp <- g2p_split[[1]]
+g2p_amp$Gene_Lin <- with(g2p_amp, paste0(Gene, "_", disease))
+
 g2p_expr <- g2p_split[[2]]
+g2p_expr$Gene_Lin <- with(g2p_expr, paste0(Gene, "_", disease))
+
 g2p_fus <- g2p_split[[3]]
@@
 g2p_fus$Drug_Fusion_Lineage <- ifelse(is.na(g2p_fus$Drug) | is.na(g2p_fus$FusionPair) | is.na(g2p_fus$disease), NA, paste0(g2p_fus$Drug, "_", g2p_fus$FusionPair, "_", g2p_fus$disease))
+g2p_fus$Fusion_Lineage <- ifelse(is.na(g2p_fus$FusionPair) | is.na(g2p_fus$disease), NA, paste0(g2p_fus$FusionPair, "_", g2p_fus$disease))
+
 g2p_mut <- g2p_split[[4]] %>% drop_na(Direction_Curated)
+g2p_mut$Gene_Lin <- paste0(g2p_mut$Gene, "_", g2p_mut$disease)
 g2p_mut_genes <- unique(sapply(strsplit(as.character(g2p_mut$Drug_Gene)[!is.na(g2p_mut$Drug_Gene)], "_", fixed = TRUE), function(x) x[2]))
 
-g2p_prot <- unique(filter(g2p, !is.na(Gene_Protein_Change) & !is.na(Drug)) %>% select(disease, Drug, Direction_Curated, Gene, Protein_Change, Gene_Protein_Change))
+g2p_prot <- unique(filter(g2p_mut, !is.na(Gene_Protein_Change) & !is.na(Drug)) %>% select(disease, Drug, Direction_Curated, Gene, Protein_Change, Gene_Protein_Change))
 g2p_prot$Drug_Gene_Protein_Change <- with(g2p_prot, ifelse(is.na(Drug) | is.na(Gene_Protein_Change), NA, paste0(Drug, "_", Gene_Protein_Change)))
 g2p_prot$Drug_Gene_Protein_Change_Lineage <- with(g2p_prot, ifelse(is.na(Drug) | is.na(Gene_Protein_Change) | is.na(disease), NA, paste0(Drug, "_", Gene_Protein_Change, "_", disease)))
+g2p_prot$Gene_Protein_Change_Lineage <- with(g2p_prot, ifelse(is.na(Gene_Protein_Change) | is.na(disease), NA, paste0(Gene_Protein_Change, "_", disease)))
 
@@
     print(paste0("Processing ", database, " data."))
-
     grid <- expand.grid("Cell_line" = unique(dataframe$Cell_line), "Gene" = gene_list)
@@
     print("Merged grid.")
-    # Merge metadata
-    ## Add columns for G2P drug-gene and drug-gene-lineage sorting
-    data$Drug_Gene <- paste0(data$Drug, "_", data$Gene)
-    data$G2P_Drug_Gene <- ifelse(data$Drug_Gene %in% g2p_dg, "Yes", "No")
-    data$Drug_Gene_Lin <- paste0(data$Drug, "_", data$Gene, "_", data$disease)
-    data$G2P_Drug_Gene_Lin <- ifelse(data$Drug_Gene_Lin %in% g2p_dgl, "Yes", "No")
-    print("Merged metadata.")
     # Merge mutation calls
@@
     data$Drug <- "CRISPR"
-    data$Drug_Gene <- paste0(data$Drug, "_", data$Gene)
-    data$G2P_Drug_Gene <- "No"
-    data$Drug_Gene_Lin <- paste0(data$Drug, "_", data$Gene, "_", data$disease)
-    data$G2P_Drug_Gene_Lin <- "No"
     print("Merged metadata.")
@@
 crispr <- readRDS("./data_munging/19Q2/crispr_data_19Q2.rds") %>% drop_na(Gene)
+crispr$Gene_Lin <- with(crispr, paste0(Gene, "_", disease))
 ```
@@
     if(is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- ifelse(signif$Drug_Gene %in% g2p_list, "Yes", "No") }
-    if(!is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- "No" }
+    if(!is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- ifelse(signif$Gene %in% g2p_list, "Yes", "No") }
   }
@@
     count_n_wide <- add_column(count_n_wide, Drug_Gene = paste0(count_n_wide$Drug, "_", count_n_wide$Gene), .after = "Gene")
+    count_n_wide <- add_column(count_n_wide, Gene_Lin = paste0(count_n_wide$Gene, "_", count_n_wide$disease), .after = "Drug_Gene")
     count_n_filt <- filter(count_n, n >= 3)
@@
     if(is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- ifelse(signif$Drug_Gene_Lin %in% g2p_list, "Yes", "No") }
-    if(!is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- "No" }
+    if(!is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- ifelse(signif$Gene_Lin %in% g2p_list, "Yes", "No") }
   }
@@
     if(is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- ifelse(signif$Drug_Gene_Protein_Change %in% g2p_list, "Yes", "No") }
-    if(!is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- "No" }
+    if(!is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- ifelse(signif$Gene_Protein_Change %in% g2p_list, "Yes", "No")  }
   }
@@
     count_n_wide <- add_column(count_n_wide, Drug_Gene_Protein_Change = paste0(count_n_wide$Drug, "_", count_n_wide$Gene_Protein_Change), .after = "Gene_Protein_Change")
+    count_n_wide <- add_column(count_n_wide, Gene_Protein_Change_Lineage = paste0(count_n_wide$Gene_Protein_Change, "_", count_n_wide$disease), .after = "Drug_Gene_Protein_Change")
     count_n_filt <- filter(count_n, n >= 3)
@@
     if(is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- ifelse(signif$Drug_Gene_Protein_Change_Lineage %in% g2p_list, "Yes", "No") }
-    if(!is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- "No" }
+    if(!is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- ifelse(signif$Gene_Protein_Change_Lineage %in% g2p_list, "Yes", "No") }
   }
@@
     if(is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- ifelse(signif$Drug_FusionPair %in% g2p_list, "Yes", "No") }
-    if(!is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- "No" }
+    if(!is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- ifelse(signif$FusionPair %in% g2p_list, "Yes", "No")  }
   }
@@
     count_n_wide <- add_column(count_n_wide, Drug_FusionPair = paste0(count_n_wide$Drug, "_", count_n_wide$FusionPair), .after = "FusionPair")
+    count_n_wide <- add_column(count_n_wide, Fusion_Lineage = paste0(count_n_wide$FusionPair, "_", count_n_wide$disease), .after = "Drug_FusionPair")
     count_n_filt <- filter(count_n, n >= 3)
@@
     if(is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- ifelse(signif$Drug_Fusion_Lineage %in% g2p_list, "Yes", "No") }
-    if(!is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- "No" }
+    if(!is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- ifelse(signif$Fusion_Lineage %in% g2p_list, "Yes", "No") }
   }
@@
 ```{r protein_change_data}
-ccle_prot <- filter(prot, Database == "CCLE")
+ccle_prot <- filter(prot, Database == "CCLE" & Drug %in% g2p_drugs)
 ccle_prot <- unfactorize(ccle_prot)
@@
 
-ctrp_prot <- filter(prot, Database == "CTRP")
+ctrp_prot <- filter(prot, Database == "CTRP" & Drug %in% g2p_drugs)
 ctrp_prot <- unfactorize(ctrp_prot)
@@
 
-gdsc_prot <- filter(prot, Database == "GDSC")
+gdsc_prot <- filter(prot, Database == "GDSC" & Drug %in% g2p_drugs)
 gdsc_prot <- unfactorize(gdsc_prot)
@@
 ```{r fus_wilcoxon_tests, eval=FALSE}
-ccle_signif_fus <- WilcoxonTestDF(dataframe = ccle_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair"), g2p_list = unique(as.character(g2p_fus$Drug_FusionPair[!is.na(g2p_fus$Drug_FusionPair)])), type = "fusion", outfile = "./data_munging/rds/ccle_signif_fusions.rds")
-ccle_signif_fus_lin <- WilcoxonTestDF(dataframe = ccle_fus, grouping = c("FusionPair", "Drug", "disease", "Drug_FusionPair", "Drug_Fusion_Lineage"), g2p_list = unique(as.character(g2p_fus$Drug_Fusion_Lineage[!is.na(g2p_fus$Drug_Fusion_Lineage)])), type = "fusion_lineage", outfile = "./data_munging/rds/ccle_signif_fusions_lineage.rds")
-
-ctrp_signif_fus <- WilcoxonTestDF(dataframe = ctrp_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair"), g2p_list = unique(as.character(g2p_fus$Drug_FusionPair[!is.na(g2p_fus$Drug_FusionPair)])), type = "fusion", outfile = "./data_munging/rds/ctrp_signif_fusions.rds")
-ctrp_signif_fus_lin<- WilcoxonTestDF(dataframe = ctrp_fus, grouping = c("FusionPair", "Drug", "disease", "Drug_FusionPair", "Drug_Fusion_Lineage"), g2p_list = unique(as.character(g2p_fus$Drug_Fusion_Lineage[!is.na(g2p_fus$Drug_Fusion_Lineage)])), type = "fusion_lineage", outfile = "./data_munging/rds/ctrp_signif_fusions_lineage.rds")
-
-gdsc_signif_fus <- WilcoxonTestDF(dataframe = gdsc_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair"), g2p_list = unique(as.character(g2p_fus$Drug_FusionPair[!is.na(g2p_fus$Drug_FusionPair)])), type = "fusion", outfile = "./data_munging/rds/gdsc_signif_fusions.rds")
-gdsc_signif_fus_lin <- WilcoxonTestDF(dataframe = gdsc_fus, grouping = c("FusionPair", "Drug", "disease", "Drug_FusionPair", "Drug_Fusion_Lineage"), g2p_list = unique(as.character(g2p_fus$Drug_Fusion_Lineage[!is.na(g2p_fus$Drug_Fusion_Lineage)])), type = "fusion_lineage", outfile = "./data_munging/rds/gdsc_signif_fusions_lineage.rds")
+ccle_signif_fus <- WilcoxonTestDF(dataframe = filter(ccle_fus, Drug %in% g2p_drugs), grouping = c("FusionPair", "Drug", "Drug_FusionPair"), g2p_list = unique(as.character(g2p_fus$Drug_FusionPair[!is.na(g2p_fus$Drug_FusionPair)])), type = "fusion", outfile = "./data_munging/rds/ccle_signif_fusions.rds")
+ccle_signif_fus_lin <- WilcoxonTestDF(dataframe = filter(ccle_fus, Drug %in% g2p_drugs), grouping = c("FusionPair", "Drug", "disease", "Drug_FusionPair", "Drug_Fusion_Lineage"), g2p_list = unique(as.character(g2p_fus$Drug_Fusion_Lineage[!is.na(g2p_fus$Drug_Fusion_Lineage)])), type = "fusion_lineage", outfile = "./data_munging/rds/ccle_signif_fusions_lineage.rds")
+
+ctrp_signif_fus <- WilcoxonTestDF(dataframe = filter(ctrp_fus, Drug %in% g2p_drugs), grouping = c("FusionPair", "Drug", "Drug_FusionPair"), g2p_list = unique(as.character(g2p_fus$Drug_FusionPair[!is.na(g2p_fus$Drug_FusionPair)])), type = "fusion", outfile = "./data_munging/rds/ctrp_signif_fusions.rds")
+ctrp_signif_fus_lin<- WilcoxonTestDF(dataframe = filter(ctrp_fus, Drug %in% g2p_drugs), grouping = c("FusionPair", "Drug", "disease", "Drug_FusionPair", "Drug_Fusion_Lineage"), g2p_list = unique(as.character(g2p_fus$Drug_Fusion_Lineage[!is.na(g2p_fus$Drug_Fusion_Lineage)])), type = "fusion_lineage", outfile = "./data_munging/rds/ctrp_signif_fusions_lineage.rds")
+
+gdsc_signif_fus <- WilcoxonTestDF(dataframe = filter(gdsc_fus, Drug %in% g2p_drugs), grouping = c("FusionPair", "Drug", "Drug_FusionPair"), g2p_list = unique(as.character(g2p_fus$Drug_FusionPair[!is.na(g2p_fus$Drug_FusionPair)])), type = "fusion", outfile = "./data_munging/rds/gdsc_signif_fusions.rds")
+gdsc_signif_fus_lin <- WilcoxonTestDF(dataframe = filter(gdsc_fus, Drug %in% g2p_drugs), grouping = c("FusionPair", "Drug", "disease", "Drug_FusionPair", "Drug_Fusion_Lineage"), g2p_list = unique(as.character(g2p_fus$Drug_Fusion_Lineage[!is.na(g2p_fus$Drug_Fusion_Lineage)])), type = "fusion_lineage", outfile = "./data_munging/rds/gdsc_signif_fusions_lineage.rds")
 ```
@@
 crispr <- unfactorize(crispr)
-crispr_signif_gene <- WilcoxonTestDF(dataframe = crispr, grouping = c("Drug", "Gene", "Drug_Gene"), type = "drug_gene", outfile = "./data_munging/rds/crispr_signif_g2p_g.rds")
-crispr_signif_lineage <- WilcoxonTestDF(dataframe = crispr, grouping =  c("Drug", "Gene", "disease", "Drug_Gene", "Drug_Gene_Lin"), type = "drug_gene_lineage", outfile = "./data_munging/rds/crispr_signif_g2p_gl.rds")
+crispr_signif_gene <- WilcoxonTestDF(dataframe = crispr, grouping = c("Drug", "Gene", "Drug_Gene"), type = "drug_gene", g2p_list = unique(as.character(g2p_mut$Gene[!is.na(g2p_mut$Gene)])), outfile = "./data_munging/rds/crispr_signif_g2p_g.rds")
+crispr_signif_lineage <- WilcoxonTestDF(dataframe = crispr, grouping =  c("Drug", "Gene", "disease", "Drug_Gene", "Drug_Gene_Lin"), type = "drug_gene_lineage", g2p_list = unique(as.character(g2p_mut$Gene_Lin[!is.na(g2p_mut$Gene_Lin)])), outfile = "./data_munging/rds/crispr_signif_g2p_gl.rds")
 
@@
 crispr_prot <- unfactorize(crispr_prot)
-crispr_signif_prot <- WilcoxonTestDF(dataframe = crispr_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change"), type = "protein_change", outfile = "./data_munging/rds/crispr_signif_protein_changes.rds")
-crispr_signif_prot_lin <- WilcoxonTestDF(dataframe = crispr_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change", "Drug_Gene_Protein_Change_Lineage", "disease"), type = "protein_change_lineage", outfile = "./data_munging/rds/crispr_signif_protein_changes_lineage.rds")
+crispr_signif_prot <- WilcoxonTestDF(dataframe = crispr_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change"), type = "protein_change", g2p_list = unique(as.character(g2p_prot$Gene_Protein_Change[!is.na(g2p_prot$Gene_Protein_Change)])), outfile = "./data_munging/rds/crispr_signif_protein_changes.rds")
+crispr_signif_prot_lin <- WilcoxonTestDF(dataframe = crispr_prot, grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change", "Drug_Gene_Protein_Change_Lineage", "disease"), type = "protein_change_lineage", g2p_list = unique(as.character(g2p_prot$Gene_Protein_Change_Lineage[!is.na(g2p_prot$Gene_Protein_Change_Lineage)])), outfile = "./data_munging/rds/crispr_signif_protein_changes_lineage.rds")
 
@@
 crispr_fus <- unfactorize(crispr_fus)
-crispr_signif_fus <- WilcoxonTestDF(dataframe = crispr_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair"), type = "fusion", outfile = "./data_munging/rds/crispr_signif_fusions.rds")
-crispr_signif_fus_lin <- WilcoxonTestDF(dataframe = crispr_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair", "disease", "Drug_Fusion_Lineage"), type = "fusion_lineage", outfile = "./data_munging/rds/crispr_signif_fusions_lineage.rds")
+crispr_signif_fus <- WilcoxonTestDF(dataframe = crispr_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair"), type = "fusion", g2p_list = unique(as.character(g2p_fus$FusionPair[!is.na(g2p_fus$FusionPair)])), outfile = "./data_munging/rds/crispr_signif_fusions.rds")
+crispr_signif_fus_lin <- WilcoxonTestDF(dataframe = crispr_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair", "disease", "Drug_Fusion_Lineage"), type = "fusion_lineage", g2p_list = unique(as.character(g2p_fus$Fusion_Lineage[!is.na(g2p_fus$Fusion_Lineage)])), outfile = "./data_munging/rds/crispr_signif_fusions_lineage.rds")
 ```
@@
 
-crispr_signif_allgenes <- readRDS("./data_munging/rds/crispr_signif_g_allgenes.rds")
-crispr_signif_lin_allgenes <- readRDS("./data_munging/rds/crispr_signif_gl_allgenes.rds")
+# crispr_signif_allgenes <- readRDS("./data_munging/rds/crispr_signif_g_allgenes.rds")
+# crispr_signif_lin_allgenes <- readRDS("./data_munging/rds/crispr_signif_gl_allgenes.rds")
 ```
@@
 
-ccle_signif_prot_lin %>% count(InG2P)
-filter(ccle_signif_prot_lin, InG2P == "Yes" & p < 0.05) %>% select(Drug, Gene_Protein_Change, disease, p.short, Direction_Curated)
-ctrp_signif_prot_lin %>% count(InG2P)
-filter(ctrp_signif_prot_lin, InG2P == "Yes" & p < 0.05) %>% select(Drug, Gene_Protein_Change, disease, p.short, Direction_Curated)
-gdsc_signif_prot_lin %>% count(InG2P)
-filter(gdsc_signif_prot_lin, InG2P == "Yes" & p < 0.05) %>% select(Drug, Gene_Protein_Change, disease, p.short, Direction_Curated)
+# ccle_signif_prot_lin %>% count(InG2P)
+# filter(ccle_signif_prot_lin, InG2P == "Yes" & p < 0.05) %>% select(Drug, Gene_Protein_Change, disease, p.short, Direction_Curated)
+# ctrp_signif_prot_lin %>% count(InG2P)
+# filter(ctrp_signif_prot_lin, InG2P == "Yes" & p < 0.05) %>% select(Drug, Gene_Protein_Change, disease, p.short, Direction_Curated)
+# gdsc_signif_prot_lin %>% count(InG2P)
+# filter(gdsc_signif_prot_lin, InG2P == "Yes" & p < 0.05) %>% select(Drug, Gene_Protein_Change, disease, p.short, Direction_Curated)
 ```
@@
 crispr_fus_filt <- filter(crispr_fus, FusionPair %in% c("ABL1-BCR", "BCR-ABL1", "PML-PARA") & Drug_Gene %in% c("CRISPR_ABL1"))
-crispr_signif_fus_filt <- filter(crispr_signif_fus, FusionPair %in% c("ABL1-BCR", "BCR-ABL1", "PML-PARA") & Drug_Gene %in% c("CRISPR_ABL1"))
+crispr_signif_fus_filt <- filter(crispr_signif_fus, FusionPair %in% c("ABL1-BCR", "BCR-ABL1", "PML-PARA"))
 
@@
 ctrp_fus_filt$Drug_f <- factor(ctrp_fus_filt$Drug, levels = intersect(g2p_drug_order, unique(ctrp_fus$Drug)))
-ctrp_signif_fus_filt <- filter(ctrp_signif_fus, Drug %in% g2p_drugs)
+ctrp_signif_fus_filt <- filter(ctrp_signif_fus, FusionPair %in% c("ABL1-BCR", "BCR-ABL1") & Drug %in% g2p_drugs)
 ctrp_signif_fus_filt$Drug_f <- factor(ctrp_signif_fus_filt$Drug, levels = intersect(g2p_drug_order, unique(ctrp_signif_fus$Drug)))
@@
 gdsc_fus_filt$Drug_f <- factor(gdsc_fus_filt$Drug, levels = intersect(g2p_drug_order, unique(gdsc_fus$Drug)))
-gdsc_signif_fus_filt <- filter(gdsc_signif_fus, Drug %in% g2p_drugs)
+gdsc_signif_fus_filt <- filter(gdsc_signif_fus, FusionPair %in% c("ABL1-BCR", "BCR-ABL1") & Drug %in% g2p_drugs)
 gdsc_signif_fus_filt$Drug_f <- factor(gdsc_signif_fus_filt$Drug, levels = intersect(g2p_drug_order, unique(gdsc_signif_fus$Drug)))
@@
       signif_grid <- signif_grid[, intersect(g2p_drug_order, colnames(signif_grid))]
-      signif_grid <- signif_grid[complete.cases(signif_grid), ]
 
@@
       print("Making CRISPR fusions grid and annotation dataframes.")
-      signif_grid <- dcast(signif_df, FusionPair ~ Drug_Gene, value.var = "p_log10", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-FusionPair)
+      signif_grid <- dcast(signif_df, FusionPair ~ Drug, value.var = "p_log10", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-FusionPair)
 
@@
 ### Pancan
-**12/16 Need to make all heatmaps tomorrow**
+
 ```{r mut_heatmaps, eval=FALSE, fig.height=10, fig.width=3}
@@
 ```{r fus_heatmaps, eval=FALSE}
-ht_crispr <- MakeWilcoxonHeatmap(signif_df = filter(crispr_signif_fus, Drug_Gene == "CRISPR_ABL1" & FusionPair %in% c("BCR-ABL1", "ABL1-BCR")), feature = "fusion crispr", legend_title = "-log10(p-value)",  legend_breaks = seq(0, 2, by = 0.5), row_names = TRUE, color = "darkorchid4", col_title = "Drugs", row_title_txt = "Fusion Pairs", radius = 0.5)
+ht_crispr <- MakeWilcoxonHeatmap(signif_df = filter(crispr_signif_fus, FusionPair %in% c("BCR-ABL1", "ABL1-BCR")), feature = "fusion crispr", legend_title = "-log10(p-value)",  legend_breaks = seq(0, 2, by = 0.5), row_names = TRUE, color = "darkorchid4", col_title = "Drugs", row_title_txt = "Fusion Pairs", radius = 0.5)
 png(filename = "./plots/manuscript/crispr_fus_heatmap.png", width = 3, height = 3, units = "in", res = 500)
@@
 
-ht_ccle <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "-log10(p-value)",  legend_breaks = seq(0, 4, by = 1), row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Fusion Pairs", radius = 0.01)
+ht_ccle <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_fus, FusionPair %in% c("BCR-ABL1", "ABL1-BCR") & Drug %in% g2p_drugs), feature = "fusion", legend_title = "-log10(p-value)",  legend_breaks = seq(0, 4, by = 1), row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Fusion Pairs", radius = 0.01)
 png(filename = "./plots/manuscript/ccle_fus_heatmap.png", width = 5, height = 3, units = "in", res = 500)
@@
 
-ht_ctrp <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "-log10(p-value)", legend_breaks = seq(0, 10, by = 2), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Fusion Pairs", radius = 0.01)
+ht_ctrp <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_fus, FusionPair %in% c("BCR-ABL1", "ABL1-BCR") & Drug %in% g2p_drugs), feature = "fusion", legend_title = "-log10(p-value)", legend_breaks = seq(0, 10, by = 2), row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Fusion Pairs", radius = 0.01)
 png(filename = "./plots/manuscript/ctrp_fus_heatmap.png", width = 13, height = 3, units = "in", res = 500)
@@
 
-ht_gdsc <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "-log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Fusion Pairs", radius = 0.01)
+ht_gdsc <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_fus, FusionPair %in% c("BCR-ABL1", "ABL1-BCR") & Drug %in% g2p_drugs), feature = "fusion", legend_title = "-log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Fusion Pairs", radius = 0.01)
 png(filename = "./plots/manuscript/gdsc_fus_heatmap.png", width = 9, height = 3, units = "in", res = 500)
@@
 
-ht_crispr2 <- MakeWilcoxonHeatmap(signif_df = filter(crispr_signif_fus, Drug_Gene == "CRISPR_ABL1" & FusionPair %in% c("BCR-ABL1", "ABL1-BCR")), feature = "fusion crispr", legend_title = "CRISPR -log10(p-value)          ",  legend_breaks = seq(0, 2, by = 0.5), row_names = TRUE, color = "darkorchid4", col_title = "", row_title_txt = "Fusion Pairs", radius = 0.15)
-ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "CCLE -log10(p-value)          ", legend_breaks = seq(0, 4, by = 1), row_names = FALSE, color = "darkgreen", col_title = "", row_title_txt = "Fusion Pairs", radius = 0.15)
-ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "CTRP -log10(p-value)          ", legend_breaks = seq(0, 10, by = 2), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Fusion Pairs", radius = 0.08)
-ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Fusion Pairs", radius = 0.08)
+ht_crispr2 <- MakeWilcoxonHeatmap(signif_df = filter(crispr_signif_fus, FusionPair %in% c("BCR-ABL1", "ABL1-BCR")), feature = "fusion crispr", legend_title = "CRISPR -log10(p-value)          ",  legend_breaks = seq(0, 2, by = 0.5), row_names = TRUE, color = "darkorchid4", col_title = "", row_title_txt = "Fusion Pairs", radius = 0.15)
+ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_fus, FusionPair %in% c("BCR-ABL1", "ABL1-BCR") & Drug %in% g2p_drugs), feature = "fusion", legend_title = "CCLE -log10(p-value)          ", legend_breaks = seq(0, 4, by = 1), row_names = FALSE, color = "darkgreen", col_title = "", row_title_txt = "Fusion Pairs", radius = 0.15)
+ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_fus, FusionPair %in% c("BCR-ABL1", "ABL1-BCR") & Drug %in% g2p_drugs), feature = "fusion", legend_title = "CTRP -log10(p-value)          ", legend_breaks = seq(0, 10, by = 2), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Fusion Pairs", radius = 0.08)
+ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_fus,FusionPair %in% c("BCR-ABL1", "ABL1-BCR") & Drug %in% g2p_drugs), feature = "fusion", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Fusion Pairs", radius = 0.08)
 
@@
 ```{r}
-MakeSpearmanCorrDF <- function(dataset, df, metric, lineage) {
+MakeSpearmanCorrDF <- function(dataset, df, metric, lineage, g2p_list) {
   df$Gene <- factor(df$Gene, ordered = FALSE)
@@
                   GE_p_log10 = -log10(GE_p))
-      res$InG2P <- ifelse(res$Drug_Gene_Lin %in% unique(as.character(g2p_expr$Drug_Gene_Lin[!is.na(g2p_expr$Drug_Gene_Lin)])), "Yes", "No")
+      res$Gene_Lin <- with(res, paste0(Gene, "_", disease))
+      if(dataset != "CRISPR") { res$InG2P <- ifelse(res$Drug_Gene_Lin %in% g2p_list, "Yes", "No") }
+      if(dataset == "CRISPR") { res$InG2P <- ifelse(res$Gene_Lin %in% g2p_list, "Yes", "No") }
       res <- merge(res, df_count, by = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), all = TRUE)
@@
                   GE_p_log10 = -log10(GE_p))
-      res$InG2P <- ifelse(res$Drug_Gene %in% unique(as.character(g2p_expr$Drug_Gene[!is.na(g2p_expr$Drug_Gene)])), "Yes", "No")
+      if(dataset != "CRISPR") { res$InG2P <- ifelse(res$Drug_Gene %in% g2p_list, "Yes", "No") }
+      if(dataset == "CRISPR") { res$InG2P <- ifelse(res$Gene %in% g2p_list, "Yes", "No") }
       res <- merge(res, df_count, by = c("Drug", "Gene", "Drug_Gene"), all = TRUE)
@@
                   CN_p_log10 = -log10(CN_p))
-      res$InG2P <- ifelse(res$Drug_Gene_Lin %in% unique(as.character(g2p_amp$Drug_Gene_Lin[!is.na(g2p_amp$Drug_Gene_Lin)])), "Yes", "No")
+      res$Gene_Lin <- with(res, paste0(Gene, "_", disease))
+      if(dataset != "CRISPR") { res$InG2P <- ifelse(res$Drug_Gene_Lin %in% g2p_list, "Yes", "No") }
+      if(dataset == "CRISPR") { res$InG2P <- ifelse(res$Gene_Lin %in% g2p_list, "Yes", "No") }
       res <- merge(res, df_count, by = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), all = TRUE)
@@
                   CN_p_log10 = -log10(CN_p))
-      res$InG2P <- ifelse(res$Drug_Gene %in% unique(as.character(g2p_expr$Drug_Gene[!is.na(g2p_expr$Drug_Gene)])), "Yes", "No")
+      if(dataset != "CRISPR") { res$InG2P <- ifelse(res$Drug_Gene %in% g2p_list, "Yes", "No") }
+      if(dataset == "CRISPR") { res$InG2P <- ifelse(res$Gene %in% g2p_list, "Yes", "No") }
       res <- merge(res, df_count, by = c("Drug", "Gene", "Drug_Gene"), all = TRUE)
@@
 ```{r spear_calc, warning=FALSE, eval=FALSE}
-crispr_cn_res <- MakeSpearmanCorrDF(dataset = "CRISPR", df = crispr, metric = "CN", lineage = FALSE)
-ccle_cn_res <- MakeSpearmanCorrDF(dataset = "CCLE", df = ccle, metric = "CN", lineage = FALSE)
-ctrp_cn_res <- MakeSpearmanCorrDF(dataset = "CTRP", df = ctrp, metric = "CN", lineage = FALSE)
-gdsc_cn_res <- MakeSpearmanCorrDF(dataset = "GDSC", df = gdsc, metric = "CN", lineage = FALSE)
+# Agnostic
+## CN
+crispr_cn_res <- MakeSpearmanCorrDF(dataset = "CRISPR", df = crispr, metric = "CN", lineage = FALSE, g2p_list = unique(as.character(g2p_amp$Gene[!is.na(g2p_amp$Gene)])))
+ccle_cn_res <- MakeSpearmanCorrDF(dataset = "CCLE", df = filter(ccle, Drug %in% g2p_drugs), metric = "CN", lineage = FALSE, g2p_list = unique(as.character(g2p_amp$Drug_Gene[!is.na(g2p_amp$Drug_Gene)])))
+ctrp_cn_res <- MakeSpearmanCorrDF(dataset = "CTRP", df = filter(ctrp, Drug %in% g2p_drugs), metric = "CN", lineage = FALSE, g2p_list = unique(as.character(g2p_amp$Drug_Gene[!is.na(g2p_amp$Drug_Gene)])))
+gdsc_cn_res <- MakeSpearmanCorrDF(dataset = "GDSC", df = filter(gdsc, Drug %in% g2p_drugs), metric = "CN", lineage = FALSE, g2p_list = unique(as.character(g2p_amp$Drug_Gene[!is.na(g2p_amp$Drug_Gene)])))
 cn_cor <- rbind(crispr_cn_res, ccle_cn_res, ctrp_cn_res, gdsc_cn_res)
 saveRDS(cn_cor, "./data_munging/rds/cn_cor.rds", compress = "xz")
-
-crispr_ge_res <- MakeSpearmanCorrDF(dataset = "CRISPR", df = crispr, metric = "GE", lineage = FALSE)
-ccle_ge_res <- MakeSpearmanCorrDF(dataset = "CCLE", df = ccle, metric = "GE", lineage = FALSE)
-ctrp_ge_res <- MakeSpearmanCorrDF(dataset = "CTRP", df = ctrp, metric = "GE", lineage = FALSE)
-gdsc_ge_res <- MakeSpearmanCorrDF(dataset = "GDSC", df = gdsc, metric = "GE", lineage = FALSE)
+## GE
+crispr_ge_res <- MakeSpearmanCorrDF(dataset = "CRISPR", df = crispr, metric = "GE", lineage = FALSE, g2p_list = unique(as.character(g2p_expr$Gene[!is.na(g2p_expr$Gene)])))
+ccle_ge_res <- MakeSpearmanCorrDF(dataset = "CCLE", df = filter(ccle, Drug %in% g2p_drugs), metric = "GE", lineage = FALSE, g2p_list = unique(as.character(g2p_expr$Drug_Gene[!is.na(g2p_expr$Drug_Gene)])))
+ctrp_ge_res <- MakeSpearmanCorrDF(dataset = "CTRP", df = filter(ctrp, Drug %in% g2p_drugs), metric = "GE", lineage = FALSE, g2p_list = unique(as.character(g2p_expr$Drug_Gene[!is.na(g2p_expr$Drug_Gene)])))
+gdsc_ge_res <- MakeSpearmanCorrDF(dataset = "GDSC", df = filter(gdsc, Drug %in% g2p_drugs), metric = "GE", lineage = FALSE, g2p_list = unique(as.character(g2p_expr$Drug_Gene[!is.na(g2p_expr$Drug_Gene)])))
 ge_cor <- rbind(crispr_ge_res, ccle_ge_res, ctrp_ge_res, gdsc_ge_res)
 saveRDS(ge_cor, "./data_munging/rds/ge_cor.rds", compress = "xz")
+
+# Lineage
+## CN
+crispr_cn_res_lin <- MakeSpearmanCorrDF(dataset = "CRISPR", df = crispr, metric = "CN", lineage = TRUE, g2p_list = unique(as.character(g2p_amp$Gene_Lin[!is.na(g2p_amp$Gene_Lin)])))
+ccle_cn_res_lin <- MakeSpearmanCorrDF(dataset = "CCLE", df = filter(ccle, Drug %in% g2p_drugs), metric = "CN", lineage = TRUE, g2p_list = unique(as.character(g2p_amp$Drug_Gene_Lin[!is.na(g2p_amp$Drug_Gene_Lin)])))
+ctrp_cn_res_lin <- MakeSpearmanCorrDF(dataset = "CTRP", df = filter(ctrp, Drug %in% g2p_drugs), metric = "CN", lineage = TRUE, g2p_list = unique(as.character(g2p_amp$Drug_Gene_Lin[!is.na(g2p_amp$Drug_Gene_Lin)])))
+gdsc_cn_res_lin <- MakeSpearmanCorrDF(dataset = "GDSC", df = filter(gdsc, Drug %in% g2p_drugs), metric = "CN", lineage = TRUE, g2p_list = unique(as.character(g2p_amp$Drug_Gene_Lin[!is.na(g2p_amp$Drug_Gene_Lin)])))
+cn_cor_lin <- rbind(crispr_cn_res_lin, ccle_cn_res_lin, ctrp_cn_res_lin, gdsc_cn_res_lin) %>% filter(CN_p_log10 != Inf)
+saveRDS(cn_cor_lin, "./data_munging/rds/cn_cor_lineage.rds")
+## GE
+crispr_ge_res <- MakeSpearmanCorrDF(dataset = "CRISPR", df = crispr, metric = "GE", lineage = TRUE, g2p_list = unique(as.character(g2p_expr$Gene_Lin[!is.na(g2p_expr$Gene_Lin)])))
+ccle_ge_res_lin <- MakeSpearmanCorrDF(dataset = "CCLE", df = filter(ccle, Drug %in% g2p_drugs), metric = "GE", lineage = TRUE, g2p_list = unique(as.character(g2p_expr$Drug_Gene_Lin[!is.na(g2p_expr$Drug_Gene_Lin)])))
+ctrp_ge_res_lin <- MakeSpearmanCorrDF(dataset = "CTRP", df = filter(ctrp, Drug %in% g2p_drugs), metric = "GE", lineage = TRUE, g2p_list = unique(as.character(g2p_expr$Drug_Gene_Lin[!is.na(g2p_expr$Drug_Gene_Lin)])))
+gdsc_ge_res_lin <- MakeSpearmanCorrDF(dataset = "GDSC", df = filter(gdsc, Drug %in% g2p_drugs), metric = "GE", lineage = TRUE, g2p_list = unique(as.character(g2p_expr$Drug_Gene_Lin[!is.na(g2p_expr$Drug_Gene_Lin)])))
+ge_cor_lin <- rbind(crispr_ge_res, ccle_ge_res_lin, ctrp_ge_res_lin, gdsc_ge_res_lin) %>% filter(GE_p_log10 != Inf)
+saveRDS(ge_cor_lin, "./data_munging/rds/ge_cor_lineage.rds")
 ```
@@
 ge_cor <- merge(ge_cor, expr_summ, by = "Drug_Gene", all.x = TRUE)
-```
-
-## Lineage
-
-**12/16 FIX THIS **
-```{r spear_calc_lin, eval=FALSE}
-# Ran on 12/3
-crispr_cn_res_lin <- MakeSpearmanCorrDF(dataset = "CRISPR", df = crispr, metric = "CN", lineage = TRUE)
-ccle_cn_res_lin <- MakeSpearmanCorrDF(dataset = "CCLE", df = ccle, metric = "CN", lineage = TRUE)
-ctrp_cn_res_lin <- MakeSpearmanCorrDF(dataset = "CTRP", df = ctrp, metric = "CN", lineage = TRUE)
-gdsc_cn_res_lin <- MakeSpearmanCorrDF(dataset = "GDSC", df = gdsc, metric = "CN", lineage = TRUE)
-cn_cor_lin <- rbind(crispr_cn_res_lin, ccle_cn_res_lin, ctrp_cn_res_lin, gdsc_cn_res_lin) %>% filter(CN_p_log10 != Inf)
-saveRDS(cn_cor_lin, "./data_munging/rds/cn_cor_lineage.rds")
-
-crispr_ge_res <- MakeSpearmanCorrDF(dataset = "CRISPR", df = crispr, metric = "GE", lineage = TRUE)
-ccle_ge_res_lin <- MakeSpearmanCorrDF(dataset = "CCLE", df = ccle, metric = "GE", lineage = TRUE)
-ctrp_ge_res_lin <- MakeSpearmanCorrDF(dataset = "CTRP", df = ctrp, metric = "GE", lineage = TRUE)
-gdsc_ge_res_lin <- MakeSpearmanCorrDF(dataset = "GDSC", df = gdsc, metric = "GE", lineage = TRUE)
-ge_cor_lin <- rbind(crispr_ge_res, ccle_ge_res_lin, ctrp_ge_res_lin, gdsc_ge_res_lin) %>% filter(GE_p_log10 != Inf)
-saveRDS(ge_cor_lin, "./data_munging/rds/ge_cor_lineage.rds")
 ```
@@
 ```{r corr_heatmap_function}
-MakeCorrHeatmap <- function(cor_res, row_names, col_title, color_range, legend_title, metric, radius) {
+MakeCorrHeatmap <- function(cor_res, row_names, heatmap_legend, col_title, color_range, legend_title, metric, radius) {
   if(toupper(metric) == "CN" | toupper(metric) == "COPY NUMBER") {
@@
                          legend_width = unit(2, "in"),
+                         title = legend_title,
                          border = "gray70",
@@
                 col = col_fun,
-                name = legend_title,
                 na_col = "gray97",
@@
                 cluster_columns = FALSE, 
+                show_heatmap_legend = as.logical(heatmap_legend),
                 show_row_names = as.logical(row_names),
@@
 crispr_cn_cor <- unfactorize(filter(cn_cor, Dataset == "CRISPR" & Gene %in% unique(g2p_amp$Gene)))
-crispr_cn_ht <- MakeCorrHeatmap(cor_res = crispr_cn_cor, row_names = TRUE, col_title = "CRISPR", color_range = c(-0.25, 0, 0.25), radius = 0.03, legend_title = "CRISPR Spearman correlation", metric = "CN")
+crispr_cn_ht <- MakeCorrHeatmap(cor_res = crispr_cn_cor, row_names = TRUE, heatmap_legend = TRUE, col_title = "CRISPR", color_range = c(-0.25, 0, 0.25), radius = 0.03, legend_title = "CRISPR Spearman correlation", metric = "CN")
 png(filename = "./plots/manuscript/crispr_cn_heatmap.png", width = 3, height = 3, units = "in", res = 500)
@@
 ccle_cn_cor <- unfactorize(filter(cn_cor, Dataset == "CCLE" & Gene %in% unique(g2p_amp$Gene)))
-ccle_cn_ht <- MakeCorrHeatmap(cor_res = ccle_cn_cor, row_names = TRUE, col_title = "CCLE", color_range = c(-0.25, 0, 0.25), radius = 0.02, legend_title = "CCLE Spearman correlation", metric = "CN")
+ccle_cn_ht <- MakeCorrHeatmap(cor_res = ccle_cn_cor, row_names = TRUE, heatmap_legend = TRUE, col_title = "CCLE", color_range = c(-0.25, 0, 0.25), radius = 0.02, legend_title = "CCLE Spearman correlation", metric = "CN")
 png(filename = "./plots/manuscript/ccle_cn_heatmap.png", width = 3, height = 4, units = "in", res = 500)
@@
 ctrp_cn_cor <- unfactorize(filter(cn_cor, Dataset == "CTRP" & Gene %in% unique(g2p_amp$Gene)))
-ctrp_cn_ht <- MakeCorrHeatmap(cor_res = ctrp_cn_cor, row_names = TRUE, col_title = "CTRP", color_range = c(-0.25, 0, 0.25), radius = 0.02, legend_title = "CTRP Spearman correlation", metric = "CN")
+ctrp_cn_ht <- MakeCorrHeatmap(cor_res = ctrp_cn_cor, row_names = TRUE, heatmap_legend = TRUE, col_title = "CTRP", color_range = c(-0.25, 0, 0.25), radius = 0.02, legend_title = "CTRP Spearman correlation", metric = "CN")
 png(filename = "./plots/manuscript/ctrp_cn_heatmap.png", width = 8, height = 3, units = "in", res = 500)
@@
 gdsc_cn_cor <- unfactorize(filter(cn_cor, Dataset == "GDSC" & Gene %in% unique(g2p_amp$Gene)))
-gdsc_cn_ht <- MakeCorrHeatmap(cor_res = gdsc_cn_cor, row_names = TRUE, col_title = "GDSC", color_range = c(-0.25, 0, 0.25), radius = 0.02, legend_title = "GDSC Spearman correlation", metric = "CN")
+gdsc_cn_ht <- MakeCorrHeatmap(cor_res = gdsc_cn_cor, row_names = TRUE, heatmap_legend = TRUE, col_title = "GDSC", color_range = c(-0.25, 0, 0.25), radius = 0.02, legend_title = "GDSC Spearman correlation", metric = "CN")
 png(filename = "./plots/manuscript/gdsc_cn_heatmap.png", width = 5, height = 3, units = "in", res = 500)
@@
 
-crispr_cn_ht2 <- MakeCorrHeatmap(cor_res = crispr_cn_cor, row_names = TRUE, col_title = "CRISPR", color_range = c(-0.25, 0, 0.25), radius = 0.15, legend_title = "Copy num.
+crispr_cn_ht2 <- MakeCorrHeatmap(cor_res = crispr_cn_cor, row_names = TRUE, heatmap_legend = TRUE, col_title = "CRISPR", color_range = c(-0.25, 0, 0.25), radius = 0.15, legend_title = "Copy num.
 Spearman correlation", metric = "CN")
-ccle_cn_ht2 <- MakeCorrHeatmap(cor_res = ccle_cn_cor, row_names = TRUE, col_title = "CCLE", color_range = c(-0.25, 0, 0.25), radius = 0.0215, legend_title = "Copy num.
+ccle_cn_ht2 <- MakeCorrHeatmap(cor_res = ccle_cn_cor, row_names = FALSE, heatmap_legend = FALSE, col_title = "CCLE", color_range = c(-0.25, 0, 0.25), radius = 0.0215, legend_title = "Copy num.
 Spearman correlation", metric = "CN")
-ctrp_cn_ht2 <- MakeCorrHeatmap(cor_res = ctrp_cn_cor, row_names = FALSE, col_title = "CTRP", color_range = c(-0.25, 0, 0.25), radius = 0.0215, legend_title = "Copy num.
+ctrp_cn_ht2 <- MakeCorrHeatmap(cor_res = ctrp_cn_cor, row_names = FALSE, heatmap_legend = FALSE, col_title = "CTRP", color_range = c(-0.25, 0, 0.25), radius = 0.0215, legend_title = "Copy num.
 Spearman correlation", metric = "CN")
-gdsc_cn_ht2 <- MakeCorrHeatmap(cor_res = gdsc_cn_cor, row_names = FALSE, col_title = "GDSC", color_range = c(-0.25, 0, 0.25), radius = 0.0215, legend_title = "Copy num.
+gdsc_cn_ht2 <- MakeCorrHeatmap(cor_res = gdsc_cn_cor, row_names = FALSE, heatmap_legend = FALSE, col_title = "GDSC", color_range = c(-0.25, 0, 0.25), radius = 0.0215, legend_title = "Copy num.
 Spearman correlation", metric = "CN")
@@
 crispr_ge_cor <- unfactorize(filter(ge_cor, Dataset == "CRISPR" & Gene %in% unique(g2p_expr$Gene)))
-crispr_ge_ht <- MakeCorrHeatmap(cor_res = crispr_ge_cor, row_names = TRUE, col_title = "CRISPR", color_range = c(-0.5, 0, 0.5), radius = 0.1, legend_title = "CRISPR Spearman correlation", metric = "GE")
+crispr_ge_ht <- MakeCorrHeatmap(cor_res = crispr_ge_cor, row_names = TRUE, heatmap_legend = TRUE, col_title = "CRISPR", color_range = c(-0.5, 0, 0.5), radius = 0.1, legend_title = "CRISPR Spearman correlation", metric = "GE")
 png(filename = "./plots/manuscript/crispr_ge_heatmap.png", width = 3, height = 3, units = "in", res = 500)
@@
 ccle_ge_cor <- unfactorize(filter(ge_cor, Dataset == "CCLE" & Gene %in% unique(g2p_expr$Gene)))
-ccle_ge_ht <- MakeCorrHeatmap(cor_res = ccle_ge_cor, row_names = TRUE, col_title = "CCLE", color_range = c(-0.5, 0, 0.5), radius = 0.2, legend_title = "CCLE Spearman correlation", metric = "GE")
+ccle_ge_ht <- MakeCorrHeatmap(cor_res = ccle_ge_cor, row_names = TRUE, heatmap_legend = TRUE, col_title = "CCLE", color_range = c(-0.5, 0, 0.5), radius = 0.2, legend_title = "CCLE Spearman correlation", metric = "GE")
 png(filename = "./plots/manuscript/ccle_ge_heatmap.png", width = 3, height = 2.5, units = "in", res = 500)
@@
 ctrp_ge_cor <- unfactorize(filter(ge_cor, Dataset == "CTRP" & Gene %in% unique(g2p_expr$Gene)))
-ctrp_ge_ht <- MakeCorrHeatmap(cor_res = ctrp_ge_cor, row_names = TRUE, col_title = "CTRP", color_range = c(-0.5, 0, 0.5), radius = 0.2, legend_title = "CTRP Spearman correlation", metric = "GE")
+ctrp_ge_ht <- MakeCorrHeatmap(cor_res = ctrp_ge_cor, row_names = TRUE, heatmap_legend = TRUE, col_title = "CTRP", color_range = c(-0.5, 0, 0.5), radius = 0.2, legend_title = "CTRP Spearman correlation", metric = "GE")
 png(filename = "./plots/manuscript/ctrp_ge_heatmap.png", width = 8, height = 2.5, units = "in", res = 500)
@@
 gdsc_ge_cor <- unfactorize(filter(ge_cor, Dataset == "GDSC" & Gene %in% unique(g2p_expr$Gene)))
-gdsc_ge_ht <- MakeCorrHeatmap(cor_res = gdsc_ge_cor, row_names = TRUE, col_title = "GDSC", color_range = c(-0.5, 0, 0.5), radius = 0.2, legend_title = "GDSC Spearman correlation", metric = "GE")
+gdsc_ge_ht <- MakeCorrHeatmap(cor_res = gdsc_ge_cor, row_names = TRUE, heatmap_legend = TRUE, col_title = "GDSC", color_range = c(-0.5, 0, 0.5), radius = 0.2, legend_title = "GDSC Spearman correlation", metric = "GE")
 png(filename = "./plots/manuscript/gdsc_ge_heatmap.png", width = 5, height = 2.5, units = "in", res = 500)
@@
 
-crispr_ge_ht2 <- MakeCorrHeatmap(cor_res = crispr_ge_cor, row_names = TRUE, col_title = "CRISPR", color_range = c(-0.5, 0, 0.5), radius = 0.155, legend_title = "Gene expr.
+crispr_ge_ht2 <- MakeCorrHeatmap(cor_res = crispr_ge_cor, row_names = TRUE, heatmap_legend = TRUE, col_title = "CRISPR", color_range = c(-0.5, 0, 0.5), radius = 0.155, legend_title = "Gene expr.
 Spearman correlation", metric = "GE")
-ccle_ge_ht2 <- MakeCorrHeatmap(cor_res = ccle_ge_cor, row_names = TRUE, col_title = "CCLE", color_range = c(-0.5, 0, 0.5), radius = 0.035, legend_title = "Gene expr.
+ccle_ge_ht2 <- MakeCorrHeatmap(cor_res = ccle_ge_cor, row_names = FALSE, heatmap_legend = FALSE, col_title = "CCLE", color_range = c(-0.5, 0, 0.5), radius = 0.035, legend_title = "Gene expr.
 Spearman correlation", metric = "GE")
-ctrp_ge_ht2 <- MakeCorrHeatmap(cor_res = ctrp_ge_cor, row_names = FALSE, col_title = "CTRP", color_range = c(-0.5, 0, 0.5), radius = 0.035, legend_title = "Gene expr.
+ctrp_ge_ht2 <- MakeCorrHeatmap(cor_res = ctrp_ge_cor, row_names = FALSE, heatmap_legend = FALSE, col_title = "CTRP", color_range = c(-0.5, 0, 0.5), radius = 0.035, legend_title = "Gene expr.
 Spearman correlation", metric = "GE")
-gdsc_ge_ht2 <- MakeCorrHeatmap(cor_res = gdsc_ge_cor, row_names = FALSE, col_title = "GDSC", color_range = c(-0.5, 0, 0.5), radius = 0.035, legend_title = "Gene expr.
+gdsc_ge_ht2 <- MakeCorrHeatmap(cor_res = gdsc_ge_cor, row_names = FALSE, heatmap_legend = FALSE, col_title = "GDSC", color_range = c(-0.5, 0, 0.5), radius = 0.035, legend_title = "Gene expr.
 Spearman correlation", metric = "GE")
@@
 
-## Figure 3
-
-```{r Figure3, fig.height=12, fig.width=12, eval=FALSE}
+## Figure 2: G2P summary heatmap
+
+```{r Figure2_g2p_summary_heatmap, fig.height=6, fig.width=8, warning=FALSE, eval=FALSE}
+# Create annotation layer
+hta_data <- data.frame(Drug = rownames(g2p_dg_counts), CCLE = NA, CTRP = NA, GDSC = NA)
+hta_data$CCLE <- ifelse(hta_data$Drug %in% unique(ccle$Drug), "Screened", "Not screened")
+hta_data$CTRP <- ifelse(hta_data$Drug %in% unique(ctrp$Drug), "Screened", "Not screened")
+hta_data$GDSC <- ifelse(hta_data$Drug %in% unique(gdsc$Drug), "Screened", "Not screened")
+rownames(hta_data) <- hta_data$Drug
+hta_data$Drug <- NULL
+
+hta_annot <- HeatmapAnnotation(text = anno_text(colnames(hta_data), offset = unit(0.4, "in"), gp = gpar(fontsize = 10)))
+hta_legend_list <- list(legend_direction = "horizontal", border = "gray70", nrow = 2)
+hta <- Heatmap(hta_data,
+               name = "Functional screen status           ",
+               col = c("Screened" = "purple4", "Not screened" = "gray97"), 
+               rect_gp = gpar(col = "gray70"),
+               top_annotation = hta_annot,
+               heatmap_legend_param = hta_legend_list,
+               row_names_side = "left",
+               row_names_gp = gpar(fontsize = 10),
+               column_names_side = "top",
+               column_names_gp = gpar(fontsize = 10),
+               show_column_names = FALSE,
+               cluster_rows = FALSE, 
+               cluster_columns = FALSE,
+               row_title = "Drugs",
+               row_title_gp = gpar(fontface = "bold", fontsize = 14),
+               column_title = "Dataset",
+               column_title_gp = gpar(fontface = "bold", fontsize = 14),
+               width = unit(1.5, "in"))
+
+# Define color scale
+col_fun <- colorRamp2(c(0, 1, 100), c("gray97", "mistyrose", "purple4"))
+# Legend properties list
+ht_legend_list <- list(legend_direction = "horizontal", legend_width = unit(2.5, "in"), border = "gray70")
+ht <- Heatmap(g2p_dg_counts, 
+              name = "Number of G2P interpretations",
+              col = col_fun,
+              na_col = "gray97",
+              rect_gp = gpar(col = "gray70"),
+              heatmap_legend_param = ht_legend_list,
+              cluster_rows = FALSE, 
+              cluster_columns = FALSE, 
+              show_row_names = FALSE,
+              row_names_side = "left",
+              row_names_gp = gpar(fontsize = 10),
+              column_names_side = "bottom",
+              show_column_names = FALSE,
+              bottom_annotation = HeatmapAnnotation(
+                  text = anno_text(colnames(g2p_dg_counts),
+                                   rot = 45,
+                                   gp = gpar(fontsize = 8),
+                                   offset = unit(1, "npc"),
+                                   just = "right"),
+                  annotation_height = unit(0.45, "in")),
+              row_title = "Drugs",
+              row_title_gp = gpar(fontface = "bold", fontsize = 14),
+              column_title = "Genes", 
+              column_title_gp = gpar(fontface = "bold", fontsize = 14),
+              column_title_side = "bottom")
+
+png(filename = "./plots/manuscript/figure2_g2p_summary_heatmap.png", width = 10, height = 9, units = "in", res = 500)
+draw(hta + ht, gap = unit(5, "mm"), heatmap_legend_side = "top")
+dev.off()
+```
+
+## Figure 3: Mutation status
+
+```{r Figure3_mutation, fig.height=12, fig.width=12, eval=FALSE}
 # A: Heatmap
 ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "mutation", legend_title = "CCLE -log10(p-value)          ", legend_breaks = seq(0, 12, by = 3), row_names = FALSE, color = "darkgreen", col_title = "", row_title_txt = "Genes", radius = 0.023)
-ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "mutation", legend_title = "CTRP -log10(p-value)          ", legend_breaks = seq(0, 18, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.007)
+ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "mutation", legend_title = "CTRP -log10(p-value)          ", legend_breaks = seq(0, 18, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.006)
 ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "mutation", legend_title = "GDSC -log10(p-value)          ", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes", radius = 0.011)
@@
 
-# B: CRISPR mutation status (agnostic)
-crispr_mut_tb <- tableGrob(crispr_signif_g2p_g %>% filter(Gene %in% unique(g2p_mut$Gene), p < 0.05) %>% select(Gene, p.format, `n WT/mut`), rows = NULL)
-crispr_mut_title <- textGrob("CRISPR", gp = gpar(fontsize = 20))
-padding <- unit(0.5, "line")
-crispr_mut_tb <- gtable_add_rows(crispr_mut_tb, heights = grobHeight(crispr_mut_title) + padding, pos = 0)
-crispr_mut_tb <- gtable_add_grob(crispr_mut_tb, list(crispr_mut_title), t = 1, l = 1, r = ncol(crispr_mut_tb))
-
-# C: Drug screen mutation status (agnostic)
+# B: Mutation status
+crispr_mut_df <- crispr_signif_g2p_g %>% filter(Gene %in% unique(g2p_mut$Gene), p < 0.05) %>% select(Drug, Gene, p.format, `n WT/mut`)
+crispr_mut_df <- add_column(crispr_mut_df, .before = "Drug", Dataset = c("CRISPR", rep("", nrow(crispr_mut_df) - 1)))
+crispr_mut_df$Drug <- NA
 ccle_mut_df <- ccle_signif_g2p_dg %>% filter(InG2P == "Yes", p < 0.05) %>% select(Drug, Gene, p.format, `n WT/mut`)
@@
 gdsc_mut_df <- add_column(gdsc_mut_df, .before = "Drug", Dataset = c("GDSC", rep("", nrow(gdsc_mut_df) - 1)))
-mut_signif_tb <- tableGrob(rbind(ccle_mut_df, ctrp_mut_df, gdsc_mut_df), rows = NULL)
-drug_mut_signif_title <- textGrob("Drug screens", gp = gpar(fontsize = 20))
-padding <- unit(0.5, "line")
-mut_signif_tb <- gtable_add_rows(mut_signif_tb, heights = grobHeight(drug_mut_signif_title) + padding, pos = 0)
-mut_signif_tb <- gtable_add_grob(mut_signif_tb, list(drug_mut_signif_title), t = 1, l = 1, r = ncol(mut_signif_tb))
-
-# D: CRISPR mutation status (lineage)
-crispr_mut_lin_tb <- tableGrob(crispr_signif_lineage %>% filter(Gene %in% unique(g2p_mut$Gene), p < 0.05) %>% select(Gene, disease, p.format, `n WT/mut`), rows = NULL)
-crispr_mut_lin_tb <- gtable_add_rows(crispr_mut_lin_tb, heights = grobHeight(crispr_mut_title) + padding, pos = 0)
-crispr_mut_lin_tb <- gtable_add_grob(crispr_mut_lin_tb, list(crispr_mut_title), t = 1, l = 1, r = ncol(crispr_mut_lin_tb))
-
-# E: Drug screen mutation status (lineage)
-ccle_mut_lin_df <- ccle_signif_g2p_dgl %>% filter(InG2P == "Yes", p < 0.05) %>% select(Drug, Gene, disease, p.format, `n WT/mut`)
+mut_signif_tb <- tableGrob(rbind(crispr_mut_df, ccle_mut_df, ctrp_mut_df, gdsc_mut_df), rows = NULL)
+# drug_mut_signif_title <- textGrob("Drug screens", gp = gpar(fontsize = 20))
+# padding <- unit(0.5, "line")
+# mut_signif_tb <- gtable_add_rows(mut_signif_tb, heights = grobHeight(drug_mut_signif_title) + padding, pos = 0)
+# mut_signif_tb <- gtable_add_grob(mut_signif_tb, list(drug_mut_signif_title), t = 1, l = 1, r = ncol(mut_signif_tb))
+
+# D: Mutation status (lineage)
+crispr_mut_lin_df <- crispr_signif_lin %>% filter(Gene_Lin %in% unique(g2p_mut$Gene_Lin), p < 0.05) %>% select(Drug, Gene, disease, p.format, `n WT/mut`)
+crispr_mut_lin_df <- add_column(crispr_mut_lin_df, .before = "Drug", Dataset = c("CRISPR", rep("", nrow(crispr_mut_lin_df) - 1)))
+crispr_mut_lin_df$Drug <- NA
+ccle_mut_lin_df <- ccle_signif_dgl %>% filter(InG2P == "Yes", p < 0.05) %>% select(Drug, Gene, disease, p.format, `n WT/mut`)
 ccle_mut_lin_df <- add_column(ccle_mut_lin_df, .before = "Drug", Dataset = c("CCLE", rep("", nrow(ccle_mut_lin_df) - 1)))
-ctrp_mut_lin_df <- ctrp_signif_g2p_dgl %>% filter(InG2P == "Yes", p < 0.05) %>% select(Drug, Gene, disease, p.format, `n WT/mut`)
+ctrp_mut_lin_df <- ctrp_signif_dgl %>% filter(InG2P == "Yes", p < 0.05) %>% select(Drug, Gene, disease, p.format, `n WT/mut`)
 ctrp_mut_lin_df <- add_column(ctrp_mut_lin_df, .before = "Drug", Dataset = c("CTRP", rep("", nrow(ctrp_mut_lin_df) - 1)))
-gdsc_mut_lin_df <- gdsc_signif_g2p_dgl %>% filter(InG2P == "Yes", p < 0.05) %>% select(Drug, Gene, disease, p.format, `n WT/mut`)
+gdsc_mut_lin_df <- gdsc_signif_dgl %>% filter(InG2P == "Yes", p < 0.05) %>% select(Drug, Gene, disease, p.format, `n WT/mut`)
 gdsc_mut_lin_df <- add_column(gdsc_mut_lin_df, .before = "Drug", Dataset = c("GDSC", rep("", nrow(gdsc_mut_lin_df) - 1)))
-mut_lin_signif_tb <- tableGrob(rbind(ccle_mut_lin_df, ctrp_mut_lin_df, gdsc_mut_lin_df), rows = NULL)
-mut_lin_signif_tb <- gtable_add_rows(mut_lin_signif_tb, heights = grobHeight(drug_mut_signif_title) + padding, pos = 0)
-mut_lin_signif_tb <- gtable_add_grob(mut_lin_signif_tb, list(drug_mut_signif_title), t = 1, l = 1, r = ncol(mut_lin_signif_tb))
-
-# F: Boxplots
+mut_lin_signif_tb <- tableGrob(rbind(crispr_mut_lin_df, ccle_mut_lin_df, ctrp_mut_lin_df, gdsc_mut_lin_df), rows = NULL)
+# mut_lin_signif_tb <- gtable_add_rows(mut_lin_signif_tb, heights = grobHeight(drug_mut_signif_title) + padding, pos = 0)
+# mut_lin_signif_tb <- gtable_add_grob(mut_lin_signif_tb, list(drug_mut_signif_title), t = 1, l = 1, r = ncol(mut_lin_signif_tb))
+
+# C and E: Boxplots
 crispr_mut_filt <- filter(crispr, Gene %in% c("BRAF", "KRAS"))
@@
 
+crispr_mut_lin_filt <- filter(crispr, Drug_Gene_Lin %in% c("CRISPR_KRAS_lung", "CRISPR_BRAF_skin"))
+crispr_mut_lin_filt_plot <- ggplot(data = crispr_mut_lin_filt, mapping = aes(x = as.character(Mutation), y = Score)) +
+  facet_wrap(~ Drug_Gene_Lin) +
+  geom_violin() +
+  geom_boxplot(outlier.shape = NA, width = 0.07) +
+  stat_compare_means(method = "wilcox", comparisons = list(c("0", "1"))) +
+  labs(title = "CRISPR, lung and skin", x = "Mutation Status")
+
 ctrp_mut_filt <- filter(ctrp, Drug_Gene %in% c("afatinib_KRAS", "dabrafenib_BRAF"))
@@
 
-crispr_mut_lin_filt <- filter(crispr, Drug_Gene_Lin %in% c("CRISPR_BRAF_skin", "CRISPR_KRAS_lung"))
-crispr_mut_lin_filt_plot <- ggplot(data = crispr_mut_lin_filt, mapping = aes(x = as.character(Mutation), y = Score)) +
+ctrp_mut_lin_filt <- filter(ctrp, Drug_Gene_Lin %in% c("afatinib_KRAS_lung", "dabrafenib_BRAF_skin"))
+ctrp_mut_lin_filt_plot <- ggplot(data = ctrp_mut_lin_filt, mapping = aes(x = as.character(Mutation), y = Score)) +
   facet_wrap(~ Drug_Gene_Lin) +
@@
   stat_compare_means(method = "wilcox", comparisons = list(c("0", "1"))) +
-  labs(title = "CRISPR, skin", x = "Mutation Status")
+  labs(title = "CTRP, lung and skin", x = "Mutation Status")
 
 # Make figure
-A <- textGrob("A", hjust = 0, vjust = 1, gp = gpar(fontsize = 20, fontface = "bold"))
-space <- textGrob("")
-B <- textGrob("B", hjust = 0, vjust = 1, gp = gpar(fontsize = 20, fontface = "bold"))
-C <- textGrob("C", hjust = 0, vjust = 1, gp = gpar(fontsize = 20, fontface = "bold"))
-D <- textGrob("D", hjust = 0, vjust = 1, gp = gpar(fontsize = 20, fontface = "bold"))
-E <- textGrob("E", hjust = 0, vjust = 1, gp = gpar(fontsize = 20, fontface = "bold"))
-f <- textGrob("F", hjust = 0, vjust = 1, gp = gpar(fontsize = 20, fontface = "bold"))
-
-lay <- rbind(c(1, 2, 2, 2),
-             c(3, 3, 3, 3),
-             c(3, 3, 3, 3),
-             c(3, 3, 3, 3),
-             c(3, 3, 3, 3),
-             c(3, 3, 3, 3),
-             c(3, 3, 3, 3),
-             c(3, 3, 3, 3),
-             c(3, 3, 3, 3),
-             c(4, 5, 6, 7),
-             c(8, 9, 10, 11),
-             c(8, 9, 10, 11),
-             c(8, 9, 10, 11),
-             c(8, 9, 10, 11),
-             c(12, 2, 2, 2),
-             c(13, 13, 13, 13),
-             c(13, 13, 13, 13),
-             c(13, 13, 13, 13),
-             c(13, 13, 13, 13),
-             c(13, 13, 13, 13))
-
-png(filename = "./plots/manuscript/figure3.png", width = 25, height = 25, units = "in", res = 500)
-grid.arrange(A, space,
-             ht_mut_grob,
-             B, C, D, E,
-             crispr_mut_tb, mut_signif_tb, crispr_mut_lin_tb, mut_lin_signif_tb,
-             f,
-             arrangeGrob(ggplotGrob(crispr_mut_filt_plot),
-                         ggplotGrob(ctrp_mut_filt_plot),
-                         ggplotGrob(crispr_mut_lin_filt_plot),
-                         nrow = 1),
-             layout_matrix = lay)
+lay <- rbind(c(1, 1, 1, 1),
+             c(1, 1, 1, 1),
+             c(2, 3, 3, 3),
+             c(4, 5, 5, 5))
+
+png(filename = "./plots/manuscript/figure3_mutation_status.png", width = 25, height = 25, units = "in", res = 500)
+grid.arrange(layout_matrix = lay,
+             arrangeGrob(ht_mut_grob, left = textGrob("A", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(mut_signif_tb, left = textGrob("B", x = unit(1, "npc"), y = unit(.95, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(ggplotGrob(crispr_mut_filt_plot), ggplotGrob(ctrp_mut_filt_plot), nrow = 1, left = textGrob("C", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(mut_lin_signif_tb, left = textGrob("D", x = unit(1, "npc"), y = unit(.95, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(ggplotGrob(crispr_mut_lin_filt_plot), ggplotGrob(ctrp_mut_lin_filt_plot), nrow = 1, left = textGrob("E", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))))
+dev.off()
+```
+
+## Figure 4: Protein changes
+
+```{r Figure4_protein_change, fig.height=12, fig.width=12, eval=FALSE}
+# A: Heatmap
+ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot_4plot, feature = "protein changes", legend_title = "CCLE -log10(p-value)          ", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "darkgreen", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.021)
+ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot_4plot, feature = "protein changes", legend_title = "CTRP -log10(p-value)          ", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.009)
+ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = gdsc_signif_prot_4plot, feature = "protein changes", legend_title = "GDSC -log10(p-value)          ", legend_breaks = seq(0, 8, by = 2), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.0125)
+ht_crispr2 <- MakeWilcoxonHeatmap(signif_df = crispr_signif_prot_4plot, feature = "protein changes CRISPR", legend_title = "CRISPR -log10(p-value)", legend_breaks = seq(0, 25, by = 5), row_names = TRUE, color = "darkorchid4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.135)
+ht_prot_list <- ht_crispr2 + ht_ccle2 + ht_ctrp2 + ht_gdsc2
+ht_prot_grob <- grid.grabExpr(draw(ht_prot_list, gap = unit(0.25, "in"), heatmap_legend_side = "right"))
+
+# B: Protein chnages (agnostic)
+crispr_prot_df <- crispr_signif_prot %>% filter(InG2P == "Yes", p < 0.05) %>% select(Drug, Gene_Protein_Change, p.format, `n WT/mut`)
+crispr_prot_df <- add_column(crispr_prot_df, .before = "Drug", Dataset = c("CRISPR", rep("", nrow(crispr_prot_df) - 1)))
+crispr_prot_df$Drug <- NA
+ccle_prot_df <- ccle_signif_prot %>% filter(InG2P == "Yes", p < 0.05) %>% select(Drug, Gene_Protein_Change, p.format, `n WT/mut`)
+# ccle_prot_df <- add_column(ccle_prot_df, .before = "Drug", Dataset = c("CCLE", rep("", nrow(ccle_prot_df) - 1)))
+ctrp_prot_df <- ctrp_signif_prot %>% filter(InG2P == "Yes", p < 0.05) %>% select(Drug, Gene_Protein_Change, p.format, `n WT/mut`)
+ctrp_prot_df <- add_column(ctrp_prot_df, .before = "Drug", Dataset = c("CTRP", rep("", nrow(ctrp_prot_df) - 1)))
+gdsc_prot_df <- gdsc_signif_prot %>% filter(InG2P == "Yes", p < 0.05) %>% select(Drug, Gene_Protein_Change, p.format, `n WT/mut`)
+gdsc_prot_df <- add_column(gdsc_prot_df, .before = "Drug", Dataset = c("GDSC", rep("", nrow(gdsc_prot_df) - 1)))
+prot_signif_tb <- tableGrob(rbind(crispr_prot_df, ccle_prot_df, ctrp_prot_df, gdsc_prot_df), rows = NULL)
+
+# D: Protein chnages (lineage)
+crispr_prot_lin_df <- crispr_signif_prot_lin %>% filter(InG2P == "Yes", p < 0.05) %>% select(Drug, Gene_Protein_Change, disease, p.format, `n WT/mut`)
+crispr_prot_lin_df <- add_column(crispr_prot_lin_df, .before = "Drug", Dataset = c("CRISPR", rep("", nrow(crispr_prot_lin_df) - 1)))
+crispr_prot_lin_df$Drug <- NA
+ccle_prot_lin_df <- ccle_signif_prot_lin %>% filter(InG2P == "Yes", p < 0.05) %>% select(Drug, Gene_Protein_Change, disease, p.format, `n WT/mut`)
+# ccle_prot_lin_df <- add_column(ccle_prot_lin_df, .before = "Drug", Dataset = c("CCLE", rep("", nrow(ccle_prot_lin_df) - 1)))
+ctrp_prot_lin_df <- ctrp_signif_prot_lin %>% filter(InG2P == "Yes", p < 0.05) %>% select(Drug, Gene_Protein_Change, disease, p.format, `n WT/mut`)
+ctrp_prot_lin_df <- add_column(ctrp_prot_lin_df, .before = "Drug", Dataset = c("CTRP", rep("", nrow(ctrp_prot_lin_df) - 1)))
+gdsc_prot_lin_df <- gdsc_signif_prot_lin %>% filter(InG2P == "Yes", p < 0.05) %>% select(Drug, Gene_Protein_Change, disease, p.format, `n WT/mut`)
+# gdsc_prot_lin_df <- add_column(gdsc_prot_lin_df, .before = "Drug", Dataset = c("GDSC", rep("", nrow(gdsc_prot_lin_df) - 1)))
+prot_lin_signif_tb <- tableGrob(rbind(crispr_prot_lin_df, ccle_prot_lin_df, ctrp_prot_lin_df, gdsc_prot_lin_df), rows = NULL)
+
+# C and E: Boxplots
+crispr_prot_filt <- filter(crispr_prot, Gene_Protein_Change %in% c("BRAF:V600E", "KRAS:G12C", "KRAS:G12D", "KRAS:G12V"))
+crispr_prot_filt_plot <- ggplot(data = crispr_prot_filt, mapping = aes(x = as.character(Change_Status), y = Score)) +
+  facet_wrap(~ Gene_Protein_Change, nrow = 1) +
+  geom_violin() +
+  geom_boxplot(outlier.shape = NA, width = 0.07) +
+  stat_compare_means(method = "wilcox", comparisons = list(c("No", "Yes"))) +
+  labs(title = "CRISPR, lineage agnostic", x = "Protein Change Status")
+
+crispr_prot_lin_filt <- filter(crispr_prot, Gene_Protein_Change_Lineage %in% c("BRAF:V600E_skin", "KRAS:G12C_lung"))
+crispr_prot_lin_filt_plot <- ggplot(data = crispr_prot_lin_filt, mapping = aes(x = as.character(Change_Status), y = Score)) +
+  facet_wrap(~ Gene_Protein_Change_Lineage, nrow = 1) +
+  geom_violin() +
+  geom_boxplot(outlier.shape = NA, width = 0.07) +
+  stat_compare_means(method = "wilcox", comparisons = list(c("No", "Yes"))) +
+  labs(title = "CRISPR, lung and skin", x = "Protein Change Status")
+
+ctrp_prot_filt <- filter(ctrp_prot, Drug_Gene_Protein_Change %in% c("dabrafenib_BRAF:V600E", "trametinib_BRAF:V600E", "vemurafenib_BRAF:V600E", "afatinib_KRAS:G12D"))
+ctrp_prot_filt_plot <- ggplot(data = ctrp_prot_filt, mapping = aes(x = as.character(Change_Status), y = Score)) +
+  facet_wrap(~ Drug_Gene_Protein_Change, nrow = 1) +
+  geom_violin() +
+  geom_boxplot(outlier.shape = NA, width = 0.07) +
+  stat_compare_means(method = "wilcox", comparisons = list(c("No", "Yes"))) +
+  labs(title = "CTRP, lineage agnostic", x = "Protein Change Status")
+
+ctrp_prot_lin_filt <- filter(ctrp_prot, Drug_Gene_Protein_Change_Lineage %in% c("dabrafenib_BRAF:V600E_skin", "vemurafenib_BRAF:V600E_skin"))
+ctrp_prot_lin_filt_plot <- ggplot(data = ctrp_prot_lin_filt, mapping = aes(x = as.character(Change_Status), y = Score)) +
+  facet_wrap(~ Drug_Gene_Protein_Change_Lineage, nrow = 1) +
+  geom_violin() +
+  geom_boxplot(outlier.shape = NA, width = 0.07) +
+  stat_compare_means(method = "wilcox", comparisons = list(c("No", "Yes"))) +
+  labs(title = "CTRP, skin", x = "Protein Change Status")
+
+# Make figure
+lay <- rbind(c(1, 1, 1, 1),
+             c(1, 1, 1, 1),
+             c(2, 3, 3, 3),
+             c(2, 3, 3, 3),
+             c(4, 5, 5, 5))
+
+png(filename = "./plots/manuscript/figure4_protein_changes.png", width = 25, height = 25, units = "in", res = 500)
+grid.arrange(layout_matrix = lay,
+             arrangeGrob(ht_prot_grob, left = textGrob("A", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(prot_signif_tb, left = textGrob("B", x = unit(1, "npc"), y = unit(.95, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(ggplotGrob(crispr_prot_filt_plot), ggplotGrob(ctrp_prot_filt_plot), nrow = 2, left = textGrob("C", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(prot_lin_signif_tb, left = textGrob("D", x = unit(1, "npc"), y = unit(.95, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(ggplotGrob(crispr_prot_lin_filt_plot), ggplotGrob(ctrp_prot_lin_filt_plot), nrow = 1, left = textGrob("E", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))))
+dev.off()
+```
+
+## Figure 5: Copy number
+
+```{r Figure5_cn, fig.height=8, fig.width=12, eval=FALSE}
+# A: Heatmap
+crispr_cn_ht2 <- MakeCorrHeatmap(cor_res = crispr_cn_cor, row_names = TRUE, heatmap_legend = TRUE, col_title = "CRISPR", color_range = c(-0.25, 0, 0.25), radius = 0.15, legend_title = "Copy num.
+Spearman correlation", metric = "CN")
+ccle_cn_ht2 <- MakeCorrHeatmap(cor_res = ccle_cn_cor, row_names = FALSE, heatmap_legend = FALSE, col_title = "CCLE", color_range = c(-0.25, 0, 0.25), radius = 0.0215, legend_title = "Copy num.
+Spearman correlation", metric = "CN")
+ctrp_cn_ht2 <- MakeCorrHeatmap(cor_res = ctrp_cn_cor, row_names = FALSE, heatmap_legend = FALSE, col_title = "CTRP", color_range = c(-0.25, 0, 0.25), radius = 0.0215, legend_title = "Copy num.
+Spearman correlation", metric = "CN")
+gdsc_cn_ht2 <- MakeCorrHeatmap(cor_res = gdsc_cn_cor, row_names = FALSE, heatmap_legend = FALSE, col_title = "GDSC", color_range = c(-0.25, 0, 0.25), radius = 0.0215, legend_title = "Copy num.
+Spearman correlation", metric = "CN")
+ht_cn_list <- crispr_cn_ht2 + ccle_cn_ht2 + ctrp_cn_ht2 + gdsc_cn_ht2
+ht_cn_grob <- grid.grabExpr(draw(ht_cn_list, gap = unit(0.25, "in"), heatmap_legend_side = "top"))
+
+# B: Copy number (agnostic)
+crispr_cn_df <- crispr_cn_cor %>% filter(InG2P == "Yes", CN_p < 0.05) %>% select(Drug, Gene, CN_r, CN_p, n)
+crispr_cn_df <- add_column(crispr_cn_df, .before = "Drug", Dataset = c("CRISPR", rep("", nrow(crispr_cn_df) - 1)))
+crispr_cn_df$Drug <- NA
+ccle_cn_df <- ccle_cn_cor %>% filter(InG2P == "Yes", CN_p < 0.05) %>% select(Drug, Gene, CN_r, CN_p, n)
+ccle_cn_df <- add_column(ccle_cn_df, .before = "Drug", Dataset = c("CCLE", rep("", nrow(ccle_cn_df) - 1)))
+ctrp_cn_df <- ctrp_cn_cor %>% filter(InG2P == "Yes", CN_p < 0.05) %>% select(Drug, Gene, CN_r, CN_p, n)
+ctrp_cn_df <- add_column(ctrp_cn_df, .before = "Drug", Dataset = c("CTRP", rep("", nrow(ctrp_cn_df) - 1)))
+gdsc_cn_df <- gdsc_cn_cor %>% filter(InG2P == "Yes", CN_p < 0.05) %>% select(Drug, Gene,CN_r,  CN_p, n)
+# gdsc_cn_df <- add_column(gdsc_cn_df, .before = "Drug", Dataset = c("GDSC", rep("", nrow(gdsc_cn_df) - 1)))
+cn_signif_tb <- tableGrob(rbind(crispr_cn_df, ccle_cn_df, ctrp_cn_df, gdsc_cn_df), rows = NULL)
+
+# D: Copy number (lineage)
+crispr_cn_lin_df <- cn_cor_lin %>% filter(Dataset == "CRISPR", InG2P == "Yes", CN_p < 0.05) %>% select(Drug, Gene, disease, CN_r, CN_p, n)
+crispr_cn_lin_df <- add_column(crispr_cn_lin_df, .before = "Drug", Dataset = c("CRISPR", rep("", nrow(crispr_cn_lin_df) - 1)))
+crispr_cn_lin_df$Drug <- NA
+ccle_cn_lin_df <- cn_cor_lin %>% filter(Dataset == "CCLE", InG2P == "Yes", CN_p < 0.05) %>% select(Drug, Gene,disease,  CN_r, CN_p, n)
+ccle_cn_lin_df <- add_column(ccle_cn_lin_df, .before = "Drug", Dataset = c("CCLE", rep("", nrow(ccle_cn_lin_df) - 1)))
+ctrp_cn_lin_df <- cn_cor_lin %>% filter(Dataset == "CTRP", InG2P == "Yes", CN_p < 0.05) %>% select(Drug, Gene, disease, CN_r, CN_p, n)
+ctrp_cn_lin_df <- add_column(ctrp_cn_lin_df, .before = "Drug", Dataset = c("CTRP", rep("", nrow(ctrp_cn_lin_df) - 1)))
+gdsc_cn_lin_df <- cn_cor_lin %>% filter(Dataset == "GDSC", InG2P == "Yes", CN_p < 0.05) %>% select(Drug, Gene, disease, CN_r,  CN_p, n)
+gdsc_cn_lin_df <- add_column(gdsc_cn_lin_df, .before = "Drug", Dataset = c("GDSC", rep("", nrow(gdsc_cn_lin_df) - 1)))
+cn_lin_signif_tb <- tableGrob(rbind(crispr_cn_lin_df, ccle_cn_lin_df, ctrp_cn_lin_df, gdsc_cn_lin_df), rows = NULL)
+
+# C and E: Scatterplots
+crispr_cn_filt <- filter(crispr, Gene %in% c("ERBB2"))
+crispr_cn_filt_plot <- ggplot(data = crispr_cn_filt, mapping = aes(x = CN, y = Score)) +
+  geom_point() +
+  labs(title = "CRISPR: ERBB2", x = "Copy Number")
+
+ccle_cn_filt1 <- filter(ccle, Drug_Gene %in% c("erlotinib_MET"))
+ccle_cn_filt_plot1 <- ggplot(data = ccle_cn_filt1, mapping = aes(x = CN, y = Score)) +
+  geom_point() +
+  labs(title = "CCLE: erlotinib, MET", x = "Copy Number")
+
+ccle_cn_filt2 <- filter(ccle, Drug_Gene %in% c("lapatinib_ERBB2"))
+ccle_cn_filt_plot2 <- ggplot(data = ccle_cn_filt2, mapping = aes(x = CN, y = Score)) +
+  geom_point() +
+  labs(title = "CCLE: lapatinib, ERBB2", x = "Copy Number")
+
+ctrp_cn_filt <- filter(ccle, Drug_Gene %in% c("erlotinib_MET"))
+ctrp_cn_filt_plot <- ggplot(data = ctrp_cn_filt, mapping = aes(x = CN, y = Score)) +
+  geom_point() +
+  labs(title = "CTRP: erlotinib, MET", x = "Copy Number")
+
+crispr_cn_lin_filt <- filter(crispr, Gene_Lin %in% c("ERBB2_breast"))
+crispr_cn_lin_filt_plot <- ggplot(data = crispr_cn_lin_filt, mapping = aes(x = CN, y = Score)) +
+  geom_point() +
+  labs(title = "CRISPR: ERBB2, breast", x = "Copy Number")
+
+ccle_cn_lin_filt <- filter(ccle, Drug_Gene_Lin %in% c("lapatinib_ERBB2_breast"))
+ccle_cn_lin_filt_plot <- ggplot(data = ccle_cn_lin_filt, mapping = aes(x = CN, y = Score)) +
+  geom_point() +
+  labs(title = "CCLE: lapatinib, ERBB2, breast", x = "Copy Number")
+
+ctrp_cn_lin_filt <- filter(ccle, Drug_Gene_Lin %in% c("lapatinib_ERBB2_breast"))
+ctrp_cn_lin_filt_plot <- ggplot(data = ctrp_cn_lin_filt, mapping = aes(x = CN, y = Score)) +
+  geom_point() +
+  labs(title = "CTRP: lapatinib, ERBB2, breast", x = "Copy Number")
+
+gdsc_cn_lin_filt <- filter(ccle, Drug_Gene_Lin %in% c("lapatinib_ERBB2_breast"))
+gdsc_cn_lin_filt_plot <- ggplot(data = gdsc_cn_lin_filt, mapping = aes(x = CN, y = Score)) +
+  geom_point() +
+  labs(title = "GDSC: lapatinib, ERBB2, breast", x = "Copy Number")
+
+# Make figure
+lay <- rbind(c(1, 1, 1, 1),
+             c(2, 3, 3, 3),
+             c(4, 5, 5, 5))
+
+png(filename = "./plots/manuscript/figure5_copy_number.png", width = 25, height = 16, units = "in", res = 500)
+grid.arrange(layout_matrix = lay,
+             arrangeGrob(ht_cn_grob, left = textGrob("A", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(cn_signif_tb, left = textGrob("B", x = unit(1, "npc"), y = unit(.95, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(ggplotGrob(crispr_cn_filt_plot), ggplotGrob(ccle_cn_filt_plot1), ggplotGrob(ccle_cn_filt_plot2), ggplotGrob(ctrp_cn_filt_plot), nrow = 1, left = textGrob("C", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(cn_lin_signif_tb, left = textGrob("D", x = unit(1, "npc"), y = unit(.95, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(ggplotGrob(crispr_cn_lin_filt_plot), ggplotGrob(ccle_cn_lin_filt_plot), ggplotGrob(ctrp_cn_lin_filt_plot), ggplotGrob(gdsc_cn_lin_filt_plot), nrow = 1, left = textGrob("E", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))))
+dev.off()
+```
+
+## Figure 6: Gene expression
+
+```{r Figure6_ge, fig.height=8, fig.width=12, eval=FALSE}
+# A: Heatmap
+crispr_ge_ht2 <- MakeCorrHeatmap(cor_res = crispr_ge_cor, row_names = TRUE, heatmap_legend = TRUE, col_title = "CRISPR", color_range = c(-0.5, 0, 0.5), radius = 0.155, legend_title = "Gene expr.
+Spearman correlation", metric = "GE")
+ccle_ge_ht2 <- MakeCorrHeatmap(cor_res = ccle_ge_cor, row_names = FALSE, heatmap_legend = FALSE, col_title = "CCLE", color_range = c(-0.5, 0, 0.5), radius = 0.035, legend_title = "Gene expr.
+Spearman correlation", metric = "GE")
+ctrp_ge_ht2 <- MakeCorrHeatmap(cor_res = ctrp_ge_cor, row_names = FALSE, heatmap_legend = FALSE, col_title = "CTRP", color_range = c(-0.5, 0, 0.5), radius = 0.035, legend_title = "Gene expr.
+Spearman correlation", metric = "GE")
+gdsc_ge_ht2 <- MakeCorrHeatmap(cor_res = gdsc_ge_cor, row_names = FALSE, heatmap_legend = FALSE, col_title = "GDSC", color_range = c(-0.5, 0, 0.5), radius = 0.035, legend_title = "Gene expr.
+Spearman correlation", metric = "GE")
+ht_ge_list <- crispr_ge_ht2 + ccle_ge_ht2 + ctrp_ge_ht2 + gdsc_ge_ht2
+ht_ge_grob <- grid.grabExpr(draw(ht_ge_list, gap = unit(0.25, "in"), heatmap_legend_side = "top"))
+
+# B: Copy number (agnostic)
+crispr_ge_df <- crispr_ge_cor %>% filter(InG2P == "Yes", GE_p < 0.05) %>% select(Drug, Gene, GE_r, GE_p, n)
+crispr_ge_df <- add_column(crispr_ge_df, .before = "Drug", Dataset = c("CRISPR", rep("", nrow(crispr_ge_df) - 1)))
+crispr_ge_df$Drug <- NA
+ccle_ge_df <- ccle_ge_cor %>% filter(InG2P == "Yes", GE_p < 0.05) %>% select(Drug, Gene, GE_r, GE_p, n)
+ccle_ge_df <- add_column(ccle_ge_df, .before = "Drug", Dataset = c("CCLE", rep("", nrow(ccle_ge_df) - 1)))
+ctrp_ge_df <- ctrp_ge_cor %>% filter(InG2P == "Yes", GE_p < 0.05) %>% select(Drug, Gene, GE_r, GE_p, n)
+ctrp_ge_df <- add_column(ctrp_ge_df, .before = "Drug", Dataset = c("CTRP", rep("", nrow(ctrp_ge_df) - 1)))
+gdsc_ge_df <- gdsc_ge_cor %>% filter(InG2P == "Yes", GE_p < 0.05) %>% select(Drug, Gene,GE_r,  GE_p, n)
+gdsc_ge_df <- add_column(gdsc_ge_df, .before = "Drug", Dataset = c("GDSC", rep("", nrow(gdsc_ge_df) - 1)))
+ge_signif_tb <- tableGrob(rbind(crispr_ge_df, ccle_ge_df, ctrp_ge_df, gdsc_ge_df), rows = NULL)
+
+# D: Copy number (lineage)
+crispr_ge_lin_df <- ge_cor_lin %>% filter(Dataset == "CRISPR", InG2P == "Yes", GE_p < 0.05) %>% select(Drug, Gene, disease, GE_r, GE_p, n)
+crispr_ge_lin_df <- add_column(crispr_ge_lin_df, .before = "Drug", Dataset = c("CRISPR", rep("", nrow(crispr_ge_lin_df) - 1)))
+crispr_ge_lin_df$Drug <- NA
+ccle_ge_lin_df <- ge_cor_lin %>% filter(Dataset == "CCLE", InG2P == "Yes", GE_p < 0.05) %>% select(Drug, Gene,disease,  GE_r, GE_p, n)
+ccle_ge_lin_df <- add_column(ccle_ge_lin_df, .before = "Drug", Dataset = c("CCLE", rep("", nrow(ccle_ge_lin_df) - 1)))
+ctrp_ge_lin_df <- ge_cor_lin %>% filter(Dataset == "CTRP", InG2P == "Yes", GE_p < 0.05) %>% select(Drug, Gene, disease, GE_r, GE_p, n)
+# ctrp_ge_lin_df <- add_column(ctrp_ge_lin_df, .before = "Drug", Dataset = c("CTRP", rep("", nrow(ctrp_ge_lin_df) - 1)))
+gdsc_ge_lin_df <- ge_cor_lin %>% filter(Dataset == "GDSC", InG2P == "Yes", GE_p < 0.05) %>% select(Drug, Gene, disease, GE_r,  GE_p, n)
+# gdsc_ge_lin_df <- add_column(gdsc_ge_lin_df, .before = "Drug", Dataset = c("GDSC", rep("", nrow(gdsc_ge_lin_df) - 1)))
+ge_lin_signif_tb <- tableGrob(rbind(crispr_ge_lin_df, ccle_ge_lin_df, ctrp_ge_lin_df, gdsc_ge_lin_df), rows = NULL)
+
+# C and E: Scatterplots
+crispr_ge_filt <- filter(crispr, Gene %in% c("ERBB2"))
+crispr_ge_filt_plot <- ggplot(data = crispr_ge_filt, mapping = aes(x = TPM, y = Score)) +
+  geom_point() +
+  labs(title = "CRISPR: ERBB2", x = "Gene Expression (TPM)")
+
+ccle_ge_filt <- filter(ccle, Drug_Gene %in% c("lapatinib_ERBB2"))
+ccle_ge_filt_plot <- ggplot(data = ccle_ge_filt, mapping = aes(x = TPM, y = Score)) +
+  geom_point() +
+  labs(title = "CCLE: lapatinib, ERBB2", x = "Gene Expression (TPM)")
+
+ctrp_ge_filt <- filter(ctrp, Drug_Gene %in% c("docetaxel_ERBB2"))
+ctrp_ge_filt_plot <- ggplot(data = ctrp_ge_filt, mapping = aes(x = TPM, y = Score)) +
+  geom_point() +
+  labs(title = "CTRP: docetaxel, ERBB2", x = "Gene Expression (TPM)")
+
+gdsc_ge_filt1 <- filter(gdsc, Drug_Gene %in% c("docetaxel_ERBB2"))
+gdsc_ge_filt_plot1 <- ggplot(data = gdsc_ge_filt1, mapping = aes(x = TPM, y = Score)) +
+  geom_point() +
+  labs(title = "GDSC: docetaxel, ERBB2", x = "Gene Expression (TPM)")
+
+gdsc_ge_filt2 <- filter(gdsc, Drug_Gene %in% c("lapatinib_ERBB2"))
+gdsc_ge_filt_plot2 <- ggplot(data = gdsc_ge_filt2, mapping = aes(x = TPM, y = Score)) +
+  geom_point() +
+  labs(title = "GDSC: lapatinib, ERBB2", x = "Gene Expression (TPM)")
+
+crispr_ge_lin_filt <- filter(crispr, Gene_Lin %in% c("ERBB2_breast"))
+crispr_ge_lin_filt_plot <- ggplot(data = crispr_ge_lin_filt, mapping = aes(x = TPM, y = Score)) +
+  geom_point() +
+  labs(title = "CRISPR: ERBB2, breast", x = "Gene Expression (TPM)")
+
+ccle_ge_lin_filt <- filter(ccle, Drug_Gene_Lin %in% c("lapatinib_ERBB2_breast"))
+ccle_ge_lin_filt_plot <- ggplot(data = ccle_ge_lin_filt, mapping = aes(x = TPM, y = Score)) +
+  geom_point() +
+  labs(title = "CCLE: lapatinib, ERBB2, breast", x = "Gene Expression (TPM)")
+
+# Make figure
+lay <- rbind(c(1, 1, 1, 1),
+             c(2, 3, 4, 4),
+             c(5, 5, 5, 5))
+
+png(filename = "./plots/manuscript/figure6_gene_expression.png", width = 25, height = 16, units = "in", res = 500)
+grid.arrange(layout_matrix = lay,
+             arrangeGrob(ht_cn_grob, left = textGrob("A", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(ge_signif_tb, left = textGrob("B", x = unit(1, "npc"), y = unit(.95, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(ge_lin_signif_tb, left = textGrob("D", x = unit(1, "npc"), y = unit(.95, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(ggplotGrob(crispr_ge_lin_filt_plot), ggplotGrob(ccle_ge_lin_filt_plot), nrow = 1, left = textGrob("E", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(ggplotGrob(crispr_ge_filt_plot), ggplotGrob(ccle_ge_filt_plot), ggplotGrob(ctrp_ge_filt_plot), ggplotGrob(gdsc_ge_filt_plot1), ggplotGrob(gdsc_ge_filt_plot2), nrow = 1, left = textGrob("F", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))))
 dev.off()

### 2020-01-04 19Q2.Rmd

@@
 
-g2p_prot <- unique(filter(g2p_mut, !is.na(Gene_Protein_Change) & !is.na(Drug)) %>% select(disease, Drug, Direction_Curated, Gene, Protein_Change, Gene_Protein_Change))
+g2p_prot <- unique(filter(g2p, !is.na(Gene_Protein_Change) & !is.na(Drug)) %>% select(disease, Drug, Direction_Curated, Gene, Protein_Change, Gene_Protein_Change))
 g2p_prot$Drug_Gene_Protein_Change <- with(g2p_prot, ifelse(is.na(Drug) | is.na(Gene_Protein_Change), NA, paste0(Drug, "_", Gene_Protein_Change)))
@@
 crispr_prot$Drug_Gene_Protein_Change_Lineage <- with(crispr_prot, ifelse(is.na(Drug) | is.na(Gene_Protein_Change) | is.na(disease), NA, paste0(Drug, "_", Gene_Protein_Change, "_", disease)))
-crispr_prot$G2P_Drug_Gene_Protein_Change <- "No"
-crispr_prot$G2P_Protein_Change <- ifelse(crispr_prot$Gene_Protein_Change %in% unique(as.character(g2p_prot$Gene_Protein_Change)), "Yes", "No")
-crispr_prot$G2P_Drug_Gene_Protein_Change_Lineage <- "No"
-crispr_prot <- merge(crispr_prot, unique(select(g2p_prot, Gene_Protein_Change, Direction_Curated)), by = "Gene_Protein_Change", all.x = TRUE)
+
 crispr_prot$Database <- "CRISPR"
 
-saveRDS(crispr_prot, "./../htscreens_giant_files/crispr_protein_changes_20191223.rds", compress = "xz")
+saveRDS(crispr_prot, "./../htscreens_giant_files/crispr_protein_changes_20200103.rds", compress = "xz")
 ```
@@
 # crispr_prot <- readRDS("./../htscreens_giant_files/crispr_protein_changes.rds")
-crispr_prot <- readRDS("./../htscreens_giant_files/crispr_protein_changes_20191223.rds")
+crispr_prot <- readRDS("./../htscreens_giant_files/crispr_protein_changes_20200103.rds")
 ```
@@
 
+```{r}
+dataframe = crispr_prot
+grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change")
+g2p_list = unique(as.character(g2p_prot$Gene_Protein_Change[!is.na(g2p_prot$Gene_Protein_Change)]))
+outfile = "./data_munging/rds/crispr_signif_protein_changes.rds"
+
+    count_n <- dataframe %>% count(Drug_Gene_Protein_Change, Change_Status)
+    count_n_wide <- dcast(count_n, Drug_Gene_Protein_Change ~ Change_Status, value.var = "n", fill = 0) %>% separate(Drug_Gene_Protein_Change, sep = "_", c("Drug", "Gene_Protein_Change"), extra = "merge", remove = FALSE)
+    colnames(count_n_wide) <- c("Drug_Gene_Protein_Change", "Drug", "Gene_Protein_Change", "Change_Status_0_count", "Change_Status_1_count")
+    count_n_filt <- filter(count_n, n >= 3)
+    count_category <- count_n_filt %>% count(Drug_Gene_Protein_Change) %>% filter(n == 2)
+    dg_keep <- intersect(count_n_filt$Drug_Gene_Protein_Change, count_category$Drug_Gene_Protein_Change)
+    dataframe <- filter(dataframe, Drug_Gene_Protein_Change %in% dg_keep)
+    dataframe$Drug_Gene_Protein_Change <- as.character(dataframe$Drug_Gene_Protein_Change)
+    signif <- compare_means(Score ~ Change_Status, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
+    signif <- adj_signif(signif, alpha = 0.05)
+    signif <- signif[order(signif$p),]
+    signif <- merge(signif, count_n_wide, by = grouping, all = TRUE)
+    signif$`n WT/mut` <- with(signif, paste0(Change_Status_0_count, "/", Change_Status_1_count))
+    if(is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- ifelse(signif$Drug_Gene_Protein_Change %in% g2p_list, "Yes", "No") }
+    if(!is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- ifelse(signif$Gene_Protein_Change %in% g2p_list, "Yes", "No")  }
+```
+
 ```{r, eval=FALSE}
@@
 
-gene_prots <- union(union(unique(ccle_signif_prot$Gene_Protein_Change), union(unique(ctrp_signif_prot$Gene_Protein_Change), unique(gdsc_signif_prot$Gene_Protein_Change))), unique(crispr_signif_prot$Gene_Protein_Change))
-
-# all_directions <- unique(rbind(select(crispr_prot, Gene_Protein_Change, Drug, Direction_Curated), select(ccle_prot, Gene_Protein_Change, Drug, Direction_Curated), select(ctrp_prot, Gene_Protein_Change, Drug, Direction_Curated), select(gdsc_prot, Gene_Protein_Change, Drug, Direction_Curated)))
-# all_directions <- filter(all_directions, !is.na(Direction_Curated))
-# saveRDS(all_directions, "./data_munging/rds/protein_changes_directions.rds")
-all_directions <- readRDS("./data_munging/rds/protein_changes_directions.rds")
-
-crispr_signif_prot_4plot <- merge(merge(merge(crispr_signif_prot, unique(select(crispr_prot, Drug, Gene_Protein_Change)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(crispr_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE), all_directions,  by = c("Drug", "Gene_Protein_Change"), all.x = TRUE)
-ccle_signif_prot_4plot <- merge(merge(merge(ccle_signif_prot, unique(select(ccle_prot, Drug, Gene_Protein_Change)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(ccle_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE), all_directions,  by = c("Drug", "Gene_Protein_Change"), all.x = TRUE)
-ctrp_signif_prot_4plot <- merge(merge(merge(ctrp_signif_prot, unique(select(ctrp_prot, Drug, Gene_Protein_Change)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(ctrp_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE), all_directions,  by = c("Drug", "Gene_Protein_Change"), all.x = TRUE)
-gdsc_signif_prot_4plot <- merge(merge(merge(gdsc_signif_prot, unique(select(gdsc_prot, Drug, Gene_Protein_Change)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(gdsc_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE), all_directions,  by = c("Drug", "Gene_Protein_Change"), all.x = TRUE)
+gene_prots <- union(union(union(unique(ccle_signif_prot$Gene_Protein_Change), unique(ctrp_signif_prot$Gene_Protein_Change)), unique(gdsc_signif_prot$Gene_Protein_Change)), unique(crispr_signif_prot$Gene_Protein_Change))
+
+crispr_directions <- unique(select(g2p_prot, Gene_Protein_Change, Direction_Curated) %>% drop_na(Direction_Curated))
+crispr_directions_n <- crispr_directions %>% count(Gene_Protein_Change)
+crispr_directions <- merge(crispr_directions, crispr_directions_n, by = "Gene_Protein_Change", all = TRUE)
+crispr_directions$Direction_Curated <- with(crispr_directions, ifelse(n == 2, "both", Direction_Curated))
+crispr_directions <- unique(crispr_directions %>% select(-n))
+
+crispr_signif_prot_4plot <- merge(merge(merge(crispr_signif_prot, unique(select(crispr_prot, Drug, Gene_Protein_Change)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(crispr_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE), crispr_directions, by = "Gene_Protein_Change", all.x = TRUE)
+ccle_signif_prot_4plot <- merge(merge(merge(ccle_signif_prot, unique(select(ccle_prot, Drug, Gene_Protein_Change)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(ccle_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE), unique(select(g2p_prot, Drug, Gene_Protein_Change, Direction_Curated)),  by = c("Drug", "Gene_Protein_Change"), all.x = TRUE)
+ctrp_signif_prot_4plot <- merge(merge(merge(ctrp_signif_prot, unique(select(ctrp_prot, Drug, Gene_Protein_Change)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(ctrp_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE), unique(select(g2p_prot, Drug, Gene_Protein_Change, Direction_Curated)),  by = c("Drug", "Gene_Protein_Change"), all.x = TRUE)
+gdsc_signif_prot_4plot <- merge(merge(merge(gdsc_signif_prot, unique(select(gdsc_prot, Drug, Gene_Protein_Change)), by = c("Drug", "Gene_Protein_Change"), all.x = TRUE), expand.grid("Drug" = unique(gdsc_signif_prot$Drug), "Gene_Protein_Change" = gene_prots), by = c("Drug", "Gene_Protein_Change"), all = TRUE), unique(select(g2p_prot, Drug, Gene_Protein_Change, Direction_Curated)),  by = c("Drug", "Gene_Protein_Change"), all.x = TRUE)
 
@@
 
-all_directions <- readRDS("./data_munging/rds/protein_changes_directions.rds")
+crispr_directions <- unique(select(g2p_prot, Gene_Protein_Change_Lineage, Direction_Curated) %>% drop_na(Direction_Curated))
+crispr_directions_n <- crispr_directions %>% count(Gene_Protein_Change_Lineage)
+crispr_directions <- merge(crispr_directions, crispr_directions_n, by = "Gene_Protein_Change_Lineage", all = TRUE)
+crispr_directions$Direction_Curated <- with(crispr_directions, ifelse(n == 2, "both", Direction_Curated))
+crispr_directions <- unique(crispr_directions %>% select(-n))
 crispr_signif_prot_lin <- readRDS("./data_munging/rds/crispr_signif_protein_changes_lineage.rds")
-crispr_signif_prot_lin <- merge(crispr_signif_prot_lin, all_directions, by = c("Gene_Protein_Change", "Drug"), all.x = TRUE)
+crispr_signif_prot_lin <- merge(crispr_signif_prot_lin, crispr_directions, by = "Gene_Protein_Change_Lineage", all.x = TRUE)
+
 ccle_signif_prot_lin <- readRDS("./data_munging/rds/ccle_signif_protein_changes_lineage.rds")
-ccle_signif_prot_lin <- merge(ccle_signif_prot_lin, all_directions, by = c("Gene_Protein_Change", "Drug"), all.x = TRUE)
+ccle_signif_prot_lin <- merge(ccle_signif_prot_lin, unique(select(g2p_prot, Drug, Gene_Protein_Change, Drug_Gene_Protein_Change_Lineage, Direction_Curated)), by = c("Drug_Gene_Protein_Change_Lineage", "Gene_Protein_Change", "Drug"), all.x = TRUE)
+
 ctrp_signif_prot_lin <- readRDS("./data_munging/rds/ctrp_signif_protein_changes_lineage.rds")
-ctrp_signif_prot_lin <- merge(ctrp_signif_prot_lin, all_directions, by = c("Gene_Protein_Change", "Drug"), all.x = TRUE)
+ctrp_signif_prot_lin <- merge(ctrp_signif_prot_lin, unique(select(g2p_prot, Drug, Gene_Protein_Change, Drug_Gene_Protein_Change_Lineage, Direction_Curated)), by = c("Drug_Gene_Protein_Change_Lineage", "Gene_Protein_Change", "Drug"), all.x = TRUE)
+
 gdsc_signif_prot_lin <- readRDS("./data_munging/rds/gdsc_signif_protein_changes_lineage.rds")
-gdsc_signif_prot_lin <- merge(gdsc_signif_prot_lin, all_directions, by = c("Gene_Protein_Change", "Drug"), all.x = TRUE)
+gdsc_signif_prot_lin <- merge(gdsc_signif_prot_lin, unique(select(g2p_prot, Drug, Gene_Protein_Change, Drug_Gene_Protein_Change_Lineage, Direction_Curated)), by = c("Drug_Gene_Protein_Change_Lineage", "Gene_Protein_Change", "Drug"), all.x = TRUE)
 
@@
 
-## Figure 2: G2P summary heatmap
+## Data summaries
+
+```{r Supp2}
+# How many datasets each drug was screened in
+hta_data <- data.frame(Drug = rownames(g2p_dg_counts), CCLE = NA, CTRP = NA, GDSC = NA)
+hta_data$CCLE <- ifelse(hta_data$Drug %in% unique(ccle$Drug), 1, 0)
+hta_data$CTRP <- ifelse(hta_data$Drug %in% unique(ctrp$Drug), 1, 0)
+hta_data$GDSC <- ifelse(hta_data$Drug %in% unique(gdsc$Drug), 1, 0)
+rownames(hta_data) <- hta_data$Drug
+hta_data$Drug <- NULL
+hta_data$NumDatasetsScreened <- rowSums(hta_data)
+
+ggplot(data = g2p) +
+  geom_bar(mapping = aes(x = disease))
+
+# How many G2P indications are for each disease
+g2p_munge <- select(g2p, disease)
+g2p_munge <- g2p_munge %>% count(disease)
+g2p_munge$Perc <- g2p_munge$n / sum(g2p_munge$n) * 100
+g2p_munge <- g2p_munge[order(g2p_munge$Perc),]
+g2p_munge$disease <- factor(g2p_munge$disease, levels = g2p_munge$disease)
+ggplot(data = g2p_munge) +
+  geom_bar(mapping = aes(x = disease, y = Perc), stat = "identity") +
+  geom_text(aes(x = disease, y = Perc + 3, label = round(Perc, 1))) +
+  scale_y_continuous(breaks = seq(0, 100, by = 10), labels = seq(0, 100, by = 10)) +
+  coord_flip()
+```
+
+```{r eval=FALSE}
+ccle_ccls <- unique(ccle$DepMap_ID)
+ctrp_ccls <- unique(ctrp$DepMap_ID)
+gdsc_ccls <- unique(gdsc$DepMap_ID)
+crispr_ccls <- unique(crispr$DepMap_ID)
+# overlap <- calculate.overlap(x = list("CCLE" = ccle_ccls, "CTRP" = ctrp_ccls, "GDSC" = gdsc_ccls, "CRISPR" = crispr_ccls))
+
+ccl_filter <- filter(ccl_meta, DepMap_ID %in% Reduce(intersect, list(ccle_ccls, ctrp_ccls, gdsc_ccls, crispr_ccls)))
+
+futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
+ccl_venn <- venn.diagram(x = list(ccle_ccls, ctrp_ccls, gdsc_ccls, crispr_ccls),
+             filename = NULL,
+             height = 2000, width = 2000, resolution = 500,
+             lwd = 1, cex = 1,
+             category.names = c("CCLE", "CTRP", "GDSC", "CRISPR"),
+             cat.cex = 1.4, cat.fontface = "bold", cat.default.pos = "outer",
+             # cat.dist = c(0.06, 0.06, 0.035),
+             fill = c("springgreen4", "steelblue4", "turquoise4", "darkorchid"))
+
+ccle_drugs <- unique(ccle$Drug)
+ctrp_drugs <- unique(ctrp$Drug)
+gdsc_drugs <- unique(gdsc$Drug)
+
+futile.logger::flog.threshold(futile.logger::ERROR, name = "VennDiagramLogger")
+drug_venn <- venn.diagram(x = list(ccle_drugs, ctrp_drugs, gdsc_drugs),
+             filename = NULL,
+             height = 2000, width = 2000, resolution = 500,
+             lwd = 1, cex = 1.4,
+             category.names = c("CCLE", "CTRP", "GDSC"),
+             cat.cex = 1.4, cat.fontface = "bold", cat.default.pos = "outer",
+             cat.dist = c(0.06, 0.06, 0.035),
+             fill = c("palegreen3", "slategray3", "paleturquoise3"))
+```
+
+```{r Supp1_summary, fig.height=7, fig.width=20, warning=FALSE, eval=FALSE}
+maf_g2p <- filter(maf_df, Gene %in% g2p_gene_order) %>% merge(ccl_meta, by = "DepMap_ID")
+maf_g2p <- with(maf_g2p, maf_g2p[order(disease),])
+maf_g2p_wide <- dcast(data = maf_g2p, formula = Gene ~ DepMap_ID, value.var = "Mutation", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
+maf_g2p_wide <- ifelse(maf_g2p_wide == 1, "Mutant", "Wildtype")
+maf_g2p_annot_df <- unique(select(maf_g2p, DepMap_ID, disease)) %>% `rownames<-`(.[,1]) %>% select(-DepMap_ID) %>% `colnames<-`("Lineage")
+
+# Cell line/mutation heatmap
+maf_g2p_annot <- HeatmapAnnotation(df = maf_g2p_annot_df, annotation_name_side = "left", annotation_legend_param = list(Lineage = list(title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 12), title_position = "topleft", nrow = 5)))
+
+maf_g2p_legend_list <- list(title = "Mutation status", legend_direction = "horizontal", border = "gray70", nrow = 1, title_gp = gpar(fontsize = 20), labels_gp = gpar(fontsize = 12))
+
+maf_g2p_ht <- Heatmap(maf_g2p_wide,
+                      col = c("Mutant" = "black", "Wildtype" = "white"),
+                      rect_gp = gpar(col = "white"),
+                      heatmap_legend_param = maf_g2p_legend_list,
+                      cluster_rows = FALSE, 
+                      cluster_columns = TRUE, 
+                      row_names_side = "left",
+                      row_names_gp = gpar(fontsize = 10),
+                      show_column_names = FALSE,
+                      row_title = "Genes",
+                      row_title_gp = gpar(fontface = "bold", fontsize = 20),
+                      column_title = "Cell lines", 
+                      column_title_gp = gpar(fontface = "bold", fontsize = 20),
+                      column_title_side = "top",
+                      top_annotation = maf_g2p_annot)
+
+draw(maf_g2p_ht, gap = unit(0.25, "in"), heatmap_legend_side = "top", annotation_legend_side = "top")
+```
+
+```{r supp_stats, eval=FALSE}
+maf_g2p_summ_gene <- maf_g2p %>% group_by(Gene) %>% count(Mutation) %>% filter (Mutation == 1) %>% merge(unique(select(maf_g2p, DepMap_ID, Gene)) %>% count(Gene), by = "Gene", suffixes = c("_mut", "_cell_lines"), all = TRUE)
+maf_g2p_summ_gene$PercCellLinesMutated <- maf_g2p_summ_gene$n_mut/maf_g2p_summ_gene$n_cell_lines * 100
+
+maf_g2p_summ <- maf_g2p %>% group_by(disease) %>% count(Mutation) %>% filter (Mutation == 1) %>% merge(unique(select(maf_g2p, DepMap_ID, disease)) %>% count(disease), by = "disease", suffixes = c("_mut", "_cell_lines"), all = TRUE)
+maf_g2p_summ$MutPerCCL <- maf_g2p_summ$n_mut/maf_g2p_summ$n_cell_lines
+
+sum(maf_g2p_summ$n_cell_lines)
+777/1588
+sum(maf_g2p_summ$n_mut[!is.na(maf_g2p_summ$n_mut)])
+2067/3151
+```
+
+## G2P summary heatmap
 
@@
 
-png(filename = "./plots/manuscript/figure2_g2p_summary_heatmap.png", width = 10, height = 9, units = "in", res = 500)
+png(filename = "./plots/manuscript_final/g2p_summary_heatmap.png", width = 10, height = 9, units = "in", res = 500)
 draw(hta + ht, gap = unit(5, "mm"), heatmap_legend_side = "top")
@@
 
-## Figure 3: Mutation status
+## Mutation status
+
+```{r fig.height=8, fig.width=15, eval=FALSE}
+ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "mutation", legend_title = "CCLE -log10(p-value)", legend_breaks = seq(0, 12, by = 3), row_names = FALSE, color = "darkgreen", col_title = "", row_title_txt = "Genes", radius = 0.023)
+ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "mutation", legend_title = "CTRP -log10(p-value)", legend_breaks = seq(0, 18, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.008)
+ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "mutation", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes", radius = 0.011)
+ht_crispr2 <- MakeWilcoxonHeatmap(signif_df = filter(crispr_signif_g2p_g, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "crispr", legend_title = "CRISPR -log10(p-value)", legend_breaks = seq(0, 45, by = 9), row_names = TRUE, color = "darkorchid4", col_title = "", row_title_txt = "Genes", radius = 0.15)
+ht_mut_list <- ht_crispr2 + ht_ccle2 + ht_ctrp2 + ht_gdsc2
+ht_mut_grob <- grid.grabExpr(draw(ht_mut_list, gap = unit(0.25, "in"), heatmap_legend_side = "top"))
+
+crispr_signif_g2p_dg_summ <- filter(crispr_signif_g2p_g, InG2P == "Yes") 
+ccle_signif_g2p_dg_summ <- filter(ccle_signif_g2p_dg, InG2P == "Yes") 
+ctrp_signif_g2p_dg_summ <- filter(ctrp_signif_g2p_dg, InG2P == "Yes") 
+gdsc_signif_g2p_dg_summ <- filter(gdsc_signif_g2p_dg, InG2P == "Yes")
+
+crispr_mut_filt <- filter(crispr, Gene %in% filter(crispr_signif_g2p_dg_summ, p < 0.05)$Gene)
+crispr_mut_filt_plot <- ggplot(data = crispr_mut_filt, aes(x = as.character(Mutation), y = Score) )+
+  facet_wrap(~ Gene, ncol = 5) +
+  geom_violin(aes(fill = as.character(Mutation))) +
+  geom_boxplot(outlier.shape = NA, width = 0.07) +
+  scale_x_discrete(labels = c("0" = "Wildtype", "1" = "Mutant")) +
+  scale_fill_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "darkorchid", "0" = "thistle")) +
+  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.4) +
+  labs(title = "CRISPR", x = "Mutation Status") +
+  theme(legend.position = "none", axis.title.x = element_blank(),
+        panel.background = element_rect(fill = "snow1", colour = "snow1", size = 0.5, linetype = "solid"),
+        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+
+ccle_mut_filt <- filter(ccle, Drug_Gene %in% filter(ccle_signif_g2p_dg_summ, p < 0.05)$Drug_Gene)
+ccle_mut_filt_plot <- ggplot(data = ccle_mut_filt, mapping = aes(x = as.character(Mutation), y = Score)) +
+  facet_wrap(~ Drug_Gene, ncol = 5) +
+  geom_violin(aes(fill = as.character(Mutation))) +
+  geom_boxplot(outlier.shape = NA, width = 0.07) +
+  scale_x_discrete(labels = c("0" = "Wildtype", "1" = "Mutant")) +
+  scale_fill_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "springgreen4", "0" = "palegreen3")) +
+  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.4) +
+  labs(title = "CCLE", x = "Mutation Status") +
+  theme(legend.position = "none", axis.title.x = element_blank(),
+        panel.background = element_rect(fill = "mintcream", colour = "mintcream", size = 0.5, linetype = "solid"),
+        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+
+ctrp_mut_filt <- filter(ctrp, Drug_Gene %in% filter(ctrp_signif_g2p_dg_summ, p < 0.05)$Drug_Gene)
+ctrp_mut_filt_plot <- ggplot(data = ctrp_mut_filt, mapping = aes(x = as.character(Mutation), y = Score)) +
+  facet_wrap(~ Drug_Gene, ncol = 7) +
+  geom_violin(aes(fill = as.character(Mutation))) +
+  geom_boxplot(outlier.shape = NA, width = 0.07,) +
+  scale_x_discrete(labels = c("0" = "Wildtype", "1" = "Mutant")) +
+  scale_fill_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "steelblue4", "0" = "slategray3")) +
+  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.4) +
+  labs(title = "CTRP", x = "Mutation Status") +
+  theme(legend.position = "none", axis.title.x = element_blank(),
+        panel.background = element_rect(fill = "whitesmoke", colour = "whitesmoke", size = 0.5, linetype = "solid"),
+        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+
+gdsc_mut_filt <- filter(gdsc, Drug_Gene %in% filter(gdsc_signif_g2p_dg_summ, p < 0.05)$Drug_Gene)
+gdsc_mut_filt_plot <- ggplot(data = gdsc_mut_filt, mapping = aes(x = as.character(Mutation), y = Score)) +
+  facet_wrap(~ Drug_Gene, ncol = 5) +
+  geom_violin(aes(fill = as.character(Mutation))) +
+  geom_boxplot(outlier.shape = NA, width = 0.07, ) +
+  scale_x_discrete(labels = c("0" = "Wildtype", "1" = "Mutant")) +
+  scale_fill_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "turquoise4", "0" = "paleturquoise3")) +
+  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.4) +
+  labs(title = "GDSC", x = "Mutation Status") +
+  theme(legend.position = "none", axis.title.x = element_blank(),
+        panel.background = element_rect(fill = "lightcyan", colour = "lightcyan", size = 0.5, linetype = "solid"),
+        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+
+lay <- rbind(c(1, 1, 1, 1, 1),
+             c(1, 1, 1, 1, 1),
+             c(1, 1, 1, 1, 1),
+             c(2, 2, 2, 2, 2),
+             c(3, 3, 5, 5, 5),
+             c(4, 4, 4, 4, 4))
+
+png(filename = "./plots/manuscript_final/all_mutation_agnostic_boxplots.png", width = 15, height = 15, units = "in", res = 500)
+grid.arrange(layout_matrix = lay,
+             arrangeGrob(ht_mut_grob, left = textGrob("A", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(ggplotGrob(crispr_mut_filt_plot), left = textGrob("B", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(ggplotGrob(ccle_mut_filt_plot), left = textGrob("C", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(ggplotGrob(ctrp_mut_filt_plot), left = textGrob("D", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(ggplotGrob(gdsc_mut_filt_plot), left = textGrob("E", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))))
+dev.off()
+```
+
+## Protein changes
+
+```{r prot_changes, eval = FALSE, fig.height=15, fig.width=15}
+ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot_4plot, feature = "protein changes", legend_title = "CCLE -log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "darkgreen", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.021)
+ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot_4plot, feature = "protein changes", legend_title = "CTRP -log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.009)
+ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = gdsc_signif_prot_4plot, feature = "protein changes", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 8, by = 2), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.0125)
+ht_crispr2 <- MakeWilcoxonHeatmap(signif_df = crispr_signif_prot_4plot, feature = "protein changes CRISPR", legend_title = "CRISPR -log10(p-value)", legend_breaks = seq(0, 25, by = 5), row_names = TRUE, color = "darkorchid4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.135)
+ht_prot_list <- ht_crispr2 + ht_ccle2 + ht_ctrp2 + ht_gdsc2
+ht_prot_grob <- grid.grabExpr(draw(ht_prot_list, gap = unit(0.25, "in"), heatmap_legend_side = "top"))
+
+crispr_signif_prot_summ <- filter(crispr_signif_prot, InG2P == "Yes") 
+ccle_signif_prot_summ <- filter(ccle_signif_prot, InG2P == "Yes") 
+ctrp_signif_prot_summ <- filter(ctrp_signif_prot, InG2P == "Yes") 
+gdsc_signif_prot_summ <- filter(gdsc_signif_prot, InG2P == "Yes")
+
+crispr_prot_filt <- filter(crispr_prot, Gene_Protein_Change %in% filter(crispr_signif_prot_summ, p < 0.05)$Gene_Protein_Change)
+crispr_prot_filt_plot <- ggplot(data = crispr_prot_filt, aes(x = as.character(Change_Status), y = Score) )+
+  facet_wrap(~ Gene_Protein_Change, nrow = 2) +
+  geom_violin(aes(fill = as.character(Change_Status))) +
+  geom_boxplot(outlier.shape = NA, width = 0.07) +
+  scale_x_discrete(labels = c("No" = "Wildtype", "Yes" = "Mutant")) +
+  scale_fill_manual(name = "Protein Change Status", labels = c("Wildtype", "Mutant"), values = c("Yes" = "darkorchid", "No" = "thistle")) +
+  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.4) +
+  labs(title = "CRISPR", x = "Protein Change Status") +
+  theme(legend.position = "none", axis.title.x = element_blank(),
+        panel.background = element_rect(fill = "snow1", colour = "snow1", size = 0.5, linetype = "solid"),
+        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+
+ccle_prot_filt <- filter(ccle_prot, Drug_Gene_Protein_Change %in% filter(ccle_signif_prot_summ, p < 0.05)$Drug_Gene_Protein_Change)
+
+ctrp_prot_filt <- filter(ctrp_prot, Drug_Gene_Protein_Change %in% filter(ctrp_signif_prot_summ, p < 0.05)$Drug_Gene_Protein_Change)
+ctrp_prot_filt_plot <- ggplot(data = ctrp_prot_filt, mapping = aes(x = as.character(Change_Status), y = Score)) +
+  facet_wrap(~ Drug_Gene_Protein_Change, nrow = 2) +
+  geom_violin(aes(fill = as.character(Change_Status))) +
+  geom_boxplot(outlier.shape = NA, width = 0.07,) +
+  scale_x_discrete(labels = c("No" = "Wildtype", "Yes" = "Mutant")) +
+  scale_fill_manual(name = "Protein Change Status", labels = c("Wildtype", "Mutant"), values = c("Yes" = "steelblue4", "No" = "slategray3")) +
+  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.4) +
+  labs(title = "CTRP", x = "Protein Change Status") +
+  theme(legend.position = "none", axis.title.x = element_blank(),
+        panel.background = element_rect(fill = "whitesmoke", colour = "whitesmoke", size = 0.5, linetype = "solid"),
+        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+
+gdsc_prot_filt <- filter(gdsc_prot, Drug_Gene_Protein_Change %in% filter(gdsc_signif_prot_summ, p < 0.05)$Drug_Gene_Protein_Change)
+gdsc_prot_filt_plot <- ggplot(data = gdsc_prot_filt, mapping = aes(x = as.character(Change_Status), y = Score)) +
+  facet_wrap(~ Drug_Gene_Protein_Change, nrow = 2) +
+  geom_violin(aes(fill = as.character(Change_Status))) +
+  geom_boxplot(outlier.shape = NA, width = 0.07, ) +
+  scale_x_discrete(labels = c("No" = "Wildtype", "Yes" = "Mutant")) +
+  scale_fill_manual(name = "Protein Change Status", labels = c("Wildtype", "Mutant"), values = c("Yes" = "turquoise4", "No" = "paleturquoise3")) +
+  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.4) +
+  labs(title = "GDSC", x = "Protein Change Status") +
+  theme(legend.position = "none", axis.title.x = element_blank(),
+        panel.background = element_rect(fill = "lightcyan", colour = "lightcyan", size = 0.5, linetype = "solid"),
+        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+
+lay <- rbind(c(1, 1, 1, 1, 1),
+             c(2, 2, 2, 2, 4),
+             c(3, 3, 3, 3, 3))
+
+png(filename = "./plots/manuscript_final/all_protein_change_agnostic_boxplots.png", width = 15, height = 15, units = "in", res = 500)
+grid.arrange(layout_matrix = lay,
+             arrangeGrob(ht_prot_grob, left = textGrob("A", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(ggplotGrob(crispr_prot_filt_plot), left = textGrob("B", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(ggplotGrob(ctrp_prot_filt_plot), left = textGrob("C", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(ggplotGrob(gdsc_prot_filt_plot), left = textGrob("D", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))))
+dev.off()
+```
+
+**1/3: Need to do CN and GE and lineage specific analyses**
+
+## First draft figures
 
@@
 
-## Figure 4: Protein changes
-
 ```{r Figure4_protein_change, fig.height=12, fig.width=12, eval=FALSE}
@@
 ```
-
-## Figure 5: Copy number
 
@@
 
-## Figure 6: Gene expression
-
 ```{r Figure6_ge, fig.height=8, fig.width=12, eval=FALSE}

### 2020-01-06 19Q2.Rmd

@@
 png(filename = "./plots/manuscript/all_cn_heatmap.png", width = 13, height = 3.5, units = "in", res = 500)
-draw(crispr_cn_ht2 +ccle_cn_ht2 + ctrp_cn_ht2 + gdsc_cn_ht2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
+draw(crispr_cn_ht2 + ccle_cn_ht2 + ctrp_cn_ht2 + gdsc_cn_ht2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
 dev.off()
@@
 ht_mut_list <- ht_crispr2 + ht_ccle2 + ht_ctrp2 + ht_gdsc2
-ht_mut_grob <- grid.grabExpr(draw(ht_mut_list, gap = unit(0.25, "in"), heatmap_legend_side = "top"))
+lgd <- list(Legend(labels = c("Resistance", "Sensitivity", "p < 0.05"), type = "points", pch = c(21, 21, 8), nrow = 1, background = "white", legend_gp = gpar(col = "black", fill = c("red", "white"))))
+ht_mut_grob <- grid.grabExpr(draw(ht_mut_list, gap = unit(0.25, "in"), heatmap_legend_side = "top", annotation_legend_list = lgd, annotation_legend_side = "top", merge_legend = TRUE))
 
@@
   scale_x_discrete(labels = c("0" = "Wildtype", "1" = "Mutant")) +
+  scale_y_continuous(breaks = seq(-3, 1, by = 0.5), labels = c("-3.0", "-2.5", "-2.0", "-1.5", "-1.0", "-0.5", "0.0", "0.5", "1.0")) +
   scale_fill_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "darkorchid", "0" = "thistle")) +
-  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.4) +
-  labs(title = "CRISPR", x = "Mutation Status") +
+  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35, label.y = 1.1) +
+  labs(title = "CRISPR", x = "Mutation Status", y = "CERES Score") +
   theme(legend.position = "none", axis.title.x = element_blank(),
@@
   scale_fill_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "springgreen4", "0" = "palegreen3")) +
-  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.4) +
-  labs(title = "CCLE", x = "Mutation Status") +
+  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35, label.y = 1.1) +
+  labs(title = "CCLE", x = "Mutation Status", y = "AUC") +
   theme(legend.position = "none", axis.title.x = element_blank(),
@@
   scale_fill_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "steelblue4", "0" = "slategray3")) +
-  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.4) +
-  labs(title = "CTRP", x = "Mutation Status") +
+  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35, label.y = 1.1) +
+  labs(title = "CTRP", x = "Mutation Status", y = "AUC") +
   theme(legend.position = "none", axis.title.x = element_blank(),
@@
   scale_fill_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "turquoise4", "0" = "paleturquoise3")) +
-  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.4) +
-  labs(title = "GDSC", x = "Mutation Status") +
+  scale_y_continuous(breaks = seq(0, 1.00, by = 0.25), labels = c("0.00", "0.25", "0.50", "0.75", "1.00")) +
+  coord_cartesian(ylim = c(0, 1.10)) +
+  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35, label.y = 1.1) +
+  labs(title = "GDSC", x = "Mutation Status", y = "AUC") +
   theme(legend.position = "none", axis.title.x = element_blank(),
@@
 
-png(filename = "./plots/manuscript_final/all_mutation_agnostic_boxplots.png", width = 15, height = 15, units = "in", res = 500)
-grid.arrange(layout_matrix = lay,
-             arrangeGrob(ht_mut_grob, left = textGrob("A", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+gs_mut <- gList(arrangeGrob(ht_mut_grob, left = textGrob("A", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
              arrangeGrob(ggplotGrob(crispr_mut_filt_plot), left = textGrob("B", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
@@
              arrangeGrob(ggplotGrob(gdsc_mut_filt_plot), left = textGrob("E", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))))
+
+png(filename = "./plots/manuscript_final/mutation_pancancer_small.png", width = 15, height = 17, units = "in", res = 100)
+grid.arrange(layout_matrix = lay, grobs = gs_mut)
+dev.off()
+
+png(filename = "./plots/manuscript_final/mutation_pancancer.png", width = 15, height = 17, units = "in", res = 500)
+grid.arrange(layout_matrix = lay, grobs = gs_mut)
 dev.off()
@@
 ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot_4plot, feature = "protein changes", legend_title = "CCLE -log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "darkgreen", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.021)
-ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot_4plot, feature = "protein changes", legend_title = "CTRP -log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.009)
+ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot_4plot, feature = "protein changes", legend_title = "CTRP -log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.012)
 ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = gdsc_signif_prot_4plot, feature = "protein changes", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 8, by = 2), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.0125)
@@
 ht_prot_list <- ht_crispr2 + ht_ccle2 + ht_ctrp2 + ht_gdsc2
-ht_prot_grob <- grid.grabExpr(draw(ht_prot_list, gap = unit(0.25, "in"), heatmap_legend_side = "top"))
+lgd <- list(Legend(labels = c("Resistance", "Sensitivity", "p < 0.05"), type = "points", pch = c(21, 21, 8), nrow = 1, background = "white", legend_gp = gpar(col = "black", fill = c("red", "white"))))
+ht_prot_grob <- grid.grabExpr(draw(ht_prot_list, gap = unit(0.25, "in"), heatmap_legend_side = "top", annotation_legend_list = lgd, annotation_legend_side = "top", merge_legend = TRUE))
 
@@
   scale_x_discrete(labels = c("No" = "Wildtype", "Yes" = "Mutant")) +
+  scale_y_continuous(breaks = seq(-3, 1, by = 0.5), labels = c("-3.0", "-2.5", "-2.0", "-1.5", "-1.0", "-0.5", "0.0", "0.5", "1.0")) +
   scale_fill_manual(name = "Protein Change Status", labels = c("Wildtype", "Mutant"), values = c("Yes" = "darkorchid", "No" = "thistle")) +
-  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.4) +
-  labs(title = "CRISPR", x = "Protein Change Status") +
+  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35, label.y = 1.1) +
+  labs(title = "CRISPR", x = "Protein Change Status", y = "CERES Score") +
   theme(legend.position = "none", axis.title.x = element_blank(),
@@
   scale_x_discrete(labels = c("No" = "Wildtype", "Yes" = "Mutant")) +
+  scale_y_continuous(breaks = seq(0, 1.00, by = 0.25), labels = c("0.00", "0.25", "0.50", "0.75", "1.00")) +
+  coord_cartesian(ylim = c(0, 1.10)) +
   scale_fill_manual(name = "Protein Change Status", labels = c("Wildtype", "Mutant"), values = c("Yes" = "steelblue4", "No" = "slategray3")) +
-  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.4) +
-  labs(title = "CTRP", x = "Protein Change Status") +
+  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35, label.y = 1.1) +
+  labs(title = "CTRP", x = "Protein Change Status", y = "AUC") +
   theme(legend.position = "none", axis.title.x = element_blank(),
@@
   scale_x_discrete(labels = c("No" = "Wildtype", "Yes" = "Mutant")) +
+  scale_y_continuous(breaks = seq(0, 1.00, by = 0.25), labels = c("0.00", "0.25", "0.50", "0.75", "1.00")) +
+  coord_cartesian(ylim = c(0, 1.10)) +
   scale_fill_manual(name = "Protein Change Status", labels = c("Wildtype", "Mutant"), values = c("Yes" = "turquoise4", "No" = "paleturquoise3")) +
-  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.4) +
-  labs(title = "GDSC", x = "Protein Change Status") +
+  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35, label.y = 1.1) +
+  labs(title = "GDSC", x = "Protein Change Status", y = "AUC") +
   theme(legend.position = "none", axis.title.x = element_blank(),
@@
 
-png(filename = "./plots/manuscript_final/all_protein_change_agnostic_boxplots.png", width = 15, height = 15, units = "in", res = 500)
-grid.arrange(layout_matrix = lay,
-             arrangeGrob(ht_prot_grob, left = textGrob("A", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+gs_prot <- gList(arrangeGrob(ht_prot_grob, left = textGrob("A", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
              arrangeGrob(ggplotGrob(crispr_prot_filt_plot), left = textGrob("B", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
@@
              arrangeGrob(ggplotGrob(gdsc_prot_filt_plot), left = textGrob("D", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))))
-dev.off()
-```
-
-**1/3: Need to do CN and GE and lineage specific analyses**
+
+png(filename = "./plots/manuscript_final/protein_change_pancancer_small.png", width = 15, height = 15, units = "in", res = 100)
+grid.arrange(layout_matrix = lay, grobs = gs_prot)
+dev.off()
+
+png(filename = "./plots/manuscript_final/protein_change_pancancer.png", width = 15, height = 15, units = "in", res = 500)
+grid.arrange(layout_matrix = lay, grobs = gs_prot)
+dev.off()
+```
+
+## CN/GE
+
+```{r CN_GE, eval = FALSE, fig.height=10, fig.width=15}
+# Copy number
+
+crispr_cn_cor_4plot <- unfactorize(filter(cn_cor, Dataset == "CRISPR" & Gene %in% unique(g2p_amp$Gene)))
+ccle_cn_cor_4plot <- unfactorize(filter(cn_cor, Dataset == "CCLE" & Gene %in% unique(g2p_amp$Gene)))
+ctrp_cn_cor_4plot <- unfactorize(filter(cn_cor, Dataset == "CTRP" & Gene %in% unique(g2p_amp$Gene)))
+gdsc_cn_cor_4plot <- unfactorize(filter(cn_cor, Dataset == "GDSC" & Gene %in% unique(g2p_amp$Gene)))
+crispr_cn_ht2 <- MakeCorrHeatmap(cor_res = crispr_cn_cor_4plot, row_names = TRUE, heatmap_legend = TRUE, col_title = "CRISPR", color_range = c(-0.25, 0, 0.25), radius = 0.15, legend_title = "Copy num.
+Spearman correlation", metric = "CN")
+ccle_cn_ht2 <- MakeCorrHeatmap(cor_res = ccle_cn_cor_4plot, row_names = FALSE, heatmap_legend = FALSE, col_title = "CCLE", color_range = c(-0.25, 0, 0.25), radius = 0.025, legend_title = "Copy num.
+Spearman correlation", metric = "CN")
+ctrp_cn_ht2 <- MakeCorrHeatmap(cor_res = ctrp_cn_cor_4plot, row_names = FALSE, heatmap_legend = FALSE, col_title = "CTRP", color_range = c(-0.25, 0, 0.25), radius = 0.025, legend_title = "Copy num.
+Spearman correlation", metric = "CN")
+gdsc_cn_ht2 <- MakeCorrHeatmap(cor_res = gdsc_cn_cor_4plot, row_names = FALSE, heatmap_legend = FALSE, col_title = "GDSC", color_range = c(-0.25, 0, 0.25), radius = 0.025, legend_title = "Copy num.
+Spearman correlation", metric = "CN")
+ht_cn_list <- crispr_cn_ht2 + ccle_cn_ht2 + ctrp_cn_ht2 + gdsc_cn_ht2
+lgd <- list(Legend(labels = c("Resistance", "Sensitivity", "p < 0.05"), type = "points", pch = c(21, 21, 8), nrow = 3, background = "white", legend_gp = gpar(col = "black", fill = c("red", "white"))))
+ht_cn_grob <- grid.grabExpr(draw(ht_cn_list, gap = unit(0.25, "in"), heatmap_legend_side = "top", annotation_legend_list = lgd, annotation_legend_side = "top", merge_legend = TRUE))
+
+cn_cor$p.format <- with(cn_cor, ifelse(CN_p < 0.001, "p < 0.001", paste0("p = ", round(CN_p, digits = 3))))
+crispr_cn_cor <- unfactorize(filter(cn_cor, Dataset == "CRISPR" & InG2P == "Yes"))
+ccle_cn_cor <- unfactorize(filter(cn_cor, Dataset == "CCLE" & InG2P == "Yes"))
+ctrp_cn_cor <- unfactorize(filter(cn_cor, Dataset == "CTRP" & InG2P == "Yes"))
+gdsc_cn_cor <- unfactorize(filter(cn_cor, Dataset == "GDSC" & InG2P == "Yes"))
+
+crispr_cn_cor_filt <- filter(crispr_cn_cor, CN_p < 0.05)
+crispr_cn_filt <- filter(crispr, Gene %in% crispr_cn_cor_filt$Gene)
+crispr_text <- data.frame(label = paste0("r = ", round(crispr_cn_cor_filt$CN_r, digits = 3), ",\n", crispr_cn_cor_filt$p.format), Gene = crispr_cn_cor_filt$Gene)
+crispr_cn_filt_plot <- ggplot(data = crispr_cn_filt, aes(x = CN, y = Score) )+
+  facet_wrap(~ Gene) +
+  geom_point(fill = "darkorchid", pch = 21, size = 1, alpha = 0.7) +
+  geom_text(data = crispr_text,
+            mapping = aes(x = +Inf, y = +Inf, label = label,
+            hjust = 1.1, vjust = 1.2)) +
+  scale_y_continuous(breaks = seq(-3, 1, by = 0.5), labels = c("-3.0", "-2.5", "-2.0", "-1.5", "-1.0", "-0.5", "0.0", "0.5", "1.0")) +
+  labs(title = "CRISPR", x = "Copy number (log2)", y = "CERES Score") +
+  theme(legend.position = "none",
+        panel.background = element_rect(fill = "snow1", colour = "snow1", size = 0.5, linetype = "solid"),
+        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+
+ccle_cn_cor_filt <- filter(ccle_cn_cor, CN_p < 0.05)
+ccle_cn_filt <- filter(ccle, Drug_Gene %in% ccle_cn_cor_filt$Drug_Gene)
+ccle_text <- data.frame(label = paste0("r = ", round(ccle_cn_cor_filt$CN_r, digits = 3), ", ", ccle_cn_cor_filt$p.format), Drug_Gene = ccle_cn_cor_filt$Drug_Gene)
+ccle_cn_filt_plot <- ggplot(data = ccle_cn_filt, aes(x = CN, y = Score) )+
+  facet_wrap(~ Drug_Gene) +
+  geom_point(fill = "springgreen4", pch = 21, size = 1, alpha = 0.7) +
+  geom_text(data = ccle_text,
+            mapping = aes(x = +Inf, y = +Inf, label = label,
+            hjust = 1.05, vjust = 1.2)) +
+  labs(title = "CCLE", x = "Copy number (log2)", y = "AUC") +
+  theme(legend.position = "none",
+        panel.background = element_rect(fill = "mintcream", colour = "mintcream", size = 0.5, linetype = "solid"),
+        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+
+ctrp_cn_cor_filt <- filter(ctrp_cn_cor, CN_p < 0.05)
+ctrp_cn_filt <- filter(ctrp, Drug_Gene %in% ctrp_cn_cor_filt$Drug_Gene)
+ctrp_text <- data.frame(label = paste0("r = ", round(ctrp_cn_cor_filt$CN_r, digits = 3), ",\n", ctrp_cn_cor_filt$p.format), Drug_Gene = ctrp_cn_cor_filt$Drug_Gene)
+ctrp_cn_filt_plot <- ggplot(data = ctrp_cn_filt, aes(x = CN, y = Score) )+
+  facet_wrap(~ Drug_Gene) +
+  geom_point(fill = "steelblue4", pch = 21, size = 1, alpha = 0.7) +
+  geom_text(data = ctrp_text,
+            mapping = aes(x = +Inf, y = +Inf, label = label,
+            hjust = 1.1, vjust = 1.2)) +
+  labs(title = "CTRP", x = "Copy number (log2)", y = "AUC") +
+  theme(legend.position = "none",
+        panel.background = element_rect(fill = "whitesmoke", colour = "whitesmoke", size = 0.5, linetype = "solid"),
+        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+
+gdsc_cn_cor_filt <- filter(gdsc_cn_cor, CN_p < 0.05)
+
+# Gene expression
+
+crispr_ge_cor_4plot <- unfactorize(filter(ge_cor, Dataset == "CRISPR" & Gene %in% unique(g2p_expr$Gene)))
+ccle_ge_cor_4plot <- unfactorize(filter(ge_cor, Dataset == "CCLE" & Gene %in% unique(g2p_expr$Gene)))
+ctrp_ge_cor_4plot <- unfactorize(filter(ge_cor, Dataset == "CTRP" & Gene %in% unique(g2p_expr$Gene)))
+gdsc_ge_cor_4plot <- unfactorize(filter(ge_cor, Dataset == "GDSC" & Gene %in% unique(g2p_expr$Gene)))
+crispr_ge_ht2 <- MakeCorrHeatmap(cor_res = crispr_ge_cor_4plot, row_names = TRUE, heatmap_legend = TRUE, col_title = "CRISPR", color_range = c(-0.5, 0, 0.5), radius = 0.155, legend_title = "Gene expr.
+Spearman correlation", metric = "GE")
+ccle_ge_ht2 <- MakeCorrHeatmap(cor_res = ccle_ge_cor_4plot, row_names = FALSE, heatmap_legend = FALSE, col_title = "CCLE", color_range = c(-0.5, 0, 0.5), radius = 0.07, legend_title = "Gene expr.
+Spearman correlation", metric = "GE")
+ctrp_ge_ht2 <- MakeCorrHeatmap(cor_res = ctrp_ge_cor_4plot, row_names = FALSE, heatmap_legend = FALSE, col_title = "CTRP", color_range = c(-0.5, 0, 0.5), radius = 0.07, legend_title = "Gene expr.
+Spearman correlation", metric = "GE")
+gdsc_ge_ht2 <- MakeCorrHeatmap(cor_res = gdsc_ge_cor_4plot, row_names = FALSE, heatmap_legend = FALSE, col_title = "GDSC", color_range = c(-0.5, 0, 0.5), radius = 0.07, legend_title = "Gene expr.
+Spearman correlation", metric = "GE")
+ht_ge_list <- crispr_ge_ht2 + ccle_ge_ht2 + ctrp_ge_ht2 + gdsc_ge_ht2
+ht_ge_grob <- grid.grabExpr(draw(ht_ge_list, gap = unit(0.25, "in"), heatmap_legend_side = "top", annotation_legend_list = lgd, annotation_legend_side = "top", merge_legend = TRUE))
+
+ge_cor$p.format <- with(ge_cor, ifelse(GE_p < 0.001, "p < 0.001", paste0("p = ", round(GE_p, digits = 3))))
+crispr_ge_cor <- unfactorize(filter(ge_cor, Dataset == "CRISPR" & InG2P == "Yes"))
+ccle_ge_cor <- unfactorize(filter(ge_cor, Dataset == "CCLE" & InG2P == "Yes"))
+ctrp_ge_cor <- unfactorize(filter(ge_cor, Dataset == "CTRP" & InG2P == "Yes"))
+gdsc_ge_cor <- unfactorize(filter(ge_cor, Dataset == "GDSC" & InG2P == "Yes"))
+
+crispr_ge_cor_filt <- filter(crispr_ge_cor, GE_p < 0.05)
+crispr_ge_filt <- filter(crispr, Gene %in% crispr_ge_cor_filt$Gene)
+crispr_text <- data.frame(label = paste0("r = ", round(crispr_ge_cor_filt$GE_r, digits = 3), ",\n", crispr_ge_cor_filt$p.format), Gene = crispr_ge_cor_filt$Gene)
+crispr_ge_filt_plot <- ggplot(data = crispr_ge_filt, aes(x = TPM, y = Score) )+
+  facet_wrap(~ Gene) +
+  geom_point(fill = "darkorchid", pch = 21, size = 1, alpha = 0.7) +
+  geom_text(data = crispr_text,
+            mapping = aes(x = +Inf, y = +Inf, label = label,
+            hjust = 1.1, vjust = 1.2)) +
+  scale_y_continuous(breaks = seq(-3, 1, by = 0.5), labels = c("-3.0", "-2.5", "-2.0", "-1.5", "-1.0", "-0.5", "0.0", "0.5", "1.0")) +
+  labs(title = "CRISPR", x = "Gene expression [log2(TPM)]", y = "CERES Score") +
+  theme(legend.position = "none",
+        panel.background = element_rect(fill = "snow1", colour = "snow1", size = 0.5, linetype = "solid"),
+        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+
+ccle_ge_cor_filt <- filter(ccle_ge_cor, GE_p < 0.05)
+ccle_ge_filt <- filter(ccle, Drug_Gene %in% ccle_ge_cor_filt$Drug_Gene)
+ccle_text <- data.frame(label = paste0("r = ", round(ccle_ge_cor_filt$GE_r, digits = 3), ", ", ccle_ge_cor_filt$p.format), Drug_Gene = ccle_ge_cor_filt$Drug_Gene)
+ccle_ge_filt_plot <- ggplot(data = ccle_ge_filt, aes(x = TPM, y = Score) )+
+  facet_wrap(~ Drug_Gene) +
+  geom_point(fill = "springgreen4", pch = 21, size = 1, alpha = 0.7) +
+  geom_text(data = ccle_text,
+            mapping = aes(x = +Inf, y = +Inf, label = label,
+            hjust = 1.37, vjust = 1.2)) +
+  labs(title = "CCLE", x = "Gene expression [log2(TPM)]", y = "AUC") +
+  theme(legend.position = "none",
+        panel.background = element_rect(fill = "mintcream", colour = "mintcream", size = 0.5, linetype = "solid"),
+        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+
+ctrp_ge_cor_filt <- filter(ctrp_ge_cor, GE_p < 0.05)
+ctrp_ge_filt <- filter(ctrp, Drug_Gene %in% ctrp_ge_cor_filt$Drug_Gene)
+ctrp_text <- data.frame(label = paste0("r = ", round(ctrp_ge_cor_filt$GE_r, digits = 3), ",\n", ctrp_ge_cor_filt$p.format), Drug_Gene = ctrp_ge_cor_filt$Drug_Gene)
+ctrp_ge_filt_plot <- ggplot(data = ctrp_ge_filt, aes(x = TPM, y = Score) )+
+  facet_wrap(~ Drug_Gene) +
+  geom_point(fill = "steelblue4", pch = 21, size = 1, alpha = 0.7) +
+  geom_text(data = ctrp_text,
+            mapping = aes(x = +Inf, y = +Inf, label = label,
+            hjust = 1.1, vjust = 9.1)) +
+  labs(title = "CTRP", x = "Gene expression [log2(TPM)]", y = "AUC") +
+  theme(legend.position = "none",
+        panel.background = element_rect(fill = "whitesmoke", colour = "whitesmoke", size = 0.5, linetype = "solid"),
+        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+
+gdsc_ge_cor_filt <- filter(gdsc_ge_cor, GE_p < 0.05)
+gdsc_ge_filt <- filter(gdsc, Drug_Gene %in% gdsc_ge_cor_filt$Drug_Gene)
+gdsc_text <- data.frame(label = paste0("r = ", round(gdsc_ge_cor_filt$GE_r, digits = 3), ",\n", gdsc_ge_cor_filt$p.format), Drug_Gene = gdsc_ge_cor_filt$Drug_Gene)
+gdsc_ge_filt_plot <- ggplot(data = gdsc_ge_filt, aes(x = TPM, y = Score) )+
+  facet_wrap(~ Drug_Gene) +
+  geom_point(fill = "turquoise4", pch = 21, size = 1, alpha = 0.7) +
+  geom_text(data = gdsc_text,
+            mapping = aes(x = +Inf, y = +Inf, label = label,
+            hjust = 1.1, vjust = 1.2)) +
+  scale_y_continuous(breaks = seq(0, 1.00, by = 0.25), labels = c("0.00", "0.25", "0.50", "0.75", "1.00")) +
+  coord_cartesian(ylim = c(0, 1.00)) +
+  labs(title = "GDSC", x = "Gene expression [log2(TPM)]", y = "AUC") +
+  theme(legend.position = "none",
+        panel.background = element_rect(fill = "lightcyan", colour = "lightcyan", size = 0.5, linetype = "solid"),
+        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+
+# Arrange figure
+
+hlay <- rbind(c(1, 1, 1, 1, 1, 1, 1),
+              c(1, 1, 1, 1, 1, 1, 1),
+              c(1, 1, 1, 1, 1, 1, 1),
+              c(2, 2, 3, 3, 4, NA, NA),
+              c(2, 2, 3, 3, 4, NA, NA),
+              c(2, 2, 3, 3, 4, NA, NA),
+              c(5, 5, 5, 5, 5, 5, 5),
+              c(5, 5, 5, 5, 5, 5, 5),
+              c(6, 7, 8, 8, 8, 9, 9),
+              c(6, 7, 8, 8, 8, 9, 9),
+              c(6, 7, 8, 8, 8, 9, 9))
+
+select_grobs <- function(lay) {
+  id <- unique(c(t(lay))) 
+  id[!is.na(id)]
+}
+
+gs_cn_ge <- gList(arrangeGrob(ht_cn_grob, left = textGrob("A", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(ggplotGrob(crispr_cn_filt_plot), left = textGrob("B", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(ggplotGrob(ccle_cn_filt_plot), left = textGrob("C", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(ggplotGrob(ctrp_cn_filt_plot), left = textGrob("D", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(ht_ge_grob, left = textGrob("E", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(ggplotGrob(crispr_ge_filt_plot), left = textGrob("F", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(ggplotGrob(ccle_ge_filt_plot), left = textGrob("G", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(ggplotGrob(ctrp_ge_filt_plot), left = textGrob("H", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(ggplotGrob(gdsc_ge_filt_plot), left = textGrob("I", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))))
+
+png(filename = "./plots/manuscript_final/cn_ge_pancancer_small.png", width = 20, height = 15, units = "in", res = 100)
+grid.arrange(layout_matrix = hlay, grobs = gs_cn_ge[select_grobs(hlay)])
+dev.off()
+
+png(filename = "./plots/manuscript_final/cn_ge_pancancer.png", width = 20, height = 15, units = "in", res = 500)
+grid.arrange(layout_matrix = hlay, grobs = gs_cn_ge[select_grobs(hlay)])
+dev.off()
+```
 

### 2020-01-07 manuscript.Rmd
edit

@@
 author              :
-- Sally E. Claridge
-- Daniel M. Charytonowicz
-- Adam A. Margolin
+- name: Sally E. Claridge
+  affiliation: Icahn School of Medicine at Mount Sinai
+- name: Daniel M. Charytonowicz
+  affiliation: Icahn School of Medicine at Mount Sinaiy
+- name: Adam A. Margolin
+  affiliation: Icahn School of Medicine at Mount Sinai
 date                : "`r format(Sys.time(), '%d %B %Y')`"

### 2020-01-07 19Q2.Rmd

@@
 
-```{r load_drug_rds}
+```{r load_drug_rds, eval=FALSE}
 # ccle_all <- readRDS("./../htscreens_giant_files/pozdeyev_data/pozdeyev2016_ccle_all_edited.rds")
@@
 
-```{r, eval = TRUE}
+```{r, eval=TRUE}
 crispr_fus <- readRDS("./data_munging/19Q2/crispr_fusions.rds")
@@
 
-```{r, eval = FALSE}
+```{r, eval=FALSE}
 crispr_allgenes <- readRDS("./../htscreens_giant_files/crispr_data_19Q2_allgenes.rds")
@@
 
+## Filter duplicate rows
+
+```{r, eval=FALSE}
+# All nrow = 0
+# crispr_prot_dup <- crispr_prot[duplicated(crispr_prot),]
+# ccle_prot_dup <- ccle_prot[duplicated(ccle_prot),]
+# ctrp_prot_dup <- ctrp_prot[duplicated(ctrp_prot),]
+# gdsc_prot_dup <- gdsc_prot[duplicated(gdsc_prot),]
+
+ccle <- readRDS("./data_munging/19Q2/ccle_data_19Q2.rds") %>% drop_na(Drug)
+ctrp <- readRDS("./../htscreens_giant_files/ctrp_data_19Q2.rds") %>% drop_na(Drug)
+gdsc <- readRDS("./data_munging/19Q2/gdsc_data_19Q2.rds") %>% drop_na(Drug)
+
+crispr <- readRDS("./data_munging/19Q2/crispr_data_19Q2.rds") %>% drop_na(Gene)
+crispr$Gene_Lin <- with(crispr, paste0(Gene, "_", disease))
+crispr_unique <- unique(crispr)
+saveRDS(crispr_unique, file = "./data_munging/19Q2/crispr_data_19Q2_unique.rds", compress = "xz")
+
+ccle_unique <- unique(ccle)
+saveRDS(ccle_unique, file = "./data_munging/19Q2/ccle_data_19Q2_unique.rds", compress = "xz")
+gdsc_unique <- unique(gdsc)
+saveRDS(gdsc_unique, file = "./data_munging/19Q2/gdsc_data_19Q2_unique.rds", compress = "xz")
+ctrp_filt <- filter(ctrp, Drug %in% g2p_drugs)
+ctrp_unique <- unique(ctrp_filt)
+saveRDS(ctrp_unique, file = "./data_munging/19Q2/ctrp_data_19Q2_g2pdrugs_unique.rds", compress = "xz")
+```
+
+```{r}
+crispr <- readRDS("./data_munging/19Q2/crispr_data_19Q2_unique.rds")
+ccle <- readRDS("./data_munging/19Q2/ccle_data_19Q2_unique.rds")
+ctrp <- readRDS("./data_munging/19Q2/gdsc_data_19Q2_unique.rds")
+gdsc <- readRDS("./data_munging/19Q2/ctrp_data_19Q2_g2pdrugs_unique.rds")
+```
+
 # EXPLORATORY FIGURES
@@
 ```{r ccl_venn, eval=FALSE}
+ccle <- readRDS("./data_munging/19Q2/ccle_data_19Q2.rds") %>% drop_na(Drug)
+ctrp <- readRDS("./../htscreens_giant_files/ctrp_data_19Q2.rds") %>% drop_na(Drug)
+gdsc <- readRDS("./data_munging/19Q2/gdsc_data_19Q2.rds") %>% drop_na(Drug)
+crispr <- readRDS("./data_munging/19Q2/crispr_data_19Q2.rds") %>% drop_na(Gene)
+
 ccle_ccls <- unique(ccle$DepMap_ID)
@@
 ```{r drug_venn, eval=FALSE}
+ccle <- readRDS("./data_munging/19Q2/ccle_data_19Q2.rds") %>% drop_na(Drug)
+ctrp <- readRDS("./../htscreens_giant_files/ctrp_data_19Q2.rds") %>% drop_na(Drug)
+gdsc <- readRDS("./data_munging/19Q2/gdsc_data_19Q2.rds") %>% drop_na(Drug)
+
 ccle_drugs <- unique(ccle$Drug)
@@
 
-```{r}
+```{r, eval=FALSE}
 dataframe = crispr_prot
@@
 
-# FIGURES
+# MANUSCRIPT
 
@@
 
-## Mutation status
-
-```{r fig.height=8, fig.width=15, eval=FALSE}
+## Mutation status figure
+
+```{r}
+crispr_g2p_count <- filter(crispr_signif_g2p_g, Gene %in% unique(g2p_mut$Gene), InG2P == "Yes")
+ccle_g2p_count <- filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene), InG2P == "Yes")
+ctrp_g2p_count <- filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene), InG2P == "Yes")
+gdsc_g2p_count <- filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene), InG2P == "Yes")
+```
+
+```{r mut_status_fig, fig.height=8, fig.width=15, eval=FALSE}
 ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "mutation", legend_title = "CCLE -log10(p-value)", legend_breaks = seq(0, 12, by = 3), row_names = FALSE, color = "darkgreen", col_title = "", row_title_txt = "Genes", radius = 0.023)
@@
   scale_fill_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "springgreen4", "0" = "palegreen3")) +
+  scale_y_continuous(breaks = seq(0, 1.00, by = 0.25), labels = c("0.00", "0.25", "0.50", "0.75", "1.00")) +
+  coord_cartesian(ylim = c(0, 1.10)) +
   stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35, label.y = 1.1) +
@@
   scale_fill_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "steelblue4", "0" = "slategray3")) +
+  scale_y_continuous(breaks = seq(0, 1.00, by = 0.25), labels = c("0.00", "0.25", "0.50", "0.75", "1.00")) +
+  coord_cartesian(ylim = c(0, 1.10)) +
   stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35, label.y = 1.1) +
@@
 
-## Protein changes
-
-```{r prot_changes, eval = FALSE, fig.height=15, fig.width=15}
+## Protein changes figure
+
+```{r}
+test2 <- select(g2p_prot, Direction_Curated, Gene,Gene_Protein_Change) %>% drop_na(Direction_Curated) %>% unique()
+unique(test2$Gene)
+
+crispr_g2p_prot<- filter(crispr_signif_prot, Gene_Protein_Change %in% unique(g2p_prot$Gene_Protein_Change), InG2P == "Yes")
+ccle_g2p_prot <- filter(ccle_signif_prot, Drug_Gene_Protein_Change %in% unique(g2p_prot$Drug_Gene_Protein_Change), InG2P == "Yes")
+sum(!is.na(ccle_g2p_prot$p))
+ctrp_g2p_prot <- filter(ctrp_signif_prot, Drug_Gene_Protein_Change %in% unique(g2p_prot$Drug_Gene_Protein_Change), InG2P == "Yes")
+sum(!is.na(ctrp_g2p_prot$p))
+gdsc_g2p_prot <- filter(gdsc_signif_prot, Drug_Gene_Protein_Change %in% unique(g2p_prot$Drug_Gene_Protein_Change), InG2P == "Yes")
+sum(!is.na(gdsc_g2p_prot$p))
+```
+
+```{r prot_changes_fig, eval=FALSE, fig.height=15, fig.width=15}
 ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot_4plot, feature = "protein changes", legend_title = "CCLE -log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "darkgreen", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.021)
@@
 
-## CN/GE
-
-```{r CN_GE, eval = FALSE, fig.height=10, fig.width=15}
+## CN/GE figure
+
+```{r CN_GE_fig, eval=FALSE, fig.height=10, fig.width=15}
 # Copy number
@@
 ctrp_cn_filt <- filter(ctrp, Drug_Gene %in% ctrp_cn_cor_filt$Drug_Gene)
-ctrp_text <- data.frame(label = paste0("r = ", round(ctrp_cn_cor_filt$CN_r, digits = 3), ",\n", ctrp_cn_cor_filt$p.format), Drug_Gene = ctrp_cn_cor_filt$Drug_Gene)
-ctrp_cn_filt_plot <- ggplot(data = ctrp_cn_filt, aes(x = CN, y = Score) )+
+# ctrp_text <- data.frame(label = paste0("r = ", round(ctrp_cn_cor_filt$CN_r, digits = 3), ",\n", ctrp_cn_cor_filt$p.format), Drug_Gene = ctrp_cn_cor_filt$Drug_Gene)
+# ctrp_cn_filt_plot <- ggplot(data = ctrp_cn_filt, aes(x = CN, y = Score) )+
+#   facet_wrap(~ Drug_Gene) +
+#   geom_point(fill = "steelblue4", pch = 21, size = 1, alpha = 0.7) +
+#   geom_text(data = ctrp_text,
+#             mapping = aes(x = +Inf, y = +Inf, label = label,
+#             hjust = 1.1, vjust = 1.2)) +
+#   labs(title = "CTRP", x = "Copy number (log2)", y = "AUC") +
+#   theme(legend.position = "none",
+#         panel.background = element_rect(fill = "whitesmoke", colour = "whitesmoke", size = 0.5, linetype = "solid"),
+#         panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+#         panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+
+gdsc_cn_cor_filt <- filter(gdsc_cn_cor, CN_p < 0.05)
+gdsc_cn_filt <- filter(gdsc, Drug_Gene %in% gdsc_cn_cor_filt$Drug_Gene)
+gdsc_text <- data.frame(label = paste0("r = ", round(gdsc_cn_cor_filt$CN_r, digits = 3), ",\n", gdsc_cn_cor_filt$p.format), Drug_Gene = gdsc_cn_cor_filt$Drug_Gene)
+gdsc_cn_filt_plot <- ggplot(data = gdsc_cn_filt, aes(x = CN, y = Score) )+
   facet_wrap(~ Drug_Gene) +
-  geom_point(fill = "steelblue4", pch = 21, size = 1, alpha = 0.7) +
-  geom_text(data = ctrp_text,
+  geom_point(fill = "turquoise4", pch = 21, size = 1, alpha = 0.7) +
+  geom_text(data = gdsc_text,
             mapping = aes(x = +Inf, y = +Inf, label = label,
             hjust = 1.1, vjust = 1.2)) +
-  labs(title = "CTRP", x = "Copy number (log2)", y = "AUC") +
+  labs(title = "GDSC", x = "Copy number (log2)", y = "AUC") +
   theme(legend.position = "none",
-        panel.background = element_rect(fill = "whitesmoke", colour = "whitesmoke", size = 0.5, linetype = "solid"),
+        panel.background = element_rect(fill = "lightcyan", colour = "lightcyan", size = 0.5, linetype = "solid"),
         panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"),
         panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
-
-gdsc_cn_cor_filt <- filter(gdsc_cn_cor, CN_p < 0.05)
 
@@
              arrangeGrob(ggplotGrob(ccle_cn_filt_plot), left = textGrob("C", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
-             arrangeGrob(ggplotGrob(ctrp_cn_filt_plot), left = textGrob("D", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(ggplotGrob(gdsc_cn_filt_plot), left = textGrob("D", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
              arrangeGrob(ht_ge_grob, left = textGrob("E", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
@@
 
-## First draft figures
+## Fusions
+
+Fusions are completely driven by HL lineage: HL cell lines are the only cell lines that contain ABL1-BCR, BCR-ABL1, and PML-PARA fusions.
+```{r}
+test <- unique(select(fus, disease, FusionPair, Fusion_Status)) %>% filter(Fusion_Status == "Yes")
+test
+```
+
+## Lineages
+
+Mutation:
+```{r}
+crispr_mut_lin <- filter(crispr_signif_lin, InG2P == "Yes")
+ccle_mut_lin <- filter(ccle_signif_dgl, InG2P == "Yes")
+ctrp_mut_lin <- filter(ctrp_signif_dgl, InG2P == "Yes")
+gdsc_mut_lin <- filter(gdsc_signif_dgl, InG2P == "Yes")
+```
+
+```{r}
+crispr_test <- filter(crispr, Gene_Lin == "PTCH1_skin")
+ggplot(crispr_test, aes(x = as.character(Mutation), y = Score)) +
+  geom_boxplot() +
+  geom_point() +
+  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35)
+```
+
+## OLD: First draft figures
 

### 2020-01-08 19Q2.Rmd

--- 2020-01-06 19Q2.Rmd
@@
 
+ccle_unique <- unique(ccle) # Pre: 1512092
+ctrp_unique <- unique(ctrp) # Pre: 47807047
+gdsc_unique <- unique(gdsc) # Pre: 10143182
+
 # Testing
@@
 crispr_prot_allgenes <- readRDS("./../htscreens_giant_files/crispr_protein_changes_allgenes.rds")
+```
+
+## DUPLICATES
+
+```{r}
+# All nrow = 0
+# crispr_prot_dup <- crispr_prot[duplicated(crispr_prot),]
+# ccle_prot_dup <- ccle_prot[duplicated(ccle_prot),]
+# ctrp_prot_dup <- ctrp_prot[duplicated(ctrp_prot),]
+# gdsc_prot_dup <- gdsc_prot[duplicated(gdsc_prot),]
+
 ```
@@
 ctrp_signif_g2p_dg_summ <- filter(ctrp_signif_g2p_dg, InG2P == "Yes") 
-gdsc_signif_g2p_dg_summ <- filter(gdsc_signif_g2p_dg, InG2P == "Yes")
+gdsc_signif_g2p_dg_summ <- filter(gdsc_signif_g2p_dg, InG2P == "Yes") q
 
@@
 
-## Protein changes
-
-```{r prot_changes, eval = FALSE, fig.height=15, fig.width=15}
+## Protein changes figure
+
+```{r}
+test2 <- select(g2p_prot, Direction_Curated, Gene,Gene_Protein_Change) %>% drop_na(Direction_Curated) %>% unique()
+unique(test2$Gene)
+
+crispr_g2p_prot<- filter(crispr_signif_prot, Gene_Protein_Change %in% unique(g2p_prot$Gene_Protein_Change), InG2P == "Yes")
+ccle_g2p_prot <- filter(ccle_signif_prot, Drug_Gene_Protein_Change %in% unique(g2p_prot$Drug_Gene_Protein_Change), InG2P == "Yes")
+sum(!is.na(ccle_g2p_prot$p))
+ctrp_g2p_prot <- filter(ctrp_signif_prot, Drug_Gene_Protein_Change %in% unique(g2p_prot$Drug_Gene_Protein_Change), InG2P == "Yes")
+sum(!is.na(ctrp_g2p_prot$p))
+gdsc_g2p_prot <- filter(gdsc_signif_prot, Drug_Gene_Protein_Change %in% unique(g2p_prot$Drug_Gene_Protein_Change), InG2P == "Yes")
+sum(!is.na(gdsc_g2p_prot$p))
+```
+
+```{r prot_changes_fig, eval = FALSE, fig.height=15, fig.width=15}
 ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot_4plot, feature = "protein changes", legend_title = "CCLE -log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "darkgreen", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.021)
@@
 
-## CN/GE
-
-```{r CN_GE, eval = FALSE, fig.height=10, fig.width=15}
+## CN/GE figure
+
+```{r CN_GE_fig, eval = FALSE, fig.height=10, fig.width=15}
 # Copy number
@@
 
-## First draft figures
+## Fusions
+
+Fusions are completely driven by HL lineage: HL cell lines are the only cell lines that contain ABL1-BCR, BCR-ABL1, and PML-PARA fusions.
+```{r}
+test <- unique(select(fus, disease, FusionPair, Fusion_Status)) %>% filter(Fusion_Status == "Yes")
+test
+```
+
+## Lineages
+
+Mutation:
+```{r}
+crispr_mut_lin <- filter(crispr_signif_lin, InG2P == "Yes")
+ccle_mut_lin <- filter(ccle_signif_dgl, InG2P == "Yes")
+ctrp_mut_lin <- filter(ctrp_signif_dgl, InG2P == "Yes")
+gdsc_mut_lin <- filter(gdsc_signif_dgl, InG2P == "Yes")
+```
+
+```{r}
+crispr_test <- filter(crispr, Gene_Lin == "PTCH1_skin")
+ggplot(crispr_test, aes(x = as.character(Mutation), y = Score)) +
+  geom_boxplot() +
+  geom_point() +
+  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35)
+```
+
+```{r}
+crispr_Dup <- crispr[duplicated(crispr),]
+ccle_Dup <- ccle[duplicated(ccle),]
+```
+
+## OLD: First draft figures
 

### 2020-01-10 19Q2.Rmd

@@
 library(openxlsx)
+library(plotly)
 library(reshape2)
 library(scales)
+library(see)
 library(stringr)
@@
 # Manually assign biomarker_types based on a combination of biomarker_type derived from the JSON string and patterns in the Feature.Names
-biomarker_type_curated <- 
-  ifelse(!is.na(str_match(string = tolower(g2p$biomarker_type), pattern = "copy number variant|amplification")[,1]) | !is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "copy number variant|amplification")), "Amplification/CNV",
-  ifelse(!is.na(str_match(string = toupper(g2p$Feature.Names), pattern = "[A-Z0-9|A-Z]+-[A-Z0-9|A-Z]+|FUSION|ALK POSITIVE")[,1]) & is.na(str_match(string = g2p$Feature.Names, pattern = "[0-9]+-[0-9]+")) | g2p$biomarker_type == "fusion" | g2p$biomarker_type == "rearrange", "Fusion",
-  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "[A-Z][0-9]+([A-Z]|[*])|[0-9A-Z]+ [A-Z][0-9]+|[A-Z][0-9]+$")[,1]), "Mutation",
-  ifelse(!is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "expression|methylation|erbb2  positive")[,1]), "Expression",
-  ifelse(!is.na(str_match(string = g2p$biomarker_type, pattern = "intron|insertion|deletion|mutant")[,1]), "Mutation",
-  ifelse(!is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "codon|positive|biallelic inactivation|del|ins|dup|mut|frameshift|missense|variant|[0-9]+fs|>")[,1]), "Mutation",
-  ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "^KIT$|^BRCA$")[,1]), "Mutation", NA)))))))
-g2p$biomarker_type_curated <- biomarker_type_curated[,1]
+biomarker_type_curated <- ifelse(!is.na(str_match(string = tolower(g2p$biomarker_type), pattern = "copy number variant|amplification")[,1]) | !is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "copy number variant|amplification")), "Amplification/CNV", NA)
+biomarker_type_curated <- ifelse(!is.na(str_match(string = toupper(g2p$Feature.Names), pattern = "[A-Z0-9|A-Z]+-[A-Z0-9|A-Z]+|FUSION|ALK POSITIVE")[,1]) & is.na(str_match(string = g2p$Feature.Names, pattern = "[0-9]+-[0-9]+")) | g2p$biomarker_type == "fusion" | g2p$biomarker_type == "rearrange", "Fusion", biomarker_type_curated)
+biomarker_type_curated <- ifelse(!is.na(str_match(string = g2p$Feature.Names, pattern = "c\\.[0-9]|^KIT$|^BRCA$|[A-Z][0-9]+([A-Z]|[*])|[0-9A-Z]+ [A-Z][0-9]+|[A-Z][0-9]+$")[,1]) | !is.na(str_match(string = g2p$biomarker_type, pattern = "intron|insertion|deletion|mutant")[,1]) | !is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "codon|positive|biallelic inactivation|del|ins|dup|mut|frameshift|missense|variant|[0-9]+fs|>")[,1]), "Mutation", biomarker_type_curated)
+biomarker_type_curated <- ifelse(!is.na(str_match(string = tolower(g2p$Feature.Names), pattern = "expression|methylation|erbb2  positive")[,1]), "Expression", biomarker_type_curated)
+g2p$biomarker_type_curated <- biomarker_type_curated
+g2p$biomarker_type_curated <- ifelse(g2p$Feature.Names == "ESR1 Amplification", "Amplification/CNV", g2p$biomarker_type_curated)
 
@@
 
+g2p <- g2p %>% drop_na(Drug)
 # Add association columns
@@
 g2p <- unique(g2p)
-write.csv(g2p, "./data_munging/g2p_db_edited_20191225.csv")
+write.csv(g2p, "./data_munging/g2p_db_edited_20200109.csv")
 ```
@@
 ```{r g2p}
-g2p <- read.delim("./data_munging/g2p_db_edited_20191225.csv", sep = ",", header = TRUE, row.names = 1)
+g2p <- read.delim("./data_munging/g2p_db_edited_20200109.csv", sep = ",", header = TRUE, row.names = 1)
 
@@
 # Select columns for maf_df
-maf_raw_edit <- filter(maf_raw, Variant_Classification != "Silent" & !is.na(Variant_Classification))
+maf_raw_edit <- filter(maf_raw, Variant_Classification != "Silent" & !is.na(Variant_Classification) & Gene %in% g2p_genes)
 maf <- subset(maf_raw_edit, select = c("Gene", "DepMap_ID"))
@@
 Load Rds:
-```{r load_omics_rds}
+```{r load_omics_rds, eval=FALSE}
 maf_df <- readRDS("./data_munging/19Q2/maf_df_19Q2_nosilent.rds")
@@
   data <- filter(data, !is.na(DepMap_ID) & !(DepMap_ID %in% c("ACH-001182", "ACH-001451")))
+  # Add grouper columns
+  data$Drug_Gene <- with(data, paste0(Drug, "_", Gene))
+  data$Drug_Gene_Lin <- with(data, paste0(Drug, "_", Gene, "_", disease))
   # Save and return dataframe
@@
 
-ccle <- readRDS("./data_munging/19Q2/ccle_data_19Q2.rds") %>% drop_na(Drug)
-ctrp <- readRDS("./../htscreens_giant_files/ctrp_data_19Q2.rds") %>% drop_na(Drug)
-gdsc <- readRDS("./data_munging/19Q2/gdsc_data_19Q2.rds") %>% drop_na(Drug)
-
-ccle_unique <- unique(ccle) # Pre: 1512092
-ctrp_unique <- unique(ctrp) # Pre: 47807047
-gdsc_unique <- unique(gdsc) # Pre: 10143182
+ccle <- readRDS("./data_munging/19Q2/ccle_data_19Q2_unique.rds") %>% drop_na(Drug)
+ctrp <- readRDS("./data_munging/19Q2/ctrp_data_19Q2_g2pdrugs_unique.rds") %>% drop_na(Drug)
+gdsc <- readRDS("./data_munging/19Q2/gdsc_data_19Q2_unique.rds") %>% drop_na(Drug)
+
+# ccle_unique <- unique(ccle) # Pre: 1512092
+# ctrp_unique <- unique(ctrp) # Pre: 47807047
+# gdsc_unique <- unique(gdsc) # Pre: 10143182
 
@@
 
-## Clustered AUC heatmap
-
-```{r auc_clustered_ht, eval=FALSE}
-ccle_auc_grid <- dcast(ccle, Drug ~ DepMap_ID, value.var = "Score", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Drug)
-ctrp_auc_grid <- dcast(ctrp, Drug ~ DepMap_ID, value.var = "Score", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Drug)
-gdsc_auc_grid <- dcast(gdsc, Drug ~ DepMap_ID, value.var = "Score", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Drug)
-
-ccle_lineages_ha <- merge(data.frame("DepMap_ID" = colnames(ccle_auc_grid)), ccl_meta, by = "DepMap_ID", all.x = TRUE) %>% `rownames<-`(.[,1]) %>% select(-DepMap_ID)
-ctrp_lineages_ha <- merge(data.frame("DepMap_ID" = colnames(ctrp_auc_grid)), ccl_meta, by = "DepMap_ID", all.x = TRUE) %>% `rownames<-`(.[,1]) %>% select(-DepMap_ID)
-gdsc_lineages_ha <- merge(data.frame("DepMap_ID" = colnames(gdsc_auc_grid)), ccl_meta, by = "DepMap_ID", all.x = TRUE) %>% `rownames<-`(.[,1]) %>% select(-DepMap_ID)
-
-ht_legend_list <- list(direction = "horizontal")
-
-ccle_col_fun <- colorRamp2(c(0, 1), c("gray97", "darkgreen"))
-ccle_auc_ha <- HeatmapAnnotation(Lineage = ccle_lineages_ha$disease, annotation_legend_param = list(Lineage = list(direction = "horizontal", nrow = 5)))
-ccle_auc_ht <- Heatmap(ccle_auc_grid,
-                       na_col = "black",
-                       col = ccle_col_fun,
-                       top_annotation = ccle_auc_ha,
-                       heatmap_legend_param = ht_legend_list,
-                       name = "AUC",
-                       show_column_names = FALSE, 
-                       row_title = "Drugs and Small Molecules",
-                       column_title = "Cancer Cell Lines",
-                       column_title_side = "top")
-
-ctrp_col_fun <- colorRamp2(c(0, 1), c("gray97", "steelblue4"))
-ctrp_auc_ha <- HeatmapAnnotation(Lineage = ctrp_lineages_ha$disease, annotation_legend_param = list(Lineage = list(direction = "horizontal", nrow = 3)))
-ctrp_auc_ht <- Heatmap(ctrp_auc_grid,
-                       na_col = "black",
-                       col = ctrp_col_fun,
-                       top_annotation = ctrp_auc_ha,
-                       heatmap_legend_param = ht_legend_list,
-                       name = "AUC",
-                       show_column_names = FALSE, 
-                       row_title = "Drugs and Small Molecules",
-                       column_title = "Cancer Cell Lines",
-                       column_title_side = "top")
-
-gdsc_col_fun <- colorRamp2(c(0, 1), c("gray97", "turquoise4"))
-gdsc_auc_ha <- HeatmapAnnotation(Lineage = gdsc_lineages_ha$disease, annotation_legend_param = list(Lineage = list(direction = "horizontal", nrow = 3)))
-gdsc_auc_ht <- Heatmap(gdsc_auc_grid,
-                       na_col = "black",
-                       col = gdsc_col_fun,
-                       top_annotation = gdsc_auc_ha,
-                       heatmap_legend_param = ht_legend_list,
-                       name = "AUC",
-                       show_column_names = FALSE, 
-                       row_title = "Drugs and Small Molecules",
-                       column_title = "Cancer Cell Lines",
-                       column_title_side = "top")
-
-png(filename = "./plots/manuscript/ccle_clustered_heatmap.png", width = 10, height = 8, units = "in", res = 500)
-draw(ccle_auc_ht, merge_legend = TRUE, heatmap_legend_side = "top", annotation_legend_side = "top")
-dev.off()
-
-png(filename = "./plots/manuscript/ctrp_clustered_heatmap.png", width = 22, height = 40, units = "in", res = 500)
-draw(ctrp_auc_ht, merge_legend = TRUE, heatmap_legend_side = "top", annotation_legend_side = "top")
-dev.off()
-
-png(filename = "./plots/manuscript/gdsc_clustered_heatmap.png", width = 18, height = 20, units = "in", res = 500)
-draw(gdsc_auc_ht, merge_legend = TRUE, heatmap_legend_side = "top", annotation_legend_side = "top")
-dev.off()
-```
-
 # WILCOXON: Mutations
@@
 ```{r mut_wilcoxon_tests, eval=FALSE}
+# ccle$Drug_Gene <- with(ccle, paste0(Drug, "_", Gene))
+# ccle$Drug_Gene_Lin <- with(ccle, paste0(Drug, "_", Gene, "_", disease))
+# 
+# ctrp$Drug_Gene <- with(ctrp, paste0(Drug, "_", Gene))
+# ctrp$Drug_Gene_Lin <- with(ctrp, paste0(Drug, "_", Gene, "_", disease))
+#   
+# gdsc$Drug_Gene <- with(gdsc, paste0(Drug, "_", Gene))
+# gdsc$Drug_Gene_Lin <- with(gdsc, paste0(Drug, "_", Gene, "_", disease))
+
 # CCLE
@@
 ## CRISPR
-
-```{r}
-dataframe = crispr_prot
-grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change")
-g2p_list = unique(as.character(g2p_prot$Gene_Protein_Change[!is.na(g2p_prot$Gene_Protein_Change)]))
-outfile = "./data_munging/rds/crispr_signif_protein_changes.rds"
-
-    count_n <- dataframe %>% count(Drug_Gene_Protein_Change, Change_Status)
-    count_n_wide <- dcast(count_n, Drug_Gene_Protein_Change ~ Change_Status, value.var = "n", fill = 0) %>% separate(Drug_Gene_Protein_Change, sep = "_", c("Drug", "Gene_Protein_Change"), extra = "merge", remove = FALSE)
-    colnames(count_n_wide) <- c("Drug_Gene_Protein_Change", "Drug", "Gene_Protein_Change", "Change_Status_0_count", "Change_Status_1_count")
-    count_n_filt <- filter(count_n, n >= 3)
-    count_category <- count_n_filt %>% count(Drug_Gene_Protein_Change) %>% filter(n == 2)
-    dg_keep <- intersect(count_n_filt$Drug_Gene_Protein_Change, count_category$Drug_Gene_Protein_Change)
-    dataframe <- filter(dataframe, Drug_Gene_Protein_Change %in% dg_keep)
-    dataframe$Drug_Gene_Protein_Change <- as.character(dataframe$Drug_Gene_Protein_Change)
-    signif <- compare_means(Score ~ Change_Status, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
-    signif <- adj_signif(signif, alpha = 0.05)
-    signif <- signif[order(signif$p),]
-    signif <- merge(signif, count_n_wide, by = grouping, all = TRUE)
-    signif$`n WT/mut` <- with(signif, paste0(Change_Status_0_count, "/", Change_Status_1_count))
-    if(is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- ifelse(signif$Drug_Gene_Protein_Change %in% g2p_list, "Yes", "No") }
-    if(!is.na(str_match(pattern = "crispr", string = outfile))) { signif$InG2P <- ifelse(signif$Gene_Protein_Change %in% g2p_list, "Yes", "No")  }
-```
 
@@
 
-```{r load_prot_wilcoxon_rds, eval=FALSE}
+```{r load_prot_wilcoxon_rds, eval=TRUE}
 crispr_signif_prot <- readRDS("./data_munging/rds/crispr_signif_protein_changes.rds") %>% filter(Change_Status_1_count >= 3)
@@
 
-## Boxplots
-
-```{r crispr_mut_boxplots, fig.height=5, fig.width=10, eval=FALSE}
-crispr_filt <- filter(crispr, Gene %in% g2p_mut_genes)
-crispr_filt$Gene <- factor(crispr_filt$Gene, levels = g2p_mut_genes)
-crispr_filt$Mutation <- as.character(crispr_filt$Mutation)
-crispr_signif_filt <- filter(crispr_signif_g2p_g, Gene %in% g2p_mut_genes)
-crispr_signif_filt$Gene <- factor(crispr_signif_filt$Gene, levels = g2p_mut_genes)
-
-crispr_gene_mut_plot <- ggplot(data = crispr_filt) +
-  facet_wrap(~ Gene, nrow = 2, drop = FALSE) +
-  scale_color_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "darkorchid", "0" = "thistle")) +
-  scale_x_discrete(name = "Mutation Status", labels = c("0" = "WT", "1" = "Mut")) +
-  geom_jitter(aes(x = Mutation, y = Score, color = Mutation), width = 0.2, alpha = 0.5, size = 0.6) +
-  geom_boxplot(aes(x = Mutation, y = Score), fill = "transparent", outlier.shape = NA, lwd = 0.3) +
-  geom_text(data = crispr_signif_filt, aes(x = 1.5, y = 2, label = p.signif)) +
-  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
-  theme(legend.position = "top", legend.direction = "horizontal") +
-  guides(color = guide_legend(override.aes = list(size = 3))) +
-  labs(y = "CERES Score")
-crispr_gene_mut_plot
-
-ggsave("./plots/manuscript/crispr_gene_mut_plot.png", crispr_gene_mut_plot, width = 12, height = 6, units = "in")
-```
-
-```{r fusion_boxplots, fig.height=5, fig.width=12, eval=FALSE}
-# CRISPR
-crispr_fus_filt <- filter(crispr_fus, FusionPair %in% c("ABL1-BCR", "BCR-ABL1", "PML-PARA") & Drug_Gene %in% c("CRISPR_ABL1"))
-crispr_signif_fus_filt <- filter(crispr_signif_fus, FusionPair %in% c("ABL1-BCR", "BCR-ABL1", "PML-PARA"))
-
-crispr_fus_boxplot <- ggplot(data = crispr_fus_filt) +
-  facet_grid(FusionPair ~ Drug_Gene) +
-  scale_color_manual(name = "Fusion Status", values = c("Yes" = "darkorchid4", "No" = "thistle")) +
-  geom_jitter(aes(x = Fusion_Status, y = Score, color = Fusion_Status), width = 0.2, alpha = 0.5, size = 0.6) +
-  geom_boxplot(aes(x = Fusion_Status, y = Score), fill = "transparent", outlier.shape = NA, lwd = 0.3) +
-  # coord_cartesian(ylim = c(0, 1.2)) +
-  # scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
-  geom_text(data = crispr_signif_fus_filt, aes(x = 1.5, y = 1, label = p.signif)) +
-  theme(legend.position = "top", legend.direction = "horizontal", axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
-  guides(color = guide_legend(override.aes = list(size = 3))) +
-  labs(y = "Score", x = "Fusion Status")
-crispr_fus_boxplot
-ggsave("./plots/manuscript/crispr_fus_boxplots.png", crispr_fus_boxplot, width = 8, height = 5, units = "in")
-
-# CCLE
-ccle_fus_filt <- filter(ccle_fus, FusionPair %in% c("ABL1-BCR", "BCR-ABL1") & Drug %in% g2p_drugs)
-ccle_fus_filt$Drug_f <- factor(ccle_fus_filt$Drug, levels = intersect(g2p_drug_order, unique(ccle_fus$Drug)))
-ccle_signif_fus_filt <- filter(ccle_signif_fus, Drug %in% g2p_drugs)
-ccle_signif_fus_filt$Drug_f <- factor(ccle_signif_fus_filt$Drug, levels = intersect(g2p_drug_order, unique(ccle_signif_fus$Drug)))
-
-ccle_fus_boxplot <- ggplot(data = ccle_fus_filt) +
-  facet_grid(FusionPair ~ Drug_f) +
-  scale_color_manual(name = "Fusion Status", values = c("Yes" = "springgreen4", "No" = "palegreen3")) +
-  geom_jitter(aes(x = Fusion_Status, y = Score, color = Fusion_Status), width = 0.2, alpha = 0.5, size = 0.6) +
-  geom_boxplot(aes(x = Fusion_Status, y = Score), fill = "transparent", outlier.shape = NA, lwd = 0.3) +
-  coord_cartesian(ylim = c(0, 1.2)) +
-  scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
-  geom_text(data = ccle_signif_fus_filt, aes(x = 1.5, y = 1.1, label = p.signif)) +
-  theme(legend.position = "top", legend.direction = "horizontal", axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
-  guides(color = guide_legend(override.aes = list(size = 3))) +
-  labs(y = "AUC", x = "Fusion Status")
-ccle_fus_boxplot
-ggsave("./plots/manuscript/ccle_fus_boxplots.png", ccle_fus_boxplot, width = 8, height = 5, units = "in")
-
-# CTRP
-ctrp_fus_filt <- filter(ctrp_fus, FusionPair %in% c("ABL1-BCR", "BCR-ABL1") & Drug %in% g2p_drugs)
-ctrp_fus_filt$Drug_f <- factor(ctrp_fus_filt$Drug, levels = intersect(g2p_drug_order, unique(ctrp_fus$Drug)))
-ctrp_signif_fus_filt <- filter(ctrp_signif_fus, FusionPair %in% c("ABL1-BCR", "BCR-ABL1") & Drug %in% g2p_drugs)
-ctrp_signif_fus_filt$Drug_f <- factor(ctrp_signif_fus_filt$Drug, levels = intersect(g2p_drug_order, unique(ctrp_signif_fus$Drug)))
-
-ctrp_fus_boxplot <- ggplot(data = ctrp_fus_filt) +
-  facet_grid(FusionPair ~ Drug_f) +
-  scale_color_manual(name = "Fusion Status", values = c("Yes" = "steelblue4", "No" = "slategray3")) +
-  geom_jitter(aes(x = Fusion_Status, y = Score, color = Fusion_Status), width = 0.2, alpha = 0.5, size = 0.6) +
-  geom_boxplot(aes(x = Fusion_Status, y = Score), fill = "transparent", outlier.shape = NA, lwd = 0.3) +
-  coord_cartesian(ylim = c(0, 1.2)) +
-  scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
-  geom_text(data = ctrp_signif_fus_filt, aes(x = 1.5, y = 1.1, label = p.signif)) +
-  theme(legend.position = "top", legend.direction = "horizontal", axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
-  guides(color = guide_legend(override.aes = list(size = 3))) +
-  labs(y = "AUC", x = "Fusion Status")
-ctrp_fus_boxplot
-ggsave("./plots/manuscript/ctrp_fus_boxplots.png", ctrp_fus_boxplot, width = 19, height = 5, units = "in")
-
-# GDSC
-gdsc_fus_filt <- filter(gdsc_fus, FusionPair %in% c("ABL1-BCR", "BCR-ABL1") & Drug %in% g2p_drugs)
-gdsc_fus_filt$Drug_f <- factor(gdsc_fus_filt$Drug, levels = intersect(g2p_drug_order, unique(gdsc_fus$Drug)))
-gdsc_signif_fus_filt <- filter(gdsc_signif_fus, FusionPair %in% c("ABL1-BCR", "BCR-ABL1") & Drug %in% g2p_drugs)
-gdsc_signif_fus_filt$Drug_f <- factor(gdsc_signif_fus_filt$Drug, levels = intersect(g2p_drug_order, unique(gdsc_signif_fus$Drug)))
-
-gdsc_fus_boxplot <- ggplot(data = gdsc_fus_filt) +
-  facet_grid(FusionPair ~ Drug_f) +
-  scale_color_manual(name = "Fusion Status", values = c("Yes" = "turquoise4", "No" = "paleturquoise3")) +
-  geom_jitter(aes(x = Fusion_Status, y = Score, color = Fusion_Status), width = 0.2, alpha = 0.5, size = 0.6) +
-  geom_boxplot(aes(x = Fusion_Status, y = Score), fill = "transparent", outlier.shape = NA, lwd = 0.3) +
-  coord_cartesian(ylim = c(0, 1.2)) +
-  scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
-  geom_text(data = gdsc_signif_fus_filt, aes(x = 1.5, y = 1.1, label = p.signif)) +
-  theme(legend.position = "top", legend.direction = "horizontal", axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
-  guides(color = guide_legend(override.aes = list(size = 3))) +
-  labs(y = "AUC", x = "Fusion Status")
-gdsc_fus_boxplot
-ggsave("./plots/manuscript/gdsc_fus_boxplots.png", gdsc_fus_boxplot, width = 12, height = 5, units = "in")
-```
-
 ## Heatmaps
@@
     signif_grid <- dcast(signif_df, Gene ~ Drug, value.var = "p_log10", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
-    signif_grid <- signif_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
-    signif_grid <- signif_grid[complete.cases(signif_grid), ]
+    signif_grid <- signif_grid[intersect(g2p_gene_order, rownames(signif_grid)), intersect(g2p_drug_order, colnames(signif_grid))]
 
@@
     signif_grid_annot <- dcast(signif_df, Gene ~ Drug, value.var = "Direction_Heatmap", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
-    signif_grid_annot <- signif_grid_annot[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
+    signif_grid_annot <- signif_grid_annot[intersect(g2p_gene_order, rownames(signif_grid)), intersect(g2p_drug_order, colnames(signif_grid))]
     signif_grid_annot <- signif_grid_annot[complete.cases(signif_grid_annot), ]
@@
 
-### Lineage
-
-```{r lineage_mut_heatmap_functions}
-MakeWilcoxonLineageHeatmap <- function(df, database, lineage) {
-  plot_colors <- c("CCLE" = "darkgreen", "CTRP" = "steelblue4", "GDSC" = "turquoise4")
-  plot_breaks <- list("CCLE" = seq(0, 5, by = 1), "CTRP" = seq(0, 12, by = 2), "GDSC" = seq(0, 8, by = 2))
-
-  df <- filter(df, disease == lineage)
-
-  ht <- MakeWilcoxonHeatmap(signif_df = df, feature = "mutation", legend_title = paste0(database, "\n", lineage, "\n-log10(p-value)"), legend_breaks = plot_breaks[[database]], row_names = TRUE, color = plot_colors[[database]], col_title = "Drugs", row_title_txt = "Genes")
-
-  return(ht)
-}
-
-SaveWilcoxonLineageHeatmap <- function(database, ht_list, lineage) {
-  ht <- ht_list[[lineage]]
-  out_height <- floor((nrow(ht@matrix) + 1) / 2) + 2
-  out_width <- ncol(ht@matrix) / 2 + 1
-
-  png(filename = paste0("./plots/manuscript/lineage_heatmaps/", tolower(database), "_", lineage, "_mut_heatmap.png"), width = out_width, height = out_height, units = "in", res = 500)
-  draw(ht, heatmap_legend_side = "top")
-  invisible(dev.off())
-}
-```
-
-```{r lineage_mut_heatmaps, eval=FALSE, message=FALSE}
-ccle_hts <- lapply(unique(ccle_signif_dgl$disease), MakeWilcoxonLineageHeatmap, df = ccle_signif_dgl, database = "CCLE")
-names(ccle_hts) <- unique(ccle_signif_dgl$disease)
-lapply(unique(ccle_signif_dgl$disease), SaveWilcoxonLineageHeatmap, ht_list = ccle_hts, database = "CCLE")
-
-ctrp_hts <- lapply(unique(ctrp_signif_dgl$disease), MakeWilcoxonLineageHeatmap, df = ctrp_signif_dgl, database = "CTRP")
-names(ctrp_hts) <- unique(ctrp_signif_dgl$disease)
-lapply(unique(ctrp_signif_dgl$disease), SaveWilcoxonLineageHeatmap, ht_list = ctrp_hts, database = "CTRP")
-
-gdsc_hts <- lapply(unique(gdsc_signif_dgl$disease), MakeWilcoxonLineageHeatmap, df = gdsc_signif_dgl, database = "GDSC")
-names(gdsc_hts) <- unique(gdsc_signif_dgl$disease)
-lapply(unique(gdsc_signif_dgl$disease), SaveWilcoxonLineageHeatmap, ht_list = gdsc_hts, database = "GDSC")
-```
-
-# SPEARMAN: GE and CN
+# Correlations: GE and CN
 
@@
       signif_grid <- dcast(cor_res, Gene ~ Drug, value.var = "CN_p", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
-      signif_grid <- signif_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
+      signif_grid <- signif_grid[intersect(g2p_gene_order, rownames(signif_grid)), intersect(g2p_drug_order, colnames(signif_grid))]
       signif_grid <- signif_grid[complete.cases(signif_grid), ]
@@
       corr_grid <- dcast(cor_res, Gene ~ Drug, value.var = "CN_r", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
-      corr_grid <- corr_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(corr_grid))]
+      corr_grid <- corr_grid[intersect(g2p_gene_order, rownames(signif_grid)), intersect(g2p_drug_order, colnames(corr_grid))]
       corr_grid <- corr_grid[complete.cases(corr_grid), ]
@@
       annot_grid <- dcast(cor_res, Gene ~ Drug, value.var = "Direction_Heatmap", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
-      annot_grid <- annot_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
+      annot_grid <- annot_grid[intersect(g2p_gene_order, rownames(signif_grid)), intersect(g2p_drug_order, colnames(signif_grid))]
       annot_grid <- annot_grid[complete.cases(annot_grid), ]
@@
       signif_grid <- dcast(cor_res, Gene ~ Drug, value.var = "GE_p", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
-      signif_grid <- signif_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
-      signif_grid <- signif_grid[complete.cases(signif_grid), ]
+      signif_grid <- signif_grid[intersect(g2p_gene_order, rownames(signif_grid)), intersect(g2p_drug_order, colnames(signif_grid))]
       signif_grid[signif_grid >= 0.05] <- ""
@@
       corr_grid <- dcast(cor_res, Gene ~ Drug, value.var = "GE_r", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
-      corr_grid <- corr_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(corr_grid))]
+      corr_grid <- corr_grid[intersect(g2p_gene_order, rownames(signif_grid)), intersect(g2p_drug_order, colnames(corr_grid))]
       corr_grid <- corr_grid[complete.cases(corr_grid), ]
@@
 
+```{r}
+g2p_diseases <- unique(g2p$disease[!is.na(g2p$disease)])
+
+ccle$disease_g2p <- ifelse(ccle$disease %in% g2p_diseases, ccle$disease, "other")
+ctrp$disease_g2p <- ifelse(ctrp$disease %in% g2p_diseases, ctrp$disease, "other")
+gdsc$disease_g2p <- ifelse(gdsc$disease %in% g2p_diseases, gdsc$disease, "other")
+
+g2p_disease_colors <- c("breast"                      = "deeppink",
+                        "central_nervous_system"      = "purple4",
+                        "colorectal"                  = "palegreen",
+                        "gastric"                     = "antiquewhite3",
+                        "haematopoietic_and_lymphoid" = "springgreen4",
+                        "kidney"                      = "cyan3",
+                        "lung"                        = "dodgerblue",
+                        "other"                       = "azure3",
+                        "ovary"                       = "palevioletred1",
+                        "skin"                        = "orange1",
+                        "thyroid"                     = "lightgoldenrod1")
+g2p_disease_colors1 <- c("breast"                      ,
+                        "central_nervous_system"      ,
+                        "colorectal"                  ,
+                        "gastric"                     ,
+                        "haematopoietic_and_lymphoid" ,
+                        "kidney"                      ,
+                        "lung"                        ,
+                        "other"                       ,
+                        "ovary"                       ,
+                        "skin"                        ,
+                        "thyroid"                     )
+g2p_disease_colors2 <- c("deeppink",
+                        "purple4",
+                        "palegreen",
+                        "antiquewhite3",
+                        "springgreen4",
+                        "cyan3",
+                        "dodgerblue",
+                        "azure3",
+                        "palevioletred1",
+                        "orange1",
+                        "lightgoldenrod1")
+
+g2p_disease_colors_df <- data.frame(disease = g2p_disease_colors1, disease_g2p = g2p_disease_colors1, color = g2p_disease_colors2)
+```
+
 ```{r Supp2}
@@
 
-ggplot(data = g2p) +
-  geom_bar(mapping = aes(x = disease))
-
 # How many G2P indications are for each disease
-g2p_munge <- select(g2p, disease)
-g2p_munge <- g2p_munge %>% count(disease)
-g2p_munge$Perc <- g2p_munge$n / sum(g2p_munge$n) * 100
-g2p_munge <- g2p_munge[order(g2p_munge$Perc),]
-g2p_munge$disease <- factor(g2p_munge$disease, levels = g2p_munge$disease)
-ggplot(data = g2p_munge) +
-  geom_bar(mapping = aes(x = disease, y = Perc), stat = "identity") +
-  geom_text(aes(x = disease, y = Perc + 3, label = round(Perc, 1))) +
-  scale_y_continuous(breaks = seq(0, 100, by = 10), labels = seq(0, 100, by = 10)) +
-  coord_flip()
+g2p_disease_n <- g2p %>% count(disease) %>% mutate(percent = n / sum(n) * 100) %>% drop_na(disease)
+g2p_disease_n <- rbind(g2p_disease_n, c("other", 0, 0))
+g2p_disease_n <- g2p_disease_n[order(g2p_disease_n$percent),]
+g2p_disease_n <- merge(g2p_disease_n, g2p_disease_colors_df, by = "disease")
+# ggplot(g2p_disease_n, aes(x = "", y = n, fill = disease))+
+#   geom_bar(width = 1, stat = "identity") +
+#   coord_polar("y", start = 0)
+
+ccle$disease_g2p <- ifelse(ccle$disease %in% g2p_diseases, ccle$disease, "other")
+ccle_disease_n <- unique(select(ccle, DepMap_ID, disease_g2p)) %>% count(disease_g2p) %>% mutate(percent = n / sum(n) * 100)
+ccle_disease_n <- ccle_disease_n[order(ccle_disease_n$percent),]
+ccle_disease_n <- merge(ccle_disease_n, g2p_disease_colors_df, by = "disease_g2p")
+
+ctrp$disease_g2p <- ifelse(ctrp$disease %in% g2p_diseases, ctrp$disease, "other")
+ctrp_disease_n <- unique(select(ctrp, DepMap_ID, disease_g2p)) %>% count(disease_g2p) %>% mutate(percent = n / sum(n) * 100)
+ctrp_disease_n <- ctrp_disease_n[order(ctrp_disease_n$percent),]
+
+gdsc$disease_g2p <- ifelse(gdsc$disease %in% g2p_diseases, gdsc$disease, "other")
+gdsc_disease_n <- unique(select(gdsc, DepMap_ID, disease_g2p)) %>% count(disease_g2p) %>% mutate(percent = n / sum(n) * 100)
+gdsc_disease_n <- gdsc_disease_n[order(gdsc_disease_n$percent),]
+
+disease_n <- data.frame("Lineage" = g2p_disease_n$disease,
+                        "G2P" = g2p_disease_n$n,
+                        "CCLE" = ccle_disease_n$n,
+                        "CTRP" = ctrp_disease_n$n,
+                        "GDSC" = gdsc_disease_n$n)
+disease_n <- melt(data = disease_n, id.vars = "Lineage", measure.vars = c("G2P", "CCLE", "CTRP", "GDSC"), variable.name = "Dataset", value.name = "n")
+disease_n$n <- as.numeric(disease_n$n)
+disease_n$Lineage <- factor(disease_n$Lineage)
+
+```
+
+```{r fig.height=10, fig.width=10}
+slices <- ccle_disease_n$n
+lbls <- paste0(ccle_disease_n$disease_g2p, " (", round(ccle_disease_n$percent, digits = 2), "%)")
+pie(slices,labels = lbls, col = ccle_disease_n$color, radius = 0.5)
+```
+
+```{r, eval=FALSE}
+plot_ly() %>%
+  add_pie(data = g2p_munge, labels = ~ disease, values = ~ n, textposition = "inside" ,textinfo = "label+percent") %>%
+  layout(title = "Lineages", showlegend = FALSE,
+         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
+         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
+
 ```
@@
 
-```{r mut_status_fig, fig.height=8, fig.width=15, eval=FALSE}
-ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "mutation", legend_title = "CCLE -log10(p-value)", legend_breaks = seq(0, 12, by = 3), row_names = FALSE, color = "darkgreen", col_title = "", row_title_txt = "Genes", radius = 0.023)
-ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "mutation", legend_title = "CTRP -log10(p-value)", legend_breaks = seq(0, 18, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.008)
-ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "mutation", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes", radius = 0.011)
-ht_crispr2 <- MakeWilcoxonHeatmap(signif_df = filter(crispr_signif_g2p_g, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "crispr", legend_title = "CRISPR -log10(p-value)", legend_breaks = seq(0, 45, by = 9), row_names = TRUE, color = "darkorchid4", col_title = "", row_title_txt = "Genes", radius = 0.15)
-ht_mut_list <- ht_crispr2 + ht_ccle2 + ht_ctrp2 + ht_gdsc2
+```{r mutation_figure, eval=FALSE}
+mut_genes <- union(union(filter(ccle_signif_g2p_dg, InG2P == "Yes")$Gene, filter(ctrp_signif_g2p_dg, InG2P == "Yes")$Gene), filter(gdsc_signif_g2p_dg, InG2P == "Yes")$Gene)
+mut_drugs <- union(union(filter(ccle_signif_g2p_dg, InG2P == "Yes")$Drug, filter(ctrp_signif_g2p_dg, InG2P == "Yes")$Drug), filter(gdsc_signif_g2p_dg, InG2P == "Yes")$Drug)
+
+ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Drug %in% mut_drugs & Gene %in% mut_genes), feature = "mutation", legend_title = "CCLE -log10(p-value)", legend_breaks = seq(0, 12, by = 3), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Genes", radius = 0.023)
+ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Drug %in% mut_drugs & Gene %in% mut_genes), feature = "mutation", legend_title = "CTRP -log10(p-value)", legend_breaks = seq(0, 18, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.008)
+ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Drug %in% mut_drugs & Gene %in% mut_genes), feature = "mutation", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes", radius = 0.011)
+ht_mut_list <- ht_ccle2 + ht_ctrp2 + ht_gdsc2
 lgd <- list(Legend(labels = c("Resistance", "Sensitivity", "p < 0.05"), type = "points", pch = c(21, 21, 8), nrow = 1, background = "white", legend_gp = gpar(col = "black", fill = c("red", "white"))))
@@
 
-crispr_signif_g2p_dg_summ <- filter(crispr_signif_g2p_g, InG2P == "Yes") 
 ccle_signif_g2p_dg_summ <- filter(ccle_signif_g2p_dg, InG2P == "Yes") 
 ctrp_signif_g2p_dg_summ <- filter(ctrp_signif_g2p_dg, InG2P == "Yes") 
-gdsc_signif_g2p_dg_summ <- filter(gdsc_signif_g2p_dg, InG2P == "Yes") q
-
-crispr_mut_filt <- filter(crispr, Gene %in% filter(crispr_signif_g2p_dg_summ, p < 0.05)$Gene)
-crispr_mut_filt_plot <- ggplot(data = crispr_mut_filt, aes(x = as.character(Mutation), y = Score) )+
-  facet_wrap(~ Gene, ncol = 5) +
-  geom_violin(aes(fill = as.character(Mutation))) +
-  geom_boxplot(outlier.shape = NA, width = 0.07) +
-  scale_x_discrete(labels = c("0" = "Wildtype", "1" = "Mutant")) +
-  scale_y_continuous(breaks = seq(-3, 1, by = 0.5), labels = c("-3.0", "-2.5", "-2.0", "-1.5", "-1.0", "-0.5", "0.0", "0.5", "1.0")) +
-  scale_fill_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "darkorchid", "0" = "thistle")) +
-  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35, label.y = 1.1) +
-  labs(title = "CRISPR", x = "Mutation Status", y = "CERES Score") +
-  theme(legend.position = "none", axis.title.x = element_blank(),
-        panel.background = element_rect(fill = "snow1", colour = "snow1", size = 0.5, linetype = "solid"),
-        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
-        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+gdsc_signif_g2p_dg_summ <- filter(gdsc_signif_g2p_dg, InG2P == "Yes")
 
@@
 ccle_mut_filt_plot <- ggplot(data = ccle_mut_filt, mapping = aes(x = as.character(Mutation), y = Score)) +
-  facet_wrap(~ Drug_Gene, ncol = 5) +
-  geom_violin(aes(fill = as.character(Mutation))) +
-  geom_boxplot(outlier.shape = NA, width = 0.07) +
+  facet_wrap(~ Drug_Gene, nrow = 1) +
+  geom_violinhalf(aes(fill = as.character(Mutation)), position = position_nudge(x = 0.2, y = 0), alpha = 0.8, show.legend = FALSE) +
+  geom_point(aes(color = disease_g2p), position = position_jitter(width = 0.15), size = 0.5, alpha = 0.6) +
+  geom_boxplot(width = 0.1, guides = FALSE, outlier.shape = NA, alpha = 0.8) +
+  scale_fill_manual(labels = c("Wildtype", "Mutant"), values = c("1" = "springgreen4", "0" = "palegreen3")) +
+  scale_color_manual(values = g2p_disease_colors) +
   scale_x_discrete(labels = c("0" = "Wildtype", "1" = "Mutant")) +
-  scale_fill_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "springgreen4", "0" = "palegreen3")) +
   scale_y_continuous(breaks = seq(0, 1.00, by = 0.25), labels = c("0.00", "0.25", "0.50", "0.75", "1.00")) +
@@
   labs(title = "CCLE", x = "Mutation Status", y = "AUC") +
+  guides(color = guide_legend(override.aes = list(size = 3))) +
   theme(legend.position = "none", axis.title.x = element_blank(),
@@
 ctrp_mut_filt_plot <- ggplot(data = ctrp_mut_filt, mapping = aes(x = as.character(Mutation), y = Score)) +
-  facet_wrap(~ Drug_Gene, ncol = 7) +
-  geom_violin(aes(fill = as.character(Mutation))) +
-  geom_boxplot(outlier.shape = NA, width = 0.07,) +
+  facet_wrap(~ Drug_Gene, ncol = 4) +
+  geom_violinhalf(aes(fill = as.character(Mutation)), position = position_nudge(x = 0.2, y = 0), alpha = 0.8, show.legend = FALSE) +
+  geom_point(aes(color = disease_g2p), position = position_jitter(width = 0.15), size = 0.5, alpha = 0.6) +
+  geom_boxplot(width = 0.1, guides = FALSE, outlier.shape = NA, alpha = 0.8) +
+  scale_fill_manual(labels = c("Wildtype", "Mutant"), values = c("1" = "steelblue4", "0" = "slategray3")) +
+  scale_color_manual(name = "Lineage", values = g2p_disease_colors) +
   scale_x_discrete(labels = c("0" = "Wildtype", "1" = "Mutant")) +
-  scale_fill_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "steelblue4", "0" = "slategray3")) +
   scale_y_continuous(breaks = seq(0, 1.00, by = 0.25), labels = c("0.00", "0.25", "0.50", "0.75", "1.00")) +
@@
   labs(title = "CTRP", x = "Mutation Status", y = "AUC") +
+  guides(color = guide_legend(override.aes = list(size = 3))) +
+  theme(axis.title.x = element_blank(),
+        panel.background = element_rect(fill = "whitesmoke", colour = "whitesmoke", size = 0.5, linetype = "solid"),
+        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+
+gdsc_mut_filt <- filter(gdsc, Drug_Gene %in% filter(gdsc_signif_g2p_dg_summ, p < 0.05)$Drug_Gene)
+gdsc_mut_filt_plot <- ggplot(data = gdsc_mut_filt, mapping = aes(x = as.character(Mutation), y = Score)) +
+  facet_wrap(~ Drug_Gene, ncol = 4) +
+  geom_violinhalf(aes(fill = as.character(Mutation)), position = position_nudge(x = 0.2, y = 0), alpha = 0.8, show.legend = FALSE) +
+  geom_point(aes(color = disease_g2p), position = position_jitter(width = 0.15), size = 0.5, alpha = 0.6) +
+  geom_boxplot(width = 0.1, guides = FALSE, outlier.shape = NA, alpha = 0.8) +
+  scale_fill_manual(labels = c("Wildtype", "Mutant"), values = c("1" = "turquoise4", "0" = "paleturquoise3")) +
+  scale_color_manual(name = "Lineages", values = g2p_disease_colors) +
+  scale_x_discrete(labels = c("0" = "Wildtype", "1" = "Mutant")) +
+  scale_y_continuous(breaks = seq(0, 1.00, by = 0.25), labels = c("0.00", "0.25", "0.50", "0.75", "1.00")) +
+  coord_cartesian(ylim = c(0, 1.10)) +
+  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35, label.y = 1.1) +
+  labs(title = "GDSC", x = "Mutation Status", y = "AUC") +
+  guides(color = guide_legend(override.aes = list(size = 3))) +
+  theme(legend.position = "none", axis.title.x = element_blank(),
+        panel.background = element_rect(fill = "azure", colour = "azure", size = 0.5, linetype = "solid"),
+        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+
+lay <- rbind(c(1, 1, 1, 1),
+             c(1, 1, 1, 1),
+             c(1, 1, 1, 1),
+             c(2, 2, 3, 3),
+             c(4, 4, 4, 4),
+             c(4, 4, 4, 4))
+
+gs_mut <- gList(arrangeGrob(ht_mut_grob, left = textGrob("A", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(ggplotGrob(ccle_mut_filt_plot), left = textGrob("B", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(ggplotGrob(gdsc_mut_filt_plot), left = textGrob("C", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(ggplotGrob(ctrp_mut_filt_plot), left = textGrob("D", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))))
+
+png(filename = "./plots/manuscript_final/drug_mutation_pancancer_small.png", width = 13, height = 14, units = "in", res = 100)
+grid.arrange(layout_matrix = lay, grobs = gs_mut)
+dev.off()
+
+png(filename = "./plots/manuscript_final/drug_mutation_pancancer.png", width = 13, height = 14, units = "in", res = 500)
+grid.arrange(layout_matrix = lay, grobs = gs_mut)
+dev.off()
+```
+
+## Protein changes figure
+
+```{r}
+ccle_prot$disease_g2p <- ifelse(ccle_prot$disease %in% g2p_diseases, ccle_prot$disease, "other")
+ctrp_prot$disease_g2p <- ifelse(ctrp_prot$disease %in% g2p_diseases, ctrp_prot$disease, "other")
+gdsc_prot$disease_g2p <- ifelse(gdsc_prot$disease %in% g2p_diseases, gdsc_prot$disease, "other")
+
+ccle_signif_prot_summ <- filter(ccle_signif_prot, InG2P == "Yes") 
+ctrp_signif_prot_summ <- filter(ctrp_signif_prot, InG2P == "Yes") 
+gdsc_signif_prot_summ <- filter(gdsc_signif_prot, InG2P == "Yes")
+
+prot_drugs <- union(union(ccle_signif_prot_summ$Drug, ctrp_signif_prot_summ$Drug), gdsc_signif_prot_summ$Drug)
+prot_drugs <- prot_drugs[!(prot_drugs %in% c("cabozantinib", "vandetinib"))]
+
+ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_prot_4plot, Drug %in% prot_drugs), feature = "protein changes", legend_title = "CCLE -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.021)
+ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_prot_4plot, Drug %in% prot_drugs), feature = "protein changes", legend_title = "CTRP -log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.012)
+ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_prot_4plot, Drug %in% prot_drugs), feature = "protein changes", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 3, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.0125)
+ht_prot_list <- ht_ccle2 + ht_ctrp2 + ht_gdsc2
+lgd <- list(Legend(labels = c("Resistance", "Sensitivity", "p < 0.05"), type = "points", pch = c(21, 21, 8), nrow = 1, background = "white", legend_gp = gpar(col = "black", fill = c("red", "white"))))
+ht_prot_grob <- grid.grabExpr(draw(ht_prot_list, gap = unit(0.25, "in"), heatmap_legend_side = "top", annotation_legend_list = lgd, annotation_legend_side = "top", merge_legend = TRUE))
+
+ccle_prot_filt <- filter(ccle_prot, Drug_Gene_Protein_Change %in% filter(ccle_signif_prot_summ, p < 0.05)$Drug_Gene_Protein_Change)
+# ccle_mut_filt_plot <- ggplot(data = ccle_mut_filt, mapping = aes(x = as.character(Mutation), y = Score)) +
+#   facet_wrap(~ Drug_Gene, nrow = 1) +
+#   geom_violinhalf(aes(fill = as.character(Mutation)), position = position_nudge(x = 0.2, y = 0), alpha = 0.8, show.legend = FALSE) +
+#   geom_point(aes(color = disease_g2p), position = position_jitter(width = 0.15), size = 0.5, alpha = 0.6) +
+#   geom_boxplot(width = 0.1, guides = FALSE, outlier.shape = NA, alpha = 0.8) +
+#   scale_fill_manual(labels = c("Wildtype", "Mutant"), values = c("1" = "springgreen4", "0" = "palegreen3")) +
+#   scale_color_manual(values = g2p_disease_colors) +
+#   scale_x_discrete(labels = c("0" = "Wildtype", "1" = "Mutant")) +
+#   scale_y_continuous(breaks = seq(0, 1.00, by = 0.25), labels = c("0.00", "0.25", "0.50", "0.75", "1.00")) +
+#   coord_cartesian(ylim = c(0, 1.10)) +
+#   stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35, label.y = 1.1) +
+#   labs(title = "CCLE", x = "Mutation Status", y = "AUC") +
+#   guides(color = guide_legend(override.aes = list(size = 3))) +
+#   theme(legend.position = "none", axis.title.x = element_blank(),
+#         panel.background = element_rect(fill = "mintcream", colour = "mintcream", size = 0.5, linetype = "solid"),
+#         panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+#         panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+
+ctrp_prot_filt <- filter(ctrp_prot, Drug_Gene_Protein_Change %in% filter(ctrp_signif_prot_summ, p < 0.05)$Drug_Gene_Protein_Change)
+ctrp_prot_filt_plot <- ggplot(data = ctrp_prot_filt, mapping = aes(x = Change_Status, y = Score)) +
+  facet_wrap(~ Drug_Gene_Protein_Change, nrow = 2) +
+  geom_violinhalf(aes(fill = Change_Status), position = position_nudge(x = 0.2, y = 0), alpha = 0.8, show.legend = FALSE) +
+  geom_point(aes(color = disease_g2p), position = position_jitter(width = 0.15), size = 0.5, alpha = 0.6) +
+  geom_boxplot(width = 0.1, guides = FALSE, outlier.shape = NA, alpha = 0.7) +
+  scale_x_discrete(labels = c("No" = "Wildtype", "Yes" = "Mutant")) +
+  scale_fill_manual(labels = c("Wildtype", "Mutant"), values = c("Yes" = "steelblue4", "No" = "slategray3")) +
+  scale_color_manual(name = "Lineage", values = g2p_disease_colors) +
+  scale_y_continuous(breaks = seq(0, 1.00, by = 0.25), labels = c("0.00", "0.25", "0.50", "0.75", "1.00")) +
+  coord_cartesian(ylim = c(0, 1.10)) +
+  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35, label.y = 1.1) +
+  labs(title = "CTRP", x = "Change Status", y = "AUC") +
+  guides(color = guide_legend(override.aes = list(size = 3))) +
   theme(legend.position = "none", axis.title.x = element_blank(),
@@
 
-gdsc_mut_filt <- filter(gdsc, Drug_Gene %in% filter(gdsc_signif_g2p_dg_summ, p < 0.05)$Drug_Gene)
-gdsc_mut_filt_plot <- ggplot(data = gdsc_mut_filt, mapping = aes(x = as.character(Mutation), y = Score)) +
-  facet_wrap(~ Drug_Gene, ncol = 5) +
-  geom_violin(aes(fill = as.character(Mutation))) +
-  geom_boxplot(outlier.shape = NA, width = 0.07, ) +
-  scale_x_discrete(labels = c("0" = "Wildtype", "1" = "Mutant")) +
-  scale_fill_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "turquoise4", "0" = "paleturquoise3")) +
+gdsc_prot_filt <- filter(gdsc_prot, Drug_Gene_Protein_Change %in% filter(gdsc_signif_prot_summ, p < 0.05)$Drug_Gene_Protein_Change)
+gdsc_prot_filt_plot <- ggplot(data = gdsc_prot_filt, mapping = aes(x = Change_Status, y = Score)) +
+  facet_wrap(~ Drug_Gene_Protein_Change, nrow = 2) +
+  geom_violinhalf(aes(fill = Change_Status), position = position_nudge(x = 0.2, y = 0), alpha = 0.8, show.legend = FALSE) +
+  geom_point(aes(color = disease_g2p), position = position_jitter(width = 0.15), size = 0.5, alpha = 0.6) +
+  geom_boxplot(width = 0.1, guides = FALSE, outlier.shape = NA, alpha = 0.7) +
+  scale_x_discrete(labels = c("No" = "Wildtype", "Yes" = "Mutant")) +
+  scale_fill_manual(labels = c("Wildtype", "Mutant"), values = c("Yes" = "turquoise4", "No" = "paleturquoise3")) +
+  scale_color_manual(name = "Lineage", values = g2p_disease_colors) +
   scale_y_continuous(breaks = seq(0, 1.00, by = 0.25), labels = c("0.00", "0.25", "0.50", "0.75", "1.00")) +
@@
   stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35, label.y = 1.1) +
-  labs(title = "GDSC", x = "Mutation Status", y = "AUC") +
-  theme(legend.position = "none", axis.title.x = element_blank(),
-        panel.background = element_rect(fill = "lightcyan", colour = "lightcyan", size = 0.5, linetype = "solid"),
+  labs(title = "GDSC", x = "CHange Status", y = "AUC") +
+  guides(color = guide_legend(override.aes = list(size = 3))) +
+  theme(axis.title.x = element_blank(),
+        panel.background = element_rect(fill = "azure", colour = "azure", size = 0.5, linetype = "solid"),
         panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
@@
 
-lay <- rbind(c(1, 1, 1, 1, 1),
-             c(1, 1, 1, 1, 1),
-             c(1, 1, 1, 1, 1),
-             c(2, 2, 2, 2, 2),
-             c(3, 3, 5, 5, 5),
-             c(4, 4, 4, 4, 4))
-
-gs_mut <- gList(arrangeGrob(ht_mut_grob, left = textGrob("A", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
-             arrangeGrob(ggplotGrob(crispr_mut_filt_plot), left = textGrob("B", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
-             arrangeGrob(ggplotGrob(ccle_mut_filt_plot), left = textGrob("C", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
-             arrangeGrob(ggplotGrob(ctrp_mut_filt_plot), left = textGrob("D", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
-             arrangeGrob(ggplotGrob(gdsc_mut_filt_plot), left = textGrob("E", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))))
-
-png(filename = "./plots/manuscript_final/mutation_pancancer_small.png", width = 15, height = 17, units = "in", res = 100)
-grid.arrange(layout_matrix = lay, grobs = gs_mut)
-dev.off()
-
-png(filename = "./plots/manuscript_final/mutation_pancancer.png", width = 15, height = 17, units = "in", res = 500)
-grid.arrange(layout_matrix = lay, grobs = gs_mut)
-dev.off()
-```
-
-## Protein changes figure
+ccle_signif_prot_lin$disease_g2p <- ifelse(ccle_signif_prot_lin$disease %in% g2p_diseases, ccle_signif_prot_lin$disease, "other")
+ctrp_signif_prot_lin$disease_g2p <- ifelse(ctrp_signif_prot_lin$disease %in% g2p_diseases, ctrp_signif_prot_lin$disease, "other")
+gdsc_signif_prot_lin$disease_g2p <- ifelse(gdsc_signif_prot_lin$disease %in% g2p_diseases, gdsc_signif_prot_lin$disease, "other")
+
+ccle_signif_prot_lin_filt <- filter(ccle_signif_prot_lin, InG2P == "Yes")
+ctrp_signif_prot_lin_filt <- filter(ctrp_signif_prot_lin, InG2P == "Yes")
+gdsc_signif_prot_lin_filt <- filter(gdsc_signif_prot_lin, InG2P == "Yes")
+
+ctrp_prot_lin_filt <- filter(ctrp_prot, Drug_Gene_Protein_Change_Lineage %in% filter(ctrp_signif_prot_lin_filt, p < 0.05)$Drug_Gene_Protein_Change_Lineage)
+ctrp_prot_lin_filt_plot <- ggplot(data = ctrp_prot_lin_filt, mapping = aes(x = Change_Status, y = Score)) +
+  facet_wrap(~ Drug_Gene_Protein_Change_Lineage, nrow = 2) +
+  geom_violinhalf(aes(fill = Change_Status), position = position_nudge(x = 0.2, y = 0), alpha = 0.8, show.legend = FALSE) +
+  geom_point(aes(color = Change_Status), position = position_jitter(width = 0.15), size = 0.5, alpha = 0.6) +
+  geom_boxplot(width = 0.1, guides = FALSE, outlier.shape = NA, alpha = 0.4) +
+  scale_x_discrete(labels = c("No" = "Wildtype", "Yes" = "Mutant")) +
+  scale_fill_manual(labels = c("Wildtype", "Mutant"), values = c("Yes" = "steelblue4", "No" = "slategray3")) +
+  scale_color_manual(labels = c("Wildtype", "Mutant"), values = c("Yes" = "steelblue4", "No" = "slategray3")) +
+  scale_y_continuous(breaks = seq(0, 1.00, by = 0.25), labels = c("0.00", "0.25", "0.50", "0.75", "1.00")) +
+  coord_cartesian(ylim = c(0, 1.10)) +
+  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35, label.y = 1.1) +
+  labs(title = "CTRP", x = "Change Status", y = "AUC") +
+  guides(color = guide_legend(override.aes = list(size = 3))) +
+  theme(legend.position = "none", axis.title.x = element_blank(),
+        panel.background = element_rect(fill = "whitesmoke", colour = "whitesmoke", size = 0.5, linetype = "solid"),
+        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+
+lay <- rbind(c(1, 1, 1, 1, 2, 2),
+             c(3, 3, 3, 3, 3, 4))
+
+gs_prot <- gList(arrangeGrob(ht_prot_grob, left = textGrob("A", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(ggplotGrob(gdsc_prot_filt_plot), left = textGrob("B", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(ggplotGrob(ctrp_prot_filt_plot), left = textGrob("C", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(ggplotGrob(ctrp_prot_lin_filt_plot), left = textGrob("D", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))))
+
+png(filename = "./plots/manuscript_final/drug_protein_pancancer_small.png", width = 13, height = 10, units = "in", res = 100)
+grid.arrange(layout_matrix = lay, grobs = gs_prot)
+dev.off()
+
+png(filename = "./plots/manuscript_final/drug_protein_pancancer.png", width = 13, height = 10, units = "in", res = 500)
+grid.arrange(layout_matrix = lay, grobs = gs_prot)
+dev.off()
+```
 
@@
 
-```{r prot_changes_fig, eval = FALSE, fig.height=15, fig.width=15}
+```{r prot_changes_fig, eval=FALSE, fig.height=15, fig.width=15}
 ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot_4plot, feature = "protein changes", legend_title = "CCLE -log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "darkgreen", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.021)
@@
         panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
-
-ccle_prot_filt <- filter(ccle_prot, Drug_Gene_Protein_Change %in% filter(ccle_signif_prot_summ, p < 0.05)$Drug_Gene_Protein_Change)
 
@@
   theme(legend.position = "none", axis.title.x = element_blank(),
-        panel.background = element_rect(fill = "lightcyan", colour = "lightcyan", size = 0.5, linetype = "solid"),
+        panel.background = element_rect(fill = "azure", colour = "azure", size = 0.5, linetype = "solid"),
         panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
@@
 
-```{r CN_GE_fig, eval = FALSE, fig.height=10, fig.width=15}
+```{r CN_GE_fig, eval=FALSE, fig.height=10, fig.width=15}
 # Copy number
-
-crispr_cn_cor_4plot <- unfactorize(filter(cn_cor, Dataset == "CRISPR" & Gene %in% unique(g2p_amp$Gene)))
-ccle_cn_cor_4plot <- unfactorize(filter(cn_cor, Dataset == "CCLE" & Gene %in% unique(g2p_amp$Gene)))
-ctrp_cn_cor_4plot <- unfactorize(filter(cn_cor, Dataset == "CTRP" & Gene %in% unique(g2p_amp$Gene)))
-gdsc_cn_cor_4plot <- unfactorize(filter(cn_cor, Dataset == "GDSC" & Gene %in% unique(g2p_amp$Gene)))
-crispr_cn_ht2 <- MakeCorrHeatmap(cor_res = crispr_cn_cor_4plot, row_names = TRUE, heatmap_legend = TRUE, col_title = "CRISPR", color_range = c(-0.25, 0, 0.25), radius = 0.15, legend_title = "Copy num.
+cn_genes <- unique(filter(cn_cor, Dataset != "CRISPR" & InG2P == "Yes")$Gene)
+cn_drugs <- unique(filter(cn_cor, Dataset != "CRISPR" & InG2P == "Yes")$Drug)
+
+ccle_cn_ht2 <- MakeCorrHeatmap(cor_res = filter(cn_cor, Dataset == "CCLE" & Drug %in% cn_drugs & Gene %in% cn_genes), row_names = TRUE, heatmap_legend = TRUE, col_title = "CCLE", color_range = c(-0.2, 0, 0.2), radius = 0.025, legend_title = "Copy num.
 Spearman correlation", metric = "CN")
-ccle_cn_ht2 <- MakeCorrHeatmap(cor_res = ccle_cn_cor_4plot, row_names = FALSE, heatmap_legend = FALSE, col_title = "CCLE", color_range = c(-0.25, 0, 0.25), radius = 0.025, legend_title = "Copy num.
+ctrp_cn_ht2 <- MakeCorrHeatmap(cor_res = filter(cn_cor, Dataset == "CTRP" & Drug %in% cn_drugs & Gene %in% cn_genes), row_names = TRUE, heatmap_legend = FALSE, col_title = "CTRP", color_range = c(-0.2, 0, 0.2), radius = 0.025, legend_title = "Copy num.
 Spearman correlation", metric = "CN")
-ctrp_cn_ht2 <- MakeCorrHeatmap(cor_res = ctrp_cn_cor_4plot, row_names = FALSE, heatmap_legend = FALSE, col_title = "CTRP", color_range = c(-0.25, 0, 0.25), radius = 0.025, legend_title = "Copy num.
+gdsc_cn_ht2 <- MakeCorrHeatmap(cor_res = filter(cn_cor, Dataset == "GDSC" & Drug %in% cn_drugs & Gene %in% cn_genes), row_names = TRUE, heatmap_legend = FALSE, col_title = "GDSC", color_range = c(-0.2, 0, 0.2), radius = 0.025, legend_title = "Copy num.
 Spearman correlation", metric = "CN")
-gdsc_cn_ht2 <- MakeCorrHeatmap(cor_res = gdsc_cn_cor_4plot, row_names = FALSE, heatmap_legend = FALSE, col_title = "GDSC", color_range = c(-0.25, 0, 0.25), radius = 0.025, legend_title = "Copy num.
-Spearman correlation", metric = "CN")
-ht_cn_list <- crispr_cn_ht2 + ccle_cn_ht2 + ctrp_cn_ht2 + gdsc_cn_ht2
+ht_cn_list <- ccle_cn_ht2 + ctrp_cn_ht2 + gdsc_cn_ht2
 lgd <- list(Legend(labels = c("Resistance", "Sensitivity", "p < 0.05"), type = "points", pch = c(21, 21, 8), nrow = 3, background = "white", legend_gp = gpar(col = "black", fill = c("red", "white"))))
-ht_cn_grob <- grid.grabExpr(draw(ht_cn_list, gap = unit(0.25, "in"), heatmap_legend_side = "top", annotation_legend_list = lgd, annotation_legend_side = "top", merge_legend = TRUE))
+ht_cn_grob <- grid.grabExpr(draw(ht_cn_list, gap = unit(0.25, "in"), heatmap_legend_side = "bottom", annotation_legend_list = lgd, annotation_legend_side = "bottom", merge_legend = TRUE))
 
 cn_cor$p.format <- with(cn_cor, ifelse(CN_p < 0.001, "p < 0.001", paste0("p = ", round(CN_p, digits = 3))))
-crispr_cn_cor <- unfactorize(filter(cn_cor, Dataset == "CRISPR" & InG2P == "Yes"))
 ccle_cn_cor <- unfactorize(filter(cn_cor, Dataset == "CCLE" & InG2P == "Yes"))
@@
 
-crispr_cn_cor_filt <- filter(crispr_cn_cor, CN_p < 0.05)
-crispr_cn_filt <- filter(crispr, Gene %in% crispr_cn_cor_filt$Gene)
-crispr_text <- data.frame(label = paste0("r = ", round(crispr_cn_cor_filt$CN_r, digits = 3), ",\n", crispr_cn_cor_filt$p.format), Gene = crispr_cn_cor_filt$Gene)
-crispr_cn_filt_plot <- ggplot(data = crispr_cn_filt, aes(x = CN, y = Score) )+
-  facet_wrap(~ Gene) +
-  geom_point(fill = "darkorchid", pch = 21, size = 1, alpha = 0.7) +
-  geom_text(data = crispr_text,
-            mapping = aes(x = +Inf, y = +Inf, label = label,
-            hjust = 1.1, vjust = 1.2)) +
-  scale_y_continuous(breaks = seq(-3, 1, by = 0.5), labels = c("-3.0", "-2.5", "-2.0", "-1.5", "-1.0", "-0.5", "0.0", "0.5", "1.0")) +
-  labs(title = "CRISPR", x = "Copy number (log2)", y = "CERES Score") +
-  theme(legend.position = "none",
-        panel.background = element_rect(fill = "snow1", colour = "snow1", size = 0.5, linetype = "solid"),
-        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
-        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
-
 ccle_cn_cor_filt <- filter(ccle_cn_cor, CN_p < 0.05)
@@
 ccle_text <- data.frame(label = paste0("r = ", round(ccle_cn_cor_filt$CN_r, digits = 3), ", ", ccle_cn_cor_filt$p.format), Drug_Gene = ccle_cn_cor_filt$Drug_Gene)
-ccle_cn_filt_plot <- ggplot(data = ccle_cn_filt, aes(x = CN, y = Score) )+
+ccle_cn_filt_plot <- ggplot(data = ccle_cn_filt, aes(x = CN, y = Score)) +
   facet_wrap(~ Drug_Gene) +
-  geom_point(fill = "springgreen4", pch = 21, size = 1, alpha = 0.7) +
+  geom_point(aes(color = disease_g2p), pch = 20, size = 1, alpha = 0.7) +
   geom_text(data = ccle_text,
@@
             hjust = 1.05, vjust = 1.2)) +
+  scale_color_manual(values = g2p_disease_colors) +
   labs(title = "CCLE", x = "Copy number (log2)", y = "AUC") +
@@
 ctrp_text <- data.frame(label = paste0("r = ", round(ctrp_cn_cor_filt$CN_r, digits = 3), ",\n", ctrp_cn_cor_filt$p.format), Drug_Gene = ctrp_cn_cor_filt$Drug_Gene)
-ctrp_cn_filt_plot <- ggplot(data = ctrp_cn_filt, aes(x = CN, y = Score) )+
+ctrp_cn_filt_plot <- ggplot(data = ctrp_cn_filt, aes(x = CN, y = Score)) +
   facet_wrap(~ Drug_Gene) +
-  geom_point(fill = "steelblue4", pch = 21, size = 1, alpha = 0.7) +
+  geom_point(aes(color = disease_g2p), pch = 20, size = 1, alpha = 0.7) +
   geom_text(data = ctrp_text,
             mapping = aes(x = +Inf, y = +Inf, label = label,
-            hjust = 1.1, vjust = 1.2)) +
+            hjust = 1.3, vjust = 1.2)) +
   labs(title = "CTRP", x = "Copy number (log2)", y = "AUC") +
+  scale_color_manual(values = g2p_disease_colors) +
   theme(legend.position = "none",
@@
 
-crispr_ge_cor_4plot <- unfactorize(filter(ge_cor, Dataset == "CRISPR" & Gene %in% unique(g2p_expr$Gene)))
-ccle_ge_cor_4plot <- unfactorize(filter(ge_cor, Dataset == "CCLE" & Gene %in% unique(g2p_expr$Gene)))
-ctrp_ge_cor_4plot <- unfactorize(filter(ge_cor, Dataset == "CTRP" & Gene %in% unique(g2p_expr$Gene)))
-gdsc_ge_cor_4plot <- unfactorize(filter(ge_cor, Dataset == "GDSC" & Gene %in% unique(g2p_expr$Gene)))
-crispr_ge_ht2 <- MakeCorrHeatmap(cor_res = crispr_ge_cor_4plot, row_names = TRUE, heatmap_legend = TRUE, col_title = "CRISPR", color_range = c(-0.5, 0, 0.5), radius = 0.155, legend_title = "Gene expr.
+ge_genes <- unique(filter(ge_cor, Dataset != "CRISPR" & InG2P == "Yes")$Gene)
+ge_drugs <- unique(filter(ge_cor, Dataset != "CRISPR" & InG2P == "Yes")$Drug)
+
+# ccle_ge_ht2 <- MakeCorrHeatmap(cor_res = filter(ge_cor, Dataset == "CCLE" & Drug %in% ge_drugs & Gene %in% ge_genes), row_names = FALSE, heatmap_legend = FALSE, col_title = "CCLE", color_range = c(-0.5, 0, 0.5), radius = 0.07, legend_title = "Gene expr.
 Spearman correlation", metric = "GE")
-ccle_ge_ht2 <- MakeCorrHeatmap(cor_res = ccle_ge_cor_4plot, row_names = FALSE, heatmap_legend = FALSE, col_title = "CCLE", color_range = c(-0.5, 0, 0.5), radius = 0.07, legend_title = "Gene expr.
+# ctrp_ge_ht2 <- MakeCorrHeatmap(cor_res = filter(ge_cor, Dataset == "CTRP" & Drug %in% ge_drugs & Gene %in% ge_genes), row_names = FALSE, heatmap_legend = FALSE, col_title = "CTRP", color_range = c(-0.5, 0, 0.5), radius = 0.07, legend_title = "Gene expr.
 Spearman correlation", metric = "GE")
-ctrp_ge_ht2 <- MakeCorrHeatmap(cor_res = ctrp_ge_cor_4plot, row_names = FALSE, heatmap_legend = FALSE, col_title = "CTRP", color_range = c(-0.5, 0, 0.5), radius = 0.07, legend_title = "Gene expr.
+# gdsc_ge_ht2 <- MakeCorrHeatmap(cor_res = filter(ge_cor, Dataset == "GDSC" & Drug %in% ge_drugs & Gene %in% ge_genes), row_names = FALSE, heatmap_legend = FALSE, col_title = "GDSC", color_range = c(-0.5, 0, 0.5), radius = 0.07, legend_title = "Gene expr.
 Spearman correlation", metric = "GE")
-gdsc_ge_ht2 <- MakeCorrHeatmap(cor_res = gdsc_ge_cor_4plot, row_names = FALSE, heatmap_legend = FALSE, col_title = "GDSC", color_range = c(-0.5, 0, 0.5), radius = 0.07, legend_title = "Gene expr.
-Spearman correlation", metric = "GE")
-ht_ge_list <- crispr_ge_ht2 + ccle_ge_ht2 + ctrp_ge_ht2 + gdsc_ge_ht2
-ht_ge_grob <- grid.grabExpr(draw(ht_ge_list, gap = unit(0.25, "in"), heatmap_legend_side = "top", annotation_legend_list = lgd, annotation_legend_side = "top", merge_legend = TRUE))
+# ht_ge_list <- ccle_ge_ht2 + ctrp_ge_ht2 + gdsc_ge_ht2
+# ht_ge_grob <- grid.grabExpr(draw(ht_ge_list, gap = unit(0.25, "in"), heatmap_legend_side = "top", annotation_legend_list = lgd, annotation_legend_side = "top", merge_legend = TRUE))
 
 ge_cor$p.format <- with(ge_cor, ifelse(GE_p < 0.001, "p < 0.001", paste0("p = ", round(GE_p, digits = 3))))
-crispr_ge_cor <- unfactorize(filter(ge_cor, Dataset == "CRISPR" & InG2P == "Yes"))
 ccle_ge_cor <- unfactorize(filter(ge_cor, Dataset == "CCLE" & InG2P == "Yes"))
@@
 gdsc_ge_cor <- unfactorize(filter(ge_cor, Dataset == "GDSC" & InG2P == "Yes"))
-
-crispr_ge_cor_filt <- filter(crispr_ge_cor, GE_p < 0.05)
-crispr_ge_filt <- filter(crispr, Gene %in% crispr_ge_cor_filt$Gene)
-crispr_text <- data.frame(label = paste0("r = ", round(crispr_ge_cor_filt$GE_r, digits = 3), ",\n", crispr_ge_cor_filt$p.format), Gene = crispr_ge_cor_filt$Gene)
-crispr_ge_filt_plot <- ggplot(data = crispr_ge_filt, aes(x = TPM, y = Score) )+
-  facet_wrap(~ Gene) +
-  geom_point(fill = "darkorchid", pch = 21, size = 1, alpha = 0.7) +
-  geom_text(data = crispr_text,
-            mapping = aes(x = +Inf, y = +Inf, label = label,
-            hjust = 1.1, vjust = 1.2)) +
-  scale_y_continuous(breaks = seq(-3, 1, by = 0.5), labels = c("-3.0", "-2.5", "-2.0", "-1.5", "-1.0", "-0.5", "0.0", "0.5", "1.0")) +
-  labs(title = "CRISPR", x = "Gene expression [log2(TPM)]", y = "CERES Score") +
-  theme(legend.position = "none",
-        panel.background = element_rect(fill = "snow1", colour = "snow1", size = 0.5, linetype = "solid"),
-        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
-        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
 
@@
   facet_wrap(~ Drug_Gene) +
-  geom_point(fill = "springgreen4", pch = 21, size = 1, alpha = 0.7) +
+  geom_point(aes(color = disease_g2p), pch = 20, size = 1, alpha = 0.7) +
   geom_text(data = ccle_text,
@@
             hjust = 1.37, vjust = 1.2)) +
+  scale_color_manual(values = g2p_disease_colors) +
   labs(title = "CCLE", x = "Gene expression [log2(TPM)]", y = "AUC") +
@@
   facet_wrap(~ Drug_Gene) +
-  geom_point(fill = "steelblue4", pch = 21, size = 1, alpha = 0.7) +
+  geom_point(aes(color = disease_g2p), pch = 20, size = 1, alpha = 0.7) +
   geom_text(data = ctrp_text,
             mapping = aes(x = +Inf, y = +Inf, label = label,
-            hjust = 1.1, vjust = 9.1)) +
+            hjust = 1.1, vjust = 1.2)) +
+  scale_color_manual(name = "Lineages", values = g2p_disease_colors) +
   labs(title = "CTRP", x = "Gene expression [log2(TPM)]", y = "AUC") +
-  theme(legend.position = "none",
-        panel.background = element_rect(fill = "whitesmoke", colour = "whitesmoke", size = 0.5, linetype = "solid"),
+  guides(color = guide_legend(override.aes = list(size = 3))) +
+  theme(panel.background = element_rect(fill = "whitesmoke", colour = "whitesmoke", size = 0.5, linetype = "solid"),
         panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
@@
   facet_wrap(~ Drug_Gene) +
-  geom_point(fill = "turquoise4", pch = 21, size = 1, alpha = 0.7) +
+  geom_point(aes(color = disease_g2p), pch = 20, size = 1, alpha = 0.7) +
   geom_text(data = gdsc_text,
@@
   coord_cartesian(ylim = c(0, 1.00)) +
+  scale_color_manual(values = g2p_disease_colors) +
   labs(title = "GDSC", x = "Gene expression [log2(TPM)]", y = "AUC") +
   theme(legend.position = "none",
-        panel.background = element_rect(fill = "lightcyan", colour = "lightcyan", size = 0.5, linetype = "solid"),
+        panel.background = element_rect(fill = "azure", colour = "azure", size = 0.5, linetype = "solid"),
         panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
@@
 
-hlay <- rbind(c(1, 1, 1, 1, 1, 1, 1),
-              c(1, 1, 1, 1, 1, 1, 1),
-              c(1, 1, 1, 1, 1, 1, 1),
-              c(2, 2, 3, 3, 4, NA, NA),
-              c(2, 2, 3, 3, 4, NA, NA),
-              c(2, 2, 3, 3, 4, NA, NA),
-              c(5, 5, 5, 5, 5, 5, 5),
-              c(5, 5, 5, 5, 5, 5, 5),
-              c(6, 7, 8, 8, 8, 9, 9),
-              c(6, 7, 8, 8, 8, 9, 9),
-              c(6, 7, 8, 8, 8, 9, 9))
-
-select_grobs <- function(lay) {
-  id <- unique(c(t(lay))) 
-  id[!is.na(id)]
-}
+lay <- rbind(c(1, 2, 3),
+             c(4, 6, 6),
+             c(5, 5, 5))
 
 gs_cn_ge <- gList(arrangeGrob(ht_cn_grob, left = textGrob("A", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
-             arrangeGrob(ggplotGrob(crispr_cn_filt_plot), left = textGrob("B", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
-             arrangeGrob(ggplotGrob(ccle_cn_filt_plot), left = textGrob("C", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
-             arrangeGrob(ggplotGrob(ctrp_cn_filt_plot), left = textGrob("D", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
-             arrangeGrob(ht_ge_grob, left = textGrob("E", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
-             arrangeGrob(ggplotGrob(crispr_ge_filt_plot), left = textGrob("F", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
-             arrangeGrob(ggplotGrob(ccle_ge_filt_plot), left = textGrob("G", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
-             arrangeGrob(ggplotGrob(ctrp_ge_filt_plot), left = textGrob("H", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
-             arrangeGrob(ggplotGrob(gdsc_ge_filt_plot), left = textGrob("I", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))))
-
-png(filename = "./plots/manuscript_final/cn_ge_pancancer_small.png", width = 20, height = 15, units = "in", res = 100)
-grid.arrange(layout_matrix = hlay, grobs = gs_cn_ge[select_grobs(hlay)])
-dev.off()
-
-png(filename = "./plots/manuscript_final/cn_ge_pancancer.png", width = 20, height = 15, units = "in", res = 500)
-grid.arrange(layout_matrix = hlay, grobs = gs_cn_ge[select_grobs(hlay)])
+             arrangeGrob(ggplotGrob(ccle_cn_filt_plot), left = textGrob("B", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(ggplotGrob(ctrp_cn_filt_plot), left = textGrob("C", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             # arrangeGrob(ht_ge_grob, left = textGrob("E", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(ggplotGrob(ccle_ge_filt_plot), left = textGrob("D", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(ggplotGrob(ctrp_ge_filt_plot), left = textGrob("F", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(ggplotGrob(gdsc_ge_filt_plot), left = textGrob("E", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))))
+
+png(filename = "./plots/manuscript_final/drug_cn_ge_pancancer_small.png", width = 15, height = 11, units = "in", res = 100)
+grid.arrange(layout_matrix = lay, grobs = gs_cn_ge)
+dev.off()
+
+png(filename = "./plots/manuscript_final/drug_cn_ge_pancancer.png", width = 15, height = 11, units = "in", res = 500)
+grid.arrange(layout_matrix = lay, grobs = gs_cn_ge)
 dev.off()
@@
 
-Mutation:
 ```{r}
-crispr_mut_lin <- filter(crispr_signif_lin, InG2P == "Yes")
+g2p_disease_colors
+
+gdsc_signif_prot_summ <- filter(gdsc_signif_prot, InG2P == "Yes") 
+ctrp_prot_filt <- filter(ctrp_prot, Drug_Gene_Protein_Change %in% filter(ctrp_signif_prot_summ, p < 0.05)$Drug_Gene_Protein_Change)
+
+# ccle_prot_annot <- select(filter(ccle_prot, Drug_Gene %in% ccle_mut_lin_filt$Drug_Gene & Change_Status == "Yes"), Drug_Gene, Protein_Change, DepMap_ID) 
+# test <- merge(ccle_mut_lin_filt, ccle_prot_annot, by = c("DepMap_ID", "Drug_Gene"), all.x = TRUE)
+```
+
+```{r}
 ccle_mut_lin <- filter(ccle_signif_dgl, InG2P == "Yes")
@@
 gdsc_mut_lin <- filter(gdsc_signif_dgl, InG2P == "Yes")
-```
-
-```{r}
-crispr_test <- filter(crispr, Gene_Lin == "PTCH1_skin")
-ggplot(crispr_test, aes(x = as.character(Mutation), y = Score)) +
-  geom_boxplot() +
-  geom_point() +
-  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35)
-```
-
-```{r}
-crispr_Dup <- crispr[duplicated(crispr),]
-ccle_Dup <- ccle[duplicated(ccle),]
+
+ccle_mut_lin_filt <- filter(ccle, Drug_Gene_Lin %in% filter(ccle_mut_lin, p < 0.05)$Drug_Gene_Lin)
+ccle_mut_lin_filt_plot <- ggplot(data = ccle_mut_lin_filt, mapping = aes(x = as.character(Mutation), y = Score)) +
+  facet_wrap(~ Drug_Gene_Lin, nrow = 1) +
+  geom_violinhalf(aes(fill = as.character(Mutation)), position = position_nudge(x = 0.2, y = 0), alpha = 0.8, show.legend = FALSE) +
+  geom_point(aes(color =  as.character(Mutation)), position = position_jitter(width = 0.15), size = 0.5, alpha = 0.6) +
+  geom_boxplot(width = 0.1, guides = FALSE, outlier.shape = NA, alpha = 0.8) +
+  scale_fill_manual(labels = c("Wildtype", "Mutant"), values = c("1" = "springgreen4", "0" = "palegreen3")) +
+  scale_color_manual(labels = c("Wildtype", "Mutant"), values = c("1" = "springgreen4", "0" = "palegreen3")) +
+  scale_x_discrete(labels = c("0" = "Wildtype", "1" = "Mutant")) +
+  scale_y_continuous(breaks = seq(0, 1.00, by = 0.25), labels = c("0.00", "0.25", "0.50", "0.75", "1.00")) +
+  coord_cartesian(ylim = c(0, 1.10)) +
+  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35, label.y = 1.1) +
+  labs(title = "CCLE", x = "Mutation Status", y = "AUC") +
+  guides(color = guide_legend(override.aes = list(size = 3))) +
+  theme(legend.position = "none",axis.title.x = element_blank(),
+        panel.background = element_rect(fill = "mintcream", colour = "mintcream", size = 0.5, linetype = "solid"),
+        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+
+ctrp_mut_lin_filt <- filter(ctrp, Drug_Gene_Lin %in% filter(ctrp_mut_lin, p < 0.05)$Drug_Gene_Lin)
+ctrp_mut_lin_filt_plot <- ggplot(data = ctrp_mut_lin_filt, mapping = aes(x = as.character(Mutation), y = Score)) +
+  facet_wrap(~ Drug_Gene_Lin, ncol = 4) +
+  geom_violinhalf(aes(fill = as.character(Mutation)), position = position_nudge(x = 0.2, y = 0), alpha = 0.8, show.legend = FALSE) +
+  geom_point(aes(color =  as.character(Mutation)), position = position_jitter(width = 0.15), size = 0.5, alpha = 0.6) +
+  geom_boxplot(width = 0.1, guides = FALSE, outlier.shape = NA, alpha = 0.8) +
+  scale_fill_manual(labels = c("Wildtype", "Mutant"), values = c("1" = "steelblue4", "0" = "slategray3")) +
+  scale_color_manual(labels = c("Wildtype", "Mutant"), values = c("1" = "steelblue4", "0" = "slategray3")) +
+  scale_x_discrete(labels = c("0" = "Wildtype", "1" = "Mutant")) +
+  scale_y_continuous(breaks = seq(0, 1.00, by = 0.25), labels = c("0.00", "0.25", "0.50", "0.75", "1.00")) +
+  coord_cartesian(ylim = c(0, 1.10)) +
+  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35, label.y = 1.1) +
+  labs(title = "CTRP", x = "Mutation Status", y = "AUC") +
+  guides(color = guide_legend(override.aes = list(size = 3))) +
+  theme(legend.position = "none", axis.title.x = element_blank(),
+        panel.background = element_rect(fill = "whitesmoke", colour = "whitesmoke", size = 0.5, linetype = "solid"),
+        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+
+gdsc_mut_lin_filt <- filter(gdsc, Drug_Gene_Lin %in% filter(gdsc_mut_lin, p < 0.05)$Drug_Gene_Lin)
+gdsc_mut_lin_filt_plot <- ggplot(data = gdsc_mut_lin_filt, mapping = aes(x = as.character(Mutation), y = Score)) +
+  facet_wrap(~ Drug_Gene_Lin, nrow = 1) +
+  geom_violinhalf(aes(fill = as.character(Mutation)), position = position_nudge(x = 0.2, y = 0), alpha = 0.8, show.legend = FALSE) +
+  geom_point(aes(color = as.character(Mutation)), position = position_jitter(width = 0.15), size = 0.5, alpha = 0.6) +
+  geom_boxplot(width = 0.1, guides = FALSE, outlier.shape = NA, alpha = 0.8) +
+  scale_fill_manual(labels = c("Wildtype", "Mutant"), values = c("1" = "turquoise4", "0" = "paleturquoise3")) +
+  scale_color_manual(labels = c("Wildtype", "Mutant"), values = c("1" = "turquoise4", "0" = "paleturquoise3")) +
+  scale_x_discrete(labels = c("0" = "Wildtype", "1" = "Mutant")) +
+  scale_y_continuous(breaks = seq(0, 1.00, by = 0.25), labels = c("0.00", "0.25", "0.50", "0.75", "1.00")) +
+  coord_cartesian(ylim = c(0, 0.6)) +
+  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35, label.y = 0.6) +
+  labs(title = "GDSC", x = "Mutation Status", y = "AUC") +
+  guides(color = guide_legend(override.aes = list(size = 3))) +
+  theme(legend.position = "none", axis.title.x = element_blank(),
+        panel.background = element_rect(fill = "azure", colour = "azure", size = 0.5, linetype = "solid"),
+        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+
+cn_cor_lin$p.format <- with(cn_cor_lin, ifelse(CN_p < 0.001, "p < 0.001", paste0("p = ", round(CN_p, digits = 3))))
+ccle_cn_lin_cor <- unfactorize(filter(cn_cor_lin, Dataset == "CCLE" & InG2P == "Yes"))
+ctrp_cn_lin_cor <- unfactorize(filter(cn_cor_lin, Dataset == "CTRP" & InG2P == "Yes"))
+gdsc_cn_lin_cor <- unfactorize(filter(cn_cor_lin, Dataset == "GDSC" & InG2P == "Yes"))
+
+ccle_cn_lin_cor_filt <- filter(ccle_cn_lin_cor, CN_p < 0.05)
+ccle_cn_lin_filt <- filter(ccle, Drug_Gene_Lin %in% ccle_cn_lin_cor_filt$Drug_Gene_Lin)
+ccle_lin_text <- data.frame(label = paste0("r = ", round(ccle_cn_lin_cor_filt$CN_r, digits = 3), ", ", ccle_cn_lin_cor_filt$p.format), Drug_Gene_Lin = ccle_cn_lin_cor_filt$Drug_Gene_Lin)
+ccle_cn_lin_filt_plot <- ggplot(data = ccle_cn_lin_filt, aes(x = CN, y = Score)) +
+  facet_wrap(~ Drug_Gene_Lin) +
+  geom_point(aes(color = disease_g2p), pch = 20, size = 1, alpha = 0.7) +
+  geom_text(data = ccle_lin_text,
+            mapping = aes(x = +Inf, y = +Inf, label = label,
+            hjust = 1.1, vjust = 1.2)) +
+  geom_smooth(stat = "smooth", method = "lm", color = "gray70", fill = "gray88", lwd = 1) +
+  scale_color_manual(values = g2p_disease_colors) +
+  coord_cartesian(ylim = c(0, 1)) +
+  labs(title = "CCLE", x = "Copy number (log2)", y = "AUC") +
+  theme(legend.position = "none",
+        panel.background = element_rect(fill = "mintcream", colour = "mintcream", size = 0.5, linetype = "solid"),
+        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+
+ctrp_cn_lin_cor_filt <- filter(ctrp_cn_lin_cor, CN_p < 0.05)
+ctrp_cn_lin_filt <- filter(ctrp, Drug_Gene_Lin %in% ctrp_cn_lin_cor_filt$Drug_Gene_Lin)
+ctrp_lin_text <- data.frame(label = paste0("r = ", round(ctrp_cn_lin_cor_filt$CN_r, digits = 3), ", ", ctrp_cn_lin_cor_filt$p.format), Drug_Gene_Lin = ctrp_cn_lin_cor_filt$Drug_Gene_Lin)
+ctrp_cn_lin_filt_plot <- ggplot(data = ctrp_cn_lin_filt, aes(x = CN, y = Score)) +
+  facet_wrap(~ Drug_Gene_Lin) +
+  geom_point(aes(color = disease_g2p), pch = 20, size = 1, alpha = 0.7) +
+  geom_text(data = ctrp_lin_text,
+            mapping = aes(x = +Inf, y = +Inf, label = label,
+            hjust = 1.1, vjust = 1.2)) +
+  geom_smooth(stat = "smooth", method = "lm", color = "gray70", fill = "gray88", lwd = 1) +
+  labs(title = "CTRP", x = "Copy number (log2)", y = "AUC") +
+  scale_color_manual(values = g2p_disease_colors) +
+  coord_cartesian(ylim = c(0, 1)) +
+  theme(legend.position = "none",
+        panel.background = element_rect(fill = "whitesmoke", colour = "whitesmoke", size = 0.5, linetype = "solid"),
+        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+
+gdsc_cn_lin_cor_filt <- filter(gdsc_cn_lin_cor, CN_p < 0.05)
+gdsc_cn_lin_filt <- filter(gdsc, Drug_Gene_Lin %in% gdsc_cn_lin_cor_filt$Drug_Gene_Lin)
+gdsc_lin_text <- data.frame(label = paste0("r = ", round(gdsc_cn_lin_cor_filt$CN_r, digits = 3), ", ", gdsc_cn_lin_cor_filt$p.format), Drug_Gene_Lin = gdsc_cn_lin_cor_filt$Drug_Gene_Lin)
+gdsc_cn_lin_filt_plot <- ggplot(data = gdsc_cn_lin_filt, aes(x = TPM, y = Score) )+
+  facet_wrap(~ Drug_Gene_Lin) +
+  geom_point(aes(color = disease_g2p), pch = 20, size = 1, alpha = 0.7) +
+  geom_text(data = gdsc_lin_text,
+            mapping = aes(x = +Inf, y = +Inf, label = label,
+            hjust = 1.1, vjust = 1.2)) +
+  geom_smooth(stat = "smooth", method = "lm", color = "gray70", fill = "gray88", lwd = 1) +
+  scale_y_continuous(breaks = seq(0, 1.00, by = 0.25), labels = c("0.00", "0.25", "0.50", "0.75", "1.00")) +
+  coord_cartesian(ylim = c(0, 1.00)) +
+  scale_color_manual(values = g2p_disease_colors) +
+  labs(title = "GDSC", x = "Copy number (log2)", y = "AUC") +
+  theme(legend.position = "none",
+        panel.background = element_rect(fill = "azure", colour = "azure", size = 0.5, linetype = "solid"),
+        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+
+ge_cor_lin$p.format <- with(ge_cor_lin, ifelse(GE_p < 0.001, "p < 0.001", paste0("p = ", round(GE_p, digits = 3))))
+ccle_ge_lin_cor <- unfactorize(filter(ge_cor_lin, Dataset == "CCLE" & InG2P == "Yes"))
+ctrp_ge_lin_cor <- unfactorize(filter(ge_cor_lin, Dataset == "CTRP" & InG2P == "Yes"))
+gdsc_ge_lin_cor <- unfactorize(filter(ge_cor_lin, Dataset == "GDSC" & InG2P == "Yes"))
+
+ccle_ge_lin_cor_filt <- filter(ccle_ge_lin_cor, GE_p < 0.05)
+ccle_ge_lin_filt <- filter(ccle, Drug_Gene_Lin %in% ccle_ge_lin_cor_filt$Drug_Gene_Lin)
+ccle_text <- data.frame(label = paste0("r = ", round(ccle_ge_lin_cor_filt$GE_r, digits = 3), ", ", ccle_ge_lin_cor_filt$p.format), Drug_Gene = ccle_ge_lin_cor_filt$Drug_Gene_Lin)
+ccle_ge_lin_filt_plot <- ggplot(data = ccle_ge_lin_filt, aes(x = TPM, y = Score))+
+  facet_wrap(~ Drug_Gene_Lin) +
+  geom_point(aes(color = disease_g2p), pch = 20, size = 1, alpha = 0.7) +
+  geom_text(data = ccle_text,
+            mapping = aes(x = +Inf, y = +Inf, label = label,
+            hjust = 1.1, vjust = 1.2)) +
+  coord_cartesian(ylim = c(0, 1)) +
+  geom_smooth(stat = "smooth", method = "lm", color = "gray70", fill = "gray88", lwd = 1) +
+  scale_color_manual(values = g2p_disease_colors) +
+  labs(title = "CCLE", x = "Gene expression [log2(TPM)]", y = "AUC") +
+  theme(legend.position = "none",
+        panel.background = element_rect(fill = "mintcream", colour = "mintcream", size = 0.5, linetype = "solid"),
+        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+
+ctrp_ge_lin_cor_filt <- filter(ctrp_ge_lin_cor, GE_p < 0.05)
+# ctrp_ge_lin_filt <- filter(ctrp, Drug_Gene_Lin %in% ctrp_ge_lin_cor_filt$Drug_Gene_Lin)
+# ctrp_text <- data.frame(label = paste0("r = ", round(ctrp_ge_lin_cor_filt$GE_r, digits = 3), ",\n", ctrp_ge_lin_cor_filt$p.format), Drug_Gene_Lin = ctrp_ge_lin_cor_filt$Drug_Gene_Lin)
+# ctrp_ge_lin_filt_plot <- ggplot(data = ctrp_ge_lin_filt, aes(x = TPM, y = Score) )+
+#   facet_wrap(~ Drug_Gene_Lin) +
+#   geom_point(aes(color = disease_g2p), pch = 20, size = 1, alpha = 0.7) +
+#   geom_text(data = ctrp_text,
+#             mapping = aes(x = +Inf, y = +Inf, label = label,
+#             hjust = 1.1, vjust = 1.2)) +
+#   scale_color_manual(name = "Lineages", values = g2p_disease_colors) +
+#   labs(title = "CTRP", x = "Gene expression [log2(TPM)]", y = "AUC") +
+#   guides(color = guide_legend(override.aes = list(size = 3))) +
+#   theme(panel.background = element_rect(fill = "whitesmoke", colour = "whitesmoke", size = 0.5, linetype = "solid"),
+#         panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+#         panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+
+gdsc_ge_lin_cor_filt <- filter(gdsc_ge_lin_cor, GE_p < 0.05)
+# gdsc_ge_lin_filt <- filter(gdsc, Drug_Gene_Lin %in% gdsc_ge_lin_cor_filt$Drug_Gene_Lin)
+# gdsc_text <- data.frame(label = paste0("r = ", round(gdsc_ge_lin_cor_filt$GE_r, digits = 3), ",\n", gdsc_ge_lin_cor_filt$p.format), Drug_Gene_Lin = gdsc_ge_lin_cor_filt$Drug_Gene_Lin)
+# gdsc_ge_lin_filt_plot <- ggplot(data = gdsc_ge_lin_filt, aes(x = TPM, y = Score) )+
+#   facet_wrap(~ Drug_Gene_Lin) +
+#   geom_point(aes(color = disease_g2p), pch = 20, size = 1, alpha = 0.7) +
+#   geom_text(data = gdsc_text,
+#             mapping = aes(x = +Inf, y = +Inf, label = label,
+#             hjust = 1.1, vjust = 1.2)) +
+#   scale_y_continuous(breaks = seq(0, 1.00, by = 0.25), labels = c("0.00", "0.25", "0.50", "0.75", "1.00")) +
+#   coord_cartesian(ylim = c(0, 1.00)) +
+#   scale_color_manual(values = g2p_disease_colors) +
+#   labs(title = "GDSC", x = "Gene expression [log2(TPM)]", y = "AUC") +
+#   theme(legend.position = "none",
+#         panel.background = element_rect(fill = "azure", colour = "azure", size = 0.5, linetype = "solid"),
+#         panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+#         panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+
+lay <- rbind(c(1, 2, 2, 2, 2, 3, 3, 3),
+             c(4, 4, 5, 5, 6, 6, 7, 7),
+             c(4, 4, 5, 5, 6, 6, 7, 7))
+
+gs_cn_ge <- gList(arrangeGrob(ggplotGrob(ccle_mut_lin_filt_plot), left = textGrob("A", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(ggplotGrob(ctrp_mut_lin_filt_plot), left = textGrob("B", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(ggplotGrob(gdsc_mut_lin_filt_plot), left = textGrob("C", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(ggplotGrob(ccle_cn_lin_filt_plot), left = textGrob("D", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(ggplotGrob(ctrp_cn_lin_filt_plot), left = textGrob("", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(ggplotGrob(gdsc_cn_lin_filt_plot), left = textGrob("", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
+             arrangeGrob(ggplotGrob(ccle_ge_lin_filt_plot), left = textGrob("E", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))))
+
+png(filename = "./plots/manuscript_final/drug_lin_pancancer_small.png", width = 18, height = 8, units = "in", res = 100)
+grid.arrange(layout_matrix = lay, grobs = gs_cn_ge)
+dev.off()
+
+png(filename = "./plots/manuscript_final/drug_lin__pancancer.png", width = 18, height = 8, units = "in", res = 500)
+grid.arrange(layout_matrix = lay, grobs = gs_cn_ge)
+dev.off()
 ```
@@
 
+## Clustered AUC heatmap
+
+```{r auc_clustered_ht, eval=FALSE}
+ccle_auc_grid <- dcast(ccle, Drug ~ DepMap_ID, value.var = "Score", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Drug)
+ctrp_auc_grid <- dcast(ctrp, Drug ~ DepMap_ID, value.var = "Score", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Drug)
+gdsc_auc_grid <- dcast(gdsc, Drug ~ DepMap_ID, value.var = "Score", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Drug)
+
+ccle_lineages_ha <- merge(data.frame("DepMap_ID" = colnames(ccle_auc_grid)), ccl_meta, by = "DepMap_ID", all.x = TRUE) %>% `rownames<-`(.[,1]) %>% select(-DepMap_ID)
+ctrp_lineages_ha <- merge(data.frame("DepMap_ID" = colnames(ctrp_auc_grid)), ccl_meta, by = "DepMap_ID", all.x = TRUE) %>% `rownames<-`(.[,1]) %>% select(-DepMap_ID)
+gdsc_lineages_ha <- merge(data.frame("DepMap_ID" = colnames(gdsc_auc_grid)), ccl_meta, by = "DepMap_ID", all.x = TRUE) %>% `rownames<-`(.[,1]) %>% select(-DepMap_ID)
+
+ht_legend_list <- list(direction = "horizontal")
+
+ccle_col_fun <- colorRamp2(c(0, 1), c("gray97", "darkgreen"))
+ccle_auc_ha <- HeatmapAnnotation(Lineage = ccle_lineages_ha$disease, annotation_legend_param = list(Lineage = list(direction = "horizontal", nrow = 5)))
+ccle_auc_ht <- Heatmap(ccle_auc_grid,
+                       na_col = "black",
+                       col = ccle_col_fun,
+                       top_annotation = ccle_auc_ha,
+                       heatmap_legend_param = ht_legend_list,
+                       name = "AUC",
+                       show_column_names = FALSE, 
+                       row_title = "Drugs and Small Molecules",
+                       column_title = "Cancer Cell Lines",
+                       column_title_side = "top")
+
+ctrp_col_fun <- colorRamp2(c(0, 1), c("gray97", "steelblue4"))
+ctrp_auc_ha <- HeatmapAnnotation(Lineage = ctrp_lineages_ha$disease, annotation_legend_param = list(Lineage = list(direction = "horizontal", nrow = 3)))
+ctrp_auc_ht <- Heatmap(ctrp_auc_grid,
+                       na_col = "black",
+                       col = ctrp_col_fun,
+                       top_annotation = ctrp_auc_ha,
+                       heatmap_legend_param = ht_legend_list,
+                       name = "AUC",
+                       show_column_names = FALSE, 
+                       row_title = "Drugs and Small Molecules",
+                       column_title = "Cancer Cell Lines",
+                       column_title_side = "top")
+
+gdsc_col_fun <- colorRamp2(c(0, 1), c("gray97", "turquoise4"))
+gdsc_auc_ha <- HeatmapAnnotation(Lineage = gdsc_lineages_ha$disease, annotation_legend_param = list(Lineage = list(direction = "horizontal", nrow = 3)))
+gdsc_auc_ht <- Heatmap(gdsc_auc_grid,
+                       na_col = "black",
+                       col = gdsc_col_fun,
+                       top_annotation = gdsc_auc_ha,
+                       heatmap_legend_param = ht_legend_list,
+                       name = "AUC",
+                       show_column_names = FALSE, 
+                       row_title = "Drugs and Small Molecules",
+                       column_title = "Cancer Cell Lines",
+                       column_title_side = "top")
+
+png(filename = "./plots/manuscript/ccle_clustered_heatmap.png", width = 10, height = 8, units = "in", res = 500)
+draw(ccle_auc_ht, merge_legend = TRUE, heatmap_legend_side = "top", annotation_legend_side = "top")
+dev.off()
+
+png(filename = "./plots/manuscript/ctrp_clustered_heatmap.png", width = 22, height = 40, units = "in", res = 500)
+draw(ctrp_auc_ht, merge_legend = TRUE, heatmap_legend_side = "top", annotation_legend_side = "top")
+dev.off()
+
+png(filename = "./plots/manuscript/gdsc_clustered_heatmap.png", width = 18, height = 20, units = "in", res = 500)
+draw(gdsc_auc_ht, merge_legend = TRUE, heatmap_legend_side = "top", annotation_legend_side = "top")
+dev.off()
+```
+
+## Boxplots: Mut and fus
+
+```{r crispr_mut_boxplots, fig.height=5, fig.width=10, eval=FALSE}
+crispr_filt <- filter(crispr, Gene %in% g2p_mut_genes)
+crispr_filt$Gene <- factor(crispr_filt$Gene, levels = g2p_mut_genes)
+crispr_filt$Mutation <- as.character(crispr_filt$Mutation)
+crispr_signif_filt <- filter(crispr_signif_g2p_g, Gene %in% g2p_mut_genes)
+crispr_signif_filt$Gene <- factor(crispr_signif_filt$Gene, levels = g2p_mut_genes)
+
+crispr_gene_mut_plot <- ggplot(data = crispr_filt) +
+  facet_wrap(~ Gene, nrow = 2, drop = FALSE) +
+  scale_color_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "darkorchid", "0" = "thistle")) +
+  scale_x_discrete(name = "Mutation Status", labels = c("0" = "WT", "1" = "Mut")) +
+  geom_jitter(aes(x = Mutation, y = Score, color = Mutation), width = 0.2, alpha = 0.5, size = 0.6) +
+  geom_boxplot(aes(x = Mutation, y = Score), fill = "transparent", outlier.shape = NA, lwd = 0.3) +
+  geom_text(data = crispr_signif_filt, aes(x = 1.5, y = 2, label = p.signif)) +
+  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
+  theme(legend.position = "top", legend.direction = "horizontal") +
+  guides(color = guide_legend(override.aes = list(size = 3))) +
+  labs(y = "CERES Score")
+crispr_gene_mut_plot
+
+ggsave("./plots/manuscript/crispr_gene_mut_plot.png", crispr_gene_mut_plot, width = 12, height = 6, units = "in")
+```
+
+```{r fusion_boxplots, fig.height=5, fig.width=12, eval=FALSE}
+# CRISPR
+crispr_fus_filt <- filter(crispr_fus, FusionPair %in% c("ABL1-BCR", "BCR-ABL1", "PML-PARA") & Drug_Gene %in% c("CRISPR_ABL1"))
+crispr_signif_fus_filt <- filter(crispr_signif_fus, FusionPair %in% c("ABL1-BCR", "BCR-ABL1", "PML-PARA"))
+
+crispr_fus_boxplot <- ggplot(data = crispr_fus_filt) +
+  facet_grid(FusionPair ~ Drug_Gene) +
+  scale_color_manual(name = "Fusion Status", values = c("Yes" = "darkorchid4", "No" = "thistle")) +
+  geom_jitter(aes(x = Fusion_Status, y = Score, color = Fusion_Status), width = 0.2, alpha = 0.5, size = 0.6) +
+  geom_boxplot(aes(x = Fusion_Status, y = Score), fill = "transparent", outlier.shape = NA, lwd = 0.3) +
+  # coord_cartesian(ylim = c(0, 1.2)) +
+  # scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
+  geom_text(data = crispr_signif_fus_filt, aes(x = 1.5, y = 1, label = p.signif)) +
+  theme(legend.position = "top", legend.direction = "horizontal", axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
+  guides(color = guide_legend(override.aes = list(size = 3))) +
+  labs(y = "Score", x = "Fusion Status")
+crispr_fus_boxplot
+ggsave("./plots/manuscript/crispr_fus_boxplots.png", crispr_fus_boxplot, width = 8, height = 5, units = "in")
+
+# CCLE
+ccle_fus_filt <- filter(ccle_fus, FusionPair %in% c("ABL1-BCR", "BCR-ABL1") & Drug %in% g2p_drugs)
+ccle_fus_filt$Drug_f <- factor(ccle_fus_filt$Drug, levels = intersect(g2p_drug_order, unique(ccle_fus$Drug)))
+ccle_signif_fus_filt <- filter(ccle_signif_fus, Drug %in% g2p_drugs)
+ccle_signif_fus_filt$Drug_f <- factor(ccle_signif_fus_filt$Drug, levels = intersect(g2p_drug_order, unique(ccle_signif_fus$Drug)))
+
+ccle_fus_boxplot <- ggplot(data = ccle_fus_filt) +
+  facet_grid(FusionPair ~ Drug_f) +
+  scale_color_manual(name = "Fusion Status", values = c("Yes" = "springgreen4", "No" = "palegreen3")) +
+  geom_jitter(aes(x = Fusion_Status, y = Score, color = Fusion_Status), width = 0.2, alpha = 0.5, size = 0.6) +
+  geom_boxplot(aes(x = Fusion_Status, y = Score), fill = "transparent", outlier.shape = NA, lwd = 0.3) +
+  coord_cartesian(ylim = c(0, 1.2)) +
+  scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
+  geom_text(data = ccle_signif_fus_filt, aes(x = 1.5, y = 1.1, label = p.signif)) +
+  theme(legend.position = "top", legend.direction = "horizontal", axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
+  guides(color = guide_legend(override.aes = list(size = 3))) +
+  labs(y = "AUC", x = "Fusion Status")
+ccle_fus_boxplot
+ggsave("./plots/manuscript/ccle_fus_boxplots.png", ccle_fus_boxplot, width = 8, height = 5, units = "in")
+
+# CTRP
+ctrp_fus_filt <- filter(ctrp_fus, FusionPair %in% c("ABL1-BCR", "BCR-ABL1") & Drug %in% g2p_drugs)
+ctrp_fus_filt$Drug_f <- factor(ctrp_fus_filt$Drug, levels = intersect(g2p_drug_order, unique(ctrp_fus$Drug)))
+ctrp_signif_fus_filt <- filter(ctrp_signif_fus, FusionPair %in% c("ABL1-BCR", "BCR-ABL1") & Drug %in% g2p_drugs)
+ctrp_signif_fus_filt$Drug_f <- factor(ctrp_signif_fus_filt$Drug, levels = intersect(g2p_drug_order, unique(ctrp_signif_fus$Drug)))
+
+ctrp_fus_boxplot <- ggplot(data = ctrp_fus_filt) +
+  facet_grid(FusionPair ~ Drug_f) +
+  scale_color_manual(name = "Fusion Status", values = c("Yes" = "steelblue4", "No" = "slategray3")) +
+  geom_jitter(aes(x = Fusion_Status, y = Score, color = Fusion_Status), width = 0.2, alpha = 0.5, size = 0.6) +
+  geom_boxplot(aes(x = Fusion_Status, y = Score), fill = "transparent", outlier.shape = NA, lwd = 0.3) +
+  coord_cartesian(ylim = c(0, 1.2)) +
+  scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
+  geom_text(data = ctrp_signif_fus_filt, aes(x = 1.5, y = 1.1, label = p.signif)) +
+  theme(legend.position = "top", legend.direction = "horizontal", axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
+  guides(color = guide_legend(override.aes = list(size = 3))) +
+  labs(y = "AUC", x = "Fusion Status")
+ctrp_fus_boxplot
+ggsave("./plots/manuscript/ctrp_fus_boxplots.png", ctrp_fus_boxplot, width = 19, height = 5, units = "in")
+
+# GDSC
+gdsc_fus_filt <- filter(gdsc_fus, FusionPair %in% c("ABL1-BCR", "BCR-ABL1") & Drug %in% g2p_drugs)
+gdsc_fus_filt$Drug_f <- factor(gdsc_fus_filt$Drug, levels = intersect(g2p_drug_order, unique(gdsc_fus$Drug)))
+gdsc_signif_fus_filt <- filter(gdsc_signif_fus, FusionPair %in% c("ABL1-BCR", "BCR-ABL1") & Drug %in% g2p_drugs)
+gdsc_signif_fus_filt$Drug_f <- factor(gdsc_signif_fus_filt$Drug, levels = intersect(g2p_drug_order, unique(gdsc_signif_fus$Drug)))
+
+gdsc_fus_boxplot <- ggplot(data = gdsc_fus_filt) +
+  facet_grid(FusionPair ~ Drug_f) +
+  scale_color_manual(name = "Fusion Status", values = c("Yes" = "turquoise4", "No" = "paleturquoise3")) +
+  geom_jitter(aes(x = Fusion_Status, y = Score, color = Fusion_Status), width = 0.2, alpha = 0.5, size = 0.6) +
+  geom_boxplot(aes(x = Fusion_Status, y = Score), fill = "transparent", outlier.shape = NA, lwd = 0.3) +
+  coord_cartesian(ylim = c(0, 1.2)) +
+  scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
+  geom_text(data = gdsc_signif_fus_filt, aes(x = 1.5, y = 1.1, label = p.signif)) +
+  theme(legend.position = "top", legend.direction = "horizontal", axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
+  guides(color = guide_legend(override.aes = list(size = 3))) +
+  labs(y = "AUC", x = "Fusion Status")
+gdsc_fus_boxplot
+ggsave("./plots/manuscript/gdsc_fus_boxplots.png", gdsc_fus_boxplot, width = 12, height = 5, units = "in")
+```
+
+### Lineage DGL heatmaps
+
+```{r lineage_mut_heatmap_functions}
+MakeWilcoxonLineageHeatmap <- function(df, database, lineage) {
+  plot_colors <- c("CCLE" = "darkgreen", "CTRP" = "steelblue4", "GDSC" = "turquoise4")
+  plot_breaks <- list("CCLE" = seq(0, 5, by = 1), "CTRP" = seq(0, 12, by = 2), "GDSC" = seq(0, 8, by = 2))
+
+  df <- filter(df, disease == lineage)
+
+  ht <- MakeWilcoxonHeatmap(signif_df = df, feature = "mutation", legend_title = paste0(database, "\n", lineage, "\n-log10(p-value)"), legend_breaks = plot_breaks[[database]], row_names = TRUE, color = plot_colors[[database]], col_title = "Drugs", row_title_txt = "Genes")
+
+  return(ht)
+}
+
+SaveWilcoxonLineageHeatmap <- function(database, ht_list, lineage) {
+  ht <- ht_list[[lineage]]
+  out_height <- floor((nrow(ht@matrix) + 1) / 2) + 2
+  out_width <- ncol(ht@matrix) / 2 + 1
+
+  png(filename = paste0("./plots/manuscript/lineage_heatmaps/", tolower(database), "_", lineage, "_mut_heatmap.png"), width = out_width, height = out_height, units = "in", res = 500)
+  draw(ht, heatmap_legend_side = "top")
+  invisible(dev.off())
+}
+```
+
+```{r lineage_mut_heatmaps, eval=FALSE, message=FALSE}
+ccle_hts <- lapply(unique(ccle_signif_dgl$disease), MakeWilcoxonLineageHeatmap, df = ccle_signif_dgl, database = "CCLE")
+names(ccle_hts) <- unique(ccle_signif_dgl$disease)
+lapply(unique(ccle_signif_dgl$disease), SaveWilcoxonLineageHeatmap, ht_list = ccle_hts, database = "CCLE")
+
+ctrp_hts <- lapply(unique(ctrp_signif_dgl$disease), MakeWilcoxonLineageHeatmap, df = ctrp_signif_dgl, database = "CTRP")
+names(ctrp_hts) <- unique(ctrp_signif_dgl$disease)
+lapply(unique(ctrp_signif_dgl$disease), SaveWilcoxonLineageHeatmap, ht_list = ctrp_hts, database = "CTRP")
+
+gdsc_hts <- lapply(unique(gdsc_signif_dgl$disease), MakeWilcoxonLineageHeatmap, df = gdsc_signif_dgl, database = "GDSC")
+names(gdsc_hts) <- unique(gdsc_signif_dgl$disease)
+lapply(unique(gdsc_signif_dgl$disease), SaveWilcoxonLineageHeatmap, ht_list = gdsc_hts, database = "GDSC")
+```
+
 ## Mut: Sen vs. Res tests

### 2020-01-10 19Q2.Rmd
update manuscript figures with restricted heatmaps, add prelim KS test res to Rmd

@@
 
-ccle_signif_dgl %>% count(InG2P)
-filter(ccle_signif_dgl, InG2P == "Yes" & p < 0.05) %>% select(Drug, Gene, disease, p.short, Direction_Heatmap)
-ctrp_signif_dgl %>% count(InG2P)
-filter(ctrp_signif_dgl, InG2P == "Yes" & p < 0.05) %>% select(Drug, Gene, disease, p.short, Direction_Heatmap)
-gdsc_signif_dgl %>% count(InG2P)
-filter(gdsc_signif_dgl, InG2P == "Yes" & p < 0.05) %>% select(Drug, Gene, disease, p.short, Direction_Heatmap)
+# ccle_signif_dgl %>% count(InG2P)
+# filter(ccle_signif_dgl, InG2P == "Yes" & p < 0.05) %>% select(Drug, Gene, disease, p.short, Direction_Heatmap)
+# ctrp_signif_dgl %>% count(InG2P)
+# filter(ctrp_signif_dgl, InG2P == "Yes" & p < 0.05) %>% select(Drug, Gene, disease, p.short, Direction_Heatmap)
+# gdsc_signif_dgl %>% count(InG2P)
+# filter(gdsc_signif_dgl, InG2P == "Yes" & p < 0.05) %>% select(Drug, Gene, disease, p.short, Direction_Heatmap)
+# library(spatstat)
 ```
@@
 gdsc_signif_prot_lin <- merge(gdsc_signif_prot_lin, unique(select(g2p_prot, Drug, Gene_Protein_Change, Drug_Gene_Protein_Change_Lineage, Direction_Curated)), by = c("Drug_Gene_Protein_Change_Lineage", "Gene_Protein_Change", "Drug"), all.x = TRUE)
-
-# ccle_signif_prot_lin %>% count(InG2P)
-# filter(ccle_signif_prot_lin, InG2P == "Yes" & p < 0.05) %>% select(Drug, Gene_Protein_Change, disease, p.short, Direction_Curated)
-# ctrp_signif_prot_lin %>% count(InG2P)
-# filter(ctrp_signif_prot_lin, InG2P == "Yes" & p < 0.05) %>% select(Drug, Gene_Protein_Change, disease, p.short, Direction_Curated)
-# gdsc_signif_prot_lin %>% count(InG2P)
-# filter(gdsc_signif_prot_lin, InG2P == "Yes" & p < 0.05) %>% select(Drug, Gene_Protein_Change, disease, p.short, Direction_Curated)
 ```
@@
 
-## Data summaries
+## KS tests
+
+**1/10/20: Restrict datasets to heatmap drug-genes and run KS tests.**
+```{r}
+ks.test(filter(ccle_signif_g2p_dg, InG2P == "Yes")$p, filter(ccle_signif_g2p_dg, InG2P == "No")$p)
+ks.test(filter(ctrp_signif_g2p_dg, InG2P == "Yes")$p, filter(ctrp_signif_g2p_dg, InG2P == "No")$p)
+ks.test(filter(gdsc_signif_g2p_dg, InG2P == "Yes")$p, filter(gdsc_signif_g2p_dg, InG2P == "No")$p)
+
+ks.test(filter(ccle_signif_dgl, InG2P == "Yes")$p, filter(ccle_signif_dgl, InG2P == "No")$p)
+ks.test(filter(ctrp_signif_dgl, InG2P == "Yes")$p, filter(ctrp_signif_dgl, InG2P == "No")$p)
+ks.test(filter(gdsc_signif_dgl, InG2P == "Yes")$p, filter(gdsc_signif_dgl, InG2P == "No")$p)
+
+ks.test(filter(ccle_signif_prot, InG2P == "Yes")$p, filter(ccle_signif_prot, InG2P == "No")$p)
+ks.test(filter(ctrp_signif_prot, InG2P == "Yes")$p, filter(ctrp_signif_prot, InG2P == "No")$p)
+ks.test(filter(gdsc_signif_prot, InG2P == "Yes")$p, filter(gdsc_signif_prot, InG2P == "No")$p)
+
+ks.test(filter(ccle_signif_prot_lin, InG2P == "Yes")$p, filter(ccle_signif_prot_lin, InG2P == "No")$p)
+ks.test(filter(ctrp_signif_prot_lin, InG2P == "Yes")$p, filter(ctrp_signif_prot_lin, InG2P == "No")$p)
+ks.test(filter(gdsc_signif_prot_lin, InG2P == "Yes")$p, filter(gdsc_signif_prot_lin, InG2P == "No")$p)
+
+ks.test(filter(cn_cor, Dataset == "CCLE" & InG2P == "Yes")$CN_r, filter(cn_cor, Dataset == "CCLE" & InG2P == "No")$CN_p)
+ks.test(filter(cn_cor, Dataset == "CTRP" & InG2P == "Yes")$CN_r, filter(cn_cor, Dataset == "CTRP" & InG2P == "No")$CN_p)
+ks.test(filter(cn_cor, Dataset == "GDSC" & InG2P == "Yes")$CN_r, filter(cn_cor, Dataset == "GDSC" & InG2P == "No")$CN_p)
+
+ks.test(filter(ge_cor, Dataset == "CCLE" & InG2P == "Yes")$GE_p, filter(ge_cor, Dataset == "CCLE" & InG2P == "No")$GE_p)
+ks.test(filter(ge_cor, Dataset == "CTRP" & InG2P == "Yes")$GE_p, filter(ge_cor, Dataset == "CTRP" & InG2P == "No")$GE_p)
+ks.test(filter(ge_cor, Dataset == "GDSC" & InG2P == "Yes")$GE_p, filter(ge_cor, Dataset == "GDSC" & InG2P == "No")$GE_p)
+
+ks.test(filter(cn_cor_lin, Dataset == "CCLE" & InG2P == "Yes")$CN_r, filter(cn_cor_lin, Dataset == "CCLE" & InG2P == "No")$CN_p)
+ks.test(filter(cn_cor_lin, Dataset == "CTRP" & InG2P == "Yes")$CN_r, filter(cn_cor_lin, Dataset == "CTRP" & InG2P == "No")$CN_p)
+ks.test(filter(cn_cor_lin, Dataset == "GDSC" & InG2P == "Yes")$CN_r, filter(cn_cor_lin, Dataset == "GDSC" & InG2P == "No")$CN_p)
+
+ks.test(filter(ge_cor_lin, Dataset == "CCLE" & InG2P == "Yes")$GE_p, filter(ge_cor_lin, Dataset == "CCLE" & InG2P == "No")$GE_p)
+ks.test(filter(ge_cor_lin, Dataset == "CTRP" & InG2P == "Yes")$GE_p, filter(ge_cor_lin, Dataset == "CTRP" & InG2P == "No")$GE_p)
+ks.test(filter(ge_cor_lin, Dataset == "GDSC" & InG2P == "Yes")$GE_p, filter(ge_cor_lin, Dataset == "GDSC" & InG2P == "No")$GE_p)
+```
+
+## Data summaries/Supp
 
@@
 
-```{r fig.height=10, fig.width=10}
+```{r fig.height=3, fig.width=3}
 slices <- ccle_disease_n$n
@@
 
+Of the top 10 most cited genes in G2P (Figure 1), 50% were also found in the top 10 most frequently mutated across all 1588 tested cell lines
 ```{r supp_stats, eval=FALSE}
-maf_g2p_summ_gene <- maf_g2p %>% group_by(Gene) %>% count(Mutation) %>% filter (Mutation == 1) %>% merge(unique(select(maf_g2p, DepMap_ID, Gene)) %>% count(Gene), by = "Gene", suffixes = c("_mut", "_cell_lines"), all = TRUE)
-maf_g2p_summ_gene$PercCellLinesMutated <- maf_g2p_summ_gene$n_mut/maf_g2p_summ_gene$n_cell_lines * 100
-
-maf_g2p_summ <- maf_g2p %>% group_by(disease) %>% count(Mutation) %>% filter (Mutation == 1) %>% merge(unique(select(maf_g2p, DepMap_ID, disease)) %>% count(disease), by = "disease", suffixes = c("_mut", "_cell_lines"), all = TRUE)
-maf_g2p_summ$MutPerCCL <- maf_g2p_summ$n_mut/maf_g2p_summ$n_cell_lines
-
-sum(maf_g2p_summ$n_cell_lines)
-777/1588
-sum(maf_g2p_summ$n_mut[!is.na(maf_g2p_summ$n_mut)])
-2067/3151
+ccls <- union(union(unique(ccle$DepMap_ID), unique(ctrp$DepMap_ID)), unique(gdsc$DepMap_ID))
+
+maf_g2p_summ_gene <- filter(maf_df, DepMap_ID %in% ccls & Gene %in% unique(g2p_mut$Gene)) %>% group_by(Gene) %>% count(Mutation) %>% filter (Mutation == 1) %>% mutate(percent = n / length(ccls) * 100)
+g2p_summ_gene <- g2p_mut %>% count(Gene) %>% mutate(percent = n / nrow(g2p_mut) * 100)
+
+maf_g2p_summ_lin <- merge(filter(maf_df, DepMap_ID %in% ccls & Gene %in% unique(g2p_mut$Gene)), ccl_meta, by = "DepMap_ID", all.x = TRUE) %>% group_by(disease) %>% count(Mutation) %>% filter (Mutation == 1)
+maf_g2p_summ_lin$percent <- with(maf_g2p_summ_lin, n / sum(n) * 100)
+
+g2p_summ_lin <- g2p %>% count(disease) %>% mutate(percent = n / nrow(g2p) * 100)
+
+ccl_summ_lin <- filter(ccl_meta, DepMap_ID %in% ccls) %>% count(disease)
+ccl_summ_lin$percent <- with(ccl_summ_lin, n / sum(n) * 100)
 ```
@@
 
-```{r}
+```{r, eval=FALSE}
 ccle_prot$disease_g2p <- ifelse(ccle_prot$disease %in% g2p_diseases, ccle_prot$disease, "other")
@@
 
-```{r}
+```{r, eval=FALSE}
 ccle_mut_lin <- filter(ccle_signif_dgl, InG2P == "Yes")

### 2020-01-12 19Q2.Rmd
reconfigured KS test -- no tests were signif, sent to Dan for input

@@
 --------------------------------------------------------------------------------
-
-## KS tests
-
-**1/10/20: Restrict datasets to heatmap drug-genes and run KS tests.**
-```{r}
-ks.test(filter(ccle_signif_g2p_dg, InG2P == "Yes")$p, filter(ccle_signif_g2p_dg, InG2P == "No")$p)
-ks.test(filter(ctrp_signif_g2p_dg, InG2P == "Yes")$p, filter(ctrp_signif_g2p_dg, InG2P == "No")$p)
-ks.test(filter(gdsc_signif_g2p_dg, InG2P == "Yes")$p, filter(gdsc_signif_g2p_dg, InG2P == "No")$p)
-
-ks.test(filter(ccle_signif_dgl, InG2P == "Yes")$p, filter(ccle_signif_dgl, InG2P == "No")$p)
-ks.test(filter(ctrp_signif_dgl, InG2P == "Yes")$p, filter(ctrp_signif_dgl, InG2P == "No")$p)
-ks.test(filter(gdsc_signif_dgl, InG2P == "Yes")$p, filter(gdsc_signif_dgl, InG2P == "No")$p)
-
-ks.test(filter(ccle_signif_prot, InG2P == "Yes")$p, filter(ccle_signif_prot, InG2P == "No")$p)
-ks.test(filter(ctrp_signif_prot, InG2P == "Yes")$p, filter(ctrp_signif_prot, InG2P == "No")$p)
-ks.test(filter(gdsc_signif_prot, InG2P == "Yes")$p, filter(gdsc_signif_prot, InG2P == "No")$p)
-
-ks.test(filter(ccle_signif_prot_lin, InG2P == "Yes")$p, filter(ccle_signif_prot_lin, InG2P == "No")$p)
-ks.test(filter(ctrp_signif_prot_lin, InG2P == "Yes")$p, filter(ctrp_signif_prot_lin, InG2P == "No")$p)
-ks.test(filter(gdsc_signif_prot_lin, InG2P == "Yes")$p, filter(gdsc_signif_prot_lin, InG2P == "No")$p)
-
-ks.test(filter(cn_cor, Dataset == "CCLE" & InG2P == "Yes")$CN_r, filter(cn_cor, Dataset == "CCLE" & InG2P == "No")$CN_p)
-ks.test(filter(cn_cor, Dataset == "CTRP" & InG2P == "Yes")$CN_r, filter(cn_cor, Dataset == "CTRP" & InG2P == "No")$CN_p)
-ks.test(filter(cn_cor, Dataset == "GDSC" & InG2P == "Yes")$CN_r, filter(cn_cor, Dataset == "GDSC" & InG2P == "No")$CN_p)
-
-ks.test(filter(ge_cor, Dataset == "CCLE" & InG2P == "Yes")$GE_p, filter(ge_cor, Dataset == "CCLE" & InG2P == "No")$GE_p)
-ks.test(filter(ge_cor, Dataset == "CTRP" & InG2P == "Yes")$GE_p, filter(ge_cor, Dataset == "CTRP" & InG2P == "No")$GE_p)
-ks.test(filter(ge_cor, Dataset == "GDSC" & InG2P == "Yes")$GE_p, filter(ge_cor, Dataset == "GDSC" & InG2P == "No")$GE_p)
-
-ks.test(filter(cn_cor_lin, Dataset == "CCLE" & InG2P == "Yes")$CN_r, filter(cn_cor_lin, Dataset == "CCLE" & InG2P == "No")$CN_p)
-ks.test(filter(cn_cor_lin, Dataset == "CTRP" & InG2P == "Yes")$CN_r, filter(cn_cor_lin, Dataset == "CTRP" & InG2P == "No")$CN_p)
-ks.test(filter(cn_cor_lin, Dataset == "GDSC" & InG2P == "Yes")$CN_r, filter(cn_cor_lin, Dataset == "GDSC" & InG2P == "No")$CN_p)
-
-ks.test(filter(ge_cor_lin, Dataset == "CCLE" & InG2P == "Yes")$GE_p, filter(ge_cor_lin, Dataset == "CCLE" & InG2P == "No")$GE_p)
-ks.test(filter(ge_cor_lin, Dataset == "CTRP" & InG2P == "Yes")$GE_p, filter(ge_cor_lin, Dataset == "CTRP" & InG2P == "No")$GE_p)
-ks.test(filter(ge_cor_lin, Dataset == "GDSC" & InG2P == "Yes")$GE_p, filter(ge_cor_lin, Dataset == "GDSC" & InG2P == "No")$GE_p)
-```
 
@@
 
-```{r}
-crispr_g2p_count <- filter(crispr_signif_g2p_g, Gene %in% unique(g2p_mut$Gene), InG2P == "Yes")
-ccle_g2p_count <- filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene), InG2P == "Yes")
-ctrp_g2p_count <- filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene), InG2P == "Yes")
-gdsc_g2p_count <- filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene), InG2P == "Yes")
-```
-
-```{r mutation_figure, eval=FALSE}
+```{r mut_ks_tests}
 mut_genes <- union(union(filter(ccle_signif_g2p_dg, InG2P == "Yes")$Gene, filter(ctrp_signif_g2p_dg, InG2P == "Yes")$Gene), filter(gdsc_signif_g2p_dg, InG2P == "Yes")$Gene)
@@
 
-ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Drug %in% mut_drugs & Gene %in% mut_genes), feature = "mutation", legend_title = "CCLE -log10(p-value)", legend_breaks = seq(0, 12, by = 3), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Genes", radius = 0.023)
-ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Drug %in% mut_drugs & Gene %in% mut_genes), feature = "mutation", legend_title = "CTRP -log10(p-value)", legend_breaks = seq(0, 18, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.008)
-ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Drug %in% mut_drugs & Gene %in% mut_genes), feature = "mutation", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes", radius = 0.011)
+ccle_mut_ht_dat <- filter(ccle_signif_g2p_dg, Drug %in% mut_drugs & Gene %in% mut_genes)
+ks.test(filter(ccle_mut_ht_dat, InG2P == "Yes")$p, filter(ccle_mut_ht_dat, InG2P == "No")$p)
+
+ctrp_mut_ht_dat <- filter(ctrp_signif_g2p_dg, Drug %in% mut_drugs & Gene %in% mut_genes)
+ks.test(filter(ctrp_mut_ht_dat, InG2P == "Yes")$p, filter(ctrp_mut_ht_dat, InG2P == "No")$p)
+
+gdsc_mut_ht_dat <- filter(gdsc_signif_g2p_dg, Drug %in% mut_drugs & Gene %in% mut_genes)
+ks.test(filter(gdsc_mut_ht_dat, InG2P == "Yes")$p, filter(gdsc_mut_ht_dat, InG2P == "No")$p)
+```
+
+```{r mutation_figure, eval=FALSE}
+ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = ccle_mut_ht_dat, feature = "mutation", legend_title = "CCLE -log10(p-value)", legend_breaks = seq(0, 12, by = 3), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Genes", radius = 0.023)
+ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = ctrp_mut_ht_dat, feature = "mutation", legend_title = "CTRP -log10(p-value)", legend_breaks = seq(0, 18, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.008)
+ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = , feature = "mutation", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes", radius = 0.011)
 ht_mut_list <- ht_ccle2 + ht_ctrp2 + ht_gdsc2
@@
 
-```{r, eval=FALSE}
+```{r prot_ks_tests}
 ccle_prot$disease_g2p <- ifelse(ccle_prot$disease %in% g2p_diseases, ccle_prot$disease, "other")
@@
 
-ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_prot_4plot, Drug %in% prot_drugs), feature = "protein changes", legend_title = "CCLE -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.021)
-ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_prot_4plot, Drug %in% prot_drugs), feature = "protein changes", legend_title = "CTRP -log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.012)
-ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_prot_4plot, Drug %in% prot_drugs), feature = "protein changes", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 3, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.0125)
+ccle_prot_ht_data <- filter(ccle_signif_prot_4plot, Drug %in% prot_drugs)
+ks.test(filter(ccle_prot_ht_data, InG2P == "Yes")$p, filter(ccle_prot_ht_data, InG2P == "No")$p)
+
+ctrp_prot_ht_data <- filter(ctrp_signif_prot_4plot, Drug %in% prot_drugs)
+ks.test(filter(ctrp_prot_ht_data, InG2P == "Yes")$p, filter(ctrp_prot_ht_data, InG2P == "No")$p)
+
+gdsc_prot_ht_data <- filter(gdsc_signif_prot_4plot, Drug %in% prot_drugs)
+ks.test(filter(gdsc_prot_ht_data, InG2P == "Yes")$p, filter(gdsc_prot_ht_data, InG2P == "No")$p)
+```
+
+```{r, eval=FALSE}
+ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = , feature = "protein changes", legend_title = "CCLE -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.021)
+ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = , feature = "protein changes", legend_title = "CTRP -log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.012)
+ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = , feature = "protein changes", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 3, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.0125)
 ht_prot_list <- ht_ccle2 + ht_ctrp2 + ht_gdsc2
@@
 
+```{r cn_ge_ks_tests}
+cn_genes <- unique(filter(cn_cor, Dataset != "CRISPR" & InG2P == "Yes")$Gene)
+cn_drugs <- unique(filter(cn_cor, Dataset != "CRISPR" & InG2P == "Yes")$Drug)
+
+ccle_cn_ht_data <- filter(cn_cor, Dataset == "CCLE" & Drug %in% cn_drugs & Gene %in% cn_genes)
+ks.test(filter(ccle_cn_ht_data, InG2P == "Yes")$CN_p, filter(ccle_cn_ht_data, InG2P == "No")$CN_p)
+ctrp_cn_ht_data <- filter(cn_cor, Dataset == "CTRP" & Drug %in% cn_drugs & Gene %in% cn_genes)
+ks.test(filter(ctrp_cn_ht_data, InG2P == "Yes")$CN_p, filter(ctrp_cn_ht_data, InG2P == "No")$CN_p)
+gdsc_cn_ht_data <- filter(cn_cor, Dataset == "GDSC" & Drug %in% cn_drugs & Gene %in% cn_genes)
+ks.test(filter(gdsc_cn_ht_data, InG2P == "Yes")$CN_p, filter(gdsc_cn_ht_data, InG2P == "No")$CN_p)
+
+ge_genes <- unique(filter(ge_cor, Dataset != "CRISPR" & InG2P == "Yes")$Gene)
+ge_drugs <- unique(filter(ge_cor, Dataset != "CRISPR" & InG2P == "Yes")$Drug)
+
+ccle_ge_ht_data <- filter(ge_cor, Dataset == "CCLE" & Drug %in% ge_drugs & Gene %in% ge_genes)
+ks.test(filter(ccle_ge_ht_data, InG2P == "Yes")$GE_p, filter(ccle_ge_ht_data, InG2P == "No")$GE_p)
+ctrp_ge_ht_data <- filter(ge_cor, Dataset == "CTRP" & Drug %in% ge_drugs & Gene %in% ge_genes)
+ks.test(filter(ctrp_ge_ht_data, InG2P == "Yes")$GE_p, filter(ctrp_ge_ht_data, InG2P == "No")$GE_p)
+gdsc_ge_ht_data <- filter(ge_cor, Dataset == "GDSC" & Drug %in% ge_drugs & Gene %in% ge_genes)
+ks.test(filter(gdsc_ge_ht_data, InG2P == "Yes")$GE_p, filter(gdsc_ge_ht_data, InG2P == "No")$GE_p)
+```
+
 ```{r CN_GE_fig, eval=FALSE, fig.height=10, fig.width=15}
 # Copy number
-cn_genes <- unique(filter(cn_cor, Dataset != "CRISPR" & InG2P == "Yes")$Gene)
-cn_drugs <- unique(filter(cn_cor, Dataset != "CRISPR" & InG2P == "Yes")$Drug)
 
@@
 # Gene expression
-
-ge_genes <- unique(filter(ge_cor, Dataset != "CRISPR" & InG2P == "Yes")$Gene)
-ge_drugs <- unique(filter(ge_cor, Dataset != "CRISPR" & InG2P == "Yes")$Drug)
 
@@
 
+```{r pancan_ks_res}
+pancan_ks_results <- data.frame("Dataset" = c(rep(c("CCLE", "CTRP", "GDSC"), 4)),
+           "Data type" = c(rep("Mutation", 3), rep("Protein change", 3), rep("Copy number", 3), rep("Gene expression", 3)),
+  "p.value" = c(ks.test(filter(ccle_mut_ht_dat, InG2P == "Yes")$p, filter(ccle_mut_ht_dat, InG2P == "No")$p)$p.value,
+  ks.test(filter(ctrp_mut_ht_dat, InG2P == "Yes")$p, filter(ctrp_mut_ht_dat, InG2P == "No")$p)$p.value,
+  ks.test(filter(gdsc_mut_ht_dat, InG2P == "Yes")$p, filter(gdsc_mut_ht_dat, InG2P == "No")$p)$p.value,
+  ks.test(filter(ccle_prot_ht_data, InG2P == "Yes")$p, filter(ccle_prot_ht_data, InG2P == "No")$p)$p.value,
+  ks.test(filter(ctrp_prot_ht_data, InG2P == "Yes")$p, filter(ctrp_prot_ht_data, InG2P == "No")$p)$p.value,
+  ks.test(filter(gdsc_prot_ht_data, InG2P == "Yes")$p, filter(gdsc_prot_ht_data, InG2P == "No")$p)$p.value,
+  ks.test(filter(ccle_cn_ht_data, InG2P == "Yes")$CN_p, filter(ccle_cn_ht_data, InG2P == "No")$CN_p)$p.value,
+  ks.test(filter(ctrp_cn_ht_data, InG2P == "Yes")$CN_p, filter(ctrp_cn_ht_data, InG2P == "No")$CN_p)$p.value,
+  ks.test(filter(gdsc_cn_ht_data, InG2P == "Yes")$CN_p, filter(gdsc_cn_ht_data, InG2P == "No")$CN_p)$p.value,
+  ks.test(filter(ccle_ge_ht_data, InG2P == "Yes")$GE_p, filter(ccle_ge_ht_data, InG2P == "No")$GE_p)$p.value,
+  ks.test(filter(ctrp_ge_ht_data, InG2P == "Yes")$GE_p, filter(ctrp_ge_ht_data, InG2P == "No")$GE_p)$p.value,
+  ks.test(filter(gdsc_ge_ht_data, InG2P == "Yes")$GE_p, filter(gdsc_ge_ht_data, InG2P == "No")$GE_p)$p.value))
+```
+
 ## Lineages
 
-```{r}
-g2p_disease_colors
-
-gdsc_signif_prot_summ <- filter(gdsc_signif_prot, InG2P == "Yes") 
-ctrp_prot_filt <- filter(ctrp_prot, Drug_Gene_Protein_Change %in% filter(ctrp_signif_prot_summ, p < 0.05)$Drug_Gene_Protein_Change)
-
-# ccle_prot_annot <- select(filter(ccle_prot, Drug_Gene %in% ccle_mut_lin_filt$Drug_Gene & Change_Status == "Yes"), Drug_Gene, Protein_Change, DepMap_ID) 
-# test <- merge(ccle_mut_lin_filt, ccle_prot_annot, by = c("DepMap_ID", "Drug_Gene"), all.x = TRUE)
+```{r lineages_ks_tests, warning=FALSE}
+ks.test(filter(ccle_signif_dgl, InG2P == "Yes")$p, filter(ccle_signif_dgl, InG2P == "No")$p)$p.value
+ks.test(filter(ctrp_signif_dgl, InG2P == "Yes")$p, filter(ctrp_signif_dgl, InG2P == "No")$p)$p.value
+ks.test(filter(gdsc_signif_dgl, InG2P == "Yes")$p, filter(gdsc_signif_dgl, InG2P == "No")$p)$p.value
+
+ks.test(filter(ccle_signif_prot_lin, InG2P == "Yes")$p, filter(ccle_signif_prot_lin, InG2P == "No")$p)$p.value
+ks.test(filter(ctrp_signif_prot_lin, InG2P == "Yes")$p, filter(ctrp_signif_prot_lin, InG2P == "No")$p)$p.value
+ks.test(filter(gdsc_signif_prot_lin, InG2P == "Yes")$p, filter(gdsc_signif_prot_lin, InG2P == "No")$p)$p.value
+
+ks.test(filter(cn_cor_lin, Dataset == "CCLE" & InG2P == "Yes")$CN_p, filter(cn_cor_lin, Dataset == "CCLE" & InG2P == "No")$CN_p)$p.value
+ks.test(filter(cn_cor_lin, Dataset == "CTRP" & InG2P == "Yes")$CN_p, filter(cn_cor_lin, Dataset == "CTRP" & InG2P == "No")$CN_p)$p.value
+ks.test(filter(cn_cor_lin, Dataset == "GDSC" & InG2P == "Yes")$CN_p, filter(cn_cor_lin, Dataset == "GDSC" & InG2P == "No")$CN_p)$p.value
+
+ks.test(filter(ge_cor_lin, Dataset == "CCLE" & InG2P == "Yes")$GE_p, filter(ge_cor_lin, Dataset == "CCLE" & InG2P == "No")$GE_p)$p.value
+ks.test(filter(ge_cor_lin, Dataset == "CTRP" & InG2P == "Yes")$GE_p, filter(ge_cor_lin, Dataset == "CTRP" & InG2P == "No")$GE_p)$p.value
+ks.test(filter(ge_cor_lin, Dataset == "GDSC" & InG2P == "Yes")$GE_p, filter(ge_cor_lin, Dataset == "GDSC" & InG2P == "No")$GE_p)$p.value
+
+lineage_ks_results <- data.frame("Dataset" = c(rep(c("CCLE", "CTRP", "GDSC"), 4)),
+           "Data type" = c(rep("Mutation", 3), rep("Protein change", 3), rep("Copy number", 3), rep("Gene expression", 3)),
+  "p.value" = c(ks.test(filter(ccle_signif_dgl, InG2P == "Yes")$p, filter(ccle_signif_dgl, InG2P == "No")$p)$p.value,
+  ks.test(filter(ctrp_signif_dgl, InG2P == "Yes")$p, filter(ctrp_signif_dgl, InG2P == "No")$p)$p.value,
+  ks.test(filter(gdsc_signif_dgl, InG2P == "Yes")$p, filter(gdsc_signif_dgl, InG2P == "No")$p)$p.value,
+  ks.test(filter(ccle_signif_prot_lin, InG2P == "Yes")$p, filter(ccle_signif_prot_lin, InG2P == "No")$p)$p.value,
+  ks.test(filter(ctrp_signif_prot_lin, InG2P == "Yes")$p, filter(ctrp_signif_prot_lin, InG2P == "No")$p)$p.value,
+  ks.test(filter(gdsc_signif_prot_lin, InG2P == "Yes")$p, filter(gdsc_signif_prot_lin, InG2P == "No")$p)$p.value,
+  ks.test(filter(cn_cor_lin, Dataset == "CCLE" & InG2P == "Yes")$CN_p, filter(cn_cor_lin, Dataset == "CCLE" & InG2P == "No")$CN_p)$p.value,
+  ks.test(filter(cn_cor_lin, Dataset == "CTRP" & InG2P == "Yes")$CN_p, filter(cn_cor_lin, Dataset == "CTRP" & InG2P == "No")$CN_p)$p.value,
+  ks.test(filter(cn_cor_lin, Dataset == "GDSC" & InG2P == "Yes")$CN_p, filter(cn_cor_lin, Dataset == "GDSC" & InG2P == "No")$CN_p)$p.value,
+  ks.test(filter(ge_cor_lin, Dataset == "CCLE" & InG2P == "Yes")$GE_p, filter(ge_cor_lin, Dataset == "CCLE" & InG2P == "No")$GE_p)$p.value,
+  ks.test(filter(ge_cor_lin, Dataset == "CTRP" & InG2P == "Yes")$GE_p, filter(ge_cor_lin, Dataset == "CTRP" & InG2P == "No")$GE_p)$p.value,
+  ks.test(filter(ge_cor_lin, Dataset == "GDSC" & InG2P == "Yes")$GE_p, filter(ge_cor_lin, Dataset == "GDSC" & InG2P == "No")$GE_p)$p.value))
 ```

### 2020-01-14 19Q2.Rmd

@@
 g2p_dg_genes <- unique(sapply(strsplit(g2p_dgl, "_", fixed = TRUE), function(x) x[2]))
-g2p_lins <- as.character(unique(g2p$group_general_lineage_name[!is.na(g2p$group_general_lineage_name)]))
+g2p_lins <- as.character(unique(g2p$disease[!is.na(g2p$disease)]))
 
@@
       res <- df_filt %>% group_by(Drug, Gene, disease, Drug_Gene_Lin) %>%
-        summarize(GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs", exact = FALSE)$estimate,
-                  GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs", exact = FALSE)$p.value, 
+        summarize(GE_r = cor.test(y = Score, x = TPM, method = "pearson", use = "complete.obs", exact = FALSE)$estimate,
+                  GE_p = cor.test(y = Score, x = TPM, method = "pearson", use = "complete.obs", exact = FALSE)$p.value, 
                   GE_p_log10 = -log10(GE_p))
@@
       res <- df %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(TPM) %>%
-        summarize(GE_r = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs", exact = FALSE)$estimate,
-                  GE_p = cor.test(y = Score, x = TPM, method = "spearman", use = "complete.obs", exact = FALSE)$p.value, 
+        summarize(GE_r = cor.test(y = Score, x = TPM, method = "pearson", use = "complete.obs", exact = FALSE)$estimate,
+                  GE_p = cor.test(y = Score, x = TPM, method = "pearson", use = "complete.obs", exact = FALSE)$p.value, 
                   GE_p_log10 = -log10(GE_p))
@@
       res <- df_filt %>% group_by(Drug, Gene, disease, Drug_Gene_Lin) %>%
-        summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs", exact = FALSE)$estimate,
-                  CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs", exact = FALSE)$p.value,
+        summarize(CN_r = cor.test(y = Score, x = CN, method = "pearson", use = "complete.obs", exact = FALSE)$estimate,
+                  CN_p = cor.test(y = Score, x = CN, method = "pearson", use = "complete.obs", exact = FALSE)$p.value,
                   CN_p_log10 = -log10(CN_p))
@@
       res <- df %>% group_by(Drug, Gene, Drug_Gene) %>% drop_na(CN) %>%
-        summarize(CN_r = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs", exact = FALSE)$estimate,
-                  CN_p = cor.test(y = Score, x = CN, method = "spearman", use = "complete.obs", exact = FALSE)$p.value, 
+        summarize(CN_r = cor.test(y = Score, x = CN, method = "pearson", use = "complete.obs", exact = FALSE)$estimate,
+                  CN_p = cor.test(y = Score, x = CN, method = "pearson", use = "complete.obs", exact = FALSE)$p.value, 
                   CN_p_log10 = -log10(CN_p))
@@
                 column_names_gp = gpar(fontsize = 10),
+                column_names_max_height = unit(2, "in"),
                 show_column_names = FALSE,
@@
 
-```{r mut_ks_tests}
-mut_genes <- union(union(filter(ccle_signif_g2p_dg, InG2P == "Yes")$Gene, filter(ctrp_signif_g2p_dg, InG2P == "Yes")$Gene), filter(gdsc_signif_g2p_dg, InG2P == "Yes")$Gene)
-mut_drugs <- union(union(filter(ccle_signif_g2p_dg, InG2P == "Yes")$Drug, filter(ctrp_signif_g2p_dg, InG2P == "Yes")$Drug), filter(gdsc_signif_g2p_dg, InG2P == "Yes")$Drug)
-
-ccle_mut_ht_dat <- filter(ccle_signif_g2p_dg, Drug %in% mut_drugs & Gene %in% mut_genes)
-ks.test(filter(ccle_mut_ht_dat, InG2P == "Yes")$p, filter(ccle_mut_ht_dat, InG2P == "No")$p)
-
-ctrp_mut_ht_dat <- filter(ctrp_signif_g2p_dg, Drug %in% mut_drugs & Gene %in% mut_genes)
-ks.test(filter(ctrp_mut_ht_dat, InG2P == "Yes")$p, filter(ctrp_mut_ht_dat, InG2P == "No")$p)
-
-gdsc_mut_ht_dat <- filter(gdsc_signif_g2p_dg, Drug %in% mut_drugs & Gene %in% mut_genes)
-ks.test(filter(gdsc_mut_ht_dat, InG2P == "Yes")$p, filter(gdsc_mut_ht_dat, InG2P == "No")$p)
-```
-
 ```{r mutation_figure, eval=FALSE}
@@
 
-```{r prot_ks_tests}
-ccle_prot$disease_g2p <- ifelse(ccle_prot$disease %in% g2p_diseases, ccle_prot$disease, "other")
-ctrp_prot$disease_g2p <- ifelse(ctrp_prot$disease %in% g2p_diseases, ctrp_prot$disease, "other")
-gdsc_prot$disease_g2p <- ifelse(gdsc_prot$disease %in% g2p_diseases, gdsc_prot$disease, "other")
-
-ccle_signif_prot_summ <- filter(ccle_signif_prot, InG2P == "Yes") 
-ctrp_signif_prot_summ <- filter(ctrp_signif_prot, InG2P == "Yes") 
-gdsc_signif_prot_summ <- filter(gdsc_signif_prot, InG2P == "Yes")
-
-prot_drugs <- union(union(ccle_signif_prot_summ$Drug, ctrp_signif_prot_summ$Drug), gdsc_signif_prot_summ$Drug)
-prot_drugs <- prot_drugs[!(prot_drugs %in% c("cabozantinib", "vandetinib"))]
-
-ccle_prot_ht_data <- filter(ccle_signif_prot_4plot, Drug %in% prot_drugs)
-ks.test(filter(ccle_prot_ht_data, InG2P == "Yes")$p, filter(ccle_prot_ht_data, InG2P == "No")$p)
-
-ctrp_prot_ht_data <- filter(ctrp_signif_prot_4plot, Drug %in% prot_drugs)
-ks.test(filter(ctrp_prot_ht_data, InG2P == "Yes")$p, filter(ctrp_prot_ht_data, InG2P == "No")$p)
-
-gdsc_prot_ht_data <- filter(gdsc_signif_prot_4plot, Drug %in% prot_drugs)
-ks.test(filter(gdsc_prot_ht_data, InG2P == "Yes")$p, filter(gdsc_prot_ht_data, InG2P == "No")$p)
-```
-
 ```{r, eval=FALSE}
@@
 
-```{r cn_ge_ks_tests}
-cn_genes <- unique(filter(cn_cor, Dataset != "CRISPR" & InG2P == "Yes")$Gene)
-cn_drugs <- unique(filter(cn_cor, Dataset != "CRISPR" & InG2P == "Yes")$Drug)
-
-ccle_cn_ht_data <- filter(cn_cor, Dataset == "CCLE" & Drug %in% cn_drugs & Gene %in% cn_genes)
-ks.test(filter(ccle_cn_ht_data, InG2P == "Yes")$CN_p, filter(ccle_cn_ht_data, InG2P == "No")$CN_p)
-ctrp_cn_ht_data <- filter(cn_cor, Dataset == "CTRP" & Drug %in% cn_drugs & Gene %in% cn_genes)
-ks.test(filter(ctrp_cn_ht_data, InG2P == "Yes")$CN_p, filter(ctrp_cn_ht_data, InG2P == "No")$CN_p)
-gdsc_cn_ht_data <- filter(cn_cor, Dataset == "GDSC" & Drug %in% cn_drugs & Gene %in% cn_genes)
-ks.test(filter(gdsc_cn_ht_data, InG2P == "Yes")$CN_p, filter(gdsc_cn_ht_data, InG2P == "No")$CN_p)
-
-ge_genes <- unique(filter(ge_cor, Dataset != "CRISPR" & InG2P == "Yes")$Gene)
-ge_drugs <- unique(filter(ge_cor, Dataset != "CRISPR" & InG2P == "Yes")$Drug)
-
-ccle_ge_ht_data <- filter(ge_cor, Dataset == "CCLE" & Drug %in% ge_drugs & Gene %in% ge_genes)
-ks.test(filter(ccle_ge_ht_data, InG2P == "Yes")$GE_p, filter(ccle_ge_ht_data, InG2P == "No")$GE_p)
-ctrp_ge_ht_data <- filter(ge_cor, Dataset == "CTRP" & Drug %in% ge_drugs & Gene %in% ge_genes)
-ks.test(filter(ctrp_ge_ht_data, InG2P == "Yes")$GE_p, filter(ctrp_ge_ht_data, InG2P == "No")$GE_p)
-gdsc_ge_ht_data <- filter(ge_cor, Dataset == "GDSC" & Drug %in% ge_drugs & Gene %in% ge_genes)
-ks.test(filter(gdsc_ge_ht_data, InG2P == "Yes")$GE_p, filter(gdsc_ge_ht_data, InG2P == "No")$GE_p)
-```
-
 ```{r CN_GE_fig, eval=FALSE, fig.height=10, fig.width=15}
@@
 ## Lineages
-
-```{r lineages_ks_tests, warning=FALSE}
-ks.test(filter(ccle_signif_dgl, InG2P == "Yes")$p, filter(ccle_signif_dgl, InG2P == "No")$p)$p.value
-ks.test(filter(ctrp_signif_dgl, InG2P == "Yes")$p, filter(ctrp_signif_dgl, InG2P == "No")$p)$p.value
-ks.test(filter(gdsc_signif_dgl, InG2P == "Yes")$p, filter(gdsc_signif_dgl, InG2P == "No")$p)$p.value
-
-ks.test(filter(ccle_signif_prot_lin, InG2P == "Yes")$p, filter(ccle_signif_prot_lin, InG2P == "No")$p)$p.value
-ks.test(filter(ctrp_signif_prot_lin, InG2P == "Yes")$p, filter(ctrp_signif_prot_lin, InG2P == "No")$p)$p.value
-ks.test(filter(gdsc_signif_prot_lin, InG2P == "Yes")$p, filter(gdsc_signif_prot_lin, InG2P == "No")$p)$p.value
-
-ks.test(filter(cn_cor_lin, Dataset == "CCLE" & InG2P == "Yes")$CN_p, filter(cn_cor_lin, Dataset == "CCLE" & InG2P == "No")$CN_p)$p.value
-ks.test(filter(cn_cor_lin, Dataset == "CTRP" & InG2P == "Yes")$CN_p, filter(cn_cor_lin, Dataset == "CTRP" & InG2P == "No")$CN_p)$p.value
-ks.test(filter(cn_cor_lin, Dataset == "GDSC" & InG2P == "Yes")$CN_p, filter(cn_cor_lin, Dataset == "GDSC" & InG2P == "No")$CN_p)$p.value
-
-ks.test(filter(ge_cor_lin, Dataset == "CCLE" & InG2P == "Yes")$GE_p, filter(ge_cor_lin, Dataset == "CCLE" & InG2P == "No")$GE_p)$p.value
-ks.test(filter(ge_cor_lin, Dataset == "CTRP" & InG2P == "Yes")$GE_p, filter(ge_cor_lin, Dataset == "CTRP" & InG2P == "No")$GE_p)$p.value
-ks.test(filter(ge_cor_lin, Dataset == "GDSC" & InG2P == "Yes")$GE_p, filter(ge_cor_lin, Dataset == "GDSC" & InG2P == "No")$GE_p)$p.value
-
-lineage_ks_results <- data.frame("Dataset" = c(rep(c("CCLE", "CTRP", "GDSC"), 4)),
-           "Data type" = c(rep("Mutation", 3), rep("Protein change", 3), rep("Copy number", 3), rep("Gene expression", 3)),
-  "p.value" = c(ks.test(filter(ccle_signif_dgl, InG2P == "Yes")$p, filter(ccle_signif_dgl, InG2P == "No")$p)$p.value,
-  ks.test(filter(ctrp_signif_dgl, InG2P == "Yes")$p, filter(ctrp_signif_dgl, InG2P == "No")$p)$p.value,
-  ks.test(filter(gdsc_signif_dgl, InG2P == "Yes")$p, filter(gdsc_signif_dgl, InG2P == "No")$p)$p.value,
-  ks.test(filter(ccle_signif_prot_lin, InG2P == "Yes")$p, filter(ccle_signif_prot_lin, InG2P == "No")$p)$p.value,
-  ks.test(filter(ctrp_signif_prot_lin, InG2P == "Yes")$p, filter(ctrp_signif_prot_lin, InG2P == "No")$p)$p.value,
-  ks.test(filter(gdsc_signif_prot_lin, InG2P == "Yes")$p, filter(gdsc_signif_prot_lin, InG2P == "No")$p)$p.value,
-  ks.test(filter(cn_cor_lin, Dataset == "CCLE" & InG2P == "Yes")$CN_p, filter(cn_cor_lin, Dataset == "CCLE" & InG2P == "No")$CN_p)$p.value,
-  ks.test(filter(cn_cor_lin, Dataset == "CTRP" & InG2P == "Yes")$CN_p, filter(cn_cor_lin, Dataset == "CTRP" & InG2P == "No")$CN_p)$p.value,
-  ks.test(filter(cn_cor_lin, Dataset == "GDSC" & InG2P == "Yes")$CN_p, filter(cn_cor_lin, Dataset == "GDSC" & InG2P == "No")$CN_p)$p.value,
-  ks.test(filter(ge_cor_lin, Dataset == "CCLE" & InG2P == "Yes")$GE_p, filter(ge_cor_lin, Dataset == "CCLE" & InG2P == "No")$GE_p)$p.value,
-  ks.test(filter(ge_cor_lin, Dataset == "CTRP" & InG2P == "Yes")$GE_p, filter(ge_cor_lin, Dataset == "CTRP" & InG2P == "No")$GE_p)$p.value,
-  ks.test(filter(ge_cor_lin, Dataset == "GDSC" & InG2P == "Yes")$GE_p, filter(ge_cor_lin, Dataset == "GDSC" & InG2P == "No")$GE_p)$p.value))
-```
 
@@
 
-png(filename = "./plots/manuscript_final/drug_lin__pancancer.png", width = 18, height = 8, units = "in", res = 500)
+png(filename = "./plots/manuscript_final/drug_lin_pancancer.png", width = 18, height = 8, units = "in", res = 500)
 grid.arrange(layout_matrix = lay, grobs = gs_cn_ge)
@@
 ```
+
+# SCCB
+
+--------------------------------------------------------------------------------
+
+```{r}
+ccle_prot_lin <- filter(ccle_signif_prot_lin, InG2P == "Yes")
+ctrp_prot_lin <- filter(ctrp_signif_prot_lin, InG2P == "Yes")
+gdsc_prot_lin <- filter(gdsc_signif_prot_lin, InG2P == "Yes")
+```
+
+```{r histology_dists_data, eval=FALSE}
+hist_count <- function(df, dataset) {
+  hists <- unique(select(df, DepMap_ID, disease_g2p)) %>% count(disease_g2p)
+  hists$Percent <- hists$n / sum(hists$n) * 100
+  hists$Dataset <- dataset
+  hists <- hists[order(hists$n, decreasing = T),]
+  return(hists)
+}
+
+ccle_hists <- hist_count(ccle, "CCLE")
+ctrp_hists <- hist_count(ctrp, "CTRP")
+gdsc_hists <- hist_count(gdsc, "GDSC")
+
+drug_hists <- rbind(ccle_hists, ctrp_hists, gdsc_hists) %>% drop_na(disease_g2p)
+drug_hists$Dataset <- factor(drug_hists$Dataset, levels = c("CCLE", "CTRP", "GDSC"))
+
+png(filename = "./plots/manuscript/all_histology_distributions.png", width = 6, height = 4.5, units = "in", res = 500)
+ggplot(drug_hists, aes(x = Dataset, y = n, fill = disease_g2p)) +
+  geom_bar(stat = "identity", color = "black") +
+  scale_fill_manual(values = g2p_disease_colors) +
+  scale_y_continuous(breaks = seq(0, 900, by = 100), labels = seq(0, 900, by = 100)) +
+  guides(fill = guide_legend(title = "Lineage", ncol = 1)) +
+  labs(y = "Count") +
+  theme(axis.title.x = element_blank())
+dev.off()
+```
+
+```{r}
+length(unique(g2p_mut$Drug_Gene))
+length(unique(g2p_mut$Drug_Gene_Lin))
+length(unique(g2p_amp$Drug_Gene_Lin))
+
+g2p_mut_egfr <- filter(g2p_mut, Gene == "EGFR") %>% select(Drug_Gene_Lin, Protein_Change, Direction_Curated)
+
+test2 <- filter(cn_cor_lin, Drug != "CRISPR" & InG2P == "Yes")
+test <- filter(ge_cor_lin, Drug != "CRISPR" & InG2P == "Yes")
+test3 <- filter(cn_cor, Gene == "MET" & InG2P == "Yes")
+```
+
+## Specific plots
+
+```{r, eval=FALSE}
+ccle_prot$disease_g2p <- ifelse(ccle_prot$disease %in% g2p_diseases, ccle_prot$disease, "other")
+ctrp_prot$disease_g2p <- ifelse(ctrp_prot$disease %in% g2p_diseases, ctrp_prot$disease, "other")
+gdsc_prot$disease_g2p <- ifelse(gdsc_prot$disease %in% g2p_diseases, gdsc_prot$disease, "other")
+ccle_signif_prot_summ <- filter(ccle_signif_prot, InG2P == "Yes") 
+ctrp_signif_prot_summ <- filter(ctrp_signif_prot, InG2P == "Yes") 
+gdsc_signif_prot_summ <- filter(gdsc_signif_prot, InG2P == "Yes") 
+prot_drugs <- union(union(ccle_signif_prot_summ$Drug, ctrp_signif_prot_summ$Drug), gdsc_signif_prot_summ$Drug)
+prot_drugs <- prot_drugs[!(prot_drugs %in% c("cabozantinib", "vandetanib"))]
+
+ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_prot_4plot, Drug %in% prot_drugs), feature = "protein changes", legend_title = "CCLE -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.04)
+ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_prot_4plot, Drug %in% prot_drugs), feature = "protein changes", legend_title = "CTRP -log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.012)
+ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_prot_4plot, Drug %in% prot_drugs), feature = "protein changes", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 3, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.02)
+ht_prot_list <- ht_ccle2 + ht_ctrp2 + ht_gdsc2
+lgd <- list(Legend(labels = c("Resistance", "Sensitivity", "p < 0.05"), type = "points", pch = c(21, 21, 8), nrow = 1, background = "white", legend_gp = gpar(col = "black", fill = c("red", "white"))))
+
+png(filename = "./plots/prot_ht.png", width = 7, height = 6, units = "in", res = 500)
+draw(ht_prot_list, gap = unit(0.25, "in"), heatmap_legend_side = "top", annotation_legend_list = lgd, annotation_legend_side = "top", merge_legend = TRUE)
+dev.off()
+```
+
+```{r, eval=FALSE}
+ccle_signif_g2p_dg_summ <- filter(ccle_signif_g2p_dg, InG2P == "Yes") 
+ctrp_signif_g2p_dg_summ <- filter(ctrp_signif_g2p_dg, InG2P == "Yes") 
+gdsc_signif_g2p_dg_summ <- filter(gdsc_signif_g2p_dg, InG2P == "Yes")
+
+ccle_signif_g2p_dgl <- filter(ccle_signif_dgl, InG2P == "Yes") 
+ctrp_signif_g2p_dgl <- filter(ctrp_signif_dgl, InG2P == "Yes") 
+gdsc_signif_g2p_dgl <- filter(gdsc_signif_dgl, InG2P == "Yes")
+
+signif_g2p_dg_summ <- rbind(ccle_signif_g2p_dg_summ, ctrp_signif_g2p_dg_summ, gdsc_signif_g2p_dg_summ)
+signif_g2p_dg_summ <- unique(select(signif_g2p_dg_summ, Drug_Gene, p))
+test <- filter(signif_g2p_dg_summ, p < 0.05)
+length(unique(signif_g2p_dg_summ$Drug_Gene))
+
+ccle_mut_filt <- filter(ccle, Drug_Gene == "crizotinib_ROS1")
+ccle_mut_filt_plot <- ggplot(data = ccle_mut_filt, mapping = aes(x = as.character(Mutation), y = Score)) +
+  # facet_wrap(~ Drug_Gene, nrow = 1) +
+  geom_violinhalf(aes(fill = as.character(Mutation)), position = position_nudge(x = 0.2, y = 0), alpha = 0.8, show.legend = FALSE) +
+  geom_boxplot(width = 0.1, guides = FALSE, outlier.shape = NA, alpha = 0.8) +
+  geom_point(aes(color = as.character(Mutation)), position = position_jitter(width = 0.15), size = 0.5, alpha = 0.6) +
+  scale_fill_manual(labels = c("Wildtype", "Mutant"), values = c("1" = "springgreen4", "0" = "palegreen3")) +
+  scale_color_manual(labels = c("Wildtype", "Mutant"), values = c("1" = "springgreen4", "0" = "palegreen3")) +
+  # scale_color_manual(values = g2p_disease_colors) +
+  scale_x_discrete(labels = c("0" = "Wildtype", "1" = "Mutant")) +
+  scale_y_continuous(breaks = seq(0, 1.00, by = 0.25), labels = c("0.00", "0.25", "0.50", "0.75", "1.00")) +
+  coord_cartesian(ylim = c(0, 1.10)) +
+  # stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35, label.y = 1.1) +
+  annotate(geom = "text", label = "p = 0.0020", x = 1.5, y = 1.1) +
+  labs(title = "CCLE: Crizotinib, ROS1", x = "Mutation Status", y = "AUC") +
+  # guides(color = guide_legend(override.aes = list(size = 3))) +
+  theme(legend.position = "none", axis.title.x = element_blank(),
+        panel.background = element_rect(fill = "mintcream", colour = "mintcream", size = 0.5, linetype = "solid"),
+        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+ggsave(plot = ccle_mut_filt_plot, filename = "./plots/crizotinib_ROS1_mut.png", width = 4, height = 3, units = "in", dpi = "retina", device = "png")
+
+ccle_mut_filt <- filter(ccle, Drug_Gene == "erlotinib_EGFR")
+ccle_mut_filt_plot <- ggplot(data = ccle_mut_filt, mapping = aes(x = as.character(Mutation), y = Score)) +
+  # facet_wrap(~ Drug_Gene, nrow = 1) +
+  geom_violinhalf(aes(fill = as.character(Mutation)), position = position_nudge(x = 0.2, y = 0), alpha = 0.8, show.legend = FALSE) +
+  geom_boxplot(width = 0.1, guides = FALSE, outlier.shape = NA, alpha = 0.8) +
+  geom_point(aes(color = disease_g2p), position = position_jitter(width = 0.15), size = 0.5, alpha = 0.6) +
+  scale_fill_manual(labels = c("Wildtype", "Mutant"), values = c("1" = "springgreen4", "0" = "palegreen3")) +
+  scale_color_manual(values = g2p_disease_colors) +
+  scale_x_discrete(labels = c("0" = "Wildtype", "1" = "Mutant")) +
+  scale_y_continuous(breaks = seq(0, 1.00, by = 0.25), labels = c("0.00", "0.25", "0.50", "0.75", "1.00")) +
+  coord_cartesian(ylim = c(0, 1.10)) +
+  # stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35, label.y = 1.1) +
+  annotate(geom = "text", label = "p = 0.0385", x = 1.5, y = 1.1) +
+  labs(title = "CCLE: Erlotinib, EGFR", x = "Mutation Status", y = "AUC") +
+  # guides(color = guide_legend(override.aes = list(size = 3))) +
+  theme(legend.position = "none", axis.title.x = element_blank(),
+        panel.background = element_rect(fill = "mintcream", colour = "mintcream", size = 0.5, linetype = "solid"),
+        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+ggsave(plot = ccle_mut_filt_plot, filename = "./plots/erlotinib_EGFR_mut.png", width = 4, height = 3, units = "in", dpi = "retina", device = "png")
+
+ctrp_mut_filt <- filter(ctrp, Drug_Gene == "vemurafenib_BRAF")
+ctrp_mut_filt_plot <- ggplot(data = ctrp_mut_filt, mapping = aes(x = as.character(Mutation), y = Score)) +
+  # facet_wrap(~ Drug_Gene, ncol = 4) +
+  geom_violinhalf(aes(fill = as.character(Mutation)), position = position_nudge(x = 0.2, y = 0), alpha = 0.8, show.legend = FALSE) +
+  geom_boxplot(width = 0.1, guides = FALSE, outlier.shape = NA, alpha = 0.8) +
+  geom_point(aes(color = disease_g2p), position = position_jitter(width = 0.15), size = 0.5, alpha = 0.6) +
+  scale_fill_manual(labels = c("Wildtype", "Mutant"), values = c("1" = "steelblue4", "0" = "slategray3")) +
+  scale_color_manual(name = "Lineage", values = g2p_disease_colors) +
+  scale_x_discrete(labels = c("0" = "Wildtype", "1" = "Mutant")) +
+  scale_y_continuous(breaks = seq(0, 1.00, by = 0.25), labels = c("0.00", "0.25", "0.50", "0.75", "1.00")) +
+  coord_cartesian(ylim = c(0, 1.10)) +
+  # stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35, label.y = 1.1) +
+  labs(title = "CTRP: Vemurafenib, BRAF", x = "Mutation Status", y = "AUC") +
+  annotate(geom = "text", label = "p = 0.00045", x = 1.5, y = 1.1) +
+  # guides(color = guide_legend(override.aes = list(size = 3))) +
+  theme(legend.position = "none", axis.title.x = element_blank(),
+        panel.background = element_rect(fill = "whitesmoke", colour = "whitesmoke", size = 0.5, linetype = "solid"),
+        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+ggsave(plot = ctrp_mut_filt_plot, filename = "./plots/vemurafenib_BRAF_mut.png", width = 4, height = 3, units = "in", dpi = "retina", device = "png")
+
+cn_cor$p.format <- with(cn_cor, ifelse(CN_p < 0.001, "p < 0.001", paste0("p = ", round(CN_p, digits = 3))))
+ccle_cn_cor <- unfactorize(filter(cn_cor, Dataset == "CCLE" & InG2P == "Yes"))
+ccle_cn_cor_filt <- filter(ccle_cn_cor, Drug_Gene == "lapatinib_ERBB2")
+ccle_cn_filt <- filter(ccle, Drug_Gene == "lapatinib_ERBB2")
+ccle_text <- data.frame(label = paste0("r = ", round(ccle_cn_cor_filt$CN_r, digits = 3), ", ", ccle_cn_cor_filt$p.format), Drug_Gene = ccle_cn_cor_filt$Drug_Gene)
+ccle_cn_filt_plot <- ggplot(data = ccle_cn_filt, aes(x = CN, y = Score)) +
+  # facet_wrap(~ Drug_Gene) +
+  geom_point(aes(color = disease_g2p), pch = 20, size = 1, alpha = 0.7) +
+  geom_text(data = ccle_text,
+            mapping = aes(x = +Inf, y = +Inf, label = label,
+            hjust = 1.1, vjust = 1.2)) +
+  scale_color_manual(values = g2p_disease_colors) +
+  labs(title = "CCLE: Lapatinib, ERBB2", x = "Copy number (log2)", y = "AUC") +
+  theme(legend.position = "none",
+        panel.background = element_rect(fill = "mintcream", colour = "mintcream", size = 0.5, linetype = "solid"),
+        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+ggsave(plot = ccle_cn_filt_plot, filename = "./plots/lapatinib_ERBB2_cn_ccle.png", width = 4, height = 3, units = "in", dpi = "retina", device = "png")
+
+ctrp_cn_cor <- unfactorize(filter(cn_cor, Dataset == "CTRP" & InG2P == "Yes"))
+ctrp_cn_cor_filt <- filter(ctrp_cn_cor, Drug_Gene == "lapatinib_ERBB2")
+ctrp_cn_filt <- filter(ctrp, Drug_Gene == "lapatinib_ERBB2")
+ctrp_text <- data.frame(label = paste0("r = ", round(ctrp_cn_cor_filt$CN_r, digits = 3), ", ", ctrp_cn_cor_filt$p.format), Drug_Gene = ctrp_cn_cor_filt$Drug_Gene)
+ctrp_cn_filt_plot <- ggplot(data = ctrp_cn_filt, aes(x = CN, y = Score)) +
+  # facet_wrap(~ Drug_Gene) +
+  geom_point(aes(color = disease_g2p), pch = 20, size = 1, alpha = 0.7) +
+  geom_text(data = ctrp_text,
+            mapping = aes(x = +Inf, y = +Inf, label = label,
+            hjust = 1.1, vjust = 1.2)) +
+  scale_color_manual(values = g2p_disease_colors) +
+  labs(title = "CTRP: Lapatinib, ERBB2", x = "Copy number (log2)", y = "AUC") +
+  theme(legend.position = "none",
+        panel.background = element_rect(fill = "whitesmoke", colour = "whitesmoke", size = 0.5, linetype = "solid"),
+        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+ggsave(plot = ctrp_cn_filt_plot, filename = "./plots/lapatinib_ERBB2_cn_ctrp.png", width = 4, height = 3, units = "in", dpi = "retina", device = "png")
+
+gdsc_cn_cor <- unfactorize(filter(cn_cor, Dataset == "GDSC" & InG2P == "Yes"))
+gdsc_cn_cor_filt <- filter(gdsc_cn_cor, Drug_Gene == "lapatinib_ERBB2")
+gdsc_cn_filt <- filter(gdsc, Drug_Gene == "lapatinib_ERBB2")
+gdsc_text <- data.frame(label = paste0("r = ", round(gdsc_cn_cor_filt$CN_r, digits = 3), ", ", gdsc_cn_cor_filt$p.format), Drug_Gene = gdsc_cn_cor_filt$Drug_Gene)
+gdsc_cn_filt_plot <- ggplot(data = gdsc_cn_filt, aes(x = CN, y = Score)) +
+  # facet_wrap(~ Drug_Gene) +
+  geom_point(aes(color = disease_g2p), pch = 20, size = 1, alpha = 0.7) +
+  geom_text(data = gdsc_text,
+            mapping = aes(x = +Inf, y = +Inf, label = label,
+            hjust = 1.1, vjust = 1.2)) +
+  scale_color_manual(values = g2p_disease_colors) +
+  labs(title = "GDSC: Lapatinib, ERBB2", x = "Copy number (log2)", y = "AUC") +
+  theme(legend.position = "none",
+        panel.background = element_rect(fill = "azure", colour = "azure", size = 0.5, linetype = "solid"),
+        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+ggsave(plot = gdsc_cn_filt_plot, filename = "./plots/lapatinib_ERBB2_cn_gdsc.png", width = 4, height = 3, units = "in", dpi = "retina", device = "png")
+
+ge_cor$p.format <- with(ge_cor, ifelse(GE_p < 0.001, "p < 0.001", paste0("p = ", round(GE_p, digits = 3))))
+gdsc_ge_cor <- unfactorize(filter(ge_cor, Dataset == "GDSC" & InG2P == "Yes"))
+gdsc_ge_cor_filt <- filter(gdsc_ge_cor, Drug_Gene  == "lapatinib_ERBB2")
+gdsc_ge_filt <- filter(gdsc, Drug_Gene  == "lapatinib_ERBB2")
+gdsc_text <- data.frame(label = paste0("r = ", round(gdsc_ge_cor_filt$GE_r, digits = 3), ", ", gdsc_ge_cor_filt$p.format), Drug_Gene = gdsc_ge_cor_filt$Drug_Gene)
+gdsc_ge_filt_plot <- ggplot(data = gdsc_ge_filt, aes(x = TPM, y = Score) )+
+  # facet_wrap(~ Drug_Gene) +
+  geom_point(aes(color = disease_g2p), pch = 20, size = 1, alpha = 0.7) +
+  geom_text(data = gdsc_text,
+            mapping = aes(x = +Inf, y = +Inf, label = label,
+            hjust = 1.1, vjust = 1.2)) +
+  scale_y_continuous(breaks = seq(0, 1.00, by = 0.25), labels = c("0.00", "0.25", "0.50", "0.75", "1.00")) +
+  coord_cartesian(ylim = c(0, 1.00)) +
+  scale_color_manual(values = g2p_disease_colors) +
+  labs(title = "GDSC: Lapatinib, ERBB2", x = "Gene expression [log2(TPM)]", y = "AUC") +
+  theme(legend.position = "none",
+        panel.background = element_rect(fill = "azure", colour = "azure", size = 0.5, linetype = "solid"),
+        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+ggsave(plot = gdsc_ge_filt_plot, filename = "./plots/lapatinib_ERBB2_ge.png", width = 5, height = 3, units = "in", dpi = "retina", device = "png")
+```
+
+## Lineage plots
+
+```{r}
+ccle_mut_lin_filt <- filter(ccle, Drug_Gene_Lin == "erlotinib_EGFR_lung")
+ccle_mut_lin_filt_plot <- ggplot(data = ccle_mut_lin_filt, mapping = aes(x = as.character(Mutation), y = Score)) +
+  # facet_wrap(~ Drug_Gene_Lin, nrow = 1) +
+  geom_violinhalf(aes(fill = as.character(Mutation)), position = position_nudge(x = 0.2, y = 0), alpha = 0.8, show.legend = FALSE) +
+  geom_boxplot(width = 0.1, guides = FALSE, outlier.shape = NA, alpha = 0.8) +
+  geom_point(aes(color = disease_g2p), position = position_jitter(width = 0.15), size = 0.5, alpha = 0.6) +
+  scale_fill_manual(labels = c("Wildtype", "Mutant"), values = c("1" = "springgreen4", "0" = "palegreen3")) +
+  # scale_color_manual(labels = c("Wildtype", "Mutant"), values = c("1" = "springgreen4", "0" = "palegreen3")) +
+  scale_color_manual(values = g2p_disease_colors) +
+  scale_x_discrete(labels = c("0" = "Wildtype", "1" = "Mutant")) +
+  scale_y_continuous(breaks = seq(0, 1.00, by = 0.25), labels = c("0.00", "0.25", "0.50", "0.75", "1.00")) +
+  coord_cartesian(ylim = c(0, 1.10)) +
+  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35, label.y = 1.1) +
+  labs(title = "CCLE: Erlotinib, EGFR, lung", x = "Mutation Status", y = "AUC") +
+  guides(color = guide_legend(override.aes = list(size = 3))) +
+  theme(legend.position = "none",axis.title.x = element_blank(),
+        panel.background = element_rect(fill = "mintcream", colour = "mintcream", size = 0.5, linetype = "solid"),
+        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+ggsave(plot = ccle_mut_lin_filt_plot, filename = "./plots/erlotinib_EGFR_lung_mut.png", width = 4, height = 3, units = "in", dpi = "retina", device = "png")
+
+ctrp_mut_lin_filt <- filter(ctrp, Drug_Gene_Lin == "vemurafenib_BRAF_skin")
+ctrp_mut_lin_filt_plot <- ggplot(data = ctrp_mut_lin_filt, mapping = aes(x = as.character(Mutation), y = Score)) +
+  # facet_wrap(~ Drug_Gene_Lin, ncol = 4) +
+  geom_violinhalf(aes(fill = as.character(Mutation)), position = position_nudge(x = 0.2, y = 0), alpha = 0.8, show.legend = FALSE) +
+  geom_point(aes(color =  disease_g2p), position = position_jitter(width = 0.15), size = 0.5, alpha = 0.6) +
+  geom_boxplot(width = 0.1, guides = FALSE, outlier.shape = NA, alpha = 0.8) +
+  scale_fill_manual(labels = c("Wildtype", "Mutant"), values = c("1" = "steelblue4", "0" = "slategray3")) +
+  # scale_color_manual(labels = c("Wildtype", "Mutant"), values = c("1" = "steelblue4", "0" = "slategray3")) +
+  scale_color_manual(values = g2p_disease_colors) +
+  scale_x_discrete(labels = c("0" = "Wildtype", "1" = "Mutant")) +
+  scale_y_continuous(breaks = seq(0, 1.00, by = 0.25), labels = c("0.00", "0.25", "0.50", "0.75", "1.00")) +
+  coord_cartesian(ylim = c(0, 1.10)) +
+  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35, label.y = 1.1) +
+  labs(title = "CTRP: Vemurafenib, BRAF, skin", x = "Mutation Status", y = "AUC") +
+  guides(color = guide_legend(override.aes = list(size = 3))) +
+  theme(legend.position = "none", axis.title.x = element_blank(),
+        panel.background = element_rect(fill = "whitesmoke", colour = "whitesmoke", size = 0.5, linetype = "solid"),
+        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+ggsave(plot = ctrp_mut_lin_filt_plot, filename = "./plots/vemurafenib_BRAF_skin_mut.png", width = 4, height = 3, units = "in", dpi = "retina", device = "png")
+
+ctrp_prot_filt <- filter(ctrp_prot, Drug_Gene_Protein_Change == "vemurafenib_BRAF:V600E")
+ctrp_prot_filt_plot <- ggplot(data = ctrp_prot_filt, mapping = aes(x = Change_Status, y = Score)) +
+  # facet_wrap(~ Drug_Gene_Protein_Change, nrow = 2) +
+  geom_violinhalf(aes(fill = Change_Status), position = position_nudge(x = 0.2, y = 0), alpha = 0.8, show.legend = FALSE) +
+  geom_point(aes(color = disease_g2p), position = position_jitter(width = 0.15), size = 0.5, alpha = 0.6) +
+  geom_boxplot(width = 0.1, guides = FALSE, outlier.shape = NA, alpha = 0.7) +
+  scale_x_discrete(labels = c("No" = "Wildtype", "Yes" = "Mutant")) +
+  scale_fill_manual(labels = c("Wildtype", "Mutant"), values = c("Yes" = "steelblue4", "No" = "slategray3")) +
+  scale_color_manual(name = "Lineage", values = g2p_disease_colors) +
+  scale_y_continuous(breaks = seq(0, 1.00, by = 0.25), labels = c("0.00", "0.25", "0.50", "0.75", "1.00")) +
+  coord_cartesian(ylim = c(0, 1.10)) +
+  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35, label.y = 1.1) +
+  labs(title = "CTRP: Vemurafenib, BRAF:V600E", x = "Change Status", y = "AUC") +
+  guides(color = guide_legend(override.aes = list(size = 3))) +
+  theme(legend.position = "none", axis.title.x = element_blank(),
+        panel.background = element_rect(fill = "whitesmoke", colour = "whitesmoke", size = 0.5, linetype = "solid"),
+        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+ggsave(plot = ctrp_prot_filt_plot, filename = "./plots/vemurafenib_BRAF_V600E_mut.png", width = 4, height = 3, units = "in", dpi = "retina", device = "png")
+
+ctrp_prot_filt <- filter(ctrp_prot, Drug_Gene_Protein_Change == "dabrafenib_BRAF:V600E")
+ctrp_prot_filt_plot <- ggplot(data = ctrp_prot_filt, mapping = aes(x = Change_Status, y = Score)) +
+  # facet_wrap(~ Drug_Gene_Protein_Change, nrow = 2) +
+  geom_violinhalf(aes(fill = Change_Status), position = position_nudge(x = 0.2, y = 0), alpha = 0.8, show.legend = FALSE) +
+  geom_point(aes(color = disease_g2p), position = position_jitter(width = 0.15), size = 0.5, alpha = 0.6) +
+  geom_boxplot(width = 0.1, guides = FALSE, outlier.shape = NA, alpha = 0.7) +
+  scale_x_discrete(labels = c("No" = "Wildtype", "Yes" = "Mutant")) +
+  scale_fill_manual(labels = c("Wildtype", "Mutant"), values = c("Yes" = "steelblue4", "No" = "slategray3")) +
+  scale_color_manual(name = "Lineage", values = g2p_disease_colors) +
+  scale_y_continuous(breaks = seq(0, 1.00, by = 0.25), labels = c("0.00", "0.25", "0.50", "0.75", "1.00")) +
+  coord_cartesian(ylim = c(0, 1.10)) +
+  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35, label.y = 1.1) +
+  labs(title = "CTRP: Dabrafenib, BRAF:V600E", x = "Change Status", y = "AUC") +
+  guides(color = guide_legend(override.aes = list(size = 3))) +
+  theme(legend.position = "none", axis.title.x = element_blank(),
+        panel.background = element_rect(fill = "whitesmoke", colour = "whitesmoke", size = 0.5, linetype = "solid"),
+        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+ggsave(plot = ctrp_prot_filt_plot, filename = "./plots/dabrafenib_BRAF_V600E_mut.png", width = 4, height = 3, units = "in", dpi = "retina", device = "png")
+
+ctrp_signif_prot_lin$disease_g2p <- ifelse(ctrp_signif_prot_lin$disease %in% g2p_diseases, ctrp_signif_prot_lin$disease, "other")
+ctrp_signif_prot_lin_filt <- filter(ctrp_signif_prot_lin, InG2P == "Yes")
+ctrp_prot_lin_filt <- filter(ctrp_prot, Drug_Gene_Protein_Change_Lineage == "vemurafenib_BRAF:V600E_skin")
+ctrp_prot_lin_filt_plot <- ggplot(data = ctrp_prot_lin_filt, mapping = aes(x = Change_Status, y = Score)) +
+  # facet_wrap(~ Drug_Gene_Protein_Change_Lineage, nrow = 2) +
+  geom_violinhalf(aes(fill = Change_Status), position = position_nudge(x = 0.2, y = 0), alpha = 0.8, show.legend = FALSE) +
+  geom_boxplot(width = 0.1, guides = FALSE, outlier.shape = NA, alpha = 0.4) +
+  geom_point(aes(color = disease_g2p), position = position_jitter(width = 0.15), size = 0.5, alpha = 0.6) +
+  scale_x_discrete(labels = c("No" = "Wildtype", "Yes" = "Mutant")) +
+  scale_fill_manual(labels = c("Wildtype", "Mutant"), values = c("Yes" = "steelblue4", "No" = "slategray3")) +
+  scale_color_manual(values = g2p_disease_colors) +
+  # scale_color_manual(labels = c("Wildtype", "Mutant"), values = c("Yes" = "steelblue4", "No" = "slategray3")) +
+  scale_y_continuous(breaks = seq(0, 1.00, by = 0.25), labels = c("0.00", "0.25", "0.50", "0.75", "1.00")) +
+  coord_cartesian(ylim = c(0, 1.10)) +
+  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35, label.y = 1.1) +
+  labs(title = "CTRP: Vemurafenib, BRAF:V600E, skin", x = "Change Status", y = "AUC") +
+  guides(color = guide_legend(override.aes = list(size = 3))) +
+  theme(legend.position = "none", axis.title.x = element_blank(),
+        panel.background = element_rect(fill = "whitesmoke", colour = "whitesmoke", size = 0.5, linetype = "solid"),
+        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+ggsave(plot = ctrp_prot_lin_filt_plot, filename = "./plots/vemuerafenib_BRAF_V600E_skin_mut.png", width = 4, height = 3, units = "in", dpi = "retina", device = "png")
+
+ctrp_signif_prot_lin$disease_g2p <- ifelse(ctrp_signif_prot_lin$disease %in% g2p_diseases, ctrp_signif_prot_lin$disease, "other")
+ctrp_signif_prot_lin_filt <- filter(ctrp_signif_prot_lin, InG2P == "Yes")
+ctrp_prot_lin_filt <- filter(ctrp_prot, Drug_Gene_Protein_Change_Lineage == "dabrafenib_BRAF:V600E_skin")
+ctrp_prot_lin_filt_plot <- ggplot(data = ctrp_prot_lin_filt, mapping = aes(x = Change_Status, y = Score)) +
+  # facet_wrap(~ Drug_Gene_Protein_Change_Lineage, nrow = 2) +
+  geom_violinhalf(aes(fill = Change_Status), position = position_nudge(x = 0.2, y = 0), alpha = 0.8, show.legend = FALSE) +
+  geom_boxplot(width = 0.1, guides = FALSE, outlier.shape = NA, alpha = 0.4) +
+  geom_point(aes(color = disease_g2p), position = position_jitter(width = 0.15), size = 0.5, alpha = 0.6) +
+  scale_x_discrete(labels = c("No" = "Wildtype", "Yes" = "Mutant")) +
+  scale_fill_manual(labels = c("Wildtype", "Mutant"), values = c("Yes" = "steelblue4", "No" = "slategray3")) +
+  scale_color_manual(values = g2p_disease_colors) +
+  # scale_color_manual(labels = c("Wildtype", "Mutant"), values = c("Yes" = "steelblue4", "No" = "slategray3")) +
+  scale_y_continuous(breaks = seq(0, 1.00, by = 0.25), labels = c("0.00", "0.25", "0.50", "0.75", "1.00")) +
+  coord_cartesian(ylim = c(0, 1.10)) +
+  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35, label.y = 1.1) +
+  labs(title = "CTRP: Dabrafenib, BRAF:V600E, skin", x = "Change Status", y = "AUC") +
+  guides(color = guide_legend(override.aes = list(size = 3))) +
+  theme(legend.position = "none", axis.title.x = element_blank(),
+        panel.background = element_rect(fill = "whitesmoke", colour = "whitesmoke", size = 0.5, linetype = "solid"),
+        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+ggsave(plot = ctrp_prot_lin_filt_plot, filename = "./plots/daberafenib_BRAF_V600E_skin_mut.png", width = 4, height = 3, units = "in", dpi = "retina", device = "png")
+
+cn_cor_lin$p.format <- with(cn_cor_lin, ifelse(CN_p < 0.001, "p < 0.001", paste0("p = ", round(CN_p, digits = 3))))
+ccle_cn_lin_cor <- unfactorize(filter(cn_cor_lin, Dataset == "CCLE" & InG2P == "Yes"))
+ctrp_cn_lin_cor <- unfactorize(filter(cn_cor_lin, Dataset == "CTRP" & InG2P == "Yes"))
+gdsc_cn_lin_cor <- unfactorize(filter(cn_cor_lin, Dataset == "GDSC" & InG2P == "Yes"))
+
+ccle_cn_lin_cor_filt <- filter(ccle_cn_lin_cor, Drug_Gene_Lin == "lapatinib_ERBB2_breast")
+ccle_cn_lin_filt <- filter(ccle, Drug_Gene_Lin == "lapatinib_ERBB2_breast")
+ccle_lin_text <- data.frame(label = paste0("r = ", round(ccle_cn_lin_cor_filt$CN_r, digits = 3), ", ", ccle_cn_lin_cor_filt$p.format), Drug_Gene_Lin = ccle_cn_lin_cor_filt$Drug_Gene_Lin)
+ccle_cn_lin_filt_plot <- ggplot(data = ccle_cn_lin_filt, aes(x = CN, y = Score)) +
+  # facet_wrap(~ Drug_Gene_Lin) +
+  geom_point(aes(color = disease_g2p), pch = 20, size = 1, alpha = 0.7) +
+  geom_smooth(stat = "smooth", method = "lm", color = "gray70", fill = "gray88", lwd = 1) +
+  geom_text(data = ccle_lin_text,
+            mapping = aes(x = +Inf, y = +Inf, label = label,
+            hjust = 1.1, vjust = 1.2)) +
+  scale_color_manual(values = g2p_disease_colors) +
+  coord_cartesian(ylim = c(0, 1)) +
+  labs(title = "CCLE: Lapatinib, ERBB2, breast", x = "Copy number (log2)", y = "AUC") +
+  theme(legend.position = "none",
+        panel.background = element_rect(fill = "mintcream", colour = "mintcream", size = 0.5, linetype = "solid"),
+        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+ggsave(plot = ccle_cn_lin_filt_plot, filename = "./plots/lapatinib_ERBB2_breast_cn_ccle.png", width = 4, height = 3, units = "in", dpi = "retina", device = "png")
+
+ctrp_cn_lin_cor_filt <- filter(ctrp_cn_lin_cor, Drug_Gene_Lin == "lapatinib_ERBB2_breast")
+ctrp_cn_lin_filt <- filter(ctrp, Drug_Gene_Lin == "lapatinib_ERBB2_breast")
+ctrp_lin_text <- data.frame(label = paste0("r = ", round(ctrp_cn_lin_cor_filt$CN_r, digits = 3), ", ", ctrp_cn_lin_cor_filt$p.format), Drug_Gene_Lin = ctrp_cn_lin_cor_filt$Drug_Gene_Lin)
+ctrp_cn_lin_filt_plot <- ggplot(data = ctrp_cn_lin_filt, aes(x = CN, y = Score)) +
+  # facet_wrap(~ Drug_Gene_Lin) +
+  geom_point(aes(color = disease_g2p), pch = 20, size = 1, alpha = 0.7) +
+  geom_smooth(stat = "smooth", method = "lm", color = "gray70", fill = "gray88", lwd = 1) +
+  geom_text(data = ctrp_lin_text,
+            mapping = aes(x = +Inf, y = +Inf, label = label,
+            hjust = 1.1, vjust = 1.2)) +
+  labs(title = "CTRP: Lapatinib, ERBB2, breast", x = "Copy number (log2)", y = "AUC") +
+  scale_color_manual(values = g2p_disease_colors) +
+  coord_cartesian(ylim = c(0, 1)) +
+  theme(legend.position = "none",
+        panel.background = element_rect(fill = "whitesmoke", colour = "whitesmoke", size = 0.5, linetype = "solid"),
+        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+ggsave(plot = ctrp_cn_lin_filt_plot, filename = "./plots/lapatinib_ERBB2_breast_cn_ctrp.png", width = 4, height = 3, units = "in", dpi = "retina", device = "png")
+
+gdsc_cn_lin_cor_filt <- filter(gdsc_cn_lin_cor, Drug_Gene_Lin == "lapatinib_ERBB2_breast")
+gdsc_cn_lin_filt <- filter(gdsc, Drug_Gene_Lin == "lapatinib_ERBB2_breast")
+gdsc_lin_text <- data.frame(label = paste0("r = ", round(gdsc_cn_lin_cor_filt$CN_r, digits = 3), ", ", gdsc_cn_lin_cor_filt$p.format), Drug_Gene_Lin = gdsc_cn_lin_cor_filt$Drug_Gene_Lin)
+gdsc_cn_lin_filt_plot <- ggplot(data = gdsc_cn_lin_filt, aes(x = CN, y = Score) )+
+  # facet_wrap(~ Drug_Gene_Lin) +
+  geom_point(aes(color = disease_g2p), pch = 20, size = 1, alpha = 0.7) +
+  geom_smooth(stat = "smooth", method = "lm", color = "gray70", fill = "gray88", lwd = 1) +
+  geom_text(data = gdsc_lin_text,
+            mapping = aes(x = +Inf, y = +Inf, label = label,
+            hjust = 1.1, vjust = 1.2)) +
+  scale_y_continuous(breaks = seq(0, 1.00, by = 0.25), labels = c("0.00", "0.25", "0.50", "0.75", "1.00")) +
+  coord_cartesian(ylim = c(0, 1.00)) +
+  scale_color_manual(values = g2p_disease_colors) +
+  labs(title = "GDSC: Lapatinib, ERBB2, breast", x = "Copy number (log2)", y = "AUC") +
+  theme(legend.position = "none",
+        panel.background = element_rect(fill = "azure", colour = "azure", size = 0.5, linetype = "solid"),
+        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+ggsave(plot = gdsc_cn_lin_filt_plot, filename = "./plots/lapatinib_ERBB2_breast_cn_gdsc.png", width = 4, height = 3, units = "in", dpi = "retina", device = "png")
+
+ge_cor_lin$p.format <- with(ge_cor_lin, ifelse(GE_p < 0.001, "p < 0.001", paste0("p = ", round(GE_p, digits = 3))))
+ccle_ge_lin_cor <- unfactorize(filter(ge_cor_lin, Dataset == "CCLE" & InG2P == "Yes"))
+ctrp_ge_lin_cor <- unfactorize(filter(ge_cor_lin, Dataset == "CTRP" & InG2P == "Yes"))
+gdsc_ge_lin_cor <- unfactorize(filter(ge_cor_lin, Dataset == "GDSC" & InG2P == "Yes"))
+
+ccle_ge_lin_cor_filt <- filter(ccle_ge_lin_cor, Drug_Gene_Lin == "lapatinib_ERBB2_breast")
+ccle_ge_lin_filt <- filter(ccle, Drug_Gene_Lin == "lapatinib_ERBB2_breast")
+ccle_lin_text <- data.frame(label = paste0("r = ", round(ccle_ge_lin_cor_filt$GE_r, digits = 3), ", ", ccle_ge_lin_cor_filt$p.format), Drug_Gene_Lin = ccle_ge_lin_cor_filt$Drug_Gene_Lin)
+ccle_ge_lin_filt_plot <- ggplot(data = ccle_ge_lin_filt, aes(x = TPM, y = Score)) +
+  # facet_wrap(~ Drug_Gene_Lin) +
+  geom_point(aes(color = disease_g2p), pch = 20, size = 1, alpha = 0.7) +
+  geom_smooth(stat = "smooth", method = "lm", color = "gray70", fill = "gray88", lwd = 1) +
+  geom_text(data = ccle_lin_text,
+            mapping = aes(x = +Inf, y = +Inf, label = label,
+            hjust = 1.1, vjust = 1.2)) +
+  scale_color_manual(values = g2p_disease_colors) +
+  coord_cartesian(ylim = c(0, 1)) +
+  labs(title = "CCLE: Lapatinib, ERBB2, breast", x = "Gene expression [log2(TPM)]", y = "AUC") +
+  theme(legend.position = "none",
+        panel.background = element_rect(fill = "mintcream", colour = "mintcream", size = 0.5, linetype = "solid"),
+        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+ggsave(plot = ccle_ge_lin_filt_plot, filename = "./plots/lapatinib_ERBB2_breast_ge_ccle.png", width = 5, height = 3, units = "in", dpi = "retina", device = "png")
+
+ctrp_ge_lin_cor_filt <- filter(ctrp_ge_lin_cor, Drug_Gene_Lin == "lapatinib_ERBB2_breast")
+ctrp_ge_lin_filt <- filter(ctrp, Drug_Gene_Lin == "lapatinib_ERBB2_breast")
+ctrp_lin_text <- data.frame(label = paste0("r = ", round(ctrp_ge_lin_cor_filt$GE_r, digits = 3), ", ", ctrp_ge_lin_cor_filt$p.format), Drug_Gene_Lin = ctrp_ge_lin_cor_filt$Drug_Gene_Lin)
+ctrp_ge_lin_filt_plot <- ggplot(data = ctrp_ge_lin_filt, aes(x = TPM, y = Score)) +
+  # facet_wrap(~ Drug_Gene_Lin) +
+  geom_point(aes(color = disease_g2p), pch = 20, size = 1, alpha = 0.7) +
+  geom_smooth(stat = "smooth", method = "lm", color = "gray70", fill = "gray88", lwd = 1) +
+  geom_text(data = ctrp_lin_text,
+            mapping = aes(x = +Inf, y = +Inf, label = label,
+            hjust = 1.1, vjust = 1.2)) +
+  labs(title = "CTRP: Lapatinib, ERBB2, breast", x = "Gene expression [log2(TPM)]", y = "AUC") +
+  scale_color_manual(values = g2p_disease_colors) +
+  coord_cartesian(ylim = c(0, 1)) +
+  theme(legend.position = "none",
+        panel.background = element_rect(fill = "whitesmoke", colour = "whitesmoke", size = 0.5, linetype = "solid"),
+        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+ggsave(plot = ctrp_ge_lin_filt_plot, filename = "./plots/lapatinib_ERBB2_breast_ge_ctrp.png", width = 5, height = 3, units = "in", dpi = "retina", device = "png")
+
+gdsc_ge_lin_cor_filt <- filter(gdsc_ge_lin_cor, Drug_Gene_Lin == "lapatinib_ERBB2_breast")
+gdsc_ge_lin_filt <- filter(gdsc, Drug_Gene_Lin == "lapatinib_ERBB2_breast")
+gdsc_lin_text <- data.frame(label = paste0("r = ", round(gdsc_ge_lin_cor_filt$GE_r, digits = 3), ", ", gdsc_ge_lin_cor_filt$p.format), Drug_Gene_Lin = gdsc_ge_lin_cor_filt$Drug_Gene_Lin)
+gdsc_ge_lin_filt_plot <- ggplot(data = gdsc_ge_lin_filt, aes(x = TPM, y = Score) )+
+  # facet_wrap(~ Drug_Gene_Lin) +
+  geom_point(aes(color = disease_g2p), pch = 20, size = 1, alpha = 0.7) +
+  geom_smooth(stat = "smooth", method = "lm", color = "gray70", fill = "gray88", lwd = 1) +
+  geom_text(data = gdsc_lin_text,
+            mapping = aes(x = +Inf, y = +Inf, label = label,
+            hjust = 1.1, vjust = 1.2)) +
+  scale_y_continuous(breaks = seq(0, 1.00, by = 0.25), labels = c("0.00", "0.25", "0.50", "0.75", "1.00")) +
+  coord_cartesian(ylim = c(0, 1.00)) +
+  scale_color_manual(values = g2p_disease_colors) +
+  labs(title = "GDSC: Lapatinib, ERBB2, breast", x = "Gene expression [log2(TPM)]", y = "AUC") +
+  theme(legend.position = "none",
+        panel.background = element_rect(fill = "azure", colour = "azure", size = 0.5, linetype = "solid"),
+        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
+        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))
+ggsave(plot = gdsc_ge_lin_filt_plot, filename = "./plots/lapatinib_ERBB2_breast_ge_gdsc.png", width = 5, height = 3, units = "in", dpi = "retina", device = "png")
+```
+
+## CN/GE heatmaps
+
+```{r, eval=FALSE}
+ccle_cn_cor <- unfactorize(filter(cn_cor, Dataset == "CCLE" & Gene %in% unique(g2p_amp$Gene)))
+ctrp_cn_cor <- unfactorize(filter(cn_cor, Dataset == "CTRP" & Gene %in% unique(g2p_amp$Gene)))
+gdsc_cn_cor <- unfactorize(filter(cn_cor, Dataset == "GDSC" & Gene %in% unique(g2p_amp$Gene)))
+
+ccle_cn_ht2 <- MakeCorrHeatmap(cor_res = ccle_cn_cor, row_names = TRUE, heatmap_legend = TRUE, col_title = "CCLE", color_range = c(-0.25, 0, 0.25), radius = 0.05, legend_title = "Copy num.
+Pearson correlation", metric = "CN")
+ctrp_cn_ht2 <- MakeCorrHeatmap(cor_res = ctrp_cn_cor, row_names = FALSE, heatmap_legend = FALSE, col_title = "CTRP", color_range = c(-0.25, 0, 0.25), radius = 0.05, legend_title = "Copy num.
+Pearson correlation", metric = "CN")
+gdsc_cn_ht2 <- MakeCorrHeatmap(cor_res = gdsc_cn_cor, row_names = FALSE, heatmap_legend = FALSE, col_title = "GDSC", color_range = c(-0.25, 0, 0.25), radius = 0.05, legend_title = "Copy num.
+Pearson correlation", metric = "CN")
+png(filename = "./plots/sccb_cn_heatmap.png", width = 13, height = 2.7, units = "in", res = 500)
+draw(ccle_cn_ht2 + ctrp_cn_ht2 + gdsc_cn_ht2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
+dev.off()
+
+ccle_ge_cor <- unfactorize(filter(ge_cor, Dataset == "CCLE" & Gene %in% unique(g2p_expr$Gene)))
+ctrp_ge_cor <- unfactorize(filter(ge_cor, Dataset == "CTRP" & Gene %in% unique(g2p_expr$Gene)))
+gdsc_ge_cor <- unfactorize(filter(ge_cor, Dataset == "GDSC" & Gene %in% unique(g2p_expr$Gene)))
+
+ccle_ge_ht2 <- MakeCorrHeatmap(cor_res = ccle_ge_cor, row_names = TRUE, heatmap_legend = TRUE, col_title = "CCLE", color_range = c(-0.5, 0, 0.5), radius = 0.08, legend_title = "Gene expr.
+Pearson correlation", metric = "GE")
+ctrp_ge_ht2 <- MakeCorrHeatmap(cor_res = ctrp_ge_cor, row_names = FALSE, heatmap_legend = FALSE, col_title = "CTRP", color_range = c(-0.5, 0, 0.5), radius = 0.08, legend_title = "Gene expr.
+Pearson correlation", metric = "GE")
+gdsc_ge_ht2 <- MakeCorrHeatmap(cor_res = gdsc_ge_cor, row_names = FALSE, heatmap_legend = FALSE, col_title = "GDSC", color_range = c(-0.5, 0, 0.5), radius = 0.08, legend_title = "Gene expr.
+Pearson correlation", metric = "GE")
+png(filename = "./plots/sccb_ge_heatmap.png", width = 13, height = 2.4, units = "in", res = 500)
+draw(ccle_ge_ht2 + ctrp_ge_ht2 + gdsc_ge_ht2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
+dev.off()
+```
+
+## KS test results
+
+```{r fig.height=3, fig.width=4}
+KSResultPlot <- function(dataframe, color_values, title_text, outfile, p_value, show) {
+  if(p_value == "p") {
+    sample1 <- filter(dataframe, InG2P == "Yes")$p
+    sample2 <- filter(dataframe, InG2P == "No")$p
+  }
+  if(p_value == "CN_p") {
+    sample1 <- filter(dataframe, InG2P == "Yes")$CN_p
+    sample2 <- filter(dataframe, InG2P == "No")$CN_p
+  }
+  if(p_value == "GE_p") {
+    sample1 <- filter(dataframe, InG2P == "Yes")$GE_p
+    sample2 <- filter(dataframe, InG2P == "No")$GE_p
+  }
+  pval <- ks.test(sample1, sample2, alternative = "greater")$p.value
+
+  cdf1 <- ecdf(sample1) 
+  cdf2 <- ecdf(sample2)
+
+  # find min and max statistics to draw line between points of greatest distance
+  minMax <- seq(min(sample1, sample2), max(sample1, sample2), length.out = length(sample1)) 
+  x0 <- minMax[which(abs(cdf1(minMax) - cdf2(minMax)) == max(abs(cdf1(minMax) - cdf2(minMax))))] 
+  y0 <- cdf1(x0) 
+  y1 <- cdf2(x0)
+
+  if(p_value == "p") {
+    ecdf_plot <- ggplot(dataframe, aes(x = p, group = InG2P, color = InG2P))+
+      scale_color_manual(values = color_values) +
+      stat_ecdf(size = 1) +
+      theme_bw(base_size = 18) +
+      theme(legend.position = "top",
+            plot.title = element_text(size = 40)) +
+      geom_vline(xintercept = 0.05, linetype = "dashed", color = "gray", lwd = 0.5) +
+      # annotate(geom = "text", label = paste0("KS test, p = ", round(p_value, digits = 3)), x = 0.18, y = 0.95) +
+      labs(y = "ECDF", x = "P-value", title = paste0(title_text, ", KS test (p = ", round(pval, digits = 3), ")"), color = "In VICC?") +
+      geom_segment(aes(x = x0[1], y = y0[1], xend = x0[1], yend = y1[1]), linetype = "dashed", color = "black") +
+      geom_point(aes(x = x0[1] , y = y0[1]), color = "black", size = 2) +
+      geom_point(aes(x = x0[1] , y = y1[1]), color = "black", size = 2) +
+      coord_cartesian(xlim = c(0, 1))) +
+      theme(legend.position = c(0.95, 0.30), legend.justification = c("right", "top"), legend.box.just = "right", legend.margin = margin(6, 6, 6, 6))
+  }
+  if(p_value == "CN_p") {
+    ecdf_plot <- ggplot(dataframe, aes(x = CN_p, group = InG2P, color = InG2P))+
+      scale_color_manual(values = color_values) +
+      stat_ecdf(size = 1) +
+      theme_bw(base_size = 18) +
+      theme(legend.position = "top",
+            plot.title = element_text(size = 40)) +
+      geom_vline(xintercept = 0.05, linetype = "dashed", color = "gray", lwd = 0.5) +
+      # annotate(geom = "text", label = paste0("KS test, p = ", round(p_value, digits = 3)), x = 0.18, y = 0.95) +
+      labs(y = "ECDF", x = "P-value", title = paste0(title_text, ", KS test (p = ", round(pval, digits = 3), ")"), color = "In VICC?") +
+      geom_segment(aes(x = x0[1], y = y0[1], xend = x0[1], yend = y1[1]), linetype = "dashed", color = "black") +
+      geom_point(aes(x = x0[1] , y = y0[1]), color = "black", size = 2) +
+      geom_point(aes(x = x0[1] , y = y1[1]), color = "black", size = 2) +
+      coord_cartesian(xlim = c(0, 1))) +
+      theme(legend.position = c(0.95, 0.30), legend.justification = c("right", "top"), legend.box.just = "right", legend.margin = margin(6, 6, 6, 6))
+  }
+  if(p_value == "GE_p") {
+    ecdf_plot <- ggplot(dataframe, aes(x = GE_p, group = InG2P, color = InG2P))+
+      scale_color_manual(values = color_values) +
+      stat_ecdf(size = 1) +
+      theme_bw(base_size = 18) +
+      theme(legend.position = "top",
+            plot.title = element_text(size = 40)) +
+      geom_vline(xintercept = 0.05, linetype = "dashed", color = "gray", lwd = 0.5) +
+      # annotate(geom = "text", label = paste0("KS test, p = ", round(p_value, digits = 3)), x = 0.18, y = 0.95) +
+      labs(y = "ECDF", x = "P-value", title = paste0(title_text, ", KS test (p = ", round(pval, digits = 3), ")"), color = "In VICC?") +
+      geom_segment(aes(x = x0[1], y = y0[1], xend = x0[1], yend = y1[1]), linetype = "dashed", color = "black") +
+      geom_point(aes(x = x0[1] , y = y0[1]), color = "black", size = 2) +
+      geom_point(aes(x = x0[1] , y = y1[1]), color = "black", size = 2) +
+      coord_cartesian(xlim = c(0, 1))) +
+      theme(legend.position = c(0.95, 0.30), legend.justification = c("right", "top"), legend.box.just = "right", legend.margin = margin(6, 6, 6, 6))
+  }
+
+  if(!missing(outfile)) {
+    ggsave(plot = ecdf_plot, filename = outfile, width = 8, height = 5, units = "in", dpi = "retina", device = "png")
+  }
+
+  if(show) {
+    return(ecdf_plot)
+  }
+}
+```
+
+Mutation:
+```{r, eval=FALSE}
+ccle_mut_ht_dat <- filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3)
+ctrp_mut_ht_dat <-filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3)
+gdsc_mut_ht_dat <- filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3)
+
+# ks.test(filter(ccle_mut_ht_dat, InG2P == "Yes")$p, filter(ccle_mut_ht_dat, InG2P == "No")$p, alternative = "greater")
+# ks.test(filter(ctrp_mut_ht_dat, InG2P == "Yes")$p, filter(ctrp_mut_ht_dat, InG2P == "No")$p, alternative = "greater")
+# ks.test(filter(gdsc_mut_ht_dat, InG2P == "Yes")$p, filter(gdsc_mut_ht_dat, InG2P == "No")$p, alternative = "greater")
+
+KSResultPlot(dataframe = ccle_mut_ht_dat, color_values = c("Yes" = "springgreen4" , "No" = "palegreen3"), title_text = "CCLE", p_value = "p", outfile = "./plots/ks_test_results/ccle_mutation.png", show = TRUE)
+KSResultPlot(dataframe = ctrp_mut_ht_dat, color_values = c("Yes" = "steelblue4" , "No" = "slategray3"), title_text = "CTRP", p_value = "p", outfile = "./plots/ks_test_results/ctrp_mutation.png", show = TRUE)
+KSResultPlot(dataframe = gdsc_mut_ht_dat, color_values = c("Yes" = "turquoise4", "No" = "paleturquoise3"), title_text = "GDSC", p_value = "p", outfile = "./plots/ks_test_results/gdsc_mutation.png", show = TRUE)
+```
+
+Protein:
+```{r, eval=FALSE}
+# ks.test(filter(ccle_signif_prot_4plot, InG2P == "Yes")$p, filter(ccle_signif_prot_4plot, InG2P == "No")$p, alternative = "less")
+# ks.test(filter(ctrp_signif_prot_4plot, InG2P == "Yes")$p, filter(ctrp_signif_prot_4plot, InG2P == "No")$p, alternative = "less")
+# ks.test(filter(gdsc_signif_prot_4plot, InG2P == "Yes")$p, filter(gdsc_signif_prot_4plot, InG2P == "No")$p, alternative = "less")
+
+KSResultPlot(dataframe = ccle_mut_ht_dat, color_values = c("Yes" = "springgreen4" , "No" = "palegreen3"), title_text = "CCLE", p_value = "p", outfile = "./plots/ks_test_results/ccle_protein.png", show = TRUE)
+KSResultPlot(dataframe = ctrp_mut_ht_dat, color_values = c("Yes" = "steelblue4" , "No" = "slategray3"), title_text = "CTRP", p_value = "p", outfile = "./plots/ks_test_results/ctrp_protein.png", show = TRUE)
+KSResultPlot(dataframe = gdsc_mut_ht_dat, color_values = c("Yes" = "turquoise4", "No" = "paleturquoise3"), title_text = "GDSC", p_value = "p", outfile = "./plots/ks_test_results/gdsc_protein.png", show = TRUE)
+```
+
+CN/GE:
+```{r, eval=FALSE}
+# cn_genes <- unique(filter(cn_cor, Dataset != "CRISPR" & InG2P == "Yes")$Gene)
+ccle_cn_ht_data <- filter(cn_cor, Dataset == "CCLE" & Gene %in% g2p_amp$Gene)
+ctrp_cn_ht_data <- filter(cn_cor, Dataset == "CTRP" & Gene %in% g2p_amp$Gene)
+gdsc_cn_ht_data <- filter(cn_cor, Dataset == "GDSC" & Gene %in% g2p_amp$Gene)
+
+# ks.test(filter(ccle_cn_ht_data, InG2P == "Yes")$CN_p, filter(ccle_cn_ht_data, InG2P == "No")$CN_p, alternative = "greater")
+# ks.test(filter(ctrp_cn_ht_data, InG2P == "Yes")$CN_p, filter(ctrp_cn_ht_data, InG2P == "No")$CN_p, alternative = "greater")
+# ks.test(filter(gdsc_cn_ht_data, InG2P == "Yes")$CN_p, filter(gdsc_cn_ht_data, InG2P == "No")$CN_p, alternative = "greater")
+
+KSResultPlot(dataframe = ccle_cn_ht_data, color_values = c("Yes" = "springgreen4" , "No" = "palegreen3"), title_text = "CCLE", p_value = "CN_p", outfile = "./plots/ks_test_results/ccle_copynumber.png", show = TRUE)
+KSResultPlot(dataframe = ctrp_cn_ht_data, color_values = c("Yes" = "steelblue4" , "No" = "slategray3"), title_text = "CTRP", p_value = "CN_p", outfile = "./plots/ks_test_results/ctrp_copynumber.png", show = TRUE)
+KSResultPlot(dataframe = gdsc_cn_ht_data, color_values = c("Yes" = "turquoise4", "No" = "paleturquoise3"), title_text = "GDSC", p_value = "CN_p", outfile = "./plots/ks_test_results/gdsc_copynumber.png", show = TRUE)
+
+# ge_genes <- unique(filter(ge_cor, Dataset != "CRISPR" & InG2P == "Yes")$Gene)
+ccle_ge_ht_data <- filter(ge_cor, Dataset == "CCLE" & Gene %in% g2p_expr$Gene)
+ctrp_ge_ht_data <- filter(ge_cor, Dataset == "CTRP" & Gene %in% g2p_expr$Gene)
+gdsc_ge_ht_data <- filter(ge_cor, Dataset == "GDSC" & Gene %in% g2p_expr$Gene)
+
+# ks.test(filter(ccle_ge_ht_data, InG2P == "Yes")$GE_p, filter(ccle_ge_ht_data, InG2P == "No")$GE_p, alternative = "greater")
+# ks.test(filter(ctrp_ge_ht_data, InG2P == "Yes")$GE_p, filter(ctrp_ge_ht_data, InG2P == "No")$GE_p, alternative = "greater")
+# ks.test(filter(gdsc_ge_ht_data, InG2P == "Yes")$GE_p, filter(gdsc_ge_ht_data, InG2P == "No")$GE_p, alternative = "greater")
+
+KSResultPlot(dataframe = ccle_ge_ht_data, color_values = c("Yes" = "springgreen4" , "No" = "palegreen3"), title_text = "CCLE", p_value = "GE_p", outfile = "./plots/ks_test_results/ccle_geneexpression.png", show = TRUE)
+KSResultPlot(dataframe = ctrp_ge_ht_data, color_values = c("Yes" = "steelblue4" , "No" = "slategray3"), title_text = "CTRP", p_value = "GE_p", outfile = "./plots/ks_test_results/ctrp_geneexpression.png", show = TRUE)
+KSResultPlot(dataframe = gdsc_ge_ht_data, color_values = c("Yes" = "turquoise4", "No" = "paleturquoise3"), title_text = "GDSC", p_value = "GE_p", outfile = "./plots/ks_test_results/gdsc_geneexpression.png", show = TRUE)
+
+# cn_genes <- unique(filter(cn_cor, Dataset != "CRISPR" & InG2P == "Yes")$Gene)
+# cn_drugs <- unique(filter(cn_cor, Dataset != "CRISPR" & InG2P == "Yes")$Drug)
+# 
+# ccle_cn_ht_data <- filter(cn_cor, Dataset == "CCLE" & Drug %in% cn_drugs & Gene %in% cn_genes)
+# ks.test(filter(ccle_cn_ht_data, InG2P == "Yes")$CN_p, filter(ccle_cn_ht_data, InG2P == "No")$CN_p)
+# ctrp_cn_ht_data <- filter(cn_cor, Dataset == "CTRP" & Drug %in% cn_drugs & Gene %in% cn_genes)
+# ks.test(filter(ctrp_cn_ht_data, InG2P == "Yes")$CN_p, filter(ctrp_cn_ht_data, InG2P == "No")$CN_p)
+# gdsc_cn_ht_data <- filter(cn_cor, Dataset == "GDSC" & Drug %in% cn_drugs & Gene %in% cn_genes)
+# ks.test(filter(gdsc_cn_ht_data, InG2P == "Yes")$CN_p, filter(gdsc_cn_ht_data, InG2P == "No")$CN_p)
+# 
+# ge_genes <- unique(filter(ge_cor, Dataset != "CRISPR" & InG2P == "Yes")$Gene)
+# ge_drugs <- unique(filter(ge_cor, Dataset != "CRISPR" & InG2P == "Yes")$Drug)
+# 
+# ccle_ge_ht_data <- filter(ge_cor, Dataset == "CCLE" & Drug %in% ge_drugs & Gene %in% ge_genes)
+# ks.test(filter(ccle_ge_ht_data, InG2P == "Yes")$GE_p, filter(ccle_ge_ht_data, InG2P == "No")$GE_p)
+# ctrp_ge_ht_data <- filter(ge_cor, Dataset == "CTRP" & Drug %in% ge_drugs & Gene %in% ge_genes)
+# ks.test(filter(ctrp_ge_ht_data, InG2P == "Yes")$GE_p, filter(ctrp_ge_ht_data, InG2P == "No")$GE_p)
+# gdsc_ge_ht_data <- filter(ge_cor, Dataset == "GDSC" & Drug %in% ge_drugs & Gene %in% ge_genes)
+# ks.test(filter(gdsc_ge_ht_data, InG2P == "Yes")$GE_p, filter(gdsc_ge_ht_data, InG2P == "No")$GE_p)
+```
+
+Lineage:
+```{r lineages_ks_tests, warning=FALSE}
+ks.test(filter(ccle_signif_dgl, disease %in% g2p_diseases & InG2P == "Yes")$p, filter(ccle_signif_dgl, disease %in% g2p_diseases & InG2P == "No")$p, alternative = "greater")$p.value
+ks.test(filter(ctrp_signif_dgl, disease %in% g2p_diseases & InG2P == "Yes")$p, filter(ctrp_signif_dgl, disease %in% g2p_diseases & InG2P == "No")$p, alternative = "greater")$p.value
+ks.test(filter(gdsc_signif_dgl, disease %in% g2p_diseases & InG2P == "Yes")$p, filter(gdsc_signif_dgl, disease %in% g2p_diseases & InG2P == "No")$p, alternative = "greater")$p.value
+
+# ccle_signif_dgl_filt <- filter(ccle_signif_dgl, disease %in% g2p_diseases)
+# KSResultPlot(dataframe = ,ccle_signif_dgl_filt, color_values = c("Yes" = "springgreen4" , "No" = "palegreen3"), title_text = "CCLE", p_value = "p", outfile = "./plots/ks_test_results/ccle_mut_lin.png", show = TRUE)
+# KSResultPlot(dataframe = filter(ctrp_signif_dgl, disease %in% g2p_diseases), color_values = c("Yes" = "steelblue4" , "No" = "slategray3"), title_text = "CTRP", p_value = "p", outfile = "./plots/ks_test_results/ctrp_mut_lin.png", show = TRUE)
+# KSResultPlot(dataframe = filter(gdsc_signif_dgl, disease %in% g2p_diseases), color_values = c("Yes" = "turquoise4", "No" = "paleturquoise3"), title_text = "GDSC", p_value = "p", outfile = "./plots/ks_test_results/gdsc_mut_lin.png", show = TRUE)
+#
+
+ks.test(filter(ccle_signif_prot_lin, disease %in% g2p_diseases & InG2P == "Yes")$p, filter(ccle_signif_prot_lin, disease %in% g2p_diseases & InG2P == "No")$p, alternative = "greater")$p.value
+ks.test(filter(ctrp_signif_prot_lin, disease %in% g2p_diseases & InG2P == "Yes")$p, filter(ctrp_signif_prot_lin, disease %in% g2p_diseases & InG2P == "No")$p, alternative = "greater")$p.value
+ks.test(filter(gdsc_signif_prot_lin, disease %in% g2p_diseases & InG2P == "Yes")$p, filter(gdsc_signif_prot_lin, disease %in% g2p_diseases & InG2P == "No")$p, alternative = "greater")$p.value
+
+ks.test(filter(cn_cor_lin, Dataset == "CCLE" & disease %in% g2p_diseases & InG2P == "Yes")$CN_p, filter(cn_cor_lin, Dataset == "CCLE" & disease %in% g2p_diseases & InG2P == "No")$CN_p, alternative = "greater")$p.value
+ks.test(filter(cn_cor_lin, Dataset == "CTRP" & disease %in% g2p_diseases & InG2P == "Yes")$CN_p, filter(cn_cor_lin, Dataset == "CTRP" & disease %in% g2p_diseases & InG2P == "No")$CN_p, alternative = "greater")$p.value
+ks.test(filter(cn_cor_lin, Dataset == "GDSC" & disease %in% g2p_diseases & InG2P == "Yes")$CN_p, filter(cn_cor_lin, Dataset == "GDSC" & disease %in% g2p_diseases & InG2P == "No")$CN_p, alternative = "greater")$p.value
+
+ks.test(filter(ge_cor_lin, Dataset == "CCLE" & disease %in% g2p_diseases & InG2P == "Yes")$GE_p, filter(ge_cor_lin, Dataset == "CCLE" & disease %in% g2p_diseases & InG2P == "No")$GE_p, alternative = "greater")$p.value
+ks.test(filter(ge_cor_lin, Dataset == "CTRP" & disease %in% g2p_diseases & InG2P == "Yes")$GE_p, filter(ge_cor_lin, Dataset == "CTRP" & disease %in% g2p_diseases & InG2P == "No")$GE_p, alternative = "greater")$p.value
+ks.test(filter(ge_cor_lin, Dataset == "GDSC" & disease %in% g2p_diseases & InG2P == "Yes")$GE_p, filter(ge_cor_lin, Dataset == "GDSC" & disease %in% g2p_diseases & InG2P == "No")$GE_p, alternative = "greater")$p.value
+
+lineage_ks_results <- data.frame("Dataset" = c(rep(c("CCLE", "CTRP", "GDSC"), 4)),
+           "Data type" = c(rep("Mutation", 3), rep("Protein change", 3), rep("Copy number", 3), rep("Gene expression", 3)),
+  "p.value" = c(ks.test(filter(ccle_signif_dgl, InG2P == "Yes")$p, filter(ccle_signif_dgl, InG2P == "No")$p)$p.value,
+  ks.test(filter(ctrp_signif_dgl, InG2P == "Yes")$p, filter(ctrp_signif_dgl, InG2P == "No")$p)$p.value,
+  ks.test(filter(gdsc_signif_dgl, InG2P == "Yes")$p, filter(gdsc_signif_dgl, InG2P == "No")$p)$p.value,
+  ks.test(filter(ccle_signif_prot_lin, InG2P == "Yes")$p, filter(ccle_signif_prot_lin, InG2P == "No")$p)$p.value,
+  ks.test(filter(ctrp_signif_prot_lin, InG2P == "Yes")$p, filter(ctrp_signif_prot_lin, InG2P == "No")$p)$p.value,
+  ks.test(filter(gdsc_signif_prot_lin, InG2P == "Yes")$p, filter(gdsc_signif_prot_lin, InG2P == "No")$p)$p.value,
+  ks.test(filter(cn_cor_lin, Dataset == "CCLE" & InG2P == "Yes")$CN_p, filter(cn_cor_lin, Dataset == "CCLE" & InG2P == "No")$CN_p)$p.value,
+  ks.test(filter(cn_cor_lin, Dataset == "CTRP" & InG2P == "Yes")$CN_p, filter(cn_cor_lin, Dataset == "CTRP" & InG2P == "No")$CN_p)$p.value,
+  ks.test(filter(cn_cor_lin, Dataset == "GDSC" & InG2P == "Yes")$CN_p, filter(cn_cor_lin, Dataset == "GDSC" & InG2P == "No")$CN_p)$p.value,
+  ks.test(filter(ge_cor_lin, Dataset == "CCLE" & InG2P == "Yes")$GE_p, filter(ge_cor_lin, Dataset == "CCLE" & InG2P == "No")$GE_p)$p.value,
+  ks.test(filter(ge_cor_lin, Dataset == "CTRP" & InG2P == "Yes")$GE_p, filter(ge_cor_lin, Dataset == "CTRP" & InG2P == "No")$GE_p)$p.value,
+  ks.test(filter(ge_cor_lin, Dataset == "GDSC" & InG2P == "Yes")$GE_p, filter(ge_cor_lin, Dataset == "GDSC" & InG2P == "No")$GE_p)$p.value))
+```
+
+# OLD CODE
+
+--------------------------------------------------------------------------------
 
@@
 
-# OLD CODE
-
---------------------------------------------------------------------------------
-
 ## Clustered AUC heatmap

### 2020-01-14 19Q2.Rmd

@@
 
-```{r pancan_ks_res}
+```{r pancan_ks_res, eval=FALSE}
 pancan_ks_results <- data.frame("Dataset" = c(rep(c("CCLE", "CTRP", "GDSC"), 4)),
@@
 test3 <- filter(cn_cor, Gene == "MET" & InG2P == "Yes")
+
+test <- filter(ge_cor_lin, Drug != "CRISPR" & InG2P == "Yes")
+test2 <- filter(cn_cor_lin, Drug != "CRISPR" & InG2P == "Yes")
 ```
